### 2020-07-20 PANCHANGE_descriptives2020-07-14.Rmd
add PANCHANGE scripts for data preprocessing and descriptives

---
title: "PANCHANGE_data_preprocessing"
author: "Katie Thompson, Topher Huebel, Molly Davies, Kirstin Purves"
date: "14/07/2020"
output:  
  html_document:
    df_print: paged
    toc: yes
    toc_depth: 2
    toc_float:
      collapsed: false
    number_sections: false
    highlight: monochrome
    theme: cerulean
code_folding: show

html_notebook:
  theme: cerulean
toc: yes
---

This will be the master script to run all analyses for the project "Anxiety, depression and trauma symptom change during the COVID-19 pandemic: retrospective versus objective assessment" - Young et al (2020)

Script written by K Purves, K Thompson, C Huebel and M Davies.
Email: kirstin.purves@kcl.ac.uk, katie.thompson@kcl.ac.uk, christopher.1.huebel@kcl.ac.uk, molly.davies@kcl.ac.uk

#Set up
Set up the Rmarkdown
+++CH: Add packages for the setup
```{r Setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      comment=NA,
                      prompt=FALSE,
                      cache=FALSE)

options(bitmapType = 'quartz') # to render fonts better
```

Clear global environment
```{r Clear global environment}
remove(list = ls())
```

Retrieve the current date
to use it for file endings to not overwrite files when one exports files
```{r Recent date}
date = Sys.Date()
```

#Packages
Install packages (if they are not available in your version of R)
```{r Installing packages}
#install.packages("summarytools")
#install.packages("tidyverse")
#install.packages("psych")
```

Load packages
```{r Load packages}
library(knitr)
library(summarytools)
library(tidyverse)
library(psych)
```

# Colour palettes
Define colours for plotting this are the standard coping colours
+++CH: Is there a document in which these colours are defined?
```{r Colour palettes: COPING}
COPINGpalette2 <- c("#78D9C5",
                    "#F5BE5E")

COPINGpalette3 <- c("#78D9C5",
                    "#F5BE5E",
                    "#EEB6E9")

COPINGpalette4 <- c("#78D9C5",
                    "#F5BE5E",
                    "#EEB6E9",
                    "#DBDB73")

COPINGpalette5 <- c("#78D9C5",
                    "#F5BE5E",
                    "#EEB6E9",
                    "#DBDB73", 
                    "#FFED98")

COPINGpalette6 <- c("#78D9C5",
                    "#F5BE5E",
                    "#EEB6E9",
                    "#DBDB73",
                    "#FFED98",
                    "#BFD2EB")

COPINGpalette7 <- c("#78D9C5",
                    "#F5BE5E",
                    "#EEB6E9",
                    "#DBDB73", 
                    "#FFED98",
                    "#BFD2EB", 
                    "#808080")

COPINGpaletteGRAD <- c("#F5BE5E",
                       "#FFD284",
                       "#FFEED1",
                       "#B5B5B5",
                       "#DEFFF8",
                       "#94F6E1",
                       "#78D9C5")

COPINGNeuCenterpalette <- c("#78D9C5",
                            "#808080",
                            "#F5BE5E")

RAMPworseGRADpalette <- c("#78D9C5",
                          "#FFEED1",
                          "#F5BE5E",
                          "#FFB1B5")
GLADpalette = c("#efc00b", 
                "#b7dee8")  
```

Choose in this chunk which palette to use
04.07.2020 - Default to 2 colour COPING palette
```{r Choose colour palette}
palette=COPINGpalette2
```

#Stratify descriptives by mental health diagnosis
 *convert diagnostic columns from wide to long format*
 +++CH: May not be necessary if the data is already in long form
```{r COVID change to long format}
###ADAPT TO CORRECT VARIABLE NAMES
dat.long <- dat.wide %>%
  gather(key = "time", value = "score", all_of(PHQ.variables)) %>% #this will be all diagnostic variables
  convert_as_factor(ID, time)
```

## Disorders - Frequencies *use this as example to convert chunk above*
```{r Disorders - Frequencies}
#0 = No to disorder; 1 = Yes to disorder
PMAD_na_drop_Dx %>%
  select(ID, #need to add columns for which you want summaries for - ASK GB & KY what they want in descriptives table
         dem.sex,
         starts_with("mhd.") & ends_with("numeric")) %>%
  gather(
    key = "Disorder",
    value = "Diagnosis",
    mhd.MDD_numeric:mhd.ADHD_numeric #all the columns that we want to be gathered
  ) %>%
  group_by(Disorder) %>%
  count(Diagnosis) #count for diagnoses
```

Calculate the time difference between the sign up month (GLAD) and pandemic measures (COPING)
***KT: NEED TO HAVE START DATE IN DATASET TO RUN THESE
```{r time difference between GLAD and COPING completion KATIE}
##IGNORE - only for testing if the date formats work 
dat <- ramp.dem.raw #start date has been removed so had to test it this way
dat$test.date <- as.POSIXct("2020-05-15")

#change naming of variables here based on what we decide for "startDate"
dat$date.diff.glad <- round( 
                      difftime(           #this function does time1 - time2 as difftime(time1, time2...)
                        dat$test.date,    #should be start date for COPING (time1)
                        dat$startDate,    #should be start date for GLAD (time2)
                        units = c("days"  #can also be "secs", "mins", "hours", "weeks"
                                  ))) 
freq(dat$date_diff.glad)        
```

Calculate the time difference between the sign up month (EDGI) and pandemic measures (COPING)
```{r time difference between EDGI and COPING completion KATIE}
#change naming of variables here based on what we decide for "startDate"
dat$date.diff.edgi <- round( 
                      difftime(           #this function does time1 - time2 as difftime(time1, time2...)
                        dat$test.date,    #should be start date for COPING (time1)
                        dat$startDate,    #should be start date for EDGI (time2)
                        units = c("days"  #can also be "secs", "mins", "hours", "weeks"
                                  ))) 
freq(dat$date_diff.edgi)      
```

Compare the GLAD/EDGI and COPING cohorts as a whole
+++CH: Diagnosis, ethnicity, gender, 
+++MD: May not be possible for NBR; potentially send them code to run it for us
```{r}

```

Descriptives for reporting: "How different are these feelings to how you felt before the pandemic?’ on a 5-point scale (much worse, a little worse, no different, a little better, much better)."
+++KLP: Discuss during the meeting if we use 3 or 5 categories
```{r}

```

##Calculate difference pre and baseline
For individuals who have objective scores for GAD, PHQ and PCL. Subtract the baseline from the pre pandemic. Plot this distribution. If they have a higher score at baseline than pre-pandemic, the difference would be positive and would indicate that the participant got worse.

```{r COVID calculate the difference between pre and post}

```

Replicate chunk above for retrospective reports. This will only be for people who say that have reported that there is a change in their scores. 
*Discuss if we should include people who reported "no change" as repition of their current GAD, PHQ, PCL report*
```{r}

```

### 2020-07-20 PANCHANGE_data_preprocessing2020-07-15.Rmd

---
title: "PANCHANGE_data_preprocessing"
author: "Katie Thompson, Topher Huebel, Molly Davies, Kirstin Purves"
date: "03/07/2020"
output:  
  html_document:
    df_print: paged
    toc: yes
    toc_depth: 2
    toc_float:
      collapsed: false
    number_sections: false
    highlight: monochrome
    theme: cerulean
code_folding: show

html_notebook:
  theme: cerulean
toc: yes

params:
  glad.dem.raw: edgi.dem.raw

---

This will be the master script to run all analyses for the project "Anxiety, depression and trauma symptom change during the COVID-19 pandemic: retrospective versus objective assessment" - Young et al (2020)

Script written by K Purves, K Thompson, C Huebel and M Davies.
Email: kirstin.purves@kcl.ac.uk, katie.thompson@kcl.ac.uk, christopher.1.huebel@kcl.ac.uk, molly.davies@kcl.ac.uk

#Set up
```{r Setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      comment=NA,
                      prompt=FALSE,
                      cache=FALSE)

options(bitmapType = 'quartz') # to render fonts better
```

Clear global environment
```{r Clear global environment}
remove(list = ls())
```

Retrieve the current date
to use it for file endings to not overwrite files when one exports files
```{r Recent date}
date = Sys.Date()
```

#Packages
Install packages (if they are not available in your version of R)
```{r Installing packages}
#install.packages("summarytools")
#install.packages("tidyverse")
#install.packages("psych")
```

Load packages
```{r Load packages}
library(knitr)
library(summarytools)
library(tidyverse)
library(psych)
```

# Colour palettes
Define colours for plotting this are the standard coping colours
+++CH: Is there a document in which these colours are defined?
```{r Colour palettes: COPING}
COPINGpalette2 <- c("#78D9C5",
                    "#F5BE5E")

COPINGpalette3 <- c("#78D9C5",
                    "#F5BE5E",
                    "#EEB6E9")

COPINGpalette4 <- c("#78D9C5",
                    "#F5BE5E",
                    "#EEB6E9",
                    "#DBDB73")

COPINGpalette5 <- c("#78D9C5",
                    "#F5BE5E",
                    "#EEB6E9",
                    "#DBDB73", 
                    "#FFED98")

COPINGpalette6 <- c("#78D9C5",
                    "#F5BE5E",
                    "#EEB6E9",
                    "#DBDB73",
                    "#FFED98",
                    "#BFD2EB")

COPINGpalette7 <- c("#78D9C5",
                    "#F5BE5E",
                    "#EEB6E9",
                    "#DBDB73", 
                    "#FFED98",
                    "#BFD2EB", 
                    "#808080")

COPINGpaletteGRAD <- c("#F5BE5E",
                       "#FFD284",
                       "#FFEED1",
                       "#B5B5B5",
                       "#DEFFF8",
                       "#94F6E1",
                       "#78D9C5")

COPINGNeuCenterpalette <- c("#78D9C5",
                            "#808080",
                            "#F5BE5E")

RAMPworseGRADpalette <- c("#78D9C5",
                          "#FFEED1",
                          "#F5BE5E",
                          "#FFB1B5")
GLADpalette = c("#efc00b", 
                "#b7dee8")  
```

Choose in this chunk which palette to use
04.07.2020 - Default to 2 colour COPING palette
```{r Choose colour palette}
palette=COPINGpalette2
```

# Data import and merging
+++CH04-07-20: I have added all read-ins of the data. How will the coping data be stored? -> Question for Yuhao
+++CH04-07-20: We need to discuss the naming of the variables PHQ9 vs phq
+++CH04-07-20: We need to discuss the naming of the variables .0 vs .retro

GLAD only receives current measures and RAMP questionnaire

All COPING surveys are separate surveys
+++TOPHER
***
++KT: Need to make sure that the startDate's for each survey are coded accordingly, e.g. startDate.glad, startDate.coping, startDate.RAMP. Otherwise people who are in both GLAD and COPING will have two dates.
+++CH: I have added this

## GLAD demographics
# Read in data
```{r glad dem cols}
glad.dem.raw <- readRDS(file = "../data_raw/glad/dem_glad.rds")
dim(glad.dem.raw)
colnames(glad.dem.raw)
```

# Select variables
```{r glad dem cleaning}
glad.dem.raw.id.unclean <- glad.dem.raw %>%
  drop_na(externalDataReference) %>% # Drop NAs
  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
  mutate(ID = as.numeric(ID),
         startDate.glad = startDate) %>% # Rename startDate
  select(
         Sample, # Sample
         ID, # ID
         startDate.glad, #Date when participant signed up to glad
         Age_raw = dem.how_old_are_you_now, # Age
         Gender = dem.which_gender_do_you_identify_with, # Gender
         Sex = dem.select_questionnaire_items_medical, #Sex
         EduYrs = dem.school_education_school_years, # Years in education
         dem.college_or_university_degree_numeric, # level of education - univeristy
         dem.a_levelsas_levels_or_equivalent_numeric, # level of education - alevel
         dem.o_levelsgcses_or_equivalent_numeric, # level of education - gcse
         dem.cses_or_equivalent_numeric, # level of education - cse
         dem.nvq_or_hnd_or_hnc_or_equivalent_numeric, # level of education - nvq
         Ethnicity = dem.questions_based_ethnic_origin # Ethnicity
         ) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

# Inspect dimensions
dim(glad.dem.raw.id.unclean)
# Inspect colnames
colnames(glad.dem.raw.id.unclean)
#Differences
dim(glad.dem.raw)[1]-dim(glad.dem.raw.id.unclean)[1]
```

Clean Age variable
Age outlier
```{r age outlier}
# define age limits 
age_upper_limit = 117 # oldest person in the world is 117 years
age_lower_limit = 16

# identify number of outliers
length(
  which(
  glad.dem.raw.id.unclean$Age_raw > age_upper_limit |
    glad.dem.raw.id.unclean$Age_raw < age_lower_limit
     )
)

# remove age outliers
glad.dem.raw.id <- glad.dem.raw.id.unclean %>%
  mutate(
    Age = 
      if_else(
        Age_raw > age_upper_limit | 
        Age_raw < age_lower_limit, 
        true = NA_real_,
        false = Age_raw,
        missing = NA_real_
      )
  )

# Inspect colnames
colnames(glad.dem.raw.id)
```

# Categorise age into groups 
In RAMP, age is indicated categorically: 16-18, 19-25, 26-35, 36-45, 46-55, 56-65, 66-70, 71-75, 76-80, 81-85, 86-90, 91-100, 100+
Age categories in GLAD, EDGI and NBR have been created to reflect this
```{r Age groups}
#if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE ) {

# Create categorical age groups per 10 years
glad.dem.raw.id <- glad.dem.raw.id %>%
  mutate(
    age_category_numeric =
      case_when(
          Age >= 16 & Age <= 18 ~ "1",
          Age >= 19 & Age <= 25 ~ "2",
          Age >= 26 & Age <= 35 ~ "3",
          Age >= 36 & Age <= 45 ~ "4",
          Age >= 46 & Age <= 55 ~ "5",
          Age >= 56 & Age <= 65 ~ "6",
          Age >= 66 & Age <= 70 ~ "7",
          Age >= 71 & Age <= 75 ~ "8",
          Age >= 76 & Age <= 80 ~ "9",
          Age >= 81 & Age <= 85 ~ "10",
          Age >= 86 & Age <= 90 ~ "11",
          Age >= 91 & Age <= 100 ~ "12",
          Age >= 101 & Age <= 120 ~ "13" # oldest person in the world is 117 years
                )
      )

glad.dem.raw.id <- glad.dem.raw.id %>%
    mutate(
      age_category =
        recode_factor(
          age_category_numeric, 
          "1" = "16 to 18 years",
          "2" = "19 to 25 years",
          "3" = "26 to 35 years",
          "4" = "36 to 45 years",
          "5" = "46 to 55 years",
          "6" = "56 to 65 years",
          "7" = "66 to 70 years",
          "8" = "71 to 75 years",
          "9" = "76 to 80 years",
          "10" = "81 to 85 years",
          "11" = "86 to 90 years",
          "12" = "91 to 100 years",
          "13" = "Above 100 years"
          )
    )

glad.dem.raw.id %>%
  freq(age_category)

#}
```

# Highest education
Proceed along qualifications fields. If field is not blank, take that as highest qual. If field is blank, check next field. If all fields are blank, NA
Assumes University degree > A level > NVQ > GCSE/O Level/CSE
```{r Highest education}
#create numeric version of the highest education variable
glad.dem.raw.id <- glad.dem.raw.id %>%
  mutate(
    highest_education_numeric =
      case_when(
        dem.college_or_university_degree_numeric == "1" ~ 4,
        dem.a_levelsas_levels_or_equivalent_numeric == "1" ~ 3,
        dem.nvq_or_hnd_or_hnc_or_equivalent_numeric == "1" ~ 2,
        dem.o_levelsgcses_or_equivalent_numeric == "1" ~ 1,
        dem.cses_or_equivalent_numeric == "1" ~ 1)
    )

#recode the numeric version into a factor
glad.dem.raw.id <- glad.dem.raw.id %>%
  mutate(
    highest_education =
      recode_factor(
        highest_education_numeric,
        `1` = "GCSE/CSE",
        `2` = "NVQ",
        `3` = "A-levels",
        `4` = "University")
    )

glad.dem.raw.id %>%
  freq(highest_education)
```

Check highest education coding
```{r Highest education check}
glad.dem.raw.id %>%
  select(highest_education,
        dem.college_or_university_degree_numeric,
        dem.a_levelsas_levels_or_equivalent_numeric,
        dem.nvq_or_hnd_or_hnc_or_equivalent_numeric,
        dem.o_levelsgcses_or_equivalent_numeric,
        dem.cses_or_equivalent_numeric
  )
```

```{r glad dem head}
head(glad.dem.raw.id)
```
++KT: The age variable here needs to be cleaned - have added a chunk above (before age grouping) for this. Before: min = -55 and max = 290. 
```{r glad dem summary}
summarytools::dfSummary(
  glad.dem.raw.id,
  graph.col = F,
  valid.col = F,
  labels.col = F)
```

# glad gad

```{r glad gad cols}
glad.gad.raw <- readRDS(file = "../data_raw/glad/gad_glad.rds")
dim(glad.gad.raw)
colnames(glad.gad.raw)
```

```{r glad gad cleaning}
glad.gad.raw.id <- glad.gad.raw %>%
  drop_na(externalDataReference) %>% # Drop NAs
  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
  mutate(ID = as.numeric(ID),
         startDate.glad = startDate) %>% # Rename startDate
  select(
    Sample, # Sample
    ID, # ID
    gad.feeling_nervous_anxious_or_on_edge_prepan = gad.feeling_nervous_anxious_or_on_edge,
    gad.control_worrying_stop_prepan = gad.control_worrying_stop,
    gad.worrying_too_much_about_different_things_prepan = gad.worrying_too_much_about_different_things,
    gad.trouble_relaxing_prepan = gad.trouble_relaxing,
    gad.sit_restless_hard_prepan = gad.sit_restless_hard,
    gad.becoming_easily_annoyed_or_irritable_prepan = gad.becoming_easily_annoyed_or_irritable,
    gad.awful_feeling_afraid_happen_prepan = gad.awful_feeling_afraid_happen,
    gad.feeling_nervous_anxious_or_on_edge_prepan_numeric = gad.feeling_nervous_anxious_or_on_edge_numeric,
    gad.control_worrying_stop_prepan_numeric = gad.control_worrying_stop_numeric,
    gad.worrying_too_much_about_different_things_prepan_numeric = gad.worrying_too_much_about_different_things_numeric,
    gad.trouble_relaxing_prepan_numeric = gad.trouble_relaxing_numeric,
    gad.sit_restless_hard_prepan_numeric = gad.sit_restless_hard_numeric,
    gad.becoming_easily_annoyed_or_irritable_prepan_numeric = gad.becoming_easily_annoyed_or_irritable_numeric,
    gad.awful_feeling_afraid_happen_prepan_numeric = gad.awful_feeling_afraid_happen_numeric
  ) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

# Inspect dimensions
dim(glad.gad.raw.id)
# Inspect colnames
colnames(glad.gad.raw.id)
#Differences
dim(glad.gad.raw)[1]-dim(glad.gad.raw.id)[1]
```

Calculate sum score for GAD-7
Max should be 21.
```{r gad sum score prepan}
# Create vector with scoring key: If the item is reversed coded use -1. 
# There needs to be the correct number of values for each item in the questionnaire. 
gad.items_key_prepan <- c(1,1,1,1,1,1,1)

# Create vector with items that are included in total score
gad.items_prepan = c(
  "gad.feeling_nervous_anxious_or_on_edge_prepan_numeric",
  "gad.control_worrying_stop_prepan_numeric",
  "gad.worrying_too_much_about_different_things_prepan_numeric",
  "gad.trouble_relaxing_prepan_numeric",
  "gad.sit_restless_hard_prepan_numeric",
  "gad.becoming_easily_annoyed_or_irritable_prepan_numeric",
  "gad.awful_feeling_afraid_happen_prepan_numeric"
  )

# Calulate total score
gad.scored_items_prepan <- scoreItems(keys = gad.items_key_prepan,
                                        items = glad.gad.raw.id[gad.items_prepan],
                                        totals = TRUE, 
                                        missing = TRUE, 
                                        impute = 'none', 
                                        min = 0, 
                                        max = 3)
# Add in column to tibble
glad.gad.raw.id$gad.sum_score_prepan <- gad.scored_items_prepan$scores

# Look at values
glad.gad.raw.id %>%
  descr(gad.sum_score_prepan,
        stats = "common"
        )
```

```{r glad gad head}
head(glad.gad.raw.id)
```

```{r glad gad summary}
summarytools::dfSummary(
  glad.gad.raw.id,
  graph.col = F,
  valid.col = F,
  labels.col = F)
```

# glad mhq

```{r glad mhq cols}
glad.mhq.raw <- readRDS(file = "../data_raw/glad/mhq_glad.rds")
dim(glad.mhq.raw)
colnames(glad.mhq.raw)
```

```{r glad mhq cleaning}
glad.mhq.raw.id <- glad.mhq.raw %>%
  drop_na(externalDataReference) %>% # Drop NAs
  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
  mutate(ID = as.numeric(ID),
         startDate.glad = startDate) %>% # Rename startDate
  select(
    Sample, # Sample
    ID, # ID
    starts_with("mhq.")
  ) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

# Inspect dimensions
dim(glad.mhq.raw.id)
# Inspect colnames
colnames(glad.mhq.raw.id)
#Differences
dim(glad.mhq.raw)[1]-dim(glad.mhq.raw.id)[1]
```

# Grouping mental health disorders
*#Disorder groupings - from COPING/RAMP analysis minutes*
1. Depressive disorder group: major depression, antenatal/postnatal depression, premenstrual depression.
2. Anxiety group: generalised anxiety, social anxiety, specific phobia, agoraphobia, panic_disorder, panic_attacks. 
3. Agoraphobia and panic_disorder group: panic_disorder, agoraphobia, panic_attacks.
4. Eating disorders group: anorexianervosa, atypical anorexia nervosa, bulimia nervosa, overeating or bingeeating.
5. Obsessive complusive disorders: obsessive compulaive disorder, obsessive compulsive related disorders. 
6. Psychotic disorders: schizophrenia, schizoaffective disorder, general psychosis or psychotic illness. 
7. Personality disorders: cluster A, cluster B, cluster C
8. Control group: no diagnosed disorders.

*Disorders of interest*
MDD and other depressive disorders
Anxiety, nerves or generalised anxiety disorder
Social anxiety 
Specific phobia 
Agoraphobia/panic disorder/panic attacks
OCD (& OCD-related disorders e.g., skin picking?)
PTSD 
Bipolar 
Eating disorders (Anorexia, BE-type EDs) 
Personality disorder: Clusters A, B, and C 
No-diagnosis group

*Analysis plan of Disorders: KY and KP analysis plan*
1. Basic: any anxiety or unipolar depressive disorder vs. those with no prior diagnosis
2. Specific: breakdown by type of prior anxiety (& related) disorder diagnosis
3. Breakdown by COVID or not (using COVIDENCE/Zoe algorithm)

Depressive disorders group
+++CH: NEEDS BETTER LOGIC FOR MALES!!!!
++KT: Sex issue fixed - code has been checked. 407 people with no MDD but have either postnatal/pmdd.
```{r glad mhq depressive_disorders}
glad.mhq.raw.id <- glad.mhq.raw.id %>%
  mutate(
    depressive_disorders_numeric =
      case_when(
        (mhq.depression_numeric == "0" &
        (mhq.pregnancy_depression_numeric == "0" | is.na(mhq.pregnancy_depression_numeric)) & 
        (mhq.premenstrual_dysphoric_disorder_pmdd_numeric == "0" | is.na(mhq.premenstrual_dysphoric_disorder_pmdd_numeric))) ~ 0,
        mhq.depression_numeric == "1" ~ 1,
        mhq.pregnancy_depression_numeric == "1" ~ 1,
        mhq.premenstrual_dysphoric_disorder_pmdd_numeric == "1" ~ 1))

glad.mhq.raw.id <- glad.mhq.raw.id %>%
  mutate(
    depressive_disorders =
      recode_factor(depressive_disorders_numeric,
                    "0" = "No depressive disorder",
                    "1" = "Depressive disorder",
                    missing = NA_character_
                    )
  )

glad.mhq.raw.id %>%
  freq(depressive_disorders)
```

```{r Check depressive_disorders}
glad.mhq.raw.id %>%
  select(
    depressive_disorders,
    depressive_disorders_numeric,
    mhq.depression_numeric,
    mhq.pregnancy_depression_numeric,
    mhq.premenstrual_dysphoric_disorder_pmdd_numeric,
    mhq.depression,
    mhq.pregnancy_depression,
    mhq.premenstrual_dysphoric_disorder_pmdd
  )
```

Anxiety disorders group
```{r glad mhq anxiety_disorders}
glad.mhq.raw.id <- glad.mhq.raw.id %>%
  mutate(
    anxiety_disorders_numeric =
      case_when(
        mhq.anxiety_nerves_or_generalised_anxiety_disorder_numeric == "1" ~ 1,
        mhq.social_anxiety_or_social_phobia_numeric == "1" ~ 1,
        mhq.specific_phobia_e.g._phobia_of_flying_numeric == "1" ~ 1,
        mhq.agoraphobia_numeric == "1" ~ 1,
        mhq.panic_disorder_numeric == "1" ~ 1,
        mhq.panic_attacks_numeric == "1" ~ 1,
        (mhq.anxiety_nerves_or_generalised_anxiety_disorder_numeric == "0" &
        mhq.social_anxiety_or_social_phobia_numeric == "0" &
        mhq.specific_phobia_e.g._phobia_of_flying_numeric == "0" &
        mhq.agoraphobia_numeric == "0" &
        mhq.panic_disorder_numeric == "0" &
        mhq.panic_attacks_numeric == "0") ~ 0
      )
  )

glad.mhq.raw.id <- glad.mhq.raw.id %>%
  mutate(
    anxiety_disorders =
      recode_factor(anxiety_disorders_numeric,
                    "0" = "No anxiety disorder",
                    "1" = "Anxiety disorder",
                    missing = NA_character_
                    )
  )

glad.mhq.raw.id %>%
  freq(anxiety_disorders)
```

```{r Check anxiety_disorders}
glad.mhq.raw.id %>%
  select(
    anxiety_disorders,
    anxiety_disorders_numeric,
    mhq.anxiety_nerves_or_generalised_anxiety_disorder_numeric,
    mhq.social_anxiety_or_social_phobia_numeric,
    mhq.specific_phobia_e.g._phobia_of_flying_numeric,
    mhq.agoraphobia_numeric,
    mhq.panic_disorder_numeric,
    mhq.panic_attacks_numeric,
    mhq.anxiety_nerves_or_generalised_anxiety_disorder,
    mhq.social_anxiety_or_social_phobia,
    mhq.specific_phobia_e.g._phobia_of_flying,
    mhq.agoraphobia,
    mhq.panic_disorder,
    mhq.panic_attacks
  )
```

Agoraphonia and panic disorder group
```{r glad mhq agoraphobia_panic_disorder}
glad.mhq.raw.id <- glad.mhq.raw.id %>%
  mutate(
    agoraphobia_panic_disorder_numeric =
      case_when(
        mhq.agoraphobia_numeric == "1" ~ 1,
        mhq.panic_disorder_numeric == "1" ~ 1,
        mhq.panic_attacks_numeric == "1" ~ 1,
        (mhq.agoraphobia_numeric == "0" &
        mhq.panic_disorder_numeric == "0" &
        mhq.panic_attacks_numeric == "0") ~ 0
      )
  )

glad.mhq.raw.id <- glad.mhq.raw.id %>%
  mutate(
    agoraphobia_panic_disorder =
      recode_factor(agoraphobia_panic_disorder_numeric,
                    "0" = "No agoraphobia/panic disorder",
                    "1" = "Agoraphobia/panic disorder",
                    missing = NA_character_
                    )
  )

glad.mhq.raw.id %>%
  freq(agoraphobia_panic_disorder)
```

```{r Check agoraphobia_panic_disorder}
glad.mhq.raw.id %>%
  select(
    agoraphobia_panic_disorder,
    agoraphobia_panic_disorder_numeric,
    mhq.agoraphobia_numeric,
    mhq.panic_disorder_numeric,
    mhq.panic_attacks_numeric,
    mhq.agoraphobia,
    mhq.panic_disorder,
    mhq.panic_attacks
  )
```
+++CH: Why are there so many NAs in mhq.panic_disorder?
++KT: Added late to questionnaire.

Eating disorders group
```{r glad mhq eating_disorders}
glad.mhq.raw.id <- glad.mhq.raw.id %>%
  mutate(
    eating_disorders_numeric =
      case_when(
        mhq.anorexia_nervosa_numeric == "1" ~ 1,
        mhq.atypical_anorexia_nervosa_numeric == "1" ~ 1,
        mhq.bulimia_nervosa_numeric == "1" ~ 1,
        mhq.psychological_overeating_or_bingeeating_numeric == "1" ~ 1,
        (mhq.anorexia_nervosa_numeric == "0" &
        mhq.atypical_anorexia_nervosa_numeric == "0" &
        mhq.bulimia_nervosa_numeric == "0" &
        mhq.psychological_overeating_or_bingeeating_numeric == "0") ~ 0
      )
  )

glad.mhq.raw.id <- glad.mhq.raw.id %>%
  mutate(
    eating_disorders =
      recode_factor(eating_disorders_numeric,
                    "0" = "No eating disorder",
                    "1" = "Eating disorder",
                    missing = NA_character_
                    )
  )

glad.mhq.raw.id %>%
  freq(eating_disorders)
```

```{r Check eating_disorders}
glad.mhq.raw.id %>%
  select(
    eating_disorders,
    eating_disorders_numeric,
    mhq.anorexia_nervosa_numeric,
    mhq.atypical_anorexia_nervosa_numeric,
    mhq.bulimia_nervosa_numeric,
    mhq.psychological_overeating_or_bingeeating_numeric,
    mhq.anorexia_nervosa,
    mhq.atypical_anorexia_nervosa,
    mhq.bulimia_nervosa,
    mhq.psychological_overeating_or_bingeeating
  )
```

Obsessive compulsive disorders
```{r glad mhq obsessive_compulsive_disorders}
glad.mhq.raw.id <- glad.mhq.raw.id %>%
  mutate(
    obsessive_compulsive_disorders_numeric =
      case_when(
        mhq.obsessivecompulsive_disorder_ocd_numeric == "1" ~ 1,
        mhq.obsessive_compulsive_related_disorders_numeric == "1" ~ 1,
        mhq.body_dysmorphic_disorder_bdd_numeric == "1" ~ 1,
        (mhq.obsessivecompulsive_disorder_ocd_numeric == "0" &
        mhq.obsessive_compulsive_related_disorders_numeric == "0" &
        mhq.body_dysmorphic_disorder_bdd_numeric == "0") ~ 0
      )
  )

glad.mhq.raw.id <- glad.mhq.raw.id %>%
  mutate(
    obsessive_compulsive_disorders =
      recode_factor(obsessive_compulsive_disorders_numeric,
                    "0" = "No obsessivecompulsive disorder",
                    "1" = "Obsessive compulsive disorder",
                    missing = NA_character_
                    )
  )

glad.mhq.raw.id %>%
  freq(obsessive_compulsive_disorders)
```

```{r Check obsessive_compulsive_disorders}
glad.mhq.raw.id %>%
  select(
    obsessive_compulsive_disorders,
    obsessive_compulsive_disorders_numeric,
    mhq.obsessivecompulsive_disorder_ocd,
    mhq.obsessivecompulsive_disorder_ocd_numeric,
    mhq.obsessive_compulsive_related_disorders,
    mhq.obsessive_compulsive_related_disorders_numeric
  )
```

Psychotic disorders group
```{r glad mhq psychotic_disorders}
glad.mhq.raw.id <- glad.mhq.raw.id %>%
  mutate(
    psychotic_disorders_numeric =
      case_when(
        mhq.schizophrenia_numeric == "1" ~ 1,
        mhq.schizoaffective_disorder_numeric == "1" ~ 1,
        mhq.type_psychosis_psychotic_illness_numeric == "1" ~ 1,
        (mhq.schizophrenia_numeric == "0" &
        mhq.schizoaffective_disorder_numeric == "0" &
        mhq.type_psychosis_psychotic_illness_numeric == "0") ~ 0
      )
  )

glad.mhq.raw.id <- glad.mhq.raw.id %>%
  mutate(
    psychotic_disorders =
      recode_factor(psychotic_disorders_numeric,
                    "0" = "No psychotic disorder",
                    "1" = "Psychotic disorder",
                    missing = NA_character_
                    )
  )

glad.mhq.raw.id %>%
  freq(psychotic_disorders)
```

+++CH: Lots of NAs in schizoaffective_disorder 
```{r Check psychotic_disorders}
glad.mhq.raw.id %>%
  select(
    psychotic_disorders,
    psychotic_disorders_numeric,
    mhq.schizophrenia_numeric,
    mhq.schizoaffective_disorder_numeric,
    mhq.type_psychosis_psychotic_illness_numeric,
    mhq.schizophrenia,
    mhq.schizoaffective_disorder,
    mhq.type_psychosis_psychotic_illness
  )
```

Overlap between self-report schizphrenia and bipolar
+++CH: Check overlap between schizophrenia group and bipolar disorder
++KT: Only 63 with comorbid sel-report bipolar and schizophrenia. More likely to have shared symptoms, less likely to have confirmed diagnoses of both. Could be too severe to be in GLAD?
```{r check bipolar overlap with schizophrenia}
glad.mhq.raw.id <- glad.mhq.raw.id %>%
  mutate(
    bipolar_and_schizophrenia_numeric =
      if_else(
        mhq.schizophrenia_numeric == "1" &
          mhq.mania_hypomania_bipolar_or_manicdepression_numeric == "1", 1, 0
      )
  )

glad.mhq.raw.id <- glad.mhq.raw.id %>%
  mutate(
    bipolar_and_schizophrenia =
      recode_factor(bipolar_and_schizophrenia_numeric,
                    "0" = "No comorbid bipoar and schizophrenia",
                    "1" = "Comorbid bipoar and schizophrenia",
                    missing = NA_character_
                    )
  )

glad.mhq.raw.id %>%
  freq(bipolar_and_schizophrenia)
```

Personality disorder groups
++KT: For all cluster coding chunks - have added other clusters as == 0, so that they are not coerced into NAs. 
Cluster A
1. Paranoid                         28 ( 1.0%)
2. Schizoid                         15 ( 0.5%)
3. Schizotypal                      14 ( 0.5%)
```{r glad mhq personality_cluster_a}
glad.mhq.raw.id <- glad.mhq.raw.id %>%
  mutate(
    personality_cluster_a_numeric =
      case_when(
        mhq.personality_disorder_diagnosed_numeric == "1" ~ 1,
        mhq.personality_disorder_diagnosed_numeric == "2" ~ 1,
        mhq.personality_disorder_diagnosed_numeric == "3" ~ 1,
        mhq.personality_disorder_diagnosed_numeric == "4" ~ 0,
        mhq.personality_disorder_diagnosed_numeric == "5" ~ 0,
        mhq.personality_disorder_diagnosed_numeric == "6" ~ 0,
        mhq.personality_disorder_diagnosed_numeric == "7" ~ 0,
        mhq.personality_disorder_diagnosed_numeric == "8" ~ 0,
        mhq.personality_disorder_diagnosed_numeric == "9" ~ 0,
        mhq.personality_disorder_diagnosed_numeric == "10" ~ 0,
        mhq.personality_disorder_numeric == "0" ~ 0
      )
  )

glad.mhq.raw.id <- glad.mhq.raw.id %>%
  mutate(
    personality_cluster_a =
      recode_factor(personality_cluster_a_numeric,
                    "0" = "No personality disorder cluster A",
                    "1" = "Personality disorder cluster A",
                    missing = NA_character_
                    )
  )

glad.mhq.raw.id %>%
  freq(personality_cluster_a)
```

```{r Check personality_cluster_a}
glad.mhq.raw.id %>%
  select(
    personality_cluster_a,
    personality_cluster_a_numeric,
    mhq.personality_disorder_diagnosed,
    mhq.personality_disorder_diagnosed_numeric
  )
```

Cluster B
4. Antisocial                       24 ( 0.8%)
5. Borderline                     2553 (89.4%)
6. Histrionic                        7 ( 0.2%)
7. Narcissistic                      8 ( 0.3%)

```{r glad mhq personality_cluster_b}
glad.mhq.raw.id <- glad.mhq.raw.id %>%
  mutate(
    personality_cluster_b_numeric =
      case_when(
        mhq.personality_disorder_diagnosed_numeric == "1" ~ 0,
        mhq.personality_disorder_diagnosed_numeric == "2" ~ 0,
        mhq.personality_disorder_diagnosed_numeric == "3" ~ 0,
        mhq.personality_disorder_diagnosed_numeric == "4" ~ 1,
        mhq.personality_disorder_diagnosed_numeric == "5" ~ 1,
        mhq.personality_disorder_diagnosed_numeric == "6" ~ 1,
        mhq.personality_disorder_diagnosed_numeric == "7" ~ 1,
        mhq.personality_disorder_diagnosed_numeric == "8" ~ 0,
        mhq.personality_disorder_diagnosed_numeric == "9" ~ 0,
        mhq.personality_disorder_diagnosed_numeric == "10" ~ 0,
        mhq.personality_disorder_numeric == "0" ~ 0
      )
  )

glad.mhq.raw.id <- glad.mhq.raw.id %>%
  mutate(
    personality_cluster_b =
      recode_factor(personality_cluster_b_numeric,
                    "0" = "No personality disorder cluster B",
                    "1" = "Personality disorder cluster B",
                    missing = NA_character_
                    )
  )

glad.mhq.raw.id %>%
  freq(personality_cluster_b)
```

```{r Check personality_cluster_b}
glad.mhq.raw.id %>%
  select(
    personality_cluster_b,
    personality_cluster_b_numeric,
    mhq.personality_disorder_diagnosed,
    mhq.personality_disorder_diagnosed_numeric
  )
```

Cluster C
8. Avoidant/anxious                133 ( 4.7%)
9. Dependent                        29 ( 1.0%)
10. Obsessive-compulsive
```{r glad mhq personality_cluster_c}
glad.mhq.raw.id <- glad.mhq.raw.id %>%
  mutate(
    personality_cluster_c_numeric =
      case_when(
        mhq.personality_disorder_diagnosed_numeric == "1" ~ 0,
        mhq.personality_disorder_diagnosed_numeric == "2" ~ 0,
        mhq.personality_disorder_diagnosed_numeric == "3" ~ 0,
        mhq.personality_disorder_diagnosed_numeric == "4" ~ 0,
        mhq.personality_disorder_diagnosed_numeric == "5" ~ 0,
        mhq.personality_disorder_diagnosed_numeric == "6" ~ 0,
        mhq.personality_disorder_diagnosed_numeric == "7" ~ 0,
        mhq.personality_disorder_diagnosed_numeric == "8" ~ 1,
        mhq.personality_disorder_diagnosed_numeric == "9" ~ 1,
        mhq.personality_disorder_diagnosed_numeric == "10" ~ 1,
        mhq.personality_disorder_numeric == "0" ~ 0
      )
  )

glad.mhq.raw.id <- glad.mhq.raw.id %>%
  mutate(
    personality_cluster_c =
      recode_factor(personality_cluster_c_numeric,
                    "0" = "No personality disorder cluster C",
                    "1" = "Personality disorder cluster C",
                    missing = NA_character_
                    )
  )

glad.mhq.raw.id %>%
  freq(personality_cluster_c)
```

```{r Check personality_cluster_c}
glad.mhq.raw.id %>%
  select(
    personality_cluster_c,
    personality_cluster_c_numeric,
    mhq.personality_disorder_diagnosed,
    mhq.personality_disorder_diagnosed_numeric
  )
```

Control grouping
These individuals have no self report diagnosis of any kind that we measure. 
Controls = 784
```{r glad mhq control}
glad.mhq.raw.id <- glad.mhq.raw.id %>%
  mutate(
    control_numeric =
      if_else(
    depressive_disorders_numeric == "0" &
    anxiety_disorders_numeric == "0" &
    eating_disorders_numeric == "0" &
    obsessive_compulsive_disorders_numeric == "0" &
    psychotic_disorders_numeric == "0" &
    mhq.mania_hypomania_bipolar_or_manicdepression_numeric == "0" &
    mhq.posttraumatic_stress_disorder_ptsd_numeric == "0" &
    mhq.autism_aspergers_or_autistic_spectrum_disorder_numeric == "0" &
    mhq.attention_deficit_hyperactivity_disorder_numeric == "0" &
    mhq.personality_disorder_numeric == "0", 
    true = 1, 
    false = 0, 
    NA_real_)
  )

glad.mhq.raw.id <- glad.mhq.raw.id %>%
  mutate(
    control =
      recode_factor(control_numeric,
                    "0" = "No control",
                    "1" = "Control",
                    missing = NA_character_
                    )
  )

glad.mhq.raw.id %>%
  freq(control)
```

Create new dataframe with the derived categories

```{r glad mhq head}
head(glad.mhq.raw.id)
```

```{r glad mhq summary}
summarytools::dfSummary(
  glad.mhq.raw.id,
  graph.col = F,
  valid.col = F,
  labels.col = F)
```

Create new dataframe with the derived categories
++KT: do we want to keep individual diagnoses here as well?? 
```{r glad mhq categories}
glad.mhq.raw.categories <- glad.mhq.raw.id %>%
  select(
    Sample,
    ID,
    anxiety_disorders_numeric,
    anxiety_disorders,
    mhq.specific_phobia_e.g._phobia_of_flying_numeric,
    mhq.specific_phobia_e.g._phobia_of_flying,
    mhq.social_anxiety_or_social_phobia_numeric,
    mhq.social_anxiety_or_social_phobia,
    agoraphobia_panic_disorder_numeric,
    agoraphobia_panic_disorder,
    depressive_disorders_numeric,
    depressive_disorders,
    eating_disorders_numeric,
    eating_disorders,
    obsessive_compulsive_disorders_numeric,
    obsessive_compulsive_disorders,
    psychotic_disorders_numeric,
    psychotic_disorders,
    mhq.mania_hypomania_bipolar_or_manicdepression_numeric,
    mhq.mania_hypomania_bipolar_or_manicdepression,
    mhq.posttraumatic_stress_disorder_ptsd_numeric,
    mhq.posttraumatic_stress_disorder_ptsd,
    mhq.autism_aspergers_or_autistic_spectrum_disorder_numeric,
    mhq.autism_aspergers_or_autistic_spectrum_disorder,
    mhq.attention_deficit_hyperactivity_disorder_numeric,
    mhq.attention_deficit_hyperactivity_disorder,
    mhq.personality_disorder_numeric,
    mhq.personality_disorder,
    personality_cluster_a_numeric,
    personality_cluster_a,
    personality_cluster_b_numeric,
    personality_cluster_b,
    personality_cluster_c_numeric,
    personality_cluster_c
    )
```

# glad pcl

```{r glad pcl cols}
glad.pcl.raw <- readRDS(file = "../data_raw/glad/pcl_glad.rds")
dim(glad.pcl.raw)
colnames(glad.pcl.raw)
```

```{r glad pcl cleaning}
glad.pcl.raw.id <- glad.pcl.raw %>%
  drop_na(externalDataReference) %>% # Drop NAs
  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
  mutate(ID = as.numeric(ID),
         startDate.glad = startDate) %>% # Rename startDate
  select(
    Sample, # Sample
    ID, # ID
    pcl.stressful_experience_repeated_images_prepan_numeric = pcl.stressful_experience_repeated_images_numeric,
    pcl.stressful_experience_repeated_images_prepan = pcl.stressful_experience_repeated_images,
    pcl.stressful_experience_upset_reminded_prepan_numeric = pcl.stressful_experience_upset_reminded_numeric,
    pcl.stressful_experience_upset_reminded_prepan = pcl.stressful_experience_upset_reminded,
    pcl.stressful_situation_avoiding_activities_prepan_numeric = pcl.stressful_situation_avoiding_activities_numeric,
    pcl.stressful_situation_avoiding_activities_prepan = pcl.stressful_situation_avoiding_activities,
    pcl.cut_people_feeling_distant_prepan_numeric = pcl.cut_people_feeling_distant_numeric,
    pcl.cut_people_feeling_distant_prepan = pcl.cut_people_feeling_distant,
    pcl.feeling_irritable_or_having_angry_outbursts_prepan_numeric = pcl.feeling_irritable_or_having_angry_outbursts_numeric,
    pcl.feeling_irritable_or_having_angry_outbursts_prepan = pcl.feeling_irritable_or_having_angry_outbursts,
    pcl.difficulty_concentrating_prepan_numeric = pcl.difficulty_concentrating_numeric,
    pcl.difficulty_concentratin_prepan = pcl.difficulty_concentrating
  ) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

# Inspect dimensions
dim(glad.pcl.raw.id)
# Inspect colnames
colnames(glad.pcl.raw.id)
#Differences
dim(glad.pcl.raw)[1]-dim(glad.pcl.raw.id)[1]
```

Calculate sum score for PCL-6
```{r pcl sum score prepan}
# Create vector with scoring key: If the item is reversed coded use -1. 
# There needs to be the correct number of values for each item in the questionnaire. 
pcl.items_key_prepan <- c(1,1,1,1,1,1)

# Create vector with items that are included in total score
pcl.items_prepan = c(
  "pcl.stressful_experience_repeated_images_prepan_numeric",
  "pcl.stressful_experience_upset_reminded_prepan_numeric",
  "pcl.stressful_situation_avoiding_activities_prepan_numeric",
  "pcl.cut_people_feeling_distant_prepan_numeric",
  "pcl.feeling_irritable_or_having_angry_outbursts_prepan_numeric",
  "pcl.difficulty_concentrating_prepan_numeric"
  )

# Calulate total score
pcl.scored_items_prepan <- scoreItems(keys = pcl.items_key_prepan,
                                        items = glad.pcl.raw.id[pcl.items_prepan],
                                        totals = TRUE, 
                                        missing = TRUE, 
                                        impute = 'none', 
                                        min = 1, 
                                        max = 5)
# Add in column to tibble
glad.pcl.raw.id$pcl.sum_score_prepan <- pcl.scored_items_prepan$scores

# Look at values
glad.pcl.raw.id %>%
  descr(pcl.sum_score_prepan,
        stats = "common"
        )
```

```{r glad pcl head}
head(glad.pcl.raw.id)
```

```{r glad pcl summary}
summarytools::dfSummary(
  glad.pcl.raw.id,
  graph.col = F,
  valid.col = F, labels.col = F)
```

# glad phq

```{r glad phq cols}
glad.phq.raw <- readRDS(file = "../data_raw/glad/phq_glad.rds")
dim(glad.phq.raw)
colnames(glad.phq.raw)
```

```{r glad phq cleaning}
glad.phq.raw.id <- glad.phq.raw %>%
  drop_na(externalDataReference) %>% # Drop NAs
  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
  mutate(ID = as.numeric(ID),
         startDate.glad = startDate) %>% # Rename startDate
  select(
    Sample, # Sample
    ID, # ID
    phq.little_interest_or_pleasure_in_doing_things_prepan = phq.little_interest_or_pleasure_in_doing_things,
    phq.feeling_down_depressed_or_hopeless_prepan = phq.feeling_down_depressed_or_hopeless,
    phq.staying_asleep_sleeping_trouble_prepan = phq.staying_asleep_sleeping_trouble,
    phq.feeling_tired_or_having_little_energy_prepan = phq.feeling_tired_or_having_little_energy,
    phq.poor_appetite_or_overeating_prepan = phq.poor_appetite_or_overeating,
    phq.feeling_bad_failure_family_prepan = phq.feeling_bad_failure_family,
    phq.trouble_concentrating_reading_newspaper_prepan = phq.trouble_concentrating_reading_newspaper,
    phq.moving_fidgety_noticed_opposite_prepan = phq.moving_fidgety_noticed_opposite,
    phq.dead_hurting_thoughts_prepan = phq.dead_hurting_thoughts,
    phq.little_interest_or_pleasure_in_doing_things_prepan_numeric = phq.little_interest_or_pleasure_in_doing_things_numeric,
    phq.feeling_down_depressed_or_hopeless_prepan_numeric = phq.feeling_down_depressed_or_hopeless_numeric,
    phq.staying_asleep_sleeping_trouble_prepan_numeric = phq.staying_asleep_sleeping_trouble_numeric,
    phq.feeling_tired_or_having_little_energy_prepan_numeric = phq.feeling_tired_or_having_little_energy_numeric,
    phq.poor_appetite_or_overeating_prepan_numeric = phq.poor_appetite_or_overeating_numeric,
    phq.feeling_bad_failure_family_prepan_numeric = phq.feeling_bad_failure_family_numeric,
    phq.trouble_concentrating_reading_newspaper_prepan_numeric = phq.trouble_concentrating_reading_newspaper_numeric,
    phq.moving_fidgety_noticed_opposite_prepan_numeric = phq.moving_fidgety_noticed_opposite_numeric,
    phq.dead_hurting_thoughts_prepan_numeric = phq.dead_hurting_thoughts_numeric
  ) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

# Inspect dimensions
dim(glad.phq.raw.id)
# Inspect colnames
colnames(glad.phq.raw.id)
#Differences
dim(glad.phq.raw)[1]-dim(glad.phq.raw.id)[1]
```

Calculate sum score for PHQ-9
```{r phq sum score prepan}
# Create vector with scoring key: If the item is reversed coded use -1. 
# There needs to be the correct number of values for each item in the questionnaire. 
phq.items_key_prepan <- c(1,1,1,1,1,1,1,1,1)

# Create vector with items that are included in sum score
phq.items_prepan = c(
  "phq.little_interest_or_pleasure_in_doing_things_prepan_numeric",
  "phq.feeling_down_depressed_or_hopeless_prepan_numeric",
  "phq.staying_asleep_sleeping_trouble_prepan_numeric",
  "phq.feeling_tired_or_having_little_energy_prepan_numeric",
  "phq.poor_appetite_or_overeating_prepan_numeric",
  "phq.feeling_bad_failure_family_prepan_numeric",
  "phq.trouble_concentrating_reading_newspaper_prepan_numeric",
  "phq.moving_fidgety_noticed_opposite_prepan_numeric",
  "phq.dead_hurting_thoughts_prepan_numeric"
  )

# Calulate sum score
phq.scored_items_prepan <- scoreItems(keys = phq.items_key_prepan,
                                        items = glad.phq.raw.id[phq.items_prepan],
                                        totals = TRUE, 
                                        missing = TRUE, 
                                        impute = 'none', 
                                        min = 0, 
                                        max = 3)
# Add in column to tibble
glad.phq.raw.id$phq.sum_score_prepan <- phq.scored_items_prepan$scores

# Look at values
glad.phq.raw.id %>%
  descr(phq.sum_score_prepan,
        stats = "common"
        )
```

```{r glad phq head}
head(glad.phq.raw.id)
```

```{r glad phq summary}
summarytools::dfSummary(
  glad.phq.raw.id,
  graph.col = F,
  valid.col = F
  )
```

## COPING GLAD: GAD-7

```{r coping glad gad cols}
coping.glad.gad.raw <- readRDS(file = "../data_raw/coping_glad/gad_coping_glad.rds")
dim(coping.glad.gad.raw)
colnames(coping.glad.gad.raw)
```

```{r coping glad gad summary}
summarytools::dfSummary(
  coping.glad.gad.raw,
  graph.col = F,
  valid.col = F,
  labels.col = F
  )
```

```{r coping glad gad cleaning}
coping.glad.gad.raw.id <- coping.glad.gad.raw %>%
  drop_na(externalDataReference) %>% # Drop NAs
  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
  mutate(ID = as.numeric(ID),
         startDate.glad = startDate) %>% # Rename startDate
  select(
    Sample, # Sample
    ID, # ID
    startDate.coping.glad = startDate,
    gad.feeling_nervous_anxious_or_on_edge_retro = gad7.feeling_nervous_anxious_or_on_edge,
    gad.control_worrying_stop_retro = gad7.control_worrying_stop,
    gad.worrying_too_much_about_different_things_retro = gad7.worrying_too_much_about_different_things,
    gad.trouble_relaxing_retro = gad7.trouble_relaxing,
    gad.sit_restless_hard_retro = gad7.sit_restless_hard,
    gad.becoming_easily_annoyed_or_irritable_retro = gad7.becoming_easily_annoyed_or_irritable,
    gad.awful_feeling_afraid_happen_retro = gad7.awful_feeling_afraid_happen,
    gad.feeling_nervous_anxious_or_on_edge_base = gad7.feeling_nervous_anxious_or_on_edge.1,
    gad.control_worrying_stop_base = gad7.control_worrying_stop.1,
    gad.worrying_too_much_about_different_things_base = gad7.worrying_too_much_about_different_things.1,
    gad.trouble_relaxing_base = gad7.trouble_relaxing.1,
    gad.sit_restless_hard_base = gad7.sit_restless_hard.1,
    gad.becoming_easily_annoyed_or_irritable_base = gad7.becoming_easily_annoyed_or_irritable.1,
    gad.awful_feeling_afraid_happen_base = gad7.awful_feeling_afraid_happen.1,
    gad.feeling_nervous_anxious_or_on_edge_retro_numeric = gad7.feeling_nervous_anxious_or_on_edge_numeric,
    gad.control_worrying_stop_retro_numeric = gad7.control_worrying_stop_numeric,
    gad.worrying_too_much_about_different_things_retro_numeric = gad7.worrying_too_much_about_different_things_numeric,
    gad.trouble_relaxing_retro_numeric = gad7.trouble_relaxing_numeric,
    gad.sit_restless_hard_retro_numeric = gad7.sit_restless_hard_numeric,
    gad.becoming_easily_annoyed_or_irritable_retro_numeric = gad7.becoming_easily_annoyed_or_irritable_numeric,
    gad.awful_feeling_afraid_happen_retro_numeric = gad7.awful_feeling_afraid_happen_numeric,
    gad.feeling_nervous_anxious_or_on_edge_base_numeric = gad7.feeling_nervous_anxious_or_on_edge.1_numeric,
    gad.control_worrying_stop_base_numeric = gad7.control_worrying_stop.1_numeric,
    gad.worrying_too_much_about_different_things_base_numeric = gad7.worrying_too_much_about_different_things.1_numeric,
    gad.trouble_relaxing_base_numeric = gad7.trouble_relaxing.1_numeric,
    gad.sit_restless_hard_base_numeric = gad7.sit_restless_hard.1_numeric,
    gad.becoming_easily_annoyed_or_irritable_base_numeric = gad7.becoming_easily_annoyed_or_irritable.1_numeric,
    gad.awful_feeling_afraid_happen_base_numeric = gad7.awful_feeling_afraid_happen.1_numeric
  ) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

# Inspect dimensions
dim(coping.glad.gad.raw.id)
# Inspect colnames
colnames(coping.glad.gad.raw.id)
#Differences
dim(coping.glad.gad.raw)[1]-dim(coping.glad.gad.raw.id)[1]
```

Calculate sum score for GAD-7 retrospective
```{r coping gad sum score retro}
# Create vector with scoring key: If the item is reversed coded use -1. 
# There needs to be the correct number of values for each item in the questionnaire. 
gad.items_key_retro <- c(1,1,1,1,1,1,1)

# Create vector with items that are included in total score
gad.items_retro = c(
  "gad.feeling_nervous_anxious_or_on_edge_retro_numeric",
  "gad.control_worrying_stop_retro_numeric",
  "gad.worrying_too_much_about_different_things_retro_numeric",
  "gad.trouble_relaxing_retro_numeric",
  "gad.sit_restless_hard_retro_numeric",
  "gad.becoming_easily_annoyed_or_irritable_retro_numeric",
  "gad.awful_feeling_afraid_happen_retro_numeric"
  )

# Calulate total score
gad.scored_items_retro <- scoreItems(keys = gad.items_key_retro,
                                        items = coping.glad.gad.raw.id[gad.items_retro],
                                        totals = TRUE, 
                                        missing = TRUE, 
                                        impute = 'none', 
                                        min = 0, 
                                        max = 3)
# Add in column to tibble
coping.glad.gad.raw.id$gad.sum_score_retro <- gad.scored_items_retro$scores

# Look at values
coping.glad.gad.raw.id %>%
  descr(gad.sum_score_retro,
        stats = "common"
        )
```

Calculate sum score for GAD-7 baseline
```{r coping gad sum score base}
# Create vector with scoring key: If the item is reversed coded use -1. 
# There needs to be the correct number of values for each item in the questionnaire. 
gad.items_key_base <- c(1,1,1,1,1,1,1)

# Create vector with items that are included in total score
gad.items_base = c(
  "gad.feeling_nervous_anxious_or_on_edge_base_numeric",
  "gad.control_worrying_stop_base_numeric",
  "gad.worrying_too_much_about_different_things_base_numeric",
  "gad.trouble_relaxing_base_numeric",
  "gad.sit_restless_hard_base_numeric",
  "gad.becoming_easily_annoyed_or_irritable_base_numeric",
  "gad.awful_feeling_afraid_happen_base_numeric"
  )

# Calulate total score
gad.scored_items_base <- scoreItems(keys = gad.items_key_base,
                                        items = coping.glad.gad.raw.id[gad.items_base],
                                        totals = TRUE, 
                                        missing = TRUE, 
                                        impute = 'none', 
                                        min = 0, 
                                        max = 3)
# Add in column to tibble
coping.glad.gad.raw.id$gad.sum_score_base <- gad.scored_items_base$scores

# Look at values
coping.glad.gad.raw.id %>%
  descr(gad.sum_score_base,
        stats = "common"
        )
```

```{r coping glad gad head}
head(coping.glad.gad.raw.id)
```

```{r coping glad gad summary 2}
summarytools::dfSummary(
  coping.glad.gad.raw.id,
  graph.col = F,
  valid.col = F,
  labels.col = F)
```

********************** 
++KT LEFT OFF HERE
**********************

+++ ADD 3 CHUNKs for phq, gad for each comparison
1) prepandemic - retro -> most interesting (in analysis needs to be adjusted for time difference between prepandemic and coping sign up)
2) prepandemic - base
3) retro - base

+++ ADD a case_when CHUNKs - who has what data - to get accurate Ns. 
1) binary coded has only prepandemic == 0
2) prepandemic and baseline == 1
3) prepandemic, baseline, and retrospective == 2

+++ chunks for missingness
1) per individual
2) per questionnaire item/total questionnaire

# COPING GLAD: PCL-6

```{r coping glad pcl cols}
coping.glad.pcl.raw <- readRDS(file = "../data_raw/coping_glad/pcl_coping_glad.rds")
dim(coping.glad.pcl.raw)
colnames(coping.glad.pcl.raw)
```

```{r coping glad pcl summary labels}
summarytools::dfSummary(
  coping.glad.pcl.raw,
  graph.col = F,
  valid.col = F,
  labels.col = F
)
```

Retro for the PCL does not mean retrospective
```{r coping glad pcl cleaning}
coping.glad.pcl.raw.id <- coping.glad.pcl.raw %>%
  drop_na(externalDataReference) %>% # Drop NAs
  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
  mutate(ID = as.numeric(ID),
         startDate.glad = startDate) %>% # Rename startDate
  select(
    Sample, # Sample
    ID, # ID
    pcl.stressful_experience_repeated_images_base_numeric = pcl6.stressful_experience_repeated_images_numeric,
    pcl.stressful_experience_repeated_images_base = pcl6.stressful_experience_repeated_images,
    pcl.stressful_experience_upset_reminded_base_numeric = pcl6.stressful_experience_upset_reminded_numeric,
    pcl.stressful_experience_upset_reminded_base = pcl6.stressful_experience_upset_reminded,
    pcl.stressful_situation_avoiding_activities_base_numeric = pcl6.avoiding_activities_stressful_experience_numeric, # differ to GLAD prepan
    pcl.stressful_situation_avoiding_activities_base = pcl6.avoiding_activities_stressful_experience, # differ to GLAD prepan
    pcl.cut_people_feeling_distant_base_numeric = pcl6.cut_people_feeling_distant_numeric,
    pcl.cut_people_feeling_distant_base = pcl6.cut_people_feeling_distant,
    pcl.feeling_irritable_or_having_angry_outbursts_base_numeric = pcl6.feeling_irritable_or_having_angry_outbursts_numeric,
    pcl.feeling_irritable_or_having_angry_outbursts_base = pcl6.feeling_irritable_or_having_angry_outbursts,
    pcl.difficulty_concentrating_base_numeric = pcl6.difficulty_concentrating_numeric,
    pcl.difficulty_concentratin_base = pcl6.difficulty_concentrating,
    pcl.stressful_experience_repeated_images_retro_numeric = pcl6.stressful_experience_repeated_images.1_numeric,
    pcl.stressful_experience_repeated_images_retro = pcl6.stressful_experience_repeated_images.1,
    pcl.stressful_experience_upset_reminded_retro_numeric = pcl6.stressful_experience_upset_reminded.1_numeric,
    pcl.stressful_experience_upset_reminded_retro = pcl6.stressful_experience_upset_reminded.1,
    pcl.stressful_situation_avoiding_activities_retro_numeric = pcl6.avoiding_activities_stressful_experience.1_numeric,
    pcl.stressful_situation_avoiding_activities_retro = pcl6.avoiding_activities_stressful_experience.1,
    pcl.cut_people_feeling_distant_retro_numeric = pcl6.cut_people_feeling_distant.1_numeric,
    pcl.cut_people_feeling_distant_retro = pcl6.cut_people_feeling_distant.1,
    pcl.feeling_irritable_or_having_angry_outbursts_retro_numeric = pcl6.feeling_irritable_or_having_angry_outbursts.1_numeric,
    pcl.feeling_irritable_or_having_angry_outbursts_retro = pcl6.feeling_irritable_or_having_angry_outbursts.1,
    pcl.difficulty_concentrating_retro_numeric = pcl6.difficulty_concentrating.1_numeric,
    pcl.difficulty_concentratin_retro = pcl6.difficulty_concentrating.1
  ) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

# Inspect dimensions
dim(coping.glad.pcl.raw.id)
# Inspect colnames
colnames(coping.glad.pcl.raw.id)
#Differences
dim(coping.glad.pcl.raw)[1]-dim(coping.glad.pcl.raw.id)[1]
```

Calculate sum score for PHQ-9 retro
```{r coping pcl sum score retro}
# Create vector with scoring key: If the item is reversed coded use -1. 
# There needs to be the correct number of values for each item in the questionnaire. 
pcl.items_key_retro <- c(1,1,1,1,1,1)

# Create vector with items that are included in total score
pcl.items_retro = c(
  "pcl.stressful_experience_repeated_images_retro_numeric",
  "pcl.stressful_experience_upset_reminded_retro_numeric",
  "pcl.stressful_situation_avoiding_activities_retro_numeric",
  "pcl.cut_people_feeling_distant_retro_numeric",
  "pcl.feeling_irritable_or_having_angry_outbursts_retro_numeric",
  "pcl.difficulty_concentrating_retro_numeric"
)

# Calulate total score
pcl.scored_items_retro <- scoreItems(keys = pcl.items_key_retro,
                                     items = coping.glad.pcl.raw.id[pcl.items_retro],
                                     totals = TRUE, 
                                     missing = TRUE, 
                                     impute = 'none', 
                                     min = 0, 
                                     max = 1)
# Add in column to tibble
coping.glad.pcl.raw.id$pcl.sum_score_retro <- pcl.scored_items_retro$scores

# Look at values
coping.glad.pcl.raw.id %>%
  descr(pcl.sum_score_retro,
        stats = "common"
  )
```

Maximum is fine with 3 x 7.

Calculate sum score for PHQ-9 base
```{r coping pcl sum score base}
# Create vector with scoring key: If the item is reversed coded use -1. 
# There needs to be the correct number of values for each item in the questionnaire. 
pcl.items_key_base <- c(1,1,1,1,1,1)

# Create vector with items that are included in total score
pcl.items_base = c(
  "pcl.stressful_experience_repeated_images_base_numeric",
  "pcl.stressful_experience_upset_reminded_base_numeric",
  "pcl.stressful_situation_avoiding_activities_base_numeric",
  "pcl.cut_people_feeling_distant_base_numeric",
  "pcl.feeling_irritable_or_having_angry_outbursts_base_numeric",
  "pcl.difficulty_concentrating_base_numeric"
)

# Calulate total score
pcl.scored_items_base <- scoreItems(keys = pcl.items_key_base,
                                    items = coping.glad.pcl.raw.id[pcl.items_base],
                                    totals = TRUE, 
                                    missing = TRUE, 
                                    impute = 'none', 
                                    min = 1, 
                                    max = 5)
# Add in column to tibble
coping.glad.pcl.raw.id$pcl.sum_score_base <- pcl.scored_items_base$scores

# Look at values
coping.glad.pcl.raw.id %>%
  descr(pcl.sum_score_base,
        stats = "common"
  )
```

```{r coping glad pcl head}
head(coping.glad.pcl.raw.id)
```

```{r coping glad pcl summary}
summarytools::dfSummary(
  coping.glad.pcl.raw.id,
  graph.col = F,
  valid.col = F,
  labels.col = F)
```

# glad COPING phq

```{r coping glad phq cols}
coping.glad.phq.raw <- readRDS(file = "../data_raw/coping_glad/phq_coping_glad.rds")
dim(coping.glad.phq.raw)
colnames(coping.glad.phq.raw)
```

```{r coping glad phq summary labels}
summarytools::dfSummary(
  coping.glad.phq.raw,
  graph.col = F,
  valid.col = F,
  #  labels.col = F
)
```

```{r}
coping.glad.phq.raw %>%
  select(contains("little")) %>%
  colnames
```

```{r coping glad phq cleaning}
coping.glad.phq.raw.id <- coping.glad.phq.raw %>%
  drop_na(externalDataReference) %>% # Drop NAs
  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
  mutate(ID = as.numeric(ID),
         startDate.glad = startDate) %>% # Rename startDate
  select(
    Sample, # Sample
    ID, # ID
    phq.little_interest_or_pleasure_in_doing_things_retro = phq9.little_interest_or_pleasure_in_doing_things,
    phq.feeling_down_depressed_or_hopeless_retro = phq9.feeling_down_depressed_or_hopeless,
    phq.staying_asleep_sleeping_trouble_retro = phq9.staying_asleep_sleeping_trouble,
    phq.feeling_tired_or_having_little_energy_retro = phq9.feeling_tired_or_having_little_energy,
    phq.poor_appetite_or_overeating_retro = phq9.poor_appetite_or_overeating,
    phq.feeling_bad_failure_family_retro = phq9.feeling_bad_failure_family,
    phq.trouble_concentrating_reading_newspaper_retro = phq9.trouble_concentrating_newspaper_reading, # differ GLAD prepandemic
    phq.moving_fidgety_noticed_opposite_retro = phq9.moving_fidgety_opposite_slowly, # differ GLAD prepandemic
    phq.dead_hurting_thoughts_retro = phq9.dead_hurting_thoughts,
    phq.little_interest_or_pleasure_in_doing_things_retro_numeric = phq9.little_interest_or_pleasure_in_doing_things_numeric,
    phq.feeling_down_depressed_or_hopeless_retro_numeric = phq9.feeling_down_depressed_or_hopeless_numeric,
    phq.staying_asleep_sleeping_trouble_retro_numeric = phq9.staying_asleep_sleeping_trouble_numeric,
    phq.feeling_tired_or_having_little_energy_retro_numeric = phq9.feeling_tired_or_having_little_energy_numeric,
    phq.poor_appetite_or_overeating_retro_numeric = phq9.poor_appetite_or_overeating_numeric,
    phq.feeling_bad_failure_family_retro_numeric = phq9.feeling_bad_failure_family_numeric,
    phq.trouble_concentrating_reading_newspaper_retro_numeric = phq9.trouble_concentrating_newspaper_reading_numeric, # differ GLAD prepandemic
    phq.moving_fidgety_noticed_opposite_retro_numeric = phq9.moving_fidgety_opposite_slowly_numeric, # differ GLAD prepandemic
    phq.dead_hurting_thoughts_retro_numeric = phq9.dead_hurting_thoughts_numeric,
    phq.little_interest_or_pleasure_in_doing_things_base = phq9.little_interest_or_pleasure_in_doing_things.1,
    phq.feeling_down_depressed_or_hopeless_base = phq9.feeling_down_depressed_or_hopeless.1,
    phq.staying_asleep_sleeping_trouble_base = phq9.staying_asleep_sleeping_trouble.1,
    phq.feeling_tired_or_having_little_energy_base = phq9.feeling_tired_or_having_little_energy.1,
    phq.poor_appetite_or_overeating_base = phq9.poor_appetite_or_overeating.1,
    phq.feeling_bad_failure_family_base = phq9.feeling_bad_failure_family.1,
    phq.trouble_concentrating_reading_newspaper_base = phq9.trouble_concentrating_newspaper_reading.1, # differ GLAD prepandemic
    phq.moving_fidgety_noticed_opposite_base = phq9.moving_fidgety_opposite_slowly.1, # differ GLAD prepandemic
    phq.dead_hurting_thoughts_base = phq9.dead_hurting_thoughts.1,
    phq.little_interest_or_pleasure_in_doing_things_base_numeric = phq9.little_interest_or_pleasure_in_doing_things.1_numeric,
    phq.feeling_down_depressed_or_hopeless_base_numeric = phq9.feeling_down_depressed_or_hopeless.1_numeric,
    phq.staying_asleep_sleeping_trouble_base_numeric = phq9.staying_asleep_sleeping_trouble.1_numeric,
    phq.feeling_tired_or_having_little_energy_base_numeric = phq9.feeling_tired_or_having_little_energy.1_numeric,
    phq.poor_appetite_or_overeating_base_numeric = phq9.poor_appetite_or_overeating.1_numeric,
    phq.feeling_bad_failure_family_base_numeric = phq9.feeling_bad_failure_family.1_numeric,
    phq.trouble_concentrating_reading_newspaper_base_numeric = phq9.trouble_concentrating_newspaper_reading.1_numeric, # differ GLAD prepandemic
    phq.moving_fidgety_noticed_opposite_base_numeric = phq9.moving_fidgety_opposite_slowly.1_numeric, # differ GLAD prepandemic
    phq.dead_hurting_thoughts_base_numeric = phq9.dead_hurting_thoughts_numeric
  ) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

# Inspect dimensions
dim(coping.glad.phq.raw.id)
# Inspect colnames
colnames(coping.glad.phq.raw.id)
#Differences
dim(coping.glad.phq.raw)[1]-dim(coping.glad.phq.raw.id)[1]
```

Calculate sum score for PHQ-9 retro
```{r coping phq sum score retro}
# Create vector with scoring key: If the item is reversed coded use -1. 
# There needs to be the correct number of values for each item in the questionnaire. 
phq.items_key_retro <- c(1,1,1,1,1,1,1,1,1)

# Create vector with items that are included in total score
phq.items_retro = c(
  "phq.little_interest_or_pleasure_in_doing_things_retro_numeric",
"phq.feeling_down_depressed_or_hopeless_retro_numeric",
"phq.staying_asleep_sleeping_trouble_retro_numeric",
"phq.feeling_tired_or_having_little_energy_retro_numeric",
"phq.poor_appetite_or_overeating_retro_numeric",
"phq.feeling_bad_failure_family_retro_numeric",
"phq.trouble_concentrating_reading_newspaper_retro_numeric",
"phq.moving_fidgety_noticed_opposite_retro_numeric",
"phq.dead_hurting_thoughts_retro_numeric"
)

# Calulate total score
phq.scored_items_retro <- scoreItems(keys = phq.items_key_retro,
                                     items = coping.glad.phq.raw.id[phq.items_retro],
                                     totals = TRUE, 
                                     missing = TRUE, 
                                     impute = 'none', 
                                     min = 0, 
                                     max = 3)
# Add in column to tibble
coping.glad.phq.raw.id$phq.sum_score_retro <- phq.scored_items_retro$scores

# Look at values
coping.glad.phq.raw.id %>%
  descr(phq.sum_score_retro,
        stats = "common"
  )
```

Maximum is fine with 3 x 7.

Calculate sum score for PHQ-9 base
```{r coping phq sum score base}
# Create vector with scoring key: If the item is reversed coded use -1. 
# There needs to be the correct number of values for each item in the questionnaire. 
phq.items_key_base <- c(1,1,1,1,1,1,1,1,1)

# Create vector with items that are included in total score
phq.items_base = c(
  "phq.little_interest_or_pleasure_in_doing_things_base_numeric",
"phq.feeling_down_depressed_or_hopeless_base_numeric",
"phq.staying_asleep_sleeping_trouble_base_numeric",
"phq.feeling_tired_or_having_little_energy_base_numeric",
"phq.poor_appetite_or_overeating_base_numeric",
"phq.feeling_bad_failure_family_base_numeric",
"phq.trouble_concentrating_reading_newspaper_base_numeric",
"phq.moving_fidgety_noticed_opposite_base_numeric",
"phq.dead_hurting_thoughts_base_numeric"
)

# Calulate total score
phq.scored_items_base <- scoreItems(keys = phq.items_key_base,
                                    items = coping.glad.phq.raw.id[phq.items_base],
                                    totals = TRUE, 
                                    missing = TRUE, 
                                    impute = 'none', 
                                    min = 0, 
                                    max = 3)
# Add in column to tibble
coping.glad.phq.raw.id$phq.sum_score_base <- phq.scored_items_base$scores

# Look at values
coping.glad.phq.raw.id %>%
  descr(phq.sum_score_base,
        stats = "common"
  )
```

```{r coping glad phq head}
head(coping.glad.phq.raw.id)
```

```{r coping glad phq summary}
summarytools::dfSummary(
  coping.glad.phq.raw.id,
  graph.col = F,
  valid.col = F,
  labels.col = F)
```

# Join tibbles together

glad data frame list
```{r glad data frame list}
glad.dfs.list <- list(
  glad.dem.raw.id,
  glad.gad.raw.id,
  glad.mhq.raw.categories,
#  glad.ocir.raw.id,
  glad.pcl.raw.id,
  glad.phq.raw.id,
  coping.glad.gad.raw.id,
  coping.glad.pcl.raw.id,
  coping.glad.phq.raw.id
)
```

```{r Join all questionnaires for glad}
dat.glad.raw <- plyr::join_all(
  glad.dfs.list,
  by = c("ID", "Sample") # Alternatively you can join by several columns EDGI -> "Age", "Sex", "Birthyear"
  )

#look at the data
skimr::skim(dat.glad.raw)
```

Check duplicates again to be save
+++KLP: RAMP: More than one column: Age, Sex, Login ID; if they match on all 3 then we treat them as a duplicate; otherwise we are going to rename the Login ID
```{r glad Check duplicates}
dat.glad.raw$ID.dup <- duplicated(dat.glad.raw$ID)

summary(as.factor(dat.glad.raw$ID.dup))

dat.dup <- dat.glad.raw %>%
  filter(ID.dup == TRUE)

dat.glad.raw.no.dup <- dat.glad.raw %>%
  filter(ID.dup == FALSE)
```

#Exclusion
Exclude those without sex, age and incomplete PHQ/GAD items
Create a new new object for each exclusion step, e.g., data.no_sex and data.no_sex.no_age
```{r Exclude participants that do not report sex}
dim(dat.glad.raw)
dat.no.sex <- dat.glad.raw %>%
  drop_na(Gender)
dim(dat.no.sex)

dim(dat.glad.raw)[1]-dim(dat.no.sex)[1]
```
`r dim(dat.glad.raw)[1]-dim(dat.no.sex)[1]` were excluded because they did not report their sex

```{r Exclude participants that do not report age}
dim(dat.no.sex)
dat.no.sex.no.age <- dat.no.sex %>%
  drop_na(age_category)
dim(dat.no.sex.no.age)

dim(dat.no.sex)[1]-dim(dat.no.sex.no.age)[1]
```
`r dim(dat.no.sex)[1]-dim(dat.no.sex.no.age)[1]` were excluded because they did not report their age

Exclusion of inflammatory bowel disease (IBD) BioResource (BR) cohort
+++CH: or alternatively sample according to IBD prevalence in UK population
+++CH: What is the IBD prevalence in the UK population? -> Literature search
+++CH: This chunk needs to be included when we have the data available from the NBR
```{r COVID exclusion of IBD}
#dim(dat.no.sex.no.age)
#
#dat.no.sex.no.age <- dat.no.sex.no.age %>%
#  filter(NBR.IBD == 0)
#
#dim(dat.no.sex.no.age.no.ibd)
#
#dim(dat.no.sex.no.age)[1]-dim(dat.no.sex.no.age.no.ibd)[1]

dat.no.sex.no.age.no.ibd <- dat.no.sex.no.age
```

#Missigness of questionnaire items
+++CH: We need to discuss how we want to exclude these participants that are missing answers to the questionnaires
GAD7 ?
PHQ9 ? 
PCL-6?
+++CH: Check for literature
```{r Exclusion of participants because of missing questionnaire items}
#dim(dat.no.sex.no.age.no.ibd)
#dat.no.sex.no.age.no.ibd.incomplete.questionnaire <- dat.no.sex.no.age.no.ibd %>%
#  filter(#ADD CONDITION HERE)
#dim(dat.no.sex.no.age.no.ibd.incomplete.questionnaire)
#
#dim(dat.no.sex.no.age.no.ibd)[1]-dim(dat.no.sex.no.age.no.ibd.incomplete.questionnaire)[1]

dat.no.sex.no.age.no.ibd.incomplete.questionnaire <- dat.no.sex.no.age.no.ibd
```

Create tidy data on which the exclusionc criteria have been applied
```{r Tidy data}
dat.glad <- dat.no.sex.no.age.no.ibd.incomplete.questionnaire

skimr::skim(dat.glad)
```
The complete rate for age and sex should be 1 now

# Definition of prepandemic and baseline 
Exlcude people who have joined GLAD/EDGI after the pandemic began (i.e., cut off that we choose)
Potentially GLAD/EDGI particiapnts between January to April. EDGI launched on February 24th.

These participants with sign ups later than these dates could  potentially be counted as COPING baseline.

Prepandemic GLAD/EDGI = Prepandemic (GLAD/EDGI sign-up questionnaire)

Retrospective = COPING/RAMP sign up questionnaire; !only of those participants who have reported a change in symptoms!

Baseline = COPING/RAMP sign up questionnaire

+++CH: Create a column based on the the startDate if the participant can be counted as "prepandemic"
+++CH: Create three columns for all the definitions of "pre-pandemic" for sensitivy analysis

Potential dates for the definition of prepandemic
```{r Potential dates for prepandemic definition}
# Date of the first COVID-19 case in the United Kingdom (UK)
date_first_case_uk_january_31 <- as.POSIXct("2020-01-31")

# Date for assumed higher awareness of COVID / Lockdown in Italy 4. March 2020 / first festivals cancelled
date_higher_awareness_march_1 <- as.POSIXct("2020-03-01")

# Date the UK went into lockdown
date_uk_lockdown_march_23 <- as.POSIXct("2020-03-23")
```

```{r Prepandemic definitions january_31}
dat.glad <- dat.glad %>%
  mutate(
    prepandemic_january_31_numeric =
      if_else(
        startDate.glad > date_first_case_uk_january_31, # The GLAD sign up is dated before the cut off (> longer ago)
        true = 0, # Participant has not signed up before the pandemic,
        false = 1, # Participant has signed up before the pandemic,
        missing = NA_real_
      )
  )

dat.glad <- dat.glad %>%
  mutate(
    prepandemic_january_31 =
      recode_factor(
        prepandemic_january_31_numeric,
        "0" = "Sign up after 31. January",
        "1" = "Sign up before 31. January"
      )
  )

dat.glad %>%
  freq(prepandemic_january_31)
```

```{r Prepandemic definitions march_1}
dat.glad <- dat.glad %>%
  mutate(
    prepandemic_march_1_numeric =
      if_else(
        startDate.glad > date_higher_awareness_march_1, # The GLAD sign up is dated before the cut off (> longer ago)
        true = 0, # Participant has not signed up before the pandemic,
        false = 1, # Participant has signed up before the pandemic,
        missing = NA_real_
      )
  )

dat.glad <- dat.glad %>%
  mutate(
    prepandemic_march_1 =
      recode_factor(
        prepandemic_march_1_numeric,
        "0" = "Sign up after 1. March",
        "1" = "Sign up before 1. March"
      )
  )

dat.glad %>%
  freq(prepandemic_march_1)
```

```{r Prepandemic definitions march_23}
dat.glad <- dat.glad %>%
  mutate(
    prepandemic_march_23_numeric =
      if_else(
        startDate.glad > date_uk_lockdown_march_23, # The GLAD sign up is dated before the cut off (> longer ago)
        true = 0, # Participant has not signed up before the pandemic,
        false = 1, # Participant has signed up before the pandemic,
        missing = NA_real_
      )
  )

dat.glad <- dat.glad %>%
  mutate(
    prepandemic_march_23 =
      recode_factor(
        prepandemic_march_23_numeric,
        "0" = "Sign up after 23. March",
        "1" = "Sign up before 23. March"
      )
  )

dat.glad %>%
  freq(prepandemic_march_23)
```

Calculate the time difference between time difference between sign up questionnaire and COPING questionnaire
```{r time difference between sign up questionnaire and COPING questionnaire}
dat.glad <- dat.glad %>%
  mutate(
    time_diff_sign_up_coping =
        as.numeric(
        difftime(           #this function does time1 - time2 as difftime(time1, time2...)
          startDate.coping.glad,    #should be start date for COPING (time1)
          startDate.glad),    #should be start date for GLAD (time2)
          units = c("days")  #can also be "secs", "mins", "hours", "weeks"
          )
        )

dat.glad %>%
  descr(
    var = time_diff_sign_up_coping,
    stats = "common"
    )
```

What proportion is over a year?
```{r eval=FALSE, include=FALSE}

```

# Probable COVID-19 case identification
Algorithm from Menni et al. to identify probable COVID-19
Variables required:
- Sex: 	0 Female, 1 Male
- Other binary variables: 0 No, 1 Yes       #THESE NAMES WILL CHANGE WHEN IMPORTING DATA - FIND AND REPLACE
- "anosmia": loss of smell or taste  
- "pcough":	Persistent cough
- "sfatigue": Severe fatigue
- "smeals": Skipped meals

```{r eval=FALSE, include=FALSE}
# Recode Gender to be binary for the model in RAMP
dat.respirotry.ramp <- dat.respirtaory.ramp %>%
		  mutate(
		    gender_binary_ramp =
		      case_when(
		        Gender == "Male" ~ "Male",
		        Gender == "Female" ~ "Female",
		        Gender == !("Male" | "Female") ~ NA_real_
		      )
		  )
```

++KT: Need help identifying cut offs for COVID probability
```{r eval=FALSE, include=FALSE}
## COVID prediction model for COPING

## Formula to calculate probability 
dat.respirotry.coping <- dat.respirtaory.coping %>%
		  mutate(
		    covid_probability = 
		      (-1.32) - 
		      (0.01*Age) + 
		      (0.44*Sex) + #we have sex here in COPING - use binary Gender variable in RAMP
		      (1.75*anosmia) + #will be renamed
		      (0.31*pcough) +  #will be renamed
		      (0.49*sfatigue) +  #will be renamed
		      (0.39*smeals) #will be renamed
		         )

## Calcualte the odds ratios 
dat.respirotry.coping <- dat.respirtaory.coping %>%
		  mutate(
		    covid_odds_ratio = 
		      exp(covid_probability) / (1 + exp(covid_probability)
		                              )

## label the variable
covid_odds_ratio <- "COVID-19 probability" #IGNORE NEED TO EDIT TO LABEL THE ABOVE VARIABLE

## generate variable covid_odds_ratio_50 -> 0, 0,5 and 1 = 0, 1, 2 (that's a column). Previous code: egen covid_odds_ratio_50 = cut(covid_odds_ratio), at(0,0.5,1) icode
dat.respirotry.coping <- dat.respirtaory.coping %>%
		  mutate(
		    covid_odds_ratio_50_numeric = 
		      case_when(
		        covid_odds_ratio >= 0 & covid_odds_ratio <= 0.4 ~ "0", #I don't know how to categorise these - how does the previous function know when to cut?
		        covid_odds_ratio >= 0.4 & covid_odds_ratio <= 0.6 ~ "1",
		        covid_odds_ratio >= 0.7 & covid_odds_ratio <= 1 ~ "2"
		      )

#create factor with labels
dat.respirotry.coping <- dat.respirtaory.coping %>%
  mutate(
    covid_odds_ratio_50 =
      recode_factor(
        covid_odds_ratio_50_numeric,
        "0" = "No COVID",
        "1" = "Probable COVID",
        "2" = "COVID case"
      )
  )

## creating a frequency table. Previous code: table covid_odds_ratio_50, c(min covid_odds_ratio max covid_odds_ratio)
covid_variables <- c(
                      "covid_odds_ratio_50",
                      "covid_odds_ratio",
                      "covid_probability"
                    )

descr(x = dat.respirotry.coping[,covid_variables],
      round.digits = 2,
      transpose = TRUE)

## create a new label for the variable (50%)
covid_odds_ratio_50 <- "COVID-19 probability >= 50%" #Need to rename variable properly

## looking at the created variable
table(dat.respirotry.coping$covid_odds_ratio_50) #same as before - not sure why this is needed? 
```

Gerome: We can get actual test data from PHE -> Cambridge
We need to move our data to Cambridge cluster
That's only for non-RAMP; EDGI, GLAD; NBR
KY: Longer term or for this paper?
Sanity check with Cambridge about the validity of the mysterious formula (Spector magic)

### 2020-07-20 PANCHANGE_data_preprocessing2020-07-15.Rmd
Changing yaml date to system date to reflect latest update, rather than date the script was created

@@
 author: "Katie Thompson, Topher Huebel, Molly Davies, Kirstin Purves"
-date: "03/07/2020"
+date: Sys.Date()
 output:  

### 2020-07-21 PANCHANGE_data_preprocessing2020-07-15.Rmd
Transfered all comments in script into action points on github

@@
 
-This will be the master script to run all analyses for the project "Anxiety, depression and trauma symptom change during the COVID-19 pandemic: retrospective versus objective assessment" - Young et al (2020)
+This will is the preprocessing script to prepare the data to run analyses for the project "Anxiety, depression and trauma symptom change during the COVID-19 pandemic: retrospective versus objective assessment" - Young et al (2020)
 
@@
 
-Retrieve the current date
-to use it for file endings to not overwrite files when one exports files
+Retrieve the current date to use it for file endings to not overwrite files when one exports files
 ```{r Recent date}
@@
 Define colours for plotting this are the standard coping colours
-+++CH: Is there a document in which these colours are defined?
 ```{r Colour palettes: COPING}
@@
 # Data import and merging
-+++CH04-07-20: I have added all read-ins of the data. How will the coping data be stored? -> Question for Yuhao
-+++CH04-07-20: We need to discuss the naming of the variables PHQ9 vs phq
-+++CH04-07-20: We need to discuss the naming of the variables .0 vs .retro
-
-GLAD only receives current measures and RAMP questionnaire
-
-All COPING surveys are separate surveys
-+++TOPHER
-***
-++KT: Need to make sure that the startDate's for each survey are coded accordingly, e.g.
-startDate.glad, startDate.coping, startDate.RAMP.
-Otherwise people who are in both GLAD and COPING will have two dates.
-+++CH: I have added this
+
+Note: GLAD only receives current measures and RAMP questionnaire
+Note: All COPING surveys are separate surveys
 
@@
 
-Clean Age variable
+#Clean Age variable
 Age outlier
@@
 ```
-++KT: The age variable here needs to be cleaned - have added a chunk above (before age grouping) for this. Before: min = -55 and max = 290. 
+
 ```{r glad dem summary}
@@
 *#Disorder groupings - from COPING/RAMP analysis minutes*
-1. Depressive disorder group: major depression, antenatal/postnatal depression, premenstrual depression.
+1. Depressive disorder group: major depression, antenatal/postnatal depression, premenstrual depression. The logic for this has been double checked for males - KT/MD. 
 2. Anxiety group: generalised anxiety, social anxiety, specific phobia, agoraphobia, panic_disorder, panic_attacks. 
@@
 
-Depressive disorders group
-+++CH: NEEDS BETTER LOGIC FOR MALES!!!!
-++KT: Sex issue fixed - code has been checked. 407 people with no MDD but have either postnatal/pmdd.
 ```{r glad mhq depressive_disorders}
@@
 ```
-+++CH: Why are there so many NAs in mhq.panic_disorder?
-++KT: Added late to questionnaire.
 
@@
 
-+++CH: Lots of NAs in schizoaffective_disorder 
 ```{r Check psychotic_disorders}
@@
 ```
-
-Create new dataframe with the derived categories
 
@@
 
-+++ ADD 3 CHUNKs for phq, gad for each comparison
-1) prepandemic - retro -> most interesting (in analysis needs to be adjusted for time difference between prepandemic and coping sign up)
-2) prepandemic - base
-3) retro - base
-
-+++ ADD a case_when CHUNKs - who has what data - to get accurate Ns. 
-1) binary coded has only prepandemic == 0
-2) prepandemic and baseline == 1
-3) prepandemic, baseline, and retrospective == 2
-
-+++ chunks for missingness
-1) per individual
-2) per questionnaire item/total questionnaire
+```{r pre, base, retro comparison for phq, pcl and gad}
+
+```
+
+```{r data level groups}
+
+```
 
@@
 
-Retro for the PCL does not mean retrospective
+Note: Retro for the PCL does not mean retrospective
+
 ```{r coping glad pcl cleaning}
@@
   valid.col = F,
-  #  labels.col = F
+  labels.col = F
 )
@@
 Exclusion of inflammatory bowel disease (IBD) BioResource (BR) cohort
-+++CH: or alternatively sample according to IBD prevalence in UK population
-+++CH: What is the IBD prevalence in the UK population? -> Literature search
-+++CH: This chunk needs to be included when we have the data available from the NBR
 ```{r COVID exclusion of IBD}
@@
 +++CH: We need to discuss how we want to exclude these participants that are missing answers to the questionnaires
-GAD7 ?
-PHQ9 ? 
-PCL-6?
-+++CH: Check for literature
+```{r missingness}
+
+```
+
 ```{r Exclusion of participants because of missing questionnaire items}
@@
 # Definition of prepandemic and baseline 
-Exlcude people who have joined GLAD/EDGI after the pandemic began (i.e., cut off that we choose)
+Exlcude people who have joined GLAD/EDGI after the pandemic began, sensitivity analyses done on the cut off's we have chosen. 
 Potentially GLAD/EDGI particiapnts between January to April. EDGI launched on February 24th.
 
-These participants with sign ups later than these dates could  potentially be counted as COPING baseline.
-
 Prepandemic GLAD/EDGI = Prepandemic (GLAD/EDGI sign-up questionnaire)
 
-Retrospective = COPING/RAMP sign up questionnaire; !only of those participants who have reported a change in symptoms!
+Retrospective = COPING/RAMP sign up questionnaire; *only of those participants who have reported a change in symptoms*
 
@@
 
-+++CH: Create a column based on the the startDate if the participant can be counted as "prepandemic"
-+++CH: Create three columns for all the definitions of "pre-pandemic" for sensitivy analysis
-
-Potential dates for the definition of prepandemic
+Dates for the definition of prepandemic
 ```{r Potential dates for prepandemic definition}
@@
 ```
-
-Gerome: We can get actual test data from PHE -> Cambridge
-We need to move our data to Cambridge cluster
-That's only for non-RAMP; EDGI, GLAD; NBR
-KY: Longer term or for this paper?
-Sanity check with Cambridge about the validity of the mysterious formula (Spector magic)

### 2020-07-22 PANCHANGE_data_preprocessing2020-07-15.Rmd
Made comments to retro and baseline comparison chunk
Update PANCHANGE_data_preprocessing2020-07-15.Rmd

@@
 
-This will is the preprocessing script to prepare the data to run analyses for the project "Anxiety, depression and trauma symptom change during the COVID-19 pandemic: retrospective versus objective assessment" - Young et al (2020)
+This is the preprocessing script to prepare the data to run analyses for the project "Anxiety, depression and trauma symptom change during the COVID-19 pandemic: retrospective versus objective assessment" - Young et al (2020)
 
@@
 ```{r pre, base, retro comparison for phq, pcl and gad}
-
+#see Issue for more details here
 ```

### 2020-07-22 PANCHANGE_data_preprocessing2020-07-15.Rmd
Added source chunk for data path and amended data chunks

--- 2020-07-21 PANCHANGE_data_preprocessing2020-07-15.Rmd
@@
 ```{r Choose colour palette}
-palette=COPINGpalette2
+palette = COPINGpalette2
 ```
@@
 Note: All COPING surveys are separate surveys
+
+# Source data file paths
+
+```{r source file path}
+#source raw data directory: data.raw_path
+source("../PANCHANGE_raw_path.R")
+```
 
@@
 ```{r glad dem cols}
-glad.dem.raw <- readRDS(file = "../data_raw/glad/dem_glad.rds")
+glad.dem.raw <- readRDS(file = paste0(data.raw_path, "/glad/dem_glad.rds"))
 dim(glad.dem.raw)
@@
 ```{r glad gad cols}
-glad.gad.raw <- readRDS(file = "../data_raw/glad/gad_glad.rds")
+glad.gad.raw <- readRDS(file = paste0(data.raw_path, "/glad/gad_glad.rds"))
 dim(glad.gad.raw)
@@
 ```{r glad mhq cols}
-glad.mhq.raw <- readRDS(file = "../data_raw/glad/mhq_glad.rds")
+glad.mhq.raw <- readRDS(file = paste0(data.raw_path,"/glad/mhq_glad.rds"))
 dim(glad.mhq.raw)
@@
 ```{r glad pcl cols}
-glad.pcl.raw <- readRDS(file = "../data_raw/glad/pcl_glad.rds")
+glad.pcl.raw <- readRDS(file = paste0(data.raw_path,"/glad/pcl_glad.rds"))
 dim(glad.pcl.raw)
@@
 ```{r glad phq cols}
-glad.phq.raw <- readRDS(file = "../data_raw/glad/phq_glad.rds")
+glad.phq.raw <- readRDS(file = paste0(data.raw_path, "/glad/phq_glad.rds"))
 dim(glad.phq.raw)
@@
 ```{r coping glad gad cols}
-coping.glad.gad.raw <- readRDS(file = "../data_raw/coping_glad/gad_coping_glad.rds")
+coping.glad.gad.raw <- readRDS(file = paste0(data.raw_path,"/coping_glad/gad_coping_glad.rds"))
 dim(coping.glad.gad.raw)
@@
 ```{r coping glad pcl cols}
-coping.glad.pcl.raw <- readRDS(file = "../data_raw/coping_glad/pcl_coping_glad.rds")
+coping.glad.pcl.raw <- readRDS(file = paste0(data.raw_path,"/coping_glad/pcl_coping_glad.rds"))
 dim(coping.glad.pcl.raw)
@@
 ```{r coping glad phq cols}
-coping.glad.phq.raw <- readRDS(file = "../data_raw/coping_glad/phq_coping_glad.rds")
+coping.glad.phq.raw <- readRDS(file = paste0(data.raw_path, "/coping_glad/phq_coping_glad.rds"))
 dim(coping.glad.phq.raw)

### 2020-07-22 PANCHANGE_data_preprocessing2020-07-15.Rmd
Reviewed GLAD PCL cleaning and scoring

@@
     pcl.difficulty_concentrating_retro_numeric = pcl6.difficulty_concentrating.1_numeric,
-    pcl.difficulty_concentratin_retro = pcl6.difficulty_concentrating.1
+    pcl.difficulty_concentrating_retro = pcl6.difficulty_concentrating.1
   ) %>%
@@
 
-Calculate sum score for PHQ-9 retro
+Calculate sum score for PCL-6 retro
 ```{r coping pcl sum score retro}
@@
 
-Maximum is fine with 3 x 7.
-
-Calculate sum score for PHQ-9 base
+Calculate sum score for PCL-6 base
 ```{r coping pcl sum score base}

### 2020-07-22 PANCHANGE_data_preprocessing2020-07-15.Rmd
Checked COPING PHQ chunks

--- 2020-07-22 PANCHANGE_data_preprocessing2020-07-15.Rmd
@@
 Calculate sum score for PCL-6 base
+The sum scores here will not be accurate if we are using complete cases. Only use sum scores here for complete cases, otherwise the minimum will be 0 where it should be 6. 
 ```{r coping pcl sum score base}
@@
                                     missing = TRUE, 
-                                    impute = 'none', 
+                                    impute = "none", 
                                     min = 1, 
@@
 
-```{r}
+```{r select phq little}
 coping.glad.phq.raw %>%

### 2020-07-22 PANCHANGE_data_preprocessing2020-07-15.Rmd
RE-reviewed sex/gender/age exclusion chunks

@@
   graph.col = F,
-  valid.col = F,
-  labels.col = F
-)
-```
-
-```{r select phq little}
-coping.glad.phq.raw %>%
-  select(contains("little")) %>%
-  colnames
-```
-
+  valid.col = F
+  #labels.col = F
+)
+```
+
+Will need to double check these namings once we have the new cleaned data -- KT. 
 ```{r coping glad phq cleaning}
@@
 
-Maximum is fine with 3 x 7.
-
 Calculate sum score for PHQ-9 base
@@
 
-Check duplicates again to be save
+Check duplicates again to be saved
 +++KLP: RAMP: More than one column: Age, Sex, Login ID; if they match on all 3 then we treat them as a duplicate; otherwise we are going to rename the Login ID
++++KT: No duplicates identified by ID in GLAD. 
 ```{r glad Check duplicates}
@@
 #Exclusion
-Exclude those without sex, age and incomplete PHQ/GAD items
-Create a new new object for each exclusion step, e.g., data.no_sex and data.no_sex.no_age
+Exclude those without sex, gender, age and incomplete PHQ/GAD items
+Create a new new object for each exclusion step, e.g., data.no_sex, data.no_gender and data.no_sex.no_age
 ```{r Exclude participants that do not report sex}
@@
 dat.no.sex <- dat.glad.raw %>%
+  drop_na(Sex)
+dim(dat.no.sex)
+
+dim(dat.glad.raw)[1]-dim(dat.no.sex)[1]
+```
+`r dim(dat.glad.raw)[1]-dim(dat.no.sex)[1]` were excluded because they did not report their sex
+
+```{r Exclude participants that do not report gender}
+dim(dat.no.sex)
+dat.no.sex.no.gender <- dat.no.sex %>%
   drop_na(Gender)
-dim(dat.no.sex)
-
-dim(dat.glad.raw)[1]-dim(dat.no.sex)[1]
-```
-`r dim(dat.glad.raw)[1]-dim(dat.no.sex)[1]` were excluded because they did not report their sex
+dim(dat.no.sex.no.gender)
+
+dim(dat.no.sex)[1]-dim(dat.no.sex.no.gender)[1]
+```
+`r dim(dat.no.sex)[1]-dim(dat.no.sex.no.gender)[1]` were excluded because they did not report their sex
 
 ```{r Exclude participants that do not report age}
-dim(dat.no.sex)
-dat.no.sex.no.age <- dat.no.sex %>%
+dim(dat.no.sex.no.gender)
+dat.no.sex.no.gender.no.age <- dat.no.sex.no.gender %>%
   drop_na(age_category)
-dim(dat.no.sex.no.age)
-
-dim(dat.no.sex)[1]-dim(dat.no.sex.no.age)[1]
-```
-`r dim(dat.no.sex)[1]-dim(dat.no.sex.no.age)[1]` were excluded because they did not report their age
+dim(dat.no.sex.no.gender.no.age)
+
+dim(dat.no.sex.no.gender)[1]-dim(dat.no.sex.no.gender.no.age)[1]
+```
+`r dim(dat.no.gender)[1]-dim(dat.no.sex.no.gender.no.age)[1]` were excluded because they did not report their age
 

### 2020-07-22 PANCHANGE_data_preprocessing2020-07-15.Rmd
reviewed IBD exclusion chunks - these still need editing as don't have the data

@@
 
-dat.no.sex.no.age.no.ibd <- dat.no.sex.no.age
+dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age
 ```
@@
 
-dat.no.sex.no.age.no.ibd.incomplete.questionnaire <- dat.no.sex.no.age.no.ibd
-```
-
-Create tidy data on which the exclusionc criteria have been applied
+dat.no.sex.no.gender.no.age.no.ibd.incomplete.questionnaire <- dat.no.sex.no.gender.no.age.no.ibd
+```
+
+Create tidy data on which the exclusion criteria have been applied
 ```{r Tidy data}
-dat.glad <- dat.no.sex.no.age.no.ibd.incomplete.questionnaire
+dat.glad <- dat.no.sex.no.gender.no.age.no.ibd.incomplete.questionnaire
 
@@
 ```
-The complete rate for age and sex should be 1 now
+The complete rate for sex, gender and age should be 1 now.
 

### 2020-07-22 PANCHANGE_data_preprocessing2020-07-15.Rmd
Reviewed time chunks for COPING-GLAD

@@
 
-What proportion is over a year?
+Proportion of people signed up over one year ago
 ```{r eval=FALSE, include=FALSE}
-
+dat.glad <- dat.glad %>%
+  mutate(
+    over_one_year_time_diff_sign_up_coping_numeric =
+      as.numeric(
+        if_else(time_diff_sign_up_coping > 365, 1, 0
+                )
+      )
+  )
+
+dat.glad <- dat.glad %>%
+  mutate(
+    over_one_year_time_diff_sign_up_coping =
+      recode_factor(
+        over_one_year_time_diff_sign_up_coping_numeric,
+        "0" = "Sign up under one year before COPING",
+        "1" = "Sign up over one year before COPING"
+      )
+  )
+
+table(dat.glad$over_one_year_time_diff_sign_up_coping)
 ```

### 2020-07-22 PANCHANGE_data_preprocessing2020-07-15.Rmd
Reviewed COVID algorithm

@@
 
+The below chunk needs to be re-thought - not as simple as categorising gender. 
 ```{r eval=FALSE, include=FALSE}
 # Recode Gender to be binary for the model in RAMP
-dat.respirotry.ramp <- dat.respirtaory.ramp %>%
+dat.respiratory.ramp <- dat.respiratory.ramp %>%
 		  mutate(
@@
 
-++KT: Need help identifying cut offs for COVID probability
+++KT: Needs to be developed further for RAMP dataset
 ```{r eval=FALSE, include=FALSE}
@@
 ## Formula to calculate probability 
-dat.respirotry.coping <- dat.respirtaory.coping %>%
+dat.respiratory.coping <- dat.respiratory.coping %>%
 		  mutate(
@@
 ## Calcualte the odds ratios 
-dat.respirotry.coping <- dat.respirtaory.coping %>%
+dat.respiratory.coping <- dat.respiratory.coping %>%
 		  mutate(
@@
 
-## label the variable
-covid_odds_ratio <- "COVID-19 probability" #IGNORE NEED TO EDIT TO LABEL THE ABOVE VARIABLE
-
 ## generate variable covid_odds_ratio_50 -> 0, 0,5 and 1 = 0, 1, 2 (that's a column). Previous code: egen covid_odds_ratio_50 = cut(covid_odds_ratio), at(0,0.5,1) icode
-dat.respirotry.coping <- dat.respirtaory.coping %>%
+dat.respiratory.coping <- dat.respiratory.coping %>%
 		  mutate(
@@
 		      case_when(
-		        covid_odds_ratio >= 0 & covid_odds_ratio <= 0.4 ~ "0", #I don't know how to categorise these - how does the previous function know when to cut?
-		        covid_odds_ratio >= 0.4 & covid_odds_ratio <= 0.6 ~ "1",
-		        covid_odds_ratio >= 0.7 & covid_odds_ratio <= 1 ~ "2"
+		        covid_odds_ratio >= 0 & covid_odds_ratio < 0.5 ~ "0", #cut off at 0.5 
+		        covid_odds_ratio >= 0.5 & covid_odds_ratio <= 1 ~ "1"
 		      )
@@
 #create factor with labels
-dat.respirotry.coping <- dat.respirtaory.coping %>%
+dat.respiratory.coping <- dat.respiratory.coping %>%
   mutate(
@@
         "0" = "No COVID",
-        "1" = "Probable COVID",
-        "2" = "COVID case"
+        "1" = "Probable COVID"
       )
@@
 
-descr(x = dat.respirotry.coping[,covid_variables],
+descr(x = dat.respiratory.coping[,covid_variables],
       round.digits = 2,
@@
 
-## create a new label for the variable (50%)
-covid_odds_ratio_50 <- "COVID-19 probability >= 50%" #Need to rename variable properly
-
-## looking at the created variable
-table(dat.respirotry.coping$covid_odds_ratio_50) #same as before - not sure why this is needed? 
-```
+## looking at cases over 0.5
+table(dat.respiratory.coping$covid_odds_ratio_50) 
+```

### 2020-07-23 PANCHANGE_data_preprocessing2020-07-15.Rmd
created phq missingness chunks

@@
 ```
-
-********************** 
-++KT LEFT OFF HERE
-**********************
 
@@
 +++CH: We need to discuss how we want to exclude these participants that are missing answers to the questionnaires
-```{r missingness}
-
+
+Complete case data for PHQ, GAD and PCL - 3345 remaining, drop 35,036.
+```{r complete cases only}
+all.items <- c(phq.items_prepan,
+                phq.items_base,
+                phq.items_retro,
+                gad.items_prepan,
+                gad.items_base,
+                gad.items_retro,
+                pcl.items_prepan,
+                pcl.items_base,
+                pcl.items_retro)
+
+dat.no.sex.no.gender.no.age.no.ibd.complete.cases <- dat.no.sex.no.gender.no.age.no.ibd[complete.cases(dat.no.sex.no.gender.no.age.no.ibd[, all.items ]),]
+
+dim(dat.no.sex.no.gender.no.age.no.ibd.complete.cases)
+dim(dat.no.sex.no.gender.no.age.no.ibd)[1]-dim(dat.no.sex.no.gender.no.age.no.ibd.complete.cases)[1]
+```
+Missingness for PHQ
+```{r phq missingness baseline}
+dat.no.sex.no.gender.no.age.no.ibd.phq.base <- dat.no.sex.no.gender.no.age.no.ibd %>%
+  mutate(
+    na.per.person.phq =
+      rowSums(is.na(dat.no.sex.no.gender.no.age.no.ibd[,colnames(dat.no.sex.no.gender.no.age.no.ibd) %in% phq.items_base]))
+  )
+
+freq(dat.no.sex.no.gender.no.age.no.ibd.phq.base$na.per.person.phq)
+table(dat.no.sex.no.gender.no.age.no.ibd.phq.base$na.per.person.phq)
+
+PHQ.cc$miss_pc_total.phq <- PHQ.cc$na.per.person.phq/PHQ.n.items
+freq(PHQ.cc$miss_pc_total.phq)
 ```
@@
 ```{r Exclusion of participants because of missing questionnaire items}
-#dim(dat.no.sex.no.age.no.ibd)
-#dat.no.sex.no.age.no.ibd.incomplete.questionnaire <- dat.no.sex.no.age.no.ibd %>%
-#  filter(#ADD CONDITION HERE)
-#dim(dat.no.sex.no.age.no.ibd.incomplete.questionnaire)
-#
-#dim(dat.no.sex.no.age.no.ibd)[1]-dim(dat.no.sex.no.age.no.ibd.incomplete.questionnaire)[1]
+dim(dat.no.sex.no.age.no.ibd)
+dat.no.sex.no.age.no.ibd.incomplete.phq.questionnaire <- dat.no.sex.no.gender.no.age.no.ibd %>%
+  filter(!is.na(phq.items_prepan))
+
+dim(dat.no.sex.no.age.no.ibd.incomplete.questionnaire)
+
+dim(dat.no.sex.no.age.no.ibd)[1]-dim(dat.no.sex.no.age.no.ibd.incomplete.questionnaire)[1]
 
@@
 ```
+
 The complete rate for sex, gender and age should be 1 now.

### 2020-07-23 PANCHANGE_data_preprocessing2020-07-15.Rmd
created gad and pcl missingness chunks

@@
 #Missigness of questionnaire items
-+++CH: We need to discuss how we want to exclude these participants that are missing answers to the questionnaires
-
 Complete case data for PHQ, GAD and PCL - 3345 remaining, drop 35,036.
@@
 ```
-Missingness for PHQ
-```{r phq missingness baseline}
-dat.no.sex.no.gender.no.age.no.ibd.phq.base <- dat.no.sex.no.gender.no.age.no.ibd %>%
-  mutate(
-    na.per.person.phq =
-      rowSums(is.na(dat.no.sex.no.gender.no.age.no.ibd[,colnames(dat.no.sex.no.gender.no.age.no.ibd) %in% phq.items_base]))
-  )
-
-freq(dat.no.sex.no.gender.no.age.no.ibd.phq.base$na.per.person.phq)
-table(dat.no.sex.no.gender.no.age.no.ibd.phq.base$na.per.person.phq)
-
-PHQ.cc$miss_pc_total.phq <- PHQ.cc$na.per.person.phq/PHQ.n.items
-freq(PHQ.cc$miss_pc_total.phq)
+
+PHQ
+Complete case data for PHQ baseline (COPING) - 9,260 remaining
+```{r complete cases phq base}
+dat.no.sex.no.gender.no.age.no.ibd.complete.cases.phq.base <- dat.no.sex.no.gender.no.age.no.ibd[complete.cases(dat.no.sex.no.gender.no.age.no.ibd[, phq.items_base ]),]
+
+dim(dat.no.sex.no.gender.no.age.no.ibd.complete.cases.phq.base)
+dim(dat.no.sex.no.gender.no.age.no.ibd)[1]-dim(dat.no.sex.no.gender.no.age.no.ibd.complete.cases.phq.base)[1]
+```
+
+Complete case data for PHQ pre-pandemic (GLAD) - 37,308 remaining
+```{r complete cases phq prepan}
+dat.no.sex.no.gender.no.age.no.ibd.complete.cases.phq.prepan <- dat.no.sex.no.gender.no.age.no.ibd[complete.cases(dat.no.sex.no.gender.no.age.no.ibd[, phq.items_prepan ]),]
+
+dim(dat.no.sex.no.gender.no.age.no.ibd.complete.cases.phq.prepan)
+dim(dat.no.sex.no.gender.no.age.no.ibd)[1]-dim(dat.no.sex.no.gender.no.age.no.ibd.complete.cases.phq.prepan)[1]
+```
+
+Complete case data for PHQ retrospective (COPING) - 9,262 remaining
+```{r complete cases phq retro}
+dat.no.sex.no.gender.no.age.no.ibd.complete.cases.phq.retro <- dat.no.sex.no.gender.no.age.no.ibd[complete.cases(dat.no.sex.no.gender.no.age.no.ibd[, phq.items_retro ]),]
+
+dim(dat.no.sex.no.gender.no.age.no.ibd.complete.cases.phq.retro)
+dim(dat.no.sex.no.gender.no.age.no.ibd)[1]-dim(dat.no.sex.no.gender.no.age.no.ibd.complete.cases.phq.retro)[1]
+```
+
+GAD
+Complete case data for GAD baseline (COPING) - 12,457 remaining
+```{r complete cases gad base}
+dat.no.sex.no.gender.no.age.no.ibd.complete.cases.gad.base <- dat.no.sex.no.gender.no.age.no.ibd[complete.cases(dat.no.sex.no.gender.no.age.no.ibd[, gad.items_base ]),]
+
+dim(dat.no.sex.no.gender.no.age.no.ibd.complete.cases.gad.base)
+dim(dat.no.sex.no.gender.no.age.no.ibd)[1]-dim(dat.no.sex.no.gender.no.age.no.ibd.complete.cases.gad.base)[1]
+```
+
+Complete case data for gad pre-pandemic (GLAD) - 36,149 remaining
+```{r complete cases gad prepan}
+dat.no.sex.no.gender.no.age.no.ibd.complete.cases.gad.prepan <- dat.no.sex.no.gender.no.age.no.ibd[complete.cases(dat.no.sex.no.gender.no.age.no.ibd[, gad.items_prepan ]),]
+
+dim(dat.no.sex.no.gender.no.age.no.ibd.complete.cases.gad.prepan)
+dim(dat.no.sex.no.gender.no.age.no.ibd)[1]-dim(dat.no.sex.no.gender.no.age.no.ibd.complete.cases.gad.prepan)[1]
+```
+
+Complete case data for gad retrospective (COPING) - 8,930 remaining
+```{r complete cases gad retro}
+dat.no.sex.no.gender.no.age.no.ibd.complete.cases.gad.retro <- dat.no.sex.no.gender.no.age.no.ibd[complete.cases(dat.no.sex.no.gender.no.age.no.ibd[, gad.items_retro ]),]
+
+dim(dat.no.sex.no.gender.no.age.no.ibd.complete.cases.gad.retro)
+dim(dat.no.sex.no.gender.no.age.no.ibd)[1]-dim(dat.no.sex.no.gender.no.age.no.ibd.complete.cases.gad.retro)[1]
+```
+
+PCL
+Complete case data for PCL baseline (COPING) - 12,376 remaining
+```{r complete cases pcl base}
+dat.no.sex.no.gender.no.age.no.ibd.complete.cases.pcl.base <- dat.no.sex.no.gender.no.age.no.ibd[complete.cases(dat.no.sex.no.gender.no.age.no.ibd[, pcl.items_base ]),]
+
+dim(dat.no.sex.no.gender.no.age.no.ibd.complete.cases.pcl.base)
+dim(dat.no.sex.no.gender.no.age.no.ibd)[1]-dim(dat.no.sex.no.gender.no.age.no.ibd.complete.cases.pcl.base)[1]
+```
+
+Complete case data for PCL pre-pandemic (GLAD) - 35,176 remaining
+```{r complete cases pcl prepan}
+dat.no.sex.no.gender.no.age.no.ibd.complete.cases.pcl.prepan <- dat.no.sex.no.gender.no.age.no.ibd[complete.cases(dat.no.sex.no.gender.no.age.no.ibd[, pcl.items_prepan ]),]
+
+dim(dat.no.sex.no.gender.no.age.no.ibd.complete.cases.pcl.prepan)
+dim(dat.no.sex.no.gender.no.age.no.ibd)[1]-dim(dat.no.sex.no.gender.no.age.no.ibd.complete.cases.pcl.prepan)[1]
+```
+
+Complete case data for PCL retrospective (COPING) - 4,618 remaining
+```{r complete cases pcl retro}
+dat.no.sex.no.gender.no.age.no.ibd.complete.cases.pcl.retro <- dat.no.sex.no.gender.no.age.no.ibd[complete.cases(dat.no.sex.no.gender.no.age.no.ibd[, pcl.items_retro ]),]
+
+dim(dat.no.sex.no.gender.no.age.no.ibd.complete.cases.pcl.retro)
+dim(dat.no.sex.no.gender.no.age.no.ibd)[1]-dim(dat.no.sex.no.gender.no.age.no.ibd.complete.cases.pcl.retro)[1]
 ```

### 2020-07-30 PANCHANGE_data_preprocessing2020-07-15.Rmd
PHQ baseline missingness per person chunk

@@
 
-#Missigness of questionnaire items
+##Missigness of questionnaire items
+#PHQ - baseline
+PHQ Missingness NAs per person - count and percentages
+```{r Missingness}
+dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
+  mutate(
+    na_per_person_phq_base =         # variable for NA per person
+      rowSums(                       
+        is.na(dat.no.sex.no.gender.no.age.no.ibd # sum the rows that are NA
+          [,colnames(dat.no.sex.no.gender.no.age.no.ibd) #for all the rows and columns that are in the PHQ items at baseline
+           %in%
+             phq.items_base]
+        )
+    )
+  )
+
+freq(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_phq_base) #have a look at the frequency
+
+dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>% #NA per person as a percentage
+  mutate(
+    miss_pc_total_phq_base = 
+      na_per_person_phq_base/9 # NA per person divided by the amount of items
+  )
+
+freq(dat.no.sex.no.gender.no.age.no.ibd$miss_pc_total_phq_base)
+```
+
+Missingness per item
+```{r Missingness per item}
+dat.no.sex.no.gender.no.age.no.ibd.miss <- as.data.frame(colnames(dat.no.sex.no.gender.no.age.no.ibd[,PHQ.items]))
+colnames(dat.no.sex.no.gender.no.age.no.ibd.miss) <- "Items"
+dat.no.sex.no.gender.no.age.no.ibd.miss$item.miss <- colSums(is.na(dat.no.sex.no.gender.no.age.no.ibd[,PHQ.items]))
+dat.no.sex.no.gender.no.age.no.ibd.miss$item.miss.pc <- dat.no.sex.no.gender.no.age.no.ibd.miss$item.miss/nrow(dat.no.sex.no.gender.no.age.no.ibd[,PHQ.items])
+table(dat.no.sex.no.gender.no.age.no.ibd.miss$Items, dat.no.sex.no.gender.no.age.no.ibd.miss$item.miss.pc)
+summary(dat.no.sex.no.gender.no.age.no.ibd.miss$item.miss.pc)
+
+ggplot(data = dat.no.sex.no.gender.no.age.no.ibd.miss,
+       aes(x = Items, y = item.miss.pc)) +
+  geom_point() +
+  labs(title = "GLAD: PHQ",
+    y ="Missingness per item") +
+  theme_minimal() +
+  coord_flip()
+```
+
+```{r count of people missing a number of items}
+table(dat.no.sex.no.gender.no.age.no.ibd$na.per.person.phq)
+```
+
 Complete case data for PHQ, GAD and PCL - 3345 remaining, drop 35,036.
@@
 
-```{r Exclusion of participants because of missing questionnaire items}
-dim(dat.no.sex.no.age.no.ibd)
-dat.no.sex.no.age.no.ibd.incomplete.phq.questionnaire <- dat.no.sex.no.gender.no.age.no.ibd %>%
-  filter(!is.na(phq.items_prepan))
-
-dim(dat.no.sex.no.age.no.ibd.incomplete.questionnaire)
-
-dim(dat.no.sex.no.age.no.ibd)[1]-dim(dat.no.sex.no.age.no.ibd.incomplete.questionnaire)[1]
-
-dat.no.sex.no.gender.no.age.no.ibd.incomplete.questionnaire <- dat.no.sex.no.gender.no.age.no.ibd
+Missingness NAs per person - count and percentages
+```{r DEM Missingness}
+dat.no.sex.no.gender.no.age.no.ibd$na.per.person.phq <- rowSums(is.na(dat.no.sex.no.gender.no.age.no.ibd[,colnames(dat.no.sex.no.gender.no.age.no.ibd) %in% all.items]))
+freq(dat.no.sex.no.gender.no.age.no.ibd$na.per.person.phq)
+
+PHQ.cc$miss_pc_total.phq <- PHQ.cc$na.per.person.phq/PHQ.n.items
+freq(PHQ.cc$miss_pc_total.phq)
 ```

### 2020-07-30 PANCHANGE_data_preprocessing2020-07-15.Rmd
PHQ retro and prepan missingness per person chunks

@@
 PHQ Missingness NAs per person - count and percentages
-```{r Missingness}
+```{r PHQ basline missingness}
 dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
@@
 freq(dat.no.sex.no.gender.no.age.no.ibd$miss_pc_total_phq_base)
+```
+
+#PHQ - retrospective
+PHQ Missingness NAs per person - count and percentages
+```{r PHQ retrospective missingness}
+dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
+  mutate(
+    na_per_person_phq_retro =         # variable for NA per person
+      rowSums(                       
+        is.na(dat.no.sex.no.gender.no.age.no.ibd # sum the rows that are NA
+          [,colnames(dat.no.sex.no.gender.no.age.no.ibd) #for all the rows and columns that are in the PHQ items at retroline
+           %in%
+             phq.items_retro]
+        )
+    )
+  )
+
+freq(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_phq_retro) #have a look at the frequency
+
+dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>% #NA per person as a percentage
+  mutate(
+    miss_pc_total_phq_retro = 
+      na_per_person_phq_retro/9 # NA per person divided by the amount of items
+  )
+
+freq(dat.no.sex.no.gender.no.age.no.ibd$miss_pc_total_phq_retro)
+```
+
+#PHQ - prepanspective
+PHQ Missingness NAs per person - count and percentages
+```{r PHQ prepanspective missingness}
+dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
+  mutate(
+    na_per_person_phq_prepan =         # variable for NA per person
+      rowSums(                       
+        is.na(dat.no.sex.no.gender.no.age.no.ibd # sum the rows that are NA
+          [,colnames(dat.no.sex.no.gender.no.age.no.ibd) #for all the rows and columns that are in the PHQ items at prepanline
+           %in%
+             phq.items_prepan]
+        )
+    )
+  )
+
+freq(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_phq_prepan) #have a look at the frequency
+
+dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>% #NA per person as a percentage
+  mutate(
+    miss_pc_total_phq_prepan = 
+      na_per_person_phq_prepan/9 # NA per person divided by the amount of items
+  )
+
+freq(dat.no.sex.no.gender.no.age.no.ibd$miss_pc_total_phq_prepan)
 ```

### 2020-07-30 PANCHANGE_data_preprocessing2020-07-15.Rmd
GAD baseline, retro and prepan missingness per person chunks

@@
 
-#PHQ - prepanspective
+#PHQ - prepandemic
 PHQ Missingness NAs per person - count and percentages
-```{r PHQ prepanspective missingness}
+```{r PHQ prepan missingness}
 dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
@@
 
-Missingness per item
-```{r Missingness per item}
-dat.no.sex.no.gender.no.age.no.ibd.miss <- as.data.frame(colnames(dat.no.sex.no.gender.no.age.no.ibd[,PHQ.items]))
-colnames(dat.no.sex.no.gender.no.age.no.ibd.miss) <- "Items"
-dat.no.sex.no.gender.no.age.no.ibd.miss$item.miss <- colSums(is.na(dat.no.sex.no.gender.no.age.no.ibd[,PHQ.items]))
-dat.no.sex.no.gender.no.age.no.ibd.miss$item.miss.pc <- dat.no.sex.no.gender.no.age.no.ibd.miss$item.miss/nrow(dat.no.sex.no.gender.no.age.no.ibd[,PHQ.items])
-table(dat.no.sex.no.gender.no.age.no.ibd.miss$Items, dat.no.sex.no.gender.no.age.no.ibd.miss$item.miss.pc)
-summary(dat.no.sex.no.gender.no.age.no.ibd.miss$item.miss.pc)
-
-ggplot(data = dat.no.sex.no.gender.no.age.no.ibd.miss,
-       aes(x = Items, y = item.miss.pc)) +
-  geom_point() +
-  labs(title = "GLAD: PHQ",
-    y ="Missingness per item") +
-  theme_minimal() +
-  coord_flip()
-```
-
-```{r count of people missing a number of items}
-table(dat.no.sex.no.gender.no.age.no.ibd$na.per.person.phq)
+Count for PHQ baseline, retrospective, and prepandemic missingness per person
+```{r count of people missing a number of items for PHQ}
+#baseline
+table(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_phq_base)
+#retrospective
+table(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_phq_retro)
+#pre-pandemic
+table(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_phq_prepan)
+```
+
+#GAD - baseline
+GAD Missingness NAs per person - count and percentages
+```{r gad basline missingness}
+dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
+  mutate(
+    na_per_person_gad_base =         # variable for NA per person
+      rowSums(                       
+        is.na(dat.no.sex.no.gender.no.age.no.ibd # sum the rows that are NA
+          [,colnames(dat.no.sex.no.gender.no.age.no.ibd) #for all the rows and columns that are in the gad items at baseline
+           %in%
+             gad.items_base]
+        )
+    )
+  )
+
+freq(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_gad_base) #have a look at the frequency
+
+dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>% #NA per person as a percentage
+  mutate(
+    miss_pc_total_gad_base = 
+      na_per_person_gad_base/7 # NA per person divided by the amount of items
+  )
+
+freq(dat.no.sex.no.gender.no.age.no.ibd$miss_pc_total_gad_base)
+```
+
+#gad - retrospective
+gad Missingness NAs per person - count and percentages
+```{r gad retrospective missingness}
+dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
+  mutate(
+    na_per_person_gad_retro =         # variable for NA per person
+      rowSums(                       
+        is.na(dat.no.sex.no.gender.no.age.no.ibd # sum the rows that are NA
+          [,colnames(dat.no.sex.no.gender.no.age.no.ibd) #for all the rows and columns that are in the gad items at retroline
+           %in%
+             gad.items_retro]
+        )
+    )
+  )
+
+freq(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_gad_retro) #have a look at the frequency
+
+dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>% #NA per person as a percentage
+  mutate(
+    miss_pc_total_gad_retro = 
+      na_per_person_gad_retro/7 # NA per person divided by the amount of items
+  )
+
+freq(dat.no.sex.no.gender.no.age.no.ibd$miss_pc_total_gad_retro)
+```
+
+#gad - prepandemic
+gad Missingness NAs per person - count and percentages
+```{r gad prepan missingness}
+dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
+  mutate(
+    na_per_person_gad_prepan =         # variable for NA per person
+      rowSums(                       
+        is.na(dat.no.sex.no.gender.no.age.no.ibd # sum the rows that are NA
+          [,colnames(dat.no.sex.no.gender.no.age.no.ibd) #for all the rows and columns that are in the gad items at prepanline
+           %in%
+             gad.items_prepan]
+        )
+    )
+  )
+
+freq(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_gad_prepan) #have a look at the frequency
+
+dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>% #NA per person as a percentage
+  mutate(
+    miss_pc_total_gad_prepan = 
+      na_per_person_gad_prepan/7 # NA per person divided by the amount of items
+  )
+
+freq(dat.no.sex.no.gender.no.age.no.ibd$miss_pc_total_gad_prepan)
+```
+
+Count for gad baseline, retrospective, and prepandemic missingness per person
+```{r count of people missing a number of items for gad}
+#baseline
+table(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_gad_base)
+#retrospective
+table(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_gad_retro)
+#pre-pandemic
+table(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_gad_prepan)
 ```

### 2020-07-30 PANCHANGE_data_preprocessing2020-07-15.Rmd
PCL baseline, retro and prepan missingness per person chunks

@@
 
-#gad - retrospective
-gad Missingness NAs per person - count and percentages
+#GAD - retrospective
+GAD Missingness NAs per person - count and percentages
 ```{r gad retrospective missingness}
@@
 
-#gad - prepandemic
-gad Missingness NAs per person - count and percentages
+#GAD - prepandemic
+GAD Missingness NAs per person - count and percentages
 ```{r gad prepan missingness}
@@
 table(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_gad_prepan)
+```
+
+#PCL - baseline
+PCL Missingness NAs per person - count and percentages
+```{r pcl basline missingness}
+dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
+  mutate(
+    na_per_person_pcl_base =         # variable for NA per person
+      rowSums(                       
+        is.na(dat.no.sex.no.gender.no.age.no.ibd # sum the rows that are NA
+          [,colnames(dat.no.sex.no.gender.no.age.no.ibd) #for all the rows and columns that are in the pcl items at baseline
+           %in%
+             pcl.items_base]
+        )
+    )
+  )
+
+freq(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_pcl_base) #have a look at the frequency
+
+dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>% #NA per person as a percentage
+  mutate(
+    miss_pc_total_pcl_base = 
+      na_per_person_pcl_base/6 # NA per person divided by the amount of items
+  )
+
+freq(dat.no.sex.no.gender.no.age.no.ibd$miss_pc_total_pcl_base)
+```
+
+#PCL - retrospective
+PCL Missingness NAs per person - count and percentages
+```{r pcl retrospective missingness}
+dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
+  mutate(
+    na_per_person_pcl_retro =         # variable for NA per person
+      rowSums(                       
+        is.na(dat.no.sex.no.gender.no.age.no.ibd # sum the rows that are NA
+          [,colnames(dat.no.sex.no.gender.no.age.no.ibd) #for all the rows and columns that are in the pcl items at retroline
+           %in%
+             pcl.items_retro]
+        )
+    )
+  )
+
+freq(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_pcl_retro) #have a look at the frequency
+
+dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>% #NA per person as a percentage
+  mutate(
+    miss_pc_total_pcl_retro = 
+      na_per_person_pcl_retro/6 # NA per person divided by the amount of items
+  )
+
+freq(dat.no.sex.no.gender.no.age.no.ibd$miss_pc_total_pcl_retro)
+```
+
+#PCL - prepandemic
+pcl Missingness NAs per person - count and percentages
+```{r pcl prepan missingness}
+dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
+  mutate(
+    na_per_person_pcl_prepan =         # variable for NA per person
+      rowSums(                       
+        is.na(dat.no.sex.no.gender.no.age.no.ibd # sum the rows that are NA
+          [,colnames(dat.no.sex.no.gender.no.age.no.ibd) #for all the rows and columns that are in the pcl items at prepanline
+           %in%
+             pcl.items_prepan]
+        )
+    )
+  )
+
+freq(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_pcl_prepan) #have a look at the frequency
+
+dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>% #NA per person as a percentage
+  mutate(
+    miss_pc_total_pcl_prepan = 
+      na_per_person_pcl_prepan/6 # NA per person divided by the amount of items
+  )
+
+freq(dat.no.sex.no.gender.no.age.no.ibd$miss_pc_total_pcl_prepan)
+```
+
+Count for pcl baseline, retrospective, and prepandemic missingness per person
+```{r count of people missing a number of items for pcl}
+#baseline
+table(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_pcl_base)
+#retrospective
+table(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_pcl_retro)
+#pre-pandemic
+table(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_pcl_prepan)
 ```

### 2020-07-30 PANCHANGE_data_preprocessing2020-07-15.Rmd
tidying up code and adding respiratory data import chunk

@@
 ```{r count of people missing a number of items for pcl}
-#baseline
+# baseline
 table(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_pcl_base)
-#retrospective
+# retrospective
 table(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_pcl_retro)
-#pre-pandemic
+# pre-pandemic
 table(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_pcl_prepan)
-```
-
+
+# rename dataset
+dat.no.sex.no.gender.no.age.no.ibd.missingness <- dat.no.sex.no.gender.no.age.no.ibd
+```
+
+#Creating "complete cases" datasets  - NOTE THIS PROBABLY WONT BE USED BUT JUST TO GIVE AN IDEA OF COMPLETE CASES NUMBERS. KT. 
 Complete case data for PHQ, GAD and PCL - 3345 remaining, drop 35,036.
@@
 
-Missingness NAs per person - count and percentages
-```{r DEM Missingness}
-dat.no.sex.no.gender.no.age.no.ibd$na.per.person.phq <- rowSums(is.na(dat.no.sex.no.gender.no.age.no.ibd[,colnames(dat.no.sex.no.gender.no.age.no.ibd) %in% all.items]))
-freq(dat.no.sex.no.gender.no.age.no.ibd$na.per.person.phq)
-
-PHQ.cc$miss_pc_total.phq <- PHQ.cc$na.per.person.phq/PHQ.n.items
-freq(PHQ.cc$miss_pc_total.phq)
-```
-
-Create tidy data on which the exclusion criteria have been applied
+##Create tidy data on which the exclusion criteria have been applied
+Complete sex, gender, age and missingness information applied. 
 ```{r Tidy data}
-dat.glad <- dat.no.sex.no.gender.no.age.no.ibd.incomplete.questionnaire
+dat.glad <- dat.no.sex.no.gender.no.age.no.ibd.missingness
 
@@
 ```
-
-The complete rate for sex, gender and age should be 1 now.
 
@@
 table(dat.glad$over_one_year_time_diff_sign_up_coping)
+```
+
+#READ IN RESPIRATORY DATA 
+```{r read in respiratory data}
+
 ```

### 2020-07-30 PANCHANGE_data_preprocessing2020-07-15.Rmd
Added data groups chunk - may need revisions

@@
   labels.col = F)
-```
-
-```{r pre, base, retro comparison for phq, pcl and gad}
-#see Issue for more details here
-```
-
-```{r data level groups}
-
 ```
@@
 
+#Total score comparison between PHQ, PCL and GAD
+```{r pre, base, retro comparison for phq, pcl and gad}
+#see Issue for more details here
+```
+
+#Data level groups
+Identify which data (prepan, retro and baseline) each participant has
+Has only prepandemic == 0
+prepandemic and baseline == 1
+prepandemic, baseline, and retrospective == 2
+++KT: not sure how best to categorise here so this may need some revision. 
+```{r data level groups}
+dat.glad <- dat.glad %>%
+  mutate(
+    data_group_full_numeric =
+      case_when(
+        !is.na(startDate.glad) & !is.na(startDate.coping.glad) & na_per_person_phq_retro == 0  & na_per_person_gad_retro == 0 & na_per_person_pcl_retro == 0 ~ 5,
+        !is.na(startDate.glad) & !is.na(startDate.coping.glad) & na_per_person_pcl_retro == 0 ~ 4,
+        !is.na(startDate.glad) & !is.na(startDate.coping.glad) & na_per_person_gad_retro == 0 ~ 3,
+        !is.na(startDate.glad) & !is.na(startDate.coping.glad) & na_per_person_phq_retro == 0 ~ 2, #in GLAD, in COPING and have no missing PCL-retro items
+        !is.na(startDate.glad) & !is.na(startDate.coping.glad) ~ 1,
+        !is.na(startDate.glad) & is.na(startDate.coping.glad) ~ 0
+      )
+  )
+
+dat.glad <- dat.glad %>%
+  mutate(
+    data_group_full = 
+      recode_factor(
+        data_group_full_numeric,
+        "0" = "Only prepandemic data",
+        "1" = "Prepandemic and baseline data",
+        "2" = "Prepandemic, baseline and retrospective PHQ data",
+        "3" = "Prepandemic, baseline and retrospective GAD data",
+        "4" = "Prepandemic, baseline and retrospective PCL data",
+        "5" = "All prepandemic, baseline and retrospective data"
+      )
+  )
+
+table(dat.glad$data_group_full)
+```
+
+```{r}
+rowSums(                       
+        is.na(dat.no.sex.no.gender.no.age.no.ibd # sum the rows that are NA
+          [,colnames(dat.no.sex.no.gender.no.age.no.ibd) #for all the rows and columns that are in the pcl items at prepanline
+           %in%
+             pcl.items_prepan]
+```
+
 #READ IN RESPIRATORY DATA 

### 2020-07-30 PANCHANGE_data_preprocessing2020-07-15.Rmd
Added PHQ and GAD difference scores for base, retro and prepan

--- 2020-07-30 PANCHANGE_data_preprocessing2020-07-15.Rmd
@@
 
+#Total score comparison between PHQ, PCL and GAD, prepandemic, retrospecive and baseline
+PHQ difference scores
+```{r phq difference scores}
+# Difference score for prepandemic and retrospective phq sum scores
+dat.glad <- dat.glad %>%
+  mutate(
+    phq.diff_score_prepan_retro =
+      as.numeric(
+        phq.sum_score_prepan - phq.sum_score_retro  # retrospective sum score MINUS prepandemic sum score 
+      )
+  )
+
+summary(dat.glad$phq.diff_score_prepan_retro)
+
+# Difference score for prepandemic and baseline phq sum scores
+dat.glad <- dat.glad %>%
+  mutate(
+    phq.diff_score_prepan_base =
+      as.numeric(
+        phq.sum_score_prepan - phq.sum_score_base  # prepandemic sum score MINUS baseline sum score 
+      )
+  )
+
+summary(dat.glad$phq.diff_score_prepan_base)
+
+# Difference score for retrospective and baseline phq sum scores
+dat.glad <- dat.glad %>%
+  mutate(
+    phq.diff_score_base_retro =
+      as.numeric(
+        phq.sum_score_base - phq.sum_score_retro  # baseline sum score MINUS retrospective sum score 
+      )
+  )
+
+summary(dat.glad$phq.diff_score_base_retro)
+
+```
+
+GAD difference scores
+```{r gad difference scores}
+# Difference score for prepandemic and retrospective gad sum scores
+dat.glad <- dat.glad %>%
+  mutate(
+    gad.diff_score_prepan_retro =
+      as.numeric(
+        gad.sum_score_prepan - gad.sum_score_retro  # retrospective sum score MINUS prepandemic sum score 
+      )
+  )
+
+summary(dat.glad$gad.diff_score_prepan_retro)
+
+# Difference score for prepandemic and baseline gad sum scores
+dat.glad <- dat.glad %>%
+  mutate(
+    gad.diff_score_prepan_base =
+      as.numeric(
+        gad.sum_score_prepan - gad.sum_score_base  # prepandemic sum score MINUS baseline sum score 
+      )
+  )
+
+summary(dat.glad$gad.diff_score_prepan_base)
+
+# Difference score for retrospective and baseline gad sum scores
+dat.glad <- dat.glad %>%
+  mutate(
+    gad.diff_score_base_retro =
+      as.numeric(
+        gad.sum_score_base - gad.sum_score_retro  # baseline sum score MINUS retrospective sum score 
+      )
+  )
+
+summary(dat.glad$gad.diff_score_base_retro)
+
+```
+
+#Data level groups
+Identify which data (prepan, retro and baseline) each participant has
+Has only prepandemic == 0
+prepandemic and baseline == 1
+prepandemic, baseline, and retrospective == 2
+++KT: not sure how best to categorise here so this may need some revision. 
+```{r data level groups}
+dat.glad <- dat.glad %>%
+  mutate(
+    data_group_full_numeric =
+      case_when(
+        !is.na(startDate.glad) & !is.na(startDate.coping.glad) & na_per_person_phq_retro == 0  & na_per_person_gad_retro == 0 & na_per_person_pcl_retro == 0 ~ 5,
+        !is.na(startDate.glad) & !is.na(startDate.coping.glad) & na_per_person_pcl_retro == 0 ~ 4, #in GLAD, in COPING and have no missing PCL-retro items
+        !is.na(startDate.glad) & !is.na(startDate.coping.glad) & na_per_person_gad_retro == 0 ~ 3, #in GLAD, in COPING and have no missing GAD-retro items
+        !is.na(startDate.glad) & !is.na(startDate.coping.glad) & na_per_person_phq_retro == 0 ~ 2, #in GLAD, in COPING and have no missing PHQ-retro items
+        !is.na(startDate.glad) & !is.na(startDate.coping.glad) ~ 1,
+        !is.na(startDate.glad) & is.na(startDate.coping.glad) ~ 0
+      )
+  )
+
+dat.glad <- dat.glad %>%
+  mutate(
+    data_group_full = 
+      recode_factor(
+        data_group_full_numeric,
+        "0" = "Only prepandemic data",
+        "1" = "Prepandemic and baseline data",
+        "2" = "Prepandemic, baseline and retrospective PHQ data",
+        "3" = "Prepandemic, baseline and retrospective GAD data",
+        "4" = "Prepandemic, baseline and retrospective PCL data",
+        "5" = "All prepandemic, baseline and retrospective data"
+      )
+  )
+
+table(dat.glad$data_group_full)
+```
+
 #READ IN RESPIRATORY DATA 

### 2020-07-30 PANCHANGE_data_preprocessing2020-07-15.Rmd
Added PCL difference score for prepan and baseline

@@
 
+PCL difference scores
+NOTE: Only computed baseline and prepandemic differences as the retro account here isn't actually retrospective, but whether the reported baseline scores are due to the pandemic. 
+```{r pcl difference scores}
+# Difference score for prepandemic and baseline pcl sum scores
+dat.glad <- dat.glad %>%
+  mutate(
+    pcl.diff_score_prepan_base =
+      as.numeric(
+        pcl.sum_score_prepan - pcl.sum_score_base  # prepandemic sum score MINUS baseline sum score 
+      )
+  )
+
+summary(dat.glad$pcl.diff_score_prepan_base)
+```
+
 #Data level groups

### 2020-07-30 PANCHANGE_data_preprocessing2020-07-15.Rmd
Cleaned up script for push

@@
 #Data level groups
-Identify which data (prepan, retro and baseline) each participant has
-Has only prepandemic == 0
-prepandemic and baseline == 1
-prepandemic, baseline, and retrospective == 2
+Identify which data (prepan, retro and baseline) each participant has.
 ++KT: not sure how best to categorise here so this may need some revision. 

### 2020-08-04 PANCHANGE_data_preprocessing2020-07-15.Rmd
Copied the PHQ block and adapted to OCI-R. Awaiting the actual data and variable names to complete the script. Need to add code to all sum scores to exclude participants with missing data.

@@
 Max should be 21.
+
+*** MD - need to adapt for participants with missing data (should be NA)
 ```{r gad sum score prepan}
@@
 Calculate sum score for PHQ-9
+
+*** MD - need to adapt for participants with missing data (should be NA)
 ```{r phq sum score prepan}
@@
 
-## COPING GLAD: GAD-7
+# glad ocir
+
+```{r glad ocir cols}
+glad.ocir.raw <- readRDS(file = paste0(data.raw_path, "/glad/ocir_glad.rds")) #File doesn't exist yet
+dim(glad.ocir.raw)
+colnames(glad.ocir.raw)
+```
+
+```{r glad ocir cleaning}
+glad.ocir.raw.id <- glad.ocir.raw %>%
+  drop_na(externalDataReference) %>% # Drop NAs
+  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
+  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
+  mutate(ID = as.numeric(ID),
+         startDate.glad = startDate) %>% # Rename startDate
+  select(
+    Sample, # Sample
+    ID, # ID
+    ocir.variables_original_name = ocir.variables_new_name,
+    ... ##Add variables to select and rename here
+  ) %>%
+  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
+  mutate_if(is.numeric, ~na_if(., -99)) %>%
+  mutate_if(is.numeric, ~na_if(., -77)) %>%
+  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
+  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
+
+# Inspect dimensions
+dim(glad.ocir.raw.id)
+# Inspect colnames
+colnames(glad.ocir.raw.id)
+#Differences
+dim(glad.ocir.raw)[1]-dim(glad.ocir.raw.id)[1]
+```
+
+Calculate sum score for OCI-R
+
+*** MD - need to adapt for participants with missing data (should be NA)
+```{r ocir sum score prepan}
+# Create vector with scoring key: If the item is reversed coded use -1. 
+# There needs to be the correct number of values for each item in the questionnaire. 
+ocir.items_key_prepan <- c(1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1)
+
+# Create vector with items that are included in sum score
+ocir.items_prepan = c(
+  "ocir.all_variables_listed_here",
+  ##add variables to include in sum score
+  )
+
+# Calulate sum score
+ocir.scored_items_prepan <- scoreItems(keys = ocir.items_key_prepan,
+                                        items = glad.ocir.raw.id[ocir.items_prepan],
+                                        totals = TRUE, 
+                                        missing = TRUE, 
+                                        impute = 'none', 
+                                        min = 0, 
+                                        max = 3)
+# Add in column to tibble
+glad.ocir.raw.id$ocir.sum_score_prepan <- ocir.scored_items_prepan$scores
+
+# Look at values
+glad.ocir.raw.id %>%
+  descr(ocir.sum_score_prepan,
+        stats = "common"
+        )
+```
+
+```{r glad ocir head}
+head(glad.ocir.raw.id)
+```
+
+```{r glad ocir summary}
+summarytools::dfSummary(
+  glad.ocir.raw.id,
+  graph.col = F,
+  valid.col = F
+  )
+```
+
+# COPING GLAD: GAD-7
 

### 2020-08-04 PANCHANGE_data_preprocessing2020-07-15.Rmd
removed old missingness chunks

--- 2020-07-30 PANCHANGE_data_preprocessing2020-07-15.Rmd
@@
 
-#Creating "complete cases" datasets  - NOTE THIS PROBABLY WONT BE USED BUT JUST TO GIVE AN IDEA OF COMPLETE CASES NUMBERS. KT. 
-Complete case data for PHQ, GAD and PCL - 3345 remaining, drop 35,036.
-```{r complete cases only}
-all.items <- c(phq.items_prepan,
-                phq.items_base,
-                phq.items_retro,
-                gad.items_prepan,
-                gad.items_base,
-                gad.items_retro,
-                pcl.items_prepan,
-                pcl.items_base,
-                pcl.items_retro)
-
-dat.no.sex.no.gender.no.age.no.ibd.complete.cases <- dat.no.sex.no.gender.no.age.no.ibd[complete.cases(dat.no.sex.no.gender.no.age.no.ibd[, all.items ]),]
-
-dim(dat.no.sex.no.gender.no.age.no.ibd.complete.cases)
-dim(dat.no.sex.no.gender.no.age.no.ibd)[1]-dim(dat.no.sex.no.gender.no.age.no.ibd.complete.cases)[1]
-```
-
-PHQ
-Complete case data for PHQ baseline (COPING) - 9,260 remaining
-```{r complete cases phq base}
-dat.no.sex.no.gender.no.age.no.ibd.complete.cases.phq.base <- dat.no.sex.no.gender.no.age.no.ibd[complete.cases(dat.no.sex.no.gender.no.age.no.ibd[, phq.items_base ]),]
-
-dim(dat.no.sex.no.gender.no.age.no.ibd.complete.cases.phq.base)
-dim(dat.no.sex.no.gender.no.age.no.ibd)[1]-dim(dat.no.sex.no.gender.no.age.no.ibd.complete.cases.phq.base)[1]
-```
-
-Complete case data for PHQ pre-pandemic (GLAD) - 37,308 remaining
-```{r complete cases phq prepan}
-dat.no.sex.no.gender.no.age.no.ibd.complete.cases.phq.prepan <- dat.no.sex.no.gender.no.age.no.ibd[complete.cases(dat.no.sex.no.gender.no.age.no.ibd[, phq.items_prepan ]),]
-
-dim(dat.no.sex.no.gender.no.age.no.ibd.complete.cases.phq.prepan)
-dim(dat.no.sex.no.gender.no.age.no.ibd)[1]-dim(dat.no.sex.no.gender.no.age.no.ibd.complete.cases.phq.prepan)[1]
-```
-
-Complete case data for PHQ retrospective (COPING) - 9,262 remaining
-```{r complete cases phq retro}
-dat.no.sex.no.gender.no.age.no.ibd.complete.cases.phq.retro <- dat.no.sex.no.gender.no.age.no.ibd[complete.cases(dat.no.sex.no.gender.no.age.no.ibd[, phq.items_retro ]),]
-
-dim(dat.no.sex.no.gender.no.age.no.ibd.complete.cases.phq.retro)
-dim(dat.no.sex.no.gender.no.age.no.ibd)[1]-dim(dat.no.sex.no.gender.no.age.no.ibd.complete.cases.phq.retro)[1]
-```
-
-GAD
-Complete case data for GAD baseline (COPING) - 12,457 remaining
-```{r complete cases gad base}
-dat.no.sex.no.gender.no.age.no.ibd.complete.cases.gad.base <- dat.no.sex.no.gender.no.age.no.ibd[complete.cases(dat.no.sex.no.gender.no.age.no.ibd[, gad.items_base ]),]
-
-dim(dat.no.sex.no.gender.no.age.no.ibd.complete.cases.gad.base)
-dim(dat.no.sex.no.gender.no.age.no.ibd)[1]-dim(dat.no.sex.no.gender.no.age.no.ibd.complete.cases.gad.base)[1]
-```
-
-Complete case data for gad pre-pandemic (GLAD) - 36,149 remaining
-```{r complete cases gad prepan}
-dat.no.sex.no.gender.no.age.no.ibd.complete.cases.gad.prepan <- dat.no.sex.no.gender.no.age.no.ibd[complete.cases(dat.no.sex.no.gender.no.age.no.ibd[, gad.items_prepan ]),]
-
-dim(dat.no.sex.no.gender.no.age.no.ibd.complete.cases.gad.prepan)
-dim(dat.no.sex.no.gender.no.age.no.ibd)[1]-dim(dat.no.sex.no.gender.no.age.no.ibd.complete.cases.gad.prepan)[1]
-```
-
-Complete case data for gad retrospective (COPING) - 8,930 remaining
-```{r complete cases gad retro}
-dat.no.sex.no.gender.no.age.no.ibd.complete.cases.gad.retro <- dat.no.sex.no.gender.no.age.no.ibd[complete.cases(dat.no.sex.no.gender.no.age.no.ibd[, gad.items_retro ]),]
-
-dim(dat.no.sex.no.gender.no.age.no.ibd.complete.cases.gad.retro)
-dim(dat.no.sex.no.gender.no.age.no.ibd)[1]-dim(dat.no.sex.no.gender.no.age.no.ibd.complete.cases.gad.retro)[1]
-```
-
-PCL
-Complete case data for PCL baseline (COPING) - 12,376 remaining
-```{r complete cases pcl base}
-dat.no.sex.no.gender.no.age.no.ibd.complete.cases.pcl.base <- dat.no.sex.no.gender.no.age.no.ibd[complete.cases(dat.no.sex.no.gender.no.age.no.ibd[, pcl.items_base ]),]
-
-dim(dat.no.sex.no.gender.no.age.no.ibd.complete.cases.pcl.base)
-dim(dat.no.sex.no.gender.no.age.no.ibd)[1]-dim(dat.no.sex.no.gender.no.age.no.ibd.complete.cases.pcl.base)[1]
-```
-
-Complete case data for PCL pre-pandemic (GLAD) - 35,176 remaining
-```{r complete cases pcl prepan}
-dat.no.sex.no.gender.no.age.no.ibd.complete.cases.pcl.prepan <- dat.no.sex.no.gender.no.age.no.ibd[complete.cases(dat.no.sex.no.gender.no.age.no.ibd[, pcl.items_prepan ]),]
-
-dim(dat.no.sex.no.gender.no.age.no.ibd.complete.cases.pcl.prepan)
-dim(dat.no.sex.no.gender.no.age.no.ibd)[1]-dim(dat.no.sex.no.gender.no.age.no.ibd.complete.cases.pcl.prepan)[1]
-```
-
-Complete case data for PCL retrospective (COPING) - 4,618 remaining
-```{r complete cases pcl retro}
-dat.no.sex.no.gender.no.age.no.ibd.complete.cases.pcl.retro <- dat.no.sex.no.gender.no.age.no.ibd[complete.cases(dat.no.sex.no.gender.no.age.no.ibd[, pcl.items_retro ]),]
-
-dim(dat.no.sex.no.gender.no.age.no.ibd.complete.cases.pcl.retro)
-dim(dat.no.sex.no.gender.no.age.no.ibd)[1]-dim(dat.no.sex.no.gender.no.age.no.ibd.complete.cases.pcl.retro)[1]
-```
-
 ##Create tidy data on which the exclusion criteria have been applied

### 2020-08-04 PANCHANGE_data_preprocessing2020-07-15.Rmd
added phq 8 item cut off chunks

@@
 
+```{r PHQ baseline missingness 8 items}
+#We need to identify those who have all items APART from the suicide ideation item - to still include these individuals. 
+dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
+  mutate(
+    phq.base_cut_off = 
+      if_else(
+        na_per_person_phq_base == 1 & 
+          is.na(phq.dead_hurting_thoughts_base_numeric), 
+        1,
+        0
+      )
+  )
+
+table(dat.no.sex.no.gender.no.age.no.ibd$phq.base_cut_off)
+```
+
 #PHQ - retrospective
@@
 
+```{r PHQ retro missingness 8 items}
+#We need to identify those who have all items APART from the suicide ideation item - to still include these individuals. 
+dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
+  mutate(
+    phq.retro_cut_off = 
+      if_else(
+        na_per_person_phq_retro == 1 & 
+          is.na(phq.dead_hurting_thoughts_retro_numeric), 
+        1,
+        0
+      )
+  )
+
+table(dat.no.sex.no.gender.no.age.no.ibd$phq.retro_cut_off)
+```
+
 #PHQ - prepandemic
@@
 freq(dat.no.sex.no.gender.no.age.no.ibd$miss_pc_total_phq_prepan)
+```
+
+```{r PHQ prepan missingness 8 items}
+#We need to identify those who have all items APART from the suicide ideation item - to still include these individuals. 
+dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
+  mutate(
+    phq.prepan_cut_off = 
+      if_else(
+        na_per_person_phq_prepan == 1 & 
+          is.na(phq.dead_hurting_thoughts_prepan_numeric), 
+        1,
+        0
+      )
+  )
+
+table(dat.no.sex.no.gender.no.age.no.ibd$phq.prepan_cut_off)
 ```

### 2020-08-04 PANCHANGE_data_preprocessing2020-07-15.Rmd
corrected missingness chunks, added item cut offs and sum score cut offs

@@
 
+#Sum scores missingness cut offs
+KT: This series of chunks creates a "full" sum score for the PHQ, GAD and PCL.
+
+PHQ
+The PHQ sum score is set to NA if they have more than one missing item, and it is not the last suicide ideation item (they do not meet the cut off criteria - phq.base_cut_off)
+```{r sum score cut offs PHQ base}
+dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
+  mutate(
+    phq.sum_score_base_full =
+      if_else(na_per_person_phq_base > 1 & phq.base_cut_off == 0,
+              NA_real_,
+              phq.sum_score_base
+              )
+  )
+
+summary(dat.no.sex.no.gender.no.age.no.ibd$phq.sum_score_base)
+summary(dat.no.sex.no.gender.no.age.no.ibd$phq.sum_score_base_full)
+```
+
+```{r sum score cut offs PHQ prepan}
+dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
+  mutate(
+    phq.sum_score_prepan_full =
+      if_else(na_per_person_phq_prepan > 1 & phq.prepan_cut_off == 0,
+              NA_real_,
+              phq.sum_score_prepan
+              )
+  )
+
+summary(dat.no.sex.no.gender.no.age.no.ibd$phq.sum_score_prepan)
+summary(dat.no.sex.no.gender.no.age.no.ibd$phq.sum_score_prepan_full)
+```
+
+```{r sum score cut offs PHQ retro}
+dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
+  mutate(
+    phq.sum_score_retro_full =
+      if_else(na_per_person_phq_retro > 1 & phq.retro_cut_off == 0,
+              NA_real_,
+              phq.sum_score_retro
+              )
+  )
+
+summary(dat.no.sex.no.gender.no.age.no.ibd$phq.sum_score_retro)
+summary(dat.no.sex.no.gender.no.age.no.ibd$phq.sum_score_retro_full)
+```
+
+GAD
+The GAD sum score is set to NA if they have any missing items
+```{r sum score cut offs GAD base}
+dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
+  mutate(
+    gad.sum_score_base_full =
+      if_else(na_per_person_gad_base > 0,
+              NA_real_,
+              gad.sum_score_base
+              )
+  )
+
+summary(dat.no.sex.no.gender.no.age.no.ibd$gad.sum_score_base)
+summary(dat.no.sex.no.gender.no.age.no.ibd$gad.sum_score_base_full)
+```
+
+```{r sum score cut offs GAD prepan}
+dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
+  mutate(
+    gad.sum_score_prepan_full =
+      if_else(na_per_person_gad_prepan > 0,
+              NA_real_,
+              gad.sum_score_prepan
+              )
+  )
+
+summary(dat.no.sex.no.gender.no.age.no.ibd$gad.sum_score_prepan)
+summary(dat.no.sex.no.gender.no.age.no.ibd$gad.sum_score_prepan_full)
+```
+
+```{r sum score cut offs GAD retro}
+dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
+  mutate(
+    gad.sum_score_retro_full =
+      if_else(na_per_person_gad_retro > 0,
+              NA_real_,
+              gad.sum_score_retro
+              )
+  )
+
+summary(dat.no.sex.no.gender.no.age.no.ibd$gad.sum_score_retro)
+summary(dat.no.sex.no.gender.no.age.no.ibd$gad.sum_score_retro_full)
+```
+
+PCL
+The PCL sum score is set to NA if they have any missing items - only for basline and prepan.
+```{r sum score cut offs PCL base}
+dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
+  mutate(
+    pcl.sum_score_base_full =
+      if_else(na_per_person_pcl_base > 0,
+              NA_real_,
+              pcl.sum_score_base
+              )
+  )
+
+summary(dat.no.sex.no.gender.no.age.no.ibd$pcl.sum_score_base)
+summary(dat.no.sex.no.gender.no.age.no.ibd$pcl.sum_score_base_full)
+```
+
+```{r sum score cut offs PCL prepan}
+dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
+  mutate(
+    pcl.sum_score_prepan_full =
+      if_else(na_per_person_pcl_prepan > 0,
+              NA_real_,
+              pcl.sum_score_prepan
+              )
+  )
+
+summary(dat.no.sex.no.gender.no.age.no.ibd$pcl.sum_score_prepan)
+summary(dat.no.sex.no.gender.no.age.no.ibd$pcl.sum_score_prepan_full)
+```
+
 ##Create tidy data on which the exclusion criteria have been applied

### 2020-08-04 PANCHANGE_data_preprocessing2020-07-15.Rmd
corrected difference score chunks base-prepan

@@
       as.numeric(
-        phq.sum_score_prepan - phq.sum_score_base  # prepandemic sum score MINUS baseline sum score 
+        phq.sum_score_base - phq.sum_score_prepan  # baseline sum score MINUS prepandemic sum score 
       )
@@
       as.numeric(
-        gad.sum_score_prepan - gad.sum_score_base  # prepandemic sum score MINUS baseline sum score 
+        gad.sum_score_base - gad.sum_score_prepan  # baseline sum score MINUS prepandemic sum score 
       )
@@
       as.numeric(
-        pcl.sum_score_prepan - pcl.sum_score_base  # prepandemic sum score MINUS baseline sum score 
+        pcl.sum_score_base - pcl.sum_score_prepan  # baseline sum score MINUS prepandemic sum score 
       )

### 2020-08-04 PANCHANGE_data_preprocessing2020-07-15.Rmd
corrected data group chunks for PHQ, GAD, PCL

@@
 Identify which data (prepan, retro and baseline) each participant has.
-++KT: not sure how best to categorise here so this may need some revision. 
-```{r data level groups}
+```{r data level groups PHQ}
 dat.glad <- dat.glad %>%
   mutate(
-    data_group_full_numeric =
+    data_group_phq_numeric =
       case_when(
-        !is.na(startDate.glad) & !is.na(startDate.coping.glad) & na_per_person_phq_retro == 0  & na_per_person_gad_retro == 0 & na_per_person_pcl_retro == 0 ~ 5,
-        !is.na(startDate.glad) & !is.na(startDate.coping.glad) & na_per_person_pcl_retro == 0 ~ 4, #in GLAD, in COPING and have no missing PCL-retro items
-        !is.na(startDate.glad) & !is.na(startDate.coping.glad) & na_per_person_gad_retro == 0 ~ 3, #in GLAD, in COPING and have no missing GAD-retro items
-        !is.na(startDate.glad) & !is.na(startDate.coping.glad) & na_per_person_phq_retro == 0 ~ 2, #in GLAD, in COPING and have no missing PHQ-retro items
-        !is.na(startDate.glad) & !is.na(startDate.coping.glad) ~ 1,
-        !is.na(startDate.glad) & is.na(startDate.coping.glad) ~ 0
+        na_per_person_phq_base == 0 & na_per_person_phq_prepan == 0 & na_per_person_phq_retro == 0 ~ 5, #all complete baseline, prepan and retro
+        na_per_person_phq_base != 0 & na_per_person_phq_prepan != 0 & na_per_person_phq_retro == 0  ~ 4, #retro data only
+        na_per_person_phq_base == 0 & na_per_person_phq_prepan != 0 & na_per_person_phq_retro != 0  ~ 3, #baseline data only
+        na_per_person_phq_base == 0 & na_per_person_phq_prepan == 0 & na_per_person_phq_retro != 0  ~ 2, #prepan and baseline data only
+        na_per_person_phq_base == 0 & na_per_person_phq_prepan != 0 & na_per_person_phq_retro == 0 ~ 1,  #baseline and retro data only
+        na_per_person_phq_base != 0 & na_per_person_phq_prepan == 0 & na_per_person_phq_retro != 0  ~ 0  #prepan data only
       )
@@
   mutate(
-    data_group_full = 
+    data_group_phq = 
       recode_factor(
-        data_group_full_numeric,
+        data_group_phq_numeric,
         "0" = "Only prepandemic data",
-        "1" = "Prepandemic and baseline data",
-        "2" = "Prepandemic, baseline and retrospective PHQ data",
-        "3" = "Prepandemic, baseline and retrospective GAD data",
-        "4" = "Prepandemic, baseline and retrospective PCL data",
+        "1" = "Baseline and retrospective data",
+        "2" = "Prepandemic and baseline data",
+        "3" = "Baseline data only",
+        "4" = "Retrospective data only",
         "5" = "All prepandemic, baseline and retrospective data"
@@
 
-table(dat.glad$data_group_full)
+table(dat.glad$data_group_phq)
+```
+
+GAD
+```{r data level groups GAD}
+dat.glad <- dat.glad %>%
+  mutate(
+    data_group_gad_numeric =
+      case_when(
+        na_per_person_gad_base == 0 & na_per_person_gad_prepan == 0 & na_per_person_gad_retro == 0 ~ 5, #all complete baseline, prepan and retro
+        na_per_person_gad_base != 0 & na_per_person_gad_prepan != 0 & na_per_person_gad_retro == 0  ~ 4, #retro data only
+        na_per_person_gad_base == 0 & na_per_person_gad_prepan != 0 & na_per_person_gad_retro != 0  ~ 3, #baseline data only
+        na_per_person_gad_base == 0 & na_per_person_gad_prepan == 0 & na_per_person_gad_retro != 0  ~ 2, #prepan and baseline data only
+        na_per_person_gad_base == 0 & na_per_person_gad_prepan != 0 & na_per_person_gad_retro == 0 ~ 1,  #baseline and retro data only
+        na_per_person_gad_base != 0 & na_per_person_gad_prepan == 0 & na_per_person_gad_retro != 0  ~ 0  #prepan data only
+      )
+  )
+
+dat.glad <- dat.glad %>%
+  mutate(
+    data_group_gad = 
+      recode_factor(
+        data_group_gad_numeric,
+        "0" = "Only prepandemic data",
+        "1" = "Baseline and retrospective data",
+        "2" = "Prepandemic and baseline data",
+        "3" = "Baseline data only",
+        "4" = "Retrospective data only",
+        "5" = "All prepandemic, baseline and retrospective data"
+      )
+  )
+
+table(dat.glad$data_group_gad)
+```
+
+PCL
+```{r data level groups PCL}
+dat.glad <- dat.glad %>%
+  mutate(
+    data_group_pcl_numeric =
+      case_when(
+        na_per_person_pcl_base == 0 & na_per_person_pcl_prepan == 0 & na_per_person_pcl_retro == 0 ~ 5, #all complete baseline, prepan and retro
+        na_per_person_pcl_base != 0 & na_per_person_pcl_prepan != 0 & na_per_person_pcl_retro == 0  ~ 4, #retro data only
+        na_per_person_pcl_base == 0 & na_per_person_pcl_prepan != 0 & na_per_person_pcl_retro != 0  ~ 3, #baseline data only
+        na_per_person_pcl_base == 0 & na_per_person_pcl_prepan == 0 & na_per_person_pcl_retro != 0  ~ 2, #prepan and baseline data only
+        na_per_person_pcl_base == 0 & na_per_person_pcl_prepan != 0 & na_per_person_pcl_retro == 0 ~ 1,  #baseline and retro data only
+        na_per_person_pcl_base != 0 & na_per_person_pcl_prepan == 0 & na_per_person_pcl_retro != 0  ~ 0  #prepan data only
+      )
+  )
+
+dat.glad <- dat.glad %>%
+  mutate(
+    data_group_pcl = 
+      recode_factor(
+        data_group_pcl_numeric,
+        "0" = "Only prepandemic data",
+        "1" = "Baseline and retrospective data",
+        "2" = "Prepandemic and baseline data",
+        "3" = "Baseline data only",
+        "4" = "Retrospective data only",
+        "5" = "All prepandemic, baseline and retrospective data"
+      )
+  )
+
+table(dat.glad$data_group_pcl)
 ```

### 2020-08-04 PANCHANGE_data_preprocessing2020-07-15.Rmd
Added path for OCI-R data and variable names to the cleaning block

--- 2020-08-04 PANCHANGE_data_preprocessing2020-07-15.Rmd
@@
 
-## COPING GLAD: GAD-7
+# glad ocir
+
+```{r glad ocir cols}
+glad.ocir.raw <- readRDS(file = paste0(data.raw_path, "/2020-08-03/glad/ocir_glad.rds"))
+dim(glad.ocir.raw)
+colnames(glad.ocir.raw)
+```
+
+```{r glad ocir cleaning}
+glad.ocir.raw.id <- glad.ocir.raw %>%
+  drop_na(externalDataReference) %>% # Drop NAs
+  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
+  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
+  mutate(ID = as.numeric(ID),
+         startDate.glad = startDate) %>% # Rename startDate
+  select(
+    Sample, # Sample
+    ID, # ID
+    ocir.i_repeatedly_check_doors_windows_drawers_etc_prepan = ocir.i_repeatedly_check_doors_windows_drawers_etc.,
+    ocir.arranged_things_change_upset_prepan = ocir.arranged_things_change_upset,
+    ocir.repeat_feel_numbers_prepan = ocir.repeat_feel_numbers,
+    ocir.clean_simply_wash_feel_prepan = ocir.clean_simply_wash_feel,
+    ocir.mind_upset_unpleasant_thoughts_prepan = ocir.mind_upset_unpleasant_thoughts,
+    ocir.afraid_avoid_throwing_things_prepan = ocir.afraid_avoid_throwing_things,
+    ocir.light_switches_water_taps_prepan = ocir.light_switches_water_taps,
+    ocir.arranged_things_prepan = ocir.arranged_things,
+    ocir.good_feel_bad_numbers_prepan = ocir.good_feel_bad_numbers,
+    ocir.hands_longer_wash_prepan = ocir.hands_longer_wash,
+    ocir.saved_things_prepan = ocir.saved_things,
+    ocir.frequently_difficulty_rid_nasty_prepan = ocir.frequently_difficulty_rid_nasty,
+    ocir.i_check_things_more_often_than_necessary_prepan = ocir.i_check_things_more_often_than_necessary.,
+    ocir.arranged_properly_objects_upset_prepan = ocir.arranged_properly_objects_upset,
+    ocir.feel_compelled_count_things_prepan = ocir.feel_compelled_count_things,
+    ocir.strangers_touch_touched_difficult_prepan = ocir.strangers_touch_touched_difficult,
+    ocir.control_difficult_find_thoughts_prepan = ocir.control_difficult_find_thoughts,
+    ocir.i_collect_things_i_dont_need_prepan = ocir.i_collect_things_i_dont_need
+  ) %>%
+  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
+  mutate_if(is.numeric, ~na_if(., -99)) %>%
+  mutate_if(is.numeric, ~na_if(., -77)) %>%
+  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
+  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
+
+# Inspect dimensions
+dim(glad.ocir.raw.id)
+# Inspect colnames
+colnames(glad.ocir.raw.id)
+#Differences
+dim(glad.ocir.raw)[1]-dim(glad.ocir.raw.id)[1]
+```
+
+Calculate sum score for OCI-R
+
+*** MD - need to adapt for participants with missing data (should be NA)
+```{r ocir sum score prepan}
+# Create vector with scoring key: If the item is reversed coded use -1. 
+# There needs to be the correct number of values for each item in the questionnaire. 
+ocir.items_key_prepan <- c(1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1)
+
+# Create vector with items that are included in sum score
+ocir.items_prepan = c(
+  "ocir.all_variables_listed_here",
+  ##add variables to include in sum score
+  )
+
+# Calulate sum score
+ocir.scored_items_prepan <- scoreItems(keys = ocir.items_key_prepan,
+                                        items = glad.ocir.raw.id[ocir.items_prepan],
+                                        totals = TRUE, 
+                                        missing = TRUE, 
+                                        impute = 'none', 
+                                        min = 0, 
+                                        max = 3)
+# Add in column to tibble
+glad.ocir.raw.id$ocir.sum_score_prepan <- ocir.scored_items_prepan$scores
+
+# Look at values
+glad.ocir.raw.id %>%
+  descr(ocir.sum_score_prepan,
+        stats = "common"
+        )
+```
+
+```{r glad ocir head}
+head(glad.ocir.raw.id)
+```
+
+```{r glad ocir summary}
+summarytools::dfSummary(
+  glad.ocir.raw.id,
+  graph.col = F,
+  valid.col = F
+  )
+```
+
+# COPING GLAD: GAD-7
 
@@
 
-```{r PHQ baseline missingness 8 items}
-#We need to identify those who have all items APART from the suicide ideation item - to still include these individuals. 
-dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
-  mutate(
-    phq.base_cut_off = 
-      if_else(
-        na_per_person_phq_base == 1 & 
-          is.na(phq.dead_hurting_thoughts_base_numeric), 
-        1,
-        0
-      )
-  )
-
-table(dat.no.sex.no.gender.no.age.no.ibd$phq.base_cut_off)
-```
-
 #PHQ - retrospective
@@
 
-```{r PHQ retro missingness 8 items}
-#We need to identify those who have all items APART from the suicide ideation item - to still include these individuals. 
-dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
-  mutate(
-    phq.retro_cut_off = 
-      if_else(
-        na_per_person_phq_retro == 1 & 
-          is.na(phq.dead_hurting_thoughts_retro_numeric), 
-        1,
-        0
-      )
-  )
-
-table(dat.no.sex.no.gender.no.age.no.ibd$phq.retro_cut_off)
-```
-
 #PHQ - prepandemic
@@
 freq(dat.no.sex.no.gender.no.age.no.ibd$miss_pc_total_phq_prepan)
-```
-
-```{r PHQ prepan missingness 8 items}
-#We need to identify those who have all items APART from the suicide ideation item - to still include these individuals. 
-dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
-  mutate(
-    phq.prepan_cut_off = 
-      if_else(
-        na_per_person_phq_prepan == 1 & 
-          is.na(phq.dead_hurting_thoughts_prepan_numeric), 
-        1,
-        0
-      )
-  )
-
-table(dat.no.sex.no.gender.no.age.no.ibd$phq.prepan_cut_off)
 ```
@@
 
-#Sum scores missingness cut offs
-KT: This series of chunks creates a "full" sum score for the PHQ, GAD and PCL.
+#Creating "complete cases" datasets  - NOTE THIS PROBABLY WONT BE USED BUT JUST TO GIVE AN IDEA OF COMPLETE CASES NUMBERS. KT. 
+Complete case data for PHQ, GAD and PCL - 3345 remaining, drop 35,036.
+```{r complete cases only}
+all.items <- c(phq.items_prepan,
+                phq.items_base,
+                phq.items_retro,
+                gad.items_prepan,
+                gad.items_base,
+                gad.items_retro,
+                pcl.items_prepan,
+                pcl.items_base,
+                pcl.items_retro)
+
+dat.no.sex.no.gender.no.age.no.ibd.complete.cases <- dat.no.sex.no.gender.no.age.no.ibd[complete.cases(dat.no.sex.no.gender.no.age.no.ibd[, all.items ]),]
+
+dim(dat.no.sex.no.gender.no.age.no.ibd.complete.cases)
+dim(dat.no.sex.no.gender.no.age.no.ibd)[1]-dim(dat.no.sex.no.gender.no.age.no.ibd.complete.cases)[1]
+```
 
 PHQ
-The PHQ sum score is set to NA if they have more than one missing item, and it is not the last suicide ideation item (they do not meet the cut off criteria - phq.base_cut_off)
-```{r sum score cut offs PHQ base}
-dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
-  mutate(
-    phq.sum_score_base_full =
-      if_else(na_per_person_phq_base > 1 & phq.base_cut_off == 0,
-              NA_real_,
-              phq.sum_score_base
-              )
-  )
-
-summary(dat.no.sex.no.gender.no.age.no.ibd$phq.sum_score_base)
-summary(dat.no.sex.no.gender.no.age.no.ibd$phq.sum_score_base_full)
-```
-
-```{r sum score cut offs PHQ prepan}
-dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
-  mutate(
-    phq.sum_score_prepan_full =
-      if_else(na_per_person_phq_prepan > 1 & phq.prepan_cut_off == 0,
-              NA_real_,
-              phq.sum_score_prepan
-              )
-  )
-
-summary(dat.no.sex.no.gender.no.age.no.ibd$phq.sum_score_prepan)
-summary(dat.no.sex.no.gender.no.age.no.ibd$phq.sum_score_prepan_full)
-```
-
-```{r sum score cut offs PHQ retro}
-dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
-  mutate(
-    phq.sum_score_retro_full =
-      if_else(na_per_person_phq_retro > 1 & phq.retro_cut_off == 0,
-              NA_real_,
-              phq.sum_score_retro
-              )
-  )
-
-summary(dat.no.sex.no.gender.no.age.no.ibd$phq.sum_score_retro)
-summary(dat.no.sex.no.gender.no.age.no.ibd$phq.sum_score_retro_full)
+Complete case data for PHQ baseline (COPING) - 9,260 remaining
+```{r complete cases phq base}
+dat.no.sex.no.gender.no.age.no.ibd.complete.cases.phq.base <- dat.no.sex.no.gender.no.age.no.ibd[complete.cases(dat.no.sex.no.gender.no.age.no.ibd[, phq.items_base ]),]
+
+dim(dat.no.sex.no.gender.no.age.no.ibd.complete.cases.phq.base)
+dim(dat.no.sex.no.gender.no.age.no.ibd)[1]-dim(dat.no.sex.no.gender.no.age.no.ibd.complete.cases.phq.base)[1]
+```
+
+Complete case data for PHQ pre-pandemic (GLAD) - 37,308 remaining
+```{r complete cases phq prepan}
+dat.no.sex.no.gender.no.age.no.ibd.complete.cases.phq.prepan <- dat.no.sex.no.gender.no.age.no.ibd[complete.cases(dat.no.sex.no.gender.no.age.no.ibd[, phq.items_prepan ]),]
+
+dim(dat.no.sex.no.gender.no.age.no.ibd.complete.cases.phq.prepan)
+dim(dat.no.sex.no.gender.no.age.no.ibd)[1]-dim(dat.no.sex.no.gender.no.age.no.ibd.complete.cases.phq.prepan)[1]
+```
+
+Complete case data for PHQ retrospective (COPING) - 9,262 remaining
+```{r complete cases phq retro}
+dat.no.sex.no.gender.no.age.no.ibd.complete.cases.phq.retro <- dat.no.sex.no.gender.no.age.no.ibd[complete.cases(dat.no.sex.no.gender.no.age.no.ibd[, phq.items_retro ]),]
+
+dim(dat.no.sex.no.gender.no.age.no.ibd.complete.cases.phq.retro)
+dim(dat.no.sex.no.gender.no.age.no.ibd)[1]-dim(dat.no.sex.no.gender.no.age.no.ibd.complete.cases.phq.retro)[1]
 ```
@@
 GAD
-The GAD sum score is set to NA if they have any missing items
-```{r sum score cut offs GAD base}
-dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
-  mutate(
-    gad.sum_score_base_full =
-      if_else(na_per_person_gad_base > 0,
-              NA_real_,
-              gad.sum_score_base
-              )
-  )
-
-summary(dat.no.sex.no.gender.no.age.no.ibd$gad.sum_score_base)
-summary(dat.no.sex.no.gender.no.age.no.ibd$gad.sum_score_base_full)
-```
-
-```{r sum score cut offs GAD prepan}
-dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
-  mutate(
-    gad.sum_score_prepan_full =
-      if_else(na_per_person_gad_prepan > 0,
-              NA_real_,
-              gad.sum_score_prepan
-              )
-  )
-
-summary(dat.no.sex.no.gender.no.age.no.ibd$gad.sum_score_prepan)
-summary(dat.no.sex.no.gender.no.age.no.ibd$gad.sum_score_prepan_full)
-```
-
-```{r sum score cut offs GAD retro}
-dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
-  mutate(
-    gad.sum_score_retro_full =
-      if_else(na_per_person_gad_retro > 0,
-              NA_real_,
-              gad.sum_score_retro
-              )
-  )
-
-summary(dat.no.sex.no.gender.no.age.no.ibd$gad.sum_score_retro)
-summary(dat.no.sex.no.gender.no.age.no.ibd$gad.sum_score_retro_full)
+Complete case data for GAD baseline (COPING) - 12,457 remaining
+```{r complete cases gad base}
+dat.no.sex.no.gender.no.age.no.ibd.complete.cases.gad.base <- dat.no.sex.no.gender.no.age.no.ibd[complete.cases(dat.no.sex.no.gender.no.age.no.ibd[, gad.items_base ]),]
+
+dim(dat.no.sex.no.gender.no.age.no.ibd.complete.cases.gad.base)
+dim(dat.no.sex.no.gender.no.age.no.ibd)[1]-dim(dat.no.sex.no.gender.no.age.no.ibd.complete.cases.gad.base)[1]
+```
+
+Complete case data for gad pre-pandemic (GLAD) - 36,149 remaining
+```{r complete cases gad prepan}
+dat.no.sex.no.gender.no.age.no.ibd.complete.cases.gad.prepan <- dat.no.sex.no.gender.no.age.no.ibd[complete.cases(dat.no.sex.no.gender.no.age.no.ibd[, gad.items_prepan ]),]
+
+dim(dat.no.sex.no.gender.no.age.no.ibd.complete.cases.gad.prepan)
+dim(dat.no.sex.no.gender.no.age.no.ibd)[1]-dim(dat.no.sex.no.gender.no.age.no.ibd.complete.cases.gad.prepan)[1]
+```
+
+Complete case data for gad retrospective (COPING) - 8,930 remaining
+```{r complete cases gad retro}
+dat.no.sex.no.gender.no.age.no.ibd.complete.cases.gad.retro <- dat.no.sex.no.gender.no.age.no.ibd[complete.cases(dat.no.sex.no.gender.no.age.no.ibd[, gad.items_retro ]),]
+
+dim(dat.no.sex.no.gender.no.age.no.ibd.complete.cases.gad.retro)
+dim(dat.no.sex.no.gender.no.age.no.ibd)[1]-dim(dat.no.sex.no.gender.no.age.no.ibd.complete.cases.gad.retro)[1]
 ```
@@
 PCL
-The PCL sum score is set to NA if they have any missing items - only for basline and prepan.
-```{r sum score cut offs PCL base}
-dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
-  mutate(
-    pcl.sum_score_base_full =
-      if_else(na_per_person_pcl_base > 0,
-              NA_real_,
-              pcl.sum_score_base
-              )
-  )
-
-summary(dat.no.sex.no.gender.no.age.no.ibd$pcl.sum_score_base)
-summary(dat.no.sex.no.gender.no.age.no.ibd$pcl.sum_score_base_full)
-```
-
-```{r sum score cut offs PCL prepan}
-dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
-  mutate(
-    pcl.sum_score_prepan_full =
-      if_else(na_per_person_pcl_prepan > 0,
-              NA_real_,
-              pcl.sum_score_prepan
-              )
-  )
-
-summary(dat.no.sex.no.gender.no.age.no.ibd$pcl.sum_score_prepan)
-summary(dat.no.sex.no.gender.no.age.no.ibd$pcl.sum_score_prepan_full)
+Complete case data for PCL baseline (COPING) - 12,376 remaining
+```{r complete cases pcl base}
+dat.no.sex.no.gender.no.age.no.ibd.complete.cases.pcl.base <- dat.no.sex.no.gender.no.age.no.ibd[complete.cases(dat.no.sex.no.gender.no.age.no.ibd[, pcl.items_base ]),]
+
+dim(dat.no.sex.no.gender.no.age.no.ibd.complete.cases.pcl.base)
+dim(dat.no.sex.no.gender.no.age.no.ibd)[1]-dim(dat.no.sex.no.gender.no.age.no.ibd.complete.cases.pcl.base)[1]
+```
+
+Complete case data for PCL pre-pandemic (GLAD) - 35,176 remaining
+```{r complete cases pcl prepan}
+dat.no.sex.no.gender.no.age.no.ibd.complete.cases.pcl.prepan <- dat.no.sex.no.gender.no.age.no.ibd[complete.cases(dat.no.sex.no.gender.no.age.no.ibd[, pcl.items_prepan ]),]
+
+dim(dat.no.sex.no.gender.no.age.no.ibd.complete.cases.pcl.prepan)
+dim(dat.no.sex.no.gender.no.age.no.ibd)[1]-dim(dat.no.sex.no.gender.no.age.no.ibd.complete.cases.pcl.prepan)[1]
+```
+
+Complete case data for PCL retrospective (COPING) - 4,618 remaining
+```{r complete cases pcl retro}
+dat.no.sex.no.gender.no.age.no.ibd.complete.cases.pcl.retro <- dat.no.sex.no.gender.no.age.no.ibd[complete.cases(dat.no.sex.no.gender.no.age.no.ibd[, pcl.items_retro ]),]
+
+dim(dat.no.sex.no.gender.no.age.no.ibd.complete.cases.pcl.retro)
+dim(dat.no.sex.no.gender.no.age.no.ibd)[1]-dim(dat.no.sex.no.gender.no.age.no.ibd.complete.cases.pcl.retro)[1]
 ```

### 2020-08-04 PANCHANGE_data_preprocessing2020-07-15.Rmd
Created the OCI-R sum score (still need to exclude participants with missing data).

@@
 ocir.items_prepan = c(
-  "ocir.all_variables_listed_here",
-  ##add variables to include in sum score
+  "ocir.i_repeatedly_check_doors_windows_drawers_etc_prepan",
+  "ocir.arranged_things_change_upset_prepan",
+  "ocir.repeat_feel_numbers_prepan",
+  "ocir.clean_simply_wash_feel_prepan",
+  "ocir.mind_upset_unpleasant_thoughts_prepan",
+  "ocir.afraid_avoid_throwing_things_prepan",
+  "ocir.light_switches_water_taps_prepan",
+  "ocir.arranged_things_prepan",
+  "ocir.good_feel_bad_numbers_prepan",
+  "ocir.hands_longer_wash_prepan",
+  "ocir.saved_things_prepan",
+  "ocir.frequently_difficulty_rid_nasty_prepan",
+  "ocir.i_check_things_more_often_than_necessary_prepan",
+  "ocir.arranged_properly_objects_upset_prepan",
+  "ocir.feel_compelled_count_things_prepan",
+  "ocir.strangers_touch_touched_difficult_prepan",
+  "ocir.control_difficult_find_thoughts_prepan",
+  "ocir.i_collect_things_i_dont_need_prepan"
   )
@@
                                         min = 0, 
-                                        max = 3)
+                                        max = 4)
 # Add in column to tibble

### 2020-08-04 PANCHANGE_data_preprocessing2020-07-15.Rmd
Added GLAD COPING OCI-R section. Read in data and completed cleaning chunk.

@@
 
+# glad COPING ocir
+
+```{r coping glad ocir cols}
+coping.glad.ocir.raw <- readRDS(file = paste0(data.raw_path, "/2020-08-03/glad/ocir_coping_glad.rds"))
+dim(coping.glad.ocir.raw)
+colnames(coping.glad.ocir.raw)
+```
+
+```{r coping glad ocir summary labels}
+summarytools::dfSummary(
+  coping.glad.ocir.raw,
+  graph.col = F,
+  valid.col = F
+  #labels.col = F
+)
+```
+
+Will need to double check these namings once we have the new cleaned data -- KT. 
+```{r coping glad ocir cleaning}
+coping.glad.ocir.raw.id <- coping.glad.ocir.raw %>%
+  drop_na(externalDataReference) %>% # Drop NAs
+  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
+  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
+  mutate(ID = as.numeric(ID),
+         startDate.glad = startDate) %>% # Rename startDate
+  select(
+    Sample, # Sample
+    ID, # ID
+    ocir.i_repeatedly_check_doors_windows_drawers_etc_retro = ocir.i_repeatedly_check_doors_windows_drawers_etc.,
+    ocir.arranged_things_change_upset_retro = ocir.arranged_things_change_upset,
+    ocir.repeat_feel_numbers_retro = ocir.numbers_repeat_feel, ## Different from GLAD prepandemic
+    ocir.clean_simply_wash_feel_retro = ocir.feel_contaminated_clean_simply, ## Different from GLAD prepandemic
+    ocir.mind_upset_unpleasant_thoughts_retro = ocir.mind_upset_unpleasant_thoughts,
+    ocir.afraid_avoid_throwing_things_retro = ocir.afraid_avoid_throwing_things,
+    ocir.light_switches_water_taps_retro = ocir.light_switches_water_taps,
+    ocir.arranged_things_retro = ocir.arranged_things,
+    ocir.good_feel_bad_numbers_retro = ocir.bad_numbers_good_feel, ## Different from GLAD prepandemic
+    ocir.hands_longer_wash_retro = ocir.longer_hands_wash, ## Different from GLAD prepandemic
+    ocir.saved_things_retro = ocir.saved_things,
+    ocir.frequently_difficulty_rid_nasty_retro = ocir.frequently_rid_difficulty_nasty, ## Different from GLAD prepandemic
+    ocir.i_check_things_more_often_than_necessary_retro = ocir.i_check_things_more_often_than_necessary.,
+    ocir.arranged_properly_objects_upset_retro = ocir.arranged_properly_objects_upset,
+    ocir.feel_compelled_count_things_retro = ocir.feel_compelled_count_things,
+    ocir.strangers_touch_touched_difficult_retro = ocir.strangers_touch_touched_object, ## Different from GLAD prepandemic
+    ocir.control_difficult_find_thoughts_retro = ocir.control_find_difficult_thoughts, ## Different from GLAD prepandemic
+    ocir.i_collect_things_i_dont_need_retro = ocir.i_collect_things_i_dont_need., ## Different from GLAD prepandemic
+    ocir.i_repeatedly_check_doors_windows_drawers_etc_base = ocir.i_repeatedly_check_doors_windows_drawers_etc..1,
+    ocir.arranged_things_change_upset_base = ocir.arranged_things_change_upset.1,
+    ocir.repeat_feel_numbers_base = ocir.numbers_repeat_feel.1, ## Different from GLAD prepandemic
+    ocir.clean_simply_wash_feel_base = ocir.feel_contaminated_clean_simply.1, ## Different from GLAD prepandemic
+    ocir.mind_upset_unpleasant_thoughts_base = ocir.mind_upset_unpleasant_thoughts.1,
+    ocir.afraid_avoid_throwing_things_base = ocir.afraid_avoid_throwing_things.1,
+    ocir.light_switches_water_taps_base = ocir.light_switches_water_taps.1,
+    ocir.arranged_things_base = ocir.arranged_things.1,
+    ocir.good_feel_bad_numbers_base = ocir.bad_numbers_good_feel.1, ## Different from GLAD prepandemic
+    ocir.hands_longer_wash_base = ocir.longer_hands_wash.1, ## Different from GLAD prepandemic
+    ocir.saved_things_base = ocir.saved_things.1,
+    ocir.frequently_difficulty_rid_nasty_base = ocir.frequently_rid_difficulty_nasty.1, ## Different from GLAD prepandemic
+    ocir.i_check_things_more_often_than_necessary_base = ocir.i_check_things_more_often_than_necessary..1,
+    ocir.arranged_properly_objects_upset_base = ocir.arranged_properly_objects_upset.1,
+    ocir.feel_compelled_count_things_base = ocir.feel_compelled_count_things.1,
+    ocir.strangers_touch_touched_difficult_base = ocir.strangers_touch_touched_object.1, ## Different from GLAD prepandemic
+    ocir.control_difficult_find_thoughts_base = ocir.control_find_difficult_thoughts.1, ## Different from GLAD prepandemic
+    ocir.i_collect_things_i_dont_need_base = ocir.i_collect_things_i_dont_need..1
+  ) %>%
+  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
+  mutate_if(is.numeric, ~na_if(., -99)) %>%
+  mutate_if(is.numeric, ~na_if(., -77)) %>%
+  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
+  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
+
+# Inspect dimensions
+dim(coping.glad.ocir.raw.id)
+# Inspect colnames
+colnames(coping.glad.ocir.raw.id)
+#Differences
+dim(coping.glad.ocir.raw)[1]-dim(coping.glad.ocir.raw.id)[1]
+```
+
+Calculate sum score for OCI-R retro
+```{r coping ocir sum score retro}
+# Create vector with scoring key: If the item is reversed coded use -1. 
+# There needs to be the correct number of values for each item in the questionnaire. 
+ocir.items_key_retro <- c(1,1,1,1,1,1,1,1,1)
+
+# Create vector with items that are included in total score
+ocir.items_retro = c(
+  "ocir.i_repeatedly_check_doors_windows_drawers_etc_retro",
+  "ocir.arranged_things_change_upset_retro",
+  "ocir.repeat_feel_numbers_retro",
+  "ocir.clean_simply_wash_feel_retro",
+  "ocir.mind_upset_unpleasant_thoughts_retro",
+  "ocir.afraid_avoid_throwing_things_retro",
+  "ocir.light_switches_water_taps_retro",
+  "ocir.arranged_things_retro",
+  "ocir.good_feel_bad_numbers_retro",
+  "ocir.hands_longer_wash_retro",
+  "ocir.saved_things_retro",
+  "ocir.frequently_difficulty_rid_nasty_retro",
+  "ocir.i_check_things_more_often_than_necessary_retro",
+  "ocir.arranged_properly_objects_upset_retro",
+  "ocir.feel_compelled_count_things_retro",
+  "ocir.strangers_touch_touched_difficult_retro",
+  "ocir.control_difficult_find_thoughts_retro",
+  "ocir.i_collect_things_i_dont_need_retro"
+)
+
+# Calulate total score
+ocir.scored_items_retro <- scoreItems(keys = ocir.items_key_retro,
+                                     items = coping.glad.ocir.raw.id[ocir.items_retro],
+                                     totals = TRUE, 
+                                     missing = TRUE, 
+                                     impute = 'none', 
+                                     min = 0, 
+                                     max = 3)
+# Add in column to tibble
+coping.glad.ocir.raw.id$ocir.sum_score_retro <- ocir.scored_items_retro$scores
+
+# Look at values
+coping.glad.ocir.raw.id %>%
+  descr(ocir.sum_score_retro,
+        stats = "common"
+  )
+```
+
+Calculate sum score for OCI-R base
+```{r coping ocir sum score base}
+# Create vector with scoring key: If the item is reversed coded use -1. 
+# There needs to be the correct number of values for each item in the questionnaire. 
+ocir.items_key_base <- c(1,1,1,1,1,1,1,1,1)
+
+# Create vector with items that are included in total score
+ocir.items_base = c(
+  "ocir.little_interest_or_pleasure_in_doing_things_base_numeric",
+"ocir.feeling_down_depressed_or_hopeless_base_numeric",
+"ocir.staying_asleep_sleeping_trouble_base_numeric",
+"ocir.feeling_tired_or_having_little_energy_base_numeric",
+"ocir.poor_appetite_or_overeating_base_numeric",
+"ocir.feeling_bad_failure_family_base_numeric",
+"ocir.trouble_concentrating_reading_newspaper_base_numeric",
+"ocir.moving_fidgety_noticed_opposite_base_numeric",
+"ocir.dead_hurting_thoughts_base_numeric"
+)
+
+# Calulate total score
+ocir.scored_items_base <- scoreItems(keys = ocir.items_key_base,
+                                    items = coping.glad.ocir.raw.id[ocir.items_base],
+                                    totals = TRUE, 
+                                    missing = TRUE, 
+                                    impute = 'none', 
+                                    min = 0, 
+                                    max = 3)
+# Add in column to tibble
+coping.glad.ocir.raw.id$ocir.sum_score_base <- ocir.scored_items_base$scores
+
+# Look at values
+coping.glad.ocir.raw.id %>%
+  descr(ocir.sum_score_base,
+        stats = "common"
+  )
+```
+
+```{r coping glad ocir head}
+head(coping.glad.ocir.raw.id)
+```
+
+```{r coping glad ocir summary}
+summarytools::dfSummary(
+  coping.glad.ocir.raw.id,
+  graph.col = F,
+  valid.col = F,
+  labels.col = F)
+```
+
 # Join tibbles together
@@
 PHQ Missingness NAs per person - count and percentages
-```{r PHQ basline missingness}
+```{r PHQ baseline missingness}
 dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
@@
 GAD Missingness NAs per person - count and percentages
-```{r gad basline missingness}
+```{r gad baseline missingness}
 dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
@@
 PCL Missingness NAs per person - count and percentages
-```{r pcl basline missingness}
+```{r pcl baseline missingness}
 dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
@@
 dat.no.sex.no.gender.no.age.no.ibd.missingness <- dat.no.sex.no.gender.no.age.no.ibd
+```
+
+#OCI-R - baseline
+OCI-R Missingness NAs per person - count and percentages
+```{r OCI-R baseline missingness}
+dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
+  mutate(
+    na_per_person_ocir_base =         # variable for NA per person
+      rowSums(                       
+        is.na(dat.no.sex.no.gender.no.age.no.ibd # sum the rows that are NA
+          [,colnames(dat.no.sex.no.gender.no.age.no.ibd) #for all the rows and columns that are in the OCI-R items at baseline
+           %in%
+             ocir.items_base]
+        )
+    )
+  )
+
+freq(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_ocir_base) #have a look at the frequency
+
+dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>% #NA per person as a percentage
+  mutate(
+    miss_pc_total_ocir_base = 
+      na_per_person_ocir_base/9 # NA per person divided by the amount of items
+  )
+
+freq(dat.no.sex.no.gender.no.age.no.ibd$miss_pc_total_ocir_base)
+```
+
+#OCI-R - retrospective
+OCI-R Missingness NAs per person - count and percentages
+```{r OCI-R retrospective missingness}
+dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
+  mutate(
+    na_per_person_ocir_retro =         # variable for NA per person
+      rowSums(                       
+        is.na(dat.no.sex.no.gender.no.age.no.ibd # sum the rows that are NA
+          [,colnames(dat.no.sex.no.gender.no.age.no.ibd) #for all the rows and columns that are in the OCI-R items at retroline
+           %in%
+             ocir.items_retro]
+        )
+    )
+  )
+
+freq(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_ocir_retro) #have a look at the frequency
+
+dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>% #NA per person as a percentage
+  mutate(
+    miss_pc_total_ocir_retro = 
+      na_per_person_ocir_retro/9 # NA per person divided by the amount of items
+  )
+
+freq(dat.no.sex.no.gender.no.age.no.ibd$miss_pc_total_ocir_retro)
+```
+
+#OCI-R - prepandemic
+OCI-R Missingness NAs per person - count and percentages
+```{r OCI-R prepan missingness}
+dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
+  mutate(
+    na_per_person_ocir_prepan =         # variable for NA per person
+      rowSums(                       
+        is.na(dat.no.sex.no.gender.no.age.no.ibd # sum the rows that are NA
+          [,colnames(dat.no.sex.no.gender.no.age.no.ibd) #for all the rows and columns that are in the OCI-R items at prepanline
+           %in%
+             ocir.items_prepan]
+        )
+    )
+  )
+
+freq(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_ocir_prepan) #have a look at the frequency
+
+dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>% #NA per person as a percentage
+  mutate(
+    miss_pc_total_ocir_prepan = 
+      na_per_person_ocir_prepan/9 # NA per person divided by the amount of items
+  )
+
+freq(dat.no.sex.no.gender.no.age.no.ibd$miss_pc_total_ocir_prepan)
+```
+
+Count for OCI-R baseline, retrospective, and prepandemic missingness per person
+```{r count of people missing a number of items for OCI-R}
+#baseline
+table(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_ocir_base)
+#retrospective
+table(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_ocir_retro)
+#pre-pandemic
+table(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_ocir_prepan)
 ```

### 2020-08-04 PANCHANGE_data_preprocessing2020-07-15.Rmd
added frequency for PCL retro

--- 2020-08-04 PANCHANGE_data_preprocessing2020-07-15.Rmd
@@
 #install.packages("psych")
+#install.packages("dplyr")
 ```
@@
 library(psych)
+library(dplyr)
+library(data.table)
 ```
@@
 Max should be 21.
-
-*** MD - need to adapt for participants with missing data (should be NA)
 ```{r gad sum score prepan}
@@
 # Create vector with items that are included in total score
-gad.items_prepan = c(
+gad.items_prepan <- c(
   "gad.feeling_nervous_anxious_or_on_edge_prepan_numeric",
@@
 # Create vector with items that are included in total score
-pcl.items_prepan = c(
+pcl.items_prepan <- c(
   "pcl.stressful_experience_repeated_images_prepan_numeric",
@@
 Calculate sum score for PHQ-9
-
-*** MD - need to adapt for participants with missing data (should be NA)
 ```{r phq sum score prepan}
@@
 # Create vector with items that are included in sum score
-phq.items_prepan = c(
+phq.items_prepan <- c(
   "phq.little_interest_or_pleasure_in_doing_things_prepan_numeric",
@@
 
-# glad ocir
-
-```{r glad ocir cols}
-glad.ocir.raw <- readRDS(file = paste0(data.raw_path, "/2020-08-03/glad/ocir_glad.rds"))
-dim(glad.ocir.raw)
-colnames(glad.ocir.raw)
-```
-
-```{r glad ocir cleaning}
-glad.ocir.raw.id <- glad.ocir.raw %>%
-  drop_na(externalDataReference) %>% # Drop NAs
-  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
-  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
-  mutate(ID = as.numeric(ID),
-         startDate.glad = startDate) %>% # Rename startDate
-  select(
-    Sample, # Sample
-    ID, # ID
-    ocir.i_repeatedly_check_doors_windows_drawers_etc_prepan = ocir.i_repeatedly_check_doors_windows_drawers_etc.,
-    ocir.arranged_things_change_upset_prepan = ocir.arranged_things_change_upset,
-    ocir.repeat_feel_numbers_prepan = ocir.repeat_feel_numbers,
-    ocir.clean_simply_wash_feel_prepan = ocir.clean_simply_wash_feel,
-    ocir.mind_upset_unpleasant_thoughts_prepan = ocir.mind_upset_unpleasant_thoughts,
-    ocir.afraid_avoid_throwing_things_prepan = ocir.afraid_avoid_throwing_things,
-    ocir.light_switches_water_taps_prepan = ocir.light_switches_water_taps,
-    ocir.arranged_things_prepan = ocir.arranged_things,
-    ocir.good_feel_bad_numbers_prepan = ocir.good_feel_bad_numbers,
-    ocir.hands_longer_wash_prepan = ocir.hands_longer_wash,
-    ocir.saved_things_prepan = ocir.saved_things,
-    ocir.frequently_difficulty_rid_nasty_prepan = ocir.frequently_difficulty_rid_nasty,
-    ocir.i_check_things_more_often_than_necessary_prepan = ocir.i_check_things_more_often_than_necessary.,
-    ocir.arranged_properly_objects_upset_prepan = ocir.arranged_properly_objects_upset,
-    ocir.feel_compelled_count_things_prepan = ocir.feel_compelled_count_things,
-    ocir.strangers_touch_touched_difficult_prepan = ocir.strangers_touch_touched_difficult,
-    ocir.control_difficult_find_thoughts_prepan = ocir.control_difficult_find_thoughts,
-    ocir.i_collect_things_i_dont_need_prepan = ocir.i_collect_things_i_dont_need
-  ) %>%
-  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
-  mutate_if(is.numeric, ~na_if(., -99)) %>%
-  mutate_if(is.numeric, ~na_if(., -77)) %>%
-  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
-  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
-
-# Inspect dimensions
-dim(glad.ocir.raw.id)
-# Inspect colnames
-colnames(glad.ocir.raw.id)
-#Differences
-dim(glad.ocir.raw)[1]-dim(glad.ocir.raw.id)[1]
-```
-
-Calculate sum score for OCI-R
-
-*** MD - need to adapt for participants with missing data (should be NA)
-```{r ocir sum score prepan}
-# Create vector with scoring key: If the item is reversed coded use -1. 
-# There needs to be the correct number of values for each item in the questionnaire. 
-ocir.items_key_prepan <- c(1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1)
-
-# Create vector with items that are included in sum score
-ocir.items_prepan = c(
-  "ocir.all_variables_listed_here",
-  ##add variables to include in sum score
-  )
-
-# Calulate sum score
-ocir.scored_items_prepan <- scoreItems(keys = ocir.items_key_prepan,
-                                        items = glad.ocir.raw.id[ocir.items_prepan],
-                                        totals = TRUE, 
-                                        missing = TRUE, 
-                                        impute = 'none', 
-                                        min = 0, 
-                                        max = 3)
-# Add in column to tibble
-glad.ocir.raw.id$ocir.sum_score_prepan <- ocir.scored_items_prepan$scores
-
-# Look at values
-glad.ocir.raw.id %>%
-  descr(ocir.sum_score_prepan,
-        stats = "common"
-        )
-```
-
-```{r glad ocir head}
-head(glad.ocir.raw.id)
-```
-
-```{r glad ocir summary}
-summarytools::dfSummary(
-  glad.ocir.raw.id,
-  graph.col = F,
-  valid.col = F
-  )
-```
-
-# COPING GLAD: GAD-7
+## COPING GLAD: GAD-7
 
@@
 # Create vector with items that are included in total score
-gad.items_retro = c(
+gad.items_retro <- c(
   "gad.feeling_nervous_anxious_or_on_edge_retro_numeric",
@@
 # Create vector with items that are included in total score
-gad.items_base = c(
+gad.items_base <- c(
   "gad.feeling_nervous_anxious_or_on_edge_base_numeric",
@@
 # Create vector with items that are included in total score
-pcl.items_retro = c(
+pcl.items_retro <- c(
   "pcl.stressful_experience_repeated_images_retro_numeric",
@@
 # Create vector with items that are included in total score
-pcl.items_base = c(
+pcl.items_base <- c(
   "pcl.stressful_experience_repeated_images_base_numeric",
@@
 
-#Creating "complete cases" datasets  - NOTE THIS PROBABLY WONT BE USED BUT JUST TO GIVE AN IDEA OF COMPLETE CASES NUMBERS. KT. 
-Complete case data for PHQ, GAD and PCL - 3345 remaining, drop 35,036.
-```{r complete cases only}
-all.items <- c(phq.items_prepan,
-                phq.items_base,
-                phq.items_retro,
-                gad.items_prepan,
-                gad.items_base,
-                gad.items_retro,
-                pcl.items_prepan,
-                pcl.items_base,
-                pcl.items_retro)
-
-dat.no.sex.no.gender.no.age.no.ibd.complete.cases <- dat.no.sex.no.gender.no.age.no.ibd[complete.cases(dat.no.sex.no.gender.no.age.no.ibd[, all.items ]),]
-
-dim(dat.no.sex.no.gender.no.age.no.ibd.complete.cases)
-dim(dat.no.sex.no.gender.no.age.no.ibd)[1]-dim(dat.no.sex.no.gender.no.age.no.ibd.complete.cases)[1]
-```
+#Sum scores missingness cut offs
+KT: This series of chunks creates a "full" sum score for the PHQ, GAD and PCL.
 
 PHQ
-Complete case data for PHQ baseline (COPING) - 9,260 remaining
-```{r complete cases phq base}
-dat.no.sex.no.gender.no.age.no.ibd.complete.cases.phq.base <- dat.no.sex.no.gender.no.age.no.ibd[complete.cases(dat.no.sex.no.gender.no.age.no.ibd[, phq.items_base ]),]
-
-dim(dat.no.sex.no.gender.no.age.no.ibd.complete.cases.phq.base)
-dim(dat.no.sex.no.gender.no.age.no.ibd)[1]-dim(dat.no.sex.no.gender.no.age.no.ibd.complete.cases.phq.base)[1]
-```
-
-Complete case data for PHQ pre-pandemic (GLAD) - 37,308 remaining
-```{r complete cases phq prepan}
-dat.no.sex.no.gender.no.age.no.ibd.complete.cases.phq.prepan <- dat.no.sex.no.gender.no.age.no.ibd[complete.cases(dat.no.sex.no.gender.no.age.no.ibd[, phq.items_prepan ]),]
-
-dim(dat.no.sex.no.gender.no.age.no.ibd.complete.cases.phq.prepan)
-dim(dat.no.sex.no.gender.no.age.no.ibd)[1]-dim(dat.no.sex.no.gender.no.age.no.ibd.complete.cases.phq.prepan)[1]
-```
-
-Complete case data for PHQ retrospective (COPING) - 9,262 remaining
-```{r complete cases phq retro}
-dat.no.sex.no.gender.no.age.no.ibd.complete.cases.phq.retro <- dat.no.sex.no.gender.no.age.no.ibd[complete.cases(dat.no.sex.no.gender.no.age.no.ibd[, phq.items_retro ]),]
-
-dim(dat.no.sex.no.gender.no.age.no.ibd.complete.cases.phq.retro)
-dim(dat.no.sex.no.gender.no.age.no.ibd)[1]-dim(dat.no.sex.no.gender.no.age.no.ibd.complete.cases.phq.retro)[1]
+The PHQ sum score is set to NA if they have more than one missing item, and it is not the last suicide ideation item (they do not meet the cut off criteria - phq.base_cut_off)
+```{r sum score cut offs PHQ base}
+dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
+  mutate(
+    phq.sum_score_base_full =
+      if_else(na_per_person_phq_base > 1 & phq.base_cut_off == 0,
+              NA_real_,
+              phq.sum_score_base
+              )
+  )
+
+summary(dat.no.sex.no.gender.no.age.no.ibd$phq.sum_score_base)
+summary(dat.no.sex.no.gender.no.age.no.ibd$phq.sum_score_base_full)
+```
+
+```{r sum score cut offs PHQ prepan}
+dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
+  mutate(
+    phq.sum_score_prepan_full =
+      if_else(na_per_person_phq_prepan > 1 & phq.prepan_cut_off == 0,
+              NA_real_,
+              phq.sum_score_prepan
+              )
+  )
+
+summary(dat.no.sex.no.gender.no.age.no.ibd$phq.sum_score_prepan)
+summary(dat.no.sex.no.gender.no.age.no.ibd$phq.sum_score_prepan_full)
+```
+
+```{r sum score cut offs PHQ retro}
+dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
+  mutate(
+    phq.sum_score_retro_full =
+      if_else(na_per_person_phq_retro > 1 & phq.retro_cut_off == 0,
+              NA_real_,
+              phq.sum_score_retro
+              )
+  )
+
+summary(dat.no.sex.no.gender.no.age.no.ibd$phq.sum_score_retro)
+summary(dat.no.sex.no.gender.no.age.no.ibd$phq.sum_score_retro_full)
 ```
@@
 GAD
-Complete case data for GAD baseline (COPING) - 12,457 remaining
-```{r complete cases gad base}
-dat.no.sex.no.gender.no.age.no.ibd.complete.cases.gad.base <- dat.no.sex.no.gender.no.age.no.ibd[complete.cases(dat.no.sex.no.gender.no.age.no.ibd[, gad.items_base ]),]
-
-dim(dat.no.sex.no.gender.no.age.no.ibd.complete.cases.gad.base)
-dim(dat.no.sex.no.gender.no.age.no.ibd)[1]-dim(dat.no.sex.no.gender.no.age.no.ibd.complete.cases.gad.base)[1]
-```
-
-Complete case data for gad pre-pandemic (GLAD) - 36,149 remaining
-```{r complete cases gad prepan}
-dat.no.sex.no.gender.no.age.no.ibd.complete.cases.gad.prepan <- dat.no.sex.no.gender.no.age.no.ibd[complete.cases(dat.no.sex.no.gender.no.age.no.ibd[, gad.items_prepan ]),]
-
-dim(dat.no.sex.no.gender.no.age.no.ibd.complete.cases.gad.prepan)
-dim(dat.no.sex.no.gender.no.age.no.ibd)[1]-dim(dat.no.sex.no.gender.no.age.no.ibd.complete.cases.gad.prepan)[1]
-```
-
-Complete case data for gad retrospective (COPING) - 8,930 remaining
-```{r complete cases gad retro}
-dat.no.sex.no.gender.no.age.no.ibd.complete.cases.gad.retro <- dat.no.sex.no.gender.no.age.no.ibd[complete.cases(dat.no.sex.no.gender.no.age.no.ibd[, gad.items_retro ]),]
-
-dim(dat.no.sex.no.gender.no.age.no.ibd.complete.cases.gad.retro)
-dim(dat.no.sex.no.gender.no.age.no.ibd)[1]-dim(dat.no.sex.no.gender.no.age.no.ibd.complete.cases.gad.retro)[1]
+The GAD sum score is set to NA if they have any missing items
+```{r sum score cut offs GAD base}
+dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
+  mutate(
+    gad.sum_score_base_full =
+      if_else(na_per_person_gad_base > 0,
+              NA_real_,
+              gad.sum_score_base
+              )
+  )
+
+summary(dat.no.sex.no.gender.no.age.no.ibd$gad.sum_score_base)
+summary(dat.no.sex.no.gender.no.age.no.ibd$gad.sum_score_base_full)
+```
+
+```{r sum score cut offs GAD prepan}
+dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
+  mutate(
+    gad.sum_score_prepan_full =
+      if_else(na_per_person_gad_prepan > 0,
+              NA_real_,
+              gad.sum_score_prepan
+              )
+  )
+
+summary(dat.no.sex.no.gender.no.age.no.ibd$gad.sum_score_prepan)
+summary(dat.no.sex.no.gender.no.age.no.ibd$gad.sum_score_prepan_full)
+```
+
+```{r sum score cut offs GAD retro}
+dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
+  mutate(
+    gad.sum_score_retro_full =
+      if_else(na_per_person_gad_retro > 0,
+              NA_real_,
+              gad.sum_score_retro
+              )
+  )
+
+summary(dat.no.sex.no.gender.no.age.no.ibd$gad.sum_score_retro)
+summary(dat.no.sex.no.gender.no.age.no.ibd$gad.sum_score_retro_full)
 ```
@@
 PCL
-Complete case data for PCL baseline (COPING) - 12,376 remaining
-```{r complete cases pcl base}
-dat.no.sex.no.gender.no.age.no.ibd.complete.cases.pcl.base <- dat.no.sex.no.gender.no.age.no.ibd[complete.cases(dat.no.sex.no.gender.no.age.no.ibd[, pcl.items_base ]),]
-
-dim(dat.no.sex.no.gender.no.age.no.ibd.complete.cases.pcl.base)
-dim(dat.no.sex.no.gender.no.age.no.ibd)[1]-dim(dat.no.sex.no.gender.no.age.no.ibd.complete.cases.pcl.base)[1]
-```
-
-Complete case data for PCL pre-pandemic (GLAD) - 35,176 remaining
-```{r complete cases pcl prepan}
-dat.no.sex.no.gender.no.age.no.ibd.complete.cases.pcl.prepan <- dat.no.sex.no.gender.no.age.no.ibd[complete.cases(dat.no.sex.no.gender.no.age.no.ibd[, pcl.items_prepan ]),]
-
-dim(dat.no.sex.no.gender.no.age.no.ibd.complete.cases.pcl.prepan)
-dim(dat.no.sex.no.gender.no.age.no.ibd)[1]-dim(dat.no.sex.no.gender.no.age.no.ibd.complete.cases.pcl.prepan)[1]
-```
-
-Complete case data for PCL retrospective (COPING) - 4,618 remaining
-```{r complete cases pcl retro}
-dat.no.sex.no.gender.no.age.no.ibd.complete.cases.pcl.retro <- dat.no.sex.no.gender.no.age.no.ibd[complete.cases(dat.no.sex.no.gender.no.age.no.ibd[, pcl.items_retro ]),]
-
-dim(dat.no.sex.no.gender.no.age.no.ibd.complete.cases.pcl.retro)
-dim(dat.no.sex.no.gender.no.age.no.ibd)[1]-dim(dat.no.sex.no.gender.no.age.no.ibd.complete.cases.pcl.retro)[1]
+The PCL sum score is set to NA if they have any missing items - only for basline and prepan.
+```{r sum score cut offs PCL base}
+dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
+  mutate(
+    pcl.sum_score_base_full =
+      if_else(na_per_person_pcl_base > 0,
+              NA_real_,
+              pcl.sum_score_base
+              )
+  )
+
+summary(dat.no.sex.no.gender.no.age.no.ibd$pcl.sum_score_base)
+summary(dat.no.sex.no.gender.no.age.no.ibd$pcl.sum_score_base_full)
+```
+
+```{r sum score cut offs PCL prepan}
+dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
+  mutate(
+    pcl.sum_score_prepan_full =
+      if_else(na_per_person_pcl_prepan > 0,
+              NA_real_,
+              pcl.sum_score_prepan
+              )
+  )
+
+summary(dat.no.sex.no.gender.no.age.no.ibd$pcl.sum_score_prepan)
+summary(dat.no.sex.no.gender.no.age.no.ibd$pcl.sum_score_prepan_full)
 ```
@@
 summary(dat.glad$pcl.diff_score_prepan_base)
+```
+
+```{r frequency of those who reported "due to pandemic" in retro PCL}
+summary(dat.glad$pcl.sum_score_retro)
+
+freq(dat.glad$pcl.stressful_experience_repeated_images_retro)
+freq(dat.glad$pcl.stressful_situation_avoiding_activities_retro)
+freq(dat.glad$pcl.feeling_irritable_or_having_angry_outbursts_retro)
+freq(dat.glad$pcl.stressful_experience_upset_reminded_retro)
+freq(dat.glad$pcl.cut_people_feeling_distant_retro)
+freq(dat.glad$pcl.difficulty_concentrating_retro)
 ```

### 2020-08-04 PANCHANGE_data_preprocessing2020-07-15.Rmd
minor edits
Adapted the code for retro and baseline OCI-R scores.

--- 2020-08-04 PANCHANGE_data_preprocessing2020-07-15.Rmd
@@
 # There needs to be the correct number of values for each item in the questionnaire. 
-ocir.items_key_retro <- c(1,1,1,1,1,1,1,1,1)
+ocir.items_key_retro <- c(1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1)
 
@@
                                      min = 0, 
-                                     max = 3)
+                                     max = 4)
 # Add in column to tibble
@@
 # There needs to be the correct number of values for each item in the questionnaire. 
-ocir.items_key_base <- c(1,1,1,1,1,1,1,1,1)
+ocir.items_key_base <- c(1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1)
 
@@
 ocir.items_base = c(
-  "ocir.little_interest_or_pleasure_in_doing_things_base_numeric",
-"ocir.feeling_down_depressed_or_hopeless_base_numeric",
-"ocir.staying_asleep_sleeping_trouble_base_numeric",
-"ocir.feeling_tired_or_having_little_energy_base_numeric",
-"ocir.poor_appetite_or_overeating_base_numeric",
-"ocir.feeling_bad_failure_family_base_numeric",
-"ocir.trouble_concentrating_reading_newspaper_base_numeric",
-"ocir.moving_fidgety_noticed_opposite_base_numeric",
-"ocir.dead_hurting_thoughts_base_numeric"
+  "ocir.i_repeatedly_check_doors_windows_drawers_etc_base",
+  "ocir.arranged_things_change_upset_base",
+  "ocir.repeat_feel_numbers_base",
+  "ocir.clean_simply_wash_feel_base",
+  "ocir.mind_upset_unpleasant_thoughts_base",
+  "ocir.afraid_avoid_throwing_things_base",
+  "ocir.light_switches_water_taps_base",
+  "ocir.arranged_things_base",
+  "ocir.good_feel_bad_numbers_base",
+  "ocir.hands_longer_wash_base",
+  "ocir.saved_things_base",
+  "ocir.frequently_difficulty_rid_nasty_base",
+  "ocir.i_check_things_more_often_than_necessary_base",
+  "ocir.arranged_properly_objects_upset_base",
+  "ocir.feel_compelled_count_things_base",
+  "ocir.strangers_touch_touched_difficult_base",
+  "ocir.control_difficult_find_thoughts_base",
+  "ocir.i_collect_things_i_dont_need_base"
 )
@@
                                     min = 0, 
-                                    max = 3)
+                                    max = 4)
 # Add in column to tibble

### 2020-08-04 PANCHANGE_data_preprocessing2020-07-15.Rmd
Added OCI-R dataframes to the tibble data frame list.

@@
   glad.mhq.raw.categories,
-#  glad.ocir.raw.id,
+  glad.ocir.raw.id,
   glad.pcl.raw.id,
@@
   coping.glad.pcl.raw.id,
-  coping.glad.phq.raw.id
+  coping.glad.phq.raw.id,
+  coping.glad.ocir.raw.id
 )

### 2020-08-04 PANCHANGE_data_preprocessing2020-07-15.Rmd
Corrected number of items in OCI-R missingness score

@@
 
-##Missigness of questionnaire items
+##Missingness of questionnaire items
 #PHQ - baseline
@@
     miss_pc_total_ocir_base = 
-      na_per_person_ocir_base/9 # NA per person divided by the amount of items
+      na_per_person_ocir_base/18 # NA per person divided by the amount of items
   )
@@
     miss_pc_total_ocir_retro = 
-      na_per_person_ocir_retro/9 # NA per person divided by the amount of items
+      na_per_person_ocir_retro/18 # NA per person divided by the amount of items
   )
@@
     miss_pc_total_ocir_prepan = 
-      na_per_person_ocir_prepan/9 # NA per person divided by the amount of items
+      na_per_person_ocir_prepan/18 # NA per person divided by the amount of items
   )

### 2020-08-04 PANCHANGE_data_preprocessing2020-07-15.Rmd
Added OCI-R sum score differences chunk. Needs to be tested once data is ready (awaiting IDs to be fixed).

@@
 
+OCI-R difference scores
+```{r ocir difference scores}
+# Difference score for prepandemic and retrospective oci-r sum scores
+dat.glad <- dat.glad %>%
+  mutate(
+    ocir.diff_score_prepan_retro =
+      as.numeric(
+        ocir.sum_score_prepan - ocir.sum_score_retro  # retrospective sum score MINUS prepandemic sum score 
+      )
+  )
+
+summary(dat.glad$ocir.diff_score_prepan_retro)
+
+# Difference score for prepandemic and baseline ocir sum scores
+dat.glad <- dat.glad %>%
+  mutate(
+    ocir.diff_score_prepan_base =
+      as.numeric(
+        ocir.sum_score_prepan - ocir.sum_score_base  # prepandemic sum score MINUS baseline sum score 
+      )
+  )
+
+summary(dat.glad$ocir.diff_score_prepan_base)
+
+# Difference score for retrospective and baseline ocir sum scores
+dat.glad <- dat.glad %>%
+  mutate(
+    ocir.diff_score_base_retro =
+      as.numeric(
+        ocir.sum_score_base - ocir.sum_score_retro  # baseline sum score MINUS retrospective sum score 
+      )
+  )
+
+summary(dat.glad$ocir.diff_score_base_retro)
+
+```
+
 #Data level groups

### 2020-08-04 PANCHANGE_data_preprocessing2020-07-15.Rmd
Corrected COPING GLAD OCI-R participant IDs

@@
 ```{r coping glad ocir cols}
-coping.glad.ocir.raw <- readRDS(file = paste0(data.raw_path, "/2020-08-03/glad/ocir_coping_glad.rds"))
+coping.glad.ocir.raw <- readRDS(file = paste0(data.raw_path, "/2020-08-04/glad/ocir_coping_glad.rds"))
 dim(coping.glad.ocir.raw)
@@
 coping.glad.ocir.raw.id <- coping.glad.ocir.raw %>%
-  drop_na(externalDataReference) %>% # Drop NAs
-  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
-  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
+  drop_na(recipientFirstName) %>% # Drop NAs
+  distinct(recipientFirstName, .keep_all = TRUE) %>% # Remove duplicates based on ID
+  separate(recipientFirstName, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
   mutate(ID = as.numeric(ID),

### 2020-08-04 PANCHANGE_data_preprocessing2020-07-15.Rmd
Cleaned up/added some comments in the script

@@
 
-*** MD - need to adapt for participants with missing data (should be NA)
+*Note that scores with missingness will be changed to NA later in the script
 ```{r gad sum score prepan}
@@
 Calculate sum score for PCL-6
+
+*Note that scores with missingness will be changed to NA later in the script
 ```{r pcl sum score prepan}
@@
 
-*** MD - need to adapt for participants with missing data (should be NA)
+*Note that scores with missingness will be changed to NA later in the script
 ```{r phq sum score prepan}
@@
 
-*** MD - need to adapt for participants with missing data (should be NA)
+*Note that scores with missingness will be changed to NA later in the script
 ```{r ocir sum score prepan}
@@
 
-Will need to double check these namings once we have the new cleaned data -- KT. 
+*Note that the COPING GLAD OCI-R ID numbers are stored under recipientFirstName (rather than ExternalDataReference)
 ```{r coping glad ocir cleaning}

### 2020-08-04 PANCHANGE_data_preprocessing2020-07-15.Rmd
read in respiratory data and created chunks to decide on cut-offs for algoirthm symptoms

--- 2020-08-04 PANCHANGE_data_preprocessing2020-07-15.Rmd
@@
 library(summarytools)
+library(psych)
+library(dplyr)
 library(tidyverse)
-library(psych)
 ```
@@
 palette = COPINGpalette2
+```
+
+#Add_numeric function
+Function used to convert character variables into numeric variables. 
+```{r add_numeric function}
+add_numeric <- function(dat, exclude = NULL) {
+  dat_fct <- sjlabelled::as_label(dat)
+
+  dat <- dat[!colnames(dat) %in% exclude]
+  colnames(dat) <- paste(colnames(dat), "numeric", sep = "_")
+  return(bind_cols(dat_fct, dat))
+}
 ```
@@
 
-# glad ocir
-
-```{r glad ocir cols}
-glad.ocir.raw <- readRDS(file = paste0(data.raw_path, "/2020-08-03/glad/ocir_glad.rds"))
-dim(glad.ocir.raw)
-colnames(glad.ocir.raw)
-```
-
-```{r glad ocir cleaning}
-glad.ocir.raw.id <- glad.ocir.raw %>%
-  drop_na(externalDataReference) %>% # Drop NAs
-  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
-  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
-  mutate(ID = as.numeric(ID),
-         startDate.glad = startDate) %>% # Rename startDate
-  select(
-    Sample, # Sample
-    ID, # ID
-    ocir.i_repeatedly_check_doors_windows_drawers_etc_prepan = ocir.i_repeatedly_check_doors_windows_drawers_etc.,
-    ocir.arranged_things_change_upset_prepan = ocir.arranged_things_change_upset,
-    ocir.repeat_feel_numbers_prepan = ocir.repeat_feel_numbers,
-    ocir.clean_simply_wash_feel_prepan = ocir.clean_simply_wash_feel,
-    ocir.mind_upset_unpleasant_thoughts_prepan = ocir.mind_upset_unpleasant_thoughts,
-    ocir.afraid_avoid_throwing_things_prepan = ocir.afraid_avoid_throwing_things,
-    ocir.light_switches_water_taps_prepan = ocir.light_switches_water_taps,
-    ocir.arranged_things_prepan = ocir.arranged_things,
-    ocir.good_feel_bad_numbers_prepan = ocir.good_feel_bad_numbers,
-    ocir.hands_longer_wash_prepan = ocir.hands_longer_wash,
-    ocir.saved_things_prepan = ocir.saved_things,
-    ocir.frequently_difficulty_rid_nasty_prepan = ocir.frequently_difficulty_rid_nasty,
-    ocir.i_check_things_more_often_than_necessary_prepan = ocir.i_check_things_more_often_than_necessary.,
-    ocir.arranged_properly_objects_upset_prepan = ocir.arranged_properly_objects_upset,
-    ocir.feel_compelled_count_things_prepan = ocir.feel_compelled_count_things,
-    ocir.strangers_touch_touched_difficult_prepan = ocir.strangers_touch_touched_difficult,
-    ocir.control_difficult_find_thoughts_prepan = ocir.control_difficult_find_thoughts,
-    ocir.i_collect_things_i_dont_need_prepan = ocir.i_collect_things_i_dont_need
-  ) %>%
-  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
-  mutate_if(is.numeric, ~na_if(., -99)) %>%
-  mutate_if(is.numeric, ~na_if(., -77)) %>%
-  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
-  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
-
-# Inspect dimensions
-dim(glad.ocir.raw.id)
-# Inspect colnames
-colnames(glad.ocir.raw.id)
-#Differences
-dim(glad.ocir.raw)[1]-dim(glad.ocir.raw.id)[1]
-```
-
-Calculate sum score for OCI-R
-
-*** MD - need to adapt for participants with missing data (should be NA)
-```{r ocir sum score prepan}
-# Create vector with scoring key: If the item is reversed coded use -1. 
-# There needs to be the correct number of values for each item in the questionnaire. 
-ocir.items_key_prepan <- c(1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1)
-
-# Create vector with items that are included in sum score
-ocir.items_prepan = c(
-  "ocir.i_repeatedly_check_doors_windows_drawers_etc_prepan",
-  "ocir.arranged_things_change_upset_prepan",
-  "ocir.repeat_feel_numbers_prepan",
-  "ocir.clean_simply_wash_feel_prepan",
-  "ocir.mind_upset_unpleasant_thoughts_prepan",
-  "ocir.afraid_avoid_throwing_things_prepan",
-  "ocir.light_switches_water_taps_prepan",
-  "ocir.arranged_things_prepan",
-  "ocir.good_feel_bad_numbers_prepan",
-  "ocir.hands_longer_wash_prepan",
-  "ocir.saved_things_prepan",
-  "ocir.frequently_difficulty_rid_nasty_prepan",
-  "ocir.i_check_things_more_often_than_necessary_prepan",
-  "ocir.arranged_properly_objects_upset_prepan",
-  "ocir.feel_compelled_count_things_prepan",
-  "ocir.strangers_touch_touched_difficult_prepan",
-  "ocir.control_difficult_find_thoughts_prepan",
-  "ocir.i_collect_things_i_dont_need_prepan"
-  )
-
-# Calulate sum score
-ocir.scored_items_prepan <- scoreItems(keys = ocir.items_key_prepan,
-                                        items = glad.ocir.raw.id[ocir.items_prepan],
-                                        totals = TRUE, 
-                                        missing = TRUE, 
-                                        impute = 'none', 
-                                        min = 0, 
-                                        max = 4)
-# Add in column to tibble
-glad.ocir.raw.id$ocir.sum_score_prepan <- ocir.scored_items_prepan$scores
-
-# Look at values
-glad.ocir.raw.id %>%
-  descr(ocir.sum_score_prepan,
-        stats = "common"
-        )
-```
-
-```{r glad ocir head}
-head(glad.ocir.raw.id)
-```
-
-```{r glad ocir summary}
-summarytools::dfSummary(
-  glad.ocir.raw.id,
-  graph.col = F,
-  valid.col = F
-  )
-```
-
-# COPING GLAD: GAD-7
+## COPING GLAD: GAD-7
 
@@
 # Create vector with items that are included in total score
-phq.items_retro = c(
+phq.items_retro <- c(
   "phq.little_interest_or_pleasure_in_doing_things_retro_numeric",
@@
 # Create vector with items that are included in total score
-phq.items_base = c(
+phq.items_base <- c(
   "phq.little_interest_or_pleasure_in_doing_things_base_numeric",
@@
 
-# glad COPING ocir
-
-```{r coping glad ocir cols}
-coping.glad.ocir.raw <- readRDS(file = paste0(data.raw_path, "/2020-08-03/glad/ocir_coping_glad.rds"))
-dim(coping.glad.ocir.raw)
-colnames(coping.glad.ocir.raw)
-```
-
-```{r coping glad ocir summary labels}
-summarytools::dfSummary(
-  coping.glad.ocir.raw,
-  graph.col = F,
-  valid.col = F
-  #labels.col = F
-)
-```
-
-Will need to double check these namings once we have the new cleaned data -- KT. 
-```{r coping glad ocir cleaning}
-coping.glad.ocir.raw.id <- coping.glad.ocir.raw %>%
+# Join tibbles together
+
+glad data frame list
+```{r glad data frame list}
+glad.dfs.list <- list(
+  glad.dem.raw.id,
+  glad.gad.raw.id,
+  glad.mhq.raw.categories,
+#  glad.ocir.raw.id,
+  glad.pcl.raw.id,
+  glad.phq.raw.id,
+  coping.glad.gad.raw.id,
+  coping.glad.pcl.raw.id,
+  coping.glad.phq.raw.id
+)
+```
+
+```{r Join all questionnaires for glad}
+dat.glad.raw <- plyr::join_all(
+  glad.dfs.list,
+  by = c("ID", "Sample") # Alternatively you can join by several columns EDGI -> "Age", "Sex", "Birthyear"
+  )
+
+#look at the data
+skimr::skim(dat.glad.raw)
+```
+
+Check duplicates again to be saved
++++KLP: RAMP: More than one column: Age, Sex, Login ID; if they match on all 3 then we treat them as a duplicate; otherwise we are going to rename the Login ID
++++KT: No duplicates identified by ID in GLAD. 
+```{r glad Check duplicates}
+dat.glad.raw$ID.dup <- duplicated(dat.glad.raw$ID)
+
+summary(as.factor(dat.glad.raw$ID.dup))
+
+dat.dup <- dat.glad.raw %>%
+  filter(ID.dup == TRUE)
+
+dat.glad.raw.no.dup <- dat.glad.raw %>%
+  filter(ID.dup == FALSE)
+```
+
+#Exclusion
+Exclude those without sex, gender, age and incomplete PHQ/GAD items
+Create a new new object for each exclusion step, e.g., data.no_sex, data.no_gender and data.no_sex.no_age
+```{r Exclude participants that do not report sex}
+dim(dat.glad.raw)
+dat.no.sex <- dat.glad.raw %>%
+  drop_na(Sex)
+dim(dat.no.sex)
+
+dim(dat.glad.raw)[1]-dim(dat.no.sex)[1]
+```
+`r dim(dat.glad.raw)[1]-dim(dat.no.sex)[1]` were excluded because they did not report their sex
+
+```{r Exclude participants that do not report gender}
+dim(dat.no.sex)
+dat.no.sex.no.gender <- dat.no.sex %>%
+  drop_na(Gender)
+dim(dat.no.sex.no.gender)
+
+dim(dat.no.sex)[1]-dim(dat.no.sex.no.gender)[1]
+```
+`r dim(dat.no.sex)[1]-dim(dat.no.sex.no.gender)[1]` were excluded because they did not report their sex
+
+```{r Exclude participants that do not report age}
+dim(dat.no.sex.no.gender)
+dat.no.sex.no.gender.no.age <- dat.no.sex.no.gender %>%
+  drop_na(age_category)
+dim(dat.no.sex.no.gender.no.age)
+
+dim(dat.no.sex.no.gender)[1]-dim(dat.no.sex.no.gender.no.age)[1]
+```
+`r dim(dat.no.gender)[1]-dim(dat.no.sex.no.gender.no.age)[1]` were excluded because they did not report their age
+
+Exclusion of inflammatory bowel disease (IBD) BioResource (BR) cohort
+```{r COVID exclusion of IBD}
+#dim(dat.no.sex.no.age)
+#
+#dat.no.sex.no.age <- dat.no.sex.no.age %>%
+#  filter(NBR.IBD == 0)
+#
+#dim(dat.no.sex.no.age.no.ibd)
+#
+#dim(dat.no.sex.no.age)[1]-dim(dat.no.sex.no.age.no.ibd)[1]
+
+dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age
+```
+
+##Missigness of questionnaire items
+#PHQ - baseline
+PHQ Missingness NAs per person - count and percentages
+```{r PHQ basline missingness}
+dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
+  mutate(
+    na_per_person_phq_base =         # variable for NA per person
+      rowSums(                       
+        is.na(dat.no.sex.no.gender.no.age.no.ibd # sum the rows that are NA
+          [,colnames(dat.no.sex.no.gender.no.age.no.ibd) #for all the rows and columns that are in the PHQ items at baseline
+           %in%
+             phq.items_base]
+        )
+    )
+  )
+
+freq(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_phq_base) #have a look at the frequency
+
+dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>% #NA per person as a percentage
+  mutate(
+    miss_pc_total_phq_base = 
+      na_per_person_phq_base/9 # NA per person divided by the amount of items
+  )
+
+freq(dat.no.sex.no.gender.no.age.no.ibd$miss_pc_total_phq_base)
+```
+
+```{r PHQ baseline missingness 8 items}
+#We need to identify those who have all items APART from the suicide ideation item - to still include these individuals. 
+dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
+  mutate(
+    phq.base_cut_off = 
+      if_else(
+        na_per_person_phq_base == 1 & 
+          is.na(phq.dead_hurting_thoughts_base_numeric), 
+        1,
+        0
+      )
+  )
+
+table(dat.no.sex.no.gender.no.age.no.ibd$phq.base_cut_off)
+```
+
+#PHQ - retrospective
+PHQ Missingness NAs per person - count and percentages
+```{r PHQ retrospective missingness}
+dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
+  mutate(
+    na_per_person_phq_retro =         # variable for NA per person
+      rowSums(                       
+        is.na(dat.no.sex.no.gender.no.age.no.ibd # sum the rows that are NA
+          [,colnames(dat.no.sex.no.gender.no.age.no.ibd) #for all the rows and columns that are in the PHQ items at retroline
+           %in%
+             phq.items_retro]
+        )
+    )
+  )
+
+freq(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_phq_retro) #have a look at the frequency
+
+dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>% #NA per person as a percentage
+  mutate(
+    miss_pc_total_phq_retro = 
+      na_per_person_phq_retro/9 # NA per person divided by the amount of items
+  )
+
+freq(dat.no.sex.no.gender.no.age.no.ibd$miss_pc_total_phq_retro)
+```
+
+```{r PHQ retro missingness 8 items}
+#We need to identify those who have all items APART from the suicide ideation item - to still include these individuals. 
+dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
+  mutate(
+    phq.retro_cut_off = 
+      if_else(
+        na_per_person_phq_retro == 1 & 
+          is.na(phq.dead_hurting_thoughts_retro_numeric), 
+        1,
+        0
+      )
+  )
+
+table(dat.no.sex.no.gender.no.age.no.ibd$phq.retro_cut_off)
+```
+
+#PHQ - prepandemic
+PHQ Missingness NAs per person - count and percentages
+```{r PHQ prepan missingness}
+dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
+  mutate(
+    na_per_person_phq_prepan =         # variable for NA per person
+      rowSums(                       
+        is.na(dat.no.sex.no.gender.no.age.no.ibd # sum the rows that are NA
+          [,colnames(dat.no.sex.no.gender.no.age.no.ibd) #for all the rows and columns that are in the PHQ items at prepanline
+           %in%
+             phq.items_prepan]
+        )
+    )
+  )
+
+freq(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_phq_prepan) #have a look at the frequency
+
+dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>% #NA per person as a percentage
+  mutate(
+    miss_pc_total_phq_prepan = 
+      na_per_person_phq_prepan/9 # NA per person divided by the amount of items
+  )
+
+freq(dat.no.sex.no.gender.no.age.no.ibd$miss_pc_total_phq_prepan)
+```
+
+```{r PHQ prepan missingness 8 items}
+#We need to identify those who have all items APART from the suicide ideation item - to still include these individuals. 
+dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
+  mutate(
+    phq.prepan_cut_off = 
+      if_else(
+        na_per_person_phq_prepan == 1 & 
+          is.na(phq.dead_hurting_thoughts_prepan_numeric), 
+        1,
+        0
+      )
+  )
+
+table(dat.no.sex.no.gender.no.age.no.ibd$phq.prepan_cut_off)
+```
+
+Count for PHQ baseline, retrospective, and prepandemic missingness per person
+```{r count of people missing a number of items for PHQ}
+#baseline
+table(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_phq_base)
+#retrospective
+table(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_phq_retro)
+#pre-pandemic
+table(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_phq_prepan)
+```
+
+#GAD - baseline
+GAD Missingness NAs per person - count and percentages
+```{r gad basline missingness}
+dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
+  mutate(
+    na_per_person_gad_base =         # variable for NA per person
+      rowSums(                       
+        is.na(dat.no.sex.no.gender.no.age.no.ibd # sum the rows that are NA
+          [,colnames(dat.no.sex.no.gender.no.age.no.ibd) #for all the rows and columns that are in the gad items at baseline
+           %in%
+             gad.items_base]
+        )
+    )
+  )
+
+freq(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_gad_base) #have a look at the frequency
+
+dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>% #NA per person as a percentage
+  mutate(
+    miss_pc_total_gad_base = 
+      na_per_person_gad_base/7 # NA per person divided by the amount of items
+  )
+
+freq(dat.no.sex.no.gender.no.age.no.ibd$miss_pc_total_gad_base)
+```
+
+#GAD - retrospective
+GAD Missingness NAs per person - count and percentages
+```{r gad retrospective missingness}
+dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
+  mutate(
+    na_per_person_gad_retro =         # variable for NA per person
+      rowSums(                       
+        is.na(dat.no.sex.no.gender.no.age.no.ibd # sum the rows that are NA
+          [,colnames(dat.no.sex.no.gender.no.age.no.ibd) #for all the rows and columns that are in the gad items at retroline
+           %in%
+             gad.items_retro]
+        )
+    )
+  )
+
+freq(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_gad_retro) #have a look at the frequency
+
+dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>% #NA per person as a percentage
+  mutate(
+    miss_pc_total_gad_retro = 
+      na_per_person_gad_retro/7 # NA per person divided by the amount of items
+  )
+
+freq(dat.no.sex.no.gender.no.age.no.ibd$miss_pc_total_gad_retro)
+```
+
+#GAD - prepandemic
+GAD Missingness NAs per person - count and percentages
+```{r gad prepan missingness}
+dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
+  mutate(
+    na_per_person_gad_prepan =         # variable for NA per person
+      rowSums(                       
+        is.na(dat.no.sex.no.gender.no.age.no.ibd # sum the rows that are NA
+          [,colnames(dat.no.sex.no.gender.no.age.no.ibd) #for all the rows and columns that are in the gad items at prepanline
+           %in%
+             gad.items_prepan]
+        )
+    )
+  )
+
+freq(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_gad_prepan) #have a look at the frequency
+
+dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>% #NA per person as a percentage
+  mutate(
+    miss_pc_total_gad_prepan = 
+      na_per_person_gad_prepan/7 # NA per person divided by the amount of items
+  )
+
+freq(dat.no.sex.no.gender.no.age.no.ibd$miss_pc_total_gad_prepan)
+```
+
+Count for gad baseline, retrospective, and prepandemic missingness per person
+```{r count of people missing a number of items for gad}
+#baseline
+table(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_gad_base)
+#retrospective
+table(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_gad_retro)
+#pre-pandemic
+table(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_gad_prepan)
+```
+
+#PCL - baseline
+PCL Missingness NAs per person - count and percentages
+```{r pcl basline missingness}
+dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
+  mutate(
+    na_per_person_pcl_base =         # variable for NA per person
+      rowSums(                       
+        is.na(dat.no.sex.no.gender.no.age.no.ibd # sum the rows that are NA
+          [,colnames(dat.no.sex.no.gender.no.age.no.ibd) #for all the rows and columns that are in the pcl items at baseline
+           %in%
+             pcl.items_base]
+        )
+    )
+  )
+
+freq(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_pcl_base) #have a look at the frequency
+
+dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>% #NA per person as a percentage
+  mutate(
+    miss_pc_total_pcl_base = 
+      na_per_person_pcl_base/6 # NA per person divided by the amount of items
+  )
+
+freq(dat.no.sex.no.gender.no.age.no.ibd$miss_pc_total_pcl_base)
+```
+
+#PCL - retrospective
+PCL Missingness NAs per person - count and percentages
+```{r pcl retrospective missingness}
+dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
+  mutate(
+    na_per_person_pcl_retro =         # variable for NA per person
+      rowSums(                       
+        is.na(dat.no.sex.no.gender.no.age.no.ibd # sum the rows that are NA
+          [,colnames(dat.no.sex.no.gender.no.age.no.ibd) #for all the rows and columns that are in the pcl items at retroline
+           %in%
+             pcl.items_retro]
+        )
+    )
+  )
+
+freq(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_pcl_retro) #have a look at the frequency
+
+dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>% #NA per person as a percentage
+  mutate(
+    miss_pc_total_pcl_retro = 
+      na_per_person_pcl_retro/6 # NA per person divided by the amount of items
+  )
+
+freq(dat.no.sex.no.gender.no.age.no.ibd$miss_pc_total_pcl_retro)
+```
+
+#PCL - prepandemic
+pcl Missingness NAs per person - count and percentages
+```{r pcl prepan missingness}
+dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
+  mutate(
+    na_per_person_pcl_prepan =         # variable for NA per person
+      rowSums(                       
+        is.na(dat.no.sex.no.gender.no.age.no.ibd # sum the rows that are NA
+          [,colnames(dat.no.sex.no.gender.no.age.no.ibd) #for all the rows and columns that are in the pcl items at prepanline
+           %in%
+             pcl.items_prepan]
+        )
+    )
+  )
+
+freq(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_pcl_prepan) #have a look at the frequency
+
+dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>% #NA per person as a percentage
+  mutate(
+    miss_pc_total_pcl_prepan = 
+      na_per_person_pcl_prepan/6 # NA per person divided by the amount of items
+  )
+
+freq(dat.no.sex.no.gender.no.age.no.ibd$miss_pc_total_pcl_prepan)
+```
+
+Count for pcl baseline, retrospective, and prepandemic missingness per person
+```{r count of people missing a number of items for pcl}
+# baseline
+table(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_pcl_base)
+# retrospective
+table(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_pcl_retro)
+# pre-pandemic
+table(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_pcl_prepan)
+
+# rename dataset
+dat.no.sex.no.gender.no.age.no.ibd.missingness <- dat.no.sex.no.gender.no.age.no.ibd
+```
+
+#Sum scores missingness cut offs
+KT: This series of chunks creates a "full" sum score for the PHQ, GAD and PCL.
+
+PHQ
+The PHQ sum score is set to NA if they have more than one missing item, and it is not the last suicide ideation item (they do not meet the cut off criteria - phq.base_cut_off)
+```{r sum score cut offs PHQ base}
+dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
+  mutate(
+    phq.sum_score_base_full =
+      if_else(na_per_person_phq_base > 1 & phq.base_cut_off == 0,
+              NA_real_,
+              phq.sum_score_base
+              )
+  )
+
+summary(dat.no.sex.no.gender.no.age.no.ibd$phq.sum_score_base)
+summary(dat.no.sex.no.gender.no.age.no.ibd$phq.sum_score_base_full)
+```
+
+```{r sum score cut offs PHQ prepan}
+dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
+  mutate(
+    phq.sum_score_prepan_full =
+      if_else(na_per_person_phq_prepan > 1 & phq.prepan_cut_off == 0,
+              NA_real_,
+              phq.sum_score_prepan
+              )
+  )
+
+summary(dat.no.sex.no.gender.no.age.no.ibd$phq.sum_score_prepan)
+summary(dat.no.sex.no.gender.no.age.no.ibd$phq.sum_score_prepan_full)
+```
+
+```{r sum score cut offs PHQ retro}
+dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
+  mutate(
+    phq.sum_score_retro_full =
+      if_else(na_per_person_phq_retro > 1 & phq.retro_cut_off == 0,
+              NA_real_,
+              phq.sum_score_retro
+              )
+  )
+
+summary(dat.no.sex.no.gender.no.age.no.ibd$phq.sum_score_retro)
+summary(dat.no.sex.no.gender.no.age.no.ibd$phq.sum_score_retro_full)
+```
+
+GAD
+The GAD sum score is set to NA if they have any missing items
+```{r sum score cut offs GAD base}
+dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
+  mutate(
+    gad.sum_score_base_full =
+      if_else(na_per_person_gad_base > 0,
+              NA_real_,
+              gad.sum_score_base
+              )
+  )
+
+summary(dat.no.sex.no.gender.no.age.no.ibd$gad.sum_score_base)
+summary(dat.no.sex.no.gender.no.age.no.ibd$gad.sum_score_base_full)
+```
+
+```{r sum score cut offs GAD prepan}
+dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
+  mutate(
+    gad.sum_score_prepan_full =
+      if_else(na_per_person_gad_prepan > 0,
+              NA_real_,
+              gad.sum_score_prepan
+              )
+  )
+
+summary(dat.no.sex.no.gender.no.age.no.ibd$gad.sum_score_prepan)
+summary(dat.no.sex.no.gender.no.age.no.ibd$gad.sum_score_prepan_full)
+```
+
+```{r sum score cut offs GAD retro}
+dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
+  mutate(
+    gad.sum_score_retro_full =
+      if_else(na_per_person_gad_retro > 0,
+              NA_real_,
+              gad.sum_score_retro
+              )
+  )
+
+summary(dat.no.sex.no.gender.no.age.no.ibd$gad.sum_score_retro)
+summary(dat.no.sex.no.gender.no.age.no.ibd$gad.sum_score_retro_full)
+```
+
+PCL
+The PCL sum score is set to NA if they have any missing items - only for basline and prepan.
+```{r sum score cut offs PCL base}
+dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
+  mutate(
+    pcl.sum_score_base_full =
+      if_else(na_per_person_pcl_base > 0,
+              NA_real_,
+              pcl.sum_score_base
+              )
+  )
+
+summary(dat.no.sex.no.gender.no.age.no.ibd$pcl.sum_score_base)
+summary(dat.no.sex.no.gender.no.age.no.ibd$pcl.sum_score_base_full)
+```
+
+```{r sum score cut offs PCL prepan}
+dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
+  mutate(
+    pcl.sum_score_prepan_full =
+      if_else(na_per_person_pcl_prepan > 0,
+              NA_real_,
+              pcl.sum_score_prepan
+              )
+  )
+
+summary(dat.no.sex.no.gender.no.age.no.ibd$pcl.sum_score_prepan)
+summary(dat.no.sex.no.gender.no.age.no.ibd$pcl.sum_score_prepan_full)
+```
+
+##Create tidy data on which the exclusion criteria have been applied
+Complete sex, gender, age and missingness information applied. 
+```{r Tidy data}
+dat.glad <- dat.no.sex.no.gender.no.age.no.ibd.missingness
+
+skimr::skim(dat.glad)
+```
+
+# Definition of prepandemic and baseline 
+Exlcude people who have joined GLAD/EDGI after the pandemic began, sensitivity analyses done on the cut off's we have chosen. 
+Potentially GLAD/EDGI particiapnts between January to April. EDGI launched on February 24th.
+
+Prepandemic GLAD/EDGI = Prepandemic (GLAD/EDGI sign-up questionnaire)
+
+Retrospective = COPING/RAMP sign up questionnaire; *only of those participants who have reported a change in symptoms*
+
+Baseline = COPING/RAMP sign up questionnaire
+
+Dates for the definition of prepandemic
+```{r Potential dates for prepandemic definition}
+# Date of the first COVID-19 case in the United Kingdom (UK)
+date_first_case_uk_january_31 <- as.POSIXct("2020-01-31")
+
+# Date for assumed higher awareness of COVID / Lockdown in Italy 4. March 2020 / first festivals cancelled
+date_higher_awareness_march_1 <- as.POSIXct("2020-03-01")
+
+# Date the UK went into lockdown
+date_uk_lockdown_march_23 <- as.POSIXct("2020-03-23")
+```
+
+```{r Prepandemic definitions january_31}
+dat.glad <- dat.glad %>%
+  mutate(
+    prepandemic_january_31_numeric =
+      if_else(
+        startDate.glad > date_first_case_uk_january_31, # The GLAD sign up is dated before the cut off (> longer ago)
+        true = 0, # Participant has not signed up before the pandemic,
+        false = 1, # Participant has signed up before the pandemic,
+        missing = NA_real_
+      )
+  )
+
+dat.glad <- dat.glad %>%
+  mutate(
+    prepandemic_january_31 =
+      recode_factor(
+        prepandemic_january_31_numeric,
+        "0" = "Sign up after 31. January",
+        "1" = "Sign up before 31. January"
+      )
+  )
+
+dat.glad %>%
+  freq(prepandemic_january_31)
+```
+
+```{r Prepandemic definitions march_1}
+dat.glad <- dat.glad %>%
+  mutate(
+    prepandemic_march_1_numeric =
+      if_else(
+        startDate.glad > date_higher_awareness_march_1, # The GLAD sign up is dated before the cut off (> longer ago)
+        true = 0, # Participant has not signed up before the pandemic,
+        false = 1, # Participant has signed up before the pandemic,
+        missing = NA_real_
+      )
+  )
+
+dat.glad <- dat.glad %>%
+  mutate(
+    prepandemic_march_1 =
+      recode_factor(
+        prepandemic_march_1_numeric,
+        "0" = "Sign up after 1. March",
+        "1" = "Sign up before 1. March"
+      )
+  )
+
+dat.glad %>%
+  freq(prepandemic_march_1)
+```
+
+```{r Prepandemic definitions march_23}
+dat.glad <- dat.glad %>%
+  mutate(
+    prepandemic_march_23_numeric =
+      if_else(
+        startDate.glad > date_uk_lockdown_march_23, # The GLAD sign up is dated before the cut off (> longer ago)
+        true = 0, # Participant has not signed up before the pandemic,
+        false = 1, # Participant has signed up before the pandemic,
+        missing = NA_real_
+      )
+  )
+
+dat.glad <- dat.glad %>%
+  mutate(
+    prepandemic_march_23 =
+      recode_factor(
+        prepandemic_march_23_numeric,
+        "0" = "Sign up after 23. March",
+        "1" = "Sign up before 23. March"
+      )
+  )
+
+dat.glad %>%
+  freq(prepandemic_march_23)
+```
+
+Calculate the time difference between time difference between sign up questionnaire and COPING questionnaire
+```{r time difference between sign up questionnaire and COPING questionnaire}
+dat.glad <- dat.glad %>%
+  mutate(
+    time_diff_sign_up_coping =
+        as.numeric(
+        difftime(           #this function does time1 - time2 as difftime(time1, time2...)
+          startDate.coping.glad,    #should be start date for COPING (time1)
+          startDate.glad),    #should be start date for GLAD (time2)
+          units = c("days")  #can also be "secs", "mins", "hours", "weeks"
+          )
+        )
+
+dat.glad %>%
+  descr(
+    var = time_diff_sign_up_coping,
+    stats = "common"
+    )
+```
+
+Proportion of people signed up over one year ago
+```{r eval=FALSE, include=FALSE}
+dat.glad <- dat.glad %>%
+  mutate(
+    over_one_year_time_diff_sign_up_coping_numeric =
+      as.numeric(
+        if_else(time_diff_sign_up_coping > 365, 1, 0
+                )
+      )
+  )
+
+dat.glad <- dat.glad %>%
+  mutate(
+    over_one_year_time_diff_sign_up_coping =
+      recode_factor(
+        over_one_year_time_diff_sign_up_coping_numeric,
+        "0" = "Sign up under one year before COPING",
+        "1" = "Sign up over one year before COPING"
+      )
+  )
+
+table(dat.glad$over_one_year_time_diff_sign_up_coping)
+```
+
+#Total score comparison between PHQ, PCL and GAD, prepandemic, retrospecive and baseline
+PHQ difference scores
+```{r phq difference scores}
+# Difference score for prepandemic and retrospective phq sum scores
+dat.glad <- dat.glad %>%
+  mutate(
+    phq.diff_score_prepan_retro =
+      as.numeric(
+        phq.sum_score_prepan - phq.sum_score_retro  # retrospective sum score MINUS prepandemic sum score 
+      )
+  )
+
+summary(dat.glad$phq.diff_score_prepan_retro)
+
+# Difference score for prepandemic and baseline phq sum scores
+dat.glad <- dat.glad %>%
+  mutate(
+    phq.diff_score_prepan_base =
+      as.numeric(
+        phq.sum_score_base - phq.sum_score_prepan  # baseline sum score MINUS prepandemic sum score 
+      )
+  )
+
+summary(dat.glad$phq.diff_score_prepan_base)
+
+# Difference score for retrospective and baseline phq sum scores
+dat.glad <- dat.glad %>%
+  mutate(
+    phq.diff_score_base_retro =
+      as.numeric(
+        phq.sum_score_base - phq.sum_score_retro  # baseline sum score MINUS retrospective sum score 
+      )
+  )
+
+summary(dat.glad$phq.diff_score_base_retro)
+
+```
+
+GAD difference scores
+```{r gad difference scores}
+# Difference score for prepandemic and retrospective gad sum scores
+dat.glad <- dat.glad %>%
+  mutate(
+    gad.diff_score_prepan_retro =
+      as.numeric(
+        gad.sum_score_prepan - gad.sum_score_retro  # retrospective sum score MINUS prepandemic sum score 
+      )
+  )
+
+summary(dat.glad$gad.diff_score_prepan_retro)
+
+# Difference score for prepandemic and baseline gad sum scores
+dat.glad <- dat.glad %>%
+  mutate(
+    gad.diff_score_prepan_base =
+      as.numeric(
+        gad.sum_score_base - gad.sum_score_prepan  # baseline sum score MINUS prepandemic sum score 
+      )
+  )
+
+summary(dat.glad$gad.diff_score_prepan_base)
+
+# Difference score for retrospective and baseline gad sum scores
+dat.glad <- dat.glad %>%
+  mutate(
+    gad.diff_score_base_retro =
+      as.numeric(
+        gad.sum_score_base - gad.sum_score_retro  # baseline sum score MINUS retrospective sum score 
+      )
+  )
+
+summary(dat.glad$gad.diff_score_base_retro)
+
+```
+
+PCL difference scores
+NOTE: Only computed baseline and prepandemic differences as the retro account here isn't actually retrospective, but whether the reported baseline scores are due to the pandemic. 
+```{r pcl difference scores}
+# Difference score for prepandemic and baseline pcl sum scores
+dat.glad <- dat.glad %>%
+  mutate(
+    pcl.diff_score_prepan_base =
+      as.numeric(
+        pcl.sum_score_base - pcl.sum_score_prepan  # baseline sum score MINUS prepandemic sum score 
+      )
+  )
+
+summary(dat.glad$pcl.diff_score_prepan_base)
+```
+
+```{r frequency of those who reported "due to pandemic" in retro PCL}
+summary(dat.glad$pcl.sum_score_retro)
+
+freq(dat.glad$pcl.stressful_experience_repeated_images_retro)
+freq(dat.glad$pcl.stressful_situation_avoiding_activities_retro)
+freq(dat.glad$pcl.feeling_irritable_or_having_angry_outbursts_retro)
+freq(dat.glad$pcl.stressful_experience_upset_reminded_retro)
+freq(dat.glad$pcl.cut_people_feeling_distant_retro)
+freq(dat.glad$pcl.difficulty_concentrating_retro)
+```
+
+#Data level groups
+Identify which data (prepan, retro and baseline) each participant has.
+```{r data level groups PHQ}
+dat.glad <- dat.glad %>%
+  mutate(
+    data_group_phq_numeric =
+      case_when(
+        na_per_person_phq_base == 0 & na_per_person_phq_prepan == 0 & na_per_person_phq_retro == 0 ~ 5, #all complete baseline, prepan and retro
+        na_per_person_phq_base != 0 & na_per_person_phq_prepan != 0 & na_per_person_phq_retro == 0  ~ 4, #retro data only
+        na_per_person_phq_base == 0 & na_per_person_phq_prepan != 0 & na_per_person_phq_retro != 0  ~ 3, #baseline data only
+        na_per_person_phq_base == 0 & na_per_person_phq_prepan == 0 & na_per_person_phq_retro != 0  ~ 2, #prepan and baseline data only
+        na_per_person_phq_base == 0 & na_per_person_phq_prepan != 0 & na_per_person_phq_retro == 0 ~ 1,  #baseline and retro data only
+        na_per_person_phq_base != 0 & na_per_person_phq_prepan == 0 & na_per_person_phq_retro != 0  ~ 0  #prepan data only
+      )
+  )
+
+dat.glad <- dat.glad %>%
+  mutate(
+    data_group_phq = 
+      recode_factor(
+        data_group_phq_numeric,
+        "0" = "Only prepandemic data",
+        "1" = "Baseline and retrospective data",
+        "2" = "Prepandemic and baseline data",
+        "3" = "Baseline data only",
+        "4" = "Retrospective data only",
+        "5" = "All prepandemic, baseline and retrospective data"
+      )
+  )
+
+table(dat.glad$data_group_phq)
+```
+
+GAD
+```{r data level groups GAD}
+dat.glad <- dat.glad %>%
+  mutate(
+    data_group_gad_numeric =
+      case_when(
+        na_per_person_gad_base == 0 & na_per_person_gad_prepan == 0 & na_per_person_gad_retro == 0 ~ 5, #all complete baseline, prepan and retro
+        na_per_person_gad_base != 0 & na_per_person_gad_prepan != 0 & na_per_person_gad_retro == 0  ~ 4, #retro data only
+        na_per_person_gad_base == 0 & na_per_person_gad_prepan != 0 & na_per_person_gad_retro != 0  ~ 3, #baseline data only
+        na_per_person_gad_base == 0 & na_per_person_gad_prepan == 0 & na_per_person_gad_retro != 0  ~ 2, #prepan and baseline data only
+        na_per_person_gad_base == 0 & na_per_person_gad_prepan != 0 & na_per_person_gad_retro == 0 ~ 1,  #baseline and retro data only
+        na_per_person_gad_base != 0 & na_per_person_gad_prepan == 0 & na_per_person_gad_retro != 0  ~ 0  #prepan data only
+      )
+  )
+
+dat.glad <- dat.glad %>%
+  mutate(
+    data_group_gad = 
+      recode_factor(
+        data_group_gad_numeric,
+        "0" = "Only prepandemic data",
+        "1" = "Baseline and retrospective data",
+        "2" = "Prepandemic and baseline data",
+        "3" = "Baseline data only",
+        "4" = "Retrospective data only",
+        "5" = "All prepandemic, baseline and retrospective data"
+      )
+  )
+
+table(dat.glad$data_group_gad)
+```
+
+PCL
+```{r data level groups PCL}
+dat.glad <- dat.glad %>%
+  mutate(
+    data_group_pcl_numeric =
+      case_when(
+        na_per_person_pcl_base == 0 & na_per_person_pcl_prepan == 0 & na_per_person_pcl_retro == 0 ~ 5, #all complete baseline, prepan and retro
+        na_per_person_pcl_base != 0 & na_per_person_pcl_prepan != 0 & na_per_person_pcl_retro == 0  ~ 4, #retro data only
+        na_per_person_pcl_base == 0 & na_per_person_pcl_prepan != 0 & na_per_person_pcl_retro != 0  ~ 3, #baseline data only
+        na_per_person_pcl_base == 0 & na_per_person_pcl_prepan == 0 & na_per_person_pcl_retro != 0  ~ 2, #prepan and baseline data only
+        na_per_person_pcl_base == 0 & na_per_person_pcl_prepan != 0 & na_per_person_pcl_retro == 0 ~ 1,  #baseline and retro data only
+        na_per_person_pcl_base != 0 & na_per_person_pcl_prepan == 0 & na_per_person_pcl_retro != 0  ~ 0  #prepan data only
+      )
+  )
+
+dat.glad <- dat.glad %>%
+  mutate(
+    data_group_pcl = 
+      recode_factor(
+        data_group_pcl_numeric,
+        "0" = "Only prepandemic data",
+        "1" = "Baseline and retrospective data",
+        "2" = "Prepandemic and baseline data",
+        "3" = "Baseline data only",
+        "4" = "Retrospective data only",
+        "5" = "All prepandemic, baseline and retrospective data"
+      )
+  )
+
+table(dat.glad$data_group_pcl)
+```
+
+#Read in respiratory data
+```{r coping resp cols}
+coping.glad.respiratory.raw <- readRDS(file = paste0(data.raw_path, "/2020-08-03/glad/respiratory_coping_glad.rds"))
+dim(coping.glad.respiratory.raw)
+colnames(coping.glad.respiratory.raw)
+```
+
+Select respiratory variables
+```{r read in respiratory data}
+coping.glad.respiratory.raw.id <- coping.glad.respiratory.raw %>%
   drop_na(externalDataReference) %>% # Drop NAs
@@
     Sample, # Sample
-    ID, # ID
-    ocir.i_repeatedly_check_doors_windows_drawers_etc_retro = ocir.i_repeatedly_check_doors_windows_drawers_etc.,
-    ocir.arranged_things_change_upset_retro = ocir.arranged_things_change_upset,
-    ocir.repeat_feel_numbers_retro = ocir.numbers_repeat_feel, ## Different from GLAD prepandemic
-    ocir.clean_simply_wash_feel_retro = ocir.feel_contaminated_clean_simply, ## Different from GLAD prepandemic
-    ocir.mind_upset_unpleasant_thoughts_retro = ocir.mind_upset_unpleasant_thoughts,
-    ocir.afraid_avoid_throwing_things_retro = ocir.afraid_avoid_throwing_things,
-    ocir.light_switches_water_taps_retro = ocir.light_switches_water_taps,
-    ocir.arranged_things_retro = ocir.arranged_things,
-    ocir.good_feel_bad_numbers_retro = ocir.bad_numbers_good_feel, ## Different from GLAD prepandemic
-    ocir.hands_longer_wash_retro = ocir.longer_hands_wash, ## Different from GLAD prepandemic
-    ocir.saved_things_retro = ocir.saved_things,
-    ocir.frequently_difficulty_rid_nasty_retro = ocir.frequently_rid_difficulty_nasty, ## Different from GLAD prepandemic
-    ocir.i_check_things_more_often_than_necessary_retro = ocir.i_check_things_more_often_than_necessary.,
-    ocir.arranged_properly_objects_upset_retro = ocir.arranged_properly_objects_upset,
-    ocir.feel_compelled_count_things_retro = ocir.feel_compelled_count_things,
-    ocir.strangers_touch_touched_difficult_retro = ocir.strangers_touch_touched_object, ## Different from GLAD prepandemic
-    ocir.control_difficult_find_thoughts_retro = ocir.control_find_difficult_thoughts, ## Different from GLAD prepandemic
-    ocir.i_collect_things_i_dont_need_retro = ocir.i_collect_things_i_dont_need., ## Different from GLAD prepandemic
-    ocir.i_repeatedly_check_doors_windows_drawers_etc_base = ocir.i_repeatedly_check_doors_windows_drawers_etc..1,
-    ocir.arranged_things_change_upset_base = ocir.arranged_things_change_upset.1,
-    ocir.repeat_feel_numbers_base = ocir.numbers_repeat_feel.1, ## Different from GLAD prepandemic
-    ocir.clean_simply_wash_feel_base = ocir.feel_contaminated_clean_simply.1, ## Different from GLAD prepandemic
-    ocir.mind_upset_unpleasant_thoughts_base = ocir.mind_upset_unpleasant_thoughts.1,
-    ocir.afraid_avoid_throwing_things_base = ocir.afraid_avoid_throwing_things.1,
-    ocir.light_switches_water_taps_base = ocir.light_switches_water_taps.1,
-    ocir.arranged_things_base = ocir.arranged_things.1,
-    ocir.good_feel_bad_numbers_base = ocir.bad_numbers_good_feel.1, ## Different from GLAD prepandemic
-    ocir.hands_longer_wash_base = ocir.longer_hands_wash.1, ## Different from GLAD prepandemic
-    ocir.saved_things_base = ocir.saved_things.1,
-    ocir.frequently_difficulty_rid_nasty_base = ocir.frequently_rid_difficulty_nasty.1, ## Different from GLAD prepandemic
-    ocir.i_check_things_more_often_than_necessary_base = ocir.i_check_things_more_often_than_necessary..1,
-    ocir.arranged_properly_objects_upset_base = ocir.arranged_properly_objects_upset.1,
-    ocir.feel_compelled_count_things_base = ocir.feel_compelled_count_things.1,
-    ocir.strangers_touch_touched_difficult_base = ocir.strangers_touch_touched_object.1, ## Different from GLAD prepandemic
-    ocir.control_difficult_find_thoughts_base = ocir.control_find_difficult_thoughts.1, ## Different from GLAD prepandemic
-    ocir.i_collect_things_i_dont_need_base = ocir.i_collect_things_i_dont_need..1
+    ID,
+    respiratory.breath_diarrhoea_fatigue_fever,
+    respiratory.worst_ill_feel,
+    respiratory.persistent_cough,
+    respiratory.skipping_meals_because_you_felt_unwell,
+    respiratory.was_your_sense_of_smell_impaired,
+    respiratory.was_your_sense_of_taste_impaired,
+    respiratory.feeling_tiredfatigued,
+    respiratory.throat_swab_coronavirus_nose,
+    respiratory.throat_swab_test_nose,
+    respiratory.coronavirus_antibody_test,
+    respiratory.results_antibody_test
+    # ID
   ) %>%
@@
 # Inspect dimensions
-dim(coping.glad.ocir.raw.id)
+dim(coping.glad.respiratory.raw.id)
 # Inspect colnames
-colnames(coping.glad.ocir.raw.id)
+colnames(coping.glad.respiratory.raw.id)
 #Differences
-dim(coping.glad.ocir.raw)[1]-dim(coping.glad.ocir.raw.id)[1]
-```
-
-Calculate sum score for OCI-R retro
-```{r coping ocir sum score retro}
-# Create vector with scoring key: If the item is reversed coded use -1. 
-# There needs to be the correct number of values for each item in the questionnaire. 
-ocir.items_key_retro <- c(1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1)
-
-# Create vector with items that are included in total score
-ocir.items_retro = c(
-  "ocir.i_repeatedly_check_doors_windows_drawers_etc_retro",
-  "ocir.arranged_things_change_upset_retro",
-  "ocir.repeat_feel_numbers_retro",
-  "ocir.clean_simply_wash_feel_retro",
-  "ocir.mind_upset_unpleasant_thoughts_retro",
-  "ocir.afraid_avoid_throwing_things_retro",
-  "ocir.light_switches_water_taps_retro",
-  "ocir.arranged_things_retro",
-  "ocir.good_feel_bad_numbers_retro",
-  "ocir.hands_longer_wash_retro",
-  "ocir.saved_things_retro",
-  "ocir.frequently_difficulty_rid_nasty_retro",
-  "ocir.i_check_things_more_often_than_necessary_retro",
-  "ocir.arranged_properly_objects_upset_retro",
-  "ocir.feel_compelled_count_things_retro",
-  "ocir.strangers_touch_touched_difficult_retro",
-  "ocir.control_difficult_find_thoughts_retro",
-  "ocir.i_collect_things_i_dont_need_retro"
-)
-
-# Calulate total score
-ocir.scored_items_retro <- scoreItems(keys = ocir.items_key_retro,
-                                     items = coping.glad.ocir.raw.id[ocir.items_retro],
-                                     totals = TRUE, 
-                                     missing = TRUE, 
-                                     impute = 'none', 
-                                     min = 0, 
-                                     max = 4)
-# Add in column to tibble
-coping.glad.ocir.raw.id$ocir.sum_score_retro <- ocir.scored_items_retro$scores
-
-# Look at values
-coping.glad.ocir.raw.id %>%
-  descr(ocir.sum_score_retro,
-        stats = "common"
-  )
-```
-
-Calculate sum score for OCI-R base
-```{r coping ocir sum score base}
-# Create vector with scoring key: If the item is reversed coded use -1. 
-# There needs to be the correct number of values for each item in the questionnaire. 
-ocir.items_key_base <- c(1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1)
-
-# Create vector with items that are included in total score
-ocir.items_base = c(
-  "ocir.i_repeatedly_check_doors_windows_drawers_etc_base",
-  "ocir.arranged_things_change_upset_base",
-  "ocir.repeat_feel_numbers_base",
-  "ocir.clean_simply_wash_feel_base",
-  "ocir.mind_upset_unpleasant_thoughts_base",
-  "ocir.afraid_avoid_throwing_things_base",
-  "ocir.light_switches_water_taps_base",
-  "ocir.arranged_things_base",
-  "ocir.good_feel_bad_numbers_base",
-  "ocir.hands_longer_wash_base",
-  "ocir.saved_things_base",
-  "ocir.frequently_difficulty_rid_nasty_base",
-  "ocir.i_check_things_more_often_than_necessary_base",
-  "ocir.arranged_properly_objects_upset_base",
-  "ocir.feel_compelled_count_things_base",
-  "ocir.strangers_touch_touched_difficult_base",
-  "ocir.control_difficult_find_thoughts_base",
-  "ocir.i_collect_things_i_dont_need_base"
-)
-
-# Calulate total score
-ocir.scored_items_base <- scoreItems(keys = ocir.items_key_base,
-                                    items = coping.glad.ocir.raw.id[ocir.items_base],
-                                    totals = TRUE, 
-                                    missing = TRUE, 
-                                    impute = 'none', 
-                                    min = 0, 
-                                    max = 4)
-# Add in column to tibble
-coping.glad.ocir.raw.id$ocir.sum_score_base <- ocir.scored_items_base$scores
-
-# Look at values
-coping.glad.ocir.raw.id %>%
-  descr(ocir.sum_score_base,
-        stats = "common"
-  )
-```
-
-```{r coping glad ocir head}
-head(coping.glad.ocir.raw.id)
-```
-
-```{r coping glad ocir summary}
-summarytools::dfSummary(
-  coping.glad.ocir.raw.id,
-  graph.col = F,
-  valid.col = F,
-  labels.col = F)
-```
-
-# Join tibbles together
-
-glad data frame list
-```{r glad data frame list}
-glad.dfs.list <- list(
-  glad.dem.raw.id,
-  glad.gad.raw.id,
-  glad.mhq.raw.categories,
-  glad.ocir.raw.id,
-  glad.pcl.raw.id,
-  glad.phq.raw.id,
-  coping.glad.gad.raw.id,
-  coping.glad.pcl.raw.id,
-  coping.glad.phq.raw.id,
-  coping.glad.ocir.raw.id
-)
-```
-
-```{r Join all questionnaires for glad}
-dat.glad.raw <- plyr::join_all(
-  glad.dfs.list,
-  by = c("ID", "Sample") # Alternatively you can join by several columns EDGI -> "Age", "Sex", "Birthyear"
-  )
-
-#look at the data
-skimr::skim(dat.glad.raw)
-```
-
-Check duplicates again to be saved
-+++KLP: RAMP: More than one column: Age, Sex, Login ID; if they match on all 3 then we treat them as a duplicate; otherwise we are going to rename the Login ID
-+++KT: No duplicates identified by ID in GLAD. 
-```{r glad Check duplicates}
-dat.glad.raw$ID.dup <- duplicated(dat.glad.raw$ID)
-
-summary(as.factor(dat.glad.raw$ID.dup))
-
-dat.dup <- dat.glad.raw %>%
-  filter(ID.dup == TRUE)
-
-dat.glad.raw.no.dup <- dat.glad.raw %>%
-  filter(ID.dup == FALSE)
-```
-
-#Exclusion
-Exclude those without sex, gender, age and incomplete PHQ/GAD items
-Create a new new object for each exclusion step, e.g., data.no_sex, data.no_gender and data.no_sex.no_age
-```{r Exclude participants that do not report sex}
-dim(dat.glad.raw)
-dat.no.sex <- dat.glad.raw %>%
-  drop_na(Sex)
-dim(dat.no.sex)
-
-dim(dat.glad.raw)[1]-dim(dat.no.sex)[1]
-```
-`r dim(dat.glad.raw)[1]-dim(dat.no.sex)[1]` were excluded because they did not report their sex
-
-```{r Exclude participants that do not report gender}
-dim(dat.no.sex)
-dat.no.sex.no.gender <- dat.no.sex %>%
-  drop_na(Gender)
-dim(dat.no.sex.no.gender)
-
-dim(dat.no.sex)[1]-dim(dat.no.sex.no.gender)[1]
-```
-`r dim(dat.no.sex)[1]-dim(dat.no.sex.no.gender)[1]` were excluded because they did not report their sex
-
-```{r Exclude participants that do not report age}
-dim(dat.no.sex.no.gender)
-dat.no.sex.no.gender.no.age <- dat.no.sex.no.gender %>%
-  drop_na(age_category)
-dim(dat.no.sex.no.gender.no.age)
-
-dim(dat.no.sex.no.gender)[1]-dim(dat.no.sex.no.gender.no.age)[1]
-```
-`r dim(dat.no.gender)[1]-dim(dat.no.sex.no.gender.no.age)[1]` were excluded because they did not report their age
-
-Exclusion of inflammatory bowel disease (IBD) BioResource (BR) cohort
-```{r COVID exclusion of IBD}
-#dim(dat.no.sex.no.age)
-#
-#dat.no.sex.no.age <- dat.no.sex.no.age %>%
-#  filter(NBR.IBD == 0)
-#
-#dim(dat.no.sex.no.age.no.ibd)
-#
-#dim(dat.no.sex.no.age)[1]-dim(dat.no.sex.no.age.no.ibd)[1]
-
-dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age
-```
-
-##Missingness of questionnaire items
-#PHQ - baseline
-PHQ Missingness NAs per person - count and percentages
-```{r PHQ baseline missingness}
-dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
-  mutate(
-    na_per_person_phq_base =         # variable for NA per person
-      rowSums(                       
-        is.na(dat.no.sex.no.gender.no.age.no.ibd # sum the rows that are NA
-          [,colnames(dat.no.sex.no.gender.no.age.no.ibd) #for all the rows and columns that are in the PHQ items at baseline
-           %in%
-             phq.items_base]
-        )
-    )
-  )
-
-freq(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_phq_base) #have a look at the frequency
-
-dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>% #NA per person as a percentage
-  mutate(
-    miss_pc_total_phq_base = 
-      na_per_person_phq_base/9 # NA per person divided by the amount of items
-  )
-
-freq(dat.no.sex.no.gender.no.age.no.ibd$miss_pc_total_phq_base)
-```
-
-#PHQ - retrospective
-PHQ Missingness NAs per person - count and percentages
-```{r PHQ retrospective missingness}
-dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
-  mutate(
-    na_per_person_phq_retro =         # variable for NA per person
-      rowSums(                       
-        is.na(dat.no.sex.no.gender.no.age.no.ibd # sum the rows that are NA
-          [,colnames(dat.no.sex.no.gender.no.age.no.ibd) #for all the rows and columns that are in the PHQ items at retroline
-           %in%
-             phq.items_retro]
-        )
-    )
-  )
-
-freq(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_phq_retro) #have a look at the frequency
-
-dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>% #NA per person as a percentage
-  mutate(
-    miss_pc_total_phq_retro = 
-      na_per_person_phq_retro/9 # NA per person divided by the amount of items
-  )
-
-freq(dat.no.sex.no.gender.no.age.no.ibd$miss_pc_total_phq_retro)
-```
-
-#PHQ - prepandemic
-PHQ Missingness NAs per person - count and percentages
-```{r PHQ prepan missingness}
-dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
-  mutate(
-    na_per_person_phq_prepan =         # variable for NA per person
-      rowSums(                       
-        is.na(dat.no.sex.no.gender.no.age.no.ibd # sum the rows that are NA
-          [,colnames(dat.no.sex.no.gender.no.age.no.ibd) #for all the rows and columns that are in the PHQ items at prepanline
-           %in%
-             phq.items_prepan]
-        )
-    )
-  )
-
-freq(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_phq_prepan) #have a look at the frequency
-
-dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>% #NA per person as a percentage
-  mutate(
-    miss_pc_total_phq_prepan = 
-      na_per_person_phq_prepan/9 # NA per person divided by the amount of items
-  )
-
-freq(dat.no.sex.no.gender.no.age.no.ibd$miss_pc_total_phq_prepan)
-```
-
-Count for PHQ baseline, retrospective, and prepandemic missingness per person
-```{r count of people missing a number of items for PHQ}
-#baseline
-table(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_phq_base)
-#retrospective
-table(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_phq_retro)
-#pre-pandemic
-table(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_phq_prepan)
-```
-
-#GAD - baseline
-GAD Missingness NAs per person - count and percentages
-```{r gad baseline missingness}
-dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
-  mutate(
-    na_per_person_gad_base =         # variable for NA per person
-      rowSums(                       
-        is.na(dat.no.sex.no.gender.no.age.no.ibd # sum the rows that are NA
-          [,colnames(dat.no.sex.no.gender.no.age.no.ibd) #for all the rows and columns that are in the gad items at baseline
-           %in%
-             gad.items_base]
-        )
-    )
-  )
-
-freq(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_gad_base) #have a look at the frequency
-
-dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>% #NA per person as a percentage
-  mutate(
-    miss_pc_total_gad_base = 
-      na_per_person_gad_base/7 # NA per person divided by the amount of items
-  )
-
-freq(dat.no.sex.no.gender.no.age.no.ibd$miss_pc_total_gad_base)
-```
-
-#GAD - retrospective
-GAD Missingness NAs per person - count and percentages
-```{r gad retrospective missingness}
-dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
-  mutate(
-    na_per_person_gad_retro =         # variable for NA per person
-      rowSums(                       
-        is.na(dat.no.sex.no.gender.no.age.no.ibd # sum the rows that are NA
-          [,colnames(dat.no.sex.no.gender.no.age.no.ibd) #for all the rows and columns that are in the gad items at retroline
-           %in%
-             gad.items_retro]
-        )
-    )
-  )
-
-freq(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_gad_retro) #have a look at the frequency
-
-dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>% #NA per person as a percentage
-  mutate(
-    miss_pc_total_gad_retro = 
-      na_per_person_gad_retro/7 # NA per person divided by the amount of items
-  )
-
-freq(dat.no.sex.no.gender.no.age.no.ibd$miss_pc_total_gad_retro)
-```
-
-#GAD - prepandemic
-GAD Missingness NAs per person - count and percentages
-```{r gad prepan missingness}
-dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
-  mutate(
-    na_per_person_gad_prepan =         # variable for NA per person
-      rowSums(                       
-        is.na(dat.no.sex.no.gender.no.age.no.ibd # sum the rows that are NA
-          [,colnames(dat.no.sex.no.gender.no.age.no.ibd) #for all the rows and columns that are in the gad items at prepanline
-           %in%
-             gad.items_prepan]
-        )
-    )
-  )
-
-freq(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_gad_prepan) #have a look at the frequency
-
-dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>% #NA per person as a percentage
-  mutate(
-    miss_pc_total_gad_prepan = 
-      na_per_person_gad_prepan/7 # NA per person divided by the amount of items
-  )
-
-freq(dat.no.sex.no.gender.no.age.no.ibd$miss_pc_total_gad_prepan)
-```
-
-Count for gad baseline, retrospective, and prepandemic missingness per person
-```{r count of people missing a number of items for gad}
-#baseline
-table(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_gad_base)
-#retrospective
-table(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_gad_retro)
-#pre-pandemic
-table(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_gad_prepan)
-```
-
-#PCL - baseline
-PCL Missingness NAs per person - count and percentages
-```{r pcl baseline missingness}
-dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
-  mutate(
-    na_per_person_pcl_base =         # variable for NA per person
-      rowSums(                       
-        is.na(dat.no.sex.no.gender.no.age.no.ibd # sum the rows that are NA
-          [,colnames(dat.no.sex.no.gender.no.age.no.ibd) #for all the rows and columns that are in the pcl items at baseline
-           %in%
-             pcl.items_base]
-        )
-    )
-  )
-
-freq(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_pcl_base) #have a look at the frequency
-
-dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>% #NA per person as a percentage
-  mutate(
-    miss_pc_total_pcl_base = 
-      na_per_person_pcl_base/6 # NA per person divided by the amount of items
-  )
-
-freq(dat.no.sex.no.gender.no.age.no.ibd$miss_pc_total_pcl_base)
-```
-
-#PCL - retrospective
-PCL Missingness NAs per person - count and percentages
-```{r pcl retrospective missingness}
-dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
-  mutate(
-    na_per_person_pcl_retro =         # variable for NA per person
-      rowSums(                       
-        is.na(dat.no.sex.no.gender.no.age.no.ibd # sum the rows that are NA
-          [,colnames(dat.no.sex.no.gender.no.age.no.ibd) #for all the rows and columns that are in the pcl items at retroline
-           %in%
-             pcl.items_retro]
-        )
-    )
-  )
-
-freq(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_pcl_retro) #have a look at the frequency
-
-dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>% #NA per person as a percentage
-  mutate(
-    miss_pc_total_pcl_retro = 
-      na_per_person_pcl_retro/6 # NA per person divided by the amount of items
-  )
-
-freq(dat.no.sex.no.gender.no.age.no.ibd$miss_pc_total_pcl_retro)
-```
-
-#PCL - prepandemic
-pcl Missingness NAs per person - count and percentages
-```{r pcl prepan missingness}
-dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
-  mutate(
-    na_per_person_pcl_prepan =         # variable for NA per person
-      rowSums(                       
-        is.na(dat.no.sex.no.gender.no.age.no.ibd # sum the rows that are NA
-          [,colnames(dat.no.sex.no.gender.no.age.no.ibd) #for all the rows and columns that are in the pcl items at prepanline
-           %in%
-             pcl.items_prepan]
-        )
-    )
-  )
-
-freq(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_pcl_prepan) #have a look at the frequency
-
-dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>% #NA per person as a percentage
-  mutate(
-    miss_pc_total_pcl_prepan = 
-      na_per_person_pcl_prepan/6 # NA per person divided by the amount of items
-  )
-
-freq(dat.no.sex.no.gender.no.age.no.ibd$miss_pc_total_pcl_prepan)
-```
-
-Count for pcl baseline, retrospective, and prepandemic missingness per person
-```{r count of people missing a number of items for pcl}
-# baseline
-table(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_pcl_base)
-# retrospective
-table(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_pcl_retro)
-# pre-pandemic
-table(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_pcl_prepan)
-
-# rename dataset
-dat.no.sex.no.gender.no.age.no.ibd.missingness <- dat.no.sex.no.gender.no.age.no.ibd
-```
-
-#OCI-R - baseline
-OCI-R Missingness NAs per person - count and percentages
-```{r OCI-R baseline missingness}
-dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
-  mutate(
-    na_per_person_ocir_base =         # variable for NA per person
-      rowSums(                       
-        is.na(dat.no.sex.no.gender.no.age.no.ibd # sum the rows that are NA
-          [,colnames(dat.no.sex.no.gender.no.age.no.ibd) #for all the rows and columns that are in the OCI-R items at baseline
-           %in%
-             ocir.items_base]
-        )
-    )
-  )
-
-freq(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_ocir_base) #have a look at the frequency
-
-dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>% #NA per person as a percentage
-  mutate(
-    miss_pc_total_ocir_base = 
-      na_per_person_ocir_base/18 # NA per person divided by the amount of items
-  )
-
-freq(dat.no.sex.no.gender.no.age.no.ibd$miss_pc_total_ocir_base)
-```
-
-#OCI-R - retrospective
-OCI-R Missingness NAs per person - count and percentages
-```{r OCI-R retrospective missingness}
-dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
-  mutate(
-    na_per_person_ocir_retro =         # variable for NA per person
-      rowSums(                       
-        is.na(dat.no.sex.no.gender.no.age.no.ibd # sum the rows that are NA
-          [,colnames(dat.no.sex.no.gender.no.age.no.ibd) #for all the rows and columns that are in the OCI-R items at retroline
-           %in%
-             ocir.items_retro]
-        )
-    )
-  )
-
-freq(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_ocir_retro) #have a look at the frequency
-
-dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>% #NA per person as a percentage
-  mutate(
-    miss_pc_total_ocir_retro = 
-      na_per_person_ocir_retro/18 # NA per person divided by the amount of items
-  )
-
-freq(dat.no.sex.no.gender.no.age.no.ibd$miss_pc_total_ocir_retro)
-```
-
-#OCI-R - prepandemic
-OCI-R Missingness NAs per person - count and percentages
-```{r OCI-R prepan missingness}
-dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
-  mutate(
-    na_per_person_ocir_prepan =         # variable for NA per person
-      rowSums(                       
-        is.na(dat.no.sex.no.gender.no.age.no.ibd # sum the rows that are NA
-          [,colnames(dat.no.sex.no.gender.no.age.no.ibd) #for all the rows and columns that are in the OCI-R items at prepanline
-           %in%
-             ocir.items_prepan]
-        )
-    )
-  )
-
-freq(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_ocir_prepan) #have a look at the frequency
-
-dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>% #NA per person as a percentage
-  mutate(
-    miss_pc_total_ocir_prepan = 
-      na_per_person_ocir_prepan/18 # NA per person divided by the amount of items
-  )
-
-freq(dat.no.sex.no.gender.no.age.no.ibd$miss_pc_total_ocir_prepan)
-```
-
-Count for OCI-R baseline, retrospective, and prepandemic missingness per person
-```{r count of people missing a number of items for OCI-R}
-#baseline
-table(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_ocir_base)
-#retrospective
-table(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_ocir_retro)
-#pre-pandemic
-table(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_ocir_prepan)
-```
-
-#Creating "complete cases" datasets  - NOTE THIS PROBABLY WONT BE USED BUT JUST TO GIVE AN IDEA OF COMPLETE CASES NUMBERS. KT. 
-Complete case data for PHQ, GAD and PCL - 3345 remaining, drop 35,036.
-```{r complete cases only}
-all.items <- c(phq.items_prepan,
-                phq.items_base,
-                phq.items_retro,
-                gad.items_prepan,
-                gad.items_base,
-                gad.items_retro,
-                pcl.items_prepan,
-                pcl.items_base,
-                pcl.items_retro)
-
-dat.no.sex.no.gender.no.age.no.ibd.complete.cases <- dat.no.sex.no.gender.no.age.no.ibd[complete.cases(dat.no.sex.no.gender.no.age.no.ibd[, all.items ]),]
-
-dim(dat.no.sex.no.gender.no.age.no.ibd.complete.cases)
-dim(dat.no.sex.no.gender.no.age.no.ibd)[1]-dim(dat.no.sex.no.gender.no.age.no.ibd.complete.cases)[1]
-```
-
-PHQ
-Complete case data for PHQ baseline (COPING) - 9,260 remaining
-```{r complete cases phq base}
-dat.no.sex.no.gender.no.age.no.ibd.complete.cases.phq.base <- dat.no.sex.no.gender.no.age.no.ibd[complete.cases(dat.no.sex.no.gender.no.age.no.ibd[, phq.items_base ]),]
-
-dim(dat.no.sex.no.gender.no.age.no.ibd.complete.cases.phq.base)
-dim(dat.no.sex.no.gender.no.age.no.ibd)[1]-dim(dat.no.sex.no.gender.no.age.no.ibd.complete.cases.phq.base)[1]
-```
-
-Complete case data for PHQ pre-pandemic (GLAD) - 37,308 remaining
-```{r complete cases phq prepan}
-dat.no.sex.no.gender.no.age.no.ibd.complete.cases.phq.prepan <- dat.no.sex.no.gender.no.age.no.ibd[complete.cases(dat.no.sex.no.gender.no.age.no.ibd[, phq.items_prepan ]),]
-
-dim(dat.no.sex.no.gender.no.age.no.ibd.complete.cases.phq.prepan)
-dim(dat.no.sex.no.gender.no.age.no.ibd)[1]-dim(dat.no.sex.no.gender.no.age.no.ibd.complete.cases.phq.prepan)[1]
-```
-
-Complete case data for PHQ retrospective (COPING) - 9,262 remaining
-```{r complete cases phq retro}
-dat.no.sex.no.gender.no.age.no.ibd.complete.cases.phq.retro <- dat.no.sex.no.gender.no.age.no.ibd[complete.cases(dat.no.sex.no.gender.no.age.no.ibd[, phq.items_retro ]),]
-
-dim(dat.no.sex.no.gender.no.age.no.ibd.complete.cases.phq.retro)
-dim(dat.no.sex.no.gender.no.age.no.ibd)[1]-dim(dat.no.sex.no.gender.no.age.no.ibd.complete.cases.phq.retro)[1]
-```
-
-GAD
-Complete case data for GAD baseline (COPING) - 12,457 remaining
-```{r complete cases gad base}
-dat.no.sex.no.gender.no.age.no.ibd.complete.cases.gad.base <- dat.no.sex.no.gender.no.age.no.ibd[complete.cases(dat.no.sex.no.gender.no.age.no.ibd[, gad.items_base ]),]
-
-dim(dat.no.sex.no.gender.no.age.no.ibd.complete.cases.gad.base)
-dim(dat.no.sex.no.gender.no.age.no.ibd)[1]-dim(dat.no.sex.no.gender.no.age.no.ibd.complete.cases.gad.base)[1]
-```
-
-Complete case data for gad pre-pandemic (GLAD) - 36,149 remaining
-```{r complete cases gad prepan}
-dat.no.sex.no.gender.no.age.no.ibd.complete.cases.gad.prepan <- dat.no.sex.no.gender.no.age.no.ibd[complete.cases(dat.no.sex.no.gender.no.age.no.ibd[, gad.items_prepan ]),]
-
-dim(dat.no.sex.no.gender.no.age.no.ibd.complete.cases.gad.prepan)
-dim(dat.no.sex.no.gender.no.age.no.ibd)[1]-dim(dat.no.sex.no.gender.no.age.no.ibd.complete.cases.gad.prepan)[1]
-```
-
-Complete case data for gad retrospective (COPING) - 8,930 remaining
-```{r complete cases gad retro}
-dat.no.sex.no.gender.no.age.no.ibd.complete.cases.gad.retro <- dat.no.sex.no.gender.no.age.no.ibd[complete.cases(dat.no.sex.no.gender.no.age.no.ibd[, gad.items_retro ]),]
-
-dim(dat.no.sex.no.gender.no.age.no.ibd.complete.cases.gad.retro)
-dim(dat.no.sex.no.gender.no.age.no.ibd)[1]-dim(dat.no.sex.no.gender.no.age.no.ibd.complete.cases.gad.retro)[1]
-```
-
-PCL
-Complete case data for PCL baseline (COPING) - 12,376 remaining
-```{r complete cases pcl base}
-dat.no.sex.no.gender.no.age.no.ibd.complete.cases.pcl.base <- dat.no.sex.no.gender.no.age.no.ibd[complete.cases(dat.no.sex.no.gender.no.age.no.ibd[, pcl.items_base ]),]
-
-dim(dat.no.sex.no.gender.no.age.no.ibd.complete.cases.pcl.base)
-dim(dat.no.sex.no.gender.no.age.no.ibd)[1]-dim(dat.no.sex.no.gender.no.age.no.ibd.complete.cases.pcl.base)[1]
-```
-
-Complete case data for PCL pre-pandemic (GLAD) - 35,176 remaining
-```{r complete cases pcl prepan}
-dat.no.sex.no.gender.no.age.no.ibd.complete.cases.pcl.prepan <- dat.no.sex.no.gender.no.age.no.ibd[complete.cases(dat.no.sex.no.gender.no.age.no.ibd[, pcl.items_prepan ]),]
-
-dim(dat.no.sex.no.gender.no.age.no.ibd.complete.cases.pcl.prepan)
-dim(dat.no.sex.no.gender.no.age.no.ibd)[1]-dim(dat.no.sex.no.gender.no.age.no.ibd.complete.cases.pcl.prepan)[1]
-```
-
-Complete case data for PCL retrospective (COPING) - 4,618 remaining
-```{r complete cases pcl retro}
-dat.no.sex.no.gender.no.age.no.ibd.complete.cases.pcl.retro <- dat.no.sex.no.gender.no.age.no.ibd[complete.cases(dat.no.sex.no.gender.no.age.no.ibd[, pcl.items_retro ]),]
-
-dim(dat.no.sex.no.gender.no.age.no.ibd.complete.cases.pcl.retro)
-dim(dat.no.sex.no.gender.no.age.no.ibd)[1]-dim(dat.no.sex.no.gender.no.age.no.ibd.complete.cases.pcl.retro)[1]
-```
-
-##Create tidy data on which the exclusion criteria have been applied
-Complete sex, gender, age and missingness information applied. 
-```{r Tidy data}
-dat.glad <- dat.no.sex.no.gender.no.age.no.ibd.missingness
-
-skimr::skim(dat.glad)
-```
-
-# Definition of prepandemic and baseline 
-Exlcude people who have joined GLAD/EDGI after the pandemic began, sensitivity analyses done on the cut off's we have chosen. 
-Potentially GLAD/EDGI particiapnts between January to April. EDGI launched on February 24th.
-
-Prepandemic GLAD/EDGI = Prepandemic (GLAD/EDGI sign-up questionnaire)
-
-Retrospective = COPING/RAMP sign up questionnaire; *only of those participants who have reported a change in symptoms*
-
-Baseline = COPING/RAMP sign up questionnaire
-
-Dates for the definition of prepandemic
-```{r Potential dates for prepandemic definition}
-# Date of the first COVID-19 case in the United Kingdom (UK)
-date_first_case_uk_january_31 <- as.POSIXct("2020-01-31")
-
-# Date for assumed higher awareness of COVID / Lockdown in Italy 4. March 2020 / first festivals cancelled
-date_higher_awareness_march_1 <- as.POSIXct("2020-03-01")
-
-# Date the UK went into lockdown
-date_uk_lockdown_march_23 <- as.POSIXct("2020-03-23")
-```
-
-```{r Prepandemic definitions january_31}
-dat.glad <- dat.glad %>%
-  mutate(
-    prepandemic_january_31_numeric =
-      if_else(
-        startDate.glad > date_first_case_uk_january_31, # The GLAD sign up is dated before the cut off (> longer ago)
-        true = 0, # Participant has not signed up before the pandemic,
-        false = 1, # Participant has signed up before the pandemic,
-        missing = NA_real_
-      )
-  )
-
-dat.glad <- dat.glad %>%
-  mutate(
-    prepandemic_january_31 =
-      recode_factor(
-        prepandemic_january_31_numeric,
-        "0" = "Sign up after 31. January",
-        "1" = "Sign up before 31. January"
-      )
-  )
-
-dat.glad %>%
-  freq(prepandemic_january_31)
-```
-
-```{r Prepandemic definitions march_1}
-dat.glad <- dat.glad %>%
-  mutate(
-    prepandemic_march_1_numeric =
-      if_else(
-        startDate.glad > date_higher_awareness_march_1, # The GLAD sign up is dated before the cut off (> longer ago)
-        true = 0, # Participant has not signed up before the pandemic,
-        false = 1, # Participant has signed up before the pandemic,
-        missing = NA_real_
-      )
-  )
-
-dat.glad <- dat.glad %>%
-  mutate(
-    prepandemic_march_1 =
-      recode_factor(
-        prepandemic_march_1_numeric,
-        "0" = "Sign up after 1. March",
-        "1" = "Sign up before 1. March"
-      )
-  )
-
-dat.glad %>%
-  freq(prepandemic_march_1)
-```
-
-```{r Prepandemic definitions march_23}
-dat.glad <- dat.glad %>%
-  mutate(
-    prepandemic_march_23_numeric =
-      if_else(
-        startDate.glad > date_uk_lockdown_march_23, # The GLAD sign up is dated before the cut off (> longer ago)
-        true = 0, # Participant has not signed up before the pandemic,
-        false = 1, # Participant has signed up before the pandemic,
-        missing = NA_real_
-      )
-  )
-
-dat.glad <- dat.glad %>%
-  mutate(
-    prepandemic_march_23 =
-      recode_factor(
-        prepandemic_march_23_numeric,
-        "0" = "Sign up after 23. March",
-        "1" = "Sign up before 23. March"
-      )
-  )
-
-dat.glad %>%
-  freq(prepandemic_march_23)
-```
-
-Calculate the time difference between time difference between sign up questionnaire and COPING questionnaire
-```{r time difference between sign up questionnaire and COPING questionnaire}
-dat.glad <- dat.glad %>%
-  mutate(
-    time_diff_sign_up_coping =
-        as.numeric(
-        difftime(           #this function does time1 - time2 as difftime(time1, time2...)
-          startDate.coping.glad,    #should be start date for COPING (time1)
-          startDate.glad),    #should be start date for GLAD (time2)
-          units = c("days")  #can also be "secs", "mins", "hours", "weeks"
-          )
-        )
-
-dat.glad %>%
-  descr(
-    var = time_diff_sign_up_coping,
-    stats = "common"
-    )
-```
-
-Proportion of people signed up over one year ago
-```{r eval=FALSE, include=FALSE}
-dat.glad <- dat.glad %>%
-  mutate(
-    over_one_year_time_diff_sign_up_coping_numeric =
-      as.numeric(
-        if_else(time_diff_sign_up_coping > 365, 1, 0
-                )
-      )
-  )
-
-dat.glad <- dat.glad %>%
-  mutate(
-    over_one_year_time_diff_sign_up_coping =
-      recode_factor(
-        over_one_year_time_diff_sign_up_coping_numeric,
-        "0" = "Sign up under one year before COPING",
-        "1" = "Sign up over one year before COPING"
-      )
-  )
-
-table(dat.glad$over_one_year_time_diff_sign_up_coping)
-```
-
-#Total score comparison between PHQ, PCL and GAD, prepandemic, retrospecive and baseline
-PHQ difference scores
-```{r phq difference scores}
-# Difference score for prepandemic and retrospective phq sum scores
-dat.glad <- dat.glad %>%
-  mutate(
-    phq.diff_score_prepan_retro =
-      as.numeric(
-        phq.sum_score_prepan - phq.sum_score_retro  # retrospective sum score MINUS prepandemic sum score 
-      )
-  )
-
-summary(dat.glad$phq.diff_score_prepan_retro)
-
-# Difference score for prepandemic and baseline phq sum scores
-dat.glad <- dat.glad %>%
-  mutate(
-    phq.diff_score_prepan_base =
-      as.numeric(
-        phq.sum_score_prepan - phq.sum_score_base  # prepandemic sum score MINUS baseline sum score 
-      )
-  )
-
-summary(dat.glad$phq.diff_score_prepan_base)
-
-# Difference score for retrospective and baseline phq sum scores
-dat.glad <- dat.glad %>%
-  mutate(
-    phq.diff_score_base_retro =
-      as.numeric(
-        phq.sum_score_base - phq.sum_score_retro  # baseline sum score MINUS retrospective sum score 
-      )
-  )
-
-summary(dat.glad$phq.diff_score_base_retro)
-
-```
-
-GAD difference scores
-```{r gad difference scores}
-# Difference score for prepandemic and retrospective gad sum scores
-dat.glad <- dat.glad %>%
-  mutate(
-    gad.diff_score_prepan_retro =
-      as.numeric(
-        gad.sum_score_prepan - gad.sum_score_retro  # retrospective sum score MINUS prepandemic sum score 
-      )
-  )
-
-summary(dat.glad$gad.diff_score_prepan_retro)
-
-# Difference score for prepandemic and baseline gad sum scores
-dat.glad <- dat.glad %>%
-  mutate(
-    gad.diff_score_prepan_base =
-      as.numeric(
-        gad.sum_score_prepan - gad.sum_score_base  # prepandemic sum score MINUS baseline sum score 
-      )
-  )
-
-summary(dat.glad$gad.diff_score_prepan_base)
-
-# Difference score for retrospective and baseline gad sum scores
-dat.glad <- dat.glad %>%
-  mutate(
-    gad.diff_score_base_retro =
-      as.numeric(
-        gad.sum_score_base - gad.sum_score_retro  # baseline sum score MINUS retrospective sum score 
-      )
-  )
-
-summary(dat.glad$gad.diff_score_base_retro)
-
-```
-
-PCL difference scores
-NOTE: Only computed baseline and prepandemic differences as the retro account here isn't actually retrospective, but whether the reported baseline scores are due to the pandemic. 
-```{r pcl difference scores}
-# Difference score for prepandemic and baseline pcl sum scores
-dat.glad <- dat.glad %>%
-  mutate(
-    pcl.diff_score_prepan_base =
-      as.numeric(
-        pcl.sum_score_prepan - pcl.sum_score_base  # prepandemic sum score MINUS baseline sum score 
-      )
-  )
-
-summary(dat.glad$pcl.diff_score_prepan_base)
-```
-
-OCI-R difference scores
-```{r ocir difference scores}
-# Difference score for prepandemic and retrospective oci-r sum scores
-dat.glad <- dat.glad %>%
-  mutate(
-    ocir.diff_score_prepan_retro =
-      as.numeric(
-        ocir.sum_score_prepan - ocir.sum_score_retro  # retrospective sum score MINUS prepandemic sum score 
-      )
-  )
-
-summary(dat.glad$ocir.diff_score_prepan_retro)
-
-# Difference score for prepandemic and baseline ocir sum scores
-dat.glad <- dat.glad %>%
-  mutate(
-    ocir.diff_score_prepan_base =
-      as.numeric(
-        ocir.sum_score_prepan - ocir.sum_score_base  # prepandemic sum score MINUS baseline sum score 
-      )
-  )
-
-summary(dat.glad$ocir.diff_score_prepan_base)
-
-# Difference score for retrospective and baseline ocir sum scores
-dat.glad <- dat.glad %>%
-  mutate(
-    ocir.diff_score_base_retro =
-      as.numeric(
-        ocir.sum_score_base - ocir.sum_score_retro  # baseline sum score MINUS retrospective sum score 
-      )
-  )
-
-summary(dat.glad$ocir.diff_score_base_retro)
-
-```
-
-#Data level groups
-Identify which data (prepan, retro and baseline) each participant has.
-++KT: not sure how best to categorise here so this may need some revision. 
-```{r data level groups}
-dat.glad <- dat.glad %>%
-  mutate(
-    data_group_full_numeric =
-      case_when(
-        !is.na(startDate.glad) & !is.na(startDate.coping.glad) & na_per_person_phq_retro == 0  & na_per_person_gad_retro == 0 & na_per_person_pcl_retro == 0 ~ 5,
-        !is.na(startDate.glad) & !is.na(startDate.coping.glad) & na_per_person_pcl_retro == 0 ~ 4, #in GLAD, in COPING and have no missing PCL-retro items
-        !is.na(startDate.glad) & !is.na(startDate.coping.glad) & na_per_person_gad_retro == 0 ~ 3, #in GLAD, in COPING and have no missing GAD-retro items
-        !is.na(startDate.glad) & !is.na(startDate.coping.glad) & na_per_person_phq_retro == 0 ~ 2, #in GLAD, in COPING and have no missing PHQ-retro items
-        !is.na(startDate.glad) & !is.na(startDate.coping.glad) ~ 1,
-        !is.na(startDate.glad) & is.na(startDate.coping.glad) ~ 0
-      )
-  )
-
-dat.glad <- dat.glad %>%
-  mutate(
-    data_group_full = 
-      recode_factor(
-        data_group_full_numeric,
-        "0" = "Only prepandemic data",
-        "1" = "Prepandemic and baseline data",
-        "2" = "Prepandemic, baseline and retrospective PHQ data",
-        "3" = "Prepandemic, baseline and retrospective GAD data",
-        "4" = "Prepandemic, baseline and retrospective PCL data",
-        "5" = "All prepandemic, baseline and retrospective data"
-      )
-  )
-
-table(dat.glad$data_group_full)
-```
-
-#READ IN RESPIRATORY DATA 
-```{r read in respiratory data}
-
+dim(coping.glad.respiratory.raw)[1]-dim(coping.glad.respiratory.raw.id)[1]
+
+```
+
+```{r create respiratory numeric variables}
+exclude_cols <- c("ID",
+                  "Sample")
+
+coping.glad.respiratory.raw.numeric <- add_numeric(coping.glad.respiratory.raw.id, exclude = exclude_cols)
+
+colnames(coping.glad.respiratory.raw.numeric)
+dim(coping.glad.respiratory.raw.numeric)
+dim(coping.glad.respiratory.raw.id)
+```
+
+```{r distribution of COVID symptoms}
+#persistent cough
+coping.glad.respiratory.raw.numeric %>%
+  ggplot(
+    mapping = aes(
+      y = respiratory.persistent_cough_numeric 
+    )
+  ) +
+  geom_bar() +
+  labs(
+    title = "Persistant cough"
+  )
+
+#severe fatigue
+coping.glad.respiratory.raw.numeric %>%
+  ggplot(
+    mapping = aes(
+        y = respiratory.feeling_tiredfatigued_numeric 
+    )
+  ) +
+  geom_bar() +
+  labs(
+    title = "Severe fatigue"
+  )
+
+#skipped meals
+coping.glad.respiratory.raw.numeric %>%
+  ggplot(
+    mapping = aes(
+        y = respiratory.skipping_meals_because_you_felt_unwell_numeric
+    )
+  ) +
+  geom_bar() +
+  labs(
+    title = "Skipped meals"
+  )
+
+```
+
+Choosing cut-offs for the likert scale symptoms of "no symptoms", "mild symptoms", "moderate symptoms" and "severe symptoms" for the fatigue, persistent cough and skipped meals variables. 
+Fatigue: "Severe symptoms" as cut off
+Persistent cought: "Mild symptoms" as cut off
+Skipped meals: "Moderate symptoms" as cut off
+```{r proportion of people who report COVID symptoms in Menni et al}
+#fatigue
+percentage_fatigue <- ((0.298*6452) + (0.1556*9186) + (0.0871*2434931))/(6452+9186+2434931) 
+percentage_fatigue   # 0.08791204% of Menni et al(2020) have fatigue
+quantile(x = coping.glad.respiratory.raw.numeric$respiratory.feeling_tiredfatigued_numeric, 
+         na.rm = TRUE, 
+         probs = 1-percentage_fatigue) #this gives 8% of the sample reporting fatigue when using the "severe symptoms" fatigue response
+
+#persistent cough
+percentage_pcough <- ((0.5673*6452) + (0.4556*9186) + (0.3017*2434931))/(6452+9186+2434931)
+percentage_pcough    # 0.3029762% of Menni et al(2020) have fatigue
+quantile(x = coping.glad.respiratory.raw.numeric$respiratory.persistent_cough_numeric, 
+         na.rm = TRUE, 
+         probs = 1-percentage_pcough) # this gives 0.3029762% of the sample reporting fatigue when using the "mild symptoms" persistent cough response
+
+#skipped meals 
+percentage_skipped_meals <- ((0.4203*6452) + (0.2493*9186) + (0.1912*2434931))/(6452+9186+2434931) 
+percentage_skipped_meals    # 0.192021% of Menni et al(2020) have fatigue
+quantile(x = coping.glad.respiratory.raw.numeric$respiratory.skipping_meals_because_you_felt_unwell_numeric, 
+         na.rm = TRUE, 
+         probs = 1-percentage_skipped_meals) # this gives 0.192021% of the sample reporting fatigue when using the "moderate symptoms" persistent cough response
 ```
@@
 - "smeals": Skipped meals
-
 The below chunk needs to be re-thought - not as simple as categorising gender. 

### 2020-08-04 PANCHANGE_data_preprocessing2020-07-15.Rmd
edits to cut-off algorithm symptom chunks

@@
 Fatigue: "Severe symptoms" as cut off
-Persistent cought: "Mild symptoms" as cut off
+Persistent cough: "Mild symptoms" as cut off
 Skipped meals: "Moderate symptoms" as cut off

### 2020-08-05 PANCHANGE_data_preprocessing2020-07-15.Rmd
creating COVID respiratory symptom binary categories

@@
 
+#Distribution of likert scale COVID-19 symptoms in COPING
 ```{r distribution of COVID symptoms}
@@
 
-Choosing cut-offs for the likert scale symptoms of "no symptoms", "mild symptoms", "moderate symptoms" and "severe symptoms" for the fatigue, persistent cough and skipped meals variables. 
+#Choosing cut-offs for the likert scale symptoms of "no symptoms", "mild symptoms", "moderate symptoms" and "severe symptoms" for the fatigue, persistent cough and skipped meals variables. 
+Coding:
+0 = No symptoms
+1 = Mild symptoms
+2 = Moderate symptoms
+3 = Severe symptoms
+
+Results:
+Persistent cough: "Mild symptoms" as cut off
 Fatigue: "Severe symptoms" as cut off
-Persistent cough: "Mild symptoms" as cut off
 Skipped meals: "Moderate symptoms" as cut off
 ```{r proportion of people who report COVID symptoms in Menni et al}
+#persistent cough
+percentage_pcough <- ((0.5673*6452) + (0.4556*9186) + (0.3017*2434931))/(6452+9186+2434931)
+percentage_pcough    # 0.3029762% of Menni et al(2020) have fatigue
+quantile(x = coping.glad.respiratory.raw.numeric$respiratory.persistent_cough_numeric, 
+         na.rm = TRUE, 
+         probs = 1-percentage_pcough) # this gives 0.3029762% of the sample reporting fatigue when using the "mild symptoms" persistent cough response
+
 #fatigue
@@
 
-#persistent cough
-percentage_pcough <- ((0.5673*6452) + (0.4556*9186) + (0.3017*2434931))/(6452+9186+2434931)
-percentage_pcough    # 0.3029762% of Menni et al(2020) have fatigue
-quantile(x = coping.glad.respiratory.raw.numeric$respiratory.persistent_cough_numeric, 
-         na.rm = TRUE, 
-         probs = 1-percentage_pcough) # this gives 0.3029762% of the sample reporting fatigue when using the "mild symptoms" persistent cough response
-
 #skipped meals 
@@
          probs = 1-percentage_skipped_meals) # this gives 0.192021% of the sample reporting fatigue when using the "moderate symptoms" persistent cough response
+```
+
+Creating binary groups for COVID symptoms
+```{r creating binary groups for COVID symptoms}
+#loss or smell or taste
+coping.glad.respiratory.raw.numeric <- coping.glad.respiratory.raw.numeric %>%
+  mutate(
+    respiratory.anosmia_binary =
+      if_else(
+        respiratory.was_your_sense_of_smell_impaired_numeric == 1 | respiratory.was_your_sense_of_taste_impaired_numeric == 1, 
+        1,
+        0
+      )
+  )
+
+freq(coping.glad.respiratory.raw.numeric$respiratory.anosmia.binary)
+
+#persistent cough
+coping.glad.respiratory.raw.numeric <- coping.glad.respiratory.raw.numeric %>%
+  mutate(
+    respiratory.pcough_binary =
+      if_else(
+        respiratory.persistent_cough_numeric >= 1, #those who score 1 or above (mild or above)
+        1,
+        0
+      )
+  )
+
+#fatigue
+coping.glad.respiratory.raw.numeric <- coping.glad.respiratory.raw.numeric %>%
+  mutate(
+    respiratory.fatigue_binary =
+      if_else(
+        respiratory.feeling_tiredfatigued_numeric >= 3, #those who score 3 (severe symptoms)
+        1,
+        0
+      )
+  )
+
+#skipped meals
+coping.glad.respiratory.raw.numeric <- coping.glad.respiratory.raw.numeric %>%
+  mutate(
+    respiratory.skipped_meals_binary =
+      if_else(
+        respiratory.skipping_meals_because_you_felt_unwell_numeric >= 2,
+        1,
+        0
+      )
+  )
 ```

### 2020-08-05 PANCHANGE_data_preprocessing2020-07-15.Rmd
minor edits and joining respiratory to GLAD data

@@
 
-freq(coping.glad.respiratory.raw.numeric$respiratory.anosmia.binary)
-
 #persistent cough
@@
 
+Frequencies of binary COVID symptoms
+```{r frequencies of COVID binary symptoms}
+freq(coping.glad.respiratory.raw.numeric$respiratory.anosmia_binary)
+freq(coping.glad.respiratory.raw.numeric$respiratory.pcough_binary)
+freq(coping.glad.respiratory.raw.numeric$respiratory.fatigue_binary)
+freq(coping.glad.respiratory.raw.numeric$respiratory.skipped_meals_binary)
+```
+
+Rename respiratory dataset joined to main dataset
+```{r clean respiratory dataset}
+coping.glad.respiratory <- coping.glad.respiratory.raw.numeric
+
+dat.glad.coping <- left_join(
+  x = dat.glad,
+  y = coping.glad.respiratory,
+  by = "ID"
+)
+```
+
 # Probable COVID-19 case identification
@@
 - Sex: 	0 Female, 1 Male
-- Other binary variables: 0 No, 1 Yes       #THESE NAMES WILL CHANGE WHEN IMPORTING DATA - FIND AND REPLACE
-- "anosmia": loss of smell or taste  
-- "pcough":	Persistent cough
-- "sfatigue": Severe fatigue
-- "smeals": Skipped meals
-The below chunk needs to be re-thought - not as simple as categorising gender. 
+- Other binary variables: 0 No, 1 Yes       
+- "respiratory.anosmia_binary": loss of smell or taste  
+- "respiratory.pcough_binary":	Persistent cough
+- "respiratory.fatigue_binary": Severe fatigue
+- "respiratory.skipped_meals_binary": Skipped meals
+
+++KT: Needs to be developed further for RAMP dataset
+COVID prediction model for COPING
 ```{r eval=FALSE, include=FALSE}
-# Recode Gender to be binary for the model in RAMP
-dat.respiratory.ramp <- dat.respiratory.ramp %>%
-		  mutate(
-		    gender_binary_ramp =
-		      case_when(
-		        Gender == "Male" ~ "Male",
-		        Gender == "Female" ~ "Female",
-		        Gender == !("Male" | "Female") ~ NA_real_
-		      )
-		  )
-```
-
-++KT: Needs to be developed further for RAMP dataset
-```{r eval=FALSE, include=FALSE}
-## COVID prediction model for COPING
-
-## Formula to calculate probability 
-dat.respiratory.coping <- dat.respiratory.coping %>%
+# Formula to calculate probability 
+dat.glad.coping <- dat.glad.coping %>%
 		  mutate(
@@
 		      (0.01*Age) + 
-		      (0.44*Sex) + #we have sex here in COPING - use binary Gender variable in RAMP
-		      (1.75*anosmia) + #will be renamed
-		      (0.31*pcough) +  #will be renamed
-		      (0.49*sfatigue) +  #will be renamed
-		      (0.39*smeals) #will be renamed
-		         )
-
-## Calcualte the odds ratios 
-dat.respiratory.coping <- dat.respiratory.coping %>%
+		      (0.44*Sex) + 
+		      (1.75*respiratory.anosmia_binary) + 
+		      (0.31*respiratory.pcough_binary) +  
+		      (0.49*respiratory.fatigue_binary) +  
+		      (0.39*respiratory.skipped_meals_binary) 
+		         )
+
+# Calcualte the odds ratios 
+dat.glad.coping <- dat.glad.coping %>%
 		  mutate(
 		    covid_odds_ratio = 
-		      exp(covid_probability) / (1 + exp(covid_probability)
-		                              )
-
-## generate variable covid_odds_ratio_50 -> 0, 0,5 and 1 = 0, 1, 2 (that's a column). Previous code: egen covid_odds_ratio_50 = cut(covid_odds_ratio), at(0,0.5,1) icode
-dat.respiratory.coping <- dat.respiratory.coping %>%
+		      exp(covid_probability) / (1 + exp(covid_probability))
+
+# generate variable covid_odds_ratio_50 -> 0, 0,5 and 1 = 0, 1, 2 (that's a column)
+dat.glad.coping <- dat.glad.coping %>%
 		  mutate(
@@
 #create factor with labels
-dat.respiratory.coping <- dat.respiratory.coping %>%
+dat.glad.coping <- dat.glad.coping %>%
   mutate(
@@
 
-descr(x = dat.respiratory.coping[,covid_variables],
+descr(x = dat.glad.coping[,covid_variables],
       round.digits = 2,
@@
 ## looking at cases over 0.5
-table(dat.respiratory.coping$covid_odds_ratio_50) 
-```
+table(dat.glad.coping$covid_odds_ratio_50) 
+```

### 2020-08-05 PANCHANGE_data_preprocessing2020-07-15.Rmd
edited and finalised COVID algorithm

@@
 COVID prediction model for COPING
-```{r eval=FALSE, include=FALSE}
-# Formula to calculate probability 
+
+```{r create numeric sex variable with male=1}
+dat.glad.coping <- dat.glad.coping %>%
+  mutate(
+    Sex_respiratory =
+      if_else(
+        Sex == "Male",
+        1,
+        0
+      )
+  )
+```
+
+```{r how many people expereinced all symptoms}
+dat.glad.coping <- dat.glad.coping %>%
+  mutate(
+    people_with_symptoms =
+      if_else(
+          !is.na(respiratory.anosmia_binary) &
+          !is.na(respiratory.pcough_binary) &
+          !is.na(respiratory.fatigue_binary) &
+          !is.na(respiratory.skipped_meals_binary),
+        1,
+        0
+       )
+  )
+
+table(dat.glad.coping$people_with_symptoms)
+```
+
+```{r COVID prediction model}
+# linear model of covid symptoms
 dat.glad.coping <- dat.glad.coping %>%
@@
 		      (0.01*Age) + 
-		      (0.44*Sex) + 
+		      (0.44*Sex_respiratory) + 
 		      (1.75*respiratory.anosmia_binary) + 
@@
     covid_odds_ratio = 
-		      exp(covid_probability) / (1 + exp(covid_probability))
-
-# generate variable covid_odds_ratio_50 -> 0, 0,5 and 1 = 0, 1, 2 (that's a column)
+      (exp(covid_probability) / (1 + exp(covid_probability)))
+  )
+
+# generate binary cutt off variable for risk of COVID 
 dat.glad.coping <- dat.glad.coping %>%
@@
 		        covid_odds_ratio >= 0.5 & covid_odds_ratio <= 1 ~ "1"
+		      )
 		  )
@@
 
-## creating a frequency table. Previous code: table covid_odds_ratio_50, c(min covid_odds_ratio max covid_odds_ratio)
-covid_variables <- c(
-                      "covid_odds_ratio_50",
-                      "covid_odds_ratio",
+#frequency table for covid variables 
+covid_variables <- c("covid_odds_ratio",
                       "covid_probability"

### 2020-08-06 PANCHANGE_data_preprocessing2020-07-15.Rmd

@@
 Max should be 21.
+
+*Note that scores with missingness will be changed to NA later in the script
 ```{r gad sum score prepan}
@@
 Calculate sum score for PHQ-9
+
+*Note that scores with missingness will be changed to NA later in the script
 ```{r phq sum score prepan}
@@
 
-## COPING GLAD: GAD-7
+# glad ocir
+
+```{r glad ocir cols}
+glad.ocir.raw <- readRDS(file = paste0(data.raw_path, "/2020-08-03/glad/ocir_glad.rds"))
+dim(glad.ocir.raw)
+colnames(glad.ocir.raw)
+```
+
+```{r glad ocir cleaning}
+glad.ocir.raw.id <- glad.ocir.raw %>%
+  drop_na(externalDataReference) %>% # Drop NAs
+  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
+  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
+  mutate(ID = as.numeric(ID),
+         startDate.glad = startDate) %>% # Rename startDate
+  select(
+    Sample, # Sample
+    ID, # ID
+    ocir.i_repeatedly_check_doors_windows_drawers_etc_prepan = ocir.i_repeatedly_check_doors_windows_drawers_etc.,
+    ocir.arranged_things_change_upset_prepan = ocir.arranged_things_change_upset,
+    ocir.repeat_feel_numbers_prepan = ocir.repeat_feel_numbers,
+    ocir.clean_simply_wash_feel_prepan = ocir.clean_simply_wash_feel,
+    ocir.mind_upset_unpleasant_thoughts_prepan = ocir.mind_upset_unpleasant_thoughts,
+    ocir.afraid_avoid_throwing_things_prepan = ocir.afraid_avoid_throwing_things,
+    ocir.light_switches_water_taps_prepan = ocir.light_switches_water_taps,
+    ocir.arranged_things_prepan = ocir.arranged_things,
+    ocir.good_feel_bad_numbers_prepan = ocir.good_feel_bad_numbers,
+    ocir.hands_longer_wash_prepan = ocir.hands_longer_wash,
+    ocir.saved_things_prepan = ocir.saved_things,
+    ocir.frequently_difficulty_rid_nasty_prepan = ocir.frequently_difficulty_rid_nasty,
+    ocir.i_check_things_more_often_than_necessary_prepan = ocir.i_check_things_more_often_than_necessary.,
+    ocir.arranged_properly_objects_upset_prepan = ocir.arranged_properly_objects_upset,
+    ocir.feel_compelled_count_things_prepan = ocir.feel_compelled_count_things,
+    ocir.strangers_touch_touched_difficult_prepan = ocir.strangers_touch_touched_difficult,
+    ocir.control_difficult_find_thoughts_prepan = ocir.control_difficult_find_thoughts,
+    ocir.i_collect_things_i_dont_need_prepan = ocir.i_collect_things_i_dont_need
+  ) %>%
+  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
+  mutate_if(is.numeric, ~na_if(., -99)) %>%
+  mutate_if(is.numeric, ~na_if(., -77)) %>%
+  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
+  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
+
+# Inspect dimensions
+dim(glad.ocir.raw.id)
+# Inspect colnames
+colnames(glad.ocir.raw.id)
+#Differences
+dim(glad.ocir.raw)[1]-dim(glad.ocir.raw.id)[1]
+```
+
+Calculate sum score for OCI-R
+
+*Note that scores with missingness will be changed to NA later in the script
+```{r ocir sum score prepan}
+# Create vector with scoring key: If the item is reversed coded use -1. 
+# There needs to be the correct number of values for each item in the questionnaire. 
+ocir.items_key_prepan <- c(1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1)
+
+# Create vector with items that are included in sum score
+ocir.items_prepan = c(
+  "ocir.i_repeatedly_check_doors_windows_drawers_etc_prepan",
+  "ocir.arranged_things_change_upset_prepan",
+  "ocir.repeat_feel_numbers_prepan",
+  "ocir.clean_simply_wash_feel_prepan",
+  "ocir.mind_upset_unpleasant_thoughts_prepan",
+  "ocir.afraid_avoid_throwing_things_prepan",
+  "ocir.light_switches_water_taps_prepan",
+  "ocir.arranged_things_prepan",
+  "ocir.good_feel_bad_numbers_prepan",
+  "ocir.hands_longer_wash_prepan",
+  "ocir.saved_things_prepan",
+  "ocir.frequently_difficulty_rid_nasty_prepan",
+  "ocir.i_check_things_more_often_than_necessary_prepan",
+  "ocir.arranged_properly_objects_upset_prepan",
+  "ocir.feel_compelled_count_things_prepan",
+  "ocir.strangers_touch_touched_difficult_prepan",
+  "ocir.control_difficult_find_thoughts_prepan",
+  "ocir.i_collect_things_i_dont_need_prepan"
+  )
+
+# Calulate sum score
+ocir.scored_items_prepan <- scoreItems(keys = ocir.items_key_prepan,
+                                        items = glad.ocir.raw.id[ocir.items_prepan],
+                                        totals = TRUE, 
+                                        missing = TRUE, 
+                                        impute = 'none', 
+                                        min = 0, 
+                                        max = 4)
+# Add in column to tibble
+glad.ocir.raw.id$ocir.sum_score_prepan <- ocir.scored_items_prepan$scores
+
+# Look at values
+glad.ocir.raw.id %>%
+  descr(ocir.sum_score_prepan,
+        stats = "common"
+        )
+```
+
+```{r glad ocir head}
+head(glad.ocir.raw.id)
+```
+
+```{r glad ocir summary}
+summarytools::dfSummary(
+  glad.ocir.raw.id,
+  graph.col = F,
+  valid.col = F
+  )
+```
+
+# COPING GLAD: GAD-7
 
@@
 
+# glad COPING ocir
+
+```{r coping glad ocir cols}
+coping.glad.ocir.raw <- readRDS(file = paste0(data.raw_path, "/2020-08-04/glad/ocir_coping_glad.rds"))
+dim(coping.glad.ocir.raw)
+colnames(coping.glad.ocir.raw)
+```
+
+```{r coping glad ocir summary labels}
+summarytools::dfSummary(
+  coping.glad.ocir.raw,
+  graph.col = F,
+  valid.col = F
+  #labels.col = F
+)
+```
+
+*Note that the COPING GLAD OCI-R ID numbers are stored under recipientFirstName (rather than ExternalDataReference)
+```{r coping glad ocir cleaning}
+coping.glad.ocir.raw.id <- coping.glad.ocir.raw %>%
+  drop_na(recipientFirstName) %>% # Drop NAs
+  distinct(recipientFirstName, .keep_all = TRUE) %>% # Remove duplicates based on ID
+  separate(recipientFirstName, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
+  mutate(ID = as.numeric(ID),
+         startDate.glad = startDate) %>% # Rename startDate
+  select(
+    Sample, # Sample
+    ID, # ID
+    ocir.i_repeatedly_check_doors_windows_drawers_etc_retro = ocir.i_repeatedly_check_doors_windows_drawers_etc.,
+    ocir.arranged_things_change_upset_retro = ocir.arranged_things_change_upset,
+    ocir.repeat_feel_numbers_retro = ocir.numbers_repeat_feel, ## Different from GLAD prepandemic
+    ocir.clean_simply_wash_feel_retro = ocir.feel_contaminated_clean_simply, ## Different from GLAD prepandemic
+    ocir.mind_upset_unpleasant_thoughts_retro = ocir.mind_upset_unpleasant_thoughts,
+    ocir.afraid_avoid_throwing_things_retro = ocir.afraid_avoid_throwing_things,
+    ocir.light_switches_water_taps_retro = ocir.light_switches_water_taps,
+    ocir.arranged_things_retro = ocir.arranged_things,
+    ocir.good_feel_bad_numbers_retro = ocir.bad_numbers_good_feel, ## Different from GLAD prepandemic
+    ocir.hands_longer_wash_retro = ocir.longer_hands_wash, ## Different from GLAD prepandemic
+    ocir.saved_things_retro = ocir.saved_things,
+    ocir.frequently_difficulty_rid_nasty_retro = ocir.frequently_rid_difficulty_nasty, ## Different from GLAD prepandemic
+    ocir.i_check_things_more_often_than_necessary_retro = ocir.i_check_things_more_often_than_necessary.,
+    ocir.arranged_properly_objects_upset_retro = ocir.arranged_properly_objects_upset,
+    ocir.feel_compelled_count_things_retro = ocir.feel_compelled_count_things,
+    ocir.strangers_touch_touched_difficult_retro = ocir.strangers_touch_touched_object, ## Different from GLAD prepandemic
+    ocir.control_difficult_find_thoughts_retro = ocir.control_find_difficult_thoughts, ## Different from GLAD prepandemic
+    ocir.i_collect_things_i_dont_need_retro = ocir.i_collect_things_i_dont_need., ## Different from GLAD prepandemic
+    ocir.i_repeatedly_check_doors_windows_drawers_etc_base = ocir.i_repeatedly_check_doors_windows_drawers_etc..1,
+    ocir.arranged_things_change_upset_base = ocir.arranged_things_change_upset.1,
+    ocir.repeat_feel_numbers_base = ocir.numbers_repeat_feel.1, ## Different from GLAD prepandemic
+    ocir.clean_simply_wash_feel_base = ocir.feel_contaminated_clean_simply.1, ## Different from GLAD prepandemic
+    ocir.mind_upset_unpleasant_thoughts_base = ocir.mind_upset_unpleasant_thoughts.1,
+    ocir.afraid_avoid_throwing_things_base = ocir.afraid_avoid_throwing_things.1,
+    ocir.light_switches_water_taps_base = ocir.light_switches_water_taps.1,
+    ocir.arranged_things_base = ocir.arranged_things.1,
+    ocir.good_feel_bad_numbers_base = ocir.bad_numbers_good_feel.1, ## Different from GLAD prepandemic
+    ocir.hands_longer_wash_base = ocir.longer_hands_wash.1, ## Different from GLAD prepandemic
+    ocir.saved_things_base = ocir.saved_things.1,
+    ocir.frequently_difficulty_rid_nasty_base = ocir.frequently_rid_difficulty_nasty.1, ## Different from GLAD prepandemic
+    ocir.i_check_things_more_often_than_necessary_base = ocir.i_check_things_more_often_than_necessary..1,
+    ocir.arranged_properly_objects_upset_base = ocir.arranged_properly_objects_upset.1,
+    ocir.feel_compelled_count_things_base = ocir.feel_compelled_count_things.1,
+    ocir.strangers_touch_touched_difficult_base = ocir.strangers_touch_touched_object.1, ## Different from GLAD prepandemic
+    ocir.control_difficult_find_thoughts_base = ocir.control_find_difficult_thoughts.1, ## Different from GLAD prepandemic
+    ocir.i_collect_things_i_dont_need_base = ocir.i_collect_things_i_dont_need..1
+  ) %>%
+  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
+  mutate_if(is.numeric, ~na_if(., -99)) %>%
+  mutate_if(is.numeric, ~na_if(., -77)) %>%
+  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
+  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
+
+# Inspect dimensions
+dim(coping.glad.ocir.raw.id)
+# Inspect colnames
+colnames(coping.glad.ocir.raw.id)
+#Differences
+dim(coping.glad.ocir.raw)[1]-dim(coping.glad.ocir.raw.id)[1]
+```
+
+Calculate sum score for OCI-R retro
+```{r coping ocir sum score retro}
+# Create vector with scoring key: If the item is reversed coded use -1. 
+# There needs to be the correct number of values for each item in the questionnaire. 
+ocir.items_key_retro <- c(1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1)
+
+# Create vector with items that are included in total score
+ocir.items_retro = c(
+  "ocir.i_repeatedly_check_doors_windows_drawers_etc_retro",
+  "ocir.arranged_things_change_upset_retro",
+  "ocir.repeat_feel_numbers_retro",
+  "ocir.clean_simply_wash_feel_retro",
+  "ocir.mind_upset_unpleasant_thoughts_retro",
+  "ocir.afraid_avoid_throwing_things_retro",
+  "ocir.light_switches_water_taps_retro",
+  "ocir.arranged_things_retro",
+  "ocir.good_feel_bad_numbers_retro",
+  "ocir.hands_longer_wash_retro",
+  "ocir.saved_things_retro",
+  "ocir.frequently_difficulty_rid_nasty_retro",
+  "ocir.i_check_things_more_often_than_necessary_retro",
+  "ocir.arranged_properly_objects_upset_retro",
+  "ocir.feel_compelled_count_things_retro",
+  "ocir.strangers_touch_touched_difficult_retro",
+  "ocir.control_difficult_find_thoughts_retro",
+  "ocir.i_collect_things_i_dont_need_retro"
+)
+
+# Calulate total score
+ocir.scored_items_retro <- scoreItems(keys = ocir.items_key_retro,
+                                     items = coping.glad.ocir.raw.id[ocir.items_retro],
+                                     totals = TRUE, 
+                                     missing = TRUE, 
+                                     impute = 'none', 
+                                     min = 0, 
+                                     max = 4)
+# Add in column to tibble
+coping.glad.ocir.raw.id$ocir.sum_score_retro <- ocir.scored_items_retro$scores
+
+# Look at values
+coping.glad.ocir.raw.id %>%
+  descr(ocir.sum_score_retro,
+        stats = "common"
+  )
+```
+
+Calculate sum score for OCI-R base
+```{r coping ocir sum score base}
+# Create vector with scoring key: If the item is reversed coded use -1. 
+# There needs to be the correct number of values for each item in the questionnaire. 
+ocir.items_key_base <- c(1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1)
+
+# Create vector with items that are included in total score
+ocir.items_base = c(
+  "ocir.i_repeatedly_check_doors_windows_drawers_etc_base",
+  "ocir.arranged_things_change_upset_base",
+  "ocir.repeat_feel_numbers_base",
+  "ocir.clean_simply_wash_feel_base",
+  "ocir.mind_upset_unpleasant_thoughts_base",
+  "ocir.afraid_avoid_throwing_things_base",
+  "ocir.light_switches_water_taps_base",
+  "ocir.arranged_things_base",
+  "ocir.good_feel_bad_numbers_base",
+  "ocir.hands_longer_wash_base",
+  "ocir.saved_things_base",
+  "ocir.frequently_difficulty_rid_nasty_base",
+  "ocir.i_check_things_more_often_than_necessary_base",
+  "ocir.arranged_properly_objects_upset_base",
+  "ocir.feel_compelled_count_things_base",
+  "ocir.strangers_touch_touched_difficult_base",
+  "ocir.control_difficult_find_thoughts_base",
+  "ocir.i_collect_things_i_dont_need_base"
+)
+
+# Calulate total score
+ocir.scored_items_base <- scoreItems(keys = ocir.items_key_base,
+                                    items = coping.glad.ocir.raw.id[ocir.items_base],
+                                    totals = TRUE, 
+                                    missing = TRUE, 
+                                    impute = 'none', 
+                                    min = 0, 
+                                    max = 4)
+# Add in column to tibble
+coping.glad.ocir.raw.id$ocir.sum_score_base <- ocir.scored_items_base$scores
+
+# Look at values
+coping.glad.ocir.raw.id %>%
+  descr(ocir.sum_score_base,
+        stats = "common"
+  )
+```
+
+```{r coping glad ocir head}
+head(coping.glad.ocir.raw.id)
+```
+
+```{r coping glad ocir summary}
+summarytools::dfSummary(
+  coping.glad.ocir.raw.id,
+  graph.col = F,
+  valid.col = F,
+  labels.col = F)
+```
+
 # Join tibbles together
@@
 
-##Missigness of questionnaire items
+##Missingness of questionnaire items
 #PHQ - baseline
 PHQ Missingness NAs per person - count and percentages
-```{r PHQ basline missingness}
+```{r PHQ baseline missingness}
 dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
@@
 
+#OCI-R - baseline
+OCI-R Missingness NAs per person - count and percentages
+```{r OCI-R baseline missingness}
+dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
+  mutate(
+    na_per_person_ocir_base =         # variable for NA per person
+      rowSums(                       
+        is.na(dat.no.sex.no.gender.no.age.no.ibd # sum the rows that are NA
+          [,colnames(dat.no.sex.no.gender.no.age.no.ibd) #for all the rows and columns that are in the OCI-R items at baseline
+           %in%
+             ocir.items_base]
+        )
+    )
+  )
+
+freq(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_ocir_base) #have a look at the frequency
+
+dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>% #NA per person as a percentage
+  mutate(
+    miss_pc_total_ocir_base = 
+      na_per_person_ocir_base/18 # NA per person divided by the amount of items
+  )
+
+freq(dat.no.sex.no.gender.no.age.no.ibd$miss_pc_total_ocir_base)
+```
+
+#OCI-R - retrospective
+OCI-R Missingness NAs per person - count and percentages
+```{r OCI-R retrospective missingness}
+dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
+  mutate(
+    na_per_person_ocir_retro =         # variable for NA per person
+      rowSums(                       
+        is.na(dat.no.sex.no.gender.no.age.no.ibd # sum the rows that are NA
+          [,colnames(dat.no.sex.no.gender.no.age.no.ibd) #for all the rows and columns that are in the OCI-R items at retroline
+           %in%
+             ocir.items_retro]
+        )
+    )
+  )
+
+freq(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_ocir_retro) #have a look at the frequency
+
+dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>% #NA per person as a percentage
+  mutate(
+    miss_pc_total_ocir_retro = 
+      na_per_person_ocir_retro/18 # NA per person divided by the amount of items
+  )
+
+freq(dat.no.sex.no.gender.no.age.no.ibd$miss_pc_total_ocir_retro)
+```
+
+#OCI-R - prepandemic
+OCI-R Missingness NAs per person - count and percentages
+```{r OCI-R prepan missingness}
+dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
+  mutate(
+    na_per_person_ocir_prepan =         # variable for NA per person
+      rowSums(                       
+        is.na(dat.no.sex.no.gender.no.age.no.ibd # sum the rows that are NA
+          [,colnames(dat.no.sex.no.gender.no.age.no.ibd) #for all the rows and columns that are in the OCI-R items at prepanline
+           %in%
+             ocir.items_prepan]
+        )
+    )
+  )
+
+freq(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_ocir_prepan) #have a look at the frequency
+
+dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>% #NA per person as a percentage
+  mutate(
+    miss_pc_total_ocir_prepan = 
+      na_per_person_ocir_prepan/18 # NA per person divided by the amount of items
+  )
+
+freq(dat.no.sex.no.gender.no.age.no.ibd$miss_pc_total_ocir_prepan)
+```
+
+Count for OCI-R baseline, retrospective, and prepandemic missingness per person
+```{r count of people missing a number of items for OCI-R}
+#baseline
+table(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_ocir_base)
+#retrospective
+table(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_ocir_retro)
+#pre-pandemic
+table(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_ocir_prepan)
+```
+
 #Sum scores missingness cut offs
@@
 freq(dat.glad$pcl.difficulty_concentrating_retro)
+```
+
+OCI-R difference scores
+```{r ocir difference scores}
+# Difference score for prepandemic and retrospective oci-r sum scores
+dat.glad <- dat.glad %>%
+  mutate(
+    ocir.diff_score_prepan_retro =
+      as.numeric(
+        ocir.sum_score_prepan - ocir.sum_score_retro  # retrospective sum score MINUS prepandemic sum score 
+      )
+  )
+
+summary(dat.glad$ocir.diff_score_prepan_retro)
+
+# Difference score for prepandemic and baseline ocir sum scores
+dat.glad <- dat.glad %>%
+  mutate(
+    ocir.diff_score_prepan_base =
+      as.numeric(
+        ocir.sum_score_prepan - ocir.sum_score_base  # prepandemic sum score MINUS baseline sum score 
+      )
+  )
+
+summary(dat.glad$ocir.diff_score_prepan_base)
+
+# Difference score for retrospective and baseline ocir sum scores
+dat.glad <- dat.glad %>%
+  mutate(
+    ocir.diff_score_base_retro =
+      as.numeric(
+        ocir.sum_score_base - ocir.sum_score_retro  # baseline sum score MINUS retrospective sum score 
+      )
+  )
+
+summary(dat.glad$ocir.diff_score_base_retro)
+
 ```

### 2020-08-07 PANCHANGE_data_preprocessing2020-07-15.Rmd
admin changes
updated the demographics read in and changed Age_raw to Age_uncleaned

@@
          startDate.glad, #Date when participant signed up to glad
-         Age_raw = dem.how_old_are_you_now, # Age
-         Gender = dem.which_gender_do_you_identify_with, # Gender
-         Sex = dem.select_questionnaire_items_medical, #Sex
-         EduYrs = dem.school_education_school_years, # Years in education
-         dem.college_or_university_degree_numeric, # level of education - univeristy
-         dem.a_levelsas_levels_or_equivalent_numeric, # level of education - alevel
-         dem.o_levelsgcses_or_equivalent_numeric, # level of education - gcse
-         dem.cses_or_equivalent_numeric, # level of education - cse
-         dem.nvq_or_hnd_or_hnc_or_equivalent_numeric, # level of education - nvq
-         Ethnicity = dem.questions_based_ethnic_origin # Ethnicity
+         Age_uncleaned = demographics.how_old_are_you_now.txt, # Age
+         Gender = demographics.which_gender_do_you_identify_with, # Gender
+         Sex = demographics.select_questionnaire_items_medical, #Sex
+         EduYrs = demographics.school_education_school_years.txt, # Years in education
+         demographics.college_or_university_degree, # level of education - univeristy
+         demographics.a_levelsas_levels_or_equivalent, # level of education - alevel
+         demographics.o_levelsgcses_or_equivalent, # level of education - gcse
+         demographics.cses_or_equivalent, # level of education - cse
+         demographics.nvq_or_hnd_or_hnc_or_equivalent, # level of education - nvq
+         Ethnicity = demographics.questions_based_ethnic_origin # Ethnicity
          ) %>%
@@
 
+Create dem numeric variables
+```{r create dem numeric variables}
+exclude_cols <- c("ID",
+                  "Sample",
+                  "startDate.glad",
+                  "Age_uncleaned",
+                  "EduYrs")
+
+glad.dem.raw.id.unclean.numeric <- add_numeric(glad.dem.raw.id.unclean, exclude = exclude_cols)
+
+# Check if factor columns have been added
+colnames(glad.dem.raw.id.unclean.numeric)
+
+# Dimensions before adding factor columns
+dim(glad.dem.raw.id.unclean)
+# Dimensions after adding factor columns
+dim(glad.dem.raw.id.unclean.numeric)
+```
+
 #Clean Age variable
@@
   which(
-  glad.dem.raw.id.unclean$Age_raw > age_upper_limit |
-    glad.dem.raw.id.unclean$Age_raw < age_lower_limit
+  glad.dem.raw.id.unclean$Age_uncleaned > age_upper_limit |
+    glad.dem.raw.id.unclean$Age_uncleaned < age_lower_limit
      )
@@
       if_else(
-        Age_raw > age_upper_limit | 
-        Age_raw < age_lower_limit, 
+        Age_uncleaned > age_upper_limit | 
+        Age_uncleaned < age_lower_limit, 
         true = NA_real_,
-        false = Age_raw,
+        false = Age_uncleaned,
         missing = NA_real_
@@
       case_when(
-        dem.college_or_university_degree_numeric == "1" ~ 4,
-        dem.a_levelsas_levels_or_equivalent_numeric == "1" ~ 3,
-        dem.nvq_or_hnd_or_hnc_or_equivalent_numeric == "1" ~ 2,
-        dem.o_levelsgcses_or_equivalent_numeric == "1" ~ 1,
-        dem.cses_or_equivalent_numeric == "1" ~ 1)
+        demographics.college_or_university_degree_numeric == "1" ~ 4,
+        demographics.a_levelsas_levels_or_equivalent_numeric == "1" ~ 3,
+        demographics.nvq_or_hnd_or_hnc_or_equivalent_numeric == "1" ~ 2,
+        demographics.o_levelsgcses_or_equivalent_numeric == "1" ~ 1,
+        demographics.cses_or_equivalent_numeric == "1" ~ 1)
     )
@@
   select(highest_education,
-        dem.college_or_university_degree_numeric,
-        dem.a_levelsas_levels_or_equivalent_numeric,
-        dem.nvq_or_hnd_or_hnc_or_equivalent_numeric,
-        dem.o_levelsgcses_or_equivalent_numeric,
-        dem.cses_or_equivalent_numeric
+        demographics.college_or_university_degree_numeric,
+        demographics.a_levelsas_levels_or_equivalent_numeric,
+        demographics.nvq_or_hnd_or_hnc_or_equivalent_numeric,
+        demographics.o_levelsgcses_or_equivalent_numeric,
+        demographics.cses_or_equivalent_numeric
   )
@@
 ## looking at cases over 0.5
-table(dat.glad.coping$covid_odds_ratio_50) 
-```
+freq(dat.glad.coping$covid_odds_ratio_50, 
+     cumul = FALSE) 
+```

### 2020-08-07 PANCHANGE_data_preprocessing2020-07-15.Rmd
added logic chunk to specify cohort
got rid of .uncleaned at the demographics object, it was double

@@
 
+# Specify cohort
+```{r}
+GLAD = TRUE
+EDGI = FALSE
+NBR = FALSE
+RAMP = FALSE
+```
+
 #Packages
@@
 ```{r glad dem cleaning}
-glad.dem.raw.id.unclean <- glad.dem.raw %>%
+glad.dem.raw.id <- glad.dem.raw %>%
   drop_na(externalDataReference) %>% # Drop NAs
@@
 # Inspect dimensions
-dim(glad.dem.raw.id.unclean)
+dim(glad.dem.raw.id)
 # Inspect colnames
-colnames(glad.dem.raw.id.unclean)
+colnames(glad.dem.raw.id)
 #Differences
-dim(glad.dem.raw)[1]-dim(glad.dem.raw.id.unclean)[1]
+dim(glad.dem.raw)[1]-dim(glad.dem.raw.id)[1]
 ```
@@
 
-glad.dem.raw.id.unclean.numeric <- add_numeric(glad.dem.raw.id.unclean, exclude = exclude_cols)
+glad.dem.raw.id.numeric <- add_numeric(glad.dem.raw.id, exclude = exclude_cols)
 
 # Check if factor columns have been added
-colnames(glad.dem.raw.id.unclean.numeric)
+colnames(glad.dem.raw.id.numeric)
 
 # Dimensions before adding factor columns
-dim(glad.dem.raw.id.unclean)
+dim(glad.dem.raw.id)
 # Dimensions after adding factor columns
-dim(glad.dem.raw.id.unclean.numeric)
+dim(glad.dem.raw.id.numeric)
 ```
@@
   which(
-  glad.dem.raw.id.unclean$Age_uncleaned > age_upper_limit |
-    glad.dem.raw.id.unclean$Age_uncleaned < age_lower_limit
+  glad.dem.raw.id$Age_uncleaned > age_upper_limit |
+    glad.dem.raw.id$Age_uncleaned < age_lower_limit
      )
@@
 # remove age outliers
-glad.dem.raw.id <- glad.dem.raw.id.unclean %>%
+glad.dem.raw.id <- glad.dem.raw.id %>%
   mutate(
@@
 ```{r Age groups}
-#if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE ) {
+if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE ) {
 
@@
 
-#}
+}
 ```

### 2020-08-07 PANCHANGE_data_preprocessing2020-07-15.Rmd
used the .numeric tibble for creating new variables

@@
   which(
-  glad.dem.raw.id$Age_uncleaned > age_upper_limit |
-    glad.dem.raw.id$Age_uncleaned < age_lower_limit
+  glad.dem.raw.id.numeric$Age_uncleaned > age_upper_limit |
+    glad.dem.raw.id.numeric$Age_uncleaned < age_lower_limit
      )
@@
 # remove age outliers
-glad.dem.raw.id <- glad.dem.raw.id %>%
+glad.dem.raw.id.numeric <- glad.dem.raw.id.numeric %>%
   mutate(
@@
 # Inspect colnames
-colnames(glad.dem.raw.id)
+colnames(glad.dem.raw.id.numeric)
 ```
@@
 # Create categorical age groups per 10 years
-glad.dem.raw.id <- glad.dem.raw.id %>%
+glad.dem.raw.id.numeric <- glad.dem.raw.id.numeric %>%
   mutate(
@@
 
-glad.dem.raw.id <- glad.dem.raw.id %>%
+glad.dem.raw.id.numeric <- glad.dem.raw.id.numeric %>%
     mutate(
@@
 
-glad.dem.raw.id %>%
+glad.dem.raw.id.numeric %>%
   freq(age_category)
@@
 #create numeric version of the highest education variable
-glad.dem.raw.id <- glad.dem.raw.id %>%
+glad.dem.raw.id.numeric <- glad.dem.raw.id.numeric %>%
   mutate(
@@
 #recode the numeric version into a factor
-glad.dem.raw.id <- glad.dem.raw.id %>%
+glad.dem.raw.id.numeric <- glad.dem.raw.id.numeric %>%
   mutate(
@@
 
-glad.dem.raw.id %>%
+glad.dem.raw.id.numeric %>%
   freq(highest_education)
@@
 ```{r Highest education check}
-glad.dem.raw.id %>%
+glad.dem.raw.id.numeric %>%
   select(highest_education,
@@
 ```{r glad dem head}
-head(glad.dem.raw.id)
+head(glad.dem.raw.id.numeric)
 ```
@@
 summarytools::dfSummary(
-  glad.dem.raw.id,
+  glad.dem.raw.id.numeric,
   graph.col = F,

### 2020-08-07 PANCHANGE_data_preprocessing2020-07-15.Rmd
changed it back without .numeric added add_numeric to cleaning chunk

@@
 ```{r glad dem cleaning}
+exclude_cols_dem <- c("ID",
+                  "Sample",
+                  "startDate.glad",
+                  "Age_uncleaned",
+                  "EduYrs")
+
 glad.dem.raw.id <- glad.dem.raw %>%
@@
          ) %>%
+  add_numeric(., exclude = exclude_cols_dem) %>%
   mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
@@
 dim(glad.dem.raw)[1]-dim(glad.dem.raw.id)[1]
-```
-
-Create dem numeric variables
-```{r create dem numeric variables}
-exclude_cols <- c("ID",
-                  "Sample",
-                  "startDate.glad",
-                  "Age_uncleaned",
-                  "EduYrs")
-
-glad.dem.raw.id.numeric <- add_numeric(glad.dem.raw.id, exclude = exclude_cols)
-
-# Check if factor columns have been added
-colnames(glad.dem.raw.id.numeric)
-
-# Dimensions before adding factor columns
-dim(glad.dem.raw.id)
-# Dimensions after adding factor columns
-dim(glad.dem.raw.id.numeric)
 ```

### 2020-08-07 PANCHANGE_data_preprocessing2020-07-15.Rmd
changed mhq to mhd

--- 2020-08-07 PANCHANGE_data_preprocessing2020-07-15.Rmd
@@
 ```{r glad gad cleaning}
+exclude_cols <- c("Sample",
+                  "ID")
+
 glad.gad.raw.id <- glad.gad.raw %>%
@@
     gad.becoming_easily_annoyed_or_irritable_prepan = gad.becoming_easily_annoyed_or_irritable,
-    gad.awful_feeling_afraid_happen_prepan = gad.awful_feeling_afraid_happen,
-    gad.feeling_nervous_anxious_or_on_edge_prepan_numeric = gad.feeling_nervous_anxious_or_on_edge_numeric,
-    gad.control_worrying_stop_prepan_numeric = gad.control_worrying_stop_numeric,
-    gad.worrying_too_much_about_different_things_prepan_numeric = gad.worrying_too_much_about_different_things_numeric,
-    gad.trouble_relaxing_prepan_numeric = gad.trouble_relaxing_numeric,
-    gad.sit_restless_hard_prepan_numeric = gad.sit_restless_hard_numeric,
-    gad.becoming_easily_annoyed_or_irritable_prepan_numeric = gad.becoming_easily_annoyed_or_irritable_numeric,
-    gad.awful_feeling_afraid_happen_prepan_numeric = gad.awful_feeling_afraid_happen_numeric
+    gad.awful_feeling_afraid_happen_prepan = gad.awful_feeling_afraid_happen
   ) %>%
+  add_numeric(., exclude = exclude_cols) %>%
   mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
@@
 
-# glad mhq
-
-```{r glad mhq cols}
-glad.mhq.raw <- readRDS(file = paste0(data.raw_path,"/glad/mhq_glad.rds"))
-dim(glad.mhq.raw)
-colnames(glad.mhq.raw)
-```
-
-```{r glad mhq cleaning}
-glad.mhq.raw.id <- glad.mhq.raw %>%
+# glad mhd
+
+```{r glad mhd cols}
+glad.mhd.raw <- readRDS(file = paste0(data.raw_path,"/glad/mhd_glad.rds"))
+dim(glad.mhd.raw)
+colnames(glad.mhd.raw)
+```
+
+```{r glad mhd cleaning}
+glad.mhd.raw.id <- glad.mhd.raw %>%
   drop_na(externalDataReference) %>% # Drop NAs
@@
     ID, # ID
-    starts_with("mhq.")
+    starts_with("mhd.")
   ) %>%
+  add_numeric(., exclude = exclude_cols) %>%
   mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
@@
 # Inspect dimensions
-dim(glad.mhq.raw.id)
+dim(glad.mhd.raw.id)
 # Inspect colnames
-colnames(glad.mhq.raw.id)
+colnames(glad.mhd.raw.id)
 #Differences
-dim(glad.mhq.raw)[1]-dim(glad.mhq.raw.id)[1]
+dim(glad.mhd.raw)[1]-dim(glad.mhd.raw.id)[1]
 ```
@@
 
-```{r glad mhq depressive_disorders}
-glad.mhq.raw.id <- glad.mhq.raw.id %>%
+```{r glad mhd depressive_disorders}
+glad.mhd.raw.id <- glad.mhd.raw.id %>%
   mutate(
@@
       case_when(
-        (mhq.depression_numeric == "0" &
-        (mhq.pregnancy_depression_numeric == "0" | is.na(mhq.pregnancy_depression_numeric)) & 
-        (mhq.premenstrual_dysphoric_disorder_pmdd_numeric == "0" | is.na(mhq.premenstrual_dysphoric_disorder_pmdd_numeric))) ~ 0,
-        mhq.depression_numeric == "1" ~ 1,
-        mhq.pregnancy_depression_numeric == "1" ~ 1,
-        mhq.premenstrual_dysphoric_disorder_pmdd_numeric == "1" ~ 1))
-
-glad.mhq.raw.id <- glad.mhq.raw.id %>%
+        (mhd.depression_numeric == "0" &
+        (mhd.pregnancy_depression_numeric == "0" | is.na(mhd.pregnancy_depression_numeric)) & 
+        (mhd.premenstrual_dysphoric_disorder_pmdd_numeric == "0" | is.na(mhd.premenstrual_dysphoric_disorder_pmdd_numeric))) ~ 0,
+        mhd.depression_numeric == "1" ~ 1,
+        mhd.pregnancy_depression_numeric == "1" ~ 1,
+        mhd.premenstrual_dysphoric_disorder_pmdd_numeric == "1" ~ 1))
+
+glad.mhd.raw.id <- glad.mhd.raw.id %>%
   mutate(
@@
 
-glad.mhq.raw.id %>%
+glad.mhd.raw.id %>%
   freq(depressive_disorders)
@@
 ```{r Check depressive_disorders}
-glad.mhq.raw.id %>%
+glad.mhd.raw.id %>%
   select(
@@
     depressive_disorders_numeric,
-    mhq.depression_numeric,
-    mhq.pregnancy_depression_numeric,
-    mhq.premenstrual_dysphoric_disorder_pmdd_numeric,
-    mhq.depression,
-    mhq.pregnancy_depression,
-    mhq.premenstrual_dysphoric_disorder_pmdd
+    mhd.depression_numeric,
+    mhd.pregnancy_depression_numeric,
+    mhd.premenstrual_dysphoric_disorder_pmdd_numeric,
+    mhd.depression,
+    mhd.pregnancy_depression,
+    mhd.premenstrual_dysphoric_disorder_pmdd
   )
@@
 Anxiety disorders group
-```{r glad mhq anxiety_disorders}
-glad.mhq.raw.id <- glad.mhq.raw.id %>%
+```{r glad mhd anxiety_disorders}
+glad.mhd.raw.id <- glad.mhd.raw.id %>%
   mutate(
@@
       case_when(
-        mhq.anxiety_nerves_or_generalised_anxiety_disorder_numeric == "1" ~ 1,
-        mhq.social_anxiety_or_social_phobia_numeric == "1" ~ 1,
-        mhq.specific_phobia_e.g._phobia_of_flying_numeric == "1" ~ 1,
-        mhq.agoraphobia_numeric == "1" ~ 1,
-        mhq.panic_disorder_numeric == "1" ~ 1,
-        mhq.panic_attacks_numeric == "1" ~ 1,
-        (mhq.anxiety_nerves_or_generalised_anxiety_disorder_numeric == "0" &
-        mhq.social_anxiety_or_social_phobia_numeric == "0" &
-        mhq.specific_phobia_e.g._phobia_of_flying_numeric == "0" &
-        mhq.agoraphobia_numeric == "0" &
-        mhq.panic_disorder_numeric == "0" &
-        mhq.panic_attacks_numeric == "0") ~ 0
-      )
-  )
-
-glad.mhq.raw.id <- glad.mhq.raw.id %>%
+        mhd.anxiety_nerves_or_generalised_anxiety_disorder_numeric == "1" ~ 1,
+        mhd.social_anxiety_or_social_phobia_numeric == "1" ~ 1,
+        mhd.specific_phobia_e.g._phobia_of_flying_numeric == "1" ~ 1,
+        mhd.agoraphobia_numeric == "1" ~ 1,
+        mhd.panic_disorder_numeric == "1" ~ 1,
+        mhd.panic_attacks_numeric == "1" ~ 1,
+        (mhd.anxiety_nerves_or_generalised_anxiety_disorder_numeric == "0" &
+        mhd.social_anxiety_or_social_phobia_numeric == "0" &
+        mhd.specific_phobia_e.g._phobia_of_flying_numeric == "0" &
+        mhd.agoraphobia_numeric == "0" &
+        mhd.panic_disorder_numeric == "0" &
+        mhd.panic_attacks_numeric == "0") ~ 0
+      )
+  )
+
+glad.mhd.raw.id <- glad.mhd.raw.id %>%
   mutate(
@@
 
-glad.mhq.raw.id %>%
+glad.mhd.raw.id %>%
   freq(anxiety_disorders)
@@
 ```{r Check anxiety_disorders}
-glad.mhq.raw.id %>%
+glad.mhd.raw.id %>%
   select(
@@
     anxiety_disorders_numeric,
-    mhq.anxiety_nerves_or_generalised_anxiety_disorder_numeric,
-    mhq.social_anxiety_or_social_phobia_numeric,
-    mhq.specific_phobia_e.g._phobia_of_flying_numeric,
-    mhq.agoraphobia_numeric,
-    mhq.panic_disorder_numeric,
-    mhq.panic_attacks_numeric,
-    mhq.anxiety_nerves_or_generalised_anxiety_disorder,
-    mhq.social_anxiety_or_social_phobia,
-    mhq.specific_phobia_e.g._phobia_of_flying,
-    mhq.agoraphobia,
-    mhq.panic_disorder,
-    mhq.panic_attacks
+    mhd.anxiety_nerves_or_generalised_anxiety_disorder_numeric,
+    mhd.social_anxiety_or_social_phobia_numeric,
+    mhd.specific_phobia_e.g._phobia_of_flying_numeric,
+    mhd.agoraphobia_numeric,
+    mhd.panic_disorder_numeric,
+    mhd.panic_attacks_numeric,
+    mhd.anxiety_nerves_or_generalised_anxiety_disorder,
+    mhd.social_anxiety_or_social_phobia,
+    mhd.specific_phobia_e.g._phobia_of_flying,
+    mhd.agoraphobia,
+    mhd.panic_disorder,
+    mhd.panic_attacks
   )
@@
 Agoraphonia and panic disorder group
-```{r glad mhq agoraphobia_panic_disorder}
-glad.mhq.raw.id <- glad.mhq.raw.id %>%
+```{r glad mhd agoraphobia_panic_disorder}
+glad.mhd.raw.id <- glad.mhd.raw.id %>%
   mutate(
@@
       case_when(
-        mhq.agoraphobia_numeric == "1" ~ 1,
-        mhq.panic_disorder_numeric == "1" ~ 1,
-        mhq.panic_attacks_numeric == "1" ~ 1,
-        (mhq.agoraphobia_numeric == "0" &
-        mhq.panic_disorder_numeric == "0" &
-        mhq.panic_attacks_numeric == "0") ~ 0
-      )
-  )
-
-glad.mhq.raw.id <- glad.mhq.raw.id %>%
+        mhd.agoraphobia_numeric == "1" ~ 1,
+        mhd.panic_disorder_numeric == "1" ~ 1,
+        mhd.panic_attacks_numeric == "1" ~ 1,
+        (mhd.agoraphobia_numeric == "0" &
+        mhd.panic_disorder_numeric == "0" &
+        mhd.panic_attacks_numeric == "0") ~ 0
+      )
+  )
+
+glad.mhd.raw.id <- glad.mhd.raw.id %>%
   mutate(
@@
 
-glad.mhq.raw.id %>%
+glad.mhd.raw.id %>%
   freq(agoraphobia_panic_disorder)
@@
 ```{r Check agoraphobia_panic_disorder}
-glad.mhq.raw.id %>%
+glad.mhd.raw.id %>%
   select(
@@
     agoraphobia_panic_disorder_numeric,
-    mhq.agoraphobia_numeric,
-    mhq.panic_disorder_numeric,
-    mhq.panic_attacks_numeric,
-    mhq.agoraphobia,
-    mhq.panic_disorder,
-    mhq.panic_attacks
+    mhd.agoraphobia_numeric,
+    mhd.panic_disorder_numeric,
+    mhd.panic_attacks_numeric,
+    mhd.agoraphobia,
+    mhd.panic_disorder,
+    mhd.panic_attacks
   )
@@
 Eating disorders group
-```{r glad mhq eating_disorders}
-glad.mhq.raw.id <- glad.mhq.raw.id %>%
+```{r glad mhd eating_disorders}
+glad.mhd.raw.id <- glad.mhd.raw.id %>%
   mutate(
@@
       case_when(
-        mhq.anorexia_nervosa_numeric == "1" ~ 1,
-        mhq.atypical_anorexia_nervosa_numeric == "1" ~ 1,
-        mhq.bulimia_nervosa_numeric == "1" ~ 1,
-        mhq.psychological_overeating_or_bingeeating_numeric == "1" ~ 1,
-        (mhq.anorexia_nervosa_numeric == "0" &
-        mhq.atypical_anorexia_nervosa_numeric == "0" &
-        mhq.bulimia_nervosa_numeric == "0" &
-        mhq.psychological_overeating_or_bingeeating_numeric == "0") ~ 0
-      )
-  )
-
-glad.mhq.raw.id <- glad.mhq.raw.id %>%
+        mhd.anorexia_nervosa_numeric == "1" ~ 1,
+        mhd.atypical_anorexia_nervosa_numeric == "1" ~ 1,
+        mhd.bulimia_nervosa_numeric == "1" ~ 1,
+        mhd.psychological_overeating_or_bingeeating_numeric == "1" ~ 1,
+        (mhd.anorexia_nervosa_numeric == "0" &
+        mhd.atypical_anorexia_nervosa_numeric == "0" &
+        mhd.bulimia_nervosa_numeric == "0" &
+        mhd.psychological_overeating_or_bingeeating_numeric == "0") ~ 0
+      )
+  )
+
+glad.mhd.raw.id <- glad.mhd.raw.id %>%
   mutate(
@@
 
-glad.mhq.raw.id %>%
+glad.mhd.raw.id %>%
   freq(eating_disorders)
@@
 ```{r Check eating_disorders}
-glad.mhq.raw.id %>%
+glad.mhd.raw.id %>%
   select(
@@
     eating_disorders_numeric,
-    mhq.anorexia_nervosa_numeric,
-    mhq.atypical_anorexia_nervosa_numeric,
-    mhq.bulimia_nervosa_numeric,
-    mhq.psychological_overeating_or_bingeeating_numeric,
-    mhq.anorexia_nervosa,
-    mhq.atypical_anorexia_nervosa,
-    mhq.bulimia_nervosa,
-    mhq.psychological_overeating_or_bingeeating
+    mhd.anorexia_nervosa_numeric,
+    mhd.atypical_anorexia_nervosa_numeric,
+    mhd.bulimia_nervosa_numeric,
+    mhd.psychological_overeating_or_bingeeating_numeric,
+    mhd.anorexia_nervosa,
+    mhd.atypical_anorexia_nervosa,
+    mhd.bulimia_nervosa,
+    mhd.psychological_overeating_or_bingeeating
   )
@@
 Obsessive compulsive disorders
-```{r glad mhq obsessive_compulsive_disorders}
-glad.mhq.raw.id <- glad.mhq.raw.id %>%
+```{r glad mhd obsessive_compulsive_disorders}
+glad.mhd.raw.id <- glad.mhd.raw.id %>%
   mutate(
@@
       case_when(
-        mhq.obsessivecompulsive_disorder_ocd_numeric == "1" ~ 1,
-        mhq.obsessive_compulsive_related_disorders_numeric == "1" ~ 1,
-        mhq.body_dysmorphic_disorder_bdd_numeric == "1" ~ 1,
-        (mhq.obsessivecompulsive_disorder_ocd_numeric == "0" &
-        mhq.obsessive_compulsive_related_disorders_numeric == "0" &
-        mhq.body_dysmorphic_disorder_bdd_numeric == "0") ~ 0
-      )
-  )
-
-glad.mhq.raw.id <- glad.mhq.raw.id %>%
+        mhd.obsessivecompulsive_disorder_ocd_numeric == "1" ~ 1,
+        mhd.obsessive_compulsive_related_disorders_numeric == "1" ~ 1,
+        mhd.body_dysmorphic_disorder_bdd_numeric == "1" ~ 1,
+        (mhd.obsessivecompulsive_disorder_ocd_numeric == "0" &
+        mhd.obsessive_compulsive_related_disorders_numeric == "0" &
+        mhd.body_dysmorphic_disorder_bdd_numeric == "0") ~ 0
+      )
+  )
+
+glad.mhd.raw.id <- glad.mhd.raw.id %>%
   mutate(
@@
 
-glad.mhq.raw.id %>%
+glad.mhd.raw.id %>%
   freq(obsessive_compulsive_disorders)
@@
 ```{r Check obsessive_compulsive_disorders}
-glad.mhq.raw.id %>%
+glad.mhd.raw.id %>%
   select(
@@
     obsessive_compulsive_disorders_numeric,
-    mhq.obsessivecompulsive_disorder_ocd,
-    mhq.obsessivecompulsive_disorder_ocd_numeric,
-    mhq.obsessive_compulsive_related_disorders,
-    mhq.obsessive_compulsive_related_disorders_numeric
+    mhd.obsessivecompulsive_disorder_ocd,
+    mhd.obsessivecompulsive_disorder_ocd_numeric,
+    mhd.obsessive_compulsive_related_disorders,
+    mhd.obsessive_compulsive_related_disorders_numeric
   )
@@
 Psychotic disorders group
-```{r glad mhq psychotic_disorders}
-glad.mhq.raw.id <- glad.mhq.raw.id %>%
+```{r glad mhd psychotic_disorders}
+glad.mhd.raw.id <- glad.mhd.raw.id %>%
   mutate(
@@
       case_when(
-        mhq.schizophrenia_numeric == "1" ~ 1,
-        mhq.schizoaffective_disorder_numeric == "1" ~ 1,
-        mhq.type_psychosis_psychotic_illness_numeric == "1" ~ 1,
-        (mhq.schizophrenia_numeric == "0" &
-        mhq.schizoaffective_disorder_numeric == "0" &
-        mhq.type_psychosis_psychotic_illness_numeric == "0") ~ 0
-      )
-  )
-
-glad.mhq.raw.id <- glad.mhq.raw.id %>%
+        mhd.schizophrenia_numeric == "1" ~ 1,
+        mhd.schizoaffective_disorder_numeric == "1" ~ 1,
+        mhd.type_psychosis_psychotic_illness_numeric == "1" ~ 1,
+        (mhd.schizophrenia_numeric == "0" &
+        mhd.schizoaffective_disorder_numeric == "0" &
+        mhd.type_psychosis_psychotic_illness_numeric == "0") ~ 0
+      )
+  )
+
+glad.mhd.raw.id <- glad.mhd.raw.id %>%
   mutate(
@@
 
-glad.mhq.raw.id %>%
+glad.mhd.raw.id %>%
   freq(psychotic_disorders)
@@
 ```{r Check psychotic_disorders}
-glad.mhq.raw.id %>%
+glad.mhd.raw.id %>%
   select(
@@
     psychotic_disorders_numeric,
-    mhq.schizophrenia_numeric,
-    mhq.schizoaffective_disorder_numeric,
-    mhq.type_psychosis_psychotic_illness_numeric,
-    mhq.schizophrenia,
-    mhq.schizoaffective_disorder,
-    mhq.type_psychosis_psychotic_illness
+    mhd.schizophrenia_numeric,
+    mhd.schizoaffective_disorder_numeric,
+    mhd.type_psychosis_psychotic_illness_numeric,
+    mhd.schizophrenia,
+    mhd.schizoaffective_disorder,
+    mhd.type_psychosis_psychotic_illness
   )
@@
 ```{r check bipolar overlap with schizophrenia}
-glad.mhq.raw.id <- glad.mhq.raw.id %>%
+glad.mhd.raw.id <- glad.mhd.raw.id %>%
   mutate(
@@
       if_else(
-        mhq.schizophrenia_numeric == "1" &
-          mhq.mania_hypomania_bipolar_or_manicdepression_numeric == "1", 1, 0
-      )
-  )
-
-glad.mhq.raw.id <- glad.mhq.raw.id %>%
+        mhd.schizophrenia_numeric == "1" &
+          mhd.mania_hypomania_bipolar_or_manicdepression_numeric == "1", 1, 0
+      )
+  )
+
+glad.mhd.raw.id <- glad.mhd.raw.id %>%
   mutate(
@@
 
-glad.mhq.raw.id %>%
+glad.mhd.raw.id %>%
   freq(bipolar_and_schizophrenia)
@@
 3. Schizotypal                      14 ( 0.5%)
-```{r glad mhq personality_cluster_a}
-glad.mhq.raw.id <- glad.mhq.raw.id %>%
+```{r glad mhd personality_cluster_a}
+glad.mhd.raw.id <- glad.mhd.raw.id %>%
   mutate(
@@
       case_when(
-        mhq.personality_disorder_diagnosed_numeric == "1" ~ 1,
-        mhq.personality_disorder_diagnosed_numeric == "2" ~ 1,
-        mhq.personality_disorder_diagnosed_numeric == "3" ~ 1,
-        mhq.personality_disorder_diagnosed_numeric == "4" ~ 0,
-        mhq.personality_disorder_diagnosed_numeric == "5" ~ 0,
-        mhq.personality_disorder_diagnosed_numeric == "6" ~ 0,
-        mhq.personality_disorder_diagnosed_numeric == "7" ~ 0,
-        mhq.personality_disorder_diagnosed_numeric == "8" ~ 0,
-        mhq.personality_disorder_diagnosed_numeric == "9" ~ 0,
-        mhq.personality_disorder_diagnosed_numeric == "10" ~ 0,
-        mhq.personality_disorder_numeric == "0" ~ 0
-      )
-  )
-
-glad.mhq.raw.id <- glad.mhq.raw.id %>%
+        mhd.personality_disorder_diagnosed_numeric == "1" ~ 1,
+        mhd.personality_disorder_diagnosed_numeric == "2" ~ 1,
+        mhd.personality_disorder_diagnosed_numeric == "3" ~ 1,
+        mhd.personality_disorder_diagnosed_numeric == "4" ~ 0,
+        mhd.personality_disorder_diagnosed_numeric == "5" ~ 0,
+        mhd.personality_disorder_diagnosed_numeric == "6" ~ 0,
+        mhd.personality_disorder_diagnosed_numeric == "7" ~ 0,
+        mhd.personality_disorder_diagnosed_numeric == "8" ~ 0,
+        mhd.personality_disorder_diagnosed_numeric == "9" ~ 0,
+        mhd.personality_disorder_diagnosed_numeric == "10" ~ 0,
+        mhd.personality_disorder_numeric == "0" ~ 0
+      )
+  )
+
+glad.mhd.raw.id <- glad.mhd.raw.id %>%
   mutate(
@@
 
-glad.mhq.raw.id %>%
+glad.mhd.raw.id %>%
   freq(personality_cluster_a)
@@
 ```{r Check personality_cluster_a}
-glad.mhq.raw.id %>%
+glad.mhd.raw.id %>%
   select(
@@
     personality_cluster_a_numeric,
-    mhq.personality_disorder_diagnosed,
-    mhq.personality_disorder_diagnosed_numeric
+    mhd.personality_disorder_diagnosed,
+    mhd.personality_disorder_diagnosed_numeric
   )
@@
 
-```{r glad mhq personality_cluster_b}
-glad.mhq.raw.id <- glad.mhq.raw.id %>%
+```{r glad mhd personality_cluster_b}
+glad.mhd.raw.id <- glad.mhd.raw.id %>%
   mutate(
@@
       case_when(
-        mhq.personality_disorder_diagnosed_numeric == "1" ~ 0,
-        mhq.personality_disorder_diagnosed_numeric == "2" ~ 0,
-        mhq.personality_disorder_diagnosed_numeric == "3" ~ 0,
-        mhq.personality_disorder_diagnosed_numeric == "4" ~ 1,
-        mhq.personality_disorder_diagnosed_numeric == "5" ~ 1,
-        mhq.personality_disorder_diagnosed_numeric == "6" ~ 1,
-        mhq.personality_disorder_diagnosed_numeric == "7" ~ 1,
-        mhq.personality_disorder_diagnosed_numeric == "8" ~ 0,
-        mhq.personality_disorder_diagnosed_numeric == "9" ~ 0,
-        mhq.personality_disorder_diagnosed_numeric == "10" ~ 0,
-        mhq.personality_disorder_numeric == "0" ~ 0
-      )
-  )
-
-glad.mhq.raw.id <- glad.mhq.raw.id %>%
+        mhd.personality_disorder_diagnosed_numeric == "1" ~ 0,
+        mhd.personality_disorder_diagnosed_numeric == "2" ~ 0,
+        mhd.personality_disorder_diagnosed_numeric == "3" ~ 0,
+        mhd.personality_disorder_diagnosed_numeric == "4" ~ 1,
+        mhd.personality_disorder_diagnosed_numeric == "5" ~ 1,
+        mhd.personality_disorder_diagnosed_numeric == "6" ~ 1,
+        mhd.personality_disorder_diagnosed_numeric == "7" ~ 1,
+        mhd.personality_disorder_diagnosed_numeric == "8" ~ 0,
+        mhd.personality_disorder_diagnosed_numeric == "9" ~ 0,
+        mhd.personality_disorder_diagnosed_numeric == "10" ~ 0,
+        mhd.personality_disorder_numeric == "0" ~ 0
+      )
+  )
+
+glad.mhd.raw.id <- glad.mhd.raw.id %>%
   mutate(
@@
 
-glad.mhq.raw.id %>%
+glad.mhd.raw.id %>%
   freq(personality_cluster_b)
@@
 ```{r Check personality_cluster_b}
-glad.mhq.raw.id %>%
+glad.mhd.raw.id %>%
   select(
@@
     personality_cluster_b_numeric,
-    mhq.personality_disorder_diagnosed,
-    mhq.personality_disorder_diagnosed_numeric
+    mhd.personality_disorder_diagnosed,
+    mhd.personality_disorder_diagnosed_numeric
   )
@@
 10. Obsessive-compulsive
-```{r glad mhq personality_cluster_c}
-glad.mhq.raw.id <- glad.mhq.raw.id %>%
+```{r glad mhd personality_cluster_c}
+glad.mhd.raw.id <- glad.mhd.raw.id %>%
   mutate(
@@
       case_when(
-        mhq.personality_disorder_diagnosed_numeric == "1" ~ 0,
-        mhq.personality_disorder_diagnosed_numeric == "2" ~ 0,
-        mhq.personality_disorder_diagnosed_numeric == "3" ~ 0,
-        mhq.personality_disorder_diagnosed_numeric == "4" ~ 0,
-        mhq.personality_disorder_diagnosed_numeric == "5" ~ 0,
-        mhq.personality_disorder_diagnosed_numeric == "6" ~ 0,
-        mhq.personality_disorder_diagnosed_numeric == "7" ~ 0,
-        mhq.personality_disorder_diagnosed_numeric == "8" ~ 1,
-        mhq.personality_disorder_diagnosed_numeric == "9" ~ 1,
-        mhq.personality_disorder_diagnosed_numeric == "10" ~ 1,
-        mhq.personality_disorder_numeric == "0" ~ 0
-      )
-  )
-
-glad.mhq.raw.id <- glad.mhq.raw.id %>%
+        mhd.personality_disorder_diagnosed_numeric == "1" ~ 0,
+        mhd.personality_disorder_diagnosed_numeric == "2" ~ 0,
+        mhd.personality_disorder_diagnosed_numeric == "3" ~ 0,
+        mhd.personality_disorder_diagnosed_numeric == "4" ~ 0,
+        mhd.personality_disorder_diagnosed_numeric == "5" ~ 0,
+        mhd.personality_disorder_diagnosed_numeric == "6" ~ 0,
+        mhd.personality_disorder_diagnosed_numeric == "7" ~ 0,
+        mhd.personality_disorder_diagnosed_numeric == "8" ~ 1,
+        mhd.personality_disorder_diagnosed_numeric == "9" ~ 1,
+        mhd.personality_disorder_diagnosed_numeric == "10" ~ 1,
+        mhd.personality_disorder_numeric == "0" ~ 0
+      )
+  )
+
+glad.mhd.raw.id <- glad.mhd.raw.id %>%
   mutate(
@@
 
-glad.mhq.raw.id %>%
+glad.mhd.raw.id %>%
   freq(personality_cluster_c)
@@
 ```{r Check personality_cluster_c}
-glad.mhq.raw.id %>%
+glad.mhd.raw.id %>%
   select(
@@
     personality_cluster_c_numeric,
-    mhq.personality_disorder_diagnosed,
-    mhq.personality_disorder_diagnosed_numeric
+    mhd.personality_disorder_diagnosed,
+    mhd.personality_disorder_diagnosed_numeric
   )
@@
 Controls = 784
-```{r glad mhq control}
-glad.mhq.raw.id <- glad.mhq.raw.id %>%
+```{r glad mhd control}
+glad.mhd.raw.id <- glad.mhd.raw.id %>%
   mutate(
@@
     psychotic_disorders_numeric == "0" &
-    mhq.mania_hypomania_bipolar_or_manicdepression_numeric == "0" &
-    mhq.posttraumatic_stress_disorder_ptsd_numeric == "0" &
-    mhq.autism_aspergers_or_autistic_spectrum_disorder_numeric == "0" &
-    mhq.attention_deficit_hyperactivity_disorder_numeric == "0" &
-    mhq.personality_disorder_numeric == "0", 
+    mhd.mania_hypomania_bipolar_or_manicdepression_numeric == "0" &
+    mhd.posttraumatic_stress_disorder_ptsd_numeric == "0" &
+    mhd.autism_aspergers_or_autistic_spectrum_disorder_numeric == "0" &
+    mhd.attention_deficit_hyperactivity_disorder_numeric == "0" &
+    mhd.personality_disorder_numeric == "0", 
     true = 1, 
@@
 
-glad.mhq.raw.id <- glad.mhq.raw.id %>%
+glad.mhd.raw.id <- glad.mhd.raw.id %>%
   mutate(
@@
 
-glad.mhq.raw.id %>%
+glad.mhd.raw.id %>%
   freq(control)
@@
 
-```{r glad mhq head}
-head(glad.mhq.raw.id)
-```
-
-```{r glad mhq summary}
+```{r glad mhd head}
+head(glad.mhd.raw.id)
+```
+
+```{r glad mhd summary}
 summarytools::dfSummary(
-  glad.mhq.raw.id,
+  glad.mhd.raw.id,
   graph.col = F,
@@
 ++KT: do we want to keep individual diagnoses here as well?? 
-```{r glad mhq categories}
-glad.mhq.raw.categories <- glad.mhq.raw.id %>%
+```{r glad mhd categories}
+glad.mhd.raw.categories <- glad.mhd.raw.id %>%
   select(
@@
     anxiety_disorders,
-    mhq.specific_phobia_e.g._phobia_of_flying_numeric,
-    mhq.specific_phobia_e.g._phobia_of_flying,
-    mhq.social_anxiety_or_social_phobia_numeric,
-    mhq.social_anxiety_or_social_phobia,
+    mhd.specific_phobia_e.g._phobia_of_flying_numeric,
+    mhd.specific_phobia_e.g._phobia_of_flying,
+    mhd.social_anxiety_or_social_phobia_numeric,
+    mhd.social_anxiety_or_social_phobia,
     agoraphobia_panic_disorder_numeric,
@@
     psychotic_disorders,
-    mhq.mania_hypomania_bipolar_or_manicdepression_numeric,
-    mhq.mania_hypomania_bipolar_or_manicdepression,
-    mhq.posttraumatic_stress_disorder_ptsd_numeric,
-    mhq.posttraumatic_stress_disorder_ptsd,
-    mhq.autism_aspergers_or_autistic_spectrum_disorder_numeric,
-    mhq.autism_aspergers_or_autistic_spectrum_disorder,
-    mhq.attention_deficit_hyperactivity_disorder_numeric,
-    mhq.attention_deficit_hyperactivity_disorder,
-    mhq.personality_disorder_numeric,
-    mhq.personality_disorder,
+    mhd.mania_hypomania_bipolar_or_manicdepression_numeric,
+    mhd.mania_hypomania_bipolar_or_manicdepression,
+    mhd.posttraumatic_stress_disorder_ptsd_numeric,
+    mhd.posttraumatic_stress_disorder_ptsd,
+    mhd.autism_aspergers_or_autistic_spectrum_disorder_numeric,
+    mhd.autism_aspergers_or_autistic_spectrum_disorder,
+    mhd.attention_deficit_hyperactivity_disorder_numeric,
+    mhd.attention_deficit_hyperactivity_disorder,
+    mhd.personality_disorder_numeric,
+    mhd.personality_disorder,
     personality_cluster_a_numeric,
@@
   glad.gad.raw.id,
-  glad.mhq.raw.categories,
+  glad.mhd.raw.categories,
   glad.ocir.raw.id,

### 2020-08-07 PANCHANGE_data_preprocessing2020-07-15.Rmd
added diagnostic chunk for DEP and ANX comorbidity

@@
 glad.mhd.raw.id %>%
-  freq(depressive_disorders)
+  freq(depressive_disorders,
+       cumul = F)
 ```
@@
 glad.mhd.raw.id %>%
-  freq(anxiety_disorders)
+  freq(anxiety_disorders,
+       cumul = F)
 ```
@@
 
+Depression and anxiety comorbidity
+```{r glad mhd depression_anxiety}
+glad.mhd.raw.id <- glad.mhd.raw.id %>%
+  mutate(
+    depression_and_anxiety_numeric =
+      case_when(
+        depressive_disorders_numeric == 1 &
+          anxiety_disorders_numeric == 1 ~ 0,
+        depressive_disorders_numeric == 1 &
+          anxiety_disorders_numeric == 1 ~ 1,
+        depressive_disorders_numeric == 1 &
+          anxiety_disorders_numeric == 0 ~ 2,
+        depressive_disorders_numeric == 0 &
+          anxiety_disorders_numeric == 1 ~ 3
+      )
+  )
+
+glad.mhd.raw.id <- glad.mhd.raw.id %>%
+  mutate(
+    depression_and_anxiety =
+      recode_factor(depression_and_anxiety_numeric,
+                    "0" = "No depressive or anxiety disorder",
+                    "1" = "Depressive and anxiety disorder",
+                    "2" = "Only depressive disorder",
+                    "2" = "Only anxiety disorder",
+                    missing = NA_character_
+                    )
+  )
+
+glad.mhd.raw.id %>%
+  freq(depression_and_anxiety,
+       cumul = F)
+```
+
 Eating disorders group
@@
 glad.mhd.raw.id %>%
-  freq(eating_disorders)
+  freq(eating_disorders,
+       cumul = F)
 ```

### 2020-08-07 PANCHANGE_data_preprocessing2020-07-15.Rmd
added diagnostic chunk eating disorder with binge eating vs without binge eating, however anorexia can also be with binge eating

@@
 
+Eating disorders with binge eating vs eating disorders without
+Caveat: Anorexia nervosa can have binge eating as well. Therefore, this would need an additional variable from the ED100K
+```{r glad mhd restricting_vs_binge_eating_eating_disorders}
+glad.mhd.raw.id <- glad.mhd.raw.id %>%
+  mutate(
+    restricting_vs_binge_eating_eating_disorders_numeric =
+      case_when(
+                mhd.anorexia_nervosa_numeric == "1" ~ 1,
+        mhd.atypical_anorexia_nervosa_numeric == "1" ~ 1,
+        mhd.bulimia_nervosa_numeric == "1" ~ 2,
+        mhd.psychological_overeating_or_bingeeating_numeric == "1" ~ 2,
+        (mhd.anorexia_nervosa_numeric == "0" &
+        mhd.atypical_anorexia_nervosa_numeric == "0" &
+        mhd.bulimia_nervosa_numeric == "0" &
+        mhd.psychological_overeating_or_bingeeating_numeric == "0") ~ 0
+      )
+  )
+
+glad.mhd.raw.id <- glad.mhd.raw.id %>%
+  mutate(
+    restricting_vs_binge_eating_eating_disorders =
+      recode_factor(restricting_vs_binge_eating_eating_disorders_numeric,
+                    "0" = "No eating disorder",
+                    "1" = "Anorexia nervosa",
+                    "2" = "Eating disorder with binge eating",
+                    missing = NA_character_
+                    )
+  )
+
+glad.mhd.raw.id %>%
+  freq(restricting_vs_binge_eating_eating_disorders,
+       cumul = F)
+```
+
 ```{r Check eating_disorders}
@@
     eating_disorders_numeric,
+    restricting_vs_binge_eating_eating_disorders,
+    restricting_vs_binge_eating_eating_disorders_numeric,
     mhd.anorexia_nervosa_numeric,

### 2020-08-07 PANCHANGE_data_preprocessing2020-07-15.Rmd
I have updated the schizophrenia and bipolar disorder comorbidity chunk, however, there is a problem with the psychotic disorder chunk that needs discussion/fixing

@@
 
-Overlap between self-report schizphrenia and bipolar
+Overlap between self-report schizophrenia and bipolar disorder
 +++CH: Check overlap between schizophrenia group and bipolar disorder
-++KT: Only 63 with comorbid sel-report bipolar and schizophrenia. More likely to have shared symptoms, less likely to have confirmed diagnoses of both. Could be too severe to be in GLAD?
-```{r check bipolar overlap with schizophrenia}
+++KT: Only 63 with comorbid self-report bipolar disorder and schizophrenia. More likely to have shared symptoms, less likely to have confirmed diagnoses of both. Could be too severe to be in GLAD?
+```{r glad mhd bipolar_and_schizophrenia_numeric}
 glad.mhd.raw.id <- glad.mhd.raw.id %>%
@@
     bipolar_and_schizophrenia_numeric =
-      if_else(
-        mhd.schizophrenia_numeric == "1" &
-          mhd.mania_hypomania_bipolar_or_manicdepression_numeric == "1", 1, 0
+      case_when(
+        psychotic_disorders_numeric == 1 &
+          mhd.mania_hypomania_bipolar_or_manicdepression == 1 ~ 0,
+        psychotic_disorders_numeric == 1 &
+          mhd.mania_hypomania_bipolar_or_manicdepression == 1 ~ 1,
+        psychotic_disorders_numeric == 1 &
+          mhd.mania_hypomania_bipolar_or_manicdepression == 0 ~ 2,
+        psychotic_disorders_numeric == 0 &
+          mhd.mania_hypomania_bipolar_or_manicdepression == 1 ~ 3
       )
@@
       recode_factor(bipolar_and_schizophrenia_numeric,
-                    "0" = "No comorbid bipoar and schizophrenia",
-                    "1" = "Comorbid bipoar and schizophrenia",
+                    "0" = "No psychotic or bipolar disorder",
+                    "1" = "Psychotic and bipolar disorder",
+                    "2" = "Only psychotic disorder",
+                    "2" = "Only bipolar disorder",
                     missing = NA_character_
@@
 glad.mhd.raw.id %>%
-  freq(bipolar_and_schizophrenia)
+  freq(bipolar_and_schizophrenia,
+       cumul = F)
 ```

### 2020-08-07 PANCHANGE_data_preprocessing2020-07-15.Rmd
I think I fixed the psychosis bit

@@
 Psychotic disorders group
+[63] "mhd.schizophrenia_numeric"                                 
+[64] "mhd.schizoaffective_disorder_numeric"                      
+[65] "mhd.type_psychosis_psychotic_illness_numeric" 
 ```{r glad mhd psychotic_disorders}
@@
 
+Overlap between self-report schizophrenia and bipolar disorder
++++CH: Check overlap between schizophrenia group and bipolar disorder
+++KT: Only 63 with comorbid self-report bipolar disorder and schizophrenia. More likely to have shared symptoms, less likely to have confirmed diagnoses of both. Could be too severe to be in GLAD?
+```{r glad mhd bipolar_and_schizophrenia_numeric}
+glad.mhd.raw.id <- glad.mhd.raw.id %>%
+  mutate(
+    bipolar_and_schizophrenia_numeric =
+      case_when(
+        psychotic_disorders_numeric == 0 &
+          mhd.mania_hypomania_bipolar_or_manicdepression_numeric == 0 ~ 0,
+                psychotic_disorders_numeric == 1 &
+          mhd.mania_hypomania_bipolar_or_manicdepression_numeric == 0 ~ 2,
+        psychotic_disorders_numeric == 0 &
+          mhd.mania_hypomania_bipolar_or_manicdepression_numeric == 1 ~ 3,
+                psychotic_disorders_numeric == 1 &
+          mhd.mania_hypomania_bipolar_or_manicdepression_numeric == 1 ~ 1
+      )
+  )
+
+glad.mhd.raw.id <- glad.mhd.raw.id %>%
+  mutate(
+    bipolar_and_schizophrenia =
+      recode_factor(bipolar_and_schizophrenia_numeric,
+                    "0" = "No psychotic or bipolar disorder",
+                    "1" = "Psychotic and bipolar disorder",
+                    "2" = "Only psychotic disorder",
+                    "3" = "Only bipolar disorder",
+                    missing = NA_character_
+                    )
+  )
+
+glad.mhd.raw.id %>%
+  freq(bipolar_and_schizophrenia,
+       cumul = F)
+```
+
 ```{r Check psychotic_disorders}
@@
     psychotic_disorders_numeric,
+    bipolar_and_schizophrenia,
+    bipolar_and_schizophrenia_numeric,
     mhd.schizophrenia_numeric,
     mhd.schizoaffective_disorder_numeric,
+    mhd.mania_hypomania_bipolar_or_manicdepression,
+    mhd.mania_hypomania_bipolar_or_manicdepression_numeric,
     mhd.type_psychosis_psychotic_illness_numeric,
@@
   )
-```
-
-Overlap between self-report schizophrenia and bipolar disorder
-+++CH: Check overlap between schizophrenia group and bipolar disorder
-++KT: Only 63 with comorbid self-report bipolar disorder and schizophrenia. More likely to have shared symptoms, less likely to have confirmed diagnoses of both. Could be too severe to be in GLAD?
-```{r glad mhd bipolar_and_schizophrenia_numeric}
-glad.mhd.raw.id <- glad.mhd.raw.id %>%
-  mutate(
-    bipolar_and_schizophrenia_numeric =
-      case_when(
-        psychotic_disorders_numeric == 1 &
-          mhd.mania_hypomania_bipolar_or_manicdepression == 1 ~ 0,
-        psychotic_disorders_numeric == 1 &
-          mhd.mania_hypomania_bipolar_or_manicdepression == 1 ~ 1,
-        psychotic_disorders_numeric == 1 &
-          mhd.mania_hypomania_bipolar_or_manicdepression == 0 ~ 2,
-        psychotic_disorders_numeric == 0 &
-          mhd.mania_hypomania_bipolar_or_manicdepression == 1 ~ 3
-      )
-  )
-
-glad.mhd.raw.id <- glad.mhd.raw.id %>%
-  mutate(
-    bipolar_and_schizophrenia =
-      recode_factor(bipolar_and_schizophrenia_numeric,
-                    "0" = "No psychotic or bipolar disorder",
-                    "1" = "Psychotic and bipolar disorder",
-                    "2" = "Only psychotic disorder",
-                    "2" = "Only bipolar disorder",
-                    missing = NA_character_
-                    )
-  )
-
-glad.mhd.raw.id %>%
-  freq(bipolar_and_schizophrenia,
-       cumul = F)
 ```

### 2020-08-07 PANCHANGE_data_preprocessing2020-07-15.Rmd
added total disorder count and comorbidity count

@@
 glad.mhd.raw.id %>%
-  freq(personality_cluster_a)
+  freq(personality_cluster_a,
+       cumul = F)
 ```
@@
 glad.mhd.raw.id %>%
-  freq(personality_cluster_b)
+  freq(personality_cluster_b,
+       cumul = F)
 ```
@@
 glad.mhd.raw.id %>%
-  freq(personality_cluster_c)
+  freq(personality_cluster_c,
+       cumul = F)
 ```
@@
 glad.mhd.raw.id %>%
-  freq(control)
+  freq(control,
+       cumul = F)
+```
+
+Total disorder count
+```{r disorders_total_count}
+disorder_columns <- c(
+    "depressive_disorders_numeric",
+    "anxiety_disorders_numeric",
+    "eating_disorders_numeric",
+    "obsessive_compulsive_disorders_numeric",
+    "psychotic_disorders_numeric",
+    "mhd.mania_hypomania_bipolar_or_manicdepression_numeric",
+    "mhd.posttraumatic_stress_disorder_ptsd_numeric",
+    "mhd.autism_aspergers_or_autistic_spectrum_disorder_numeric",
+    "mhd.attention_deficit_hyperactivity_disorder_numeric",
+    "mhd.personality_disorder_numeric"
+)
+
+glad.mhd.raw.id <- glad.mhd.raw.id %>%
+  select(all_of(disorder_columns)) %>%
+  mutate(
+    disorders_total_count =
+      rowSums(.)
+  )
+
+glad.mhd.raw.id %>%
+  freq(disorders_total_count,
+       cumul = F)
+```
+
+Comorbidity count
+```{r}
+glad.mhd.raw.id <- glad.mhd.raw.id %>%
+  mutate(
+    comorbidity_total_count = 
+      case_when(
+        disorders_total_count == 1 ~ 0,
+        disorders_total_count > 1 ~ disorders_total_count - 1
+  )
+  )
+
+glad.mhd.raw.id %>%
+  freq(comorbidity_total_count,
+       cumul = F)
 ```

### 2020-08-07 PANCHANGE_data_preprocessing2020-07-15.Rmd
added the additional mhd columns to the finalised mhd tibble

@@
 glad.mhd.raw.id <- glad.mhd.raw.id %>%
-  select(all_of(disorder_columns)) %>%
   mutate(
     disorders_total_count =
-      rowSums(.)
+      rowSums(.[disorder_columns])
   )
@@
 Comorbidity count
-```{r}
+```{r cormorbidity_total_count}
 glad.mhd.raw.id <- glad.mhd.raw.id %>%
   mutate(
-    comorbidity_total_count = 
+    comorbidity_total_count_numeric = 
       case_when(
@@
 glad.mhd.raw.id %>%
-  freq(comorbidity_total_count,
+  freq(comorbidity_total_count_numeric,
+       cumul = F)
+```
+
+```{r}
+glad.mhd.raw.id <- glad.mhd.raw.id %>%
+  mutate(
+    comorbidity_total_count_factor_numeric =
+      case_when(
+    comorbidity_total_count_numeric == "0" ~ 0,
+    comorbidity_total_count_numeric == "1" ~ 1,
+    comorbidity_total_count_numeric == "2" ~ 2,
+    comorbidity_total_count_numeric > 2 ~ 3
+    )
+  )
+
+glad.mhd.raw.id <- glad.mhd.raw.id %>%
+  mutate(
+    comorbidity_total_count_factor =
+      recode_factor(comorbidity_total_count_factor_numeric,
+                    "0" = "No comorbidity",
+                    "1" = "1 comorbid disoder",
+                    "2" = "2 comorbid disoders",
+                    "3" = "3+ comorbid disoder",
+                    missing = NA_character_
+                    )
+  )
+
+glad.mhd.raw.id %>%
+  freq(comorbidity_total_count_factor,
        cumul = F)
@@
     personality_cluster_c_numeric,
-    personality_cluster_c
+    personality_cluster_c,
+    depression_and_anxiety_numeric,
+    depression_and_anxiety,
+    restricting_vs_binge_eating_eating_disorders_numeric,
+    restricting_vs_binge_eating_eating_disorders,
+    bipolar_and_schizophrenia_numeric,
+    bipolar_and_schizophrenia,
+    control_numeric,
+    control,
+    disorders_total_count,
+    comorbidity_total_count_numeric,
+    comorbidity_total_count_factor_numeric,
+    comorbidity_total_count_factor
     )

### 2020-08-07 PANCHANGE_data_preprocessing2020-07-15.Rmd
added .numeric to the ocir

@@
     ID, # ID
-    pcl.stressful_experience_repeated_images_prepan_numeric = pcl.stressful_experience_repeated_images_numeric,
     pcl.stressful_experience_repeated_images_prepan = pcl.stressful_experience_repeated_images,
-    pcl.stressful_experience_upset_reminded_prepan_numeric = pcl.stressful_experience_upset_reminded_numeric,
     pcl.stressful_experience_upset_reminded_prepan = pcl.stressful_experience_upset_reminded,
-    pcl.stressful_situation_avoiding_activities_prepan_numeric = pcl.stressful_situation_avoiding_activities_numeric,
     pcl.stressful_situation_avoiding_activities_prepan = pcl.stressful_situation_avoiding_activities,
-    pcl.cut_people_feeling_distant_prepan_numeric = pcl.cut_people_feeling_distant_numeric,
     pcl.cut_people_feeling_distant_prepan = pcl.cut_people_feeling_distant,
-    pcl.feeling_irritable_or_having_angry_outbursts_prepan_numeric = pcl.feeling_irritable_or_having_angry_outbursts_numeric,
     pcl.feeling_irritable_or_having_angry_outbursts_prepan = pcl.feeling_irritable_or_having_angry_outbursts,
-    pcl.difficulty_concentrating_prepan_numeric = pcl.difficulty_concentrating_numeric,
-    pcl.difficulty_concentratin_prepan = pcl.difficulty_concentrating
+    pcl.difficulty_concentrating_prepan = pcl.difficulty_concentrating
   ) %>%
+  add_numeric(., exclude = exclude_cols) %>%
   mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
@@
     phq.moving_fidgety_noticed_opposite_prepan = phq.moving_fidgety_noticed_opposite,
-    phq.dead_hurting_thoughts_prepan = phq.dead_hurting_thoughts,
-    phq.little_interest_or_pleasure_in_doing_things_prepan_numeric = phq.little_interest_or_pleasure_in_doing_things_numeric,
-    phq.feeling_down_depressed_or_hopeless_prepan_numeric = phq.feeling_down_depressed_or_hopeless_numeric,
-    phq.staying_asleep_sleeping_trouble_prepan_numeric = phq.staying_asleep_sleeping_trouble_numeric,
-    phq.feeling_tired_or_having_little_energy_prepan_numeric = phq.feeling_tired_or_having_little_energy_numeric,
-    phq.poor_appetite_or_overeating_prepan_numeric = phq.poor_appetite_or_overeating_numeric,
-    phq.feeling_bad_failure_family_prepan_numeric = phq.feeling_bad_failure_family_numeric,
-    phq.trouble_concentrating_reading_newspaper_prepan_numeric = phq.trouble_concentrating_reading_newspaper_numeric,
-    phq.moving_fidgety_noticed_opposite_prepan_numeric = phq.moving_fidgety_noticed_opposite_numeric,
-    phq.dead_hurting_thoughts_prepan_numeric = phq.dead_hurting_thoughts_numeric
+    phq.dead_hurting_thoughts_prepan = phq.dead_hurting_thoughts
   ) %>%
+  add_numeric(., exclude = exclude_cols) %>%
   mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
@@
 ```{r glad ocir cols}
-glad.ocir.raw <- readRDS(file = paste0(data.raw_path, "/2020-08-03/glad/ocir_glad.rds"))
+glad.ocir.raw <- readRDS(file = paste0(data.raw_path, "/glad/ocir_glad.rds"))
 dim(glad.ocir.raw)
@@
   ) %>%
+  add_numeric(., exclude = exclude_cols) %>%
   mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables

### 2020-08-07 PANCHANGE_data_preprocessing2020-07-15.Rmd
corrected the coping and the ocir file path

@@
 ocir.items_prepan = c(
-  "ocir.i_repeatedly_check_doors_windows_drawers_etc_prepan",
-  "ocir.arranged_things_change_upset_prepan",
-  "ocir.repeat_feel_numbers_prepan",
-  "ocir.clean_simply_wash_feel_prepan",
-  "ocir.mind_upset_unpleasant_thoughts_prepan",
-  "ocir.afraid_avoid_throwing_things_prepan",
-  "ocir.light_switches_water_taps_prepan",
-  "ocir.arranged_things_prepan",
-  "ocir.good_feel_bad_numbers_prepan",
-  "ocir.hands_longer_wash_prepan",
-  "ocir.saved_things_prepan",
-  "ocir.frequently_difficulty_rid_nasty_prepan",
-  "ocir.i_check_things_more_often_than_necessary_prepan",
-  "ocir.arranged_properly_objects_upset_prepan",
-  "ocir.feel_compelled_count_things_prepan",
-  "ocir.strangers_touch_touched_difficult_prepan",
-  "ocir.control_difficult_find_thoughts_prepan",
-  "ocir.i_collect_things_i_dont_need_prepan"
+  "ocir.i_repeatedly_check_doors_windows_drawers_etc_prepan_numeric",
+  "ocir.arranged_things_change_upset_prepan_numeric",
+  "ocir.repeat_feel_numbers_prepan_numeric",
+  "ocir.clean_simply_wash_feel_prepan_numeric",
+  "ocir.mind_upset_unpleasant_thoughts_prepan_numeric",
+  "ocir.afraid_avoid_throwing_things_prepan_numeric",
+  "ocir.light_switches_water_taps_prepan_numeric",
+  "ocir.arranged_things_prepan_numeric",
+  "ocir.good_feel_bad_numbers_prepan_numeric",
+  "ocir.hands_longer_wash_prepan_numeric",
+  "ocir.saved_things_prepan_numeric",
+  "ocir.frequently_difficulty_rid_nasty_prepan_numeric",
+  "ocir.i_check_things_more_often_than_necessary_prepan_numeric",
+  "ocir.arranged_properly_objects_upset_prepan_numeric",
+  "ocir.feel_compelled_count_things_prepan_numeric",
+  "ocir.strangers_touch_touched_difficult_prepan_numeric",
+  "ocir.control_difficult_find_thoughts_prepan_numeric",
+  "ocir.i_collect_things_i_dont_need_prepan_numeric"
   )

### 2020-08-07 PANCHANGE_data_preprocessing2020-07-15.Rmd
read in of coping ocir, phq, gad, and pcl

@@
     ID, # ID
+    phq.problems_made_difficult_care, # Impairment
+    phq.pandemic_felt_feelings, # Comparison to before the pandemic (retro)
     phq.little_interest_or_pleasure_in_doing_things_prepan = phq.little_interest_or_pleasure_in_doing_things,
@@
 ```{r coping glad gad cols}
-coping.glad.gad.raw <- readRDS(file = paste0(data.raw_path,"/coping_glad/gad_coping_glad.rds"))
+coping.glad.gad.raw <- readRDS(file = paste0(data.raw_path,"/glad/gad_coping_glad.rds"))
 dim(coping.glad.gad.raw)
@@
     startDate.coping.glad = startDate,
-    gad.feeling_nervous_anxious_or_on_edge_retro = gad7.feeling_nervous_anxious_or_on_edge,
-    gad.control_worrying_stop_retro = gad7.control_worrying_stop,
-    gad.worrying_too_much_about_different_things_retro = gad7.worrying_too_much_about_different_things,
-    gad.trouble_relaxing_retro = gad7.trouble_relaxing,
-    gad.sit_restless_hard_retro = gad7.sit_restless_hard,
-    gad.becoming_easily_annoyed_or_irritable_retro = gad7.becoming_easily_annoyed_or_irritable,
-    gad.awful_feeling_afraid_happen_retro = gad7.awful_feeling_afraid_happen,
-    gad.feeling_nervous_anxious_or_on_edge_base = gad7.feeling_nervous_anxious_or_on_edge.1,
-    gad.control_worrying_stop_base = gad7.control_worrying_stop.1,
-    gad.worrying_too_much_about_different_things_base = gad7.worrying_too_much_about_different_things.1,
-    gad.trouble_relaxing_base = gad7.trouble_relaxing.1,
-    gad.sit_restless_hard_base = gad7.sit_restless_hard.1,
-    gad.becoming_easily_annoyed_or_irritable_base = gad7.becoming_easily_annoyed_or_irritable.1,
-    gad.awful_feeling_afraid_happen_base = gad7.awful_feeling_afraid_happen.1,
-    gad.feeling_nervous_anxious_or_on_edge_retro_numeric = gad7.feeling_nervous_anxious_or_on_edge_numeric,
-    gad.control_worrying_stop_retro_numeric = gad7.control_worrying_stop_numeric,
-    gad.worrying_too_much_about_different_things_retro_numeric = gad7.worrying_too_much_about_different_things_numeric,
-    gad.trouble_relaxing_retro_numeric = gad7.trouble_relaxing_numeric,
-    gad.sit_restless_hard_retro_numeric = gad7.sit_restless_hard_numeric,
-    gad.becoming_easily_annoyed_or_irritable_retro_numeric = gad7.becoming_easily_annoyed_or_irritable_numeric,
-    gad.awful_feeling_afraid_happen_retro_numeric = gad7.awful_feeling_afraid_happen_numeric,
-    gad.feeling_nervous_anxious_or_on_edge_base_numeric = gad7.feeling_nervous_anxious_or_on_edge.1_numeric,
-    gad.control_worrying_stop_base_numeric = gad7.control_worrying_stop.1_numeric,
-    gad.worrying_too_much_about_different_things_base_numeric = gad7.worrying_too_much_about_different_things.1_numeric,
-    gad.trouble_relaxing_base_numeric = gad7.trouble_relaxing.1_numeric,
-    gad.sit_restless_hard_base_numeric = gad7.sit_restless_hard.1_numeric,
-    gad.becoming_easily_annoyed_or_irritable_base_numeric = gad7.becoming_easily_annoyed_or_irritable.1_numeric,
-    gad.awful_feeling_afraid_happen_base_numeric = gad7.awful_feeling_afraid_happen.1_numeric
+    gad.problems_made_difficult_care, # Impairment
+    gad.pandemic_felt_feelings, # Comparison to before the pandemic (retro)
+    gad.feeling_nervous_anxious_or_on_edge_retro = gad.feeling_nervous_anxious_or_on_edge,
+    gad.control_worrying_stop_retro = gad.control_worrying_stop,
+    gad.worrying_too_much_about_different_things_retro = gad.worrying_too_much_about_different_things,
+    gad.trouble_relaxing_retro = gad.trouble_relaxing,
+    gad.sit_restless_hard_retro = gad.sit_restless_hard,
+    gad.becoming_easily_annoyed_or_irritable_retro = gad.becoming_easily_annoyed_or_irritable,
+    gad.awful_feeling_afraid_happen_retro = gad.awful_feeling_afraid_happen,
+    gad.feeling_nervous_anxious_or_on_edge_base = gad.feeling_nervous_anxious_or_on_edge.1,
+    gad.control_worrying_stop_base = gad.control_worrying_stop.1,
+    gad.worrying_too_much_about_different_things_base = gad.worrying_too_much_about_different_things.1,
+    gad.trouble_relaxing_base = gad.trouble_relaxing.1,
+    gad.sit_restless_hard_base = gad.sit_restless_hard.1,
+    gad.becoming_easily_annoyed_or_irritable_base = gad.becoming_easily_annoyed_or_irritable.1,
+    gad.awful_feeling_afraid_happen_base = gad.awful_feeling_afraid_happen.1
   ) %>%
+  add_numeric(., exclude = exclude_cols) %>%
   mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
@@
 ```{r coping glad pcl cols}
-coping.glad.pcl.raw <- readRDS(file = paste0(data.raw_path,"/coping_glad/pcl_coping_glad.rds"))
+coping.glad.pcl.raw <- readRDS(file = paste0(data.raw_path,"/glad/pcl_coping_glad.rds"))
 dim(coping.glad.pcl.raw)
@@
 ```{r coping glad phq cols}
-coping.glad.phq.raw <- readRDS(file = paste0(data.raw_path, "/coping_glad/phq_coping_glad.rds"))
+coping.glad.phq.raw <- readRDS(file = paste0(data.raw_path, "/glad/phq_coping_glad.rds"))
 dim(coping.glad.phq.raw)

### 2020-08-07 PANCHANGE_data_preprocessing2020-07-15.Rmd
read in of coping ocir, phq, gad, and pcl 2

@@
     ID, # ID
-    pcl.stressful_experience_repeated_images_base_numeric = pcl6.stressful_experience_repeated_images_numeric,
-    pcl.stressful_experience_repeated_images_base = pcl6.stressful_experience_repeated_images,
-    pcl.stressful_experience_upset_reminded_base_numeric = pcl6.stressful_experience_upset_reminded_numeric,
-    pcl.stressful_experience_upset_reminded_base = pcl6.stressful_experience_upset_reminded,
-    pcl.stressful_situation_avoiding_activities_base_numeric = pcl6.avoiding_activities_stressful_experience_numeric, # differ to GLAD prepan
-    pcl.stressful_situation_avoiding_activities_base = pcl6.avoiding_activities_stressful_experience, # differ to GLAD prepan
-    pcl.cut_people_feeling_distant_base_numeric = pcl6.cut_people_feeling_distant_numeric,
-    pcl.cut_people_feeling_distant_base = pcl6.cut_people_feeling_distant,
-    pcl.feeling_irritable_or_having_angry_outbursts_base_numeric = pcl6.feeling_irritable_or_having_angry_outbursts_numeric,
-    pcl.feeling_irritable_or_having_angry_outbursts_base = pcl6.feeling_irritable_or_having_angry_outbursts,
-    pcl.difficulty_concentrating_base_numeric = pcl6.difficulty_concentrating_numeric,
-    pcl.difficulty_concentratin_base = pcl6.difficulty_concentrating,
-    pcl.stressful_experience_repeated_images_retro_numeric = pcl6.stressful_experience_repeated_images.1_numeric,
-    pcl.stressful_experience_repeated_images_retro = pcl6.stressful_experience_repeated_images.1,
-    pcl.stressful_experience_upset_reminded_retro_numeric = pcl6.stressful_experience_upset_reminded.1_numeric,
-    pcl.stressful_experience_upset_reminded_retro = pcl6.stressful_experience_upset_reminded.1,
-    pcl.stressful_situation_avoiding_activities_retro_numeric = pcl6.avoiding_activities_stressful_experience.1_numeric,
-    pcl.stressful_situation_avoiding_activities_retro = pcl6.avoiding_activities_stressful_experience.1,
-    pcl.cut_people_feeling_distant_retro_numeric = pcl6.cut_people_feeling_distant.1_numeric,
-    pcl.cut_people_feeling_distant_retro = pcl6.cut_people_feeling_distant.1,
-    pcl.feeling_irritable_or_having_angry_outbursts_retro_numeric = pcl6.feeling_irritable_or_having_angry_outbursts.1_numeric,
-    pcl.feeling_irritable_or_having_angry_outbursts_retro = pcl6.feeling_irritable_or_having_angry_outbursts.1,
-    pcl.difficulty_concentrating_retro_numeric = pcl6.difficulty_concentrating.1_numeric,
-    pcl.difficulty_concentrating_retro = pcl6.difficulty_concentrating.1
+    pcl.stressful_experience_repeated_images_base = pcl.stressful_experience_repeated_images,
+    pcl.stressful_experience_upset_reminded_base = pcl.stressful_experience_upset_reminded, # differ to GLAD prepan
+    pcl.stressful_situation_avoiding_activities_base = pcl.avoiding_activities_stressful_experience, # differ to GLAD prepan
+    pcl.cut_people_feeling_distant_base = pcl.cut_people_feeling_distant,
+    pcl.feeling_irritable_or_having_angry_outbursts_base = pcl.feeling_irritable_or_having_angry_outbursts,
+    pcl.difficulty_concentrating_base = pcl.difficulty_concentrating,
+    pcl.stressful_experience_repeated_images_retro = pcl.stressful_experience_repeated_images.1,
+    pcl.stressful_experience_upset_reminded_retro = pcl.stressful_experience_upset_reminded.1,
+    pcl.stressful_situation_avoiding_activities_retro = pcl.avoiding_activities_stressful_experience.1,
+    pcl.cut_people_feeling_distant_retro = pcl.cut_people_feeling_distant.1,
+    pcl.feeling_irritable_or_having_angry_outbursts_retro = pcl.feeling_irritable_or_having_angry_outbursts.1,
+    pcl.difficulty_concentrating_retro = pcl.difficulty_concentrating.1
   ) %>%
+  add_numeric(., exclude = exclude_cols) %>%
   mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
@@
     ID, # ID
-    phq.little_interest_or_pleasure_in_doing_things_retro = phq9.little_interest_or_pleasure_in_doing_things,
-    phq.feeling_down_depressed_or_hopeless_retro = phq9.feeling_down_depressed_or_hopeless,
-    phq.staying_asleep_sleeping_trouble_retro = phq9.staying_asleep_sleeping_trouble,
-    phq.feeling_tired_or_having_little_energy_retro = phq9.feeling_tired_or_having_little_energy,
-    phq.poor_appetite_or_overeating_retro = phq9.poor_appetite_or_overeating,
-    phq.feeling_bad_failure_family_retro = phq9.feeling_bad_failure_family,
-    phq.trouble_concentrating_reading_newspaper_retro = phq9.trouble_concentrating_newspaper_reading, # differ GLAD prepandemic
-    phq.moving_fidgety_noticed_opposite_retro = phq9.moving_fidgety_opposite_slowly, # differ GLAD prepandemic
-    phq.dead_hurting_thoughts_retro = phq9.dead_hurting_thoughts,
-    phq.little_interest_or_pleasure_in_doing_things_retro_numeric = phq9.little_interest_or_pleasure_in_doing_things_numeric,
-    phq.feeling_down_depressed_or_hopeless_retro_numeric = phq9.feeling_down_depressed_or_hopeless_numeric,
-    phq.staying_asleep_sleeping_trouble_retro_numeric = phq9.staying_asleep_sleeping_trouble_numeric,
-    phq.feeling_tired_or_having_little_energy_retro_numeric = phq9.feeling_tired_or_having_little_energy_numeric,
-    phq.poor_appetite_or_overeating_retro_numeric = phq9.poor_appetite_or_overeating_numeric,
-    phq.feeling_bad_failure_family_retro_numeric = phq9.feeling_bad_failure_family_numeric,
-    phq.trouble_concentrating_reading_newspaper_retro_numeric = phq9.trouble_concentrating_newspaper_reading_numeric, # differ GLAD prepandemic
-    phq.moving_fidgety_noticed_opposite_retro_numeric = phq9.moving_fidgety_opposite_slowly_numeric, # differ GLAD prepandemic
-    phq.dead_hurting_thoughts_retro_numeric = phq9.dead_hurting_thoughts_numeric,
-    phq.little_interest_or_pleasure_in_doing_things_base = phq9.little_interest_or_pleasure_in_doing_things.1,
-    phq.feeling_down_depressed_or_hopeless_base = phq9.feeling_down_depressed_or_hopeless.1,
-    phq.staying_asleep_sleeping_trouble_base = phq9.staying_asleep_sleeping_trouble.1,
-    phq.feeling_tired_or_having_little_energy_base = phq9.feeling_tired_or_having_little_energy.1,
-    phq.poor_appetite_or_overeating_base = phq9.poor_appetite_or_overeating.1,
-    phq.feeling_bad_failure_family_base = phq9.feeling_bad_failure_family.1,
-    phq.trouble_concentrating_reading_newspaper_base = phq9.trouble_concentrating_newspaper_reading.1, # differ GLAD prepandemic
-    phq.moving_fidgety_noticed_opposite_base = phq9.moving_fidgety_opposite_slowly.1, # differ GLAD prepandemic
-    phq.dead_hurting_thoughts_base = phq9.dead_hurting_thoughts.1,
-    phq.little_interest_or_pleasure_in_doing_things_base_numeric = phq9.little_interest_or_pleasure_in_doing_things.1_numeric,
-    phq.feeling_down_depressed_or_hopeless_base_numeric = phq9.feeling_down_depressed_or_hopeless.1_numeric,
-    phq.staying_asleep_sleeping_trouble_base_numeric = phq9.staying_asleep_sleeping_trouble.1_numeric,
-    phq.feeling_tired_or_having_little_energy_base_numeric = phq9.feeling_tired_or_having_little_energy.1_numeric,
-    phq.poor_appetite_or_overeating_base_numeric = phq9.poor_appetite_or_overeating.1_numeric,
-    phq.feeling_bad_failure_family_base_numeric = phq9.feeling_bad_failure_family.1_numeric,
-    phq.trouble_concentrating_reading_newspaper_base_numeric = phq9.trouble_concentrating_newspaper_reading.1_numeric, # differ GLAD prepandemic
-    phq.moving_fidgety_noticed_opposite_base_numeric = phq9.moving_fidgety_opposite_slowly.1_numeric, # differ GLAD prepandemic
-    phq.dead_hurting_thoughts_base_numeric = phq9.dead_hurting_thoughts_numeric
+    phq.problems_made_difficult_care,
+    phq.pandemic_felt_feelings,
+    phq.little_interest_or_pleasure_in_doing_things_retro = phq.little_interest_or_pleasure_in_doing_things,
+    phq.feeling_down_depressed_or_hopeless_retro = phq.feeling_down_depressed_or_hopeless,
+    phq.staying_asleep_sleeping_trouble_retro = phq.staying_asleep_sleeping_trouble,
+    phq.feeling_tired_or_having_little_energy_retro = phq.feeling_tired_or_having_little_energy,
+    phq.poor_appetite_or_overeating_retro = phq.poor_appetite_or_overeating,
+    phq.feeling_bad_failure_family_retro = phq.feeling_bad_failure_family,
+    phq.trouble_concentrating_reading_newspaper_retro = phq.trouble_concentrating_newspaper_reading, # differ GLAD prepandemic
+    phq.moving_fidgety_noticed_opposite_retro = phq.moving_fidgety_opposite_slowly, # differ GLAD prepandemic
+    phq.dead_hurting_thoughts_retro = phq.dead_hurting_thoughts,
+    phq.little_interest_or_pleasure_in_doing_things_base = phq.little_interest_or_pleasure_in_doing_things.1,
+    phq.feeling_down_depressed_or_hopeless_base = phq.feeling_down_depressed_or_hopeless.1,
+    phq.staying_asleep_sleeping_trouble_base = phq.staying_asleep_sleeping_trouble.1,
+    phq.feeling_tired_or_having_little_energy_base = phq.feeling_tired_or_having_little_energy.1,
+    phq.poor_appetite_or_overeating_base = phq.poor_appetite_or_overeating.1,
+    phq.feeling_bad_failure_family_base = phq.feeling_bad_failure_family.1,
+    phq.trouble_concentrating_reading_newspaper_base = phq.trouble_concentrating_newspaper_reading.1, # differ GLAD prepandemic
+    phq.moving_fidgety_noticed_opposite_base = phq.moving_fidgety_opposite_slowly.1, # differ GLAD prepandemic
+    phq.dead_hurting_thoughts_base = phq.dead_hurting_thoughts.1
   ) %>%
+  add_numeric(., exclude = exclude_cols) %>%
   mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
@@
     ID, # ID
+    ocir.felt_pandemic_feelings,
     ocir.i_repeatedly_check_doors_windows_drawers_etc_retro = ocir.i_repeatedly_check_doors_windows_drawers_etc.,

### 2020-08-07 PANCHANGE_data_preprocessing2020-07-15.Rmd
cleaning respiratory

@@
     ID, # ID
-    phq.problems_made_difficult_care, # Impairment
-    phq.pandemic_felt_feelings, # Comparison to before the pandemic (retro)
     phq.little_interest_or_pleasure_in_doing_things_prepan = phq.little_interest_or_pleasure_in_doing_things,
@@
     ID, # ID
-    ocir.felt_pandemic_feelings,
+    ocir.felt_pandemic_feelings, # Comparison to before the pandemic
     ocir.i_repeatedly_check_doors_windows_drawers_etc_retro = ocir.i_repeatedly_check_doors_windows_drawers_etc.,
@@
     Sample, # Sample
-    ID,
+    ID, # ID
     respiratory.breath_diarrhoea_fatigue_fever,
@@
     respiratory.results_antibody_test
-    # ID
   ) %>%
+  add_numeric(., exclude = exclude_cols) %>%
   mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
@@
 
-```{r create respiratory numeric variables}
-exclude_cols <- c("ID",
-                  "Sample")
-
-coping.glad.respiratory.raw.numeric <- add_numeric(coping.glad.respiratory.raw.id, exclude = exclude_cols)
-
-colnames(coping.glad.respiratory.raw.numeric)
-dim(coping.glad.respiratory.raw.numeric)
-dim(coping.glad.respiratory.raw.id)
-```
-
 #Distribution of likert scale COVID-19 symptoms in COPING
@@
 #persistent cough
-coping.glad.respiratory.raw.numeric %>%
+coping.glad.respiratory.raw.id %>%
   ggplot(
@@
 #severe fatigue
-coping.glad.respiratory.raw.numeric %>%
+coping.glad.respiratory.raw.id %>%
   ggplot(
@@
 #skipped meals
-coping.glad.respiratory.raw.numeric %>%
+coping.glad.respiratory.raw.id %>%
   ggplot(
@@
 percentage_pcough    # 0.3029762% of Menni et al(2020) have fatigue
-quantile(x = coping.glad.respiratory.raw.numeric$respiratory.persistent_cough_numeric, 
+quantile(x = coping.glad.respiratory.raw.id$respiratory.persistent_cough_numeric, 
          na.rm = TRUE, 
@@
 percentage_fatigue   # 0.08791204% of Menni et al(2020) have fatigue
-quantile(x = coping.glad.respiratory.raw.numeric$respiratory.feeling_tiredfatigued_numeric, 
+quantile(x = coping.glad.respiratory.raw.id$respiratory.feeling_tiredfatigued_numeric, 
          na.rm = TRUE, 
@@
 percentage_skipped_meals    # 0.192021% of Menni et al(2020) have fatigue
-quantile(x = coping.glad.respiratory.raw.numeric$respiratory.skipping_meals_because_you_felt_unwell_numeric, 
+quantile(x = coping.glad.respiratory.raw.id$respiratory.skipping_meals_because_you_felt_unwell_numeric, 
          na.rm = TRUE, 
@@
 #loss or smell or taste
-coping.glad.respiratory.raw.numeric <- coping.glad.respiratory.raw.numeric %>%
+coping.glad.respiratory.raw.id <- coping.glad.respiratory.raw.id %>%
   mutate(
@@
 #persistent cough
-coping.glad.respiratory.raw.numeric <- coping.glad.respiratory.raw.numeric %>%
+coping.glad.respiratory.raw.id <- coping.glad.respiratory.raw.id %>%
   mutate(
@@
 #fatigue
-coping.glad.respiratory.raw.numeric <- coping.glad.respiratory.raw.numeric %>%
+coping.glad.respiratory.raw.id <- coping.glad.respiratory.raw.id %>%
   mutate(
@@
 #skipped meals
-coping.glad.respiratory.raw.numeric <- coping.glad.respiratory.raw.numeric %>%
+coping.glad.respiratory.raw.id <- coping.glad.respiratory.raw.id %>%
   mutate(
@@
 ```{r frequencies of COVID binary symptoms}
-freq(coping.glad.respiratory.raw.numeric$respiratory.anosmia_binary)
-freq(coping.glad.respiratory.raw.numeric$respiratory.pcough_binary)
-freq(coping.glad.respiratory.raw.numeric$respiratory.fatigue_binary)
-freq(coping.glad.respiratory.raw.numeric$respiratory.skipped_meals_binary)
+freq(coping.glad.respiratory.raw.id$respiratory.anosmia_binary)
+freq(coping.glad.respiratory.raw.id$respiratory.pcough_binary)
+freq(coping.glad.respiratory.raw.id$respiratory.fatigue_binary)
+freq(coping.glad.respiratory.raw.id$respiratory.skipped_meals_binary)
 ```
@@
 ```{r clean respiratory dataset}
-coping.glad.respiratory <- coping.glad.respiratory.raw.numeric
+coping.glad.respiratory <- coping.glad.respiratory.raw.id
 

### 2020-08-07 PANCHANGE_data_preprocessing2020-07-15.Rmd
added half a year sign up difference coping and prepandemic

@@
 ```{r coping glad gad cleaning}
+exclude_cols_coping_glad <- c(
+  "Sample",
+  "ID",
+  "startDate.coping.glad"
+)
+
 coping.glad.gad.raw.id <- coping.glad.gad.raw %>%
@@
   ) %>%
-  add_numeric(., exclude = exclude_cols) %>%
+  add_numeric(., exclude = exclude_cols_coping_glad) %>%
   mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
@@
 ```{r coping glad ocir cols}
-coping.glad.ocir.raw <- readRDS(file = paste0(data.raw_path, "/2020-08-04/glad/ocir_coping_glad.rds"))
+coping.glad.ocir.raw <- readRDS(file = paste0(data.raw_path, "/glad/ocir_coping_glad.rds"))
 dim(coping.glad.ocir.raw)
@@
 
-table(dat.glad$over_one_year_time_diff_sign_up_coping)
+dat.glad %>%
+  freq(over_one_year_time_diff_sign_up_coping, cumul = F)
+```
+
+Proportion of people signed up over one year ago
+```{r eval=FALSE, include=FALSE}
+dat.glad <- dat.glad %>%
+  mutate(
+    over_half_a_year_time_diff_sign_up_coping_numeric =
+      as.numeric(
+        if_else(time_diff_sign_up_coping > 182.5, 1, 0
+                )
+      )
+  )
+
+dat.glad <- dat.glad %>%
+  mutate(
+    over_half_a_year_time_diff_sign_up_coping =
+      recode_factor(
+        over_half_a_year_time_diff_sign_up_coping_numeric,
+        "0" = "Sign up under half a year before COPING",
+        "1" = "Sign up over half a year before COPING"
+      )
+  )
+
+dat.glad %>%
+  freq(over_half_a_year_time_diff_sign_up_coping, cumul = F)
 ```

### 2020-08-07 PANCHANGE_data_preprocessing2020-07-15.Rmd
fixed the comment about anxiety and depression from Katie

@@
       case_when(
-        depressive_disorders_numeric == 1 &
-          anxiety_disorders_numeric == 1 ~ 0,
+        depressive_disorders_numeric == 0 &
+          anxiety_disorders_numeric == 0 ~ 0,
         depressive_disorders_numeric == 1 &

### 2020-08-07 PANCHANGE_data_preprocessing2020-07-15.Rmd
reducation of the missingness variable

@@
 #PHQ - baseline
-PHQ Missingness NAs per person - count and percentages
+PHQ Missingness NAs per person - count
 ```{r PHQ baseline missingness}
-dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
+coping.glad.phq.raw.id <- coping.glad.phq.raw.id %>%
   mutate(
@@
       rowSums(                       
-        is.na(dat.no.sex.no.gender.no.age.no.ibd # sum the rows that are NA
-          [,colnames(dat.no.sex.no.gender.no.age.no.ibd) #for all the rows and columns that are in the PHQ items at baseline
-           %in%
-             phq.items_base]
-        )
-    )
-  )
-
-freq(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_phq_base) #have a look at the frequency
-
-dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>% #NA per person as a percentage
-  mutate(
-    miss_pc_total_phq_base = 
-      na_per_person_phq_base/9 # NA per person divided by the amount of items
-  )
-
-freq(dat.no.sex.no.gender.no.age.no.ibd$miss_pc_total_phq_base)
+        is.na(.[phq.items_base])
+        )
+    )
+
+coping.glad.phq.raw.id %>%
+freq(na_per_person_phq_base, cumul = F) #have a look at the frequency
 ```

### 2020-08-07 PANCHANGE_data_preprocessing2020-07-15.Rmd
reducation of the missingness variable phq

@@
 
-##Missingness of questionnaire items
-#PHQ - baseline
-PHQ Missingness NAs per person - count
+# PHQ missingness (NAs per person)
+
+## baseline
 ```{r PHQ baseline missingness}
@@
 
-```{r PHQ baseline missingness 8 items}
-#We need to identify those who have all items APART from the suicide ideation item - to still include these individuals. 
-dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
-  mutate(
-    phq.base_cut_off = 
+We need to identify those who have all items APART from the suicide ideation item - to still include these individuals. 
+```{r PHQ base missingness 8 items}
+coping.glad.phq.raw.id <- coping.glad.phq.raw.id %>%
+  mutate(
+    phq.missing_only_suicide_item_base = 
       if_else(
-        na_per_person_phq_base == 1 & 
+        condition = na_per_person_phq_base == 1 & 
           is.na(phq.dead_hurting_thoughts_base_numeric), 
-        1,
-        0
-      )
-  )
-
-table(dat.no.sex.no.gender.no.age.no.ibd$phq.base_cut_off)
-```
-
-#PHQ - retrospective
-PHQ Missingness NAs per person - count and percentages
+        true = 1,
+        false = 0,
+        missing = NA_real_
+      )
+  )
+
+coping.glad.phq.raw.id %>%
+  freq(phq.missing_only_suicide_item_base,
+       cumul = F)
+```
+
+## retrospective
 ```{r PHQ retrospective missingness}
-dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
+coping.glad.phq.raw.id <- coping.glad.phq.raw.id %>%
   mutate(
@@
       rowSums(
-        is.na(dat.no.sex.no.gender.no.age.no.ibd # sum the rows that are NA
-          [,colnames(dat.no.sex.no.gender.no.age.no.ibd) #for all the rows and columns that are in the PHQ items at retroline
-           %in%
-             phq.items_retro]
-        )
-    )
-  )
-
-freq(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_phq_retro) #have a look at the frequency
-
-dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>% #NA per person as a percentage
-  mutate(
-    miss_pc_total_phq_retro = 
-      na_per_person_phq_retro/9 # NA per person divided by the amount of items
-  )
-
-freq(dat.no.sex.no.gender.no.age.no.ibd$miss_pc_total_phq_retro)
+        is.na(.[phq.items_retro])
+        )
+    )
+
+coping.glad.phq.raw.id %>%
+freq(na_per_person_phq_retro, cumul = F) #have a look at the frequency
 ```
@@
 ```{r PHQ retro missingness 8 items}
-#We need to identify those who have all items APART from the suicide ideation item - to still include these individuals. 
-dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
-  mutate(
-    phq.retro_cut_off = 
+coping.glad.phq.raw.id <- coping.glad.phq.raw.id %>%
+  mutate(
+    phq.missing_only_suicide_item_retro = 
       if_else(
-        na_per_person_phq_retro == 1 & 
+        condition = na_per_person_phq_retro == 1 & 
           is.na(phq.dead_hurting_thoughts_retro_numeric), 
-        1,
-        0
-      )
-  )
-
-table(dat.no.sex.no.gender.no.age.no.ibd$phq.retro_cut_off)
-```
-
-#PHQ - prepandemic
-PHQ Missingness NAs per person - count and percentages
+        true = 1,
+        false = 0,
+        missing = NA_real_
+      )
+  )
+
+coping.glad.phq.raw.id %>%
+  freq(phq.missing_only_suicide_item_retro,
+       cumul = F)
+```
+
+## prepandemic
 ```{r PHQ prepan missingness}
-dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
+glad.phq.raw.id <- glad.phq.raw.id %>%
   mutate(
@@
       rowSums(                       
-        is.na(dat.no.sex.no.gender.no.age.no.ibd # sum the rows that are NA
-          [,colnames(dat.no.sex.no.gender.no.age.no.ibd) #for all the rows and columns that are in the PHQ items at prepanline
-           %in%
-             phq.items_prepan]
-        )
-    )
-  )
-
-freq(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_phq_prepan) #have a look at the frequency
-
-dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>% #NA per person as a percentage
-  mutate(
-    miss_pc_total_phq_prepan = 
-      na_per_person_phq_prepan/9 # NA per person divided by the amount of items
-  )
-
-freq(dat.no.sex.no.gender.no.age.no.ibd$miss_pc_total_phq_prepan)
+        is.na(.[phq.items_prepan])
+        )
+    )
+
+glad.phq.raw.id %>%
+  freq(na_per_person_phq_prepan,
+       cumul = F)
 ```
@@
 ```{r PHQ prepan missingness 8 items}
-#We need to identify those who have all items APART from the suicide ideation item - to still include these individuals. 
-dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
-  mutate(
-    phq.prepan_cut_off = 
+glad.phq.raw.id <- glad.phq.raw.id %>%
+  mutate(
+    phq.missing_only_suicide_item_prepan = 
       if_else(
-        na_per_person_phq_prepan == 1 & 
+        condition = na_per_person_phq_prepan == 1 & 
           is.na(phq.dead_hurting_thoughts_prepan_numeric), 
-        1,
-        0
-      )
-  )
-
-table(dat.no.sex.no.gender.no.age.no.ibd$phq.prepan_cut_off)
-```
-
-Count for PHQ baseline, retrospective, and prepandemic missingness per person
-```{r count of people missing a number of items for PHQ}
-#baseline
-table(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_phq_base)
-#retrospective
-table(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_phq_retro)
-#pre-pandemic
-table(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_phq_prepan)
+        true = 1,
+        false = 0,
+        missing = NA_real_
+      )
+  )
+
+glad.phq.raw.id %>%
+  freq(phq.missing_only_suicide_item_prepan,
+       cumul = F)
 ```
@@
 PHQ
-The PHQ sum score is set to NA if they have more than one missing item, and it is not the last suicide ideation item (they do not meet the cut off criteria - phq.base_cut_off)
+The PHQ sum score is set to NA if they have more than one missing item, and it is not the last suicide ideation item (they do not meet the cut off criteria - phq.missing_only_suicide_item)
 ```{r sum score cut offs PHQ base}
@@
     phq.sum_score_base_full =
-      if_else(na_per_person_phq_base > 1 & phq.base_cut_off == 0,
+      if_else(na_per_person_phq_base > 1 & phq.missing_only_suicide_item == 0,
               NA_real_,

### 2020-08-10 PANCHANGE_data_preprocessing2020-07-15.Rmd
moved missigness in the place with the questionnaires

@@
 
+# PHQ missingness (NAs per person)
+
+## prepandemic
+```{r PHQ prepan missingness}
+glad.phq.raw.id <- glad.phq.raw.id %>%
+  mutate(
+    na_per_person_phq_prepan =         # variable for NA per person
+      rowSums(                       
+        is.na(.[phq.items_prepan])
+      )
+  )
+
+glad.phq.raw.id %>%
+  freq(na_per_person_phq_prepan,
+       cumul = F)
+```
+
+```{r PHQ prepan missingness 8 items}
+glad.phq.raw.id <- glad.phq.raw.id %>%
+  mutate(
+    phq.missing_only_suicide_item_prepan = 
+      if_else(
+        condition = na_per_person_phq_prepan == 1 & 
+          is.na(phq.dead_hurting_thoughts_prepan_numeric), 
+        true = 1,
+        false = 0,
+        missing = NA_real_
+      )
+  )
+
+glad.phq.raw.id %>%
+  freq(phq.missing_only_suicide_item_prepan,
+       cumul = F)
+```
+
 ```{r glad phq head}
@@
         )
+```
+
+# GAD missingness
+
+## baseline
+```{r GAD baseline missingness}
+coping.glad.gad.raw.id <- coping.glad.gad.raw.id %>%
+  mutate(
+    na_per_person_gad_base =         # variable for NA per person
+      rowSums(                       
+        is.na(.[gad.items_base])
+      )
+  )
+
+coping.glad.gad.raw.id %>%
+  freq(na_per_person_gad_base, cumul = F) #have a look at the frequency
+```
+
+We need to identify those who have all items APART from the suicide ideation item - to still include these individuals. 
+```{r GAD base missingness 8 items}
+coping.glad.gad.raw.id <- coping.glad.gad.raw.id %>%
+  mutate(
+    gad.missing_only_suicide_item_base = 
+      if_else(
+        condition = na_per_person_gad_base == 1 & 
+          is.na(gad.dead_hurting_thoughts_base_numeric), 
+        true = 1,
+        false = 0,
+        missing = NA_real_
+      )
+  )
+
+coping.glad.gad.raw.id %>%
+  freq(gad.missing_only_suicide_item_base,
+       cumul = F)
+```
+
+## retrospective
+```{r GAD retrospective missingness}
+coping.glad.gad.raw.id <- coping.glad.gad.raw.id %>%
+  mutate(
+    na_per_person_gad_retro =         # variable for NA per person
+      rowSums(
+        is.na(.[gad.items_retro])
+      )
+  )
+
+coping.glad.gad.raw.id %>%
+  freq(na_per_person_gad_retro, cumul = F) #have a look at the frequency
+```
+
+```{r GAD retro missingness 8 items}
+coping.glad.gad.raw.id <- coping.glad.gad.raw.id %>%
+  mutate(
+    gad.missing_only_suicide_item_retro = 
+      if_else(
+        condition = na_per_person_gad_retro == 1 & 
+          is.na(gad.dead_hurting_thoughts_retro_numeric), 
+        true = 1,
+        false = 0,
+        missing = NA_real_
+      )
+  )
+
+coping.glad.gad.raw.id %>%
+  freq(gad.missing_only_suicide_item_retro,
+       cumul = F)
 ```
@@
   )
+```
+
+# PHQ missigness
+
+## retrospective
+```{r PHQ retrospective missingness}
+coping.glad.phq.raw.id <- coping.glad.phq.raw.id %>%
+  mutate(
+    na_per_person_phq_retro =         # variable for NA per person
+      rowSums(
+        is.na(.[phq.items_retro])
+      )
+  )
+
+coping.glad.phq.raw.id %>%
+  freq(na_per_person_phq_retro, cumul = F) #have a look at the frequency
+```
+
+```{r PHQ retro missingness 8 items}
+coping.glad.phq.raw.id <- coping.glad.phq.raw.id %>%
+  mutate(
+    phq.missing_only_suicide_item_retro = 
+      if_else(
+        condition = na_per_person_phq_retro == 1 & 
+          is.na(phq.dead_hurting_thoughts_retro_numeric), 
+        true = 1,
+        false = 0,
+        missing = NA_real_
+      )
+  )
+
+coping.glad.phq.raw.id %>%
+  freq(phq.missing_only_suicide_item_retro,
+       cumul = F)
+```
+
+## baseline
+```{r PHQ baseline missingness}
+coping.glad.phq.raw.id <- coping.glad.phq.raw.id %>%
+  mutate(
+    na_per_person_phq_base =         # variable for NA per person
+      rowSums(                       
+        is.na(.[phq.items_base])
+      )
+  )
+
+coping.glad.phq.raw.id %>%
+  freq(na_per_person_phq_base, cumul = F) #have a look at the frequency
+```
+
+We need to identify those who have all items APART from the suicide ideation item - to still include these individuals. 
+```{r PHQ base missingness 8 items}
+coping.glad.phq.raw.id <- coping.glad.phq.raw.id %>%
+  mutate(
+    phq.missing_only_suicide_item_base = 
+      if_else(
+        condition = na_per_person_phq_base == 1 & 
+          is.na(phq.dead_hurting_thoughts_base_numeric), 
+        true = 1,
+        false = 0,
+        missing = NA_real_
+      )
+  )
+
+coping.glad.phq.raw.id %>%
+  freq(phq.missing_only_suicide_item_base,
+       cumul = F)
 ```
@@
 
-# PHQ missingness (NAs per person)
-
-## baseline
-```{r PHQ baseline missingness}
-coping.glad.phq.raw.id <- coping.glad.phq.raw.id %>%
-  mutate(
-    na_per_person_phq_base =         # variable for NA per person
-      rowSums(                       
-        is.na(.[phq.items_base])
-        )
-    )
-
-coping.glad.phq.raw.id %>%
-freq(na_per_person_phq_base, cumul = F) #have a look at the frequency
-```
-
-We need to identify those who have all items APART from the suicide ideation item - to still include these individuals. 
-```{r PHQ base missingness 8 items}
-coping.glad.phq.raw.id <- coping.glad.phq.raw.id %>%
-  mutate(
-    phq.missing_only_suicide_item_base = 
-      if_else(
-        condition = na_per_person_phq_base == 1 & 
-          is.na(phq.dead_hurting_thoughts_base_numeric), 
-        true = 1,
-        false = 0,
-        missing = NA_real_
-      )
-  )
-
-coping.glad.phq.raw.id %>%
-  freq(phq.missing_only_suicide_item_base,
-       cumul = F)
-```
-
-## retrospective
-```{r PHQ retrospective missingness}
-coping.glad.phq.raw.id <- coping.glad.phq.raw.id %>%
-  mutate(
-    na_per_person_phq_retro =         # variable for NA per person
-      rowSums(
-        is.na(.[phq.items_retro])
-        )
-    )
-
-coping.glad.phq.raw.id %>%
-freq(na_per_person_phq_retro, cumul = F) #have a look at the frequency
-```
-
-```{r PHQ retro missingness 8 items}
-coping.glad.phq.raw.id <- coping.glad.phq.raw.id %>%
-  mutate(
-    phq.missing_only_suicide_item_retro = 
-      if_else(
-        condition = na_per_person_phq_retro == 1 & 
-          is.na(phq.dead_hurting_thoughts_retro_numeric), 
-        true = 1,
-        false = 0,
-        missing = NA_real_
-      )
-  )
-
-coping.glad.phq.raw.id %>%
-  freq(phq.missing_only_suicide_item_retro,
-       cumul = F)
-```
-
-## prepandemic
-```{r PHQ prepan missingness}
-glad.phq.raw.id <- glad.phq.raw.id %>%
-  mutate(
-    na_per_person_phq_prepan =         # variable for NA per person
-      rowSums(                       
-        is.na(.[phq.items_prepan])
-        )
-    )
-
-glad.phq.raw.id %>%
-  freq(na_per_person_phq_prepan,
-       cumul = F)
-```
-
-```{r PHQ prepan missingness 8 items}
-glad.phq.raw.id <- glad.phq.raw.id %>%
-  mutate(
-    phq.missing_only_suicide_item_prepan = 
-      if_else(
-        condition = na_per_person_phq_prepan == 1 & 
-          is.na(phq.dead_hurting_thoughts_prepan_numeric), 
-        true = 1,
-        false = 0,
-        missing = NA_real_
-      )
-  )
-
-glad.phq.raw.id %>%
-  freq(phq.missing_only_suicide_item_prepan,
-       cumul = F)
-```
-
 #GAD - baseline

### 2020-08-10 PANCHANGE_data_preprocessing2020-07-15.Rmd
more missigness updates

--- 2020-08-07 PANCHANGE_data_preprocessing2020-07-15.Rmd
@@
 
+## Missigness
+
+## prepandemic
+```{r PCL prepan missingness}
+glad.pcl.raw.id <- glad.pcl.raw.id %>%
+  mutate(
+    na_per_person_pcl_prepan =         # variable for NA per person
+      rowSums(                       
+        is.na(.[pcl.items_prepan])
+      )
+  )
+
+glad.pcl.raw.id %>%
+  freq(na_per_person_pcl_prepan,
+       cumul = F)
+```
+
 ```{r glad pcl head}
@@
         )
+```
+
+# PHQ missingness (NAs per person)
+
+## prepandemic
+```{r PHQ prepan missingness}
+glad.phq.raw.id <- glad.phq.raw.id %>%
+  mutate(
+    na_per_person_phq_prepan =         # variable for NA per person
+      rowSums(                       
+        is.na(.[phq.items_prepan])
+      )
+  )
+
+glad.phq.raw.id %>%
+  freq(na_per_person_phq_prepan,
+       cumul = F)
+```
+
+```{r PHQ prepan missingness 8 items}
+glad.phq.raw.id <- glad.phq.raw.id %>%
+  mutate(
+    phq.missing_only_suicide_item_prepan = 
+      if_else(
+        condition = na_per_person_phq_prepan == 1 & 
+          is.na(phq.dead_hurting_thoughts_prepan_numeric), 
+        true = 1,
+        false = 0,
+        missing = NA_real_
+      )
+  )
+
+glad.phq.raw.id %>%
+  freq(phq.missing_only_suicide_item_prepan,
+       cumul = F)
 ```
@@
 
+Missigness
+
+baseline
+```{r coping gad baseline missingness}
+coping.glad.gad.raw.id <- coping.glad.gad.raw.id %>%
+  mutate(
+    na_per_person_gad_base =         # variable for NA per person
+      rowSums(                       
+        is.na(.[gad.items_base])
+      )
+  )
+
+coping.glad.gad.raw.id %>%
+  freq(na_per_person_gad_base, cumul = F) #have a look at the frequency
+```
+
+```{r coping gad retrospective missingness}
+coping.glad.gad.raw.id <- coping.glad.gad.raw.id %>%
+  mutate(
+    na_per_person_gad_retro =         # variable for NA per person
+      rowSums(
+        is.na(.[gad.items_retro])
+      )
+  )
+
+coping.glad.gad.raw.id %>%
+  freq(na_per_person_gad_retro, cumul = F) #have a look at the frequency
+```
+
 ```{r coping glad gad head}
@@
   )
+```
+
+PCL missingness (NAs per person)
+
+baseline
+```{r coping pcl baseline missingness}
+coping.glad.pcl.raw.id <- coping.glad.pcl.raw.id %>%
+  mutate(
+    na_per_person_pcl_base =         # variable for NA per person
+      rowSums(                       
+        is.na(.[pcl.items_base])
+      )
+  )
+
+coping.glad.pcl.raw.id %>%
+  freq(na_per_person_pcl_base, cumul = F) #have a look at the frequency
+```
+
+retrospective
+```{r coping pcl retrospective missingness}
+coping.glad.pcl.raw.id <- coping.glad.pcl.raw.id %>%
+  mutate(
+    na_per_person_pcl_retro =         # variable for NA per person
+      rowSums(
+        is.na(.[pcl.items_retro])
+      )
+  )
+
+coping.glad.pcl.raw.id %>%
+  freq(na_per_person_pcl_retro, cumul = F) #have a look at the frequency
 ```
@@
 
-# PHQ missingness (NAs per person)
-
-## baseline
-```{r PHQ baseline missingness}
-coping.glad.phq.raw.id <- coping.glad.phq.raw.id %>%
-  mutate(
-    na_per_person_phq_base =         # variable for NA per person
-      rowSums(                       
-        is.na(.[phq.items_base])
-        )
-    )
-
-coping.glad.phq.raw.id %>%
-freq(na_per_person_phq_base, cumul = F) #have a look at the frequency
-```
-
-We need to identify those who have all items APART from the suicide ideation item - to still include these individuals. 
-```{r PHQ base missingness 8 items}
-coping.glad.phq.raw.id <- coping.glad.phq.raw.id %>%
-  mutate(
-    phq.missing_only_suicide_item_base = 
-      if_else(
-        condition = na_per_person_phq_base == 1 & 
-          is.na(phq.dead_hurting_thoughts_base_numeric), 
-        true = 1,
-        false = 0,
-        missing = NA_real_
-      )
-  )
-
-coping.glad.phq.raw.id %>%
-  freq(phq.missing_only_suicide_item_base,
-       cumul = F)
-```
-
-## retrospective
-```{r PHQ retrospective missingness}
-coping.glad.phq.raw.id <- coping.glad.phq.raw.id %>%
-  mutate(
-    na_per_person_phq_retro =         # variable for NA per person
-      rowSums(
-        is.na(.[phq.items_retro])
-        )
-    )
-
-coping.glad.phq.raw.id %>%
-freq(na_per_person_phq_retro, cumul = F) #have a look at the frequency
-```
-
-```{r PHQ retro missingness 8 items}
-coping.glad.phq.raw.id <- coping.glad.phq.raw.id %>%
-  mutate(
-    phq.missing_only_suicide_item_retro = 
-      if_else(
-        condition = na_per_person_phq_retro == 1 & 
-          is.na(phq.dead_hurting_thoughts_retro_numeric), 
-        true = 1,
-        false = 0,
-        missing = NA_real_
-      )
-  )
-
-coping.glad.phq.raw.id %>%
-  freq(phq.missing_only_suicide_item_retro,
-       cumul = F)
-```
-
-## prepandemic
-```{r PHQ prepan missingness}
-glad.phq.raw.id <- glad.phq.raw.id %>%
-  mutate(
-    na_per_person_phq_prepan =         # variable for NA per person
-      rowSums(                       
-        is.na(.[phq.items_prepan])
-        )
-    )
-
-glad.phq.raw.id %>%
-  freq(na_per_person_phq_prepan,
-       cumul = F)
-```
-
-```{r PHQ prepan missingness 8 items}
-glad.phq.raw.id <- glad.phq.raw.id %>%
-  mutate(
-    phq.missing_only_suicide_item_prepan = 
-      if_else(
-        condition = na_per_person_phq_prepan == 1 & 
-          is.na(phq.dead_hurting_thoughts_prepan_numeric), 
-        true = 1,
-        false = 0,
-        missing = NA_real_
-      )
-  )
-
-glad.phq.raw.id %>%
-  freq(phq.missing_only_suicide_item_prepan,
-       cumul = F)
-```
-
-#GAD - baseline
-GAD Missingness NAs per person - count and percentages
-```{r gad baseline missingness}
-dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
-  mutate(
-    na_per_person_gad_base =         # variable for NA per person
-      rowSums(                       
-        is.na(dat.no.sex.no.gender.no.age.no.ibd # sum the rows that are NA
-          [,colnames(dat.no.sex.no.gender.no.age.no.ibd) #for all the rows and columns that are in the gad items at baseline
-           %in%
-             gad.items_base]
-        )
-    )
-  )
-
-freq(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_gad_base) #have a look at the frequency
-
-dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>% #NA per person as a percentage
-  mutate(
-    miss_pc_total_gad_base = 
-      na_per_person_gad_base/7 # NA per person divided by the amount of items
-  )
-
-freq(dat.no.sex.no.gender.no.age.no.ibd$miss_pc_total_gad_base)
-```
-
-#GAD - retrospective
-GAD Missingness NAs per person - count and percentages
-```{r gad retrospective missingness}
-dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
-  mutate(
-    na_per_person_gad_retro =         # variable for NA per person
-      rowSums(                       
-        is.na(dat.no.sex.no.gender.no.age.no.ibd # sum the rows that are NA
-          [,colnames(dat.no.sex.no.gender.no.age.no.ibd) #for all the rows and columns that are in the gad items at retroline
-           %in%
-             gad.items_retro]
-        )
-    )
-  )
-
-freq(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_gad_retro) #have a look at the frequency
-
-dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>% #NA per person as a percentage
-  mutate(
-    miss_pc_total_gad_retro = 
-      na_per_person_gad_retro/7 # NA per person divided by the amount of items
-  )
-
-freq(dat.no.sex.no.gender.no.age.no.ibd$miss_pc_total_gad_retro)
-```
-
-#GAD - prepandemic
-GAD Missingness NAs per person - count and percentages
-```{r gad prepan missingness}
-dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
-  mutate(
-    na_per_person_gad_prepan =         # variable for NA per person
-      rowSums(                       
-        is.na(dat.no.sex.no.gender.no.age.no.ibd # sum the rows that are NA
-          [,colnames(dat.no.sex.no.gender.no.age.no.ibd) #for all the rows and columns that are in the gad items at prepanline
-           %in%
-             gad.items_prepan]
-        )
-    )
-  )
-
-freq(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_gad_prepan) #have a look at the frequency
-
-dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>% #NA per person as a percentage
-  mutate(
-    miss_pc_total_gad_prepan = 
-      na_per_person_gad_prepan/7 # NA per person divided by the amount of items
-  )
-
-freq(dat.no.sex.no.gender.no.age.no.ibd$miss_pc_total_gad_prepan)
-```
-
-Count for gad baseline, retrospective, and prepandemic missingness per person
-```{r count of people missing a number of items for gad}
-#baseline
-table(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_gad_base)
-#retrospective
-table(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_gad_retro)
-#pre-pandemic
-table(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_gad_prepan)
-```
-
 #PCL - baseline

### 2020-08-10 PANCHANGE_data_preprocessing2020-07-15.Rmd
ocir coping  missigness updates

@@
 
-# PHQ missigness
-
-## retrospective
-```{r PHQ retrospective missingness}
+missigness
+
+retrospective
+```{r coping phq retro missingness}
 coping.glad.phq.raw.id <- coping.glad.phq.raw.id %>%
@@
 
-```{r PHQ retro missingness 8 items}
+```{r coping phq retro missingness 8 items}
 coping.glad.phq.raw.id <- coping.glad.phq.raw.id %>%
@@
 
-## baseline
-```{r PHQ baseline missingness}
+baseline
+```{r coping phq base missingness}
 coping.glad.phq.raw.id <- coping.glad.phq.raw.id %>%
@@
 We need to identify those who have all items APART from the suicide ideation item - to still include these individuals. 
-```{r PHQ base missingness 8 items}
+```{r coping phq base missingness 8 items}
 coping.glad.phq.raw.id <- coping.glad.phq.raw.id %>%
@@
 
+missigness
+
+retrospective
+```{r coping ocir retro missingness}
+coping.glad.ocir.raw.id <- coping.glad.ocir.raw.id %>%
+  mutate(
+    na_per_person_ocir_retro =         # variable for NA per person
+      rowSums(
+        is.na(.[ocir.items_retro])
+      )
+  )
+
+coping.glad.ocir.raw.id %>%
+  freq(na_per_person_ocir_retro, cumul = F) #have a look at the frequency
+```
+
+baseline
+```{r coping ocir base missingness}
+coping.glad.ocir.raw.id <- coping.glad.ocir.raw.id %>%
+  mutate(
+    na_per_person_ocir_base =         # variable for NA per person
+      rowSums(                       
+        is.na(.[ocir.items_base])
+      )
+  )
+
+coping.glad.ocir.raw.id %>%
+  freq(na_per_person_ocir_base, cumul = F) #have a look at the frequency
+```
+
 ```{r coping glad ocir head}

### 2020-08-10 PANCHANGE_data_preprocessing2020-07-15.Rmd
ocir prepand missigness added

@@
 
-## Missigness
-
-## prepandemic
-```{r PCL prepan missingness}
+Missigness
+
+prepandemic
+```{r pcl prepan missingness}
 glad.pcl.raw.id <- glad.pcl.raw.id %>%
@@
 
-# PHQ missingness (NAs per person)
-
-## prepandemic
-```{r PHQ prepan missingness}
+PHQ missingness (NAs per person)
+
+prepandemic
+```{r phq prepan missingness}
 glad.phq.raw.id <- glad.phq.raw.id %>%
@@
 
-```{r PHQ prepan missingness 8 items}
+```{r phq prepan missingness 8 items}
 glad.phq.raw.id <- glad.phq.raw.id %>%
@@
         )
+```
+
+prepandemic
+```{r ocir prepan missingness}
+glad.ocir.raw.id <- glad.ocir.raw.id %>%
+  mutate(
+    na_per_person_ocir_prepan =         # variable for NA per person
+      rowSums(                       
+        is.na(.[ocir.items_prepan])
+      )
+  )
+
+glad.ocir.raw.id %>%
+  freq(na_per_person_ocir_prepan,
+       cumul = F)
 ```

### 2020-08-10 PANCHANGE_data_preprocessing2020-07-15.Rmd
deleted old missigness chunks

@@
 
-#PCL - baseline
-PCL Missingness NAs per person - count and percentages
-```{r pcl baseline missingness}
-dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
-  mutate(
-    na_per_person_pcl_base =         # variable for NA per person
-      rowSums(                       
-        is.na(dat.no.sex.no.gender.no.age.no.ibd # sum the rows that are NA
-          [,colnames(dat.no.sex.no.gender.no.age.no.ibd) #for all the rows and columns that are in the pcl items at baseline
-           %in%
-             pcl.items_base]
-        )
-    )
-  )
-
-freq(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_pcl_base) #have a look at the frequency
-
-dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>% #NA per person as a percentage
-  mutate(
-    miss_pc_total_pcl_base = 
-      na_per_person_pcl_base/6 # NA per person divided by the amount of items
-  )
-
-freq(dat.no.sex.no.gender.no.age.no.ibd$miss_pc_total_pcl_base)
-```
-
-#PCL - retrospective
-PCL Missingness NAs per person - count and percentages
-```{r pcl retrospective missingness}
-dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
-  mutate(
-    na_per_person_pcl_retro =         # variable for NA per person
-      rowSums(                       
-        is.na(dat.no.sex.no.gender.no.age.no.ibd # sum the rows that are NA
-          [,colnames(dat.no.sex.no.gender.no.age.no.ibd) #for all the rows and columns that are in the pcl items at retroline
-           %in%
-             pcl.items_retro]
-        )
-    )
-  )
-
-freq(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_pcl_retro) #have a look at the frequency
-
-dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>% #NA per person as a percentage
-  mutate(
-    miss_pc_total_pcl_retro = 
-      na_per_person_pcl_retro/6 # NA per person divided by the amount of items
-  )
-
-freq(dat.no.sex.no.gender.no.age.no.ibd$miss_pc_total_pcl_retro)
-```
-
-#PCL - prepandemic
-pcl Missingness NAs per person - count and percentages
-```{r pcl prepan missingness}
-dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
-  mutate(
-    na_per_person_pcl_prepan =         # variable for NA per person
-      rowSums(                       
-        is.na(dat.no.sex.no.gender.no.age.no.ibd # sum the rows that are NA
-          [,colnames(dat.no.sex.no.gender.no.age.no.ibd) #for all the rows and columns that are in the pcl items at prepanline
-           %in%
-             pcl.items_prepan]
-        )
-    )
-  )
-
-freq(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_pcl_prepan) #have a look at the frequency
-
-dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>% #NA per person as a percentage
-  mutate(
-    miss_pc_total_pcl_prepan = 
-      na_per_person_pcl_prepan/6 # NA per person divided by the amount of items
-  )
-
-freq(dat.no.sex.no.gender.no.age.no.ibd$miss_pc_total_pcl_prepan)
-```
-
-Count for pcl baseline, retrospective, and prepandemic missingness per person
-```{r count of people missing a number of items for pcl}
-# baseline
-table(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_pcl_base)
-# retrospective
-table(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_pcl_retro)
-# pre-pandemic
-table(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_pcl_prepan)
-
-# rename dataset
-dat.no.sex.no.gender.no.age.no.ibd.missingness <- dat.no.sex.no.gender.no.age.no.ibd
-```
-
-#OCI-R - baseline
-OCI-R Missingness NAs per person - count and percentages
-```{r OCI-R baseline missingness}
-dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
-  mutate(
-    na_per_person_ocir_base =         # variable for NA per person
-      rowSums(                       
-        is.na(dat.no.sex.no.gender.no.age.no.ibd # sum the rows that are NA
-          [,colnames(dat.no.sex.no.gender.no.age.no.ibd) #for all the rows and columns that are in the OCI-R items at baseline
-           %in%
-             ocir.items_base]
-        )
-    )
-  )
-
-freq(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_ocir_base) #have a look at the frequency
-
-dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>% #NA per person as a percentage
-  mutate(
-    miss_pc_total_ocir_base = 
-      na_per_person_ocir_base/18 # NA per person divided by the amount of items
-  )
-
-freq(dat.no.sex.no.gender.no.age.no.ibd$miss_pc_total_ocir_base)
-```
-
-#OCI-R - retrospective
-OCI-R Missingness NAs per person - count and percentages
-```{r OCI-R retrospective missingness}
-dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
-  mutate(
-    na_per_person_ocir_retro =         # variable for NA per person
-      rowSums(                       
-        is.na(dat.no.sex.no.gender.no.age.no.ibd # sum the rows that are NA
-          [,colnames(dat.no.sex.no.gender.no.age.no.ibd) #for all the rows and columns that are in the OCI-R items at retroline
-           %in%
-             ocir.items_retro]
-        )
-    )
-  )
-
-freq(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_ocir_retro) #have a look at the frequency
-
-dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>% #NA per person as a percentage
-  mutate(
-    miss_pc_total_ocir_retro = 
-      na_per_person_ocir_retro/18 # NA per person divided by the amount of items
-  )
-
-freq(dat.no.sex.no.gender.no.age.no.ibd$miss_pc_total_ocir_retro)
-```
-
-#OCI-R - prepandemic
-OCI-R Missingness NAs per person - count and percentages
-```{r OCI-R prepan missingness}
-dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
-  mutate(
-    na_per_person_ocir_prepan =         # variable for NA per person
-      rowSums(                       
-        is.na(dat.no.sex.no.gender.no.age.no.ibd # sum the rows that are NA
-          [,colnames(dat.no.sex.no.gender.no.age.no.ibd) #for all the rows and columns that are in the OCI-R items at prepanline
-           %in%
-             ocir.items_prepan]
-        )
-    )
-  )
-
-freq(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_ocir_prepan) #have a look at the frequency
-
-dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>% #NA per person as a percentage
-  mutate(
-    miss_pc_total_ocir_prepan = 
-      na_per_person_ocir_prepan/18 # NA per person divided by the amount of items
-  )
-
-freq(dat.no.sex.no.gender.no.age.no.ibd$miss_pc_total_ocir_prepan)
-```
-
-Count for OCI-R baseline, retrospective, and prepandemic missingness per person
-```{r count of people missing a number of items for OCI-R}
-#baseline
-table(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_ocir_base)
-#retrospective
-table(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_ocir_retro)
-#pre-pandemic
-table(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_ocir_prepan)
-```
-
 #Sum scores missingness cut offs

### 2020-08-10 PANCHANGE_data_preprocessing2020-07-15.Rmd
set to NA if missigness

@@
 
-## GLAD demographics
-# Read in data
+# GLAD demographics
+## Read in data
 ```{r glad dem cols}
@@
 *Note that scores with missingness will be changed to NA later in the script
-```{r gad sum score prepan}
+```{r gad sum score prepan raw}
 # Create vector with scoring key: If the item is reversed coded use -1. 
@@
 # Add in column to tibble
-glad.gad.raw.id$gad.sum_score_prepan <- gad.scored_items_prepan$scores
+glad.gad.raw.id$gad.sum_score_prepan_raw <- gad.scored_items_prepan$scores
 
@@
 glad.gad.raw.id %>%
-  descr(gad.sum_score_prepan,
+  descr(gad.sum_score_prepan_raw,
         stats = "common"
         )
+```
+
+missingness (NAs per person)
+
+prepandemic
+```{r gad prepan missingness}
+glad.gad.raw.id <- glad.gad.raw.id %>%
+  mutate(
+    na_per_person_gad_prepan_raw =         # variable for NA per person
+      rowSums(                       
+        is.na(.[gad.items_prepan])
+      )
+  )
+
+glad.gad.raw.id %>%
+  freq(na_per_person_gad_prepan_raw,
+       cumul = F)
+```
+
+```{r gad prepan sum score if missigng items set to NA}
+glad.gad.raw.id <- glad.gad.raw.id %>%
+  mutate(
+    gad.sum_score_prepan =
+      if_else(condition = na_per_person_phq_prepan_raw > 0,
+              true = NA_real_,
+              false = gad.sum_score_prepan,
+              missing = NA_real_
+              )
+  )
+
+summary(glad.gad.raw.id$gad.sum_score_prepan_raw)
+summary(glad.gad.raw.id$gad.sum_score_prepan)
 ```
@@
 
-```{r sum score cut offs PHQ prepan}
-dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
-  mutate(
-    phq.sum_score_prepan_full =
-      if_else(na_per_person_phq_prepan > 1 & phq.prepan_cut_off == 0,
-              NA_real_,
-              phq.sum_score_prepan
-              )
-  )
-
-summary(dat.no.sex.no.gender.no.age.no.ibd$phq.sum_score_prepan)
-summary(dat.no.sex.no.gender.no.age.no.ibd$phq.sum_score_prepan_full)
-```
-
 ```{r sum score cut offs PHQ retro}

### 2020-08-10 PANCHANGE_data_preprocessing2020-07-15.Rmd
set sum score to NA if missigness in phq

@@
   mutate(
-    na_per_person_gad_prepan_raw =         # variable for NA per person
+    na_per_person_gad_prepan =         # variable for NA per person
       rowSums(                       
@@
 glad.gad.raw.id %>%
-  freq(na_per_person_gad_prepan_raw,
+  freq(na_per_person_gad_prepan,
        cumul = F)
@@
     gad.sum_score_prepan =
-      if_else(condition = na_per_person_phq_prepan_raw > 0,
+      if_else(condition = na_per_person_gad_prepan > 0,
               true = NA_real_,
-              false = gad.sum_score_prepan,
+              false = gad.sum_score_prepan_raw,
               missing = NA_real_
@@
 
-summary(glad.gad.raw.id$gad.sum_score_prepan_raw)
-summary(glad.gad.raw.id$gad.sum_score_prepan)
+glad.gad.raw.id %>%
+  descr(gad.sum_score_prepan_raw, stats = "common")
+
+glad.gad.raw.id %>%
+  descr(gad.sum_score_prepan, stats = "common")
 ```
@@
        cumul = F)
+```
+
+all times
+```{r phq prepan sum score if missigng items set to NA - all times}
+glad.phq.raw.id <- glad.phq.raw.id %>%
+  mutate(
+    phq.sum_score_prepan =
+      if_else(condition = na_per_person_phq_prepan > 0,
+              true = NA_real_,
+              false = phq.sum_score_prepan_raw,
+              missing = NA_real_
+      )
+  )
+
+glad.phq.raw.id %>%
+  descr(phq.sum_score_prepan_raw, stats = "common")
+
+glad.phq.raw.id %>%
+  descr(phq.sum_score_prepan, stats = "common")
+```
+
+8 items
+```{r phq prepan sum score if missigng items set to NA - all times}
+glad.phq.raw.id <- glad.phq.raw.id %>%
+  mutate(
+    phq.sum_score_8items_prepan =
+      if_else(condition = na_per_person_phq_prepan > 1 &
+                phq.missing_only_suicide_item_prepan == 1,
+              true = NA_real_,
+              false = phq.sum_score_prepan_raw,
+              missing = NA_real_
+      )
+  )
+
+glad.phq.raw.id %>%
+  descr(phq.sum_score_8items_prepan_raw, stats = "common")
+
+glad.phq.raw.id %>%
+  descr(phq.sum_score_8items_prepan, stats = "common")
 ```

### 2020-08-10 PANCHANGE_data_preprocessing2020-07-15.Rmd
renamed all sums cores to sum_score_raw

@@
 # Add in column to tibble
-glad.pcl.raw.id$pcl.sum_score_prepan <- pcl.scored_items_prepan$scores
+glad.pcl.raw.id$pcl.sum_score_prepan_raw <- pcl.scored_items_prepan$scores
 
@@
 glad.pcl.raw.id %>%
-  descr(pcl.sum_score_prepan,
+  descr(pcl.sum_score_prepan_raw,
         stats = "common"
@@
        cumul = F)
+```
+
+```{r pcl prepan sum score if missigng items set to NA}
+glad.pcl.raw.id <- glad.pcl.raw.id %>%
+  mutate(
+    pcl.sum_score_prepan =
+      if_else(condition = na_per_person_pcl_prepan > 0,
+              true = NA_real_,
+              false = pcl.sum_score_prepan_raw,
+              missing = NA_real_
+      )
+  )
+
+glad.pcl.raw.id %>%
+  descr(pcl.sum_score_prepan_raw, stats = "common")
+
+glad.pcl.raw.id %>%
+  descr(pcl.sum_score_prepan, stats = "common")
 ```
@@
 # Add in column to tibble
-glad.phq.raw.id$phq.sum_score_prepan <- phq.scored_items_prepan$scores
+glad.phq.raw.id$phq.sum_score_prepan_raw <- phq.scored_items_prepan$scores
 
@@
 glad.phq.raw.id %>%
-  descr(phq.sum_score_prepan,
+  descr(phq.sum_score_prepan_raw,
         stats = "common"
@@
 # Add in column to tibble
-coping.glad.gad.raw.id$gad.sum_score_retro <- gad.scored_items_retro$scores
+coping.glad.gad.raw.id$gad.sum_score_retro_raw <- gad.scored_items_retro$scores
 
@@
 coping.glad.gad.raw.id %>%
-  descr(gad.sum_score_retro,
+  descr(gad.sum_score_retro_raw,
         stats = "common"
@@
 # Add in column to tibble
-coping.glad.gad.raw.id$gad.sum_score_base <- gad.scored_items_base$scores
+coping.glad.gad.raw.id$gad.sum_score_base_raw <- gad.scored_items_base$scores
 
@@
 coping.glad.gad.raw.id %>%
-  descr(gad.sum_score_base,
+  descr(gad.sum_score_base_raw,
         stats = "common"
@@
 # Add in column to tibble
-coping.glad.pcl.raw.id$pcl.sum_score_retro <- pcl.scored_items_retro$scores
+coping.glad.pcl.raw.id$pcl.sum_score_retro_raw <- pcl.scored_items_retro$scores
 
@@
 coping.glad.pcl.raw.id %>%
-  descr(pcl.sum_score_retro,
+  descr(pcl.sum_score_retro_raw,
         stats = "common"
@@
 # Add in column to tibble
-coping.glad.pcl.raw.id$pcl.sum_score_base <- pcl.scored_items_base$scores
+coping.glad.pcl.raw.id$pcl.sum_score_base_raw <- pcl.scored_items_base$scores
 
@@
 coping.glad.pcl.raw.id %>%
-  descr(pcl.sum_score_base,
+  descr(pcl.sum_score_base_raw,
         stats = "common"
@@
 # Add in column to tibble
-coping.glad.phq.raw.id$phq.sum_score_retro <- phq.scored_items_retro$scores
+coping.glad.phq.raw.id$phq.sum_score_retro_raw <- phq.scored_items_retro$scores
 
@@
 coping.glad.phq.raw.id %>%
-  descr(phq.sum_score_retro,
+  descr(phq.sum_score_retro_raw,
         stats = "common"
@@
 # Add in column to tibble
-coping.glad.phq.raw.id$phq.sum_score_base <- phq.scored_items_base$scores
+coping.glad.phq.raw.id$phq.sum_score_base_raw <- phq.scored_items_base$scores
 
@@
 coping.glad.phq.raw.id %>%
-  descr(phq.sum_score_base,
+  descr(phq.sum_score_base_raw,
         stats = "common"
@@
 # Add in column to tibble
-coping.glad.ocir.raw.id$ocir.sum_score_retro <- ocir.scored_items_retro$scores
+coping.glad.ocir.raw.id$ocir.sum_score_retro_raw <- ocir.scored_items_retro$scores
 
@@
 coping.glad.ocir.raw.id %>%
-  descr(ocir.sum_score_retro,
+  descr(ocir.sum_score_retro_raw,
         stats = "common"
@@
 # Add in column to tibble
-coping.glad.ocir.raw.id$ocir.sum_score_base <- ocir.scored_items_base$scores
+coping.glad.ocir.raw.id$ocir.sum_score_base_raw <- ocir.scored_items_base$scores
 
@@
 coping.glad.ocir.raw.id %>%
-  descr(ocir.sum_score_base,
+  descr(ocir.sum_score_base_raw,
         stats = "common"

### 2020-08-10 PANCHANGE_data_preprocessing2020-07-15.Rmd
fixed variable name inconistencies

@@
 all times
-```{r phq prepan sum score if missigng items set to NA - all times}
+```{r phq prepan sum score if missigng items set to NA - all items}
 glad.phq.raw.id <- glad.phq.raw.id %>%
@@
 
++++CH: THINK ABOUT THIS!!!
+
 8 items
-```{r phq prepan sum score if missigng items set to NA - all times}
+```{r phq prepan sum score if missigng items set to NA - 8 items}
 glad.phq.raw.id <- glad.phq.raw.id %>%
@@
 glad.phq.raw.id %>%
-  descr(phq.sum_score_8items_prepan_raw, stats = "common")
+  descr(phq.sum_score_8items_prepan, stats = "common")
 
@@
 
+```{r coping gad base sum score if missigng items set to NA}
+coping.glad.gad.raw.id <- coping.glad.gad.raw.id %>%
+  mutate(
+    gad.sum_score_base =
+      if_else(condition = na_per_person_gad_base > 0,
+              true = NA_real_,
+              false = gad.sum_score_base_raw,
+              missing = NA_real_
+      )
+  )
+
+coping.glad.gad.raw.id %>%
+  descr(gad.sum_score_base_raw, stats = "common")
+
+coping.glad.gad.raw.id %>%
+  descr(gad.sum_score_base, stats = "common")
+```
+
+```{r coping gad retro sum score if missigng items set to NA}
+coping.glad.gad.raw.id <- coping.glad.gad.raw.id %>%
+  mutate(
+    gad.sum_score_retro =
+      if_else(condition = na_per_person_gad_retro > 0,
+              true = NA_real_,
+              false = gad.sum_score_retro_raw,
+              missing = NA_real_
+      )
+  )
+
+coping.glad.gad.raw.id %>%
+  descr(gad.sum_score_retro_raw, stats = "common")
+
+coping.glad.gad.raw.id %>%
+  descr(gad.sum_score_retro, stats = "common")
+```
+
 ```{r coping glad gad head}
@@
   freq(na_per_person_pcl_retro, cumul = F) #have a look at the frequency
+```
+
+```{r coping pcl base sum score if missigng items set to NA}
+coping.glad.pcl.raw.id <- coping.glad.pcl.raw.id %>%
+  mutate(
+    pcl.sum_score_base =
+      if_else(condition = na_per_person_pcl_base > 0,
+              true = NA_real_,
+              false = pcl.sum_score_base_raw,
+              missing = NA_real_
+      )
+  )
+
+coping.glad.pcl.raw.id %>%
+  descr(pcl.sum_score_base_raw, stats = "common")
+
+coping.glad.pcl.raw.id %>%
+  descr(pcl.sum_score_base, stats = "common")
+```
+
+```{r coping pcl retro sum score if missigng items set to NA}
+coping.glad.pcl.raw.id <- coping.glad.pcl.raw.id %>%
+  mutate(
+    pcl.sum_score_retro =
+      if_else(condition = na_per_person_pcl_retro > 0,
+              true = NA_real_,
+              false = pcl.sum_score_retro_raw,
+              missing = NA_real_
+      )
+  )
+
+coping.glad.pcl.raw.id %>%
+  descr(pcl.sum_score_retro_raw, stats = "common")
+
+coping.glad.pcl.raw.id %>%
+  descr(pcl.sum_score_retro, stats = "common")
 ```
@@
        cumul = F)
+```
+
+```{r coping phq base sum score if missigng items set to NA}
+coping.glad.phq.raw.id <- coping.glad.phq.raw.id %>%
+  mutate(
+    phq.sum_score_base =
+      if_else(condition = na_per_person_phq_base > 0,
+              true = NA_real_,
+              false = phq.sum_score_base_raw,
+              missing = NA_real_
+      )
+  )
+
+coping.glad.phq.raw.id %>%
+  descr(phq.sum_score_base_raw, stats = "common")
+
+coping.glad.phq.raw.id %>%
+  descr(phq.sum_score_base, stats = "common")
+```
+
+8 items
+```{r phq base sum score if missigng items set to NA - 8 items}
+coping.glad.phq.raw.id <- coping.glad.phq.raw.id %>%
+  mutate(
+    phq.sum_score_8items_base =
+      if_else(condition = na_per_person_phq_base > 1 &
+                phq.missing_only_suicide_item_base == 1,
+              true = NA_real_,
+              false = phq.sum_score_base_raw,
+              missing = NA_real_
+      )
+  )
+
+coping.glad.phq.raw.id %>%
+  descr(phq.sum_score_8items_base, stats = "common")
+```
+
+```{r coping phq retro sum score if missigng items set to NA}
+coping.glad.phq.raw.id <- coping.glad.phq.raw.id %>%
+  mutate(
+    phq.sum_score_retro =
+      if_else(condition = na_per_person_phq_retro > 0,
+              true = NA_real_,
+              false = phq.sum_score_retro_raw,
+              missing = NA_real_
+      )
+  )
+
+coping.glad.phq.raw.id %>%
+  descr(phq.sum_score_retro_raw, stats = "common")
+
+coping.glad.phq.raw.id %>%
+  descr(phq.sum_score_retro, stats = "common")
+```
+
+8 items
+```{r phq retro sum score if missigng items set to NA - 8 items}
+coping.glad.phq.raw.id <- coping.glad.phq.raw.id %>%
+  mutate(
+    phq.sum_score_8items_retro =
+      if_else(condition = na_per_person_phq_retro > 1 &
+                phq.missing_only_suicide_item_retro == 1,
+              true = NA_real_,
+              false = phq.sum_score_retro_raw,
+              missing = NA_real_
+      )
+  )
+
+coping.glad.phq.raw.id %>%
+  descr(phq.sum_score_8items_retro, stats = "common")
 ```
@@
 
-#Sum scores missingness cut offs
-KT: This series of chunks creates a "full" sum score for the PHQ, GAD and PCL.
-
-PHQ
-The PHQ sum score is set to NA if they have more than one missing item, and it is not the last suicide ideation item (they do not meet the cut off criteria - phq.missing_only_suicide_item)
-```{r sum score cut offs PHQ base}
-dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
-  mutate(
-    phq.sum_score_base_full =
-      if_else(na_per_person_phq_base > 1 & phq.missing_only_suicide_item == 0,
-              NA_real_,
-              phq.sum_score_base
-              )
-  )
-
-summary(dat.no.sex.no.gender.no.age.no.ibd$phq.sum_score_base)
-summary(dat.no.sex.no.gender.no.age.no.ibd$phq.sum_score_base_full)
-```
-
-```{r sum score cut offs PHQ retro}
-dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
-  mutate(
-    phq.sum_score_retro_full =
-      if_else(na_per_person_phq_retro > 1 & phq.retro_cut_off == 0,
-              NA_real_,
-              phq.sum_score_retro
-              )
-  )
-
-summary(dat.no.sex.no.gender.no.age.no.ibd$phq.sum_score_retro)
-summary(dat.no.sex.no.gender.no.age.no.ibd$phq.sum_score_retro_full)
-```
-
-GAD
-The GAD sum score is set to NA if they have any missing items
-```{r sum score cut offs GAD base}
-dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
-  mutate(
-    gad.sum_score_base_full =
-      if_else(na_per_person_gad_base > 0,
-              NA_real_,
-              gad.sum_score_base
-              )
-  )
-
-summary(dat.no.sex.no.gender.no.age.no.ibd$gad.sum_score_base)
-summary(dat.no.sex.no.gender.no.age.no.ibd$gad.sum_score_base_full)
-```
-
-```{r sum score cut offs GAD prepan}
-dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
-  mutate(
-    gad.sum_score_prepan_full =
-      if_else(na_per_person_gad_prepan > 0,
-              NA_real_,
-              gad.sum_score_prepan
-              )
-  )
-
-summary(dat.no.sex.no.gender.no.age.no.ibd$gad.sum_score_prepan)
-summary(dat.no.sex.no.gender.no.age.no.ibd$gad.sum_score_prepan_full)
-```
-
-```{r sum score cut offs GAD retro}
-dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
-  mutate(
-    gad.sum_score_retro_full =
-      if_else(na_per_person_gad_retro > 0,
-              NA_real_,
-              gad.sum_score_retro
-              )
-  )
-
-summary(dat.no.sex.no.gender.no.age.no.ibd$gad.sum_score_retro)
-summary(dat.no.sex.no.gender.no.age.no.ibd$gad.sum_score_retro_full)
-```
-
-PCL
-The PCL sum score is set to NA if they have any missing items - only for basline and prepan.
-```{r sum score cut offs PCL base}
-dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
-  mutate(
-    pcl.sum_score_base_full =
-      if_else(na_per_person_pcl_base > 0,
-              NA_real_,
-              pcl.sum_score_base
-              )
-  )
-
-summary(dat.no.sex.no.gender.no.age.no.ibd$pcl.sum_score_base)
-summary(dat.no.sex.no.gender.no.age.no.ibd$pcl.sum_score_base_full)
-```
-
-```{r sum score cut offs PCL prepan}
-dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
-  mutate(
-    pcl.sum_score_prepan_full =
-      if_else(na_per_person_pcl_prepan > 0,
-              NA_real_,
-              pcl.sum_score_prepan
-              )
-  )
-
-summary(dat.no.sex.no.gender.no.age.no.ibd$pcl.sum_score_prepan)
-summary(dat.no.sex.no.gender.no.age.no.ibd$pcl.sum_score_prepan_full)
-```
-
 ##Create tidy data on which the exclusion criteria have been applied
@@
 ```{r Tidy data}
-dat.glad <- dat.no.sex.no.gender.no.age.no.ibd.missingness
+dat.glad <- dat.no.sex.no.gender.no.age.no.ibd
 

### 2020-08-10 PANCHANGE_data_preprocessing2020-07-15.Rmd

@@
 
+```{r coping ocir base sum score if missigng items set to NA}
+coping.glad.ocir.raw.id <- coping.glad.ocir.raw.id %>%
+  mutate(
+    ocir.sum_score_base =
+      if_else(condition = na_per_person_ocir_base > 0,
+              true = NA_real_,
+              false = ocir.sum_score_base_raw,
+              missing = NA_real_
+      )
+  )
+
+coping.glad.ocir.raw.id %>%
+  descr(ocir.sum_score_base_raw, stats = "common")
+
+coping.glad.ocir.raw.id %>%
+  descr(ocir.sum_score_base, stats = "common")
+```
+
+```{r coping ocir retro sum score if missigng items set to NA}
+coping.glad.ocir.raw.id <- coping.glad.ocir.raw.id %>%
+  mutate(
+    ocir.sum_score_retro =
+      if_else(condition = na_per_person_ocir_retro > 0,
+              true = NA_real_,
+              false = ocir.sum_score_retro_raw,
+              missing = NA_real_
+      )
+  )
+
+coping.glad.ocir.raw.id %>%
+  descr(ocir.sum_score_retro_raw, stats = "common")
+
+coping.glad.ocir.raw.id %>%
+  descr(ocir.sum_score_retro, stats = "common")
+```
+
 ```{r coping glad ocir head}

### 2020-08-10 PANCHANGE_data_preprocessing2020-07-15.Rmd
renamed the covid symptoms variable

@@
   mutate(
-    people_with_symptoms =
+    covid_symptoms =
       if_else(
@@
 
-table(dat.glad.coping$people_with_symptoms)
+dat.glad.coping %>%
+  freq(covid_symptoms, cumul = F)
 ```

### 2020-08-10 PANCHANGE_data_preprocessing2020-07-15.Rmd
changed file path to respiratory data

@@
 ```{r coping resp cols}
-coping.glad.respiratory.raw <- readRDS(file = paste0(data.raw_path, "/2020-08-03/glad/respiratory_coping_glad.rds"))
+coping.glad.respiratory.raw <- readRDS(file = paste0(data.raw_path, "/glad/respiratory_coping_glad.rds"))
 dim(coping.glad.respiratory.raw)
@@
 COVID prediction model for COPING
-
+The COVID prediction model has coded the sexes opposite to our data set
 ```{r create numeric sex variable with male=1}
@@
         Sex == "Male",
-        1,
-        0
+        true = 1,
+        false = 0
       )

### 2020-08-10 PANCHANGE_data_preprocessing2020-07-15.Rmd
add respiratory part with routing question

@@
 
+# NBR cohort information
+```{r nbr cohort information}
+if(NBR = TRUE){
+  nbr.cohort <- readxl::read_xlsx(
+    path = paste0(data.raw_path, "/nbr/coping_participants_export_20200730.xlsx")
+    )
+
+  dim(nbr.cohort)
+  colnames(nbr.cohort)
+  }
+
+```
+
 # glad gad
@@
 
-```{r}
+```{r comordbitiy_total_count_factor}
 glad.mhd.raw.id <- glad.mhd.raw.id %>%
@@
 ```
+
+Probable COVID case including the routing question
+```{r}
+dat.glad.coping <- dat.glad.coping %>%
+  mutate(
+    covid_probable_case_incl_screening_numeric =
+      case_when(
+        respiratory.breath_diarrhoea_fatigue_fever_numeric == 0 ~ 0,
+        covid_odds_ratio_50_numeric == 0 ~ 0,
+        covid_odds_ratio_50_numeric == 1 ~ 1
+      )
+  )
+
+#create factor with labels
+dat.glad.coping <- dat.glad.coping %>%
+  mutate(
+    covid_probable_case_incl_screening =
+      recode_factor(
+        covid_probable_case_incl_screening_numeric,
+        "0" = "No COVID",
+        "1" = "Probable COVID"
+      )
+  )
+
+dat.glad.coping %>%
+  freq(covid_probable_case_incl_screening, 
+     cumul = FALSE) 
+```

### 2020-08-10 PANCHANGE_data_preprocessing2020-07-15.Rmd
added read in for nbr demo data
started reading in the nbr data

@@
 
+# NBR cohort information
+```{r nbr cohort information}
+if(NBR == TRUE){
+  nbr.cohort.raw <- readxl::read_xlsx(
+    path = paste0(data.raw_path, "/nbr/coping_participants_export_20200730.xlsx")
+    )
+
+  dim(nbr.cohort)
+  colnames(nbr.cohort)
+  }
+```
+
+```{r nbr dem cleaning}
+if(NBR == TRUE) {
+exclude_cols_dem <- c("ID",
+                  "Sample",
+                  "startDate.coping",
+                  "Age_uncleaned",
+                  "EduYrs")
+
+nbr.cohort.raw.id <- nbr.cohort.raw %>%
+  drop_na(`NBR ID`) %>% # Drop NAs
+  distinct(`NBR ID`, .keep_all = TRUE) %>% # Remove duplicates based on ID
+  separate(`NBR ID`, into = c("Sample", "ID.intm"), sep = 6) %>% # Split ID in Sample and Number
+  separate(ID.intm, into = "ID", sep = 7) %>%
+  mutate(
+    ID = as.numeric(ID),
+#         startDate.coping = startDate
+         ) %>% # Rename startDate
+  select(
+         Sample, # Sample
+         ID, # ID
+#         startDate.coping, #Date when participant signed up to NBR COPING
+         Age_uncleaned = age, # Age
+         Gender = gender, # Gender
+#         Sex = demographics.select_questionnaire_items_medical, #Sex
+#         EduYrs = demographics.school_education_school_years.txt, # Years in education
+#         demographics.college_or_university_degree, # level of education - univeristy
+#         demographics.a_levelsas_levels_or_equivalent, # level of education - alevel
+#         demographics.o_levelsgcses_or_equivalent, # level of education - gcse
+#         demographics.cses_or_equivalent, # level of education - cse
+#         demographics.nvq_or_hnd_or_hnc_or_equivalent, # level of education - nvq
+         Ethnicity = ethnicity # Ethnicity
+         ) %>%
+  add_numeric(., exclude = exclude_cols_dem) %>%
+  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
+  mutate_if(is.numeric, ~na_if(., -99)) %>%
+  mutate_if(is.numeric, ~na_if(., -77)) %>%
+  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
+  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
+
+# Inspect dimensions
+dim(nbr.cohort.raw.id)
+# Inspect colnames
+colnames(nbr.cohort.raw.id)
+#Differences
+dim(nbr.cohort.raw)[1]-dim(nbr.cohort.raw.id)[1]
+}
+```
+
+```{r nbr demo summary}
+if(NBR == TRUE) {
+summarytools::dfSummary(
+  nbr.cohort.raw.id,
+  graph.col = F,
+  valid.col = F,
+  labels.col = F)
+}
+```
+
 #Clean Age variable
@@
   labels.col = F)
-```
-
-# NBR cohort information
-```{r nbr cohort information}
-if(NBR = TRUE){
-  nbr.cohort <- readxl::read_xlsx(
-    path = paste0(data.raw_path, "/nbr/coping_participants_export_20200730.xlsx")
-    )
-
-  dim(nbr.cohort)
-  colnames(nbr.cohort)
-  }
-
 ```

### 2020-08-11 PANCHANGE_data_preprocessing2020-07-15.Rmd
added if statements for education and started reading in the NBR data

@@
 # Specify cohort
-```{r}
-GLAD = TRUE
+```{r Specify cohort}
+GLAD = FALSE
 EDGI = FALSE
-NBR = FALSE
+NBR = TRUE
 RAMP = FALSE
@@
 ```{r glad dem cols}
+if(GLAD == TRUE){
 glad.dem.raw <- readRDS(file = paste0(data.raw_path, "/glad/dem_glad.rds"))
@@
 colnames(glad.dem.raw)
+}
 ```
@@
 ```{r glad dem cleaning}
+if(GLAD == TRUE){
 exclude_cols_dem <- c("ID",
@@
 dim(glad.dem.raw)[1]-dim(glad.dem.raw.id)[1]
-```
-
-# NBR cohort information
+}
+```
+
+# NBR demographics
+
+## Read in data
+```{r nbr dem cols}
+if(NBR == TRUE){
+  nbr.dem.raw <- readRDS(file = paste0(data.raw_path, "/nbr/dem_nbr.rds"))
+  dim(nbr.dem.raw)
+  colnames(nbr.dem.raw)
+}
+```
+
+# Select variables
+```{r nbr dem cleaning}
+if(NBR == TRUE){
+  exclude_cols_dem <- c("ID",
+                        "Sample",
+                        "startDate.nbr",
+                        "Age_uncleaned",
+                        "EduYrs")
+
+  nbr.dem.raw.id <- nbr.dem.raw %>%
+    drop_na(subjectid) %>% # Drop NAs
+    distinct(subjectid, .keep_all = TRUE) %>% # Remove duplicates based on ID
+    separate(subjectid, into = c("Sample", "ID.intm"), sep = 6) %>% # Split ID in Sample and Number
+    separate(ID.intm, into = "ID", sep = 7) %>%
+    mutate(ID = as.numeric(ID),
+           startDate.coping = startDate) %>% # Rename startDate
+    select(
+      Sample, # Sample
+      ID, # ID
+      startDate.coping, #Date when participant signed up to nbr
+#      Age_uncleaned = demographics.how_old_are_you_now.txt, # Age
+      Birthyear = demographics.year, # Birthyear
+      Gender = demographics.which_gender_do_you_identify_with, # Gender
+      Sex = demographics.select_questionnaire_items_medical, #Sex
+      EduYrs = demographics.school_education_school_years.txt, # Years in education
+      demographics.college_or_university_degree, # level of education - univeristy
+      demographics.a_levelsas_levels_or_equivalent, # level of education - alevel
+      demographics.o_levelsgcses_or_equivalent, # level of education - gcse
+      demographics.cses_or_equivalent, # level of education - cse
+      demographics.nvq_or_hnd_or_hnc_or_equivalent, # level of education - nvq
+      Ethnicity = demographics.questions_based_ethnic_origin # Ethnicity
+    ) %>%
+    add_numeric(., exclude = exclude_cols_dem) %>%
+    mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
+    mutate_if(is.numeric, ~na_if(., -99)) %>%
+    mutate_if(is.numeric, ~na_if(., -77)) %>%
+    mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
+    mutate_if(is.factor, ~na_if(., "Don't know")) %>%
+    mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
+    mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
+    mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
+    mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
+    mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
+    mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
+
+  # Inspect dimensions
+  dim(nbr.dem.raw.id)
+  # Inspect colnames
+  colnames(nbr.dem.raw.id)
+  #Differences
+  dim(nbr.dem.raw)[1]-dim(nbr.dem.raw.id)[1]
+}
+```
+
+## Cohort information
+Information on INTERVAL, COMPARE, and STRIDES
+http://www.donorhealth-btru.nihr.ac.uk/studies/
 ```{r nbr cohort information}
@@
 
-  dim(nbr.cohort)
-  colnames(nbr.cohort)
+  dim(nbr.cohort.raw)
+  colnames(nbr.cohort.raw)
   }
@@
 ```{r Highest education}
+if(GLAD == TRUE | EDGI == TRUE) {
 #create numeric version of the highest education variable
@@
   freq(highest_education)
+}
 ```
@@
 ```{r Highest education check}
+if(GLAD == TRUE | EDGI == TRUE) {
 glad.dem.raw.id %>%
@@
   )
+}
 ```

### 2020-08-11 PANCHANGE_data_preprocessing2020-07-15.Rmd
key worker chunk

@@
   labels.col = F)
+```
+
+# GLAD employment
+## Read in data
+```{r glad dem cols}
+if(GLAD == TRUE){
+glad.employment.raw <- readRDS(file = paste0(data.raw_path, "/glad/employment_coping_glad.rds"))
+dim(glad.employment.raw)
+colnames(glad.employment.raw)
+}
+```
+
+# Select variables
+```{r glad employment cleaning}
+if(GLAD == TRUE){
+exclude_cols_employment <- c("ID",
+                  "Sample")
+
+glad.employment.raw.id <- glad.employment.raw %>%
+  drop_na(externalDataReference) %>% # Drop NAs
+  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
+  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
+  mutate(
+    ID = as.numeric(ID)
+    ) %>%
+  select(
+         Sample, # Sample
+         ID, # ID
+         employment.phd, # level of education - univeristy
+         employment.masters_degree_or_equivalent, # level of education - univeristy
+         employment.postgraduate_degree_or_equivalent, # level of education - univeristy
+         employment.bachelors_degree_or_equivalent, # level of education - univeristy
+         employment.a_levelsas_levels_or_equivalent, # level of education - alevel
+         employment.o_levelsgcses_or_equivalent, # level of education - gcse
+         employment.cses_or_equivalent, # level of education - cse
+         employment.nvq_or_hnd_or_hnc_or_equivalent, # level of education - nvq
+         employment.government_work_key_workers
+         ) %>%
+  add_numeric(., exclude = exclude_cols_employment) %>%
+  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
+  mutate_if(is.numeric, ~na_if(., -99)) %>%
+  mutate_if(is.numeric, ~na_if(., -77)) %>%
+  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
+  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
+
+# Inspect dimensions
+dim(glad.employment.raw.id)
+# Inspect colnames
+colnames(glad.employment.raw.id)
+#Differences
+dim(glad.employment.raw)[1]-dim(glad.employment.raw.id)[1]
+}
+```
+
+# Highest education
+Proceed along qualifications fields. If field is not blank, take that as highest qual. If field is blank, check next field. If all fields are blank, NA
+Assumes University degree > A level > NVQ > GCSE/O Level/CSE
+```{r Highest education}
+if(GLAD == TRUE | EDGI == TRUE) {
+#create numeric version of the highest education variable
+glad.employment.raw.id <- glad.employment.raw.id %>%
+  mutate(
+    highest_education_numeric =
+      case_when(
+        employment.phd_numeric == "1" ~ 4,
+        employment.masters_degree_or_equivalent_numeric == "1" ~ 4,
+        employment.postgraduate_degree_or_equivalent_numeric == "1" ~ 4,
+        employment.bachelors_degree_or_equivalent_numeric == "1" ~ 4,
+        employment.a_levelsas_levels_or_equivalent_numeric == "1" ~ 3,
+        employment.nvq_or_hnd_or_hnc_or_equivalent_numeric == "1" ~ 2,
+        employment.o_levelsgcses_or_equivalent_numeric == "1" ~ 1,
+        employment.cses_or_equivalent_numeric == "1" ~ 1
+      )
+    )
+
+#recode the numeric version into a factor
+glad.employment.raw.id <- glad.employment.raw.id %>%
+  mutate(
+    highest_education =
+      recode_factor(
+        highest_education_numeric,
+        `1` = "GCSE/CSE",
+        `2` = "NVQ",
+        `3` = "A-levels",
+        `4` = "University")
+    )
+
+glad.employment.raw.id %>%
+  freq(highest_education)
+}
+```
+
+Check highest education coding
+```{r Highest education check}
+if(GLAD == TRUE | EDGI == TRUE) {
+glad.employment.raw.id %>%
+  select(highest_education,
+         employment.phd_numeric,
+         employment.masters_degree_or_equivalent_numeric,
+         employment.postgraduate_degree_or_equivalent_numeric,
+         employment.bachelors_degree_or_equivalent_numeric,
+         employment.a_levelsas_levels_or_equivalent_numeric,
+         employment.nvq_or_hnd_or_hnc_or_equivalent_numeric,
+         employment.o_levelsgcses_or_equivalent_numeric,
+         employment.cses_or_equivalent_numeric
+  )
+}
+```
+
+# Key worker status
+```{r Key worker}
+if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE | RAMP == TRUE) {
+#create numeric version of the variable
+glad.employment.raw.id <- glad.employment.raw.id %>%
+  mutate(
+    key_worker_numeric =
+      case_when(
+        employment.government_work_key_workers_numeric == "0" ~ 0,
+        employment.government_work_key_workers_numeric > 0 ~ 1
+      )
+    )
+
+#recode the numeric version into a factor
+glad.employment.raw.id <- glad.employment.raw.id %>%
+  mutate(
+    key_worker =
+      recode_factor(
+        key_worker_numeric,
+        `0` = "No key worker",
+        `1` = "Key worker"
+        )
+    )
+
+glad.employment.raw.id %>%
+  freq(key_worker)
+}
 ```

### 2020-08-11 PANCHANGE_data_preprocessing2020-07-15.Rmd
added first edgi read in chunk

@@
 
+```{r nbr copy dem}
+if(NBR == TRUE){
+dem.raw.id <- nbr.dem.raw.id
+}
+```
+
 ```{r nbr demo summary}
@@
          employment.nvq_or_hnd_or_hnc_or_equivalent, # level of education - nvq
-         employment.government_work_key_workers
+         employment.government_work_key_workers # key worker status
          ) %>%
@@
 ```{r glad gad cols}
+if(GLAD == TRUE){
 glad.gad.raw <- readRDS(file = paste0(data.raw_path, "/glad/gad_glad.rds"))
@@
 colnames(glad.gad.raw)
+}
 ```
@@
 
+```{r nbr copy gad}
+if(NBR == TRUE){
+gad.raw.id <- glad.gad.raw.id
+}
+```
+
+```{r edgi gad cols}
+if(EDGI == TRUE){
+  edgi.gad.raw <- readRDS(file = paste0(data.raw_path, "/edgi/gad_edgi.rds"))
+  dim(edgi.gad.raw)
+  colnames(edgi.gad.raw)
+}
+```
+
+```{r edgi gad cleaning}
+exclude_cols <- c("Sample",
+                  "ID")
+
+edgi.gad.raw.id <- edgi.gad.raw %>%
+  drop_na(externalDataReference) %>% # Drop NAs
+  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
+  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
+  mutate(ID = as.numeric(ID),
+         startDate.edgi = startDate) %>% # Rename startDate
+  select(
+    Sample, # Sample
+    ID, # ID
+    gad.feeling_nervous_anxious_or_on_edge_prepan = gad.feeling_nervous_anxious_or_on_edge,
+    gad.control_worrying_stop_prepan = gad.control_worrying_stop,
+    gad.worrying_too_much_about_different_things_prepan = gad.worrying_too_much_about_different_things,
+    gad.trouble_relaxing_prepan = gad.trouble_relaxing,
+    gad.sit_restless_hard_prepan = gad.sit_restless_hard,
+    gad.becoming_easily_annoyed_or_irritable_prepan = gad.becoming_easily_annoyed_or_irritable,
+    gad.awful_feeling_afraid_happen_prepan = gad.awful_feeling_afraid_happen
+  ) %>%
+  add_numeric(., exclude = exclude_cols) %>%
+  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
+  mutate_if(is.numeric, ~na_if(., -99)) %>%
+  mutate_if(is.numeric, ~na_if(., -77)) %>%
+  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
+  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
+
+# Inspect dimensions
+dim(edgi.gad.raw.id)
+# Inspect colnames
+colnames(edgi.gad.raw.id)
+#Differences
+dim(edgi.gad.raw)[1]-dim(edgi.gad.raw.id)[1]
+```
+
+```{r nbr copy gad}
+if(NBR == TRUE){
+  gad.raw.id <- edgi.gad.raw.id
+}
+```
+
 Calculate sum score for GAD-7
@@
 # Add in column to tibble
-glad.gad.raw.id$gad.sum_score_prepan_raw <- gad.scored_items_prepan$scores
+GADraw.id$gad.sum_score_prepan_raw <- gad.scored_items_prepan$scores
 
 # Look at values
-glad.gad.raw.id %>%
+GADraw.id %>%
   descr(gad.sum_score_prepan_raw,
@@
 ```{r gad prepan missingness}
-glad.gad.raw.id <- glad.gad.raw.id %>%
+glad.gad.raw.id <- gad.raw.id %>%
   mutate(
@@
 
-glad.gad.raw.id %>%
+gad.raw.id %>%
   freq(na_per_person_gad_prepan,
@@
 ```{r gad prepan sum score if missigng items set to NA}
-glad.gad.raw.id <- glad.gad.raw.id %>%
+gad.raw.id <- gad.raw.id %>%
   mutate(
@@
 
-glad.gad.raw.id %>%
+gad.raw.id %>%
   descr(gad.sum_score_prepan_raw, stats = "common")
 
-glad.gad.raw.id %>%
+gad.raw.id %>%
   descr(gad.sum_score_prepan, stats = "common")
@@
 ```{r glad gad head}
-head(glad.gad.raw.id)
+head(gad.raw.id)
 ```
@@
 summarytools::dfSummary(
-  glad.gad.raw.id,
+  gad.raw.id,
   graph.col = F,

### 2020-08-11 PANCHANGE_data_preprocessing2020-07-15.Rmd
renamed startDate.glad to startDate.prepandemic

@@
                   "Sample",
-                  "startDate.glad",
+                  "startDate.prepandemic",
                   "Age_uncleaned",
@@
   mutate(ID = as.numeric(ID),
-         startDate.glad = startDate) %>% # Rename startDate
+         startDate.prepandemic = startDate) %>% # Rename startDate
   select(
@@
          ID, # ID
-         startDate.glad, #Date when participant signed up to glad
+         startDate.prepandemic, #Date when participant signed up to glad
          Age_uncleaned = demographics.how_old_are_you_now.txt, # Age
@@
 
+```{r glad copy dem}
+if(GLAD == TRUE){
+dem.raw.id <- glad.dem.raw.id
+}
+```
+
+# EDGI demographics
+## Read in data
+```{r edgi dem cols}
+if(EDGI == TRUE){
+  edgi.dem.raw <- readRDS(file = paste0(data.raw_path, "/edgi/dem_edgi.rds"))
+  dim(edgi.dem.raw)
+  colnames(edgi.dem.raw)
+}
+```
+
+# Select variables
+```{r edgi dem cleaning}
+if(EDGI == TRUE){
+  exclude_cols_dem <- c("ID",
+                        "Sample",
+                        "startDate.edgi",
+                        "Age_uncleaned",
+                        "EduYrs")
+
+  edgi.dem.raw.id <- edgi.dem.raw %>%
+    drop_na(externalDataReference) %>% # Drop NAs
+    distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
+    separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
+    mutate(ID = as.numeric(ID),
+           startDate.edgi = startDate) %>% # Rename startDate
+    select(
+      Sample, # Sample
+      ID, # ID
+      startDate.edgi, #Date when participant signed up to edgi
+      Age_uncleaned = demographics.how_old_are_you_now.txt, # Age
+      Gender = demographics.which_gender_do_you_identify_with, # Gender
+      Sex = demographics.select_questionnaire_items_medical, #Sex
+      EduYrs = demographics.school_education_school_years.txt, # Years in education
+      demographics.college_or_university_degree, # level of education - univeristy
+      demographics.a_levelsas_levels_or_equivalent, # level of education - alevel
+      demographics.o_levelsgcses_or_equivalent, # level of education - gcse
+      demographics.cses_or_equivalent, # level of education - cse
+      demographics.nvq_or_hnd_or_hnc_or_equivalent, # level of education - nvq
+      Ethnicity = demographics.questions_based_ethnic_origin # Ethnicity
+    ) %>%
+    add_numeric(., exclude = exclude_cols_dem) %>%
+    mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
+    mutate_if(is.numeric, ~na_if(., -99)) %>%
+    mutate_if(is.numeric, ~na_if(., -77)) %>%
+    mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
+    mutate_if(is.factor, ~na_if(., "Don't know")) %>%
+    mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
+    mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
+    mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
+    mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
+    mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
+    mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
+
+  # Inspect dimensions
+  dim(edgi.dem.raw.id)
+  # Inspect colnames
+  colnames(edgi.dem.raw.id)
+  #Differences
+  dim(edgi.dem.raw)[1]-dim(edgi.dem.raw.id)[1]
+}
+```
+
+```{r edgi copy dem}
+if(EDGI == TRUE){
+  dem.raw.id <- edgi.dem.raw.id
+}
+```
+
 # NBR demographics
-
 ## Read in data
@@
   "ID",
-  "startDate.coping.glad"
+  "startDate.coping"
 )
@@
   mutate(ID = as.numeric(ID),
-         startDate.glad = startDate) %>% # Rename startDate
+         startDate.coping = startDate) %>% # Rename startDate
   select(
@@
       if_else(
-        startDate.glad > date_first_case_uk_january_31, # The GLAD sign up is dated before the cut off (> longer ago)
+        startDate.prepandemic > date_first_case_uk_january_31, # The GLAD sign up is dated before the cut off (> longer ago)
         true = 0, # Participant has not signed up before the pandemic,
@@
       if_else(
-        startDate.glad > date_higher_awareness_march_1, # The GLAD sign up is dated before the cut off (> longer ago)
+        startDate.prepandemic > date_higher_awareness_march_1, # The GLAD sign up is dated before the cut off (> longer ago)
         true = 0, # Participant has not signed up before the pandemic,
@@
       if_else(
-        startDate.glad > date_uk_lockdown_march_23, # The GLAD sign up is dated before the cut off (> longer ago)
+        startDate.prepandemic > date_uk_lockdown_march_23, # The GLAD sign up is dated before the cut off (> longer ago)
         true = 0, # Participant has not signed up before the pandemic,
@@
         difftime(           #this function does time1 - time2 as difftime(time1, time2...)
-          startDate.coping.glad,    #should be start date for COPING (time1)
-          startDate.glad),    #should be start date for GLAD (time2)
+          startDate.coping,    #should be start date for COPING (time1)
+          startDate.prepandemic),    #should be start date for GLAD (time2)
           units = c("days")  #can also be "secs", "mins", "hours", "weeks"
@@
   separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
-  mutate(ID = as.numeric(ID),
-         startDate.glad = startDate) %>% # Rename startDate
+  mutate(ID = as.numeric(ID)) %>%
   select(

### 2020-08-11 PANCHANGE_data_preprocessing2020-07-15.Rmd

@@
 ```{r Specify cohort}
-GLAD = FALSE
+GLAD = TRUE
 EDGI = FALSE
-NBR = TRUE
+NBR = FALSE
 RAMP = FALSE
@@
                         "Sample",
-                        "startDate.edgi",
+                        "startDate.prepandemic",
                         "Age_uncleaned",
@@
       Age_uncleaned = demographics.how_old_are_you_now.txt, # Age
-      Gender = demographics.which_gender_do_you_identify_with, # Gender
-      Sex = demographics.select_questionnaire_items_medical, #Sex
-      EduYrs = demographics.school_education_school_years.txt, # Years in education
+      Gender = demographics.what_gender_do_you_identify_with, # Gender (which [GLAD] vs what [EDGI])
+      Sex = demographics.select_questionnaire_items_birth, #Sex (different to GLAD)
+      EduYrs = demographics.university_education_attend_school.txt, # Years in education (different to GLAD)
       demographics.college_or_university_degree, # level of education - univeristy
@@
 
-```{r nbr copy gad}
-if(NBR == TRUE){
+```{r glad copy gad}
+if(GLAD == TRUE){
 gad.raw.id <- glad.gad.raw.id
@@
 ```{r edgi gad cleaning}
+if(EDGI == TRUE){
 exclude_cols <- c("Sample",
@@
 dim(edgi.gad.raw)[1]-dim(edgi.gad.raw.id)[1]
+}
 ```
@@
 ```{r nbr copy gad}
-if(NBR == TRUE){
+if(EDGI == TRUE){
   gad.raw.id <- edgi.gad.raw.id
@@
 gad.scored_items_prepan <- scoreItems(keys = gad.items_key_prepan,
-                                        items = glad.gad.raw.id[gad.items_prepan],
+                                        items = gad.raw.id[gad.items_prepan],
                                         totals = TRUE, 
@@
 # Add in column to tibble
-GADraw.id$gad.sum_score_prepan_raw <- gad.scored_items_prepan$scores
+gad.raw.id$gad.sum_score_prepan_raw <- gad.scored_items_prepan$scores
 
 # Look at values
-GADraw.id %>%
+gad.raw.id %>%
   descr(gad.sum_score_prepan_raw,
@@
 ```{r gad prepan missingness}
-glad.gad.raw.id <- gad.raw.id %>%
+gad.raw.id <- gad.raw.id %>%
   mutate(

### 2020-08-11 PANCHANGE_data_preprocessing2020-07-15.Rmd
added if statements to glad.gad (prepan)

@@
 ```{r glad gad cleaning}
+if(GLAD ==TRUE){
 exclude_cols <- c("Sample",
                   "ID")
-
 glad.gad.raw.id <- glad.gad.raw %>%
@@
 dim(glad.gad.raw)[1]-dim(glad.gad.raw.id)[1]
+}
 ```
@@
 if(GLAD == TRUE){
-gad.raw.id <- glad.gad.raw.id
+prepan.gad.raw.id <- glad.gad.raw.id
 }
@@
 if(EDGI == TRUE){
-  gad.raw.id <- edgi.gad.raw.id
+  prepan.gad.raw.id <- edgi.gad.raw.id
 }
@@
 ```{r gad sum score prepan raw}
+if(GLAD ==TRUE | EDGI == TRUE){
 # Create vector with scoring key: If the item is reversed coded use -1. 
@@
 gad.scored_items_prepan <- scoreItems(keys = gad.items_key_prepan,
-                                        items = gad.raw.id[gad.items_prepan],
+                                        items = prepan.gad.raw.id[gad.items_prepan],
                                         totals = TRUE, 
@@
 # Add in column to tibble
-gad.raw.id$gad.sum_score_prepan_raw <- gad.scored_items_prepan$scores
+prepan.gad.raw.id$gad.sum_score_prepan_raw <- gad.scored_items_prepan$scores
 
 # Look at values
-gad.raw.id %>%
+prepan.gad.raw.id %>%
   descr(gad.sum_score_prepan_raw,
@@
         )
+}
 ```
@@
 ```{r gad prepan missingness}
-gad.raw.id <- gad.raw.id %>%
+if(GLAD ==TRUE | EDGI == TRUE){
+prepan.gad.raw.id <- prepan.gad.raw.id %>%
   mutate(
@@
 
-gad.raw.id %>%
+prepan.gad.raw.id %>%
   freq(na_per_person_gad_prepan,
        cumul = F)
+}
 ```
@@
 ```{r gad prepan sum score if missigng items set to NA}
-gad.raw.id <- gad.raw.id %>%
+if(GLAD ==TRUE | EDGI == TRUE){
+prepan.gad.raw.id <- prepan.gad.raw.id %>%
   mutate(
@@
 
-gad.raw.id %>%
+prepan.gad.raw.id %>%
   descr(gad.sum_score_prepan_raw, stats = "common")
 
-gad.raw.id %>%
+prepan.gad.raw.id %>%
   descr(gad.sum_score_prepan, stats = "common")
+}
 ```
@@
 ```{r glad gad head}
-head(gad.raw.id)
+if(GLAD ==TRUE | EDGI == TRUE){
+head(prepan.gad.raw.id)
+}
 ```
@@
 ```{r glad gad summary}
+if(GLAD ==TRUE | EDGI == TRUE){
 summarytools::dfSummary(
-  gad.raw.id,
+  prepan.gad.raw.id,
   graph.col = F,
@@
   labels.col = F)
+}
 ```
@@
 
-```{r glad pcl cols}
+```{r glad prepandemic pcl cols}
+if(GLAD == TRUE) {
 glad.pcl.raw <- readRDS(file = paste0(data.raw_path,"/glad/pcl_glad.rds"))
@@
 colnames(glad.pcl.raw)
-```
-
-```{r glad pcl cleaning}
+}
+```
+
+```{r glad prepandemic pcl cleaning}
+if(GLAD == TRUE) {
 glad.pcl.raw.id <- glad.pcl.raw %>%
@@
 dim(glad.pcl.raw)[1]-dim(glad.pcl.raw.id)[1]
+}
+```
+
+```{r glad pcl copy}
+if(GLAD == TRUE) {
+  prepan.pcl.raw.id <- glad.pcl.raw.id
+}
+```
+
+# edgi pcl
+
+```{r edgi pcl cols}
+if(EDGI == TRUE) {
+  edgi.pcl.raw <- readRDS(file = paste0(data.raw_path,"/edgi/pcl_edgi.rds"))
+  dim(edgi.pcl.raw)
+  colnames(edgi.pcl.raw)
+}
+```
+
+```{r edgi pcl cleaning}
+if(EDGI == TRUE) {
+  edgi.pcl.raw.id <- edgi.pcl.raw %>%
+    drop_na(externalDataReference) %>% # Drop NAs
+    distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
+    separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
+    mutate(ID = as.numeric(ID),
+           startDate.prepandemic = startDate) %>% # Rename startDate
+    select(
+      Sample, # Sample
+      ID, # ID
+      pcl.stressful_experience_repeated_images_prepan = pcl.stressful_experience_repeated_images,
+      pcl.stressful_experience_upset_reminded_prepan = pcl.stressful_experience_upset_reminded,
+      pcl.stressful_situation_avoiding_activities_prepan = pcl.stressful_situation_avoiding_activities,
+      pcl.cut_people_feeling_distant_prepan = pcl.cut_people_feeling_distant,
+      pcl.feeling_irritable_or_having_angry_outbursts_prepan = pcl.feeling_irritable_or_having_angry_outbursts,
+      pcl.difficulty_concentrating_prepan = pcl.difficulty_concentrating
+    ) %>%
+    add_numeric(., exclude = exclude_cols) %>%
+    mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
+    mutate_if(is.numeric, ~na_if(., -99)) %>%
+    mutate_if(is.numeric, ~na_if(., -77)) %>%
+    mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
+    mutate_if(is.factor, ~na_if(., "Don't know")) %>%
+    mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
+    mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
+    mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
+    mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
+    mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
+    mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
+
+  # Inspect dimensions
+  dim(edgi.pcl.raw.id)
+  # Inspect colnames
+  colnames(edgi.pcl.raw.id)
+  #Differences
+  dim(edgi.pcl.raw)[1]-dim(edgi.pcl.raw.id)[1]
+}
+```
+
+```{r edgi pcl copy}
+if(EDGI == TRUE) {
+  prepan.pcl.raw.id <- edgi.pcl.raw.id
+}
 ```
@@
 pcl.scored_items_prepan <- scoreItems(keys = pcl.items_key_prepan,
-                                        items = glad.pcl.raw.id[pcl.items_prepan],
+                                        items = prepan.pcl.raw.id[pcl.items_prepan],
                                         totals = TRUE, 
@@
 # Add in column to tibble
-glad.pcl.raw.id$pcl.sum_score_prepan_raw <- pcl.scored_items_prepan$scores
+prepan.pcl.raw.id$pcl.sum_score_prepan_raw <- pcl.scored_items_prepan$scores
 
 # Look at values
-glad.pcl.raw.id %>%
+prepan.pcl.raw.id %>%
   descr(pcl.sum_score_prepan_raw,

### 2020-08-11 PANCHANGE_data_preprocessing2020-07-15.Rmd
if statement added for pcl prepan

@@
 if(GLAD == TRUE) {
+exclude_cols <- c("Sample",
+                  "ID")
 glad.pcl.raw.id <- glad.pcl.raw %>%
@@
 ```{r pcl sum score prepan}
+if(GLAD == TRUE | EDGI == TRUE){
 # Create vector with scoring key: If the item is reversed coded use -1. 
@@
 ```{r pcl prepan missingness}
-glad.pcl.raw.id <- glad.pcl.raw.id %>%
+if(GLAD == TRUE | EDGI == TRUE){
+prepan.pcl.raw.id <- prepan.pcl.raw.id %>%
   mutate(
@@
 
-glad.pcl.raw.id %>%
+prepan.pcl.raw.id %>%
   freq(na_per_person_pcl_prepan,
        cumul = F)
+}
 ```
@@
 ```{r pcl prepan sum score if missigng items set to NA}
-glad.pcl.raw.id <- glad.pcl.raw.id %>%
+if(GLAD == TRUE | EDGI == TRUE){
+prepan.pcl.raw.id <- prepan.pcl.raw.id %>%
   mutate(
@@
 
-glad.pcl.raw.id %>%
+prepan.pcl.raw.id %>%
   descr(pcl.sum_score_prepan_raw, stats = "common")
 
-glad.pcl.raw.id %>%
+prepan.pcl.raw.id %>%
   descr(pcl.sum_score_prepan, stats = "common")
+}
 ```
@@
 ```{r glad pcl head}
-head(glad.pcl.raw.id)
+if(GLAD == TRUE | EDGI == TRUE){
+head(prepan.pcl.raw.id)
+}
 ```
@@
 ```{r glad pcl summary}
+if(GLAD == TRUE | EDGI == TRUE){
 summarytools::dfSummary(
-  glad.pcl.raw.id,
+  prepan.pcl.raw.id,
   graph.col = F,
   valid.col = F, labels.col = F)
+}
 ```
@@
 ```{r glad phq cleaning}
+if(GLAD == TRUE){
 glad.phq.raw.id <- glad.phq.raw %>%
@@
 dim(glad.phq.raw)[1]-dim(glad.phq.raw.id)[1]
+}
 ```

### 2020-08-11 PANCHANGE_data_preprocessing2020-07-15.Rmd
if statement added for phq prepan

@@
 
-```{r glad pcl copy}
+```{r glad pcl prepan copy}
 if(GLAD == TRUE) {
@@
 
-```{r edgi pcl copy}
+```{r edgi pcl prepan copy}
 if(EDGI == TRUE) {
@@
 ```{r glad phq cols}
+if(GLAD == TRUE){
 glad.phq.raw <- readRDS(file = paste0(data.raw_path, "/glad/phq_glad.rds"))
@@
 colnames(glad.phq.raw)
+}
 ```
@@
 
+```{r glad phq prepan copy}
+if(GLAD == TRUE) {
+  prepan.phq.raw.id <- glad.phq.raw.id
+}
+```
+
+# edgi phq
+
+```{r edgi phq cols}
+if(EDGI == TRUE){
+  edgi.phq.raw <- readRDS(file = paste0(data.raw_path, "/edgi/phq_edgi.rds"))
+  dim(edgi.phq.raw)
+  colnames(edgi.phq.raw)
+}
+```
+
+```{r edgi phq cleaning}
+if(EDGI == TRUE){
+  edgi.phq.raw.id <- edgi.phq.raw %>%
+    drop_na(externalDataReference) %>% # Drop NAs
+    distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
+    separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
+    mutate(ID = as.numeric(ID),
+           startDate.prepandemic = startDate) %>% # Rename startDate
+    select(
+      Sample, # Sample
+      ID, # ID
+      phq.little_interest_or_pleasure_in_doing_things_prepan = phq.little_interest_or_pleasure_in_doing_things,
+      phq.feeling_down_depressed_or_hopeless_prepan = phq.feeling_down_depressed_or_hopeless,
+      phq.staying_asleep_sleeping_trouble_prepan = phq.staying_asleep_sleeping_trouble,
+      phq.feeling_tired_or_having_little_energy_prepan = phq.feeling_tired_or_having_little_energy,
+      phq.poor_appetite_or_overeating_prepan = phq.poor_appetite_or_overeating,
+      phq.feeling_bad_failure_family_prepan = phq.feeling_bad_failure_family,
+      phq.trouble_concentrating_reading_newspaper_prepan = phq.trouble_concentrating_reading_newspaper,
+      phq.moving_fidgety_noticed_opposite_prepan = phq.moving_fidgety_noticed_opposite,
+      phq.dead_hurting_thoughts_prepan = phq.dead_hurting_thoughts
+    ) %>%
+    add_numeric(., exclude = exclude_cols) %>%
+    mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
+    mutate_if(is.numeric, ~na_if(., -99)) %>%
+    mutate_if(is.numeric, ~na_if(., -77)) %>%
+    mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
+    mutate_if(is.factor, ~na_if(., "Don't know")) %>%
+    mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
+    mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
+    mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
+    mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
+    mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
+    mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
+
+  # Inspect dimensions
+  dim(edgi.phq.raw.id)
+  # Inspect colnames
+  colnames(edgi.phq.raw.id)
+  #Differences
+  dim(edgi.phq.raw)[1]-dim(edgi.phq.raw.id)[1]
+}
+```
+
+```{r edgi phq prepan copy}
+if(EDGI == TRUE) {
+  prepan.phq.raw.id <- edgi.phq.raw.id
+}
+```
+
 Calculate sum score for PHQ-9
@@
 ```{r phq sum score prepan}
+if(GLAD == TRUE | EDGI == TRUE) {
 # Create vector with scoring key: If the item is reversed coded use -1. 
@@
 phq.scored_items_prepan <- scoreItems(keys = phq.items_key_prepan,
-                                        items = glad.phq.raw.id[phq.items_prepan],
+                                        items = prepan.phq.raw.id[phq.items_prepan],
                                         totals = TRUE, 
@@
 # Add in column to tibble
-glad.phq.raw.id$phq.sum_score_prepan_raw <- phq.scored_items_prepan$scores
+prepan.phq.raw.id$phq.sum_score_prepan_raw <- phq.scored_items_prepan$scores
 
 # Look at values
-glad.phq.raw.id %>%
+prepan.phq.raw.id %>%
   descr(phq.sum_score_prepan_raw,
@@
 ```{r phq prepan missingness}
-glad.phq.raw.id <- glad.phq.raw.id %>%
+prepan.phq.raw.id <- prepan.phq.raw.id %>%
   mutate(
@@
 
-glad.phq.raw.id %>%
+prepan.phq.raw.id %>%
   freq(na_per_person_phq_prepan,
@@
 ```{r phq prepan missingness 8 items}
-glad.phq.raw.id <- glad.phq.raw.id %>%
+prepan.phq.raw.id <- prepan.phq.raw.id %>%
   mutate(
@@
 
-glad.phq.raw.id %>%
+prepan.phq.raw.id %>%
   freq(phq.missing_only_suicide_item_prepan,
@@
 ```{r phq prepan sum score if missigng items set to NA - all items}
-glad.phq.raw.id <- glad.phq.raw.id %>%
+prepan.phq.raw.id <- prepan.phq.raw.id %>%
   mutate(
@@
 
-glad.phq.raw.id %>%
+prepan.phq.raw.id %>%
   descr(phq.sum_score_prepan_raw, stats = "common")
 
-glad.phq.raw.id %>%
+prepan.phq.raw.id %>%
   descr(phq.sum_score_prepan, stats = "common")

### 2020-08-11 PANCHANGE_data_preprocessing2020-07-15.Rmd

@@
 
+# eclude cols
+
+```{r cols to exclude}
+exclude_cols <- c("Sample",
+                  "ID")
+```
+
 # glad pcl
@@
 ```{r phq prepan missingness}
+if(GLAD == TRUE | EDGI == TRUE) {
 prepan.phq.raw.id <- prepan.phq.raw.id %>%
@@
        cumul = F)
+}
 ```
@@
 ```{r phq prepan missingness 8 items}
+if(GLAD == TRUE | EDGI == TRUE) {
 prepan.phq.raw.id <- prepan.phq.raw.id %>%
@@
 ```{r phq prepan sum score if missigng items set to NA - all items}
+if(GLAD == TRUE | EDGI == TRUE) {
 prepan.phq.raw.id <- prepan.phq.raw.id %>%
@@
   descr(phq.sum_score_prepan, stats = "common")
+}
 ```
@@
 ```{r phq prepan sum score if missigng items set to NA - 8 items}
-glad.phq.raw.id <- glad.phq.raw.id %>%
+if(GLAD == TRUE | EDGI == TRUE) {
+prepan.phq.raw.id <- prepan.phq.raw.id %>%
   mutate(
@@
 
-glad.phq.raw.id %>%
+prepan.phq.raw.id %>%
   descr(phq.sum_score_8items_prepan, stats = "common")
 
-glad.phq.raw.id %>%
+prepan.phq.raw.id %>%
   descr(phq.sum_score_8items_prepan, stats = "common")
+}
 ```
@@
 ```{r glad phq head}
-head(glad.phq.raw.id)
+if(GLAD == TRUE | EDGI == TRUE) {
+head(prepan.phq.raw.id)
+}
 ```
@@
 ```{r glad phq summary}
+if(GLAD == TRUE | EDGI == TRUE) {
 summarytools::dfSummary(
-  glad.phq.raw.id,
+  prepan.phq.raw.id,
   graph.col = F,
@@
 ```{r glad ocir cols}
+if(GLAD == TRUE){
 glad.ocir.raw <- readRDS(file = paste0(data.raw_path, "/glad/ocir_glad.rds"))
@@
 colnames(glad.ocir.raw)
+}
 ```
@@
 ```{r glad ocir cleaning}
+if(GLAD == TRUE){
 glad.ocir.raw.id <- glad.ocir.raw %>%
@@
 dim(glad.ocir.raw)[1]-dim(glad.ocir.raw.id)[1]
+}
+```
+
+```{r glad ocir prepan copy}
+if(GLAD == TRUE) {
+  prepan.ocir.raw.id <- glad.ocir.raw.id
+}
+```
+
+# edgi ocir
+
+```{r edgi ocir cols}
+if(EDGI == TRUE){
+  edgi.ocir.raw <- readRDS(file = paste0(data.raw_path, "/edgi/ocir_edgi.rds"))
+  dim(edgi.ocir.raw)
+  colnames(edgi.ocir.raw)
+}
+```
+
+```{r edgi ocir cleaning}
+if(EDGI == TRUE){
+  edgi.ocir.raw.id <- edgi.ocir.raw %>%
+    drop_na(externalDataReference) %>% # Drop NAs
+    distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
+    separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
+    mutate(ID = as.numeric(ID),
+           startDate.prepandemic = startDate) %>% # Rename startDate
+    select(
+      Sample, # Sample
+      ID, # ID
+      ocir.i_repeatedly_check_doors_windows_drawers_etc_prepan = ocir.i_repeatedly_check_doors_windows_drawers_etc.,
+      ocir.arranged_things_change_upset_prepan = ocir.arranged_things_change_upset,
+      ocir.repeat_feel_numbers_prepan = ocir.repeat_feel_numbers,
+      ocir.clean_simply_wash_feel_prepan = ocir.clean_simply_wash_feel,
+      ocir.mind_upset_unpleasant_thoughts_prepan = ocir.mind_upset_unpleasant_thoughts,
+      ocir.afraid_avoid_throwing_things_prepan = ocir.afraid_avoid_throwing_things,
+      ocir.light_switches_water_taps_prepan = ocir.light_switches_water_taps,
+      ocir.arranged_things_prepan = ocir.arranged_things,
+      ocir.good_feel_bad_numbers_prepan = ocir.good_feel_bad_numbers,
+      ocir.hands_longer_wash_prepan = ocir.hands_longer_wash,
+      ocir.saved_things_prepan = ocir.saved_things,
+      ocir.frequently_difficulty_rid_nasty_prepan = ocir.frequently_difficulty_rid_nasty,
+      ocir.i_check_things_more_often_than_necessary_prepan = ocir.i_check_things_more_often_than_necessary.,
+      ocir.arranged_properly_objects_upset_prepan = ocir.arranged_properly_objects_upset,
+      ocir.feel_compelled_count_things_prepan = ocir.feel_compelled_count_things,
+      ocir.strangers_touch_touched_difficult_prepan = ocir.strangers_touch_touched_difficult,
+      ocir.control_difficult_find_thoughts_prepan = ocir.control_difficult_find_thoughts,
+      ocir.i_collect_things_i_dont_need_prepan = ocir.i_collect_things_i_dont_need
+    ) %>%
+    add_numeric(., exclude = exclude_cols) %>%
+    mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
+    mutate_if(is.numeric, ~na_if(., -99)) %>%
+    mutate_if(is.numeric, ~na_if(., -77)) %>%
+    mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
+    mutate_if(is.factor, ~na_if(., "Don't know")) %>%
+    mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
+    mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
+    mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
+    mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
+    mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
+    mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
+
+  # Inspect dimensions
+  dim(edgi.ocir.raw.id)
+  # Inspect colnames
+  colnames(edgi.ocir.raw.id)
+  #Differences
+  dim(edgi.ocir.raw)[1]-dim(edgi.ocir.raw.id)[1]
+}
+```
+
+```{r edgi ocir prepan copy}
+if(EDGI == TRUE) {
+  prepan.ocir.raw.id <- edgi.ocir.raw.id
+}
 ```
@@
 ```{r ocir sum score prepan}
+if(GLAD == TRUE | EDGI == TRUE) {
 # Create vector with scoring key: If the item is reversed coded use -1. 
@@
 ocir.scored_items_prepan <- scoreItems(keys = ocir.items_key_prepan,
-                                        items = glad.ocir.raw.id[ocir.items_prepan],
+                                        items = prepan.ocir.raw.id[ocir.items_prepan],
                                         totals = TRUE, 
@@
 # Add in column to tibble
-glad.ocir.raw.id$ocir.sum_score_prepan <- ocir.scored_items_prepan$scores
+prepan.ocir.raw.id$ocir.sum_score_prepan <- ocir.scored_items_prepan$scores
 
 # Look at values
-glad.ocir.raw.id %>%
+prepan.ocir.raw.id %>%
   descr(ocir.sum_score_prepan,
@@
 ```{r ocir prepan missingness}
-glad.ocir.raw.id <- glad.ocir.raw.id %>%
+if(GLAD == TRUE | EDGI == TRUE) {
+prepan.ocir.raw.id <- prepan.ocir.raw.id %>%
   mutate(
@@
 
-glad.ocir.raw.id %>%
+prepan.ocir.raw.id %>%
   freq(na_per_person_ocir_prepan,
        cumul = F)
+}
 ```
@@
 ```{r glad ocir head}
-head(glad.ocir.raw.id)
+if(GLAD == TRUE | EDGI == TRUE) {
+head(prepan.ocir.raw.id)
+}
 ```
@@
 ```{r glad ocir summary}
+if(GLAD == TRUE | EDGI == TRUE) {
 summarytools::dfSummary(
-  glad.ocir.raw.id,
+  prepan.ocir.raw.id,
   graph.col = F,

### 2020-08-11 PANCHANGE_data_preprocessing2020-07-15.Rmd
renamed coping.glad

@@
 
-coping.glad.gad.raw.id <- coping.glad.gad.raw %>%
+coping.gad.raw.id <- coping.gad.raw %>%
   drop_na(externalDataReference) %>% # Drop NAs
@@
     ID, # ID
-    startDate.coping.glad = startDate,
+    startDate.coping = startDate,
     gad.problems_made_difficult_care, # Impairment
@@
 # Inspect dimensions
-dim(coping.glad.gad.raw.id)
+dim(coping.gad.raw.id)
 # Inspect colnames
-colnames(coping.glad.gad.raw.id)
+colnames(coping.gad.raw.id)
 #Differences
-dim(coping.glad.gad.raw)[1]-dim(coping.glad.gad.raw.id)[1]
+dim(coping.gad.raw)[1]-dim(coping.gad.raw.id)[1]
 ```
@@
 gad.scored_items_retro <- scoreItems(keys = gad.items_key_retro,
-                                        items = coping.glad.gad.raw.id[gad.items_retro],
+                                        items = coping.gad.raw.id[gad.items_retro],
                                         totals = TRUE, 
@@
 # Add in column to tibble
-coping.glad.gad.raw.id$gad.sum_score_retro_raw <- gad.scored_items_retro$scores
+coping.gad.raw.id$gad.sum_score_retro_raw <- gad.scored_items_retro$scores
 
 # Look at values
-coping.glad.gad.raw.id %>%
+coping.gad.raw.id %>%
   descr(gad.sum_score_retro_raw,
@@
 gad.scored_items_base <- scoreItems(keys = gad.items_key_base,
-                                        items = coping.glad.gad.raw.id[gad.items_base],
+                                        items = coping.gad.raw.id[gad.items_base],
                                         totals = TRUE, 
@@
 # Add in column to tibble
-coping.glad.gad.raw.id$gad.sum_score_base_raw <- gad.scored_items_base$scores
+coping.gad.raw.id$gad.sum_score_base_raw <- gad.scored_items_base$scores
 
 # Look at values
-coping.glad.gad.raw.id %>%
+coping.gad.raw.id %>%
   descr(gad.sum_score_base_raw,
@@
 ```{r coping gad baseline missingness}
-coping.glad.gad.raw.id <- coping.glad.gad.raw.id %>%
+coping.gad.raw.id <- coping.gad.raw.id %>%
   mutate(
@@
 
-coping.glad.gad.raw.id %>%
+coping.gad.raw.id %>%
   freq(na_per_person_gad_base, cumul = F) #have a look at the frequency
@@
 ```{r coping gad retrospective missingness}
-coping.glad.gad.raw.id <- coping.glad.gad.raw.id %>%
+coping.gad.raw.id <- coping.gad.raw.id %>%
   mutate(
@@
 
-coping.glad.gad.raw.id %>%
+coping.gad.raw.id %>%
   freq(na_per_person_gad_retro, cumul = F) #have a look at the frequency
@@
 ```{r coping gad base sum score if missigng items set to NA}
-coping.glad.gad.raw.id <- coping.glad.gad.raw.id %>%
+coping.gad.raw.id <- coping.gad.raw.id %>%
   mutate(
@@
 
-coping.glad.gad.raw.id %>%
+coping.gad.raw.id %>%
   descr(gad.sum_score_base_raw, stats = "common")
 
-coping.glad.gad.raw.id %>%
+coping.gad.raw.id %>%
   descr(gad.sum_score_base, stats = "common")
@@
 ```{r coping gad retro sum score if missigng items set to NA}
-coping.glad.gad.raw.id <- coping.glad.gad.raw.id %>%
+coping.gad.raw.id <- coping.gad.raw.id %>%
   mutate(
@@
 
-coping.glad.gad.raw.id %>%
+coping.gad.raw.id %>%
   descr(gad.sum_score_retro_raw, stats = "common")
 
-coping.glad.gad.raw.id %>%
+coping.gad.raw.id %>%
   descr(gad.sum_score_retro, stats = "common")
@@
 ```{r coping glad gad head}
-head(coping.glad.gad.raw.id)
+head(coping.gad.raw.id)
 ```
@@
 summarytools::dfSummary(
-  coping.glad.gad.raw.id,
+  coping.gad.raw.id,
   graph.col = F,
@@
 pcl.scored_items_retro <- scoreItems(keys = pcl.items_key_retro,
-                                     items = coping.glad.pcl.raw.id[pcl.items_retro],
+                                     items = coping.pcl.raw.id[pcl.items_retro],
                                      totals = TRUE, 
@@
 # Add in column to tibble
-coping.glad.pcl.raw.id$pcl.sum_score_retro_raw <- pcl.scored_items_retro$scores
+coping.pcl.raw.id$pcl.sum_score_retro_raw <- pcl.scored_items_retro$scores
 
 # Look at values
-coping.glad.pcl.raw.id %>%
+coping.pcl.raw.id %>%
   descr(pcl.sum_score_retro_raw,
@@
 pcl.scored_items_base <- scoreItems(keys = pcl.items_key_base,
-                                    items = coping.glad.pcl.raw.id[pcl.items_base],
+                                    items = coping.pcl.raw.id[pcl.items_base],
                                     totals = TRUE, 
@@
 # Add in column to tibble
-coping.glad.pcl.raw.id$pcl.sum_score_base_raw <- pcl.scored_items_base$scores
+coping.pcl.raw.id$pcl.sum_score_base_raw <- pcl.scored_items_base$scores
 
 # Look at values
-coping.glad.pcl.raw.id %>%
+coping.pcl.raw.id %>%
   descr(pcl.sum_score_base_raw,
@@
 ```{r coping pcl baseline missingness}
-coping.glad.pcl.raw.id <- coping.glad.pcl.raw.id %>%
+coping.pcl.raw.id <- coping.pcl.raw.id %>%
   mutate(
@@
 
-coping.glad.pcl.raw.id %>%
+coping.pcl.raw.id %>%
   freq(na_per_person_pcl_base, cumul = F) #have a look at the frequency
@@
 ```{r coping pcl retrospective missingness}
-coping.glad.pcl.raw.id <- coping.glad.pcl.raw.id %>%
+coping.pcl.raw.id <- coping.pcl.raw.id %>%
   mutate(
@@
 
-coping.glad.pcl.raw.id %>%
+coping.pcl.raw.id %>%
   freq(na_per_person_pcl_retro, cumul = F) #have a look at the frequency
@@
 ```{r coping pcl base sum score if missigng items set to NA}
-coping.glad.pcl.raw.id <- coping.glad.pcl.raw.id %>%
+coping.pcl.raw.id <- coping.pcl.raw.id %>%
   mutate(
@@
 
-coping.glad.pcl.raw.id %>%
+coping.pcl.raw.id %>%
   descr(pcl.sum_score_base_raw, stats = "common")
 
-coping.glad.pcl.raw.id %>%
+coping.pcl.raw.id %>%
   descr(pcl.sum_score_base, stats = "common")
@@
 ```{r coping pcl retro sum score if missigng items set to NA}
-coping.glad.pcl.raw.id <- coping.glad.pcl.raw.id %>%
+coping.pcl.raw.id <- coping.pcl.raw.id %>%
   mutate(
@@
 
-coping.glad.pcl.raw.id %>%
+coping.pcl.raw.id %>%
   descr(pcl.sum_score_retro_raw, stats = "common")
 
-coping.glad.pcl.raw.id %>%
+coping.pcl.raw.id %>%
   descr(pcl.sum_score_retro, stats = "common")
@@
 ```{r coping glad pcl head}
-head(coping.glad.pcl.raw.id)
+head(coping.pcl.raw.id)
 ```
@@
 summarytools::dfSummary(
-  coping.glad.pcl.raw.id,
+  coping.pcl.raw.id,
   graph.col = F,
@@
 phq.scored_items_retro <- scoreItems(keys = phq.items_key_retro,
-                                     items = coping.glad.phq.raw.id[phq.items_retro],
+                                     items = coping.phq.raw.id[phq.items_retro],
                                      totals = TRUE, 
@@
 # Add in column to tibble
-coping.glad.phq.raw.id$phq.sum_score_retro_raw <- phq.scored_items_retro$scores
+coping.phq.raw.id$phq.sum_score_retro_raw <- phq.scored_items_retro$scores
 
 # Look at values
-coping.glad.phq.raw.id %>%
+coping.phq.raw.id %>%
   descr(phq.sum_score_retro_raw,
@@
 phq.scored_items_base <- scoreItems(keys = phq.items_key_base,
-                                    items = coping.glad.phq.raw.id[phq.items_base],
+                                    items = coping.phq.raw.id[phq.items_base],
                                     totals = TRUE, 
@@
 # Add in column to tibble
-coping.glad.phq.raw.id$phq.sum_score_base_raw <- phq.scored_items_base$scores
+coping.phq.raw.id$phq.sum_score_base_raw <- phq.scored_items_base$scores
 
 # Look at values
-coping.glad.phq.raw.id %>%
+coping.phq.raw.id %>%
   descr(phq.sum_score_base_raw,
@@
 ```{r coping phq retro missingness}
-coping.glad.phq.raw.id <- coping.glad.phq.raw.id %>%
+coping.phq.raw.id <- coping.phq.raw.id %>%
   mutate(
@@
 
-coping.glad.phq.raw.id %>%
+coping.phq.raw.id %>%
   freq(na_per_person_phq_retro, cumul = F) #have a look at the frequency
@@
 ```{r coping phq retro missingness 8 items}
-coping.glad.phq.raw.id <- coping.glad.phq.raw.id %>%
+coping.phq.raw.id <- coping.phq.raw.id %>%
   mutate(
@@
 
-coping.glad.phq.raw.id %>%
+coping.phq.raw.id %>%
   freq(phq.missing_only_suicide_item_retro,
@@
 ```{r coping phq base missingness}
-coping.glad.phq.raw.id <- coping.glad.phq.raw.id %>%
+coping.phq.raw.id <- coping.phq.raw.id %>%
   mutate(
@@
 
-coping.glad.phq.raw.id %>%
+coping.phq.raw.id %>%
   freq(na_per_person_phq_base, cumul = F) #have a look at the frequency
@@
 ```{r coping phq base missingness 8 items}
-coping.glad.phq.raw.id <- coping.glad.phq.raw.id %>%
+coping.phq.raw.id <- coping.phq.raw.id %>%
   mutate(
@@
 
-coping.glad.phq.raw.id %>%
+coping.phq.raw.id %>%
   freq(phq.missing_only_suicide_item_base,
@@
 ```{r coping phq base sum score if missigng items set to NA}
-coping.glad.phq.raw.id <- coping.glad.phq.raw.id %>%
+coping.phq.raw.id <- coping.phq.raw.id %>%
   mutate(
@@
 
-coping.glad.phq.raw.id %>%
+coping.phq.raw.id %>%
   descr(phq.sum_score_base_raw, stats = "common")
 
-coping.glad.phq.raw.id %>%
+coping.phq.raw.id %>%
   descr(phq.sum_score_base, stats = "common")
@@
 ```{r phq base sum score if missigng items set to NA - 8 items}
-coping.glad.phq.raw.id <- coping.glad.phq.raw.id %>%
+coping.phq.raw.id <- coping.phq.raw.id %>%
   mutate(
@@
 
-coping.glad.phq.raw.id %>%
+coping.phq.raw.id %>%
   descr(phq.sum_score_8items_base, stats = "common")
@@
 ```{r coping phq retro sum score if missigng items set to NA}
-coping.glad.phq.raw.id <- coping.glad.phq.raw.id %>%
+coping.phq.raw.id <- coping.phq.raw.id %>%
   mutate(
@@
 
-coping.glad.phq.raw.id %>%
+coping.phq.raw.id %>%
   descr(phq.sum_score_retro_raw, stats = "common")
 
-coping.glad.phq.raw.id %>%
+coping.phq.raw.id %>%
   descr(phq.sum_score_retro, stats = "common")
@@
 ```{r phq retro sum score if missigng items set to NA - 8 items}
-coping.glad.phq.raw.id <- coping.glad.phq.raw.id %>%
+coping.phq.raw.id <- coping.phq.raw.id %>%
   mutate(
@@
 
-coping.glad.phq.raw.id %>%
+coping.phq.raw.id %>%
   descr(phq.sum_score_8items_retro, stats = "common")
@@
 ```{r coping glad phq head}
-head(coping.glad.phq.raw.id)
+head(coping.phq.raw.id)
 ```
@@
 summarytools::dfSummary(
-  coping.glad.phq.raw.id,
+  coping.phq.raw.id,
   graph.col = F,
@@
 ocir.scored_items_retro <- scoreItems(keys = ocir.items_key_retro,
-                                     items = coping.glad.ocir.raw.id[ocir.items_retro],
+                                     items = coping.ocir.raw.id[ocir.items_retro],
                                      totals = TRUE, 
@@
 # Add in column to tibble
-coping.glad.ocir.raw.id$ocir.sum_score_retro_raw <- ocir.scored_items_retro$scores
+coping.ocir.raw.id$ocir.sum_score_retro_raw <- ocir.scored_items_retro$scores
 
 # Look at values
-coping.glad.ocir.raw.id %>%
+coping.ocir.raw.id %>%
   descr(ocir.sum_score_retro_raw,
@@
 ocir.scored_items_base <- scoreItems(keys = ocir.items_key_base,
-                                    items = coping.glad.ocir.raw.id[ocir.items_base],
+                                    items = coping.ocir.raw.id[ocir.items_base],
                                     totals = TRUE, 
@@
 # Add in column to tibble
-coping.glad.ocir.raw.id$ocir.sum_score_base_raw <- ocir.scored_items_base$scores
+coping.ocir.raw.id$ocir.sum_score_base_raw <- ocir.scored_items_base$scores
 
 # Look at values
-coping.glad.ocir.raw.id %>%
+coping.ocir.raw.id %>%
   descr(ocir.sum_score_base_raw,
@@
 ```{r coping ocir retro missingness}
-coping.glad.ocir.raw.id <- coping.glad.ocir.raw.id %>%
+coping.ocir.raw.id <- coping.ocir.raw.id %>%
   mutate(
@@
 
-coping.glad.ocir.raw.id %>%
+coping.ocir.raw.id %>%
   freq(na_per_person_ocir_retro, cumul = F) #have a look at the frequency
@@
 ```{r coping ocir base missingness}
-coping.glad.ocir.raw.id <- coping.glad.ocir.raw.id %>%
+coping.ocir.raw.id <- coping.ocir.raw.id %>%
   mutate(
@@
 
-coping.glad.ocir.raw.id %>%
+coping.ocir.raw.id %>%
   freq(na_per_person_ocir_base, cumul = F) #have a look at the frequency
@@
 ```{r coping ocir base sum score if missigng items set to NA}
-coping.glad.ocir.raw.id <- coping.glad.ocir.raw.id %>%
+coping.ocir.raw.id <- coping.ocir.raw.id %>%
   mutate(
@@
 
-coping.glad.ocir.raw.id %>%
+coping.ocir.raw.id %>%
   descr(ocir.sum_score_base_raw, stats = "common")
 
-coping.glad.ocir.raw.id %>%
+coping.ocir.raw.id %>%
   descr(ocir.sum_score_base, stats = "common")
@@
 ```{r coping ocir retro sum score if missigng items set to NA}
-coping.glad.ocir.raw.id <- coping.glad.ocir.raw.id %>%
+coping.ocir.raw.id <- coping.ocir.raw.id %>%
   mutate(
@@
 
-coping.glad.ocir.raw.id %>%
+coping.ocir.raw.id %>%
   descr(ocir.sum_score_retro_raw, stats = "common")
 
-coping.glad.ocir.raw.id %>%
+coping.ocir.raw.id %>%
   descr(ocir.sum_score_retro, stats = "common")
@@
 ```{r coping glad ocir head}
-head(coping.glad.ocir.raw.id)
+head(coping.ocir.raw.id)
 ```
@@
 summarytools::dfSummary(
-  coping.glad.ocir.raw.id,
+  coping.ocir.raw.id,
   graph.col = F,
@@
   glad.phq.raw.id,
-  coping.glad.gad.raw.id,
-  coping.glad.pcl.raw.id,
-  coping.glad.phq.raw.id,
-  coping.glad.ocir.raw.id
+  coping.gad.raw.id,
+  coping.pcl.raw.id,
+  coping.phq.raw.id,
+  coping.ocir.raw.id
 )

### 2020-08-11 PANCHANGE_data_preprocessing2020-07-15.Rmd
fixed coping glad gad data read in

@@
 ```{r coping glad gad cols}
+if(GLAD == TRUE) {
 coping.glad.gad.raw <- readRDS(file = paste0(data.raw_path,"/glad/gad_coping_glad.rds"))
@@
 colnames(coping.glad.gad.raw)
+}
 ```
@@
 ```{r coping glad gad summary}
+if(GLAD == TRUE) {
 summarytools::dfSummary(
@@
 ```{r coping glad gad cleaning}
+if(GLAD == TRUE) {
 exclude_cols_coping_glad <- c(
@@
   separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
-  mutate(ID = as.numeric(ID),
-         startDate.coping = startDate) %>% # Rename startDate
+  mutate(ID = as.numeric(ID)
+         ) %>% 
   select(
@@
     ID, # ID
-    startDate.coping = startDate,
+    startDate.coping = startDate, # Rename startDate
     gad.problems_made_difficult_care, # Impairment
@@
 dim(coping.gad.raw)[1]-dim(coping.gad.raw.id)[1]
+}
+```
+
+```{r coping glad gad copy}
+if(GLAD == TRUE) {
+  prepan.ocir.raw.id <- glad.ocir.raw.id
+}
 ```

### 2020-08-11 PANCHANGE_data_preprocessing2020-07-15.Rmd
added coping gad

@@
 
-coping.gad.raw.id <- coping.gad.raw %>%
+coping.glad.gad.raw.id <- coping.glad.gad.raw %>%
   drop_na(externalDataReference) %>% # Drop NAs
@@
 # Inspect dimensions
-dim(coping.gad.raw.id)
+dim(coping.glad.gad.raw.id)
 # Inspect colnames
-colnames(coping.gad.raw.id)
+colnames(coping.glad.gad.raw.id)
 #Differences
-dim(coping.gad.raw)[1]-dim(coping.gad.raw.id)[1]
+dim(coping.glad.gad.raw)[1]-dim(coping.glad.gad.raw.id)[1]
 }
@@
 if(GLAD == TRUE) {
-  prepan.ocir.raw.id <- glad.ocir.raw.id
+  coping.gad.raw.id <- coping.glad.gad.raw.id
+}
+```
+
+```{r coping edgi gad cols}
+if(EDGI == TRUE) {
+  coping.edgi.gad.raw <- readRDS(file = paste0(data.raw_path,"/edgi/gad_coping_edgi.rds"))
+  dim(coping.edgi.gad.raw)
+  colnames(coping.edgi.gad.raw)
+}
+```
+
+```{r coping edgi gad summary}
+if(EDGI == TRUE) {
+  summarytools::dfSummary(
+    coping.edgi.gad.raw,
+    graph.col = F,
+    valid.col = F,
+    labels.col = F
+  )
+}
+```
+
+```{r coping edgi gad cleaning}
+if(EDGI == TRUE) {
+  exclude_cols_coping_edgi <- c(
+    "Sample",
+    "ID",
+    "startDate.coping"
+  )
+
+  coping.edgi.gad.raw.id <- coping.edgi.gad.raw %>%
+    drop_na(externalDataReference) %>% # Drop NAs
+    distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
+    separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
+    mutate(ID = as.numeric(ID)
+    ) %>% 
+    select(
+      Sample, # Sample
+      ID, # ID
+      startDate.coping = startDate, # Rename startDate
+      gad.problems_made_difficult_care, # Impairment
+      gad.pandemic_felt_feelings, # Comparison to before the pandemic (retro)
+      gad.feeling_nervous_anxious_or_on_edge_retro = gad.feeling_nervous_anxious_or_on_edge,
+      gad.control_worrying_stop_retro = gad.control_worrying_stop,
+      gad.worrying_too_much_about_different_things_retro = gad.worrying_too_much_about_different_things,
+      gad.trouble_relaxing_retro = gad.trouble_relaxing,
+      gad.sit_restless_hard_retro = gad.sit_restless_hard,
+      gad.becoming_easily_annoyed_or_irritable_retro = gad.becoming_easily_annoyed_or_irritable,
+      gad.awful_feeling_afraid_happen_retro = gad.awful_feeling_afraid_happen,
+      gad.feeling_nervous_anxious_or_on_edge_base = gad.feeling_nervous_anxious_or_on_edge.1,
+      gad.control_worrying_stop_base = gad.control_worrying_stop.1,
+      gad.worrying_too_much_about_different_things_base = gad.worrying_too_much_about_different_things.1,
+      gad.trouble_relaxing_base = gad.trouble_relaxing.1,
+      gad.sit_restless_hard_base = gad.sit_restless_hard.1,
+      gad.becoming_easily_annoyed_or_irritable_base = gad.becoming_easily_annoyed_or_irritable.1,
+      gad.awful_feeling_afraid_happen_base = gad.awful_feeling_afraid_happen.1
+    ) %>%
+    add_numeric(., exclude = exclude_cols_coping_edgi) %>%
+    mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
+    mutate_if(is.numeric, ~na_if(., -99)) %>%
+    mutate_if(is.numeric, ~na_if(., -77)) %>%
+    mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
+    mutate_if(is.factor, ~na_if(., "Don't know")) %>%
+    mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
+    mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
+    mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
+    mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
+    mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
+    mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
+
+  # Inspect dimensions
+  dim(coping.edgi.gad.raw.id)
+  # Inspect colnames
+  colnames(coping.edgi.gad.raw.id)
+  #Differences
+  dim(coping.edgi.gad.raw)[1]-dim(coping.edgi.gad.raw.id)[1]
+}
+```
+
+```{r coping edgi gad copy}
+if(EDGI == TRUE) {
+  coping.gad.raw.id <- coping.edgi.gad.raw.id
+}
+```
+
+```{r coping nbr gad cols}
+if(NBR == TRUE) {
+  coping.nbr.gad.raw <- readRDS(file = paste0(data.raw_path,"/nbr/gad_coping_nbr.rds"))
+  dim(coping.nbr.gad.raw)
+  colnames(coping.nbr.gad.raw)
+}
+```
+
+```{r coping nbr gad summary}
+if(NBR == TRUE) {
+  summarytools::dfSummary(
+    coping.nbr.gad.raw,
+    graph.col = F,
+    valid.col = F,
+    labels.col = F
+  )
+}
+```
+
+```{r coping nbr gad cleaning}
+if(NBR == TRUE) {
+  exclude_cols_coping_nbr <- c(
+    "Sample",
+    "ID",
+    "startDate.coping"
+  )
+
+  coping.nbr.gad.raw.id <- coping.nbr.gad.raw %>%
+    drop_na(externalDataReference) %>% # Drop NAs
+    distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
+    separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
+    mutate(ID = as.numeric(ID)
+    ) %>% 
+    select(
+      Sample, # Sample
+      ID, # ID
+      startDate.coping = startDate, # Rename startDate
+      gad.problems_made_difficult_care, # Impairment
+      gad.pandemic_felt_feelings, # Comparison to before the pandemic (retro)
+      gad.feeling_nervous_anxious_or_on_edge_retro = gad.feeling_nervous_anxious_or_on_edge,
+      gad.control_worrying_stop_retro = gad.control_worrying_stop,
+      gad.worrying_too_much_about_different_things_retro = gad.worrying_too_much_about_different_things,
+      gad.trouble_relaxing_retro = gad.trouble_relaxing,
+      gad.sit_restless_hard_retro = gad.sit_restless_hard,
+      gad.becoming_easily_annoyed_or_irritable_retro = gad.becoming_easily_annoyed_or_irritable,
+      gad.awful_feeling_afraid_happen_retro = gad.awful_feeling_afraid_happen,
+      gad.feeling_nervous_anxious_or_on_edge_base = gad.feeling_nervous_anxious_or_on_edge.1,
+      gad.control_worrying_stop_base = gad.control_worrying_stop.1,
+      gad.worrying_too_much_about_different_things_base = gad.worrying_too_much_about_different_things.1,
+      gad.trouble_relaxing_base = gad.trouble_relaxing.1,
+      gad.sit_restless_hard_base = gad.sit_restless_hard.1,
+      gad.becoming_easily_annoyed_or_irritable_base = gad.becoming_easily_annoyed_or_irritable.1,
+      gad.awful_feeling_afraid_happen_base = gad.awful_feeling_afraid_happen.1
+    ) %>%
+    add_numeric(., exclude = exclude_cols_coping_nbr) %>%
+    mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
+    mutate_if(is.numeric, ~na_if(., -99)) %>%
+    mutate_if(is.numeric, ~na_if(., -77)) %>%
+    mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
+    mutate_if(is.factor, ~na_if(., "Don't know")) %>%
+    mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
+    mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
+    mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
+    mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
+    mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
+    mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
+
+  # Inspect dimensions
+  dim(coping.nbr.gad.raw.id)
+  # Inspect colnames
+  colnames(coping.nbr.gad.raw.id)
+  #Differences
+  dim(coping.nbr.gad.raw)[1]-dim(coping.nbr.gad.raw.id)[1]
+}
+```
+
+```{r coping nbr gad copy}
+if(NBR == TRUE) {
+  coping.gad.raw.id <- coping.nbr.gad.raw.id
+}
+```
+
+```{r coping ramp gad cols}
+if(RAMP == TRUE) {
+  coping.ramp.gad.raw <- readRDS(file = paste0(data.raw_path,"/ramp/gad_coping_ramp.rds"))
+  dim(coping.ramp.gad.raw)
+  colnames(coping.ramp.gad.raw)
+}
+```
+
+```{r coping ramp gad summary}
+if(RAMP == TRUE) {
+  summarytools::dfSummary(
+    coping.ramp.gad.raw,
+    graph.col = F,
+    valid.col = F,
+    labels.col = F
+  )
+}
+```
+
+```{r coping ramp gad cleaning}
+if(RAMP == TRUE) {
+  exclude_cols_coping_ramp <- c(
+    "Sample",
+    "ID",
+    "startDate.coping"
+  )
+
+  coping.ramp.gad.raw.id <- coping.ramp.gad.raw %>%
+    drop_na(externalDataReference) %>% # Drop NAs
+    distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
+    separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
+    mutate(ID = as.numeric(ID)
+    ) %>% 
+    select(
+      Sample, # Sample
+      ID, # ID
+      startDate.coping = startDate, # Rename startDate
+      gad.problems_made_difficult_care, # Impairment
+      gad.pandemic_felt_feelings, # Comparison to before the pandemic (retro)
+      gad.feeling_nervous_anxious_or_on_edge_retro = gad.feeling_nervous_anxious_or_on_edge,
+      gad.control_worrying_stop_retro = gad.control_worrying_stop,
+      gad.worrying_too_much_about_different_things_retro = gad.worrying_too_much_about_different_things,
+      gad.trouble_relaxing_retro = gad.trouble_relaxing,
+      gad.sit_restless_hard_retro = gad.sit_restless_hard,
+      gad.becoming_easily_annoyed_or_irritable_retro = gad.becoming_easily_annoyed_or_irritable,
+      gad.awful_feeling_afraid_happen_retro = gad.awful_feeling_afraid_happen,
+      gad.feeling_nervous_anxious_or_on_edge_base = gad.feeling_nervous_anxious_or_on_edge.1,
+      gad.control_worrying_stop_base = gad.control_worrying_stop.1,
+      gad.worrying_too_much_about_different_things_base = gad.worrying_too_much_about_different_things.1,
+      gad.trouble_relaxing_base = gad.trouble_relaxing.1,
+      gad.sit_restless_hard_base = gad.sit_restless_hard.1,
+      gad.becoming_easily_annoyed_or_irritable_base = gad.becoming_easily_annoyed_or_irritable.1,
+      gad.awful_feeling_afraid_happen_base = gad.awful_feeling_afraid_happen.1
+    ) %>%
+    add_numeric(., exclude = exclude_cols_coping_ramp) %>%
+    mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
+    mutate_if(is.numeric, ~na_if(., -99)) %>%
+    mutate_if(is.numeric, ~na_if(., -77)) %>%
+    mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
+    mutate_if(is.factor, ~na_if(., "Don't know")) %>%
+    mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
+    mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
+    mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
+    mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
+    mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
+    mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
+
+  # Inspect dimensions
+  dim(coping.ramp.gad.raw.id)
+  # Inspect colnames
+  colnames(coping.ramp.gad.raw.id)
+  #Differences
+  dim(coping.ramp.gad.raw)[1]-dim(coping.ramp.gad.raw.id)[1]
+}
+```
+
+```{r coping ramp gad copy}
+if(RAMP == TRUE) {
+  coping.gad.raw.id <- coping.ramp.gad.raw.id
 }

### 2020-08-11 PANCHANGE_data_preprocessing2020-07-15.Rmd
added coping pcl data sets

@@
 
-# COPING GLAD: GAD-7
-
+# COPING GAD-7
+## GLAD
 ```{r coping glad gad cols}
@@
 
+## EDGI
 ```{r coping edgi gad cols}
@@
 
+## NBR
 ```{r coping nbr gad cols}
@@
 
+## RAMP
 ```{r coping ramp gad cols}
@@
 
+## Sum scores
 Calculate sum score for GAD-7 retrospective
@@
 
-Missigness
+## Missingness
 
@@
 
-# COPING GLAD: PCL-6
-
+# COPING: PCL-6
+
+## GLAD
 ```{r coping glad pcl cols}
@@
 
+```{r coping glad pcl copy}
+if(GLAD == TRUE) {
+  coping.pcl.raw.id <- coping.glad.pcl.raw.id
+}
+```
+
+## EDGI
+```{r coping edgi pcl cols}
+coping.edgi.pcl.raw <- readRDS(file = paste0(data.raw_path,"/edgi/pcl_coping_edgi.rds"))
+dim(coping.edgi.pcl.raw)
+colnames(coping.edgi.pcl.raw)
+```
+
+```{r coping edgi pcl summary labels}
+summarytools::dfSummary(
+  coping.edgi.pcl.raw,
+  graph.col = F,
+  valid.col = F,
+  labels.col = F
+)
+```
+
+Note: Retro for the PCL does not mean retrospective
+
+```{r coping edgi pcl cleaning}
+coping.edgi.pcl.raw.id <- coping.edgi.pcl.raw %>%
+  drop_na(externalDataReference) %>% # Drop NAs
+  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
+  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
+  mutate(ID = as.numeric(ID),
+         startDate.coping = startDate) %>% # Rename startDate
+  select(
+    Sample, # Sample
+    ID, # ID
+    pcl.stressful_experience_repeated_images_base = pcl.stressful_experience_repeated_images,
+    pcl.stressful_experience_upset_reminded_base = pcl.stressful_experience_upset_reminded, # differ to EDGI prepan
+    pcl.stressful_situation_avoiding_activities_base = pcl.avoiding_activities_stressful_experience, # differ to EDGI prepan
+    pcl.cut_people_feeling_distant_base = pcl.cut_people_feeling_distant,
+    pcl.feeling_irritable_or_having_angry_outbursts_base = pcl.feeling_irritable_or_having_angry_outbursts,
+    pcl.difficulty_concentrating_base = pcl.difficulty_concentrating,
+    pcl.stressful_experience_repeated_images_retro = pcl.stressful_experience_repeated_images.1,
+    pcl.stressful_experience_upset_reminded_retro = pcl.stressful_experience_upset_reminded.1,
+    pcl.stressful_situation_avoiding_activities_retro = pcl.avoiding_activities_stressful_experience.1,
+    pcl.cut_people_feeling_distant_retro = pcl.cut_people_feeling_distant.1,
+    pcl.feeling_irritable_or_having_angry_outbursts_retro = pcl.feeling_irritable_or_having_angry_outbursts.1,
+    pcl.difficulty_concentrating_retro = pcl.difficulty_concentrating.1
+  ) %>%
+  add_numeric(., exclude = exclude_cols) %>%
+  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
+  mutate_if(is.numeric, ~na_if(., -99)) %>%
+  mutate_if(is.numeric, ~na_if(., -77)) %>%
+  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
+  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
+
+# Inspect dimensions
+dim(coping.edgi.pcl.raw.id)
+# Inspect colnames
+colnames(coping.edgi.pcl.raw.id)
+#Differences
+dim(coping.edgi.pcl.raw)[1]-dim(coping.edgi.pcl.raw.id)[1]
+```
+
+```{r coping edgi pcl copy}
+if(EDGI == TRUE) {
+  coping.pcl.raw.id <- coping.edgi.pcl.raw.id
+}
+```
+
+## NBR
+```{r coping nbr pcl cols}
+coping.nbr.pcl.raw <- readRDS(file = paste0(data.raw_path,"/nbr/pcl_coping_nbr.rds"))
+dim(coping.nbr.pcl.raw)
+colnames(coping.nbr.pcl.raw)
+```
+
+```{r coping nbr pcl summary labels}
+summarytools::dfSummary(
+  coping.nbr.pcl.raw,
+  graph.col = F,
+  valid.col = F,
+  labels.col = F
+)
+```
+
+Note: Retro for the PCL does not mean retrospective
+
+```{r coping nbr pcl cleaning}
+coping.nbr.pcl.raw.id <- coping.nbr.pcl.raw %>%
+  drop_na(externalDataReference) %>% # Drop NAs
+  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
+  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
+  mutate(ID = as.numeric(ID),
+         startDate.coping = startDate) %>% # Rename startDate
+  select(
+    Sample, # Sample
+    ID, # ID
+    pcl.stressful_experience_repeated_images_base = pcl.stressful_experience_repeated_images,
+    pcl.stressful_experience_upset_reminded_base = pcl.stressful_experience_upset_reminded, # differ to NBR prepan
+    pcl.stressful_situation_avoiding_activities_base = pcl.avoiding_activities_stressful_experience, # differ to NBR prepan
+    pcl.cut_people_feeling_distant_base = pcl.cut_people_feeling_distant,
+    pcl.feeling_irritable_or_having_angry_outbursts_base = pcl.feeling_irritable_or_having_angry_outbursts,
+    pcl.difficulty_concentrating_base = pcl.difficulty_concentrating,
+    pcl.stressful_experience_repeated_images_retro = pcl.stressful_experience_repeated_images.1,
+    pcl.stressful_experience_upset_reminded_retro = pcl.stressful_experience_upset_reminded.1,
+    pcl.stressful_situation_avoiding_activities_retro = pcl.avoiding_activities_stressful_experience.1,
+    pcl.cut_people_feeling_distant_retro = pcl.cut_people_feeling_distant.1,
+    pcl.feeling_irritable_or_having_angry_outbursts_retro = pcl.feeling_irritable_or_having_angry_outbursts.1,
+    pcl.difficulty_concentrating_retro = pcl.difficulty_concentrating.1
+  ) %>%
+  add_numeric(., exclude = exclude_cols) %>%
+  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
+  mutate_if(is.numeric, ~na_if(., -99)) %>%
+  mutate_if(is.numeric, ~na_if(., -77)) %>%
+  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
+  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
+
+# Inspect dimensions
+dim(coping.nbr.pcl.raw.id)
+# Inspect colnames
+colnames(coping.nbr.pcl.raw.id)
+#Differences
+dim(coping.nbr.pcl.raw)[1]-dim(coping.nbr.pcl.raw.id)[1]
+```
+
+```{r coping nbr pcl copy}
+if(NBR == TRUE) {
+  coping.pcl.raw.id <- coping.nbr.pcl.raw.id
+}
+```
+
+## RAMP
+```{r coping ramp pcl cols}
+coping.ramp.pcl.raw <- readRDS(file = paste0(data.raw_path,"/ramp/pcl_coping_ramp.rds"))
+dim(coping.ramp.pcl.raw)
+colnames(coping.ramp.pcl.raw)
+```
+
+```{r coping ramp pcl summary labels}
+summarytools::dfSummary(
+  coping.ramp.pcl.raw,
+  graph.col = F,
+  valid.col = F,
+  labels.col = F
+)
+```
+
+Note: Retro for the PCL does not mean retrospective
+
+```{r coping ramp pcl cleaning}
+coping.ramp.pcl.raw.id <- coping.ramp.pcl.raw %>%
+  drop_na(externalDataReference) %>% # Drop NAs
+  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
+  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
+  mutate(ID = as.numeric(ID),
+         startDate.coping = startDate) %>% # Rename startDate
+  select(
+    Sample, # Sample
+    ID, # ID
+    pcl.stressful_experience_repeated_images_base = pcl.stressful_experience_repeated_images,
+    pcl.stressful_experience_upset_reminded_base = pcl.stressful_experience_upset_reminded, # differ to RAMP prepan
+    pcl.stressful_situation_avoiding_activities_base = pcl.avoiding_activities_stressful_experience, # differ to RAMP prepan
+    pcl.cut_people_feeling_distant_base = pcl.cut_people_feeling_distant,
+    pcl.feeling_irritable_or_having_angry_outbursts_base = pcl.feeling_irritable_or_having_angry_outbursts,
+    pcl.difficulty_concentrating_base = pcl.difficulty_concentrating,
+    pcl.stressful_experience_repeated_images_retro = pcl.stressful_experience_repeated_images.1,
+    pcl.stressful_experience_upset_reminded_retro = pcl.stressful_experience_upset_reminded.1,
+    pcl.stressful_situation_avoiding_activities_retro = pcl.avoiding_activities_stressful_experience.1,
+    pcl.cut_people_feeling_distant_retro = pcl.cut_people_feeling_distant.1,
+    pcl.feeling_irritable_or_having_angry_outbursts_retro = pcl.feeling_irritable_or_having_angry_outbursts.1,
+    pcl.difficulty_concentrating_retro = pcl.difficulty_concentrating.1
+  ) %>%
+  add_numeric(., exclude = exclude_cols) %>%
+  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
+  mutate_if(is.numeric, ~na_if(., -99)) %>%
+  mutate_if(is.numeric, ~na_if(., -77)) %>%
+  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
+  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
+
+# Inspect dimensions
+dim(coping.ramp.pcl.raw.id)
+# Inspect colnames
+colnames(coping.ramp.pcl.raw.id)
+#Differences
+dim(coping.ramp.pcl.raw)[1]-dim(coping.ramp.pcl.raw.id)[1]
+```
+
+```{r coping ramp pcl copy}
+if(RAMP == TRUE) {
+  coping.pcl.raw.id <- coping.ramp.pcl.raw.id
+}
+```
+
 Calculate sum score for PCL-6 retro
@@
   separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
-  mutate(ID = as.numeric(ID),
-         startDate.coping = startDate) %>% # Rename startDate
+  mutate(ID = as.numeric(ID)
+         ) %>%
   select(

### 2020-08-11 PANCHANGE_data_preprocessing2020-07-15.Rmd
added coping phq data sets

@@
 
+## Inspection
 ```{r coping glad gad head}
@@
 
+## Sum scores
 Calculate sum score for PCL-6 retro
@@
 
+## Missingness
 PCL missingness (NAs per person)
@@
 
+## Inspection
 ```{r coping glad pcl head}
@@
 
-# glad COPING phq
-
+# COPING: PHQ
+
+## GLAD
 ```{r coping glad phq cols}
@@
 
+```{r coping glad gad copy}
+if(GLAD == TRUE) {
+  coping.gad.raw.id <- coping.glad.gad.raw.id
+}
+```
+
+## EDGI
+```{r coping edgi phq cols}
+coping.edgi.phq.raw <- readRDS(file = paste0(data.raw_path, "/edgi/phq_coping_edgi.rds"))
+dim(coping.edgi.phq.raw)
+colnames(coping.edgi.phq.raw)
+```
+
+```{r coping edgi phq summary labels}
+summarytools::dfSummary(
+  coping.edgi.phq.raw,
+  graph.col = F,
+  valid.col = F
+  #labels.col = F
+)
+```
+
+Will need to double check these namings once we have the new cleaned data -- KT. 
+```{r coping edgi phq cleaning}
+coping.edgi.phq.raw.id <- coping.edgi.phq.raw %>%
+  drop_na(externalDataReference) %>% # Drop NAs
+  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
+  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
+  mutate(ID = as.numeric(ID)
+  ) %>%
+  select(
+    Sample, # Sample
+    ID, # ID
+    phq.problems_made_difficult_care,
+    phq.pandemic_felt_feelings,
+    phq.little_interest_or_pleasure_in_doing_things_retro = phq.little_interest_or_pleasure_in_doing_things,
+    phq.feeling_down_depressed_or_hopeless_retro = phq.feeling_down_depressed_or_hopeless,
+    phq.staying_asleep_sleeping_trouble_retro = phq.staying_asleep_sleeping_trouble,
+    phq.feeling_tired_or_having_little_energy_retro = phq.feeling_tired_or_having_little_energy,
+    phq.poor_appetite_or_overeating_retro = phq.poor_appetite_or_overeating,
+    phq.feeling_bad_failure_family_retro = phq.feeling_bad_failure_family,
+    phq.trouble_concentrating_reading_newspaper_retro = phq.trouble_concentrating_newspaper_reading, # differ EDGI prepandemic
+    phq.moving_fidgety_noticed_opposite_retro = phq.moving_fidgety_opposite_slowly, # differ EDGI prepandemic
+    phq.dead_hurting_thoughts_retro = phq.dead_hurting_thoughts,
+    phq.little_interest_or_pleasure_in_doing_things_base = phq.little_interest_or_pleasure_in_doing_things.1,
+    phq.feeling_down_depressed_or_hopeless_base = phq.feeling_down_depressed_or_hopeless.1,
+    phq.staying_asleep_sleeping_trouble_base = phq.staying_asleep_sleeping_trouble.1,
+    phq.feeling_tired_or_having_little_energy_base = phq.feeling_tired_or_having_little_energy.1,
+    phq.poor_appetite_or_overeating_base = phq.poor_appetite_or_overeating.1,
+    phq.feeling_bad_failure_family_base = phq.feeling_bad_failure_family.1,
+    phq.trouble_concentrating_reading_newspaper_base = phq.trouble_concentrating_newspaper_reading.1, # differ EDGI prepandemic
+    phq.moving_fidgety_noticed_opposite_base = phq.moving_fidgety_opposite_slowly.1, # differ EDGI prepandemic
+    phq.dead_hurting_thoughts_base = phq.dead_hurting_thoughts.1
+  ) %>%
+  add_numeric(., exclude = exclude_cols) %>%
+  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
+  mutate_if(is.numeric, ~na_if(., -99)) %>%
+  mutate_if(is.numeric, ~na_if(., -77)) %>%
+  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
+  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
+
+# Inspect dimensions
+dim(coping.edgi.phq.raw.id)
+# Inspect colnames
+colnames(coping.edgi.phq.raw.id)
+#Differences
+dim(coping.edgi.phq.raw)[1]-dim(coping.edgi.phq.raw.id)[1]
+```
+
+```{r coping edgi gad copy}
+if(EDGI == TRUE) {
+  coping.gad.raw.id <- coping.edgi.gad.raw.id
+}
+```
+
+## NBR
+```{r coping nbr phq cols}
+coping.nbr.phq.raw <- readRDS(file = paste0(data.raw_path, "/nbr/phq_coping_nbr.rds"))
+dim(coping.nbr.phq.raw)
+colnames(coping.nbr.phq.raw)
+```
+
+```{r coping nbr phq summary labels}
+summarytools::dfSummary(
+  coping.nbr.phq.raw,
+  graph.col = F,
+  valid.col = F
+  #labels.col = F
+)
+```
+
+Will need to double check these namings once we have the new cleaned data -- KT. 
+```{r coping nbr phq cleaning}
+coping.nbr.phq.raw.id <- coping.nbr.phq.raw %>%
+  drop_na(externalDataReference) %>% # Drop NAs
+  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
+  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
+  mutate(ID = as.numeric(ID)
+  ) %>%
+  select(
+    Sample, # Sample
+    ID, # ID
+    phq.problems_made_difficult_care,
+    phq.pandemic_felt_feelings,
+    phq.little_interest_or_pleasure_in_doing_things_retro = phq.little_interest_or_pleasure_in_doing_things,
+    phq.feeling_down_depressed_or_hopeless_retro = phq.feeling_down_depressed_or_hopeless,
+    phq.staying_asleep_sleeping_trouble_retro = phq.staying_asleep_sleeping_trouble,
+    phq.feeling_tired_or_having_little_energy_retro = phq.feeling_tired_or_having_little_energy,
+    phq.poor_appetite_or_overeating_retro = phq.poor_appetite_or_overeating,
+    phq.feeling_bad_failure_family_retro = phq.feeling_bad_failure_family,
+    phq.trouble_concentrating_reading_newspaper_retro = phq.trouble_concentrating_newspaper_reading, # differ NBR prepandemic
+    phq.moving_fidgety_noticed_opposite_retro = phq.moving_fidgety_opposite_slowly, # differ NBR prepandemic
+    phq.dead_hurting_thoughts_retro = phq.dead_hurting_thoughts,
+    phq.little_interest_or_pleasure_in_doing_things_base = phq.little_interest_or_pleasure_in_doing_things.1,
+    phq.feeling_down_depressed_or_hopeless_base = phq.feeling_down_depressed_or_hopeless.1,
+    phq.staying_asleep_sleeping_trouble_base = phq.staying_asleep_sleeping_trouble.1,
+    phq.feeling_tired_or_having_little_energy_base = phq.feeling_tired_or_having_little_energy.1,
+    phq.poor_appetite_or_overeating_base = phq.poor_appetite_or_overeating.1,
+    phq.feeling_bad_failure_family_base = phq.feeling_bad_failure_family.1,
+    phq.trouble_concentrating_reading_newspaper_base = phq.trouble_concentrating_newspaper_reading.1, # differ NBR prepandemic
+    phq.moving_fidgety_noticed_opposite_base = phq.moving_fidgety_opposite_slowly.1, # differ NBR prepandemic
+    phq.dead_hurting_thoughts_base = phq.dead_hurting_thoughts.1
+  ) %>%
+  add_numeric(., exclude = exclude_cols) %>%
+  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
+  mutate_if(is.numeric, ~na_if(., -99)) %>%
+  mutate_if(is.numeric, ~na_if(., -77)) %>%
+  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
+  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
+
+# Inspect dimensions
+dim(coping.nbr.phq.raw.id)
+# Inspect colnames
+colnames(coping.nbr.phq.raw.id)
+#Differences
+dim(coping.nbr.phq.raw)[1]-dim(coping.nbr.phq.raw.id)[1]
+```
+
+```{r coping nbr gad copy}
+if(NBR == TRUE) {
+  coping.gad.raw.id <- coping.nbr.gad.raw.id
+}
+```
+
+## RAMP
+```{r coping ramp phq cols}
+coping.ramp.phq.raw <- readRDS(file = paste0(data.raw_path, "/ramp/phq_coping_ramp.rds"))
+dim(coping.ramp.phq.raw)
+colnames(coping.ramp.phq.raw)
+```
+
+```{r coping ramp phq summary labels}
+summarytools::dfSummary(
+  coping.ramp.phq.raw,
+  graph.col = F,
+  valid.col = F
+  #labels.col = F
+)
+```
+
+Will need to double check these namings once we have the new cleaned data -- KT. 
+```{r coping ramp phq cleaning}
+coping.ramp.phq.raw.id <- coping.ramp.phq.raw %>%
+  drop_na(externalDataReference) %>% # Drop NAs
+  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
+  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
+  mutate(ID = as.numeric(ID)
+  ) %>%
+  select(
+    Sample, # Sample
+    ID, # ID
+    phq.problems_made_difficult_care,
+    phq.pandemic_felt_feelings,
+    phq.little_interest_or_pleasure_in_doing_things_retro = phq.little_interest_or_pleasure_in_doing_things,
+    phq.feeling_down_depressed_or_hopeless_retro = phq.feeling_down_depressed_or_hopeless,
+    phq.staying_asleep_sleeping_trouble_retro = phq.staying_asleep_sleeping_trouble,
+    phq.feeling_tired_or_having_little_energy_retro = phq.feeling_tired_or_having_little_energy,
+    phq.poor_appetite_or_overeating_retro = phq.poor_appetite_or_overeating,
+    phq.feeling_bad_failure_family_retro = phq.feeling_bad_failure_family,
+    phq.trouble_concentrating_reading_newspaper_retro = phq.trouble_concentrating_newspaper_reading, # differ RAMP prepandemic
+    phq.moving_fidgety_noticed_opposite_retro = phq.moving_fidgety_opposite_slowly, # differ RAMP prepandemic
+    phq.dead_hurting_thoughts_retro = phq.dead_hurting_thoughts,
+    phq.little_interest_or_pleasure_in_doing_things_base = phq.little_interest_or_pleasure_in_doing_things.1,
+    phq.feeling_down_depressed_or_hopeless_base = phq.feeling_down_depressed_or_hopeless.1,
+    phq.staying_asleep_sleeping_trouble_base = phq.staying_asleep_sleeping_trouble.1,
+    phq.feeling_tired_or_having_little_energy_base = phq.feeling_tired_or_having_little_energy.1,
+    phq.poor_appetite_or_overeating_base = phq.poor_appetite_or_overeating.1,
+    phq.feeling_bad_failure_family_base = phq.feeling_bad_failure_family.1,
+    phq.trouble_concentrating_reading_newspaper_base = phq.trouble_concentrating_newspaper_reading.1, # differ RAMP prepandemic
+    phq.moving_fidgety_noticed_opposite_base = phq.moving_fidgety_opposite_slowly.1, # differ RAMP prepandemic
+    phq.dead_hurting_thoughts_base = phq.dead_hurting_thoughts.1
+  ) %>%
+  add_numeric(., exclude = exclude_cols) %>%
+  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
+  mutate_if(is.numeric, ~na_if(., -99)) %>%
+  mutate_if(is.numeric, ~na_if(., -77)) %>%
+  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
+  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
+
+# Inspect dimensions
+dim(coping.ramp.phq.raw.id)
+# Inspect colnames
+colnames(coping.ramp.phq.raw.id)
+#Differences
+dim(coping.ramp.phq.raw)[1]-dim(coping.ramp.phq.raw.id)[1]
+```
+
+```{r coping ramp gad copy}
+if(RAMP == TRUE) {
+  coping.gad.raw.id <- coping.ramp.gad.raw.id
+}
+```
+
+## Sum scores
+
 Calculate sum score for PHQ-9 retro
@@
 
-missigness
+# Missingness
 
@@
 ```
+
+## Inspection
 

### 2020-08-11 PANCHANGE_data_preprocessing2020-07-15.Rmd
added coping ocir data sets

@@
 if(GLAD == TRUE) {
-  coping.gad.raw.id <- coping.glad.gad.raw.id
+  coping.phq.raw.id <- coping.glad.phq.raw.id
 }
@@
 if(EDGI == TRUE) {
-  coping.gad.raw.id <- coping.edgi.gad.raw.id
+  coping.phq.raw.id <- coping.edgi.phq.raw.id
 }
@@
 if(NBR == TRUE) {
-  coping.gad.raw.id <- coping.nbr.gad.raw.id
+  coping.phq.raw.id <- coping.nbr.phq.raw.id
 }
@@
 if(RAMP == TRUE) {
-  coping.gad.raw.id <- coping.ramp.gad.raw.id
+  coping.phq.raw.id <- coping.ramp.phq.raw.id
 }
@@
 
-# glad COPING ocir
-
+# COPING: OCI-R
+
+## GLAD
 ```{r coping glad ocir cols}
@@
 
+```{r coping glad ocir copy}
+if(GLAD == TRUE) {
+  coping.ocir.raw.id <- coping.glad.ocir.raw.id
+}
+```
+
+## EDGI
+```{r coping edgi ocir cols}
+coping.edgi.ocir.raw <- readRDS(file = paste0(data.raw_path, "/edgi/ocir_coping_edgi.rds"))
+dim(coping.edgi.ocir.raw)
+colnames(coping.edgi.ocir.raw)
+```
+
+```{r coping edgi ocir summary labels}
+summarytools::dfSummary(
+  coping.edgi.ocir.raw,
+  graph.col = F,
+  valid.col = F
+  #labels.col = F
+)
+```
+
+*Note that the COPING EDGI OCI-R ID numbers are stored under recipientFirstName (rather than ExternalDataReference)
+```{r coping edgi ocir cleaning}
+coping.edgi.ocir.raw.id <- coping.edgi.ocir.raw %>%
+  drop_na(recipientFirstName) %>% # Drop NAs
+  distinct(recipientFirstName, .keep_all = TRUE) %>% # Remove duplicates based on ID
+  separate(recipientFirstName, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
+  mutate(ID = as.numeric(ID),
+         startDate.coping = startDate) %>% # Rename startDate
+  select(
+    Sample, # Sample
+    ID, # ID
+    ocir.felt_pandemic_feelings, # Comparison to before the pandemic
+    ocir.i_repeatedly_check_doors_windows_drawers_etc_retro = ocir.i_repeatedly_check_doors_windows_drawers_etc.,
+    ocir.arranged_things_change_upset_retro = ocir.arranged_things_change_upset,
+    ocir.repeat_feel_numbers_retro = ocir.numbers_repeat_feel, ## Different from EDGI prepandemic
+    ocir.clean_simply_wash_feel_retro = ocir.feel_contaminated_clean_simply, ## Different from EDGI prepandemic
+    ocir.mind_upset_unpleasant_thoughts_retro = ocir.mind_upset_unpleasant_thoughts,
+    ocir.afraid_avoid_throwing_things_retro = ocir.afraid_avoid_throwing_things,
+    ocir.light_switches_water_taps_retro = ocir.light_switches_water_taps,
+    ocir.arranged_things_retro = ocir.arranged_things,
+    ocir.good_feel_bad_numbers_retro = ocir.bad_numbers_good_feel, ## Different from EDGI prepandemic
+    ocir.hands_longer_wash_retro = ocir.longer_hands_wash, ## Different from EDGI prepandemic
+    ocir.saved_things_retro = ocir.saved_things,
+    ocir.frequently_difficulty_rid_nasty_retro = ocir.frequently_rid_difficulty_nasty, ## Different from EDGI prepandemic
+    ocir.i_check_things_more_often_than_necessary_retro = ocir.i_check_things_more_often_than_necessary.,
+    ocir.arranged_properly_objects_upset_retro = ocir.arranged_properly_objects_upset,
+    ocir.feel_compelled_count_things_retro = ocir.feel_compelled_count_things,
+    ocir.strangers_touch_touched_difficult_retro = ocir.strangers_touch_touched_object, ## Different from EDGI prepandemic
+    ocir.control_difficult_find_thoughts_retro = ocir.control_find_difficult_thoughts, ## Different from EDGI prepandemic
+    ocir.i_collect_things_i_dont_need_retro = ocir.i_collect_things_i_dont_need., ## Different from EDGI prepandemic
+    ocir.i_repeatedly_check_doors_windows_drawers_etc_base = ocir.i_repeatedly_check_doors_windows_drawers_etc..1,
+    ocir.arranged_things_change_upset_base = ocir.arranged_things_change_upset.1,
+    ocir.repeat_feel_numbers_base = ocir.numbers_repeat_feel.1, ## Different from EDGI prepandemic
+    ocir.clean_simply_wash_feel_base = ocir.feel_contaminated_clean_simply.1, ## Different from EDGI prepandemic
+    ocir.mind_upset_unpleasant_thoughts_base = ocir.mind_upset_unpleasant_thoughts.1,
+    ocir.afraid_avoid_throwing_things_base = ocir.afraid_avoid_throwing_things.1,
+    ocir.light_switches_water_taps_base = ocir.light_switches_water_taps.1,
+    ocir.arranged_things_base = ocir.arranged_things.1,
+    ocir.good_feel_bad_numbers_base = ocir.bad_numbers_good_feel.1, ## Different from EDGI prepandemic
+    ocir.hands_longer_wash_base = ocir.longer_hands_wash.1, ## Different from EDGI prepandemic
+    ocir.saved_things_base = ocir.saved_things.1,
+    ocir.frequently_difficulty_rid_nasty_base = ocir.frequently_rid_difficulty_nasty.1, ## Different from EDGI prepandemic
+    ocir.i_check_things_more_often_than_necessary_base = ocir.i_check_things_more_often_than_necessary..1,
+    ocir.arranged_properly_objects_upset_base = ocir.arranged_properly_objects_upset.1,
+    ocir.feel_compelled_count_things_base = ocir.feel_compelled_count_things.1,
+    ocir.strangers_touch_touched_difficult_base = ocir.strangers_touch_touched_object.1, ## Different from EDGI prepandemic
+    ocir.control_difficult_find_thoughts_base = ocir.control_find_difficult_thoughts.1, ## Different from EDGI prepandemic
+    ocir.i_collect_things_i_dont_need_base = ocir.i_collect_things_i_dont_need..1
+  ) %>%
+  add_numeric(., exclude = exclude_cols) %>%
+  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
+  mutate_if(is.numeric, ~na_if(., -99)) %>%
+  mutate_if(is.numeric, ~na_if(., -77)) %>%
+  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
+  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
+
+# Inspect dimensions
+dim(coping.edgi.ocir.raw.id)
+# Inspect colnames
+colnames(coping.edgi.ocir.raw.id)
+#Differences
+dim(coping.edgi.ocir.raw)[1]-dim(coping.edgi.ocir.raw.id)[1]
+```
+
+```{r coping edgi ocir copy}
+if(EDGI == TRUE) {
+  coping.ocir.raw.id <- coping.edgi.ocir.raw.id
+}
+```
+
+## NBR
+```{r coping nbr ocir cols}
+coping.nbr.ocir.raw <- readRDS(file = paste0(data.raw_path, "/nbr/ocir_coping_nbr.rds"))
+dim(coping.nbr.ocir.raw)
+colnames(coping.nbr.ocir.raw)
+```
+
+```{r coping nbr ocir summary labels}
+summarytools::dfSummary(
+  coping.nbr.ocir.raw,
+  graph.col = F,
+  valid.col = F
+  #labels.col = F
+)
+```
+
+*Note that the COPING NBR OCI-R ID numbers are stored under recipientFirstName (rather than ExternalDataReference)
+```{r coping nbr ocir cleaning}
+coping.nbr.ocir.raw.id <- coping.nbr.ocir.raw %>%
+  drop_na(recipientFirstName) %>% # Drop NAs
+  distinct(recipientFirstName, .keep_all = TRUE) %>% # Remove duplicates based on ID
+  separate(recipientFirstName, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
+  mutate(ID = as.numeric(ID),
+         startDate.coping = startDate) %>% # Rename startDate
+  select(
+    Sample, # Sample
+    ID, # ID
+    ocir.felt_pandemic_feelings, # Comparison to before the pandemic
+    ocir.i_repeatedly_check_doors_windows_drawers_etc_retro = ocir.i_repeatedly_check_doors_windows_drawers_etc.,
+    ocir.arranged_things_change_upset_retro = ocir.arranged_things_change_upset,
+    ocir.repeat_feel_numbers_retro = ocir.numbers_repeat_feel, ## Different from NBR prepandemic
+    ocir.clean_simply_wash_feel_retro = ocir.feel_contaminated_clean_simply, ## Different from NBR prepandemic
+    ocir.mind_upset_unpleasant_thoughts_retro = ocir.mind_upset_unpleasant_thoughts,
+    ocir.afraid_avoid_throwing_things_retro = ocir.afraid_avoid_throwing_things,
+    ocir.light_switches_water_taps_retro = ocir.light_switches_water_taps,
+    ocir.arranged_things_retro = ocir.arranged_things,
+    ocir.good_feel_bad_numbers_retro = ocir.bad_numbers_good_feel, ## Different from NBR prepandemic
+    ocir.hands_longer_wash_retro = ocir.longer_hands_wash, ## Different from NBR prepandemic
+    ocir.saved_things_retro = ocir.saved_things,
+    ocir.frequently_difficulty_rid_nasty_retro = ocir.frequently_rid_difficulty_nasty, ## Different from NBR prepandemic
+    ocir.i_check_things_more_often_than_necessary_retro = ocir.i_check_things_more_often_than_necessary.,
+    ocir.arranged_properly_objects_upset_retro = ocir.arranged_properly_objects_upset,
+    ocir.feel_compelled_count_things_retro = ocir.feel_compelled_count_things,
+    ocir.strangers_touch_touched_difficult_retro = ocir.strangers_touch_touched_object, ## Different from NBR prepandemic
+    ocir.control_difficult_find_thoughts_retro = ocir.control_find_difficult_thoughts, ## Different from NBR prepandemic
+    ocir.i_collect_things_i_dont_need_retro = ocir.i_collect_things_i_dont_need., ## Different from NBR prepandemic
+    ocir.i_repeatedly_check_doors_windows_drawers_etc_base = ocir.i_repeatedly_check_doors_windows_drawers_etc..1,
+    ocir.arranged_things_change_upset_base = ocir.arranged_things_change_upset.1,
+    ocir.repeat_feel_numbers_base = ocir.numbers_repeat_feel.1, ## Different from NBR prepandemic
+    ocir.clean_simply_wash_feel_base = ocir.feel_contaminated_clean_simply.1, ## Different from NBR prepandemic
+    ocir.mind_upset_unpleasant_thoughts_base = ocir.mind_upset_unpleasant_thoughts.1,
+    ocir.afraid_avoid_throwing_things_base = ocir.afraid_avoid_throwing_things.1,
+    ocir.light_switches_water_taps_base = ocir.light_switches_water_taps.1,
+    ocir.arranged_things_base = ocir.arranged_things.1,
+    ocir.good_feel_bad_numbers_base = ocir.bad_numbers_good_feel.1, ## Different from NBR prepandemic
+    ocir.hands_longer_wash_base = ocir.longer_hands_wash.1, ## Different from NBR prepandemic
+    ocir.saved_things_base = ocir.saved_things.1,
+    ocir.frequently_difficulty_rid_nasty_base = ocir.frequently_rid_difficulty_nasty.1, ## Different from NBR prepandemic
+    ocir.i_check_things_more_often_than_necessary_base = ocir.i_check_things_more_often_than_necessary..1,
+    ocir.arranged_properly_objects_upset_base = ocir.arranged_properly_objects_upset.1,
+    ocir.feel_compelled_count_things_base = ocir.feel_compelled_count_things.1,
+    ocir.strangers_touch_touched_difficult_base = ocir.strangers_touch_touched_object.1, ## Different from NBR prepandemic
+    ocir.control_difficult_find_thoughts_base = ocir.control_find_difficult_thoughts.1, ## Different from NBR prepandemic
+    ocir.i_collect_things_i_dont_need_base = ocir.i_collect_things_i_dont_need..1
+  ) %>%
+  add_numeric(., exclude = exclude_cols) %>%
+  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
+  mutate_if(is.numeric, ~na_if(., -99)) %>%
+  mutate_if(is.numeric, ~na_if(., -77)) %>%
+  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
+  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
+
+# Inspect dimensions
+dim(coping.nbr.ocir.raw.id)
+# Inspect colnames
+colnames(coping.nbr.ocir.raw.id)
+#Differences
+dim(coping.nbr.ocir.raw)[1]-dim(coping.nbr.ocir.raw.id)[1]
+```
+
+```{r coping nbr ocir copy}
+if(NBR == TRUE) {
+  coping.ocir.raw.id <- coping.nbr.ocir.raw.id
+}
+```
+
+## RAMP
+```{r coping ramp ocir cols}
+coping.ramp.ocir.raw <- readRDS(file = paste0(data.raw_path, "/ramp/ocir_coping_ramp.rds"))
+dim(coping.ramp.ocir.raw)
+colnames(coping.ramp.ocir.raw)
+```
+
+```{r coping ramp ocir summary labels}
+summarytools::dfSummary(
+  coping.ramp.ocir.raw,
+  graph.col = F,
+  valid.col = F
+  #labels.col = F
+)
+```
+
+*Note that the COPING RAMP OCI-R ID numbers are stored under recipientFirstName (rather than ExternalDataReference)
+```{r coping ramp ocir cleaning}
+coping.ramp.ocir.raw.id <- coping.ramp.ocir.raw %>%
+  drop_na(recipientFirstName) %>% # Drop NAs
+  distinct(recipientFirstName, .keep_all = TRUE) %>% # Remove duplicates based on ID
+  separate(recipientFirstName, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
+  mutate(ID = as.numeric(ID),
+         startDate.coping = startDate) %>% # Rename startDate
+  select(
+    Sample, # Sample
+    ID, # ID
+    ocir.felt_pandemic_feelings, # Comparison to before the pandemic
+    ocir.i_repeatedly_check_doors_windows_drawers_etc_retro = ocir.i_repeatedly_check_doors_windows_drawers_etc.,
+    ocir.arranged_things_change_upset_retro = ocir.arranged_things_change_upset,
+    ocir.repeat_feel_numbers_retro = ocir.numbers_repeat_feel, ## Different from RAMP prepandemic
+    ocir.clean_simply_wash_feel_retro = ocir.feel_contaminated_clean_simply, ## Different from RAMP prepandemic
+    ocir.mind_upset_unpleasant_thoughts_retro = ocir.mind_upset_unpleasant_thoughts,
+    ocir.afraid_avoid_throwing_things_retro = ocir.afraid_avoid_throwing_things,
+    ocir.light_switches_water_taps_retro = ocir.light_switches_water_taps,
+    ocir.arranged_things_retro = ocir.arranged_things,
+    ocir.good_feel_bad_numbers_retro = ocir.bad_numbers_good_feel, ## Different from RAMP prepandemic
+    ocir.hands_longer_wash_retro = ocir.longer_hands_wash, ## Different from RAMP prepandemic
+    ocir.saved_things_retro = ocir.saved_things,
+    ocir.frequently_difficulty_rid_nasty_retro = ocir.frequently_rid_difficulty_nasty, ## Different from RAMP prepandemic
+    ocir.i_check_things_more_often_than_necessary_retro = ocir.i_check_things_more_often_than_necessary.,
+    ocir.arranged_properly_objects_upset_retro = ocir.arranged_properly_objects_upset,
+    ocir.feel_compelled_count_things_retro = ocir.feel_compelled_count_things,
+    ocir.strangers_touch_touched_difficult_retro = ocir.strangers_touch_touched_object, ## Different from RAMP prepandemic
+    ocir.control_difficult_find_thoughts_retro = ocir.control_find_difficult_thoughts, ## Different from RAMP prepandemic
+    ocir.i_collect_things_i_dont_need_retro = ocir.i_collect_things_i_dont_need., ## Different from RAMP prepandemic
+    ocir.i_repeatedly_check_doors_windows_drawers_etc_base = ocir.i_repeatedly_check_doors_windows_drawers_etc..1,
+    ocir.arranged_things_change_upset_base = ocir.arranged_things_change_upset.1,
+    ocir.repeat_feel_numbers_base = ocir.numbers_repeat_feel.1, ## Different from RAMP prepandemic
+    ocir.clean_simply_wash_feel_base = ocir.feel_contaminated_clean_simply.1, ## Different from RAMP prepandemic
+    ocir.mind_upset_unpleasant_thoughts_base = ocir.mind_upset_unpleasant_thoughts.1,
+    ocir.afraid_avoid_throwing_things_base = ocir.afraid_avoid_throwing_things.1,
+    ocir.light_switches_water_taps_base = ocir.light_switches_water_taps.1,
+    ocir.arranged_things_base = ocir.arranged_things.1,
+    ocir.good_feel_bad_numbers_base = ocir.bad_numbers_good_feel.1, ## Different from RAMP prepandemic
+    ocir.hands_longer_wash_base = ocir.longer_hands_wash.1, ## Different from RAMP prepandemic
+    ocir.saved_things_base = ocir.saved_things.1,
+    ocir.frequently_difficulty_rid_nasty_base = ocir.frequently_rid_difficulty_nasty.1, ## Different from RAMP prepandemic
+    ocir.i_check_things_more_often_than_necessary_base = ocir.i_check_things_more_often_than_necessary..1,
+    ocir.arranged_properly_objects_upset_base = ocir.arranged_properly_objects_upset.1,
+    ocir.feel_compelled_count_things_base = ocir.feel_compelled_count_things.1,
+    ocir.strangers_touch_touched_difficult_base = ocir.strangers_touch_touched_object.1, ## Different from RAMP prepandemic
+    ocir.control_difficult_find_thoughts_base = ocir.control_find_difficult_thoughts.1, ## Different from RAMP prepandemic
+    ocir.i_collect_things_i_dont_need_base = ocir.i_collect_things_i_dont_need..1
+  ) %>%
+  add_numeric(., exclude = exclude_cols) %>%
+  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
+  mutate_if(is.numeric, ~na_if(., -99)) %>%
+  mutate_if(is.numeric, ~na_if(., -77)) %>%
+  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
+  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
+
+# Inspect dimensions
+dim(coping.ramp.ocir.raw.id)
+# Inspect colnames
+colnames(coping.ramp.ocir.raw.id)
+#Differences
+dim(coping.ramp.ocir.raw)[1]-dim(coping.ramp.ocir.raw.id)[1]
+```
+
+```{r coping ramp ocir copy}
+if(RAMP == TRUE) {
+  coping.ocir.raw.id <- coping.ramp.ocir.raw.id
+}
+```
+
+## Sum scores
+
 Calculate sum score for OCI-R retro
@@
 ```
+
+# Inspection
 

### 2020-08-12 PANCHANGE_data_preprocessing2020-07-15.Rmd
added if statements

--- 2020-08-11 PANCHANGE_data_preprocessing2020-07-15.Rmd
@@
 ```{r coping glad pcl cols}
+if(GLAD == TRUE) {
 coping.glad.pcl.raw <- readRDS(file = paste0(data.raw_path,"/glad/pcl_coping_glad.rds"))
@@
 colnames(coping.glad.pcl.raw)
+}
 ```
@@
 ```{r coping glad pcl summary labels}
+if(GLAD == TRUE) {
 summarytools::dfSummary(
@@
 )
+}
 ```
@@
 ```{r coping glad pcl cleaning}
+if(GLAD == TRUE) {
 coping.glad.pcl.raw.id <- coping.glad.pcl.raw %>%
@@
 dim(coping.glad.pcl.raw)[1]-dim(coping.glad.pcl.raw.id)[1]
+}
 ```
@@
 ```{r coping edgi pcl cols}
+if(EDGI == TRUE) {
 coping.edgi.pcl.raw <- readRDS(file = paste0(data.raw_path,"/edgi/pcl_coping_edgi.rds"))
@@
 colnames(coping.edgi.pcl.raw)
+}
 ```
@@
 ```{r coping edgi pcl summary labels}
+if(EDGI == TRUE) {
 summarytools::dfSummary(
@@
 ```{r coping edgi pcl cleaning}
+if(EDGI == TRUE) {
 coping.edgi.pcl.raw.id <- coping.edgi.pcl.raw %>%
@@
 dim(coping.edgi.pcl.raw)[1]-dim(coping.edgi.pcl.raw.id)[1]
+}
 ```
@@
 ```{r coping nbr pcl cols}
+if(NBR == TRUE) {
 coping.nbr.pcl.raw <- readRDS(file = paste0(data.raw_path,"/nbr/pcl_coping_nbr.rds"))
@@
 colnames(coping.nbr.pcl.raw)
+}
 ```
@@
 ```{r coping nbr pcl summary labels}
+if(NBR == TRUE) {
 summarytools::dfSummary(
@@
 ```{r coping nbr pcl cleaning}
+if(NBR == TRUE) {
 coping.nbr.pcl.raw.id <- coping.nbr.pcl.raw %>%
@@
 dim(coping.nbr.pcl.raw)[1]-dim(coping.nbr.pcl.raw.id)[1]
+}
 ```
@@
 ```{r coping ramp pcl cols}
+if(RAMP == TRUE) {
 coping.ramp.pcl.raw <- readRDS(file = paste0(data.raw_path,"/ramp/pcl_coping_ramp.rds"))
@@
 colnames(coping.ramp.pcl.raw)
+}
 ```
@@
 ```{r coping ramp pcl summary labels}
+if(RAMP == TRUE) {
 summarytools::dfSummary(
@@
 ```{r coping ramp pcl cleaning}
+if(RAMP == TRUE) {
 coping.ramp.pcl.raw.id <- coping.ramp.pcl.raw %>%
@@
 dim(coping.ramp.pcl.raw)[1]-dim(coping.ramp.pcl.raw.id)[1]
+}
 ```
@@
 
-# glad COPING phq
-
+# COPING: PHQ
+
+## GLAD
 ```{r coping glad phq cols}
+if(GLAD == TRUE) {
 coping.glad.phq.raw <- readRDS(file = paste0(data.raw_path, "/glad/phq_coping_glad.rds"))
@@
 colnames(coping.glad.phq.raw)
+}
 ```
@@
 ```{r coping glad phq summary labels}
+if(GLAD == TRUE) {
 summarytools::dfSummary(
@@
 ```{r coping glad phq cleaning}
+if(GLAD == TRUE) {
 coping.glad.phq.raw.id <- coping.glad.phq.raw %>%
@@
 dim(coping.glad.phq.raw)[1]-dim(coping.glad.phq.raw.id)[1]
-```
+}
+```
+
+```{r coping glad gad copy}
+if(GLAD == TRUE) {
+  coping.phq.raw.id <- coping.glad.phq.raw.id
+}
+```
+
+## EDGI
+```{r coping edgi phq cols}
+if(EDGI == TRUE) {
+coping.edgi.phq.raw <- readRDS(file = paste0(data.raw_path, "/edgi/phq_coping_edgi.rds"))
+dim(coping.edgi.phq.raw)
+colnames(coping.edgi.phq.raw)
+}
+```
+
+```{r coping edgi phq summary labels}
+if(EDGI == TRUE) {
+summarytools::dfSummary(
+  coping.edgi.phq.raw,
+  graph.col = F,
+  valid.col = F
+  #labels.col = F
+)
+}
+```
+
+Will need to double check these namings once we have the new cleaned data -- KT. 
+```{r coping edgi phq cleaning}
+if(EDGI == TRUE) {
+coping.edgi.phq.raw.id <- coping.edgi.phq.raw %>%
+  drop_na(externalDataReference) %>% # Drop NAs
+  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
+  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
+  mutate(ID = as.numeric(ID)
+  ) %>%
+  select(
+    Sample, # Sample
+    ID, # ID
+    phq.problems_made_difficult_care,
+    phq.pandemic_felt_feelings,
+    phq.little_interest_or_pleasure_in_doing_things_retro = phq.little_interest_or_pleasure_in_doing_things,
+    phq.feeling_down_depressed_or_hopeless_retro = phq.feeling_down_depressed_or_hopeless,
+    phq.staying_asleep_sleeping_trouble_retro = phq.staying_asleep_sleeping_trouble,
+    phq.feeling_tired_or_having_little_energy_retro = phq.feeling_tired_or_having_little_energy,
+    phq.poor_appetite_or_overeating_retro = phq.poor_appetite_or_overeating,
+    phq.feeling_bad_failure_family_retro = phq.feeling_bad_failure_family,
+    phq.trouble_concentrating_reading_newspaper_retro = phq.trouble_concentrating_newspaper_reading, # differ EDGI prepandemic
+    phq.moving_fidgety_noticed_opposite_retro = phq.moving_fidgety_opposite_slowly, # differ EDGI prepandemic
+    phq.dead_hurting_thoughts_retro = phq.dead_hurting_thoughts,
+    phq.little_interest_or_pleasure_in_doing_things_base = phq.little_interest_or_pleasure_in_doing_things.1,
+    phq.feeling_down_depressed_or_hopeless_base = phq.feeling_down_depressed_or_hopeless.1,
+    phq.staying_asleep_sleeping_trouble_base = phq.staying_asleep_sleeping_trouble.1,
+    phq.feeling_tired_or_having_little_energy_base = phq.feeling_tired_or_having_little_energy.1,
+    phq.poor_appetite_or_overeating_base = phq.poor_appetite_or_overeating.1,
+    phq.feeling_bad_failure_family_base = phq.feeling_bad_failure_family.1,
+    phq.trouble_concentrating_reading_newspaper_base = phq.trouble_concentrating_newspaper_reading.1, # differ EDGI prepandemic
+    phq.moving_fidgety_noticed_opposite_base = phq.moving_fidgety_opposite_slowly.1, # differ EDGI prepandemic
+    phq.dead_hurting_thoughts_base = phq.dead_hurting_thoughts.1
+  ) %>%
+  add_numeric(., exclude = exclude_cols) %>%
+  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
+  mutate_if(is.numeric, ~na_if(., -99)) %>%
+  mutate_if(is.numeric, ~na_if(., -77)) %>%
+  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
+  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
+
+# Inspect dimensions
+dim(coping.edgi.phq.raw.id)
+# Inspect colnames
+colnames(coping.edgi.phq.raw.id)
+#Differences
+dim(coping.edgi.phq.raw)[1]-dim(coping.edgi.phq.raw.id)[1]
+}
+```
+
+```{r coping edgi gad copy}
+if(EDGI == TRUE) {
+  coping.phq.raw.id <- coping.edgi.phq.raw.id
+}
+```
+
+## NBR
+```{r coping nbr phq cols}
+if(NBR == TRUE) {
+coping.nbr.phq.raw <- readRDS(file = paste0(data.raw_path, "/nbr/phq_coping_nbr.rds"))
+dim(coping.nbr.phq.raw)
+colnames(coping.nbr.phq.raw)
+}
+```
+
+```{r coping nbr phq summary labels}
+if(NBR == TRUE) {
+summarytools::dfSummary(
+  coping.nbr.phq.raw,
+  graph.col = F,
+  valid.col = F
+  #labels.col = F
+)
+}
+```
+
+Will need to double check these namings once we have the new cleaned data -- KT. 
+```{r coping nbr phq cleaning}
+if(NBR == TRUE) {
+coping.nbr.phq.raw.id <- coping.nbr.phq.raw %>%
+  drop_na(externalDataReference) %>% # Drop NAs
+  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
+  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
+  mutate(ID = as.numeric(ID)
+  ) %>%
+  select(
+    Sample, # Sample
+    ID, # ID
+    phq.problems_made_difficult_care,
+    phq.pandemic_felt_feelings,
+    phq.little_interest_or_pleasure_in_doing_things_retro = phq.little_interest_or_pleasure_in_doing_things,
+    phq.feeling_down_depressed_or_hopeless_retro = phq.feeling_down_depressed_or_hopeless,
+    phq.staying_asleep_sleeping_trouble_retro = phq.staying_asleep_sleeping_trouble,
+    phq.feeling_tired_or_having_little_energy_retro = phq.feeling_tired_or_having_little_energy,
+    phq.poor_appetite_or_overeating_retro = phq.poor_appetite_or_overeating,
+    phq.feeling_bad_failure_family_retro = phq.feeling_bad_failure_family,
+    phq.trouble_concentrating_reading_newspaper_retro = phq.trouble_concentrating_newspaper_reading, # differ NBR prepandemic
+    phq.moving_fidgety_noticed_opposite_retro = phq.moving_fidgety_opposite_slowly, # differ NBR prepandemic
+    phq.dead_hurting_thoughts_retro = phq.dead_hurting_thoughts,
+    phq.little_interest_or_pleasure_in_doing_things_base = phq.little_interest_or_pleasure_in_doing_things.1,
+    phq.feeling_down_depressed_or_hopeless_base = phq.feeling_down_depressed_or_hopeless.1,
+    phq.staying_asleep_sleeping_trouble_base = phq.staying_asleep_sleeping_trouble.1,
+    phq.feeling_tired_or_having_little_energy_base = phq.feeling_tired_or_having_little_energy.1,
+    phq.poor_appetite_or_overeating_base = phq.poor_appetite_or_overeating.1,
+    phq.feeling_bad_failure_family_base = phq.feeling_bad_failure_family.1,
+    phq.trouble_concentrating_reading_newspaper_base = phq.trouble_concentrating_newspaper_reading.1, # differ NBR prepandemic
+    phq.moving_fidgety_noticed_opposite_base = phq.moving_fidgety_opposite_slowly.1, # differ NBR prepandemic
+    phq.dead_hurting_thoughts_base = phq.dead_hurting_thoughts.1
+  ) %>%
+  add_numeric(., exclude = exclude_cols) %>%
+  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
+  mutate_if(is.numeric, ~na_if(., -99)) %>%
+  mutate_if(is.numeric, ~na_if(., -77)) %>%
+  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
+  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
+
+# Inspect dimensions
+dim(coping.nbr.phq.raw.id)
+# Inspect colnames
+colnames(coping.nbr.phq.raw.id)
+#Differences
+dim(coping.nbr.phq.raw)[1]-dim(coping.nbr.phq.raw.id)[1]
+}
+```
+
+```{r coping nbr gad copy}
+if(NBR == TRUE) {
+  coping.phq.raw.id <- coping.nbr.phq.raw.id
+}
+```
+
+## RAMP
+```{r coping ramp phq cols}
+if(RAMP == TRUE) {
+coping.ramp.phq.raw <- readRDS(file = paste0(data.raw_path, "/ramp/phq_coping_ramp.rds"))
+dim(coping.ramp.phq.raw)
+colnames(coping.ramp.phq.raw)
+}
+```
+
+```{r coping ramp phq summary labels}
+if(RAMP == TRUE) {
+summarytools::dfSummary(
+  coping.ramp.phq.raw,
+  graph.col = F,
+  valid.col = F
+  #labels.col = F
+)
+}
+```
+
+Will need to double check these namings once we have the new cleaned data -- KT. 
+```{r coping ramp phq cleaning}
+if(RAMP == TRUE) {
+coping.ramp.phq.raw.id <- coping.ramp.phq.raw %>%
+  drop_na(externalDataReference) %>% # Drop NAs
+  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
+  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
+  mutate(ID = as.numeric(ID)
+  ) %>%
+  select(
+    Sample, # Sample
+    ID, # ID
+    phq.problems_made_difficult_care,
+    phq.pandemic_felt_feelings,
+    phq.little_interest_or_pleasure_in_doing_things_retro = phq.little_interest_or_pleasure_in_doing_things,
+    phq.feeling_down_depressed_or_hopeless_retro = phq.feeling_down_depressed_or_hopeless,
+    phq.staying_asleep_sleeping_trouble_retro = phq.staying_asleep_sleeping_trouble,
+    phq.feeling_tired_or_having_little_energy_retro = phq.feeling_tired_or_having_little_energy,
+    phq.poor_appetite_or_overeating_retro = phq.poor_appetite_or_overeating,
+    phq.feeling_bad_failure_family_retro = phq.feeling_bad_failure_family,
+    phq.trouble_concentrating_reading_newspaper_retro = phq.trouble_concentrating_newspaper_reading, # differ RAMP prepandemic
+    phq.moving_fidgety_noticed_opposite_retro = phq.moving_fidgety_opposite_slowly, # differ RAMP prepandemic
+    phq.dead_hurting_thoughts_retro = phq.dead_hurting_thoughts,
+    phq.little_interest_or_pleasure_in_doing_things_base = phq.little_interest_or_pleasure_in_doing_things.1,
+    phq.feeling_down_depressed_or_hopeless_base = phq.feeling_down_depressed_or_hopeless.1,
+    phq.staying_asleep_sleeping_trouble_base = phq.staying_asleep_sleeping_trouble.1,
+    phq.feeling_tired_or_having_little_energy_base = phq.feeling_tired_or_having_little_energy.1,
+    phq.poor_appetite_or_overeating_base = phq.poor_appetite_or_overeating.1,
+    phq.feeling_bad_failure_family_base = phq.feeling_bad_failure_family.1,
+    phq.trouble_concentrating_reading_newspaper_base = phq.trouble_concentrating_newspaper_reading.1, # differ RAMP prepandemic
+    phq.moving_fidgety_noticed_opposite_base = phq.moving_fidgety_opposite_slowly.1, # differ RAMP prepandemic
+    phq.dead_hurting_thoughts_base = phq.dead_hurting_thoughts.1
+  ) %>%
+  add_numeric(., exclude = exclude_cols) %>%
+  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
+  mutate_if(is.numeric, ~na_if(., -99)) %>%
+  mutate_if(is.numeric, ~na_if(., -77)) %>%
+  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
+  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
+
+# Inspect dimensions
+dim(coping.ramp.phq.raw.id)
+# Inspect colnames
+colnames(coping.ramp.phq.raw.id)
+#Differences
+dim(coping.ramp.phq.raw)[1]-dim(coping.ramp.phq.raw.id)[1]
+}
+```
+
+```{r coping ramp gad copy}
+if(RAMP == TRUE) {
+  coping.phq.raw.id <- coping.ramp.phq.raw.id
+}
+```
+
+## Sum scores
 
@@
 
+## Inspection
+
 ```{r coping glad phq head}
@@
 
-# glad COPING ocir
-
+# COPING: OCI-R
+
+## GLAD
 ```{r coping glad ocir cols}
+if(GLAD == TRUE) {
 coping.glad.ocir.raw <- readRDS(file = paste0(data.raw_path, "/glad/ocir_coping_glad.rds"))
@@
 colnames(coping.glad.ocir.raw)
+}
 ```
@@
 ```{r coping glad ocir summary labels}
+if(GLAD == TRUE) {
 summarytools::dfSummary(
@@
 ```{r coping glad ocir cleaning}
+if(GLAD == TRUE) {
 coping.glad.ocir.raw.id <- coping.glad.ocir.raw %>%
@@
 dim(coping.glad.ocir.raw)[1]-dim(coping.glad.ocir.raw.id)[1]
-```
+}
+```
+
+```{r coping glad ocir copy}
+if(GLAD == TRUE) {
+  coping.ocir.raw.id <- coping.glad.ocir.raw.id
+}
+```
+
+## EDGI
+```{r coping edgi ocir cols}
+if(EDGI == TRUE) {
+coping.edgi.ocir.raw <- readRDS(file = paste0(data.raw_path, "/edgi/ocir_coping_edgi.rds"))
+dim(coping.edgi.ocir.raw)
+colnames(coping.edgi.ocir.raw)
+}
+```
+
+```{r coping edgi ocir summary labels}
+if(EDGI == TRUE) {
+summarytools::dfSummary(
+  coping.edgi.ocir.raw,
+  graph.col = F,
+  valid.col = F
+  #labels.col = F
+)
+}
+```
+
+*Note that the COPING EDGI OCI-R ID numbers are stored under recipientFirstName (rather than ExternalDataReference)
+```{r coping edgi ocir cleaning}
+if(EDGI == TRUE) {
+coping.edgi.ocir.raw.id <- coping.edgi.ocir.raw %>%
+  drop_na(recipientFirstName) %>% # Drop NAs
+  distinct(recipientFirstName, .keep_all = TRUE) %>% # Remove duplicates based on ID
+  separate(recipientFirstName, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
+  mutate(ID = as.numeric(ID),
+         startDate.coping = startDate) %>% # Rename startDate
+  select(
+    Sample, # Sample
+    ID, # ID
+    ocir.felt_pandemic_feelings, # Comparison to before the pandemic
+    ocir.i_repeatedly_check_doors_windows_drawers_etc_retro = ocir.i_repeatedly_check_doors_windows_drawers_etc.,
+    ocir.arranged_things_change_upset_retro = ocir.arranged_things_change_upset,
+    ocir.repeat_feel_numbers_retro = ocir.numbers_repeat_feel, ## Different from EDGI prepandemic
+    ocir.clean_simply_wash_feel_retro = ocir.feel_contaminated_clean_simply, ## Different from EDGI prepandemic
+    ocir.mind_upset_unpleasant_thoughts_retro = ocir.mind_upset_unpleasant_thoughts,
+    ocir.afraid_avoid_throwing_things_retro = ocir.afraid_avoid_throwing_things,
+    ocir.light_switches_water_taps_retro = ocir.light_switches_water_taps,
+    ocir.arranged_things_retro = ocir.arranged_things,
+    ocir.good_feel_bad_numbers_retro = ocir.bad_numbers_good_feel, ## Different from EDGI prepandemic
+    ocir.hands_longer_wash_retro = ocir.longer_hands_wash, ## Different from EDGI prepandemic
+    ocir.saved_things_retro = ocir.saved_things,
+    ocir.frequently_difficulty_rid_nasty_retro = ocir.frequently_rid_difficulty_nasty, ## Different from EDGI prepandemic
+    ocir.i_check_things_more_often_than_necessary_retro = ocir.i_check_things_more_often_than_necessary.,
+    ocir.arranged_properly_objects_upset_retro = ocir.arranged_properly_objects_upset,
+    ocir.feel_compelled_count_things_retro = ocir.feel_compelled_count_things,
+    ocir.strangers_touch_touched_difficult_retro = ocir.strangers_touch_touched_object, ## Different from EDGI prepandemic
+    ocir.control_difficult_find_thoughts_retro = ocir.control_find_difficult_thoughts, ## Different from EDGI prepandemic
+    ocir.i_collect_things_i_dont_need_retro = ocir.i_collect_things_i_dont_need., ## Different from EDGI prepandemic
+    ocir.i_repeatedly_check_doors_windows_drawers_etc_base = ocir.i_repeatedly_check_doors_windows_drawers_etc..1,
+    ocir.arranged_things_change_upset_base = ocir.arranged_things_change_upset.1,
+    ocir.repeat_feel_numbers_base = ocir.numbers_repeat_feel.1, ## Different from EDGI prepandemic
+    ocir.clean_simply_wash_feel_base = ocir.feel_contaminated_clean_simply.1, ## Different from EDGI prepandemic
+    ocir.mind_upset_unpleasant_thoughts_base = ocir.mind_upset_unpleasant_thoughts.1,
+    ocir.afraid_avoid_throwing_things_base = ocir.afraid_avoid_throwing_things.1,
+    ocir.light_switches_water_taps_base = ocir.light_switches_water_taps.1,
+    ocir.arranged_things_base = ocir.arranged_things.1,
+    ocir.good_feel_bad_numbers_base = ocir.bad_numbers_good_feel.1, ## Different from EDGI prepandemic
+    ocir.hands_longer_wash_base = ocir.longer_hands_wash.1, ## Different from EDGI prepandemic
+    ocir.saved_things_base = ocir.saved_things.1,
+    ocir.frequently_difficulty_rid_nasty_base = ocir.frequently_rid_difficulty_nasty.1, ## Different from EDGI prepandemic
+    ocir.i_check_things_more_often_than_necessary_base = ocir.i_check_things_more_often_than_necessary..1,
+    ocir.arranged_properly_objects_upset_base = ocir.arranged_properly_objects_upset.1,
+    ocir.feel_compelled_count_things_base = ocir.feel_compelled_count_things.1,
+    ocir.strangers_touch_touched_difficult_base = ocir.strangers_touch_touched_object.1, ## Different from EDGI prepandemic
+    ocir.control_difficult_find_thoughts_base = ocir.control_find_difficult_thoughts.1, ## Different from EDGI prepandemic
+    ocir.i_collect_things_i_dont_need_base = ocir.i_collect_things_i_dont_need..1
+  ) %>%
+  add_numeric(., exclude = exclude_cols) %>%
+  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
+  mutate_if(is.numeric, ~na_if(., -99)) %>%
+  mutate_if(is.numeric, ~na_if(., -77)) %>%
+  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
+  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
+
+# Inspect dimensions
+dim(coping.edgi.ocir.raw.id)
+# Inspect colnames
+colnames(coping.edgi.ocir.raw.id)
+#Differences
+dim(coping.edgi.ocir.raw)[1]-dim(coping.edgi.ocir.raw.id)[1]
+}
+```
+
+```{r coping edgi ocir copy}
+if(EDGI == TRUE) {
+  coping.ocir.raw.id <- coping.edgi.ocir.raw.id
+}
+```
+
+## NBR
+```{r coping nbr ocir cols}
+if(NBR == TRUE) {
+coping.nbr.ocir.raw <- readRDS(file = paste0(data.raw_path, "/nbr/ocir_coping_nbr.rds"))
+dim(coping.nbr.ocir.raw)
+colnames(coping.nbr.ocir.raw)
+}
+```
+
+```{r coping nbr ocir summary labels}
+if(NBR == TRUE) {
+summarytools::dfSummary(
+  coping.nbr.ocir.raw,
+  graph.col = F,
+  valid.col = F
+  #labels.col = F
+)
+}
+```
+
+*Note that the COPING NBR OCI-R ID numbers are stored under recipientFirstName (rather than ExternalDataReference)
+```{r coping nbr ocir cleaning}
+if(NBR == TRUE) {
+coping.nbr.ocir.raw.id <- coping.nbr.ocir.raw %>%
+  drop_na(recipientFirstName) %>% # Drop NAs
+  distinct(recipientFirstName, .keep_all = TRUE) %>% # Remove duplicates based on ID
+  separate(recipientFirstName, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
+  mutate(ID = as.numeric(ID),
+         startDate.coping = startDate) %>% # Rename startDate
+  select(
+    Sample, # Sample
+    ID, # ID
+    ocir.felt_pandemic_feelings, # Comparison to before the pandemic
+    ocir.i_repeatedly_check_doors_windows_drawers_etc_retro = ocir.i_repeatedly_check_doors_windows_drawers_etc.,
+    ocir.arranged_things_change_upset_retro = ocir.arranged_things_change_upset,
+    ocir.repeat_feel_numbers_retro = ocir.numbers_repeat_feel, ## Different from NBR prepandemic
+    ocir.clean_simply_wash_feel_retro = ocir.feel_contaminated_clean_simply, ## Different from NBR prepandemic
+    ocir.mind_upset_unpleasant_thoughts_retro = ocir.mind_upset_unpleasant_thoughts,
+    ocir.afraid_avoid_throwing_things_retro = ocir.afraid_avoid_throwing_things,
+    ocir.light_switches_water_taps_retro = ocir.light_switches_water_taps,
+    ocir.arranged_things_retro = ocir.arranged_things,
+    ocir.good_feel_bad_numbers_retro = ocir.bad_numbers_good_feel, ## Different from NBR prepandemic
+    ocir.hands_longer_wash_retro = ocir.longer_hands_wash, ## Different from NBR prepandemic
+    ocir.saved_things_retro = ocir.saved_things,
+    ocir.frequently_difficulty_rid_nasty_retro = ocir.frequently_rid_difficulty_nasty, ## Different from NBR prepandemic
+    ocir.i_check_things_more_often_than_necessary_retro = ocir.i_check_things_more_often_than_necessary.,
+    ocir.arranged_properly_objects_upset_retro = ocir.arranged_properly_objects_upset,
+    ocir.feel_compelled_count_things_retro = ocir.feel_compelled_count_things,
+    ocir.strangers_touch_touched_difficult_retro = ocir.strangers_touch_touched_object, ## Different from NBR prepandemic
+    ocir.control_difficult_find_thoughts_retro = ocir.control_find_difficult_thoughts, ## Different from NBR prepandemic
+    ocir.i_collect_things_i_dont_need_retro = ocir.i_collect_things_i_dont_need., ## Different from NBR prepandemic
+    ocir.i_repeatedly_check_doors_windows_drawers_etc_base = ocir.i_repeatedly_check_doors_windows_drawers_etc..1,
+    ocir.arranged_things_change_upset_base = ocir.arranged_things_change_upset.1,
+    ocir.repeat_feel_numbers_base = ocir.numbers_repeat_feel.1, ## Different from NBR prepandemic
+    ocir.clean_simply_wash_feel_base = ocir.feel_contaminated_clean_simply.1, ## Different from NBR prepandemic
+    ocir.mind_upset_unpleasant_thoughts_base = ocir.mind_upset_unpleasant_thoughts.1,
+    ocir.afraid_avoid_throwing_things_base = ocir.afraid_avoid_throwing_things.1,
+    ocir.light_switches_water_taps_base = ocir.light_switches_water_taps.1,
+    ocir.arranged_things_base = ocir.arranged_things.1,
+    ocir.good_feel_bad_numbers_base = ocir.bad_numbers_good_feel.1, ## Different from NBR prepandemic
+    ocir.hands_longer_wash_base = ocir.longer_hands_wash.1, ## Different from NBR prepandemic
+    ocir.saved_things_base = ocir.saved_things.1,
+    ocir.frequently_difficulty_rid_nasty_base = ocir.frequently_rid_difficulty_nasty.1, ## Different from NBR prepandemic
+    ocir.i_check_things_more_often_than_necessary_base = ocir.i_check_things_more_often_than_necessary..1,
+    ocir.arranged_properly_objects_upset_base = ocir.arranged_properly_objects_upset.1,
+    ocir.feel_compelled_count_things_base = ocir.feel_compelled_count_things.1,
+    ocir.strangers_touch_touched_difficult_base = ocir.strangers_touch_touched_object.1, ## Different from NBR prepandemic
+    ocir.control_difficult_find_thoughts_base = ocir.control_find_difficult_thoughts.1, ## Different from NBR prepandemic
+    ocir.i_collect_things_i_dont_need_base = ocir.i_collect_things_i_dont_need..1
+  ) %>%
+  add_numeric(., exclude = exclude_cols) %>%
+  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
+  mutate_if(is.numeric, ~na_if(., -99)) %>%
+  mutate_if(is.numeric, ~na_if(., -77)) %>%
+  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
+  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
+
+# Inspect dimensions
+dim(coping.nbr.ocir.raw.id)
+# Inspect colnames
+colnames(coping.nbr.ocir.raw.id)
+#Differences
+dim(coping.nbr.ocir.raw)[1]-dim(coping.nbr.ocir.raw.id)[1]
+}
+```
+
+```{r coping nbr ocir copy}
+if(NBR == TRUE) {
+  coping.ocir.raw.id <- coping.nbr.ocir.raw.id
+}
+```
+
+## RAMP
+```{r coping ramp ocir cols}
+if(RAMP == TRUE) {
+coping.ramp.ocir.raw <- readRDS(file = paste0(data.raw_path, "/ramp/ocir_coping_ramp.rds"))
+dim(coping.ramp.ocir.raw)
+colnames(coping.ramp.ocir.raw)
+}
+```
+
+```{r coping ramp ocir summary labels}
+if(RAMP == TRUE) {
+summarytools::dfSummary(
+  coping.ramp.ocir.raw,
+  graph.col = F,
+  valid.col = F
+  #labels.col = F
+)
+}
+```
+
+*Note that the COPING RAMP OCI-R ID numbers are stored under recipientFirstName (rather than ExternalDataReference)
+```{r coping ramp ocir cleaning}
+if(RAMP == TRUE) {
+coping.ramp.ocir.raw.id <- coping.ramp.ocir.raw %>%
+  drop_na(recipientFirstName) %>% # Drop NAs
+  distinct(recipientFirstName, .keep_all = TRUE) %>% # Remove duplicates based on ID
+  separate(recipientFirstName, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
+  mutate(ID = as.numeric(ID),
+         startDate.coping = startDate) %>% # Rename startDate
+  select(
+    Sample, # Sample
+    ID, # ID
+    ocir.felt_pandemic_feelings, # Comparison to before the pandemic
+    ocir.i_repeatedly_check_doors_windows_drawers_etc_retro = ocir.i_repeatedly_check_doors_windows_drawers_etc.,
+    ocir.arranged_things_change_upset_retro = ocir.arranged_things_change_upset,
+    ocir.repeat_feel_numbers_retro = ocir.numbers_repeat_feel, ## Different from RAMP prepandemic
+    ocir.clean_simply_wash_feel_retro = ocir.feel_contaminated_clean_simply, ## Different from RAMP prepandemic
+    ocir.mind_upset_unpleasant_thoughts_retro = ocir.mind_upset_unpleasant_thoughts,
+    ocir.afraid_avoid_throwing_things_retro = ocir.afraid_avoid_throwing_things,
+    ocir.light_switches_water_taps_retro = ocir.light_switches_water_taps,
+    ocir.arranged_things_retro = ocir.arranged_things,
+    ocir.good_feel_bad_numbers_retro = ocir.bad_numbers_good_feel, ## Different from RAMP prepandemic
+    ocir.hands_longer_wash_retro = ocir.longer_hands_wash, ## Different from RAMP prepandemic
+    ocir.saved_things_retro = ocir.saved_things,
+    ocir.frequently_difficulty_rid_nasty_retro = ocir.frequently_rid_difficulty_nasty, ## Different from RAMP prepandemic
+    ocir.i_check_things_more_often_than_necessary_retro = ocir.i_check_things_more_often_than_necessary.,
+    ocir.arranged_properly_objects_upset_retro = ocir.arranged_properly_objects_upset,
+    ocir.feel_compelled_count_things_retro = ocir.feel_compelled_count_things,
+    ocir.strangers_touch_touched_difficult_retro = ocir.strangers_touch_touched_object, ## Different from RAMP prepandemic
+    ocir.control_difficult_find_thoughts_retro = ocir.control_find_difficult_thoughts, ## Different from RAMP prepandemic
+    ocir.i_collect_things_i_dont_need_retro = ocir.i_collect_things_i_dont_need., ## Different from RAMP prepandemic
+    ocir.i_repeatedly_check_doors_windows_drawers_etc_base = ocir.i_repeatedly_check_doors_windows_drawers_etc..1,
+    ocir.arranged_things_change_upset_base = ocir.arranged_things_change_upset.1,
+    ocir.repeat_feel_numbers_base = ocir.numbers_repeat_feel.1, ## Different from RAMP prepandemic
+    ocir.clean_simply_wash_feel_base = ocir.feel_contaminated_clean_simply.1, ## Different from RAMP prepandemic
+    ocir.mind_upset_unpleasant_thoughts_base = ocir.mind_upset_unpleasant_thoughts.1,
+    ocir.afraid_avoid_throwing_things_base = ocir.afraid_avoid_throwing_things.1,
+    ocir.light_switches_water_taps_base = ocir.light_switches_water_taps.1,
+    ocir.arranged_things_base = ocir.arranged_things.1,
+    ocir.good_feel_bad_numbers_base = ocir.bad_numbers_good_feel.1, ## Different from RAMP prepandemic
+    ocir.hands_longer_wash_base = ocir.longer_hands_wash.1, ## Different from RAMP prepandemic
+    ocir.saved_things_base = ocir.saved_things.1,
+    ocir.frequently_difficulty_rid_nasty_base = ocir.frequently_rid_difficulty_nasty.1, ## Different from RAMP prepandemic
+    ocir.i_check_things_more_often_than_necessary_base = ocir.i_check_things_more_often_than_necessary..1,
+    ocir.arranged_properly_objects_upset_base = ocir.arranged_properly_objects_upset.1,
+    ocir.feel_compelled_count_things_base = ocir.feel_compelled_count_things.1,
+    ocir.strangers_touch_touched_difficult_base = ocir.strangers_touch_touched_object.1, ## Different from RAMP prepandemic
+    ocir.control_difficult_find_thoughts_base = ocir.control_find_difficult_thoughts.1, ## Different from RAMP prepandemic
+    ocir.i_collect_things_i_dont_need_base = ocir.i_collect_things_i_dont_need..1
+  ) %>%
+  add_numeric(., exclude = exclude_cols) %>%
+  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
+  mutate_if(is.numeric, ~na_if(., -99)) %>%
+  mutate_if(is.numeric, ~na_if(., -77)) %>%
+  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
+  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
+
+# Inspect dimensions
+dim(coping.ramp.ocir.raw.id)
+# Inspect colnames
+colnames(coping.ramp.ocir.raw.id)
+#Differences
+dim(coping.ramp.ocir.raw)[1]-dim(coping.ramp.ocir.raw.id)[1]
+}
+```
+
+```{r coping ramp ocir copy}
+if(RAMP == TRUE) {
+  coping.ocir.raw.id <- coping.ramp.ocir.raw.id
+}
+```
+
+## Sum scores
 

### 2020-08-12 PANCHANGE_data_preprocessing2020-07-15.Rmd
changed mhd object name

@@
 
-# glad mhd
-
+# mhd
+
+## GLAD
 ```{r glad mhd cols}
+if(GLAD == TRUE) {
 glad.mhd.raw <- readRDS(file = paste0(data.raw_path,"/glad/mhd_glad.rds"))
@@
 colnames(glad.mhd.raw)
+}
 ```
@@
 ```{r glad mhd cleaning}
+if(GLAD == TRUE) {
 glad.mhd.raw.id <- glad.mhd.raw %>%
@@
 dim(glad.mhd.raw)[1]-dim(glad.mhd.raw.id)[1]
+}
 ```
@@
 ```{r glad mhd depressive_disorders}
-glad.mhd.raw.id <- glad.mhd.raw.id %>%
+mhd.raw.id <- mhd.raw.id %>%
   mutate(
@@
 
-glad.mhd.raw.id <- glad.mhd.raw.id %>%
+mhd.raw.id <- mhd.raw.id %>%
   mutate(
@@
 
-glad.mhd.raw.id %>%
+mhd.raw.id %>%
   freq(depressive_disorders,
@@
 ```{r Check depressive_disorders}
-glad.mhd.raw.id %>%
+mhd.raw.id %>%
   select(
@@
 ```{r glad mhd anxiety_disorders}
-glad.mhd.raw.id <- glad.mhd.raw.id %>%
+mhd.raw.id <- mhd.raw.id %>%
   mutate(
@@
 
-glad.mhd.raw.id %>%
+mhd.raw.id %>%
   freq(anxiety_disorders,
@@
 ```{r Check anxiety_disorders}
-glad.mhd.raw.id %>%
+mhd.raw.id %>%
   select(
@@
 ```{r glad mhd agoraphobia_panic_disorder}
-glad.mhd.raw.id <- glad.mhd.raw.id %>%
+mhd.raw.id <- mhd.raw.id %>%
   mutate(
@@
 
-glad.mhd.raw.id %>%
+mhd.raw.id %>%
   freq(agoraphobia_panic_disorder)
@@
 ```{r Check agoraphobia_panic_disorder}
-glad.mhd.raw.id %>%
+mhd.raw.id %>%
   select(
@@
 ```{r glad mhd depression_anxiety}
-glad.mhd.raw.id <- glad.mhd.raw.id %>%
+mhd.raw.id <- mhd.raw.id %>%
   mutate(
@@
 
-glad.mhd.raw.id %>%
+mhd.raw.id %>%
   freq(depression_and_anxiety,
@@
 ```{r glad mhd eating_disorders}
-glad.mhd.raw.id <- glad.mhd.raw.id %>%
+mhd.raw.id <- mhd.raw.id %>%
   mutate(
@@
 
-glad.mhd.raw.id %>%
+mhd.raw.id %>%
   freq(eating_disorders,
@@
 ```{r glad mhd restricting_vs_binge_eating_eating_disorders}
-glad.mhd.raw.id <- glad.mhd.raw.id %>%
+mhd.raw.id <- mhd.raw.id %>%
   mutate(
@@
 
-glad.mhd.raw.id %>%
+mhd.raw.id %>%
   freq(restricting_vs_binge_eating_eating_disorders,
@@
 ```{r Check eating_disorders}
-glad.mhd.raw.id %>%
+mhd.raw.id %>%
   select(
@@
 ```{r glad mhd obsessive_compulsive_disorders}
-glad.mhd.raw.id <- glad.mhd.raw.id %>%
+mhd.raw.id <- mhd.raw.id %>%
   mutate(
@@
 
-glad.mhd.raw.id %>%
+mhd.raw.id %>%
   freq(obsessive_compulsive_disorders)
@@
 ```{r Check obsessive_compulsive_disorders}
-glad.mhd.raw.id %>%
+mhd.raw.id %>%
   select(
@@
 ```{r glad mhd psychotic_disorders}
-glad.mhd.raw.id <- glad.mhd.raw.id %>%
+mhd.raw.id <- mhd.raw.id %>%
   mutate(
@@
 
-glad.mhd.raw.id %>%
+mhd.raw.id %>%
   freq(psychotic_disorders)
@@
 ```{r glad mhd bipolar_and_schizophrenia_numeric}
-glad.mhd.raw.id <- glad.mhd.raw.id %>%
+mhd.raw.id <- mhd.raw.id %>%
   mutate(
@@
 
-glad.mhd.raw.id %>%
+mhd.raw.id %>%
   freq(bipolar_and_schizophrenia,
@@
 ```{r Check psychotic_disorders}
-glad.mhd.raw.id %>%
+mhd.raw.id %>%
   select(
@@
 ```{r glad mhd personality_cluster_a}
-glad.mhd.raw.id <- glad.mhd.raw.id %>%
+mhd.raw.id <- mhd.raw.id %>%
   mutate(
@@
 
-glad.mhd.raw.id %>%
+mhd.raw.id %>%
   freq(personality_cluster_a,
@@
 ```{r Check personality_cluster_a}
-glad.mhd.raw.id %>%
+mhd.raw.id %>%
   select(
@@
 ```{r glad mhd personality_cluster_b}
-glad.mhd.raw.id <- glad.mhd.raw.id %>%
+mhd.raw.id <- mhd.raw.id %>%
   mutate(
@@
 
-glad.mhd.raw.id %>%
+mhd.raw.id %>%
   freq(personality_cluster_b,
@@
 ```{r Check personality_cluster_b}
-glad.mhd.raw.id %>%
+mhd.raw.id %>%
   select(
@@
 ```{r glad mhd personality_cluster_c}
-glad.mhd.raw.id <- glad.mhd.raw.id %>%
+mhd.raw.id <- mhd.raw.id %>%
   mutate(
@@
 
-glad.mhd.raw.id %>%
+mhd.raw.id %>%
   freq(personality_cluster_c,
@@
 ```{r Check personality_cluster_c}
-glad.mhd.raw.id %>%
+mhd.raw.id %>%
   select(
@@
 ```{r glad mhd control}
-glad.mhd.raw.id <- glad.mhd.raw.id %>%
+mhd.raw.id <- mhd.raw.id %>%
   mutate(
@@
 
-glad.mhd.raw.id %>%
+mhd.raw.id %>%
   freq(control,
@@
 
-glad.mhd.raw.id %>%
+mhd.raw.id %>%
   freq(disorders_total_count,
@@
 ```{r cormorbidity_total_count}
-glad.mhd.raw.id <- glad.mhd.raw.id %>%
+mhd.raw.id <- mhd.raw.id %>%
   mutate(
@@
 
-glad.mhd.raw.id %>%
+mhd.raw.id %>%
   freq(comorbidity_total_count_numeric,
@@
 ```{r comordbitiy_total_count_factor}
-glad.mhd.raw.id <- glad.mhd.raw.id %>%
+mhd.raw.id <- mhd.raw.id %>%
   mutate(
@@
 
-glad.mhd.raw.id %>%
+mhd.raw.id %>%
   freq(comorbidity_total_count_factor,
@@
 ```{r glad mhd head}
-head(glad.mhd.raw.id)
+head(mhd.raw.id)
 ```
@@
 summarytools::dfSummary(
-  glad.mhd.raw.id,
+  mhd.raw.id,
   graph.col = F,
@@
 ```{r glad mhd categories}
-glad.mhd.raw.categories <- glad.mhd.raw.id %>%
+mhd.raw.categories <- mhd.raw.id %>%
   select(
@@
 glad.dfs.list <- list(
-  glad.dem.raw.id,
-  glad.gad.raw.id,
-  glad.mhd.raw.categories,
-  glad.ocir.raw.id,
-  glad.pcl.raw.id,
-  glad.phq.raw.id,
+  dem.raw.id,
+  prepan.gad.raw.id,
+  prepan.mhd.raw.categories,
+  prepan.ocir.raw.id,
+  prepan.pcl.raw.id,
+  prepan.phq.raw.id,
   coping.gad.raw.id,

### 2020-08-12 PANCHANGE_data_preprocessing2020-07-15.Rmd

@@
   which(
-  glad.dem.raw.id$Age_uncleaned > age_upper_limit |
-    glad.dem.raw.id$Age_uncleaned < age_lower_limit
+  dem.raw.id$Age_uncleaned > age_upper_limit |
+    dem.raw.id$Age_uncleaned < age_lower_limit
      )
@@
 # remove age outliers
-glad.dem.raw.id <- glad.dem.raw.id %>%
+dem.raw.id <- dem.raw.id %>%
   mutate(
@@
 # Inspect colnames
-colnames(glad.dem.raw.id)
+colnames(dem.raw.id)
 ```
@@
 # Create categorical age groups per 10 years
-glad.dem.raw.id <- glad.dem.raw.id %>%
+dem.raw.id <- dem.raw.id %>%
   mutate(
@@
 
-glad.dem.raw.id <- glad.dem.raw.id %>%
+dem.raw.id <- dem.raw.id %>%
     mutate(
@@
 
-glad.dem.raw.id %>%
+dem.raw.id %>%
   freq(age_category)
@@
 #create numeric version of the highest education variable
-glad.dem.raw.id <- glad.dem.raw.id %>%
+dem.raw.id <- dem.raw.id %>%
   mutate(
@@
 #recode the numeric version into a factor
-glad.dem.raw.id <- glad.dem.raw.id %>%
+dem.raw.id <- dem.raw.id %>%
   mutate(
@@
 
-glad.dem.raw.id %>%
+dem.raw.id %>%
   freq(highest_education)
@@
 if(GLAD == TRUE | EDGI == TRUE) {
-glad.dem.raw.id %>%
+dem.raw.id %>%
   select(highest_education,
@@
 ```{r glad dem head}
-head(glad.dem.raw.id)
+head(dem.raw.id)
 ```
@@
 summarytools::dfSummary(
-  glad.dem.raw.id,
+  dem.raw.id,
   graph.col = F,
@@
 dim(glad.mhd.raw)[1]-dim(glad.mhd.raw.id)[1]
+}
+```
+
+```{r glad mhd copy}
+if(GLAD == TRUE) {
+  mhd.raw.id <- glad.mhd.raw.id
 }
@@
   prepan.gad.raw.id,
-  prepan.mhd.raw.categories,
+  mhd.raw.categories,
   prepan.ocir.raw.id,

### 2020-08-12 PANCHANGE_data_preprocessing2020-07-15.Rmd
Added read in chunk for RAMP demographic data

@@
 ```{r Specify cohort}
-GLAD = TRUE
+GLAD = FALSE
 EDGI = FALSE
 NBR = FALSE
-RAMP = FALSE
+RAMP = TRUE
 ```
@@
 
+# RAMP demographics
+## Read in data
+```{r ramp dem cols}
+if(RAMP == TRUE){
+  ramp.dem.raw <- readRDS(file = paste0(data.raw_path, "/ramp/dem_ramp.rds"))
+  dim(ramp.dem.raw)
+  colnames(ramp.dem.raw)
+}
+```
+
+```{r}
+
+```
+
+# Select variables
+```{r ramp dem cleaning}
+if(RAMP == TRUE){
+  exclude_cols_dem <- c("ID",
+                        "Sample",
+                        "startDate.ramp")
+
+ramp.dem.raw$externalDataReference <- ramp.dem.raw$`Login ID` #move Login ID to external data reference
+
+  ramp.dem.raw.id <- ramp.dem.raw %>%
+    drop_na(externalDataReference) %>% # Drop NAs
+    distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
+    separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
+    mutate(ID = as.numeric(ID),
+           startDate.ramp = startDate) %>% # Rename startDate
+    select(
+      Sample, # Sample
+     # "Login ID", # ID
+      startDate.ramp, #Date when participant signed up to ramp
+      age_category = demographics.how_old_are_you, # Age
+      Gender = demographics.which_gender_do_you_identify_with, # Gender (what [GLAD] vs which [RAMP])
+     # EduYrs = demographics.university_education_attend_school.txt, # Years in education - not in RAMP dataset
+     # demographics.college_or_university_degree, # level of education - univeristy - level of education is in employment file
+     # demographics.a_levelsas_levels_or_equivalent, # level of education - alevel
+    #  demographics.o_levelsgcses_or_equivalent, # level of education - gcse
+     # demographics.cses_or_equivalent, # level of education - cse
+     # demographics.nvq_or_hnd_or_hnc_or_equivalent, # level of education - nvq
+      Transgender_uncleaned = demographics.do_you_identify_as_transgender,
+      Ethnicity = demographics.what_is_your_ethnic_origin # Ethnicity
+    ) %>%
+    add_numeric(., exclude = exclude_cols_dem) %>%
+    mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
+    mutate_if(is.numeric, ~na_if(., -99)) %>%
+    mutate_if(is.numeric, ~na_if(., -77)) %>%
+    mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
+    mutate_if(is.factor, ~na_if(., "Don't know")) %>%
+    mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
+    mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
+    mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
+    mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
+    mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
+    mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
+
+  # Inspect dimensions
+  dim(ramp.dem.raw.id)
+  # Inspect colnames
+  colnames(ramp.dem.raw.id)
+  #Differences
+  dim(ramp.dem.raw)[1]-dim(ramp.dem.raw.id)[1]
+}
+```
+
+```{r ramp copy dem}
+if(RAMP == TRUE){
+  dem.raw.id <- ramp.dem.raw.id
+}
+```
+
 #Clean Age variable
@@
 ```{r age outlier}
+if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE ) {
 # define age limits 
@@
 colnames(dem.raw.id)
+}
 ```
@@
       )
+}
 
@@
     mutate(
-      age_category =
+      age_category_full =
         recode_factor(
@@
 dem.raw.id %>%
-  freq(age_category)
-
+  freq(age_category_full)
+
+```
+
+# RAMP employment
+## Read in data
+```{r ramp emp cols}
+if(RAMP == TRUE){
+  ramp.emp.raw <- readRDS(file = paste0(data.raw_path, "/ramp/employment_ramp.rds"))
+  dim(ramp.emp.raw)
+  colnames(ramp.emp.raw)
+}
+```
+
+# Select variables
+```{r ramp emp cleaning}
+if(RAMP == TRUE){
+  exclude_cols_emp <- c("ID",
+                        "Sample")
+
+ramp.dem.raw$externalDataReference <- ramp.dem.raw$`Login ID` #move Login ID to external data reference
+
+ramp.emp.raw.id <- ramp.emp.raw %>%
+    drop_na(externalDataReference) %>% # Drop NAs
+    distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
+    separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
+    mutate(ID = as.numeric(ID),
+           startDate.ramp = startDate) %>% # Rename startDate
+    select(
+      highest_education_ramp = employment.what_is_your_highest_level_of_education
+      # EduYrs = employment.university_education_attend_school.txt, # Years in education - not in RAMP dataset
+      # employment.college_or_university_degree, # level of education - univeristy - level of education is in employment file
+      # employment.a_levelsas_levels_or_equivalent, # level of education - alevel
+      # employment.o_levelsgcses_or_equivalent, # level of education - gcse
+      # employment.cses_or_equivalent, # level of education - cse
+      # employment.nvq_or_hnd_or_hnc_or_equivalent, # level of education - nvq
+    ) %>%
+    add_numeric(., exclude = exclude_cols_emp) %>%
+    mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
+    mutate_if(is.numeric, ~na_if(., -99)) %>%
+    mutate_if(is.numeric, ~na_if(., -77)) %>%
+    mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
+    mutate_if(is.factor, ~na_if(., "Don't know")) %>%
+    mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
+    mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
+    mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
+    mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
+    mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
+    mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
+
+  # Inspect dimensions
+  dim(ramp.emp.raw.id)
+  # Inspect colnames
+  colnames(ramp.emp.raw.id)
+  #Differences
+  dim(ramp.emp.raw)[1]-dim(ramp.emp.raw.id)[1]
+}
+```
+
+```{r ramp copy emp}
+if(RAMP == TRUE){
+  emp.raw.id <- ramp.emp.raw.id
 }

### 2020-08-12 PANCHANGE_data_preprocessing2020-07-15.Rmd
Removed education cleaning from NBR demographics because these variables are in a different section for NBR.

--- 2020-08-12 PANCHANGE_data_preprocessing2020-07-15.Rmd
@@
 ```{r Specify cohort}
-GLAD = TRUE
+GLAD = FALSE
 EDGI = FALSE
-NBR = FALSE
+NBR = TRUE
 RAMP = FALSE
@@
       Sex = demographics.select_questionnaire_items_medical, #Sex
-      EduYrs = demographics.school_education_school_years.txt, # Years in education
-      demographics.college_or_university_degree, # level of education - univeristy
-      demographics.a_levelsas_levels_or_equivalent, # level of education - alevel
-      demographics.o_levelsgcses_or_equivalent, # level of education - gcse
-      demographics.cses_or_equivalent, # level of education - cse
-      demographics.nvq_or_hnd_or_hnc_or_equivalent, # level of education - nvq
       Ethnicity = demographics.questions_based_ethnic_origin # Ethnicity

### 2020-08-12 PANCHANGE_data_preprocessing2020-07-15.Rmd
Added chunk to calculate NBR age and to combine NBR cohort and COPING demographic data.

@@
 #install.packages("dplyr")
+#install.packages("eeptools")
 ```
@@
 library(tidyverse)
+library(eeptools)
 ```
@@
 #      Age_uncleaned = demographics.how_old_are_you_now.txt, # Age
-      Birthyear = demographics.year, # Birthyear
+      Birthyear_unc = demographics.year, # Birthyear
+      Birthmonth = demographics.month, #Birthmonth
+      Birthday = demographics.day, #Birthday
       Gender = demographics.which_gender_do_you_identify_with, # Gender
       Sex = demographics.select_questionnaire_items_medical, #Sex
-      Ethnicity = demographics.questions_based_ethnic_origin # Ethnicity
+#      Ethnicity = demographics.questions_based_ethnic_origin # Ethnicity
     ) %>%
@@
 
+```{r nbr dem calculating age from birthday}
+if(NBR == TRUE) {
+#add 1900 to birthyear
+nbr.dem.raw.id$Birthyear_numeric <- nbr.dem.raw.id$Birthyear_unc_numeric + 1900
+
+#create dob as date format
+nbr.dem.raw.id$Birthdate <- as.Date(paste(nbr.dem.raw.id$Birthyear_numeric,
+                                  nbr.dem.raw.id$Birthmonth_numeric,
+                                  nbr.dem.raw.id$Birthday_numeric,
+                                  sep = "-"))
+
+head(nbr.dem.raw.id$Birthdate)
+
+#Calculate dem.age(remove NAs as it throws an error)
+ages <- age_calc(na.omit(nbr.dem.raw.id$Birthdate), enddate = Sys.Date(), units = "years")
+
+#Create dem.agecolumn
+nbr.dem.raw.id$Age_uncleaned<- NA
+
+#Populate with values (excluding NAs)
+nbr.dem.raw.id$Age_uncleaned[!is.na(nbr.dem.raw.id$Birthdate)] <- ages
+
+#Round age down
+nbr.dem.raw.id$Age_uncleaned <- floor(nbr.dem.raw.id$Age_uncleaned)
+
+#Visualise
+head(nbr.dem.raw.id$Age_uncleaned)
+head(nbr.dem.raw.id$Birthdate)
+}
+```
+
 ## Cohort information
@@
 #         startDate.coping, #Date when participant signed up to NBR COPING
-         Age_uncleaned = age, # Age
+#         Age_uncleaned = age, # Age
          Gender = gender, # Gender
@@
 
-```{r nbr copy dem}
+```{r nbr combine demographics}
 if(NBR == TRUE){
-dem.raw.id <- nbr.dem.raw.id
+dem.raw.id <- merge(nbr.cohort.raw.id, nbr.dem.raw.id, by = "ID")
 }

### 2020-08-12 PANCHANGE_data_preprocessing2020-07-15.Rmd
Corrected some errors. Kept gender only in the NBR COPING data to avoid duplication. Included NBR cohort variable.

@@
          ID, # ID
+         Cohort = cohort, #cohort information
 #         startDate.coping, #Date when participant signed up to NBR COPING
 #         Age_uncleaned = age, # Age
-         Gender = gender, # Gender
+#         Gender = gender, # Gender
 #         Sex = demographics.select_questionnaire_items_medical, #Sex
@@
 if(NBR == TRUE){
-dem.raw.id <- merge(nbr.cohort.raw.id, nbr.dem.raw.id, by = "ID")
+dem.raw.id <- merge(nbr.cohort.raw.id, nbr.dem.raw.id, by = c("Sample", "ID"))
 }
@@
 summarytools::dfSummary(
-  nbr.cohort.raw.id,
+  dem.raw.id,
   graph.col = F,

### 2020-08-13 PANCHANGE_data_preprocessing2020-07-15.Rmd
read in RMAP employment data

--- 2020-08-12 PANCHANGE_data_preprocessing2020-07-15.Rmd
@@
 EDGI = FALSE
-NBR = TRUE
-RAMP = FALSE
+NBR = FALSE
+RAMP = TRUE
 ```
@@
       Sex = demographics.select_questionnaire_items_medical, #Sex
+      EduYrs = demographics.school_education_school_years.txt, # Years in education
+      demographics.college_or_university_degree, # level of education - univeristy
+      demographics.a_levelsas_levels_or_equivalent, # level of education - alevel
+      demographics.o_levelsgcses_or_equivalent, # level of education - gcse
+      demographics.cses_or_equivalent, # level of education - cse
+      demographics.nvq_or_hnd_or_hnc_or_equivalent, # level of education - nvq
       Ethnicity = demographics.questions_based_ethnic_origin # Ethnicity
@@
 dem.raw.id %>%
-  freq(age_category)
-
+  freq(age_category_full)
+
+```
+
+# RAMP employment
+## Read in data
+```{r ramp emp cols}
+if(RAMP == TRUE){
+  ramp.emp.raw <- readRDS(file = paste0(data.raw_path, "/ramp/employment_ramp.rds"))
+  dim(ramp.emp.raw)
+  colnames(ramp.emp.raw)
+}
+```
+
+# Select variables
+```{r ramp emp cleaning}
+if(RAMP == TRUE){
+  exclude_cols_emp <- c("ID",
+                        "Sample")
+
+ramp.emp.raw$externalDataReference <- ramp.emp.raw$`Login ID` #move Login ID to external data reference
+
+ramp.emp.raw.id <- ramp.emp.raw %>%
+    drop_na(externalDataReference) %>% # Drop NAs
+    distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
+    separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
+    mutate(ID = as.numeric(ID),
+           startDate.ramp = startDate) %>% # Rename startDate
+    select(
+      highest_education_ramp = employment.what_is_your_highest_level_of_education,
+      # EduYrs = employment.university_education_attend_school.txt, # Years in education - not in RAMP dataset
+      employment.government_work_key_workers
+    ) %>%
+    add_numeric(., exclude = exclude_cols_emp) %>%
+    mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
+    mutate_if(is.numeric, ~na_if(., -99)) %>%
+    mutate_if(is.numeric, ~na_if(., -77)) %>%
+    mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
+    mutate_if(is.factor, ~na_if(., "Don't know")) %>%
+    mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
+    mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
+    mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
+    mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
+    mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
+    mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
+
+  # Inspect dimensions
+  dim(ramp.emp.raw.id)
+  # Inspect colnames
+  colnames(ramp.emp.raw.id)
+  #Differences
+  dim(ramp.emp.raw)[1]-dim(ramp.emp.raw.id)[1]
+}
+```
+
+```{r ramp copy emp}
+if(RAMP == TRUE){
+  emp.raw.id <- ramp.emp.raw.id
 }

### 2020-08-13 PANCHANGE_data_preprocessing2020-07-15.Rmd
Script running up until glad.gad

@@
       Sample, # Sample
-     # "Login ID", # ID
+      ID, # ID
       startDate.ramp, #Date when participant signed up to ramp
@@
 if(RAMP == TRUE){
-  ramp.emp.raw <- readRDS(file = paste0(data.raw_path, "/ramp/employment_ramp.rds"))
-  dim(ramp.emp.raw)
-  colnames(ramp.emp.raw)
+  ramp.employment.raw <- readRDS(file = paste0(data.raw_path, "/ramp/employment_ramp.rds"))
+  dim(ramp.employment.raw)
+  colnames(ramp.employment.raw)
 }
@@
 if(RAMP == TRUE){
-  exclude_cols_emp <- c("ID",
-                        "Sample")
-
-ramp.emp.raw$externalDataReference <- ramp.emp.raw$`Login ID` #move Login ID to external data reference
-
-ramp.emp.raw.id <- ramp.emp.raw %>%
+  exclude_cols_employment <- c("ID",
+                        "Sample",
+                        "startDate.ramp")
+
+ramp.employment.raw$externalDataReference <- ramp.employment.raw$`Login ID` #move Login ID to external data reference
+
+ramp.employment.raw.id <- ramp.employment.raw %>%
     drop_na(externalDataReference) %>% # Drop NAs
@@
     select(
-      highest_education_ramp = employment.what_is_your_highest_level_of_education,
+      Sample,
+      ID,
+      startDate.ramp,
+      highest_education_ramp = employment.what_is_your_highest_level_of_education, #this is missing NVQ or equivalent which we have in GLAD-COPING
       # EduYrs = employment.university_education_attend_school.txt, # Years in education - not in RAMP dataset
@@
   # Inspect dimensions
-  dim(ramp.emp.raw.id)
+  dim(ramp.employment.raw.id)
   # Inspect colnames
-  colnames(ramp.emp.raw.id)
+  colnames(ramp.employment.raw.id)
   #Differences
-  dim(ramp.emp.raw)[1]-dim(ramp.emp.raw.id)[1]
+  dim(ramp.employment.raw)[1]-dim(ramp.employment.raw.id)[1]
 }
@@
 if(RAMP == TRUE){
-  emp.raw.id <- ramp.emp.raw.id
+  employment.raw.id <- ramp.employment.raw.id
 }
@@
 
+```{r GLAD copy employment}
+if(RAMP == GLAD){
+  employment.raw.id <- glad.employment.raw.id
+}
+```
+
 # Highest education
@@
 #create numeric version of the highest education variable
-glad.employment.raw.id <- glad.employment.raw.id %>%
+employment.raw.id <- employment.raw.id %>%
   mutate(
@@
 #recode the numeric version into a factor
-glad.employment.raw.id <- glad.employment.raw.id %>%
+employment.raw.id <- employment.raw.id %>%
   mutate(
@@
 
-glad.employment.raw.id %>%
+employment.raw.id %>%
   freq(highest_education)
@@
 if(GLAD == TRUE | EDGI == TRUE) {
-glad.employment.raw.id %>%
+employment.raw.id %>%
   select(highest_education,
@@
 #create numeric version of the variable
-glad.employment.raw.id <- glad.employment.raw.id %>%
+employment.raw.id <- employment.raw.id %>%
   mutate(
@@
 
-glad.employment.raw.id %>%
+employment.raw.id %>%
   freq(key_worker)

### 2020-08-13 PANCHANGE_data_preprocessing2020-07-15.Rmd
forgot to save recent changes

@@
     ) %>%
-    add_numeric(., exclude = exclude_cols_emp) %>%
+    add_numeric(., exclude = exclude_cols_employment) %>%
     mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables

### 2020-08-13 PANCHANGE_data_preprocessing2020-07-15.Rmd
Recoded NBR ethnicity factors to match GLAD/EDGI/RAMP. Edited script to merge NBR dem and cohort datasets to use tidyverse.

--- 2020-08-13 PANCHANGE_data_preprocessing2020-07-15.Rmd
@@
 EDGI = FALSE
-NBR = FALSE
-RAMP = TRUE
+NBR = TRUE
+RAMP = FALSE
 ```
@@
 
-# Select variables
+## Select variables
 ```{r glad dem cleaning}
@@
 
-# Select variables
+## Select variables
 ```{r edgi dem cleaning}
@@
 
-# Select variables
+## Select variables
 ```{r nbr dem cleaning}
@@
 #      Age_uncleaned = demographics.how_old_are_you_now.txt, # Age
-      Birthyear = demographics.year, # Birthyear
+      Birthyear_unc = demographics.year, # Birthyear
+      Birthmonth = demographics.month, #Birthmonth
+      Birthday = demographics.day, #Birthday
       Gender = demographics.which_gender_do_you_identify_with, # Gender
       Sex = demographics.select_questionnaire_items_medical, #Sex
-      EduYrs = demographics.school_education_school_years.txt, # Years in education
-      demographics.college_or_university_degree, # level of education - univeristy
-      demographics.a_levelsas_levels_or_equivalent, # level of education - alevel
-      demographics.o_levelsgcses_or_equivalent, # level of education - gcse
-      demographics.cses_or_equivalent, # level of education - cse
-      demographics.nvq_or_hnd_or_hnc_or_equivalent, # level of education - nvq
-      Ethnicity = demographics.questions_based_ethnic_origin # Ethnicity
+#      Ethnicity = demographics.questions_based_ethnic_origin # Ethnicity
     ) %>%
@@
 
-```{r nbr dem cleaning}
+```{r nbr cohort cleaning}
 if(NBR == TRUE) {
@@
          ID, # ID
+         Cohort = cohort, #cohort information
 #         startDate.coping, #Date when participant signed up to NBR COPING
-         Age_uncleaned = age, # Age
-         Gender = gender, # Gender
+#         Age_uncleaned = age, # Age
+#         Gender = gender, # Gender
 #         Sex = demographics.select_questionnaire_items_medical, #Sex
@@
 #         demographics.nvq_or_hnd_or_hnc_or_equivalent, # level of education - nvq
-         Ethnicity = ethnicity # Ethnicity
+         Ethnicity.unc = ethnicity # Ethnicity
          ) %>%
@@
 
-```{r nbr copy dem}
+```{r nbr cohort recode ethnicity}
+#Recode details ethnicity info
+nbr.cohort.raw.id$Ethnicity_full <- recode_factor(nbr.cohort.raw.id$Ethnicity.unc,
+                                             "A" = "White - British",
+                                             "B" = "White - Irish",
+                                             "C" = "White - Other",
+                                             "D" = "Mixed - White & Black Caribbean",
+                                             "E" = "Mixed - White & Black African",
+                                             "F" = "Mixed - White & Asian",
+                                             "G" = "Mixed - Other",
+                                             "H" = "Asian - Indian",
+                                             "J" = "Asian - Pakistani",
+                                             "K" = "Asian - Bangladeshi",
+                                             "L" = "Asian - Other",
+                                             "M" = "Black - Caribbean",
+                                             "N" = "Black - African",
+                                             "P" = "Black - Other",
+                                             "R" = "Chinese - Chinese",
+                                             "S" = "Chinese - Other",
+                                             "W" = NULL, ## Asking NBR what this level means
+                                             "Z" = NULL,
+                                             "99" = NULL)
+
+#Match GLAD/EDGI/RAMP categories
+nbr.cohort.raw.id$Ethnicity <- recode_factor(nbr.cohort.raw.id$Ethnicity.unc,
+                                             "A" = "White, white European or Caucasian",
+                                             "B" = "White, white European or Caucasian",
+                                             "C" = "White, white European or Caucasian",
+                                             "D" = "Mixed or multiple ethnic origins",
+                                             "E" = "Mixed or multiple ethnic origins",
+                                             "F" = "Mixed or multiple ethnic origins",
+                                             "G" = "Mixed or multiple ethnic origins",
+                                             "H" = "Asian or Asian British (including Chinese)",
+                                             "J" = "Asian or Asian British (including Chinese)",
+                                             "K" = "Asian or Asian British (including Chinese)",
+                                             "L" = "Asian or Asian British (including Chinese)",
+                                             "M" = "Black or Black British",
+                                             "N" = "Black or Black British",
+                                             "P" = "Black or Black British",
+                                             "R" = "Asian or Asian British (including Chinese)",
+                                             "S" = "Asian or Asian British (including Chinese)",
+                                             "W" = NULL, ## Asking NBR what this level means
+                                             "Z" = NULL,
+                                             "99" = NULL)
+
+```
+
+```{r nbr combine demographics}
 if(NBR == TRUE){
-dem.raw.id <- nbr.dem.raw.id
+dem.raw.id <- left_join(nbr.dem.raw.id, nbr.cohort.raw.id, by = c("Sample", "ID"))
+
+# Inspect dimensions
+dim(dem.raw.id)
+# Inspect colnames
+colnames(dem.raw.id)
+#Differences
+dim(nbr.dem.raw.id)[1]-dim(dem.raw.id)[1]
 }
@@
 
-# RAMP demographics
-## Read in data
-```{r ramp dem cols}
-if(RAMP == TRUE){
-  ramp.dem.raw <- readRDS(file = paste0(data.raw_path, "/ramp/dem_ramp.rds"))
-  dim(ramp.dem.raw)
-  colnames(ramp.dem.raw)
-}
-```
-
-```{r}
-
-```
-
-# Select variables
-```{r ramp dem cleaning}
-if(RAMP == TRUE){
-  exclude_cols_dem <- c("ID",
-                        "Sample",
-                        "startDate.ramp")
-
-ramp.dem.raw$externalDataReference <- ramp.dem.raw$`Login ID` #move Login ID to external data reference
-
-  ramp.dem.raw.id <- ramp.dem.raw %>%
-    drop_na(externalDataReference) %>% # Drop NAs
-    distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
-    separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
-    mutate(ID = as.numeric(ID),
-           startDate.ramp = startDate) %>% # Rename startDate
-    select(
-      Sample, # Sample
-     # "Login ID", # ID
-      startDate.ramp, #Date when participant signed up to ramp
-      age_category = demographics.how_old_are_you, # Age
-      Gender = demographics.which_gender_do_you_identify_with, # Gender (what [GLAD] vs which [RAMP])
-     # EduYrs = demographics.university_education_attend_school.txt, # Years in education - not in RAMP dataset
-     # demographics.college_or_university_degree, # level of education - univeristy - level of education is in employment file
-     # demographics.a_levelsas_levels_or_equivalent, # level of education - alevel
-    #  demographics.o_levelsgcses_or_equivalent, # level of education - gcse
-     # demographics.cses_or_equivalent, # level of education - cse
-     # demographics.nvq_or_hnd_or_hnc_or_equivalent, # level of education - nvq
-      Transgender_uncleaned = demographics.do_you_identify_as_transgender,
-      Ethnicity = demographics.what_is_your_ethnic_origin # Ethnicity
-    ) %>%
-    add_numeric(., exclude = exclude_cols_dem) %>%
-    mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
-    mutate_if(is.numeric, ~na_if(., -99)) %>%
-    mutate_if(is.numeric, ~na_if(., -77)) %>%
-    mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
-    mutate_if(is.factor, ~na_if(., "Don't know")) %>%
-    mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
-    mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
-    mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
-    mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
-    mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
-    mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
-
-  # Inspect dimensions
-  dim(ramp.dem.raw.id)
-  # Inspect colnames
-  colnames(ramp.dem.raw.id)
-  #Differences
-  dim(ramp.dem.raw)[1]-dim(ramp.dem.raw.id)[1]
-}
-```
-
-```{r ramp copy dem}
-if(RAMP == TRUE){
-  dem.raw.id <- ramp.dem.raw.id
-}
-```
-
 #Clean Age variable
@@
 ```{r age outlier}
-if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE ) {
 # define age limits 
@@
 colnames(dem.raw.id)
-}
 ```
@@
       )
-}
 
@@
     mutate(
-      age_category_full =
+      age_category =
         recode_factor(
@@
 dem.raw.id %>%
-  freq(age_category_full)
-
-```
-
-# RAMP employment
-## Read in data
-```{r ramp emp cols}
-if(RAMP == TRUE){
-  ramp.emp.raw <- readRDS(file = paste0(data.raw_path, "/ramp/employment_ramp.rds"))
-  dim(ramp.emp.raw)
-  colnames(ramp.emp.raw)
-}
-```
-
-# Select variables
-```{r ramp emp cleaning}
-if(RAMP == TRUE){
-  exclude_cols_emp <- c("ID",
-                        "Sample")
-
-ramp.emp.raw$externalDataReference <- ramp.emp.raw$`Login ID` #move Login ID to external data reference
-
-ramp.emp.raw.id <- ramp.emp.raw %>%
-    drop_na(externalDataReference) %>% # Drop NAs
-    distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
-    separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
-    mutate(ID = as.numeric(ID),
-           startDate.ramp = startDate) %>% # Rename startDate
-    select(
-      highest_education_ramp = employment.what_is_your_highest_level_of_education,
-      # EduYrs = employment.university_education_attend_school.txt, # Years in education - not in RAMP dataset
-      employment.government_work_key_workers
-    ) %>%
-    add_numeric(., exclude = exclude_cols_emp) %>%
-    mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
-    mutate_if(is.numeric, ~na_if(., -99)) %>%
-    mutate_if(is.numeric, ~na_if(., -77)) %>%
-    mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
-    mutate_if(is.factor, ~na_if(., "Don't know")) %>%
-    mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
-    mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
-    mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
-    mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
-    mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
-    mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
-
-  # Inspect dimensions
-  dim(ramp.emp.raw.id)
-  # Inspect colnames
-  colnames(ramp.emp.raw.id)
-  #Differences
-  dim(ramp.emp.raw)[1]-dim(ramp.emp.raw.id)[1]
-}
-```
-
-```{r ramp copy emp}
-if(RAMP == TRUE){
-  emp.raw.id <- ramp.emp.raw.id
-}
-```
-
-# Highest education
+  freq(age_category)
+
+}
+```
+
+# Highest education (prepandemic)
 Proceed along qualifications fields. If field is not blank, take that as highest qual. If field is blank, check next field. If all fields are blank, NA
 Assumes University degree > A level > NVQ > GCSE/O Level/CSE
-```{r Highest education}
+```{r Highest education prepandemic}
 if(GLAD == TRUE | EDGI == TRUE) {
@@
 Check highest education coding
-```{r Highest education check}
+```{r Highest education prepandemic check}
 if(GLAD == TRUE | EDGI == TRUE) {
@@
 
-# GLAD employment
+# Employment/highest education (baseline)
+
 ## Read in data
-```{r glad dem cols}
+```{r glad employment cols}
 if(GLAD == TRUE){
@@
 dim(glad.employment.raw)[1]-dim(glad.employment.raw.id)[1]
+}
+```
+
+```{r nbr employment cols}
+if(NBR == TRUE){
+nbr.employment.raw <- readRDS(file = paste0(data.raw_path, "/nbr/employment_coping_nbr.rds"))
+dim(nbr.employment.raw)
+colnames(nbr.employment.raw)
+}
+```
+
+# Select variables
+```{r nbr employment cleaning}
+if(NBR == TRUE){
+exclude_cols_employment <- c("ID",
+                  "Sample")
+
+nbr.employment.raw.id <- nbr.employment.raw %>%
+  drop_na(externalDataReference) %>% # Drop NAs
+  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
+  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
+  mutate(
+    ID = as.numeric(ID)
+    ) %>%
+  select(
+         Sample, # Sample
+         ID, # ID
+         employment.phd, # level of education - univeristy
+         employment.masters_degree_or_equivalent, # level of education - univeristy
+         employment.postgraduate_degree_or_equivalent, # level of education - univeristy
+         employment.bachelors_degree_or_equivalent, # level of education - univeristy
+         employment.a_levelsas_levels_or_equivalent, # level of education - alevel
+         employment.o_levelsgcses_or_equivalent, # level of education - gcse
+         employment.cses_or_equivalent, # level of education - cse
+         employment.nvq_or_hnd_or_hnc_or_equivalent, # level of education - nvq
+         employment.government_work_key_workers # key worker status
+         ) %>%
+  add_numeric(., exclude = exclude_cols_employment) %>%
+  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
+  mutate_if(is.numeric, ~na_if(., -99)) %>%
+  mutate_if(is.numeric, ~na_if(., -77)) %>%
+  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
+  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
+
+# Inspect dimensions
+dim(nbr.employment.raw.id)
+# Inspect colnames
+colnames(nbr.employment.raw.id)
+#Differences
+dim(nbr.employment.raw)[1]-dim(nbr.employment.raw.id)[1]
 }

### 2020-08-13 PANCHANGE_data_preprocessing2020-07-15.Rmd
Reorganised dem summary chunks for the cohorts to make more sense.

@@
 
+```{r glad dem summary}
+if(GLAD == TRUE) {
+summarytools::dfSummary(
+  dem.raw.id,
+  graph.col = F,
+  valid.col = F,
+  labels.col = F)
+}
+```
+
 # EDGI demographics
@@
 
+```{r edgi dem summary}
+if(EDGI == TRUE) {
+summarytools::dfSummary(
+  dem.raw.id,
+  graph.col = F,
+  valid.col = F,
+  labels.col = F)
+}
+```
+
 # NBR demographics
@@
 
-```{r nbr demo summary}
+```{r nbr dem summary}
 if(NBR == TRUE) {
@@
 
-```{r glad dem head}
-head(dem.raw.id)
-```
-
-```{r glad dem summary}
+```{r dem summary}
+if(GLAD == TRUE | EDGI == TRUE) {
 summarytools::dfSummary(

### 2020-08-13 PANCHANGE_data_preprocessing2020-07-15.Rmd
Edited the education/employment section to run similarly for each cohort. Added chunks for EDGI and NBR.

@@
   mutate(
-    highest_education_numeric =
+    highest_education_prepan_numeric =
       case_when(
@@
   mutate(
-    highest_education =
+    highest_education_prepan =
       recode_factor(
@@
 dem.raw.id %>%
-  freq(highest_education)
+  freq(highest_education_prepan)
 }
@@
 dem.raw.id %>%
-  select(highest_education,
+  select(highest_education_prepan,
         demographics.college_or_university_degree_numeric,
@@
 
-## Read in data
+## GLAD
+### Read in data
 ```{r glad employment cols}
@@
 
-# Select variables
+### Select variables
 ```{r glad employment cleaning}
@@
 
-```{r nbr employment cols}
-if(NBR == TRUE){
-nbr.employment.raw <- readRDS(file = paste0(data.raw_path, "/nbr/employment_coping_nbr.rds"))
-dim(nbr.employment.raw)
-colnames(nbr.employment.raw)
-}
-```
-
-# Select variables
-```{r nbr employment cleaning}
-if(NBR == TRUE){
+```{r glad copy employment}
+if(GLAD == TRUE){
+  employment.raw.id <- glad.employment.raw.id
+}
+```
+
+## EDGI
+### Read in data
+```{r edgi employment cols}
+if(EDGI == TRUE){
+edgi.employment.raw <- readRDS(file = paste0(data.raw_path, "/edgi/employment_coping_edgi.rds"))
+dim(edgi.employment.raw)
+colnames(edgi.employment.raw)
+}
+```
+
+### Select variables
+```{r edgi employment cleaning}
+if(EDGI == TRUE){
 exclude_cols_employment <- c("ID",
@@
 
-nbr.employment.raw.id <- nbr.employment.raw %>%
+edgi.employment.raw.id <- edgi.employment.raw %>%
   drop_na(externalDataReference) %>% # Drop NAs
@@
 # Inspect dimensions
+dim(edgi.employment.raw.id)
+# Inspect colnames
+colnames(edgi.employment.raw.id)
+#Differences
+dim(edgi.employment.raw)[1]-dim(edgi.employment.raw.id)[1]
+}
+```
+
+```{r edgi copy employment}
+if(EDGI == TRUE){
+  employment.raw.id <- edgi.employment.raw.id
+}
+```
+
+## NBR
+### Read in data
+```{r nbr employment cols}
+if(NBR == TRUE){
+nbr.employment.raw <- readRDS(file = paste0(data.raw_path, "/nbr/employment_coping_nbr.rds"))
+dim(nbr.employment.raw)
+colnames(nbr.employment.raw)
+}
+```
+
+### Select variables
+```{r nbr employment cleaning}
+if(NBR == TRUE){
+exclude_cols_employment <- c("ID",
+                  "Sample")
+
+nbr.employment.raw.id <- nbr.employment.raw %>%
+  drop_na(subjectid) %>% # Drop NAs
+  distinct(subjectid, .keep_all = TRUE) %>% # Remove duplicates based on ID
+  separate(subjectid, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
+  mutate(
+    ID = as.numeric(ID)
+    ) %>%
+  select(
+         Sample, # Sample
+         ID, # ID
+         employment.phd, # level of education - univeristy
+         employment.masters_degree_or_equivalent, # level of education - univeristy
+         employment.postgraduate_degree_or_equivalent, # level of education - univeristy
+         employment.bachelors_degree_or_equivalent, # level of education - univeristy
+         employment.a_levelsas_levels_or_equivalent, # level of education - alevel
+         employment.o_levelsgcses_or_equivalent, # level of education - gcse
+         employment.cses_or_equivalent, # level of education - cse
+         employment.nvq_or_hnd_or_hnc_or_equivalent, # level of education - nvq
+         employment.government_work_key_workers # key worker status
+         ) %>%
+  add_numeric(., exclude = exclude_cols_employment) %>%
+  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
+  mutate_if(is.numeric, ~na_if(., -99)) %>%
+  mutate_if(is.numeric, ~na_if(., -77)) %>%
+  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
+  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
+
+# Inspect dimensions
 dim(nbr.employment.raw.id)
@@
 
-# Highest education
+```{r nbr copy employment}
+if(NBR == TRUE){
+  employment.raw.id <- nbr.employment.raw.id
+}
+```
+
+## Highest education (baseline)
 Proceed along qualifications fields. If field is not blank, take that as highest qual. If field is blank, check next field. If all fields are blank, NA
 Assumes University degree > A level > NVQ > GCSE/O Level/CSE
-```{r Highest education}
-if(GLAD == TRUE | EDGI == TRUE) {
+```{r Highest education baseline}
+if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE) {
 #create numeric version of the highest education variable
-glad.employment.raw.id <- glad.employment.raw.id %>%
+employment.raw.id <- employment.raw.id %>%
   mutate(
@@
 ```{r Highest education check}
-if(GLAD == TRUE | EDGI == TRUE) {
-glad.employment.raw.id %>%
+if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE) {
+employment.raw.id %>%
   select(highest_education,

### 2020-08-13 PANCHANGE_data_preprocessing2020-07-15.Rmd
Amended key worker status chunk to work for all cohorts.

@@
 
-# Key worker status
+## Key worker status
 ```{r Key worker}

### 2020-08-13 PANCHANGE_data_preprocessing2020-07-15.Rmd
Added chunk for RAMP into highest education.

@@
 
+## RAMP
+### Read in data
+```{r ramp employment cols}
+if(RAMP == TRUE){
+ramp.employment.raw <- readRDS(file = paste0(data.raw_path, "/ramp/employment_coping_ramp.rds"))
+dim(ramp.employment.raw)
+colnames(ramp.employment.raw)
+}
+```
+
+### Select variables
+```{r ramp employment cleaning}
+if(RAMP == TRUE){
+exclude_cols_employment <- c("ID",
+                  "Sample")
+
+ramp.employment.raw.id <- ramp.employment.raw %>%
+  drop_na(subjectid) %>% # Drop NAs
+  distinct(subjectid, .keep_all = TRUE) %>% # Remove duplicates based on ID
+  separate(subjectid, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
+  mutate(
+    ID = as.numeric(ID)
+    ) %>%
+  select(
+         Sample, # Sample
+         ID, # ID
+         employment.phd, # level of education - univeristy
+         employment.masters_degree_or_equivalent, # level of education - univeristy
+         employment.postgraduate_degree_or_equivalent, # level of education - univeristy
+         employment.bachelors_degree_or_equivalent, # level of education - univeristy
+         employment.a_levelsas_levels_or_equivalent, # level of education - alevel
+         employment.o_levelsgcses_or_equivalent, # level of education - gcse
+         employment.cses_or_equivalent, # level of education - cse
+         employment.nvq_or_hnd_or_hnc_or_equivalent, # level of education - nvq
+         employment.government_work_key_workers # key worker status
+         ) %>%
+  add_numeric(., exclude = exclude_cols_employment) %>%
+  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
+  mutate_if(is.numeric, ~na_if(., -99)) %>%
+  mutate_if(is.numeric, ~na_if(., -77)) %>%
+  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
+  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
+
+# Inspect dimensions
+dim(ramp.employment.raw.id)
+# Inspect colnames
+colnames(ramp.employment.raw.id)
+#Differences
+dim(ramp.employment.raw)[1]-dim(ramp.employment.raw.id)[1]
+}
+```
+
+```{r ramp copy employment}
+if(RAMP == TRUE){
+  employment.raw.id <- ramp.employment.raw.id
+}
+```
+
 ## Highest education (baseline)
@@
 ```{r Highest education baseline}
-if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE) {
+if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE | RAMP = TRUE) {
 #create numeric version of the highest education variable
@@
 ```{r Highest education check}
-if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE) {
+if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE | RAMP = TRUE) {
 employment.raw.id %>%

### 2020-08-13 PANCHANGE_data_preprocessing2020-07-15.Rmd
First stage of adapting MHD section for NBR. Reading in data and cleaning depressive disorders chunks completed.

@@
 
+## EDGI
+```{r edgi mhd cols}
+if(EDGI == TRUE) {
+edgi.mhd.raw <- readRDS(file = paste0(data.raw_path,"/edgi/mhd_edgi.rds"))
+dim(edgi.mhd.raw)
+colnames(edgi.mhd.raw)
+}
+```
+
+```{r edgi mhd cleaning}
+if(EDGI == TRUE) {
+edgi.mhd.raw.id <- edgi.mhd.raw %>%
+  drop_na(externalDataReference) %>% # Drop NAs
+  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
+  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
+  mutate(ID = as.numeric(ID),
+         startDate.prepandemic = startDate) %>% # Rename startDate
+  select(
+    Sample, # Sample
+    ID, # ID
+    starts_with("mhd.")
+  ) %>%
+  add_numeric(., exclude = exclude_cols) %>%
+  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
+  mutate_if(is.numeric, ~na_if(., -99)) %>%
+  mutate_if(is.numeric, ~na_if(., -77)) %>%
+  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
+  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
+
+# Inspect dimensions
+dim(edgi.mhd.raw.id)
+# Inspect colnames
+colnames(edgi.mhd.raw.id)
+#Differences
+dim(edgi.mhd.raw)[1]-dim(edgi.mhd.raw.id)[1]
+}
+```
+
+```{r edgi mhd copy}
+if(EDGI == TRUE) {
+  mhd.raw.id <- edgi.mhd.raw.id
+}
+```
+
+## NBR
+```{r nbr mhd cols}
+if(NBR == TRUE) {
+nbr.mhd.raw <- readRDS(file = paste0(data.raw_path,"/nbr/mhd_nbr.rds"))
+dim(nbr.mhd.raw)
+colnames(nbr.mhd.raw)
+}
+```
+
+```{r nbr mhd cleaning}
+if(NBR == TRUE) {
+exclude_cols <- c("Sample",
+                  "ID")
+
+nbr.mhd.raw.id <- nbr.mhd.raw %>%
+  drop_na(subjectid) %>% # Drop NAs
+  distinct(subjectid, .keep_all = TRUE) %>% # Remove duplicates based on ID
+  separate(subjectid, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
+  mutate(ID = as.numeric(ID),
+         startDate.prepandemic = startDate) %>% # Rename startDate
+  select(
+    Sample, # Sample
+    ID, # ID
+    starts_with("mhd.")
+  ) %>%
+  add_numeric(., exclude = exclude_cols) %>%
+  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
+  mutate_if(is.numeric, ~na_if(., -99)) %>%
+  mutate_if(is.numeric, ~na_if(., -77)) %>%
+  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
+  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
+
+# Inspect dimensions
+dim(nbr.mhd.raw.id)
+# Inspect colnames
+colnames(nbr.mhd.raw.id)
+#Differences
+dim(nbr.mhd.raw)[1]-dim(nbr.mhd.raw.id)[1]
+}
+```
+
+```{r nbr mhd copy}
+if(NBR == TRUE) {
+  mhd.raw.id <- nbr.mhd.raw.id
+}
+```
+
 # Grouping mental health disorders
@@
 
-```{r glad mhd depressive_disorders}
+```{r mhd depressive_disorders}
+## CHECK THAT THIS CHUNK WORKS FOR EDGI AS WELL (confirmed that it works for NBR)
+if(GLAD = TRUE | EDGI = TRUE | NBR = TRUE)
 mhd.raw.id <- mhd.raw.id %>%
@@
 ```{r glad mhd anxiety_disorders}
+if(GLAD = TRUE) {
 mhd.raw.id <- mhd.raw.id %>%
@@
        cumul = F)
+}
+```
+
+```{r nbr mhd anxiety_disorders}
+if(NBR = TRUE) {
+mhd.raw.id <- mhd.raw.id %>%
+  mutate(
+    anxiety_disorders_numeric =
+      case_when(
+        mhd.anxiety_nerves_or_generalised_anxiety_disorder_numeric == "1" ~ 1,
+        mhd.social_anxiety_or_social_phobia_numeric == "1" ~ 1,
+        mhd.specific_phobia_e.g._phobia_of_flying_numeric == "1" ~ 1,
+        mhd.agoraphobia_numeric == "1" ~ 1,
+        mhd.panic_disorder_numeric == "1" ~ 1,
+        mhd.panic_attacks_numeric == "1" ~ 1,
+        (mhd.anxiety_nerves_or_generalised_anxiety_disorder_numeric == "0" &
+        mhd.social_anxiety_or_social_phobia_numeric == "0" &
+        mhd.specific_phobia_e.g._phobia_of_flying_numeric == "0" &
+        mhd.agoraphobia_numeric == "0" &
+        mhd.panic_disorder_numeric == "0" &
+        mhd.panic_attacks_numeric == "0") ~ 0
+      )
+  )
+
+mhd.raw.id <- mhd.raw.id %>%
+  mutate(
+    anxiety_disorders =
+      recode_factor(anxiety_disorders_numeric,
+                    "0" = "No anxiety disorder",
+                    "1" = "Anxiety disorder",
+                    missing = NA_character_
+                    )
+  )
+
+mhd.raw.id %>%
+  freq(anxiety_disorders,
+       cumul = F)
+}
 ```

### 2020-08-13 PANCHANGE_data_preprocessing2020-07-15.Rmd
Finished adapting MHD depression, anxiety, and eating disorder sections for NBR.

@@
 
+# Rename columns that differ from GLAD
+nbr.mhd.raw.id <- nbr.mhd.raw.id %>% 
+  mutate(
+    mhd.specific_phobia_e.g._phobia_of_flying = mhd.specific_phobia_e.g._fear_of_flying,
+    mhd.specific_phobia_e.g._phobia_of_flying_numeric = mhd.specific_phobia_e.g._fear_of_flying_numeric,
+    mhd.psychological_overeating_or_bingeeating = mhd.bingeeating_disorder,
+    mhd.psychological_overeating_or_bingeeating_numeric = mhd.bingeeating_disorder_numeric
+  )
+
 # Inspect dimensions
@@
 ```{r mhd depressive_disorders}
-## CHECK THAT THIS CHUNK WORKS FOR EDGI AS WELL (confirmed that it works for NBR)
-if(GLAD = TRUE | EDGI = TRUE | NBR = TRUE)
+if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE | RAMP == TRUE)
 mhd.raw.id <- mhd.raw.id %>%
@@
 ```{r Check depressive_disorders}
+if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE | RAMP == TRUE) {
 mhd.raw.id %>%
@@
 Anxiety disorders group
-```{r glad mhd anxiety_disorders}
-if(GLAD = TRUE) {
+```{r mhd anxiety_disorders}
+if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE | RAMP == TRUE) {
 mhd.raw.id <- mhd.raw.id %>%
@@
 
-```{r nbr mhd anxiety_disorders}
-if(NBR = TRUE) {
-mhd.raw.id <- mhd.raw.id %>%
-  mutate(
-    anxiety_disorders_numeric =
-      case_when(
-        mhd.anxiety_nerves_or_generalised_anxiety_disorder_numeric == "1" ~ 1,
-        mhd.social_anxiety_or_social_phobia_numeric == "1" ~ 1,
-        mhd.specific_phobia_e.g._phobia_of_flying_numeric == "1" ~ 1,
-        mhd.agoraphobia_numeric == "1" ~ 1,
-        mhd.panic_disorder_numeric == "1" ~ 1,
-        mhd.panic_attacks_numeric == "1" ~ 1,
-        (mhd.anxiety_nerves_or_generalised_anxiety_disorder_numeric == "0" &
-        mhd.social_anxiety_or_social_phobia_numeric == "0" &
-        mhd.specific_phobia_e.g._phobia_of_flying_numeric == "0" &
-        mhd.agoraphobia_numeric == "0" &
-        mhd.panic_disorder_numeric == "0" &
-        mhd.panic_attacks_numeric == "0") ~ 0
-      )
-  )
-
-mhd.raw.id <- mhd.raw.id %>%
-  mutate(
-    anxiety_disorders =
-      recode_factor(anxiety_disorders_numeric,
-                    "0" = "No anxiety disorder",
-                    "1" = "Anxiety disorder",
-                    missing = NA_character_
-                    )
-  )
-
-mhd.raw.id %>%
-  freq(anxiety_disorders,
-       cumul = F)
-}
-```
-
 ```{r Check anxiety_disorders}
+if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE | RAMP == TRUE) {
 mhd.raw.id %>%
@@
 Agoraphonia and panic disorder group
-```{r glad mhd agoraphobia_panic_disorder}
+```{r mhd agoraphobia_panic_disorder}
+if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE | RAMP == TRUE) {
 mhd.raw.id <- mhd.raw.id %>%
@@
   freq(agoraphobia_panic_disorder)
+}
 ```
@@
 ```{r Check agoraphobia_panic_disorder}
+if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE | RAMP == TRUE) {
 mhd.raw.id %>%
@@
 Depression and anxiety comorbidity
-```{r glad mhd depression_anxiety}
+```{r mhd depression_anxiety}
+if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE | RAMP == TRUE) {
 mhd.raw.id <- mhd.raw.id %>%
@@
 Eating disorders group
-```{r glad mhd eating_disorders}
+```{r mhd eating_disorders}
+if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE | RAMP == TRUE) {
 mhd.raw.id <- mhd.raw.id %>%
@@
 Caveat: Anorexia nervosa can have binge eating as well. Therefore, this would need an additional variable from the ED100K
-```{r glad mhd restricting_vs_binge_eating_eating_disorders}
+```{r mhd restricting_vs_binge_eating_eating_disorders}
+if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE | RAMP == TRUE) {
 mhd.raw.id <- mhd.raw.id %>%
@@
 ```{r Check eating_disorders}
+if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE | RAMP == TRUE) {
 mhd.raw.id %>%

### 2020-08-13 PANCHANGE_data_preprocessing2020-07-15.Rmd
Amended psychosis sections. Removed dplyr from packages because it's part of tidyverse.

@@
 #install.packages("psych")
-#install.packages("dplyr")
 #install.packages("eeptools")
@@
 library(psych)
-library(dplyr)
 library(tidyverse)
-library(eeptools)
+library(eeptools) #Needed to calculate age from birthdate
 ```
@@
 ```{r nbr cohort recode ethnicity}
+if(NBR == TRUE) {
 #Recode details ethnicity info
@@
                                              "99" = NULL)
-
+}
 ```
@@
 if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE ) {
-
 # Create categorical age groups per 10 years
@@
 # Rename columns that differ from GLAD
-nbr.mhd.raw.id <- nbr.mhd.raw.id %>% 
+nbr.mhd.raw.id_renamed <- nbr.mhd.raw.id %>% 
   mutate(
@@
     mhd.psychological_overeating_or_bingeeating = mhd.bingeeating_disorder,
-    mhd.psychological_overeating_or_bingeeating_numeric = mhd.bingeeating_disorder_numeric
+    mhd.psychological_overeating_or_bingeeating_numeric = mhd.bingeeating_disorder_numeric,
+    mhd.type_psychosis_psychotic_illness = mhd.psychosis_type_psychotic_illness,
+    mhd.type_psychosis_psychotic_illness_numeric = mhd.psychosis_type_psychotic_illness_numeric
+    ) %>% 
+  add_column(
+    mhd.schizoaffective_disorder = NA, #NBR dooesn't ask about schizoaffective
+    mhd.schizoaffective_disorder_numeric = NA
   )
@@
 # Inspect dimensions
-dim(nbr.mhd.raw.id)
+dim(nbr.mhd.raw.id_renamed)
 # Inspect colnames
-colnames(nbr.mhd.raw.id)
+colnames(nbr.mhd.raw.id_renamed)
 #Differences
-dim(nbr.mhd.raw)[1]-dim(nbr.mhd.raw.id)[1]
+dim(nbr.mhd.raw)[1]-dim(nbr.mhd.raw.id_renamed)[1]
 }
@@
 if(NBR == TRUE) {
-  mhd.raw.id <- nbr.mhd.raw.id
+  mhd.raw.id <- nbr.mhd.raw.id_renamed
 }
@@
 Obsessive compulsive disorders
-```{r glad mhd obsessive_compulsive_disorders}
+```{r mhd obsessive_compulsive_disorders}
+if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE | RAMP == TRUE) {
 mhd.raw.id <- mhd.raw.id %>%
@@
   freq(obsessive_compulsive_disorders)
+}
 ```
@@
 ```{r Check obsessive_compulsive_disorders}
+if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE | RAMP == TRUE) {
 mhd.raw.id %>%
@@
 [65] "mhd.type_psychosis_psychotic_illness_numeric" 
-```{r glad mhd psychotic_disorders}
+```{r mhd psychotic_disorders}
+if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE | RAMP == TRUE) {
 mhd.raw.id <- mhd.raw.id %>%
@@
         (mhd.schizophrenia_numeric == "0" &
-        mhd.schizoaffective_disorder_numeric == "0" &
+        (mhd.schizoaffective_disorder_numeric == "0" | is.na(mhd.schizoaffective_disorder_numeric == "0") &
         mhd.type_psychosis_psychotic_illness_numeric == "0") ~ 0
@@
   freq(psychotic_disorders)
+}
 ```
@@
 ++KT: Only 63 with comorbid self-report bipolar disorder and schizophrenia. More likely to have shared symptoms, less likely to have confirmed diagnoses of both. Could be too severe to be in GLAD?
-```{r glad mhd bipolar_and_schizophrenia_numeric}
+```{r mhd bipolar_and_schizophrenia_numeric}
+if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE | RAMP == TRUE) {
 mhd.raw.id <- mhd.raw.id %>%
@@
 ```{r Check psychotic_disorders}
+if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE | RAMP == TRUE) {
 mhd.raw.id %>%

### 2020-08-13 PANCHANGE_data_preprocessing2020-07-15.Rmd
NBR MHD finished. Adding eating disorders cleaning section to account for routing logic. Verified mhd section all ran properly.

@@
 library(summarytools)
-library(psych)
+#library(psych)
 library(tidyverse)
@@
   separate(subjectid, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
+  #mutate(
+  #  ID = as.numeric(ID) ##NBR IDs have a letter at the end so can't be coerced to numeric
+  #  ) %>% 
+  select(
+         Sample, # Sample
+         ID, # ID
+         employment.phd, # level of education - univeristy
+         employment.masters_degree_or_equivalent, # level of education - univeristy
+         employment.postgraduate_degree_or_equivalent, # level of education - univeristy
+         employment.bachelors_degree_or_equivalent, # level of education - univeristy
+         employment.a_levelsas_levels_or_equivalent, # level of education - alevel
+         employment.o_levelsgcses_or_equivalent, # level of education - gcse
+         employment.cses_or_equivalent, # level of education - cse
+         employment.nvq_or_hnd_or_hnc_or_equivalent, # level of education - nvq
+         employment.government_work_key_workers # key worker status
+         ) %>%
+  add_numeric(., exclude = exclude_cols_employment) %>%
+  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
+  mutate_if(is.numeric, ~na_if(., -99)) %>%
+  mutate_if(is.numeric, ~na_if(., -77)) %>%
+  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
+  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
+
+# Inspect dimensions
+dim(nbr.employment.raw.id)
+# Inspect colnames
+colnames(nbr.employment.raw.id)
+#Differences
+dim(nbr.employment.raw)[1]-dim(nbr.employment.raw.id)[1]
+head(nbr.employment.raw.id
+     )
+}
+```
+
+```{r nbr copy employment}
+if(NBR == TRUE){
+  employment.raw.id <- nbr.employment.raw.id
+}
+```
+
+## RAMP
+### Read in data
+```{r ramp employment cols}
+if(RAMP == TRUE){
+ramp.employment.raw <- readRDS(file = paste0(data.raw_path, "/ramp/employment_coping_ramp.rds"))
+dim(ramp.employment.raw)
+colnames(ramp.employment.raw)
+}
+```
+
+### Select variables
+```{r ramp employment cleaning}
+if(RAMP == TRUE){
+exclude_cols_employment <- c("ID",
+                  "Sample")
+
+ramp.employment.raw.id <- ramp.employment.raw %>%
+  drop_na(subjectid) %>% # Drop NAs
+  distinct(subjectid, .keep_all = TRUE) %>% # Remove duplicates based on ID
+  separate(subjectid, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
   mutate(
@@
 # Inspect dimensions
-dim(nbr.employment.raw.id)
-# Inspect colnames
-colnames(nbr.employment.raw.id)
-#Differences
-dim(nbr.employment.raw)[1]-dim(nbr.employment.raw.id)[1]
-}
-```
-
-```{r nbr copy employment}
-if(NBR == TRUE){
-  employment.raw.id <- nbr.employment.raw.id
-}
-```
-
-## RAMP
-### Read in data
-```{r ramp employment cols}
-if(RAMP == TRUE){
-ramp.employment.raw <- readRDS(file = paste0(data.raw_path, "/ramp/employment_coping_ramp.rds"))
-dim(ramp.employment.raw)
-colnames(ramp.employment.raw)
-}
-```
-
-### Select variables
-```{r ramp employment cleaning}
-if(RAMP == TRUE){
-exclude_cols_employment <- c("ID",
-                  "Sample")
-
-ramp.employment.raw.id <- ramp.employment.raw %>%
-  drop_na(subjectid) %>% # Drop NAs
-  distinct(subjectid, .keep_all = TRUE) %>% # Remove duplicates based on ID
-  separate(subjectid, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
-  mutate(
-    ID = as.numeric(ID)
-    ) %>%
-  select(
-         Sample, # Sample
-         ID, # ID
-         employment.phd, # level of education - univeristy
-         employment.masters_degree_or_equivalent, # level of education - univeristy
-         employment.postgraduate_degree_or_equivalent, # level of education - univeristy
-         employment.bachelors_degree_or_equivalent, # level of education - univeristy
-         employment.a_levelsas_levels_or_equivalent, # level of education - alevel
-         employment.o_levelsgcses_or_equivalent, # level of education - gcse
-         employment.cses_or_equivalent, # level of education - cse
-         employment.nvq_or_hnd_or_hnc_or_equivalent, # level of education - nvq
-         employment.government_work_key_workers # key worker status
-         ) %>%
-  add_numeric(., exclude = exclude_cols_employment) %>%
-  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
-  mutate_if(is.numeric, ~na_if(., -99)) %>%
-  mutate_if(is.numeric, ~na_if(., -77)) %>%
-  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
-  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
-
-# Inspect dimensions
 dim(ramp.employment.raw.id)
@@
 ```{r Highest education baseline}
-if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE | RAMP = TRUE) {
+if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE | RAMP == TRUE) {
 #create numeric version of the highest education variable
@@
 ```{r Highest education check}
-if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE | RAMP = TRUE) {
+if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE | RAMP == TRUE) {
 employment.raw.id %>%
@@
 
-# glad gad
-
-```{r glad gad cols}
+# glad gad (prepan)
+
+```{r glad gad prepan cols}
 if(GLAD == TRUE){
@@
 
-```{r glad gad cleaning}
+```{r glad gad prepan cleaning}
 if(GLAD ==TRUE){
@@
 
-```{r glad copy gad}
+```{r glad copy prepan gad}
 if(GLAD == TRUE){
@@
 
-```{r edgi gad cols}
+```{r edgi gad prepan cols}
 if(EDGI == TRUE){
@@
 
-```{r edgi gad cleaning}
+```{r edgi gad prepan cleaning}
 if(EDGI == TRUE){
@@
 
-```{r nbr copy gad}
+```{r edgi copy prepan gad}
 if(EDGI == TRUE){
@@
   separate(subjectid, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
-  mutate(ID = as.numeric(ID),
+  mutate(#ID = as.numeric(ID), ## NBR IDs end with letters so can't be numeric
          startDate.prepandemic = startDate) %>% # Rename startDate
@@
     mhd.type_psychosis_psychotic_illness = mhd.psychosis_type_psychotic_illness,
-    mhd.type_psychosis_psychotic_illness_numeric = mhd.psychosis_type_psychotic_illness_numeric
+    mhd.type_psychosis_psychotic_illness_numeric = mhd.psychosis_type_psychotic_illness_numeric,
+    mhd.autism_aspergers_or_autistic_spectrum_disorder = mhd.autism_spectrum_disorder_asd,
+    mhd.autism_aspergers_or_autistic_spectrum_disorder_numeric = mhd.autism_spectrum_disorder_asd_numeric
     ) %>% 
   add_column(
-    mhd.schizoaffective_disorder = NA, #NBR dooesn't ask about schizoaffective
+    mhd.schizoaffective_disorder = NA, #NBR doesn't ask about schizoaffective
     mhd.schizoaffective_disorder_numeric = NA
@@
                     "2" = "Only depressive disorder",
-                    "2" = "Only anxiety disorder",
+                    "3" = "Only anxiety disorder",
                     missing = NA_character_
@@
 Eating disorders group
+
+```{r nbr cleaning eating disorders}
+if(NBR == TRUE) {
+#Recode as 0 if ppt respnds no to screening question (mhd.suspected_eating_disorder_diagnosed_numeric)
+mhd.raw.id <- mhd.raw.id %>%
+  mutate(
+    mhd.anorexia_nervosa_numeric =
+      case_when(mhd.suspected_eating_disorder_diagnosed_numeric == "0" ~ 0,
+                mhd.anorexia_nervosa_numeric == "0" ~ 0,
+                mhd.anorexia_nervosa_numeric == "1" ~ 1),
+    mhd.atypical_anorexia_nervosa_numeric =
+      case_when(mhd.suspected_eating_disorder_diagnosed_numeric == "0" ~ 0,
+                mhd.atypical_anorexia_nervosa_numeric == "0" ~ 0,
+                mhd.atypical_anorexia_nervosa_numeric == "1" ~ 1),
+    mhd.bulimia_nervosa_numeric =
+      case_when(mhd.suspected_eating_disorder_diagnosed_numeric == "0" ~ 0,
+                mhd.bulimia_nervosa_numeric == "0" ~ 0,
+                mhd.bulimia_nervosa_numeric == "1" ~ 1),
+    mhd.psychological_overeating_or_bingeeating_numeric =
+      case_when(mhd.suspected_eating_disorder_diagnosed_numeric == "0" ~ 0,
+                mhd.psychological_overeating_or_bingeeating_numeric == "0" ~ 0,
+                mhd.psychological_overeating_or_bingeeating_numeric == "1" ~ 1)
+    )
+}
+
+```
+
 ```{r mhd eating_disorders}
@@
         (mhd.schizophrenia_numeric == "0" &
-        (mhd.schizoaffective_disorder_numeric == "0" | is.na(mhd.schizoaffective_disorder_numeric == "0") &
-        mhd.type_psychosis_psychotic_illness_numeric == "0") ~ 0
+        (mhd.schizoaffective_disorder_numeric == "0" | is.na(mhd.schizoaffective_disorder_numeric == "0") & #NA included because some cohorts don't have schizoaffective disorder
+        mhd.type_psychosis_psychotic_illness_numeric == "0") ~ 0)
         )
@@
         psychotic_disorders_numeric == 1 &
+          mhd.mania_hypomania_bipolar_or_manicdepression_numeric == 1 ~ 1,
+        psychotic_disorders_numeric == 1 &
           mhd.mania_hypomania_bipolar_or_manicdepression_numeric == 0 ~ 2,
         psychotic_disorders_numeric == 0 &
-          mhd.mania_hypomania_bipolar_or_manicdepression_numeric == 1 ~ 3,
-                psychotic_disorders_numeric == 1 &
-          mhd.mania_hypomania_bipolar_or_manicdepression_numeric == 1 ~ 1
+          mhd.mania_hypomania_bipolar_or_manicdepression_numeric == 1 ~ 3
       )
@@
 3. Schizotypal                      14 ( 0.5%)
-```{r glad mhd personality_cluster_a}
+```{r mhd personality_cluster_a}
 mhd.raw.id <- mhd.raw.id %>%
@@
 
-```{r glad mhd personality_cluster_b}
+```{r mhd personality_cluster_b}
 mhd.raw.id <- mhd.raw.id %>%
@@
 These individuals have no self report diagnosis of any kind that we measure. 
-Controls = 784
-```{r glad mhd control}
+```{r mhd control}
 mhd.raw.id <- mhd.raw.id %>%
@@
 
-```{r glad mhd summary}
+```{r mhd summary}
 summarytools::dfSummary(
@@
 ++KT: do we want to keep individual diagnoses here as well?? 
-```{r glad mhd categories}
+```{r mhd categories}
 mhd.raw.categories <- mhd.raw.id %>%
@@
 
-# eclude cols
+# exclude cols
 
@@
 
-# glad pcl
+# glad prepandemic pcl
 

### 2020-08-13 PANCHANGE_data_preprocessing2020-07-15.Rmd
Tidied up script and chunk naming.

@@
   freq(key_worker)
-}
-```
-
-# glad gad (prepan)
-
-```{r glad gad prepan cols}
-if(GLAD == TRUE){
-glad.gad.raw <- readRDS(file = paste0(data.raw_path, "/glad/gad_glad.rds"))
-dim(glad.gad.raw)
-colnames(glad.gad.raw)
-}
-```
-
-```{r glad gad prepan cleaning}
-if(GLAD ==TRUE){
-exclude_cols <- c("Sample",
-                  "ID")
-glad.gad.raw.id <- glad.gad.raw %>%
-  drop_na(externalDataReference) %>% # Drop NAs
-  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
-  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
-  mutate(ID = as.numeric(ID),
-         startDate.prepandemic = startDate) %>% # Rename startDate
-  select(
-    Sample, # Sample
-    ID, # ID
-    gad.feeling_nervous_anxious_or_on_edge_prepan = gad.feeling_nervous_anxious_or_on_edge,
-    gad.control_worrying_stop_prepan = gad.control_worrying_stop,
-    gad.worrying_too_much_about_different_things_prepan = gad.worrying_too_much_about_different_things,
-    gad.trouble_relaxing_prepan = gad.trouble_relaxing,
-    gad.sit_restless_hard_prepan = gad.sit_restless_hard,
-    gad.becoming_easily_annoyed_or_irritable_prepan = gad.becoming_easily_annoyed_or_irritable,
-    gad.awful_feeling_afraid_happen_prepan = gad.awful_feeling_afraid_happen
-  ) %>%
-  add_numeric(., exclude = exclude_cols) %>%
-  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
-  mutate_if(is.numeric, ~na_if(., -99)) %>%
-  mutate_if(is.numeric, ~na_if(., -77)) %>%
-  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
-  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
-
-# Inspect dimensions
-dim(glad.gad.raw.id)
-# Inspect colnames
-colnames(glad.gad.raw.id)
-#Differences
-dim(glad.gad.raw)[1]-dim(glad.gad.raw.id)[1]
-}
-```
-
-```{r glad copy prepan gad}
-if(GLAD == TRUE){
-prepan.gad.raw.id <- glad.gad.raw.id
-}
-```
-
-```{r edgi gad prepan cols}
-if(EDGI == TRUE){
-  edgi.gad.raw <- readRDS(file = paste0(data.raw_path, "/edgi/gad_edgi.rds"))
-  dim(edgi.gad.raw)
-  colnames(edgi.gad.raw)
-}
-```
-
-```{r edgi gad prepan cleaning}
-if(EDGI == TRUE){
-exclude_cols <- c("Sample",
-                  "ID")
-
-edgi.gad.raw.id <- edgi.gad.raw %>%
-  drop_na(externalDataReference) %>% # Drop NAs
-  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
-  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
-  mutate(ID = as.numeric(ID),
-         startDate.edgi = startDate) %>% # Rename startDate
-  select(
-    Sample, # Sample
-    ID, # ID
-    gad.feeling_nervous_anxious_or_on_edge_prepan = gad.feeling_nervous_anxious_or_on_edge,
-    gad.control_worrying_stop_prepan = gad.control_worrying_stop,
-    gad.worrying_too_much_about_different_things_prepan = gad.worrying_too_much_about_different_things,
-    gad.trouble_relaxing_prepan = gad.trouble_relaxing,
-    gad.sit_restless_hard_prepan = gad.sit_restless_hard,
-    gad.becoming_easily_annoyed_or_irritable_prepan = gad.becoming_easily_annoyed_or_irritable,
-    gad.awful_feeling_afraid_happen_prepan = gad.awful_feeling_afraid_happen
-  ) %>%
-  add_numeric(., exclude = exclude_cols) %>%
-  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
-  mutate_if(is.numeric, ~na_if(., -99)) %>%
-  mutate_if(is.numeric, ~na_if(., -77)) %>%
-  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
-  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
-
-# Inspect dimensions
-dim(edgi.gad.raw.id)
-# Inspect colnames
-colnames(edgi.gad.raw.id)
-#Differences
-dim(edgi.gad.raw)[1]-dim(edgi.gad.raw.id)[1]
-}
-```
-
-```{r edgi copy prepan gad}
-if(EDGI == TRUE){
-  prepan.gad.raw.id <- edgi.gad.raw.id
-}
-```
-
-Calculate sum score for GAD-7
-Max should be 21.
-
-*Note that scores with missingness will be changed to NA later in the script
-```{r gad sum score prepan raw}
-if(GLAD ==TRUE | EDGI == TRUE){
-# Create vector with scoring key: If the item is reversed coded use -1. 
-# There needs to be the correct number of values for each item in the questionnaire. 
-gad.items_key_prepan <- c(1,1,1,1,1,1,1)
-
-# Create vector with items that are included in total score
-gad.items_prepan <- c(
-  "gad.feeling_nervous_anxious_or_on_edge_prepan_numeric",
-  "gad.control_worrying_stop_prepan_numeric",
-  "gad.worrying_too_much_about_different_things_prepan_numeric",
-  "gad.trouble_relaxing_prepan_numeric",
-  "gad.sit_restless_hard_prepan_numeric",
-  "gad.becoming_easily_annoyed_or_irritable_prepan_numeric",
-  "gad.awful_feeling_afraid_happen_prepan_numeric"
-  )
-
-# Calulate total score
-gad.scored_items_prepan <- scoreItems(keys = gad.items_key_prepan,
-                                        items = prepan.gad.raw.id[gad.items_prepan],
-                                        totals = TRUE, 
-                                        missing = TRUE, 
-                                        impute = 'none', 
-                                        min = 0, 
-                                        max = 3)
-# Add in column to tibble
-prepan.gad.raw.id$gad.sum_score_prepan_raw <- gad.scored_items_prepan$scores
-
-# Look at values
-prepan.gad.raw.id %>%
-  descr(gad.sum_score_prepan_raw,
-        stats = "common"
-        )
-}
-```
-
-missingness (NAs per person)
-
-prepandemic
-```{r gad prepan missingness}
-if(GLAD ==TRUE | EDGI == TRUE){
-prepan.gad.raw.id <- prepan.gad.raw.id %>%
-  mutate(
-    na_per_person_gad_prepan =         # variable for NA per person
-      rowSums(                       
-        is.na(.[gad.items_prepan])
-      )
-  )
-
-prepan.gad.raw.id %>%
-  freq(na_per_person_gad_prepan,
-       cumul = F)
-}
-```
-
-```{r gad prepan sum score if missigng items set to NA}
-if(GLAD ==TRUE | EDGI == TRUE){
-prepan.gad.raw.id <- prepan.gad.raw.id %>%
-  mutate(
-    gad.sum_score_prepan =
-      if_else(condition = na_per_person_gad_prepan > 0,
-              true = NA_real_,
-              false = gad.sum_score_prepan_raw,
-              missing = NA_real_
-              )
-  )
-
-prepan.gad.raw.id %>%
-  descr(gad.sum_score_prepan_raw, stats = "common")
-
-prepan.gad.raw.id %>%
-  descr(gad.sum_score_prepan, stats = "common")
-}
-```
-
-```{r glad gad head}
-if(GLAD ==TRUE | EDGI == TRUE){
-head(prepan.gad.raw.id)
-}
-```
-
-```{r glad gad summary}
-if(GLAD ==TRUE | EDGI == TRUE){
-summarytools::dfSummary(
-  prepan.gad.raw.id,
-  graph.col = F,
-  valid.col = F,
-  labels.col = F)
 }
@@
 
-# glad prepandemic pcl
+# Prepandemic
+
+## gad (prepan)
+
+```{r glad gad prepan cols}
+if(GLAD == TRUE){
+glad.gad.raw <- readRDS(file = paste0(data.raw_path, "/glad/gad_glad.rds"))
+dim(glad.gad.raw)
+colnames(glad.gad.raw)
+}
+```
+
+```{r glad gad prepan cleaning}
+if(GLAD ==TRUE){
+exclude_cols <- c("Sample",
+                  "ID")
+glad.gad.raw.id <- glad.gad.raw %>%
+  drop_na(externalDataReference) %>% # Drop NAs
+  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
+  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
+  mutate(ID = as.numeric(ID),
+         startDate.prepandemic = startDate) %>% # Rename startDate
+  select(
+    Sample, # Sample
+    ID, # ID
+    gad.feeling_nervous_anxious_or_on_edge_prepan = gad.feeling_nervous_anxious_or_on_edge,
+    gad.control_worrying_stop_prepan = gad.control_worrying_stop,
+    gad.worrying_too_much_about_different_things_prepan = gad.worrying_too_much_about_different_things,
+    gad.trouble_relaxing_prepan = gad.trouble_relaxing,
+    gad.sit_restless_hard_prepan = gad.sit_restless_hard,
+    gad.becoming_easily_annoyed_or_irritable_prepan = gad.becoming_easily_annoyed_or_irritable,
+    gad.awful_feeling_afraid_happen_prepan = gad.awful_feeling_afraid_happen
+  ) %>%
+  add_numeric(., exclude = exclude_cols) %>%
+  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
+  mutate_if(is.numeric, ~na_if(., -99)) %>%
+  mutate_if(is.numeric, ~na_if(., -77)) %>%
+  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
+  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
+
+# Inspect dimensions
+dim(glad.gad.raw.id)
+# Inspect colnames
+colnames(glad.gad.raw.id)
+#Differences
+dim(glad.gad.raw)[1]-dim(glad.gad.raw.id)[1]
+}
+```
+
+```{r glad copy prepan gad}
+if(GLAD == TRUE){
+prepan.gad.raw.id <- glad.gad.raw.id
+}
+```
+
+```{r edgi gad prepan cols}
+if(EDGI == TRUE){
+  edgi.gad.raw <- readRDS(file = paste0(data.raw_path, "/edgi/gad_edgi.rds"))
+  dim(edgi.gad.raw)
+  colnames(edgi.gad.raw)
+}
+```
+
+```{r edgi gad prepan cleaning}
+if(EDGI == TRUE){
+exclude_cols <- c("Sample",
+                  "ID")
+
+edgi.gad.raw.id <- edgi.gad.raw %>%
+  drop_na(externalDataReference) %>% # Drop NAs
+  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
+  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
+  mutate(ID = as.numeric(ID),
+         startDate.edgi = startDate) %>% # Rename startDate
+  select(
+    Sample, # Sample
+    ID, # ID
+    gad.feeling_nervous_anxious_or_on_edge_prepan = gad.feeling_nervous_anxious_or_on_edge,
+    gad.control_worrying_stop_prepan = gad.control_worrying_stop,
+    gad.worrying_too_much_about_different_things_prepan = gad.worrying_too_much_about_different_things,
+    gad.trouble_relaxing_prepan = gad.trouble_relaxing,
+    gad.sit_restless_hard_prepan = gad.sit_restless_hard,
+    gad.becoming_easily_annoyed_or_irritable_prepan = gad.becoming_easily_annoyed_or_irritable,
+    gad.awful_feeling_afraid_happen_prepan = gad.awful_feeling_afraid_happen
+  ) %>%
+  add_numeric(., exclude = exclude_cols) %>%
+  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
+  mutate_if(is.numeric, ~na_if(., -99)) %>%
+  mutate_if(is.numeric, ~na_if(., -77)) %>%
+  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
+  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
+
+# Inspect dimensions
+dim(edgi.gad.raw.id)
+# Inspect colnames
+colnames(edgi.gad.raw.id)
+#Differences
+dim(edgi.gad.raw)[1]-dim(edgi.gad.raw.id)[1]
+}
+```
+
+```{r edgi copy prepan gad}
+if(EDGI == TRUE){
+  prepan.gad.raw.id <- edgi.gad.raw.id
+}
+```
+
+Calculate sum score for GAD-7
+Max should be 21.
+
+*Note that scores with missingness will be changed to NA later in the script
+```{r gad sum score prepan raw}
+if(GLAD ==TRUE | EDGI == TRUE){
+# Create vector with scoring key: If the item is reversed coded use -1. 
+# There needs to be the correct number of values for each item in the questionnaire. 
+gad.items_key_prepan <- c(1,1,1,1,1,1,1)
+
+# Create vector with items that are included in total score
+gad.items_prepan <- c(
+  "gad.feeling_nervous_anxious_or_on_edge_prepan_numeric",
+  "gad.control_worrying_stop_prepan_numeric",
+  "gad.worrying_too_much_about_different_things_prepan_numeric",
+  "gad.trouble_relaxing_prepan_numeric",
+  "gad.sit_restless_hard_prepan_numeric",
+  "gad.becoming_easily_annoyed_or_irritable_prepan_numeric",
+  "gad.awful_feeling_afraid_happen_prepan_numeric"
+  )
+
+# Calulate total score
+gad.scored_items_prepan <- scoreItems(keys = gad.items_key_prepan,
+                                        items = prepan.gad.raw.id[gad.items_prepan],
+                                        totals = TRUE, 
+                                        missing = TRUE, 
+                                        impute = 'none', 
+                                        min = 0, 
+                                        max = 3)
+# Add in column to tibble
+prepan.gad.raw.id$gad.sum_score_prepan_raw <- gad.scored_items_prepan$scores
+
+# Look at values
+prepan.gad.raw.id %>%
+  descr(gad.sum_score_prepan_raw,
+        stats = "common"
+        )
+}
+```
+
+missingness (NAs per person)
+
+prepandemic
+```{r gad prepan missingness}
+if(GLAD ==TRUE | EDGI == TRUE){
+prepan.gad.raw.id <- prepan.gad.raw.id %>%
+  mutate(
+    na_per_person_gad_prepan =         # variable for NA per person
+      rowSums(                       
+        is.na(.[gad.items_prepan])
+      )
+  )
+
+prepan.gad.raw.id %>%
+  freq(na_per_person_gad_prepan,
+       cumul = F)
+}
+```
+
+```{r gad prepan sum score if missigng items set to NA}
+if(GLAD ==TRUE | EDGI == TRUE){
+prepan.gad.raw.id <- prepan.gad.raw.id %>%
+  mutate(
+    gad.sum_score_prepan =
+      if_else(condition = na_per_person_gad_prepan > 0,
+              true = NA_real_,
+              false = gad.sum_score_prepan_raw,
+              missing = NA_real_
+              )
+  )
+
+prepan.gad.raw.id %>%
+  descr(gad.sum_score_prepan_raw, stats = "common")
+
+prepan.gad.raw.id %>%
+  descr(gad.sum_score_prepan, stats = "common")
+}
+```
+
+```{r glad prepan gad head}
+if(GLAD ==TRUE | EDGI == TRUE){
+head(prepan.gad.raw.id)
+}
+```
+
+```{r glad prepan gad summary}
+if(GLAD ==TRUE | EDGI == TRUE){
+summarytools::dfSummary(
+  prepan.gad.raw.id,
+  graph.col = F,
+  valid.col = F,
+  labels.col = F)
+}
+```
+
+## pcl (prepan)
 
@@
 
-# edgi pcl
-
 ```{r edgi pcl cols}
@@
 
-```{r glad pcl head}
+```{r pcl prepan head}
 if(GLAD == TRUE | EDGI == TRUE){
@@
 
-```{r glad pcl summary}
+```{r pcl prepan summary}
 if(GLAD == TRUE | EDGI == TRUE){
@@
 
-# glad phq
+## phq (prepan)
 
@@
 
-# edgi phq
-
 ```{r edgi phq cols}
@@
 
-```{r glad phq head}
+```{r phq prepan head}
 if(GLAD == TRUE | EDGI == TRUE) {
@@
 
-```{r glad phq summary}
+```{r phq prepan summary}
 if(GLAD == TRUE | EDGI == TRUE) {
@@
 
-# glad ocir
-
-```{r glad ocir cols}
+## ocir (prepan)
+
+```{r glad ocir prepan cols}
 if(GLAD == TRUE){
@@
 
-```{r glad ocir cleaning}
+```{r glad ocir prepan cleaning}
 if(GLAD == TRUE){
@@
 
-# edgi ocir
-
-```{r edgi ocir cols}
+```{r edgi ocir prepan cols}
 if(EDGI == TRUE){
@@
 
-```{r edgi ocir cleaning}
+```{r edgi ocir prepan cleaning}
 if(EDGI == TRUE){
@@
 
-```{r glad ocir head}
+```{r ocir prepan head}
 if(GLAD == TRUE | EDGI == TRUE) {
@@
 
-```{r glad ocir summary}
+```{r ocir prepan summary}
 if(GLAD == TRUE | EDGI == TRUE) {

### 2020-08-14 PANCHANGE_data_preprocessing2020-07-15.Rmd

@@
 library(summarytools)
-#library(psych)
+library(psych)
 library(tidyverse)

### 2020-08-14 PANCHANGE_data_preprocessing2020-07-15.Rmd

@@
 
+# RAMP demographics
+## Read in data
+```{r ramp dem cols}
+if(RAMP == TRUE){
+  ramp.dem.raw <- readRDS(file = paste0(data.raw_path, "/ramp/dem_ramp.rds"))
+  dim(ramp.dem.raw)
+  colnames(ramp.dem.raw)
+}
+```
+
+```{r}
+
+```
+
+# Select variables
+```{r ramp dem cleaning}
+if(RAMP == TRUE){
+  exclude_cols_dem <- c("ID",
+                        "Sample",
+                        "startDate.ramp")
+
+ramp.dem.raw$externalDataReference <- ramp.dem.raw$`Login ID` #move Login ID to external data reference
+
+  ramp.dem.raw.id <- ramp.dem.raw %>%
+    drop_na(externalDataReference) %>% # Drop NAs
+    distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
+    separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
+    mutate(ID = as.numeric(ID),
+           startDate.ramp = startDate) %>% # Rename startDate
+    select(
+      Sample, # Sample
+      ID, # ID
+      startDate.ramp, #Date when participant signed up to ramp
+      age_category = demographics.how_old_are_you, # Age
+      Gender = demographics.which_gender_do_you_identify_with, # Gender (what [GLAD] vs which [RAMP])
+     # EduYrs = demographics.university_education_attend_school.txt, # Years in education - not in RAMP dataset
+     # demographics.college_or_university_degree, # level of education - univeristy - level of education is in employment file
+     # demographics.a_levelsas_levels_or_equivalent, # level of education - alevel
+    #  demographics.o_levelsgcses_or_equivalent, # level of education - gcse
+     # demographics.cses_or_equivalent, # level of education - cse
+     # demographics.nvq_or_hnd_or_hnc_or_equivalent, # level of education - nvq
+      Transgender_uncleaned = demographics.do_you_identify_as_transgender,
+      Ethnicity = demographics.what_is_your_ethnic_origin # Ethnicity
+    ) %>%
+    add_numeric(., exclude = exclude_cols_dem) %>%
+    mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
+    mutate_if(is.numeric, ~na_if(., -99)) %>%
+    mutate_if(is.numeric, ~na_if(., -77)) %>%
+    mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
+    mutate_if(is.factor, ~na_if(., "Don't know")) %>%
+    mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
+    mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
+    mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
+    mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
+    mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
+    mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
+
+  # Inspect dimensions
+  dim(ramp.dem.raw.id)
+  # Inspect colnames
+  colnames(ramp.dem.raw.id)
+  #Differences
+  dim(ramp.dem.raw)[1]-dim(ramp.dem.raw.id)[1]
+}
+```
+
+```{r ramp copy dem}
+if(RAMP == TRUE){
+  dem.raw.id <- ramp.dem.raw.id
+}
+```
+
 #Clean Age variable
@@
 dem.raw.id %>%
-  freq(age_category)
-
+  freq(age_category_full)
+
+```
+
+# RAMP employment
+## Read in data
+```{r ramp emp cols}
+if(RAMP == TRUE){
+  ramp.employment.raw <- readRDS(file = paste0(data.raw_path, "/ramp/employment_ramp.rds"))
+  dim(ramp.employment.raw)
+  colnames(ramp.employment.raw)
+}
+```
+
+# Select variables
+```{r ramp employment cleaning}
+if(RAMP == TRUE){
+  exclude_cols_employment <- c("ID",
+                        "Sample",
+                        "startDate.ramp")
+
+ramp.employment.raw$externalDataReference <- ramp.employment.raw$`Login ID` #move Login ID to external data reference
+
+ramp.employment.raw.id <- ramp.employment.raw %>%
+    drop_na(externalDataReference) %>% # Drop NAs
+    distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
+    separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
+    mutate(ID = as.numeric(ID),
+           startDate.ramp = startDate) %>% # Rename startDate
+    select(
+      Sample,
+      ID,
+      startDate.ramp,
+      highest_education_ramp = employment.what_is_your_highest_level_of_education, #this is missing NVQ or equivalent which we have in GLAD-COPING
+      # EduYrs = employment.university_education_attend_school.txt, # Years in education - not in RAMP dataset
+      employment.government_work_key_workers
+    ) %>%
+    add_numeric(., exclude = exclude_cols_employment) %>%
+    mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
+    mutate_if(is.numeric, ~na_if(., -99)) %>%
+    mutate_if(is.numeric, ~na_if(., -77)) %>%
+    mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
+    mutate_if(is.factor, ~na_if(., "Don't know")) %>%
+    mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
+    mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
+    mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
+    mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
+    mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
+    mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
+
+  # Inspect dimensions
+  dim(ramp.employment.raw.id)
+  # Inspect colnames
+  colnames(ramp.employment.raw.id)
+  #Differences
+  dim(ramp.employment.raw)[1]-dim(ramp.employment.raw.id)[1]
+}
+```
+
+```{r ramp copy emp}
+if(RAMP == TRUE){
+  employment.raw.id <- ramp.employment.raw.id
 }

### 2020-08-14 PANCHANGE_data_preprocessing2020-07-15.Rmd
fixed NBR IDs

@@
 GLAD = FALSE
-EDGI = FALSE
+EDGI = TRUE
 NBR = FALSE
-RAMP = TRUE
+RAMP = FALSE
 ```
@@
 library(psych)
+library(eeptools) # Needed to calculate age from birthdate
 library(tidyverse)
-library(eeptools) #Needed to calculate age from birthdate
 ```
@@
 
-# GLAD demographics
-## Read in data
+# Demographics
+## GLAD
+### Read in data
 ```{r glad dem cols}
@@
 
-## Select variables
+### Select variables
 ```{r glad dem cleaning}
@@
 
-# EDGI demographics
-## Read in data
+## EDGI
+### Read in data
 ```{r edgi dem cols}
@@
     mutate(ID = as.numeric(ID),
-           startDate.edgi = startDate) %>% # Rename startDate
+           startDate.prepandemic = startDate) %>% # Rename startDate
     select(
@@
       ID, # ID
-      startDate.edgi, #Date when participant signed up to edgi
+      startDate.prepandemic, #Date when participant signed up to edgi
       Age_uncleaned = demographics.how_old_are_you_now.txt, # Age
@@
                         "Sample",
-                        "startDate.nbr",
+                        "startDate.coping",
                         "Age_uncleaned",
@@
 if(NBR == TRUE) {
-exclude_cols_dem <- c("ID",
+exclude_cols_cohort_nbr <- c("ID",
                   "Sample",
-                  "startDate.coping",
                   "Age_uncleaned",
@@
   mutate(
-    ID = as.numeric(ID),
-#         startDate.coping = startDate
-         ) %>% # Rename startDate
+    ID = as.numeric(ID)) %>%
   select(
@@
          ) %>%
-  add_numeric(., exclude = exclude_cols_dem) %>%
+  add_numeric(., exclude = exclude_cols_cohort_nbr) %>%
   mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
@@
                         "Sample",
-                        "startDate.ramp")
+                        "startDate.coping")
 
@@
     mutate(ID = as.numeric(ID),
-           startDate.ramp = startDate) %>% # Rename startDate
+           startDate.coping = startDate) %>% # Rename startDate
     select(
@@
       ID, # ID
-      startDate.ramp, #Date when participant signed up to ramp
+      startDate.coping, #Date when participant signed up to ramp
       age_category = demographics.how_old_are_you, # Age
@@
   exclude_cols_employment <- c("ID",
-                        "Sample",
-                        "startDate.ramp")
+                        "Sample")
 
@@
     separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
-    mutate(ID = as.numeric(ID),
-           startDate.ramp = startDate) %>% # Rename startDate
+    mutate(ID = as.numeric(ID)) %>%
     select(
@@
       ID,
-      startDate.ramp,
       highest_education_ramp = employment.what_is_your_highest_level_of_education, #this is missing NVQ or equivalent which we have in GLAD-COPING
@@
   distinct(subjectid, .keep_all = TRUE) %>% # Remove duplicates based on ID
-  separate(subjectid, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
-  #mutate(
-  #  ID = as.numeric(ID) ##NBR IDs have a letter at the end so can't be coerced to numeric
-  #  ) %>% 
+  separate(subjectid, into = c("Sample", "ID.intm"), sep = 6) %>% # Split ID in Sample and Number
+  separate(ID.intm, into = "ID", sep = 7) %>%
+  mutate(
+    ID = as.numeric(ID)) %>%
   select(
@@
   separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
-  mutate(ID = as.numeric(ID),
-         startDate.prepandemic = startDate) %>% # Rename startDate
+  mutate(ID = as.numeric(ID)) %>%
   select(
@@
   distinct(subjectid, .keep_all = TRUE) %>% # Remove duplicates based on ID
-  separate(subjectid, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
-  mutate(#ID = as.numeric(ID), ## NBR IDs end with letters so can't be numeric
-         startDate.prepandemic = startDate) %>% # Rename startDate
+  separate(subjectid, into = c("Sample", "ID.intm"), sep = 6) %>% # Split ID in Sample and Number
+  separate(ID.intm, into = "ID", sep = 7) %>%
+  mutate(
+    ID = as.numeric(ID)) %>%
   select(
@@
   coping.nbr.gad.raw.id <- coping.nbr.gad.raw %>%
-    drop_na(externalDataReference) %>% # Drop NAs
-    distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
-    separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
-    mutate(ID = as.numeric(ID)
-    ) %>% 
+  drop_na(subjectid) %>% # Drop NAs
+  distinct(subjectid, .keep_all = TRUE) %>% # Remove duplicates based on ID
+  separate(subjectid, into = c("Sample", "ID.intm"), sep = 6) %>% # Split ID in Sample and Number
+  separate(ID.intm, into = "ID", sep = 7) %>%
+  mutate(ID = as.numeric(ID)) %>% 
     select(
@@
 coping.nbr.pcl.raw.id <- coping.nbr.pcl.raw %>%
-  drop_na(externalDataReference) %>% # Drop NAs
-  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
-  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
-  mutate(ID = as.numeric(ID),
-         startDate.coping = startDate) %>% # Rename startDate
+  drop_na(subjectid) %>% # Drop NAs
+  distinct(subjectid, .keep_all = TRUE) %>% # Remove duplicates based on ID
+  separate(subjectid, into = c("Sample", "ID.intm"), sep = 6) %>% # Split ID in Sample and Number
+  separate(ID.intm, into = "ID", sep = 7) %>%
+  mutate(ID = as.numeric(ID)) %>%
   select(
@@
 coping.nbr.phq.raw.id <- coping.nbr.phq.raw %>%
-  drop_na(externalDataReference) %>% # Drop NAs
-  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
-  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
-  mutate(ID = as.numeric(ID)
-  ) %>%
+  drop_na(subjectid) %>% # Drop NAs
+  distinct(subjectid, .keep_all = TRUE) %>% # Remove duplicates based on ID
+  separate(subjectid, into = c("Sample", "ID.intm"), sep = 6) %>% # Split ID in Sample and Number
+  separate(ID.intm, into = "ID", sep = 7) %>%
+  mutate(ID = as.numeric(ID)) %>%
   select(
@@
   distinct(recipientFirstName, .keep_all = TRUE) %>% # Remove duplicates based on ID
-  separate(recipientFirstName, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
-  mutate(ID = as.numeric(ID),
-         startDate.coping = startDate) %>% # Rename startDate
+  separate(recipientFirstName, into = c("Sample", "ID.intm"), sep = 6) %>% # Split ID in Sample and Number
+  separate(ID.intm, into = "ID", sep = 7) %>%
+  mutate(ID = as.numeric(ID)) %>%
   select(

### 2020-08-14 PANCHANGE_data_preprocessing2020-07-15.Rmd
fixed the startDate startDate.coping is in the gad chunk for ALL cohorts

@@
          ID, # ID
-         startDate.prepandemic, #Date when participant signed up to glad
+         startDate.prepandemic = startDate, #Date when participant signed up to glad
          Age_uncleaned = demographics.how_old_are_you_now.txt, # Age
@@
     separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
-    mutate(ID = as.numeric(ID),
-           startDate.prepandemic = startDate) %>% # Rename startDate
+    mutate(ID = as.numeric(ID)) %>%
     select(
@@
       ID, # ID
-      startDate.prepandemic, #Date when participant signed up to edgi
+      startDate.prepandemic = startDate, #Date when participant signed up to edgi
       Age_uncleaned = demographics.how_old_are_you_now.txt, # Age
@@
                         "Sample",
-                        "startDate.coping",
                         "Age_uncleaned",
@@
     separate(ID.intm, into = "ID", sep = 7) %>%
-    mutate(ID = as.numeric(ID),
-           startDate.coping = startDate) %>% # Rename startDate
+    mutate(ID = as.numeric(ID)) %>%
     select(
@@
       ID, # ID
-      startDate.coping, #Date when participant signed up to nbr
+#      startDate.coping, # Date when participant signed up to nbr (is in the coping gad chunk)
 #      Age_uncleaned = demographics.how_old_are_you_now.txt, # Age
@@
          Cohort = cohort, #cohort information
-#         startDate.coping, #Date when participant signed up to NBR COPING
+#         startDate.coping, #Date when participant signed up to NBR COPING (is in the coping gad chunk)
 #         Age_uncleaned = age, # Age
@@
   exclude_cols_dem <- c("ID",
-                        "Sample",
-                        "startDate.coping")
+                        "Sample")
 
@@
     separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
-    mutate(ID = as.numeric(ID),
-           startDate.coping = startDate) %>% # Rename startDate
+    mutate(ID = as.numeric(ID)) %>%
     select(
@@
       ID, # ID
-      startDate.coping, #Date when participant signed up to ramp
+#      startDate.coping, #Date when participant signed up to ramp  (is in the coping gad chunk)
       age_category = demographics.how_old_are_you, # Age
@@
   separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
-  mutate(ID = as.numeric(ID),
-         startDate.edgi = startDate) %>% # Rename startDate
+  mutate(ID = as.numeric(ID)) %>%
   select(
@@
   separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
-  mutate(ID = as.numeric(ID),
-         startDate.prepandemic = startDate) %>% # Rename startDate
+  mutate(ID = as.numeric(ID),) %>%
   select(
@@
   separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
-  mutate(ID = as.numeric(ID),
-         startDate.coping = startDate) %>% # Rename startDate
+  mutate(ID = as.numeric(ID)) %>%
   select(
@@
   separate(recipientFirstName, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
-  mutate(ID = as.numeric(ID),
-         startDate.coping = startDate) %>% # Rename startDate
+  mutate(ID = as.numeric(ID)) %>%
   select(

### 2020-08-14 PANCHANGE_data_preprocessing2020-07-15.Rmd
fixed Highest education prepandemic

@@
 
-## Select variables
+### Select variables
 ```{r edgi dem cleaning}
@@
       demographics.nvq_or_hnd_or_hnc_or_equivalent, # level of education - nvq
-      Ethnicity = demographics.questions_based_ethnic_origin # Ethnicity
+      Ethnicity = demographics.what_is_your_ethnic_origin # Ethnicity (different to GLAD)
     ) %>%
@@
 
-# NBR demographics
-## Read in data
+## NBR
+### Read in data
 ```{r nbr dem cols}
@@
 
-## Select variables
+### Select variables
 ```{r nbr dem cleaning}
@@
 
-## Cohort information
+### Cohort information
 Information on INTERVAL, COMPARE, and STRIDES
@@
 }
-```
-
-```{r}
-
 ```
@@
 if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE ) {
-# define age limits 
-age_upper_limit = 117 # oldest person in the world is 117 years
+# Define age limits 
+age_upper_limit = 117 # The oldest person in the world is 117 years
 age_lower_limit = 16
@@
 
-# Inspect colnames
-colnames(dem.raw.id)
+# Inspect variable
+dem.raw.id %>%
+  descr(
+    Age,
+    #stats = "common"
+    )
 }
@@
       recode_factor(
-        highest_education_numeric,
+        highest_education_prepan_numeric,
         `1` = "GCSE/CSE",

### 2020-08-14 PANCHANGE_data_preprocessing2020-07-15.Rmd
deleted one RAMP employment section because it was duplicated

@@
 
-# RAMP demographics
-## Read in data
+## RAMP
+### Read in data
 ```{r ramp dem cols}
@@
 
-# Select variables
+### Select variables
 ```{r ramp dem cleaning}
@@
 
-#Clean Age variable
+# Demographics variable creation
+## Clean Age variable
 Age outlier
@@
 
-# Categorise age into groups 
+## Categorise age into groups 
 In RAMP, age is indicated categorically: 16-18, 19-25, 26-35, 36-45, 46-55, 56-65, 66-70, 71-75, 76-80, 81-85, 86-90, 91-100, 100+
@@
 
-# RAMP employment
-## Read in data
-```{r ramp emp cols}
-if(RAMP == TRUE){
-  ramp.employment.raw <- readRDS(file = paste0(data.raw_path, "/ramp/employment_ramp.rds"))
-  dim(ramp.employment.raw)
-  colnames(ramp.employment.raw)
-}
-```
-
-# Select variables
-```{r ramp employment cleaning}
-if(RAMP == TRUE){
-  exclude_cols_employment <- c("ID",
-                        "Sample")
-
-ramp.employment.raw$externalDataReference <- ramp.employment.raw$`Login ID` #move Login ID to external data reference
-
-ramp.employment.raw.id <- ramp.employment.raw %>%
-    drop_na(externalDataReference) %>% # Drop NAs
-    distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
-    separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
-    mutate(ID = as.numeric(ID)) %>%
-    select(
-      Sample,
-      ID,
-      highest_education_ramp = employment.what_is_your_highest_level_of_education, #this is missing NVQ or equivalent which we have in GLAD-COPING
-      # EduYrs = employment.university_education_attend_school.txt, # Years in education - not in RAMP dataset
-      employment.government_work_key_workers
-    ) %>%
-    add_numeric(., exclude = exclude_cols_employment) %>%
-    mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
-    mutate_if(is.numeric, ~na_if(., -99)) %>%
-    mutate_if(is.numeric, ~na_if(., -77)) %>%
-    mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
-    mutate_if(is.factor, ~na_if(., "Don't know")) %>%
-    mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
-    mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
-    mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
-    mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
-    mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
-    mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
-
-  # Inspect dimensions
-  dim(ramp.employment.raw.id)
-  # Inspect colnames
-  colnames(ramp.employment.raw.id)
-  #Differences
-  dim(ramp.employment.raw)[1]-dim(ramp.employment.raw.id)[1]
-}
-```
-
-```{r ramp copy emp}
-if(RAMP == TRUE){
-  employment.raw.id <- ramp.employment.raw.id
-}
-```
+# employment
+
+## GLAD / EDGI
 
@@
 if(EDGI == TRUE) {
+  exclude_cols <- c("Sample",
+                  "ID")
+
 edgi.mhd.raw.id <- edgi.mhd.raw %>%

### 2020-08-14 PANCHANGE_data_preprocessing2020-07-15.Rmd
cleaning up headers
clean up nbr mhd data read in

@@
 
-# employment
-
-## GLAD / EDGI
-
-# Highest education (prepandemic)
+## Highest education (prepandemic, GLAD & EDGI)
+
 Proceed along qualifications fields. If field is not blank, take that as highest qual. If field is blank, check next field. If all fields are blank, NA
@@
 
-# Employment/highest education (baseline)
+# Employment
 
@@
 
-## Highest education (baseline)
+## Highest education (baseline, GLAD, EDGI, NBR, RAMP)
 Proceed along qualifications fields. If field is not blank, take that as highest qual. If field is blank, check next field. If all fields are blank, NA
@@
     ID, # ID
-    starts_with("mhd.")
+    mhd.anorexia_nervosa,
+    mhd.atypical_anorexia_nervosa,
+    mhd.bulimia_nervosa,
+    mhd.atypical_bulimia_nervosa,
+    mhd.bingeeating_disorder,
+    mhd.atypical_bingeeating_disorder,
   ) %>%
@@
     ID, # ID
-    starts_with("mhd.")
+    starts_with("mhd."),
+    mhd.specific_phobia_e.g._phobia_of_flying = mhd.specific_phobia_e.g._fear_of_flying,
+    mhd.specific_phobia_e.g._phobia_of_flying_numeric = mhd.specific_phobia_e.g._fear_of_flying_numeric,
+    mhd.psychological_overeating_or_bingeeating = mhd.bingeeating_disorder,
+    mhd.psychological_overeating_or_bingeeating_numeric = mhd.bingeeating_disorder_numeric,
+    mhd.type_psychosis_psychotic_illness = mhd.psychosis_type_psychotic_illness,
+    mhd.type_psychosis_psychotic_illness_numeric = mhd.psychosis_type_psychotic_illness_numeric,
+    mhd.autism_aspergers_or_autistic_spectrum_disorder = mhd.autism_spectrum_disorder_asd,
+    mhd.autism_aspergers_or_autistic_spectrum_disorder_numeric = mhd.autism_spectrum_disorder_asd_numeric,
+    mhd.anorexia_nervosa_unc,
+    mhd.atypical_anorexia_nervosa_unc,
+    mhd.bulimia_nervosa_unc,
+    mhd.psychological_overeating_or_bingeeating_unc
   ) %>%
+  add_column(
+    mhd.schizoaffective_disorder = NA, #NBR doesn't ask about schizoaffective disorder. This means the column das not exist in the data set
+    mhd.schizoaffective_disorder_numeric = NA
+  )
   add_numeric(., exclude = exclude_cols) %>%
@@
 
-# Rename columns that differ from GLAD
-nbr.mhd.raw.id_renamed <- nbr.mhd.raw.id %>% 
-  mutate(
-    mhd.specific_phobia_e.g._phobia_of_flying = mhd.specific_phobia_e.g._fear_of_flying,
-    mhd.specific_phobia_e.g._phobia_of_flying_numeric = mhd.specific_phobia_e.g._fear_of_flying_numeric,
-    mhd.psychological_overeating_or_bingeeating = mhd.bingeeating_disorder,
-    mhd.psychological_overeating_or_bingeeating_numeric = mhd.bingeeating_disorder_numeric,
-    mhd.type_psychosis_psychotic_illness = mhd.psychosis_type_psychotic_illness,
-    mhd.type_psychosis_psychotic_illness_numeric = mhd.psychosis_type_psychotic_illness_numeric,
-    mhd.autism_aspergers_or_autistic_spectrum_disorder = mhd.autism_spectrum_disorder_asd,
-    mhd.autism_aspergers_or_autistic_spectrum_disorder_numeric = mhd.autism_spectrum_disorder_asd_numeric
-    ) %>% 
-  add_column(
-    mhd.schizoaffective_disorder = NA, #NBR doesn't ask about schizoaffective
-    mhd.schizoaffective_disorder_numeric = NA
-  )
-
 # Inspect dimensions
-dim(nbr.mhd.raw.id_renamed)
+dim(nbr.mhd.raw.id)
 # Inspect colnames
-colnames(nbr.mhd.raw.id_renamed)
+colnames(nbr.mhd.raw.id)
 #Differences
-dim(nbr.mhd.raw)[1]-dim(nbr.mhd.raw.id_renamed)[1]
+dim(nbr.mhd.raw)[1]-dim(nbr.mhd.raw.id)[1]
 }
@@
 
-# Grouping mental health disorders
+## Grouping mental health disorders
 *#Disorder groupings - from COPING/RAMP analysis minutes*
@@
 
+### Depressive disorders
 ```{r mhd depressive_disorders}
@@
 
-Anxiety disorders group
+### Anxiety disorders
 ```{r mhd anxiety_disorders}
@@
 
-Eating disorders group
-
+### Eating disorders
+
+There is routing questionnaire if participants have been diagnosed with an eating disorder and afterwards they get asked the specific disorders.
+Therefore, mhd.suspected_eating_disorder_diagnosed_numeric needs to be recoded as 0 otherwise they would be NAs.
 ```{r nbr cleaning eating disorders}
@@
       case_when(mhd.suspected_eating_disorder_diagnosed_numeric == "0" ~ 0,
-                mhd.anorexia_nervosa_numeric == "0" ~ 0,
-                mhd.anorexia_nervosa_numeric == "1" ~ 1),
+                mhd.anorexia_nervosa_unc_numeric == "0" ~ 0,
+                mhd.anorexia_nervosa_unc_numeric == "1" ~ 1),
     mhd.atypical_anorexia_nervosa_numeric =
       case_when(mhd.suspected_eating_disorder_diagnosed_numeric == "0" ~ 0,
-                mhd.atypical_anorexia_nervosa_numeric == "0" ~ 0,
-                mhd.atypical_anorexia_nervosa_numeric == "1" ~ 1),
+                mhd.atypical_anorexia_nervosa_unc_numeric == "0" ~ 0,
+                mhd.atypical_anorexia_nervosa_unc_numeric == "1" ~ 1),
     mhd.bulimia_nervosa_numeric =
       case_when(mhd.suspected_eating_disorder_diagnosed_numeric == "0" ~ 0,
-                mhd.bulimia_nervosa_numeric == "0" ~ 0,
-                mhd.bulimia_nervosa_numeric == "1" ~ 1),
+                mhd.bulimia_nervosa_unc_numeric == "0" ~ 0,
+                mhd.bulimia_nervosa_unc_numeric == "1" ~ 1),
     mhd.psychological_overeating_or_bingeeating_numeric =
       case_when(mhd.suspected_eating_disorder_diagnosed_numeric == "0" ~ 0,
-                mhd.psychological_overeating_or_bingeeating_numeric == "0" ~ 0,
-                mhd.psychological_overeating_or_bingeeating_numeric == "1" ~ 1)
+                mhd.psychological_overeating_or_bingeeating_unc_numeric == "0" ~ 0,
+                mhd.psychological_overeating_or_bingeeating_unc_numeric == "1" ~ 1)
     )
@@
 
-Obsessive compulsive disorders
+### Obsessive compulsive disorders
 ```{r mhd obsessive_compulsive_disorders}

### 2020-08-14 PANCHANGE_data_preprocessing2020-07-15.Rmd
adding headers with #

@@
 
-Psychotic disorders group
-[63] "mhd.schizophrenia_numeric"                                 
-[64] "mhd.schizoaffective_disorder_numeric"                      
-[65] "mhd.type_psychosis_psychotic_illness_numeric" 
+### Psychotic disorders
+"mhd.schizophrenia_numeric"                                 
+"mhd.schizoaffective_disorder_numeric"                      
+"mhd.type_psychosis_psychotic_illness_numeric" 
 ```{r mhd psychotic_disorders}

### 2020-08-14 PANCHANGE_data_preprocessing2020-07-15.Rmd
adding headers with # no 2

@@
 
-Personality disorder groups
+### Personality disorders
 ++KT: For all cluster coding chunks - have added other clusters as == 0, so that they are not coerced into NAs. 
@@
 
-Control grouping
+### Controls
 These individuals have no self report diagnosis of any kind that we measure. 
@@
 
-Total disorder count
+## Total disorder count
 ```{r disorders_total_count}
@@
 
-Comorbidity count
+## Comorbidity count
 ```{r cormorbidity_total_count}
@@
 
+## Inspection
 ```{r glad mhd head}
@@
 
-# exclude cols
+# Columns to exclude from add_numeric
 

### 2020-08-14 PANCHANGE_data_preprocessing2020-07-15.Rmd
working on the mhd sections for EDGI

@@
     ID, # ID
-    starts_with("mhd.")
+    starts_with("mhd."),
+    mhd.bingeeating_disorder = mhd.psychological_overeating_or_bingeeating
   ) %>%
@@
 
-```{r edgi mhd copy}
+```{r edgi mhd2 cols}
 if(EDGI == TRUE) {
-  mhd.raw.id <- edgi.mhd.raw.id
+edgi.mhd2.raw <- readRDS(file = paste0(data.raw_path,"/edgi/dem_edgi.rds"))
+dim(edgi.mhd2.raw)
+colnames(edgi.mhd2.raw)
+}
+```
+
+```{r edgi mhd2 cleaning}
+if(EDGI == TRUE){
+  exclude_cols_mhd2 <- c("ID",
+                        "Sample",
+                        "startDate.prepandemic",
+                        "Age_uncleaned",
+                        "EduYrs")
+
+  edgi.mhd2.raw.id <- edgi.mhd2.raw %>%
+    drop_na(externalDataReference) %>% # Drop NAs
+    distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
+    separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
+    mutate(ID = as.numeric(ID)) %>%
+    select(
+      Sample, # Sample
+      ID, # ID
+    mhd.depression = demographics.depression,
+    mhd.pregnancy_depression = demographics.pregnancy_depression,
+    mhd.premenstrual_dysphoric_disorder_pmdd = demographics.premenstrual_dysphoric_disorder_pmdd,
+    mhd.anxiety_nerves_or_generalised_anxiety_disorder = demographics.anxiety_nerves_or_generalised_anxiety_disorder,
+    mhd.social_anxiety_or_social_phobia = demographics.social_anxiety_or_social_phobia,
+    mhd.specific_phobia_e.g._phobia_of_flying = demographics.specific_phobia_e.g._fear_of_flying, # fear instead of phobia
+    mhd.agoraphobia = demographics.agoraphobia,
+    mhd.panic_disorder = demographics.panic_disorder,
+    mhd.panic_attacks = demographics.panic_attacks,
+    mhd.obsessivecompulsive_disorder_ocd = demographics.obsessivecompulsive_disorder_ocd,
+    mhd.obsessive_compulsive_related_disorders = demographics.obsessive_compulsive_related_disorders,
+    mhd.mania_hypomania_bipolar_or_manicdepression = demographics.mania_hypomania_bipolar_or_manicdepression,
+    mhd.schizophrenia = demographics.schizophrenia,
+    mhd.type_psychosis_psychotic_illness = demographics.psychosis_type_psychotic_illness, # word type psychosis changed order compared to GLAD 
+#    mhd.personality_disorder_diagnosed = demographics.personality_disorder_diagnosed, # does not exist in EDGI because it is multiple choice in EDGI
+    mhd.posttraumatic_stress_disorder_ptsd = demographics.posttraumatic_stress_disorder_ptsd,
+    mhd.autism_aspergers_or_autistic_spectrum_disorder = demographics.autism_spectrum_disorder_asd, # different name in EDGI
+    ) %>%
+    add_column(
+      mhd.schizoaffective_disorder = NA_character_
+    ) %>%
+    add_numeric(., exclude = exclude_cols_mhd2) %>%
+    mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
+    mutate_if(is.numeric, ~na_if(., -99)) %>%
+    mutate_if(is.numeric, ~na_if(., -77)) %>%
+    mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
+    mutate_if(is.factor, ~na_if(., "Don't know")) %>%
+    mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
+    mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
+    mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
+    mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
+    mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
+    mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
+
+  # Inspect dimensions
+  dim(edgi.mhd2.raw.id)
+  # Inspect colnames
+  colnames(edgi.mhd2.raw.id)
+  #Differences
+  dim(edgi.mhd2.raw)[1]-dim(edgi.mhd2.raw.id)[1]
+}
+```
+
+```{r edgi combine mhd copy}
+if(EDGI == TRUE){
+mhd.raw.id <- left_join(
+  x = edgi.mhd.raw.id,
+  y = edgi.mhd2.raw.id,
+  by = c("Sample", "ID")
+  )
+
+# Inspect dimensions
+dim(mhd.raw.id)
+# Inspect colnames
+colnames(mhd.raw.id)
 }
@@
     mhd.specific_phobia_e.g._phobia_of_flying = mhd.specific_phobia_e.g._fear_of_flying,
-    mhd.specific_phobia_e.g._phobia_of_flying_numeric = mhd.specific_phobia_e.g._fear_of_flying_numeric,
-    mhd.psychological_overeating_or_bingeeating = mhd.bingeeating_disorder,
-    mhd.psychological_overeating_or_bingeeating_numeric = mhd.bingeeating_disorder_numeric,
     mhd.type_psychosis_psychotic_illness = mhd.psychosis_type_psychotic_illness,
-    mhd.type_psychosis_psychotic_illness_numeric = mhd.psychosis_type_psychotic_illness_numeric,
     mhd.autism_aspergers_or_autistic_spectrum_disorder = mhd.autism_spectrum_disorder_asd,
-    mhd.autism_aspergers_or_autistic_spectrum_disorder_numeric = mhd.autism_spectrum_disorder_asd_numeric,
-    mhd.anorexia_nervosa_unc,
-    mhd.atypical_anorexia_nervosa_unc,
-    mhd.bulimia_nervosa_unc,
-    mhd.psychological_overeating_or_bingeeating_unc
+    mhd.anorexia_nervosa_unc = mhd.anorexia_nervosa,
+    mhd.atypical_anorexia_nervosa_unc = mhd.atypical_anorexia_nervosa,
+    mhd.bulimia_nervosa_unc = mhd.bulimia_nervosa,
+    mhd.psychological_overeating_or_bingeeating_unc = mhd.psychological_overeating_or_bingeeating
   ) %>%
@@
                 mhd.bulimia_nervosa_unc_numeric == "1" ~ 1),
-    mhd.psychological_overeating_or_bingeeating_numeric =
+    mhd.bingeeating_disorder_numeric =
       case_when(mhd.suspected_eating_disorder_diagnosed_numeric == "0" ~ 0,
-                mhd.psychological_overeating_or_bingeeating_unc_numeric == "0" ~ 0,
-                mhd.psychological_overeating_or_bingeeating_unc_numeric == "1" ~ 1)
+                mhd.bingeeating_disorder_numeric == "0" ~ 0,
+                mhd.bingeeating_disorder_numeric == "1" ~ 1)
     )
@@
 ```{r mhd eating_disorders}
-if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE | RAMP == TRUE) {
+if(GLAD == TRUE | NBR == TRUE | RAMP == TRUE) {
 mhd.raw.id <- mhd.raw.id %>%
@@
         mhd.bulimia_nervosa_numeric == "1" ~ 1,
-        mhd.psychological_overeating_or_bingeeating_numeric == "1" ~ 1,
+        mhd.bingeeating_disorder_numeric == "1" ~ 1,
         (mhd.anorexia_nervosa_numeric == "0" &
@@
         mhd.bulimia_nervosa_numeric == "0" &
-        mhd.psychological_overeating_or_bingeeating_numeric == "0") ~ 0
+        mhd.bingeeating_disorder_numeric == "0") ~ 0
       )
@@
 
+For EDGI does not include other eating disorders, such as purging disorder, rumination disorder, ARFID, or Pica
+```{r edgi mhd eating_disorders}
+if(EDGI == TRUE) {
+mhd.raw.id <- mhd.raw.id %>%
+  mutate(
+    eating_disorders_numeric =
+      case_when(
+        mhd.anorexia_nervosa_numeric == "1" ~ 1,
+        mhd.atypical_anorexia_nervosa_numeric == "1" ~ 1,
+        mhd.bulimia_nervosa_numeric == "1" ~ 1,
+        mhd.atypical_bulimia_nervosa_numeric == "1" ~ 1, # additional diagnosis in EDGI but not in GLAD
+        mhd.bingeeating_disorder_numeric == "1" ~ 1,
+        mhd.atypical_bingeeating_disorder_numeric == "1" ~ 1, # additional diagnosis in EDGI
+        (mhd.anorexia_nervosa_numeric == "0" &
+        mhd.atypical_anorexia_nervosa_numeric == "0" &
+          mhd.atypical_anorexia_nervosa_numeric == "0" &
+        mhd.bulimia_nervosa_numeric == "0" &
+          mhd.atypical_bulimia_nervosa_numeric == "0" &
+        mhd.bingeeating_disorder_numeric == "0" &
+          mhd.atypical_bingeeating_disorder_numeric == "0") ~ 0
+      )
+  )
+
+mhd.raw.id <- mhd.raw.id %>%
+  mutate(
+    eating_disorders =
+      recode_factor(eating_disorders_numeric,
+                    "0" = "No eating disorder",
+                    "1" = "Eating disorder",
+                    missing = NA_character_
+                    )
+  )
+
+mhd.raw.id %>%
+  freq(eating_disorders,
+       cumul = F)
+}
+```
+
 Eating disorders with binge eating vs eating disorders without
@@
 ```{r mhd restricting_vs_binge_eating_eating_disorders}
-if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE | RAMP == TRUE) {
+if(GLAD == TRUE | NBR == TRUE | RAMP == TRUE) {
 mhd.raw.id <- mhd.raw.id %>%
@@
         mhd.bulimia_nervosa_numeric == "1" ~ 2,
-        mhd.psychological_overeating_or_bingeeating_numeric == "1" ~ 2,
+        mhd.bingeeating_disorder_numeric == "1" ~ 2,
         (mhd.anorexia_nervosa_numeric == "0" &
@@
         mhd.bulimia_nervosa_numeric == "0" &
-        mhd.psychological_overeating_or_bingeeating_numeric == "0") ~ 0
+        mhd.bingeeating_disorder_numeric == "0") ~ 0
+      )
+  )
+
+mhd.raw.id <- mhd.raw.id %>%
+  mutate(
+    restricting_vs_binge_eating_eating_disorders =
+      recode_factor(restricting_vs_binge_eating_eating_disorders_numeric,
+                    "0" = "No eating disorder",
+                    "1" = "Anorexia nervosa",
+                    "2" = "Eating disorder with binge eating",
+                    missing = NA_character_
+                    )
+  )
+
+mhd.raw.id %>%
+  freq(restricting_vs_binge_eating_eating_disorders,
+       cumul = F)
+}
+```
+
+```{r mhd restricting_vs_binge_eating_eating_disorders}
+if(EDGI == TRUE) {
+mhd.raw.id <- mhd.raw.id %>%
+  mutate(
+    restricting_vs_binge_eating_eating_disorders_numeric =
+      case_when(
+        mhd.anorexia_nervosa_numeric == "1" ~ 1,
+        mhd.atypical_anorexia_nervosa_numeric == "1" ~ 1,
+        mhd.bulimia_nervosa_numeric == "1" ~ 2,
+        mhd.atypical_bulimia_nervosa_numeric == "1" ~ 2, # additional diagnosis in EDGI but not in GLAD
+        mhd.bingeeating_disorder_numeric == "1" ~ 2,
+        mhd.atypical_bingeeating_disorder_numeric == "1" ~ 2, # additional diagnosis in EDGI
+        (mhd.anorexia_nervosa_numeric == "0" &
+        mhd.atypical_anorexia_nervosa_numeric == "0" &
+          mhd.atypical_anorexia_nervosa_numeric == "0" &
+        mhd.bulimia_nervosa_numeric == "0" &
+          mhd.atypical_bulimia_nervosa_numeric == "0" &
+        mhd.bingeeating_disorder_numeric == "0" &
+          mhd.atypical_bingeeating_disorder_numeric == "0") ~ 0
       )
@@
     mhd.bulimia_nervosa_numeric,
-    mhd.psychological_overeating_or_bingeeating_numeric,
+    mhd.bingeeating_disorder_numeric,
     mhd.anorexia_nervosa,
@@
     mhd.bulimia_nervosa,
-    mhd.psychological_overeating_or_bingeeating
+    mhd.bingeeating_disorder
+  )
+}
+```
+
+```{r Check eating_disorders}
+if(EDGI == TRUE) {
+mhd.raw.id %>%
+  select(
+    eating_disorders,
+    eating_disorders_numeric,
+    restricting_vs_binge_eating_eating_disorders,
+    restricting_vs_binge_eating_eating_disorders_numeric,
+    mhd.anorexia_nervosa_numeric,
+    mhd.atypical_anorexia_nervosa_numeric,
+    mhd.bulimia_nervosa_numeric,
+    mhd.bingeeating_disorder_numeric,
+    mhd.anorexia_nervosa,
+    mhd.atypical_anorexia_nervosa,
+    mhd.bulimia_nervosa,
+    mhd.atypical_bulimia_nervosa,
+    mhd.bingeeating_disorder,
+    mhd.atypical_bingeeating_disorder,
   )

### 2020-08-14 PANCHANGE_data_preprocessing2020-07-15.Rmd
added body dysmorphic disorder to the checking chunk

@@
     mhd.obsessive_compulsive_related_disorders = demographics.obsessive_compulsive_related_disorders,
+    mhd.body_dysmorphic_disorder_bdd_numeric = demographics.body_dysmorphic_disorder,
     mhd.mania_hypomania_bipolar_or_manicdepression = demographics.mania_hypomania_bipolar_or_manicdepression,
@@
     mhd.obsessive_compulsive_related_disorders,
-    mhd.obsessive_compulsive_related_disorders_numeric
+    mhd.obsessive_compulsive_related_disorders_numeric,
+    mhd.body_dysmorphic_disorder_bdd,
+    mhd.body_dysmorphic_disorder_bdd_numeric
   )

### 2020-08-14 PANCHANGE_data_preprocessing2020-07-15.Rmd
edgi added adhd and personality disorder

@@
     mhd.obsessive_compulsive_related_disorders = demographics.obsessive_compulsive_related_disorders,
-    mhd.body_dysmorphic_disorder_bdd_numeric = demographics.body_dysmorphic_disorder,
+    mhd.body_dysmorphic_disorder_bdd = demographics.body_dysmorphic_disorder,
     mhd.mania_hypomania_bipolar_or_manicdepression = demographics.mania_hypomania_bipolar_or_manicdepression,
@@
     mhd.autism_aspergers_or_autistic_spectrum_disorder = demographics.autism_spectrum_disorder_asd, # different name in EDGI
+    mhd.personality_disorder = demographics.personality_disorder,
+    mhd.attention_deficit_hyperactivity_disorder = demographics.attention_deficit_hyperactivity_disorder
     ) %>%
@@
 ```{r mhd personality_cluster_a}
+if(GLAD == TRUE | NBR == TRUE | RAMP == TRUE) {
 mhd.raw.id <- mhd.raw.id %>%
@@
 ```{r Check personality_cluster_a}
+if(GLAD == TRUE | NBR == TRUE | RAMP == TRUE) {
 mhd.raw.id %>%
@@
 ```{r mhd personality_cluster_b}
+if(GLAD == TRUE | NBR == TRUE | RAMP == TRUE) {
 mhd.raw.id <- mhd.raw.id %>%
@@
 ```{r Check personality_cluster_b}
+if(GLAD == TRUE | NBR == TRUE | RAMP == TRUE) {
 mhd.raw.id %>%
@@
 ```{r glad mhd personality_cluster_c}
+if(GLAD == TRUE | NBR == TRUE | RAMP == TRUE) {
 mhd.raw.id <- mhd.raw.id %>%
@@
 ```{r Check personality_cluster_c}
+if(GLAD == TRUE | NBR == TRUE | RAMP == TRUE) {
 mhd.raw.id %>%

### 2020-08-14 PANCHANGE_data_preprocessing2020-07-15.Rmd
Final edits to MHD section. All runs properly for NBR now.

--- 2020-08-14 PANCHANGE_data_preprocessing2020-07-15.Rmd
@@
     mhd.bulimia_nervosa_unc = mhd.bulimia_nervosa,
-    mhd.psychological_overeating_or_bingeeating_unc = mhd.psychological_overeating_or_bingeeating
+    mhd.bingeeating_disorder_unc = mhd.bingeeating_disorder
   ) %>%
   add_column(
-    mhd.schizoaffective_disorder = NA, #NBR doesn't ask about schizoaffective disorder. This means the column das not exist in the data set
-    mhd.schizoaffective_disorder_numeric = NA
-  )
+    mhd.schizoaffective_disorder = NA #NBR doesn't ask about schizoaffective disorder. This means the column das not exist in the data set
+  ) %>% 
   add_numeric(., exclude = exclude_cols) %>%
@@
 if(NBR == TRUE) {
-  mhd.raw.id <- nbr.mhd.raw.id_renamed
+  mhd.raw.id <- nbr.mhd.raw.id
 }
@@
 if(NBR == TRUE) {
-#Recode as 0 if ppt respnds no to screening question (mhd.suspected_eating_disorder_diagnosed_numeric)
+#Recode as 0 if ppt responds no to screening question (mhd.suspected_eating_disorder_diagnosed_numeric)
 mhd.raw.id <- mhd.raw.id %>%
@@
       case_when(mhd.suspected_eating_disorder_diagnosed_numeric == "0" ~ 0,
-                mhd.bingeeating_disorder_numeric == "0" ~ 0,
-                mhd.bingeeating_disorder_numeric == "1" ~ 1)
+                mhd.bingeeating_disorder_unc_numeric == "0" ~ 0,
+                mhd.bingeeating_disorder_unc_numeric == "1" ~ 1),
+    mhd.anorexia_nervosa =
+      case_when(mhd.suspected_eating_disorder_diagnosed_numeric == "0" ~ "Not Anorexia nervosa",
+                mhd.anorexia_nervosa_unc_numeric == "0" ~ "Not Anorexia nervosa",
+                mhd.anorexia_nervosa_unc_numeric == "1" ~ "Anorexia nervosa"),
+    mhd.atypical_anorexia_nervosa =
+      case_when(mhd.suspected_eating_disorder_diagnosed_numeric == "0" ~ "Not Atypical anorexia nervosa",
+                mhd.atypical_anorexia_nervosa_unc_numeric == "0" ~ "Not Atypical anorexia nervosa",
+                mhd.atypical_anorexia_nervosa_unc_numeric == "1" ~ "Atypical anorexia nervosa"),
+    mhd.bulimia_nervosa =
+      case_when(mhd.suspected_eating_disorder_diagnosed_numeric == "0" ~ "Not Bulimia nervosa",
+                mhd.bulimia_nervosa_unc_numeric == "0" ~ "Not Bulimia nervosa",
+                mhd.bulimia_nervosa_unc_numeric == "1" ~ "Bulimia nervosa"),
+    mhd.bingeeating_disorder =
+      case_when(mhd.suspected_eating_disorder_diagnosed_numeric == "0" ~ "Not Binge-eating disorder",
+                mhd.bingeeating_disorder_unc_numeric == "0" ~ "Not Binge-eating disorder",
+                mhd.bingeeating_disorder_unc_numeric == "1" ~ "Binge-eating disorder")
     )

### 2020-08-14 PANCHANGE_data_preprocessing2020-07-15.Rmd
pattern to skip personality disorders

--- 2020-08-14 PANCHANGE_data_preprocessing2020-07-15.Rmd
@@
 ```{r mhd categories}
+if(GLAD == TRUE | NBR == TRUE | RAMP == TRUE) {
 mhd.raw.categories <- mhd.raw.id %>%
@@
     )
+}
+```
+
+```{r mhd categories}
+if(EDGI == TRUE) {
+mhd.raw.categories <- mhd.raw.id %>%
+  select(
+    Sample,
+    ID,
+    anxiety_disorders_numeric,
+    anxiety_disorders,
+    mhd.specific_phobia_e.g._phobia_of_flying_numeric,
+    mhd.specific_phobia_e.g._phobia_of_flying,
+    mhd.social_anxiety_or_social_phobia_numeric,
+    mhd.social_anxiety_or_social_phobia,
+    agoraphobia_panic_disorder_numeric,
+    agoraphobia_panic_disorder,
+    depressive_disorders_numeric,
+    depressive_disorders,
+    eating_disorders_numeric,
+    eating_disorders,
+    obsessive_compulsive_disorders_numeric,
+    obsessive_compulsive_disorders,
+    psychotic_disorders_numeric,
+    psychotic_disorders,
+    mhd.mania_hypomania_bipolar_or_manicdepression_numeric,
+    mhd.mania_hypomania_bipolar_or_manicdepression,
+    mhd.posttraumatic_stress_disorder_ptsd_numeric,
+    mhd.posttraumatic_stress_disorder_ptsd,
+    mhd.autism_aspergers_or_autistic_spectrum_disorder_numeric,
+    mhd.autism_aspergers_or_autistic_spectrum_disorder,
+    mhd.attention_deficit_hyperactivity_disorder_numeric,
+    mhd.attention_deficit_hyperactivity_disorder,
+    mhd.personality_disorder_numeric,
+    mhd.personality_disorder,
+#    personality_cluster_a_numeric,
+#    personality_cluster_a,
+#    personality_cluster_b_numeric,
+#    personality_cluster_b,
+#    personality_cluster_c_numeric,
+#    personality_cluster_c,
+    depression_and_anxiety_numeric,
+    depression_and_anxiety,
+    restricting_vs_binge_eating_eating_disorders_numeric,
+    restricting_vs_binge_eating_eating_disorders,
+    bipolar_and_schizophrenia_numeric,
+    bipolar_and_schizophrenia,
+    control_numeric,
+    control,
+    disorders_total_count,
+    comorbidity_total_count_numeric,
+    comorbidity_total_count_factor_numeric,
+    comorbidity_total_count_factor
+    ) %>%
+  add_column(
+    personality_cluster_a_numeric = NA_real_,
+    personality_cluster_a = NA_real_,
+    personality_cluster_b_numeric = NA_real_,
+    personality_cluster_b = NA_real_,
+    personality_cluster_c_numeric = NA_real_,
+    personality_cluster_c = NA_real_,    
+  )
+}
 ```
@@
       pcl.stressful_experience_upset_reminded_prepan = pcl.stressful_experience_upset_reminded,
-      pcl.stressful_situation_avoiding_activities_prepan = pcl.stressful_situation_avoiding_activities,
+      pcl.stressful_situation_avoiding_activities_prepan = pcl.stressful_situation_situations_reminded, # different to glad: pcl.stressful_situation_avoiding_activities,
       pcl.cut_people_feeling_distant_prepan = pcl.cut_people_feeling_distant,

### 2020-08-14 PANCHANGE_data_preprocessing2020-07-15.Rmd
adapted ocir prepan

@@
       ocir.i_repeatedly_check_doors_windows_drawers_etc_prepan = ocir.i_repeatedly_check_doors_windows_drawers_etc.,
-      ocir.arranged_things_change_upset_prepan = ocir.arranged_things_change_upset,
-      ocir.repeat_feel_numbers_prepan = ocir.repeat_feel_numbers,
-      ocir.clean_simply_wash_feel_prepan = ocir.clean_simply_wash_feel,
-      ocir.mind_upset_unpleasant_thoughts_prepan = ocir.mind_upset_unpleasant_thoughts,
-      ocir.afraid_avoid_throwing_things_prepan = ocir.afraid_avoid_throwing_things,
-      ocir.light_switches_water_taps_prepan = ocir.light_switches_water_taps,
-      ocir.arranged_things_prepan = ocir.arranged_things,
-      ocir.good_feel_bad_numbers_prepan = ocir.good_feel_bad_numbers,
-      ocir.hands_longer_wash_prepan = ocir.hands_longer_wash,
+      ocir.arranged_things_change_upset_prepan = ocir.arranged_properly_objects_upset, # different GLAD: ocir.arranged_things_change_upset,
+      ocir.repeat_feel_numbers_prepan = ocir.repeat_feel_numbers.87, # ocir.repeat_feel_numbers,
+      ocir.clean_simply_wash_feel_prepan = ocir.clean_simply_wash_feel.9, # ocir.clean_simply_wash_feel,
+      ocir.mind_upset_unpleasant_thoughts_prepan = ocir.mind_upset_unpleasant_thoughts.11, # ocir.mind_upset_unpleasant_thoughts,
+      ocir.afraid_avoid_throwing_things_prepan = ocir.afraid_avoid_throwing_things.7, # ocir.afraid_avoid_throwing_things,
+      ocir.light_switches_water_taps_prepan = ocir.light_switches_water_taps.7, # ocir.light_switches_water_taps,
+      ocir.arranged_things_prepan = ocir.arranged_things.32, # ocir.arranged_things,
+      ocir.good_feel_bad_numbers_prepan = ocir.good_feel_bad_numbers.60, # ocir.good_feel_bad_numbers,
+      ocir.hands_longer_wash_prepan = ocir.hands_longer_wash.23, # ocir.hands_longer_wash,
       ocir.saved_things_prepan = ocir.saved_things,
-      ocir.frequently_difficulty_rid_nasty_prepan = ocir.frequently_difficulty_rid_nasty,
+      ocir.frequently_difficulty_rid_nasty_prepan = ocir.frequently_difficulty_rid_nasty.16, # ocir.frequently_difficulty_rid_nasty,
       ocir.i_check_things_more_often_than_necessary_prepan = ocir.i_check_things_more_often_than_necessary.,
       ocir.arranged_properly_objects_upset_prepan = ocir.arranged_properly_objects_upset,
-      ocir.feel_compelled_count_things_prepan = ocir.feel_compelled_count_things,
-      ocir.strangers_touch_touched_difficult_prepan = ocir.strangers_touch_touched_difficult,
-      ocir.control_difficult_find_thoughts_prepan = ocir.control_difficult_find_thoughts,
-      ocir.i_collect_things_i_dont_need_prepan = ocir.i_collect_things_i_dont_need
+      ocir.feel_compelled_count_things_prepan = ocir.feel_compelled_count_things.27, # ocir.feel_compelled_count_things,
+      ocir.strangers_touch_touched_difficult_prepan = ocir.strangers_touch_touched_difficult.33, # ocir.strangers_touch_touched_difficult,
+      ocir.control_difficult_find_thoughts_prepan = ocir.control_difficult_find_thoughts.30, #ocir.control_difficult_find_thoughts,
+      ocir.i_collect_things_i_dont_need_prepan = ocir.i_collect_things_i_dont_need.348, # ocir.i_collect_things_i_dont_need
     ) %>%

### 2020-08-14 PANCHANGE_data_preprocessing2020-07-15.Rmd
fixed baseline and retro questionnaires

@@
     valid.col = F,
-    labels.col = F
+    labels.col = T # to see what is baseline and what is retro
   )
@@
       startDate.coping = startDate, # Rename startDate
-      gad.problems_made_difficult_care, # Impairment
-      gad.pandemic_felt_feelings, # Comparison to before the pandemic (retro)
+      gad.problems_made_difficult_care = gad.care_difficult_home_things, # Impairment (different to GLAD)
+      gad.pandemic_felt_feelings = gad.pandemic_feelings_felt, # Comparison to before the pandemic (retro; different to GLAD)
       gad.feeling_nervous_anxious_or_on_edge_retro = gad.feeling_nervous_anxious_or_on_edge,
@@
       gad.becoming_easily_annoyed_or_irritable_retro = gad.becoming_easily_annoyed_or_irritable,
-      gad.awful_feeling_afraid_happen_retro = gad.awful_feeling_afraid_happen,
+      gad.awful_feeling_afraid_happen_retro = gad.feeling_afraid_awful_happen, # different to GLAD: gad.awful_feeling_afraid_happen,
       gad.feeling_nervous_anxious_or_on_edge_base = gad.feeling_nervous_anxious_or_on_edge.1,
@@
       gad.becoming_easily_annoyed_or_irritable_base = gad.becoming_easily_annoyed_or_irritable.1,
-      gad.awful_feeling_afraid_happen_base = gad.awful_feeling_afraid_happen.1
+      gad.awful_feeling_afraid_happen_base = gad.feeling_afraid_awful_happen.1 # different to GLAD: gad.awful_feeling_afraid_happen.1
     ) %>%
@@
     ID, # ID
-    pcl.stressful_experience_repeated_images_base = pcl.stressful_experience_repeated_images,
-    pcl.stressful_experience_upset_reminded_base = pcl.stressful_experience_upset_reminded, # differ to EDGI prepan
-    pcl.stressful_situation_avoiding_activities_base = pcl.avoiding_activities_stressful_experience, # differ to EDGI prepan
+    pcl.stressful_experience_repeated_images_base = pcl.repeated_images_thoughts_past, # different pcl.stressful_experience_repeated_images,
+    pcl.stressful_experience_upset_reminded_base = pcl.upset_reminded_past_feeling, # differ to EDGI prepan
+    pcl.stressful_situation_avoiding_activities_base = pcl.avoiding_activities_reminded_situations, # differ to EDGI prepan
     pcl.cut_people_feeling_distant_base = pcl.cut_people_feeling_distant,
@@
     pcl.difficulty_concentrating_base = pcl.difficulty_concentrating,
-    pcl.stressful_experience_repeated_images_retro = pcl.stressful_experience_repeated_images.1,
-    pcl.stressful_experience_upset_reminded_retro = pcl.stressful_experience_upset_reminded.1,
-    pcl.stressful_situation_avoiding_activities_retro = pcl.avoiding_activities_stressful_experience.1,
+    pcl.stressful_experience_repeated_images_retro = pcl.repeated_images_thoughts_past.1,
+    pcl.stressful_experience_upset_reminded_retro = pcl.upset_reminded_past_feeling.1,
+    pcl.stressful_situation_avoiding_activities_retro = pcl.avoiding_activities_reminded_situations.1,
     pcl.cut_people_feeling_distant_retro = pcl.cut_people_feeling_distant.1,
@@
 
-Will need to double check these namings once we have the new cleaned data -- KT. 
 ```{r coping edgi phq cleaning}
@@
     ID, # ID
-    phq.problems_made_difficult_care,
-    phq.pandemic_felt_feelings,
+    phq.problems_made_difficult_care = phq.care_difficult_home_things,
+    phq.pandemic_felt_feelings = phq.pandemic_feelings_felt,
     phq.little_interest_or_pleasure_in_doing_things_retro = phq.little_interest_or_pleasure_in_doing_things,
@@
     phq.poor_appetite_or_overeating_retro = phq.poor_appetite_or_overeating,
-    phq.feeling_bad_failure_family_retro = phq.feeling_bad_failure_family,
+    phq.feeling_bad_failure_family_retro = phq.family_feeling_bad_failure, # differ GLAD phq.feeling_bad_failure_family,
     phq.trouble_concentrating_reading_newspaper_retro = phq.trouble_concentrating_newspaper_reading, # differ EDGI prepandemic
@@
     phq.poor_appetite_or_overeating_base = phq.poor_appetite_or_overeating.1,
-    phq.feeling_bad_failure_family_base = phq.feeling_bad_failure_family.1,
+    phq.feeling_bad_failure_family_base = phq.family_feeling_bad_failure.1, # differ GLAD
     phq.trouble_concentrating_reading_newspaper_base = phq.trouble_concentrating_newspaper_reading.1, # differ EDGI prepandemic
@@
     ocir.arranged_things_change_upset_retro = ocir.arranged_things_change_upset,
-    ocir.repeat_feel_numbers_retro = ocir.numbers_repeat_feel, ## Different from EDGI prepandemic
+    ocir.repeat_feel_numbers_retro = ocir.repeat_numbers_feel, # Different from EDGI prepandemic ocir.numbers_repeat_feel,
     ocir.clean_simply_wash_feel_retro = ocir.feel_contaminated_clean_simply, ## Different from EDGI prepandemic
@@
     ocir.afraid_avoid_throwing_things_retro = ocir.afraid_avoid_throwing_things,
-    ocir.light_switches_water_taps_retro = ocir.light_switches_water_taps,
+    ocir.light_switches_water_taps_retro = ocir.water_taps_light_switches, #  differ ocir.light_switches_water_taps,
     ocir.arranged_things_retro = ocir.arranged_things,
@@
     ocir.strangers_touch_touched_difficult_retro = ocir.strangers_touch_touched_object, ## Different from EDGI prepandemic
-    ocir.control_difficult_find_thoughts_retro = ocir.control_find_difficult_thoughts, ## Different from EDGI prepandemic
+    ocir.control_difficult_find_thoughts_retro = ocir.control_difficult_thoughts_find, # Differ to EDGI prepan ocir.control_find_difficult_thoughts,
     ocir.i_collect_things_i_dont_need_retro = ocir.i_collect_things_i_dont_need., ## Different from EDGI prepandemic
@@
     ocir.arranged_things_change_upset_base = ocir.arranged_things_change_upset.1,
-    ocir.repeat_feel_numbers_base = ocir.numbers_repeat_feel.1, ## Different from EDGI prepandemic
+    ocir.repeat_feel_numbers_base = ocir.repeat_numbers_feel.1, ## Different from EDGI prepandemic
     ocir.clean_simply_wash_feel_base = ocir.feel_contaminated_clean_simply.1, ## Different from EDGI prepandemic
@@
     ocir.afraid_avoid_throwing_things_base = ocir.afraid_avoid_throwing_things.1,
-    ocir.light_switches_water_taps_base = ocir.light_switches_water_taps.1,
+    ocir.light_switches_water_taps_base = ocir.water_taps_light_switches.1, # differ
     ocir.arranged_things_base = ocir.arranged_things.1,
@@
     ocir.strangers_touch_touched_difficult_base = ocir.strangers_touch_touched_object.1, ## Different from EDGI prepandemic
-    ocir.control_difficult_find_thoughts_base = ocir.control_find_difficult_thoughts.1, ## Different from EDGI prepandemic
+    ocir.control_difficult_find_thoughts_base = ocir.control_difficult_thoughts_find.1, ## Different from EDGI prepandemic
     ocir.i_collect_things_i_dont_need_base = ocir.i_collect_things_i_dont_need..1

### 2020-08-14 PANCHANGE_data_preprocessing2020-07-15.Rmd
fixed the sample in left join

@@
 #      startDate.coping, #Date when participant signed up to ramp  (is in the coping gad chunk)
-      age_category = demographics.how_old_are_you, # Age
+      age_category_full = demographics.how_old_are_you, # Age
       Gender = demographics.which_gender_do_you_identify_with, # Gender (what [GLAD] vs which [RAMP])
@@
 coping.edgi.ocir.raw.id <- coping.edgi.ocir.raw %>%
-  drop_na(recipientFirstName) %>% # Drop NAs
-  distinct(recipientFirstName, .keep_all = TRUE) %>% # Remove duplicates based on ID
-  separate(recipientFirstName, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
+  drop_na(externalDataReference) %>% # Drop NAs
+  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
+  separate(externalDataReference, into = c("Sample", "ID"), sep = 6) %>% # Split ID in Sample and Number
   mutate(ID = as.numeric(ID)) %>%
@@
 dat.no.sex.no.gender.no.age <- dat.no.sex.no.gender %>%
-  drop_na(age_category)
+  drop_na(age_category_full)
 dim(dat.no.sex.no.gender.no.age)

### 2020-08-14 PANCHANGE_data_preprocessing2020-07-15.Rmd
moved exclude cols up

@@
 ```{r Specify cohort}
-GLAD = FALSE
-EDGI = TRUE
+GLAD = TRUE
+EDGI = FALSE
 NBR = FALSE
@@
 }
+```
+
+# Columns to exclude from add_numeric
+
+```{r cols to exclude}
+exclude_cols <- c("Sample",
+                  "ID")
 ```
@@
 }
-```
-
-# Columns to exclude from add_numeric
-
-```{r cols to exclude}
-exclude_cols <- c("Sample",
-                  "ID")
 ```
@@
   y = coping.glad.respiratory,
-  by = "ID"
+  by = ("Sample", "ID")
 )

### 2020-08-14 PANCHANGE_data_preprocessing2020-07-15.Rmd
fixed merging
GAD section corrected for NBR. Runs properly.

--- 2020-08-14 PANCHANGE_data_preprocessing2020-07-15.Rmd
@@
     mhd.obsessive_compulsive_related_disorders = demographics.obsessive_compulsive_related_disorders,
-    mhd.body_dysmorphic_disorder_bdd = demographics.body_dysmorphic_disorder,
     mhd.mania_hypomania_bipolar_or_manicdepression = demographics.mania_hypomania_bipolar_or_manicdepression,
@@
     mhd.autism_aspergers_or_autistic_spectrum_disorder = demographics.autism_spectrum_disorder_asd, # different name in EDGI
-    mhd.personality_disorder = demographics.personality_disorder,
-    mhd.attention_deficit_hyperactivity_disorder = demographics.attention_deficit_hyperactivity_disorder
     ) %>%
@@
       recode_factor(obsessive_compulsive_disorders_numeric,
-                    "0" = "No obsessivecompulsive disorder",
+                    "0" = "No obsessive compulsive disorder",
                     "1" = "Obsessive compulsive disorder",
@@
     mhd.obsessive_compulsive_related_disorders,
-    mhd.obsessive_compulsive_related_disorders_numeric,
-    mhd.body_dysmorphic_disorder_bdd,
-    mhd.body_dysmorphic_disorder_bdd_numeric
+    mhd.obsessive_compulsive_related_disorders_numeric
   )
@@
 ```{r mhd personality_cluster_a}
-if(GLAD == TRUE | NBR == TRUE | RAMP == TRUE) {
 mhd.raw.id <- mhd.raw.id %>%
@@
        cumul = F)
-}
 ```
@@
 ```{r Check personality_cluster_a}
-if(GLAD == TRUE | NBR == TRUE | RAMP == TRUE) {
 mhd.raw.id %>%
@@
   )
-}
 ```
@@
 ```{r mhd personality_cluster_b}
-if(GLAD == TRUE | NBR == TRUE | RAMP == TRUE) {
 mhd.raw.id <- mhd.raw.id %>%
@@
 ```{r Check personality_cluster_b}
-if(GLAD == TRUE | NBR == TRUE | RAMP == TRUE) {
 mhd.raw.id %>%
@@
 ```{r glad mhd personality_cluster_c}
-if(GLAD == TRUE | NBR == TRUE | RAMP == TRUE) {
 mhd.raw.id <- mhd.raw.id %>%
@@
 ```{r Check personality_cluster_c}
-if(GLAD == TRUE | NBR == TRUE | RAMP == TRUE) {
 mhd.raw.id %>%
@@
 ```{r mhd categories}
-if(GLAD == TRUE | NBR == TRUE | RAMP == TRUE) {
 mhd.raw.categories <- mhd.raw.id %>%
@@
     )
-}
-```
-
-```{r mhd categories}
-if(EDGI == TRUE) {
-mhd.raw.categories <- mhd.raw.id %>%
-  select(
-    Sample,
-    ID,
-    anxiety_disorders_numeric,
-    anxiety_disorders,
-    mhd.specific_phobia_e.g._phobia_of_flying_numeric,
-    mhd.specific_phobia_e.g._phobia_of_flying,
-    mhd.social_anxiety_or_social_phobia_numeric,
-    mhd.social_anxiety_or_social_phobia,
-    agoraphobia_panic_disorder_numeric,
-    agoraphobia_panic_disorder,
-    depressive_disorders_numeric,
-    depressive_disorders,
-    eating_disorders_numeric,
-    eating_disorders,
-    obsessive_compulsive_disorders_numeric,
-    obsessive_compulsive_disorders,
-    psychotic_disorders_numeric,
-    psychotic_disorders,
-    mhd.mania_hypomania_bipolar_or_manicdepression_numeric,
-    mhd.mania_hypomania_bipolar_or_manicdepression,
-    mhd.posttraumatic_stress_disorder_ptsd_numeric,
-    mhd.posttraumatic_stress_disorder_ptsd,
-    mhd.autism_aspergers_or_autistic_spectrum_disorder_numeric,
-    mhd.autism_aspergers_or_autistic_spectrum_disorder,
-    mhd.attention_deficit_hyperactivity_disorder_numeric,
-    mhd.attention_deficit_hyperactivity_disorder,
-    mhd.personality_disorder_numeric,
-    mhd.personality_disorder,
-#    personality_cluster_a_numeric,
-#    personality_cluster_a,
-#    personality_cluster_b_numeric,
-#    personality_cluster_b,
-#    personality_cluster_c_numeric,
-#    personality_cluster_c,
-    depression_and_anxiety_numeric,
-    depression_and_anxiety,
-    restricting_vs_binge_eating_eating_disorders_numeric,
-    restricting_vs_binge_eating_eating_disorders,
-    bipolar_and_schizophrenia_numeric,
-    bipolar_and_schizophrenia,
-    control_numeric,
-    control,
-    disorders_total_count,
-    comorbidity_total_count_numeric,
-    comorbidity_total_count_factor_numeric,
-    comorbidity_total_count_factor
-    ) %>%
-  add_column(
-    personality_cluster_a_numeric = NA_real_,
-    personality_cluster_a = NA_real_,
-    personality_cluster_b_numeric = NA_real_,
-    personality_cluster_b = NA_real_,
-    personality_cluster_c_numeric = NA_real_,
-    personality_cluster_c = NA_real_,    
-  )
-}
 ```
@@
       pcl.stressful_experience_upset_reminded_prepan = pcl.stressful_experience_upset_reminded,
-      pcl.stressful_situation_avoiding_activities_prepan = pcl.stressful_situation_situations_reminded, # different to glad: pcl.stressful_situation_avoiding_activities,
+      pcl.stressful_situation_avoiding_activities_prepan = pcl.stressful_situation_avoiding_activities,
       pcl.cut_people_feeling_distant_prepan = pcl.cut_people_feeling_distant,
@@
       ocir.i_repeatedly_check_doors_windows_drawers_etc_prepan = ocir.i_repeatedly_check_doors_windows_drawers_etc.,
-      ocir.arranged_things_change_upset_prepan = ocir.arranged_properly_objects_upset, # different GLAD: ocir.arranged_things_change_upset,
-      ocir.repeat_feel_numbers_prepan = ocir.repeat_feel_numbers.87, # ocir.repeat_feel_numbers,
-      ocir.clean_simply_wash_feel_prepan = ocir.clean_simply_wash_feel.9, # ocir.clean_simply_wash_feel,
-      ocir.mind_upset_unpleasant_thoughts_prepan = ocir.mind_upset_unpleasant_thoughts.11, # ocir.mind_upset_unpleasant_thoughts,
-      ocir.afraid_avoid_throwing_things_prepan = ocir.afraid_avoid_throwing_things.7, # ocir.afraid_avoid_throwing_things,
-      ocir.light_switches_water_taps_prepan = ocir.light_switches_water_taps.7, # ocir.light_switches_water_taps,
-      ocir.arranged_things_prepan = ocir.arranged_things.32, # ocir.arranged_things,
-      ocir.good_feel_bad_numbers_prepan = ocir.good_feel_bad_numbers.60, # ocir.good_feel_bad_numbers,
-      ocir.hands_longer_wash_prepan = ocir.hands_longer_wash.23, # ocir.hands_longer_wash,
+      ocir.arranged_things_change_upset_prepan = ocir.arranged_things_change_upset,
+      ocir.repeat_feel_numbers_prepan = ocir.repeat_feel_numbers,
+      ocir.clean_simply_wash_feel_prepan = ocir.clean_simply_wash_feel,
+      ocir.mind_upset_unpleasant_thoughts_prepan = ocir.mind_upset_unpleasant_thoughts,
+      ocir.afraid_avoid_throwing_things_prepan = ocir.afraid_avoid_throwing_things,
+      ocir.light_switches_water_taps_prepan = ocir.light_switches_water_taps,
+      ocir.arranged_things_prepan = ocir.arranged_things,
+      ocir.good_feel_bad_numbers_prepan = ocir.good_feel_bad_numbers,
+      ocir.hands_longer_wash_prepan = ocir.hands_longer_wash,
       ocir.saved_things_prepan = ocir.saved_things,
-      ocir.frequently_difficulty_rid_nasty_prepan = ocir.frequently_difficulty_rid_nasty.16, # ocir.frequently_difficulty_rid_nasty,
+      ocir.frequently_difficulty_rid_nasty_prepan = ocir.frequently_difficulty_rid_nasty,
       ocir.i_check_things_more_often_than_necessary_prepan = ocir.i_check_things_more_often_than_necessary.,
       ocir.arranged_properly_objects_upset_prepan = ocir.arranged_properly_objects_upset,
-      ocir.feel_compelled_count_things_prepan = ocir.feel_compelled_count_things.27, # ocir.feel_compelled_count_things,
-      ocir.strangers_touch_touched_difficult_prepan = ocir.strangers_touch_touched_difficult.33, # ocir.strangers_touch_touched_difficult,
-      ocir.control_difficult_find_thoughts_prepan = ocir.control_difficult_find_thoughts.30, #ocir.control_difficult_find_thoughts,
-      ocir.i_collect_things_i_dont_need_prepan = ocir.i_collect_things_i_dont_need.348, # ocir.i_collect_things_i_dont_need
+      ocir.feel_compelled_count_things_prepan = ocir.feel_compelled_count_things,
+      ocir.strangers_touch_touched_difficult_prepan = ocir.strangers_touch_touched_difficult,
+      ocir.control_difficult_find_thoughts_prepan = ocir.control_difficult_find_thoughts,
+      ocir.i_collect_things_i_dont_need_prepan = ocir.i_collect_things_i_dont_need
     ) %>%
@@
     valid.col = F,
-    labels.col = T # to see what is baseline and what is retro
+    labels.col = F
   )
@@
     ) %>% 
-    select(
-      Sample, # Sample
-      ID, # ID
-      startDate.coping = startDate, # Rename startDate
-      gad.problems_made_difficult_care = gad.care_difficult_home_things, # Impairment (different to GLAD)
-      gad.pandemic_felt_feelings = gad.pandemic_feelings_felt, # Comparison to before the pandemic (retro; different to GLAD)
-      gad.feeling_nervous_anxious_or_on_edge_retro = gad.feeling_nervous_anxious_or_on_edge,
-      gad.control_worrying_stop_retro = gad.control_worrying_stop,
-      gad.worrying_too_much_about_different_things_retro = gad.worrying_too_much_about_different_things,
-      gad.trouble_relaxing_retro = gad.trouble_relaxing,
-      gad.sit_restless_hard_retro = gad.sit_restless_hard,
-      gad.becoming_easily_annoyed_or_irritable_retro = gad.becoming_easily_annoyed_or_irritable,
-      gad.awful_feeling_afraid_happen_retro = gad.feeling_afraid_awful_happen, # different to GLAD: gad.awful_feeling_afraid_happen,
-      gad.feeling_nervous_anxious_or_on_edge_base = gad.feeling_nervous_anxious_or_on_edge.1,
-      gad.control_worrying_stop_base = gad.control_worrying_stop.1,
-      gad.worrying_too_much_about_different_things_base = gad.worrying_too_much_about_different_things.1,
-      gad.trouble_relaxing_base = gad.trouble_relaxing.1,
-      gad.sit_restless_hard_base = gad.sit_restless_hard.1,
-      gad.becoming_easily_annoyed_or_irritable_base = gad.becoming_easily_annoyed_or_irritable.1,
-      gad.awful_feeling_afraid_happen_base = gad.feeling_afraid_awful_happen.1 # different to GLAD: gad.awful_feeling_afraid_happen.1
-    ) %>%
-    add_numeric(., exclude = exclude_cols_coping_edgi) %>%
-    mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
-    mutate_if(is.numeric, ~na_if(., -99)) %>%
-    mutate_if(is.numeric, ~na_if(., -77)) %>%
-    mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
-    mutate_if(is.factor, ~na_if(., "Don't know")) %>%
-    mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
-    mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
-    mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
-    mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
-    mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
-    mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
-
-  # Inspect dimensions
-  dim(coping.edgi.gad.raw.id)
-  # Inspect colnames
-  colnames(coping.edgi.gad.raw.id)
-  #Differences
-  dim(coping.edgi.gad.raw)[1]-dim(coping.edgi.gad.raw.id)[1]
-}
-```
-
-```{r coping edgi gad copy}
-if(EDGI == TRUE) {
-  coping.gad.raw.id <- coping.edgi.gad.raw.id
-}
-```
-
-## NBR
-```{r coping nbr gad cols}
-if(NBR == TRUE) {
-  coping.nbr.gad.raw <- readRDS(file = paste0(data.raw_path,"/nbr/gad_coping_nbr.rds"))
-  dim(coping.nbr.gad.raw)
-  colnames(coping.nbr.gad.raw)
-}
-```
-
-```{r coping nbr gad summary}
-if(NBR == TRUE) {
-  summarytools::dfSummary(
-    coping.nbr.gad.raw,
-    graph.col = F,
-    valid.col = F,
-    labels.col = F
-  )
-}
-```
-
-```{r coping nbr gad cleaning}
-if(NBR == TRUE) {
-  exclude_cols_coping_nbr <- c(
-    "Sample",
-    "ID",
-    "startDate.coping"
-  )
-
-  coping.nbr.gad.raw.id <- coping.nbr.gad.raw %>%
-  drop_na(subjectid) %>% # Drop NAs
-  distinct(subjectid, .keep_all = TRUE) %>% # Remove duplicates based on ID
-  separate(subjectid, into = c("Sample", "ID.intm"), sep = 6) %>% # Split ID in Sample and Number
-  separate(ID.intm, into = "ID", sep = 7) %>%
-  mutate(ID = as.numeric(ID)) %>% 
     select(
@@
       gad.awful_feeling_afraid_happen_base = gad.awful_feeling_afraid_happen.1
+    ) %>%
+    add_numeric(., exclude = exclude_cols_coping_edgi) %>%
+    mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
+    mutate_if(is.numeric, ~na_if(., -99)) %>%
+    mutate_if(is.numeric, ~na_if(., -77)) %>%
+    mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
+    mutate_if(is.factor, ~na_if(., "Don't know")) %>%
+    mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
+    mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
+    mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
+    mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
+    mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
+    mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
+
+  # Inspect dimensions
+  dim(coping.edgi.gad.raw.id)
+  # Inspect colnames
+  colnames(coping.edgi.gad.raw.id)
+  #Differences
+  dim(coping.edgi.gad.raw)[1]-dim(coping.edgi.gad.raw.id)[1]
+}
+```
+
+```{r coping edgi gad copy}
+if(EDGI == TRUE) {
+  coping.gad.raw.id <- coping.edgi.gad.raw.id
+}
+```
+
+## NBR
+```{r coping nbr gad cols}
+if(NBR == TRUE) {
+  coping.nbr.gad.raw <- readRDS(file = paste0(data.raw_path,"/nbr/gad_coping_nbr.rds"))
+  dim(coping.nbr.gad.raw)
+  colnames(coping.nbr.gad.raw)
+}
+```
+
+```{r coping nbr gad summary}
+if(NBR == TRUE) {
+  summarytools::dfSummary(
+    coping.nbr.gad.raw,
+    graph.col = F,
+    valid.col = F,
+    labels.col = F
+  )
+}
+```
+
+```{r coping nbr gad cleaning}
+if(NBR == TRUE) {
+  exclude_cols_coping_nbr <- c(
+    "Sample",
+    "ID",
+    "startDate.coping"
+  )
+
+  coping.nbr.gad.raw.id <- coping.nbr.gad.raw %>%
+  drop_na(subjectid) %>% # Drop NAs
+  distinct(subjectid, .keep_all = TRUE) %>% # Remove duplicates based on ID
+  separate(subjectid, into = c("Sample", "ID.intm"), sep = 6) %>% # Split ID in Sample and Number
+  separate(ID.intm, into = "ID", sep = 7) %>%
+  mutate(ID = as.numeric(ID)) %>% 
+    select(
+      Sample, # Sample
+      ID, # ID
+      startDate.coping = startDate, # Rename startDate
+      gad.problems_made_difficult_care = gad.problems_made_care_difficult, # Impairment (different from GLAD)
+      gad.pandemic_felt_feelings, # Comparison to before the pandemic (retro)
+      gad.feeling_nervous_anxious_or_on_edge_retro = gad.feeling_nervous_anxious_or_on_edge,
+      gad.control_worrying_stop_retro = gad.control_worrying_stop,
+      gad.worrying_too_much_about_different_things_retro = gad.worrying_too_much_about_different_things,
+      gad.trouble_relaxing_retro = gad.trouble_relaxing,
+      gad.sit_restless_hard_retro = gad.sit_restless_hard,
+      gad.becoming_easily_annoyed_or_irritable_retro = gad.becoming_easily_annoyed_or_irritable,
+      gad.awful_feeling_afraid_happen_retro = gad.feeling_afraid_awful_happen, #Different from GLAD
+      gad.feeling_nervous_anxious_or_on_edge_base = gad.feeling_nervous_anxious_or_on_edge.1,
+      gad.control_worrying_stop_base = gad.control_worrying_stop.1,
+      gad.worrying_too_much_about_different_things_base = gad.worrying_too_much_about_different_things.1,
+      gad.trouble_relaxing_base = gad.trouble_relaxing.1,
+      gad.sit_restless_hard_base = gad.sit_restless_hard.1,
+      gad.becoming_easily_annoyed_or_irritable_base = gad.becoming_easily_annoyed_or_irritable.1,
+      gad.awful_feeling_afraid_happen_base = gad.feeling_afraid_awful_happen.1 #Different from GLAD
     ) %>%
@@
 
-```{r coping gad base sum score if missigng items set to NA}
+```{r coping gad base sum score if missing items set to NA}
 coping.gad.raw.id <- coping.gad.raw.id %>%
@@
 
-```{r coping gad retro sum score if missigng items set to NA}
+```{r coping gad retro sum score if missing items set to NA}
 coping.gad.raw.id <- coping.gad.raw.id %>%
@@
     ID, # ID
-    pcl.stressful_experience_repeated_images_base = pcl.repeated_images_thoughts_past, # different pcl.stressful_experience_repeated_images,
-    pcl.stressful_experience_upset_reminded_base = pcl.upset_reminded_past_feeling, # differ to EDGI prepan
-    pcl.stressful_situation_avoiding_activities_base = pcl.avoiding_activities_reminded_situations, # differ to EDGI prepan
+    pcl.stressful_experience_repeated_images_base = pcl.stressful_experience_repeated_images,
+    pcl.stressful_experience_upset_reminded_base = pcl.stressful_experience_upset_reminded, # differ to EDGI prepan
+    pcl.stressful_situation_avoiding_activities_base = pcl.avoiding_activities_stressful_experience, # differ to EDGI prepan
     pcl.cut_people_feeling_distant_base = pcl.cut_people_feeling_distant,
@@
     pcl.difficulty_concentrating_base = pcl.difficulty_concentrating,
-    pcl.stressful_experience_repeated_images_retro = pcl.repeated_images_thoughts_past.1,
-    pcl.stressful_experience_upset_reminded_retro = pcl.upset_reminded_past_feeling.1,
-    pcl.stressful_situation_avoiding_activities_retro = pcl.avoiding_activities_reminded_situations.1,
+    pcl.stressful_experience_repeated_images_retro = pcl.stressful_experience_repeated_images.1,
+    pcl.stressful_experience_upset_reminded_retro = pcl.stressful_experience_upset_reminded.1,
+    pcl.stressful_situation_avoiding_activities_retro = pcl.avoiding_activities_stressful_experience.1,
     pcl.cut_people_feeling_distant_retro = pcl.cut_people_feeling_distant.1,
@@
 
+Will need to double check these namings once we have the new cleaned data -- KT. 
 ```{r coping edgi phq cleaning}
@@
     ID, # ID
-    phq.problems_made_difficult_care = phq.care_difficult_home_things,
-    phq.pandemic_felt_feelings = phq.pandemic_feelings_felt,
+    phq.problems_made_difficult_care,
+    phq.pandemic_felt_feelings,
     phq.little_interest_or_pleasure_in_doing_things_retro = phq.little_interest_or_pleasure_in_doing_things,
@@
     phq.poor_appetite_or_overeating_retro = phq.poor_appetite_or_overeating,
-    phq.feeling_bad_failure_family_retro = phq.family_feeling_bad_failure, # differ GLAD phq.feeling_bad_failure_family,
+    phq.feeling_bad_failure_family_retro = phq.feeling_bad_failure_family,
     phq.trouble_concentrating_reading_newspaper_retro = phq.trouble_concentrating_newspaper_reading, # differ EDGI prepandemic
@@
     phq.poor_appetite_or_overeating_base = phq.poor_appetite_or_overeating.1,
-    phq.feeling_bad_failure_family_base = phq.family_feeling_bad_failure.1, # differ GLAD
+    phq.feeling_bad_failure_family_base = phq.feeling_bad_failure_family.1,
     phq.trouble_concentrating_reading_newspaper_base = phq.trouble_concentrating_newspaper_reading.1, # differ EDGI prepandemic
@@
     ocir.arranged_things_change_upset_retro = ocir.arranged_things_change_upset,
-    ocir.repeat_feel_numbers_retro = ocir.repeat_numbers_feel, # Different from EDGI prepandemic ocir.numbers_repeat_feel,
+    ocir.repeat_feel_numbers_retro = ocir.numbers_repeat_feel, ## Different from EDGI prepandemic
     ocir.clean_simply_wash_feel_retro = ocir.feel_contaminated_clean_simply, ## Different from EDGI prepandemic
@@
     ocir.afraid_avoid_throwing_things_retro = ocir.afraid_avoid_throwing_things,
-    ocir.light_switches_water_taps_retro = ocir.water_taps_light_switches, #  differ ocir.light_switches_water_taps,
+    ocir.light_switches_water_taps_retro = ocir.light_switches_water_taps,
     ocir.arranged_things_retro = ocir.arranged_things,
@@
     ocir.strangers_touch_touched_difficult_retro = ocir.strangers_touch_touched_object, ## Different from EDGI prepandemic
-    ocir.control_difficult_find_thoughts_retro = ocir.control_difficult_thoughts_find, # Differ to EDGI prepan ocir.control_find_difficult_thoughts,
+    ocir.control_difficult_find_thoughts_retro = ocir.control_find_difficult_thoughts, ## Different from EDGI prepandemic
     ocir.i_collect_things_i_dont_need_retro = ocir.i_collect_things_i_dont_need., ## Different from EDGI prepandemic
@@
     ocir.arranged_things_change_upset_base = ocir.arranged_things_change_upset.1,
-    ocir.repeat_feel_numbers_base = ocir.repeat_numbers_feel.1, ## Different from EDGI prepandemic
+    ocir.repeat_feel_numbers_base = ocir.numbers_repeat_feel.1, ## Different from EDGI prepandemic
     ocir.clean_simply_wash_feel_base = ocir.feel_contaminated_clean_simply.1, ## Different from EDGI prepandemic
@@
     ocir.afraid_avoid_throwing_things_base = ocir.afraid_avoid_throwing_things.1,
-    ocir.light_switches_water_taps_base = ocir.water_taps_light_switches.1, # differ
+    ocir.light_switches_water_taps_base = ocir.light_switches_water_taps.1,
     ocir.arranged_things_base = ocir.arranged_things.1,
@@
     ocir.strangers_touch_touched_difficult_base = ocir.strangers_touch_touched_object.1, ## Different from EDGI prepandemic
-    ocir.control_difficult_find_thoughts_base = ocir.control_difficult_thoughts_find.1, ## Different from EDGI prepandemic
+    ocir.control_difficult_find_thoughts_base = ocir.control_find_difficult_thoughts.1, ## Different from EDGI prepandemic
     ocir.i_collect_things_i_dont_need_base = ocir.i_collect_things_i_dont_need..1

### 2020-08-14 PANCHANGE_data_preprocessing2020-07-15.Rmd
PHQ section adapted for NBR, confirmed it works.

@@
 
-```{r coping pcl base sum score if missigng items set to NA}
+```{r coping pcl base sum score if missing items set to NA}
 coping.pcl.raw.id <- coping.pcl.raw.id %>%
@@
 
-```{r coping pcl retro sum score if missigng items set to NA}
+```{r coping pcl retro sum score if missing items set to NA}
 coping.pcl.raw.id <- coping.pcl.raw.id %>%
@@
     ID, # ID
-    phq.problems_made_difficult_care,
+    phq.problems_made_difficult_care = phq.problems_made_care_difficult,
     phq.pandemic_felt_feelings,
@@
     phq.poor_appetite_or_overeating_retro = phq.poor_appetite_or_overeating,
-    phq.feeling_bad_failure_family_retro = phq.feeling_bad_failure_family,
+    phq.feeling_bad_failure_family_retro = phq.family_feeling_bad_failure,
     phq.trouble_concentrating_reading_newspaper_retro = phq.trouble_concentrating_newspaper_reading, # differ NBR prepandemic
@@
     phq.poor_appetite_or_overeating_base = phq.poor_appetite_or_overeating.1,
-    phq.feeling_bad_failure_family_base = phq.feeling_bad_failure_family.1,
+    phq.feeling_bad_failure_family_base = phq.family_feeling_bad_failure.1,
     phq.trouble_concentrating_reading_newspaper_base = phq.trouble_concentrating_newspaper_reading.1, # differ NBR prepandemic
@@
 
-```{r coping phq base sum score if missigng items set to NA}
+```{r coping phq base sum score if missing items set to NA}
 coping.phq.raw.id <- coping.phq.raw.id %>%
@@
 8 items
-```{r phq base sum score if missigng items set to NA - 8 items}
+```{r phq base sum score if missing items set to NA - 8 items}
 coping.phq.raw.id <- coping.phq.raw.id %>%
@@
 
-```{r coping phq retro sum score if missigng items set to NA}
+```{r coping phq retro sum score if missing items set to NA}
 coping.phq.raw.id <- coping.phq.raw.id %>%
@@
 8 items
-```{r phq retro sum score if missigng items set to NA - 8 items}
+```{r phq retro sum score if missing items set to NA - 8 items}
 coping.phq.raw.id <- coping.phq.raw.id %>%

### 2020-08-14 PANCHANGE_data_preprocessing2020-07-15.Rmd
Fixed OCI-R script for NBR so it runs. One ID gets coerced to NA and there are some missing IDs we may want to find in the future.

@@
     ocir.arranged_things_change_upset_retro = ocir.arranged_things_change_upset,
-    ocir.repeat_feel_numbers_retro = ocir.numbers_repeat_feel, ## Different from NBR prepandemic
-    ocir.clean_simply_wash_feel_retro = ocir.feel_contaminated_clean_simply, ## Different from NBR prepandemic
+    ocir.repeat_feel_numbers_retro = ocir.repeat_numbers_feel, ## Different from GLAD
+    ocir.clean_simply_wash_feel_retro = ocir.feel_contaminated_clean_simply,
     ocir.mind_upset_unpleasant_thoughts_retro = ocir.mind_upset_unpleasant_thoughts,
     ocir.afraid_avoid_throwing_things_retro = ocir.afraid_avoid_throwing_things,
-    ocir.light_switches_water_taps_retro = ocir.light_switches_water_taps,
+    ocir.light_switches_water_taps_retro = ocir.water_taps_light_switches, ## Different from GLAD
     ocir.arranged_things_retro = ocir.arranged_things,
-    ocir.good_feel_bad_numbers_retro = ocir.bad_numbers_good_feel, ## Different from NBR prepandemic
-    ocir.hands_longer_wash_retro = ocir.longer_hands_wash, ## Different from NBR prepandemic
+    ocir.good_feel_bad_numbers_retro = ocir.bad_numbers_good_feel,
+    ocir.hands_longer_wash_retro = ocir.longer_hands_wash, 
     ocir.saved_things_retro = ocir.saved_things,
-    ocir.frequently_difficulty_rid_nasty_retro = ocir.frequently_rid_difficulty_nasty, ## Different from NBR prepandemic
+    ocir.frequently_difficulty_rid_nasty_retro = ocir.frequently_rid_difficulty_nasty, 
     ocir.i_check_things_more_often_than_necessary_retro = ocir.i_check_things_more_often_than_necessary.,
@@
     ocir.feel_compelled_count_things_retro = ocir.feel_compelled_count_things,
-    ocir.strangers_touch_touched_difficult_retro = ocir.strangers_touch_touched_object, ## Different from NBR prepandemic
-    ocir.control_difficult_find_thoughts_retro = ocir.control_find_difficult_thoughts, ## Different from NBR prepandemic
-    ocir.i_collect_things_i_dont_need_retro = ocir.i_collect_things_i_dont_need., ## Different from NBR prepandemic
+    ocir.strangers_touch_touched_difficult_retro = ocir.strangers_touch_touched_object, 
+    ocir.control_difficult_find_thoughts_retro = ocir.control_difficult_thoughts_find, ## Different from GLAD 
+    ocir.i_collect_things_i_dont_need_retro = ocir.i_collect_things_i_dont_need., 
     ocir.i_repeatedly_check_doors_windows_drawers_etc_base = ocir.i_repeatedly_check_doors_windows_drawers_etc..1,
     ocir.arranged_things_change_upset_base = ocir.arranged_things_change_upset.1,
-    ocir.repeat_feel_numbers_base = ocir.numbers_repeat_feel.1, ## Different from NBR prepandemic
-    ocir.clean_simply_wash_feel_base = ocir.feel_contaminated_clean_simply.1, ## Different from NBR prepandemic
+    ocir.repeat_feel_numbers_base = ocir.repeat_numbers_feel.1, ## Different from GLAD
+    ocir.clean_simply_wash_feel_base = ocir.feel_contaminated_clean_simply.1,
     ocir.mind_upset_unpleasant_thoughts_base = ocir.mind_upset_unpleasant_thoughts.1,
     ocir.afraid_avoid_throwing_things_base = ocir.afraid_avoid_throwing_things.1,
-    ocir.light_switches_water_taps_base = ocir.light_switches_water_taps.1,
+    ocir.light_switches_water_taps_base = ocir.water_taps_light_switches.1, ## Different from GLAD
     ocir.arranged_things_base = ocir.arranged_things.1,
-    ocir.good_feel_bad_numbers_base = ocir.bad_numbers_good_feel.1, ## Different from NBR prepandemic
-    ocir.hands_longer_wash_base = ocir.longer_hands_wash.1, ## Different from NBR prepandemic
+    ocir.good_feel_bad_numbers_base = ocir.bad_numbers_good_feel.1, 
+    ocir.hands_longer_wash_base = ocir.longer_hands_wash.1, 
     ocir.saved_things_base = ocir.saved_things.1,
-    ocir.frequently_difficulty_rid_nasty_base = ocir.frequently_rid_difficulty_nasty.1, ## Different from NBR prepandemic
+    ocir.frequently_difficulty_rid_nasty_base = ocir.frequently_rid_difficulty_nasty.1, 
     ocir.i_check_things_more_often_than_necessary_base = ocir.i_check_things_more_often_than_necessary..1,
@@
     ocir.feel_compelled_count_things_base = ocir.feel_compelled_count_things.1,
-    ocir.strangers_touch_touched_difficult_base = ocir.strangers_touch_touched_object.1, ## Different from NBR prepandemic
-    ocir.control_difficult_find_thoughts_base = ocir.control_find_difficult_thoughts.1, ## Different from NBR prepandemic
+    ocir.strangers_touch_touched_difficult_base = ocir.strangers_touch_touched_object.1, 
+    ocir.control_difficult_find_thoughts_base = ocir.control_difficult_thoughts_find.1,
     ocir.i_collect_things_i_dont_need_base = ocir.i_collect_things_i_dont_need..1

### 2020-08-14 PANCHANGE_data_preprocessing2020-07-15.Rmd
Finished adapting dataset combination and difference score chunks. Started adapting respiratory sections.

@@
 
-glad data frame list
-```{r glad data frame list}
-glad.dfs.list <- list(
+glad/edgi data frame list
+```{r glad/edgi data frame list}
+if(GLAD == TRUE | EDGI == TRUE) {
+dfs.list <- list(
   dem.raw.id,
@@
 )
-```
-
-```{r Join all questionnaires for glad}
-dat.glad.raw <- plyr::join_all(
-  glad.dfs.list,
+}
+```
+
+Removing all prepandemic dataframes from NBR/RAMP (prepandemic measures don't exist for these cohorts)
+```{r nbr/ramp data frame list}
+if(NBR == TRUE | RAMP == TRUE) {
+dfs.list <- list(
+  dem.raw.id,
+  mhd.raw.categories,
+  coping.gad.raw.id,
+  coping.pcl.raw.id,
+  coping.phq.raw.id,
+  coping.ocir.raw.id
+)
+}
+```
+
+```{r Join all questionnaires}
+dat.raw <- plyr::join_all(
+  dfs.list,
   by = c("ID", "Sample") # Alternatively you can join by several columns EDGI -> "Age", "Sex", "Birthyear"
@@
 #look at the data
-skimr::skim(dat.glad.raw)
+skimr::skim(dat.raw)
 ```
@@
 +++KT: No duplicates identified by ID in GLAD. 
-```{r glad Check duplicates}
-dat.glad.raw$ID.dup <- duplicated(dat.glad.raw$ID)
-
-summary(as.factor(dat.glad.raw$ID.dup))
-
-dat.dup <- dat.glad.raw %>%
++++MD: Duplicates have been removed in cleaning script for NBR. No duplicates at this stage.
+```{r Check duplicates}
+dat.raw$ID.dup <- duplicated(dat.raw$ID)
+
+summary(as.factor(dat.raw$ID.dup))
+
+dat.dup <- dat.raw %>%
   filter(ID.dup == TRUE)
 
-dat.glad.raw.no.dup <- dat.glad.raw %>%
+dat.raw.no.dup <- dat.raw %>%
   filter(ID.dup == FALSE)
@@
 ```{r Exclude participants that do not report sex}
-dim(dat.glad.raw)
-dat.no.sex <- dat.glad.raw %>%
+dim(dat.raw)
+dat.no.sex <- dat.raw %>%
   drop_na(Sex)
@@
 
-dim(dat.glad.raw)[1]-dim(dat.no.sex)[1]
+dim(dat.raw)[1]-dim(dat.no.sex)[1]
 ```
@@
 Exclusion of inflammatory bowel disease (IBD) BioResource (BR) cohort
+++MD: 3,410 participants from NBR IBD cohort excluded
 ```{r COVID exclusion of IBD}
-#dim(dat.no.sex.no.age)
-#
-#dat.no.sex.no.age <- dat.no.sex.no.age %>%
-#  filter(NBR.IBD == 0)
-#
-#dim(dat.no.sex.no.age.no.ibd)
-#
-#dim(dat.no.sex.no.age)[1]-dim(dat.no.sex.no.age.no.ibd)[1]
-
+if(NBR == TRUE) {
+dim(dat.no.sex.no.gender.no.age)
+
+dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age %>%
+  filter(Cohort != "IBD")
+
+dim(dat.no.sex.no.gender.no.age.no.ibd)
+dim(dat.no.sex.no.gender.no.age)[1]-dim(dat.no.sex.no.gender.no.age.no.ibd)[1]
+}
+
+if(GLAD == TRUE | EDGI == TRUE | RAMP == TRUE) {
 dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age
+}
 ```
@@
 ```{r Tidy data}
-dat.glad <- dat.no.sex.no.gender.no.age.no.ibd
-
-skimr::skim(dat.glad)
+dat <- dat.no.sex.no.gender.no.age.no.ibd
+
+skimr::skim(dat)
 ```
@@
 ```{r Prepandemic definitions january_31}
-dat.glad <- dat.glad %>%
+if(GLAD == TRUE | EDGI == TRUE){
+dat <- dat %>%
   mutate(
@@
 
-dat.glad <- dat.glad %>%
+dat <- dat %>%
   mutate(
@@
 
-dat.glad %>%
+dat %>%
   freq(prepandemic_january_31)
+}
 ```
@@
 ```{r Prepandemic definitions march_1}
-dat.glad <- dat.glad %>%
+if(GLAD == TRUE | EDGI == TRUE){
+dat <- dat %>%
   mutate(
@@
 
-dat.glad %>%
+dat %>%
   freq(prepandemic_march_1)
+}
 ```
@@
 ```{r Prepandemic definitions march_23}
-dat.glad <- dat.glad %>%
+if(GLAD == TRUE | EDGI == TRUE){
+dat <- dat %>%
   mutate(
@@
 
-dat.glad %>%
+dat %>%
   freq(prepandemic_march_23)
+}
 ```
@@
 ```{r time difference between sign up questionnaire and COPING questionnaire}
-dat.glad <- dat.glad %>%
+if(GLAD == TRUE | EDGI == TRUE){
+dat <- dat %>%
   mutate(
@@
 
-dat.glad %>%
+dat %>%
   descr(
@@
     )
+}
 ```
@@
 Proportion of people signed up over one year ago
-```{r eval=FALSE, include=FALSE}
-dat.glad <- dat.glad %>%
+```{r glad/edgi ppts signed up over one year ago, eval=FALSE, include=FALSE}
+if(GLAD == TRUE | EDGI == TRUE){
+dat <- dat %>%
   mutate(
@@
 
-dat.glad %>%
+dat %>%
   freq(over_one_year_time_diff_sign_up_coping, cumul = F)
-```
-
-Proportion of people signed up over one year ago
-```{r eval=FALSE, include=FALSE}
-dat.glad <- dat.glad %>%
+}
+```
+
+Proportion of people signed up over half a year ago
+```{r glad/edgi ppts signed up over half a year ago, r eval=FALSE, include=FALSE}
+if(GLAD == TRUE | EDGI == TRUE){
+dat <- dat %>%
   mutate(
@@
 
-dat.glad %>%
+dat %>%
   freq(over_half_a_year_time_diff_sign_up_coping, cumul = F)
+}
 ```
@@
 ```{r phq difference scores}
+if(GLAD == TRUE | EDGI == TRUE){
 # Difference score for prepandemic and retrospective phq sum scores
-dat.glad <- dat.glad %>%
+dat <- dat %>%
   mutate(
@@
 
-summary(dat.glad$phq.diff_score_prepan_retro)
+summary(dat$phq.diff_score_prepan_retro)
 
 # Difference score for prepandemic and baseline phq sum scores
-dat.glad <- dat.glad %>%
+dat <- dat %>%
   mutate(
@@
 
-summary(dat.glad$phq.diff_score_prepan_base)
-
+summary(dat$phq.diff_score_prepan_base)
+}
 # Difference score for retrospective and baseline phq sum scores
-dat.glad <- dat.glad %>%
+dat <- dat %>%
   mutate(
@@
 
-summary(dat.glad$phq.diff_score_base_retro)
+summary(dat$phq.diff_score_base_retro)
 
@@
 ```{r gad difference scores}
+if(GLAD == TRUE | EDGI == TRUE){
 # Difference score for prepandemic and retrospective gad sum scores
-dat.glad <- dat.glad %>%
+dat <- dat %>%
   mutate(
@@
 
-summary(dat.glad$gad.diff_score_prepan_retro)
+summary(dat$gad.diff_score_prepan_retro)
 
 # Difference score for prepandemic and baseline gad sum scores
-dat.glad <- dat.glad %>%
+dat <- dat %>%
   mutate(
@@
 
-summary(dat.glad$gad.diff_score_prepan_base)
-
+summary(dat$gad.diff_score_prepan_base)
+}
 # Difference score for retrospective and baseline gad sum scores
-dat.glad <- dat.glad %>%
+dat <- dat %>%
   mutate(
@@
 
-summary(dat.glad$gad.diff_score_base_retro)
+summary(dat$gad.diff_score_base_retro)
 
@@
 ```{r pcl difference scores}
+if(GLAD == TRUE | EDGI == TRUE){
 # Difference score for prepandemic and baseline pcl sum scores
-dat.glad <- dat.glad %>%
+dat <- dat %>%
   mutate(
@@
 
-summary(dat.glad$pcl.diff_score_prepan_base)
+summary(dat$pcl.diff_score_prepan_base)
+}
 ```
@@
 ```{r frequency of those who reported "due to pandemic" in retro PCL}
-summary(dat.glad$pcl.sum_score_retro)
-
-freq(dat.glad$pcl.stressful_experience_repeated_images_retro)
-freq(dat.glad$pcl.stressful_situation_avoiding_activities_retro)
-freq(dat.glad$pcl.feeling_irritable_or_having_angry_outbursts_retro)
-freq(dat.glad$pcl.stressful_experience_upset_reminded_retro)
-freq(dat.glad$pcl.cut_people_feeling_distant_retro)
-freq(dat.glad$pcl.difficulty_concentrating_retro)
+summary(dat$pcl.sum_score_retro)
+
+freq(dat$pcl.stressful_experience_repeated_images_retro)
+freq(dat$pcl.stressful_situation_avoiding_activities_retro)
+freq(dat$pcl.feeling_irritable_or_having_angry_outbursts_retro)
+freq(dat$pcl.stressful_experience_upset_reminded_retro)
+freq(dat$pcl.cut_people_feeling_distant_retro)
+freq(dat$pcl.difficulty_concentrating_retro)
 ```
@@
 ```{r ocir difference scores}
+if(GLAD == TRUE | EDGI == TRUE){
 # Difference score for prepandemic and retrospective oci-r sum scores
-dat.glad <- dat.glad %>%
+dat <- dat %>%
   mutate(
@@
 
-summary(dat.glad$ocir.diff_score_prepan_retro)
+summary(dat$ocir.diff_score_prepan_retro)
 
 # Difference score for prepandemic and baseline ocir sum scores
-dat.glad <- dat.glad %>%
+dat <- dat %>%
   mutate(
@@
 
-summary(dat.glad$ocir.diff_score_prepan_base)
-
+summary(dat$ocir.diff_score_prepan_base)
+}
 # Difference score for retrospective and baseline ocir sum scores
-dat.glad <- dat.glad %>%
+dat <- dat %>%
   mutate(
@@
 
-summary(dat.glad$ocir.diff_score_base_retro)
+summary(dat$ocir.diff_score_base_retro)
 
@@
 Identify which data (prepan, retro and baseline) each participant has.
-```{r data level groups PHQ}
-dat.glad <- dat.glad %>%
+```{r glad/edgi data level groups PHQ}
+if(GLAD == TRUE | EDGI == TRUE){
+dat <- dat %>%
   mutate(
@@
 
-table(dat.glad$data_group_phq)
+table(dat$data_group_phq)
+}
+```
+
+```{r nbr/ramp data level groups PHQ}
+if(NBR == TRUE | RAMP == TRUE){
+dat <- dat %>%
+  mutate(
+    data_group_phq_numeric =
+      case_when(
+#        na_per_person_phq_base == 0 & na_per_person_phq_prepan == 0 & na_per_person_phq_retro == 0 ~ 5, #all complete baseline, prepan and retro
+        na_per_person_phq_base != 0 & na_per_person_phq_retro == 0  ~ 4, #retro data only
+        na_per_person_phq_base == 0 & na_per_person_phq_retro != 0  ~ 3, #baseline data only
+#        na_per_person_phq_base == 0 & na_per_person_phq_prepan == 0 & na_per_person_phq_retro != 0  ~ 2, #prepan and baseline data only
+        na_per_person_phq_base == 0 & na_per_person_phq_retro == 0 ~ 1,  #baseline and retro data only
+#        na_per_person_phq_base != 0 & na_per_person_phq_prepan == 0 & na_per_person_phq_retro != 0  ~ 0  #prepan data only
+      )
+  )
+
+dat <- dat %>%
+  mutate(
+    data_group_phq = 
+      recode_factor(
+        data_group_phq_numeric,
+        "0" = "Only prepandemic data",
+        "1" = "Baseline and retrospective data",
+        "2" = "Prepandemic and baseline data",
+        "3" = "Baseline data only",
+        "4" = "Retrospective data only",
+        "5" = "All prepandemic, baseline and retrospective data"
+      )
+  )
+
+table(dat$data_group_phq)
+}
 ```
@@
 GAD
-```{r data level groups GAD}
-dat.glad <- dat.glad %>%
+```{r glad/edgi data level groups GAD}
+if(GLAD == TRUE | EDGI == TRUE){
+dat <- dat %>%
   mutate(
@@
 
-table(dat.glad$data_group_gad)
+table(dat$data_group_gad)
+}
+```
+
+```{r nbr/ramp data level groups GAD}
+if(NBR == TRUE | RAMP == TRUE){
+dat <- dat %>%
+  mutate(
+    data_group_gad_numeric =
+      case_when(
+#        na_per_person_gad_base == 0 & na_per_person_gad_prepan == 0 & na_per_person_gad_retro == 0 ~ 5, #all complete baseline, prepan and retro
+        na_per_person_gad_base != 0 & na_per_person_gad_retro == 0  ~ 4, #retro data only
+        na_per_person_gad_base == 0 & na_per_person_gad_retro != 0  ~ 3, #baseline data only
+#        na_per_person_gad_base == 0 & na_per_person_gad_prepan == 0 & na_per_person_gad_retro != 0  ~ 2, #prepan and baseline data only
+        na_per_person_gad_base == 0 & na_per_person_gad_retro == 0 ~ 1,  #baseline and retro data only
+#        na_per_person_gad_base != 0 & na_per_person_gad_prepan == 0 & na_per_person_gad_retro != 0  ~ 0  #prepan data only
+      )
+  )
+
+dat <- dat %>%
+  mutate(
+    data_group_gad = 
+      recode_factor(
+        data_group_gad_numeric,
+        "0" = "Only prepandemic data",
+        "1" = "Baseline and retrospective data",
+        "2" = "Prepandemic and baseline data",
+        "3" = "Baseline data only",
+        "4" = "Retrospective data only",
+        "5" = "All prepandemic, baseline and retrospective data"
+      )
+  )
+
+table(dat$data_group_gad)
+}
 ```
@@
 PCL
-```{r data level groups PCL}
-dat.glad <- dat.glad %>%
+```{r glad/edgi data level groups PCL}
+if(GLAD == TRUE | EDGI == TRUE){
+dat <- dat %>%
   mutate(
@@
 
-table(dat.glad$data_group_pcl)
+table(dat$data_group_pcl)
+}
+```
+
+```{r nbr/ramp data level groups PCL}
+if(NBR == TRUE | RAMP == TRUE){
+dat <- dat %>%
+  mutate(
+    data_group_pcl_numeric =
+      case_when(
+#        na_per_person_pcl_base == 0 & na_per_person_pcl_prepan == 0 & na_per_person_pcl_retro == 0 ~ 5, #all complete baseline, prepan and retro
+        na_per_person_pcl_base != 0 & na_per_person_pcl_retro == 0  ~ 4, #retro data only
+        na_per_person_pcl_base == 0 & na_per_person_pcl_retro != 0  ~ 3, #baseline data only
+#        na_per_person_pcl_base == 0 & na_per_person_pcl_prepan == 0 & na_per_person_pcl_retro != 0  ~ 2, #prepan and baseline data only
+        na_per_person_pcl_base == 0 & na_per_person_pcl_retro == 0 ~ 1,  #baseline and retro data only
+#        na_per_person_pcl_base != 0 & na_per_person_pcl_prepan == 0 & na_per_person_pcl_retro != 0  ~ 0  #prepan data only
+      )
+  )
+
+dat <- dat %>%
+  mutate(
+    data_group_pcl = 
+      recode_factor(
+        data_group_pcl_numeric,
+        "0" = "Only prepandemic data",
+        "1" = "Baseline and retrospective data",
+        "2" = "Prepandemic and baseline data",
+        "3" = "Baseline data only",
+        "4" = "Retrospective data only",
+        "5" = "All prepandemic, baseline and retrospective data"
+      )
+  )
+
+table(dat$data_group_pcl)
+}
 ```
@@
 #Read in respiratory data
-```{r coping resp cols}
+
+## GLAD respiratory
+```{r glad coping respiratory cols}
+if(GLAD == TRUE){
 coping.glad.respiratory.raw <- readRDS(file = paste0(data.raw_path, "/glad/respiratory_coping_glad.rds"))
@@
 colnames(coping.glad.respiratory.raw)
+}
 ```
@@
 Select respiratory variables
-```{r read in respiratory data}
+```{r coping glad respiratory cleaning}
+if(GLAD == TRUE){
 coping.glad.respiratory.raw.id <- coping.glad.respiratory.raw %>%
@@
 dim(coping.glad.respiratory.raw)[1]-dim(coping.glad.respiratory.raw.id)[1]
-
+}
+```
+
+## EDGI respiratory
+```{r edgi coping respiratory cols}
+if(EDGI == TRUE){
+coping.edgi.respiratory.raw <- readRDS(file = paste0(data.raw_path, "/edgi/respiratory_coping_edgi.rds"))
+dim(coping.edgi.respiratory.raw)
+colnames(coping.edgi.respiratory.raw)
+}
+```
+
+Select respiratory variables
+```{r coping edgi respiratory cleaning}
+if(EDGI == TRUE){
+coping.edgi.respiratory.raw.id <- coping.edgi.respiratory.raw %>%
+  drop_na(externalDataReference) %>% # Drop NAs
+  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
+  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
+  mutate(ID = as.numeric(ID)) %>%
+  select(
+    Sample, # Sample
+    ID, # ID
+    respiratory.breath_diarrhoea_fatigue_fever,
+    respiratory.worst_ill_feel,
+    respiratory.persistent_cough,
+    respiratory.skipping_meals_because_you_felt_unwell,
+    respiratory.was_your_sense_of_smell_impaired,
+    respiratory.was_your_sense_of_taste_impaired,
+    respiratory.feeling_tiredfatigued,
+    respiratory.throat_swab_coronavirus_nose,
+    respiratory.throat_swab_test_nose,
+    respiratory.coronavirus_antibody_test,
+    respiratory.results_antibody_test
+  ) %>%
+  add_numeric(., exclude = exclude_cols) %>%
+  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
+  mutate_if(is.numeric, ~na_if(., -99)) %>%
+  mutate_if(is.numeric, ~na_if(., -77)) %>%
+  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
+  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
+
+# Inspect dimensions
+dim(coping.edgi.respiratory.raw.id)
+# Inspect colnames
+colnames(coping.edgi.respiratory.raw.id)
+#Differences
+dim(coping.edgi.respiratory.raw)[1]-dim(coping.edgi.respiratory.raw.id)[1]
+}
 ```
@@
 
-dat.glad.coping <- left_join(
-  x = dat.glad,
+dat.coping <- left_join(
+  x = dat,
   y = coping.glad.respiratory,
@@
 ```{r create numeric sex variable with male=1}
-dat.glad.coping <- dat.glad.coping %>%
+dat.coping <- dat.coping %>%
   mutate(
@@
 ```{r how many people expereinced all symptoms}
-dat.glad.coping <- dat.glad.coping %>%
+dat.coping <- dat.coping %>%
   mutate(
@@
 
-dat.glad.coping %>%
+dat.coping %>%
   freq(covid_symptoms, cumul = F)
@@
 # linear model of covid symptoms
-dat.glad.coping <- dat.glad.coping %>%
+dat.coping <- dat.coping %>%
 		  mutate(
@@
 # Calcualte the odds ratios 
-dat.glad.coping <- dat.glad.coping %>%
+dat.coping <- dat.coping %>%
   mutate(
@@
 # generate binary cutt off variable for risk of COVID 
-dat.glad.coping <- dat.glad.coping %>%
+dat.coping <- dat.coping %>%
 		  mutate(
@@
 #create factor with labels
-dat.glad.coping <- dat.glad.coping %>%
+dat.coping <- dat.coping %>%
   mutate(
@@
 
-descr(x = dat.glad.coping[,covid_variables],
+descr(x = dat.coping[,covid_variables],
       round.digits = 2,
@@
 ## looking at cases over 0.5
-freq(dat.glad.coping$covid_odds_ratio_50, 
+freq(dat.coping$covid_odds_ratio_50, 
      cumul = FALSE) 
@@
 ```{r}
-dat.glad.coping <- dat.glad.coping %>%
+dat.coping <- dat.coping %>%
   mutate(
@@
 
-dat.glad.coping %>%
+dat.coping %>%
   freq(covid_probable_case_incl_screening, 

### 2020-08-14 PANCHANGE_data_preprocessing2020-07-15.Rmd
Finished adapting respiratory section. Confirmed the script runs fully for NBR cohort.

@@
 GLAD = FALSE
-EDGI = TRUE
-NBR = FALSE
+EDGI = FALSE
+NBR = TRUE
 RAMP = FALSE
@@
     mhd.type_psychosis_psychotic_illness = demographics.psychosis_type_psychotic_illness, # word type psychosis changed order compared to GLAD 
-#    mhd.personality_disorder_diagnosed = demographics.personality_disorder_diagnosed, # does not exist in EDGI because it is multiple choice in EDGI
+#    mhd.personality_disorder_diagnosed = demographics.personality_disorder, # does not exist in EDGI because it is multiple choice in EDGI
     mhd.posttraumatic_stress_disorder_ptsd = demographics.posttraumatic_stress_disorder_ptsd,
     mhd.autism_aspergers_or_autistic_spectrum_disorder = demographics.autism_spectrum_disorder_asd, # different name in EDGI
+    mhd.body_dysmorphic_disorder_bdd = demographics.body_dysmorphic_disorder,
+    mhd.personality_disorder = demographics.personality_disorder, # routing variable in EDGI is named differently; renamed here to match GLAD
     ) %>%
@@
 *Note that the COPING NBR OCI-R ID numbers are stored under recipientFirstName (rather than ExternalDataReference)
+
+++MD: One NBR ID is being converted to NA by the as.numeric(ID) line of code.
 ```{r coping nbr ocir cleaning}
@@
 
+```{r coping glad respiratory copy}
+if(GLAD == TRUE){
+respiratory.raw.id <- coping.glad.respiratory.raw.id
+}
+```
+
 ## EDGI respiratory
@@
 
+```{r coping edgi respiratory copy}
+if(EDGI == TRUE){
+respiratory.raw.id <- coping.edgi.respiratory.raw.id
+}
+```
+
+## NBR respiratory
+```{r nbr coping respiratory cols}
+if(NBR == TRUE){
+coping.nbr.respiratory.raw <- readRDS(file = paste0(data.raw_path, "/nbr/respiratory_coping_nbr.rds"))
+dim(coping.nbr.respiratory.raw)
+colnames(coping.nbr.respiratory.raw)
+}
+```
+
+Select respiratory variables
+```{r coping nbr respiratory cleaning}
+if(NBR == TRUE){
+coping.nbr.respiratory.raw.id <- coping.nbr.respiratory.raw %>%
+  drop_na(subjectid) %>% # Drop NAs
+  distinct(subjectid, .keep_all = TRUE) %>% # Remove duplicates based on ID
+  separate(subjectid, into = c("Sample", "ID.intm"), sep = 6) %>% # Split ID in Sample and Number
+  separate(ID.intm, into = "ID", sep = 7) %>%
+  mutate(ID = as.numeric(ID)) %>%
+  select(
+    Sample, # Sample
+    ID, # ID
+    respiratory.breath_diarrhoea_fatigue_fever = respiratory.unusual_shortness_breath_diarrhoea,
+    respiratory.worst_ill_feel,
+    respiratory.persistent_cough,
+    respiratory.skipping_meals_because_you_felt_unwell,
+    respiratory.was_your_sense_of_smell_impaired,
+    respiratory.was_your_sense_of_taste_impaired,
+    respiratory.feeling_tiredfatigued,
+    respiratory.throat_swab_coronavirus_nose,
+    respiratory.throat_swab_test_nose,
+    respiratory.coronavirus_antibody_test,
+    respiratory.results_antibody_test
+  ) %>%
+  add_numeric(., exclude = exclude_cols) %>%
+  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
+  mutate_if(is.numeric, ~na_if(., -99)) %>%
+  mutate_if(is.numeric, ~na_if(., -77)) %>%
+  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
+  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
+
+# Inspect dimensions
+dim(coping.nbr.respiratory.raw.id)
+# Inspect colnames
+colnames(coping.nbr.respiratory.raw.id)
+#Differences
+dim(coping.nbr.respiratory.raw)[1]-dim(coping.nbr.respiratory.raw.id)[1]
+}
+```
+
+```{r coping nbr respiratory copy}
+if(NBR == TRUE){
+respiratory.raw.id <- coping.nbr.respiratory.raw.id
+}
+```
+
+## RAMP respiratory
+```{r ramp coping respiratory cols}
+if(RAMP == TRUE){
+ramp.respiratory.raw <- readRDS(file = paste0(data.raw_path, "/ramp/respiratory_coping_ramp.rds"))
+dim(ramp.respiratory.raw)
+colnames(ramp.respiratory.raw)
+}
+```
+
+Select respiratory variables
+```{r coping ramp respiratory cleaning}
+if(RAMP == TRUE){
+ramp.respiratory.raw.id <- ramp.respiratory.raw %>%
+  drop_na(externalDataReference) %>% # Drop NAs
+  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
+  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
+  mutate(ID = as.numeric(ID)) %>%
+  select(
+    Sample, # Sample
+    ID, # ID
+    respiratory.breath_diarrhoea_fatigue_fever,
+    respiratory.worst_ill_feel,
+    respiratory.persistent_cough,
+    respiratory.skipping_meals_because_you_felt_unwell,
+    respiratory.was_your_sense_of_smell_impaired,
+    respiratory.was_your_sense_of_taste_impaired,
+    respiratory.feeling_tiredfatigued,
+    respiratory.throat_swab_coronavirus_nose,
+    respiratory.throat_swab_test_nose,
+    respiratory.coronavirus_antibody_test,
+    respiratory.results_antibody_test
+  ) %>%
+  add_numeric(., exclude = exclude_cols) %>%
+  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
+  mutate_if(is.numeric, ~na_if(., -99)) %>%
+  mutate_if(is.numeric, ~na_if(., -77)) %>%
+  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
+  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
+
+# Inspect dimensions
+dim(ramp.respiratory.raw.id)
+# Inspect colnames
+colnames(ramp.respiratory.raw.id)
+#Differences
+dim(ramp.respiratory.raw)[1]-dim(ramp.respiratory.raw.id)[1]
+}
+```
+
+```{r ramp respiratory copy}
+if(RAMP == TRUE){
+respiratory.raw.id <- ramp.respiratory.raw.id
+}
+```
+
 #Distribution of likert scale COVID-19 symptoms in COPING
@@
 #persistent cough
-coping.glad.respiratory.raw.id %>%
+respiratory.raw.id %>%
   ggplot(
@@
 #severe fatigue
-coping.glad.respiratory.raw.id %>%
+respiratory.raw.id %>%
   ggplot(
@@
 #skipped meals
-coping.glad.respiratory.raw.id %>%
+respiratory.raw.id %>%
   ggplot(
@@
 percentage_pcough    # 0.3029762% of Menni et al(2020) have fatigue
-quantile(x = coping.glad.respiratory.raw.id$respiratory.persistent_cough_numeric, 
+quantile(x = respiratory.raw.id$respiratory.persistent_cough_numeric, 
          na.rm = TRUE, 
@@
 percentage_fatigue   # 0.08791204% of Menni et al(2020) have fatigue
-quantile(x = coping.glad.respiratory.raw.id$respiratory.feeling_tiredfatigued_numeric, 
+quantile(x = respiratory.raw.id$respiratory.feeling_tiredfatigued_numeric, 
          na.rm = TRUE, 
@@
 percentage_skipped_meals    # 0.192021% of Menni et al(2020) have fatigue
-quantile(x = coping.glad.respiratory.raw.id$respiratory.skipping_meals_because_you_felt_unwell_numeric, 
+quantile(x = respiratory.raw.id$respiratory.skipping_meals_because_you_felt_unwell_numeric, 
          na.rm = TRUE, 
@@
 #loss or smell or taste
-coping.glad.respiratory.raw.id <- coping.glad.respiratory.raw.id %>%
+respiratory.raw.id <- respiratory.raw.id %>%
   mutate(
@@
 #persistent cough
-coping.glad.respiratory.raw.id <- coping.glad.respiratory.raw.id %>%
+respiratory.raw.id <- respiratory.raw.id %>%
   mutate(
@@
 #fatigue
-coping.glad.respiratory.raw.id <- coping.glad.respiratory.raw.id %>%
+respiratory.raw.id <- respiratory.raw.id %>%
   mutate(
@@
 #skipped meals
-coping.glad.respiratory.raw.id <- coping.glad.respiratory.raw.id %>%
+respiratory.raw.id <- respiratory.raw.id %>%
   mutate(
@@
 ```{r frequencies of COVID binary symptoms}
-freq(coping.glad.respiratory.raw.id$respiratory.anosmia_binary)
-freq(coping.glad.respiratory.raw.id$respiratory.pcough_binary)
-freq(coping.glad.respiratory.raw.id$respiratory.fatigue_binary)
-freq(coping.glad.respiratory.raw.id$respiratory.skipped_meals_binary)
+freq(respiratory.raw.id$respiratory.anosmia_binary)
+freq(respiratory.raw.id$respiratory.pcough_binary)
+freq(respiratory.raw.id$respiratory.fatigue_binary)
+freq(respiratory.raw.id$respiratory.skipped_meals_binary)
 ```
@@
 Rename respiratory dataset joined to main dataset
+
+++MD: Do we want to name the RAMP dataset something different, if the algorithm will need to be changed because they have categorical age and gender not sex?
+(otherwise can remove the if statement and rename the dataset 'dat.full' instead of dat.coping)
 ```{r clean respiratory dataset}
-coping.glad.respiratory <- coping.glad.respiratory.raw.id
+if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE){
+respiratory <- respiratory.raw.id
 
@@
   x = dat,
-  y = coping.glad.respiratory,
+  y = respiratory,
   by = "ID"
 )
+}
 ```
@@
 
-```{r how many people expereinced all symptoms}
+```{r how many people experinced all symptoms}
 dat.coping <- dat.coping %>%
@@
 Probable COVID case including the routing question
-```{r}
+```{r recoding probable covid to account for screening question}
 dat.coping <- dat.coping %>%

### 2020-08-17 PANCHANGE_data_preprocessing2020-07-15.Rmd

@@
 GLAD = FALSE
-EDGI = FALSE
-NBR = TRUE
+EDGI = TRUE
+NBR = FALSE
 RAMP = FALSE
@@
     mhd.type_psychosis_psychotic_illness = demographics.psychosis_type_psychotic_illness, # word type psychosis changed order compared to GLAD 
-#    mhd.personality_disorder_diagnosed = demographics.personality_disorder, # does not exist in EDGI because it is multiple choice in EDGI
+    mhd.personality_disorder_diagnosed = demographics.diagnosed_personality_disorder, # named differently in EDGI
     mhd.posttraumatic_stress_disorder_ptsd = demographics.posttraumatic_stress_disorder_ptsd,
@@
     mhd.personality_disorder = demographics.personality_disorder, # routing variable in EDGI is named differently; renamed here to match GLAD
+    mhd.attention_deficit_hyperactivity_disorder = demographics.attention_deficit_hyperactivity_disorder
     ) %>%

### 2020-08-17 PANCHANGE_data_preprocessing2020-07-15.Rmd
commit so I can push

--- 2020-08-14 PANCHANGE_data_preprocessing2020-07-15.Rmd
@@
 GLAD = FALSE
-EDGI = TRUE
+EDGI = FALSE
 NBR = FALSE
-RAMP = FALSE
+RAMP = TRUE
 ```
@@
 ```{r Age groups}
-if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE ) {
+if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE) {
 # Create categorical age groups per 10 years
@@
   freq(age_category_full)
-
+}
 ```
@@
 
+# Columns to exclude from add_numeric
+
+```{r cols to exclude}
+exclude_cols <- c("Sample",
+                  "ID")
+```
+
 # mhd
@@
     mhd.obsessive_compulsive_related_disorders = demographics.obsessive_compulsive_related_disorders,
+    mhd.body_dysmorphic_disorder_bdd = demographics.body_dysmorphic_disorder,
     mhd.mania_hypomania_bipolar_or_manicdepression = demographics.mania_hypomania_bipolar_or_manicdepression,
@@
     mhd.bulimia_nervosa_unc = mhd.bulimia_nervosa,
-    mhd.bingeeating_disorder_unc = mhd.bingeeating_disorder
+    mhd.psychological_overeating_or_bingeeating_unc = mhd.psychological_overeating_or_bingeeating
   ) %>%
   add_column(
-    mhd.schizoaffective_disorder = NA #NBR doesn't ask about schizoaffective disorder. This means the column das not exist in the data set
-  ) %>% 
+    mhd.schizoaffective_disorder = NA, #NBR doesn't ask about schizoaffective disorder. This means the column das not exist in the data set
+    mhd.schizoaffective_disorder_numeric = NA
+  )
   add_numeric(., exclude = exclude_cols) %>%
@@
 if(NBR == TRUE) {
-#Recode as 0 if ppt responds no to screening question (mhd.suspected_eating_disorder_diagnosed_numeric)
+#Recode as 0 if ppt respnds no to screening question (mhd.suspected_eating_disorder_diagnosed_numeric)
 mhd.raw.id <- mhd.raw.id %>%
@@
       case_when(mhd.suspected_eating_disorder_diagnosed_numeric == "0" ~ 0,
-                mhd.bingeeating_disorder_unc_numeric == "0" ~ 0,
-                mhd.bingeeating_disorder_unc_numeric == "1" ~ 1),
-    mhd.anorexia_nervosa =
-      case_when(mhd.suspected_eating_disorder_diagnosed_numeric == "0" ~ "Not Anorexia nervosa",
-                mhd.anorexia_nervosa_unc_numeric == "0" ~ "Not Anorexia nervosa",
-                mhd.anorexia_nervosa_unc_numeric == "1" ~ "Anorexia nervosa"),
-    mhd.atypical_anorexia_nervosa =
-      case_when(mhd.suspected_eating_disorder_diagnosed_numeric == "0" ~ "Not Atypical anorexia nervosa",
-                mhd.atypical_anorexia_nervosa_unc_numeric == "0" ~ "Not Atypical anorexia nervosa",
-                mhd.atypical_anorexia_nervosa_unc_numeric == "1" ~ "Atypical anorexia nervosa"),
-    mhd.bulimia_nervosa =
-      case_when(mhd.suspected_eating_disorder_diagnosed_numeric == "0" ~ "Not Bulimia nervosa",
-                mhd.bulimia_nervosa_unc_numeric == "0" ~ "Not Bulimia nervosa",
-                mhd.bulimia_nervosa_unc_numeric == "1" ~ "Bulimia nervosa"),
-    mhd.bingeeating_disorder =
-      case_when(mhd.suspected_eating_disorder_diagnosed_numeric == "0" ~ "Not Binge-eating disorder",
-                mhd.bingeeating_disorder_unc_numeric == "0" ~ "Not Binge-eating disorder",
-                mhd.bingeeating_disorder_unc_numeric == "1" ~ "Binge-eating disorder")
+                mhd.bingeeating_disorder_numeric == "0" ~ 0,
+                mhd.bingeeating_disorder_numeric == "1" ~ 1)
     )
@@
       recode_factor(obsessive_compulsive_disorders_numeric,
-                    "0" = "No obsessive compulsive disorder",
+                    "0" = "No obsessivecompulsive disorder",
                     "1" = "Obsessive compulsive disorder",
@@
     )
-```
-
-# Columns to exclude from add_numeric
-
-```{r cols to exclude}
-exclude_cols <- c("Sample",
-                  "ID")
+}
+```
+
+```{r mhd categories}
+if(EDGI == TRUE) {
+mhd.raw.categories <- mhd.raw.id %>%
+  select(
+    Sample,
+    ID,
+    anxiety_disorders_numeric,
+    anxiety_disorders,
+    mhd.specific_phobia_e.g._phobia_of_flying_numeric,
+    mhd.specific_phobia_e.g._phobia_of_flying,
+    mhd.social_anxiety_or_social_phobia_numeric,
+    mhd.social_anxiety_or_social_phobia,
+    agoraphobia_panic_disorder_numeric,
+    agoraphobia_panic_disorder,
+    depressive_disorders_numeric,
+    depressive_disorders,
+    eating_disorders_numeric,
+    eating_disorders,
+    obsessive_compulsive_disorders_numeric,
+    obsessive_compulsive_disorders,
+    psychotic_disorders_numeric,
+    psychotic_disorders,
+    mhd.mania_hypomania_bipolar_or_manicdepression_numeric,
+    mhd.mania_hypomania_bipolar_or_manicdepression,
+    mhd.posttraumatic_stress_disorder_ptsd_numeric,
+    mhd.posttraumatic_stress_disorder_ptsd,
+    mhd.autism_aspergers_or_autistic_spectrum_disorder_numeric,
+    mhd.autism_aspergers_or_autistic_spectrum_disorder,
+    mhd.attention_deficit_hyperactivity_disorder_numeric,
+    mhd.attention_deficit_hyperactivity_disorder,
+    mhd.personality_disorder_numeric,
+    mhd.personality_disorder,
+#    personality_cluster_a_numeric,
+#    personality_cluster_a,
+#    personality_cluster_b_numeric,
+#    personality_cluster_b,
+#    personality_cluster_c_numeric,
+#    personality_cluster_c,
+    depression_and_anxiety_numeric,
+    depression_and_anxiety,
+    restricting_vs_binge_eating_eating_disorders_numeric,
+    restricting_vs_binge_eating_eating_disorders,
+    bipolar_and_schizophrenia_numeric,
+    bipolar_and_schizophrenia,
+    control_numeric,
+    control,
+    disorders_total_count,
+    comorbidity_total_count_numeric,
+    comorbidity_total_count_factor_numeric,
+    comorbidity_total_count_factor
+    ) %>%
+  add_column(
+    personality_cluster_a_numeric = NA_real_,
+    personality_cluster_a = NA_real_,
+    personality_cluster_b_numeric = NA_real_,
+    personality_cluster_b = NA_real_,
+    personality_cluster_c_numeric = NA_real_,
+    personality_cluster_c = NA_real_,    
+  )
+}
 ```
@@
     ) %>% 
+    select(
+      Sample, # Sample
+      ID, # ID
+      startDate.coping = startDate, # Rename startDate
+      gad.problems_made_difficult_care = gad.care_difficult_home_things, # Impairment (different to GLAD)
+      gad.pandemic_felt_feelings = gad.pandemic_feelings_felt, # Comparison to before the pandemic (retro; different to GLAD)
+      gad.feeling_nervous_anxious_or_on_edge_retro = gad.feeling_nervous_anxious_or_on_edge,
+      gad.control_worrying_stop_retro = gad.control_worrying_stop,
+      gad.worrying_too_much_about_different_things_retro = gad.worrying_too_much_about_different_things,
+      gad.trouble_relaxing_retro = gad.trouble_relaxing,
+      gad.sit_restless_hard_retro = gad.sit_restless_hard,
+      gad.becoming_easily_annoyed_or_irritable_retro = gad.becoming_easily_annoyed_or_irritable,
+      gad.awful_feeling_afraid_happen_retro = gad.feeling_afraid_awful_happen, # different to GLAD: gad.awful_feeling_afraid_happen,
+      gad.feeling_nervous_anxious_or_on_edge_base = gad.feeling_nervous_anxious_or_on_edge.1,
+      gad.control_worrying_stop_base = gad.control_worrying_stop.1,
+      gad.worrying_too_much_about_different_things_base = gad.worrying_too_much_about_different_things.1,
+      gad.trouble_relaxing_base = gad.trouble_relaxing.1,
+      gad.sit_restless_hard_base = gad.sit_restless_hard.1,
+      gad.becoming_easily_annoyed_or_irritable_base = gad.becoming_easily_annoyed_or_irritable.1,
+      gad.awful_feeling_afraid_happen_base = gad.feeling_afraid_awful_happen.1 # different to GLAD: gad.awful_feeling_afraid_happen.1
+    ) %>%
+    add_numeric(., exclude = exclude_cols_coping_edgi) %>%
+    mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
+    mutate_if(is.numeric, ~na_if(., -99)) %>%
+    mutate_if(is.numeric, ~na_if(., -77)) %>%
+    mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
+    mutate_if(is.factor, ~na_if(., "Don't know")) %>%
+    mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
+    mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
+    mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
+    mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
+    mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
+    mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
+
+  # Inspect dimensions
+  dim(coping.edgi.gad.raw.id)
+  # Inspect colnames
+  colnames(coping.edgi.gad.raw.id)
+  #Differences
+  dim(coping.edgi.gad.raw)[1]-dim(coping.edgi.gad.raw.id)[1]
+}
+```
+
+```{r coping edgi gad copy}
+if(EDGI == TRUE) {
+  coping.gad.raw.id <- coping.edgi.gad.raw.id
+}
+```
+
+## NBR
+```{r coping nbr gad cols}
+if(NBR == TRUE) {
+  coping.nbr.gad.raw <- readRDS(file = paste0(data.raw_path,"/nbr/gad_coping_nbr.rds"))
+  dim(coping.nbr.gad.raw)
+  colnames(coping.nbr.gad.raw)
+}
+```
+
+```{r coping nbr gad summary}
+if(NBR == TRUE) {
+  summarytools::dfSummary(
+    coping.nbr.gad.raw,
+    graph.col = F,
+    valid.col = F,
+    labels.col = F
+  )
+}
+```
+
+```{r coping nbr gad cleaning}
+if(NBR == TRUE) {
+  exclude_cols_coping_nbr <- c(
+    "Sample",
+    "ID",
+    "startDate.coping"
+  )
+
+  coping.nbr.gad.raw.id <- coping.nbr.gad.raw %>%
+  drop_na(subjectid) %>% # Drop NAs
+  distinct(subjectid, .keep_all = TRUE) %>% # Remove duplicates based on ID
+  separate(subjectid, into = c("Sample", "ID.intm"), sep = 6) %>% # Split ID in Sample and Number
+  separate(ID.intm, into = "ID", sep = 7) %>%
+  mutate(ID = as.numeric(ID)) %>% 
     select(
@@
       gad.awful_feeling_afraid_happen_base = gad.awful_feeling_afraid_happen.1
-    ) %>%
-    add_numeric(., exclude = exclude_cols_coping_edgi) %>%
-    mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
-    mutate_if(is.numeric, ~na_if(., -99)) %>%
-    mutate_if(is.numeric, ~na_if(., -77)) %>%
-    mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
-    mutate_if(is.factor, ~na_if(., "Don't know")) %>%
-    mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
-    mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
-    mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
-    mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
-    mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
-    mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
-
-  # Inspect dimensions
-  dim(coping.edgi.gad.raw.id)
-  # Inspect colnames
-  colnames(coping.edgi.gad.raw.id)
-  #Differences
-  dim(coping.edgi.gad.raw)[1]-dim(coping.edgi.gad.raw.id)[1]
-}
-```
-
-```{r coping edgi gad copy}
-if(EDGI == TRUE) {
-  coping.gad.raw.id <- coping.edgi.gad.raw.id
-}
-```
-
-## NBR
-```{r coping nbr gad cols}
-if(NBR == TRUE) {
-  coping.nbr.gad.raw <- readRDS(file = paste0(data.raw_path,"/nbr/gad_coping_nbr.rds"))
-  dim(coping.nbr.gad.raw)
-  colnames(coping.nbr.gad.raw)
-}
-```
-
-```{r coping nbr gad summary}
-if(NBR == TRUE) {
-  summarytools::dfSummary(
-    coping.nbr.gad.raw,
-    graph.col = F,
-    valid.col = F,
-    labels.col = F
-  )
-}
-```
-
-```{r coping nbr gad cleaning}
-if(NBR == TRUE) {
-  exclude_cols_coping_nbr <- c(
-    "Sample",
-    "ID",
-    "startDate.coping"
-  )
-
-  coping.nbr.gad.raw.id <- coping.nbr.gad.raw %>%
-  drop_na(subjectid) %>% # Drop NAs
-  distinct(subjectid, .keep_all = TRUE) %>% # Remove duplicates based on ID
-  separate(subjectid, into = c("Sample", "ID.intm"), sep = 6) %>% # Split ID in Sample and Number
-  separate(ID.intm, into = "ID", sep = 7) %>%
-  mutate(ID = as.numeric(ID)) %>% 
-    select(
-      Sample, # Sample
-      ID, # ID
-      startDate.coping = startDate, # Rename startDate
-      gad.problems_made_difficult_care = gad.problems_made_care_difficult, # Impairment (different from GLAD)
-      gad.pandemic_felt_feelings, # Comparison to before the pandemic (retro)
-      gad.feeling_nervous_anxious_or_on_edge_retro = gad.feeling_nervous_anxious_or_on_edge,
-      gad.control_worrying_stop_retro = gad.control_worrying_stop,
-      gad.worrying_too_much_about_different_things_retro = gad.worrying_too_much_about_different_things,
-      gad.trouble_relaxing_retro = gad.trouble_relaxing,
-      gad.sit_restless_hard_retro = gad.sit_restless_hard,
-      gad.becoming_easily_annoyed_or_irritable_retro = gad.becoming_easily_annoyed_or_irritable,
-      gad.awful_feeling_afraid_happen_retro = gad.feeling_afraid_awful_happen, #Different from GLAD
-      gad.feeling_nervous_anxious_or_on_edge_base = gad.feeling_nervous_anxious_or_on_edge.1,
-      gad.control_worrying_stop_base = gad.control_worrying_stop.1,
-      gad.worrying_too_much_about_different_things_base = gad.worrying_too_much_about_different_things.1,
-      gad.trouble_relaxing_base = gad.trouble_relaxing.1,
-      gad.sit_restless_hard_base = gad.sit_restless_hard.1,
-      gad.becoming_easily_annoyed_or_irritable_base = gad.becoming_easily_annoyed_or_irritable.1,
-      gad.awful_feeling_afraid_happen_base = gad.feeling_afraid_awful_happen.1 #Different from GLAD
     ) %>%
@@
 
-```{r coping gad base sum score if missing items set to NA}
+```{r coping gad base sum score if missigng items set to NA}
 coping.gad.raw.id <- coping.gad.raw.id %>%
@@
 
-```{r coping gad retro sum score if missing items set to NA}
+```{r coping gad retro sum score if missigng items set to NA}
 coping.gad.raw.id <- coping.gad.raw.id %>%
@@
 
-```{r coping pcl base sum score if missing items set to NA}
+```{r coping pcl base sum score if missigng items set to NA}
 coping.pcl.raw.id <- coping.pcl.raw.id %>%
@@
 
-```{r coping pcl retro sum score if missing items set to NA}
+```{r coping pcl retro sum score if missigng items set to NA}
 coping.pcl.raw.id <- coping.pcl.raw.id %>%
@@
     ID, # ID
-    phq.problems_made_difficult_care = phq.problems_made_care_difficult,
+    phq.problems_made_difficult_care,
     phq.pandemic_felt_feelings,
@@
     phq.poor_appetite_or_overeating_retro = phq.poor_appetite_or_overeating,
-    phq.feeling_bad_failure_family_retro = phq.family_feeling_bad_failure,
+    phq.feeling_bad_failure_family_retro = phq.feeling_bad_failure_family,
     phq.trouble_concentrating_reading_newspaper_retro = phq.trouble_concentrating_newspaper_reading, # differ NBR prepandemic
@@
     phq.poor_appetite_or_overeating_base = phq.poor_appetite_or_overeating.1,
-    phq.feeling_bad_failure_family_base = phq.family_feeling_bad_failure.1,
+    phq.feeling_bad_failure_family_base = phq.feeling_bad_failure_family.1,
     phq.trouble_concentrating_reading_newspaper_base = phq.trouble_concentrating_newspaper_reading.1, # differ NBR prepandemic
@@
 
-```{r coping phq base sum score if missing items set to NA}
+```{r coping phq base sum score if missigng items set to NA}
 coping.phq.raw.id <- coping.phq.raw.id %>%
@@
 8 items
-```{r phq base sum score if missing items set to NA - 8 items}
+```{r phq base sum score if missigng items set to NA - 8 items}
 coping.phq.raw.id <- coping.phq.raw.id %>%
@@
 
-```{r coping phq retro sum score if missing items set to NA}
+```{r coping phq retro sum score if missigng items set to NA}
 coping.phq.raw.id <- coping.phq.raw.id %>%
@@
 8 items
-```{r phq retro sum score if missing items set to NA - 8 items}
+```{r phq retro sum score if missigng items set to NA - 8 items}
 coping.phq.raw.id <- coping.phq.raw.id %>%
@@
     ocir.arranged_things_change_upset_retro = ocir.arranged_things_change_upset,
-    ocir.repeat_feel_numbers_retro = ocir.repeat_numbers_feel, ## Different from GLAD
-    ocir.clean_simply_wash_feel_retro = ocir.feel_contaminated_clean_simply,
+    ocir.repeat_feel_numbers_retro = ocir.numbers_repeat_feel, ## Different from NBR prepandemic
+    ocir.clean_simply_wash_feel_retro = ocir.feel_contaminated_clean_simply, ## Different from NBR prepandemic
     ocir.mind_upset_unpleasant_thoughts_retro = ocir.mind_upset_unpleasant_thoughts,
     ocir.afraid_avoid_throwing_things_retro = ocir.afraid_avoid_throwing_things,
-    ocir.light_switches_water_taps_retro = ocir.water_taps_light_switches, ## Different from GLAD
+    ocir.light_switches_water_taps_retro = ocir.light_switches_water_taps,
     ocir.arranged_things_retro = ocir.arranged_things,
-    ocir.good_feel_bad_numbers_retro = ocir.bad_numbers_good_feel,
-    ocir.hands_longer_wash_retro = ocir.longer_hands_wash, 
+    ocir.good_feel_bad_numbers_retro = ocir.bad_numbers_good_feel, ## Different from NBR prepandemic
+    ocir.hands_longer_wash_retro = ocir.longer_hands_wash, ## Different from NBR prepandemic
     ocir.saved_things_retro = ocir.saved_things,
-    ocir.frequently_difficulty_rid_nasty_retro = ocir.frequently_rid_difficulty_nasty, 
+    ocir.frequently_difficulty_rid_nasty_retro = ocir.frequently_rid_difficulty_nasty, ## Different from NBR prepandemic
     ocir.i_check_things_more_often_than_necessary_retro = ocir.i_check_things_more_often_than_necessary.,
@@
     ocir.feel_compelled_count_things_retro = ocir.feel_compelled_count_things,
-    ocir.strangers_touch_touched_difficult_retro = ocir.strangers_touch_touched_object, 
-    ocir.control_difficult_find_thoughts_retro = ocir.control_difficult_thoughts_find, ## Different from GLAD 
-    ocir.i_collect_things_i_dont_need_retro = ocir.i_collect_things_i_dont_need., 
+    ocir.strangers_touch_touched_difficult_retro = ocir.strangers_touch_touched_object, ## Different from NBR prepandemic
+    ocir.control_difficult_find_thoughts_retro = ocir.control_find_difficult_thoughts, ## Different from NBR prepandemic
+    ocir.i_collect_things_i_dont_need_retro = ocir.i_collect_things_i_dont_need., ## Different from NBR prepandemic
     ocir.i_repeatedly_check_doors_windows_drawers_etc_base = ocir.i_repeatedly_check_doors_windows_drawers_etc..1,
     ocir.arranged_things_change_upset_base = ocir.arranged_things_change_upset.1,
-    ocir.repeat_feel_numbers_base = ocir.repeat_numbers_feel.1, ## Different from GLAD
-    ocir.clean_simply_wash_feel_base = ocir.feel_contaminated_clean_simply.1,
+    ocir.repeat_feel_numbers_base = ocir.numbers_repeat_feel.1, ## Different from NBR prepandemic
+    ocir.clean_simply_wash_feel_base = ocir.feel_contaminated_clean_simply.1, ## Different from NBR prepandemic
     ocir.mind_upset_unpleasant_thoughts_base = ocir.mind_upset_unpleasant_thoughts.1,
     ocir.afraid_avoid_throwing_things_base = ocir.afraid_avoid_throwing_things.1,
-    ocir.light_switches_water_taps_base = ocir.water_taps_light_switches.1, ## Different from GLAD
+    ocir.light_switches_water_taps_base = ocir.light_switches_water_taps.1,
     ocir.arranged_things_base = ocir.arranged_things.1,
-    ocir.good_feel_bad_numbers_base = ocir.bad_numbers_good_feel.1, 
-    ocir.hands_longer_wash_base = ocir.longer_hands_wash.1, 
+    ocir.good_feel_bad_numbers_base = ocir.bad_numbers_good_feel.1, ## Different from NBR prepandemic
+    ocir.hands_longer_wash_base = ocir.longer_hands_wash.1, ## Different from NBR prepandemic
     ocir.saved_things_base = ocir.saved_things.1,
-    ocir.frequently_difficulty_rid_nasty_base = ocir.frequently_rid_difficulty_nasty.1, 
+    ocir.frequently_difficulty_rid_nasty_base = ocir.frequently_rid_difficulty_nasty.1, ## Different from NBR prepandemic
     ocir.i_check_things_more_often_than_necessary_base = ocir.i_check_things_more_often_than_necessary..1,
@@
     ocir.feel_compelled_count_things_base = ocir.feel_compelled_count_things.1,
-    ocir.strangers_touch_touched_difficult_base = ocir.strangers_touch_touched_object.1, 
-    ocir.control_difficult_find_thoughts_base = ocir.control_difficult_thoughts_find.1,
+    ocir.strangers_touch_touched_difficult_base = ocir.strangers_touch_touched_object.1, ## Different from NBR prepandemic
+    ocir.control_difficult_find_thoughts_base = ocir.control_find_difficult_thoughts.1, ## Different from NBR prepandemic
     ocir.i_collect_things_i_dont_need_base = ocir.i_collect_things_i_dont_need..1
@@
 
-glad/edgi data frame list
-```{r glad/edgi data frame list}
-if(GLAD == TRUE | EDGI == TRUE) {
-dfs.list <- list(
+glad data frame list
+```{r glad data frame list}
+glad.dfs.list <- list(
   dem.raw.id,
@@
 )
-}
-```
-
-Removing all prepandemic dataframes from NBR/RAMP (prepandemic measures don't exist for these cohorts)
-```{r nbr/ramp data frame list}
-if(NBR == TRUE | RAMP == TRUE) {
-dfs.list <- list(
-  dem.raw.id,
-  mhd.raw.categories,
-  coping.gad.raw.id,
-  coping.pcl.raw.id,
-  coping.phq.raw.id,
-  coping.ocir.raw.id
-)
-}
-```
-
-```{r Join all questionnaires}
-dat.raw <- plyr::join_all(
-  dfs.list,
+```
+
+```{r Join all questionnaires for glad}
+dat.glad.raw <- plyr::join_all(
+  glad.dfs.list,
   by = c("ID", "Sample") # Alternatively you can join by several columns EDGI -> "Age", "Sex", "Birthyear"
@@
 #look at the data
-skimr::skim(dat.raw)
+skimr::skim(dat.glad.raw)
 ```
@@
 +++KT: No duplicates identified by ID in GLAD. 
-+++MD: Duplicates have been removed in cleaning script for NBR. No duplicates at this stage.
-```{r Check duplicates}
-dat.raw$ID.dup <- duplicated(dat.raw$ID)
-
-summary(as.factor(dat.raw$ID.dup))
-
-dat.dup <- dat.raw %>%
+```{r glad Check duplicates}
+dat.glad.raw$ID.dup <- duplicated(dat.glad.raw$ID)
+
+summary(as.factor(dat.glad.raw$ID.dup))
+
+dat.dup <- dat.glad.raw %>%
   filter(ID.dup == TRUE)
 
-dat.raw.no.dup <- dat.raw %>%
+dat.glad.raw.no.dup <- dat.glad.raw %>%
   filter(ID.dup == FALSE)
@@
 ```{r Exclude participants that do not report sex}
-dim(dat.raw)
-dat.no.sex <- dat.raw %>%
+dim(dat.glad.raw)
+dat.no.sex <- dat.glad.raw %>%
   drop_na(Sex)
@@
 
-dim(dat.raw)[1]-dim(dat.no.sex)[1]
+dim(dat.glad.raw)[1]-dim(dat.no.sex)[1]
 ```
@@
 Exclusion of inflammatory bowel disease (IBD) BioResource (BR) cohort
-++MD: 3,410 participants from NBR IBD cohort excluded
 ```{r COVID exclusion of IBD}
-if(NBR == TRUE) {
-dim(dat.no.sex.no.gender.no.age)
-
-dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age %>%
-  filter(Cohort != "IBD")
-
-dim(dat.no.sex.no.gender.no.age.no.ibd)
-dim(dat.no.sex.no.gender.no.age)[1]-dim(dat.no.sex.no.gender.no.age.no.ibd)[1]
-}
-
-if(GLAD == TRUE | EDGI == TRUE | RAMP == TRUE) {
+#dim(dat.no.sex.no.age)
+#
+#dat.no.sex.no.age <- dat.no.sex.no.age %>%
+#  filter(NBR.IBD == 0)
+#
+#dim(dat.no.sex.no.age.no.ibd)
+#
+#dim(dat.no.sex.no.age)[1]-dim(dat.no.sex.no.age.no.ibd)[1]
+
 dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age
-}
 ```
@@
 ```{r Tidy data}
-dat <- dat.no.sex.no.gender.no.age.no.ibd
-
-skimr::skim(dat)
+dat.glad <- dat.no.sex.no.gender.no.age.no.ibd
+
+skimr::skim(dat.glad)
 ```
@@
 ```{r Prepandemic definitions january_31}
-if(GLAD == TRUE | EDGI == TRUE){
-dat <- dat %>%
+dat.glad <- dat.glad %>%
   mutate(
@@
 
-dat <- dat %>%
+dat.glad <- dat.glad %>%
   mutate(
@@
 
-dat %>%
+dat.glad %>%
   freq(prepandemic_january_31)
-}
 ```
@@
 ```{r Prepandemic definitions march_1}
-if(GLAD == TRUE | EDGI == TRUE){
-dat <- dat %>%
+dat.glad <- dat.glad %>%
   mutate(
@@
 
-dat %>%
+dat.glad %>%
   freq(prepandemic_march_1)
-}
 ```
@@
 ```{r Prepandemic definitions march_23}
-if(GLAD == TRUE | EDGI == TRUE){
-dat <- dat %>%
+dat.glad <- dat.glad %>%
   mutate(
@@
 
-dat %>%
+dat.glad %>%
   freq(prepandemic_march_23)
-}
 ```
@@
 ```{r time difference between sign up questionnaire and COPING questionnaire}
-if(GLAD == TRUE | EDGI == TRUE){
-dat <- dat %>%
+dat.glad <- dat.glad %>%
   mutate(
@@
 
-dat %>%
+dat.glad %>%
   descr(
@@
     )
-}
 ```
@@
 Proportion of people signed up over one year ago
-```{r glad/edgi ppts signed up over one year ago, eval=FALSE, include=FALSE}
-if(GLAD == TRUE | EDGI == TRUE){
-dat <- dat %>%
+```{r eval=FALSE, include=FALSE}
+dat.glad <- dat.glad %>%
   mutate(
@@
 
-dat %>%
+dat.glad %>%
   freq(over_one_year_time_diff_sign_up_coping, cumul = F)
-}
-```
-
-Proportion of people signed up over half a year ago
-```{r glad/edgi ppts signed up over half a year ago, r eval=FALSE, include=FALSE}
-if(GLAD == TRUE | EDGI == TRUE){
-dat <- dat %>%
+```
+
+Proportion of people signed up over one year ago
+```{r eval=FALSE, include=FALSE}
+dat.glad <- dat.glad %>%
   mutate(
@@
 
-dat %>%
+dat.glad %>%
   freq(over_half_a_year_time_diff_sign_up_coping, cumul = F)
-}
 ```
@@
 ```{r phq difference scores}
-if(GLAD == TRUE | EDGI == TRUE){
 # Difference score for prepandemic and retrospective phq sum scores
-dat <- dat %>%
+dat.glad <- dat.glad %>%
   mutate(
@@
 
-summary(dat$phq.diff_score_prepan_retro)
+summary(dat.glad$phq.diff_score_prepan_retro)
 
 # Difference score for prepandemic and baseline phq sum scores
-dat <- dat %>%
+dat.glad <- dat.glad %>%
   mutate(
@@
 
-summary(dat$phq.diff_score_prepan_base)
-}
+summary(dat.glad$phq.diff_score_prepan_base)
+
 # Difference score for retrospective and baseline phq sum scores
-dat <- dat %>%
+dat.glad <- dat.glad %>%
   mutate(
@@
 
-summary(dat$phq.diff_score_base_retro)
+summary(dat.glad$phq.diff_score_base_retro)
 
@@
 ```{r gad difference scores}
-if(GLAD == TRUE | EDGI == TRUE){
 # Difference score for prepandemic and retrospective gad sum scores
-dat <- dat %>%
+dat.glad <- dat.glad %>%
   mutate(
@@
 
-summary(dat$gad.diff_score_prepan_retro)
+summary(dat.glad$gad.diff_score_prepan_retro)
 
 # Difference score for prepandemic and baseline gad sum scores
-dat <- dat %>%
+dat.glad <- dat.glad %>%
   mutate(
@@
 
-summary(dat$gad.diff_score_prepan_base)
-}
+summary(dat.glad$gad.diff_score_prepan_base)
+
 # Difference score for retrospective and baseline gad sum scores
-dat <- dat %>%
+dat.glad <- dat.glad %>%
   mutate(
@@
 
-summary(dat$gad.diff_score_base_retro)
+summary(dat.glad$gad.diff_score_base_retro)
 
@@
 ```{r pcl difference scores}
-if(GLAD == TRUE | EDGI == TRUE){
 # Difference score for prepandemic and baseline pcl sum scores
-dat <- dat %>%
+dat.glad <- dat.glad %>%
   mutate(
@@
 
-summary(dat$pcl.diff_score_prepan_base)
-}
+summary(dat.glad$pcl.diff_score_prepan_base)
 ```
@@
 ```{r frequency of those who reported "due to pandemic" in retro PCL}
-summary(dat$pcl.sum_score_retro)
-
-freq(dat$pcl.stressful_experience_repeated_images_retro)
-freq(dat$pcl.stressful_situation_avoiding_activities_retro)
-freq(dat$pcl.feeling_irritable_or_having_angry_outbursts_retro)
-freq(dat$pcl.stressful_experience_upset_reminded_retro)
-freq(dat$pcl.cut_people_feeling_distant_retro)
-freq(dat$pcl.difficulty_concentrating_retro)
+summary(dat.glad$pcl.sum_score_retro)
+
+freq(dat.glad$pcl.stressful_experience_repeated_images_retro)
+freq(dat.glad$pcl.stressful_situation_avoiding_activities_retro)
+freq(dat.glad$pcl.feeling_irritable_or_having_angry_outbursts_retro)
+freq(dat.glad$pcl.stressful_experience_upset_reminded_retro)
+freq(dat.glad$pcl.cut_people_feeling_distant_retro)
+freq(dat.glad$pcl.difficulty_concentrating_retro)
 ```
@@
 ```{r ocir difference scores}
-if(GLAD == TRUE | EDGI == TRUE){
 # Difference score for prepandemic and retrospective oci-r sum scores
-dat <- dat %>%
+dat.glad <- dat.glad %>%
   mutate(
@@
 
-summary(dat$ocir.diff_score_prepan_retro)
+summary(dat.glad$ocir.diff_score_prepan_retro)
 
 # Difference score for prepandemic and baseline ocir sum scores
-dat <- dat %>%
+dat.glad <- dat.glad %>%
   mutate(
@@
 
-summary(dat$ocir.diff_score_prepan_base)
-}
+summary(dat.glad$ocir.diff_score_prepan_base)
+
 # Difference score for retrospective and baseline ocir sum scores
-dat <- dat %>%
+dat.glad <- dat.glad %>%
   mutate(
@@
 
-summary(dat$ocir.diff_score_base_retro)
+summary(dat.glad$ocir.diff_score_base_retro)
 
@@
 Identify which data (prepan, retro and baseline) each participant has.
-```{r glad/edgi data level groups PHQ}
-if(GLAD == TRUE | EDGI == TRUE){
-dat <- dat %>%
+```{r data level groups PHQ}
+dat.glad <- dat.glad %>%
   mutate(
@@
 
-table(dat$data_group_phq)
-}
-```
-
-```{r nbr/ramp data level groups PHQ}
-if(NBR == TRUE | RAMP == TRUE){
-dat <- dat %>%
-  mutate(
-    data_group_phq_numeric =
-      case_when(
-#        na_per_person_phq_base == 0 & na_per_person_phq_prepan == 0 & na_per_person_phq_retro == 0 ~ 5, #all complete baseline, prepan and retro
-        na_per_person_phq_base != 0 & na_per_person_phq_retro == 0  ~ 4, #retro data only
-        na_per_person_phq_base == 0 & na_per_person_phq_retro != 0  ~ 3, #baseline data only
-#        na_per_person_phq_base == 0 & na_per_person_phq_prepan == 0 & na_per_person_phq_retro != 0  ~ 2, #prepan and baseline data only
-        na_per_person_phq_base == 0 & na_per_person_phq_retro == 0 ~ 1,  #baseline and retro data only
-#        na_per_person_phq_base != 0 & na_per_person_phq_prepan == 0 & na_per_person_phq_retro != 0  ~ 0  #prepan data only
-      )
-  )
-
-dat <- dat %>%
-  mutate(
-    data_group_phq = 
-      recode_factor(
-        data_group_phq_numeric,
-        "0" = "Only prepandemic data",
-        "1" = "Baseline and retrospective data",
-        "2" = "Prepandemic and baseline data",
-        "3" = "Baseline data only",
-        "4" = "Retrospective data only",
-        "5" = "All prepandemic, baseline and retrospective data"
-      )
-  )
-
-table(dat$data_group_phq)
-}
+table(dat.glad$data_group_phq)
 ```
@@
 GAD
-```{r glad/edgi data level groups GAD}
-if(GLAD == TRUE | EDGI == TRUE){
-dat <- dat %>%
+```{r data level groups GAD}
+dat.glad <- dat.glad %>%
   mutate(
@@
 
-table(dat$data_group_gad)
-}
-```
-
-```{r nbr/ramp data level groups GAD}
-if(NBR == TRUE | RAMP == TRUE){
-dat <- dat %>%
-  mutate(
-    data_group_gad_numeric =
-      case_when(
-#        na_per_person_gad_base == 0 & na_per_person_gad_prepan == 0 & na_per_person_gad_retro == 0 ~ 5, #all complete baseline, prepan and retro
-        na_per_person_gad_base != 0 & na_per_person_gad_retro == 0  ~ 4, #retro data only
-        na_per_person_gad_base == 0 & na_per_person_gad_retro != 0  ~ 3, #baseline data only
-#        na_per_person_gad_base == 0 & na_per_person_gad_prepan == 0 & na_per_person_gad_retro != 0  ~ 2, #prepan and baseline data only
-        na_per_person_gad_base == 0 & na_per_person_gad_retro == 0 ~ 1,  #baseline and retro data only
-#        na_per_person_gad_base != 0 & na_per_person_gad_prepan == 0 & na_per_person_gad_retro != 0  ~ 0  #prepan data only
-      )
-  )
-
-dat <- dat %>%
-  mutate(
-    data_group_gad = 
-      recode_factor(
-        data_group_gad_numeric,
-        "0" = "Only prepandemic data",
-        "1" = "Baseline and retrospective data",
-        "2" = "Prepandemic and baseline data",
-        "3" = "Baseline data only",
-        "4" = "Retrospective data only",
-        "5" = "All prepandemic, baseline and retrospective data"
-      )
-  )
-
-table(dat$data_group_gad)
-}
+table(dat.glad$data_group_gad)
 ```
@@
 PCL
-```{r glad/edgi data level groups PCL}
-if(GLAD == TRUE | EDGI == TRUE){
-dat <- dat %>%
+```{r data level groups PCL}
+dat.glad <- dat.glad %>%
   mutate(
@@
 
-table(dat$data_group_pcl)
-}
-```
-
-```{r nbr/ramp data level groups PCL}
-if(NBR == TRUE | RAMP == TRUE){
-dat <- dat %>%
-  mutate(
-    data_group_pcl_numeric =
-      case_when(
-#        na_per_person_pcl_base == 0 & na_per_person_pcl_prepan == 0 & na_per_person_pcl_retro == 0 ~ 5, #all complete baseline, prepan and retro
-        na_per_person_pcl_base != 0 & na_per_person_pcl_retro == 0  ~ 4, #retro data only
-        na_per_person_pcl_base == 0 & na_per_person_pcl_retro != 0  ~ 3, #baseline data only
-#        na_per_person_pcl_base == 0 & na_per_person_pcl_prepan == 0 & na_per_person_pcl_retro != 0  ~ 2, #prepan and baseline data only
-        na_per_person_pcl_base == 0 & na_per_person_pcl_retro == 0 ~ 1,  #baseline and retro data only
-#        na_per_person_pcl_base != 0 & na_per_person_pcl_prepan == 0 & na_per_person_pcl_retro != 0  ~ 0  #prepan data only
-      )
-  )
-
-dat <- dat %>%
-  mutate(
-    data_group_pcl = 
-      recode_factor(
-        data_group_pcl_numeric,
-        "0" = "Only prepandemic data",
-        "1" = "Baseline and retrospective data",
-        "2" = "Prepandemic and baseline data",
-        "3" = "Baseline data only",
-        "4" = "Retrospective data only",
-        "5" = "All prepandemic, baseline and retrospective data"
-      )
-  )
-
-table(dat$data_group_pcl)
-}
+table(dat.glad$data_group_pcl)
 ```
@@
 #Read in respiratory data
-
-## GLAD respiratory
-```{r glad coping respiratory cols}
-if(GLAD == TRUE){
+```{r coping resp cols}
 coping.glad.respiratory.raw <- readRDS(file = paste0(data.raw_path, "/glad/respiratory_coping_glad.rds"))
@@
 colnames(coping.glad.respiratory.raw)
-}
 ```
@@
 Select respiratory variables
-```{r coping glad respiratory cleaning}
-if(GLAD == TRUE){
+```{r read in respiratory data}
 coping.glad.respiratory.raw.id <- coping.glad.respiratory.raw %>%
@@
 dim(coping.glad.respiratory.raw)[1]-dim(coping.glad.respiratory.raw.id)[1]
-}
-```
-
-## EDGI respiratory
-```{r edgi coping respiratory cols}
-if(EDGI == TRUE){
-coping.edgi.respiratory.raw <- readRDS(file = paste0(data.raw_path, "/edgi/respiratory_coping_edgi.rds"))
-dim(coping.edgi.respiratory.raw)
-colnames(coping.edgi.respiratory.raw)
-}
-```
-
-Select respiratory variables
-```{r coping edgi respiratory cleaning}
-if(EDGI == TRUE){
-coping.edgi.respiratory.raw.id <- coping.edgi.respiratory.raw %>%
-  drop_na(externalDataReference) %>% # Drop NAs
-  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
-  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
-  mutate(ID = as.numeric(ID)) %>%
-  select(
-    Sample, # Sample
-    ID, # ID
-    respiratory.breath_diarrhoea_fatigue_fever,
-    respiratory.worst_ill_feel,
-    respiratory.persistent_cough,
-    respiratory.skipping_meals_because_you_felt_unwell,
-    respiratory.was_your_sense_of_smell_impaired,
-    respiratory.was_your_sense_of_taste_impaired,
-    respiratory.feeling_tiredfatigued,
-    respiratory.throat_swab_coronavirus_nose,
-    respiratory.throat_swab_test_nose,
-    respiratory.coronavirus_antibody_test,
-    respiratory.results_antibody_test
-  ) %>%
-  add_numeric(., exclude = exclude_cols) %>%
-  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
-  mutate_if(is.numeric, ~na_if(., -99)) %>%
-  mutate_if(is.numeric, ~na_if(., -77)) %>%
-  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
-  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
-
-# Inspect dimensions
-dim(coping.edgi.respiratory.raw.id)
-# Inspect colnames
-colnames(coping.edgi.respiratory.raw.id)
-#Differences
-dim(coping.edgi.respiratory.raw)[1]-dim(coping.edgi.respiratory.raw.id)[1]
-}
+
 ```
@@
 
-dat.coping <- left_join(
-  x = dat,
+dat.glad.coping <- left_join(
+  x = dat.glad,
   y = coping.glad.respiratory,
-  by = "ID"
+  by = c("Sample", "ID")
 )
@@
 ```{r create numeric sex variable with male=1}
-dat.coping <- dat.coping %>%
+dat.glad.coping <- dat.glad.coping %>%
   mutate(
@@
 ```{r how many people expereinced all symptoms}
-dat.coping <- dat.coping %>%
+dat.glad.coping <- dat.glad.coping %>%
   mutate(
@@
 
-dat.coping %>%
+dat.glad.coping %>%
   freq(covid_symptoms, cumul = F)
@@
 # linear model of covid symptoms
-dat.coping <- dat.coping %>%
+dat.glad.coping <- dat.glad.coping %>%
 		  mutate(
@@
 # Calcualte the odds ratios 
-dat.coping <- dat.coping %>%
+dat.glad.coping <- dat.glad.coping %>%
   mutate(
@@
 # generate binary cutt off variable for risk of COVID 
-dat.coping <- dat.coping %>%
+dat.glad.coping <- dat.glad.coping %>%
 		  mutate(
@@
 #create factor with labels
-dat.coping <- dat.coping %>%
+dat.glad.coping <- dat.glad.coping %>%
   mutate(
@@
 
-descr(x = dat.coping[,covid_variables],
+descr(x = dat.glad.coping[,covid_variables],
       round.digits = 2,
@@
 ## looking at cases over 0.5
-freq(dat.coping$covid_odds_ratio_50, 
+freq(dat.glad.coping$covid_odds_ratio_50, 
      cumul = FALSE) 
@@
 ```{r}
-dat.coping <- dat.coping %>%
+dat.glad.coping <- dat.glad.coping %>%
   mutate(
@@
 
-dat.coping %>%
+dat.glad.coping %>%
   freq(covid_probable_case_incl_screening, 

### 2020-08-17 PANCHANGE_data_preprocessing2020-07-15.Rmd
changing ramp employment file name

@@
 if(RAMP == TRUE){
-ramp.employment.raw <- readRDS(file = paste0(data.raw_path, "/ramp/employment_coping_ramp.rds"))
+ramp.employment.raw <- readRDS(file = paste0(data.raw_path, "/ramp/employment_ramp.rds"))
 dim(ramp.employment.raw)

### 2020-08-17 PANCHANGE_data_preprocessing2020-07-15.Rmd
change external ref to login ID for RAMP

@@
 
-ramp.dem.raw$externalDataReference <- ramp.dem.raw$`Login ID` #move Login ID to external data reference
-
   ramp.dem.raw.id <- ramp.dem.raw %>%
-    drop_na(externalDataReference) %>% # Drop NAs
-    distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
-    separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
+    drop_na(`Login ID`) %>% # Drop NAs
+    distinct(`Login ID`, .keep_all = TRUE) %>% # Remove duplicates based on ID
+    separate(`Login ID`, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
     mutate(ID = as.numeric(ID)) %>%
@@
 ramp.employment.raw.id <- ramp.employment.raw %>%
-  drop_na(subjectid) %>% # Drop NAs
+  drop_na('Login ID') %>% # Drop NAs
   distinct(subjectid, .keep_all = TRUE) %>% # Remove duplicates based on ID

### 2020-08-17 PANCHANGE_data_preprocessing2020-07-15.Rmd
editing RAMP highest education chunk

@@
 ramp.employment.raw.id <- ramp.employment.raw %>%
-  drop_na('Login ID') %>% # Drop NAs
-  distinct(subjectid, .keep_all = TRUE) %>% # Remove duplicates based on ID
-  separate(subjectid, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
+  drop_na(`Login ID`) %>% # Drop NAs
+  distinct(`Login ID`, .keep_all = TRUE) %>% # Remove duplicates based on ID
+  separate(`Login ID`, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
   mutate(
@@
          ID, # ID
-         employment.phd, # level of education - univeristy
-         employment.masters_degree_or_equivalent, # level of education - univeristy
-         employment.postgraduate_degree_or_equivalent, # level of education - univeristy
-         employment.bachelors_degree_or_equivalent, # level of education - univeristy
-         employment.a_levelsas_levels_or_equivalent, # level of education - alevel
-         employment.o_levelsgcses_or_equivalent, # level of education - gcse
-         employment.cses_or_equivalent, # level of education - cse
-         employment.nvq_or_hnd_or_hnc_or_equivalent, # level of education - nvq
+         employment.what_is_your_highest_level_of_education, #highest level of edcuation
          employment.government_work_key_workers # key worker status
@@
 ```{r Highest education baseline}
-if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE | RAMP == TRUE) {
+if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE) {
 #create numeric version of the highest education variable
@@
 ```{r Highest education check}
-if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE | RAMP == TRUE) {
+if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE) {
 employment.raw.id %>%

### 2020-08-17 PANCHANGE_data_preprocessing2020-07-15.Rmd
finished editing ramp employment chunk

@@
 
-## Highest education (baseline, GLAD, EDGI, NBR, RAMP)
+## Highest education (baseline, GLAD, EDGI, NBR)
 Proceed along qualifications fields. If field is not blank, take that as highest qual. If field is blank, check next field. If all fields are blank, NA
@@
          employment.cses_or_equivalent_numeric
+  )
+}
+```
+
+## Highest education (baseline, RAMP)
+```{r highest level of education for ramp}
+if(RAMP == TRUE) {
+#create numeric version of the highest education variable
+employment.raw.id <- employment.raw.id %>%
+  mutate(
+    highest_education_numeric =
+      case_when(
+        employment.what_is_your_highest_level_of_education == "PhD" ~ 4,
+        employment.what_is_your_highest_level_of_education == "Postgraduate degree or equivalent" ~ 4,
+        employment.what_is_your_highest_level_of_education == "Master's degree or equivalent" ~ 4,
+        employment.what_is_your_highest_level_of_education == "Bachelor's degree or equivalent" ~ 4,
+        employment.what_is_your_highest_level_of_education == "A-level or equivalent" ~ 3,
+        employment.what_is_your_highest_level_of_education == "GCSE or equivalent" ~ 2,
+        employment.what_is_your_highest_level_of_education == "None of these" ~ 1
+      )
+    )
+
+#recode the numeric version into a factor
+employment.raw.id <- employment.raw.id %>%
+  mutate(
+    highest_education =
+      recode_factor(
+        highest_education_numeric,
+        `1` = "None",
+        `2` = "GCSE/CSE",
+        `3` = "A-levels",
+        `4` = "University")
+    )
+
+employment.raw.id %>%
+  freq(highest_education)
+}
+```
+
+Check highest education coding for RAMP
+```{r Highest education check for RAMP}
+if(RAMP == TRUE) {
+employment.raw.id %>%
+  select(highest_education,
+         employment.what_is_your_highest_level_of_education,
+         employment.what_is_your_highest_level_of_education_numeric
   )

### 2020-08-17 PANCHANGE_data_preprocessing2020-07-15.Rmd
RAMP mhd section finished

@@
     mhd.bingeeating_disorder,
-    mhd.atypical_bingeeating_disorder,
+    mhd.atypical_bingeeating_disorder
   ) %>%
@@
 
+## RAMP
+```{r ramp mhd cols}
+if(RAMP == TRUE) {
+ramp.mhd.raw <- readRDS(file = paste0(data.raw_path,"/ramp/mhd_ramp.rds"))
+dim(ramp.mhd.raw)
+colnames(ramp.mhd.raw)
+}
+```
+
+```{r ramp mhd cleaning}
+if(RAMP == TRUE) {
+exclude_cols <- c("Sample",
+                  "ID")
+
+ramp.mhd.raw.id <- ramp.mhd.raw %>%
+  drop_na(`Login ID`) %>% # Drop NAs
+  distinct(`Login ID`, .keep_all = TRUE) %>% # Remove duplicates based on ID
+  separate(`Login ID`, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
+  separate(ID, into = "ID", sep = 7) %>%
+  mutate(
+    ID = as.numeric(ID)) %>%
+  select(
+    Sample, # Sample
+    ID, # ID
+    mhd.depression = NA.30.depression,
+    mhd.pregnancy_depression = NA.30.pregnancy_depression,
+    mhd.premenstrual_dysphoric_disorder_pmdd = NA.30.premenstrual_dysphoric_disorder_pmdd,
+    mhd.mania_hypomania_bipolar_or_manicdepression = NA.30.mania_hypomania_bipolar_or_manicdepression,
+    mhd.anxiety_nerves_or_generalised_anxiety_disorder = NA.30.anxiety_nerves_or_generalised_anxiety_disorder,
+    mhd.social_anxiety_or_social_phobia = NA.30.social_anxiety_or_social_phobia,
+    mhd.specific_phobia_e.g._phobia_of_flying = NA.30.specific_phobia_e.g._phobia_of_flying,
+    mhd.agoraphobia = NA.30.agoraphobia,
+    mhd.panic_disorder = NA.30.panic_disorder,
+    mhd.panic_attacks = NA.30.panic_attacks,
+    mhd.posttraumatic_stress_disorder_ptsd = NA.30.posttraumatic_stress_disorder_ptsd,
+    mhd.obsessivecompulsive_disorder_ocd = NA.30.obsessivecompulsive_disorder_ocd, 
+    mhd.body_dysmorphic_disorder_bdd = NA.30.body_dysmorphic_disorder_bdd,
+    mhd.skin_picking_obsessive_compulsive = NA.30.skin_picking_obsessive_compulsive,
+    mhd.anorexia_nervosa = NA.30.anorexia_nervosa,
+    mhd.atypical_anorexia_nervosa = NA.30.atypical_anorexia_nervosa,
+    mhd.bulimia_nervosa = NA.30.bulimia_nervosa,
+    mhd.bingeeating_disorder = NA.30.psychological_overeating_or_bingeeating_disorder,
+    mhd.schizophrenia = NA.30.schizophrenia,
+    mhd.schizoaffective_disorder = NA.30.schizoaffective_disorder,
+    mhd.type_psychosis_psychotic_illness = NA.30.psychosis_type_psychotic_illness,
+    mhd.personality_disorder = NA.30.personality_disorder,
+    mhd.autism_aspergers_or_autistic_spectrum_disorder = NA.30.autism_aspergers_or_autistic_spectrum_disorder,
+    mhd.attention_deficit_hyperactivity_disorder = NA.30.attention_deficit_hyperactivity_disorder,
+    mhd.personality_disorder_diagnosed = NA.30.personality_disorder_diagnosed
+  ) %>%
+  add_numeric(., exclude = exclude_cols) %>%
+  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
+  mutate_if(is.numeric, ~na_if(., -99)) %>%
+  mutate_if(is.numeric, ~na_if(., -77)) %>%
+  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
+  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
+
+# Inspect dimensions
+dim(ramp.mhd.raw.id)
+# Inspect colnames
+colnames(ramp.mhd.raw.id)
+#Differences
+dim(ramp.mhd.raw)[1]-dim(ramp.mhd.raw.id)[1]
+}
+```
+
+```{r ramp mhd copy}
+if(RAMP == TRUE) {
+  mhd.raw.id <- ramp.mhd.raw.id
+}
+```
+
 ## Grouping mental health disorders
@@
     mhd.bingeeating_disorder,
-    mhd.atypical_bingeeating_disorder,
+    mhd.atypical_bingeeating_disorder
   )
@@
 ```{r mhd obsessive_compulsive_disorders}
-if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE | RAMP == TRUE) {
+if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE) {
 mhd.raw.id <- mhd.raw.id %>%
@@
 
+```{r mhd obsessive_compulsive_disorders for ramp}
+if(RAMP == TRUE) {
+mhd.raw.id <- mhd.raw.id %>%
+  mutate(
+    obsessive_compulsive_disorders_numeric =
+      case_when(
+        mhd.obsessivecompulsive_disorder_ocd_numeric == "1" ~ 1,
+        mhd.skin_picking_obsessive_compulsive_numeric == "1" ~ 1,
+        mhd.body_dysmorphic_disorder_bdd_numeric == "1" ~ 1,
+        (mhd.obsessivecompulsive_disorder_ocd_numeric == "0" &
+        mhd.skin_picking_obsessive_compulsive_numeric == "0" &
+        mhd.body_dysmorphic_disorder_bdd_numeric == "0") ~ 0
+      )
+  )
+
+mhd.raw.id <- mhd.raw.id %>%
+  mutate(
+    obsessive_compulsive_disorders =
+      recode_factor(obsessive_compulsive_disorders_numeric,
+                    "0" = "No obsessive compulsive disorder",
+                    "1" = "Obsessive compulsive disorder",
+                    missing = NA_character_
+                    )
+  )
+
+mhd.raw.id %>%
+  freq(obsessive_compulsive_disorders)
+}
+```
+
 ```{r Check obsessive_compulsive_disorders}
-if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE | RAMP == TRUE) {
+if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE) {
 mhd.raw.id %>%
@@
     mhd.obsessive_compulsive_related_disorders_numeric,
+    mhd.body_dysmorphic_disorder_bdd,
+    mhd.body_dysmorphic_disorder_bdd_numeric
+  )
+}
+```
+
+```{r Check obsessive_compulsive_disorders ramp}
+if(RAMP == TRUE) {
+mhd.raw.id %>%
+  select(
+    obsessive_compulsive_disorders,
+    obsessive_compulsive_disorders_numeric,
+    mhd.obsessivecompulsive_disorder_ocd,
+    mhd.obsessivecompulsive_disorder_ocd_numeric,
+    mhd.skin_picking_obsessive_compulsive,
+    mhd.skin_picking_obsessive_compulsive_numeric,
     mhd.body_dysmorphic_disorder_bdd,
@@
 Create new dataframe with the derived categories
-++KT: do we want to keep individual diagnoses here as well?? 
 ```{r mhd categories}
@@
     personality_cluster_c_numeric = NA_real_,
-    personality_cluster_c = NA_real_,    
+    personality_cluster_c = NA_real_    
   )

### 2020-08-17 PANCHANGE_data_preprocessing2020-07-15.Rmd
data export chunks

--- 2020-08-17 PANCHANGE_data_preprocessing2020-07-15.Rmd
@@
 
+ramp.dem.raw$externalDataReference <- ramp.dem.raw$`Login ID` #move Login ID to external data reference
+
   ramp.dem.raw.id <- ramp.dem.raw %>%
-    drop_na(`Login ID`) %>% # Drop NAs
-    distinct(`Login ID`, .keep_all = TRUE) %>% # Remove duplicates based on ID
-    separate(`Login ID`, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
+    drop_na(externalDataReference) %>% # Drop NAs
+    distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
+    separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
     mutate(ID = as.numeric(ID)) %>%
@@
 if(RAMP == TRUE){
-ramp.employment.raw <- readRDS(file = paste0(data.raw_path, "/ramp/employment_ramp.rds"))
+ramp.employment.raw <- readRDS(file = paste0(data.raw_path, "/ramp/employment_coping_ramp.rds"))
 dim(ramp.employment.raw)
@@
 ramp.employment.raw.id <- ramp.employment.raw %>%
-  drop_na(`Login ID`) %>% # Drop NAs
-  distinct(`Login ID`, .keep_all = TRUE) %>% # Remove duplicates based on ID
-  separate(`Login ID`, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
+  drop_na(subjectid) %>% # Drop NAs
+  distinct(subjectid, .keep_all = TRUE) %>% # Remove duplicates based on ID
+  separate(subjectid, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
   mutate(
@@
          ID, # ID
-         employment.what_is_your_highest_level_of_education, #highest level of edcuation
+         employment.phd, # level of education - univeristy
+         employment.masters_degree_or_equivalent, # level of education - univeristy
+         employment.postgraduate_degree_or_equivalent, # level of education - univeristy
+         employment.bachelors_degree_or_equivalent, # level of education - univeristy
+         employment.a_levelsas_levels_or_equivalent, # level of education - alevel
+         employment.o_levelsgcses_or_equivalent, # level of education - gcse
+         employment.cses_or_equivalent, # level of education - cse
+         employment.nvq_or_hnd_or_hnc_or_equivalent, # level of education - nvq
          employment.government_work_key_workers # key worker status
@@
 ```{r Highest education baseline}
-if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE) {
+if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE | RAMP == TRUE) {
 #create numeric version of the highest education variable
@@
 ```{r Highest education check}
-if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE) {
+if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE | RAMP == TRUE) {
 employment.raw.id %>%
@@
 ```
+
+```{r dat.coping summary}
+summarytools::dfSummary(
+  dat.coping,
+  graph.col = F,
+  valid.col = F,
+  labels.col = F)
+```
+
+# Export data
+```{r export data}
+if(GLAD == TRUE){
+saveRDS(object = dat.coping, file = paste0(data_path, "/glad.rds"))
+}
+
+if(EDGI == TRUE){
+saveRDS(object = dat.coping, file = paste0(data_path, "/edgi.rds"))
+}
+
+if(NBR == TRUE){
+saveRDS(object = dat.coping, file = paste0(data_path, "/nbr.rds"))
+}
+
+if(RAMP == TRUE){
+saveRDS(object = dat.coping, file = paste0(data_path, "/ramp.rds"))
+}
+
+```

### 2020-08-17 PANCHANGE_data_preprocessing2020-07-15.Rmd
read in RAMP baseline GAD

--- 2020-08-17 PANCHANGE_data_preprocessing2020-07-15.Rmd
@@
 if(RAMP == TRUE) {
-  coping.ramp.gad.raw <- readRDS(file = paste0(data.raw_path,"/ramp/gad_coping_ramp.rds"))
-  dim(coping.ramp.gad.raw)
-  colnames(coping.ramp.gad.raw)
+  ramp.gad.raw <- readRDS(file = paste0(data.raw_path,"/ramp/gad_ramp.rds"))
+  dim(ramp.gad.raw)
+  colnames(ramp.gad.raw)
 }
@@
   summarytools::dfSummary(
-    coping.ramp.gad.raw,
+    ramp.gad.raw,
     graph.col = F,
@@
 if(RAMP == TRUE) {
-  exclude_cols_coping_ramp <- c(
+  exclude_cols_ramp <- c(
     "Sample",
     "ID",
-    "startDate.coping"
-  )
-
-  coping.ramp.gad.raw.id <- coping.ramp.gad.raw %>%
-    drop_na(externalDataReference) %>% # Drop NAs
-    distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
-    separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
+    "startDate.ramp"
+  )
+
+  ramp.gad.raw.id <- ramp.gad.raw %>%
+    drop_na(`Login ID`) %>% # Drop NAs
+    distinct(`Login ID`, .keep_all = TRUE) %>% # Remove duplicates based on ID
+    separate(`Login ID`, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
     mutate(ID = as.numeric(ID)
@@
       ID, # ID
-      startDate.coping = startDate, # Rename startDate
-      gad.problems_made_difficult_care, # Impairment
-      gad.pandemic_felt_feelings, # Comparison to before the pandemic (retro)
-      gad.feeling_nervous_anxious_or_on_edge_retro = gad.feeling_nervous_anxious_or_on_edge,
-      gad.control_worrying_stop_retro = gad.control_worrying_stop,
-      gad.worrying_too_much_about_different_things_retro = gad.worrying_too_much_about_different_things,
-      gad.trouble_relaxing_retro = gad.trouble_relaxing,
-      gad.sit_restless_hard_retro = gad.sit_restless_hard,
-      gad.becoming_easily_annoyed_or_irritable_retro = gad.becoming_easily_annoyed_or_irritable,
-      gad.awful_feeling_afraid_happen_retro = gad.awful_feeling_afraid_happen,
-      gad.feeling_nervous_anxious_or_on_edge_base = gad.feeling_nervous_anxious_or_on_edge.1,
-      gad.control_worrying_stop_base = gad.control_worrying_stop.1,
-      gad.worrying_too_much_about_different_things_base = gad.worrying_too_much_about_different_things.1,
-      gad.trouble_relaxing_base = gad.trouble_relaxing.1,
-      gad.sit_restless_hard_base = gad.sit_restless_hard.1,
-      gad.becoming_easily_annoyed_or_irritable_base = gad.becoming_easily_annoyed_or_irritable.1,
-      gad.awful_feeling_afraid_happen_base = gad.awful_feeling_afraid_happen.1
+      startDate.ramp = startDate, # Rename startDate
+      gad.problems_made_difficult_care = gad.issues_made_carrying_daily, # Impairment
+      gad.pandemic_felt_feelings = gad.feelings_pandemic_felt, # Comparison to before the pandemic (retro)
+      gad.feeling_nervous_anxious_or_on_edge_retro = gad.feeling_nervous_anxious_or_on_edge.1, #retro and baseline coding are reversed for RAMP
+      gad.control_worrying_stop_retro = gad.control_worrying_stop.1, #.1 = retro
+      gad.worrying_too_much_about_different_things_retro = gad.worrying_too_much_about_different_things.1,
+      gad.trouble_relaxing_retro = gad.trouble_relaxing.1,
+      gad.sit_restless_hard_retro = gad.sit_hard_restless.1,
+      gad.becoming_easily_annoyed_or_irritable_retro = gad.becoming_easily_annoyed_or_irritable.1,
+      gad.awful_feeling_afraid_happen_retro = gad.awful_feeling_afraid_happen.1,
+      gad.feeling_nervous_anxious_or_on_edge_base = gad.feeling_nervous_anxious_or_on_edge,
+      gad.control_worrying_stop_base = gad.control_worrying_stop,
+      gad.worrying_too_much_about_different_things_base = gad.worrying_too_much_about_different_things,
+      gad.trouble_relaxing_base = gad.trouble_relaxing,
+      gad.sit_restless_hard_base = gad.sit_hard_restless,
+      gad.becoming_easily_annoyed_or_irritable_base = gad.becoming_easily_annoyed_or_irritable,
+      gad.awful_feeling_afraid_happen_base = gad.awful_feeling_afraid_happen
     ) %>%
@@
   # Inspect dimensions
-  dim(coping.ramp.gad.raw.id)
+  dim(ramp.gad.raw.id)
   # Inspect colnames
-  colnames(coping.ramp.gad.raw.id)
+  colnames(ramp.gad.raw.id)
   #Differences
-  dim(coping.ramp.gad.raw)[1]-dim(coping.ramp.gad.raw.id)[1]
+  dim(ramp.gad.raw)[1]-dim(ramp.gad.raw.id)[1]
 }

### 2020-08-17 PANCHANGE_data_preprocessing2020-07-15.Rmd
change a left join to include Sample
finished RAMP GAD and hashed out RAMP PCL - don't have data yet

@@
 if(RAMP == TRUE) {
-  coping.gad.raw.id <- coping.ramp.gad.raw.id
+  coping.gad.raw.id <- ramp.gad.raw.id
 }
@@
 
-## RAMP
+## RAMP - NOT YET HAVE THE RAMP PCL DATA READY
 ```{r coping ramp pcl cols}
-if(RAMP == TRUE) {
-coping.ramp.pcl.raw <- readRDS(file = paste0(data.raw_path,"/ramp/pcl_coping_ramp.rds"))
-dim(coping.ramp.pcl.raw)
-colnames(coping.ramp.pcl.raw)
-}
+# if(RAMP == TRUE) {
+# coping.ramp.pcl.raw <- readRDS(file = paste0(data.raw_path,"/ramp/pcl_ramp.rds"))
+# dim(coping.ramp.pcl.raw)
+# colnames(coping.ramp.pcl.raw)
+# }
 ```
@@
 ```{r coping ramp pcl summary labels}
-if(RAMP == TRUE) {
-summarytools::dfSummary(
-  coping.ramp.pcl.raw,
-  graph.col = F,
-  valid.col = F,
-  labels.col = F
-)
-}
+# if(RAMP == TRUE) {
+# summarytools::dfSummary(
+#   coping.ramp.pcl.raw,
+#   graph.col = F,
+#   valid.col = F,
+#   labels.col = F
+# )
+# }
 ```
@@
 ```{r coping ramp pcl cleaning}
-if(RAMP == TRUE) {
-coping.ramp.pcl.raw.id <- coping.ramp.pcl.raw %>%
-  drop_na(externalDataReference) %>% # Drop NAs
-  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
-  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
-  mutate(ID = as.numeric(ID)) %>%
-  select(
-    Sample, # Sample
-    ID, # ID
-    pcl.stressful_experience_repeated_images_base = pcl.stressful_experience_repeated_images,
-    pcl.stressful_experience_upset_reminded_base = pcl.stressful_experience_upset_reminded, # differ to RAMP prepan
-    pcl.stressful_situation_avoiding_activities_base = pcl.avoiding_activities_stressful_experience, # differ to RAMP prepan
-    pcl.cut_people_feeling_distant_base = pcl.cut_people_feeling_distant,
-    pcl.feeling_irritable_or_having_angry_outbursts_base = pcl.feeling_irritable_or_having_angry_outbursts,
-    pcl.difficulty_concentrating_base = pcl.difficulty_concentrating,
-    pcl.stressful_experience_repeated_images_retro = pcl.stressful_experience_repeated_images.1,
-    pcl.stressful_experience_upset_reminded_retro = pcl.stressful_experience_upset_reminded.1,
-    pcl.stressful_situation_avoiding_activities_retro = pcl.avoiding_activities_stressful_experience.1,
-    pcl.cut_people_feeling_distant_retro = pcl.cut_people_feeling_distant.1,
-    pcl.feeling_irritable_or_having_angry_outbursts_retro = pcl.feeling_irritable_or_having_angry_outbursts.1,
-    pcl.difficulty_concentrating_retro = pcl.difficulty_concentrating.1
-  ) %>%
-  add_numeric(., exclude = exclude_cols) %>%
-  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
-  mutate_if(is.numeric, ~na_if(., -99)) %>%
-  mutate_if(is.numeric, ~na_if(., -77)) %>%
-  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
-  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
-
-# Inspect dimensions
-dim(coping.ramp.pcl.raw.id)
-# Inspect colnames
-colnames(coping.ramp.pcl.raw.id)
-#Differences
-dim(coping.ramp.pcl.raw)[1]-dim(coping.ramp.pcl.raw.id)[1]
-}
+# if(RAMP == TRUE) {
+# coping.ramp.pcl.raw.id <- coping.ramp.pcl.raw %>%
+#   drop_na(externalDataReference) %>% # Drop NAs
+#   distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
+#   separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
+#   mutate(ID = as.numeric(ID)) %>%
+#   select(
+#     Sample, # Sample
+#     ID, # ID
+#     pcl.stressful_experience_repeated_images_base = pcl.stressful_experience_repeated_images,
+#     pcl.stressful_experience_upset_reminded_base = pcl.stressful_experience_upset_reminded, # differ to RAMP prepan
+#     pcl.stressful_situation_avoiding_activities_base = pcl.avoiding_activities_stressful_experience, # differ to RAMP prepan
+#     pcl.cut_people_feeling_distant_base = pcl.cut_people_feeling_distant,
+#     pcl.feeling_irritable_or_having_angry_outbursts_base = pcl.feeling_irritable_or_having_angry_outbursts,
+#     pcl.difficulty_concentrating_base = pcl.difficulty_concentrating,
+#     pcl.stressful_experience_repeated_images_retro = pcl.stressful_experience_repeated_images.1,
+#     pcl.stressful_experience_upset_reminded_retro = pcl.stressful_experience_upset_reminded.1,
+#     pcl.stressful_situation_avoiding_activities_retro = pcl.avoiding_activities_stressful_experience.1,
+#     pcl.cut_people_feeling_distant_retro = pcl.cut_people_feeling_distant.1,
+#     pcl.feeling_irritable_or_having_angry_outbursts_retro = pcl.feeling_irritable_or_having_angry_outbursts.1,
+#     pcl.difficulty_concentrating_retro = pcl.difficulty_concentrating.1
+#   ) %>%
+#   add_numeric(., exclude = exclude_cols) %>%
+#   mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
+#   mutate_if(is.numeric, ~na_if(., -99)) %>%
+#   mutate_if(is.numeric, ~na_if(., -77)) %>%
+#   mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
+#   mutate_if(is.factor, ~na_if(., "Don't know")) %>%
+#   mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
+#   mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
+#   mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
+#   mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
+#   mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
+#   mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
+# 
+# # Inspect dimensions
+# dim(coping.ramp.pcl.raw.id)
+# # Inspect colnames
+# colnames(coping.ramp.pcl.raw.id)
+# #Differences
+# dim(coping.ramp.pcl.raw)[1]-dim(coping.ramp.pcl.raw.id)[1]
+# }
 ```
@@
 ```{r coping ramp pcl copy}
-if(RAMP == TRUE) {
-  coping.pcl.raw.id <- coping.ramp.pcl.raw.id
-}
+# if(RAMP == TRUE) {
+#   coping.pcl.raw.id <- coping.ramp.pcl.raw.id
+# }
 ```

### 2020-08-17 PANCHANGE_data_preprocessing2020-07-15.Rmd
read in RAMP PHQ data

@@
 if(RAMP == TRUE) {
-coping.ramp.phq.raw <- readRDS(file = paste0(data.raw_path, "/ramp/phq_coping_ramp.rds"))
-dim(coping.ramp.phq.raw)
-colnames(coping.ramp.phq.raw)
+ramp.phq.raw <- readRDS(file = paste0(data.raw_path, "/ramp/phq_ramp.rds"))
+dim(ramp.phq.raw)
+colnames(ramp.phq.raw)
 }
@@
 summarytools::dfSummary(
-  coping.ramp.phq.raw,
+  ramp.phq.raw,
   graph.col = F,
@@
 if(RAMP == TRUE) {
-coping.ramp.phq.raw.id <- coping.ramp.phq.raw %>%
-  drop_na(externalDataReference) %>% # Drop NAs
-  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
-  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
+ramp.phq.raw.id <- ramp.phq.raw %>%
+  drop_na(`Login ID`) %>% # Drop NAs
+  distinct(`Login ID`, .keep_all = TRUE) %>% # Remove duplicates based on ID
+  separate(`Login ID`, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
   mutate(ID = as.numeric(ID)
@@
     ID, # ID
-    phq.problems_made_difficult_care,
-    phq.pandemic_felt_feelings,
-    phq.little_interest_or_pleasure_in_doing_things_retro = phq.little_interest_or_pleasure_in_doing_things,
-    phq.feeling_down_depressed_or_hopeless_retro = phq.feeling_down_depressed_or_hopeless,
-    phq.staying_asleep_sleeping_trouble_retro = phq.staying_asleep_sleeping_trouble,
-    phq.feeling_tired_or_having_little_energy_retro = phq.feeling_tired_or_having_little_energy,
-    phq.poor_appetite_or_overeating_retro = phq.poor_appetite_or_overeating,
-    phq.feeling_bad_failure_family_retro = phq.feeling_bad_failure_family,
-    phq.trouble_concentrating_reading_newspaper_retro = phq.trouble_concentrating_newspaper_reading, # differ RAMP prepandemic
-    phq.moving_fidgety_noticed_opposite_retro = phq.moving_fidgety_opposite_slowly, # differ RAMP prepandemic
-    phq.dead_hurting_thoughts_retro = phq.dead_hurting_thoughts,
-    phq.little_interest_or_pleasure_in_doing_things_base = phq.little_interest_or_pleasure_in_doing_things.1,
-    phq.feeling_down_depressed_or_hopeless_base = phq.feeling_down_depressed_or_hopeless.1,
-    phq.staying_asleep_sleeping_trouble_base = phq.staying_asleep_sleeping_trouble.1,
-    phq.feeling_tired_or_having_little_energy_base = phq.feeling_tired_or_having_little_energy.1,
-    phq.poor_appetite_or_overeating_base = phq.poor_appetite_or_overeating.1,
-    phq.feeling_bad_failure_family_base = phq.feeling_bad_failure_family.1,
-    phq.trouble_concentrating_reading_newspaper_base = phq.trouble_concentrating_newspaper_reading.1, # differ RAMP prepandemic
-    phq.moving_fidgety_noticed_opposite_base = phq.moving_fidgety_opposite_slowly.1, # differ RAMP prepandemic
-    phq.dead_hurting_thoughts_base = phq.dead_hurting_thoughts.1
+    phq.problems_made_difficult_care = phq.issues_made_carrying_daily, #impact
+    phq.pandemic_felt_feelings = phq.feelings_pandemic_felt, #before the pandemic question
+    phq.little_interest_or_pleasure_in_doing_things_retro = phq.little_interest_or_pleasure_in_doing_things.1,
+    phq.feeling_down_depressed_or_hopeless_retro = phq.feeling_down_depression_or_hopeless, #THIS IS CORRECT - strange naming in raw dataset
+    phq.staying_asleep_sleeping_trouble_retro = phq.staying_asleep_sleeping_trouble.1,
+    phq.feeling_tired_or_having_little_energy_retro = phq.feeling_tired_or_having_little_energy.1,
+    phq.poor_appetite_or_overeating_retro = phq.poor_appetite_or_overeating.1,
+    phq.feeling_bad_failure_family_retro = phq.failure_family_feeling_bad.1,
+    phq.trouble_concentrating_reading_newspaper_retro = phq.trouble_concentrating_newspaper_reading.1, 
+    phq.moving_fidgety_noticed_opposite_retro = phq.moving_fidgety_opposite_slowly.1, 
+    phq.dead_hurting_thoughts_retro = phq.dead_hurting_thoughts.1,
+    phq.little_interest_or_pleasure_in_doing_things_base = phq.little_interest_or_pleasure_in_doing_things,
+    phq.feeling_down_depressed_or_hopeless_base = phq.feeling_down_depressed_or_hopeless,
+    phq.staying_asleep_sleeping_trouble_base = phq.staying_asleep_sleeping_trouble,
+    phq.feeling_tired_or_having_little_energy_base = phq.feeling_tired_or_having_little_energy,
+    phq.poor_appetite_or_overeating_base = phq.poor_appetite_or_overeating,
+    phq.feeling_bad_failure_family_base = phq.failure_family_feeling_bad,
+    phq.trouble_concentrating_reading_newspaper_base = phq.trouble_concentrating_newspaper_reading, # differ RAMP prepandemic
+    phq.moving_fidgety_noticed_opposite_base = phq.moving_fidgety_opposite_slowly, # differ RAMP prepandemic
+    phq.dead_hurting_thoughts_base = phq.dead_hurting_thoughts
   ) %>%
@@
 # Inspect dimensions
-dim(coping.ramp.phq.raw.id)
+dim(ramp.phq.raw.id)
 # Inspect colnames
-colnames(coping.ramp.phq.raw.id)
+colnames(ramp.phq.raw.id)
 #Differences
-dim(coping.ramp.phq.raw)[1]-dim(coping.ramp.phq.raw.id)[1]
+dim(ramp.phq.raw)[1]-dim(ramp.phq.raw.id)[1]
 }
@@
 if(RAMP == TRUE) {
-  coping.phq.raw.id <- coping.ramp.phq.raw.id
+  coping.phq.raw.id <- ramp.phq.raw.id
 }

### 2020-08-17 PANCHANGE_data_preprocessing2020-07-15.Rmd
read in OCIR RAMP data

@@
 if(RAMP == TRUE) {
-coping.ramp.ocir.raw <- readRDS(file = paste0(data.raw_path, "/ramp/ocir_coping_ramp.rds"))
-dim(coping.ramp.ocir.raw)
-colnames(coping.ramp.ocir.raw)
+ramp.ocir.raw <- readRDS(file = paste0(data.raw_path, "/ramp/ocir_ramp.rds"))
+dim(ramp.ocir.raw)
+colnames(ramp.ocir.raw)
 }
@@
 summarytools::dfSummary(
-  coping.ramp.ocir.raw,
+  ramp.ocir.raw,
   graph.col = F,
@@
 if(RAMP == TRUE) {
-coping.ramp.ocir.raw.id <- coping.ramp.ocir.raw %>%
-  drop_na(recipientFirstName) %>% # Drop NAs
-  distinct(recipientFirstName, .keep_all = TRUE) %>% # Remove duplicates based on ID
-  separate(recipientFirstName, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
+ramp.ocir.raw.id <- ramp.ocir.raw %>%
+  drop_na(`Login ID`) %>% # Drop NAs
+  distinct(`Login ID`, .keep_all = TRUE) %>% # Remove duplicates based on ID
+  separate(`Login ID`, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
   mutate(ID = as.numeric(ID)) %>%
@@
     ID, # ID
-    ocir.felt_pandemic_feelings, # Comparison to before the pandemic
-    ocir.i_repeatedly_check_doors_windows_drawers_etc_retro = ocir.i_repeatedly_check_doors_windows_drawers_etc.,
-    ocir.arranged_things_change_upset_retro = ocir.arranged_things_change_upset,
-    ocir.repeat_feel_numbers_retro = ocir.numbers_repeat_feel, ## Different from RAMP prepandemic
-    ocir.clean_simply_wash_feel_retro = ocir.feel_contaminated_clean_simply, ## Different from RAMP prepandemic
-    ocir.mind_upset_unpleasant_thoughts_retro = ocir.mind_upset_unpleasant_thoughts,
-    ocir.afraid_avoid_throwing_things_retro = ocir.afraid_avoid_throwing_things,
-    ocir.light_switches_water_taps_retro = ocir.light_switches_water_taps,
-    ocir.arranged_things_retro = ocir.arranged_things,
-    ocir.good_feel_bad_numbers_retro = ocir.bad_numbers_good_feel, ## Different from RAMP prepandemic
-    ocir.hands_longer_wash_retro = ocir.longer_hands_wash, ## Different from RAMP prepandemic
-    ocir.saved_things_retro = ocir.saved_things,
-    ocir.frequently_difficulty_rid_nasty_retro = ocir.frequently_rid_difficulty_nasty, ## Different from RAMP prepandemic
-    ocir.i_check_things_more_often_than_necessary_retro = ocir.i_check_things_more_often_than_necessary.,
+    ocir.felt_pandemic_feelings = ocir.feelings_pandemic_felt, # Comparison to before the pandemic
+    ocir.saved_things_retro = ocir.saved_things.1,
+    ocir.i_check_things_more_often_than_necessary_retro = ocir.i_check_things_more_often_than_necessary..1,
+    ocir.i_repeatedly_check_doors_windows_drawers_etc_retro = ocir.i_repeatedly_check_doors_windows_drawers_etc..1,
+    ocir.arranged_things_change_upset_retro = ocir.arranged_things_change_upset.1,
+    ocir.repeat_feel_numbers_retro = ocir.numbers_repeat_feel.1, 
+    ocir.clean_simply_wash_feel_retro = ocir.feel_contaminated_clean_simply.1, 
+    ocir.mind_upset_unpleasant_thoughts_retro = ocir.unpleasant_thoughts_mind_upset.1,
+    ocir.afraid_avoid_throwing_things_retro = ocir.afraid_avoid_throwing_things.1,
+    ocir.light_switches_water_taps_retro = ocir.repeatedly_check_gas_water.1,
+    ocir.arranged_things_retro = ocir.arranged_things.1,
+    ocir.good_feel_bad_numbers_retro = ocir.bad_numbers_good_feel.1, 
+    ocir.hands_longer_wash_retro = ocir.longer_hands_wash.1, 
+    ocir.frequently_difficulty_rid_nasty_retro = ocir.difficulty_rid_frequently_nasty.1,
+
     ocir.arranged_properly_objects_upset_retro = ocir.arranged_properly_objects_upset,
     ocir.feel_compelled_count_things_retro = ocir.feel_compelled_count_things,
-    ocir.strangers_touch_touched_difficult_retro = ocir.strangers_touch_touched_object, ## Different from RAMP prepandemic
-    ocir.control_difficult_find_thoughts_retro = ocir.control_find_difficult_thoughts, ## Different from RAMP prepandemic
-    ocir.i_collect_things_i_dont_need_retro = ocir.i_collect_things_i_dont_need., ## Different from RAMP prepandemic
+    ocir.strangers_touch_touched_difficult_retro = ocir.strangers_touch_touched_object, 
+    ocir.control_difficult_find_thoughts_retro = ocir.control_find_difficult_thoughts, 
+    ocir.i_collect_things_i_dont_need_retro = ocir.i_collect_things_i_dont_need., 
     ocir.i_repeatedly_check_doors_windows_drawers_etc_base = ocir.i_repeatedly_check_doors_windows_drawers_etc..1,
@@
 # Inspect dimensions
-dim(coping.ramp.ocir.raw.id)
+dim(ramp.ocir.raw.id)
 # Inspect colnames
-colnames(coping.ramp.ocir.raw.id)
+colnames(ramp.ocir.raw.id)
 #Differences
-dim(coping.ramp.ocir.raw)[1]-dim(coping.ramp.ocir.raw.id)[1]
+dim(ramp.ocir.raw)[1]-dim(ramp.ocir.raw.id)[1]
 }

### 2020-08-17 PANCHANGE_data_preprocessing2020-07-15.Rmd
fixed age categories and sum_scores matrix -> numeric

--- 2020-08-17 PANCHANGE_data_preprocessing2020-07-15.Rmd
@@
       case_when(
-          Age >= 16 & Age <= 18 ~ "1",
-          Age >= 19 & Age <= 25 ~ "2",
-          Age >= 26 & Age <= 35 ~ "3",
-          Age >= 36 & Age <= 45 ~ "4",
-          Age >= 46 & Age <= 55 ~ "5",
-          Age >= 56 & Age <= 65 ~ "6",
-          Age >= 66 & Age <= 70 ~ "7",
-          Age >= 71 & Age <= 75 ~ "8",
-          Age >= 76 & Age <= 80 ~ "9",
-          Age >= 81 & Age <= 85 ~ "10",
-          Age >= 86 & Age <= 90 ~ "11",
-          Age >= 91 & Age <= 100 ~ "12",
-          Age >= 101 & Age <= 120 ~ "13" # oldest person in the world is 117 years
+          Age >= 16 & Age <= 18 ~ 1,
+          Age >= 19 & Age <= 25 ~ 2,
+          Age >= 26 & Age <= 35 ~ 3,
+          Age >= 36 & Age <= 45 ~ 4,
+          Age >= 46 & Age <= 55 ~ 5,
+          Age >= 56 & Age <= 65 ~ 6,
+          Age >= 66 & Age <= 70 ~ 7,
+          Age >= 71 & Age <= 75 ~ 8,
+          Age >= 76 & Age <= 80 ~ 9,
+          Age >= 81 & Age <= 85 ~ 10,
+          Age >= 86 & Age <= 90 ~ 11,
+          Age >= 91 & Age <= 100 ~ 12,
+          Age >= 101 & Age <= 120 ~ 13 # oldest person in the world is 117 years
                 )
@@
 
-## Highest education (baseline, GLAD, EDGI, NBR)
+## Highest education (baseline, GLAD, EDGI, NBR, RAMP)
 Proceed along qualifications fields. If field is not blank, take that as highest qual. If field is blank, check next field. If all fields are blank, NA
@@
          employment.cses_or_equivalent_numeric
-  )
-}
-```
-
-## Highest education (baseline, RAMP)
-```{r highest level of education for ramp}
-if(RAMP == TRUE) {
-#create numeric version of the highest education variable
-employment.raw.id <- employment.raw.id %>%
-  mutate(
-    highest_education_numeric =
-      case_when(
-        employment.what_is_your_highest_level_of_education == "PhD" ~ 4,
-        employment.what_is_your_highest_level_of_education == "Postgraduate degree or equivalent" ~ 4,
-        employment.what_is_your_highest_level_of_education == "Master's degree or equivalent" ~ 4,
-        employment.what_is_your_highest_level_of_education == "Bachelor's degree or equivalent" ~ 4,
-        employment.what_is_your_highest_level_of_education == "A-level or equivalent" ~ 3,
-        employment.what_is_your_highest_level_of_education == "GCSE or equivalent" ~ 2,
-        employment.what_is_your_highest_level_of_education == "None of these" ~ 1
-      )
-    )
-
-#recode the numeric version into a factor
-employment.raw.id <- employment.raw.id %>%
-  mutate(
-    highest_education =
-      recode_factor(
-        highest_education_numeric,
-        `1` = "None",
-        `2` = "GCSE/CSE",
-        `3` = "A-levels",
-        `4` = "University")
-    )
-
-employment.raw.id %>%
-  freq(highest_education)
-}
-```
-
-Check highest education coding for RAMP
-```{r Highest education check for RAMP}
-if(RAMP == TRUE) {
-employment.raw.id %>%
-  select(highest_education,
-         employment.what_is_your_highest_level_of_education,
-         employment.what_is_your_highest_level_of_education_numeric
   )
@@
     mhd.bingeeating_disorder,
-    mhd.atypical_bingeeating_disorder
+    mhd.atypical_bingeeating_disorder,
   ) %>%
@@
 
-## RAMP
-```{r ramp mhd cols}
-if(RAMP == TRUE) {
-ramp.mhd.raw <- readRDS(file = paste0(data.raw_path,"/ramp/mhd_ramp.rds"))
-dim(ramp.mhd.raw)
-colnames(ramp.mhd.raw)
-}
-```
-
-```{r ramp mhd cleaning}
-if(RAMP == TRUE) {
-exclude_cols <- c("Sample",
-                  "ID")
-
-ramp.mhd.raw.id <- ramp.mhd.raw %>%
-  drop_na(`Login ID`) %>% # Drop NAs
-  distinct(`Login ID`, .keep_all = TRUE) %>% # Remove duplicates based on ID
-  separate(`Login ID`, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
-  separate(ID, into = "ID", sep = 7) %>%
-  mutate(
-    ID = as.numeric(ID)) %>%
-  select(
-    Sample, # Sample
-    ID, # ID
-    mhd.depression = NA.30.depression,
-    mhd.pregnancy_depression = NA.30.pregnancy_depression,
-    mhd.premenstrual_dysphoric_disorder_pmdd = NA.30.premenstrual_dysphoric_disorder_pmdd,
-    mhd.mania_hypomania_bipolar_or_manicdepression = NA.30.mania_hypomania_bipolar_or_manicdepression,
-    mhd.anxiety_nerves_or_generalised_anxiety_disorder = NA.30.anxiety_nerves_or_generalised_anxiety_disorder,
-    mhd.social_anxiety_or_social_phobia = NA.30.social_anxiety_or_social_phobia,
-    mhd.specific_phobia_e.g._phobia_of_flying = NA.30.specific_phobia_e.g._phobia_of_flying,
-    mhd.agoraphobia = NA.30.agoraphobia,
-    mhd.panic_disorder = NA.30.panic_disorder,
-    mhd.panic_attacks = NA.30.panic_attacks,
-    mhd.posttraumatic_stress_disorder_ptsd = NA.30.posttraumatic_stress_disorder_ptsd,
-    mhd.obsessivecompulsive_disorder_ocd = NA.30.obsessivecompulsive_disorder_ocd, 
-    mhd.body_dysmorphic_disorder_bdd = NA.30.body_dysmorphic_disorder_bdd,
-    mhd.skin_picking_obsessive_compulsive = NA.30.skin_picking_obsessive_compulsive,
-    mhd.anorexia_nervosa = NA.30.anorexia_nervosa,
-    mhd.atypical_anorexia_nervosa = NA.30.atypical_anorexia_nervosa,
-    mhd.bulimia_nervosa = NA.30.bulimia_nervosa,
-    mhd.bingeeating_disorder = NA.30.psychological_overeating_or_bingeeating_disorder,
-    mhd.schizophrenia = NA.30.schizophrenia,
-    mhd.schizoaffective_disorder = NA.30.schizoaffective_disorder,
-    mhd.type_psychosis_psychotic_illness = NA.30.psychosis_type_psychotic_illness,
-    mhd.personality_disorder = NA.30.personality_disorder,
-    mhd.autism_aspergers_or_autistic_spectrum_disorder = NA.30.autism_aspergers_or_autistic_spectrum_disorder,
-    mhd.attention_deficit_hyperactivity_disorder = NA.30.attention_deficit_hyperactivity_disorder,
-    mhd.personality_disorder_diagnosed = NA.30.personality_disorder_diagnosed
-  ) %>%
-  add_numeric(., exclude = exclude_cols) %>%
-  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
-  mutate_if(is.numeric, ~na_if(., -99)) %>%
-  mutate_if(is.numeric, ~na_if(., -77)) %>%
-  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
-  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
-
-# Inspect dimensions
-dim(ramp.mhd.raw.id)
-# Inspect colnames
-colnames(ramp.mhd.raw.id)
-#Differences
-dim(ramp.mhd.raw)[1]-dim(ramp.mhd.raw.id)[1]
-}
-```
-
-```{r ramp mhd copy}
-if(RAMP == TRUE) {
-  mhd.raw.id <- ramp.mhd.raw.id
-}
-```
-
 ## Grouping mental health disorders
@@
     mhd.bingeeating_disorder,
-    mhd.atypical_bingeeating_disorder
+    mhd.atypical_bingeeating_disorder,
   )
@@
 ```{r mhd obsessive_compulsive_disorders}
-if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE) {
+if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE | RAMP == TRUE) {
 mhd.raw.id <- mhd.raw.id %>%
@@
 
-```{r mhd obsessive_compulsive_disorders for ramp}
-if(RAMP == TRUE) {
-mhd.raw.id <- mhd.raw.id %>%
-  mutate(
-    obsessive_compulsive_disorders_numeric =
-      case_when(
-        mhd.obsessivecompulsive_disorder_ocd_numeric == "1" ~ 1,
-        mhd.skin_picking_obsessive_compulsive_numeric == "1" ~ 1,
-        mhd.body_dysmorphic_disorder_bdd_numeric == "1" ~ 1,
-        (mhd.obsessivecompulsive_disorder_ocd_numeric == "0" &
-        mhd.skin_picking_obsessive_compulsive_numeric == "0" &
-        mhd.body_dysmorphic_disorder_bdd_numeric == "0") ~ 0
-      )
-  )
-
-mhd.raw.id <- mhd.raw.id %>%
-  mutate(
-    obsessive_compulsive_disorders =
-      recode_factor(obsessive_compulsive_disorders_numeric,
-                    "0" = "No obsessive compulsive disorder",
-                    "1" = "Obsessive compulsive disorder",
-                    missing = NA_character_
-                    )
-  )
-
-mhd.raw.id %>%
-  freq(obsessive_compulsive_disorders)
-}
-```
-
 ```{r Check obsessive_compulsive_disorders}
-if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE) {
+if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE | RAMP == TRUE) {
 mhd.raw.id %>%
@@
     mhd.obsessive_compulsive_related_disorders_numeric,
-    mhd.body_dysmorphic_disorder_bdd,
-    mhd.body_dysmorphic_disorder_bdd_numeric
-  )
-}
-```
-
-```{r Check obsessive_compulsive_disorders ramp}
-if(RAMP == TRUE) {
-mhd.raw.id %>%
-  select(
-    obsessive_compulsive_disorders,
-    obsessive_compulsive_disorders_numeric,
-    mhd.obsessivecompulsive_disorder_ocd,
-    mhd.obsessivecompulsive_disorder_ocd_numeric,
-    mhd.skin_picking_obsessive_compulsive,
-    mhd.skin_picking_obsessive_compulsive_numeric,
     mhd.body_dysmorphic_disorder_bdd,
@@
                     "2" = "2 comorbid disoders",
-                    "3" = "3+ comorbid disoder",
+                    "3" = "3+ comorbid disoders",
                     missing = NA_character_
@@
 Create new dataframe with the derived categories
+++KT: do we want to keep individual diagnoses here as well?? 
 ```{r mhd categories}
@@
     personality_cluster_c_numeric = NA_real_,
-    personality_cluster_c = NA_real_    
+    personality_cluster_c = NA_real_,    
   )
@@
 # Add in column to tibble
-prepan.gad.raw.id$gad.sum_score_prepan_raw <- gad.scored_items_prepan$scores
+prepan.gad.raw.id$gad.sum_score_prepan_raw <- as.numeric(gad.scored_items_prepan$scores)
 
@@
 # Add in column to tibble
-prepan.pcl.raw.id$pcl.sum_score_prepan_raw <- pcl.scored_items_prepan$scores
+prepan.pcl.raw.id$pcl.sum_score_prepan_raw <- as.numeric(pcl.scored_items_prepan$scores)
 
@@
 # Add in column to tibble
-prepan.phq.raw.id$phq.sum_score_prepan_raw <- phq.scored_items_prepan$scores
+prepan.phq.raw.id$phq.sum_score_prepan_raw <- as.numeric(phq.scored_items_prepan$scores)
 
@@
 if(RAMP == TRUE) {
-  ramp.gad.raw <- readRDS(file = paste0(data.raw_path,"/ramp/gad_ramp.rds"))
-  dim(ramp.gad.raw)
-  colnames(ramp.gad.raw)
+  coping.ramp.gad.raw <- readRDS(file = paste0(data.raw_path,"/ramp/gad_coping_ramp.rds"))
+  dim(coping.ramp.gad.raw)
+  colnames(coping.ramp.gad.raw)
 }
@@
   summarytools::dfSummary(
-    ramp.gad.raw,
+    coping.ramp.gad.raw,
     graph.col = F,
@@
 if(RAMP == TRUE) {
-  exclude_cols_ramp <- c(
+  exclude_cols_coping_ramp <- c(
     "Sample",
     "ID",
-    "startDate.ramp"
-  )
-
-  ramp.gad.raw.id <- ramp.gad.raw %>%
-    drop_na(`Login ID`) %>% # Drop NAs
-    distinct(`Login ID`, .keep_all = TRUE) %>% # Remove duplicates based on ID
-    separate(`Login ID`, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
+    "startDate.coping"
+  )
+
+  coping.ramp.gad.raw.id <- coping.ramp.gad.raw %>%
+    drop_na(externalDataReference) %>% # Drop NAs
+    distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
+    separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
     mutate(ID = as.numeric(ID)
@@
       ID, # ID
-      startDate.ramp = startDate, # Rename startDate
-      gad.problems_made_difficult_care = gad.issues_made_carrying_daily, # Impairment
-      gad.pandemic_felt_feelings = gad.feelings_pandemic_felt, # Comparison to before the pandemic (retro)
-      gad.feeling_nervous_anxious_or_on_edge_retro = gad.feeling_nervous_anxious_or_on_edge.1, #retro and baseline coding are reversed for RAMP
-      gad.control_worrying_stop_retro = gad.control_worrying_stop.1, #.1 = retro
-      gad.worrying_too_much_about_different_things_retro = gad.worrying_too_much_about_different_things.1,
-      gad.trouble_relaxing_retro = gad.trouble_relaxing.1,
-      gad.sit_restless_hard_retro = gad.sit_hard_restless.1,
-      gad.becoming_easily_annoyed_or_irritable_retro = gad.becoming_easily_annoyed_or_irritable.1,
-      gad.awful_feeling_afraid_happen_retro = gad.awful_feeling_afraid_happen.1,
-      gad.feeling_nervous_anxious_or_on_edge_base = gad.feeling_nervous_anxious_or_on_edge,
-      gad.control_worrying_stop_base = gad.control_worrying_stop,
-      gad.worrying_too_much_about_different_things_base = gad.worrying_too_much_about_different_things,
-      gad.trouble_relaxing_base = gad.trouble_relaxing,
-      gad.sit_restless_hard_base = gad.sit_hard_restless,
-      gad.becoming_easily_annoyed_or_irritable_base = gad.becoming_easily_annoyed_or_irritable,
-      gad.awful_feeling_afraid_happen_base = gad.awful_feeling_afraid_happen
+      startDate.coping = startDate, # Rename startDate
+      gad.problems_made_difficult_care, # Impairment
+      gad.pandemic_felt_feelings, # Comparison to before the pandemic (retro)
+      gad.feeling_nervous_anxious_or_on_edge_retro = gad.feeling_nervous_anxious_or_on_edge,
+      gad.control_worrying_stop_retro = gad.control_worrying_stop,
+      gad.worrying_too_much_about_different_things_retro = gad.worrying_too_much_about_different_things,
+      gad.trouble_relaxing_retro = gad.trouble_relaxing,
+      gad.sit_restless_hard_retro = gad.sit_restless_hard,
+      gad.becoming_easily_annoyed_or_irritable_retro = gad.becoming_easily_annoyed_or_irritable,
+      gad.awful_feeling_afraid_happen_retro = gad.awful_feeling_afraid_happen,
+      gad.feeling_nervous_anxious_or_on_edge_base = gad.feeling_nervous_anxious_or_on_edge.1,
+      gad.control_worrying_stop_base = gad.control_worrying_stop.1,
+      gad.worrying_too_much_about_different_things_base = gad.worrying_too_much_about_different_things.1,
+      gad.trouble_relaxing_base = gad.trouble_relaxing.1,
+      gad.sit_restless_hard_base = gad.sit_restless_hard.1,
+      gad.becoming_easily_annoyed_or_irritable_base = gad.becoming_easily_annoyed_or_irritable.1,
+      gad.awful_feeling_afraid_happen_base = gad.awful_feeling_afraid_happen.1
     ) %>%
@@
   # Inspect dimensions
-  dim(ramp.gad.raw.id)
+  dim(coping.ramp.gad.raw.id)
   # Inspect colnames
-  colnames(ramp.gad.raw.id)
+  colnames(coping.ramp.gad.raw.id)
   #Differences
-  dim(ramp.gad.raw)[1]-dim(ramp.gad.raw.id)[1]
+  dim(coping.ramp.gad.raw)[1]-dim(coping.ramp.gad.raw.id)[1]
 }
@@
 if(RAMP == TRUE) {
-  coping.gad.raw.id <- ramp.gad.raw.id
+  coping.gad.raw.id <- coping.ramp.gad.raw.id
 }
@@
 # Add in column to tibble
-coping.gad.raw.id$gad.sum_score_retro_raw <- gad.scored_items_retro$scores
+coping.gad.raw.id$gad.sum_score_retro_raw <- as.numeric(gad.scored_items_retro$scores)
 
@@
 # Add in column to tibble
-coping.gad.raw.id$gad.sum_score_base_raw <- gad.scored_items_base$scores
+coping.gad.raw.id$gad.sum_score_base_raw <- as.numeric(gad.scored_items_base$scores)
 
@@
 
-## RAMP - NOT YET HAVE THE RAMP PCL DATA READY
+## RAMP
 ```{r coping ramp pcl cols}
-# if(RAMP == TRUE) {
-# coping.ramp.pcl.raw <- readRDS(file = paste0(data.raw_path,"/ramp/pcl_ramp.rds"))
-# dim(coping.ramp.pcl.raw)
-# colnames(coping.ramp.pcl.raw)
-# }
+if(RAMP == TRUE) {
+coping.ramp.pcl.raw <- readRDS(file = paste0(data.raw_path,"/ramp/pcl_coping_ramp.rds"))
+dim(coping.ramp.pcl.raw)
+colnames(coping.ramp.pcl.raw)
+}
 ```
@@
 ```{r coping ramp pcl summary labels}
-# if(RAMP == TRUE) {
-# summarytools::dfSummary(
-#   coping.ramp.pcl.raw,
-#   graph.col = F,
-#   valid.col = F,
-#   labels.col = F
-# )
-# }
+if(RAMP == TRUE) {
+summarytools::dfSummary(
+  coping.ramp.pcl.raw,
+  graph.col = F,
+  valid.col = F,
+  labels.col = F
+)
+}
 ```
@@
 ```{r coping ramp pcl cleaning}
-# if(RAMP == TRUE) {
-# coping.ramp.pcl.raw.id <- coping.ramp.pcl.raw %>%
-#   drop_na(externalDataReference) %>% # Drop NAs
-#   distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
-#   separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
-#   mutate(ID = as.numeric(ID)) %>%
-#   select(
-#     Sample, # Sample
-#     ID, # ID
-#     pcl.stressful_experience_repeated_images_base = pcl.stressful_experience_repeated_images,
-#     pcl.stressful_experience_upset_reminded_base = pcl.stressful_experience_upset_reminded, # differ to RAMP prepan
-#     pcl.stressful_situation_avoiding_activities_base = pcl.avoiding_activities_stressful_experience, # differ to RAMP prepan
-#     pcl.cut_people_feeling_distant_base = pcl.cut_people_feeling_distant,
-#     pcl.feeling_irritable_or_having_angry_outbursts_base = pcl.feeling_irritable_or_having_angry_outbursts,
-#     pcl.difficulty_concentrating_base = pcl.difficulty_concentrating,
-#     pcl.stressful_experience_repeated_images_retro = pcl.stressful_experience_repeated_images.1,
-#     pcl.stressful_experience_upset_reminded_retro = pcl.stressful_experience_upset_reminded.1,
-#     pcl.stressful_situation_avoiding_activities_retro = pcl.avoiding_activities_stressful_experience.1,
-#     pcl.cut_people_feeling_distant_retro = pcl.cut_people_feeling_distant.1,
-#     pcl.feeling_irritable_or_having_angry_outbursts_retro = pcl.feeling_irritable_or_having_angry_outbursts.1,
-#     pcl.difficulty_concentrating_retro = pcl.difficulty_concentrating.1
-#   ) %>%
-#   add_numeric(., exclude = exclude_cols) %>%
-#   mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
-#   mutate_if(is.numeric, ~na_if(., -99)) %>%
-#   mutate_if(is.numeric, ~na_if(., -77)) %>%
-#   mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
-#   mutate_if(is.factor, ~na_if(., "Don't know")) %>%
-#   mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
-#   mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
-#   mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
-#   mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
-#   mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
-#   mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
-# 
-# # Inspect dimensions
-# dim(coping.ramp.pcl.raw.id)
-# # Inspect colnames
-# colnames(coping.ramp.pcl.raw.id)
-# #Differences
-# dim(coping.ramp.pcl.raw)[1]-dim(coping.ramp.pcl.raw.id)[1]
-# }
+if(RAMP == TRUE) {
+coping.ramp.pcl.raw.id <- coping.ramp.pcl.raw %>%
+  drop_na(externalDataReference) %>% # Drop NAs
+  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
+  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
+  mutate(ID = as.numeric(ID)) %>%
+  select(
+    Sample, # Sample
+    ID, # ID
+    pcl.stressful_experience_repeated_images_base = pcl.stressful_experience_repeated_images,
+    pcl.stressful_experience_upset_reminded_base = pcl.stressful_experience_upset_reminded, # differ to RAMP prepan
+    pcl.stressful_situation_avoiding_activities_base = pcl.avoiding_activities_stressful_experience, # differ to RAMP prepan
+    pcl.cut_people_feeling_distant_base = pcl.cut_people_feeling_distant,
+    pcl.feeling_irritable_or_having_angry_outbursts_base = pcl.feeling_irritable_or_having_angry_outbursts,
+    pcl.difficulty_concentrating_base = pcl.difficulty_concentrating,
+    pcl.stressful_experience_repeated_images_retro = pcl.stressful_experience_repeated_images.1,
+    pcl.stressful_experience_upset_reminded_retro = pcl.stressful_experience_upset_reminded.1,
+    pcl.stressful_situation_avoiding_activities_retro = pcl.avoiding_activities_stressful_experience.1,
+    pcl.cut_people_feeling_distant_retro = pcl.cut_people_feeling_distant.1,
+    pcl.feeling_irritable_or_having_angry_outbursts_retro = pcl.feeling_irritable_or_having_angry_outbursts.1,
+    pcl.difficulty_concentrating_retro = pcl.difficulty_concentrating.1
+  ) %>%
+  add_numeric(., exclude = exclude_cols) %>%
+  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
+  mutate_if(is.numeric, ~na_if(., -99)) %>%
+  mutate_if(is.numeric, ~na_if(., -77)) %>%
+  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
+  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
+
+# Inspect dimensions
+dim(coping.ramp.pcl.raw.id)
+# Inspect colnames
+colnames(coping.ramp.pcl.raw.id)
+#Differences
+dim(coping.ramp.pcl.raw)[1]-dim(coping.ramp.pcl.raw.id)[1]
+}
 ```
@@
 ```{r coping ramp pcl copy}
-# if(RAMP == TRUE) {
-#   coping.pcl.raw.id <- coping.ramp.pcl.raw.id
-# }
+if(RAMP == TRUE) {
+  coping.pcl.raw.id <- coping.ramp.pcl.raw.id
+}
 ```
@@
 # Add in column to tibble
-coping.pcl.raw.id$pcl.sum_score_retro_raw <- pcl.scored_items_retro$scores
+coping.pcl.raw.id$pcl.sum_score_retro_raw <- as.numeric(pcl.scored_items_retro$scores)
 
@@
 # Add in column to tibble
-coping.pcl.raw.id$pcl.sum_score_base_raw <- pcl.scored_items_base$scores
+coping.pcl.raw.id$pcl.sum_score_base_raw <- as.numeric(pcl.scored_items_base$scores)
 
@@
 # Add in column to tibble
-coping.phq.raw.id$phq.sum_score_retro_raw <- phq.scored_items_retro$scores
+coping.phq.raw.id$phq.sum_score_retro_raw <- as.numeric(phq.scored_items_retro$scores)
 
@@
 # Add in column to tibble
-coping.phq.raw.id$phq.sum_score_base_raw <- phq.scored_items_base$scores
+coping.phq.raw.id$phq.sum_score_base_raw <- as.numeric(phq.scored_items_base$scores)
 
@@
 # Add in column to tibble
-coping.ocir.raw.id$ocir.sum_score_retro_raw <- ocir.scored_items_retro$scores
+coping.ocir.raw.id$ocir.sum_score_retro_raw <- as.numeric(ocir.scored_items_retro$scores)
 
@@
 # Add in column to tibble
-coping.ocir.raw.id$ocir.sum_score_base_raw <- ocir.scored_items_base$scores
+coping.ocir.raw.id$ocir.sum_score_base_raw <- as.numeric(ocir.scored_items_base$scores)
 
@@
   y = respiratory,
-  by = "ID"
+  by = c("Sample", "ID")
 )

### 2020-08-17 PANCHANGE_data_preprocessing2020-07-15.Rmd
minor edits for RAMP data

--- 2020-08-17 PANCHANGE_data_preprocessing2020-07-15.Rmd
@@
 #install.packages("eeptools")
+#install.packages("skimr")
 ```
@@
     ID, # ID
-    ocir.felt_pandemic_feelings, # Comparison to before the pandemic
-    ocir.i_repeatedly_check_doors_windows_drawers_etc_retro = ocir.i_repeatedly_check_doors_windows_drawers_etc.,
-    ocir.arranged_things_change_upset_retro = ocir.arranged_things_change_upset,
-    ocir.repeat_feel_numbers_retro = ocir.numbers_repeat_feel, ## Different from RAMP prepandemic
-    ocir.clean_simply_wash_feel_retro = ocir.feel_contaminated_clean_simply, ## Different from RAMP prepandemic
-    ocir.mind_upset_unpleasant_thoughts_retro = ocir.mind_upset_unpleasant_thoughts,
-    ocir.afraid_avoid_throwing_things_retro = ocir.afraid_avoid_throwing_things,
-    ocir.light_switches_water_taps_retro = ocir.light_switches_water_taps,
-    ocir.arranged_things_retro = ocir.arranged_things,
-    ocir.good_feel_bad_numbers_retro = ocir.bad_numbers_good_feel, ## Different from RAMP prepandemic
-    ocir.hands_longer_wash_retro = ocir.longer_hands_wash, ## Different from RAMP prepandemic
-    ocir.saved_things_retro = ocir.saved_things,
-    ocir.frequently_difficulty_rid_nasty_retro = ocir.frequently_rid_difficulty_nasty, ## Different from RAMP prepandemic
-    ocir.i_check_things_more_often_than_necessary_retro = ocir.i_check_things_more_often_than_necessary.,
-    ocir.arranged_properly_objects_upset_retro = ocir.arranged_properly_objects_upset,
-    ocir.feel_compelled_count_things_retro = ocir.feel_compelled_count_things,
-    ocir.strangers_touch_touched_difficult_retro = ocir.strangers_touch_touched_object, ## Different from RAMP prepandemic
-    ocir.control_difficult_find_thoughts_retro = ocir.control_find_difficult_thoughts, ## Different from RAMP prepandemic
-    ocir.i_collect_things_i_dont_need_retro = ocir.i_collect_things_i_dont_need., ## Different from RAMP prepandemic
-    ocir.i_repeatedly_check_doors_windows_drawers_etc_base = ocir.i_repeatedly_check_doors_windows_drawers_etc..1,
-    ocir.arranged_things_change_upset_base = ocir.arranged_things_change_upset.1,
-    ocir.repeat_feel_numbers_base = ocir.numbers_repeat_feel.1, ## Different from RAMP prepandemic
-    ocir.clean_simply_wash_feel_base = ocir.feel_contaminated_clean_simply.1, ## Different from RAMP prepandemic
-    ocir.mind_upset_unpleasant_thoughts_base = ocir.mind_upset_unpleasant_thoughts.1,
-    ocir.afraid_avoid_throwing_things_base = ocir.afraid_avoid_throwing_things.1,
-    ocir.light_switches_water_taps_base = ocir.light_switches_water_taps.1,
-    ocir.arranged_things_base = ocir.arranged_things.1,
-    ocir.good_feel_bad_numbers_base = ocir.bad_numbers_good_feel.1, ## Different from RAMP prepandemic
-    ocir.hands_longer_wash_base = ocir.longer_hands_wash.1, ## Different from RAMP prepandemic
-    ocir.saved_things_base = ocir.saved_things.1,
-    ocir.frequently_difficulty_rid_nasty_base = ocir.frequently_rid_difficulty_nasty.1, ## Different from RAMP prepandemic
-    ocir.i_check_things_more_often_than_necessary_base = ocir.i_check_things_more_often_than_necessary..1,
-    ocir.arranged_properly_objects_upset_base = ocir.arranged_properly_objects_upset.1,
-    ocir.feel_compelled_count_things_base = ocir.feel_compelled_count_things.1,
-    ocir.strangers_touch_touched_difficult_base = ocir.strangers_touch_touched_object.1, ## Different from RAMP prepandemic
-    ocir.control_difficult_find_thoughts_base = ocir.control_find_difficult_thoughts.1, ## Different from RAMP prepandemic
-    ocir.i_collect_things_i_dont_need_base = ocir.i_collect_things_i_dont_need..1
+    ocir.felt_pandemic_feelings = ocir.feelings_pandemic_felt, # Comparison to before the pandemic
+    ocir.saved_things_retro = ocir.saved_things.1, #reordered items to reflect questionnaire
+    ocir.i_check_things_more_often_than_necessary_retro = ocir.i_check_things_more_often_than_necessary..1, #in RAMP .1 = retrospective
+    ocir.arranged_properly_objects_upset_retro = ocir.arranged_properly_objects_upset.1,
+    ocir.feel_compelled_count_things_retro = ocir.feel_compelled_count_things.1,
+    ocir.strangers_touch_touched_difficult_retro = ocir.touch_touched_strangers_object.1,
+    ocir.control_difficult_find_thoughts_retro = ocir.find_control_difficult_thoughts.1,
+    ocir.i_collect_things_i_dont_need_retro = ocir.i_collect_things_i_dont_need..1,
+    ocir.i_repeatedly_check_doors_windows_drawers_etc_retro = ocir.i_repeatedly_check_doors_windows_drawers_etc..1,
+    ocir.arranged_things_change_upset_retro = ocir.arranged_things_change_upset.1,
+    ocir.repeat_feel_numbers_retro = ocir.numbers_repeat_feel.1, 
+    ocir.clean_simply_wash_feel_retro = ocir.feel_contaminated_clean_simply.1, 
+    ocir.mind_upset_unpleasant_thoughts_retro = ocir.unpleasant_thoughts_mind_upset.1,
+    ocir.afraid_avoid_throwing_things_retro = ocir.afraid_avoid_throwing_things.1,
+    ocir.light_switches_water_taps_retro = ocir.repeatedly_check_gas_water.1,
+    ocir.arranged_things_retro = ocir.arranged_things.1,
+    ocir.good_feel_bad_numbers_retro = ocir.bad_numbers_good_feel.1, 
+    ocir.hands_longer_wash_retro = ocir.longer_hands_wash.1, 
+    ocir.frequently_difficulty_rid_nasty_retro = ocir.difficulty_rid_frequently_nasty.1, 
+    ocir.saved_things_base = ocir.saved_things,
+    ocir.i_check_things_more_often_than_necessary_base = ocir.i_check_things_more_often_than_necessary.,
+    ocir.arranged_properly_objects_upset_base = ocir.arranged_properly_objects_upset,
+    ocir.feel_compelled_count_things_base = ocir.feel_compelled_count_things,
+    ocir.strangers_touch_touched_difficult_base = ocir.touch_touched_strangers_object, 
+    ocir.control_difficult_find_thoughts_base = ocir.find_control_difficult_thoughts, 
+    ocir.i_collect_things_i_dont_need_base = ocir.i_collect_things_i_dont_need.,
+    ocir.i_repeatedly_check_doors_windows_drawers_etc_base = ocir.i_repeatedly_check_doors_windows_drawers_etc.,
+    ocir.arranged_things_change_upset_base = ocir.arranged_things_change_upset,
+    ocir.repeat_feel_numbers_base = ocir.numbers_repeat_feel, 
+    ocir.clean_simply_wash_feel_base = ocir.feel_contaminated_clean_simply, 
+    ocir.mind_upset_unpleasant_thoughts_base = ocir.unpleasant_thoughts_mind_upset,
+    ocir.afraid_avoid_throwing_things_base = ocir.afraid_avoid_throwing_things,
+    ocir.light_switches_water_taps_base = ocir.repeatedly_check_gas_water,
+    ocir.arranged_things_base = ocir.arranged_things,
+    ocir.good_feel_bad_numbers_base = ocir.bad_numbers_good_feel, 
+    ocir.hands_longer_wash_base = ocir.longer_hands_wash, 
+    ocir.frequently_difficulty_rid_nasty_base = ocir.difficulty_rid_frequently_nasty
   ) %>%
@@
 if(RAMP == TRUE) {
-  coping.ocir.raw.id <- coping.ramp.ocir.raw.id
+  coping.ocir.raw.id <- ramp.ocir.raw.id
 }
@@
   coping.gad.raw.id,
-  coping.pcl.raw.id,
+ # coping.pcl.raw.id, #WAITING FOR PCL DATA FOR RAMP
   coping.phq.raw.id,
@@
 ```{r Exclude participants that do not report sex}
+if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE){
 dim(dat.raw)
@@
 dim(dat.raw)[1]-dim(dat.no.sex)[1]
+}
 ```
 `r dim(dat.glad.raw)[1]-dim(dat.no.sex)[1]` were excluded because they did not report their sex
+
+```{r rename dataset for ramp}
+if(RAMP == TRUE){
+#there is no sex variable in ramp
+dat.no.sex <- dat.raw
+}
+```
 
@@
 }
+
 # Difference score for retrospective and baseline phq sum scores
@@
 }
+
 # Difference score for retrospective and baseline gad sum scores
@@
 #        na_per_person_phq_base == 0 & na_per_person_phq_prepan == 0 & na_per_person_phq_retro != 0  ~ 2, #prepan and baseline data only
-        na_per_person_phq_base == 0 & na_per_person_phq_retro == 0 ~ 1,  #baseline and retro data only
+        na_per_person_phq_base == 0 & na_per_person_phq_retro == 0 ~ 1  #baseline and retro data only
 #        na_per_person_phq_base != 0 & na_per_person_phq_prepan == 0 & na_per_person_phq_retro != 0  ~ 0  #prepan data only
@@
 #        na_per_person_gad_base == 0 & na_per_person_gad_prepan == 0 & na_per_person_gad_retro != 0  ~ 2, #prepan and baseline data only
-        na_per_person_gad_base == 0 & na_per_person_gad_retro == 0 ~ 1,  #baseline and retro data only
+        na_per_person_gad_base == 0 & na_per_person_gad_retro == 0 ~ 1  #baseline and retro data only
 #        na_per_person_gad_base != 0 & na_per_person_gad_prepan == 0 & na_per_person_gad_retro != 0  ~ 0  #prepan data only
@@
 #        na_per_person_pcl_base == 0 & na_per_person_pcl_prepan == 0 & na_per_person_pcl_retro != 0  ~ 2, #prepan and baseline data only
-        na_per_person_pcl_base == 0 & na_per_person_pcl_retro == 0 ~ 1,  #baseline and retro data only
+        na_per_person_pcl_base == 0 & na_per_person_pcl_retro == 0 ~ 1  #baseline and retro data only
 #        na_per_person_pcl_base != 0 & na_per_person_pcl_prepan == 0 & na_per_person_pcl_retro != 0  ~ 0  #prepan data only
@@
 if(RAMP == TRUE){
-ramp.respiratory.raw <- readRDS(file = paste0(data.raw_path, "/ramp/respiratory_coping_ramp.rds"))
+ramp.respiratory.raw <- readRDS(file = paste0(data.raw_path, "/ramp/respiratory_ramp.rds"))
 dim(ramp.respiratory.raw)
@@
 ramp.respiratory.raw.id <- ramp.respiratory.raw %>%
-  drop_na(externalDataReference) %>% # Drop NAs
-  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
-  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
+  drop_na(`Login ID`) %>% # Drop NAs
+  distinct(`Login ID`, .keep_all = TRUE) %>% # Remove duplicates based on ID
+  separate(`Login ID`, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
   mutate(ID = as.numeric(ID)) %>%
@@
     ID, # ID
-    respiratory.breath_diarrhoea_fatigue_fever,
+    respiratory.breath_diarrhoea_fatigue_fever = respiratory.experienced_symptoms_unusual_shortness,
     respiratory.worst_ill_feel,
@@
     respiratory.skipping_meals_because_you_felt_unwell,
-    respiratory.was_your_sense_of_smell_impaired,
-    respiratory.was_your_sense_of_taste_impaired,
+    respiratory.was_your_sense_of_smell_impaired = respiratory.smell_impaired_sense_weeks,
+    respiratory.was_your_sense_of_taste_impaired = respiratory.taste_impaired_sense_weeks,
     respiratory.feeling_tiredfatigued,
@@
     respiratory.throat_swab_test_nose,
-    respiratory.coronavirus_antibody_test,
+    respiratory.coronavirus_week_antibody_test,
     respiratory.results_antibody_test
@@
 (otherwise can remove the if statement and rename the dataset 'dat.full' instead of dat.coping)
+++KT: this is not the bit that needs changing for RAMP so have taken this out. 
 ```{r clean respiratory dataset}
-if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE){
 respiratory <- respiratory.raw.id
@@
 )
-}
+
 ```
@@
 ```{r create numeric sex variable with male=1}
+
 dat.coping <- dat.coping %>%

### 2020-08-17 PANCHANGE_data_preprocessing2020-07-15.Rmd
fixed sum_scores back to  matrix

--- 2020-08-17 PANCHANGE_data_preprocessing2020-07-15.Rmd
@@
 # Add in column to tibble
-prepan.gad.raw.id$gad.sum_score_prepan_raw <- as.numeric(gad.scored_items_prepan$scores)
+prepan.gad.raw.id$gad.sum_score_prepan_raw <- gad.scored_items_prepan$scores
 
@@
 # Add in column to tibble
-prepan.pcl.raw.id$pcl.sum_score_prepan_raw <- as.numeric(pcl.scored_items_prepan$scores)
+prepan.pcl.raw.id$pcl.sum_score_prepan_raw <- pcl.scored_items_prepan$scores
 
@@
 # Add in column to tibble
-prepan.phq.raw.id$phq.sum_score_prepan_raw <- as.numeric(phq.scored_items_prepan$scores)
+prepan.phq.raw.id$phq.sum_score_prepan_raw <- phq.scored_items_prepan$scores
 
@@
 # Add in column to tibble
-coping.gad.raw.id$gad.sum_score_retro_raw <- as.numeric(gad.scored_items_retro$scores)
+coping.gad.raw.id$gad.sum_score_retro_raw <- gad.scored_items_retro$scores
 
@@
 # Add in column to tibble
-coping.gad.raw.id$gad.sum_score_base_raw <- as.numeric(gad.scored_items_base$scores)
+coping.gad.raw.id$gad.sum_score_base_raw <- gad.scored_items_base$scores
 
@@
 # Add in column to tibble
-coping.pcl.raw.id$pcl.sum_score_retro_raw <- as.numeric(pcl.scored_items_retro$scores)
+coping.pcl.raw.id$pcl.sum_score_retro_raw <- pcl.scored_items_retro$scores
 
@@
 # Add in column to tibble
-coping.pcl.raw.id$pcl.sum_score_base_raw <- as.numeric(pcl.scored_items_base$scores)
+coping.pcl.raw.id$pcl.sum_score_base_raw <- pcl.scored_items_base$scores
 
@@
 # Add in column to tibble
-coping.phq.raw.id$phq.sum_score_retro_raw <- as.numeric(phq.scored_items_retro$scores)
+coping.phq.raw.id$phq.sum_score_retro_raw <- phq.scored_items_retro$scores
 
@@
 # Add in column to tibble
-coping.phq.raw.id$phq.sum_score_base_raw <- as.numeric(phq.scored_items_base$scores)
+coping.phq.raw.id$phq.sum_score_base_raw <- phq.scored_items_base$scores
 
@@
 # Add in column to tibble
-coping.ocir.raw.id$ocir.sum_score_retro_raw <- as.numeric(ocir.scored_items_retro$scores)
+coping.ocir.raw.id$ocir.sum_score_retro_raw <- ocir.scored_items_retro$scores
 
@@
 # Add in column to tibble
-coping.ocir.raw.id$ocir.sum_score_base_raw <- as.numeric(ocir.scored_items_base$scores)
+coping.ocir.raw.id$ocir.sum_score_base_raw <- ocir.scored_items_base$scores
 

### 2020-08-17 PANCHANGE_data_preprocessing2020-07-15.Rmd
finished RAMP COVID prediction model

--- 2020-08-17 PANCHANGE_data_preprocessing2020-07-15.Rmd
@@
 
-++KT: Needs to be developed further for RAMP dataset
-COVID prediction model for COPING
 The COVID prediction model has coded the sexes opposite to our data set
 ```{r create numeric sex variable with male=1}
-
+if(GLAD == TRUE | NBR == TRUE | EDGI == TRUE){
 dat.coping <- dat.coping %>%
@@
         true = 1,
-        false = 0
-      )
-  )
+        false = 0,
+        missing = NA_real_
+      )
+  )
+}
+```
+
+Sex is no available in the RAMP dataset, therefore a proxy sex variable is created whereby Gender = Male and Transgender = No. 
+```{r create numeric sex variable with male=1 for ramp}
+if(RAMP == TRUE){
+dat.coping <- dat.coping %>%
+  mutate(
+    Sex_respiratory =
+      if_else(
+        Gender == "Male" &
+        Transgender_uncleaned == "No",
+        true = 1,
+        false = 0,
+        missing = NA_real_
+      )
+  )
+}
+```
+
+Age is not available in RAMP, only categorical age. We will assign each individual the middle value of each age category. 
+```{r create age - proxy variable for ramp}
+if(RAMP == TRUE){
+dat.coping <- dat.coping %>%
+  mutate(
+    Age =
+      case_when(
+        age_category_full == "16-18" ~ 17,
+        age_category_full == "19-25" ~ 22,
+        age_category_full == "26-35" ~ 30.5,
+        age_category_full == "36-45" ~ 40.5,
+        age_category_full == "46-55" ~ 50.5,
+        age_category_full == "56-65" ~ 60.5,
+        age_category_full == "66-70" ~ 68,
+        age_category_full == "71-75" ~ 73,
+        age_category_full == "76-80" ~ 78,
+        age_category_full == "81-85" ~ 83,
+        age_category_full == "86-90" ~ 88,
+        age_category_full == "91-100" ~ 93,
+      age_category_full == "100+" ~ 100
+      )
+  )
+}
 ```
@@
 
+#COVID prediction model
 ```{r COVID prediction model}
@@
      cumul = FALSE)
+
 ```

### 2020-08-17 PANCHANGE_data_preprocessing2020-07-15.Rmd

@@
 
-++MD: Do we want to name the RAMP dataset something different, if the algorithm will need to be changed because they have categorical age and gender not sex?
-(otherwise can remove the if statement and rename the dataset 'dat.full' instead of dat.coping)
-++KT: this is not the bit that needs changing for RAMP so have taken this out. 
 ```{r clean respiratory dataset}
@@
 )
-
 ```
@@
 # Probable COVID-19 case identification
+
 Algorithm from Menni et al. to identify probable COVID-19

### 2020-08-17 PANCHANGE_data_preprocessing2020-07-15.Rmd

@@
 ```{r Specify cohort}
-GLAD = FALSE
+GLAD = TRUE
 EDGI = FALSE
 NBR = FALSE
-RAMP = TRUE
+RAMP = FALSE
 ```

### 2020-08-17 PANCHANGE_data_merging.Rmd
created merging script

--- 2020-08-17 PANCHANGE_data_preprocessing2020-07-15.Rmd
@@
 ---
-title: "PANCHANGE_data_preprocessing"
-author: "Katie Thompson, Topher Huebel, Molly Davies, Kirstin Purves"
-date: Sys.Date()
-output:  
-  html_document:
-    df_print: paged
-    toc: yes
-    toc_depth: 2
-    toc_float:
-      collapsed: false
-    number_sections: false
-    highlight: monochrome
-    theme: cerulean
-code_folding: show
-
-html_notebook:
-  theme: cerulean
-toc: yes
-
-params:
-  glad.dem.raw: edgi.dem.raw
-
+title: "PANCHANGE_data_merging"
+author: "Christopher Huebel"
+date: "17/08/2020"
+output: html_document
 ---
@@
 
-# Specify cohort
-```{r Specify cohort}
-GLAD = FALSE
-EDGI = FALSE
-NBR = FALSE
-RAMP = TRUE
+Load packages
+```{r}
+library(tidyverse)
+library(skimr)
 ```
-
-#Packages
-Install packages (if they are not available in your version of R)
-```{r Installing packages}
-#install.packages("summarytools")
-#install.packages("tidyverse")
-#install.packages("psych")
-#install.packages("eeptools")
-#install.packages("skimr")
-```
-
-Load packages
-```{r Load packages}
-library(knitr)
-library(summarytools)
-library(psych)
-library(eeptools) # Needed to calculate age from birthdate
-library(tidyverse)
-```
-
-# Colour palettes
-Define colours for plotting this are the standard coping colours
-```{r Colour palettes: COPING}
-COPINGpalette2 <- c("#78D9C5",
-                    "#F5BE5E")
-
-COPINGpalette3 <- c("#78D9C5",
-                    "#F5BE5E",
-                    "#EEB6E9")
-
-COPINGpalette4 <- c("#78D9C5",
-                    "#F5BE5E",
-                    "#EEB6E9",
-                    "#DBDB73")
-
-COPINGpalette5 <- c("#78D9C5",
-                    "#F5BE5E",
-                    "#EEB6E9",
-                    "#DBDB73", 
-                    "#FFED98")
-
-COPINGpalette6 <- c("#78D9C5",
-                    "#F5BE5E",
-                    "#EEB6E9",
-                    "#DBDB73",
-                    "#FFED98",
-                    "#BFD2EB")
-
-COPINGpalette7 <- c("#78D9C5",
-                    "#F5BE5E",
-                    "#EEB6E9",
-                    "#DBDB73", 
-                    "#FFED98",
-                    "#BFD2EB", 
-                    "#808080")
-
-COPINGpaletteGRAD <- c("#F5BE5E",
-                       "#FFD284",
-                       "#FFEED1",
-                       "#B5B5B5",
-                       "#DEFFF8",
-                       "#94F6E1",
-                       "#78D9C5")
-
-COPINGNeuCenterpalette <- c("#78D9C5",
-                            "#808080",
-                            "#F5BE5E")
-
-RAMPworseGRADpalette <- c("#78D9C5",
-                          "#FFEED1",
-                          "#F5BE5E",
-                          "#FFB1B5")
-GLADpalette = c("#efc00b", 
-                "#b7dee8")  
-```
-
-Choose in this chunk which palette to use
-04.07.2020 - Default to 2 colour COPING palette
-```{r Choose colour palette}
-palette = COPINGpalette2
-```
-
-#Add_numeric function
-Function used to convert character variables into numeric variables. 
-```{r add_numeric function}
-add_numeric <- function(dat, exclude = NULL) {
-  dat_fct <- sjlabelled::as_label(dat)
-
-  dat <- dat[!colnames(dat) %in% exclude]
-  colnames(dat) <- paste(colnames(dat), "numeric", sep = "_")
-  return(bind_cols(dat_fct, dat))
-}
-```
-
-# Data import and merging
-
-Note: GLAD only receives current measures and RAMP questionnaire
-Note: All COPING surveys are separate surveys
 
@@
 
-# Demographics
-## GLAD
-### Read in data
-```{r glad dem cols}
-if(GLAD == TRUE){
-glad.dem.raw <- readRDS(file = paste0(data.raw_path, "/glad/dem_glad.rds"))
-dim(glad.dem.raw)
-colnames(glad.dem.raw)
-}
+# Import data
+```{r export data}
+glad <- read_rds(path = paste0(data_path, "/glad.rds"))
+
+edgi <- read_rds(path = paste0(data_path, "/edgi.rds"))
+
+nbr <- read_rds(path = paste0(data_path, "/nbr.rds"))
+
+ramp <- read_rds(path = paste0(data_path, "/ramp.rds"))
 ```
 
-### Select variables
-```{r glad dem cleaning}
-if(GLAD == TRUE){
-exclude_cols_dem <- c("ID",
-                  "Sample",
-                  "startDate.prepandemic",
-                  "Age_uncleaned",
-                  "EduYrs")
-
-glad.dem.raw.id <- glad.dem.raw %>%
-  drop_na(externalDataReference) %>% # Drop NAs
-  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
-  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
-  mutate(ID = as.numeric(ID)) %>%
-  select(
-         Sample, # Sample
-         ID, # ID
-         startDate.prepandemic = startDate, #Date when participant signed up to glad
-         Age_uncleaned = demographics.how_old_are_you_now.txt, # Age
-         Gender = demographics.which_gender_do_you_identify_with, # Gender
-         Sex = demographics.select_questionnaire_items_medical, #Sex
-         EduYrs = demographics.school_education_school_years.txt, # Years in education
-         demographics.college_or_university_degree, # level of education - univeristy
-         demographics.a_levelsas_levels_or_equivalent, # level of education - alevel
-         demographics.o_levelsgcses_or_equivalent, # level of education - gcse
-         demographics.cses_or_equivalent, # level of education - cse
-         demographics.nvq_or_hnd_or_hnc_or_equivalent, # level of education - nvq
-         Ethnicity = demographics.questions_based_ethnic_origin # Ethnicity
-         ) %>%
-  add_numeric(., exclude = exclude_cols_dem) %>%
-  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
-  mutate_if(is.numeric, ~na_if(., -99)) %>%
-  mutate_if(is.numeric, ~na_if(., -77)) %>%
-  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
-  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
-
-# Inspect dimensions
-dim(glad.dem.raw.id)
-# Inspect colnames
-colnames(glad.dem.raw.id)
-#Differences
-dim(glad.dem.raw)[1]-dim(glad.dem.raw.id)[1]
-}
-```
-
-```{r glad copy dem}
-if(GLAD == TRUE){
-dem.raw.id <- glad.dem.raw.id
-}
-```
-
-```{r glad dem summary}
-if(GLAD == TRUE) {
-summarytools::dfSummary(
-  dem.raw.id,
-  graph.col = F,
-  valid.col = F,
-  labels.col = F)
-}
-```
-
-## EDGI
-### Read in data
-```{r edgi dem cols}
-if(EDGI == TRUE){
-  edgi.dem.raw <- readRDS(file = paste0(data.raw_path, "/edgi/dem_edgi.rds"))
-  dim(edgi.dem.raw)
-  colnames(edgi.dem.raw)
-}
-```
-
-### Select variables
-```{r edgi dem cleaning}
-if(EDGI == TRUE){
-  exclude_cols_dem <- c("ID",
-                        "Sample",
-                        "startDate.prepandemic",
-                        "Age_uncleaned",
-                        "EduYrs")
-
-  edgi.dem.raw.id <- edgi.dem.raw %>%
-    drop_na(externalDataReference) %>% # Drop NAs
-    distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
-    separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
-    mutate(ID = as.numeric(ID)) %>%
-    select(
-      Sample, # Sample
-      ID, # ID
-      startDate.prepandemic = startDate, #Date when participant signed up to edgi
-      Age_uncleaned = demographics.how_old_are_you_now.txt, # Age
-      Gender = demographics.what_gender_do_you_identify_with, # Gender (which [GLAD] vs what [EDGI])
-      Sex = demographics.select_questionnaire_items_birth, #Sex (different to GLAD)
-      EduYrs = demographics.university_education_attend_school.txt, # Years in education (different to GLAD)
-      demographics.college_or_university_degree, # level of education - univeristy
-      demographics.a_levelsas_levels_or_equivalent, # level of education - alevel
-      demographics.o_levelsgcses_or_equivalent, # level of education - gcse
-      demographics.cses_or_equivalent, # level of education - cse
-      demographics.nvq_or_hnd_or_hnc_or_equivalent, # level of education - nvq
-      Ethnicity = demographics.what_is_your_ethnic_origin # Ethnicity (different to GLAD)
-    ) %>%
-    add_numeric(., exclude = exclude_cols_dem) %>%
-    mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
-    mutate_if(is.numeric, ~na_if(., -99)) %>%
-    mutate_if(is.numeric, ~na_if(., -77)) %>%
-    mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
-    mutate_if(is.factor, ~na_if(., "Don't know")) %>%
-    mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
-    mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
-    mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
-    mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
-    mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
-    mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
-
-  # Inspect dimensions
-  dim(edgi.dem.raw.id)
-  # Inspect colnames
-  colnames(edgi.dem.raw.id)
-  #Differences
-  dim(edgi.dem.raw)[1]-dim(edgi.dem.raw.id)[1]
-}
-```
-
-```{r edgi copy dem}
-if(EDGI == TRUE){
-  dem.raw.id <- edgi.dem.raw.id
-}
-```
-
-```{r edgi dem summary}
-if(EDGI == TRUE) {
-summarytools::dfSummary(
-  dem.raw.id,
-  graph.col = F,
-  valid.col = F,
-  labels.col = F)
-}
-```
-
-## NBR
-### Read in data
-```{r nbr dem cols}
-if(NBR == TRUE){
-  nbr.dem.raw <- readRDS(file = paste0(data.raw_path, "/nbr/dem_nbr.rds"))
-  dim(nbr.dem.raw)
-  colnames(nbr.dem.raw)
-}
-```
-
-### Select variables
-```{r nbr dem cleaning}
-if(NBR == TRUE){
-  exclude_cols_dem <- c("ID",
-                        "Sample",
-                        "Age_uncleaned",
-                        "EduYrs")
-
-  nbr.dem.raw.id <- nbr.dem.raw %>%
-    drop_na(subjectid) %>% # Drop NAs
-    distinct(subjectid, .keep_all = TRUE) %>% # Remove duplicates based on ID
-    separate(subjectid, into = c("Sample", "ID.intm"), sep = 6) %>% # Split ID in Sample and Number
-    separate(ID.intm, into = "ID", sep = 7) %>%
-    mutate(ID = as.numeric(ID)) %>%
-    select(
-      Sample, # Sample
-      ID, # ID
-#      startDate.coping, # Date when participant signed up to nbr (is in the coping gad chunk)
-#      Age_uncleaned = demographics.how_old_are_you_now.txt, # Age
-      Birthyear_unc = demographics.year, # Birthyear
-      Birthmonth = demographics.month, #Birthmonth
-      Birthday = demographics.day, #Birthday
-      Gender = demographics.which_gender_do_you_identify_with, # Gender
-      Sex = demographics.select_questionnaire_items_medical, #Sex
-#      Ethnicity = demographics.questions_based_ethnic_origin # Ethnicity
-    ) %>%
-    add_numeric(., exclude = exclude_cols_dem) %>%
-    mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
-    mutate_if(is.numeric, ~na_if(., -99)) %>%
-    mutate_if(is.numeric, ~na_if(., -77)) %>%
-    mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
-    mutate_if(is.factor, ~na_if(., "Don't know")) %>%
-    mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
-    mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
-    mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
-    mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
-    mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
-    mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
-
-  # Inspect dimensions
-  dim(nbr.dem.raw.id)
-  # Inspect colnames
-  colnames(nbr.dem.raw.id)
-  #Differences
-  dim(nbr.dem.raw)[1]-dim(nbr.dem.raw.id)[1]
-}
-```
-
-```{r nbr dem calculating age from birthday}
-if(NBR == TRUE) {
-#add 1900 to birthyear
-nbr.dem.raw.id$Birthyear_numeric <- nbr.dem.raw.id$Birthyear_unc_numeric + 1900
-
-#create dob as date format
-nbr.dem.raw.id$Birthdate <- as.Date(paste(nbr.dem.raw.id$Birthyear_numeric,
-                                  nbr.dem.raw.id$Birthmonth_numeric,
-                                  nbr.dem.raw.id$Birthday_numeric,
-                                  sep = "-"))
-
-head(nbr.dem.raw.id$Birthdate)
-
-#Calculate dem.age(remove NAs as it throws an error)
-ages <- age_calc(na.omit(nbr.dem.raw.id$Birthdate), enddate = Sys.Date(), units = "years")
-
-#Create dem.agecolumn
-nbr.dem.raw.id$Age_uncleaned<- NA
-
-#Populate with values (excluding NAs)
-nbr.dem.raw.id$Age_uncleaned[!is.na(nbr.dem.raw.id$Birthdate)] <- ages
-
-#Round age down
-nbr.dem.raw.id$Age_uncleaned <- floor(nbr.dem.raw.id$Age_uncleaned)
-
-#Visualise
-head(nbr.dem.raw.id$Age_uncleaned)
-head(nbr.dem.raw.id$Birthdate)
-}
-```
-
-### Cohort information
-Information on INTERVAL, COMPARE, and STRIDES
-http://www.donorhealth-btru.nihr.ac.uk/studies/
-```{r nbr cohort information}
-if(NBR == TRUE){
-  nbr.cohort.raw <- readxl::read_xlsx(
-    path = paste0(data.raw_path, "/nbr/coping_participants_export_20200730.xlsx")
-    )
-
-  dim(nbr.cohort.raw)
-  colnames(nbr.cohort.raw)
-  }
-```
-
-```{r nbr cohort cleaning}
-if(NBR == TRUE) {
-exclude_cols_cohort_nbr <- c("ID",
-                  "Sample",
-                  "Age_uncleaned",
-                  "EduYrs")
-
-nbr.cohort.raw.id <- nbr.cohort.raw %>%
-  drop_na(`NBR ID`) %>% # Drop NAs
-  distinct(`NBR ID`, .keep_all = TRUE) %>% # Remove duplicates based on ID
-  separate(`NBR ID`, into = c("Sample", "ID.intm"), sep = 6) %>% # Split ID in Sample and Number
-  separate(ID.intm, into = "ID", sep = 7) %>%
-  mutate(
-    ID = as.numeric(ID)) %>%
-  select(
-         Sample, # Sample
-         ID, # ID
-         Cohort = cohort, #cohort information
-#         startDate.coping, #Date when participant signed up to NBR COPING (is in the coping gad chunk)
-#         Age_uncleaned = age, # Age
-#         Gender = gender, # Gender
-#         Sex = demographics.select_questionnaire_items_medical, #Sex
-#         EduYrs = demographics.school_education_school_years.txt, # Years in education
-#         demographics.college_or_university_degree, # level of education - univeristy
-#         demographics.a_levelsas_levels_or_equivalent, # level of education - alevel
-#         demographics.o_levelsgcses_or_equivalent, # level of education - gcse
-#         demographics.cses_or_equivalent, # level of education - cse
-#         demographics.nvq_or_hnd_or_hnc_or_equivalent, # level of education - nvq
-         Ethnicity.unc = ethnicity # Ethnicity
-         ) %>%
-  add_numeric(., exclude = exclude_cols_cohort_nbr) %>%
-  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
-  mutate_if(is.numeric, ~na_if(., -99)) %>%
-  mutate_if(is.numeric, ~na_if(., -77)) %>%
-  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
-  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
-
-# Inspect dimensions
-dim(nbr.cohort.raw.id)
-# Inspect colnames
-colnames(nbr.cohort.raw.id)
-#Differences
-dim(nbr.cohort.raw)[1]-dim(nbr.cohort.raw.id)[1]
-}
-```
-
-```{r nbr cohort recode ethnicity}
-if(NBR == TRUE) {
-#Recode details ethnicity info
-nbr.cohort.raw.id$Ethnicity_full <- recode_factor(nbr.cohort.raw.id$Ethnicity.unc,
-                                             "A" = "White - British",
-                                             "B" = "White - Irish",
-                                             "C" = "White - Other",
-                                             "D" = "Mixed - White & Black Caribbean",
-                                             "E" = "Mixed - White & Black African",
-                                             "F" = "Mixed - White & Asian",
-                                             "G" = "Mixed - Other",
-                                             "H" = "Asian - Indian",
-                                             "J" = "Asian - Pakistani",
-                                             "K" = "Asian - Bangladeshi",
-                                             "L" = "Asian - Other",
-                                             "M" = "Black - Caribbean",
-                                             "N" = "Black - African",
-                                             "P" = "Black - Other",
-                                             "R" = "Chinese - Chinese",
-                                             "S" = "Chinese - Other",
-                                             "W" = NULL, ## Asking NBR what this level means
-                                             "Z" = NULL,
-                                             "99" = NULL)
-
-#Match GLAD/EDGI/RAMP categories
-nbr.cohort.raw.id$Ethnicity <- recode_factor(nbr.cohort.raw.id$Ethnicity.unc,
-                                             "A" = "White, white European or Caucasian",
-                                             "B" = "White, white European or Caucasian",
-                                             "C" = "White, white European or Caucasian",
-                                             "D" = "Mixed or multiple ethnic origins",
-                                             "E" = "Mixed or multiple ethnic origins",
-                                             "F" = "Mixed or multiple ethnic origins",
-                                             "G" = "Mixed or multiple ethnic origins",
-                                             "H" = "Asian or Asian British (including Chinese)",
-                                             "J" = "Asian or Asian British (including Chinese)",
-                                             "K" = "Asian or Asian British (including Chinese)",
-                                             "L" = "Asian or Asian British (including Chinese)",
-                                             "M" = "Black or Black British",
-                                             "N" = "Black or Black British",
-                                             "P" = "Black or Black British",
-                                             "R" = "Asian or Asian British (including Chinese)",
-                                             "S" = "Asian or Asian British (including Chinese)",
-                                             "W" = NULL, ## Asking NBR what this level means
-                                             "Z" = NULL,
-                                             "99" = NULL)
-}
-```
-
-```{r nbr combine demographics}
-if(NBR == TRUE){
-dem.raw.id <- left_join(nbr.dem.raw.id, nbr.cohort.raw.id, by = c("Sample", "ID"))
-
-# Inspect dimensions
-dim(dem.raw.id)
-# Inspect colnames
-colnames(dem.raw.id)
-#Differences
-dim(nbr.dem.raw.id)[1]-dim(dem.raw.id)[1]
-}
-```
-
-```{r nbr dem summary}
-if(NBR == TRUE) {
-summarytools::dfSummary(
-  dem.raw.id,
-  graph.col = F,
-  valid.col = F,
-  labels.col = F)
-}
-```
-
-## RAMP
-### Read in data
-```{r ramp dem cols}
-if(RAMP == TRUE){
-  ramp.dem.raw <- readRDS(file = paste0(data.raw_path, "/ramp/dem_ramp.rds"))
-  dim(ramp.dem.raw)
-  colnames(ramp.dem.raw)
-}
-```
-
-### Select variables
-```{r ramp dem cleaning}
-if(RAMP == TRUE){
-  exclude_cols_dem <- c("ID",
-                        "Sample")
-
-  ramp.dem.raw.id <- ramp.dem.raw %>%
-    drop_na(`Login ID`) %>% # Drop NAs
-    distinct(`Login ID`, .keep_all = TRUE) %>% # Remove duplicates based on ID
-    separate(`Login ID`, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
-    mutate(ID = as.numeric(ID)) %>%
-    select(
-      Sample, # Sample
-      ID, # ID
-#      startDate.coping, #Date when participant signed up to ramp  (is in the coping gad chunk)
-      age_category_full = demographics.how_old_are_you, # Age
-      Gender = demographics.which_gender_do_you_identify_with, # Gender (what [GLAD] vs which [RAMP])
-#     EduYrs = demographics.university_education_attend_school.txt, # Years in education - not in RAMP dataset
-#     demographics.college_or_university_degree, # level of education - univeristy - level of education is in employment file
-#     demographics.a_levelsas_levels_or_equivalent, # level of education - alevel
-#     demographics.o_levelsgcses_or_equivalent, # level of education - gcse
-#     demographics.cses_or_equivalent, # level of education - cse
-#     demographics.nvq_or_hnd_or_hnc_or_equivalent, # level of education - nvq
-      Transgender_uncleaned = demographics.do_you_identify_as_transgender,
-      Ethnicity = demographics.what_is_your_ethnic_origin # Ethnicity
-    ) %>%
-    add_numeric(., exclude = exclude_cols_dem) %>%
-    mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
-    mutate_if(is.numeric, ~na_if(., -99)) %>%
-    mutate_if(is.numeric, ~na_if(., -77)) %>%
-    mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
-    mutate_if(is.factor, ~na_if(., "Don't know")) %>%
-    mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
-    mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
-    mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
-    mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
-    mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
-    mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
-
-  # Inspect dimensions
-  dim(ramp.dem.raw.id)
-  # Inspect colnames
-  colnames(ramp.dem.raw.id)
-  #Differences
-  dim(ramp.dem.raw)[1]-dim(ramp.dem.raw.id)[1]
-}
-```
-
-```{r ramp copy dem}
-if(RAMP == TRUE){
-  dem.raw.id <- ramp.dem.raw.id
-}
-```
-
-# Demographics variable creation
-## Clean Age variable
-Age outlier
-```{r age outlier}
-if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE ) {
-# Define age limits 
-age_upper_limit = 117 # The oldest person in the world is 117 years
-age_lower_limit = 16
-
-# identify number of outliers
-length(
-  which(
-  dem.raw.id$Age_uncleaned > age_upper_limit |
-    dem.raw.id$Age_uncleaned < age_lower_limit
-     )
-)
-
-# remove age outliers
-dem.raw.id <- dem.raw.id %>%
-  mutate(
-    Age = 
-      if_else(
-        Age_uncleaned > age_upper_limit | 
-        Age_uncleaned < age_lower_limit, 
-        true = NA_real_,
-        false = Age_uncleaned,
-        missing = NA_real_
-      )
-  )
-
-# Inspect variable
-dem.raw.id %>%
-  descr(
-    Age,
-    #stats = "common"
-    )
-}
-```
-
-## Categorise age into groups 
-In RAMP, age is indicated categorically: 16-18, 19-25, 26-35, 36-45, 46-55, 56-65, 66-70, 71-75, 76-80, 81-85, 86-90, 91-100, 100+
-Age categories in GLAD, EDGI and NBR have been created to reflect this
-```{r Age groups}
-if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE) {
-# Create categorical age groups per 10 years
-dem.raw.id <- dem.raw.id %>%
-  mutate(
-    age_category_numeric =
-      case_when(
-          Age >= 16 & Age <= 18 ~ "1",
-          Age >= 19 & Age <= 25 ~ "2",
-          Age >= 26 & Age <= 35 ~ "3",
-          Age >= 36 & Age <= 45 ~ "4",
-          Age >= 46 & Age <= 55 ~ "5",
-          Age >= 56 & Age <= 65 ~ "6",
-          Age >= 66 & Age <= 70 ~ "7",
-          Age >= 71 & Age <= 75 ~ "8",
-          Age >= 76 & Age <= 80 ~ "9",
-          Age >= 81 & Age <= 85 ~ "10",
-          Age >= 86 & Age <= 90 ~ "11",
-          Age >= 91 & Age <= 100 ~ "12",
-          Age >= 101 & Age <= 120 ~ "13" # oldest person in the world is 117 years
-                )
-      )
-
-dem.raw.id <- dem.raw.id %>%
-    mutate(
-      age_category_full =
-        recode_factor(
-          age_category_numeric, 
-          "1" = "16 to 18 years",
-          "2" = "19 to 25 years",
-          "3" = "26 to 35 years",
-          "4" = "36 to 45 years",
-          "5" = "46 to 55 years",
-          "6" = "56 to 65 years",
-          "7" = "66 to 70 years",
-          "8" = "71 to 75 years",
-          "9" = "76 to 80 years",
-          "10" = "81 to 85 years",
-          "11" = "86 to 90 years",
-          "12" = "91 to 100 years",
-          "13" = "Above 100 years"
-          )
-    )
-
-dem.raw.id %>%
-  freq(age_category_full)
-}
-```
-
-## Highest education (prepandemic, GLAD & EDGI)
-
-Proceed along qualifications fields. If field is not blank, take that as highest qual. If field is blank, check next field. If all fields are blank, NA
-Assumes University degree > A level > NVQ > GCSE/O Level/CSE
-```{r Highest education prepandemic}
-if(GLAD == TRUE | EDGI == TRUE) {
-#create numeric version of the highest education variable
-dem.raw.id <- dem.raw.id %>%
-  mutate(
-    highest_education_prepan_numeric =
-      case_when(
-        demographics.college_or_university_degree_numeric == "1" ~ 4,
-        demographics.a_levelsas_levels_or_equivalent_numeric == "1" ~ 3,
-        demographics.nvq_or_hnd_or_hnc_or_equivalent_numeric == "1" ~ 2,
-        demographics.o_levelsgcses_or_equivalent_numeric == "1" ~ 1,
-        demographics.cses_or_equivalent_numeric == "1" ~ 1)
-    )
-
-#recode the numeric version into a factor
-dem.raw.id <- dem.raw.id %>%
-  mutate(
-    highest_education_prepan =
-      recode_factor(
-        highest_education_prepan_numeric,
-        `1` = "GCSE/CSE",
-        `2` = "NVQ",
-        `3` = "A-levels",
-        `4` = "University")
-    )
-
-dem.raw.id %>%
-  freq(highest_education_prepan)
-}
-```
-
-Check highest education coding
-```{r Highest education prepandemic check}
-if(GLAD == TRUE | EDGI == TRUE) {
-dem.raw.id %>%
-  select(highest_education_prepan,
-        demographics.college_or_university_degree_numeric,
-        demographics.a_levelsas_levels_or_equivalent_numeric,
-        demographics.nvq_or_hnd_or_hnc_or_equivalent_numeric,
-        demographics.o_levelsgcses_or_equivalent_numeric,
-        demographics.cses_or_equivalent_numeric
-  )
-}
-```
-
-```{r dem summary}
-if(GLAD == TRUE | EDGI == TRUE) {
-summarytools::dfSummary(
-  dem.raw.id,
-  graph.col = F,
-  valid.col = F,
-  labels.col = F)
-}
-```
-
-# Employment
-
-## GLAD
-### Read in data
-```{r glad employment cols}
-if(GLAD == TRUE){
-glad.employment.raw <- readRDS(file = paste0(data.raw_path, "/glad/employment_coping_glad.rds"))
-dim(glad.employment.raw)
-colnames(glad.employment.raw)
-}
-```
-
-### Select variables
-```{r glad employment cleaning}
-if(GLAD == TRUE){
-exclude_cols_employment <- c("ID",
-                  "Sample")
-
-glad.employment.raw.id <- glad.employment.raw %>%
-  drop_na(externalDataReference) %>% # Drop NAs
-  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
-  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
-  mutate(
-    ID = as.numeric(ID)
-    ) %>%
-  select(
-         Sample, # Sample
-         ID, # ID
-         employment.phd, # level of education - univeristy
-         employment.masters_degree_or_equivalent, # level of education - univeristy
-         employment.postgraduate_degree_or_equivalent, # level of education - univeristy
-         employment.bachelors_degree_or_equivalent, # level of education - univeristy
-         employment.a_levelsas_levels_or_equivalent, # level of education - alevel
-         employment.o_levelsgcses_or_equivalent, # level of education - gcse
-         employment.cses_or_equivalent, # level of education - cse
-         employment.nvq_or_hnd_or_hnc_or_equivalent, # level of education - nvq
-         employment.government_work_key_workers # key worker status
-         ) %>%
-  add_numeric(., exclude = exclude_cols_employment) %>%
-  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
-  mutate_if(is.numeric, ~na_if(., -99)) %>%
-  mutate_if(is.numeric, ~na_if(., -77)) %>%
-  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
-  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
-
-# Inspect dimensions
-dim(glad.employment.raw.id)
-# Inspect colnames
-colnames(glad.employment.raw.id)
-#Differences
-dim(glad.employment.raw)[1]-dim(glad.employment.raw.id)[1]
-}
-```
-
-```{r glad copy employment}
-if(GLAD == TRUE){
-  employment.raw.id <- glad.employment.raw.id
-}
-```
-
-## EDGI
-### Read in data
-```{r edgi employment cols}
-if(EDGI == TRUE){
-edgi.employment.raw <- readRDS(file = paste0(data.raw_path, "/edgi/employment_coping_edgi.rds"))
-dim(edgi.employment.raw)
-colnames(edgi.employment.raw)
-}
-```
-
-### Select variables
-```{r edgi employment cleaning}
-if(EDGI == TRUE){
-exclude_cols_employment <- c("ID",
-                  "Sample")
-
-edgi.employment.raw.id <- edgi.employment.raw %>%
-  drop_na(externalDataReference) %>% # Drop NAs
-  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
-  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
-  mutate(
-    ID = as.numeric(ID)
-    ) %>%
-  select(
-         Sample, # Sample
-         ID, # ID
-         employment.phd, # level of education - univeristy
-         employment.masters_degree_or_equivalent, # level of education - univeristy
-         employment.postgraduate_degree_or_equivalent, # level of education - univeristy
-         employment.bachelors_degree_or_equivalent, # level of education - univeristy
-         employment.a_levelsas_levels_or_equivalent, # level of education - alevel
-         employment.o_levelsgcses_or_equivalent, # level of education - gcse
-         employment.cses_or_equivalent, # level of education - cse
-         employment.nvq_or_hnd_or_hnc_or_equivalent, # level of education - nvq
-         employment.government_work_key_workers # key worker status
-         ) %>%
-  add_numeric(., exclude = exclude_cols_employment) %>%
-  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
-  mutate_if(is.numeric, ~na_if(., -99)) %>%
-  mutate_if(is.numeric, ~na_if(., -77)) %>%
-  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
-  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
-
-# Inspect dimensions
-dim(edgi.employment.raw.id)
-# Inspect colnames
-colnames(edgi.employment.raw.id)
-#Differences
-dim(edgi.employment.raw)[1]-dim(edgi.employment.raw.id)[1]
-}
-```
-
-```{r edgi copy employment}
-if(EDGI == TRUE){
-  employment.raw.id <- edgi.employment.raw.id
-}
-```
-
-## NBR
-### Read in data
-```{r nbr employment cols}
-if(NBR == TRUE){
-nbr.employment.raw <- readRDS(file = paste0(data.raw_path, "/nbr/employment_coping_nbr.rds"))
-dim(nbr.employment.raw)
-colnames(nbr.employment.raw)
-}
-```
-
-### Select variables
-```{r nbr employment cleaning}
-if(NBR == TRUE){
-exclude_cols_employment <- c("ID",
-                  "Sample")
-
-nbr.employment.raw.id <- nbr.employment.raw %>%
-  drop_na(subjectid) %>% # Drop NAs
-  distinct(subjectid, .keep_all = TRUE) %>% # Remove duplicates based on ID
-  separate(subjectid, into = c("Sample", "ID.intm"), sep = 6) %>% # Split ID in Sample and Number
-  separate(ID.intm, into = "ID", sep = 7) %>%
-  mutate(
-    ID = as.numeric(ID)) %>%
-  select(
-         Sample, # Sample
-         ID, # ID
-         employment.phd, # level of education - univeristy
-         employment.masters_degree_or_equivalent, # level of education - univeristy
-         employment.postgraduate_degree_or_equivalent, # level of education - univeristy
-         employment.bachelors_degree_or_equivalent, # level of education - univeristy
-         employment.a_levelsas_levels_or_equivalent, # level of education - alevel
-         employment.o_levelsgcses_or_equivalent, # level of education - gcse
-         employment.cses_or_equivalent, # level of education - cse
-         employment.nvq_or_hnd_or_hnc_or_equivalent, # level of education - nvq
-         employment.government_work_key_workers # key worker status
-         ) %>%
-  add_numeric(., exclude = exclude_cols_employment) %>%
-  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
-  mutate_if(is.numeric, ~na_if(., -99)) %>%
-  mutate_if(is.numeric, ~na_if(., -77)) %>%
-  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
-  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
-
-# Inspect dimensions
-dim(nbr.employment.raw.id)
-# Inspect colnames
-colnames(nbr.employment.raw.id)
-#Differences
-dim(nbr.employment.raw)[1]-dim(nbr.employment.raw.id)[1]
-head(nbr.employment.raw.id
-     )
-}
-```
-
-```{r nbr copy employment}
-if(NBR == TRUE){
-  employment.raw.id <- nbr.employment.raw.id
-}
-```
-
-## RAMP
-### Read in data
-```{r ramp employment cols}
-if(RAMP == TRUE){
-ramp.employment.raw <- readRDS(file = paste0(data.raw_path, "/ramp/employment_ramp.rds"))
-dim(ramp.employment.raw)
-colnames(ramp.employment.raw)
-}
-```
-
-### Select variables
-```{r ramp employment cleaning}
-if(RAMP == TRUE){
-exclude_cols_employment <- c("ID",
-                  "Sample")
-
-ramp.employment.raw.id <- ramp.employment.raw %>%
-  drop_na(`Login ID`) %>% # Drop NAs
-  distinct(`Login ID`, .keep_all = TRUE) %>% # Remove duplicates based on ID
-  separate(`Login ID`, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
-  mutate(
-    ID = as.numeric(ID)
-    ) %>%
-  select(
-         Sample, # Sample
-         ID, # ID
-         employment.what_is_your_highest_level_of_education, #highest level of edcuation
-         employment.government_work_key_workers # key worker status
-         ) %>%
-  add_numeric(., exclude = exclude_cols_employment) %>%
-  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
-  mutate_if(is.numeric, ~na_if(., -99)) %>%
-  mutate_if(is.numeric, ~na_if(., -77)) %>%
-  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
-  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
-
-# Inspect dimensions
-dim(ramp.employment.raw.id)
-# Inspect colnames
-colnames(ramp.employment.raw.id)
-#Differences
-dim(ramp.employment.raw)[1]-dim(ramp.employment.raw.id)[1]
-}
-```
-
-```{r ramp copy employment}
-if(RAMP == TRUE){
-  employment.raw.id <- ramp.employment.raw.id
-}
-```
-
-## Highest education (baseline, GLAD, EDGI, NBR)
-Proceed along qualifications fields. If field is not blank, take that as highest qual. If field is blank, check next field. If all fields are blank, NA
-Assumes University degree > A level > NVQ > GCSE/O Level/CSE
-```{r Highest education baseline}
-if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE) {
-#create numeric version of the highest education variable
-employment.raw.id <- employment.raw.id %>%
-  mutate(
-    highest_education_numeric =
-      case_when(
-        employment.phd_numeric == "1" ~ 4,
-        employment.masters_degree_or_equivalent_numeric == "1" ~ 4,
-        employment.postgraduate_degree_or_equivalent_numeric == "1" ~ 4,
-        employment.bachelors_degree_or_equivalent_numeric == "1" ~ 4,
-        employment.a_levelsas_levels_or_equivalent_numeric == "1" ~ 3,
-        employment.nvq_or_hnd_or_hnc_or_equivalent_numeric == "1" ~ 2,
-        employment.o_levelsgcses_or_equivalent_numeric == "1" ~ 1,
-        employment.cses_or_equivalent_numeric == "1" ~ 1
-      )
-    )
-
-#recode the numeric version into a factor
-employment.raw.id <- employment.raw.id %>%
-  mutate(
-    highest_education =
-      recode_factor(
-        highest_education_numeric,
-        `1` = "GCSE/CSE",
-        `2` = "NVQ",
-        `3` = "A-levels",
-        `4` = "University")
-    )
-
-employment.raw.id %>%
-  freq(highest_education)
-}
-```
-
-Check highest education coding
-```{r Highest education check}
-if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE) {
-employment.raw.id %>%
-  select(highest_education,
-         employment.phd_numeric,
-         employment.masters_degree_or_equivalent_numeric,
-         employment.postgraduate_degree_or_equivalent_numeric,
-         employment.bachelors_degree_or_equivalent_numeric,
-         employment.a_levelsas_levels_or_equivalent_numeric,
-         employment.nvq_or_hnd_or_hnc_or_equivalent_numeric,
-         employment.o_levelsgcses_or_equivalent_numeric,
-         employment.cses_or_equivalent_numeric
-  )
-}
-```
-
-## Highest education (baseline, RAMP)
-```{r highest level of education for ramp}
-if(RAMP == TRUE) {
-#create numeric version of the highest education variable
-employment.raw.id <- employment.raw.id %>%
-  mutate(
-    highest_education_numeric =
-      case_when(
-        employment.what_is_your_highest_level_of_education == "PhD" ~ 4,
-        employment.what_is_your_highest_level_of_education == "Postgraduate degree or equivalent" ~ 4,
-        employment.what_is_your_highest_level_of_education == "Master's degree or equivalent" ~ 4,
-        employment.what_is_your_highest_level_of_education == "Bachelor's degree or equivalent" ~ 4,
-        employment.what_is_your_highest_level_of_education == "A-level or equivalent" ~ 3,
-        employment.what_is_your_highest_level_of_education == "GCSE or equivalent" ~ 2,
-        employment.what_is_your_highest_level_of_education == "None of these" ~ 1
-      )
-    )
-
-#recode the numeric version into a factor
-employment.raw.id <- employment.raw.id %>%
-  mutate(
-    highest_education =
-      recode_factor(
-        highest_education_numeric,
-        `1` = "None",
-        `2` = "GCSE/CSE",
-        `3` = "A-levels",
-        `4` = "University")
-    )
-
-employment.raw.id %>%
-  freq(highest_education)
-}
-```
-
-Check highest education coding for RAMP
-```{r Highest education check for RAMP}
-if(RAMP == TRUE) {
-employment.raw.id %>%
-  select(highest_education,
-         employment.what_is_your_highest_level_of_education,
-         employment.what_is_your_highest_level_of_education_numeric
-  )
-}
-```
-
-## Key worker status
-```{r Key worker}
-if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE | RAMP == TRUE) {
-#create numeric version of the variable
-employment.raw.id <- employment.raw.id %>%
-  mutate(
-    key_worker_numeric =
-      case_when(
-        employment.government_work_key_workers_numeric == "0" ~ 0,
-        employment.government_work_key_workers_numeric > 0 ~ 1
-      )
-    )
-
-#recode the numeric version into a factor
-employment.raw.id <- employment.raw.id %>%
-  mutate(
-    key_worker =
-      recode_factor(
-        key_worker_numeric,
-        `0` = "No key worker",
-        `1` = "Key worker"
-        )
-    )
-
-employment.raw.id %>%
-  freq(key_worker)
-}
-```
-
-# Columns to exclude from add_numeric
-
-```{r cols to exclude}
-exclude_cols <- c("Sample",
-                  "ID")
-```
-
-# mhd
-
-## GLAD
-```{r glad mhd cols}
-if(GLAD == TRUE) {
-glad.mhd.raw <- readRDS(file = paste0(data.raw_path,"/glad/mhd_glad.rds"))
-dim(glad.mhd.raw)
-colnames(glad.mhd.raw)
-}
-```
-
-```{r glad mhd cleaning}
-if(GLAD == TRUE) {
-glad.mhd.raw.id <- glad.mhd.raw %>%
-  drop_na(externalDataReference) %>% # Drop NAs
-  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
-  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
-  mutate(ID = as.numeric(ID)) %>%
-  select(
-    Sample, # Sample
-    ID, # ID
-    starts_with("mhd."),
-    mhd.bingeeating_disorder = mhd.psychological_overeating_or_bingeeating
-  ) %>%
-  add_numeric(., exclude = exclude_cols) %>%
-  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
-  mutate_if(is.numeric, ~na_if(., -99)) %>%
-  mutate_if(is.numeric, ~na_if(., -77)) %>%
-  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
-  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
-
-# Inspect dimensions
-dim(glad.mhd.raw.id)
-# Inspect colnames
-colnames(glad.mhd.raw.id)
-#Differences
-dim(glad.mhd.raw)[1]-dim(glad.mhd.raw.id)[1]
-}
-```
-
-```{r glad mhd copy}
-if(GLAD == TRUE) {
-  mhd.raw.id <- glad.mhd.raw.id
-}
-```
-
-## EDGI
-```{r edgi mhd cols}
-if(EDGI == TRUE) {
-edgi.mhd.raw <- readRDS(file = paste0(data.raw_path,"/edgi/mhd_edgi.rds"))
-dim(edgi.mhd.raw)
-colnames(edgi.mhd.raw)
-}
-```
-
-```{r edgi mhd cleaning}
-if(EDGI == TRUE) {
-  exclude_cols <- c("Sample",
-                  "ID")
-
-edgi.mhd.raw.id <- edgi.mhd.raw %>%
-  drop_na(externalDataReference) %>% # Drop NAs
-  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
-  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
-  mutate(ID = as.numeric(ID)) %>%
-  select(
-    Sample, # Sample
-    ID, # ID
-    mhd.anorexia_nervosa,
-    mhd.atypical_anorexia_nervosa,
-    mhd.bulimia_nervosa,
-    mhd.atypical_bulimia_nervosa,
-    mhd.bingeeating_disorder,
-    mhd.atypical_bingeeating_disorder
-  ) %>%
-  add_numeric(., exclude = exclude_cols) %>%
-  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
-  mutate_if(is.numeric, ~na_if(., -99)) %>%
-  mutate_if(is.numeric, ~na_if(., -77)) %>%
-  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
-  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
-
-# Inspect dimensions
-dim(edgi.mhd.raw.id)
-# Inspect colnames
-colnames(edgi.mhd.raw.id)
-#Differences
-dim(edgi.mhd.raw)[1]-dim(edgi.mhd.raw.id)[1]
-}
-```
-
-```{r edgi mhd2 cols}
-if(EDGI == TRUE) {
-edgi.mhd2.raw <- readRDS(file = paste0(data.raw_path,"/edgi/dem_edgi.rds"))
-dim(edgi.mhd2.raw)
-colnames(edgi.mhd2.raw)
-}
-```
-
-```{r edgi mhd2 cleaning}
-if(EDGI == TRUE){
-  exclude_cols_mhd2 <- c("ID",
-                        "Sample",
-                        "startDate.prepandemic",
-                        "Age_uncleaned",
-                        "EduYrs")
-
-  edgi.mhd2.raw.id <- edgi.mhd2.raw %>%
-    drop_na(externalDataReference) %>% # Drop NAs
-    distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
-    separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
-    mutate(ID = as.numeric(ID)) %>%
-    select(
-      Sample, # Sample
-      ID, # ID
-    mhd.depression = demographics.depression,
-    mhd.pregnancy_depression = demographics.pregnancy_depression,
-    mhd.premenstrual_dysphoric_disorder_pmdd = demographics.premenstrual_dysphoric_disorder_pmdd,
-    mhd.anxiety_nerves_or_generalised_anxiety_disorder = demographics.anxiety_nerves_or_generalised_anxiety_disorder,
-    mhd.social_anxiety_or_social_phobia = demographics.social_anxiety_or_social_phobia,
-    mhd.specific_phobia_e.g._phobia_of_flying = demographics.specific_phobia_e.g._fear_of_flying, # fear instead of phobia
-    mhd.agoraphobia = demographics.agoraphobia,
-    mhd.panic_disorder = demographics.panic_disorder,
-    mhd.panic_attacks = demographics.panic_attacks,
-    mhd.obsessivecompulsive_disorder_ocd = demographics.obsessivecompulsive_disorder_ocd,
-    mhd.obsessive_compulsive_related_disorders = demographics.obsessive_compulsive_related_disorders,
-    mhd.body_dysmorphic_disorder_bdd = demographics.body_dysmorphic_disorder,
-    mhd.mania_hypomania_bipolar_or_manicdepression = demographics.mania_hypomania_bipolar_or_manicdepression,
-    mhd.schizophrenia = demographics.schizophrenia,
-    mhd.type_psychosis_psychotic_illness = demographics.psychosis_type_psychotic_illness, # word type psychosis changed order compared to GLAD 
-    mhd.personality_disorder_diagnosed = demographics.diagnosed_personality_disorder, # named differently in EDGI
-    mhd.posttraumatic_stress_disorder_ptsd = demographics.posttraumatic_stress_disorder_ptsd,
-    mhd.autism_aspergers_or_autistic_spectrum_disorder = demographics.autism_spectrum_disorder_asd, # different name in EDGI
-    mhd.body_dysmorphic_disorder_bdd = demographics.body_dysmorphic_disorder,
-    mhd.personality_disorder = demographics.personality_disorder, # routing variable in EDGI is named differently; renamed here to match GLAD
-    mhd.attention_deficit_hyperactivity_disorder = demographics.attention_deficit_hyperactivity_disorder
-    ) %>%
-    add_column(
-      mhd.schizoaffective_disorder = NA_character_
-    ) %>%
-    add_numeric(., exclude = exclude_cols_mhd2) %>%
-    mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
-    mutate_if(is.numeric, ~na_if(., -99)) %>%
-    mutate_if(is.numeric, ~na_if(., -77)) %>%
-    mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
-    mutate_if(is.factor, ~na_if(., "Don't know")) %>%
-    mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
-    mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
-    mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
-    mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
-    mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
-    mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
-
-  # Inspect dimensions
-  dim(edgi.mhd2.raw.id)
-  # Inspect colnames
-  colnames(edgi.mhd2.raw.id)
-  #Differences
-  dim(edgi.mhd2.raw)[1]-dim(edgi.mhd2.raw.id)[1]
-}
-```
-
-```{r edgi combine mhd copy}
-if(EDGI == TRUE){
-mhd.raw.id <- left_join(
-  x = edgi.mhd.raw.id,
-  y = edgi.mhd2.raw.id,
-  by = c("Sample", "ID")
-  )
-
-# Inspect dimensions
-dim(mhd.raw.id)
-# Inspect colnames
-colnames(mhd.raw.id)
-}
-```
-
-## NBR
-```{r nbr mhd cols}
-if(NBR == TRUE) {
-nbr.mhd.raw <- readRDS(file = paste0(data.raw_path,"/nbr/mhd_nbr.rds"))
-dim(nbr.mhd.raw)
-colnames(nbr.mhd.raw)
-}
-```
-
-```{r nbr mhd cleaning}
-if(NBR == TRUE) {
-exclude_cols <- c("Sample",
-                  "ID")
-
-nbr.mhd.raw.id <- nbr.mhd.raw %>%
-  drop_na(subjectid) %>% # Drop NAs
-  distinct(subjectid, .keep_all = TRUE) %>% # Remove duplicates based on ID
-  separate(subjectid, into = c("Sample", "ID.intm"), sep = 6) %>% # Split ID in Sample and Number
-  separate(ID.intm, into = "ID", sep = 7) %>%
-  mutate(
-    ID = as.numeric(ID)) %>%
-  select(
-    Sample, # Sample
-    ID, # ID
-    starts_with("mhd."),
-    mhd.specific_phobia_e.g._phobia_of_flying = mhd.specific_phobia_e.g._fear_of_flying,
-    mhd.type_psychosis_psychotic_illness = mhd.psychosis_type_psychotic_illness,
-    mhd.autism_aspergers_or_autistic_spectrum_disorder = mhd.autism_spectrum_disorder_asd,
-    mhd.anorexia_nervosa_unc = mhd.anorexia_nervosa,
-    mhd.atypical_anorexia_nervosa_unc = mhd.atypical_anorexia_nervosa,
-    mhd.bulimia_nervosa_unc = mhd.bulimia_nervosa,
-    mhd.bingeeating_disorder_unc = mhd.bingeeating_disorder
-  ) %>%
-  add_column(
-    mhd.schizoaffective_disorder = NA #NBR doesn't ask about schizoaffective disorder. This means the column das not exist in the data set
-  ) %>% 
-  add_numeric(., exclude = exclude_cols) %>%
-  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
-  mutate_if(is.numeric, ~na_if(., -99)) %>%
-  mutate_if(is.numeric, ~na_if(., -77)) %>%
-  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
-  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
-
-# Inspect dimensions
-dim(nbr.mhd.raw.id)
-# Inspect colnames
-colnames(nbr.mhd.raw.id)
-#Differences
-dim(nbr.mhd.raw)[1]-dim(nbr.mhd.raw.id)[1]
-}
-```
-
-```{r nbr mhd copy}
-if(NBR == TRUE) {
-  mhd.raw.id <- nbr.mhd.raw.id
-}
-```
-
-## RAMP
-```{r ramp mhd cols}
-if(RAMP == TRUE) {
-ramp.mhd.raw <- readRDS(file = paste0(data.raw_path,"/ramp/mhd_ramp.rds"))
-dim(ramp.mhd.raw)
-colnames(ramp.mhd.raw)
-}
-```
-
-```{r ramp mhd cleaning}
-if(RAMP == TRUE) {
-exclude_cols <- c("Sample",
-                  "ID")
-
-ramp.mhd.raw.id <- ramp.mhd.raw %>%
-  drop_na(`Login ID`) %>% # Drop NAs
-  distinct(`Login ID`, .keep_all = TRUE) %>% # Remove duplicates based on ID
-  separate(`Login ID`, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
-  separate(ID, into = "ID", sep = 7) %>%
-  mutate(
-    ID = as.numeric(ID)) %>%
-  select(
-    Sample, # Sample
-    ID, # ID
-    mhd.depression = NA.30.depression,
-    mhd.pregnancy_depression = NA.30.pregnancy_depression,
-    mhd.premenstrual_dysphoric_disorder_pmdd = NA.30.premenstrual_dysphoric_disorder_pmdd,
-    mhd.mania_hypomania_bipolar_or_manicdepression = NA.30.mania_hypomania_bipolar_or_manicdepression,
-    mhd.anxiety_nerves_or_generalised_anxiety_disorder = NA.30.anxiety_nerves_or_generalised_anxiety_disorder,
-    mhd.social_anxiety_or_social_phobia = NA.30.social_anxiety_or_social_phobia,
-    mhd.specific_phobia_e.g._phobia_of_flying = NA.30.specific_phobia_e.g._phobia_of_flying,
-    mhd.agoraphobia = NA.30.agoraphobia,
-    mhd.panic_disorder = NA.30.panic_disorder,
-    mhd.panic_attacks = NA.30.panic_attacks,
-    mhd.posttraumatic_stress_disorder_ptsd = NA.30.posttraumatic_stress_disorder_ptsd,
-    mhd.obsessivecompulsive_disorder_ocd = NA.30.obsessivecompulsive_disorder_ocd, 
-    mhd.body_dysmorphic_disorder_bdd = NA.30.body_dysmorphic_disorder_bdd,
-    mhd.skin_picking_obsessive_compulsive = NA.30.skin_picking_obsessive_compulsive,
-    mhd.anorexia_nervosa = NA.30.anorexia_nervosa,
-    mhd.atypical_anorexia_nervosa = NA.30.atypical_anorexia_nervosa,
-    mhd.bulimia_nervosa = NA.30.bulimia_nervosa,
-    mhd.bingeeating_disorder = NA.30.psychological_overeating_or_bingeeating_disorder,
-    mhd.schizophrenia = NA.30.schizophrenia,
-    mhd.schizoaffective_disorder = NA.30.schizoaffective_disorder,
-    mhd.type_psychosis_psychotic_illness = NA.30.psychosis_type_psychotic_illness,
-    mhd.personality_disorder = NA.30.personality_disorder,
-    mhd.autism_aspergers_or_autistic_spectrum_disorder = NA.30.autism_aspergers_or_autistic_spectrum_disorder,
-    mhd.attention_deficit_hyperactivity_disorder = NA.30.attention_deficit_hyperactivity_disorder,
-    mhd.personality_disorder_diagnosed = NA.30.personality_disorder_diagnosed
-  ) %>%
-  add_numeric(., exclude = exclude_cols) %>%
-  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
-  mutate_if(is.numeric, ~na_if(., -99)) %>%
-  mutate_if(is.numeric, ~na_if(., -77)) %>%
-  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
-  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
-
-# Inspect dimensions
-dim(ramp.mhd.raw.id)
-# Inspect colnames
-colnames(ramp.mhd.raw.id)
-#Differences
-dim(ramp.mhd.raw)[1]-dim(ramp.mhd.raw.id)[1]
-}
-```
-
-```{r ramp mhd copy}
-if(RAMP == TRUE) {
-  mhd.raw.id <- ramp.mhd.raw.id
-}
-```
-
-## Grouping mental health disorders
-*#Disorder groupings - from COPING/RAMP analysis minutes*
-1. Depressive disorder group: major depression, antenatal/postnatal depression, premenstrual depression. The logic for this has been double checked for males - KT/MD. 
-2. Anxiety group: generalised anxiety, social anxiety, specific phobia, agoraphobia, panic_disorder, panic_attacks. 
-3. Agoraphobia and panic_disorder group: panic_disorder, agoraphobia, panic_attacks.
-4. Eating disorders group: anorexianervosa, atypical anorexia nervosa, bulimia nervosa, overeating or bingeeating.
-5. Obsessive complusive disorders: obsessive compulaive disorder, obsessive compulsive related disorders. 
-6. Psychotic disorders: schizophrenia, schizoaffective disorder, general psychosis or psychotic illness. 
-7. Personality disorders: cluster A, cluster B, cluster C
-8. Control group: no diagnosed disorders.
-
-*Disorders of interest*
-MDD and other depressive disorders
-Anxiety, nerves or generalised anxiety disorder
-Social anxiety 
-Specific phobia 
-Agoraphobia/panic disorder/panic attacks
-OCD (& OCD-related disorders e.g., skin picking?)
-PTSD 
-Bipolar 
-Eating disorders (Anorexia, BE-type EDs) 
-Personality disorder: Clusters A, B, and C 
-No-diagnosis group
-
-*Analysis plan of Disorders: KY and KP analysis plan*
-1. Basic: any anxiety or unipolar depressive disorder vs. those with no prior diagnosis
-2. Specific: breakdown by type of prior anxiety (& related) disorder diagnosis
-3. Breakdown by COVID or not (using COVIDENCE/Zoe algorithm)
-
-### Depressive disorders
-```{r mhd depressive_disorders}
-if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE | RAMP == TRUE)
-mhd.raw.id <- mhd.raw.id %>%
-  mutate(
-    depressive_disorders_numeric =
-      case_when(
-        (mhd.depression_numeric == "0" &
-        (mhd.pregnancy_depression_numeric == "0" | is.na(mhd.pregnancy_depression_numeric)) & 
-        (mhd.premenstrual_dysphoric_disorder_pmdd_numeric == "0" | is.na(mhd.premenstrual_dysphoric_disorder_pmdd_numeric))) ~ 0,
-        mhd.depression_numeric == "1" ~ 1,
-        mhd.pregnancy_depression_numeric == "1" ~ 1,
-        mhd.premenstrual_dysphoric_disorder_pmdd_numeric == "1" ~ 1))
-
-mhd.raw.id <- mhd.raw.id %>%
-  mutate(
-    depressive_disorders =
-      recode_factor(depressive_disorders_numeric,
-                    "0" = "No depressive disorder",
-                    "1" = "Depressive disorder",
-                    missing = NA_character_
-                    )
-  )
-
-mhd.raw.id %>%
-  freq(depressive_disorders,
-       cumul = F)
-```
-
-```{r Check depressive_disorders}
-if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE | RAMP == TRUE) {
-mhd.raw.id %>%
-  select(
-    depressive_disorders,
-    depressive_disorders_numeric,
-    mhd.depression_numeric,
-    mhd.pregnancy_depression_numeric,
-    mhd.premenstrual_dysphoric_disorder_pmdd_numeric,
-    mhd.depression,
-    mhd.pregnancy_depression,
-    mhd.premenstrual_dysphoric_disorder_pmdd
-  )
-}
-```
-
-### Anxiety disorders
-```{r mhd anxiety_disorders}
-if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE | RAMP == TRUE) {
-mhd.raw.id <- mhd.raw.id %>%
-  mutate(
-    anxiety_disorders_numeric =
-      case_when(
-        mhd.anxiety_nerves_or_generalised_anxiety_disorder_numeric == "1" ~ 1,
-        mhd.social_anxiety_or_social_phobia_numeric == "1" ~ 1,
-        mhd.specific_phobia_e.g._phobia_of_flying_numeric == "1" ~ 1,
-        mhd.agoraphobia_numeric == "1" ~ 1,
-        mhd.panic_disorder_numeric == "1" ~ 1,
-        mhd.panic_attacks_numeric == "1" ~ 1,
-        (mhd.anxiety_nerves_or_generalised_anxiety_disorder_numeric == "0" &
-        mhd.social_anxiety_or_social_phobia_numeric == "0" &
-        mhd.specific_phobia_e.g._phobia_of_flying_numeric == "0" &
-        mhd.agoraphobia_numeric == "0" &
-        mhd.panic_disorder_numeric == "0" &
-        mhd.panic_attacks_numeric == "0") ~ 0
-      )
-  )
-
-mhd.raw.id <- mhd.raw.id %>%
-  mutate(
-    anxiety_disorders =
-      recode_factor(anxiety_disorders_numeric,
-                    "0" = "No anxiety disorder",
-                    "1" = "Anxiety disorder",
-                    missing = NA_character_
-                    )
-  )
-
-mhd.raw.id %>%
-  freq(anxiety_disorders,
-       cumul = F)
-}
-```
-
-```{r Check anxiety_disorders}
-if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE | RAMP == TRUE) {
-mhd.raw.id %>%
-  select(
-    anxiety_disorders,
-    anxiety_disorders_numeric,
-    mhd.anxiety_nerves_or_generalised_anxiety_disorder_numeric,
-    mhd.social_anxiety_or_social_phobia_numeric,
-    mhd.specific_phobia_e.g._phobia_of_flying_numeric,
-    mhd.agoraphobia_numeric,
-    mhd.panic_disorder_numeric,
-    mhd.panic_attacks_numeric,
-    mhd.anxiety_nerves_or_generalised_anxiety_disorder,
-    mhd.social_anxiety_or_social_phobia,
-    mhd.specific_phobia_e.g._phobia_of_flying,
-    mhd.agoraphobia,
-    mhd.panic_disorder,
-    mhd.panic_attacks
-  )
-}
-```
-
-Agoraphonia and panic disorder group
-```{r mhd agoraphobia_panic_disorder}
-if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE | RAMP == TRUE) {
-mhd.raw.id <- mhd.raw.id %>%
-  mutate(
-    agoraphobia_panic_disorder_numeric =
-      case_when(
-        mhd.agoraphobia_numeric == "1" ~ 1,
-        mhd.panic_disorder_numeric == "1" ~ 1,
-        mhd.panic_attacks_numeric == "1" ~ 1,
-        (mhd.agoraphobia_numeric == "0" &
-        mhd.panic_disorder_numeric == "0" &
-        mhd.panic_attacks_numeric == "0") ~ 0
-      )
-  )
-
-mhd.raw.id <- mhd.raw.id %>%
-  mutate(
-    agoraphobia_panic_disorder =
-      recode_factor(agoraphobia_panic_disorder_numeric,
-                    "0" = "No agoraphobia/panic disorder",
-                    "1" = "Agoraphobia/panic disorder",
-                    missing = NA_character_
-                    )
-  )
-
-mhd.raw.id %>%
-  freq(agoraphobia_panic_disorder)
-}
-```
-
-```{r Check agoraphobia_panic_disorder}
-if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE | RAMP == TRUE) {
-mhd.raw.id %>%
-  select(
-    agoraphobia_panic_disorder,
-    agoraphobia_panic_disorder_numeric,
-    mhd.agoraphobia_numeric,
-    mhd.panic_disorder_numeric,
-    mhd.panic_attacks_numeric,
-    mhd.agoraphobia,
-    mhd.panic_disorder,
-    mhd.panic_attacks
-  )
-}
-```
-
-Depression and anxiety comorbidity
-```{r mhd depression_anxiety}
-if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE | RAMP == TRUE) {
-mhd.raw.id <- mhd.raw.id %>%
-  mutate(
-    depression_and_anxiety_numeric =
-      case_when(
-        depressive_disorders_numeric == 0 &
-          anxiety_disorders_numeric == 0 ~ 0,
-        depressive_disorders_numeric == 1 &
-          anxiety_disorders_numeric == 1 ~ 1,
-        depressive_disorders_numeric == 1 &
-          anxiety_disorders_numeric == 0 ~ 2,
-        depressive_disorders_numeric == 0 &
-          anxiety_disorders_numeric == 1 ~ 3
-      )
-  )
-
-mhd.raw.id <- mhd.raw.id %>%
-  mutate(
-    depression_and_anxiety =
-      recode_factor(depression_and_anxiety_numeric,
-                    "0" = "No depressive or anxiety disorder",
-                    "1" = "Depressive and anxiety disorder",
-                    "2" = "Only depressive disorder",
-                    "3" = "Only anxiety disorder",
-                    missing = NA_character_
-                    )
-  )
-
-mhd.raw.id %>%
-  freq(depression_and_anxiety,
-       cumul = F)
-}
-```
-
-### Eating disorders
-
-There is routing questionnaire if participants have been diagnosed with an eating disorder and afterwards they get asked the specific disorders.
-Therefore, mhd.suspected_eating_disorder_diagnosed_numeric needs to be recoded as 0 otherwise they would be NAs.
-```{r nbr cleaning eating disorders}
-if(NBR == TRUE) {
-#Recode as 0 if ppt responds no to screening question (mhd.suspected_eating_disorder_diagnosed_numeric)
-mhd.raw.id <- mhd.raw.id %>%
-  mutate(
-    mhd.anorexia_nervosa_numeric =
-      case_when(mhd.suspected_eating_disorder_diagnosed_numeric == "0" ~ 0,
-                mhd.anorexia_nervosa_unc_numeric == "0" ~ 0,
-                mhd.anorexia_nervosa_unc_numeric == "1" ~ 1),
-    mhd.atypical_anorexia_nervosa_numeric =
-      case_when(mhd.suspected_eating_disorder_diagnosed_numeric == "0" ~ 0,
-                mhd.atypical_anorexia_nervosa_unc_numeric == "0" ~ 0,
-                mhd.atypical_anorexia_nervosa_unc_numeric == "1" ~ 1),
-    mhd.bulimia_nervosa_numeric =
-      case_when(mhd.suspected_eating_disorder_diagnosed_numeric == "0" ~ 0,
-                mhd.bulimia_nervosa_unc_numeric == "0" ~ 0,
-                mhd.bulimia_nervosa_unc_numeric == "1" ~ 1),
-    mhd.bingeeating_disorder_numeric =
-      case_when(mhd.suspected_eating_disorder_diagnosed_numeric == "0" ~ 0,
-                mhd.bingeeating_disorder_unc_numeric == "0" ~ 0,
-                mhd.bingeeating_disorder_unc_numeric == "1" ~ 1),
-    mhd.anorexia_nervosa =
-      case_when(mhd.suspected_eating_disorder_diagnosed_numeric == "0" ~ "Not Anorexia nervosa",
-                mhd.anorexia_nervosa_unc_numeric == "0" ~ "Not Anorexia nervosa",
-                mhd.anorexia_nervosa_unc_numeric == "1" ~ "Anorexia nervosa"),
-    mhd.atypical_anorexia_nervosa =
-      case_when(mhd.suspected_eating_disorder_diagnosed_numeric == "0" ~ "Not Atypical anorexia nervosa",
-                mhd.atypical_anorexia_nervosa_unc_numeric == "0" ~ "Not Atypical anorexia nervosa",
-                mhd.atypical_anorexia_nervosa_unc_numeric == "1" ~ "Atypical anorexia nervosa"),
-    mhd.bulimia_nervosa =
-      case_when(mhd.suspected_eating_disorder_diagnosed_numeric == "0" ~ "Not Bulimia nervosa",
-                mhd.bulimia_nervosa_unc_numeric == "0" ~ "Not Bulimia nervosa",
-                mhd.bulimia_nervosa_unc_numeric == "1" ~ "Bulimia nervosa"),
-    mhd.bingeeating_disorder =
-      case_when(mhd.suspected_eating_disorder_diagnosed_numeric == "0" ~ "Not Binge-eating disorder",
-                mhd.bingeeating_disorder_unc_numeric == "0" ~ "Not Binge-eating disorder",
-                mhd.bingeeating_disorder_unc_numeric == "1" ~ "Binge-eating disorder")
-    )
-}
-
-```
-
-```{r mhd eating_disorders}
-if(GLAD == TRUE | NBR == TRUE | RAMP == TRUE) {
-mhd.raw.id <- mhd.raw.id %>%
-  mutate(
-    eating_disorders_numeric =
-      case_when(
-        mhd.anorexia_nervosa_numeric == "1" ~ 1,
-        mhd.atypical_anorexia_nervosa_numeric == "1" ~ 1,
-        mhd.bulimia_nervosa_numeric == "1" ~ 1,
-        mhd.bingeeating_disorder_numeric == "1" ~ 1,
-        (mhd.anorexia_nervosa_numeric == "0" &
-        mhd.atypical_anorexia_nervosa_numeric == "0" &
-        mhd.bulimia_nervosa_numeric == "0" &
-        mhd.bingeeating_disorder_numeric == "0") ~ 0
-      )
-  )
-
-mhd.raw.id <- mhd.raw.id %>%
-  mutate(
-    eating_disorders =
-      recode_factor(eating_disorders_numeric,
-                    "0" = "No eating disorder",
-                    "1" = "Eating disorder",
-                    missing = NA_character_
-                    )
-  )
-
-mhd.raw.id %>%
-  freq(eating_disorders,
-       cumul = F)
-}
-```
-
-For EDGI does not include other eating disorders, such as purging disorder, rumination disorder, ARFID, or Pica
-```{r edgi mhd eating_disorders}
-if(EDGI == TRUE) {
-mhd.raw.id <- mhd.raw.id %>%
-  mutate(
-    eating_disorders_numeric =
-      case_when(
-        mhd.anorexia_nervosa_numeric == "1" ~ 1,
-        mhd.atypical_anorexia_nervosa_numeric == "1" ~ 1,
-        mhd.bulimia_nervosa_numeric == "1" ~ 1,
-        mhd.atypical_bulimia_nervosa_numeric == "1" ~ 1, # additional diagnosis in EDGI but not in GLAD
-        mhd.bingeeating_disorder_numeric == "1" ~ 1,
-        mhd.atypical_bingeeating_disorder_numeric == "1" ~ 1, # additional diagnosis in EDGI
-        (mhd.anorexia_nervosa_numeric == "0" &
-        mhd.atypical_anorexia_nervosa_numeric == "0" &
-          mhd.atypical_anorexia_nervosa_numeric == "0" &
-        mhd.bulimia_nervosa_numeric == "0" &
-          mhd.atypical_bulimia_nervosa_numeric == "0" &
-        mhd.bingeeating_disorder_numeric == "0" &
-          mhd.atypical_bingeeating_disorder_numeric == "0") ~ 0
-      )
-  )
-
-mhd.raw.id <- mhd.raw.id %>%
-  mutate(
-    eating_disorders =
-      recode_factor(eating_disorders_numeric,
-                    "0" = "No eating disorder",
-                    "1" = "Eating disorder",
-                    missing = NA_character_
-                    )
-  )
-
-mhd.raw.id %>%
-  freq(eating_disorders,
-       cumul = F)
-}
-```
-
-Eating disorders with binge eating vs eating disorders without
-Caveat: Anorexia nervosa can have binge eating as well. Therefore, this would need an additional variable from the ED100K
-```{r mhd restricting_vs_binge_eating_eating_disorders}
-if(GLAD == TRUE | NBR == TRUE | RAMP == TRUE) {
-mhd.raw.id <- mhd.raw.id %>%
-  mutate(
-    restricting_vs_binge_eating_eating_disorders_numeric =
-      case_when(
-        mhd.anorexia_nervosa_numeric == "1" ~ 1,
-        mhd.atypical_anorexia_nervosa_numeric == "1" ~ 1,
-        mhd.bulimia_nervosa_numeric == "1" ~ 2,
-        mhd.bingeeating_disorder_numeric == "1" ~ 2,
-        (mhd.anorexia_nervosa_numeric == "0" &
-        mhd.atypical_anorexia_nervosa_numeric == "0" &
-        mhd.bulimia_nervosa_numeric == "0" &
-        mhd.bingeeating_disorder_numeric == "0") ~ 0
-      )
-  )
-
-mhd.raw.id <- mhd.raw.id %>%
-  mutate(
-    restricting_vs_binge_eating_eating_disorders =
-      recode_factor(restricting_vs_binge_eating_eating_disorders_numeric,
-                    "0" = "No eating disorder",
-                    "1" = "Anorexia nervosa",
-                    "2" = "Eating disorder with binge eating",
-                    missing = NA_character_
-                    )
-  )
-
-mhd.raw.id %>%
-  freq(restricting_vs_binge_eating_eating_disorders,
-       cumul = F)
-}
-```
-
-```{r mhd restricting_vs_binge_eating_eating_disorders}
-if(EDGI == TRUE) {
-mhd.raw.id <- mhd.raw.id %>%
-  mutate(
-    restricting_vs_binge_eating_eating_disorders_numeric =
-      case_when(
-        mhd.anorexia_nervosa_numeric == "1" ~ 1,
-        mhd.atypical_anorexia_nervosa_numeric == "1" ~ 1,
-        mhd.bulimia_nervosa_numeric == "1" ~ 2,
-        mhd.atypical_bulimia_nervosa_numeric == "1" ~ 2, # additional diagnosis in EDGI but not in GLAD
-        mhd.bingeeating_disorder_numeric == "1" ~ 2,
-        mhd.atypical_bingeeating_disorder_numeric == "1" ~ 2, # additional diagnosis in EDGI
-        (mhd.anorexia_nervosa_numeric == "0" &
-        mhd.atypical_anorexia_nervosa_numeric == "0" &
-          mhd.atypical_anorexia_nervosa_numeric == "0" &
-        mhd.bulimia_nervosa_numeric == "0" &
-          mhd.atypical_bulimia_nervosa_numeric == "0" &
-        mhd.bingeeating_disorder_numeric == "0" &
-          mhd.atypical_bingeeating_disorder_numeric == "0") ~ 0
-      )
-  )
-
-mhd.raw.id <- mhd.raw.id %>%
-  mutate(
-    restricting_vs_binge_eating_eating_disorders =
-      recode_factor(restricting_vs_binge_eating_eating_disorders_numeric,
-                    "0" = "No eating disorder",
-                    "1" = "Anorexia nervosa",
-                    "2" = "Eating disorder with binge eating",
-                    missing = NA_character_
-                    )
-  )
-
-mhd.raw.id %>%
-  freq(restricting_vs_binge_eating_eating_disorders,
-       cumul = F)
-}
-```
-
-```{r Check eating_disorders}
-if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE | RAMP == TRUE) {
-mhd.raw.id %>%
-  select(
-    eating_disorders,
-    eating_disorders_numeric,
-    restricting_vs_binge_eating_eating_disorders,
-    restricting_vs_binge_eating_eating_disorders_numeric,
-    mhd.anorexia_nervosa_numeric,
-    mhd.atypical_anorexia_nervosa_numeric,
-    mhd.bulimia_nervosa_numeric,
-    mhd.bingeeating_disorder_numeric,
-    mhd.anorexia_nervosa,
-    mhd.atypical_anorexia_nervosa,
-    mhd.bulimia_nervosa,
-    mhd.bingeeating_disorder
-  )
-}
-```
-
-```{r Check eating_disorders}
-if(EDGI == TRUE) {
-mhd.raw.id %>%
-  select(
-    eating_disorders,
-    eating_disorders_numeric,
-    restricting_vs_binge_eating_eating_disorders,
-    restricting_vs_binge_eating_eating_disorders_numeric,
-    mhd.anorexia_nervosa_numeric,
-    mhd.atypical_anorexia_nervosa_numeric,
-    mhd.bulimia_nervosa_numeric,
-    mhd.bingeeating_disorder_numeric,
-    mhd.anorexia_nervosa,
-    mhd.atypical_anorexia_nervosa,
-    mhd.bulimia_nervosa,
-    mhd.atypical_bulimia_nervosa,
-    mhd.bingeeating_disorder,
-    mhd.atypical_bingeeating_disorder
-  )
-}
-```
-
-### Obsessive compulsive disorders
-```{r mhd obsessive_compulsive_disorders}
-if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE) {
-mhd.raw.id <- mhd.raw.id %>%
-  mutate(
-    obsessive_compulsive_disorders_numeric =
-      case_when(
-        mhd.obsessivecompulsive_disorder_ocd_numeric == "1" ~ 1,
-        mhd.obsessive_compulsive_related_disorders_numeric == "1" ~ 1,
-        mhd.body_dysmorphic_disorder_bdd_numeric == "1" ~ 1,
-        (mhd.obsessivecompulsive_disorder_ocd_numeric == "0" &
-        mhd.obsessive_compulsive_related_disorders_numeric == "0" &
-        mhd.body_dysmorphic_disorder_bdd_numeric == "0") ~ 0
-      )
-  )
-
-mhd.raw.id <- mhd.raw.id %>%
-  mutate(
-    obsessive_compulsive_disorders =
-      recode_factor(obsessive_compulsive_disorders_numeric,
-                    "0" = "No obsessive compulsive disorder",
-                    "1" = "Obsessive compulsive disorder",
-                    missing = NA_character_
-                    )
-  )
-
-mhd.raw.id %>%
-  freq(obsessive_compulsive_disorders)
-}
-```
-
-```{r mhd obsessive_compulsive_disorders for ramp}
-if(RAMP == TRUE) {
-mhd.raw.id <- mhd.raw.id %>%
-  mutate(
-    obsessive_compulsive_disorders_numeric =
-      case_when(
-        mhd.obsessivecompulsive_disorder_ocd_numeric == "1" ~ 1,
-        mhd.skin_picking_obsessive_compulsive_numeric == "1" ~ 1,
-        mhd.body_dysmorphic_disorder_bdd_numeric == "1" ~ 1,
-        (mhd.obsessivecompulsive_disorder_ocd_numeric == "0" &
-        mhd.skin_picking_obsessive_compulsive_numeric == "0" &
-        mhd.body_dysmorphic_disorder_bdd_numeric == "0") ~ 0
-      )
-  )
-
-mhd.raw.id <- mhd.raw.id %>%
-  mutate(
-    obsessive_compulsive_disorders =
-      recode_factor(obsessive_compulsive_disorders_numeric,
-                    "0" = "No obsessive compulsive disorder",
-                    "1" = "Obsessive compulsive disorder",
-                    missing = NA_character_
-                    )
-  )
-
-mhd.raw.id %>%
-  freq(obsessive_compulsive_disorders)
-}
-```
-
-```{r Check obsessive_compulsive_disorders}
-if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE) {
-mhd.raw.id %>%
-  select(
-    obsessive_compulsive_disorders,
-    obsessive_compulsive_disorders_numeric,
-    mhd.obsessivecompulsive_disorder_ocd,
-    mhd.obsessivecompulsive_disorder_ocd_numeric,
-    mhd.obsessive_compulsive_related_disorders,
-    mhd.obsessive_compulsive_related_disorders_numeric,
-    mhd.body_dysmorphic_disorder_bdd,
-    mhd.body_dysmorphic_disorder_bdd_numeric
-  )
-}
-```
-
-```{r Check obsessive_compulsive_disorders ramp}
-if(RAMP == TRUE) {
-mhd.raw.id %>%
-  select(
-    obsessive_compulsive_disorders,
-    obsessive_compulsive_disorders_numeric,
-    mhd.obsessivecompulsive_disorder_ocd,
-    mhd.obsessivecompulsive_disorder_ocd_numeric,
-    mhd.skin_picking_obsessive_compulsive,
-    mhd.skin_picking_obsessive_compulsive_numeric,
-    mhd.body_dysmorphic_disorder_bdd,
-    mhd.body_dysmorphic_disorder_bdd_numeric
-  )
-}
-```
-
-### Psychotic disorders
-"mhd.schizophrenia_numeric"                                 
-"mhd.schizoaffective_disorder_numeric"                      
-"mhd.type_psychosis_psychotic_illness_numeric" 
-```{r mhd psychotic_disorders}
-if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE | RAMP == TRUE) {
-mhd.raw.id <- mhd.raw.id %>%
-  mutate(
-    psychotic_disorders_numeric =
-      case_when(
-        mhd.schizophrenia_numeric == "1" ~ 1,
-        mhd.schizoaffective_disorder_numeric == "1" ~ 1,
-        mhd.type_psychosis_psychotic_illness_numeric == "1" ~ 1,
-        (mhd.schizophrenia_numeric == "0" &
-        (mhd.schizoaffective_disorder_numeric == "0" | is.na(mhd.schizoaffective_disorder_numeric == "0") & #NA included because some cohorts don't have schizoaffective disorder
-        mhd.type_psychosis_psychotic_illness_numeric == "0") ~ 0)
-        )
-    )
-
-mhd.raw.id <- mhd.raw.id %>%
-  mutate(
-    psychotic_disorders =
-      recode_factor(psychotic_disorders_numeric,
-                    "0" = "No psychotic disorder",
-                    "1" = "Psychotic disorder",
-                    missing = NA_character_
-                    )
-  )
-
-mhd.raw.id %>%
-  freq(psychotic_disorders)
-}
-```
-
-Overlap between self-report schizophrenia and bipolar disorder
-+++CH: Check overlap between schizophrenia group and bipolar disorder
-++KT: Only 63 with comorbid self-report bipolar disorder and schizophrenia. More likely to have shared symptoms, less likely to have confirmed diagnoses of both. Could be too severe to be in GLAD?
-```{r mhd bipolar_and_schizophrenia_numeric}
-if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE | RAMP == TRUE) {
-mhd.raw.id <- mhd.raw.id %>%
-  mutate(
-    bipolar_and_schizophrenia_numeric =
-      case_when(
-        psychotic_disorders_numeric == 0 &
-          mhd.mania_hypomania_bipolar_or_manicdepression_numeric == 0 ~ 0,
-        psychotic_disorders_numeric == 1 &
-          mhd.mania_hypomania_bipolar_or_manicdepression_numeric == 1 ~ 1,
-        psychotic_disorders_numeric == 1 &
-          mhd.mania_hypomania_bipolar_or_manicdepression_numeric == 0 ~ 2,
-        psychotic_disorders_numeric == 0 &
-          mhd.mania_hypomania_bipolar_or_manicdepression_numeric == 1 ~ 3
-      )
-  )
-
-mhd.raw.id <- mhd.raw.id %>%
-  mutate(
-    bipolar_and_schizophrenia =
-      recode_factor(bipolar_and_schizophrenia_numeric,
-                    "0" = "No psychotic or bipolar disorder",
-                    "1" = "Psychotic and bipolar disorder",
-                    "2" = "Only psychotic disorder",
-                    "3" = "Only bipolar disorder",
-                    missing = NA_character_
-                    )
-  )
-
-mhd.raw.id %>%
-  freq(bipolar_and_schizophrenia,
-       cumul = F)
-}
-```
-
-```{r Check psychotic_disorders}
-if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE | RAMP == TRUE) {
-mhd.raw.id %>%
-  select(
-    psychotic_disorders,
-    psychotic_disorders_numeric,
-    bipolar_and_schizophrenia,
-    bipolar_and_schizophrenia_numeric,
-    mhd.schizophrenia_numeric,
-    mhd.schizoaffective_disorder_numeric,
-    mhd.mania_hypomania_bipolar_or_manicdepression,
-    mhd.mania_hypomania_bipolar_or_manicdepression_numeric,
-    mhd.type_psychosis_psychotic_illness_numeric,
-    mhd.schizophrenia,
-    mhd.schizoaffective_disorder,
-    mhd.type_psychosis_psychotic_illness
-  )
-}
-```
-
-### Personality disorders
-++KT: For all cluster coding chunks - have added other clusters as == 0, so that they are not coerced into NAs. 
-Cluster A
-1. Paranoid                         28 ( 1.0%)
-2. Schizoid                         15 ( 0.5%)
-3. Schizotypal                      14 ( 0.5%)
-```{r mhd personality_cluster_a}
-if(GLAD == TRUE | NBR == TRUE | RAMP == TRUE) {
-mhd.raw.id <- mhd.raw.id %>%
-  mutate(
-    personality_cluster_a_numeric =
-      case_when(
-        mhd.personality_disorder_diagnosed_numeric == "1" ~ 1,
-        mhd.personality_disorder_diagnosed_numeric == "2" ~ 1,
-        mhd.personality_disorder_diagnosed_numeric == "3" ~ 1,
-        mhd.personality_disorder_diagnosed_numeric == "4" ~ 0,
-        mhd.personality_disorder_diagnosed_numeric == "5" ~ 0,
-        mhd.personality_disorder_diagnosed_numeric == "6" ~ 0,
-        mhd.personality_disorder_diagnosed_numeric == "7" ~ 0,
-        mhd.personality_disorder_diagnosed_numeric == "8" ~ 0,
-        mhd.personality_disorder_diagnosed_numeric == "9" ~ 0,
-        mhd.personality_disorder_diagnosed_numeric == "10" ~ 0,
-        mhd.personality_disorder_numeric == "0" ~ 0
-      )
-  )
-
-mhd.raw.id <- mhd.raw.id %>%
-  mutate(
-    personality_cluster_a =
-      recode_factor(personality_cluster_a_numeric,
-                    "0" = "No personality disorder cluster A",
-                    "1" = "Personality disorder cluster A",
-                    missing = NA_character_
-                    )
-  )
-
-mhd.raw.id %>%
-  freq(personality_cluster_a,
-       cumul = F)
-}
-```
-
-```{r Check personality_cluster_a}
-if(GLAD == TRUE | NBR == TRUE | RAMP == TRUE) {
-mhd.raw.id %>%
-  select(
-    personality_cluster_a,
-    personality_cluster_a_numeric,
-    mhd.personality_disorder_diagnosed,
-    mhd.personality_disorder_diagnosed_numeric
-  )
-}
-```
-
-Cluster B
-4. Antisocial                       24 ( 0.8%)
-5. Borderline                     2553 (89.4%)
-6. Histrionic                        7 ( 0.2%)
-7. Narcissistic                      8 ( 0.3%)
-
-```{r mhd personality_cluster_b}
-if(GLAD == TRUE | NBR == TRUE | RAMP == TRUE) {
-mhd.raw.id <- mhd.raw.id %>%
-  mutate(
-    personality_cluster_b_numeric =
-      case_when(
-        mhd.personality_disorder_diagnosed_numeric == "1" ~ 0,
-        mhd.personality_disorder_diagnosed_numeric == "2" ~ 0,
-        mhd.personality_disorder_diagnosed_numeric == "3" ~ 0,
-        mhd.personality_disorder_diagnosed_numeric == "4" ~ 1,
-        mhd.personality_disorder_diagnosed_numeric == "5" ~ 1,
-        mhd.personality_disorder_diagnosed_numeric == "6" ~ 1,
-        mhd.personality_disorder_diagnosed_numeric == "7" ~ 1,
-        mhd.personality_disorder_diagnosed_numeric == "8" ~ 0,
-        mhd.personality_disorder_diagnosed_numeric == "9" ~ 0,
-        mhd.personality_disorder_diagnosed_numeric == "10" ~ 0,
-        mhd.personality_disorder_numeric == "0" ~ 0
-      )
-  )
-
-mhd.raw.id <- mhd.raw.id %>%
-  mutate(
-    personality_cluster_b =
-      recode_factor(personality_cluster_b_numeric,
-                    "0" = "No personality disorder cluster B",
-                    "1" = "Personality disorder cluster B",
-                    missing = NA_character_
-                    )
-  )
-
-mhd.raw.id %>%
-  freq(personality_cluster_b,
-       cumul = F)
-}
-```
-
-```{r Check personality_cluster_b}
-if(GLAD == TRUE | NBR == TRUE | RAMP == TRUE) {
-mhd.raw.id %>%
-  select(
-    personality_cluster_b,
-    personality_cluster_b_numeric,
-    mhd.personality_disorder_diagnosed,
-    mhd.personality_disorder_diagnosed_numeric
-  )
-}
-```
-
-Cluster C
-8. Avoidant/anxious                133 ( 4.7%)
-9. Dependent                        29 ( 1.0%)
-10. Obsessive-compulsive
-```{r glad mhd personality_cluster_c}
-if(GLAD == TRUE | NBR == TRUE | RAMP == TRUE) {
-mhd.raw.id <- mhd.raw.id %>%
-  mutate(
-    personality_cluster_c_numeric =
-      case_when(
-        mhd.personality_disorder_diagnosed_numeric == "1" ~ 0,
-        mhd.personality_disorder_diagnosed_numeric == "2" ~ 0,
-        mhd.personality_disorder_diagnosed_numeric == "3" ~ 0,
-        mhd.personality_disorder_diagnosed_numeric == "4" ~ 0,
-        mhd.personality_disorder_diagnosed_numeric == "5" ~ 0,
-        mhd.personality_disorder_diagnosed_numeric == "6" ~ 0,
-        mhd.personality_disorder_diagnosed_numeric == "7" ~ 0,
-        mhd.personality_disorder_diagnosed_numeric == "8" ~ 1,
-        mhd.personality_disorder_diagnosed_numeric == "9" ~ 1,
-        mhd.personality_disorder_diagnosed_numeric == "10" ~ 1,
-        mhd.personality_disorder_numeric == "0" ~ 0
-      )
-  )
-
-mhd.raw.id <- mhd.raw.id %>%
-  mutate(
-    personality_cluster_c =
-      recode_factor(personality_cluster_c_numeric,
-                    "0" = "No personality disorder cluster C",
-                    "1" = "Personality disorder cluster C",
-                    missing = NA_character_
-                    )
-  )
-
-mhd.raw.id %>%
-  freq(personality_cluster_c,
-       cumul = F)
-}
-```
-
-```{r Check personality_cluster_c}
-if(GLAD == TRUE | NBR == TRUE | RAMP == TRUE) {
-mhd.raw.id %>%
-  select(
-    personality_cluster_c,
-    personality_cluster_c_numeric,
-    mhd.personality_disorder_diagnosed,
-    mhd.personality_disorder_diagnosed_numeric
-  )
-}
-```
-
-### Controls
-These individuals have no self report diagnosis of any kind that we measure. 
-```{r mhd control}
-mhd.raw.id <- mhd.raw.id %>%
-  mutate(
-    control_numeric =
-      if_else(
-    depressive_disorders_numeric == "0" &
-    anxiety_disorders_numeric == "0" &
-    eating_disorders_numeric == "0" &
-    obsessive_compulsive_disorders_numeric == "0" &
-    psychotic_disorders_numeric == "0" &
-    mhd.mania_hypomania_bipolar_or_manicdepression_numeric == "0" &
-    mhd.posttraumatic_stress_disorder_ptsd_numeric == "0" &
-    mhd.autism_aspergers_or_autistic_spectrum_disorder_numeric == "0" &
-    mhd.attention_deficit_hyperactivity_disorder_numeric == "0" &
-    mhd.personality_disorder_numeric == "0", 
-    true = 1, 
-    false = 0, 
-    NA_real_)
-  )
-
-mhd.raw.id <- mhd.raw.id %>%
-  mutate(
-    control =
-      recode_factor(control_numeric,
-                    "0" = "No control",
-                    "1" = "Control",
-                    missing = NA_character_
-                    )
-  )
-
-mhd.raw.id %>%
-  freq(control,
-       cumul = F)
-```
-
-## Total disorder count
-```{r disorders_total_count}
-disorder_columns <- c(
-    "depressive_disorders_numeric",
-    "anxiety_disorders_numeric",
-    "eating_disorders_numeric",
-    "obsessive_compulsive_disorders_numeric",
-    "psychotic_disorders_numeric",
-    "mhd.mania_hypomania_bipolar_or_manicdepression_numeric",
-    "mhd.posttraumatic_stress_disorder_ptsd_numeric",
-    "mhd.autism_aspergers_or_autistic_spectrum_disorder_numeric",
-    "mhd.attention_deficit_hyperactivity_disorder_numeric",
-    "mhd.personality_disorder_numeric"
-)
-
-mhd.raw.id <- mhd.raw.id %>%
-  mutate(
-    disorders_total_count =
-      rowSums(.[disorder_columns])
-  )
-
-mhd.raw.id %>%
-  freq(disorders_total_count,
-       cumul = F)
-```
-
-## Comorbidity count
-```{r cormorbidity_total_count}
-mhd.raw.id <- mhd.raw.id %>%
-  mutate(
-    comorbidity_total_count_numeric = 
-      case_when(
-        disorders_total_count == 1 ~ 0,
-        disorders_total_count > 1 ~ disorders_total_count - 1
-  )
-  )
-
-mhd.raw.id %>%
-  freq(comorbidity_total_count_numeric,
-       cumul = F)
-```
-
-```{r comordbitiy_total_count_factor}
-mhd.raw.id <- mhd.raw.id %>%
-  mutate(
-    comorbidity_total_count_factor_numeric =
-      case_when(
-    comorbidity_total_count_numeric == "0" ~ 0,
-    comorbidity_total_count_numeric == "1" ~ 1,
-    comorbidity_total_count_numeric == "2" ~ 2,
-    comorbidity_total_count_numeric > 2 ~ 3
-    )
-  )
-
-mhd.raw.id <- mhd.raw.id %>%
-  mutate(
-    comorbidity_total_count_factor =
-      recode_factor(comorbidity_total_count_factor_numeric,
-                    "0" = "No comorbidity",
-                    "1" = "1 comorbid disoder",
-                    "2" = "2 comorbid disoders",
-                    "3" = "3+ comorbid disoder",
-                    missing = NA_character_
-                    )
-  )
-
-mhd.raw.id %>%
-  freq(comorbidity_total_count_factor,
-       cumul = F)
-```
-
-## Inspection
-```{r glad mhd head}
-head(mhd.raw.id)
-```
-
-```{r mhd summary}
-summarytools::dfSummary(
-  mhd.raw.id,
-  graph.col = F,
-  valid.col = F,
-  labels.col = F)
-```
-
-Create new dataframe with the derived categories
-```{r mhd categories}
-if(GLAD == TRUE | NBR == TRUE | RAMP == TRUE) {
-mhd.raw.categories <- mhd.raw.id %>%
-  select(
-    Sample,
-    ID,
-    anxiety_disorders_numeric,
-    anxiety_disorders,
-    mhd.specific_phobia_e.g._phobia_of_flying_numeric,
-    mhd.specific_phobia_e.g._phobia_of_flying,
-    mhd.social_anxiety_or_social_phobia_numeric,
-    mhd.social_anxiety_or_social_phobia,
-    agoraphobia_panic_disorder_numeric,
-    agoraphobia_panic_disorder,
-    depressive_disorders_numeric,
-    depressive_disorders,
-    eating_disorders_numeric,
-    eating_disorders,
-    obsessive_compulsive_disorders_numeric,
-    obsessive_compulsive_disorders,
-    psychotic_disorders_numeric,
-    psychotic_disorders,
-    mhd.mania_hypomania_bipolar_or_manicdepression_numeric,
-    mhd.mania_hypomania_bipolar_or_manicdepression,
-    mhd.posttraumatic_stress_disorder_ptsd_numeric,
-    mhd.posttraumatic_stress_disorder_ptsd,
-    mhd.autism_aspergers_or_autistic_spectrum_disorder_numeric,
-    mhd.autism_aspergers_or_autistic_spectrum_disorder,
-    mhd.attention_deficit_hyperactivity_disorder_numeric,
-    mhd.attention_deficit_hyperactivity_disorder,
-    mhd.personality_disorder_numeric,
-    mhd.personality_disorder,
-    personality_cluster_a_numeric,
-    personality_cluster_a,
-    personality_cluster_b_numeric,
-    personality_cluster_b,
-    personality_cluster_c_numeric,
-    personality_cluster_c,
-    depression_and_anxiety_numeric,
-    depression_and_anxiety,
-    restricting_vs_binge_eating_eating_disorders_numeric,
-    restricting_vs_binge_eating_eating_disorders,
-    bipolar_and_schizophrenia_numeric,
-    bipolar_and_schizophrenia,
-    control_numeric,
-    control,
-    disorders_total_count,
-    comorbidity_total_count_numeric,
-    comorbidity_total_count_factor_numeric,
-    comorbidity_total_count_factor
-    )
-}
-```
-
-```{r mhd categories}
-if(EDGI == TRUE) {
-mhd.raw.categories <- mhd.raw.id %>%
-  select(
-    Sample,
-    ID,
-    anxiety_disorders_numeric,
-    anxiety_disorders,
-    mhd.specific_phobia_e.g._phobia_of_flying_numeric,
-    mhd.specific_phobia_e.g._phobia_of_flying,
-    mhd.social_anxiety_or_social_phobia_numeric,
-    mhd.social_anxiety_or_social_phobia,
-    agoraphobia_panic_disorder_numeric,
-    agoraphobia_panic_disorder,
-    depressive_disorders_numeric,
-    depressive_disorders,
-    eating_disorders_numeric,
-    eating_disorders,
-    obsessive_compulsive_disorders_numeric,
-    obsessive_compulsive_disorders,
-    psychotic_disorders_numeric,
-    psychotic_disorders,
-    mhd.mania_hypomania_bipolar_or_manicdepression_numeric,
-    mhd.mania_hypomania_bipolar_or_manicdepression,
-    mhd.posttraumatic_stress_disorder_ptsd_numeric,
-    mhd.posttraumatic_stress_disorder_ptsd,
-    mhd.autism_aspergers_or_autistic_spectrum_disorder_numeric,
-    mhd.autism_aspergers_or_autistic_spectrum_disorder,
-    mhd.attention_deficit_hyperactivity_disorder_numeric,
-    mhd.attention_deficit_hyperactivity_disorder,
-    mhd.personality_disorder_numeric,
-    mhd.personality_disorder,
-#    personality_cluster_a_numeric,
-#    personality_cluster_a,
-#    personality_cluster_b_numeric,
-#    personality_cluster_b,
-#    personality_cluster_c_numeric,
-#    personality_cluster_c,
-    depression_and_anxiety_numeric,
-    depression_and_anxiety,
-    restricting_vs_binge_eating_eating_disorders_numeric,
-    restricting_vs_binge_eating_eating_disorders,
-    bipolar_and_schizophrenia_numeric,
-    bipolar_and_schizophrenia,
-    control_numeric,
-    control,
-    disorders_total_count,
-    comorbidity_total_count_numeric,
-    comorbidity_total_count_factor_numeric,
-    comorbidity_total_count_factor
-    ) %>%
-  add_column(
-    personality_cluster_a_numeric = NA_real_,
-    personality_cluster_a = NA_real_,
-    personality_cluster_b_numeric = NA_real_,
-    personality_cluster_b = NA_real_,
-    personality_cluster_c_numeric = NA_real_,
-    personality_cluster_c = NA_real_    
-  )
-}
-```
-
-# Prepandemic
-
-## gad (prepan)
-
-```{r glad gad prepan cols}
-if(GLAD == TRUE){
-glad.gad.raw <- readRDS(file = paste0(data.raw_path, "/glad/gad_glad.rds"))
-dim(glad.gad.raw)
-colnames(glad.gad.raw)
-}
-```
-
-```{r glad gad prepan cleaning}
-if(GLAD ==TRUE){
-exclude_cols <- c("Sample",
-                  "ID")
-glad.gad.raw.id <- glad.gad.raw %>%
-  drop_na(externalDataReference) %>% # Drop NAs
-  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
-  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
-  mutate(ID = as.numeric(ID)) %>%
-  select(
-    Sample, # Sample
-    ID, # ID
-    gad.feeling_nervous_anxious_or_on_edge_prepan = gad.feeling_nervous_anxious_or_on_edge,
-    gad.control_worrying_stop_prepan = gad.control_worrying_stop,
-    gad.worrying_too_much_about_different_things_prepan = gad.worrying_too_much_about_different_things,
-    gad.trouble_relaxing_prepan = gad.trouble_relaxing,
-    gad.sit_restless_hard_prepan = gad.sit_restless_hard,
-    gad.becoming_easily_annoyed_or_irritable_prepan = gad.becoming_easily_annoyed_or_irritable,
-    gad.awful_feeling_afraid_happen_prepan = gad.awful_feeling_afraid_happen
-  ) %>%
-  add_numeric(., exclude = exclude_cols) %>%
-  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
-  mutate_if(is.numeric, ~na_if(., -99)) %>%
-  mutate_if(is.numeric, ~na_if(., -77)) %>%
-  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
-  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
-
-# Inspect dimensions
-dim(glad.gad.raw.id)
-# Inspect colnames
-colnames(glad.gad.raw.id)
-#Differences
-dim(glad.gad.raw)[1]-dim(glad.gad.raw.id)[1]
-}
-```
-
-```{r glad copy prepan gad}
-if(GLAD == TRUE){
-prepan.gad.raw.id <- glad.gad.raw.id
-}
-```
-
-```{r edgi gad prepan cols}
-if(EDGI == TRUE){
-  edgi.gad.raw <- readRDS(file = paste0(data.raw_path, "/edgi/gad_edgi.rds"))
-  dim(edgi.gad.raw)
-  colnames(edgi.gad.raw)
-}
-```
-
-```{r edgi gad prepan cleaning}
-if(EDGI == TRUE){
-exclude_cols <- c("Sample",
-                  "ID")
-
-edgi.gad.raw.id <- edgi.gad.raw %>%
-  drop_na(externalDataReference) %>% # Drop NAs
-  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
-  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
-  mutate(ID = as.numeric(ID)) %>%
-  select(
-    Sample, # Sample
-    ID, # ID
-    gad.feeling_nervous_anxious_or_on_edge_prepan = gad.feeling_nervous_anxious_or_on_edge,
-    gad.control_worrying_stop_prepan = gad.control_worrying_stop,
-    gad.worrying_too_much_about_different_things_prepan = gad.worrying_too_much_about_different_things,
-    gad.trouble_relaxing_prepan = gad.trouble_relaxing,
-    gad.sit_restless_hard_prepan = gad.sit_restless_hard,
-    gad.becoming_easily_annoyed_or_irritable_prepan = gad.becoming_easily_annoyed_or_irritable,
-    gad.awful_feeling_afraid_happen_prepan = gad.awful_feeling_afraid_happen
-  ) %>%
-  add_numeric(., exclude = exclude_cols) %>%
-  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
-  mutate_if(is.numeric, ~na_if(., -99)) %>%
-  mutate_if(is.numeric, ~na_if(., -77)) %>%
-  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
-  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
-
-# Inspect dimensions
-dim(edgi.gad.raw.id)
-# Inspect colnames
-colnames(edgi.gad.raw.id)
-#Differences
-dim(edgi.gad.raw)[1]-dim(edgi.gad.raw.id)[1]
-}
-```
-
-```{r edgi copy prepan gad}
-if(EDGI == TRUE){
-  prepan.gad.raw.id <- edgi.gad.raw.id
-}
-```
-
-Calculate sum score for GAD-7
-Max should be 21.
-
-*Note that scores with missingness will be changed to NA later in the script
-```{r gad sum score prepan raw}
-if(GLAD ==TRUE | EDGI == TRUE){
-# Create vector with scoring key: If the item is reversed coded use -1. 
-# There needs to be the correct number of values for each item in the questionnaire. 
-gad.items_key_prepan <- c(1,1,1,1,1,1,1)
-
-# Create vector with items that are included in total score
-gad.items_prepan <- c(
-  "gad.feeling_nervous_anxious_or_on_edge_prepan_numeric",
-  "gad.control_worrying_stop_prepan_numeric",
-  "gad.worrying_too_much_about_different_things_prepan_numeric",
-  "gad.trouble_relaxing_prepan_numeric",
-  "gad.sit_restless_hard_prepan_numeric",
-  "gad.becoming_easily_annoyed_or_irritable_prepan_numeric",
-  "gad.awful_feeling_afraid_happen_prepan_numeric"
-  )
-
-# Calulate total score
-gad.scored_items_prepan <- scoreItems(keys = gad.items_key_prepan,
-                                        items = prepan.gad.raw.id[gad.items_prepan],
-                                        totals = TRUE, 
-                                        missing = TRUE, 
-                                        impute = 'none', 
-                                        min = 0, 
-                                        max = 3)
-# Add in column to tibble
-prepan.gad.raw.id$gad.sum_score_prepan_raw <- gad.scored_items_prepan$scores
-
-# Look at values
-prepan.gad.raw.id %>%
-  descr(gad.sum_score_prepan_raw,
-        stats = "common"
-        )
-}
-```
-
-missingness (NAs per person)
-
-prepandemic
-```{r gad prepan missingness}
-if(GLAD ==TRUE | EDGI == TRUE){
-prepan.gad.raw.id <- prepan.gad.raw.id %>%
-  mutate(
-    na_per_person_gad_prepan =         # variable for NA per person
-      rowSums(                       
-        is.na(.[gad.items_prepan])
-      )
-  )
-
-prepan.gad.raw.id %>%
-  freq(na_per_person_gad_prepan,
-       cumul = F)
-}
-```
-
-```{r gad prepan sum score if missigng items set to NA}
-if(GLAD ==TRUE | EDGI == TRUE){
-prepan.gad.raw.id <- prepan.gad.raw.id %>%
-  mutate(
-    gad.sum_score_prepan =
-      if_else(condition = na_per_person_gad_prepan > 0,
-              true = NA_real_,
-              false = gad.sum_score_prepan_raw,
-              missing = NA_real_
-              )
-  )
-
-prepan.gad.raw.id %>%
-  descr(gad.sum_score_prepan_raw, stats = "common")
-
-prepan.gad.raw.id %>%
-  descr(gad.sum_score_prepan, stats = "common")
-}
-```
-
-```{r glad prepan gad head}
-if(GLAD ==TRUE | EDGI == TRUE){
-head(prepan.gad.raw.id)
-}
-```
-
-```{r glad prepan gad summary}
-if(GLAD ==TRUE | EDGI == TRUE){
-summarytools::dfSummary(
-  prepan.gad.raw.id,
-  graph.col = F,
-  valid.col = F,
-  labels.col = F)
-}
-```
-
-## pcl (prepan)
-
-```{r glad prepandemic pcl cols}
-if(GLAD == TRUE) {
-glad.pcl.raw <- readRDS(file = paste0(data.raw_path,"/glad/pcl_glad.rds"))
-dim(glad.pcl.raw)
-colnames(glad.pcl.raw)
-}
-```
-
-```{r glad prepandemic pcl cleaning}
-if(GLAD == TRUE) {
-exclude_cols <- c("Sample",
-                  "ID")
-glad.pcl.raw.id <- glad.pcl.raw %>%
-  drop_na(externalDataReference) %>% # Drop NAs
-  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
-  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
-  mutate(ID = as.numeric(ID)) %>%
-  select(
-    Sample, # Sample
-    ID, # ID
-    pcl.stressful_experience_repeated_images_prepan = pcl.stressful_experience_repeated_images,
-    pcl.stressful_experience_upset_reminded_prepan = pcl.stressful_experience_upset_reminded,
-    pcl.stressful_situation_avoiding_activities_prepan = pcl.stressful_situation_avoiding_activities,
-    pcl.cut_people_feeling_distant_prepan = pcl.cut_people_feeling_distant,
-    pcl.feeling_irritable_or_having_angry_outbursts_prepan = pcl.feeling_irritable_or_having_angry_outbursts,
-    pcl.difficulty_concentrating_prepan = pcl.difficulty_concentrating
-  ) %>%
-  add_numeric(., exclude = exclude_cols) %>%
-  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
-  mutate_if(is.numeric, ~na_if(., -99)) %>%
-  mutate_if(is.numeric, ~na_if(., -77)) %>%
-  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
-  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
-
-# Inspect dimensions
-dim(glad.pcl.raw.id)
-# Inspect colnames
-colnames(glad.pcl.raw.id)
-#Differences
-dim(glad.pcl.raw)[1]-dim(glad.pcl.raw.id)[1]
-}
-```
-
-```{r glad pcl prepan copy}
-if(GLAD == TRUE) {
-  prepan.pcl.raw.id <- glad.pcl.raw.id
-}
-```
-
-```{r edgi pcl cols}
-if(EDGI == TRUE) {
-  edgi.pcl.raw <- readRDS(file = paste0(data.raw_path,"/edgi/pcl_edgi.rds"))
-  dim(edgi.pcl.raw)
-  colnames(edgi.pcl.raw)
-}
-```
-
-```{r edgi pcl cleaning}
-if(EDGI == TRUE) {
-  edgi.pcl.raw.id <- edgi.pcl.raw %>%
-    drop_na(externalDataReference) %>% # Drop NAs
-    distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
-    separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
-    mutate(ID = as.numeric(ID)) %>%
-    select(
-      Sample, # Sample
-      ID, # ID
-      pcl.stressful_experience_repeated_images_prepan = pcl.stressful_experience_repeated_images,
-      pcl.stressful_experience_upset_reminded_prepan = pcl.stressful_experience_upset_reminded,
-      pcl.stressful_situation_avoiding_activities_prepan = pcl.stressful_situation_situations_reminded, # different to glad: pcl.stressful_situation_avoiding_activities,
-      pcl.cut_people_feeling_distant_prepan = pcl.cut_people_feeling_distant,
-      pcl.feeling_irritable_or_having_angry_outbursts_prepan = pcl.feeling_irritable_or_having_angry_outbursts,
-      pcl.difficulty_concentrating_prepan = pcl.difficulty_concentrating
-    ) %>%
-    add_numeric(., exclude = exclude_cols) %>%
-    mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
-    mutate_if(is.numeric, ~na_if(., -99)) %>%
-    mutate_if(is.numeric, ~na_if(., -77)) %>%
-    mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
-    mutate_if(is.factor, ~na_if(., "Don't know")) %>%
-    mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
-    mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
-    mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
-    mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
-    mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
-    mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
-
-  # Inspect dimensions
-  dim(edgi.pcl.raw.id)
-  # Inspect colnames
-  colnames(edgi.pcl.raw.id)
-  #Differences
-  dim(edgi.pcl.raw)[1]-dim(edgi.pcl.raw.id)[1]
-}
-```
-
-```{r edgi pcl prepan copy}
-if(EDGI == TRUE) {
-  prepan.pcl.raw.id <- edgi.pcl.raw.id
-}
-```
-
-Calculate sum score for PCL-6
-
-*Note that scores with missingness will be changed to NA later in the script
-```{r pcl sum score prepan}
-if(GLAD == TRUE | EDGI == TRUE){
-# Create vector with scoring key: If the item is reversed coded use -1. 
-# There needs to be the correct number of values for each item in the questionnaire. 
-pcl.items_key_prepan <- c(1,1,1,1,1,1)
-
-# Create vector with items that are included in total score
-pcl.items_prepan <- c(
-  "pcl.stressful_experience_repeated_images_prepan_numeric",
-  "pcl.stressful_experience_upset_reminded_prepan_numeric",
-  "pcl.stressful_situation_avoiding_activities_prepan_numeric",
-  "pcl.cut_people_feeling_distant_prepan_numeric",
-  "pcl.feeling_irritable_or_having_angry_outbursts_prepan_numeric",
-  "pcl.difficulty_concentrating_prepan_numeric"
-  )
-
-# Calulate total score
-pcl.scored_items_prepan <- scoreItems(keys = pcl.items_key_prepan,
-                                        items = prepan.pcl.raw.id[pcl.items_prepan],
-                                        totals = TRUE, 
-                                        missing = TRUE, 
-                                        impute = 'none', 
-                                        min = 1, 
-                                        max = 5)
-# Add in column to tibble
-prepan.pcl.raw.id$pcl.sum_score_prepan_raw <- pcl.scored_items_prepan$scores
-
-# Look at values
-prepan.pcl.raw.id %>%
-  descr(pcl.sum_score_prepan_raw,
-        stats = "common"
-        )
-}
-```
-
-Missigness
-
-prepandemic
-```{r pcl prepan missingness}
-if(GLAD == TRUE | EDGI == TRUE){
-prepan.pcl.raw.id <- prepan.pcl.raw.id %>%
-  mutate(
-    na_per_person_pcl_prepan =         # variable for NA per person
-      rowSums(                       
-        is.na(.[pcl.items_prepan])
-      )
-  )
-
-prepan.pcl.raw.id %>%
-  freq(na_per_person_pcl_prepan,
-       cumul = F)
-}
-```
-
-```{r pcl prepan sum score if missigng items set to NA}
-if(GLAD == TRUE | EDGI == TRUE){
-prepan.pcl.raw.id <- prepan.pcl.raw.id %>%
-  mutate(
-    pcl.sum_score_prepan =
-      if_else(condition = na_per_person_pcl_prepan > 0,
-              true = NA_real_,
-              false = pcl.sum_score_prepan_raw,
-              missing = NA_real_
-      )
-  )
-
-prepan.pcl.raw.id %>%
-  descr(pcl.sum_score_prepan_raw, stats = "common")
-
-prepan.pcl.raw.id %>%
-  descr(pcl.sum_score_prepan, stats = "common")
-}
-```
-
-```{r pcl prepan head}
-if(GLAD == TRUE | EDGI == TRUE){
-head(prepan.pcl.raw.id)
-}
-```
-
-```{r pcl prepan summary}
-if(GLAD == TRUE | EDGI == TRUE){
-summarytools::dfSummary(
-  prepan.pcl.raw.id,
-  graph.col = F,
-  valid.col = F, labels.col = F)
-}
-```
-
-## phq (prepan)
-
-```{r glad phq cols}
-if(GLAD == TRUE){
-glad.phq.raw <- readRDS(file = paste0(data.raw_path, "/glad/phq_glad.rds"))
-dim(glad.phq.raw)
-colnames(glad.phq.raw)
-}
-```
-
-```{r glad phq cleaning}
-if(GLAD == TRUE){
-glad.phq.raw.id <- glad.phq.raw %>%
-  drop_na(externalDataReference) %>% # Drop NAs
-  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
-  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
-  mutate(ID = as.numeric(ID)) %>%
-  select(
-    Sample, # Sample
-    ID, # ID
-    phq.little_interest_or_pleasure_in_doing_things_prepan = phq.little_interest_or_pleasure_in_doing_things,
-    phq.feeling_down_depressed_or_hopeless_prepan = phq.feeling_down_depressed_or_hopeless,
-    phq.staying_asleep_sleeping_trouble_prepan = phq.staying_asleep_sleeping_trouble,
-    phq.feeling_tired_or_having_little_energy_prepan = phq.feeling_tired_or_having_little_energy,
-    phq.poor_appetite_or_overeating_prepan = phq.poor_appetite_or_overeating,
-    phq.feeling_bad_failure_family_prepan = phq.feeling_bad_failure_family,
-    phq.trouble_concentrating_reading_newspaper_prepan = phq.trouble_concentrating_reading_newspaper,
-    phq.moving_fidgety_noticed_opposite_prepan = phq.moving_fidgety_noticed_opposite,
-    phq.dead_hurting_thoughts_prepan = phq.dead_hurting_thoughts
-  ) %>%
-  add_numeric(., exclude = exclude_cols) %>%
-  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
-  mutate_if(is.numeric, ~na_if(., -99)) %>%
-  mutate_if(is.numeric, ~na_if(., -77)) %>%
-  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
-  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
-
-# Inspect dimensions
-dim(glad.phq.raw.id)
-# Inspect colnames
-colnames(glad.phq.raw.id)
-#Differences
-dim(glad.phq.raw)[1]-dim(glad.phq.raw.id)[1]
-}
-```
-
-```{r glad phq prepan copy}
-if(GLAD == TRUE) {
-  prepan.phq.raw.id <- glad.phq.raw.id
-}
-```
-
-```{r edgi phq cols}
-if(EDGI == TRUE){
-  edgi.phq.raw <- readRDS(file = paste0(data.raw_path, "/edgi/phq_edgi.rds"))
-  dim(edgi.phq.raw)
-  colnames(edgi.phq.raw)
-}
-```
-
-```{r edgi phq cleaning}
-if(EDGI == TRUE){
-  edgi.phq.raw.id <- edgi.phq.raw %>%
-    drop_na(externalDataReference) %>% # Drop NAs
-    distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
-    separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
-    mutate(ID = as.numeric(ID)) %>%
-    select(
-      Sample, # Sample
-      ID, # ID
-      phq.little_interest_or_pleasure_in_doing_things_prepan = phq.little_interest_or_pleasure_in_doing_things,
-      phq.feeling_down_depressed_or_hopeless_prepan = phq.feeling_down_depressed_or_hopeless,
-      phq.staying_asleep_sleeping_trouble_prepan = phq.staying_asleep_sleeping_trouble,
-      phq.feeling_tired_or_having_little_energy_prepan = phq.feeling_tired_or_having_little_energy,
-      phq.poor_appetite_or_overeating_prepan = phq.poor_appetite_or_overeating,
-      phq.feeling_bad_failure_family_prepan = phq.feeling_bad_failure_family,
-      phq.trouble_concentrating_reading_newspaper_prepan = phq.trouble_concentrating_reading_newspaper,
-      phq.moving_fidgety_noticed_opposite_prepan = phq.moving_fidgety_noticed_opposite,
-      phq.dead_hurting_thoughts_prepan = phq.dead_hurting_thoughts
-    ) %>%
-    add_numeric(., exclude = exclude_cols) %>%
-    mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
-    mutate_if(is.numeric, ~na_if(., -99)) %>%
-    mutate_if(is.numeric, ~na_if(., -77)) %>%
-    mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
-    mutate_if(is.factor, ~na_if(., "Don't know")) %>%
-    mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
-    mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
-    mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
-    mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
-    mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
-    mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
-
-  # Inspect dimensions
-  dim(edgi.phq.raw.id)
-  # Inspect colnames
-  colnames(edgi.phq.raw.id)
-  #Differences
-  dim(edgi.phq.raw)[1]-dim(edgi.phq.raw.id)[1]
-}
-```
-
-```{r edgi phq prepan copy}
-if(EDGI == TRUE) {
-  prepan.phq.raw.id <- edgi.phq.raw.id
-}
-```
-
-Calculate sum score for PHQ-9
-
-*Note that scores with missingness will be changed to NA later in the script
-```{r phq sum score prepan}
-if(GLAD == TRUE | EDGI == TRUE) {
-# Create vector with scoring key: If the item is reversed coded use -1. 
-# There needs to be the correct number of values for each item in the questionnaire. 
-phq.items_key_prepan <- c(1,1,1,1,1,1,1,1,1)
-
-# Create vector with items that are included in sum score
-phq.items_prepan <- c(
-  "phq.little_interest_or_pleasure_in_doing_things_prepan_numeric",
-  "phq.feeling_down_depressed_or_hopeless_prepan_numeric",
-  "phq.staying_asleep_sleeping_trouble_prepan_numeric",
-  "phq.feeling_tired_or_having_little_energy_prepan_numeric",
-  "phq.poor_appetite_or_overeating_prepan_numeric",
-  "phq.feeling_bad_failure_family_prepan_numeric",
-  "phq.trouble_concentrating_reading_newspaper_prepan_numeric",
-  "phq.moving_fidgety_noticed_opposite_prepan_numeric",
-  "phq.dead_hurting_thoughts_prepan_numeric"
-  )
-
-# Calulate sum score
-phq.scored_items_prepan <- scoreItems(keys = phq.items_key_prepan,
-                                        items = prepan.phq.raw.id[phq.items_prepan],
-                                        totals = TRUE, 
-                                        missing = TRUE, 
-                                        impute = 'none', 
-                                        min = 0, 
-                                        max = 3)
-# Add in column to tibble
-prepan.phq.raw.id$phq.sum_score_prepan_raw <- phq.scored_items_prepan$scores
-
-# Look at values
-prepan.phq.raw.id %>%
-  descr(phq.sum_score_prepan_raw,
-        stats = "common"
-        )
-}
-```
-
-PHQ missingness (NAs per person)
-
-prepandemic
-```{r phq prepan missingness}
-if(GLAD == TRUE | EDGI == TRUE) {
-prepan.phq.raw.id <- prepan.phq.raw.id %>%
-  mutate(
-    na_per_person_phq_prepan =         # variable for NA per person
-      rowSums(                       
-        is.na(.[phq.items_prepan])
-      )
-  )
-
-prepan.phq.raw.id %>%
-  freq(na_per_person_phq_prepan,
-       cumul = F)
-}
-```
-
-```{r phq prepan missingness 8 items}
-if(GLAD == TRUE | EDGI == TRUE) {
-prepan.phq.raw.id <- prepan.phq.raw.id %>%
-  mutate(
-    phq.missing_only_suicide_item_prepan = 
-      if_else(
-        condition = na_per_person_phq_prepan == 1 & 
-          is.na(phq.dead_hurting_thoughts_prepan_numeric), 
-        true = 1,
-        false = 0,
-        missing = NA_real_
-      )
-  )
-
-prepan.phq.raw.id %>%
-  freq(phq.missing_only_suicide_item_prepan,
-       cumul = F)
-}
-```
-
-all times
-```{r phq prepan sum score if missigng items set to NA - all items}
-if(GLAD == TRUE | EDGI == TRUE) {
-prepan.phq.raw.id <- prepan.phq.raw.id %>%
-  mutate(
-    phq.sum_score_prepan =
-      if_else(condition = na_per_person_phq_prepan > 0,
-              true = NA_real_,
-              false = phq.sum_score_prepan_raw,
-              missing = NA_real_
-      )
-  )
-
-prepan.phq.raw.id %>%
-  descr(phq.sum_score_prepan_raw, stats = "common")
-
-prepan.phq.raw.id %>%
-  descr(phq.sum_score_prepan, stats = "common")
-}
-```
-
-+++CH: THINK ABOUT THIS!!!
-
-8 items
-```{r phq prepan sum score if missigng items set to NA - 8 items}
-if(GLAD == TRUE | EDGI == TRUE) {
-prepan.phq.raw.id <- prepan.phq.raw.id %>%
-  mutate(
-    phq.sum_score_8items_prepan =
-      if_else(condition = na_per_person_phq_prepan > 1 &
-                phq.missing_only_suicide_item_prepan == 1,
-              true = NA_real_,
-              false = phq.sum_score_prepan_raw,
-              missing = NA_real_
-      )
-  )
-
-prepan.phq.raw.id %>%
-  descr(phq.sum_score_8items_prepan, stats = "common")
-
-prepan.phq.raw.id %>%
-  descr(phq.sum_score_8items_prepan, stats = "common")
-}
-```
-
-```{r phq prepan head}
-if(GLAD == TRUE | EDGI == TRUE) {
-head(prepan.phq.raw.id)
-}
-```
-
-```{r phq prepan summary}
-if(GLAD == TRUE | EDGI == TRUE) {
-summarytools::dfSummary(
-  prepan.phq.raw.id,
-  graph.col = F,
-  valid.col = F
-  )
-}
-```
-
-## ocir (prepan)
-
-```{r glad ocir prepan cols}
-if(GLAD == TRUE){
-glad.ocir.raw <- readRDS(file = paste0(data.raw_path, "/glad/ocir_glad.rds"))
-dim(glad.ocir.raw)
-colnames(glad.ocir.raw)
-}
-```
-
-```{r glad ocir prepan cleaning}
-if(GLAD == TRUE){
-glad.ocir.raw.id <- glad.ocir.raw %>%
-  drop_na(externalDataReference) %>% # Drop NAs
-  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
-  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
-  mutate(ID = as.numeric(ID),) %>%
-  select(
-    Sample, # Sample
-    ID, # ID
-    ocir.i_repeatedly_check_doors_windows_drawers_etc_prepan = ocir.i_repeatedly_check_doors_windows_drawers_etc.,
-    ocir.arranged_things_change_upset_prepan = ocir.arranged_things_change_upset,
-    ocir.repeat_feel_numbers_prepan = ocir.repeat_feel_numbers,
-    ocir.clean_simply_wash_feel_prepan = ocir.clean_simply_wash_feel,
-    ocir.mind_upset_unpleasant_thoughts_prepan = ocir.mind_upset_unpleasant_thoughts,
-    ocir.afraid_avoid_throwing_things_prepan = ocir.afraid_avoid_throwing_things,
-    ocir.light_switches_water_taps_prepan = ocir.light_switches_water_taps,
-    ocir.arranged_things_prepan = ocir.arranged_things,
-    ocir.good_feel_bad_numbers_prepan = ocir.good_feel_bad_numbers,
-    ocir.hands_longer_wash_prepan = ocir.hands_longer_wash,
-    ocir.saved_things_prepan = ocir.saved_things,
-    ocir.frequently_difficulty_rid_nasty_prepan = ocir.frequently_difficulty_rid_nasty,
-    ocir.i_check_things_more_often_than_necessary_prepan = ocir.i_check_things_more_often_than_necessary.,
-    ocir.arranged_properly_objects_upset_prepan = ocir.arranged_properly_objects_upset,
-    ocir.feel_compelled_count_things_prepan = ocir.feel_compelled_count_things,
-    ocir.strangers_touch_touched_difficult_prepan = ocir.strangers_touch_touched_difficult,
-    ocir.control_difficult_find_thoughts_prepan = ocir.control_difficult_find_thoughts,
-    ocir.i_collect_things_i_dont_need_prepan = ocir.i_collect_things_i_dont_need
-  ) %>%
-  add_numeric(., exclude = exclude_cols) %>%
-  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
-  mutate_if(is.numeric, ~na_if(., -99)) %>%
-  mutate_if(is.numeric, ~na_if(., -77)) %>%
-  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
-  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
-
-# Inspect dimensions
-dim(glad.ocir.raw.id)
-# Inspect colnames
-colnames(glad.ocir.raw.id)
-#Differences
-dim(glad.ocir.raw)[1]-dim(glad.ocir.raw.id)[1]
-}
-```
-
-```{r glad ocir prepan copy}
-if(GLAD == TRUE) {
-  prepan.ocir.raw.id <- glad.ocir.raw.id
-}
-```
-
-```{r edgi ocir prepan cols}
-if(EDGI == TRUE){
-  edgi.ocir.raw <- readRDS(file = paste0(data.raw_path, "/edgi/ocir_edgi.rds"))
-  dim(edgi.ocir.raw)
-  colnames(edgi.ocir.raw)
-}
-```
-
-```{r edgi ocir prepan cleaning}
-if(EDGI == TRUE){
-  edgi.ocir.raw.id <- edgi.ocir.raw %>%
-    drop_na(externalDataReference) %>% # Drop NAs
-    distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
-    separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
-    mutate(ID = as.numeric(ID)) %>%
-    select(
-      Sample, # Sample
-      ID, # ID
-      ocir.i_repeatedly_check_doors_windows_drawers_etc_prepan = ocir.i_repeatedly_check_doors_windows_drawers_etc.,
-      ocir.arranged_things_change_upset_prepan = ocir.arranged_properly_objects_upset, # different GLAD: ocir.arranged_things_change_upset,
-      ocir.repeat_feel_numbers_prepan = ocir.repeat_feel_numbers.87, # ocir.repeat_feel_numbers,
-      ocir.clean_simply_wash_feel_prepan = ocir.clean_simply_wash_feel.9, # ocir.clean_simply_wash_feel,
-      ocir.mind_upset_unpleasant_thoughts_prepan = ocir.mind_upset_unpleasant_thoughts.11, # ocir.mind_upset_unpleasant_thoughts,
-      ocir.afraid_avoid_throwing_things_prepan = ocir.afraid_avoid_throwing_things.7, # ocir.afraid_avoid_throwing_things,
-      ocir.light_switches_water_taps_prepan = ocir.light_switches_water_taps.7, # ocir.light_switches_water_taps,
-      ocir.arranged_things_prepan = ocir.arranged_things.32, # ocir.arranged_things,
-      ocir.good_feel_bad_numbers_prepan = ocir.good_feel_bad_numbers.60, # ocir.good_feel_bad_numbers,
-      ocir.hands_longer_wash_prepan = ocir.hands_longer_wash.23, # ocir.hands_longer_wash,
-      ocir.saved_things_prepan = ocir.saved_things,
-      ocir.frequently_difficulty_rid_nasty_prepan = ocir.frequently_difficulty_rid_nasty.16, # ocir.frequently_difficulty_rid_nasty,
-      ocir.i_check_things_more_often_than_necessary_prepan = ocir.i_check_things_more_often_than_necessary.,
-      ocir.arranged_properly_objects_upset_prepan = ocir.arranged_properly_objects_upset,
-      ocir.feel_compelled_count_things_prepan = ocir.feel_compelled_count_things.27, # ocir.feel_compelled_count_things,
-      ocir.strangers_touch_touched_difficult_prepan = ocir.strangers_touch_touched_difficult.33, # ocir.strangers_touch_touched_difficult,
-      ocir.control_difficult_find_thoughts_prepan = ocir.control_difficult_find_thoughts.30, #ocir.control_difficult_find_thoughts,
-      ocir.i_collect_things_i_dont_need_prepan = ocir.i_collect_things_i_dont_need.348, # ocir.i_collect_things_i_dont_need
-    ) %>%
-    add_numeric(., exclude = exclude_cols) %>%
-    mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
-    mutate_if(is.numeric, ~na_if(., -99)) %>%
-    mutate_if(is.numeric, ~na_if(., -77)) %>%
-    mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
-    mutate_if(is.factor, ~na_if(., "Don't know")) %>%
-    mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
-    mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
-    mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
-    mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
-    mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
-    mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
-
-  # Inspect dimensions
-  dim(edgi.ocir.raw.id)
-  # Inspect colnames
-  colnames(edgi.ocir.raw.id)
-  #Differences
-  dim(edgi.ocir.raw)[1]-dim(edgi.ocir.raw.id)[1]
-}
-```
-
-```{r edgi ocir prepan copy}
-if(EDGI == TRUE) {
-  prepan.ocir.raw.id <- edgi.ocir.raw.id
-}
-```
-
-Calculate sum score for OCI-R
-
-*Note that scores with missingness will be changed to NA later in the script
-```{r ocir sum score prepan}
-if(GLAD == TRUE | EDGI == TRUE) {
-# Create vector with scoring key: If the item is reversed coded use -1. 
-# There needs to be the correct number of values for each item in the questionnaire. 
-ocir.items_key_prepan <- c(1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1)
-
-# Create vector with items that are included in sum score
-ocir.items_prepan = c(
-  "ocir.i_repeatedly_check_doors_windows_drawers_etc_prepan_numeric",
-  "ocir.arranged_things_change_upset_prepan_numeric",
-  "ocir.repeat_feel_numbers_prepan_numeric",
-  "ocir.clean_simply_wash_feel_prepan_numeric",
-  "ocir.mind_upset_unpleasant_thoughts_prepan_numeric",
-  "ocir.afraid_avoid_throwing_things_prepan_numeric",
-  "ocir.light_switches_water_taps_prepan_numeric",
-  "ocir.arranged_things_prepan_numeric",
-  "ocir.good_feel_bad_numbers_prepan_numeric",
-  "ocir.hands_longer_wash_prepan_numeric",
-  "ocir.saved_things_prepan_numeric",
-  "ocir.frequently_difficulty_rid_nasty_prepan_numeric",
-  "ocir.i_check_things_more_often_than_necessary_prepan_numeric",
-  "ocir.arranged_properly_objects_upset_prepan_numeric",
-  "ocir.feel_compelled_count_things_prepan_numeric",
-  "ocir.strangers_touch_touched_difficult_prepan_numeric",
-  "ocir.control_difficult_find_thoughts_prepan_numeric",
-  "ocir.i_collect_things_i_dont_need_prepan_numeric"
-  )
-
-# Calulate sum score
-ocir.scored_items_prepan <- scoreItems(keys = ocir.items_key_prepan,
-                                        items = prepan.ocir.raw.id[ocir.items_prepan],
-                                        totals = TRUE, 
-                                        missing = TRUE, 
-                                        impute = 'none', 
-                                        min = 0, 
-                                        max = 4)
-# Add in column to tibble
-prepan.ocir.raw.id$ocir.sum_score_prepan <- ocir.scored_items_prepan$scores
-
-# Look at values
-prepan.ocir.raw.id %>%
-  descr(ocir.sum_score_prepan,
-        stats = "common"
-        )
-}
-```
-
-prepandemic
-```{r ocir prepan missingness}
-if(GLAD == TRUE | EDGI == TRUE) {
-prepan.ocir.raw.id <- prepan.ocir.raw.id %>%
-  mutate(
-    na_per_person_ocir_prepan =         # variable for NA per person
-      rowSums(                       
-        is.na(.[ocir.items_prepan])
-      )
-  )
-
-prepan.ocir.raw.id %>%
-  freq(na_per_person_ocir_prepan,
-       cumul = F)
-}
-```
-
-```{r ocir prepan head}
-if(GLAD == TRUE | EDGI == TRUE) {
-head(prepan.ocir.raw.id)
-}
-```
-
-```{r ocir prepan summary}
-if(GLAD == TRUE | EDGI == TRUE) {
-summarytools::dfSummary(
-  prepan.ocir.raw.id,
-  graph.col = F,
-  valid.col = F
-  )
-}
-```
-
-# COPING GAD-7
-## GLAD
-```{r coping glad gad cols}
-if(GLAD == TRUE) {
-coping.glad.gad.raw <- readRDS(file = paste0(data.raw_path,"/glad/gad_coping_glad.rds"))
-dim(coping.glad.gad.raw)
-colnames(coping.glad.gad.raw)
-}
-```
-
-```{r coping glad gad summary}
-if(GLAD == TRUE) {
-summarytools::dfSummary(
-  coping.glad.gad.raw,
-  graph.col = F,
-  valid.col = F,
-  labels.col = F
-  )
-}
-```
-
-```{r coping glad gad cleaning}
-if(GLAD == TRUE) {
-exclude_cols_coping_glad <- c(
-  "Sample",
-  "ID",
-  "startDate.coping"
-)
-
-coping.glad.gad.raw.id <- coping.glad.gad.raw %>%
-  drop_na(externalDataReference) %>% # Drop NAs
-  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
-  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
-  mutate(ID = as.numeric(ID)
-         ) %>% 
-  select(
-    Sample, # Sample
-    ID, # ID
-    startDate.coping = startDate, # Rename startDate
-    gad.problems_made_difficult_care, # Impairment
-    gad.pandemic_felt_feelings, # Comparison to before the pandemic (retro)
-    gad.feeling_nervous_anxious_or_on_edge_retro = gad.feeling_nervous_anxious_or_on_edge,
-    gad.control_worrying_stop_retro = gad.control_worrying_stop,
-    gad.worrying_too_much_about_different_things_retro = gad.worrying_too_much_about_different_things,
-    gad.trouble_relaxing_retro = gad.trouble_relaxing,
-    gad.sit_restless_hard_retro = gad.sit_restless_hard,
-    gad.becoming_easily_annoyed_or_irritable_retro = gad.becoming_easily_annoyed_or_irritable,
-    gad.awful_feeling_afraid_happen_retro = gad.awful_feeling_afraid_happen,
-    gad.feeling_nervous_anxious_or_on_edge_base = gad.feeling_nervous_anxious_or_on_edge.1,
-    gad.control_worrying_stop_base = gad.control_worrying_stop.1,
-    gad.worrying_too_much_about_different_things_base = gad.worrying_too_much_about_different_things.1,
-    gad.trouble_relaxing_base = gad.trouble_relaxing.1,
-    gad.sit_restless_hard_base = gad.sit_restless_hard.1,
-    gad.becoming_easily_annoyed_or_irritable_base = gad.becoming_easily_annoyed_or_irritable.1,
-    gad.awful_feeling_afraid_happen_base = gad.awful_feeling_afraid_happen.1
-  ) %>%
-  add_numeric(., exclude = exclude_cols_coping_glad) %>%
-  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
-  mutate_if(is.numeric, ~na_if(., -99)) %>%
-  mutate_if(is.numeric, ~na_if(., -77)) %>%
-  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
-  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
-
-# Inspect dimensions
-dim(coping.glad.gad.raw.id)
-# Inspect colnames
-colnames(coping.glad.gad.raw.id)
-#Differences
-dim(coping.glad.gad.raw)[1]-dim(coping.glad.gad.raw.id)[1]
-}
-```
-
-```{r coping glad gad copy}
-if(GLAD == TRUE) {
-  coping.gad.raw.id <- coping.glad.gad.raw.id
-}
-```
-
-## EDGI
-```{r coping edgi gad cols}
-if(EDGI == TRUE) {
-  coping.edgi.gad.raw <- readRDS(file = paste0(data.raw_path,"/edgi/gad_coping_edgi.rds"))
-  dim(coping.edgi.gad.raw)
-  colnames(coping.edgi.gad.raw)
-}
-```
-
-```{r coping edgi gad summary}
-if(EDGI == TRUE) {
-  summarytools::dfSummary(
-    coping.edgi.gad.raw,
-    graph.col = F,
-    valid.col = F,
-    labels.col = T # to see what is baseline and what is retro
-  )
-}
-```
-
-```{r coping edgi gad cleaning}
-if(EDGI == TRUE) {
-  exclude_cols_coping_edgi <- c(
-    "Sample",
-    "ID",
-    "startDate.coping"
-  )
-
-  coping.edgi.gad.raw.id <- coping.edgi.gad.raw %>%
-    drop_na(externalDataReference) %>% # Drop NAs
-    distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
-    separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
-    mutate(ID = as.numeric(ID)
-    ) %>% 
-    select(
-      Sample, # Sample
-      ID, # ID
-      startDate.coping = startDate, # Rename startDate
-      gad.problems_made_difficult_care = gad.care_difficult_home_things, # Impairment (different to GLAD)
-      gad.pandemic_felt_feelings = gad.pandemic_feelings_felt, # Comparison to before the pandemic (retro; different to GLAD)
-      gad.feeling_nervous_anxious_or_on_edge_retro = gad.feeling_nervous_anxious_or_on_edge,
-      gad.control_worrying_stop_retro = gad.control_worrying_stop,
-      gad.worrying_too_much_about_different_things_retro = gad.worrying_too_much_about_different_things,
-      gad.trouble_relaxing_retro = gad.trouble_relaxing,
-      gad.sit_restless_hard_retro = gad.sit_restless_hard,
-      gad.becoming_easily_annoyed_or_irritable_retro = gad.becoming_easily_annoyed_or_irritable,
-      gad.awful_feeling_afraid_happen_retro = gad.feeling_afraid_awful_happen, # different to GLAD: gad.awful_feeling_afraid_happen,
-      gad.feeling_nervous_anxious_or_on_edge_base = gad.feeling_nervous_anxious_or_on_edge.1,
-      gad.control_worrying_stop_base = gad.control_worrying_stop.1,
-      gad.worrying_too_much_about_different_things_base = gad.worrying_too_much_about_different_things.1,
-      gad.trouble_relaxing_base = gad.trouble_relaxing.1,
-      gad.sit_restless_hard_base = gad.sit_restless_hard.1,
-      gad.becoming_easily_annoyed_or_irritable_base = gad.becoming_easily_annoyed_or_irritable.1,
-      gad.awful_feeling_afraid_happen_base = gad.feeling_afraid_awful_happen.1 # different to GLAD: gad.awful_feeling_afraid_happen.1
-    ) %>%
-    add_numeric(., exclude = exclude_cols_coping_edgi) %>%
-    mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
-    mutate_if(is.numeric, ~na_if(., -99)) %>%
-    mutate_if(is.numeric, ~na_if(., -77)) %>%
-    mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
-    mutate_if(is.factor, ~na_if(., "Don't know")) %>%
-    mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
-    mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
-    mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
-    mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
-    mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
-    mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
-
-  # Inspect dimensions
-  dim(coping.edgi.gad.raw.id)
-  # Inspect colnames
-  colnames(coping.edgi.gad.raw.id)
-  #Differences
-  dim(coping.edgi.gad.raw)[1]-dim(coping.edgi.gad.raw.id)[1]
-}
-```
-
-```{r coping edgi gad copy}
-if(EDGI == TRUE) {
-  coping.gad.raw.id <- coping.edgi.gad.raw.id
-}
-```
-
-## NBR
-```{r coping nbr gad cols}
-if(NBR == TRUE) {
-  coping.nbr.gad.raw <- readRDS(file = paste0(data.raw_path,"/nbr/gad_coping_nbr.rds"))
-  dim(coping.nbr.gad.raw)
-  colnames(coping.nbr.gad.raw)
-}
-```
-
-```{r coping nbr gad summary}
-if(NBR == TRUE) {
-  summarytools::dfSummary(
-    coping.nbr.gad.raw,
-    graph.col = F,
-    valid.col = F,
-    labels.col = F
-  )
-}
-```
-
-```{r coping nbr gad cleaning}
-if(NBR == TRUE) {
-  exclude_cols_coping_nbr <- c(
-    "Sample",
-    "ID",
-    "startDate.coping"
-  )
-
-  coping.nbr.gad.raw.id <- coping.nbr.gad.raw %>%
-  drop_na(subjectid) %>% # Drop NAs
-  distinct(subjectid, .keep_all = TRUE) %>% # Remove duplicates based on ID
-  separate(subjectid, into = c("Sample", "ID.intm"), sep = 6) %>% # Split ID in Sample and Number
-  separate(ID.intm, into = "ID", sep = 7) %>%
-  mutate(ID = as.numeric(ID)) %>% 
-    select(
-      Sample, # Sample
-      ID, # ID
-      startDate.coping = startDate, # Rename startDate
-      gad.problems_made_difficult_care = gad.problems_made_care_difficult, # Impairment (different from GLAD)
-      gad.pandemic_felt_feelings, # Comparison to before the pandemic (retro)
-      gad.feeling_nervous_anxious_or_on_edge_retro = gad.feeling_nervous_anxious_or_on_edge,
-      gad.control_worrying_stop_retro = gad.control_worrying_stop,
-      gad.worrying_too_much_about_different_things_retro = gad.worrying_too_much_about_different_things,
-      gad.trouble_relaxing_retro = gad.trouble_relaxing,
-      gad.sit_restless_hard_retro = gad.sit_restless_hard,
-      gad.becoming_easily_annoyed_or_irritable_retro = gad.becoming_easily_annoyed_or_irritable,
-      gad.awful_feeling_afraid_happen_retro = gad.feeling_afraid_awful_happen, #Different from GLAD
-      gad.feeling_nervous_anxious_or_on_edge_base = gad.feeling_nervous_anxious_or_on_edge.1,
-      gad.control_worrying_stop_base = gad.control_worrying_stop.1,
-      gad.worrying_too_much_about_different_things_base = gad.worrying_too_much_about_different_things.1,
-      gad.trouble_relaxing_base = gad.trouble_relaxing.1,
-      gad.sit_restless_hard_base = gad.sit_restless_hard.1,
-      gad.becoming_easily_annoyed_or_irritable_base = gad.becoming_easily_annoyed_or_irritable.1,
-      gad.awful_feeling_afraid_happen_base = gad.feeling_afraid_awful_happen.1 #Different from GLAD
-    ) %>%
-    add_numeric(., exclude = exclude_cols_coping_nbr) %>%
-    mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
-    mutate_if(is.numeric, ~na_if(., -99)) %>%
-    mutate_if(is.numeric, ~na_if(., -77)) %>%
-    mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
-    mutate_if(is.factor, ~na_if(., "Don't know")) %>%
-    mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
-    mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
-    mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
-    mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
-    mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
-    mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
-
-  # Inspect dimensions
-  dim(coping.nbr.gad.raw.id)
-  # Inspect colnames
-  colnames(coping.nbr.gad.raw.id)
-  #Differences
-  dim(coping.nbr.gad.raw)[1]-dim(coping.nbr.gad.raw.id)[1]
-}
-```
-
-```{r coping nbr gad copy}
-if(NBR == TRUE) {
-  coping.gad.raw.id <- coping.nbr.gad.raw.id
-}
-```
-
-## RAMP
-```{r coping ramp gad cols}
-if(RAMP == TRUE) {
-  ramp.gad.raw <- readRDS(file = paste0(data.raw_path,"/ramp/gad_ramp.rds"))
-  dim(ramp.gad.raw)
-  colnames(ramp.gad.raw)
-}
-```
-
-```{r coping ramp gad summary}
-if(RAMP == TRUE) {
-  summarytools::dfSummary(
-    ramp.gad.raw,
-    graph.col = F,
-    valid.col = F,
-    labels.col = F
-  )
-}
-```
-
-```{r coping ramp gad cleaning}
-if(RAMP == TRUE) {
-  exclude_cols_ramp <- c(
-    "Sample",
-    "ID",
-    "startDate.ramp"
-  )
-
-  ramp.gad.raw.id <- ramp.gad.raw %>%
-    drop_na(`Login ID`) %>% # Drop NAs
-    distinct(`Login ID`, .keep_all = TRUE) %>% # Remove duplicates based on ID
-    separate(`Login ID`, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
-    mutate(ID = as.numeric(ID)
-    ) %>% 
-    select(
-      Sample, # Sample
-      ID, # ID
-      startDate.ramp = startDate, # Rename startDate
-      gad.problems_made_difficult_care = gad.issues_made_carrying_daily, # Impairment
-      gad.pandemic_felt_feelings = gad.feelings_pandemic_felt, # Comparison to before the pandemic (retro)
-      gad.feeling_nervous_anxious_or_on_edge_retro = gad.feeling_nervous_anxious_or_on_edge.1, #retro and baseline coding are reversed for RAMP
-      gad.control_worrying_stop_retro = gad.control_worrying_stop.1, #.1 = retro
-      gad.worrying_too_much_about_different_things_retro = gad.worrying_too_much_about_different_things.1,
-      gad.trouble_relaxing_retro = gad.trouble_relaxing.1,
-      gad.sit_restless_hard_retro = gad.sit_hard_restless.1,
-      gad.becoming_easily_annoyed_or_irritable_retro = gad.becoming_easily_annoyed_or_irritable.1,
-      gad.awful_feeling_afraid_happen_retro = gad.awful_feeling_afraid_happen.1,
-      gad.feeling_nervous_anxious_or_on_edge_base = gad.feeling_nervous_anxious_or_on_edge,
-      gad.control_worrying_stop_base = gad.control_worrying_stop,
-      gad.worrying_too_much_about_different_things_base = gad.worrying_too_much_about_different_things,
-      gad.trouble_relaxing_base = gad.trouble_relaxing,
-      gad.sit_restless_hard_base = gad.sit_hard_restless,
-      gad.becoming_easily_annoyed_or_irritable_base = gad.becoming_easily_annoyed_or_irritable,
-      gad.awful_feeling_afraid_happen_base = gad.awful_feeling_afraid_happen
-    ) %>%
-    add_numeric(., exclude = exclude_cols_coping_ramp) %>%
-    mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
-    mutate_if(is.numeric, ~na_if(., -99)) %>%
-    mutate_if(is.numeric, ~na_if(., -77)) %>%
-    mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
-    mutate_if(is.factor, ~na_if(., "Don't know")) %>%
-    mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
-    mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
-    mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
-    mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
-    mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
-    mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
-
-  # Inspect dimensions
-  dim(ramp.gad.raw.id)
-  # Inspect colnames
-  colnames(ramp.gad.raw.id)
-  #Differences
-  dim(ramp.gad.raw)[1]-dim(ramp.gad.raw.id)[1]
-}
-```
-
-```{r coping ramp gad copy}
-if(RAMP == TRUE) {
-  coping.gad.raw.id <- ramp.gad.raw.id
-}
-```
-
-## Sum scores
-Calculate sum score for GAD-7 retrospective
-```{r coping gad sum score retro}
-# Create vector with scoring key: If the item is reversed coded use -1. 
-# There needs to be the correct number of values for each item in the questionnaire. 
-gad.items_key_retro <- c(1,1,1,1,1,1,1)
-
-# Create vector with items that are included in total score
-gad.items_retro <- c(
-  "gad.feeling_nervous_anxious_or_on_edge_retro_numeric",
-  "gad.control_worrying_stop_retro_numeric",
-  "gad.worrying_too_much_about_different_things_retro_numeric",
-  "gad.trouble_relaxing_retro_numeric",
-  "gad.sit_restless_hard_retro_numeric",
-  "gad.becoming_easily_annoyed_or_irritable_retro_numeric",
-  "gad.awful_feeling_afraid_happen_retro_numeric"
-  )
-
-# Calulate total score
-gad.scored_items_retro <- scoreItems(keys = gad.items_key_retro,
-                                        items = coping.gad.raw.id[gad.items_retro],
-                                        totals = TRUE, 
-                                        missing = TRUE, 
-                                        impute = 'none', 
-                                        min = 0, 
-                                        max = 3)
-# Add in column to tibble
-coping.gad.raw.id$gad.sum_score_retro_raw <- gad.scored_items_retro$scores
-
-# Look at values
-coping.gad.raw.id %>%
-  descr(gad.sum_score_retro_raw,
-        stats = "common"
+glad/edgi data frame list
+```{r glad/edgi data frame list}
+dfs.list <- list(
+  glad,
+  edgi,
+  nbr,
+  ramp
 )
@@
 
-Calculate sum score for GAD-7 baseline
-```{r coping gad sum score base}
-# Create vector with scoring key: If the item is reversed coded use -1. 
-# There needs to be the correct number of values for each item in the questionnaire. 
-gad.items_key_base <- c(1,1,1,1,1,1,1)
-
-# Create vector with items that are included in total score
-gad.items_base <- c(
-  "gad.feeling_nervous_anxious_or_on_edge_base_numeric",
-  "gad.control_worrying_stop_base_numeric",
-  "gad.worrying_too_much_about_different_things_base_numeric",
-  "gad.trouble_relaxing_base_numeric",
-  "gad.sit_restless_hard_base_numeric",
-  "gad.becoming_easily_annoyed_or_irritable_base_numeric",
-  "gad.awful_feeling_afraid_happen_base_numeric"
-  )
-
-# Calulate total score
-gad.scored_items_base <- scoreItems(keys = gad.items_key_base,
-                                        items = coping.gad.raw.id[gad.items_base],
-                                        totals = TRUE, 
-                                        missing = TRUE, 
-                                        impute = 'none', 
-                                        min = 0, 
-                                        max = 3)
-# Add in column to tibble
-coping.gad.raw.id$gad.sum_score_base_raw <- gad.scored_items_base$scores
-
-# Look at values
-coping.gad.raw.id %>%
-  descr(gad.sum_score_base_raw,
-        stats = "common"
-        )
-```
-
-## Missingness
-
-baseline
-```{r coping gad baseline missingness}
-coping.gad.raw.id <- coping.gad.raw.id %>%
-  mutate(
-    na_per_person_gad_base =         # variable for NA per person
-      rowSums(                       
-        is.na(.[gad.items_base])
-      )
-  )
-
-coping.gad.raw.id %>%
-  freq(na_per_person_gad_base, cumul = F) #have a look at the frequency
-```
-
-```{r coping gad retrospective missingness}
-coping.gad.raw.id <- coping.gad.raw.id %>%
-  mutate(
-    na_per_person_gad_retro =         # variable for NA per person
-      rowSums(
-        is.na(.[gad.items_retro])
-      )
-  )
-
-coping.gad.raw.id %>%
-  freq(na_per_person_gad_retro, cumul = F) #have a look at the frequency
-```
-
-```{r coping gad base sum score if missing items set to NA}
-coping.gad.raw.id <- coping.gad.raw.id %>%
-  mutate(
-    gad.sum_score_base =
-      if_else(condition = na_per_person_gad_base > 0,
-              true = NA_real_,
-              false = gad.sum_score_base_raw,
-              missing = NA_real_
-      )
-  )
-
-coping.gad.raw.id %>%
-  descr(gad.sum_score_base_raw, stats = "common")
-
-coping.gad.raw.id %>%
-  descr(gad.sum_score_base, stats = "common")
-```
-
-```{r coping gad retro sum score if missing items set to NA}
-coping.gad.raw.id <- coping.gad.raw.id %>%
-  mutate(
-    gad.sum_score_retro =
-      if_else(condition = na_per_person_gad_retro > 0,
-              true = NA_real_,
-              false = gad.sum_score_retro_raw,
-              missing = NA_real_
-      )
-  )
-
-coping.gad.raw.id %>%
-  descr(gad.sum_score_retro_raw, stats = "common")
-
-coping.gad.raw.id %>%
-  descr(gad.sum_score_retro, stats = "common")
-```
-
-## Inspection
-```{r coping glad gad head}
-head(coping.gad.raw.id)
-```
-
-```{r coping glad gad summary 2}
-summarytools::dfSummary(
-  coping.gad.raw.id,
-  graph.col = F,
-  valid.col = F,
-  labels.col = F)
-```
-
-# COPING: PCL-6
-
-## GLAD
-```{r coping glad pcl cols}
-if(GLAD == TRUE) {
-coping.glad.pcl.raw <- readRDS(file = paste0(data.raw_path,"/glad/pcl_coping_glad.rds"))
-dim(coping.glad.pcl.raw)
-colnames(coping.glad.pcl.raw)
-}
-```
-
-```{r coping glad pcl summary labels}
-if(GLAD == TRUE) {
-summarytools::dfSummary(
-  coping.glad.pcl.raw,
-  graph.col = F,
-  valid.col = F,
-  labels.col = F
-)
-}
-```
-
-Note: Retro for the PCL does not mean retrospective
-
-```{r coping glad pcl cleaning}
-if(GLAD == TRUE) {
-coping.glad.pcl.raw.id <- coping.glad.pcl.raw %>%
-  drop_na(externalDataReference) %>% # Drop NAs
-  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
-  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
-  mutate(ID = as.numeric(ID)) %>%
-  select(
-    Sample, # Sample
-    ID, # ID
-    pcl.stressful_experience_repeated_images_base = pcl.stressful_experience_repeated_images,
-    pcl.stressful_experience_upset_reminded_base = pcl.stressful_experience_upset_reminded, # differ to GLAD prepan
-    pcl.stressful_situation_avoiding_activities_base = pcl.avoiding_activities_stressful_experience, # differ to GLAD prepan
-    pcl.cut_people_feeling_distant_base = pcl.cut_people_feeling_distant,
-    pcl.feeling_irritable_or_having_angry_outbursts_base = pcl.feeling_irritable_or_having_angry_outbursts,
-    pcl.difficulty_concentrating_base = pcl.difficulty_concentrating,
-    pcl.stressful_experience_repeated_images_retro = pcl.stressful_experience_repeated_images.1,
-    pcl.stressful_experience_upset_reminded_retro = pcl.stressful_experience_upset_reminded.1,
-    pcl.stressful_situation_avoiding_activities_retro = pcl.avoiding_activities_stressful_experience.1,
-    pcl.cut_people_feeling_distant_retro = pcl.cut_people_feeling_distant.1,
-    pcl.feeling_irritable_or_having_angry_outbursts_retro = pcl.feeling_irritable_or_having_angry_outbursts.1,
-    pcl.difficulty_concentrating_retro = pcl.difficulty_concentrating.1
-  ) %>%
-  add_numeric(., exclude = exclude_cols) %>%
-  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
-  mutate_if(is.numeric, ~na_if(., -99)) %>%
-  mutate_if(is.numeric, ~na_if(., -77)) %>%
-  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
-  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
-
-# Inspect dimensions
-dim(coping.glad.pcl.raw.id)
-# Inspect colnames
-colnames(coping.glad.pcl.raw.id)
-#Differences
-dim(coping.glad.pcl.raw)[1]-dim(coping.glad.pcl.raw.id)[1]
-}
-```
-
-```{r coping glad pcl copy}
-if(GLAD == TRUE) {
-  coping.pcl.raw.id <- coping.glad.pcl.raw.id
-}
-```
-
-## EDGI
-```{r coping edgi pcl cols}
-if(EDGI == TRUE) {
-coping.edgi.pcl.raw <- readRDS(file = paste0(data.raw_path,"/edgi/pcl_coping_edgi.rds"))
-dim(coping.edgi.pcl.raw)
-colnames(coping.edgi.pcl.raw)
-}
-```
-
-```{r coping edgi pcl summary labels}
-if(EDGI == TRUE) {
-summarytools::dfSummary(
-  coping.edgi.pcl.raw,
-  graph.col = F,
-  valid.col = F,
-  labels.col = F
-)
-}
-```
-
-Note: Retro for the PCL does not mean retrospective
-
-```{r coping edgi pcl cleaning}
-if(EDGI == TRUE) {
-coping.edgi.pcl.raw.id <- coping.edgi.pcl.raw %>%
-  drop_na(externalDataReference) %>% # Drop NAs
-  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
-  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
-  mutate(ID = as.numeric(ID)) %>%
-  select(
-    Sample, # Sample
-    ID, # ID
-    pcl.stressful_experience_repeated_images_base = pcl.repeated_images_thoughts_past, # different pcl.stressful_experience_repeated_images,
-    pcl.stressful_experience_upset_reminded_base = pcl.upset_reminded_past_feeling, # differ to EDGI prepan
-    pcl.stressful_situation_avoiding_activities_base = pcl.avoiding_activities_reminded_situations, # differ to EDGI prepan
-    pcl.cut_people_feeling_distant_base = pcl.cut_people_feeling_distant,
-    pcl.feeling_irritable_or_having_angry_outbursts_base = pcl.feeling_irritable_or_having_angry_outbursts,
-    pcl.difficulty_concentrating_base = pcl.difficulty_concentrating,
-    pcl.stressful_experience_repeated_images_retro = pcl.repeated_images_thoughts_past.1,
-    pcl.stressful_experience_upset_reminded_retro = pcl.upset_reminded_past_feeling.1,
-    pcl.stressful_situation_avoiding_activities_retro = pcl.avoiding_activities_reminded_situations.1,
-    pcl.cut_people_feeling_distant_retro = pcl.cut_people_feeling_distant.1,
-    pcl.feeling_irritable_or_having_angry_outbursts_retro = pcl.feeling_irritable_or_having_angry_outbursts.1,
-    pcl.difficulty_concentrating_retro = pcl.difficulty_concentrating.1
-  ) %>%
-  add_numeric(., exclude = exclude_cols) %>%
-  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
-  mutate_if(is.numeric, ~na_if(., -99)) %>%
-  mutate_if(is.numeric, ~na_if(., -77)) %>%
-  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
-  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
-
-# Inspect dimensions
-dim(coping.edgi.pcl.raw.id)
-# Inspect colnames
-colnames(coping.edgi.pcl.raw.id)
-#Differences
-dim(coping.edgi.pcl.raw)[1]-dim(coping.edgi.pcl.raw.id)[1]
-}
-```
-
-```{r coping edgi pcl copy}
-if(EDGI == TRUE) {
-  coping.pcl.raw.id <- coping.edgi.pcl.raw.id
-}
-```
-
-## NBR
-```{r coping nbr pcl cols}
-if(NBR == TRUE) {
-coping.nbr.pcl.raw <- readRDS(file = paste0(data.raw_path,"/nbr/pcl_coping_nbr.rds"))
-dim(coping.nbr.pcl.raw)
-colnames(coping.nbr.pcl.raw)
-}
-```
-
-```{r coping nbr pcl summary labels}
-if(NBR == TRUE) {
-summarytools::dfSummary(
-  coping.nbr.pcl.raw,
-  graph.col = F,
-  valid.col = F,
-  labels.col = F
-)
-}
-```
-
-Note: Retro for the PCL does not mean retrospective
-
-```{r coping nbr pcl cleaning}
-if(NBR == TRUE) {
-coping.nbr.pcl.raw.id <- coping.nbr.pcl.raw %>%
-  drop_na(subjectid) %>% # Drop NAs
-  distinct(subjectid, .keep_all = TRUE) %>% # Remove duplicates based on ID
-  separate(subjectid, into = c("Sample", "ID.intm"), sep = 6) %>% # Split ID in Sample and Number
-  separate(ID.intm, into = "ID", sep = 7) %>%
-  mutate(ID = as.numeric(ID)) %>%
-  select(
-    Sample, # Sample
-    ID, # ID
-    pcl.stressful_experience_repeated_images_base = pcl.stressful_experience_repeated_images,
-    pcl.stressful_experience_upset_reminded_base = pcl.stressful_experience_upset_reminded, # differ to NBR prepan
-    pcl.stressful_situation_avoiding_activities_base = pcl.avoiding_activities_stressful_experience, # differ to NBR prepan
-    pcl.cut_people_feeling_distant_base = pcl.cut_people_feeling_distant,
-    pcl.feeling_irritable_or_having_angry_outbursts_base = pcl.feeling_irritable_or_having_angry_outbursts,
-    pcl.difficulty_concentrating_base = pcl.difficulty_concentrating,
-    pcl.stressful_experience_repeated_images_retro = pcl.stressful_experience_repeated_images.1,
-    pcl.stressful_experience_upset_reminded_retro = pcl.stressful_experience_upset_reminded.1,
-    pcl.stressful_situation_avoiding_activities_retro = pcl.avoiding_activities_stressful_experience.1,
-    pcl.cut_people_feeling_distant_retro = pcl.cut_people_feeling_distant.1,
-    pcl.feeling_irritable_or_having_angry_outbursts_retro = pcl.feeling_irritable_or_having_angry_outbursts.1,
-    pcl.difficulty_concentrating_retro = pcl.difficulty_concentrating.1
-  ) %>%
-  add_numeric(., exclude = exclude_cols) %>%
-  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
-  mutate_if(is.numeric, ~na_if(., -99)) %>%
-  mutate_if(is.numeric, ~na_if(., -77)) %>%
-  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
-  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
-
-# Inspect dimensions
-dim(coping.nbr.pcl.raw.id)
-# Inspect colnames
-colnames(coping.nbr.pcl.raw.id)
-#Differences
-dim(coping.nbr.pcl.raw)[1]-dim(coping.nbr.pcl.raw.id)[1]
-}
-```
-
-```{r coping nbr pcl copy}
-if(NBR == TRUE) {
-  coping.pcl.raw.id <- coping.nbr.pcl.raw.id
-}
-```
-
-## RAMP - NOT YET HAVE THE RAMP PCL DATA READY
-```{r coping ramp pcl cols}
-# if(RAMP == TRUE) {
-# coping.ramp.pcl.raw <- readRDS(file = paste0(data.raw_path,"/ramp/pcl_ramp.rds"))
-# dim(coping.ramp.pcl.raw)
-# colnames(coping.ramp.pcl.raw)
-# }
-```
-
-```{r coping ramp pcl summary labels}
-# if(RAMP == TRUE) {
-# summarytools::dfSummary(
-#   coping.ramp.pcl.raw,
-#   graph.col = F,
-#   valid.col = F,
-#   labels.col = F
-# )
-# }
-```
-
-Note: Retro for the PCL does not mean retrospective
-
-```{r coping ramp pcl cleaning}
-# if(RAMP == TRUE) {
-# coping.ramp.pcl.raw.id <- coping.ramp.pcl.raw %>%
-#   drop_na(externalDataReference) %>% # Drop NAs
-#   distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
-#   separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
-#   mutate(ID = as.numeric(ID)) %>%
-#   select(
-#     Sample, # Sample
-#     ID, # ID
-#     pcl.stressful_experience_repeated_images_base = pcl.stressful_experience_repeated_images,
-#     pcl.stressful_experience_upset_reminded_base = pcl.stressful_experience_upset_reminded, # differ to RAMP prepan
-#     pcl.stressful_situation_avoiding_activities_base = pcl.avoiding_activities_stressful_experience, # differ to RAMP prepan
-#     pcl.cut_people_feeling_distant_base = pcl.cut_people_feeling_distant,
-#     pcl.feeling_irritable_or_having_angry_outbursts_base = pcl.feeling_irritable_or_having_angry_outbursts,
-#     pcl.difficulty_concentrating_base = pcl.difficulty_concentrating,
-#     pcl.stressful_experience_repeated_images_retro = pcl.stressful_experience_repeated_images.1,
-#     pcl.stressful_experience_upset_reminded_retro = pcl.stressful_experience_upset_reminded.1,
-#     pcl.stressful_situation_avoiding_activities_retro = pcl.avoiding_activities_stressful_experience.1,
-#     pcl.cut_people_feeling_distant_retro = pcl.cut_people_feeling_distant.1,
-#     pcl.feeling_irritable_or_having_angry_outbursts_retro = pcl.feeling_irritable_or_having_angry_outbursts.1,
-#     pcl.difficulty_concentrating_retro = pcl.difficulty_concentrating.1
-#   ) %>%
-#   add_numeric(., exclude = exclude_cols) %>%
-#   mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
-#   mutate_if(is.numeric, ~na_if(., -99)) %>%
-#   mutate_if(is.numeric, ~na_if(., -77)) %>%
-#   mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
-#   mutate_if(is.factor, ~na_if(., "Don't know")) %>%
-#   mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
-#   mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
-#   mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
-#   mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
-#   mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
-#   mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
-# 
-# # Inspect dimensions
-# dim(coping.ramp.pcl.raw.id)
-# # Inspect colnames
-# colnames(coping.ramp.pcl.raw.id)
-# #Differences
-# dim(coping.ramp.pcl.raw)[1]-dim(coping.ramp.pcl.raw.id)[1]
-# }
-```
-
-```{r coping ramp pcl copy}
-# if(RAMP == TRUE) {
-#   coping.pcl.raw.id <- coping.ramp.pcl.raw.id
-# }
-```
-
-## Sum scores
-Calculate sum score for PCL-6 retro
-```{r coping pcl sum score retro}
-# Create vector with scoring key: If the item is reversed coded use -1. 
-# There needs to be the correct number of values for each item in the questionnaire. 
-pcl.items_key_retro <- c(1,1,1,1,1,1)
-
-# Create vector with items that are included in total score
-pcl.items_retro <- c(
-  "pcl.stressful_experience_repeated_images_retro_numeric",
-  "pcl.stressful_experience_upset_reminded_retro_numeric",
-  "pcl.stressful_situation_avoiding_activities_retro_numeric",
-  "pcl.cut_people_feeling_distant_retro_numeric",
-  "pcl.feeling_irritable_or_having_angry_outbursts_retro_numeric",
-  "pcl.difficulty_concentrating_retro_numeric"
-)
-
-# Calulate total score
-pcl.scored_items_retro <- scoreItems(keys = pcl.items_key_retro,
-                                     items = coping.pcl.raw.id[pcl.items_retro],
-                                     totals = TRUE, 
-                                     missing = TRUE, 
-                                     impute = 'none', 
-                                     min = 0, 
-                                     max = 1)
-# Add in column to tibble
-coping.pcl.raw.id$pcl.sum_score_retro_raw <- pcl.scored_items_retro$scores
-
-# Look at values
-coping.pcl.raw.id %>%
-  descr(pcl.sum_score_retro_raw,
-        stats = "common"
-  )
-```
-
-Calculate sum score for PCL-6 base
-The sum scores here will not be accurate if we are using complete cases. Only use sum scores here for complete cases, otherwise the minimum will be 0 where it should be 6. 
-```{r coping pcl sum score base}
-# Create vector with scoring key: If the item is reversed coded use -1. 
-# There needs to be the correct number of values for each item in the questionnaire. 
-pcl.items_key_base <- c(1,1,1,1,1,1)
-
-# Create vector with items that are included in total score
-pcl.items_base <- c(
-  "pcl.stressful_experience_repeated_images_base_numeric",
-  "pcl.stressful_experience_upset_reminded_base_numeric",
-  "pcl.stressful_situation_avoiding_activities_base_numeric",
-  "pcl.cut_people_feeling_distant_base_numeric",
-  "pcl.feeling_irritable_or_having_angry_outbursts_base_numeric",
-  "pcl.difficulty_concentrating_base_numeric"
-)
-
-# Calulate total score
-pcl.scored_items_base <- scoreItems(keys = pcl.items_key_base,
-                                    items = coping.pcl.raw.id[pcl.items_base],
-                                    totals = TRUE, 
-                                    missing = TRUE, 
-                                    impute = "none", 
-                                    min = 1, 
-                                    max = 5)
-# Add in column to tibble
-coping.pcl.raw.id$pcl.sum_score_base_raw <- pcl.scored_items_base$scores
-
-# Look at values
-coping.pcl.raw.id %>%
-  descr(pcl.sum_score_base_raw,
-        stats = "common"
-  )
-```
-
-## Missingness
-PCL missingness (NAs per person)
-
-baseline
-```{r coping pcl baseline missingness}
-coping.pcl.raw.id <- coping.pcl.raw.id %>%
-  mutate(
-    na_per_person_pcl_base =         # variable for NA per person
-      rowSums(                       
-        is.na(.[pcl.items_base])
-      )
-  )
-
-coping.pcl.raw.id %>%
-  freq(na_per_person_pcl_base, cumul = F) #have a look at the frequency
-```
-
-retrospective
-```{r coping pcl retrospective missingness}
-coping.pcl.raw.id <- coping.pcl.raw.id %>%
-  mutate(
-    na_per_person_pcl_retro =         # variable for NA per person
-      rowSums(
-        is.na(.[pcl.items_retro])
-      )
-  )
-
-coping.pcl.raw.id %>%
-  freq(na_per_person_pcl_retro, cumul = F) #have a look at the frequency
-```
-
-```{r coping pcl base sum score if missing items set to NA}
-coping.pcl.raw.id <- coping.pcl.raw.id %>%
-  mutate(
-    pcl.sum_score_base =
-      if_else(condition = na_per_person_pcl_base > 0,
-              true = NA_real_,
-              false = pcl.sum_score_base_raw,
-              missing = NA_real_
-      )
-  )
-
-coping.pcl.raw.id %>%
-  descr(pcl.sum_score_base_raw, stats = "common")
-
-coping.pcl.raw.id %>%
-  descr(pcl.sum_score_base, stats = "common")
-```
-
-```{r coping pcl retro sum score if missing items set to NA}
-coping.pcl.raw.id <- coping.pcl.raw.id %>%
-  mutate(
-    pcl.sum_score_retro =
-      if_else(condition = na_per_person_pcl_retro > 0,
-              true = NA_real_,
-              false = pcl.sum_score_retro_raw,
-              missing = NA_real_
-      )
-  )
-
-coping.pcl.raw.id %>%
-  descr(pcl.sum_score_retro_raw, stats = "common")
-
-coping.pcl.raw.id %>%
-  descr(pcl.sum_score_retro, stats = "common")
-```
-
-## Inspection
-```{r coping glad pcl head}
-head(coping.pcl.raw.id)
-```
-
-```{r coping glad pcl summary}
-summarytools::dfSummary(
-  coping.pcl.raw.id,
-  graph.col = F,
-  valid.col = F,
-  labels.col = F)
-```
-
-# COPING: PHQ
-
-## GLAD
-```{r coping glad phq cols}
-if(GLAD == TRUE) {
-coping.glad.phq.raw <- readRDS(file = paste0(data.raw_path, "/glad/phq_coping_glad.rds"))
-dim(coping.glad.phq.raw)
-colnames(coping.glad.phq.raw)
-}
-```
-
-```{r coping glad phq summary labels}
-if(GLAD == TRUE) {
-summarytools::dfSummary(
-  coping.glad.phq.raw,
-  graph.col = F,
-  valid.col = F
-  #labels.col = F
-)
-}
-```
-
-Will need to double check these namings once we have the new cleaned data -- KT. 
-```{r coping glad phq cleaning}
-if(GLAD == TRUE) {
-coping.glad.phq.raw.id <- coping.glad.phq.raw %>%
-  drop_na(externalDataReference) %>% # Drop NAs
-  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
-  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
-  mutate(ID = as.numeric(ID)
-         ) %>%
-  select(
-    Sample, # Sample
-    ID, # ID
-    phq.problems_made_difficult_care,
-    phq.pandemic_felt_feelings,
-    phq.little_interest_or_pleasure_in_doing_things_retro = phq.little_interest_or_pleasure_in_doing_things,
-    phq.feeling_down_depressed_or_hopeless_retro = phq.feeling_down_depressed_or_hopeless,
-    phq.staying_asleep_sleeping_trouble_retro = phq.staying_asleep_sleeping_trouble,
-    phq.feeling_tired_or_having_little_energy_retro = phq.feeling_tired_or_having_little_energy,
-    phq.poor_appetite_or_overeating_retro = phq.poor_appetite_or_overeating,
-    phq.feeling_bad_failure_family_retro = phq.feeling_bad_failure_family,
-    phq.trouble_concentrating_reading_newspaper_retro = phq.trouble_concentrating_newspaper_reading, # differ GLAD prepandemic
-    phq.moving_fidgety_noticed_opposite_retro = phq.moving_fidgety_opposite_slowly, # differ GLAD prepandemic
-    phq.dead_hurting_thoughts_retro = phq.dead_hurting_thoughts,
-    phq.little_interest_or_pleasure_in_doing_things_base = phq.little_interest_or_pleasure_in_doing_things.1,
-    phq.feeling_down_depressed_or_hopeless_base = phq.feeling_down_depressed_or_hopeless.1,
-    phq.staying_asleep_sleeping_trouble_base = phq.staying_asleep_sleeping_trouble.1,
-    phq.feeling_tired_or_having_little_energy_base = phq.feeling_tired_or_having_little_energy.1,
-    phq.poor_appetite_or_overeating_base = phq.poor_appetite_or_overeating.1,
-    phq.feeling_bad_failure_family_base = phq.feeling_bad_failure_family.1,
-    phq.trouble_concentrating_reading_newspaper_base = phq.trouble_concentrating_newspaper_reading.1, # differ GLAD prepandemic
-    phq.moving_fidgety_noticed_opposite_base = phq.moving_fidgety_opposite_slowly.1, # differ GLAD prepandemic
-    phq.dead_hurting_thoughts_base = phq.dead_hurting_thoughts.1
-  ) %>%
-  add_numeric(., exclude = exclude_cols) %>%
-  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
-  mutate_if(is.numeric, ~na_if(., -99)) %>%
-  mutate_if(is.numeric, ~na_if(., -77)) %>%
-  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
-  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
-
-# Inspect dimensions
-dim(coping.glad.phq.raw.id)
-# Inspect colnames
-colnames(coping.glad.phq.raw.id)
-#Differences
-dim(coping.glad.phq.raw)[1]-dim(coping.glad.phq.raw.id)[1]
-}
-```
-
-```{r coping glad gad copy}
-if(GLAD == TRUE) {
-  coping.phq.raw.id <- coping.glad.phq.raw.id
-}
-```
-
-## EDGI
-```{r coping edgi phq cols}
-if(EDGI == TRUE) {
-coping.edgi.phq.raw <- readRDS(file = paste0(data.raw_path, "/edgi/phq_coping_edgi.rds"))
-dim(coping.edgi.phq.raw)
-colnames(coping.edgi.phq.raw)
-}
-```
-
-```{r coping edgi phq summary labels}
-if(EDGI == TRUE) {
-summarytools::dfSummary(
-  coping.edgi.phq.raw,
-  graph.col = F,
-  valid.col = F
-  #labels.col = F
-)
-}
-```
-
-```{r coping edgi phq cleaning}
-if(EDGI == TRUE) {
-coping.edgi.phq.raw.id <- coping.edgi.phq.raw %>%
-  drop_na(externalDataReference) %>% # Drop NAs
-  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
-  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
-  mutate(ID = as.numeric(ID)
-  ) %>%
-  select(
-    Sample, # Sample
-    ID, # ID
-    phq.problems_made_difficult_care = phq.care_difficult_home_things,
-    phq.pandemic_felt_feelings = phq.pandemic_feelings_felt,
-    phq.little_interest_or_pleasure_in_doing_things_retro = phq.little_interest_or_pleasure_in_doing_things,
-    phq.feeling_down_depressed_or_hopeless_retro = phq.feeling_down_depressed_or_hopeless,
-    phq.staying_asleep_sleeping_trouble_retro = phq.staying_asleep_sleeping_trouble,
-    phq.feeling_tired_or_having_little_energy_retro = phq.feeling_tired_or_having_little_energy,
-    phq.poor_appetite_or_overeating_retro = phq.poor_appetite_or_overeating,
-    phq.feeling_bad_failure_family_retro = phq.family_feeling_bad_failure, # differ GLAD phq.feeling_bad_failure_family,
-    phq.trouble_concentrating_reading_newspaper_retro = phq.trouble_concentrating_newspaper_reading, # differ EDGI prepandemic
-    phq.moving_fidgety_noticed_opposite_retro = phq.moving_fidgety_opposite_slowly, # differ EDGI prepandemic
-    phq.dead_hurting_thoughts_retro = phq.dead_hurting_thoughts,
-    phq.little_interest_or_pleasure_in_doing_things_base = phq.little_interest_or_pleasure_in_doing_things.1,
-    phq.feeling_down_depressed_or_hopeless_base = phq.feeling_down_depressed_or_hopeless.1,
-    phq.staying_asleep_sleeping_trouble_base = phq.staying_asleep_sleeping_trouble.1,
-    phq.feeling_tired_or_having_little_energy_base = phq.feeling_tired_or_having_little_energy.1,
-    phq.poor_appetite_or_overeating_base = phq.poor_appetite_or_overeating.1,
-    phq.feeling_bad_failure_family_base = phq.family_feeling_bad_failure.1, # differ GLAD
-    phq.trouble_concentrating_reading_newspaper_base = phq.trouble_concentrating_newspaper_reading.1, # differ EDGI prepandemic
-    phq.moving_fidgety_noticed_opposite_base = phq.moving_fidgety_opposite_slowly.1, # differ EDGI prepandemic
-    phq.dead_hurting_thoughts_base = phq.dead_hurting_thoughts.1
-  ) %>%
-  add_numeric(., exclude = exclude_cols) %>%
-  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
-  mutate_if(is.numeric, ~na_if(., -99)) %>%
-  mutate_if(is.numeric, ~na_if(., -77)) %>%
-  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
-  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
-
-# Inspect dimensions
-dim(coping.edgi.phq.raw.id)
-# Inspect colnames
-colnames(coping.edgi.phq.raw.id)
-#Differences
-dim(coping.edgi.phq.raw)[1]-dim(coping.edgi.phq.raw.id)[1]
-}
-```
-
-```{r coping edgi gad copy}
-if(EDGI == TRUE) {
-  coping.phq.raw.id <- coping.edgi.phq.raw.id
-}
-```
-
-## NBR
-```{r coping nbr phq cols}
-if(NBR == TRUE) {
-coping.nbr.phq.raw <- readRDS(file = paste0(data.raw_path, "/nbr/phq_coping_nbr.rds"))
-dim(coping.nbr.phq.raw)
-colnames(coping.nbr.phq.raw)
-}
-```
-
-```{r coping nbr phq summary labels}
-if(NBR == TRUE) {
-summarytools::dfSummary(
-  coping.nbr.phq.raw,
-  graph.col = F,
-  valid.col = F
-  #labels.col = F
-)
-}
-```
-
-Will need to double check these namings once we have the new cleaned data -- KT. 
-```{r coping nbr phq cleaning}
-if(NBR == TRUE) {
-coping.nbr.phq.raw.id <- coping.nbr.phq.raw %>%
-  drop_na(subjectid) %>% # Drop NAs
-  distinct(subjectid, .keep_all = TRUE) %>% # Remove duplicates based on ID
-  separate(subjectid, into = c("Sample", "ID.intm"), sep = 6) %>% # Split ID in Sample and Number
-  separate(ID.intm, into = "ID", sep = 7) %>%
-  mutate(ID = as.numeric(ID)) %>%
-  select(
-    Sample, # Sample
-    ID, # ID
-    phq.problems_made_difficult_care = phq.problems_made_care_difficult,
-    phq.pandemic_felt_feelings,
-    phq.little_interest_or_pleasure_in_doing_things_retro = phq.little_interest_or_pleasure_in_doing_things,
-    phq.feeling_down_depressed_or_hopeless_retro = phq.feeling_down_depressed_or_hopeless,
-    phq.staying_asleep_sleeping_trouble_retro = phq.staying_asleep_sleeping_trouble,
-    phq.feeling_tired_or_having_little_energy_retro = phq.feeling_tired_or_having_little_energy,
-    phq.poor_appetite_or_overeating_retro = phq.poor_appetite_or_overeating,
-    phq.feeling_bad_failure_family_retro = phq.family_feeling_bad_failure,
-    phq.trouble_concentrating_reading_newspaper_retro = phq.trouble_concentrating_newspaper_reading, # differ NBR prepandemic
-    phq.moving_fidgety_noticed_opposite_retro = phq.moving_fidgety_opposite_slowly, # differ NBR prepandemic
-    phq.dead_hurting_thoughts_retro = phq.dead_hurting_thoughts,
-    phq.little_interest_or_pleasure_in_doing_things_base = phq.little_interest_or_pleasure_in_doing_things.1,
-    phq.feeling_down_depressed_or_hopeless_base = phq.feeling_down_depressed_or_hopeless.1,
-    phq.staying_asleep_sleeping_trouble_base = phq.staying_asleep_sleeping_trouble.1,
-    phq.feeling_tired_or_having_little_energy_base = phq.feeling_tired_or_having_little_energy.1,
-    phq.poor_appetite_or_overeating_base = phq.poor_appetite_or_overeating.1,
-    phq.feeling_bad_failure_family_base = phq.family_feeling_bad_failure.1,
-    phq.trouble_concentrating_reading_newspaper_base = phq.trouble_concentrating_newspaper_reading.1, # differ NBR prepandemic
-    phq.moving_fidgety_noticed_opposite_base = phq.moving_fidgety_opposite_slowly.1, # differ NBR prepandemic
-    phq.dead_hurting_thoughts_base = phq.dead_hurting_thoughts.1
-  ) %>%
-  add_numeric(., exclude = exclude_cols) %>%
-  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
-  mutate_if(is.numeric, ~na_if(., -99)) %>%
-  mutate_if(is.numeric, ~na_if(., -77)) %>%
-  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
-  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
-
-# Inspect dimensions
-dim(coping.nbr.phq.raw.id)
-# Inspect colnames
-colnames(coping.nbr.phq.raw.id)
-#Differences
-dim(coping.nbr.phq.raw)[1]-dim(coping.nbr.phq.raw.id)[1]
-}
-```
-
-```{r coping nbr gad copy}
-if(NBR == TRUE) {
-  coping.phq.raw.id <- coping.nbr.phq.raw.id
-}
-```
-
-## RAMP
-```{r coping ramp phq cols}
-if(RAMP == TRUE) {
-ramp.phq.raw <- readRDS(file = paste0(data.raw_path, "/ramp/phq_ramp.rds"))
-dim(ramp.phq.raw)
-colnames(ramp.phq.raw)
-}
-```
-
-```{r coping ramp phq summary labels}
-if(RAMP == TRUE) {
-summarytools::dfSummary(
-  ramp.phq.raw,
-  graph.col = F,
-  valid.col = F
-  #labels.col = F
-)
-}
-```
-
-Will need to double check these namings once we have the new cleaned data -- KT. 
-```{r coping ramp phq cleaning}
-if(RAMP == TRUE) {
-ramp.phq.raw.id <- ramp.phq.raw %>%
-  drop_na(`Login ID`) %>% # Drop NAs
-  distinct(`Login ID`, .keep_all = TRUE) %>% # Remove duplicates based on ID
-  separate(`Login ID`, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
-  mutate(ID = as.numeric(ID)
-  ) %>%
-  select(
-    Sample, # Sample
-    ID, # ID
-    phq.problems_made_difficult_care = phq.issues_made_carrying_daily, #impact
-    phq.pandemic_felt_feelings = phq.feelings_pandemic_felt, #before the pandemic question
-    phq.little_interest_or_pleasure_in_doing_things_retro = phq.little_interest_or_pleasure_in_doing_things.1,
-    phq.feeling_down_depressed_or_hopeless_retro = phq.feeling_down_depression_or_hopeless, #THIS IS CORRECT - strange naming in raw dataset
-    phq.staying_asleep_sleeping_trouble_retro = phq.staying_asleep_sleeping_trouble.1,
-    phq.feeling_tired_or_having_little_energy_retro = phq.feeling_tired_or_having_little_energy.1,
-    phq.poor_appetite_or_overeating_retro = phq.poor_appetite_or_overeating.1,
-    phq.feeling_bad_failure_family_retro = phq.failure_family_feeling_bad.1,
-    phq.trouble_concentrating_reading_newspaper_retro = phq.trouble_concentrating_newspaper_reading.1, 
-    phq.moving_fidgety_noticed_opposite_retro = phq.moving_fidgety_opposite_slowly.1, 
-    phq.dead_hurting_thoughts_retro = phq.dead_hurting_thoughts.1,
-    phq.little_interest_or_pleasure_in_doing_things_base = phq.little_interest_or_pleasure_in_doing_things,
-    phq.feeling_down_depressed_or_hopeless_base = phq.feeling_down_depressed_or_hopeless,
-    phq.staying_asleep_sleeping_trouble_base = phq.staying_asleep_sleeping_trouble,
-    phq.feeling_tired_or_having_little_energy_base = phq.feeling_tired_or_having_little_energy,
-    phq.poor_appetite_or_overeating_base = phq.poor_appetite_or_overeating,
-    phq.feeling_bad_failure_family_base = phq.failure_family_feeling_bad,
-    phq.trouble_concentrating_reading_newspaper_base = phq.trouble_concentrating_newspaper_reading, # differ RAMP prepandemic
-    phq.moving_fidgety_noticed_opposite_base = phq.moving_fidgety_opposite_slowly, # differ RAMP prepandemic
-    phq.dead_hurting_thoughts_base = phq.dead_hurting_thoughts
-  ) %>%
-  add_numeric(., exclude = exclude_cols) %>%
-  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
-  mutate_if(is.numeric, ~na_if(., -99)) %>%
-  mutate_if(is.numeric, ~na_if(., -77)) %>%
-  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
-  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
-
-# Inspect dimensions
-dim(ramp.phq.raw.id)
-# Inspect colnames
-colnames(ramp.phq.raw.id)
-#Differences
-dim(ramp.phq.raw)[1]-dim(ramp.phq.raw.id)[1]
-}
-```
-
-```{r coping ramp gad copy}
-if(RAMP == TRUE) {
-  coping.phq.raw.id <- ramp.phq.raw.id
-}
-```
-
-## Sum scores
-
-Calculate sum score for PHQ-9 retro
-```{r coping phq sum score retro}
-# Create vector with scoring key: If the item is reversed coded use -1. 
-# There needs to be the correct number of values for each item in the questionnaire. 
-phq.items_key_retro <- c(1,1,1,1,1,1,1,1,1)
-
-# Create vector with items that are included in total score
-phq.items_retro <- c(
-  "phq.little_interest_or_pleasure_in_doing_things_retro_numeric",
-"phq.feeling_down_depressed_or_hopeless_retro_numeric",
-"phq.staying_asleep_sleeping_trouble_retro_numeric",
-"phq.feeling_tired_or_having_little_energy_retro_numeric",
-"phq.poor_appetite_or_overeating_retro_numeric",
-"phq.feeling_bad_failure_family_retro_numeric",
-"phq.trouble_concentrating_reading_newspaper_retro_numeric",
-"phq.moving_fidgety_noticed_opposite_retro_numeric",
-"phq.dead_hurting_thoughts_retro_numeric"
-)
-
-# Calulate total score
-phq.scored_items_retro <- scoreItems(keys = phq.items_key_retro,
-                                     items = coping.phq.raw.id[phq.items_retro],
-                                     totals = TRUE, 
-                                     missing = TRUE, 
-                                     impute = 'none', 
-                                     min = 0, 
-                                     max = 3)
-# Add in column to tibble
-coping.phq.raw.id$phq.sum_score_retro_raw <- phq.scored_items_retro$scores
-
-# Look at values
-coping.phq.raw.id %>%
-  descr(phq.sum_score_retro_raw,
-        stats = "common"
-  )
-```
-
-Calculate sum score for PHQ-9 base
-```{r coping phq sum score base}
-# Create vector with scoring key: If the item is reversed coded use -1. 
-# There needs to be the correct number of values for each item in the questionnaire. 
-phq.items_key_base <- c(1,1,1,1,1,1,1,1,1)
-
-# Create vector with items that are included in total score
-phq.items_base <- c(
-  "phq.little_interest_or_pleasure_in_doing_things_base_numeric",
-"phq.feeling_down_depressed_or_hopeless_base_numeric",
-"phq.staying_asleep_sleeping_trouble_base_numeric",
-"phq.feeling_tired_or_having_little_energy_base_numeric",
-"phq.poor_appetite_or_overeating_base_numeric",
-"phq.feeling_bad_failure_family_base_numeric",
-"phq.trouble_concentrating_reading_newspaper_base_numeric",
-"phq.moving_fidgety_noticed_opposite_base_numeric",
-"phq.dead_hurting_thoughts_base_numeric"
-)
-
-# Calulate total score
-phq.scored_items_base <- scoreItems(keys = phq.items_key_base,
-                                    items = coping.phq.raw.id[phq.items_base],
-                                    totals = TRUE, 
-                                    missing = TRUE, 
-                                    impute = 'none', 
-                                    min = 0, 
-                                    max = 3)
-# Add in column to tibble
-coping.phq.raw.id$phq.sum_score_base_raw <- phq.scored_items_base$scores
-
-# Look at values
-coping.phq.raw.id %>%
-  descr(phq.sum_score_base_raw,
-        stats = "common"
-  )
-```
-
-# Missingness
-
-retrospective
-```{r coping phq retro missingness}
-coping.phq.raw.id <- coping.phq.raw.id %>%
-  mutate(
-    na_per_person_phq_retro =         # variable for NA per person
-      rowSums(
-        is.na(.[phq.items_retro])
-      )
-  )
-
-coping.phq.raw.id %>%
-  freq(na_per_person_phq_retro, cumul = F) #have a look at the frequency
-```
-
-```{r coping phq retro missingness 8 items}
-coping.phq.raw.id <- coping.phq.raw.id %>%
-  mutate(
-    phq.missing_only_suicide_item_retro = 
-      if_else(
-        condition = na_per_person_phq_retro == 1 & 
-          is.na(phq.dead_hurting_thoughts_retro_numeric), 
-        true = 1,
-        false = 0,
-        missing = NA_real_
-      )
-  )
-
-coping.phq.raw.id %>%
-  freq(phq.missing_only_suicide_item_retro,
-       cumul = F)
-```
-
-baseline
-```{r coping phq base missingness}
-coping.phq.raw.id <- coping.phq.raw.id %>%
-  mutate(
-    na_per_person_phq_base =         # variable for NA per person
-      rowSums(                       
-        is.na(.[phq.items_base])
-      )
-  )
-
-coping.phq.raw.id %>%
-  freq(na_per_person_phq_base, cumul = F) #have a look at the frequency
-```
-
-We need to identify those who have all items APART from the suicide ideation item - to still include these individuals. 
-```{r coping phq base missingness 8 items}
-coping.phq.raw.id <- coping.phq.raw.id %>%
-  mutate(
-    phq.missing_only_suicide_item_base = 
-      if_else(
-        condition = na_per_person_phq_base == 1 & 
-          is.na(phq.dead_hurting_thoughts_base_numeric), 
-        true = 1,
-        false = 0,
-        missing = NA_real_
-      )
-  )
-
-coping.phq.raw.id %>%
-  freq(phq.missing_only_suicide_item_base,
-       cumul = F)
-```
-
-```{r coping phq base sum score if missing items set to NA}
-coping.phq.raw.id <- coping.phq.raw.id %>%
-  mutate(
-    phq.sum_score_base =
-      if_else(condition = na_per_person_phq_base > 0,
-              true = NA_real_,
-              false = phq.sum_score_base_raw,
-              missing = NA_real_
-      )
-  )
-
-coping.phq.raw.id %>%
-  descr(phq.sum_score_base_raw, stats = "common")
-
-coping.phq.raw.id %>%
-  descr(phq.sum_score_base, stats = "common")
-```
-
-8 items
-```{r phq base sum score if missing items set to NA - 8 items}
-coping.phq.raw.id <- coping.phq.raw.id %>%
-  mutate(
-    phq.sum_score_8items_base =
-      if_else(condition = na_per_person_phq_base > 1 &
-                phq.missing_only_suicide_item_base == 1,
-              true = NA_real_,
-              false = phq.sum_score_base_raw,
-              missing = NA_real_
-      )
-  )
-
-coping.phq.raw.id %>%
-  descr(phq.sum_score_8items_base, stats = "common")
-```
-
-```{r coping phq retro sum score if missing items set to NA}
-coping.phq.raw.id <- coping.phq.raw.id %>%
-  mutate(
-    phq.sum_score_retro =
-      if_else(condition = na_per_person_phq_retro > 0,
-              true = NA_real_,
-              false = phq.sum_score_retro_raw,
-              missing = NA_real_
-      )
-  )
-
-coping.phq.raw.id %>%
-  descr(phq.sum_score_retro_raw, stats = "common")
-
-coping.phq.raw.id %>%
-  descr(phq.sum_score_retro, stats = "common")
-```
-
-8 items
-```{r phq retro sum score if missing items set to NA - 8 items}
-coping.phq.raw.id <- coping.phq.raw.id %>%
-  mutate(
-    phq.sum_score_8items_retro =
-      if_else(condition = na_per_person_phq_retro > 1 &
-                phq.missing_only_suicide_item_retro == 1,
-              true = NA_real_,
-              false = phq.sum_score_retro_raw,
-              missing = NA_real_
-      )
-  )
-
-coping.phq.raw.id %>%
-  descr(phq.sum_score_8items_retro, stats = "common")
-```
-
-## Inspection
-
-```{r coping glad phq head}
-head(coping.phq.raw.id)
-```
-
-```{r coping glad phq summary}
-summarytools::dfSummary(
-  coping.phq.raw.id,
-  graph.col = F,
-  valid.col = F,
-  labels.col = F)
-```
-
-# COPING: OCI-R
-
-## GLAD
-```{r coping glad ocir cols}
-if(GLAD == TRUE) {
-coping.glad.ocir.raw <- readRDS(file = paste0(data.raw_path, "/glad/ocir_coping_glad.rds"))
-dim(coping.glad.ocir.raw)
-colnames(coping.glad.ocir.raw)
-}
-```
-
-```{r coping glad ocir summary labels}
-if(GLAD == TRUE) {
-summarytools::dfSummary(
-  coping.glad.ocir.raw,
-  graph.col = F,
-  valid.col = F
-  #labels.col = F
-)
-}
-```
-
-*Note that the COPING GLAD OCI-R ID numbers are stored under recipientFirstName (rather than ExternalDataReference)
-```{r coping glad ocir cleaning}
-if(GLAD == TRUE) {
-coping.glad.ocir.raw.id <- coping.glad.ocir.raw %>%
-  drop_na(recipientFirstName) %>% # Drop NAs
-  distinct(recipientFirstName, .keep_all = TRUE) %>% # Remove duplicates based on ID
-  separate(recipientFirstName, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
-  mutate(ID = as.numeric(ID)) %>%
-  select(
-    Sample, # Sample
-    ID, # ID
-    ocir.felt_pandemic_feelings, # Comparison to before the pandemic
-    ocir.i_repeatedly_check_doors_windows_drawers_etc_retro = ocir.i_repeatedly_check_doors_windows_drawers_etc.,
-    ocir.arranged_things_change_upset_retro = ocir.arranged_things_change_upset,
-    ocir.repeat_feel_numbers_retro = ocir.numbers_repeat_feel, ## Different from GLAD prepandemic
-    ocir.clean_simply_wash_feel_retro = ocir.feel_contaminated_clean_simply, ## Different from GLAD prepandemic
-    ocir.mind_upset_unpleasant_thoughts_retro = ocir.mind_upset_unpleasant_thoughts,
-    ocir.afraid_avoid_throwing_things_retro = ocir.afraid_avoid_throwing_things,
-    ocir.light_switches_water_taps_retro = ocir.light_switches_water_taps,
-    ocir.arranged_things_retro = ocir.arranged_things,
-    ocir.good_feel_bad_numbers_retro = ocir.bad_numbers_good_feel, ## Different from GLAD prepandemic
-    ocir.hands_longer_wash_retro = ocir.longer_hands_wash, ## Different from GLAD prepandemic
-    ocir.saved_things_retro = ocir.saved_things,
-    ocir.frequently_difficulty_rid_nasty_retro = ocir.frequently_rid_difficulty_nasty, ## Different from GLAD prepandemic
-    ocir.i_check_things_more_often_than_necessary_retro = ocir.i_check_things_more_often_than_necessary.,
-    ocir.arranged_properly_objects_upset_retro = ocir.arranged_properly_objects_upset,
-    ocir.feel_compelled_count_things_retro = ocir.feel_compelled_count_things,
-    ocir.strangers_touch_touched_difficult_retro = ocir.strangers_touch_touched_object, ## Different from GLAD prepandemic
-    ocir.control_difficult_find_thoughts_retro = ocir.control_find_difficult_thoughts, ## Different from GLAD prepandemic
-    ocir.i_collect_things_i_dont_need_retro = ocir.i_collect_things_i_dont_need., ## Different from GLAD prepandemic
-    ocir.i_repeatedly_check_doors_windows_drawers_etc_base = ocir.i_repeatedly_check_doors_windows_drawers_etc..1,
-    ocir.arranged_things_change_upset_base = ocir.arranged_things_change_upset.1,
-    ocir.repeat_feel_numbers_base = ocir.numbers_repeat_feel.1, ## Different from GLAD prepandemic
-    ocir.clean_simply_wash_feel_base = ocir.feel_contaminated_clean_simply.1, ## Different from GLAD prepandemic
-    ocir.mind_upset_unpleasant_thoughts_base = ocir.mind_upset_unpleasant_thoughts.1,
-    ocir.afraid_avoid_throwing_things_base = ocir.afraid_avoid_throwing_things.1,
-    ocir.light_switches_water_taps_base = ocir.light_switches_water_taps.1,
-    ocir.arranged_things_base = ocir.arranged_things.1,
-    ocir.good_feel_bad_numbers_base = ocir.bad_numbers_good_feel.1, ## Different from GLAD prepandemic
-    ocir.hands_longer_wash_base = ocir.longer_hands_wash.1, ## Different from GLAD prepandemic
-    ocir.saved_things_base = ocir.saved_things.1,
-    ocir.frequently_difficulty_rid_nasty_base = ocir.frequently_rid_difficulty_nasty.1, ## Different from GLAD prepandemic
-    ocir.i_check_things_more_often_than_necessary_base = ocir.i_check_things_more_often_than_necessary..1,
-    ocir.arranged_properly_objects_upset_base = ocir.arranged_properly_objects_upset.1,
-    ocir.feel_compelled_count_things_base = ocir.feel_compelled_count_things.1,
-    ocir.strangers_touch_touched_difficult_base = ocir.strangers_touch_touched_object.1, ## Different from GLAD prepandemic
-    ocir.control_difficult_find_thoughts_base = ocir.control_find_difficult_thoughts.1, ## Different from GLAD prepandemic
-    ocir.i_collect_things_i_dont_need_base = ocir.i_collect_things_i_dont_need..1
-  ) %>%
-  add_numeric(., exclude = exclude_cols) %>%
-  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
-  mutate_if(is.numeric, ~na_if(., -99)) %>%
-  mutate_if(is.numeric, ~na_if(., -77)) %>%
-  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
-  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
-
-# Inspect dimensions
-dim(coping.glad.ocir.raw.id)
-# Inspect colnames
-colnames(coping.glad.ocir.raw.id)
-#Differences
-dim(coping.glad.ocir.raw)[1]-dim(coping.glad.ocir.raw.id)[1]
-}
-```
-
-```{r coping glad ocir copy}
-if(GLAD == TRUE) {
-  coping.ocir.raw.id <- coping.glad.ocir.raw.id
-}
-```
-
-## EDGI
-```{r coping edgi ocir cols}
-if(EDGI == TRUE) {
-coping.edgi.ocir.raw <- readRDS(file = paste0(data.raw_path, "/edgi/ocir_coping_edgi.rds"))
-dim(coping.edgi.ocir.raw)
-colnames(coping.edgi.ocir.raw)
-}
-```
-
-```{r coping edgi ocir summary labels}
-if(EDGI == TRUE) {
-summarytools::dfSummary(
-  coping.edgi.ocir.raw,
-  graph.col = F,
-  valid.col = F
-  #labels.col = F
-)
-}
-```
-
-*Note that the COPING EDGI OCI-R ID numbers are stored under recipientFirstName (rather than ExternalDataReference)
-```{r coping edgi ocir cleaning}
-if(EDGI == TRUE) {
-coping.edgi.ocir.raw.id <- coping.edgi.ocir.raw %>%
-  drop_na(externalDataReference) %>% # Drop NAs
-  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
-  separate(externalDataReference, into = c("Sample", "ID"), sep = 6) %>% # Split ID in Sample and Number
-  mutate(ID = as.numeric(ID)) %>%
-  select(
-    Sample, # Sample
-    ID, # ID
-    ocir.felt_pandemic_feelings, # Comparison to before the pandemic
-    ocir.i_repeatedly_check_doors_windows_drawers_etc_retro = ocir.i_repeatedly_check_doors_windows_drawers_etc.,
-    ocir.arranged_things_change_upset_retro = ocir.arranged_things_change_upset,
-    ocir.repeat_feel_numbers_retro = ocir.repeat_numbers_feel, # Different from EDGI prepandemic ocir.numbers_repeat_feel,
-    ocir.clean_simply_wash_feel_retro = ocir.feel_contaminated_clean_simply, ## Different from EDGI prepandemic
-    ocir.mind_upset_unpleasant_thoughts_retro = ocir.mind_upset_unpleasant_thoughts,
-    ocir.afraid_avoid_throwing_things_retro = ocir.afraid_avoid_throwing_things,
-    ocir.light_switches_water_taps_retro = ocir.water_taps_light_switches, #  differ ocir.light_switches_water_taps,
-    ocir.arranged_things_retro = ocir.arranged_things,
-    ocir.good_feel_bad_numbers_retro = ocir.bad_numbers_good_feel, ## Different from EDGI prepandemic
-    ocir.hands_longer_wash_retro = ocir.longer_hands_wash, ## Different from EDGI prepandemic
-    ocir.saved_things_retro = ocir.saved_things,
-    ocir.frequently_difficulty_rid_nasty_retro = ocir.frequently_rid_difficulty_nasty, ## Different from EDGI prepandemic
-    ocir.i_check_things_more_often_than_necessary_retro = ocir.i_check_things_more_often_than_necessary.,
-    ocir.arranged_properly_objects_upset_retro = ocir.arranged_properly_objects_upset,
-    ocir.feel_compelled_count_things_retro = ocir.feel_compelled_count_things,
-    ocir.strangers_touch_touched_difficult_retro = ocir.strangers_touch_touched_object, ## Different from EDGI prepandemic
-    ocir.control_difficult_find_thoughts_retro = ocir.control_difficult_thoughts_find, # Differ to EDGI prepan ocir.control_find_difficult_thoughts,
-    ocir.i_collect_things_i_dont_need_retro = ocir.i_collect_things_i_dont_need., ## Different from EDGI prepandemic
-    ocir.i_repeatedly_check_doors_windows_drawers_etc_base = ocir.i_repeatedly_check_doors_windows_drawers_etc..1,
-    ocir.arranged_things_change_upset_base = ocir.arranged_things_change_upset.1,
-    ocir.repeat_feel_numbers_base = ocir.repeat_numbers_feel.1, ## Different from EDGI prepandemic
-    ocir.clean_simply_wash_feel_base = ocir.feel_contaminated_clean_simply.1, ## Different from EDGI prepandemic
-    ocir.mind_upset_unpleasant_thoughts_base = ocir.mind_upset_unpleasant_thoughts.1,
-    ocir.afraid_avoid_throwing_things_base = ocir.afraid_avoid_throwing_things.1,
-    ocir.light_switches_water_taps_base = ocir.water_taps_light_switches.1, # differ
-    ocir.arranged_things_base = ocir.arranged_things.1,
-    ocir.good_feel_bad_numbers_base = ocir.bad_numbers_good_feel.1, ## Different from EDGI prepandemic
-    ocir.hands_longer_wash_base = ocir.longer_hands_wash.1, ## Different from EDGI prepandemic
-    ocir.saved_things_base = ocir.saved_things.1,
-    ocir.frequently_difficulty_rid_nasty_base = ocir.frequently_rid_difficulty_nasty.1, ## Different from EDGI prepandemic
-    ocir.i_check_things_more_often_than_necessary_base = ocir.i_check_things_more_often_than_necessary..1,
-    ocir.arranged_properly_objects_upset_base = ocir.arranged_properly_objects_upset.1,
-    ocir.feel_compelled_count_things_base = ocir.feel_compelled_count_things.1,
-    ocir.strangers_touch_touched_difficult_base = ocir.strangers_touch_touched_object.1, ## Different from EDGI prepandemic
-    ocir.control_difficult_find_thoughts_base = ocir.control_difficult_thoughts_find.1, ## Different from EDGI prepandemic
-    ocir.i_collect_things_i_dont_need_base = ocir.i_collect_things_i_dont_need..1
-  ) %>%
-  add_numeric(., exclude = exclude_cols) %>%
-  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
-  mutate_if(is.numeric, ~na_if(., -99)) %>%
-  mutate_if(is.numeric, ~na_if(., -77)) %>%
-  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
-  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
-
-# Inspect dimensions
-dim(coping.edgi.ocir.raw.id)
-# Inspect colnames
-colnames(coping.edgi.ocir.raw.id)
-#Differences
-dim(coping.edgi.ocir.raw)[1]-dim(coping.edgi.ocir.raw.id)[1]
-}
-```
-
-```{r coping edgi ocir copy}
-if(EDGI == TRUE) {
-  coping.ocir.raw.id <- coping.edgi.ocir.raw.id
-}
-```
-
-## NBR
-```{r coping nbr ocir cols}
-if(NBR == TRUE) {
-coping.nbr.ocir.raw <- readRDS(file = paste0(data.raw_path, "/nbr/ocir_coping_nbr.rds"))
-dim(coping.nbr.ocir.raw)
-colnames(coping.nbr.ocir.raw)
-}
-```
-
-```{r coping nbr ocir summary labels}
-if(NBR == TRUE) {
-summarytools::dfSummary(
-  coping.nbr.ocir.raw,
-  graph.col = F,
-  valid.col = F
-  #labels.col = F
-)
-}
-```
-
-*Note that the COPING NBR OCI-R ID numbers are stored under recipientFirstName (rather than ExternalDataReference)
-
-++MD: One NBR ID is being converted to NA by the as.numeric(ID) line of code.
-```{r coping nbr ocir cleaning}
-if(NBR == TRUE) {
-coping.nbr.ocir.raw.id <- coping.nbr.ocir.raw %>%
-  drop_na(recipientFirstName) %>% # Drop NAs
-  distinct(recipientFirstName, .keep_all = TRUE) %>% # Remove duplicates based on ID
-  separate(recipientFirstName, into = c("Sample", "ID.intm"), sep = 6) %>% # Split ID in Sample and Number
-  separate(ID.intm, into = "ID", sep = 7) %>%
-  mutate(ID = as.numeric(ID)) %>%
-  select(
-    Sample, # Sample
-    ID, # ID
-    ocir.felt_pandemic_feelings, # Comparison to before the pandemic
-    ocir.i_repeatedly_check_doors_windows_drawers_etc_retro = ocir.i_repeatedly_check_doors_windows_drawers_etc.,
-    ocir.arranged_things_change_upset_retro = ocir.arranged_things_change_upset,
-    ocir.repeat_feel_numbers_retro = ocir.repeat_numbers_feel, ## Different from GLAD
-    ocir.clean_simply_wash_feel_retro = ocir.feel_contaminated_clean_simply,
-    ocir.mind_upset_unpleasant_thoughts_retro = ocir.mind_upset_unpleasant_thoughts,
-    ocir.afraid_avoid_throwing_things_retro = ocir.afraid_avoid_throwing_things,
-    ocir.light_switches_water_taps_retro = ocir.water_taps_light_switches, ## Different from GLAD
-    ocir.arranged_things_retro = ocir.arranged_things,
-    ocir.good_feel_bad_numbers_retro = ocir.bad_numbers_good_feel,
-    ocir.hands_longer_wash_retro = ocir.longer_hands_wash, 
-    ocir.saved_things_retro = ocir.saved_things,
-    ocir.frequently_difficulty_rid_nasty_retro = ocir.frequently_rid_difficulty_nasty, 
-    ocir.i_check_things_more_often_than_necessary_retro = ocir.i_check_things_more_often_than_necessary.,
-    ocir.arranged_properly_objects_upset_retro = ocir.arranged_properly_objects_upset,
-    ocir.feel_compelled_count_things_retro = ocir.feel_compelled_count_things,
-    ocir.strangers_touch_touched_difficult_retro = ocir.strangers_touch_touched_object, 
-    ocir.control_difficult_find_thoughts_retro = ocir.control_difficult_thoughts_find, ## Different from GLAD 
-    ocir.i_collect_things_i_dont_need_retro = ocir.i_collect_things_i_dont_need., 
-    ocir.i_repeatedly_check_doors_windows_drawers_etc_base = ocir.i_repeatedly_check_doors_windows_drawers_etc..1,
-    ocir.arranged_things_change_upset_base = ocir.arranged_things_change_upset.1,
-    ocir.repeat_feel_numbers_base = ocir.repeat_numbers_feel.1, ## Different from GLAD
-    ocir.clean_simply_wash_feel_base = ocir.feel_contaminated_clean_simply.1,
-    ocir.mind_upset_unpleasant_thoughts_base = ocir.mind_upset_unpleasant_thoughts.1,
-    ocir.afraid_avoid_throwing_things_base = ocir.afraid_avoid_throwing_things.1,
-    ocir.light_switches_water_taps_base = ocir.water_taps_light_switches.1, ## Different from GLAD
-    ocir.arranged_things_base = ocir.arranged_things.1,
-    ocir.good_feel_bad_numbers_base = ocir.bad_numbers_good_feel.1, 
-    ocir.hands_longer_wash_base = ocir.longer_hands_wash.1, 
-    ocir.saved_things_base = ocir.saved_things.1,
-    ocir.frequently_difficulty_rid_nasty_base = ocir.frequently_rid_difficulty_nasty.1, 
-    ocir.i_check_things_more_often_than_necessary_base = ocir.i_check_things_more_often_than_necessary..1,
-    ocir.arranged_properly_objects_upset_base = ocir.arranged_properly_objects_upset.1,
-    ocir.feel_compelled_count_things_base = ocir.feel_compelled_count_things.1,
-    ocir.strangers_touch_touched_difficult_base = ocir.strangers_touch_touched_object.1, 
-    ocir.control_difficult_find_thoughts_base = ocir.control_difficult_thoughts_find.1,
-    ocir.i_collect_things_i_dont_need_base = ocir.i_collect_things_i_dont_need..1
-  ) %>%
-  add_numeric(., exclude = exclude_cols) %>%
-  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
-  mutate_if(is.numeric, ~na_if(., -99)) %>%
-  mutate_if(is.numeric, ~na_if(., -77)) %>%
-  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
-  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
-
-# Inspect dimensions
-dim(coping.nbr.ocir.raw.id)
-# Inspect colnames
-colnames(coping.nbr.ocir.raw.id)
-#Differences
-dim(coping.nbr.ocir.raw)[1]-dim(coping.nbr.ocir.raw.id)[1]
-}
-```
-
-```{r coping nbr ocir copy}
-if(NBR == TRUE) {
-  coping.ocir.raw.id <- coping.nbr.ocir.raw.id
-}
-```
-
-## RAMP
-```{r coping ramp ocir cols}
-if(RAMP == TRUE) {
-ramp.ocir.raw <- readRDS(file = paste0(data.raw_path, "/ramp/ocir_ramp.rds"))
-dim(ramp.ocir.raw)
-colnames(ramp.ocir.raw)
-}
-```
-
-```{r coping ramp ocir summary labels}
-if(RAMP == TRUE) {
-summarytools::dfSummary(
-  ramp.ocir.raw,
-  graph.col = F,
-  valid.col = F
-  #labels.col = F
-)
-}
-```
-
-*Note that the COPING RAMP OCI-R ID numbers are stored under recipientFirstName (rather than ExternalDataReference)
-```{r coping ramp ocir cleaning}
-if(RAMP == TRUE) {
-ramp.ocir.raw.id <- ramp.ocir.raw %>%
-  drop_na(`Login ID`) %>% # Drop NAs
-  distinct(`Login ID`, .keep_all = TRUE) %>% # Remove duplicates based on ID
-  separate(`Login ID`, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
-  mutate(ID = as.numeric(ID)) %>%
-  select(
-    Sample, # Sample
-    ID, # ID
-    ocir.felt_pandemic_feelings = ocir.feelings_pandemic_felt, # Comparison to before the pandemic
-    ocir.saved_things_retro = ocir.saved_things.1, #reordered items to reflect questionnaire
-    ocir.i_check_things_more_often_than_necessary_retro = ocir.i_check_things_more_often_than_necessary..1, #in RAMP .1 = retrospective
-    ocir.arranged_properly_objects_upset_retro = ocir.arranged_properly_objects_upset.1,
-    ocir.feel_compelled_count_things_retro = ocir.feel_compelled_count_things.1,
-    ocir.strangers_touch_touched_difficult_retro = ocir.touch_touched_strangers_object.1,
-    ocir.control_difficult_find_thoughts_retro = ocir.find_control_difficult_thoughts.1,
-    ocir.i_collect_things_i_dont_need_retro = ocir.i_collect_things_i_dont_need..1,
-    ocir.i_repeatedly_check_doors_windows_drawers_etc_retro = ocir.i_repeatedly_check_doors_windows_drawers_etc..1,
-    ocir.arranged_things_change_upset_retro = ocir.arranged_things_change_upset.1,
-    ocir.repeat_feel_numbers_retro = ocir.numbers_repeat_feel.1, 
-    ocir.clean_simply_wash_feel_retro = ocir.feel_contaminated_clean_simply.1, 
-    ocir.mind_upset_unpleasant_thoughts_retro = ocir.unpleasant_thoughts_mind_upset.1,
-    ocir.afraid_avoid_throwing_things_retro = ocir.afraid_avoid_throwing_things.1,
-    ocir.light_switches_water_taps_retro = ocir.repeatedly_check_gas_water.1,
-    ocir.arranged_things_retro = ocir.arranged_things.1,
-    ocir.good_feel_bad_numbers_retro = ocir.bad_numbers_good_feel.1, 
-    ocir.hands_longer_wash_retro = ocir.longer_hands_wash.1, 
-    ocir.frequently_difficulty_rid_nasty_retro = ocir.difficulty_rid_frequently_nasty.1, 
-    ocir.saved_things_base = ocir.saved_things,
-    ocir.i_check_things_more_often_than_necessary_base = ocir.i_check_things_more_often_than_necessary.,
-    ocir.arranged_properly_objects_upset_base = ocir.arranged_properly_objects_upset,
-    ocir.feel_compelled_count_things_base = ocir.feel_compelled_count_things,
-    ocir.strangers_touch_touched_difficult_base = ocir.touch_touched_strangers_object, 
-    ocir.control_difficult_find_thoughts_base = ocir.find_control_difficult_thoughts, 
-    ocir.i_collect_things_i_dont_need_base = ocir.i_collect_things_i_dont_need.,
-    ocir.i_repeatedly_check_doors_windows_drawers_etc_base = ocir.i_repeatedly_check_doors_windows_drawers_etc.,
-    ocir.arranged_things_change_upset_base = ocir.arranged_things_change_upset,
-    ocir.repeat_feel_numbers_base = ocir.numbers_repeat_feel, 
-    ocir.clean_simply_wash_feel_base = ocir.feel_contaminated_clean_simply, 
-    ocir.mind_upset_unpleasant_thoughts_base = ocir.unpleasant_thoughts_mind_upset,
-    ocir.afraid_avoid_throwing_things_base = ocir.afraid_avoid_throwing_things,
-    ocir.light_switches_water_taps_base = ocir.repeatedly_check_gas_water,
-    ocir.arranged_things_base = ocir.arranged_things,
-    ocir.good_feel_bad_numbers_base = ocir.bad_numbers_good_feel, 
-    ocir.hands_longer_wash_base = ocir.longer_hands_wash, 
-    ocir.frequently_difficulty_rid_nasty_base = ocir.difficulty_rid_frequently_nasty
-  ) %>%
-  add_numeric(., exclude = exclude_cols) %>%
-  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
-  mutate_if(is.numeric, ~na_if(., -99)) %>%
-  mutate_if(is.numeric, ~na_if(., -77)) %>%
-  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
-  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
-
-# Inspect dimensions
-dim(ramp.ocir.raw.id)
-# Inspect colnames
-colnames(ramp.ocir.raw.id)
-#Differences
-dim(ramp.ocir.raw)[1]-dim(ramp.ocir.raw.id)[1]
-}
-```
-
-```{r coping ramp ocir copy}
-if(RAMP == TRUE) {
-  coping.ocir.raw.id <- ramp.ocir.raw.id
-}
-```
-
-## Sum scores
-
-Calculate sum score for OCI-R retro
-```{r coping ocir sum score retro}
-# Create vector with scoring key: If the item is reversed coded use -1. 
-# There needs to be the correct number of values for each item in the questionnaire. 
-ocir.items_key_retro <- c(1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1)
-
-# Create vector with items that are included in total score
-ocir.items_retro = c(
-  "ocir.i_repeatedly_check_doors_windows_drawers_etc_retro",
-  "ocir.arranged_things_change_upset_retro",
-  "ocir.repeat_feel_numbers_retro",
-  "ocir.clean_simply_wash_feel_retro",
-  "ocir.mind_upset_unpleasant_thoughts_retro",
-  "ocir.afraid_avoid_throwing_things_retro",
-  "ocir.light_switches_water_taps_retro",
-  "ocir.arranged_things_retro",
-  "ocir.good_feel_bad_numbers_retro",
-  "ocir.hands_longer_wash_retro",
-  "ocir.saved_things_retro",
-  "ocir.frequently_difficulty_rid_nasty_retro",
-  "ocir.i_check_things_more_often_than_necessary_retro",
-  "ocir.arranged_properly_objects_upset_retro",
-  "ocir.feel_compelled_count_things_retro",
-  "ocir.strangers_touch_touched_difficult_retro",
-  "ocir.control_difficult_find_thoughts_retro",
-  "ocir.i_collect_things_i_dont_need_retro"
-)
-
-# Calulate total score
-ocir.scored_items_retro <- scoreItems(keys = ocir.items_key_retro,
-                                     items = coping.ocir.raw.id[ocir.items_retro],
-                                     totals = TRUE, 
-                                     missing = TRUE, 
-                                     impute = 'none', 
-                                     min = 0, 
-                                     max = 4)
-# Add in column to tibble
-coping.ocir.raw.id$ocir.sum_score_retro_raw <- ocir.scored_items_retro$scores
-
-# Look at values
-coping.ocir.raw.id %>%
-  descr(ocir.sum_score_retro_raw,
-        stats = "common"
-  )
-```
-
-Calculate sum score for OCI-R base
-```{r coping ocir sum score base}
-# Create vector with scoring key: If the item is reversed coded use -1. 
-# There needs to be the correct number of values for each item in the questionnaire. 
-ocir.items_key_base <- c(1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1)
-
-# Create vector with items that are included in total score
-ocir.items_base = c(
-  "ocir.i_repeatedly_check_doors_windows_drawers_etc_base",
-  "ocir.arranged_things_change_upset_base",
-  "ocir.repeat_feel_numbers_base",
-  "ocir.clean_simply_wash_feel_base",
-  "ocir.mind_upset_unpleasant_thoughts_base",
-  "ocir.afraid_avoid_throwing_things_base",
-  "ocir.light_switches_water_taps_base",
-  "ocir.arranged_things_base",
-  "ocir.good_feel_bad_numbers_base",
-  "ocir.hands_longer_wash_base",
-  "ocir.saved_things_base",
-  "ocir.frequently_difficulty_rid_nasty_base",
-  "ocir.i_check_things_more_often_than_necessary_base",
-  "ocir.arranged_properly_objects_upset_base",
-  "ocir.feel_compelled_count_things_base",
-  "ocir.strangers_touch_touched_difficult_base",
-  "ocir.control_difficult_find_thoughts_base",
-  "ocir.i_collect_things_i_dont_need_base"
-)
-
-# Calulate total score
-ocir.scored_items_base <- scoreItems(keys = ocir.items_key_base,
-                                    items = coping.ocir.raw.id[ocir.items_base],
-                                    totals = TRUE, 
-                                    missing = TRUE, 
-                                    impute = 'none', 
-                                    min = 0, 
-                                    max = 4)
-# Add in column to tibble
-coping.ocir.raw.id$ocir.sum_score_base_raw <- ocir.scored_items_base$scores
-
-# Look at values
-coping.ocir.raw.id %>%
-  descr(ocir.sum_score_base_raw,
-        stats = "common"
-  )
-```
-
-# Missingness
-
-retrospective
-```{r coping ocir retro missingness}
-coping.ocir.raw.id <- coping.ocir.raw.id %>%
-  mutate(
-    na_per_person_ocir_retro =         # variable for NA per person
-      rowSums(
-        is.na(.[ocir.items_retro])
-      )
-  )
-
-coping.ocir.raw.id %>%
-  freq(na_per_person_ocir_retro, cumul = F) #have a look at the frequency
-```
-
-baseline
-```{r coping ocir base missingness}
-coping.ocir.raw.id <- coping.ocir.raw.id %>%
-  mutate(
-    na_per_person_ocir_base =         # variable for NA per person
-      rowSums(                       
-        is.na(.[ocir.items_base])
-      )
-  )
-
-coping.ocir.raw.id %>%
-  freq(na_per_person_ocir_base, cumul = F) #have a look at the frequency
-```
-
-```{r coping ocir base sum score if missigng items set to NA}
-coping.ocir.raw.id <- coping.ocir.raw.id %>%
-  mutate(
-    ocir.sum_score_base =
-      if_else(condition = na_per_person_ocir_base > 0,
-              true = NA_real_,
-              false = ocir.sum_score_base_raw,
-              missing = NA_real_
-      )
-  )
-
-coping.ocir.raw.id %>%
-  descr(ocir.sum_score_base_raw, stats = "common")
-
-coping.ocir.raw.id %>%
-  descr(ocir.sum_score_base, stats = "common")
-```
-
-```{r coping ocir retro sum score if missigng items set to NA}
-coping.ocir.raw.id <- coping.ocir.raw.id %>%
-  mutate(
-    ocir.sum_score_retro =
-      if_else(condition = na_per_person_ocir_retro > 0,
-              true = NA_real_,
-              false = ocir.sum_score_retro_raw,
-              missing = NA_real_
-      )
-  )
-
-coping.ocir.raw.id %>%
-  descr(ocir.sum_score_retro_raw, stats = "common")
-
-coping.ocir.raw.id %>%
-  descr(ocir.sum_score_retro, stats = "common")
-```
-
-# Inspection
-
-```{r coping glad ocir head}
-head(coping.ocir.raw.id)
-```
-
-```{r coping glad ocir summary}
-summarytools::dfSummary(
-  coping.ocir.raw.id,
-  graph.col = F,
-  valid.col = F,
-  labels.col = F)
-```
-
-# Join tibbles together
-
-glad/edgi data frame list
-```{r glad/edgi data frame list}
-if(GLAD == TRUE | EDGI == TRUE) {
-dfs.list <- list(
-  dem.raw.id,
-  prepan.gad.raw.id,
-  mhd.raw.categories,
-  prepan.ocir.raw.id,
-  prepan.pcl.raw.id,
-  prepan.phq.raw.id,
-  coping.gad.raw.id,
-  coping.pcl.raw.id,
-  coping.phq.raw.id,
-  coping.ocir.raw.id
-)
-}
-```
-
-Removing all prepandemic dataframes from NBR/RAMP (prepandemic measures don't exist for these cohorts)
-```{r nbr/ramp data frame list}
-if(NBR == TRUE | RAMP == TRUE) {
-dfs.list <- list(
-  dem.raw.id,
-  mhd.raw.categories,
-  coping.gad.raw.id,
- # coping.pcl.raw.id, #WAITING FOR PCL DATA FOR RAMP
-  coping.phq.raw.id,
-  coping.ocir.raw.id
-)
-}
-```
-
 ```{r Join all questionnaires}
-dat.raw <- plyr::join_all(
+dat <- plyr::join_all(
   dfs.list,
@@
 #look at the data
-skimr::skim(dat.raw)
-```
-
-Check duplicates again to be saved
-+++KLP: RAMP: More than one column: Age, Sex, Login ID; if they match on all 3 then we treat them as a duplicate; otherwise we are going to rename the Login ID
-+++KT: No duplicates identified by ID in GLAD. 
-+++MD: Duplicates have been removed in cleaning script for NBR. No duplicates at this stage.
-```{r Check duplicates}
-dat.raw$ID.dup <- duplicated(dat.raw$ID)
-
-summary(as.factor(dat.raw$ID.dup))
-
-dat.dup <- dat.raw %>%
-  filter(ID.dup == TRUE)
-
-dat.raw.no.dup <- dat.raw %>%
-  filter(ID.dup == FALSE)
-```
-
-#Exclusion
-Exclude those without sex, gender, age and incomplete PHQ/GAD items
-Create a new new object for each exclusion step, e.g., data.no_sex, data.no_gender and data.no_sex.no_age
-```{r Exclude participants that do not report sex}
-if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE){
-dim(dat.raw)
-dat.no.sex <- dat.raw %>%
-  drop_na(Sex)
-dim(dat.no.sex)
-
-dim(dat.raw)[1]-dim(dat.no.sex)[1]
-}
-```
-`r dim(dat.glad.raw)[1]-dim(dat.no.sex)[1]` were excluded because they did not report their sex
-
-```{r rename dataset for ramp}
-if(RAMP == TRUE){
-#there is no sex variable in ramp
-dat.no.sex <- dat.raw
-}
-```
-
-```{r Exclude participants that do not report gender}
-dim(dat.no.sex)
-dat.no.sex.no.gender <- dat.no.sex %>%
-  drop_na(Gender)
-dim(dat.no.sex.no.gender)
-
-dim(dat.no.sex)[1]-dim(dat.no.sex.no.gender)[1]
-```
-`r dim(dat.no.sex)[1]-dim(dat.no.sex.no.gender)[1]` were excluded because they did not report their sex
-
-```{r Exclude participants that do not report age}
-dim(dat.no.sex.no.gender)
-dat.no.sex.no.gender.no.age <- dat.no.sex.no.gender %>%
-  drop_na(age_category_full)
-dim(dat.no.sex.no.gender.no.age)
-
-dim(dat.no.sex.no.gender)[1]-dim(dat.no.sex.no.gender.no.age)[1]
-```
-`r dim(dat.no.gender)[1]-dim(dat.no.sex.no.gender.no.age)[1]` were excluded because they did not report their age
-
-Exclusion of inflammatory bowel disease (IBD) BioResource (BR) cohort
-++MD: 3,410 participants from NBR IBD cohort excluded
-```{r COVID exclusion of IBD}
-if(NBR == TRUE) {
-dim(dat.no.sex.no.gender.no.age)
-
-dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age %>%
-  filter(Cohort != "IBD")
-
-dim(dat.no.sex.no.gender.no.age.no.ibd)
-dim(dat.no.sex.no.gender.no.age)[1]-dim(dat.no.sex.no.gender.no.age.no.ibd)[1]
-}
-
-if(GLAD == TRUE | EDGI == TRUE | RAMP == TRUE) {
-dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age
-}
-```
-
-##Create tidy data on which the exclusion criteria have been applied
-Complete sex, gender, age and missingness information applied. 
-```{r Tidy data}
-dat <- dat.no.sex.no.gender.no.age.no.ibd
-
 skimr::skim(dat)
@@
 
-# Definition of prepandemic and baseline 
-Exlcude people who have joined GLAD/EDGI after the pandemic began, sensitivity analyses done on the cut off's we have chosen. 
-Potentially GLAD/EDGI particiapnts between January to April. EDGI launched on February 24th.
-
-Prepandemic GLAD/EDGI = Prepandemic (GLAD/EDGI sign-up questionnaire)
-
-Retrospective = COPING/RAMP sign up questionnaire; *only of those participants who have reported a change in symptoms*
-
-Baseline = COPING/RAMP sign up questionnaire
-
-Dates for the definition of prepandemic
-```{r Potential dates for prepandemic definition}
-# Date of the first COVID-19 case in the United Kingdom (UK)
-date_first_case_uk_january_31 <- as.POSIXct("2020-01-31")
-
-# Date for assumed higher awareness of COVID / Lockdown in Italy 4. March 2020 / first festivals cancelled
-date_higher_awareness_march_1 <- as.POSIXct("2020-03-01")
-
-# Date the UK went into lockdown
-date_uk_lockdown_march_23 <- as.POSIXct("2020-03-23")
+```{r Save four cohorts as rds file}
+saveRDS(object = dat, file = paste0(data_path, "/four_cohorts.rds"))
 ```
-
-```{r Prepandemic definitions january_31}
-if(GLAD == TRUE | EDGI == TRUE){
-dat <- dat %>%
-  mutate(
-    prepandemic_january_31_numeric =
-      if_else(
-        startDate.prepandemic > date_first_case_uk_january_31, # The GLAD sign up is dated before the cut off (> longer ago)
-        true = 0, # Participant has not signed up before the pandemic,
-        false = 1, # Participant has signed up before the pandemic,
-        missing = NA_real_
-      )
-  )
-
-dat <- dat %>%
-  mutate(
-    prepandemic_january_31 =
-      recode_factor(
-        prepandemic_january_31_numeric,
-        "0" = "Sign up after 31. January",
-        "1" = "Sign up before 31. January"
-      )
-  )
-
-dat %>%
-  freq(prepandemic_january_31)
-}
-```
-
-```{r Prepandemic definitions march_1}
-if(GLAD == TRUE | EDGI == TRUE){
-dat <- dat %>%
-  mutate(
-    prepandemic_march_1_numeric =
-      if_else(
-        startDate.prepandemic > date_higher_awareness_march_1, # The GLAD sign up is dated before the cut off (> longer ago)
-        true = 0, # Participant has not signed up before the pandemic,
-        false = 1, # Participant has signed up before the pandemic,
-        missing = NA_real_
-      )
-  )
-
-dat <- dat %>%
-  mutate(
-    prepandemic_march_1 =
-      recode_factor(
-        prepandemic_march_1_numeric,
-        "0" = "Sign up after 1. March",
-        "1" = "Sign up before 1. March"
-      )
-  )
-
-dat %>%
-  freq(prepandemic_march_1)
-}
-```
-
-```{r Prepandemic definitions march_23}
-if(GLAD == TRUE | EDGI == TRUE){
-dat <- dat %>%
-  mutate(
-    prepandemic_march_23_numeric =
-      if_else(
-        startDate.prepandemic > date_uk_lockdown_march_23, # The GLAD sign up is dated before the cut off (> longer ago)
-        true = 0, # Participant has not signed up before the pandemic,
-        false = 1, # Participant has signed up before the pandemic,
-        missing = NA_real_
-      )
-  )
-
-dat <- dat %>%
-  mutate(
-    prepandemic_march_23 =
-      recode_factor(
-        prepandemic_march_23_numeric,
-        "0" = "Sign up after 23. March",
-        "1" = "Sign up before 23. March"
-      )
-  )
-
-dat %>%
-  freq(prepandemic_march_23)
-}
-```
-
-Calculate the time difference between time difference between sign up questionnaire and COPING questionnaire
-```{r time difference between sign up questionnaire and COPING questionnaire}
-if(GLAD == TRUE | EDGI == TRUE){
-dat <- dat %>%
-  mutate(
-    time_diff_sign_up_coping =
-        as.numeric(
-        difftime(           #this function does time1 - time2 as difftime(time1, time2...)
-          startDate.coping,    #should be start date for COPING (time1)
-          startDate.prepandemic),    #should be start date for GLAD (time2)
-          units = c("days")  #can also be "secs", "mins", "hours", "weeks"
-          )
-        )
-
-dat %>%
-  descr(
-    var = time_diff_sign_up_coping,
-    stats = "common"
-    )
-}
-```
-
-Proportion of people signed up over one year ago
-```{r glad/edgi ppts signed up over one year ago, eval=FALSE, include=FALSE}
-if(GLAD == TRUE | EDGI == TRUE){
-dat <- dat %>%
-  mutate(
-    over_one_year_time_diff_sign_up_coping_numeric =
-      as.numeric(
-        if_else(time_diff_sign_up_coping > 365, 1, 0
-                )
-      )
-  )
-
-dat <- dat %>%
-  mutate(
-    over_one_year_time_diff_sign_up_coping =
-      recode_factor(
-        over_one_year_time_diff_sign_up_coping_numeric,
-        "0" = "Sign up under one year before COPING",
-        "1" = "Sign up over one year before COPING"
-      )
-  )
-
-dat %>%
-  freq(over_one_year_time_diff_sign_up_coping, cumul = F)
-}
-```
-
-Proportion of people signed up over half a year ago
-```{r glad/edgi ppts signed up over half a year ago, r eval=FALSE, include=FALSE}
-if(GLAD == TRUE | EDGI == TRUE){
-dat <- dat %>%
-  mutate(
-    over_half_a_year_time_diff_sign_up_coping_numeric =
-      as.numeric(
-        if_else(time_diff_sign_up_coping > 182.5, 1, 0
-                )
-      )
-  )
-
-dat <- dat %>%
-  mutate(
-    over_half_a_year_time_diff_sign_up_coping =
-      recode_factor(
-        over_half_a_year_time_diff_sign_up_coping_numeric,
-        "0" = "Sign up under half a year before COPING",
-        "1" = "Sign up over half a year before COPING"
-      )
-  )
-
-dat %>%
-  freq(over_half_a_year_time_diff_sign_up_coping, cumul = F)
-}
-```
-
-#Total score comparison between PHQ, PCL and GAD, prepandemic, retrospecive and baseline
-PHQ difference scores
-```{r phq difference scores}
-if(GLAD == TRUE | EDGI == TRUE){
-# Difference score for prepandemic and retrospective phq sum scores
-dat <- dat %>%
-  mutate(
-    phq.diff_score_prepan_retro =
-      as.numeric(
-        phq.sum_score_prepan - phq.sum_score_retro  # retrospective sum score MINUS prepandemic sum score 
-      )
-  )
-
-summary(dat$phq.diff_score_prepan_retro)
-
-# Difference score for prepandemic and baseline phq sum scores
-dat <- dat %>%
-  mutate(
-    phq.diff_score_prepan_base =
-      as.numeric(
-        phq.sum_score_base - phq.sum_score_prepan  # baseline sum score MINUS prepandemic sum score 
-      )
-  )
-
-summary(dat$phq.diff_score_prepan_base)
-}
-
-# Difference score for retrospective and baseline phq sum scores
-dat <- dat %>%
-  mutate(
-    phq.diff_score_base_retro =
-      as.numeric(
-        phq.sum_score_base - phq.sum_score_retro  # baseline sum score MINUS retrospective sum score 
-      )
-  )
-
-summary(dat$phq.diff_score_base_retro)
-
-```
-
-GAD difference scores
-```{r gad difference scores}
-if(GLAD == TRUE | EDGI == TRUE){
-# Difference score for prepandemic and retrospective gad sum scores
-dat <- dat %>%
-  mutate(
-    gad.diff_score_prepan_retro =
-      as.numeric(
-        gad.sum_score_prepan - gad.sum_score_retro  # retrospective sum score MINUS prepandemic sum score 
-      )
-  )
-
-summary(dat$gad.diff_score_prepan_retro)
-
-# Difference score for prepandemic and baseline gad sum scores
-dat <- dat %>%
-  mutate(
-    gad.diff_score_prepan_base =
-      as.numeric(
-        gad.sum_score_base - gad.sum_score_prepan  # baseline sum score MINUS prepandemic sum score 
-      )
-  )
-
-summary(dat$gad.diff_score_prepan_base)
-}
-
-# Difference score for retrospective and baseline gad sum scores
-dat <- dat %>%
-  mutate(
-    gad.diff_score_base_retro =
-      as.numeric(
-        gad.sum_score_base - gad.sum_score_retro  # baseline sum score MINUS retrospective sum score 
-      )
-  )
-
-summary(dat$gad.diff_score_base_retro)
-
-```
-
-PCL difference scores
-NOTE: Only computed baseline and prepandemic differences as the retro account here isn't actually retrospective, but whether the reported baseline scores are due to the pandemic. 
-```{r pcl difference scores}
-if(GLAD == TRUE | EDGI == TRUE){
-# Difference score for prepandemic and baseline pcl sum scores
-dat <- dat %>%
-  mutate(
-    pcl.diff_score_prepan_base =
-      as.numeric(
-        pcl.sum_score_base - pcl.sum_score_prepan  # baseline sum score MINUS prepandemic sum score 
-      )
-  )
-
-summary(dat$pcl.diff_score_prepan_base)
-}
-```
-
-```{r frequency of those who reported "due to pandemic" in retro PCL}
-summary(dat$pcl.sum_score_retro)
-
-freq(dat$pcl.stressful_experience_repeated_images_retro)
-freq(dat$pcl.stressful_situation_avoiding_activities_retro)
-freq(dat$pcl.feeling_irritable_or_having_angry_outbursts_retro)
-freq(dat$pcl.stressful_experience_upset_reminded_retro)
-freq(dat$pcl.cut_people_feeling_distant_retro)
-freq(dat$pcl.difficulty_concentrating_retro)
-```
-
-OCI-R difference scores
-```{r ocir difference scores}
-if(GLAD == TRUE | EDGI == TRUE){
-# Difference score for prepandemic and retrospective oci-r sum scores
-dat <- dat %>%
-  mutate(
-    ocir.diff_score_prepan_retro =
-      as.numeric(
-        ocir.sum_score_prepan - ocir.sum_score_retro  # retrospective sum score MINUS prepandemic sum score 
-      )
-  )
-
-summary(dat$ocir.diff_score_prepan_retro)
-
-# Difference score for prepandemic and baseline ocir sum scores
-dat <- dat %>%
-  mutate(
-    ocir.diff_score_prepan_base =
-      as.numeric(
-        ocir.sum_score_prepan - ocir.sum_score_base  # prepandemic sum score MINUS baseline sum score 
-      )
-  )
-
-summary(dat$ocir.diff_score_prepan_base)
-}
-# Difference score for retrospective and baseline ocir sum scores
-dat <- dat %>%
-  mutate(
-    ocir.diff_score_base_retro =
-      as.numeric(
-        ocir.sum_score_base - ocir.sum_score_retro  # baseline sum score MINUS retrospective sum score 
-      )
-  )
-
-summary(dat$ocir.diff_score_base_retro)
-
-```
-
-#Data level groups
-Identify which data (prepan, retro and baseline) each participant has.
-```{r glad/edgi data level groups PHQ}
-if(GLAD == TRUE | EDGI == TRUE){
-dat <- dat %>%
-  mutate(
-    data_group_phq_numeric =
-      case_when(
-        na_per_person_phq_base == 0 & na_per_person_phq_prepan == 0 & na_per_person_phq_retro == 0 ~ 5, #all complete baseline, prepan and retro
-        na_per_person_phq_base != 0 & na_per_person_phq_prepan != 0 & na_per_person_phq_retro == 0  ~ 4, #retro data only
-        na_per_person_phq_base == 0 & na_per_person_phq_prepan != 0 & na_per_person_phq_retro != 0  ~ 3, #baseline data only
-        na_per_person_phq_base == 0 & na_per_person_phq_prepan == 0 & na_per_person_phq_retro != 0  ~ 2, #prepan and baseline data only
-        na_per_person_phq_base == 0 & na_per_person_phq_prepan != 0 & na_per_person_phq_retro == 0 ~ 1,  #baseline and retro data only
-        na_per_person_phq_base != 0 & na_per_person_phq_prepan == 0 & na_per_person_phq_retro != 0  ~ 0  #prepan data only
-      )
-  )
-
-dat <- dat %>%
-  mutate(
-    data_group_phq = 
-      recode_factor(
-        data_group_phq_numeric,
-        "0" = "Only prepandemic data",
-        "1" = "Baseline and retrospective data",
-        "2" = "Prepandemic and baseline data",
-        "3" = "Baseline data only",
-        "4" = "Retrospective data only",
-        "5" = "All prepandemic, baseline and retrospective data"
-      )
-  )
-
-table(dat$data_group_phq)
-}
-```
-
-```{r nbr/ramp data level groups PHQ}
-if(NBR == TRUE | RAMP == TRUE){
-dat <- dat %>%
-  mutate(
-    data_group_phq_numeric =
-      case_when(
-#        na_per_person_phq_base == 0 & na_per_person_phq_prepan == 0 & na_per_person_phq_retro == 0 ~ 5, #all complete baseline, prepan and retro
-        na_per_person_phq_base != 0 & na_per_person_phq_retro == 0  ~ 4, #retro data only
-        na_per_person_phq_base == 0 & na_per_person_phq_retro != 0  ~ 3, #baseline data only
-#        na_per_person_phq_base == 0 & na_per_person_phq_prepan == 0 & na_per_person_phq_retro != 0  ~ 2, #prepan and baseline data only
-        na_per_person_phq_base == 0 & na_per_person_phq_retro == 0 ~ 1  #baseline and retro data only
-#        na_per_person_phq_base != 0 & na_per_person_phq_prepan == 0 & na_per_person_phq_retro != 0  ~ 0  #prepan data only
-      )
-  )
-
-dat <- dat %>%
-  mutate(
-    data_group_phq = 
-      recode_factor(
-        data_group_phq_numeric,
-        "0" = "Only prepandemic data",
-        "1" = "Baseline and retrospective data",
-        "2" = "Prepandemic and baseline data",
-        "3" = "Baseline data only",
-        "4" = "Retrospective data only",
-        "5" = "All prepandemic, baseline and retrospective data"
-      )
-  )
-
-table(dat$data_group_phq)
-}
-```
-
-GAD
-```{r glad/edgi data level groups GAD}
-if(GLAD == TRUE | EDGI == TRUE){
-dat <- dat %>%
-  mutate(
-    data_group_gad_numeric =
-      case_when(
-        na_per_person_gad_base == 0 & na_per_person_gad_prepan == 0 & na_per_person_gad_retro == 0 ~ 5, #all complete baseline, prepan and retro
-        na_per_person_gad_base != 0 & na_per_person_gad_prepan != 0 & na_per_person_gad_retro == 0  ~ 4, #retro data only
-        na_per_person_gad_base == 0 & na_per_person_gad_prepan != 0 & na_per_person_gad_retro != 0  ~ 3, #baseline data only
-        na_per_person_gad_base == 0 & na_per_person_gad_prepan == 0 & na_per_person_gad_retro != 0  ~ 2, #prepan and baseline data only
-        na_per_person_gad_base == 0 & na_per_person_gad_prepan != 0 & na_per_person_gad_retro == 0 ~ 1,  #baseline and retro data only
-        na_per_person_gad_base != 0 & na_per_person_gad_prepan == 0 & na_per_person_gad_retro != 0  ~ 0  #prepan data only
-      )
-  )
-
-dat <- dat %>%
-  mutate(
-    data_group_gad = 
-      recode_factor(
-        data_group_gad_numeric,
-        "0" = "Only prepandemic data",
-        "1" = "Baseline and retrospective data",
-        "2" = "Prepandemic and baseline data",
-        "3" = "Baseline data only",
-        "4" = "Retrospective data only",
-        "5" = "All prepandemic, baseline and retrospective data"
-      )
-  )
-
-table(dat$data_group_gad)
-}
-```
-
-```{r nbr/ramp data level groups GAD}
-if(NBR == TRUE | RAMP == TRUE){
-dat <- dat %>%
-  mutate(
-    data_group_gad_numeric =
-      case_when(
-#        na_per_person_gad_base == 0 & na_per_person_gad_prepan == 0 & na_per_person_gad_retro == 0 ~ 5, #all complete baseline, prepan and retro
-        na_per_person_gad_base != 0 & na_per_person_gad_retro == 0  ~ 4, #retro data only
-        na_per_person_gad_base == 0 & na_per_person_gad_retro != 0  ~ 3, #baseline data only
-#        na_per_person_gad_base == 0 & na_per_person_gad_prepan == 0 & na_per_person_gad_retro != 0  ~ 2, #prepan and baseline data only
-        na_per_person_gad_base == 0 & na_per_person_gad_retro == 0 ~ 1  #baseline and retro data only
-#        na_per_person_gad_base != 0 & na_per_person_gad_prepan == 0 & na_per_person_gad_retro != 0  ~ 0  #prepan data only
-      )
-  )
-
-dat <- dat %>%
-  mutate(
-    data_group_gad = 
-      recode_factor(
-        data_group_gad_numeric,
-        "0" = "Only prepandemic data",
-        "1" = "Baseline and retrospective data",
-        "2" = "Prepandemic and baseline data",
-        "3" = "Baseline data only",
-        "4" = "Retrospective data only",
-        "5" = "All prepandemic, baseline and retrospective data"
-      )
-  )
-
-table(dat$data_group_gad)
-}
-```
-
-PCL
-```{r glad/edgi data level groups PCL}
-if(GLAD == TRUE | EDGI == TRUE){
-dat <- dat %>%
-  mutate(
-    data_group_pcl_numeric =
-      case_when(
-        na_per_person_pcl_base == 0 & na_per_person_pcl_prepan == 0 & na_per_person_pcl_retro == 0 ~ 5, #all complete baseline, prepan and retro
-        na_per_person_pcl_base != 0 & na_per_person_pcl_prepan != 0 & na_per_person_pcl_retro == 0  ~ 4, #retro data only
-        na_per_person_pcl_base == 0 & na_per_person_pcl_prepan != 0 & na_per_person_pcl_retro != 0  ~ 3, #baseline data only
-        na_per_person_pcl_base == 0 & na_per_person_pcl_prepan == 0 & na_per_person_pcl_retro != 0  ~ 2, #prepan and baseline data only
-        na_per_person_pcl_base == 0 & na_per_person_pcl_prepan != 0 & na_per_person_pcl_retro == 0 ~ 1,  #baseline and retro data only
-        na_per_person_pcl_base != 0 & na_per_person_pcl_prepan == 0 & na_per_person_pcl_retro != 0  ~ 0  #prepan data only
-      )
-  )
-
-dat <- dat %>%
-  mutate(
-    data_group_pcl = 
-      recode_factor(
-        data_group_pcl_numeric,
-        "0" = "Only prepandemic data",
-        "1" = "Baseline and retrospective data",
-        "2" = "Prepandemic and baseline data",
-        "3" = "Baseline data only",
-        "4" = "Retrospective data only",
-        "5" = "All prepandemic, baseline and retrospective data"
-      )
-  )
-
-table(dat$data_group_pcl)
-}
-```
-
-```{r nbr/ramp data level groups PCL}
-if(NBR == TRUE | RAMP == TRUE){
-dat <- dat %>%
-  mutate(
-    data_group_pcl_numeric =
-      case_when(
-#        na_per_person_pcl_base == 0 & na_per_person_pcl_prepan == 0 & na_per_person_pcl_retro == 0 ~ 5, #all complete baseline, prepan and retro
-        na_per_person_pcl_base != 0 & na_per_person_pcl_retro == 0  ~ 4, #retro data only
-        na_per_person_pcl_base == 0 & na_per_person_pcl_retro != 0  ~ 3, #baseline data only
-#        na_per_person_pcl_base == 0 & na_per_person_pcl_prepan == 0 & na_per_person_pcl_retro != 0  ~ 2, #prepan and baseline data only
-        na_per_person_pcl_base == 0 & na_per_person_pcl_retro == 0 ~ 1  #baseline and retro data only
-#        na_per_person_pcl_base != 0 & na_per_person_pcl_prepan == 0 & na_per_person_pcl_retro != 0  ~ 0  #prepan data only
-      )
-  )
-
-dat <- dat %>%
-  mutate(
-    data_group_pcl = 
-      recode_factor(
-        data_group_pcl_numeric,
-        "0" = "Only prepandemic data",
-        "1" = "Baseline and retrospective data",
-        "2" = "Prepandemic and baseline data",
-        "3" = "Baseline data only",
-        "4" = "Retrospective data only",
-        "5" = "All prepandemic, baseline and retrospective data"
-      )
-  )
-
-table(dat$data_group_pcl)
-}
-```
-
-#Read in respiratory data
-
-## GLAD respiratory
-```{r glad coping respiratory cols}
-if(GLAD == TRUE){
-coping.glad.respiratory.raw <- readRDS(file = paste0(data.raw_path, "/glad/respiratory_coping_glad.rds"))
-dim(coping.glad.respiratory.raw)
-colnames(coping.glad.respiratory.raw)
-}
-```
-
-Select respiratory variables
-```{r coping glad respiratory cleaning}
-if(GLAD == TRUE){
-coping.glad.respiratory.raw.id <- coping.glad.respiratory.raw %>%
-  drop_na(externalDataReference) %>% # Drop NAs
-  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
-  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
-  mutate(ID = as.numeric(ID)) %>%
-  select(
-    Sample, # Sample
-    ID, # ID
-    respiratory.breath_diarrhoea_fatigue_fever,
-    respiratory.worst_ill_feel,
-    respiratory.persistent_cough,
-    respiratory.skipping_meals_because_you_felt_unwell,
-    respiratory.was_your_sense_of_smell_impaired,
-    respiratory.was_your_sense_of_taste_impaired,
-    respiratory.feeling_tiredfatigued,
-    respiratory.throat_swab_coronavirus_nose,
-    respiratory.throat_swab_test_nose,
-    respiratory.coronavirus_antibody_test,
-    respiratory.results_antibody_test
-  ) %>%
-  add_numeric(., exclude = exclude_cols) %>%
-  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
-  mutate_if(is.numeric, ~na_if(., -99)) %>%
-  mutate_if(is.numeric, ~na_if(., -77)) %>%
-  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
-  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
-
-# Inspect dimensions
-dim(coping.glad.respiratory.raw.id)
-# Inspect colnames
-colnames(coping.glad.respiratory.raw.id)
-#Differences
-dim(coping.glad.respiratory.raw)[1]-dim(coping.glad.respiratory.raw.id)[1]
-}
-```
-
-```{r coping glad respiratory copy}
-if(GLAD == TRUE){
-respiratory.raw.id <- coping.glad.respiratory.raw.id
-}
-```
-
-## EDGI respiratory
-```{r edgi coping respiratory cols}
-if(EDGI == TRUE){
-coping.edgi.respiratory.raw <- readRDS(file = paste0(data.raw_path, "/edgi/respiratory_coping_edgi.rds"))
-dim(coping.edgi.respiratory.raw)
-colnames(coping.edgi.respiratory.raw)
-}
-```
-
-Select respiratory variables
-```{r coping edgi respiratory cleaning}
-if(EDGI == TRUE){
-coping.edgi.respiratory.raw.id <- coping.edgi.respiratory.raw %>%
-  drop_na(externalDataReference) %>% # Drop NAs
-  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
-  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
-  mutate(ID = as.numeric(ID)) %>%
-  select(
-    Sample, # Sample
-    ID, # ID
-    respiratory.breath_diarrhoea_fatigue_fever,
-    respiratory.worst_ill_feel,
-    respiratory.persistent_cough,
-    respiratory.skipping_meals_because_you_felt_unwell,
-    respiratory.was_your_sense_of_smell_impaired,
-    respiratory.was_your_sense_of_taste_impaired,
-    respiratory.feeling_tiredfatigued,
-    respiratory.throat_swab_coronavirus_nose,
-    respiratory.throat_swab_test_nose,
-    respiratory.coronavirus_antibody_test,
-    respiratory.results_antibody_test
-  ) %>%
-  add_numeric(., exclude = exclude_cols) %>%
-  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
-  mutate_if(is.numeric, ~na_if(., -99)) %>%
-  mutate_if(is.numeric, ~na_if(., -77)) %>%
-  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
-  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
-
-# Inspect dimensions
-dim(coping.edgi.respiratory.raw.id)
-# Inspect colnames
-colnames(coping.edgi.respiratory.raw.id)
-#Differences
-dim(coping.edgi.respiratory.raw)[1]-dim(coping.edgi.respiratory.raw.id)[1]
-}
-```
-
-```{r coping edgi respiratory copy}
-if(EDGI == TRUE){
-respiratory.raw.id <- coping.edgi.respiratory.raw.id
-}
-```
-
-## NBR respiratory
-```{r nbr coping respiratory cols}
-if(NBR == TRUE){
-coping.nbr.respiratory.raw <- readRDS(file = paste0(data.raw_path, "/nbr/respiratory_coping_nbr.rds"))
-dim(coping.nbr.respiratory.raw)
-colnames(coping.nbr.respiratory.raw)
-}
-```
-
-Select respiratory variables
-```{r coping nbr respiratory cleaning}
-if(NBR == TRUE){
-coping.nbr.respiratory.raw.id <- coping.nbr.respiratory.raw %>%
-  drop_na(subjectid) %>% # Drop NAs
-  distinct(subjectid, .keep_all = TRUE) %>% # Remove duplicates based on ID
-  separate(subjectid, into = c("Sample", "ID.intm"), sep = 6) %>% # Split ID in Sample and Number
-  separate(ID.intm, into = "ID", sep = 7) %>%
-  mutate(ID = as.numeric(ID)) %>%
-  select(
-    Sample, # Sample
-    ID, # ID
-    respiratory.breath_diarrhoea_fatigue_fever = respiratory.unusual_shortness_breath_diarrhoea,
-    respiratory.worst_ill_feel,
-    respiratory.persistent_cough,
-    respiratory.skipping_meals_because_you_felt_unwell,
-    respiratory.was_your_sense_of_smell_impaired,
-    respiratory.was_your_sense_of_taste_impaired,
-    respiratory.feeling_tiredfatigued,
-    respiratory.throat_swab_coronavirus_nose,
-    respiratory.throat_swab_test_nose,
-    respiratory.coronavirus_antibody_test,
-    respiratory.results_antibody_test
-  ) %>%
-  add_numeric(., exclude = exclude_cols) %>%
-  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
-  mutate_if(is.numeric, ~na_if(., -99)) %>%
-  mutate_if(is.numeric, ~na_if(., -77)) %>%
-  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
-  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
-
-# Inspect dimensions
-dim(coping.nbr.respiratory.raw.id)
-# Inspect colnames
-colnames(coping.nbr.respiratory.raw.id)
-#Differences
-dim(coping.nbr.respiratory.raw)[1]-dim(coping.nbr.respiratory.raw.id)[1]
-}
-```
-
-```{r coping nbr respiratory copy}
-if(NBR == TRUE){
-respiratory.raw.id <- coping.nbr.respiratory.raw.id
-}
-```
-
-## RAMP respiratory
-```{r ramp coping respiratory cols}
-if(RAMP == TRUE){
-ramp.respiratory.raw <- readRDS(file = paste0(data.raw_path, "/ramp/respiratory_ramp.rds"))
-dim(ramp.respiratory.raw)
-colnames(ramp.respiratory.raw)
-}
-```
-
-Select respiratory variables
-```{r coping ramp respiratory cleaning}
-if(RAMP == TRUE){
-ramp.respiratory.raw.id <- ramp.respiratory.raw %>%
-  drop_na(`Login ID`) %>% # Drop NAs
-  distinct(`Login ID`, .keep_all = TRUE) %>% # Remove duplicates based on ID
-  separate(`Login ID`, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
-  mutate(ID = as.numeric(ID)) %>%
-  select(
-    Sample, # Sample
-    ID, # ID
-    respiratory.breath_diarrhoea_fatigue_fever = respiratory.experienced_symptoms_unusual_shortness,
-    respiratory.worst_ill_feel,
-    respiratory.persistent_cough,
-    respiratory.skipping_meals_because_you_felt_unwell,
-    respiratory.was_your_sense_of_smell_impaired = respiratory.smell_impaired_sense_weeks,
-    respiratory.was_your_sense_of_taste_impaired = respiratory.taste_impaired_sense_weeks,
-    respiratory.feeling_tiredfatigued,
-    respiratory.throat_swab_coronavirus_nose,
-    respiratory.throat_swab_test_nose,
-    respiratory.coronavirus_week_antibody_test,
-    respiratory.results_antibody_test
-  ) %>%
-  add_numeric(., exclude = exclude_cols) %>%
-  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
-  mutate_if(is.numeric, ~na_if(., -99)) %>%
-  mutate_if(is.numeric, ~na_if(., -77)) %>%
-  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
-  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
-
-# Inspect dimensions
-dim(ramp.respiratory.raw.id)
-# Inspect colnames
-colnames(ramp.respiratory.raw.id)
-#Differences
-dim(ramp.respiratory.raw)[1]-dim(ramp.respiratory.raw.id)[1]
-}
-```
-
-```{r ramp respiratory copy}
-if(RAMP == TRUE){
-respiratory.raw.id <- ramp.respiratory.raw.id
-}
-```
-
-#Distribution of likert scale COVID-19 symptoms in COPING
-```{r distribution of COVID symptoms}
-#persistent cough
-respiratory.raw.id %>%
-  ggplot(
-    mapping = aes(
-      y = respiratory.persistent_cough_numeric 
-    )
-  ) +
-  geom_bar() +
-  labs(
-    title = "Persistant cough"
-  )
-
-#severe fatigue
-respiratory.raw.id %>%
-  ggplot(
-    mapping = aes(
-        y = respiratory.feeling_tiredfatigued_numeric 
-    )
-  ) +
-  geom_bar() +
-  labs(
-    title = "Severe fatigue"
-  )
-
-#skipped meals
-respiratory.raw.id %>%
-  ggplot(
-    mapping = aes(
-        y = respiratory.skipping_meals_because_you_felt_unwell_numeric
-    )
-  ) +
-  geom_bar() +
-  labs(
-    title = "Skipped meals"
-  )
-
-```
-
-#Choosing cut-offs for the likert scale symptoms of "no symptoms", "mild symptoms", "moderate symptoms" and "severe symptoms" for the fatigue, persistent cough and skipped meals variables. 
-Coding:
-0 = No symptoms
-1 = Mild symptoms
-2 = Moderate symptoms
-3 = Severe symptoms
-
-Results:
-Persistent cough: "Mild symptoms" as cut off
-Fatigue: "Severe symptoms" as cut off
-Skipped meals: "Moderate symptoms" as cut off
-```{r proportion of people who report COVID symptoms in Menni et al}
-#persistent cough
-percentage_pcough <- ((0.5673*6452) + (0.4556*9186) + (0.3017*2434931))/(6452+9186+2434931)
-percentage_pcough    # 0.3029762% of Menni et al(2020) have fatigue
-quantile(x = respiratory.raw.id$respiratory.persistent_cough_numeric, 
-         na.rm = TRUE, 
-         probs = 1-percentage_pcough) # this gives 0.3029762% of the sample reporting fatigue when using the "mild symptoms" persistent cough response
-
-#fatigue
-percentage_fatigue <- ((0.298*6452) + (0.1556*9186) + (0.0871*2434931))/(6452+9186+2434931) 
-percentage_fatigue   # 0.08791204% of Menni et al(2020) have fatigue
-quantile(x = respiratory.raw.id$respiratory.feeling_tiredfatigued_numeric, 
-         na.rm = TRUE, 
-         probs = 1-percentage_fatigue) #this gives 8% of the sample reporting fatigue when using the "severe symptoms" fatigue response
-
-#skipped meals 
-percentage_skipped_meals <- ((0.4203*6452) + (0.2493*9186) + (0.1912*2434931))/(6452+9186+2434931) 
-percentage_skipped_meals    # 0.192021% of Menni et al(2020) have fatigue
-quantile(x = respiratory.raw.id$respiratory.skipping_meals_because_you_felt_unwell_numeric, 
-         na.rm = TRUE, 
-         probs = 1-percentage_skipped_meals) # this gives 0.192021% of the sample reporting fatigue when using the "moderate symptoms" persistent cough response
-```
-
-Creating binary groups for COVID symptoms
-```{r creating binary groups for COVID symptoms}
-#loss or smell or taste
-respiratory.raw.id <- respiratory.raw.id %>%
-  mutate(
-    respiratory.anosmia_binary =
-      if_else(
-        respiratory.was_your_sense_of_smell_impaired_numeric == 1 | respiratory.was_your_sense_of_taste_impaired_numeric == 1, 
-        1,
-        0
-      )
-  )
-
-#persistent cough
-respiratory.raw.id <- respiratory.raw.id %>%
-  mutate(
-    respiratory.pcough_binary =
-      if_else(
-        respiratory.persistent_cough_numeric >= 1, #those who score 1 or above (mild or above)
-        1,
-        0
-      )
-  )
-
-#fatigue
-respiratory.raw.id <- respiratory.raw.id %>%
-  mutate(
-    respiratory.fatigue_binary =
-      if_else(
-        respiratory.feeling_tiredfatigued_numeric >= 3, #those who score 3 (severe symptoms)
-        1,
-        0
-      )
-  )
-
-#skipped meals
-respiratory.raw.id <- respiratory.raw.id %>%
-  mutate(
-    respiratory.skipped_meals_binary =
-      if_else(
-        respiratory.skipping_meals_because_you_felt_unwell_numeric >= 2,
-        1,
-        0
-      )
-  )
-```
-
-Frequencies of binary COVID symptoms
-```{r frequencies of COVID binary symptoms}
-freq(respiratory.raw.id$respiratory.anosmia_binary)
-freq(respiratory.raw.id$respiratory.pcough_binary)
-freq(respiratory.raw.id$respiratory.fatigue_binary)
-freq(respiratory.raw.id$respiratory.skipped_meals_binary)
-```
-
-Rename respiratory dataset joined to main dataset
-
-```{r clean respiratory dataset}
-respiratory <- respiratory.raw.id
-
-dat.coping <- left_join(
-  x = dat,
-  y = respiratory,
-  by = "ID"
-)
-```
-
-# Probable COVID-19 case identification
-
-Algorithm from Menni et al. to identify probable COVID-19
-Variables required:
-- Sex: 	0 Female, 1 Male
-- Other binary variables: 0 No, 1 Yes       
-- "respiratory.anosmia_binary": loss of smell or taste  
-- "respiratory.pcough_binary":	Persistent cough
-- "respiratory.fatigue_binary": Severe fatigue
-- "respiratory.skipped_meals_binary": Skipped meals
-
-The COVID prediction model has coded the sexes opposite to our data set
-```{r create numeric sex variable with male=1}
-if(GLAD == TRUE | NBR == TRUE | EDGI == TRUE){
-dat.coping <- dat.coping %>%
-  mutate(
-    Sex_respiratory =
-      if_else(
-        Sex == "Male",
-        true = 1,
-        false = 0,
-        missing = NA_real_
-      )
-  )
-}
-```
-
-Sex is no available in the RAMP dataset, therefore a proxy sex variable is created whereby Gender = Male and Transgender = No. 
-```{r create numeric sex variable with male=1 for ramp}
-if(RAMP == TRUE){
-dat.coping <- dat.coping %>%
-  mutate(
-    Sex_respiratory =
-      if_else(
-        Gender == "Male" &
-        Transgender_uncleaned == "No",
-        true = 1,
-        false = 0,
-        missing = NA_real_
-      )
-  )
-}
-```
-
-Age is not available in RAMP, only categorical age. We will assign each individual the middle value of each age category. 
-```{r create age - proxy variable for ramp}
-if(RAMP == TRUE){
-dat.coping <- dat.coping %>%
-  mutate(
-    Age =
-      case_when(
-        age_category_full == "16-18" ~ 17,
-        age_category_full == "19-25" ~ 22,
-        age_category_full == "26-35" ~ 30.5,
-        age_category_full == "36-45" ~ 40.5,
-        age_category_full == "46-55" ~ 50.5,
-        age_category_full == "56-65" ~ 60.5,
-        age_category_full == "66-70" ~ 68,
-        age_category_full == "71-75" ~ 73,
-        age_category_full == "76-80" ~ 78,
-        age_category_full == "81-85" ~ 83,
-        age_category_full == "86-90" ~ 88,
-        age_category_full == "91-100" ~ 93,
-      age_category_full == "100+" ~ 100
-      )
-  )
-}
-```
-
-```{r how many people experinced all symptoms}
-dat.coping <- dat.coping %>%
-  mutate(
-    covid_symptoms =
-      if_else(
-          !is.na(respiratory.anosmia_binary) &
-          !is.na(respiratory.pcough_binary) &
-          !is.na(respiratory.fatigue_binary) &
-          !is.na(respiratory.skipped_meals_binary),
-        1,
-        0
-       )
-  )
-
-dat.coping %>%
-  freq(covid_symptoms, cumul = F)
-```
-
-#COVID prediction model
-```{r COVID prediction model}
-# linear model of covid symptoms
-dat.coping <- dat.coping %>%
-		  mutate(
-		    covid_probability = 
-		      (-1.32) - 
-		      (0.01*Age) + 
-		      (0.44*Sex_respiratory) + 
-		      (1.75*respiratory.anosmia_binary) + 
-		      (0.31*respiratory.pcough_binary) +  
-		      (0.49*respiratory.fatigue_binary) +  
-		      (0.39*respiratory.skipped_meals_binary) 
-		         )
-
-# Calcualte the odds ratios 
-dat.coping <- dat.coping %>%
-  mutate(
-    covid_odds_ratio = 
-      (exp(covid_probability) / (1 + exp(covid_probability)))
-  )
-
-# generate binary cutt off variable for risk of COVID 
-dat.coping <- dat.coping %>%
-		  mutate(
-		    covid_odds_ratio_50_numeric = 
-		      case_when(
-		        covid_odds_ratio >= 0 & covid_odds_ratio < 0.5 ~ "0", #cut off at 0.5 
-		        covid_odds_ratio >= 0.5 & covid_odds_ratio <= 1 ~ "1"
-		      )
-		  )
-
-#create factor with labels
-dat.coping <- dat.coping %>%
-  mutate(
-    covid_odds_ratio_50 =
-      recode_factor(
-        covid_odds_ratio_50_numeric,
-        "0" = "No COVID",
-        "1" = "Probable COVID"
-      )
-  )
-
-#frequency table for covid variables 
-covid_variables <- c("covid_odds_ratio",
-                      "covid_probability"
-                    )
-
-descr(x = dat.coping[,covid_variables],
-      round.digits = 2,
-      transpose = TRUE)
-
-## looking at cases over 0.5
-freq(dat.coping$covid_odds_ratio_50, 
-     cumul = FALSE)
-
-```
-
-Probable COVID case including the routing question
-```{r recoding probable covid to account for screening question}
-dat.coping <- dat.coping %>%
-  mutate(
-    covid_probable_case_incl_screening_numeric =
-      case_when(
-        respiratory.breath_diarrhoea_fatigue_fever_numeric == 0 ~ 0,
-        covid_odds_ratio_50_numeric == 0 ~ 0,
-        covid_odds_ratio_50_numeric == 1 ~ 1
-      )
-  )
-
-#create factor with labels
-dat.coping <- dat.coping %>%
-  mutate(
-    covid_probable_case_incl_screening =
-      recode_factor(
-        covid_probable_case_incl_screening_numeric,
-        "0" = "No COVID",
-        "1" = "Probable COVID"
-      )
-  )
-
-dat.coping %>%
-  freq(covid_probable_case_incl_screening, 
-     cumul = FALSE) 
-```

### 2020-08-17 PANCHANGE_data_preprocessing2020-07-15.Rmd

@@
 toc: yes
-
-params:
-  glad.dem.raw: edgi.dem.raw
-
 ---
@@
 ```{r Specify cohort}
-GLAD = TRUE
-EDGI = FALSE
+GLAD = FALSE
+EDGI = TRUE
 NBR = FALSE
@@
     ID, # ID
-    respiratory.breath_diarrhoea_fatigue_fever,
+    respiratory.breath_diarrhoea_fatigue_fever = respiratory.unusual_shortness_breath_diarrhoea,
     respiratory.worst_ill_feel,

### 2020-08-17 PANCHANGE_data_preprocessing2020-07-15.Rmd
add the employmen to the data merging

@@
   dem.raw.id,
+  employment.raw.id,
+  mhd.raw.categories,
   prepan.gad.raw.id,
-  mhd.raw.categories,
-  prepan.ocir.raw.id,
   prepan.pcl.raw.id,
   prepan.phq.raw.id,
+  prepan.ocir.raw.id,
   coping.gad.raw.id,

### 2020-08-17 PANCHANGE_data_preprocessing2020-07-15.Rmd
fix exclusion cols in ramp

@@
     ) %>%
-    add_numeric(., exclude = exclude_cols_coping_ramp) %>%
+    add_numeric(., exclude = exclude_cols_ramp) %>%
     mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables

### 2020-08-17 PANCHANGE_data_merging.Rmd
changes to merging script

@@
 glad <- read_rds(path = paste0(data_path, "/glad.rds"))
+dim(glad)
 
 edgi <- read_rds(path = paste0(data_path, "/edgi.rds"))
+dim(edgi)
 
 nbr <- read_rds(path = paste0(data_path, "/nbr.rds"))
+dim(nbr)
 
 ramp <- read_rds(path = paste0(data_path, "/ramp.rds"))
+dim(ramp)
 ```
@@
 ```{r glad/edgi data frame list}
-dfs.list <- list(
+dat <- bind_rows(
   glad,
@@
 
-```{r Join all questionnaires}
-dat <- plyr::join_all(
-  dfs.list,
-  by = c("ID", "Sample") # Alternatively you can join by several columns EDGI -> "Age", "Sex", "Birthyear"
-  )
-
+```{r Skim data}
 #look at the data

### 2020-08-17 PANCHANGE_data_preprocessing2020-07-15.Rmd
changes to merging script
NA changes to be able to row_bind

@@
     personality_cluster_a_numeric = NA_real_,
-    personality_cluster_a = NA_real_,
+    personality_cluster_a = NA_character_,
     personality_cluster_b_numeric = NA_real_,
-    personality_cluster_b = NA_real_,
+    personality_cluster_b = NA_character_,
     personality_cluster_c_numeric = NA_real_,
-    personality_cluster_c = NA_real_    
+    personality_cluster_c = NA_character_
   )

### 2020-08-18 PANCHANGE_data_preprocessing2020-07-15.Rmd
changed start date

--- 2020-08-17 PANCHANGE_data_preprocessing2020-07-15.Rmd
@@
     "ID",
-    "startDate.ramp"
+    "startDate.coping"
   )
@@
       ID, # ID
-      startDate.ramp = startDate, # Rename startDate
+      startDate.coping = startDate, # Rename startDate
       gad.problems_made_difficult_care = gad.issues_made_carrying_daily, # Impairment
@@
   dem.raw.id,
-  employment.raw.id,
+  prepan.gad.raw.id,
   mhd.raw.categories,
-  prepan.gad.raw.id,
+  prepan.ocir.raw.id,
   prepan.pcl.raw.id,
   prepan.phq.raw.id,
-  prepan.ocir.raw.id,
   coping.gad.raw.id,

### 2020-08-18 PANCHANGE_analysis.Rmd
created analysis script

--- 2020-08-18 PANCHANGE_data_preprocessing2020-07-15.Rmd
@@
 ---
-title: "PANCHANGE_data_preprocessing"
+title: "PANCHANGE_analysis"
 author: "Katie Thompson, Topher Huebel, Molly Davies, Kirstin Purves"
@@
 
-This is the preprocessing script to prepare the data to run analyses for the project "Anxiety, depression and trauma symptom change during the COVID-19 pandemic: retrospective versus objective assessment" - Young et al (2020)
+This is the analysis script to prepare the data to run analyses for the project "Anxiety, depression and trauma symptom change during the COVID-19 pandemic: retrospective versus objective assessment" - Young et al (2020)
 
@@
 date = Sys.Date()
-```
-
-# Specify cohort
-```{r Specify cohort}
-GLAD = FALSE
-EDGI = TRUE
-NBR = FALSE
-RAMP = FALSE
 ```
@@
 
-#Add_numeric function
-Function used to convert character variables into numeric variables. 
-```{r add_numeric function}
-add_numeric <- function(dat, exclude = NULL) {
-  dat_fct <- sjlabelled::as_label(dat)
+# Data import
 
-  dat <- dat[!colnames(dat) %in% exclude]
-  colnames(dat) <- paste(colnames(dat), "numeric", sep = "_")
-  return(bind_cols(dat_fct, dat))
-}
-```
-
-# Data import and merging
-
-Note: GLAD only receives current measures and RAMP questionnaire
-Note: All COPING surveys are separate surveys
-
-# Source data file paths
+## Source data file paths
 
@@
 
-# Demographics
-## GLAD
 ### Read in data
-```{r glad dem cols}
-if(GLAD == TRUE){
-glad.dem.raw <- readRDS(file = paste0(data.raw_path, "/glad/dem_glad.rds"))
-dim(glad.dem.raw)
-colnames(glad.dem.raw)
-}
+```{r read in data}
+dat <- readRDS(file = paste0(data_path, "/four_cohorts.rds"))
+dim(dat)
+colnames(dat)
 ```
 
-### Select variables
-```{r glad dem cleaning}
-if(GLAD == TRUE){
-exclude_cols_dem <- c("ID",
-                  "Sample",
-                  "startDate.prepandemic",
-                  "Age_uncleaned",
-                  "EduYrs")
-
-glad.dem.raw.id <- glad.dem.raw %>%
-  drop_na(externalDataReference) %>% # Drop NAs
-  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
-  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
-  mutate(ID = as.numeric(ID)) %>%
-  select(
-         Sample, # Sample
-         ID, # ID
-         startDate.prepandemic = startDate, #Date when participant signed up to glad
-         Age_uncleaned = demographics.how_old_are_you_now.txt, # Age
-         Gender = demographics.which_gender_do_you_identify_with, # Gender
-         Sex = demographics.select_questionnaire_items_medical, #Sex
-         EduYrs = demographics.school_education_school_years.txt, # Years in education
-         demographics.college_or_university_degree, # level of education - univeristy
-         demographics.a_levelsas_levels_or_equivalent, # level of education - alevel
-         demographics.o_levelsgcses_or_equivalent, # level of education - gcse
-         demographics.cses_or_equivalent, # level of education - cse
-         demographics.nvq_or_hnd_or_hnc_or_equivalent, # level of education - nvq
-         Ethnicity = demographics.questions_based_ethnic_origin # Ethnicity
-         ) %>%
-  add_numeric(., exclude = exclude_cols_dem) %>%
-  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
-  mutate_if(is.numeric, ~na_if(., -99)) %>%
-  mutate_if(is.numeric, ~na_if(., -77)) %>%
-  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
-  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
-
-# Inspect dimensions
-dim(glad.dem.raw.id)
-# Inspect colnames
-colnames(glad.dem.raw.id)
-#Differences
-dim(glad.dem.raw)[1]-dim(glad.dem.raw.id)[1]
-}
-```
-
-```{r glad copy dem}
-if(GLAD == TRUE){
-dem.raw.id <- glad.dem.raw.id
-}
-```
-
-```{r glad dem summary}
-if(GLAD == TRUE) {
+```{r dat.coping summary}
 summarytools::dfSummary(
-  dem.raw.id,
-  graph.col = F,
-  valid.col = F,
-  labels.col = F)
-}
-```
-
-## EDGI
-### Read in data
-```{r edgi dem cols}
-if(EDGI == TRUE){
-  edgi.dem.raw <- readRDS(file = paste0(data.raw_path, "/edgi/dem_edgi.rds"))
-  dim(edgi.dem.raw)
-  colnames(edgi.dem.raw)
-}
-```
-
-### Select variables
-```{r edgi dem cleaning}
-if(EDGI == TRUE){
-  exclude_cols_dem <- c("ID",
-                        "Sample",
-                        "startDate.prepandemic",
-                        "Age_uncleaned",
-                        "EduYrs")
-
-  edgi.dem.raw.id <- edgi.dem.raw %>%
-    drop_na(externalDataReference) %>% # Drop NAs
-    distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
-    separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
-    mutate(ID = as.numeric(ID)) %>%
-    select(
-      Sample, # Sample
-      ID, # ID
-      startDate.prepandemic = startDate, #Date when participant signed up to edgi
-      Age_uncleaned = demographics.how_old_are_you_now.txt, # Age
-      Gender = demographics.what_gender_do_you_identify_with, # Gender (which [GLAD] vs what [EDGI])
-      Sex = demographics.select_questionnaire_items_birth, #Sex (different to GLAD)
-      EduYrs = demographics.university_education_attend_school.txt, # Years in education (different to GLAD)
-      demographics.college_or_university_degree, # level of education - univeristy
-      demographics.a_levelsas_levels_or_equivalent, # level of education - alevel
-      demographics.o_levelsgcses_or_equivalent, # level of education - gcse
-      demographics.cses_or_equivalent, # level of education - cse
-      demographics.nvq_or_hnd_or_hnc_or_equivalent, # level of education - nvq
-      Ethnicity = demographics.what_is_your_ethnic_origin # Ethnicity (different to GLAD)
-    ) %>%
-    add_numeric(., exclude = exclude_cols_dem) %>%
-    mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
-    mutate_if(is.numeric, ~na_if(., -99)) %>%
-    mutate_if(is.numeric, ~na_if(., -77)) %>%
-    mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
-    mutate_if(is.factor, ~na_if(., "Don't know")) %>%
-    mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
-    mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
-    mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
-    mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
-    mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
-    mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
-
-  # Inspect dimensions
-  dim(edgi.dem.raw.id)
-  # Inspect colnames
-  colnames(edgi.dem.raw.id)
-  #Differences
-  dim(edgi.dem.raw)[1]-dim(edgi.dem.raw.id)[1]
-}
-```
-
-```{r edgi copy dem}
-if(EDGI == TRUE){
-  dem.raw.id <- edgi.dem.raw.id
-}
-```
-
-```{r edgi dem summary}
-if(EDGI == TRUE) {
-summarytools::dfSummary(
-  dem.raw.id,
-  graph.col = F,
-  valid.col = F,
-  labels.col = F)
-}
-```
-
-## NBR
-### Read in data
-```{r nbr dem cols}
-if(NBR == TRUE){
-  nbr.dem.raw <- readRDS(file = paste0(data.raw_path, "/nbr/dem_nbr.rds"))
-  dim(nbr.dem.raw)
-  colnames(nbr.dem.raw)
-}
-```
-
-### Select variables
-```{r nbr dem cleaning}
-if(NBR == TRUE){
-  exclude_cols_dem <- c("ID",
-                        "Sample",
-                        "Age_uncleaned",
-                        "EduYrs")
-
-  nbr.dem.raw.id <- nbr.dem.raw %>%
-    drop_na(subjectid) %>% # Drop NAs
-    distinct(subjectid, .keep_all = TRUE) %>% # Remove duplicates based on ID
-    separate(subjectid, into = c("Sample", "ID.intm"), sep = 6) %>% # Split ID in Sample and Number
-    separate(ID.intm, into = "ID", sep = 7) %>%
-    mutate(ID = as.numeric(ID)) %>%
-    select(
-      Sample, # Sample
-      ID, # ID
-#      startDate.coping, # Date when participant signed up to nbr (is in the coping gad chunk)
-#      Age_uncleaned = demographics.how_old_are_you_now.txt, # Age
-      Birthyear_unc = demographics.year, # Birthyear
-      Birthmonth = demographics.month, #Birthmonth
-      Birthday = demographics.day, #Birthday
-      Gender = demographics.which_gender_do_you_identify_with, # Gender
-      Sex = demographics.select_questionnaire_items_medical, #Sex
-#      Ethnicity = demographics.questions_based_ethnic_origin # Ethnicity
-    ) %>%
-    add_numeric(., exclude = exclude_cols_dem) %>%
-    mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
-    mutate_if(is.numeric, ~na_if(., -99)) %>%
-    mutate_if(is.numeric, ~na_if(., -77)) %>%
-    mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
-    mutate_if(is.factor, ~na_if(., "Don't know")) %>%
-    mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
-    mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
-    mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
-    mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
-    mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
-    mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
-
-  # Inspect dimensions
-  dim(nbr.dem.raw.id)
-  # Inspect colnames
-  colnames(nbr.dem.raw.id)
-  #Differences
-  dim(nbr.dem.raw)[1]-dim(nbr.dem.raw.id)[1]
-}
-```
-
-```{r nbr dem calculating age from birthday}
-if(NBR == TRUE) {
-#add 1900 to birthyear
-nbr.dem.raw.id$Birthyear_numeric <- nbr.dem.raw.id$Birthyear_unc_numeric + 1900
-
-#create dob as date format
-nbr.dem.raw.id$Birthdate <- as.Date(paste(nbr.dem.raw.id$Birthyear_numeric,
-                                  nbr.dem.raw.id$Birthmonth_numeric,
-                                  nbr.dem.raw.id$Birthday_numeric,
-                                  sep = "-"))
-
-head(nbr.dem.raw.id$Birthdate)
-
-#Calculate dem.age(remove NAs as it throws an error)
-ages <- age_calc(na.omit(nbr.dem.raw.id$Birthdate), enddate = Sys.Date(), units = "years")
-
-#Create dem.agecolumn
-nbr.dem.raw.id$Age_uncleaned<- NA
-
-#Populate with values (excluding NAs)
-nbr.dem.raw.id$Age_uncleaned[!is.na(nbr.dem.raw.id$Birthdate)] <- ages
-
-#Round age down
-nbr.dem.raw.id$Age_uncleaned <- floor(nbr.dem.raw.id$Age_uncleaned)
-
-#Visualise
-head(nbr.dem.raw.id$Age_uncleaned)
-head(nbr.dem.raw.id$Birthdate)
-}
-```
-
-### Cohort information
-Information on INTERVAL, COMPARE, and STRIDES
-http://www.donorhealth-btru.nihr.ac.uk/studies/
-```{r nbr cohort information}
-if(NBR == TRUE){
-  nbr.cohort.raw <- readxl::read_xlsx(
-    path = paste0(data.raw_path, "/nbr/coping_participants_export_20200730.xlsx")
-    )
-
-  dim(nbr.cohort.raw)
-  colnames(nbr.cohort.raw)
-  }
-```
-
-```{r nbr cohort cleaning}
-if(NBR == TRUE) {
-exclude_cols_cohort_nbr <- c("ID",
-                  "Sample",
-                  "Age_uncleaned",
-                  "EduYrs")
-
-nbr.cohort.raw.id <- nbr.cohort.raw %>%
-  drop_na(`NBR ID`) %>% # Drop NAs
-  distinct(`NBR ID`, .keep_all = TRUE) %>% # Remove duplicates based on ID
-  separate(`NBR ID`, into = c("Sample", "ID.intm"), sep = 6) %>% # Split ID in Sample and Number
-  separate(ID.intm, into = "ID", sep = 7) %>%
-  mutate(
-    ID = as.numeric(ID)) %>%
-  select(
-         Sample, # Sample
-         ID, # ID
-         Cohort = cohort, #cohort information
-#         startDate.coping, #Date when participant signed up to NBR COPING (is in the coping gad chunk)
-#         Age_uncleaned = age, # Age
-#         Gender = gender, # Gender
-#         Sex = demographics.select_questionnaire_items_medical, #Sex
-#         EduYrs = demographics.school_education_school_years.txt, # Years in education
-#         demographics.college_or_university_degree, # level of education - univeristy
-#         demographics.a_levelsas_levels_or_equivalent, # level of education - alevel
-#         demographics.o_levelsgcses_or_equivalent, # level of education - gcse
-#         demographics.cses_or_equivalent, # level of education - cse
-#         demographics.nvq_or_hnd_or_hnc_or_equivalent, # level of education - nvq
-         Ethnicity.unc = ethnicity # Ethnicity
-         ) %>%
-  add_numeric(., exclude = exclude_cols_cohort_nbr) %>%
-  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
-  mutate_if(is.numeric, ~na_if(., -99)) %>%
-  mutate_if(is.numeric, ~na_if(., -77)) %>%
-  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
-  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
-
-# Inspect dimensions
-dim(nbr.cohort.raw.id)
-# Inspect colnames
-colnames(nbr.cohort.raw.id)
-#Differences
-dim(nbr.cohort.raw)[1]-dim(nbr.cohort.raw.id)[1]
-}
-```
-
-```{r nbr cohort recode ethnicity}
-if(NBR == TRUE) {
-#Recode details ethnicity info
-nbr.cohort.raw.id$Ethnicity_full <- recode_factor(nbr.cohort.raw.id$Ethnicity.unc,
-                                             "A" = "White - British",
-                                             "B" = "White - Irish",
-                                             "C" = "White - Other",
-                                             "D" = "Mixed - White & Black Caribbean",
-                                             "E" = "Mixed - White & Black African",
-                                             "F" = "Mixed - White & Asian",
-                                             "G" = "Mixed - Other",
-                                             "H" = "Asian - Indian",
-                                             "J" = "Asian - Pakistani",
-                                             "K" = "Asian - Bangladeshi",
-                                             "L" = "Asian - Other",
-                                             "M" = "Black - Caribbean",
-                                             "N" = "Black - African",
-                                             "P" = "Black - Other",
-                                             "R" = "Chinese - Chinese",
-                                             "S" = "Chinese - Other",
-                                             "W" = NULL, ## Asking NBR what this level means
-                                             "Z" = NULL,
-                                             "99" = NULL)
-
-#Match GLAD/EDGI/RAMP categories
-nbr.cohort.raw.id$Ethnicity <- recode_factor(nbr.cohort.raw.id$Ethnicity.unc,
-                                             "A" = "White, white European or Caucasian",
-                                             "B" = "White, white European or Caucasian",
-                                             "C" = "White, white European or Caucasian",
-                                             "D" = "Mixed or multiple ethnic origins",
-                                             "E" = "Mixed or multiple ethnic origins",
-                                             "F" = "Mixed or multiple ethnic origins",
-                                             "G" = "Mixed or multiple ethnic origins",
-                                             "H" = "Asian or Asian British (including Chinese)",
-                                             "J" = "Asian or Asian British (including Chinese)",
-                                             "K" = "Asian or Asian British (including Chinese)",
-                                             "L" = "Asian or Asian British (including Chinese)",
-                                             "M" = "Black or Black British",
-                                             "N" = "Black or Black British",
-                                             "P" = "Black or Black British",
-                                             "R" = "Asian or Asian British (including Chinese)",
-                                             "S" = "Asian or Asian British (including Chinese)",
-                                             "W" = NULL, ## Asking NBR what this level means
-                                             "Z" = NULL,
-                                             "99" = NULL)
-}
-```
-
-```{r nbr combine demographics}
-if(NBR == TRUE){
-dem.raw.id <- left_join(nbr.dem.raw.id, nbr.cohort.raw.id, by = c("Sample", "ID"))
-
-# Inspect dimensions
-dim(dem.raw.id)
-# Inspect colnames
-colnames(dem.raw.id)
-#Differences
-dim(nbr.dem.raw.id)[1]-dim(dem.raw.id)[1]
-}
-```
-
-```{r nbr dem summary}
-if(NBR == TRUE) {
-summarytools::dfSummary(
-  dem.raw.id,
-  graph.col = F,
-  valid.col = F,
-  labels.col = F)
-}
-```
-
-## RAMP
-### Read in data
-```{r ramp dem cols}
-if(RAMP == TRUE){
-  ramp.dem.raw <- readRDS(file = paste0(data.raw_path, "/ramp/dem_ramp.rds"))
-  dim(ramp.dem.raw)
-  colnames(ramp.dem.raw)
-}
-```
-
-### Select variables
-```{r ramp dem cleaning}
-if(RAMP == TRUE){
-  exclude_cols_dem <- c("ID",
-                        "Sample")
-
-  ramp.dem.raw.id <- ramp.dem.raw %>%
-    drop_na(`Login ID`) %>% # Drop NAs
-    distinct(`Login ID`, .keep_all = TRUE) %>% # Remove duplicates based on ID
-    separate(`Login ID`, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
-    mutate(ID = as.numeric(ID)) %>%
-    select(
-      Sample, # Sample
-      ID, # ID
-#      startDate.coping, #Date when participant signed up to ramp  (is in the coping gad chunk)
-      age_category_full = demographics.how_old_are_you, # Age
-      Gender = demographics.which_gender_do_you_identify_with, # Gender (what [GLAD] vs which [RAMP])
-#     EduYrs = demographics.university_education_attend_school.txt, # Years in education - not in RAMP dataset
-#     demographics.college_or_university_degree, # level of education - univeristy - level of education is in employment file
-#     demographics.a_levelsas_levels_or_equivalent, # level of education - alevel
-#     demographics.o_levelsgcses_or_equivalent, # level of education - gcse
-#     demographics.cses_or_equivalent, # level of education - cse
-#     demographics.nvq_or_hnd_or_hnc_or_equivalent, # level of education - nvq
-      Transgender_uncleaned = demographics.do_you_identify_as_transgender,
-      Ethnicity = demographics.what_is_your_ethnic_origin # Ethnicity
-    ) %>%
-    add_numeric(., exclude = exclude_cols_dem) %>%
-    mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
-    mutate_if(is.numeric, ~na_if(., -99)) %>%
-    mutate_if(is.numeric, ~na_if(., -77)) %>%
-    mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
-    mutate_if(is.factor, ~na_if(., "Don't know")) %>%
-    mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
-    mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
-    mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
-    mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
-    mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
-    mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
-
-  # Inspect dimensions
-  dim(ramp.dem.raw.id)
-  # Inspect colnames
-  colnames(ramp.dem.raw.id)
-  #Differences
-  dim(ramp.dem.raw)[1]-dim(ramp.dem.raw.id)[1]
-}
-```
-
-```{r ramp copy dem}
-if(RAMP == TRUE){
-  dem.raw.id <- ramp.dem.raw.id
-}
-```
-
-# Demographics variable creation
-## Clean Age variable
-Age outlier
-```{r age outlier}
-if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE ) {
-# Define age limits 
-age_upper_limit = 117 # The oldest person in the world is 117 years
-age_lower_limit = 16
-
-# identify number of outliers
-length(
-  which(
-  dem.raw.id$Age_uncleaned > age_upper_limit |
-    dem.raw.id$Age_uncleaned < age_lower_limit
-     )
-)
-
-# remove age outliers
-dem.raw.id <- dem.raw.id %>%
-  mutate(
-    Age = 
-      if_else(
-        Age_uncleaned > age_upper_limit | 
-        Age_uncleaned < age_lower_limit, 
-        true = NA_real_,
-        false = Age_uncleaned,
-        missing = NA_real_
-      )
-  )
-
-# Inspect variable
-dem.raw.id %>%
-  descr(
-    Age,
-    #stats = "common"
-    )
-}
-```
-
-## Categorise age into groups 
-In RAMP, age is indicated categorically: 16-18, 19-25, 26-35, 36-45, 46-55, 56-65, 66-70, 71-75, 76-80, 81-85, 86-90, 91-100, 100+
-Age categories in GLAD, EDGI and NBR have been created to reflect this
-```{r Age groups}
-if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE) {
-# Create categorical age groups per 10 years
-dem.raw.id <- dem.raw.id %>%
-  mutate(
-    age_category_numeric =
-      case_when(
-          Age >= 16 & Age <= 18 ~ 1,
-          Age >= 19 & Age <= 25 ~ 2,
-          Age >= 26 & Age <= 35 ~ 3,
-          Age >= 36 & Age <= 45 ~ 4,
-          Age >= 46 & Age <= 55 ~ 5,
-          Age >= 56 & Age <= 65 ~ 6,
-          Age >= 66 & Age <= 70 ~ 7,
-          Age >= 71 & Age <= 75 ~ 8,
-          Age >= 76 & Age <= 80 ~ 9,
-          Age >= 81 & Age <= 85 ~ 10,
-          Age >= 86 & Age <= 90 ~ 11,
-          Age >= 91 & Age <= 100 ~ 12,
-          Age >= 101 & Age <= 120 ~ 13 # oldest person in the world is 117 years
-                )
-      )
-
-dem.raw.id <- dem.raw.id %>%
-    mutate(
-      age_category_full =
-        recode_factor(
-          age_category_numeric, 
-          "1" = "16 to 18 years",
-          "2" = "19 to 25 years",
-          "3" = "26 to 35 years",
-          "4" = "36 to 45 years",
-          "5" = "46 to 55 years",
-          "6" = "56 to 65 years",
-          "7" = "66 to 70 years",
-          "8" = "71 to 75 years",
-          "9" = "76 to 80 years",
-          "10" = "81 to 85 years",
-          "11" = "86 to 90 years",
-          "12" = "91 to 100 years",
-          "13" = "Above 100 years"
-          )
-    )
-
-dem.raw.id %>%
-  freq(age_category_full)
-}
-```
-
-## Highest education (prepandemic, GLAD & EDGI)
-
-Proceed along qualifications fields. If field is not blank, take that as highest qual. If field is blank, check next field. If all fields are blank, NA
-Assumes University degree > A level > NVQ > GCSE/O Level/CSE
-```{r Highest education prepandemic}
-if(GLAD == TRUE | EDGI == TRUE) {
-#create numeric version of the highest education variable
-dem.raw.id <- dem.raw.id %>%
-  mutate(
-    highest_education_prepan_numeric =
-      case_when(
-        demographics.college_or_university_degree_numeric == "1" ~ 4,
-        demographics.a_levelsas_levels_or_equivalent_numeric == "1" ~ 3,
-        demographics.nvq_or_hnd_or_hnc_or_equivalent_numeric == "1" ~ 2,
-        demographics.o_levelsgcses_or_equivalent_numeric == "1" ~ 1,
-        demographics.cses_or_equivalent_numeric == "1" ~ 1)
-    )
-
-#recode the numeric version into a factor
-dem.raw.id <- dem.raw.id %>%
-  mutate(
-    highest_education_prepan =
-      recode_factor(
-        highest_education_prepan_numeric,
-        `1` = "GCSE/CSE",
-        `2` = "NVQ",
-        `3` = "A-levels",
-        `4` = "University")
-    )
-
-dem.raw.id %>%
-  freq(highest_education_prepan)
-}
-```
-
-Check highest education coding
-```{r Highest education prepandemic check}
-if(GLAD == TRUE | EDGI == TRUE) {
-dem.raw.id %>%
-  select(highest_education_prepan,
-        demographics.college_or_university_degree_numeric,
-        demographics.a_levelsas_levels_or_equivalent_numeric,
-        demographics.nvq_or_hnd_or_hnc_or_equivalent_numeric,
-        demographics.o_levelsgcses_or_equivalent_numeric,
-        demographics.cses_or_equivalent_numeric
-  )
-}
-```
-
-```{r dem summary}
-if(GLAD == TRUE | EDGI == TRUE) {
-summarytools::dfSummary(
-  dem.raw.id,
-  graph.col = F,
-  valid.col = F,
-  labels.col = F)
-}
-```
-
-# Employment
-
-## GLAD
-### Read in data
-```{r glad employment cols}
-if(GLAD == TRUE){
-glad.employment.raw <- readRDS(file = paste0(data.raw_path, "/glad/employment_coping_glad.rds"))
-dim(glad.employment.raw)
-colnames(glad.employment.raw)
-}
-```
-
-### Select variables
-```{r glad employment cleaning}
-if(GLAD == TRUE){
-exclude_cols_employment <- c("ID",
-                  "Sample")
-
-glad.employment.raw.id <- glad.employment.raw %>%
-  drop_na(externalDataReference) %>% # Drop NAs
-  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
-  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
-  mutate(
-    ID = as.numeric(ID)
-    ) %>%
-  select(
-         Sample, # Sample
-         ID, # ID
-         employment.phd, # level of education - univeristy
-         employment.masters_degree_or_equivalent, # level of education - univeristy
-         employment.postgraduate_degree_or_equivalent, # level of education - univeristy
-         employment.bachelors_degree_or_equivalent, # level of education - univeristy
-         employment.a_levelsas_levels_or_equivalent, # level of education - alevel
-         employment.o_levelsgcses_or_equivalent, # level of education - gcse
-         employment.cses_or_equivalent, # level of education - cse
-         employment.nvq_or_hnd_or_hnc_or_equivalent, # level of education - nvq
-         employment.government_work_key_workers # key worker status
-         ) %>%
-  add_numeric(., exclude = exclude_cols_employment) %>%
-  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
-  mutate_if(is.numeric, ~na_if(., -99)) %>%
-  mutate_if(is.numeric, ~na_if(., -77)) %>%
-  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
-  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
-
-# Inspect dimensions
-dim(glad.employment.raw.id)
-# Inspect colnames
-colnames(glad.employment.raw.id)
-#Differences
-dim(glad.employment.raw)[1]-dim(glad.employment.raw.id)[1]
-}
-```
-
-```{r glad copy employment}
-if(GLAD == TRUE){
-  employment.raw.id <- glad.employment.raw.id
-}
-```
-
-## EDGI
-### Read in data
-```{r edgi employment cols}
-if(EDGI == TRUE){
-edgi.employment.raw <- readRDS(file = paste0(data.raw_path, "/edgi/employment_coping_edgi.rds"))
-dim(edgi.employment.raw)
-colnames(edgi.employment.raw)
-}
-```
-
-### Select variables
-```{r edgi employment cleaning}
-if(EDGI == TRUE){
-exclude_cols_employment <- c("ID",
-                  "Sample")
-
-edgi.employment.raw.id <- edgi.employment.raw %>%
-  drop_na(externalDataReference) %>% # Drop NAs
-  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
-  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
-  mutate(
-    ID = as.numeric(ID)
-    ) %>%
-  select(
-         Sample, # Sample
-         ID, # ID
-         employment.phd, # level of education - univeristy
-         employment.masters_degree_or_equivalent, # level of education - univeristy
-         employment.postgraduate_degree_or_equivalent, # level of education - univeristy
-         employment.bachelors_degree_or_equivalent, # level of education - univeristy
-         employment.a_levelsas_levels_or_equivalent, # level of education - alevel
-         employment.o_levelsgcses_or_equivalent, # level of education - gcse
-         employment.cses_or_equivalent, # level of education - cse
-         employment.nvq_or_hnd_or_hnc_or_equivalent, # level of education - nvq
-         employment.government_work_key_workers # key worker status
-         ) %>%
-  add_numeric(., exclude = exclude_cols_employment) %>%
-  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
-  mutate_if(is.numeric, ~na_if(., -99)) %>%
-  mutate_if(is.numeric, ~na_if(., -77)) %>%
-  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
-  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
-
-# Inspect dimensions
-dim(edgi.employment.raw.id)
-# Inspect colnames
-colnames(edgi.employment.raw.id)
-#Differences
-dim(edgi.employment.raw)[1]-dim(edgi.employment.raw.id)[1]
-}
-```
-
-```{r edgi copy employment}
-if(EDGI == TRUE){
-  employment.raw.id <- edgi.employment.raw.id
-}
-```
-
-## NBR
-### Read in data
-```{r nbr employment cols}
-if(NBR == TRUE){
-nbr.employment.raw <- readRDS(file = paste0(data.raw_path, "/nbr/employment_coping_nbr.rds"))
-dim(nbr.employment.raw)
-colnames(nbr.employment.raw)
-}
-```
-
-### Select variables
-```{r nbr employment cleaning}
-if(NBR == TRUE){
-exclude_cols_employment <- c("ID",
-                  "Sample")
-
-nbr.employment.raw.id <- nbr.employment.raw %>%
-  drop_na(subjectid) %>% # Drop NAs
-  distinct(subjectid, .keep_all = TRUE) %>% # Remove duplicates based on ID
-  separate(subjectid, into = c("Sample", "ID.intm"), sep = 6) %>% # Split ID in Sample and Number
-  separate(ID.intm, into = "ID", sep = 7) %>%
-  mutate(
-    ID = as.numeric(ID)) %>%
-  select(
-         Sample, # Sample
-         ID, # ID
-         employment.phd, # level of education - univeristy
-         employment.masters_degree_or_equivalent, # level of education - univeristy
-         employment.postgraduate_degree_or_equivalent, # level of education - univeristy
-         employment.bachelors_degree_or_equivalent, # level of education - univeristy
-         employment.a_levelsas_levels_or_equivalent, # level of education - alevel
-         employment.o_levelsgcses_or_equivalent, # level of education - gcse
-         employment.cses_or_equivalent, # level of education - cse
-         employment.nvq_or_hnd_or_hnc_or_equivalent, # level of education - nvq
-         employment.government_work_key_workers # key worker status
-         ) %>%
-  add_numeric(., exclude = exclude_cols_employment) %>%
-  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
-  mutate_if(is.numeric, ~na_if(., -99)) %>%
-  mutate_if(is.numeric, ~na_if(., -77)) %>%
-  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
-  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
-
-# Inspect dimensions
-dim(nbr.employment.raw.id)
-# Inspect colnames
-colnames(nbr.employment.raw.id)
-#Differences
-dim(nbr.employment.raw)[1]-dim(nbr.employment.raw.id)[1]
-head(nbr.employment.raw.id
-     )
-}
-```
-
-```{r nbr copy employment}
-if(NBR == TRUE){
-  employment.raw.id <- nbr.employment.raw.id
-}
-```
-
-## RAMP
-### Read in data
-```{r ramp employment cols}
-if(RAMP == TRUE){
-ramp.employment.raw <- readRDS(file = paste0(data.raw_path, "/ramp/employment_ramp.rds"))
-dim(ramp.employment.raw)
-colnames(ramp.employment.raw)
-}
-```
-
-### Select variables
-```{r ramp employment cleaning}
-if(RAMP == TRUE){
-exclude_cols_employment <- c("ID",
-                  "Sample")
-
-ramp.employment.raw.id <- ramp.employment.raw %>%
-  drop_na(`Login ID`) %>% # Drop NAs
-  distinct(`Login ID`, .keep_all = TRUE) %>% # Remove duplicates based on ID
-  separate(`Login ID`, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
-  mutate(
-    ID = as.numeric(ID)
-    ) %>%
-  select(
-         Sample, # Sample
-         ID, # ID
-         employment.what_is_your_highest_level_of_education, #highest level of edcuation
-         employment.government_work_key_workers # key worker status
-         ) %>%
-  add_numeric(., exclude = exclude_cols_employment) %>%
-  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
-  mutate_if(is.numeric, ~na_if(., -99)) %>%
-  mutate_if(is.numeric, ~na_if(., -77)) %>%
-  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
-  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
-
-# Inspect dimensions
-dim(ramp.employment.raw.id)
-# Inspect colnames
-colnames(ramp.employment.raw.id)
-#Differences
-dim(ramp.employment.raw)[1]-dim(ramp.employment.raw.id)[1]
-}
-```
-
-```{r ramp copy employment}
-if(RAMP == TRUE){
-  employment.raw.id <- ramp.employment.raw.id
-}
-```
-
-## Highest education (baseline, GLAD, EDGI, NBR)
-Proceed along qualifications fields. If field is not blank, take that as highest qual. If field is blank, check next field. If all fields are blank, NA
-Assumes University degree > A level > NVQ > GCSE/O Level/CSE
-```{r Highest education baseline}
-if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE) {
-#create numeric version of the highest education variable
-employment.raw.id <- employment.raw.id %>%
-  mutate(
-    highest_education_numeric =
-      case_when(
-        employment.phd_numeric == "1" ~ 4,
-        employment.masters_degree_or_equivalent_numeric == "1" ~ 4,
-        employment.postgraduate_degree_or_equivalent_numeric == "1" ~ 4,
-        employment.bachelors_degree_or_equivalent_numeric == "1" ~ 4,
-        employment.a_levelsas_levels_or_equivalent_numeric == "1" ~ 3,
-        employment.nvq_or_hnd_or_hnc_or_equivalent_numeric == "1" ~ 2,
-        employment.o_levelsgcses_or_equivalent_numeric == "1" ~ 1,
-        employment.cses_or_equivalent_numeric == "1" ~ 1
-      )
-    )
-
-#recode the numeric version into a factor
-employment.raw.id <- employment.raw.id %>%
-  mutate(
-    highest_education =
-      recode_factor(
-        highest_education_numeric,
-        `1` = "GCSE/CSE",
-        `2` = "NVQ",
-        `3` = "A-levels",
-        `4` = "University")
-    )
-
-employment.raw.id %>%
-  freq(highest_education)
-}
-```
-
-Check highest education coding
-```{r Highest education check}
-if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE) {
-employment.raw.id %>%
-  select(highest_education,
-         employment.phd_numeric,
-         employment.masters_degree_or_equivalent_numeric,
-         employment.postgraduate_degree_or_equivalent_numeric,
-         employment.bachelors_degree_or_equivalent_numeric,
-         employment.a_levelsas_levels_or_equivalent_numeric,
-         employment.nvq_or_hnd_or_hnc_or_equivalent_numeric,
-         employment.o_levelsgcses_or_equivalent_numeric,
-         employment.cses_or_equivalent_numeric
-  )
-}
-```
-
-## Highest education (baseline, RAMP)
-```{r highest level of education for ramp}
-if(RAMP == TRUE) {
-#create numeric version of the highest education variable
-employment.raw.id <- employment.raw.id %>%
-  mutate(
-    highest_education_numeric =
-      case_when(
-        employment.what_is_your_highest_level_of_education == "PhD" ~ 4,
-        employment.what_is_your_highest_level_of_education == "Postgraduate degree or equivalent" ~ 4,
-        employment.what_is_your_highest_level_of_education == "Master's degree or equivalent" ~ 4,
-        employment.what_is_your_highest_level_of_education == "Bachelor's degree or equivalent" ~ 4,
-        employment.what_is_your_highest_level_of_education == "A-level or equivalent" ~ 3,
-        employment.what_is_your_highest_level_of_education == "GCSE or equivalent" ~ 2,
-        employment.what_is_your_highest_level_of_education == "None of these" ~ 1
-      )
-    )
-
-#recode the numeric version into a factor
-employment.raw.id <- employment.raw.id %>%
-  mutate(
-    highest_education =
-      recode_factor(
-        highest_education_numeric,
-        `1` = "None",
-        `2` = "GCSE/CSE",
-        `3` = "A-levels",
-        `4` = "University")
-    )
-
-employment.raw.id %>%
-  freq(highest_education)
-}
-```
-
-Check highest education coding for RAMP
-```{r Highest education check for RAMP}
-if(RAMP == TRUE) {
-employment.raw.id %>%
-  select(highest_education,
-         employment.what_is_your_highest_level_of_education,
-         employment.what_is_your_highest_level_of_education_numeric
-  )
-}
-```
-
-## Key worker status
-```{r Key worker}
-if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE | RAMP == TRUE) {
-#create numeric version of the variable
-employment.raw.id <- employment.raw.id %>%
-  mutate(
-    key_worker_numeric =
-      case_when(
-        employment.government_work_key_workers_numeric == "0" ~ 0,
-        employment.government_work_key_workers_numeric > 0 ~ 1
-      )
-    )
-
-#recode the numeric version into a factor
-employment.raw.id <- employment.raw.id %>%
-  mutate(
-    key_worker =
-      recode_factor(
-        key_worker_numeric,
-        `0` = "No key worker",
-        `1` = "Key worker"
-        )
-    )
-
-employment.raw.id %>%
-  freq(key_worker)
-}
-```
-
-# Columns to exclude from add_numeric
-
-```{r cols to exclude}
-exclude_cols <- c("Sample",
-                  "ID")
-```
-
-# mhd
-
-## GLAD
-```{r glad mhd cols}
-if(GLAD == TRUE) {
-glad.mhd.raw <- readRDS(file = paste0(data.raw_path,"/glad/mhd_glad.rds"))
-dim(glad.mhd.raw)
-colnames(glad.mhd.raw)
-}
-```
-
-```{r glad mhd cleaning}
-if(GLAD == TRUE) {
-glad.mhd.raw.id <- glad.mhd.raw %>%
-  drop_na(externalDataReference) %>% # Drop NAs
-  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
-  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
-  mutate(ID = as.numeric(ID)) %>%
-  select(
-    Sample, # Sample
-    ID, # ID
-    starts_with("mhd."),
-    mhd.bingeeating_disorder = mhd.psychological_overeating_or_bingeeating
-  ) %>%
-  add_numeric(., exclude = exclude_cols) %>%
-  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
-  mutate_if(is.numeric, ~na_if(., -99)) %>%
-  mutate_if(is.numeric, ~na_if(., -77)) %>%
-  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
-  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
-
-# Inspect dimensions
-dim(glad.mhd.raw.id)
-# Inspect colnames
-colnames(glad.mhd.raw.id)
-#Differences
-dim(glad.mhd.raw)[1]-dim(glad.mhd.raw.id)[1]
-}
-```
-
-```{r glad mhd copy}
-if(GLAD == TRUE) {
-  mhd.raw.id <- glad.mhd.raw.id
-}
-```
-
-## EDGI
-```{r edgi mhd cols}
-if(EDGI == TRUE) {
-edgi.mhd.raw <- readRDS(file = paste0(data.raw_path,"/edgi/mhd_edgi.rds"))
-dim(edgi.mhd.raw)
-colnames(edgi.mhd.raw)
-}
-```
-
-```{r edgi mhd cleaning}
-if(EDGI == TRUE) {
-  exclude_cols <- c("Sample",
-                  "ID")
-
-edgi.mhd.raw.id <- edgi.mhd.raw %>%
-  drop_na(externalDataReference) %>% # Drop NAs
-  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
-  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
-  mutate(ID = as.numeric(ID)) %>%
-  select(
-    Sample, # Sample
-    ID, # ID
-    mhd.anorexia_nervosa,
-    mhd.atypical_anorexia_nervosa,
-    mhd.bulimia_nervosa,
-    mhd.atypical_bulimia_nervosa,
-    mhd.bingeeating_disorder,
-    mhd.atypical_bingeeating_disorder
-  ) %>%
-  add_numeric(., exclude = exclude_cols) %>%
-  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
-  mutate_if(is.numeric, ~na_if(., -99)) %>%
-  mutate_if(is.numeric, ~na_if(., -77)) %>%
-  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
-  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
-
-# Inspect dimensions
-dim(edgi.mhd.raw.id)
-# Inspect colnames
-colnames(edgi.mhd.raw.id)
-#Differences
-dim(edgi.mhd.raw)[1]-dim(edgi.mhd.raw.id)[1]
-}
-```
-
-```{r edgi mhd2 cols}
-if(EDGI == TRUE) {
-edgi.mhd2.raw <- readRDS(file = paste0(data.raw_path,"/edgi/dem_edgi.rds"))
-dim(edgi.mhd2.raw)
-colnames(edgi.mhd2.raw)
-}
-```
-
-```{r edgi mhd2 cleaning}
-if(EDGI == TRUE){
-  exclude_cols_mhd2 <- c("ID",
-                        "Sample",
-                        "startDate.prepandemic",
-                        "Age_uncleaned",
-                        "EduYrs")
-
-  edgi.mhd2.raw.id <- edgi.mhd2.raw %>%
-    drop_na(externalDataReference) %>% # Drop NAs
-    distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
-    separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
-    mutate(ID = as.numeric(ID)) %>%
-    select(
-      Sample, # Sample
-      ID, # ID
-    mhd.depression = demographics.depression,
-    mhd.pregnancy_depression = demographics.pregnancy_depression,
-    mhd.premenstrual_dysphoric_disorder_pmdd = demographics.premenstrual_dysphoric_disorder_pmdd,
-    mhd.anxiety_nerves_or_generalised_anxiety_disorder = demographics.anxiety_nerves_or_generalised_anxiety_disorder,
-    mhd.social_anxiety_or_social_phobia = demographics.social_anxiety_or_social_phobia,
-    mhd.specific_phobia_e.g._phobia_of_flying = demographics.specific_phobia_e.g._fear_of_flying, # fear instead of phobia
-    mhd.agoraphobia = demographics.agoraphobia,
-    mhd.panic_disorder = demographics.panic_disorder,
-    mhd.panic_attacks = demographics.panic_attacks,
-    mhd.obsessivecompulsive_disorder_ocd = demographics.obsessivecompulsive_disorder_ocd,
-    mhd.obsessive_compulsive_related_disorders = demographics.obsessive_compulsive_related_disorders,
-    mhd.body_dysmorphic_disorder_bdd = demographics.body_dysmorphic_disorder,
-    mhd.mania_hypomania_bipolar_or_manicdepression = demographics.mania_hypomania_bipolar_or_manicdepression,
-    mhd.schizophrenia = demographics.schizophrenia,
-    mhd.type_psychosis_psychotic_illness = demographics.psychosis_type_psychotic_illness, # word type psychosis changed order compared to GLAD 
-    mhd.personality_disorder_diagnosed = demographics.diagnosed_personality_disorder, # named differently in EDGI
-    mhd.posttraumatic_stress_disorder_ptsd = demographics.posttraumatic_stress_disorder_ptsd,
-    mhd.autism_aspergers_or_autistic_spectrum_disorder = demographics.autism_spectrum_disorder_asd, # different name in EDGI
-    mhd.body_dysmorphic_disorder_bdd = demographics.body_dysmorphic_disorder,
-    mhd.personality_disorder = demographics.personality_disorder, # routing variable in EDGI is named differently; renamed here to match GLAD
-    mhd.attention_deficit_hyperactivity_disorder = demographics.attention_deficit_hyperactivity_disorder
-    ) %>%
-    add_column(
-      mhd.schizoaffective_disorder = NA_character_
-    ) %>%
-    add_numeric(., exclude = exclude_cols_mhd2) %>%
-    mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
-    mutate_if(is.numeric, ~na_if(., -99)) %>%
-    mutate_if(is.numeric, ~na_if(., -77)) %>%
-    mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
-    mutate_if(is.factor, ~na_if(., "Don't know")) %>%
-    mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
-    mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
-    mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
-    mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
-    mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
-    mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
-
-  # Inspect dimensions
-  dim(edgi.mhd2.raw.id)
-  # Inspect colnames
-  colnames(edgi.mhd2.raw.id)
-  #Differences
-  dim(edgi.mhd2.raw)[1]-dim(edgi.mhd2.raw.id)[1]
-}
-```
-
-```{r edgi combine mhd copy}
-if(EDGI == TRUE){
-mhd.raw.id <- left_join(
-  x = edgi.mhd.raw.id,
-  y = edgi.mhd2.raw.id,
-  by = c("Sample", "ID")
-  )
-
-# Inspect dimensions
-dim(mhd.raw.id)
-# Inspect colnames
-colnames(mhd.raw.id)
-}
-```
-
-## NBR
-```{r nbr mhd cols}
-if(NBR == TRUE) {
-nbr.mhd.raw <- readRDS(file = paste0(data.raw_path,"/nbr/mhd_nbr.rds"))
-dim(nbr.mhd.raw)
-colnames(nbr.mhd.raw)
-}
-```
-
-```{r nbr mhd cleaning}
-if(NBR == TRUE) {
-exclude_cols <- c("Sample",
-                  "ID")
-
-nbr.mhd.raw.id <- nbr.mhd.raw %>%
-  drop_na(subjectid) %>% # Drop NAs
-  distinct(subjectid, .keep_all = TRUE) %>% # Remove duplicates based on ID
-  separate(subjectid, into = c("Sample", "ID.intm"), sep = 6) %>% # Split ID in Sample and Number
-  separate(ID.intm, into = "ID", sep = 7) %>%
-  mutate(
-    ID = as.numeric(ID)) %>%
-  select(
-    Sample, # Sample
-    ID, # ID
-    starts_with("mhd."),
-    mhd.specific_phobia_e.g._phobia_of_flying = mhd.specific_phobia_e.g._fear_of_flying,
-    mhd.type_psychosis_psychotic_illness = mhd.psychosis_type_psychotic_illness,
-    mhd.autism_aspergers_or_autistic_spectrum_disorder = mhd.autism_spectrum_disorder_asd,
-    mhd.anorexia_nervosa_unc = mhd.anorexia_nervosa,
-    mhd.atypical_anorexia_nervosa_unc = mhd.atypical_anorexia_nervosa,
-    mhd.bulimia_nervosa_unc = mhd.bulimia_nervosa,
-    mhd.bingeeating_disorder_unc = mhd.bingeeating_disorder
-  ) %>%
-  add_column(
-    mhd.schizoaffective_disorder = NA #NBR doesn't ask about schizoaffective disorder. This means the column das not exist in the data set
-  ) %>% 
-  add_numeric(., exclude = exclude_cols) %>%
-  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
-  mutate_if(is.numeric, ~na_if(., -99)) %>%
-  mutate_if(is.numeric, ~na_if(., -77)) %>%
-  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
-  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
-
-# Inspect dimensions
-dim(nbr.mhd.raw.id)
-# Inspect colnames
-colnames(nbr.mhd.raw.id)
-#Differences
-dim(nbr.mhd.raw)[1]-dim(nbr.mhd.raw.id)[1]
-}
-```
-
-```{r nbr mhd copy}
-if(NBR == TRUE) {
-  mhd.raw.id <- nbr.mhd.raw.id
-}
-```
-
-## RAMP
-```{r ramp mhd cols}
-if(RAMP == TRUE) {
-ramp.mhd.raw <- readRDS(file = paste0(data.raw_path,"/ramp/mhd_ramp.rds"))
-dim(ramp.mhd.raw)
-colnames(ramp.mhd.raw)
-}
-```
-
-```{r ramp mhd cleaning}
-if(RAMP == TRUE) {
-exclude_cols <- c("Sample",
-                  "ID")
-
-ramp.mhd.raw.id <- ramp.mhd.raw %>%
-  drop_na(`Login ID`) %>% # Drop NAs
-  distinct(`Login ID`, .keep_all = TRUE) %>% # Remove duplicates based on ID
-  separate(`Login ID`, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
-  separate(ID, into = "ID", sep = 7) %>%
-  mutate(
-    ID = as.numeric(ID)) %>%
-  select(
-    Sample, # Sample
-    ID, # ID
-    mhd.depression = NA.30.depression,
-    mhd.pregnancy_depression = NA.30.pregnancy_depression,
-    mhd.premenstrual_dysphoric_disorder_pmdd = NA.30.premenstrual_dysphoric_disorder_pmdd,
-    mhd.mania_hypomania_bipolar_or_manicdepression = NA.30.mania_hypomania_bipolar_or_manicdepression,
-    mhd.anxiety_nerves_or_generalised_anxiety_disorder = NA.30.anxiety_nerves_or_generalised_anxiety_disorder,
-    mhd.social_anxiety_or_social_phobia = NA.30.social_anxiety_or_social_phobia,
-    mhd.specific_phobia_e.g._phobia_of_flying = NA.30.specific_phobia_e.g._phobia_of_flying,
-    mhd.agoraphobia = NA.30.agoraphobia,
-    mhd.panic_disorder = NA.30.panic_disorder,
-    mhd.panic_attacks = NA.30.panic_attacks,
-    mhd.posttraumatic_stress_disorder_ptsd = NA.30.posttraumatic_stress_disorder_ptsd,
-    mhd.obsessivecompulsive_disorder_ocd = NA.30.obsessivecompulsive_disorder_ocd, 
-    mhd.body_dysmorphic_disorder_bdd = NA.30.body_dysmorphic_disorder_bdd,
-    mhd.skin_picking_obsessive_compulsive = NA.30.skin_picking_obsessive_compulsive,
-    mhd.anorexia_nervosa = NA.30.anorexia_nervosa,
-    mhd.atypical_anorexia_nervosa = NA.30.atypical_anorexia_nervosa,
-    mhd.bulimia_nervosa = NA.30.bulimia_nervosa,
-    mhd.bingeeating_disorder = NA.30.psychological_overeating_or_bingeeating_disorder,
-    mhd.schizophrenia = NA.30.schizophrenia,
-    mhd.schizoaffective_disorder = NA.30.schizoaffective_disorder,
-    mhd.type_psychosis_psychotic_illness = NA.30.psychosis_type_psychotic_illness,
-    mhd.personality_disorder = NA.30.personality_disorder,
-    mhd.autism_aspergers_or_autistic_spectrum_disorder = NA.30.autism_aspergers_or_autistic_spectrum_disorder,
-    mhd.attention_deficit_hyperactivity_disorder = NA.30.attention_deficit_hyperactivity_disorder,
-    mhd.personality_disorder_diagnosed = NA.30.personality_disorder_diagnosed
-  ) %>%
-  add_numeric(., exclude = exclude_cols) %>%
-  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
-  mutate_if(is.numeric, ~na_if(., -99)) %>%
-  mutate_if(is.numeric, ~na_if(., -77)) %>%
-  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
-  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
-
-# Inspect dimensions
-dim(ramp.mhd.raw.id)
-# Inspect colnames
-colnames(ramp.mhd.raw.id)
-#Differences
-dim(ramp.mhd.raw)[1]-dim(ramp.mhd.raw.id)[1]
-}
-```
-
-```{r ramp mhd copy}
-if(RAMP == TRUE) {
-  mhd.raw.id <- ramp.mhd.raw.id
-}
-```
-
-## Grouping mental health disorders
-*#Disorder groupings - from COPING/RAMP analysis minutes*
-1. Depressive disorder group: major depression, antenatal/postnatal depression, premenstrual depression. The logic for this has been double checked for males - KT/MD. 
-2. Anxiety group: generalised anxiety, social anxiety, specific phobia, agoraphobia, panic_disorder, panic_attacks. 
-3. Agoraphobia and panic_disorder group: panic_disorder, agoraphobia, panic_attacks.
-4. Eating disorders group: anorexianervosa, atypical anorexia nervosa, bulimia nervosa, overeating or bingeeating.
-5. Obsessive complusive disorders: obsessive compulaive disorder, obsessive compulsive related disorders. 
-6. Psychotic disorders: schizophrenia, schizoaffective disorder, general psychosis or psychotic illness. 
-7. Personality disorders: cluster A, cluster B, cluster C
-8. Control group: no diagnosed disorders.
-
-*Disorders of interest*
-MDD and other depressive disorders
-Anxiety, nerves or generalised anxiety disorder
-Social anxiety 
-Specific phobia 
-Agoraphobia/panic disorder/panic attacks
-OCD (& OCD-related disorders e.g., skin picking?)
-PTSD 
-Bipolar 
-Eating disorders (Anorexia, BE-type EDs) 
-Personality disorder: Clusters A, B, and C 
-No-diagnosis group
-
-*Analysis plan of Disorders: KY and KP analysis plan*
-1. Basic: any anxiety or unipolar depressive disorder vs. those with no prior diagnosis
-2. Specific: breakdown by type of prior anxiety (& related) disorder diagnosis
-3. Breakdown by COVID or not (using COVIDENCE/Zoe algorithm)
-
-### Depressive disorders
-```{r mhd depressive_disorders}
-if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE | RAMP == TRUE)
-mhd.raw.id <- mhd.raw.id %>%
-  mutate(
-    depressive_disorders_numeric =
-      case_when(
-        (mhd.depression_numeric == "0" &
-        (mhd.pregnancy_depression_numeric == "0" | is.na(mhd.pregnancy_depression_numeric)) & 
-        (mhd.premenstrual_dysphoric_disorder_pmdd_numeric == "0" | is.na(mhd.premenstrual_dysphoric_disorder_pmdd_numeric))) ~ 0,
-        mhd.depression_numeric == "1" ~ 1,
-        mhd.pregnancy_depression_numeric == "1" ~ 1,
-        mhd.premenstrual_dysphoric_disorder_pmdd_numeric == "1" ~ 1))
-
-mhd.raw.id <- mhd.raw.id %>%
-  mutate(
-    depressive_disorders =
-      recode_factor(depressive_disorders_numeric,
-                    "0" = "No depressive disorder",
-                    "1" = "Depressive disorder",
-                    missing = NA_character_
-                    )
-  )
-
-mhd.raw.id %>%
-  freq(depressive_disorders,
-       cumul = F)
-```
-
-```{r Check depressive_disorders}
-if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE | RAMP == TRUE) {
-mhd.raw.id %>%
-  select(
-    depressive_disorders,
-    depressive_disorders_numeric,
-    mhd.depression_numeric,
-    mhd.pregnancy_depression_numeric,
-    mhd.premenstrual_dysphoric_disorder_pmdd_numeric,
-    mhd.depression,
-    mhd.pregnancy_depression,
-    mhd.premenstrual_dysphoric_disorder_pmdd
-  )
-}
-```
-
-### Anxiety disorders
-```{r mhd anxiety_disorders}
-if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE | RAMP == TRUE) {
-mhd.raw.id <- mhd.raw.id %>%
-  mutate(
-    anxiety_disorders_numeric =
-      case_when(
-        mhd.anxiety_nerves_or_generalised_anxiety_disorder_numeric == "1" ~ 1,
-        mhd.social_anxiety_or_social_phobia_numeric == "1" ~ 1,
-        mhd.specific_phobia_e.g._phobia_of_flying_numeric == "1" ~ 1,
-        mhd.agoraphobia_numeric == "1" ~ 1,
-        mhd.panic_disorder_numeric == "1" ~ 1,
-        mhd.panic_attacks_numeric == "1" ~ 1,
-        (mhd.anxiety_nerves_or_generalised_anxiety_disorder_numeric == "0" &
-        mhd.social_anxiety_or_social_phobia_numeric == "0" &
-        mhd.specific_phobia_e.g._phobia_of_flying_numeric == "0" &
-        mhd.agoraphobia_numeric == "0" &
-        mhd.panic_disorder_numeric == "0" &
-        mhd.panic_attacks_numeric == "0") ~ 0
-      )
-  )
-
-mhd.raw.id <- mhd.raw.id %>%
-  mutate(
-    anxiety_disorders =
-      recode_factor(anxiety_disorders_numeric,
-                    "0" = "No anxiety disorder",
-                    "1" = "Anxiety disorder",
-                    missing = NA_character_
-                    )
-  )
-
-mhd.raw.id %>%
-  freq(anxiety_disorders,
-       cumul = F)
-}
-```
-
-```{r Check anxiety_disorders}
-if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE | RAMP == TRUE) {
-mhd.raw.id %>%
-  select(
-    anxiety_disorders,
-    anxiety_disorders_numeric,
-    mhd.anxiety_nerves_or_generalised_anxiety_disorder_numeric,
-    mhd.social_anxiety_or_social_phobia_numeric,
-    mhd.specific_phobia_e.g._phobia_of_flying_numeric,
-    mhd.agoraphobia_numeric,
-    mhd.panic_disorder_numeric,
-    mhd.panic_attacks_numeric,
-    mhd.anxiety_nerves_or_generalised_anxiety_disorder,
-    mhd.social_anxiety_or_social_phobia,
-    mhd.specific_phobia_e.g._phobia_of_flying,
-    mhd.agoraphobia,
-    mhd.panic_disorder,
-    mhd.panic_attacks
-  )
-}
-```
-
-Agoraphonia and panic disorder group
-```{r mhd agoraphobia_panic_disorder}
-if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE | RAMP == TRUE) {
-mhd.raw.id <- mhd.raw.id %>%
-  mutate(
-    agoraphobia_panic_disorder_numeric =
-      case_when(
-        mhd.agoraphobia_numeric == "1" ~ 1,
-        mhd.panic_disorder_numeric == "1" ~ 1,
-        mhd.panic_attacks_numeric == "1" ~ 1,
-        (mhd.agoraphobia_numeric == "0" &
-        mhd.panic_disorder_numeric == "0" &
-        mhd.panic_attacks_numeric == "0") ~ 0
-      )
-  )
-
-mhd.raw.id <- mhd.raw.id %>%
-  mutate(
-    agoraphobia_panic_disorder =
-      recode_factor(agoraphobia_panic_disorder_numeric,
-                    "0" = "No agoraphobia/panic disorder",
-                    "1" = "Agoraphobia/panic disorder",
-                    missing = NA_character_
-                    )
-  )
-
-mhd.raw.id %>%
-  freq(agoraphobia_panic_disorder)
-}
-```
-
-```{r Check agoraphobia_panic_disorder}
-if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE | RAMP == TRUE) {
-mhd.raw.id %>%
-  select(
-    agoraphobia_panic_disorder,
-    agoraphobia_panic_disorder_numeric,
-    mhd.agoraphobia_numeric,
-    mhd.panic_disorder_numeric,
-    mhd.panic_attacks_numeric,
-    mhd.agoraphobia,
-    mhd.panic_disorder,
-    mhd.panic_attacks
-  )
-}
-```
-
-Depression and anxiety comorbidity
-```{r mhd depression_anxiety}
-if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE | RAMP == TRUE) {
-mhd.raw.id <- mhd.raw.id %>%
-  mutate(
-    depression_and_anxiety_numeric =
-      case_when(
-        depressive_disorders_numeric == 0 &
-          anxiety_disorders_numeric == 0 ~ 0,
-        depressive_disorders_numeric == 1 &
-          anxiety_disorders_numeric == 1 ~ 1,
-        depressive_disorders_numeric == 1 &
-          anxiety_disorders_numeric == 0 ~ 2,
-        depressive_disorders_numeric == 0 &
-          anxiety_disorders_numeric == 1 ~ 3
-      )
-  )
-
-mhd.raw.id <- mhd.raw.id %>%
-  mutate(
-    depression_and_anxiety =
-      recode_factor(depression_and_anxiety_numeric,
-                    "0" = "No depressive or anxiety disorder",
-                    "1" = "Depressive and anxiety disorder",
-                    "2" = "Only depressive disorder",
-                    "3" = "Only anxiety disorder",
-                    missing = NA_character_
-                    )
-  )
-
-mhd.raw.id %>%
-  freq(depression_and_anxiety,
-       cumul = F)
-}
-```
-
-### Eating disorders
-
-There is routing questionnaire if participants have been diagnosed with an eating disorder and afterwards they get asked the specific disorders.
-Therefore, mhd.suspected_eating_disorder_diagnosed_numeric needs to be recoded as 0 otherwise they would be NAs.
-```{r nbr cleaning eating disorders}
-if(NBR == TRUE) {
-#Recode as 0 if ppt responds no to screening question (mhd.suspected_eating_disorder_diagnosed_numeric)
-mhd.raw.id <- mhd.raw.id %>%
-  mutate(
-    mhd.anorexia_nervosa_numeric =
-      case_when(mhd.suspected_eating_disorder_diagnosed_numeric == "0" ~ 0,
-                mhd.anorexia_nervosa_unc_numeric == "0" ~ 0,
-                mhd.anorexia_nervosa_unc_numeric == "1" ~ 1),
-    mhd.atypical_anorexia_nervosa_numeric =
-      case_when(mhd.suspected_eating_disorder_diagnosed_numeric == "0" ~ 0,
-                mhd.atypical_anorexia_nervosa_unc_numeric == "0" ~ 0,
-                mhd.atypical_anorexia_nervosa_unc_numeric == "1" ~ 1),
-    mhd.bulimia_nervosa_numeric =
-      case_when(mhd.suspected_eating_disorder_diagnosed_numeric == "0" ~ 0,
-                mhd.bulimia_nervosa_unc_numeric == "0" ~ 0,
-                mhd.bulimia_nervosa_unc_numeric == "1" ~ 1),
-    mhd.bingeeating_disorder_numeric =
-      case_when(mhd.suspected_eating_disorder_diagnosed_numeric == "0" ~ 0,
-                mhd.bingeeating_disorder_unc_numeric == "0" ~ 0,
-                mhd.bingeeating_disorder_unc_numeric == "1" ~ 1),
-    mhd.anorexia_nervosa =
-      case_when(mhd.suspected_eating_disorder_diagnosed_numeric == "0" ~ "Not Anorexia nervosa",
-                mhd.anorexia_nervosa_unc_numeric == "0" ~ "Not Anorexia nervosa",
-                mhd.anorexia_nervosa_unc_numeric == "1" ~ "Anorexia nervosa"),
-    mhd.atypical_anorexia_nervosa =
-      case_when(mhd.suspected_eating_disorder_diagnosed_numeric == "0" ~ "Not Atypical anorexia nervosa",
-                mhd.atypical_anorexia_nervosa_unc_numeric == "0" ~ "Not Atypical anorexia nervosa",
-                mhd.atypical_anorexia_nervosa_unc_numeric == "1" ~ "Atypical anorexia nervosa"),
-    mhd.bulimia_nervosa =
-      case_when(mhd.suspected_eating_disorder_diagnosed_numeric == "0" ~ "Not Bulimia nervosa",
-                mhd.bulimia_nervosa_unc_numeric == "0" ~ "Not Bulimia nervosa",
-                mhd.bulimia_nervosa_unc_numeric == "1" ~ "Bulimia nervosa"),
-    mhd.bingeeating_disorder =
-      case_when(mhd.suspected_eating_disorder_diagnosed_numeric == "0" ~ "Not Binge-eating disorder",
-                mhd.bingeeating_disorder_unc_numeric == "0" ~ "Not Binge-eating disorder",
-                mhd.bingeeating_disorder_unc_numeric == "1" ~ "Binge-eating disorder")
-    )
-}
-
-```
-
-```{r mhd eating_disorders}
-if(GLAD == TRUE | NBR == TRUE | RAMP == TRUE) {
-mhd.raw.id <- mhd.raw.id %>%
-  mutate(
-    eating_disorders_numeric =
-      case_when(
-        mhd.anorexia_nervosa_numeric == "1" ~ 1,
-        mhd.atypical_anorexia_nervosa_numeric == "1" ~ 1,
-        mhd.bulimia_nervosa_numeric == "1" ~ 1,
-        mhd.bingeeating_disorder_numeric == "1" ~ 1,
-        (mhd.anorexia_nervosa_numeric == "0" &
-        mhd.atypical_anorexia_nervosa_numeric == "0" &
-        mhd.bulimia_nervosa_numeric == "0" &
-        mhd.bingeeating_disorder_numeric == "0") ~ 0
-      )
-  )
-
-mhd.raw.id <- mhd.raw.id %>%
-  mutate(
-    eating_disorders =
-      recode_factor(eating_disorders_numeric,
-                    "0" = "No eating disorder",
-                    "1" = "Eating disorder",
-                    missing = NA_character_
-                    )
-  )
-
-mhd.raw.id %>%
-  freq(eating_disorders,
-       cumul = F)
-}
-```
-
-For EDGI does not include other eating disorders, such as purging disorder, rumination disorder, ARFID, or Pica
-```{r edgi mhd eating_disorders}
-if(EDGI == TRUE) {
-mhd.raw.id <- mhd.raw.id %>%
-  mutate(
-    eating_disorders_numeric =
-      case_when(
-        mhd.anorexia_nervosa_numeric == "1" ~ 1,
-        mhd.atypical_anorexia_nervosa_numeric == "1" ~ 1,
-        mhd.bulimia_nervosa_numeric == "1" ~ 1,
-        mhd.atypical_bulimia_nervosa_numeric == "1" ~ 1, # additional diagnosis in EDGI but not in GLAD
-        mhd.bingeeating_disorder_numeric == "1" ~ 1,
-        mhd.atypical_bingeeating_disorder_numeric == "1" ~ 1, # additional diagnosis in EDGI
-        (mhd.anorexia_nervosa_numeric == "0" &
-        mhd.atypical_anorexia_nervosa_numeric == "0" &
-          mhd.atypical_anorexia_nervosa_numeric == "0" &
-        mhd.bulimia_nervosa_numeric == "0" &
-          mhd.atypical_bulimia_nervosa_numeric == "0" &
-        mhd.bingeeating_disorder_numeric == "0" &
-          mhd.atypical_bingeeating_disorder_numeric == "0") ~ 0
-      )
-  )
-
-mhd.raw.id <- mhd.raw.id %>%
-  mutate(
-    eating_disorders =
-      recode_factor(eating_disorders_numeric,
-                    "0" = "No eating disorder",
-                    "1" = "Eating disorder",
-                    missing = NA_character_
-                    )
-  )
-
-mhd.raw.id %>%
-  freq(eating_disorders,
-       cumul = F)
-}
-```
-
-Eating disorders with binge eating vs eating disorders without
-Caveat: Anorexia nervosa can have binge eating as well. Therefore, this would need an additional variable from the ED100K
-```{r mhd restricting_vs_binge_eating_eating_disorders}
-if(GLAD == TRUE | NBR == TRUE | RAMP == TRUE) {
-mhd.raw.id <- mhd.raw.id %>%
-  mutate(
-    restricting_vs_binge_eating_eating_disorders_numeric =
-      case_when(
-        mhd.anorexia_nervosa_numeric == "1" ~ 1,
-        mhd.atypical_anorexia_nervosa_numeric == "1" ~ 1,
-        mhd.bulimia_nervosa_numeric == "1" ~ 2,
-        mhd.bingeeating_disorder_numeric == "1" ~ 2,
-        (mhd.anorexia_nervosa_numeric == "0" &
-        mhd.atypical_anorexia_nervosa_numeric == "0" &
-        mhd.bulimia_nervosa_numeric == "0" &
-        mhd.bingeeating_disorder_numeric == "0") ~ 0
-      )
-  )
-
-mhd.raw.id <- mhd.raw.id %>%
-  mutate(
-    restricting_vs_binge_eating_eating_disorders =
-      recode_factor(restricting_vs_binge_eating_eating_disorders_numeric,
-                    "0" = "No eating disorder",
-                    "1" = "Anorexia nervosa",
-                    "2" = "Eating disorder with binge eating",
-                    missing = NA_character_
-                    )
-  )
-
-mhd.raw.id %>%
-  freq(restricting_vs_binge_eating_eating_disorders,
-       cumul = F)
-}
-```
-
-```{r mhd restricting_vs_binge_eating_eating_disorders}
-if(EDGI == TRUE) {
-mhd.raw.id <- mhd.raw.id %>%
-  mutate(
-    restricting_vs_binge_eating_eating_disorders_numeric =
-      case_when(
-        mhd.anorexia_nervosa_numeric == "1" ~ 1,
-        mhd.atypical_anorexia_nervosa_numeric == "1" ~ 1,
-        mhd.bulimia_nervosa_numeric == "1" ~ 2,
-        mhd.atypical_bulimia_nervosa_numeric == "1" ~ 2, # additional diagnosis in EDGI but not in GLAD
-        mhd.bingeeating_disorder_numeric == "1" ~ 2,
-        mhd.atypical_bingeeating_disorder_numeric == "1" ~ 2, # additional diagnosis in EDGI
-        (mhd.anorexia_nervosa_numeric == "0" &
-        mhd.atypical_anorexia_nervosa_numeric == "0" &
-          mhd.atypical_anorexia_nervosa_numeric == "0" &
-        mhd.bulimia_nervosa_numeric == "0" &
-          mhd.atypical_bulimia_nervosa_numeric == "0" &
-        mhd.bingeeating_disorder_numeric == "0" &
-          mhd.atypical_bingeeating_disorder_numeric == "0") ~ 0
-      )
-  )
-
-mhd.raw.id <- mhd.raw.id %>%
-  mutate(
-    restricting_vs_binge_eating_eating_disorders =
-      recode_factor(restricting_vs_binge_eating_eating_disorders_numeric,
-                    "0" = "No eating disorder",
-                    "1" = "Anorexia nervosa",
-                    "2" = "Eating disorder with binge eating",
-                    missing = NA_character_
-                    )
-  )
-
-mhd.raw.id %>%
-  freq(restricting_vs_binge_eating_eating_disorders,
-       cumul = F)
-}
-```
-
-```{r Check eating_disorders}
-if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE | RAMP == TRUE) {
-mhd.raw.id %>%
-  select(
-    eating_disorders,
-    eating_disorders_numeric,
-    restricting_vs_binge_eating_eating_disorders,
-    restricting_vs_binge_eating_eating_disorders_numeric,
-    mhd.anorexia_nervosa_numeric,
-    mhd.atypical_anorexia_nervosa_numeric,
-    mhd.bulimia_nervosa_numeric,
-    mhd.bingeeating_disorder_numeric,
-    mhd.anorexia_nervosa,
-    mhd.atypical_anorexia_nervosa,
-    mhd.bulimia_nervosa,
-    mhd.bingeeating_disorder
-  )
-}
-```
-
-```{r Check eating_disorders}
-if(EDGI == TRUE) {
-mhd.raw.id %>%
-  select(
-    eating_disorders,
-    eating_disorders_numeric,
-    restricting_vs_binge_eating_eating_disorders,
-    restricting_vs_binge_eating_eating_disorders_numeric,
-    mhd.anorexia_nervosa_numeric,
-    mhd.atypical_anorexia_nervosa_numeric,
-    mhd.bulimia_nervosa_numeric,
-    mhd.bingeeating_disorder_numeric,
-    mhd.anorexia_nervosa,
-    mhd.atypical_anorexia_nervosa,
-    mhd.bulimia_nervosa,
-    mhd.atypical_bulimia_nervosa,
-    mhd.bingeeating_disorder,
-    mhd.atypical_bingeeating_disorder
-  )
-}
-```
-
-### Obsessive compulsive disorders
-```{r mhd obsessive_compulsive_disorders}
-if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE) {
-mhd.raw.id <- mhd.raw.id %>%
-  mutate(
-    obsessive_compulsive_disorders_numeric =
-      case_when(
-        mhd.obsessivecompulsive_disorder_ocd_numeric == "1" ~ 1,
-        mhd.obsessive_compulsive_related_disorders_numeric == "1" ~ 1,
-        mhd.body_dysmorphic_disorder_bdd_numeric == "1" ~ 1,
-        (mhd.obsessivecompulsive_disorder_ocd_numeric == "0" &
-        mhd.obsessive_compulsive_related_disorders_numeric == "0" &
-        mhd.body_dysmorphic_disorder_bdd_numeric == "0") ~ 0
-      )
-  )
-
-mhd.raw.id <- mhd.raw.id %>%
-  mutate(
-    obsessive_compulsive_disorders =
-      recode_factor(obsessive_compulsive_disorders_numeric,
-                    "0" = "No obsessive compulsive disorder",
-                    "1" = "Obsessive compulsive disorder",
-                    missing = NA_character_
-                    )
-  )
-
-mhd.raw.id %>%
-  freq(obsessive_compulsive_disorders)
-}
-```
-
-```{r mhd obsessive_compulsive_disorders for ramp}
-if(RAMP == TRUE) {
-mhd.raw.id <- mhd.raw.id %>%
-  mutate(
-    obsessive_compulsive_disorders_numeric =
-      case_when(
-        mhd.obsessivecompulsive_disorder_ocd_numeric == "1" ~ 1,
-        mhd.skin_picking_obsessive_compulsive_numeric == "1" ~ 1,
-        mhd.body_dysmorphic_disorder_bdd_numeric == "1" ~ 1,
-        (mhd.obsessivecompulsive_disorder_ocd_numeric == "0" &
-        mhd.skin_picking_obsessive_compulsive_numeric == "0" &
-        mhd.body_dysmorphic_disorder_bdd_numeric == "0") ~ 0
-      )
-  )
-
-mhd.raw.id <- mhd.raw.id %>%
-  mutate(
-    obsessive_compulsive_disorders =
-      recode_factor(obsessive_compulsive_disorders_numeric,
-                    "0" = "No obsessive compulsive disorder",
-                    "1" = "Obsessive compulsive disorder",
-                    missing = NA_character_
-                    )
-  )
-
-mhd.raw.id %>%
-  freq(obsessive_compulsive_disorders)
-}
-```
-
-```{r Check obsessive_compulsive_disorders}
-if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE) {
-mhd.raw.id %>%
-  select(
-    obsessive_compulsive_disorders,
-    obsessive_compulsive_disorders_numeric,
-    mhd.obsessivecompulsive_disorder_ocd,
-    mhd.obsessivecompulsive_disorder_ocd_numeric,
-    mhd.obsessive_compulsive_related_disorders,
-    mhd.obsessive_compulsive_related_disorders_numeric,
-    mhd.body_dysmorphic_disorder_bdd,
-    mhd.body_dysmorphic_disorder_bdd_numeric
-  )
-}
-```
-
-```{r Check obsessive_compulsive_disorders ramp}
-if(RAMP == TRUE) {
-mhd.raw.id %>%
-  select(
-    obsessive_compulsive_disorders,
-    obsessive_compulsive_disorders_numeric,
-    mhd.obsessivecompulsive_disorder_ocd,
-    mhd.obsessivecompulsive_disorder_ocd_numeric,
-    mhd.skin_picking_obsessive_compulsive,
-    mhd.skin_picking_obsessive_compulsive_numeric,
-    mhd.body_dysmorphic_disorder_bdd,
-    mhd.body_dysmorphic_disorder_bdd_numeric
-  )
-}
-```
-
-### Psychotic disorders
-"mhd.schizophrenia_numeric"                                 
-"mhd.schizoaffective_disorder_numeric"                      
-"mhd.type_psychosis_psychotic_illness_numeric" 
-```{r mhd psychotic_disorders}
-if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE | RAMP == TRUE) {
-mhd.raw.id <- mhd.raw.id %>%
-  mutate(
-    psychotic_disorders_numeric =
-      case_when(
-        mhd.schizophrenia_numeric == "1" ~ 1,
-        mhd.schizoaffective_disorder_numeric == "1" ~ 1,
-        mhd.type_psychosis_psychotic_illness_numeric == "1" ~ 1,
-        (mhd.schizophrenia_numeric == "0" &
-        (mhd.schizoaffective_disorder_numeric == "0" | is.na(mhd.schizoaffective_disorder_numeric == "0") & #NA included because some cohorts don't have schizoaffective disorder
-        mhd.type_psychosis_psychotic_illness_numeric == "0") ~ 0)
-        )
-    )
-
-mhd.raw.id <- mhd.raw.id %>%
-  mutate(
-    psychotic_disorders =
-      recode_factor(psychotic_disorders_numeric,
-                    "0" = "No psychotic disorder",
-                    "1" = "Psychotic disorder",
-                    missing = NA_character_
-                    )
-  )
-
-mhd.raw.id %>%
-  freq(psychotic_disorders)
-}
-```
-
-Overlap between self-report schizophrenia and bipolar disorder
-+++CH: Check overlap between schizophrenia group and bipolar disorder
-++KT: Only 63 with comorbid self-report bipolar disorder and schizophrenia. More likely to have shared symptoms, less likely to have confirmed diagnoses of both. Could be too severe to be in GLAD?
-```{r mhd bipolar_and_schizophrenia_numeric}
-if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE | RAMP == TRUE) {
-mhd.raw.id <- mhd.raw.id %>%
-  mutate(
-    bipolar_and_schizophrenia_numeric =
-      case_when(
-        psychotic_disorders_numeric == 0 &
-          mhd.mania_hypomania_bipolar_or_manicdepression_numeric == 0 ~ 0,
-        psychotic_disorders_numeric == 1 &
-          mhd.mania_hypomania_bipolar_or_manicdepression_numeric == 1 ~ 1,
-        psychotic_disorders_numeric == 1 &
-          mhd.mania_hypomania_bipolar_or_manicdepression_numeric == 0 ~ 2,
-        psychotic_disorders_numeric == 0 &
-          mhd.mania_hypomania_bipolar_or_manicdepression_numeric == 1 ~ 3
-      )
-  )
-
-mhd.raw.id <- mhd.raw.id %>%
-  mutate(
-    bipolar_and_schizophrenia =
-      recode_factor(bipolar_and_schizophrenia_numeric,
-                    "0" = "No psychotic or bipolar disorder",
-                    "1" = "Psychotic and bipolar disorder",
-                    "2" = "Only psychotic disorder",
-                    "3" = "Only bipolar disorder",
-                    missing = NA_character_
-                    )
-  )
-
-mhd.raw.id %>%
-  freq(bipolar_and_schizophrenia,
-       cumul = F)
-}
-```
-
-```{r Check psychotic_disorders}
-if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE | RAMP == TRUE) {
-mhd.raw.id %>%
-  select(
-    psychotic_disorders,
-    psychotic_disorders_numeric,
-    bipolar_and_schizophrenia,
-    bipolar_and_schizophrenia_numeric,
-    mhd.schizophrenia_numeric,
-    mhd.schizoaffective_disorder_numeric,
-    mhd.mania_hypomania_bipolar_or_manicdepression,
-    mhd.mania_hypomania_bipolar_or_manicdepression_numeric,
-    mhd.type_psychosis_psychotic_illness_numeric,
-    mhd.schizophrenia,
-    mhd.schizoaffective_disorder,
-    mhd.type_psychosis_psychotic_illness
-  )
-}
-```
-
-### Personality disorders
-++KT: For all cluster coding chunks - have added other clusters as == 0, so that they are not coerced into NAs. 
-Cluster A
-1. Paranoid                         28 ( 1.0%)
-2. Schizoid                         15 ( 0.5%)
-3. Schizotypal                      14 ( 0.5%)
-```{r mhd personality_cluster_a}
-if(GLAD == TRUE | NBR == TRUE | RAMP == TRUE) {
-mhd.raw.id <- mhd.raw.id %>%
-  mutate(
-    personality_cluster_a_numeric =
-      case_when(
-        mhd.personality_disorder_diagnosed_numeric == "1" ~ 1,
-        mhd.personality_disorder_diagnosed_numeric == "2" ~ 1,
-        mhd.personality_disorder_diagnosed_numeric == "3" ~ 1,
-        mhd.personality_disorder_diagnosed_numeric == "4" ~ 0,
-        mhd.personality_disorder_diagnosed_numeric == "5" ~ 0,
-        mhd.personality_disorder_diagnosed_numeric == "6" ~ 0,
-        mhd.personality_disorder_diagnosed_numeric == "7" ~ 0,
-        mhd.personality_disorder_diagnosed_numeric == "8" ~ 0,
-        mhd.personality_disorder_diagnosed_numeric == "9" ~ 0,
-        mhd.personality_disorder_diagnosed_numeric == "10" ~ 0,
-        mhd.personality_disorder_numeric == "0" ~ 0
-      )
-  )
-
-mhd.raw.id <- mhd.raw.id %>%
-  mutate(
-    personality_cluster_a =
-      recode_factor(personality_cluster_a_numeric,
-                    "0" = "No personality disorder cluster A",
-                    "1" = "Personality disorder cluster A",
-                    missing = NA_character_
-                    )
-  )
-
-mhd.raw.id %>%
-  freq(personality_cluster_a,
-       cumul = F)
-}
-```
-
-```{r Check personality_cluster_a}
-if(GLAD == TRUE | NBR == TRUE | RAMP == TRUE) {
-mhd.raw.id %>%
-  select(
-    personality_cluster_a,
-    personality_cluster_a_numeric,
-    mhd.personality_disorder_diagnosed,
-    mhd.personality_disorder_diagnosed_numeric
-  )
-}
-```
-
-Cluster B
-4. Antisocial                       24 ( 0.8%)
-5. Borderline                     2553 (89.4%)
-6. Histrionic                        7 ( 0.2%)
-7. Narcissistic                      8 ( 0.3%)
-
-```{r mhd personality_cluster_b}
-if(GLAD == TRUE | NBR == TRUE | RAMP == TRUE) {
-mhd.raw.id <- mhd.raw.id %>%
-  mutate(
-    personality_cluster_b_numeric =
-      case_when(
-        mhd.personality_disorder_diagnosed_numeric == "1" ~ 0,
-        mhd.personality_disorder_diagnosed_numeric == "2" ~ 0,
-        mhd.personality_disorder_diagnosed_numeric == "3" ~ 0,
-        mhd.personality_disorder_diagnosed_numeric == "4" ~ 1,
-        mhd.personality_disorder_diagnosed_numeric == "5" ~ 1,
-        mhd.personality_disorder_diagnosed_numeric == "6" ~ 1,
-        mhd.personality_disorder_diagnosed_numeric == "7" ~ 1,
-        mhd.personality_disorder_diagnosed_numeric == "8" ~ 0,
-        mhd.personality_disorder_diagnosed_numeric == "9" ~ 0,
-        mhd.personality_disorder_diagnosed_numeric == "10" ~ 0,
-        mhd.personality_disorder_numeric == "0" ~ 0
-      )
-  )
-
-mhd.raw.id <- mhd.raw.id %>%
-  mutate(
-    personality_cluster_b =
-      recode_factor(personality_cluster_b_numeric,
-                    "0" = "No personality disorder cluster B",
-                    "1" = "Personality disorder cluster B",
-                    missing = NA_character_
-                    )
-  )
-
-mhd.raw.id %>%
-  freq(personality_cluster_b,
-       cumul = F)
-}
-```
-
-```{r Check personality_cluster_b}
-if(GLAD == TRUE | NBR == TRUE | RAMP == TRUE) {
-mhd.raw.id %>%
-  select(
-    personality_cluster_b,
-    personality_cluster_b_numeric,
-    mhd.personality_disorder_diagnosed,
-    mhd.personality_disorder_diagnosed_numeric
-  )
-}
-```
-
-Cluster C
-8. Avoidant/anxious                133 ( 4.7%)
-9. Dependent                        29 ( 1.0%)
-10. Obsessive-compulsive
-```{r glad mhd personality_cluster_c}
-if(GLAD == TRUE | NBR == TRUE | RAMP == TRUE) {
-mhd.raw.id <- mhd.raw.id %>%
-  mutate(
-    personality_cluster_c_numeric =
-      case_when(
-        mhd.personality_disorder_diagnosed_numeric == "1" ~ 0,
-        mhd.personality_disorder_diagnosed_numeric == "2" ~ 0,
-        mhd.personality_disorder_diagnosed_numeric == "3" ~ 0,
-        mhd.personality_disorder_diagnosed_numeric == "4" ~ 0,
-        mhd.personality_disorder_diagnosed_numeric == "5" ~ 0,
-        mhd.personality_disorder_diagnosed_numeric == "6" ~ 0,
-        mhd.personality_disorder_diagnosed_numeric == "7" ~ 0,
-        mhd.personality_disorder_diagnosed_numeric == "8" ~ 1,
-        mhd.personality_disorder_diagnosed_numeric == "9" ~ 1,
-        mhd.personality_disorder_diagnosed_numeric == "10" ~ 1,
-        mhd.personality_disorder_numeric == "0" ~ 0
-      )
-  )
-
-mhd.raw.id <- mhd.raw.id %>%
-  mutate(
-    personality_cluster_c =
-      recode_factor(personality_cluster_c_numeric,
-                    "0" = "No personality disorder cluster C",
-                    "1" = "Personality disorder cluster C",
-                    missing = NA_character_
-                    )
-  )
-
-mhd.raw.id %>%
-  freq(personality_cluster_c,
-       cumul = F)
-}
-```
-
-```{r Check personality_cluster_c}
-if(GLAD == TRUE | NBR == TRUE | RAMP == TRUE) {
-mhd.raw.id %>%
-  select(
-    personality_cluster_c,
-    personality_cluster_c_numeric,
-    mhd.personality_disorder_diagnosed,
-    mhd.personality_disorder_diagnosed_numeric
-  )
-}
-```
-
-### Controls
-These individuals have no self report diagnosis of any kind that we measure. 
-```{r mhd control}
-mhd.raw.id <- mhd.raw.id %>%
-  mutate(
-    control_numeric =
-      if_else(
-    depressive_disorders_numeric == "0" &
-    anxiety_disorders_numeric == "0" &
-    eating_disorders_numeric == "0" &
-    obsessive_compulsive_disorders_numeric == "0" &
-    psychotic_disorders_numeric == "0" &
-    mhd.mania_hypomania_bipolar_or_manicdepression_numeric == "0" &
-    mhd.posttraumatic_stress_disorder_ptsd_numeric == "0" &
-    mhd.autism_aspergers_or_autistic_spectrum_disorder_numeric == "0" &
-    mhd.attention_deficit_hyperactivity_disorder_numeric == "0" &
-    mhd.personality_disorder_numeric == "0", 
-    true = 1, 
-    false = 0, 
-    NA_real_)
-  )
-
-mhd.raw.id <- mhd.raw.id %>%
-  mutate(
-    control =
-      recode_factor(control_numeric,
-                    "0" = "No control",
-                    "1" = "Control",
-                    missing = NA_character_
-                    )
-  )
-
-mhd.raw.id %>%
-  freq(control,
-       cumul = F)
-```
-
-## Total disorder count
-```{r disorders_total_count}
-disorder_columns <- c(
-    "depressive_disorders_numeric",
-    "anxiety_disorders_numeric",
-    "eating_disorders_numeric",
-    "obsessive_compulsive_disorders_numeric",
-    "psychotic_disorders_numeric",
-    "mhd.mania_hypomania_bipolar_or_manicdepression_numeric",
-    "mhd.posttraumatic_stress_disorder_ptsd_numeric",
-    "mhd.autism_aspergers_or_autistic_spectrum_disorder_numeric",
-    "mhd.attention_deficit_hyperactivity_disorder_numeric",
-    "mhd.personality_disorder_numeric"
-)
-
-mhd.raw.id <- mhd.raw.id %>%
-  mutate(
-    disorders_total_count =
-      rowSums(.[disorder_columns])
-  )
-
-mhd.raw.id %>%
-  freq(disorders_total_count,
-       cumul = F)
-```
-
-## Comorbidity count
-```{r cormorbidity_total_count}
-mhd.raw.id <- mhd.raw.id %>%
-  mutate(
-    comorbidity_total_count_numeric = 
-      case_when(
-        disorders_total_count == 1 ~ 0,
-        disorders_total_count > 1 ~ disorders_total_count - 1
-  )
-  )
-
-mhd.raw.id %>%
-  freq(comorbidity_total_count_numeric,
-       cumul = F)
-```
-
-```{r comordbitiy_total_count_factor}
-mhd.raw.id <- mhd.raw.id %>%
-  mutate(
-    comorbidity_total_count_factor_numeric =
-      case_when(
-    comorbidity_total_count_numeric == "0" ~ 0,
-    comorbidity_total_count_numeric == "1" ~ 1,
-    comorbidity_total_count_numeric == "2" ~ 2,
-    comorbidity_total_count_numeric > 2 ~ 3
-    )
-  )
-
-mhd.raw.id <- mhd.raw.id %>%
-  mutate(
-    comorbidity_total_count_factor =
-      recode_factor(comorbidity_total_count_factor_numeric,
-                    "0" = "No comorbidity",
-                    "1" = "1 comorbid disoder",
-                    "2" = "2 comorbid disoders",
-                    "3" = "3+ comorbid disoders",
-                    missing = NA_character_
-                    )
-  )
-
-mhd.raw.id %>%
-  freq(comorbidity_total_count_factor,
-       cumul = F)
-```
-
-## Inspection
-```{r glad mhd head}
-head(mhd.raw.id)
-```
-
-```{r mhd summary}
-summarytools::dfSummary(
-  mhd.raw.id,
+  dat,
   graph.col = F,
@@
 ```
-
-Create new dataframe with the derived categories
-```{r mhd categories}
-if(GLAD == TRUE | NBR == TRUE | RAMP == TRUE) {
-mhd.raw.categories <- mhd.raw.id %>%
-  select(
-    Sample,
-    ID,
-    anxiety_disorders_numeric,
-    anxiety_disorders,
-    mhd.specific_phobia_e.g._phobia_of_flying_numeric,
-    mhd.specific_phobia_e.g._phobia_of_flying,
-    mhd.social_anxiety_or_social_phobia_numeric,
-    mhd.social_anxiety_or_social_phobia,
-    agoraphobia_panic_disorder_numeric,
-    agoraphobia_panic_disorder,
-    depressive_disorders_numeric,
-    depressive_disorders,
-    eating_disorders_numeric,
-    eating_disorders,
-    obsessive_compulsive_disorders_numeric,
-    obsessive_compulsive_disorders,
-    psychotic_disorders_numeric,
-    psychotic_disorders,
-    mhd.mania_hypomania_bipolar_or_manicdepression_numeric,
-    mhd.mania_hypomania_bipolar_or_manicdepression,
-    mhd.posttraumatic_stress_disorder_ptsd_numeric,
-    mhd.posttraumatic_stress_disorder_ptsd,
-    mhd.autism_aspergers_or_autistic_spectrum_disorder_numeric,
-    mhd.autism_aspergers_or_autistic_spectrum_disorder,
-    mhd.attention_deficit_hyperactivity_disorder_numeric,
-    mhd.attention_deficit_hyperactivity_disorder,
-    mhd.personality_disorder_numeric,
-    mhd.personality_disorder,
-    personality_cluster_a_numeric,
-    personality_cluster_a,
-    personality_cluster_b_numeric,
-    personality_cluster_b,
-    personality_cluster_c_numeric,
-    personality_cluster_c,
-    depression_and_anxiety_numeric,
-    depression_and_anxiety,
-    restricting_vs_binge_eating_eating_disorders_numeric,
-    restricting_vs_binge_eating_eating_disorders,
-    bipolar_and_schizophrenia_numeric,
-    bipolar_and_schizophrenia,
-    control_numeric,
-    control,
-    disorders_total_count,
-    comorbidity_total_count_numeric,
-    comorbidity_total_count_factor_numeric,
-    comorbidity_total_count_factor
-    )
-}
-```
-
-```{r mhd categories}
-if(EDGI == TRUE) {
-mhd.raw.categories <- mhd.raw.id %>%
-  select(
-    Sample,
-    ID,
-    anxiety_disorders_numeric,
-    anxiety_disorders,
-    mhd.specific_phobia_e.g._phobia_of_flying_numeric,
-    mhd.specific_phobia_e.g._phobia_of_flying,
-    mhd.social_anxiety_or_social_phobia_numeric,
-    mhd.social_anxiety_or_social_phobia,
-    agoraphobia_panic_disorder_numeric,
-    agoraphobia_panic_disorder,
-    depressive_disorders_numeric,
-    depressive_disorders,
-    eating_disorders_numeric,
-    eating_disorders,
-    obsessive_compulsive_disorders_numeric,
-    obsessive_compulsive_disorders,
-    psychotic_disorders_numeric,
-    psychotic_disorders,
-    mhd.mania_hypomania_bipolar_or_manicdepression_numeric,
-    mhd.mania_hypomania_bipolar_or_manicdepression,
-    mhd.posttraumatic_stress_disorder_ptsd_numeric,
-    mhd.posttraumatic_stress_disorder_ptsd,
-    mhd.autism_aspergers_or_autistic_spectrum_disorder_numeric,
-    mhd.autism_aspergers_or_autistic_spectrum_disorder,
-    mhd.attention_deficit_hyperactivity_disorder_numeric,
-    mhd.attention_deficit_hyperactivity_disorder,
-    mhd.personality_disorder_numeric,
-    mhd.personality_disorder,
-#    personality_cluster_a_numeric,
-#    personality_cluster_a,
-#    personality_cluster_b_numeric,
-#    personality_cluster_b,
-#    personality_cluster_c_numeric,
-#    personality_cluster_c,
-    depression_and_anxiety_numeric,
-    depression_and_anxiety,
-    restricting_vs_binge_eating_eating_disorders_numeric,
-    restricting_vs_binge_eating_eating_disorders,
-    bipolar_and_schizophrenia_numeric,
-    bipolar_and_schizophrenia,
-    control_numeric,
-    control,
-    disorders_total_count,
-    comorbidity_total_count_numeric,
-    comorbidity_total_count_factor_numeric,
-    comorbidity_total_count_factor
-    ) %>%
-  add_column(
-    personality_cluster_a_numeric = NA_real_,
-    personality_cluster_a = NA_real_,
-    personality_cluster_b_numeric = NA_real_,
-    personality_cluster_b = NA_real_,
-    personality_cluster_c_numeric = NA_real_,
-    personality_cluster_c = NA_real_    
-  )
-}
-```
-
-# Prepandemic
-
-## gad (prepan)
-
-```{r glad gad prepan cols}
-if(GLAD == TRUE){
-glad.gad.raw <- readRDS(file = paste0(data.raw_path, "/glad/gad_glad.rds"))
-dim(glad.gad.raw)
-colnames(glad.gad.raw)
-}
-```
-
-```{r glad gad prepan cleaning}
-if(GLAD ==TRUE){
-exclude_cols <- c("Sample",
-                  "ID")
-glad.gad.raw.id <- glad.gad.raw %>%
-  drop_na(externalDataReference) %>% # Drop NAs
-  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
-  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
-  mutate(ID = as.numeric(ID)) %>%
-  select(
-    Sample, # Sample
-    ID, # ID
-    gad.feeling_nervous_anxious_or_on_edge_prepan = gad.feeling_nervous_anxious_or_on_edge,
-    gad.control_worrying_stop_prepan = gad.control_worrying_stop,
-    gad.worrying_too_much_about_different_things_prepan = gad.worrying_too_much_about_different_things,
-    gad.trouble_relaxing_prepan = gad.trouble_relaxing,
-    gad.sit_restless_hard_prepan = gad.sit_restless_hard,
-    gad.becoming_easily_annoyed_or_irritable_prepan = gad.becoming_easily_annoyed_or_irritable,
-    gad.awful_feeling_afraid_happen_prepan = gad.awful_feeling_afraid_happen
-  ) %>%
-  add_numeric(., exclude = exclude_cols) %>%
-  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
-  mutate_if(is.numeric, ~na_if(., -99)) %>%
-  mutate_if(is.numeric, ~na_if(., -77)) %>%
-  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
-  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
-
-# Inspect dimensions
-dim(glad.gad.raw.id)
-# Inspect colnames
-colnames(glad.gad.raw.id)
-#Differences
-dim(glad.gad.raw)[1]-dim(glad.gad.raw.id)[1]
-}
-```
-
-```{r glad copy prepan gad}
-if(GLAD == TRUE){
-prepan.gad.raw.id <- glad.gad.raw.id
-}
-```
-
-```{r edgi gad prepan cols}
-if(EDGI == TRUE){
-  edgi.gad.raw <- readRDS(file = paste0(data.raw_path, "/edgi/gad_edgi.rds"))
-  dim(edgi.gad.raw)
-  colnames(edgi.gad.raw)
-}
-```
-
-```{r edgi gad prepan cleaning}
-if(EDGI == TRUE){
-exclude_cols <- c("Sample",
-                  "ID")
-
-edgi.gad.raw.id <- edgi.gad.raw %>%
-  drop_na(externalDataReference) %>% # Drop NAs
-  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
-  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
-  mutate(ID = as.numeric(ID)) %>%
-  select(
-    Sample, # Sample
-    ID, # ID
-    gad.feeling_nervous_anxious_or_on_edge_prepan = gad.feeling_nervous_anxious_or_on_edge,
-    gad.control_worrying_stop_prepan = gad.control_worrying_stop,
-    gad.worrying_too_much_about_different_things_prepan = gad.worrying_too_much_about_different_things,
-    gad.trouble_relaxing_prepan = gad.trouble_relaxing,
-    gad.sit_restless_hard_prepan = gad.sit_restless_hard,
-    gad.becoming_easily_annoyed_or_irritable_prepan = gad.becoming_easily_annoyed_or_irritable,
-    gad.awful_feeling_afraid_happen_prepan = gad.awful_feeling_afraid_happen
-  ) %>%
-  add_numeric(., exclude = exclude_cols) %>%
-  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
-  mutate_if(is.numeric, ~na_if(., -99)) %>%
-  mutate_if(is.numeric, ~na_if(., -77)) %>%
-  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
-  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
-
-# Inspect dimensions
-dim(edgi.gad.raw.id)
-# Inspect colnames
-colnames(edgi.gad.raw.id)
-#Differences
-dim(edgi.gad.raw)[1]-dim(edgi.gad.raw.id)[1]
-}
-```
-
-```{r edgi copy prepan gad}
-if(EDGI == TRUE){
-  prepan.gad.raw.id <- edgi.gad.raw.id
-}
-```
-
-Calculate sum score for GAD-7
-Max should be 21.
-
-*Note that scores with missingness will be changed to NA later in the script
-```{r gad sum score prepan raw}
-if(GLAD ==TRUE | EDGI == TRUE){
-# Create vector with scoring key: If the item is reversed coded use -1. 
-# There needs to be the correct number of values for each item in the questionnaire. 
-gad.items_key_prepan <- c(1,1,1,1,1,1,1)
-
-# Create vector with items that are included in total score
-gad.items_prepan <- c(
-  "gad.feeling_nervous_anxious_or_on_edge_prepan_numeric",
-  "gad.control_worrying_stop_prepan_numeric",
-  "gad.worrying_too_much_about_different_things_prepan_numeric",
-  "gad.trouble_relaxing_prepan_numeric",
-  "gad.sit_restless_hard_prepan_numeric",
-  "gad.becoming_easily_annoyed_or_irritable_prepan_numeric",
-  "gad.awful_feeling_afraid_happen_prepan_numeric"
-  )
-
-# Calulate total score
-gad.scored_items_prepan <- scoreItems(keys = gad.items_key_prepan,
-                                        items = prepan.gad.raw.id[gad.items_prepan],
-                                        totals = TRUE, 
-                                        missing = TRUE, 
-                                        impute = 'none', 
-                                        min = 0, 
-                                        max = 3)
-# Add in column to tibble
-prepan.gad.raw.id$gad.sum_score_prepan_raw <- gad.scored_items_prepan$scores
-
-# Look at values
-prepan.gad.raw.id %>%
-  descr(gad.sum_score_prepan_raw,
-        stats = "common"
-        )
-}
-```
-
-missingness (NAs per person)
-
-prepandemic
-```{r gad prepan missingness}
-if(GLAD ==TRUE | EDGI == TRUE){
-prepan.gad.raw.id <- prepan.gad.raw.id %>%
-  mutate(
-    na_per_person_gad_prepan =         # variable for NA per person
-      rowSums(                       
-        is.na(.[gad.items_prepan])
-      )
-  )
-
-prepan.gad.raw.id %>%
-  freq(na_per_person_gad_prepan,
-       cumul = F)
-}
-```
-
-```{r gad prepan sum score if missigng items set to NA}
-if(GLAD ==TRUE | EDGI == TRUE){
-prepan.gad.raw.id <- prepan.gad.raw.id %>%
-  mutate(
-    gad.sum_score_prepan =
-      if_else(condition = na_per_person_gad_prepan > 0,
-              true = NA_real_,
-              false = gad.sum_score_prepan_raw,
-              missing = NA_real_
-              )
-  )
-
-prepan.gad.raw.id %>%
-  descr(gad.sum_score_prepan_raw, stats = "common")
-
-prepan.gad.raw.id %>%
-  descr(gad.sum_score_prepan, stats = "common")
-}
-```
-
-```{r glad prepan gad head}
-if(GLAD ==TRUE | EDGI == TRUE){
-head(prepan.gad.raw.id)
-}
-```
-
-```{r glad prepan gad summary}
-if(GLAD ==TRUE | EDGI == TRUE){
-summarytools::dfSummary(
-  prepan.gad.raw.id,
-  graph.col = F,
-  valid.col = F,
-  labels.col = F)
-}
-```
-
-## pcl (prepan)
-
-```{r glad prepandemic pcl cols}
-if(GLAD == TRUE) {
-glad.pcl.raw <- readRDS(file = paste0(data.raw_path,"/glad/pcl_glad.rds"))
-dim(glad.pcl.raw)
-colnames(glad.pcl.raw)
-}
-```
-
-```{r glad prepandemic pcl cleaning}
-if(GLAD == TRUE) {
-exclude_cols <- c("Sample",
-                  "ID")
-glad.pcl.raw.id <- glad.pcl.raw %>%
-  drop_na(externalDataReference) %>% # Drop NAs
-  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
-  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
-  mutate(ID = as.numeric(ID)) %>%
-  select(
-    Sample, # Sample
-    ID, # ID
-    pcl.stressful_experience_repeated_images_prepan = pcl.stressful_experience_repeated_images,
-    pcl.stressful_experience_upset_reminded_prepan = pcl.stressful_experience_upset_reminded,
-    pcl.stressful_situation_avoiding_activities_prepan = pcl.stressful_situation_avoiding_activities,
-    pcl.cut_people_feeling_distant_prepan = pcl.cut_people_feeling_distant,
-    pcl.feeling_irritable_or_having_angry_outbursts_prepan = pcl.feeling_irritable_or_having_angry_outbursts,
-    pcl.difficulty_concentrating_prepan = pcl.difficulty_concentrating
-  ) %>%
-  add_numeric(., exclude = exclude_cols) %>%
-  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
-  mutate_if(is.numeric, ~na_if(., -99)) %>%
-  mutate_if(is.numeric, ~na_if(., -77)) %>%
-  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
-  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
-
-# Inspect dimensions
-dim(glad.pcl.raw.id)
-# Inspect colnames
-colnames(glad.pcl.raw.id)
-#Differences
-dim(glad.pcl.raw)[1]-dim(glad.pcl.raw.id)[1]
-}
-```
-
-```{r glad pcl prepan copy}
-if(GLAD == TRUE) {
-  prepan.pcl.raw.id <- glad.pcl.raw.id
-}
-```
-
-```{r edgi pcl cols}
-if(EDGI == TRUE) {
-  edgi.pcl.raw <- readRDS(file = paste0(data.raw_path,"/edgi/pcl_edgi.rds"))
-  dim(edgi.pcl.raw)
-  colnames(edgi.pcl.raw)
-}
-```
-
-```{r edgi pcl cleaning}
-if(EDGI == TRUE) {
-  edgi.pcl.raw.id <- edgi.pcl.raw %>%
-    drop_na(externalDataReference) %>% # Drop NAs
-    distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
-    separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
-    mutate(ID = as.numeric(ID)) %>%
-    select(
-      Sample, # Sample
-      ID, # ID
-      pcl.stressful_experience_repeated_images_prepan = pcl.stressful_experience_repeated_images,
-      pcl.stressful_experience_upset_reminded_prepan = pcl.stressful_experience_upset_reminded,
-      pcl.stressful_situation_avoiding_activities_prepan = pcl.stressful_situation_situations_reminded, # different to glad: pcl.stressful_situation_avoiding_activities,
-      pcl.cut_people_feeling_distant_prepan = pcl.cut_people_feeling_distant,
-      pcl.feeling_irritable_or_having_angry_outbursts_prepan = pcl.feeling_irritable_or_having_angry_outbursts,
-      pcl.difficulty_concentrating_prepan = pcl.difficulty_concentrating
-    ) %>%
-    add_numeric(., exclude = exclude_cols) %>%
-    mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
-    mutate_if(is.numeric, ~na_if(., -99)) %>%
-    mutate_if(is.numeric, ~na_if(., -77)) %>%
-    mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
-    mutate_if(is.factor, ~na_if(., "Don't know")) %>%
-    mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
-    mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
-    mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
-    mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
-    mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
-    mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
-
-  # Inspect dimensions
-  dim(edgi.pcl.raw.id)
-  # Inspect colnames
-  colnames(edgi.pcl.raw.id)
-  #Differences
-  dim(edgi.pcl.raw)[1]-dim(edgi.pcl.raw.id)[1]
-}
-```
-
-```{r edgi pcl prepan copy}
-if(EDGI == TRUE) {
-  prepan.pcl.raw.id <- edgi.pcl.raw.id
-}
-```
-
-Calculate sum score for PCL-6
-
-*Note that scores with missingness will be changed to NA later in the script
-```{r pcl sum score prepan}
-if(GLAD == TRUE | EDGI == TRUE){
-# Create vector with scoring key: If the item is reversed coded use -1. 
-# There needs to be the correct number of values for each item in the questionnaire. 
-pcl.items_key_prepan <- c(1,1,1,1,1,1)
-
-# Create vector with items that are included in total score
-pcl.items_prepan <- c(
-  "pcl.stressful_experience_repeated_images_prepan_numeric",
-  "pcl.stressful_experience_upset_reminded_prepan_numeric",
-  "pcl.stressful_situation_avoiding_activities_prepan_numeric",
-  "pcl.cut_people_feeling_distant_prepan_numeric",
-  "pcl.feeling_irritable_or_having_angry_outbursts_prepan_numeric",
-  "pcl.difficulty_concentrating_prepan_numeric"
-  )
-
-# Calulate total score
-pcl.scored_items_prepan <- scoreItems(keys = pcl.items_key_prepan,
-                                        items = prepan.pcl.raw.id[pcl.items_prepan],
-                                        totals = TRUE, 
-                                        missing = TRUE, 
-                                        impute = 'none', 
-                                        min = 1, 
-                                        max = 5)
-# Add in column to tibble
-prepan.pcl.raw.id$pcl.sum_score_prepan_raw <- pcl.scored_items_prepan$scores
-
-# Look at values
-prepan.pcl.raw.id %>%
-  descr(pcl.sum_score_prepan_raw,
-        stats = "common"
-        )
-}
-```
-
-Missigness
-
-prepandemic
-```{r pcl prepan missingness}
-if(GLAD == TRUE | EDGI == TRUE){
-prepan.pcl.raw.id <- prepan.pcl.raw.id %>%
-  mutate(
-    na_per_person_pcl_prepan =         # variable for NA per person
-      rowSums(                       
-        is.na(.[pcl.items_prepan])
-      )
-  )
-
-prepan.pcl.raw.id %>%
-  freq(na_per_person_pcl_prepan,
-       cumul = F)
-}
-```
-
-```{r pcl prepan sum score if missigng items set to NA}
-if(GLAD == TRUE | EDGI == TRUE){
-prepan.pcl.raw.id <- prepan.pcl.raw.id %>%
-  mutate(
-    pcl.sum_score_prepan =
-      if_else(condition = na_per_person_pcl_prepan > 0,
-              true = NA_real_,
-              false = pcl.sum_score_prepan_raw,
-              missing = NA_real_
-      )
-  )
-
-prepan.pcl.raw.id %>%
-  descr(pcl.sum_score_prepan_raw, stats = "common")
-
-prepan.pcl.raw.id %>%
-  descr(pcl.sum_score_prepan, stats = "common")
-}
-```
-
-```{r pcl prepan head}
-if(GLAD == TRUE | EDGI == TRUE){
-head(prepan.pcl.raw.id)
-}
-```
-
-```{r pcl prepan summary}
-if(GLAD == TRUE | EDGI == TRUE){
-summarytools::dfSummary(
-  prepan.pcl.raw.id,
-  graph.col = F,
-  valid.col = F, labels.col = F)
-}
-```
-
-## phq (prepan)
-
-```{r glad phq cols}
-if(GLAD == TRUE){
-glad.phq.raw <- readRDS(file = paste0(data.raw_path, "/glad/phq_glad.rds"))
-dim(glad.phq.raw)
-colnames(glad.phq.raw)
-}
-```
-
-```{r glad phq cleaning}
-if(GLAD == TRUE){
-glad.phq.raw.id <- glad.phq.raw %>%
-  drop_na(externalDataReference) %>% # Drop NAs
-  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
-  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
-  mutate(ID = as.numeric(ID)) %>%
-  select(
-    Sample, # Sample
-    ID, # ID
-    phq.little_interest_or_pleasure_in_doing_things_prepan = phq.little_interest_or_pleasure_in_doing_things,
-    phq.feeling_down_depressed_or_hopeless_prepan = phq.feeling_down_depressed_or_hopeless,
-    phq.staying_asleep_sleeping_trouble_prepan = phq.staying_asleep_sleeping_trouble,
-    phq.feeling_tired_or_having_little_energy_prepan = phq.feeling_tired_or_having_little_energy,
-    phq.poor_appetite_or_overeating_prepan = phq.poor_appetite_or_overeating,
-    phq.feeling_bad_failure_family_prepan = phq.feeling_bad_failure_family,
-    phq.trouble_concentrating_reading_newspaper_prepan = phq.trouble_concentrating_reading_newspaper,
-    phq.moving_fidgety_noticed_opposite_prepan = phq.moving_fidgety_noticed_opposite,
-    phq.dead_hurting_thoughts_prepan = phq.dead_hurting_thoughts
-  ) %>%
-  add_numeric(., exclude = exclude_cols) %>%
-  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
-  mutate_if(is.numeric, ~na_if(., -99)) %>%
-  mutate_if(is.numeric, ~na_if(., -77)) %>%
-  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
-  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
-
-# Inspect dimensions
-dim(glad.phq.raw.id)
-# Inspect colnames
-colnames(glad.phq.raw.id)
-#Differences
-dim(glad.phq.raw)[1]-dim(glad.phq.raw.id)[1]
-}
-```
-
-```{r glad phq prepan copy}
-if(GLAD == TRUE) {
-  prepan.phq.raw.id <- glad.phq.raw.id
-}
-```
-
-```{r edgi phq cols}
-if(EDGI == TRUE){
-  edgi.phq.raw <- readRDS(file = paste0(data.raw_path, "/edgi/phq_edgi.rds"))
-  dim(edgi.phq.raw)
-  colnames(edgi.phq.raw)
-}
-```
-
-```{r edgi phq cleaning}
-if(EDGI == TRUE){
-  edgi.phq.raw.id <- edgi.phq.raw %>%
-    drop_na(externalDataReference) %>% # Drop NAs
-    distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
-    separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
-    mutate(ID = as.numeric(ID)) %>%
-    select(
-      Sample, # Sample
-      ID, # ID
-      phq.little_interest_or_pleasure_in_doing_things_prepan = phq.little_interest_or_pleasure_in_doing_things,
-      phq.feeling_down_depressed_or_hopeless_prepan = phq.feeling_down_depressed_or_hopeless,
-      phq.staying_asleep_sleeping_trouble_prepan = phq.staying_asleep_sleeping_trouble,
-      phq.feeling_tired_or_having_little_energy_prepan = phq.feeling_tired_or_having_little_energy,
-      phq.poor_appetite_or_overeating_prepan = phq.poor_appetite_or_overeating,
-      phq.feeling_bad_failure_family_prepan = phq.feeling_bad_failure_family,
-      phq.trouble_concentrating_reading_newspaper_prepan = phq.trouble_concentrating_reading_newspaper,
-      phq.moving_fidgety_noticed_opposite_prepan = phq.moving_fidgety_noticed_opposite,
-      phq.dead_hurting_thoughts_prepan = phq.dead_hurting_thoughts
-    ) %>%
-    add_numeric(., exclude = exclude_cols) %>%
-    mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
-    mutate_if(is.numeric, ~na_if(., -99)) %>%
-    mutate_if(is.numeric, ~na_if(., -77)) %>%
-    mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
-    mutate_if(is.factor, ~na_if(., "Don't know")) %>%
-    mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
-    mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
-    mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
-    mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
-    mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
-    mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
-
-  # Inspect dimensions
-  dim(edgi.phq.raw.id)
-  # Inspect colnames
-  colnames(edgi.phq.raw.id)
-  #Differences
-  dim(edgi.phq.raw)[1]-dim(edgi.phq.raw.id)[1]
-}
-```
-
-```{r edgi phq prepan copy}
-if(EDGI == TRUE) {
-  prepan.phq.raw.id <- edgi.phq.raw.id
-}
-```
-
-Calculate sum score for PHQ-9
-
-*Note that scores with missingness will be changed to NA later in the script
-```{r phq sum score prepan}
-if(GLAD == TRUE | EDGI == TRUE) {
-# Create vector with scoring key: If the item is reversed coded use -1. 
-# There needs to be the correct number of values for each item in the questionnaire. 
-phq.items_key_prepan <- c(1,1,1,1,1,1,1,1,1)
-
-# Create vector with items that are included in sum score
-phq.items_prepan <- c(
-  "phq.little_interest_or_pleasure_in_doing_things_prepan_numeric",
-  "phq.feeling_down_depressed_or_hopeless_prepan_numeric",
-  "phq.staying_asleep_sleeping_trouble_prepan_numeric",
-  "phq.feeling_tired_or_having_little_energy_prepan_numeric",
-  "phq.poor_appetite_or_overeating_prepan_numeric",
-  "phq.feeling_bad_failure_family_prepan_numeric",
-  "phq.trouble_concentrating_reading_newspaper_prepan_numeric",
-  "phq.moving_fidgety_noticed_opposite_prepan_numeric",
-  "phq.dead_hurting_thoughts_prepan_numeric"
-  )
-
-# Calulate sum score
-phq.scored_items_prepan <- scoreItems(keys = phq.items_key_prepan,
-                                        items = prepan.phq.raw.id[phq.items_prepan],
-                                        totals = TRUE, 
-                                        missing = TRUE, 
-                                        impute = 'none', 
-                                        min = 0, 
-                                        max = 3)
-# Add in column to tibble
-prepan.phq.raw.id$phq.sum_score_prepan_raw <- phq.scored_items_prepan$scores
-
-# Look at values
-prepan.phq.raw.id %>%
-  descr(phq.sum_score_prepan_raw,
-        stats = "common"
-        )
-}
-```
-
-PHQ missingness (NAs per person)
-
-prepandemic
-```{r phq prepan missingness}
-if(GLAD == TRUE | EDGI == TRUE) {
-prepan.phq.raw.id <- prepan.phq.raw.id %>%
-  mutate(
-    na_per_person_phq_prepan =         # variable for NA per person
-      rowSums(                       
-        is.na(.[phq.items_prepan])
-      )
-  )
-
-prepan.phq.raw.id %>%
-  freq(na_per_person_phq_prepan,
-       cumul = F)
-}
-```
-
-```{r phq prepan missingness 8 items}
-if(GLAD == TRUE | EDGI == TRUE) {
-prepan.phq.raw.id <- prepan.phq.raw.id %>%
-  mutate(
-    phq.missing_only_suicide_item_prepan = 
-      if_else(
-        condition = na_per_person_phq_prepan == 1 & 
-          is.na(phq.dead_hurting_thoughts_prepan_numeric), 
-        true = 1,
-        false = 0,
-        missing = NA_real_
-      )
-  )
-
-prepan.phq.raw.id %>%
-  freq(phq.missing_only_suicide_item_prepan,
-       cumul = F)
-}
-```
-
-all times
-```{r phq prepan sum score if missigng items set to NA - all items}
-if(GLAD == TRUE | EDGI == TRUE) {
-prepan.phq.raw.id <- prepan.phq.raw.id %>%
-  mutate(
-    phq.sum_score_prepan =
-      if_else(condition = na_per_person_phq_prepan > 0,
-              true = NA_real_,
-              false = phq.sum_score_prepan_raw,
-              missing = NA_real_
-      )
-  )
-
-prepan.phq.raw.id %>%
-  descr(phq.sum_score_prepan_raw, stats = "common")
-
-prepan.phq.raw.id %>%
-  descr(phq.sum_score_prepan, stats = "common")
-}
-```
-
-+++CH: THINK ABOUT THIS!!!
-
-8 items
-```{r phq prepan sum score if missigng items set to NA - 8 items}
-if(GLAD == TRUE | EDGI == TRUE) {
-prepan.phq.raw.id <- prepan.phq.raw.id %>%
-  mutate(
-    phq.sum_score_8items_prepan =
-      if_else(condition = na_per_person_phq_prepan > 1 &
-                phq.missing_only_suicide_item_prepan == 1,
-              true = NA_real_,
-              false = phq.sum_score_prepan_raw,
-              missing = NA_real_
-      )
-  )
-
-prepan.phq.raw.id %>%
-  descr(phq.sum_score_8items_prepan, stats = "common")
-
-prepan.phq.raw.id %>%
-  descr(phq.sum_score_8items_prepan, stats = "common")
-}
-```
-
-```{r phq prepan head}
-if(GLAD == TRUE | EDGI == TRUE) {
-head(prepan.phq.raw.id)
-}
-```
-
-```{r phq prepan summary}
-if(GLAD == TRUE | EDGI == TRUE) {
-summarytools::dfSummary(
-  prepan.phq.raw.id,
-  graph.col = F,
-  valid.col = F
-  )
-}
-```
-
-## ocir (prepan)
-
-```{r glad ocir prepan cols}
-if(GLAD == TRUE){
-glad.ocir.raw <- readRDS(file = paste0(data.raw_path, "/glad/ocir_glad.rds"))
-dim(glad.ocir.raw)
-colnames(glad.ocir.raw)
-}
-```
-
-```{r glad ocir prepan cleaning}
-if(GLAD == TRUE){
-glad.ocir.raw.id <- glad.ocir.raw %>%
-  drop_na(externalDataReference) %>% # Drop NAs
-  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
-  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
-  mutate(ID = as.numeric(ID),) %>%
-  select(
-    Sample, # Sample
-    ID, # ID
-    ocir.i_repeatedly_check_doors_windows_drawers_etc_prepan = ocir.i_repeatedly_check_doors_windows_drawers_etc.,
-    ocir.arranged_things_change_upset_prepan = ocir.arranged_things_change_upset,
-    ocir.repeat_feel_numbers_prepan = ocir.repeat_feel_numbers,
-    ocir.clean_simply_wash_feel_prepan = ocir.clean_simply_wash_feel,
-    ocir.mind_upset_unpleasant_thoughts_prepan = ocir.mind_upset_unpleasant_thoughts,
-    ocir.afraid_avoid_throwing_things_prepan = ocir.afraid_avoid_throwing_things,
-    ocir.light_switches_water_taps_prepan = ocir.light_switches_water_taps,
-    ocir.arranged_things_prepan = ocir.arranged_things,
-    ocir.good_feel_bad_numbers_prepan = ocir.good_feel_bad_numbers,
-    ocir.hands_longer_wash_prepan = ocir.hands_longer_wash,
-    ocir.saved_things_prepan = ocir.saved_things,
-    ocir.frequently_difficulty_rid_nasty_prepan = ocir.frequently_difficulty_rid_nasty,
-    ocir.i_check_things_more_often_than_necessary_prepan = ocir.i_check_things_more_often_than_necessary.,
-    ocir.arranged_properly_objects_upset_prepan = ocir.arranged_properly_objects_upset,
-    ocir.feel_compelled_count_things_prepan = ocir.feel_compelled_count_things,
-    ocir.strangers_touch_touched_difficult_prepan = ocir.strangers_touch_touched_difficult,
-    ocir.control_difficult_find_thoughts_prepan = ocir.control_difficult_find_thoughts,
-    ocir.i_collect_things_i_dont_need_prepan = ocir.i_collect_things_i_dont_need
-  ) %>%
-  add_numeric(., exclude = exclude_cols) %>%
-  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
-  mutate_if(is.numeric, ~na_if(., -99)) %>%
-  mutate_if(is.numeric, ~na_if(., -77)) %>%
-  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
-  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
-
-# Inspect dimensions
-dim(glad.ocir.raw.id)
-# Inspect colnames
-colnames(glad.ocir.raw.id)
-#Differences
-dim(glad.ocir.raw)[1]-dim(glad.ocir.raw.id)[1]
-}
-```
-
-```{r glad ocir prepan copy}
-if(GLAD == TRUE) {
-  prepan.ocir.raw.id <- glad.ocir.raw.id
-}
-```
-
-```{r edgi ocir prepan cols}
-if(EDGI == TRUE){
-  edgi.ocir.raw <- readRDS(file = paste0(data.raw_path, "/edgi/ocir_edgi.rds"))
-  dim(edgi.ocir.raw)
-  colnames(edgi.ocir.raw)
-}
-```
-
-```{r edgi ocir prepan cleaning}
-if(EDGI == TRUE){
-  edgi.ocir.raw.id <- edgi.ocir.raw %>%
-    drop_na(externalDataReference) %>% # Drop NAs
-    distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
-    separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
-    mutate(ID = as.numeric(ID)) %>%
-    select(
-      Sample, # Sample
-      ID, # ID
-      ocir.i_repeatedly_check_doors_windows_drawers_etc_prepan = ocir.i_repeatedly_check_doors_windows_drawers_etc.,
-      ocir.arranged_things_change_upset_prepan = ocir.arranged_properly_objects_upset, # different GLAD: ocir.arranged_things_change_upset,
-      ocir.repeat_feel_numbers_prepan = ocir.repeat_feel_numbers.87, # ocir.repeat_feel_numbers,
-      ocir.clean_simply_wash_feel_prepan = ocir.clean_simply_wash_feel.9, # ocir.clean_simply_wash_feel,
-      ocir.mind_upset_unpleasant_thoughts_prepan = ocir.mind_upset_unpleasant_thoughts.11, # ocir.mind_upset_unpleasant_thoughts,
-      ocir.afraid_avoid_throwing_things_prepan = ocir.afraid_avoid_throwing_things.7, # ocir.afraid_avoid_throwing_things,
-      ocir.light_switches_water_taps_prepan = ocir.light_switches_water_taps.7, # ocir.light_switches_water_taps,
-      ocir.arranged_things_prepan = ocir.arranged_things.32, # ocir.arranged_things,
-      ocir.good_feel_bad_numbers_prepan = ocir.good_feel_bad_numbers.60, # ocir.good_feel_bad_numbers,
-      ocir.hands_longer_wash_prepan = ocir.hands_longer_wash.23, # ocir.hands_longer_wash,
-      ocir.saved_things_prepan = ocir.saved_things,
-      ocir.frequently_difficulty_rid_nasty_prepan = ocir.frequently_difficulty_rid_nasty.16, # ocir.frequently_difficulty_rid_nasty,
-      ocir.i_check_things_more_often_than_necessary_prepan = ocir.i_check_things_more_often_than_necessary.,
-      ocir.arranged_properly_objects_upset_prepan = ocir.arranged_properly_objects_upset,
-      ocir.feel_compelled_count_things_prepan = ocir.feel_compelled_count_things.27, # ocir.feel_compelled_count_things,
-      ocir.strangers_touch_touched_difficult_prepan = ocir.strangers_touch_touched_difficult.33, # ocir.strangers_touch_touched_difficult,
-      ocir.control_difficult_find_thoughts_prepan = ocir.control_difficult_find_thoughts.30, #ocir.control_difficult_find_thoughts,
-      ocir.i_collect_things_i_dont_need_prepan = ocir.i_collect_things_i_dont_need.348, # ocir.i_collect_things_i_dont_need
-    ) %>%
-    add_numeric(., exclude = exclude_cols) %>%
-    mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
-    mutate_if(is.numeric, ~na_if(., -99)) %>%
-    mutate_if(is.numeric, ~na_if(., -77)) %>%
-    mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
-    mutate_if(is.factor, ~na_if(., "Don't know")) %>%
-    mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
-    mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
-    mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
-    mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
-    mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
-    mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
-
-  # Inspect dimensions
-  dim(edgi.ocir.raw.id)
-  # Inspect colnames
-  colnames(edgi.ocir.raw.id)
-  #Differences
-  dim(edgi.ocir.raw)[1]-dim(edgi.ocir.raw.id)[1]
-}
-```
-
-```{r edgi ocir prepan copy}
-if(EDGI == TRUE) {
-  prepan.ocir.raw.id <- edgi.ocir.raw.id
-}
-```
-
-Calculate sum score for OCI-R
-
-*Note that scores with missingness will be changed to NA later in the script
-```{r ocir sum score prepan}
-if(GLAD == TRUE | EDGI == TRUE) {
-# Create vector with scoring key: If the item is reversed coded use -1. 
-# There needs to be the correct number of values for each item in the questionnaire. 
-ocir.items_key_prepan <- c(1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1)
-
-# Create vector with items that are included in sum score
-ocir.items_prepan = c(
-  "ocir.i_repeatedly_check_doors_windows_drawers_etc_prepan_numeric",
-  "ocir.arranged_things_change_upset_prepan_numeric",
-  "ocir.repeat_feel_numbers_prepan_numeric",
-  "ocir.clean_simply_wash_feel_prepan_numeric",
-  "ocir.mind_upset_unpleasant_thoughts_prepan_numeric",
-  "ocir.afraid_avoid_throwing_things_prepan_numeric",
-  "ocir.light_switches_water_taps_prepan_numeric",
-  "ocir.arranged_things_prepan_numeric",
-  "ocir.good_feel_bad_numbers_prepan_numeric",
-  "ocir.hands_longer_wash_prepan_numeric",
-  "ocir.saved_things_prepan_numeric",
-  "ocir.frequently_difficulty_rid_nasty_prepan_numeric",
-  "ocir.i_check_things_more_often_than_necessary_prepan_numeric",
-  "ocir.arranged_properly_objects_upset_prepan_numeric",
-  "ocir.feel_compelled_count_things_prepan_numeric",
-  "ocir.strangers_touch_touched_difficult_prepan_numeric",
-  "ocir.control_difficult_find_thoughts_prepan_numeric",
-  "ocir.i_collect_things_i_dont_need_prepan_numeric"
-  )
-
-# Calulate sum score
-ocir.scored_items_prepan <- scoreItems(keys = ocir.items_key_prepan,
-                                        items = prepan.ocir.raw.id[ocir.items_prepan],
-                                        totals = TRUE, 
-                                        missing = TRUE, 
-                                        impute = 'none', 
-                                        min = 0, 
-                                        max = 4)
-# Add in column to tibble
-prepan.ocir.raw.id$ocir.sum_score_prepan <- ocir.scored_items_prepan$scores
-
-# Look at values
-prepan.ocir.raw.id %>%
-  descr(ocir.sum_score_prepan,
-        stats = "common"
-        )
-}
-```
-
-prepandemic
-```{r ocir prepan missingness}
-if(GLAD == TRUE | EDGI == TRUE) {
-prepan.ocir.raw.id <- prepan.ocir.raw.id %>%
-  mutate(
-    na_per_person_ocir_prepan =         # variable for NA per person
-      rowSums(                       
-        is.na(.[ocir.items_prepan])
-      )
-  )
-
-prepan.ocir.raw.id %>%
-  freq(na_per_person_ocir_prepan,
-       cumul = F)
-}
-```
-
-```{r ocir prepan head}
-if(GLAD == TRUE | EDGI == TRUE) {
-head(prepan.ocir.raw.id)
-}
-```
-
-```{r ocir prepan summary}
-if(GLAD == TRUE | EDGI == TRUE) {
-summarytools::dfSummary(
-  prepan.ocir.raw.id,
-  graph.col = F,
-  valid.col = F
-  )
-}
-```
-
-# COPING GAD-7
-## GLAD
-```{r coping glad gad cols}
-if(GLAD == TRUE) {
-coping.glad.gad.raw <- readRDS(file = paste0(data.raw_path,"/glad/gad_coping_glad.rds"))
-dim(coping.glad.gad.raw)
-colnames(coping.glad.gad.raw)
-}
-```
-
-```{r coping glad gad summary}
-if(GLAD == TRUE) {
-summarytools::dfSummary(
-  coping.glad.gad.raw,
-  graph.col = F,
-  valid.col = F,
-  labels.col = F
-  )
-}
-```
-
-```{r coping glad gad cleaning}
-if(GLAD == TRUE) {
-exclude_cols_coping_glad <- c(
-  "Sample",
-  "ID",
-  "startDate.coping"
-)
-
-coping.glad.gad.raw.id <- coping.glad.gad.raw %>%
-  drop_na(externalDataReference) %>% # Drop NAs
-  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
-  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
-  mutate(ID = as.numeric(ID)
-         ) %>% 
-  select(
-    Sample, # Sample
-    ID, # ID
-    startDate.coping = startDate, # Rename startDate
-    gad.problems_made_difficult_care, # Impairment
-    gad.pandemic_felt_feelings, # Comparison to before the pandemic (retro)
-    gad.feeling_nervous_anxious_or_on_edge_retro = gad.feeling_nervous_anxious_or_on_edge,
-    gad.control_worrying_stop_retro = gad.control_worrying_stop,
-    gad.worrying_too_much_about_different_things_retro = gad.worrying_too_much_about_different_things,
-    gad.trouble_relaxing_retro = gad.trouble_relaxing,
-    gad.sit_restless_hard_retro = gad.sit_restless_hard,
-    gad.becoming_easily_annoyed_or_irritable_retro = gad.becoming_easily_annoyed_or_irritable,
-    gad.awful_feeling_afraid_happen_retro = gad.awful_feeling_afraid_happen,
-    gad.feeling_nervous_anxious_or_on_edge_base = gad.feeling_nervous_anxious_or_on_edge.1,
-    gad.control_worrying_stop_base = gad.control_worrying_stop.1,
-    gad.worrying_too_much_about_different_things_base = gad.worrying_too_much_about_different_things.1,
-    gad.trouble_relaxing_base = gad.trouble_relaxing.1,
-    gad.sit_restless_hard_base = gad.sit_restless_hard.1,
-    gad.becoming_easily_annoyed_or_irritable_base = gad.becoming_easily_annoyed_or_irritable.1,
-    gad.awful_feeling_afraid_happen_base = gad.awful_feeling_afraid_happen.1
-  ) %>%
-  add_numeric(., exclude = exclude_cols_coping_glad) %>%
-  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
-  mutate_if(is.numeric, ~na_if(., -99)) %>%
-  mutate_if(is.numeric, ~na_if(., -77)) %>%
-  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
-  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
-
-# Inspect dimensions
-dim(coping.glad.gad.raw.id)
-# Inspect colnames
-colnames(coping.glad.gad.raw.id)
-#Differences
-dim(coping.glad.gad.raw)[1]-dim(coping.glad.gad.raw.id)[1]
-}
-```
-
-```{r coping glad gad copy}
-if(GLAD == TRUE) {
-  coping.gad.raw.id <- coping.glad.gad.raw.id
-}
-```
-
-## EDGI
-```{r coping edgi gad cols}
-if(EDGI == TRUE) {
-  coping.edgi.gad.raw <- readRDS(file = paste0(data.raw_path,"/edgi/gad_coping_edgi.rds"))
-  dim(coping.edgi.gad.raw)
-  colnames(coping.edgi.gad.raw)
-}
-```
-
-```{r coping edgi gad summary}
-if(EDGI == TRUE) {
-  summarytools::dfSummary(
-    coping.edgi.gad.raw,
-    graph.col = F,
-    valid.col = F,
-    labels.col = T # to see what is baseline and what is retro
-  )
-}
-```
-
-```{r coping edgi gad cleaning}
-if(EDGI == TRUE) {
-  exclude_cols_coping_edgi <- c(
-    "Sample",
-    "ID",
-    "startDate.coping"
-  )
-
-  coping.edgi.gad.raw.id <- coping.edgi.gad.raw %>%
-    drop_na(externalDataReference) %>% # Drop NAs
-    distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
-    separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
-    mutate(ID = as.numeric(ID)
-    ) %>% 
-    select(
-      Sample, # Sample
-      ID, # ID
-      startDate.coping = startDate, # Rename startDate
-      gad.problems_made_difficult_care = gad.care_difficult_home_things, # Impairment (different to GLAD)
-      gad.pandemic_felt_feelings = gad.pandemic_feelings_felt, # Comparison to before the pandemic (retro; different to GLAD)
-      gad.feeling_nervous_anxious_or_on_edge_retro = gad.feeling_nervous_anxious_or_on_edge,
-      gad.control_worrying_stop_retro = gad.control_worrying_stop,
-      gad.worrying_too_much_about_different_things_retro = gad.worrying_too_much_about_different_things,
-      gad.trouble_relaxing_retro = gad.trouble_relaxing,
-      gad.sit_restless_hard_retro = gad.sit_restless_hard,
-      gad.becoming_easily_annoyed_or_irritable_retro = gad.becoming_easily_annoyed_or_irritable,
-      gad.awful_feeling_afraid_happen_retro = gad.feeling_afraid_awful_happen, # different to GLAD: gad.awful_feeling_afraid_happen,
-      gad.feeling_nervous_anxious_or_on_edge_base = gad.feeling_nervous_anxious_or_on_edge.1,
-      gad.control_worrying_stop_base = gad.control_worrying_stop.1,
-      gad.worrying_too_much_about_different_things_base = gad.worrying_too_much_about_different_things.1,
-      gad.trouble_relaxing_base = gad.trouble_relaxing.1,
-      gad.sit_restless_hard_base = gad.sit_restless_hard.1,
-      gad.becoming_easily_annoyed_or_irritable_base = gad.becoming_easily_annoyed_or_irritable.1,
-      gad.awful_feeling_afraid_happen_base = gad.feeling_afraid_awful_happen.1 # different to GLAD: gad.awful_feeling_afraid_happen.1
-    ) %>%
-    add_numeric(., exclude = exclude_cols_coping_edgi) %>%
-    mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
-    mutate_if(is.numeric, ~na_if(., -99)) %>%
-    mutate_if(is.numeric, ~na_if(., -77)) %>%
-    mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
-    mutate_if(is.factor, ~na_if(., "Don't know")) %>%
-    mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
-    mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
-    mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
-    mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
-    mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
-    mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
-
-  # Inspect dimensions
-  dim(coping.edgi.gad.raw.id)
-  # Inspect colnames
-  colnames(coping.edgi.gad.raw.id)
-  #Differences
-  dim(coping.edgi.gad.raw)[1]-dim(coping.edgi.gad.raw.id)[1]
-}
-```
-
-```{r coping edgi gad copy}
-if(EDGI == TRUE) {
-  coping.gad.raw.id <- coping.edgi.gad.raw.id
-}
-```
-
-## NBR
-```{r coping nbr gad cols}
-if(NBR == TRUE) {
-  coping.nbr.gad.raw <- readRDS(file = paste0(data.raw_path,"/nbr/gad_coping_nbr.rds"))
-  dim(coping.nbr.gad.raw)
-  colnames(coping.nbr.gad.raw)
-}
-```
-
-```{r coping nbr gad summary}
-if(NBR == TRUE) {
-  summarytools::dfSummary(
-    coping.nbr.gad.raw,
-    graph.col = F,
-    valid.col = F,
-    labels.col = F
-  )
-}
-```
-
-```{r coping nbr gad cleaning}
-if(NBR == TRUE) {
-  exclude_cols_coping_nbr <- c(
-    "Sample",
-    "ID",
-    "startDate.coping"
-  )
-
-  coping.nbr.gad.raw.id <- coping.nbr.gad.raw %>%
-  drop_na(subjectid) %>% # Drop NAs
-  distinct(subjectid, .keep_all = TRUE) %>% # Remove duplicates based on ID
-  separate(subjectid, into = c("Sample", "ID.intm"), sep = 6) %>% # Split ID in Sample and Number
-  separate(ID.intm, into = "ID", sep = 7) %>%
-  mutate(ID = as.numeric(ID)) %>% 
-    select(
-      Sample, # Sample
-      ID, # ID
-      startDate.coping = startDate, # Rename startDate
-      gad.problems_made_difficult_care = gad.problems_made_care_difficult, # Impairment (different from GLAD)
-      gad.pandemic_felt_feelings, # Comparison to before the pandemic (retro)
-      gad.feeling_nervous_anxious_or_on_edge_retro = gad.feeling_nervous_anxious_or_on_edge,
-      gad.control_worrying_stop_retro = gad.control_worrying_stop,
-      gad.worrying_too_much_about_different_things_retro = gad.worrying_too_much_about_different_things,
-      gad.trouble_relaxing_retro = gad.trouble_relaxing,
-      gad.sit_restless_hard_retro = gad.sit_restless_hard,
-      gad.becoming_easily_annoyed_or_irritable_retro = gad.becoming_easily_annoyed_or_irritable,
-      gad.awful_feeling_afraid_happen_retro = gad.feeling_afraid_awful_happen, #Different from GLAD
-      gad.feeling_nervous_anxious_or_on_edge_base = gad.feeling_nervous_anxious_or_on_edge.1,
-      gad.control_worrying_stop_base = gad.control_worrying_stop.1,
-      gad.worrying_too_much_about_different_things_base = gad.worrying_too_much_about_different_things.1,
-      gad.trouble_relaxing_base = gad.trouble_relaxing.1,
-      gad.sit_restless_hard_base = gad.sit_restless_hard.1,
-      gad.becoming_easily_annoyed_or_irritable_base = gad.becoming_easily_annoyed_or_irritable.1,
-      gad.awful_feeling_afraid_happen_base = gad.feeling_afraid_awful_happen.1 #Different from GLAD
-    ) %>%
-    add_numeric(., exclude = exclude_cols_coping_nbr) %>%
-    mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
-    mutate_if(is.numeric, ~na_if(., -99)) %>%
-    mutate_if(is.numeric, ~na_if(., -77)) %>%
-    mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
-    mutate_if(is.factor, ~na_if(., "Don't know")) %>%
-    mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
-    mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
-    mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
-    mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
-    mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
-    mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
-
-  # Inspect dimensions
-  dim(coping.nbr.gad.raw.id)
-  # Inspect colnames
-  colnames(coping.nbr.gad.raw.id)
-  #Differences
-  dim(coping.nbr.gad.raw)[1]-dim(coping.nbr.gad.raw.id)[1]
-}
-```
-
-```{r coping nbr gad copy}
-if(NBR == TRUE) {
-  coping.gad.raw.id <- coping.nbr.gad.raw.id
-}
-```
-
-## RAMP
-```{r coping ramp gad cols}
-if(RAMP == TRUE) {
-  ramp.gad.raw <- readRDS(file = paste0(data.raw_path,"/ramp/gad_ramp.rds"))
-  dim(ramp.gad.raw)
-  colnames(ramp.gad.raw)
-}
-```
-
-```{r coping ramp gad summary}
-if(RAMP == TRUE) {
-  summarytools::dfSummary(
-    ramp.gad.raw,
-    graph.col = F,
-    valid.col = F,
-    labels.col = F
-  )
-}
-```
-
-```{r coping ramp gad cleaning}
-if(RAMP == TRUE) {
-  exclude_cols_ramp <- c(
-    "Sample",
-    "ID",
-    "startDate.coping"
-  )
-
-  ramp.gad.raw.id <- ramp.gad.raw %>%
-    drop_na(`Login ID`) %>% # Drop NAs
-    distinct(`Login ID`, .keep_all = TRUE) %>% # Remove duplicates based on ID
-    separate(`Login ID`, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
-    mutate(ID = as.numeric(ID)
-    ) %>% 
-    select(
-      Sample, # Sample
-      ID, # ID
-      startDate.coping = startDate, # Rename startDate
-      gad.problems_made_difficult_care = gad.issues_made_carrying_daily, # Impairment
-      gad.pandemic_felt_feelings = gad.feelings_pandemic_felt, # Comparison to before the pandemic (retro)
-      gad.feeling_nervous_anxious_or_on_edge_retro = gad.feeling_nervous_anxious_or_on_edge.1, #retro and baseline coding are reversed for RAMP
-      gad.control_worrying_stop_retro = gad.control_worrying_stop.1, #.1 = retro
-      gad.worrying_too_much_about_different_things_retro = gad.worrying_too_much_about_different_things.1,
-      gad.trouble_relaxing_retro = gad.trouble_relaxing.1,
-      gad.sit_restless_hard_retro = gad.sit_hard_restless.1,
-      gad.becoming_easily_annoyed_or_irritable_retro = gad.becoming_easily_annoyed_or_irritable.1,
-      gad.awful_feeling_afraid_happen_retro = gad.awful_feeling_afraid_happen.1,
-      gad.feeling_nervous_anxious_or_on_edge_base = gad.feeling_nervous_anxious_or_on_edge,
-      gad.control_worrying_stop_base = gad.control_worrying_stop,
-      gad.worrying_too_much_about_different_things_base = gad.worrying_too_much_about_different_things,
-      gad.trouble_relaxing_base = gad.trouble_relaxing,
-      gad.sit_restless_hard_base = gad.sit_hard_restless,
-      gad.becoming_easily_annoyed_or_irritable_base = gad.becoming_easily_annoyed_or_irritable,
-      gad.awful_feeling_afraid_happen_base = gad.awful_feeling_afraid_happen
-    ) %>%
-    add_numeric(., exclude = exclude_cols_coping_ramp) %>%
-    mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
-    mutate_if(is.numeric, ~na_if(., -99)) %>%
-    mutate_if(is.numeric, ~na_if(., -77)) %>%
-    mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
-    mutate_if(is.factor, ~na_if(., "Don't know")) %>%
-    mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
-    mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
-    mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
-    mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
-    mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
-    mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
-
-  # Inspect dimensions
-  dim(ramp.gad.raw.id)
-  # Inspect colnames
-  colnames(ramp.gad.raw.id)
-  #Differences
-  dim(ramp.gad.raw)[1]-dim(ramp.gad.raw.id)[1]
-}
-```
-
-```{r coping ramp gad copy}
-if(RAMP == TRUE) {
-  coping.gad.raw.id <- ramp.gad.raw.id
-}
-```
-
-## Sum scores
-Calculate sum score for GAD-7 retrospective
-```{r coping gad sum score retro}
-# Create vector with scoring key: If the item is reversed coded use -1. 
-# There needs to be the correct number of values for each item in the questionnaire. 
-gad.items_key_retro <- c(1,1,1,1,1,1,1)
-
-# Create vector with items that are included in total score
-gad.items_retro <- c(
-  "gad.feeling_nervous_anxious_or_on_edge_retro_numeric",
-  "gad.control_worrying_stop_retro_numeric",
-  "gad.worrying_too_much_about_different_things_retro_numeric",
-  "gad.trouble_relaxing_retro_numeric",
-  "gad.sit_restless_hard_retro_numeric",
-  "gad.becoming_easily_annoyed_or_irritable_retro_numeric",
-  "gad.awful_feeling_afraid_happen_retro_numeric"
-  )
-
-# Calulate total score
-gad.scored_items_retro <- scoreItems(keys = gad.items_key_retro,
-                                        items = coping.gad.raw.id[gad.items_retro],
-                                        totals = TRUE, 
-                                        missing = TRUE, 
-                                        impute = 'none', 
-                                        min = 0, 
-                                        max = 3)
-# Add in column to tibble
-coping.gad.raw.id$gad.sum_score_retro_raw <- gad.scored_items_retro$scores
-
-# Look at values
-coping.gad.raw.id %>%
-  descr(gad.sum_score_retro_raw,
-        stats = "common"
-        )
-```
-
-Calculate sum score for GAD-7 baseline
-```{r coping gad sum score base}
-# Create vector with scoring key: If the item is reversed coded use -1. 
-# There needs to be the correct number of values for each item in the questionnaire. 
-gad.items_key_base <- c(1,1,1,1,1,1,1)
-
-# Create vector with items that are included in total score
-gad.items_base <- c(
-  "gad.feeling_nervous_anxious_or_on_edge_base_numeric",
-  "gad.control_worrying_stop_base_numeric",
-  "gad.worrying_too_much_about_different_things_base_numeric",
-  "gad.trouble_relaxing_base_numeric",
-  "gad.sit_restless_hard_base_numeric",
-  "gad.becoming_easily_annoyed_or_irritable_base_numeric",
-  "gad.awful_feeling_afraid_happen_base_numeric"
-  )
-
-# Calulate total score
-gad.scored_items_base <- scoreItems(keys = gad.items_key_base,
-                                        items = coping.gad.raw.id[gad.items_base],
-                                        totals = TRUE, 
-                                        missing = TRUE, 
-                                        impute = 'none', 
-                                        min = 0, 
-                                        max = 3)
-# Add in column to tibble
-coping.gad.raw.id$gad.sum_score_base_raw <- gad.scored_items_base$scores
-
-# Look at values
-coping.gad.raw.id %>%
-  descr(gad.sum_score_base_raw,
-        stats = "common"
-        )
-```
-
-## Missingness
-
-baseline
-```{r coping gad baseline missingness}
-coping.gad.raw.id <- coping.gad.raw.id %>%
-  mutate(
-    na_per_person_gad_base =         # variable for NA per person
-      rowSums(                       
-        is.na(.[gad.items_base])
-      )
-  )
-
-coping.gad.raw.id %>%
-  freq(na_per_person_gad_base, cumul = F) #have a look at the frequency
-```
-
-```{r coping gad retrospective missingness}
-coping.gad.raw.id <- coping.gad.raw.id %>%
-  mutate(
-    na_per_person_gad_retro =         # variable for NA per person
-      rowSums(
-        is.na(.[gad.items_retro])
-      )
-  )
-
-coping.gad.raw.id %>%
-  freq(na_per_person_gad_retro, cumul = F) #have a look at the frequency
-```
-
-```{r coping gad base sum score if missing items set to NA}
-coping.gad.raw.id <- coping.gad.raw.id %>%
-  mutate(
-    gad.sum_score_base =
-      if_else(condition = na_per_person_gad_base > 0,
-              true = NA_real_,
-              false = gad.sum_score_base_raw,
-              missing = NA_real_
-      )
-  )
-
-coping.gad.raw.id %>%
-  descr(gad.sum_score_base_raw, stats = "common")
-
-coping.gad.raw.id %>%
-  descr(gad.sum_score_base, stats = "common")
-```
-
-```{r coping gad retro sum score if missing items set to NA}
-coping.gad.raw.id <- coping.gad.raw.id %>%
-  mutate(
-    gad.sum_score_retro =
-      if_else(condition = na_per_person_gad_retro > 0,
-              true = NA_real_,
-              false = gad.sum_score_retro_raw,
-              missing = NA_real_
-      )
-  )
-
-coping.gad.raw.id %>%
-  descr(gad.sum_score_retro_raw, stats = "common")
-
-coping.gad.raw.id %>%
-  descr(gad.sum_score_retro, stats = "common")
-```
-
-## Inspection
-```{r coping glad gad head}
-head(coping.gad.raw.id)
-```
-
-```{r coping glad gad summary 2}
-summarytools::dfSummary(
-  coping.gad.raw.id,
-  graph.col = F,
-  valid.col = F,
-  labels.col = F)
-```
-
-# COPING: PCL-6
-
-## GLAD
-```{r coping glad pcl cols}
-if(GLAD == TRUE) {
-coping.glad.pcl.raw <- readRDS(file = paste0(data.raw_path,"/glad/pcl_coping_glad.rds"))
-dim(coping.glad.pcl.raw)
-colnames(coping.glad.pcl.raw)
-}
-```
-
-```{r coping glad pcl summary labels}
-if(GLAD == TRUE) {
-summarytools::dfSummary(
-  coping.glad.pcl.raw,
-  graph.col = F,
-  valid.col = F,
-  labels.col = F
-)
-}
-```
-
-Note: Retro for the PCL does not mean retrospective
-
-```{r coping glad pcl cleaning}
-if(GLAD == TRUE) {
-coping.glad.pcl.raw.id <- coping.glad.pcl.raw %>%
-  drop_na(externalDataReference) %>% # Drop NAs
-  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
-  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
-  mutate(ID = as.numeric(ID)) %>%
-  select(
-    Sample, # Sample
-    ID, # ID
-    pcl.stressful_experience_repeated_images_base = pcl.stressful_experience_repeated_images,
-    pcl.stressful_experience_upset_reminded_base = pcl.stressful_experience_upset_reminded, # differ to GLAD prepan
-    pcl.stressful_situation_avoiding_activities_base = pcl.avoiding_activities_stressful_experience, # differ to GLAD prepan
-    pcl.cut_people_feeling_distant_base = pcl.cut_people_feeling_distant,
-    pcl.feeling_irritable_or_having_angry_outbursts_base = pcl.feeling_irritable_or_having_angry_outbursts,
-    pcl.difficulty_concentrating_base = pcl.difficulty_concentrating,
-    pcl.stressful_experience_repeated_images_retro = pcl.stressful_experience_repeated_images.1,
-    pcl.stressful_experience_upset_reminded_retro = pcl.stressful_experience_upset_reminded.1,
-    pcl.stressful_situation_avoiding_activities_retro = pcl.avoiding_activities_stressful_experience.1,
-    pcl.cut_people_feeling_distant_retro = pcl.cut_people_feeling_distant.1,
-    pcl.feeling_irritable_or_having_angry_outbursts_retro = pcl.feeling_irritable_or_having_angry_outbursts.1,
-    pcl.difficulty_concentrating_retro = pcl.difficulty_concentrating.1
-  ) %>%
-  add_numeric(., exclude = exclude_cols) %>%
-  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
-  mutate_if(is.numeric, ~na_if(., -99)) %>%
-  mutate_if(is.numeric, ~na_if(., -77)) %>%
-  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
-  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
-
-# Inspect dimensions
-dim(coping.glad.pcl.raw.id)
-# Inspect colnames
-colnames(coping.glad.pcl.raw.id)
-#Differences
-dim(coping.glad.pcl.raw)[1]-dim(coping.glad.pcl.raw.id)[1]
-}
-```
-
-```{r coping glad pcl copy}
-if(GLAD == TRUE) {
-  coping.pcl.raw.id <- coping.glad.pcl.raw.id
-}
-```
-
-## EDGI
-```{r coping edgi pcl cols}
-if(EDGI == TRUE) {
-coping.edgi.pcl.raw <- readRDS(file = paste0(data.raw_path,"/edgi/pcl_coping_edgi.rds"))
-dim(coping.edgi.pcl.raw)
-colnames(coping.edgi.pcl.raw)
-}
-```
-
-```{r coping edgi pcl summary labels}
-if(EDGI == TRUE) {
-summarytools::dfSummary(
-  coping.edgi.pcl.raw,
-  graph.col = F,
-  valid.col = F,
-  labels.col = F
-)
-}
-```
-
-Note: Retro for the PCL does not mean retrospective
-
-```{r coping edgi pcl cleaning}
-if(EDGI == TRUE) {
-coping.edgi.pcl.raw.id <- coping.edgi.pcl.raw %>%
-  drop_na(externalDataReference) %>% # Drop NAs
-  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
-  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
-  mutate(ID = as.numeric(ID)) %>%
-  select(
-    Sample, # Sample
-    ID, # ID
-    pcl.stressful_experience_repeated_images_base = pcl.repeated_images_thoughts_past, # different pcl.stressful_experience_repeated_images,
-    pcl.stressful_experience_upset_reminded_base = pcl.upset_reminded_past_feeling, # differ to EDGI prepan
-    pcl.stressful_situation_avoiding_activities_base = pcl.avoiding_activities_reminded_situations, # differ to EDGI prepan
-    pcl.cut_people_feeling_distant_base = pcl.cut_people_feeling_distant,
-    pcl.feeling_irritable_or_having_angry_outbursts_base = pcl.feeling_irritable_or_having_angry_outbursts,
-    pcl.difficulty_concentrating_base = pcl.difficulty_concentrating,
-    pcl.stressful_experience_repeated_images_retro = pcl.repeated_images_thoughts_past.1,
-    pcl.stressful_experience_upset_reminded_retro = pcl.upset_reminded_past_feeling.1,
-    pcl.stressful_situation_avoiding_activities_retro = pcl.avoiding_activities_reminded_situations.1,
-    pcl.cut_people_feeling_distant_retro = pcl.cut_people_feeling_distant.1,
-    pcl.feeling_irritable_or_having_angry_outbursts_retro = pcl.feeling_irritable_or_having_angry_outbursts.1,
-    pcl.difficulty_concentrating_retro = pcl.difficulty_concentrating.1
-  ) %>%
-  add_numeric(., exclude = exclude_cols) %>%
-  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
-  mutate_if(is.numeric, ~na_if(., -99)) %>%
-  mutate_if(is.numeric, ~na_if(., -77)) %>%
-  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
-  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
-
-# Inspect dimensions
-dim(coping.edgi.pcl.raw.id)
-# Inspect colnames
-colnames(coping.edgi.pcl.raw.id)
-#Differences
-dim(coping.edgi.pcl.raw)[1]-dim(coping.edgi.pcl.raw.id)[1]
-}
-```
-
-```{r coping edgi pcl copy}
-if(EDGI == TRUE) {
-  coping.pcl.raw.id <- coping.edgi.pcl.raw.id
-}
-```
-
-## NBR
-```{r coping nbr pcl cols}
-if(NBR == TRUE) {
-coping.nbr.pcl.raw <- readRDS(file = paste0(data.raw_path,"/nbr/pcl_coping_nbr.rds"))
-dim(coping.nbr.pcl.raw)
-colnames(coping.nbr.pcl.raw)
-}
-```
-
-```{r coping nbr pcl summary labels}
-if(NBR == TRUE) {
-summarytools::dfSummary(
-  coping.nbr.pcl.raw,
-  graph.col = F,
-  valid.col = F,
-  labels.col = F
-)
-}
-```
-
-Note: Retro for the PCL does not mean retrospective
-
-```{r coping nbr pcl cleaning}
-if(NBR == TRUE) {
-coping.nbr.pcl.raw.id <- coping.nbr.pcl.raw %>%
-  drop_na(subjectid) %>% # Drop NAs
-  distinct(subjectid, .keep_all = TRUE) %>% # Remove duplicates based on ID
-  separate(subjectid, into = c("Sample", "ID.intm"), sep = 6) %>% # Split ID in Sample and Number
-  separate(ID.intm, into = "ID", sep = 7) %>%
-  mutate(ID = as.numeric(ID)) %>%
-  select(
-    Sample, # Sample
-    ID, # ID
-    pcl.stressful_experience_repeated_images_base = pcl.stressful_experience_repeated_images,
-    pcl.stressful_experience_upset_reminded_base = pcl.stressful_experience_upset_reminded, # differ to NBR prepan
-    pcl.stressful_situation_avoiding_activities_base = pcl.avoiding_activities_stressful_experience, # differ to NBR prepan
-    pcl.cut_people_feeling_distant_base = pcl.cut_people_feeling_distant,
-    pcl.feeling_irritable_or_having_angry_outbursts_base = pcl.feeling_irritable_or_having_angry_outbursts,
-    pcl.difficulty_concentrating_base = pcl.difficulty_concentrating,
-    pcl.stressful_experience_repeated_images_retro = pcl.stressful_experience_repeated_images.1,
-    pcl.stressful_experience_upset_reminded_retro = pcl.stressful_experience_upset_reminded.1,
-    pcl.stressful_situation_avoiding_activities_retro = pcl.avoiding_activities_stressful_experience.1,
-    pcl.cut_people_feeling_distant_retro = pcl.cut_people_feeling_distant.1,
-    pcl.feeling_irritable_or_having_angry_outbursts_retro = pcl.feeling_irritable_or_having_angry_outbursts.1,
-    pcl.difficulty_concentrating_retro = pcl.difficulty_concentrating.1
-  ) %>%
-  add_numeric(., exclude = exclude_cols) %>%
-  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
-  mutate_if(is.numeric, ~na_if(., -99)) %>%
-  mutate_if(is.numeric, ~na_if(., -77)) %>%
-  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
-  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
-
-# Inspect dimensions
-dim(coping.nbr.pcl.raw.id)
-# Inspect colnames
-colnames(coping.nbr.pcl.raw.id)
-#Differences
-dim(coping.nbr.pcl.raw)[1]-dim(coping.nbr.pcl.raw.id)[1]
-}
-```
-
-```{r coping nbr pcl copy}
-if(NBR == TRUE) {
-  coping.pcl.raw.id <- coping.nbr.pcl.raw.id
-}
-```
-
-## RAMP - NOT YET HAVE THE RAMP PCL DATA READY
-```{r coping ramp pcl cols}
-# if(RAMP == TRUE) {
-# coping.ramp.pcl.raw <- readRDS(file = paste0(data.raw_path,"/ramp/pcl_ramp.rds"))
-# dim(coping.ramp.pcl.raw)
-# colnames(coping.ramp.pcl.raw)
-# }
-```
-
-```{r coping ramp pcl summary labels}
-# if(RAMP == TRUE) {
-# summarytools::dfSummary(
-#   coping.ramp.pcl.raw,
-#   graph.col = F,
-#   valid.col = F,
-#   labels.col = F
-# )
-# }
-```
-
-Note: Retro for the PCL does not mean retrospective
-
-```{r coping ramp pcl cleaning}
-# if(RAMP == TRUE) {
-# coping.ramp.pcl.raw.id <- coping.ramp.pcl.raw %>%
-#   drop_na(externalDataReference) %>% # Drop NAs
-#   distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
-#   separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
-#   mutate(ID = as.numeric(ID)) %>%
-#   select(
-#     Sample, # Sample
-#     ID, # ID
-#     pcl.stressful_experience_repeated_images_base = pcl.stressful_experience_repeated_images,
-#     pcl.stressful_experience_upset_reminded_base = pcl.stressful_experience_upset_reminded, # differ to RAMP prepan
-#     pcl.stressful_situation_avoiding_activities_base = pcl.avoiding_activities_stressful_experience, # differ to RAMP prepan
-#     pcl.cut_people_feeling_distant_base = pcl.cut_people_feeling_distant,
-#     pcl.feeling_irritable_or_having_angry_outbursts_base = pcl.feeling_irritable_or_having_angry_outbursts,
-#     pcl.difficulty_concentrating_base = pcl.difficulty_concentrating,
-#     pcl.stressful_experience_repeated_images_retro = pcl.stressful_experience_repeated_images.1,
-#     pcl.stressful_experience_upset_reminded_retro = pcl.stressful_experience_upset_reminded.1,
-#     pcl.stressful_situation_avoiding_activities_retro = pcl.avoiding_activities_stressful_experience.1,
-#     pcl.cut_people_feeling_distant_retro = pcl.cut_people_feeling_distant.1,
-#     pcl.feeling_irritable_or_having_angry_outbursts_retro = pcl.feeling_irritable_or_having_angry_outbursts.1,
-#     pcl.difficulty_concentrating_retro = pcl.difficulty_concentrating.1
-#   ) %>%
-#   add_numeric(., exclude = exclude_cols) %>%
-#   mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
-#   mutate_if(is.numeric, ~na_if(., -99)) %>%
-#   mutate_if(is.numeric, ~na_if(., -77)) %>%
-#   mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
-#   mutate_if(is.factor, ~na_if(., "Don't know")) %>%
-#   mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
-#   mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
-#   mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
-#   mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
-#   mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
-#   mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
-# 
-# # Inspect dimensions
-# dim(coping.ramp.pcl.raw.id)
-# # Inspect colnames
-# colnames(coping.ramp.pcl.raw.id)
-# #Differences
-# dim(coping.ramp.pcl.raw)[1]-dim(coping.ramp.pcl.raw.id)[1]
-# }
-```
-
-```{r coping ramp pcl copy}
-# if(RAMP == TRUE) {
-#   coping.pcl.raw.id <- coping.ramp.pcl.raw.id
-# }
-```
-
-## Sum scores
-Calculate sum score for PCL-6 retro
-```{r coping pcl sum score retro}
-# Create vector with scoring key: If the item is reversed coded use -1. 
-# There needs to be the correct number of values for each item in the questionnaire. 
-pcl.items_key_retro <- c(1,1,1,1,1,1)
-
-# Create vector with items that are included in total score
-pcl.items_retro <- c(
-  "pcl.stressful_experience_repeated_images_retro_numeric",
-  "pcl.stressful_experience_upset_reminded_retro_numeric",
-  "pcl.stressful_situation_avoiding_activities_retro_numeric",
-  "pcl.cut_people_feeling_distant_retro_numeric",
-  "pcl.feeling_irritable_or_having_angry_outbursts_retro_numeric",
-  "pcl.difficulty_concentrating_retro_numeric"
-)
-
-# Calulate total score
-pcl.scored_items_retro <- scoreItems(keys = pcl.items_key_retro,
-                                     items = coping.pcl.raw.id[pcl.items_retro],
-                                     totals = TRUE, 
-                                     missing = TRUE, 
-                                     impute = 'none', 
-                                     min = 0, 
-                                     max = 1)
-# Add in column to tibble
-coping.pcl.raw.id$pcl.sum_score_retro_raw <- pcl.scored_items_retro$scores
-
-# Look at values
-coping.pcl.raw.id %>%
-  descr(pcl.sum_score_retro_raw,
-        stats = "common"
-  )
-```
-
-Calculate sum score for PCL-6 base
-The sum scores here will not be accurate if we are using complete cases. Only use sum scores here for complete cases, otherwise the minimum will be 0 where it should be 6. 
-```{r coping pcl sum score base}
-# Create vector with scoring key: If the item is reversed coded use -1. 
-# There needs to be the correct number of values for each item in the questionnaire. 
-pcl.items_key_base <- c(1,1,1,1,1,1)
-
-# Create vector with items that are included in total score
-pcl.items_base <- c(
-  "pcl.stressful_experience_repeated_images_base_numeric",
-  "pcl.stressful_experience_upset_reminded_base_numeric",
-  "pcl.stressful_situation_avoiding_activities_base_numeric",
-  "pcl.cut_people_feeling_distant_base_numeric",
-  "pcl.feeling_irritable_or_having_angry_outbursts_base_numeric",
-  "pcl.difficulty_concentrating_base_numeric"
-)
-
-# Calulate total score
-pcl.scored_items_base <- scoreItems(keys = pcl.items_key_base,
-                                    items = coping.pcl.raw.id[pcl.items_base],
-                                    totals = TRUE, 
-                                    missing = TRUE, 
-                                    impute = "none", 
-                                    min = 1, 
-                                    max = 5)
-# Add in column to tibble
-coping.pcl.raw.id$pcl.sum_score_base_raw <- pcl.scored_items_base$scores
-
-# Look at values
-coping.pcl.raw.id %>%
-  descr(pcl.sum_score_base_raw,
-        stats = "common"
-  )
-```
-
-## Missingness
-PCL missingness (NAs per person)
-
-baseline
-```{r coping pcl baseline missingness}
-coping.pcl.raw.id <- coping.pcl.raw.id %>%
-  mutate(
-    na_per_person_pcl_base =         # variable for NA per person
-      rowSums(                       
-        is.na(.[pcl.items_base])
-      )
-  )
-
-coping.pcl.raw.id %>%
-  freq(na_per_person_pcl_base, cumul = F) #have a look at the frequency
-```
-
-retrospective
-```{r coping pcl retrospective missingness}
-coping.pcl.raw.id <- coping.pcl.raw.id %>%
-  mutate(
-    na_per_person_pcl_retro =         # variable for NA per person
-      rowSums(
-        is.na(.[pcl.items_retro])
-      )
-  )
-
-coping.pcl.raw.id %>%
-  freq(na_per_person_pcl_retro, cumul = F) #have a look at the frequency
-```
-
-```{r coping pcl base sum score if missing items set to NA}
-coping.pcl.raw.id <- coping.pcl.raw.id %>%
-  mutate(
-    pcl.sum_score_base =
-      if_else(condition = na_per_person_pcl_base > 0,
-              true = NA_real_,
-              false = pcl.sum_score_base_raw,
-              missing = NA_real_
-      )
-  )
-
-coping.pcl.raw.id %>%
-  descr(pcl.sum_score_base_raw, stats = "common")
-
-coping.pcl.raw.id %>%
-  descr(pcl.sum_score_base, stats = "common")
-```
-
-```{r coping pcl retro sum score if missing items set to NA}
-coping.pcl.raw.id <- coping.pcl.raw.id %>%
-  mutate(
-    pcl.sum_score_retro =
-      if_else(condition = na_per_person_pcl_retro > 0,
-              true = NA_real_,
-              false = pcl.sum_score_retro_raw,
-              missing = NA_real_
-      )
-  )
-
-coping.pcl.raw.id %>%
-  descr(pcl.sum_score_retro_raw, stats = "common")
-
-coping.pcl.raw.id %>%
-  descr(pcl.sum_score_retro, stats = "common")
-```
-
-## Inspection
-```{r coping glad pcl head}
-head(coping.pcl.raw.id)
-```
-
-```{r coping glad pcl summary}
-summarytools::dfSummary(
-  coping.pcl.raw.id,
-  graph.col = F,
-  valid.col = F,
-  labels.col = F)
-```
-
-# COPING: PHQ
-
-## GLAD
-```{r coping glad phq cols}
-if(GLAD == TRUE) {
-coping.glad.phq.raw <- readRDS(file = paste0(data.raw_path, "/glad/phq_coping_glad.rds"))
-dim(coping.glad.phq.raw)
-colnames(coping.glad.phq.raw)
-}
-```
-
-```{r coping glad phq summary labels}
-if(GLAD == TRUE) {
-summarytools::dfSummary(
-  coping.glad.phq.raw,
-  graph.col = F,
-  valid.col = F
-  #labels.col = F
-)
-}
-```
-
-Will need to double check these namings once we have the new cleaned data -- KT. 
-```{r coping glad phq cleaning}
-if(GLAD == TRUE) {
-coping.glad.phq.raw.id <- coping.glad.phq.raw %>%
-  drop_na(externalDataReference) %>% # Drop NAs
-  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
-  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
-  mutate(ID = as.numeric(ID)
-         ) %>%
-  select(
-    Sample, # Sample
-    ID, # ID
-    phq.problems_made_difficult_care,
-    phq.pandemic_felt_feelings,
-    phq.little_interest_or_pleasure_in_doing_things_retro = phq.little_interest_or_pleasure_in_doing_things,
-    phq.feeling_down_depressed_or_hopeless_retro = phq.feeling_down_depressed_or_hopeless,
-    phq.staying_asleep_sleeping_trouble_retro = phq.staying_asleep_sleeping_trouble,
-    phq.feeling_tired_or_having_little_energy_retro = phq.feeling_tired_or_having_little_energy,
-    phq.poor_appetite_or_overeating_retro = phq.poor_appetite_or_overeating,
-    phq.feeling_bad_failure_family_retro = phq.feeling_bad_failure_family,
-    phq.trouble_concentrating_reading_newspaper_retro = phq.trouble_concentrating_newspaper_reading, # differ GLAD prepandemic
-    phq.moving_fidgety_noticed_opposite_retro = phq.moving_fidgety_opposite_slowly, # differ GLAD prepandemic
-    phq.dead_hurting_thoughts_retro = phq.dead_hurting_thoughts,
-    phq.little_interest_or_pleasure_in_doing_things_base = phq.little_interest_or_pleasure_in_doing_things.1,
-    phq.feeling_down_depressed_or_hopeless_base = phq.feeling_down_depressed_or_hopeless.1,
-    phq.staying_asleep_sleeping_trouble_base = phq.staying_asleep_sleeping_trouble.1,
-    phq.feeling_tired_or_having_little_energy_base = phq.feeling_tired_or_having_little_energy.1,
-    phq.poor_appetite_or_overeating_base = phq.poor_appetite_or_overeating.1,
-    phq.feeling_bad_failure_family_base = phq.feeling_bad_failure_family.1,
-    phq.trouble_concentrating_reading_newspaper_base = phq.trouble_concentrating_newspaper_reading.1, # differ GLAD prepandemic
-    phq.moving_fidgety_noticed_opposite_base = phq.moving_fidgety_opposite_slowly.1, # differ GLAD prepandemic
-    phq.dead_hurting_thoughts_base = phq.dead_hurting_thoughts.1
-  ) %>%
-  add_numeric(., exclude = exclude_cols) %>%
-  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
-  mutate_if(is.numeric, ~na_if(., -99)) %>%
-  mutate_if(is.numeric, ~na_if(., -77)) %>%
-  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
-  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
-
-# Inspect dimensions
-dim(coping.glad.phq.raw.id)
-# Inspect colnames
-colnames(coping.glad.phq.raw.id)
-#Differences
-dim(coping.glad.phq.raw)[1]-dim(coping.glad.phq.raw.id)[1]
-}
-```
-
-```{r coping glad gad copy}
-if(GLAD == TRUE) {
-  coping.phq.raw.id <- coping.glad.phq.raw.id
-}
-```
-
-## EDGI
-```{r coping edgi phq cols}
-if(EDGI == TRUE) {
-coping.edgi.phq.raw <- readRDS(file = paste0(data.raw_path, "/edgi/phq_coping_edgi.rds"))
-dim(coping.edgi.phq.raw)
-colnames(coping.edgi.phq.raw)
-}
-```
-
-```{r coping edgi phq summary labels}
-if(EDGI == TRUE) {
-summarytools::dfSummary(
-  coping.edgi.phq.raw,
-  graph.col = F,
-  valid.col = F
-  #labels.col = F
-)
-}
-```
-
-```{r coping edgi phq cleaning}
-if(EDGI == TRUE) {
-coping.edgi.phq.raw.id <- coping.edgi.phq.raw %>%
-  drop_na(externalDataReference) %>% # Drop NAs
-  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
-  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
-  mutate(ID = as.numeric(ID)
-  ) %>%
-  select(
-    Sample, # Sample
-    ID, # ID
-    phq.problems_made_difficult_care = phq.care_difficult_home_things,
-    phq.pandemic_felt_feelings = phq.pandemic_feelings_felt,
-    phq.little_interest_or_pleasure_in_doing_things_retro = phq.little_interest_or_pleasure_in_doing_things,
-    phq.feeling_down_depressed_or_hopeless_retro = phq.feeling_down_depressed_or_hopeless,
-    phq.staying_asleep_sleeping_trouble_retro = phq.staying_asleep_sleeping_trouble,
-    phq.feeling_tired_or_having_little_energy_retro = phq.feeling_tired_or_having_little_energy,
-    phq.poor_appetite_or_overeating_retro = phq.poor_appetite_or_overeating,
-    phq.feeling_bad_failure_family_retro = phq.family_feeling_bad_failure, # differ GLAD phq.feeling_bad_failure_family,
-    phq.trouble_concentrating_reading_newspaper_retro = phq.trouble_concentrating_newspaper_reading, # differ EDGI prepandemic
-    phq.moving_fidgety_noticed_opposite_retro = phq.moving_fidgety_opposite_slowly, # differ EDGI prepandemic
-    phq.dead_hurting_thoughts_retro = phq.dead_hurting_thoughts,
-    phq.little_interest_or_pleasure_in_doing_things_base = phq.little_interest_or_pleasure_in_doing_things.1,
-    phq.feeling_down_depressed_or_hopeless_base = phq.feeling_down_depressed_or_hopeless.1,
-    phq.staying_asleep_sleeping_trouble_base = phq.staying_asleep_sleeping_trouble.1,
-    phq.feeling_tired_or_having_little_energy_base = phq.feeling_tired_or_having_little_energy.1,
-    phq.poor_appetite_or_overeating_base = phq.poor_appetite_or_overeating.1,
-    phq.feeling_bad_failure_family_base = phq.family_feeling_bad_failure.1, # differ GLAD
-    phq.trouble_concentrating_reading_newspaper_base = phq.trouble_concentrating_newspaper_reading.1, # differ EDGI prepandemic
-    phq.moving_fidgety_noticed_opposite_base = phq.moving_fidgety_opposite_slowly.1, # differ EDGI prepandemic
-    phq.dead_hurting_thoughts_base = phq.dead_hurting_thoughts.1
-  ) %>%
-  add_numeric(., exclude = exclude_cols) %>%
-  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
-  mutate_if(is.numeric, ~na_if(., -99)) %>%
-  mutate_if(is.numeric, ~na_if(., -77)) %>%
-  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
-  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
-
-# Inspect dimensions
-dim(coping.edgi.phq.raw.id)
-# Inspect colnames
-colnames(coping.edgi.phq.raw.id)
-#Differences
-dim(coping.edgi.phq.raw)[1]-dim(coping.edgi.phq.raw.id)[1]
-}
-```
-
-```{r coping edgi gad copy}
-if(EDGI == TRUE) {
-  coping.phq.raw.id <- coping.edgi.phq.raw.id
-}
-```
-
-## NBR
-```{r coping nbr phq cols}
-if(NBR == TRUE) {
-coping.nbr.phq.raw <- readRDS(file = paste0(data.raw_path, "/nbr/phq_coping_nbr.rds"))
-dim(coping.nbr.phq.raw)
-colnames(coping.nbr.phq.raw)
-}
-```
-
-```{r coping nbr phq summary labels}
-if(NBR == TRUE) {
-summarytools::dfSummary(
-  coping.nbr.phq.raw,
-  graph.col = F,
-  valid.col = F
-  #labels.col = F
-)
-}
-```
-
-Will need to double check these namings once we have the new cleaned data -- KT. 
-```{r coping nbr phq cleaning}
-if(NBR == TRUE) {
-coping.nbr.phq.raw.id <- coping.nbr.phq.raw %>%
-  drop_na(subjectid) %>% # Drop NAs
-  distinct(subjectid, .keep_all = TRUE) %>% # Remove duplicates based on ID
-  separate(subjectid, into = c("Sample", "ID.intm"), sep = 6) %>% # Split ID in Sample and Number
-  separate(ID.intm, into = "ID", sep = 7) %>%
-  mutate(ID = as.numeric(ID)) %>%
-  select(
-    Sample, # Sample
-    ID, # ID
-    phq.problems_made_difficult_care = phq.problems_made_care_difficult,
-    phq.pandemic_felt_feelings,
-    phq.little_interest_or_pleasure_in_doing_things_retro = phq.little_interest_or_pleasure_in_doing_things,
-    phq.feeling_down_depressed_or_hopeless_retro = phq.feeling_down_depressed_or_hopeless,
-    phq.staying_asleep_sleeping_trouble_retro = phq.staying_asleep_sleeping_trouble,
-    phq.feeling_tired_or_having_little_energy_retro = phq.feeling_tired_or_having_little_energy,
-    phq.poor_appetite_or_overeating_retro = phq.poor_appetite_or_overeating,
-    phq.feeling_bad_failure_family_retro = phq.family_feeling_bad_failure,
-    phq.trouble_concentrating_reading_newspaper_retro = phq.trouble_concentrating_newspaper_reading, # differ NBR prepandemic
-    phq.moving_fidgety_noticed_opposite_retro = phq.moving_fidgety_opposite_slowly, # differ NBR prepandemic
-    phq.dead_hurting_thoughts_retro = phq.dead_hurting_thoughts,
-    phq.little_interest_or_pleasure_in_doing_things_base = phq.little_interest_or_pleasure_in_doing_things.1,
-    phq.feeling_down_depressed_or_hopeless_base = phq.feeling_down_depressed_or_hopeless.1,
-    phq.staying_asleep_sleeping_trouble_base = phq.staying_asleep_sleeping_trouble.1,
-    phq.feeling_tired_or_having_little_energy_base = phq.feeling_tired_or_having_little_energy.1,
-    phq.poor_appetite_or_overeating_base = phq.poor_appetite_or_overeating.1,
-    phq.feeling_bad_failure_family_base = phq.family_feeling_bad_failure.1,
-    phq.trouble_concentrating_reading_newspaper_base = phq.trouble_concentrating_newspaper_reading.1, # differ NBR prepandemic
-    phq.moving_fidgety_noticed_opposite_base = phq.moving_fidgety_opposite_slowly.1, # differ NBR prepandemic
-    phq.dead_hurting_thoughts_base = phq.dead_hurting_thoughts.1
-  ) %>%
-  add_numeric(., exclude = exclude_cols) %>%
-  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
-  mutate_if(is.numeric, ~na_if(., -99)) %>%
-  mutate_if(is.numeric, ~na_if(., -77)) %>%
-  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
-  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
-
-# Inspect dimensions
-dim(coping.nbr.phq.raw.id)
-# Inspect colnames
-colnames(coping.nbr.phq.raw.id)
-#Differences
-dim(coping.nbr.phq.raw)[1]-dim(coping.nbr.phq.raw.id)[1]
-}
-```
-
-```{r coping nbr gad copy}
-if(NBR == TRUE) {
-  coping.phq.raw.id <- coping.nbr.phq.raw.id
-}
-```
-
-## RAMP
-```{r coping ramp phq cols}
-if(RAMP == TRUE) {
-ramp.phq.raw <- readRDS(file = paste0(data.raw_path, "/ramp/phq_ramp.rds"))
-dim(ramp.phq.raw)
-colnames(ramp.phq.raw)
-}
-```
-
-```{r coping ramp phq summary labels}
-if(RAMP == TRUE) {
-summarytools::dfSummary(
-  ramp.phq.raw,
-  graph.col = F,
-  valid.col = F
-  #labels.col = F
-)
-}
-```
-
-Will need to double check these namings once we have the new cleaned data -- KT. 
-```{r coping ramp phq cleaning}
-if(RAMP == TRUE) {
-ramp.phq.raw.id <- ramp.phq.raw %>%
-  drop_na(`Login ID`) %>% # Drop NAs
-  distinct(`Login ID`, .keep_all = TRUE) %>% # Remove duplicates based on ID
-  separate(`Login ID`, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
-  mutate(ID = as.numeric(ID)
-  ) %>%
-  select(
-    Sample, # Sample
-    ID, # ID
-    phq.problems_made_difficult_care = phq.issues_made_carrying_daily, #impact
-    phq.pandemic_felt_feelings = phq.feelings_pandemic_felt, #before the pandemic question
-    phq.little_interest_or_pleasure_in_doing_things_retro = phq.little_interest_or_pleasure_in_doing_things.1,
-    phq.feeling_down_depressed_or_hopeless_retro = phq.feeling_down_depression_or_hopeless, #THIS IS CORRECT - strange naming in raw dataset
-    phq.staying_asleep_sleeping_trouble_retro = phq.staying_asleep_sleeping_trouble.1,
-    phq.feeling_tired_or_having_little_energy_retro = phq.feeling_tired_or_having_little_energy.1,
-    phq.poor_appetite_or_overeating_retro = phq.poor_appetite_or_overeating.1,
-    phq.feeling_bad_failure_family_retro = phq.failure_family_feeling_bad.1,
-    phq.trouble_concentrating_reading_newspaper_retro = phq.trouble_concentrating_newspaper_reading.1, 
-    phq.moving_fidgety_noticed_opposite_retro = phq.moving_fidgety_opposite_slowly.1, 
-    phq.dead_hurting_thoughts_retro = phq.dead_hurting_thoughts.1,
-    phq.little_interest_or_pleasure_in_doing_things_base = phq.little_interest_or_pleasure_in_doing_things,
-    phq.feeling_down_depressed_or_hopeless_base = phq.feeling_down_depressed_or_hopeless,
-    phq.staying_asleep_sleeping_trouble_base = phq.staying_asleep_sleeping_trouble,
-    phq.feeling_tired_or_having_little_energy_base = phq.feeling_tired_or_having_little_energy,
-    phq.poor_appetite_or_overeating_base = phq.poor_appetite_or_overeating,
-    phq.feeling_bad_failure_family_base = phq.failure_family_feeling_bad,
-    phq.trouble_concentrating_reading_newspaper_base = phq.trouble_concentrating_newspaper_reading, # differ RAMP prepandemic
-    phq.moving_fidgety_noticed_opposite_base = phq.moving_fidgety_opposite_slowly, # differ RAMP prepandemic
-    phq.dead_hurting_thoughts_base = phq.dead_hurting_thoughts
-  ) %>%
-  add_numeric(., exclude = exclude_cols) %>%
-  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
-  mutate_if(is.numeric, ~na_if(., -99)) %>%
-  mutate_if(is.numeric, ~na_if(., -77)) %>%
-  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
-  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
-
-# Inspect dimensions
-dim(ramp.phq.raw.id)
-# Inspect colnames
-colnames(ramp.phq.raw.id)
-#Differences
-dim(ramp.phq.raw)[1]-dim(ramp.phq.raw.id)[1]
-}
-```
-
-```{r coping ramp gad copy}
-if(RAMP == TRUE) {
-  coping.phq.raw.id <- ramp.phq.raw.id
-}
-```
-
-## Sum scores
-
-Calculate sum score for PHQ-9 retro
-```{r coping phq sum score retro}
-# Create vector with scoring key: If the item is reversed coded use -1. 
-# There needs to be the correct number of values for each item in the questionnaire. 
-phq.items_key_retro <- c(1,1,1,1,1,1,1,1,1)
-
-# Create vector with items that are included in total score
-phq.items_retro <- c(
-  "phq.little_interest_or_pleasure_in_doing_things_retro_numeric",
-"phq.feeling_down_depressed_or_hopeless_retro_numeric",
-"phq.staying_asleep_sleeping_trouble_retro_numeric",
-"phq.feeling_tired_or_having_little_energy_retro_numeric",
-"phq.poor_appetite_or_overeating_retro_numeric",
-"phq.feeling_bad_failure_family_retro_numeric",
-"phq.trouble_concentrating_reading_newspaper_retro_numeric",
-"phq.moving_fidgety_noticed_opposite_retro_numeric",
-"phq.dead_hurting_thoughts_retro_numeric"
-)
-
-# Calulate total score
-phq.scored_items_retro <- scoreItems(keys = phq.items_key_retro,
-                                     items = coping.phq.raw.id[phq.items_retro],
-                                     totals = TRUE, 
-                                     missing = TRUE, 
-                                     impute = 'none', 
-                                     min = 0, 
-                                     max = 3)
-# Add in column to tibble
-coping.phq.raw.id$phq.sum_score_retro_raw <- phq.scored_items_retro$scores
-
-# Look at values
-coping.phq.raw.id %>%
-  descr(phq.sum_score_retro_raw,
-        stats = "common"
-  )
-```
-
-Calculate sum score for PHQ-9 base
-```{r coping phq sum score base}
-# Create vector with scoring key: If the item is reversed coded use -1. 
-# There needs to be the correct number of values for each item in the questionnaire. 
-phq.items_key_base <- c(1,1,1,1,1,1,1,1,1)
-
-# Create vector with items that are included in total score
-phq.items_base <- c(
-  "phq.little_interest_or_pleasure_in_doing_things_base_numeric",
-"phq.feeling_down_depressed_or_hopeless_base_numeric",
-"phq.staying_asleep_sleeping_trouble_base_numeric",
-"phq.feeling_tired_or_having_little_energy_base_numeric",
-"phq.poor_appetite_or_overeating_base_numeric",
-"phq.feeling_bad_failure_family_base_numeric",
-"phq.trouble_concentrating_reading_newspaper_base_numeric",
-"phq.moving_fidgety_noticed_opposite_base_numeric",
-"phq.dead_hurting_thoughts_base_numeric"
-)
-
-# Calulate total score
-phq.scored_items_base <- scoreItems(keys = phq.items_key_base,
-                                    items = coping.phq.raw.id[phq.items_base],
-                                    totals = TRUE, 
-                                    missing = TRUE, 
-                                    impute = 'none', 
-                                    min = 0, 
-                                    max = 3)
-# Add in column to tibble
-coping.phq.raw.id$phq.sum_score_base_raw <- phq.scored_items_base$scores
-
-# Look at values
-coping.phq.raw.id %>%
-  descr(phq.sum_score_base_raw,
-        stats = "common"
-  )
-```
-
-# Missingness
-
-retrospective
-```{r coping phq retro missingness}
-coping.phq.raw.id <- coping.phq.raw.id %>%
-  mutate(
-    na_per_person_phq_retro =         # variable for NA per person
-      rowSums(
-        is.na(.[phq.items_retro])
-      )
-  )
-
-coping.phq.raw.id %>%
-  freq(na_per_person_phq_retro, cumul = F) #have a look at the frequency
-```
-
-```{r coping phq retro missingness 8 items}
-coping.phq.raw.id <- coping.phq.raw.id %>%
-  mutate(
-    phq.missing_only_suicide_item_retro = 
-      if_else(
-        condition = na_per_person_phq_retro == 1 & 
-          is.na(phq.dead_hurting_thoughts_retro_numeric), 
-        true = 1,
-        false = 0,
-        missing = NA_real_
-      )
-  )
-
-coping.phq.raw.id %>%
-  freq(phq.missing_only_suicide_item_retro,
-       cumul = F)
-```
-
-baseline
-```{r coping phq base missingness}
-coping.phq.raw.id <- coping.phq.raw.id %>%
-  mutate(
-    na_per_person_phq_base =         # variable for NA per person
-      rowSums(                       
-        is.na(.[phq.items_base])
-      )
-  )
-
-coping.phq.raw.id %>%
-  freq(na_per_person_phq_base, cumul = F) #have a look at the frequency
-```
-
-We need to identify those who have all items APART from the suicide ideation item - to still include these individuals. 
-```{r coping phq base missingness 8 items}
-coping.phq.raw.id <- coping.phq.raw.id %>%
-  mutate(
-    phq.missing_only_suicide_item_base = 
-      if_else(
-        condition = na_per_person_phq_base == 1 & 
-          is.na(phq.dead_hurting_thoughts_base_numeric), 
-        true = 1,
-        false = 0,
-        missing = NA_real_
-      )
-  )
-
-coping.phq.raw.id %>%
-  freq(phq.missing_only_suicide_item_base,
-       cumul = F)
-```
-
-```{r coping phq base sum score if missing items set to NA}
-coping.phq.raw.id <- coping.phq.raw.id %>%
-  mutate(
-    phq.sum_score_base =
-      if_else(condition = na_per_person_phq_base > 0,
-              true = NA_real_,
-              false = phq.sum_score_base_raw,
-              missing = NA_real_
-      )
-  )
-
-coping.phq.raw.id %>%
-  descr(phq.sum_score_base_raw, stats = "common")
-
-coping.phq.raw.id %>%
-  descr(phq.sum_score_base, stats = "common")
-```
-
-8 items
-```{r phq base sum score if missing items set to NA - 8 items}
-coping.phq.raw.id <- coping.phq.raw.id %>%
-  mutate(
-    phq.sum_score_8items_base =
-      if_else(condition = na_per_person_phq_base > 1 &
-                phq.missing_only_suicide_item_base == 1,
-              true = NA_real_,
-              false = phq.sum_score_base_raw,
-              missing = NA_real_
-      )
-  )
-
-coping.phq.raw.id %>%
-  descr(phq.sum_score_8items_base, stats = "common")
-```
-
-```{r coping phq retro sum score if missing items set to NA}
-coping.phq.raw.id <- coping.phq.raw.id %>%
-  mutate(
-    phq.sum_score_retro =
-      if_else(condition = na_per_person_phq_retro > 0,
-              true = NA_real_,
-              false = phq.sum_score_retro_raw,
-              missing = NA_real_
-      )
-  )
-
-coping.phq.raw.id %>%
-  descr(phq.sum_score_retro_raw, stats = "common")
-
-coping.phq.raw.id %>%
-  descr(phq.sum_score_retro, stats = "common")
-```
-
-8 items
-```{r phq retro sum score if missing items set to NA - 8 items}
-coping.phq.raw.id <- coping.phq.raw.id %>%
-  mutate(
-    phq.sum_score_8items_retro =
-      if_else(condition = na_per_person_phq_retro > 1 &
-                phq.missing_only_suicide_item_retro == 1,
-              true = NA_real_,
-              false = phq.sum_score_retro_raw,
-              missing = NA_real_
-      )
-  )
-
-coping.phq.raw.id %>%
-  descr(phq.sum_score_8items_retro, stats = "common")
-```
-
-## Inspection
-
-```{r coping glad phq head}
-head(coping.phq.raw.id)
-```
-
-```{r coping glad phq summary}
-summarytools::dfSummary(
-  coping.phq.raw.id,
-  graph.col = F,
-  valid.col = F,
-  labels.col = F)
-```
-
-# COPING: OCI-R
-
-## GLAD
-```{r coping glad ocir cols}
-if(GLAD == TRUE) {
-coping.glad.ocir.raw <- readRDS(file = paste0(data.raw_path, "/glad/ocir_coping_glad.rds"))
-dim(coping.glad.ocir.raw)
-colnames(coping.glad.ocir.raw)
-}
-```
-
-```{r coping glad ocir summary labels}
-if(GLAD == TRUE) {
-summarytools::dfSummary(
-  coping.glad.ocir.raw,
-  graph.col = F,
-  valid.col = F
-  #labels.col = F
-)
-}
-```
-
-*Note that the COPING GLAD OCI-R ID numbers are stored under recipientFirstName (rather than ExternalDataReference)
-```{r coping glad ocir cleaning}
-if(GLAD == TRUE) {
-coping.glad.ocir.raw.id <- coping.glad.ocir.raw %>%
-  drop_na(recipientFirstName) %>% # Drop NAs
-  distinct(recipientFirstName, .keep_all = TRUE) %>% # Remove duplicates based on ID
-  separate(recipientFirstName, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
-  mutate(ID = as.numeric(ID)) %>%
-  select(
-    Sample, # Sample
-    ID, # ID
-    ocir.felt_pandemic_feelings, # Comparison to before the pandemic
-    ocir.i_repeatedly_check_doors_windows_drawers_etc_retro = ocir.i_repeatedly_check_doors_windows_drawers_etc.,
-    ocir.arranged_things_change_upset_retro = ocir.arranged_things_change_upset,
-    ocir.repeat_feel_numbers_retro = ocir.numbers_repeat_feel, ## Different from GLAD prepandemic
-    ocir.clean_simply_wash_feel_retro = ocir.feel_contaminated_clean_simply, ## Different from GLAD prepandemic
-    ocir.mind_upset_unpleasant_thoughts_retro = ocir.mind_upset_unpleasant_thoughts,
-    ocir.afraid_avoid_throwing_things_retro = ocir.afraid_avoid_throwing_things,
-    ocir.light_switches_water_taps_retro = ocir.light_switches_water_taps,
-    ocir.arranged_things_retro = ocir.arranged_things,
-    ocir.good_feel_bad_numbers_retro = ocir.bad_numbers_good_feel, ## Different from GLAD prepandemic
-    ocir.hands_longer_wash_retro = ocir.longer_hands_wash, ## Different from GLAD prepandemic
-    ocir.saved_things_retro = ocir.saved_things,
-    ocir.frequently_difficulty_rid_nasty_retro = ocir.frequently_rid_difficulty_nasty, ## Different from GLAD prepandemic
-    ocir.i_check_things_more_often_than_necessary_retro = ocir.i_check_things_more_often_than_necessary.,
-    ocir.arranged_properly_objects_upset_retro = ocir.arranged_properly_objects_upset,
-    ocir.feel_compelled_count_things_retro = ocir.feel_compelled_count_things,
-    ocir.strangers_touch_touched_difficult_retro = ocir.strangers_touch_touched_object, ## Different from GLAD prepandemic
-    ocir.control_difficult_find_thoughts_retro = ocir.control_find_difficult_thoughts, ## Different from GLAD prepandemic
-    ocir.i_collect_things_i_dont_need_retro = ocir.i_collect_things_i_dont_need., ## Different from GLAD prepandemic
-    ocir.i_repeatedly_check_doors_windows_drawers_etc_base = ocir.i_repeatedly_check_doors_windows_drawers_etc..1,
-    ocir.arranged_things_change_upset_base = ocir.arranged_things_change_upset.1,
-    ocir.repeat_feel_numbers_base = ocir.numbers_repeat_feel.1, ## Different from GLAD prepandemic
-    ocir.clean_simply_wash_feel_base = ocir.feel_contaminated_clean_simply.1, ## Different from GLAD prepandemic
-    ocir.mind_upset_unpleasant_thoughts_base = ocir.mind_upset_unpleasant_thoughts.1,
-    ocir.afraid_avoid_throwing_things_base = ocir.afraid_avoid_throwing_things.1,
-    ocir.light_switches_water_taps_base = ocir.light_switches_water_taps.1,
-    ocir.arranged_things_base = ocir.arranged_things.1,
-    ocir.good_feel_bad_numbers_base = ocir.bad_numbers_good_feel.1, ## Different from GLAD prepandemic
-    ocir.hands_longer_wash_base = ocir.longer_hands_wash.1, ## Different from GLAD prepandemic
-    ocir.saved_things_base = ocir.saved_things.1,
-    ocir.frequently_difficulty_rid_nasty_base = ocir.frequently_rid_difficulty_nasty.1, ## Different from GLAD prepandemic
-    ocir.i_check_things_more_often_than_necessary_base = ocir.i_check_things_more_often_than_necessary..1,
-    ocir.arranged_properly_objects_upset_base = ocir.arranged_properly_objects_upset.1,
-    ocir.feel_compelled_count_things_base = ocir.feel_compelled_count_things.1,
-    ocir.strangers_touch_touched_difficult_base = ocir.strangers_touch_touched_object.1, ## Different from GLAD prepandemic
-    ocir.control_difficult_find_thoughts_base = ocir.control_find_difficult_thoughts.1, ## Different from GLAD prepandemic
-    ocir.i_collect_things_i_dont_need_base = ocir.i_collect_things_i_dont_need..1
-  ) %>%
-  add_numeric(., exclude = exclude_cols) %>%
-  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
-  mutate_if(is.numeric, ~na_if(., -99)) %>%
-  mutate_if(is.numeric, ~na_if(., -77)) %>%
-  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
-  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
-
-# Inspect dimensions
-dim(coping.glad.ocir.raw.id)
-# Inspect colnames
-colnames(coping.glad.ocir.raw.id)
-#Differences
-dim(coping.glad.ocir.raw)[1]-dim(coping.glad.ocir.raw.id)[1]
-}
-```
-
-```{r coping glad ocir copy}
-if(GLAD == TRUE) {
-  coping.ocir.raw.id <- coping.glad.ocir.raw.id
-}
-```
-
-## EDGI
-```{r coping edgi ocir cols}
-if(EDGI == TRUE) {
-coping.edgi.ocir.raw <- readRDS(file = paste0(data.raw_path, "/edgi/ocir_coping_edgi.rds"))
-dim(coping.edgi.ocir.raw)
-colnames(coping.edgi.ocir.raw)
-}
-```
-
-```{r coping edgi ocir summary labels}
-if(EDGI == TRUE) {
-summarytools::dfSummary(
-  coping.edgi.ocir.raw,
-  graph.col = F,
-  valid.col = F
-  #labels.col = F
-)
-}
-```
-
-*Note that the COPING EDGI OCI-R ID numbers are stored under recipientFirstName (rather than ExternalDataReference)
-```{r coping edgi ocir cleaning}
-if(EDGI == TRUE) {
-coping.edgi.ocir.raw.id <- coping.edgi.ocir.raw %>%
-  drop_na(externalDataReference) %>% # Drop NAs
-  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
-  separate(externalDataReference, into = c("Sample", "ID"), sep = 6) %>% # Split ID in Sample and Number
-  mutate(ID = as.numeric(ID)) %>%
-  select(
-    Sample, # Sample
-    ID, # ID
-    ocir.felt_pandemic_feelings, # Comparison to before the pandemic
-    ocir.i_repeatedly_check_doors_windows_drawers_etc_retro = ocir.i_repeatedly_check_doors_windows_drawers_etc.,
-    ocir.arranged_things_change_upset_retro = ocir.arranged_things_change_upset,
-    ocir.repeat_feel_numbers_retro = ocir.repeat_numbers_feel, # Different from EDGI prepandemic ocir.numbers_repeat_feel,
-    ocir.clean_simply_wash_feel_retro = ocir.feel_contaminated_clean_simply, ## Different from EDGI prepandemic
-    ocir.mind_upset_unpleasant_thoughts_retro = ocir.mind_upset_unpleasant_thoughts,
-    ocir.afraid_avoid_throwing_things_retro = ocir.afraid_avoid_throwing_things,
-    ocir.light_switches_water_taps_retro = ocir.water_taps_light_switches, #  differ ocir.light_switches_water_taps,
-    ocir.arranged_things_retro = ocir.arranged_things,
-    ocir.good_feel_bad_numbers_retro = ocir.bad_numbers_good_feel, ## Different from EDGI prepandemic
-    ocir.hands_longer_wash_retro = ocir.longer_hands_wash, ## Different from EDGI prepandemic
-    ocir.saved_things_retro = ocir.saved_things,
-    ocir.frequently_difficulty_rid_nasty_retro = ocir.frequently_rid_difficulty_nasty, ## Different from EDGI prepandemic
-    ocir.i_check_things_more_often_than_necessary_retro = ocir.i_check_things_more_often_than_necessary.,
-    ocir.arranged_properly_objects_upset_retro = ocir.arranged_properly_objects_upset,
-    ocir.feel_compelled_count_things_retro = ocir.feel_compelled_count_things,
-    ocir.strangers_touch_touched_difficult_retro = ocir.strangers_touch_touched_object, ## Different from EDGI prepandemic
-    ocir.control_difficult_find_thoughts_retro = ocir.control_difficult_thoughts_find, # Differ to EDGI prepan ocir.control_find_difficult_thoughts,
-    ocir.i_collect_things_i_dont_need_retro = ocir.i_collect_things_i_dont_need., ## Different from EDGI prepandemic
-    ocir.i_repeatedly_check_doors_windows_drawers_etc_base = ocir.i_repeatedly_check_doors_windows_drawers_etc..1,
-    ocir.arranged_things_change_upset_base = ocir.arranged_things_change_upset.1,
-    ocir.repeat_feel_numbers_base = ocir.repeat_numbers_feel.1, ## Different from EDGI prepandemic
-    ocir.clean_simply_wash_feel_base = ocir.feel_contaminated_clean_simply.1, ## Different from EDGI prepandemic
-    ocir.mind_upset_unpleasant_thoughts_base = ocir.mind_upset_unpleasant_thoughts.1,
-    ocir.afraid_avoid_throwing_things_base = ocir.afraid_avoid_throwing_things.1,
-    ocir.light_switches_water_taps_base = ocir.water_taps_light_switches.1, # differ
-    ocir.arranged_things_base = ocir.arranged_things.1,
-    ocir.good_feel_bad_numbers_base = ocir.bad_numbers_good_feel.1, ## Different from EDGI prepandemic
-    ocir.hands_longer_wash_base = ocir.longer_hands_wash.1, ## Different from EDGI prepandemic
-    ocir.saved_things_base = ocir.saved_things.1,
-    ocir.frequently_difficulty_rid_nasty_base = ocir.frequently_rid_difficulty_nasty.1, ## Different from EDGI prepandemic
-    ocir.i_check_things_more_often_than_necessary_base = ocir.i_check_things_more_often_than_necessary..1,
-    ocir.arranged_properly_objects_upset_base = ocir.arranged_properly_objects_upset.1,
-    ocir.feel_compelled_count_things_base = ocir.feel_compelled_count_things.1,
-    ocir.strangers_touch_touched_difficult_base = ocir.strangers_touch_touched_object.1, ## Different from EDGI prepandemic
-    ocir.control_difficult_find_thoughts_base = ocir.control_difficult_thoughts_find.1, ## Different from EDGI prepandemic
-    ocir.i_collect_things_i_dont_need_base = ocir.i_collect_things_i_dont_need..1
-  ) %>%
-  add_numeric(., exclude = exclude_cols) %>%
-  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
-  mutate_if(is.numeric, ~na_if(., -99)) %>%
-  mutate_if(is.numeric, ~na_if(., -77)) %>%
-  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
-  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
-
-# Inspect dimensions
-dim(coping.edgi.ocir.raw.id)
-# Inspect colnames
-colnames(coping.edgi.ocir.raw.id)
-#Differences
-dim(coping.edgi.ocir.raw)[1]-dim(coping.edgi.ocir.raw.id)[1]
-}
-```
-
-```{r coping edgi ocir copy}
-if(EDGI == TRUE) {
-  coping.ocir.raw.id <- coping.edgi.ocir.raw.id
-}
-```
-
-## NBR
-```{r coping nbr ocir cols}
-if(NBR == TRUE) {
-coping.nbr.ocir.raw <- readRDS(file = paste0(data.raw_path, "/nbr/ocir_coping_nbr.rds"))
-dim(coping.nbr.ocir.raw)
-colnames(coping.nbr.ocir.raw)
-}
-```
-
-```{r coping nbr ocir summary labels}
-if(NBR == TRUE) {
-summarytools::dfSummary(
-  coping.nbr.ocir.raw,
-  graph.col = F,
-  valid.col = F
-  #labels.col = F
-)
-}
-```
-
-*Note that the COPING NBR OCI-R ID numbers are stored under recipientFirstName (rather than ExternalDataReference)
-
-++MD: One NBR ID is being converted to NA by the as.numeric(ID) line of code.
-```{r coping nbr ocir cleaning}
-if(NBR == TRUE) {
-coping.nbr.ocir.raw.id <- coping.nbr.ocir.raw %>%
-  drop_na(recipientFirstName) %>% # Drop NAs
-  distinct(recipientFirstName, .keep_all = TRUE) %>% # Remove duplicates based on ID
-  separate(recipientFirstName, into = c("Sample", "ID.intm"), sep = 6) %>% # Split ID in Sample and Number
-  separate(ID.intm, into = "ID", sep = 7) %>%
-  mutate(ID = as.numeric(ID)) %>%
-  select(
-    Sample, # Sample
-    ID, # ID
-    ocir.felt_pandemic_feelings, # Comparison to before the pandemic
-    ocir.i_repeatedly_check_doors_windows_drawers_etc_retro = ocir.i_repeatedly_check_doors_windows_drawers_etc.,
-    ocir.arranged_things_change_upset_retro = ocir.arranged_things_change_upset,
-    ocir.repeat_feel_numbers_retro = ocir.repeat_numbers_feel, ## Different from GLAD
-    ocir.clean_simply_wash_feel_retro = ocir.feel_contaminated_clean_simply,
-    ocir.mind_upset_unpleasant_thoughts_retro = ocir.mind_upset_unpleasant_thoughts,
-    ocir.afraid_avoid_throwing_things_retro = ocir.afraid_avoid_throwing_things,
-    ocir.light_switches_water_taps_retro = ocir.water_taps_light_switches, ## Different from GLAD
-    ocir.arranged_things_retro = ocir.arranged_things,
-    ocir.good_feel_bad_numbers_retro = ocir.bad_numbers_good_feel,
-    ocir.hands_longer_wash_retro = ocir.longer_hands_wash, 
-    ocir.saved_things_retro = ocir.saved_things,
-    ocir.frequently_difficulty_rid_nasty_retro = ocir.frequently_rid_difficulty_nasty, 
-    ocir.i_check_things_more_often_than_necessary_retro = ocir.i_check_things_more_often_than_necessary.,
-    ocir.arranged_properly_objects_upset_retro = ocir.arranged_properly_objects_upset,
-    ocir.feel_compelled_count_things_retro = ocir.feel_compelled_count_things,
-    ocir.strangers_touch_touched_difficult_retro = ocir.strangers_touch_touched_object, 
-    ocir.control_difficult_find_thoughts_retro = ocir.control_difficult_thoughts_find, ## Different from GLAD 
-    ocir.i_collect_things_i_dont_need_retro = ocir.i_collect_things_i_dont_need., 
-    ocir.i_repeatedly_check_doors_windows_drawers_etc_base = ocir.i_repeatedly_check_doors_windows_drawers_etc..1,
-    ocir.arranged_things_change_upset_base = ocir.arranged_things_change_upset.1,
-    ocir.repeat_feel_numbers_base = ocir.repeat_numbers_feel.1, ## Different from GLAD
-    ocir.clean_simply_wash_feel_base = ocir.feel_contaminated_clean_simply.1,
-    ocir.mind_upset_unpleasant_thoughts_base = ocir.mind_upset_unpleasant_thoughts.1,
-    ocir.afraid_avoid_throwing_things_base = ocir.afraid_avoid_throwing_things.1,
-    ocir.light_switches_water_taps_base = ocir.water_taps_light_switches.1, ## Different from GLAD
-    ocir.arranged_things_base = ocir.arranged_things.1,
-    ocir.good_feel_bad_numbers_base = ocir.bad_numbers_good_feel.1, 
-    ocir.hands_longer_wash_base = ocir.longer_hands_wash.1, 
-    ocir.saved_things_base = ocir.saved_things.1,
-    ocir.frequently_difficulty_rid_nasty_base = ocir.frequently_rid_difficulty_nasty.1, 
-    ocir.i_check_things_more_often_than_necessary_base = ocir.i_check_things_more_often_than_necessary..1,
-    ocir.arranged_properly_objects_upset_base = ocir.arranged_properly_objects_upset.1,
-    ocir.feel_compelled_count_things_base = ocir.feel_compelled_count_things.1,
-    ocir.strangers_touch_touched_difficult_base = ocir.strangers_touch_touched_object.1, 
-    ocir.control_difficult_find_thoughts_base = ocir.control_difficult_thoughts_find.1,
-    ocir.i_collect_things_i_dont_need_base = ocir.i_collect_things_i_dont_need..1
-  ) %>%
-  add_numeric(., exclude = exclude_cols) %>%
-  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
-  mutate_if(is.numeric, ~na_if(., -99)) %>%
-  mutate_if(is.numeric, ~na_if(., -77)) %>%
-  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
-  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
-
-# Inspect dimensions
-dim(coping.nbr.ocir.raw.id)
-# Inspect colnames
-colnames(coping.nbr.ocir.raw.id)
-#Differences
-dim(coping.nbr.ocir.raw)[1]-dim(coping.nbr.ocir.raw.id)[1]
-}
-```
-
-```{r coping nbr ocir copy}
-if(NBR == TRUE) {
-  coping.ocir.raw.id <- coping.nbr.ocir.raw.id
-}
-```
-
-## RAMP
-```{r coping ramp ocir cols}
-if(RAMP == TRUE) {
-ramp.ocir.raw <- readRDS(file = paste0(data.raw_path, "/ramp/ocir_ramp.rds"))
-dim(ramp.ocir.raw)
-colnames(ramp.ocir.raw)
-}
-```
-
-```{r coping ramp ocir summary labels}
-if(RAMP == TRUE) {
-summarytools::dfSummary(
-  ramp.ocir.raw,
-  graph.col = F,
-  valid.col = F
-  #labels.col = F
-)
-}
-```
-
-*Note that the COPING RAMP OCI-R ID numbers are stored under recipientFirstName (rather than ExternalDataReference)
-```{r coping ramp ocir cleaning}
-if(RAMP == TRUE) {
-ramp.ocir.raw.id <- ramp.ocir.raw %>%
-  drop_na(`Login ID`) %>% # Drop NAs
-  distinct(`Login ID`, .keep_all = TRUE) %>% # Remove duplicates based on ID
-  separate(`Login ID`, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
-  mutate(ID = as.numeric(ID)) %>%
-  select(
-    Sample, # Sample
-    ID, # ID
-    ocir.felt_pandemic_feelings = ocir.feelings_pandemic_felt, # Comparison to before the pandemic
-    ocir.saved_things_retro = ocir.saved_things.1, #reordered items to reflect questionnaire
-    ocir.i_check_things_more_often_than_necessary_retro = ocir.i_check_things_more_often_than_necessary..1, #in RAMP .1 = retrospective
-    ocir.arranged_properly_objects_upset_retro = ocir.arranged_properly_objects_upset.1,
-    ocir.feel_compelled_count_things_retro = ocir.feel_compelled_count_things.1,
-    ocir.strangers_touch_touched_difficult_retro = ocir.touch_touched_strangers_object.1,
-    ocir.control_difficult_find_thoughts_retro = ocir.find_control_difficult_thoughts.1,
-    ocir.i_collect_things_i_dont_need_retro = ocir.i_collect_things_i_dont_need..1,
-    ocir.i_repeatedly_check_doors_windows_drawers_etc_retro = ocir.i_repeatedly_check_doors_windows_drawers_etc..1,
-    ocir.arranged_things_change_upset_retro = ocir.arranged_things_change_upset.1,
-    ocir.repeat_feel_numbers_retro = ocir.numbers_repeat_feel.1, 
-    ocir.clean_simply_wash_feel_retro = ocir.feel_contaminated_clean_simply.1, 
-    ocir.mind_upset_unpleasant_thoughts_retro = ocir.unpleasant_thoughts_mind_upset.1,
-    ocir.afraid_avoid_throwing_things_retro = ocir.afraid_avoid_throwing_things.1,
-    ocir.light_switches_water_taps_retro = ocir.repeatedly_check_gas_water.1,
-    ocir.arranged_things_retro = ocir.arranged_things.1,
-    ocir.good_feel_bad_numbers_retro = ocir.bad_numbers_good_feel.1, 
-    ocir.hands_longer_wash_retro = ocir.longer_hands_wash.1, 
-    ocir.frequently_difficulty_rid_nasty_retro = ocir.difficulty_rid_frequently_nasty.1, 
-    ocir.saved_things_base = ocir.saved_things,
-    ocir.i_check_things_more_often_than_necessary_base = ocir.i_check_things_more_often_than_necessary.,
-    ocir.arranged_properly_objects_upset_base = ocir.arranged_properly_objects_upset,
-    ocir.feel_compelled_count_things_base = ocir.feel_compelled_count_things,
-    ocir.strangers_touch_touched_difficult_base = ocir.touch_touched_strangers_object, 
-    ocir.control_difficult_find_thoughts_base = ocir.find_control_difficult_thoughts, 
-    ocir.i_collect_things_i_dont_need_base = ocir.i_collect_things_i_dont_need.,
-    ocir.i_repeatedly_check_doors_windows_drawers_etc_base = ocir.i_repeatedly_check_doors_windows_drawers_etc.,
-    ocir.arranged_things_change_upset_base = ocir.arranged_things_change_upset,
-    ocir.repeat_feel_numbers_base = ocir.numbers_repeat_feel, 
-    ocir.clean_simply_wash_feel_base = ocir.feel_contaminated_clean_simply, 
-    ocir.mind_upset_unpleasant_thoughts_base = ocir.unpleasant_thoughts_mind_upset,
-    ocir.afraid_avoid_throwing_things_base = ocir.afraid_avoid_throwing_things,
-    ocir.light_switches_water_taps_base = ocir.repeatedly_check_gas_water,
-    ocir.arranged_things_base = ocir.arranged_things,
-    ocir.good_feel_bad_numbers_base = ocir.bad_numbers_good_feel, 
-    ocir.hands_longer_wash_base = ocir.longer_hands_wash, 
-    ocir.frequently_difficulty_rid_nasty_base = ocir.difficulty_rid_frequently_nasty
-  ) %>%
-  add_numeric(., exclude = exclude_cols) %>%
-  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
-  mutate_if(is.numeric, ~na_if(., -99)) %>%
-  mutate_if(is.numeric, ~na_if(., -77)) %>%
-  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
-  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
-
-# Inspect dimensions
-dim(ramp.ocir.raw.id)
-# Inspect colnames
-colnames(ramp.ocir.raw.id)
-#Differences
-dim(ramp.ocir.raw)[1]-dim(ramp.ocir.raw.id)[1]
-}
-```
-
-```{r coping ramp ocir copy}
-if(RAMP == TRUE) {
-  coping.ocir.raw.id <- ramp.ocir.raw.id
-}
-```
-
-## Sum scores
-
-Calculate sum score for OCI-R retro
-```{r coping ocir sum score retro}
-# Create vector with scoring key: If the item is reversed coded use -1. 
-# There needs to be the correct number of values for each item in the questionnaire. 
-ocir.items_key_retro <- c(1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1)
-
-# Create vector with items that are included in total score
-ocir.items_retro = c(
-  "ocir.i_repeatedly_check_doors_windows_drawers_etc_retro",
-  "ocir.arranged_things_change_upset_retro",
-  "ocir.repeat_feel_numbers_retro",
-  "ocir.clean_simply_wash_feel_retro",
-  "ocir.mind_upset_unpleasant_thoughts_retro",
-  "ocir.afraid_avoid_throwing_things_retro",
-  "ocir.light_switches_water_taps_retro",
-  "ocir.arranged_things_retro",
-  "ocir.good_feel_bad_numbers_retro",
-  "ocir.hands_longer_wash_retro",
-  "ocir.saved_things_retro",
-  "ocir.frequently_difficulty_rid_nasty_retro",
-  "ocir.i_check_things_more_often_than_necessary_retro",
-  "ocir.arranged_properly_objects_upset_retro",
-  "ocir.feel_compelled_count_things_retro",
-  "ocir.strangers_touch_touched_difficult_retro",
-  "ocir.control_difficult_find_thoughts_retro",
-  "ocir.i_collect_things_i_dont_need_retro"
-)
-
-# Calulate total score
-ocir.scored_items_retro <- scoreItems(keys = ocir.items_key_retro,
-                                     items = coping.ocir.raw.id[ocir.items_retro],
-                                     totals = TRUE, 
-                                     missing = TRUE, 
-                                     impute = 'none', 
-                                     min = 0, 
-                                     max = 4)
-# Add in column to tibble
-coping.ocir.raw.id$ocir.sum_score_retro_raw <- ocir.scored_items_retro$scores
-
-# Look at values
-coping.ocir.raw.id %>%
-  descr(ocir.sum_score_retro_raw,
-        stats = "common"
-  )
-```
-
-Calculate sum score for OCI-R base
-```{r coping ocir sum score base}
-# Create vector with scoring key: If the item is reversed coded use -1. 
-# There needs to be the correct number of values for each item in the questionnaire. 
-ocir.items_key_base <- c(1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1)
-
-# Create vector with items that are included in total score
-ocir.items_base = c(
-  "ocir.i_repeatedly_check_doors_windows_drawers_etc_base",
-  "ocir.arranged_things_change_upset_base",
-  "ocir.repeat_feel_numbers_base",
-  "ocir.clean_simply_wash_feel_base",
-  "ocir.mind_upset_unpleasant_thoughts_base",
-  "ocir.afraid_avoid_throwing_things_base",
-  "ocir.light_switches_water_taps_base",
-  "ocir.arranged_things_base",
-  "ocir.good_feel_bad_numbers_base",
-  "ocir.hands_longer_wash_base",
-  "ocir.saved_things_base",
-  "ocir.frequently_difficulty_rid_nasty_base",
-  "ocir.i_check_things_more_often_than_necessary_base",
-  "ocir.arranged_properly_objects_upset_base",
-  "ocir.feel_compelled_count_things_base",
-  "ocir.strangers_touch_touched_difficult_base",
-  "ocir.control_difficult_find_thoughts_base",
-  "ocir.i_collect_things_i_dont_need_base"
-)
-
-# Calulate total score
-ocir.scored_items_base <- scoreItems(keys = ocir.items_key_base,
-                                    items = coping.ocir.raw.id[ocir.items_base],
-                                    totals = TRUE, 
-                                    missing = TRUE, 
-                                    impute = 'none', 
-                                    min = 0, 
-                                    max = 4)
-# Add in column to tibble
-coping.ocir.raw.id$ocir.sum_score_base_raw <- ocir.scored_items_base$scores
-
-# Look at values
-coping.ocir.raw.id %>%
-  descr(ocir.sum_score_base_raw,
-        stats = "common"
-  )
-```
-
-# Missingness
-
-retrospective
-```{r coping ocir retro missingness}
-coping.ocir.raw.id <- coping.ocir.raw.id %>%
-  mutate(
-    na_per_person_ocir_retro =         # variable for NA per person
-      rowSums(
-        is.na(.[ocir.items_retro])
-      )
-  )
-
-coping.ocir.raw.id %>%
-  freq(na_per_person_ocir_retro, cumul = F) #have a look at the frequency
-```
-
-baseline
-```{r coping ocir base missingness}
-coping.ocir.raw.id <- coping.ocir.raw.id %>%
-  mutate(
-    na_per_person_ocir_base =         # variable for NA per person
-      rowSums(                       
-        is.na(.[ocir.items_base])
-      )
-  )
-
-coping.ocir.raw.id %>%
-  freq(na_per_person_ocir_base, cumul = F) #have a look at the frequency
-```
-
-```{r coping ocir base sum score if missigng items set to NA}
-coping.ocir.raw.id <- coping.ocir.raw.id %>%
-  mutate(
-    ocir.sum_score_base =
-      if_else(condition = na_per_person_ocir_base > 0,
-              true = NA_real_,
-              false = ocir.sum_score_base_raw,
-              missing = NA_real_
-      )
-  )
-
-coping.ocir.raw.id %>%
-  descr(ocir.sum_score_base_raw, stats = "common")
-
-coping.ocir.raw.id %>%
-  descr(ocir.sum_score_base, stats = "common")
-```
-
-```{r coping ocir retro sum score if missigng items set to NA}
-coping.ocir.raw.id <- coping.ocir.raw.id %>%
-  mutate(
-    ocir.sum_score_retro =
-      if_else(condition = na_per_person_ocir_retro > 0,
-              true = NA_real_,
-              false = ocir.sum_score_retro_raw,
-              missing = NA_real_
-      )
-  )
-
-coping.ocir.raw.id %>%
-  descr(ocir.sum_score_retro_raw, stats = "common")
-
-coping.ocir.raw.id %>%
-  descr(ocir.sum_score_retro, stats = "common")
-```
-
-# Inspection
-
-```{r coping glad ocir head}
-head(coping.ocir.raw.id)
-```
-
-```{r coping glad ocir summary}
-summarytools::dfSummary(
-  coping.ocir.raw.id,
-  graph.col = F,
-  valid.col = F,
-  labels.col = F)
-```
-
-# Join tibbles together
-
-glad/edgi data frame list
-```{r glad/edgi data frame list}
-if(GLAD == TRUE | EDGI == TRUE) {
-dfs.list <- list(
-  dem.raw.id,
-  prepan.gad.raw.id,
-  mhd.raw.categories,
-  prepan.ocir.raw.id,
-  prepan.pcl.raw.id,
-  prepan.phq.raw.id,
-  coping.gad.raw.id,
-  coping.pcl.raw.id,
-  coping.phq.raw.id,
-  coping.ocir.raw.id
-)
-}
-```
-
-Removing all prepandemic dataframes from NBR/RAMP (prepandemic measures don't exist for these cohorts)
-```{r nbr/ramp data frame list}
-if(NBR == TRUE | RAMP == TRUE) {
-dfs.list <- list(
-  dem.raw.id,
-  mhd.raw.categories,
-  coping.gad.raw.id,
- # coping.pcl.raw.id, #WAITING FOR PCL DATA FOR RAMP
-  coping.phq.raw.id,
-  coping.ocir.raw.id
-)
-}
-```
-
-```{r Join all questionnaires}
-dat.raw <- plyr::join_all(
-  dfs.list,
-  by = c("ID", "Sample") # Alternatively you can join by several columns EDGI -> "Age", "Sex", "Birthyear"
-  )
-
-#look at the data
-skimr::skim(dat.raw)
-```
-
-Check duplicates again to be saved
-+++KLP: RAMP: More than one column: Age, Sex, Login ID; if they match on all 3 then we treat them as a duplicate; otherwise we are going to rename the Login ID
-+++KT: No duplicates identified by ID in GLAD. 
-+++MD: Duplicates have been removed in cleaning script for NBR. No duplicates at this stage.
-```{r Check duplicates}
-dat.raw$ID.dup <- duplicated(dat.raw$ID)
-
-summary(as.factor(dat.raw$ID.dup))
-
-dat.dup <- dat.raw %>%
-  filter(ID.dup == TRUE)
-
-dat.raw.no.dup <- dat.raw %>%
-  filter(ID.dup == FALSE)
-```
-
-#Exclusion
-Exclude those without sex, gender, age and incomplete PHQ/GAD items
-Create a new new object for each exclusion step, e.g., data.no_sex, data.no_gender and data.no_sex.no_age
-```{r Exclude participants that do not report sex}
-if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE){
-dim(dat.raw)
-dat.no.sex <- dat.raw %>%
-  drop_na(Sex)
-dim(dat.no.sex)
-
-dim(dat.raw)[1]-dim(dat.no.sex)[1]
-}
-```
-`r dim(dat.glad.raw)[1]-dim(dat.no.sex)[1]` were excluded because they did not report their sex
-
-```{r rename dataset for ramp}
-if(RAMP == TRUE){
-#there is no sex variable in ramp
-dat.no.sex <- dat.raw
-}
-```
-
-```{r Exclude participants that do not report gender}
-dim(dat.no.sex)
-dat.no.sex.no.gender <- dat.no.sex %>%
-  drop_na(Gender)
-dim(dat.no.sex.no.gender)
-
-dim(dat.no.sex)[1]-dim(dat.no.sex.no.gender)[1]
-```
-`r dim(dat.no.sex)[1]-dim(dat.no.sex.no.gender)[1]` were excluded because they did not report their sex
-
-```{r Exclude participants that do not report age}
-dim(dat.no.sex.no.gender)
-dat.no.sex.no.gender.no.age <- dat.no.sex.no.gender %>%
-  drop_na(age_category_full)
-dim(dat.no.sex.no.gender.no.age)
-
-dim(dat.no.sex.no.gender)[1]-dim(dat.no.sex.no.gender.no.age)[1]
-```
-`r dim(dat.no.gender)[1]-dim(dat.no.sex.no.gender.no.age)[1]` were excluded because they did not report their age
-
-Exclusion of inflammatory bowel disease (IBD) BioResource (BR) cohort
-++MD: 3,410 participants from NBR IBD cohort excluded
-```{r COVID exclusion of IBD}
-if(NBR == TRUE) {
-dim(dat.no.sex.no.gender.no.age)
-
-dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age %>%
-  filter(Cohort != "IBD")
-
-dim(dat.no.sex.no.gender.no.age.no.ibd)
-dim(dat.no.sex.no.gender.no.age)[1]-dim(dat.no.sex.no.gender.no.age.no.ibd)[1]
-}
-
-if(GLAD == TRUE | EDGI == TRUE | RAMP == TRUE) {
-dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age
-}
-```
-
-##Create tidy data on which the exclusion criteria have been applied
-Complete sex, gender, age and missingness information applied. 
-```{r Tidy data}
-dat <- dat.no.sex.no.gender.no.age.no.ibd
-
-skimr::skim(dat)
-```
-
-# Definition of prepandemic and baseline 
-Exlcude people who have joined GLAD/EDGI after the pandemic began, sensitivity analyses done on the cut off's we have chosen. 
-Potentially GLAD/EDGI particiapnts between January to April. EDGI launched on February 24th.
-
-Prepandemic GLAD/EDGI = Prepandemic (GLAD/EDGI sign-up questionnaire)
-
-Retrospective = COPING/RAMP sign up questionnaire; *only of those participants who have reported a change in symptoms*
-
-Baseline = COPING/RAMP sign up questionnaire
-
-Dates for the definition of prepandemic
-```{r Potential dates for prepandemic definition}
-# Date of the first COVID-19 case in the United Kingdom (UK)
-date_first_case_uk_january_31 <- as.POSIXct("2020-01-31")
-
-# Date for assumed higher awareness of COVID / Lockdown in Italy 4. March 2020 / first festivals cancelled
-date_higher_awareness_march_1 <- as.POSIXct("2020-03-01")
-
-# Date the UK went into lockdown
-date_uk_lockdown_march_23 <- as.POSIXct("2020-03-23")
-```
-
-```{r Prepandemic definitions january_31}
-if(GLAD == TRUE | EDGI == TRUE){
-dat <- dat %>%
-  mutate(
-    prepandemic_january_31_numeric =
-      if_else(
-        startDate.prepandemic > date_first_case_uk_january_31, # The GLAD sign up is dated before the cut off (> longer ago)
-        true = 0, # Participant has not signed up before the pandemic,
-        false = 1, # Participant has signed up before the pandemic,
-        missing = NA_real_
-      )
-  )
-
-dat <- dat %>%
-  mutate(
-    prepandemic_january_31 =
-      recode_factor(
-        prepandemic_january_31_numeric,
-        "0" = "Sign up after 31. January",
-        "1" = "Sign up before 31. January"
-      )
-  )
-
-dat %>%
-  freq(prepandemic_january_31)
-}
-```
-
-```{r Prepandemic definitions march_1}
-if(GLAD == TRUE | EDGI == TRUE){
-dat <- dat %>%
-  mutate(
-    prepandemic_march_1_numeric =
-      if_else(
-        startDate.prepandemic > date_higher_awareness_march_1, # The GLAD sign up is dated before the cut off (> longer ago)
-        true = 0, # Participant has not signed up before the pandemic,
-        false = 1, # Participant has signed up before the pandemic,
-        missing = NA_real_
-      )
-  )
-
-dat <- dat %>%
-  mutate(
-    prepandemic_march_1 =
-      recode_factor(
-        prepandemic_march_1_numeric,
-        "0" = "Sign up after 1. March",
-        "1" = "Sign up before 1. March"
-      )
-  )
-
-dat %>%
-  freq(prepandemic_march_1)
-}
-```
-
-```{r Prepandemic definitions march_23}
-if(GLAD == TRUE | EDGI == TRUE){
-dat <- dat %>%
-  mutate(
-    prepandemic_march_23_numeric =
-      if_else(
-        startDate.prepandemic > date_uk_lockdown_march_23, # The GLAD sign up is dated before the cut off (> longer ago)
-        true = 0, # Participant has not signed up before the pandemic,
-        false = 1, # Participant has signed up before the pandemic,
-        missing = NA_real_
-      )
-  )
-
-dat <- dat %>%
-  mutate(
-    prepandemic_march_23 =
-      recode_factor(
-        prepandemic_march_23_numeric,
-        "0" = "Sign up after 23. March",
-        "1" = "Sign up before 23. March"
-      )
-  )
-
-dat %>%
-  freq(prepandemic_march_23)
-}
-```
-
-Calculate the time difference between time difference between sign up questionnaire and COPING questionnaire
-```{r time difference between sign up questionnaire and COPING questionnaire}
-if(GLAD == TRUE | EDGI == TRUE){
-dat <- dat %>%
-  mutate(
-    time_diff_sign_up_coping =
-        as.numeric(
-        difftime(           #this function does time1 - time2 as difftime(time1, time2...)
-          startDate.coping,    #should be start date for COPING (time1)
-          startDate.prepandemic),    #should be start date for GLAD (time2)
-          units = c("days")  #can also be "secs", "mins", "hours", "weeks"
-          )
-        )
-
-dat %>%
-  descr(
-    var = time_diff_sign_up_coping,
-    stats = "common"
-    )
-}
-```
-
-Proportion of people signed up over one year ago
-```{r glad/edgi ppts signed up over one year ago, eval=FALSE, include=FALSE}
-if(GLAD == TRUE | EDGI == TRUE){
-dat <- dat %>%
-  mutate(
-    over_one_year_time_diff_sign_up_coping_numeric =
-      as.numeric(
-        if_else(time_diff_sign_up_coping > 365, 1, 0
-                )
-      )
-  )
-
-dat <- dat %>%
-  mutate(
-    over_one_year_time_diff_sign_up_coping =
-      recode_factor(
-        over_one_year_time_diff_sign_up_coping_numeric,
-        "0" = "Sign up under one year before COPING",
-        "1" = "Sign up over one year before COPING"
-      )
-  )
-
-dat %>%
-  freq(over_one_year_time_diff_sign_up_coping, cumul = F)
-}
-```
-
-Proportion of people signed up over half a year ago
-```{r glad/edgi ppts signed up over half a year ago, r eval=FALSE, include=FALSE}
-if(GLAD == TRUE | EDGI == TRUE){
-dat <- dat %>%
-  mutate(
-    over_half_a_year_time_diff_sign_up_coping_numeric =
-      as.numeric(
-        if_else(time_diff_sign_up_coping > 182.5, 1, 0
-                )
-      )
-  )
-
-dat <- dat %>%
-  mutate(
-    over_half_a_year_time_diff_sign_up_coping =
-      recode_factor(
-        over_half_a_year_time_diff_sign_up_coping_numeric,
-        "0" = "Sign up under half a year before COPING",
-        "1" = "Sign up over half a year before COPING"
-      )
-  )
-
-dat %>%
-  freq(over_half_a_year_time_diff_sign_up_coping, cumul = F)
-}
-```
-
-#Total score comparison between PHQ, PCL and GAD, prepandemic, retrospecive and baseline
-PHQ difference scores
-```{r phq difference scores}
-if(GLAD == TRUE | EDGI == TRUE){
-# Difference score for prepandemic and retrospective phq sum scores
-dat <- dat %>%
-  mutate(
-    phq.diff_score_prepan_retro =
-      as.numeric(
-        phq.sum_score_prepan - phq.sum_score_retro  # retrospective sum score MINUS prepandemic sum score 
-      )
-  )
-
-summary(dat$phq.diff_score_prepan_retro)
-
-# Difference score for prepandemic and baseline phq sum scores
-dat <- dat %>%
-  mutate(
-    phq.diff_score_prepan_base =
-      as.numeric(
-        phq.sum_score_base - phq.sum_score_prepan  # baseline sum score MINUS prepandemic sum score 
-      )
-  )
-
-summary(dat$phq.diff_score_prepan_base)
-}
-
-# Difference score for retrospective and baseline phq sum scores
-dat <- dat %>%
-  mutate(
-    phq.diff_score_base_retro =
-      as.numeric(
-        phq.sum_score_base - phq.sum_score_retro  # baseline sum score MINUS retrospective sum score 
-      )
-  )
-
-summary(dat$phq.diff_score_base_retro)
-
-```
-
-GAD difference scores
-```{r gad difference scores}
-if(GLAD == TRUE | EDGI == TRUE){
-# Difference score for prepandemic and retrospective gad sum scores
-dat <- dat %>%
-  mutate(
-    gad.diff_score_prepan_retro =
-      as.numeric(
-        gad.sum_score_prepan - gad.sum_score_retro  # retrospective sum score MINUS prepandemic sum score 
-      )
-  )
-
-summary(dat$gad.diff_score_prepan_retro)
-
-# Difference score for prepandemic and baseline gad sum scores
-dat <- dat %>%
-  mutate(
-    gad.diff_score_prepan_base =
-      as.numeric(
-        gad.sum_score_base - gad.sum_score_prepan  # baseline sum score MINUS prepandemic sum score 
-      )
-  )
-
-summary(dat$gad.diff_score_prepan_base)
-}
-
-# Difference score for retrospective and baseline gad sum scores
-dat <- dat %>%
-  mutate(
-    gad.diff_score_base_retro =
-      as.numeric(
-        gad.sum_score_base - gad.sum_score_retro  # baseline sum score MINUS retrospective sum score 
-      )
-  )
-
-summary(dat$gad.diff_score_base_retro)
-
-```
-
-PCL difference scores
-NOTE: Only computed baseline and prepandemic differences as the retro account here isn't actually retrospective, but whether the reported baseline scores are due to the pandemic. 
-```{r pcl difference scores}
-if(GLAD == TRUE | EDGI == TRUE){
-# Difference score for prepandemic and baseline pcl sum scores
-dat <- dat %>%
-  mutate(
-    pcl.diff_score_prepan_base =
-      as.numeric(
-        pcl.sum_score_base - pcl.sum_score_prepan  # baseline sum score MINUS prepandemic sum score 
-      )
-  )
-
-summary(dat$pcl.diff_score_prepan_base)
-}
-```
-
-```{r frequency of those who reported "due to pandemic" in retro PCL}
-summary(dat$pcl.sum_score_retro)
-
-freq(dat$pcl.stressful_experience_repeated_images_retro)
-freq(dat$pcl.stressful_situation_avoiding_activities_retro)
-freq(dat$pcl.feeling_irritable_or_having_angry_outbursts_retro)
-freq(dat$pcl.stressful_experience_upset_reminded_retro)
-freq(dat$pcl.cut_people_feeling_distant_retro)
-freq(dat$pcl.difficulty_concentrating_retro)
-```
-
-OCI-R difference scores
-```{r ocir difference scores}
-if(GLAD == TRUE | EDGI == TRUE){
-# Difference score for prepandemic and retrospective oci-r sum scores
-dat <- dat %>%
-  mutate(
-    ocir.diff_score_prepan_retro =
-      as.numeric(
-        ocir.sum_score_prepan - ocir.sum_score_retro  # retrospective sum score MINUS prepandemic sum score 
-      )
-  )
-
-summary(dat$ocir.diff_score_prepan_retro)
-
-# Difference score for prepandemic and baseline ocir sum scores
-dat <- dat %>%
-  mutate(
-    ocir.diff_score_prepan_base =
-      as.numeric(
-        ocir.sum_score_prepan - ocir.sum_score_base  # prepandemic sum score MINUS baseline sum score 
-      )
-  )
-
-summary(dat$ocir.diff_score_prepan_base)
-}
-# Difference score for retrospective and baseline ocir sum scores
-dat <- dat %>%
-  mutate(
-    ocir.diff_score_base_retro =
-      as.numeric(
-        ocir.sum_score_base - ocir.sum_score_retro  # baseline sum score MINUS retrospective sum score 
-      )
-  )
-
-summary(dat$ocir.diff_score_base_retro)
-
-```
-
-#Data level groups
-Identify which data (prepan, retro and baseline) each participant has.
-```{r glad/edgi data level groups PHQ}
-if(GLAD == TRUE | EDGI == TRUE){
-dat <- dat %>%
-  mutate(
-    data_group_phq_numeric =
-      case_when(
-        na_per_person_phq_base == 0 & na_per_person_phq_prepan == 0 & na_per_person_phq_retro == 0 ~ 5, #all complete baseline, prepan and retro
-        na_per_person_phq_base != 0 & na_per_person_phq_prepan != 0 & na_per_person_phq_retro == 0  ~ 4, #retro data only
-        na_per_person_phq_base == 0 & na_per_person_phq_prepan != 0 & na_per_person_phq_retro != 0  ~ 3, #baseline data only
-        na_per_person_phq_base == 0 & na_per_person_phq_prepan == 0 & na_per_person_phq_retro != 0  ~ 2, #prepan and baseline data only
-        na_per_person_phq_base == 0 & na_per_person_phq_prepan != 0 & na_per_person_phq_retro == 0 ~ 1,  #baseline and retro data only
-        na_per_person_phq_base != 0 & na_per_person_phq_prepan == 0 & na_per_person_phq_retro != 0  ~ 0  #prepan data only
-      )
-  )
-
-dat <- dat %>%
-  mutate(
-    data_group_phq = 
-      recode_factor(
-        data_group_phq_numeric,
-        "0" = "Only prepandemic data",
-        "1" = "Baseline and retrospective data",
-        "2" = "Prepandemic and baseline data",
-        "3" = "Baseline data only",
-        "4" = "Retrospective data only",
-        "5" = "All prepandemic, baseline and retrospective data"
-      )
-  )
-
-table(dat$data_group_phq)
-}
-```
-
-```{r nbr/ramp data level groups PHQ}
-if(NBR == TRUE | RAMP == TRUE){
-dat <- dat %>%
-  mutate(
-    data_group_phq_numeric =
-      case_when(
-#        na_per_person_phq_base == 0 & na_per_person_phq_prepan == 0 & na_per_person_phq_retro == 0 ~ 5, #all complete baseline, prepan and retro
-        na_per_person_phq_base != 0 & na_per_person_phq_retro == 0  ~ 4, #retro data only
-        na_per_person_phq_base == 0 & na_per_person_phq_retro != 0  ~ 3, #baseline data only
-#        na_per_person_phq_base == 0 & na_per_person_phq_prepan == 0 & na_per_person_phq_retro != 0  ~ 2, #prepan and baseline data only
-        na_per_person_phq_base == 0 & na_per_person_phq_retro == 0 ~ 1  #baseline and retro data only
-#        na_per_person_phq_base != 0 & na_per_person_phq_prepan == 0 & na_per_person_phq_retro != 0  ~ 0  #prepan data only
-      )
-  )
-
-dat <- dat %>%
-  mutate(
-    data_group_phq = 
-      recode_factor(
-        data_group_phq_numeric,
-        "0" = "Only prepandemic data",
-        "1" = "Baseline and retrospective data",
-        "2" = "Prepandemic and baseline data",
-        "3" = "Baseline data only",
-        "4" = "Retrospective data only",
-        "5" = "All prepandemic, baseline and retrospective data"
-      )
-  )
-
-table(dat$data_group_phq)
-}
-```
-
-GAD
-```{r glad/edgi data level groups GAD}
-if(GLAD == TRUE | EDGI == TRUE){
-dat <- dat %>%
-  mutate(
-    data_group_gad_numeric =
-      case_when(
-        na_per_person_gad_base == 0 & na_per_person_gad_prepan == 0 & na_per_person_gad_retro == 0 ~ 5, #all complete baseline, prepan and retro
-        na_per_person_gad_base != 0 & na_per_person_gad_prepan != 0 & na_per_person_gad_retro == 0  ~ 4, #retro data only
-        na_per_person_gad_base == 0 & na_per_person_gad_prepan != 0 & na_per_person_gad_retro != 0  ~ 3, #baseline data only
-        na_per_person_gad_base == 0 & na_per_person_gad_prepan == 0 & na_per_person_gad_retro != 0  ~ 2, #prepan and baseline data only
-        na_per_person_gad_base == 0 & na_per_person_gad_prepan != 0 & na_per_person_gad_retro == 0 ~ 1,  #baseline and retro data only
-        na_per_person_gad_base != 0 & na_per_person_gad_prepan == 0 & na_per_person_gad_retro != 0  ~ 0  #prepan data only
-      )
-  )
-
-dat <- dat %>%
-  mutate(
-    data_group_gad = 
-      recode_factor(
-        data_group_gad_numeric,
-        "0" = "Only prepandemic data",
-        "1" = "Baseline and retrospective data",
-        "2" = "Prepandemic and baseline data",
-        "3" = "Baseline data only",
-        "4" = "Retrospective data only",
-        "5" = "All prepandemic, baseline and retrospective data"
-      )
-  )
-
-table(dat$data_group_gad)
-}
-```
-
-```{r nbr/ramp data level groups GAD}
-if(NBR == TRUE | RAMP == TRUE){
-dat <- dat %>%
-  mutate(
-    data_group_gad_numeric =
-      case_when(
-#        na_per_person_gad_base == 0 & na_per_person_gad_prepan == 0 & na_per_person_gad_retro == 0 ~ 5, #all complete baseline, prepan and retro
-        na_per_person_gad_base != 0 & na_per_person_gad_retro == 0  ~ 4, #retro data only
-        na_per_person_gad_base == 0 & na_per_person_gad_retro != 0  ~ 3, #baseline data only
-#        na_per_person_gad_base == 0 & na_per_person_gad_prepan == 0 & na_per_person_gad_retro != 0  ~ 2, #prepan and baseline data only
-        na_per_person_gad_base == 0 & na_per_person_gad_retro == 0 ~ 1  #baseline and retro data only
-#        na_per_person_gad_base != 0 & na_per_person_gad_prepan == 0 & na_per_person_gad_retro != 0  ~ 0  #prepan data only
-      )
-  )
-
-dat <- dat %>%
-  mutate(
-    data_group_gad = 
-      recode_factor(
-        data_group_gad_numeric,
-        "0" = "Only prepandemic data",
-        "1" = "Baseline and retrospective data",
-        "2" = "Prepandemic and baseline data",
-        "3" = "Baseline data only",
-        "4" = "Retrospective data only",
-        "5" = "All prepandemic, baseline and retrospective data"
-      )
-  )
-
-table(dat$data_group_gad)
-}
-```
-
-PCL
-```{r glad/edgi data level groups PCL}
-if(GLAD == TRUE | EDGI == TRUE){
-dat <- dat %>%
-  mutate(
-    data_group_pcl_numeric =
-      case_when(
-        na_per_person_pcl_base == 0 & na_per_person_pcl_prepan == 0 & na_per_person_pcl_retro == 0 ~ 5, #all complete baseline, prepan and retro
-        na_per_person_pcl_base != 0 & na_per_person_pcl_prepan != 0 & na_per_person_pcl_retro == 0  ~ 4, #retro data only
-        na_per_person_pcl_base == 0 & na_per_person_pcl_prepan != 0 & na_per_person_pcl_retro != 0  ~ 3, #baseline data only
-        na_per_person_pcl_base == 0 & na_per_person_pcl_prepan == 0 & na_per_person_pcl_retro != 0  ~ 2, #prepan and baseline data only
-        na_per_person_pcl_base == 0 & na_per_person_pcl_prepan != 0 & na_per_person_pcl_retro == 0 ~ 1,  #baseline and retro data only
-        na_per_person_pcl_base != 0 & na_per_person_pcl_prepan == 0 & na_per_person_pcl_retro != 0  ~ 0  #prepan data only
-      )
-  )
-
-dat <- dat %>%
-  mutate(
-    data_group_pcl = 
-      recode_factor(
-        data_group_pcl_numeric,
-        "0" = "Only prepandemic data",
-        "1" = "Baseline and retrospective data",
-        "2" = "Prepandemic and baseline data",
-        "3" = "Baseline data only",
-        "4" = "Retrospective data only",
-        "5" = "All prepandemic, baseline and retrospective data"
-      )
-  )
-
-table(dat$data_group_pcl)
-}
-```
-
-```{r nbr/ramp data level groups PCL}
-if(NBR == TRUE | RAMP == TRUE){
-dat <- dat %>%
-  mutate(
-    data_group_pcl_numeric =
-      case_when(
-#        na_per_person_pcl_base == 0 & na_per_person_pcl_prepan == 0 & na_per_person_pcl_retro == 0 ~ 5, #all complete baseline, prepan and retro
-        na_per_person_pcl_base != 0 & na_per_person_pcl_retro == 0  ~ 4, #retro data only
-        na_per_person_pcl_base == 0 & na_per_person_pcl_retro != 0  ~ 3, #baseline data only
-#        na_per_person_pcl_base == 0 & na_per_person_pcl_prepan == 0 & na_per_person_pcl_retro != 0  ~ 2, #prepan and baseline data only
-        na_per_person_pcl_base == 0 & na_per_person_pcl_retro == 0 ~ 1  #baseline and retro data only
-#        na_per_person_pcl_base != 0 & na_per_person_pcl_prepan == 0 & na_per_person_pcl_retro != 0  ~ 0  #prepan data only
-      )
-  )
-
-dat <- dat %>%
-  mutate(
-    data_group_pcl = 
-      recode_factor(
-        data_group_pcl_numeric,
-        "0" = "Only prepandemic data",
-        "1" = "Baseline and retrospective data",
-        "2" = "Prepandemic and baseline data",
-        "3" = "Baseline data only",
-        "4" = "Retrospective data only",
-        "5" = "All prepandemic, baseline and retrospective data"
-      )
-  )
-
-table(dat$data_group_pcl)
-}
-```
-
-#Read in respiratory data
-
-## GLAD respiratory
-```{r glad coping respiratory cols}
-if(GLAD == TRUE){
-coping.glad.respiratory.raw <- readRDS(file = paste0(data.raw_path, "/glad/respiratory_coping_glad.rds"))
-dim(coping.glad.respiratory.raw)
-colnames(coping.glad.respiratory.raw)
-}
-```
-
-Select respiratory variables
-```{r coping glad respiratory cleaning}
-if(GLAD == TRUE){
-coping.glad.respiratory.raw.id <- coping.glad.respiratory.raw %>%
-  drop_na(externalDataReference) %>% # Drop NAs
-  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
-  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
-  mutate(ID = as.numeric(ID)) %>%
-  select(
-    Sample, # Sample
-    ID, # ID
-    respiratory.breath_diarrhoea_fatigue_fever,
-    respiratory.worst_ill_feel,
-    respiratory.persistent_cough,
-    respiratory.skipping_meals_because_you_felt_unwell,
-    respiratory.was_your_sense_of_smell_impaired,
-    respiratory.was_your_sense_of_taste_impaired,
-    respiratory.feeling_tiredfatigued,
-    respiratory.throat_swab_coronavirus_nose,
-    respiratory.throat_swab_test_nose,
-    respiratory.coronavirus_antibody_test,
-    respiratory.results_antibody_test
-  ) %>%
-  add_numeric(., exclude = exclude_cols) %>%
-  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
-  mutate_if(is.numeric, ~na_if(., -99)) %>%
-  mutate_if(is.numeric, ~na_if(., -77)) %>%
-  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
-  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
-
-# Inspect dimensions
-dim(coping.glad.respiratory.raw.id)
-# Inspect colnames
-colnames(coping.glad.respiratory.raw.id)
-#Differences
-dim(coping.glad.respiratory.raw)[1]-dim(coping.glad.respiratory.raw.id)[1]
-}
-```
-
-```{r coping glad respiratory copy}
-if(GLAD == TRUE){
-respiratory.raw.id <- coping.glad.respiratory.raw.id
-}
-```
-
-## EDGI respiratory
-```{r edgi coping respiratory cols}
-if(EDGI == TRUE){
-coping.edgi.respiratory.raw <- readRDS(file = paste0(data.raw_path, "/edgi/respiratory_coping_edgi.rds"))
-dim(coping.edgi.respiratory.raw)
-colnames(coping.edgi.respiratory.raw)
-}
-```
-
-Select respiratory variables
-```{r coping edgi respiratory cleaning}
-if(EDGI == TRUE){
-coping.edgi.respiratory.raw.id <- coping.edgi.respiratory.raw %>%
-  drop_na(externalDataReference) %>% # Drop NAs
-  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
-  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
-  mutate(ID = as.numeric(ID)) %>%
-  select(
-    Sample, # Sample
-    ID, # ID
-    respiratory.breath_diarrhoea_fatigue_fever = respiratory.unusual_shortness_breath_diarrhoea,
-    respiratory.worst_ill_feel,
-    respiratory.persistent_cough,
-    respiratory.skipping_meals_because_you_felt_unwell,
-    respiratory.was_your_sense_of_smell_impaired,
-    respiratory.was_your_sense_of_taste_impaired,
-    respiratory.feeling_tiredfatigued,
-    respiratory.throat_swab_coronavirus_nose,
-    respiratory.throat_swab_test_nose,
-    respiratory.coronavirus_antibody_test,
-    respiratory.results_antibody_test
-  ) %>%
-  add_numeric(., exclude = exclude_cols) %>%
-  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
-  mutate_if(is.numeric, ~na_if(., -99)) %>%
-  mutate_if(is.numeric, ~na_if(., -77)) %>%
-  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
-  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
-
-# Inspect dimensions
-dim(coping.edgi.respiratory.raw.id)
-# Inspect colnames
-colnames(coping.edgi.respiratory.raw.id)
-#Differences
-dim(coping.edgi.respiratory.raw)[1]-dim(coping.edgi.respiratory.raw.id)[1]
-}
-```
-
-```{r coping edgi respiratory copy}
-if(EDGI == TRUE){
-respiratory.raw.id <- coping.edgi.respiratory.raw.id
-}
-```
-
-## NBR respiratory
-```{r nbr coping respiratory cols}
-if(NBR == TRUE){
-coping.nbr.respiratory.raw <- readRDS(file = paste0(data.raw_path, "/nbr/respiratory_coping_nbr.rds"))
-dim(coping.nbr.respiratory.raw)
-colnames(coping.nbr.respiratory.raw)
-}
-```
-
-Select respiratory variables
-```{r coping nbr respiratory cleaning}
-if(NBR == TRUE){
-coping.nbr.respiratory.raw.id <- coping.nbr.respiratory.raw %>%
-  drop_na(subjectid) %>% # Drop NAs
-  distinct(subjectid, .keep_all = TRUE) %>% # Remove duplicates based on ID
-  separate(subjectid, into = c("Sample", "ID.intm"), sep = 6) %>% # Split ID in Sample and Number
-  separate(ID.intm, into = "ID", sep = 7) %>%
-  mutate(ID = as.numeric(ID)) %>%
-  select(
-    Sample, # Sample
-    ID, # ID
-    respiratory.breath_diarrhoea_fatigue_fever = respiratory.unusual_shortness_breath_diarrhoea,
-    respiratory.worst_ill_feel,
-    respiratory.persistent_cough,
-    respiratory.skipping_meals_because_you_felt_unwell,
-    respiratory.was_your_sense_of_smell_impaired,
-    respiratory.was_your_sense_of_taste_impaired,
-    respiratory.feeling_tiredfatigued,
-    respiratory.throat_swab_coronavirus_nose,
-    respiratory.throat_swab_test_nose,
-    respiratory.coronavirus_antibody_test,
-    respiratory.results_antibody_test
-  ) %>%
-  add_numeric(., exclude = exclude_cols) %>%
-  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
-  mutate_if(is.numeric, ~na_if(., -99)) %>%
-  mutate_if(is.numeric, ~na_if(., -77)) %>%
-  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
-  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
-
-# Inspect dimensions
-dim(coping.nbr.respiratory.raw.id)
-# Inspect colnames
-colnames(coping.nbr.respiratory.raw.id)
-#Differences
-dim(coping.nbr.respiratory.raw)[1]-dim(coping.nbr.respiratory.raw.id)[1]
-}
-```
-
-```{r coping nbr respiratory copy}
-if(NBR == TRUE){
-respiratory.raw.id <- coping.nbr.respiratory.raw.id
-}
-```
-
-## RAMP respiratory
-```{r ramp coping respiratory cols}
-if(RAMP == TRUE){
-ramp.respiratory.raw <- readRDS(file = paste0(data.raw_path, "/ramp/respiratory_ramp.rds"))
-dim(ramp.respiratory.raw)
-colnames(ramp.respiratory.raw)
-}
-```
-
-Select respiratory variables
-```{r coping ramp respiratory cleaning}
-if(RAMP == TRUE){
-ramp.respiratory.raw.id <- ramp.respiratory.raw %>%
-  drop_na(`Login ID`) %>% # Drop NAs
-  distinct(`Login ID`, .keep_all = TRUE) %>% # Remove duplicates based on ID
-  separate(`Login ID`, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
-  mutate(ID = as.numeric(ID)) %>%
-  select(
-    Sample, # Sample
-    ID, # ID
-    respiratory.breath_diarrhoea_fatigue_fever = respiratory.experienced_symptoms_unusual_shortness,
-    respiratory.worst_ill_feel,
-    respiratory.persistent_cough,
-    respiratory.skipping_meals_because_you_felt_unwell,
-    respiratory.was_your_sense_of_smell_impaired = respiratory.smell_impaired_sense_weeks,
-    respiratory.was_your_sense_of_taste_impaired = respiratory.taste_impaired_sense_weeks,
-    respiratory.feeling_tiredfatigued,
-    respiratory.throat_swab_coronavirus_nose,
-    respiratory.throat_swab_test_nose,
-    respiratory.coronavirus_week_antibody_test,
-    respiratory.results_antibody_test
-  ) %>%
-  add_numeric(., exclude = exclude_cols) %>%
-  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
-  mutate_if(is.numeric, ~na_if(., -99)) %>%
-  mutate_if(is.numeric, ~na_if(., -77)) %>%
-  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
-  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
-  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
-  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
-
-# Inspect dimensions
-dim(ramp.respiratory.raw.id)
-# Inspect colnames
-colnames(ramp.respiratory.raw.id)
-#Differences
-dim(ramp.respiratory.raw)[1]-dim(ramp.respiratory.raw.id)[1]
-}
-```
-
-```{r ramp respiratory copy}
-if(RAMP == TRUE){
-respiratory.raw.id <- ramp.respiratory.raw.id
-}
-```
-
-#Distribution of likert scale COVID-19 symptoms in COPING
-```{r distribution of COVID symptoms}
-#persistent cough
-respiratory.raw.id %>%
-  ggplot(
-    mapping = aes(
-      y = respiratory.persistent_cough_numeric 
-    )
-  ) +
-  geom_bar() +
-  labs(
-    title = "Persistant cough"
-  )
-
-#severe fatigue
-respiratory.raw.id %>%
-  ggplot(
-    mapping = aes(
-        y = respiratory.feeling_tiredfatigued_numeric 
-    )
-  ) +
-  geom_bar() +
-  labs(
-    title = "Severe fatigue"
-  )
-
-#skipped meals
-respiratory.raw.id %>%
-  ggplot(
-    mapping = aes(
-        y = respiratory.skipping_meals_because_you_felt_unwell_numeric
-    )
-  ) +
-  geom_bar() +
-  labs(
-    title = "Skipped meals"
-  )
-
-```
-
-#Choosing cut-offs for the likert scale symptoms of "no symptoms", "mild symptoms", "moderate symptoms" and "severe symptoms" for the fatigue, persistent cough and skipped meals variables. 
-Coding:
-0 = No symptoms
-1 = Mild symptoms
-2 = Moderate symptoms
-3 = Severe symptoms
-
-Results:
-Persistent cough: "Mild symptoms" as cut off
-Fatigue: "Severe symptoms" as cut off
-Skipped meals: "Moderate symptoms" as cut off
-```{r proportion of people who report COVID symptoms in Menni et al}
-#persistent cough
-percentage_pcough <- ((0.5673*6452) + (0.4556*9186) + (0.3017*2434931))/(6452+9186+2434931)
-percentage_pcough    # 0.3029762% of Menni et al(2020) have fatigue
-quantile(x = respiratory.raw.id$respiratory.persistent_cough_numeric, 
-         na.rm = TRUE, 
-         probs = 1-percentage_pcough) # this gives 0.3029762% of the sample reporting fatigue when using the "mild symptoms" persistent cough response
-
-#fatigue
-percentage_fatigue <- ((0.298*6452) + (0.1556*9186) + (0.0871*2434931))/(6452+9186+2434931) 
-percentage_fatigue   # 0.08791204% of Menni et al(2020) have fatigue
-quantile(x = respiratory.raw.id$respiratory.feeling_tiredfatigued_numeric, 
-         na.rm = TRUE, 
-         probs = 1-percentage_fatigue) #this gives 8% of the sample reporting fatigue when using the "severe symptoms" fatigue response
-
-#skipped meals 
-percentage_skipped_meals <- ((0.4203*6452) + (0.2493*9186) + (0.1912*2434931))/(6452+9186+2434931) 
-percentage_skipped_meals    # 0.192021% of Menni et al(2020) have fatigue
-quantile(x = respiratory.raw.id$respiratory.skipping_meals_because_you_felt_unwell_numeric, 
-         na.rm = TRUE, 
-         probs = 1-percentage_skipped_meals) # this gives 0.192021% of the sample reporting fatigue when using the "moderate symptoms" persistent cough response
-```
-
-Creating binary groups for COVID symptoms
-```{r creating binary groups for COVID symptoms}
-#loss or smell or taste
-respiratory.raw.id <- respiratory.raw.id %>%
-  mutate(
-    respiratory.anosmia_binary =
-      if_else(
-        respiratory.was_your_sense_of_smell_impaired_numeric == 1 | respiratory.was_your_sense_of_taste_impaired_numeric == 1, 
-        1,
-        0
-      )
-  )
-
-#persistent cough
-respiratory.raw.id <- respiratory.raw.id %>%
-  mutate(
-    respiratory.pcough_binary =
-      if_else(
-        respiratory.persistent_cough_numeric >= 1, #those who score 1 or above (mild or above)
-        1,
-        0
-      )
-  )
-
-#fatigue
-respiratory.raw.id <- respiratory.raw.id %>%
-  mutate(
-    respiratory.fatigue_binary =
-      if_else(
-        respiratory.feeling_tiredfatigued_numeric >= 3, #those who score 3 (severe symptoms)
-        1,
-        0
-      )
-  )
-
-#skipped meals
-respiratory.raw.id <- respiratory.raw.id %>%
-  mutate(
-    respiratory.skipped_meals_binary =
-      if_else(
-        respiratory.skipping_meals_because_you_felt_unwell_numeric >= 2,
-        1,
-        0
-      )
-  )
-```
-
-Frequencies of binary COVID symptoms
-```{r frequencies of COVID binary symptoms}
-freq(respiratory.raw.id$respiratory.anosmia_binary)
-freq(respiratory.raw.id$respiratory.pcough_binary)
-freq(respiratory.raw.id$respiratory.fatigue_binary)
-freq(respiratory.raw.id$respiratory.skipped_meals_binary)
-```
-
-Rename respiratory dataset joined to main dataset
-
-```{r clean respiratory dataset}
-respiratory <- respiratory.raw.id
-
-dat.coping <- left_join(
-  x = dat,
-  y = respiratory,
-  by = c("Sample", "ID")
-)
-```
-
-# Probable COVID-19 case identification
-
-Algorithm from Menni et al. to identify probable COVID-19
-Variables required:
-- Sex: 	0 Female, 1 Male
-- Other binary variables: 0 No, 1 Yes       
-- "respiratory.anosmia_binary": loss of smell or taste  
-- "respiratory.pcough_binary":	Persistent cough
-- "respiratory.fatigue_binary": Severe fatigue
-- "respiratory.skipped_meals_binary": Skipped meals
-
-The COVID prediction model has coded the sexes opposite to our data set
-```{r create numeric sex variable with male=1}
-if(GLAD == TRUE | NBR == TRUE | EDGI == TRUE){
-dat.coping <- dat.coping %>%
-  mutate(
-    Sex_respiratory =
-      if_else(
-        Sex == "Male",
-        true = 1,
-        false = 0,
-        missing = NA_real_
-      )
-  )
-}
-```
-
-Sex is no available in the RAMP dataset, therefore a proxy sex variable is created whereby Gender = Male and Transgender = No. 
-```{r create numeric sex variable with male=1 for ramp}
-if(RAMP == TRUE){
-dat.coping <- dat.coping %>%
-  mutate(
-    Sex_respiratory =
-      if_else(
-        Gender == "Male" &
-        Transgender_uncleaned == "No",
-        true = 1,
-        false = 0,
-        missing = NA_real_
-      )
-  )
-}
-```
-
-Age is not available in RAMP, only categorical age. We will assign each individual the middle value of each age category. 
-```{r create age - proxy variable for ramp}
-if(RAMP == TRUE){
-dat.coping <- dat.coping %>%
-  mutate(
-    Age =
-      case_when(
-        age_category_full == "16-18" ~ 17,
-        age_category_full == "19-25" ~ 22,
-        age_category_full == "26-35" ~ 30.5,
-        age_category_full == "36-45" ~ 40.5,
-        age_category_full == "46-55" ~ 50.5,
-        age_category_full == "56-65" ~ 60.5,
-        age_category_full == "66-70" ~ 68,
-        age_category_full == "71-75" ~ 73,
-        age_category_full == "76-80" ~ 78,
-        age_category_full == "81-85" ~ 83,
-        age_category_full == "86-90" ~ 88,
-        age_category_full == "91-100" ~ 93,
-      age_category_full == "100+" ~ 100
-      )
-  )
-}
-```
-
-```{r how many people experinced all symptoms}
-dat.coping <- dat.coping %>%
-  mutate(
-    covid_symptoms =
-      if_else(
-          !is.na(respiratory.anosmia_binary) &
-          !is.na(respiratory.pcough_binary) &
-          !is.na(respiratory.fatigue_binary) &
-          !is.na(respiratory.skipped_meals_binary),
-        1,
-        0
-       )
-  )
-
-dat.coping %>%
-  freq(covid_symptoms, cumul = F)
-```
-
-#COVID prediction model
-```{r COVID prediction model}
-# linear model of covid symptoms
-dat.coping <- dat.coping %>%
-		  mutate(
-		    covid_probability = 
-		      (-1.32) - 
-		      (0.01*Age) + 
-		      (0.44*Sex_respiratory) + 
-		      (1.75*respiratory.anosmia_binary) + 
-		      (0.31*respiratory.pcough_binary) +  
-		      (0.49*respiratory.fatigue_binary) +  
-		      (0.39*respiratory.skipped_meals_binary) 
-		         )
-
-# Calcualte the odds ratios 
-dat.coping <- dat.coping %>%
-  mutate(
-    covid_odds_ratio = 
-      (exp(covid_probability) / (1 + exp(covid_probability)))
-  )
-
-# generate binary cutt off variable for risk of COVID 
-dat.coping <- dat.coping %>%
-		  mutate(
-		    covid_odds_ratio_50_numeric = 
-		      case_when(
-		        covid_odds_ratio >= 0 & covid_odds_ratio < 0.5 ~ "0", #cut off at 0.5 
-		        covid_odds_ratio >= 0.5 & covid_odds_ratio <= 1 ~ "1"
-		      )
-		  )
-
-#create factor with labels
-dat.coping <- dat.coping %>%
-  mutate(
-    covid_odds_ratio_50 =
-      recode_factor(
-        covid_odds_ratio_50_numeric,
-        "0" = "No COVID",
-        "1" = "Probable COVID"
-      )
-  )
-
-#frequency table for covid variables 
-covid_variables <- c("covid_odds_ratio",
-                      "covid_probability"
-                    )
-
-descr(x = dat.coping[,covid_variables],
-      round.digits = 2,
-      transpose = TRUE)
-
-## looking at cases over 0.5
-freq(dat.coping$covid_odds_ratio_50, 
-     cumul = FALSE)
-
-```
-
-Probable COVID case including the routing question
-```{r recoding probable covid to account for screening question}
-dat.coping <- dat.coping %>%
-  mutate(
-    covid_probable_case_incl_screening_numeric =
-      case_when(
-        respiratory.breath_diarrhoea_fatigue_fever_numeric == 0 ~ 0,
-        covid_odds_ratio_50_numeric == 0 ~ 0,
-        covid_odds_ratio_50_numeric == 1 ~ 1
-      )
-  )
-
-#create factor with labels
-dat.coping <- dat.coping %>%
-  mutate(
-    covid_probable_case_incl_screening =
-      recode_factor(
-        covid_probable_case_incl_screening_numeric,
-        "0" = "No COVID",
-        "1" = "Probable COVID"
-      )
-  )
-
-dat.coping %>%
-  freq(covid_probable_case_incl_screening, 
-     cumul = FALSE) 
-```
-
-```{r dat.coping summary}
-summarytools::dfSummary(
-  dat.coping,
-  graph.col = F,
-  valid.col = F,
-  labels.col = F)
-```
-
-# Export data
-```{r export data}
-if(GLAD == TRUE){
-saveRDS(object = dat.coping, file = paste0(data_path, "/glad.rds"))
-}
-
-if(EDGI == TRUE){
-saveRDS(object = dat.coping, file = paste0(data_path, "/edgi.rds"))
-}
-
-if(NBR == TRUE){
-saveRDS(object = dat.coping, file = paste0(data_path, "/nbr.rds"))
-}
-
-if(RAMP == TRUE){
-saveRDS(object = dat.coping, file = paste0(data_path, "/ramp.rds"))
-}
-
-```

### 2020-08-18 PANCHANGE_data_preprocessing2020-07-15.Rmd
added pcl to ramp

--- 2020-08-17 PANCHANGE_data_preprocessing2020-07-15.Rmd
@@
 ```{r coping ramp pcl cols}
-# if(RAMP == TRUE) {
-# coping.ramp.pcl.raw <- readRDS(file = paste0(data.raw_path,"/ramp/pcl_ramp.rds"))
-# dim(coping.ramp.pcl.raw)
-# colnames(coping.ramp.pcl.raw)
-# }
+if(RAMP == TRUE) {
+coping.ramp.pcl.raw <- readRDS(file = paste0(data.raw_path,"/ramp/pcl_ramp.rds"))
+dim(coping.ramp.pcl.raw)
+colnames(coping.ramp.pcl.raw)
+}
 ```
@@
 ```{r coping ramp pcl summary labels}
-# if(RAMP == TRUE) {
-# summarytools::dfSummary(
-#   coping.ramp.pcl.raw,
-#   graph.col = F,
-#   valid.col = F,
-#   labels.col = F
-# )
-# }
+if(RAMP == TRUE) {
+summarytools::dfSummary(
+  coping.ramp.pcl.raw,
+  graph.col = F,
+  valid.col = F,
+  labels.col = T
+)
+}
 ```
@@
 ```{r coping ramp pcl cleaning}
-# if(RAMP == TRUE) {
-# coping.ramp.pcl.raw.id <- coping.ramp.pcl.raw %>%
-#   drop_na(externalDataReference) %>% # Drop NAs
-#   distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
-#   separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
-#   mutate(ID = as.numeric(ID)) %>%
-#   select(
-#     Sample, # Sample
-#     ID, # ID
-#     pcl.stressful_experience_repeated_images_base = pcl.stressful_experience_repeated_images,
-#     pcl.stressful_experience_upset_reminded_base = pcl.stressful_experience_upset_reminded, # differ to RAMP prepan
-#     pcl.stressful_situation_avoiding_activities_base = pcl.avoiding_activities_stressful_experience, # differ to RAMP prepan
-#     pcl.cut_people_feeling_distant_base = pcl.cut_people_feeling_distant,
-#     pcl.feeling_irritable_or_having_angry_outbursts_base = pcl.feeling_irritable_or_having_angry_outbursts,
-#     pcl.difficulty_concentrating_base = pcl.difficulty_concentrating,
-#     pcl.stressful_experience_repeated_images_retro = pcl.stressful_experience_repeated_images.1,
-#     pcl.stressful_experience_upset_reminded_retro = pcl.stressful_experience_upset_reminded.1,
-#     pcl.stressful_situation_avoiding_activities_retro = pcl.avoiding_activities_stressful_experience.1,
-#     pcl.cut_people_feeling_distant_retro = pcl.cut_people_feeling_distant.1,
-#     pcl.feeling_irritable_or_having_angry_outbursts_retro = pcl.feeling_irritable_or_having_angry_outbursts.1,
-#     pcl.difficulty_concentrating_retro = pcl.difficulty_concentrating.1
-#   ) %>%
-#   add_numeric(., exclude = exclude_cols) %>%
-#   mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
-#   mutate_if(is.numeric, ~na_if(., -99)) %>%
-#   mutate_if(is.numeric, ~na_if(., -77)) %>%
-#   mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
-#   mutate_if(is.factor, ~na_if(., "Don't know")) %>%
-#   mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
-#   mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
-#   mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
-#   mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
-#   mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
-#   mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
-# 
-# # Inspect dimensions
-# dim(coping.ramp.pcl.raw.id)
-# # Inspect colnames
-# colnames(coping.ramp.pcl.raw.id)
-# #Differences
-# dim(coping.ramp.pcl.raw)[1]-dim(coping.ramp.pcl.raw.id)[1]
-# }
+if(RAMP == TRUE) {
+coping.ramp.pcl.raw.id <- coping.ramp.pcl.raw %>%
+  drop_na(`Login ID`) %>% # Drop NAs
+  distinct(`Login ID`, .keep_all = TRUE) %>% # Remove duplicates based on ID
+  separate(`Login ID`, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
+  mutate(ID = as.numeric(ID)) %>%
+  select(
+    Sample, # Sample
+    ID, # ID
+    pcl.stressful_experience_repeated_images_base = pcl.stressful_experience_repeated_images,
+    pcl.stressful_experience_upset_reminded_base = pcl.stressful_experience_reminded_upset, # differ to RAMP prepan
+    pcl.stressful_situation_avoiding_activities_base = pcl.stressful_experience_avoiding_activities, # differ to RAMP prepan
+    pcl.cut_people_feeling_distant_base = pcl.feeling_distant_cut_people, # differ
+    pcl.feeling_irritable_or_having_angry_outbursts_base = pcl.feeling_irritable_or_having_angry_outbursts,
+    pcl.difficulty_concentrating_base = pcl.difficulty_concentrating,
+    pcl.stressful_experience_repeated_images_retro = pcl.stressful_experience_repeated_images.1,
+    pcl.stressful_experience_upset_reminded_retro = pcl.stressful_experience_reminded_upset.1, # differ
+    pcl.stressful_situation_avoiding_activities_retro = pcl.stressful_experience_avoiding_activities.1, # differ
+    pcl.cut_people_feeling_distant_retro = pcl.feeling_distant_cut_people.1, # differ
+    pcl.feeling_irritable_or_having_angry_outbursts_retro = pcl.feeling_irritable_or_having_angry_outbursts.1,
+    pcl.difficulty_concentrating_retro = pcl.difficulty_concentrating.1
+  ) %>%
+  add_numeric(., exclude = exclude_cols) %>%
+  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
+  mutate_if(is.numeric, ~na_if(., -99)) %>%
+  mutate_if(is.numeric, ~na_if(., -77)) %>%
+  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
+  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
+
+# Inspect dimensions
+dim(coping.ramp.pcl.raw.id)
+# Inspect colnames
+colnames(coping.ramp.pcl.raw.id)
+#Differences
+dim(coping.ramp.pcl.raw)[1]-dim(coping.ramp.pcl.raw.id)[1]
+}
 ```
@@
   coping.gad.raw.id,
-#  coping.pcl.raw.id, #WAITING FOR PCL DATA FOR RAMP
+  coping.pcl.raw.id,
   coping.phq.raw.id,

### 2020-08-18 PANCHANGE_data_preprocessing2020-07-15.Rmd
edits to age respiratory variable

--- 2020-08-18 PANCHANGE_data_preprocessing2020-07-15.Rmd
@@
   mutate(
-    Age =
+    Age_respiratory =
       case_when(
@@
 }
+
+if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE){
+dat.coping <- dat.coping %>%
+  mutate(
+    Age_respiratory = Age
+  )
+}
 ```
@@
 ```{r COVID prediction model}
-# linear model of covid symptoms
+# linear model of COVID symptoms
 dat.coping <- dat.coping %>%
@@
 		      (-1.32) - 
-		      (0.01*Age) + 
+		      (0.01*Age_respiratory) + 
 		      (0.44*Sex_respiratory) + 
@@
 
-# Calcualte the odds ratios 
+# Calculate the odds ratios 
 dat.coping <- dat.coping %>%
@@
 
-# generate binary cutt off variable for risk of COVID 
+# generate binary cut off variable for risk of COVID 
 dat.coping <- dat.coping %>%

### 2020-08-18 PANCHANGE_analysis.Rmd
changes

@@
 
-```{r dat.coping summary}
+```{r dat.coping summary, eval=FALSE, include=FALSE}
 summarytools::dfSummary(
@@
 ```
+
+Data availability
+```{r gad availability}
+dat %>%
+  freq(
+    data_group_gad,
+    cumul = F)
+```
+
+```{r phq availability}
+dat %>%
+  freq(
+    data_group_phq,
+    cumul = F)
+```
+
+```{r pcl availability}
+dat %>%
+  freq(
+    data_group_pcl,
+    cumul = F)
+```

### 2020-08-19 PANCHANGE_analysis.Rmd
convert to long format

@@
 ```
+
+```{r vector with psychiatric disorders}
+disorder_columns <- c(
+    "depressive_disorders_numeric",
+    "anxiety_disorders_numeric",
+    "eating_disorders_numeric",
+    "obsessive_compulsive_disorders_numeric",
+    "psychotic_disorders_numeric",
+    "mhd.mania_hypomania_bipolar_or_manicdepression_numeric",
+    "mhd.posttraumatic_stress_disorder_ptsd_numeric",
+    "mhd.autism_aspergers_or_autistic_spectrum_disorder_numeric",
+    "mhd.attention_deficit_hyperactivity_disorder_numeric",
+    "mhd.personality_disorder_numeric"
+)
+```
+
+```{r gather to long format}
+dat.long <- dat %>%
+  gather(
+    key = "Disorder",
+    value = "Diagnosis",
+    all_of(disorder_columns)) %>%
+  select(
+    ID,
+    Sample,
+    Disorder,
+    Diagnosis
+  )
+
+head(dat.long)
+```
+
+Define disorder columns in vector
+```{r}
+dat.long %>%
+  group_by(Disorder) %>%
+  count()
+```
+
+## Disorders - Frequencies *use this as example to convert chunk above*
+```{r Disorders - Frequencies}
+#0 = No to disorder; 1 = Yes to disorder
+PMAD_na_drop_Dx %>%
+  select(ID, #need to add columns for which you want summaries for - ASK GB & KY what they want in descriptives table
+         dem.sex,
+         starts_with("mhd.") & ends_with("numeric")) %>%
+  gather(
+    key = "Disorder",
+    value = "Diagnosis",
+    mhd.MDD_numeric:mhd.ADHD_numeric #all the columns that we want to be gathered
+  ) %>%
+  group_by(Disorder) %>%
+  count(Diagnosis) #count for diagnoses
+```
+
+Compare the GLAD/EDGI and COPING cohorts as a whole
++++CH: Diagnosis, ethnicity, gender, 
++++MD: May not be possible for NBR; potentially send them code to run it for us
+
+Ethnicity
+```{r}
+
+```
+
+Gender
+```{r}
+
+```
+
+Education
+```{r}
+
+```
+
+Key worker status
+```{r}
+
+```
+
+COVID test positive
+```{r}
+
+```
+
+COVID probable diagnosis
+```{r}
+
+```
+
+Calculate mean change per disorder group 
+Disorders (9) 
+Sex 
+Age (13; RAMP; potentially collapse above 65 depending on group sizes) 
+Ethnicity groups (5; White European, Black (British), Asian, Arab, Mixed)
+
+Rank the disorders by the size of the change
+
+# Regression
+Regress covariates out of the change? Which?
+
+Model 0: Disorders
+```{r}
+
+```
+
+Model 1: Model 0 + Sex + Age + Ethnicity + Time registration and baseline
+```{r}
+
+```
+
+Re-calculate change
+```{r}
+
+```
+
+Re-rank the change again
+```{r}
+
+```
+
+PCL:  
+Calculate the total GLAD, COPING, RAMP baseline 
+```{r}
+
+```
+
+For each item 
+present percentages of how say that this is due to the pandemic 
+```{r}
+
+```
+
+Calculate a variable PCL pandemic score 
+```{r}
+
+```
+
+If one item is highly endorsed due to pandemic -> exclude in sensitivity analysis 
+```{r}
+
+```
+
+Descriptives for reporting: "How different are these feelings to how you felt before the pandemic?’ on a 5-point scale (much worse, a little worse, no different, a little better, much better)."
++++KLP: Discuss during the meeting if we use 3 or 5 categories
+```{r}
+
+```
+
+Replicate chunk above for retrospective reports. This will only be for people who say that have reported that there is a change in their scores. 
+*Discuss if we should include people who reported "no change" as repition of their current GAD, PHQ, PCL report*
+```{r}
+
+```
+
+```{r}
+
+```

### 2020-08-19 PANCHANGE_data_preprocessing2020-07-15.Rmd
convert to long format

@@
 if(EDGI == TRUE){
-exclude_cols_employment <- c("ID",
-                  "Sample")
+exclude_cols_employment_edgi <- c("ID",
+                  "Sample",
+                  "COPING_ID")
 
@@
   separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
+  separate("Login ID", into = c("COPING_Sample", "COPING_ID"), sep = 6) %>% # Split ID in Sample and Number
+  mutate(COPING_ID = as.numeric(COPING_ID)) %>%
   mutate(
@@
          ID, # ID
+         COPING_ID,
          employment.phd, # level of education - univeristy
@@
          ) %>%
-  add_numeric(., exclude = exclude_cols_employment) %>%
+  add_numeric(., exclude = exclude_cols_employment_edgi) %>%
   mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
@@
 
-## RAMP - NOT YET HAVE THE RAMP PCL DATA READY
+## RAMP
 ```{r coping ramp pcl cols}
@@
 if(GLAD == TRUE) {
+
 coping.glad.ocir.raw.id <- coping.glad.ocir.raw %>%
@@
 ```{r coping edgi ocir cleaning}
+exclude_cols_coping_edgi_ocir <- c("COPING_Sample", "COPING_ID")
+
 if(EDGI == TRUE) {
@@
   distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
-  separate(externalDataReference, into = c("Sample", "ID"), sep = 6) %>% # Split ID in Sample and Number
-  mutate(ID = as.numeric(ID)) %>%
+  separate(externalDataReference, into = c("COPING_Sample", "COPING_ID"), sep = 6) %>% # Split ID in Sample and Number
+  mutate(COPING_ID = as.numeric(COPING_ID)) %>%
   select(
-    Sample, # Sample
-    ID, # ID
+#    Sample, # Sample
+    COPING_ID, # ID
     ocir.felt_pandemic_feelings, # Comparison to before the pandemic
@@
   ) %>%
-  add_numeric(., exclude = exclude_cols) %>%
+  add_column(Sample = "EDGI") %>%
+  add_numeric(., exclude = exclude_cols_coping_edgi_ocir) %>%
   mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
@@
 
-glad/edgi data frame list
+```{r edgi employment and coping ocir}
+if(EDGI == TRUE){
+edgi.employment.coping.ocir <-  full_join(
+    x = employment.raw.id,
+    y = coping.ocir.raw.id,
+    by = 
+      c("Sample",
+        "COPING_ID")
+)
+}
+```
+
+edgi data frame list
+```{r edgi data frame list}
+if(EDGI == TRUE) {
+dfs.list <- list(
+  dem.raw.id,
+  edgi.employment.coping.ocir,
+  mhd.raw.categories,
+  prepan.gad.raw.id,
+  prepan.pcl.raw.id,
+  prepan.phq.raw.id,
+  prepan.ocir.raw.id,
+  coping.gad.raw.id,
+  coping.pcl.raw.id,
+  coping.phq.raw.id
+#  coping.ocir.raw.id
+)
+}
+```
+
+glad data frame list
 ```{r glad/edgi data frame list}
-if(GLAD == TRUE | EDGI == TRUE) {
+if(GLAD == TRUE) {
 dfs.list <- list(
@@
 percentage_pcough    # 0.3029762% of Menni et al(2020) have fatigue
-quantile(x = respiratory.raw.id$respiratory.persistent_cough_numeric, 
+pcough_cutoff <- quantile(x = respiratory.raw.id$respiratory.persistent_cough_numeric, 
          na.rm = TRUE, 
          probs = 1-percentage_pcough) # this gives 0.3029762% of the sample reporting fatigue when using the "mild symptoms" persistent cough response
+pcough_cutoff
 
@@
 percentage_fatigue   # 0.08791204% of Menni et al(2020) have fatigue
-quantile(x = respiratory.raw.id$respiratory.feeling_tiredfatigued_numeric, 
+fatigue_cutoff <- quantile(x = respiratory.raw.id$respiratory.feeling_tiredfatigued_numeric, 
          na.rm = TRUE, 
          probs = 1-percentage_fatigue) #this gives 8% of the sample reporting fatigue when using the "severe symptoms" fatigue response
+fatigue_cutoff
 
@@
 percentage_skipped_meals    # 0.192021% of Menni et al(2020) have fatigue
-quantile(x = respiratory.raw.id$respiratory.skipping_meals_because_you_felt_unwell_numeric, 
+skipped_meals_cutoff <- quantile(x = respiratory.raw.id$respiratory.skipping_meals_because_you_felt_unwell_numeric, 
          na.rm = TRUE, 
          probs = 1-percentage_skipped_meals) # this gives 0.192021% of the sample reporting fatigue when using the "moderate symptoms" persistent cough response
+skipped_meals_cutoff
 ```
@@
       if_else(
-        respiratory.persistent_cough_numeric >= 1, #those who score 1 or above (mild or above)
+        respiratory.persistent_cough_numeric >= pcough_cutoff, #those who score 1 or above (mild or above)
         1,
@@
       if_else(
-        respiratory.feeling_tiredfatigued_numeric >= 3, #those who score 3 (severe symptoms)
+        respiratory.feeling_tiredfatigued_numeric >= fatigue_cutoff, #those who score 3 (severe symptoms)
         1,
@@
       if_else(
-        respiratory.skipping_meals_because_you_felt_unwell_numeric >= 2,
+        respiratory.skipping_meals_because_you_felt_unwell_numeric >= skipped_meals_cutoff,
         1,

### 2020-08-19 PANCHANGE_analysis.Rmd
added some frequency calculations and mean scores for change per disorder

@@
 
+```{r}
+diff_score_cols <- dat %>%
+  select(contains("diff_score")) %>% 
+  colnames()
+
+diff_score_cols
+```
+
 ```{r dat.coping summary, eval=FALSE, include=FALSE}
@@
     Sample,
+    Gender,
+    Ethnicity,
+    all_of(diff_score_cols),
     Disorder,
@@
 Define disorder columns in vector
-```{r}
+
+```{r Disorder by Gender}
 dat.long %>%
-  group_by(Disorder) %>%
-  count()
+  filter(Diagnosis == 1) %>%
+  group_by(Disorder, Gender) %>%
+  count(Disorder)
+```
+
+```{r Disorder by Sample}
+dat.long %>%
+  filter(Diagnosis == 1) %>%
+  group_by(Disorder, Sample) %>%
+  count(Disorder)
+```
+
+```{r Disorder by Ethnicity}
+dat.long %>%
+  filter(Diagnosis == 1) %>%
+  group_by(Disorder, Ethnicity) %>%
+  count(Disorder)
 ```
@@
 #0 = No to disorder; 1 = Yes to disorder
-PMAD_na_drop_Dx %>%
-  select(ID, #need to add columns for which you want summaries for - ASK GB & KY what they want in descriptives table
+dat.long %>%
+  select(ID, #need to add columns for which you want summaries for 
          dem.sex,
@@
 ```{r}
-
+dat %>%
+  group_by(Ethnicity, Sample) %>%
+  count(Ethnicity)
 ```
@@
 ```{r}
-
+dat %>%
+  group_by(Gender, Sample) %>%
+  count(Gender)
 ```
 
-Education
+highest_education
 ```{r}
-
+dat %>%
+  group_by(highest_education, Sample) %>%
+  count(highest_education)
 ```
@@
 ```{r}
-
+dat %>%
+  group_by(key_worker, Sample) %>%
+  count(key_worker)
 ```
@@
 ```{r}
+dat %>%
+  group_by(respiratory.throat_swab_test_nose, Sample) %>%
+  count(respiratory.throat_swab_test_nose)
+```
 
+```{r}
+dat %>%
+  group_by(respiratory.results_antibody_test, Sample) %>%
+  count(respiratory.results_antibody_test)
 ```
@@
 ```{r}
-
+dat %>%
+  group_by(covid_probable_case_incl_screening, Sample) %>%
+  count(covid_probable_case_incl_screening)
 ```
@@
 Ethnicity groups (5; White European, Black (British), Asian, Arab, Mixed)
+
+```{r}
+dat.long %>%
+  filter(Diagnosis == 1) %>%
+  group_by(Disorder) %>%
+  summarise(
+    gad_base_retro = mean(gad.diff_score_base_retro, na.rm = T),
+    gad_prepan_retro = mean(gad.diff_score_prepan_retro, na.rm = T),
+    gad_prepan_base = mean(gad.diff_score_prepan_base, na.rm = T),
+    phq_base_retro = mean(phq.diff_score_base_retro, na.rm = T),
+    phq_prepan_retro = mean(phq.diff_score_prepan_retro, na.rm = T),
+    phq_prepan_base = mean(phq.diff_score_prepan_base, na.rm = T)
+    )
+```
 

### 2020-08-19 PANCHANGE_analysis.Rmd
plots

@@
 library(psych)
-library(eeptools) # Needed to calculate age from birthdate
+library(patchwork)
 library(tidyverse)
@@
 
+```{r}
+gad.diff_score_prepan_base_plot <- dat %>%
+  ggplot(mapping = aes(y = gad.diff_score_prepan_base)) +
+  geom_bar()
+
+gad.diff_score_prepan_retro_plot <- dat %>%
+  ggplot(mapping = aes(y = gad.diff_score_prepan_retro)) +
+  geom_bar()
+
+gad.diff_score_prepan_base_plot <- dat %>%
+  ggplot(mapping = aes(y = gad.diff_score_prepan_base)) +
+  geom_bar()
+
+```
+
+```{r fig.height=5, fig.width=5}
+gad.diff_score_prepan_base_plot /
+  gad.diff_score_prepan_retro_plot /
+  gad.diff_score_prepan_base_plot +
+  plot_layout(guides = "collect", heights = c(1,1,1)) +
+  plot_annotation(tag_levels = "A")
+```
+
 Calculate mean change per disorder group 

### 2020-08-19 PANCHANGE_analysis.Rmd
first crude regression models

--- 2020-08-19 PANCHANGE_analysis.Rmd
@@
 library(psych)
-library(eeptools) # Needed to calculate age from birthdate
+library(patchwork)
+library(broom)
 library(tidyverse)
@@
 
+```{r}
+gad.diff_score_prepan_base_plot <- dat %>%
+  ggplot(mapping = aes(y = gad.diff_score_prepan_base)) +
+  geom_bar() +
+  theme_minimal()
+
+gad.diff_score_prepan_retro_plot <- dat %>%
+  ggplot(mapping = aes(y = gad.diff_score_prepan_retro)) +
+  geom_bar() +
+  theme_minimal()
+
+gad.diff_score_prepan_base_plot <- dat %>%
+  ggplot(mapping = aes(y = gad.diff_score_prepan_base)) +
+  geom_bar() +
+  theme_minimal()
+
+```
+
+```{r fig.height=5, fig.width=5}
+gad.diff_score_prepan_base_plot /
+  gad.diff_score_prepan_retro_plot /
+  gad.diff_score_prepan_base_plot +
+  plot_layout(guides = "collect", heights = c(1,1,1)) +
+  plot_annotation(tag_levels = "A")
+```
+
 Calculate mean change per disorder group 
@@
 ```{r}
+model0 <- lm(
+  formula = gad.diff_score_base_retro ~ Disorder,
+  data = dat.long)
 
+summary(model0)
+```
+
+```{r}
+tidy(model0)
+```
+
+```{r}
+model1 <- lm(
+  formula = gad.diff_score_base_retro ~ time_diff_sign_up_coping,
+  data = dat)
+
+summary(model1)
 ```
@@
 ```{r}
+model1 <- lm(
+  formula = gad.diff_score_base_retro ~ Gender + Age + Ethnicity + time_diff_sign_up_coping + Sample,
+  data = dat)
 
+summary(model1)
 ```

### 2020-08-19 PANCHANGE_analysis.Rmd
add ocir means

@@
     phq_prepan_retro = mean(phq.diff_score_prepan_retro, na.rm = T),
-    phq_prepan_base = mean(phq.diff_score_prepan_base, na.rm = T)
+    phq_prepan_base = mean(phq.diff_score_prepan_base, na.rm = T),
+    ocir_base_retro = mean(ocir.diff_score_base_retro, na.rm = T),
+    ocir_prepan_retro = mean(ocir.diff_score_prepan_retro, na.rm = T),
+    ocir_prepan_base = mean(ocir.diff_score_prepan_base, na.rm = T)
     )

### 2020-08-19 PANCHANGE_analysis.Rmd
fixed the joining chunk

@@
 
-```{r}
+```{r Vectors with diff_score_cols}
 diff_score_cols <- dat %>%
@@
 diff_score_cols
+
+phq.diff_score_cols <- dat %>%
+  select(contains("phq")) %>%
+  select(contains("diff_score")) %>% 
+  colnames()
+
+phq.diff_score_cols
+
+gad.diff_score_cols <- dat %>%
+  select(contains("gad")) %>%
+  select(contains("diff_score")) %>% 
+  colnames()
+
+gad.diff_score_cols
+
+ocir.diff_score_cols <- dat %>%
+  select(contains("ocir")) %>%
+  select(contains("diff_score")) %>% 
+  colnames()
+
+ocir.diff_score_cols
 ```
@@
     "mhd.attention_deficit_hyperactivity_disorder_numeric",
-    "mhd.personality_disorder_numeric"
+    "mhd.personality_disorder_numeric",
+    "control_numeric"
 )
@@
 
-```{r gather to long format}
+```{r gather to long format Disorder}
 dat.long <- dat %>%
@@
   count(Disorder)
-```
-
-## Disorders - Frequencies *use this as example to convert chunk above*
-```{r Disorders - Frequencies}
-#0 = No to disorder; 1 = Yes to disorder
-dat.long %>%
-  select(ID, #need to add columns for which you want summaries for 
-         dem.sex,
-         starts_with("mhd.") & ends_with("numeric")) %>%
-  gather(
-    key = "Disorder",
-    value = "Diagnosis",
-    mhd.MDD_numeric:mhd.ADHD_numeric #all the columns that we want to be gathered
-  ) %>%
-  group_by(Disorder) %>%
-  count(Diagnosis) #count for diagnoses
 ```
@@
   count(covid_probable_case_incl_screening)
+```
+
+Questionnaire columns
+```{r Questionnaire columns}
+
+```
+
+```{r gather to long format Time_points}
+dat.long.gad.diff <- dat %>%
+  gather(
+    key = "Time_point_raw",
+    value = "gad.diff_score",
+    all_of(gad.diff_score_cols)) %>%
+  select(
+    ID,
+    Sample,
+    Gender,
+    Ethnicity,
+    Time_point_raw,
+    gad.diff_score
+  ) %>%
+  mutate(Time_point = str_replace(Time_point_raw, "gad.diff_score_", "")) %>%
+  select(-Time_point_raw)
+
+head(dat.long.gad.diff)
+```
+
+```{r}
+dat.long.gad.diff %>%
+  ggplot(mapping = aes(y = gad.diff_score)) +
+  geom_bar() +
+  theme_minimal() +
+  facet_wrap(facets = vars(Time_point))
+```
+
+```{r gather to long format Time_points}
+dat.long.phq.diff <- dat %>%
+  gather(
+    key = "Time_point_raw",
+    value = "phq.diff_score",
+    all_of(phq.diff_score_cols)) %>%
+  select(
+    ID,
+    Sample,
+    Gender,
+    Ethnicity,
+    Time_point_raw,
+    phq.diff_score
+  ) %>%
+  mutate(Time_point = str_replace(Time_point_raw, "phq.diff_score_", "")) %>%
+  select(-Time_point_raw)
+
+head(dat.long.phq.diff)
+```
+
+```{r}
+dat.long.phq.diff %>%
+  ggplot(mapping = aes(y = phq.diff_score)) +
+  geom_bar() +
+  theme_minimal() +
+  facet_wrap(facets = vars(Time_point))
+```
+
+```{r gather to long format Time_points}
+dat.long.ocir.diff <- dat %>%
+  gather(
+    key = "Time_point_raw",
+    value = "ocir.diff_score",
+    all_of(ocir.diff_score_cols)) %>%
+  select(
+    ID,
+    Sample,
+    Gender,
+    Ethnicity,
+    Time_point_raw,
+    ocir.diff_score
+  ) %>%
+  mutate(Time_point = str_replace(Time_point_raw, "ocir.diff_score_", "")) %>%
+  select(-Time_point_raw)
+
+head(dat.long.ocir.diff)
+```
+
+```{r}
+dat.long.ocir.diff %>%
+  ggplot(mapping = aes(y = ocir.diff_score)) +
+  geom_bar() +
+  theme_minimal() +
+  facet_wrap(facets = vars(Time_point))
 ```

### 2020-08-19 PANCHANGE_analysis.Rmd

@@
 
+Filter data frame to exclude participants that never answered COPING
+```{r}
+
+```
+
 ```{r Vectors with diff_score_cols}
@@
 
+Data availability OCI-R
+```{r}
+
+```
+
+Descriptives of age
+```{r}
+
+```
+
 ```{r vector with psychiatric disorders}
@@
 
+Ethnicity should be recoded
+European
+Mixed or multiplce ethnic origins
+Africian or African British
+Asian or Asian British
+Arab
 ```{r Disorder by Ethnicity}
@@
 
-Questionnaire columns
-```{r Questionnaire columns}
-
-```
-
 ```{r gather to long format Time_points}
@@
 
+makes this into percentages
 ```{r}
@@
   mutate(Time_point = str_replace(Time_point_raw, "phq.diff_score_", "")) %>%
-  select(-Time_point_raw)
+  select(-Time_point_raw) %>%
+  drop_na(phq.diff_score)
 
@@
 dat.long.phq.diff %>%
-  ggplot(mapping = aes(y = phq.diff_score)) +
-  geom_bar() +
-  theme_minimal() +
-  facet_wrap(facets = vars(Time_point))
+  filter(Time_point != "prepan_retro") %>%
+  ggplot(mapping = aes(
+    x = phq.diff_score,
+    y = stat(density*width),
+    fill = Time_point)) +
+   geom_histogram(
+    binwidth = 1,
+    position = position_dodge2(preserve = "single")
+    ) +
+  theme_minimal()
+```
+
+```{r}
+dat.long.phq.diff %>%
+  filter(Time_point == "prepan_retro") %>%
+  ggplot(mapping = aes(
+    x = phq.diff_score,
+    y = stat(density*width),
+    fill = Time_point)) +
+   geom_histogram(
+    binwidth = 1,
+    position = position_dodge2(preserve = "single")
+    ) +
+  theme_minimal()
 ```

### 2020-08-19 PANCHANGE_data_preprocessing2020-07-15.Rmd

@@
   select(highest_education,
+         highest_education_numeric,
          employment.phd_numeric,
@@
         employment.what_is_your_highest_level_of_education == "A-level or equivalent" ~ 3,
-        employment.what_is_your_highest_level_of_education == "GCSE or equivalent" ~ 2,
-        employment.what_is_your_highest_level_of_education == "None of these" ~ 1
+        employment.what_is_your_highest_level_of_education == "GCSE or equivalent" ~ 1,
+        employment.what_is_your_highest_level_of_education == "None of these" ~ 5
       )
@@
         highest_education_numeric,
-        `1` = "None",
-        `2` = "GCSE/CSE",
+        `1` = "GCSE/CSE",
+        `2` = NA_character_,
         `3` = "A-levels",
-        `4` = "University")
+        `4` = "University",
+        `5` = NA_character_)
     )
@@
   select(highest_education,
+         highest_education_numeric,
          employment.what_is_your_highest_level_of_education,
@@
 if(EDGI == TRUE){
+  dim(employment.raw.id)
+  dim(coping.ocir.raw.id)
+
 edgi.employment.coping.ocir <-  full_join(
@@
 )
+
+    dim(edgi.employment.coping.ocir)
 }
@@
   dem.raw.id,
+  employment.raw.id,
   mhd.raw.categories,

### 2020-08-19 PANCHANGE_data_preprocessing2020-07-15.Rmd
added ocir availability chunk

@@
 
+OCI-R
+```{r glad/edgi data level groups ocir}
+if(GLAD == TRUE | EDGI == TRUE){
+dat <- dat %>%
+  mutate(
+    data_group_ocir_numeric =
+      case_when(
+        na_per_person_ocir_base == 0 & na_per_person_ocir_prepan == 0 & na_per_person_ocir_retro == 0 ~ 5, #all complete baseline, prepan and retro
+        na_per_person_ocir_base != 0 & na_per_person_ocir_prepan != 0 & na_per_person_ocir_retro == 0  ~ 4, #retro data only
+        na_per_person_ocir_base == 0 & na_per_person_ocir_prepan != 0 & na_per_person_ocir_retro != 0  ~ 3, #baseline data only
+        na_per_person_ocir_base == 0 & na_per_person_ocir_prepan == 0 & na_per_person_ocir_retro != 0  ~ 2, #prepan and baseline data only
+        na_per_person_ocir_base == 0 & na_per_person_ocir_prepan != 0 & na_per_person_ocir_retro == 0 ~ 1,  #baseline and retro data only
+        na_per_person_ocir_base != 0 & na_per_person_ocir_prepan == 0 & na_per_person_ocir_retro != 0  ~ 0  #prepan data only
+      )
+  )
+
+dat <- dat %>%
+  mutate(
+    data_group_ocir = 
+      recode_factor(
+        data_group_ocir_numeric,
+        "0" = "Only prepandemic data",
+        "1" = "Baseline and retrospective data",
+        "2" = "Prepandemic and baseline data",
+        "3" = "Baseline data only",
+        "4" = "Retrospective data only",
+        "5" = "All prepandemic, baseline and retrospective data"
+      )
+  )
+
+table(dat$data_group_ocir)
+}
+```
+
+```{r nbr/ramp data level groups ocir}
+if(NBR == TRUE | RAMP == TRUE){
+dat <- dat %>%
+  mutate(
+    data_group_ocir_numeric =
+      case_when(
+#        na_per_person_ocir_base == 0 & na_per_person_ocir_prepan == 0 & na_per_person_ocir_retro == 0 ~ 5, #all complete baseline, prepan and retro
+        na_per_person_ocir_base != 0 & na_per_person_ocir_retro == 0  ~ 4, #retro data only
+        na_per_person_ocir_base == 0 & na_per_person_ocir_retro != 0  ~ 3, #baseline data only
+#        na_per_person_ocir_base == 0 & na_per_person_ocir_prepan == 0 & na_per_person_ocir_retro != 0  ~ 2, #prepan and baseline data only
+        na_per_person_ocir_base == 0 & na_per_person_ocir_retro == 0 ~ 1  #baseline and retro data only
+#        na_per_person_ocir_base != 0 & na_per_person_ocir_prepan == 0 & na_per_person_ocir_retro != 0  ~ 0  #prepan data only
+      )
+  )
+
+dat <- dat %>%
+  mutate(
+    data_group_ocir = 
+      recode_factor(
+        data_group_ocir_numeric,
+        "0" = "Only prepandemic data",
+        "1" = "Baseline and retrospective data",
+        "2" = "Prepandemic and baseline data",
+        "3" = "Baseline data only",
+        "4" = "Retrospective data only",
+        "5" = "All prepandemic, baseline and retrospective data"
+      )
+  )
+
+table(dat$data_group_ocir)
+}
+```
+
 #Read in respiratory data

### 2020-08-19 PANCHANGE_data_preprocessing2020-07-15.Rmd
synchronised gender vairable across cohorts

@@
          Age_uncleaned = demographics.how_old_are_you_now.txt, # Age
-         Gender = demographics.which_gender_do_you_identify_with, # Gender
+         Gender_unc = demographics.which_gender_do_you_identify_with, # Gender
          Sex = demographics.select_questionnaire_items_medical, #Sex
@@
       Age_uncleaned = demographics.how_old_are_you_now.txt, # Age
-      Gender = demographics.what_gender_do_you_identify_with, # Gender (which [GLAD] vs what [EDGI])
+      Gender_unc = demographics.what_gender_do_you_identify_with, # Gender (which [GLAD] vs what [EDGI])
       Sex = demographics.select_questionnaire_items_birth, #Sex (different to GLAD)
@@
       Birthday = demographics.day, #Birthday
-      Gender = demographics.which_gender_do_you_identify_with, # Gender
+      Gender_unc = demographics.which_gender_do_you_identify_with, # Gender
       Sex = demographics.select_questionnaire_items_medical, #Sex
@@
 
-# Demographics variable creation
-## Clean Age variable
+## Demographics variable creation
+
+# Gender categories synchronised
+
+```{r gender recoding for GLAD}
+if(GLAD == TRUE) {
+
+dem.raw.id <- dem.raw.id %>%
+  mutate(
+    Gender = 
+      recode_factor(Gender_unc,
+        "Male" = "Male",
+        "Female" = "Female",
+        "Non-binary" = "Non-binary",
+        "Prefer to self-define (please tell us more)" = "Prefer to self-define"
+      )
+  )
+}
+```
+
+```{r gender recoding for EDGI}
+if(EDGI == TRUE) {
+
+dem.raw.id <- dem.raw.id %>%
+  mutate(
+    Gender = 
+      recode_factor(Gender_unc,
+        "Male" = "Male",
+        "Female" = "Female",
+        "Non-binary" = "Non-binary",
+        "Prefer to self-define (please tell us more):" = "Prefer to self-define"
+      )
+  )
+}
+```
+
+```{r gender recoding for NBR}
+if(NBR == TRUE ) {
+
+dem.raw.id <- dem.raw.id %>%
+  mutate(
+    Gender = 
+      recode_factor(Gender_unc,
+        "Male" = "Male",
+        "Female" = "Female",
+        "Non-binary" = "Non-binary",
+        "Prefer to self-define (please tell us more)" = "Prefer to self-define"
+      )
+  )
+}
+```
+
+# Clean Age variable
 Age outlier

### 2020-08-19 PANCHANGE_analysis.Rmd
fixed ethnicity categories

@@
 European
-Mixed or multiplce ethnic origins
-Africian or African British
+Mixed or multiple ethnic origins
+African or African British
 Asian or Asian British

### 2020-08-19 PANCHANGE_data_preprocessing2020-07-15.Rmd
fixed ethnicity categories

@@
          demographics.nvq_or_hnd_or_hnc_or_equivalent, # level of education - nvq
-         Ethnicity = demographics.questions_based_ethnic_origin # Ethnicity
+         Ethnicity_unc = demographics.questions_based_ethnic_origin # Ethnicity
          ) %>%
@@
       demographics.nvq_or_hnd_or_hnc_or_equivalent, # level of education - nvq
-      Ethnicity = demographics.what_is_your_ethnic_origin # Ethnicity (different to GLAD)
+      Ethnicity_unc = demographics.what_is_your_ethnic_origin # Ethnicity (different to GLAD)
     ) %>%
@@
 #Match GLAD/EDGI/RAMP categories
-nbr.cohort.raw.id$Ethnicity <- recode_factor(nbr.cohort.raw.id$Ethnicity.unc,
+nbr.cohort.raw.id$Ethnicity_unc <- recode_factor(nbr.cohort.raw.id$Ethnicity.unc,
                                              "A" = "White, white European or Caucasian",
@@
       Transgender_uncleaned = demographics.do_you_identify_as_transgender,
-      Ethnicity = demographics.what_is_your_ethnic_origin # Ethnicity
+      Ethnicity_unc = demographics.what_is_your_ethnic_origin # Ethnicity
     ) %>%
@@
 ```{r gender recoding for GLAD}
-if(GLAD == TRUE) {
+if(GLAD == TRUE | NBR == TRUE) {
 
@@
       )
+  ) %>%
+  rename(
+    Gender_numeric = Gender_unc_numeric
   )
@@
       )
-  )
-}
-```
-
-```{r gender recoding for NBR}
-if(NBR == TRUE ) {
+  ) %>%
+  rename(
+    Gender_numeric = Gender_unc_numeric
+  )
+}
+```
+
+# Ethnicity recoding
+
+```{r ethnicity recoding for EDGI}
+if(EDGI == TRUE) {
 
@@
   mutate(
-    Gender = 
-      recode_factor(Gender_unc,
-        "Male" = "Male",
-        "Female" = "Female",
-        "Non-binary" = "Non-binary",
-        "Prefer to self-define (please tell us more)" = "Prefer to self-define"
+    Ethnicity = 
+      recode_factor(Ethnicity_unc,
+        "White" = "European",
+        "Mixed" = "Mixed or multiple ethnic origins",
+        "Asian or Asian British" = "Asian or Asian British",
+        "Black or Black British" = "African or African British",
+        "Arab" = "Arab",
+        "Other ethnic group:" = "Other ethnic group"
+      )
+  ) %>%
+  rename(
+    Ethnicity_numeric = Ethnicity_unc_numeric
+  )
+}
+```
+
+```{r ethnicity recoding for GLAD and RAMP}
+if(GLAD == TRUE | RAMP == TRUE) {
+
+dem.raw.id <- dem.raw.id %>%
+  mutate(
+    Ethnicity = 
+      recode_factor(Ethnicity_unc,
+        "White, white European or Caucasian" = "European",
+        "Mixed or multiple ethnic origins" = "Mixed or multiple ethnic origins",
+        "Asian or Asian British (including Chinese)" = "Asian or Asian British",
+        "Black or Black British" = "African or African British",
+        "Arab" = "Arab",
+        "Other ethnic group (please specify)" = "Other ethnic group"
+      )
+  ) %>%
+  rename(
+    Ethnicity_numeric = Ethnicity_unc_numeric
+  )
+}
+```
+
+```{r ethnicity recoding for NBR}
+if(NBR == TRUE) {
+
+dem.raw.id <- dem.raw.id %>%
+  mutate(
+    Ethnicity = 
+      recode_factor(Ethnicity_unc,
+        "White, white European or Caucasian" = "European",
+        "Mixed or multiple ethnic origins" = "Mixed or multiple ethnic origins",
+        "Asian or Asian British (including Chinese)" = "Asian or Asian British",
+        "Black or Black British" = "African or African British",
+        "Arab" = "Arab",
+        "Other ethnic group (please specify)" = "Other ethnic group"
+      )
+  ) %>%
+  mutate(
+    Ethnicity_numeric = 
+      recode(Ethnicity_unc,
+        "European" = 1,
+        "Mixed or multiple ethnic origins" = 2,
+        "Asian or Asian British" = 3,
+        "African or African British" = 4,
+        "Arab" = 5,
+        "Other ethnic group" = 6
       )

### 2020-08-19 PANCHANGE_data_preprocessing2020-07-15.Rmd
changed diff score naming

@@
 # Gender categories synchronised
-
+RAMP has the correct Gender categories so does not need editing. 
 ```{r gender recoding for GLAD}
@@
   mutate(
-    phq.diff_score_prepan_base =
+    phq.diff_score_base_prepan =
       as.numeric(
@@
   mutate(
-    gad.diff_score_prepan_base =
+    gad.diff_score_base_prepan =
       as.numeric(
@@
   mutate(
-    pcl.diff_score_prepan_base =
+    pcl.diff_score_base_prepan =
       as.numeric(
@@
 
+# Rename NBR Sample ID 
+```{r rename NBR sample ID}
+if(NBR == TRUE){
+dat.coping <- dat.coping %>%
+  recode(Sample,
+         "SP0068" = "NBR"
+         )
+}
+```
+
 # Export data

### 2020-08-19 PANCHANGE_data_preprocessing2020-07-15.Rmd
renamed NBR Sample ID
filtered out extra GLAD people from NBR cohort

@@
 
-Exclusion of inflammatory bowel disease (IBD) BioResource (BR) cohort
+Exclusion of inflammatory bowel disease (IBD) and GLAD BioResource (NBR) cohort
 ++MD: 3,410 participants from NBR IBD cohort excluded
-```{r COVID exclusion of IBD}
+++KT: 3 duplicated GLAD participants are excluded
+```{r COVID exclusion of IBD and GLAD from NBR sample}
 if(NBR == TRUE) {
@@
 dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age %>%
-  filter(Cohort != "IBD")
+  filter(Cohort != "IBD") %>%
+  filter(Cohort != "GLAD")
 
@@
 dat.coping <- dat.coping %>%
-  recode(Sample,
+  mutate(
+    Sample = 
+    recode(
+      Sample, 
       "SP0068" = "NBR"
+    )
   )

### 2020-08-19 PANCHANGE_data_preprocessing2020-07-15.Rmd
edgi joining fix

--- 2020-08-19 PANCHANGE_data_preprocessing2020-07-15.Rmd
@@
          Age_uncleaned = demographics.how_old_are_you_now.txt, # Age
-         Gender_unc = demographics.which_gender_do_you_identify_with, # Gender
+         Gender = demographics.which_gender_do_you_identify_with, # Gender
          Sex = demographics.select_questionnaire_items_medical, #Sex
@@
          demographics.nvq_or_hnd_or_hnc_or_equivalent, # level of education - nvq
-         Ethnicity_unc = demographics.questions_based_ethnic_origin # Ethnicity
+         Ethnicity = demographics.questions_based_ethnic_origin # Ethnicity
          ) %>%
@@
       Age_uncleaned = demographics.how_old_are_you_now.txt, # Age
-      Gender_unc = demographics.what_gender_do_you_identify_with, # Gender (which [GLAD] vs what [EDGI])
+      Gender = demographics.what_gender_do_you_identify_with, # Gender (which [GLAD] vs what [EDGI])
       Sex = demographics.select_questionnaire_items_birth, #Sex (different to GLAD)
@@
       demographics.nvq_or_hnd_or_hnc_or_equivalent, # level of education - nvq
-      Ethnicity_unc = demographics.what_is_your_ethnic_origin # Ethnicity (different to GLAD)
+      Ethnicity = demographics.what_is_your_ethnic_origin # Ethnicity (different to GLAD)
     ) %>%
@@
       Birthday = demographics.day, #Birthday
-      Gender_unc = demographics.which_gender_do_you_identify_with, # Gender
+      Gender = demographics.which_gender_do_you_identify_with, # Gender
       Sex = demographics.select_questionnaire_items_medical, #Sex
@@
 #Match GLAD/EDGI/RAMP categories
-nbr.cohort.raw.id$Ethnicity_unc <- recode_factor(nbr.cohort.raw.id$Ethnicity.unc,
+nbr.cohort.raw.id$Ethnicity <- recode_factor(nbr.cohort.raw.id$Ethnicity.unc,
                                              "A" = "White, white European or Caucasian",
@@
       Transgender_uncleaned = demographics.do_you_identify_as_transgender,
-      Ethnicity_unc = demographics.what_is_your_ethnic_origin # Ethnicity
+      Ethnicity = demographics.what_is_your_ethnic_origin # Ethnicity
     ) %>%
@@
 
-## Demographics variable creation
-
-# Gender categories synchronised
-
-```{r gender recoding for GLAD}
-if(GLAD == TRUE | NBR == TRUE) {
-
-dem.raw.id <- dem.raw.id %>%
-  mutate(
-    Gender = 
-      recode_factor(Gender_unc,
-        "Male" = "Male",
-        "Female" = "Female",
-        "Non-binary" = "Non-binary",
-        "Prefer to self-define (please tell us more)" = "Prefer to self-define"
-      )
-  ) %>%
-  rename(
-    Gender_numeric = Gender_unc_numeric
-  )
-}
-```
-
-```{r gender recoding for EDGI}
-if(EDGI == TRUE) {
-
-dem.raw.id <- dem.raw.id %>%
-  mutate(
-    Gender = 
-      recode_factor(Gender_unc,
-        "Male" = "Male",
-        "Female" = "Female",
-        "Non-binary" = "Non-binary",
-        "Prefer to self-define (please tell us more):" = "Prefer to self-define"
-      )
-  ) %>%
-  rename(
-    Gender_numeric = Gender_unc_numeric
-  )
-}
-```
-
-# Ethnicity recoding
-
-```{r ethnicity recoding for EDGI}
-if(EDGI == TRUE) {
-
-dem.raw.id <- dem.raw.id %>%
-  mutate(
-    Ethnicity = 
-      recode_factor(Ethnicity_unc,
-        "White" = "European",
-        "Mixed" = "Mixed or multiple ethnic origins",
-        "Asian or Asian British" = "Asian or Asian British",
-        "Black or Black British" = "African or African British",
-        "Arab" = "Arab",
-        "Other ethnic group:" = "Other ethnic group"
-      )
-  ) %>%
-  rename(
-    Ethnicity_numeric = Ethnicity_unc_numeric
-  )
-}
-```
-
-```{r ethnicity recoding for GLAD and RAMP}
-if(GLAD == TRUE | RAMP == TRUE) {
-
-dem.raw.id <- dem.raw.id %>%
-  mutate(
-    Ethnicity = 
-      recode_factor(Ethnicity_unc,
-        "White, white European or Caucasian" = "European",
-        "Mixed or multiple ethnic origins" = "Mixed or multiple ethnic origins",
-        "Asian or Asian British (including Chinese)" = "Asian or Asian British",
-        "Black or Black British" = "African or African British",
-        "Arab" = "Arab",
-        "Other ethnic group (please specify)" = "Other ethnic group"
-      )
-  ) %>%
-  rename(
-    Ethnicity_numeric = Ethnicity_unc_numeric
-  )
-}
-```
-
-```{r ethnicity recoding for NBR}
-if(NBR == TRUE) {
-
-dem.raw.id <- dem.raw.id %>%
-  mutate(
-    Ethnicity = 
-      recode_factor(Ethnicity_unc,
-        "White, white European or Caucasian" = "European",
-        "Mixed or multiple ethnic origins" = "Mixed or multiple ethnic origins",
-        "Asian or Asian British (including Chinese)" = "Asian or Asian British",
-        "Black or Black British" = "African or African British",
-        "Arab" = "Arab",
-        "Other ethnic group (please specify)" = "Other ethnic group"
-      )
-  ) %>%
-  mutate(
-    Ethnicity_numeric = 
-      recode(Ethnicity_unc,
-        "European" = 1,
-        "Mixed or multiple ethnic origins" = 2,
-        "Asian or Asian British" = 3,
-        "African or African British" = 4,
-        "Arab" = 5,
-        "Other ethnic group" = 6
-      )
-  )
-}
-```
-
-# Clean Age variable
+# Demographics variable creation
+## Clean Age variable
 Age outlier
@@
   separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
-  separate("Login ID", into = c("COPING_Sample", "COPING_ID"), sep = 6) %>% # Split ID in Sample and Number
-  mutate(COPING_ID = as.numeric(COPING_ID)) %>%
-  mutate(
-    ID = as.numeric(ID)
+#  separate("Login ID", into = c("COPING_Sample", "COPING_ID"), sep = 6) %>% # Split ID in Sample and Number
+  mutate(
+    ID = as.numeric(ID),
+#    COPING_ID = as.numeric(COPING_ID)
     ) %>%
@@
          ID, # ID
-         COPING_ID,
+         COPING_ID = "Login ID",
          employment.phd, # level of education - univeristy
@@
   distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
-  separate(externalDataReference, into = c("COPING_Sample", "COPING_ID"), sep = 6) %>% # Split ID in Sample and Number
-  mutate(COPING_ID = as.numeric(COPING_ID)) %>%
+#  separate(externalDataReference, into = c("COPING_Sample", "COPING_ID"), sep = 6) %>% # Split ID in Sample and Number
+#  mutate(COPING_ID = as.numeric(COPING_ID)) %>%
   select(
 #    Sample, # Sample
-    COPING_ID, # ID
+    COPING_ID = externalDataReference, # ID
     ocir.felt_pandemic_feelings, # Comparison to before the pandemic
@@
 
-edgi.employment.coping.ocir <-  full_join(
+edgi.employment.coping.ocir <- left_join(
     x = employment.raw.id,
     y = coping.ocir.raw.id,
-    by = 
-      c("Sample",
-        "COPING_ID")
+    by = c(
+      "COPING_ID",
+      "Sample")
 )
@@
 table(dat$data_group_pcl)
-}
-```
-
-OCI-R
-```{r glad/edgi data level groups ocir}
-if(GLAD == TRUE | EDGI == TRUE){
-dat <- dat %>%
-  mutate(
-    data_group_ocir_numeric =
-      case_when(
-        na_per_person_ocir_base == 0 & na_per_person_ocir_prepan == 0 & na_per_person_ocir_retro == 0 ~ 5, #all complete baseline, prepan and retro
-        na_per_person_ocir_base != 0 & na_per_person_ocir_prepan != 0 & na_per_person_ocir_retro == 0  ~ 4, #retro data only
-        na_per_person_ocir_base == 0 & na_per_person_ocir_prepan != 0 & na_per_person_ocir_retro != 0  ~ 3, #baseline data only
-        na_per_person_ocir_base == 0 & na_per_person_ocir_prepan == 0 & na_per_person_ocir_retro != 0  ~ 2, #prepan and baseline data only
-        na_per_person_ocir_base == 0 & na_per_person_ocir_prepan != 0 & na_per_person_ocir_retro == 0 ~ 1,  #baseline and retro data only
-        na_per_person_ocir_base != 0 & na_per_person_ocir_prepan == 0 & na_per_person_ocir_retro != 0  ~ 0  #prepan data only
-      )
-  )
-
-dat <- dat %>%
-  mutate(
-    data_group_ocir = 
-      recode_factor(
-        data_group_ocir_numeric,
-        "0" = "Only prepandemic data",
-        "1" = "Baseline and retrospective data",
-        "2" = "Prepandemic and baseline data",
-        "3" = "Baseline data only",
-        "4" = "Retrospective data only",
-        "5" = "All prepandemic, baseline and retrospective data"
-      )
-  )
-
-table(dat$data_group_ocir)
-}
-```
-
-```{r nbr/ramp data level groups ocir}
-if(NBR == TRUE | RAMP == TRUE){
-dat <- dat %>%
-  mutate(
-    data_group_ocir_numeric =
-      case_when(
-#        na_per_person_ocir_base == 0 & na_per_person_ocir_prepan == 0 & na_per_person_ocir_retro == 0 ~ 5, #all complete baseline, prepan and retro
-        na_per_person_ocir_base != 0 & na_per_person_ocir_retro == 0  ~ 4, #retro data only
-        na_per_person_ocir_base == 0 & na_per_person_ocir_retro != 0  ~ 3, #baseline data only
-#        na_per_person_ocir_base == 0 & na_per_person_ocir_prepan == 0 & na_per_person_ocir_retro != 0  ~ 2, #prepan and baseline data only
-        na_per_person_ocir_base == 0 & na_per_person_ocir_retro == 0 ~ 1  #baseline and retro data only
-#        na_per_person_ocir_base != 0 & na_per_person_ocir_prepan == 0 & na_per_person_ocir_retro != 0  ~ 0  #prepan data only
-      )
-  )
-
-dat <- dat %>%
-  mutate(
-    data_group_ocir = 
-      recode_factor(
-        data_group_ocir_numeric,
-        "0" = "Only prepandemic data",
-        "1" = "Baseline and retrospective data",
-        "2" = "Prepandemic and baseline data",
-        "3" = "Baseline data only",
-        "4" = "Retrospective data only",
-        "5" = "All prepandemic, baseline and retrospective data"
-      )
-  )
-
-table(dat$data_group_ocir)
 }

### 2020-08-19 PANCHANGE_analysis.Rmd
added calculated frequencies and plots

@@
 
-### Read in data
+## Read in data
 ```{r read in data}
-dat <- readRDS(file = paste0(data_path, "/four_cohorts.rds"))
-dim(dat)
-colnames(dat)
+dat.raw <- readRDS(file = paste0(data_path, "/four_cohorts.rds"))
+dim(dat.raw)
+colnames(dat.raw)
 ```
 
-Filter data frame to exclude participants that never answered COPING
-```{r}
-
+```{r dat.coping summary, eval=FALSE, include=FALSE}
+summarytools::dfSummary(
+  dat.raw,
+  graph.col = F,
+  valid.col = F,
+  labels.col = F)
 ```
 
+# Data availability
+```{r gad availability}
+dat.raw %>%
+  freq(
+    data_group_gad,
+    cumul = F)
+```
+
+```{r phq availability}
+dat.raw %>%
+  freq(
+    data_group_phq,
+    cumul = F)
+```
+
+```{r pcl availability}
+dat.raw %>%
+  freq(
+    data_group_pcl,
+    cumul = F)
+```
+
+Data availability OCI-R
+```{r ocir availability}
+dat.raw %>%
+  freq(
+    data_group_ocir,
+    cumul = F)
+```
+
+# Exclusion
+Filter data frame to exclude participants that never answered COPING
+```{r exclusion criteria dat}
+dat <- dat.raw %>%
+  filter(
+    (data_group_gad == "Baseline and retrospective data" |
+      data_group_gad == "Prepandemic and baseline data" |
+      data_group_gad == "All prepandemic, baseline and retrospective data") |
+      (data_group_phq == "Baseline and retrospective data" |
+      data_group_phq == "Prepandemic and baseline data" |
+      data_group_phq == "All prepandemic, baseline and retrospective data") |
+      (data_group_pcl == "Baseline and retrospective data" |
+      data_group_pcl == "Prepandemic and baseline data" |
+      data_group_pcl == "All prepandemic, baseline and retrospective data") |
+      (data_group_ocir == "Baseline and retrospective data" |
+      data_group_ocir == "Prepandemic and baseline data" |
+      data_group_ocir == "All prepandemic, baseline and retrospective data")
+  )
+```
+
+```{r dimensions of total dat}
+dim(dat)
+```
+
+# ggplot theme
+```{r ggplot theme}
+theme_personal <-  theme(
+    text = element_text(color = "black"),
+    axis.title = element_text(color = "black"),
+    axis.text = element_text(color = "black"),
+    axis.title.y = element_blank(), 
+    legend.background = element_blank(),
+    legend.box.background = element_blank(),
+    panel.background = element_blank(), 
+    panel.grid.minor.x = element_blank(),
+    panel.grid.major.x = element_line(
+      colour = "gray",
+      linetype = "dashed",
+      size = 0.2
+      ),
+    axis.ticks = element_blank()
+    )
+```
+
+# Age
+```{r descriptives Ages}
+dat %>%
+  group_by(Sample) %>%
+  summarise(Mean = mean(Age),
+            SD = sd(Age),
+            Min = min(Age),
+            Max = max(Age))
+```
+
+# Vectors for diff_score
 ```{r Vectors with diff_score_cols}
@@
 
-```{r dat.coping summary, eval=FALSE, include=FALSE}
-summarytools::dfSummary(
-  dat,
-  graph.col = F,
-  valid.col = F,
-  labels.col = F)
-```
-
-Data availability
-```{r gad availability}
-dat %>%
-  freq(
-    data_group_gad,
-    cumul = F)
-```
-
-```{r phq availability}
-dat %>%
-  freq(
-    data_group_phq,
-    cumul = F)
-```
-
-```{r pcl availability}
-dat %>%
-  freq(
-    data_group_pcl,
-    cumul = F)
-```
-
-Data availability OCI-R
-```{r}
-
-```
-
-Descriptives of age
-```{r}
-
-```
-
+# Psychiatric disorders
 ```{r vector with psychiatric disorders}
@@
 ```{r gather to long format Disorder}
-dat.long <- dat %>%
+dat.long.psych <- dat %>%
   gather(
-    key = "Disorder",
+    key = "Disorder_raw",
     value = "Diagnosis",
@@
     all_of(diff_score_cols),
-    Disorder,
+    Disorder_raw,
     Diagnosis
-  )
+  ) %>%
+  mutate(Disorder =
+           recode_factor(
+             Disorder_raw,
+             anxiety_disorders_numeric = "Anxiety disorders",
+             depressive_disorders_numeric = "Depressive disorders",
+             eating_disorders_numeric = "Eating disorders",
+             obsessive_compulsive_disorders_numeric = "OCDs",
+             psychotic_disorders_numeric = "Psychotic disorders",
+             mhd.mania_hypomania_bipolar_or_manicdepression_numeric = "Bipolar disorders",
+             mhd.posttraumatic_stress_disorder_ptsd_numeric = "PTSD",
+             mhd.autism_aspergers_or_autistic_spectrum_disorder_numeric = "Autism",
+             mhd.attention_deficit_hyperactivity_disorder_numeric = "ADHD",
+             mhd.personality_disorder_numeric = "Personality disorders",
+             control_numeric = "Controls"
+           ))
 
-head(dat.long)
+head(dat.long.psych)
 ```
@@
 ```{r Disorder by Gender}
-dat.long %>%
+Disorder_by_Gender <- dat.long.psych %>%
   filter(Diagnosis == 1) %>%
@@
   count(Disorder)
+
+Disorder_by_Gender
+```
+
+```{r Disorder by Gender plot}
+Disorder_by_Gender %>%
+  ggplot(mapping = aes(
+    x = Disorder,
+    y = n)
+    ) +
+  geom_bar(
+    aes(fill = Gender),
+#    position = "dodge",
+    stat="identity",
+    binwidth = 1,
+    position = position_dodge2(preserve = "single")
+  ) +
+  labs(
+    x = "Disorder",
+    y = "Number of participants",
+    fill = "Gender") +
+  theme_personal +
+  scale_fill_manual(
+    values = COPINGpalette4,
+#    labels = c("Prepandemic", "Retrospective")
+    ) +
+  coord_flip()
 ```
@@
 ```{r Disorder by Sample}
-dat.long %>%
+Disorder_by_Sample <- dat.long.psych %>%
   filter(Diagnosis == 1) %>%
@@
   count(Disorder)
+```
+
+```{r Disorder by Sample plot}
+Disorder_by_Sample %>%
+  ggplot(mapping = aes(
+    x = Disorder,
+    y = n)
+    ) +
+  geom_bar(
+    aes(fill = Sample),
+#    position = "dodge",
+    stat="identity",
+    binwidth = 1,
+    position = position_dodge2(preserve = "single")
+  ) +
+  labs(
+    x = "Disorder",
+    y = "Number of participants",
+    fill = "Sample") +
+  theme_personal +
+  scale_fill_manual(
+    values = COPINGpalette4,
+#    labels = c("Prepandemic", "Retrospective")
+    ) +
+  coord_flip()
 ```
@@
 ```{r Disorder by Ethnicity}
-dat.long %>%
+Disorder_by_Ethnicity <- dat.long.psych %>%
   filter(Diagnosis == 1) %>%
@@
   count(Disorder)
+```
+
+```{r Disorder by Ethnicity plot}
+Disorder_by_Ethnicity %>%
+  ggplot(mapping = aes(
+    x = Disorder,
+    y = n)
+  ) +
+  geom_bar(
+    aes(fill = Ethnicity),
+    #    position = "dodge",
+    stat="identity",
+    binwidth = 1,
+    position = position_dodge2(preserve = "single")
+  ) +
+  labs(
+    x = "Disorder",
+    y = "Number of participants",
+    fill = "Ethnicity") +
+  theme_personal +
+  scale_fill_manual(
+    values = COPINGpalette6,
+    #    labels = c("Prepandemic", "Retrospective")
+  ) +
+  coord_flip()
 ```
@@
 
-Ethnicity
-```{r}
-dat %>%
+# Ethnicity
+```{r Ethnicity per Sample}
+Ethnicity_by_Sample <- dat %>%
   group_by(Ethnicity, Sample) %>%
   count(Ethnicity)
+
+Ethnicity_by_Sample
 ```
 
-Gender
-```{r}
+```{r Ethnicity by Sample plot}
+Ethnicity_by_Sample %>%
+  ggplot(mapping = aes(
+    x = Ethnicity,
+    y = n)
+  ) +
+  geom_bar(
+    aes(fill = Sample),
+    #    position = "dodge",
+    stat="identity",
+    binwidth = 1,
+    position = position_dodge2(preserve = "single")
+  ) +
+  labs(
+    x = "Ethnicity",
+    y = "Number of participants",
+    fill = "Sample") +
+  theme_personal +
+  scale_fill_manual(
+    values = COPINGpalette6,
+    #    labels = c("Prepandemic", "Retrospective")
+  ) +
+  coord_flip()
+```
+
+# Gender
+```{r Gender per Sample}
 dat %>%
@@
 
-highest_education
-```{r}
+# highest_education
+```{r highest_education per Sample}
 dat %>%
@@
 
-Key worker status
-```{r}
+# Key worker status
+```{r Key worker status per sample}
 dat %>%
@@
 
-COVID test positive
-```{r}
+# COVID
+## COVID swab test positive
+```{r COVID positive swap}
 dat %>%
@@
 
-```{r}
+## antibody test
+```{r COVID positive antibody test}
 dat %>%
@@
 
-COVID probable diagnosis
-```{r}
+## COVID probable diagnosis
+```{r COVID probable diagnosis}
 dat %>%
@@
 
-```{r gather to long format Time_points}
+# Questionnaire comparions
+
+## gad
+```{r gad gather to long format Time_points}
 dat.long.gad.diff <- dat %>%
@@
 makes this into percentages
-```{r}
+```{r gad absolut plot}
 dat.long.gad.diff %>%
@@
 
-```{r gather to long format Time_points}
+```{r gad percentage plot prepan_retro}
+dat.long.gad.diff %>%
+  filter(Time_point != "prepan_retro") %>%
+  ggplot(mapping = aes(
+    x = gad.diff_score,
+    y = stat(density*width),
+    fill = Time_point)) +
+  geom_histogram(
+    binwidth = 1,
+    position = position_dodge2(preserve = "single")
+  ) +
+  labs(
+    x = "Difference GAD7 score",
+    y = "Percentage of participants",
+    fill = "Comparison:\nBaseline vs") +
+  theme_personal +
+  scale_fill_manual(values = palette, labels = c("Prepandemic", "Retrospective"))
+```
+
+```{r gad plot prepan_retro diff}
+dat.long.gad.diff %>%
+  filter(Time_point == "prepan_retro") %>%
+  ggplot(mapping = aes(
+    x = gad.diff_score,
+    y = stat(density*width),
+    fill = Time_point)) +
+  geom_histogram(
+    binwidth = 1,
+    position = position_dodge2(preserve = "single")
+  ) +
+  labs(
+    x = "Difference GAD7 score",
+    y = "Percentage of participants",
+    fill = "Comparison:\nPrepandemic vs") +
+  theme_personal +
+  scale_fill_manual(values = palette, labels = c("Retrospective"))
+```
+
+# phq
+
+```{r phq gather to long format Time_points}
 dat.long.phq.diff <- dat %>%

### 2020-08-20 PANCHANGE_analysis.Rmd
added more plots and tables

@@
 
+Install packages
+```{r}
+#install.packages("infer")
+```
+
 Load packages
@@
 library(psych)
+library(infer)
 library(patchwork)
@@
 # Data availability
+
+Data availability GAD
 ```{r gad availability}
@@
 
+Data availability PHQ
 ```{r phq availability}
@@
 
+Data availability PCL
 ```{r pcl availability}
@@
 
+# Vectors for diff_score
+```{r Vectors with diff_score_cols}
+diff_score_cols <- dat %>%
+  select(contains("diff_score")) %>% 
+  colnames()
+
+diff_score_cols
+
+phq.diff_score_cols <- dat %>%
+  select(contains("phq")) %>%
+  select(contains("diff_score")) %>% 
+  colnames()
+
+phq.diff_score_cols
+
+gad.diff_score_cols <- dat %>%
+  select(contains("gad")) %>%
+  select(contains("diff_score")) %>% 
+  colnames()
+
+gad.diff_score_cols
+
+ocir.diff_score_cols <- dat %>%
+  select(contains("ocir")) %>%
+  select(contains("diff_score")) %>% 
+  colnames()
+
+ocir.diff_score_cols
+```
+
 # ggplot theme
+Set up ggplot theme for the plots
 ```{r ggplot theme}
@@
 
-# Vectors for diff_score
-```{r Vectors with diff_score_cols}
-diff_score_cols <- dat %>%
-  select(contains("diff_score")) %>% 
-  colnames()
++++ADD CHUNK FOR AGE CATEGORIES HERE
+```{r Age categories}
 
-diff_score_cols
-
-phq.diff_score_cols <- dat %>%
-  select(contains("phq")) %>%
-  select(contains("diff_score")) %>% 
-  colnames()
-
-phq.diff_score_cols
-
-gad.diff_score_cols <- dat %>%
-  select(contains("gad")) %>%
-  select(contains("diff_score")) %>% 
-  colnames()
-
-gad.diff_score_cols
-
-ocir.diff_score_cols <- dat %>%
-  select(contains("ocir")) %>%
-  select(contains("diff_score")) %>% 
-  colnames()
-
-ocir.diff_score_cols
 ```
@@
   filter(Diagnosis == 1) %>%
-  group_by(Disorder, Gender) %>%
-  count(Disorder)
+  count(Disorder, Gender) %>%
+  mutate(Prop = round(n/sum(n), 2))
+
+Disorder_by_Gender
+```
+
+```{r Disorder by Gender}
+Disorder_by_Gender <- dat.long.psych %>%
+  group_by(Disorder) %>%
+  filter(Diagnosis == 1) %>%
+  count(Gender) %>%
+  mutate(Prop = round(n/sum(n), 2))
 
@@
   filter(Diagnosis == 1) %>%
-  group_by(Disorder, Ethnicity) %>%
-  count(Disorder)
+  count(Disorder, Ethnicity) %>%
+  mutate(Prop = round(n/sum(n), 2))
+
+Disorder_by_Ethnicity
 ```
@@
 Ethnicity_by_Sample <- dat %>%
-  group_by(Ethnicity, Sample) %>%
-  count(Ethnicity)
+  count(Ethnicity, Sample) %>%
+  mutate(Prop = round(n/sum(n), 2))
 
@@
 # Gender
-```{r Gender per Sample}
+```{r Gender per Sample prop per total}
 dat %>%
-  group_by(Gender, Sample) %>%
-  count(Gender)
+  count(Gender, Sample) %>%
+  mutate(Prop = round(n/sum(n), 2))
+```
+
+```{r Gender per Sample prop per Sample}
+dat %>%
+  group_by(Sample) %>%
+  count(Gender, Sample) %>%
+  mutate(Prop = round(n/sum(n), 2))
+```
+
+```{r Gender per Sample prop cross table}
+dat %>%
+  group_by(Sample) %>%
+  count(Gender, Sample) %>%
+  mutate(Prop = round(n/sum(n), 2)) %>%
+  pivot_wider(names_from = Sample, values_from = c(n, Prop))
+```
+
+```{r Gender per Sample count cross table}
+dat %>%
+  count(Gender, Sample) %>%
+  spread(key = Sample, value = n)
+```
+
+```{r}
+dat %>%
+  count(Gender, Sample) %>%
+  spread(key = Sample, value = n) %>%
+  select(-Gender) %>%
+  chisq.test() %>%
+  glance()
+```
+
+```{r Gender per Sample chisquare}
+dat %>% 
+  specify(Gender ~ Sample)  %>% 
+  hypothesize(null = "independence") %>% 
+  generate(reps = 1000, type = "permute") %>% 
+  calculate(stat = "Chisq") %>% 
+  visualize()# +
+#  geom_vline(aes(xintercept = observed_stat), color = "red") # add a vertical line for the data
 ```

### 2020-08-20 PANCHANGE_analysis.Rmd
added plots and tables for phq gad and ocir

@@
 
-```{r Gender per Sample chisquare}
-dat %>% 
-  specify(Gender ~ Sample)  %>% 
-  hypothesize(null = "independence") %>% 
-  generate(reps = 1000, type = "permute") %>% 
-  calculate(stat = "Chisq") %>% 
-  visualize()# +
-#  geom_vline(aes(xintercept = observed_stat), color = "red") # add a vertical line for the data
-```
-
 # highest_education
@@
 dat %>%
-  group_by(highest_education, Sample) %>%
-  count(highest_education)
+  count(highest_education, Sample) %>%
+  mutate(Prop = round(n/sum(n), 2))
 ```
@@
 dat %>%
-  group_by(key_worker, Sample) %>%
-  count(key_worker)
+  count(key_worker, Sample) %>%
+  mutate(Prop = round(n/sum(n), 2))
 ```
@@
 dat %>%
-  group_by(respiratory.throat_swab_test_nose, Sample) %>%
-  count(respiratory.throat_swab_test_nose)
+  count(respiratory.throat_swab_test_nose, Sample) %>%
+  mutate(Prop = round(n/sum(n), 2))
 ```
@@
 dat %>%
-  group_by(respiratory.results_antibody_test, Sample) %>%
-  count(respiratory.results_antibody_test)
+  count(respiratory.results_antibody_test, Sample) %>%
+  mutate(Prop = round(n/sum(n), 2))
 ```
@@
 dat %>%
-  group_by(covid_probable_case_incl_screening, Sample) %>%
-  count(covid_probable_case_incl_screening)
+  count(covid_probable_case_incl_screening, Sample) %>%
+  mutate(Prop = round(n/sum(n), 2))
 ```
@@
 ## gad
+
+```{r descriptives gad.diff_score_cols}
+gad.numeric_table <- dat %>% 
+#  group_by(dem.sex) %>%
+  summarise_at( 
+    vars(
+      "Base - prepan" = gad.diff_score_base_prepan,
+      "Base - retro" = gad.diff_score_base_retro,
+      "Prepan - retro" = gad.diff_score_prepan_retro,
+    ),
+    .funs =
+      list(
+        ~mean(., na.rm = T),
+        ~sd(., na.rm = T),
+        ~median(., na.rm = T),
+        ~min(., na.rm = T),
+        ~max(., na.rm = T),
+        ~skew(., na.rm = T),
+        kurtosis = ~kurtosi(., na.rm = T)
+      )
+  )
+
+gad.numeric_table
+```
+
+```{r smart numeric summary tables}
+# reshape the table
+gad.numeric_summary_table_reshaped <- gad.numeric_table %>% 
+  gather(key, value) %>% 
+  separate(key, c("variable", "measure"), sep = "_") %>%
+  mutate(measure = factor(
+    x = measure,
+    levels =  c( # this is the order I want my columns to appear in
+      "missing",
+      "min",
+      "max",
+      "mean", 
+      "median", 
+      "mode",
+      "sd",
+      "skew",
+      "kurtosis"
+    ))) %>% 
+  spread(measure, value) %>% 
+  # we can apply a function to all variables to edit them so that they are publication ready
+  rename_all(
+    .funs = ~str_to_title(.)
+    ) %>% 
+  # or we can individually rename variables 
+  rename(
+    SD = Sd
+  )
+
+gad.numeric_summary_table_reshaped
+```
+
+Table for knitting
+gad diff summary table
+```{r gad diff summary table}
+kable(gad.numeric_summary_table_reshaped)
+```
+
 ```{r gad gather to long format Time_points}
@@
 
-# phq
+## phq
+
+```{r descriptives phq.diff_score_cols}
+phq.numeric_table <- dat %>% 
+  #  group_by(dem.sex) %>%
+  summarise_at( 
+    vars(
+      "Base - prepan" = phq.diff_score_base_prepan,
+      "Base - retro" = phq.diff_score_base_retro,
+      "Prepan - retro" = phq.diff_score_prepan_retro,
+    ),
+    .funs =
+      list(
+        ~mean(., na.rm = T),
+        ~sd(., na.rm = T),
+        ~median(., na.rm = T),
+        ~min(., na.rm = T),
+        ~max(., na.rm = T),
+        ~skew(., na.rm = T),
+        kurtosis = ~kurtosi(., na.rm = T)
+      )
+  )
+
+phq.numeric_table
+```
+
+```{r smart numeric summary tables}
+# reshape the table
+phq.numeric_summary_table_reshaped <- phq.numeric_table %>% 
+  gather(key, value) %>% 
+  separate(key, c("variable", "measure"), sep = "_") %>%
+  mutate(measure = factor(
+    x = measure,
+    levels =  c( # this is the order I want my columns to appear in
+      "missing",
+      "min",
+      "max",
+      "mean", 
+      "median", 
+      "mode",
+      "sd",
+      "skew",
+      "kurtosis"
+    ))) %>% 
+  spread(measure, value) %>% 
+  # we can apply a function to all variables to edit them so that they are publication ready
+  rename_all(
+    .funs = ~str_to_title(.)
+  ) %>% 
+  # or we can individually rename variables 
+  rename(
+    SD = Sd
+  )
+
+phq.numeric_summary_table_reshaped
+```
+
+Table for knitting
+phq diff summary table
+```{r phq diff summary table}
+kable(phq.numeric_summary_table_reshaped)
+```
 
@@
   mutate(Time_point = str_replace(Time_point_raw, "phq.diff_score_", "")) %>%
-  select(-Time_point_raw) %>%
-  drop_na(phq.diff_score)
+  select(-Time_point_raw)
 
@@
 
-```{r}
+makes this into percentages
+```{r phq absolut plot}
+dat.long.phq.diff %>%
+  ggplot(mapping = aes(y = phq.diff_score)) +
+  geom_bar() +
+  theme_minimal() +
+  facet_wrap(facets = vars(Time_point))
+```
+
+```{r phq percentage plot prepan_retro}
 dat.long.phq.diff %>%
@@
   ) +
-  theme_minimal()
+  labs(
+    x = "Difference phq7 score",
+    y = "Percentage of participants",
+    fill = "Comparison:\nBaseline vs") +
+  theme_personal +
+  scale_fill_manual(values = palette, labels = c("Prepandemic", "Retrospective"))
 ```
 
-```{r}
+```{r phq plot prepan_retro diff}
 dat.long.phq.diff %>%
@@
   ) +
-  theme_minimal()
+  labs(
+    x = "Difference phq7 score",
+    y = "Percentage of participants",
+    fill = "Comparison:\nPrepandemic vs") +
+  theme_personal +
+  scale_fill_manual(values = palette, labels = c("Retrospective"))
 ```
 
-```{r gather to long format Time_points}
+## ocir
+
+```{r descriptives ocir.diff_score_cols}
+ocir.numeric_table <- dat %>% 
+  #  group_by(dem.sex) %>%
+  summarise_at( 
+    vars(
+      "Base - prepan" = ocir.diff_score_base_prepan,
+      "Base - retro" = ocir.diff_score_base_retro,
+      "Prepan - retro" = ocir.diff_score_prepan_retro,
+    ),
+    .funs =
+      list(
+        ~mean(., na.rm = T),
+        ~sd(., na.rm = T),
+        ~median(., na.rm = T),
+        ~min(., na.rm = T),
+        ~max(., na.rm = T),
+        ~skew(., na.rm = T),
+        kurtosis = ~kurtosi(., na.rm = T)
+      )
+  )
+
+ocir.numeric_table
+```
+
+```{r smart numeric summary tables}
+# reshape the table
+ocir.numeric_summary_table_reshaped <- ocir.numeric_table %>% 
+  gather(key, value) %>% 
+  separate(key, c("variable", "measure"), sep = "_") %>%
+  mutate(measure = factor(
+    x = measure,
+    levels =  c( # this is the order I want my columns to appear in
+      "missing",
+      "min",
+      "max",
+      "mean", 
+      "median", 
+      "mode",
+      "sd",
+      "skew",
+      "kurtosis"
+    ))) %>% 
+  spread(measure, value) %>% 
+  # we can apply a function to all variables to edit them so that they are publication ready
+  rename_all(
+    .funs = ~str_to_title(.)
+  ) %>% 
+  # or we can individually rename variables 
+  rename(
+    SD = Sd
+  )
+
+ocir.numeric_summary_table_reshaped
+```
+
+Table for knitting
+ocir diff summary table
+```{r ocir diff summary table}
+kable(ocir.numeric_summary_table_reshaped)
+```
+
+```{r ocir gather to long format Time_points}
 dat.long.ocir.diff <- dat %>%
@@
 
-```{r}
+makes this into percentages
+```{r ocir absolut plot}
 dat.long.ocir.diff %>%
@@
 ```
+
+```{r ocir percentage plot prepan_retro}
+dat.long.ocir.diff %>%
+  filter(Time_point != "prepan_retro") %>%
+  ggplot(mapping = aes(
+    x = ocir.diff_score,
+    y = stat(density*width),
+    fill = Time_point)) +
+  geom_histogram(
+    binwidth = 1,
+    position = position_dodge2(preserve = "single")
+  ) +
+  labs(
+    x = "Difference ocir7 score",
+    y = "Percentage of participants",
+    fill = "Comparison:\nBaseline vs") +
+  theme_personal +
+  scale_fill_manual(values = palette, labels = c("Prepandemic", "Retrospective"))
+```
+
+```{r ocir plot prepan_retro diff}
+dat.long.ocir.diff %>%
+  filter(Time_point == "prepan_retro") %>%
+  ggplot(mapping = aes(
+    x = ocir.diff_score,
+    y = stat(density*width),
+    fill = Time_point)) +
+  geom_histogram(
+    binwidth = 1,
+    position = position_dodge2(preserve = "single")
+  ) +
+  labs(
+    x = "Difference ocir7 score",
+    y = "Percentage of participants",
+    fill = "Comparison:\nPrepandemic vs") +
+  theme_personal +
+  scale_fill_manual(values = palette, labels = c("Retrospective"))
+```
+
++++ Everything underneath here is only SCRATCH
 

### 2020-08-20 PANCHANGE_data_preprocessing2020-07-15.Rmd
corrected OCIR diff score

@@
   mutate(
-    ocir.diff_score_prepan_base =
+    ocir.diff_score_base_prepan =
       as.numeric(
-        ocir.sum_score_prepan - ocir.sum_score_base  # prepandemic sum score MINUS baseline sum score 
+        ocir.sum_score_base - ocir.sum_score_prepan   # prepandemic sum score MINUS baseline sum score 
       )

### 2020-08-20 PANCHANGE_analysis.Rmd
hierarchy

@@
 #install.packages("psych")
-#install.packages("eeptools")
+#install.packages("broom")
 #install.packages("skimr")
-```
-
-Install packages
-```{r}
-#install.packages("infer")
 ```
@@
 library(psych)
-library(infer)
 library(patchwork)
@@
     )
+```
+
+# Psychiatric disorder hierarchy
+```{r}
+dat %>%
+  mutate(
+    Disorder_exclusive_numeric =
+      case_when(
+        control_numeric == 1 ~ 0 
+        depressive_disorders_numeric = "Depressive disorders",
+        anxiety_disorders_numeric = "Anxiety disorders",
+        mhd.posttraumatic_stress_disorder_ptsd_numeric = "PTSD",
+        eating_disorders_numeric = "Eating disorders",
+        obsessive_compulsive_disorders_numeric = "OCDs",
+        mhd.attention_deficit_hyperactivity_disorder_numeric = "ADHD",
+        mhd.personality_disorder_numeric == 1 ~ 7,
+        mhd.autism_aspergers_or_autistic_spectrum_disorder_numeric == 1 ~ 8,
+        mhd.mania_hypomania_bipolar_or_manicdepression_numeric == 1 ~ 9,
+        psychotic_disorders_numeric == 1 ~ 10,
+           ))
+
+      )
+  )
+
+dat %>%
+  mutate(
+    Disorder_exclusive =
+      recode_factor(
+        Disorder_exclusive,
+        "0" = "Controls",
+        "4" = 
+        "5" = "OCDs"
+        "6" = "ADHD"
+        "7" = "Personality disorders"
+        "8" = "Autism",
+        "9" = "Bipolar disorders",
+        "10" = "Psychotic disorders"
+      )
+  )
+
 ```

### 2020-08-20 PANCHANGE_data_preprocessing2020-07-15.Rmd

@@
   mutate(
-    phq.diff_score_prepan_retro =
+    phq.diff_score_retro_prepan =
       as.numeric(
-        phq.sum_score_prepan - phq.sum_score_retro  # retrospective sum score MINUS prepandemic sum score 
+        phq.sum_score_retro - phq.sum_score_prepan  # retrospective sum score MINUS prepandemic sum score 
       )
@@
   mutate(
-    gad.diff_score_prepan_retro =
+    gad.diff_score_retro_prepan =
       as.numeric(
-        gad.sum_score_prepan - gad.sum_score_retro  # retrospective sum score MINUS prepandemic sum score 
+        gad.sum_score_retro - gad.sum_score_prepan  # retrospective sum score MINUS prepandemic sum score 
       )
@@
   mutate(
-    ocir.diff_score_prepan_retro =
+    ocir.diff_score_retro_prepan =
       as.numeric(
-        ocir.sum_score_prepan - ocir.sum_score_retro  # retrospective sum score MINUS prepandemic sum score 
+        ocir.sum_score_retro - ocir.sum_score_prepan  # retrospective sum score MINUS prepandemic sum score 
       )

### 2020-08-20 PANCHANGE_analysis.Rmd
pcl summary

--- 2020-08-20 PANCHANGE_analysis.Rmd
@@
 
+# Psychiatric disorder hierarchy
+
+control_numeric == 1 ~ 0,
+depressive_disorders_numeric == 1 ~ 1,
+anxiety_disorders_numeric == 1 ~ 2,
+mhd.posttraumatic_stress_disorder_ptsd_numeric == 1 ~ 3,
+eating_disorders_numeric == 1 ~ 4,
+obsessive_compulsive_disorders_numeric == 1 ~ 5,
+mhd.attention_deficit_hyperactivity_disorder_numeric == 1 ~ 6,
+mhd.personality_disorder_numeric == 1 ~ 7,
+mhd.autism_aspergers_or_autistic_spectrum_disorder_numeric == 1 ~ 8,
+mhd.mania_hypomania_bipolar_or_manicdepression_numeric == 1 ~ 9,
+psychotic_disorders_numeric == 1 ~ 10
+
+psychotic_disorders_numeric == 1 ~ 10
+mhd.mania_hypomania_bipolar_or_manicdepression_numeric == 1 ~ 9,
+mhd.autism_aspergers_or_autistic_spectrum_disorder_numeric == 1 ~ 8,
+mhd.personality_disorder_numeric == 1 ~ 7,
+mhd.attention_deficit_hyperactivity_disorder_numeric == 1 ~ 6,
+obsessive_compulsive_disorders_numeric == 1 ~ 5,
+eating_disorders_numeric == 1 ~ 4,
+mhd.posttraumatic_stress_disorder_ptsd_numeric == 1 ~ 3,
+anxiety_disorders_numeric == 1 ~ 2,
+depressive_disorders_numeric == 1 ~ 1,
+control_numeric == 1 ~ 0,
+
+```{r Psychiatric disorders hierarchy}
+dat <- dat %>%
+  mutate(
+    Disorder_numeric =
+      case_when(
+        psychotic_disorders_numeric == 1 ~ 11,
+        mhd.mania_hypomania_bipolar_or_manicdepression_numeric == 1 ~ 10,
+        mhd.autism_aspergers_or_autistic_spectrum_disorder_numeric == 1 ~ 9,
+        mhd.personality_disorder_numeric == 1 ~ 8,
+        mhd.attention_deficit_hyperactivity_disorder_numeric == 1 ~ 7,
+        obsessive_compulsive_disorders_numeric == 1 ~ 6,
+        eating_disorders_numeric == 1 ~ 5,
+        mhd.posttraumatic_stress_disorder_ptsd_numeric == 1 ~ 4,
+        (anxiety_disorders_numeric == 1 &
+        depressive_disorders_numeric == 1) ~ 3,
+        anxiety_disorders_numeric == 1 ~ 2,
+        depressive_disorders_numeric == 1 ~ 1,
+        control_numeric == 1 ~ 0
+      )
+  )
+
+dat <- dat %>%
+  mutate(
+    Disorder =
+      recode_factor(
+        Disorder_numeric,
+        `0` = "Controls",
+        `1` = "Depressive disorders",
+        `2` = "Anxiety disorders",
+        `3` = "Depressive & anxiety disorders",
+        `4` = "PTSD",
+        `5` = "Eating disorders",
+        `6` = "OCDs",
+        `7` = "ADHD",
+        `8` = "Personality disorders",
+        `9` = "Autism",
+        `10` = "Bipolar disorders",
+        `11` = "Psychotic disorders"
+      )
+  )
+
+dat %>%
+  freq(Disorder)
+```
+
+```{r}
+dat %>%
+  filter(is.na(Disorder)) %>%
+  freq(Sample)
+```
+
 # Age
@@
   gather(
-    key = "Disorder_raw",
+    key = "Disorder_inc_raw",
     value = "Diagnosis",
@@
     all_of(diff_score_cols),
-    Disorder_raw,
+    Disorder_inc_raw,
     Diagnosis
   ) %>%
-  mutate(Disorder =
+  mutate(Disorder_inc =
            recode_factor(
-             Disorder_raw,
+             Disorder_inc_raw,
              anxiety_disorders_numeric = "Anxiety disorders",
@@
 
-```{r Disorder by Gender}
+```{r Disorder_inc by Gender}
 Disorder_by_Gender <- dat.long.psych %>%
   filter(Diagnosis == 1) %>%
-  count(Disorder, Gender) %>%
+  count(Disorder_inc, Gender) %>%
   mutate(Prop = round(n/sum(n), 2))
 
-Disorder_by_Gender
-```
-
-```{r Disorder by Gender}
-Disorder_by_Gender <- dat.long.psych %>%
-  group_by(Disorder) %>%
+Disorder_inc_by_Gender
+```
+
+```{r Disorder_inc by Gender}
+Disorder_inc_by_Gender <- dat.long.psych %>%
+  group_by(Disorder_inc) %>%
   filter(Diagnosis == 1) %>%
@@
 
-Disorder_by_Gender
-```
-
-```{r Disorder by Gender plot}
-Disorder_by_Gender %>%
+Disorder_inc_by_Gender
+```
+
+```{r Disorder_inc by Gender plot}
+Disorder_inc_by_Gender %>%
   ggplot(mapping = aes(
-    x = Disorder,
+    x = Disorder_inc,
     y = n)
@@
   labs(
-    x = "Disorder",
+    x = "Disorders",
     y = "Number of participants",
@@
 
-```{r Disorder by Sample}
-Disorder_by_Sample <- dat.long.psych %>%
+```{r Disorder_inc by Sample}
+Disorder_inc_by_Sample <- dat.long.psych %>%
   filter(Diagnosis == 1) %>%
-  group_by(Disorder, Sample) %>%
-  count(Disorder)
-```
-
-```{r Disorder by Sample plot}
-Disorder_by_Sample %>%
+  count(Disorder_inc, Sample)
+```
+
+```{r Disorder_inc by Sample plot}
+Disorder_inc_by_Sample %>%
   ggplot(mapping = aes(
-    x = Disorder,
+    x = Disorder_inc,
     y = n)
@@
 Arab
-```{r Disorder by Ethnicity}
-Disorder_by_Ethnicity <- dat.long.psych %>%
+```{r Disorder_inc by Ethnicity}
+Disorder_inc_by_Ethnicity <- dat.long.psych %>%
   filter(Diagnosis == 1) %>%
-  count(Disorder, Ethnicity) %>%
+  count(Disorder_inc, Ethnicity) %>%
   mutate(Prop = round(n/sum(n), 2))
 
-Disorder_by_Ethnicity
-```
-
-```{r Disorder by Ethnicity plot}
-Disorder_by_Ethnicity %>%
+Disorder_inc_by_Ethnicity
+```
+
+```{r Disorder_inc by Ethnicity plot}
+Disorder_inc_by_Ethnicity %>%
   ggplot(mapping = aes(
-    x = Disorder,
+    x = Disorder_inc,
     y = n)
@@
 
-```{r}
+```{r RUBBISH 1}
 gad.diff_score_prepan_base_plot <- dat %>%
@@
 
-```{r fig.height=5, fig.width=5}
+```{r RUBBISH 2 fig.height=5, fig.width=5}
 gad.diff_score_prepan_base_plot /
@@
 
-```{r}
-dat.long %>%
-  filter(Diagnosis == 1) %>%
-  group_by(Disorder) %>%
-  summarise(
-    gad_base_retro = mean(gad.diff_score_base_retro, na.rm = T),
-    gad_prepan_retro = mean(gad.diff_score_prepan_retro, na.rm = T),
-    gad_prepan_base = mean(gad.diff_score_prepan_base, na.rm = T),
-    phq_base_retro = mean(phq.diff_score_base_retro, na.rm = T),
-    phq_prepan_retro = mean(phq.diff_score_prepan_retro, na.rm = T),
-    phq_prepan_base = mean(phq.diff_score_prepan_base, na.rm = T),
-    ocir_base_retro = mean(ocir.diff_score_base_retro, na.rm = T),
-    ocir_prepan_retro = mean(ocir.diff_score_prepan_retro, na.rm = T),
-    ocir_prepan_base = mean(ocir.diff_score_prepan_base, na.rm = T)
-    )
+```{r RUBBISH }
+#ADD
 ```
@@
 model0 <- lm(
-  formula = gad.diff_score_base_retro ~ Disorder,
-  data = dat.long)
+  formula = gad.diff_score_prepan_retro ~ Disorder,
+  data = dat)
 
@@
 tidy(model0)
-```
-
-```{r}
-model1 <- lm(
-  formula = gad.diff_score_base_retro ~ time_diff_sign_up_coping,
-  data = dat)
-
-summary(model1)
 ```
@@
 model1 <- lm(
-  formula = gad.diff_score_base_retro ~ Gender + Age + Ethnicity + time_diff_sign_up_coping + Sample,
+  formula = gad.diff_score_base_retro ~ Disorder + Gender + Age + Ethnicity + time_diff_sign_up_coping,
   data = dat)
@@
 summary(model1)
-```
-
-Re-calculate change
-```{r}
-
-```
-
-Re-rank the change again
-```{r}
-
 ```
@@
 Calculate the total GLAD, COPING, RAMP baseline 
-```{r}
-
+## pcl
+
+```{r descriptives pcl.diff_score_cols}
+pcl.numeric_table <- dat %>% 
+#    group_by(Sample) %>%
+  summarise_at( 
+    vars(
+      "Base - prepan" = pcl.diff_score_base_prepan
+    ),
+    .funs =
+      list(
+        ~mean(., na.rm = T),
+        ~sd(., na.rm = T),
+        ~median(., na.rm = T),
+        ~min(., na.rm = T),
+        ~max(., na.rm = T),
+        ~skew(., na.rm = T),
+        kurtosis = ~kurtosi(., na.rm = T)
+      )
+  )
+
+pcl.numeric_table
+```
+
+```{r smart numeric summary tables}
+# reshape the table
+pcl.numeric_summary_table_reshaped <- pcl.numeric_table %>% 
+  gather(key, value) %>% 
+  separate(key, c("variable", "measure"), sep = "_") %>%
+  mutate(measure = factor(
+    x = measure,
+    levels =  c( # this is the order I want my columns to appear in
+      "missing",
+      "min",
+      "max",
+      "mean", 
+      "median", 
+      "mode",
+      "sd",
+      "skew",
+      "kurtosis"
+    ))) %>% 
+  spread(measure, value) %>% 
+  # we can apply a function to all variables to edit them so that they are publication ready
+  rename_all(
+    .funs = ~str_to_title(.)
+  ) %>% 
+  # or we can individually rename variables 
+  rename(
+    SD = Sd
+  )
+
+pcl.numeric_summary_table_reshaped
+```
+
+Table for knitting
+pcl diff summary table
+```{r pcl diff summary table}
+kable(pcl.numeric_summary_table_reshaped)
+```
+
+```{r descriptives pcl.diff_score_cols}
+pcl.numeric_table <- dat %>% 
+#    group_by(Sample) %>%
+  summarise_at( 
+    vars(
+      "Prepan" = pcl.sum_score_prepan,
+      "Base" = pcl.sum_score_base
+    ),
+    .funs =
+      list(
+        ~mean(., na.rm = T),
+        ~sd(., na.rm = T),
+        ~median(., na.rm = T),
+        ~min(., na.rm = T),
+        ~max(., na.rm = T),
+        ~skew(., na.rm = T),
+        kurtosis = ~kurtosi(., na.rm = T)
+      )
+  )
+
+pcl.numeric_table
+```
+
+```{r smart numeric summary tables}
+# reshape the table
+pcl.numeric_summary_table_reshaped <- pcl.numeric_table %>% 
+  gather(key, value) %>% 
+  separate(key, c("variable", "measure"), sep = "_") %>%
+  mutate(measure = factor(
+    x = measure,
+    levels =  c( # this is the order I want my columns to appear in
+      "missing",
+      "min",
+      "max",
+      "mean", 
+      "median", 
+      "mode",
+      "sd",
+      "skew",
+      "kurtosis"
+    ))) %>% 
+  spread(measure, value) %>% 
+  # we can apply a function to all variables to edit them so that they are publication ready
+  rename_all(
+    .funs = ~str_to_title(.)
+  ) %>% 
+  # or we can individually rename variables 
+  rename(
+    SD = Sd
+  )
+
+pcl.numeric_summary_table_reshaped
+```
+
+Table for knitting
+pcl diff summary table
+```{r pcl diff summary table}
+kable(pcl.numeric_summary_table_reshaped)
 ```

### 2020-08-20 PANCHANGE_data_preprocessing2020-07-15.Rmd
corrected OCIR prepan total score

@@
 
-## gad (prepan)
+## GAD (prepan)
 
@@
 
-# Calulate total score
+# Calculate total score
 gad.scored_items_prepan <- scoreItems(keys = gad.items_key_prepan,
@@
 
-## pcl (prepan)
+## PCL (prepan)
 
@@
 
-# Calulate total score
+# Calculate total score
 pcl.scored_items_prepan <- scoreItems(keys = pcl.items_key_prepan,
@@
 
-## phq (prepan)
+## PHQ (prepan)
 
@@
 
-# Calulate sum score
+# Calculate sum score
 phq.scored_items_prepan <- scoreItems(keys = phq.items_key_prepan,
@@
 
-## ocir (prepan)
+## OCIR (prepan)
 
@@
 
-# Calulate sum score
+# Calculate sum score
 ocir.scored_items_prepan <- scoreItems(keys = ocir.items_key_prepan,
@@
                                         max = 4)
+
 # Add in column to tibble
-prepan.ocir.raw.id$ocir.sum_score_prepan <- ocir.scored_items_prepan$scores
+prepan.ocir.raw.id$ocir.sum_score_prepan_raw <- ocir.scored_items_prepan$scores
 
@@
 prepan.ocir.raw.id %>%
-  descr(ocir.sum_score_prepan,
+  descr(ocir.sum_score_prepan_raw,
         stats = "common"
@@
        cumul = F)
+}
+```
+
+```{r ocir prepan sum score if missigng items set to NA - all items}
+if(GLAD == TRUE | EDGI == TRUE) {
+prepan.ocir.raw.id <- prepan.ocir.raw.id %>%
+  mutate(
+    ocir.sum_score_prepan =
+      if_else(condition = na_per_person_ocir_prepan > 0,
+              true = NA_real_,
+              false = ocir.sum_score_prepan_raw,
+              missing = NA_real_
+      )
+  )
+
+prepan.ocir.raw.id %>%
+  descr(ocir.sum_score_prepan_raw, stats = "common")
+
+prepan.ocir.raw.id %>%
+  descr(ocir.sum_score_prepan, stats = "common")
 }
@@
 
-# Calulate total score
+# Calculate total score
 gad.scored_items_retro <- scoreItems(keys = gad.items_key_retro,
@@
 
-# Calulate total score
+# Calculate total score
 gad.scored_items_base <- scoreItems(keys = gad.items_key_base,
@@
 
-# Calulate total score
+# Calculate total score
 pcl.scored_items_retro <- scoreItems(keys = pcl.items_key_retro,
@@
 
-# Calulate total score
+# Calculate total score
 pcl.scored_items_base <- scoreItems(keys = pcl.items_key_base,
@@
 
-# Calulate total score
+# Calculate total score
 phq.scored_items_retro <- scoreItems(keys = phq.items_key_retro,
@@
 
-# Calulate total score
+# Calculate total score
 phq.scored_items_base <- scoreItems(keys = phq.items_key_base,
@@
 
-# Calulate total score
+# Calculate total score
 ocir.scored_items_retro <- scoreItems(keys = ocir.items_key_retro,
@@
 
-# Calulate total score
+# Calculate total score
 ocir.scored_items_base <- scoreItems(keys = ocir.items_key_base,

### 2020-08-20 PANCHANGE_analysis.Rmd
sum scores for pcl, gad, phq, and ocir

@@
 
+### Summary scores
+```{r descriptives gad.diff_score_cols}
+gad.sum_score_numeric_table <- dat %>% 
+  #    group_by(Sample) %>%
+  summarise_at( 
+    vars(
+      "Prepan" = gad.sum_score_prepan,
+      "Base" = gad.sum_score_base,
+      "Retro" = gad.sum_score_retro
+    ),
+    .funs =
+      list(
+        ~mean(., na.rm = T),
+        ~sd(., na.rm = T),
+        ~median(., na.rm = T),
+        ~min(., na.rm = T),
+        ~max(., na.rm = T),
+        ~skew(., na.rm = T),
+        kurtosis = ~kurtosi(., na.rm = T)
+      )
+  )
+
+gad.sum_score_numeric_table
+```
+
+```{r smart numeric summary tables}
+# reshape the table
+gad.sum_score_numeric_summary_table_reshaped <- gad.sum_score_numeric_table %>% 
+  gather(key, value) %>% 
+  separate(key, c("variable", "measure"), sep = "_") %>%
+  mutate(measure = factor(
+    x = measure,
+    levels =  c( # this is the order I want my columns to appear in
+      "missing",
+      "min",
+      "max",
+      "mean", 
+      "median", 
+      "mode",
+      "sd",
+      "skew",
+      "kurtosis"
+    ))) %>% 
+  spread(measure, value) %>% 
+  # we can apply a function to all variables to edit them so that they are publication ready
+  rename_all(
+    .funs = ~str_to_title(.)
+  ) %>% 
+  # or we can individually rename variables 
+  rename(
+    SD = Sd
+  )
+
+gad.sum_score_numeric_summary_table_reshaped
+```
+
+Table for knitting
+gad diff summary table
+```{r gad diff summary table}
+kable(gad.sum_score_numeric_summary_table_reshaped)
+```
+
+### Differences scores
+
 ```{r descriptives gad.diff_score_cols}
@@
 
+### Long format
+
 ```{r gad gather to long format Time_points}
@@
 
+### Plots
+
 makes this into percentages
@@
 
+### Summary scores
+```{r descriptives phq.diff_score_cols}
+phq.sum_score_numeric_table <- dat %>% 
+  #    group_by(Sample) %>%
+  summarise_at( 
+    vars(
+      "Prepan" = phq.sum_score_prepan,
+      "Base" = phq.sum_score_base,
+      "Retro" = phq.sum_score_retro
+    ),
+    .funs =
+      list(
+        ~mean(., na.rm = T),
+        ~sd(., na.rm = T),
+        ~median(., na.rm = T),
+        ~min(., na.rm = T),
+        ~max(., na.rm = T),
+        ~skew(., na.rm = T),
+        kurtosis = ~kurtosi(., na.rm = T)
+      )
+  )
+
+phq.sum_score_numeric_table
+```
+
+```{r smart numeric summary tables}
+# reshape the table
+phq.sum_score_numeric_summary_table_reshaped <- phq.sum_score_numeric_table %>% 
+  gather(key, value) %>% 
+  separate(key, c("variable", "measure"), sep = "_") %>%
+  mutate(measure = factor(
+    x = measure,
+    levels =  c( # this is the order I want my columns to appear in
+      "missing",
+      "min",
+      "max",
+      "mean", 
+      "median", 
+      "mode",
+      "sd",
+      "skew",
+      "kurtosis"
+    ))) %>% 
+  spread(measure, value) %>% 
+  # we can apply a function to all variables to edit them so that they are publication ready
+  rename_all(
+    .funs = ~str_to_title(.)
+  ) %>% 
+  # or we can individually rename variables 
+  rename(
+    SD = Sd
+  )
+
+phq.sum_score_numeric_summary_table_reshaped
+```
+
+Table for knitting
+phq diff summary table
+```{r phq diff summary table}
+kable(phq.sum_score_numeric_summary_table_reshaped)
+```
+
+### Differences score
+
 ```{r descriptives phq.diff_score_cols}
@@
       "Base - retro" = phq.diff_score_base_retro,
-      "Prepan - retro" = phq.diff_score_prepan_retro,
+      "Prepan - retro" = phq.diff_score_prepan_retro
     ),
@@
 
+### Long format
+
 ```{r phq gather to long format Time_points}
@@
 ## ocir
+
+### Summary scores
+```{r descriptives ocir.diff_score_cols}
+ocir.sum_score_numeric_table <- dat %>% 
+  #    group_by(Sample) %>%
+  summarise_at( 
+    vars(
+      "Prepan" = ocir.sum_score_prepan,
+      "Base" = ocir.sum_score_base,
+      "Retro" = ocir.sum_score_retro
+    ),
+    .funs =
+      list(
+        ~mean(., na.rm = T),
+        ~sd(., na.rm = T),
+        ~median(., na.rm = T),
+        ~min(., na.rm = T),
+        ~max(., na.rm = T),
+        ~skew(., na.rm = T),
+        kurtosis = ~kurtosi(., na.rm = T)
+      )
+  )
+
+ocir.sum_score_numeric_table
+```
+
+```{r smart numeric summary tables}
+# reshape the table
+ocir.sum_score_numeric_summary_table_reshaped <- ocir.sum_score_numeric_table %>% 
+  gather(key, value) %>% 
+  separate(key, c("variable", "measure"), sep = "_") %>%
+  mutate(measure = factor(
+    x = measure,
+    levels =  c( # this is the order I want my columns to appear in
+      "missing",
+      "min",
+      "max",
+      "mean", 
+      "median", 
+      "mode",
+      "sd",
+      "skew",
+      "kurtosis"
+    ))) %>% 
+  spread(measure, value) %>% 
+  # we can apply a function to all variables to edit them so that they are publication ready
+  rename_all(
+    .funs = ~str_to_title(.)
+  ) %>% 
+  # or we can individually rename variables 
+  rename(
+    SD = Sd
+  )
+
+ocir.sum_score_numeric_summary_table_reshaped
+```
+
+Table for knitting
+ocir diff summary table
+```{r ocir diff summary table}
+kable(ocir.sum_score_numeric_summary_table_reshaped)
+```
+
+### Differences scores
 
@@
 
+### Long format
+
 ```{r ocir gather to long format Time_points}
@@
 ```
+
+# RUBBISH
 
@@
 ```{r descriptives pcl.diff_score_cols}
-pcl.numeric_table <- dat %>% 
+pcl.sum_score_numeric_table <- dat %>% 
 #    group_by(Sample) %>%
@@
 # reshape the table
-pcl.numeric_summary_table_reshaped <- pcl.numeric_table %>% 
+pcl.sum_score_numeric_summary_table_reshaped <- pcl.sum_score_numeric_table %>% 
   gather(key, value) %>% 
@@
 
-pcl.numeric_summary_table_reshaped
+pcl.sum_score_numeric_summary_table_reshaped
 ```
@@
 ```{r pcl diff summary table}
-kable(pcl.numeric_summary_table_reshaped)
+kable(pcl.sum_score_numeric_summary_table_reshaped)
 ```

### 2020-08-20 PANCHANGE_data_preprocessing2020-07-15.Rmd
corrected PCL retro coding

@@
     pcl.difficulty_concentrating_base = pcl.difficulty_concentrating,
-    pcl.stressful_experience_repeated_images_retro = pcl.stressful_experience_repeated_images.1,
-    pcl.stressful_experience_upset_reminded_retro = pcl.stressful_experience_reminded_upset.1, # differ
-    pcl.stressful_situation_avoiding_activities_retro = pcl.stressful_experience_avoiding_activities.1, # differ
-    pcl.cut_people_feeling_distant_retro = pcl.feeling_distant_cut_people.1, # differ
-    pcl.feeling_irritable_or_having_angry_outbursts_retro = pcl.feeling_irritable_or_having_angry_outbursts.1,
-    pcl.difficulty_concentrating_retro = pcl.difficulty_concentrating.1
+    pcl.stressful_experience_repeated_images_retro_unc = pcl.stressful_experience_repeated_images.1,
+    pcl.stressful_experience_upset_reminded_retro_unc = pcl.stressful_experience_reminded_upset.1, # differ
+    pcl.stressful_situation_avoiding_activities_retro_unc = pcl.stressful_experience_avoiding_activities.1, # differ
+    pcl.cut_people_feeling_distant_retro_unc = pcl.feeling_distant_cut_people.1, # differ
+    pcl.feeling_irritable_or_having_angry_outbursts_retro_unc = pcl.feeling_irritable_or_having_angry_outbursts.1,
+    pcl.difficulty_concentrating_retro_unc = pcl.difficulty_concentrating.1
   ) %>%
@@
 
+Recode RAMP PCL retro scores
+```{r recode ramp pcl retro scores}
+if(RAMP == TRUE) {
+
+pcl_retro_numeric_recode_vars <- c(
+    "pcl.stressful_experience_repeated_images_retro_unc_numeric",
+    "pcl.stressful_experience_upset_reminded_retro_unc_numeric",
+    "pcl.stressful_situation_avoiding_activities_retro_unc_numeric",
+    "pcl.cut_people_feeling_distant_retro_unc_numeric",
+    "pcl.feeling_irritable_or_having_angry_outbursts_retro_unc_numeric",
+    "pcl.difficulty_concentrating_retro_unc_numeric"
+)
+
+#recode and rename numeric retro items
+coping.pcl.raw.id <- coping.pcl.raw.id %>%
+  mutate_at(vars(all_of(pcl_retro_numeric_recode_vars)),
+    ~ recode(.,
+           `1` = 1, # 1 = Yes = 1
+           `2` = 0, # 2 = No = 0
+           `3` = NA_real_ # NA = 3 = NA
+                   )) %>%
+  rename_at(vars(ends_with("_retro_unc_numeric")), 
+            funs(str_replace(., 
+                             "_retro_unc_numeric", 
+                             "_retro_numeric")
+                 )
+            )
+
+pcl_retro_recode_vars <- c(
+    "pcl.stressful_experience_repeated_images_retro_numeric",
+    "pcl.stressful_experience_upset_reminded_retro_numeric",
+    "pcl.stressful_situation_avoiding_activities_retro_numeric",
+    "pcl.cut_people_feeling_distant_retro_numeric",
+    "pcl.feeling_irritable_or_having_angry_outbursts_retro_numeric",
+    "pcl.difficulty_concentrating_retro_numeric"
+)
+
+#create factor versions 
+coping.pcl.raw.id <- coping.pcl.raw.id %>%
+  mutate_at(vars(
+    all_of(pcl_retro_recode_vars)),
+    list("factor" = 
+            ~ recode_factor(.,
+           "1" = "Yes", # 1 = Yes = 1
+           "0" = "No" # 2 = No = 0
+                   ))) %>%
+  rename_at(vars(ends_with( "retro_numeric_factor")), 
+            list(~gsub(
+              pattern = "_retro_numeric_factor",
+              replacement = "_retro",
+              .)
+              )
+            ) %>%
+  select(
+    -ends_with("unc")
+  )
+}
+
+colnames(coping.pcl.raw.id)
+```
+
 ## Sum scores
@@
   )
+
 ```

### 2020-08-20 PANCHANGE_analysis.Rmd

@@
 
-```{r}
+Investigate NAs 
+Ask Leo?
+```{r NAs in diagnosis}
 dat %>%
@@
 ```{r Disorder_inc by Gender}
-Disorder_by_Gender <- dat.long.psych %>%
+Disorder_inc_by_Gender <- dat.long.psych %>%
   filter(Diagnosis == 1) %>%
@@
 
-```{r Disorder_inc by Gender}
+```{r Disorder_inc by Gender prop}
 Disorder_inc_by_Gender <- dat.long.psych %>%
@@
 ```
+
+100% bar per diagnosis with percentages of contribution per sample
 
@@
 
++++CHECK OVERLAP BETWEEN TESTS and probable COVID
+
 # Questionnaire comparions
@@
 ### Summary scores
-```{r descriptives gad.diff_score_cols}
+```{r descriptives gad.sum_score_cols}
 gad.sum_score_numeric_table <- dat %>% 
@@
     Ethnicity,
+    Disorder,
     Time_point_raw,
@@
 
+```{r gad percentage plot prepan_retro}
+dat.long.gad.diff %>%
+  filter(Time_point != "prepan_retro") %>%
+  ggplot(mapping = aes(
+    x = gad.diff_score,
+    y = stat(density*width),
+    fill = Time_point)) +
+  geom_histogram(
+    binwidth = 1,
+    position = position_dodge2(preserve = "single")
+  ) +
+  labs(
+    x = "Difference GAD7 score",
+    y = "Percentage of participants",
+    fill = "Comparison:\nBaseline vs") +
+  theme_personal +
+  scale_fill_manual(values = palette, labels = c("Prepandemic", "Retrospective")) +
+  facet_wrap("Disorder")
+```
+
 ```{r gad plot prepan_retro diff}
@@
 ### Summary scores
-```{r descriptives phq.diff_score_cols}
+```{r descriptives phq.sum_score}
 phq.sum_score_numeric_table <- dat %>% 
@@
 ### Summary scores
-```{r descriptives ocir.diff_score_cols}
+```{r descriptives ocir.sum_score}
 ocir.sum_score_numeric_table <- dat %>% 
@@
 model0 <- lm(
-  formula = gad.diff_score_prepan_retro ~ Disorder,
+  formula = phq.diff_score_base_prepan ~ Disorder,
+  data = dat)
+
+summary(model0)
+```
+
+Model 0: Disorders
+```{r}
+model0 <- lm(
+  formula = gad.diff_score_base_prepan ~ Disorder,
   data = dat)
@@
 model1 <- lm(
-  formula = gad.diff_score_base_retro ~ Disorder + Gender + Age + Ethnicity + time_diff_sign_up_coping,
+  formula = phq.diff_score_base_prepan ~ Disorder + Gender + Age + Ethnicity + time_diff_sign_up_coping,
+  data = dat)
+
+summary(model1)
+```
+
+Model 1: Model 0 + Sex + Age + Ethnicity + Time registration and baseline
+```{r}
+model1 <- lm(
+  formula = gad.diff_score_base_prepan ~ Disorder + Gender + Age + Ethnicity + time_diff_sign_up_coping,
   data = dat)
@@
 
-```{r descriptives pcl.diff_score_cols}
+```{r descriptives pcl.sum_score}
 pcl.sum_score_numeric_table <- dat %>% 

### 2020-08-21 PANCHANGE_data_preprocessing2020-07-15.Rmd
created time difference between start of pandemic and start of coping questionnaire

@@
 
-Calculate the time difference between time difference between sign up questionnaire and COPING questionnaire
+Calculate the time difference between starting the COPING questionnaire and the beginning of the pandemic
+```{r time difference between starting the COP|NG questionnaire and the beginning of the pandemic}
+if(GLAD == TRUE | EDGI == TRUE | RAMP == TRUE | NBR == TRUE){
+# using date of pandemic as 23rd of March
+dat <- dat %>%
+  mutate(
+    time_diff_coping_lockdown_march_23 =
+        as.numeric(
+        difftime(           #this function does time1 - time2 as difftime(time1, time2...)
+          startDate.coping,    #should be start date for COPING (time1)
+          date_uk_lockdown_march_23),    #should be start date for GLAD (time2)
+          units = c("days")  #can also be "secs", "mins", "hours", "weeks"
+          )
+        )
+
+dat %>%
+  descr(
+    var = time_diff_coping_lockdown_march_23,
+    stats = "common"
+    )
+
+# using date as 1st of March  
+dat <- dat %>%
+  mutate(
+    time_diff_coping_awareness_march_1 =
+        as.numeric(
+        difftime(           #this function does time1 - time2 as difftime(time1, time2...)
+          startDate.coping,    #should be start date for COPING (time1)
+          date_higher_awareness_march_1),    #should be start date for GLAD (time2)
+          units = c("days")  #can also be "secs", "mins", "hours", "weeks"
+          )
+        )
+
+dat %>%
+  descr(
+    var = time_diff_coping_awareness_march_1,
+    stats = "common"
+    )
+
+# using date as 31st January
+
+dat <- dat %>%
+  mutate(
+    time_diff_coping_first_case_uk_jan_31 =
+        as.numeric(
+        difftime(           #this function does time1 - time2 as difftime(time1, time2...)
+          startDate.coping,    #should be start date for COPING (time1)
+          date_first_case_uk_january_31),    #should be start date for GLAD (time2)
+          units = c("days")  #can also be "secs", "mins", "hours", "weeks"
+          )
+        )
+
+dat %>%
+  descr(
+    var = time_diff_coping_first_case_uk_jan_31,
+    stats = "common"
+    )
+}
+```
+
+Calculate the time difference between sign up questionnaire and COPING questionnaire
 ```{r time difference between sign up questionnaire and COPING questionnaire}

### 2020-08-24 PANCHANGE_data_preprocessing2020-07-15.Rmd

@@
           startDate.prepandemic),    #should be start date for GLAD (time2)
-          units = c("days")  #can also be "secs", "mins", "hours", "weeks"
+          units = c("weeks")  #can also be "secs", "mins", "hours", "weeks"
           )

### 2020-08-24 PANCHANGE_data_preprocessing2020-07-15.Rmd
changed from days to weeks

--- 2020-08-20 PANCHANGE_data_preprocessing2020-07-15.Rmd
@@
 
-Calculate the time difference between time difference between sign up questionnaire and COPING questionnaire
+Calculate the time difference between starting the COPING questionnaire and the beginning of the pandemic
+```{r time difference between starting the COP|NG questionnaire and the beginning of the pandemic}
+if(GLAD == TRUE | EDGI == TRUE | RAMP == TRUE | NBR == TRUE){
+# using date of pandemic as 23rd of March
+dat <- dat %>%
+  mutate(
+    time_diff_coping_lockdown_march_23 =
+        as.numeric(
+        difftime(           #this function does time1 - time2 as difftime(time1, time2...)
+          startDate.coping,    #should be start date for COPING (time1)
+          date_uk_lockdown_march_23),    #should be start date for GLAD (time2)
+          units = c("weeks")  #can also be "secs", "mins", "hours", "weeks"
+          )
+        )
+
+dat %>%
+  descr(
+    var = time_diff_coping_lockdown_march_23,
+    stats = "common"
+    )
+
+# using date as 1st of March  
+dat <- dat %>%
+  mutate(
+    time_diff_coping_awareness_march_1 =
+        as.numeric(
+        difftime(           #this function does time1 - time2 as difftime(time1, time2...)
+          startDate.coping,    #should be start date for COPING (time1)
+          date_higher_awareness_march_1),    #should be start date for GLAD (time2)
+          units = c("weeks")  #can also be "secs", "mins", "hours", "weeks"
+          )
+        )
+
+dat %>%
+  descr(
+    var = time_diff_coping_awareness_march_1,
+    stats = "common"
+    )
+
+# using date as 31st January
+
+dat <- dat %>%
+  mutate(
+    time_diff_coping_first_case_uk_jan_31 =
+        as.numeric(
+        difftime(           #this function does time1 - time2 as difftime(time1, time2...)
+          startDate.coping,    #should be start date for COPING (time1)
+          date_first_case_uk_january_31),    #should be start date for GLAD (time2)
+          units = c("weeks")  #can also be "secs", "mins", "hours", "weeks"
+          )
+        )
+
+dat %>%
+  descr(
+    var = time_diff_coping_first_case_uk_jan_31,
+    stats = "common"
+    )
+}
+```
+
+Calculate the time difference between sign up questionnaire and COPING questionnaire
 ```{r time difference between sign up questionnaire and COPING questionnaire}

### 2020-08-24 PANCHANGE_data_preprocessing2020-07-15.Rmd
personality disorder fixing

@@
 ```{r coping edgi ocir cleaning}
-exclude_cols_coping_edgi_ocir <- c("COPING_Sample", "COPING_ID")
+exclude_cols_coping_edgi_ocir <- c(
+  "COPING_Sample",
+  "COPING_ID")
 
@@
   ) %>%
+  add_numeric(., exclude = exclude_cols_coping_edgi_ocir) %>%
   add_column(Sample = "EDGI") %>%
-  add_numeric(., exclude = exclude_cols_coping_edgi_ocir) %>%
   mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables

### 2020-08-24 PANCHANGE_analysis.Rmd
added pcl percentages and made changes to the preprocessing script

@@
       "Base - retro" = gad.diff_score_base_retro,
-      "Prepan - retro" = gad.diff_score_prepan_retro,
+      "Prepan - retro" = gad.diff_score_retro_prepan,
     ),
@@
 
-```{r gad percentage plot prepan_retro}
+```{r gad percentage plot retro_prepan}
 dat.long.gad.diff %>%
-  filter(Time_point != "prepan_retro") %>%
+  filter(Time_point != "retro_prepan") %>%
   ggplot(mapping = aes(
@@
 
-```{r gad plot prepan_retro diff}
+```{r gad plot retro_prepan diff}
 dat.long.gad.diff %>%
-  filter(Time_point == "prepan_retro") %>%
+  filter(Time_point == "retro_prepan") %>%
   ggplot(mapping = aes(
@@
       "Base - retro" = phq.diff_score_base_retro,
-      "Prepan - retro" = phq.diff_score_prepan_retro
+      "Prepan - retro" = phq.diff_score_retro_prepan
     ),
@@
 
-```{r phq percentage plot prepan_retro}
+```{r phq percentage plot retro_prepan}
 dat.long.phq.diff %>%
-  filter(Time_point != "prepan_retro") %>%
+  filter(Time_point != "retro_prepan") %>%
   ggplot(mapping = aes(
@@
 
-```{r phq plot prepan_retro diff}
+```{r phq plot retro_prepan diff}
 dat.long.phq.diff %>%
-  filter(Time_point == "prepan_retro") %>%
+  filter(Time_point == "retro_prepan") %>%
   ggplot(mapping = aes(
@@
       "Base - retro" = ocir.diff_score_base_retro,
-      "Prepan - retro" = ocir.diff_score_prepan_retro,
+      "Prepan - retro" = ocir.diff_score_retro_prepan
     ),
@@
 
-```{r ocir percentage plot prepan_retro}
+```{r ocir percentage plot retro_prepan}
 dat.long.ocir.diff %>%
-  filter(Time_point != "prepan_retro") %>%
+  filter(Time_point != "retro_prepan") %>%
   ggplot(mapping = aes(
@@
 
-```{r ocir plot prepan_retro diff}
+```{r ocir plot retro_prepan diff}
 dat.long.ocir.diff %>%
-  filter(Time_point == "prepan_retro") %>%
+  filter(Time_point == "retro_prepan") %>%
   ggplot(mapping = aes(
@@
 ```{r RUBBISH 1}
-gad.diff_score_prepan_base_plot <- dat %>%
-  ggplot(mapping = aes(y = gad.diff_score_prepan_base)) +
+gad.diff_score_base_prepan_plot <- dat %>%
+  ggplot(mapping = aes(y = gad.diff_score_base_prepan)) +
   geom_bar() +
@@
 
-gad.diff_score_prepan_retro_plot <- dat %>%
-  ggplot(mapping = aes(y = gad.diff_score_prepan_retro)) +
+gad.diff_score_retro_prepan_plot <- dat %>%
+  ggplot(mapping = aes(y = gad.diff_score_retro_prepan)) +
   geom_bar() +
@@
 
-gad.diff_score_prepan_base_plot <- dat %>%
-  ggplot(mapping = aes(y = gad.diff_score_prepan_base)) +
+gad.diff_score_base_retro_plot <- dat %>%
+  ggplot(mapping = aes(y = gad.diff_score_base_retro)) +
   geom_bar() +
@@
 
-```{r RUBBISH 2 fig.height=5, fig.width=5}
-gad.diff_score_prepan_base_plot /
-  gad.diff_score_prepan_retro_plot /
-  gad.diff_score_prepan_base_plot +
+```{r RUBBISH 2 fig.height=7, fig.width=5}
+gad.diff_score_base_prepan_plot /
+  gad.diff_score_retro_prepan_plot /
+  gad.diff_score_base_retro_plot +
   plot_layout(guides = "collect", heights = c(1,1,1)) +
@@
 ```{r}
-
+pcl.retro.items <- c(
+  "pcl.stressful_experience_upset_reminded_retro_numeric",
+  "pcl.stressful_experience_repeated_images_retro_numeric",
+  "pcl.stressful_situation_avoiding_activities_retro_numeric",
+  "pcl.cut_people_feeling_distant_retro_numeric",
+  "pcl.difficulty_concentrating_retro_numeric",
+  "pcl.feeling_irritable_or_having_angry_outbursts_retro_numeric"
+)
+
+pcl.percentages.summary <- dat %>%
+  select(
+    all_of(pcl.retro.items)
+  ) %>%
+  gather(
+    key = "PCL Item",
+    value = "Binary_score",
+    all_of(pcl.retro.items)
+  ) %>%
+  mutate(Binary_score = fct_explicit_na(as.factor(Binary_score), na_level = "Missing")) %>%
+  group_by(`PCL Item`) %>%
+  count(`PCL Item`, Binary_score) %>%
+  mutate(prop = round(n/sum(n), 3)*100) %>%
+  mutate(n_prop = paste0(n," (",prop, "%)"))
+
+pcl.percentages.summary
 ```

### 2020-08-24 PANCHANGE_analysis.Rmd
gad change stratification

@@
 
+### Split sample in improvement and worsening
+```{r gad improvment worsening stratification}
+dat <- dat %>%
+  mutate(gad.change_binary_numeric =
+           case_when(
+             gad.pandemic_felt_feelings_numeric == 1 ~ 1,
+             gad.pandemic_felt_feelings_numeric == 2 ~ 1,
+             gad.pandemic_felt_feelings_numeric == 3 ~ 0,
+             gad.pandemic_felt_feelings_numeric == 4 ~ 2,
+             gad.pandemic_felt_feelings_numeric == 5 ~ 2
+           )
+         )
+
+dat <- dat %>%
+  mutate(gad.change_binary =
+           recode_factor(
+             gad.change_binary_numeric,
+             `1` = "Worsening",
+             `2` = "No change",
+             `3` = "Improvement"
+           )
+         )
+
+dat %>%
+  freq(gad.change_binary)
+```
+
+```{r}
+dat %>%
+  freq(gad.pandemic_felt_feelings_numeric)
+```
+
 ### Summary scores
@@
 present percentages of how say that this is due to the pandemic 
-```{r}
+```{r pcl percentages due to pandemic}
 pcl.retro.items <- c(

### 2020-08-24 PANCHANGE_analysis.Rmd
phq and ocir stratification

@@
 
-```{r}
-dat %>%
-  freq(gad.pandemic_felt_feelings_numeric)
-```
-
 ### Summary scores
@@
 
+### Split sample in improvement and worsening
+```{r phq improvment worsening stratification}
+dat <- dat %>%
+  mutate(phq.change_binary_numeric =
+           case_when(
+             phq.pandemic_felt_feelings_numeric == 1 ~ 1,
+             phq.pandemic_felt_feelings_numeric == 2 ~ 1,
+             phq.pandemic_felt_feelings_numeric == 3 ~ 0,
+             phq.pandemic_felt_feelings_numeric == 4 ~ 2,
+             phq.pandemic_felt_feelings_numeric == 5 ~ 2
+           )
+  )
+
+dat <- dat %>%
+  mutate(phq.change_binary =
+           recode_factor(
+             phq.change_binary_numeric,
+             `1` = "Worsening",
+             `2` = "No change",
+             `3` = "Improvement"
+           )
+  )
+
+dat %>%
+  freq(phq.change_binary)
+```
+
 ### Summary scores
@@
 
+### Split sample in improvement and worsening
+```{r ocir improvment worsening stratification}
+dat <- dat %>%
+  mutate(ocir.change_binary_numeric =
+           case_when(
+             ocir.pandemic_felt_feelings_numeric == 1 ~ 1,
+             ocir.pandemic_felt_feelings_numeric == 2 ~ 1,
+             ocir.pandemic_felt_feelings_numeric == 3 ~ 0,
+             ocir.pandemic_felt_feelings_numeric == 4 ~ 2,
+             ocir.pandemic_felt_feelings_numeric == 5 ~ 2
+           )
+  )
+
+dat <- dat %>%
+  mutate(ocir.change_binary =
+           recode_factor(
+             ocir.change_binary_numeric,
+             `1` = "Worsening",
+             `2` = "No change",
+             `3` = "Improvement"
+           )
+  )
+
+dat %>%
+  freq(ocir.change_binary)
+```
+
 ### Summary scores

### 2020-08-24 PANCHANGE_analysis.Rmd
disorder plot

@@
 gad.sum_score_numeric_table <- dat %>% 
-  #    group_by(Sample) %>%
+  group_by(gad.change_binary) %>%
   summarise_at( 
@@
 gad.sum_score_numeric_summary_table_reshaped <- gad.sum_score_numeric_table %>% 
-  gather(key, value) %>% 
+  gather(key, value, -gad.change_binary) %>% 
+  separate(key, c("variable", "measure"), sep = "_") %>%
+  mutate(measure = factor(
+    x = measure,
+    levels =  c( # this is the order I want my columns to appear in
+      "missing",
+      "min",
+      "max",
+      "mean", 
+      "median", 
+      "mode",
+      "sd",
+      "skew",
+      "kurtosis"
+    ))) %>% 
+  spread(measure, value) %>% 
+  # we can apply a function to all variables to edit them so that they are publication ready
+  rename_all(
+    .funs = ~str_to_title(.)
+  ) %>% 
+  # or we can individually rename variables 
+  rename(
+    Change = Gad.change_binary,
+    SD = Sd
+  )
+
+gad.sum_score_numeric_summary_table_reshaped
+```
+
+Table for knitting
+gad diff summary table
+```{r gad diff summary table}
+kable(gad.sum_score_numeric_summary_table_reshaped)
+```
+
+### Differences scores
+
+```{r descriptives gad.diff_score_cols}
+gad.numeric_table <- dat %>% 
+  group_by(gad.change_binary) %>%
+  summarise_at( 
+    vars(
+      "Base - prepan" = gad.diff_score_base_prepan,
+      "Base - retro" = gad.diff_score_base_retro,
+      "Prepan - retro" = gad.diff_score_retro_prepan
+    ),
+    .funs =
+      list(
+        ~mean(., na.rm = T),
+        ~sd(., na.rm = T),
+        ~median(., na.rm = T),
+        ~min(., na.rm = T),
+        ~max(., na.rm = T),
+        ~skew(., na.rm = T),
+        kurtosis = ~kurtosi(., na.rm = T)
+      )
+  )
+
+gad.numeric_table
+```
+
+```{r smart numeric summary tables}
+# reshape the table
+gad.numeric_summary_table_reshaped <- gad.numeric_table %>% 
+  gather(key, value, -gad.change_binary) %>% 
+  separate(key, c("variable", "measure"), sep = "_") %>%
+  mutate(measure = factor(
+    x = measure,
+    levels =  c( # this is the order I want my columns to appear in
+      "missing",
+      "min",
+      "max",
+      "mean", 
+      "median", 
+      "mode",
+      "sd",
+      "skew",
+      "kurtosis"
+    ))) %>% 
+  spread(measure, value) %>% 
+  # we can apply a function to all variables to edit them so that they are publication ready
+  rename_all(
+    .funs = ~str_to_title(.)
+    ) %>% 
+  # or we can individually rename variables 
+  rename(
+    Change = Gad.change_binary,
+    SD = Sd
+  )
+
+gad.numeric_summary_table_reshaped
+```
+
+Table for knitting
+gad diff summary table
+```{r gad diff summary table}
+kable(gad.numeric_summary_table_reshaped)
+```
+
+### Long format
+
+```{r gad gather to long format Time_points}
+dat.long.gad.diff <- dat %>%
+  gather(
+    key = "Time_point_raw",
+    value = "gad.diff_score",
+    all_of(gad.diff_score_cols)) %>%
+  select(
+    ID,
+    Sample,
+    Gender,
+    Ethnicity,
+    Disorder,
+    Time_point_raw,
+    gad.diff_score
+  ) %>%
+  mutate(Time_point = str_replace(Time_point_raw, "gad.diff_score_", "")) %>%
+  select(-Time_point_raw)
+
+head(dat.long.gad.diff)
+```
+
+### Plots
+
+makes this into percentages
+```{r gad absolut plot}
+dat.long.gad.diff %>%
+  ggplot(mapping = aes(y = gad.diff_score)) +
+  geom_bar() +
+  theme_minimal() +
+  facet_wrap(facets = vars(Time_point))
+```
+
+```{r gad percentage plot retro_prepan}
+dat.long.gad.diff %>%
+  filter(Time_point != "retro_prepan") %>%
+  ggplot(mapping = aes(
+    x = gad.diff_score,
+    y = stat(density*width),
+    fill = Time_point)) +
+  geom_histogram(
+    binwidth = 1,
+    position = position_dodge2(preserve = "single")
+  ) +
+  labs(
+    x = "Difference GAD7 score",
+    y = "Percentage of participants",
+    fill = "Comparison:\nBaseline vs") +
+  theme_personal +
+  scale_fill_manual(values = palette, labels = c("Prepandemic", "Retrospective"))
+```
+
+```{r gad percentage plot retro_prepan, fig.height=6, fig.width=10}
+dat.long.gad.diff %>%
+  filter(Time_point != "retro_prepan") %>%
+  ggplot(mapping = aes(
+    x = gad.diff_score,
+    y = stat(density*width),
+    fill = Time_point)) +
+  geom_histogram(
+    binwidth = 1,
+    position = position_dodge2(preserve = "single")
+  ) +
+  labs(
+    x = "Difference GAD7 score",
+    y = "Percentage of participants",
+    fill = "Comparison:\nBaseline vs") +
+  theme_personal +
+  scale_fill_manual(values = palette, labels = c("Prepandemic", "Retrospective")) +
+  facet_wrap("Disorder")
+```
+
+```{r gad plot retro_prepan diff}
+dat.long.gad.diff %>%
+  filter(Time_point == "retro_prepan") %>%
+  ggplot(mapping = aes(
+    x = gad.diff_score,
+    y = stat(density*width),
+    fill = Time_point)) +
+  geom_histogram(
+    binwidth = 1,
+    position = position_dodge2(preserve = "single")
+  ) +
+  labs(
+    x = "Difference GAD7 score",
+    y = "Percentage of participants",
+    fill = "Comparison:\nPrepandemic vs") +
+  theme_personal +
+  scale_fill_manual(values = palette, labels = c("Retrospective"))
+```
+
+## phq
+
+### Split sample in improvement and worsening
+```{r phq improvment worsening stratification}
+dat <- dat %>%
+  mutate(phq.change_binary_numeric =
+           case_when(
+             phq.pandemic_felt_feelings_numeric == 1 ~ 1,
+             phq.pandemic_felt_feelings_numeric == 2 ~ 1,
+             phq.pandemic_felt_feelings_numeric == 3 ~ 0,
+             phq.pandemic_felt_feelings_numeric == 4 ~ 2,
+             phq.pandemic_felt_feelings_numeric == 5 ~ 2
+           )
+  )
+
+dat <- dat %>%
+  mutate(phq.change_binary =
+           recode_factor(
+             phq.change_binary_numeric,
+             `1` = "Worsening",
+             `2` = "No change",
+             `3` = "Improvement"
+           )
+  )
+
+dat %>%
+  freq(phq.change_binary)
+```
+
+### Summary scores
+```{r descriptives phq.sum_score}
+phq.sum_score_numeric_table <- dat %>% 
+  group_by(phq.change_binary) %>%
+  summarise_at( 
+    vars(
+      "Prepan" = phq.sum_score_prepan,
+      "Base" = phq.sum_score_base,
+      "Retro" = phq.sum_score_retro
+    ),
+    .funs =
+      list(
+        ~mean(., na.rm = T),
+        ~sd(., na.rm = T),
+        ~median(., na.rm = T),
+        ~min(., na.rm = T),
+        ~max(., na.rm = T),
+        ~skew(., na.rm = T),
+        kurtosis = ~kurtosi(., na.rm = T)
+      )
+  )
+
+phq.sum_score_numeric_table
+```
+
+```{r smart numeric summary tables}
+# reshape the table
+phq.sum_score_numeric_summary_table_reshaped <- phq.sum_score_numeric_table %>%
+  gather(key, value, -phq.change_binary) %>% 
   separate(key, c("variable", "measure"), sep = "_") %>%
@@
 
-gad.sum_score_numeric_summary_table_reshaped
+phq.sum_score_numeric_summary_table_reshaped
 ```
@@
 Table for knitting
-gad diff summary table
-```{r gad diff summary table}
-kable(gad.sum_score_numeric_summary_table_reshaped)
-```
-
-### Differences scores
-
-```{r descriptives gad.diff_score_cols}
-gad.numeric_table <- dat %>% 
-#  group_by(dem.sex) %>%
+phq diff summary table
+```{r phq diff summary table}
+kable(phq.sum_score_numeric_summary_table_reshaped)
+```
+
+### Differences score
+
+```{r descriptives phq.diff_score_cols}
+phq.numeric_table <- dat %>% 
+  group_by(phq.change_binary) %>%
   summarise_at( 
     vars(
-      "Base - prepan" = gad.diff_score_base_prepan,
-      "Base - retro" = gad.diff_score_base_retro,
-      "Prepan - retro" = gad.diff_score_retro_prepan,
+      "Base - prepan" = phq.diff_score_base_prepan,
+      "Base - retro" = phq.diff_score_base_retro,
+      "Prepan - retro" = phq.diff_score_retro_prepan
     ),
@@
 
-gad.numeric_table
+phq.numeric_table
 ```
@@
 # reshape the table
-gad.numeric_summary_table_reshaped <- gad.numeric_table %>% 
-  gather(key, value) %>% 
+phq.numeric_summary_table_reshaped <- phq.numeric_table %>% 
+  gather(key, value, -phq.change_binary) %>% 
   separate(key, c("variable", "measure"), sep = "_") %>%
@@
 
-gad.numeric_summary_table_reshaped
-```
-
-Table for knitting
-gad diff summary table
-```{r gad diff summary table}
-kable(gad.numeric_summary_table_reshaped)
-```
-
-### Long format
-
-```{r gad gather to long format Time_points}
-dat.long.gad.diff <- dat %>%
-  gather(
-    key = "Time_point_raw",
-    value = "gad.diff_score",
-    all_of(gad.diff_score_cols)) %>%
-  select(
-    ID,
-    Sample,
-    Gender,
-    Ethnicity,
-    Disorder,
-    Time_point_raw,
-    gad.diff_score
-  ) %>%
-  mutate(Time_point = str_replace(Time_point_raw, "gad.diff_score_", "")) %>%
-  select(-Time_point_raw)
-
-head(dat.long.gad.diff)
-```
-
-### Plots
-
-makes this into percentages
-```{r gad absolut plot}
-dat.long.gad.diff %>%
-  ggplot(mapping = aes(y = gad.diff_score)) +
-  geom_bar() +
-  theme_minimal() +
-  facet_wrap(facets = vars(Time_point))
-```
-
-```{r gad percentage plot retro_prepan}
-dat.long.gad.diff %>%
-  filter(Time_point != "retro_prepan") %>%
-  ggplot(mapping = aes(
-    x = gad.diff_score,
-    y = stat(density*width),
-    fill = Time_point)) +
-  geom_histogram(
-    binwidth = 1,
-    position = position_dodge2(preserve = "single")
-  ) +
-  labs(
-    x = "Difference GAD7 score",
-    y = "Percentage of participants",
-    fill = "Comparison:\nBaseline vs") +
-  theme_personal +
-  scale_fill_manual(values = palette, labels = c("Prepandemic", "Retrospective"))
-```
-
-```{r gad percentage plot retro_prepan}
-dat.long.gad.diff %>%
-  filter(Time_point != "retro_prepan") %>%
-  ggplot(mapping = aes(
-    x = gad.diff_score,
-    y = stat(density*width),
-    fill = Time_point)) +
-  geom_histogram(
-    binwidth = 1,
-    position = position_dodge2(preserve = "single")
-  ) +
-  labs(
-    x = "Difference GAD7 score",
-    y = "Percentage of participants",
-    fill = "Comparison:\nBaseline vs") +
-  theme_personal +
-  scale_fill_manual(values = palette, labels = c("Prepandemic", "Retrospective")) +
-  facet_wrap("Disorder")
-```
-
-```{r gad plot retro_prepan diff}
-dat.long.gad.diff %>%
-  filter(Time_point == "retro_prepan") %>%
-  ggplot(mapping = aes(
-    x = gad.diff_score,
-    y = stat(density*width),
-    fill = Time_point)) +
-  geom_histogram(
-    binwidth = 1,
-    position = position_dodge2(preserve = "single")
-  ) +
-  labs(
-    x = "Difference GAD7 score",
-    y = "Percentage of participants",
-    fill = "Comparison:\nPrepandemic vs") +
-  theme_personal +
-  scale_fill_manual(values = palette, labels = c("Retrospective"))
-```
-
-## phq
-
-### Split sample in improvement and worsening
-```{r phq improvment worsening stratification}
-dat <- dat %>%
-  mutate(phq.change_binary_numeric =
-           case_when(
-             phq.pandemic_felt_feelings_numeric == 1 ~ 1,
-             phq.pandemic_felt_feelings_numeric == 2 ~ 1,
-             phq.pandemic_felt_feelings_numeric == 3 ~ 0,
-             phq.pandemic_felt_feelings_numeric == 4 ~ 2,
-             phq.pandemic_felt_feelings_numeric == 5 ~ 2
-           )
-  )
-
-dat <- dat %>%
-  mutate(phq.change_binary =
-           recode_factor(
-             phq.change_binary_numeric,
-             `1` = "Worsening",
-             `2` = "No change",
-             `3` = "Improvement"
-           )
-  )
-
-dat %>%
-  freq(phq.change_binary)
-```
-
-### Summary scores
-```{r descriptives phq.sum_score}
-phq.sum_score_numeric_table <- dat %>% 
-  #    group_by(Sample) %>%
-  summarise_at( 
-    vars(
-      "Prepan" = phq.sum_score_prepan,
-      "Base" = phq.sum_score_base,
-      "Retro" = phq.sum_score_retro
-    ),
-    .funs =
-      list(
-        ~mean(., na.rm = T),
-        ~sd(., na.rm = T),
-        ~median(., na.rm = T),
-        ~min(., na.rm = T),
-        ~max(., na.rm = T),
-        ~skew(., na.rm = T),
-        kurtosis = ~kurtosi(., na.rm = T)
-      )
-  )
-
-phq.sum_score_numeric_table
-```
-
-```{r smart numeric summary tables}
-# reshape the table
-phq.sum_score_numeric_summary_table_reshaped <- phq.sum_score_numeric_table %>% 
-  gather(key, value) %>% 
-  separate(key, c("variable", "measure"), sep = "_") %>%
-  mutate(measure = factor(
-    x = measure,
-    levels =  c( # this is the order I want my columns to appear in
-      "missing",
-      "min",
-      "max",
-      "mean", 
-      "median", 
-      "mode",
-      "sd",
-      "skew",
-      "kurtosis"
-    ))) %>% 
-  spread(measure, value) %>% 
-  # we can apply a function to all variables to edit them so that they are publication ready
-  rename_all(
-    .funs = ~str_to_title(.)
-  ) %>% 
-  # or we can individually rename variables 
-  rename(
-    SD = Sd
-  )
-
-phq.sum_score_numeric_summary_table_reshaped
-```
-
-Table for knitting
-phq diff summary table
-```{r phq diff summary table}
-kable(phq.sum_score_numeric_summary_table_reshaped)
-```
-
-### Differences score
-
-```{r descriptives phq.diff_score_cols}
-phq.numeric_table <- dat %>% 
-  #  group_by(dem.sex) %>%
-  summarise_at( 
-    vars(
-      "Base - prepan" = phq.diff_score_base_prepan,
-      "Base - retro" = phq.diff_score_base_retro,
-      "Prepan - retro" = phq.diff_score_retro_prepan
-    ),
-    .funs =
-      list(
-        ~mean(., na.rm = T),
-        ~sd(., na.rm = T),
-        ~median(., na.rm = T),
-        ~min(., na.rm = T),
-        ~max(., na.rm = T),
-        ~skew(., na.rm = T),
-        kurtosis = ~kurtosi(., na.rm = T)
-      )
-  )
-
-phq.numeric_table
-```
-
-```{r smart numeric summary tables}
-# reshape the table
-phq.numeric_summary_table_reshaped <- phq.numeric_table %>% 
-  gather(key, value) %>% 
-  separate(key, c("variable", "measure"), sep = "_") %>%
-  mutate(measure = factor(
-    x = measure,
-    levels =  c( # this is the order I want my columns to appear in
-      "missing",
-      "min",
-      "max",
-      "mean", 
-      "median", 
-      "mode",
-      "sd",
-      "skew",
-      "kurtosis"
-    ))) %>% 
-  spread(measure, value) %>% 
-  # we can apply a function to all variables to edit them so that they are publication ready
-  rename_all(
-    .funs = ~str_to_title(.)
-  ) %>% 
-  # or we can individually rename variables 
-  rename(
-    SD = Sd
-  )
-
 phq.numeric_summary_table_reshaped
@@
 
+```{r phq percentage plot retro_prepan, fig.height=6, fig.width=10}
+dat.long.phq.diff %>%
+  filter(Time_point != "retro_prepan") %>%
+  ggplot(mapping = aes(
+    x = phq.diff_score,
+    y = stat(density*width),
+    fill = Time_point)) +
+  geom_histogram(
+    binwidth = 1,
+    position = position_dodge2(preserve = "single")
+  ) +
+  labs(
+    x = "Difference PHQ9 score",
+    y = "Percentage of participants",
+    fill = "Comparison:\nBaseline vs") +
+  theme_personal +
+  scale_fill_manual(values = palette, labels = c("Prepandemic", "Retrospective")) +
+  facet_wrap("Disorder")
+```
+
 ## ocir
@@
            case_when(
-             ocir.pandemic_felt_feelings_numeric == 1 ~ 1,
-             ocir.pandemic_felt_feelings_numeric == 2 ~ 1,
-             ocir.pandemic_felt_feelings_numeric == 3 ~ 0,
-             ocir.pandemic_felt_feelings_numeric == 4 ~ 2,
-             ocir.pandemic_felt_feelings_numeric == 5 ~ 2
+             ocir.felt_pandemic_feelings_numeric == 1 ~ 1,
+             ocir.felt_pandemic_feelings_numeric == 2 ~ 1,
+             ocir.felt_pandemic_feelings_numeric == 3 ~ 0,
+             ocir.felt_pandemic_feelings_numeric == 4 ~ 2,
+             ocir.felt_pandemic_feelings_numeric == 5 ~ 2
            )
@@
 ocir.sum_score_numeric_table <- dat %>% 
-  #    group_by(Sample) %>%
+  group_by(ocir.change_binary) %>%
   summarise_at( 
@@
 ocir.sum_score_numeric_summary_table_reshaped <- ocir.sum_score_numeric_table %>%
+  filter(ocir.change_binary == "Worsening") %>%
+  select(-ocir.change_binary) %>%
   gather(key, value) %>% 
@@
   labs(
-    x = "Difference ocir7 score",
+    x = "Difference OCI-R score",
     y = "Percentage of participants",
@@
   scale_fill_manual(values = palette, labels = c("Retrospective"))
+```
+
+```{r ocir percentage plot retro_prepan, fig.height=6, fig.width=10}
+dat.long.ocir.diff %>%
+  filter(Time_point != "retro_prepan") %>%
+  ggplot(mapping = aes(
+    x = ocir.diff_score,
+    y = stat(density*width),
+    fill = Time_point)) +
+  geom_histogram(
+    binwidth = 1,
+    position = position_dodge2(preserve = "single")
+  ) +
+  labs(
+    x = "Difference OCI-R score",
+    y = "Percentage of participants",
+    fill = "Comparison:\nBaseline vs") +
+  theme_personal +
+  scale_fill_manual(values = palette, labels = c("Prepandemic", "Retrospective")) +
+  facet_wrap("Disorder")
 ```

### 2020-08-24 PANCHANGE_analysis.Rmd
model 0b disorders dummy coded

@@
 
-Model 0: Disorders
+Model 0a: Disorders
 ```{r}
-model0 <- lm(
+model0a <- lm(
   formula = phq.diff_score_base_prepan ~ Disorder,
@@
 
-summary(model0)
+summary(model0a)
+```
+
+Model 0b: Disorders
+```{r}
+model0b <- lm(
+  formula = phq.diff_score_base_prepan ~
+    anxiety_disorders +
+    depressive_disorders +
+    eating_disorders +
+    obsessive_compulsive_disorders +
+    psychotic_disorders +
+    mhd.mania_hypomania_bipolar_or_manicdepression +
+    mhd.posttraumatic_stress_disorder_ptsd +
+    mhd.autism_aspergers_or_autistic_spectrum_disorder +
+    mhd.attention_deficit_hyperactivity_disorder +
+    mhd.personality_disorder,
+  data = dat)
+
+summary(model0b)
 ```

### 2020-08-25 PANCHANGE_analysis.Rmd
added covid positive single and double

@@
   freq(Sample)
+```
+
+# Positive covid test results
+```{r}
+
 ```
@@
 # COVID
+## Recode variable
+```{r gad covid test positive double}
+dat <- dat %>%
+  mutate(gad.covid_test_positive_double_numeric =
+           case_when(
+             (respiratory.throat_swab_test_nose_numeric == 1 &
+               respiratory.results_antibody_test_numeric == 1) ~ 2,
+             respiratory.throat_swab_test_nose_numeric == 1 ~ 1,
+             respiratory.throat_swab_test_nose_numeric == 2 ~ 0,
+             respiratory.results_antibody_test_numeric == 1 ~ 1,
+             respiratory.results_antibody_test_numeric == 2 ~ 0
+           )
+         )
+
+dat <- dat %>%
+  mutate(covid_test_positive_double =
+           recode_factor(
+             gad.covid_test_positive_double_numeric,
+             `0` = "Negative",
+             `1` = "Positive",
+             `2` = "Double positive"
+           )
+         )
+
+dat %>%
+  freq(covid_test_positive_double)
+```
+
+```{r gad covid test positive}
+dat <- dat %>%
+  mutate(gad.covid_test_positive_numeric =
+           case_when(
+             (respiratory.throat_swab_test_nose_numeric == 1 &
+               respiratory.results_antibody_test_numeric == 1) ~ 1, # with two positive test results get coded as positive
+             respiratory.throat_swab_test_nose_numeric == 1 ~ 1,
+             respiratory.throat_swab_test_nose_numeric == 2 ~ 0,
+             respiratory.results_antibody_test_numeric == 1 ~ 1,
+             respiratory.results_antibody_test_numeric == 2 ~ 0
+           )
+         )
+
+dat <- dat %>%
+  mutate(covid_test_positive =
+           recode_factor(
+             gad.covid_test_positive_numeric,
+             `0` = "Negative",
+             `1` = "Positive"
+#             `2` = "Double positive"
+           )
+         )
+
+dat %>%
+  freq(covid_test_positive)
+```
+
 ## COVID swab test positive
@@
   mutate(Prop = round(n/sum(n), 2))
+```
+
+## Cross table probable covid and covid test positive
+```{r}
+dat %>%
 ```

### 2020-08-25 PANCHANGE_analysis.Rmd
added covid probable vs test cross table

@@
 ## Cross table probable covid and covid test positive
-```{r}
-dat %>%
+```{r Cross table probable covid and covid test positive}
+dat %>%
+  count(covid_test_positive, covid_probable_case_incl_screening) %>%
+  spread(key = covid_test_positive, value = n)
 ```
@@
              gad.change_binary_numeric,
+             `0` = "No change",
              `1` = "Worsening",
-             `2` = "No change",
-             `3` = "Improvement"
+             `2` = "Improvement"
            )
@@
              phq.change_binary_numeric,
+             `0` = "No change",
              `1` = "Worsening",
-             `2` = "No change",
-             `3` = "Improvement"
+             `2` = "Improvement"
            )
@@
              ocir.change_binary_numeric,
+             `0` = "No change",
              `1` = "Worsening",
-             `2` = "No change",
-             `3` = "Improvement"
+             `2` = "Improvement"
            )

### 2020-08-25 PANCHANGE_data_preprocessing2020-07-15.Rmd
added pcl percentages and made changes to the preprocessing script
add autism chunk for harmonising

@@
 }
+```
+
+### Autism spectrum disorder
+```{r mhd autism_spectrum_disorder}
+if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE | RAMP == TRUE){
+  mhd.raw.id <- mhd.raw.id %>%
+    mutate(
+      autism_spectrum_disorder_numeric =
+        case_when(
+          mhd.autism_aspergers_or_autistic_spectrum_disorder_numeric == 0 ~ 0,
+          mhd.autism_aspergers_or_autistic_spectrum_disorder_numeric == 1 ~ 1
+        )
+    )
+
+  mhd.raw.id <- mhd.raw.id %>%
+    mutate(
+      autism_spectrum_disorder =
+        recode_factor(
+          autism_spectrum_disorder_numeric,
+          `0` = "No autism spectrum disorder",
+          `1` = "Autism spectrum disorder"
+        )
+    )
+
+  mhd.raw.id %>%
+    freq(autism_spectrum_disorder)
+}
+```
+
+```{r Check psychotic_disorders}
+if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE | RAMP == TRUE) {
+mhd.raw.id %>%
+  select(
+    autism_spectrum_disorder,
+    autism_spectrum_disorder_numeric,
+    mhd.autism_aspergers_or_autistic_spectrum_disorder,
+    mhd.autism_aspergers_or_autistic_spectrum_disorder_numeric
+  )
+}
+```
+
+```{r}
+mhd.raw.id %>%
+  freq(mhd.autism_aspergers_or_autistic_spectrum_disorder)
+
+mhd.raw.id %>%
+  freq(mhd.autism_aspergers_or_autistic_spectrum_disorder_numeric)
+
 ```

### 2020-08-25 PANCHANGE_data_preprocessing2020-07-15.Rmd
re-running pre-processing

@@
     mhd.autism_aspergers_or_autistic_spectrum_disorder_numeric
-  )
-}
-```
-
-```{r}
-mhd.raw.id %>%
-  freq(mhd.autism_aspergers_or_autistic_spectrum_disorder)
-
-mhd.raw.id %>%
-  freq(mhd.autism_aspergers_or_autistic_spectrum_disorder_numeric)
-
+  ) %>%
+    filter(autism_spectrum_disorder == "Autism spectrum disorder")
+}
 ```

### 2020-08-25 PANCHANGE_analysis.Rmd
add autism chunk for harmonising
harmonising age categories with RAMP

@@
 # Exclusion
+
+## COPING
 Filter data frame to exclude participants that never answered COPING
@@
 dim(dat)
+```
+
+```{r}
+dat.raw %>%
+  freq(age_category_full)
+```
+
+## GAD
+```{r}
+dat.gad <- dat.raw %>%
+  drop_na()
+  filter(
+    (data_group_gad == "Baseline and retrospective data" |
+      data_group_gad == "Prepandemic and baseline data" |
+      data_group_gad == "All prepandemic, baseline and retrospective data")
+  )
+
+dim(dat.gad)
 ```
@@
 
-+++CHECK OVERLAP BETWEEN TESTS and probable COVID
-
 # Questionnaire comparions

### 2020-08-25 PANCHANGE_data_preprocessing2020-07-15.Rmd
harmonising age categories with RAMP

@@
           age_category_numeric, 
-          "1" = "16 to 18 years",
-          "2" = "19 to 25 years",
-          "3" = "26 to 35 years",
-          "4" = "36 to 45 years",
-          "5" = "46 to 55 years",
-          "6" = "56 to 65 years",
-          "7" = "66 to 70 years",
-          "8" = "71 to 75 years",
-          "9" = "76 to 80 years",
-          "10" = "81 to 85 years",
-          "11" = "86 to 90 years",
-          "12" = "91 to 100 years",
-          "13" = "Above 100 years"
+          "1" = "16-18",
+          "2" = "19-25",
+          "3" = "26-35",
+          "4" = "36-45",
+          "5" = "46-55",
+          "6" = "56-65",
+          "7" = "66-70",
+          "8" = "71-75",
+          "9" = "76-80",
+          "10" = "81-85",
+          "11" = "86-90",
+          "12" = "91-100",
+          "13" = "100+"
           )

### 2020-08-25 PANCHANGE_analysis.Rmd
ethnicity and gender collapsing

@@
     cumul = F)
+```
+
+```{r}
+dat.raw %>%
+  freq(age_category_full)
+```
+
+# Collapsing categories
+
+## Gender
+```{r Inspect Gender}
+dat.raw %>%
+  freq(Gender)
+
+dat.raw %>%
+  freq(Gender_numeric)
+```
+
+```{r Collapse Gender}
+dat.raw <- dat.raw %>%
+  mutate(Gender_collapsed_numeric =
+           case_when(
+             Gender_numeric == 0 ~ 0,
+             Gender_numeric == 1 ~ 1,
+             Gender_numeric == 2 ~ 2,
+             Gender_numeric == 3 ~ 2
+           )
+         )
+
+dat.raw <- dat.raw %>%
+  mutate(Gender_collapsed =
+           recode_factor(
+             Gender_collapsed_numeric,
+             `0` = "Male",
+             `1` = "Female",
+             `2` = "Non-binary/Self-defined"
+           )
+         )
+
+dat.raw %>%
+  freq(Gender_collapsed)
+```
+
+## Ethnicity
+```{r Inspect Ethnicity}
+dat.raw %>%
+  freq(Ethnicity)
+
+dat.raw %>%
+  freq(Ethnicity_numeric)
+```
+
+```{r Collapse Ethnicity}
+dat.raw <- dat.raw %>%
+  mutate(Ethnicity_collapsed_numeric =
+           case_when(
+             Ethnicity_numeric == 1 ~ 0,
+             Ethnicity_numeric == 2 ~ 1,
+             Ethnicity_numeric == 3 ~ 2,
+             Ethnicity_numeric == 4 ~ 3,
+             Ethnicity_numeric == 5 ~ 3,
+             Ethnicity_numeric == 6 ~ 4
+           )
+  )
+
+dat.raw <- dat.raw %>%
+  mutate(Ethnicity_collapsed =
+           recode_factor(
+             Ethnicity_collapsed_numeric,
+             `0` = "European",
+             `1` = "Mixed or multiple ethnic origins",
+             `2` = "Asian or Asian British",
+             `3` = "African or African British",
+             `4` = "Asian or Asian British"
+           )
+  )
+
+dat.raw %>%
+  freq(Ethnicity_collapsed)
 ```
@@
 ```{r}
-dat.raw %>%
-  freq(age_category_full)
+dat %>%
+  freq(disorders_total_count)
 ```
@@
 dat.gad <- dat.raw %>%
-  drop_na()
+  drop_na(
+  ) %>%
   filter(
@@
   freq(Sample)
-```
-
-# Positive covid test results
-```{r}
-
 ```
@@
 dat <- dat %>%
-  mutate(gad.covid_test_positive_double_numeric =
+  mutate(covid_test_positive_double_numeric =
            case_when(
@@
            recode_factor(
-             gad.covid_test_positive_double_numeric,
+             covid_test_positive_double_numeric,
              `0` = "Negative",

### 2020-08-25 PANCHANGE_analysis.Rmd
vectors with sum scores

@@
     cumul = F)
+```
+
+```{r}
+dat.raw %>%
+  freq(Sample)
 ```
@@
 
-## GAD
-```{r}
-dat.gad <- dat.raw %>%
-  drop_na(
-  ) %>%
-  filter(
-    (data_group_gad == "Baseline and retrospective data" |
-      data_group_gad == "Prepandemic and baseline data" |
-      data_group_gad == "All prepandemic, baseline and retrospective data")
-  )
-
-dim(dat.gad)
+# Vectors for sum_score
+```{r Vectors with sum_score_cols}
+sum_score_cols <- dat %>%
+  select(contains("sum_score")) %>%
+  select(-ends_with("raw")) %>%
+  colnames()
+
+sum_score_cols
+
+phq.sum_score_cols <- dat %>%
+  select(contains("phq")) %>%
+  select(contains("sum_score")) %>% 
+  select(-ends_with("raw")) %>%
+  select(-contains("8items")) %>%
+  colnames()
+
+phq.sum_score_cols
+
+gad.sum_score_cols <- dat %>%
+  select(contains("gad")) %>%
+  select(contains("sum_score")) %>% 
+  select(-ends_with("raw")) %>%
+  colnames()
+
+gad.sum_score_cols
+
+ocir.sum_score_cols <- dat %>%
+  select(contains("ocir")) %>%
+  select(contains("sum_score")) %>% 
+  select(-ends_with("raw")) %>%
+  colnames()
+
+ocir.sum_score_cols
 ```
@@
 mhd.personality_disorder_numeric == 1 ~ 7,
-mhd.autism_aspergers_or_autistic_spectrum_disorder_numeric == 1 ~ 8,
+autism_spectrum_disorder_numeric == 1 ~ 8,
 mhd.mania_hypomania_bipolar_or_manicdepression_numeric == 1 ~ 9,
@@
 mhd.mania_hypomania_bipolar_or_manicdepression_numeric == 1 ~ 9,
-mhd.autism_aspergers_or_autistic_spectrum_disorder_numeric == 1 ~ 8,
+autism_spectrum_disorder_numeric == 1 ~ 8,
 mhd.personality_disorder_numeric == 1 ~ 7,
@@
   mutate(
-    Disorder_numeric =
+    Disorder_hierarchical_numeric =
       case_when(
@@
         mhd.mania_hypomania_bipolar_or_manicdepression_numeric == 1 ~ 10,
-        mhd.autism_aspergers_or_autistic_spectrum_disorder_numeric == 1 ~ 9,
+        autism_spectrum_disorder_numeric == 1 ~ 9,
         mhd.personality_disorder_numeric == 1 ~ 8,
@@
   mutate(
-    Disorder =
+    Disorder_hierarchical =
       recode_factor(
-        Disorder_numeric,
+        Disorder_hierarchical_numeric,
         `0` = "Controls",
@@
 dat %>%
-  freq(Disorder)
+  freq(Disorder_hierarchical)
 ```
@@
 dat %>%
-  filter(is.na(Disorder)) %>%
+  filter(is.na(Disorder_hierarchical)) %>%
   freq(Sample)
@@
 
++++ ADD AGE PLOT HERE
+
 +++ADD CHUNK FOR AGE CATEGORIES HERE
 ```{r Age categories}
-
+dat %>%
+  freq(age_category_full)
+```
+
++++ADD CHUNK FOR AGE CATEGORIES HERE
+```{r Age categories}
+dat %>%
+  group_by(Sample) %>%
+  count(age_category_full, Sample)
 ```
@@
     "mhd.posttraumatic_stress_disorder_ptsd_numeric",
-    "mhd.autism_aspergers_or_autistic_spectrum_disorder_numeric",
+    "autism_spectrum_disorder_numeric",
     "mhd.attention_deficit_hyperactivity_disorder_numeric",
@@
 
-```{r gather to long format Disorder}
+```{r gather to long format Disorder_hierarchical}
 dat.long.psych <- dat %>%
@@
              mhd.posttraumatic_stress_disorder_ptsd_numeric = "PTSD",
-             mhd.autism_aspergers_or_autistic_spectrum_disorder_numeric = "Autism",
+             autism_spectrum_disorder_numeric = "Autism",
              mhd.attention_deficit_hyperactivity_disorder_numeric = "ADHD",
@@
 
+# Ethnicity
+```{r Ethnicity per Sample}
+Ethnicity_by_Sample <- dat %>%
+  group_by(Sample) %>%
+  count(Ethnicity, Sample) %>%
+  mutate(Prop = round(n/sum(n), 2))
+
+Ethnicity_by_Sample
+```
+
 ```{r Ethnicity by Sample plot}
@@
 dat %>%
+  group_by(Sample) %>%
   count(highest_education, Sample) %>%
@@
 dat %>%
+  group_by(Sample) %>%
   count(key_worker, Sample) %>%
@@
   spread(key = covid_test_positive, value = n)
+```
+
+# Create data set per cohort
+
+## GAD
+```{r}
+dat.gad <- dat %>%
+#  drop_na() %>%
+  filter(
+    (data_group_gad == "Baseline and retrospective data" |
+      data_group_gad == "Prepandemic and baseline data" |
+      data_group_gad == "All prepandemic, baseline and retrospective data")
+  )
+
+dim(dat.gad)
 ```
@@
 
-```{r gad gather to long format Time_points}
+```{r gad gather to long format Time_points gad.diff_score}
 dat.long.gad.diff <- dat %>%
@@
     Ethnicity,
-    Disorder,
+    Disorder_hierarchical,
     Time_point_raw,
@@
   scale_fill_manual(values = palette, labels = c("Prepandemic", "Retrospective")) +
-  facet_wrap("Disorder")
+  facet_wrap("Disorder_hierarchical")
 ```
@@
     y = "Percentage of participants",
-    fill = "Comparison:\nPrepandemic vs") +
+    fill = "Comparison:\nRetrospective vs") +
   theme_personal +
-  scale_fill_manual(values = palette, labels = c("Retrospective"))
+  scale_fill_manual(values = palette, labels = c("Prepandemic"))
 ```
@@
   labs(
-    x = "Difference phq7 score",
+    x = "Difference PHQ9 score",
     y = "Percentage of participants",
@@
   scale_fill_manual(values = palette, labels = c("Prepandemic", "Retrospective")) +
-  facet_wrap("Disorder")
-```
-
-# RUBBISH
-
-+++ Everything underneath here is only SCRATCH
-
-```{r RUBBISH 1}
-gad.diff_score_base_prepan_plot <- dat %>%
-  ggplot(mapping = aes(y = gad.diff_score_base_prepan)) +
-  geom_bar() +
-  theme_minimal()
-
-gad.diff_score_retro_prepan_plot <- dat %>%
-  ggplot(mapping = aes(y = gad.diff_score_retro_prepan)) +
-  geom_bar() +
-  theme_minimal()
-
-gad.diff_score_base_retro_plot <- dat %>%
-  ggplot(mapping = aes(y = gad.diff_score_base_retro)) +
-  geom_bar() +
-  theme_minimal()
-
-```
-
-```{r RUBBISH 2 fig.height=7, fig.width=5}
-gad.diff_score_base_prepan_plot /
-  gad.diff_score_retro_prepan_plot /
-  gad.diff_score_base_retro_plot +
-  plot_layout(guides = "collect", heights = c(1,1,1)) +
-  plot_annotation(tag_levels = "A")
-```
-
-Calculate mean change per disorder group 
-Disorders (9) 
-Sex 
-Age (13; RAMP; potentially collapse above 65 depending on group sizes) 
-Ethnicity groups (5; White European, Black (British), Asian, Arab, Mixed)
-
-```{r RUBBISH }
-#ADD
+  facet_wrap("Disorder_hierarchical")
 ```
@@
 Rank the disorders by the size of the change
-
-# Regression
-Regress covariates out of the change? Which?
-
-Model 0a: Disorders
-```{r}
-model0a <- lm(
-  formula = phq.diff_score_base_prepan ~ Disorder,
-  data = dat)
-
-summary(model0a)
-```
-
-Model 0b: Disorders
-```{r}
-model0b <- lm(
-  formula = phq.diff_score_base_prepan ~
-    anxiety_disorders +
-    depressive_disorders +
-    eating_disorders +
-    obsessive_compulsive_disorders +
-    psychotic_disorders +
-    mhd.mania_hypomania_bipolar_or_manicdepression +
-    mhd.posttraumatic_stress_disorder_ptsd +
-    mhd.autism_aspergers_or_autistic_spectrum_disorder +
-    mhd.attention_deficit_hyperactivity_disorder +
-    mhd.personality_disorder,
-  data = dat)
-
-summary(model0b)
-```
-
-Model 0: Disorders
-```{r}
-model0 <- lm(
-  formula = gad.diff_score_base_prepan ~ Disorder,
-  data = dat)
-
-summary(model0)
-```
-
-```{r}
-tidy(model0)
-```
-
-Model 1: Model 0 + Sex + Age + Ethnicity + Time registration and baseline
-```{r}
-model1 <- lm(
-  formula = phq.diff_score_base_prepan ~ Disorder + Gender + Age + Ethnicity + time_diff_sign_up_coping,
-  data = dat)
-
-summary(model1)
-```
-
-Model 1: Model 0 + Sex + Age + Ethnicity + Time registration and baseline
-```{r}
-model1 <- lm(
-  formula = gad.diff_score_base_prepan ~ Disorder + Gender + Age + Ethnicity + time_diff_sign_up_coping,
-  data = dat)
-
-summary(model1)
-```
 
@@
 
+# Regression
+Regress covariates out of the change? Which?
+
+Model 0a: Disorder_hierarchical
+```{r Model 0a: Disorder_hierarchical}
+model0a <- lm(
+  formula = gad.diff_score_base_prepan ~ Disorder_hierarchical,
+  data = dat.gad)
+
+summary(model0a)
+```
+
+Model 0b: Disorders
+```{r}
+model0b <- lm(
+  formula = ocir.diff_score_base_prepan ~
+    anxiety_disorders +
+    depressive_disorders +
+    eating_disorders +
+    obsessive_compulsive_disorders +
+    psychotic_disorders +
+    mhd.mania_hypomania_bipolar_or_manicdepression +
+    mhd.posttraumatic_stress_disorder_ptsd +
+    autism_spectrum_disorder +
+    mhd.attention_deficit_hyperactivity_disorder +
+    mhd.personality_disorder,
+  data = dat)
+
+summary(model0b)
+```
+
+Model 0: Disorders
+```{r}
+model0 <- lm(
+  formula = gad.diff_score_base_prepan ~ Disorder,
+  data = dat)
+
+summary(model0)
+```
+
+```{r}
+tidy(model0)
+```
+
+Model 1: Model 0 + Sex + Age + Ethnicity + Time registration and baseline
+```{r}
+model1 <- lm(
+  formula = phq.diff_score_base_prepan ~
+    anxiety_disorders +
+    depressive_disorders +
+    eating_disorders +
+    obsessive_compulsive_disorders +
+    psychotic_disorders +
+    mhd.mania_hypomania_bipolar_or_manicdepression +
+    mhd.posttraumatic_stress_disorder_ptsd +
+    autism_spectrum_disorder +
+    mhd.attention_deficit_hyperactivity_disorder +
+    mhd.personality_disorder +
+    Gender + age_category_full + Ethnicity + time_diff_sign_up_coping,
+  data = dat)
+
+summary(model1)
+```
+
+Model 1: Model 0 + Sex + Age + Ethnicity + Time registration and baseline
+```{r}
+model1 <- lm(
+  formula = pcl.diff_score_base_prepan ~ Disorder_hierarchical + Gender + age_category_full + Ethnicity + time_diff_sign_up_coping,
+  data = dat)
+
+summary(model1)
+```
+
+Model 1: Model 0 + Sex + Age + Ethnicity + Time registration and baseline
+```{r}
+model1 <- lm(
+  formula = gad.diff_score_base_prepan ~ Disorder + Gender + Age + Ethnicity + time_diff_sign_up_coping,
+  data = dat)
+
+summary(model1)
+```
+
+# RUBBISH
+
++++ Everything underneath here is only SCRATCH
+
+```{r RUBBISH 1}
+gad.diff_score_base_prepan_plot <- dat %>%
+  ggplot(mapping = aes(y = gad.diff_score_base_prepan)) +
+  geom_bar() +
+  theme_minimal()
+
+gad.diff_score_retro_prepan_plot <- dat %>%
+  ggplot(mapping = aes(y = gad.diff_score_retro_prepan)) +
+  geom_bar() +
+  theme_minimal()
+
+gad.diff_score_base_retro_plot <- dat %>%
+  ggplot(mapping = aes(y = gad.diff_score_base_retro)) +
+  geom_bar() +
+  theme_minimal()
+
+```
+
+```{r RUBBISH 2 fig.height=7, fig.width=5}
+gad.diff_score_base_prepan_plot /
+  gad.diff_score_retro_prepan_plot /
+  gad.diff_score_base_retro_plot +
+  plot_layout(guides = "collect", heights = c(1,1,1)) +
+  plot_annotation(tag_levels = "A")
+```
+
+Calculate mean change per disorder group 
+Disorders (9) 
+Sex 
+Age (13; RAMP; potentially collapse above 65 depending on group sizes) 
+Ethnicity groups (5; White European, Black (British), Asian, Arab, Mixed)
+
+```{r RUBBISH }
+#ADD
+```
+
 Calculate a variable PCL pandemic score 

### 2020-08-25 PANCHANGE_data_preprocessing2020-07-15.Rmd
vectors with sum scores

@@
 
-```{r Check psychotic_disorders}
+```{r Check autism_spectrum_disorder}
 if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE | RAMP == TRUE) {
@@
     mhd.posttraumatic_stress_disorder_ptsd_numeric == "0" &
-    mhd.autism_aspergers_or_autistic_spectrum_disorder_numeric == "0" &
+    autism_spectrum_disorder_numeric == "0" &
     mhd.attention_deficit_hyperactivity_disorder_numeric == "0" &
@@
     mhd.posttraumatic_stress_disorder_ptsd,
-    mhd.autism_aspergers_or_autistic_spectrum_disorder_numeric,
-    mhd.autism_aspergers_or_autistic_spectrum_disorder,
+    autism_spectrum_disorder_numeric,
+    autism_spectrum_disorder,
     mhd.attention_deficit_hyperactivity_disorder_numeric,

### 2020-08-25 PANCHANGE_analysis.Rmd
fixing age categories

@@
 
-```{r}
+# Collapsing categories
+
+## age_category_full
+```{r Inspect age_category_full}
 dat.raw %>%
   freq(age_category_full)
-```
-
-# Collapsing categories
+
+dat.raw %>%
+  freq(age_category_full_numeric)
+```
+
+```{r Collapse age_category_full}
+dat.raw <- dat.raw %>%
+  mutate(age_category_collapsed_numeric =
+           case_when(
+             age_category_full_numeric == 1 ~ 0,
+             age_category_full_numeric == 2 ~ 1,
+             age_category_full_numeric == 3 ~ 2,
+             age_category_full_numeric == 4 ~ 3,
+             age_category_full_numeric == 5 ~ 4,
+             age_category_full_numeric == 6 ~ 5,
+             age_category_full_numeric == 7 ~ 6,
+             age_category_full_numeric == 8 ~ 7,
+             age_category_full_numeric == 9 ~ 9,
+             age_category_full_numeric == 10 ~ 9,
+             age_category_full_numeric == 11 ~ 9,
+             age_category_full_numeric == 12 ~ 9,
+             age_category_full_numeric == 13 ~ 9
+
+           )
+  )
+
+dat.raw <- dat.raw %>%
+  mutate(age_category_collapsed =
+           recode_factor(
+             age_category_collapsed_numeric,
+             `0` = "16-18",
+             `1` = "19-25",
+             `2` = "26-35",
+             `3` = "36-45",
+             `4` = "46-55",
+             `5` = "56-65",
+             `6` = "66-70",
+             `7` = "71-75",
+             `8` = "76+"
+           )
+  )
+
+dat.raw %>%
+  freq(age_category_collapsed)
+```
 
@@
 ocir.sum_score_cols
+
+pcl.sum_score_cols <- dat %>%
+  select(contains("pcl")) %>%
+  select(contains("sum_score")) %>% 
+  select(-ends_with("raw")) %>%
+  colnames()
+
+pcl.sum_score_cols
 ```
@@
 +++ADD CHUNK FOR AGE CATEGORIES HERE
-```{r Age categories}
+```{r Age categories by Sample}
 dat %>%
   group_by(Sample) %>%
-  count(age_category_full, Sample)
+  count(age_category_full, Sample) %>%
+  mutate(Prop = round(n/sum(n), 2))
 ```
@@
 
-### Plots
+```{r gad gather to long format Time_points gad.sum_score}
+dat.long.gad.sum <- dat %>%
+  gather(
+    key = "Time_point_raw",
+    value = "gad.sum_score",
+    all_of(gad.sum_score_cols)) %>%
+  select(
+    ID,
+    Sample,
+    Gender,
+    Ethnicity,
+    Disorder_hierarchical,
+    Time_point_raw,
+    gad.sum_score
+  ) %>%
+  mutate(Time_point = str_replace(Time_point_raw, "gad.sum_score_", "")) %>%
+  select(-Time_point_raw)
+
+head(dat.long.gad.sum)
+```
+
+### Plots diff
 
@@
 
-```{r gad percentage plot retro_prepan}
+```{r gad percentage plot retro_prepan diff}
 dat.long.gad.diff %>%
@@
   scale_fill_manual(values = palette, labels = c("Prepandemic"))
+```
+
+### Plots sum
+
+```{r gad percentage plot retro_prepan sum}
+dat.long.gad.sum %>%
+#  filter(Time_point != "retro_prepan") %>%
+  ggplot(mapping = aes(
+    x = gad.sum_score,
+    y = stat(density*width),
+    fill = Time_point)) +
+  geom_histogram(
+    binwidth = 1,
+    position = position_dodge2(preserve = "single")
+  ) +
+  labs(
+    x = "GAD7 scores",
+    y = "Percentage of participants",
+    fill = "Time point") +
+  theme_personal +
+  scale_fill_manual(
+    values = COPINGpalette3,
+    labels = c("Baseline", "Prepandemic", "Retrospective")
+    )
+```
+
+```{r gad percentage plot retro_prepan sum, fig.height=6, fig.width=10}
+dat.long.gad.sum %>%
+#  filter(Time_point != "retro_prepan") %>%
+  ggplot(mapping = aes(
+    x = gad.sum_score,
+    y = stat(density*width),
+    fill = Time_point)) +
+  geom_histogram(
+    binwidth = 1,
+    position = position_dodge2(preserve = "single")
+  ) +
+  labs(
+    x = "GAD7 score",
+    y = "Percentage of participants",
+    fill = "Time point") +
+  theme_personal +
+  scale_fill_manual(
+    values = COPINGpalette3,
+#    labels = c("Prepandemic", "Retrospective")
+    ) +
+  facet_wrap("Disorder_hierarchical")
 ```
@@
 
+```{r phq gather to long format Time_points phq.sum_score}
+dat.long.phq.sum <- dat %>%
+  gather(
+    key = "Time_point_raw",
+    value = "phq.sum_score",
+    all_of(phq.sum_score_cols)) %>%
+  select(
+    ID,
+    Sample,
+    Gender,
+    Ethnicity,
+    Disorder_hierarchical,
+    Time_point_raw,
+    phq.sum_score
+  ) %>%
+  mutate(Time_point = str_replace(Time_point_raw, "phq.sum_score_", "")) %>%
+  select(-Time_point_raw)
+
+head(dat.long.phq.sum)
+```
+
 ### Plots
@@
   scale_fill_manual(values = palette, labels = c("Prepandemic", "Retrospective")) +
+  facet_wrap("Disorder_hierarchical")
+```
+
+### Plots sum
+
+```{r phq percentage plot retro_prepan sum}
+dat.long.phq.sum %>%
+  #  filter(Time_point != "retro_prepan") %>%
+  ggplot(mapping = aes(
+    x = phq.sum_score,
+    y = stat(density*width),
+    fill = Time_point)) +
+  geom_histogram(
+    binwidth = 1,
+    position = position_dodge2(preserve = "single")
+  ) +
+  labs(
+    x = "PHQ9 scores",
+    y = "Percentage of participants",
+    fill = "Time point") +
+  theme_personal +
+  scale_fill_manual(
+    values = COPINGpalette3,
+    labels = c("Baseline", "Prepandemic", "Retrospective")
+  )
+```
+
+```{r phq percentage plot retro_prepan sum, fig.height=6, fig.width=10}
+dat.long.phq.sum %>%
+  #  filter(Time_point != "retro_prepan") %>%
+  ggplot(mapping = aes(
+    x = phq.sum_score,
+    y = stat(density*width),
+    fill = Time_point)) +
+  geom_histogram(
+    binwidth = 1,
+    position = position_dodge2(preserve = "single")
+  ) +
+  labs(
+    x = "PHQ9 score",
+    y = "Percentage of participants",
+    fill = "Time point") +
+  theme_personal +
+  scale_fill_manual(
+    values = COPINGpalette3,
+    labels = c("Baseline", "Prepandemic", "Retrospective")
+  ) +
   facet_wrap("Disorder_hierarchical")
@@
 
+```{r ocir gather to long format Time_points ocir.sum_score}
+dat.long.ocir.sum <- dat %>%
+  gather(
+    key = "Time_point_raw",
+    value = "ocir.sum_score",
+    all_of(ocir.sum_score_cols)) %>%
+  select(
+    ID,
+    Sample,
+    Gender,
+    Ethnicity,
+    Disorder_hierarchical,
+    Time_point_raw,
+    ocir.sum_score
+  ) %>%
+  mutate(Time_point = str_replace(Time_point_raw, "ocir.sum_score_", "")) %>%
+  select(-Time_point_raw)
+
+head(dat.long.ocir.sum)
+```
+
 ### Plots
@@
   scale_fill_manual(values = palette, labels = c("Prepandemic", "Retrospective")) +
+  facet_wrap("Disorder_hierarchical")
+```
+
+### Plots sum
+
+```{r ocir percentage plot retro_prepan sum}
+dat.long.ocir.sum %>%
+  ggplot(mapping = aes(
+    x = ocir.sum_score,
+    y = stat(density*width),
+    fill = Time_point)) +
+  geom_histogram(
+    binwidth = 1,
+    position = position_dodge2(preserve = "single")
+  ) +
+  labs(
+    x = "OCI-R scores",
+    y = "Percentage of participants",
+    fill = "Time point") +
+  theme_personal +
+  scale_fill_manual(
+    values = COPINGpalette3,
+    labels = c("Baseline", "Prepandemic", "Retrospective")
+  )
+```
+
+```{r ocir percentage plot retro_prepan sum, fig.height=6, fig.width=10}
+dat.long.ocir.sum %>%
+  ggplot(mapping = aes(
+    x = ocir.sum_score,
+    y = stat(density*width),
+    fill = Time_point)) +
+  geom_histogram(
+    binwidth = 1,
+    position = position_dodge2(preserve = "single")
+  ) +
+  labs(
+    x = "OCI-R score",
+    y = "Percentage of participants",
+    fill = "Time point") +
+  theme_personal +
+  scale_fill_manual(
+    values = COPINGpalette3,
+    labels = c("Baseline", "Prepandemic", "Retrospective")
+  ) +
   facet_wrap("Disorder_hierarchical")
@@
 
+```{r pcl gather to long format Time_points pcl.sum_score}
+dat.long.pcl.sum <- dat %>%
+  gather(
+    key = "Time_point_raw",
+    value = "pcl.sum_score",
+    all_of(pcl.sum_score_cols)) %>%
+  select(
+    ID,
+    Sample,
+    Gender,
+    Ethnicity,
+    Disorder_hierarchical,
+    Time_point_raw,
+    pcl.sum_score
+  ) %>%
+  mutate(Time_point = str_replace(Time_point_raw, "pcl.sum_score_", "")) %>%
+  select(-Time_point_raw)
+
+head(dat.long.pcl.sum)
+```
+
 For each item 
@@
 pcl.percentages.summary
+```
+
+### Plots sum
+
+```{r pcl percentage plot retro_prepan sum}
+dat.long.pcl.sum %>%
+  ggplot(mapping = aes(
+    x = pcl.sum_score,
+    y = stat(density*width),
+    fill = Time_point)) +
+  geom_histogram(
+    binwidth = 1,
+    position = position_dodge2(preserve = "single")
+  ) +
+  labs(
+    x = "PCL scores",
+    y = "Percentage of participants",
+    fill = "Time point") +
+  theme_personal +
+  scale_fill_manual(
+    values = COPINGpalette3,
+    labels = c("Baseline", "Prepandemic", "Retrospective")
+  )
+```
+
+```{r pcl percentage plot retro_prepan sum, fig.height=6, fig.width=10}
+dat.long.pcl.sum %>%
+  ggplot(mapping = aes(
+    x = pcl.sum_score,
+    y = stat(density*width),
+    fill = Time_point)) +
+  geom_histogram(
+    binwidth = 1,
+    position = position_dodge2(preserve = "single")
+  ) +
+  labs(
+    x = "PCL score",
+    y = "Percentage of participants",
+    fill = "Time point") +
+  theme_personal +
+  scale_fill_manual(
+    values = COPINGpalette3,
+    labels = c("Baseline", "Prepandemic", "Retrospective")
+  ) +
+  facet_wrap("Disorder_hierarchical")
 ```

### 2020-08-25 PANCHANGE_data_preprocessing2020-07-15.Rmd
fixing age categories

@@
 #      startDate.coping, #Date when participant signed up to ramp  (is in the coping gad chunk)
-      age_category_full = demographics.how_old_are_you, # Age
+      age_category = demographics.how_old_are_you, # Age
       Gender = demographics.which_gender_do_you_identify_with, # Gender (what [GLAD] vs which [RAMP])
@@
 dem.raw.id %>%
-  freq(age_category_full)
+  freq(age_category)
 }
@@
 dat.no.sex.no.gender.no.age <- dat.no.sex.no.gender %>%
-  drop_na(age_category_full)
+  drop_na(age_category)
 dim(dat.no.sex.no.gender.no.age)
@@
       case_when(
-        age_category_full == "16-18" ~ 17,
-        age_category_full == "19-25" ~ 22,
-        age_category_full == "26-35" ~ 30.5,
-        age_category_full == "36-45" ~ 40.5,
-        age_category_full == "46-55" ~ 50.5,
-        age_category_full == "56-65" ~ 60.5,
-        age_category_full == "66-70" ~ 68,
-        age_category_full == "71-75" ~ 73,
-        age_category_full == "76-80" ~ 78,
-        age_category_full == "81-85" ~ 83,
-        age_category_full == "86-90" ~ 88,
-        age_category_full == "91-100" ~ 93,
-      age_category_full == "100+" ~ 100
+        age_category == "16-18" ~ 17,
+        age_category == "19-25" ~ 22,
+        age_category == "26-35" ~ 30.5,
+        age_category == "36-45" ~ 40.5,
+        age_category == "46-55" ~ 50.5,
+        age_category == "56-65" ~ 60.5,
+        age_category == "66-70" ~ 68,
+        age_category == "71-75" ~ 73,
+        age_category == "76-80" ~ 78,
+        age_category == "81-85" ~ 83,
+        age_category == "86-90" ~ 88,
+        age_category == "91-100" ~ 93,
+      age_category == "100+" ~ 100
       )

### 2020-08-25 PANCHANGE_analysis.Rmd
add age category chi square

@@
 
-## age_category_full
-```{r Inspect age_category_full}
+## age_category
+```{r Inspect age_category}
 dat.raw %>%
-  freq(age_category_full)
+  freq(age_category)
 
 dat.raw %>%
-  freq(age_category_full_numeric)
-```
-
-```{r Collapse age_category_full}
+  freq(age_category_numeric)
+```
+
+```{r Collapse age_category}
 dat.raw <- dat.raw %>%
@@
            case_when(
-             age_category_full_numeric == 1 ~ 0,
-             age_category_full_numeric == 2 ~ 1,
-             age_category_full_numeric == 3 ~ 2,
-             age_category_full_numeric == 4 ~ 3,
-             age_category_full_numeric == 5 ~ 4,
-             age_category_full_numeric == 6 ~ 5,
-             age_category_full_numeric == 7 ~ 6,
-             age_category_full_numeric == 8 ~ 7,
-             age_category_full_numeric == 9 ~ 9,
-             age_category_full_numeric == 10 ~ 9,
-             age_category_full_numeric == 11 ~ 9,
-             age_category_full_numeric == 12 ~ 9,
-             age_category_full_numeric == 13 ~ 9
+             age_category_numeric == 1 ~ 0,
+             age_category_numeric == 2 ~ 1,
+             age_category_numeric == 3 ~ 2,
+             age_category_numeric == 4 ~ 3,
+             age_category_numeric == 5 ~ 4,
+             age_category_numeric == 6 ~ 5,
+             age_category_numeric == 7 ~ 6,
+             age_category_numeric == 8 ~ 7,
+             age_category_numeric == 9 ~ 8,
+             age_category_numeric == 10 ~ 8,
+             age_category_numeric == 11 ~ 8,
+             age_category_numeric == 12 ~ 8,
+             age_category_numeric == 13 ~ 8
 
@@
 dat %>%
-  freq(age_category_full)
+  freq(age_category)
 ```
@@
   group_by(Sample) %>%
-  count(age_category_full, Sample) %>%
+  count(age_category, Sample) %>%
   mutate(Prop = round(n/sum(n), 2))
+```
+
+```{r Gender per Sample count cross table}
+dat %>%
+  count(age_category, Sample) %>%
+  spread(key = Sample, value = n)
+```
+
+```{r Gender per Sample count cross table chi square test}
+dat %>%
+  count(age_category, Sample) %>%
+  spread(key = Sample, value = n) %>%
+  select(-age_category) %>%
+  mutate(
+    EDGI = as.integer(replace_na(EDGI, 0)),
+    GLAD = as.integer(replace_na(GLAD, 0))
+    ) %>%
+  chisq.test() %>%
+  glance()
 ```
@@
     mhd.personality_disorder +
-    Gender + age_category_full + Ethnicity + time_diff_sign_up_coping,
+    Gender + age_category + Ethnicity + time_diff_sign_up_coping,
   data = dat)
@@
 model1 <- lm(
-  formula = pcl.diff_score_base_prepan ~ Disorder_hierarchical + Gender + age_category_full + Ethnicity + time_diff_sign_up_coping,
+  formula = pcl.diff_score_base_prepan ~ Disorder_hierarchical + Gender + age_category + Ethnicity + time_diff_sign_up_coping,
   data = dat)

### 2020-08-26 PANCHANGE_analysis.Rmd
added correlation matrix for disorders

@@
 library(psych)
+library(polycor)
+library(corrplot)
 library(patchwork)
@@
     "control_numeric"
+)
+```
+
+Correlation matrix of psychiatric disorders
+```{r Correlation matrix of psychiatric disorders}
+# Select items for correlation matrix
+mhd.items <- c(
+    "depressive_disorders",
+    "anxiety_disorders",
+    "eating_disorders",
+    "obsessive_compulsive_disorders",
+    "psychotic_disorders",
+    "mhd.mania_hypomania_bipolar_or_manicdepression",
+    "mhd.posttraumatic_stress_disorder_ptsd",
+    "autism_spectrum_disorder",
+    "mhd.attention_deficit_hyperactivity_disorder",
+    "mhd.personality_disorder",
+    "control"
+)
+
+# Calculate correlation matrix on specific columns (variables) from your data frame
+mhd.corr.mat <- hetcor(
+  as.data.frame(dat[,mhd.items]), # Specify the data
+  use = "pairwise.complete.obs" # Use all pairwise observations
+)
+
+# Print the correlation matrix
+print(mhd.corr.mat, digits = max(3, getOption("digits") - 3))
+
+# Save the correlations from the correlation matrix in an object
+mhd.corr.matrix <- as.matrix(mhd.corr.mat)
+
+# Save the p values from the correlation matrix in an object
+mhd.p.matrix <- as.matrix(mhd.corr.mat$tests)
+```
+
+Create the correlation matrix plot using the corrplot package
+```{r Correlation matrix of psychiatric disorders plot, fig.height=7}
+corrplot(mhd.corr.matrix, 
+         method = "color", # objects to represent the correlations on plot
+         type = "lower", # only use the lower triangle of the matrix
+         diag = FALSE, # do not show the correlations on the diagonal
+         addgrid.col = NA,
+         addCoef.col = "black", # colour for the correlation coefficients in the plot
+         tl.cex = 0.8,
+         tl.col = "black",
+         col=colorRampPalette(c("dodgerblue4","white","firebrick4"))(200), # colours for correlations
+         # Combine with significance
+         p.mat = mhd.p.matrix, # Matrix with p values
+         sig.level = 0.01, # Choose significant level
+         insig = "blank" # Nonsignificant correlations have no colour
          )

### 2020-08-26 PANCHANGE_analysis.Rmd
cleaning up Gender per Sample

@@
 # Ethnicity
-```{r Ethnicity per Sample}
-Ethnicity_by_Sample <- dat %>%
+```{r Ethnicity per Sample prop per total}
+Ethnicity_by_Sample_prop_total <- dat %>%
   count(Ethnicity, Sample) %>%
@@
 
-Ethnicity_by_Sample
-```
-
-# Ethnicity
-```{r Ethnicity per Sample}
-Ethnicity_by_Sample <- dat %>%
+Ethnicity_by_Sample_prop_total
+```
+
+```{r Ethnicity per Sample prop per sample}
+Ethnicity_by_Sample_prop_sample <- dat %>%
   group_by(Sample) %>%
@@
 
-Ethnicity_by_Sample
+Ethnicity_by_Sample_prop_sample
+```
+
+```{r Ethnicity per Sample prop cross table}
+dat %>%
+  group_by(Sample) %>%
+  count(Ethnicity, Sample) %>%
+  mutate(Prop = round(n/sum(n), 2)) %>%
+  pivot_wider(names_from = Sample, values_from = c(n, Prop))
+```
+
+```{r Ethnicity per Sample count cross table}
+dat %>%
+  count(Ethnicity, Sample) %>%
+  spread(key = Sample, value = n) %>%
+  mutate(
+    EDGI = as.integer(replace_na(EDGI, 0)),
+    GLAD = as.integer(replace_na(GLAD, 0)),
+    NBR = as.integer(replace_na(NBR, 0)),
+    RAMP = as.integer(replace_na(RAMP, 0))
+  )
+```
+
+```{r Ethnicity per Sample chisquare test}
+dat %>%
+  count(Ethnicity, Sample) %>%
+  spread(key = Sample, value = n) %>%
+  select(-Ethnicity) %>%
+  mutate(
+    EDGI = as.integer(replace_na(EDGI, 0)),
+    GLAD = as.integer(replace_na(GLAD, 0)),
+    NBR = as.integer(replace_na(NBR, 0)),
+    RAMP = as.integer(replace_na(RAMP, 0))
+  ) %>%  
+  chisq.test() %>%
+  glance()
 ```
@@
     aes(fill = Sample),
-    #    position = "dodge",
     stat="identity",
@@
   scale_fill_manual(
-    values = COPINGpalette6,
-    #    labels = c("Prepandemic", "Retrospective")
+    values = COPINGpalette6
   ) +
@@
 ```{r Gender per Sample prop per total}
-dat %>%
+Gender_per_Sample_prop_total <- dat %>%
   count(Gender, Sample) %>%
   mutate(Prop = round(n/sum(n), 2))
+
+kable(Gender_per_Sample_prop_total)
+Gender_per_Sample_prop_total
 ```
@@
 ```{r Gender per Sample prop per Sample}
-dat %>%
+Gender_per_Sample_prop_Sample <- dat %>%
   group_by(Sample) %>%
@@
   mutate(Prop = round(n/sum(n), 2))
+
+kable(Gender_per_Sample_prop_Sample)
+Gender_per_Sample_prop_Sample
 ```
@@
 ```{r Gender per Sample prop cross table}
-dat %>%
+Gender_per_Sample_prop_Sample_cross_table <- dat %>%
   group_by(Sample) %>%
@@
   pivot_wider(names_from = Sample, values_from = c(n, Prop))
+
+kable(Gender_per_Sample_prop_Sample_cross_table)
+Gender_per_Sample_prop_Sample_cross_table
 ```
@@
 ```{r Gender per Sample count cross table}
-dat %>%
+Gender_per_Sample_count_cross_table <- dat %>%
   count(Gender, Sample) %>%
-  spread(key = Sample, value = n)
-```
-
-```{r}
-dat %>%
+  spread(key = Sample, value = n) %>%
+  mutate(
+    EDGI = as.integer(replace_na(EDGI, 0)),
+    GLAD = as.integer(replace_na(GLAD, 0)),
+    NBR = as.integer(replace_na(NBR, 0)),
+    RAMP = as.integer(replace_na(RAMP, 0))
+  )
+
+kable(Gender_per_Sample_count_cross_table)
+Gender_per_Sample_count_cross_table
+```
+
+```{r Gender per Sample chisquare test}
+Gender_per_Sample_chissquare_test <- dat %>%
   count(Gender, Sample) %>%
@@
   select(-Gender) %>%
+  mutate(
+    EDGI = as.integer(replace_na(EDGI, 0)),
+    GLAD = as.integer(replace_na(GLAD, 0)),
+    NBR = as.integer(replace_na(NBR, 0)),
+    RAMP = as.integer(replace_na(RAMP, 0))
+  ) %>%
   chisq.test() %>%
   glance()
+
+kable(Gender_per_Sample_chissquare_test)
+Gender_per_Sample_chissquare_test
 ```

### 2020-08-26 PANCHANGE_analysis.Rmd
cleaning up Gender

@@
 
+```{r Gender by Sample count plot}
+Gender_by_Sample_count_plot <- Gender_per_Sample_prop_Sample %>%
+  ggplot(mapping = aes(
+    x = Gender,
+    y = n)
+  ) +
+  geom_bar(
+    aes(fill = Sample),
+    stat="identity",
+    binwidth = 1,
+    position = position_dodge2(preserve = "single")
+  ) +
+  labs(
+    x = "Gender",
+    y = "Number of participants",
+    fill = "Sample") +
+  theme_personal +
+  scale_fill_manual(
+    values = COPINGpalette6
+  ) +
+  coord_flip()
+
+Gender_by_Sample_count_plot
+```
+
+```{r Gender by Sample prop plot}
+Gender_by_Sample_prop_plot <- Gender_per_Sample_prop_Sample %>%
+  ggplot(mapping = aes(
+    x = Gender,
+    y = Prop)
+  ) +
+  geom_bar(
+    aes(fill = Sample),
+    stat="identity",
+    binwidth = 1,
+    position = position_dodge2(preserve = "single")
+  ) +
+  labs(
+    x = "Gender",
+    y = "Number of participants",
+    fill = "Sample") +
+  theme_personal +
+  scale_fill_manual(
+    values = COPINGpalette6
+  ) +
+  coord_flip()
+
+Gender_by_Sample_prop_plot
+```
+
 # highest_education
-```{r highest_education per Sample}
+```{r highest_education per Sample prop per total}
+highest_education_per_Sample_prop_total <- dat %>%
+  count(highest_education, Sample) %>%
+  mutate(Prop = round(n/sum(n), 2))
+
+kable(highest_education_per_Sample_prop_total)
+highest_education_per_Sample_prop_total
+```
+
+```{r highest_education per Sample prop per Sample}
+highest_education_per_Sample_prop_Sample <- dat %>%
+  group_by(Sample) %>%
+  count(highest_education, Sample) %>%
+  mutate(Prop = round(n/sum(n), 2))
+
+kable(highest_education_per_Sample_prop_Sample)
+highest_education_per_Sample_prop_Sample
+```
+
+```{r highest_education per Sample prop cross table}
 dat %>%
@@
   count(highest_education, Sample) %>%
+  mutate(Prop = round(n/sum(n), 2)) %>%
+  pivot_wider(names_from = Sample, values_from = c(n, Prop))
+```
+
+```{r highest_education per Sample count cross table}
+dat %>%
+  count(highest_education, Sample) %>%
+  spread(key = Sample, value = n) %>%
+  mutate(
+    EDGI = as.integer(replace_na(EDGI, 0)),
+    GLAD = as.integer(replace_na(GLAD, 0)),
+    NBR = as.integer(replace_na(NBR, 0)),
+    RAMP = as.integer(replace_na(RAMP, 0))
+  )
+```
+
+```{r highest_education per Sample chisquare test}
+dat %>%
+  count(highest_education, Sample) %>%
+  spread(key = Sample, value = n) %>%
+  select(-highest_education) %>%
+  mutate(
+    EDGI = as.integer(replace_na(EDGI, 0)),
+    GLAD = as.integer(replace_na(GLAD, 0)),
+    NBR = as.integer(replace_na(NBR, 0)),
+    RAMP = as.integer(replace_na(RAMP, 0))
+  ) %>%
+  chisq.test() %>%
+  glance()
+```
+
+```{r highest_education by Sample count plot}
+highest_education_per_Sample_prop_Sample %>%
+  ggplot(mapping = aes(
+    x = highest_education,
+    y = n)
+  ) +
+  geom_bar(
+    aes(fill = Sample),
+    stat="identity",
+    binwidth = 1,
+    position = position_dodge2(preserve = "single")
+  ) +
+  labs(
+    x = "highest_education",
+    y = "Number of participants",
+    fill = "Sample") +
+  theme_personal +
+  scale_fill_manual(
+    values = COPINGpalette6
+  ) +
+  coord_flip()
+```
+
+```{r highest_education by Sample prop plot}
+highest_education_per_Sample_prop_Sample %>%
+  ggplot(mapping = aes(
+    x = highest_education,
+    y = Prop)
+  ) +
+  geom_bar(
+    aes(fill = Sample),
+    stat="identity",
+    binwidth = 1,
+    position = position_dodge2(preserve = "single")
+  ) +
+  labs(
+    x = "highest_education",
+    y = "Number of participants",
+    fill = "Sample") +
+  theme_personal +
+  scale_fill_manual(
+    values = COPINGpalette6
+  ) +
+  coord_flip()
+```
+
+# key_worker
+```{r key_worker per Sample prop per total}
+key_worker_per_Sample_prop_total <- dat %>%
+  count(key_worker, Sample) %>%
   mutate(Prop = round(n/sum(n), 2))
-```
-
-# Key worker status
-```{r Key worker status per sample}
+
+kable(key_worker_per_Sample_prop_total)
+key_worker_per_Sample_prop_total
+```
+
+```{r key_worker per Sample prop per Sample}
+key_worker_per_Sample_prop_Sample <- dat %>%
+  group_by(Sample) %>%
+  count(key_worker, Sample) %>%
+  mutate(Prop = round(n/sum(n), 2))
+
+kable(key_worker_per_Sample_prop_Sample)
+key_worker_per_Sample_prop_Sample
+```
+
+```{r key_worker per Sample prop cross table}
 dat %>%
@@
   count(key_worker, Sample) %>%
-  mutate(Prop = round(n/sum(n), 2))
+  mutate(Prop = round(n/sum(n), 2)) %>%
+  pivot_wider(names_from = Sample, values_from = c(n, Prop))
+```
+
+```{r key_worker per Sample count cross table}
+dat %>%
+  count(key_worker, Sample) %>%
+  spread(key = Sample, value = n) %>%
+  mutate(
+    EDGI = as.integer(replace_na(EDGI, 0)),
+    GLAD = as.integer(replace_na(GLAD, 0)),
+    NBR = as.integer(replace_na(NBR, 0)),
+    RAMP = as.integer(replace_na(RAMP, 0))
+  )
+```
+
+```{r key_worker per Sample chisquare test}
+dat %>%
+  count(key_worker, Sample) %>%
+  spread(key = Sample, value = n) %>%
+  select(-key_worker) %>%
+  mutate(
+    EDGI = as.integer(replace_na(EDGI, 0)),
+    GLAD = as.integer(replace_na(GLAD, 0)),
+    NBR = as.integer(replace_na(NBR, 0)),
+    RAMP = as.integer(replace_na(RAMP, 0))
+  ) %>%
+  chisq.test() %>%
+  glance()
+```
+
+```{r key_worker by Sample count plot}
+key_worker_per_Sample_prop_Sample %>%
+  ggplot(mapping = aes(
+    x = key_worker,
+    y = n)
+  ) +
+  geom_bar(
+    aes(fill = Sample),
+    stat="identity",
+    binwidth = 1,
+    position = position_dodge2(preserve = "single")
+  ) +
+  labs(
+    x = "key_worker",
+    y = "Number of participants",
+    fill = "Sample") +
+  theme_personal +
+  scale_fill_manual(
+    values = COPINGpalette6
+  ) +
+  coord_flip()
+```
+
+```{r key_worker by Sample prop plot}
+key_worker_per_Sample_prop_Sample %>%
+  ggplot(mapping = aes(
+    x = key_worker,
+    y = Prop)
+  ) +
+  geom_bar(
+    aes(fill = Sample),
+    stat="identity",
+    binwidth = 1,
+    position = position_dodge2(preserve = "single")
+  ) +
+  labs(
+    x = "key_worker",
+    y = "Number of participants",
+    fill = "Sample") +
+  theme_personal +
+  scale_fill_manual(
+    values = COPINGpalette6
+  ) +
+  coord_flip()
 ```

### 2020-08-26 PANCHANGE_analysis.Rmd
Gender and Ethnicity collapsed

@@
 
-# Ethnicity
-```{r Ethnicity per Sample prop per total}
-Ethnicity_by_Sample_prop_total <- dat %>%
-  count(Ethnicity, Sample) %>%
+# Ethnicity_collapsed
+```{r Ethnicity_collapsed per Sample prop per total}
+Ethnicity_collapsed_per_Sample_prop_total <- dat %>%
+  count(Ethnicity_collapsed, Sample) %>%
   mutate(Prop = round(n/sum(n), 2))
 
-Ethnicity_by_Sample_prop_total
-```
-
-```{r Ethnicity per Sample prop per sample}
-Ethnicity_by_Sample_prop_sample <- dat %>%
+kable(Ethnicity_collapsed_per_Sample_prop_total)
+Ethnicity_collapsed_per_Sample_prop_total
+```
+
+```{r Ethnicity_collapsed per Sample prop per Sample}
+Ethnicity_collapsed_per_Sample_prop_Sample <- dat %>%
   group_by(Sample) %>%
-  count(Ethnicity, Sample) %>%
+  count(Ethnicity_collapsed, Sample) %>%
   mutate(Prop = round(n/sum(n), 2))
 
-Ethnicity_by_Sample_prop_sample
-```
-
-```{r Ethnicity per Sample prop cross table}
-dat %>%
+kable(Ethnicity_collapsed_per_Sample_prop_Sample)
+Ethnicity_collapsed_per_Sample_prop_Sample
+```
+
+```{r Ethnicity_collapsed per Sample prop cross table}
+Ethnicity_collapsed_per_Sample_prop_Sample_cross_table <- dat %>%
   group_by(Sample) %>%
-  count(Ethnicity, Sample) %>%
+  count(Ethnicity_collapsed, Sample) %>%
   mutate(Prop = round(n/sum(n), 2)) %>%
   pivot_wider(names_from = Sample, values_from = c(n, Prop))
-```
-
-```{r Ethnicity per Sample count cross table}
-dat %>%
-  count(Ethnicity, Sample) %>%
+
+kable(Ethnicity_collapsed_per_Sample_prop_Sample_cross_table)
+Ethnicity_collapsed_per_Sample_prop_Sample_cross_table
+```
+
+```{r Ethnicity_collapsed per Sample count cross table}
+Ethnicity_collapsed_per_Sample_count_cross_table <- dat %>%
+  count(Ethnicity_collapsed, Sample) %>%
   spread(key = Sample, value = n) %>%
@@
   )
-```
-
-```{r Ethnicity per Sample chisquare test}
-dat %>%
-  count(Ethnicity, Sample) %>%
+
+kable(Ethnicity_collapsed_per_Sample_count_cross_table)
+Ethnicity_collapsed_per_Sample_count_cross_table
+```
+
+```{r Ethnicity_collapsed per Sample chisquare test}
+Ethnicity_collapsed_per_Sample_chissquare_test <- dat %>%
+  count(Ethnicity_collapsed, Sample) %>%
   spread(key = Sample, value = n) %>%
-  select(-Ethnicity) %>%
+  select(-Ethnicity_collapsed) %>%
   mutate(
@@
   glance()
-```
-
-```{r Ethnicity by Sample plot}
-Ethnicity_by_Sample %>%
-  ggplot(mapping = aes(
-    x = Ethnicity,
+
+kable(Ethnicity_collapsed_per_Sample_chissquare_test)
+Ethnicity_collapsed_per_Sample_chissquare_test
+```
+
+```{r Ethnicity_collapsed by Sample count plot}
+Ethnicity_collapsed_by_Sample_count_plot <- Ethnicity_collapsed_per_Sample_prop_Sample %>%
+  ggplot(mapping = aes(
+    x = Ethnicity_collapsed,
     y = n)
@@
   labs(
-    x = "Ethnicity",
+    x = "Ethnicity_collapsed",
     y = "Number of participants",
@@
   coord_flip()
-```
-
-# Gender
-```{r Gender per Sample prop per total}
-Gender_per_Sample_prop_total <- dat %>%
-  count(Gender, Sample) %>%
+
+Ethnicity_collapsed_by_Sample_count_plot
+```
+
+```{r Ethnicity_collapsed by Sample prop plot}
+Ethnicity_collapsed_by_Sample_prop_plot <- Ethnicity_collapsed_per_Sample_prop_Sample %>%
+  ggplot(mapping = aes(
+    x = Ethnicity_collapsed,
+    y = Prop)
+  ) +
+  geom_bar(
+    aes(fill = Sample),
+    stat="identity",
+    binwidth = 1,
+    position = position_dodge2(preserve = "single")
+  ) +
+  labs(
+    x = "Ethnicity_collapsed",
+    y = "Number of participants",
+    fill = "Sample") +
+  theme_personal +
+  scale_fill_manual(
+    values = COPINGpalette6
+  ) +
+  coord_flip()
+
+Ethnicity_collapsed_by_Sample_prop_plot
+```
+
+# Gender_collapsed
+```{r Gender_collapsed per Sample prop per total}
+Gender_collapsed_per_Sample_prop_total <- dat %>%
+  count(Gender_collapsed, Sample) %>%
   mutate(Prop = round(n/sum(n), 2))
 
-kable(Gender_per_Sample_prop_total)
-Gender_per_Sample_prop_total
-```
-
-```{r Gender per Sample prop per Sample}
-Gender_per_Sample_prop_Sample <- dat %>%
+kable(Gender_collapsed_per_Sample_prop_total)
+Gender_collapsed_per_Sample_prop_total
+```
+
+```{r Gender_collapsed per Sample prop per Sample}
+Gender_collapsed_per_Sample_prop_Sample <- dat %>%
   group_by(Sample) %>%
-  count(Gender, Sample) %>%
+  count(Gender_collapsed, Sample) %>%
   mutate(Prop = round(n/sum(n), 2))
 
-kable(Gender_per_Sample_prop_Sample)
-Gender_per_Sample_prop_Sample
-```
-
-```{r Gender per Sample prop cross table}
-Gender_per_Sample_prop_Sample_cross_table <- dat %>%
+kable(Gender_collapsed_per_Sample_prop_Sample)
+Gender_collapsed_per_Sample_prop_Sample
+```
+
+```{r Gender_collapsed per Sample prop cross table}
+Gender_collapsed_per_Sample_prop_Sample_cross_table <- dat %>%
   group_by(Sample) %>%
-  count(Gender, Sample) %>%
+  count(Gender_collapsed, Sample) %>%
   mutate(Prop = round(n/sum(n), 2)) %>%
@@
 
-kable(Gender_per_Sample_prop_Sample_cross_table)
-Gender_per_Sample_prop_Sample_cross_table
-```
-
-```{r Gender per Sample count cross table}
-Gender_per_Sample_count_cross_table <- dat %>%
-  count(Gender, Sample) %>%
+kable(Gender_collapsed_per_Sample_prop_Sample_cross_table)
+Gender_collapsed_per_Sample_prop_Sample_cross_table
+```
+
+```{r Gender_collapsed per Sample count cross table}
+Gender_collapsed_per_Sample_count_cross_table <- dat %>%
+  count(Gender_collapsed, Sample) %>%
   spread(key = Sample, value = n) %>%
@@
 
-kable(Gender_per_Sample_count_cross_table)
-Gender_per_Sample_count_cross_table
-```
-
-```{r Gender per Sample chisquare test}
-Gender_per_Sample_chissquare_test <- dat %>%
-  count(Gender, Sample) %>%
+kable(Gender_collapsed_per_Sample_count_cross_table)
+Gender_collapsed_per_Sample_count_cross_table
+```
+
+```{r Gender_collapsed per Sample chisquare test}
+Gender_collapsed_per_Sample_chissquare_test <- dat %>%
+  count(Gender_collapsed, Sample) %>%
   spread(key = Sample, value = n) %>%
-  select(-Gender) %>%
+  select(-Gender_collapsed) %>%
   mutate(
@@
 
-kable(Gender_per_Sample_chissquare_test)
-Gender_per_Sample_chissquare_test
-```
-
-```{r Gender by Sample count plot}
-Gender_by_Sample_count_plot <- Gender_per_Sample_prop_Sample %>%
-  ggplot(mapping = aes(
-    x = Gender,
+kable(Gender_collapsed_per_Sample_chissquare_test)
+Gender_collapsed_per_Sample_chissquare_test
+```
+
+```{r Gender_collapsed by Sample count plot}
+Gender_collapsed_by_Sample_count_plot <- Gender_collapsed_per_Sample_prop_Sample %>%
+  ggplot(mapping = aes(
+    x = Gender_collapsed,
     y = n)
@@
   labs(
-    x = "Gender",
+    x = "Gender_collapsed",
     y = "Number of participants",
@@
 
-Gender_by_Sample_count_plot
-```
-
-```{r Gender by Sample prop plot}
-Gender_by_Sample_prop_plot <- Gender_per_Sample_prop_Sample %>%
-  ggplot(mapping = aes(
-    x = Gender,
+Gender_collapsed_by_Sample_count_plot
+```
+
+```{r Gender_collapsed by Sample prop plot}
+Gender_collapsed_by_Sample_prop_plot <- Gender_collapsed_per_Sample_prop_Sample %>%
+  ggplot(mapping = aes(
+    x = Gender_collapsed,
     y = Prop)
@@
 
-Gender_by_Sample_prop_plot
+Gender_collapsed_by_Sample_prop_plot
 ```

### 2020-08-26 PANCHANGE_analysis.Rmd
added key_worker and highest_education

@@
     x = "Ethnicity_collapsed",
-    y = "Number of participants",
+    y = "Percentage per sample",
     fill = "Sample") +
@@
     x = "Gender_collapsed",
-    y = "Number of participants",
+    y = "Percentage per sample",
     fill = "Sample") +
@@
 ```{r highest_education per Sample prop cross table}
-dat %>%
+highest_education_per_Sample_prop_Sample_cross_table <- dat %>%
   group_by(Sample) %>%
@@
   pivot_wider(names_from = Sample, values_from = c(n, Prop))
+
+kable(highest_education_per_Sample_prop_Sample_cross_table)
+highest_education_per_Sample_prop_Sample_cross_table
 ```
@@
 ```{r highest_education per Sample count cross table}
-dat %>%
+highest_education_per_Sample_count_cross_table <- dat %>%
   count(highest_education, Sample) %>%
@@
   )
+
+kable(highest_education_per_Sample_count_cross_table)
+highest_education_per_Sample_count_cross_table
 ```
@@
 ```{r highest_education per Sample chisquare test}
-dat %>%
+highest_education_per_Sample_chissquare_test <- dat %>%
   count(highest_education, Sample) %>%
@@
   glance()
+
+kable(highest_education_per_Sample_chissquare_test)
+highest_education_per_Sample_chissquare_test
 ```
@@
 ```{r highest_education by Sample count plot}
-highest_education_per_Sample_prop_Sample %>%
+highest_education_by_Sample_count_plot <- highest_education_per_Sample_prop_Sample %>%
   ggplot(mapping = aes(
@@
   coord_flip()
+
+highest_education_by_Sample_count_plot
 ```
@@
 ```{r highest_education by Sample prop plot}
-highest_education_per_Sample_prop_Sample %>%
+highest_education_by_Sample_prop_plot <- highest_education_per_Sample_prop_Sample %>%
   ggplot(mapping = aes(
@@
     x = "highest_education",
-    y = "Number of participants",
+    y = "Percentage per sample",
     fill = "Sample") +
@@
   coord_flip()
+
+highest_education_by_Sample_prop_plot
 ```
@@
 ```{r key_worker per Sample prop cross table}
-dat %>%
+key_worker_per_Sample_prop_Sample_cross_table <- dat %>%
   group_by(Sample) %>%
@@
   pivot_wider(names_from = Sample, values_from = c(n, Prop))
+
+kable(key_worker_per_Sample_prop_Sample_cross_table)
+key_worker_per_Sample_prop_Sample_cross_table
 ```
@@
 ```{r key_worker per Sample count cross table}
-dat %>%
+key_worker_per_Sample_count_cross_table <- dat %>%
   count(key_worker, Sample) %>%
@@
   )
+
+kable(key_worker_per_Sample_count_cross_table)
+key_worker_per_Sample_count_cross_table
 ```
@@
 ```{r key_worker per Sample chisquare test}
-dat %>%
+key_worker_per_Sample_chissquare_test <- dat %>%
   count(key_worker, Sample) %>%
@@
   glance()
+
+kable(key_worker_per_Sample_chissquare_test)
+key_worker_per_Sample_chissquare_test
 ```
@@
 ```{r key_worker by Sample count plot}
-key_worker_per_Sample_prop_Sample %>%
+key_worker_by_Sample_count_plot <- key_worker_per_Sample_prop_Sample %>%
   ggplot(mapping = aes(
@@
   coord_flip()
+
+key_worker_by_Sample_count_plot
 ```
@@
 ```{r key_worker by Sample prop plot}
-key_worker_per_Sample_prop_Sample %>%
+key_worker_by_Sample_prop_plot <- key_worker_per_Sample_prop_Sample %>%
   ggplot(mapping = aes(
@@
     x = "key_worker",
-    y = "Number of participants",
+    y = "Percentage per sample",
     fill = "Sample") +
@@
   coord_flip()
+
+key_worker_by_Sample_prop_plot
 ```

### 2020-08-26 PANCHANGE_analysis.Rmd
cleaning up the disorder chunk

@@
 
-# Age
-```{r descriptives Ages}
-dat %>%
-  group_by(Sample) %>%
-  summarise(Mean = mean(Age),
-            SD = sd(Age),
-            Min = min(Age),
-            Max = max(Age))
-```
-
-+++ ADD AGE PLOT HERE
-
-+++ADD CHUNK FOR AGE CATEGORIES HERE
-```{r Age categories}
-dat %>%
-  freq(age_category)
-```
-
-+++ADD CHUNK FOR AGE CATEGORIES HERE
-```{r Age categories by Sample}
-dat %>%
-  group_by(Sample) %>%
-  count(age_category, Sample) %>%
-  mutate(Prop = round(n/sum(n), 2))
-```
-
-```{r Gender per Sample count cross table}
-dat %>%
-  count(age_category, Sample) %>%
-  spread(key = Sample, value = n)
-```
-
-```{r Gender per Sample count cross table chi square test}
-dat %>%
-  count(age_category, Sample) %>%
-  spread(key = Sample, value = n) %>%
-  select(-age_category) %>%
-  mutate(
-    EDGI = as.integer(replace_na(EDGI, 0)),
-    GLAD = as.integer(replace_na(GLAD, 0))
-    ) %>%
-  chisq.test() %>%
-  glance()
-```
-
 # Psychiatric disorders
+
+## Vector
 ```{r vector with psychiatric disorders}
@@
 
-Correlation matrix of psychiatric disorders
+## Correlation matrix
 ```{r Correlation matrix of psychiatric disorders}
@@
 
-Define disorder columns in vector
-
-```{r Disorder_inc by Gender}
-Disorder_inc_by_Gender <- dat.long.psych %>%
+```{r Disorder_inc by Gender_collapsed}
+Disorder_inc_by_Gender_collapsed <- dat.long.psych %>%
   filter(Diagnosis == 1) %>%
-  count(Disorder_inc, Gender) %>%
+  count(Disorder_inc, Gender_collapsed) %>%
   mutate(Prop = round(n/sum(n), 2))
 
-Disorder_inc_by_Gender
-```
-
-```{r Disorder_inc by Gender prop}
-Disorder_inc_by_Gender <- dat.long.psych %>%
+Disorder_inc_by_Gender_collapsed
+```
+
+```{r Disorder_inc by Gender_collapsed prop}
+Disorder_inc_by_Gender_collapsed <- dat.long.psych %>%
   group_by(Disorder_inc) %>%
   filter(Diagnosis == 1) %>%
-  count(Gender) %>%
+  count(Gender_collapsed) %>%
   mutate(Prop = round(n/sum(n), 2))
 
-Disorder_inc_by_Gender
-```
-
-```{r Disorder_inc by Gender plot}
-Disorder_inc_by_Gender %>%
+Disorder_inc_by_Gender_collapsed
+```
+
+```{r Disorder_inc by Gender_collapsed count plot}
+Disorder_inc_by_Gender_collapsed_count_plot <- Disorder_inc_by_Gender_collapsed %>%
   ggplot(mapping = aes(
@@
   geom_bar(
-    aes(fill = Gender),
-#    position = "dodge",
+    aes(fill = Gender_collapsed),
     stat="identity",
@@
     y = "Number of participants",
-    fill = "Gender") +
+    fill = "Gender_collapsed") +
   theme_personal +
   scale_fill_manual(
-    values = COPINGpalette4,
-#    labels = c("Prepandemic", "Retrospective")
+    values = COPINGpalette4
     ) +
   coord_flip()
+
+Disorder_inc_by_Gender_collapsed_count_plot
+```
+
+```{r Disorder_inc by Gender_collapsed prop plot}
+Disorder_inc_by_Gender_collapsed_prop_plot <- Disorder_inc_by_Gender_collapsed %>%
+  ggplot(mapping = aes(
+    x = Disorder_inc,
+    y = Prop)
+    ) +
+  geom_bar(
+    aes(fill = Gender_collapsed),
+    stat="identity",
+    binwidth = 1,
+    position = position_dodge2(preserve = "single")
+  ) +
+  labs(
+    x = "Disorders",
+    y = "Number of participants",
+    fill = "Gender_collapsed") +
+  theme_personal +
+  scale_fill_manual(
+    values = COPINGpalette4
+    ) +
+  coord_flip()
+
+Disorder_inc_by_Gender_collapsed_prop_plot
 ```
@@
 Compare the GLAD/EDGI and COPING cohorts as a whole
-+++CH: Diagnosis, ethnicity, gender, 
-+++MD: May not be possible for NBR; potentially send them code to run it for us
++++CH: Diagnosis, ethnicity, gender, age
+
+# age_category
+```{r age_category per Sample prop per total}
+age_category_per_Sample_prop_total <- dat %>%
+  count(age_category, Sample) %>%
+  mutate(Prop = round(n/sum(n), 2))
+
+kable(age_category_per_Sample_prop_total)
+age_category_per_Sample_prop_total
+```
+
+```{r age_category per Sample prop per Sample}
+age_category_per_Sample_prop_Sample <- dat %>%
+  group_by(Sample) %>%
+  count(age_category, Sample) %>%
+  mutate(Prop = round(n/sum(n), 2))
+
+kable(age_category_per_Sample_prop_Sample)
+age_category_per_Sample_prop_Sample
+```
+
+```{r age_category per Sample prop cross table}
+age_category_per_Sample_prop_Sample_cross_table <- dat %>%
+  group_by(Sample) %>%
+  count(age_category, Sample) %>%
+  mutate(Prop = round(n/sum(n), 2)) %>%
+  pivot_wider(names_from = Sample, values_from = c(n, Prop))
+
+kable(age_category_per_Sample_prop_Sample_cross_table)
+age_category_per_Sample_prop_Sample_cross_table
+```
+
+```{r age_category per Sample count cross table}
+age_category_per_Sample_count_cross_table <- dat %>%
+  count(age_category, Sample) %>%
+  spread(key = Sample, value = n) %>%
+  mutate(
+    EDGI = as.integer(replace_na(EDGI, 0)),
+    GLAD = as.integer(replace_na(GLAD, 0)),
+    NBR = as.integer(replace_na(NBR, 0)),
+    RAMP = as.integer(replace_na(RAMP, 0))
+  )
+
+kable(age_category_per_Sample_count_cross_table)
+age_category_per_Sample_count_cross_table
+```
+
+```{r age_category per Sample chisquare test}
+age_category_per_Sample_chissquare_test <- dat %>%
+  count(age_category, Sample) %>%
+  spread(key = Sample, value = n) %>%
+  select(-age_category) %>%
+  mutate(
+    EDGI = as.integer(replace_na(EDGI, 0)),
+    GLAD = as.integer(replace_na(GLAD, 0)),
+    NBR = as.integer(replace_na(NBR, 0)),
+    RAMP = as.integer(replace_na(RAMP, 0))
+  ) %>%
+  chisq.test() %>%
+  glance()
+
+kable(age_category_per_Sample_chissquare_test)
+age_category_per_Sample_chissquare_test
+```
+
+```{r age_category by Sample count plot}
+age_category_by_Sample_count_plot <- age_category_per_Sample_prop_Sample %>%
+  ggplot(mapping = aes(
+    x = age_category,
+    y = n)
+  ) +
+  geom_bar(
+    aes(fill = Sample),
+    stat="identity",
+    binwidth = 1,
+    position = position_dodge2(preserve = "single")
+  ) +
+  labs(
+    x = "age_category",
+    y = "Number of participants",
+    fill = "Sample") +
+  theme_personal +
+  scale_fill_manual(
+    values = COPINGpalette6
+  ) +
+  coord_flip()
+
+age_category_by_Sample_count_plot
+```
+
+```{r age_category by Sample prop plot}
+age_category_by_Sample_prop_plot <- age_category_per_Sample_prop_Sample %>%
+  ggplot(mapping = aes(
+    x = age_category,
+    y = Prop)
+  ) +
+  geom_bar(
+    aes(fill = Sample),
+    stat="identity",
+    binwidth = 1,
+    position = position_dodge2(preserve = "single")
+  ) +
+  labs(
+    x = "age_category",
+    y = "Percentage per sample",
+    fill = "Sample") +
+  theme_personal +
+  scale_fill_manual(
+    values = COPINGpalette6
+  ) +
+  coord_flip()
+
+age_category_by_Sample_prop_plot
+```
 

### 2020-08-26 PANCHANGE_analysis.Rmd
Gender and Ethnicity collapsed

@@
 disorder_columns <- c(
+  "control_numeric",  
   "depressive_disorders_numeric",
     "anxiety_disorders_numeric",
+    "mhd.posttraumatic_stress_disorder_ptsd_numeric",
     "eating_disorders_numeric",
     "obsessive_compulsive_disorders_numeric",
-    "psychotic_disorders_numeric",
-    "mhd.mania_hypomania_bipolar_or_manicdepression_numeric",
-    "mhd.posttraumatic_stress_disorder_ptsd_numeric",
-    "autism_spectrum_disorder_numeric",
     "mhd.attention_deficit_hyperactivity_disorder_numeric",
     "mhd.personality_disorder_numeric",
-    "control_numeric"
+    "autism_spectrum_disorder_numeric",
+    "mhd.mania_hypomania_bipolar_or_manicdepression_numeric",
+    "psychotic_disorders_numeric"
 )
@@
     Sample,
-    Gender,
-    Ethnicity,
+    Gender_collapsed,
+    Ethnicity_collapsed,
     all_of(diff_score_cols),
@@
 Arab
-```{r Disorder_inc by Ethnicity}
+```{r Disorder_inc by Ethnicity_collapsed}
 Disorder_inc_by_Ethnicity <- dat.long.psych %>%
   filter(Diagnosis == 1) %>%
-  count(Disorder_inc, Ethnicity) %>%
+  count(Disorder_inc, Ethnicity_collapsed) %>%
   mutate(Prop = round(n/sum(n), 2))
@@
 
-```{r Disorder_inc by Ethnicity plot}
+```{r Disorder_inc by Ethnicity_collapsed plot}
 Disorder_inc_by_Ethnicity %>%
@@
   geom_bar(
-    aes(fill = Ethnicity),
+    aes(fill = Ethnicity_collapsed),
     #    position = "dodge",
@@
     y = "Number of participants",
-    fill = "Ethnicity") +
+    fill = "Ethnicity_collapsed") +
   theme_personal +
@@
     Sample,
-    Gender,
-    Ethnicity,
+    Gender_collapsed,
+    Ethnicity_collapsed,
     Disorder_hierarchical,
@@
 
-Model 1: Model 0 + Sex + Age + Ethnicity + Time registration and baseline
+Model 1: Model 0 + Sex + Age + Ethnicity_collapsed + Time registration and baseline
 ```{r}
@@
     mhd.personality_disorder +
-    Gender + age_category + Ethnicity + time_diff_sign_up_coping,
+    Gender_collapsed + age_category + Ethnicity_collapsed + time_diff_sign_up_coping,
   data = dat)
@@
 
-Model 1: Model 0 + Sex + Age + Ethnicity + Time registration and baseline
+Model 1: Model 0 + Sex + Age + Ethnicity_collapsed + Time registration and baseline
 ```{r}
 model1 <- lm(
-  formula = pcl.diff_score_base_prepan ~ Disorder_hierarchical + Gender + age_category + Ethnicity + time_diff_sign_up_coping,
+  formula = pcl.diff_score_base_prepan ~ Disorder_hierarchical + Gender_collapsed + age_category + Ethnicity_collapsed + time_diff_sign_up_coping,
   data = dat)
@@
 
-Model 1: Model 0 + Sex + Age + Ethnicity + Time registration and baseline
+Model 1: Model 0 + Sex + Age + Ethnicity_collapsed + Time registration and baseline
 ```{r}
 model1 <- lm(
-  formula = gad.diff_score_base_prepan ~ Disorder + Gender + Age + Ethnicity + time_diff_sign_up_coping,
+  formula = gad.diff_score_base_prepan ~ Disorder + Gender_collapsed + Age + Ethnicity_collapsed + time_diff_sign_up_coping,
   data = dat)

### 2020-08-26 PANCHANGE_data_preprocessing2020-07-15.Rmd
added none_of_the_above columns to all mhd

@@
     mhd.bingeeating_disorder,
-    mhd.atypical_bingeeating_disorder
+    mhd.atypical_bingeeating_disorder,
+    mhd.ed_none_of_the_above = mhd.none_of_the_above
   ) %>%
@@
     mhd.personality_disorder = demographics.personality_disorder, # routing variable in EDGI is named differently; renamed here to match GLAD
-    mhd.attention_deficit_hyperactivity_disorder = demographics.attention_deficit_hyperactivity_disorder
+    mhd.attention_deficit_hyperactivity_disorder = demographics.attention_deficit_hyperactivity_disorder,
+    mhd.none_of_the_above = demographics.none_of_the_above.1,
+    mhd.none_of_the_above.1 = demographics.none_of_the_above.8
     ) %>%
@@
     mhd.bulimia_nervosa_unc = mhd.bulimia_nervosa,
-    mhd.bingeeating_disorder_unc = mhd.bingeeating_disorder
+    mhd.bingeeating_disorder_unc = mhd.bingeeating_disorder,
+    mhd.ed_none_of_the_above = mhd.none_of_the_above.2
   ) %>%
@@
     mhd.attention_deficit_hyperactivity_disorder = NA.30.attention_deficit_hyperactivity_disorder,
-    mhd.personality_disorder_diagnosed = NA.30.personality_disorder_diagnosed
+    mhd.personality_disorder_diagnosed = NA.30.personality_disorder_diagnosed,
+    mhd.none_of_the_above = NA.30.none_of_these,
+    mhd.none_of_the_above.1 = NA.30.none_of_these.1
   ) %>%
@@
        cumul = F)
+```
+
+```{r}
+mhd.raw.id %>%
+  select(
+    control,
+    mhd.none_of_the_above,
+    mhd.none_of_the_above.1
+  )
+
+mhd.raw.id %>%
+  group_by(mhd.none_of_the_above.1) %>%
+  count(
+    control,
+    mhd.none_of_the_above
+  )
+
+mhd.raw.id %>%
+  count(
+    control,
+    age_
+  )
+```
+
+```{r Check personality_cluster_c}
+if(GLAD == TRUE | NBR == TRUE | RAMP == TRUE) {
+mhd.raw.id %>%
+  select(
+    control,
+    depressive_disorders_numeric,
+    anxiety_disorders_numeric,
+    eating_disorders_numeric,
+    obsessive_compulsive_disorders_numeric,
+    psychotic_disorders_numeric,
+    mhd.mania_hypomania_bipolar_or_manicdepression_numeric,
+    mhd.posttraumatic_stress_disorder_ptsd_numeric,
+    autism_spectrum_disorder_numeric,
+    mhd.attention_deficit_hyperactivity_disorder_numeric,
+    mhd.personality_disorder_numeric, 
+  )
+}
 ```

### 2020-08-31 PANCHANGE_data_preprocessing2020-07-15.Rmd
investigating none of the above

@@
 ```{r}
+if(RAMP == TRUE) {
 mhd.raw.id %>%
@@
 mhd.raw.id %>%
-  group_by(mhd.none_of_the_above.1) %>%
+  group_by(control) %>%
   count(
-    control,
+    mhd.none_of_the_above.1,
     mhd.none_of_the_above
@@
   )
+}
+```
+
+Inspect the participants that do not qualify as double "None of these"
+```{r}
+if(RAMP == TRUE) {
+mhd.raw.id %>%
+  filter(
+    (mhd.none_of_the_above.1 == "Not None of these" |
+    mhd.none_of_the_above == "Not None of these") &
+      control == "Control"
+  )
+}
 ```

### 2020-08-31 PANCHANGE_data_preprocessing2020-07-15.Rmd
added prefer not to answer and dont know to mhd control

--- 2020-08-26 PANCHANGE_data_preprocessing2020-07-15.Rmd
@@
     mhd.none_of_the_above = NA.30.none_of_these,
-    mhd.none_of_the_above.1 = NA.30.none_of_these.1
+    mhd.dont_know = NA.30.dont_know,
+    mhd.prefer_not_to_answer = NA.30.prefer_not_to_answer,
+    mhd.none_of_the_above.1 = NA.30.none_of_these.1,
+    mhd.dont_know.1 = NA.30.dont_know.1,
+    mhd.prefer_not_to_answer.1 = NA.30.prefer_not_to_answer.1
   ) %>%
@@
 
-Agoraphonia and panic disorder group
+Agoraphobia and panic disorder group
 ```{r mhd agoraphobia_panic_disorder}
@@
     mhd.attention_deficit_hyperactivity_disorder_numeric == "0" &
-    mhd.personality_disorder_numeric == "0", 
+    mhd.personality_disorder_numeric == "0" &
+      mhd.prefer_not_to_answer_numeric == "0" & # added 31. August 2020
+      mhd.prefer_not_to_answer.1_numeric == "0" & # added 31. August 2020
+      mhd.dont_know_numeric == "0" & # added 31. August 2020
+      mhd.dont_know.1_numeric == "0", # added 31. August 2020
     true = 1, 
@@
 
-```{r}
+```{r mhd check none of the above}
+if(RAMP == TRUE) {
 mhd.raw.id %>%
@@
 
+#mhd.raw.id %>%
+#  count(
+#    control,
+#    age_
+#  )
+}
+```
+
+Inspect the participants that do not qualify as double "None of these"
+```{r RAMP none of these comparison}
+if(RAMP == TRUE) {
 mhd.raw.id %>%
-  count(
-    control,
-    age_
-  )
-```
-
-```{r Check personality_cluster_c}
+  filter(
+    (mhd.none_of_the_above.1 == "Not None of these" |
+    mhd.none_of_the_above == "Not None of these") &
+      control == "Control"
+  ) %>%
+    select(
+      mhd.none_of_the_above_numeric,
+      mhd.dont_know_numeric,
+      mhd.prefer_not_to_answer_numeric,
+      mhd.none_of_the_above.1_numeric,
+      mhd.dont_know.1_numeric,
+      mhd.prefer_not_to_answer.1_numeric
+      )
+}
+```
+
+```{r Check control columns}
 if(GLAD == TRUE | NBR == TRUE | RAMP == TRUE) {
@@
     mhd.attention_deficit_hyperactivity_disorder_numeric,
-    mhd.personality_disorder_numeric, 
+    mhd.personality_disorder_numeric
   )
@@
     comorbidity_total_count_factor_numeric,
-    comorbidity_total_count_factor
+    comorbidity_total_count_factor,
+    mhd.none_of_the_above,
+    mhd.none_of_the_above.1
     )
@@
 
-```{r rename dataset for ramp}
+```{r Rename dataset for ramp}
 if(RAMP == TRUE){
@@
 skimr::skim(dat)
+```
+
+```{r Investigating RAMP NAs}
+dat %>%
+  group_by(control) %>%
+  count(
+    mhd.none_of_the_above.1,
+    mhd.none_of_the_above,
+    control,
+    age_category
+  )
+
+dat %>%
+  select(contains("none"))
+
+dat %>%
+  filter(
+    (mhd.none_of_the_above.1 == "Not None of these" |
+    mhd.none_of_the_above == "Not None of these") &
+      control == "Control"
+  )
+
 ```

### 2020-09-01 PANCHANGE_data_preprocessing2020-07-15.Rmd
added other 23 controls that did not qualify as full controls

@@
     mhd.dont_know.1 = NA.30.dont_know.1,
-    mhd.prefer_not_to_answer.1 = NA.30.prefer_not_to_answer.1
+    mhd.prefer_not_to_answer.1 = NA.30.prefer_not_to_answer.1,
+    mhd.other = NA.30.other_please_tell_us_more
   ) %>%
@@
     mhd.none_of_the_above.1,
-    mhd.none_of_the_above
+    mhd.none_of_the_above,
+    mhd.other
   )
@@
       mhd.dont_know.1_numeric,
-      mhd.prefer_not_to_answer.1_numeric
+      mhd.prefer_not_to_answer.1_numeric,
+      mhd.other
       )

### 2020-09-01 PANCHANGE_data_preprocessing2020-07-15.Rmd
changed to mhd.other_please_tell_us_more

--- 2020-08-31 PANCHANGE_data_preprocessing2020-07-15.Rmd
@@
     mhd.dont_know.1 = NA.30.dont_know.1,
-    mhd.prefer_not_to_answer.1 = NA.30.prefer_not_to_answer.1
+    mhd.prefer_not_to_answer.1 = NA.30.prefer_not_to_answer.1,
+    mhd.other_please_tell_us_more = NA.30.other_please_tell_us_more
   ) %>%
@@
       mhd.dont_know_numeric == "0" & # added 31. August 2020
-      mhd.dont_know.1_numeric == "0", # added 31. August 2020
+      mhd.dont_know.1_numeric == "0" & # added 31. August 2020
+      mhd.other_please_tell_us_more_numeric == "0",
     true = 1, 
@@
     mhd.none_of_the_above.1,
-    mhd.none_of_the_above
+    mhd.none_of_the_above,
+    mhd.other_please_tell_us_more
   )
@@
       mhd.dont_know.1_numeric,
-      mhd.prefer_not_to_answer.1_numeric
+      mhd.prefer_not_to_answer.1_numeric,
+      mhd.other_please_tell_us_more_numeric
       )

### 2020-09-01 PANCHANGE_data_preprocessing2020-07-15.Rmd
added dont know pnta for NBR ED because of screening question

@@
     mhd.atypical_bingeeating_disorder,
-    mhd.ed_none_of_the_above = mhd.none_of_the_above
+    mhd.none_of_the_above_eating_disorder = mhd.none_of_the_above
   ) %>%
@@
     mhd.autism_aspergers_or_autistic_spectrum_disorder = mhd.autism_spectrum_disorder_asd,
+    mhd.other_please_tell_us_more = mhd.other,
     mhd.anorexia_nervosa_unc = mhd.anorexia_nervosa,
@@
     mhd.bingeeating_disorder_unc = mhd.bingeeating_disorder,
-    mhd.ed_none_of_the_above = mhd.none_of_the_above.2
+    mhd.other_eating_disorder_unc = mhd.other_eating_disorder,
+    mhd.none_of_the_above_eating_disorder_unc = mhd.none_of_the_above.2,
+    mhd.dont_know_eating_disorder_unc = mhd.dont_know.2,
+    mhd.prefer_not_to_answer_eating_disorder_unc = mhd.prefer_not_to_answer.2
   ) %>%
@@
                 mhd.bingeeating_disorder_unc_numeric == "1" ~ 1),
+    mhd.none_of_the_above_eating_disorder_numeric =
+      case_when(mhd.suspected_eating_disorder_diagnosed_numeric == "0" ~ 0,
+                mhd.none_of_the_above_eating_disorder_unc_numeric == "0" ~ 0,
+                mhd.none_of_the_above_eating_disorder_unc_numeric == "1" ~ 1),
+    mhd.dont_know_eating_disorder_numeric =
+      case_when(mhd.suspected_eating_disorder_diagnosed_numeric == "0" ~ 0,
+                mhd.dont_know_eating_disorder_unc_numeric == "0" ~ 0,
+                mhd.dont_know_eating_disorder_unc_numeric == "1" ~ 1),
+    mhd.prefer_not_to_answer_eating_disorder_numeric =
+      case_when(mhd.suspected_eating_disorder_diagnosed_numeric == "0" ~ 0,
+                mhd.prefer_not_to_answer_eating_disorder_unc_numeric == "0" ~ 0,
+                mhd.prefer_not_to_answer_eating_disorder_unc_numeric == "1" ~ 1),
+    mhd.other_eating_disorder_numeric = 
+      case_when(mhd.suspected_eating_disorder_diagnosed_numeric == "0" ~ 0,
+                mhd.other_eating_disorder_unc_numeric == "0" ~ 0,
+                mhd.other_eating_disorder_unc_numeric == "1" ~ 1),        
     mhd.anorexia_nervosa =
@@
                 mhd.bingeeating_disorder_unc_numeric == "0" ~ "Not Binge-eating disorder",
-                mhd.bingeeating_disorder_unc_numeric == "1" ~ "Binge-eating disorder")
+                mhd.bingeeating_disorder_unc_numeric == "1" ~ "Binge-eating disorder"),
+    mhd.none_of_the_above_eating_disorder =
+      case_when(mhd.suspected_eating_disorder_diagnosed_numeric == "0" ~ "Not None of the above",
+                mhd.none_of_the_above_eating_disorder_unc == "0" ~ "Not None of the above",
+                mhd.none_of_the_above_eating_disorder_unc == "1" ~ "None of the above"),
+    mhd.dont_know_eating_disorder =
+      case_when(mhd.suspected_eating_disorder_diagnosed_numeric == "0" ~ "Not Don't know",
+                mhd.dont_know_eating_disorder_numeric == "0" ~ "Not Don't know",
+                mhd.dont_know_eating_disorder_numeric == "1" ~ "Don't know"),
+    mhd.prefer_not_to_answer_eating_disorder =
+      case_when(mhd.suspected_eating_disorder_diagnosed_numeric == "0" ~ "Not Prefer not to answer",
+                mhd.prefer_not_to_answer_eating_disorder_unc == "0" ~ "Not Prefer not to answer",
+                mhd.prefer_not_to_answer_eating_disorder_unc == "1" ~ "Prefer not to answer"),
+    mhd.other_eating_disorder = 
+      case_when(mhd.suspected_eating_disorder_diagnosed_numeric == "0" ~ "Not Other eating disorder",
+                mhd.other_eating_disorder_unc_numeric == "0" ~ "Not Other eating disorder",
+                mhd.other_eating_disorder_unc_numeric == "1" ~ "Other eating disorder")
     )
@@
 These individuals have no self report diagnosis of any kind that we measure. 
-```{r mhd control}
+```{r mhd control GLAD RAMP}
+if(GLAD == TRUE | RAMP == TRUE) {
 mhd.raw.id <- mhd.raw.id %>%
@@
        cumul = F)
+}
+```
+
+```{r mhd control EDGI NBR}
+if(EDGI == TRUE | NBR == TRUE) {
+mhd.raw.id <- mhd.raw.id %>%
+  mutate(
+    control_numeric =
+      if_else(
+    depressive_disorders_numeric == "0" &
+    anxiety_disorders_numeric == "0" &
+    eating_disorders_numeric == "0" &
+    obsessive_compulsive_disorders_numeric == "0" &
+    psychotic_disorders_numeric == "0" &
+    mhd.mania_hypomania_bipolar_or_manicdepression_numeric == "0" &
+    mhd.posttraumatic_stress_disorder_ptsd_numeric == "0" &
+    autism_spectrum_disorder_numeric == "0" &
+    mhd.attention_deficit_hyperactivity_disorder_numeric == "0" &
+    mhd.personality_disorder_numeric == "0" &
+      mhd.prefer_not_to_answer_numeric == "0" & # added 31. August 2020
+      mhd.prefer_not_to_answer.1_numeric == "0" & # added 31. August 2020
+      mhd.dont_know_numeric == "0" & # added 31. August 2020
+      mhd.dont_know.1_numeric == "0" & # added 31. August 2020
+      mhd.other_please_tell_us_more_numeric == "0" &
+      mhd.dont_know_eating_disorder_numeric == "0",# &
+#      mhd.prefer_not_to_answer_eating_disorder_numeric == "0" &
+#      mhd.other_eating_disorder_numeric == "0",
+    true = 1,
+    false = 0, 
+    NA_real_)
+  )
+
+mhd.raw.id <- mhd.raw.id %>%
+  mutate(
+    control =
+      recode_factor(control_numeric,
+                    "0" = "No control",
+                    "1" = "Control",
+                    missing = NA_character_
+                    )
+  )
+
+mhd.raw.id %>%
+  freq(control,
+       cumul = F)
+}
 ```

### 2020-09-01 PANCHANGE_data_preprocessing2020-07-15.Rmd
modified control definition for nbr

@@
       mhd.other_please_tell_us_more_numeric == "0" &
-      mhd.dont_know_eating_disorder_numeric == "0",# &
-#      mhd.prefer_not_to_answer_eating_disorder_numeric == "0" &
-#      mhd.other_eating_disorder_numeric == "0",
+      mhd.dont_know_eating_disorder_numeric == "0" &
+      mhd.prefer_not_to_answer_eating_disorder_numeric == "0" &
+      mhd.other_eating_disorder_numeric == "0",
     true = 1,
@@
   )
-
-#mhd.raw.id %>%
-#  count(
-#    control,
-#    age_
-#  )
+}
+```
+
+```{r mhd check none of the above}
+if(NBR == TRUE) {
+mhd.raw.id %>%
+  group_by(control) %>%
+  count(
+    mhd.none_of_the_above.1,
+    mhd.none_of_the_above,
+    mhd.other_please_tell_us_more,
+    mhd.other_eating_disorder
+  )
 }

### 2020-09-02 PANCHANGE_analysis.Rmd

@@
 ```{r exclusion criteria dat}
-dat <- dat.raw %>%
+dat.2.timepoints <- dat.raw %>%
   filter(
@@
   )
+
+dim(dat.2.timepoints)
+```
+
+```{r}
+
+```
+
+```{r}
+dat.2.timepoints %>%
+  select(age_category) %>%
+  filter(is.na(age_category))
+```
+
+Exclusion
+```{r Exclusion}
+dat <- dat.2.timepoints %>%
+
 ```

### 2020-09-02 PANCHANGE_data_preprocessing2020-07-15.Rmd

@@
     mhd.atypical_bingeeating_disorder,
-    mhd.none_of_the_above_eating_disorder = mhd.none_of_the_above
+    mhd.other_eating_disorder,
+    mhd.none_of_the_above_eating_disorder = mhd.none_of_the_above,
+    mhd.dont_know_eating_disorder = mhd.dont_know,
+    mhd.prefer_not_to_answer_eating_disorder = mhd.prefer_not_to_answer
   ) %>%
@@
     mhd.none_of_the_above = demographics.none_of_the_above.1,
-    mhd.none_of_the_above.1 = demographics.none_of_the_above.8
+    mhd.dont_know = demographics.dont_know,
+    mhd.prefer_not_to_answer = demographics.prefer_not_to_answer.3,
+    mhd.none_of_the_above.1 = demographics.none_of_the_above.8,
+    mhd.dont_know.1 = demographics.dont_know.7,
+    mhd.prefer_not_to_answer.1 = demographics.prefer_not_to_answer.11,
+    mhd.other_please_tell_us_more = demographics.other.1
     ) %>%
@@
     mhd.other_eating_disorder = 
-      case_when(mhd.suspected_eating_disorder_diagnosed_numeric == "0" ~ "Not Other eating disorder",
-                mhd.other_eating_disorder_unc_numeric == "0" ~ "Not Other eating disorder",
-                mhd.other_eating_disorder_unc_numeric == "1" ~ "Other eating disorder")
+      case_when(mhd.suspected_eating_disorder_diagnosed_numeric == "0" ~ "Not Other eating disorder:",
+                mhd.other_eating_disorder_unc_numeric == "0" ~ "Not Other eating disorder:",
+                mhd.other_eating_disorder_unc_numeric == "1" ~ "Other eating disorder:")
     )
@@
 ```{r mhd check none of the above}
-if(NBR == TRUE) {
+if(NBR == TRUE | EDGI == TRUE) {
 mhd.raw.id %>%
@@
 ```{r Investigating RAMP NAs}
+if(RAMP == TRUE) {
 dat %>%
@@
   )
-
+}
 ```

### 2020-09-02 PANCHANGE_analysis.Rmd
Small edits to the set-up and comment about summarising whole datset.

@@
 #install.packages("skimr")
+#install.packages("polycor")
+#install.packages("corrplot")
+#install.packages("patchwork")
 ```
@@
 ```{r source file path}
-#source raw data directory: data.raw_path
+#source data directory: data_path
 source("../PANCHANGE_raw_path.R")
@@
 
+++MD: I had to cancel this chunk while running because it took too long - there are 473 variables in this dataset, so I don't think summarising all at once is useful!
 ```{r dat.coping summary, eval=FALSE, include=FALSE}

### 2020-09-02 PANCHANGE_analysis.Rmd
Added chunks to create 3 datasets for the analyses, excluding individuals on varying criteria.

@@
 ```{r dat.coping summary, eval=FALSE, include=FALSE}
-summarytools::dfSummary(
-  dat.raw,
-  graph.col = F,
-  valid.col = F,
-  labels.col = F)
+#summarytools::dfSummary(
+#  dat.raw,
+#  graph.col = F,
+#  valid.col = F,
+#  labels.col = F)
 ```
@@
 
+++MD: Need to decide what to do with the Arab grouping.
 ```{r Collapse Ethnicity}
@@
 # Exclusion
-
-## COPING
-Filter data frame to exclude participants that never answered COPING
-```{r exclusion criteria dat}
-dat.2.timepoints <- dat.raw %>%
+Filter data frame to create 3 datasets:
+  1. Diagnoses analyses
+        i. Exclude individuals with NA for MHD
+  2. Retrospective - baseline change anlyses
+        i. Exclude individuals with NAs for:
+              1. MHD
+              2. Age
+              3. Gender
+  3. Prepandemic - baseline change analyses
+          i. Exclude individuals with NAs for:
+              1. MHD
+              2. Age
+              3. Gender
+          ii. Exclude individuals with prepandemic data collected after 1st March.
+
+Diagnoses analyses
+Exclude individuals with NA for the MHD categories
+```{r exclusion criteria for diagnoses analysis}
+dat.mhd <- dat.raw %>%
   filter(
-    (data_group_gad == "Baseline and retrospective data" |
+    !is.na(depressive_disorders) &
+      !is.na(eating_disorders) &
+      !is.na(psychotic_disorders) &
+      !is.na(obsessive_compulsive_disorders) &
+      !is.na(autism_spectrum_disorder) &
+      !is.na(mhd.mania_hypomania_bipolar_or_manicdepression_numeric) &
+      !is.na(mhd.posttraumatic_stress_disorder_ptsd_numeric)
+  )
+
+dim(dat.mhd)
+
+```
+
+Retro-baseline analyses
+Exclude individuals with NA for MHD, age, gender
+```{r exclusion criteria for retro-baseline analysis}
+dat.retro <- dat.mhd %>%
+  filter(
+    ((data_group_gad == "Baseline and retrospective data" |
+      data_group_gad == "All prepandemic, baseline and retrospective data") |
+      (data_group_phq == "Baseline and retrospective data" |
+      data_group_phq == "All prepandemic, baseline and retrospective data") |
+      (data_group_pcl == "Baseline and retrospective data" |
+      data_group_pcl == "All prepandemic, baseline and retrospective data") |
+      (data_group_ocir == "Baseline and retrospective data" |
+      data_group_ocir == "All prepandemic, baseline and retrospective data")) &
+      !is.na(age_category) &
+      !is.na(Gender_collapsed)
+  )
+
+dim(dat.retro)
+```
+
+Prepan-baseline analyses
+Exclude individuals with NA for MHD, age, gender; exclude if prepan data collected after 1 March
+```{r exclusion criteria for prepan-baseline analysis}
+dat.prepan <- dat.mhd %>%
+  filter(
+    ((data_group_gad == "Baseline and retrospective data" |
       data_group_gad == "Prepandemic and baseline data" |
@@
       data_group_ocir == "Prepandemic and baseline data" |
-      data_group_ocir == "All prepandemic, baseline and retrospective data")
-  )
-
-dim(dat.2.timepoints)
-```
-
-```{r}
-
-```
-
-```{r}
-dat.2.timepoints %>%
-  select(age_category) %>%
-  filter(is.na(age_category))
-```
-
-Exclusion
-```{r Exclusion}
-dat <- dat.2.timepoints %>%
-
+      data_group_ocir == "All prepandemic, baseline and retrospective data")) &
+      !is.na(age_category) &
+      !is.na(Gender_collapsed) &
+      prepandemic_march_1_numeric == 1
+  )
+
+dim(dat.prepan)
 ```
@@
 ```{r dimensions of total dat}
-dim(dat)
-```
-
-```{r}
-dat %>%
+dim(dat.raw)
+```
+
+```{r disorders total count}
+dat.raw %>%
   freq(disorders_total_count)

### 2020-09-02 PANCHANGE_analysis.Rmd
Disorder hierarchy chunk amended to match Gerome's request.

@@
 
-```{r dimensions of total dat}
-dim(dat.raw)
-```
-
 ```{r disorders total count}
@@
 # Vectors for sum_score
-```{r Vectors with sum_score_cols}
-sum_score_cols <- dat %>%
+
+Diagnoses analyses
+```{r dat.mhd - Vectors with sum_score_cols}
+sum_score_cols <- dat.mhd %>%
   select(contains("sum_score")) %>%
@@
 
-phq.sum_score_cols <- dat %>%
+phq.sum_score_cols <- dat.mhd %>%
   select(contains("phq")) %>%
@@
 
-gad.sum_score_cols <- dat %>%
+gad.sum_score_cols <- dat.mhd %>%
   select(contains("gad")) %>%
@@
 
-ocir.sum_score_cols <- dat %>%
+ocir.sum_score_cols <- dat.mhd %>%
   select(contains("ocir")) %>%
@@
 
-pcl.sum_score_cols <- dat %>%
+pcl.sum_score_cols <- dat.mhd %>%
   select(contains("pcl")) %>%
@@
 # Vectors for diff_score
+
 ```{r Vectors with diff_score_cols}
-diff_score_cols <- dat %>%
+diff_score_cols <- dat.mhd %>%
   select(contains("diff_score")) %>% 
@@
 
-phq.diff_score_cols <- dat %>%
+phq.diff_score_cols <- dat.mhd %>%
   select(contains("phq")) %>%
@@
 
-gad.diff_score_cols <- dat %>%
+gad.diff_score_cols <- dat.mhd %>%
   select(contains("gad")) %>%
@@
 
-ocir.diff_score_cols <- dat %>%
+ocir.diff_score_cols <- dat.mhd %>%
   select(contains("ocir")) %>%
@@
 # Psychiatric disorder hierarchy
-
+------------
+OLD VERSIONS:
 control_numeric == 1 ~ 0,
@@
 control_numeric == 1 ~ 0,
-
-```{r Psychiatric disorders hierarchy}
-dat <- dat %>%
+------------
+
+Disorder hierarchy
+1: Psychotic disorders (create one with, create one without to test in analyses)
+2: Bipolar disorder
+3: MDD
+4: PTSD
+5: OCD
+6: Eating disorders
+7: Anxiety disorders
+
+## Hierarchy including psychosis
+Diagnoses analyses
+```{r Psychiatric disorders hierarchy including psychosis - dat.mhd}
+dat.mhd <- dat.mhd %>%
+  mutate(
+    Disorder_hierarchical_psychosis_numeric =
+      case_when(
+        psychotic_disorders_numeric == 1 ~ 7,
+        mhd.mania_hypomania_bipolar_or_manicdepression_numeric == 1 ~ 6,
+        depressive_disorders_numeric == 1 ~ 5,
+        mhd.posttraumatic_stress_disorder_ptsd_numeric == 1 ~ 4,
+        obsessive_compulsive_disorders_numeric == 1 ~ 3,
+        eating_disorders_numeric == 1 ~ 2,
+        anxiety_disorders_numeric == 1 ~ 1,
+        control_numeric == 1 ~ 0
+      )
+  )
+
+dat.mhd <- dat.mhd %>%
+  mutate(
+    Disorder_hierarchical_psychosis =
+      recode_factor(
+        Disorder_hierarchical_psychosis_numeric,
+        `0` = "Controls",
+        `1` = "Anxiety disorders",
+        `2` = "Eating disorders",
+        `3` = "OCDs",
+        `4` = "PTSD",
+        `5` = "Depressive disorders",
+        `6` = "Bipolar disorders",
+        `7` = "Psychotic disorders"
+      )
+  )
+
+dat.mhd %>%
+  freq(Disorder_hierarchical_psychosis)
+```
+
+Retro-baseline
+```{r Psychiatric disorders hierarchy including psychosis - dat.retro}
+dat.retro <- dat.retro %>%
+  mutate(
+    Disorder_hierarchical_psychosis_numeric =
+      case_when(
+        psychotic_disorders_numeric == 1 ~ 7,
+        mhd.mania_hypomania_bipolar_or_manicdepression_numeric == 1 ~ 6,
+        depressive_disorders_numeric == 1 ~ 5,
+        mhd.posttraumatic_stress_disorder_ptsd_numeric == 1 ~ 4,
+        obsessive_compulsive_disorders_numeric == 1 ~ 3,
+        eating_disorders_numeric == 1 ~ 2,
+        anxiety_disorders_numeric == 1 ~ 1,
+        control_numeric == 1 ~ 0
+      )
+  )
+
+dat.retro <- dat.retro %>%
+  mutate(
+    Disorder_hierarchical_psychosis =
+      recode_factor(
+        Disorder_hierarchical_psychosis_numeric,
+        `0` = "Controls",
+        `1` = "Anxiety disorders",
+        `2` = "Eating disorders",
+        `3` = "OCDs",
+        `4` = "PTSD",
+        `5` = "Depressive disorders",
+        `6` = "Bipolar disorders",
+        `7` = "Psychotic disorders"
+      )
+  )
+
+dat.retro %>%
+  freq(Disorder_hierarchical_psychosis)
+```
+
+Prepan-baseline
+++MD: For GLAD/EDGI we shouldn't have any controls, but some have crept in because they likely haven't ever received a diagnosis (despite qualifying on the CIDI or current measures of psychopathology).
+We should consider just excluding them.
+```{r Psychiatric disorders hierarchy including psychosis - dat.prepan}
+dat.prepan <- dat.prepan %>%
+  mutate(
+    Disorder_hierarchical_psychosis_numeric =
+      case_when(
+        psychotic_disorders_numeric == 1 ~ 7,
+        mhd.mania_hypomania_bipolar_or_manicdepression_numeric == 1 ~ 6,
+        depressive_disorders_numeric == 1 ~ 5,
+        mhd.posttraumatic_stress_disorder_ptsd_numeric == 1 ~ 4,
+        obsessive_compulsive_disorders_numeric == 1 ~ 3,
+        eating_disorders_numeric == 1 ~ 2,
+        anxiety_disorders_numeric == 1 ~ 1,
+        control_numeric == 1 ~ 0
+      )
+  )
+
+dat.prepan <- dat.prepan %>%
+  mutate(
+    Disorder_hierarchical_psychosis =
+      recode_factor(
+        Disorder_hierarchical_psychosis_numeric,
+        `0` = "Controls",
+        `1` = "Anxiety disorders",
+        `2` = "Eating disorders",
+        `3` = "OCDs",
+        `4` = "PTSD",
+        `5` = "Depressive disorders",
+        `6` = "Bipolar disorders",
+        `7` = "Psychotic disorders"
+      )
+  )
+
+dat.prepan %>%
+  freq(Disorder_hierarchical_psychosis)
+```
+
+## Hierarchy NOT including psychosis
+Diagnoses analyses
+```{r Psychiatric disorders hierarchy without psychosis - dat.mhd}
+dat.mhd <- dat.mhd %>%
   mutate(
@@
       case_when(
-        psychotic_disorders_numeric == 1 ~ 11,
-        mhd.mania_hypomania_bipolar_or_manicdepression_numeric == 1 ~ 10,
-        autism_spectrum_disorder_numeric == 1 ~ 9,
-        mhd.personality_disorder_numeric == 1 ~ 8,
-        mhd.attention_deficit_hyperactivity_disorder_numeric == 1 ~ 7,
-        obsessive_compulsive_disorders_numeric == 1 ~ 6,
-        eating_disorders_numeric == 1 ~ 5,
+        mhd.mania_hypomania_bipolar_or_manicdepression_numeric == 1 ~ 6,
+        depressive_disorders_numeric == 1 ~ 5,
         mhd.posttraumatic_stress_disorder_ptsd_numeric == 1 ~ 4,
-        (anxiety_disorders_numeric == 1 &
-        depressive_disorders_numeric == 1) ~ 3,
-        anxiety_disorders_numeric == 1 ~ 2,
-        depressive_disorders_numeric == 1 ~ 1,
+        obsessive_compulsive_disorders_numeric == 1 ~ 3,
+        eating_disorders_numeric == 1 ~ 2,
+        anxiety_disorders_numeric == 1 ~ 1,
         control_numeric == 1 ~ 0
@@
 
-dat <- dat %>%
+dat.mhd <- dat.mhd %>%
   mutate(
@@
         `0` = "Controls",
-        `1` = "Depressive disorders",
-        `2` = "Anxiety disorders",
-        `3` = "Depressive & anxiety disorders",
+        `1` = "Anxiety disorders",
+        `2` = "Eating disorders",
+        `3` = "OCDs",
         `4` = "PTSD",
-        `5` = "Eating disorders",
-        `6` = "OCDs",
-        `7` = "ADHD",
-        `8` = "Personality disorders",
-        `9` = "Autism",
-        `10` = "Bipolar disorders",
-        `11` = "Psychotic disorders"
-      )
-  )
-
-dat %>%
+        `5` = "Depressive disorders",
+        `6` = "Bipolar disorders"
+      )
+  )
+
+dat.mhd %>%
   freq(Disorder_hierarchical) 
+dat.mhd %>% 
+  freq(Disorder_hierarchical_psychosis)
+```
+
+Retro-baseline
+```{r Psychiatric disorders hierarchy without psychosis - dat.retro}
+dat.retro <- dat.retro %>%
+  mutate(
+    Disorder_hierarchical_numeric =
+      case_when(
+        mhd.mania_hypomania_bipolar_or_manicdepression_numeric == 1 ~ 6,
+        depressive_disorders_numeric == 1 ~ 5,
+        mhd.posttraumatic_stress_disorder_ptsd_numeric == 1 ~ 4,
+        obsessive_compulsive_disorders_numeric == 1 ~ 3,
+        eating_disorders_numeric == 1 ~ 2,
+        anxiety_disorders_numeric == 1 ~ 1,
+        control_numeric == 1 ~ 0
+      )
+  )
+
+dat.retro <- dat.retro %>%
+  mutate(
+    Disorder_hierarchical =
+      recode_factor(
+        Disorder_hierarchical_numeric,
+        `0` = "Controls",
+        `1` = "Anxiety disorders",
+        `2` = "Eating disorders",
+        `3` = "OCDs",
+        `4` = "PTSD",
+        `5` = "Depressive disorders",
+        `6` = "Bipolar disorders"
+      )
+  )
+
+dat.retro %>%
+  freq(Disorder_hierarchical)
+dat.retro %>%
+  freq(Disorder_hierarchical_psychosis)
+```
+
+Prepan-baseline
+```{r Psychiatric disorders hierarchy without psychosis - dat.prepan}
+dat.prepan <- dat.prepan %>%
+  mutate(
+    Disorder_hierarchical_numeric =
+      case_when(
+        mhd.mania_hypomania_bipolar_or_manicdepression_numeric == 1 ~ 6,
+        depressive_disorders_numeric == 1 ~ 5,
+        mhd.posttraumatic_stress_disorder_ptsd_numeric == 1 ~ 4,
+        obsessive_compulsive_disorders_numeric == 1 ~ 3,
+        eating_disorders_numeric == 1 ~ 2,
+        anxiety_disorders_numeric == 1 ~ 1,
+        control_numeric == 1 ~ 0
+      )
+  )
+
+dat.prepan <- dat.prepan %>%
+  mutate(
+    Disorder_hierarchical =
+      recode_factor(
+        Disorder_hierarchical_numeric,
+        `0` = "Controls",
+        `1` = "Anxiety disorders",
+        `2` = "Eating disorders",
+        `3` = "OCDs",
+        `4` = "PTSD",
+        `5` = "Depressive disorders",
+        `6` = "Bipolar disorders"
+      )
+  )
+
+dat.prepan %>%
+  freq(Disorder_hierarchical)
+dat.prepan %>%
+  freq(Disorder_hierarchical_psychosis)
 ```
@@
 Ask Leo?
+++MD: you'll have NAs for individuals that don't have one of the listed disorders in the hierarchy, but who have another diagnosis that excludes them from being a control (e.g.
+personality disorder, ADHD, ASD).
+We can add an "Other" category to cover those other diagnoses, or exclude them from these analyses.
 ```{r NAs in diagnosis}
-dat %>%
+dat.mhd %>%
+  filter(is.na(Disorder_hierarchical)) %>%
+  freq(Sample)
+
+dat.retro %>%
+  filter(is.na(Disorder_hierarchical)) %>%
+  freq(Sample)
+
+dat.prepan %>%
   filter(is.na(Disorder_hierarchical)) %>%

### 2020-09-03 PANCHANGE_analysis.Rmd

@@
 ## Correlation matrix
+++MD: Should we use the dat.mhd for this correlation matrix, as it has the least stringent inclusion criteria?
+Or just use dat.raw and include everyone?
+(alternatively, can create a correlation matrix for all 3 datasets)
 ```{r Correlation matrix of psychiatric disorders}
@@
 mhd.corr.mat <- hetcor(
-  as.data.frame(dat[,mhd.items]), # Specify the data
+  as.data.frame(dat.mhd[,mhd.items]), # Specify the data
   use = "pairwise.complete.obs" # Use all pairwise observations
@@
 ```{r gather to long format Disorder_hierarchical}
-dat.long.psych <- dat %>%
+dat.long.psych <- dat.mhd %>%
   gather(

### 2020-09-03 PANCHANGE_analysis.Rmd
Moved the exclusion block to lower in the script. Adjusted the disorder hierarchy section as a result of the change.

@@
 
-++MD: I had to cancel this chunk while running because it took too long - there are 473 variables in this dataset, so I don't think summarising all at once is useful!
 ```{r dat.coping summary, eval=FALSE, include=FALSE}
@@
 
-```{r}
+```{r sample frequencies}
 dat.raw %>%
@@
 
+# Vectors for sum_score
+
+Diagnoses analyses
+```{r dat.mhd - Vectors with sum_score_cols}
+sum_score_cols <- dat.mhd %>%
+  select(contains("sum_score")) %>%
+  select(-ends_with("raw")) %>%
+  colnames()
+
+sum_score_cols
+
+phq.sum_score_cols <- dat.mhd %>%
+  select(contains("phq")) %>%
+  select(contains("sum_score")) %>% 
+  select(-ends_with("raw")) %>%
+  select(-contains("8items")) %>%
+  colnames()
+
+phq.sum_score_cols
+
+gad.sum_score_cols <- dat.mhd %>%
+  select(contains("gad")) %>%
+  select(contains("sum_score")) %>% 
+  select(-ends_with("raw")) %>%
+  colnames()
+
+gad.sum_score_cols
+
+ocir.sum_score_cols <- dat.mhd %>%
+  select(contains("ocir")) %>%
+  select(contains("sum_score")) %>% 
+  select(-ends_with("raw")) %>%
+  colnames()
+
+ocir.sum_score_cols
+
+pcl.sum_score_cols <- dat.mhd %>%
+  select(contains("pcl")) %>%
+  select(contains("sum_score")) %>% 
+  select(-ends_with("raw")) %>%
+  colnames()
+
+pcl.sum_score_cols
+```
+
+# Vectors for diff_score
+
+```{r Vectors with diff_score_cols}
+diff_score_cols <- dat.mhd %>%
+  select(contains("diff_score")) %>% 
+  colnames()
+
+diff_score_cols
+
+phq.diff_score_cols <- dat.mhd %>%
+  select(contains("phq")) %>%
+  select(contains("diff_score")) %>% 
+  colnames()
+
+phq.diff_score_cols
+
+gad.diff_score_cols <- dat.mhd %>%
+  select(contains("gad")) %>%
+  select(contains("diff_score")) %>% 
+  colnames()
+
+gad.diff_score_cols
+
+ocir.diff_score_cols <- dat.mhd %>%
+  select(contains("ocir")) %>%
+  select(contains("diff_score")) %>% 
+  colnames()
+
+ocir.diff_score_cols
+```
+
+# ggplot theme
+Set up ggplot theme for the plots
+```{r ggplot theme}
+theme_personal <-  theme(
+    text = element_text(color = "black"),
+    axis.title = element_text(color = "black"),
+    axis.text = element_text(color = "black"),
+    axis.title.y = element_blank(), 
+    legend.background = element_blank(),
+    legend.box.background = element_blank(),
+    panel.background = element_blank(), 
+    panel.grid.minor.x = element_blank(),
+    panel.grid.major.x = element_line(
+      colour = "gray",
+      linetype = "dashed",
+      size = 0.2
+      ),
+    axis.ticks = element_blank()
+    )
+```
+
+# Psychiatric disorder hierarchy
+------------
+OLD VERSIONS:
+control_numeric == 1 ~ 0,
+depressive_disorders_numeric == 1 ~ 1,
+anxiety_disorders_numeric == 1 ~ 2,
+mhd.posttraumatic_stress_disorder_ptsd_numeric == 1 ~ 3,
+eating_disorders_numeric == 1 ~ 4,
+obsessive_compulsive_disorders_numeric == 1 ~ 5,
+mhd.attention_deficit_hyperactivity_disorder_numeric == 1 ~ 6,
+mhd.personality_disorder_numeric == 1 ~ 7,
+autism_spectrum_disorder_numeric == 1 ~ 8,
+mhd.mania_hypomania_bipolar_or_manicdepression_numeric == 1 ~ 9,
+psychotic_disorders_numeric == 1 ~ 10
+
+psychotic_disorders_numeric == 1 ~ 10
+mhd.mania_hypomania_bipolar_or_manicdepression_numeric == 1 ~ 9,
+autism_spectrum_disorder_numeric == 1 ~ 8,
+mhd.personality_disorder_numeric == 1 ~ 7,
+mhd.attention_deficit_hyperactivity_disorder_numeric == 1 ~ 6,
+obsessive_compulsive_disorders_numeric == 1 ~ 5,
+eating_disorders_numeric == 1 ~ 4,
+mhd.posttraumatic_stress_disorder_ptsd_numeric == 1 ~ 3,
+anxiety_disorders_numeric == 1 ~ 2,
+depressive_disorders_numeric == 1 ~ 1,
+control_numeric == 1 ~ 0,
+------------
+
+Disorder hierarchy
+1: Psychotic disorders (create one with, create one without to test in analyses)
+2: Bipolar disorder
+3: MDD
+4: PTSD
+5: OCD
+6: Eating disorders
+7: Anxiety disorders
+
+## Hierarchy including psychosis
+```{r Psychiatric disorders hierarchy including psychosis - dat.mhd}
+dat.raw <- dat.raw %>%
+  mutate(
+    Disorder_hierarchical_psychosis_numeric =
+      case_when(
+        psychotic_disorders_numeric == 1 ~ 7,
+        mhd.mania_hypomania_bipolar_or_manicdepression_numeric == 1 ~ 6,
+        depressive_disorders_numeric == 1 ~ 5,
+        mhd.posttraumatic_stress_disorder_ptsd_numeric == 1 ~ 4,
+        obsessive_compulsive_disorders_numeric == 1 ~ 3,
+        eating_disorders_numeric == 1 ~ 2,
+        anxiety_disorders_numeric == 1 ~ 1,
+        control_numeric == 1 ~ 0
+      )
+  )
+
+dat.raw <- dat.raw %>%
+  mutate(
+    Disorder_hierarchical_psychosis =
+      recode_factor(
+        Disorder_hierarchical_psychosis_numeric,
+        `0` = "Controls",
+        `1` = "Anxiety disorders",
+        `2` = "Eating disorders",
+        `3` = "OCDs",
+        `4` = "PTSD",
+        `5` = "Depressive disorders",
+        `6` = "Bipolar disorders",
+        `7` = "Psychotic disorders"
+      )
+  )
+
+dat.raw %>%
+  freq(Disorder_hierarchical_psychosis)
+```
+
+```{r Psychiatric disorders hierarchy without psychosis - dat.mhd}
+dat.raw <- dat.raw %>%
+  mutate(
+    Disorder_hierarchical_numeric =
+      case_when(
+        mhd.mania_hypomania_bipolar_or_manicdepression_numeric == 1 ~ 6,
+        depressive_disorders_numeric == 1 ~ 5,
+        mhd.posttraumatic_stress_disorder_ptsd_numeric == 1 ~ 4,
+        obsessive_compulsive_disorders_numeric == 1 ~ 3,
+        eating_disorders_numeric == 1 ~ 2,
+        anxiety_disorders_numeric == 1 ~ 1,
+        control_numeric == 1 ~ 0
+      )
+  )
+
+dat.raw <- dat.raw %>%
+  mutate(
+    Disorder_hierarchical =
+      recode_factor(
+        Disorder_hierarchical_numeric,
+        `0` = "Controls",
+        `1` = "Anxiety disorders",
+        `2` = "Eating disorders",
+        `3` = "OCDs",
+        `4` = "PTSD",
+        `5` = "Depressive disorders",
+        `6` = "Bipolar disorders"
+      )
+  )
+
+dat.raw %>%
+  freq(Disorder_hierarchical) 
+dat.raw %>% 
+  freq(Disorder_hierarchical_psychosis)
+```
+
+Investigate NAs 
+NAs are coded for individuals that don't have one of the listed disorders in the hierarchy, but who have another diagnosis that excludes them from being a control (e.g.
+personality disorder, ADHD, ASD).
+These individuals will be excluded from the analyses.
+```{r NAs in diagnosis}
+dat.raw %>%
+  filter(is.na(Disorder_hierarchical)) %>%
+  freq(Sample)
+```
+
 # Exclusion
@@
       !is.na(mhd.mania_hypomania_bipolar_or_manicdepression_numeric) &
-      !is.na(mhd.posttraumatic_stress_disorder_ptsd_numeric)
+      !is.na(mhd.posttraumatic_stress_disorder_ptsd_numeric) &
+      !is.na(control)
   )
@@
 
+# Psychiatric disorders
+
 ```{r disorders total count}
-dat.raw %>%
+dat.mhd %>%
   freq(disorders_total_count)
 ```
-
-# Vectors for sum_score
-
-Diagnoses analyses
-```{r dat.mhd - Vectors with sum_score_cols}
-sum_score_cols <- dat.mhd %>%
-  select(contains("sum_score")) %>%
-  select(-ends_with("raw")) %>%
-  colnames()
-
-sum_score_cols
-
-phq.sum_score_cols <- dat.mhd %>%
-  select(contains("phq")) %>%
-  select(contains("sum_score")) %>% 
-  select(-ends_with("raw")) %>%
-  select(-contains("8items")) %>%
-  colnames()
-
-phq.sum_score_cols
-
-gad.sum_score_cols <- dat.mhd %>%
-  select(contains("gad")) %>%
-  select(contains("sum_score")) %>% 
-  select(-ends_with("raw")) %>%
-  colnames()
-
-gad.sum_score_cols
-
-ocir.sum_score_cols <- dat.mhd %>%
-  select(contains("ocir")) %>%
-  select(contains("sum_score")) %>% 
-  select(-ends_with("raw")) %>%
-  colnames()
-
-ocir.sum_score_cols
-
-pcl.sum_score_cols <- dat.mhd %>%
-  select(contains("pcl")) %>%
-  select(contains("sum_score")) %>% 
-  select(-ends_with("raw")) %>%
-  colnames()
-
-pcl.sum_score_cols
-```
-
-# Vectors for diff_score
-
-```{r Vectors with diff_score_cols}
-diff_score_cols <- dat.mhd %>%
-  select(contains("diff_score")) %>% 
-  colnames()
-
-diff_score_cols
-
-phq.diff_score_cols <- dat.mhd %>%
-  select(contains("phq")) %>%
-  select(contains("diff_score")) %>% 
-  colnames()
-
-phq.diff_score_cols
-
-gad.diff_score_cols <- dat.mhd %>%
-  select(contains("gad")) %>%
-  select(contains("diff_score")) %>% 
-  colnames()
-
-gad.diff_score_cols
-
-ocir.diff_score_cols <- dat.mhd %>%
-  select(contains("ocir")) %>%
-  select(contains("diff_score")) %>% 
-  colnames()
-
-ocir.diff_score_cols
-```
-
-# ggplot theme
-Set up ggplot theme for the plots
-```{r ggplot theme}
-theme_personal <-  theme(
-    text = element_text(color = "black"),
-    axis.title = element_text(color = "black"),
-    axis.text = element_text(color = "black"),
-    axis.title.y = element_blank(), 
-    legend.background = element_blank(),
-    legend.box.background = element_blank(),
-    panel.background = element_blank(), 
-    panel.grid.minor.x = element_blank(),
-    panel.grid.major.x = element_line(
-      colour = "gray",
-      linetype = "dashed",
-      size = 0.2
-      ),
-    axis.ticks = element_blank()
-    )
-```
-
-# Psychiatric disorder hierarchy
-------------
-OLD VERSIONS:
-control_numeric == 1 ~ 0,
-depressive_disorders_numeric == 1 ~ 1,
-anxiety_disorders_numeric == 1 ~ 2,
-mhd.posttraumatic_stress_disorder_ptsd_numeric == 1 ~ 3,
-eating_disorders_numeric == 1 ~ 4,
-obsessive_compulsive_disorders_numeric == 1 ~ 5,
-mhd.attention_deficit_hyperactivity_disorder_numeric == 1 ~ 6,
-mhd.personality_disorder_numeric == 1 ~ 7,
-autism_spectrum_disorder_numeric == 1 ~ 8,
-mhd.mania_hypomania_bipolar_or_manicdepression_numeric == 1 ~ 9,
-psychotic_disorders_numeric == 1 ~ 10
-
-psychotic_disorders_numeric == 1 ~ 10
-mhd.mania_hypomania_bipolar_or_manicdepression_numeric == 1 ~ 9,
-autism_spectrum_disorder_numeric == 1 ~ 8,
-mhd.personality_disorder_numeric == 1 ~ 7,
-mhd.attention_deficit_hyperactivity_disorder_numeric == 1 ~ 6,
-obsessive_compulsive_disorders_numeric == 1 ~ 5,
-eating_disorders_numeric == 1 ~ 4,
-mhd.posttraumatic_stress_disorder_ptsd_numeric == 1 ~ 3,
-anxiety_disorders_numeric == 1 ~ 2,
-depressive_disorders_numeric == 1 ~ 1,
-control_numeric == 1 ~ 0,
-------------
-
-Disorder hierarchy
-1: Psychotic disorders (create one with, create one without to test in analyses)
-2: Bipolar disorder
-3: MDD
-4: PTSD
-5: OCD
-6: Eating disorders
-7: Anxiety disorders
-
-## Hierarchy including psychosis
-Diagnoses analyses
-```{r Psychiatric disorders hierarchy including psychosis - dat.mhd}
-dat.mhd <- dat.mhd %>%
-  mutate(
-    Disorder_hierarchical_psychosis_numeric =
-      case_when(
-        psychotic_disorders_numeric == 1 ~ 7,
-        mhd.mania_hypomania_bipolar_or_manicdepression_numeric == 1 ~ 6,
-        depressive_disorders_numeric == 1 ~ 5,
-        mhd.posttraumatic_stress_disorder_ptsd_numeric == 1 ~ 4,
-        obsessive_compulsive_disorders_numeric == 1 ~ 3,
-        eating_disorders_numeric == 1 ~ 2,
-        anxiety_disorders_numeric == 1 ~ 1,
-        control_numeric == 1 ~ 0
-      )
-  )
-
-dat.mhd <- dat.mhd %>%
-  mutate(
-    Disorder_hierarchical_psychosis =
-      recode_factor(
-        Disorder_hierarchical_psychosis_numeric,
-        `0` = "Controls",
-        `1` = "Anxiety disorders",
-        `2` = "Eating disorders",
-        `3` = "OCDs",
-        `4` = "PTSD",
-        `5` = "Depressive disorders",
-        `6` = "Bipolar disorders",
-        `7` = "Psychotic disorders"
-      )
-  )
-
-dat.mhd %>%
-  freq(Disorder_hierarchical_psychosis)
-```
-
-Retro-baseline
-```{r Psychiatric disorders hierarchy including psychosis - dat.retro}
-dat.retro <- dat.retro %>%
-  mutate(
-    Disorder_hierarchical_psychosis_numeric =
-      case_when(
-        psychotic_disorders_numeric == 1 ~ 7,
-        mhd.mania_hypomania_bipolar_or_manicdepression_numeric == 1 ~ 6,
-        depressive_disorders_numeric == 1 ~ 5,
-        mhd.posttraumatic_stress_disorder_ptsd_numeric == 1 ~ 4,
-        obsessive_compulsive_disorders_numeric == 1 ~ 3,
-        eating_disorders_numeric == 1 ~ 2,
-        anxiety_disorders_numeric == 1 ~ 1,
-        control_numeric == 1 ~ 0
-      )
-  )
-
-dat.retro <- dat.retro %>%
-  mutate(
-    Disorder_hierarchical_psychosis =
-      recode_factor(
-        Disorder_hierarchical_psychosis_numeric,
-        `0` = "Controls",
-        `1` = "Anxiety disorders",
-        `2` = "Eating disorders",
-        `3` = "OCDs",
-        `4` = "PTSD",
-        `5` = "Depressive disorders",
-        `6` = "Bipolar disorders",
-        `7` = "Psychotic disorders"
-      )
-  )
-
-dat.retro %>%
-  freq(Disorder_hierarchical_psychosis)
-```
-
-Prepan-baseline
-++MD: For GLAD/EDGI we shouldn't have any controls, but some have crept in because they likely haven't ever received a diagnosis (despite qualifying on the CIDI or current measures of psychopathology).
-We should consider just excluding them.
-```{r Psychiatric disorders hierarchy including psychosis - dat.prepan}
-dat.prepan <- dat.prepan %>%
-  mutate(
-    Disorder_hierarchical_psychosis_numeric =
-      case_when(
-        psychotic_disorders_numeric == 1 ~ 7,
-        mhd.mania_hypomania_bipolar_or_manicdepression_numeric == 1 ~ 6,
-        depressive_disorders_numeric == 1 ~ 5,
-        mhd.posttraumatic_stress_disorder_ptsd_numeric == 1 ~ 4,
-        obsessive_compulsive_disorders_numeric == 1 ~ 3,
-        eating_disorders_numeric == 1 ~ 2,
-        anxiety_disorders_numeric == 1 ~ 1,
-        control_numeric == 1 ~ 0
-      )
-  )
-
-dat.prepan <- dat.prepan %>%
-  mutate(
-    Disorder_hierarchical_psychosis =
-      recode_factor(
-        Disorder_hierarchical_psychosis_numeric,
-        `0` = "Controls",
-        `1` = "Anxiety disorders",
-        `2` = "Eating disorders",
-        `3` = "OCDs",
-        `4` = "PTSD",
-        `5` = "Depressive disorders",
-        `6` = "Bipolar disorders",
-        `7` = "Psychotic disorders"
-      )
-  )
-
-dat.prepan %>%
-  freq(Disorder_hierarchical_psychosis)
-```
-
-## Hierarchy NOT including psychosis
-Diagnoses analyses
-```{r Psychiatric disorders hierarchy without psychosis - dat.mhd}
-dat.mhd <- dat.mhd %>%
-  mutate(
-    Disorder_hierarchical_numeric =
-      case_when(
-        mhd.mania_hypomania_bipolar_or_manicdepression_numeric == 1 ~ 6,
-        depressive_disorders_numeric == 1 ~ 5,
-        mhd.posttraumatic_stress_disorder_ptsd_numeric == 1 ~ 4,
-        obsessive_compulsive_disorders_numeric == 1 ~ 3,
-        eating_disorders_numeric == 1 ~ 2,
-        anxiety_disorders_numeric == 1 ~ 1,
-        control_numeric == 1 ~ 0
-      )
-  )
-
-dat.mhd <- dat.mhd %>%
-  mutate(
-    Disorder_hierarchical =
-      recode_factor(
-        Disorder_hierarchical_numeric,
-        `0` = "Controls",
-        `1` = "Anxiety disorders",
-        `2` = "Eating disorders",
-        `3` = "OCDs",
-        `4` = "PTSD",
-        `5` = "Depressive disorders",
-        `6` = "Bipolar disorders"
-      )
-  )
-
-dat.mhd %>%
-  freq(Disorder_hierarchical) 
-dat.mhd %>% 
-  freq(Disorder_hierarchical_psychosis)
-```
-
-Retro-baseline
-```{r Psychiatric disorders hierarchy without psychosis - dat.retro}
-dat.retro <- dat.retro %>%
-  mutate(
-    Disorder_hierarchical_numeric =
-      case_when(
-        mhd.mania_hypomania_bipolar_or_manicdepression_numeric == 1 ~ 6,
-        depressive_disorders_numeric == 1 ~ 5,
-        mhd.posttraumatic_stress_disorder_ptsd_numeric == 1 ~ 4,
-        obsessive_compulsive_disorders_numeric == 1 ~ 3,
-        eating_disorders_numeric == 1 ~ 2,
-        anxiety_disorders_numeric == 1 ~ 1,
-        control_numeric == 1 ~ 0
-      )
-  )
-
-dat.retro <- dat.retro %>%
-  mutate(
-    Disorder_hierarchical =
-      recode_factor(
-        Disorder_hierarchical_numeric,
-        `0` = "Controls",
-        `1` = "Anxiety disorders",
-        `2` = "Eating disorders",
-        `3` = "OCDs",
-        `4` = "PTSD",
-        `5` = "Depressive disorders",
-        `6` = "Bipolar disorders"
-      )
-  )
-
-dat.retro %>%
-  freq(Disorder_hierarchical)
-dat.retro %>%
-  freq(Disorder_hierarchical_psychosis)
-```
-
-Prepan-baseline
-```{r Psychiatric disorders hierarchy without psychosis - dat.prepan}
-dat.prepan <- dat.prepan %>%
-  mutate(
-    Disorder_hierarchical_numeric =
-      case_when(
-        mhd.mania_hypomania_bipolar_or_manicdepression_numeric == 1 ~ 6,
-        depressive_disorders_numeric == 1 ~ 5,
-        mhd.posttraumatic_stress_disorder_ptsd_numeric == 1 ~ 4,
-        obsessive_compulsive_disorders_numeric == 1 ~ 3,
-        eating_disorders_numeric == 1 ~ 2,
-        anxiety_disorders_numeric == 1 ~ 1,
-        control_numeric == 1 ~ 0
-      )
-  )
-
-dat.prepan <- dat.prepan %>%
-  mutate(
-    Disorder_hierarchical =
-      recode_factor(
-        Disorder_hierarchical_numeric,
-        `0` = "Controls",
-        `1` = "Anxiety disorders",
-        `2` = "Eating disorders",
-        `3` = "OCDs",
-        `4` = "PTSD",
-        `5` = "Depressive disorders",
-        `6` = "Bipolar disorders"
-      )
-  )
-
-dat.prepan %>%
-  freq(Disorder_hierarchical)
-dat.prepan %>%
-  freq(Disorder_hierarchical_psychosis)
-```
-
-Investigate NAs 
-Ask Leo?
-++MD: you'll have NAs for individuals that don't have one of the listed disorders in the hierarchy, but who have another diagnosis that excludes them from being a control (e.g.
-personality disorder, ADHD, ASD).
-We can add an "Other" category to cover those other diagnoses, or exclude them from these analyses.
-```{r NAs in diagnosis}
-dat.mhd %>%
-  filter(is.na(Disorder_hierarchical)) %>%
-  freq(Sample)
-
-dat.retro %>%
-  filter(is.na(Disorder_hierarchical)) %>%
-  freq(Sample)
-
-dat.prepan %>%
-  filter(is.na(Disorder_hierarchical)) %>%
-  freq(Sample)
-```
-
-# Psychiatric disorders
 
@@
 ## Correlation matrix
-++MD: Should we use the dat.mhd for this correlation matrix, as it has the least stringent inclusion criteria?
-Or just use dat.raw and include everyone?
-(alternatively, can create a correlation matrix for all 3 datasets)
+Using dat.mhd for the correlation matrix.
 ```{r Correlation matrix of psychiatric disorders}

### 2020-09-03 PANCHANGE_analysis.Rmd
Exclusions chunk moved again to just above models, so that data manipulation chunks only have to be run once.

@@
 # Psychiatric disorder hierarchy
-------------
+- - - -
 OLD VERSIONS:
@@
 control_numeric == 1 ~ 0,
-------------
+- - - -
 
@@
 
-## Hierarchy including psychosis
-```{r Psychiatric disorders hierarchy including psychosis - dat.mhd}
-dat.raw <- dat.raw %>%
+```{r Psychiatric disorders hierarchy including psychosis}
+dat <- dat.raw %>%
   mutate(
@@
 
-dat.raw <- dat.raw %>%
+dat <- dat.raw %>%
   mutate(
@@
 
-dat.raw %>%
+dat %>%
   freq(Disorder_hierarchical_psychosis)
@@
 
-```{r Psychiatric disorders hierarchy without psychosis - dat.mhd}
-dat.raw <- dat.raw %>%
+```{r Psychiatric disorders hierarchy without psychosis}
+dat <- dat %>%
   mutate(
@@
 
-dat.raw <- dat.raw %>%
+dat <- dat %>%
   mutate(
@@
 
-dat.raw %>%
+dat %>%
   freq(Disorder_hierarchical) 
-dat.raw %>% 
+dat %>% 
   freq(Disorder_hierarchical_psychosis)
@@
 ```{r NAs in diagnosis}
-dat.raw %>%
+dat %>%
   filter(is.na(Disorder_hierarchical)) %>%
   freq(Sample)
+```
+
+Compare the GLAD/EDGI and COPING cohorts as a whole
++++CH: Diagnosis, ethnicity, gender, age
+
+# age_category
+```{r age_category per Sample prop per total}
+age_category_per_Sample_prop_total <- dat %>%
+  count(age_category, Sample) %>%
+  mutate(Prop = round(n/sum(n), 2))
+
+kable(age_category_per_Sample_prop_total)
+age_category_per_Sample_prop_total
+```
+
+```{r age_category per Sample prop per Sample}
+age_category_per_Sample_prop_Sample <- dat %>%
+  group_by(Sample) %>%
+  count(age_category, Sample) %>%
+  mutate(Prop = round(n/sum(n), 2))
+
+kable(age_category_per_Sample_prop_Sample)
+age_category_per_Sample_prop_Sample
+```
+
+```{r age_category per Sample prop cross table}
+age_category_per_Sample_prop_Sample_cross_table <- dat %>%
+  group_by(Sample) %>%
+  count(age_category, Sample) %>%
+  mutate(Prop = round(n/sum(n), 2)) %>%
+  pivot_wider(names_from = Sample, values_from = c(n, Prop))
+
+kable(age_category_per_Sample_prop_Sample_cross_table)
+age_category_per_Sample_prop_Sample_cross_table
+```
+
+```{r age_category per Sample count cross table}
+age_category_per_Sample_count_cross_table <- dat %>%
+  count(age_category, Sample) %>%
+  spread(key = Sample, value = n) %>%
+  mutate(
+    EDGI = as.integer(replace_na(EDGI, 0)),
+    GLAD = as.integer(replace_na(GLAD, 0)),
+    NBR = as.integer(replace_na(NBR, 0)),
+    RAMP = as.integer(replace_na(RAMP, 0))
+  )
+
+kable(age_category_per_Sample_count_cross_table)
+age_category_per_Sample_count_cross_table
+```
+
+```{r age_category per Sample chisquare test}
+age_category_per_Sample_chissquare_test <- dat %>%
+  count(age_category, Sample) %>%
+  spread(key = Sample, value = n) %>%
+  select(-age_category) %>%
+  mutate(
+    EDGI = as.integer(replace_na(EDGI, 0)),
+    GLAD = as.integer(replace_na(GLAD, 0)),
+    NBR = as.integer(replace_na(NBR, 0)),
+    RAMP = as.integer(replace_na(RAMP, 0))
+  ) %>%
+  chisq.test() %>%
+  glance()
+
+kable(age_category_per_Sample_chissquare_test)
+age_category_per_Sample_chissquare_test
+```
+
+```{r age_category by Sample count plot}
+age_category_by_Sample_count_plot <- age_category_per_Sample_prop_Sample %>%
+  ggplot(mapping = aes(
+    x = age_category,
+    y = n)
+  ) +
+  geom_bar(
+    aes(fill = Sample),
+    stat="identity",
+    binwidth = 1,
+    position = position_dodge2(preserve = "single")
+  ) +
+  labs(
+    x = "age_category",
+    y = "Number of participants",
+    fill = "Sample") +
+  theme_personal +
+  scale_fill_manual(
+    values = COPINGpalette6
+  ) +
+  coord_flip()
+
+age_category_by_Sample_count_plot
+```
+
+```{r age_category by Sample prop plot}
+age_category_by_Sample_prop_plot <- age_category_per_Sample_prop_Sample %>%
+  ggplot(mapping = aes(
+    x = age_category,
+    y = Prop)
+  ) +
+  geom_bar(
+    aes(fill = Sample),
+    stat="identity",
+    binwidth = 1,
+    position = position_dodge2(preserve = "single")
+  ) +
+  labs(
+    x = "age_category",
+    y = "Percentage per sample",
+    fill = "Sample") +
+  theme_personal +
+  scale_fill_manual(
+    values = COPINGpalette6
+  ) +
+  coord_flip()
+
+age_category_by_Sample_prop_plot
+```
+
+# Ethnicity_collapsed
+```{r Ethnicity_collapsed per Sample prop per total}
+Ethnicity_collapsed_per_Sample_prop_total <- dat %>%
+  count(Ethnicity_collapsed, Sample) %>%
+  mutate(Prop = round(n/sum(n), 2))
+
+kable(Ethnicity_collapsed_per_Sample_prop_total)
+Ethnicity_collapsed_per_Sample_prop_total
+```
+
+```{r Ethnicity_collapsed per Sample prop per Sample}
+Ethnicity_collapsed_per_Sample_prop_Sample <- dat %>%
+  group_by(Sample) %>%
+  count(Ethnicity_collapsed, Sample) %>%
+  mutate(Prop = round(n/sum(n), 2))
+
+kable(Ethnicity_collapsed_per_Sample_prop_Sample)
+Ethnicity_collapsed_per_Sample_prop_Sample
+```
+
+```{r Ethnicity_collapsed per Sample prop cross table}
+Ethnicity_collapsed_per_Sample_prop_Sample_cross_table <- dat %>%
+  group_by(Sample) %>%
+  count(Ethnicity_collapsed, Sample) %>%
+  mutate(Prop = round(n/sum(n), 2)) %>%
+  pivot_wider(names_from = Sample, values_from = c(n, Prop))
+
+kable(Ethnicity_collapsed_per_Sample_prop_Sample_cross_table)
+Ethnicity_collapsed_per_Sample_prop_Sample_cross_table
+```
+
+```{r Ethnicity_collapsed per Sample count cross table}
+Ethnicity_collapsed_per_Sample_count_cross_table <- dat %>%
+  count(Ethnicity_collapsed, Sample) %>%
+  spread(key = Sample, value = n) %>%
+  mutate(
+    EDGI = as.integer(replace_na(EDGI, 0)),
+    GLAD = as.integer(replace_na(GLAD, 0)),
+    NBR = as.integer(replace_na(NBR, 0)),
+    RAMP = as.integer(replace_na(RAMP, 0))
+  )
+
+kable(Ethnicity_collapsed_per_Sample_count_cross_table)
+Ethnicity_collapsed_per_Sample_count_cross_table
+```
+
+```{r Ethnicity_collapsed per Sample chisquare test}
+Ethnicity_collapsed_per_Sample_chissquare_test <- dat %>%
+  count(Ethnicity_collapsed, Sample) %>%
+  spread(key = Sample, value = n) %>%
+  select(-Ethnicity_collapsed) %>%
+  mutate(
+    EDGI = as.integer(replace_na(EDGI, 0)),
+    GLAD = as.integer(replace_na(GLAD, 0)),
+    NBR = as.integer(replace_na(NBR, 0)),
+    RAMP = as.integer(replace_na(RAMP, 0))
+  ) %>%
+  chisq.test() %>%
+  glance()
+
+kable(Ethnicity_collapsed_per_Sample_chissquare_test)
+Ethnicity_collapsed_per_Sample_chissquare_test
+```
+
+```{r Ethnicity_collapsed by Sample count plot}
+Ethnicity_collapsed_by_Sample_count_plot <- Ethnicity_collapsed_per_Sample_prop_Sample %>%
+  ggplot(mapping = aes(
+    x = Ethnicity_collapsed,
+    y = n)
+  ) +
+  geom_bar(
+    aes(fill = Sample),
+    stat="identity",
+    binwidth = 1,
+    position = position_dodge2(preserve = "single")
+  ) +
+  labs(
+    x = "Ethnicity_collapsed",
+    y = "Number of participants",
+    fill = "Sample") +
+  theme_personal +
+  scale_fill_manual(
+    values = COPINGpalette6
+  ) +
+  coord_flip()
+
+Ethnicity_collapsed_by_Sample_count_plot
+```
+
+```{r Ethnicity_collapsed by Sample prop plot}
+Ethnicity_collapsed_by_Sample_prop_plot <- Ethnicity_collapsed_per_Sample_prop_Sample %>%
+  ggplot(mapping = aes(
+    x = Ethnicity_collapsed,
+    y = Prop)
+  ) +
+  geom_bar(
+    aes(fill = Sample),
+    stat="identity",
+    binwidth = 1,
+    position = position_dodge2(preserve = "single")
+  ) +
+  labs(
+    x = "Ethnicity_collapsed",
+    y = "Percentage per sample",
+    fill = "Sample") +
+  theme_personal +
+  scale_fill_manual(
+    values = COPINGpalette6
+  ) +
+  coord_flip()
+
+Ethnicity_collapsed_by_Sample_prop_plot
+```
+
+# Gender_collapsed
+```{r Gender_collapsed per Sample prop per total}
+Gender_collapsed_per_Sample_prop_total <- dat %>%
+  count(Gender_collapsed, Sample) %>%
+  mutate(Prop = round(n/sum(n), 2))
+
+kable(Gender_collapsed_per_Sample_prop_total)
+Gender_collapsed_per_Sample_prop_total
+```
+
+```{r Gender_collapsed per Sample prop per Sample}
+Gender_collapsed_per_Sample_prop_Sample <- dat %>%
+  group_by(Sample) %>%
+  count(Gender_collapsed, Sample) %>%
+  mutate(Prop = round(n/sum(n), 2))
+
+kable(Gender_collapsed_per_Sample_prop_Sample)
+Gender_collapsed_per_Sample_prop_Sample
+```
+
+```{r Gender_collapsed per Sample prop cross table}
+Gender_collapsed_per_Sample_prop_Sample_cross_table <- dat %>%
+  group_by(Sample) %>%
+  count(Gender_collapsed, Sample) %>%
+  mutate(Prop = round(n/sum(n), 2)) %>%
+  pivot_wider(names_from = Sample, values_from = c(n, Prop))
+
+kable(Gender_collapsed_per_Sample_prop_Sample_cross_table)
+Gender_collapsed_per_Sample_prop_Sample_cross_table
+```
+
+```{r Gender_collapsed per Sample count cross table}
+Gender_collapsed_per_Sample_count_cross_table <- dat %>%
+  count(Gender_collapsed, Sample) %>%
+  spread(key = Sample, value = n) %>%
+  mutate(
+    EDGI = as.integer(replace_na(EDGI, 0)),
+    GLAD = as.integer(replace_na(GLAD, 0)),
+    NBR = as.integer(replace_na(NBR, 0)),
+    RAMP = as.integer(replace_na(RAMP, 0))
+  )
+
+kable(Gender_collapsed_per_Sample_count_cross_table)
+Gender_collapsed_per_Sample_count_cross_table
+```
+
+```{r Gender_collapsed per Sample chisquare test}
+Gender_collapsed_per_Sample_chissquare_test <- dat %>%
+  count(Gender_collapsed, Sample) %>%
+  spread(key = Sample, value = n) %>%
+  select(-Gender_collapsed) %>%
+  mutate(
+    EDGI = as.integer(replace_na(EDGI, 0)),
+    GLAD = as.integer(replace_na(GLAD, 0)),
+    NBR = as.integer(replace_na(NBR, 0)),
+    RAMP = as.integer(replace_na(RAMP, 0))
+  ) %>%
+  chisq.test() %>%
+  glance()
+
+kable(Gender_collapsed_per_Sample_chissquare_test)
+Gender_collapsed_per_Sample_chissquare_test
+```
+
+```{r Gender_collapsed by Sample count plot}
+Gender_collapsed_by_Sample_count_plot <- Gender_collapsed_per_Sample_prop_Sample %>%
+  ggplot(mapping = aes(
+    x = Gender_collapsed,
+    y = n)
+  ) +
+  geom_bar(
+    aes(fill = Sample),
+    stat="identity",
+    binwidth = 1,
+    position = position_dodge2(preserve = "single")
+  ) +
+  labs(
+    x = "Gender_collapsed",
+    y = "Number of participants",
+    fill = "Sample") +
+  theme_personal +
+  scale_fill_manual(
+    values = COPINGpalette6
+  ) +
+  coord_flip()
+
+Gender_collapsed_by_Sample_count_plot
+```
+
+```{r Gender_collapsed by Sample prop plot}
+Gender_collapsed_by_Sample_prop_plot <- Gender_collapsed_per_Sample_prop_Sample %>%
+  ggplot(mapping = aes(
+    x = Gender_collapsed,
+    y = Prop)
+  ) +
+  geom_bar(
+    aes(fill = Sample),
+    stat="identity",
+    binwidth = 1,
+    position = position_dodge2(preserve = "single")
+  ) +
+  labs(
+    x = "Gender_collapsed",
+    y = "Percentage per sample",
+    fill = "Sample") +
+  theme_personal +
+  scale_fill_manual(
+    values = COPINGpalette6
+  ) +
+  coord_flip()
+
+Gender_collapsed_by_Sample_prop_plot
+```
+
+# highest_education
+```{r highest_education per Sample prop per total}
+highest_education_per_Sample_prop_total <- dat %>%
+  count(highest_education, Sample) %>%
+  mutate(Prop = round(n/sum(n), 2))
+
+kable(highest_education_per_Sample_prop_total)
+highest_education_per_Sample_prop_total
+```
+
+```{r highest_education per Sample prop per Sample}
+highest_education_per_Sample_prop_Sample <- dat %>%
+  group_by(Sample) %>%
+  count(highest_education, Sample) %>%
+  mutate(Prop = round(n/sum(n), 2))
+
+kable(highest_education_per_Sample_prop_Sample)
+highest_education_per_Sample_prop_Sample
+```
+
+```{r highest_education per Sample prop cross table}
+highest_education_per_Sample_prop_Sample_cross_table <- dat %>%
+  group_by(Sample) %>%
+  count(highest_education, Sample) %>%
+  mutate(Prop = round(n/sum(n), 2)) %>%
+  pivot_wider(names_from = Sample, values_from = c(n, Prop))
+
+kable(highest_education_per_Sample_prop_Sample_cross_table)
+highest_education_per_Sample_prop_Sample_cross_table
+```
+
+```{r highest_education per Sample count cross table}
+highest_education_per_Sample_count_cross_table <- dat %>%
+  count(highest_education, Sample) %>%
+  spread(key = Sample, value = n) %>%
+  mutate(
+    EDGI = as.integer(replace_na(EDGI, 0)),
+    GLAD = as.integer(replace_na(GLAD, 0)),
+    NBR = as.integer(replace_na(NBR, 0)),
+    RAMP = as.integer(replace_na(RAMP, 0))
+  )
+
+kable(highest_education_per_Sample_count_cross_table)
+highest_education_per_Sample_count_cross_table
+```
+
+```{r highest_education per Sample chisquare test}
+highest_education_per_Sample_chissquare_test <- dat %>%
+  count(highest_education, Sample) %>%
+  spread(key = Sample, value = n) %>%
+  select(-highest_education) %>%
+  mutate(
+    EDGI = as.integer(replace_na(EDGI, 0)),
+    GLAD = as.integer(replace_na(GLAD, 0)),
+    NBR = as.integer(replace_na(NBR, 0)),
+    RAMP = as.integer(replace_na(RAMP, 0))
+  ) %>%
+  chisq.test() %>%
+  glance()
+
+kable(highest_education_per_Sample_chissquare_test)
+highest_education_per_Sample_chissquare_test
+```
+
+```{r highest_education by Sample count plot}
+highest_education_by_Sample_count_plot <- highest_education_per_Sample_prop_Sample %>%
+  ggplot(mapping = aes(
+    x = highest_education,
+    y = n)
+  ) +
+  geom_bar(
+    aes(fill = Sample),
+    stat="identity",
+    binwidth = 1,
+    position = position_dodge2(preserve = "single")
+  ) +
+  labs(
+    x = "highest_education",
+    y = "Number of participants",
+    fill = "Sample") +
+  theme_personal +
+  scale_fill_manual(
+    values = COPINGpalette6
+  ) +
+  coord_flip()
+
+highest_education_by_Sample_count_plot
+```
+
+```{r highest_education by Sample prop plot}
+highest_education_by_Sample_prop_plot <- highest_education_per_Sample_prop_Sample %>%
+  ggplot(mapping = aes(
+    x = highest_education,
+    y = Prop)
+  ) +
+  geom_bar(
+    aes(fill = Sample),
+    stat="identity",
+    binwidth = 1,
+    position = position_dodge2(preserve = "single")
+  ) +
+  labs(
+    x = "highest_education",
+    y = "Percentage per sample",
+    fill = "Sample") +
+  theme_personal +
+  scale_fill_manual(
+    values = COPINGpalette6
+  ) +
+  coord_flip()
+
+highest_education_by_Sample_prop_plot
+```
+
+# key_worker
+```{r key_worker per Sample prop per total}
+key_worker_per_Sample_prop_total <- dat %>%
+  count(key_worker, Sample) %>%
+  mutate(Prop = round(n/sum(n), 2))
+
+kable(key_worker_per_Sample_prop_total)
+key_worker_per_Sample_prop_total
+```
+
+```{r key_worker per Sample prop per Sample}
+key_worker_per_Sample_prop_Sample <- dat %>%
+  group_by(Sample) %>%
+  count(key_worker, Sample) %>%
+  mutate(Prop = round(n/sum(n), 2))
+
+kable(key_worker_per_Sample_prop_Sample)
+key_worker_per_Sample_prop_Sample
+```
+
+```{r key_worker per Sample prop cross table}
+key_worker_per_Sample_prop_Sample_cross_table <- dat %>%
+  group_by(Sample) %>%
+  count(key_worker, Sample) %>%
+  mutate(Prop = round(n/sum(n), 2)) %>%
+  pivot_wider(names_from = Sample, values_from = c(n, Prop))
+
+kable(key_worker_per_Sample_prop_Sample_cross_table)
+key_worker_per_Sample_prop_Sample_cross_table
+```
+
+```{r key_worker per Sample count cross table}
+key_worker_per_Sample_count_cross_table <- dat %>%
+  count(key_worker, Sample) %>%
+  spread(key = Sample, value = n) %>%
+  mutate(
+    EDGI = as.integer(replace_na(EDGI, 0)),
+    GLAD = as.integer(replace_na(GLAD, 0)),
+    NBR = as.integer(replace_na(NBR, 0)),
+    RAMP = as.integer(replace_na(RAMP, 0))
+  )
+
+kable(key_worker_per_Sample_count_cross_table)
+key_worker_per_Sample_count_cross_table
+```
+
+```{r key_worker per Sample chisquare test}
+key_worker_per_Sample_chissquare_test <- dat %>%
+  count(key_worker, Sample) %>%
+  spread(key = Sample, value = n) %>%
+  select(-key_worker) %>%
+  mutate(
+    EDGI = as.integer(replace_na(EDGI, 0)),
+    GLAD = as.integer(replace_na(GLAD, 0)),
+    NBR = as.integer(replace_na(NBR, 0)),
+    RAMP = as.integer(replace_na(RAMP, 0))
+  ) %>%
+  chisq.test() %>%
+  glance()
+
+kable(key_worker_per_Sample_chissquare_test)
+key_worker_per_Sample_chissquare_test
+```
+
+```{r key_worker by Sample count plot}
+key_worker_by_Sample_count_plot <- key_worker_per_Sample_prop_Sample %>%
+  ggplot(mapping = aes(
+    x = key_worker,
+    y = n)
+  ) +
+  geom_bar(
+    aes(fill = Sample),
+    stat="identity",
+    binwidth = 1,
+    position = position_dodge2(preserve = "single")
+  ) +
+  labs(
+    x = "key_worker",
+    y = "Number of participants",
+    fill = "Sample") +
+  theme_personal +
+  scale_fill_manual(
+    values = COPINGpalette6
+  ) +
+  coord_flip()
+
+key_worker_by_Sample_count_plot
+```
+
+```{r key_worker by Sample prop plot}
+key_worker_by_Sample_prop_plot <- key_worker_per_Sample_prop_Sample %>%
+  ggplot(mapping = aes(
+    x = key_worker,
+    y = Prop)
+  ) +
+  geom_bar(
+    aes(fill = Sample),
+    stat="identity",
+    binwidth = 1,
+    position = position_dodge2(preserve = "single")
+  ) +
+  labs(
+    x = "key_worker",
+    y = "Percentage per sample",
+    fill = "Sample") +
+  theme_personal +
+  scale_fill_manual(
+    values = COPINGpalette6
+  ) +
+  coord_flip()
+
+key_worker_by_Sample_prop_plot
+```
+
+# COVID
+## Recode variable
+```{r gad covid test positive double}
+dat <- dat %>%
+  mutate(covid_test_positive_double_numeric =
+           case_when(
+             (respiratory.throat_swab_test_nose_numeric == 1 &
+               respiratory.results_antibody_test_numeric == 1) ~ 2,
+             respiratory.throat_swab_test_nose_numeric == 1 ~ 1,
+             respiratory.throat_swab_test_nose_numeric == 2 ~ 0,
+             respiratory.results_antibody_test_numeric == 1 ~ 1,
+             respiratory.results_antibody_test_numeric == 2 ~ 0
+           )
+         )
+
+dat <- dat %>%
+  mutate(covid_test_positive_double =
+           recode_factor(
+             covid_test_positive_double_numeric,
+             `0` = "Negative",
+             `1` = "Positive",
+             `2` = "Double positive"
+           )
+         )
+
+dat %>%
+  freq(covid_test_positive_double)
+```
+
+```{r gad covid test positive}
+dat <- dat %>%
+  mutate(gad.covid_test_positive_numeric =
+           case_when(
+             (respiratory.throat_swab_test_nose_numeric == 1 &
+               respiratory.results_antibody_test_numeric == 1) ~ 1, # with two positive test results get coded as positive
+             respiratory.throat_swab_test_nose_numeric == 1 ~ 1,
+             respiratory.throat_swab_test_nose_numeric == 2 ~ 0,
+             respiratory.results_antibody_test_numeric == 1 ~ 1,
+             respiratory.results_antibody_test_numeric == 2 ~ 0
+           )
+         )
+
+dat <- dat %>%
+  mutate(covid_test_positive =
+           recode_factor(
+             gad.covid_test_positive_numeric,
+             `0` = "Negative",
+             `1` = "Positive"
+#             `2` = "Double positive"
+           )
+         )
+
+dat %>%
+  freq(covid_test_positive)
+```
+
+## COVID swab test positive
+```{r COVID positive swap}
+dat %>%
+  count(respiratory.throat_swab_test_nose, Sample) %>%
+  mutate(Prop = round(n/sum(n), 2))
+```
+
+## antibody test
+```{r COVID positive antibody test}
+dat %>%
+  count(respiratory.results_antibody_test, Sample) %>%
+  mutate(Prop = round(n/sum(n), 2))
+```
+
+## COVID probable diagnosis
+```{r COVID probable diagnosis}
+dat %>%
+  count(covid_probable_case_incl_screening, Sample) %>%
+  mutate(Prop = round(n/sum(n), 2))
+```
+
+## Cross table probable covid and covid test positive
+```{r Cross table probable covid and covid test positive}
+dat %>%
+  count(covid_test_positive, covid_probable_case_incl_screening) %>%
+  spread(key = covid_test_positive, value = n)
+```
+
+# Create data set per cohort
+
+## GAD
+```{r}
+dat.gad <- dat %>%
+#  drop_na() %>%
+  filter(
+    (data_group_gad == "Baseline and retrospective data" |
+      data_group_gad == "Prepandemic and baseline data" |
+      data_group_gad == "All prepandemic, baseline and retrospective data")
+  )
+
+dim(dat.gad)
+```
+
+# Questionnaire comparions
+
+## gad
+
+### Split sample in improvement and worsening
+```{r gad improvment worsening stratification}
+dat <- dat %>%
+  mutate(gad.change_binary_numeric =
+           case_when(
+             gad.pandemic_felt_feelings_numeric == 1 ~ 1,
+             gad.pandemic_felt_feelings_numeric == 2 ~ 1,
+             gad.pandemic_felt_feelings_numeric == 3 ~ 0,
+             gad.pandemic_felt_feelings_numeric == 4 ~ 2,
+             gad.pandemic_felt_feelings_numeric == 5 ~ 2
+           )
+         )
+
+dat <- dat %>%
+  mutate(gad.change_binary =
+           recode_factor(
+             gad.change_binary_numeric,
+             `0` = "No change",
+             `1` = "Worsening",
+             `2` = "Improvement"
+           )
+         )
+
+dat %>%
+  freq(gad.change_binary)
+```
+
+### Summary scores
+```{r descriptives gad.sum_score_cols}
+gad.sum_score_numeric_table <- dat %>% 
+  group_by(gad.change_binary) %>%
+  summarise_at( 
+    vars(
+      "Prepan" = gad.sum_score_prepan,
+      "Base" = gad.sum_score_base,
+      "Retro" = gad.sum_score_retro
+    ),
+    .funs =
+      list(
+        ~mean(., na.rm = T),
+        ~sd(., na.rm = T),
+        ~median(., na.rm = T),
+        ~min(., na.rm = T),
+        ~max(., na.rm = T),
+        ~skew(., na.rm = T),
+        kurtosis = ~kurtosi(., na.rm = T)
+      )
+  )
+
+gad.sum_score_numeric_table
+```
+
+```{r smart numeric summary tables}
+# reshape the table
+gad.sum_score_numeric_summary_table_reshaped <- gad.sum_score_numeric_table %>% 
+  gather(key, value, -gad.change_binary) %>% 
+  separate(key, c("variable", "measure"), sep = "_") %>%
+  mutate(measure = factor(
+    x = measure,
+    levels =  c( # this is the order I want my columns to appear in
+      "missing",
+      "min",
+      "max",
+      "mean", 
+      "median", 
+      "mode",
+      "sd",
+      "skew",
+      "kurtosis"
+    ))) %>% 
+  spread(measure, value) %>% 
+  # we can apply a function to all variables to edit them so that they are publication ready
+  rename_all(
+    .funs = ~str_to_title(.)
+  ) %>% 
+  # or we can individually rename variables 
+  rename(
+    Change = Gad.change_binary,
+    SD = Sd
+  )
+
+gad.sum_score_numeric_summary_table_reshaped
+```
+
+Table for knitting
+gad diff summary table
+```{r gad diff summary table}
+kable(gad.sum_score_numeric_summary_table_reshaped)
+```
+
+### Differences scores
+
+```{r descriptives gad.diff_score_cols}
+gad.numeric_table <- dat %>% 
+  group_by(gad.change_binary) %>%
+  summarise_at( 
+    vars(
+      "Base - prepan" = gad.diff_score_base_prepan,
+      "Base - retro" = gad.diff_score_base_retro,
+      "Prepan - retro" = gad.diff_score_retro_prepan
+    ),
+    .funs =
+      list(
+        ~mean(., na.rm = T),
+        ~sd(., na.rm = T),
+        ~median(., na.rm = T),
+        ~min(., na.rm = T),
+        ~max(., na.rm = T),
+        ~skew(., na.rm = T),
+        kurtosis = ~kurtosi(., na.rm = T)
+      )
+  )
+
+gad.numeric_table
+```
+
+```{r smart numeric summary tables}
+# reshape the table
+gad.numeric_summary_table_reshaped <- gad.numeric_table %>% 
+  gather(key, value, -gad.change_binary) %>% 
+  separate(key, c("variable", "measure"), sep = "_") %>%
+  mutate(measure = factor(
+    x = measure,
+    levels =  c( # this is the order I want my columns to appear in
+      "missing",
+      "min",
+      "max",
+      "mean", 
+      "median", 
+      "mode",
+      "sd",
+      "skew",
+      "kurtosis"
+    ))) %>% 
+  spread(measure, value) %>% 
+  # we can apply a function to all variables to edit them so that they are publication ready
+  rename_all(
+    .funs = ~str_to_title(.)
+    ) %>% 
+  # or we can individually rename variables 
+  rename(
+    Change = Gad.change_binary,
+    SD = Sd
+  )
+
+gad.numeric_summary_table_reshaped
+```
+
+Table for knitting
+gad diff summary table
+```{r gad diff summary table}
+kable(gad.numeric_summary_table_reshaped)
+```
+
+### Long format
+
+```{r gad gather to long format Time_points gad.diff_score}
+dat.long.gad.diff <- dat %>%
+  gather(
+    key = "Time_point_raw",
+    value = "gad.diff_score",
+    all_of(gad.diff_score_cols)) %>%
+  select(
+    ID,
+    Sample,
+    Gender_collapsed,
+    Ethnicity_collapsed,
+    Disorder_hierarchical,
+    Time_point_raw,
+    gad.diff_score
+  ) %>%
+  mutate(Time_point = str_replace(Time_point_raw, "gad.diff_score_", "")) %>%
+  select(-Time_point_raw)
+
+head(dat.long.gad.diff)
+```
+
+```{r gad gather to long format Time_points gad.sum_score}
+dat.long.gad.sum <- dat %>%
+  gather(
+    key = "Time_point_raw",
+    value = "gad.sum_score",
+    all_of(gad.sum_score_cols)) %>%
+  select(
+    ID,
+    Sample,
+    Gender_collapsed,
+    Ethnicity_collapsed,
+    Disorder_hierarchical,
+    Time_point_raw,
+    gad.sum_score
+  ) %>%
+  mutate(Time_point = str_replace(Time_point_raw, "gad.sum_score_", "")) %>%
+  select(-Time_point_raw)
+
+head(dat.long.gad.sum)
+```
+
+### Plots diff
+
+makes this into percentages
+```{r gad absolut plot}
+dat.long.gad.diff %>%
+  ggplot(mapping = aes(y = gad.diff_score)) +
+  geom_bar() +
+  theme_minimal() +
+  facet_wrap(facets = vars(Time_point))
+```
+
+```{r gad percentage plot retro_prepan diff}
+dat.long.gad.diff %>%
+  filter(Time_point != "retro_prepan") %>%
+  ggplot(mapping = aes(
+    x = gad.diff_score,
+    y = stat(density*width),
+    fill = Time_point)) +
+  geom_histogram(
+    binwidth = 1,
+    position = position_dodge2(preserve = "single")
+  ) +
+  labs(
+    x = "Difference GAD7 score",
+    y = "Percentage of participants",
+    fill = "Comparison:\nBaseline vs") +
+  theme_personal +
+  scale_fill_manual(values = palette, labels = c("Prepandemic", "Retrospective"))
+```
+
+```{r gad percentage plot retro_prepan, fig.height=6, fig.width=10}
+dat.long.gad.diff %>%
+  filter(Time_point != "retro_prepan") %>%
+  ggplot(mapping = aes(
+    x = gad.diff_score,
+    y = stat(density*width),
+    fill = Time_point)) +
+  geom_histogram(
+    binwidth = 1,
+    position = position_dodge2(preserve = "single")
+  ) +
+  labs(
+    x = "Difference GAD7 score",
+    y = "Percentage of participants",
+    fill = "Comparison:\nBaseline vs") +
+  theme_personal +
+  scale_fill_manual(values = palette, labels = c("Prepandemic", "Retrospective")) +
+  facet_wrap("Disorder_hierarchical")
+```
+
+```{r gad plot retro_prepan diff}
+dat.long.gad.diff %>%
+  filter(Time_point == "retro_prepan") %>%
+  ggplot(mapping = aes(
+    x = gad.diff_score,
+    y = stat(density*width),
+    fill = Time_point)) +
+  geom_histogram(
+    binwidth = 1,
+    position = position_dodge2(preserve = "single")
+  ) +
+  labs(
+    x = "Difference GAD7 score",
+    y = "Percentage of participants",
+    fill = "Comparison:\nRetrospective vs") +
+  theme_personal +
+  scale_fill_manual(values = palette, labels = c("Prepandemic"))
+```
+
+### Plots sum
+
+```{r gad percentage plot retro_prepan sum}
+dat.long.gad.sum %>%
+#  filter(Time_point != "retro_prepan") %>%
+  ggplot(mapping = aes(
+    x = gad.sum_score,
+    y = stat(density*width),
+    fill = Time_point)) +
+  geom_histogram(
+    binwidth = 1,
+    position = position_dodge2(preserve = "single")
+  ) +
+  labs(
+    x = "GAD7 scores",
+    y = "Percentage of participants",
+    fill = "Time point") +
+  theme_personal +
+  scale_fill_manual(
+    values = COPINGpalette3,
+    labels = c("Baseline", "Prepandemic", "Retrospective")
+    )
+```
+
+```{r gad percentage plot retro_prepan sum, fig.height=6, fig.width=10}
+dat.long.gad.sum %>%
+#  filter(Time_point != "retro_prepan") %>%
+  ggplot(mapping = aes(
+    x = gad.sum_score,
+    y = stat(density*width),
+    fill = Time_point)) +
+  geom_histogram(
+    binwidth = 1,
+    position = position_dodge2(preserve = "single")
+  ) +
+  labs(
+    x = "GAD7 score",
+    y = "Percentage of participants",
+    fill = "Time point") +
+  theme_personal +
+  scale_fill_manual(
+    values = COPINGpalette3,
+#    labels = c("Prepandemic", "Retrospective")
+    ) +
+  facet_wrap("Disorder_hierarchical")
+```
+
+## phq
+
+### Split sample in improvement and worsening
+```{r phq improvment worsening stratification}
+dat <- dat %>%
+  mutate(phq.change_binary_numeric =
+           case_when(
+             phq.pandemic_felt_feelings_numeric == 1 ~ 1,
+             phq.pandemic_felt_feelings_numeric == 2 ~ 1,
+             phq.pandemic_felt_feelings_numeric == 3 ~ 0,
+             phq.pandemic_felt_feelings_numeric == 4 ~ 2,
+             phq.pandemic_felt_feelings_numeric == 5 ~ 2
+           )
+  )
+
+dat <- dat %>%
+  mutate(phq.change_binary =
+           recode_factor(
+             phq.change_binary_numeric,
+             `0` = "No change",
+             `1` = "Worsening",
+             `2` = "Improvement"
+           )
+  )
+
+dat %>%
+  freq(phq.change_binary)
+```
+
+### Summary scores
+```{r descriptives phq.sum_score}
+phq.sum_score_numeric_table <- dat %>% 
+  group_by(phq.change_binary) %>%
+  summarise_at( 
+    vars(
+      "Prepan" = phq.sum_score_prepan,
+      "Base" = phq.sum_score_base,
+      "Retro" = phq.sum_score_retro
+    ),
+    .funs =
+      list(
+        ~mean(., na.rm = T),
+        ~sd(., na.rm = T),
+        ~median(., na.rm = T),
+        ~min(., na.rm = T),
+        ~max(., na.rm = T),
+        ~skew(., na.rm = T),
+        kurtosis = ~kurtosi(., na.rm = T)
+      )
+  )
+
+phq.sum_score_numeric_table
+```
+
+```{r smart numeric summary tables}
+# reshape the table
+phq.sum_score_numeric_summary_table_reshaped <- phq.sum_score_numeric_table %>%
+  gather(key, value, -phq.change_binary) %>% 
+  separate(key, c("variable", "measure"), sep = "_") %>%
+  mutate(measure = factor(
+    x = measure,
+    levels =  c( # this is the order I want my columns to appear in
+      "missing",
+      "min",
+      "max",
+      "mean", 
+      "median", 
+      "mode",
+      "sd",
+      "skew",
+      "kurtosis"
+    ))) %>% 
+  spread(measure, value) %>% 
+  # we can apply a function to all variables to edit them so that they are publication ready
+  rename_all(
+    .funs = ~str_to_title(.)
+  ) %>% 
+  # or we can individually rename variables 
+  rename(
+    SD = Sd
+  )
+
+phq.sum_score_numeric_summary_table_reshaped
+```
+
+Table for knitting
+phq diff summary table
+```{r phq diff summary table}
+kable(phq.sum_score_numeric_summary_table_reshaped)
+```
+
+### Differences score
+
+```{r descriptives phq.diff_score_cols}
+phq.numeric_table <- dat %>% 
+  group_by(phq.change_binary) %>%
+  summarise_at( 
+    vars(
+      "Base - prepan" = phq.diff_score_base_prepan,
+      "Base - retro" = phq.diff_score_base_retro,
+      "Prepan - retro" = phq.diff_score_retro_prepan
+    ),
+    .funs =
+      list(
+        ~mean(., na.rm = T),
+        ~sd(., na.rm = T),
+        ~median(., na.rm = T),
+        ~min(., na.rm = T),
+        ~max(., na.rm = T),
+        ~skew(., na.rm = T),
+        kurtosis = ~kurtosi(., na.rm = T)
+      )
+  )
+
+phq.numeric_table
+```
+
+```{r smart numeric summary tables}
+# reshape the table
+phq.numeric_summary_table_reshaped <- phq.numeric_table %>% 
+  gather(key, value, -phq.change_binary) %>% 
+  separate(key, c("variable", "measure"), sep = "_") %>%
+  mutate(measure = factor(
+    x = measure,
+    levels =  c( # this is the order I want my columns to appear in
+      "missing",
+      "min",
+      "max",
+      "mean", 
+      "median", 
+      "mode",
+      "sd",
+      "skew",
+      "kurtosis"
+    ))) %>% 
+  spread(measure, value) %>% 
+  # we can apply a function to all variables to edit them so that they are publication ready
+  rename_all(
+    .funs = ~str_to_title(.)
+  ) %>% 
+  # or we can individually rename variables 
+  rename(
+    SD = Sd
+  )
+
+phq.numeric_summary_table_reshaped
+```
+
+Table for knitting
+phq diff summary table
+```{r phq diff summary table}
+kable(phq.numeric_summary_table_reshaped)
+```
+
+### Long format
+
+```{r phq gather to long format Time_points}
+dat.long.phq.diff <- dat %>%
+  gather(
+    key = "Time_point_raw",
+    value = "phq.diff_score",
+    all_of(phq.diff_score_cols)) %>%
+  select(
+    ID,
+    Sample,
+    Gender_collapsed,
+    Ethnicity_collapsed,
+    Disorder_hierarchical,
+    Time_point_raw,
+    phq.diff_score
+  ) %>%
+  mutate(Time_point = str_replace(Time_point_raw, "phq.diff_score_", "")) %>%
+  select(-Time_point_raw)
+
+head(dat.long.phq.diff)
+```
+
+```{r phq gather to long format Time_points phq.sum_score}
+dat.long.phq.sum <- dat %>%
+  gather(
+    key = "Time_point_raw",
+    value = "phq.sum_score",
+    all_of(phq.sum_score_cols)) %>%
+  select(
+    ID,
+    Sample,
+    Gender_collapsed,
+    Ethnicity_collapsed,
+    Disorder_hierarchical,
+    Time_point_raw,
+    phq.sum_score
+  ) %>%
+  mutate(Time_point = str_replace(Time_point_raw, "phq.sum_score_", "")) %>%
+  select(-Time_point_raw)
+
+head(dat.long.phq.sum)
+```
+
+### Plots
+
+makes this into percentages
+```{r phq absolut plot}
+dat.long.phq.diff %>%
+  ggplot(mapping = aes(y = phq.diff_score)) +
+  geom_bar() +
+  theme_minimal() +
+  facet_wrap(facets = vars(Time_point))
+```
+
+```{r phq percentage plot retro_prepan}
+dat.long.phq.diff %>%
+  filter(Time_point != "retro_prepan") %>%
+  ggplot(mapping = aes(
+    x = phq.diff_score,
+    y = stat(density*width),
+    fill = Time_point)) +
+  geom_histogram(
+    binwidth = 1,
+    position = position_dodge2(preserve = "single")
+  ) +
+  labs(
+    x = "Difference PHQ9 score",
+    y = "Percentage of participants",
+    fill = "Comparison:\nBaseline vs") +
+  theme_personal +
+  scale_fill_manual(values = palette, labels = c("Prepandemic", "Retrospective"))
+```
+
+```{r phq plot retro_prepan diff}
+dat.long.phq.diff %>%
+  filter(Time_point == "retro_prepan") %>%
+  ggplot(mapping = aes(
+    x = phq.diff_score,
+    y = stat(density*width),
+    fill = Time_point)) +
+  geom_histogram(
+    binwidth = 1,
+    position = position_dodge2(preserve = "single")
+  ) +
+  labs(
+    x = "Difference phq7 score",
+    y = "Percentage of participants",
+    fill = "Comparison:\nPrepandemic vs") +
+  theme_personal +
+  scale_fill_manual(values = palette, labels = c("Retrospective"))
+```
+
+```{r phq percentage plot retro_prepan, fig.height=6, fig.width=10}
+dat.long.phq.diff %>%
+  filter(Time_point != "retro_prepan") %>%
+  ggplot(mapping = aes(
+    x = phq.diff_score,
+    y = stat(density*width),
+    fill = Time_point)) +
+  geom_histogram(
+    binwidth = 1,
+    position = position_dodge2(preserve = "single")
+  ) +
+  labs(
+    x = "Difference PHQ9 score",
+    y = "Percentage of participants",
+    fill = "Comparison:\nBaseline vs") +
+  theme_personal +
+  scale_fill_manual(values = palette, labels = c("Prepandemic", "Retrospective")) +
+  facet_wrap("Disorder_hierarchical")
+```
+
+### Plots sum
+
+```{r phq percentage plot retro_prepan sum}
+dat.long.phq.sum %>%
+  #  filter(Time_point != "retro_prepan") %>%
+  ggplot(mapping = aes(
+    x = phq.sum_score,
+    y = stat(density*width),
+    fill = Time_point)) +
+  geom_histogram(
+    binwidth = 1,
+    position = position_dodge2(preserve = "single")
+  ) +
+  labs(
+    x = "PHQ9 scores",
+    y = "Percentage of participants",
+    fill = "Time point") +
+  theme_personal +
+  scale_fill_manual(
+    values = COPINGpalette3,
+    labels = c("Baseline", "Prepandemic", "Retrospective")
+  )
+```
+
+```{r phq percentage plot retro_prepan sum, fig.height=6, fig.width=10}
+dat.long.phq.sum %>%
+  #  filter(Time_point != "retro_prepan") %>%
+  ggplot(mapping = aes(
+    x = phq.sum_score,
+    y = stat(density*width),
+    fill = Time_point)) +
+  geom_histogram(
+    binwidth = 1,
+    position = position_dodge2(preserve = "single")
+  ) +
+  labs(
+    x = "PHQ9 score",
+    y = "Percentage of participants",
+    fill = "Time point") +
+  theme_personal +
+  scale_fill_manual(
+    values = COPINGpalette3,
+    labels = c("Baseline", "Prepandemic", "Retrospective")
+  ) +
+  facet_wrap("Disorder_hierarchical")
+```
+
+## ocir
+
+### Split sample in improvement and worsening
+```{r ocir improvment worsening stratification}
+dat <- dat %>%
+  mutate(ocir.change_binary_numeric =
+           case_when(
+             ocir.felt_pandemic_feelings_numeric == 1 ~ 1,
+             ocir.felt_pandemic_feelings_numeric == 2 ~ 1,
+             ocir.felt_pandemic_feelings_numeric == 3 ~ 0,
+             ocir.felt_pandemic_feelings_numeric == 4 ~ 2,
+             ocir.felt_pandemic_feelings_numeric == 5 ~ 2
+           )
+  )
+
+dat <- dat %>%
+  mutate(ocir.change_binary =
+           recode_factor(
+             ocir.change_binary_numeric,
+             `0` = "No change",
+             `1` = "Worsening",
+             `2` = "Improvement"
+           )
+  )
+
+dat %>%
+  freq(ocir.change_binary)
+```
+
+### Summary scores
+```{r descriptives ocir.sum_score}
+ocir.sum_score_numeric_table <- dat %>% 
+  group_by(ocir.change_binary) %>%
+  summarise_at( 
+    vars(
+      "Prepan" = ocir.sum_score_prepan,
+      "Base" = ocir.sum_score_base,
+      "Retro" = ocir.sum_score_retro
+    ),
+    .funs =
+      list(
+        ~mean(., na.rm = T),
+        ~sd(., na.rm = T),
+        ~median(., na.rm = T),
+        ~min(., na.rm = T),
+        ~max(., na.rm = T),
+        ~skew(., na.rm = T),
+        kurtosis = ~kurtosi(., na.rm = T)
+      )
+  )
+
+ocir.sum_score_numeric_table
+```
+
+```{r smart numeric summary tables}
+# reshape the table
+ocir.sum_score_numeric_summary_table_reshaped <- ocir.sum_score_numeric_table %>%
+  filter(ocir.change_binary == "Worsening") %>%
+  select(-ocir.change_binary) %>%
+  gather(key, value) %>% 
+  separate(key, c("variable", "measure"), sep = "_") %>%
+  mutate(measure = factor(
+    x = measure,
+    levels =  c( # this is the order I want my columns to appear in
+      "missing",
+      "min",
+      "max",
+      "mean", 
+      "median", 
+      "mode",
+      "sd",
+      "skew",
+      "kurtosis"
+    ))) %>% 
+  spread(measure, value) %>% 
+  # we can apply a function to all variables to edit them so that they are publication ready
+  rename_all(
+    .funs = ~str_to_title(.)
+  ) %>% 
+  # or we can individually rename variables 
+  rename(
+    SD = Sd
+  )
+
+ocir.sum_score_numeric_summary_table_reshaped
+```
+
+Table for knitting
+ocir diff summary table
+```{r ocir diff summary table}
+kable(ocir.sum_score_numeric_summary_table_reshaped)
+```
+
+### Differences scores
+
+```{r descriptives ocir.diff_score_cols}
+ocir.numeric_table <- dat %>% 
+  #  group_by(dem.sex) %>%
+  summarise_at( 
+    vars(
+      "Base - prepan" = ocir.diff_score_base_prepan,
+      "Base - retro" = ocir.diff_score_base_retro,
+      "Prepan - retro" = ocir.diff_score_retro_prepan
+    ),
+    .funs =
+      list(
+        ~mean(., na.rm = T),
+        ~sd(., na.rm = T),
+        ~median(., na.rm = T),
+        ~min(., na.rm = T),
+        ~max(., na.rm = T),
+        ~skew(., na.rm = T),
+        kurtosis = ~kurtosi(., na.rm = T)
+      )
+  )
+
+ocir.numeric_table
+```
+
+```{r smart numeric summary tables}
+# reshape the table
+ocir.numeric_summary_table_reshaped <- ocir.numeric_table %>% 
+  gather(key, value) %>% 
+  separate(key, c("variable", "measure"), sep = "_") %>%
+  mutate(measure = factor(
+    x = measure,
+    levels =  c( # this is the order I want my columns to appear in
+      "missing",
+      "min",
+      "max",
+      "mean", 
+      "median", 
+      "mode",
+      "sd",
+      "skew",
+      "kurtosis"
+    ))) %>% 
+  spread(measure, value) %>% 
+  # we can apply a function to all variables to edit them so that they are publication ready
+  rename_all(
+    .funs = ~str_to_title(.)
+  ) %>% 
+  # or we can individually rename variables 
+  rename(
+    SD = Sd
+  )
+
+ocir.numeric_summary_table_reshaped
+```
+
+Table for knitting
+ocir diff summary table
+```{r ocir diff summary table}
+kable(ocir.numeric_summary_table_reshaped)
+```
+
+### Long format
+
+```{r ocir gather to long format Time_points}
+dat.long.ocir.diff <- dat %>%
+  gather(
+    key = "Time_point_raw",
+    value = "ocir.diff_score",
+    all_of(ocir.diff_score_cols)) %>%
+  select(
+    ID,
+    Sample,
+    Gender_collapsed,
+    Ethnicity_collapsed,
+    Disorder_hierarchical,
+    Time_point_raw,
+    ocir.diff_score
+  ) %>%
+  mutate(Time_point = str_replace(Time_point_raw, "ocir.diff_score_", "")) %>%
+  select(-Time_point_raw)
+
+head(dat.long.ocir.diff)
+```
+
+```{r ocir gather to long format Time_points ocir.sum_score}
+dat.long.ocir.sum <- dat %>%
+  gather(
+    key = "Time_point_raw",
+    value = "ocir.sum_score",
+    all_of(ocir.sum_score_cols)) %>%
+  select(
+    ID,
+    Sample,
+    Gender_collapsed,
+    Ethnicity_collapsed,
+    Disorder_hierarchical,
+    Time_point_raw,
+    ocir.sum_score
+  ) %>%
+  mutate(Time_point = str_replace(Time_point_raw, "ocir.sum_score_", "")) %>%
+  select(-Time_point_raw)
+
+head(dat.long.ocir.sum)
+```
+
+### Plots
+
+makes this into percentages
+```{r ocir absolut plot}
+dat.long.ocir.diff %>%
+  ggplot(mapping = aes(y = ocir.diff_score)) +
+  geom_bar() +
+  theme_minimal() +
+  facet_wrap(facets = vars(Time_point))
+```
+
+```{r ocir percentage plot retro_prepan}
+dat.long.ocir.diff %>%
+  filter(Time_point != "retro_prepan") %>%
+  ggplot(mapping = aes(
+    x = ocir.diff_score,
+    y = stat(density*width),
+    fill = Time_point)) +
+  geom_histogram(
+    binwidth = 1,
+    position = position_dodge2(preserve = "single")
+  ) +
+  labs(
+    x = "Difference OCI-R score",
+    y = "Percentage of participants",
+    fill = "Comparison:\nBaseline vs") +
+  theme_personal +
+  scale_fill_manual(values = palette, labels = c("Prepandemic", "Retrospective"))
+```
+
+```{r ocir plot retro_prepan diff}
+dat.long.ocir.diff %>%
+  filter(Time_point == "retro_prepan") %>%
+  ggplot(mapping = aes(
+    x = ocir.diff_score,
+    y = stat(density*width),
+    fill = Time_point)) +
+  geom_histogram(
+    binwidth = 1,
+    position = position_dodge2(preserve = "single")
+  ) +
+  labs(
+    x = "Difference ocir7 score",
+    y = "Percentage of participants",
+    fill = "Comparison:\nPrepandemic vs") +
+  theme_personal +
+  scale_fill_manual(values = palette, labels = c("Retrospective"))
+```
+
+```{r ocir percentage plot retro_prepan, fig.height=6, fig.width=10}
+dat.long.ocir.diff %>%
+  filter(Time_point != "retro_prepan") %>%
+  ggplot(mapping = aes(
+    x = ocir.diff_score,
+    y = stat(density*width),
+    fill = Time_point)) +
+  geom_histogram(
+    binwidth = 1,
+    position = position_dodge2(preserve = "single")
+  ) +
+  labs(
+    x = "Difference OCI-R score",
+    y = "Percentage of participants",
+    fill = "Comparison:\nBaseline vs") +
+  theme_personal +
+  scale_fill_manual(values = palette, labels = c("Prepandemic", "Retrospective")) +
+  facet_wrap("Disorder_hierarchical")
+```
+
+### Plots sum
+
+```{r ocir percentage plot retro_prepan sum}
+dat.long.ocir.sum %>%
+  ggplot(mapping = aes(
+    x = ocir.sum_score,
+    y = stat(density*width),
+    fill = Time_point)) +
+  geom_histogram(
+    binwidth = 1,
+    position = position_dodge2(preserve = "single")
+  ) +
+  labs(
+    x = "OCI-R scores",
+    y = "Percentage of participants",
+    fill = "Time point") +
+  theme_personal +
+  scale_fill_manual(
+    values = COPINGpalette3,
+    labels = c("Baseline", "Prepandemic", "Retrospective")
+  )
+```
+
+```{r ocir percentage plot retro_prepan sum, fig.height=6, fig.width=10}
+dat.long.ocir.sum %>%
+  ggplot(mapping = aes(
+    x = ocir.sum_score,
+    y = stat(density*width),
+    fill = Time_point)) +
+  geom_histogram(
+    binwidth = 1,
+    position = position_dodge2(preserve = "single")
+  ) +
+  labs(
+    x = "OCI-R score",
+    y = "Percentage of participants",
+    fill = "Time point") +
+  theme_personal +
+  scale_fill_manual(
+    values = COPINGpalette3,
+    labels = c("Baseline", "Prepandemic", "Retrospective")
+  ) +
+  facet_wrap("Disorder_hierarchical")
+```
+
+Rank the disorders by the size of the change
+
+PCL:  
+Calculate the total GLAD, COPING, RAMP baseline 
+## pcl
+
+```{r descriptives pcl.diff_score_cols}
+pcl.numeric_table <- dat %>% 
+#    group_by(Sample) %>%
+  summarise_at( 
+    vars(
+      "Base - prepan" = pcl.diff_score_base_prepan
+    ),
+    .funs =
+      list(
+        ~mean(., na.rm = T),
+        ~sd(., na.rm = T),
+        ~median(., na.rm = T),
+        ~min(., na.rm = T),
+        ~max(., na.rm = T),
+        ~skew(., na.rm = T),
+        kurtosis = ~kurtosi(., na.rm = T)
+      )
+  )
+
+pcl.numeric_table
+```
+
+```{r smart numeric summary tables}
+# reshape the table
+pcl.numeric_summary_table_reshaped <- pcl.numeric_table %>% 
+  gather(key, value) %>% 
+  separate(key, c("variable", "measure"), sep = "_") %>%
+  mutate(measure = factor(
+    x = measure,
+    levels =  c( # this is the order I want my columns to appear in
+      "missing",
+      "min",
+      "max",
+      "mean", 
+      "median", 
+      "mode",
+      "sd",
+      "skew",
+      "kurtosis"
+    ))) %>% 
+  spread(measure, value) %>% 
+  # we can apply a function to all variables to edit them so that they are publication ready
+  rename_all(
+    .funs = ~str_to_title(.)
+  ) %>% 
+  # or we can individually rename variables 
+  rename(
+    SD = Sd
+  )
+
+pcl.numeric_summary_table_reshaped
+```
+
+Table for knitting
+pcl diff summary table
+```{r pcl diff summary table}
+kable(pcl.numeric_summary_table_reshaped)
+```
+
+```{r descriptives pcl.sum_score}
+pcl.sum_score_numeric_table <- dat %>% 
+#    group_by(Sample) %>%
+  summarise_at( 
+    vars(
+      "Prepan" = pcl.sum_score_prepan,
+      "Base" = pcl.sum_score_base
+    ),
+    .funs =
+      list(
+        ~mean(., na.rm = T),
+        ~sd(., na.rm = T),
+        ~median(., na.rm = T),
+        ~min(., na.rm = T),
+        ~max(., na.rm = T),
+        ~skew(., na.rm = T),
+        kurtosis = ~kurtosi(., na.rm = T)
+      )
+  )
+
+pcl.numeric_table
+```
+
+```{r smart numeric summary tables}
+# reshape the table
+pcl.sum_score_numeric_summary_table_reshaped <- pcl.sum_score_numeric_table %>% 
+  gather(key, value) %>% 
+  separate(key, c("variable", "measure"), sep = "_") %>%
+  mutate(measure = factor(
+    x = measure,
+    levels =  c( # this is the order I want my columns to appear in
+      "missing",
+      "min",
+      "max",
+      "mean", 
+      "median", 
+      "mode",
+      "sd",
+      "skew",
+      "kurtosis"
+    ))) %>% 
+  spread(measure, value) %>% 
+  # we can apply a function to all variables to edit them so that they are publication ready
+  rename_all(
+    .funs = ~str_to_title(.)
+  ) %>% 
+  # or we can individually rename variables 
+  rename(
+    SD = Sd
+  )
+
+pcl.sum_score_numeric_summary_table_reshaped
+```
+
+Table for knitting
+pcl diff summary table
+```{r pcl diff summary table}
+kable(pcl.sum_score_numeric_summary_table_reshaped)
+```
+
+```{r pcl gather to long format Time_points pcl.sum_score}
+dat.long.pcl.sum <- dat %>%
+  gather(
+    key = "Time_point_raw",
+    value = "pcl.sum_score",
+    all_of(pcl.sum_score_cols)) %>%
+  select(
+    ID,
+    Sample,
+    Gender_collapsed,
+    Ethnicity_collapsed,
+    Disorder_hierarchical,
+    Time_point_raw,
+    pcl.sum_score
+  ) %>%
+  mutate(Time_point = str_replace(Time_point_raw, "pcl.sum_score_", "")) %>%
+  select(-Time_point_raw)
+
+head(dat.long.pcl.sum)
+```
+
+For each item 
+present percentages of how say that this is due to the pandemic 
+```{r pcl percentages due to pandemic}
+pcl.retro.items <- c(
+  "pcl.stressful_experience_upset_reminded_retro_numeric",
+  "pcl.stressful_experience_repeated_images_retro_numeric",
+  "pcl.stressful_situation_avoiding_activities_retro_numeric",
+  "pcl.cut_people_feeling_distant_retro_numeric",
+  "pcl.difficulty_concentrating_retro_numeric",
+  "pcl.feeling_irritable_or_having_angry_outbursts_retro_numeric"
+)
+
+pcl.percentages.summary <- dat %>%
+  select(
+    all_of(pcl.retro.items)
+  ) %>%
+  gather(
+    key = "PCL Item",
+    value = "Binary_score",
+    all_of(pcl.retro.items)
+  ) %>%
+  mutate(Binary_score = fct_explicit_na(as.factor(Binary_score), na_level = "Missing")) %>%
+  group_by(`PCL Item`) %>%
+  count(`PCL Item`, Binary_score) %>%
+  mutate(prop = round(n/sum(n), 3)*100) %>%
+  mutate(n_prop = paste0(n," (",prop, "%)"))
+
+pcl.percentages.summary
+```
+
+### Plots sum
+
+```{r pcl percentage plot retro_prepan sum}
+dat.long.pcl.sum %>%
+  ggplot(mapping = aes(
+    x = pcl.sum_score,
+    y = stat(density*width),
+    fill = Time_point)) +
+  geom_histogram(
+    binwidth = 1,
+    position = position_dodge2(preserve = "single")
+  ) +
+  labs(
+    x = "PCL scores",
+    y = "Percentage of participants",
+    fill = "Time point") +
+  theme_personal +
+  scale_fill_manual(
+    values = COPINGpalette3,
+    labels = c("Baseline", "Prepandemic", "Retrospective")
+  )
+```
+
+```{r pcl percentage plot retro_prepan sum, fig.height=6, fig.width=10}
+dat.long.pcl.sum %>%
+  ggplot(mapping = aes(
+    x = pcl.sum_score,
+    y = stat(density*width),
+    fill = Time_point)) +
+  geom_histogram(
+    binwidth = 1,
+    position = position_dodge2(preserve = "single")
+  ) +
+  labs(
+    x = "PCL score",
+    y = "Percentage of participants",
+    fill = "Time point") +
+  theme_personal +
+  scale_fill_manual(
+    values = COPINGpalette3,
+    labels = c("Baseline", "Prepandemic", "Retrospective")
+  ) +
+  facet_wrap("Disorder_hierarchical")
 ```
@@
 ```{r disorders total count}
-dat.mhd %>%
+dat %>%
   freq(disorders_total_count)
@@
 ## Correlation matrix
-Using dat.mhd for the correlation matrix.
+Using dat for the correlation matrix.
 ```{r Correlation matrix of psychiatric disorders}
@@
 mhd.corr.mat <- hetcor(
-  as.data.frame(dat.mhd[,mhd.items]), # Specify the data
+  as.data.frame(dat[,mhd.items]), # Specify the data
   use = "pairwise.complete.obs" # Use all pairwise observations
@@
 ```{r gather to long format Disorder_hierarchical}
-dat.long.psych <- dat.mhd %>%
+dat.long.psych <- dat %>%
   gather(
@@
 
-Compare the GLAD/EDGI and COPING cohorts as a whole
-+++CH: Diagnosis, ethnicity, gender, age
-
-# age_category
-```{r age_category per Sample prop per total}
-age_category_per_Sample_prop_total <- dat %>%
-  count(age_category, Sample) %>%
-  mutate(Prop = round(n/sum(n), 2))
-
-kable(age_category_per_Sample_prop_total)
-age_category_per_Sample_prop_total
-```
-
-```{r age_category per Sample prop per Sample}
-age_category_per_Sample_prop_Sample <- dat %>%
-  group_by(Sample) %>%
-  count(age_category, Sample) %>%
-  mutate(Prop = round(n/sum(n), 2))
-
-kable(age_category_per_Sample_prop_Sample)
-age_category_per_Sample_prop_Sample
-```
-
-```{r age_category per Sample prop cross table}
-age_category_per_Sample_prop_Sample_cross_table <- dat %>%
-  group_by(Sample) %>%
-  count(age_category, Sample) %>%
-  mutate(Prop = round(n/sum(n), 2)) %>%
-  pivot_wider(names_from = Sample, values_from = c(n, Prop))
-
-kable(age_category_per_Sample_prop_Sample_cross_table)
-age_category_per_Sample_prop_Sample_cross_table
-```
-
-```{r age_category per Sample count cross table}
-age_category_per_Sample_count_cross_table <- dat %>%
-  count(age_category, Sample) %>%
-  spread(key = Sample, value = n) %>%
-  mutate(
-    EDGI = as.integer(replace_na(EDGI, 0)),
-    GLAD = as.integer(replace_na(GLAD, 0)),
-    NBR = as.integer(replace_na(NBR, 0)),
-    RAMP = as.integer(replace_na(RAMP, 0))
-  )
-
-kable(age_category_per_Sample_count_cross_table)
-age_category_per_Sample_count_cross_table
-```
-
-```{r age_category per Sample chisquare test}
-age_category_per_Sample_chissquare_test <- dat %>%
-  count(age_category, Sample) %>%
-  spread(key = Sample, value = n) %>%
-  select(-age_category) %>%
-  mutate(
-    EDGI = as.integer(replace_na(EDGI, 0)),
-    GLAD = as.integer(replace_na(GLAD, 0)),
-    NBR = as.integer(replace_na(NBR, 0)),
-    RAMP = as.integer(replace_na(RAMP, 0))
-  ) %>%
-  chisq.test() %>%
-  glance()
-
-kable(age_category_per_Sample_chissquare_test)
-age_category_per_Sample_chissquare_test
-```
-
-```{r age_category by Sample count plot}
-age_category_by_Sample_count_plot <- age_category_per_Sample_prop_Sample %>%
-  ggplot(mapping = aes(
-    x = age_category,
-    y = n)
-  ) +
-  geom_bar(
-    aes(fill = Sample),
-    stat="identity",
-    binwidth = 1,
-    position = position_dodge2(preserve = "single")
-  ) +
-  labs(
-    x = "age_category",
-    y = "Number of participants",
-    fill = "Sample") +
-  theme_personal +
-  scale_fill_manual(
-    values = COPINGpalette6
-  ) +
-  coord_flip()
-
-age_category_by_Sample_count_plot
-```
-
-```{r age_category by Sample prop plot}
-age_category_by_Sample_prop_plot <- age_category_per_Sample_prop_Sample %>%
-  ggplot(mapping = aes(
-    x = age_category,
-    y = Prop)
-  ) +
-  geom_bar(
-    aes(fill = Sample),
-    stat="identity",
-    binwidth = 1,
-    position = position_dodge2(preserve = "single")
-  ) +
-  labs(
-    x = "age_category",
-    y = "Percentage per sample",
-    fill = "Sample") +
-  theme_personal +
-  scale_fill_manual(
-    values = COPINGpalette6
-  ) +
-  coord_flip()
-
-age_category_by_Sample_prop_plot
-```
-
-# Ethnicity_collapsed
-```{r Ethnicity_collapsed per Sample prop per total}
-Ethnicity_collapsed_per_Sample_prop_total <- dat %>%
-  count(Ethnicity_collapsed, Sample) %>%
-  mutate(Prop = round(n/sum(n), 2))
-
-kable(Ethnicity_collapsed_per_Sample_prop_total)
-Ethnicity_collapsed_per_Sample_prop_total
-```
-
-```{r Ethnicity_collapsed per Sample prop per Sample}
-Ethnicity_collapsed_per_Sample_prop_Sample <- dat %>%
-  group_by(Sample) %>%
-  count(Ethnicity_collapsed, Sample) %>%
-  mutate(Prop = round(n/sum(n), 2))
-
-kable(Ethnicity_collapsed_per_Sample_prop_Sample)
-Ethnicity_collapsed_per_Sample_prop_Sample
-```
-
-```{r Ethnicity_collapsed per Sample prop cross table}
-Ethnicity_collapsed_per_Sample_prop_Sample_cross_table <- dat %>%
-  group_by(Sample) %>%
-  count(Ethnicity_collapsed, Sample) %>%
-  mutate(Prop = round(n/sum(n), 2)) %>%
-  pivot_wider(names_from = Sample, values_from = c(n, Prop))
-
-kable(Ethnicity_collapsed_per_Sample_prop_Sample_cross_table)
-Ethnicity_collapsed_per_Sample_prop_Sample_cross_table
-```
-
-```{r Ethnicity_collapsed per Sample count cross table}
-Ethnicity_collapsed_per_Sample_count_cross_table <- dat %>%
-  count(Ethnicity_collapsed, Sample) %>%
-  spread(key = Sample, value = n) %>%
-  mutate(
-    EDGI = as.integer(replace_na(EDGI, 0)),
-    GLAD = as.integer(replace_na(GLAD, 0)),
-    NBR = as.integer(replace_na(NBR, 0)),
-    RAMP = as.integer(replace_na(RAMP, 0))
-  )
-
-kable(Ethnicity_collapsed_per_Sample_count_cross_table)
-Ethnicity_collapsed_per_Sample_count_cross_table
-```
-
-```{r Ethnicity_collapsed per Sample chisquare test}
-Ethnicity_collapsed_per_Sample_chissquare_test <- dat %>%
-  count(Ethnicity_collapsed, Sample) %>%
-  spread(key = Sample, value = n) %>%
-  select(-Ethnicity_collapsed) %>%
-  mutate(
-    EDGI = as.integer(replace_na(EDGI, 0)),
-    GLAD = as.integer(replace_na(GLAD, 0)),
-    NBR = as.integer(replace_na(NBR, 0)),
-    RAMP = as.integer(replace_na(RAMP, 0))
-  ) %>%
-  chisq.test() %>%
-  glance()
-
-kable(Ethnicity_collapsed_per_Sample_chissquare_test)
-Ethnicity_collapsed_per_Sample_chissquare_test
-```
-
-```{r Ethnicity_collapsed by Sample count plot}
-Ethnicity_collapsed_by_Sample_count_plot <- Ethnicity_collapsed_per_Sample_prop_Sample %>%
-  ggplot(mapping = aes(
-    x = Ethnicity_collapsed,
-    y = n)
-  ) +
-  geom_bar(
-    aes(fill = Sample),
-    stat="identity",
-    binwidth = 1,
-    position = position_dodge2(preserve = "single")
-  ) +
-  labs(
-    x = "Ethnicity_collapsed",
-    y = "Number of participants",
-    fill = "Sample") +
-  theme_personal +
-  scale_fill_manual(
-    values = COPINGpalette6
-  ) +
-  coord_flip()
-
-Ethnicity_collapsed_by_Sample_count_plot
-```
-
-```{r Ethnicity_collapsed by Sample prop plot}
-Ethnicity_collapsed_by_Sample_prop_plot <- Ethnicity_collapsed_per_Sample_prop_Sample %>%
-  ggplot(mapping = aes(
-    x = Ethnicity_collapsed,
-    y = Prop)
-  ) +
-  geom_bar(
-    aes(fill = Sample),
-    stat="identity",
-    binwidth = 1,
-    position = position_dodge2(preserve = "single")
-  ) +
-  labs(
-    x = "Ethnicity_collapsed",
-    y = "Percentage per sample",
-    fill = "Sample") +
-  theme_personal +
-  scale_fill_manual(
-    values = COPINGpalette6
-  ) +
-  coord_flip()
-
-Ethnicity_collapsed_by_Sample_prop_plot
-```
-
-# Gender_collapsed
-```{r Gender_collapsed per Sample prop per total}
-Gender_collapsed_per_Sample_prop_total <- dat %>%
-  count(Gender_collapsed, Sample) %>%
-  mutate(Prop = round(n/sum(n), 2))
-
-kable(Gender_collapsed_per_Sample_prop_total)
-Gender_collapsed_per_Sample_prop_total
-```
-
-```{r Gender_collapsed per Sample prop per Sample}
-Gender_collapsed_per_Sample_prop_Sample <- dat %>%
-  group_by(Sample) %>%
-  count(Gender_collapsed, Sample) %>%
-  mutate(Prop = round(n/sum(n), 2))
-
-kable(Gender_collapsed_per_Sample_prop_Sample)
-Gender_collapsed_per_Sample_prop_Sample
-```
-
-```{r Gender_collapsed per Sample prop cross table}
-Gender_collapsed_per_Sample_prop_Sample_cross_table <- dat %>%
-  group_by(Sample) %>%
-  count(Gender_collapsed, Sample) %>%
-  mutate(Prop = round(n/sum(n), 2)) %>%
-  pivot_wider(names_from = Sample, values_from = c(n, Prop))
-
-kable(Gender_collapsed_per_Sample_prop_Sample_cross_table)
-Gender_collapsed_per_Sample_prop_Sample_cross_table
-```
-
-```{r Gender_collapsed per Sample count cross table}
-Gender_collapsed_per_Sample_count_cross_table <- dat %>%
-  count(Gender_collapsed, Sample) %>%
-  spread(key = Sample, value = n) %>%
-  mutate(
-    EDGI = as.integer(replace_na(EDGI, 0)),
-    GLAD = as.integer(replace_na(GLAD, 0)),
-    NBR = as.integer(replace_na(NBR, 0)),
-    RAMP = as.integer(replace_na(RAMP, 0))
-  )
-
-kable(Gender_collapsed_per_Sample_count_cross_table)
-Gender_collapsed_per_Sample_count_cross_table
-```
-
-```{r Gender_collapsed per Sample chisquare test}
-Gender_collapsed_per_Sample_chissquare_test <- dat %>%
-  count(Gender_collapsed, Sample) %>%
-  spread(key = Sample, value = n) %>%
-  select(-Gender_collapsed) %>%
-  mutate(
-    EDGI = as.integer(replace_na(EDGI, 0)),
-    GLAD = as.integer(replace_na(GLAD, 0)),
-    NBR = as.integer(replace_na(NBR, 0)),
-    RAMP = as.integer(replace_na(RAMP, 0))
-  ) %>%
-  chisq.test() %>%
-  glance()
-
-kable(Gender_collapsed_per_Sample_chissquare_test)
-Gender_collapsed_per_Sample_chissquare_test
-```
-
-```{r Gender_collapsed by Sample count plot}
-Gender_collapsed_by_Sample_count_plot <- Gender_collapsed_per_Sample_prop_Sample %>%
-  ggplot(mapping = aes(
-    x = Gender_collapsed,
-    y = n)
-  ) +
-  geom_bar(
-    aes(fill = Sample),
-    stat="identity",
-    binwidth = 1,
-    position = position_dodge2(preserve = "single")
-  ) +
-  labs(
-    x = "Gender_collapsed",
-    y = "Number of participants",
-    fill = "Sample") +
-  theme_personal +
-  scale_fill_manual(
-    values = COPINGpalette6
-  ) +
-  coord_flip()
-
-Gender_collapsed_by_Sample_count_plot
-```
-
-```{r Gender_collapsed by Sample prop plot}
-Gender_collapsed_by_Sample_prop_plot <- Gender_collapsed_per_Sample_prop_Sample %>%
-  ggplot(mapping = aes(
-    x = Gender_collapsed,
-    y = Prop)
-  ) +
-  geom_bar(
-    aes(fill = Sample),
-    stat="identity",
-    binwidth = 1,
-    position = position_dodge2(preserve = "single")
-  ) +
-  labs(
-    x = "Gender_collapsed",
-    y = "Percentage per sample",
-    fill = "Sample") +
-  theme_personal +
-  scale_fill_manual(
-    values = COPINGpalette6
-  ) +
-  coord_flip()
-
-Gender_collapsed_by_Sample_prop_plot
-```
-
-# highest_education
-```{r highest_education per Sample prop per total}
-highest_education_per_Sample_prop_total <- dat %>%
-  count(highest_education, Sample) %>%
-  mutate(Prop = round(n/sum(n), 2))
-
-kable(highest_education_per_Sample_prop_total)
-highest_education_per_Sample_prop_total
-```
-
-```{r highest_education per Sample prop per Sample}
-highest_education_per_Sample_prop_Sample <- dat %>%
-  group_by(Sample) %>%
-  count(highest_education, Sample) %>%
-  mutate(Prop = round(n/sum(n), 2))
-
-kable(highest_education_per_Sample_prop_Sample)
-highest_education_per_Sample_prop_Sample
-```
-
-```{r highest_education per Sample prop cross table}
-highest_education_per_Sample_prop_Sample_cross_table <- dat %>%
-  group_by(Sample) %>%
-  count(highest_education, Sample) %>%
-  mutate(Prop = round(n/sum(n), 2)) %>%
-  pivot_wider(names_from = Sample, values_from = c(n, Prop))
-
-kable(highest_education_per_Sample_prop_Sample_cross_table)
-highest_education_per_Sample_prop_Sample_cross_table
-```
-
-```{r highest_education per Sample count cross table}
-highest_education_per_Sample_count_cross_table <- dat %>%
-  count(highest_education, Sample) %>%
-  spread(key = Sample, value = n) %>%
-  mutate(
-    EDGI = as.integer(replace_na(EDGI, 0)),
-    GLAD = as.integer(replace_na(GLAD, 0)),
-    NBR = as.integer(replace_na(NBR, 0)),
-    RAMP = as.integer(replace_na(RAMP, 0))
-  )
-
-kable(highest_education_per_Sample_count_cross_table)
-highest_education_per_Sample_count_cross_table
-```
-
-```{r highest_education per Sample chisquare test}
-highest_education_per_Sample_chissquare_test <- dat %>%
-  count(highest_education, Sample) %>%
-  spread(key = Sample, value = n) %>%
-  select(-highest_education) %>%
-  mutate(
-    EDGI = as.integer(replace_na(EDGI, 0)),
-    GLAD = as.integer(replace_na(GLAD, 0)),
-    NBR = as.integer(replace_na(NBR, 0)),
-    RAMP = as.integer(replace_na(RAMP, 0))
-  ) %>%
-  chisq.test() %>%
-  glance()
-
-kable(highest_education_per_Sample_chissquare_test)
-highest_education_per_Sample_chissquare_test
-```
-
-```{r highest_education by Sample count plot}
-highest_education_by_Sample_count_plot <- highest_education_per_Sample_prop_Sample %>%
-  ggplot(mapping = aes(
-    x = highest_education,
-    y = n)
-  ) +
-  geom_bar(
-    aes(fill = Sample),
-    stat="identity",
-    binwidth = 1,
-    position = position_dodge2(preserve = "single")
-  ) +
-  labs(
-    x = "highest_education",
-    y = "Number of participants",
-    fill = "Sample") +
-  theme_personal +
-  scale_fill_manual(
-    values = COPINGpalette6
-  ) +
-  coord_flip()
-
-highest_education_by_Sample_count_plot
-```
-
-```{r highest_education by Sample prop plot}
-highest_education_by_Sample_prop_plot <- highest_education_per_Sample_prop_Sample %>%
-  ggplot(mapping = aes(
-    x = highest_education,
-    y = Prop)
-  ) +
-  geom_bar(
-    aes(fill = Sample),
-    stat="identity",
-    binwidth = 1,
-    position = position_dodge2(preserve = "single")
-  ) +
-  labs(
-    x = "highest_education",
-    y = "Percentage per sample",
-    fill = "Sample") +
-  theme_personal +
-  scale_fill_manual(
-    values = COPINGpalette6
-  ) +
-  coord_flip()
-
-highest_education_by_Sample_prop_plot
-```
-
-# key_worker
-```{r key_worker per Sample prop per total}
-key_worker_per_Sample_prop_total <- dat %>%
-  count(key_worker, Sample) %>%
-  mutate(Prop = round(n/sum(n), 2))
-
-kable(key_worker_per_Sample_prop_total)
-key_worker_per_Sample_prop_total
-```
-
-```{r key_worker per Sample prop per Sample}
-key_worker_per_Sample_prop_Sample <- dat %>%
-  group_by(Sample) %>%
-  count(key_worker, Sample) %>%
-  mutate(Prop = round(n/sum(n), 2))
-
-kable(key_worker_per_Sample_prop_Sample)
-key_worker_per_Sample_prop_Sample
-```
-
-```{r key_worker per Sample prop cross table}
-key_worker_per_Sample_prop_Sample_cross_table <- dat %>%
-  group_by(Sample) %>%
-  count(key_worker, Sample) %>%
-  mutate(Prop = round(n/sum(n), 2)) %>%
-  pivot_wider(names_from = Sample, values_from = c(n, Prop))
-
-kable(key_worker_per_Sample_prop_Sample_cross_table)
-key_worker_per_Sample_prop_Sample_cross_table
-```
-
-```{r key_worker per Sample count cross table}
-key_worker_per_Sample_count_cross_table <- dat %>%
-  count(key_worker, Sample) %>%
-  spread(key = Sample, value = n) %>%
-  mutate(
-    EDGI = as.integer(replace_na(EDGI, 0)),
-    GLAD = as.integer(replace_na(GLAD, 0)),
-    NBR = as.integer(replace_na(NBR, 0)),
-    RAMP = as.integer(replace_na(RAMP, 0))
-  )
-
-kable(key_worker_per_Sample_count_cross_table)
-key_worker_per_Sample_count_cross_table
-```
-
-```{r key_worker per Sample chisquare test}
-key_worker_per_Sample_chissquare_test <- dat %>%
-  count(key_worker, Sample) %>%
-  spread(key = Sample, value = n) %>%
-  select(-key_worker) %>%
-  mutate(
-    EDGI = as.integer(replace_na(EDGI, 0)),
-    GLAD = as.integer(replace_na(GLAD, 0)),
-    NBR = as.integer(replace_na(NBR, 0)),
-    RAMP = as.integer(replace_na(RAMP, 0))
-  ) %>%
-  chisq.test() %>%
-  glance()
-
-kable(key_worker_per_Sample_chissquare_test)
-key_worker_per_Sample_chissquare_test
-```
-
-```{r key_worker by Sample count plot}
-key_worker_by_Sample_count_plot <- key_worker_per_Sample_prop_Sample %>%
-  ggplot(mapping = aes(
-    x = key_worker,
-    y = n)
-  ) +
-  geom_bar(
-    aes(fill = Sample),
-    stat="identity",
-    binwidth = 1,
-    position = position_dodge2(preserve = "single")
-  ) +
-  labs(
-    x = "key_worker",
-    y = "Number of participants",
-    fill = "Sample") +
-  theme_personal +
-  scale_fill_manual(
-    values = COPINGpalette6
-  ) +
-  coord_flip()
-
-key_worker_by_Sample_count_plot
-```
-
-```{r key_worker by Sample prop plot}
-key_worker_by_Sample_prop_plot <- key_worker_per_Sample_prop_Sample %>%
-  ggplot(mapping = aes(
-    x = key_worker,
-    y = Prop)
-  ) +
-  geom_bar(
-    aes(fill = Sample),
-    stat="identity",
-    binwidth = 1,
-    position = position_dodge2(preserve = "single")
-  ) +
-  labs(
-    x = "key_worker",
-    y = "Percentage per sample",
-    fill = "Sample") +
-  theme_personal +
-  scale_fill_manual(
-    values = COPINGpalette6
-  ) +
-  coord_flip()
-
-key_worker_by_Sample_prop_plot
-```
-
-# COVID
-## Recode variable
-```{r gad covid test positive double}
-dat <- dat %>%
-  mutate(covid_test_positive_double_numeric =
-           case_when(
-             (respiratory.throat_swab_test_nose_numeric == 1 &
-               respiratory.results_antibody_test_numeric == 1) ~ 2,
-             respiratory.throat_swab_test_nose_numeric == 1 ~ 1,
-             respiratory.throat_swab_test_nose_numeric == 2 ~ 0,
-             respiratory.results_antibody_test_numeric == 1 ~ 1,
-             respiratory.results_antibody_test_numeric == 2 ~ 0
-           )
-         )
-
-dat <- dat %>%
-  mutate(covid_test_positive_double =
-           recode_factor(
-             covid_test_positive_double_numeric,
-             `0` = "Negative",
-             `1` = "Positive",
-             `2` = "Double positive"
-           )
-         )
-
-dat %>%
-  freq(covid_test_positive_double)
-```
-
-```{r gad covid test positive}
-dat <- dat %>%
-  mutate(gad.covid_test_positive_numeric =
-           case_when(
-             (respiratory.throat_swab_test_nose_numeric == 1 &
-               respiratory.results_antibody_test_numeric == 1) ~ 1, # with two positive test results get coded as positive
-             respiratory.throat_swab_test_nose_numeric == 1 ~ 1,
-             respiratory.throat_swab_test_nose_numeric == 2 ~ 0,
-             respiratory.results_antibody_test_numeric == 1 ~ 1,
-             respiratory.results_antibody_test_numeric == 2 ~ 0
-           )
-         )
-
-dat <- dat %>%
-  mutate(covid_test_positive =
-           recode_factor(
-             gad.covid_test_positive_numeric,
-             `0` = "Negative",
-             `1` = "Positive"
-#             `2` = "Double positive"
-           )
-         )
-
-dat %>%
-  freq(covid_test_positive)
-```
-
-## COVID swab test positive
-```{r COVID positive swap}
-dat %>%
-  count(respiratory.throat_swab_test_nose, Sample) %>%
-  mutate(Prop = round(n/sum(n), 2))
-```
-
-## antibody test
-```{r COVID positive antibody test}
-dat %>%
-  count(respiratory.results_antibody_test, Sample) %>%
-  mutate(Prop = round(n/sum(n), 2))
-```
-
-## COVID probable diagnosis
-```{r COVID probable diagnosis}
-dat %>%
-  count(covid_probable_case_incl_screening, Sample) %>%
-  mutate(Prop = round(n/sum(n), 2))
-```
-
-## Cross table probable covid and covid test positive
-```{r Cross table probable covid and covid test positive}
-dat %>%
-  count(covid_test_positive, covid_probable_case_incl_screening) %>%
-  spread(key = covid_test_positive, value = n)
-```
-
-# Create data set per cohort
-
-## GAD
-```{r}
-dat.gad <- dat %>%
-#  drop_na() %>%
-  filter(
-    (data_group_gad == "Baseline and retrospective data" |
-      data_group_gad == "Prepandemic and baseline data" |
-      data_group_gad == "All prepandemic, baseline and retrospective data")
-  )
-
-dim(dat.gad)
-```
-
-# Questionnaire comparions
-
-## gad
-
-### Split sample in improvement and worsening
-```{r gad improvment worsening stratification}
-dat <- dat %>%
-  mutate(gad.change_binary_numeric =
-           case_when(
-             gad.pandemic_felt_feelings_numeric == 1 ~ 1,
-             gad.pandemic_felt_feelings_numeric == 2 ~ 1,
-             gad.pandemic_felt_feelings_numeric == 3 ~ 0,
-             gad.pandemic_felt_feelings_numeric == 4 ~ 2,
-             gad.pandemic_felt_feelings_numeric == 5 ~ 2
-           )
-         )
-
-dat <- dat %>%
-  mutate(gad.change_binary =
-           recode_factor(
-             gad.change_binary_numeric,
-             `0` = "No change",
-             `1` = "Worsening",
-             `2` = "Improvement"
-           )
-         )
-
-dat %>%
-  freq(gad.change_binary)
-```
-
-### Summary scores
-```{r descriptives gad.sum_score_cols}
-gad.sum_score_numeric_table <- dat %>% 
-  group_by(gad.change_binary) %>%
-  summarise_at( 
-    vars(
-      "Prepan" = gad.sum_score_prepan,
-      "Base" = gad.sum_score_base,
-      "Retro" = gad.sum_score_retro
-    ),
-    .funs =
-      list(
-        ~mean(., na.rm = T),
-        ~sd(., na.rm = T),
-        ~median(., na.rm = T),
-        ~min(., na.rm = T),
-        ~max(., na.rm = T),
-        ~skew(., na.rm = T),
-        kurtosis = ~kurtosi(., na.rm = T)
-      )
-  )
-
-gad.sum_score_numeric_table
-```
-
-```{r smart numeric summary tables}
-# reshape the table
-gad.sum_score_numeric_summary_table_reshaped <- gad.sum_score_numeric_table %>% 
-  gather(key, value, -gad.change_binary) %>% 
-  separate(key, c("variable", "measure"), sep = "_") %>%
-  mutate(measure = factor(
-    x = measure,
-    levels =  c( # this is the order I want my columns to appear in
-      "missing",
-      "min",
-      "max",
-      "mean", 
-      "median", 
-      "mode",
-      "sd",
-      "skew",
-      "kurtosis"
-    ))) %>% 
-  spread(measure, value) %>% 
-  # we can apply a function to all variables to edit them so that they are publication ready
-  rename_all(
-    .funs = ~str_to_title(.)
-  ) %>% 
-  # or we can individually rename variables 
-  rename(
-    Change = Gad.change_binary,
-    SD = Sd
-  )
-
-gad.sum_score_numeric_summary_table_reshaped
-```
-
-Table for knitting
-gad diff summary table
-```{r gad diff summary table}
-kable(gad.sum_score_numeric_summary_table_reshaped)
-```
-
-### Differences scores
-
-```{r descriptives gad.diff_score_cols}
-gad.numeric_table <- dat %>% 
-  group_by(gad.change_binary) %>%
-  summarise_at( 
-    vars(
-      "Base - prepan" = gad.diff_score_base_prepan,
-      "Base - retro" = gad.diff_score_base_retro,
-      "Prepan - retro" = gad.diff_score_retro_prepan
-    ),
-    .funs =
-      list(
-        ~mean(., na.rm = T),
-        ~sd(., na.rm = T),
-        ~median(., na.rm = T),
-        ~min(., na.rm = T),
-        ~max(., na.rm = T),
-        ~skew(., na.rm = T),
-        kurtosis = ~kurtosi(., na.rm = T)
-      )
-  )
-
-gad.numeric_table
-```
-
-```{r smart numeric summary tables}
-# reshape the table
-gad.numeric_summary_table_reshaped <- gad.numeric_table %>% 
-  gather(key, value, -gad.change_binary) %>% 
-  separate(key, c("variable", "measure"), sep = "_") %>%
-  mutate(measure = factor(
-    x = measure,
-    levels =  c( # this is the order I want my columns to appear in
-      "missing",
-      "min",
-      "max",
-      "mean", 
-      "median", 
-      "mode",
-      "sd",
-      "skew",
-      "kurtosis"
-    ))) %>% 
-  spread(measure, value) %>% 
-  # we can apply a function to all variables to edit them so that they are publication ready
-  rename_all(
-    .funs = ~str_to_title(.)
-    ) %>% 
-  # or we can individually rename variables 
-  rename(
-    Change = Gad.change_binary,
-    SD = Sd
-  )
-
-gad.numeric_summary_table_reshaped
-```
-
-Table for knitting
-gad diff summary table
-```{r gad diff summary table}
-kable(gad.numeric_summary_table_reshaped)
-```
-
-### Long format
-
-```{r gad gather to long format Time_points gad.diff_score}
-dat.long.gad.diff <- dat %>%
-  gather(
-    key = "Time_point_raw",
-    value = "gad.diff_score",
-    all_of(gad.diff_score_cols)) %>%
-  select(
-    ID,
-    Sample,
-    Gender_collapsed,
-    Ethnicity_collapsed,
-    Disorder_hierarchical,
-    Time_point_raw,
-    gad.diff_score
-  ) %>%
-  mutate(Time_point = str_replace(Time_point_raw, "gad.diff_score_", "")) %>%
-  select(-Time_point_raw)
-
-head(dat.long.gad.diff)
-```
-
-```{r gad gather to long format Time_points gad.sum_score}
-dat.long.gad.sum <- dat %>%
-  gather(
-    key = "Time_point_raw",
-    value = "gad.sum_score",
-    all_of(gad.sum_score_cols)) %>%
-  select(
-    ID,
-    Sample,
-    Gender_collapsed,
-    Ethnicity_collapsed,
-    Disorder_hierarchical,
-    Time_point_raw,
-    gad.sum_score
-  ) %>%
-  mutate(Time_point = str_replace(Time_point_raw, "gad.sum_score_", "")) %>%
-  select(-Time_point_raw)
-
-head(dat.long.gad.sum)
-```
-
-### Plots diff
-
-makes this into percentages
-```{r gad absolut plot}
-dat.long.gad.diff %>%
-  ggplot(mapping = aes(y = gad.diff_score)) +
-  geom_bar() +
-  theme_minimal() +
-  facet_wrap(facets = vars(Time_point))
-```
-
-```{r gad percentage plot retro_prepan diff}
-dat.long.gad.diff %>%
-  filter(Time_point != "retro_prepan") %>%
-  ggplot(mapping = aes(
-    x = gad.diff_score,
-    y = stat(density*width),
-    fill = Time_point)) +
-  geom_histogram(
-    binwidth = 1,
-    position = position_dodge2(preserve = "single")
-  ) +
-  labs(
-    x = "Difference GAD7 score",
-    y = "Percentage of participants",
-    fill = "Comparison:\nBaseline vs") +
-  theme_personal +
-  scale_fill_manual(values = palette, labels = c("Prepandemic", "Retrospective"))
-```
-
-```{r gad percentage plot retro_prepan, fig.height=6, fig.width=10}
-dat.long.gad.diff %>%
-  filter(Time_point != "retro_prepan") %>%
-  ggplot(mapping = aes(
-    x = gad.diff_score,
-    y = stat(density*width),
-    fill = Time_point)) +
-  geom_histogram(
-    binwidth = 1,
-    position = position_dodge2(preserve = "single")
-  ) +
-  labs(
-    x = "Difference GAD7 score",
-    y = "Percentage of participants",
-    fill = "Comparison:\nBaseline vs") +
-  theme_personal +
-  scale_fill_manual(values = palette, labels = c("Prepandemic", "Retrospective")) +
-  facet_wrap("Disorder_hierarchical")
-```
-
-```{r gad plot retro_prepan diff}
-dat.long.gad.diff %>%
-  filter(Time_point == "retro_prepan") %>%
-  ggplot(mapping = aes(
-    x = gad.diff_score,
-    y = stat(density*width),
-    fill = Time_point)) +
-  geom_histogram(
-    binwidth = 1,
-    position = position_dodge2(preserve = "single")
-  ) +
-  labs(
-    x = "Difference GAD7 score",
-    y = "Percentage of participants",
-    fill = "Comparison:\nRetrospective vs") +
-  theme_personal +
-  scale_fill_manual(values = palette, labels = c("Prepandemic"))
-```
-
-### Plots sum
-
-```{r gad percentage plot retro_prepan sum}
-dat.long.gad.sum %>%
-#  filter(Time_point != "retro_prepan") %>%
-  ggplot(mapping = aes(
-    x = gad.sum_score,
-    y = stat(density*width),
-    fill = Time_point)) +
-  geom_histogram(
-    binwidth = 1,
-    position = position_dodge2(preserve = "single")
-  ) +
-  labs(
-    x = "GAD7 scores",
-    y = "Percentage of participants",
-    fill = "Time point") +
-  theme_personal +
-  scale_fill_manual(
-    values = COPINGpalette3,
-    labels = c("Baseline", "Prepandemic", "Retrospective")
-    )
-```
-
-```{r gad percentage plot retro_prepan sum, fig.height=6, fig.width=10}
-dat.long.gad.sum %>%
-#  filter(Time_point != "retro_prepan") %>%
-  ggplot(mapping = aes(
-    x = gad.sum_score,
-    y = stat(density*width),
-    fill = Time_point)) +
-  geom_histogram(
-    binwidth = 1,
-    position = position_dodge2(preserve = "single")
-  ) +
-  labs(
-    x = "GAD7 score",
-    y = "Percentage of participants",
-    fill = "Time point") +
-  theme_personal +
-  scale_fill_manual(
-    values = COPINGpalette3,
-#    labels = c("Prepandemic", "Retrospective")
-    ) +
-  facet_wrap("Disorder_hierarchical")
-```
-
-## phq
-
-### Split sample in improvement and worsening
-```{r phq improvment worsening stratification}
-dat <- dat %>%
-  mutate(phq.change_binary_numeric =
-           case_when(
-             phq.pandemic_felt_feelings_numeric == 1 ~ 1,
-             phq.pandemic_felt_feelings_numeric == 2 ~ 1,
-             phq.pandemic_felt_feelings_numeric == 3 ~ 0,
-             phq.pandemic_felt_feelings_numeric == 4 ~ 2,
-             phq.pandemic_felt_feelings_numeric == 5 ~ 2
-           )
-  )
-
-dat <- dat %>%
-  mutate(phq.change_binary =
-           recode_factor(
-             phq.change_binary_numeric,
-             `0` = "No change",
-             `1` = "Worsening",
-             `2` = "Improvement"
-           )
-  )
-
-dat %>%
-  freq(phq.change_binary)
-```
-
-### Summary scores
-```{r descriptives phq.sum_score}
-phq.sum_score_numeric_table <- dat %>% 
-  group_by(phq.change_binary) %>%
-  summarise_at( 
-    vars(
-      "Prepan" = phq.sum_score_prepan,
-      "Base" = phq.sum_score_base,
-      "Retro" = phq.sum_score_retro
-    ),
-    .funs =
-      list(
-        ~mean(., na.rm = T),
-        ~sd(., na.rm = T),
-        ~median(., na.rm = T),
-        ~min(., na.rm = T),
-        ~max(., na.rm = T),
-        ~skew(., na.rm = T),
-        kurtosis = ~kurtosi(., na.rm = T)
-      )
-  )
-
-phq.sum_score_numeric_table
-```
-
-```{r smart numeric summary tables}
-# reshape the table
-phq.sum_score_numeric_summary_table_reshaped <- phq.sum_score_numeric_table %>%
-  gather(key, value, -phq.change_binary) %>% 
-  separate(key, c("variable", "measure"), sep = "_") %>%
-  mutate(measure = factor(
-    x = measure,
-    levels =  c( # this is the order I want my columns to appear in
-      "missing",
-      "min",
-      "max",
-      "mean", 
-      "median", 
-      "mode",
-      "sd",
-      "skew",
-      "kurtosis"
-    ))) %>% 
-  spread(measure, value) %>% 
-  # we can apply a function to all variables to edit them so that they are publication ready
-  rename_all(
-    .funs = ~str_to_title(.)
-  ) %>% 
-  # or we can individually rename variables 
-  rename(
-    SD = Sd
-  )
-
-phq.sum_score_numeric_summary_table_reshaped
-```
-
-Table for knitting
-phq diff summary table
-```{r phq diff summary table}
-kable(phq.sum_score_numeric_summary_table_reshaped)
-```
-
-### Differences score
-
-```{r descriptives phq.diff_score_cols}
-phq.numeric_table <- dat %>% 
-  group_by(phq.change_binary) %>%
-  summarise_at( 
-    vars(
-      "Base - prepan" = phq.diff_score_base_prepan,
-      "Base - retro" = phq.diff_score_base_retro,
-      "Prepan - retro" = phq.diff_score_retro_prepan
-    ),
-    .funs =
-      list(
-        ~mean(., na.rm = T),
-        ~sd(., na.rm = T),
-        ~median(., na.rm = T),
-        ~min(., na.rm = T),
-        ~max(., na.rm = T),
-        ~skew(., na.rm = T),
-        kurtosis = ~kurtosi(., na.rm = T)
-      )
-  )
-
-phq.numeric_table
-```
-
-```{r smart numeric summary tables}
-# reshape the table
-phq.numeric_summary_table_reshaped <- phq.numeric_table %>% 
-  gather(key, value, -phq.change_binary) %>% 
-  separate(key, c("variable", "measure"), sep = "_") %>%
-  mutate(measure = factor(
-    x = measure,
-    levels =  c( # this is the order I want my columns to appear in
-      "missing",
-      "min",
-      "max",
-      "mean", 
-      "median", 
-      "mode",
-      "sd",
-      "skew",
-      "kurtosis"
-    ))) %>% 
-  spread(measure, value) %>% 
-  # we can apply a function to all variables to edit them so that they are publication ready
-  rename_all(
-    .funs = ~str_to_title(.)
-  ) %>% 
-  # or we can individually rename variables 
-  rename(
-    SD = Sd
-  )
-
-phq.numeric_summary_table_reshaped
-```
-
-Table for knitting
-phq diff summary table
-```{r phq diff summary table}
-kable(phq.numeric_summary_table_reshaped)
-```
-
-### Long format
-
-```{r phq gather to long format Time_points}
-dat.long.phq.diff <- dat %>%
-  gather(
-    key = "Time_point_raw",
-    value = "phq.diff_score",
-    all_of(phq.diff_score_cols)) %>%
-  select(
-    ID,
-    Sample,
-    Gender_collapsed,
-    Ethnicity_collapsed,
-    Disorder_hierarchical,
-    Time_point_raw,
-    phq.diff_score
-  ) %>%
-  mutate(Time_point = str_replace(Time_point_raw, "phq.diff_score_", "")) %>%
-  select(-Time_point_raw)
-
-head(dat.long.phq.diff)
-```
-
-```{r phq gather to long format Time_points phq.sum_score}
-dat.long.phq.sum <- dat %>%
-  gather(
-    key = "Time_point_raw",
-    value = "phq.sum_score",
-    all_of(phq.sum_score_cols)) %>%
-  select(
-    ID,
-    Sample,
-    Gender_collapsed,
-    Ethnicity_collapsed,
-    Disorder_hierarchical,
-    Time_point_raw,
-    phq.sum_score
-  ) %>%
-  mutate(Time_point = str_replace(Time_point_raw, "phq.sum_score_", "")) %>%
-  select(-Time_point_raw)
-
-head(dat.long.phq.sum)
-```
-
-### Plots
-
-makes this into percentages
-```{r phq absolut plot}
-dat.long.phq.diff %>%
-  ggplot(mapping = aes(y = phq.diff_score)) +
-  geom_bar() +
-  theme_minimal() +
-  facet_wrap(facets = vars(Time_point))
-```
-
-```{r phq percentage plot retro_prepan}
-dat.long.phq.diff %>%
-  filter(Time_point != "retro_prepan") %>%
-  ggplot(mapping = aes(
-    x = phq.diff_score,
-    y = stat(density*width),
-    fill = Time_point)) +
-  geom_histogram(
-    binwidth = 1,
-    position = position_dodge2(preserve = "single")
-  ) +
-  labs(
-    x = "Difference PHQ9 score",
-    y = "Percentage of participants",
-    fill = "Comparison:\nBaseline vs") +
-  theme_personal +
-  scale_fill_manual(values = palette, labels = c("Prepandemic", "Retrospective"))
-```
-
-```{r phq plot retro_prepan diff}
-dat.long.phq.diff %>%
-  filter(Time_point == "retro_prepan") %>%
-  ggplot(mapping = aes(
-    x = phq.diff_score,
-    y = stat(density*width),
-    fill = Time_point)) +
-  geom_histogram(
-    binwidth = 1,
-    position = position_dodge2(preserve = "single")
-  ) +
-  labs(
-    x = "Difference phq7 score",
-    y = "Percentage of participants",
-    fill = "Comparison:\nPrepandemic vs") +
-  theme_personal +
-  scale_fill_manual(values = palette, labels = c("Retrospective"))
-```
-
-```{r phq percentage plot retro_prepan, fig.height=6, fig.width=10}
-dat.long.phq.diff %>%
-  filter(Time_point != "retro_prepan") %>%
-  ggplot(mapping = aes(
-    x = phq.diff_score,
-    y = stat(density*width),
-    fill = Time_point)) +
-  geom_histogram(
-    binwidth = 1,
-    position = position_dodge2(preserve = "single")
-  ) +
-  labs(
-    x = "Difference PHQ9 score",
-    y = "Percentage of participants",
-    fill = "Comparison:\nBaseline vs") +
-  theme_personal +
-  scale_fill_manual(values = palette, labels = c("Prepandemic", "Retrospective")) +
-  facet_wrap("Disorder_hierarchical")
-```
-
-### Plots sum
-
-```{r phq percentage plot retro_prepan sum}
-dat.long.phq.sum %>%
-  #  filter(Time_point != "retro_prepan") %>%
-  ggplot(mapping = aes(
-    x = phq.sum_score,
-    y = stat(density*width),
-    fill = Time_point)) +
-  geom_histogram(
-    binwidth = 1,
-    position = position_dodge2(preserve = "single")
-  ) +
-  labs(
-    x = "PHQ9 scores",
-    y = "Percentage of participants",
-    fill = "Time point") +
-  theme_personal +
-  scale_fill_manual(
-    values = COPINGpalette3,
-    labels = c("Baseline", "Prepandemic", "Retrospective")
-  )
-```
-
-```{r phq percentage plot retro_prepan sum, fig.height=6, fig.width=10}
-dat.long.phq.sum %>%
-  #  filter(Time_point != "retro_prepan") %>%
-  ggplot(mapping = aes(
-    x = phq.sum_score,
-    y = stat(density*width),
-    fill = Time_point)) +
-  geom_histogram(
-    binwidth = 1,
-    position = position_dodge2(preserve = "single")
-  ) +
-  labs(
-    x = "PHQ9 score",
-    y = "Percentage of participants",
-    fill = "Time point") +
-  theme_personal +
-  scale_fill_manual(
-    values = COPINGpalette3,
-    labels = c("Baseline", "Prepandemic", "Retrospective")
-  ) +
-  facet_wrap("Disorder_hierarchical")
-```
-
-## ocir
-
-### Split sample in improvement and worsening
-```{r ocir improvment worsening stratification}
-dat <- dat %>%
-  mutate(ocir.change_binary_numeric =
-           case_when(
-             ocir.felt_pandemic_feelings_numeric == 1 ~ 1,
-             ocir.felt_pandemic_feelings_numeric == 2 ~ 1,
-             ocir.felt_pandemic_feelings_numeric == 3 ~ 0,
-             ocir.felt_pandemic_feelings_numeric == 4 ~ 2,
-             ocir.felt_pandemic_feelings_numeric == 5 ~ 2
-           )
-  )
-
-dat <- dat %>%
-  mutate(ocir.change_binary =
-           recode_factor(
-             ocir.change_binary_numeric,
-             `0` = "No change",
-             `1` = "Worsening",
-             `2` = "Improvement"
-           )
-  )
-
-dat %>%
-  freq(ocir.change_binary)
-```
-
-### Summary scores
-```{r descriptives ocir.sum_score}
-ocir.sum_score_numeric_table <- dat %>% 
-  group_by(ocir.change_binary) %>%
-  summarise_at( 
-    vars(
-      "Prepan" = ocir.sum_score_prepan,
-      "Base" = ocir.sum_score_base,
-      "Retro" = ocir.sum_score_retro
-    ),
-    .funs =
-      list(
-        ~mean(., na.rm = T),
-        ~sd(., na.rm = T),
-        ~median(., na.rm = T),
-        ~min(., na.rm = T),
-        ~max(., na.rm = T),
-        ~skew(., na.rm = T),
-        kurtosis = ~kurtosi(., na.rm = T)
-      )
-  )
-
-ocir.sum_score_numeric_table
-```
-
-```{r smart numeric summary tables}
-# reshape the table
-ocir.sum_score_numeric_summary_table_reshaped <- ocir.sum_score_numeric_table %>%
-  filter(ocir.change_binary == "Worsening") %>%
-  select(-ocir.change_binary) %>%
-  gather(key, value) %>% 
-  separate(key, c("variable", "measure"), sep = "_") %>%
-  mutate(measure = factor(
-    x = measure,
-    levels =  c( # this is the order I want my columns to appear in
-      "missing",
-      "min",
-      "max",
-      "mean", 
-      "median", 
-      "mode",
-      "sd",
-      "skew",
-      "kurtosis"
-    ))) %>% 
-  spread(measure, value) %>% 
-  # we can apply a function to all variables to edit them so that they are publication ready
-  rename_all(
-    .funs = ~str_to_title(.)
-  ) %>% 
-  # or we can individually rename variables 
-  rename(
-    SD = Sd
-  )
-
-ocir.sum_score_numeric_summary_table_reshaped
-```
-
-Table for knitting
-ocir diff summary table
-```{r ocir diff summary table}
-kable(ocir.sum_score_numeric_summary_table_reshaped)
-```
-
-### Differences scores
-
-```{r descriptives ocir.diff_score_cols}
-ocir.numeric_table <- dat %>% 
-  #  group_by(dem.sex) %>%
-  summarise_at( 
-    vars(
-      "Base - prepan" = ocir.diff_score_base_prepan,
-      "Base - retro" = ocir.diff_score_base_retro,
-      "Prepan - retro" = ocir.diff_score_retro_prepan
-    ),
-    .funs =
-      list(
-        ~mean(., na.rm = T),
-        ~sd(., na.rm = T),
-        ~median(., na.rm = T),
-        ~min(., na.rm = T),
-        ~max(., na.rm = T),
-        ~skew(., na.rm = T),
-        kurtosis = ~kurtosi(., na.rm = T)
-      )
-  )
-
-ocir.numeric_table
-```
-
-```{r smart numeric summary tables}
-# reshape the table
-ocir.numeric_summary_table_reshaped <- ocir.numeric_table %>% 
-  gather(key, value) %>% 
-  separate(key, c("variable", "measure"), sep = "_") %>%
-  mutate(measure = factor(
-    x = measure,
-    levels =  c( # this is the order I want my columns to appear in
-      "missing",
-      "min",
-      "max",
-      "mean", 
-      "median", 
-      "mode",
-      "sd",
-      "skew",
-      "kurtosis"
-    ))) %>% 
-  spread(measure, value) %>% 
-  # we can apply a function to all variables to edit them so that they are publication ready
-  rename_all(
-    .funs = ~str_to_title(.)
-  ) %>% 
-  # or we can individually rename variables 
-  rename(
-    SD = Sd
-  )
-
-ocir.numeric_summary_table_reshaped
-```
-
-Table for knitting
-ocir diff summary table
-```{r ocir diff summary table}
-kable(ocir.numeric_summary_table_reshaped)
-```
-
-### Long format
-
-```{r ocir gather to long format Time_points}
-dat.long.ocir.diff <- dat %>%
-  gather(
-    key = "Time_point_raw",
-    value = "ocir.diff_score",
-    all_of(ocir.diff_score_cols)) %>%
-  select(
-    ID,
-    Sample,
-    Gender_collapsed,
-    Ethnicity_collapsed,
-    Disorder_hierarchical,
-    Time_point_raw,
-    ocir.diff_score
-  ) %>%
-  mutate(Time_point = str_replace(Time_point_raw, "ocir.diff_score_", "")) %>%
-  select(-Time_point_raw)
-
-head(dat.long.ocir.diff)
-```
-
-```{r ocir gather to long format Time_points ocir.sum_score}
-dat.long.ocir.sum <- dat %>%
-  gather(
-    key = "Time_point_raw",
-    value = "ocir.sum_score",
-    all_of(ocir.sum_score_cols)) %>%
-  select(
-    ID,
-    Sample,
-    Gender_collapsed,
-    Ethnicity_collapsed,
-    Disorder_hierarchical,
-    Time_point_raw,
-    ocir.sum_score
-  ) %>%
-  mutate(Time_point = str_replace(Time_point_raw, "ocir.sum_score_", "")) %>%
-  select(-Time_point_raw)
-
-head(dat.long.ocir.sum)
-```
-
-### Plots
-
-makes this into percentages
-```{r ocir absolut plot}
-dat.long.ocir.diff %>%
-  ggplot(mapping = aes(y = ocir.diff_score)) +
-  geom_bar() +
-  theme_minimal() +
-  facet_wrap(facets = vars(Time_point))
-```
-
-```{r ocir percentage plot retro_prepan}
-dat.long.ocir.diff %>%
-  filter(Time_point != "retro_prepan") %>%
-  ggplot(mapping = aes(
-    x = ocir.diff_score,
-    y = stat(density*width),
-    fill = Time_point)) +
-  geom_histogram(
-    binwidth = 1,
-    position = position_dodge2(preserve = "single")
-  ) +
-  labs(
-    x = "Difference OCI-R score",
-    y = "Percentage of participants",
-    fill = "Comparison:\nBaseline vs") +
-  theme_personal +
-  scale_fill_manual(values = palette, labels = c("Prepandemic", "Retrospective"))
-```
-
-```{r ocir plot retro_prepan diff}
-dat.long.ocir.diff %>%
-  filter(Time_point == "retro_prepan") %>%
-  ggplot(mapping = aes(
-    x = ocir.diff_score,
-    y = stat(density*width),
-    fill = Time_point)) +
-  geom_histogram(
-    binwidth = 1,
-    position = position_dodge2(preserve = "single")
-  ) +
-  labs(
-    x = "Difference ocir7 score",
-    y = "Percentage of participants",
-    fill = "Comparison:\nPrepandemic vs") +
-  theme_personal +
-  scale_fill_manual(values = palette, labels = c("Retrospective"))
-```
-
-```{r ocir percentage plot retro_prepan, fig.height=6, fig.width=10}
-dat.long.ocir.diff %>%
-  filter(Time_point != "retro_prepan") %>%
-  ggplot(mapping = aes(
-    x = ocir.diff_score,
-    y = stat(density*width),
-    fill = Time_point)) +
-  geom_histogram(
-    binwidth = 1,
-    position = position_dodge2(preserve = "single")
-  ) +
-  labs(
-    x = "Difference OCI-R score",
-    y = "Percentage of participants",
-    fill = "Comparison:\nBaseline vs") +
-  theme_personal +
-  scale_fill_manual(values = palette, labels = c("Prepandemic", "Retrospective")) +
-  facet_wrap("Disorder_hierarchical")
-```
-
-### Plots sum
-
-```{r ocir percentage plot retro_prepan sum}
-dat.long.ocir.sum %>%
-  ggplot(mapping = aes(
-    x = ocir.sum_score,
-    y = stat(density*width),
-    fill = Time_point)) +
-  geom_histogram(
-    binwidth = 1,
-    position = position_dodge2(preserve = "single")
-  ) +
-  labs(
-    x = "OCI-R scores",
-    y = "Percentage of participants",
-    fill = "Time point") +
-  theme_personal +
-  scale_fill_manual(
-    values = COPINGpalette3,
-    labels = c("Baseline", "Prepandemic", "Retrospective")
-  )
-```
-
-```{r ocir percentage plot retro_prepan sum, fig.height=6, fig.width=10}
-dat.long.ocir.sum %>%
-  ggplot(mapping = aes(
-    x = ocir.sum_score,
-    y = stat(density*width),
-    fill = Time_point)) +
-  geom_histogram(
-    binwidth = 1,
-    position = position_dodge2(preserve = "single")
-  ) +
-  labs(
-    x = "OCI-R score",
-    y = "Percentage of participants",
-    fill = "Time point") +
-  theme_personal +
-  scale_fill_manual(
-    values = COPINGpalette3,
-    labels = c("Baseline", "Prepandemic", "Retrospective")
-  ) +
-  facet_wrap("Disorder_hierarchical")
-```
-
-Rank the disorders by the size of the change
-
-PCL:  
-Calculate the total GLAD, COPING, RAMP baseline 
-## pcl
-
-```{r descriptives pcl.diff_score_cols}
-pcl.numeric_table <- dat %>% 
-#    group_by(Sample) %>%
-  summarise_at( 
-    vars(
-      "Base - prepan" = pcl.diff_score_base_prepan
-    ),
-    .funs =
-      list(
-        ~mean(., na.rm = T),
-        ~sd(., na.rm = T),
-        ~median(., na.rm = T),
-        ~min(., na.rm = T),
-        ~max(., na.rm = T),
-        ~skew(., na.rm = T),
-        kurtosis = ~kurtosi(., na.rm = T)
-      )
-  )
-
-pcl.numeric_table
-```
-
-```{r smart numeric summary tables}
-# reshape the table
-pcl.numeric_summary_table_reshaped <- pcl.numeric_table %>% 
-  gather(key, value) %>% 
-  separate(key, c("variable", "measure"), sep = "_") %>%
-  mutate(measure = factor(
-    x = measure,
-    levels =  c( # this is the order I want my columns to appear in
-      "missing",
-      "min",
-      "max",
-      "mean", 
-      "median", 
-      "mode",
-      "sd",
-      "skew",
-      "kurtosis"
-    ))) %>% 
-  spread(measure, value) %>% 
-  # we can apply a function to all variables to edit them so that they are publication ready
-  rename_all(
-    .funs = ~str_to_title(.)
-  ) %>% 
-  # or we can individually rename variables 
-  rename(
-    SD = Sd
-  )
-
-pcl.numeric_summary_table_reshaped
-```
-
-Table for knitting
-pcl diff summary table
-```{r pcl diff summary table}
-kable(pcl.numeric_summary_table_reshaped)
-```
-
-```{r descriptives pcl.sum_score}
-pcl.sum_score_numeric_table <- dat %>% 
-#    group_by(Sample) %>%
-  summarise_at( 
-    vars(
-      "Prepan" = pcl.sum_score_prepan,
-      "Base" = pcl.sum_score_base
-    ),
-    .funs =
-      list(
-        ~mean(., na.rm = T),
-        ~sd(., na.rm = T),
-        ~median(., na.rm = T),
-        ~min(., na.rm = T),
-        ~max(., na.rm = T),
-        ~skew(., na.rm = T),
-        kurtosis = ~kurtosi(., na.rm = T)
-      )
-  )
-
-pcl.numeric_table
-```
-
-```{r smart numeric summary tables}
-# reshape the table
-pcl.sum_score_numeric_summary_table_reshaped <- pcl.sum_score_numeric_table %>% 
-  gather(key, value) %>% 
-  separate(key, c("variable", "measure"), sep = "_") %>%
-  mutate(measure = factor(
-    x = measure,
-    levels =  c( # this is the order I want my columns to appear in
-      "missing",
-      "min",
-      "max",
-      "mean", 
-      "median", 
-      "mode",
-      "sd",
-      "skew",
-      "kurtosis"
-    ))) %>% 
-  spread(measure, value) %>% 
-  # we can apply a function to all variables to edit them so that they are publication ready
-  rename_all(
-    .funs = ~str_to_title(.)
-  ) %>% 
-  # or we can individually rename variables 
-  rename(
-    SD = Sd
-  )
-
-pcl.sum_score_numeric_summary_table_reshaped
-```
-
-Table for knitting
-pcl diff summary table
-```{r pcl diff summary table}
-kable(pcl.sum_score_numeric_summary_table_reshaped)
-```
-
-```{r pcl gather to long format Time_points pcl.sum_score}
-dat.long.pcl.sum <- dat %>%
-  gather(
-    key = "Time_point_raw",
-    value = "pcl.sum_score",
-    all_of(pcl.sum_score_cols)) %>%
-  select(
-    ID,
-    Sample,
-    Gender_collapsed,
-    Ethnicity_collapsed,
-    Disorder_hierarchical,
-    Time_point_raw,
-    pcl.sum_score
-  ) %>%
-  mutate(Time_point = str_replace(Time_point_raw, "pcl.sum_score_", "")) %>%
-  select(-Time_point_raw)
-
-head(dat.long.pcl.sum)
-```
-
-For each item 
-present percentages of how say that this is due to the pandemic 
-```{r pcl percentages due to pandemic}
-pcl.retro.items <- c(
-  "pcl.stressful_experience_upset_reminded_retro_numeric",
-  "pcl.stressful_experience_repeated_images_retro_numeric",
-  "pcl.stressful_situation_avoiding_activities_retro_numeric",
-  "pcl.cut_people_feeling_distant_retro_numeric",
-  "pcl.difficulty_concentrating_retro_numeric",
-  "pcl.feeling_irritable_or_having_angry_outbursts_retro_numeric"
-)
-
-pcl.percentages.summary <- dat %>%
-  select(
-    all_of(pcl.retro.items)
-  ) %>%
-  gather(
-    key = "PCL Item",
-    value = "Binary_score",
-    all_of(pcl.retro.items)
-  ) %>%
-  mutate(Binary_score = fct_explicit_na(as.factor(Binary_score), na_level = "Missing")) %>%
-  group_by(`PCL Item`) %>%
-  count(`PCL Item`, Binary_score) %>%
-  mutate(prop = round(n/sum(n), 3)*100) %>%
-  mutate(n_prop = paste0(n," (",prop, "%)"))
-
-pcl.percentages.summary
-```
-
-### Plots sum
-
-```{r pcl percentage plot retro_prepan sum}
-dat.long.pcl.sum %>%
-  ggplot(mapping = aes(
-    x = pcl.sum_score,
-    y = stat(density*width),
-    fill = Time_point)) +
-  geom_histogram(
-    binwidth = 1,
-    position = position_dodge2(preserve = "single")
-  ) +
-  labs(
-    x = "PCL scores",
-    y = "Percentage of participants",
-    fill = "Time point") +
-  theme_personal +
-  scale_fill_manual(
-    values = COPINGpalette3,
-    labels = c("Baseline", "Prepandemic", "Retrospective")
-  )
-```
-
-```{r pcl percentage plot retro_prepan sum, fig.height=6, fig.width=10}
-dat.long.pcl.sum %>%
-  ggplot(mapping = aes(
-    x = pcl.sum_score,
-    y = stat(density*width),
-    fill = Time_point)) +
-  geom_histogram(
-    binwidth = 1,
-    position = position_dodge2(preserve = "single")
-  ) +
-  labs(
-    x = "PCL score",
-    y = "Percentage of participants",
-    fill = "Time point") +
-  theme_personal +
-  scale_fill_manual(
-    values = COPINGpalette3,
-    labels = c("Baseline", "Prepandemic", "Retrospective")
-  ) +
-  facet_wrap("Disorder_hierarchical")
-```
-
 # Regression

### 2020-09-03 PANCHANGE_analysis.Rmd
Corrected dataset namings, required after the exclusion chunk was moved.

@@
 ```{r dat.mhd - Vectors with sum_score_cols}
-sum_score_cols <- dat.mhd %>%
+sum_score_cols <- dat.raw %>%
   select(contains("sum_score")) %>%
@@
 
-phq.sum_score_cols <- dat.mhd %>%
+phq.sum_score_cols <- dat.raw %>%
   select(contains("phq")) %>%
@@
 
-gad.sum_score_cols <- dat.mhd %>%
+gad.sum_score_cols <- dat.raw %>%
   select(contains("gad")) %>%
@@
 
-ocir.sum_score_cols <- dat.mhd %>%
+ocir.sum_score_cols <- dat.raw %>%
   select(contains("ocir")) %>%
@@
 
-pcl.sum_score_cols <- dat.mhd %>%
+pcl.sum_score_cols <- dat.raw %>%
   select(contains("pcl")) %>%
@@
 ```{r Vectors with diff_score_cols}
-diff_score_cols <- dat.mhd %>%
+diff_score_cols <- dat.raw %>%
   select(contains("diff_score")) %>% 
@@
 
-phq.diff_score_cols <- dat.mhd %>%
+phq.diff_score_cols <- dat.raw %>%
   select(contains("phq")) %>%
@@
 
-gad.diff_score_cols <- dat.mhd %>%
+gad.diff_score_cols <- dat.raw %>%
   select(contains("gad")) %>%
@@
 
-ocir.diff_score_cols <- dat.mhd %>%
+ocir.diff_score_cols <- dat.raw %>%
   select(contains("ocir")) %>%
@@
 
-dat <- dat.raw %>%
+dat <- dat %>%
   mutate(

### 2020-09-03 PANCHANGE_analysis.Rmd
Exclusions block rearranged again. Small changes to dataset names. Notes made where data needs fixing.

@@
 
+# Exclusions
+
+Exclude GLAD/EDGI individuals that didn't take part in COPING
+Exclude individuals with NA for the MHD categories
+
+++MD: There's an issue with the EDGI obsessive_compulsive_disorders variable. There are >400 NAs so we are only left with 78 EDGI participants in the dataset.
+```{r exclusion criteria for diagnoses analysis}
+dat <- dat.raw %>%
+  filter(
+    !is.na(depressive_disorders) &
+      !is.na(eating_disorders) &
+      !is.na(psychotic_disorders) &
+      !is.na(obsessive_compulsive_disorders) &
+      !is.na(autism_spectrum_disorder) &
+      !is.na(mhd.mania_hypomania_bipolar_or_manicdepression_numeric) &
+      !is.na(mhd.posttraumatic_stress_disorder_ptsd_numeric) &
+      !is.na(control)
+  ) %>% 
+  drop_na(startDate.coping)
+
+dim(dat.raw)
+dim(dat)
+
+```
+
 # Collapsing categories
@@
 ```{r Inspect age_category}
-dat.raw %>%
+dat %>%
   freq(age_category)
 
-dat.raw %>%
+dat %>%
   freq(age_category_numeric)
@@
 ```{r Collapse age_category}
-dat.raw <- dat.raw %>%
+dat <- dat %>%
   mutate(age_category_collapsed_numeric =
@@
 
-dat.raw <- dat.raw %>%
+dat <- dat %>%
   mutate(age_category_collapsed =
@@
 
-dat.raw %>%
+dat %>%
   freq(age_category_collapsed)
@@
 ```{r Inspect Gender}
-dat.raw %>%
+dat %>%
   freq(Gender)
 
-dat.raw %>%
+dat %>%
   freq(Gender_numeric)
@@
 ```{r Collapse Gender}
-dat.raw <- dat.raw %>%
+dat <- dat %>%
   mutate(Gender_collapsed_numeric =
@@
 
-dat.raw <- dat.raw %>%
+dat <- dat %>%
   mutate(Gender_collapsed =
@@
 
-dat.raw %>%
+dat %>%
   freq(Gender_collapsed)
@@
 ## Ethnicity
+++MD: The ethnicity_numeric variable has more NAs (N = 14304) than the ethnicity categorical variable (N = 3568). Something strange must have happened during the conversion to numeric?
 ```{r Inspect Ethnicity}
-dat.raw %>%
+dat %>%
   freq(Ethnicity)
 
-dat.raw %>%
+dat %>%
   freq(Ethnicity_numeric)
+
 ```
@@
 ++MD: Need to decide what to do with the Arab grouping.
+++MD: Why is "Other ethnic group" recoded as Asian or Asian British?
 ```{r Collapse Ethnicity}
-dat.raw <- dat.raw %>%
+dat <- dat %>%
   mutate(Ethnicity_collapsed_numeric =
            case_when(
-             Ethnicity_numeric == 1 ~ 0,
-             Ethnicity_numeric == 2 ~ 1,
-             Ethnicity_numeric == 3 ~ 2,
-             Ethnicity_numeric == 4 ~ 3,
-             Ethnicity_numeric == 5 ~ 3,
-             Ethnicity_numeric == 6 ~ 4
-           )
-  )
-
-dat.raw <- dat.raw %>%
+             Ethnicity_numeric == 1 ~ 0, #European
+             Ethnicity_numeric == 2 ~ 1, #Mixed or multiple ethnic origins 
+             Ethnicity_numeric == 3 ~ 2, #Asian or Asian British
+             Ethnicity_numeric == 4 ~ 3, #African or African British
+             Ethnicity_numeric == 5 ~ 3, #Arab - combined with African/African British
+             Ethnicity_numeric == 6 ~ 4  #Other ethnic group
+           )
+  )
+
+dat <- dat %>%
   mutate(Ethnicity_collapsed =
@@
 
-dat.raw %>%
+dat %>%
   freq(Ethnicity_collapsed)
@@
 
-Diagnoses analyses
-```{r dat.mhd - Vectors with sum_score_cols}
-sum_score_cols <- dat.raw %>%
+```{r Vectors with sum_score_cols}
+sum_score_cols <- dat %>%
   select(contains("sum_score")) %>%
@@
 
-phq.sum_score_cols <- dat.raw %>%
+phq.sum_score_cols <- dat %>%
   select(contains("phq")) %>%
@@
 
-gad.sum_score_cols <- dat.raw %>%
+gad.sum_score_cols <- dat %>%
   select(contains("gad")) %>%
@@
 
-ocir.sum_score_cols <- dat.raw %>%
+ocir.sum_score_cols <- dat %>%
   select(contains("ocir")) %>%
@@
 
-pcl.sum_score_cols <- dat.raw %>%
+pcl.sum_score_cols <- dat %>%
   select(contains("pcl")) %>%
@@
 ```{r Vectors with diff_score_cols}
-diff_score_cols <- dat.raw %>%
+diff_score_cols <- dat %>%
   select(contains("diff_score")) %>% 
@@
 
-phq.diff_score_cols <- dat.raw %>%
+phq.diff_score_cols <- dat %>%
   select(contains("phq")) %>%
@@
 
-gad.diff_score_cols <- dat.raw %>%
+gad.diff_score_cols <- dat %>%
   select(contains("gad")) %>%
@@
 
-ocir.diff_score_cols <- dat.raw %>%
+ocir.diff_score_cols <- dat %>%
   select(contains("ocir")) %>%
@@
 ```{r Psychiatric disorders hierarchy including psychosis}
-dat <- dat.raw %>%
+dat <- dat %>%
   mutate(
@@
 ## Recode variable
-```{r gad covid test positive double}
+```{r covid test positive double}
 dat <- dat %>%
@@
 # Create data set per cohort
+++MD: Do we want to break up the datasets by cohort again? Or is this breaking up datasets into GAD
 
@@
 
-# Exclusion
-Filter data frame to create 3 datasets:
-  1. Diagnoses analyses
-        i. Exclude individuals with NA for MHD
-  2. Retrospective - baseline change anlyses
-        i. Exclude individuals with NAs for:
-              1. MHD
-              2. Age
-              3. Gender
-  3. Prepandemic - baseline change analyses
-          i. Exclude individuals with NAs for:
-              1. MHD
-              2. Age
-              3. Gender
-          ii. Exclude individuals with prepandemic data collected after 1st March.
-
-Diagnoses analyses
-Exclude individuals with NA for the MHD categories
-```{r exclusion criteria for diagnoses analysis}
-dat.mhd <- dat.raw %>%
-  filter(
-    !is.na(depressive_disorders) &
-      !is.na(eating_disorders) &
-      !is.na(psychotic_disorders) &
-      !is.na(obsessive_compulsive_disorders) &
-      !is.na(autism_spectrum_disorder) &
-      !is.na(mhd.mania_hypomania_bipolar_or_manicdepression_numeric) &
-      !is.na(mhd.posttraumatic_stress_disorder_ptsd_numeric) &
-      !is.na(control)
-  )
-
-dim(dat.mhd)
-
-```
-
-Retro-baseline analyses
-Exclude individuals with NA for MHD, age, gender
-```{r exclusion criteria for retro-baseline analysis}
-dat.retro <- dat.mhd %>%
-  filter(
-    ((data_group_gad == "Baseline and retrospective data" |
-      data_group_gad == "All prepandemic, baseline and retrospective data") |
-      (data_group_phq == "Baseline and retrospective data" |
-      data_group_phq == "All prepandemic, baseline and retrospective data") |
-      (data_group_pcl == "Baseline and retrospective data" |
-      data_group_pcl == "All prepandemic, baseline and retrospective data") |
-      (data_group_ocir == "Baseline and retrospective data" |
-      data_group_ocir == "All prepandemic, baseline and retrospective data")) &
-      !is.na(age_category) &
-      !is.na(Gender_collapsed)
-  )
-
-dim(dat.retro)
-```
-
-Prepan-baseline analyses
-Exclude individuals with NA for MHD, age, gender; exclude if prepan data collected after 1 March
-```{r exclusion criteria for prepan-baseline analysis}
-dat.prepan <- dat.mhd %>%
-  filter(
-    ((data_group_gad == "Baseline and retrospective data" |
-      data_group_gad == "Prepandemic and baseline data" |
-      data_group_gad == "All prepandemic, baseline and retrospective data") |
-      (data_group_phq == "Baseline and retrospective data" |
-      data_group_phq == "Prepandemic and baseline data" |
-      data_group_phq == "All prepandemic, baseline and retrospective data") |
-      (data_group_pcl == "Baseline and retrospective data" |
-      data_group_pcl == "Prepandemic and baseline data" |
-      data_group_pcl == "All prepandemic, baseline and retrospective data") |
-      (data_group_ocir == "Baseline and retrospective data" |
-      data_group_ocir == "Prepandemic and baseline data" |
-      data_group_ocir == "All prepandemic, baseline and retrospective data")) &
-      !is.na(age_category) &
-      !is.na(Gender_collapsed) &
-      prepandemic_march_1_numeric == 1
-  )
-
-dim(dat.prepan)
-```
-
 # Psychiatric disorders
@@
 ## Correlation matrix
-Using dat for the correlation matrix.
 ```{r Correlation matrix of psychiatric disorders}
@@
 
+# Create additional datasets for analyses
+Filter data frame to create 3 datasets:
+
+  1. Retrospective - baseline change anlyses
+        i. Exclude individuals with NAs for:
+              1. MHD
+              2. Age
+              3. Gender
+              4. Missing retrospective and/or baseline data
+  2. Prepandemic - baseline change analyses
+          i. Exclude individuals with NAs for:
+              1. MHD
+              2. Age
+              3. Gender
+              4. Missing pandemic and/or baseline data
+          ii. Exclude individuals with prepandemic data collected after 1st March.
+
+Retro-baseline analyses
+Exclude individuals with NA for MHD, age, gender
+```{r exclusion criteria for retro-baseline analysis}
+dat.retro <- dat %>%
+  filter(
+    ((data_group_gad == "Baseline and retrospective data" |
+      data_group_gad == "All prepandemic, baseline and retrospective data") |
+      (data_group_phq == "Baseline and retrospective data" |
+      data_group_phq == "All prepandemic, baseline and retrospective data") |
+      (data_group_pcl == "Baseline and retrospective data" |
+      data_group_pcl == "All prepandemic, baseline and retrospective data") |
+      (data_group_ocir == "Baseline and retrospective data" |
+      data_group_ocir == "All prepandemic, baseline and retrospective data"))
+  )
+
+dim(dat.retro)
+```
+
+Prepan-baseline analyses
+Exclude individuals with NA for MHD, age, gender; exclude if prepan data collected after 1 March
+```{r exclusion criteria for prepan-baseline analysis}
+dat.prepan <- dat %>%
+  filter(
+    ((data_group_gad == "Baseline and retrospective data" |
+      data_group_gad == "Prepandemic and baseline data" |
+      data_group_gad == "All prepandemic, baseline and retrospective data") |
+      (data_group_phq == "Baseline and retrospective data" |
+      data_group_phq == "Prepandemic and baseline data" |
+      data_group_phq == "All prepandemic, baseline and retrospective data") |
+      (data_group_pcl == "Baseline and retrospective data" |
+      data_group_pcl == "Prepandemic and baseline data" |
+      data_group_pcl == "All prepandemic, baseline and retrospective data") |
+      (data_group_ocir == "Baseline and retrospective data" |
+      data_group_ocir == "Prepandemic and baseline data" |
+      data_group_ocir == "All prepandemic, baseline and retrospective data")) &
+      prepandemic_march_1_numeric == 1
+  )
+
+dim(dat.prepan)
+```
+
 # Regression

### 2020-09-03 PANCHANGE_analysis.Rmd
Reorganised the regression models and created prepan-baseline and retro-baseline models for all disorders.

@@
 Exclude individuals with NA for the MHD categories
+Individuals with NAs for age/gender have already been excluded in pre-processing script.
 
@@
 
-# Create data set per cohort
-++MD: Do we want to break up the datasets by cohort again? Or is this breaking up datasets into GAD
+# Create data set per measure
+++MD: Do we want to break up the datasets by measure?
+I think the datasets we've already specified should be sufficient.
+I've tested the results of the regression model and it's the same using dat.gad vs.
+dat datasets.
 
@@
 # Create additional datasets for analyses
-Filter data frame to create 3 datasets:
+Filter data frame to create 2 additional datasets. Additional exclusion criteria (beyond those listed above) are specified below:
 
   1. Retrospective - baseline change anlyses
-        i. Exclude individuals with NAs for:
-              1. MHD
-              2. Age
-              3. Gender
-              4. Missing retrospective and/or baseline data
+        i. Exclude individuals missing retrospective and/or baseline data
   2. Prepandemic - baseline change analyses
-          i. Exclude individuals with NAs for:
-              1. MHD
-              2. Age
-              3. Gender
-              4. Missing pandemic and/or baseline data
+          i. Exclude individuals missing pandemic and/or baseline data
           ii. Exclude individuals with prepandemic data collected after 1st March.
@@
 
-Model 0a: Disorder_hierarchical
-```{r Model 0a: Disorder_hierarchical}
-model0a <- lm(
-  formula = gad.diff_score_base_prepan ~ Disorder_hierarchical,
-  data = dat.gad)
-
-summary(model0a)
-```
-
-Model 0b: Disorders
-```{r}
-model0b <- lm(
-  formula = ocir.diff_score_base_prepan ~
+Model naming conventions:
+0 - unadjusted
+1 - adjusted
+a - hierarchical disorders
+b - overlapping disorder categories
+
+++MD: We may want to exclude disorders from Model b that aren't including in the hierarchy (e.g. ADHD, ASD)
+
+## Prepan-baseline change
+
+### GAD
+Model 0a: Disorder_hierarchical, Unadjusted
+```{r GAD prepan Model 0a}
+gad_prepan_model0a <- lm(
+  formula = gad.diff_score_base_prepan ~ 
+    Disorder_hierarchical,
+  data = dat.prepan)
+
+summary(gad_prepan_model0a)
+tidy(gad_prepan_model0a)
+```
+
+Model 0b: Overlapping disorders, Unadjusted
+```{r GAD prepan Model 0b}
+gad_prepan_model0b <- lm(
+  formula = gad.diff_score_base_prepan ~
     anxiety_disorders +
@@
     mhd.personality_disorder,
-  data = dat)
-
-summary(model0b)
-```
-
-Model 0: Disorders
-```{r}
-model0 <- lm(
-  formula = gad.diff_score_base_prepan ~ Disorder,
-  data = dat)
-
-summary(model0)
-```
-
-```{r}
-tidy(model0)
-```
-
-Model 1: Model 0 + Sex + Age + Ethnicity_collapsed + Time registration and baseline
-```{r}
-model1 <- lm(
+  data = dat.prepan)
+
+summary(gad_prepan_model0b)
+tidy(gad_prepan_model0b)
+```
+
+Model 1a: Disorder hierarchical, Adjusted
+  Model 0a + Sex + Age + Ethnicity_collapsed + Time registration and baseline
+```{r GAD prepan Model 1a}
+gad_prepan_model1a <- lm(
+  formula = gad.diff_score_base_prepan ~ 
+    Disorder_hierarchical + 
+    Gender_collapsed + 
+    age_category + 
+    Ethnicity_collapsed + 
+    time_diff_sign_up_coping,
+  data = dat.prepan)
+
+summary(gad_prepan_model1a)
+tidy(gad_prepan_model1a)
+```
+
+Model 1b: Overlapping disorders, Adjusted
+  Model 0b + Sex + Age + Ethnicity_collapsed + Time registration and baseline
+```{r GAD prepan Model 1b}
+gad_prepan_model1b <- lm(
+  formula = gad.diff_score_base_prepan ~
+    anxiety_disorders +
+    depressive_disorders +
+    eating_disorders +
+    obsessive_compulsive_disorders +
+    psychotic_disorders +
+    mhd.mania_hypomania_bipolar_or_manicdepression +
+    mhd.posttraumatic_stress_disorder_ptsd +
+    autism_spectrum_disorder +
+    mhd.attention_deficit_hyperactivity_disorder +
+    mhd.personality_disorder +
+    Gender_collapsed + age_category + Ethnicity_collapsed + time_diff_sign_up_coping,
+  data = dat.prepan)
+
+summary(gad_prepan_model1b)
+tidy(gad_prepan_model1b)
+```
+
+### PHQ
+Model 0a: Disorder_hierarchical, Unadjusted
+```{r PHQ prepan Model 0a}
+phq_prepan_model0a <- lm(
+  formula = phq.diff_score_base_prepan ~ 
+    Disorder_hierarchical,
+  data = dat.prepan)
+
+summary(phq_prepan_model0a)
+tidy(phq_prepan_model0a)
+```
+
+Model 0b: Overlapping disorders, Unadjusted
+```{r PHQ prepan Model 0b}
+phq_prepan_model0b <- lm(
+  formula = phq.diff_score_base_prepan ~
+    anxiety_disorders +
+    depressive_disorders +
+    eating_disorders +
+    obsessive_compulsive_disorders +
+    psychotic_disorders +
+    mhd.mania_hypomania_bipolar_or_manicdepression +
+    mhd.posttraumatic_stress_disorder_ptsd +
+    autism_spectrum_disorder +
+    mhd.attention_deficit_hyperactivity_disorder +
+    mhd.personality_disorder,
+  data = dat.prepan)
+
+summary(phq_prepan_model0b)
+tidy(phq_prepan_model0b)
+```
+
+Model 1a: Disorder hierarchical, Adjusted
+  Model 0a + Sex + Age + Ethnicity_collapsed + Time registration and baseline
+```{r PHQ prepan Model 1a}
+phq_prepan_model1a <- lm(
+  formula = phq.diff_score_base_prepan ~ 
+    Disorder_hierarchical + 
+    Gender_collapsed + 
+    age_category + 
+    Ethnicity_collapsed + 
+    time_diff_sign_up_coping,
+  data = dat.prepan)
+
+summary(phq_prepan_model1a)
+tidy(phq_prepan_model1a)
+```
+
+Model 1b: Overlapping disorders, Adjusted
+  Model 0b + Sex + Age + Ethnicity_collapsed + Time registration and baseline
+```{r PHQ prepan Model 1b}
+phq_prepan_model1b <- lm(
   formula = phq.diff_score_base_prepan ~
@@
     Gender_collapsed + age_category + Ethnicity_collapsed + time_diff_sign_up_coping,
-  data = dat)
-
-summary(model1)
-```
-
-Model 1: Model 0 + Sex + Age + Ethnicity_collapsed + Time registration and baseline
-```{r}
-model1 <- lm(
-  formula = pcl.diff_score_base_prepan ~ Disorder_hierarchical + Gender_collapsed + age_category + Ethnicity_collapsed + time_diff_sign_up_coping,
-  data = dat)
-
-summary(model1)
-```
-
-Model 1: Model 0 + Sex + Age + Ethnicity_collapsed + Time registration and baseline
-```{r}
-model1 <- lm(
-  formula = gad.diff_score_base_prepan ~ Disorder + Gender_collapsed + Age + Ethnicity_collapsed + time_diff_sign_up_coping,
-  data = dat)
-
-summary(model1)
+  data = dat.prepan)
+
+summary(phq_prepan_model1b)
+tidy(phq_prepan_model1b)
+```
+
+### PCL
+Model 0a: Disorder_hierarchical, Unadjusted
+```{r PCL prepan Model 0a}
+pcl_prepan_model0a <- lm(
+  formula = pcl.diff_score_base_prepan ~ 
+    Disorder_hierarchical,
+  data = dat.prepan)
+
+summary(pcl_prepan_model0a)
+tidy(pcl_prepan_model0a)
+```
+
+Model 0b: Overlapping disorders, Unadjusted
+```{r PCL prepan Model 0b}
+pcl_prepan_model0b <- lm(
+  formula = pcl.diff_score_base_prepan ~
+    anxiety_disorders +
+    depressive_disorders +
+    eating_disorders +
+    obsessive_compulsive_disorders +
+    psychotic_disorders +
+    mhd.mania_hypomania_bipolar_or_manicdepression +
+    mhd.posttraumatic_stress_disorder_ptsd +
+    autism_spectrum_disorder +
+    mhd.attention_deficit_hyperactivity_disorder +
+    mhd.personality_disorder,
+  data = dat.prepan)
+
+summary(pcl_prepan_model0b)
+tidy(pcl_prepan_model0b)
+```
+
+Model 1a: Disorder hierarchical, Adjusted
+  Model 0a + Sex + Age + Ethnicity_collapsed + Time registration and baseline
+```{r PCL prepan Model 1a}
+pcl_prepan_model1a <- lm(
+  formula = pcl.diff_score_base_prepan ~ 
+    Disorder_hierarchical + 
+    Gender_collapsed + 
+    age_category + 
+    Ethnicity_collapsed + 
+    time_diff_sign_up_coping,
+  data = dat.prepan)
+
+summary(pcl_prepan_model1a)
+tidy(pcl_prepan_model1a)
+```
+
+Model 1b: Overlapping disorders, Adjusted
+  Model 0b + Sex + Age + Ethnicity_collapsed + Time registration and baseline
+```{r PCL prepan Model 1b}
+pcl_prepan_model1b <- lm(
+  formula = pcl.diff_score_base_prepan ~
+    anxiety_disorders +
+    depressive_disorders +
+    eating_disorders +
+    obsessive_compulsive_disorders +
+    psychotic_disorders +
+    mhd.mania_hypomania_bipolar_or_manicdepression +
+    mhd.posttraumatic_stress_disorder_ptsd +
+    autism_spectrum_disorder +
+    mhd.attention_deficit_hyperactivity_disorder +
+    mhd.personality_disorder +
+    Gender_collapsed + age_category + Ethnicity_collapsed + time_diff_sign_up_coping,
+  data = dat.prepan)
+
+summary(pcl_prepan_model1b)
+tidy(pcl_prepan_model1b)
+```
+
+### OCIR
+Model 0a: Disorder_hierarchical, Unadjusted
+```{r OCIR prepan Model 0a}
+ocir_prepan_model0a <- lm(
+  formula = ocir.diff_score_base_prepan ~ 
+    Disorder_hierarchical,
+  data = dat.prepan)
+
+summary(ocir_prepan_model0a)
+tidy(ocir_prepan_model0a)
+```
+
+Model 0b: Overlapping disorders, Unadjusted
+```{r OCIR prepan Model 0b}
+ocir_prepan_model0b <- lm(
+  formula = ocir.diff_score_base_prepan ~
+    anxiety_disorders +
+    depressive_disorders +
+    eating_disorders +
+    obsessive_compulsive_disorders +
+    psychotic_disorders +
+    mhd.mania_hypomania_bipolar_or_manicdepression +
+    mhd.posttraumatic_stress_disorder_ptsd +
+    autism_spectrum_disorder +
+    mhd.attention_deficit_hyperactivity_disorder +
+    mhd.personality_disorder,
+  data = dat.prepan)
+
+summary(ocir_prepan_model0b)
+tidy(ocir_prepan_model0b)
+```
+
+Model 1a: Disorder hierarchical, Adjusted
+  Model 0a + Sex + Age + Ethnicity_collapsed + Time registration and baseline
+```{r OCIR prepan Model 1a}
+ocir_prepan_model1a <- lm(
+  formula = ocir.diff_score_base_prepan ~ 
+    Disorder_hierarchical + 
+    Gender_collapsed + 
+    age_category + 
+    Ethnicity_collapsed + 
+    time_diff_sign_up_coping,
+  data = dat.prepan)
+
+summary(ocir_prepan_model1a)
+tidy(ocir_prepan_model1a)
+```
+
+Model 1b: Overlapping disorders, Adjusted
+  Model 0b + Sex + Age + Ethnicity_collapsed + Time registration and baseline
+```{r OCIR prepan Model 1b}
+ocir_prepan_model1b <- lm(
+  formula = ocir.diff_score_base_prepan ~
+    anxiety_disorders +
+    depressive_disorders +
+    eating_disorders +
+    obsessive_compulsive_disorders +
+    psychotic_disorders +
+    mhd.mania_hypomania_bipolar_or_manicdepression +
+    mhd.posttraumatic_stress_disorder_ptsd +
+    autism_spectrum_disorder +
+    mhd.attention_deficit_hyperactivity_disorder +
+    mhd.personality_disorder +
+    Gender_collapsed + age_category + Ethnicity_collapsed + time_diff_sign_up_coping,
+  data = dat.prepan)
+
+summary(ocir_prepan_model1b)
+tidy(ocir_prepan_model1b)
+```
+
+## Retro-baseline change
+
+### GAD
+Model 0a: Disorder_hierarchical, Unadjusted
+```{r GAD retro Model 0a}
+gad_retro_model0a <- lm(
+  formula = gad.diff_score_base_retro ~ 
+    Disorder_hierarchical,
+  data = dat.retro)
+
+summary(gad_retro_model0a)
+tidy(gad_retro_model0a)
+```
+
+Model 0b: Overlapping disorders, Unadjusted
+```{r GAD retro Model 0b}
+gad_retro_model0b <- lm(
+  formula = gad.diff_score_base_retro ~
+    anxiety_disorders +
+    depressive_disorders +
+    eating_disorders +
+    obsessive_compulsive_disorders +
+    psychotic_disorders +
+    mhd.mania_hypomania_bipolar_or_manicdepression +
+    mhd.posttraumatic_stress_disorder_ptsd +
+    autism_spectrum_disorder +
+    mhd.attention_deficit_hyperactivity_disorder +
+    mhd.personality_disorder,
+  data = dat.retro)
+
+summary(gad_retro_model0b)
+tidy(gad_retro_model0b)
+```
+
+Model 1a: Disorder hierarchical, Adjusted
+  Model 0a + Sex + Age + Ethnicity_collapsed + Time registration and baseline
+```{r GAD retro Model 1a}
+gad_retro_model1a <- lm(
+  formula = gad.diff_score_base_retro ~ 
+    Disorder_hierarchical + 
+    Gender_collapsed + 
+    age_category + 
+    Ethnicity_collapsed + 
+    time_diff_sign_up_coping,
+  data = dat.retro)
+
+summary(gad_retro_model1a)
+tidy(gad_retro_model1a)
+```
+
+Model 1b: Overlapping disorders, Adjusted
+  Model 0b + Sex + Age + Ethnicity_collapsed + Time registration and baseline
+```{r GAD retro Model 1b}
+gad_retro_model1b <- lm(
+  formula = gad.diff_score_base_retro ~
+    anxiety_disorders +
+    depressive_disorders +
+    eating_disorders +
+    obsessive_compulsive_disorders +
+    psychotic_disorders +
+    mhd.mania_hypomania_bipolar_or_manicdepression +
+    mhd.posttraumatic_stress_disorder_ptsd +
+    autism_spectrum_disorder +
+    mhd.attention_deficit_hyperactivity_disorder +
+    mhd.personality_disorder +
+    Gender_collapsed + age_category + Ethnicity_collapsed + time_diff_sign_up_coping,
+  data = dat.retro)
+
+summary(gad_retro_model1b)
+tidy(gad_retro_model1b)
+```
+
+### PHQ
+Model 0a: Disorder_hierarchical, Unadjusted
+```{r PHQ retro Model 0a}
+phq_retro_model0a <- lm(
+  formula = phq.diff_score_base_retro ~ 
+    Disorder_hierarchical,
+  data = dat.retro)
+
+summary(phq_retro_model0a)
+tidy(phq_retro_model0a)
+```
+
+Model 0b: Overlapping disorders, Unadjusted
+```{r PHQ retro Model 0b}
+phq_retro_model0b <- lm(
+  formula = phq.diff_score_base_retro ~
+    anxiety_disorders +
+    depressive_disorders +
+    eating_disorders +
+    obsessive_compulsive_disorders +
+    psychotic_disorders +
+    mhd.mania_hypomania_bipolar_or_manicdepression +
+    mhd.posttraumatic_stress_disorder_ptsd +
+    autism_spectrum_disorder +
+    mhd.attention_deficit_hyperactivity_disorder +
+    mhd.personality_disorder,
+  data = dat.retro)
+
+summary(phq_retro_model0b)
+tidy(phq_retro_model0b)
+```
+
+Model 1a: Disorder hierarchical, Adjusted
+  Model 0a + Sex + Age + Ethnicity_collapsed + Time registration and baseline
+```{r PHQ retro Model 1a}
+phq_retro_model1a <- lm(
+  formula = phq.diff_score_base_retro ~ 
+    Disorder_hierarchical + 
+    Gender_collapsed + 
+    age_category + 
+    Ethnicity_collapsed + 
+    time_diff_sign_up_coping,
+  data = dat.retro)
+
+summary(phq_retro_model1a)
+tidy(phq_retro_model1a)
+```
+
+Model 1b: Overlapping disorders, Adjusted
+  Model 0b + Sex + Age + Ethnicity_collapsed + Time registration and baseline
+```{r PHQ retro Model 1b}
+phq_retro_model1b <- lm(
+  formula = phq.diff_score_base_retro ~
+    anxiety_disorders +
+    depressive_disorders +
+    eating_disorders +
+    obsessive_compulsive_disorders +
+    psychotic_disorders +
+    mhd.mania_hypomania_bipolar_or_manicdepression +
+    mhd.posttraumatic_stress_disorder_ptsd +
+    autism_spectrum_disorder +
+    mhd.attention_deficit_hyperactivity_disorder +
+    mhd.personality_disorder +
+    Gender_collapsed + age_category + Ethnicity_collapsed + time_diff_sign_up_coping,
+  data = dat.retro)
+
+summary(phq_retro_model1b)
+tidy(phq_retro_model1b)
+```
+
+### PCL
+Model 0a: Disorder_hierarchical, Unadjusted
+```{r PCL retro Model 0a}
+pcl_retro_model0a <- lm(
+  formula = pcl.diff_score_base_retro ~ 
+    Disorder_hierarchical,
+  data = dat.retro)
+
+summary(pcl_retro_model0a)
+tidy(pcl_retro_model0a)
+```
+
+Model 0b: Overlapping disorders, Unadjusted
+```{r PCL retro Model 0b}
+pcl_retro_model0b <- lm(
+  formula = pcl.diff_score_base_retro ~
+    anxiety_disorders +
+    depressive_disorders +
+    eating_disorders +
+    obsessive_compulsive_disorders +
+    psychotic_disorders +
+    mhd.mania_hypomania_bipolar_or_manicdepression +
+    mhd.posttraumatic_stress_disorder_ptsd +
+    autism_spectrum_disorder +
+    mhd.attention_deficit_hyperactivity_disorder +
+    mhd.personality_disorder,
+  data = dat.retro)
+
+summary(pcl_retro_model0b)
+tidy(pcl_retro_model0b)
+```
+
+Model 1a: Disorder hierarchical, Adjusted
+  Model 0a + Sex + Age + Ethnicity_collapsed + Time registration and baseline
+```{r PCL retro Model 1a}
+pcl_retro_model1a <- lm(
+  formula = pcl.diff_score_base_retro ~ 
+    Disorder_hierarchical + 
+    Gender_collapsed + 
+    age_category + 
+    Ethnicity_collapsed + 
+    time_diff_sign_up_coping,
+  data = dat.retro)
+
+summary(pcl_retro_model1a)
+tidy(pcl_retro_model1a)
+```
+
+Model 1b: Overlapping disorders, Adjusted
+  Model 0b + Sex + Age + Ethnicity_collapsed + Time registration and baseline
+```{r PCL retro Model 1b}
+pcl_retro_model1b <- lm(
+  formula = pcl.diff_score_base_retro ~
+    anxiety_disorders +
+    depressive_disorders +
+    eating_disorders +
+    obsessive_compulsive_disorders +
+    psychotic_disorders +
+    mhd.mania_hypomania_bipolar_or_manicdepression +
+    mhd.posttraumatic_stress_disorder_ptsd +
+    autism_spectrum_disorder +
+    mhd.attention_deficit_hyperactivity_disorder +
+    mhd.personality_disorder +
+    Gender_collapsed + age_category + Ethnicity_collapsed + time_diff_sign_up_coping,
+  data = dat.retro)
+
+summary(pcl_retro_model1b)
+tidy(pcl_retro_model1b)
+```
+
+### OCIR
+Model 0a: Disorder_hierarchical, Unadjusted
+```{r OCIR retro Model 0a}
+ocir_retro_model0a <- lm(
+  formula = ocir.diff_score_base_retro ~ 
+    Disorder_hierarchical,
+  data = dat.retro)
+
+summary(ocir_retro_model0a)
+tidy(ocir_retro_model0a)
+```
+
+Model 0b: Overlapping disorders, Unadjusted
+```{r OCIR retro Model 0b}
+ocir_retro_model0b <- lm(
+  formula = ocir.diff_score_base_retro ~
+    anxiety_disorders +
+    depressive_disorders +
+    eating_disorders +
+    obsessive_compulsive_disorders +
+    psychotic_disorders +
+    mhd.mania_hypomania_bipolar_or_manicdepression +
+    mhd.posttraumatic_stress_disorder_ptsd +
+    autism_spectrum_disorder +
+    mhd.attention_deficit_hyperactivity_disorder +
+    mhd.personality_disorder,
+  data = dat.retro)
+
+summary(ocir_retro_model0b)
+tidy(ocir_retro_model0b)
+```
+
+Model 1a: Disorder hierarchical, Adjusted
+  Model 0a + Sex + Age + Ethnicity_collapsed + Time registration and baseline
+```{r OCIR retro Model 1a}
+ocir_retro_model1a <- lm(
+  formula = ocir.diff_score_base_retro ~ 
+    Disorder_hierarchical + 
+    Gender_collapsed + 
+    age_category + 
+    Ethnicity_collapsed + 
+    time_diff_sign_up_coping,
+  data = dat.retro)
+
+summary(ocir_retro_model1a)
+tidy(ocir_retro_model1a)
+```
+
+Model 1b: Overlapping disorders, Adjusted
+  Model 0b + Sex + Age + Ethnicity_collapsed + Time registration and baseline
+```{r OCIR retro Model 1b}
+ocir_retro_model1b <- lm(
+  formula = ocir.diff_score_base_retro ~
+    anxiety_disorders +
+    depressive_disorders +
+    eating_disorders +
+    obsessive_compulsive_disorders +
+    psychotic_disorders +
+    mhd.mania_hypomania_bipolar_or_manicdepression +
+    mhd.posttraumatic_stress_disorder_ptsd +
+    autism_spectrum_disorder +
+    mhd.attention_deficit_hyperactivity_disorder +
+    mhd.personality_disorder +
+    Gender_collapsed + age_category + Ethnicity_collapsed + time_diff_sign_up_coping,
+  data = dat.retro)
+
+summary(ocir_retro_model1b)
+tidy(ocir_retro_model1b)
 ```

### 2020-09-03 PANCHANGE_analysis.Rmd
PCL regression chunks amended. Outcome variable currently N symptoms that participants report being impacted by the pandemic (likely will want to change this?).

@@
 ### PCL
+
+++MD: Not sure if this is how we want to run the PCL regression - the outcome variable I've included is "How many PCL items the participants report are related to the pandemic", but I think we might want a more nuanced approach than this.
+
+```{r recode PCL retro variable as numeric}
+dat.retro <- dat.retro %>% 
+  mutate(
+    pcl.sum_score_retro = 
+      as.numeric(pcl.sum_score_retro_raw)
+  )
+```
+
 Model 0a: Disorder_hierarchical, Unadjusted
@@
 pcl_retro_model0a <- lm(
-  formula = pcl.diff_score_base_retro ~ 
+  formula = pcl.sum_score_retro ~ 
     Disorder_hierarchical,
@@
 pcl_retro_model0b <- lm(
-  formula = pcl.diff_score_base_retro ~
+  formula = pcl.sum_score_retro ~
     anxiety_disorders +
@@
 pcl_retro_model1a <- lm(
-  formula = pcl.diff_score_base_retro ~ 
+  formula = pcl.sum_score_retro ~ 
     Disorder_hierarchical + 
@@
 pcl_retro_model1b <- lm(
-  formula = pcl.diff_score_base_retro ~
+  formula = pcl.sum_score_retro ~
     anxiety_disorders +

### 2020-09-03 PANCHANGE_analysis.Rmd

@@
 
-# Regression
+#ANALYSIS PLAN
+1. Calculate mean change per disorder group 
+    i. Disorders (9)
+      a. Rank the disorders by the size of the change
+    ii. Sex 
+    iii. Age (13; RAMP; potentially collapse above 65 depending on group sizes) 
+    iv. Ethnicity groups (5; White European, Black (British), Asian, Arab, Mixed)
+
+2. Regression models (Regress covariates out of the change? Which?)
+    i. Model 0: Disorders  
+    ii. Model 1: Model 0 + Sex + Age + Ethnicity + Time registration and baseline
+
+3. Re-calculate change
+
+4. Re-rank the change again
+
+5. PCL:  
+    i. Calculate the total GLAD, COPING, RAMP baseline
+    ii. For each item:
+          a. present percentages of how say that this is due to the pandemic 
+          b. Calculate a variable PCL pandemic score 
+          c. If one item is highly endorsed due to pandemic -> exclude in sensitivity analysis
+
+# 1. Calculate mean change per group
+
+# 2. Regression
 Regress covariates out of the change? Which?

### 2020-09-07 PANCHANGE_data_preprocessing2020-07-15.Rmd

@@
                                              "S" = "Chinese - Other",
-                                             "W" = NULL, ## Asking NBR what this level means
+                                             "W" = "White - not disclosed", ## Asking NBR what this level means
                                              "Z" = NULL,
@@
                                              "S" = "Asian or Asian British (including Chinese)",
-                                             "W" = NULL, ## Asking NBR what this level means
+                                             "W" = "White, white European or Caucasian", 
                                              "Z" = NULL,
@@
     Ethnicity_numeric = 
-      recode(Ethnicity_unc,
+      recode(Ethnicity,
         "European" = 1,
@@
          employment.nvq_or_hnd_or_hnc_or_equivalent, # level of education - nvq
-         employment.government_work_key_workers # key worker status
+         employment.government_work_key_workers, # key worker status
+         employment.government_work_key_workers, # key worker status
+         employment.unemployed, #key worker routing variable
+         employment.zerohours_contract, #key worker routing variable
+         employment.stayathome_parent_or_carer, #key worker routing variable
+         employment.retired, #key worker routing variable
+         employment.student_gcse_or_a_level, #key worker routing variable
+         employment.student_university, #key worker routing variable
+         employment.became_unemployed, #key worker routing variable
+         employment.furloughed_or_paid_leave_government_funded, #key worker routing variable
+         employment.furloughed_or_paid_leave_company_funded, #key worker routing variable
+         employment.paid_leave_furloughed #key worker routing variable
          ) %>%
@@
          employment.nvq_or_hnd_or_hnc_or_equivalent, # level of education - nvq
-         employment.government_work_key_workers # key worker status
+         employment.government_work_key_workers, # key worker status
+         employment.unemployed, #key worker routing variable
+         employment.zerohours_contract, #key worker routing variable
+         employment.stayathome_parent_or_carer, #key worker routing variable
+         employment.retired, #key worker routing variable
+         employment.student_gcse_or_a_level, #key worker routing variable
+         employment.student_university, #key worker routing variable
+         employment.became_unemployed, #key worker routing variable
+         employment.furloughed_or_paid_leave_government_funded, #key worker routing variable
+         employment.furloughed_or_paid_leave_company_funded, #key worker routing variable
+         employment.paid_leave_furloughed #key worker routing variable
          ) %>%
@@
          employment.what_is_your_highest_level_of_education, #highest level of edcuation
-         employment.government_work_key_workers # key worker status
+         employment.government_work_key_workers, # key worker status
+         employment.government_work_key_workers, # key worker status
+         employment.unemployed, #key worker routing variable
+         employment.zerohours_contract, #key worker routing variable
+         employment.stayathome_parent_or_carer, #key worker routing variable
+         employment.retired, #key worker routing variable
+         employment.student_gcse_or_a_level, #key worker routing variable
+         employment.student_university, #key worker routing variable
+         employment.became_unemployed, #key worker routing variable
+         employment.furloughed_or_paid_leave_government_funded, #key worker routing variable
+         employment.furloughed_or_paid_leave_company_funded, #key worker routing variable
+         employment.paid_leave_furloughed #key worker routing variable
          ) %>%
@@
         employment.government_work_key_workers_numeric == "0" ~ 0,
-        employment.government_work_key_workers_numeric > 0 ~ 1
+        employment.government_work_key_workers_numeric > 0 ~ 1,
+        employment.unemployed_numeric == "1" ~ 0,
+        employment.stayathome_parent_or_carer_numeric == "1" ~ 0,
+        employment.retired_numeric == "1" ~ 0, 
+        employment.became_unemployed_numeric == "0" ~ 0,
+        employment.student_gcse_or_a_level_numeric == "1" ~ 0,
+        employment.student_university_numeric == "1" ~ 0,
+        employment.furloughed_or_paid_leave_government_funded_numeric == "1" ~ 0,
+        employment.furloughed_or_paid_leave_company_funded_numeric == "1" ~ 0,
+        employment.paid_leave_furloughed_numeric == "1" ~ 0
       )
@@
 }
+
 ```
@@
     mhd.obsessive_compulsive_related_disorders = demographics.obsessive_compulsive_related_disorders,
-    mhd.body_dysmorphic_disorder_bdd = demographics.body_dysmorphic_disorder,
+    mhd.body_dysmorphic_disorder_bdd = demographics.body_dysmorphic_disorder_bdd,
     mhd.mania_hypomania_bipolar_or_manicdepression = demographics.mania_hypomania_bipolar_or_manicdepression,
@@
     mhd.autism_aspergers_or_autistic_spectrum_disorder = demographics.autism_spectrum_disorder_asd, # different name in EDGI
-    mhd.body_dysmorphic_disorder_bdd = demographics.body_dysmorphic_disorder,
     mhd.personality_disorder = demographics.personality_disorder, # routing variable in EDGI is named differently; renamed here to match GLAD

### 2020-09-07 PANCHANGE_analysis.Rmd
Added script to create pie charts (ungrouped) for ethnicity, gender, and education. Added a bar plot of age frequencies of whole sample. These are for Kirstin's MQ presentation 08/09/2020

@@
 #install.packages("patchwork")
+#instlal.packages("ggpubr")
 ```
@@
 library(tidyverse)
+library(ggpubr)
 ```
@@
              `3` = "African or African British",
-             `4` = "Asian or Asian British"
+             `4` = "Other"
            )
@@
 
+age bar plot for whole sample (not grouped)
+
+Create a nice summary dataset for age and display it as a bar plot
+
+```{r age_category prop total (ungrouped)}
+
+age_category_prop_total <- dat %>%
+  count(age_category) %>%
+  mutate(Prop = round(n/sum(n), 2))
+
+# add a column to help order the factor
+age_category_prop_total$order <- c(1,2,3,4,5,6,7,8,9,10,11,12,13)
+
+# total responders
+ageN <- sum(age_category_prop_total$n)
+
+kable(age_category_prop_total)
+age_category_prop_total
+
+```
+
+```{r age_category prop total (ungrouped) plot}
+#Colour palette
+RAMPagepalette <- c(
+  "#00D9AC","#21D9B3","#4DD9BC","#78D9C5","#8ED9C9","#A3D9CE",
+  "#CFD9D7",
+  "#DAD0BA","#DAC38F","#DAC38F","#DAB663" ,"#DAA937","#DA9C0C")
+
+#Bar plot
+plot.age <-
+
+  age_category_prop_total %>%
+    mutate(age_category = fct_reorder(age_category,order)) %>%
+
+  ggplot(aes(x = age_category)) +
+  geom_bar(aes(y = n, color=age_category, fill=age_category, alpha = 1),
+           stat ="summary") +
+  scale_fill_manual(values =  RAMPagepalette) +
+  scale_color_manual(values =  RAMPagepalette) +
+  labs(x = "",
+       y = "Total count",
+       title = paste("Number of participants in each age category",sep=" "),
+       subtitle = paste("n = ", ageN,
+                        sep = ""),
+       fill = "Age category") +
+   guides(alpha = FALSE, color = FALSE, fill = FALSE) +
+  scale_x_discrete(limits = (levels(age_category_prop_total$age_category))) +
+  theme_classic2() +
+   theme(axis.text.x = element_text(colour="black", size = 12,angle=45,
+                                    vjust=0.5),
+        axis.text.y = element_text(colour="black", size = 12))
+
+plot.age
+
+```
+
 # Ethnicity_collapsed
@@
 
+### pie charts
+
+```{r Ethnicity_collapsed prop per total summary}
+
+Ethnicity_collapsed_prop_Sample <- dat %>%
+  count(Ethnicity_collapsed) %>%
+  drop_na() %>%
+  mutate(freq = round(n/sum(n), 2))
+
+# total responders
+ethN <- sum(Ethnicity_collapsed_prop_Sample$n)
+
+kable(Ethnicity_collapsed_prop_Sample)
+Ethnicity_collapsed_prop_Sample
+
+```
+
+pie chart with only European label
+
+```{r ethnicity pie chart biggest group label}
+
+eth_pie_alllabel <-
+
+  Ethnicity_collapsed_prop_Sample %>%
+   mutate(Ethnicity_collapsed = fct_reorder(Ethnicity_collapsed,-n)) %>%
+
+  ggplot(aes(x="", y=freq, fill=Ethnicity_collapsed)) +
+  geom_bar(width = 1, stat = "identity") +
+  scale_fill_manual(values =  COPINGpalette6) +
+  scale_color_manual(values =  COPINGpalette6) +
+  coord_polar("y",start=0) +
+  theme_void() +
+   labs(title = paste("RAMP/COPING sample self reported ethnicity",
+                      sep=" "),
+        subtitle = paste("n =", sum(Ethnicity_collapsed_prop_Sample$n),
+                         sep = " "),
+        fill = "Self reported ethnicity")  +
+    geom_text(aes(y = c(0.5),
+                  label= c(paste0(round((freq[1]*100),0),"%"))), #Frequency of European only
+             size=5,
+             face="bold"
+             )
+
+eth_pie_alllabel
+
+```
+
+pie chart - no labels
+
+```{r ethnicity pie chart no label}
+
+eth_pie <-
+
+    Ethnicity_collapsed_prop_Sample %>%
+   mutate(Ethnicity_collapsed = fct_reorder(Ethnicity_collapsed,-n)) %>%
+
+  ggplot(aes(x="", y=freq, fill=Ethnicity_collapsed)) +
+  geom_bar(width = 1, stat = "identity") +
+  scale_fill_manual(values =  COPINGpalette6) +
+  scale_color_manual(values =  COPINGpalette6) +
+  coord_polar("y",start=0) +
+  theme_void() +
+   labs(title = paste("RAMP/COPING sample self reported ethnicity",
+                      sep=" "),
+        subtitle = paste("n =", sum(Ethnicity_collapsed_prop_Sample$n),
+                         sep = " "),
+        fill = "Self reported ethnicity")
+
+eth_pie
+
+```
+
 # Gender_collapsed
@@
 
+```{r summary gender}
+
+summarytools::freq(data_dem[(grep("gender",names(data_dem)))],
+                   style = "rmarkdown")
+
+```
+
+### pie charts
+
+```{r Gender_collapsed prop per total}
+
+Gender_collapsed_prop_total <- dat %>%
+  count(Gender_collapsed) %>%
+  mutate(freq = round(n/sum(n), 2))
+
+kable(Gender_collapsed_prop_total)
+Gender_collapsed_prop_total
+
+```
+
+```{r gender pie chart - all labels}
+
+gen_pie_alllabel <- 
+  ggplot(Gender_collapsed_prop_total, aes(x="", y=freq, fill=Gender_collapsed)) +
+  geom_bar(width = 1, stat = "identity") +
+  scale_fill_manual(values =  COPINGpalette5) +
+  scale_color_manual(values =  COPINGpalette5) +
+  coord_polar("y",start=0) +
+  theme_void() +
+   labs(title = paste("RAMP/COPING sample self reported gender",
+                      sep=" "),
+        subtitle = paste("n", sum(Gender_collapsed_prop_total$n),
+                         sep = " "),
+        fill = "Self reported gender")  +
+    geom_text(aes(y = c(0.85,0.35,0),
+                  x = c(1.2,1.2,1.8),
+                  label= c(paste0(round((freq[1:2]*100),0),"%"),paste0(round((freq[3]*100),1),"%"))),
+             size=5,
+             face="bold"
+             )
+
+gen_pie_alllabel
+
+```
+
+pie chart - only labelling two largest groups (male and female)
+
+```{r gender pie chart - male/female labels only}
+
+gen_pie <- 
+  ggplot(Gender_collapsed_prop_total, aes(x="", y=freq, fill=Gender_collapsed)) +
+  geom_bar(width = 1, stat = "identity") +
+  scale_fill_manual(values =  COPINGpalette5) +
+  scale_color_manual(values =  COPINGpalette5) +
+  coord_polar("y",start=0) +
+  theme_void() +
+   labs(title = paste("RAMP/COPING sample self reported gender",
+                      sep=" "),
+        subtitle = paste("n", sum(Gender_collapsed_prop_total$n),
+                         sep = " "),
+        fill = "Self reported gender")  +
+    geom_text(aes(y = c(0.85,0.35,0),
+                  x = c(1.2,1.2,1.8),
+                  label= c(paste0(round((freq[1:2]*100),0),"%"),"")),
+             size=5,
+             face="bold"
+             )
+
+gen_pie
+
+```
+
+pie chart -  no labels
+
+```{r gender pie chart - no labels }
+
+gen_pie_nolabel <- 
+  ggplot(Gender_collapsed_prop_total, aes(x="", y=freq, fill=Gender_collapsed)) +
+  geom_bar(width = 1, stat = "identity") +
+  scale_fill_manual(values =  COPINGpalette5) +
+  scale_color_manual(values =  COPINGpalette5) +
+  coord_polar("y",start=0) +
+  theme_void() +
+   labs(title = paste("RAMP/COPING sample self reported gender",
+                      sep=" "),
+        subtitle = paste("n", sum(Gender_collapsed_prop_total$n),
+                         sep = " "),
+        fill = "Self reported gender")
+
+gen_pie_nolabel
+
+```
+
 # highest_education
@@
 highest_education_by_Sample_prop_plot
+```
+
+### pie chart
+
+summary dataset with frequencies
+
+```{r highest education prop per total}
+
+highest_education_prop_total <- dat %>%
+  count(highest_education) %>%
+  mutate(freq = round(n/sum(n), 2)) %>% 
+  drop_na()
+
+kable(highest_education_prop_total)
+highest_education_prop_total
+
+# total responders
+eduN <- sum(highest_education_prop_total$n)
+
+edubindat <- dat %>%
+  mutate(demographics.education_binary =
+           case_when(
+             highest_education_numeric == "4" ~ "Bachelors or higher",
+             highest_education_numeric == "3" ~ "A-levels or lower"
+           )) %>%
+  summarise(n = n()) %>%
+  drop_na() %>%
+  mutate(freq = n / sum(n))
+
+educatdat <- dat %>%
+  mutate(demographics.education_three = 
+           case_when(
+             highest_education_numeric == "4" ~ "Bachelors or higher",
+             highest_education_numeric == "3" ~ "A-levels",
+             highest_education_numeric == "1" ~ "GCSEs or lower"
+           )) %>%
+  summarise(n = n()) %>%
+  drop_na() %>%
+  mutate(freq = n / sum(n))
+
+```
+
+pie chart labels
+
+```{r education pie chart all labels}
+
+edu_pie_alllabel <-
+
+    highest_education_prop_total %>%
+    mutate(demographics.highest_level_of_education = fct_reorder(highest_education,-n)) %>%
+
+  ggplot(aes(x="", y=freq, fill=demographics.highest_level_of_education)) +
+  geom_bar(width = 1, stat = "identity") +
+  scale_fill_manual(values =  COPINGpalette7) +
+  scale_color_manual(values =  COPINGpalette7) +
+  coord_polar("y",start=0) +
+  theme_void() +
+   labs(title = paste("RAMP/COPING sample self reported level of education",
+                      sep=" "),
+        subtitle = paste("n", sum(highest_education_prop_total$n),
+                         sep = " "),
+        fill = "Self reported level of education")  +
+    geom_text(aes(y = c(0.13,0.04,0.3,0.65),
+                  x = c(1.2,1.2,1.2,1.2), #GCSE, NVQ, A-levels, university
+                  label= paste0(round((freq*100),0),"%")),
+             size=5,
+             face="bold"
+             )
+
+edu_pie_alllabel
+
+#y = c(0.57,0.85,0.25,0.38,0.015,0.05,0.14),
+#x = c(1.2,1.2,1.2,1.2,1.35,1.2,1.2)
+
+```
+
+```{r binary education pie chart all labels}
+
+edu_pie_binlabel <-
+
+    edubindat %>%
+    mutate(demographics.education_binary = fct_reorder(demographics.education_binary,-n)) %>%
+
+  ggplot(aes(x="", y=freq, fill=demographics.education_binary)) +
+  geom_bar(width = 1, stat = "identity") +
+  scale_fill_manual(values =  COPINGpalette7) +
+  scale_color_manual(values =  COPINGpalette7) +
+  coord_polar("y",start=0) +
+  theme_void() +
+   labs(title = paste("RAMP sample self reported highest level of education, above or below bachelor degree or equivalent",
+                      sep=" "),
+        subtitle = paste("n", sum(edubindat$n),
+                         sep = " "),
+        fill = "Self reported level of education")  +
+    geom_text(aes(y = c(0.25,0.75),
+                  label= paste0(round((freq*100),0),"%")),
+             size=5,
+             face="bold"
+             )
+
+edu_pie_binlabel
+
+```
+
+```{r 3 category education pie chart all labels}
+
+edu_pie_catlabel <-
+
+    educatdat %>%
+    mutate(demographics.education_three = fct_reorder(demographics.education_three,-n)) %>%
+
+  ggplot(aes(x="", y=freq, fill=demographics.education_three)) +
+  geom_bar(width = 1, stat = "identity") +
+  scale_fill_manual(values =  COPINGpalette7) +
+  scale_color_manual(values =  COPINGpalette7) +
+  coord_polar("y",start=0) +
+  theme_void() +
+   labs(title = paste("RAMP sample self reported highest level of education, above or below bachelor degree or equivalent",
+                      sep=" "),
+        subtitle = paste("n", sum(educatdat$n),
+                         sep = " "),
+        fill = "Self reported level of education")  +
+    geom_text(aes(y = c(0.25,0.75,0.02),
+                  label= c(paste0(round((freq[1:2]*100),0),"%"),"") ),
+             size=5,
+             face="bold"
+             )
+
+edu_pie_catlabel
+
+```
+
+```{r education pie chart - largest groups labelled }
+
+edu_pie_somelabel <-
+
+    edudat %>%
+    mutate(demographics.highest_level_of_education = fct_reorder(demographics.highest_level_of_education,-n)) %>%
+
+  ggplot(aes(x="", y=freq, fill=demographics.highest_level_of_education)) +
+  geom_bar(width = 1, stat = "identity") +
+  scale_fill_manual(values =  COPINGpalette7) +
+  scale_color_manual(values =  COPINGpalette7) +
+  coord_polar("y",start=0) +
+  theme_void() +
+   labs(title = paste("RAMP sample self reported level of education",
+                      sep=" "),
+        subtitle = paste("n", sum(edudat$n),
+                         sep = " "),
+        fill = "Self reported level of education")  +
+    geom_text(aes(y = c(0.57,0.85,0.25,0.38,0.015,0.05,0.14),
+                  x = c(1.2,1.2,1.2,1.2,1.35,1.2,1.2),
+                  label=c( paste0(round((freq[1:4]*100),0),"%"),"",
+                  paste0(round((freq[6:7]*100),0),"%"))),
+             size=5,
+             face="bold"
+             )
+edu_pie_somelabel
+
+```
+
+pie chart -  no labels
+
+```{r education pie chart no labels }
+
+edu_pie_nolabel <- 
+   edudat %>%
+    mutate(demographics.highest_level_of_education = fct_reorder(demographics.highest_level_of_education,-n)) %>%
+
+  ggplot(aes(x="", y=freq, fill=demographics.highest_level_of_education)) +
+  geom_bar(width = 1, stat = "identity") +
+  scale_fill_manual(values =  COPINGpalette7) +
+  scale_color_manual(values =  COPINGpalette7) +
+  coord_polar("y",start=0) +
+  theme_void() +
+   labs(title = paste("RAMP sample self reported level of education",
+                      sep=" "),
+        subtitle = paste("n", sum(edudat$n),
+                         sep = " "),
+        fill = "Self reported level of education")
+
+edu_pie_nolabel
+
 ```
@@
          tl.col = "black",
-         col=colorRampPalette(c("dodgerblue4","white","firebrick4"))(200), # colours for correlations
+         col=colorCOPINGpalette(c("dodgerblue4","white","firebrick4"))(200), # colours for correlations
          # Combine with significance

### 2020-09-07 PANCHANGE_analysis.Rmd
Rough counts added for frequencies to be included in presentation.

@@
   freq(disorders_total_count)
+```
+
+```{r psychiatric disorders frequencies}
+#Ppts with least one psychiatric disorder
+dat %>%
+  count(disorders_total_count >= 1)
+
+#Ppts with anxiety OR depressive disorder
+dat %>% 
+  count(anxiety_disorders_numeric == 1 | depressive_disorders == 1)
+
+#Ppts with anxiety & depression
+dat %>% 
+  count(depression_and_anxiety_numeric == 1)
 ```

### 2020-09-07 PANCHANGE_analysis.Rmd
Minor error in new chunks fixed. Confirmed that the script runs without error.

@@
 
-```{r summary gender}
-
-summarytools::freq(data_dem[(grep("gender",names(data_dem)))],
-                   style = "rmarkdown")
-
-```
-
 ### pie charts
@@
              highest_education_numeric == "4" ~ "Bachelors or higher",
-             highest_education_numeric == "3" ~ "A-levels or lower"
+             highest_education_numeric == "3" ~ "A-levels or lower",
+             highest_education_numeric == "2" ~ "A-levels or lower",
+             highest_education_numeric == "1" ~ "A-levels or lower"
            )) %>%
-  summarise(n = n()) %>%
-  drop_na() %>%
-  mutate(freq = n / sum(n))
+  count(demographics.education_binary) %>%
+  mutate(freq = round(n/sum(n), 2)) %>% 
+  drop_na()
 
@@
            )) %>%
-  summarise(n = n()) %>%
-  drop_na() %>%
-  mutate(freq = n / sum(n))
+  count(demographics.education_three) %>%
+  mutate(freq = round(n/sum(n), 2)) %>% 
+  drop_na()
 
@@
 
-#y = c(0.57,0.85,0.25,0.38,0.015,0.05,0.14),
-#x = c(1.2,1.2,1.2,1.2,1.35,1.2,1.2)
-
 ```
@@
   theme_void() +
-   labs(title = paste("RAMP sample self reported highest level of education, above or below bachelor degree or equivalent",
+   labs(title = paste("RAMP/COPING sample self reported highest level of education, above or below bachelor degree or equivalent",
                       sep=" "),
@@
         fill = "Self reported level of education")  +
-    geom_text(aes(y = c(0.25,0.75,0.02),
-                  label= c(paste0(round((freq[1:2]*100),0),"%"),"") ),
+    geom_text(aes(y = c(0.23,0.65,0.05),
+                  label= c(paste0(round((freq[1:3]*100),0),"%")),
              size=5,
              face="bold"
-             )
+             ))
 
@@
 
-```{r education pie chart - largest groups labelled }
-
-edu_pie_somelabel <-
-
-    edudat %>%
-    mutate(demographics.highest_level_of_education = fct_reorder(demographics.highest_level_of_education,-n)) %>%
+pie chart -  no labels
+
+```{r education pie chart no labels }
+
+edu_pie_nolabel <-
+
+  edu_pie_alllabel <-
+
+    highest_education_prop_total %>%
+    mutate(demographics.highest_level_of_education = fct_reorder(highest_education,-n)) %>%
 
@@
   theme_void() +
-   labs(title = paste("RAMP sample self reported level of education",
+   labs(title = paste("RAMP/COPING sample self reported level of education",
                       sep=" "),
-        subtitle = paste("n", sum(edudat$n),
-                         sep = " "),
-        fill = "Self reported level of education")  +
-    geom_text(aes(y = c(0.57,0.85,0.25,0.38,0.015,0.05,0.14),
-                  x = c(1.2,1.2,1.2,1.2,1.35,1.2,1.2),
-                  label=c( paste0(round((freq[1:4]*100),0),"%"),"",
-                  paste0(round((freq[6:7]*100),0),"%"))),
-             size=5,
-             face="bold"
-             )
-edu_pie_somelabel
-
-```
-
-pie chart -  no labels
-
-```{r education pie chart no labels }
-
-edu_pie_nolabel <- 
-   edudat %>%
-    mutate(demographics.highest_level_of_education = fct_reorder(demographics.highest_level_of_education,-n)) %>%
-
-  ggplot(aes(x="", y=freq, fill=demographics.highest_level_of_education)) +
-  geom_bar(width = 1, stat = "identity") +
-  scale_fill_manual(values =  COPINGpalette7) +
-  scale_color_manual(values =  COPINGpalette7) +
-  coord_polar("y",start=0) +
-  theme_void() +
-   labs(title = paste("RAMP sample self reported level of education",
-                      sep=" "),
-        subtitle = paste("n", sum(edudat$n),
+        subtitle = paste("n", sum(highest_education_prop_total$n),
                          sep = " "),
         fill = "Self reported level of education")
-
-edu_pie_nolabel
 
@@
 
-```{r smart numeric summary tables}
+```{r gad sum score smart numeric summary tables}
 # reshape the table
@@
 Table for knitting
-gad diff summary table
-```{r gad diff summary table}
+gad sum score summary table
+```{r gad sum score summary table}
 kable(gad.sum_score_numeric_summary_table_reshaped)
@@
 
-```{r smart numeric summary tables}
+```{r gad diff score smart numeric summary tables}
 # reshape the table
@@
 
-```{r gad percentage plot retro_prepan, fig.height=6, fig.width=10}
+```{r gad percentage plot retro_prepan resized, fig.height=6, fig.width=10}
 dat.long.gad.diff %>%
@@
 
-```{r gad percentage plot retro_prepan sum, fig.height=6, fig.width=10}
+```{r gad percentage plot retro_prepan sum resized, fig.height=6, fig.width=10}
 dat.long.gad.sum %>%
@@
 
-```{r smart numeric summary tables}
+```{r phq sum score smart numeric summary tables}
 # reshape the table
@@
 Table for knitting
-phq diff summary table
-```{r phq diff summary table}
+phq sum score summary table
+```{r phq sum score summary table}
 kable(phq.sum_score_numeric_summary_table_reshaped)
@@
 
-```{r smart numeric summary tables}
+```{r phq diff score smart numeric summary tables}
 # reshape the table
@@
 
-```{r phq percentage plot retro_prepan, fig.height=6, fig.width=10}
+```{r phq percentage plot retro_prepan resized, fig.height=6, fig.width=10}
 dat.long.phq.diff %>%
@@
 
-```{r phq percentage plot retro_prepan sum, fig.height=6, fig.width=10}
+```{r phq percentage plot retro_prepan sum resized, fig.height=6, fig.width=10}
 dat.long.phq.sum %>%
@@
 
-```{r smart numeric summary tables}
+```{r ocir sum score smart numeric summary tables}
 # reshape the table
@@
 Table for knitting
-ocir diff summary table
-```{r ocir diff summary table}
+ocir sum score summary table
+```{r ocir sum score summary table}
 kable(ocir.sum_score_numeric_summary_table_reshaped)
@@
 
-```{r smart numeric summary tables}
+```{r ocir diff score smart numeric summary tables}
 # reshape the table
@@
 
-```{r ocir percentage plot retro_prepan, fig.height=6, fig.width=10}
+```{r ocir percentage plot retro_prepan resized, fig.height=6, fig.width=10}
 dat.long.ocir.diff %>%
@@
 
-```{r ocir percentage plot retro_prepan sum, fig.height=6, fig.width=10}
+```{r ocir percentage plot retro_prepan sum resized, fig.height=6, fig.width=10}
 dat.long.ocir.sum %>%
@@
 
-```{r smart numeric summary tables}
+```{r pcl sum score smart numeric summary tables}
 # reshape the table
@@
 Table for knitting
-pcl diff summary table
-```{r pcl diff summary table}
+pcl sum score summary table
+```{r pcl sum score summary table}
 kable(pcl.numeric_summary_table_reshaped)
@@
 
-```{r smart numeric summary tables}
+```{r pcl diff score smart numeric summary tables}
 # reshape the table
@@
 
-```{r pcl percentage plot retro_prepan sum, fig.height=6, fig.width=10}
+```{r pcl percentage plot retro_prepan sum resized, fig.height=6, fig.width=10}
 dat.long.pcl.sum %>%
@@
          tl.col = "black",
-         col=colorCOPINGpalette(c("dodgerblue4","white","firebrick4"))(200), # colours for correlations
+         col=colorRampPalette(c("dodgerblue4","white","firebrick4"))(200), # colours for correlations
          # Combine with significance
@@
 
-```{r RUBBISH 2 fig.height=7, fig.width=5}
+```{r RUBBISH 2, fig.height=7, fig.width=5}
 gad.diff_score_base_prepan_plot /

### 2020-09-08 PANCHANGE_analysis.Rmd
Added import/renaming blocks for all the neuro blocks in the baseline questionnaires. GLAD/EDGI are confirmed to work. Awaiting NBR data.

@@
     depressive_disorders +
+    depression_and_anxiety +
     eating_disorders +

### 2020-09-09 PANCHANGE_data_preprocessing2020-07-15.Rmd

@@
 
+# Neurological symptoms
+
+## ALS (alsfrs)
+
+### GLAD
+Read in data
+```{r glad als cols}
+if(GLAD == TRUE){
+glad.als.raw <- readRDS(file = paste0(data.raw_path, "/glad/alsfrs_coping_glad.rds"))
+dim(glad.als.raw)
+colnames(glad.als.raw)
+}
+```
+
+Select variables
+```{r glad als cleaning}
+if(GLAD == TRUE){
+
+glad.als.raw.id <- glad.als.raw %>%
+  drop_na(externalDataReference) %>% # Drop NAs
+  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
+  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
+  mutate(ID = as.numeric(ID)) %>%
+  select(
+         Sample, # Sample
+         ID, # ID
+         alsfrs.limb_weakness_noticed_past,
+         alsfrs.normal,
+         alsfrs.slow_or_sloppy_all_words_are_legible,
+         alsfrs.not_all_words_are_legible,
+         alsfrs.able_to_grip_pen,
+         alsfrs.unable_to_grip_pen,
+         alsfrs.have_you_noticed_any_difficulty_walking,
+         alsfrs.do_you_have_any_difficulty_climbing_stairs
+         ) %>%
+  add_numeric(., exclude = exclude_cols) %>%
+  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
+  mutate_if(is.numeric, ~na_if(., -99)) %>%
+  mutate_if(is.numeric, ~na_if(., -77)) %>%
+  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
+  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
+
+# Inspect dimensions
+dim(glad.als.raw.id)
+# Inspect colnames
+colnames(glad.als.raw.id)
+#Differences
+dim(glad.als.raw)[1]-dim(glad.als.raw.id)[1]
+}
+```
+
+```{r glad copy als}
+if(GLAD == TRUE){
+als.raw.id <- glad.als.raw.id
+}
+```
+
+### EDGI
+Read in data
+```{r edgi als cols}
+if(EDGI == TRUE){
+edgi.als.raw <- readRDS(file = paste0(data.raw_path, "/edgi/alsfrs_coping_edgi.rds"))
+dim(edgi.als.raw)
+colnames(edgi.als.raw)
+}
+```
+
+Select variables
+```{r edgi als cleaning}
+if(EDGI == TRUE){
+
+edgi.als.raw.id <- edgi.als.raw %>%
+  drop_na(externalDataReference) %>% # Drop NAs
+  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
+  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
+  mutate(ID = as.numeric(ID)) %>%
+  select(
+         Sample, # Sample
+         ID, # ID
+         alsfrs.limb_weakness_noticed_past,
+         alsfrs.normal,
+         alsfrs.slow_or_sloppy_all_words_are_legible,
+         alsfrs.not_all_words_are_legible,
+         alsfrs.able_to_grip_pen,
+         alsfrs.unable_to_grip_pen,
+         alsfrs.have_you_noticed_any_difficulty_walking,
+         alsfrs.do_you_have_any_difficulty_climbing_stairs
+         ) %>%
+  add_numeric(., exclude = exclude_cols) %>%
+  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
+  mutate_if(is.numeric, ~na_if(., -99)) %>%
+  mutate_if(is.numeric, ~na_if(., -77)) %>%
+  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
+  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
+
+# Inspect dimensions
+dim(edgi.als.raw.id)
+# Inspect colnames
+colnames(edgi.als.raw.id)
+#Differences
+dim(edgi.als.raw)[1]-dim(edgi.als.raw.id)[1]
+}
+```
+
+```{r edgi copy als}
+if(EDGI == TRUE){
+als.raw.id <- edgi.als.raw.id
+}
+```
+
+### NBR
+Read in data
+```{r nbr als cols}
+if(NBR == TRUE){
+nbr.als.raw <- readRDS(file = paste0(data.raw_path, "/nbr/alsfrs_coping_nbr.rds"))
+dim(nbr.als.raw)
+colnames(nbr.als.raw)
+}
+```
+
+Select variables
+```{r nbr als cleaning}
+if(NBR == TRUE){
+
+nbr.als.raw.id <- nbr.als.raw %>%
+  drop_na(subjectid) %>% # Drop NAs
+  distinct(subjectid, .keep_all = TRUE) %>% # Remove duplicates based on ID
+  separate(subjectid, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
+  mutate(ID = as.numeric(ID)) %>%
+  select(
+         Sample, # Sample
+         ID, # ID
+         alsfrs.limb_weakness_noticed_past,
+         alsfrs.normal,
+         alsfrs.slow_or_sloppy_all_words_are_legible,
+         alsfrs.not_all_words_are_legible,
+         alsfrs.able_to_grip_pen,
+         alsfrs.unable_to_grip_pen,
+         alsfrs.have_you_noticed_any_difficulty_walking,
+         alsfrs.do_you_have_any_difficulty_climbing_stairs
+         ) %>%
+  add_numeric(., exclude = exclude_cols) %>%
+  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
+  mutate_if(is.numeric, ~na_if(., -99)) %>%
+  mutate_if(is.numeric, ~na_if(., -77)) %>%
+  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
+  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
+
+# Inspect dimensions
+dim(nbr.als.raw.id)
+# Inspect colnames
+colnames(nbr.als.raw.id)
+#Differences
+dim(nbr.als.raw)[1]-dim(nbr.als.raw.id)[1]
+}
+```
+
+```{r nbr copy als}
+if(NBR == TRUE){
+als.raw.id <- nbr.als.raw.id
+}
+```
+
+### RAMP
+Read in data
+```{r ramp als cols}
+if(RAMP == TRUE){
+ramp.als.raw <- readRDS(file = paste0(data.raw_path, "/ramp/alsfrs_ramp.rds"))
+dim(ramp.als.raw)
+colnames(ramp.als.raw)
+}
+```
+
+Select variables
+```{r ramp als cleaning}
+if(RAMP == TRUE){
+
+ramp.als.raw.id <- ramp.als.raw %>%
+  drop_na(`Login ID`) %>% # Drop NAs
+  distinct(`Login ID`, .keep_all = TRUE) %>% # Remove duplicates based on ID
+  separate(`Login ID`, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
+  mutate(ID = as.numeric(ID)) %>%
+  select(
+         Sample, # Sample
+         ID, # ID
+         alsfrs.limb_weakness_noticed_past,
+         alsfrs.normal,
+         alsfrs.slow_or_sloppy_all_words_are_legible,
+         alsfrs.not_all_words_are_legible,
+         alsfrs.able_to_grip_pen,
+         alsfrs.unable_to_grip_pen,
+         alsfrs.have_you_noticed_any_difficulty_walking,
+         alsfrs.do_you_have_any_difficulty_climbing_stairs
+         ) %>%
+  add_numeric(., exclude = exclude_cols) %>%
+  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
+  mutate_if(is.numeric, ~na_if(., -99)) %>%
+  mutate_if(is.numeric, ~na_if(., -77)) %>%
+  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
+  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
+
+# Inspect dimensions
+dim(ramp.als.raw.id)
+# Inspect colnames
+colnames(ramp.als.raw.id)
+#Differences
+dim(ramp.als.raw)[1]-dim(ramp.als.raw.id)[1]
+}
+```
+
+```{r ramp copy als}
+if(RAMP == TRUE){
+als.raw.id <- ramp.als.raw.id
+}
+```
+
+## Epsworth sleep scale (ess)
+
+### GLAD
+Read in data
+```{r glad ess cols}
+if(GLAD == TRUE){
+glad.ess.raw <- readRDS(file = paste0(data.raw_path, "/glad/ess_coping_glad.rds"))
+dim(glad.ess.raw)
+colnames(glad.ess.raw)
+}
+```
+
+Select variables
+```{r glad ess cleaning}
+if(GLAD == TRUE){
+
+glad.ess.raw.id <- glad.ess.raw %>%
+  drop_na(externalDataReference) %>% # Drop NAs
+  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
+  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
+  mutate(ID = as.numeric(ID)) %>%
+  select(
+         Sample, # Sample
+         ID, # ID
+         ess.felt_excessively_sleepy_past= ess.day_past_month_felt,
+         ess.sitting_and_reading,
+         ess.watching_tv,
+         ess.sitting_inactive_in_a_public_place,
+         ess.break_passenger_hour_car,
+         ess.afternoon_rest_circumstances_lying,
+         ess.sitting_and_talking_to_someone,
+         ess.sitting_quietly_after_a_lunch_without_alcohol,
+         ess.car_minutes_stopped_traffic,
+         ess.insomnia,
+         ess.narcolepsy,
+         ess.rem_sleep_behaviour_disorder,
+         ess.restless_legs_syndrome,
+         ess.sleep_apnea,
+         ess.sleep_terrors,
+         ess.sleepwalking,
+         ess.other,
+         ess.none   
+         ) %>%
+  add_numeric(., exclude = exclude_cols) %>%
+  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
+  mutate_if(is.numeric, ~na_if(., -99)) %>%
+  mutate_if(is.numeric, ~na_if(., -77)) %>%
+  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
+  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
+
+# Inspect dimensions
+dim(glad.ess.raw.id)
+# Inspect colnames
+colnames(glad.ess.raw.id)
+#Differences
+dim(glad.ess.raw)[1]-dim(glad.ess.raw.id)[1]
+}
+```
+
+```{r glad copy ess}
+if(GLAD == TRUE){
+ess.raw.id <- glad.ess.raw.id
+}
+```
+
+### EDGI
+Read in data
+```{r edgi ess cols}
+if(EDGI == TRUE){
+edgi.ess.raw <- readRDS(file = paste0(data.raw_path, "/edgi/ess_coping_edgi.rds"))
+dim(edgi.ess.raw)
+colnames(edgi.ess.raw)
+}
+```
+
+Select variables
+```{r edgi ess cleaning}
+if(EDGI == TRUE){
+
+edgi.ess.raw.id <- edgi.ess.raw %>%
+  drop_na(externalDataReference) %>% # Drop NAs
+  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
+  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
+  mutate(ID = as.numeric(ID)) %>%
+  select(
+         Sample, # Sample
+         ID, # ID
+         ess.felt_excessively_sleepy_past,
+         ess.sitting_and_reading,
+         ess.watching_tv,
+         ess.sitting_inactive_in_a_public_place,
+         ess.break_passenger_hour_car,
+         ess.afternoon_rest_circumstances_lying,
+         ess.sitting_and_talking_to_someone,
+         ess.sitting_quietly_after_a_lunch_without_alcohol,
+         ess.car_minutes_stopped_traffic,
+         ess.insomnia,
+         ess.narcolepsy,
+         ess.rem_sleep_behaviour_disorder,
+         ess.restless_legs_syndrome,
+         ess.sleep_apnea,
+         ess.sleep_terrors,
+         ess.sleepwalking,
+         ess.other,
+         ess.none  
+         ) %>%
+  add_numeric(., exclude = exclude_cols) %>%
+  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
+  mutate_if(is.numeric, ~na_if(., -99)) %>%
+  mutate_if(is.numeric, ~na_if(., -77)) %>%
+  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
+  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
+
+# Inspect dimensions
+dim(edgi.ess.raw.id)
+# Inspect colnames
+colnames(edgi.ess.raw.id)
+#Differences
+dim(edgi.ess.raw)[1]-dim(edgi.ess.raw.id)[1]
+}
+```
+
+```{r edgi copy ess}
+if(EDGI == TRUE){
+ess.raw.id <- edgi.ess.raw.id
+}
+```
+
+### NBR
+Read in data
+```{r nbr ess cols}
+if(NBR == TRUE){
+nbr.ess.raw <- readRDS(file = paste0(data.raw_path, "/nbr/ess_coping_nbr.rds"))
+dim(nbr.ess.raw)
+colnames(nbr.ess.raw)
+}
+```
+
+Select variables
+```{r nbr ess cleaning}
+if(NBR == TRUE){
+
+nbr.ess.raw.id <- nbr.ess.raw %>%
+  drop_na(subjectid) %>% # Drop NAs
+  distinct(subjectid, .keep_all = TRUE) %>% # Remove duplicates based on ID
+  separate(subjectid, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
+  mutate(ID = as.numeric(ID)) %>%
+  select(
+         Sample, # Sample
+         ID, # ID
+         ess.felt_excessively_sleepy_past,
+         ess.sitting_and_reading,
+         ess.watching_tv,
+         ess.sitting_inactive_in_a_public_place,
+         ess.break_passenger_hour_car,
+         ess.afternoon_rest_circumstances_lying,
+         ess.sitting_and_talking_to_someone,
+         ess.sitting_quietly_after_a_lunch_without_alcohol,
+         ess.car_minutes_stopped_traffic,
+         ess.insomnia,
+         ess.narcolepsy,
+         ess.rem_sleep_behaviour_disorder,
+         ess.restless_legs_syndrome,
+         ess.sleep_apnea,
+         ess.sleep_terrors,
+         ess.sleepwalking,
+         ess.other,
+         ess.none  
+         ) %>%
+  add_numeric(., exclude = exclude_cols) %>%
+  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
+  mutate_if(is.numeric, ~na_if(., -99)) %>%
+  mutate_if(is.numeric, ~na_if(., -77)) %>%
+  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
+  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
+
+# Inspect dimensions
+dim(nbr.ess.raw.id)
+# Inspect colnames
+colnames(nbr.ess.raw.id)
+#Differences
+dim(nbr.ess.raw)[1]-dim(nbr.ess.raw.id)[1]
+}
+```
+
+```{r nbr copy ess}
+if(NBR == TRUE){
+ess.raw.id <- nbr.ess.raw.id
+}
+```
+
+### RAMP
+Read in data
+```{r ramp ess cols}
+if(RAMP == TRUE){
+ramp.ess.raw <- readRDS(file = paste0(data.raw_path, "/ramp/ess_ramp.rds"))
+dim(ramp.ess.raw)
+colnames(ramp.ess.raw)
+}
+```
+
+Select variables
+```{r ramp ess cleaning}
+if(RAMP == TRUE){
+
+ramp.ess.raw.id <- ramp.ess.raw %>%
+  drop_na(`Login ID`) %>% # Drop NAs
+  distinct(`Login ID`, .keep_all = TRUE) %>% # Remove duplicates based on ID
+  separate(`Login ID`, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
+  mutate(ID = as.numeric(ID)) %>%
+  select(
+         Sample, # Sample
+         ID, # ID
+         ess.felt_excessively_sleepy_past,
+         ess.sitting_and_reading,
+         ess.watching_tv,
+         ess.sitting_inactive_in_a_public_place,
+         ess.break_passenger_hour_car,
+         ess.afternoon_rest_circumstances_lying,
+         ess.sitting_and_talking_to_someone,
+         ess.sitting_quietly_after_a_lunch_without_alcohol,
+         ess.car_minutes_stopped_traffic,
+         ess.insomnia,
+         ess.narcolepsy,
+         ess.rem_sleep_behaviour_disorder,
+         ess.restless_legs_syndrome,
+         ess.sleep_apnea,
+         ess.sleep_terrors,
+         ess.sleepwalking,
+         ess.other,
+         ess.none  
+         ) %>%
+  add_numeric(., exclude = exclude_cols) %>%
+  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
+  mutate_if(is.numeric, ~na_if(., -99)) %>%
+  mutate_if(is.numeric, ~na_if(., -77)) %>%
+  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
+  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
+
+# Inspect dimensions
+dim(ramp.ess.raw.id)
+# Inspect colnames
+colnames(ramp.ess.raw.id)
+#Differences
+dim(ramp.ess.raw)[1]-dim(ramp.ess.raw.id)[1]
+}
+```
+
+```{r ramp copy ess}
+if(RAMP == TRUE){
+ess.raw.id <- ramp.ess.raw.id
+}
+```
+
+## Migraines (midas)
+
+### GLAD
+Read in data
+```{r glad midas cols}
+if(GLAD == TRUE){
+glad.midas.raw <- readRDS(file = paste0(data.raw_path, "/glad/midas_coping_glad.rds"))
+dim(glad.midas.raw)
+colnames(glad.midas.raw)
+}
+```
+
+Select variables
+```{r glad midas cleaning}
+if(GLAD == TRUE){
+
+glad.midas.raw.id <- glad.midas.raw %>%
+  drop_na(externalDataReference) %>% # Drop NAs
+  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
+  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
+  mutate(ID = as.numeric(ID)) %>%
+  select(
+         Sample, # Sample
+         ID, # ID
+         midas.headaches_suffered_past_month,
+         midas.days_past_month_miss_work_school = midas.days_past_month,
+         midas.days_past_month_work_school_half_productivity = midas.days_past_month.1,
+         midas.days_past_month_miss_housework = midas.days_past_month.2,
+         midas.days_past_month_housework_half_productivity = midas.days_past_month.3,
+         midas.days_past_month_miss_social_activities = midas.days_past_month.4
+         ) %>%
+  add_numeric(., exclude = exclude_cols) %>%
+  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
+  mutate_if(is.numeric, ~na_if(., -99)) %>%
+  mutate_if(is.numeric, ~na_if(., -77)) %>%
+  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
+  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
+
+# Inspect dimensions
+dim(glad.midas.raw.id)
+# Inspect colnames
+colnames(glad.midas.raw.id)
+#Differences
+dim(glad.midas.raw)[1]-dim(glad.midas.raw.id)[1]
+}
+```
+
+```{r glad copy midas}
+if(GLAD == TRUE){
+midas.raw.id <- glad.midas.raw.id
+}
+```
+
+### EDGI
+Read in data
+```{r edgi midas cols}
+if(EDGI == TRUE){
+edgi.midas.raw <- readRDS(file = paste0(data.raw_path, "/edgi/midas_coping_edgi.rds"))
+dim(edgi.midas.raw)
+colnames(edgi.midas.raw)
+}
+```
+
+Select variables
+```{r edgi midas cleaning}
+if(EDGI == TRUE){
+
+edgi.midas.raw.id <- edgi.midas.raw %>%
+  drop_na(externalDataReference) %>% # Drop NAs
+  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
+  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
+  mutate(ID = as.numeric(ID)) %>%
+  select(
+         Sample, # Sample
+         ID, # ID
+         midas.headaches_suffered_past_month,
+         midas.days_past_month_miss_work_school = midas.past_month_days,
+         midas.days_past_month_work_school_half_productivity = midas.past_month_days.1,
+         midas.days_past_month_miss_housework = midas.past_month_days.2,
+         midas.days_past_month_housework_half_productivity = midas.past_month_days.3,
+         midas.days_past_month_miss_social_activities = midas.past_month_days.4  
+         ) %>%
+  add_numeric(., exclude = exclude_cols) %>%
+  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
+  mutate_if(is.numeric, ~na_if(., -99)) %>%
+  mutate_if(is.numeric, ~na_if(., -77)) %>%
+  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
+  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
+
+# Inspect dimensions
+dim(edgi.midas.raw.id)
+# Inspect colnames
+colnames(edgi.midas.raw.id)
+#Differences
+dim(edgi.midas.raw)[1]-dim(edgi.midas.raw.id)[1]
+}
+```
+
+```{r edgi copy midas}
+if(EDGI == TRUE){
+midas.raw.id <- edgi.midas.raw.id
+}
+```
+
+### NBR
+Read in data
+```{r nbr midas cols}
+if(NBR == TRUE){
+nbr.midas.raw <- readRDS(file = paste0(data.raw_path, "/nbr/midas_coping_nbr.rds"))
+dim(nbr.midas.raw)
+colnames(nbr.midas.raw)
+}
+```
+
+Select variables
+```{r nbr midas cleaning}
+if(NBR == TRUE){
+
+nbr.midas.raw.id <- nbr.midas.raw %>%
+  drop_na(subjectid) %>% # Drop NAs
+  distinct(subjectid, .keep_all = TRUE) %>% # Remove duplicates based on ID
+  separate(subjectid, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
+  mutate(ID = as.numeric(ID)) %>%
+  select(
+         Sample, # Sample
+         ID, # ID
+         midas.day_past_month_felt,
+         midas.sitting_and_reading,
+         midas.watching_tv,
+         midas.sitting_inactive_in_a_public_place,
+         midas.break_passenger_hour_car,
+         midas.afternoon_rest_circumstances_lying,
+         midas.sitting_and_talking_to_someone,
+         midas.sitting_quietly_after_a_lunch_without_alcohol,
+         midas.car_minutes_stopped_traffic,
+         midas.insomnia,
+         midas.narcolepsy,
+         midas.rem_sleep_behaviour_disorder,
+         midas.restlmidas_legs_syndrome,
+         midas.sleep_apnea,
+         midas.sleep_terrors,
+         midas.sleepwalking,
+         midas.other,
+         midas.none  
+         ) %>%
+  add_numeric(., exclude = exclude_cols) %>%
+  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
+  mutate_if(is.numeric, ~na_if(., -99)) %>%
+  mutate_if(is.numeric, ~na_if(., -77)) %>%
+  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
+  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
+
+# Inspect dimensions
+dim(nbr.midas.raw.id)
+# Inspect colnames
+colnames(nbr.midas.raw.id)
+#Differences
+dim(nbr.midas.raw)[1]-dim(nbr.midas.raw.id)[1]
+}
+```
+
+```{r nbr copy midas}
+if(NBR == TRUE){
+midas.raw.id <- nbr.midas.raw.id
+}
+```
+
+### RAMP
+Read in data
+```{r ramp midas cols}
+if(RAMP == TRUE){
+ramp.midas.raw <- readRDS(file = paste0(data.raw_path, "/ramp/midas_ramp.rds"))
+dim(ramp.midas.raw)
+colnames(ramp.midas.raw)
+}
+```
+
+Select variables
+```{r ramp midas cleaning}
+if(RAMP == TRUE){
+
+ramp.midas.raw.id <- ramp.midas.raw %>%
+  drop_na(`Login ID`) %>% # Drop NAs
+  distinct(`Login ID`, .keep_all = TRUE) %>% # Remove duplicates based on ID
+  separate(`Login ID`, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
+  mutate(ID = as.numeric(ID)) %>%
+  select(
+         Sample, # Sample
+         ID, # ID
+         midas.day_past_month_felt,
+         midas.sitting_and_reading,
+         midas.watching_tv,
+         midas.sitting_inactive_in_a_public_place,
+         midas.break_passenger_hour_car,
+         midas.afternoon_rest_circumstances_lying,
+         midas.sitting_and_talking_to_someone,
+         midas.sitting_quietly_after_a_lunch_without_alcohol,
+         midas.car_minutes_stopped_traffic,
+         midas.insomnia,
+         midas.narcolepsy,
+         midas.rem_sleep_behaviour_disorder,
+         midas.restlmidas_legs_syndrome,
+         midas.sleep_apnea,
+         midas.sleep_terrors,
+         midas.sleepwalking,
+         midas.other,
+         midas.none  
+         ) %>%
+  add_numeric(., exclude = exclude_cols) %>%
+  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
+  mutate_if(is.numeric, ~na_if(., -99)) %>%
+  mutate_if(is.numeric, ~na_if(., -77)) %>%
+  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
+  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
+
+# Inspect dimensions
+dim(ramp.midas.raw.id)
+# Inspect colnames
+colnames(ramp.midas.raw.id)
+#Differences
+dim(ramp.midas.raw)[1]-dim(ramp.midas.raw.id)[1]
+}
+```
+
+```{r ramp copy midas}
+if(RAMP == TRUE){
+midas.raw.id <- ramp.midas.raw.id
+}
+```
+
+## Loss of taste/smell (nmss)
+
+### GLAD
+Read in data
+```{r glad nmss cols}
+if(GLAD == TRUE){
+glad.nmss.raw <- readRDS(file = paste0(data.raw_path, "/glad/nmss_coping_glad.rds"))
+dim(glad.nmss.raw)
+colnames(glad.nmss.raw)
+}
+```
+
+Select variables
+```{r glad nmss cleaning}
+if(GLAD == TRUE){
+
+glad.nmss.raw.id <- glad.nmss.raw %>%
+  drop_na(externalDataReference) %>% # Drop NAs
+  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
+  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
+  mutate(ID = as.numeric(ID)) %>%
+  select(
+         Sample, # Sample
+         ID, # ID
+         nmss.ability_taste_food_change,
+         nmss.severe_taste_smell_loss
+         ) %>%
+  add_numeric(., exclude = exclude_cols) %>%
+  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
+  mutate_if(is.numeric, ~na_if(., -99)) %>%
+  mutate_if(is.numeric, ~na_if(., -77)) %>%
+  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
+  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
+
+# Inspect dimensions
+dim(glad.nmss.raw.id)
+# Inspect colnames
+colnames(glad.nmss.raw.id)
+#Differences
+dim(glad.nmss.raw)[1]-dim(glad.nmss.raw.id)[1]
+}
+```
+
+```{r glad copy nmss}
+if(GLAD == TRUE){
+nmss.raw.id <- glad.nmss.raw.id
+}
+```
+
+### EDGI
+Read in data
+```{r edgi nmss cols}
+if(EDGI == TRUE){
+edgi.nmss.raw <- readRDS(file = paste0(data.raw_path, "/edgi/nmss_coping_edgi.rds"))
+dim(edgi.nmss.raw)
+colnames(edgi.nmss.raw)
+}
+```
+
+Select variables
+```{r edgi nmss cleaning}
+if(EDGI == TRUE){
+
+edgi.nmss.raw.id <- edgi.nmss.raw %>%
+  drop_na(externalDataReference) %>% # Drop NAs
+  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
+  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
+  mutate(ID = as.numeric(ID)) %>%
+  select(
+         Sample, # Sample
+         ID, # ID
+         nmss.ability_taste_food_change = nmss.taste_food_ability_smell,
+         nmss.severe_taste_smell_loss
+         ) %>%
+  add_numeric(., exclude = exclude_cols) %>%
+  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
+  mutate_if(is.numeric, ~na_if(., -99)) %>%
+  mutate_if(is.numeric, ~na_if(., -77)) %>%
+  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
+  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
+
+# Inspect dimensions
+dim(edgi.nmss.raw.id)
+# Inspect colnames
+colnames(edgi.nmss.raw.id)
+#Differences
+dim(edgi.nmss.raw)[1]-dim(edgi.nmss.raw.id)[1]
+}
+```
+
+```{r edgi copy nmss}
+if(EDGI == TRUE){
+nmss.raw.id <- edgi.nmss.raw.id
+}
+```
+
+### NBR
+Read in data
+```{r nbr nmss cols}
+if(NBR == TRUE){
+nbr.nmss.raw <- readRDS(file = paste0(data.raw_path, "/nbr/nmss_coping_nbr.rds"))
+dim(nbr.nmss.raw)
+colnames(nbr.nmss.raw)
+}
+```
+
+Select variables
+```{r nbr nmss cleaning}
+if(NBR == TRUE){
+
+nbr.nmss.raw.id <- nbr.nmss.raw %>%
+  drop_na(subjectid) %>% # Drop NAs
+  distinct(subjectid, .keep_all = TRUE) %>% # Remove duplicates based on ID
+  separate(subjectid, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
+  mutate(ID = as.numeric(ID)) %>%
+  select(
+         Sample, # Sample
+         ID, # ID
+         nmss.ability_taste_food_change,
+         nmss.severe_taste_smell_loss 
+         ) %>%
+  add_numeric(., exclude = exclude_cols) %>%
+  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
+  mutate_if(is.numeric, ~na_if(., -99)) %>%
+  mutate_if(is.numeric, ~na_if(., -77)) %>%
+  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
+  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
+
+# Inspect dimensions
+dim(nbr.nmss.raw.id)
+# Inspect colnames
+colnames(nbr.nmss.raw.id)
+#Differences
+dim(nbr.nmss.raw)[1]-dim(nbr.nmss.raw.id)[1]
+}
+```
+
+```{r nbr copy nmss}
+if(NBR == TRUE){
+nmss.raw.id <- nbr.nmss.raw.id
+}
+```
+
+### RAMP
+Read in data
+```{r ramp nmss cols}
+if(RAMP == TRUE){
+ramp.nmss.raw <- readRDS(file = paste0(data.raw_path, "/ramp/nmss_ramp.rds"))
+dim(ramp.nmss.raw)
+colnames(ramp.nmss.raw)
+}
+```
+
+Select variables
+```{r ramp nmss cleaning}
+if(RAMP == TRUE){
+
+ramp.nmss.raw.id <- ramp.nmss.raw %>%
+  drop_na(`Login ID`) %>% # Drop NAs
+  distinct(`Login ID`, .keep_all = TRUE) %>% # Remove duplicates based on ID
+  separate(`Login ID`, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
+  mutate(ID = as.numeric(ID)) %>%
+  select(
+         Sample, # Sample
+         ID, # ID
+         nmss.ability_taste_food_change,
+         nmss.severe_taste_smell_loss 
+         ) %>%
+  add_numeric(., exclude = exclude_cols) %>%
+  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
+  mutate_if(is.numeric, ~na_if(., -99)) %>%
+  mutate_if(is.numeric, ~na_if(., -77)) %>%
+  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
+  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
+
+# Inspect dimensions
+dim(ramp.nmss.raw.id)
+# Inspect colnames
+colnames(ramp.nmss.raw.id)
+#Differences
+dim(ramp.nmss.raw)[1]-dim(ramp.nmss.raw.id)[1]
+}
+```
+
+```{r ramp copy nmss}
+if(RAMP == TRUE){
+nmss.raw.id <- ramp.nmss.raw.id
+}
+```
+
+## Non-motor symptoms (nmsw)
+
+### GLAD
+Read in data
+```{r glad nmsw cols}
+if(GLAD == TRUE){
+glad.nmsw.raw <- readRDS(file = paste0(data.raw_path, "/glad/nmsw_coping_glad.rds"))
+dim(glad.nmsw.raw)
+colnames(glad.nmsw.raw)
+}
+```
+
+Select variables
+```{r glad nmsw cleaning}
+if(GLAD == TRUE){
+
+glad.nmsw.raw.id <- glad.nmsw.raw %>%
+  drop_na(externalDataReference) %>% # Drop NAs
+  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
+  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
+  mutate(ID = as.numeric(ID)) %>%
+  select(
+         Sample, # Sample
+         ID, # ID
+         nmsw.drink_problems_choking_difficulty,
+         nmsw.night_regularly_pass_urine,
+         nmsw.sex_finding_difficult,
+         nmsw.weak_standing_feeling_light,
+         nmsw.acting_moving_sleep_talking,
+         nmsw.double_vision     
+         ) %>%
+  add_numeric(., exclude = exclude_cols) %>%
+  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
+  mutate_if(is.numeric, ~na_if(., -99)) %>%
+  mutate_if(is.numeric, ~na_if(., -77)) %>%
+  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
+  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
+
+# Inspect dimensions
+dim(glad.nmsw.raw.id)
+# Inspect colnames
+colnames(glad.nmsw.raw.id)
+#Differences
+dim(glad.nmsw.raw)[1]-dim(glad.nmsw.raw.id)[1]
+}
+```
+
+```{r glad copy nmsw}
+if(GLAD == TRUE){
+nmsw.raw.id <- glad.nmsw.raw.id
+}
+```
+
+### EDGI
+Read in data
+```{r edgi nmsw cols}
+if(EDGI == TRUE){
+edgi.nmsw.raw <- readRDS(file = paste0(data.raw_path, "/edgi/nmsw_coping_edgi.rds"))
+dim(edgi.nmsw.raw)
+colnames(edgi.nmsw.raw)
+}
+```
+
+Select variables
+```{r edgi nmsw cleaning}
+if(EDGI == TRUE){
+
+edgi.nmsw.raw.id <- edgi.nmsw.raw %>%
+  drop_na(externalDataReference) %>% # Drop NAs
+  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
+  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
+  mutate(ID = as.numeric(ID)) %>%
+  select(
+         Sample, # Sample
+         ID, # ID
+         nmsw.drink_problems_choking_difficulty,
+         nmsw.night_regularly_pass_urine = nmsw.regularly_night_pass_urine,
+         nmsw.sex_finding_difficult = nmsw.sex_difficult_finding,
+         nmsw.weak_standing_feeling_light,
+         nmsw.acting_moving_sleep_talking,
+         nmsw.double_vision
+         ) %>%
+  add_numeric(., exclude = exclude_cols) %>%
+  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
+  mutate_if(is.numeric, ~na_if(., -99)) %>%
+  mutate_if(is.numeric, ~na_if(., -77)) %>%
+  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
+  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
+
+# Inspect dimensions
+dim(edgi.nmsw.raw.id)
+# Inspect colnames
+colnames(edgi.nmsw.raw.id)
+#Differences
+dim(edgi.nmsw.raw)[1]-dim(edgi.nmsw.raw.id)[1]
+}
+```
+
+```{r edgi copy nmsw}
+if(EDGI == TRUE){
+nmsw.raw.id <- edgi.nmsw.raw.id
+}
+```
+
+### NBR
+Read in data
+```{r nbr nmsw cols}
+if(NBR == TRUE){
+nbr.nmsw.raw <- readRDS(file = paste0(data.raw_path, "/nbr/nmsw_coping_nbr.rds"))
+dim(nbr.nmsw.raw)
+colnames(nbr.nmsw.raw)
+}
+```
+
+Select variables
+```{r nbr nmsw cleaning}
+if(NBR == TRUE){
+
+nbr.nmsw.raw.id <- nbr.nmsw.raw %>%
+  drop_na(subjectid) %>% # Drop NAs
+  distinct(subjectid, .keep_all = TRUE) %>% # Remove duplicates based on ID
+  separate(subjectid, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
+  mutate(ID = as.numeric(ID)) %>%
+  select(
+         Sample, # Sample
+         ID, # ID
+         nmsw.drink_problems_choking_difficulty,
+         nmsw.night_regularly_pass_urine,
+         nmsw.sex_finding_difficult,
+         nmsw.weak_standing_feeling_light,
+         nmsw.acting_moving_sleep_talking,
+         nmsw.double_vision 
+         ) %>%
+  add_numeric(., exclude = exclude_cols) %>%
+  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
+  mutate_if(is.numeric, ~na_if(., -99)) %>%
+  mutate_if(is.numeric, ~na_if(., -77)) %>%
+  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
+  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
+
+# Inspect dimensions
+dim(nbr.nmsw.raw.id)
+# Inspect colnames
+colnames(nbr.nmsw.raw.id)
+#Differences
+dim(nbr.nmsw.raw)[1]-dim(nbr.nmsw.raw.id)[1]
+}
+```
+
+```{r nbr copy nmsw}
+if(NBR == TRUE){
+nmsw.raw.id <- nbr.nmsw.raw.id
+}
+```
+
+### RAMP
+Read in data
+```{r ramp nmsw cols}
+if(RAMP == TRUE){
+ramp.nmsw.raw <- readRDS(file = paste0(data.raw_path, "/ramp/nmsw_ramp.rds"))
+dim(ramp.nmsw.raw)
+colnames(ramp.nmsw.raw)
+}
+```
+
+Select variables
+```{r ramp nmsw cleaning}
+if(RAMP == TRUE){
+
+ramp.nmsw.raw.id <- ramp.nmsw.raw %>%
+  drop_na(`Login ID`) %>% # Drop NAs
+  distinct(`Login ID`, .keep_all = TRUE) %>% # Remove duplicates based on ID
+  separate(`Login ID`, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
+  mutate(ID = as.numeric(ID)) %>%
+  select(
+         Sample, # Sample
+         ID, # ID
+         nmsw.drink_problems_choking_difficulty,
+         nmsw.night_regularly_pass_urine,
+         nmsw.sex_finding_difficult,
+         nmsw.weak_standing_feeling_light,
+         nmsw.acting_moving_sleep_talking,
+         nmsw.double_vision 
+         ) %>%
+  add_numeric(., exclude = exclude_cols) %>%
+  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
+  mutate_if(is.numeric, ~na_if(., -99)) %>%
+  mutate_if(is.numeric, ~na_if(., -77)) %>%
+  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
+  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
+
+# Inspect dimensions
+dim(ramp.nmsw.raw.id)
+# Inspect colnames
+colnames(ramp.nmsw.raw.id)
+#Differences
+dim(ramp.nmsw.raw)[1]-dim(ramp.nmsw.raw.id)[1]
+}
+```
+
+```{r ramp copy nmsw}
+if(RAMP == TRUE){
+nmsw.raw.id <- ramp.nmsw.raw.id
+}
+```
+
+## Tinnitus
+
+### GLAD
+Read in data
+```{r glad tinnitus cols}
+if(GLAD == TRUE){
+glad.tinnitus.raw <- readRDS(file = paste0(data.raw_path, "/glad/tinnitus_coping_glad.rds"))
+dim(glad.tinnitus.raw)
+colnames(glad.tinnitus.raw)
+}
+```
+
+Select variables
+```{r glad tinnitus cleaning}
+if(GLAD == TRUE){
+
+glad.tinnitus.raw.id <- glad.tinnitus.raw %>%
+  drop_na(externalDataReference) %>% # Drop NAs
+  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
+  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
+  mutate(ID = as.numeric(ID)) %>%
+  select(
+         Sample, # Sample
+         ID, # ID
+         tinnitus.ears_noises_head_minutes,
+         tinnitus.lasts_ears_noises_head,
+         tinnitus.noises_worry_worst_upset    
+         ) %>%
+  add_numeric(., exclude = exclude_cols) %>%
+  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
+  mutate_if(is.numeric, ~na_if(., -99)) %>%
+  mutate_if(is.numeric, ~na_if(., -77)) %>%
+  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
+  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
+
+# Inspect dimensions
+dim(glad.tinnitus.raw.id)
+# Inspect colnames
+colnames(glad.tinnitus.raw.id)
+#Differences
+dim(glad.tinnitus.raw)[1]-dim(glad.tinnitus.raw.id)[1]
+}
+```
+
+```{r glad copy tinnitus}
+if(GLAD == TRUE){
+tinnitus.raw.id <- glad.tinnitus.raw.id
+}
+```
+
+### EDGI
+Read in data
+```{r edgi tinnitus cols}
+if(EDGI == TRUE){
+edgi.tinnitus.raw <- readRDS(file = paste0(data.raw_path, "/edgi/tinnitus_coping_edgi.rds"))
+dim(edgi.tinnitus.raw)
+colnames(edgi.tinnitus.raw)
+}
+```
+
+Select variables
+```{r edgi tinnitus cleaning}
+if(EDGI == TRUE){
+
+edgi.tinnitus.raw.id <- edgi.tinnitus.raw %>%
+  drop_na(externalDataReference) %>% # Drop NAs
+  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
+  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
+  mutate(ID = as.numeric(ID)) %>%
+  select(
+         Sample, # Sample
+         ID, # ID
+         tinnitus.ears_noises_head_minutes = tinnitus.ears_noises_minutes_head,
+         tinnitus.lasts_ears_noises_head = tinnitus.ears_noises_minutes_head.1,
+         tinnitus.noises_worry_worst_upset
+         ) %>%
+  add_numeric(., exclude = exclude_cols) %>%
+  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
+  mutate_if(is.numeric, ~na_if(., -99)) %>%
+  mutate_if(is.numeric, ~na_if(., -77)) %>%
+  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
+  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
+
+# Inspect dimensions
+dim(edgi.tinnitus.raw.id)
+# Inspect colnames
+colnames(edgi.tinnitus.raw.id)
+#Differences
+dim(edgi.tinnitus.raw)[1]-dim(edgi.tinnitus.raw.id)[1]
+}
+```
+
+```{r edgi copy tinnitus}
+if(EDGI == TRUE){
+tinnitus.raw.id <- edgi.tinnitus.raw.id
+}
+```
+
+### NBR
+Read in data
+```{r nbr tinnitus cols}
+if(NBR == TRUE){
+nbr.tinnitus.raw <- readRDS(file = paste0(data.raw_path, "/nbr/tinnitus_coping_nbr.rds"))
+dim(nbr.tinnitus.raw)
+colnames(nbr.tinnitus.raw)
+}
+```
+
+Select variables
+```{r nbr tinnitus cleaning}
+if(NBR == TRUE){
+
+nbr.tinnitus.raw.id <- nbr.tinnitus.raw %>%
+  drop_na(subjectid) %>% # Drop NAs
+  distinct(subjectid, .keep_all = TRUE) %>% # Remove duplicates based on ID
+  separate(subjectid, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
+  mutate(ID = as.numeric(ID)) %>%
+  select(
+         Sample, # Sample
+         ID, # ID
+         tinnitus.ears_noises_head_minutes,
+         tinnitus.lasts_ears_noises_head,
+         tinnitus.noises_worry_worst_upset 
+         ) %>%
+  add_numeric(., exclude = exclude_cols) %>%
+  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
+  mutate_if(is.numeric, ~na_if(., -99)) %>%
+  mutate_if(is.numeric, ~na_if(., -77)) %>%
+  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
+  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
+
+# Inspect dimensions
+dim(nbr.tinnitus.raw.id)
+# Inspect colnames
+colnames(nbr.tinnitus.raw.id)
+#Differences
+dim(nbr.tinnitus.raw)[1]-dim(nbr.tinnitus.raw.id)[1]
+}
+```
+
+```{r nbr copy tinnitus}
+if(NBR == TRUE){
+tinnitus.raw.id <- nbr.tinnitus.raw.id
+}
+```
+
+### RAMP
+Read in data
+```{r ramp tinnitus cols}
+if(RAMP == TRUE){
+ramp.tinnitus.raw <- readRDS(file = paste0(data.raw_path, "/ramp/tinnitus_ramp.rds"))
+dim(ramp.tinnitus.raw)
+colnames(ramp.tinnitus.raw)
+}
+```
+
+Select variables
+```{r ramp tinnitus cleaning}
+if(RAMP == TRUE){
+
+ramp.tinnitus.raw.id <- ramp.tinnitus.raw %>%
+  drop_na(`Login ID`) %>% # Drop NAs
+  distinct(`Login ID`, .keep_all = TRUE) %>% # Remove duplicates based on ID
+  separate(`Login ID`, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
+  mutate(ID = as.numeric(ID)) %>%
+  select(
+         Sample, # Sample
+         ID, # ID
+         tinnitus.ears_noises_head_minutes,
+         tinnitus.lasts_ears_noises_head,
+         tinnitus.noises_worry_worst_upset
+         ) %>%
+  add_numeric(., exclude = exclude_cols) %>%
+  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
+  mutate_if(is.numeric, ~na_if(., -99)) %>%
+  mutate_if(is.numeric, ~na_if(., -77)) %>%
+  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
+  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
+
+# Inspect dimensions
+dim(ramp.tinnitus.raw.id)
+# Inspect colnames
+colnames(ramp.tinnitus.raw.id)
+#Differences
+dim(ramp.tinnitus.raw)[1]-dim(ramp.tinnitus.raw.id)[1]
+}
+```
+
+```{r ramp copy tinnitus}
+if(RAMP == TRUE){
+tinnitus.raw.id <- ramp.tinnitus.raw.id
+}
+```
+
 # Join tibbles together
@@
   coping.pcl.raw.id,
-  coping.phq.raw.id
+  coping.phq.raw.id,
+  als.raw.id,
+  ess.raw.id,
+  midas.raw.id,
+  nmss.raw.id,
+  nmsw.raw.id,
+  tinnitus.raw.id
 #  coping.ocir.raw.id
@@
   coping.phq.raw.id,
-  coping.ocir.raw.id
+  coping.ocir.raw.id,
+  als.raw.id,
+  ess.raw.id,
+  midas.raw.id,
+  nmss.raw.id,
+  nmsw.raw.id,
+  tinnitus.raw.id
 )
@@
 The COVID prediction model has coded the sexes opposite to our data set
-```{r create numeric sex variable with male=1}
+```{r create numeric sex variable with male eq 1}
 if(GLAD == TRUE | NBR == TRUE | EDGI == TRUE){
@@
 Sex is no available in the RAMP dataset, therefore a proxy sex variable is created whereby Gender = Male and Transgender = No. 
-```{r create numeric sex variable with male=1 for ramp}
+```{r create numeric sex variable with male eq 1 for ramp}
 if(RAMP == TRUE){

### 2020-09-10 PANCHANGE_data_preprocessing2020-07-15.Rmd
added RAMP and NBR neurological questionnaires

--- 2020-09-07 PANCHANGE_data_preprocessing2020-07-15.Rmd
@@
 
+# Neurological symptoms
+
+## ALS (alsfrs)
+
+### GLAD
+Read in data
+```{r glad als cols}
+if(GLAD == TRUE){
+glad.als.raw <- readRDS(file = paste0(data.raw_path, "/glad/alsfrs_coping_glad.rds"))
+dim(glad.als.raw)
+colnames(glad.als.raw)
+}
+```
+
+Select variables
+```{r glad als cleaning}
+if(GLAD == TRUE){
+
+glad.als.raw.id <- glad.als.raw %>%
+  drop_na(externalDataReference) %>% # Drop NAs
+  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
+  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
+  mutate(ID = as.numeric(ID)) %>%
+  select(
+         Sample, # Sample
+         ID, # ID
+         alsfrs.limb_weakness_noticed_past,
+         alsfrs.normal,
+         alsfrs.slow_or_sloppy_all_words_are_legible,
+         alsfrs.not_all_words_are_legible,
+         alsfrs.able_to_grip_pen,
+         alsfrs.unable_to_grip_pen,
+         alsfrs.have_you_noticed_any_difficulty_walking,
+         alsfrs.do_you_have_any_difficulty_climbing_stairs
+         ) %>%
+  add_numeric(., exclude = exclude_cols) %>%
+  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
+  mutate_if(is.numeric, ~na_if(., -99)) %>%
+  mutate_if(is.numeric, ~na_if(., -77)) %>%
+  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
+  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
+
+# Inspect dimensions
+dim(glad.als.raw.id)
+# Inspect colnames
+colnames(glad.als.raw.id)
+#Differences
+dim(glad.als.raw)[1]-dim(glad.als.raw.id)[1]
+}
+```
+
+```{r glad copy als}
+if(GLAD == TRUE){
+als.raw.id <- glad.als.raw.id
+}
+```
+
+### EDGI
+Read in data
+```{r edgi als cols}
+if(EDGI == TRUE){
+edgi.als.raw <- readRDS(file = paste0(data.raw_path, "/edgi/alsfrs_coping_edgi.rds"))
+dim(edgi.als.raw)
+colnames(edgi.als.raw)
+}
+```
+
+Select variables
+```{r edgi als cleaning}
+if(EDGI == TRUE){
+
+edgi.als.raw.id <- edgi.als.raw %>%
+  drop_na(externalDataReference) %>% # Drop NAs
+  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
+  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
+  mutate(ID = as.numeric(ID)) %>%
+  select(
+         Sample, # Sample
+         ID, # ID
+         alsfrs.limb_weakness_noticed_past,
+         alsfrs.normal,
+         alsfrs.slow_or_sloppy_all_words_are_legible,
+         alsfrs.not_all_words_are_legible,
+         alsfrs.able_to_grip_pen,
+         alsfrs.unable_to_grip_pen,
+         alsfrs.have_you_noticed_any_difficulty_walking,
+         alsfrs.do_you_have_any_difficulty_climbing_stairs
+         ) %>%
+  add_numeric(., exclude = exclude_cols) %>%
+  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
+  mutate_if(is.numeric, ~na_if(., -99)) %>%
+  mutate_if(is.numeric, ~na_if(., -77)) %>%
+  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
+  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
+
+# Inspect dimensions
+dim(edgi.als.raw.id)
+# Inspect colnames
+colnames(edgi.als.raw.id)
+#Differences
+dim(edgi.als.raw)[1]-dim(edgi.als.raw.id)[1]
+}
+```
+
+```{r edgi copy als}
+if(EDGI == TRUE){
+als.raw.id <- edgi.als.raw.id
+}
+```
+
+### NBR
+Read in data
+```{r nbr als cols}
+if(NBR == TRUE){
+nbr.als.raw <- readRDS(file = paste0(data.raw_path, "/nbr/alsfrs_coping_nbr.rds"))
+dim(nbr.als.raw)
+colnames(nbr.als.raw)
+}
+```
+
+Select variables
+```{r nbr als cleaning}
+if(NBR == TRUE){
+
+nbr.als.raw.id <- nbr.als.raw %>%
+  drop_na(subjectid) %>% # Drop NAs
+  distinct(subjectid, .keep_all = TRUE) %>% # Remove duplicates based on ID
+  separate(subjectid, into = c("Sample", "ID.intm"), sep = 6) %>% # Split ID in Sample and Number
+  separate(ID.intm, into = "ID", sep = 7) %>%
+  mutate(ID = as.numeric(ID)) %>%
+  select(
+         Sample, # Sample
+         ID, # ID
+         alsfrs.limb_weakness_noticed_past,
+         alsfrs.normal,
+         alsfrs.slow_or_sloppy_all_words_are_legible,
+         alsfrs.not_all_words_are_legible,
+         alsfrs.able_to_grip_pen,
+         alsfrs.unable_to_grip_pen,
+         alsfrs.have_you_noticed_any_difficulty_walking,
+         alsfrs.do_you_have_any_difficulty_climbing_stairs
+         ) %>%
+  add_numeric(., exclude = exclude_cols) %>%
+  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
+  mutate_if(is.numeric, ~na_if(., -99)) %>%
+  mutate_if(is.numeric, ~na_if(., -77)) %>%
+  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
+  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
+
+# Inspect dimensions
+dim(nbr.als.raw.id)
+# Inspect colnames
+colnames(nbr.als.raw.id)
+#Differences
+dim(nbr.als.raw)[1]-dim(nbr.als.raw.id)[1]
+}
+```
+
+```{r nbr copy als}
+if(NBR == TRUE){
+als.raw.id <- nbr.als.raw.id
+}
+```
+
+### RAMP
+Read in data
+```{r ramp als cols}
+if(RAMP == TRUE){
+ramp.als.raw <- readRDS(file = paste0(data.raw_path, "/ramp/alsfrs_ramp.rds"))
+dim(ramp.als.raw)
+colnames(ramp.als.raw)
+}
+```
+
+Select variables
+```{r ramp als cleaning}
+if(RAMP == TRUE){
+
+ramp.als.raw.id <- ramp.als.raw %>%
+  drop_na(`Login ID`) %>% # Drop NAs
+  distinct(`Login ID`, .keep_all = TRUE) %>% # Remove duplicates based on ID
+  separate(`Login ID`, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
+  mutate(ID = as.numeric(ID)) %>%
+  select(
+         Sample, # Sample
+         ID, # ID
+         alsfrs.limb_weakness_noticed_past = alsfrs.limb_weakness_past_month,
+         alsfrs.normal,
+         alsfrs.slow_or_sloppy_all_words_are_legible,
+         alsfrs.not_all_words_are_legible,
+         alsfrs.able_to_grip_pen,
+         alsfrs.unable_to_grip_pen,
+         alsfrs.have_you_noticed_any_difficulty_walking,
+         alsfrs.do_you_have_any_difficulty_climbing_stairs
+         ) %>%
+  add_numeric(., exclude = exclude_cols) %>%
+  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
+  mutate_if(is.numeric, ~na_if(., -99)) %>%
+  mutate_if(is.numeric, ~na_if(., -77)) %>%
+  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
+  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
+
+# Inspect dimensions
+dim(ramp.als.raw.id)
+# Inspect colnames
+colnames(ramp.als.raw.id)
+#Differences
+dim(ramp.als.raw)[1]-dim(ramp.als.raw.id)[1]
+}
+```
+
+```{r ramp copy als}
+if(RAMP == TRUE){
+als.raw.id <- ramp.als.raw.id
+}
+```
+
+## Epsworth sleep scale (ess)
+
+### GLAD
+Read in data
+```{r glad ess cols}
+if(GLAD == TRUE){
+glad.ess.raw <- readRDS(file = paste0(data.raw_path, "/glad/ess_coping_glad.rds"))
+dim(glad.ess.raw)
+colnames(glad.ess.raw)
+}
+```
+
+Select variables
+```{r glad ess cleaning}
+if(GLAD == TRUE){
+
+glad.ess.raw.id <- glad.ess.raw %>%
+  drop_na(externalDataReference) %>% # Drop NAs
+  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
+  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
+  mutate(ID = as.numeric(ID)) %>%
+  select(
+         Sample, # Sample
+         ID, # ID
+         ess.felt_excessively_sleepy_past,
+         ess.sitting_and_reading,
+         ess.watching_tv,
+         ess.sitting_inactive_in_a_public_place,
+         ess.break_passenger_car_hour,
+         ess.afternoon_rest_circumstances_lying,
+         ess.sitting_and_talking_to_someone,
+         ess.sitting_quietly_after_a_lunch_without_alcohol,
+         ess.car_minutes_stopped_traffic,
+         ess.insomnia,
+         ess.narcolepsy,
+         ess.rem_sleep_behaviour_disorder,
+         ess.restless_legs_syndrome,
+         ess.sleep_apnea,
+         ess.sleep_terrors,
+         ess.sleepwalking,
+         ess.other,
+         ess.none   
+         ) %>%
+  add_numeric(., exclude = exclude_cols) %>%
+  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
+  mutate_if(is.numeric, ~na_if(., -99)) %>%
+  mutate_if(is.numeric, ~na_if(., -77)) %>%
+  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
+  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
+
+# Inspect dimensions
+dim(glad.ess.raw.id)
+# Inspect colnames
+colnames(glad.ess.raw.id)
+#Differences
+dim(glad.ess.raw)[1]-dim(glad.ess.raw.id)[1]
+}
+```
+
+```{r glad copy ess}
+if(GLAD == TRUE){
+ess.raw.id <- glad.ess.raw.id
+}
+```
+
+### EDGI
+Read in data
+```{r edgi ess cols}
+if(EDGI == TRUE){
+edgi.ess.raw <- readRDS(file = paste0(data.raw_path, "/edgi/ess_coping_edgi.rds"))
+dim(edgi.ess.raw)
+colnames(edgi.ess.raw)
+}
+```
+
+Select variables
+```{r edgi ess cleaning}
+if(EDGI == TRUE){
+
+edgi.ess.raw.id <- edgi.ess.raw %>%
+  drop_na(externalDataReference) %>% # Drop NAs
+  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
+  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
+  mutate(ID = as.numeric(ID)) %>%
+  select(
+         Sample, # Sample
+         ID, # ID
+         ess.felt_excessively_sleepy_past,
+         ess.sitting_and_reading,
+         ess.watching_tv,
+         ess.sitting_inactive_in_a_public_place,
+         ess.break_passenger_car_hour = ess.break_passenger_hour_car,
+         ess.afternoon_rest_circumstances_lying,
+         ess.sitting_and_talking_to_someone,
+         ess.sitting_quietly_after_a_lunch_without_alcohol,
+         ess.car_minutes_stopped_traffic,
+         ess.insomnia,
+         ess.narcolepsy,
+         ess.rem_sleep_behaviour_disorder,
+         ess.restless_legs_syndrome,
+         ess.sleep_apnea,
+         ess.sleep_terrors,
+         ess.sleepwalking,
+         ess.other,
+         ess.none  
+         ) %>%
+  add_numeric(., exclude = exclude_cols) %>%
+  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
+  mutate_if(is.numeric, ~na_if(., -99)) %>%
+  mutate_if(is.numeric, ~na_if(., -77)) %>%
+  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
+  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
+
+# Inspect dimensions
+dim(edgi.ess.raw.id)
+# Inspect colnames
+colnames(edgi.ess.raw.id)
+#Differences
+dim(edgi.ess.raw)[1]-dim(edgi.ess.raw.id)[1]
+}
+```
+
+```{r edgi copy ess}
+if(EDGI == TRUE){
+ess.raw.id <- edgi.ess.raw.id
+}
+```
+
+### NBR
+Read in data
+```{r nbr ess cols}
+if(NBR == TRUE){
+nbr.ess.raw <- readRDS(file = paste0(data.raw_path, "/nbr/ess_coping_nbr.rds"))
+dim(nbr.ess.raw)
+colnames(nbr.ess.raw)
+}
+```
+
+Select variables
+```{r nbr ess cleaning}
+if(NBR == TRUE){
+
+nbr.ess.raw.id <- nbr.ess.raw %>%
+  drop_na(subjectid) %>% # Drop NAs
+  distinct(subjectid, .keep_all = TRUE) %>% # Remove duplicates based on ID
+  separate(subjectid, into = c("Sample", "ID.intm"), sep = 6) %>% # Split ID in Sample and Number
+  separate(ID.intm, into = "ID", sep = 7) %>%
+  mutate(ID = as.numeric(ID)) %>%
+  select(
+         Sample, # Sample
+         ID, # ID
+         ess.felt_excessively_sleepy_past,
+         ess.sitting_and_reading,
+         ess.watching_tv,
+         ess.sitting_inactive_in_a_public_place,
+         ess.break_passenger_car_hour,
+         ess.afternoon_rest_circumstances_lying,
+         ess.sitting_and_talking_to_someone,
+         ess.sitting_quietly_after_a_lunch_without_alcohol,
+         ess.car_minutes_stopped_traffic,
+         ess.insomnia,
+         ess.narcolepsy,
+         ess.rem_sleep_behaviour_disorder,
+         ess.restless_legs_syndrome,
+         ess.sleep_apnea,
+         ess.sleep_terrors,
+         ess.sleepwalking,
+         ess.other,
+         ess.none  
+         ) %>%
+  add_numeric(., exclude = exclude_cols) %>%
+  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
+  mutate_if(is.numeric, ~na_if(., -99)) %>%
+  mutate_if(is.numeric, ~na_if(., -77)) %>%
+  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
+  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
+
+# Inspect dimensions
+dim(nbr.ess.raw.id)
+# Inspect colnames
+colnames(nbr.ess.raw.id)
+#Differences
+dim(nbr.ess.raw)[1]-dim(nbr.ess.raw.id)[1]
+}
+```
+
+```{r nbr copy ess}
+if(NBR == TRUE){
+ess.raw.id <- nbr.ess.raw.id
+}
+```
+
+### RAMP
+Read in data
+```{r ramp ess cols}
+if(RAMP == TRUE){
+ramp.ess.raw <- readRDS(file = paste0(data.raw_path, "/ramp/ess_ramp.rds"))
+dim(ramp.ess.raw)
+colnames(ramp.ess.raw)
+}
+```
+
+Select variables
+```{r ramp ess cleaning}
+if(RAMP == TRUE){
+
+ramp.ess.raw.id <- ramp.ess.raw %>%
+  drop_na(`Login ID`) %>% # Drop NAs
+  distinct(`Login ID`, .keep_all = TRUE) %>% # Remove duplicates based on ID
+  separate(`Login ID`, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
+  mutate(ID = as.numeric(ID)) %>%
+  select(
+         Sample, # Sample
+         ID, # ID
+         ess.felt_excessively_sleepy_past = ess.felt_excessively_sleepy_day,
+         ess.sitting_and_reading,
+         ess.watching_tv,
+         ess.sitting_inactive_in_a_public_place,
+         ess.break_passenger_car_hour = ess.break_hour_passenger_car,
+         ess.afternoon_rest_circumstances_lying,
+         ess.sitting_and_talking_to_someone,
+         ess.sitting_quietly_after_a_lunch_without_alcohol,
+         ess.car_minutes_stopped_traffic#,
+#         ess.insomnia, # questions are not asked in RAMP
+#         ess.narcolepsy,
+#         ess.rem_sleep_behaviour_disorder,
+#         ess.restless_legs_syndrome,
+#         ess.sleep_apnea,
+#         ess.sleep_terrors,
+#         ess.sleepwalking,
+#         ess.other,
+#         ess.none  
+         ) %>%
+  add_column(
+    ess.insomnia = NA_real_,
+    ess.narcolepsy = NA_real_,
+    ess.rem_sleep_behaviour_disorder = NA_real_,
+    ess.restless_legs_syndrome = NA_real_,
+    ess.sleep_apnea = NA_real_,
+    ess.sleep_terrors = NA_real_,
+    ess.sleepwalking = NA_real_,
+    ess.other = NA_real_,
+    ess.none = NA_real_
+    ) %>%
+  add_numeric(., exclude = exclude_cols) %>%
+  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
+  mutate_if(is.numeric, ~na_if(., -99)) %>%
+  mutate_if(is.numeric, ~na_if(., -77)) %>%
+  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
+  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
+
+# Inspect dimensions
+dim(ramp.ess.raw.id)
+# Inspect colnames
+colnames(ramp.ess.raw.id)
+#Differences
+dim(ramp.ess.raw)[1]-dim(ramp.ess.raw.id)[1]
+}
+```
+
+```{r ramp copy ess}
+if(RAMP == TRUE){
+ess.raw.id <- ramp.ess.raw.id
+}
+```
+
+## Migraines (midas)
+
+### GLAD
+Read in data
+```{r glad midas cols}
+if(GLAD == TRUE){
+glad.midas.raw <- readRDS(file = paste0(data.raw_path, "/glad/midas_coping_glad.rds"))
+dim(glad.midas.raw)
+colnames(glad.midas.raw)
+}
+```
+
+Select variables
+```{r glad midas cleaning}
+if(GLAD == TRUE){
+
+glad.midas.raw.id <- glad.midas.raw %>%
+  drop_na(externalDataReference) %>% # Drop NAs
+  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
+  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
+  mutate(ID = as.numeric(ID)) %>%
+  select(
+         Sample, # Sample
+         ID, # ID
+         midas.headaches_suffered_past_month,
+         midas.days_past_month_miss_work_school = midas.past_month_days,
+         midas.days_past_month_work_school_half_productivity = midas.past_month_days.1,
+         midas.days_past_month_miss_housework = midas.past_month_days.2,
+         midas.days_past_month_housework_half_productivity = midas.past_month_days.3,
+         midas.days_past_month_miss_social_activities = midas.past_month_days.4
+         ) %>%
+  add_numeric(., exclude = exclude_cols) %>%
+  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
+  mutate_if(is.numeric, ~na_if(., -99)) %>%
+  mutate_if(is.numeric, ~na_if(., -77)) %>%
+  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
+  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
+
+# Inspect dimensions
+dim(glad.midas.raw.id)
+# Inspect colnames
+colnames(glad.midas.raw.id)
+#Differences
+dim(glad.midas.raw)[1]-dim(glad.midas.raw.id)[1]
+}
+```
+
+```{r glad copy midas}
+if(GLAD == TRUE){
+midas.raw.id <- glad.midas.raw.id
+}
+```
+
+### EDGI
+Read in data
+```{r edgi midas cols}
+if(EDGI == TRUE){
+edgi.midas.raw <- readRDS(file = paste0(data.raw_path, "/edgi/midas_coping_edgi.rds"))
+dim(edgi.midas.raw)
+colnames(edgi.midas.raw)
+}
+```
+
+Select variables
+```{r edgi midas cleaning}
+if(EDGI == TRUE){
+
+edgi.midas.raw.id <- edgi.midas.raw %>%
+  drop_na(externalDataReference) %>% # Drop NAs
+  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
+  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
+  mutate(ID = as.numeric(ID)) %>%
+  select(
+         Sample, # Sample
+         ID, # ID
+         midas.headaches_suffered_past_month,
+         midas.days_past_month_miss_work_school = midas.past_month_days,
+         midas.days_past_month_work_school_half_productivity = midas.past_month_days.1,
+         midas.days_past_month_miss_housework = midas.past_month_days.2,
+         midas.days_past_month_housework_half_productivity = midas.past_month_days.3,
+         midas.days_past_month_miss_social_activities = midas.past_month_days.4  
+         ) %>%
+  add_numeric(., exclude = exclude_cols) %>%
+  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
+  mutate_if(is.numeric, ~na_if(., -99)) %>%
+  mutate_if(is.numeric, ~na_if(., -77)) %>%
+  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
+  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
+
+# Inspect dimensions
+dim(edgi.midas.raw.id)
+# Inspect colnames
+colnames(edgi.midas.raw.id)
+#Differences
+dim(edgi.midas.raw)[1]-dim(edgi.midas.raw.id)[1]
+}
+```
+
+```{r edgi copy midas}
+if(EDGI == TRUE){
+midas.raw.id <- edgi.midas.raw.id
+}
+```
+
+### NBR
+Read in data
+```{r nbr midas cols}
+if(NBR == TRUE){
+nbr.midas.raw <- readRDS(file = paste0(data.raw_path, "/nbr/midas_coping_nbr.rds"))
+dim(nbr.midas.raw)
+colnames(nbr.midas.raw)
+}
+```
+
+```{r nbr midas summary labels}
+if(NBR == TRUE) {
+summarytools::dfSummary(
+  nbr.midas.raw,
+  graph.col = F,
+  valid.col = F
+  #labels.col = F
+)
+}
+```
+
+Select variables
+```{r nbr midas cleaning}
+if(NBR == TRUE){
+
+nbr.midas.raw.id <- nbr.midas.raw %>%
+  drop_na(subjectid) %>% # Drop NAs
+  distinct(subjectid, .keep_all = TRUE) %>% # Remove duplicates based on ID
+  separate(subjectid, into = c("Sample", "ID.intm"), sep = 6) %>% # Split ID in Sample and Number
+  separate(ID.intm, into = "ID", sep = 7) %>%
+  mutate(ID = as.numeric(ID)) %>%
+  select(
+         Sample, # Sample
+         ID, # ID
+         midas.headaches_suffered_past_month,
+         midas.days_past_month_miss_work_school = midas.past_month_days,
+         midas.days_past_month_work_school_half_productivity = midas.past_month_days.1,
+         midas.days_past_month_miss_housework = midas.past_month_days.2,
+         midas.days_past_month_housework_half_productivity = midas.past_month_days.3,
+         midas.days_past_month_miss_social_activities = midas.past_month_days.4 
+         ) %>%
+  add_numeric(., exclude = exclude_cols) %>%
+  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
+  mutate_if(is.numeric, ~na_if(., -99)) %>%
+  mutate_if(is.numeric, ~na_if(., -77)) %>%
+  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
+  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
+
+# Inspect dimensions
+dim(nbr.midas.raw.id)
+# Inspect colnames
+colnames(nbr.midas.raw.id)
+#Differences
+dim(nbr.midas.raw)[1]-dim(nbr.midas.raw.id)[1]
+}
+```
+
+```{r nbr copy midas}
+if(NBR == TRUE){
+midas.raw.id <- nbr.midas.raw.id
+}
+```
+
+### RAMP
+Read in data
+```{r ramp midas cols}
+if(RAMP == TRUE){
+ramp.midas.raw <- readRDS(file = paste0(data.raw_path, "/ramp/midas_ramp.rds"))
+dim(ramp.midas.raw)
+colnames(ramp.midas.raw)
+}
+```
+
+```{r ramp midas summary labels}
+if(RAMP == TRUE) {
+summarytools::dfSummary(
+  ramp.midas.raw,
+  graph.col = F,
+  valid.col = F
+  #labels.col = F
+)
+}
+```
+
+Select variables
+```{r ramp midas cleaning}
+if(RAMP == TRUE){
+
+ramp.midas.raw.id <- ramp.midas.raw %>%
+  drop_na(`Login ID`) %>% # Drop NAs
+  distinct(`Login ID`, .keep_all = TRUE) %>% # Remove duplicates based on ID
+  separate(`Login ID`, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
+  mutate(ID = as.numeric(ID)) %>%
+  select(
+         Sample, # Sample
+         ID, # ID
+         midas.headaches_suffered_past_month,
+         midas.days_past_month_miss_work_school = midas.scale_line_click_firmly,
+         midas.days_past_month_work_school_half_productivity = midas.scale_line_click_firmly.1,
+         midas.days_past_month_miss_housework = midas.scale_line_click_firmly.2,
+         midas.days_past_month_housework_half_productivity = midas.scale_line_click_firmly.3,
+         midas.days_past_month_miss_social_activities = midas.scale_line_click_firmly.4
+         ) %>%
+  add_numeric(., exclude = exclude_cols) %>%
+  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
+  mutate_if(is.numeric, ~na_if(., -99)) %>%
+  mutate_if(is.numeric, ~na_if(., -77)) %>%
+  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
+  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
+
+# Inspect dimensions
+dim(ramp.midas.raw.id)
+# Inspect colnames
+colnames(ramp.midas.raw.id)
+#Differences
+dim(ramp.midas.raw)[1]-dim(ramp.midas.raw.id)[1]
+}
+```
+
+```{r ramp copy midas}
+if(RAMP == TRUE){
+midas.raw.id <- ramp.midas.raw.id
+}
+```
+
+## Loss of taste/smell (nmss)
+
+### GLAD
+Read in data
+```{r glad nmss cols}
+if(GLAD == TRUE){
+glad.nmss.raw <- readRDS(file = paste0(data.raw_path, "/glad/nmss_coping_glad.rds"))
+dim(glad.nmss.raw)
+colnames(glad.nmss.raw)
+}
+```
+
+Select variables
+```{r glad nmss cleaning}
+if(GLAD == TRUE){
+
+glad.nmss.raw.id <- glad.nmss.raw %>%
+  drop_na(externalDataReference) %>% # Drop NAs
+  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
+  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
+  mutate(ID = as.numeric(ID)) %>%
+  select(
+         Sample, # Sample
+         ID, # ID
+         nmss.ability_taste_food_smell,
+         nmss.severe_taste_smell_loss
+         ) %>%
+  add_numeric(., exclude = exclude_cols) %>%
+  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
+  mutate_if(is.numeric, ~na_if(., -99)) %>%
+  mutate_if(is.numeric, ~na_if(., -77)) %>%
+  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
+  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
+
+# Inspect dimensions
+dim(glad.nmss.raw.id)
+# Inspect colnames
+colnames(glad.nmss.raw.id)
+#Differences
+dim(glad.nmss.raw)[1]-dim(glad.nmss.raw.id)[1]
+}
+```
+
+```{r glad copy nmss}
+if(GLAD == TRUE){
+nmss.raw.id <- glad.nmss.raw.id
+}
+```
+
+### EDGI
+Read in data
+```{r edgi nmss cols}
+if(EDGI == TRUE){
+edgi.nmss.raw <- readRDS(file = paste0(data.raw_path, "/edgi/nmss_coping_edgi.rds"))
+dim(edgi.nmss.raw)
+colnames(edgi.nmss.raw)
+}
+```
+
+Select variables
+```{r edgi nmss cleaning}
+if(EDGI == TRUE){
+
+edgi.nmss.raw.id <- edgi.nmss.raw %>%
+  drop_na(externalDataReference) %>% # Drop NAs
+  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
+  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
+  mutate(ID = as.numeric(ID)) %>%
+  select(
+         Sample, # Sample
+         ID, # ID
+         nmss.ability_taste_food_smell = nmss.taste_food_ability_smell, # different to glad
+         nmss.severe_taste_smell_loss
+         ) %>%
+  add_numeric(., exclude = exclude_cols) %>%
+  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
+  mutate_if(is.numeric, ~na_if(., -99)) %>%
+  mutate_if(is.numeric, ~na_if(., -77)) %>%
+  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
+  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
+
+# Inspect dimensions
+dim(edgi.nmss.raw.id)
+# Inspect colnames
+colnames(edgi.nmss.raw.id)
+#Differences
+dim(edgi.nmss.raw)[1]-dim(edgi.nmss.raw.id)[1]
+}
+```
+
+```{r edgi copy nmss}
+if(EDGI == TRUE){
+nmss.raw.id <- edgi.nmss.raw.id
+}
+```
+
+### NBR
+Read in data
+```{r nbr nmss cols}
+if(NBR == TRUE){
+nbr.nmss.raw <- readRDS(file = paste0(data.raw_path, "/nbr/nmss_coping_nbr.rds"))
+dim(nbr.nmss.raw)
+colnames(nbr.nmss.raw)
+}
+```
+
+Select variables
+```{r nbr nmss cleaning}
+if(NBR == TRUE){
+
+nbr.nmss.raw.id <- nbr.nmss.raw %>%
+  drop_na(subjectid) %>% # Drop NAs
+  distinct(subjectid, .keep_all = TRUE) %>% # Remove duplicates based on ID
+  separate(subjectid, into = c("Sample", "ID.intm"), sep = 6) %>% # Split ID in Sample and Number
+  separate(ID.intm, into = "ID", sep = 7) %>%
+  mutate(ID = as.numeric(ID)) %>%
+  select(
+         Sample, # Sample
+         ID, # ID
+         nmss.ability_taste_food_smell,
+         nmss.severe_taste_smell_loss 
+         ) %>%
+  add_numeric(., exclude = exclude_cols) %>%
+  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
+  mutate_if(is.numeric, ~na_if(., -99)) %>%
+  mutate_if(is.numeric, ~na_if(., -77)) %>%
+  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
+  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
+
+# Inspect dimensions
+dim(nbr.nmss.raw.id)
+# Inspect colnames
+colnames(nbr.nmss.raw.id)
+#Differences
+dim(nbr.nmss.raw)[1]-dim(nbr.nmss.raw.id)[1]
+}
+```
+
+```{r nbr copy nmss}
+if(NBR == TRUE){
+nmss.raw.id <- nbr.nmss.raw.id
+}
+```
+
+### RAMP
+Read in data
+```{r ramp nmss cols}
+if(RAMP == TRUE){
+ramp.nmss.raw <- readRDS(file = paste0(data.raw_path, "/ramp/nmss_ramp.rds"))
+dim(ramp.nmss.raw)
+colnames(ramp.nmss.raw)
+}
+```
+
+Select variables
+```{r ramp nmss cleaning}
+if(RAMP == TRUE){
+
+ramp.nmss.raw.id <- ramp.nmss.raw %>%
+  drop_na(`Login ID`) %>% # Drop NAs
+  distinct(`Login ID`, .keep_all = TRUE) %>% # Remove duplicates based on ID
+  separate(`Login ID`, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
+  mutate(ID = as.numeric(ID)) %>%
+  select(
+         Sample, # Sample
+         ID, # ID
+         nmss.ability_taste_food_smell,
+         nmss.severe_taste_smell_loss = nmss.severe_taste_loss_smell 
+         ) %>%
+  add_numeric(., exclude = exclude_cols) %>%
+  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
+  mutate_if(is.numeric, ~na_if(., -99)) %>%
+  mutate_if(is.numeric, ~na_if(., -77)) %>%
+  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
+  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
+
+# Inspect dimensions
+dim(ramp.nmss.raw.id)
+# Inspect colnames
+colnames(ramp.nmss.raw.id)
+#Differences
+dim(ramp.nmss.raw)[1]-dim(ramp.nmss.raw.id)[1]
+}
+```
+
+```{r ramp copy nmss}
+if(RAMP == TRUE){
+nmss.raw.id <- ramp.nmss.raw.id
+}
+```
+
+## Non-motor symptoms (nmsw)
+
+### GLAD
+Read in data
+```{r glad nmsw cols}
+if(GLAD == TRUE){
+glad.nmsw.raw <- readRDS(file = paste0(data.raw_path, "/glad/nmsw_coping_glad.rds"))
+dim(glad.nmsw.raw)
+colnames(glad.nmsw.raw)
+}
+```
+
+Select variables
+```{r glad nmsw cleaning}
+if(GLAD == TRUE){
+
+glad.nmsw.raw.id <- glad.nmsw.raw %>%
+  drop_na(externalDataReference) %>% # Drop NAs
+  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
+  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
+  mutate(ID = as.numeric(ID)) %>%
+  select(
+         Sample, # Sample
+         ID, # ID
+         nmsw.drink_problems_choking_difficulty,
+         nmsw.regularly_night_pass_urine,
+         nmsw.sex_difficult_finding,
+         nmsw.weak_standing_feeling_light,
+         nmsw.acting_moving_sleep_talking,
+         nmsw.double_vision     
+         ) %>%
+  add_numeric(., exclude = exclude_cols) %>%
+  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
+  mutate_if(is.numeric, ~na_if(., -99)) %>%
+  mutate_if(is.numeric, ~na_if(., -77)) %>%
+  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
+  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
+
+# Inspect dimensions
+dim(glad.nmsw.raw.id)
+# Inspect colnames
+colnames(glad.nmsw.raw.id)
+#Differences
+dim(glad.nmsw.raw)[1]-dim(glad.nmsw.raw.id)[1]
+}
+```
+
+```{r glad copy nmsw}
+if(GLAD == TRUE){
+nmsw.raw.id <- glad.nmsw.raw.id
+}
+```
+
+### EDGI
+Read in data
+```{r edgi nmsw cols}
+if(EDGI == TRUE){
+edgi.nmsw.raw <- readRDS(file = paste0(data.raw_path, "/edgi/nmsw_coping_edgi.rds"))
+dim(edgi.nmsw.raw)
+colnames(edgi.nmsw.raw)
+}
+```
+
+Select variables
+```{r edgi nmsw cleaning}
+if(EDGI == TRUE){
+
+edgi.nmsw.raw.id <- edgi.nmsw.raw %>%
+  drop_na(externalDataReference) %>% # Drop NAs
+  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
+  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
+  mutate(ID = as.numeric(ID)) %>%
+  select(
+         Sample, # Sample
+         ID, # ID
+         nmsw.drink_problems_choking_difficulty,
+         nmsw.regularly_night_pass_urine,
+         nmsw.sex_difficult_finding,
+         nmsw.weak_standing_feeling_light,
+         nmsw.acting_moving_sleep_talking,
+         nmsw.double_vision
+         ) %>%
+  add_numeric(., exclude = exclude_cols) %>%
+  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
+  mutate_if(is.numeric, ~na_if(., -99)) %>%
+  mutate_if(is.numeric, ~na_if(., -77)) %>%
+  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
+  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
+
+# Inspect dimensions
+dim(edgi.nmsw.raw.id)
+# Inspect colnames
+colnames(edgi.nmsw.raw.id)
+#Differences
+dim(edgi.nmsw.raw)[1]-dim(edgi.nmsw.raw.id)[1]
+}
+```
+
+```{r edgi copy nmsw}
+if(EDGI == TRUE){
+nmsw.raw.id <- edgi.nmsw.raw.id
+}
+```
+
+### NBR
+Read in data
+```{r nbr nmsw cols}
+if(NBR == TRUE){
+nbr.nmsw.raw <- readRDS(file = paste0(data.raw_path, "/nbr/nmsw_coping_nbr.rds"))
+dim(nbr.nmsw.raw)
+colnames(nbr.nmsw.raw)
+}
+```
+
+Select variables
+```{r nbr nmsw cleaning}
+if(NBR == TRUE){
+
+nbr.nmsw.raw.id <- nbr.nmsw.raw %>%
+  drop_na(subjectid) %>% # Drop NAs
+  distinct(subjectid, .keep_all = TRUE) %>% # Remove duplicates based on ID
+  separate(subjectid, into = c("Sample", "ID.intm"), sep = 6) %>% # Split ID in Sample and Number
+  separate(ID.intm, into = "ID", sep = 7) %>%
+  mutate(ID = as.numeric(ID)) %>%
+  select(
+         Sample, # Sample
+         ID, # ID
+         nmsw.drink_problems_choking_difficulty,
+         nmsw.regularly_night_pass_urine,
+         nmsw.sex_difficult_finding,
+         nmsw.weak_standing_feeling_light,
+         nmsw.acting_moving_sleep_talking,
+         nmsw.double_vision 
+         ) %>%
+  add_numeric(., exclude = exclude_cols) %>%
+  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
+  mutate_if(is.numeric, ~na_if(., -99)) %>%
+  mutate_if(is.numeric, ~na_if(., -77)) %>%
+  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
+  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
+
+# Inspect dimensions
+dim(nbr.nmsw.raw.id)
+# Inspect colnames
+colnames(nbr.nmsw.raw.id)
+#Differences
+dim(nbr.nmsw.raw)[1]-dim(nbr.nmsw.raw.id)[1]
+}
+```
+
+```{r nbr copy nmsw}
+if(NBR == TRUE){
+nmsw.raw.id <- nbr.nmsw.raw.id
+}
+```
+
+### RAMP
+Read in data
+```{r ramp nmsw cols}
+if(RAMP == TRUE){
+ramp.nmsw.raw <- readRDS(file = paste0(data.raw_path, "/ramp/nmsw_ramp.rds"))
+dim(ramp.nmsw.raw)
+colnames(ramp.nmsw.raw)
+}
+```
+
+Select variables
+```{r ramp nmsw cleaning}
+if(RAMP == TRUE){
+
+ramp.nmsw.raw.id <- ramp.nmsw.raw %>%
+  drop_na(`Login ID`) %>% # Drop NAs
+  distinct(`Login ID`, .keep_all = TRUE) %>% # Remove duplicates based on ID
+  separate(`Login ID`, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
+  mutate(ID = as.numeric(ID)) %>%
+  select(
+         Sample, # Sample
+         ID, # ID
+         nmsw.drink_problems_choking_difficulty,
+         nmsw.regularly_night_pass_urine = nmsw.night_regularly_pass_urine, # different glad
+         nmsw.sex_difficult_finding = nmsw.sex_finding_difficult, # different glad
+         nmsw.weak_standing_feeling_light = nmsw.weak_standing_dizzy_feeling, # different glad
+         nmsw.acting_moving_sleep_talking,
+         nmsw.double_vision 
+         ) %>%
+  add_numeric(., exclude = exclude_cols) %>%
+  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
+  mutate_if(is.numeric, ~na_if(., -99)) %>%
+  mutate_if(is.numeric, ~na_if(., -77)) %>%
+  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
+  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
+
+# Inspect dimensions
+dim(ramp.nmsw.raw.id)
+# Inspect colnames
+colnames(ramp.nmsw.raw.id)
+#Differences
+dim(ramp.nmsw.raw)[1]-dim(ramp.nmsw.raw.id)[1]
+}
+```
+
+```{r ramp copy nmsw}
+if(RAMP == TRUE){
+nmsw.raw.id <- ramp.nmsw.raw.id
+}
+```
+
+## Tinnitus
+
+### GLAD
+Read in data
+```{r glad tinnitus cols}
+if(GLAD == TRUE){
+glad.tinnitus.raw <- readRDS(file = paste0(data.raw_path, "/glad/tinnitus_coping_glad.rds"))
+dim(glad.tinnitus.raw)
+colnames(glad.tinnitus.raw)
+}
+```
+
+Select variables
+```{r glad tinnitus cleaning}
+if(GLAD == TRUE){
+
+glad.tinnitus.raw.id <- glad.tinnitus.raw %>%
+  drop_na(externalDataReference) %>% # Drop NAs
+  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
+  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
+  mutate(ID = as.numeric(ID)) %>%
+  select(
+         Sample, # Sample
+         ID, # ID
+         tinnitus.ears_noises_minutes_head,
+         tinnitus.ears_noises_minutes_head_frequency = tinnitus.ears_noises_minutes_head.1,
+         tinnitus.noises_worry_worst_upset    
+         ) %>%
+  add_numeric(., exclude = exclude_cols) %>%
+  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
+  mutate_if(is.numeric, ~na_if(., -99)) %>%
+  mutate_if(is.numeric, ~na_if(., -77)) %>%
+  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
+  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
+
+# Inspect dimensions
+dim(glad.tinnitus.raw.id)
+# Inspect colnames
+colnames(glad.tinnitus.raw.id)
+#Differences
+dim(glad.tinnitus.raw)[1]-dim(glad.tinnitus.raw.id)[1]
+}
+```
+
+```{r glad copy tinnitus}
+if(GLAD == TRUE){
+tinnitus.raw.id <- glad.tinnitus.raw.id
+}
+```
+
+### EDGI
+Read in data
+```{r edgi tinnitus cols}
+if(EDGI == TRUE){
+edgi.tinnitus.raw <- readRDS(file = paste0(data.raw_path, "/edgi/tinnitus_coping_edgi.rds"))
+dim(edgi.tinnitus.raw)
+colnames(edgi.tinnitus.raw)
+}
+```
+
+Select variables
+```{r edgi tinnitus cleaning}
+if(EDGI == TRUE){
+
+edgi.tinnitus.raw.id <- edgi.tinnitus.raw %>%
+  drop_na(externalDataReference) %>% # Drop NAs
+  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
+  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
+  mutate(ID = as.numeric(ID)) %>%
+  select(
+         Sample, # Sample
+         ID, # ID
+         tinnitus.ears_noises_minutes_head,
+         tinnitus.ears_noises_minutes_head_frequency = tinnitus.ears_noises_minutes_head.1,
+         tinnitus.noises_worry_worst_upset 
+         ) %>%
+  add_numeric(., exclude = exclude_cols) %>%
+  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
+  mutate_if(is.numeric, ~na_if(., -99)) %>%
+  mutate_if(is.numeric, ~na_if(., -77)) %>%
+  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
+  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
+
+# Inspect dimensions
+dim(edgi.tinnitus.raw.id)
+# Inspect colnames
+colnames(edgi.tinnitus.raw.id)
+#Differences
+dim(edgi.tinnitus.raw)[1]-dim(edgi.tinnitus.raw.id)[1]
+}
+```
+
+```{r edgi copy tinnitus}
+if(EDGI == TRUE){
+tinnitus.raw.id <- edgi.tinnitus.raw.id
+}
+```
+
+### NBR
+Read in data
+```{r nbr tinnitus cols}
+if(NBR == TRUE){
+nbr.tinnitus.raw <- readRDS(file = paste0(data.raw_path, "/nbr/tinnitus_coping_nbr.rds"))
+dim(nbr.tinnitus.raw)
+colnames(nbr.tinnitus.raw)
+}
+```
+
+```{r ramp tinnitus summary labels}
+if(NBR == TRUE) {
+summarytools::dfSummary(
+  nbr.tinnitus.raw,
+  graph.col = F,
+  valid.col = F
+  #labels.col = F
+)
+}
+```
+
+Select variables
+```{r nbr tinnitus cleaning}
+if(NBR == TRUE){
+
+nbr.tinnitus.raw.id <- nbr.tinnitus.raw %>%
+  drop_na(subjectid) %>% # Drop NAs
+  distinct(subjectid, .keep_all = TRUE) %>% # Remove duplicates based on ID
+  separate(subjectid, into = c("Sample", "ID.intm"), sep = 6) %>% # Split ID in Sample and Number
+  separate(ID.intm, into = "ID", sep = 7) %>%
+  mutate(ID = as.numeric(ID)) %>%
+  select(
+         Sample, # Sample
+         ID, # ID
+         tinnitus.ears_noises_minutes_head,
+         tinnitus.ears_noises_minutes_head_frequency = tinnitus.ears_noises_minutes_head.1,
+         tinnitus.noises_worry_worst_upset
+         ) %>%
+  add_numeric(., exclude = exclude_cols) %>%
+  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
+  mutate_if(is.numeric, ~na_if(., -99)) %>%
+  mutate_if(is.numeric, ~na_if(., -77)) %>%
+  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
+  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
+
+# Inspect dimensions
+dim(nbr.tinnitus.raw.id)
+# Inspect colnames
+colnames(nbr.tinnitus.raw.id)
+#Differences
+dim(nbr.tinnitus.raw)[1]-dim(nbr.tinnitus.raw.id)[1]
+}
+```
+
+```{r nbr copy tinnitus}
+if(NBR == TRUE){
+tinnitus.raw.id <- nbr.tinnitus.raw.id
+}
+```
+
+### RAMP
+Read in data
+```{r ramp tinnitus cols}
+if(RAMP == TRUE){
+ramp.tinnitus.raw <- readRDS(file = paste0(data.raw_path, "/ramp/tinnitus_ramp.rds"))
+dim(ramp.tinnitus.raw)
+colnames(ramp.tinnitus.raw)
+}
+```
+
+Select variables
+```{r ramp tinnitus cleaning}
+if(RAMP == TRUE){
+
+ramp.tinnitus.raw.id <- ramp.tinnitus.raw %>%
+  drop_na(`Login ID`) %>% # Drop NAs
+  distinct(`Login ID`, .keep_all = TRUE) %>% # Remove duplicates based on ID
+  separate(`Login ID`, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
+  mutate(ID = as.numeric(ID)) %>%
+  select(
+         Sample, # Sample
+         ID, # ID
+         tinnitus.ears_noises_minutes_head,
+         tinnitus.ears_noises_minutes_head_frequency = tinnitus.lasts_ears_noises_minutes,
+         tinnitus.noises_worry_worst_upset = tinnitus.noises_worry_worst_annoy
+         ) %>%
+  add_numeric(., exclude = exclude_cols) %>%
+  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
+  mutate_if(is.numeric, ~na_if(., -99)) %>%
+  mutate_if(is.numeric, ~na_if(., -77)) %>%
+  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
+  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
+  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
+  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
+
+# Inspect dimensions
+dim(ramp.tinnitus.raw.id)
+# Inspect colnames
+colnames(ramp.tinnitus.raw.id)
+#Differences
+dim(ramp.tinnitus.raw)[1]-dim(ramp.tinnitus.raw.id)[1]
+}
+```
+
+```{r ramp copy tinnitus}
+if(RAMP == TRUE){
+tinnitus.raw.id <- ramp.tinnitus.raw.id
+}
+```
+
 # Join tibbles together
@@
   coping.pcl.raw.id,
-  coping.phq.raw.id
-#  coping.ocir.raw.id
+  coping.phq.raw.id,
+#  coping.ocir.raw.id,
+  als.raw.id,
+  ess.raw.id,
+  midas.raw.id,
+  nmss.raw.id,
+  nmsw.raw.id,
+  tinnitus.raw.id
 )

### 2020-09-10 PANCHANGE_data_preprocessing2020-07-15.Rmd
fixed NAs

@@
          ) %>%
+  add_numeric(., exclude = exclude_cols) %>%
     add_column(
-    ess.insomnia = NA_real_,
-    ess.narcolepsy = NA_real_,
-    ess.rem_sleep_behaviour_disorder = NA_real_,
-    ess.restless_legs_syndrome = NA_real_,
-    ess.sleep_apnea = NA_real_,
-    ess.sleep_terrors = NA_real_,
-    ess.sleepwalking = NA_real_,
-    ess.other = NA_real_,
-    ess.none = NA_real_
+    ess.insomnia = NA_character_,
+    ess.narcolepsy = NA_character_,
+    ess.rem_sleep_behaviour_disorder = NA_character_,
+    ess.restless_legs_syndrome = NA_character_,
+    ess.sleep_apnea = NA_character_,
+    ess.sleep_terrors = NA_character_,
+    ess.sleepwalking = NA_character_,
+    ess.other = NA_character_,
+    ess.none = NA_character_,
+    ess.insomnia_numeric = NA_real_,
+    ess.narcolepsy_numeric = NA_real_,
+    ess.rem_sleep_behaviour_disorder_numeric = NA_real_,
+    ess.restless_legs_syndrome_numeric = NA_real_,
+    ess.sleep_apnea_numeric = NA_real_,
+    ess.sleep_terrors_numeric = NA_real_,
+    ess.sleepwalking_numeric = NA_real_,
+    ess.other_numeric = NA_real_,
+    ess.none_numeric = NA_real_
     ) %>%
-  add_numeric(., exclude = exclude_cols) %>%
   mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables

### 2020-09-10 PANCHANGE_data_preprocessing2020-07-15.Rmd
added comment about edgi ocir coping missing ID

@@
   coping.phq.raw.id,
-#  coping.ocir.raw.id,
+#  coping.ocir.raw.id, # joint in the chunk before because it was missing the EDGI ID in any column
   als.raw.id,

### 2020-09-10 PANCHANGE_analysis.Rmd
added comment about edgi ocir coping missing ID
PANNEURO script and neuro chunks in analysis script

@@
 
+# COVID
+## Recode variable
+```{r covid test positive double}
+dat.raw <- dat.raw %>%
+  mutate(covid_test_positive_double_numeric =
+           case_when(
+             (respiratory.throat_swab_test_nose_numeric == 1 &
+               respiratory.results_antibody_test_numeric == 1) ~ 2,
+             respiratory.throat_swab_test_nose_numeric == 1 ~ 1,
+             respiratory.throat_swab_test_nose_numeric == 2 ~ 0,
+             respiratory.results_antibody_test_numeric == 1 ~ 1,
+             respiratory.results_antibody_test_numeric == 2 ~ 0
+           )
+         )
+
+dat.raw <- dat.raw %>%
+  mutate(covid_test_positive_double =
+           recode_factor(
+             covid_test_positive_double_numeric,
+             `0` = "Negative",
+             `1` = "Positive",
+             `2` = "Double positive"
+           )
+         )
+
+dat.raw %>%
+  freq(covid_test_positive_double)
+```
+
+```{r gad covid test positive}
+dat.raw <- dat.raw %>%
+  mutate(gad.covid_test_positive_numeric =
+           case_when(
+             (respiratory.throat_swab_test_nose_numeric == 1 &
+               respiratory.results_antibody_test_numeric == 1) ~ 1, # with two positive test results get coded as positive
+             respiratory.throat_swab_test_nose_numeric == 1 ~ 1,
+             respiratory.throat_swab_test_nose_numeric == 2 ~ 0,
+             respiratory.results_antibody_test_numeric == 1 ~ 1,
+             respiratory.results_antibody_test_numeric == 2 ~ 0
+           )
+         )
+
+dat.raw <- dat.raw %>%
+  mutate(covid_test_positive =
+           recode_factor(
+             gad.covid_test_positive_numeric,
+             `0` = "Negative",
+             `1` = "Positive"
+#             `2` = "Double positive"
+           )
+         )
+
+dat.raw %>%
+  freq(covid_test_positive)
+```
+
+## COVID swab test positive
+```{r COVID positive swap}
+dat.raw %>%
+  count(respiratory.throat_swab_test_nose, Sample) %>%
+  mutate(Prop = round(n/sum(n), 2))
+```
+
+## antibody test
+```{r COVID positive antibody test}
+dat.raw %>%
+  count(respiratory.results_antibody_test, Sample) %>%
+  mutate(Prop = round(n/sum(n), 2))
+```
+
+## COVID probable diagnosis
+```{r COVID probable diagnosis}
+dat.raw %>%
+  count(covid_probable_case_incl_screening, Sample) %>%
+  mutate(Prop = round(n/sum(n), 2))
+```
+
+## Cross table probable covid and covid test positive
+```{r Cross table probable covid and covid test positive}
+dat.raw %>%
+  count(covid_test_positive, covid_probable_case_incl_screening) %>%
+  spread(key = covid_test_positive, value = n)
+```
+
+# Neurological frequencies
+
+```{r neurological frequencies}
+dat.raw %>%
+  filter(!is.na(startDate.coping)) %>%
+  filter(!is.na(covid_test_positive)) %>%
+  group_by(covid_test_positive) %>%
+  select(
+    starts_with("alsfrs"),
+    -ends_with("numeric")
+  ) %>% 
+  colnames()
+```
+
+alsfrs.limb_weakness_noticed_past,
+alsfrs.normal,
+alsfrs.slow_or_sloppy_all_words_are_legible,
+alsfrs.not_all_words_are_legible,
+alsfrs.able_to_grip_pen,
+alsfrs.unable_to_grip_pen,
+alsfrs.have_you_noticed_any_difficulty_walking,
+alsfrs.do_you_have_any_difficulty_climbing_stairs
+
+```{r neurological frequencies alsfrs.limb_weakness_noticed_past}
+dat.raw %>%
+  filter(!is.na(startDate.coping)) %>%
+  filter(!is.na(covid_test_positive)) %>%
+  filter(!is.na(alsfrs.limb_weakness_noticed_past)) %>%
+  count(covid_test_positive, alsfrs.limb_weakness_noticed_past) %>%
+  mutate(Prop = round(n/sum(n), 2))
+```
+
+```{r neurological frequencies alsfrs.normal}
+dat.raw %>%
+  filter(!is.na(startDate.coping)) %>%
+  filter(!is.na(covid_test_positive)) %>%
+  filter(!is.na(alsfrs.normal)) %>%
+  group_by(covid_test_positive) %>%
+  count(covid_test_positive, alsfrs.normal) %>%
+  mutate(Prop = round(n/sum(n), 2))
+```
+
+```{r neurological frequencies alsfrs.slow_or_sloppy_all_words_are_legible}
+dat.raw %>%
+  filter(!is.na(startDate.coping)) %>%
+  filter(!is.na(covid_test_positive)) %>%
+  filter(!is.na(alsfrs.slow_or_sloppy_all_words_are_legible)) %>%
+  group_by(covid_test_positive) %>%
+  count(covid_test_positive, alsfrs.slow_or_sloppy_all_words_are_legible) %>%
+  mutate(Prop = round(n/sum(n), 2))
+```
+
+```{r neurological frequencies alsfrs.not_all_words_are_legible}
+dat.raw %>%
+  filter(!is.na(startDate.coping)) %>%
+  filter(!is.na(covid_test_positive)) %>%
+  filter(!is.na(alsfrs.not_all_words_are_legible)) %>%
+  group_by(covid_test_positive) %>%
+  count(covid_test_positive, alsfrs.not_all_words_are_legible) %>%
+  mutate(Prop = round(n/sum(n), 2))
+```
+
+```{r neurological frequencies alsfrs.able_to_grip_pen}
+dat.raw %>%
+  filter(!is.na(startDate.coping)) %>%
+  filter(!is.na(covid_test_positive)) %>%
+  filter(!is.na(alsfrs.able_to_grip_pen)) %>%
+  group_by(covid_test_positive) %>%
+  count(covid_test_positive, alsfrs.able_to_grip_pen) %>%
+  mutate(Prop = round(n/sum(n), 2))
+```
+
+```{r neurological frequencies alsfrs.unable_to_grip_pen}
+dat.raw %>%
+  filter(!is.na(startDate.coping)) %>%
+  filter(!is.na(covid_test_positive)) %>%
+  filter(!is.na(alsfrs.unable_to_grip_pen)) %>%
+  group_by(covid_test_positive) %>%
+  count(covid_test_positive, alsfrs.unable_to_grip_pen) %>%
+  mutate(Prop = round(n/sum(n), 2))
+```
+
+```{r neurological frequencies alsfrs.have_you_noticed_any_difficulty_walking}
+dat.raw %>%
+  filter(!is.na(startDate.coping)) %>%
+  filter(!is.na(covid_test_positive)) %>%
+  filter(!is.na(alsfrs.have_you_noticed_any_difficulty_walking)) %>%
+  group_by(covid_test_positive) %>%
+  count(covid_test_positive, alsfrs.have_you_noticed_any_difficulty_walking) %>%
+  mutate(Prop = round(n/sum(n), 2))
+```
+
+```{r neurological frequencies alsfrs.do_you_have_any_difficulty_climbing_stairs}
+dat.raw %>%
+  filter(!is.na(startDate.coping)) %>%
+  filter(!is.na(covid_test_positive)) %>%
+  filter(!is.na(alsfrs.do_you_have_any_difficulty_climbing_stairs)) %>%
+  group_by(covid_test_positive) %>%
+  count(covid_test_positive, alsfrs.do_you_have_any_difficulty_climbing_stairs) %>%
+  mutate(Prop = round(n/sum(n), 2))
+```
+
+```{r neurological frequencies ess}
+dat.raw %>%
+  filter(!is.na(startDate.coping)) %>%
+  filter(!is.na(covid_test_positive)) %>%
+  group_by(covid_test_positive) %>%
+  select(
+    starts_with("ess"),
+    -ends_with("numeric")
+  ) %>% 
+  colnames()
+```
+
+```{r neurological frequencies ess.felt_excessively_sleepy_past}
+dat.raw %>%
+  filter(!is.na(startDate.coping)) %>%
+  filter(!is.na(covid_test_positive)) %>%
+  filter(!is.na(ess.felt_excessively_sleepy_past)) %>%
+  group_by(covid_test_positive) %>%
+  count(covid_test_positive, ess.felt_excessively_sleepy_past) %>%
+  mutate(Prop = round(n/sum(n), 2))
+```
+
+```{r neurological frequencies ess.sitting_and_reading}
+dat.raw %>%
+  filter(!is.na(startDate.coping)) %>%
+  filter(!is.na(covid_test_positive)) %>%
+  filter(!is.na(ess.sitting_and_reading)) %>%
+  group_by(covid_test_positive) %>%
+  count(covid_test_positive, ess.sitting_and_reading) %>%
+  mutate(Prop = round(n/sum(n), 2))
+```
+
+```{r neurological frequencies ess.watching_tv}
+dat.raw %>%
+  filter(!is.na(startDate.coping)) %>%
+  filter(!is.na(covid_test_positive)) %>%
+  filter(!is.na(ess.watching_tv)) %>%
+  group_by(covid_test_positive) %>%
+  count(covid_test_positive, ess.watching_tv) %>%
+  mutate(Prop = round(n/sum(n), 2))
+```
+
+```{r neurological frequencies ess.sitting_inactive_in_a_public_place}
+dat.raw %>%
+  filter(!is.na(startDate.coping)) %>%
+  filter(!is.na(covid_test_positive)) %>%
+  filter(!is.na(ess.sitting_inactive_in_a_public_place)) %>%
+  group_by(covid_test_positive) %>%
+  count(covid_test_positive, ess.sitting_inactive_in_a_public_place) %>%
+  mutate(Prop = round(n/sum(n), 2))
+```
+
+```{r neurological frequencies ess.break_passenger_car_hour}
+dat.raw %>%
+  filter(!is.na(startDate.coping)) %>%
+  filter(!is.na(covid_test_positive)) %>%
+  filter(!is.na(ess.break_passenger_car_hour)) %>%
+  group_by(covid_test_positive) %>%
+  count(covid_test_positive, ess.break_passenger_car_hour) %>%
+  mutate(Prop = round(n/sum(n), 2))
+```
+
+```{r neurological frequencies ess.afternoon_rest_circumstances_lying}
+dat.raw %>%
+  filter(!is.na(startDate.coping)) %>%
+  filter(!is.na(covid_test_positive)) %>%
+  filter(!is.na(ess.afternoon_rest_circumstances_lying)) %>%
+  group_by(covid_test_positive) %>%
+  count(covid_test_positive, ess.afternoon_rest_circumstances_lying) %>%
+  mutate(Prop = round(n/sum(n), 2))
+```
+
+```{r neurological frequencies ess.sitting_and_talking_to_someone}
+dat.raw %>%
+  filter(!is.na(startDate.coping)) %>%
+  filter(!is.na(covid_test_positive)) %>%
+  filter(!is.na(ess.sitting_and_talking_to_someone)) %>%
+  group_by(covid_test_positive) %>%
+  count(covid_test_positive, ess.sitting_and_talking_to_someone) %>%
+  mutate(Prop = round(n/sum(n), 2))
+```
+
+```{r neurological frequencies ess.sitting_quietly_after_a_lunch_without_alcohol}
+dat.raw %>%
+  filter(!is.na(startDate.coping)) %>%
+  filter(!is.na(covid_test_positive)) %>%
+  filter(!is.na(ess.sitting_quietly_after_a_lunch_without_alcohol)) %>%
+  group_by(covid_test_positive) %>%
+  count(covid_test_positive, ess.sitting_quietly_after_a_lunch_without_alcohol) %>%
+  mutate(Prop = round(n/sum(n), 2))
+```
+
+```{r neurological frequencies ess.car_minutes_stopped_traffic}
+dat.raw %>%
+  filter(!is.na(startDate.coping)) %>%
+  filter(!is.na(covid_test_positive)) %>%
+  filter(!is.na(ess.car_minutes_stopped_traffic)) %>%
+  group_by(covid_test_positive) %>%
+  count(covid_test_positive, ess.car_minutes_stopped_traffic) %>%
+  mutate(Prop = round(n/sum(n), 2))
+```
+
+```{r neurological frequencies ess.insomnia}
+dat.raw %>%
+  filter(!is.na(startDate.coping)) %>%
+  filter(!is.na(covid_test_positive)) %>%
+  filter(!is.na(ess.insomnia)) %>%
+  group_by(covid_test_positive) %>%
+  count(covid_test_positive, ess.insomnia) %>%
+  mutate(Prop = round(n/sum(n), 2))
+```
+
+```{r neurological frequencies ess.narcolepsy}
+dat.raw %>%
+  filter(!is.na(startDate.coping)) %>%
+  filter(!is.na(covid_test_positive)) %>%
+  filter(!is.na(ess.narcolepsy)) %>%
+  group_by(covid_test_positive) %>%
+  count(covid_test_positive, ess.narcolepsy) %>%
+  mutate(Prop = round(n/sum(n), 2))
+```
+
+```{r neurological frequencies ess.rem_sleep_behaviour_disorder}
+dat.raw %>%
+  filter(!is.na(startDate.coping)) %>%
+  filter(!is.na(covid_test_positive)) %>%
+  filter(!is.na(ess.rem_sleep_behaviour_disorder)) %>%
+  group_by(covid_test_positive) %>%
+  count(covid_test_positive, ess.rem_sleep_behaviour_disorder) %>%
+  mutate(Prop = round(n/sum(n), 2))
+```
+
+```{r neurological frequencies ess.restless_legs_syndrome}
+dat.raw %>%
+  filter(!is.na(startDate.coping)) %>%
+  filter(!is.na(covid_test_positive)) %>%
+  filter(!is.na(ess.restless_legs_syndrome)) %>%
+  group_by(covid_test_positive) %>%
+  count(covid_test_positive, ess.restless_legs_syndrome) %>%
+  mutate(Prop = round(n/sum(n), 2))
+```
+
+```{r neurological frequencies ess.sleep_apnea}
+dat.raw %>%
+  filter(!is.na(startDate.coping)) %>%
+  filter(!is.na(covid_test_positive)) %>%
+  filter(!is.na(ess.sleep_apnea)) %>%
+  group_by(covid_test_positive) %>%
+  count(covid_test_positive, ess.sleep_apnea) %>%
+  mutate(Prop = round(n/sum(n), 2))
+```
+
+```{r neurological frequencies ess.sleep_terrors}
+dat.raw %>%
+  filter(!is.na(startDate.coping)) %>%
+  filter(!is.na(covid_test_positive)) %>%
+  filter(!is.na(ess.sleep_terrors)) %>%
+  group_by(covid_test_positive) %>%
+  count(covid_test_positive, ess.sleep_terrors) %>%
+  mutate(Prop = round(n/sum(n), 2))
+```
+
+```{r neurological frequencies ess.sleepwalking}
+dat.raw %>%
+  filter(!is.na(startDate.coping)) %>%
+  filter(!is.na(covid_test_positive)) %>%
+  filter(!is.na(ess.sleepwalking)) %>%
+  group_by(covid_test_positive) %>%
+  count(covid_test_positive, ess.sleepwalking) %>%
+  mutate(Prop = round(n/sum(n), 2))
+```
+
+```{r neurological frequencies ess.other}
+dat.raw %>%
+  filter(!is.na(startDate.coping)) %>%
+  filter(!is.na(covid_test_positive)) %>%
+  filter(!is.na(ess.other)) %>%
+  group_by(covid_test_positive) %>%
+  count(covid_test_positive, ess.other) %>%
+  mutate(Prop = round(n/sum(n), 2))
+```
+
+```{r neurological frequencies ess.none}
+dat.raw %>%
+  filter(!is.na(startDate.coping)) %>%
+  filter(!is.na(covid_test_positive)) %>%
+  filter(!is.na(ess.none)) %>%
+  group_by(covid_test_positive) %>%
+  count(covid_test_positive, ess.none) %>%
+  mutate(Prop = round(n/sum(n), 2))
+```
+
+```{r neurological frequencies midas}
+dat.raw %>%
+  filter(!is.na(startDate.coping)) %>%
+  filter(!is.na(covid_test_positive)) %>%
+  group_by(covid_test_positive) %>%
+  select(
+    starts_with("midas"),
+    -ends_with("numeric")
+  ) %>% 
+  colnames()
+```
+
+```{r neurological frequencies midas.headaches_suffered_past_month}
+dat.raw %>%
+  filter(!is.na(startDate.coping)) %>%
+  filter(!is.na(covid_test_positive)) %>%
+  filter(!is.na(midas.headaches_suffered_past_month)) %>%
+  group_by(covid_test_positive) %>%
+  count(covid_test_positive, midas.headaches_suffered_past_month) %>%
+  mutate(Prop = round(n/sum(n), 2))
+```
+
+```{r neurological frequencies midas.days_past_month_miss_work_school}
+dat.raw %>%
+  filter(!is.na(startDate.coping)) %>%
+  filter(!is.na(covid_test_positive)) %>%
+  filter(!is.na(midas.days_past_month_miss_work_school)) %>%
+  group_by(covid_test_positive) %>%
+  count(covid_test_positive, midas.days_past_month_miss_work_school) %>%
+  mutate(Prop = round(n/sum(n), 2))
+```
+
+```{r neurological frequencies midas.days_past_month_work_school_half_productivity}
+dat.raw %>%
+  filter(!is.na(startDate.coping)) %>%
+  filter(!is.na(covid_test_positive)) %>%
+  filter(!is.na(midas.days_past_month_work_school_half_productivity)) %>%
+  group_by(covid_test_positive) %>%
+  count(covid_test_positive, midas.days_past_month_work_school_half_productivity) %>%
+  mutate(Prop = round(n/sum(n), 2))
+```
+
+```{r neurological frequencies midas.days_past_month_miss_housework}
+dat.raw %>%
+  filter(!is.na(startDate.coping)) %>%
+  filter(!is.na(covid_test_positive)) %>%
+  filter(!is.na(midas.days_past_month_miss_housework)) %>%
+  group_by(covid_test_positive) %>%
+  count(covid_test_positive, midas.days_past_month_miss_housework) %>%
+  mutate(Prop = round(n/sum(n), 2))
+```
+
+```{r neurological frequencies midas.days_past_month_housework_half_productivity}
+dat.raw %>%
+  filter(!is.na(startDate.coping)) %>%
+  filter(!is.na(covid_test_positive)) %>%
+  filter(!is.na(midas.days_past_month_housework_half_productivity)) %>%
+  group_by(covid_test_positive) %>%
+  count(covid_test_positive, midas.days_past_month_housework_half_productivity) %>%
+  mutate(Prop = round(n/sum(n), 2))
+```
+
+```{r neurological frequencies midas.days_past_month_miss_social_activities}
+dat.raw %>%
+  filter(!is.na(startDate.coping)) %>%
+  filter(!is.na(covid_test_positive)) %>%
+  filter(!is.na(midas.days_past_month_miss_social_activities)) %>%
+  group_by(covid_test_positive) %>%
+  count(covid_test_positive, midas.days_past_month_miss_social_activities) %>%
+  mutate(Prop = round(n/sum(n), 2))
+```
+
+```{r neurological frequencies}
+dat.raw %>%
+  filter(!is.na(startDate.coping)) %>%
+  filter(!is.na(covid_test_positive)) %>%
+  group_by(covid_test_positive) %>%
+  select(
+    starts_with("nmss"),
+    -ends_with("numeric")
+  ) %>% 
+  colnames()
+```
+
+```{r neurological frequencies nmss.ability_taste_food_smell}
+dat.raw %>%
+  filter(!is.na(startDate.coping)) %>%
+  filter(!is.na(covid_test_positive)) %>%
+  filter(!is.na(nmss.ability_taste_food_smell)) %>%
+  group_by(covid_test_positive) %>%
+  count(covid_test_positive, nmss.ability_taste_food_smell) %>%
+  mutate(Prop = round(n/sum(n), 2))
+```
+
+```{r neurological frequencies nmss.severe_taste_smell_loss}
+dat.raw %>%
+  filter(!is.na(startDate.coping)) %>%
+  filter(!is.na(covid_test_positive)) %>%
+  filter(!is.na(nmss.severe_taste_smell_loss)) %>%
+  group_by(covid_test_positive) %>%
+  count(covid_test_positive, nmss.severe_taste_smell_loss) %>%
+  mutate(Prop = round(n/sum(n), 2))
+```
+
+```{r neurological frequencies}
+dat.raw %>%
+  filter(!is.na(startDate.coping)) %>%
+  filter(!is.na(covid_test_positive)) %>%
+  group_by(covid_test_positive) %>%
+  select(
+    starts_with("nmsw"),
+    -ends_with("numeric")
+  ) %>% 
+  colnames()
+```
+
+```{r neurological frequencies nmsw.drink_problems_choking_difficulty}
+dat.raw %>%
+  filter(!is.na(startDate.coping)) %>%
+  filter(!is.na(covid_test_positive)) %>%
+  filter(!is.na(nmsw.drink_problems_choking_difficulty)) %>%
+  group_by(covid_test_positive) %>%
+  count(covid_test_positive, nmsw.drink_problems_choking_difficulty) %>%
+  mutate(Prop = round(n/sum(n), 2))
+```
+
+```{r neurological frequencies nmsw.regularly_night_pass_urine}
+dat.raw %>%
+  filter(!is.na(startDate.coping)) %>%
+  filter(!is.na(covid_test_positive)) %>%
+  filter(!is.na(nmsw.regularly_night_pass_urine)) %>%
+  group_by(covid_test_positive) %>%
+  count(covid_test_positive, nmsw.regularly_night_pass_urine) %>%
+  mutate(Prop = round(n/sum(n), 2))
+```
+
+```{r neurological frequencies nmsw.sex_difficult_finding}
+dat.raw %>%
+  filter(!is.na(startDate.coping)) %>%
+  filter(!is.na(covid_test_positive)) %>%
+  filter(!is.na(nmsw.sex_difficult_finding)) %>%
+  group_by(covid_test_positive) %>%
+  count(covid_test_positive, nmsw.sex_difficult_finding) %>%
+  mutate(Prop = round(n/sum(n), 2))
+```
+
+```{r neurological frequencies nmsw.weak_standing_feeling_light}
+dat.raw %>%
+  filter(!is.na(startDate.coping)) %>%
+  filter(!is.na(covid_test_positive)) %>%
+  filter(!is.na(nmsw.weak_standing_feeling_light)) %>%
+  group_by(covid_test_positive) %>%
+  count(covid_test_positive, nmsw.weak_standing_feeling_light) %>%
+  mutate(Prop = round(n/sum(n), 2))
+```
+
+```{r neurological frequencies nmsw.acting_moving_sleep_talking}
+dat.raw %>%
+  filter(!is.na(startDate.coping)) %>%
+  filter(!is.na(covid_test_positive)) %>%
+  filter(!is.na(nmsw.acting_moving_sleep_talking)) %>%
+  group_by(covid_test_positive) %>%
+  count(covid_test_positive, nmsw.acting_moving_sleep_talking) %>%
+  mutate(Prop = round(n/sum(n), 2))
+```
+
+```{r neurological frequencies nmsw.double_vision}
+dat.raw %>%
+  filter(!is.na(startDate.coping)) %>%
+  filter(!is.na(covid_test_positive)) %>%
+  filter(!is.na(nmsw.double_vision)) %>%
+  group_by(covid_test_positive) %>%
+  count(covid_test_positive, nmsw.double_vision) %>%
+  mutate(Prop = round(n/sum(n), 2))
+```
+
+```{r neurological frequencies}
+dat.raw %>%
+  filter(!is.na(startDate.coping)) %>%
+  filter(!is.na(covid_test_positive)) %>%
+  group_by(covid_test_positive) %>%
+  select(
+    starts_with("tinnitus"),
+    -ends_with("numeric")
+  ) %>% 
+  colnames()
+```
+
+```{r neurological frequencies tinnitus.ears_noises_minutes_head}
+dat.raw %>%
+  filter(!is.na(startDate.coping)) %>%
+  filter(!is.na(covid_test_positive)) %>%
+  filter(!is.na(tinnitus.ears_noises_minutes_head)) %>%
+  group_by(covid_test_positive) %>%
+  count(covid_test_positive, tinnitus.ears_noises_minutes_head) %>%
+  mutate(Prop = round(n/sum(n), 2))
+```
+
+```{r neurological frequencies tinnitus.ears_noises_minutes_head_frequency}
+dat.raw %>%
+  filter(!is.na(startDate.coping)) %>%
+  filter(!is.na(covid_test_positive)) %>%
+  filter(!is.na(tinnitus.ears_noises_minutes_head_frequency)) %>%
+  group_by(covid_test_positive) %>%
+  count(covid_test_positive, tinnitus.ears_noises_minutes_head_frequency) %>%
+  mutate(Prop = round(n/sum(n), 2))
+```
+
+```{r neurological frequencies tinnitus.noises_worry_worst_upset}
+dat.raw %>%
+  filter(!is.na(startDate.coping)) %>%
+  filter(!is.na(covid_test_positive)) %>%
+  filter(!is.na(tinnitus.noises_worry_worst_upset)) %>%
+  group_by(covid_test_positive) %>%
+  count(covid_test_positive, tinnitus.noises_worry_worst_upset) %>%
+  mutate(Prop = round(n/sum(n), 2))
+```
+
+# Ethnicity_collapsed
+```{r Ethnicity_collapsed per Sample prop per total}
+Ethnicity_collapsed_per_Sample_prop_total <- dat %>%
+  count(Ethnicity_collapsed, Sample) %>%
+  mutate(Prop = round(n/sum(n), 2))
+
+kable(Ethnicity_collapsed_per_Sample_prop_total)
+Ethnicity_collapsed_per_Sample_prop_total
+```
+
 # Exclusions
@@
 
-++MD: There's an issue with the EDGI obsessive_compulsive_disorders variable. There are >400 NAs so we are only left with 78 EDGI participants in the dataset.
 ```{r exclusion criteria for diagnoses analysis}

### 2020-09-10 PANNEURO_analysis.Rmd
PANNEURO script and neuro chunks in analysis script

--- 2020-09-10 PANCHANGE_analysis.Rmd
@@
 ---
-title: "PANCHANGE_analysis"
-author: "Katie Thompson, Topher Huebel, Molly Davies, Kirstin Purves"
-date: Sys.Date()
+title: "PANNEURO_analysis"
+author: "Christopher Huebel"
+date: "Sys.Date()"
 output:
+  word_document:
+    toc: yes
+    toc_depth: '2'
+  pdf_document:
+    toc: yes
+    toc_depth: '2'
   html_document:
     df_print: paged
+    highlight: monochrome
+    number_sections: no
+    theme: cerulean
     toc: yes
@@
     toc_float:
-      collapsed: false
-    number_sections: false
-    highlight: monochrome
+      collapsed: no
+html_notebook:
   theme: cerulean
 code_folding: show
-
-html_notebook:
-  theme: cerulean
 toc: yes
@@
 
-This is the analysis script to prepare the data to run analyses for the project "Anxiety, depression and trauma symptom change during the COVID-19 pandemic: retrospective versus objective assessment" - Young et al (2020)
-
-Script written by K Purves, K Thompson, C Huebel and M Davies.
-Email: kirstin.purves@kcl.ac.uk, katie.thompson@kcl.ac.uk, christopher.1.huebel@kcl.ac.uk, molly.davies@kcl.ac.uk
+Frequencies of neurological symptoms in participants of the COPING/RAMP studies
+
+Filtered by participants that self-reported a swap or antibody test
+
+and that answered the neurological questionnaire
+
+Script written by C Huebel
+Email: christopher.1.huebel@kcl.ac.uk
 
@@
 
-```{r neurological frequencies}
+```{r neurological frequencies alsfrs}
 dat.raw %>%
@@
 
-```{r neurological frequencies}
+```{r neurological frequencies nmss}
 dat.raw %>%
@@
 
-```{r neurological frequencies}
+```{r neurological frequencies nmsw}
 dat.raw %>%
@@
 
-```{r neurological frequencies}
+```{r neurological frequencies tinnitus}
 dat.raw %>%
@@
 ```
-
-# Ethnicity_collapsed
-```{r Ethnicity_collapsed per Sample prop per total}
-Ethnicity_collapsed_per_Sample_prop_total <- dat %>%
-  count(Ethnicity_collapsed, Sample) %>%
-  mutate(Prop = round(n/sum(n), 2))
-
-kable(Ethnicity_collapsed_per_Sample_prop_total)
-Ethnicity_collapsed_per_Sample_prop_total
-```
-
-# Exclusions
-
-Exclude GLAD/EDGI individuals that didn't take part in COPING
-Exclude individuals with NA for the MHD categories
-Individuals with NAs for age/gender have already been excluded in pre-processing script.
-
-```{r exclusion criteria for diagnoses analysis}
-dat <- dat.raw %>%
-  filter(
-    !is.na(depressive_disorders) &
-      !is.na(eating_disorders) &
-      !is.na(psychotic_disorders) &
-      !is.na(obsessive_compulsive_disorders) &
-      !is.na(autism_spectrum_disorder) &
-      !is.na(mhd.mania_hypomania_bipolar_or_manicdepression_numeric) &
-      !is.na(mhd.posttraumatic_stress_disorder_ptsd_numeric) &
-      !is.na(control)
-  ) %>% 
-  drop_na(startDate.coping)
-
-dim(dat.raw)
-dim(dat)
-
-```
-
-# Collapsing categories
-
-## age_category
-```{r Inspect age_category}
-dat %>%
-  freq(age_category)
-
-dat %>%
-  freq(age_category_numeric)
-```
-
-```{r Collapse age_category}
-dat <- dat %>%
-  mutate(age_category_collapsed_numeric =
-           case_when(
-             age_category_numeric == 1 ~ 0,
-             age_category_numeric == 2 ~ 1,
-             age_category_numeric == 3 ~ 2,
-             age_category_numeric == 4 ~ 3,
-             age_category_numeric == 5 ~ 4,
-             age_category_numeric == 6 ~ 5,
-             age_category_numeric == 7 ~ 6,
-             age_category_numeric == 8 ~ 7,
-             age_category_numeric == 9 ~ 8,
-             age_category_numeric == 10 ~ 8,
-             age_category_numeric == 11 ~ 8,
-             age_category_numeric == 12 ~ 8,
-             age_category_numeric == 13 ~ 8
-
-           )
-  )
-
-dat <- dat %>%
-  mutate(age_category_collapsed =
-           recode_factor(
-             age_category_collapsed_numeric,
-             `0` = "16-18",
-             `1` = "19-25",
-             `2` = "26-35",
-             `3` = "36-45",
-             `4` = "46-55",
-             `5` = "56-65",
-             `6` = "66-70",
-             `7` = "71-75",
-             `8` = "76+"
-           )
-  )
-
-dat %>%
-  freq(age_category_collapsed)
-```
-
-## Gender
-```{r Inspect Gender}
-dat %>%
-  freq(Gender)
-
-dat %>%
-  freq(Gender_numeric)
-```
-
-```{r Collapse Gender}
-dat <- dat %>%
-  mutate(Gender_collapsed_numeric =
-           case_when(
-             Gender_numeric == 0 ~ 0,
-             Gender_numeric == 1 ~ 1,
-             Gender_numeric == 2 ~ 2,
-             Gender_numeric == 3 ~ 2
-           )
-         )
-
-dat <- dat %>%
-  mutate(Gender_collapsed =
-           recode_factor(
-             Gender_collapsed_numeric,
-             `0` = "Male",
-             `1` = "Female",
-             `2` = "Non-binary/Self-defined"
-           )
-         )
-
-dat %>%
-  freq(Gender_collapsed)
-```
-
-## Ethnicity
-++MD: The ethnicity_numeric variable has more NAs (N = 14304) than the ethnicity categorical variable (N = 3568). Something strange must have happened during the conversion to numeric?
-```{r Inspect Ethnicity}
-dat %>%
-  freq(Ethnicity)
-
-dat %>%
-  freq(Ethnicity_numeric)
-
-```
-
-++MD: Need to decide what to do with the Arab grouping.
-++MD: Why is "Other ethnic group" recoded as Asian or Asian British?
-```{r Collapse Ethnicity}
-dat <- dat %>%
-  mutate(Ethnicity_collapsed_numeric =
-           case_when(
-             Ethnicity_numeric == 1 ~ 0, #European
-             Ethnicity_numeric == 2 ~ 1, #Mixed or multiple ethnic origins 
-             Ethnicity_numeric == 3 ~ 2, #Asian or Asian British
-             Ethnicity_numeric == 4 ~ 3, #African or African British
-             Ethnicity_numeric == 5 ~ 3, #Arab - combined with African/African British
-             Ethnicity_numeric == 6 ~ 4  #Other ethnic group
-           )
-  )
-
-dat <- dat %>%
-  mutate(Ethnicity_collapsed =
-           recode_factor(
-             Ethnicity_collapsed_numeric,
-             `0` = "European",
-             `1` = "Mixed or multiple ethnic origins",
-             `2` = "Asian or Asian British",
-             `3` = "African or African British",
-             `4` = "Other"
-           )
-  )
-
-dat %>%
-  freq(Ethnicity_collapsed)
-```
-
-# Vectors for sum_score
-
-```{r Vectors with sum_score_cols}
-sum_score_cols <- dat %>%
-  select(contains("sum_score")) %>%
-  select(-ends_with("raw")) %>%
-  colnames()
-
-sum_score_cols
-
-phq.sum_score_cols <- dat %>%
-  select(contains("phq")) %>%
-  select(contains("sum_score")) %>% 
-  select(-ends_with("raw")) %>%
-  select(-contains("8items")) %>%
-  colnames()
-
-phq.sum_score_cols
-
-gad.sum_score_cols <- dat %>%
-  select(contains("gad")) %>%
-  select(contains("sum_score")) %>% 
-  select(-ends_with("raw")) %>%
-  colnames()
-
-gad.sum_score_cols
-
-ocir.sum_score_cols <- dat %>%
-  select(contains("ocir")) %>%
-  select(contains("sum_score")) %>% 
-  select(-ends_with("raw")) %>%
-  colnames()
-
-ocir.sum_score_cols
-
-pcl.sum_score_cols <- dat %>%
-  select(contains("pcl")) %>%
-  select(contains("sum_score")) %>% 
-  select(-ends_with("raw")) %>%
-  colnames()
-
-pcl.sum_score_cols
-```
-
-# Vectors for diff_score
-
-```{r Vectors with diff_score_cols}
-diff_score_cols <- dat %>%
-  select(contains("diff_score")) %>% 
-  colnames()
-
-diff_score_cols
-
-phq.diff_score_cols <- dat %>%
-  select(contains("phq")) %>%
-  select(contains("diff_score")) %>% 
-  colnames()
-
-phq.diff_score_cols
-
-gad.diff_score_cols <- dat %>%
-  select(contains("gad")) %>%
-  select(contains("diff_score")) %>% 
-  colnames()
-
-gad.diff_score_cols
-
-ocir.diff_score_cols <- dat %>%
-  select(contains("ocir")) %>%
-  select(contains("diff_score")) %>% 
-  colnames()
-
-ocir.diff_score_cols
-```
-
-# ggplot theme
-Set up ggplot theme for the plots
-```{r ggplot theme}
-theme_personal <-  theme(
-    text = element_text(color = "black"),
-    axis.title = element_text(color = "black"),
-    axis.text = element_text(color = "black"),
-    axis.title.y = element_blank(), 
-    legend.background = element_blank(),
-    legend.box.background = element_blank(),
-    panel.background = element_blank(), 
-    panel.grid.minor.x = element_blank(),
-    panel.grid.major.x = element_line(
-      colour = "gray",
-      linetype = "dashed",
-      size = 0.2
-      ),
-    axis.ticks = element_blank()
-    )
-```
-
-# Psychiatric disorder hierarchy
-- - - -
-OLD VERSIONS:
-control_numeric == 1 ~ 0,
-depressive_disorders_numeric == 1 ~ 1,
-anxiety_disorders_numeric == 1 ~ 2,
-mhd.posttraumatic_stress_disorder_ptsd_numeric == 1 ~ 3,
-eating_disorders_numeric == 1 ~ 4,
-obsessive_compulsive_disorders_numeric == 1 ~ 5,
-mhd.attention_deficit_hyperactivity_disorder_numeric == 1 ~ 6,
-mhd.personality_disorder_numeric == 1 ~ 7,
-autism_spectrum_disorder_numeric == 1 ~ 8,
-mhd.mania_hypomania_bipolar_or_manicdepression_numeric == 1 ~ 9,
-psychotic_disorders_numeric == 1 ~ 10
-
-psychotic_disorders_numeric == 1 ~ 10
-mhd.mania_hypomania_bipolar_or_manicdepression_numeric == 1 ~ 9,
-autism_spectrum_disorder_numeric == 1 ~ 8,
-mhd.personality_disorder_numeric == 1 ~ 7,
-mhd.attention_deficit_hyperactivity_disorder_numeric == 1 ~ 6,
-obsessive_compulsive_disorders_numeric == 1 ~ 5,
-eating_disorders_numeric == 1 ~ 4,
-mhd.posttraumatic_stress_disorder_ptsd_numeric == 1 ~ 3,
-anxiety_disorders_numeric == 1 ~ 2,
-depressive_disorders_numeric == 1 ~ 1,
-control_numeric == 1 ~ 0,
-- - - -
-
-Disorder hierarchy
-1: Psychotic disorders (create one with, create one without to test in analyses)
-2: Bipolar disorder
-3: MDD
-4: PTSD
-5: OCD
-6: Eating disorders
-7: Anxiety disorders
-
-```{r Psychiatric disorders hierarchy including psychosis}
-dat <- dat %>%
-  mutate(
-    Disorder_hierarchical_psychosis_numeric =
-      case_when(
-        psychotic_disorders_numeric == 1 ~ 7,
-        mhd.mania_hypomania_bipolar_or_manicdepression_numeric == 1 ~ 6,
-        depressive_disorders_numeric == 1 ~ 5,
-        mhd.posttraumatic_stress_disorder_ptsd_numeric == 1 ~ 4,
-        obsessive_compulsive_disorders_numeric == 1 ~ 3,
-        eating_disorders_numeric == 1 ~ 2,
-        anxiety_disorders_numeric == 1 ~ 1,
-        control_numeric == 1 ~ 0
-      )
-  )
-
-dat <- dat %>%
-  mutate(
-    Disorder_hierarchical_psychosis =
-      recode_factor(
-        Disorder_hierarchical_psychosis_numeric,
-        `0` = "Controls",
-        `1` = "Anxiety disorders",
-        `2` = "Eating disorders",
-        `3` = "OCDs",
-        `4` = "PTSD",
-        `5` = "Depressive disorders",
-        `6` = "Bipolar disorders",
-        `7` = "Psychotic disorders"
-      )
-  )
-
-dat %>%
-  freq(Disorder_hierarchical_psychosis)
-```
-
-```{r Psychiatric disorders hierarchy without psychosis}
-dat <- dat %>%
-  mutate(
-    Disorder_hierarchical_numeric =
-      case_when(
-        mhd.mania_hypomania_bipolar_or_manicdepression_numeric == 1 ~ 6,
-        depressive_disorders_numeric == 1 ~ 5,
-        mhd.posttraumatic_stress_disorder_ptsd_numeric == 1 ~ 4,
-        obsessive_compulsive_disorders_numeric == 1 ~ 3,
-        eating_disorders_numeric == 1 ~ 2,
-        anxiety_disorders_numeric == 1 ~ 1,
-        control_numeric == 1 ~ 0
-      )
-  )
-
-dat <- dat %>%
-  mutate(
-    Disorder_hierarchical =
-      recode_factor(
-        Disorder_hierarchical_numeric,
-        `0` = "Controls",
-        `1` = "Anxiety disorders",
-        `2` = "Eating disorders",
-        `3` = "OCDs",
-        `4` = "PTSD",
-        `5` = "Depressive disorders",
-        `6` = "Bipolar disorders"
-      )
-  )
-
-dat %>%
-  freq(Disorder_hierarchical) 
-dat %>% 
-  freq(Disorder_hierarchical_psychosis)
-```
-
-Investigate NAs 
-NAs are coded for individuals that don't have one of the listed disorders in the hierarchy, but who have another diagnosis that excludes them from being a control (e.g.
-personality disorder, ADHD, ASD).
-These individuals will be excluded from the analyses.
-```{r NAs in diagnosis}
-dat %>%
-  filter(is.na(Disorder_hierarchical)) %>%
-  freq(Sample)
-```
-
-Compare the GLAD/EDGI and COPING cohorts as a whole
-+++CH: Diagnosis, ethnicity, gender, age
-
-# age_category
-```{r age_category per Sample prop per total}
-age_category_per_Sample_prop_total <- dat %>%
-  count(age_category, Sample) %>%
-  mutate(Prop = round(n/sum(n), 2))
-
-kable(age_category_per_Sample_prop_total)
-age_category_per_Sample_prop_total
-```
-
-```{r age_category per Sample prop per Sample}
-age_category_per_Sample_prop_Sample <- dat %>%
-  group_by(Sample) %>%
-  count(age_category, Sample) %>%
-  mutate(Prop = round(n/sum(n), 2))
-
-kable(age_category_per_Sample_prop_Sample)
-age_category_per_Sample_prop_Sample
-```
-
-```{r age_category per Sample prop cross table}
-age_category_per_Sample_prop_Sample_cross_table <- dat %>%
-  group_by(Sample) %>%
-  count(age_category, Sample) %>%
-  mutate(Prop = round(n/sum(n), 2)) %>%
-  pivot_wider(names_from = Sample, values_from = c(n, Prop))
-
-kable(age_category_per_Sample_prop_Sample_cross_table)
-age_category_per_Sample_prop_Sample_cross_table
-```
-
-```{r age_category per Sample count cross table}
-age_category_per_Sample_count_cross_table <- dat %>%
-  count(age_category, Sample) %>%
-  spread(key = Sample, value = n) %>%
-  mutate(
-    EDGI = as.integer(replace_na(EDGI, 0)),
-    GLAD = as.integer(replace_na(GLAD, 0)),
-    NBR = as.integer(replace_na(NBR, 0)),
-    RAMP = as.integer(replace_na(RAMP, 0))
-  )
-
-kable(age_category_per_Sample_count_cross_table)
-age_category_per_Sample_count_cross_table
-```
-
-```{r age_category per Sample chisquare test}
-age_category_per_Sample_chissquare_test <- dat %>%
-  count(age_category, Sample) %>%
-  spread(key = Sample, value = n) %>%
-  select(-age_category) %>%
-  mutate(
-    EDGI = as.integer(replace_na(EDGI, 0)),
-    GLAD = as.integer(replace_na(GLAD, 0)),
-    NBR = as.integer(replace_na(NBR, 0)),
-    RAMP = as.integer(replace_na(RAMP, 0))
-  ) %>%
-  chisq.test() %>%
-  glance()
-
-kable(age_category_per_Sample_chissquare_test)
-age_category_per_Sample_chissquare_test
-```
-
-```{r age_category by Sample count plot}
-age_category_by_Sample_count_plot <- age_category_per_Sample_prop_Sample %>%
-  ggplot(mapping = aes(
-    x = age_category,
-    y = n)
-  ) +
-  geom_bar(
-    aes(fill = Sample),
-    stat="identity",
-    binwidth = 1,
-    position = position_dodge2(preserve = "single")
-  ) +
-  labs(
-    x = "age_category",
-    y = "Number of participants",
-    fill = "Sample") +
-  theme_personal +
-  scale_fill_manual(
-    values = COPINGpalette6
-  ) +
-  coord_flip()
-
-age_category_by_Sample_count_plot
-```
-
-```{r age_category by Sample prop plot}
-age_category_by_Sample_prop_plot <- age_category_per_Sample_prop_Sample %>%
-  ggplot(mapping = aes(
-    x = age_category,
-    y = Prop)
-  ) +
-  geom_bar(
-    aes(fill = Sample),
-    stat="identity",
-    binwidth = 1,
-    position = position_dodge2(preserve = "single")
-  ) +
-  labs(
-    x = "age_category",
-    y = "Percentage per sample",
-    fill = "Sample") +
-  theme_personal +
-  scale_fill_manual(
-    values = COPINGpalette6
-  ) +
-  coord_flip()
-
-age_category_by_Sample_prop_plot
-```
-
-age bar plot for whole sample (not grouped)
-
-Create a nice summary dataset for age and display it as a bar plot
-
-```{r age_category prop total (ungrouped)}
-
-age_category_prop_total <- dat %>%
-  count(age_category) %>%
-  mutate(Prop = round(n/sum(n), 2))
-
-# add a column to help order the factor
-age_category_prop_total$order <- c(1,2,3,4,5,6,7,8,9,10,11,12,13)
-
-# total responders
-ageN <- sum(age_category_prop_total$n)
-
-kable(age_category_prop_total)
-age_category_prop_total
-
-```
-
-```{r age_category prop total (ungrouped) plot}
-#Colour palette
-RAMPagepalette <- c(
-  "#00D9AC","#21D9B3","#4DD9BC","#78D9C5","#8ED9C9","#A3D9CE",
-  "#CFD9D7",
-  "#DAD0BA","#DAC38F","#DAC38F","#DAB663" ,"#DAA937","#DA9C0C")
-
-#Bar plot
-plot.age <-
-
-  age_category_prop_total %>%
-    mutate(age_category = fct_reorder(age_category,order)) %>%
-
-  ggplot(aes(x = age_category)) +
-  geom_bar(aes(y = n, color=age_category, fill=age_category, alpha = 1),
-           stat ="summary") +
-  scale_fill_manual(values =  RAMPagepalette) +
-  scale_color_manual(values =  RAMPagepalette) +
-  labs(x = "",
-       y = "Total count",
-       title = paste("Number of participants in each age category",sep=" "),
-       subtitle = paste("n = ", ageN,
-                        sep = ""),
-       fill = "Age category") +
-   guides(alpha = FALSE, color = FALSE, fill = FALSE) +
-  scale_x_discrete(limits = (levels(age_category_prop_total$age_category))) +
-  theme_classic2() +
-   theme(axis.text.x = element_text(colour="black", size = 12,angle=45,
-                                    vjust=0.5),
-        axis.text.y = element_text(colour="black", size = 12))
-
-plot.age
-
-```
-
-# Ethnicity_collapsed
-```{r Ethnicity_collapsed per Sample prop per total}
-Ethnicity_collapsed_per_Sample_prop_total <- dat %>%
-  count(Ethnicity_collapsed, Sample) %>%
-  mutate(Prop = round(n/sum(n), 2))
-
-kable(Ethnicity_collapsed_per_Sample_prop_total)
-Ethnicity_collapsed_per_Sample_prop_total
-```
-
-```{r Ethnicity_collapsed per Sample prop per Sample}
-Ethnicity_collapsed_per_Sample_prop_Sample <- dat %>%
-  group_by(Sample) %>%
-  count(Ethnicity_collapsed, Sample) %>%
-  mutate(Prop = round(n/sum(n), 2))
-
-kable(Ethnicity_collapsed_per_Sample_prop_Sample)
-Ethnicity_collapsed_per_Sample_prop_Sample
-```
-
-```{r Ethnicity_collapsed per Sample prop cross table}
-Ethnicity_collapsed_per_Sample_prop_Sample_cross_table <- dat %>%
-  group_by(Sample) %>%
-  count(Ethnicity_collapsed, Sample) %>%
-  mutate(Prop = round(n/sum(n), 2)) %>%
-  pivot_wider(names_from = Sample, values_from = c(n, Prop))
-
-kable(Ethnicity_collapsed_per_Sample_prop_Sample_cross_table)
-Ethnicity_collapsed_per_Sample_prop_Sample_cross_table
-```
-
-```{r Ethnicity_collapsed per Sample count cross table}
-Ethnicity_collapsed_per_Sample_count_cross_table <- dat %>%
-  count(Ethnicity_collapsed, Sample) %>%
-  spread(key = Sample, value = n) %>%
-  mutate(
-    EDGI = as.integer(replace_na(EDGI, 0)),
-    GLAD = as.integer(replace_na(GLAD, 0)),
-    NBR = as.integer(replace_na(NBR, 0)),
-    RAMP = as.integer(replace_na(RAMP, 0))
-  )
-
-kable(Ethnicity_collapsed_per_Sample_count_cross_table)
-Ethnicity_collapsed_per_Sample_count_cross_table
-```
-
-```{r Ethnicity_collapsed per Sample chisquare test}
-Ethnicity_collapsed_per_Sample_chissquare_test <- dat %>%
-  count(Ethnicity_collapsed, Sample) %>%
-  spread(key = Sample, value = n) %>%
-  select(-Ethnicity_collapsed) %>%
-  mutate(
-    EDGI = as.integer(replace_na(EDGI, 0)),
-    GLAD = as.integer(replace_na(GLAD, 0)),
-    NBR = as.integer(replace_na(NBR, 0)),
-    RAMP = as.integer(replace_na(RAMP, 0))
-  ) %>%
-  chisq.test() %>%
-  glance()
-
-kable(Ethnicity_collapsed_per_Sample_chissquare_test)
-Ethnicity_collapsed_per_Sample_chissquare_test
-```
-
-```{r Ethnicity_collapsed by Sample count plot}
-Ethnicity_collapsed_by_Sample_count_plot <- Ethnicity_collapsed_per_Sample_prop_Sample %>%
-  ggplot(mapping = aes(
-    x = Ethnicity_collapsed,
-    y = n)
-  ) +
-  geom_bar(
-    aes(fill = Sample),
-    stat="identity",
-    binwidth = 1,
-    position = position_dodge2(preserve = "single")
-  ) +
-  labs(
-    x = "Ethnicity_collapsed",
-    y = "Number of participants",
-    fill = "Sample") +
-  theme_personal +
-  scale_fill_manual(
-    values = COPINGpalette6
-  ) +
-  coord_flip()
-
-Ethnicity_collapsed_by_Sample_count_plot
-```
-
-```{r Ethnicity_collapsed by Sample prop plot}
-Ethnicity_collapsed_by_Sample_prop_plot <- Ethnicity_collapsed_per_Sample_prop_Sample %>%
-  ggplot(mapping = aes(
-    x = Ethnicity_collapsed,
-    y = Prop)
-  ) +
-  geom_bar(
-    aes(fill = Sample),
-    stat="identity",
-    binwidth = 1,
-    position = position_dodge2(preserve = "single")
-  ) +
-  labs(
-    x = "Ethnicity_collapsed",
-    y = "Percentage per sample",
-    fill = "Sample") +
-  theme_personal +
-  scale_fill_manual(
-    values = COPINGpalette6
-  ) +
-  coord_flip()
-
-Ethnicity_collapsed_by_Sample_prop_plot
-```
-
-### pie charts
-
-```{r Ethnicity_collapsed prop per total summary}
-
-Ethnicity_collapsed_prop_Sample <- dat %>%
-  count(Ethnicity_collapsed) %>%
-  drop_na() %>%
-  mutate(freq = round(n/sum(n), 2))
-
-# total responders
-ethN <- sum(Ethnicity_collapsed_prop_Sample$n)
-
-kable(Ethnicity_collapsed_prop_Sample)
-Ethnicity_collapsed_prop_Sample
-
-```
-
-pie chart with only European label
-
-```{r ethnicity pie chart biggest group label}
-
-eth_pie_alllabel <-
-
-  Ethnicity_collapsed_prop_Sample %>%
-   mutate(Ethnicity_collapsed = fct_reorder(Ethnicity_collapsed,-n)) %>%
-
-  ggplot(aes(x="", y=freq, fill=Ethnicity_collapsed)) +
-  geom_bar(width = 1, stat = "identity") +
-  scale_fill_manual(values =  COPINGpalette6) +
-  scale_color_manual(values =  COPINGpalette6) +
-  coord_polar("y",start=0) +
-  theme_void() +
-   labs(title = paste("RAMP/COPING sample self reported ethnicity",
-                      sep=" "),
-        subtitle = paste("n =", sum(Ethnicity_collapsed_prop_Sample$n),
-                         sep = " "),
-        fill = "Self reported ethnicity")  +
-    geom_text(aes(y = c(0.5),
-                  label= c(paste0(round((freq[1]*100),0),"%"))), #Frequency of European only
-             size=5,
-             face="bold"
-             )
-
-eth_pie_alllabel
-
-```
-
-pie chart - no labels
-
-```{r ethnicity pie chart no label}
-
-eth_pie <-
-
-    Ethnicity_collapsed_prop_Sample %>%
-   mutate(Ethnicity_collapsed = fct_reorder(Ethnicity_collapsed,-n)) %>%
-
-  ggplot(aes(x="", y=freq, fill=Ethnicity_collapsed)) +
-  geom_bar(width = 1, stat = "identity") +
-  scale_fill_manual(values =  COPINGpalette6) +
-  scale_color_manual(values =  COPINGpalette6) +
-  coord_polar("y",start=0) +
-  theme_void() +
-   labs(title = paste("RAMP/COPING sample self reported ethnicity",
-                      sep=" "),
-        subtitle = paste("n =", sum(Ethnicity_collapsed_prop_Sample$n),
-                         sep = " "),
-        fill = "Self reported ethnicity")
-
-eth_pie
-
-```
-
-# Gender_collapsed
-```{r Gender_collapsed per Sample prop per total}
-Gender_collapsed_per_Sample_prop_total <- dat %>%
-  count(Gender_collapsed, Sample) %>%
-  mutate(Prop = round(n/sum(n), 2))
-
-kable(Gender_collapsed_per_Sample_prop_total)
-Gender_collapsed_per_Sample_prop_total
-```
-
-```{r Gender_collapsed per Sample prop per Sample}
-Gender_collapsed_per_Sample_prop_Sample <- dat %>%
-  group_by(Sample) %>%
-  count(Gender_collapsed, Sample) %>%
-  mutate(Prop = round(n/sum(n), 2))
-
-kable(Gender_collapsed_per_Sample_prop_Sample)
-Gender_collapsed_per_Sample_prop_Sample
-```
-
-```{r Gender_collapsed per Sample prop cross table}
-Gender_collapsed_per_Sample_prop_Sample_cross_table <- dat %>%
-  group_by(Sample) %>%
-  count(Gender_collapsed, Sample) %>%
-  mutate(Prop = round(n/sum(n), 2)) %>%
-  pivot_wider(names_from = Sample, values_from = c(n, Prop))
-
-kable(Gender_collapsed_per_Sample_prop_Sample_cross_table)
-Gender_collapsed_per_Sample_prop_Sample_cross_table
-```
-
-```{r Gender_collapsed per Sample count cross table}
-Gender_collapsed_per_Sample_count_cross_table <- dat %>%
-  count(Gender_collapsed, Sample) %>%
-  spread(key = Sample, value = n) %>%
-  mutate(
-    EDGI = as.integer(replace_na(EDGI, 0)),
-    GLAD = as.integer(replace_na(GLAD, 0)),
-    NBR = as.integer(replace_na(NBR, 0)),
-    RAMP = as.integer(replace_na(RAMP, 0))
-  )
-
-kable(Gender_collapsed_per_Sample_count_cross_table)
-Gender_collapsed_per_Sample_count_cross_table
-```
-
-```{r Gender_collapsed per Sample chisquare test}
-Gender_collapsed_per_Sample_chissquare_test <- dat %>%
-  count(Gender_collapsed, Sample) %>%
-  spread(key = Sample, value = n) %>%
-  select(-Gender_collapsed) %>%
-  mutate(
-    EDGI = as.integer(replace_na(EDGI, 0)),
-    GLAD = as.integer(replace_na(GLAD, 0)),
-    NBR = as.integer(replace_na(NBR, 0)),
-    RAMP = as.integer(replace_na(RAMP, 0))
-  ) %>%
-  chisq.test() %>%
-  glance()
-
-kable(Gender_collapsed_per_Sample_chissquare_test)
-Gender_collapsed_per_Sample_chissquare_test
-```
-
-```{r Gender_collapsed by Sample count plot}
-Gender_collapsed_by_Sample_count_plot <- Gender_collapsed_per_Sample_prop_Sample %>%
-  ggplot(mapping = aes(
-    x = Gender_collapsed,
-    y = n)
-  ) +
-  geom_bar(
-    aes(fill = Sample),
-    stat="identity",
-    binwidth = 1,
-    position = position_dodge2(preserve = "single")
-  ) +
-  labs(
-    x = "Gender_collapsed",
-    y = "Number of participants",
-    fill = "Sample") +
-  theme_personal +
-  scale_fill_manual(
-    values = COPINGpalette6
-  ) +
-  coord_flip()
-
-Gender_collapsed_by_Sample_count_plot
-```
-
-```{r Gender_collapsed by Sample prop plot}
-Gender_collapsed_by_Sample_prop_plot <- Gender_collapsed_per_Sample_prop_Sample %>%
-  ggplot(mapping = aes(
-    x = Gender_collapsed,
-    y = Prop)
-  ) +
-  geom_bar(
-    aes(fill = Sample),
-    stat="identity",
-    binwidth = 1,
-    position = position_dodge2(preserve = "single")
-  ) +
-  labs(
-    x = "Gender_collapsed",
-    y = "Percentage per sample",
-    fill = "Sample") +
-  theme_personal +
-  scale_fill_manual(
-    values = COPINGpalette6
-  ) +
-  coord_flip()
-
-Gender_collapsed_by_Sample_prop_plot
-```
-
-### pie charts
-
-```{r Gender_collapsed prop per total}
-
-Gender_collapsed_prop_total <- dat %>%
-  count(Gender_collapsed) %>%
-  mutate(freq = round(n/sum(n), 2))
-
-kable(Gender_collapsed_prop_total)
-Gender_collapsed_prop_total
-
-```
-
-```{r gender pie chart - all labels}
-
-gen_pie_alllabel <- 
-  ggplot(Gender_collapsed_prop_total, aes(x="", y=freq, fill=Gender_collapsed)) +
-  geom_bar(width = 1, stat = "identity") +
-  scale_fill_manual(values =  COPINGpalette5) +
-  scale_color_manual(values =  COPINGpalette5) +
-  coord_polar("y",start=0) +
-  theme_void() +
-   labs(title = paste("RAMP/COPING sample self reported gender",
-                      sep=" "),
-        subtitle = paste("n", sum(Gender_collapsed_prop_total$n),
-                         sep = " "),
-        fill = "Self reported gender")  +
-    geom_text(aes(y = c(0.85,0.35,0),
-                  x = c(1.2,1.2,1.8),
-                  label= c(paste0(round((freq[1:2]*100),0),"%"),paste0(round((freq[3]*100),1),"%"))),
-             size=5,
-             face="bold"
-             )
-
-gen_pie_alllabel
-
-```
-
-pie chart - only labelling two largest groups (male and female)
-
-```{r gender pie chart - male/female labels only}
-
-gen_pie <- 
-  ggplot(Gender_collapsed_prop_total, aes(x="", y=freq, fill=Gender_collapsed)) +
-  geom_bar(width = 1, stat = "identity") +
-  scale_fill_manual(values =  COPINGpalette5) +
-  scale_color_manual(values =  COPINGpalette5) +
-  coord_polar("y",start=0) +
-  theme_void() +
-   labs(title = paste("RAMP/COPING sample self reported gender",
-                      sep=" "),
-        subtitle = paste("n", sum(Gender_collapsed_prop_total$n),
-                         sep = " "),
-        fill = "Self reported gender")  +
-    geom_text(aes(y = c(0.85,0.35,0),
-                  x = c(1.2,1.2,1.8),
-                  label= c(paste0(round((freq[1:2]*100),0),"%"),"")),
-             size=5,
-             face="bold"
-             )
-
-gen_pie
-
-```
-
-pie chart -  no labels
-
-```{r gender pie chart - no labels }
-
-gen_pie_nolabel <- 
-  ggplot(Gender_collapsed_prop_total, aes(x="", y=freq, fill=Gender_collapsed)) +
-  geom_bar(width = 1, stat = "identity") +
-  scale_fill_manual(values =  COPINGpalette5) +
-  scale_color_manual(values =  COPINGpalette5) +
-  coord_polar("y",start=0) +
-  theme_void() +
-   labs(title = paste("RAMP/COPING sample self reported gender",
-                      sep=" "),
-        subtitle = paste("n", sum(Gender_collapsed_prop_total$n),
-                         sep = " "),
-        fill = "Self reported gender")
-
-gen_pie_nolabel
-
-```
-
-# highest_education
-```{r highest_education per Sample prop per total}
-highest_education_per_Sample_prop_total <- dat %>%
-  count(highest_education, Sample) %>%
-  mutate(Prop = round(n/sum(n), 2))
-
-kable(highest_education_per_Sample_prop_total)
-highest_education_per_Sample_prop_total
-```
-
-```{r highest_education per Sample prop per Sample}
-highest_education_per_Sample_prop_Sample <- dat %>%
-  group_by(Sample) %>%
-  count(highest_education, Sample) %>%
-  mutate(Prop = round(n/sum(n), 2))
-
-kable(highest_education_per_Sample_prop_Sample)
-highest_education_per_Sample_prop_Sample
-```
-
-```{r highest_education per Sample prop cross table}
-highest_education_per_Sample_prop_Sample_cross_table <- dat %>%
-  group_by(Sample) %>%
-  count(highest_education, Sample) %>%
-  mutate(Prop = round(n/sum(n), 2)) %>%
-  pivot_wider(names_from = Sample, values_from = c(n, Prop))
-
-kable(highest_education_per_Sample_prop_Sample_cross_table)
-highest_education_per_Sample_prop_Sample_cross_table
-```
-
-```{r highest_education per Sample count cross table}
-highest_education_per_Sample_count_cross_table <- dat %>%
-  count(highest_education, Sample) %>%
-  spread(key = Sample, value = n) %>%
-  mutate(
-    EDGI = as.integer(replace_na(EDGI, 0)),
-    GLAD = as.integer(replace_na(GLAD, 0)),
-    NBR = as.integer(replace_na(NBR, 0)),
-    RAMP = as.integer(replace_na(RAMP, 0))
-  )
-
-kable(highest_education_per_Sample_count_cross_table)
-highest_education_per_Sample_count_cross_table
-```
-
-```{r highest_education per Sample chisquare test}
-highest_education_per_Sample_chissquare_test <- dat %>%
-  count(highest_education, Sample) %>%
-  spread(key = Sample, value = n) %>%
-  select(-highest_education) %>%
-  mutate(
-    EDGI = as.integer(replace_na(EDGI, 0)),
-    GLAD = as.integer(replace_na(GLAD, 0)),
-    NBR = as.integer(replace_na(NBR, 0)),
-    RAMP = as.integer(replace_na(RAMP, 0))
-  ) %>%
-  chisq.test() %>%
-  glance()
-
-kable(highest_education_per_Sample_chissquare_test)
-highest_education_per_Sample_chissquare_test
-```
-
-```{r highest_education by Sample count plot}
-highest_education_by_Sample_count_plot <- highest_education_per_Sample_prop_Sample %>%
-  ggplot(mapping = aes(
-    x = highest_education,
-    y = n)
-  ) +
-  geom_bar(
-    aes(fill = Sample),
-    stat="identity",
-    binwidth = 1,
-    position = position_dodge2(preserve = "single")
-  ) +
-  labs(
-    x = "highest_education",
-    y = "Number of participants",
-    fill = "Sample") +
-  theme_personal +
-  scale_fill_manual(
-    values = COPINGpalette6
-  ) +
-  coord_flip()
-
-highest_education_by_Sample_count_plot
-```
-
-```{r highest_education by Sample prop plot}
-highest_education_by_Sample_prop_plot <- highest_education_per_Sample_prop_Sample %>%
-  ggplot(mapping = aes(
-    x = highest_education,
-    y = Prop)
-  ) +
-  geom_bar(
-    aes(fill = Sample),
-    stat="identity",
-    binwidth = 1,
-    position = position_dodge2(preserve = "single")
-  ) +
-  labs(
-    x = "highest_education",
-    y = "Percentage per sample",
-    fill = "Sample") +
-  theme_personal +
-  scale_fill_manual(
-    values = COPINGpalette6
-  ) +
-  coord_flip()
-
-highest_education_by_Sample_prop_plot
-```
-
-### pie chart
-
-summary dataset with frequencies
-
-```{r highest education prop per total}
-
-highest_education_prop_total <- dat %>%
-  count(highest_education) %>%
-  mutate(freq = round(n/sum(n), 2)) %>% 
-  drop_na()
-
-kable(highest_education_prop_total)
-highest_education_prop_total
-
-# total responders
-eduN <- sum(highest_education_prop_total$n)
-
-edubindat <- dat %>%
-  mutate(demographics.education_binary =
-           case_when(
-             highest_education_numeric == "4" ~ "Bachelors or higher",
-             highest_education_numeric == "3" ~ "A-levels or lower",
-             highest_education_numeric == "2" ~ "A-levels or lower",
-             highest_education_numeric == "1" ~ "A-levels or lower"
-           )) %>%
-  count(demographics.education_binary) %>%
-  mutate(freq = round(n/sum(n), 2)) %>% 
-  drop_na()
-
-educatdat <- dat %>%
-  mutate(demographics.education_three = 
-           case_when(
-             highest_education_numeric == "4" ~ "Bachelors or higher",
-             highest_education_numeric == "3" ~ "A-levels",
-             highest_education_numeric == "1" ~ "GCSEs or lower"
-           )) %>%
-  count(demographics.education_three) %>%
-  mutate(freq = round(n/sum(n), 2)) %>% 
-  drop_na()
-
-```
-
-pie chart labels
-
-```{r education pie chart all labels}
-
-edu_pie_alllabel <-
-
-    highest_education_prop_total %>%
-    mutate(demographics.highest_level_of_education = fct_reorder(highest_education,-n)) %>%
-
-  ggplot(aes(x="", y=freq, fill=demographics.highest_level_of_education)) +
-  geom_bar(width = 1, stat = "identity") +
-  scale_fill_manual(values =  COPINGpalette7) +
-  scale_color_manual(values =  COPINGpalette7) +
-  coord_polar("y",start=0) +
-  theme_void() +
-   labs(title = paste("RAMP/COPING sample self reported level of education",
-                      sep=" "),
-        subtitle = paste("n", sum(highest_education_prop_total$n),
-                         sep = " "),
-        fill = "Self reported level of education")  +
-    geom_text(aes(y = c(0.13,0.04,0.3,0.65),
-                  x = c(1.2,1.2,1.2,1.2), #GCSE, NVQ, A-levels, university
-                  label= paste0(round((freq*100),0),"%")),
-             size=5,
-             face="bold"
-             )
-
-edu_pie_alllabel
-
-```
-
-```{r binary education pie chart all labels}
-
-edu_pie_binlabel <-
-
-    edubindat %>%
-    mutate(demographics.education_binary = fct_reorder(demographics.education_binary,-n)) %>%
-
-  ggplot(aes(x="", y=freq, fill=demographics.education_binary)) +
-  geom_bar(width = 1, stat = "identity") +
-  scale_fill_manual(values =  COPINGpalette7) +
-  scale_color_manual(values =  COPINGpalette7) +
-  coord_polar("y",start=0) +
-  theme_void() +
-   labs(title = paste("RAMP/COPING sample self reported highest level of education, above or below bachelor degree or equivalent",
-                      sep=" "),
-        subtitle = paste("n", sum(edubindat$n),
-                         sep = " "),
-        fill = "Self reported level of education")  +
-    geom_text(aes(y = c(0.25,0.75),
-                  label= paste0(round((freq*100),0),"%")),
-             size=5,
-             face="bold"
-             )
-
-edu_pie_binlabel
-
-```
-
-```{r 3 category education pie chart all labels}
-
-edu_pie_catlabel <-
-
-    educatdat %>%
-    mutate(demographics.education_three = fct_reorder(demographics.education_three,-n)) %>%
-
-  ggplot(aes(x="", y=freq, fill=demographics.education_three)) +
-  geom_bar(width = 1, stat = "identity") +
-  scale_fill_manual(values =  COPINGpalette7) +
-  scale_color_manual(values =  COPINGpalette7) +
-  coord_polar("y",start=0) +
-  theme_void() +
-   labs(title = paste("RAMP/COPING sample self reported highest level of education, above or below bachelor degree or equivalent",
-                      sep=" "),
-        subtitle = paste("n", sum(educatdat$n),
-                         sep = " "),
-        fill = "Self reported level of education")  +
-    geom_text(aes(y = c(0.23,0.65,0.05),
-                  label= c(paste0(round((freq[1:3]*100),0),"%")),
-             size=5,
-             face="bold"
-             ))
-
-edu_pie_catlabel
-
-```
-
-pie chart -  no labels
-
-```{r education pie chart no labels }
-
-edu_pie_nolabel <-
-
-  edu_pie_alllabel <-
-
-    highest_education_prop_total %>%
-    mutate(demographics.highest_level_of_education = fct_reorder(highest_education,-n)) %>%
-
-  ggplot(aes(x="", y=freq, fill=demographics.highest_level_of_education)) +
-  geom_bar(width = 1, stat = "identity") +
-  scale_fill_manual(values =  COPINGpalette7) +
-  scale_color_manual(values =  COPINGpalette7) +
-  coord_polar("y",start=0) +
-  theme_void() +
-   labs(title = paste("RAMP/COPING sample self reported level of education",
-                      sep=" "),
-        subtitle = paste("n", sum(highest_education_prop_total$n),
-                         sep = " "),
-        fill = "Self reported level of education")
-
-```
-
-# key_worker
-```{r key_worker per Sample prop per total}
-key_worker_per_Sample_prop_total <- dat %>%
-  count(key_worker, Sample) %>%
-  mutate(Prop = round(n/sum(n), 2))
-
-kable(key_worker_per_Sample_prop_total)
-key_worker_per_Sample_prop_total
-```
-
-```{r key_worker per Sample prop per Sample}
-key_worker_per_Sample_prop_Sample <- dat %>%
-  group_by(Sample) %>%
-  count(key_worker, Sample) %>%
-  mutate(Prop = round(n/sum(n), 2))
-
-kable(key_worker_per_Sample_prop_Sample)
-key_worker_per_Sample_prop_Sample
-```
-
-```{r key_worker per Sample prop cross table}
-key_worker_per_Sample_prop_Sample_cross_table <- dat %>%
-  group_by(Sample) %>%
-  count(key_worker, Sample) %>%
-  mutate(Prop = round(n/sum(n), 2)) %>%
-  pivot_wider(names_from = Sample, values_from = c(n, Prop))
-
-kable(key_worker_per_Sample_prop_Sample_cross_table)
-key_worker_per_Sample_prop_Sample_cross_table
-```
-
-```{r key_worker per Sample count cross table}
-key_worker_per_Sample_count_cross_table <- dat %>%
-  count(key_worker, Sample) %>%
-  spread(key = Sample, value = n) %>%
-  mutate(
-    EDGI = as.integer(replace_na(EDGI, 0)),
-    GLAD = as.integer(replace_na(GLAD, 0)),
-    NBR = as.integer(replace_na(NBR, 0)),
-    RAMP = as.integer(replace_na(RAMP, 0))
-  )
-
-kable(key_worker_per_Sample_count_cross_table)
-key_worker_per_Sample_count_cross_table
-```
-
-```{r key_worker per Sample chisquare test}
-key_worker_per_Sample_chissquare_test <- dat %>%
-  count(key_worker, Sample) %>%
-  spread(key = Sample, value = n) %>%
-  select(-key_worker) %>%
-  mutate(
-    EDGI = as.integer(replace_na(EDGI, 0)),
-    GLAD = as.integer(replace_na(GLAD, 0)),
-    NBR = as.integer(replace_na(NBR, 0)),
-    RAMP = as.integer(replace_na(RAMP, 0))
-  ) %>%
-  chisq.test() %>%
-  glance()
-
-kable(key_worker_per_Sample_chissquare_test)
-key_worker_per_Sample_chissquare_test
-```
-
-```{r key_worker by Sample count plot}
-key_worker_by_Sample_count_plot <- key_worker_per_Sample_prop_Sample %>%
-  ggplot(mapping = aes(
-    x = key_worker,
-    y = n)
-  ) +
-  geom_bar(
-    aes(fill = Sample),
-    stat="identity",
-    binwidth = 1,
-    position = position_dodge2(preserve = "single")
-  ) +
-  labs(
-    x = "key_worker",
-    y = "Number of participants",
-    fill = "Sample") +
-  theme_personal +
-  scale_fill_manual(
-    values = COPINGpalette6
-  ) +
-  coord_flip()
-
-key_worker_by_Sample_count_plot
-```
-
-```{r key_worker by Sample prop plot}
-key_worker_by_Sample_prop_plot <- key_worker_per_Sample_prop_Sample %>%
-  ggplot(mapping = aes(
-    x = key_worker,
-    y = Prop)
-  ) +
-  geom_bar(
-    aes(fill = Sample),
-    stat="identity",
-    binwidth = 1,
-    position = position_dodge2(preserve = "single")
-  ) +
-  labs(
-    x = "key_worker",
-    y = "Percentage per sample",
-    fill = "Sample") +
-  theme_personal +
-  scale_fill_manual(
-    values = COPINGpalette6
-  ) +
-  coord_flip()
-
-key_worker_by_Sample_prop_plot
-```
-
-# COVID
-## Recode variable
-```{r covid test positive double}
-dat <- dat %>%
-  mutate(covid_test_positive_double_numeric =
-           case_when(
-             (respiratory.throat_swab_test_nose_numeric == 1 &
-               respiratory.results_antibody_test_numeric == 1) ~ 2,
-             respiratory.throat_swab_test_nose_numeric == 1 ~ 1,
-             respiratory.throat_swab_test_nose_numeric == 2 ~ 0,
-             respiratory.results_antibody_test_numeric == 1 ~ 1,
-             respiratory.results_antibody_test_numeric == 2 ~ 0
-           )
-         )
-
-dat <- dat %>%
-  mutate(covid_test_positive_double =
-           recode_factor(
-             covid_test_positive_double_numeric,
-             `0` = "Negative",
-             `1` = "Positive",
-             `2` = "Double positive"
-           )
-         )
-
-dat %>%
-  freq(covid_test_positive_double)
-```
-
-```{r gad covid test positive}
-dat <- dat %>%
-  mutate(gad.covid_test_positive_numeric =
-           case_when(
-             (respiratory.throat_swab_test_nose_numeric == 1 &
-               respiratory.results_antibody_test_numeric == 1) ~ 1, # with two positive test results get coded as positive
-             respiratory.throat_swab_test_nose_numeric == 1 ~ 1,
-             respiratory.throat_swab_test_nose_numeric == 2 ~ 0,
-             respiratory.results_antibody_test_numeric == 1 ~ 1,
-             respiratory.results_antibody_test_numeric == 2 ~ 0
-           )
-         )
-
-dat <- dat %>%
-  mutate(covid_test_positive =
-           recode_factor(
-             gad.covid_test_positive_numeric,
-             `0` = "Negative",
-             `1` = "Positive"
-#             `2` = "Double positive"
-           )
-         )
-
-dat %>%
-  freq(covid_test_positive)
-```
-
-## COVID swab test positive
-```{r COVID positive swap}
-dat %>%
-  count(respiratory.throat_swab_test_nose, Sample) %>%
-  mutate(Prop = round(n/sum(n), 2))
-```
-
-## antibody test
-```{r COVID positive antibody test}
-dat %>%
-  count(respiratory.results_antibody_test, Sample) %>%
-  mutate(Prop = round(n/sum(n), 2))
-```
-
-## COVID probable diagnosis
-```{r COVID probable diagnosis}
-dat %>%
-  count(covid_probable_case_incl_screening, Sample) %>%
-  mutate(Prop = round(n/sum(n), 2))
-```
-
-## Cross table probable covid and covid test positive
-```{r Cross table probable covid and covid test positive}
-dat %>%
-  count(covid_test_positive, covid_probable_case_incl_screening) %>%
-  spread(key = covid_test_positive, value = n)
-```
-
-# Create data set per measure
-++MD: Do we want to break up the datasets by measure?
-I think the datasets we've already specified should be sufficient.
-I've tested the results of the regression model and it's the same using dat.gad vs.
-dat datasets.
-
-## GAD
-```{r}
-dat.gad <- dat %>%
-#  drop_na() %>%
-  filter(
-    (data_group_gad == "Baseline and retrospective data" |
-      data_group_gad == "Prepandemic and baseline data" |
-      data_group_gad == "All prepandemic, baseline and retrospective data")
-  )
-
-dim(dat.gad)
-```
-
-# Questionnaire comparions
-
-## gad
-
-### Split sample in improvement and worsening
-```{r gad improvment worsening stratification}
-dat <- dat %>%
-  mutate(gad.change_binary_numeric =
-           case_when(
-             gad.pandemic_felt_feelings_numeric == 1 ~ 1,
-             gad.pandemic_felt_feelings_numeric == 2 ~ 1,
-             gad.pandemic_felt_feelings_numeric == 3 ~ 0,
-             gad.pandemic_felt_feelings_numeric == 4 ~ 2,
-             gad.pandemic_felt_feelings_numeric == 5 ~ 2
-           )
-         )
-
-dat <- dat %>%
-  mutate(gad.change_binary =
-           recode_factor(
-             gad.change_binary_numeric,
-             `0` = "No change",
-             `1` = "Worsening",
-             `2` = "Improvement"
-           )
-         )
-
-dat %>%
-  freq(gad.change_binary)
-```
-
-### Summary scores
-```{r descriptives gad.sum_score_cols}
-gad.sum_score_numeric_table <- dat %>% 
-  group_by(gad.change_binary) %>%
-  summarise_at( 
-    vars(
-      "Prepan" = gad.sum_score_prepan,
-      "Base" = gad.sum_score_base,
-      "Retro" = gad.sum_score_retro
-    ),
-    .funs =
-      list(
-        ~mean(., na.rm = T),
-        ~sd(., na.rm = T),
-        ~median(., na.rm = T),
-        ~min(., na.rm = T),
-        ~max(., na.rm = T),
-        ~skew(., na.rm = T),
-        kurtosis = ~kurtosi(., na.rm = T)
-      )
-  )
-
-gad.sum_score_numeric_table
-```
-
-```{r gad sum score smart numeric summary tables}
-# reshape the table
-gad.sum_score_numeric_summary_table_reshaped <- gad.sum_score_numeric_table %>% 
-  gather(key, value, -gad.change_binary) %>% 
-  separate(key, c("variable", "measure"), sep = "_") %>%
-  mutate(measure = factor(
-    x = measure,
-    levels =  c( # this is the order I want my columns to appear in
-      "missing",
-      "min",
-      "max",
-      "mean", 
-      "median", 
-      "mode",
-      "sd",
-      "skew",
-      "kurtosis"
-    ))) %>% 
-  spread(measure, value) %>% 
-  # we can apply a function to all variables to edit them so that they are publication ready
-  rename_all(
-    .funs = ~str_to_title(.)
-  ) %>% 
-  # or we can individually rename variables 
-  rename(
-    Change = Gad.change_binary,
-    SD = Sd
-  )
-
-gad.sum_score_numeric_summary_table_reshaped
-```
-
-Table for knitting
-gad sum score summary table
-```{r gad sum score summary table}
-kable(gad.sum_score_numeric_summary_table_reshaped)
-```
-
-### Differences scores
-
-```{r descriptives gad.diff_score_cols}
-gad.numeric_table <- dat %>% 
-  group_by(gad.change_binary) %>%
-  summarise_at( 
-    vars(
-      "Base - prepan" = gad.diff_score_base_prepan,
-      "Base - retro" = gad.diff_score_base_retro,
-      "Prepan - retro" = gad.diff_score_retro_prepan
-    ),
-    .funs =
-      list(
-        ~mean(., na.rm = T),
-        ~sd(., na.rm = T),
-        ~median(., na.rm = T),
-        ~min(., na.rm = T),
-        ~max(., na.rm = T),
-        ~skew(., na.rm = T),
-        kurtosis = ~kurtosi(., na.rm = T)
-      )
-  )
-
-gad.numeric_table
-```
-
-```{r gad diff score smart numeric summary tables}
-# reshape the table
-gad.numeric_summary_table_reshaped <- gad.numeric_table %>% 
-  gather(key, value, -gad.change_binary) %>% 
-  separate(key, c("variable", "measure"), sep = "_") %>%
-  mutate(measure = factor(
-    x = measure,
-    levels =  c( # this is the order I want my columns to appear in
-      "missing",
-      "min",
-      "max",
-      "mean", 
-      "median", 
-      "mode",
-      "sd",
-      "skew",
-      "kurtosis"
-    ))) %>% 
-  spread(measure, value) %>% 
-  # we can apply a function to all variables to edit them so that they are publication ready
-  rename_all(
-    .funs = ~str_to_title(.)
-    ) %>% 
-  # or we can individually rename variables 
-  rename(
-    Change = Gad.change_binary,
-    SD = Sd
-  )
-
-gad.numeric_summary_table_reshaped
-```
-
-Table for knitting
-gad diff summary table
-```{r gad diff summary table}
-kable(gad.numeric_summary_table_reshaped)
-```
-
-### Long format
-
-```{r gad gather to long format Time_points gad.diff_score}
-dat.long.gad.diff <- dat %>%
-  gather(
-    key = "Time_point_raw",
-    value = "gad.diff_score",
-    all_of(gad.diff_score_cols)) %>%
-  select(
-    ID,
-    Sample,
-    Gender_collapsed,
-    Ethnicity_collapsed,
-    Disorder_hierarchical,
-    Time_point_raw,
-    gad.diff_score
-  ) %>%
-  mutate(Time_point = str_replace(Time_point_raw, "gad.diff_score_", "")) %>%
-  select(-Time_point_raw)
-
-head(dat.long.gad.diff)
-```
-
-```{r gad gather to long format Time_points gad.sum_score}
-dat.long.gad.sum <- dat %>%
-  gather(
-    key = "Time_point_raw",
-    value = "gad.sum_score",
-    all_of(gad.sum_score_cols)) %>%
-  select(
-    ID,
-    Sample,
-    Gender_collapsed,
-    Ethnicity_collapsed,
-    Disorder_hierarchical,
-    Time_point_raw,
-    gad.sum_score
-  ) %>%
-  mutate(Time_point = str_replace(Time_point_raw, "gad.sum_score_", "")) %>%
-  select(-Time_point_raw)
-
-head(dat.long.gad.sum)
-```
-
-### Plots diff
-
-makes this into percentages
-```{r gad absolut plot}
-dat.long.gad.diff %>%
-  ggplot(mapping = aes(y = gad.diff_score)) +
-  geom_bar() +
-  theme_minimal() +
-  facet_wrap(facets = vars(Time_point))
-```
-
-```{r gad percentage plot retro_prepan diff}
-dat.long.gad.diff %>%
-  filter(Time_point != "retro_prepan") %>%
-  ggplot(mapping = aes(
-    x = gad.diff_score,
-    y = stat(density*width),
-    fill = Time_point)) +
-  geom_histogram(
-    binwidth = 1,
-    position = position_dodge2(preserve = "single")
-  ) +
-  labs(
-    x = "Difference GAD7 score",
-    y = "Percentage of participants",
-    fill = "Comparison:\nBaseline vs") +
-  theme_personal +
-  scale_fill_manual(values = palette, labels = c("Prepandemic", "Retrospective"))
-```
-
-```{r gad percentage plot retro_prepan resized, fig.height=6, fig.width=10}
-dat.long.gad.diff %>%
-  filter(Time_point != "retro_prepan") %>%
-  ggplot(mapping = aes(
-    x = gad.diff_score,
-    y = stat(density*width),
-    fill = Time_point)) +
-  geom_histogram(
-    binwidth = 1,
-    position = position_dodge2(preserve = "single")
-  ) +
-  labs(
-    x = "Difference GAD7 score",
-    y = "Percentage of participants",
-    fill = "Comparison:\nBaseline vs") +
-  theme_personal +
-  scale_fill_manual(values = palette, labels = c("Prepandemic", "Retrospective")) +
-  facet_wrap("Disorder_hierarchical")
-```
-
-```{r gad plot retro_prepan diff}
-dat.long.gad.diff %>%
-  filter(Time_point == "retro_prepan") %>%
-  ggplot(mapping = aes(
-    x = gad.diff_score,
-    y = stat(density*width),
-    fill = Time_point)) +
-  geom_histogram(
-    binwidth = 1,
-    position = position_dodge2(preserve = "single")
-  ) +
-  labs(
-    x = "Difference GAD7 score",
-    y = "Percentage of participants",
-    fill = "Comparison:\nRetrospective vs") +
-  theme_personal +
-  scale_fill_manual(values = palette, labels = c("Prepandemic"))
-```
-
-### Plots sum
-
-```{r gad percentage plot retro_prepan sum}
-dat.long.gad.sum %>%
-#  filter(Time_point != "retro_prepan") %>%
-  ggplot(mapping = aes(
-    x = gad.sum_score,
-    y = stat(density*width),
-    fill = Time_point)) +
-  geom_histogram(
-    binwidth = 1,
-    position = position_dodge2(preserve = "single")
-  ) +
-  labs(
-    x = "GAD7 scores",
-    y = "Percentage of participants",
-    fill = "Time point") +
-  theme_personal +
-  scale_fill_manual(
-    values = COPINGpalette3,
-    labels = c("Baseline", "Prepandemic", "Retrospective")
-    )
-```
-
-```{r gad percentage plot retro_prepan sum resized, fig.height=6, fig.width=10}
-dat.long.gad.sum %>%
-#  filter(Time_point != "retro_prepan") %>%
-  ggplot(mapping = aes(
-    x = gad.sum_score,
-    y = stat(density*width),
-    fill = Time_point)) +
-  geom_histogram(
-    binwidth = 1,
-    position = position_dodge2(preserve = "single")
-  ) +
-  labs(
-    x = "GAD7 score",
-    y = "Percentage of participants",
-    fill = "Time point") +
-  theme_personal +
-  scale_fill_manual(
-    values = COPINGpalette3,
-#    labels = c("Prepandemic", "Retrospective")
-    ) +
-  facet_wrap("Disorder_hierarchical")
-```
-
-## phq
-
-### Split sample in improvement and worsening
-```{r phq improvment worsening stratification}
-dat <- dat %>%
-  mutate(phq.change_binary_numeric =
-           case_when(
-             phq.pandemic_felt_feelings_numeric == 1 ~ 1,
-             phq.pandemic_felt_feelings_numeric == 2 ~ 1,
-             phq.pandemic_felt_feelings_numeric == 3 ~ 0,
-             phq.pandemic_felt_feelings_numeric == 4 ~ 2,
-             phq.pandemic_felt_feelings_numeric == 5 ~ 2
-           )
-  )
-
-dat <- dat %>%
-  mutate(phq.change_binary =
-           recode_factor(
-             phq.change_binary_numeric,
-             `0` = "No change",
-             `1` = "Worsening",
-             `2` = "Improvement"
-           )
-  )
-
-dat %>%
-  freq(phq.change_binary)
-```
-
-### Summary scores
-```{r descriptives phq.sum_score}
-phq.sum_score_numeric_table <- dat %>% 
-  group_by(phq.change_binary) %>%
-  summarise_at( 
-    vars(
-      "Prepan" = phq.sum_score_prepan,
-      "Base" = phq.sum_score_base,
-      "Retro" = phq.sum_score_retro
-    ),
-    .funs =
-      list(
-        ~mean(., na.rm = T),
-        ~sd(., na.rm = T),
-        ~median(., na.rm = T),
-        ~min(., na.rm = T),
-        ~max(., na.rm = T),
-        ~skew(., na.rm = T),
-        kurtosis = ~kurtosi(., na.rm = T)
-      )
-  )
-
-phq.sum_score_numeric_table
-```
-
-```{r phq sum score smart numeric summary tables}
-# reshape the table
-phq.sum_score_numeric_summary_table_reshaped <- phq.sum_score_numeric_table %>%
-  gather(key, value, -phq.change_binary) %>% 
-  separate(key, c("variable", "measure"), sep = "_") %>%
-  mutate(measure = factor(
-    x = measure,
-    levels =  c( # this is the order I want my columns to appear in
-      "missing",
-      "min",
-      "max",
-      "mean", 
-      "median", 
-      "mode",
-      "sd",
-      "skew",
-      "kurtosis"
-    ))) %>% 
-  spread(measure, value) %>% 
-  # we can apply a function to all variables to edit them so that they are publication ready
-  rename_all(
-    .funs = ~str_to_title(.)
-  ) %>% 
-  # or we can individually rename variables 
-  rename(
-    SD = Sd
-  )
-
-phq.sum_score_numeric_summary_table_reshaped
-```
-
-Table for knitting
-phq sum score summary table
-```{r phq sum score summary table}
-kable(phq.sum_score_numeric_summary_table_reshaped)
-```
-
-### Differences score
-
-```{r descriptives phq.diff_score_cols}
-phq.numeric_table <- dat %>% 
-  group_by(phq.change_binary) %>%
-  summarise_at( 
-    vars(
-      "Base - prepan" = phq.diff_score_base_prepan,
-      "Base - retro" = phq.diff_score_base_retro,
-      "Prepan - retro" = phq.diff_score_retro_prepan
-    ),
-    .funs =
-      list(
-        ~mean(., na.rm = T),
-        ~sd(., na.rm = T),
-        ~median(., na.rm = T),
-        ~min(., na.rm = T),
-        ~max(., na.rm = T),
-        ~skew(., na.rm = T),
-        kurtosis = ~kurtosi(., na.rm = T)
-      )
-  )
-
-phq.numeric_table
-```
-
-```{r phq diff score smart numeric summary tables}
-# reshape the table
-phq.numeric_summary_table_reshaped <- phq.numeric_table %>% 
-  gather(key, value, -phq.change_binary) %>% 
-  separate(key, c("variable", "measure"), sep = "_") %>%
-  mutate(measure = factor(
-    x = measure,
-    levels =  c( # this is the order I want my columns to appear in
-      "missing",
-      "min",
-      "max",
-      "mean", 
-      "median", 
-      "mode",
-      "sd",
-      "skew",
-      "kurtosis"
-    ))) %>% 
-  spread(measure, value) %>% 
-  # we can apply a function to all variables to edit them so that they are publication ready
-  rename_all(
-    .funs = ~str_to_title(.)
-  ) %>% 
-  # or we can individually rename variables 
-  rename(
-    SD = Sd
-  )
-
-phq.numeric_summary_table_reshaped
-```
-
-Table for knitting
-phq diff summary table
-```{r phq diff summary table}
-kable(phq.numeric_summary_table_reshaped)
-```
-
-### Long format
-
-```{r phq gather to long format Time_points}
-dat.long.phq.diff <- dat %>%
-  gather(
-    key = "Time_point_raw",
-    value = "phq.diff_score",
-    all_of(phq.diff_score_cols)) %>%
-  select(
-    ID,
-    Sample,
-    Gender_collapsed,
-    Ethnicity_collapsed,
-    Disorder_hierarchical,
-    Time_point_raw,
-    phq.diff_score
-  ) %>%
-  mutate(Time_point = str_replace(Time_point_raw, "phq.diff_score_", "")) %>%
-  select(-Time_point_raw)
-
-head(dat.long.phq.diff)
-```
-
-```{r phq gather to long format Time_points phq.sum_score}
-dat.long.phq.sum <- dat %>%
-  gather(
-    key = "Time_point_raw",
-    value = "phq.sum_score",
-    all_of(phq.sum_score_cols)) %>%
-  select(
-    ID,
-    Sample,
-    Gender_collapsed,
-    Ethnicity_collapsed,
-    Disorder_hierarchical,
-    Time_point_raw,
-    phq.sum_score
-  ) %>%
-  mutate(Time_point = str_replace(Time_point_raw, "phq.sum_score_", "")) %>%
-  select(-Time_point_raw)
-
-head(dat.long.phq.sum)
-```
-
-### Plots
-
-makes this into percentages
-```{r phq absolut plot}
-dat.long.phq.diff %>%
-  ggplot(mapping = aes(y = phq.diff_score)) +
-  geom_bar() +
-  theme_minimal() +
-  facet_wrap(facets = vars(Time_point))
-```
-
-```{r phq percentage plot retro_prepan}
-dat.long.phq.diff %>%
-  filter(Time_point != "retro_prepan") %>%
-  ggplot(mapping = aes(
-    x = phq.diff_score,
-    y = stat(density*width),
-    fill = Time_point)) +
-  geom_histogram(
-    binwidth = 1,
-    position = position_dodge2(preserve = "single")
-  ) +
-  labs(
-    x = "Difference PHQ9 score",
-    y = "Percentage of participants",
-    fill = "Comparison:\nBaseline vs") +
-  theme_personal +
-  scale_fill_manual(values = palette, labels = c("Prepandemic", "Retrospective"))
-```
-
-```{r phq plot retro_prepan diff}
-dat.long.phq.diff %>%
-  filter(Time_point == "retro_prepan") %>%
-  ggplot(mapping = aes(
-    x = phq.diff_score,
-    y = stat(density*width),
-    fill = Time_point)) +
-  geom_histogram(
-    binwidth = 1,
-    position = position_dodge2(preserve = "single")
-  ) +
-  labs(
-    x = "Difference phq7 score",
-    y = "Percentage of participants",
-    fill = "Comparison:\nPrepandemic vs") +
-  theme_personal +
-  scale_fill_manual(values = palette, labels = c("Retrospective"))
-```
-
-```{r phq percentage plot retro_prepan resized, fig.height=6, fig.width=10}
-dat.long.phq.diff %>%
-  filter(Time_point != "retro_prepan") %>%
-  ggplot(mapping = aes(
-    x = phq.diff_score,
-    y = stat(density*width),
-    fill = Time_point)) +
-  geom_histogram(
-    binwidth = 1,
-    position = position_dodge2(preserve = "single")
-  ) +
-  labs(
-    x = "Difference PHQ9 score",
-    y = "Percentage of participants",
-    fill = "Comparison:\nBaseline vs") +
-  theme_personal +
-  scale_fill_manual(values = palette, labels = c("Prepandemic", "Retrospective")) +
-  facet_wrap("Disorder_hierarchical")
-```
-
-### Plots sum
-
-```{r phq percentage plot retro_prepan sum}
-dat.long.phq.sum %>%
-  #  filter(Time_point != "retro_prepan") %>%
-  ggplot(mapping = aes(
-    x = phq.sum_score,
-    y = stat(density*width),
-    fill = Time_point)) +
-  geom_histogram(
-    binwidth = 1,
-    position = position_dodge2(preserve = "single")
-  ) +
-  labs(
-    x = "PHQ9 scores",
-    y = "Percentage of participants",
-    fill = "Time point") +
-  theme_personal +
-  scale_fill_manual(
-    values = COPINGpalette3,
-    labels = c("Baseline", "Prepandemic", "Retrospective")
-  )
-```
-
-```{r phq percentage plot retro_prepan sum resized, fig.height=6, fig.width=10}
-dat.long.phq.sum %>%
-  #  filter(Time_point != "retro_prepan") %>%
-  ggplot(mapping = aes(
-    x = phq.sum_score,
-    y = stat(density*width),
-    fill = Time_point)) +
-  geom_histogram(
-    binwidth = 1,
-    position = position_dodge2(preserve = "single")
-  ) +
-  labs(
-    x = "PHQ9 score",
-    y = "Percentage of participants",
-    fill = "Time point") +
-  theme_personal +
-  scale_fill_manual(
-    values = COPINGpalette3,
-    labels = c("Baseline", "Prepandemic", "Retrospective")
-  ) +
-  facet_wrap("Disorder_hierarchical")
-```
-
-## ocir
-
-### Split sample in improvement and worsening
-```{r ocir improvment worsening stratification}
-dat <- dat %>%
-  mutate(ocir.change_binary_numeric =
-           case_when(
-             ocir.felt_pandemic_feelings_numeric == 1 ~ 1,
-             ocir.felt_pandemic_feelings_numeric == 2 ~ 1,
-             ocir.felt_pandemic_feelings_numeric == 3 ~ 0,
-             ocir.felt_pandemic_feelings_numeric == 4 ~ 2,
-             ocir.felt_pandemic_feelings_numeric == 5 ~ 2
-           )
-  )
-
-dat <- dat %>%
-  mutate(ocir.change_binary =
-           recode_factor(
-             ocir.change_binary_numeric,
-             `0` = "No change",
-             `1` = "Worsening",
-             `2` = "Improvement"
-           )
-  )
-
-dat %>%
-  freq(ocir.change_binary)
-```
-
-### Summary scores
-```{r descriptives ocir.sum_score}
-ocir.sum_score_numeric_table <- dat %>% 
-  group_by(ocir.change_binary) %>%
-  summarise_at( 
-    vars(
-      "Prepan" = ocir.sum_score_prepan,
-      "Base" = ocir.sum_score_base,
-      "Retro" = ocir.sum_score_retro
-    ),
-    .funs =
-      list(
-        ~mean(., na.rm = T),
-        ~sd(., na.rm = T),
-        ~median(., na.rm = T),
-        ~min(., na.rm = T),
-        ~max(., na.rm = T),
-        ~skew(., na.rm = T),
-        kurtosis = ~kurtosi(., na.rm = T)
-      )
-  )
-
-ocir.sum_score_numeric_table
-```
-
-```{r ocir sum score smart numeric summary tables}
-# reshape the table
-ocir.sum_score_numeric_summary_table_reshaped <- ocir.sum_score_numeric_table %>%
-  filter(ocir.change_binary == "Worsening") %>%
-  select(-ocir.change_binary) %>%
-  gather(key, value) %>% 
-  separate(key, c("variable", "measure"), sep = "_") %>%
-  mutate(measure = factor(
-    x = measure,
-    levels =  c( # this is the order I want my columns to appear in
-      "missing",
-      "min",
-      "max",
-      "mean", 
-      "median", 
-      "mode",
-      "sd",
-      "skew",
-      "kurtosis"
-    ))) %>% 
-  spread(measure, value) %>% 
-  # we can apply a function to all variables to edit them so that they are publication ready
-  rename_all(
-    .funs = ~str_to_title(.)
-  ) %>% 
-  # or we can individually rename variables 
-  rename(
-    SD = Sd
-  )
-
-ocir.sum_score_numeric_summary_table_reshaped
-```
-
-Table for knitting
-ocir sum score summary table
-```{r ocir sum score summary table}
-kable(ocir.sum_score_numeric_summary_table_reshaped)
-```
-
-### Differences scores
-
-```{r descriptives ocir.diff_score_cols}
-ocir.numeric_table <- dat %>% 
-  #  group_by(dem.sex) %>%
-  summarise_at( 
-    vars(
-      "Base - prepan" = ocir.diff_score_base_prepan,
-      "Base - retro" = ocir.diff_score_base_retro,
-      "Prepan - retro" = ocir.diff_score_retro_prepan
-    ),
-    .funs =
-      list(
-        ~mean(., na.rm = T),
-        ~sd(., na.rm = T),
-        ~median(., na.rm = T),
-        ~min(., na.rm = T),
-        ~max(., na.rm = T),
-        ~skew(., na.rm = T),
-        kurtosis = ~kurtosi(., na.rm = T)
-      )
-  )
-
-ocir.numeric_table
-```
-
-```{r ocir diff score smart numeric summary tables}
-# reshape the table
-ocir.numeric_summary_table_reshaped <- ocir.numeric_table %>% 
-  gather(key, value) %>% 
-  separate(key, c("variable", "measure"), sep = "_") %>%
-  mutate(measure = factor(
-    x = measure,
-    levels =  c( # this is the order I want my columns to appear in
-      "missing",
-      "min",
-      "max",
-      "mean", 
-      "median", 
-      "mode",
-      "sd",
-      "skew",
-      "kurtosis"
-    ))) %>% 
-  spread(measure, value) %>% 
-  # we can apply a function to all variables to edit them so that they are publication ready
-  rename_all(
-    .funs = ~str_to_title(.)
-  ) %>% 
-  # or we can individually rename variables 
-  rename(
-    SD = Sd
-  )
-
-ocir.numeric_summary_table_reshaped
-```
-
-Table for knitting
-ocir diff summary table
-```{r ocir diff summary table}
-kable(ocir.numeric_summary_table_reshaped)
-```
-
-### Long format
-
-```{r ocir gather to long format Time_points}
-dat.long.ocir.diff <- dat %>%
-  gather(
-    key = "Time_point_raw",
-    value = "ocir.diff_score",
-    all_of(ocir.diff_score_cols)) %>%
-  select(
-    ID,
-    Sample,
-    Gender_collapsed,
-    Ethnicity_collapsed,
-    Disorder_hierarchical,
-    Time_point_raw,
-    ocir.diff_score
-  ) %>%
-  mutate(Time_point = str_replace(Time_point_raw, "ocir.diff_score_", "")) %>%
-  select(-Time_point_raw)
-
-head(dat.long.ocir.diff)
-```
-
-```{r ocir gather to long format Time_points ocir.sum_score}
-dat.long.ocir.sum <- dat %>%
-  gather(
-    key = "Time_point_raw",
-    value = "ocir.sum_score",
-    all_of(ocir.sum_score_cols)) %>%
-  select(
-    ID,
-    Sample,
-    Gender_collapsed,
-    Ethnicity_collapsed,
-    Disorder_hierarchical,
-    Time_point_raw,
-    ocir.sum_score
-  ) %>%
-  mutate(Time_point = str_replace(Time_point_raw, "ocir.sum_score_", "")) %>%
-  select(-Time_point_raw)
-
-head(dat.long.ocir.sum)
-```
-
-### Plots
-
-makes this into percentages
-```{r ocir absolut plot}
-dat.long.ocir.diff %>%
-  ggplot(mapping = aes(y = ocir.diff_score)) +
-  geom_bar() +
-  theme_minimal() +
-  facet_wrap(facets = vars(Time_point))
-```
-
-```{r ocir percentage plot retro_prepan}
-dat.long.ocir.diff %>%
-  filter(Time_point != "retro_prepan") %>%
-  ggplot(mapping = aes(
-    x = ocir.diff_score,
-    y = stat(density*width),
-    fill = Time_point)) +
-  geom_histogram(
-    binwidth = 1,
-    position = position_dodge2(preserve = "single")
-  ) +
-  labs(
-    x = "Difference OCI-R score",
-    y = "Percentage of participants",
-    fill = "Comparison:\nBaseline vs") +
-  theme_personal +
-  scale_fill_manual(values = palette, labels = c("Prepandemic", "Retrospective"))
-```
-
-```{r ocir plot retro_prepan diff}
-dat.long.ocir.diff %>%
-  filter(Time_point == "retro_prepan") %>%
-  ggplot(mapping = aes(
-    x = ocir.diff_score,
-    y = stat(density*width),
-    fill = Time_point)) +
-  geom_histogram(
-    binwidth = 1,
-    position = position_dodge2(preserve = "single")
-  ) +
-  labs(
-    x = "Difference ocir7 score",
-    y = "Percentage of participants",
-    fill = "Comparison:\nPrepandemic vs") +
-  theme_personal +
-  scale_fill_manual(values = palette, labels = c("Retrospective"))
-```
-
-```{r ocir percentage plot retro_prepan resized, fig.height=6, fig.width=10}
-dat.long.ocir.diff %>%
-  filter(Time_point != "retro_prepan") %>%
-  ggplot(mapping = aes(
-    x = ocir.diff_score,
-    y = stat(density*width),
-    fill = Time_point)) +
-  geom_histogram(
-    binwidth = 1,
-    position = position_dodge2(preserve = "single")
-  ) +
-  labs(
-    x = "Difference OCI-R score",
-    y = "Percentage of participants",
-    fill = "Comparison:\nBaseline vs") +
-  theme_personal +
-  scale_fill_manual(values = palette, labels = c("Prepandemic", "Retrospective")) +
-  facet_wrap("Disorder_hierarchical")
-```
-
-### Plots sum
-
-```{r ocir percentage plot retro_prepan sum}
-dat.long.ocir.sum %>%
-  ggplot(mapping = aes(
-    x = ocir.sum_score,
-    y = stat(density*width),
-    fill = Time_point)) +
-  geom_histogram(
-    binwidth = 1,
-    position = position_dodge2(preserve = "single")
-  ) +
-  labs(
-    x = "OCI-R scores",
-    y = "Percentage of participants",
-    fill = "Time point") +
-  theme_personal +
-  scale_fill_manual(
-    values = COPINGpalette3,
-    labels = c("Baseline", "Prepandemic", "Retrospective")
-  )
-```
-
-```{r ocir percentage plot retro_prepan sum resized, fig.height=6, fig.width=10}
-dat.long.ocir.sum %>%
-  ggplot(mapping = aes(
-    x = ocir.sum_score,
-    y = stat(density*width),
-    fill = Time_point)) +
-  geom_histogram(
-    binwidth = 1,
-    position = position_dodge2(preserve = "single")
-  ) +
-  labs(
-    x = "OCI-R score",
-    y = "Percentage of participants",
-    fill = "Time point") +
-  theme_personal +
-  scale_fill_manual(
-    values = COPINGpalette3,
-    labels = c("Baseline", "Prepandemic", "Retrospective")
-  ) +
-  facet_wrap("Disorder_hierarchical")
-```
-
-Rank the disorders by the size of the change
-
-PCL:  
-Calculate the total GLAD, COPING, RAMP baseline 
-## pcl
-
-```{r descriptives pcl.diff_score_cols}
-pcl.numeric_table <- dat %>% 
-#    group_by(Sample) %>%
-  summarise_at( 
-    vars(
-      "Base - prepan" = pcl.diff_score_base_prepan
-    ),
-    .funs =
-      list(
-        ~mean(., na.rm = T),
-        ~sd(., na.rm = T),
-        ~median(., na.rm = T),
-        ~min(., na.rm = T),
-        ~max(., na.rm = T),
-        ~skew(., na.rm = T),
-        kurtosis = ~kurtosi(., na.rm = T)
-      )
-  )
-
-pcl.numeric_table
-```
-
-```{r pcl sum score smart numeric summary tables}
-# reshape the table
-pcl.numeric_summary_table_reshaped <- pcl.numeric_table %>% 
-  gather(key, value) %>% 
-  separate(key, c("variable", "measure"), sep = "_") %>%
-  mutate(measure = factor(
-    x = measure,
-    levels =  c( # this is the order I want my columns to appear in
-      "missing",
-      "min",
-      "max",
-      "mean", 
-      "median", 
-      "mode",
-      "sd",
-      "skew",
-      "kurtosis"
-    ))) %>% 
-  spread(measure, value) %>% 
-  # we can apply a function to all variables to edit them so that they are publication ready
-  rename_all(
-    .funs = ~str_to_title(.)
-  ) %>% 
-  # or we can individually rename variables 
-  rename(
-    SD = Sd
-  )
-
-pcl.numeric_summary_table_reshaped
-```
-
-Table for knitting
-pcl sum score summary table
-```{r pcl sum score summary table}
-kable(pcl.numeric_summary_table_reshaped)
-```
-
-```{r descriptives pcl.sum_score}
-pcl.sum_score_numeric_table <- dat %>% 
-#    group_by(Sample) %>%
-  summarise_at( 
-    vars(
-      "Prepan" = pcl.sum_score_prepan,
-      "Base" = pcl.sum_score_base
-    ),
-    .funs =
-      list(
-        ~mean(., na.rm = T),
-        ~sd(., na.rm = T),
-        ~median(., na.rm = T),
-        ~min(., na.rm = T),
-        ~max(., na.rm = T),
-        ~skew(., na.rm = T),
-        kurtosis = ~kurtosi(., na.rm = T)
-      )
-  )
-
-pcl.numeric_table
-```
-
-```{r pcl diff score smart numeric summary tables}
-# reshape the table
-pcl.sum_score_numeric_summary_table_reshaped <- pcl.sum_score_numeric_table %>% 
-  gather(key, value) %>% 
-  separate(key, c("variable", "measure"), sep = "_") %>%
-  mutate(measure = factor(
-    x = measure,
-    levels =  c( # this is the order I want my columns to appear in
-      "missing",
-      "min",
-      "max",
-      "mean", 
-      "median", 
-      "mode",
-      "sd",
-      "skew",
-      "kurtosis"
-    ))) %>% 
-  spread(measure, value) %>% 
-  # we can apply a function to all variables to edit them so that they are publication ready
-  rename_all(
-    .funs = ~str_to_title(.)
-  ) %>% 
-  # or we can individually rename variables 
-  rename(
-    SD = Sd
-  )
-
-pcl.sum_score_numeric_summary_table_reshaped
-```
-
-Table for knitting
-pcl diff summary table
-```{r pcl diff summary table}
-kable(pcl.sum_score_numeric_summary_table_reshaped)
-```
-
-```{r pcl gather to long format Time_points pcl.sum_score}
-dat.long.pcl.sum <- dat %>%
-  gather(
-    key = "Time_point_raw",
-    value = "pcl.sum_score",
-    all_of(pcl.sum_score_cols)) %>%
-  select(
-    ID,
-    Sample,
-    Gender_collapsed,
-    Ethnicity_collapsed,
-    Disorder_hierarchical,
-    Time_point_raw,
-    pcl.sum_score
-  ) %>%
-  mutate(Time_point = str_replace(Time_point_raw, "pcl.sum_score_", "")) %>%
-  select(-Time_point_raw)
-
-head(dat.long.pcl.sum)
-```
-
-For each item 
-present percentages of how say that this is due to the pandemic 
-```{r pcl percentages due to pandemic}
-pcl.retro.items <- c(
-  "pcl.stressful_experience_upset_reminded_retro_numeric",
-  "pcl.stressful_experience_repeated_images_retro_numeric",
-  "pcl.stressful_situation_avoiding_activities_retro_numeric",
-  "pcl.cut_people_feeling_distant_retro_numeric",
-  "pcl.difficulty_concentrating_retro_numeric",
-  "pcl.feeling_irritable_or_having_angry_outbursts_retro_numeric"
-)
-
-pcl.percentages.summary <- dat %>%
-  select(
-    all_of(pcl.retro.items)
-  ) %>%
-  gather(
-    key = "PCL Item",
-    value = "Binary_score",
-    all_of(pcl.retro.items)
-  ) %>%
-  mutate(Binary_score = fct_explicit_na(as.factor(Binary_score), na_level = "Missing")) %>%
-  group_by(`PCL Item`) %>%
-  count(`PCL Item`, Binary_score) %>%
-  mutate(prop = round(n/sum(n), 3)*100) %>%
-  mutate(n_prop = paste0(n," (",prop, "%)"))
-
-pcl.percentages.summary
-```
-
-### Plots sum
-
-```{r pcl percentage plot retro_prepan sum}
-dat.long.pcl.sum %>%
-  ggplot(mapping = aes(
-    x = pcl.sum_score,
-    y = stat(density*width),
-    fill = Time_point)) +
-  geom_histogram(
-    binwidth = 1,
-    position = position_dodge2(preserve = "single")
-  ) +
-  labs(
-    x = "PCL scores",
-    y = "Percentage of participants",
-    fill = "Time point") +
-  theme_personal +
-  scale_fill_manual(
-    values = COPINGpalette3,
-    labels = c("Baseline", "Prepandemic", "Retrospective")
-  )
-```
-
-```{r pcl percentage plot retro_prepan sum resized, fig.height=6, fig.width=10}
-dat.long.pcl.sum %>%
-  ggplot(mapping = aes(
-    x = pcl.sum_score,
-    y = stat(density*width),
-    fill = Time_point)) +
-  geom_histogram(
-    binwidth = 1,
-    position = position_dodge2(preserve = "single")
-  ) +
-  labs(
-    x = "PCL score",
-    y = "Percentage of participants",
-    fill = "Time point") +
-  theme_personal +
-  scale_fill_manual(
-    values = COPINGpalette3,
-    labels = c("Baseline", "Prepandemic", "Retrospective")
-  ) +
-  facet_wrap("Disorder_hierarchical")
-```
-
-# Psychiatric disorders
-
-```{r disorders total count}
-dat %>%
-  freq(disorders_total_count)
-```
-
-```{r psychiatric disorders frequencies}
-#Ppts with least one psychiatric disorder
-dat %>%
-  count(disorders_total_count >= 1)
-
-#Ppts with anxiety OR depressive disorder
-dat %>% 
-  count(anxiety_disorders_numeric == 1 | depressive_disorders == 1)
-
-#Ppts with anxiety & depression
-dat %>% 
-  count(depression_and_anxiety_numeric == 1)
-```
-
-## Vector
-```{r vector with psychiatric disorders}
-disorder_columns <- c(
-  "control_numeric",  
-  "depressive_disorders_numeric",
-    "anxiety_disorders_numeric",
-    "mhd.posttraumatic_stress_disorder_ptsd_numeric",
-    "eating_disorders_numeric",
-    "obsessive_compulsive_disorders_numeric",
-    "mhd.attention_deficit_hyperactivity_disorder_numeric",
-    "mhd.personality_disorder_numeric",
-    "autism_spectrum_disorder_numeric",
-    "mhd.mania_hypomania_bipolar_or_manicdepression_numeric",
-    "psychotic_disorders_numeric"
-)
-```
-
-## Correlation matrix
-```{r Correlation matrix of psychiatric disorders}
-# Select items for correlation matrix
-mhd.items <- c(
-    "depressive_disorders",
-    "anxiety_disorders",
-    "eating_disorders",
-    "obsessive_compulsive_disorders",
-    "psychotic_disorders",
-    "mhd.mania_hypomania_bipolar_or_manicdepression",
-    "mhd.posttraumatic_stress_disorder_ptsd",
-    "autism_spectrum_disorder",
-    "mhd.attention_deficit_hyperactivity_disorder",
-    "mhd.personality_disorder",
-    "control"
-)
-
-# Calculate correlation matrix on specific columns (variables) from your data frame
-mhd.corr.mat <- hetcor(
-  as.data.frame(dat[,mhd.items]), # Specify the data
-  use = "pairwise.complete.obs" # Use all pairwise observations
-)
-
-# Print the correlation matrix
-print(mhd.corr.mat, digits = max(3, getOption("digits") - 3))
-
-# Save the correlations from the correlation matrix in an object
-mhd.corr.matrix <- as.matrix(mhd.corr.mat)
-
-# Save the p values from the correlation matrix in an object
-mhd.p.matrix <- as.matrix(mhd.corr.mat$tests)
-```
-
-Create the correlation matrix plot using the corrplot package
-```{r Correlation matrix of psychiatric disorders plot, fig.height=7}
-corrplot(mhd.corr.matrix, 
-         method = "color", # objects to represent the correlations on plot
-         type = "lower", # only use the lower triangle of the matrix
-         diag = FALSE, # do not show the correlations on the diagonal
-         addgrid.col = NA,
-         addCoef.col = "black", # colour for the correlation coefficients in the plot
-         tl.cex = 0.8,
-         tl.col = "black",
-         col=colorRampPalette(c("dodgerblue4","white","firebrick4"))(200), # colours for correlations
-         # Combine with significance
-         p.mat = mhd.p.matrix, # Matrix with p values
-         sig.level = 0.01, # Choose significant level
-         insig = "blank" # Nonsignificant correlations have no colour
-         )
-```
-
-```{r gather to long format Disorder_hierarchical}
-dat.long.psych <- dat %>%
-  gather(
-    key = "Disorder_inc_raw",
-    value = "Diagnosis",
-    all_of(disorder_columns)) %>%
-  select(
-    ID,
-    Sample,
-    Gender_collapsed,
-    Ethnicity_collapsed,
-    all_of(diff_score_cols),
-    Disorder_inc_raw,
-    Diagnosis
-  ) %>%
-  mutate(Disorder_inc =
-           recode_factor(
-             Disorder_inc_raw,
-             anxiety_disorders_numeric = "Anxiety disorders",
-             depressive_disorders_numeric = "Depressive disorders",
-             eating_disorders_numeric = "Eating disorders",
-             obsessive_compulsive_disorders_numeric = "OCDs",
-             psychotic_disorders_numeric = "Psychotic disorders",
-             mhd.mania_hypomania_bipolar_or_manicdepression_numeric = "Bipolar disorders",
-             mhd.posttraumatic_stress_disorder_ptsd_numeric = "PTSD",
-             autism_spectrum_disorder_numeric = "Autism",
-             mhd.attention_deficit_hyperactivity_disorder_numeric = "ADHD",
-             mhd.personality_disorder_numeric = "Personality disorders",
-             control_numeric = "Controls"
-           ))
-
-head(dat.long.psych)
-```
-
-```{r Disorder_inc by Gender_collapsed}
-Disorder_inc_by_Gender_collapsed <- dat.long.psych %>%
-  filter(Diagnosis == 1) %>%
-  count(Disorder_inc, Gender_collapsed) %>%
-  mutate(Prop = round(n/sum(n), 2))
-
-Disorder_inc_by_Gender_collapsed
-```
-
-```{r Disorder_inc by Gender_collapsed prop}
-Disorder_inc_by_Gender_collapsed <- dat.long.psych %>%
-  group_by(Disorder_inc) %>%
-  filter(Diagnosis == 1) %>%
-  count(Gender_collapsed) %>%
-  mutate(Prop = round(n/sum(n), 2))
-
-Disorder_inc_by_Gender_collapsed
-```
-
-```{r Disorder_inc by Gender_collapsed count plot}
-Disorder_inc_by_Gender_collapsed_count_plot <- Disorder_inc_by_Gender_collapsed %>%
-  ggplot(mapping = aes(
-    x = Disorder_inc,
-    y = n)
-    ) +
-  geom_bar(
-    aes(fill = Gender_collapsed),
-    stat="identity",
-    binwidth = 1,
-    position = position_dodge2(preserve = "single")
-  ) +
-  labs(
-    x = "Disorders",
-    y = "Number of participants",
-    fill = "Gender_collapsed") +
-  theme_personal +
-  scale_fill_manual(
-    values = COPINGpalette4
-    ) +
-  coord_flip()
-
-Disorder_inc_by_Gender_collapsed_count_plot
-```
-
-```{r Disorder_inc by Gender_collapsed prop plot}
-Disorder_inc_by_Gender_collapsed_prop_plot <- Disorder_inc_by_Gender_collapsed %>%
-  ggplot(mapping = aes(
-    x = Disorder_inc,
-    y = Prop)
-    ) +
-  geom_bar(
-    aes(fill = Gender_collapsed),
-    stat="identity",
-    binwidth = 1,
-    position = position_dodge2(preserve = "single")
-  ) +
-  labs(
-    x = "Disorders",
-    y = "Number of participants",
-    fill = "Gender_collapsed") +
-  theme_personal +
-  scale_fill_manual(
-    values = COPINGpalette4
-    ) +
-  coord_flip()
-
-Disorder_inc_by_Gender_collapsed_prop_plot
-```
-
-100% bar per diagnosis with percentages of contribution per sample
-
-```{r Disorder_inc by Sample}
-Disorder_inc_by_Sample <- dat.long.psych %>%
-  filter(Diagnosis == 1) %>%
-  count(Disorder_inc, Sample)
-```
-
-```{r Disorder_inc by Sample plot}
-Disorder_inc_by_Sample %>%
-  ggplot(mapping = aes(
-    x = Disorder_inc,
-    y = n)
-    ) +
-  geom_bar(
-    aes(fill = Sample),
-#    position = "dodge",
-    stat="identity",
-    binwidth = 1,
-    position = position_dodge2(preserve = "single")
-  ) +
-  labs(
-    x = "Disorders",
-    y = "Number of participants",
-    fill = "Sample") +
-  theme_personal +
-  scale_fill_manual(
-    values = COPINGpalette4,
-#    labels = c("Prepandemic", "Retrospective")
-    ) +
-  coord_flip()
-```
-
-Ethnicity should be recoded
-European
-Mixed or multiple ethnic origins
-African or African British
-Asian or Asian British
-Arab
-```{r Disorder_inc by Ethnicity_collapsed}
-Disorder_inc_by_Ethnicity <- dat.long.psych %>%
-  filter(Diagnosis == 1) %>%
-  count(Disorder_inc, Ethnicity_collapsed) %>%
-  mutate(Prop = round(n/sum(n), 2))
-
-Disorder_inc_by_Ethnicity
-```
-
-```{r Disorder_inc by Ethnicity_collapsed plot}
-Disorder_inc_by_Ethnicity %>%
-  ggplot(mapping = aes(
-    x = Disorder_inc,
-    y = n)
-  ) +
-  geom_bar(
-    aes(fill = Ethnicity_collapsed),
-    #    position = "dodge",
-    stat="identity",
-    binwidth = 1,
-    position = position_dodge2(preserve = "single")
-  ) +
-  labs(
-    x = "Disorders",
-    y = "Number of participants",
-    fill = "Ethnicity_collapsed") +
-  theme_personal +
-  scale_fill_manual(
-    values = COPINGpalette6,
-    #    labels = c("Prepandemic", "Retrospective")
-  ) +
-  coord_flip()
-```
-
-# Create additional datasets for analyses
-Filter data frame to create 2 additional datasets. Additional exclusion criteria (beyond those listed above) are specified below:
-
-  1. Retrospective - baseline change anlyses
-        i. Exclude individuals missing retrospective and/or baseline data
-  2. Prepandemic - baseline change analyses
-          i. Exclude individuals missing pandemic and/or baseline data
-          ii. Exclude individuals with prepandemic data collected after 1st March.
-
-Retro-baseline analyses
-Exclude individuals with NA for MHD, age, gender
-```{r exclusion criteria for retro-baseline analysis}
-dat.retro <- dat %>%
-  filter(
-    ((data_group_gad == "Baseline and retrospective data" |
-      data_group_gad == "All prepandemic, baseline and retrospective data") |
-      (data_group_phq == "Baseline and retrospective data" |
-      data_group_phq == "All prepandemic, baseline and retrospective data") |
-      (data_group_pcl == "Baseline and retrospective data" |
-      data_group_pcl == "All prepandemic, baseline and retrospective data") |
-      (data_group_ocir == "Baseline and retrospective data" |
-      data_group_ocir == "All prepandemic, baseline and retrospective data"))
-  )
-
-dim(dat.retro)
-```
-
-Prepan-baseline analyses
-Exclude individuals with NA for MHD, age, gender; exclude if prepan data collected after 1 March
-```{r exclusion criteria for prepan-baseline analysis}
-dat.prepan <- dat %>%
-  filter(
-    ((data_group_gad == "Baseline and retrospective data" |
-      data_group_gad == "Prepandemic and baseline data" |
-      data_group_gad == "All prepandemic, baseline and retrospective data") |
-      (data_group_phq == "Baseline and retrospective data" |
-      data_group_phq == "Prepandemic and baseline data" |
-      data_group_phq == "All prepandemic, baseline and retrospective data") |
-      (data_group_pcl == "Baseline and retrospective data" |
-      data_group_pcl == "Prepandemic and baseline data" |
-      data_group_pcl == "All prepandemic, baseline and retrospective data") |
-      (data_group_ocir == "Baseline and retrospective data" |
-      data_group_ocir == "Prepandemic and baseline data" |
-      data_group_ocir == "All prepandemic, baseline and retrospective data")) &
-      prepandemic_march_1_numeric == 1
-  )
-
-dim(dat.prepan)
-```
-
-#ANALYSIS PLAN
-1. Calculate mean change per disorder group 
-    i. Disorders (9)
-      a. Rank the disorders by the size of the change
-    ii. Sex 
-    iii. Age (13; RAMP; potentially collapse above 65 depending on group sizes) 
-    iv. Ethnicity groups (5; White European, Black (British), Asian, Arab, Mixed)
-
-2. Regression models (Regress covariates out of the change? Which?)
-    i. Model 0: Disorders  
-    ii. Model 1: Model 0 + Sex + Age + Ethnicity + Time registration and baseline
-
-3. Re-calculate change
-
-4. Re-rank the change again
-
-5. PCL:  
-    i. Calculate the total GLAD, COPING, RAMP baseline
-    ii. For each item:
-          a. present percentages of how say that this is due to the pandemic 
-          b. Calculate a variable PCL pandemic score 
-          c. If one item is highly endorsed due to pandemic -> exclude in sensitivity analysis
-
-# 1. Calculate mean change per group
-
-# 2. Regression
-Regress covariates out of the change? Which?
-
-Model naming conventions:
-0 - unadjusted
-1 - adjusted
-a - hierarchical disorders
-b - overlapping disorder categories
-
-++MD: We may want to exclude disorders from Model b that aren't including in the hierarchy (e.g. ADHD, ASD)
-
-## Prepan-baseline change
-
-### GAD
-Model 0a: Disorder_hierarchical, Unadjusted
-```{r GAD prepan Model 0a}
-gad_prepan_model0a <- lm(
-  formula = gad.diff_score_base_prepan ~ 
-    Disorder_hierarchical,
-  data = dat.prepan)
-
-summary(gad_prepan_model0a)
-tidy(gad_prepan_model0a)
-```
-
-Model 0b: Overlapping disorders, Unadjusted
-```{r GAD prepan Model 0b}
-gad_prepan_model0b <- lm(
-  formula = gad.diff_score_base_prepan ~
-    anxiety_disorders +
-    depressive_disorders +
-    depression_and_anxiety +
-    eating_disorders +
-    obsessive_compulsive_disorders +
-    psychotic_disorders +
-    mhd.mania_hypomania_bipolar_or_manicdepression +
-    mhd.posttraumatic_stress_disorder_ptsd +
-    autism_spectrum_disorder +
-    mhd.attention_deficit_hyperactivity_disorder +
-    mhd.personality_disorder,
-  data = dat.prepan)
-
-summary(gad_prepan_model0b)
-tidy(gad_prepan_model0b)
-```
-
-Model 1a: Disorder hierarchical, Adjusted
-  Model 0a + Sex + Age + Ethnicity_collapsed + Time registration and baseline
-```{r GAD prepan Model 1a}
-gad_prepan_model1a <- lm(
-  formula = gad.diff_score_base_prepan ~ 
-    Disorder_hierarchical + 
-    Gender_collapsed + 
-    age_category + 
-    Ethnicity_collapsed + 
-    time_diff_sign_up_coping,
-  data = dat.prepan)
-
-summary(gad_prepan_model1a)
-tidy(gad_prepan_model1a)
-```
-
-Model 1b: Overlapping disorders, Adjusted
-  Model 0b + Sex + Age + Ethnicity_collapsed + Time registration and baseline
-```{r GAD prepan Model 1b}
-gad_prepan_model1b <- lm(
-  formula = gad.diff_score_base_prepan ~
-    anxiety_disorders +
-    depressive_disorders +
-    depression_and_anxiety +
-    eating_disorders +
-    obsessive_compulsive_disorders +
-    psychotic_disorders +
-    mhd.mania_hypomania_bipolar_or_manicdepression +
-    mhd.posttraumatic_stress_disorder_ptsd +
-    autism_spectrum_disorder +
-    mhd.attention_deficit_hyperactivity_disorder +
-    mhd.personality_disorder +
-    Gender_collapsed + age_category + Ethnicity_collapsed + time_diff_sign_up_coping,
-  data = dat.prepan)
-
-summary(gad_prepan_model1b)
-tidy(gad_prepan_model1b)
-```
-
-### PHQ
-Model 0a: Disorder_hierarchical, Unadjusted
-```{r PHQ prepan Model 0a}
-phq_prepan_model0a <- lm(
-  formula = phq.diff_score_base_prepan ~ 
-    Disorder_hierarchical,
-  data = dat.prepan)
-
-summary(phq_prepan_model0a)
-tidy(phq_prepan_model0a)
-```
-
-Model 0b: Overlapping disorders, Unadjusted
-```{r PHQ prepan Model 0b}
-phq_prepan_model0b <- lm(
-  formula = phq.diff_score_base_prepan ~
-    anxiety_disorders +
-    depressive_disorders +
-    depression_and_anxiety +
-    eating_disorders +
-    obsessive_compulsive_disorders +
-    psychotic_disorders +
-    mhd.mania_hypomania_bipolar_or_manicdepression +
-    mhd.posttraumatic_stress_disorder_ptsd +
-    autism_spectrum_disorder +
-    mhd.attention_deficit_hyperactivity_disorder +
-    mhd.personality_disorder,
-  data = dat.prepan)
-
-summary(phq_prepan_model0b)
-tidy(phq_prepan_model0b)
-```
-
-Model 1a: Disorder hierarchical, Adjusted
-  Model 0a + Sex + Age + Ethnicity_collapsed + Time registration and baseline
-```{r PHQ prepan Model 1a}
-phq_prepan_model1a <- lm(
-  formula = phq.diff_score_base_prepan ~ 
-    Disorder_hierarchical + 
-    Gender_collapsed + 
-    age_category + 
-    Ethnicity_collapsed + 
-    time_diff_sign_up_coping,
-  data = dat.prepan)
-
-summary(phq_prepan_model1a)
-tidy(phq_prepan_model1a)
-```
-
-Model 1b: Overlapping disorders, Adjusted
-  Model 0b + Sex + Age + Ethnicity_collapsed + Time registration and baseline
-```{r PHQ prepan Model 1b}
-phq_prepan_model1b <- lm(
-  formula = phq.diff_score_base_prepan ~
-    anxiety_disorders +
-    depressive_disorders +
-    depression_and_anxiety +
-    eating_disorders +
-    obsessive_compulsive_disorders +
-    psychotic_disorders +
-    mhd.mania_hypomania_bipolar_or_manicdepression +
-    mhd.posttraumatic_stress_disorder_ptsd +
-    autism_spectrum_disorder +
-    mhd.attention_deficit_hyperactivity_disorder +
-    mhd.personality_disorder +
-    Gender_collapsed + age_category + Ethnicity_collapsed + time_diff_sign_up_coping,
-  data = dat.prepan)
-
-summary(phq_prepan_model1b)
-tidy(phq_prepan_model1b)
-```
-
-### PCL
-Model 0a: Disorder_hierarchical, Unadjusted
-```{r PCL prepan Model 0a}
-pcl_prepan_model0a <- lm(
-  formula = pcl.diff_score_base_prepan ~ 
-    Disorder_hierarchical,
-  data = dat.prepan)
-
-summary(pcl_prepan_model0a)
-tidy(pcl_prepan_model0a)
-```
-
-Model 0b: Overlapping disorders, Unadjusted
-```{r PCL prepan Model 0b}
-pcl_prepan_model0b <- lm(
-  formula = pcl.diff_score_base_prepan ~
-    anxiety_disorders +
-    depressive_disorders +
-    depression_and_anxiety +
-    eating_disorders +
-    obsessive_compulsive_disorders +
-    psychotic_disorders +
-    mhd.mania_hypomania_bipolar_or_manicdepression +
-    mhd.posttraumatic_stress_disorder_ptsd +
-    autism_spectrum_disorder +
-    mhd.attention_deficit_hyperactivity_disorder +
-    mhd.personality_disorder,
-  data = dat.prepan)
-
-summary(pcl_prepan_model0b)
-tidy(pcl_prepan_model0b)
-```
-
-Model 1a: Disorder hierarchical, Adjusted
-  Model 0a + Sex + Age + Ethnicity_collapsed + Time registration and baseline
-```{r PCL prepan Model 1a}
-pcl_prepan_model1a <- lm(
-  formula = pcl.diff_score_base_prepan ~ 
-    Disorder_hierarchical + 
-    Gender_collapsed + 
-    age_category + 
-    Ethnicity_collapsed + 
-    time_diff_sign_up_coping,
-  data = dat.prepan)
-
-summary(pcl_prepan_model1a)
-tidy(pcl_prepan_model1a)
-```
-
-Model 1b: Overlapping disorders, Adjusted
-  Model 0b + Sex + Age + Ethnicity_collapsed + Time registration and baseline
-```{r PCL prepan Model 1b}
-pcl_prepan_model1b <- lm(
-  formula = pcl.diff_score_base_prepan ~
-    anxiety_disorders +
-    depressive_disorders +
-    depression_and_anxiety +
-    eating_disorders +
-    obsessive_compulsive_disorders +
-    psychotic_disorders +
-    mhd.mania_hypomania_bipolar_or_manicdepression +
-    mhd.posttraumatic_stress_disorder_ptsd +
-    autism_spectrum_disorder +
-    mhd.attention_deficit_hyperactivity_disorder +
-    mhd.personality_disorder +
-    Gender_collapsed + age_category + Ethnicity_collapsed + time_diff_sign_up_coping,
-  data = dat.prepan)
-
-summary(pcl_prepan_model1b)
-tidy(pcl_prepan_model1b)
-```
-
-### OCIR
-Model 0a: Disorder_hierarchical, Unadjusted
-```{r OCIR prepan Model 0a}
-ocir_prepan_model0a <- lm(
-  formula = ocir.diff_score_base_prepan ~ 
-    Disorder_hierarchical,
-  data = dat.prepan)
-
-summary(ocir_prepan_model0a)
-tidy(ocir_prepan_model0a)
-```
-
-Model 0b: Overlapping disorders, Unadjusted
-```{r OCIR prepan Model 0b}
-ocir_prepan_model0b <- lm(
-  formula = ocir.diff_score_base_prepan ~
-    anxiety_disorders +
-    depressive_disorders +
-    depression_and_anxiety +
-    eating_disorders +
-    obsessive_compulsive_disorders +
-    psychotic_disorders +
-    mhd.mania_hypomania_bipolar_or_manicdepression +
-    mhd.posttraumatic_stress_disorder_ptsd +
-    autism_spectrum_disorder +
-    mhd.attention_deficit_hyperactivity_disorder +
-    mhd.personality_disorder,
-  data = dat.prepan)
-
-summary(ocir_prepan_model0b)
-tidy(ocir_prepan_model0b)
-```
-
-Model 1a: Disorder hierarchical, Adjusted
-  Model 0a + Sex + Age + Ethnicity_collapsed + Time registration and baseline
-```{r OCIR prepan Model 1a}
-ocir_prepan_model1a <- lm(
-  formula = ocir.diff_score_base_prepan ~ 
-    Disorder_hierarchical + 
-    Gender_collapsed + 
-    age_category + 
-    Ethnicity_collapsed + 
-    time_diff_sign_up_coping,
-  data = dat.prepan)
-
-summary(ocir_prepan_model1a)
-tidy(ocir_prepan_model1a)
-```
-
-Model 1b: Overlapping disorders, Adjusted
-  Model 0b + Sex + Age + Ethnicity_collapsed + Time registration and baseline
-```{r OCIR prepan Model 1b}
-ocir_prepan_model1b <- lm(
-  formula = ocir.diff_score_base_prepan ~
-    anxiety_disorders +
-    depressive_disorders +
-    depression_and_anxiety +
-    eating_disorders +
-    obsessive_compulsive_disorders +
-    psychotic_disorders +
-    mhd.mania_hypomania_bipolar_or_manicdepression +
-    mhd.posttraumatic_stress_disorder_ptsd +
-    autism_spectrum_disorder +
-    mhd.attention_deficit_hyperactivity_disorder +
-    mhd.personality_disorder +
-    Gender_collapsed + age_category + Ethnicity_collapsed + time_diff_sign_up_coping,
-  data = dat.prepan)
-
-summary(ocir_prepan_model1b)
-tidy(ocir_prepan_model1b)
-```
-
-## Retro-baseline change
-
-### GAD
-Model 0a: Disorder_hierarchical, Unadjusted
-```{r GAD retro Model 0a}
-gad_retro_model0a <- lm(
-  formula = gad.diff_score_base_retro ~ 
-    Disorder_hierarchical,
-  data = dat.retro)
-
-summary(gad_retro_model0a)
-tidy(gad_retro_model0a)
-```
-
-Model 0b: Overlapping disorders, Unadjusted
-```{r GAD retro Model 0b}
-gad_retro_model0b <- lm(
-  formula = gad.diff_score_base_retro ~
-    anxiety_disorders +
-    depressive_disorders +
-    depression_and_anxiety +
-    eating_disorders +
-    obsessive_compulsive_disorders +
-    psychotic_disorders +
-    mhd.mania_hypomania_bipolar_or_manicdepression +
-    mhd.posttraumatic_stress_disorder_ptsd +
-    autism_spectrum_disorder +
-    mhd.attention_deficit_hyperactivity_disorder +
-    mhd.personality_disorder,
-  data = dat.retro)
-
-summary(gad_retro_model0b)
-tidy(gad_retro_model0b)
-```
-
-Model 1a: Disorder hierarchical, Adjusted
-  Model 0a + Sex + Age + Ethnicity_collapsed + Time registration and baseline
-```{r GAD retro Model 1a}
-gad_retro_model1a <- lm(
-  formula = gad.diff_score_base_retro ~ 
-    Disorder_hierarchical + 
-    Gender_collapsed + 
-    age_category + 
-    Ethnicity_collapsed + 
-    time_diff_sign_up_coping,
-  data = dat.retro)
-
-summary(gad_retro_model1a)
-tidy(gad_retro_model1a)
-```
-
-Model 1b: Overlapping disorders, Adjusted
-  Model 0b + Sex + Age + Ethnicity_collapsed + Time registration and baseline
-```{r GAD retro Model 1b}
-gad_retro_model1b <- lm(
-  formula = gad.diff_score_base_retro ~
-    anxiety_disorders +
-    depressive_disorders +
-    depression_and_anxiety +
-    eating_disorders +
-    obsessive_compulsive_disorders +
-    psychotic_disorders +
-    mhd.mania_hypomania_bipolar_or_manicdepression +
-    mhd.posttraumatic_stress_disorder_ptsd +
-    autism_spectrum_disorder +
-    mhd.attention_deficit_hyperactivity_disorder +
-    mhd.personality_disorder +
-    Gender_collapsed + age_category + Ethnicity_collapsed + time_diff_sign_up_coping,
-  data = dat.retro)
-
-summary(gad_retro_model1b)
-tidy(gad_retro_model1b)
-```
-
-### PHQ
-Model 0a: Disorder_hierarchical, Unadjusted
-```{r PHQ retro Model 0a}
-phq_retro_model0a <- lm(
-  formula = phq.diff_score_base_retro ~ 
-    Disorder_hierarchical,
-  data = dat.retro)
-
-summary(phq_retro_model0a)
-tidy(phq_retro_model0a)
-```
-
-Model 0b: Overlapping disorders, Unadjusted
-```{r PHQ retro Model 0b}
-phq_retro_model0b <- lm(
-  formula = phq.diff_score_base_retro ~
-    anxiety_disorders +
-    depressive_disorders +
-    depression_and_anxiety +
-    eating_disorders +
-    obsessive_compulsive_disorders +
-    psychotic_disorders +
-    mhd.mania_hypomania_bipolar_or_manicdepression +
-    mhd.posttraumatic_stress_disorder_ptsd +
-    autism_spectrum_disorder +
-    mhd.attention_deficit_hyperactivity_disorder +
-    mhd.personality_disorder,
-  data = dat.retro)
-
-summary(phq_retro_model0b)
-tidy(phq_retro_model0b)
-```
-
-Model 1a: Disorder hierarchical, Adjusted
-  Model 0a + Sex + Age + Ethnicity_collapsed + Time registration and baseline
-```{r PHQ retro Model 1a}
-phq_retro_model1a <- lm(
-  formula = phq.diff_score_base_retro ~ 
-    Disorder_hierarchical + 
-    Gender_collapsed + 
-    age_category + 
-    Ethnicity_collapsed + 
-    time_diff_sign_up_coping,
-  data = dat.retro)
-
-summary(phq_retro_model1a)
-tidy(phq_retro_model1a)
-```
-
-Model 1b: Overlapping disorders, Adjusted
-  Model 0b + Sex + Age + Ethnicity_collapsed + Time registration and baseline
-```{r PHQ retro Model 1b}
-phq_retro_model1b <- lm(
-  formula = phq.diff_score_base_retro ~
-    anxiety_disorders +
-    depressive_disorders +
-    depression_and_anxiety +
-    eating_disorders +
-    obsessive_compulsive_disorders +
-    psychotic_disorders +
-    mhd.mania_hypomania_bipolar_or_manicdepression +
-    mhd.posttraumatic_stress_disorder_ptsd +
-    autism_spectrum_disorder +
-    mhd.attention_deficit_hyperactivity_disorder +
-    mhd.personality_disorder +
-    Gender_collapsed + age_category + Ethnicity_collapsed + time_diff_sign_up_coping,
-  data = dat.retro)
-
-summary(phq_retro_model1b)
-tidy(phq_retro_model1b)
-```
-
-### PCL
-
-++MD: Not sure if this is how we want to run the PCL regression - the outcome variable I've included is "How many PCL items the participants report are related to the pandemic", but I think we might want a more nuanced approach than this.
-
-```{r recode PCL retro variable as numeric}
-dat.retro <- dat.retro %>% 
-  mutate(
-    pcl.sum_score_retro = 
-      as.numeric(pcl.sum_score_retro_raw)
-  )
-```
-
-Model 0a: Disorder_hierarchical, Unadjusted
-```{r PCL retro Model 0a}
-pcl_retro_model0a <- lm(
-  formula = pcl.sum_score_retro ~ 
-    Disorder_hierarchical,
-  data = dat.retro)
-
-summary(pcl_retro_model0a)
-tidy(pcl_retro_model0a)
-```
-
-Model 0b: Overlapping disorders, Unadjusted
-```{r PCL retro Model 0b}
-pcl_retro_model0b <- lm(
-  formula = pcl.sum_score_retro ~
-    anxiety_disorders +
-    depressive_disorders +
-    depression_and_anxiety +
-    eating_disorders +
-    obsessive_compulsive_disorders +
-    psychotic_disorders +
-    mhd.mania_hypomania_bipolar_or_manicdepression +
-    mhd.posttraumatic_stress_disorder_ptsd +
-    autism_spectrum_disorder +
-    mhd.attention_deficit_hyperactivity_disorder +
-    mhd.personality_disorder,
-  data = dat.retro)
-
-summary(pcl_retro_model0b)
-tidy(pcl_retro_model0b)
-```
-
-Model 1a: Disorder hierarchical, Adjusted
-  Model 0a + Sex + Age + Ethnicity_collapsed + Time registration and baseline
-```{r PCL retro Model 1a}
-pcl_retro_model1a <- lm(
-  formula = pcl.sum_score_retro ~ 
-    Disorder_hierarchical + 
-    Gender_collapsed + 
-    age_category + 
-    Ethnicity_collapsed + 
-    time_diff_sign_up_coping,
-  data = dat.retro)
-
-summary(pcl_retro_model1a)
-tidy(pcl_retro_model1a)
-```
-
-Model 1b: Overlapping disorders, Adjusted
-  Model 0b + Sex + Age + Ethnicity_collapsed + Time registration and baseline
-```{r PCL retro Model 1b}
-pcl_retro_model1b <- lm(
-  formula = pcl.sum_score_retro ~
-    anxiety_disorders +
-    depressive_disorders +
-    depression_and_anxiety +
-    eating_disorders +
-    obsessive_compulsive_disorders +
-    psychotic_disorders +
-    mhd.mania_hypomania_bipolar_or_manicdepression +
-    mhd.posttraumatic_stress_disorder_ptsd +
-    autism_spectrum_disorder +
-    mhd.attention_deficit_hyperactivity_disorder +
-    mhd.personality_disorder +
-    Gender_collapsed + age_category + Ethnicity_collapsed + time_diff_sign_up_coping,
-  data = dat.retro)
-
-summary(pcl_retro_model1b)
-tidy(pcl_retro_model1b)
-```
-
-### OCIR
-Model 0a: Disorder_hierarchical, Unadjusted
-```{r OCIR retro Model 0a}
-ocir_retro_model0a <- lm(
-  formula = ocir.diff_score_base_retro ~ 
-    Disorder_hierarchical,
-  data = dat.retro)
-
-summary(ocir_retro_model0a)
-tidy(ocir_retro_model0a)
-```
-
-Model 0b: Overlapping disorders, Unadjusted
-```{r OCIR retro Model 0b}
-ocir_retro_model0b <- lm(
-  formula = ocir.diff_score_base_retro ~
-    anxiety_disorders +
-    depressive_disorders +
-    depression_and_anxiety +
-    eating_disorders +
-    obsessive_compulsive_disorders +
-    psychotic_disorders +
-    mhd.mania_hypomania_bipolar_or_manicdepression +
-    mhd.posttraumatic_stress_disorder_ptsd +
-    autism_spectrum_disorder +
-    mhd.attention_deficit_hyperactivity_disorder +
-    mhd.personality_disorder,
-  data = dat.retro)
-
-summary(ocir_retro_model0b)
-tidy(ocir_retro_model0b)
-```
-
-Model 1a: Disorder hierarchical, Adjusted
-  Model 0a + Sex + Age + Ethnicity_collapsed + Time registration and baseline
-```{r OCIR retro Model 1a}
-ocir_retro_model1a <- lm(
-  formula = ocir.diff_score_base_retro ~ 
-    Disorder_hierarchical + 
-    Gender_collapsed + 
-    age_category + 
-    Ethnicity_collapsed + 
-    time_diff_sign_up_coping,
-  data = dat.retro)
-
-summary(ocir_retro_model1a)
-tidy(ocir_retro_model1a)
-```
-
-Model 1b: Overlapping disorders, Adjusted
-  Model 0b + Sex + Age + Ethnicity_collapsed + Time registration and baseline
-```{r OCIR retro Model 1b}
-ocir_retro_model1b <- lm(
-  formula = ocir.diff_score_base_retro ~
-    anxiety_disorders +
-    depressive_disorders +
-    depression_and_anxiety +
-    eating_disorders +
-    obsessive_compulsive_disorders +
-    psychotic_disorders +
-    mhd.mania_hypomania_bipolar_or_manicdepression +
-    mhd.posttraumatic_stress_disorder_ptsd +
-    autism_spectrum_disorder +
-    mhd.attention_deficit_hyperactivity_disorder +
-    mhd.personality_disorder +
-    Gender_collapsed + age_category + Ethnicity_collapsed + time_diff_sign_up_coping,
-  data = dat.retro)
-
-summary(ocir_retro_model1b)
-tidy(ocir_retro_model1b)
-```
-
-# RUBBISH
-
-+++ Everything underneath here is only SCRATCH
-
-```{r RUBBISH 1}
-gad.diff_score_base_prepan_plot <- dat %>%
-  ggplot(mapping = aes(y = gad.diff_score_base_prepan)) +
-  geom_bar() +
-  theme_minimal()
-
-gad.diff_score_retro_prepan_plot <- dat %>%
-  ggplot(mapping = aes(y = gad.diff_score_retro_prepan)) +
-  geom_bar() +
-  theme_minimal()
-
-gad.diff_score_base_retro_plot <- dat %>%
-  ggplot(mapping = aes(y = gad.diff_score_base_retro)) +
-  geom_bar() +
-  theme_minimal()
-
-```
-
-```{r RUBBISH 2, fig.height=7, fig.width=5}
-gad.diff_score_base_prepan_plot /
-  gad.diff_score_retro_prepan_plot /
-  gad.diff_score_base_retro_plot +
-  plot_layout(guides = "collect", heights = c(1,1,1)) +
-  plot_annotation(tag_levels = "A")
-```
-
-Calculate mean change per disorder group 
-Disorders (9) 
-Sex 
-Age (13; RAMP; potentially collapse above 65 depending on group sizes) 
-Ethnicity groups (5; White European, Black (British), Asian, Arab, Mixed)
-
-```{r RUBBISH }
-#ADD
-```
-
-Calculate a variable PCL pandemic score 
-```{r}
-
-```
-
-If one item is highly endorsed due to pandemic -> exclude in sensitivity analysis 
-```{r}
-
-```
-
-Descriptives for reporting: "How different are these feelings to how you felt before the pandemic?’ on a 5-point scale (much worse, a little worse, no different, a little better, much better)."
-+++KLP: Discuss during the meeting if we use 3 or 5 categories
-```{r}
-
-```
-
-Replicate chunk above for retrospective reports. This will only be for people who say that have reported that there is a change in their scores. 
-*Discuss if we should include people who reported "no change" as repition of their current GAD, PHQ, PCL report*
-```{r}
-
-```
-
-```{r}
-
-```

### 2020-09-15 PANCHANGE_data_preprocessing2020-07-15.Rmd
added difference between start of pandemic and prepandemic sign up questionnaire

@@
 Calculate the time difference between starting the COPING questionnaire and the beginning of the pandemic
-```{r time difference between starting the COP|NG questionnaire and the beginning of the pandemic}
+```{r time difference between starting the COPING questionnaire and the beginning of the pandemic}
 if(GLAD == TRUE | EDGI == TRUE | RAMP == TRUE | NBR == TRUE){
@@
     )
+}
+```
+
+Calculate the time difference between sign up questionnaire and the beginning of the pandemic
+```{r time difference between sign up and the beginning of the pandemic}
+if(GLAD == TRUE | EDGI == TRUE){
+# using date of pandemic as 23rd of March
+dat <- dat %>%
+  mutate(
+    time_diff_signup_lockdown_march_23 =
+        as.numeric(
+        difftime(           #this function does time1 - time2 as difftime(time1, time2...)
+          date_uk_lockdown_march_23,    # should be start date of the pandemic (time1)
+          startDate.prepandemic),    # should be start date for sign up questionnaire EDGI or GLAD (time2)
+          units = c("weeks")  #can also be "secs", "mins", "hours", "weeks"
+          )
+        )
+
+dat %>%
+  descr(
+    var = time_diff_signup_lockdown_march_23,
+    stats = "common"
+    )
+
+# using date as 1st of March  
+dat <- dat %>%
+  mutate(
+    time_diff_signup_awareness_march_1 =
+        as.numeric(
+        difftime(           #this function does time1 - time2 as difftime(time1, time2...)
+          date_higher_awareness_march_1,    # should be start date of the pandemic (time1)
+          startDate.prepandemic),    # should be start date for sign up questionnaire EDGI or GLAD (time2)
+          units = c("weeks")  #can also be "secs", "mins", "hours", "weeks"
+          )
+        )
+
+dat %>%
+  descr(
+    var = time_diff_signup_awareness_march_1,
+    stats = "common"
+    )
+
+# using date as 31st January
+
+dat <- dat %>%
+  mutate(
+    time_diff_signup_first_case_uk_jan_31 =
+        as.numeric(
+        difftime(           #this function does time1 - time2 as difftime(time1, time2...)
+          date_first_case_uk_january_31,    # should be start date of the pandemic (time1)
+          startDate.prepandemic),    # should be start date for sign up questionnaire EDGI or GLAD (time2)
+          units = c("weeks")  #can also be "secs", "mins", "hours", "weeks"
+          )
+        )
+
+dat %>%
+  descr(
+    var = time_diff_signup_first_case_uk_jan_31,
+    stats = "common"
+    )
+}
+```
+
+Testing 3, 6, and 9 months before pandemic
+```{r Testing 3, 6, and 6 months before pandemic}
+if(GLAD == TRUE | EDGI == TRUE){
+dat %>%
+  filter(time_diff_signup_lockdown_march_23 < 12) %>%
+  nrow()
+
+dat %>%
+  filter(time_diff_signup_lockdown_march_23 < 24) %>%
+  nrow()
+
+dat %>%
+  filter(time_diff_signup_lockdown_march_23 < 36) %>%
+  nrow()
+
+dat %>%
+  filter(time_diff_signup_awareness_march_1 < 12) %>%
+  nrow()
+
+dat %>%
+  filter(time_diff_signup_awareness_march_1 < 24) %>%
+  nrow()
+
+dat %>%
+  filter(time_diff_signup_awareness_march_1 < 36) %>%
+  nrow()
+
+dat %>%
+  filter(time_diff_signup_first_case_uk_jan_31 < 12) %>%
+  nrow()
+
+dat %>%
+  filter(time_diff_signup_first_case_uk_jan_31 < 24) %>%
+  nrow()
+
+dat %>%
+  filter(time_diff_signup_first_case_uk_jan_31 < 36) %>%
+  nrow()
 }

### 2020-09-15 PANCHANGE_analysis.Rmd
deleted the neurological stuff from the PANCHANGE_analysis script

--- 2020-09-08 PANCHANGE_analysis.Rmd
@@
 
+# COVID
+## Recode variable
+```{r covid test positive double}
+dat.raw <- dat.raw %>%
+  mutate(covid_test_positive_double_numeric =
+           case_when(
+             (respiratory.throat_swab_test_nose_numeric == 1 &
+               respiratory.results_antibody_test_numeric == 1) ~ 2,
+             respiratory.throat_swab_test_nose_numeric == 1 ~ 1,
+             respiratory.throat_swab_test_nose_numeric == 2 ~ 0,
+             respiratory.results_antibody_test_numeric == 1 ~ 1,
+             respiratory.results_antibody_test_numeric == 2 ~ 0
+           )
+         )
+
+dat.raw <- dat.raw %>%
+  mutate(covid_test_positive_double =
+           recode_factor(
+             covid_test_positive_double_numeric,
+             `0` = "Negative",
+             `1` = "Positive",
+             `2` = "Double positive"
+           )
+         )
+
+dat.raw %>%
+  freq(covid_test_positive_double)
+```
+
+```{r gad covid test positive}
+dat.raw <- dat.raw %>%
+  mutate(gad.covid_test_positive_numeric =
+           case_when(
+             (respiratory.throat_swab_test_nose_numeric == 1 &
+               respiratory.results_antibody_test_numeric == 1) ~ 1, # with two positive test results get coded as positive
+             respiratory.throat_swab_test_nose_numeric == 1 ~ 1,
+             respiratory.throat_swab_test_nose_numeric == 2 ~ 0,
+             respiratory.results_antibody_test_numeric == 1 ~ 1,
+             respiratory.results_antibody_test_numeric == 2 ~ 0
+           )
+         )
+
+dat.raw <- dat.raw %>%
+  mutate(covid_test_positive =
+           recode_factor(
+             gad.covid_test_positive_numeric,
+             `0` = "Negative",
+             `1` = "Positive"
+#             `2` = "Double positive"
+           )
+         )
+
+dat.raw %>%
+  freq(covid_test_positive)
+```
+
+## COVID swab test positive
+```{r COVID positive swap}
+dat.raw %>%
+  count(respiratory.throat_swab_test_nose, Sample) %>%
+  mutate(Prop = round(n/sum(n), 2))
+```
+
+## antibody test
+```{r COVID positive antibody test}
+dat.raw %>%
+  count(respiratory.results_antibody_test, Sample) %>%
+  mutate(Prop = round(n/sum(n), 2))
+```
+
+## COVID probable diagnosis
+```{r COVID probable diagnosis}
+dat.raw %>%
+  count(covid_probable_case_incl_screening, Sample) %>%
+  mutate(Prop = round(n/sum(n), 2))
+```
+
+## Cross table probable covid and covid test positive
+```{r Cross table probable covid and covid test positive}
+dat.raw %>%
+  count(covid_test_positive, covid_probable_case_incl_screening) %>%
+  spread(key = covid_test_positive, value = n)
+```
+
 # Exclusions

### 2020-09-15 PANCHANGE_analysis.Rmd
variable creation script

--- 2020-09-08 PANCHANGE_analysis.Rmd
@@
 palette = COPINGpalette2
-```
-
-# Data import
-
-## Source data file paths
-
-```{r source file path}
-#source data directory: data_path
-source("../PANCHANGE_raw_path.R")
-```
-
-## Read in data
-```{r read in data}
-dat.raw <- readRDS(file = paste0(data_path, "/four_cohorts.rds"))
-dim(dat.raw)
-colnames(dat.raw)
-```
-
-```{r dat.coping summary, eval=FALSE, include=FALSE}
-#summarytools::dfSummary(
-#  dat.raw,
-#  graph.col = F,
-#  valid.col = F,
-#  labels.col = F)
-```
-
-# Data availability
-
-Data availability GAD
-```{r gad availability}
-dat.raw %>%
-  freq(
-    data_group_gad,
-    cumul = F)
-```
-
-Data availability PHQ
-```{r phq availability}
-dat.raw %>%
-  freq(
-    data_group_phq,
-    cumul = F)
-```
-
-Data availability PCL
-```{r pcl availability}
-dat.raw %>%
-  freq(
-    data_group_pcl,
-    cumul = F)
-```
-
-Data availability OCI-R
-```{r ocir availability}
-dat.raw %>%
-  freq(
-    data_group_ocir,
-    cumul = F)
-```
-
-```{r sample frequencies}
-dat.raw %>%
-  freq(Sample)
-```
-
-# Exclusions
-
-Exclude GLAD/EDGI individuals that didn't take part in COPING
-Exclude individuals with NA for the MHD categories
-Individuals with NAs for age/gender have already been excluded in pre-processing script.
-
-++MD: There's an issue with the EDGI obsessive_compulsive_disorders variable. There are >400 NAs so we are only left with 78 EDGI participants in the dataset.
-```{r exclusion criteria for diagnoses analysis}
-dat <- dat.raw %>%
-  filter(
-    !is.na(depressive_disorders) &
-      !is.na(eating_disorders) &
-      !is.na(psychotic_disorders) &
-      !is.na(obsessive_compulsive_disorders) &
-      !is.na(autism_spectrum_disorder) &
-      !is.na(mhd.mania_hypomania_bipolar_or_manicdepression_numeric) &
-      !is.na(mhd.posttraumatic_stress_disorder_ptsd_numeric) &
-      !is.na(control)
-  ) %>% 
-  drop_na(startDate.coping)
-
-dim(dat.raw)
-dim(dat)
-
-```
-
-# Collapsing categories
-
-## age_category
-```{r Inspect age_category}
-dat %>%
-  freq(age_category)
-
-dat %>%
-  freq(age_category_numeric)
-```
-
-```{r Collapse age_category}
-dat <- dat %>%
-  mutate(age_category_collapsed_numeric =
-           case_when(
-             age_category_numeric == 1 ~ 0,
-             age_category_numeric == 2 ~ 1,
-             age_category_numeric == 3 ~ 2,
-             age_category_numeric == 4 ~ 3,
-             age_category_numeric == 5 ~ 4,
-             age_category_numeric == 6 ~ 5,
-             age_category_numeric == 7 ~ 6,
-             age_category_numeric == 8 ~ 7,
-             age_category_numeric == 9 ~ 8,
-             age_category_numeric == 10 ~ 8,
-             age_category_numeric == 11 ~ 8,
-             age_category_numeric == 12 ~ 8,
-             age_category_numeric == 13 ~ 8
-
-           )
-  )
-
-dat <- dat %>%
-  mutate(age_category_collapsed =
-           recode_factor(
-             age_category_collapsed_numeric,
-             `0` = "16-18",
-             `1` = "19-25",
-             `2` = "26-35",
-             `3` = "36-45",
-             `4` = "46-55",
-             `5` = "56-65",
-             `6` = "66-70",
-             `7` = "71-75",
-             `8` = "76+"
-           )
-  )
-
-dat %>%
-  freq(age_category_collapsed)
-```
-
-## Gender
-```{r Inspect Gender}
-dat %>%
-  freq(Gender)
-
-dat %>%
-  freq(Gender_numeric)
-```
-
-```{r Collapse Gender}
-dat <- dat %>%
-  mutate(Gender_collapsed_numeric =
-           case_when(
-             Gender_numeric == 0 ~ 0,
-             Gender_numeric == 1 ~ 1,
-             Gender_numeric == 2 ~ 2,
-             Gender_numeric == 3 ~ 2
-           )
-         )
-
-dat <- dat %>%
-  mutate(Gender_collapsed =
-           recode_factor(
-             Gender_collapsed_numeric,
-             `0` = "Male",
-             `1` = "Female",
-             `2` = "Non-binary/Self-defined"
-           )
-         )
-
-dat %>%
-  freq(Gender_collapsed)
-```
-
-## Ethnicity
-++MD: The ethnicity_numeric variable has more NAs (N = 14304) than the ethnicity categorical variable (N = 3568). Something strange must have happened during the conversion to numeric?
-```{r Inspect Ethnicity}
-dat %>%
-  freq(Ethnicity)
-
-dat %>%
-  freq(Ethnicity_numeric)
-
-```
-
-++MD: Need to decide what to do with the Arab grouping.
-++MD: Why is "Other ethnic group" recoded as Asian or Asian British?
-```{r Collapse Ethnicity}
-dat <- dat %>%
-  mutate(Ethnicity_collapsed_numeric =
-           case_when(
-             Ethnicity_numeric == 1 ~ 0, #European
-             Ethnicity_numeric == 2 ~ 1, #Mixed or multiple ethnic origins 
-             Ethnicity_numeric == 3 ~ 2, #Asian or Asian British
-             Ethnicity_numeric == 4 ~ 3, #African or African British
-             Ethnicity_numeric == 5 ~ 3, #Arab - combined with African/African British
-             Ethnicity_numeric == 6 ~ 4  #Other ethnic group
-           )
-  )
-
-dat <- dat %>%
-  mutate(Ethnicity_collapsed =
-           recode_factor(
-             Ethnicity_collapsed_numeric,
-             `0` = "European",
-             `1` = "Mixed or multiple ethnic origins",
-             `2` = "Asian or Asian British",
-             `3` = "African or African British",
-             `4` = "Other"
-           )
-  )
-
-dat %>%
-  freq(Ethnicity_collapsed)
-```
-
-# Vectors for sum_score
-
-```{r Vectors with sum_score_cols}
-sum_score_cols <- dat %>%
-  select(contains("sum_score")) %>%
-  select(-ends_with("raw")) %>%
-  colnames()
-
-sum_score_cols
-
-phq.sum_score_cols <- dat %>%
-  select(contains("phq")) %>%
-  select(contains("sum_score")) %>% 
-  select(-ends_with("raw")) %>%
-  select(-contains("8items")) %>%
-  colnames()
-
-phq.sum_score_cols
-
-gad.sum_score_cols <- dat %>%
-  select(contains("gad")) %>%
-  select(contains("sum_score")) %>% 
-  select(-ends_with("raw")) %>%
-  colnames()
-
-gad.sum_score_cols
-
-ocir.sum_score_cols <- dat %>%
-  select(contains("ocir")) %>%
-  select(contains("sum_score")) %>% 
-  select(-ends_with("raw")) %>%
-  colnames()
-
-ocir.sum_score_cols
-
-pcl.sum_score_cols <- dat %>%
-  select(contains("pcl")) %>%
-  select(contains("sum_score")) %>% 
-  select(-ends_with("raw")) %>%
-  colnames()
-
-pcl.sum_score_cols
-```
-
-# Vectors for diff_score
-
-```{r Vectors with diff_score_cols}
-diff_score_cols <- dat %>%
-  select(contains("diff_score")) %>% 
-  colnames()
-
-diff_score_cols
-
-phq.diff_score_cols <- dat %>%
-  select(contains("phq")) %>%
-  select(contains("diff_score")) %>% 
-  colnames()
-
-phq.diff_score_cols
-
-gad.diff_score_cols <- dat %>%
-  select(contains("gad")) %>%
-  select(contains("diff_score")) %>% 
-  colnames()
-
-gad.diff_score_cols
-
-ocir.diff_score_cols <- dat %>%
-  select(contains("ocir")) %>%
-  select(contains("diff_score")) %>% 
-  colnames()
-
-ocir.diff_score_cols
 ```
@@
 
-# Psychiatric disorder hierarchy
-- - - -
-OLD VERSIONS:
-control_numeric == 1 ~ 0,
-depressive_disorders_numeric == 1 ~ 1,
-anxiety_disorders_numeric == 1 ~ 2,
-mhd.posttraumatic_stress_disorder_ptsd_numeric == 1 ~ 3,
-eating_disorders_numeric == 1 ~ 4,
-obsessive_compulsive_disorders_numeric == 1 ~ 5,
-mhd.attention_deficit_hyperactivity_disorder_numeric == 1 ~ 6,
-mhd.personality_disorder_numeric == 1 ~ 7,
-autism_spectrum_disorder_numeric == 1 ~ 8,
-mhd.mania_hypomania_bipolar_or_manicdepression_numeric == 1 ~ 9,
-psychotic_disorders_numeric == 1 ~ 10
-
-psychotic_disorders_numeric == 1 ~ 10
-mhd.mania_hypomania_bipolar_or_manicdepression_numeric == 1 ~ 9,
-autism_spectrum_disorder_numeric == 1 ~ 8,
-mhd.personality_disorder_numeric == 1 ~ 7,
-mhd.attention_deficit_hyperactivity_disorder_numeric == 1 ~ 6,
-obsessive_compulsive_disorders_numeric == 1 ~ 5,
-eating_disorders_numeric == 1 ~ 4,
-mhd.posttraumatic_stress_disorder_ptsd_numeric == 1 ~ 3,
-anxiety_disorders_numeric == 1 ~ 2,
-depressive_disorders_numeric == 1 ~ 1,
-control_numeric == 1 ~ 0,
-- - - -
-
-Disorder hierarchy
-1: Psychotic disorders (create one with, create one without to test in analyses)
-2: Bipolar disorder
-3: MDD
-4: PTSD
-5: OCD
-6: Eating disorders
-7: Anxiety disorders
-
-```{r Psychiatric disorders hierarchy including psychosis}
-dat <- dat %>%
-  mutate(
-    Disorder_hierarchical_psychosis_numeric =
-      case_when(
-        psychotic_disorders_numeric == 1 ~ 7,
-        mhd.mania_hypomania_bipolar_or_manicdepression_numeric == 1 ~ 6,
-        depressive_disorders_numeric == 1 ~ 5,
-        mhd.posttraumatic_stress_disorder_ptsd_numeric == 1 ~ 4,
-        obsessive_compulsive_disorders_numeric == 1 ~ 3,
-        eating_disorders_numeric == 1 ~ 2,
-        anxiety_disorders_numeric == 1 ~ 1,
-        control_numeric == 1 ~ 0
-      )
-  )
-
-dat <- dat %>%
-  mutate(
-    Disorder_hierarchical_psychosis =
-      recode_factor(
-        Disorder_hierarchical_psychosis_numeric,
-        `0` = "Controls",
-        `1` = "Anxiety disorders",
-        `2` = "Eating disorders",
-        `3` = "OCDs",
-        `4` = "PTSD",
-        `5` = "Depressive disorders",
-        `6` = "Bipolar disorders",
-        `7` = "Psychotic disorders"
-      )
-  )
-
-dat %>%
-  freq(Disorder_hierarchical_psychosis)
-```
-
-```{r Psychiatric disorders hierarchy without psychosis}
-dat <- dat %>%
-  mutate(
-    Disorder_hierarchical_numeric =
-      case_when(
-        mhd.mania_hypomania_bipolar_or_manicdepression_numeric == 1 ~ 6,
-        depressive_disorders_numeric == 1 ~ 5,
-        mhd.posttraumatic_stress_disorder_ptsd_numeric == 1 ~ 4,
-        obsessive_compulsive_disorders_numeric == 1 ~ 3,
-        eating_disorders_numeric == 1 ~ 2,
-        anxiety_disorders_numeric == 1 ~ 1,
-        control_numeric == 1 ~ 0
-      )
-  )
-
-dat <- dat %>%
-  mutate(
-    Disorder_hierarchical =
-      recode_factor(
-        Disorder_hierarchical_numeric,
-        `0` = "Controls",
-        `1` = "Anxiety disorders",
-        `2` = "Eating disorders",
-        `3` = "OCDs",
-        `4` = "PTSD",
-        `5` = "Depressive disorders",
-        `6` = "Bipolar disorders"
-      )
-  )
-
-dat %>%
-  freq(Disorder_hierarchical) 
-dat %>% 
-  freq(Disorder_hierarchical_psychosis)
-```
-
-Investigate NAs 
-NAs are coded for individuals that don't have one of the listed disorders in the hierarchy, but who have another diagnosis that excludes them from being a control (e.g.
-personality disorder, ADHD, ASD).
-These individuals will be excluded from the analyses.
-```{r NAs in diagnosis}
-dat %>%
-  filter(is.na(Disorder_hierarchical)) %>%
-  freq(Sample)
-```
-
-Compare the GLAD/EDGI and COPING cohorts as a whole
-+++CH: Diagnosis, ethnicity, gender, age
-
-# age_category
-```{r age_category per Sample prop per total}
-age_category_per_Sample_prop_total <- dat %>%
-  count(age_category, Sample) %>%
-  mutate(Prop = round(n/sum(n), 2))
-
-kable(age_category_per_Sample_prop_total)
-age_category_per_Sample_prop_total
-```
-
-```{r age_category per Sample prop per Sample}
-age_category_per_Sample_prop_Sample <- dat %>%
-  group_by(Sample) %>%
-  count(age_category, Sample) %>%
-  mutate(Prop = round(n/sum(n), 2))
-
-kable(age_category_per_Sample_prop_Sample)
-age_category_per_Sample_prop_Sample
-```
-
-```{r age_category per Sample prop cross table}
-age_category_per_Sample_prop_Sample_cross_table <- dat %>%
-  group_by(Sample) %>%
-  count(age_category, Sample) %>%
-  mutate(Prop = round(n/sum(n), 2)) %>%
-  pivot_wider(names_from = Sample, values_from = c(n, Prop))
-
-kable(age_category_per_Sample_prop_Sample_cross_table)
-age_category_per_Sample_prop_Sample_cross_table
-```
-
-```{r age_category per Sample count cross table}
-age_category_per_Sample_count_cross_table <- dat %>%
-  count(age_category, Sample) %>%
-  spread(key = Sample, value = n) %>%
-  mutate(
-    EDGI = as.integer(replace_na(EDGI, 0)),
-    GLAD = as.integer(replace_na(GLAD, 0)),
-    NBR = as.integer(replace_na(NBR, 0)),
-    RAMP = as.integer(replace_na(RAMP, 0))
-  )
-
-kable(age_category_per_Sample_count_cross_table)
-age_category_per_Sample_count_cross_table
-```
-
-```{r age_category per Sample chisquare test}
-age_category_per_Sample_chissquare_test <- dat %>%
-  count(age_category, Sample) %>%
-  spread(key = Sample, value = n) %>%
-  select(-age_category) %>%
-  mutate(
-    EDGI = as.integer(replace_na(EDGI, 0)),
-    GLAD = as.integer(replace_na(GLAD, 0)),
-    NBR = as.integer(replace_na(NBR, 0)),
-    RAMP = as.integer(replace_na(RAMP, 0))
-  ) %>%
-  chisq.test() %>%
-  glance()
-
-kable(age_category_per_Sample_chissquare_test)
-age_category_per_Sample_chissquare_test
-```
-
-```{r age_category by Sample count plot}
-age_category_by_Sample_count_plot <- age_category_per_Sample_prop_Sample %>%
-  ggplot(mapping = aes(
-    x = age_category,
-    y = n)
-  ) +
-  geom_bar(
-    aes(fill = Sample),
-    stat="identity",
-    binwidth = 1,
-    position = position_dodge2(preserve = "single")
-  ) +
-  labs(
-    x = "age_category",
-    y = "Number of participants",
-    fill = "Sample") +
-  theme_personal +
-  scale_fill_manual(
-    values = COPINGpalette6
-  ) +
-  coord_flip()
-
-age_category_by_Sample_count_plot
-```
-
-```{r age_category by Sample prop plot}
-age_category_by_Sample_prop_plot <- age_category_per_Sample_prop_Sample %>%
-  ggplot(mapping = aes(
-    x = age_category,
-    y = Prop)
-  ) +
-  geom_bar(
-    aes(fill = Sample),
-    stat="identity",
-    binwidth = 1,
-    position = position_dodge2(preserve = "single")
-  ) +
-  labs(
-    x = "age_category",
-    y = "Percentage per sample",
-    fill = "Sample") +
-  theme_personal +
-  scale_fill_manual(
-    values = COPINGpalette6
-  ) +
-  coord_flip()
-
-age_category_by_Sample_prop_plot
-```
-
-age bar plot for whole sample (not grouped)
-
-Create a nice summary dataset for age and display it as a bar plot
-
-```{r age_category prop total (ungrouped)}
-
-age_category_prop_total <- dat %>%
-  count(age_category) %>%
-  mutate(Prop = round(n/sum(n), 2))
-
-# add a column to help order the factor
-age_category_prop_total$order <- c(1,2,3,4,5,6,7,8,9,10,11,12,13)
-
-# total responders
-ageN <- sum(age_category_prop_total$n)
-
-kable(age_category_prop_total)
-age_category_prop_total
-
-```
-
-```{r age_category prop total (ungrouped) plot}
-#Colour palette
-RAMPagepalette <- c(
-  "#00D9AC","#21D9B3","#4DD9BC","#78D9C5","#8ED9C9","#A3D9CE",
-  "#CFD9D7",
-  "#DAD0BA","#DAC38F","#DAC38F","#DAB663" ,"#DAA937","#DA9C0C")
-
-#Bar plot
-plot.age <-
-
-  age_category_prop_total %>%
-    mutate(age_category = fct_reorder(age_category,order)) %>%
-
-  ggplot(aes(x = age_category)) +
-  geom_bar(aes(y = n, color=age_category, fill=age_category, alpha = 1),
-           stat ="summary") +
-  scale_fill_manual(values =  RAMPagepalette) +
-  scale_color_manual(values =  RAMPagepalette) +
-  labs(x = "",
-       y = "Total count",
-       title = paste("Number of participants in each age category",sep=" "),
-       subtitle = paste("n = ", ageN,
-                        sep = ""),
-       fill = "Age category") +
-   guides(alpha = FALSE, color = FALSE, fill = FALSE) +
-  scale_x_discrete(limits = (levels(age_category_prop_total$age_category))) +
-  theme_classic2() +
-   theme(axis.text.x = element_text(colour="black", size = 12,angle=45,
-                                    vjust=0.5),
-        axis.text.y = element_text(colour="black", size = 12))
-
-plot.age
-
-```
-
-# Ethnicity_collapsed
-```{r Ethnicity_collapsed per Sample prop per total}
-Ethnicity_collapsed_per_Sample_prop_total <- dat %>%
-  count(Ethnicity_collapsed, Sample) %>%
-  mutate(Prop = round(n/sum(n), 2))
-
-kable(Ethnicity_collapsed_per_Sample_prop_total)
-Ethnicity_collapsed_per_Sample_prop_total
-```
-
-```{r Ethnicity_collapsed per Sample prop per Sample}
-Ethnicity_collapsed_per_Sample_prop_Sample <- dat %>%
-  group_by(Sample) %>%
-  count(Ethnicity_collapsed, Sample) %>%
-  mutate(Prop = round(n/sum(n), 2))
-
-kable(Ethnicity_collapsed_per_Sample_prop_Sample)
-Ethnicity_collapsed_per_Sample_prop_Sample
-```
-
-```{r Ethnicity_collapsed per Sample prop cross table}
-Ethnicity_collapsed_per_Sample_prop_Sample_cross_table <- dat %>%
-  group_by(Sample) %>%
-  count(Ethnicity_collapsed, Sample) %>%
-  mutate(Prop = round(n/sum(n), 2)) %>%
-  pivot_wider(names_from = Sample, values_from = c(n, Prop))
-
-kable(Ethnicity_collapsed_per_Sample_prop_Sample_cross_table)
-Ethnicity_collapsed_per_Sample_prop_Sample_cross_table
-```
-
-```{r Ethnicity_collapsed per Sample count cross table}
-Ethnicity_collapsed_per_Sample_count_cross_table <- dat %>%
-  count(Ethnicity_collapsed, Sample) %>%
-  spread(key = Sample, value = n) %>%
-  mutate(
-    EDGI = as.integer(replace_na(EDGI, 0)),
-    GLAD = as.integer(replace_na(GLAD, 0)),
-    NBR = as.integer(replace_na(NBR, 0)),
-    RAMP = as.integer(replace_na(RAMP, 0))
-  )
-
-kable(Ethnicity_collapsed_per_Sample_count_cross_table)
-Ethnicity_collapsed_per_Sample_count_cross_table
-```
-
-```{r Ethnicity_collapsed per Sample chisquare test}
-Ethnicity_collapsed_per_Sample_chissquare_test <- dat %>%
-  count(Ethnicity_collapsed, Sample) %>%
-  spread(key = Sample, value = n) %>%
-  select(-Ethnicity_collapsed) %>%
-  mutate(
-    EDGI = as.integer(replace_na(EDGI, 0)),
-    GLAD = as.integer(replace_na(GLAD, 0)),
-    NBR = as.integer(replace_na(NBR, 0)),
-    RAMP = as.integer(replace_na(RAMP, 0))
-  ) %>%
-  chisq.test() %>%
-  glance()
-
-kable(Ethnicity_collapsed_per_Sample_chissquare_test)
-Ethnicity_collapsed_per_Sample_chissquare_test
-```
-
-```{r Ethnicity_collapsed by Sample count plot}
-Ethnicity_collapsed_by_Sample_count_plot <- Ethnicity_collapsed_per_Sample_prop_Sample %>%
-  ggplot(mapping = aes(
-    x = Ethnicity_collapsed,
-    y = n)
-  ) +
-  geom_bar(
-    aes(fill = Sample),
-    stat="identity",
-    binwidth = 1,
-    position = position_dodge2(preserve = "single")
-  ) +
-  labs(
-    x = "Ethnicity_collapsed",
-    y = "Number of participants",
-    fill = "Sample") +
-  theme_personal +
-  scale_fill_manual(
-    values = COPINGpalette6
-  ) +
-  coord_flip()
-
-Ethnicity_collapsed_by_Sample_count_plot
-```
-
-```{r Ethnicity_collapsed by Sample prop plot}
-Ethnicity_collapsed_by_Sample_prop_plot <- Ethnicity_collapsed_per_Sample_prop_Sample %>%
-  ggplot(mapping = aes(
-    x = Ethnicity_collapsed,
-    y = Prop)
-  ) +
-  geom_bar(
-    aes(fill = Sample),
-    stat="identity",
-    binwidth = 1,
-    position = position_dodge2(preserve = "single")
-  ) +
-  labs(
-    x = "Ethnicity_collapsed",
-    y = "Percentage per sample",
-    fill = "Sample") +
-  theme_personal +
-  scale_fill_manual(
-    values = COPINGpalette6
-  ) +
-  coord_flip()
-
-Ethnicity_collapsed_by_Sample_prop_plot
-```
-
-### pie charts
-
-```{r Ethnicity_collapsed prop per total summary}
-
-Ethnicity_collapsed_prop_Sample <- dat %>%
-  count(Ethnicity_collapsed) %>%
-  drop_na() %>%
-  mutate(freq = round(n/sum(n), 2))
-
-# total responders
-ethN <- sum(Ethnicity_collapsed_prop_Sample$n)
-
-kable(Ethnicity_collapsed_prop_Sample)
-Ethnicity_collapsed_prop_Sample
-
-```
-
-pie chart with only European label
-
-```{r ethnicity pie chart biggest group label}
-
-eth_pie_alllabel <-
-
-  Ethnicity_collapsed_prop_Sample %>%
-   mutate(Ethnicity_collapsed = fct_reorder(Ethnicity_collapsed,-n)) %>%
-
-  ggplot(aes(x="", y=freq, fill=Ethnicity_collapsed)) +
-  geom_bar(width = 1, stat = "identity") +
-  scale_fill_manual(values =  COPINGpalette6) +
-  scale_color_manual(values =  COPINGpalette6) +
-  coord_polar("y",start=0) +
-  theme_void() +
-   labs(title = paste("RAMP/COPING sample self reported ethnicity",
-                      sep=" "),
-        subtitle = paste("n =", sum(Ethnicity_collapsed_prop_Sample$n),
-                         sep = " "),
-        fill = "Self reported ethnicity")  +
-    geom_text(aes(y = c(0.5),
-                  label= c(paste0(round((freq[1]*100),0),"%"))), #Frequency of European only
-             size=5,
-             face="bold"
-             )
-
-eth_pie_alllabel
-
-```
-
-pie chart - no labels
-
-```{r ethnicity pie chart no label}
-
-eth_pie <-
-
-    Ethnicity_collapsed_prop_Sample %>%
-   mutate(Ethnicity_collapsed = fct_reorder(Ethnicity_collapsed,-n)) %>%
-
-  ggplot(aes(x="", y=freq, fill=Ethnicity_collapsed)) +
-  geom_bar(width = 1, stat = "identity") +
-  scale_fill_manual(values =  COPINGpalette6) +
-  scale_color_manual(values =  COPINGpalette6) +
-  coord_polar("y",start=0) +
-  theme_void() +
-   labs(title = paste("RAMP/COPING sample self reported ethnicity",
-                      sep=" "),
-        subtitle = paste("n =", sum(Ethnicity_collapsed_prop_Sample$n),
-                         sep = " "),
-        fill = "Self reported ethnicity")
-
-eth_pie
-
-```
-
-# Gender_collapsed
-```{r Gender_collapsed per Sample prop per total}
-Gender_collapsed_per_Sample_prop_total <- dat %>%
-  count(Gender_collapsed, Sample) %>%
-  mutate(Prop = round(n/sum(n), 2))
-
-kable(Gender_collapsed_per_Sample_prop_total)
-Gender_collapsed_per_Sample_prop_total
-```
-
-```{r Gender_collapsed per Sample prop per Sample}
-Gender_collapsed_per_Sample_prop_Sample <- dat %>%
-  group_by(Sample) %>%
-  count(Gender_collapsed, Sample) %>%
-  mutate(Prop = round(n/sum(n), 2))
-
-kable(Gender_collapsed_per_Sample_prop_Sample)
-Gender_collapsed_per_Sample_prop_Sample
-```
-
-```{r Gender_collapsed per Sample prop cross table}
-Gender_collapsed_per_Sample_prop_Sample_cross_table <- dat %>%
-  group_by(Sample) %>%
-  count(Gender_collapsed, Sample) %>%
-  mutate(Prop = round(n/sum(n), 2)) %>%
-  pivot_wider(names_from = Sample, values_from = c(n, Prop))
-
-kable(Gender_collapsed_per_Sample_prop_Sample_cross_table)
-Gender_collapsed_per_Sample_prop_Sample_cross_table
-```
-
-```{r Gender_collapsed per Sample count cross table}
-Gender_collapsed_per_Sample_count_cross_table <- dat %>%
-  count(Gender_collapsed, Sample) %>%
-  spread(key = Sample, value = n) %>%
-  mutate(
-    EDGI = as.integer(replace_na(EDGI, 0)),
-    GLAD = as.integer(replace_na(GLAD, 0)),
-    NBR = as.integer(replace_na(NBR, 0)),
-    RAMP = as.integer(replace_na(RAMP, 0))
-  )
-
-kable(Gender_collapsed_per_Sample_count_cross_table)
-Gender_collapsed_per_Sample_count_cross_table
-```
-
-```{r Gender_collapsed per Sample chisquare test}
-Gender_collapsed_per_Sample_chissquare_test <- dat %>%
-  count(Gender_collapsed, Sample) %>%
-  spread(key = Sample, value = n) %>%
-  select(-Gender_collapsed) %>%
-  mutate(
-    EDGI = as.integer(replace_na(EDGI, 0)),
-    GLAD = as.integer(replace_na(GLAD, 0)),
-    NBR = as.integer(replace_na(NBR, 0)),
-    RAMP = as.integer(replace_na(RAMP, 0))
-  ) %>%
-  chisq.test() %>%
-  glance()
-
-kable(Gender_collapsed_per_Sample_chissquare_test)
-Gender_collapsed_per_Sample_chissquare_test
-```
-
-```{r Gender_collapsed by Sample count plot}
-Gender_collapsed_by_Sample_count_plot <- Gender_collapsed_per_Sample_prop_Sample %>%
-  ggplot(mapping = aes(
-    x = Gender_collapsed,
-    y = n)
-  ) +
-  geom_bar(
-    aes(fill = Sample),
-    stat="identity",
-    binwidth = 1,
-    position = position_dodge2(preserve = "single")
-  ) +
-  labs(
-    x = "Gender_collapsed",
-    y = "Number of participants",
-    fill = "Sample") +
-  theme_personal +
-  scale_fill_manual(
-    values = COPINGpalette6
-  ) +
-  coord_flip()
-
-Gender_collapsed_by_Sample_count_plot
-```
-
-```{r Gender_collapsed by Sample prop plot}
-Gender_collapsed_by_Sample_prop_plot <- Gender_collapsed_per_Sample_prop_Sample %>%
-  ggplot(mapping = aes(
-    x = Gender_collapsed,
-    y = Prop)
-  ) +
-  geom_bar(
-    aes(fill = Sample),
-    stat="identity",
-    binwidth = 1,
-    position = position_dodge2(preserve = "single")
-  ) +
-  labs(
-    x = "Gender_collapsed",
-    y = "Percentage per sample",
-    fill = "Sample") +
-  theme_personal +
-  scale_fill_manual(
-    values = COPINGpalette6
-  ) +
-  coord_flip()
-
-Gender_collapsed_by_Sample_prop_plot
-```
-
-### pie charts
-
-```{r Gender_collapsed prop per total}
-
-Gender_collapsed_prop_total <- dat %>%
-  count(Gender_collapsed) %>%
-  mutate(freq = round(n/sum(n), 2))
-
-kable(Gender_collapsed_prop_total)
-Gender_collapsed_prop_total
-
-```
-
-```{r gender pie chart - all labels}
-
-gen_pie_alllabel <- 
-  ggplot(Gender_collapsed_prop_total, aes(x="", y=freq, fill=Gender_collapsed)) +
-  geom_bar(width = 1, stat = "identity") +
-  scale_fill_manual(values =  COPINGpalette5) +
-  scale_color_manual(values =  COPINGpalette5) +
-  coord_polar("y",start=0) +
-  theme_void() +
-   labs(title = paste("RAMP/COPING sample self reported gender",
-                      sep=" "),
-        subtitle = paste("n", sum(Gender_collapsed_prop_total$n),
-                         sep = " "),
-        fill = "Self reported gender")  +
-    geom_text(aes(y = c(0.85,0.35,0),
-                  x = c(1.2,1.2,1.8),
-                  label= c(paste0(round((freq[1:2]*100),0),"%"),paste0(round((freq[3]*100),1),"%"))),
-             size=5,
-             face="bold"
-             )
-
-gen_pie_alllabel
-
-```
-
-pie chart - only labelling two largest groups (male and female)
-
-```{r gender pie chart - male/female labels only}
-
-gen_pie <- 
-  ggplot(Gender_collapsed_prop_total, aes(x="", y=freq, fill=Gender_collapsed)) +
-  geom_bar(width = 1, stat = "identity") +
-  scale_fill_manual(values =  COPINGpalette5) +
-  scale_color_manual(values =  COPINGpalette5) +
-  coord_polar("y",start=0) +
-  theme_void() +
-   labs(title = paste("RAMP/COPING sample self reported gender",
-                      sep=" "),
-        subtitle = paste("n", sum(Gender_collapsed_prop_total$n),
-                         sep = " "),
-        fill = "Self reported gender")  +
-    geom_text(aes(y = c(0.85,0.35,0),
-                  x = c(1.2,1.2,1.8),
-                  label= c(paste0(round((freq[1:2]*100),0),"%"),"")),
-             size=5,
-             face="bold"
-             )
-
-gen_pie
-
-```
-
-pie chart -  no labels
-
-```{r gender pie chart - no labels }
-
-gen_pie_nolabel <- 
-  ggplot(Gender_collapsed_prop_total, aes(x="", y=freq, fill=Gender_collapsed)) +
-  geom_bar(width = 1, stat = "identity") +
-  scale_fill_manual(values =  COPINGpalette5) +
-  scale_color_manual(values =  COPINGpalette5) +
-  coord_polar("y",start=0) +
-  theme_void() +
-   labs(title = paste("RAMP/COPING sample self reported gender",
-                      sep=" "),
-        subtitle = paste("n", sum(Gender_collapsed_prop_total$n),
-                         sep = " "),
-        fill = "Self reported gender")
-
-gen_pie_nolabel
-
-```
-
-# highest_education
-```{r highest_education per Sample prop per total}
-highest_education_per_Sample_prop_total <- dat %>%
-  count(highest_education, Sample) %>%
-  mutate(Prop = round(n/sum(n), 2))
-
-kable(highest_education_per_Sample_prop_total)
-highest_education_per_Sample_prop_total
-```
-
-```{r highest_education per Sample prop per Sample}
-highest_education_per_Sample_prop_Sample <- dat %>%
-  group_by(Sample) %>%
-  count(highest_education, Sample) %>%
-  mutate(Prop = round(n/sum(n), 2))
-
-kable(highest_education_per_Sample_prop_Sample)
-highest_education_per_Sample_prop_Sample
-```
-
-```{r highest_education per Sample prop cross table}
-highest_education_per_Sample_prop_Sample_cross_table <- dat %>%
-  group_by(Sample) %>%
-  count(highest_education, Sample) %>%
-  mutate(Prop = round(n/sum(n), 2)) %>%
-  pivot_wider(names_from = Sample, values_from = c(n, Prop))
-
-kable(highest_education_per_Sample_prop_Sample_cross_table)
-highest_education_per_Sample_prop_Sample_cross_table
-```
-
-```{r highest_education per Sample count cross table}
-highest_education_per_Sample_count_cross_table <- dat %>%
-  count(highest_education, Sample) %>%
-  spread(key = Sample, value = n) %>%
-  mutate(
-    EDGI = as.integer(replace_na(EDGI, 0)),
-    GLAD = as.integer(replace_na(GLAD, 0)),
-    NBR = as.integer(replace_na(NBR, 0)),
-    RAMP = as.integer(replace_na(RAMP, 0))
-  )
-
-kable(highest_education_per_Sample_count_cross_table)
-highest_education_per_Sample_count_cross_table
-```
-
-```{r highest_education per Sample chisquare test}
-highest_education_per_Sample_chissquare_test <- dat %>%
-  count(highest_education, Sample) %>%
-  spread(key = Sample, value = n) %>%
-  select(-highest_education) %>%
-  mutate(
-    EDGI = as.integer(replace_na(EDGI, 0)),
-    GLAD = as.integer(replace_na(GLAD, 0)),
-    NBR = as.integer(replace_na(NBR, 0)),
-    RAMP = as.integer(replace_na(RAMP, 0))
-  ) %>%
-  chisq.test() %>%
-  glance()
-
-kable(highest_education_per_Sample_chissquare_test)
-highest_education_per_Sample_chissquare_test
-```
-
-```{r highest_education by Sample count plot}
-highest_education_by_Sample_count_plot <- highest_education_per_Sample_prop_Sample %>%
-  ggplot(mapping = aes(
-    x = highest_education,
-    y = n)
-  ) +
-  geom_bar(
-    aes(fill = Sample),
-    stat="identity",
-    binwidth = 1,
-    position = position_dodge2(preserve = "single")
-  ) +
-  labs(
-    x = "highest_education",
-    y = "Number of participants",
-    fill = "Sample") +
-  theme_personal +
-  scale_fill_manual(
-    values = COPINGpalette6
-  ) +
-  coord_flip()
-
-highest_education_by_Sample_count_plot
-```
-
-```{r highest_education by Sample prop plot}
-highest_education_by_Sample_prop_plot <- highest_education_per_Sample_prop_Sample %>%
-  ggplot(mapping = aes(
-    x = highest_education,
-    y = Prop)
-  ) +
-  geom_bar(
-    aes(fill = Sample),
-    stat="identity",
-    binwidth = 1,
-    position = position_dodge2(preserve = "single")
-  ) +
-  labs(
-    x = "highest_education",
-    y = "Percentage per sample",
-    fill = "Sample") +
-  theme_personal +
-  scale_fill_manual(
-    values = COPINGpalette6
-  ) +
-  coord_flip()
-
-highest_education_by_Sample_prop_plot
-```
-
-### pie chart
-
-summary dataset with frequencies
-
-```{r highest education prop per total}
-
-highest_education_prop_total <- dat %>%
-  count(highest_education) %>%
-  mutate(freq = round(n/sum(n), 2)) %>% 
-  drop_na()
-
-kable(highest_education_prop_total)
-highest_education_prop_total
-
-# total responders
-eduN <- sum(highest_education_prop_total$n)
-
-edubindat <- dat %>%
-  mutate(demographics.education_binary =
-           case_when(
-             highest_education_numeric == "4" ~ "Bachelors or higher",
-             highest_education_numeric == "3" ~ "A-levels or lower",
-             highest_education_numeric == "2" ~ "A-levels or lower",
-             highest_education_numeric == "1" ~ "A-levels or lower"
-           )) %>%
-  count(demographics.education_binary) %>%
-  mutate(freq = round(n/sum(n), 2)) %>% 
-  drop_na()
-
-educatdat <- dat %>%
-  mutate(demographics.education_three = 
-           case_when(
-             highest_education_numeric == "4" ~ "Bachelors or higher",
-             highest_education_numeric == "3" ~ "A-levels",
-             highest_education_numeric == "1" ~ "GCSEs or lower"
-           )) %>%
-  count(demographics.education_three) %>%
-  mutate(freq = round(n/sum(n), 2)) %>% 
-  drop_na()
-
-```
-
-pie chart labels
-
-```{r education pie chart all labels}
-
-edu_pie_alllabel <-
-
-    highest_education_prop_total %>%
-    mutate(demographics.highest_level_of_education = fct_reorder(highest_education,-n)) %>%
-
-  ggplot(aes(x="", y=freq, fill=demographics.highest_level_of_education)) +
-  geom_bar(width = 1, stat = "identity") +
-  scale_fill_manual(values =  COPINGpalette7) +
-  scale_color_manual(values =  COPINGpalette7) +
-  coord_polar("y",start=0) +
-  theme_void() +
-   labs(title = paste("RAMP/COPING sample self reported level of education",
-                      sep=" "),
-        subtitle = paste("n", sum(highest_education_prop_total$n),
-                         sep = " "),
-        fill = "Self reported level of education")  +
-    geom_text(aes(y = c(0.13,0.04,0.3,0.65),
-                  x = c(1.2,1.2,1.2,1.2), #GCSE, NVQ, A-levels, university
-                  label= paste0(round((freq*100),0),"%")),
-             size=5,
-             face="bold"
-             )
-
-edu_pie_alllabel
-
-```
-
-```{r binary education pie chart all labels}
-
-edu_pie_binlabel <-
-
-    edubindat %>%
-    mutate(demographics.education_binary = fct_reorder(demographics.education_binary,-n)) %>%
-
-  ggplot(aes(x="", y=freq, fill=demographics.education_binary)) +
-  geom_bar(width = 1, stat = "identity") +
-  scale_fill_manual(values =  COPINGpalette7) +
-  scale_color_manual(values =  COPINGpalette7) +
-  coord_polar("y",start=0) +
-  theme_void() +
-   labs(title = paste("RAMP/COPING sample self reported highest level of education, above or below bachelor degree or equivalent",
-                      sep=" "),
-        subtitle = paste("n", sum(edubindat$n),
-                         sep = " "),
-        fill = "Self reported level of education")  +
-    geom_text(aes(y = c(0.25,0.75),
-                  label= paste0(round((freq*100),0),"%")),
-             size=5,
-             face="bold"
-             )
-
-edu_pie_binlabel
-
-```
-
-```{r 3 category education pie chart all labels}
-
-edu_pie_catlabel <-
-
-    educatdat %>%
-    mutate(demographics.education_three = fct_reorder(demographics.education_three,-n)) %>%
-
-  ggplot(aes(x="", y=freq, fill=demographics.education_three)) +
-  geom_bar(width = 1, stat = "identity") +
-  scale_fill_manual(values =  COPINGpalette7) +
-  scale_color_manual(values =  COPINGpalette7) +
-  coord_polar("y",start=0) +
-  theme_void() +
-   labs(title = paste("RAMP/COPING sample self reported highest level of education, above or below bachelor degree or equivalent",
-                      sep=" "),
-        subtitle = paste("n", sum(educatdat$n),
-                         sep = " "),
-        fill = "Self reported level of education")  +
-    geom_text(aes(y = c(0.23,0.65,0.05),
-                  label= c(paste0(round((freq[1:3]*100),0),"%")),
-             size=5,
-             face="bold"
-             ))
-
-edu_pie_catlabel
-
-```
-
-pie chart -  no labels
-
-```{r education pie chart no labels }
-
-edu_pie_nolabel <-
-
-  edu_pie_alllabel <-
-
-    highest_education_prop_total %>%
-    mutate(demographics.highest_level_of_education = fct_reorder(highest_education,-n)) %>%
-
-  ggplot(aes(x="", y=freq, fill=demographics.highest_level_of_education)) +
-  geom_bar(width = 1, stat = "identity") +
-  scale_fill_manual(values =  COPINGpalette7) +
-  scale_color_manual(values =  COPINGpalette7) +
-  coord_polar("y",start=0) +
-  theme_void() +
-   labs(title = paste("RAMP/COPING sample self reported level of education",
-                      sep=" "),
-        subtitle = paste("n", sum(highest_education_prop_total$n),
-                         sep = " "),
-        fill = "Self reported level of education")
-
-```
-
-# key_worker
-```{r key_worker per Sample prop per total}
-key_worker_per_Sample_prop_total <- dat %>%
-  count(key_worker, Sample) %>%
-  mutate(Prop = round(n/sum(n), 2))
-
-kable(key_worker_per_Sample_prop_total)
-key_worker_per_Sample_prop_total
-```
-
-```{r key_worker per Sample prop per Sample}
-key_worker_per_Sample_prop_Sample <- dat %>%
-  group_by(Sample) %>%
-  count(key_worker, Sample) %>%
-  mutate(Prop = round(n/sum(n), 2))
-
-kable(key_worker_per_Sample_prop_Sample)
-key_worker_per_Sample_prop_Sample
-```
-
-```{r key_worker per Sample prop cross table}
-key_worker_per_Sample_prop_Sample_cross_table <- dat %>%
-  group_by(Sample) %>%
-  count(key_worker, Sample) %>%
-  mutate(Prop = round(n/sum(n), 2)) %>%
-  pivot_wider(names_from = Sample, values_from = c(n, Prop))
-
-kable(key_worker_per_Sample_prop_Sample_cross_table)
-key_worker_per_Sample_prop_Sample_cross_table
-```
-
-```{r key_worker per Sample count cross table}
-key_worker_per_Sample_count_cross_table <- dat %>%
-  count(key_worker, Sample) %>%
-  spread(key = Sample, value = n) %>%
-  mutate(
-    EDGI = as.integer(replace_na(EDGI, 0)),
-    GLAD = as.integer(replace_na(GLAD, 0)),
-    NBR = as.integer(replace_na(NBR, 0)),
-    RAMP = as.integer(replace_na(RAMP, 0))
-  )
-
-kable(key_worker_per_Sample_count_cross_table)
-key_worker_per_Sample_count_cross_table
-```
-
-```{r key_worker per Sample chisquare test}
-key_worker_per_Sample_chissquare_test <- dat %>%
-  count(key_worker, Sample) %>%
-  spread(key = Sample, value = n) %>%
-  select(-key_worker) %>%
-  mutate(
-    EDGI = as.integer(replace_na(EDGI, 0)),
-    GLAD = as.integer(replace_na(GLAD, 0)),
-    NBR = as.integer(replace_na(NBR, 0)),
-    RAMP = as.integer(replace_na(RAMP, 0))
-  ) %>%
-  chisq.test() %>%
-  glance()
-
-kable(key_worker_per_Sample_chissquare_test)
-key_worker_per_Sample_chissquare_test
-```
-
-```{r key_worker by Sample count plot}
-key_worker_by_Sample_count_plot <- key_worker_per_Sample_prop_Sample %>%
-  ggplot(mapping = aes(
-    x = key_worker,
-    y = n)
-  ) +
-  geom_bar(
-    aes(fill = Sample),
-    stat="identity",
-    binwidth = 1,
-    position = position_dodge2(preserve = "single")
-  ) +
-  labs(
-    x = "key_worker",
-    y = "Number of participants",
-    fill = "Sample") +
-  theme_personal +
-  scale_fill_manual(
-    values = COPINGpalette6
-  ) +
-  coord_flip()
-
-key_worker_by_Sample_count_plot
-```
-
-```{r key_worker by Sample prop plot}
-key_worker_by_Sample_prop_plot <- key_worker_per_Sample_prop_Sample %>%
-  ggplot(mapping = aes(
-    x = key_worker,
-    y = Prop)
-  ) +
-  geom_bar(
-    aes(fill = Sample),
-    stat="identity",
-    binwidth = 1,
-    position = position_dodge2(preserve = "single")
-  ) +
-  labs(
-    x = "key_worker",
-    y = "Percentage per sample",
-    fill = "Sample") +
-  theme_personal +
-  scale_fill_manual(
-    values = COPINGpalette6
-  ) +
-  coord_flip()
-
-key_worker_by_Sample_prop_plot
-```
-
-# COVID
-## Recode variable
-```{r covid test positive double}
-dat <- dat %>%
-  mutate(covid_test_positive_double_numeric =
-           case_when(
-             (respiratory.throat_swab_test_nose_numeric == 1 &
-               respiratory.results_antibody_test_numeric == 1) ~ 2,
-             respiratory.throat_swab_test_nose_numeric == 1 ~ 1,
-             respiratory.throat_swab_test_nose_numeric == 2 ~ 0,
-             respiratory.results_antibody_test_numeric == 1 ~ 1,
-             respiratory.results_antibody_test_numeric == 2 ~ 0
-           )
-         )
-
-dat <- dat %>%
-  mutate(covid_test_positive_double =
-           recode_factor(
-             covid_test_positive_double_numeric,
-             `0` = "Negative",
-             `1` = "Positive",
-             `2` = "Double positive"
-           )
-         )
-
-dat %>%
-  freq(covid_test_positive_double)
-```
-
-```{r gad covid test positive}
-dat <- dat %>%
-  mutate(gad.covid_test_positive_numeric =
-           case_when(
-             (respiratory.throat_swab_test_nose_numeric == 1 &
-               respiratory.results_antibody_test_numeric == 1) ~ 1, # with two positive test results get coded as positive
-             respiratory.throat_swab_test_nose_numeric == 1 ~ 1,
-             respiratory.throat_swab_test_nose_numeric == 2 ~ 0,
-             respiratory.results_antibody_test_numeric == 1 ~ 1,
-             respiratory.results_antibody_test_numeric == 2 ~ 0
-           )
-         )
-
-dat <- dat %>%
-  mutate(covid_test_positive =
-           recode_factor(
-             gad.covid_test_positive_numeric,
-             `0` = "Negative",
-             `1` = "Positive"
-#             `2` = "Double positive"
-           )
-         )
-
-dat %>%
-  freq(covid_test_positive)
-```
-
-## COVID swab test positive
-```{r COVID positive swap}
-dat %>%
-  count(respiratory.throat_swab_test_nose, Sample) %>%
-  mutate(Prop = round(n/sum(n), 2))
-```
-
-## antibody test
-```{r COVID positive antibody test}
-dat %>%
-  count(respiratory.results_antibody_test, Sample) %>%
-  mutate(Prop = round(n/sum(n), 2))
-```
-
-## COVID probable diagnosis
-```{r COVID probable diagnosis}
-dat %>%
-  count(covid_probable_case_incl_screening, Sample) %>%
-  mutate(Prop = round(n/sum(n), 2))
-```
-
-## Cross table probable covid and covid test positive
-```{r Cross table probable covid and covid test positive}
-dat %>%
-  count(covid_test_positive, covid_probable_case_incl_screening) %>%
-  spread(key = covid_test_positive, value = n)
-```
-
-# Create data set per measure
-++MD: Do we want to break up the datasets by measure?
-I think the datasets we've already specified should be sufficient.
-I've tested the results of the regression model and it's the same using dat.gad vs.
-dat datasets.
-
-## GAD
-```{r}
-dat.gad <- dat %>%
-#  drop_na() %>%
-  filter(
-    (data_group_gad == "Baseline and retrospective data" |
-      data_group_gad == "Prepandemic and baseline data" |
-      data_group_gad == "All prepandemic, baseline and retrospective data")
-  )
-
-dim(dat.gad)
+# Data import
+
+## Source data file paths
+
+```{r source file path}
+#source data directory: data_path
+source("../PANCHANGE_raw_path.R")
+```
+
+## Read in data
+```{r read in data}
+dat.raw <- readRDS(file = paste0(data_path, "/four_cohorts.rds"))
+dim(dat.raw)
+colnames(dat.raw)
+```
+
+# Vectors for sum_score
+
+```{r Vectors with sum_score_cols}
+sum_score_cols <- dat %>%
+  select(contains("sum_score")) %>%
+  select(-ends_with("raw")) %>%
+  colnames()
+
+sum_score_cols
+
+phq.sum_score_cols <- dat %>%
+  select(contains("phq")) %>%
+  select(contains("sum_score")) %>% 
+  select(-ends_with("raw")) %>%
+  select(-contains("8items")) %>%
+  colnames()
+
+phq.sum_score_cols
+
+gad.sum_score_cols <- dat %>%
+  select(contains("gad")) %>%
+  select(contains("sum_score")) %>% 
+  select(-ends_with("raw")) %>%
+  colnames()
+
+gad.sum_score_cols
+
+ocir.sum_score_cols <- dat %>%
+  select(contains("ocir")) %>%
+  select(contains("sum_score")) %>% 
+  select(-ends_with("raw")) %>%
+  colnames()
+
+ocir.sum_score_cols
+
+pcl.sum_score_cols <- dat %>%
+  select(contains("pcl")) %>%
+  select(contains("sum_score")) %>% 
+  select(-ends_with("raw")) %>%
+  colnames()
+
+pcl.sum_score_cols
+```
+
+# Vectors for diff_score
+
+```{r Vectors with diff_score_cols}
+diff_score_cols <- dat %>%
+  select(contains("diff_score")) %>% 
+  colnames()
+
+diff_score_cols
+
+phq.diff_score_cols <- dat %>%
+  select(contains("phq")) %>%
+  select(contains("diff_score")) %>% 
+  colnames()
+
+phq.diff_score_cols
+
+gad.diff_score_cols <- dat %>%
+  select(contains("gad")) %>%
+  select(contains("diff_score")) %>% 
+  colnames()
+
+gad.diff_score_cols
+
+ocir.diff_score_cols <- dat %>%
+  select(contains("ocir")) %>%
+  select(contains("diff_score")) %>% 
+  colnames()
+
+ocir.diff_score_cols
 ```
@@
 ## gad
-
-### Split sample in improvement and worsening
-```{r gad improvment worsening stratification}
-dat <- dat %>%
-  mutate(gad.change_binary_numeric =
-           case_when(
-             gad.pandemic_felt_feelings_numeric == 1 ~ 1,
-             gad.pandemic_felt_feelings_numeric == 2 ~ 1,
-             gad.pandemic_felt_feelings_numeric == 3 ~ 0,
-             gad.pandemic_felt_feelings_numeric == 4 ~ 2,
-             gad.pandemic_felt_feelings_numeric == 5 ~ 2
-           )
-         )
-
-dat <- dat %>%
-  mutate(gad.change_binary =
-           recode_factor(
-             gad.change_binary_numeric,
-             `0` = "No change",
-             `1` = "Worsening",
-             `2` = "Improvement"
-           )
-         )
-
-dat %>%
-  freq(gad.change_binary)
-```
-
 ### Summary scores
@@
 
-### Split sample in improvement and worsening
-```{r phq improvment worsening stratification}
-dat <- dat %>%
-  mutate(phq.change_binary_numeric =
-           case_when(
-             phq.pandemic_felt_feelings_numeric == 1 ~ 1,
-             phq.pandemic_felt_feelings_numeric == 2 ~ 1,
-             phq.pandemic_felt_feelings_numeric == 3 ~ 0,
-             phq.pandemic_felt_feelings_numeric == 4 ~ 2,
-             phq.pandemic_felt_feelings_numeric == 5 ~ 2
-           )
-  )
-
-dat <- dat %>%
-  mutate(phq.change_binary =
-           recode_factor(
-             phq.change_binary_numeric,
-             `0` = "No change",
-             `1` = "Worsening",
-             `2` = "Improvement"
-           )
-  )
-
-dat %>%
-  freq(phq.change_binary)
-```
-
 ### Summary scores
@@
 ## ocir
-
-### Split sample in improvement and worsening
-```{r ocir improvment worsening stratification}
-dat <- dat %>%
-  mutate(ocir.change_binary_numeric =
-           case_when(
-             ocir.felt_pandemic_feelings_numeric == 1 ~ 1,
-             ocir.felt_pandemic_feelings_numeric == 2 ~ 1,
-             ocir.felt_pandemic_feelings_numeric == 3 ~ 0,
-             ocir.felt_pandemic_feelings_numeric == 4 ~ 2,
-             ocir.felt_pandemic_feelings_numeric == 5 ~ 2
-           )
-  )
-
-dat <- dat %>%
-  mutate(ocir.change_binary =
-           recode_factor(
-             ocir.change_binary_numeric,
-             `0` = "No change",
-             `1` = "Worsening",
-             `2` = "Improvement"
-           )
-  )
-
-dat %>%
-  freq(ocir.change_binary)
-```
 
@@
 
-# Psychiatric disorders
-
-```{r disorders total count}
-dat %>%
-  freq(disorders_total_count)
-```
-
-```{r psychiatric disorders frequencies}
-#Ppts with least one psychiatric disorder
-dat %>%
-  count(disorders_total_count >= 1)
-
-#Ppts with anxiety OR depressive disorder
-dat %>% 
-  count(anxiety_disorders_numeric == 1 | depressive_disorders == 1)
-
-#Ppts with anxiety & depression
-dat %>% 
-  count(depression_and_anxiety_numeric == 1)
-```
-
-## Vector
-```{r vector with psychiatric disorders}
-disorder_columns <- c(
-  "control_numeric",  
-  "depressive_disorders_numeric",
-    "anxiety_disorders_numeric",
-    "mhd.posttraumatic_stress_disorder_ptsd_numeric",
-    "eating_disorders_numeric",
-    "obsessive_compulsive_disorders_numeric",
-    "mhd.attention_deficit_hyperactivity_disorder_numeric",
-    "mhd.personality_disorder_numeric",
-    "autism_spectrum_disorder_numeric",
-    "mhd.mania_hypomania_bipolar_or_manicdepression_numeric",
-    "psychotic_disorders_numeric"
-)
-```
-
-## Correlation matrix
-```{r Correlation matrix of psychiatric disorders}
-# Select items for correlation matrix
-mhd.items <- c(
-    "depressive_disorders",
-    "anxiety_disorders",
-    "eating_disorders",
-    "obsessive_compulsive_disorders",
-    "psychotic_disorders",
-    "mhd.mania_hypomania_bipolar_or_manicdepression",
-    "mhd.posttraumatic_stress_disorder_ptsd",
-    "autism_spectrum_disorder",
-    "mhd.attention_deficit_hyperactivity_disorder",
-    "mhd.personality_disorder",
-    "control"
-)
-
-# Calculate correlation matrix on specific columns (variables) from your data frame
-mhd.corr.mat <- hetcor(
-  as.data.frame(dat[,mhd.items]), # Specify the data
-  use = "pairwise.complete.obs" # Use all pairwise observations
-)
-
-# Print the correlation matrix
-print(mhd.corr.mat, digits = max(3, getOption("digits") - 3))
-
-# Save the correlations from the correlation matrix in an object
-mhd.corr.matrix <- as.matrix(mhd.corr.mat)
-
-# Save the p values from the correlation matrix in an object
-mhd.p.matrix <- as.matrix(mhd.corr.mat$tests)
-```
-
-Create the correlation matrix plot using the corrplot package
-```{r Correlation matrix of psychiatric disorders plot, fig.height=7}
-corrplot(mhd.corr.matrix, 
-         method = "color", # objects to represent the correlations on plot
-         type = "lower", # only use the lower triangle of the matrix
-         diag = FALSE, # do not show the correlations on the diagonal
-         addgrid.col = NA,
-         addCoef.col = "black", # colour for the correlation coefficients in the plot
-         tl.cex = 0.8,
-         tl.col = "black",
-         col=colorRampPalette(c("dodgerblue4","white","firebrick4"))(200), # colours for correlations
-         # Combine with significance
-         p.mat = mhd.p.matrix, # Matrix with p values
-         sig.level = 0.01, # Choose significant level
-         insig = "blank" # Nonsignificant correlations have no colour
-         )
-```
-
-```{r gather to long format Disorder_hierarchical}
-dat.long.psych <- dat %>%
-  gather(
-    key = "Disorder_inc_raw",
-    value = "Diagnosis",
-    all_of(disorder_columns)) %>%
-  select(
-    ID,
-    Sample,
-    Gender_collapsed,
-    Ethnicity_collapsed,
-    all_of(diff_score_cols),
-    Disorder_inc_raw,
-    Diagnosis
-  ) %>%
-  mutate(Disorder_inc =
-           recode_factor(
-             Disorder_inc_raw,
-             anxiety_disorders_numeric = "Anxiety disorders",
-             depressive_disorders_numeric = "Depressive disorders",
-             eating_disorders_numeric = "Eating disorders",
-             obsessive_compulsive_disorders_numeric = "OCDs",
-             psychotic_disorders_numeric = "Psychotic disorders",
-             mhd.mania_hypomania_bipolar_or_manicdepression_numeric = "Bipolar disorders",
-             mhd.posttraumatic_stress_disorder_ptsd_numeric = "PTSD",
-             autism_spectrum_disorder_numeric = "Autism",
-             mhd.attention_deficit_hyperactivity_disorder_numeric = "ADHD",
-             mhd.personality_disorder_numeric = "Personality disorders",
-             control_numeric = "Controls"
-           ))
-
-head(dat.long.psych)
-```
-
-```{r Disorder_inc by Gender_collapsed}
-Disorder_inc_by_Gender_collapsed <- dat.long.psych %>%
-  filter(Diagnosis == 1) %>%
-  count(Disorder_inc, Gender_collapsed) %>%
-  mutate(Prop = round(n/sum(n), 2))
-
-Disorder_inc_by_Gender_collapsed
-```
-
-```{r Disorder_inc by Gender_collapsed prop}
-Disorder_inc_by_Gender_collapsed <- dat.long.psych %>%
-  group_by(Disorder_inc) %>%
-  filter(Diagnosis == 1) %>%
-  count(Gender_collapsed) %>%
-  mutate(Prop = round(n/sum(n), 2))
-
-Disorder_inc_by_Gender_collapsed
-```
-
-```{r Disorder_inc by Gender_collapsed count plot}
-Disorder_inc_by_Gender_collapsed_count_plot <- Disorder_inc_by_Gender_collapsed %>%
-  ggplot(mapping = aes(
-    x = Disorder_inc,
-    y = n)
-    ) +
-  geom_bar(
-    aes(fill = Gender_collapsed),
-    stat="identity",
-    binwidth = 1,
-    position = position_dodge2(preserve = "single")
-  ) +
-  labs(
-    x = "Disorders",
-    y = "Number of participants",
-    fill = "Gender_collapsed") +
-  theme_personal +
-  scale_fill_manual(
-    values = COPINGpalette4
-    ) +
-  coord_flip()
-
-Disorder_inc_by_Gender_collapsed_count_plot
-```
-
-```{r Disorder_inc by Gender_collapsed prop plot}
-Disorder_inc_by_Gender_collapsed_prop_plot <- Disorder_inc_by_Gender_collapsed %>%
-  ggplot(mapping = aes(
-    x = Disorder_inc,
-    y = Prop)
-    ) +
-  geom_bar(
-    aes(fill = Gender_collapsed),
-    stat="identity",
-    binwidth = 1,
-    position = position_dodge2(preserve = "single")
-  ) +
-  labs(
-    x = "Disorders",
-    y = "Number of participants",
-    fill = "Gender_collapsed") +
-  theme_personal +
-  scale_fill_manual(
-    values = COPINGpalette4
-    ) +
-  coord_flip()
-
-Disorder_inc_by_Gender_collapsed_prop_plot
-```
-
-100% bar per diagnosis with percentages of contribution per sample
-
-```{r Disorder_inc by Sample}
-Disorder_inc_by_Sample <- dat.long.psych %>%
-  filter(Diagnosis == 1) %>%
-  count(Disorder_inc, Sample)
-```
-
-```{r Disorder_inc by Sample plot}
-Disorder_inc_by_Sample %>%
-  ggplot(mapping = aes(
-    x = Disorder_inc,
-    y = n)
-    ) +
-  geom_bar(
-    aes(fill = Sample),
-#    position = "dodge",
-    stat="identity",
-    binwidth = 1,
-    position = position_dodge2(preserve = "single")
-  ) +
-  labs(
-    x = "Disorders",
-    y = "Number of participants",
-    fill = "Sample") +
-  theme_personal +
-  scale_fill_manual(
-    values = COPINGpalette4,
-#    labels = c("Prepandemic", "Retrospective")
-    ) +
-  coord_flip()
-```
-
-Ethnicity should be recoded
-European
-Mixed or multiple ethnic origins
-African or African British
-Asian or Asian British
-Arab
-```{r Disorder_inc by Ethnicity_collapsed}
-Disorder_inc_by_Ethnicity <- dat.long.psych %>%
-  filter(Diagnosis == 1) %>%
-  count(Disorder_inc, Ethnicity_collapsed) %>%
-  mutate(Prop = round(n/sum(n), 2))
-
-Disorder_inc_by_Ethnicity
-```
-
-```{r Disorder_inc by Ethnicity_collapsed plot}
-Disorder_inc_by_Ethnicity %>%
-  ggplot(mapping = aes(
-    x = Disorder_inc,
-    y = n)
-  ) +
-  geom_bar(
-    aes(fill = Ethnicity_collapsed),
-    #    position = "dodge",
-    stat="identity",
-    binwidth = 1,
-    position = position_dodge2(preserve = "single")
-  ) +
-  labs(
-    x = "Disorders",
-    y = "Number of participants",
-    fill = "Ethnicity_collapsed") +
-  theme_personal +
-  scale_fill_manual(
-    values = COPINGpalette6,
-    #    labels = c("Prepandemic", "Retrospective")
-  ) +
-  coord_flip()
-```
-
 # Create additional datasets for analyses
@@
 
-```{r RUBBISH 1}
-gad.diff_score_base_prepan_plot <- dat %>%
-  ggplot(mapping = aes(y = gad.diff_score_base_prepan)) +
-  geom_bar() +
-  theme_minimal()
-
-gad.diff_score_retro_prepan_plot <- dat %>%
-  ggplot(mapping = aes(y = gad.diff_score_retro_prepan)) +
-  geom_bar() +
-  theme_minimal()
-
-gad.diff_score_base_retro_plot <- dat %>%
-  ggplot(mapping = aes(y = gad.diff_score_base_retro)) +
-  geom_bar() +
-  theme_minimal()
-
-```
-
 ```{r RUBBISH 2, fig.height=7, fig.width=5}
@@
 ```
-
-Calculate mean change per disorder group 
-Disorders (9) 
-Sex 
-Age (13; RAMP; potentially collapse above 65 depending on group sizes) 
-Ethnicity groups (5; White European, Black (British), Asian, Arab, Mixed)
-
-```{r RUBBISH }
-#ADD
-```
-
-Calculate a variable PCL pandemic score 
-```{r}
-
-```
-
-If one item is highly endorsed due to pandemic -> exclude in sensitivity analysis 
-```{r}
-
-```
-
-Descriptives for reporting: "How different are these feelings to how you felt before the pandemic?’ on a 5-point scale (much worse, a little worse, no different, a little better, much better)."
-+++KLP: Discuss during the meeting if we use 3 or 5 categories
-```{r}
-
-```
-
-Replicate chunk above for retrospective reports. This will only be for people who say that have reported that there is a change in their scores. 
-*Discuss if we should include people who reported "no change" as repition of their current GAD, PHQ, PCL report*
-```{r}
-
-```
-
-```{r}
-
-```

### 2020-09-15 PANCHANGE_descriptives.Rmd
variable creation script

---
title: "PANCHANGE_descriptives"
author: "Katie Thompson, Topher Huebel, Molly Davies, Kirstin Purves"
date: Sys.Date()
output:  
  html_document:
    df_print: paged
    toc: yes
    toc_depth: 2
    toc_float:
      collapsed: false
    number_sections: false
    highlight: monochrome
    theme: cerulean
code_folding: show

html_notebook:
  theme: cerulean
toc: yes
---

This is the analysis script to prepare the data to run analyses for the project "Anxiety, depression and trauma symptom change during the COVID-19 pandemic: retrospective versus objective assessment" - Young et al (2020)

Script written by K Purves, K Thompson, C Huebel and M Davies.
Email: kirstin.purves@kcl.ac.uk, katie.thompson@kcl.ac.uk, christopher.1.huebel@kcl.ac.uk, molly.davies@kcl.ac.uk

#Set up
```{r Setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      comment=NA,
                      prompt=FALSE,
                      cache=FALSE)

options(bitmapType = 'quartz') # to render fonts better
```

Clear global environment
```{r Clear global environment}
remove(list = ls())
```

Retrieve the current date to use it for file endings to not overwrite files when one exports files
```{r Recent date}
date = Sys.Date()
```

#Packages
Install packages (if they are not available in your version of R)
```{r Installing packages}
#install.packages("summarytools")
#install.packages("tidyverse")
#install.packages("psych")
#install.packages("broom")
#install.packages("skimr")
#install.packages("polycor")
#install.packages("corrplot")
#install.packages("patchwork")
#instlal.packages("ggpubr")
```

Load packages
```{r Load packages}
library(knitr)
library(summarytools)
library(psych)
library(polycor)
library(corrplot)
library(patchwork)
library(broom)
library(tidyverse)
library(ggpubr)
```

# Colour palettes
Define colours for plotting this are the standard coping colours
```{r Colour palettes: COPING}
COPINGpalette2 <- c("#78D9C5",
                    "#F5BE5E")

COPINGpalette3 <- c("#78D9C5",
                    "#F5BE5E",
                    "#EEB6E9")

COPINGpalette4 <- c("#78D9C5",
                    "#F5BE5E",
                    "#EEB6E9",
                    "#DBDB73")

COPINGpalette5 <- c("#78D9C5",
                    "#F5BE5E",
                    "#EEB6E9",
                    "#DBDB73", 
                    "#FFED98")

COPINGpalette6 <- c("#78D9C5",
                    "#F5BE5E",
                    "#EEB6E9",
                    "#DBDB73",
                    "#FFED98",
                    "#BFD2EB")

COPINGpalette7 <- c("#78D9C5",
                    "#F5BE5E",
                    "#EEB6E9",
                    "#DBDB73", 
                    "#FFED98",
                    "#BFD2EB", 
                    "#808080")

COPINGpaletteGRAD <- c("#F5BE5E",
                       "#FFD284",
                       "#FFEED1",
                       "#B5B5B5",
                       "#DEFFF8",
                       "#94F6E1",
                       "#78D9C5")

COPINGNeuCenterpalette <- c("#78D9C5",
                            "#808080",
                            "#F5BE5E")

RAMPworseGRADpalette <- c("#78D9C5",
                          "#FFEED1",
                          "#F5BE5E",
                          "#FFB1B5")
GLADpalette = c("#efc00b", 
                "#b7dee8")  
```

Choose in this chunk which palette to use
04.07.2020 - Default to 2 colour COPING palette
```{r Choose colour palette}
palette = COPINGpalette2
```

# ggplot theme
Set up ggplot theme for the plots
```{r ggplot theme}
theme_personal <-  theme(
    text = element_text(color = "black"),
    axis.title = element_text(color = "black"),
    axis.text = element_text(color = "black"),
    axis.title.y = element_blank(), 
    legend.background = element_blank(),
    legend.box.background = element_blank(),
    panel.background = element_blank(), 
    panel.grid.minor.x = element_blank(),
    panel.grid.major.x = element_line(
      colour = "gray",
      linetype = "dashed",
      size = 0.2
      ),
    axis.ticks = element_blank()
    )
```

# Data import

## Source data file paths

```{r source file path}
#source data directory: data_path
source("../PANCHANGE_raw_path.R")
```

## Read in data
```{r read in data}
dat.raw <- readRDS(file = paste0(data_path, "/four_cohorts.rds")) # NEEDS CHANGING TO THE DATA SET THAT COMES OUT OF THE VARIABLE CREATION
dim(dat.raw)
colnames(dat.raw)
```

# Exclusions

Exclude GLAD/EDGI individuals that didn't take part in COPING
Exclude individuals with NA for the MHD categories
Individuals with NAs for age/gender have already been excluded in pre-processing script.

```{r exclusion criteria for diagnoses analysis}
dat <- dat.raw %>%
  filter(
    !is.na(depressive_disorders) &
      !is.na(eating_disorders) &
      !is.na(psychotic_disorders) &
      !is.na(obsessive_compulsive_disorders) &
      !is.na(autism_spectrum_disorder) &
      !is.na(mhd.mania_hypomania_bipolar_or_manicdepression_numeric) &
      !is.na(mhd.posttraumatic_stress_disorder_ptsd_numeric) &
      !is.na(control)
  ) %>% 
  drop_na(startDate.coping)

dim(dat.raw)
dim(dat)
nrow(dat.raw)-nrow(dat)
```

# Data availability per questionnaire GAD, PHQ, PCL, and OCI-R

Data availability GAD
```{r gad availability}
dat.raw %>%
  freq(
    data_group_gad,
    cumul = F)
```

Data availability PHQ
```{r phq availability}
dat.raw %>%
  freq(
    data_group_phq,
    cumul = F)
```

Data availability PCL
```{r pcl availability}
dat.raw %>%
  freq(
    data_group_pcl,
    cumul = F)
```

Data availability OCI-R
```{r ocir availability}
dat.raw %>%
  freq(
    data_group_ocir,
    cumul = F)
```

# Whole sample

## Participants per Sample
Eating Disorders Genetics Initative
Genetic Links to Anxiety and Depression
National BioResource
Rapid Assessment of MP
```{r sample frequencies}
dat %>%
  freq(Sample)
```

## Age categories

Age bar plot for whole sample (not grouped)
Summary dataset for age and display it as a bar plot
```{r age_category prop total (ungrouped)}
age_category_prop_total <- dat %>%
  count(age_category) %>%
  mutate(Prop = round(n/sum(n), 2))

# add a column to help order the factor
age_category_prop_total$order <- c(1,2,3,4,5,6,7,8,9,10,11,12,13)

# total responders
ageN <- sum(age_category_prop_total$n)

kable(age_category_prop_total)
age_category_prop_total
```

```{r age_category prop total (ungrouped) plot}
#Colour palette
RAMPagepalette <- c(
  "#00D9AC","#21D9B3","#4DD9BC","#78D9C5","#8ED9C9","#A3D9CE",
  "#CFD9D7",
  "#DAD0BA","#DAC38F","#DAC38F","#DAB663" ,"#DAA937","#DA9C0C")

#Bar plot
plot.age <- 
  age_category_prop_total %>%
    mutate(age_category = fct_reorder(age_category,order)) %>%

  ggplot(aes(x = age_category)) +
  geom_bar(aes(y = n, color=age_category, fill=age_category, alpha = 1),
           stat ="summary") +
  scale_fill_manual(values =  RAMPagepalette) +
  scale_color_manual(values =  RAMPagepalette) +
  labs(x = "",
       y = "Total count",
       title = paste("Number of participants in each age category",sep=" "),
       subtitle = paste("n = ", ageN,
                        sep = ""),
       fill = "Age category") +
   guides(alpha = FALSE, color = FALSE, fill = FALSE) +
  scale_x_discrete(limits = (levels(age_category_prop_total$age_category))) +
  theme_classic2() +
   theme(axis.text.x = element_text(colour="black", size = 12,angle=45,
                                    vjust=0.5),
        axis.text.y = element_text(colour="black", size = 12))

plot.age
```

# Compare the GLAD/EDGI and COPING subcohorts: EDGI, GLAD, NBR, RAMP
+++CH: Diagnosis, ethnicity, gender, age

# age_category
```{r age_category per Sample prop per total}
age_category_per_Sample_prop_total <- dat %>%
  count(age_category, Sample) %>%
  mutate(Prop = round(n/sum(n), 2))

kable(age_category_per_Sample_prop_total)
age_category_per_Sample_prop_total
```

```{r age_category per Sample prop per Sample}
age_category_per_Sample_prop_Sample <- dat %>%
  group_by(Sample) %>%
  count(age_category, Sample) %>%
  mutate(Prop = round(n/sum(n), 2))

kable(age_category_per_Sample_prop_Sample)
age_category_per_Sample_prop_Sample
```

```{r age_category per Sample prop cross table}
age_category_per_Sample_prop_Sample_cross_table <- dat %>%
  group_by(Sample) %>%
  count(age_category, Sample) %>%
  mutate(Prop = round(n/sum(n), 2)) %>%
  pivot_wider(names_from = Sample, values_from = c(n, Prop))

kable(age_category_per_Sample_prop_Sample_cross_table)
age_category_per_Sample_prop_Sample_cross_table
```

```{r age_category per Sample count cross table}
age_category_per_Sample_count_cross_table <- dat %>%
  count(age_category, Sample) %>%
  spread(key = Sample, value = n) %>%
  mutate(
    EDGI = as.integer(replace_na(EDGI, 0)),
    GLAD = as.integer(replace_na(GLAD, 0)),
    NBR = as.integer(replace_na(NBR, 0)),
    RAMP = as.integer(replace_na(RAMP, 0))
  )

kable(age_category_per_Sample_count_cross_table)
age_category_per_Sample_count_cross_table
```

```{r age_category per Sample chisquare test}
age_category_per_Sample_chissquare_test <- dat %>%
  count(age_category, Sample) %>%
  spread(key = Sample, value = n) %>%
  select(-age_category) %>%
  mutate(
    EDGI = as.integer(replace_na(EDGI, 0)),
    GLAD = as.integer(replace_na(GLAD, 0)),
    NBR = as.integer(replace_na(NBR, 0)),
    RAMP = as.integer(replace_na(RAMP, 0))
  ) %>%
  chisq.test() %>%
  glance()

kable(age_category_per_Sample_chissquare_test)
age_category_per_Sample_chissquare_test
```

```{r age_category by Sample count plot}
age_category_by_Sample_count_plot <- age_category_per_Sample_prop_Sample %>%
  ggplot(mapping = aes(
    x = age_category,
    y = n)
  ) +
  geom_bar(
    aes(fill = Sample),
    stat="identity",
    binwidth = 1,
    position = position_dodge2(preserve = "single")
  ) +
  labs(
    x = "age_category",
    y = "Number of participants",
    fill = "Sample") +
  theme_personal +
  scale_fill_manual(
    values = COPINGpalette6
  ) +
  coord_flip()

age_category_by_Sample_count_plot
```

```{r age_category by Sample prop plot}
age_category_by_Sample_prop_plot <- age_category_per_Sample_prop_Sample %>%
  ggplot(mapping = aes(
    x = age_category,
    y = Prop)
  ) +
  geom_bar(
    aes(fill = Sample),
    stat="identity",
    binwidth = 1,
    position = position_dodge2(preserve = "single")
  ) +
  labs(
    x = "age_category",
    y = "Percentage per sample",
    fill = "Sample") +
  theme_personal +
  scale_fill_manual(
    values = COPINGpalette6
  ) +
  coord_flip()

age_category_by_Sample_prop_plot
```

# Ethnicity_collapsed
```{r Ethnicity_collapsed per Sample prop per total}
Ethnicity_collapsed_per_Sample_prop_total <- dat %>%
  count(Ethnicity_collapsed, Sample) %>%
  mutate(Prop = round(n/sum(n), 2))

kable(Ethnicity_collapsed_per_Sample_prop_total)
Ethnicity_collapsed_per_Sample_prop_total
```

```{r Ethnicity_collapsed per Sample prop per Sample}
Ethnicity_collapsed_per_Sample_prop_Sample <- dat %>%
  group_by(Sample) %>%
  count(Ethnicity_collapsed, Sample) %>%
  mutate(Prop = round(n/sum(n), 2))

kable(Ethnicity_collapsed_per_Sample_prop_Sample)
Ethnicity_collapsed_per_Sample_prop_Sample
```

```{r Ethnicity_collapsed per Sample prop cross table}
Ethnicity_collapsed_per_Sample_prop_Sample_cross_table <- dat %>%
  group_by(Sample) %>%
  count(Ethnicity_collapsed, Sample) %>%
  mutate(Prop = round(n/sum(n), 2)) %>%
  pivot_wider(names_from = Sample, values_from = c(n, Prop))

kable(Ethnicity_collapsed_per_Sample_prop_Sample_cross_table)
Ethnicity_collapsed_per_Sample_prop_Sample_cross_table
```

```{r Ethnicity_collapsed per Sample count cross table}
Ethnicity_collapsed_per_Sample_count_cross_table <- dat %>%
  count(Ethnicity_collapsed, Sample) %>%
  spread(key = Sample, value = n) %>%
  mutate(
    EDGI = as.integer(replace_na(EDGI, 0)),
    GLAD = as.integer(replace_na(GLAD, 0)),
    NBR = as.integer(replace_na(NBR, 0)),
    RAMP = as.integer(replace_na(RAMP, 0))
  )

kable(Ethnicity_collapsed_per_Sample_count_cross_table)
Ethnicity_collapsed_per_Sample_count_cross_table
```

```{r Ethnicity_collapsed per Sample chisquare test}
Ethnicity_collapsed_per_Sample_chissquare_test <- dat %>%
  count(Ethnicity_collapsed, Sample) %>%
  spread(key = Sample, value = n) %>%
  select(-Ethnicity_collapsed) %>%
  mutate(
    EDGI = as.integer(replace_na(EDGI, 0)),
    GLAD = as.integer(replace_na(GLAD, 0)),
    NBR = as.integer(replace_na(NBR, 0)),
    RAMP = as.integer(replace_na(RAMP, 0))
  ) %>%
  chisq.test() %>%
  glance()

kable(Ethnicity_collapsed_per_Sample_chissquare_test)
Ethnicity_collapsed_per_Sample_chissquare_test
```

```{r Ethnicity_collapsed by Sample count plot}
Ethnicity_collapsed_by_Sample_count_plot <- Ethnicity_collapsed_per_Sample_prop_Sample %>%
  ggplot(mapping = aes(
    x = Ethnicity_collapsed,
    y = n)
  ) +
  geom_bar(
    aes(fill = Sample),
    stat="identity",
    binwidth = 1,
    position = position_dodge2(preserve = "single")
  ) +
  labs(
    x = "Ethnicity_collapsed",
    y = "Number of participants",
    fill = "Sample") +
  theme_personal +
  scale_fill_manual(
    values = COPINGpalette6
  ) +
  coord_flip()

Ethnicity_collapsed_by_Sample_count_plot
```

```{r Ethnicity_collapsed by Sample prop plot}
Ethnicity_collapsed_by_Sample_prop_plot <- Ethnicity_collapsed_per_Sample_prop_Sample %>%
  ggplot(mapping = aes(
    x = Ethnicity_collapsed,
    y = Prop)
  ) +
  geom_bar(
    aes(fill = Sample),
    stat="identity",
    binwidth = 1,
    position = position_dodge2(preserve = "single")
  ) +
  labs(
    x = "Ethnicity_collapsed",
    y = "Percentage per sample",
    fill = "Sample") +
  theme_personal +
  scale_fill_manual(
    values = COPINGpalette6
  ) +
  coord_flip()

Ethnicity_collapsed_by_Sample_prop_plot
```

### pie charts

```{r Ethnicity_collapsed prop per total summary}

Ethnicity_collapsed_prop_Sample <- dat %>%
  count(Ethnicity_collapsed) %>%
  drop_na() %>%
  mutate(freq = round(n/sum(n), 2))

# total responders
ethN <- sum(Ethnicity_collapsed_prop_Sample$n)

kable(Ethnicity_collapsed_prop_Sample)
Ethnicity_collapsed_prop_Sample

```

pie chart with only European label

```{r ethnicity pie chart biggest group label}

eth_pie_alllabel <-

  Ethnicity_collapsed_prop_Sample %>%
   mutate(Ethnicity_collapsed = fct_reorder(Ethnicity_collapsed,-n)) %>%

  ggplot(aes(x="", y=freq, fill=Ethnicity_collapsed)) +
  geom_bar(width = 1, stat = "identity") +
  scale_fill_manual(values =  COPINGpalette6) +
  scale_color_manual(values =  COPINGpalette6) +
  coord_polar("y",start=0) +
  theme_void() +
   labs(title = paste("RAMP/COPING sample self reported ethnicity",
                      sep=" "),
        subtitle = paste("n =", sum(Ethnicity_collapsed_prop_Sample$n),
                         sep = " "),
        fill = "Self reported ethnicity")  +
    geom_text(aes(y = c(0.5),
                  label= c(paste0(round((freq[1]*100),0),"%"))), #Frequency of European only
             size=5,
             face="bold"
             )

eth_pie_alllabel

```

pie chart - no labels

```{r ethnicity pie chart no label}

eth_pie <-

    Ethnicity_collapsed_prop_Sample %>%
   mutate(Ethnicity_collapsed = fct_reorder(Ethnicity_collapsed,-n)) %>%

  ggplot(aes(x="", y=freq, fill=Ethnicity_collapsed)) +
  geom_bar(width = 1, stat = "identity") +
  scale_fill_manual(values =  COPINGpalette6) +
  scale_color_manual(values =  COPINGpalette6) +
  coord_polar("y",start=0) +
  theme_void() +
   labs(title = paste("RAMP/COPING sample self reported ethnicity",
                      sep=" "),
        subtitle = paste("n =", sum(Ethnicity_collapsed_prop_Sample$n),
                         sep = " "),
        fill = "Self reported ethnicity")

eth_pie

```

# Gender_collapsed
```{r Gender_collapsed per Sample prop per total}
Gender_collapsed_per_Sample_prop_total <- dat %>%
  count(Gender_collapsed, Sample) %>%
  mutate(Prop = round(n/sum(n), 2))

kable(Gender_collapsed_per_Sample_prop_total)
Gender_collapsed_per_Sample_prop_total
```

```{r Gender_collapsed per Sample prop per Sample}
Gender_collapsed_per_Sample_prop_Sample <- dat %>%
  group_by(Sample) %>%
  count(Gender_collapsed, Sample) %>%
  mutate(Prop = round(n/sum(n), 2))

kable(Gender_collapsed_per_Sample_prop_Sample)
Gender_collapsed_per_Sample_prop_Sample
```

```{r Gender_collapsed per Sample prop cross table}
Gender_collapsed_per_Sample_prop_Sample_cross_table <- dat %>%
  group_by(Sample) %>%
  count(Gender_collapsed, Sample) %>%
  mutate(Prop = round(n/sum(n), 2)) %>%
  pivot_wider(names_from = Sample, values_from = c(n, Prop))

kable(Gender_collapsed_per_Sample_prop_Sample_cross_table)
Gender_collapsed_per_Sample_prop_Sample_cross_table
```

```{r Gender_collapsed per Sample count cross table}
Gender_collapsed_per_Sample_count_cross_table <- dat %>%
  count(Gender_collapsed, Sample) %>%
  spread(key = Sample, value = n) %>%
  mutate(
    EDGI = as.integer(replace_na(EDGI, 0)),
    GLAD = as.integer(replace_na(GLAD, 0)),
    NBR = as.integer(replace_na(NBR, 0)),
    RAMP = as.integer(replace_na(RAMP, 0))
  )

kable(Gender_collapsed_per_Sample_count_cross_table)
Gender_collapsed_per_Sample_count_cross_table
```

```{r Gender_collapsed per Sample chisquare test}
Gender_collapsed_per_Sample_chissquare_test <- dat %>%
  count(Gender_collapsed, Sample) %>%
  spread(key = Sample, value = n) %>%
  select(-Gender_collapsed) %>%
  mutate(
    EDGI = as.integer(replace_na(EDGI, 0)),
    GLAD = as.integer(replace_na(GLAD, 0)),
    NBR = as.integer(replace_na(NBR, 0)),
    RAMP = as.integer(replace_na(RAMP, 0))
  ) %>%
  chisq.test() %>%
  glance()

kable(Gender_collapsed_per_Sample_chissquare_test)
Gender_collapsed_per_Sample_chissquare_test
```

```{r Gender_collapsed by Sample count plot}
Gender_collapsed_by_Sample_count_plot <- Gender_collapsed_per_Sample_prop_Sample %>%
  ggplot(mapping = aes(
    x = Gender_collapsed,
    y = n)
  ) +
  geom_bar(
    aes(fill = Sample),
    stat="identity",
    binwidth = 1,
    position = position_dodge2(preserve = "single")
  ) +
  labs(
    x = "Gender_collapsed",
    y = "Number of participants",
    fill = "Sample") +
  theme_personal +
  scale_fill_manual(
    values = COPINGpalette6
  ) +
  coord_flip()

Gender_collapsed_by_Sample_count_plot
```

```{r Gender_collapsed by Sample prop plot}
Gender_collapsed_by_Sample_prop_plot <- Gender_collapsed_per_Sample_prop_Sample %>%
  ggplot(mapping = aes(
    x = Gender_collapsed,
    y = Prop)
  ) +
  geom_bar(
    aes(fill = Sample),
    stat="identity",
    binwidth = 1,
    position = position_dodge2(preserve = "single")
  ) +
  labs(
    x = "Gender_collapsed",
    y = "Percentage per sample",
    fill = "Sample") +
  theme_personal +
  scale_fill_manual(
    values = COPINGpalette6
  ) +
  coord_flip()

Gender_collapsed_by_Sample_prop_plot
```

### pie charts

```{r Gender_collapsed prop per total}

Gender_collapsed_prop_total <- dat %>%
  count(Gender_collapsed) %>%
  mutate(freq = round(n/sum(n), 2))

kable(Gender_collapsed_prop_total)
Gender_collapsed_prop_total

```

```{r gender pie chart - all labels}

gen_pie_alllabel <- 
  ggplot(Gender_collapsed_prop_total, aes(x="", y=freq, fill=Gender_collapsed)) +
  geom_bar(width = 1, stat = "identity") +
  scale_fill_manual(values =  COPINGpalette5) +
  scale_color_manual(values =  COPINGpalette5) +
  coord_polar("y",start=0) +
  theme_void() +
   labs(title = paste("RAMP/COPING sample self reported gender",
                      sep=" "),
        subtitle = paste("n", sum(Gender_collapsed_prop_total$n),
                         sep = " "),
        fill = "Self reported gender")  +
    geom_text(aes(y = c(0.85,0.35,0),
                  x = c(1.2,1.2,1.8),
                  label= c(paste0(round((freq[1:2]*100),0),"%"),paste0(round((freq[3]*100),1),"%"))),
             size=5,
             face="bold"
             )

gen_pie_alllabel

```

pie chart - only labelling two largest groups (male and female)

```{r gender pie chart - male/female labels only}

gen_pie <- 
  ggplot(Gender_collapsed_prop_total, aes(x="", y=freq, fill=Gender_collapsed)) +
  geom_bar(width = 1, stat = "identity") +
  scale_fill_manual(values =  COPINGpalette5) +
  scale_color_manual(values =  COPINGpalette5) +
  coord_polar("y",start=0) +
  theme_void() +
   labs(title = paste("RAMP/COPING sample self reported gender",
                      sep=" "),
        subtitle = paste("n", sum(Gender_collapsed_prop_total$n),
                         sep = " "),
        fill = "Self reported gender")  +
    geom_text(aes(y = c(0.85,0.35,0),
                  x = c(1.2,1.2,1.8),
                  label= c(paste0(round((freq[1:2]*100),0),"%"),"")),
             size=5,
             face="bold"
             )

gen_pie

```

pie chart -  no labels

```{r gender pie chart - no labels }

gen_pie_nolabel <- 
  ggplot(Gender_collapsed_prop_total, aes(x="", y=freq, fill=Gender_collapsed)) +
  geom_bar(width = 1, stat = "identity") +
  scale_fill_manual(values =  COPINGpalette5) +
  scale_color_manual(values =  COPINGpalette5) +
  coord_polar("y",start=0) +
  theme_void() +
   labs(title = paste("RAMP/COPING sample self reported gender",
                      sep=" "),
        subtitle = paste("n", sum(Gender_collapsed_prop_total$n),
                         sep = " "),
        fill = "Self reported gender")

gen_pie_nolabel

```

# highest_education
```{r highest_education per Sample prop per total}
highest_education_per_Sample_prop_total <- dat %>%
  count(highest_education, Sample) %>%
  mutate(Prop = round(n/sum(n), 2))

kable(highest_education_per_Sample_prop_total)
highest_education_per_Sample_prop_total
```

```{r highest_education per Sample prop per Sample}
highest_education_per_Sample_prop_Sample <- dat %>%
  group_by(Sample) %>%
  count(highest_education, Sample) %>%
  mutate(Prop = round(n/sum(n), 2))

kable(highest_education_per_Sample_prop_Sample)
highest_education_per_Sample_prop_Sample
```

```{r highest_education per Sample prop cross table}
highest_education_per_Sample_prop_Sample_cross_table <- dat %>%
  group_by(Sample) %>%
  count(highest_education, Sample) %>%
  mutate(Prop = round(n/sum(n), 2)) %>%
  pivot_wider(names_from = Sample, values_from = c(n, Prop))

kable(highest_education_per_Sample_prop_Sample_cross_table)
highest_education_per_Sample_prop_Sample_cross_table
```

```{r highest_education per Sample count cross table}
highest_education_per_Sample_count_cross_table <- dat %>%
  count(highest_education, Sample) %>%
  spread(key = Sample, value = n) %>%
  mutate(
    EDGI = as.integer(replace_na(EDGI, 0)),
    GLAD = as.integer(replace_na(GLAD, 0)),
    NBR = as.integer(replace_na(NBR, 0)),
    RAMP = as.integer(replace_na(RAMP, 0))
  )

kable(highest_education_per_Sample_count_cross_table)
highest_education_per_Sample_count_cross_table
```

```{r highest_education per Sample chisquare test}
highest_education_per_Sample_chissquare_test <- dat %>%
  count(highest_education, Sample) %>%
  spread(key = Sample, value = n) %>%
  select(-highest_education) %>%
  mutate(
    EDGI = as.integer(replace_na(EDGI, 0)),
    GLAD = as.integer(replace_na(GLAD, 0)),
    NBR = as.integer(replace_na(NBR, 0)),
    RAMP = as.integer(replace_na(RAMP, 0))
  ) %>%
  chisq.test() %>%
  glance()

kable(highest_education_per_Sample_chissquare_test)
highest_education_per_Sample_chissquare_test
```

```{r highest_education by Sample count plot}
highest_education_by_Sample_count_plot <- highest_education_per_Sample_prop_Sample %>%
  ggplot(mapping = aes(
    x = highest_education,
    y = n)
  ) +
  geom_bar(
    aes(fill = Sample),
    stat="identity",
    binwidth = 1,
    position = position_dodge2(preserve = "single")
  ) +
  labs(
    x = "highest_education",
    y = "Number of participants",
    fill = "Sample") +
  theme_personal +
  scale_fill_manual(
    values = COPINGpalette6
  ) +
  coord_flip()

highest_education_by_Sample_count_plot
```

```{r highest_education by Sample prop plot}
highest_education_by_Sample_prop_plot <- highest_education_per_Sample_prop_Sample %>%
  ggplot(mapping = aes(
    x = highest_education,
    y = Prop)
  ) +
  geom_bar(
    aes(fill = Sample),
    stat="identity",
    binwidth = 1,
    position = position_dodge2(preserve = "single")
  ) +
  labs(
    x = "highest_education",
    y = "Percentage per sample",
    fill = "Sample") +
  theme_personal +
  scale_fill_manual(
    values = COPINGpalette6
  ) +
  coord_flip()

highest_education_by_Sample_prop_plot
```

### pie chart

summary dataset with frequencies

```{r highest education prop per total}

highest_education_prop_total <- dat %>%
  count(highest_education) %>%
  mutate(freq = round(n/sum(n), 2)) %>% 
  drop_na()

kable(highest_education_prop_total)
highest_education_prop_total

# total responders
eduN <- sum(highest_education_prop_total$n)

edubindat <- dat %>%
  mutate(demographics.education_binary =
           case_when(
             highest_education_numeric == "4" ~ "Bachelors or higher",
             highest_education_numeric == "3" ~ "A-levels or lower",
             highest_education_numeric == "2" ~ "A-levels or lower",
             highest_education_numeric == "1" ~ "A-levels or lower"
           )) %>%
  count(demographics.education_binary) %>%
  mutate(freq = round(n/sum(n), 2)) %>% 
  drop_na()

educatdat <- dat %>%
  mutate(demographics.education_three = 
           case_when(
             highest_education_numeric == "4" ~ "Bachelors or higher",
             highest_education_numeric == "3" ~ "A-levels",
             highest_education_numeric == "1" ~ "GCSEs or lower"
           )) %>%
  count(demographics.education_three) %>%
  mutate(freq = round(n/sum(n), 2)) %>% 
  drop_na()

```

pie chart labels

```{r education pie chart all labels}

edu_pie_alllabel <-

    highest_education_prop_total %>%
    mutate(demographics.highest_level_of_education = fct_reorder(highest_education,-n)) %>%

  ggplot(aes(x="", y=freq, fill=demographics.highest_level_of_education)) +
  geom_bar(width = 1, stat = "identity") +
  scale_fill_manual(values =  COPINGpalette7) +
  scale_color_manual(values =  COPINGpalette7) +
  coord_polar("y",start=0) +
  theme_void() +
   labs(title = paste("RAMP/COPING sample self reported level of education",
                      sep=" "),
        subtitle = paste("n", sum(highest_education_prop_total$n),
                         sep = " "),
        fill = "Self reported level of education")  +
    geom_text(aes(y = c(0.13,0.04,0.3,0.65),
                  x = c(1.2,1.2,1.2,1.2), #GCSE, NVQ, A-levels, university
                  label= paste0(round((freq*100),0),"%")),
             size=5,
             face="bold"
             )

edu_pie_alllabel

```

```{r binary education pie chart all labels}

edu_pie_binlabel <-

    edubindat %>%
    mutate(demographics.education_binary = fct_reorder(demographics.education_binary,-n)) %>%

  ggplot(aes(x="", y=freq, fill=demographics.education_binary)) +
  geom_bar(width = 1, stat = "identity") +
  scale_fill_manual(values =  COPINGpalette7) +
  scale_color_manual(values =  COPINGpalette7) +
  coord_polar("y",start=0) +
  theme_void() +
   labs(title = paste("RAMP/COPING sample self reported highest level of education, above or below bachelor degree or equivalent",
                      sep=" "),
        subtitle = paste("n", sum(edubindat$n),
                         sep = " "),
        fill = "Self reported level of education")  +
    geom_text(aes(y = c(0.25,0.75),
                  label= paste0(round((freq*100),0),"%")),
             size=5,
             face="bold"
             )

edu_pie_binlabel

```

```{r 3 category education pie chart all labels}

edu_pie_catlabel <-

    educatdat %>%
    mutate(demographics.education_three = fct_reorder(demographics.education_three,-n)) %>%

  ggplot(aes(x="", y=freq, fill=demographics.education_three)) +
  geom_bar(width = 1, stat = "identity") +
  scale_fill_manual(values =  COPINGpalette7) +
  scale_color_manual(values =  COPINGpalette7) +
  coord_polar("y",start=0) +
  theme_void() +
   labs(title = paste("RAMP/COPING sample self reported highest level of education, above or below bachelor degree or equivalent",
                      sep=" "),
        subtitle = paste("n", sum(educatdat$n),
                         sep = " "),
        fill = "Self reported level of education")  +
    geom_text(aes(y = c(0.23,0.65,0.05),
                  label= c(paste0(round((freq[1:3]*100),0),"%")),
             size=5,
             face="bold"
             ))

edu_pie_catlabel

```

pie chart -  no labels

```{r education pie chart no labels }

edu_pie_nolabel <-

  edu_pie_alllabel <-

    highest_education_prop_total %>%
    mutate(demographics.highest_level_of_education = fct_reorder(highest_education,-n)) %>%

  ggplot(aes(x="", y=freq, fill=demographics.highest_level_of_education)) +
  geom_bar(width = 1, stat = "identity") +
  scale_fill_manual(values =  COPINGpalette7) +
  scale_color_manual(values =  COPINGpalette7) +
  coord_polar("y",start=0) +
  theme_void() +
   labs(title = paste("RAMP/COPING sample self reported level of education",
                      sep=" "),
        subtitle = paste("n", sum(highest_education_prop_total$n),
                         sep = " "),
        fill = "Self reported level of education")

```

# key_worker
```{r key_worker per Sample prop per total}
key_worker_per_Sample_prop_total <- dat %>%
  count(key_worker, Sample) %>%
  mutate(Prop = round(n/sum(n), 2))

kable(key_worker_per_Sample_prop_total)
key_worker_per_Sample_prop_total
```

```{r key_worker per Sample prop per Sample}
key_worker_per_Sample_prop_Sample <- dat %>%
  group_by(Sample) %>%
  count(key_worker, Sample) %>%
  mutate(Prop = round(n/sum(n), 2))

kable(key_worker_per_Sample_prop_Sample)
key_worker_per_Sample_prop_Sample
```

```{r key_worker per Sample prop cross table}
key_worker_per_Sample_prop_Sample_cross_table <- dat %>%
  group_by(Sample) %>%
  count(key_worker, Sample) %>%
  mutate(Prop = round(n/sum(n), 2)) %>%
  pivot_wider(names_from = Sample, values_from = c(n, Prop))

kable(key_worker_per_Sample_prop_Sample_cross_table)
key_worker_per_Sample_prop_Sample_cross_table
```

```{r key_worker per Sample count cross table}
key_worker_per_Sample_count_cross_table <- dat %>%
  count(key_worker, Sample) %>%
  spread(key = Sample, value = n) %>%
  mutate(
    EDGI = as.integer(replace_na(EDGI, 0)),
    GLAD = as.integer(replace_na(GLAD, 0)),
    NBR = as.integer(replace_na(NBR, 0)),
    RAMP = as.integer(replace_na(RAMP, 0))
  )

kable(key_worker_per_Sample_count_cross_table)
key_worker_per_Sample_count_cross_table
```

```{r key_worker per Sample chisquare test}
key_worker_per_Sample_chissquare_test <- dat %>%
  count(key_worker, Sample) %>%
  spread(key = Sample, value = n) %>%
  select(-key_worker) %>%
  mutate(
    EDGI = as.integer(replace_na(EDGI, 0)),
    GLAD = as.integer(replace_na(GLAD, 0)),
    NBR = as.integer(replace_na(NBR, 0)),
    RAMP = as.integer(replace_na(RAMP, 0))
  ) %>%
  chisq.test() %>%
  glance()

kable(key_worker_per_Sample_chissquare_test)
key_worker_per_Sample_chissquare_test
```

```{r key_worker by Sample count plot}
key_worker_by_Sample_count_plot <- key_worker_per_Sample_prop_Sample %>%
  ggplot(mapping = aes(
    x = key_worker,
    y = n)
  ) +
  geom_bar(
    aes(fill = Sample),
    stat="identity",
    binwidth = 1,
    position = position_dodge2(preserve = "single")
  ) +
  labs(
    x = "key_worker",
    y = "Number of participants",
    fill = "Sample") +
  theme_personal +
  scale_fill_manual(
    values = COPINGpalette6
  ) +
  coord_flip()

key_worker_by_Sample_count_plot
```

```{r key_worker by Sample prop plot}
key_worker_by_Sample_prop_plot <- key_worker_per_Sample_prop_Sample %>%
  ggplot(mapping = aes(
    x = key_worker,
    y = Prop)
  ) +
  geom_bar(
    aes(fill = Sample),
    stat="identity",
    binwidth = 1,
    position = position_dodge2(preserve = "single")
  ) +
  labs(
    x = "key_worker",
    y = "Percentage per sample",
    fill = "Sample") +
  theme_personal +
  scale_fill_manual(
    values = COPINGpalette6
  ) +
  coord_flip()

key_worker_by_Sample_prop_plot
```

# Psychiatric disorders

```{r disorders total count}
dat %>%
  freq(disorders_total_count)
```

```{r psychiatric disorders frequencies}
#Ppts with least one psychiatric disorder
dat %>%
  count(disorders_total_count >= 1)

#Ppts with anxiety OR depressive disorder
dat %>% 
  count(anxiety_disorders_numeric == 1 | depressive_disorders == 1)

#Ppts with anxiety & depression
dat %>% 
  count(depression_and_anxiety_numeric == 1)
```

## Vector
```{r vector with psychiatric disorders}
disorder_columns <- c(
  "control_numeric",  
  "depressive_disorders_numeric",
    "anxiety_disorders_numeric",
    "mhd.posttraumatic_stress_disorder_ptsd_numeric",
    "eating_disorders_numeric",
    "obsessive_compulsive_disorders_numeric",
    "mhd.attention_deficit_hyperactivity_disorder_numeric",
    "mhd.personality_disorder_numeric",
    "autism_spectrum_disorder_numeric",
    "mhd.mania_hypomania_bipolar_or_manicdepression_numeric",
    "psychotic_disorders_numeric"
)
```

## Correlation matrix
```{r Correlation matrix of psychiatric disorders}
# Select items for correlation matrix
mhd.items <- c(
    "depressive_disorders",
    "anxiety_disorders",
    "eating_disorders",
    "obsessive_compulsive_disorders",
    "psychotic_disorders",
    "mhd.mania_hypomania_bipolar_or_manicdepression",
    "mhd.posttraumatic_stress_disorder_ptsd",
    "autism_spectrum_disorder",
    "mhd.attention_deficit_hyperactivity_disorder",
    "mhd.personality_disorder",
    "control"
)

# Calculate correlation matrix on specific columns (variables) from your data frame
mhd.corr.mat <- hetcor(
  as.data.frame(dat[,mhd.items]), # Specify the data
  use = "pairwise.complete.obs" # Use all pairwise observations
)

# Print the correlation matrix
print(mhd.corr.mat, digits = max(3, getOption("digits") - 3))

# Save the correlations from the correlation matrix in an object
mhd.corr.matrix <- as.matrix(mhd.corr.mat)

# Save the p values from the correlation matrix in an object
mhd.p.matrix <- as.matrix(mhd.corr.mat$tests)
```

Create the correlation matrix plot using the corrplot package
```{r Correlation matrix of psychiatric disorders plot, fig.height=7}
corrplot(mhd.corr.matrix, 
         method = "color", # objects to represent the correlations on plot
         type = "lower", # only use the lower triangle of the matrix
         diag = FALSE, # do not show the correlations on the diagonal
         addgrid.col = NA,
         addCoef.col = "black", # colour for the correlation coefficients in the plot
         tl.cex = 0.8,
         tl.col = "black",
         col=colorRampPalette(c("dodgerblue4","white","firebrick4"))(200), # colours for correlations
         # Combine with significance
         p.mat = mhd.p.matrix, # Matrix with p values
         sig.level = 0.01, # Choose significant level
         insig = "blank" # Nonsignificant correlations have no colour
         )
```

```{r gather to long format Disorder_hierarchical}
dat.long.psych <- dat %>%
  gather(
    key = "Disorder_inc_raw",
    value = "Diagnosis",
    all_of(disorder_columns)) %>%
  select(
    ID,
    Sample,
    Gender_collapsed,
    Ethnicity_collapsed,
    all_of(diff_score_cols),
    Disorder_inc_raw,
    Diagnosis
  ) %>%
  mutate(Disorder_inc =
           recode_factor(
             Disorder_inc_raw,
             anxiety_disorders_numeric = "Anxiety disorders",
             depressive_disorders_numeric = "Depressive disorders",
             eating_disorders_numeric = "Eating disorders",
             obsessive_compulsive_disorders_numeric = "OCDs",
             psychotic_disorders_numeric = "Psychotic disorders",
             mhd.mania_hypomania_bipolar_or_manicdepression_numeric = "Bipolar disorders",
             mhd.posttraumatic_stress_disorder_ptsd_numeric = "PTSD",
             autism_spectrum_disorder_numeric = "Autism",
             mhd.attention_deficit_hyperactivity_disorder_numeric = "ADHD",
             mhd.personality_disorder_numeric = "Personality disorders",
             control_numeric = "Controls"
           ))

head(dat.long.psych)
```

```{r Disorder_inc by Gender_collapsed}
Disorder_inc_by_Gender_collapsed <- dat.long.psych %>%
  filter(Diagnosis == 1) %>%
  count(Disorder_inc, Gender_collapsed) %>%
  mutate(Prop = round(n/sum(n), 2))

Disorder_inc_by_Gender_collapsed
```

```{r Disorder_inc by Gender_collapsed prop}
Disorder_inc_by_Gender_collapsed <- dat.long.psych %>%
  group_by(Disorder_inc) %>%
  filter(Diagnosis == 1) %>%
  count(Gender_collapsed) %>%
  mutate(Prop = round(n/sum(n), 2))

Disorder_inc_by_Gender_collapsed
```

```{r Disorder_inc by Gender_collapsed count plot}
Disorder_inc_by_Gender_collapsed_count_plot <- Disorder_inc_by_Gender_collapsed %>%
  ggplot(mapping = aes(
    x = Disorder_inc,
    y = n)
    ) +
  geom_bar(
    aes(fill = Gender_collapsed),
    stat="identity",
    binwidth = 1,
    position = position_dodge2(preserve = "single")
  ) +
  labs(
    x = "Disorders",
    y = "Number of participants",
    fill = "Gender_collapsed") +
  theme_personal +
  scale_fill_manual(
    values = COPINGpalette4
    ) +
  coord_flip()

Disorder_inc_by_Gender_collapsed_count_plot
```

```{r Disorder_inc by Gender_collapsed prop plot}
Disorder_inc_by_Gender_collapsed_prop_plot <- Disorder_inc_by_Gender_collapsed %>%
  ggplot(mapping = aes(
    x = Disorder_inc,
    y = Prop)
    ) +
  geom_bar(
    aes(fill = Gender_collapsed),
    stat="identity",
    binwidth = 1,
    position = position_dodge2(preserve = "single")
  ) +
  labs(
    x = "Disorders",
    y = "Number of participants",
    fill = "Gender_collapsed") +
  theme_personal +
  scale_fill_manual(
    values = COPINGpalette4
    ) +
  coord_flip()

Disorder_inc_by_Gender_collapsed_prop_plot
```

100% bar per diagnosis with percentages of contribution per sample

```{r Disorder_inc by Sample}
Disorder_inc_by_Sample <- dat.long.psych %>%
  filter(Diagnosis == 1) %>%
  count(Disorder_inc, Sample)
```

```{r Disorder_inc by Sample plot}
Disorder_inc_by_Sample %>%
  ggplot(mapping = aes(
    x = Disorder_inc,
    y = n)
    ) +
  geom_bar(
    aes(fill = Sample),
#    position = "dodge",
    stat="identity",
    binwidth = 1,
    position = position_dodge2(preserve = "single")
  ) +
  labs(
    x = "Disorders",
    y = "Number of participants",
    fill = "Sample") +
  theme_personal +
  scale_fill_manual(
    values = COPINGpalette4,
#    labels = c("Prepandemic", "Retrospective")
    ) +
  coord_flip()
```

```{r Disorder_inc by Ethnicity_collapsed}
Disorder_inc_by_Ethnicity <- dat.long.psych %>%
  filter(Diagnosis == 1) %>%
  count(Disorder_inc, Ethnicity_collapsed) %>%
  mutate(Prop = round(n/sum(n), 2))

Disorder_inc_by_Ethnicity
```

```{r Disorder_inc by Ethnicity_collapsed plot}
Disorder_inc_by_Ethnicity %>%
  ggplot(mapping = aes(
    x = Disorder_inc,
    y = n)
  ) +
  geom_bar(
    aes(fill = Ethnicity_collapsed),
    #    position = "dodge",
    stat="identity",
    binwidth = 1,
    position = position_dodge2(preserve = "single")
  ) +
  labs(
    x = "Disorders",
    y = "Number of participants",
    fill = "Ethnicity_collapsed") +
  theme_personal +
  scale_fill_manual(
    values = COPINGpalette6,
    #    labels = c("Prepandemic", "Retrospective")
  ) +
  coord_flip()
```

### 2020-09-15 PANCHANGE_variable_creation.Rmd
variable creation script

---
title: "PANCHANGE_variable_creation"
author: "Katie Thompson, Topher Huebel, Molly Davies, Kirstin Purves"
date: Sys.Date()
output:  
  html_document:
    df_print: paged
    toc: yes
    toc_depth: 2
    toc_float:
      collapsed: false
    number_sections: false
    highlight: monochrome
    theme: cerulean
code_folding: show

html_notebook:
  theme: cerulean
toc: yes
---

This is the analysis script to prepare the data to run analyses for the project "Anxiety, depression and trauma symptom change during the COVID-19 pandemic: retrospective versus objective assessment" - Young et al (2020)

Script written by K Purves, K Thompson, C Huebel and M Davies.
Email: kirstin.purves@kcl.ac.uk, katie.thompson@kcl.ac.uk, christopher.1.huebel@kcl.ac.uk, molly.davies@kcl.ac.uk

#Set up
```{r Setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      comment=NA,
                      prompt=FALSE,
                      cache=FALSE)

options(bitmapType = 'quartz') # to render fonts better
```

Clear global environment
```{r Clear global environment}
remove(list = ls())
```

Retrieve the current date to use it for file endings to not overwrite files when one exports files
```{r Recent date}
date = Sys.Date()
```

#Packages
Install packages (if they are not available in your version of R)
```{r Installing packages}
#install.packages("summarytools")
#install.packages("tidyverse")
#install.packages("psych")
#install.packages("broom")
#install.packages("skimr")
#install.packages("polycor")
#install.packages("corrplot")
#install.packages("patchwork")
#instlal.packages("ggpubr")
```

Load packages
```{r Load packages}
library(knitr)
library(summarytools)
library(psych)
library(polycor)
library(corrplot)
library(patchwork)
library(broom)
library(tidyverse)
library(ggpubr)
```

# Colour palettes
Define colours for plotting this are the standard coping colours
```{r Colour palettes: COPING}
COPINGpalette2 <- c("#78D9C5",
                    "#F5BE5E")

COPINGpalette3 <- c("#78D9C5",
                    "#F5BE5E",
                    "#EEB6E9")

COPINGpalette4 <- c("#78D9C5",
                    "#F5BE5E",
                    "#EEB6E9",
                    "#DBDB73")

COPINGpalette5 <- c("#78D9C5",
                    "#F5BE5E",
                    "#EEB6E9",
                    "#DBDB73", 
                    "#FFED98")

COPINGpalette6 <- c("#78D9C5",
                    "#F5BE5E",
                    "#EEB6E9",
                    "#DBDB73",
                    "#FFED98",
                    "#BFD2EB")

COPINGpalette7 <- c("#78D9C5",
                    "#F5BE5E",
                    "#EEB6E9",
                    "#DBDB73", 
                    "#FFED98",
                    "#BFD2EB", 
                    "#808080")

COPINGpaletteGRAD <- c("#F5BE5E",
                       "#FFD284",
                       "#FFEED1",
                       "#B5B5B5",
                       "#DEFFF8",
                       "#94F6E1",
                       "#78D9C5")

COPINGNeuCenterpalette <- c("#78D9C5",
                            "#808080",
                            "#F5BE5E")

RAMPworseGRADpalette <- c("#78D9C5",
                          "#FFEED1",
                          "#F5BE5E",
                          "#FFB1B5")
GLADpalette = c("#efc00b", 
                "#b7dee8")  
```

Choose in this chunk which palette to use
04.07.2020 - Default to 2 colour COPING palette
```{r Choose colour palette}
palette = COPINGpalette2
```

# ggplot theme
Set up ggplot theme for the plots
```{r ggplot theme}
theme_personal <-  theme(
    text = element_text(color = "black"),
    axis.title = element_text(color = "black"),
    axis.text = element_text(color = "black"),
    axis.title.y = element_blank(), 
    legend.background = element_blank(),
    legend.box.background = element_blank(),
    panel.background = element_blank(), 
    panel.grid.minor.x = element_blank(),
    panel.grid.major.x = element_line(
      colour = "gray",
      linetype = "dashed",
      size = 0.2
      ),
    axis.ticks = element_blank()
    )
```

# Data import

## Source data file paths

```{r source file path}
#source data directory: data_path
source("../PANCHANGE_raw_path.R")
```

## Read in data
```{r read in data}
dat.raw <- readRDS(file = paste0(data_path, "/four_cohorts.rds"))
dim(dat.raw)
colnames(dat.raw)
```

# COVID
## Recode variable
```{r covid test positive double}
dat.raw <- dat.raw %>%
  mutate(covid_test_positive_double_numeric =
           case_when(
             (respiratory.throat_swab_test_nose_numeric == 1 &
               respiratory.results_antibody_test_numeric == 1) ~ 2,
             respiratory.throat_swab_test_nose_numeric == 1 ~ 1,
             respiratory.throat_swab_test_nose_numeric == 2 ~ 0,
             respiratory.results_antibody_test_numeric == 1 ~ 1,
             respiratory.results_antibody_test_numeric == 2 ~ 0
           )
         )

dat.raw <- dat.raw %>%
  mutate(covid_test_positive_double =
           recode_factor(
             covid_test_positive_double_numeric,
             `0` = "Negative",
             `1` = "Positive",
             `2` = "Double positive"
           )
         )

dat.raw %>%
  freq(covid_test_positive_double)
```

```{r gad covid test positive}
dat.raw <- dat.raw %>%
  mutate(gad.covid_test_positive_numeric =
           case_when(
             (respiratory.throat_swab_test_nose_numeric == 1 &
               respiratory.results_antibody_test_numeric == 1) ~ 1, # with two positive test results get coded as positive
             respiratory.throat_swab_test_nose_numeric == 1 ~ 1,
             respiratory.throat_swab_test_nose_numeric == 2 ~ 0,
             respiratory.results_antibody_test_numeric == 1 ~ 1,
             respiratory.results_antibody_test_numeric == 2 ~ 0
           )
         )

dat.raw <- dat.raw %>%
  mutate(covid_test_positive =
           recode_factor(
             gad.covid_test_positive_numeric,
             `0` = "Negative",
             `1` = "Positive"
#             `2` = "Double positive"
           )
         )

dat.raw %>%
  freq(covid_test_positive)
```

## COVID swab test positive
```{r COVID positive swap}
dat.raw %>%
  count(respiratory.throat_swab_test_nose, Sample) %>%
  mutate(Prop = round(n/sum(n), 2))
```

## antibody test
```{r COVID positive antibody test}
dat.raw %>%
  count(respiratory.results_antibody_test, Sample) %>%
  mutate(Prop = round(n/sum(n), 2))
```

## COVID probable diagnosis
```{r COVID probable diagnosis}
dat.raw %>%
  count(covid_probable_case_incl_screening, Sample) %>%
  mutate(Prop = round(n/sum(n), 2))
```

## Cross table probable covid and covid test positive
```{r Cross table probable covid and covid test positive}
dat.raw %>%
  count(covid_test_positive, covid_probable_case_incl_screening) %>%
  spread(key = covid_test_positive, value = n)
```

# Collapsing categories

## age_category
```{r Inspect age_category}
dat %>%
  freq(age_category)

dat %>%
  freq(age_category_numeric)
```

```{r Collapse age_category}
dat <- dat %>%
  mutate(age_category_collapsed_numeric =
           case_when(
             age_category_numeric == 1 ~ 0,
             age_category_numeric == 2 ~ 1,
             age_category_numeric == 3 ~ 2,
             age_category_numeric == 4 ~ 3,
             age_category_numeric == 5 ~ 4,
             age_category_numeric == 6 ~ 5,
             age_category_numeric == 7 ~ 6,
             age_category_numeric == 8 ~ 7,
             age_category_numeric == 9 ~ 8,
             age_category_numeric == 10 ~ 8,
             age_category_numeric == 11 ~ 8,
             age_category_numeric == 12 ~ 8,
             age_category_numeric == 13 ~ 8

           )
  )

dat <- dat %>%
  mutate(age_category_collapsed =
           recode_factor(
             age_category_collapsed_numeric,
             `0` = "16-18",
             `1` = "19-25",
             `2` = "26-35",
             `3` = "36-45",
             `4` = "46-55",
             `5` = "56-65",
             `6` = "66-70",
             `7` = "71-75",
             `8` = "76+"
           )
  )

dat %>%
  freq(age_category_collapsed)
```

## Gender
```{r Inspect Gender}
dat %>%
  freq(Gender)

dat %>%
  freq(Gender_numeric)
```

```{r Collapse Gender}
dat <- dat %>%
  mutate(Gender_collapsed_numeric =
           case_when(
             Gender_numeric == 0 ~ 0,
             Gender_numeric == 1 ~ 1,
             Gender_numeric == 2 ~ 2,
             Gender_numeric == 3 ~ 2
           )
         )

dat <- dat %>%
  mutate(Gender_collapsed =
           recode_factor(
             Gender_collapsed_numeric,
             `0` = "Male",
             `1` = "Female",
             `2` = "Non-binary/Self-defined"
           )
         )

dat %>%
  freq(Gender_collapsed)
```

## Ethnicity
```{r Inspect Ethnicity}
dat %>%
  freq(Ethnicity)

dat %>%
  freq(Ethnicity_numeric)
```

```{r Collapse Ethnicity}
dat <- dat %>%
  mutate(Ethnicity_collapsed_numeric =
           case_when(
             Ethnicity_numeric == 1 ~ 0, #European
             Ethnicity_numeric == 2 ~ 1, #Mixed or multiple ethnic origins 
             Ethnicity_numeric == 3 ~ 2, #Asian or Asian British
             Ethnicity_numeric == 4 ~ 3, #African or African British
             Ethnicity_numeric == 5 ~ 3, #Arab - combined with African/African British
             Ethnicity_numeric == 6 ~ 4  #Other ethnic group
           )
  )

dat <- dat %>%
  mutate(Ethnicity_collapsed =
           recode_factor(
             Ethnicity_collapsed_numeric,
             `0` = "European",
             `1` = "Mixed or multiple ethnic origins",
             `2` = "Asian or Asian British",
             `3` = "African or African British",
             `4` = "Other"
           )
  )

dat %>%
  freq(Ethnicity_collapsed)
```

# Psychiatric disorder hierarchy
- - - -
OLD VERSIONS:
control_numeric == 1 ~ 0,
depressive_disorders_numeric == 1 ~ 1,
anxiety_disorders_numeric == 1 ~ 2,
mhd.posttraumatic_stress_disorder_ptsd_numeric == 1 ~ 3,
eating_disorders_numeric == 1 ~ 4,
obsessive_compulsive_disorders_numeric == 1 ~ 5,
mhd.attention_deficit_hyperactivity_disorder_numeric == 1 ~ 6,
mhd.personality_disorder_numeric == 1 ~ 7,
autism_spectrum_disorder_numeric == 1 ~ 8,
mhd.mania_hypomania_bipolar_or_manicdepression_numeric == 1 ~ 9,
psychotic_disorders_numeric == 1 ~ 10

psychotic_disorders_numeric == 1 ~ 10
mhd.mania_hypomania_bipolar_or_manicdepression_numeric == 1 ~ 9,
autism_spectrum_disorder_numeric == 1 ~ 8,
mhd.personality_disorder_numeric == 1 ~ 7,
mhd.attention_deficit_hyperactivity_disorder_numeric == 1 ~ 6,
obsessive_compulsive_disorders_numeric == 1 ~ 5,
eating_disorders_numeric == 1 ~ 4,
mhd.posttraumatic_stress_disorder_ptsd_numeric == 1 ~ 3,
anxiety_disorders_numeric == 1 ~ 2,
depressive_disorders_numeric == 1 ~ 1,
control_numeric == 1 ~ 0,
- - - -

Disorder hierarchy
1: Psychotic disorders (create one with, create one without to test in analyses)
2: Bipolar disorder
3: MDD
4: PTSD
5: OCD
6: Eating disorders
7: Anxiety disorders

```{r Psychiatric disorders hierarchy including psychosis}
dat <- dat %>%
  mutate(
    Disorder_hierarchical_psychosis_numeric =
      case_when(
        psychotic_disorders_numeric == 1 ~ 7,
        mhd.mania_hypomania_bipolar_or_manicdepression_numeric == 1 ~ 6,
        depressive_disorders_numeric == 1 ~ 5,
        mhd.posttraumatic_stress_disorder_ptsd_numeric == 1 ~ 4,
        obsessive_compulsive_disorders_numeric == 1 ~ 3,
        eating_disorders_numeric == 1 ~ 2,
        anxiety_disorders_numeric == 1 ~ 1,
        control_numeric == 1 ~ 0
      )
  )

dat <- dat %>%
  mutate(
    Disorder_hierarchical_psychosis =
      recode_factor(
        Disorder_hierarchical_psychosis_numeric,
        `0` = "Controls",
        `1` = "Anxiety disorders",
        `2` = "Eating disorders",
        `3` = "OCDs",
        `4` = "PTSD",
        `5` = "Depressive disorders",
        `6` = "Bipolar disorders",
        `7` = "Psychotic disorders"
      )
  )

dat %>%
  freq(Disorder_hierarchical_psychosis)
```

```{r Psychiatric disorders hierarchy without psychosis}
dat <- dat %>%
  mutate(
    Disorder_hierarchical_numeric =
      case_when(
        mhd.mania_hypomania_bipolar_or_manicdepression_numeric == 1 ~ 6,
        depressive_disorders_numeric == 1 ~ 5,
        mhd.posttraumatic_stress_disorder_ptsd_numeric == 1 ~ 4,
        obsessive_compulsive_disorders_numeric == 1 ~ 3,
        eating_disorders_numeric == 1 ~ 2,
        anxiety_disorders_numeric == 1 ~ 1,
        control_numeric == 1 ~ 0
      )
  )

dat <- dat %>%
  mutate(
    Disorder_hierarchical =
      recode_factor(
        Disorder_hierarchical_numeric,
        `0` = "Controls",
        `1` = "Anxiety disorders",
        `2` = "Eating disorders",
        `3` = "OCDs",
        `4` = "PTSD",
        `5` = "Depressive disorders",
        `6` = "Bipolar disorders"
      )
  )

dat %>%
  freq(Disorder_hierarchical) 
dat %>% 
  freq(Disorder_hierarchical_psychosis)
```

Investigate NAs 
NAs are coded for individuals that don't have one of the listed disorders in the hierarchy, but who have another diagnosis that excludes them from being a control (e.g. personality disorder, ADHD, ASD). These individuals will be excluded from the analyses.
```{r NAs in diagnosis}
dat %>%
  filter(is.na(Disorder_hierarchical)) %>%
  freq(Sample)
```

# Create variables for improvement and worsening

## gad
```{r gad improvment worsening stratification}
dat <- dat %>%
  mutate(gad.change_binary_numeric =
           case_when(
             gad.pandemic_felt_feelings_numeric == 1 ~ 1,
             gad.pandemic_felt_feelings_numeric == 2 ~ 1,
             gad.pandemic_felt_feelings_numeric == 3 ~ 0,
             gad.pandemic_felt_feelings_numeric == 4 ~ 2,
             gad.pandemic_felt_feelings_numeric == 5 ~ 2
           )
         )

dat <- dat %>%
  mutate(gad.change_binary =
           recode_factor(
             gad.change_binary_numeric,
             `0` = "No change",
             `1` = "Worsening",
             `2` = "Improvement"
           )
         )

dat %>%
  freq(gad.change_binary)
```

## phq
```{r phq improvment worsening stratification}
dat <- dat %>%
  mutate(phq.change_binary_numeric =
           case_when(
             phq.pandemic_felt_feelings_numeric == 1 ~ 1,
             phq.pandemic_felt_feelings_numeric == 2 ~ 1,
             phq.pandemic_felt_feelings_numeric == 3 ~ 0,
             phq.pandemic_felt_feelings_numeric == 4 ~ 2,
             phq.pandemic_felt_feelings_numeric == 5 ~ 2
           )
  )

dat <- dat %>%
  mutate(phq.change_binary =
           recode_factor(
             phq.change_binary_numeric,
             `0` = "No change",
             `1` = "Worsening",
             `2` = "Improvement"
           )
  )

dat %>%
  freq(phq.change_binary)
```

## ocir
```{r ocir improvment worsening stratification}
dat <- dat %>%
  mutate(ocir.change_binary_numeric =
           case_when(
             ocir.felt_pandemic_feelings_numeric == 1 ~ 1,
             ocir.felt_pandemic_feelings_numeric == 2 ~ 1,
             ocir.felt_pandemic_feelings_numeric == 3 ~ 0,
             ocir.felt_pandemic_feelings_numeric == 4 ~ 2,
             ocir.felt_pandemic_feelings_numeric == 5 ~ 2
           )
  )

dat <- dat %>%
  mutate(ocir.change_binary =
           recode_factor(
             ocir.change_binary_numeric,
             `0` = "No change",
             `1` = "Worsening",
             `2` = "Improvement"
           )
  )

dat %>%
  freq(ocir.change_binary)
```

```{r Save four cohorts as rds file}
saveRDS(object = dat, file = paste0(data_path, "/four_cohorts_variables.rds"))
```

### 2020-09-15 PANNEURO_analysis.Rmd
variable creation script

@@
 
+# ggplot theme
+Set up ggplot theme for the plots
+```{r ggplot theme}
+theme_personal <-  theme(
+    text = element_text(color = "black"),
+    axis.title = element_text(color = "black"),
+    axis.text = element_text(color = "black"),
+    axis.title.y = element_blank(), 
+    legend.background = element_blank(),
+    legend.box.background = element_blank(),
+    panel.background = element_blank(), 
+    panel.grid.minor.x = element_blank(),
+    panel.grid.major.x = element_line(
+      colour = "gray",
+      linetype = "dashed",
+      size = 0.2
+      ),
+    axis.ticks = element_blank()
+    )
+```
+
 # Data import
@@
 ```{r read in data}
-dat.raw <- readRDS(file = paste0(data_path, "/four_cohorts.rds"))
+dat.raw <- readRDS(file = paste0(data_path, "/four_cohorts.rds")) #NEEDS CHANGING
 dim(dat.raw)
 colnames(dat.raw)
-```
-
-```{r dat.coping summary, eval=FALSE, include=FALSE}
-#summarytools::dfSummary(
-#  dat.raw,
-#  graph.col = F,
-#  valid.col = F,
-#  labels.col = F)
-```
-
-# Data availability
-
-Data availability GAD
-```{r gad availability}
-dat.raw %>%
-  freq(
-    data_group_gad,
-    cumul = F)
-```
-
-Data availability PHQ
-```{r phq availability}
-dat.raw %>%
-  freq(
-    data_group_phq,
-    cumul = F)
-```
-
-Data availability PCL
-```{r pcl availability}
-dat.raw %>%
-  freq(
-    data_group_pcl,
-    cumul = F)
-```
-
-Data availability OCI-R
-```{r ocir availability}
-dat.raw %>%
-  freq(
-    data_group_ocir,
-    cumul = F)
-```
-
-```{r sample frequencies}
-dat.raw %>%
-  freq(Sample)
-```
-
-# COVID
-## Recode variable
-```{r covid test positive double}
-dat.raw <- dat.raw %>%
-  mutate(covid_test_positive_double_numeric =
-           case_when(
-             (respiratory.throat_swab_test_nose_numeric == 1 &
-               respiratory.results_antibody_test_numeric == 1) ~ 2,
-             respiratory.throat_swab_test_nose_numeric == 1 ~ 1,
-             respiratory.throat_swab_test_nose_numeric == 2 ~ 0,
-             respiratory.results_antibody_test_numeric == 1 ~ 1,
-             respiratory.results_antibody_test_numeric == 2 ~ 0
-           )
-         )
-
-dat.raw <- dat.raw %>%
-  mutate(covid_test_positive_double =
-           recode_factor(
-             covid_test_positive_double_numeric,
-             `0` = "Negative",
-             `1` = "Positive",
-             `2` = "Double positive"
-           )
-         )
-
-dat.raw %>%
-  freq(covid_test_positive_double)
-```
-
-```{r gad covid test positive}
-dat.raw <- dat.raw %>%
-  mutate(gad.covid_test_positive_numeric =
-           case_when(
-             (respiratory.throat_swab_test_nose_numeric == 1 &
-               respiratory.results_antibody_test_numeric == 1) ~ 1, # with two positive test results get coded as positive
-             respiratory.throat_swab_test_nose_numeric == 1 ~ 1,
-             respiratory.throat_swab_test_nose_numeric == 2 ~ 0,
-             respiratory.results_antibody_test_numeric == 1 ~ 1,
-             respiratory.results_antibody_test_numeric == 2 ~ 0
-           )
-         )
-
-dat.raw <- dat.raw %>%
-  mutate(covid_test_positive =
-           recode_factor(
-             gad.covid_test_positive_numeric,
-             `0` = "Negative",
-             `1` = "Positive"
-#             `2` = "Double positive"
-           )
-         )
-
-dat.raw %>%
-  freq(covid_test_positive)
 ```

### 2020-09-15 PANCHANGE_analysis.Rmd
split of scripts

@@
 ```{r read in data}
-dat.raw <- readRDS(file = paste0(data_path, "/four_cohorts.rds"))
-dim(dat.raw)
-colnames(dat.raw)
-```
-
-# Vectors for sum_score
+dat <- readRDS(file = paste0(data_path, "/four_cohorts.rds"))
+dim(dat)
+colnames(dat)
+```
+
+## Important vectors with collections of columns
+
+## Vectors for sum_score
 
@@
 
-# Vectors for diff_score
+## Vectors for diff_score
 

### 2020-09-15 PANCHANGE_descriptives.Rmd
split of scripts

@@
 ```{r read in data}
-dat.raw <- readRDS(file = paste0(data_path, "/four_cohorts.rds")) # NEEDS CHANGING TO THE DATA SET THAT COMES OUT OF THE VARIABLE CREATION
+dat.raw <- readRDS(file = paste0(data_path, "/four_cohorts_variables.rds")) # NEEDS CHANGING TO THE DATA SET THAT COMES OUT OF THE VARIABLE CREATION
 dim(dat.raw)
 colnames(dat.raw)
+```
+
+## Important vectors with collections of columns
+
+## Vectors for sum_score
+
+```{r Vectors with sum_score_cols}
+sum_score_cols <- dat.raw %>%
+  select(contains("sum_score")) %>%
+  select(-ends_with("raw")) %>%
+  colnames()
+
+sum_score_cols
+
+phq.sum_score_cols <- dat.raw %>%
+  select(contains("phq")) %>%
+  select(contains("sum_score")) %>% 
+  select(-ends_with("raw")) %>%
+  select(-contains("8items")) %>%
+  colnames()
+
+phq.sum_score_cols
+
+gad.sum_score_cols <- dat.raw %>%
+  select(contains("gad")) %>%
+  select(contains("sum_score")) %>% 
+  select(-ends_with("raw")) %>%
+  colnames()
+
+gad.sum_score_cols
+
+ocir.sum_score_cols <- dat.raw %>%
+  select(contains("ocir")) %>%
+  select(contains("sum_score")) %>% 
+  select(-ends_with("raw")) %>%
+  colnames()
+
+ocir.sum_score_cols
+
+pcl.sum_score_cols <- dat.raw %>%
+  select(contains("pcl")) %>%
+  select(contains("sum_score")) %>% 
+  select(-ends_with("raw")) %>%
+  colnames()
+
+pcl.sum_score_cols
+```
+
+## Vectors for diff_score
+
+```{r Vectors with diff_score_cols}
+diff_score_cols <- dat.raw %>%
+  select(contains("diff_score")) %>% 
+  colnames()
+
+diff_score_cols
+
+phq.diff_score_cols <- dat.raw %>%
+  select(contains("phq")) %>%
+  select(contains("diff_score")) %>% 
+  colnames()
+
+phq.diff_score_cols
+
+gad.diff_score_cols <- dat.raw %>%
+  select(contains("gad")) %>%
+  select(contains("diff_score")) %>% 
+  colnames()
+
+gad.diff_score_cols
+
+ocir.diff_score_cols <- dat.raw %>%
+  select(contains("ocir")) %>%
+  select(contains("diff_score")) %>% 
+  colnames()
+
+ocir.diff_score_cols
 ```
@@
 RAMPagepalette <- c(
-  "#00D9AC","#21D9B3","#4DD9BC","#78D9C5","#8ED9C9","#A3D9CE",
+  "#00D9AC",
+  "#21D9B3",
+  "#4DD9BC",
+  "#78D9C5",
+  "#8ED9C9",
+  "#A3D9CE",
   "#CFD9D7",
-  "#DAD0BA","#DAC38F","#DAC38F","#DAB663" ,"#DAA937","#DA9C0C")
-
-#Bar plot
+  "#DAD0BA",
+  "#DAC38F",
+  "#DAC38F",
+  "#DAB663",
+  "#DAA937",
+  "#DA9C0C"
+  )
+
+# Bar plot
 plot.age <- 
   age_category_prop_total %>%
-    mutate(age_category = fct_reorder(age_category,order)) %>%
-
+    mutate(age_category = fct_reorder(age_category, order)) %>%
   ggplot(aes(x = age_category)) +
-  geom_bar(aes(y = n, color=age_category, fill=age_category, alpha = 1),
-           stat ="summary") +
+  geom_bar(aes(
+    y = n,
+    color = age_category,
+    fill = age_category,
+    alpha = 1),
+    stat ="identity"
+    ) +
   scale_fill_manual(values =  RAMPagepalette) +
@@
        y = "Total count",
-       title = paste("Number of participants in each age category",sep=" "),
-       subtitle = paste("n = ", ageN,
-                        sep = ""),
+       title = "Number of participants in each age category",
+       subtitle = paste0("n = ", ageN),
        fill = "Age category") +
-   guides(alpha = FALSE, color = FALSE, fill = FALSE) +
-  scale_x_discrete(limits = (levels(age_category_prop_total$age_category))) +
+   guides(
+     alpha = FALSE, # Display no guide for alpha
+     color = FALSE, # Display no guide for color
+     fill = FALSE # Display no guide for fill
+     ) +
+  scale_x_discrete(
+    limits = (levels(age_category_prop_total$age_category))
+    ) +
   theme_classic2() +
-   theme(axis.text.x = element_text(colour="black", size = 12,angle=45,
-                                    vjust=0.5),
-        axis.text.y = element_text(colour="black", size = 12))
+   theme(
+     axis.text.x = element_text(
+       colour="black",
+       size = 12,
+       angle = 45,
+       vjust = 0.5),
+     axis.text.y = element_text(
+       colour="black",
+       size = 12)
+     )
 
@@
 # age_category
+## Proportion tables
 ```{r age_category per Sample prop per total}
@@
 
+## Cross tables
 ```{r age_category per Sample prop cross table}
@@
 # Ethnicity_collapsed
+## Proportion tables
 ```{r Ethnicity_collapsed per Sample prop per total}
@@
 
+## Cross tables
 ```{r Ethnicity_collapsed per Sample prop cross table}
@@
 # Gender_collapsed
+## Proportion tables
 ```{r Gender_collapsed per Sample prop per total}
@@
 
+## Cross tables
 ```{r Gender_collapsed per Sample prop cross table}
@@
 # highest_education
+## Proportion tables
 ```{r highest_education per Sample prop per total}
@@
 
+## Cross tables
 ```{r highest_education per Sample prop cross table}
@@
 # key_worker
+## Proportion tables
 ```{r key_worker per Sample prop per total}
@@
 
+## Cross tables
 ```{r key_worker per Sample prop cross table}
@@
 
+## Create long data frame
 ```{r gather to long format Disorder_hierarchical}
@@
 
+## Disorders per Gender
 ```{r Disorder_inc by Gender_collapsed}
@@
 
+## Disorders per sample
 ```{r Disorder_inc by Sample}
@@
 
+## Disorder per ethnicity
 ```{r Disorder_inc by Ethnicity_collapsed}

### 2020-09-15 PANCHANGE_exclusion_descriptives.Rmd
test run of all scripts

--- 2020-09-15 PANCHANGE_descriptives.Rmd
@@
 Rapid Assessment of MP
-```{r sample frequencies}
+```{r participants per subsample frequencies}
 dat %>%
   freq(Sample)
-```
-
-## Age categories
-
-Age bar plot for whole sample (not grouped)
-Summary dataset for age and display it as a bar plot
-```{r age_category prop total (ungrouped)}
-age_category_prop_total <- dat %>%
-  count(age_category) %>%
-  mutate(Prop = round(n/sum(n), 2))
-
-# add a column to help order the factor
-age_category_prop_total$order <- c(1,2,3,4,5,6,7,8,9,10,11,12,13)
-
-# total responders
-ageN <- sum(age_category_prop_total$n)
-
-kable(age_category_prop_total)
-age_category_prop_total
-```
-
-```{r age_category prop total (ungrouped) plot}
-#Colour palette
-RAMPagepalette <- c(
-  "#00D9AC",
-  "#21D9B3",
-  "#4DD9BC",
-  "#78D9C5",
-  "#8ED9C9",
-  "#A3D9CE",
-  "#CFD9D7",
-  "#DAD0BA",
-  "#DAC38F",
-  "#DAC38F",
-  "#DAB663",
-  "#DAA937",
-  "#DA9C0C"
-  )
-
-# Bar plot
-plot.age <- 
-  age_category_prop_total %>%
-    mutate(age_category = fct_reorder(age_category, order)) %>%
-  ggplot(aes(x = age_category)) +
-  geom_bar(aes(
-    y = n,
-    color = age_category,
-    fill = age_category,
-    alpha = 1),
-    stat ="identity"
-    ) +
-  scale_fill_manual(values =  RAMPagepalette) +
-  scale_color_manual(values =  RAMPagepalette) +
-  labs(x = "",
-       y = "Total count",
-       title = "Number of participants in each age category",
-       subtitle = paste0("n = ", ageN),
-       fill = "Age category") +
-   guides(
-     alpha = FALSE, # Display no guide for alpha
-     color = FALSE, # Display no guide for color
-     fill = FALSE # Display no guide for fill
-     ) +
-  scale_x_discrete(
-    limits = (levels(age_category_prop_total$age_category))
-    ) +
-  theme_classic2() +
-   theme(
-     axis.text.x = element_text(
-       colour="black",
-       size = 12,
-       angle = 45,
-       vjust = 0.5),
-     axis.text.y = element_text(
-       colour="black",
-       size = 12)
-     )
-
-plot.age
-```
-
-# Compare the GLAD/EDGI and COPING subcohorts: EDGI, GLAD, NBR, RAMP
-+++CH: Diagnosis, ethnicity, gender, age
-
-# age_category
-## Proportion tables
-```{r age_category per Sample prop per total}
-age_category_per_Sample_prop_total <- dat %>%
-  count(age_category, Sample) %>%
-  mutate(Prop = round(n/sum(n), 2))
-
-kable(age_category_per_Sample_prop_total)
-age_category_per_Sample_prop_total
-```
-
-```{r age_category per Sample prop per Sample}
-age_category_per_Sample_prop_Sample <- dat %>%
-  group_by(Sample) %>%
-  count(age_category, Sample) %>%
-  mutate(Prop = round(n/sum(n), 2))
-
-kable(age_category_per_Sample_prop_Sample)
-age_category_per_Sample_prop_Sample
-```
-
-## Cross tables
-```{r age_category per Sample prop cross table}
-age_category_per_Sample_prop_Sample_cross_table <- dat %>%
-  group_by(Sample) %>%
-  count(age_category, Sample) %>%
-  mutate(Prop = round(n/sum(n), 2)) %>%
-  pivot_wider(names_from = Sample, values_from = c(n, Prop))
-
-kable(age_category_per_Sample_prop_Sample_cross_table)
-age_category_per_Sample_prop_Sample_cross_table
-```
-
-```{r age_category per Sample count cross table}
-age_category_per_Sample_count_cross_table <- dat %>%
-  count(age_category, Sample) %>%
-  spread(key = Sample, value = n) %>%
-  mutate(
-    EDGI = as.integer(replace_na(EDGI, 0)),
-    GLAD = as.integer(replace_na(GLAD, 0)),
-    NBR = as.integer(replace_na(NBR, 0)),
-    RAMP = as.integer(replace_na(RAMP, 0))
-  )
-
-kable(age_category_per_Sample_count_cross_table)
-age_category_per_Sample_count_cross_table
-```
-
-```{r age_category per Sample chisquare test}
-age_category_per_Sample_chissquare_test <- dat %>%
-  count(age_category, Sample) %>%
-  spread(key = Sample, value = n) %>%
-  select(-age_category) %>%
-  mutate(
-    EDGI = as.integer(replace_na(EDGI, 0)),
-    GLAD = as.integer(replace_na(GLAD, 0)),
-    NBR = as.integer(replace_na(NBR, 0)),
-    RAMP = as.integer(replace_na(RAMP, 0))
-  ) %>%
-  chisq.test() %>%
-  glance()
-
-kable(age_category_per_Sample_chissquare_test)
-age_category_per_Sample_chissquare_test
-```
-
-```{r age_category by Sample count plot}
-age_category_by_Sample_count_plot <- age_category_per_Sample_prop_Sample %>%
-  ggplot(mapping = aes(
-    x = age_category,
-    y = n)
-  ) +
-  geom_bar(
-    aes(fill = Sample),
-    stat="identity",
-    binwidth = 1,
-    position = position_dodge2(preserve = "single")
-  ) +
-  labs(
-    x = "age_category",
-    y = "Number of participants",
-    fill = "Sample") +
-  theme_personal +
-  scale_fill_manual(
-    values = COPINGpalette6
-  ) +
-  coord_flip()
-
-age_category_by_Sample_count_plot
-```
-
-```{r age_category by Sample prop plot}
-age_category_by_Sample_prop_plot <- age_category_per_Sample_prop_Sample %>%
-  ggplot(mapping = aes(
-    x = age_category,
-    y = Prop)
-  ) +
-  geom_bar(
-    aes(fill = Sample),
-    stat="identity",
-    binwidth = 1,
-    position = position_dodge2(preserve = "single")
-  ) +
-  labs(
-    x = "age_category",
-    y = "Percentage per sample",
-    fill = "Sample") +
-  theme_personal +
-  scale_fill_manual(
-    values = COPINGpalette6
-  ) +
-  coord_flip()
-
-age_category_by_Sample_prop_plot
-```
-
-# Ethnicity_collapsed
-## Proportion tables
-```{r Ethnicity_collapsed per Sample prop per total}
-Ethnicity_collapsed_per_Sample_prop_total <- dat %>%
-  count(Ethnicity_collapsed, Sample) %>%
-  mutate(Prop = round(n/sum(n), 2))
-
-kable(Ethnicity_collapsed_per_Sample_prop_total)
-Ethnicity_collapsed_per_Sample_prop_total
-```
-
-```{r Ethnicity_collapsed per Sample prop per Sample}
-Ethnicity_collapsed_per_Sample_prop_Sample <- dat %>%
-  group_by(Sample) %>%
-  count(Ethnicity_collapsed, Sample) %>%
-  mutate(Prop = round(n/sum(n), 2))
-
-kable(Ethnicity_collapsed_per_Sample_prop_Sample)
-Ethnicity_collapsed_per_Sample_prop_Sample
-```
-
-## Cross tables
-```{r Ethnicity_collapsed per Sample prop cross table}
-Ethnicity_collapsed_per_Sample_prop_Sample_cross_table <- dat %>%
-  group_by(Sample) %>%
-  count(Ethnicity_collapsed, Sample) %>%
-  mutate(Prop = round(n/sum(n), 2)) %>%
-  pivot_wider(names_from = Sample, values_from = c(n, Prop))
-
-kable(Ethnicity_collapsed_per_Sample_prop_Sample_cross_table)
-Ethnicity_collapsed_per_Sample_prop_Sample_cross_table
-```
-
-```{r Ethnicity_collapsed per Sample count cross table}
-Ethnicity_collapsed_per_Sample_count_cross_table <- dat %>%
-  count(Ethnicity_collapsed, Sample) %>%
-  spread(key = Sample, value = n) %>%
-  mutate(
-    EDGI = as.integer(replace_na(EDGI, 0)),
-    GLAD = as.integer(replace_na(GLAD, 0)),
-    NBR = as.integer(replace_na(NBR, 0)),
-    RAMP = as.integer(replace_na(RAMP, 0))
-  )
-
-kable(Ethnicity_collapsed_per_Sample_count_cross_table)
-Ethnicity_collapsed_per_Sample_count_cross_table
-```
-
-```{r Ethnicity_collapsed per Sample chisquare test}
-Ethnicity_collapsed_per_Sample_chissquare_test <- dat %>%
-  count(Ethnicity_collapsed, Sample) %>%
-  spread(key = Sample, value = n) %>%
-  select(-Ethnicity_collapsed) %>%
-  mutate(
-    EDGI = as.integer(replace_na(EDGI, 0)),
-    GLAD = as.integer(replace_na(GLAD, 0)),
-    NBR = as.integer(replace_na(NBR, 0)),
-    RAMP = as.integer(replace_na(RAMP, 0))
-  ) %>%
-  chisq.test() %>%
-  glance()
-
-kable(Ethnicity_collapsed_per_Sample_chissquare_test)
-Ethnicity_collapsed_per_Sample_chissquare_test
-```
-
-```{r Ethnicity_collapsed by Sample count plot}
-Ethnicity_collapsed_by_Sample_count_plot <- Ethnicity_collapsed_per_Sample_prop_Sample %>%
-  ggplot(mapping = aes(
-    x = Ethnicity_collapsed,
-    y = n)
-  ) +
-  geom_bar(
-    aes(fill = Sample),
-    stat="identity",
-    binwidth = 1,
-    position = position_dodge2(preserve = "single")
-  ) +
-  labs(
-    x = "Ethnicity_collapsed",
-    y = "Number of participants",
-    fill = "Sample") +
-  theme_personal +
-  scale_fill_manual(
-    values = COPINGpalette6
-  ) +
-  coord_flip()
-
-Ethnicity_collapsed_by_Sample_count_plot
-```
-
-```{r Ethnicity_collapsed by Sample prop plot}
-Ethnicity_collapsed_by_Sample_prop_plot <- Ethnicity_collapsed_per_Sample_prop_Sample %>%
-  ggplot(mapping = aes(
-    x = Ethnicity_collapsed,
-    y = Prop)
-  ) +
-  geom_bar(
-    aes(fill = Sample),
-    stat="identity",
-    binwidth = 1,
-    position = position_dodge2(preserve = "single")
-  ) +
-  labs(
-    x = "Ethnicity_collapsed",
-    y = "Percentage per sample",
-    fill = "Sample") +
-  theme_personal +
-  scale_fill_manual(
-    values = COPINGpalette6
-  ) +
-  coord_flip()
-
-Ethnicity_collapsed_by_Sample_prop_plot
-```
-
-### pie charts
-
-```{r Ethnicity_collapsed prop per total summary}
-
-Ethnicity_collapsed_prop_Sample <- dat %>%
-  count(Ethnicity_collapsed) %>%
-  drop_na() %>%
-  mutate(freq = round(n/sum(n), 2))
-
-# total responders
-ethN <- sum(Ethnicity_collapsed_prop_Sample$n)
-
-kable(Ethnicity_collapsed_prop_Sample)
-Ethnicity_collapsed_prop_Sample
-
-```
-
-pie chart with only European label
-
-```{r ethnicity pie chart biggest group label}
-
-eth_pie_alllabel <-
-
-  Ethnicity_collapsed_prop_Sample %>%
-   mutate(Ethnicity_collapsed = fct_reorder(Ethnicity_collapsed,-n)) %>%
-
-  ggplot(aes(x="", y=freq, fill=Ethnicity_collapsed)) +
-  geom_bar(width = 1, stat = "identity") +
-  scale_fill_manual(values =  COPINGpalette6) +
-  scale_color_manual(values =  COPINGpalette6) +
-  coord_polar("y",start=0) +
-  theme_void() +
-   labs(title = paste("RAMP/COPING sample self reported ethnicity",
-                      sep=" "),
-        subtitle = paste("n =", sum(Ethnicity_collapsed_prop_Sample$n),
-                         sep = " "),
-        fill = "Self reported ethnicity")  +
-    geom_text(aes(y = c(0.5),
-                  label= c(paste0(round((freq[1]*100),0),"%"))), #Frequency of European only
-             size=5,
-             face="bold"
-             )
-
-eth_pie_alllabel
-
-```
-
-pie chart - no labels
-
-```{r ethnicity pie chart no label}
-
-eth_pie <-
-
-    Ethnicity_collapsed_prop_Sample %>%
-   mutate(Ethnicity_collapsed = fct_reorder(Ethnicity_collapsed,-n)) %>%
-
-  ggplot(aes(x="", y=freq, fill=Ethnicity_collapsed)) +
-  geom_bar(width = 1, stat = "identity") +
-  scale_fill_manual(values =  COPINGpalette6) +
-  scale_color_manual(values =  COPINGpalette6) +
-  coord_polar("y",start=0) +
-  theme_void() +
-   labs(title = paste("RAMP/COPING sample self reported ethnicity",
-                      sep=" "),
-        subtitle = paste("n =", sum(Ethnicity_collapsed_prop_Sample$n),
-                         sep = " "),
-        fill = "Self reported ethnicity")
-
-eth_pie
-
-```
-
-# Gender_collapsed
-## Proportion tables
-```{r Gender_collapsed per Sample prop per total}
-Gender_collapsed_per_Sample_prop_total <- dat %>%
-  count(Gender_collapsed, Sample) %>%
-  mutate(Prop = round(n/sum(n), 2))
-
-kable(Gender_collapsed_per_Sample_prop_total)
-Gender_collapsed_per_Sample_prop_total
-```
-
-```{r Gender_collapsed per Sample prop per Sample}
-Gender_collapsed_per_Sample_prop_Sample <- dat %>%
-  group_by(Sample) %>%
-  count(Gender_collapsed, Sample) %>%
-  mutate(Prop = round(n/sum(n), 2))
-
-kable(Gender_collapsed_per_Sample_prop_Sample)
-Gender_collapsed_per_Sample_prop_Sample
-```
-
-## Cross tables
-```{r Gender_collapsed per Sample prop cross table}
-Gender_collapsed_per_Sample_prop_Sample_cross_table <- dat %>%
-  group_by(Sample) %>%
-  count(Gender_collapsed, Sample) %>%
-  mutate(Prop = round(n/sum(n), 2)) %>%
-  pivot_wider(names_from = Sample, values_from = c(n, Prop))
-
-kable(Gender_collapsed_per_Sample_prop_Sample_cross_table)
-Gender_collapsed_per_Sample_prop_Sample_cross_table
-```
-
-```{r Gender_collapsed per Sample count cross table}
-Gender_collapsed_per_Sample_count_cross_table <- dat %>%
-  count(Gender_collapsed, Sample) %>%
-  spread(key = Sample, value = n) %>%
-  mutate(
-    EDGI = as.integer(replace_na(EDGI, 0)),
-    GLAD = as.integer(replace_na(GLAD, 0)),
-    NBR = as.integer(replace_na(NBR, 0)),
-    RAMP = as.integer(replace_na(RAMP, 0))
-  )
-
-kable(Gender_collapsed_per_Sample_count_cross_table)
-Gender_collapsed_per_Sample_count_cross_table
-```
-
-```{r Gender_collapsed per Sample chisquare test}
-Gender_collapsed_per_Sample_chissquare_test <- dat %>%
-  count(Gender_collapsed, Sample) %>%
-  spread(key = Sample, value = n) %>%
-  select(-Gender_collapsed) %>%
-  mutate(
-    EDGI = as.integer(replace_na(EDGI, 0)),
-    GLAD = as.integer(replace_na(GLAD, 0)),
-    NBR = as.integer(replace_na(NBR, 0)),
-    RAMP = as.integer(replace_na(RAMP, 0))
-  ) %>%
-  chisq.test() %>%
-  glance()
-
-kable(Gender_collapsed_per_Sample_chissquare_test)
-Gender_collapsed_per_Sample_chissquare_test
-```
-
-```{r Gender_collapsed by Sample count plot}
-Gender_collapsed_by_Sample_count_plot <- Gender_collapsed_per_Sample_prop_Sample %>%
-  ggplot(mapping = aes(
-    x = Gender_collapsed,
-    y = n)
-  ) +
-  geom_bar(
-    aes(fill = Sample),
-    stat="identity",
-    binwidth = 1,
-    position = position_dodge2(preserve = "single")
-  ) +
-  labs(
-    x = "Gender_collapsed",
-    y = "Number of participants",
-    fill = "Sample") +
-  theme_personal +
-  scale_fill_manual(
-    values = COPINGpalette6
-  ) +
-  coord_flip()
-
-Gender_collapsed_by_Sample_count_plot
-```
-
-```{r Gender_collapsed by Sample prop plot}
-Gender_collapsed_by_Sample_prop_plot <- Gender_collapsed_per_Sample_prop_Sample %>%
-  ggplot(mapping = aes(
-    x = Gender_collapsed,
-    y = Prop)
-  ) +
-  geom_bar(
-    aes(fill = Sample),
-    stat="identity",
-    binwidth = 1,
-    position = position_dodge2(preserve = "single")
-  ) +
-  labs(
-    x = "Gender_collapsed",
-    y = "Percentage per sample",
-    fill = "Sample") +
-  theme_personal +
-  scale_fill_manual(
-    values = COPINGpalette6
-  ) +
-  coord_flip()
-
-Gender_collapsed_by_Sample_prop_plot
-```
-
-### pie charts
-
-```{r Gender_collapsed prop per total}
-
-Gender_collapsed_prop_total <- dat %>%
-  count(Gender_collapsed) %>%
-  mutate(freq = round(n/sum(n), 2))
-
-kable(Gender_collapsed_prop_total)
-Gender_collapsed_prop_total
-
-```
-
-```{r gender pie chart - all labels}
-
-gen_pie_alllabel <- 
-  ggplot(Gender_collapsed_prop_total, aes(x="", y=freq, fill=Gender_collapsed)) +
-  geom_bar(width = 1, stat = "identity") +
-  scale_fill_manual(values =  COPINGpalette5) +
-  scale_color_manual(values =  COPINGpalette5) +
-  coord_polar("y",start=0) +
-  theme_void() +
-   labs(title = paste("RAMP/COPING sample self reported gender",
-                      sep=" "),
-        subtitle = paste("n", sum(Gender_collapsed_prop_total$n),
-                         sep = " "),
-        fill = "Self reported gender")  +
-    geom_text(aes(y = c(0.85,0.35,0),
-                  x = c(1.2,1.2,1.8),
-                  label= c(paste0(round((freq[1:2]*100),0),"%"),paste0(round((freq[3]*100),1),"%"))),
-             size=5,
-             face="bold"
-             )
-
-gen_pie_alllabel
-
-```
-
-pie chart - only labelling two largest groups (male and female)
-
-```{r gender pie chart - male/female labels only}
-
-gen_pie <- 
-  ggplot(Gender_collapsed_prop_total, aes(x="", y=freq, fill=Gender_collapsed)) +
-  geom_bar(width = 1, stat = "identity") +
-  scale_fill_manual(values =  COPINGpalette5) +
-  scale_color_manual(values =  COPINGpalette5) +
-  coord_polar("y",start=0) +
-  theme_void() +
-   labs(title = paste("RAMP/COPING sample self reported gender",
-                      sep=" "),
-        subtitle = paste("n", sum(Gender_collapsed_prop_total$n),
-                         sep = " "),
-        fill = "Self reported gender")  +
-    geom_text(aes(y = c(0.85,0.35,0),
-                  x = c(1.2,1.2,1.8),
-                  label= c(paste0(round((freq[1:2]*100),0),"%"),"")),
-             size=5,
-             face="bold"
-             )
-
-gen_pie
-
-```
-
-pie chart -  no labels
-
-```{r gender pie chart - no labels }
-
-gen_pie_nolabel <- 
-  ggplot(Gender_collapsed_prop_total, aes(x="", y=freq, fill=Gender_collapsed)) +
-  geom_bar(width = 1, stat = "identity") +
-  scale_fill_manual(values =  COPINGpalette5) +
-  scale_color_manual(values =  COPINGpalette5) +
-  coord_polar("y",start=0) +
-  theme_void() +
-   labs(title = paste("RAMP/COPING sample self reported gender",
-                      sep=" "),
-        subtitle = paste("n", sum(Gender_collapsed_prop_total$n),
-                         sep = " "),
-        fill = "Self reported gender")
-
-gen_pie_nolabel
-
-```
-
-# highest_education
-## Proportion tables
-```{r highest_education per Sample prop per total}
-highest_education_per_Sample_prop_total <- dat %>%
-  count(highest_education, Sample) %>%
-  mutate(Prop = round(n/sum(n), 2))
-
-kable(highest_education_per_Sample_prop_total)
-highest_education_per_Sample_prop_total
-```
-
-```{r highest_education per Sample prop per Sample}
-highest_education_per_Sample_prop_Sample <- dat %>%
-  group_by(Sample) %>%
-  count(highest_education, Sample) %>%
-  mutate(Prop = round(n/sum(n), 2))
-
-kable(highest_education_per_Sample_prop_Sample)
-highest_education_per_Sample_prop_Sample
-```
-
-## Cross tables
-```{r highest_education per Sample prop cross table}
-highest_education_per_Sample_prop_Sample_cross_table <- dat %>%
-  group_by(Sample) %>%
-  count(highest_education, Sample) %>%
-  mutate(Prop = round(n/sum(n), 2)) %>%
-  pivot_wider(names_from = Sample, values_from = c(n, Prop))
-
-kable(highest_education_per_Sample_prop_Sample_cross_table)
-highest_education_per_Sample_prop_Sample_cross_table
-```
-
-```{r highest_education per Sample count cross table}
-highest_education_per_Sample_count_cross_table <- dat %>%
-  count(highest_education, Sample) %>%
-  spread(key = Sample, value = n) %>%
-  mutate(
-    EDGI = as.integer(replace_na(EDGI, 0)),
-    GLAD = as.integer(replace_na(GLAD, 0)),
-    NBR = as.integer(replace_na(NBR, 0)),
-    RAMP = as.integer(replace_na(RAMP, 0))
-  )
-
-kable(highest_education_per_Sample_count_cross_table)
-highest_education_per_Sample_count_cross_table
-```
-
-```{r highest_education per Sample chisquare test}
-highest_education_per_Sample_chissquare_test <- dat %>%
-  count(highest_education, Sample) %>%
-  spread(key = Sample, value = n) %>%
-  select(-highest_education) %>%
-  mutate(
-    EDGI = as.integer(replace_na(EDGI, 0)),
-    GLAD = as.integer(replace_na(GLAD, 0)),
-    NBR = as.integer(replace_na(NBR, 0)),
-    RAMP = as.integer(replace_na(RAMP, 0))
-  ) %>%
-  chisq.test() %>%
-  glance()
-
-kable(highest_education_per_Sample_chissquare_test)
-highest_education_per_Sample_chissquare_test
-```
-
-```{r highest_education by Sample count plot}
-highest_education_by_Sample_count_plot <- highest_education_per_Sample_prop_Sample %>%
-  ggplot(mapping = aes(
-    x = highest_education,
-    y = n)
-  ) +
-  geom_bar(
-    aes(fill = Sample),
-    stat="identity",
-    binwidth = 1,
-    position = position_dodge2(preserve = "single")
-  ) +
-  labs(
-    x = "highest_education",
-    y = "Number of participants",
-    fill = "Sample") +
-  theme_personal +
-  scale_fill_manual(
-    values = COPINGpalette6
-  ) +
-  coord_flip()
-
-highest_education_by_Sample_count_plot
-```
-
-```{r highest_education by Sample prop plot}
-highest_education_by_Sample_prop_plot <- highest_education_per_Sample_prop_Sample %>%
-  ggplot(mapping = aes(
-    x = highest_education,
-    y = Prop)
-  ) +
-  geom_bar(
-    aes(fill = Sample),
-    stat="identity",
-    binwidth = 1,
-    position = position_dodge2(preserve = "single")
-  ) +
-  labs(
-    x = "highest_education",
-    y = "Percentage per sample",
-    fill = "Sample") +
-  theme_personal +
-  scale_fill_manual(
-    values = COPINGpalette6
-  ) +
-  coord_flip()
-
-highest_education_by_Sample_prop_plot
-```
-
-### pie chart
-
-summary dataset with frequencies
-
-```{r highest education prop per total}
-
-highest_education_prop_total <- dat %>%
-  count(highest_education) %>%
-  mutate(freq = round(n/sum(n), 2)) %>% 
-  drop_na()
-
-kable(highest_education_prop_total)
-highest_education_prop_total
-
-# total responders
-eduN <- sum(highest_education_prop_total$n)
-
-edubindat <- dat %>%
-  mutate(demographics.education_binary =
-           case_when(
-             highest_education_numeric == "4" ~ "Bachelors or higher",
-             highest_education_numeric == "3" ~ "A-levels or lower",
-             highest_education_numeric == "2" ~ "A-levels or lower",
-             highest_education_numeric == "1" ~ "A-levels or lower"
-           )) %>%
-  count(demographics.education_binary) %>%
-  mutate(freq = round(n/sum(n), 2)) %>% 
-  drop_na()
-
-educatdat <- dat %>%
-  mutate(demographics.education_three = 
-           case_when(
-             highest_education_numeric == "4" ~ "Bachelors or higher",
-             highest_education_numeric == "3" ~ "A-levels",
-             highest_education_numeric == "1" ~ "GCSEs or lower"
-           )) %>%
-  count(demographics.education_three) %>%
-  mutate(freq = round(n/sum(n), 2)) %>% 
-  drop_na()
-
-```
-
-pie chart labels
-
-```{r education pie chart all labels}
-
-edu_pie_alllabel <-
-
-    highest_education_prop_total %>%
-    mutate(demographics.highest_level_of_education = fct_reorder(highest_education,-n)) %>%
-
-  ggplot(aes(x="", y=freq, fill=demographics.highest_level_of_education)) +
-  geom_bar(width = 1, stat = "identity") +
-  scale_fill_manual(values =  COPINGpalette7) +
-  scale_color_manual(values =  COPINGpalette7) +
-  coord_polar("y",start=0) +
-  theme_void() +
-   labs(title = paste("RAMP/COPING sample self reported level of education",
-                      sep=" "),
-        subtitle = paste("n", sum(highest_education_prop_total$n),
-                         sep = " "),
-        fill = "Self reported level of education")  +
-    geom_text(aes(y = c(0.13,0.04,0.3,0.65),
-                  x = c(1.2,1.2,1.2,1.2), #GCSE, NVQ, A-levels, university
-                  label= paste0(round((freq*100),0),"%")),
-             size=5,
-             face="bold"
-             )
-
-edu_pie_alllabel
-
-```
-
-```{r binary education pie chart all labels}
-
-edu_pie_binlabel <-
-
-    edubindat %>%
-    mutate(demographics.education_binary = fct_reorder(demographics.education_binary,-n)) %>%
-
-  ggplot(aes(x="", y=freq, fill=demographics.education_binary)) +
-  geom_bar(width = 1, stat = "identity") +
-  scale_fill_manual(values =  COPINGpalette7) +
-  scale_color_manual(values =  COPINGpalette7) +
-  coord_polar("y",start=0) +
-  theme_void() +
-   labs(title = paste("RAMP/COPING sample self reported highest level of education, above or below bachelor degree or equivalent",
-                      sep=" "),
-        subtitle = paste("n", sum(edubindat$n),
-                         sep = " "),
-        fill = "Self reported level of education")  +
-    geom_text(aes(y = c(0.25,0.75),
-                  label= paste0(round((freq*100),0),"%")),
-             size=5,
-             face="bold"
-             )
-
-edu_pie_binlabel
-
-```
-
-```{r 3 category education pie chart all labels}
-
-edu_pie_catlabel <-
-
-    educatdat %>%
-    mutate(demographics.education_three = fct_reorder(demographics.education_three,-n)) %>%
-
-  ggplot(aes(x="", y=freq, fill=demographics.education_three)) +
-  geom_bar(width = 1, stat = "identity") +
-  scale_fill_manual(values =  COPINGpalette7) +
-  scale_color_manual(values =  COPINGpalette7) +
-  coord_polar("y",start=0) +
-  theme_void() +
-   labs(title = paste("RAMP/COPING sample self reported highest level of education, above or below bachelor degree or equivalent",
-                      sep=" "),
-        subtitle = paste("n", sum(educatdat$n),
-                         sep = " "),
-        fill = "Self reported level of education")  +
-    geom_text(aes(y = c(0.23,0.65,0.05),
-                  label= c(paste0(round((freq[1:3]*100),0),"%")),
-             size=5,
-             face="bold"
-             ))
-
-edu_pie_catlabel
-
-```
-
-pie chart -  no labels
-
-```{r education pie chart no labels }
-
-edu_pie_nolabel <-
-
-  edu_pie_alllabel <-
-
-    highest_education_prop_total %>%
-    mutate(demographics.highest_level_of_education = fct_reorder(highest_education,-n)) %>%
-
-  ggplot(aes(x="", y=freq, fill=demographics.highest_level_of_education)) +
-  geom_bar(width = 1, stat = "identity") +
-  scale_fill_manual(values =  COPINGpalette7) +
-  scale_color_manual(values =  COPINGpalette7) +
-  coord_polar("y",start=0) +
-  theme_void() +
-   labs(title = paste("RAMP/COPING sample self reported level of education",
-                      sep=" "),
-        subtitle = paste("n", sum(highest_education_prop_total$n),
-                         sep = " "),
-        fill = "Self reported level of education")
-
-```
-
-# key_worker
-## Proportion tables
-```{r key_worker per Sample prop per total}
-key_worker_per_Sample_prop_total <- dat %>%
-  count(key_worker, Sample) %>%
-  mutate(Prop = round(n/sum(n), 2))
-
-kable(key_worker_per_Sample_prop_total)
-key_worker_per_Sample_prop_total
-```
-
-```{r key_worker per Sample prop per Sample}
-key_worker_per_Sample_prop_Sample <- dat %>%
-  group_by(Sample) %>%
-  count(key_worker, Sample) %>%
-  mutate(Prop = round(n/sum(n), 2))
-
-kable(key_worker_per_Sample_prop_Sample)
-key_worker_per_Sample_prop_Sample
-```
-
-## Cross tables
-```{r key_worker per Sample prop cross table}
-key_worker_per_Sample_prop_Sample_cross_table <- dat %>%
-  group_by(Sample) %>%
-  count(key_worker, Sample) %>%
-  mutate(Prop = round(n/sum(n), 2)) %>%
-  pivot_wider(names_from = Sample, values_from = c(n, Prop))
-
-kable(key_worker_per_Sample_prop_Sample_cross_table)
-key_worker_per_Sample_prop_Sample_cross_table
-```
-
-```{r key_worker per Sample count cross table}
-key_worker_per_Sample_count_cross_table <- dat %>%
-  count(key_worker, Sample) %>%
-  spread(key = Sample, value = n) %>%
-  mutate(
-    EDGI = as.integer(replace_na(EDGI, 0)),
-    GLAD = as.integer(replace_na(GLAD, 0)),
-    NBR = as.integer(replace_na(NBR, 0)),
-    RAMP = as.integer(replace_na(RAMP, 0))
-  )
-
-kable(key_worker_per_Sample_count_cross_table)
-key_worker_per_Sample_count_cross_table
-```
-
-```{r key_worker per Sample chisquare test}
-key_worker_per_Sample_chissquare_test <- dat %>%
-  count(key_worker, Sample) %>%
-  spread(key = Sample, value = n) %>%
-  select(-key_worker) %>%
-  mutate(
-    EDGI = as.integer(replace_na(EDGI, 0)),
-    GLAD = as.integer(replace_na(GLAD, 0)),
-    NBR = as.integer(replace_na(NBR, 0)),
-    RAMP = as.integer(replace_na(RAMP, 0))
-  ) %>%
-  chisq.test() %>%
-  glance()
-
-kable(key_worker_per_Sample_chissquare_test)
-key_worker_per_Sample_chissquare_test
-```
-
-```{r key_worker by Sample count plot}
-key_worker_by_Sample_count_plot <- key_worker_per_Sample_prop_Sample %>%
-  ggplot(mapping = aes(
-    x = key_worker,
-    y = n)
-  ) +
-  geom_bar(
-    aes(fill = Sample),
-    stat="identity",
-    binwidth = 1,
-    position = position_dodge2(preserve = "single")
-  ) +
-  labs(
-    x = "key_worker",
-    y = "Number of participants",
-    fill = "Sample") +
-  theme_personal +
-  scale_fill_manual(
-    values = COPINGpalette6
-  ) +
-  coord_flip()
-
-key_worker_by_Sample_count_plot
-```
-
-```{r key_worker by Sample prop plot}
-key_worker_by_Sample_prop_plot <- key_worker_per_Sample_prop_Sample %>%
-  ggplot(mapping = aes(
-    x = key_worker,
-    y = Prop)
-  ) +
-  geom_bar(
-    aes(fill = Sample),
-    stat="identity",
-    binwidth = 1,
-    position = position_dodge2(preserve = "single")
-  ) +
-  labs(
-    x = "key_worker",
-    y = "Percentage per sample",
-    fill = "Sample") +
-  theme_personal +
-  scale_fill_manual(
-    values = COPINGpalette6
-  ) +
-  coord_flip()
-
-key_worker_by_Sample_prop_plot
 ```
@@
 ```
+
+## Age categories
+Age bar plot for whole sample (not grouped)
+Summary dataset for age and display it as a bar plot
+```{r age_category prop total (ungrouped)}
+age_category_prop_total <- dat %>%
+  count(age_category) %>%
+  mutate(Prop = round(n/sum(n), 2))
+
+# add a column to help order the factor
+age_category_prop_total$order <- c(1,2,3,4,5,6,7,8,9,10,11,12,13)
+
+# total responders
+ageN <- sum(age_category_prop_total$n)
+
+kable(age_category_prop_total)
+age_category_prop_total
+```
+
+## Education
+
+### Pie charts
+
+summary dataset with frequencies
+
+```{r highest education prop per total}
+highest_education_prop_total <- dat %>%
+  count(highest_education) %>%
+  mutate(freq = round(n/sum(n), 2)) %>% 
+  drop_na()
+
+kable(highest_education_prop_total)
+highest_education_prop_total
+
+# total responders
+eduN <- sum(highest_education_prop_total$n)
+
+edubindat <- dat %>%
+  mutate(demographics.education_binary =
+           case_when(
+             highest_education_numeric == "4" ~ "Bachelors or higher",
+             highest_education_numeric == "3" ~ "A-levels or lower",
+             highest_education_numeric == "2" ~ "A-levels or lower",
+             highest_education_numeric == "1" ~ "A-levels or lower"
+           )) %>%
+  count(demographics.education_binary) %>%
+  mutate(freq = round(n/sum(n), 2)) %>% 
+  drop_na()
+
+educatdat <- dat %>%
+  mutate(demographics.education_three = 
+           case_when(
+             highest_education_numeric == "4" ~ "Bachelors or higher",
+             highest_education_numeric == "3" ~ "A-levels",
+             highest_education_numeric == "1" ~ "GCSEs or lower"
+           )) %>%
+  count(demographics.education_three) %>%
+  mutate(freq = round(n/sum(n), 2)) %>% 
+  drop_na()
+
+```
+
+pie chart labels
+
+```{r education pie chart all labels}
+
+edu_pie_alllabel <-
+
+    highest_education_prop_total %>%
+    mutate(demographics.highest_level_of_education = fct_reorder(highest_education,-n)) %>%
+
+  ggplot(aes(x="", y=freq, fill=demographics.highest_level_of_education)) +
+  geom_bar(width = 1, stat = "identity") +
+  scale_fill_manual(values =  COPINGpalette7) +
+  scale_color_manual(values =  COPINGpalette7) +
+  coord_polar("y",start=0) +
+  theme_void() +
+   labs(title = paste("RAMP/COPING sample self reported level of education",
+                      sep=" "),
+        subtitle = paste("n", sum(highest_education_prop_total$n),
+                         sep = " "),
+        fill = "Self reported level of education")  +
+    geom_text(aes(y = c(0.13,0.04,0.3,0.65),
+                  x = c(1.2,1.2,1.2,1.2), #GCSE, NVQ, A-levels, university
+                  label= paste0(round((freq*100),0),"%")),
+             size=5,
+             face="bold"
+             )
+
+edu_pie_alllabel
+
+```
+
+```{r binary education pie chart all labels}
+edu_pie_binlabel <- 
+    edubindat %>%
+    mutate(demographics.education_binary = fct_reorder(demographics.education_binary,-n)) %>%
+  ggplot(aes(x="", y=freq, fill=demographics.education_binary)) +
+  geom_bar(width = 1, stat = "identity") +
+  scale_fill_manual(values =  COPINGpalette7) +
+  scale_color_manual(values =  COPINGpalette7) +
+  coord_polar("y",start=0) +
+  theme_void() +
+   labs(title = paste("RAMP/COPING sample self reported highest level of education, above or below bachelor degree or equivalent",
+                      sep=" "),
+        subtitle = paste("n", sum(edubindat$n),
+                         sep = " "),
+        fill = "Self reported level of education")  +
+    geom_text(aes(y = c(0.25,0.75),
+                  label= paste0(round((freq*100),0),"%")),
+             size=5,
+             face="bold"
+             )
+
+edu_pie_binlabel
+```
+
+```{r 3 category education pie chart all labels}
+
+edu_pie_catlabel <-
+
+    educatdat %>%
+    mutate(demographics.education_three = fct_reorder(demographics.education_three,-n)) %>%
+
+  ggplot(aes(x="", y=freq, fill=demographics.education_three)) +
+  geom_bar(width = 1, stat = "identity") +
+  scale_fill_manual(values =  COPINGpalette7) +
+  scale_color_manual(values =  COPINGpalette7) +
+  coord_polar("y",start=0) +
+  theme_void() +
+   labs(title = paste("RAMP/COPING sample self reported highest level of education, above or below bachelor degree or equivalent",
+                      sep=" "),
+        subtitle = paste("n", sum(educatdat$n),
+                         sep = " "),
+        fill = "Self reported level of education")  +
+    geom_text(aes(y = c(0.23,0.65,0.05),
+                  label= c(paste0(round((freq[1:3]*100),0),"%")),
+             size=5,
+             face="bold"
+             ))
+
+edu_pie_catlabel
+
+```
+
+pie chart -  no labels
+
+```{r education pie chart no labels }
+edu_pie_nolabel <-
+
+    highest_education_prop_total %>%
+    mutate(demographics.highest_level_of_education = fct_reorder(highest_education,-n)) %>%
+
+  ggplot(aes(x="", y=freq, fill=demographics.highest_level_of_education)) +
+  geom_bar(width = 1, stat = "identity") +
+  scale_fill_manual(values =  COPINGpalette7) +
+  scale_color_manual(values =  COPINGpalette7) +
+  coord_polar("y",start=0) +
+  theme_void() +
+   labs(title = paste("RAMP/COPING sample self reported level of education",
+                      sep=" "),
+        subtitle = paste("n =", sum(highest_education_prop_total$n),
+                         sep = " "),
+        fill = "Self reported level of education")
+
+edu_pie_nolabel
+```
+
+## Ethnicity_collapsed
+### Pie charts
+
+```{r Ethnicity_collapsed prop per total summary}
+Ethnicity_collapsed_prop_Sample <- dat %>%
+  count(Ethnicity_collapsed) %>%
+  drop_na() %>%
+  mutate(freq = round(n/sum(n), 2))
+
+# total responders
+ethN <- sum(Ethnicity_collapsed_prop_Sample$n)
+
+kable(Ethnicity_collapsed_prop_Sample)
+Ethnicity_collapsed_prop_Sample
+```
+
+pie chart with only European label
+
+```{r ethnicity pie chart biggest group label}
+eth_pie_alllabel <- 
+  Ethnicity_collapsed_prop_Sample %>%
+   mutate(Ethnicity_collapsed = fct_reorder(Ethnicity_collapsed,-n)) %>%
+
+  ggplot(aes(x="", y=freq, fill=Ethnicity_collapsed)) +
+  geom_bar(width = 1, stat = "identity") +
+  scale_fill_manual(values =  COPINGpalette6) +
+  scale_color_manual(values =  COPINGpalette6) +
+  coord_polar("y",start=0) +
+  theme_void() +
+   labs(title = paste("RAMP/COPING sample self reported ethnicity",
+                      sep=" "),
+        subtitle = paste("n =", sum(Ethnicity_collapsed_prop_Sample$n),
+                         sep = " "),
+        fill = "Self reported ethnicity")  +
+    geom_text(aes(y = c(0.5),
+                  label= c(paste0(round((freq[1]*100),0),"%"))), #Frequency of European only
+             size=5,
+             face="bold"
+             )
+
+eth_pie_alllabel
+```
+
+Pie chart - no labels
+
+```{r ethnicity pie chart no label}
+eth_pie_nolabel <- 
+  Ethnicity_collapsed_prop_Sample %>%
+   mutate(Ethnicity_collapsed = fct_reorder(Ethnicity_collapsed,-n)) %>%
+
+  ggplot(aes(x="", y=freq, fill=Ethnicity_collapsed)) +
+  geom_bar(width = 1, stat = "identity") +
+  scale_fill_manual(values =  COPINGpalette6) +
+  scale_color_manual(values =  COPINGpalette6) +
+  coord_polar("y",start=0) +
+  theme_void() +
+   labs(title = paste("RAMP/COPING sample self reported ethnicity",
+                      sep=" "),
+        subtitle = paste("n =", sum(Ethnicity_collapsed_prop_Sample$n),
+                         sep = " "),
+        fill = "Self reported ethnicity")
+
+eth_pie_nolabel
+```
+
+## Gender collapsed
+### Pie charts
+```{r Gender_collapsed prop per total}
+Gender_collapsed_prop_total <- dat %>%
+  count(Gender_collapsed) %>%
+  mutate(freq = round(n/sum(n), 2))
+
+kable(Gender_collapsed_prop_total)
+Gender_collapsed_prop_total
+```
+
+```{r gender pie chart - all labels}
+gen_pie_alllabel <- 
+  ggplot(Gender_collapsed_prop_total, aes(x="", y=freq, fill=Gender_collapsed)) +
+  geom_bar(width = 1, stat = "identity") +
+  scale_fill_manual(values =  COPINGpalette5) +
+  scale_color_manual(values =  COPINGpalette5) +
+  coord_polar("y",start=0) +
+  theme_void() +
+   labs(title = paste("RAMP/COPING sample self reported gender",
+                      sep=" "),
+        subtitle = paste("n", sum(Gender_collapsed_prop_total$n),
+                         sep = " "),
+        fill = "Self reported gender")  +
+    geom_text(aes(y = c(0.85,0.35,0),
+                  x = c(1.2,1.2,1.8),
+                  label= c(paste0(round((freq[1:2]*100),0),"%"),paste0(round((freq[3]*100),1),"%"))),
+             size=5,
+             face="bold"
+             )
+
+gen_pie_alllabel
+```
+
+Pie chart - only labelling two largest groups (male and female)
+```{r gender pie chart - male/female labels only}
+gen_pie <- 
+  ggplot(Gender_collapsed_prop_total, aes(x="", y=freq, fill=Gender_collapsed)) +
+  geom_bar(width = 1, stat = "identity") +
+  scale_fill_manual(values =  COPINGpalette5) +
+  scale_color_manual(values =  COPINGpalette5) +
+  coord_polar("y",start=0) +
+  theme_void() +
+   labs(title = paste("RAMP/COPING sample self reported gender",
+                      sep=" "),
+        subtitle = paste("n", sum(Gender_collapsed_prop_total$n),
+                         sep = " "),
+        fill = "Self reported gender")  +
+    geom_text(aes(y = c(0.85,0.35,0),
+                  x = c(1.2,1.2,1.8),
+                  label= c(paste0(round((freq[1:2]*100),0),"%"),"")),
+             size=5,
+             face="bold"
+             )
+
+gen_pie
+```
+
+Pie chart -  no labels
+```{r gender pie chart - no labels }
+gen_pie_nolabel <- 
+  ggplot(Gender_collapsed_prop_total, aes(x="", y=freq, fill=Gender_collapsed)) +
+  geom_bar(width = 1, stat = "identity") +
+  scale_fill_manual(values =  COPINGpalette5) +
+  scale_color_manual(values =  COPINGpalette5) +
+  coord_polar("y",start=0) +
+  theme_void() +
+   labs(title = paste("RAMP/COPING sample self reported gender",
+                      sep=" "),
+        subtitle = paste("n", sum(Gender_collapsed_prop_total$n),
+                         sep = " "),
+        fill = "Self reported gender")
+
+gen_pie_nolabel
+```
+
+```{r age_category prop total (ungrouped) plot}
+#Colour palette
+RAMPagepalette <- c(
+  "#00D9AC",
+  "#21D9B3",
+  "#4DD9BC",
+  "#78D9C5",
+  "#8ED9C9",
+  "#A3D9CE",
+  "#CFD9D7",
+  "#DAD0BA",
+  "#DAC38F",
+  "#DAC38F",
+  "#DAB663",
+  "#DAA937",
+  "#DA9C0C"
+  )
+
+# Bar plot
+plot.age <- 
+  age_category_prop_total %>%
+    mutate(age_category = fct_reorder(age_category, order)) %>%
+  ggplot(aes(x = age_category)) +
+  geom_bar(aes(
+    y = n,
+    color = age_category,
+    fill = age_category,
+    alpha = 1),
+    stat ="identity"
+    ) +
+  scale_fill_manual(values =  RAMPagepalette) +
+  scale_color_manual(values =  RAMPagepalette) +
+  labs(x = "",
+       y = "Total count",
+       title = "Number of participants in each age category",
+       subtitle = paste0("n = ", ageN),
+       fill = "Age category") +
+   guides(
+     alpha = FALSE, # Display no guide for alpha
+     color = FALSE, # Display no guide for color
+     fill = FALSE # Display no guide for fill
+     ) +
+  scale_x_discrete(
+    limits = (levels(age_category_prop_total$age_category))
+    ) +
+  theme_classic2() +
+   theme(
+     axis.text.x = element_text(
+       colour="black",
+       size = 12,
+       angle = 45,
+       vjust = 0.5),
+     axis.text.y = element_text(
+       colour="black",
+       size = 12)
+     )
+
+plot.age
+```
+
+# Compare the GLAD/EDGI and COPING subcohorts: EDGI, GLAD, NBR, RAMP
++++CH: Diagnosis, ethnicity, gender, age
+
+# age_category
+## Proportion tables
+```{r age_category per Sample prop per total}
+age_category_per_Sample_prop_total <- dat %>%
+  count(age_category, Sample) %>%
+  mutate(Prop = round(n/sum(n), 2))
+
+kable(age_category_per_Sample_prop_total)
+age_category_per_Sample_prop_total
+```
+
+```{r age_category per Sample prop per Sample}
+age_category_per_Sample_prop_Sample <- dat %>%
+  group_by(Sample) %>%
+  count(age_category, Sample) %>%
+  mutate(Prop = round(n/sum(n), 2))
+
+kable(age_category_per_Sample_prop_Sample)
+age_category_per_Sample_prop_Sample
+```
+
+## Cross tables
+```{r age_category per Sample prop cross table}
+age_category_per_Sample_prop_Sample_cross_table <- dat %>%
+  group_by(Sample) %>%
+  count(age_category, Sample) %>%
+  mutate(Prop = round(n/sum(n), 2)) %>%
+  pivot_wider(names_from = Sample, values_from = c(n, Prop))
+
+kable(age_category_per_Sample_prop_Sample_cross_table)
+age_category_per_Sample_prop_Sample_cross_table
+```
+
+```{r age_category per Sample count cross table}
+age_category_per_Sample_count_cross_table <- dat %>%
+  count(age_category, Sample) %>%
+  spread(key = Sample, value = n) %>%
+  mutate(
+    EDGI = as.integer(replace_na(EDGI, 0)),
+    GLAD = as.integer(replace_na(GLAD, 0)),
+    NBR = as.integer(replace_na(NBR, 0)),
+    RAMP = as.integer(replace_na(RAMP, 0))
+  )
+
+kable(age_category_per_Sample_count_cross_table)
+age_category_per_Sample_count_cross_table
+```
+
+## Chi square test
+```{r age_category per Sample chisquare test}
+age_category_per_Sample_chissquare_test <- dat %>%
+  count(age_category, Sample) %>%
+  spread(key = Sample, value = n) %>%
+  select(-age_category) %>%
+  mutate(
+    EDGI = as.integer(replace_na(EDGI, 0)),
+    GLAD = as.integer(replace_na(GLAD, 0)),
+    NBR = as.integer(replace_na(NBR, 0)),
+    RAMP = as.integer(replace_na(RAMP, 0))
+  ) %>%
+  chisq.test() %>%
+  glance()
+
+kable(age_category_per_Sample_chissquare_test)
+age_category_per_Sample_chissquare_test
+```
+
+```{r age_category by Sample count plot}
+age_category_by_Sample_count_plot <- age_category_per_Sample_prop_Sample %>%
+  ggplot(mapping = aes(
+    x = age_category,
+    y = n)
+  ) +
+  geom_bar(
+    aes(fill = Sample),
+    stat="identity",
+    binwidth = 1,
+    position = position_dodge2(preserve = "single")
+  ) +
+  labs(
+    x = "age_category",
+    y = "Number of participants",
+    fill = "Sample") +
+  theme_personal +
+  scale_fill_manual(
+    values = COPINGpalette6
+  ) +
+  coord_flip()
+
+age_category_by_Sample_count_plot
+```
+
+```{r age_category by Sample prop plot}
+age_category_by_Sample_prop_plot <- age_category_per_Sample_prop_Sample %>%
+  ggplot(mapping = aes(
+    x = age_category,
+    y = Prop)
+  ) +
+  geom_bar(
+    aes(fill = Sample),
+    stat="identity",
+    binwidth = 1,
+    position = position_dodge2(preserve = "single")
+  ) +
+  labs(
+    x = "age_category",
+    y = "Percentage per sample",
+    fill = "Sample") +
+  theme_personal +
+  scale_fill_manual(
+    values = COPINGpalette6
+  ) +
+  coord_flip()
+
+age_category_by_Sample_prop_plot
+```
+
+# Ethnicity_collapsed
+## Proportion tables
+```{r Ethnicity_collapsed per Sample prop per total}
+Ethnicity_collapsed_per_Sample_prop_total <- dat %>%
+  count(Ethnicity_collapsed, Sample) %>%
+  mutate(Prop = round(n/sum(n), 2))
+
+kable(Ethnicity_collapsed_per_Sample_prop_total)
+Ethnicity_collapsed_per_Sample_prop_total
+```
+
+```{r Ethnicity_collapsed per Sample prop per Sample}
+Ethnicity_collapsed_per_Sample_prop_Sample <- dat %>%
+  group_by(Sample) %>%
+  count(Ethnicity_collapsed, Sample) %>%
+  mutate(Prop = round(n/sum(n), 2))
+
+kable(Ethnicity_collapsed_per_Sample_prop_Sample)
+Ethnicity_collapsed_per_Sample_prop_Sample
+```
+
+## Cross tables
+```{r Ethnicity_collapsed per Sample prop cross table}
+Ethnicity_collapsed_per_Sample_prop_Sample_cross_table <- dat %>%
+  group_by(Sample) %>%
+  count(Ethnicity_collapsed, Sample) %>%
+  mutate(Prop = round(n/sum(n), 2)) %>%
+  pivot_wider(names_from = Sample, values_from = c(n, Prop))
+
+kable(Ethnicity_collapsed_per_Sample_prop_Sample_cross_table)
+Ethnicity_collapsed_per_Sample_prop_Sample_cross_table
+```
+
+```{r Ethnicity_collapsed per Sample count cross table}
+Ethnicity_collapsed_per_Sample_count_cross_table <- dat %>%
+  count(Ethnicity_collapsed, Sample) %>%
+  spread(key = Sample, value = n) %>%
+  mutate(
+    EDGI = as.integer(replace_na(EDGI, 0)),
+    GLAD = as.integer(replace_na(GLAD, 0)),
+    NBR = as.integer(replace_na(NBR, 0)),
+    RAMP = as.integer(replace_na(RAMP, 0))
+  )
+
+kable(Ethnicity_collapsed_per_Sample_count_cross_table)
+Ethnicity_collapsed_per_Sample_count_cross_table
+```
+
+## Chi square test
+```{r Ethnicity_collapsed per Sample chisquare test}
+Ethnicity_collapsed_per_Sample_chissquare_test <- dat %>%
+  count(Ethnicity_collapsed, Sample) %>%
+  spread(key = Sample, value = n) %>%
+  select(-Ethnicity_collapsed) %>%
+  mutate(
+    EDGI = as.integer(replace_na(EDGI, 0)),
+    GLAD = as.integer(replace_na(GLAD, 0)),
+    NBR = as.integer(replace_na(NBR, 0)),
+    RAMP = as.integer(replace_na(RAMP, 0))
+  ) %>%
+  chisq.test() %>%
+  glance()
+
+kable(Ethnicity_collapsed_per_Sample_chissquare_test)
+Ethnicity_collapsed_per_Sample_chissquare_test
+```
+
+```{r Ethnicity_collapsed by Sample count plot}
+Ethnicity_collapsed_by_Sample_count_plot <- Ethnicity_collapsed_per_Sample_prop_Sample %>%
+  ggplot(mapping = aes(
+    x = Ethnicity_collapsed,
+    y = n)
+  ) +
+  geom_bar(
+    aes(fill = Sample),
+    stat="identity",
+    binwidth = 1,
+    position = position_dodge2(preserve = "single")
+  ) +
+  labs(
+    x = "Ethnicity_collapsed",
+    y = "Number of participants",
+    fill = "Sample") +
+  theme_personal +
+  scale_fill_manual(
+    values = COPINGpalette6
+  ) +
+  coord_flip()
+
+Ethnicity_collapsed_by_Sample_count_plot
+```
+
+```{r Ethnicity_collapsed by Sample prop plot}
+Ethnicity_collapsed_by_Sample_prop_plot <- Ethnicity_collapsed_per_Sample_prop_Sample %>%
+  ggplot(mapping = aes(
+    x = Ethnicity_collapsed,
+    y = Prop)
+  ) +
+  geom_bar(
+    aes(fill = Sample),
+    stat="identity",
+    binwidth = 1,
+    position = position_dodge2(preserve = "single")
+  ) +
+  labs(
+    x = "Ethnicity_collapsed",
+    y = "Percentage per sample",
+    fill = "Sample") +
+  theme_personal +
+  scale_fill_manual(
+    values = COPINGpalette6
+  ) +
+  coord_flip()
+
+Ethnicity_collapsed_by_Sample_prop_plot
+```
+
+# Gender_collapsed
+## Proportion tables
+```{r Gender_collapsed per Sample prop per total}
+Gender_collapsed_per_Sample_prop_total <- dat %>%
+  count(Gender_collapsed, Sample) %>%
+  mutate(Prop = round(n/sum(n), 2))
+
+kable(Gender_collapsed_per_Sample_prop_total)
+Gender_collapsed_per_Sample_prop_total
+```
+
+```{r Gender_collapsed per Sample prop per Sample}
+Gender_collapsed_per_Sample_prop_Sample <- dat %>%
+  group_by(Sample) %>%
+  count(Gender_collapsed, Sample) %>%
+  mutate(Prop = round(n/sum(n), 2))
+
+kable(Gender_collapsed_per_Sample_prop_Sample)
+Gender_collapsed_per_Sample_prop_Sample
+```
+
+## Cross tables
+```{r Gender_collapsed per Sample prop cross table}
+Gender_collapsed_per_Sample_prop_Sample_cross_table <- dat %>%
+  group_by(Sample) %>%
+  count(Gender_collapsed, Sample) %>%
+  mutate(Prop = round(n/sum(n), 2)) %>%
+  pivot_wider(names_from = Sample, values_from = c(n, Prop))
+
+kable(Gender_collapsed_per_Sample_prop_Sample_cross_table)
+Gender_collapsed_per_Sample_prop_Sample_cross_table
+```
+
+```{r Gender_collapsed per Sample count cross table}
+Gender_collapsed_per_Sample_count_cross_table <- dat %>%
+  count(Gender_collapsed, Sample) %>%
+  spread(key = Sample, value = n) %>%
+  mutate(
+    EDGI = as.integer(replace_na(EDGI, 0)),
+    GLAD = as.integer(replace_na(GLAD, 0)),
+    NBR = as.integer(replace_na(NBR, 0)),
+    RAMP = as.integer(replace_na(RAMP, 0))
+  )
+
+kable(Gender_collapsed_per_Sample_count_cross_table)
+Gender_collapsed_per_Sample_count_cross_table
+```
+
+## Chi square test
+```{r Gender_collapsed per Sample chisquare test}
+Gender_collapsed_per_Sample_chissquare_test <- dat %>%
+  count(Gender_collapsed, Sample) %>%
+  spread(key = Sample, value = n) %>%
+  select(-Gender_collapsed) %>%
+  mutate(
+    EDGI = as.integer(replace_na(EDGI, 0)),
+    GLAD = as.integer(replace_na(GLAD, 0)),
+    NBR = as.integer(replace_na(NBR, 0)),
+    RAMP = as.integer(replace_na(RAMP, 0))
+  ) %>%
+  chisq.test() %>%
+  glance()
+
+kable(Gender_collapsed_per_Sample_chissquare_test)
+Gender_collapsed_per_Sample_chissquare_test
+```
+
+```{r Gender_collapsed by Sample count plot}
+Gender_collapsed_by_Sample_count_plot <- Gender_collapsed_per_Sample_prop_Sample %>%
+  ggplot(mapping = aes(
+    x = Gender_collapsed,
+    y = n)
+  ) +
+  geom_bar(
+    aes(fill = Sample),
+    stat="identity",
+    binwidth = 1,
+    position = position_dodge2(preserve = "single")
+  ) +
+  labs(
+    x = "Gender_collapsed",
+    y = "Number of participants",
+    fill = "Sample") +
+  theme_personal +
+  scale_fill_manual(
+    values = COPINGpalette6
+  ) +
+  coord_flip()
+
+Gender_collapsed_by_Sample_count_plot
+```
+
+```{r Gender_collapsed by Sample prop plot}
+Gender_collapsed_by_Sample_prop_plot <- Gender_collapsed_per_Sample_prop_Sample %>%
+  ggplot(mapping = aes(
+    x = Gender_collapsed,
+    y = Prop)
+  ) +
+  geom_bar(
+    aes(fill = Sample),
+    stat="identity",
+    binwidth = 1,
+    position = position_dodge2(preserve = "single")
+  ) +
+  labs(
+    x = "Gender_collapsed",
+    y = "Percentage per sample",
+    fill = "Sample") +
+  theme_personal +
+  scale_fill_manual(
+    values = COPINGpalette6
+  ) +
+  coord_flip()
+
+Gender_collapsed_by_Sample_prop_plot
+```
+
+# highest_education
+## Proportion tables
+```{r highest_education per Sample prop per total}
+highest_education_per_Sample_prop_total <- dat %>%
+  count(highest_education, Sample) %>%
+  mutate(Prop = round(n/sum(n), 2))
+
+kable(highest_education_per_Sample_prop_total)
+highest_education_per_Sample_prop_total
+```
+
+```{r highest_education per Sample prop per Sample}
+highest_education_per_Sample_prop_Sample <- dat %>%
+  group_by(Sample) %>%
+  count(highest_education, Sample) %>%
+  mutate(Prop = round(n/sum(n), 2))
+
+kable(highest_education_per_Sample_prop_Sample)
+highest_education_per_Sample_prop_Sample
+```
+
+## Cross tables
+```{r highest_education per Sample prop cross table}
+highest_education_per_Sample_prop_Sample_cross_table <- dat %>%
+  group_by(Sample) %>%
+  count(highest_education, Sample) %>%
+  mutate(Prop = round(n/sum(n), 2)) %>%
+  pivot_wider(names_from = Sample, values_from = c(n, Prop))
+
+kable(highest_education_per_Sample_prop_Sample_cross_table)
+highest_education_per_Sample_prop_Sample_cross_table
+```
+
+```{r highest_education per Sample count cross table}
+highest_education_per_Sample_count_cross_table <- dat %>%
+  count(highest_education, Sample) %>%
+  spread(key = Sample, value = n) %>%
+  mutate(
+    EDGI = as.integer(replace_na(EDGI, 0)),
+    GLAD = as.integer(replace_na(GLAD, 0)),
+    NBR = as.integer(replace_na(NBR, 0)),
+    RAMP = as.integer(replace_na(RAMP, 0))
+  )
+
+kable(highest_education_per_Sample_count_cross_table)
+highest_education_per_Sample_count_cross_table
+```
+
+## Chi square test
+```{r highest_education per Sample chisquare test}
+highest_education_per_Sample_chissquare_test <- dat %>%
+  count(highest_education, Sample) %>%
+  spread(key = Sample, value = n) %>%
+  select(-highest_education) %>%
+  mutate(
+    EDGI = as.integer(replace_na(EDGI, 0)),
+    GLAD = as.integer(replace_na(GLAD, 0)),
+    NBR = as.integer(replace_na(NBR, 0)),
+    RAMP = as.integer(replace_na(RAMP, 0))
+  ) %>%
+  chisq.test() %>%
+  glance()
+
+kable(highest_education_per_Sample_chissquare_test)
+highest_education_per_Sample_chissquare_test
+```
+
+## Bar plots
+```{r highest_education by Sample count plot}
+highest_education_by_Sample_count_plot <- highest_education_per_Sample_prop_Sample %>%
+  ggplot(mapping = aes(
+    x = highest_education,
+    y = n)
+  ) +
+  geom_bar(
+    aes(fill = Sample),
+    stat="identity",
+    binwidth = 1,
+    position = position_dodge2(preserve = "single")
+  ) +
+  labs(
+    x = "highest_education",
+    y = "Number of participants",
+    fill = "Sample") +
+  theme_personal +
+  scale_fill_manual(
+    values = COPINGpalette6
+  ) +
+  coord_flip()
+
+highest_education_by_Sample_count_plot
+```
+
+```{r highest_education by Sample prop plot}
+highest_education_by_Sample_prop_plot <- highest_education_per_Sample_prop_Sample %>%
+  ggplot(mapping = aes(
+    x = highest_education,
+    y = Prop)
+  ) +
+  geom_bar(
+    aes(fill = Sample),
+    stat="identity",
+    binwidth = 1,
+    position = position_dodge2(preserve = "single")
+  ) +
+  labs(
+    x = "highest_education",
+    y = "Percentage per sample",
+    fill = "Sample") +
+  theme_personal +
+  scale_fill_manual(
+    values = COPINGpalette6
+  ) +
+  coord_flip()
+
+highest_education_by_Sample_prop_plot
+```
+
+# key_worker
+## Proportion tables
+```{r key_worker per Sample prop per total}
+key_worker_per_Sample_prop_total <- dat %>%
+  count(key_worker, Sample) %>%
+  mutate(Prop = round(n/sum(n), 2))
+
+kable(key_worker_per_Sample_prop_total)
+key_worker_per_Sample_prop_total
+```
+
+```{r key_worker per Sample prop per Sample}
+key_worker_per_Sample_prop_Sample <- dat %>%
+  group_by(Sample) %>%
+  count(key_worker, Sample) %>%
+  mutate(Prop = round(n/sum(n), 2))
+
+kable(key_worker_per_Sample_prop_Sample)
+key_worker_per_Sample_prop_Sample
+```
+
+## Cross tables
+```{r key_worker per Sample prop cross table}
+key_worker_per_Sample_prop_Sample_cross_table <- dat %>%
+  group_by(Sample) %>%
+  count(key_worker, Sample) %>%
+  mutate(Prop = round(n/sum(n), 2)) %>%
+  pivot_wider(names_from = Sample, values_from = c(n, Prop))
+
+kable(key_worker_per_Sample_prop_Sample_cross_table)
+key_worker_per_Sample_prop_Sample_cross_table
+```
+
+```{r key_worker per Sample count cross table}
+key_worker_per_Sample_count_cross_table <- dat %>%
+  count(key_worker, Sample) %>%
+  spread(key = Sample, value = n) %>%
+  mutate(
+    EDGI = as.integer(replace_na(EDGI, 0)),
+    GLAD = as.integer(replace_na(GLAD, 0)),
+    NBR = as.integer(replace_na(NBR, 0)),
+    RAMP = as.integer(replace_na(RAMP, 0))
+  )
+
+kable(key_worker_per_Sample_count_cross_table)
+key_worker_per_Sample_count_cross_table
+```
+
+## Chi square test
+```{r key_worker per Sample chisquare test}
+key_worker_per_Sample_chissquare_test <- dat %>%
+  count(key_worker, Sample) %>%
+  spread(key = Sample, value = n) %>%
+  select(-key_worker) %>%
+  mutate(
+    EDGI = as.integer(replace_na(EDGI, 0)),
+    GLAD = as.integer(replace_na(GLAD, 0)),
+    NBR = as.integer(replace_na(NBR, 0)),
+    RAMP = as.integer(replace_na(RAMP, 0))
+  ) %>%
+  chisq.test() %>%
+  glance()
+
+kable(key_worker_per_Sample_chissquare_test)
+key_worker_per_Sample_chissquare_test
+```
+
+## Bar plots
+```{r key_worker by Sample count plot}
+key_worker_by_Sample_count_plot <- key_worker_per_Sample_prop_Sample %>%
+  ggplot(mapping = aes(
+    x = key_worker,
+    y = n)
+  ) +
+  geom_bar(
+    aes(fill = Sample),
+    stat="identity",
+    binwidth = 1,
+    position = position_dodge2(preserve = "single")
+  ) +
+  labs(
+    x = "key_worker",
+    y = "Number of participants",
+    fill = "Sample") +
+  theme_personal +
+  scale_fill_manual(
+    values = COPINGpalette6
+  ) +
+  coord_flip()
+
+key_worker_by_Sample_count_plot
+```
+
+```{r key_worker by Sample prop plot}
+key_worker_by_Sample_prop_plot <- key_worker_per_Sample_prop_Sample %>%
+  ggplot(mapping = aes(
+    x = key_worker,
+    y = Prop)
+  ) +
+  geom_bar(
+    aes(fill = Sample),
+    stat="identity",
+    binwidth = 1,
+    position = position_dodge2(preserve = "single")
+  ) +
+  labs(
+    x = "key_worker",
+    y = "Percentage per sample",
+    fill = "Sample") +
+  theme_personal +
+  scale_fill_manual(
+    values = COPINGpalette6
+  ) +
+  coord_flip()
+
+key_worker_by_Sample_prop_plot
+```
+
+```{r Save four cohorts as rds file}
+saveRDS(object = dat, file = paste0(data_path, "/four_cohorts_variables_exclusion.rds"))
+```

### 2020-09-16 PANCHANGE_data_preprocessing2020-07-15.Rmd
deleted the neurological stuff from the PANCHANGE_analysis script
Small edits to pre-processing script made to enable knitting.

@@
 
-```{r mhd restricting_vs_binge_eating_eating_disorders}
+```{r EDGI mhd restricting_vs_binge_eating_eating_disorders}
 if(EDGI == TRUE) {
@@
 ```{r Check eating_disorders}
-if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE | RAMP == TRUE) {
+if(GLAD == TRUE | NBR == TRUE | RAMP == TRUE) {
 mhd.raw.id %>%
@@
 
-```{r Check eating_disorders}
+```{r EDGI Check eating_disorders}
 if(EDGI == TRUE) {
@@
 
-```{r mhd check none of the above}
+```{r RAMP mhd check none of the above}
 if(RAMP == TRUE) {
@@
 
-```{r mhd check none of the above}
+```{r NBR EDGI mhd check none of the above}
 if(NBR == TRUE | EDGI == TRUE) {
@@
 
-```{r mhd categories}
+```{r EDGI mhd categories}
 if(EDGI == TRUE) {
@@
 
-```{r coping glad gad copy}
+```{r coping glad phq copy}
 if(GLAD == TRUE) {
@@
 
-```{r coping edgi gad copy}
+```{r coping edgi phq copy}
 if(EDGI == TRUE) {
@@
 
-```{r coping nbr gad copy}
+```{r coping nbr phq copy}
 if(NBR == TRUE) {
@@
 
-```{r coping ramp gad copy}
+```{r coping ramp phq copy}
 if(RAMP == TRUE) {
@@
 dim(dat.raw)[1]-dim(dat.no.sex)[1]
-}
-```
-`r dim(dat.glad.raw)[1]-dim(dat.no.sex)[1]` were excluded because they did not report their sex
+
+excluded_no_sex <- dim(dat.raw)[1]-dim(dat.no.sex)[1]
+
+paste("N =", excluded_no_sex, "were excluded because they did not report their sex", sep = " ")
+}
+```
 
@@
 dim(dat.no.sex.no.gender)[1]-dim(dat.no.sex.no.gender.no.age)[1]
-```
-`r dim(dat.no.gender)[1]-dim(dat.no.sex.no.gender.no.age)[1]` were excluded because they did not report their age
+
+```
+`dim(dat.no.sex.no.gender)[1]-dim(dat.no.sex.no.gender.no.age)[1]` were excluded because they did not report their age
 
@@
 Proportion of people signed up over half a year ago
-```{r glad/edgi ppts signed up over half a year ago, r eval=FALSE, include=FALSE}
+```{r glad/edgi ppts signed up over half a year ago, eval=FALSE, include=FALSE}
 if(GLAD == TRUE | EDGI == TRUE){

### 2020-09-16 PANCHANGE_analysis.Rmd

@@
 ```{r read in data}
-dat <- readRDS(file = paste0(data_path, "/four_cohorts.rds"))
+dat <- readRDS(file = paste0(data_path, "/four_cohorts_variables_exclusion.rds"))
 dim(dat)
@@
 
-Rank the disorders by the size of the change
+++CH: Rank the disorders by the size of the change
 
@@
 Exclude individuals with NA for MHD, age, gender; exclude if prepan data collected after 1 March
+
+++CH: exclusion criteria need double checking
 ```{r exclusion criteria for prepan-baseline analysis}
@@
 ```{r RUBBISH 2, fig.height=7, fig.width=5}
-gad.diff_score_base_prepan_plot /
-  gad.diff_score_retro_prepan_plot /
-  gad.diff_score_base_retro_plot +
-  plot_layout(guides = "collect", heights = c(1,1,1)) +
-  plot_annotation(tag_levels = "A")
-```
+#gad.diff_score_base_prepan_plot /
+#  gad.diff_score_retro_prepan_plot /
+#  gad.diff_score_base_retro_plot +
+#  plot_layout(guides = "collect", heights = c(1,1,1)) +
+#  plot_annotation(tag_levels = "A")
+```

### 2020-09-16 PANCHANGE_analysis.Rmd
added pandemic v prepandemic regression without difference scores

@@
 
+### CHANGE SCORES
+
 ### GAD
@@
   formula = ocir.diff_score_base_prepan ~
+    anxiety_disorders +
+    depressive_disorders +
+    depression_and_anxiety +
+    eating_disorders +
+    obsessive_compulsive_disorders +
+    psychotic_disorders +
+    mhd.mania_hypomania_bipolar_or_manicdepression +
+    mhd.posttraumatic_stress_disorder_ptsd +
+    autism_spectrum_disorder +
+    mhd.attention_deficit_hyperactivity_disorder +
+    mhd.personality_disorder +
+    Gender_collapsed + age_category + Ethnicity_collapsed + time_diff_sign_up_coping,
+  data = dat.prepan)
+
+summary(ocir_prepan_model1b)
+tidy(ocir_prepan_model1b)
+```
+
+### PANDEMIC BASELINE CONTROLLING FOR PREPANDEMIC
+
+### GAD
+Model 0a: Disorder_hierarchical, Unadjusted
+```{r GAD prepan Model 0a}
+gad_prepan_model0a <- lm(
+  formula = gad.sum_score_base ~ gad.sum_score_prepan + 
+    Disorder_hierarchical,
+  data = dat.prepan)
+
+summary(gad_prepan_model0a)
+tidy(gad_prepan_model0a)
+```
+
+Model 0b: Overlapping disorders, Unadjusted
+```{r GAD prepan Model 0b}
+gad_prepan_model0b <- lm(
+  formula = gad.sum_score_base ~ gad.sum_score_prepan +
+    anxiety_disorders +
+    depressive_disorders +
+    depression_and_anxiety +
+    eating_disorders +
+    obsessive_compulsive_disorders +
+    psychotic_disorders +
+    mhd.mania_hypomania_bipolar_or_manicdepression +
+    mhd.posttraumatic_stress_disorder_ptsd +
+    autism_spectrum_disorder +
+    mhd.attention_deficit_hyperactivity_disorder +
+    mhd.personality_disorder,
+  data = dat.prepan)
+
+summary(gad_prepan_model0b)
+tidy(gad_prepan_model0b)
+```
+
+Model 1a: Disorder hierarchical, Adjusted
+  Model 0a + Sex + Age + Ethnicity_collapsed + Time registration and baseline
+```{r GAD prepan Model 1a}
+gad_prepan_model1a <- lm(
+  formula = gad.sum_score_base ~ gad.sum_score_prepan + 
+    Disorder_hierarchical + 
+    Gender_collapsed + 
+    age_category + 
+    Ethnicity_collapsed + 
+    time_diff_sign_up_coping,
+  data = dat.prepan)
+
+summary(gad_prepan_model1a)
+tidy(gad_prepan_model1a)
+```
+
+Model 1b: Overlapping disorders, Adjusted
+  Model 0b + Sex + Age + Ethnicity_collapsed + Time registration and baseline
+```{r GAD prepan Model 1b}
+gad_prepan_model1b <- lm(
+  formula = gad.sum_score_base ~ gad.sum_score_prepan +
+    anxiety_disorders +
+    depressive_disorders +
+    depression_and_anxiety +
+    eating_disorders +
+    obsessive_compulsive_disorders +
+    psychotic_disorders +
+    mhd.mania_hypomania_bipolar_or_manicdepression +
+    mhd.posttraumatic_stress_disorder_ptsd +
+    autism_spectrum_disorder +
+    mhd.attention_deficit_hyperactivity_disorder +
+    mhd.personality_disorder +
+    Gender_collapsed + age_category + Ethnicity_collapsed + time_diff_sign_up_coping,
+  data = dat.prepan)
+
+summary(gad_prepan_model1b)
+tidy(gad_prepan_model1b)
+```
+
+### PHQ
+Model 0a: Disorder_hierarchical, Unadjusted
+```{r PHQ prepan Model 0a}
+phq_prepan_model0a <- lm(
+  formula = phq.sum_score_base ~ phq.sum_score_prepan + 
+    Disorder_hierarchical,
+  data = dat.prepan)
+
+summary(phq_prepan_model0a)
+tidy(phq_prepan_model0a)
+```
+
+Model 0b: Overlapping disorders, Unadjusted
+```{r PHQ prepan Model 0b}
+phq_prepan_model0b <- lm(
+  formula = phq.sum_score_base ~ phq.sum_score_prepan +
+    anxiety_disorders +
+    depressive_disorders +
+    depression_and_anxiety +
+    eating_disorders +
+    obsessive_compulsive_disorders +
+    psychotic_disorders +
+    mhd.mania_hypomania_bipolar_or_manicdepression +
+    mhd.posttraumatic_stress_disorder_ptsd +
+    autism_spectrum_disorder +
+    mhd.attention_deficit_hyperactivity_disorder +
+    mhd.personality_disorder,
+  data = dat.prepan)
+
+summary(phq_prepan_model0b)
+tidy(phq_prepan_model0b)
+```
+
+Model 1a: Disorder hierarchical, Adjusted
+  Model 0a + Sex + Age + Ethnicity_collapsed + Time registration and baseline
+```{r PHQ prepan Model 1a}
+phq_prepan_model1a <- lm(
+  formula = phq.sum_score_base ~ phq.sum_score_prepan + 
+    Disorder_hierarchical + 
+    Gender_collapsed + 
+    age_category + 
+    Ethnicity_collapsed + 
+    time_diff_sign_up_coping,
+  data = dat.prepan)
+
+summary(phq_prepan_model1a)
+tidy(phq_prepan_model1a)
+```
+
+Model 1b: Overlapping disorders, Adjusted
+  Model 0b + Sex + Age + Ethnicity_collapsed + Time registration and baseline
+```{r PHQ prepan Model 1b}
+phq_prepan_model1b <- lm(
+  formula = phq.sum_score_base ~ phq.sum_score_prepan +
+    anxiety_disorders +
+    depressive_disorders +
+    depression_and_anxiety +
+    eating_disorders +
+    obsessive_compulsive_disorders +
+    psychotic_disorders +
+    mhd.mania_hypomania_bipolar_or_manicdepression +
+    mhd.posttraumatic_stress_disorder_ptsd +
+    autism_spectrum_disorder +
+    mhd.attention_deficit_hyperactivity_disorder +
+    mhd.personality_disorder +
+    Gender_collapsed + age_category + Ethnicity_collapsed + time_diff_sign_up_coping,
+  data = dat.prepan)
+
+summary(phq_prepan_model1b)
+tidy(phq_prepan_model1b)
+```
+
+### PCL
+Model 0a: Disorder_hierarchical, Unadjusted
+```{r PCL prepan Model 0a}
+pcl_prepan_model0a <- lm(
+  formula = pcl.sum_score_base ~ pcl.sum_score_prepan + 
+    Disorder_hierarchical,
+  data = dat.prepan)
+
+summary(pcl_prepan_model0a)
+tidy(pcl_prepan_model0a)
+```
+
+Model 0b: Overlapping disorders, Unadjusted
+```{r PCL prepan Model 0b}
+pcl_prepan_model0b <- lm(
+  formula = pcl.sum_score_base ~ pcl.sum_score_prepan +
+    anxiety_disorders +
+    depressive_disorders +
+    depression_and_anxiety +
+    eating_disorders +
+    obsessive_compulsive_disorders +
+    psychotic_disorders +
+    mhd.mania_hypomania_bipolar_or_manicdepression +
+    mhd.posttraumatic_stress_disorder_ptsd +
+    autism_spectrum_disorder +
+    mhd.attention_deficit_hyperactivity_disorder +
+    mhd.personality_disorder,
+  data = dat.prepan)
+
+summary(pcl_prepan_model0b)
+tidy(pcl_prepan_model0b)
+```
+
+Model 1a: Disorder hierarchical, Adjusted
+  Model 0a + Sex + Age + Ethnicity_collapsed + Time registration and baseline
+```{r PCL prepan Model 1a}
+pcl_prepan_model1a <- lm(
+  formula = pcl.sum_score_base ~ pcl.sum_score_prepan + 
+    Disorder_hierarchical + 
+    Gender_collapsed + 
+    age_category + 
+    Ethnicity_collapsed + 
+    time_diff_sign_up_coping,
+  data = dat.prepan)
+
+summary(pcl_prepan_model1a)
+tidy(pcl_prepan_model1a)
+```
+
+Model 1b: Overlapping disorders, Adjusted
+  Model 0b + Sex + Age + Ethnicity_collapsed + Time registration and baseline
+```{r PCL prepan Model 1b}
+pcl_prepan_model1b <- lm(
+  formula = pcl.sum_score_base ~ pcl.sum_score_prepan +
+    anxiety_disorders +
+    depressive_disorders +
+    depression_and_anxiety +
+    eating_disorders +
+    obsessive_compulsive_disorders +
+    psychotic_disorders +
+    mhd.mania_hypomania_bipolar_or_manicdepression +
+    mhd.posttraumatic_stress_disorder_ptsd +
+    autism_spectrum_disorder +
+    mhd.attention_deficit_hyperactivity_disorder +
+    mhd.personality_disorder +
+    Gender_collapsed + age_category + Ethnicity_collapsed + time_diff_sign_up_coping,
+  data = dat.prepan)
+
+summary(pcl_prepan_model1b)
+tidy(pcl_prepan_model1b)
+```
+
+### OCIR
+Model 0a: Disorder_hierarchical, Unadjusted
+```{r OCIR prepan Model 0a}
+ocir_prepan_model0a <- lm(
+  formula = ocir.sum_score_base ~ ocir.sum_score_prepan + 
+    Disorder_hierarchical,
+  data = dat.prepan)
+
+summary(ocir_prepan_model0a)
+tidy(ocir_prepan_model0a)
+```
+
+Model 0b: Overlapping disorders, Unadjusted
+```{r OCIR prepan Model 0b}
+ocir_prepan_model0b <- lm(
+  formula = ocir.sum_score_base ~ ocir.sum_score_prepan +
+    anxiety_disorders +
+    depressive_disorders +
+    depression_and_anxiety +
+    eating_disorders +
+    obsessive_compulsive_disorders +
+    psychotic_disorders +
+    mhd.mania_hypomania_bipolar_or_manicdepression +
+    mhd.posttraumatic_stress_disorder_ptsd +
+    autism_spectrum_disorder +
+    mhd.attention_deficit_hyperactivity_disorder +
+    mhd.personality_disorder,
+  data = dat.prepan)
+
+summary(ocir_prepan_model0b)
+tidy(ocir_prepan_model0b)
+```
+
+Model 1a: Disorder hierarchical, Adjusted
+  Model 0a + Sex + Age + Ethnicity_collapsed + Time registration and baseline
+```{r OCIR prepan Model 1a}
+ocir_prepan_model1a <- lm(
+  formula = ocir.sum_score_base ~ ocir.sum_score_prepan + 
+    Disorder_hierarchical + 
+    Gender_collapsed + 
+    age_category + 
+    Ethnicity_collapsed + 
+    time_diff_sign_up_coping,
+  data = dat.prepan)
+
+summary(ocir_prepan_model1a)
+tidy(ocir_prepan_model1a)
+```
+
+Model 1b: Overlapping disorders, Adjusted
+  Model 0b + Sex + Age + Ethnicity_collapsed + Time registration and baseline
+```{r OCIR prepan Model 1b}
+ocir_prepan_model1b <- lm(
+  formula = ocir.sum_score_base ~ ocir.sum_score_prepan +
     anxiety_disorders +

### 2020-09-16 PANCHANGE_analysis.Rmd
added pandemic v retrospective regression without difference scores

@@
 
+### PANDEMIC BASELINE CONTROLLING FOR RETROSPECTIVE
+
+### GAD
+Model 0a: Disorder_hierarchical, Unadjusted
+```{r GAD retro Model 0a}
+gad_retro_model0a <- lm(
+  formula = gad.sum_score_base ~ gad.sum_score_retro + 
+    Disorder_hierarchical,
+  data = dat.retro)
+
+summary(gad_retro_model0a)
+tidy(gad_retro_model0a)
+```
+
+Model 0b: Overlapping disorders, Unadjusted
+```{r GAD retro Model 0b}
+gad_retro_model0b <- lm(
+  formula = gad.sum_score_base ~ gad.sum_score_retro +
+    anxiety_disorders +
+    depressive_disorders +
+    depression_and_anxiety +
+    eating_disorders +
+    obsessive_compulsive_disorders +
+    psychotic_disorders +
+    mhd.mania_hypomania_bipolar_or_manicdepression +
+    mhd.posttraumatic_stress_disorder_ptsd +
+    autism_spectrum_disorder +
+    mhd.attention_deficit_hyperactivity_disorder +
+    mhd.personality_disorder,
+  data = dat.retro)
+
+summary(gad_retro_model0b)
+tidy(gad_retro_model0b)
+```
+
+Model 1a: Disorder hierarchical, Adjusted
+  Model 0a + Sex + Age + Ethnicity_collapsed + Time registration and baseline
+```{r GAD retro Model 1a}
+gad_retro_model1a <- lm(
+  formula = gad.sum_score_base ~ gad.sum_score_retro + 
+    Disorder_hierarchical + 
+    Gender_collapsed + 
+    age_category + 
+    Ethnicity_collapsed + 
+    time_diff_sign_up_coping,
+  data = dat.retro)
+
+summary(gad_retro_model1a)
+tidy(gad_retro_model1a)
+```
+
+Model 1b: Overlapping disorders, Adjusted
+  Model 0b + Sex + Age + Ethnicity_collapsed + Time registration and baseline
+```{r GAD retro Model 1b}
+gad_retro_model1b <- lm(
+  formula = gad.sum_score_base ~ gad.sum_score_retro +
+    anxiety_disorders +
+    depressive_disorders +
+    depression_and_anxiety +
+    eating_disorders +
+    obsessive_compulsive_disorders +
+    psychotic_disorders +
+    mhd.mania_hypomania_bipolar_or_manicdepression +
+    mhd.posttraumatic_stress_disorder_ptsd +
+    autism_spectrum_disorder +
+    mhd.attention_deficit_hyperactivity_disorder +
+    mhd.personality_disorder +
+    Gender_collapsed + age_category + Ethnicity_collapsed + time_diff_sign_up_coping,
+  data = dat.retro)
+
+summary(gad_retro_model1b)
+tidy(gad_retro_model1b)
+```
+
+### PHQ
+Model 0a: Disorder_hierarchical, Unadjusted
+```{r PHQ retro Model 0a}
+phq_retro_model0a <- lm(
+  formula = phq.sum_score_base ~ phq.sum_score_retro + 
+    Disorder_hierarchical,
+  data = dat.retro)
+
+summary(phq_retro_model0a)
+tidy(phq_retro_model0a)
+```
+
+Model 0b: Overlapping disorders, Unadjusted
+```{r PHQ retro Model 0b}
+phq_retro_model0b <- lm(
+  formula = phq.sum_score_base ~ phq.sum_score_retro +
+    anxiety_disorders +
+    depressive_disorders +
+    depression_and_anxiety +
+    eating_disorders +
+    obsessive_compulsive_disorders +
+    psychotic_disorders +
+    mhd.mania_hypomania_bipolar_or_manicdepression +
+    mhd.posttraumatic_stress_disorder_ptsd +
+    autism_spectrum_disorder +
+    mhd.attention_deficit_hyperactivity_disorder +
+    mhd.personality_disorder,
+  data = dat.retro)
+
+summary(phq_retro_model0b)
+tidy(phq_retro_model0b)
+```
+
+Model 1a: Disorder hierarchical, Adjusted
+  Model 0a + Sex + Age + Ethnicity_collapsed + Time registration and baseline
+```{r PHQ retro Model 1a}
+phq_retro_model1a <- lm(
+  formula = phq.sum_score_base ~ phq.sum_score_retro + 
+    Disorder_hierarchical + 
+    Gender_collapsed + 
+    age_category + 
+    Ethnicity_collapsed + 
+    time_diff_sign_up_coping,
+  data = dat.retro)
+
+summary(phq_retro_model1a)
+tidy(phq_retro_model1a)
+```
+
+Model 1b: Overlapping disorders, Adjusted
+  Model 0b + Sex + Age + Ethnicity_collapsed + Time registration and baseline
+```{r PHQ retro Model 1b}
+phq_retro_model1b <- lm(
+  formula = phq.sum_score_base ~ phq.sum_score_retro +
+    anxiety_disorders +
+    depressive_disorders +
+    depression_and_anxiety +
+    eating_disorders +
+    obsessive_compulsive_disorders +
+    psychotic_disorders +
+    mhd.mania_hypomania_bipolar_or_manicdepression +
+    mhd.posttraumatic_stress_disorder_ptsd +
+    autism_spectrum_disorder +
+    mhd.attention_deficit_hyperactivity_disorder +
+    mhd.personality_disorder +
+    Gender_collapsed + age_category + Ethnicity_collapsed + time_diff_sign_up_coping,
+  data = dat.retro)
+
+summary(phq_retro_model1b)
+tidy(phq_retro_model1b)
+```
+
+### PCL
+Model 0a: Disorder_hierarchical, Unadjusted
+```{r PCL retro Model 0a}
+pcl_retro_model0a <- lm(
+  formula = pcl.sum_score_base ~ pcl.sum_score_retro + 
+    Disorder_hierarchical,
+  data = dat.retro)
+
+summary(pcl_retro_model0a)
+tidy(pcl_retro_model0a)
+```
+
+Model 0b: Overlapping disorders, Unadjusted
+```{r PCL retro Model 0b}
+pcl_retro_model0b <- lm(
+  formula = pcl.sum_score_base ~ pcl.sum_score_retro +
+    anxiety_disorders +
+    depressive_disorders +
+    depression_and_anxiety +
+    eating_disorders +
+    obsessive_compulsive_disorders +
+    psychotic_disorders +
+    mhd.mania_hypomania_bipolar_or_manicdepression +
+    mhd.posttraumatic_stress_disorder_ptsd +
+    autism_spectrum_disorder +
+    mhd.attention_deficit_hyperactivity_disorder +
+    mhd.personality_disorder,
+  data = dat.retro)
+
+summary(pcl_retro_model0b)
+tidy(pcl_retro_model0b)
+```
+
+Model 1a: Disorder hierarchical, Adjusted
+  Model 0a + Sex + Age + Ethnicity_collapsed + Time registration and baseline
+```{r PCL retro Model 1a}
+pcl_retro_model1a <- lm(
+  formula = pcl.sum_score_base ~ pcl.sum_score_retro + 
+    Disorder_hierarchical + 
+    Gender_collapsed + 
+    age_category + 
+    Ethnicity_collapsed + 
+    time_diff_sign_up_coping,
+  data = dat.retro)
+
+summary(pcl_retro_model1a)
+tidy(pcl_retro_model1a)
+```
+
+Model 1b: Overlapping disorders, Adjusted
+  Model 0b + Sex + Age + Ethnicity_collapsed + Time registration and baseline
+```{r PCL retro Model 1b}
+pcl_retro_model1b <- lm(
+  formula = pcl.sum_score_base ~ pcl.sum_score_retro +
+    anxiety_disorders +
+    depressive_disorders +
+    depression_and_anxiety +
+    eating_disorders +
+    obsessive_compulsive_disorders +
+    psychotic_disorders +
+    mhd.mania_hypomania_bipolar_or_manicdepression +
+    mhd.posttraumatic_stress_disorder_ptsd +
+    autism_spectrum_disorder +
+    mhd.attention_deficit_hyperactivity_disorder +
+    mhd.personality_disorder +
+    Gender_collapsed + age_category + Ethnicity_collapsed + time_diff_sign_up_coping,
+  data = dat.retro)
+
+summary(pcl_retro_model1b)
+tidy(pcl_retro_model1b)
+```
+
+### OCIR
+Model 0a: Disorder_hierarchical, Unadjusted
+```{r OCIR retro Model 0a}
+ocir_retro_model0a <- lm(
+  formula = ocir.sum_score_base ~ ocir.sum_score_retro + 
+    Disorder_hierarchical,
+  data = dat.retro)
+
+summary(ocir_retro_model0a)
+tidy(ocir_retro_model0a)
+```
+
+Model 0b: Overlapping disorders, Unadjusted
+```{r OCIR retro Model 0b}
+ocir_retro_model0b <- lm(
+  formula = ocir.sum_score_base ~ ocir.sum_score_retro +
+    anxiety_disorders +
+    depressive_disorders +
+    depression_and_anxiety +
+    eating_disorders +
+    obsessive_compulsive_disorders +
+    psychotic_disorders +
+    mhd.mania_hypomania_bipolar_or_manicdepression +
+    mhd.posttraumatic_stress_disorder_ptsd +
+    autism_spectrum_disorder +
+    mhd.attention_deficit_hyperactivity_disorder +
+    mhd.personality_disorder,
+  data = dat.retro)
+
+summary(ocir_retro_model0b)
+tidy(ocir_retro_model0b)
+```
+
+Model 1a: Disorder hierarchical, Adjusted
+  Model 0a + Sex + Age + Ethnicity_collapsed + Time registration and baseline
+```{r OCIR retro Model 1a}
+ocir_retro_model1a <- lm(
+  formula = ocir.sum_score_base ~ ocir.sum_score_retro + 
+    Disorder_hierarchical + 
+    Gender_collapsed + 
+    age_category + 
+    Ethnicity_collapsed + 
+    time_diff_sign_up_coping,
+  data = dat.retro)
+
+summary(ocir_retro_model1a)
+tidy(ocir_retro_model1a)
+```
+
+Model 1b: Overlapping disorders, Adjusted
+  Model 0b + Sex + Age + Ethnicity_collapsed + Time registration and baseline
+```{r OCIR retro Model 1b}
+ocir_retro_model1b <- lm(
+  formula = ocir.sum_score_base ~ ocir.sum_score_retro +
+    anxiety_disorders +
+    depressive_disorders +
+    depression_and_anxiety +
+    eating_disorders +
+    obsessive_compulsive_disorders +
+    psychotic_disorders +
+    mhd.mania_hypomania_bipolar_or_manicdepression +
+    mhd.posttraumatic_stress_disorder_ptsd +
+    autism_spectrum_disorder +
+    mhd.attention_deficit_hyperactivity_disorder +
+    mhd.personality_disorder +
+    Gender_collapsed + age_category + Ethnicity_collapsed + time_diff_sign_up_coping,
+  data = dat.retro)
+
+summary(ocir_retro_model1b)
+tidy(ocir_retro_model1b)
+```
+
 # RUBBISH

### 2020-09-17 PANCHANGE_analysis.Rmd

--- 2020-09-16 PANCHANGE_analysis.Rmd
@@
 
+### PANDEMIC BASELINE CONTROLLING FOR PREPANDEMIC
+
+### GAD
+Model 0a: Disorder_hierarchical, Unadjusted
+```{r GAD prepan Model absolute values absolute values 0a}
+gad_prepan_model0a <- lm(
+  formula = gad.sum_score_base ~ gad.sum_score_prepan + 
+    Disorder_hierarchical,
+  data = dat.prepan)
+
+summary(gad_prepan_model0a)
+tidy(gad_prepan_model0a)
+```
+
+Model 0b: Overlapping disorders, Unadjusted
+```{r GAD prepan Model absolute values 0b}
+gad_prepan_model0b <- lm(
+  formula = gad.sum_score_base ~ gad.sum_score_prepan +
+    anxiety_disorders +
+    depressive_disorders +
+    depression_and_anxiety +
+    eating_disorders +
+    obsessive_compulsive_disorders +
+    psychotic_disorders +
+    mhd.mania_hypomania_bipolar_or_manicdepression +
+    mhd.posttraumatic_stress_disorder_ptsd +
+    autism_spectrum_disorder +
+    mhd.attention_deficit_hyperactivity_disorder +
+    mhd.personality_disorder,
+  data = dat.prepan)
+
+summary(gad_prepan_model0b)
+tidy(gad_prepan_model0b)
+```
+
+Model 1a: Disorder hierarchical, Adjusted
+  Model 0a + Sex + Age + Ethnicity_collapsed + Time registration and baseline
+```{r GAD prepan Model absolute values 1a}
+gad_prepan_model1a <- lm(
+  formula = gad.sum_score_base ~ gad.sum_score_prepan + 
+    Disorder_hierarchical + 
+    Gender_collapsed + 
+    age_category + 
+    Ethnicity_collapsed + 
+    time_diff_sign_up_coping,
+  data = dat.prepan)
+
+summary(gad_prepan_model1a)
+tidy(gad_prepan_model1a)
+```
+
+Model 1b: Overlapping disorders, Adjusted
+  Model 0b + Sex + Age + Ethnicity_collapsed + Time registration and baseline
+```{r GAD prepan Model absolute values 1b}
+gad_prepan_model1b <- lm(
+  formula = gad.sum_score_base ~ gad.sum_score_prepan +
+    anxiety_disorders +
+    depressive_disorders +
+    depression_and_anxiety +
+    eating_disorders +
+    obsessive_compulsive_disorders +
+    psychotic_disorders +
+    mhd.mania_hypomania_bipolar_or_manicdepression +
+    mhd.posttraumatic_stress_disorder_ptsd +
+    autism_spectrum_disorder +
+    mhd.attention_deficit_hyperactivity_disorder +
+    mhd.personality_disorder +
+    Gender_collapsed + age_category + Ethnicity_collapsed + time_diff_sign_up_coping,
+  data = dat.prepan)
+
+summary(gad_prepan_model1b)
+tidy(gad_prepan_model1b)
+```
+
+### PHQ
+Model 0a: Disorder_hierarchical, Unadjusted
+```{r PHQ prepan Model absolute values 0a}
+phq_prepan_model0a <- lm(
+  formula = phq.sum_score_base ~ phq.sum_score_prepan + 
+    Disorder_hierarchical,
+  data = dat.prepan)
+
+summary(phq_prepan_model0a)
+tidy(phq_prepan_model0a)
+```
+
+Model 0b: Overlapping disorders, Unadjusted
+```{r PHQ prepan Model absolute values 0b}
+phq_prepan_model0b <- lm(
+  formula = phq.sum_score_base ~ phq.sum_score_prepan +
+    anxiety_disorders +
+    depressive_disorders +
+    depression_and_anxiety +
+    eating_disorders +
+    obsessive_compulsive_disorders +
+    psychotic_disorders +
+    mhd.mania_hypomania_bipolar_or_manicdepression +
+    mhd.posttraumatic_stress_disorder_ptsd +
+    autism_spectrum_disorder +
+    mhd.attention_deficit_hyperactivity_disorder +
+    mhd.personality_disorder,
+  data = dat.prepan)
+
+summary(phq_prepan_model0b)
+tidy(phq_prepan_model0b)
+```
+
+Model 1a: Disorder hierarchical, Adjusted
+  Model 0a + Sex + Age + Ethnicity_collapsed + Time registration and baseline
+```{r PHQ prepan Model absolute values 1a}
+phq_prepan_model1a <- lm(
+  formula = phq.sum_score_base ~ phq.sum_score_prepan + 
+    Disorder_hierarchical + 
+    Gender_collapsed + 
+    age_category + 
+    Ethnicity_collapsed + 
+    time_diff_sign_up_coping,
+  data = dat.prepan)
+
+summary(phq_prepan_model1a)
+tidy(phq_prepan_model1a)
+```
+
+Model 1b: Overlapping disorders, Adjusted
+  Model 0b + Sex + Age + Ethnicity_collapsed + Time registration and baseline
+```{r PHQ prepan Model absolute values 1b}
+phq_prepan_model1b <- lm(
+  formula = phq.sum_score_base ~ phq.sum_score_prepan +
+    anxiety_disorders +
+    depressive_disorders +
+    depression_and_anxiety +
+    eating_disorders +
+    obsessive_compulsive_disorders +
+    psychotic_disorders +
+    mhd.mania_hypomania_bipolar_or_manicdepression +
+    mhd.posttraumatic_stress_disorder_ptsd +
+    autism_spectrum_disorder +
+    mhd.attention_deficit_hyperactivity_disorder +
+    mhd.personality_disorder +
+    Gender_collapsed + age_category + Ethnicity_collapsed + time_diff_sign_up_coping,
+  data = dat.prepan)
+
+summary(phq_prepan_model1b)
+tidy(phq_prepan_model1b)
+```
+
+### PCL
+Model 0a: Disorder_hierarchical, Unadjusted
+```{r PCL prepan Model absolute values 0a}
+pcl_prepan_model0a <- lm(
+  formula = pcl.sum_score_base ~ pcl.sum_score_prepan + 
+    Disorder_hierarchical,
+  data = dat.prepan)
+
+summary(pcl_prepan_model0a)
+tidy(pcl_prepan_model0a)
+```
+
+Model 0b: Overlapping disorders, Unadjusted
+```{r PCL prepan Model absolute values 0b}
+pcl_prepan_model0b <- lm(
+  formula = pcl.sum_score_base ~ pcl.sum_score_prepan +
+    anxiety_disorders +
+    depressive_disorders +
+    depression_and_anxiety +
+    eating_disorders +
+    obsessive_compulsive_disorders +
+    psychotic_disorders +
+    mhd.mania_hypomania_bipolar_or_manicdepression +
+    mhd.posttraumatic_stress_disorder_ptsd +
+    autism_spectrum_disorder +
+    mhd.attention_deficit_hyperactivity_disorder +
+    mhd.personality_disorder,
+  data = dat.prepan)
+
+summary(pcl_prepan_model0b)
+tidy(pcl_prepan_model0b)
+```
+
+Model 1a: Disorder hierarchical, Adjusted
+  Model 0a + Sex + Age + Ethnicity_collapsed + Time registration and baseline
+```{r PCL prepan Model absolute values 1a}
+pcl_prepan_model1a <- lm(
+  formula = pcl.sum_score_base ~ pcl.sum_score_prepan + 
+    Disorder_hierarchical + 
+    Gender_collapsed + 
+    age_category + 
+    Ethnicity_collapsed + 
+    time_diff_sign_up_coping,
+  data = dat.prepan)
+
+summary(pcl_prepan_model1a)
+tidy(pcl_prepan_model1a)
+```
+
+Model 1b: Overlapping disorders, Adjusted
+  Model 0b + Sex + Age + Ethnicity_collapsed + Time registration and baseline
+```{r PCL prepan Model absolute values 1b}
+pcl_prepan_model1b <- lm(
+  formula = pcl.sum_score_base ~ pcl.sum_score_prepan +
+    anxiety_disorders +
+    depressive_disorders +
+    depression_and_anxiety +
+    eating_disorders +
+    obsessive_compulsive_disorders +
+    psychotic_disorders +
+    mhd.mania_hypomania_bipolar_or_manicdepression +
+    mhd.posttraumatic_stress_disorder_ptsd +
+    autism_spectrum_disorder +
+    mhd.attention_deficit_hyperactivity_disorder +
+    mhd.personality_disorder +
+    Gender_collapsed + age_category + Ethnicity_collapsed + time_diff_sign_up_coping,
+  data = dat.prepan)
+
+summary(pcl_prepan_model1b)
+tidy(pcl_prepan_model1b)
+```
+
+### OCIR
+Model 0a: Disorder_hierarchical, Unadjusted
+```{r OCIR prepan Model absolute values 0a}
+ocir_prepan_model0a <- lm(
+  formula = ocir.sum_score_base ~ ocir.sum_score_prepan + 
+    Disorder_hierarchical,
+  data = dat.prepan)
+
+summary(ocir_prepan_model0a)
+tidy(ocir_prepan_model0a)
+```
+
+Model 0b: Overlapping disorders, Unadjusted
+```{r OCIR prepan Model absolute values 0b}
+ocir_prepan_model0b <- lm(
+  formula = ocir.sum_score_base ~ ocir.sum_score_prepan +
+    anxiety_disorders +
+    depressive_disorders +
+    depression_and_anxiety +
+    eating_disorders +
+    obsessive_compulsive_disorders +
+    psychotic_disorders +
+    mhd.mania_hypomania_bipolar_or_manicdepression +
+    mhd.posttraumatic_stress_disorder_ptsd +
+    autism_spectrum_disorder +
+    mhd.attention_deficit_hyperactivity_disorder +
+    mhd.personality_disorder,
+  data = dat.prepan)
+
+summary(ocir_prepan_model0b)
+tidy(ocir_prepan_model0b)
+```
+
+Model 1a: Disorder hierarchical, Adjusted
+  Model 0a + Sex + Age + Ethnicity_collapsed + Time registration and baseline
+```{r OCIR prepan Model absolute values 1a}
+ocir_prepan_model1a <- lm(
+  formula = ocir.sum_score_base ~ ocir.sum_score_prepan + 
+    Disorder_hierarchical + 
+    Gender_collapsed + 
+    age_category + 
+    Ethnicity_collapsed + 
+    time_diff_sign_up_coping,
+  data = dat.prepan)
+
+summary(ocir_prepan_model1a)
+tidy(ocir_prepan_model1a)
+```
+
+Model 1b: Overlapping disorders, Adjusted
+  Model 0b + Sex + Age + Ethnicity_collapsed + Time registration and baseline
+```{r OCIR prepan Model absolute values 1b}
+ocir_prepan_model1b <- lm(
+  formula = ocir.sum_score_base ~ ocir.sum_score_prepan +
+    anxiety_disorders +
+    depressive_disorders +
+    depression_and_anxiety +
+    eating_disorders +
+    obsessive_compulsive_disorders +
+    psychotic_disorders +
+    mhd.mania_hypomania_bipolar_or_manicdepression +
+    mhd.posttraumatic_stress_disorder_ptsd +
+    autism_spectrum_disorder +
+    mhd.attention_deficit_hyperactivity_disorder +
+    mhd.personality_disorder +
+    Gender_collapsed + age_category + Ethnicity_collapsed + time_diff_sign_up_coping,
+  data = dat.prepan)
+
+summary(ocir_prepan_model1b)
+tidy(ocir_prepan_model1b)
+```
+
 ## Retro-baseline change
+
+### CHANGE SCORES
 
@@
 
+### PANDEMIC BASELINE CONTROLLING FOR RETROSPECTIVE
+
+### GAD
+Model 0a: Disorder_hierarchical, Unadjusted
+```{r GAD retro Model absolute values 0a}
+gad_retro_model0a <- lm(
+  formula = gad.sum_score_base ~ gad.sum_score_retro + 
+    Disorder_hierarchical,
+  data = dat.retro)
+
+summary(gad_retro_model0a)
+tidy(gad_retro_model0a)
+```
+
+Model 0b: Overlapping disorders, Unadjusted
+```{r GAD retro Model absolute values 0b}
+gad_retro_model0b <- lm(
+  formula = gad.sum_score_base ~ gad.sum_score_retro +
+    anxiety_disorders +
+    depressive_disorders +
+    depression_and_anxiety +
+    eating_disorders +
+    obsessive_compulsive_disorders +
+    psychotic_disorders +
+    mhd.mania_hypomania_bipolar_or_manicdepression +
+    mhd.posttraumatic_stress_disorder_ptsd +
+    autism_spectrum_disorder +
+    mhd.attention_deficit_hyperactivity_disorder +
+    mhd.personality_disorder,
+  data = dat.retro)
+
+summary(gad_retro_model0b)
+tidy(gad_retro_model0b)
+```
+
+Model 1a: Disorder hierarchical, Adjusted
+  Model 0a + Sex + Age + Ethnicity_collapsed + Time registration and baseline
+```{r GAD retro Model absolute values 1a}
+gad_retro_model1a <- lm(
+  formula = gad.sum_score_base ~ gad.sum_score_retro + 
+    Disorder_hierarchical + 
+    Gender_collapsed + 
+    age_category + 
+    Ethnicity_collapsed + 
+    time_diff_sign_up_coping,
+  data = dat.retro)
+
+summary(gad_retro_model1a)
+tidy(gad_retro_model1a)
+```
+
+Model 1b: Overlapping disorders, Adjusted
+  Model 0b + Sex + Age + Ethnicity_collapsed + Time registration and baseline
+```{r GAD retro Model absolute values 1b}
+gad_retro_model1b <- lm(
+  formula = gad.sum_score_base ~ gad.sum_score_retro +
+    anxiety_disorders +
+    depressive_disorders +
+    depression_and_anxiety +
+    eating_disorders +
+    obsessive_compulsive_disorders +
+    psychotic_disorders +
+    mhd.mania_hypomania_bipolar_or_manicdepression +
+    mhd.posttraumatic_stress_disorder_ptsd +
+    autism_spectrum_disorder +
+    mhd.attention_deficit_hyperactivity_disorder +
+    mhd.personality_disorder +
+    Gender_collapsed + age_category + Ethnicity_collapsed + time_diff_sign_up_coping,
+  data = dat.retro)
+
+summary(gad_retro_model1b)
+tidy(gad_retro_model1b)
+```
+
+### PHQ
+Model 0a: Disorder_hierarchical, Unadjusted
+```{r PHQ retro Model absolute values 0a}
+phq_retro_model0a <- lm(
+  formula = phq.sum_score_base ~ phq.sum_score_retro + 
+    Disorder_hierarchical,
+  data = dat.retro)
+
+summary(phq_retro_model0a)
+tidy(phq_retro_model0a)
+```
+
+Model 0b: Overlapping disorders, Unadjusted
+```{r PHQ retro Model absolute values 0b}
+phq_retro_model0b <- lm(
+  formula = phq.sum_score_base ~ phq.sum_score_retro +
+    anxiety_disorders +
+    depressive_disorders +
+    depression_and_anxiety +
+    eating_disorders +
+    obsessive_compulsive_disorders +
+    psychotic_disorders +
+    mhd.mania_hypomania_bipolar_or_manicdepression +
+    mhd.posttraumatic_stress_disorder_ptsd +
+    autism_spectrum_disorder +
+    mhd.attention_deficit_hyperactivity_disorder +
+    mhd.personality_disorder,
+  data = dat.retro)
+
+summary(phq_retro_model0b)
+tidy(phq_retro_model0b)
+```
+
+Model 1a: Disorder hierarchical, Adjusted
+  Model 0a + Sex + Age + Ethnicity_collapsed + Time registration and baseline
+```{r PHQ retro Model absolute values 1a}
+phq_retro_model1a <- lm(
+  formula = phq.sum_score_base ~ phq.sum_score_retro + 
+    Disorder_hierarchical + 
+    Gender_collapsed + 
+    age_category + 
+    Ethnicity_collapsed + 
+    time_diff_sign_up_coping,
+  data = dat.retro)
+
+summary(phq_retro_model1a)
+tidy(phq_retro_model1a)
+```
+
+Model 1b: Overlapping disorders, Adjusted
+  Model 0b + Sex + Age + Ethnicity_collapsed + Time registration and baseline
+```{r PHQ retro Model absolute values 1b}
+phq_retro_model1b <- lm(
+  formula = phq.sum_score_base ~ phq.sum_score_retro +
+    anxiety_disorders +
+    depressive_disorders +
+    depression_and_anxiety +
+    eating_disorders +
+    obsessive_compulsive_disorders +
+    psychotic_disorders +
+    mhd.mania_hypomania_bipolar_or_manicdepression +
+    mhd.posttraumatic_stress_disorder_ptsd +
+    autism_spectrum_disorder +
+    mhd.attention_deficit_hyperactivity_disorder +
+    mhd.personality_disorder +
+    Gender_collapsed + age_category + Ethnicity_collapsed + time_diff_sign_up_coping,
+  data = dat.retro)
+
+summary(phq_retro_model1b)
+tidy(phq_retro_model1b)
+```
+
+### PCL
+Model 0a: Disorder_hierarchical, Unadjusted
+```{r PCL retro Model absolute values 0a}
+pcl_retro_model0a <- lm(
+  formula = pcl.sum_score_base ~ pcl.sum_score_retro + 
+    Disorder_hierarchical,
+  data = dat.retro)
+
+summary(pcl_retro_model0a)
+tidy(pcl_retro_model0a)
+```
+
+Model 0b: Overlapping disorders, Unadjusted
+```{r PCL retro Model absolute values 0b}
+pcl_retro_model0b <- lm(
+  formula = pcl.sum_score_base ~ pcl.sum_score_retro +
+    anxiety_disorders +
+    depressive_disorders +
+    depression_and_anxiety +
+    eating_disorders +
+    obsessive_compulsive_disorders +
+    psychotic_disorders +
+    mhd.mania_hypomania_bipolar_or_manicdepression +
+    mhd.posttraumatic_stress_disorder_ptsd +
+    autism_spectrum_disorder +
+    mhd.attention_deficit_hyperactivity_disorder +
+    mhd.personality_disorder,
+  data = dat.retro)
+
+summary(pcl_retro_model0b)
+tidy(pcl_retro_model0b)
+```
+
+Model 1a: Disorder hierarchical, Adjusted
+  Model 0a + Sex + Age + Ethnicity_collapsed + Time registration and baseline
+```{r PCL retro Model absolute values 1a}
+pcl_retro_model1a <- lm(
+  formula = pcl.sum_score_base ~ pcl.sum_score_retro + 
+    Disorder_hierarchical + 
+    Gender_collapsed + 
+    age_category + 
+    Ethnicity_collapsed + 
+    time_diff_sign_up_coping,
+  data = dat.retro)
+
+summary(pcl_retro_model1a)
+tidy(pcl_retro_model1a)
+```
+
+Model 1b: Overlapping disorders, Adjusted
+  Model 0b + Sex + Age + Ethnicity_collapsed + Time registration and baseline
+```{r PCL retro Model absolute values 1b}
+pcl_retro_model1b <- lm(
+  formula = pcl.sum_score_base ~ pcl.sum_score_retro +
+    anxiety_disorders +
+    depressive_disorders +
+    depression_and_anxiety +
+    eating_disorders +
+    obsessive_compulsive_disorders +
+    psychotic_disorders +
+    mhd.mania_hypomania_bipolar_or_manicdepression +
+    mhd.posttraumatic_stress_disorder_ptsd +
+    autism_spectrum_disorder +
+    mhd.attention_deficit_hyperactivity_disorder +
+    mhd.personality_disorder +
+    Gender_collapsed + age_category + Ethnicity_collapsed + time_diff_sign_up_coping,
+  data = dat.retro)
+
+summary(pcl_retro_model1b)
+tidy(pcl_retro_model1b)
+```
+
+### OCIR
+Model 0a: Disorder_hierarchical, Unadjusted
+```{r OCIR retro Model absolute values 0a}
+ocir_retro_model0a <- lm(
+  formula = ocir.sum_score_base ~ ocir.sum_score_retro + 
+    Disorder_hierarchical,
+  data = dat.retro)
+
+summary(ocir_retro_model0a)
+tidy(ocir_retro_model0a)
+```
+
+Model 0b: Overlapping disorders, Unadjusted
+```{r OCIR retro Model absolute values 0b}
+ocir_retro_model0b <- lm(
+  formula = ocir.sum_score_base ~ ocir.sum_score_retro +
+    anxiety_disorders +
+    depressive_disorders +
+    depression_and_anxiety +
+    eating_disorders +
+    obsessive_compulsive_disorders +
+    psychotic_disorders +
+    mhd.mania_hypomania_bipolar_or_manicdepression +
+    mhd.posttraumatic_stress_disorder_ptsd +
+    autism_spectrum_disorder +
+    mhd.attention_deficit_hyperactivity_disorder +
+    mhd.personality_disorder,
+  data = dat.retro)
+
+summary(ocir_retro_model0b)
+tidy(ocir_retro_model0b)
+```
+
+Model 1a: Disorder hierarchical, Adjusted
+  Model 0a + Sex + Age + Ethnicity_collapsed + Time registration and baseline
+```{r OCIR retro Model absolute values 1a}
+ocir_retro_model1a <- lm(
+  formula = ocir.sum_score_base ~ ocir.sum_score_retro + 
+    Disorder_hierarchical + 
+    Gender_collapsed + 
+    age_category + 
+    Ethnicity_collapsed + 
+    time_diff_sign_up_coping,
+  data = dat.retro)
+
+summary(ocir_retro_model1a)
+tidy(ocir_retro_model1a)
+```
+
+Model 1b: Overlapping disorders, Adjusted
+  Model 0b + Sex + Age + Ethnicity_collapsed + Time registration and baseline
+```{r OCIR retro Model absolute values 1b}
+ocir_retro_model1b <- lm(
+  formula = ocir.sum_score_base ~ ocir.sum_score_retro +
+    anxiety_disorders +
+    depressive_disorders +
+    depression_and_anxiety +
+    eating_disorders +
+    obsessive_compulsive_disorders +
+    psychotic_disorders +
+    mhd.mania_hypomania_bipolar_or_manicdepression +
+    mhd.posttraumatic_stress_disorder_ptsd +
+    autism_spectrum_disorder +
+    mhd.attention_deficit_hyperactivity_disorder +
+    mhd.personality_disorder +
+    Gender_collapsed + age_category + Ethnicity_collapsed + time_diff_sign_up_coping,
+  data = dat.retro)
+
+summary(ocir_retro_model1b)
+tidy(ocir_retro_model1b)
+```
+
 # RUBBISH

### 2020-09-17 PANCHANGE_analysis.Rmd
adding tidy and glance models summaries

@@
 
-# Questionnaire comparions
+#ANALYSIS PLAN
+1. Calculate mean change per disorder group 
+    i. Disorders (9)
+      a. Rank the disorders by the size of the change
+    ii. Sex
+    iii. Age (13; RAMP; potentially collapse above 65 depending on group sizes) 
+    iv. Ethnicity groups (5; White European, Black (British), Asian, Arab, Mixed)
+
+# 1. Questionnaire comparions: Calculate mean change per group
 
@@
     values = COPINGpalette3,
-    labels = c("Baseline", "Prepandemic", "Retrospective")
+ #   labels = c("Baseline", "Prepandemic", "Retrospective")
     )
@@
 Retro-baseline analyses
+++CH: need to discuss exclusion criteria
 Exclude individuals with NA for MHD, age, gender
+
+```{r Exclusion criteria}
+
+```
+
 ```{r exclusion criteria for retro-baseline analysis}
@@
 
-#ANALYSIS PLAN
-1. Calculate mean change per disorder group 
-    i. Disorders (9)
-      a. Rank the disorders by the size of the change
-    ii. Sex 
-    iii. Age (13; RAMP; potentially collapse above 65 depending on group sizes) 
-    iv. Ethnicity groups (5; White European, Black (British), Asian, Arab, Mixed)
-
 2. Regression models (Regress covariates out of the change? Which?)
@@
 
-# 1. Calculate mean change per group
-
 # 2. Regression
@@
 ```{r GAD prepan Model 0a}
+# Model
 gad_prepan_model0a <- lm(
@@
 summary(gad_prepan_model0a)
-tidy(gad_prepan_model0a)
+
+# Regression statistics
+gad_prepan_model0a_reg_stats <- glance(gad_prepan_model0a) %>%
+  mutate(
+    "n" = format(
+      round(nobs,
+            digits = 0),
+      nsmall = 0),
+    "R2" = format(
+      round(r.squared,
+            digits = 2),
+      nsmall = 2),
+    "adjust. R2" = format(
+      round(adj.r.squared,
+            digits = 2),
+      nsmall = 2),
+    "F" = format(
+      round(statistic,
+            digits = 2),
+      nsmall = 2),
+    "p value" = case_when(
+      p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
+      p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
+      p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
+  )
+  ) %>%
+  select(
+    "n",
+    "R2",
+    "adjust. R2",
+    "F",
+    "p value",
+    "df"
+  )
+
+kable(gad_prepan_model0a_reg_stats)
+gad_prepan_model0a_reg_stats
+
+# Estimate summary table
+gad_prepan_model0a_estimates <- tidy(gad_prepan_model0a) %>%
+  mutate(
+    "Indepent variable" = recode_factor(
+      term,
+      "(Intercept)" = "Intercept",
+      "Disorder_hierarchicalAnxiety disorders" = "Anxiety disorders",
+      "Disorder_hierarchicalEating disorders" = "Eating disorders",
+      "Disorder_hierarchicalOCDs" = "OCDs",
+      "Disorder_hierarchicalPTSD" = "PTSD",
+      "Disorder_hierarchicalDepressive disorders" = "Depressive disorders",
+      "Disorder_hierarchicalBipolar disorders" = "Bipolar disorders"
+    ),
+    "Estimate" = format(
+      round(estimate,
+            digits = 2),
+      nsmall = 2),
+    "SE" = format(
+      round(std.error,
+            digits = 2),
+      nsmall = 2),
+    "z score" = format(
+      round(statistic,
+            digits = 2),
+      nsmall = 2),
+    "p value" = case_when(
+      p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
+      p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
+      p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
+  )
+  ) %>%
+  select(
+    "Indepent variable",
+    "Estimate",
+    "SE",
+#    "z score",
+    "p value"
+  )
+
+kable(gad_prepan_model0a_estimates)
+gad_prepan_model0a_estimates
 ```
@@
 summary(gad_prepan_model0b)
-tidy(gad_prepan_model0b)
+
+# Regression statistics
+gad_prepan_model0b_reg_stats <- glance(gad_prepan_model0b) %>%
+  mutate(
+    "n" = format(
+      round(nobs,
+            digits = 0),
+      nsmall = 0),
+    "R2" = format(
+      round(r.squared,
+            digits = 2),
+      nsmall = 2),
+    "adjust. R2" = format(
+      round(adj.r.squared,
+            digits = 2),
+      nsmall = 2),
+    "F" = format(
+      round(statistic,
+            digits = 2),
+      nsmall = 2),
+    "p value" = case_when(
+      p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
+      p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
+      p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
+  )
+  ) %>%
+  select(
+    "n",
+    "R2",
+    "adjust. R2",
+    "F",
+    "p value",
+    "df"
+  )
+
+kable(gad_prepan_model0b_reg_stats)
+gad_prepan_model0b_reg_stats
+
+# Estimate summary table
+gad_prepan_model0b_estimates <- tidy(gad_prepan_model0b) %>%
+  mutate(
+    "Indepent variable" = recode_factor(
+      term,
+      "(Intercept)" = "Intercept",
+      "anxiety_disordersAnxiety disorder" = "Anxiety disorders",
+      "depressive_disordersDepressive disorder" = "Depressive disorders",
+      "depression_and_anxietyDepressive and anxiety disorder" = "Depressive and anxiety disorder",
+      "depression_and_anxietyOnly depressive disorder" = "Only depressive disorder",
+      "depression_and_anxietyOnly anxiety disorder" = "Only anxiety disorder",
+      "eating_disordersEating disorder" = "Eating disorders",
+      "obsessive_compulsive_disordersObsessive compulsive disorder" = "OCDs",
+      "psychotic_disordersPsychotic disorder" = "Psychotic disorder",
+      "mhd.mania_hypomania_bipolar_or_manicdepressionMania, hypomania, bipolar or manic-depression" = "Bipolar disorder",
+      "mhd.posttraumatic_stress_disorder_ptsdPost-traumatic stress disorder (PTSD)" = "PTSD",
+      "autism_spectrum_disorderAutism spectrum disorder" = "ASD",
+      "mhd.attention_deficit_hyperactivity_disorderAttention deficit or attention deficit and hyperactivity disorder (ADD/ADHD)" = "ADHD",
+      "mhd.personality_disorderPersonality disorder" = "Personality disorder"
+    ),
+    "Estimate" = format(
+      round(estimate,
+            digits = 2),
+      nsmall = 2),
+    "SE" = format(
+      round(std.error,
+            digits = 2),
+      nsmall = 2),
+    "z score" = format(
+      round(statistic,
+            digits = 2),
+      nsmall = 2),
+    "p value" = case_when(
+      p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
+      p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
+      p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
+  )
+  ) %>%
+  select(
+    "Indepent variable",
+    "Estimate",
+    "SE",
+#    "z score",
+    "p value"
+  )
+
+kable(gad_prepan_model0b_estimates)
+gad_prepan_model0b_estimates
 ```
@@
     Gender_collapsed + 
-    age_category + 
+    age_category_collapsed + 
     Ethnicity_collapsed + 
@@
 summary(gad_prepan_model1a)
-tidy(gad_prepan_model1a)
+
+# Regression statistics
+gad_prepan_model1a_reg_stats <- glance(gad_prepan_model1a) %>%
+  mutate(
+    "n" = format(
+      round(nobs,
+            digits = 0),
+      nsmall = 0),
+    "R2" = format(
+      round(r.squared,
+            digits = 2),
+      nsmall = 2),
+    "adjust. R2" = format(
+      round(adj.r.squared,
+            digits = 2),
+      nsmall = 2),
+    "F" = format(
+      round(statistic,
+            digits = 2),
+      nsmall = 2),
+    "p value" = case_when(
+      p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
+      p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
+      p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
+    )
+  ) %>%
+  select(
+    "n",
+    "R2",
+    "adjust. R2",
+    "F",
+    "p value",
+    "df"
+  )
+
+kable(gad_prepan_model1a_reg_stats)
+gad_prepan_model1a_reg_stats
+
+# Estimate summary table
+gad_prepan_model1a_estimates <- tidy(gad_prepan_model1a) %>%
+  mutate(
+    "Indepent variable" = recode_factor(
+      term,
+      "(Intercept)" = "Intercept",
+      "Disorder_hierarchicalAnxiety disorders" = "Anxiety disorders",
+      "Disorder_hierarchicalEating disorders" = "Eating disorders",
+      "Disorder_hierarchicalOCDs" = "OCDs",
+      "Disorder_hierarchicalPTSD" = "PTSD",
+      "Disorder_hierarchicalDepressive disorders" = "Depressive disorders",
+      "Disorder_hierarchicalBipolar disorders" = "Bipolar disorders",
+      "Gender_collapsedFemale" = "Female",
+      "Gender_collapsedNon-binary/Self-defined" = "Non-binary/Self-defined",
+      "age_category_collapsed19-25" = "19-25 years",
+      "age_category_collapsed26-35" = "26-35 years",
+      "age_category_collapsed36-45" = "36-45 years",
+      "age_category_collapsed46-55" = "46-55 years",
+      "age_category_collapsed56-65" = "56-65 years",
+      "age_category_collapsed66-70" = "66-70 years",
+      "age_category_collapsed71-75" = "71-75 years",
+      "age_category_collapsed76+" = "76+ years",
+      "Ethnicity_collapsedMixed or multiple ethnic origins" = "Mixed or multiple ethnic origins",
+      "Ethnicity_collapsedAsian or Asian British" = "Asian or Asian British",
+      "Ethnicity_collapsedAfrican or African British" = "African or African British",
+      "Ethnicity_collapsedOther" = "Other ethnicity",
+      "time_diff_sign_up_coping" = "Time difference: prepandemic to COPING"
+    ),
+    "Estimate" = format(
+      round(estimate,
+            digits = 2),
+      nsmall = 2),
+    "SE" = format(
+      round(std.error,
+            digits = 2),
+      nsmall = 2),
+    "z score" = format(
+      round(statistic,
+            digits = 2),
+      nsmall = 2),
+    "p value" = case_when(
+      p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
+      p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
+      p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
+    )
+  ) %>%
+  select(
+    "Indepent variable",
+    "Estimate",
+    "SE",
+    #    "z score",
+    "p value"
+  )
+
+kable(gad_prepan_model1a_estimates)
+gad_prepan_model1a_estimates
 ```
@@
     mhd.personality_disorder +
-    Gender_collapsed + age_category + Ethnicity_collapsed + time_diff_sign_up_coping,
+    Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + time_diff_sign_up_coping,
   data = dat.prepan)
@@
     mhd.personality_disorder +
-    Gender_collapsed + age_category + Ethnicity_collapsed + time_diff_sign_up_coping,
+    Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + time_diff_sign_up_coping,
   data = dat.retro)

### 2020-09-17 PANCHANGE_analysis.Rmd
added functions for regression models with diff/change scores

@@
 
-### CHANGE SCORES
-
-### GAD
-Model 0a: Disorder_hierarchical, Unadjusted
-```{r GAD prepan Model 0a}
-# Model
-gad_prepan_model0a <- lm(
-  formula = gad.diff_score_base_prepan ~ 
-    Disorder_hierarchical,
-  data = dat.prepan)
-
-summary(gad_prepan_model0a)
-
-# Regression statistics
-gad_prepan_model0a_reg_stats <- glance(gad_prepan_model0a) %>%
-  mutate(
-    "n" = format(
-      round(nobs,
-            digits = 0),
-      nsmall = 0),
-    "R2" = format(
-      round(r.squared,
-            digits = 2),
-      nsmall = 2),
-    "adjust. R2" = format(
-      round(adj.r.squared,
-            digits = 2),
-      nsmall = 2),
-    "F" = format(
-      round(statistic,
-            digits = 2),
-      nsmall = 2),
-    "p value" = case_when(
-      p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
-      p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
-      p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
-  )
-  ) %>%
-  select(
-    "n",
-    "R2",
-    "adjust. R2",
-    "F",
-    "p value",
-    "df"
-  )
-
-kable(gad_prepan_model0a_reg_stats)
-gad_prepan_model0a_reg_stats
-
-# Estimate summary table
-gad_prepan_model0a_estimates <- tidy(gad_prepan_model0a) %>%
+```{r model0a function}
+model0a.estimates <- function(outcome, data_set) {
+  # define the variable name of the dependent variable
+  dependent.variable <- outcome
+  # define the independent variables
+  independent.variables <- c("Disorder_hierarchical")
+  # create the formula
+  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
+  glm.formula
+
+  # run the glm
+  assign(paste0(outcome,".model0a"),
+         lm( formula = glm.formula,
+              data = get(data_set)
+              )
+  )
+
+  assign(paste0(outcome,"model0a_estimates"),
+         tidy(get(paste0(outcome,".model0a")), conf.int = TRUE) %>%
            mutate(
@@
       nsmall = 2),
+    "95% CI low" = format(
+      round(conf.low,
+            digits = 2),
+      nsmall = 2),
+    "95% CI up" = format(
+      round(conf.high,
+            digits = 2),
+      nsmall = 2),
     "SE" = format(
@@
     "Estimate",
+    "95% CI low",
+    "95% CI up",
+    "SE",
+#    "z score",
+    "p value"
+  )
+  )
+
+  return(get(paste0(outcome,"model0a_estimates")))
+}
+
+model0a.reg.stats <- function(outcome, data_set) {
+  # define the variable name of the dependent variable
+  dependent.variable <- outcome
+  # define the independent variables
+  independent.variables <- c("Disorder_hierarchical")
+  # create the formula
+  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
+  glm.formula
+
+  # run the glm
+  assign(paste0(outcome,".model0a"),
+         lm( formula = glm.formula,
+              data = get(data_set)
+              )
+  )
+
+  assign(paste0(outcome,"model0a_reg_stats"),
+         glance(get(paste0(outcome,".model0a"))) %>%
+           mutate(
+             "n" = format(
+               round(nobs,
+                     digits = 0),
+               nsmall = 0),
+             "R2" = format(
+               round(r.squared,
+                     digits = 2),
+               nsmall = 2),
+             "adjust. R2" = format(
+               round(adj.r.squared,
+                     digits = 2),
+               nsmall = 2),
+             "F" = format(
+               round(statistic,
+                     digits = 2),
+               nsmall = 2),
+             "p value" = case_when(
+               p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
+               p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
+               p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
+             )
+           ) %>%
+           select(
+             "n",
+             "R2",
+             "adjust. R2",
+             "F",
+             "p value",
+             "df"
+           )
+  )
+
+  return(get(paste0(outcome,"model0a_reg_stats")))
+}
+```
+
+```{r}
+model0a.estimates(outcome = "gad.diff_score_base_prepan", data_set = "dat.prepan")
+model0a.reg.stats(outcome = "gad.diff_score_base_prepan", data_set = "dat.prepan")
+```
+
+```{r model0b function}
+model0b.estimates <- function(outcome, data_set) {
+  # define the variable name of the dependent variable
+  dependent.variable <- outcome
+  # define the independent variables
+  independent.variables <- c("anxiety_disorders",
+                             "depressive_disorders",
+                             "depression_and_anxiety",
+                             "eating_disorders",
+                             "obsessive_compulsive_disorders",
+                             "psychotic_disorders",
+                             "mhd.mania_hypomania_bipolar_or_manicdepression",
+                             "mhd.posttraumatic_stress_disorder_ptsd",
+                             "autism_spectrum_disorder",
+                             "mhd.attention_deficit_hyperactivity_disorder",
+                             "mhd.personality_disorder"
+                                )
+  # create the formula
+  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
+  glm.formula
+
+  # run the glm
+  assign(paste0(outcome,".model0b"),
+         lm( formula = glm.formula,
+             data = get(data_set)
+         )
+  )
+
+  assign(paste0(outcome,"model0b_estimates"),
+         tidy(get(paste0(outcome,".model0b")), conf.int = TRUE) %>%
+           mutate(
+             "Indepent variable" = recode_factor(
+               term,
+               "(Intercept)" = "Intercept",
+               "anxiety_disordersAnxiety disorder" = "Anxiety disorders",
+               "depressive_disordersDepressive disorder" = "Depressive disorders",
+               "depression_and_anxietyDepressive and anxiety disorder" = "Depressive and anxiety disorder",
+               "depression_and_anxietyOnly depressive disorder" = "Only depressive disorder",
+               "depression_and_anxietyOnly anxiety disorder" = "Only anxiety disorder",
+               "eating_disordersEating disorder" = "Eating disorders",
+               "obsessive_compulsive_disordersObsessive compulsive disorder" = "OCDs",
+               "psychotic_disordersPsychotic disorder" = "Psychotic disorder",
+               "mhd.mania_hypomania_bipolar_or_manicdepressionMania, hypomania, bipolar or manic-depression" = "Bipolar disorder",
+               "mhd.posttraumatic_stress_disorder_ptsdPost-traumatic stress disorder (PTSD)" = "PTSD",
+               "autism_spectrum_disorderAutism spectrum disorder" = "ASD",
+               "mhd.attention_deficit_hyperactivity_disorderAttention deficit or attention deficit and hyperactivity disorder (ADD/ADHD)" = "ADHD",
+               "mhd.personality_disorderPersonality disorder" = "Personality disorder"
+             ),
+             "Estimate" = format(
+               round(estimate,
+                     digits = 2),
+               nsmall = 2),
+             "95% CI low" = format(
+               round(conf.low,
+                     digits = 2),
+               nsmall = 2),
+             "95% CI up" = format(
+               round(conf.high,
+                     digits = 2),
+               nsmall = 2),
+             "SE" = format(
+               round(std.error,
+                     digits = 2),
+               nsmall = 2),
+             "z score" = format(
+               round(statistic,
+                     digits = 2),
+               nsmall = 2),
+             "p value" = case_when(
+               p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
+               p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
+               p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
+             )
+           ) %>%
+           select(
+             "Indepent variable",
+             "Estimate",
+             "95% CI low",
+             "95% CI up",
+             "SE",
+             #    "z score",
+             "p value"
+           )
+  )
+
+  return(get(paste0(outcome,"model0b_estimates")))
+}
+
+model0b.reg.stats <- function(outcome, data_set) {
+  # define the variable name of the dependent variable
+  dependent.variable <- outcome
+  # define the independent variables
+  independent.variables <- c("Disorder_hierarchical")
+  # create the formula
+  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
+  glm.formula
+
+  # run the glm
+  assign(paste0(outcome,".model0b"),
+         lm( formula = glm.formula,
+             data = get(data_set)
+         )
+  )
+
+  assign(paste0(outcome,"model0b_reg_stats"),
+         glance(get(paste0(outcome,".model0b"))) %>%
+           mutate(
+             "n" = format(
+               round(nobs,
+                     digits = 0),
+               nsmall = 0),
+             "R2" = format(
+               round(r.squared,
+                     digits = 2),
+               nsmall = 2),
+             "adjust. R2" = format(
+               round(adj.r.squared,
+                     digits = 2),
+               nsmall = 2),
+             "F" = format(
+               round(statistic,
+                     digits = 2),
+               nsmall = 2),
+             "p value" = case_when(
+               p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
+               p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
+               p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
+             )
+           ) %>%
+           select(
+             "n",
+             "R2",
+             "adjust. R2",
+             "F",
+             "p value",
+             "df"
+           )
+  )
+
+  return(get(paste0(outcome,"model0b_reg_stats")))
+}
+```
+
+```{r}
+model0b.estimates(outcome = "gad.diff_score_base_prepan", data_set = "dat.prepan")
+model0b.reg.stats(outcome = "gad.diff_score_base_prepan", data_set = "dat.prepan")
+```
+
+```{r model1a function}
+model1a.estimates <- function(outcome, data_set) {
+  # define the variable name of the dependent variable
+  dependent.variable <- outcome
+  # define the independent variables
+  independent.variables <- c("Disorder_hierarchical",
+                            "Gender_collapsed",
+                            "age_category_collapsed",
+                            "Ethnicity_collapsed",
+                            "time_diff_sign_up_coping"
+                            )
+  # create the formula
+  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
+  glm.formula
+
+  # run the glm
+  assign(paste0(outcome,".model1a"),
+         lm( formula = glm.formula,
+             data = get(data_set)
+         )
+  )
+
+  assign(paste0(outcome,"model1a_estimates"),
+         tidy(get(paste0(outcome,".model1a")), conf.int = TRUE) %>%
+           mutate(
+             "Indepent variable" = recode_factor(
+               term,
+               "(Intercept)" = "Intercept",
+               "Disorder_hierarchicalAnxiety disorders" = "Anxiety disorders",
+               "Disorder_hierarchicalEating disorders" = "Eating disorders",
+               "Disorder_hierarchicalOCDs" = "OCDs",
+               "Disorder_hierarchicalPTSD" = "PTSD",
+               "Disorder_hierarchicalDepressive disorders" = "Depressive disorders",
+               "Disorder_hierarchicalBipolar disorders" = "Bipolar disorders",
+               "Gender_collapsedFemale" = "Female",
+               "Gender_collapsedNon-binary/Self-defined" = "Non-binary/Self-defined",
+               "age_category_collapsed19-25" = "19-25 years",
+               "age_category_collapsed26-35" = "26-35 years",
+               "age_category_collapsed36-45" = "36-45 years",
+               "age_category_collapsed46-55" = "46-55 years",
+               "age_category_collapsed56-65" = "56-65 years",
+               "age_category_collapsed66-70" = "66-70 years",
+               "age_category_collapsed71-75" = "71-75 years",
+               "age_category_collapsed76+" = "76+ years",
+               "Ethnicity_collapsedMixed or multiple ethnic origins" = "Mixed or multiple ethnic origins",
+               "Ethnicity_collapsedAsian or Asian British" = "Asian or Asian British",
+               "Ethnicity_collapsedAfrican or African British" = "African or African British",
+               "Ethnicity_collapsedOther" = "Other ethnicity",
+               "time_diff_sign_up_coping" = "Time difference: prepandemic to COPING"
+             ),
+             "Estimate" = format(
+               round(estimate,
+                     digits = 2),
+               nsmall = 2),
+             "95% CI low" = format(
+               round(conf.low,
+                     digits = 2),
+               nsmall = 2),
+             "95% CI up" = format(
+               round(conf.high,
+                     digits = 2),
+               nsmall = 2),
+             "SE" = format(
+               round(std.error,
+                     digits = 2),
+               nsmall = 2),
+             "z score" = format(
+               round(statistic,
+                     digits = 2),
+               nsmall = 2),
+             "p value" = case_when(
+               p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
+               p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
+               p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
+             )
+           ) %>%
+           select(
+             "Indepent variable",
+             "Estimate",
+             "95% CI low",
+             "95% CI up",
+             "SE",
+             #    "z score",
+             "p value"
+           )
+  )
+
+  return(get(paste0(outcome,"model1a_estimates")))
+}
+
+model1a.reg.stats <- function(outcome, data_set) {
+  # define the variable name of the dependent variable
+  dependent.variable <- outcome
+  # define the independent variables
+  independent.variables <- c("Disorder_hierarchical")
+  # create the formula
+  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
+  glm.formula
+
+  # run the glm
+  assign(paste0(outcome,".model1a"),
+         lm( formula = glm.formula,
+             data = get(data_set)
+         )
+  )
+
+  assign(paste0(outcome,"model1a_reg_stats"),
+         glance(get(paste0(outcome,".model1a"))) %>%
+           mutate(
+             "n" = format(
+               round(nobs,
+                     digits = 0),
+               nsmall = 0),
+             "R2" = format(
+               round(r.squared,
+                     digits = 2),
+               nsmall = 2),
+             "adjust. R2" = format(
+               round(adj.r.squared,
+                     digits = 2),
+               nsmall = 2),
+             "F" = format(
+               round(statistic,
+                     digits = 2),
+               nsmall = 2),
+             "p value" = case_when(
+               p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
+               p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
+               p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
+             )
+           ) %>%
+           select(
+             "n",
+             "R2",
+             "adjust. R2",
+             "F",
+             "p value",
+             "df"
+           )
+  )
+
+  return(get(paste0(outcome,"model1a_reg_stats")))
+}
+```
+
+```{r}
+model1a.estimates(outcome = "gad.diff_score_base_prepan", data_set = "dat.prepan")
+model1a.reg.stats(outcome = "gad.diff_score_base_prepan", data_set = "dat.prepan")
+```
+
+```{r model1b function}
+model1b.estimates <- function(outcome, data_set) {
+  # define the variable name of the dependent variable
+  dependent.variable <- outcome
+  # define the independent variables
+  independent.variables <- c("anxiety_disorders",
+                             "depressive_disorders",
+                             "depression_and_anxiety",
+                             "eating_disorders",
+                             "obsessive_compulsive_disorders",
+                             "psychotic_disorders",
+                             "mhd.mania_hypomania_bipolar_or_manicdepression",
+                             "mhd.posttraumatic_stress_disorder_ptsd",
+                             "autism_spectrum_disorder",
+                             "mhd.attention_deficit_hyperactivity_disorder",
+                             "mhd.personality_disorder",
+                             "Gender_collapsed",
+                             "age_category_collapsed",
+                             "Ethnicity_collapsed",
+                             "time_diff_sign_up_coping"
+                                )
+  # create the formula
+  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
+  glm.formula
+
+  # run the glm
+  assign(paste0(outcome,".model1b"),
+         lm( formula = glm.formula,
+             data = get(data_set)
+         )
+  )
+
+  assign(paste0(outcome,"model1b_estimates"),
+         tidy(get(paste0(outcome,".model1b")), conf.int = TRUE) %>%
+           mutate(
+             "Indepent variable" = recode_factor(
+               term,
+               "(Intercept)" = "Intercept",
+               "anxiety_disordersAnxiety disorder" = "Anxiety disorders",
+               "depressive_disordersDepressive disorder" = "Depressive disorders",
+               "depression_and_anxietyDepressive and anxiety disorder" = "Depressive and anxiety disorder",
+               "depression_and_anxietyOnly depressive disorder" = "Only depressive disorder",
+               "depression_and_anxietyOnly anxiety disorder" = "Only anxiety disorder",
+               "eating_disordersEating disorder" = "Eating disorders",
+               "obsessive_compulsive_disordersObsessive compulsive disorder" = "OCDs",
+               "psychotic_disordersPsychotic disorder" = "Psychotic disorder",
+               "mhd.mania_hypomania_bipolar_or_manicdepressionMania, hypomania, bipolar or manic-depression" = "Bipolar disorder",
+               "mhd.posttraumatic_stress_disorder_ptsdPost-traumatic stress disorder (PTSD)" = "PTSD",
+               "autism_spectrum_disorderAutism spectrum disorder" = "ASD",
+               "mhd.attention_deficit_hyperactivity_disorderAttention deficit or attention deficit and hyperactivity disorder (ADD/ADHD)" = "ADHD",
+               "mhd.personality_disorderPersonality disorder" = "Personality disorder",
+               "Gender_collapsedFemale" = "Female",
+               "Gender_collapsedNon-binary/Self-defined" = "Non-binary/Self-defined",
+               "age_category_collapsed19-25" = "19-25 years",
+               "age_category_collapsed26-35" = "26-35 years",
+               "age_category_collapsed36-45" = "36-45 years",
+               "age_category_collapsed46-55" = "46-55 years",
+               "age_category_collapsed56-65" = "56-65 years",
+               "age_category_collapsed66-70" = "66-70 years",
+               "age_category_collapsed71-75" = "71-75 years",
+               "age_category_collapsed76+" = "76+ years",
+               "Ethnicity_collapsedMixed or multiple ethnic origins" = "Mixed or multiple ethnic origins",
+               "Ethnicity_collapsedAsian or Asian British" = "Asian or Asian British",
+               "Ethnicity_collapsedAfrican or African British" = "African or African British",
+               "Ethnicity_collapsedOther" = "Other ethnicity",
+               "time_diff_sign_up_coping" = "Time difference: prepandemic to COPING"
+             ),
+             "Estimate" = format(
+               round(estimate,
+                     digits = 2),
+               nsmall = 2),
+             "95% CI low" = format(
+               round(conf.low,
+                     digits = 2),
+               nsmall = 2),
+             "95% CI up" = format(
+               round(conf.high,
+                     digits = 2),
+               nsmall = 2),
+             "SE" = format(
+               round(std.error,
+                     digits = 2),
+               nsmall = 2),
+             "z score" = format(
+               round(statistic,
+                     digits = 2),
+               nsmall = 2),
+             "p value" = case_when(
+               p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
+               p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
+               p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
+             )
+           ) %>%
+           select(
+             "Indepent variable",
+             "Estimate",
+             "95% CI low",
+             "95% CI up",
+             "SE",
+             #    "z score",
+             "p value"
+           )
+  )
+
+  return(get(paste0(outcome,"model1b_estimates")))
+}
+
+model1b.reg.stats <- function(outcome, data_set) {
+  # define the variable name of the dependent variable
+  dependent.variable <- outcome
+  # define the independent variables
+  independent.variables <- c("Disorder_hierarchical")
+  # create the formula
+  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
+  glm.formula
+
+  # run the glm
+  assign(paste0(outcome,".model1b"),
+         lm( formula = glm.formula,
+             data = get(data_set)
+         )
+  )
+
+  assign(paste0(outcome,"model1b_reg_stats"),
+         glance(get(paste0(outcome,".model1b"))) %>%
+           mutate(
+             "n" = format(
+               round(nobs,
+                     digits = 0),
+               nsmall = 0),
+             "R2" = format(
+               round(r.squared,
+                     digits = 2),
+               nsmall = 2),
+             "adjust. R2" = format(
+               round(adj.r.squared,
+                     digits = 2),
+               nsmall = 2),
+             "F" = format(
+               round(statistic,
+                     digits = 2),
+               nsmall = 2),
+             "p value" = case_when(
+               p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
+               p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
+               p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
+             )
+           ) %>%
+           select(
+             "n",
+             "R2",
+             "adjust. R2",
+             "F",
+             "p value",
+             "df"
+           )
+  )
+
+  return(get(paste0(outcome,"model1b_reg_stats")))
+}
+```
+
+```{r}
+model1b.estimates(outcome = "gad.diff_score_base_prepan", data_set = "dat.prepan")
+model1b.reg.stats(outcome = "gad.diff_score_base_prepan", data_set = "dat.prepan")
+```
+
+```{r model0a.explan function}
+model0a.explan.estimates <- function(outcome, explan_var, data_set) {
+  # define the variable name of the dependent variable
+  dependent.variable <- outcome
+  # define the independent variables
+  independent.variables <- c(explan_var, "Disorder_hierarchical")
+  # create the formula
+  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
+  glm.formula
+
+  # run the glm
+  assign(paste0(outcome,".",explan_var,".model0a.explan"),
+         lm( formula = glm.formula,
+             data = get(data_set)
+         )
+  )
+
+  assign(paste0(outcome,".",explan_var,"model0a.explan_estimates"),
+         tidy(get(paste0(outcome,".",explan_var,".model0a.explan")), conf.int = TRUE) %>%
+           mutate(
+             "Indepent variable" = recode_factor(
+               term,
+               "(Intercept)" = "Intercept",
+               "Disorder_hierarchicalAnxiety disorders" = "Anxiety disorders",
+               "Disorder_hierarchicalEating disorders" = "Eating disorders",
+               "Disorder_hierarchicalOCDs" = "OCDs",
+               "Disorder_hierarchicalPTSD" = "PTSD",
+               "Disorder_hierarchicalDepressive disorders" = "Depressive disorders",
+               "Disorder_hierarchicalBipolar disorders" = "Bipolar disorders"
+             ),
+             "Estimate" = format(
+               round(estimate,
+                     digits = 2),
+               nsmall = 2),
+             "95% CI low" = format(
+               round(conf.low,
+                     digits = 2),
+               nsmall = 2),
+             "95% CI up" = format(
+               round(conf.high,
+                     digits = 2),
+               nsmall = 2),
+             "SE" = format(
+               round(std.error,
+                     digits = 2),
+               nsmall = 2),
+             "z score" = format(
+               round(statistic,
+                     digits = 2),
+               nsmall = 2),
+             "p value" = case_when(
+               p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
+               p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
+               p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
+             )
+           ) %>%
+           select(
+             "Indepent variable",
+             "Estimate",
+             "95% CI low",
+             "95% CI up",
+             "SE",
+             #    "z score",
+             "p value"
+           )
+  )
+
+  return(get(paste0(outcome,".",explan_var,"model0a.explan_estimates")))
+}
+
+model0a.explan.reg.stats <- function(outcome, explan_var, data_set) {
+  # define the variable name of the dependent variable
+  dependent.variable <- outcome
+  # define the independent variables
+  independent.variables <- c(explan_var, "Disorder_hierarchical")
+  # create the formula
+  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
+  glm.formula
+
+  # run the glm
+  assign(paste0(outcome,".",explan_var,".model0a.explan"),
+         lm( formula = glm.formula,
+             data = get(data_set)
+         )
+  )
+
+  assign(paste0(outcome,".",explan_var,"model0a.explan_reg_stats"),
+         glance(get(paste0(outcome,".",explan_var,".model0a.explan"))) %>%
+           mutate(
+             "n" = format(
+               round(nobs,
+                     digits = 0),
+               nsmall = 0),
+             "R2" = format(
+               round(r.squared,
+                     digits = 2),
+               nsmall = 2),
+             "adjust. R2" = format(
+               round(adj.r.squared,
+                     digits = 2),
+               nsmall = 2),
+             "F" = format(
+               round(statistic,
+                     digits = 2),
+               nsmall = 2),
+             "p value" = case_when(
+               p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
+               p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
+               p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
+             )
+           ) %>%
+           select(
+             "n",
+             "R2",
+             "adjust. R2",
+             "F",
+             "p value",
+             "df"
+           )
+  )
+
+  return(get(paste0(outcome,".",explan_var,"model0a.explan_reg_stats")))
+}
+```
+
+```{r}
+model0a.explan.estimates(outcome = "gad.diff_score_base_prepan", explan_var = "gad.sum_score_retro", data_set = "dat.prepan")
+model0a.explan.reg.stats(outcome = "gad.diff_score_base_prepan", explan_var = "gad.sum_score_retro", data_set = "dat.prepan")
+```
+
+### CHANGE SCORES
+
+### GAD
+Model 0a: Disorder_hierarchical, Unadjusted
+```{r GAD prepan Model 0a}
+# Model
+gad_prepan_model0a <- lm(
+  formula = gad.diff_score_base_prepan ~ 
+    Disorder_hierarchical,
+  data = dat.prepan)
+
+summary(gad_prepan_model0a)
+
+# Regression statistics
+gad_prepan_model0a_reg_stats <- glance(gad_prepan_model0a) %>%
+  mutate(
+    "n" = format(
+      round(nobs,
+            digits = 0),
+      nsmall = 0),
+    "R2" = format(
+      round(r.squared,
+            digits = 2),
+      nsmall = 2),
+    "adjust. R2" = format(
+      round(adj.r.squared,
+            digits = 2),
+      nsmall = 2),
+    "F" = format(
+      round(statistic,
+            digits = 2),
+      nsmall = 2),
+    "p value" = case_when(
+      p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
+      p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
+      p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
+  )
+  ) %>%
+  select(
+    "n",
+    "R2",
+    "adjust. R2",
+    "F",
+    "p value",
+    "df"
+  )
+
+kable(gad_prepan_model0a_reg_stats)
+gad_prepan_model0a_reg_stats
+
+# Estimate summary table
+gad_prepan_model0a_estimates <- tidy(gad_prepan_model0a, conf.int = TRUE) %>%
+  mutate(
+    "Indepent variable" = recode_factor(
+      term,
+      "(Intercept)" = "Intercept",
+      "Disorder_hierarchicalAnxiety disorders" = "Anxiety disorders",
+      "Disorder_hierarchicalEating disorders" = "Eating disorders",
+      "Disorder_hierarchicalOCDs" = "OCDs",
+      "Disorder_hierarchicalPTSD" = "PTSD",
+      "Disorder_hierarchicalDepressive disorders" = "Depressive disorders",
+      "Disorder_hierarchicalBipolar disorders" = "Bipolar disorders"
+    ),
+    "Estimate" = format(
+      round(estimate,
+            digits = 2),
+      nsmall = 2),
+    "95% CI low" = format(
+      round(conf.low,
+            digits = 2),
+      nsmall = 2),
+    "95% CI up" = format(
+      round(conf.high,
+            digits = 2),
+      nsmall = 2),
+    "SE" = format(
+      round(std.error,
+            digits = 2),
+      nsmall = 2),
+    "z score" = format(
+      round(statistic,
+            digits = 2),
+      nsmall = 2),
+    "p value" = case_when(
+      p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
+      p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
+      p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
+  )
+  ) %>%
+  select(
+    "Indepent variable",
+    "Estimate",
+    "95% CI low",
+    "95% CI up",
     "SE",

### 2020-09-17 PANCHANGE_data_preprocessing2020-07-15.Rmd
Fixed OCI-R retro and baseline scoring by changing to using the numeric variables.

--- 2020-09-10 PANCHANGE_data_preprocessing2020-07-15.Rmd
@@
 
-```{r ocir prepan sum score if missigng items set to NA - all items}
+```{r ocir prepan sum score if missing items set to NA - all items}
 if(GLAD == TRUE | EDGI == TRUE) {
@@
 ocir.items_retro = c(
-  "ocir.i_repeatedly_check_doors_windows_drawers_etc_retro",
-  "ocir.arranged_things_change_upset_retro",
-  "ocir.repeat_feel_numbers_retro",
-  "ocir.clean_simply_wash_feel_retro",
-  "ocir.mind_upset_unpleasant_thoughts_retro",
-  "ocir.afraid_avoid_throwing_things_retro",
-  "ocir.light_switches_water_taps_retro",
-  "ocir.arranged_things_retro",
-  "ocir.good_feel_bad_numbers_retro",
-  "ocir.hands_longer_wash_retro",
-  "ocir.saved_things_retro",
-  "ocir.frequently_difficulty_rid_nasty_retro",
-  "ocir.i_check_things_more_often_than_necessary_retro",
-  "ocir.arranged_properly_objects_upset_retro",
-  "ocir.feel_compelled_count_things_retro",
-  "ocir.strangers_touch_touched_difficult_retro",
-  "ocir.control_difficult_find_thoughts_retro",
-  "ocir.i_collect_things_i_dont_need_retro"
+  "ocir.i_repeatedly_check_doors_windows_drawers_etc_retro_numeric",
+  "ocir.arranged_things_change_upset_retro_numeric",
+  "ocir.repeat_feel_numbers_retro_numeric",
+  "ocir.clean_simply_wash_feel_retro_numeric",
+  "ocir.mind_upset_unpleasant_thoughts_retro_numeric",
+  "ocir.afraid_avoid_throwing_things_retro_numeric",
+  "ocir.light_switches_water_taps_retro_numeric",
+  "ocir.arranged_things_retro_numeric",
+  "ocir.good_feel_bad_numbers_retro_numeric",
+  "ocir.hands_longer_wash_retro_numeric",
+  "ocir.saved_things_retro_numeric",
+  "ocir.frequently_difficulty_rid_nasty_retro_numeric",
+  "ocir.i_check_things_more_often_than_necessary_retro_numeric",
+  "ocir.arranged_properly_objects_upset_retro_numeric",
+  "ocir.feel_compelled_count_things_retro_numeric",
+  "ocir.strangers_touch_touched_difficult_retro_numeric",
+  "ocir.control_difficult_find_thoughts_retro_numeric",
+  "ocir.i_collect_things_i_dont_need_retro_numeric"
 )
@@
 ocir.items_base = c(
-  "ocir.i_repeatedly_check_doors_windows_drawers_etc_base",
-  "ocir.arranged_things_change_upset_base",
-  "ocir.repeat_feel_numbers_base",
-  "ocir.clean_simply_wash_feel_base",
-  "ocir.mind_upset_unpleasant_thoughts_base",
-  "ocir.afraid_avoid_throwing_things_base",
-  "ocir.light_switches_water_taps_base",
-  "ocir.arranged_things_base",
-  "ocir.good_feel_bad_numbers_base",
-  "ocir.hands_longer_wash_base",
-  "ocir.saved_things_base",
-  "ocir.frequently_difficulty_rid_nasty_base",
-  "ocir.i_check_things_more_often_than_necessary_base",
-  "ocir.arranged_properly_objects_upset_base",
-  "ocir.feel_compelled_count_things_base",
-  "ocir.strangers_touch_touched_difficult_base",
-  "ocir.control_difficult_find_thoughts_base",
-  "ocir.i_collect_things_i_dont_need_base"
+  "ocir.i_repeatedly_check_doors_windows_drawers_etc_base_numeric",
+  "ocir.arranged_things_change_upset_base_numeric",
+  "ocir.repeat_feel_numbers_base_numeric",
+  "ocir.clean_simply_wash_feel_base_numeric",
+  "ocir.mind_upset_unpleasant_thoughts_base_numeric",
+  "ocir.afraid_avoid_throwing_things_base_numeric",
+  "ocir.light_switches_water_taps_base_numeric",
+  "ocir.arranged_things_base_numeric",
+  "ocir.good_feel_bad_numbers_base_numeric",
+  "ocir.hands_longer_wash_base_numeric",
+  "ocir.saved_things_base_numeric",
+  "ocir.frequently_difficulty_rid_nasty_base_numeric",
+  "ocir.i_check_things_more_often_than_necessary_base_numeric",
+  "ocir.arranged_properly_objects_upset_base_numeric",
+  "ocir.feel_compelled_count_things_base_numeric",
+  "ocir.strangers_touch_touched_difficult_base_numeric",
+  "ocir.control_difficult_find_thoughts_base_numeric",
+  "ocir.i_collect_things_i_dont_need_base_numeric"
 )
@@
   distinct(subjectid, .keep_all = TRUE) %>% # Remove duplicates based on ID
-  separate(subjectid, into = c("Sample", "ID.intm"), sep = 6) %>% # Split ID in Sample and Number
-  separate(ID.intm, into = "ID", sep = 7) %>%
+  separate(subjectid, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
   mutate(ID = as.numeric(ID)) %>%
@@
          ID, # ID
-         alsfrs.limb_weakness_noticed_past = alsfrs.limb_weakness_past_month,
+         alsfrs.limb_weakness_noticed_past,
          alsfrs.normal,
@@
          ID, # ID
-         ess.felt_excessively_sleepy_past,
+         ess.felt_excessively_sleepy_past= ess.day_past_month_felt,
          ess.sitting_and_reading,
@@
          ess.sitting_inactive_in_a_public_place,
-         ess.break_passenger_car_hour,
+         ess.break_passenger_hour_car,
          ess.afternoon_rest_circumstances_lying,
@@
          ess.sitting_inactive_in_a_public_place,
-         ess.break_passenger_car_hour = ess.break_passenger_hour_car,
+         ess.break_passenger_hour_car,
          ess.afternoon_rest_circumstances_lying,
@@
          ID, # ID
-         ess.felt_excessively_sleepy_past = ess.felt_excessively_sleepy_day,
+         ess.felt_excessively_sleepy_past,
          ess.sitting_and_reading,
@@
          ess.sitting_inactive_in_a_public_place,
-         ess.break_passenger_car_hour = ess.break_hour_passenger_car,
+         ess.break_passenger_hour_car,
          ess.afternoon_rest_circumstances_lying,
@@
          ess.sitting_quietly_after_a_lunch_without_alcohol,
-         ess.car_minutes_stopped_traffic#,
-#         ess.insomnia, # questions are not asked in RAMP
-#         ess.narcolepsy,
-#         ess.rem_sleep_behaviour_disorder,
-#         ess.restless_legs_syndrome,
-#         ess.sleep_apnea,
-#         ess.sleep_terrors,
-#         ess.sleepwalking,
-#         ess.other,
-#         ess.none  
+         ess.car_minutes_stopped_traffic,
+         ess.insomnia,
+         ess.narcolepsy,
+         ess.rem_sleep_behaviour_disorder,
+         ess.restless_legs_syndrome,
+         ess.sleep_apnea,
+         ess.sleep_terrors,
+         ess.sleepwalking,
+         ess.other,
+         ess.none  
          ) %>%
   add_numeric(., exclude = exclude_cols) %>%
-    add_column(
-    ess.insomnia = NA_character_,
-    ess.narcolepsy = NA_character_,
-    ess.rem_sleep_behaviour_disorder = NA_character_,
-    ess.restless_legs_syndrome = NA_character_,
-    ess.sleep_apnea = NA_character_,
-    ess.sleep_terrors = NA_character_,
-    ess.sleepwalking = NA_character_,
-    ess.other = NA_character_,
-    ess.none = NA_character_,
-    ess.insomnia_numeric = NA_real_,
-    ess.narcolepsy_numeric = NA_real_,
-    ess.rem_sleep_behaviour_disorder_numeric = NA_real_,
-    ess.restless_legs_syndrome_numeric = NA_real_,
-    ess.sleep_apnea_numeric = NA_real_,
-    ess.sleep_terrors_numeric = NA_real_,
-    ess.sleepwalking_numeric = NA_real_,
-    ess.other_numeric = NA_real_,
-    ess.none_numeric = NA_real_
-    ) %>%
   mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
@@
          midas.headaches_suffered_past_month,
-         midas.days_past_month_miss_work_school = midas.past_month_days,
-         midas.days_past_month_work_school_half_productivity = midas.past_month_days.1,
-         midas.days_past_month_miss_housework = midas.past_month_days.2,
-         midas.days_past_month_housework_half_productivity = midas.past_month_days.3,
-         midas.days_past_month_miss_social_activities = midas.past_month_days.4
+         midas.days_past_month_miss_work_school = midas.days_past_month,
+         midas.days_past_month_work_school_half_productivity = midas.days_past_month.1,
+         midas.days_past_month_miss_housework = midas.days_past_month.2,
+         midas.days_past_month_housework_half_productivity = midas.days_past_month.3,
+         midas.days_past_month_miss_social_activities = midas.days_past_month.4
          ) %>%
@@
 
-```{r nbr midas summary labels}
-if(NBR == TRUE) {
-summarytools::dfSummary(
-  nbr.midas.raw,
-  graph.col = F,
-  valid.col = F
-  #labels.col = F
-)
-}
-```
-
 Select variables
@@
          ID, # ID
-         midas.headaches_suffered_past_month,
-         midas.days_past_month_miss_work_school = midas.past_month_days,
-         midas.days_past_month_work_school_half_productivity = midas.past_month_days.1,
-         midas.days_past_month_miss_housework = midas.past_month_days.2,
-         midas.days_past_month_housework_half_productivity = midas.past_month_days.3,
-         midas.days_past_month_miss_social_activities = midas.past_month_days.4 
+         midas.day_past_month_felt,
+         midas.sitting_and_reading,
+         midas.watching_tv,
+         midas.sitting_inactive_in_a_public_place,
+         midas.break_passenger_hour_car,
+         midas.afternoon_rest_circumstances_lying,
+         midas.sitting_and_talking_to_someone,
+         midas.sitting_quietly_after_a_lunch_without_alcohol,
+         midas.car_minutes_stopped_traffic,
+         midas.insomnia,
+         midas.narcolepsy,
+         midas.rem_sleep_behaviour_disorder,
+         midas.restlmidas_legs_syndrome,
+         midas.sleep_apnea,
+         midas.sleep_terrors,
+         midas.sleepwalking,
+         midas.other,
+         midas.none  
          ) %>%
@@
 
-```{r ramp midas summary labels}
-if(RAMP == TRUE) {
-summarytools::dfSummary(
-  ramp.midas.raw,
-  graph.col = F,
-  valid.col = F
-  #labels.col = F
-)
-}
-```
-
 Select variables
@@
          ID, # ID
-         midas.headaches_suffered_past_month,
-         midas.days_past_month_miss_work_school = midas.scale_line_click_firmly,
-         midas.days_past_month_work_school_half_productivity = midas.scale_line_click_firmly.1,
-         midas.days_past_month_miss_housework = midas.scale_line_click_firmly.2,
-         midas.days_past_month_housework_half_productivity = midas.scale_line_click_firmly.3,
-         midas.days_past_month_miss_social_activities = midas.scale_line_click_firmly.4
+         midas.day_past_month_felt,
+         midas.sitting_and_reading,
+         midas.watching_tv,
+         midas.sitting_inactive_in_a_public_place,
+         midas.break_passenger_hour_car,
+         midas.afternoon_rest_circumstances_lying,
+         midas.sitting_and_talking_to_someone,
+         midas.sitting_quietly_after_a_lunch_without_alcohol,
+         midas.car_minutes_stopped_traffic,
+         midas.insomnia,
+         midas.narcolepsy,
+         midas.rem_sleep_behaviour_disorder,
+         midas.restlmidas_legs_syndrome,
+         midas.sleep_apnea,
+         midas.sleep_terrors,
+         midas.sleepwalking,
+         midas.other,
+         midas.none  
          ) %>%
@@
          ID, # ID
-         nmss.ability_taste_food_smell,
+         nmss.ability_taste_food_change,
          nmss.severe_taste_smell_loss
@@
          ID, # ID
-         nmss.ability_taste_food_smell = nmss.taste_food_ability_smell, # different to glad
+         nmss.ability_taste_food_change = nmss.taste_food_ability_smell,
          nmss.severe_taste_smell_loss
@@
          ID, # ID
-         nmss.ability_taste_food_smell,
+         nmss.ability_taste_food_change,
          nmss.severe_taste_smell_loss 
@@
          ID, # ID
-         nmss.ability_taste_food_smell,
-         nmss.severe_taste_smell_loss = nmss.severe_taste_loss_smell 
+         nmss.ability_taste_food_change,
+         nmss.severe_taste_smell_loss 
          ) %>%
@@
          nmsw.drink_problems_choking_difficulty,
-         nmsw.regularly_night_pass_urine,
-         nmsw.sex_difficult_finding,
+         nmsw.night_regularly_pass_urine,
+         nmsw.sex_finding_difficult,
          nmsw.weak_standing_feeling_light,
@@
          nmsw.drink_problems_choking_difficulty,
-         nmsw.regularly_night_pass_urine,
-         nmsw.sex_difficult_finding,
+         nmsw.night_regularly_pass_urine = nmsw.regularly_night_pass_urine,
+         nmsw.sex_finding_difficult = nmsw.sex_difficult_finding,
          nmsw.weak_standing_feeling_light,
@@
          nmsw.drink_problems_choking_difficulty,
-         nmsw.regularly_night_pass_urine = nmsw.night_regularly_pass_urine, # different glad
-         nmsw.sex_difficult_finding = nmsw.sex_finding_difficult, # different glad
-         nmsw.weak_standing_feeling_light = nmsw.weak_standing_dizzy_feeling, # different glad
+         nmsw.night_regularly_pass_urine,
+         nmsw.sex_finding_difficult,
+         nmsw.weak_standing_feeling_light,
          nmsw.acting_moving_sleep_talking,
@@
          ID, # ID
-         tinnitus.ears_noises_minutes_head,
-         tinnitus.ears_noises_minutes_head_frequency = tinnitus.ears_noises_minutes_head.1,
+         tinnitus.ears_noises_head_minutes,
+         tinnitus.lasts_ears_noises_head,
          tinnitus.noises_worry_worst_upset    
@@
          ID, # ID
-         tinnitus.ears_noises_minutes_head,
-         tinnitus.ears_noises_minutes_head_frequency = tinnitus.ears_noises_minutes_head.1,
+         tinnitus.ears_noises_head_minutes = tinnitus.ears_noises_minutes_head,
+         tinnitus.lasts_ears_noises_head = tinnitus.ears_noises_minutes_head.1,
          tinnitus.noises_worry_worst_upset
@@
 
-```{r ramp tinnitus summary labels}
-if(NBR == TRUE) {
-summarytools::dfSummary(
-  nbr.tinnitus.raw,
-  graph.col = F,
-  valid.col = F
-  #labels.col = F
-)
-}
-```
-
 Select variables
@@
          ID, # ID
-         tinnitus.ears_noises_minutes_head,
-         tinnitus.ears_noises_minutes_head_frequency = tinnitus.ears_noises_minutes_head.1,
+         tinnitus.ears_noises_head_minutes,
+         tinnitus.lasts_ears_noises_head,
          tinnitus.noises_worry_worst_upset 
@@
          ID, # ID
-         tinnitus.ears_noises_minutes_head,
-         tinnitus.ears_noises_minutes_head_frequency = tinnitus.lasts_ears_noises_minutes,
-         tinnitus.noises_worry_worst_upset = tinnitus.noises_worry_worst_annoy
+         tinnitus.ears_noises_head_minutes,
+         tinnitus.lasts_ears_noises_head,
+         tinnitus.noises_worry_worst_upset
          ) %>%
@@
   coping.phq.raw.id,
-#  coping.ocir.raw.id, # joint in the chunk before because it was missing the EDGI ID in any column
   als.raw.id,
@@
   tinnitus.raw.id
+#  coping.ocir.raw.id
 )

### 2020-09-18 PANCHANGE_analysis.Rmd
deleted all regressions and replaced with short forms due to functions

@@
 
-## Prepan-baseline change
+# Functions
 
@@
 }
-```
-
-```{r}
-model0a.estimates(outcome = "gad.diff_score_base_prepan", data_set = "dat.prepan")
-model0a.reg.stats(outcome = "gad.diff_score_base_prepan", data_set = "dat.prepan")
 ```
@@
 }
-```
-
-```{r}
-model0b.estimates(outcome = "gad.diff_score_base_prepan", data_set = "dat.prepan")
-model0b.reg.stats(outcome = "gad.diff_score_base_prepan", data_set = "dat.prepan")
 ```
@@
 }
-```
-
-```{r}
-model1a.estimates(outcome = "gad.diff_score_base_prepan", data_set = "dat.prepan")
-model1a.reg.stats(outcome = "gad.diff_score_base_prepan", data_set = "dat.prepan")
 ```
@@
 
-```{r}
-model1b.estimates(outcome = "gad.diff_score_base_prepan", data_set = "dat.prepan")
-model1b.reg.stats(outcome = "gad.diff_score_base_prepan", data_set = "dat.prepan")
-```
-
 ```{r model0a.explan function}
@@
 
-```{r}
-model0a.explan.estimates(outcome = "gad.diff_score_base_prepan", explan_var = "gad.sum_score_retro", data_set = "dat.prepan")
-model0a.explan.reg.stats(outcome = "gad.diff_score_base_prepan", explan_var = "gad.sum_score_retro", data_set = "dat.prepan")
-```
-
-### CHANGE SCORES
-
-### GAD
-Model 0a: Disorder_hierarchical, Unadjusted
-```{r GAD prepan Model 0a}
-# Model
-gad_prepan_model0a <- lm(
-  formula = gad.diff_score_base_prepan ~ 
-    Disorder_hierarchical,
-  data = dat.prepan)
-
-summary(gad_prepan_model0a)
-
-# Regression statistics
-gad_prepan_model0a_reg_stats <- glance(gad_prepan_model0a) %>%
-  mutate(
-    "n" = format(
-      round(nobs,
-            digits = 0),
-      nsmall = 0),
-    "R2" = format(
-      round(r.squared,
-            digits = 2),
-      nsmall = 2),
-    "adjust. R2" = format(
-      round(adj.r.squared,
-            digits = 2),
-      nsmall = 2),
-    "F" = format(
-      round(statistic,
-            digits = 2),
-      nsmall = 2),
-    "p value" = case_when(
-      p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
-      p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
-      p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
-  )
-  ) %>%
-  select(
-    "n",
-    "R2",
-    "adjust. R2",
-    "F",
-    "p value",
-    "df"
-  )
-
-kable(gad_prepan_model0a_reg_stats)
-gad_prepan_model0a_reg_stats
-
-# Estimate summary table
-gad_prepan_model0a_estimates <- tidy(gad_prepan_model0a, conf.int = TRUE) %>%
-  mutate(
-    "Indepent variable" = recode_factor(
-      term,
-      "(Intercept)" = "Intercept",
-      "Disorder_hierarchicalAnxiety disorders" = "Anxiety disorders",
-      "Disorder_hierarchicalEating disorders" = "Eating disorders",
-      "Disorder_hierarchicalOCDs" = "OCDs",
-      "Disorder_hierarchicalPTSD" = "PTSD",
-      "Disorder_hierarchicalDepressive disorders" = "Depressive disorders",
-      "Disorder_hierarchicalBipolar disorders" = "Bipolar disorders"
-    ),
-    "Estimate" = format(
-      round(estimate,
-            digits = 2),
-      nsmall = 2),
-    "95% CI low" = format(
-      round(conf.low,
-            digits = 2),
-      nsmall = 2),
-    "95% CI up" = format(
-      round(conf.high,
-            digits = 2),
-      nsmall = 2),
-    "SE" = format(
-      round(std.error,
-            digits = 2),
-      nsmall = 2),
-    "z score" = format(
-      round(statistic,
-            digits = 2),
-      nsmall = 2),
-    "p value" = case_when(
-      p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
-      p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
-      p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
-  )
-  ) %>%
-  select(
-    "Indepent variable",
-    "Estimate",
-    "95% CI low",
-    "95% CI up",
-    "SE",
-#    "z score",
-    "p value"
-  )
-
-kable(gad_prepan_model0a_estimates)
-gad_prepan_model0a_estimates
-```
-
-Model 0b: Overlapping disorders, Unadjusted
-```{r GAD prepan Model 0b}
-gad_prepan_model0b <- lm(
-  formula = gad.diff_score_base_prepan ~
-    anxiety_disorders +
-    depressive_disorders +
-    depression_and_anxiety +
-    eating_disorders +
-    obsessive_compulsive_disorders +
-    psychotic_disorders +
-    mhd.mania_hypomania_bipolar_or_manicdepression +
-    mhd.posttraumatic_stress_disorder_ptsd +
-    autism_spectrum_disorder +
-    mhd.attention_deficit_hyperactivity_disorder +
-    mhd.personality_disorder,
-  data = dat.prepan)
-
-summary(gad_prepan_model0b)
-
-# Regression statistics
-gad_prepan_model0b_reg_stats <- glance(gad_prepan_model0b) %>%
-  mutate(
-    "n" = format(
-      round(nobs,
-            digits = 0),
-      nsmall = 0),
-    "R2" = format(
-      round(r.squared,
-            digits = 2),
-      nsmall = 2),
-    "adjust. R2" = format(
-      round(adj.r.squared,
-            digits = 2),
-      nsmall = 2),
-    "F" = format(
-      round(statistic,
-            digits = 2),
-      nsmall = 2),
-    "p value" = case_when(
-      p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
-      p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
-      p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
-  )
-  ) %>%
-  select(
-    "n",
-    "R2",
-    "adjust. R2",
-    "F",
-    "p value",
-    "df"
-  )
-
-kable(gad_prepan_model0b_reg_stats)
-gad_prepan_model0b_reg_stats
-
-# Estimate summary table
-gad_prepan_model0b_estimates <- tidy(gad_prepan_model0b) %>%
+```{r model0b.explan function}
+model0b.explan.estimates <- function(outcome, explan_var, data_set) {
+  # define the variable name of the dependent variable
+  dependent.variable <- outcome
+  # define the independent variables
+  independent.variables <- c(explan_var, 
+                             "anxiety_disorders",
+                             "depressive_disorders",
+                             "depression_and_anxiety",
+                             "eating_disorders",
+                             "obsessive_compulsive_disorders",
+                             "psychotic_disorders",
+                             "mhd.mania_hypomania_bipolar_or_manicdepression",
+                             "mhd.posttraumatic_stress_disorder_ptsd",
+                             "autism_spectrum_disorder",
+                             "mhd.attention_deficit_hyperactivity_disorder",
+                             "mhd.personality_disorder"
+  )
+  # create the formula
+  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
+  glm.formula
+
+  # run the glm
+  assign(paste0(outcome,".",explan_var,".model0b.explan"),
+         lm( formula = glm.formula,
+             data = get(data_set)
+         )
+  )
+
+  assign(paste0(outcome,".",explan_var,"model0b.explan_estimates"),
+         tidy(get(paste0(outcome,".",explan_var,".model0b.explan")), conf.int = TRUE) %>%
            mutate(
@@
                nsmall = 2),
+             "95% CI low" = format(
+               round(conf.low,
+                     digits = 2),
+               nsmall = 2),
+             "95% CI up" = format(
+               round(conf.high,
+                     digits = 2),
+               nsmall = 2),
              "SE" = format(
@@
              "Estimate",
+             "95% CI low",
+             "95% CI up",
              "SE",
@@
            )
-
-kable(gad_prepan_model0b_estimates)
-gad_prepan_model0b_estimates
-```
-
-Model 1a: Disorder hierarchical, Adjusted
-  Model 0a + Sex + Age + Ethnicity_collapsed + Time registration and baseline
-```{r GAD prepan Model 1a}
-gad_prepan_model1a <- lm(
-  formula = gad.diff_score_base_prepan ~ 
-    Disorder_hierarchical + 
-    Gender_collapsed + 
-    age_category_collapsed + 
-    Ethnicity_collapsed + 
-    time_diff_sign_up_coping,
-  data = dat.prepan)
-
-summary(gad_prepan_model1a)
-
-# Regression statistics
-gad_prepan_model1a_reg_stats <- glance(gad_prepan_model1a) %>%
+  )
+
+  return(get(paste0(outcome,".",explan_var,"model0b.explan_estimates")))
+}
+
+model0b.explan.reg.stats <- function(outcome, explan_var, data_set) {
+  # define the variable name of the dependent variable
+  dependent.variable <- outcome
+  # define the independent variables
+  independent.variables <- c("Disorder_hierarchical")
+  # create the formula
+  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
+  glm.formula
+
+  # run the glm
+  assign(paste0(outcome,".",explan_var,".model0b.explan"),
+         lm( formula = glm.formula,
+             data = get(data_set)
+         )
+  )
+
+  assign(paste0(outcome,".",explan_var,"model0b.explan_reg_stats"),
+         glance(get(paste0(outcome,".",explan_var,".model0b.explan"))) %>%
            mutate(
@@
            )
-
-kable(gad_prepan_model1a_reg_stats)
-gad_prepan_model1a_reg_stats
-
-# Estimate summary table
-gad_prepan_model1a_estimates <- tidy(gad_prepan_model1a) %>%
+  )
+
+  return(get(paste0(outcome,".",explan_var,"model0b.explan_reg_stats")))
+}
+```
+
+```{r model1a.explan function}
+model1a.explan.estimates <- function(outcome, explan_var, data_set) {
+  # define the variable name of the dependent variable
+  dependent.variable <- outcome
+  # define the independent variables
+  independent.variables <- c(explan_var,
+                             "Disorder_hierarchical",
+                             "Gender_collapsed",
+                             "age_category_collapsed",
+                             "Ethnicity_collapsed",
+                             "time_diff_sign_up_coping"
+  )
+  # create the formula
+  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
+  glm.formula
+
+  # run the glm
+  assign(paste0(outcome,".",explan_var,".model1a.explan"),
+         lm( formula = glm.formula,
+             data = get(data_set)
+         )
+  )
+
+  assign(paste0(outcome,".",explan_var,"model1a.explan_estimates"),
+         tidy(get(paste0(outcome,".",explan_var,".model1a.explan")), conf.int = TRUE) %>%
            mutate(
@@
            )
-
+  )
+
+  return(get(paste0(outcome,".",explan_var,"model1a.explan_estimates")))
+}
+
+model1a.explan.reg.stats <- function(outcome, explan_var, data_set) {
+  # define the variable name of the dependent variable
+  dependent.variable <- outcome
+  # define the independent variables
+  independent.variables <- c("Disorder_hierarchical")
+  # create the formula
+  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
+  glm.formula
+
+  # run the glm
+  assign(paste0(outcome,".",explan_var,".model1a.explan"),
+         lm( formula = glm.formula,
+             data = get(data_set)
+         )
+  )
+
+  assign(paste0(outcome,".",explan_var,"model1a.explan_reg_stats"),
+         glance(get(paste0(outcome,".",explan_var,".model1a.explan"))) %>%
+           mutate(
+             "n" = format(
+               round(nobs,
+                     digits = 0),
+               nsmall = 0),
+             "R2" = format(
+               round(r.squared,
+                     digits = 2),
+               nsmall = 2),
+             "adjust. R2" = format(
+               round(adj.r.squared,
+                     digits = 2),
+               nsmall = 2),
+             "F" = format(
+               round(statistic,
+                     digits = 2),
+               nsmall = 2),
+             "p value" = case_when(
+               p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
+               p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
+               p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
+             )
+           ) %>%
+           select(
+             "n",
+             "R2",
+             "adjust. R2",
+             "F",
+             "p value",
+             "df"
+           )
+  )
+
+  return(get(paste0(outcome,".",explan_var,"model1a.explan_reg_stats")))
+}
+```
+
+```{r model1b.explan function}
+model1b.explan.estimates <- function(outcome, explan_var, data_set) {
+  # define the variable name of the dependent variable
+  dependent.variable <- outcome
+  # define the independent variables
+  independent.variables <- c(explan_var,
+                             "anxiety_disorders",
+                             "depressive_disorders",
+                             "depression_and_anxiety",
+                             "eating_disorders",
+                             "obsessive_compulsive_disorders",
+                             "psychotic_disorders",
+                             "mhd.mania_hypomania_bipolar_or_manicdepression",
+                             "mhd.posttraumatic_stress_disorder_ptsd",
+                             "autism_spectrum_disorder",
+                             "mhd.attention_deficit_hyperactivity_disorder",
+                             "mhd.personality_disorder",
+                             "Gender_collapsed",
+                             "age_category_collapsed",
+                             "Ethnicity_collapsed",
+                             "time_diff_sign_up_coping"
+  )
+  # create the formula
+  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
+  glm.formula
+
+  # run the glm
+  assign(paste0(outcome,".",explan_var,".model1b.explan"),
+         lm( formula = glm.formula,
+             data = get(data_set)
+         )
+  )
+
+  assign(paste0(outcome,".",explan_var,"model1b.explan_estimates"),
+         tidy(get(paste0(outcome,".",explan_var,".model1b.explan")), conf.int = TRUE) %>%
+           mutate(
+             "Indepent variable" = recode_factor(
+               term,
+               "(Intercept)" = "Intercept",
+               "anxiety_disordersAnxiety disorder" = "Anxiety disorders",
+               "depressive_disordersDepressive disorder" = "Depressive disorders",
+               "depression_and_anxietyDepressive and anxiety disorder" = "Depressive and anxiety disorder",
+               "depression_and_anxietyOnly depressive disorder" = "Only depressive disorder",
+               "depression_and_anxietyOnly anxiety disorder" = "Only anxiety disorder",
+               "eating_disordersEating disorder" = "Eating disorders",
+               "obsessive_compulsive_disordersObsessive compulsive disorder" = "OCDs",
+               "psychotic_disordersPsychotic disorder" = "Psychotic disorder",
+               "mhd.mania_hypomania_bipolar_or_manicdepressionMania, hypomania, bipolar or manic-depression" = "Bipolar disorder",
+               "mhd.posttraumatic_stress_disorder_ptsdPost-traumatic stress disorder (PTSD)" = "PTSD",
+               "autism_spectrum_disorderAutism spectrum disorder" = "ASD",
+               "mhd.attention_deficit_hyperactivity_disorderAttention deficit or attention deficit and hyperactivity disorder (ADD/ADHD)" = "ADHD",
+               "mhd.personality_disorderPersonality disorder" = "Personality disorder",
+               "Gender_collapsedFemale" = "Female",
+               "Gender_collapsedNon-binary/Self-defined" = "Non-binary/Self-defined",
+               "age_category_collapsed19-25" = "19-25 years",
+               "age_category_collapsed26-35" = "26-35 years",
+               "age_category_collapsed36-45" = "36-45 years",
+               "age_category_collapsed46-55" = "46-55 years",
+               "age_category_collapsed56-65" = "56-65 years",
+               "age_category_collapsed66-70" = "66-70 years",
+               "age_category_collapsed71-75" = "71-75 years",
+               "age_category_collapsed76+" = "76+ years",
+               "Ethnicity_collapsedMixed or multiple ethnic origins" = "Mixed or multiple ethnic origins",
+               "Ethnicity_collapsedAsian or Asian British" = "Asian or Asian British",
+               "Ethnicity_collapsedAfrican or African British" = "African or African British",
+               "Ethnicity_collapsedOther" = "Other ethnicity",
+               "time_diff_sign_up_coping" = "Time difference: prepandemic to COPING"
+             ),
+             "Estimate" = format(
+               round(estimate,
+                     digits = 2),
+               nsmall = 2),
+             "95% CI low" = format(
+               round(conf.low,
+                     digits = 2),
+               nsmall = 2),
+             "95% CI up" = format(
+               round(conf.high,
+                     digits = 2),
+               nsmall = 2),
+             "SE" = format(
+               round(std.error,
+                     digits = 2),
+               nsmall = 2),
+             "z score" = format(
+               round(statistic,
+                     digits = 2),
+               nsmall = 2),
+             "p value" = case_when(
+               p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
+               p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
+               p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
+             )
+           ) %>%
+           select(
+             "Indepent variable",
+             "Estimate",
+             "95% CI low",
+             "95% CI up",
+             "SE",
+             #    "z score",
+             "p value"
+           )
+  )
+
+  return(get(paste0(outcome,".",explan_var,"model1b.explan_estimates")))
+}
+
+model1b.explan.reg.stats <- function(outcome, explan_var, data_set) {
+  # define the variable name of the dependent variable
+  dependent.variable <- outcome
+  # define the independent variables
+  independent.variables <- c("Disorder_hierarchical")
+  # create the formula
+  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
+  glm.formula
+
+  # run the glm
+  assign(paste0(outcome,".",explan_var,".model1b.explan"),
+         lm( formula = glm.formula,
+             data = get(data_set)
+         )
+  )
+
+  assign(paste0(outcome,".",explan_var,"model1b.explan_reg_stats"),
+         glance(get(paste0(outcome,".",explan_var,".model1b.explan"))) %>%
+           mutate(
+             "n" = format(
+               round(nobs,
+                     digits = 0),
+               nsmall = 0),
+             "R2" = format(
+               round(r.squared,
+                     digits = 2),
+               nsmall = 2),
+             "adjust. R2" = format(
+               round(adj.r.squared,
+                     digits = 2),
+               nsmall = 2),
+             "F" = format(
+               round(statistic,
+                     digits = 2),
+               nsmall = 2),
+             "p value" = case_when(
+               p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
+               p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
+               p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
+             )
+           ) %>%
+           select(
+             "n",
+             "R2",
+             "adjust. R2",
+             "F",
+             "p value",
+             "df"
+           )
+  )
+
+  return(get(paste0(outcome,".",explan_var,"model1b.explan_reg_stats")))
+}
+```
+
+# GAD prepan
+## Regression: Change scores
+### Model 0a: Disorder_hierarchical, Unadjusted
+```{r gad model0a diff_score prepan}
+# Regression coefficients
+gad_prepan_model0a_estimates <- model0a.estimates(outcome = "gad.diff_score_base_prepan",
+                  data_set = "dat.prepan")
+kable(gad_prepan_model0a_estimates)
+gad_prepan_model0a_estimates
+
+# Regression diagnostic statistics
+gad_prepan_model0a_reg_stats <- model0a.reg.stats(outcome = "gad.diff_score_base_prepan",
+                  data_set = "dat.prepan")
+kable(gad_prepan_model0a_reg_stats)
+gad_prepan_model0a_reg_stats
+```
+
+### Model 0b: Overlapping disorders, Unadjusted
+```{r gad model0b diff_score prepan}
+# Regression coefficients
+gad_prepan_model0b_estimates <- model0b.estimates(outcome = "gad.diff_score_base_prepan",
+                  data_set = "dat.prepan")
+kable(gad_prepan_model0b_estimates)
+gad_prepan_model0b_estimates
+
+# Regression diagnostic statistics
+gad_prepan_model0b_reg_stats <- model0b.reg.stats(outcome = "gad.diff_score_base_prepan",
+                  data_set = "dat.prepan")
+kable(gad_prepan_model0b_reg_stats)
+gad_prepan_model0b_reg_stats
+```
+
+### Model 1a: Disorder hierarchical, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r gad model1a diff_score prepan}
+# Regression coefficients
+gad_prepan_model1a_estimates <- model1a.estimates(outcome = "gad.diff_score_base_prepan",
+                  data_set = "dat.prepan")
 kable(gad_prepan_model1a_estimates)
 gad_prepan_model1a_estimates
-```
-
-Model 1b: Overlapping disorders, Adjusted
-  Model 0b + Sex + Age + Ethnicity_collapsed + Time registration and baseline
-```{r GAD prepan Model 1b}
-gad_prepan_model1b <- lm(
-  formula = gad.diff_score_base_prepan ~
-    anxiety_disorders +
-    depressive_disorders +
-    depression_and_anxiety +
-    eating_disorders +
-    obsessive_compulsive_disorders +
-    psychotic_disorders +
-    mhd.mania_hypomania_bipolar_or_manicdepression +
-    mhd.posttraumatic_stress_disorder_ptsd +
-    autism_spectrum_disorder +
-    mhd.attention_deficit_hyperactivity_disorder +
-    mhd.personality_disorder +
-    Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + time_diff_sign_up_coping,
-  data = dat.prepan)
-
-summary(gad_prepan_model1b)
-tidy(gad_prepan_model1b)
-```
-
-### PHQ
-Model 0a: Disorder_hierarchical, Unadjusted
-```{r PHQ prepan Model 0a}
-phq_prepan_model0a <- lm(
-  formula = phq.diff_score_base_prepan ~ 
-    Disorder_hierarchical,
-  data = dat.prepan)
-
-summary(phq_prepan_model0a)
-tidy(phq_prepan_model0a)
-```
-
-Model 0b: Overlapping disorders, Unadjusted
-```{r PHQ prepan Model 0b}
-phq_prepan_model0b <- lm(
-  formula = phq.diff_score_base_prepan ~
-    anxiety_disorders +
-    depressive_disorders +
-    depression_and_anxiety +
-    eating_disorders +
-    obsessive_compulsive_disorders +
-    psychotic_disorders +
-    mhd.mania_hypomania_bipolar_or_manicdepression +
-    mhd.posttraumatic_stress_disorder_ptsd +
-    autism_spectrum_disorder +
-    mhd.attention_deficit_hyperactivity_disorder +
-    mhd.personality_disorder,
-  data = dat.prepan)
-
-summary(phq_prepan_model0b)
-tidy(phq_prepan_model0b)
-```
-
-Model 1a: Disorder hierarchical, Adjusted
-  Model 0a + Sex + Age + Ethnicity_collapsed + Time registration and baseline
-```{r PHQ prepan Model 1a}
-phq_prepan_model1a <- lm(
-  formula = phq.diff_score_base_prepan ~ 
-    Disorder_hierarchical + 
-    Gender_collapsed + 
-    age_category_collapsed + 
-    Ethnicity_collapsed + 
-    time_diff_sign_up_coping,
-  data = dat.prepan)
-
-summary(phq_prepan_model1a)
-tidy(phq_prepan_model1a)
-```
-
-Model 1b: Overlapping disorders, Adjusted
-  Model 0b + Sex + Age + Ethnicity_collapsed + Time registration and baseline
-```{r PHQ prepan Model 1b}
-phq_prepan_model1b <- lm(
-  formula = phq.diff_score_base_prepan ~
-    anxiety_disorders +
-    depressive_disorders +
-    depression_and_anxiety +
-    eating_disorders +
-    obsessive_compulsive_disorders +
-    psychotic_disorders +
-    mhd.mania_hypomania_bipolar_or_manicdepression +
-    mhd.posttraumatic_stress_disorder_ptsd +
-    autism_spectrum_disorder +
-    mhd.attention_deficit_hyperactivity_disorder +
-    mhd.personality_disorder +
-    Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + time_diff_sign_up_coping,
-  data = dat.prepan)
-
-summary(phq_prepan_model1b)
-tidy(phq_prepan_model1b)
-```
-
-### PCL
-Model 0a: Disorder_hierarchical, Unadjusted
-```{r PCL prepan Model 0a}
-pcl_prepan_model0a <- lm(
-  formula = pcl.diff_score_base_prepan ~ 
-    Disorder_hierarchical,
-  data = dat.prepan)
-
-summary(pcl_prepan_model0a)
-tidy(pcl_prepan_model0a)
-```
-
-Model 0b: Overlapping disorders, Unadjusted
-```{r PCL prepan Model 0b}
-pcl_prepan_model0b <- lm(
-  formula = pcl.diff_score_base_prepan ~
-    anxiety_disorders +
-    depressive_disorders +
-    depression_and_anxiety +
-    eating_disorders +
-    obsessive_compulsive_disorders +
-    psychotic_disorders +
-    mhd.mania_hypomania_bipolar_or_manicdepression +
-    mhd.posttraumatic_stress_disorder_ptsd +
-    autism_spectrum_disorder +
-    mhd.attention_deficit_hyperactivity_disorder +
-    mhd.personality_disorder,
-  data = dat.prepan)
-
-summary(pcl_prepan_model0b)
-tidy(pcl_prepan_model0b)
-```
-
-Model 1a: Disorder hierarchical, Adjusted
-  Model 0a + Sex + Age + Ethnicity_collapsed + Time registration and baseline
-```{r PCL prepan Model 1a}
-pcl_prepan_model1a <- lm(
-  formula = pcl.diff_score_base_prepan ~ 
-    Disorder_hierarchical + 
-    Gender_collapsed + 
-    age_category_collapsed + 
-    Ethnicity_collapsed + 
-    time_diff_sign_up_coping,
-  data = dat.prepan)
-
-summary(pcl_prepan_model1a)
-tidy(pcl_prepan_model1a)
-```
-
-Model 1b: Overlapping disorders, Adjusted
-  Model 0b + Sex + Age + Ethnicity_collapsed + Time registration and baseline
-```{r PCL prepan Model 1b}
-pcl_prepan_model1b <- lm(
-  formula = pcl.diff_score_base_prepan ~
-    anxiety_disorders +
-    depressive_disorders +
-    depression_and_anxiety +
-    eating_disorders +
-    obsessive_compulsive_disorders +
-    psychotic_disorders +
-    mhd.mania_hypomania_bipolar_or_manicdepression +
-    mhd.posttraumatic_stress_disorder_ptsd +
-    autism_spectrum_disorder +
-    mhd.attention_deficit_hyperactivity_disorder +
-    mhd.personality_disorder +
-    Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + time_diff_sign_up_coping,
-  data = dat.prepan)
-
-summary(pcl_prepan_model1b)
-tidy(pcl_prepan_model1b)
-```
-
-### OCIR
-Model 0a: Disorder_hierarchical, Unadjusted
-```{r OCIR prepan Model 0a}
-ocir_prepan_model0a <- lm(
-  formula = ocir.diff_score_base_prepan ~ 
-    Disorder_hierarchical,
-  data = dat.prepan)
-
-summary(ocir_prepan_model0a)
-tidy(ocir_prepan_model0a)
-```
-
-Model 0b: Overlapping disorders, Unadjusted
-```{r OCIR prepan Model 0b}
-ocir_prepan_model0b <- lm(
-  formula = ocir.diff_score_base_prepan ~
-    anxiety_disorders +
-    depressive_disorders +
-    depression_and_anxiety +
-    eating_disorders +
-    obsessive_compulsive_disorders +
-    psychotic_disorders +
-    mhd.mania_hypomania_bipolar_or_manicdepression +
-    mhd.posttraumatic_stress_disorder_ptsd +
-    autism_spectrum_disorder +
-    mhd.attention_deficit_hyperactivity_disorder +
-    mhd.personality_disorder,
-  data = dat.prepan)
-
-summary(ocir_prepan_model0b)
-tidy(ocir_prepan_model0b)
-```
-
-Model 1a: Disorder hierarchical, Adjusted
-  Model 0a + Sex + Age + Ethnicity_collapsed + Time registration and baseline
-```{r OCIR prepan Model 1a}
-ocir_prepan_model1a <- lm(
-  formula = ocir.diff_score_base_prepan ~ 
-    Disorder_hierarchical + 
-    Gender_collapsed + 
-    age_category_collapsed + 
-    Ethnicity_collapsed + 
-    time_diff_sign_up_coping,
-  data = dat.prepan)
-
-summary(ocir_prepan_model1a)
-tidy(ocir_prepan_model1a)
-```
-
-Model 1b: Overlapping disorders, Adjusted
-  Model 0b + Sex + Age + Ethnicity_collapsed + Time registration and baseline
-```{r OCIR prepan Model 1b}
-ocir_prepan_model1b <- lm(
-  formula = ocir.diff_score_base_prepan ~
-    anxiety_disorders +
-    depressive_disorders +
-    depression_and_anxiety +
-    eating_disorders +
-    obsessive_compulsive_disorders +
-    psychotic_disorders +
-    mhd.mania_hypomania_bipolar_or_manicdepression +
-    mhd.posttraumatic_stress_disorder_ptsd +
-    autism_spectrum_disorder +
-    mhd.attention_deficit_hyperactivity_disorder +
-    mhd.personality_disorder +
-    Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + time_diff_sign_up_coping,
-  data = dat.prepan)
-
-summary(ocir_prepan_model1b)
-tidy(ocir_prepan_model1b)
-```
-
-### PANDEMIC BASELINE CONTROLLING FOR PREPANDEMIC
-
-### GAD
-Model 0a: Disorder_hierarchical, Unadjusted
-```{r GAD prepan Model absolute values absolute values 0a}
-gad_prepan_model0a <- lm(
-  formula = gad.sum_score_base ~ gad.sum_score_prepan + 
-    Disorder_hierarchical,
-  data = dat.prepan)
-
-summary(gad_prepan_model0a)
-tidy(gad_prepan_model0a)
-```
-
-Model 0b: Overlapping disorders, Unadjusted
-```{r GAD prepan Model absolute values 0b}
-gad_prepan_model0b <- lm(
-  formula = gad.sum_score_base ~ gad.sum_score_prepan +
-    anxiety_disorders +
-    depressive_disorders +
-    depression_and_anxiety +
-    eating_disorders +
-    obsessive_compulsive_disorders +
-    psychotic_disorders +
-    mhd.mania_hypomania_bipolar_or_manicdepression +
-    mhd.posttraumatic_stress_disorder_ptsd +
-    autism_spectrum_disorder +
-    mhd.attention_deficit_hyperactivity_disorder +
-    mhd.personality_disorder,
-  data = dat.prepan)
-
-summary(gad_prepan_model0b)
-tidy(gad_prepan_model0b)
-```
-
-Model 1a: Disorder hierarchical, Adjusted
-  Model 0a + Sex + Age + Ethnicity_collapsed + Time registration and baseline
-```{r GAD prepan Model absolute values 1a}
-gad_prepan_model1a <- lm(
-  formula = gad.sum_score_base ~ gad.sum_score_prepan + 
-    Disorder_hierarchical + 
-    Gender_collapsed + 
-    age_category_collapsed + 
-    Ethnicity_collapsed + 
-    time_diff_sign_up_coping,
-  data = dat.prepan)
-
-summary(gad_prepan_model1a)
-tidy(gad_prepan_model1a)
-```
-
-Model 1b: Overlapping disorders, Adjusted
-  Model 0b + Sex + Age + Ethnicity_collapsed + Time registration and baseline
-```{r GAD prepan Model absolute values 1b}
-gad_prepan_model1b <- lm(
-  formula = gad.sum_score_base ~ gad.sum_score_prepan +
-    anxiety_disorders +
-    depressive_disorders +
-    depression_and_anxiety +
-    eating_disorders +
-    obsessive_compulsive_disorders +
-    psychotic_disorders +
-    mhd.mania_hypomania_bipolar_or_manicdepression +
-    mhd.posttraumatic_stress_disorder_ptsd +
-    autism_spectrum_disorder +
-    mhd.attention_deficit_hyperactivity_disorder +
-    mhd.personality_disorder +
-    Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + time_diff_sign_up_coping,
-  data = dat.prepan)
-
-summary(gad_prepan_model1b)
-tidy(gad_prepan_model1b)
-```
-
-### PHQ
-Model 0a: Disorder_hierarchical, Unadjusted
-```{r PHQ prepan Model absolute values 0a}
-phq_prepan_model0a <- lm(
-  formula = phq.sum_score_base ~ phq.sum_score_prepan + 
-    Disorder_hierarchical,
-  data = dat.prepan)
-
-summary(phq_prepan_model0a)
-tidy(phq_prepan_model0a)
-```
-
-Model 0b: Overlapping disorders, Unadjusted
-```{r PHQ prepan Model absolute values 0b}
-phq_prepan_model0b <- lm(
-  formula = phq.sum_score_base ~ phq.sum_score_prepan +
-    anxiety_disorders +
-    depressive_disorders +
-    depression_and_anxiety +
-    eating_disorders +
-    obsessive_compulsive_disorders +
-    psychotic_disorders +
-    mhd.mania_hypomania_bipolar_or_manicdepression +
-    mhd.posttraumatic_stress_disorder_ptsd +
-    autism_spectrum_disorder +
-    mhd.attention_deficit_hyperactivity_disorder +
-    mhd.personality_disorder,
-  data = dat.prepan)
-
-summary(phq_prepan_model0b)
-tidy(phq_prepan_model0b)
-```
-
-Model 1a: Disorder hierarchical, Adjusted
-  Model 0a + Sex + Age + Ethnicity_collapsed + Time registration and baseline
-```{r PHQ prepan Model absolute values 1a}
-phq_prepan_model1a <- lm(
-  formula = phq.sum_score_base ~ phq.sum_score_prepan + 
-    Disorder_hierarchical + 
-    Gender_collapsed + 
-    age_category_collapsed + 
-    Ethnicity_collapsed + 
-    time_diff_sign_up_coping,
-  data = dat.prepan)
-
-summary(phq_prepan_model1a)
-tidy(phq_prepan_model1a)
-```
-
-Model 1b: Overlapping disorders, Adjusted
-  Model 0b + Sex + Age + Ethnicity_collapsed + Time registration and baseline
-```{r PHQ prepan Model absolute values 1b}
-phq_prepan_model1b <- lm(
-  formula = phq.sum_score_base ~ phq.sum_score_prepan +
-    anxiety_disorders +
-    depressive_disorders +
-    depression_and_anxiety +
-    eating_disorders +
-    obsessive_compulsive_disorders +
-    psychotic_disorders +
-    mhd.mania_hypomania_bipolar_or_manicdepression +
-    mhd.posttraumatic_stress_disorder_ptsd +
-    autism_spectrum_disorder +
-    mhd.attention_deficit_hyperactivity_disorder +
-    mhd.personality_disorder +
-    Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + time_diff_sign_up_coping,
-  data = dat.prepan)
-
-summary(phq_prepan_model1b)
-tidy(phq_prepan_model1b)
-```
-
-### PCL
-Model 0a: Disorder_hierarchical, Unadjusted
-```{r PCL prepan Model absolute values 0a}
-pcl_prepan_model0a <- lm(
-  formula = pcl.sum_score_base ~ pcl.sum_score_prepan + 
-    Disorder_hierarchical,
-  data = dat.prepan)
-
-summary(pcl_prepan_model0a)
-tidy(pcl_prepan_model0a)
-```
-
-Model 0b: Overlapping disorders, Unadjusted
-```{r PCL prepan Model absolute values 0b}
-pcl_prepan_model0b <- lm(
-  formula = pcl.sum_score_base ~ pcl.sum_score_prepan +
-    anxiety_disorders +
-    depressive_disorders +
-    depression_and_anxiety +
-    eating_disorders +
-    obsessive_compulsive_disorders +
-    psychotic_disorders +
-    mhd.mania_hypomania_bipolar_or_manicdepression +
-    mhd.posttraumatic_stress_disorder_ptsd +
-    autism_spectrum_disorder +
-    mhd.attention_deficit_hyperactivity_disorder +
-    mhd.personality_disorder,
-  data = dat.prepan)
-
-summary(pcl_prepan_model0b)
-tidy(pcl_prepan_model0b)
-```
-
-Model 1a: Disorder hierarchical, Adjusted
-  Model 0a + Sex + Age + Ethnicity_collapsed + Time registration and baseline
-```{r PCL prepan Model absolute values 1a}
-pcl_prepan_model1a <- lm(
-  formula = pcl.sum_score_base ~ pcl.sum_score_prepan + 
-    Disorder_hierarchical + 
-    Gender_collapsed + 
-    age_category_collapsed + 
-    Ethnicity_collapsed + 
-    time_diff_sign_up_coping,
-  data = dat.prepan)
-
-summary(pcl_prepan_model1a)
-tidy(pcl_prepan_model1a)
-```
-
-Model 1b: Overlapping disorders, Adjusted
-  Model 0b + Sex + Age + Ethnicity_collapsed + Time registration and baseline
-```{r PCL prepan Model absolute values 1b}
-pcl_prepan_model1b <- lm(
-  formula = pcl.sum_score_base ~ pcl.sum_score_prepan +
-    anxiety_disorders +
-    depressive_disorders +
-    depression_and_anxiety +
-    eating_disorders +
-    obsessive_compulsive_disorders +
-    psychotic_disorders +
-    mhd.mania_hypomania_bipolar_or_manicdepression +
-    mhd.posttraumatic_stress_disorder_ptsd +
-    autism_spectrum_disorder +
-    mhd.attention_deficit_hyperactivity_disorder +
-    mhd.personality_disorder +
-    Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + time_diff_sign_up_coping,
-  data = dat.prepan)
-
-summary(pcl_prepan_model1b)
-tidy(pcl_prepan_model1b)
-```
-
-### OCIR
-Model 0a: Disorder_hierarchical, Unadjusted
-```{r OCIR prepan Model absolute values 0a}
-ocir_prepan_model0a <- lm(
-  formula = ocir.sum_score_base ~ ocir.sum_score_prepan + 
-    Disorder_hierarchical,
-  data = dat.prepan)
-
-summary(ocir_prepan_model0a)
-tidy(ocir_prepan_model0a)
-```
-
-Model 0b: Overlapping disorders, Unadjusted
-```{r OCIR prepan Model absolute values 0b}
-ocir_prepan_model0b <- lm(
-  formula = ocir.sum_score_base ~ ocir.sum_score_prepan +
-    anxiety_disorders +
-    depressive_disorders +
-    depression_and_anxiety +
-    eating_disorders +
-    obsessive_compulsive_disorders +
-    psychotic_disorders +
-    mhd.mania_hypomania_bipolar_or_manicdepression +
-    mhd.posttraumatic_stress_disorder_ptsd +
-    autism_spectrum_disorder +
-    mhd.attention_deficit_hyperactivity_disorder +
-    mhd.personality_disorder,
-  data = dat.prepan)
-
-summary(ocir_prepan_model0b)
-tidy(ocir_prepan_model0b)
-```
-
-Model 1a: Disorder hierarchical, Adjusted
-  Model 0a + Sex + Age + Ethnicity_collapsed + Time registration and baseline
-```{r OCIR prepan Model absolute values 1a}
-ocir_prepan_model1a <- lm(
-  formula = ocir.sum_score_base ~ ocir.sum_score_prepan + 
-    Disorder_hierarchical + 
-    Gender_collapsed + 
-    age_category_collapsed + 
-    Ethnicity_collapsed + 
-    time_diff_sign_up_coping,
-  data = dat.prepan)
-
-summary(ocir_prepan_model1a)
-tidy(ocir_prepan_model1a)
-```
-
-Model 1b: Overlapping disorders, Adjusted
-  Model 0b + Sex + Age + Ethnicity_collapsed + Time registration and baseline
-```{r OCIR prepan Model absolute values 1b}
-ocir_prepan_model1b <- lm(
-  formula = ocir.sum_score_base ~ ocir.sum_score_prepan +
-    anxiety_disorders +
-    depressive_disorders +
-    depression_and_anxiety +
-    eating_disorders +
-    obsessive_compulsive_disorders +
-    psychotic_disorders +
-    mhd.mania_hypomania_bipolar_or_manicdepression +
-    mhd.posttraumatic_stress_disorder_ptsd +
-    autism_spectrum_disorder +
-    mhd.attention_deficit_hyperactivity_disorder +
-    mhd.personality_disorder +
-    Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + time_diff_sign_up_coping,
-  data = dat.prepan)
-
-summary(ocir_prepan_model1b)
-tidy(ocir_prepan_model1b)
-```
-
-## Retro-baseline change
-
-### CHANGE SCORES
-
-### GAD
-Model 0a: Disorder_hierarchical, Unadjusted
-```{r GAD retro Model 0a}
-gad_retro_model0a <- lm(
-  formula = gad.diff_score_base_retro ~ 
-    Disorder_hierarchical,
-  data = dat.retro)
-
-summary(gad_retro_model0a)
-tidy(gad_retro_model0a)
-```
-
-Model 0b: Overlapping disorders, Unadjusted
-```{r GAD retro Model 0b}
-gad_retro_model0b <- lm(
-  formula = gad.diff_score_base_retro ~
-    anxiety_disorders +
-    depressive_disorders +
-    depression_and_anxiety +
-    eating_disorders +
-    obsessive_compulsive_disorders +
-    psychotic_disorders +
-    mhd.mania_hypomania_bipolar_or_manicdepression +
-    mhd.posttraumatic_stress_disorder_ptsd +
-    autism_spectrum_disorder +
-    mhd.attention_deficit_hyperactivity_disorder +
-    mhd.personality_disorder,
-  data = dat.retro)
-
-summary(gad_retro_model0b)
-tidy(gad_retro_model0b)
-```
-
-Model 1a: Disorder hierarchical, Adjusted
-  Model 0a + Sex + Age + Ethnicity_collapsed + Time registration and baseline
-```{r GAD retro Model 1a}
-gad_retro_model1a <- lm(
-  formula = gad.diff_score_base_retro ~ 
-    Disorder_hierarchical + 
-    Gender_collapsed + 
-    age_category_collapsed + 
-    Ethnicity_collapsed + 
-    time_diff_sign_up_coping,
-  data = dat.retro)
-
-summary(gad_retro_model1a)
-tidy(gad_retro_model1a)
-```
-
-Model 1b: Overlapping disorders, Adjusted
-  Model 0b + Sex + Age + Ethnicity_collapsed + Time registration and baseline
-```{r GAD retro Model 1b}
-gad_retro_model1b <- lm(
-  formula = gad.diff_score_base_retro ~
-    anxiety_disorders +
-    depressive_disorders +
-    depression_and_anxiety +
-    eating_disorders +
-    obsessive_compulsive_disorders +
-    psychotic_disorders +
-    mhd.mania_hypomania_bipolar_or_manicdepression +
-    mhd.posttraumatic_stress_disorder_ptsd +
-    autism_spectrum_disorder +
-    mhd.attention_deficit_hyperactivity_disorder +
-    mhd.personality_disorder +
-    Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + time_diff_sign_up_coping,
-  data = dat.retro)
-
-summary(gad_retro_model1b)
-tidy(gad_retro_model1b)
-```
-
-### PHQ
-Model 0a: Disorder_hierarchical, Unadjusted
-```{r PHQ retro Model 0a}
-phq_retro_model0a <- lm(
-  formula = phq.diff_score_base_retro ~ 
-    Disorder_hierarchical,
-  data = dat.retro)
-
-summary(phq_retro_model0a)
-tidy(phq_retro_model0a)
-```
-
-Model 0b: Overlapping disorders, Unadjusted
-```{r PHQ retro Model 0b}
-phq_retro_model0b <- lm(
-  formula = phq.diff_score_base_retro ~
-    anxiety_disorders +
-    depressive_disorders +
-    depression_and_anxiety +
-    eating_disorders +
-    obsessive_compulsive_disorders +
-    psychotic_disorders +
-    mhd.mania_hypomania_bipolar_or_manicdepression +
-    mhd.posttraumatic_stress_disorder_ptsd +
-    autism_spectrum_disorder +
-    mhd.attention_deficit_hyperactivity_disorder +
-    mhd.personality_disorder,
-  data = dat.retro)
-
-summary(phq_retro_model0b)
-tidy(phq_retro_model0b)
-```
-
-Model 1a: Disorder hierarchical, Adjusted
-  Model 0a + Sex + Age + Ethnicity_collapsed + Time registration and baseline
-```{r PHQ retro Model 1a}
-phq_retro_model1a <- lm(
-  formula = phq.diff_score_base_retro ~ 
-    Disorder_hierarchical + 
-    Gender_collapsed + 
-    age_category_collapsed + 
-    Ethnicity_collapsed + 
-    time_diff_sign_up_coping,
-  data = dat.retro)
-
-summary(phq_retro_model1a)
-tidy(phq_retro_model1a)
-```
-
-Model 1b: Overlapping disorders, Adjusted
-  Model 0b + Sex + Age + Ethnicity_collapsed + Time registration and baseline
-```{r PHQ retro Model 1b}
-phq_retro_model1b <- lm(
-  formula = phq.diff_score_base_retro ~
-    anxiety_disorders +
-    depressive_disorders +
-    depression_and_anxiety +
-    eating_disorders +
-    obsessive_compulsive_disorders +
-    psychotic_disorders +
-    mhd.mania_hypomania_bipolar_or_manicdepression +
-    mhd.posttraumatic_stress_disorder_ptsd +
-    autism_spectrum_disorder +
-    mhd.attention_deficit_hyperactivity_disorder +
-    mhd.personality_disorder +
-    Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + time_diff_sign_up_coping,
-  data = dat.retro)
-
-summary(phq_retro_model1b)
-tidy(phq_retro_model1b)
-```
-
-### PCL
-
-++MD: Not sure if this is how we want to run the PCL regression - the outcome variable I've included is "How many PCL items the participants report are related to the pandemic", but I think we might want a more nuanced approach than this.
-
-```{r recode PCL retro variable as numeric}
-dat.retro <- dat.retro %>% 
-  mutate(
-    pcl.sum_score_retro = 
-      as.numeric(pcl.sum_score_retro_raw)
-  )
-```
-
-Model 0a: Disorder_hierarchical, Unadjusted
-```{r PCL retro Model 0a}
-pcl_retro_model0a <- lm(
-  formula = pcl.sum_score_retro ~ 
-    Disorder_hierarchical,
-  data = dat.retro)
-
-summary(pcl_retro_model0a)
-tidy(pcl_retro_model0a)
-```
-
-Model 0b: Overlapping disorders, Unadjusted
-```{r PCL retro Model 0b}
-pcl_retro_model0b <- lm(
-  formula = pcl.sum_score_retro ~
-    anxiety_disorders +
-    depressive_disorders +
-    depression_and_anxiety +
-    eating_disorders +
-    obsessive_compulsive_disorders +
-    psychotic_disorders +
-    mhd.mania_hypomania_bipolar_or_manicdepression +
-    mhd.posttraumatic_stress_disorder_ptsd +
-    autism_spectrum_disorder +
-    mhd.attention_deficit_hyperactivity_disorder +
-    mhd.personality_disorder,
-  data = dat.retro)
-
-summary(pcl_retro_model0b)
-tidy(pcl_retro_model0b)
-```
-
-Model 1a: Disorder hierarchical, Adjusted
-  Model 0a + Sex + Age + Ethnicity_collapsed + Time registration and baseline
-```{r PCL retro Model 1a}
-pcl_retro_model1a <- lm(
-  formula = pcl.sum_score_retro ~ 
-    Disorder_hierarchical + 
-    Gender_collapsed + 
-    age_category_collapsed + 
-    Ethnicity_collapsed + 
-    time_diff_sign_up_coping,
-  data = dat.retro)
-
-summary(pcl_retro_model1a)
-tidy(pcl_retro_model1a)
-```
-
-Model 1b: Overlapping disorders, Adjusted
-  Model 0b + Sex + Age + Ethnicity_collapsed + Time registration and baseline
-```{r PCL retro Model 1b}
-pcl_retro_model1b <- lm(
-  formula = pcl.sum_score_retro ~
-    anxiety_disorders +
-    depressive_disorders +
-    depression_and_anxiety +
-    eating_disorders +
-    obsessive_compulsive_disorders +
-    psychotic_disorders +
-    mhd.mania_hypomania_bipolar_or_manicdepression +
-    mhd.posttraumatic_stress_disorder_ptsd +
-    autism_spectrum_disorder +
-    mhd.attention_deficit_hyperactivity_disorder +
-    mhd.personality_disorder +
-    Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + time_diff_sign_up_coping,
-  data = dat.retro)
-
-summary(pcl_retro_model1b)
-tidy(pcl_retro_model1b)
-```
-
-### OCIR
-Model 0a: Disorder_hierarchical, Unadjusted
-```{r OCIR retro Model 0a}
-ocir_retro_model0a <- lm(
-  formula = ocir.diff_score_base_retro ~ 
-    Disorder_hierarchical,
-  data = dat.retro)
-
-summary(ocir_retro_model0a)
-tidy(ocir_retro_model0a)
-```
-
-Model 0b: Overlapping disorders, Unadjusted
-```{r OCIR retro Model 0b}
-ocir_retro_model0b <- lm(
-  formula = ocir.diff_score_base_retro ~
-    anxiety_disorders +
-    depressive_disorders +
-    depression_and_anxiety +
-    eating_disorders +
-    obsessive_compulsive_disorders +
-    psychotic_disorders +
-    mhd.mania_hypomania_bipolar_or_manicdepression +
-    mhd.posttraumatic_stress_disorder_ptsd +
-    autism_spectrum_disorder +
-    mhd.attention_deficit_hyperactivity_disorder +
-    mhd.personality_disorder,
-  data = dat.retro)
-
-summary(ocir_retro_model0b)
-tidy(ocir_retro_model0b)
-```
-
-Model 1a: Disorder hierarchical, Adjusted
-  Model 0a + Sex + Age + Ethnicity_collapsed + Time registration and baseline
-```{r OCIR retro Model 1a}
-ocir_retro_model1a <- lm(
-  formula = ocir.diff_score_base_retro ~ 
-    Disorder_hierarchical + 
-    Gender_collapsed + 
-    age_category_collapsed + 
-    Ethnicity_collapsed + 
-    time_diff_sign_up_coping,
-  data = dat.retro)
-
-summary(ocir_retro_model1a)
-tidy(ocir_retro_model1a)
-```
-
-Model 1b: Overlapping disorders, Adjusted
-  Model 0b + Sex + Age + Ethnicity_collapsed + Time registration and baseline
-```{r OCIR retro Model 1b}
-ocir_retro_model1b <- lm(
-  formula = ocir.diff_score_base_retro ~
-    anxiety_disorders +
-    depressive_disorders +
-    depression_and_anxiety +
-    eating_disorders +
-    obsessive_compulsive_disorders +
-    psychotic_disorders +
-    mhd.mania_hypomania_bipolar_or_manicdepression +
-    mhd.posttraumatic_stress_disorder_ptsd +
-    autism_spectrum_disorder +
-    mhd.attention_deficit_hyperactivity_disorder +
-    mhd.personality_disorder +
-    Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + time_diff_sign_up_coping,
-  data = dat.retro)
-
-summary(ocir_retro_model1b)
-tidy(ocir_retro_model1b)
-```
-
-### PANDEMIC BASELINE CONTROLLING FOR RETROSPECTIVE
-
-### GAD
-Model 0a: Disorder_hierarchical, Unadjusted
-```{r GAD retro Model absolute values 0a}
-gad_retro_model0a <- lm(
-  formula = gad.sum_score_base ~ gad.sum_score_retro + 
-    Disorder_hierarchical,
-  data = dat.retro)
-
-summary(gad_retro_model0a)
-tidy(gad_retro_model0a)
-```
-
-Model 0b: Overlapping disorders, Unadjusted
-```{r GAD retro Model absolute values 0b}
-gad_retro_model0b <- lm(
-  formula = gad.sum_score_base ~ gad.sum_score_retro +
-    anxiety_disorders +
-    depressive_disorders +
-    depression_and_anxiety +
-    eating_disorders +
-    obsessive_compulsive_disorders +
-    psychotic_disorders +
-    mhd.mania_hypomania_bipolar_or_manicdepression +
-    mhd.posttraumatic_stress_disorder_ptsd +
-    autism_spectrum_disorder +
-    mhd.attention_deficit_hyperactivity_disorder +
-    mhd.personality_disorder,
-  data = dat.retro)
-
-summary(gad_retro_model0b)
-tidy(gad_retro_model0b)
-```
-
-Model 1a: Disorder hierarchical, Adjusted
-  Model 0a + Sex + Age + Ethnicity_collapsed + Time registration and baseline
-```{r GAD retro Model absolute values 1a}
-gad_retro_model1a <- lm(
-  formula = gad.sum_score_base ~ gad.sum_score_retro + 
-    Disorder_hierarchical + 
-    Gender_collapsed + 
-    age_category_collapsed + 
-    Ethnicity_collapsed + 
-    time_diff_sign_up_coping,
-  data = dat.retro)
-
-summary(gad_retro_model1a)
-tidy(gad_retro_model1a)
-```
-
-Model 1b: Overlapping disorders, Adjusted
-  Model 0b + Sex + Age + Ethnicity_collapsed + Time registration and baseline
-```{r GAD retro Model absolute values 1b}
-gad_retro_model1b <- lm(
-  formula = gad.sum_score_base ~ gad.sum_score_retro +
-    anxiety_disorders +
-    depressive_disorders +
-    depression_and_anxiety +
-    eating_disorders +
-    obsessive_compulsive_disorders +
-    psychotic_disorders +
-    mhd.mania_hypomania_bipolar_or_manicdepression +
-    mhd.posttraumatic_stress_disorder_ptsd +
-    autism_spectrum_disorder +
-    mhd.attention_deficit_hyperactivity_disorder +
-    mhd.personality_disorder +
-    Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + time_diff_sign_up_coping,
-  data = dat.retro)
-
-summary(gad_retro_model1b)
-tidy(gad_retro_model1b)
-```
-
-### PHQ
-Model 0a: Disorder_hierarchical, Unadjusted
-```{r PHQ retro Model absolute values 0a}
-phq_retro_model0a <- lm(
-  formula = phq.sum_score_base ~ phq.sum_score_retro + 
-    Disorder_hierarchical,
-  data = dat.retro)
-
-summary(phq_retro_model0a)
-tidy(phq_retro_model0a)
-```
-
-Model 0b: Overlapping disorders, Unadjusted
-```{r PHQ retro Model absolute values 0b}
-phq_retro_model0b <- lm(
-  formula = phq.sum_score_base ~ phq.sum_score_retro +
-    anxiety_disorders +
-    depressive_disorders +
-    depression_and_anxiety +
-    eating_disorders +
-    obsessive_compulsive_disorders +
-    psychotic_disorders +
-    mhd.mania_hypomania_bipolar_or_manicdepression +
-    mhd.posttraumatic_stress_disorder_ptsd +
-    autism_spectrum_disorder +
-    mhd.attention_deficit_hyperactivity_disorder +
-    mhd.personality_disorder,
-  data = dat.retro)
-
-summary(phq_retro_model0b)
-tidy(phq_retro_model0b)
-```
-
-Model 1a: Disorder hierarchical, Adjusted
-  Model 0a + Sex + Age + Ethnicity_collapsed + Time registration and baseline
-```{r PHQ retro Model absolute values 1a}
-phq_retro_model1a <- lm(
-  formula = phq.sum_score_base ~ phq.sum_score_retro + 
-    Disorder_hierarchical + 
-    Gender_collapsed + 
-    age_category_collapsed + 
-    Ethnicity_collapsed + 
-    time_diff_sign_up_coping,
-  data = dat.retro)
-
-summary(phq_retro_model1a)
-tidy(phq_retro_model1a)
-```
-
-Model 1b: Overlapping disorders, Adjusted
-  Model 0b + Sex + Age + Ethnicity_collapsed + Time registration and baseline
-```{r PHQ retro Model absolute values 1b}
-phq_retro_model1b <- lm(
-  formula = phq.sum_score_base ~ phq.sum_score_retro +
-    anxiety_disorders +
-    depressive_disorders +
-    depression_and_anxiety +
-    eating_disorders +
-    obsessive_compulsive_disorders +
-    psychotic_disorders +
-    mhd.mania_hypomania_bipolar_or_manicdepression +
-    mhd.posttraumatic_stress_disorder_ptsd +
-    autism_spectrum_disorder +
-    mhd.attention_deficit_hyperactivity_disorder +
-    mhd.personality_disorder +
-    Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + time_diff_sign_up_coping,
-  data = dat.retro)
-
-summary(phq_retro_model1b)
-tidy(phq_retro_model1b)
-```
-
-### PCL
-Model 0a: Disorder_hierarchical, Unadjusted
-```{r PCL retro Model absolute values 0a}
-pcl_retro_model0a <- lm(
-  formula = pcl.sum_score_base ~ pcl.sum_score_retro + 
-    Disorder_hierarchical,
-  data = dat.retro)
-
-summary(pcl_retro_model0a)
-tidy(pcl_retro_model0a)
-```
-
-Model 0b: Overlapping disorders, Unadjusted
-```{r PCL retro Model absolute values 0b}
-pcl_retro_model0b <- lm(
-  formula = pcl.sum_score_base ~ pcl.sum_score_retro +
-    anxiety_disorders +
-    depressive_disorders +
-    depression_and_anxiety +
-    eating_disorders +
-    obsessive_compulsive_disorders +
-    psychotic_disorders +
-    mhd.mania_hypomania_bipolar_or_manicdepression +
-    mhd.posttraumatic_stress_disorder_ptsd +
-    autism_spectrum_disorder +
-    mhd.attention_deficit_hyperactivity_disorder +
-    mhd.personality_disorder,
-  data = dat.retro)
-
-summary(pcl_retro_model0b)
-tidy(pcl_retro_model0b)
-```
-
-Model 1a: Disorder hierarchical, Adjusted
-  Model 0a + Sex + Age + Ethnicity_collapsed + Time registration and baseline
-```{r PCL retro Model absolute values 1a}
-pcl_retro_model1a <- lm(
-  formula = pcl.sum_score_base ~ pcl.sum_score_retro + 
-    Disorder_hierarchical + 
-    Gender_collapsed + 
-    age_category_collapsed + 
-    Ethnicity_collapsed + 
-    time_diff_sign_up_coping,
-  data = dat.retro)
-
-summary(pcl_retro_model1a)
-tidy(pcl_retro_model1a)
-```
-
-Model 1b: Overlapping disorders, Adjusted
-  Model 0b + Sex + Age + Ethnicity_collapsed + Time registration and baseline
-```{r PCL retro Model absolute values 1b}
-pcl_retro_model1b <- lm(
-  formula = pcl.sum_score_base ~ pcl.sum_score_retro +
-    anxiety_disorders +
-    depressive_disorders +
-    depression_and_anxiety +
-    eating_disorders +
-    obsessive_compulsive_disorders +
-    psychotic_disorders +
-    mhd.mania_hypomania_bipolar_or_manicdepression +
-    mhd.posttraumatic_stress_disorder_ptsd +
-    autism_spectrum_disorder +
-    mhd.attention_deficit_hyperactivity_disorder +
-    mhd.personality_disorder +
-    Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + time_diff_sign_up_coping,
-  data = dat.retro)
-
-summary(pcl_retro_model1b)
-tidy(pcl_retro_model1b)
-```
-
-### OCIR
-Model 0a: Disorder_hierarchical, Unadjusted
-```{r OCIR retro Model absolute values 0a}
-ocir_retro_model0a <- lm(
-  formula = ocir.sum_score_base ~ ocir.sum_score_retro + 
-    Disorder_hierarchical,
-  data = dat.retro)
-
-summary(ocir_retro_model0a)
-tidy(ocir_retro_model0a)
-```
-
-Model 0b: Overlapping disorders, Unadjusted
-```{r OCIR retro Model absolute values 0b}
-ocir_retro_model0b <- lm(
-  formula = ocir.sum_score_base ~ ocir.sum_score_retro +
-    anxiety_disorders +
-    depressive_disorders +
-    depression_and_anxiety +
-    eating_disorders +
-    obsessive_compulsive_disorders +
-    psychotic_disorders +
-    mhd.mania_hypomania_bipolar_or_manicdepression +
-    mhd.posttraumatic_stress_disorder_ptsd +
-    autism_spectrum_disorder +
-    mhd.attention_deficit_hyperactivity_disorder +
-    mhd.personality_disorder,
-  data = dat.retro)
-
-summary(ocir_retro_model0b)
-tidy(ocir_retro_model0b)
-```
-
-Model 1a: Disorder hierarchical, Adjusted
-  Model 0a + Sex + Age + Ethnicity_collapsed + Time registration and baseline
-```{r OCIR retro Model absolute values 1a}
-ocir_retro_model1a <- lm(
-  formula = ocir.sum_score_base ~ ocir.sum_score_retro + 
-    Disorder_hierarchical + 
-    Gender_collapsed + 
-    age_category_collapsed + 
-    Ethnicity_collapsed + 
-    time_diff_sign_up_coping,
-  data = dat.retro)
-
-summary(ocir_retro_model1a)
-tidy(ocir_retro_model1a)
-```
-
-Model 1b: Overlapping disorders, Adjusted
-  Model 0b + Sex + Age + Ethnicity_collapsed + Time registration and baseline
-```{r OCIR retro Model absolute values 1b}
-ocir_retro_model1b <- lm(
-  formula = ocir.sum_score_base ~ ocir.sum_score_retro +
-    anxiety_disorders +
-    depressive_disorders +
-    depression_and_anxiety +
-    eating_disorders +
-    obsessive_compulsive_disorders +
-    psychotic_disorders +
-    mhd.mania_hypomania_bipolar_or_manicdepression +
-    mhd.posttraumatic_stress_disorder_ptsd +
-    autism_spectrum_disorder +
-    mhd.attention_deficit_hyperactivity_disorder +
-    mhd.personality_disorder +
-    Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + time_diff_sign_up_coping,
-  data = dat.retro)
-
-summary(ocir_retro_model1b)
-tidy(ocir_retro_model1b)
-```
-
-# RUBBISH
-
-+++ Everything underneath here is only SCRATCH
-
-```{r RUBBISH 2, fig.height=7, fig.width=5}
-#gad.diff_score_base_prepan_plot /
-#  gad.diff_score_retro_prepan_plot /
-#  gad.diff_score_base_retro_plot +
-#  plot_layout(guides = "collect", heights = c(1,1,1)) +
-#  plot_annotation(tag_levels = "A")
-```
+
+# Regression diagnostic statistics
+gad_prepan_model1a_reg_stats <- model1a.reg.stats(outcome = "gad.diff_score_base_prepan",
+                  data_set = "dat.prepan")
+kable(gad_prepan_model1a_reg_stats)
+gad_prepan_model1a_reg_stats
+```
+
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r gad model1b diff_score prepan}
+# Regression coefficients
+gad_prepan_model1b_estimates <- model1b.estimates(outcome = "gad.diff_score_base_prepan",
+                  data_set = "dat.prepan")
+kable(gad_prepan_model1b_estimates)
+gad_prepan_model1b_estimates
+
+# Regression diagnostic statistics
+gad_prepan_model1b_reg_stats <- model1b.reg.stats(outcome = "gad.diff_score_base_prepan",
+                  data_set = "dat.prepan")
+kable(gad_prepan_model1b_reg_stats)
+gad_prepan_model1b_reg_stats
+```
+
+## Regression: Absolute scores
+### Model 0a: Disorder_hierarchical, Unadjusted
+```{r gad model0a sum_score prepan}
+# Regression coefficients
+gad_prepan_model0a_explan_estimates <- model0a.explan.estimates(outcome = "gad.sum_score_base",
+                         explan_var = "gad.sum_score_prepan",
+                         data_set = "dat.prepan")
+kable(gad_prepan_model0a_explan_estimates)
+gad_prepan_model0a_explan_estimates
+
+# Regression diagnostic statistics
+gad_prepan_model0a_explan_reg_stats <- model0a.explan.reg.stats(outcome = "gad.sum_score_base",
+                         explan_var = "gad.sum_score_prepan",
+                         data_set = "dat.prepan")
+kable(gad_prepan_model0a_explan_reg_stats)
+gad_prepan_model0a_explan_reg_stats
+```
+
+### Model 0b: Overlapping disorders, Unadjusted
+```{r gad model0b sum_score prepan}
+# Regression coefficients
+gad_prepan_model0b_explan_estimates <- model0b.explan.estimates(outcome = "gad.sum_score_base",
+                         explan_var = "gad.sum_score_prepan",
+                         data_set = "dat.prepan")
+kable(gad_prepan_model0b_explan_estimates)
+gad_prepan_model0b_explan_estimates
+
+# Regression diagnostic statistics
+gad_prepan_model0b_explan_reg_stats <- model0b.explan.reg.stats(outcome = "gad.sum_score_base",
+                         explan_var = "gad.sum_score_prepan",
+                         data_set = "dat.prepan")
+kable(gad_prepan_model0b_explan_reg_stats)
+gad_prepan_model0b_explan_reg_stats
+```
+
+### Model 1a: Disorder hierarchical, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r gad model1a sum_score prepan}
+# Regression coefficients
+gad_prepan_model1a_explan_estimates <- model1a.explan.estimates(outcome = "gad.sum_score_base",
+                         explan_var = "gad.sum_score_prepan",
+                         data_set = "dat.prepan")
+kable(gad_prepan_model1a_explan_estimates)
+gad_prepan_model1a_explan_estimates
+
+# Regression diagnostic statistics
+gad_prepan_model1a_explan_reg_stats <- model1a.explan.reg.stats(outcome = "gad.sum_score_base",
+                         explan_var = "gad.sum_score_prepan",
+                         data_set = "dat.prepan")
+kable(gad_prepan_model1a_explan_reg_stats)
+gad_prepan_model1a_explan_reg_stats
+```
+
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r gad model1b sum_score prepan}
+# Regression coefficients
+gad_prepan_model1b_explan_estimates <- model1b.explan.estimates(outcome = "gad.sum_score_base",
+                         explan_var = "gad.sum_score_prepan",
+                         data_set = "dat.prepan")
+kable(gad_prepan_model1b_explan_estimates)
+gad_prepan_model1b_explan_estimates
+
+# Regression diagnostic statistics
+gad_prepan_model1b_explan_reg_stats <- model1b.explan.reg.stats(outcome = "gad.sum_score_base",
+                         explan_var = "gad.sum_score_prepan",
+                         data_set = "dat.prepan")
+kable(gad_prepan_model1b_explan_reg_stats)
+gad_prepan_model1b_explan_reg_stats
+```
+
+# GAD retro
+## Regression: Change scores
+### Model 0a: Disorder_hierarchical, Unadjusted
+```{r gad model0a diff_score retro}
+# Regression coefficients
+gad_retro_model0a_estimates <- model0a.estimates(outcome = "gad.diff_score_base_retro",
+                                                 data_set = "dat.retro")
+kable(gad_retro_model0a_estimates)
+gad_retro_model0a_estimates
+
+# Regression diagnostic statistics
+gad_retro_model0a_reg_stats <- model0a.reg.stats(outcome = "gad.diff_score_base_retro",
+                                                 data_set = "dat.retro")
+kable(gad_retro_model0a_reg_stats)
+gad_retro_model0a_reg_stats
+```
+
+### Model 0b: Overlapping disorders, Unadjusted
+```{r gad model0b diff_score retro}
+# Regression coefficients
+gad_retro_model0b_estimates <- model0b.estimates(outcome = "gad.diff_score_base_retro",
+                                                 data_set = "dat.retro")
+kable(gad_retro_model0b_estimates)
+gad_retro_model0b_estimates
+
+# Regression diagnostic statistics
+gad_retro_model0b_reg_stats <- model0b.reg.stats(outcome = "gad.diff_score_base_retro",
+                                                 data_set = "dat.retro")
+kable(gad_retro_model0b_reg_stats)
+gad_retro_model0b_reg_stats
+```
+
+### Model 1a: Disorder hierarchical, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r gad model1a diff_score retro}
+# Regression coefficients
+gad_retro_model1a_estimates <- model1a.estimates(outcome = "gad.diff_score_base_retro",
+                                                 data_set = "dat.retro")
+kable(gad_retro_model1a_estimates)
+gad_retro_model1a_estimates
+
+# Regression diagnostic statistics
+gad_retro_model1a_reg_stats <- model1a.reg.stats(outcome = "gad.diff_score_base_retro",
+                                                 data_set = "dat.retro")
+kable(gad_retro_model1a_reg_stats)
+gad_retro_model1a_reg_stats
+```
+
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r gad model1b diff_score retro}
+# Regression coefficients
+gad_retro_model1b_estimates <- model1b.estimates(outcome = "gad.diff_score_base_retro",
+                                                 data_set = "dat.retro")
+kable(gad_retro_model1b_estimates)
+gad_retro_model1b_estimates
+
+# Regression diagnostic statistics
+gad_retro_model1b_reg_stats <- model1b.reg.stats(outcome = "gad.diff_score_base_retro",
+                                                 data_set = "dat.retro")
+kable(gad_retro_model1b_reg_stats)
+gad_retro_model1b_reg_stats
+```
+
+## Regression: Absolute scores
+### Model 0a: Disorder_hierarchical, Unadjusted
+```{r gad model0a sum_score retro}
+# Regression coefficients
+gad_retro_model0a_explan_estimates <- model0a.explan.estimates(outcome = "gad.sum_score_base",
+                                                               explan_var = "gad.sum_score_retro",
+                                                               data_set = "dat.retro")
+kable(gad_retro_model0a_explan_estimates)
+gad_retro_model0a_explan_estimates
+
+# Regression diagnostic statistics
+gad_retro_model0a_explan_reg_stats <- model0a.explan.reg.stats(outcome = "gad.sum_score_base",
+                                                               explan_var = "gad.sum_score_retro",
+                                                               data_set = "dat.retro")
+kable(gad_retro_model0a_explan_reg_stats)
+gad_retro_model0a_explan_reg_stats
+```
+
+### Model 0b: Overlapping disorders, Unadjusted
+```{r gad model0b sum_score retro}
+# Regression coefficients
+gad_retro_model0b_explan_estimates <- model0b.explan.estimates(outcome = "gad.sum_score_base",
+                                                               explan_var = "gad.sum_score_retro",
+                                                               data_set = "dat.retro")
+kable(gad_retro_model0b_explan_estimates)
+gad_retro_model0b_explan_estimates
+
+# Regression diagnostic statistics
+gad_retro_model0b_explan_reg_stats <- model0b.explan.reg.stats(outcome = "gad.sum_score_base",
+                                                               explan_var = "gad.sum_score_retro",
+                                                               data_set = "dat.retro")
+kable(gad_retro_model0b_explan_reg_stats)
+gad_retro_model0b_explan_reg_stats
+```
+
+### Model 1a: Disorder hierarchical, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r gad model1a sum_score retro}
+# Regression coefficients
+gad_retro_model1a_explan_estimates <- model1a.explan.estimates(outcome = "gad.sum_score_base",
+                                                               explan_var = "gad.sum_score_retro",
+                                                               data_set = "dat.retro")
+kable(gad_retro_model1a_explan_estimates)
+gad_retro_model1a_explan_estimates
+
+# Regression diagnostic statistics
+gad_retro_model1a_explan_reg_stats <- model1a.explan.reg.stats(outcome = "gad.sum_score_base",
+                                                               explan_var = "gad.sum_score_retro",
+                                                               data_set = "dat.retro")
+kable(gad_retro_model1a_explan_reg_stats)
+gad_retro_model1a_explan_reg_stats
+```
+
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r gad model1b sum_score retro}
+# Regression coefficients
+gad_retro_model1b_explan_estimates <- model1b.explan.estimates(outcome = "gad.sum_score_base",
+                                                               explan_var = "gad.sum_score_retro",
+                                                               data_set = "dat.retro")
+kable(gad_retro_model1b_explan_estimates)
+gad_retro_model1b_explan_estimates
+
+# Regression diagnostic statistics
+gad_retro_model1b_explan_reg_stats <- model1b.explan.reg.stats(outcome = "gad.sum_score_base",
+                                                               explan_var = "gad.sum_score_retro",
+                                                               data_set = "dat.retro")
+kable(gad_retro_model1b_explan_reg_stats)
+gad_retro_model1b_explan_reg_stats
+```

### 2020-09-18 archive/PANCHANGE_analysis_backup.Rmd
deleted all regressions and replaced with short forms due to functions

---
title: "PANCHANGE_analysis_backup"
author: "Christopher Huebel"
date: "18/09/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### CHANGE SCORES

### GAD

```{r GAD prepan Model 0a}
# Model
gad_prepan_model0a <- lm(
  formula = gad.diff_score_base_prepan ~ 
    Disorder_hierarchical,
  data = dat.prepan)

summary(gad_prepan_model0a)

# Regression statistics
gad_prepan_model0a_reg_stats <- glance(gad_prepan_model0a) %>%
  mutate(
    "n" = format(
      round(nobs,
            digits = 0),
      nsmall = 0),
    "R2" = format(
      round(r.squared,
            digits = 2),
      nsmall = 2),
    "adjust. R2" = format(
      round(adj.r.squared,
            digits = 2),
      nsmall = 2),
    "F" = format(
      round(statistic,
            digits = 2),
      nsmall = 2),
    "p value" = case_when(
      p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
      p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
      p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
  )
  ) %>%
  select(
    "n",
    "R2",
    "adjust. R2",
    "F",
    "p value",
    "df"
  )

kable(gad_prepan_model0a_reg_stats)
gad_prepan_model0a_reg_stats

# Estimate summary table
gad_prepan_model0a_estimates <- tidy(gad_prepan_model0a, conf.int = TRUE) %>%
  mutate(
    "Indepent variable" = recode_factor(
      term,
      "(Intercept)" = "Intercept",
      "Disorder_hierarchicalAnxiety disorders" = "Anxiety disorders",
      "Disorder_hierarchicalEating disorders" = "Eating disorders",
      "Disorder_hierarchicalOCDs" = "OCDs",
      "Disorder_hierarchicalPTSD" = "PTSD",
      "Disorder_hierarchicalDepressive disorders" = "Depressive disorders",
      "Disorder_hierarchicalBipolar disorders" = "Bipolar disorders"
    ),
    "Estimate" = format(
      round(estimate,
            digits = 2),
      nsmall = 2),
    "95% CI low" = format(
      round(conf.low,
            digits = 2),
      nsmall = 2),
    "95% CI up" = format(
      round(conf.high,
            digits = 2),
      nsmall = 2),
    "SE" = format(
      round(std.error,
            digits = 2),
      nsmall = 2),
    "z score" = format(
      round(statistic,
            digits = 2),
      nsmall = 2),
    "p value" = case_when(
      p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
      p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
      p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
  )
  ) %>%
  select(
    "Indepent variable",
    "Estimate",
    "95% CI low",
    "95% CI up",
    "SE",
#    "z score",
    "p value"
  )

kable(gad_prepan_model0a_estimates)
gad_prepan_model0a_estimates
```

```{r GAD prepan Model 0b}
gad_prepan_model0b <- lm(
  formula = gad.diff_score_base_prepan ~
    anxiety_disorders +
    depressive_disorders +
    depression_and_anxiety +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder,
  data = dat.prepan)

summary(gad_prepan_model0b)

# Regression statistics
gad_prepan_model0b_reg_stats <- glance(gad_prepan_model0b) %>%
  mutate(
    "n" = format(
      round(nobs,
            digits = 0),
      nsmall = 0),
    "R2" = format(
      round(r.squared,
            digits = 2),
      nsmall = 2),
    "adjust. R2" = format(
      round(adj.r.squared,
            digits = 2),
      nsmall = 2),
    "F" = format(
      round(statistic,
            digits = 2),
      nsmall = 2),
    "p value" = case_when(
      p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
      p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
      p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
  )
  ) %>%
  select(
    "n",
    "R2",
    "adjust. R2",
    "F",
    "p value",
    "df"
  )

kable(gad_prepan_model0b_reg_stats)
gad_prepan_model0b_reg_stats

# Estimate summary table
gad_prepan_model0b_estimates <- tidy(gad_prepan_model0b) %>%
  mutate(
    "Indepent variable" = recode_factor(
      term,
      "(Intercept)" = "Intercept",
      "anxiety_disordersAnxiety disorder" = "Anxiety disorders",
      "depressive_disordersDepressive disorder" = "Depressive disorders",
      "depression_and_anxietyDepressive and anxiety disorder" = "Depressive and anxiety disorder",
      "depression_and_anxietyOnly depressive disorder" = "Only depressive disorder",
      "depression_and_anxietyOnly anxiety disorder" = "Only anxiety disorder",
      "eating_disordersEating disorder" = "Eating disorders",
      "obsessive_compulsive_disordersObsessive compulsive disorder" = "OCDs",
      "psychotic_disordersPsychotic disorder" = "Psychotic disorder",
      "mhd.mania_hypomania_bipolar_or_manicdepressionMania, hypomania, bipolar or manic-depression" = "Bipolar disorder",
      "mhd.posttraumatic_stress_disorder_ptsdPost-traumatic stress disorder (PTSD)" = "PTSD",
      "autism_spectrum_disorderAutism spectrum disorder" = "ASD",
      "mhd.attention_deficit_hyperactivity_disorderAttention deficit or attention deficit and hyperactivity disorder (ADD/ADHD)" = "ADHD",
      "mhd.personality_disorderPersonality disorder" = "Personality disorder"
    ),
    "Estimate" = format(
      round(estimate,
            digits = 2),
      nsmall = 2),
    "SE" = format(
      round(std.error,
            digits = 2),
      nsmall = 2),
    "z score" = format(
      round(statistic,
            digits = 2),
      nsmall = 2),
    "p value" = case_when(
      p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
      p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
      p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
  )
  ) %>%
  select(
    "Indepent variable",
    "Estimate",
    "SE",
#    "z score",
    "p value"
  )

kable(gad_prepan_model0b_estimates)
gad_prepan_model0b_estimates
```

```{r GAD prepan Model 1a}
gad_prepan_model1a <- lm(
  formula = gad.diff_score_base_prepan ~ 
    Disorder_hierarchical + 
    Gender_collapsed + 
    age_category_collapsed + 
    Ethnicity_collapsed + 
    time_diff_sign_up_coping,
  data = dat.prepan)

summary(gad_prepan_model1a)

# Regression statistics
gad_prepan_model1a_reg_stats <- glance(gad_prepan_model1a) %>%
  mutate(
    "n" = format(
      round(nobs,
            digits = 0),
      nsmall = 0),
    "R2" = format(
      round(r.squared,
            digits = 2),
      nsmall = 2),
    "adjust. R2" = format(
      round(adj.r.squared,
            digits = 2),
      nsmall = 2),
    "F" = format(
      round(statistic,
            digits = 2),
      nsmall = 2),
    "p value" = case_when(
      p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
      p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
      p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
    )
  ) %>%
  select(
    "n",
    "R2",
    "adjust. R2",
    "F",
    "p value",
    "df"
  )

kable(gad_prepan_model1a_reg_stats)
gad_prepan_model1a_reg_stats

# Estimate summary table
gad_prepan_model1a_estimates <- tidy(gad_prepan_model1a) %>%
  mutate(
    "Indepent variable" = recode_factor(
      term,
      "(Intercept)" = "Intercept",
      "Disorder_hierarchicalAnxiety disorders" = "Anxiety disorders",
      "Disorder_hierarchicalEating disorders" = "Eating disorders",
      "Disorder_hierarchicalOCDs" = "OCDs",
      "Disorder_hierarchicalPTSD" = "PTSD",
      "Disorder_hierarchicalDepressive disorders" = "Depressive disorders",
      "Disorder_hierarchicalBipolar disorders" = "Bipolar disorders",
      "Gender_collapsedFemale" = "Female",
      "Gender_collapsedNon-binary/Self-defined" = "Non-binary/Self-defined",
      "age_category_collapsed19-25" = "19-25 years",
      "age_category_collapsed26-35" = "26-35 years",
      "age_category_collapsed36-45" = "36-45 years",
      "age_category_collapsed46-55" = "46-55 years",
      "age_category_collapsed56-65" = "56-65 years",
      "age_category_collapsed66-70" = "66-70 years",
      "age_category_collapsed71-75" = "71-75 years",
      "age_category_collapsed76+" = "76+ years",
      "Ethnicity_collapsedMixed or multiple ethnic origins" = "Mixed or multiple ethnic origins",
      "Ethnicity_collapsedAsian or Asian British" = "Asian or Asian British",
      "Ethnicity_collapsedAfrican or African British" = "African or African British",
      "Ethnicity_collapsedOther" = "Other ethnicity",
      "time_diff_sign_up_coping" = "Time difference: prepandemic to COPING"
    ),
    "Estimate" = format(
      round(estimate,
            digits = 2),
      nsmall = 2),
    "SE" = format(
      round(std.error,
            digits = 2),
      nsmall = 2),
    "z score" = format(
      round(statistic,
            digits = 2),
      nsmall = 2),
    "p value" = case_when(
      p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
      p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
      p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
    )
  ) %>%
  select(
    "Indepent variable",
    "Estimate",
    "SE",
    #    "z score",
    "p value"
  )

kable(gad_prepan_model1a_estimates)
gad_prepan_model1a_estimates
```

Model 1b: Overlapping disorders, Adjusted
  Model 0b + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r GAD prepan Model 1b}
gad_prepan_model1b <- lm(
  formula = gad.diff_score_base_prepan ~
    anxiety_disorders +
    depressive_disorders +
    depression_and_anxiety +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder +
    Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + time_diff_sign_up_coping,
  data = dat.prepan)

summary(gad_prepan_model1b)
tidy(gad_prepan_model1b)
```

### PHQ
Model 0a: Disorder_hierarchical, Unadjusted
```{r PHQ prepan Model 0a}
phq_prepan_model0a <- lm(
  formula = phq.diff_score_base_prepan ~ 
    Disorder_hierarchical,
  data = dat.prepan)

summary(phq_prepan_model0a)
tidy(phq_prepan_model0a)
```

Model 0b: Overlapping disorders, Unadjusted
```{r PHQ prepan Model 0b}
phq_prepan_model0b <- lm(
  formula = phq.diff_score_base_prepan ~
    anxiety_disorders +
    depressive_disorders +
    depression_and_anxiety +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder,
  data = dat.prepan)

summary(phq_prepan_model0b)
tidy(phq_prepan_model0b)
```

Model 1a: Disorder hierarchical, Adjusted
  Model 0a + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r PHQ prepan Model 1a}
phq_prepan_model1a <- lm(
  formula = phq.diff_score_base_prepan ~ 
    Disorder_hierarchical + 
    Gender_collapsed + 
    age_category_collapsed + 
    Ethnicity_collapsed + 
    time_diff_sign_up_coping,
  data = dat.prepan)

summary(phq_prepan_model1a)
tidy(phq_prepan_model1a)
```

Model 1b: Overlapping disorders, Adjusted
  Model 0b + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r PHQ prepan Model 1b}
phq_prepan_model1b <- lm(
  formula = phq.diff_score_base_prepan ~
    anxiety_disorders +
    depressive_disorders +
    depression_and_anxiety +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder +
    Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + time_diff_sign_up_coping,
  data = dat.prepan)

summary(phq_prepan_model1b)
tidy(phq_prepan_model1b)
```

### PCL
Model 0a: Disorder_hierarchical, Unadjusted
```{r PCL prepan Model 0a}
pcl_prepan_model0a <- lm(
  formula = pcl.diff_score_base_prepan ~ 
    Disorder_hierarchical,
  data = dat.prepan)

summary(pcl_prepan_model0a)
tidy(pcl_prepan_model0a)
```

Model 0b: Overlapping disorders, Unadjusted
```{r PCL prepan Model 0b}
pcl_prepan_model0b <- lm(
  formula = pcl.diff_score_base_prepan ~
    anxiety_disorders +
    depressive_disorders +
    depression_and_anxiety +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder,
  data = dat.prepan)

summary(pcl_prepan_model0b)
tidy(pcl_prepan_model0b)
```

Model 1a: Disorder hierarchical, Adjusted
  Model 0a + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r PCL prepan Model 1a}
pcl_prepan_model1a <- lm(
  formula = pcl.diff_score_base_prepan ~ 
    Disorder_hierarchical + 
    Gender_collapsed + 
    age_category_collapsed + 
    Ethnicity_collapsed + 
    time_diff_sign_up_coping,
  data = dat.prepan)

summary(pcl_prepan_model1a)
tidy(pcl_prepan_model1a)
```

Model 1b: Overlapping disorders, Adjusted
  Model 0b + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r PCL prepan Model 1b}
pcl_prepan_model1b <- lm(
  formula = pcl.diff_score_base_prepan ~
    anxiety_disorders +
    depressive_disorders +
    depression_and_anxiety +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder +
    Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + time_diff_sign_up_coping,
  data = dat.prepan)

summary(pcl_prepan_model1b)
tidy(pcl_prepan_model1b)
```

### OCIR
Model 0a: Disorder_hierarchical, Unadjusted
```{r OCIR prepan Model 0a}
ocir_prepan_model0a <- lm(
  formula = ocir.diff_score_base_prepan ~ 
    Disorder_hierarchical,
  data = dat.prepan)

summary(ocir_prepan_model0a)
tidy(ocir_prepan_model0a)
```

Model 0b: Overlapping disorders, Unadjusted
```{r OCIR prepan Model 0b}
ocir_prepan_model0b <- lm(
  formula = ocir.diff_score_base_prepan ~
    anxiety_disorders +
    depressive_disorders +
    depression_and_anxiety +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder,
  data = dat.prepan)

summary(ocir_prepan_model0b)
tidy(ocir_prepan_model0b)
```

Model 1a: Disorder hierarchical, Adjusted
  Model 0a + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r OCIR prepan Model 1a}
ocir_prepan_model1a <- lm(
  formula = ocir.diff_score_base_prepan ~ 
    Disorder_hierarchical + 
    Gender_collapsed + 
    age_category_collapsed + 
    Ethnicity_collapsed + 
    time_diff_sign_up_coping,
  data = dat.prepan)

summary(ocir_prepan_model1a)
tidy(ocir_prepan_model1a)
```

Model 1b: Overlapping disorders, Adjusted
  Model 0b + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r OCIR prepan Model 1b}
ocir_prepan_model1b <- lm(
  formula = ocir.diff_score_base_prepan ~
    anxiety_disorders +
    depressive_disorders +
    depression_and_anxiety +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder +
    Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + time_diff_sign_up_coping,
  data = dat.prepan)

summary(ocir_prepan_model1b)
tidy(ocir_prepan_model1b)
```

### PANDEMIC BASELINE CONTROLLING FOR PREPANDEMIC

### GAD
Model 0a: Disorder_hierarchical, Unadjusted
```{r GAD prepan Model absolute values absolute values 0a}
gad_prepan_model0a <- lm(
  formula = gad.sum_score_base ~ gad.sum_score_prepan + 
    Disorder_hierarchical,
  data = dat.prepan)

summary(gad_prepan_model0a)
tidy(gad_prepan_model0a)
```

Model 0b: Overlapping disorders, Unadjusted
```{r GAD prepan Model absolute values 0b}
gad_prepan_model0b <- lm(
  formula = gad.sum_score_base ~ gad.sum_score_prepan +
    anxiety_disorders +
    depressive_disorders +
    depression_and_anxiety +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder,
  data = dat.prepan)

summary(gad_prepan_model0b)
tidy(gad_prepan_model0b)
```

Model 1a: Disorder hierarchical, Adjusted
  Model 0a + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r GAD prepan Model absolute values 1a}
gad_prepan_model1a <- lm(
  formula = gad.sum_score_base ~ gad.sum_score_prepan + 
    Disorder_hierarchical + 
    Gender_collapsed + 
    age_category_collapsed + 
    Ethnicity_collapsed + 
    time_diff_sign_up_coping,
  data = dat.prepan)

summary(gad_prepan_model1a)
tidy(gad_prepan_model1a)
```

Model 1b: Overlapping disorders, Adjusted
  Model 0b + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r GAD prepan Model absolute values 1b}
gad_prepan_model1b <- lm(
  formula = gad.sum_score_base ~ gad.sum_score_prepan +
    anxiety_disorders +
    depressive_disorders +
    depression_and_anxiety +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder +
    Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + time_diff_sign_up_coping,
  data = dat.prepan)

summary(gad_prepan_model1b)
tidy(gad_prepan_model1b)
```

### PHQ
Model 0a: Disorder_hierarchical, Unadjusted
```{r PHQ prepan Model absolute values 0a}
phq_prepan_model0a <- lm(
  formula = phq.sum_score_base ~ phq.sum_score_prepan + 
    Disorder_hierarchical,
  data = dat.prepan)

summary(phq_prepan_model0a)
tidy(phq_prepan_model0a)
```

Model 0b: Overlapping disorders, Unadjusted
```{r PHQ prepan Model absolute values 0b}
phq_prepan_model0b <- lm(
  formula = phq.sum_score_base ~ phq.sum_score_prepan +
    anxiety_disorders +
    depressive_disorders +
    depression_and_anxiety +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder,
  data = dat.prepan)

summary(phq_prepan_model0b)
tidy(phq_prepan_model0b)
```

Model 1a: Disorder hierarchical, Adjusted
  Model 0a + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r PHQ prepan Model absolute values 1a}
phq_prepan_model1a <- lm(
  formula = phq.sum_score_base ~ phq.sum_score_prepan + 
    Disorder_hierarchical + 
    Gender_collapsed + 
    age_category_collapsed + 
    Ethnicity_collapsed + 
    time_diff_sign_up_coping,
  data = dat.prepan)

summary(phq_prepan_model1a)
tidy(phq_prepan_model1a)
```

Model 1b: Overlapping disorders, Adjusted
  Model 0b + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r PHQ prepan Model absolute values 1b}
phq_prepan_model1b <- lm(
  formula = phq.sum_score_base ~ phq.sum_score_prepan +
    anxiety_disorders +
    depressive_disorders +
    depression_and_anxiety +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder +
    Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + time_diff_sign_up_coping,
  data = dat.prepan)

summary(phq_prepan_model1b)
tidy(phq_prepan_model1b)
```

### PCL
Model 0a: Disorder_hierarchical, Unadjusted
```{r PCL prepan Model absolute values 0a}
pcl_prepan_model0a <- lm(
  formula = pcl.sum_score_base ~ pcl.sum_score_prepan + 
    Disorder_hierarchical,
  data = dat.prepan)

summary(pcl_prepan_model0a)
tidy(pcl_prepan_model0a)
```

Model 0b: Overlapping disorders, Unadjusted
```{r PCL prepan Model absolute values 0b}
pcl_prepan_model0b <- lm(
  formula = pcl.sum_score_base ~ pcl.sum_score_prepan +
    anxiety_disorders +
    depressive_disorders +
    depression_and_anxiety +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder,
  data = dat.prepan)

summary(pcl_prepan_model0b)
tidy(pcl_prepan_model0b)
```

Model 1a: Disorder hierarchical, Adjusted
  Model 0a + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r PCL prepan Model absolute values 1a}
pcl_prepan_model1a <- lm(
  formula = pcl.sum_score_base ~ pcl.sum_score_prepan + 
    Disorder_hierarchical + 
    Gender_collapsed + 
    age_category_collapsed + 
    Ethnicity_collapsed + 
    time_diff_sign_up_coping,
  data = dat.prepan)

summary(pcl_prepan_model1a)
tidy(pcl_prepan_model1a)
```

Model 1b: Overlapping disorders, Adjusted
  Model 0b + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r PCL prepan Model absolute values 1b}
pcl_prepan_model1b <- lm(
  formula = pcl.sum_score_base ~ pcl.sum_score_prepan +
    anxiety_disorders +
    depressive_disorders +
    depression_and_anxiety +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder +
    Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + time_diff_sign_up_coping,
  data = dat.prepan)

summary(pcl_prepan_model1b)
tidy(pcl_prepan_model1b)
```

### OCIR
Model 0a: Disorder_hierarchical, Unadjusted
```{r OCIR prepan Model absolute values 0a}
ocir_prepan_model0a <- lm(
  formula = ocir.sum_score_base ~ ocir.sum_score_prepan + 
    Disorder_hierarchical,
  data = dat.prepan)

summary(ocir_prepan_model0a)
tidy(ocir_prepan_model0a)
```

Model 0b: Overlapping disorders, Unadjusted
```{r OCIR prepan Model absolute values 0b}
ocir_prepan_model0b <- lm(
  formula = ocir.sum_score_base ~ ocir.sum_score_prepan +
    anxiety_disorders +
    depressive_disorders +
    depression_and_anxiety +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder,
  data = dat.prepan)

summary(ocir_prepan_model0b)
tidy(ocir_prepan_model0b)
```

Model 1a: Disorder hierarchical, Adjusted
  Model 0a + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r OCIR prepan Model absolute values 1a}
ocir_prepan_model1a <- lm(
  formula = ocir.sum_score_base ~ ocir.sum_score_prepan + 
    Disorder_hierarchical + 
    Gender_collapsed + 
    age_category_collapsed + 
    Ethnicity_collapsed + 
    time_diff_sign_up_coping,
  data = dat.prepan)

summary(ocir_prepan_model1a)
tidy(ocir_prepan_model1a)
```

Model 1b: Overlapping disorders, Adjusted
  Model 0b + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r OCIR prepan Model absolute values 1b}
ocir_prepan_model1b <- lm(
  formula = ocir.sum_score_base ~ ocir.sum_score_prepan +
    anxiety_disorders +
    depressive_disorders +
    depression_and_anxiety +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder +
    Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + time_diff_sign_up_coping,
  data = dat.prepan)

summary(ocir_prepan_model1b)
tidy(ocir_prepan_model1b)
```

## Retro-baseline change

### CHANGE SCORES

### GAD
Model 0a: Disorder_hierarchical, Unadjusted
```{r GAD retro Model 0a}
gad_retro_model0a <- lm(
  formula = gad.diff_score_base_retro ~ 
    Disorder_hierarchical,
  data = dat.retro)

summary(gad_retro_model0a)
tidy(gad_retro_model0a)
```

Model 0b: Overlapping disorders, Unadjusted
```{r GAD retro Model 0b}
gad_retro_model0b <- lm(
  formula = gad.diff_score_base_retro ~
    anxiety_disorders +
    depressive_disorders +
    depression_and_anxiety +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder,
  data = dat.retro)

summary(gad_retro_model0b)
tidy(gad_retro_model0b)
```

Model 1a: Disorder hierarchical, Adjusted
  Model 0a + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r GAD retro Model 1a}
gad_retro_model1a <- lm(
  formula = gad.diff_score_base_retro ~ 
    Disorder_hierarchical + 
    Gender_collapsed + 
    age_category_collapsed + 
    Ethnicity_collapsed + 
    time_diff_sign_up_coping,
  data = dat.retro)

summary(gad_retro_model1a)
tidy(gad_retro_model1a)
```

Model 1b: Overlapping disorders, Adjusted
  Model 0b + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r GAD retro Model 1b}
gad_retro_model1b <- lm(
  formula = gad.diff_score_base_retro ~
    anxiety_disorders +
    depressive_disorders +
    depression_and_anxiety +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder +
    Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + time_diff_sign_up_coping,
  data = dat.retro)

summary(gad_retro_model1b)
tidy(gad_retro_model1b)
```

### PHQ
Model 0a: Disorder_hierarchical, Unadjusted
```{r PHQ retro Model 0a}
phq_retro_model0a <- lm(
  formula = phq.diff_score_base_retro ~ 
    Disorder_hierarchical,
  data = dat.retro)

summary(phq_retro_model0a)
tidy(phq_retro_model0a)
```

Model 0b: Overlapping disorders, Unadjusted
```{r PHQ retro Model 0b}
phq_retro_model0b <- lm(
  formula = phq.diff_score_base_retro ~
    anxiety_disorders +
    depressive_disorders +
    depression_and_anxiety +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder,
  data = dat.retro)

summary(phq_retro_model0b)
tidy(phq_retro_model0b)
```

Model 1a: Disorder hierarchical, Adjusted
  Model 0a + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r PHQ retro Model 1a}
phq_retro_model1a <- lm(
  formula = phq.diff_score_base_retro ~ 
    Disorder_hierarchical + 
    Gender_collapsed + 
    age_category_collapsed + 
    Ethnicity_collapsed + 
    time_diff_sign_up_coping,
  data = dat.retro)

summary(phq_retro_model1a)
tidy(phq_retro_model1a)
```

Model 1b: Overlapping disorders, Adjusted
  Model 0b + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r PHQ retro Model 1b}
phq_retro_model1b <- lm(
  formula = phq.diff_score_base_retro ~
    anxiety_disorders +
    depressive_disorders +
    depression_and_anxiety +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder +
    Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + time_diff_sign_up_coping,
  data = dat.retro)

summary(phq_retro_model1b)
tidy(phq_retro_model1b)
```

### PCL

++MD: Not sure if this is how we want to run the PCL regression - the outcome variable I've included is "How many PCL items the participants report are related to the pandemic", but I think we might want a more nuanced approach than this.

```{r recode PCL retro variable as numeric}
dat.retro <- dat.retro %>% 
  mutate(
    pcl.sum_score_retro = 
      as.numeric(pcl.sum_score_retro_raw)
  )
```

Model 0a: Disorder_hierarchical, Unadjusted
```{r PCL retro Model 0a}
pcl_retro_model0a <- lm(
  formula = pcl.sum_score_retro ~ 
    Disorder_hierarchical,
  data = dat.retro)

summary(pcl_retro_model0a)
tidy(pcl_retro_model0a)
```

Model 0b: Overlapping disorders, Unadjusted
```{r PCL retro Model 0b}
pcl_retro_model0b <- lm(
  formula = pcl.sum_score_retro ~
    anxiety_disorders +
    depressive_disorders +
    depression_and_anxiety +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder,
  data = dat.retro)

summary(pcl_retro_model0b)
tidy(pcl_retro_model0b)
```

Model 1a: Disorder hierarchical, Adjusted
  Model 0a + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r PCL retro Model 1a}
pcl_retro_model1a <- lm(
  formula = pcl.sum_score_retro ~ 
    Disorder_hierarchical + 
    Gender_collapsed + 
    age_category_collapsed + 
    Ethnicity_collapsed + 
    time_diff_sign_up_coping,
  data = dat.retro)

summary(pcl_retro_model1a)
tidy(pcl_retro_model1a)
```

Model 1b: Overlapping disorders, Adjusted
  Model 0b + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r PCL retro Model 1b}
pcl_retro_model1b <- lm(
  formula = pcl.sum_score_retro ~
    anxiety_disorders +
    depressive_disorders +
    depression_and_anxiety +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder +
    Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + time_diff_sign_up_coping,
  data = dat.retro)

summary(pcl_retro_model1b)
tidy(pcl_retro_model1b)
```

### OCIR
Model 0a: Disorder_hierarchical, Unadjusted
```{r OCIR retro Model 0a}
ocir_retro_model0a <- lm(
  formula = ocir.diff_score_base_retro ~ 
    Disorder_hierarchical,
  data = dat.retro)

summary(ocir_retro_model0a)
tidy(ocir_retro_model0a)
```

Model 0b: Overlapping disorders, Unadjusted
```{r OCIR retro Model 0b}
ocir_retro_model0b <- lm(
  formula = ocir.diff_score_base_retro ~
    anxiety_disorders +
    depressive_disorders +
    depression_and_anxiety +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder,
  data = dat.retro)

summary(ocir_retro_model0b)
tidy(ocir_retro_model0b)
```

Model 1a: Disorder hierarchical, Adjusted
  Model 0a + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r OCIR retro Model 1a}
ocir_retro_model1a <- lm(
  formula = ocir.diff_score_base_retro ~ 
    Disorder_hierarchical + 
    Gender_collapsed + 
    age_category_collapsed + 
    Ethnicity_collapsed + 
    time_diff_sign_up_coping,
  data = dat.retro)

summary(ocir_retro_model1a)
tidy(ocir_retro_model1a)
```

Model 1b: Overlapping disorders, Adjusted
  Model 0b + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r OCIR retro Model 1b}
ocir_retro_model1b <- lm(
  formula = ocir.diff_score_base_retro ~
    anxiety_disorders +
    depressive_disorders +
    depression_and_anxiety +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder +
    Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + time_diff_sign_up_coping,
  data = dat.retro)

summary(ocir_retro_model1b)
tidy(ocir_retro_model1b)
```

### PANDEMIC BASELINE CONTROLLING FOR RETROSPECTIVE

### GAD
Model 0a: Disorder_hierarchical, Unadjusted
```{r GAD retro Model absolute values 0a}
gad_retro_model0a <- lm(
  formula = gad.sum_score_base ~ gad.sum_score_retro + 
    Disorder_hierarchical,
  data = dat.retro)

summary(gad_retro_model0a)
tidy(gad_retro_model0a)
```

Model 0b: Overlapping disorders, Unadjusted
```{r GAD retro Model absolute values 0b}
gad_retro_model0b <- lm(
  formula = gad.sum_score_base ~ gad.sum_score_retro +
    anxiety_disorders +
    depressive_disorders +
    depression_and_anxiety +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder,
  data = dat.retro)

summary(gad_retro_model0b)
tidy(gad_retro_model0b)
```

Model 1a: Disorder hierarchical, Adjusted
  Model 0a + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r GAD retro Model absolute values 1a}
gad_retro_model1a <- lm(
  formula = gad.sum_score_base ~ gad.sum_score_retro + 
    Disorder_hierarchical + 
    Gender_collapsed + 
    age_category_collapsed + 
    Ethnicity_collapsed + 
    time_diff_sign_up_coping,
  data = dat.retro)

summary(gad_retro_model1a)
tidy(gad_retro_model1a)
```

Model 1b: Overlapping disorders, Adjusted
  Model 0b + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r GAD retro Model absolute values 1b}
gad_retro_model1b <- lm(
  formula = gad.sum_score_base ~ gad.sum_score_retro +
    anxiety_disorders +
    depressive_disorders +
    depression_and_anxiety +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder +
    Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + time_diff_sign_up_coping,
  data = dat.retro)

summary(gad_retro_model1b)
tidy(gad_retro_model1b)
```

### PHQ
Model 0a: Disorder_hierarchical, Unadjusted
```{r PHQ retro Model absolute values 0a}
phq_retro_model0a <- lm(
  formula = phq.sum_score_base ~ phq.sum_score_retro + 
    Disorder_hierarchical,
  data = dat.retro)

summary(phq_retro_model0a)
tidy(phq_retro_model0a)
```

Model 0b: Overlapping disorders, Unadjusted
```{r PHQ retro Model absolute values 0b}
phq_retro_model0b <- lm(
  formula = phq.sum_score_base ~ phq.sum_score_retro +
    anxiety_disorders +
    depressive_disorders +
    depression_and_anxiety +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder,
  data = dat.retro)

summary(phq_retro_model0b)
tidy(phq_retro_model0b)
```

Model 1a: Disorder hierarchical, Adjusted
  Model 0a + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r PHQ retro Model absolute values 1a}
phq_retro_model1a <- lm(
  formula = phq.sum_score_base ~ phq.sum_score_retro + 
    Disorder_hierarchical + 
    Gender_collapsed + 
    age_category_collapsed + 
    Ethnicity_collapsed + 
    time_diff_sign_up_coping,
  data = dat.retro)

summary(phq_retro_model1a)
tidy(phq_retro_model1a)
```

Model 1b: Overlapping disorders, Adjusted
  Model 0b + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r PHQ retro Model absolute values 1b}
phq_retro_model1b <- lm(
  formula = phq.sum_score_base ~ phq.sum_score_retro +
    anxiety_disorders +
    depressive_disorders +
    depression_and_anxiety +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder +
    Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + time_diff_sign_up_coping,
  data = dat.retro)

summary(phq_retro_model1b)
tidy(phq_retro_model1b)
```

### PCL
Model 0a: Disorder_hierarchical, Unadjusted
```{r PCL retro Model absolute values 0a}
pcl_retro_model0a <- lm(
  formula = pcl.sum_score_base ~ pcl.sum_score_retro + 
    Disorder_hierarchical,
  data = dat.retro)

summary(pcl_retro_model0a)
tidy(pcl_retro_model0a)
```

Model 0b: Overlapping disorders, Unadjusted
```{r PCL retro Model absolute values 0b}
pcl_retro_model0b <- lm(
  formula = pcl.sum_score_base ~ pcl.sum_score_retro +
    anxiety_disorders +
    depressive_disorders +
    depression_and_anxiety +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder,
  data = dat.retro)

summary(pcl_retro_model0b)
tidy(pcl_retro_model0b)
```

Model 1a: Disorder hierarchical, Adjusted
  Model 0a + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r PCL retro Model absolute values 1a}
pcl_retro_model1a <- lm(
  formula = pcl.sum_score_base ~ pcl.sum_score_retro + 
    Disorder_hierarchical + 
    Gender_collapsed + 
    age_category_collapsed + 
    Ethnicity_collapsed + 
    time_diff_sign_up_coping,
  data = dat.retro)

summary(pcl_retro_model1a)
tidy(pcl_retro_model1a)
```

Model 1b: Overlapping disorders, Adjusted
  Model 0b + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r PCL retro Model absolute values 1b}
pcl_retro_model1b <- lm(
  formula = pcl.sum_score_base ~ pcl.sum_score_retro +
    anxiety_disorders +
    depressive_disorders +
    depression_and_anxiety +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder +
    Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + time_diff_sign_up_coping,
  data = dat.retro)

summary(pcl_retro_model1b)
tidy(pcl_retro_model1b)
```

### OCIR
Model 0a: Disorder_hierarchical, Unadjusted
```{r OCIR retro Model absolute values 0a}
ocir_retro_model0a <- lm(
  formula = ocir.sum_score_base ~ ocir.sum_score_retro + 
    Disorder_hierarchical,
  data = dat.retro)

summary(ocir_retro_model0a)
tidy(ocir_retro_model0a)
```

Model 0b: Overlapping disorders, Unadjusted
```{r OCIR retro Model absolute values 0b}
ocir_retro_model0b <- lm(
  formula = ocir.sum_score_base ~ ocir.sum_score_retro +
    anxiety_disorders +
    depressive_disorders +
    depression_and_anxiety +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder,
  data = dat.retro)

summary(ocir_retro_model0b)
tidy(ocir_retro_model0b)
```

Model 1a: Disorder hierarchical, Adjusted
  Model 0a + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r OCIR retro Model absolute values 1a}
ocir_retro_model1a <- lm(
  formula = ocir.sum_score_base ~ ocir.sum_score_retro + 
    Disorder_hierarchical + 
    Gender_collapsed + 
    age_category_collapsed + 
    Ethnicity_collapsed + 
    time_diff_sign_up_coping,
  data = dat.retro)

summary(ocir_retro_model1a)
tidy(ocir_retro_model1a)
```

Model 1b: Overlapping disorders, Adjusted
  Model 0b + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r OCIR retro Model absolute values 1b}
ocir_retro_model1b <- lm(
  formula = ocir.sum_score_base ~ ocir.sum_score_retro +
    anxiety_disorders +
    depressive_disorders +
    depression_and_anxiety +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder +
    Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + time_diff_sign_up_coping,
  data = dat.retro)

summary(ocir_retro_model1b)
tidy(ocir_retro_model1b)
```

# RUBBISH

+++ Everything underneath here is only SCRATCH

```{r RUBBISH 2, fig.height=7, fig.width=5}
#gad.diff_score_base_prepan_plot /
#  gad.diff_score_retro_prepan_plot /
#  gad.diff_score_base_retro_plot +
#  plot_layout(guides = "collect", heights = c(1,1,1)) +
#  plot_annotation(tag_levels = "A")
```

### 2020-09-18 PANCHANGE_analysis.Rmd
deleted the pcl retro regression because it does not exist

@@
 Calculate the total GLAD, COPING, RAMP baseline 
-## pcl
+## PCL
 
@@
 
+kable(pcl.percentages.summary)
 pcl.percentages.summary
@@
 Retro-baseline analyses
-++CH: need to discuss exclusion criteria
-Exclude individuals with NA for MHD, age, gender
-
-```{r Exclusion criteria}
-
-```
-
-```{r exclusion criteria for retro-baseline analysis}
+
+```{r subsample for retro-baseline analysis}
 dat.retro <- dat %>%
@@
 
-++CH: exclusion criteria need double checking
-```{r exclusion criteria for prepan-baseline analysis}
+```{r subsample for prepan-baseline analysis}
 dat.prepan <- dat %>%
@@
 ```
+
+# PHQ prepan
+## Regression: Change scores
+### Model 0a: Disorder_hierarchical, Unadjusted
+```{r phq model0a diff_score prepan}
+# Regression coefficients
+phq_prepan_model0a_estimates <- model0a.estimates(outcome = "phq.diff_score_base_prepan",
+                  data_set = "dat.prepan")
+kable(phq_prepan_model0a_estimates)
+phq_prepan_model0a_estimates
+
+# Regression diagnostic statistics
+phq_prepan_model0a_reg_stats <- model0a.reg.stats(outcome = "phq.diff_score_base_prepan",
+                  data_set = "dat.prepan")
+kable(phq_prepan_model0a_reg_stats)
+phq_prepan_model0a_reg_stats
+```
+
+### Model 0b: Overlapping disorders, Unadjusted
+```{r phq model0b diff_score prepan}
+# Regression coefficients
+phq_prepan_model0b_estimates <- model0b.estimates(outcome = "phq.diff_score_base_prepan",
+                  data_set = "dat.prepan")
+kable(phq_prepan_model0b_estimates)
+phq_prepan_model0b_estimates
+
+# Regression diagnostic statistics
+phq_prepan_model0b_reg_stats <- model0b.reg.stats(outcome = "phq.diff_score_base_prepan",
+                  data_set = "dat.prepan")
+kable(phq_prepan_model0b_reg_stats)
+phq_prepan_model0b_reg_stats
+```
+
+### Model 1a: Disorder hierarchical, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r phq model1a diff_score prepan}
+# Regression coefficients
+phq_prepan_model1a_estimates <- model1a.estimates(outcome = "phq.diff_score_base_prepan",
+                  data_set = "dat.prepan")
+kable(phq_prepan_model1a_estimates)
+phq_prepan_model1a_estimates
+
+# Regression diagnostic statistics
+phq_prepan_model1a_reg_stats <- model1a.reg.stats(outcome = "phq.diff_score_base_prepan",
+                  data_set = "dat.prepan")
+kable(phq_prepan_model1a_reg_stats)
+phq_prepan_model1a_reg_stats
+```
+
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r phq model1b diff_score prepan}
+# Regression coefficients
+phq_prepan_model1b_estimates <- model1b.estimates(outcome = "phq.diff_score_base_prepan",
+                  data_set = "dat.prepan")
+kable(phq_prepan_model1b_estimates)
+phq_prepan_model1b_estimates
+
+# Regression diagnostic statistics
+phq_prepan_model1b_reg_stats <- model1b.reg.stats(outcome = "phq.diff_score_base_prepan",
+                  data_set = "dat.prepan")
+kable(phq_prepan_model1b_reg_stats)
+phq_prepan_model1b_reg_stats
+```
+
+## Regression: Absolute scores
+### Model 0a: Disorder_hierarchical, Unadjusted
+```{r phq model0a sum_score prepan}
+# Regression coefficients
+phq_prepan_model0a_explan_estimates <- model0a.explan.estimates(outcome = "phq.sum_score_base",
+                         explan_var = "phq.sum_score_prepan",
+                         data_set = "dat.prepan")
+kable(phq_prepan_model0a_explan_estimates)
+phq_prepan_model0a_explan_estimates
+
+# Regression diagnostic statistics
+phq_prepan_model0a_explan_reg_stats <- model0a.explan.reg.stats(outcome = "phq.sum_score_base",
+                         explan_var = "phq.sum_score_prepan",
+                         data_set = "dat.prepan")
+kable(phq_prepan_model0a_explan_reg_stats)
+phq_prepan_model0a_explan_reg_stats
+```
+
+### Model 0b: Overlapping disorders, Unadjusted
+```{r phq model0b sum_score prepan}
+# Regression coefficients
+phq_prepan_model0b_explan_estimates <- model0b.explan.estimates(outcome = "phq.sum_score_base",
+                         explan_var = "phq.sum_score_prepan",
+                         data_set = "dat.prepan")
+kable(phq_prepan_model0b_explan_estimates)
+phq_prepan_model0b_explan_estimates
+
+# Regression diagnostic statistics
+phq_prepan_model0b_explan_reg_stats <- model0b.explan.reg.stats(outcome = "phq.sum_score_base",
+                         explan_var = "phq.sum_score_prepan",
+                         data_set = "dat.prepan")
+kable(phq_prepan_model0b_explan_reg_stats)
+phq_prepan_model0b_explan_reg_stats
+```
+
+### Model 1a: Disorder hierarchical, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r phq model1a sum_score prepan}
+# Regression coefficients
+phq_prepan_model1a_explan_estimates <- model1a.explan.estimates(outcome = "phq.sum_score_base",
+                         explan_var = "phq.sum_score_prepan",
+                         data_set = "dat.prepan")
+kable(phq_prepan_model1a_explan_estimates)
+phq_prepan_model1a_explan_estimates
+
+# Regression diagnostic statistics
+phq_prepan_model1a_explan_reg_stats <- model1a.explan.reg.stats(outcome = "phq.sum_score_base",
+                         explan_var = "phq.sum_score_prepan",
+                         data_set = "dat.prepan")
+kable(phq_prepan_model1a_explan_reg_stats)
+phq_prepan_model1a_explan_reg_stats
+```
+
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r phq model1b sum_score prepan}
+# Regression coefficients
+phq_prepan_model1b_explan_estimates <- model1b.explan.estimates(outcome = "phq.sum_score_base",
+                         explan_var = "phq.sum_score_prepan",
+                         data_set = "dat.prepan")
+kable(phq_prepan_model1b_explan_estimates)
+phq_prepan_model1b_explan_estimates
+
+# Regression diagnostic statistics
+phq_prepan_model1b_explan_reg_stats <- model1b.explan.reg.stats(outcome = "phq.sum_score_base",
+                         explan_var = "phq.sum_score_prepan",
+                         data_set = "dat.prepan")
+kable(phq_prepan_model1b_explan_reg_stats)
+phq_prepan_model1b_explan_reg_stats
+```
+
+# PHQ retro
+## Regression: Change scores
+### Model 0a: Disorder_hierarchical, Unadjusted
+```{r phq model0a diff_score retro}
+# Regression coefficients
+phq_retro_model0a_estimates <- model0a.estimates(outcome = "phq.diff_score_base_retro",
+                                                 data_set = "dat.retro")
+kable(phq_retro_model0a_estimates)
+phq_retro_model0a_estimates
+
+# Regression diagnostic statistics
+phq_retro_model0a_reg_stats <- model0a.reg.stats(outcome = "phq.diff_score_base_retro",
+                                                 data_set = "dat.retro")
+kable(phq_retro_model0a_reg_stats)
+phq_retro_model0a_reg_stats
+```
+
+### Model 0b: Overlapping disorders, Unadjusted
+```{r phq model0b diff_score retro}
+# Regression coefficients
+phq_retro_model0b_estimates <- model0b.estimates(outcome = "phq.diff_score_base_retro",
+                                                 data_set = "dat.retro")
+kable(phq_retro_model0b_estimates)
+phq_retro_model0b_estimates
+
+# Regression diagnostic statistics
+phq_retro_model0b_reg_stats <- model0b.reg.stats(outcome = "phq.diff_score_base_retro",
+                                                 data_set = "dat.retro")
+kable(phq_retro_model0b_reg_stats)
+phq_retro_model0b_reg_stats
+```
+
+### Model 1a: Disorder hierarchical, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r phq model1a diff_score retro}
+# Regression coefficients
+phq_retro_model1a_estimates <- model1a.estimates(outcome = "phq.diff_score_base_retro",
+                                                 data_set = "dat.retro")
+kable(phq_retro_model1a_estimates)
+phq_retro_model1a_estimates
+
+# Regression diagnostic statistics
+phq_retro_model1a_reg_stats <- model1a.reg.stats(outcome = "phq.diff_score_base_retro",
+                                                 data_set = "dat.retro")
+kable(phq_retro_model1a_reg_stats)
+phq_retro_model1a_reg_stats
+```
+
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r phq model1b diff_score retro}
+# Regression coefficients
+phq_retro_model1b_estimates <- model1b.estimates(outcome = "phq.diff_score_base_retro",
+                                                 data_set = "dat.retro")
+kable(phq_retro_model1b_estimates)
+phq_retro_model1b_estimates
+
+# Regression diagnostic statistics
+phq_retro_model1b_reg_stats <- model1b.reg.stats(outcome = "phq.diff_score_base_retro",
+                                                 data_set = "dat.retro")
+kable(phq_retro_model1b_reg_stats)
+phq_retro_model1b_reg_stats
+```
+
+## Regression: Absolute scores
+### Model 0a: Disorder_hierarchical, Unadjusted
+```{r phq model0a sum_score retro}
+# Regression coefficients
+phq_retro_model0a_explan_estimates <- model0a.explan.estimates(outcome = "phq.sum_score_base",
+                                                               explan_var = "phq.sum_score_retro",
+                                                               data_set = "dat.retro")
+kable(phq_retro_model0a_explan_estimates)
+phq_retro_model0a_explan_estimates
+
+# Regression diagnostic statistics
+phq_retro_model0a_explan_reg_stats <- model0a.explan.reg.stats(outcome = "phq.sum_score_base",
+                                                               explan_var = "phq.sum_score_retro",
+                                                               data_set = "dat.retro")
+kable(phq_retro_model0a_explan_reg_stats)
+phq_retro_model0a_explan_reg_stats
+```
+
+### Model 0b: Overlapping disorders, Unadjusted
+```{r phq model0b sum_score retro}
+# Regression coefficients
+phq_retro_model0b_explan_estimates <- model0b.explan.estimates(outcome = "phq.sum_score_base",
+                                                               explan_var = "phq.sum_score_retro",
+                                                               data_set = "dat.retro")
+kable(phq_retro_model0b_explan_estimates)
+phq_retro_model0b_explan_estimates
+
+# Regression diagnostic statistics
+phq_retro_model0b_explan_reg_stats <- model0b.explan.reg.stats(outcome = "phq.sum_score_base",
+                                                               explan_var = "phq.sum_score_retro",
+                                                               data_set = "dat.retro")
+kable(phq_retro_model0b_explan_reg_stats)
+phq_retro_model0b_explan_reg_stats
+```
+
+### Model 1a: Disorder hierarchical, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r phq model1a sum_score retro}
+# Regression coefficients
+phq_retro_model1a_explan_estimates <- model1a.explan.estimates(outcome = "phq.sum_score_base",
+                                                               explan_var = "phq.sum_score_retro",
+                                                               data_set = "dat.retro")
+kable(phq_retro_model1a_explan_estimates)
+phq_retro_model1a_explan_estimates
+
+# Regression diagnostic statistics
+phq_retro_model1a_explan_reg_stats <- model1a.explan.reg.stats(outcome = "phq.sum_score_base",
+                                                               explan_var = "phq.sum_score_retro",
+                                                               data_set = "dat.retro")
+kable(phq_retro_model1a_explan_reg_stats)
+phq_retro_model1a_explan_reg_stats
+```
+
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r phq model1b sum_score retro}
+# Regression coefficients
+phq_retro_model1b_explan_estimates <- model1b.explan.estimates(outcome = "phq.sum_score_base",
+                                                               explan_var = "phq.sum_score_retro",
+                                                               data_set = "dat.retro")
+kable(phq_retro_model1b_explan_estimates)
+phq_retro_model1b_explan_estimates
+
+# Regression diagnostic statistics
+phq_retro_model1b_explan_reg_stats <- model1b.explan.reg.stats(outcome = "phq.sum_score_base",
+                                                               explan_var = "phq.sum_score_retro",
+                                                               data_set = "dat.retro")
+kable(phq_retro_model1b_explan_reg_stats)
+phq_retro_model1b_explan_reg_stats
+```
+
+# OCIR prepan
+## Regression: Change scores
+### Model 0a: Disorder_hierarchical, Unadjusted
+```{r ocir model0a diff_score prepan}
+# Regression coefficients
+ocir_prepan_model0a_estimates <- model0a.estimates(outcome = "ocir.diff_score_base_prepan",
+                  data_set = "dat.prepan")
+kable(ocir_prepan_model0a_estimates)
+ocir_prepan_model0a_estimates
+
+# Regression diagnostic statistics
+ocir_prepan_model0a_reg_stats <- model0a.reg.stats(outcome = "ocir.diff_score_base_prepan",
+                  data_set = "dat.prepan")
+kable(ocir_prepan_model0a_reg_stats)
+ocir_prepan_model0a_reg_stats
+```
+
+### Model 0b: Overlapping disorders, Unadjusted
+```{r ocir model0b diff_score prepan}
+# Regression coefficients
+ocir_prepan_model0b_estimates <- model0b.estimates(outcome = "ocir.diff_score_base_prepan",
+                  data_set = "dat.prepan")
+kable(ocir_prepan_model0b_estimates)
+ocir_prepan_model0b_estimates
+
+# Regression diagnostic statistics
+ocir_prepan_model0b_reg_stats <- model0b.reg.stats(outcome = "ocir.diff_score_base_prepan",
+                  data_set = "dat.prepan")
+kable(ocir_prepan_model0b_reg_stats)
+ocir_prepan_model0b_reg_stats
+```
+
+### Model 1a: Disorder hierarchical, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r ocir model1a diff_score prepan}
+# Regression coefficients
+ocir_prepan_model1a_estimates <- model1a.estimates(outcome = "ocir.diff_score_base_prepan",
+                  data_set = "dat.prepan")
+kable(ocir_prepan_model1a_estimates)
+ocir_prepan_model1a_estimates
+
+# Regression diagnostic statistics
+ocir_prepan_model1a_reg_stats <- model1a.reg.stats(outcome = "ocir.diff_score_base_prepan",
+                  data_set = "dat.prepan")
+kable(ocir_prepan_model1a_reg_stats)
+ocir_prepan_model1a_reg_stats
+```
+
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r ocir model1b diff_score prepan}
+# Regression coefficients
+ocir_prepan_model1b_estimates <- model1b.estimates(outcome = "ocir.diff_score_base_prepan",
+                  data_set = "dat.prepan")
+kable(ocir_prepan_model1b_estimates)
+ocir_prepan_model1b_estimates
+
+# Regression diagnostic statistics
+ocir_prepan_model1b_reg_stats <- model1b.reg.stats(outcome = "ocir.diff_score_base_prepan",
+                  data_set = "dat.prepan")
+kable(ocir_prepan_model1b_reg_stats)
+ocir_prepan_model1b_reg_stats
+```
+
+## Regression: Absolute scores
+### Model 0a: Disorder_hierarchical, Unadjusted
+```{r ocir model0a sum_score prepan}
+# Regression coefficients
+ocir_prepan_model0a_explan_estimates <- model0a.explan.estimates(outcome = "ocir.sum_score_base",
+                         explan_var = "ocir.sum_score_prepan",
+                         data_set = "dat.prepan")
+kable(ocir_prepan_model0a_explan_estimates)
+ocir_prepan_model0a_explan_estimates
+
+# Regression diagnostic statistics
+ocir_prepan_model0a_explan_reg_stats <- model0a.explan.reg.stats(outcome = "ocir.sum_score_base",
+                         explan_var = "ocir.sum_score_prepan",
+                         data_set = "dat.prepan")
+kable(ocir_prepan_model0a_explan_reg_stats)
+ocir_prepan_model0a_explan_reg_stats
+```
+
+### Model 0b: Overlapping disorders, Unadjusted
+```{r ocir model0b sum_score prepan}
+# Regression coefficients
+ocir_prepan_model0b_explan_estimates <- model0b.explan.estimates(outcome = "ocir.sum_score_base",
+                         explan_var = "ocir.sum_score_prepan",
+                         data_set = "dat.prepan")
+kable(ocir_prepan_model0b_explan_estimates)
+ocir_prepan_model0b_explan_estimates
+
+# Regression diagnostic statistics
+ocir_prepan_model0b_explan_reg_stats <- model0b.explan.reg.stats(outcome = "ocir.sum_score_base",
+                         explan_var = "ocir.sum_score_prepan",
+                         data_set = "dat.prepan")
+kable(ocir_prepan_model0b_explan_reg_stats)
+ocir_prepan_model0b_explan_reg_stats
+```
+
+### Model 1a: Disorder hierarchical, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r ocir model1a sum_score prepan}
+# Regression coefficients
+ocir_prepan_model1a_explan_estimates <- model1a.explan.estimates(outcome = "ocir.sum_score_base",
+                         explan_var = "ocir.sum_score_prepan",
+                         data_set = "dat.prepan")
+kable(ocir_prepan_model1a_explan_estimates)
+ocir_prepan_model1a_explan_estimates
+
+# Regression diagnostic statistics
+ocir_prepan_model1a_explan_reg_stats <- model1a.explan.reg.stats(outcome = "ocir.sum_score_base",
+                         explan_var = "ocir.sum_score_prepan",
+                         data_set = "dat.prepan")
+kable(ocir_prepan_model1a_explan_reg_stats)
+ocir_prepan_model1a_explan_reg_stats
+```
+
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r ocir model1b sum_score prepan}
+# Regression coefficients
+ocir_prepan_model1b_explan_estimates <- model1b.explan.estimates(outcome = "ocir.sum_score_base",
+                         explan_var = "ocir.sum_score_prepan",
+                         data_set = "dat.prepan")
+kable(ocir_prepan_model1b_explan_estimates)
+ocir_prepan_model1b_explan_estimates
+
+# Regression diagnostic statistics
+ocir_prepan_model1b_explan_reg_stats <- model1b.explan.reg.stats(outcome = "ocir.sum_score_base",
+                         explan_var = "ocir.sum_score_prepan",
+                         data_set = "dat.prepan")
+kable(ocir_prepan_model1b_explan_reg_stats)
+ocir_prepan_model1b_explan_reg_stats
+```
+
+# OCIR retro
+## Regression: Change scores
+### Model 0a: Disorder_hierarchical, Unadjusted
+```{r ocir model0a diff_score retro}
+# Regression coefficients
+ocir_retro_model0a_estimates <- model0a.estimates(outcome = "ocir.diff_score_base_retro",
+                                                 data_set = "dat.retro")
+kable(ocir_retro_model0a_estimates)
+ocir_retro_model0a_estimates
+
+# Regression diagnostic statistics
+ocir_retro_model0a_reg_stats <- model0a.reg.stats(outcome = "ocir.diff_score_base_retro",
+                                                 data_set = "dat.retro")
+kable(ocir_retro_model0a_reg_stats)
+ocir_retro_model0a_reg_stats
+```
+
+### Model 0b: Overlapping disorders, Unadjusted
+```{r ocir model0b diff_score retro}
+# Regression coefficients
+ocir_retro_model0b_estimates <- model0b.estimates(outcome = "ocir.diff_score_base_retro",
+                                                 data_set = "dat.retro")
+kable(ocir_retro_model0b_estimates)
+ocir_retro_model0b_estimates
+
+# Regression diagnostic statistics
+ocir_retro_model0b_reg_stats <- model0b.reg.stats(outcome = "ocir.diff_score_base_retro",
+                                                 data_set = "dat.retro")
+kable(ocir_retro_model0b_reg_stats)
+ocir_retro_model0b_reg_stats
+```
+
+### Model 1a: Disorder hierarchical, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r ocir model1a diff_score retro}
+# Regression coefficients
+ocir_retro_model1a_estimates <- model1a.estimates(outcome = "ocir.diff_score_base_retro",
+                                                 data_set = "dat.retro")
+kable(ocir_retro_model1a_estimates)
+ocir_retro_model1a_estimates
+
+# Regression diagnostic statistics
+ocir_retro_model1a_reg_stats <- model1a.reg.stats(outcome = "ocir.diff_score_base_retro",
+                                                 data_set = "dat.retro")
+kable(ocir_retro_model1a_reg_stats)
+ocir_retro_model1a_reg_stats
+```
+
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r ocir model1b diff_score retro}
+# Regression coefficients
+ocir_retro_model1b_estimates <- model1b.estimates(outcome = "ocir.diff_score_base_retro",
+                                                 data_set = "dat.retro")
+kable(ocir_retro_model1b_estimates)
+ocir_retro_model1b_estimates
+
+# Regression diagnostic statistics
+ocir_retro_model1b_reg_stats <- model1b.reg.stats(outcome = "ocir.diff_score_base_retro",
+                                                 data_set = "dat.retro")
+kable(ocir_retro_model1b_reg_stats)
+ocir_retro_model1b_reg_stats
+```
+
+## Regression: Absolute scores
+### Model 0a: Disorder_hierarchical, Unadjusted
+```{r ocir model0a sum_score retro}
+# Regression coefficients
+ocir_retro_model0a_explan_estimates <- model0a.explan.estimates(outcome = "ocir.sum_score_base",
+                                                               explan_var = "ocir.sum_score_retro",
+                                                               data_set = "dat.retro")
+kable(ocir_retro_model0a_explan_estimates)
+ocir_retro_model0a_explan_estimates
+
+# Regression diagnostic statistics
+ocir_retro_model0a_explan_reg_stats <- model0a.explan.reg.stats(outcome = "ocir.sum_score_base",
+                                                               explan_var = "ocir.sum_score_retro",
+                                                               data_set = "dat.retro")
+kable(ocir_retro_model0a_explan_reg_stats)
+ocir_retro_model0a_explan_reg_stats
+```
+
+### Model 0b: Overlapping disorders, Unadjusted
+```{r ocir model0b sum_score retro}
+# Regression coefficients
+ocir_retro_model0b_explan_estimates <- model0b.explan.estimates(outcome = "ocir.sum_score_base",
+                                                               explan_var = "ocir.sum_score_retro",
+                                                               data_set = "dat.retro")
+kable(ocir_retro_model0b_explan_estimates)
+ocir_retro_model0b_explan_estimates
+
+# Regression diagnostic statistics
+ocir_retro_model0b_explan_reg_stats <- model0b.explan.reg.stats(outcome = "ocir.sum_score_base",
+                                                               explan_var = "ocir.sum_score_retro",
+                                                               data_set = "dat.retro")
+kable(ocir_retro_model0b_explan_reg_stats)
+ocir_retro_model0b_explan_reg_stats
+```
+
+### Model 1a: Disorder hierarchical, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r ocir model1a sum_score retro}
+# Regression coefficients
+ocir_retro_model1a_explan_estimates <- model1a.explan.estimates(outcome = "ocir.sum_score_base",
+                                                               explan_var = "ocir.sum_score_retro",
+                                                               data_set = "dat.retro")
+kable(ocir_retro_model1a_explan_estimates)
+ocir_retro_model1a_explan_estimates
+
+# Regression diagnostic statistics
+ocir_retro_model1a_explan_reg_stats <- model1a.explan.reg.stats(outcome = "ocir.sum_score_base",
+                                                               explan_var = "ocir.sum_score_retro",
+                                                               data_set = "dat.retro")
+kable(ocir_retro_model1a_explan_reg_stats)
+ocir_retro_model1a_explan_reg_stats
+```
+
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r ocir model1b sum_score retro}
+# Regression coefficients
+ocir_retro_model1b_explan_estimates <- model1b.explan.estimates(outcome = "ocir.sum_score_base",
+                                                               explan_var = "ocir.sum_score_retro",
+                                                               data_set = "dat.retro")
+kable(ocir_retro_model1b_explan_estimates)
+ocir_retro_model1b_explan_estimates
+
+# Regression diagnostic statistics
+ocir_retro_model1b_explan_reg_stats <- model1b.explan.reg.stats(outcome = "ocir.sum_score_base",
+                                                               explan_var = "ocir.sum_score_retro",
+                                                               data_set = "dat.retro")
+kable(ocir_retro_model1b_explan_reg_stats)
+ocir_retro_model1b_explan_reg_stats
+```
+
+# PCL prepan
+## Regression: Change scores
+### Model 0a: Disorder_hierarchical, Unadjusted
+```{r pcl model0a diff_score prepan}
+# Regression coefficients
+pcl_prepan_model0a_estimates <- model0a.estimates(outcome = "pcl.diff_score_base_prepan",
+                  data_set = "dat.prepan")
+kable(pcl_prepan_model0a_estimates)
+pcl_prepan_model0a_estimates
+
+# Regression diagnostic statistics
+pcl_prepan_model0a_reg_stats <- model0a.reg.stats(outcome = "pcl.diff_score_base_prepan",
+                  data_set = "dat.prepan")
+kable(pcl_prepan_model0a_reg_stats)
+pcl_prepan_model0a_reg_stats
+```
+
+### Model 0b: Overlapping disorders, Unadjusted
+```{r pcl model0b diff_score prepan}
+# Regression coefficients
+pcl_prepan_model0b_estimates <- model0b.estimates(outcome = "pcl.diff_score_base_prepan",
+                  data_set = "dat.prepan")
+kable(pcl_prepan_model0b_estimates)
+pcl_prepan_model0b_estimates
+
+# Regression diagnostic statistics
+pcl_prepan_model0b_reg_stats <- model0b.reg.stats(outcome = "pcl.diff_score_base_prepan",
+                  data_set = "dat.prepan")
+kable(pcl_prepan_model0b_reg_stats)
+pcl_prepan_model0b_reg_stats
+```
+
+### Model 1a: Disorder hierarchical, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r pcl model1a diff_score prepan}
+# Regression coefficients
+pcl_prepan_model1a_estimates <- model1a.estimates(outcome = "pcl.diff_score_base_prepan",
+                  data_set = "dat.prepan")
+kable(pcl_prepan_model1a_estimates)
+pcl_prepan_model1a_estimates
+
+# Regression diagnostic statistics
+pcl_prepan_model1a_reg_stats <- model1a.reg.stats(outcome = "pcl.diff_score_base_prepan",
+                  data_set = "dat.prepan")
+kable(pcl_prepan_model1a_reg_stats)
+pcl_prepan_model1a_reg_stats
+```
+
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r pcl model1b diff_score prepan}
+# Regression coefficients
+pcl_prepan_model1b_estimates <- model1b.estimates(outcome = "pcl.diff_score_base_prepan",
+                  data_set = "dat.prepan")
+kable(pcl_prepan_model1b_estimates)
+pcl_prepan_model1b_estimates
+
+# Regression diagnostic statistics
+pcl_prepan_model1b_reg_stats <- model1b.reg.stats(outcome = "pcl.diff_score_base_prepan",
+                  data_set = "dat.prepan")
+kable(pcl_prepan_model1b_reg_stats)
+pcl_prepan_model1b_reg_stats
+```
+
+## Regression: Absolute scores
+### Model 0a: Disorder_hierarchical, Unadjusted
+```{r pcl model0a sum_score prepan}
+# Regression coefficients
+pcl_prepan_model0a_explan_estimates <- model0a.explan.estimates(outcome = "pcl.sum_score_base",
+                         explan_var = "pcl.sum_score_prepan",
+                         data_set = "dat.prepan")
+kable(pcl_prepan_model0a_explan_estimates)
+pcl_prepan_model0a_explan_estimates
+
+# Regression diagnostic statistics
+pcl_prepan_model0a_explan_reg_stats <- model0a.explan.reg.stats(outcome = "pcl.sum_score_base",
+                         explan_var = "pcl.sum_score_prepan",
+                         data_set = "dat.prepan")
+kable(pcl_prepan_model0a_explan_reg_stats)
+pcl_prepan_model0a_explan_reg_stats
+```
+
+### Model 0b: Overlapping disorders, Unadjusted
+```{r pcl model0b sum_score prepan}
+# Regression coefficients
+pcl_prepan_model0b_explan_estimates <- model0b.explan.estimates(outcome = "pcl.sum_score_base",
+                         explan_var = "pcl.sum_score_prepan",
+                         data_set = "dat.prepan")
+kable(pcl_prepan_model0b_explan_estimates)
+pcl_prepan_model0b_explan_estimates
+
+# Regression diagnostic statistics
+pcl_prepan_model0b_explan_reg_stats <- model0b.explan.reg.stats(outcome = "pcl.sum_score_base",
+                         explan_var = "pcl.sum_score_prepan",
+                         data_set = "dat.prepan")
+kable(pcl_prepan_model0b_explan_reg_stats)
+pcl_prepan_model0b_explan_reg_stats
+```
+
+### Model 1a: Disorder hierarchical, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r pcl model1a sum_score prepan}
+# Regression coefficients
+pcl_prepan_model1a_explan_estimates <- model1a.explan.estimates(outcome = "pcl.sum_score_base",
+                         explan_var = "pcl.sum_score_prepan",
+                         data_set = "dat.prepan")
+kable(pcl_prepan_model1a_explan_estimates)
+pcl_prepan_model1a_explan_estimates
+
+# Regression diagnostic statistics
+pcl_prepan_model1a_explan_reg_stats <- model1a.explan.reg.stats(outcome = "pcl.sum_score_base",
+                         explan_var = "pcl.sum_score_prepan",
+                         data_set = "dat.prepan")
+kable(pcl_prepan_model1a_explan_reg_stats)
+pcl_prepan_model1a_explan_reg_stats
+```
+
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r pcl model1b sum_score prepan}
+# Regression coefficients
+pcl_prepan_model1b_explan_estimates <- model1b.explan.estimates(outcome = "pcl.sum_score_base",
+                         explan_var = "pcl.sum_score_prepan",
+                         data_set = "dat.prepan")
+kable(pcl_prepan_model1b_explan_estimates)
+pcl_prepan_model1b_explan_estimates
+
+# Regression diagnostic statistics
+pcl_prepan_model1b_explan_reg_stats <- model1b.explan.reg.stats(outcome = "pcl.sum_score_base",
+                         explan_var = "pcl.sum_score_prepan",
+                         data_set = "dat.prepan")
+kable(pcl_prepan_model1b_explan_reg_stats)
+pcl_prepan_model1b_explan_reg_stats
+```

### 2020-09-18 PANCHANGE_exclusion_descriptives.Rmd
updated the exclusion chunk in the exclusion_descriptives script

@@
 ```{r read in data}
-dat.raw <- readRDS(file = paste0(data_path, "/four_cohorts_variables.rds")) # NEEDS CHANGING TO THE DATA SET THAT COMES OUT OF THE VARIABLE CREATION
+dat.raw <- readRDS(file = paste0(data_path, "/four_cohorts_variables.rds"))
 dim(dat.raw)
@@
 Exclude individuals with NA for the MHD categories
-Individuals with NAs for age/gender have already been excluded in pre-processing script.
-
-```{r exclusion criteria for diagnoses analysis}
+Individuals with NAs for age/gender have already been excluded in pre-processing script, but they get excluded here to be save and to double check previous programming.
+
+"anxiety_disorders",
+                             "depressive_disorders",
+                             "depression_and_anxiety",
+                             "eating_disorders",
+                             "obsessive_compulsive_disorders",
+                             "psychotic_disorders",
+                             "mhd.mania_hypomania_bipolar_or_manicdepression",
+                             "mhd.posttraumatic_stress_disorder_ptsd",
+                             "autism_spectrum_disorder",
+                             "mhd.attention_deficit_hyperactivity_disorder",
+                             "mhd.personality_disorder",
+                             "Gender_collapsed",
+                             "age_category_collapsed",
+                             "Ethnicity_collapsed",
+                             "time_diff_sign_up_coping"
+
+```{r}
+             anxiety_disorders_numeric = "Anxiety disorders",
+             depressive_disorders_numeric = "Depressive disorders",
+             eating_disorders_numeric = "Eating disorders",
+             obsessive_compulsive_disorders_numeric = "OCDs",
+             psychotic_disorders_numeric = "Psychotic disorders",
+             mhd.mania_hypomania_bipolar_or_manicdepression_numeric = "Bipolar disorders",
+             mhd.posttraumatic_stress_disorder_ptsd_numeric = "PTSD",
+             autism_spectrum_disorder_numeric = "Autism",
+             mhd.attention_deficit_hyperactivity_disorder_numeric = "ADHD",
+             mhd.personality_disorder_numeric = "Personality disorders",
+             control_numeric = "Controls"
+```
+
+```{r Exclusion criteria for PANCHANGE}
 dat <- dat.raw %>%
-  filter(
+  filter( # Participants should have responded to the mental health diagnosis (MHD) questionnaire
   !is.na(depressive_disorders) &
+ !is.na(anxiety_disorders) &
   !is.na(eating_disorders) &
+  !is.na(obsessive_compulsive_disorders) &
  !is.na(psychotic_disorders) &
-      !is.na(obsessive_compulsive_disorders) &
+  !is.na(mhd.mania_hypomania_bipolar_or_manicdepression) &
+  !is.na(mhd.posttraumatic_stress_disorder_ptsd) &    
   !is.na(autism_spectrum_disorder) &
-      !is.na(mhd.mania_hypomania_bipolar_or_manicdepression_numeric) &
-      !is.na(mhd.posttraumatic_stress_disorder_ptsd_numeric) &
+  !is.na(mhd.attention_deficit_hyperactivity_disorder) &
+  !is.na(mhd.personality_disorder) &
   !is.na(control)
   ) %>% 
-  drop_na(startDate.coping)
+ filter(
+   !is.na(data_group_gad) & # Participants should have answered at least the GAD, the PHQ, or the PCL once
+   !is.na(data_group_phq) &
+   !is.na(data_group_pcl)
+ ) %>%
+  drop_na(startDate.coping) %>% # Participant has answered the COPING/RAMP baseline questionnaire
+  drop_na(Gender_collapsed) %>% # Participant has self-reported their gender
+  drop_na(age_category_collapsed) # Participant has self-reported their age
 

### 2020-09-18 PANCHANGE_exclusion_descriptives.Rmd
ran all scripts merge -> variable_creation -> exclusion_descriptives -> analysis for testing and knitting

@@
 Individuals with NAs for age/gender have already been excluded in pre-processing script, but they get excluded here to be save and to double check previous programming.
-
-"anxiety_disorders",
-                             "depressive_disorders",
-                             "depression_and_anxiety",
-                             "eating_disorders",
-                             "obsessive_compulsive_disorders",
-                             "psychotic_disorders",
-                             "mhd.mania_hypomania_bipolar_or_manicdepression",
-                             "mhd.posttraumatic_stress_disorder_ptsd",
-                             "autism_spectrum_disorder",
-                             "mhd.attention_deficit_hyperactivity_disorder",
-                             "mhd.personality_disorder",
-                             "Gender_collapsed",
-                             "age_category_collapsed",
-                             "Ethnicity_collapsed",
-                             "time_diff_sign_up_coping"
-
-```{r}
-             anxiety_disorders_numeric = "Anxiety disorders",
-             depressive_disorders_numeric = "Depressive disorders",
-             eating_disorders_numeric = "Eating disorders",
-             obsessive_compulsive_disorders_numeric = "OCDs",
-             psychotic_disorders_numeric = "Psychotic disorders",
-             mhd.mania_hypomania_bipolar_or_manicdepression_numeric = "Bipolar disorders",
-             mhd.posttraumatic_stress_disorder_ptsd_numeric = "PTSD",
-             autism_spectrum_disorder_numeric = "Autism",
-             mhd.attention_deficit_hyperactivity_disorder_numeric = "ADHD",
-             mhd.personality_disorder_numeric = "Personality disorders",
-             control_numeric = "Controls"
-```
 

### 2020-09-21 PANCHANGE_variable_creation.Rmd

@@
 ```{r read in data}
-dat.raw <- readRDS(file = paste0(data_path, "/four_cohorts.rds"))
-dim(dat.raw)
-colnames(dat.raw)
+dat <- readRDS(file = paste0(data_path, "/four_cohorts.rds"))
+dim(dat)
+colnames(dat)
 ```
@@
 ```{r covid test positive double}
-dat.raw <- dat.raw %>%
+dat <- dat %>%
   mutate(covid_test_positive_double_numeric =
@@
 
-dat.raw <- dat.raw %>%
+dat <- dat %>%
   mutate(covid_test_positive_double =
@@
 
-dat.raw %>%
+dat %>%
   freq(covid_test_positive_double)
@@
 ```{r gad covid test positive}
-dat.raw <- dat.raw %>%
+dat <- dat %>%
   mutate(gad.covid_test_positive_numeric =
@@
 
-dat.raw <- dat.raw %>%
+dat <- dat %>%
   mutate(covid_test_positive =
@@
 
-dat.raw %>%
+dat %>%
   freq(covid_test_positive)
@@
 ```{r COVID positive swap}
-dat.raw %>%
+dat %>%
   count(respiratory.throat_swab_test_nose, Sample) %>%
@@
 ```{r COVID positive antibody test}
-dat.raw %>%
+dat %>%
   count(respiratory.results_antibody_test, Sample) %>%
@@
 ```{r COVID probable diagnosis}
-dat.raw %>%
+dat %>%
   count(covid_probable_case_incl_screening, Sample) %>%
@@
 ```{r Cross table probable covid and covid test positive}
-dat.raw %>%
+dat %>%
   count(covid_test_positive, covid_probable_case_incl_screening) %>%

### 2020-09-22 PANCHANGE_analysis.Rmd
updated the exclusion chunk in the exclusion_descriptives script

@@
   theme_personal +
-  scale_fill_manual(values = palette, labels = c("Prepandemic", "Retrospective"))
+  scale_fill_manual(
+    values = palette,
+    labels = c("Prepandemic", "Retrospective"))
 ```
@@
   theme_personal +
-  scale_fill_manual(values = palette, labels = c("Prepandemic", "Retrospective")) +
+  scale_fill_manual(
+    values = palette,
+    labels = c("Prepandemic", "Retrospective")) +
   facet_wrap("Disorder_hierarchical")
@@
   theme_personal +
-  scale_fill_manual(values = palette, labels = c("Prepandemic"))
+  scale_fill_manual(
+    values = palette,
+    labels = c("Prepandemic"))
 ```
@@
     values = COPINGpalette3,
- #   labels = c("Baseline", "Prepandemic", "Retrospective")
+    breaks = c("prepan", "retro", "base"),
+    labels = c("base" = "Baseline", "prepan" = "Prepandemic", "retro" = "Retrospective")
     )
@@
     values = COPINGpalette3,
-#    labels = c("Prepandemic", "Retrospective")
+    breaks = c("prepan", "retro", "base"),
+    labels = c("base" = "Baseline", "prepan" = "Prepandemic", "retro" = "Retrospective")
     ) +
@@
   theme_personal +
-  scale_fill_manual(values = palette, labels = c("Retrospective"))
+  scale_fill_manual(
+    values = palette,
+    labels = c("Retrospective"))
 ```
@@
   theme_personal +
-  scale_fill_manual(values = palette, labels = c("Prepandemic", "Retrospective")) +
+  scale_fill_manual(
+    values = palette,
+    labels = c("Prepandemic", "Retrospective")
+    ) +
   facet_wrap("Disorder_hierarchical")
@@
     values = COPINGpalette3,
-    labels = c("Baseline", "Prepandemic", "Retrospective")
+    breaks = c("prepan", "retro", "base"),
+    labels = c("base" = "Baseline", "prepan" = "Prepandemic", "retro" = "Retrospective")
   )
@@
     values = COPINGpalette3,
-    labels = c("Baseline", "Prepandemic", "Retrospective")
+    breaks = c("prepan", "retro", "base"),
+    labels = c("base" = "Baseline", "prepan" = "Prepandemic", "retro" = "Retrospective")
   ) +
@@
 
-# Create additional datasets for analyses
+# Create subsets of data for analyses
 Filter data frame to create 2 additional datasets. Additional exclusion criteria (beyond those listed above) are specified below:
@@
   # define the independent variables
-  independent.variables <- c("anxiety_disorders",
-                             "depressive_disorders",
-                             "depression_and_anxiety",
+  independent.variables <- c("depression_and_anxiety",
                              "eating_disorders",
                              "obsessive_compulsive_disorders",
-                             "psychotic_disorders",
-                             "mhd.mania_hypomania_bipolar_or_manicdepression",
+                             "bipolar_and_schizophrenia",
                              "mhd.posttraumatic_stress_disorder_ptsd",
@@
                "obsessive_compulsive_disordersObsessive compulsive disorder" = "OCDs",
+               "bipolar_and_schizophreniaPsychotic and bipolar disorder" = "Psychotic and bipolar disorder",
+               "bipolar_and_schizophreniaOnly psychotic disorder" = "Only psychotic disorder",
+               "bipolar_and_schizophreniaOnly bipolar disorder" = "Only bipolar disorder",
                "psychotic_disordersPsychotic disorder" = "Psychotic disorder",
@@
   independent.variables <- c(explan_var, 
-                             "anxiety_disorders",
-                             "depressive_disorders",
                              "depression_and_anxiety",
@@
                              "obsessive_compulsive_disorders",
-                             "psychotic_disorders",
-                             "mhd.mania_hypomania_bipolar_or_manicdepression",
+                             "bipolar_and_schizophrenia",
                              "mhd.posttraumatic_stress_disorder_ptsd",
@@
   independent.variables <- c(explan_var,
-                             "anxiety_disorders",
-                             "depressive_disorders",
                              "depression_and_anxiety",

### 2020-09-25 PANCHANGE_analysis.Rmd
changed time variable in regression

@@
                             "Ethnicity_collapsed",
-                            "time_diff_sign_up_coping"
+                            "time_diff_coping_lockdown_march_23"
                             )
@@
                "Ethnicity_collapsedOther" = "Other ethnicity",
-               "time_diff_sign_up_coping" = "Time difference: prepandemic to COPING"
+               "time_diff_coping_lockdown_march_23" = "Time difference: Lockdown to baseline"
              ),
@@
                              "Ethnicity_collapsed",
-                             "time_diff_sign_up_coping"
+                             "time_diff_coping_lockdown_march_23"
                                 )
@@
                              "Ethnicity_collapsed",
-                             "time_diff_sign_up_coping"
+                             "time_diff_coping_lockdown_march_23"
   )

### 2020-09-25 PANCHANGE_analysis.Rmd
added regression with baseline only for all measures

@@
 
+#GAD baseline, not controlling for prior symptoms
+### Model 0a: Disorder_hierarchical, Unadjusted
+```{r gad model0a absolute whole sample}
+# Regression coefficients
+gad_baseline_model0a_estimates <- model0a.estimates(outcome = "gad.sum_score_base",
+                                                 data_set = "dat")
+kable(gad_baseline_model0a_estimates)
+gad_baseline_model0a_estimates
+
+# Regression diagnostic statistics
+gad_baseline_model0a_reg_stats <- model0a.reg.stats(outcome = "gad.sum_score_base",
+                                                 data_set = "dat")
+kable(gad_baseline_model0a_reg_stats)
+gad_baseline_model0a_reg_stats
+```
+
+### Model 0b: Overlapping disorders, Unadjusted
+```{r gad model0b absolute whole sample}
+# Regression coefficients
+gad_baseline_model0b_estimates <- model0b.estimates(outcome = "gad.sum_score_base",
+                                                 data_set = "dat")
+kable(gad_baseline_model0b_estimates)
+gad_baseline_model0b_estimates
+
+# Regression diagnostic statistics
+gad_baseline_model0b_reg_stats <- model0b.reg.stats(outcome = "gad.sum_score_base",
+                                                 data_set = "dat")
+kable(gad_baseline_model0b_reg_stats)
+gad_baseline_model0b_reg_stats
+```
+
+### Model 1a: Disorder hierarchical, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r gad model1a absolute whole sample}
+# Regression coefficients
+gad_baseline_model1a_estimates <- model1a.estimates(outcome = "gad.sum_score_base",
+                                                 data_set = "dat")
+kable(gad_baseline_model1a_estimates)
+gad_baseline_model1a_estimates
+
+# Regression diagnostic statistics
+gad_baseline_model1a_reg_stats <- model1a.reg.stats(outcome = "gad.sum_score_base",
+                                                 data_set = "dat")
+kable(gad_baseline_model1a_reg_stats)
+gad_baseline_model1a_reg_stats
+```
+
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r gad model1b absolute whole sample}
+# Regression coefficients
+gad_baseline_model1b_estimates <- model1b.estimates(outcome = "gad.sum_score_base",
+                                                 data_set = "dat")
+kable(gad_baseline_model1b_estimates)
+gad_baseline_model1b_estimates
+
+# Regression diagnostic statistics
+gad_baseline_model1b_reg_stats <- model1b.reg.stats(outcome = "gad.sum_score_base",
+                                                 data_set = "dat")
+kable(gad_baseline_model1b_reg_stats)
+gad_baseline_model1b_reg_stats
+```
+
 # GAD prepan
@@
 
+#PHQ baseline, not controlling for prior symptoms
+### Model 0a: Disorder_hierarchical, Unadjusted
+```{r phq model0a absolute whole sample}
+# Regression coefficients
+phq_baseline_model0a_estimates <- model0a.estimates(outcome = "phq.sum_score_base",
+                                                 data_set = "dat")
+kable(phq_baseline_model0a_estimates)
+phq_baseline_model0a_estimates
+
+# Regression diagnostic statistics
+phq_baseline_model0a_reg_stats <- model0a.reg.stats(outcome = "phq.sum_score_base",
+                                                 data_set = "dat")
+kable(phq_baseline_model0a_reg_stats)
+phq_baseline_model0a_reg_stats
+```
+
+### Model 0b: Overlapping disorders, Unadjusted
+```{r phq model0b absolute whole sample}
+# Regression coefficients
+phq_baseline_model0b_estimates <- model0b.estimates(outcome = "phq.sum_score_base",
+                                                 data_set = "dat")
+kable(phq_baseline_model0b_estimates)
+phq_baseline_model0b_estimates
+
+# Regression diagnostic statistics
+phq_baseline_model0b_reg_stats <- model0b.reg.stats(outcome = "phq.sum_score_base",
+                                                 data_set = "dat")
+kable(phq_baseline_model0b_reg_stats)
+phq_baseline_model0b_reg_stats
+```
+
+### Model 1a: Disorder hierarchical, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r phq model1a absolute whole sample}
+# Regression coefficients
+phq_baseline_model1a_estimates <- model1a.estimates(outcome = "phq.sum_score_base",
+                                                 data_set = "dat")
+kable(phq_baseline_model1a_estimates)
+phq_baseline_model1a_estimates
+
+# Regression diagnostic statistics
+phq_baseline_model1a_reg_stats <- model1a.reg.stats(outcome = "phq.sum_score_base",
+                                                 data_set = "dat")
+kable(phq_baseline_model1a_reg_stats)
+phq_baseline_model1a_reg_stats
+```
+
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r phq model1b absolute whole sample}
+# Regression coefficients
+phq_baseline_model1b_estimates <- model1b.estimates(outcome = "phq.sum_score_base",
+                                                 data_set = "dat")
+kable(phq_baseline_model1b_estimates)
+phq_baseline_model1b_estimates
+
+# Regression diagnostic statistics
+phq_baseline_model1b_reg_stats <- model1b.reg.stats(outcome = "phq.sum_score_base",
+                                                 data_set = "dat")
+kable(phq_baseline_model1b_reg_stats)
+phq_baseline_model1b_reg_stats
+```
+
 # PHQ prepan
@@
 
+# OCI-R baseline, not controlling for prior symptoms
+### Model 0a: Disorder_hierarchical, Unadjusted
+```{r ocir model0a absolute whole sample}
+# Regression coefficients
+ocir_baseline_model0a_estimates <- model0a.estimates(outcome = "ocir.sum_score_base",
+                                                 data_set = "dat")
+kable(ocir_baseline_model0a_estimates)
+ocir_baseline_model0a_estimates
+
+# Regression diagnostic statistics
+ocir_baseline_model0a_reg_stats <- model0a.reg.stats(outcome = "ocir.sum_score_base",
+                                                 data_set = "dat")
+kable(ocir_baseline_model0a_reg_stats)
+ocir_baseline_model0a_reg_stats
+```
+
+### Model 0b: Overlapping disorders, Unadjusted
+```{r ocir model0b absolute whole sample}
+# Regression coefficients
+ocir_baseline_model0b_estimates <- model0b.estimates(outcome = "ocir.sum_score_base",
+                                                 data_set = "dat")
+kable(ocir_baseline_model0b_estimates)
+ocir_baseline_model0b_estimates
+
+# Regression diagnostic statistics
+ocir_baseline_model0b_reg_stats <- model0b.reg.stats(outcome = "ocir.sum_score_base",
+                                                 data_set = "dat")
+kable(ocir_baseline_model0b_reg_stats)
+ocir_baseline_model0b_reg_stats
+```
+
+### Model 1a: Disorder hierarchical, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r ocir model1a absolute whole sample}
+# Regression coefficients
+ocir_baseline_model1a_estimates <- model1a.estimates(outcome = "ocir.sum_score_base",
+                                                 data_set = "dat")
+kable(ocir_baseline_model1a_estimates)
+ocir_baseline_model1a_estimates
+
+# Regression diagnostic statistics
+ocir_baseline_model1a_reg_stats <- model1a.reg.stats(outcome = "ocir.sum_score_base",
+                                                 data_set = "dat")
+kable(ocir_baseline_model1a_reg_stats)
+ocir_baseline_model1a_reg_stats
+```
+
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r ocir model1b absolute whole sample}
+# Regression coefficients
+ocir_baseline_model1b_estimates <- model1b.estimates(outcome = "ocir.sum_score_base",
+                                                 data_set = "dat")
+kable(ocir_baseline_model1b_estimates)
+ocir_baseline_model1b_estimates
+
+# Regression diagnostic statistics
+ocir_baseline_model1b_reg_stats <- model1b.reg.stats(outcome = "ocir.sum_score_base",
+                                                 data_set = "dat")
+kable(ocir_baseline_model1b_reg_stats)
+ocir_baseline_model1b_reg_stats
+```
+
 # OCIR prepan
@@
 
+# PCL baseline, not controlling for prior symptoms
+### Model 0a: Disorder_hierarchical, Unadjusted
+```{r pcl model0a absolute whole sample}
+# Regression coefficients
+pcl_baseline_model0a_estimates <- model0a.estimates(outcome = "pcl.sum_score_base",
+                                                 data_set = "dat")
+kable(pcl_baseline_model0a_estimates)
+pcl_baseline_model0a_estimates
+
+# Regression diagnostic statistics
+pcl_baseline_model0a_reg_stats <- model0a.reg.stats(outcome = "pcl.sum_score_base",
+                                                 data_set = "dat")
+kable(pcl_baseline_model0a_reg_stats)
+pcl_baseline_model0a_reg_stats
+```
+
+### Model 0b: Overlapping disorders, Unadjusted
+```{r pcl model0b absolute whole sample}
+# Regression coefficients
+pcl_baseline_model0b_estimates <- model0b.estimates(outcome = "pcl.sum_score_base",
+                                                 data_set = "dat")
+kable(pcl_baseline_model0b_estimates)
+pcl_baseline_model0b_estimates
+
+# Regression diagnostic statistics
+pcl_baseline_model0b_reg_stats <- model0b.reg.stats(outcome = "pcl.sum_score_base",
+                                                 data_set = "dat")
+kable(pcl_baseline_model0b_reg_stats)
+pcl_baseline_model0b_reg_stats
+```
+
+### Model 1a: Disorder hierarchical, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r pcl model1a absolute whole sample}
+# Regression coefficients
+pcl_baseline_model1a_estimates <- model1a.estimates(outcome = "pcl.sum_score_base",
+                                                 data_set = "dat")
+kable(pcl_baseline_model1a_estimates)
+pcl_baseline_model1a_estimates
+
+# Regression diagnostic statistics
+pcl_baseline_model1a_reg_stats <- model1a.reg.stats(outcome = "pcl.sum_score_base",
+                                                 data_set = "dat")
+kable(pcl_baseline_model1a_reg_stats)
+pcl_baseline_model1a_reg_stats
+```
+
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r pcl model1b absolute whole sample}
+# Regression coefficients
+pcl_baseline_model1b_estimates <- model1b.estimates(outcome = "pcl.sum_score_base",
+                                                 data_set = "dat")
+kable(pcl_baseline_model1b_estimates)
+pcl_baseline_model1b_estimates
+
+# Regression diagnostic statistics
+pcl_baseline_model1b_reg_stats <- model1b.reg.stats(outcome = "pcl.sum_score_base",
+                                                 data_set = "dat")
+kable(pcl_baseline_model1b_reg_stats)
+pcl_baseline_model1b_reg_stats
+```
+
 # PCL prepan

### 2020-09-28 PANCHANGE_analysis.Rmd
added half-violin function

--- 2020-09-22 PANCHANGE_analysis.Rmd
@@
 library(ggpubr)
+```
+
+# R functions
+## Half-violin plot
+```{r Half-violin plot}
+source("https://raw.githubusercontent.com/datavizpyr/data/master/half_flat_violinplot.R")
 ```
@@
     )
+```
+
+# Function for split violin plot
+```{r Function for split violin plot}
+GeomSplitViolin <- ggproto("GeomSplitViolin", GeomViolin, 
+                           draw_group = function(self, data, ..., draw_quantiles = NULL) {
+  data <- transform(data, xminv = x - violinwidth * (x - xmin), xmaxv = x + violinwidth * (xmax - x))
+  grp <- data[1, "group"]
+  newdata <- plyr::arrange(transform(data, x = if (grp %% 2 == 1) xminv else xmaxv), if (grp %% 2 == 1) y else -y)
+  newdata <- rbind(newdata[1, ], newdata, newdata[nrow(newdata), ], newdata[1, ])
+  newdata[c(1, nrow(newdata) - 1, nrow(newdata)), "x"] <- round(newdata[1, "x"])
+
+  if (length(draw_quantiles) > 0 & !scales::zero_range(range(data$y))) {
+    stopifnot(all(draw_quantiles >= 0), all(draw_quantiles <=
+      1))
+    quantiles <- ggplot2:::create_quantile_segment_frame(data, draw_quantiles)
+    aesthetics <- data[rep(1, nrow(quantiles)), setdiff(names(data), c("x", "y")), drop = FALSE]
+    aesthetics$alpha <- rep(1, nrow(quantiles))
+    both <- cbind(quantiles, aesthetics)
+    quantile_grob <- GeomPath$draw_panel(both, ...)
+    ggplot2:::ggname("geom_split_violin", grid::grobTree(GeomPolygon$draw_panel(newdata, ...), quantile_grob))
+  }
+  else {
+    ggplot2:::ggname("geom_split_violin", GeomPolygon$draw_panel(newdata, ...))
+  }
+})
+
+geom_split_violin <- function(mapping = NULL, data = NULL, stat = "ydensity", position = "identity", ..., 
+                              draw_quantiles = NULL, trim = TRUE, scale = "area", na.rm = FALSE, 
+                              show.legend = NA, inherit.aes = TRUE) {
+  layer(data = data, mapping = mapping, stat = stat, geom = GeomSplitViolin, 
+        position = position, show.legend = show.legend, inherit.aes = inherit.aes, 
+        params = list(trim = trim, scale = scale, draw_quantiles = draw_quantiles, na.rm = na.rm, ...))
+}
 ```
@@
   mutate(Time_point = str_replace(Time_point_raw, "gad.sum_score_", "")) %>%
-  select(-Time_point_raw)
+  select(-Time_point_raw) %>%
+  add_column(Full_cohort = as.factor("Full cohort")) %>%
+  mutate(Time_point_dup = Time_point)
 
@@
   facet_wrap("Disorder_hierarchical")
+```
+
+```{r}
+summary_data <- dat.long.gad.sum %>%
+  group_by(Time_point) %>%
+  summarise(
+    mean = mean(gad.sum_score, na.rm = T),
+    min = mean(gad.sum_score, na.rm = T) - qnorm(0.975)*sd(gad.sum_score, na.rm = T)/sqrt(n()),
+    max = mean(gad.sum_score, na.rm = T) + qnorm(0.975)*sd(gad.sum_score, na.rm = T)/sqrt(n()),
+    sd_low = mean(gad.sum_score, na.rm = T) - sd(gad.sum_score, na.rm = T),
+    sd_up = mean(gad.sum_score, na.rm = T) + sd(gad.sum_score, na.rm = T)
+  )
+
+summary_data
+```
+
+```{r}
+dat.long.gad.sum %>%
+  filter(Time_point != "base") %>%
+  ggplot(mapping = aes(
+    x = Full_cohort,
+    y = gad.sum_score,
+    fill = Time_point)) +
+  geom_hline(yintercept = 5, linetype = "dashed", color = "gray") +
+  geom_hline(yintercept = 10, linetype = "dashed", color = "gray") +
+  geom_hline(yintercept = 15, linetype = "dashed", color = "gray") +
+  geom_split_violin(
+    trim = FALSE,
+    alpha = 0.5
+    ) +
+ stat_summary(fun.y = mean,
+               fun.ymin = function(x) mean(x) - sd(x), 
+               fun.ymax = function(x) mean(x) + sd(x), 
+               geom = "pointrange",
+              position = position_dodge(width = .25)) +
+  labs(
+    x = "GAD7 scores",
+    y = "Percentage of participants",
+    fill = "Time point") +
+  theme_personal +
+  scale_fill_manual(
+    values = COPINGpalette3,
+    breaks = c("prepan", "retro", "base"),
+    labels = c("base" = "Baseline", "prepan" = "Prepandemic", "retro" = "Retrospective")
+    )
+```
+
+```{r gad violin sum}
+violin.gad.sum.prepan.retro <- dat.long.gad.sum %>%
+  filter(Time_point != "base") %>%
+  ggplot(mapping = aes(
+    x = Full_cohort,
+    y = gad.sum_score,
+    fill = Time_point)) +
+    geom_hline(yintercept = 5, linetype = "dashed", color = "gray") +
+  geom_hline(yintercept = 10, linetype = "dashed", color = "gray") +
+  geom_hline(yintercept = 15, linetype = "dashed", color = "gray") +
+  geom_split_violin(
+    trim = FALSE,
+    alpha = 0.5
+    ) +
+ stat_summary(fun.y = mean,
+               fun.ymin = function(x) mean(x) - sd(x), 
+               fun.ymax = function(x) mean(x) + sd(x), 
+               geom = "pointrange",
+              position = position_dodge(width = .25)) +
+    labs(
+    x = "GAD7 scores",
+    y = "Percentage of participants",
+    fill = "Time point") +
+  theme_personal +
+  scale_fill_manual(
+    values = COPINGpalette3,
+    breaks = c("prepan", "retro", "base"),
+    labels = c("base" = "Baseline", "prepan" = "Prepandemic", "retro" = "Retrospective")
+    )
+violin.gad.sum.prepan.retro
+
+violin.gad.sum.prepan.base <- dat.long.gad.sum %>%
+  filter(Time_point != "retro") %>%
+  ggplot(mapping = aes(
+    x = Full_cohort,
+    y = gad.sum_score,
+    fill = Time_point)) +
+    geom_hline(yintercept = 5, linetype = "dashed", color = "gray") +
+  geom_hline(yintercept = 10, linetype = "dashed", color = "gray") +
+  geom_hline(yintercept = 15, linetype = "dashed", color = "gray") +
+  geom_split_violin(
+    trim = FALSE,
+    alpha = 0.5
+    ) +
+ stat_summary(fun.y = mean,
+               fun.ymin = function(x) mean(x) - sd(x), 
+               fun.ymax = function(x) mean(x) + sd(x), 
+               geom = "pointrange",
+              position = position_dodge(width = .25)) +
+  labs(
+    x = "GAD7 scores",
+    y = "Percentage of participants",
+    fill = "Time point") +
+  theme_personal +
+  scale_fill_manual(
+    values = COPINGpalette3,
+    breaks = c("prepan", "retro", "base"),
+    labels = c("base" = "Baseline", "prepan" = "Prepandemic", "retro" = "Retrospective")
+    )
+violin.gad.sum.prepan.base
+
+violin.gad.sum.retro.base <- dat.long.gad.sum %>%
+  filter(Time_point != "prepan") %>%
+  ggplot(mapping = aes(
+    x = Full_cohort,
+    y = gad.sum_score,
+    fill = Time_point)) +
+    geom_hline(yintercept = 5, linetype = "dashed", color = "gray") +
+  geom_hline(yintercept = 10, linetype = "dashed", color = "gray") +
+  geom_hline(yintercept = 15, linetype = "dashed", color = "gray") +
+  geom_split_violin(
+    trim = FALSE,
+    alpha = 0.5
+    ) +
+ stat_summary(fun.y = mean,
+               fun.ymin = function(x) mean(x) - sd(x), 
+               fun.ymax = function(x) mean(x) + sd(x), 
+               geom = "pointrange",
+              position = position_dodge(width = .25)) +
+  labs(
+    x = "GAD7 scores",
+    y = "Percentage of participants",
+    fill = "Time point") +
+  theme_personal +
+  scale_fill_manual(
+    values = COPINGpalette3,
+    breaks = c("prepan", "retro", "base"),
+    labels = c("base" = "Baseline", "prepan" = "Prepandemic", "retro" = "Retrospective")
+    )
+violin.gad.sum.retro.base
+
+violin.gad.sum.prepan.retro +
+  violin.gad.sum.prepan.base +
+  violin.gad.sum.retro.base +
+  plot_layout(guides = "collect", widths = c(1,1,1)) +
+  plot_annotation(tag_levels = "A")
+```
+
+```{r gad violin sum}
+dat.long.gad.sum %>%
+  filter(Time_point != "base") %>%
+  ggplot(mapping = aes(
+    x = Sample,
+    y = gad.sum_score,
+    fill = Time_point)) +
+  geom_split_violin(
+#    color = textcolor,
+    trim = FALSE,
+    alpha = 0.5
+    ) +
+  labs(
+    x = "GAD7 scores",
+    y = "Percentage of participants",
+    fill = "Time point") +
+  theme_personal +
+  scale_fill_manual(
+    values = COPINGpalette3,
+    breaks = c("prepan", "retro", "base"),
+    labels = c("base" = "Baseline", "prepan" = "Prepandemic", "retro" = "Retrospective")
+    )+
+  coord_flip()
+```
+
+```{r gad violin sum}
+dat.long.gad.sum %>%
+  filter(Time_point != "base") %>%
+  ggplot(mapping = aes(
+    x = Disorder_hierarchical,
+    y = gad.sum_score,
+    fill = Time_point)) +
+  geom_split_violin(
+#    color = textcolor,
+    trim = FALSE,
+    alpha = 0.5
+    ) +
+  labs(
+    x = "GAD7 scores",
+    y = "Percentage of participants",
+    fill = "Time point") +
+  theme_personal +
+  scale_fill_manual(
+    values = COPINGpalette3,
+    breaks = c("prepan", "retro", "base"),
+    labels = c("base" = "Baseline", "prepan" = "Prepandemic", "retro" = "Retrospective")
+    )+
+  coord_flip()
+```
+
+```{r gad violin sum}
+dat.long.gad.sum %>%
+  filter(Time_point != "retro") %>%
+  ggplot(mapping = aes(
+    x = Disorder_hierarchical,
+    y = gad.sum_score,
+    fill = Time_point)) +
+  geom_split_violin(
+#    color = textcolor,
+    trim = FALSE,
+    alpha = 0.5
+    ) +
+  labs(
+    x = "GAD7 scores",
+    y = "Percentage of participants",
+    fill = "Time point") +
+  theme_personal +
+  scale_fill_manual(
+    values = COPINGpalette3,
+    breaks = c("prepan", "retro", "base"),
+    labels = c("base" = "Baseline", "prepan" = "Prepandemic", "retro" = "Retrospective")
+    )+
+  coord_flip()
+```
+
+```{r gad violin sum}
+dat.long.gad.sum %>%
+  filter(Time_point != "prepan") %>%
+  ggplot(mapping = aes(
+    x = Disorder_hierarchical,
+    y = gad.sum_score,
+    fill = Time_point)) +
+  geom_split_violin(
+#    color = textcolor,
+    trim = FALSE,
+    alpha = 0.5
+    ) +
+  labs(
+    x = "GAD7 scores",
+    y = "Percentage of participants",
+    fill = "Time point") +
+  theme_personal +
+  scale_fill_manual(
+    values = COPINGpalette3,
+    breaks = c("prepan", "retro", "base"),
+    labels = c("base" = "Baseline", "prepan" = "Prepandemic", "retro" = "Retrospective")
+    )+
+  coord_flip()
+```
+
+```{r gad violin sum}
+dat.long.gad.sum %>%
+  filter(Sample == "GLAD") %>%
+  filter(Time_point != "base") %>%
+  ggplot(mapping = aes(
+    x = Disorder_hierarchical,
+    y = gad.sum_score,
+    fill = Time_point)) +
+  geom_split_violin(
+#    color = textcolor,
+    trim = FALSE,
+    alpha = 0.5
+    ) +
+  labs(
+    x = "GAD7 scores",
+    y = "Percentage of participants",
+    fill = "Time point") +
+  theme_personal +
+  scale_fill_manual(
+    values = COPINGpalette3,
+    breaks = c("prepan", "retro", "base"),
+    labels = c("base" = "Baseline", "prepan" = "Prepandemic", "retro" = "Retrospective")
+    ) +
+  coord_flip()
+```
+
+```{r}
+data %>%
+  ggplot(aes(sex, dv, fill = face_sex)) +
+  geom_hline(yintercept=0, color=textcolor, size=1) +
+  geom_split_violin(color=textcolor, trim=FALSE, alpha = 0.5) +
+  geom_boxplot(color = textcolor, 
+               width = 0.25, 
+               position = position_dodge(width=0.25)) +
+  ylab("DV") +
+  xlab("Participant Sex") +
+  ylim(-5, 5) + 
+  scale_fill_manual(values = c("#3D66CC", "#892110")) +
+  my_theme
 ```
@@
       data_group_ocir == "All prepandemic, baseline and retrospective data")) &
-      prepandemic_march_1_numeric == 1
+      prepandemic_march_1_numeric == 1 # Exclude participants that signed up after the 1. March
   )

### 2020-09-29 PANCHANGE_analysis.Rmd

--- 2020-09-25 PANCHANGE_analysis.Rmd
@@
                              "Ethnicity_collapsed",
+                             "key_worker_numeric",
                              "time_diff_coping_lockdown_march_23"

### 2020-09-29 PANCHANGE_analysis.Rmd
KT Added full names to script

@@
 title: "PANCHANGE_analysis"
-author: "Katie Thompson, Topher Huebel, Molly Davies, Kirstin Purves"
+author: "Katherine N Thompson, Christopher Hüebel, Molly R Davies, Kirstin L Purves"
 date: Sys.Date()
@@
 
-Script written by K Purves, K Thompson, C Huebel and M Davies.
+Script written by K L Purves, K N Thompson, C Huebel and M Davies.
 Email: kirstin.purves@kcl.ac.uk, katie.thompson@kcl.ac.uk, christopher.1.huebel@kcl.ac.uk, molly.davies@kcl.ac.uk
@@
 #install.packages("patchwork")
-#instlal.packages("ggpubr")
+#install.packages("ggpubr")
 ```

### 2020-09-29 PANCHANGE_analysis.Rmd

@@
                              "Ethnicity_collapsed",
-                             "key_worker_numeric",
+                             "key_worker",
                              "time_diff_coping_lockdown_march_23"
@@
                "Ethnicity_collapsedOther" = "Other ethnicity",
+               "key_workerKey worker" = "Key worker",
                "time_diff_coping_lockdown_march_23" = "Time difference: Lockdown to baseline"
@@
                              "Ethnicity_collapsed",
+                             "key_worker",
                              "time_diff_coping_lockdown_march_23"
@@
 
-#GAD baseline, not controlling for prior symptoms
+# GAD baseline, not controlling for prior symptoms
 ### Model 0a: Disorder_hierarchical, Unadjusted
@@
 
-#PHQ baseline, not controlling for prior symptoms
+# PHQ baseline, not controlling for prior symptoms
 ### Model 0a: Disorder_hierarchical, Unadjusted

### 2020-09-30 PANCHANGE_analysis.Rmd
violin plots for, phq, gad, ocir

--- 2020-09-29 PANCHANGE_analysis.Rmd
@@
   facet_wrap("Disorder_hierarchical")
+```
+
+### Violin plots
+
+```{r gad.sum violin plot}
+dat.long.gad.sum %>%
+  mutate(Time_point_renamed = fct_recode(Time_point, 
+            "Prepandemic" = "prepan",
+            "Retrospective" = "retro",
+            "Baseline" = "base")
+         ) %>%
+         mutate(Time_point_reordered = fct_relevel(Time_point_renamed, 
+            "Baseline",
+            "Retrospective",
+            "Prepandemic")
+         ) %>%
+  ggplot(mapping = aes(
+    x = Time_point_reordered,
+    y = gad.sum_score,
+    fill = Time_point_reordered)) +
+  geom_hline(yintercept = 5, linetype = "dashed", color = "gray") +
+  geom_hline(yintercept = 10, linetype = "dashed", color = "gray") +
+  geom_hline(yintercept = 15, linetype = "dashed", color = "gray") +
+  geom_flat_violin(
+    position = position_nudge(x = .2, y = 0),
+    trim = FALSE,
+    alpha = 0.5
+    ) +
+  geom_point(
+    aes(
+      y = gad.sum_score,
+      color = Time_point_reordered),
+    position = position_jitter(width = .15),
+    size = .5,
+    alpha = 0.8) +
+#  geom_boxplot(
+#    width = .1,
+#    guides = FALSE,
+#    outlier.shape = NA,
+#    alpha = 0.5) +
+ stat_summary(fun.y = mean,
+              fun.ymin = function(x) mean(x) - sd(x), 
+              fun.ymax = function(x) mean(x) + sd(x), 
+              geom = "pointrange"
+              ) +
+  labs(
+    y = "GAD7 scores",
+    fill = "Time point") +
+  theme_personal +
+  theme(
+    axis.text.y = element_blank()
+  ) +
+  scale_fill_manual(
+    values = COPINGpalette3,
+    breaks = c("Prepandemic", "Retrospective", "Baseline")
+) +
+  scale_alpha(guide = 'none') +
+  scale_size(guide = 'none') +
+  scale_color_manual(
+    values = COPINGpalette3,
+    breaks = c("Prepandemic", "Retrospective", "Baseline"),
+    guide = "none") +
+  coord_flip()
+```
+
+```{r gad.sum violin plot Sample, fig.height=3.5, fig.width=2.5}
+dat.long.gad.sum %>%
+  mutate(Time_point_renamed = fct_recode(Time_point, 
+            "Prepandemic" = "prepan",
+            "Retrospective" = "retro",
+            "Baseline" = "base")
+         ) %>%
+         mutate(Time_point_reordered = fct_relevel(Time_point_renamed, 
+            "Baseline",
+            "Retrospective",
+            "Prepandemic")
+         ) %>%
+  ggplot(mapping = aes(
+    x = Time_point_reordered,
+    y = gad.sum_score,
+    fill = Time_point_reordered)) +
+  geom_hline(yintercept = 5, linetype = "dashed", color = "gray") +
+  geom_hline(yintercept = 10, linetype = "dashed", color = "gray") +
+  geom_hline(yintercept = 15, linetype = "dashed", color = "gray") +
+  geom_flat_violin(
+    position = position_nudge(x = .2, y = 0),
+    trim = FALSE,
+    alpha = 0.5
+    ) +
+  geom_point(
+    aes(
+      y = gad.sum_score,
+      color = Time_point_reordered),
+    position = position_jitter(width = .15),
+    size = .5,
+    alpha = 0.8) +
+#  geom_boxplot(
+#    width = .1,
+#    guides = FALSE,
+#    outlier.shape = NA,
+#    alpha = 0.5) +
+ stat_summary(fun.y = mean,
+              fun.ymin = function(x) mean(x) - sd(x), 
+              fun.ymax = function(x) mean(x) + sd(x), 
+              geom = "pointrange"
+              ) +
+  labs(
+    y = "GAD7 scores",
+    fill = "Time point") +
+  theme_personal +
+  theme(
+    axis.text.y = element_blank()
+  ) +
+  scale_fill_manual(
+    values = COPINGpalette3,
+    breaks = c("Prepandemic", "Retrospective", "Baseline")) +
+  scale_alpha(guide = 'none') +
+  scale_size(guide = 'none') +
+  scale_color_manual(
+    values = COPINGpalette3,
+    breaks = c("Prepandemic", "Retrospective", "Baseline"),
+    guide = "none") +
+  facet_wrap(facets = vars(Sample),
+             nrow = 4
+             ) +
+  coord_flip()
+```
+
+```{r gad.sum violin plot Disorder_hierarchical}
+dat.long.gad.sum %>%
+  mutate(Time_point_renamed = fct_recode(Time_point, 
+            "Prepandemic" = "prepan",
+            "Retrospective" = "retro",
+            "Baseline" = "base")
+         ) %>%
+         mutate(Time_point_reordered = fct_relevel(Time_point_renamed, 
+            "Baseline",
+            "Retrospective",
+            "Prepandemic")
+         ) %>%
+  ggplot(mapping = aes(
+    x = Time_point_reordered,
+    y = gad.sum_score,
+    fill = Time_point_reordered)) +
+  geom_hline(yintercept = 5, linetype = "dashed", color = "gray") +
+  geom_hline(yintercept = 10, linetype = "dashed", color = "gray") +
+  geom_hline(yintercept = 15, linetype = "dashed", color = "gray") +
+  geom_flat_violin(
+    position = position_nudge(x = .2, y = 0),
+    trim = FALSE,
+    alpha = 0.5
+    ) +
+  geom_point(
+    aes(
+      y = gad.sum_score,
+      color = Time_point_reordered),
+    position = position_jitter(width = .15),
+    size = .5,
+    alpha = 0.8) +
+#  geom_boxplot(
+#    width = .1,
+#    guides = FALSE,
+#    outlier.shape = NA,
+#    alpha = 0.5) +
+ stat_summary(fun.y = mean,
+              fun.ymin = function(x) mean(x) - sd(x), 
+              fun.ymax = function(x) mean(x) + sd(x), 
+              geom = "pointrange"
+              ) +
+  labs(
+    y = "GAD7 scores",
+    fill = "Time point") +
+  theme_personal +
+  theme(
+    axis.text.y = element_blank()
+  ) +
+  scale_fill_manual(
+    values = COPINGpalette3,
+    breaks = c("Prepandemic", "Retrospective", "Baseline")) +
+  scale_alpha(guide = 'none') +
+  scale_size(guide = 'none') +
+  scale_color_manual(
+    values = COPINGpalette3,
+    breaks = c("Prepandemic", "Retrospective", "Baseline"),
+    guide = "none") +
+  facet_wrap(facets = vars(Disorder_hierarchical)
+             ) +
+  coord_flip()
 ```
@@
   facet_wrap("Disorder_hierarchical")
+```
+
+### Violin plots
+
+```{r phq.sum violin plot}
+dat.long.phq.sum %>%
+  mutate(Time_point_renamed = fct_recode(Time_point, 
+                                         "Prepandemic" = "prepan",
+                                         "Retrospective" = "retro",
+                                         "Baseline" = "base")
+  ) %>%
+  mutate(Time_point_reordered = fct_relevel(Time_point_renamed, 
+                                            "Baseline",
+                                            "Retrospective",
+                                            "Prepandemic")
+  ) %>%
+  ggplot(mapping = aes(
+    x = Time_point_reordered,
+    y = phq.sum_score,
+    fill = Time_point_reordered)) +
+  geom_hline(yintercept = 8, linetype = "dashed", color = "gray") +
+  geom_hline(yintercept = 11, linetype = "dashed", color = "gray") +
+#  geom_hline(yintercept = 15, linetype = "dashed", color = "gray") +
+  geom_flat_violin(
+    position = position_nudge(x = .2, y = 0),
+    trim = FALSE,
+    alpha = 0.5
+  ) +
+  geom_point(
+    aes(
+      y = phq.sum_score,
+      color = Time_point_reordered),
+    position = position_jitter(width = .15),
+    size = .5,
+    alpha = 0.8) +
+  #  geom_boxplot(
+  #    width = .1,
+  #    guides = FALSE,
+  #    outlier.shape = NA,
+  #    alpha = 0.5) +
+  stat_summary(fun.y = mean,
+               fun.ymin = function(x) mean(x) - sd(x), 
+               fun.ymax = function(x) mean(x) + sd(x), 
+               geom = "pointrange"
+  ) +
+  labs(
+    y = "PHQ9 scores",
+    fill = "Time point") +
+  theme_personal +
+  theme(
+    axis.text.y = element_blank()
+  ) +
+  scale_fill_manual(
+    values = COPINGpalette3,
+    breaks = c("Prepandemic", "Retrospective", "Baseline")
+  ) +
+  scale_alpha(guide = 'none') +
+  scale_size(guide = 'none') +
+  scale_color_manual(
+    values = COPINGpalette3,
+    breaks = c("Prepandemic", "Retrospective", "Baseline"),
+    guide = "none") +
+  coord_flip()
+```
+
+```{r phq.sum violin plot Sample, fig.height=3.5, fig.width=2.5}
+dat.long.phq.sum %>%
+  mutate(Time_point_renamed = fct_recode(Time_point, 
+                                         "Prepandemic" = "prepan",
+                                         "Retrospective" = "retro",
+                                         "Baseline" = "base")
+  ) %>%
+  mutate(Time_point_reordered = fct_relevel(Time_point_renamed, 
+                                            "Baseline",
+                                            "Retrospective",
+                                            "Prepandemic")
+  ) %>%
+  ggplot(mapping = aes(
+    x = Time_point_reordered,
+    y = phq.sum_score,
+    fill = Time_point_reordered)) +
+  geom_hline(yintercept = 8, linetype = "dashed", color = "gray") +
+  geom_hline(yintercept = 11, linetype = "dashed", color = "gray") +
+#  geom_hline(yintercept = 15, linetype = "dashed", color = "gray") +
+  geom_flat_violin(
+    position = position_nudge(x = .2, y = 0),
+    trim = FALSE,
+    alpha = 0.5
+  ) +
+  geom_point(
+    aes(
+      y = phq.sum_score,
+      color = Time_point_reordered),
+    position = position_jitter(width = .15),
+    size = .5,
+    alpha = 0.8) +
+  #  geom_boxplot(
+  #    width = .1,
+  #    guides = FALSE,
+  #    outlier.shape = NA,
+  #    alpha = 0.5) +
+  stat_summary(fun.y = mean,
+               fun.ymin = function(x) mean(x) - sd(x), 
+               fun.ymax = function(x) mean(x) + sd(x), 
+               geom = "pointrange"
+  ) +
+  labs(
+    y = "PHQ9 scores",
+    fill = "Time point") +
+  theme_personal +
+  theme(
+    axis.text.y = element_blank()
+  ) +
+  scale_fill_manual(
+    values = COPINGpalette3,
+    breaks = c("Prepandemic", "Retrospective", "Baseline")) +
+  scale_alpha(guide = 'none') +
+  scale_size(guide = 'none') +
+  scale_color_manual(
+    values = COPINGpalette3,
+    breaks = c("Prepandemic", "Retrospective", "Baseline"),
+    guide = "none") +
+  facet_wrap(facets = vars(Sample),
+             nrow = 4
+  ) +
+  coord_flip()
+```
+
+```{r phq.sum violin plot Disorder_hierarchical}
+dat.long.phq.sum %>%
+  mutate(Time_point_renamed = fct_recode(Time_point, 
+                                         "Prepandemic" = "prepan",
+                                         "Retrospective" = "retro",
+                                         "Baseline" = "base")
+  ) %>%
+  mutate(Time_point_reordered = fct_relevel(Time_point_renamed, 
+                                            "Baseline",
+                                            "Retrospective",
+                                            "Prepandemic")
+  ) %>%
+  ggplot(mapping = aes(
+    x = Time_point_reordered,
+    y = phq.sum_score,
+    fill = Time_point_reordered)) +
+  geom_hline(yintercept = 8, linetype = "dashed", color = "gray") +
+  geom_hline(yintercept = 11, linetype = "dashed", color = "gray") +
+#  geom_hline(yintercept = 15, linetype = "dashed", color = "gray") +
+  geom_flat_violin(
+    position = position_nudge(x = .2, y = 0),
+    trim = FALSE,
+    alpha = 0.5
+  ) +
+  geom_point(
+    aes(
+      y = phq.sum_score,
+      color = Time_point_reordered),
+    position = position_jitter(width = .15),
+    size = .5,
+    alpha = 0.8) +
+  #  geom_boxplot(
+  #    width = .1,
+  #    guides = FALSE,
+  #    outlier.shape = NA,
+  #    alpha = 0.5) +
+  stat_summary(fun.y = mean,
+               fun.ymin = function(x) mean(x) - sd(x), 
+               fun.ymax = function(x) mean(x) + sd(x), 
+               geom = "pointrange"
+  ) +
+  labs(
+    y = "PHQ9 scores",
+    fill = "Time point") +
+  theme_personal +
+  theme(
+    axis.text.y = element_blank()
+  ) +
+  scale_fill_manual(
+    values = COPINGpalette3,
+    breaks = c("Prepandemic", "Retrospective", "Baseline")) +
+  scale_alpha(guide = 'none') +
+  scale_size(guide = 'none') +
+  scale_color_manual(
+    values = COPINGpalette3,
+    breaks = c("Prepandemic", "Retrospective", "Baseline"),
+    guide = "none") +
+  facet_wrap(facets = vars(Disorder_hierarchical)
+  ) +
+  coord_flip()
 ```
@@
 
+### Violin plots
+
+```{r ocir.sum violin plot}
+dat.long.ocir.sum %>%
+  mutate(Time_point_renamed = fct_recode(Time_point, 
+                                         "Prepandemic" = "prepan",
+                                         "Retrospective" = "retro",
+                                         "Baseline" = "base")
+  ) %>%
+  mutate(Time_point_reordered = fct_relevel(Time_point_renamed, 
+                                            "Baseline",
+                                            "Retrospective",
+                                            "Prepandemic")
+  ) %>%
+  ggplot(mapping = aes(
+    x = Time_point_reordered,
+    y = ocir.sum_score,
+    fill = Time_point_reordered)) +
+  geom_hline(yintercept = 21, linetype = "dashed", color = "gray") +
+#  geom_hline(yintercept = 10, linetype = "dashed", color = "gray") +
+#  geom_hline(yintercept = 15, linetype = "dashed", color = "gray") +
+  geom_flat_violin(
+    position = position_nudge(x = .2, y = 0),
+    trim = FALSE,
+    alpha = 0.5
+  ) +
+  geom_point(
+    aes(
+      y = ocir.sum_score,
+      color = Time_point_reordered),
+    position = position_jitter(width = .15),
+    size = .5,
+    alpha = 0.8) +
+  #  geom_boxplot(
+  #    width = .1,
+  #    guides = FALSE,
+  #    outlier.shape = NA,
+  #    alpha = 0.5) +
+  stat_summary(fun.y = mean,
+               fun.ymin = function(x) mean(x) - sd(x), 
+               fun.ymax = function(x) mean(x) + sd(x), 
+               geom = "pointrange"
+  ) +
+  labs(
+    y = "OCI-R scores",
+    fill = "Time point") +
+  theme_personal +
+  theme(
+    axis.text.y = element_blank()
+  ) +
+  scale_fill_manual(
+    values = COPINGpalette3,
+    breaks = c("Prepandemic", "Retrospective", "Baseline")
+  ) +
+  scale_alpha(guide = 'none') +
+  scale_size(guide = 'none') +
+  scale_color_manual(
+    values = COPINGpalette3,
+    breaks = c("Prepandemic", "Retrospective", "Baseline"),
+    guide = "none") +
+  coord_flip()
+```
+
+```{r ocir.sum violin plot Sample, fig.height=3.5, fig.width=2.5}
+dat.long.ocir.sum %>%
+  mutate(Time_point_renamed = fct_recode(Time_point, 
+                                         "Prepandemic" = "prepan",
+                                         "Retrospective" = "retro",
+                                         "Baseline" = "base")
+  ) %>%
+  mutate(Time_point_reordered = fct_relevel(Time_point_renamed, 
+                                            "Baseline",
+                                            "Retrospective",
+                                            "Prepandemic")
+  ) %>%
+  ggplot(mapping = aes(
+    x = Time_point_reordered,
+    y = ocir.sum_score,
+    fill = Time_point_reordered)) +
+  geom_hline(yintercept = 21, linetype = "dashed", color = "gray") +
+#  geom_hline(yintercept = 10, linetype = "dashed", color = "gray") +
+#  geom_hline(yintercept = 15, linetype = "dashed", color = "gray") +
+  geom_flat_violin(
+    position = position_nudge(x = .2, y = 0),
+    trim = FALSE,
+    alpha = 0.5
+  ) +
+  geom_point(
+    aes(
+      y = ocir.sum_score,
+      color = Time_point_reordered),
+    position = position_jitter(width = .15),
+    size = .5,
+    alpha = 0.8) +
+  #  geom_boxplot(
+  #    width = .1,
+  #    guides = FALSE,
+  #    outlier.shape = NA,
+  #    alpha = 0.5) +
+  stat_summary(fun.y = mean,
+               fun.ymin = function(x) mean(x) - sd(x), 
+               fun.ymax = function(x) mean(x) + sd(x), 
+               geom = "pointrange"
+  ) +
+  labs(
+    y = "OCI-R scores",
+    fill = "Time point") +
+  theme_personal +
+  theme(
+    axis.text.y = element_blank()
+  ) +
+  scale_fill_manual(
+    values = COPINGpalette3,
+    breaks = c("Prepandemic", "Retrospective", "Baseline")) +
+  scale_alpha(guide = 'none') +
+  scale_size(guide = 'none') +
+  scale_color_manual(
+    values = COPINGpalette3,
+    breaks = c("Prepandemic", "Retrospective", "Baseline"),
+    guide = "none") +
+  facet_wrap(facets = vars(Sample),
+             nrow = 4
+  ) +
+  coord_flip()
+```
+
+```{r ocir.sum violin plot Disorder_hierarchical}
+dat.long.ocir.sum %>%
+  mutate(Time_point_renamed = fct_recode(Time_point, 
+                                         "Prepandemic" = "prepan",
+                                         "Retrospective" = "retro",
+                                         "Baseline" = "base")
+  ) %>%
+  mutate(Time_point_reordered = fct_relevel(Time_point_renamed, 
+                                            "Baseline",
+                                            "Retrospective",
+                                            "Prepandemic")
+  ) %>%
+  ggplot(mapping = aes(
+    x = Time_point_reordered,
+    y = ocir.sum_score,
+    fill = Time_point_reordered)) +
+  geom_hline(yintercept = 21, linetype = "dashed", color = "gray") +
+#  geom_hline(yintercept = 10, linetype = "dashed", color = "gray") +
+#  geom_hline(yintercept = 15, linetype = "dashed", color = "gray") +
+  geom_flat_violin(
+    position = position_nudge(x = .2, y = 0),
+    trim = FALSE,
+    alpha = 0.5
+  ) +
+  geom_point(
+    aes(
+      y = ocir.sum_score,
+      color = Time_point_reordered),
+    position = position_jitter(width = .15),
+    size = .5,
+    alpha = 0.8) +
+  #  geom_boxplot(
+  #    width = .1,
+  #    guides = FALSE,
+  #    outlier.shape = NA,
+  #    alpha = 0.5) +
+  stat_summary(fun.y = mean,
+               fun.ymin = function(x) mean(x) - sd(x), 
+               fun.ymax = function(x) mean(x) + sd(x), 
+               geom = "pointrange"
+  ) +
+  labs(
+    y = "OCI-R scores",
+    fill = "Time point") +
+  theme_personal +
+  theme(
+    axis.text.y = element_blank()
+  ) +
+  scale_fill_manual(
+    values = COPINGpalette3,
+    breaks = c("Prepandemic", "Retrospective", "Baseline")) +
+  scale_alpha(guide = 'none') +
+  scale_size(guide = 'none') +
+  scale_color_manual(
+    values = COPINGpalette3,
+    breaks = c("Prepandemic", "Retrospective", "Baseline"),
+    guide = "none") +
+  facet_wrap(facets = vars(Disorder_hierarchical)
+  ) +
+  coord_flip()
+```
+
 ++CH: Rank the disorders by the size of the change
@@
                             "Ethnicity_collapsed",
-                            "time_diff_coping_lockdown_march_23"
+                            "time_diff_sign_up_coping"
                             )
@@
                "Ethnicity_collapsedOther" = "Other ethnicity",
-               "time_diff_coping_lockdown_march_23" = "Time difference: Lockdown to baseline"
+               "time_diff_sign_up_coping" = "Time difference: prepandemic to COPING"
              ),
@@
                              "Ethnicity_collapsed",
-                             "key_worker_numeric",
-                             "time_diff_coping_lockdown_march_23"
+                             "time_diff_sign_up_coping"
                                 )
@@
                              "Ethnicity_collapsed",
-                             "time_diff_coping_lockdown_march_23"
+                             "time_diff_sign_up_coping"
   )
@@
 
-#GAD baseline, not controlling for prior symptoms
-### Model 0a: Disorder_hierarchical, Unadjusted
-```{r gad model0a absolute whole sample}
-# Regression coefficients
-gad_baseline_model0a_estimates <- model0a.estimates(outcome = "gad.sum_score_base",
-                                                 data_set = "dat")
-kable(gad_baseline_model0a_estimates)
-gad_baseline_model0a_estimates
-
-# Regression diagnostic statistics
-gad_baseline_model0a_reg_stats <- model0a.reg.stats(outcome = "gad.sum_score_base",
-                                                 data_set = "dat")
-kable(gad_baseline_model0a_reg_stats)
-gad_baseline_model0a_reg_stats
-```
-
-### Model 0b: Overlapping disorders, Unadjusted
-```{r gad model0b absolute whole sample}
-# Regression coefficients
-gad_baseline_model0b_estimates <- model0b.estimates(outcome = "gad.sum_score_base",
-                                                 data_set = "dat")
-kable(gad_baseline_model0b_estimates)
-gad_baseline_model0b_estimates
-
-# Regression diagnostic statistics
-gad_baseline_model0b_reg_stats <- model0b.reg.stats(outcome = "gad.sum_score_base",
-                                                 data_set = "dat")
-kable(gad_baseline_model0b_reg_stats)
-gad_baseline_model0b_reg_stats
-```
-
-### Model 1a: Disorder hierarchical, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
-```{r gad model1a absolute whole sample}
-# Regression coefficients
-gad_baseline_model1a_estimates <- model1a.estimates(outcome = "gad.sum_score_base",
-                                                 data_set = "dat")
-kable(gad_baseline_model1a_estimates)
-gad_baseline_model1a_estimates
-
-# Regression diagnostic statistics
-gad_baseline_model1a_reg_stats <- model1a.reg.stats(outcome = "gad.sum_score_base",
-                                                 data_set = "dat")
-kable(gad_baseline_model1a_reg_stats)
-gad_baseline_model1a_reg_stats
-```
-
-### Model 1b: Overlapping disorders, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
-```{r gad model1b absolute whole sample}
-# Regression coefficients
-gad_baseline_model1b_estimates <- model1b.estimates(outcome = "gad.sum_score_base",
-                                                 data_set = "dat")
-kable(gad_baseline_model1b_estimates)
-gad_baseline_model1b_estimates
-
-# Regression diagnostic statistics
-gad_baseline_model1b_reg_stats <- model1b.reg.stats(outcome = "gad.sum_score_base",
-                                                 data_set = "dat")
-kable(gad_baseline_model1b_reg_stats)
-gad_baseline_model1b_reg_stats
-```
-
 # GAD prepan
@@
 
-#PHQ baseline, not controlling for prior symptoms
-### Model 0a: Disorder_hierarchical, Unadjusted
-```{r phq model0a absolute whole sample}
-# Regression coefficients
-phq_baseline_model0a_estimates <- model0a.estimates(outcome = "phq.sum_score_base",
-                                                 data_set = "dat")
-kable(phq_baseline_model0a_estimates)
-phq_baseline_model0a_estimates
-
-# Regression diagnostic statistics
-phq_baseline_model0a_reg_stats <- model0a.reg.stats(outcome = "phq.sum_score_base",
-                                                 data_set = "dat")
-kable(phq_baseline_model0a_reg_stats)
-phq_baseline_model0a_reg_stats
-```
-
-### Model 0b: Overlapping disorders, Unadjusted
-```{r phq model0b absolute whole sample}
-# Regression coefficients
-phq_baseline_model0b_estimates <- model0b.estimates(outcome = "phq.sum_score_base",
-                                                 data_set = "dat")
-kable(phq_baseline_model0b_estimates)
-phq_baseline_model0b_estimates
-
-# Regression diagnostic statistics
-phq_baseline_model0b_reg_stats <- model0b.reg.stats(outcome = "phq.sum_score_base",
-                                                 data_set = "dat")
-kable(phq_baseline_model0b_reg_stats)
-phq_baseline_model0b_reg_stats
-```
-
-### Model 1a: Disorder hierarchical, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
-```{r phq model1a absolute whole sample}
-# Regression coefficients
-phq_baseline_model1a_estimates <- model1a.estimates(outcome = "phq.sum_score_base",
-                                                 data_set = "dat")
-kable(phq_baseline_model1a_estimates)
-phq_baseline_model1a_estimates
-
-# Regression diagnostic statistics
-phq_baseline_model1a_reg_stats <- model1a.reg.stats(outcome = "phq.sum_score_base",
-                                                 data_set = "dat")
-kable(phq_baseline_model1a_reg_stats)
-phq_baseline_model1a_reg_stats
-```
-
-### Model 1b: Overlapping disorders, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
-```{r phq model1b absolute whole sample}
-# Regression coefficients
-phq_baseline_model1b_estimates <- model1b.estimates(outcome = "phq.sum_score_base",
-                                                 data_set = "dat")
-kable(phq_baseline_model1b_estimates)
-phq_baseline_model1b_estimates
-
-# Regression diagnostic statistics
-phq_baseline_model1b_reg_stats <- model1b.reg.stats(outcome = "phq.sum_score_base",
-                                                 data_set = "dat")
-kable(phq_baseline_model1b_reg_stats)
-phq_baseline_model1b_reg_stats
-```
-
 # PHQ prepan
@@
 
-# OCI-R baseline, not controlling for prior symptoms
-### Model 0a: Disorder_hierarchical, Unadjusted
-```{r ocir model0a absolute whole sample}
-# Regression coefficients
-ocir_baseline_model0a_estimates <- model0a.estimates(outcome = "ocir.sum_score_base",
-                                                 data_set = "dat")
-kable(ocir_baseline_model0a_estimates)
-ocir_baseline_model0a_estimates
-
-# Regression diagnostic statistics
-ocir_baseline_model0a_reg_stats <- model0a.reg.stats(outcome = "ocir.sum_score_base",
-                                                 data_set = "dat")
-kable(ocir_baseline_model0a_reg_stats)
-ocir_baseline_model0a_reg_stats
-```
-
-### Model 0b: Overlapping disorders, Unadjusted
-```{r ocir model0b absolute whole sample}
-# Regression coefficients
-ocir_baseline_model0b_estimates <- model0b.estimates(outcome = "ocir.sum_score_base",
-                                                 data_set = "dat")
-kable(ocir_baseline_model0b_estimates)
-ocir_baseline_model0b_estimates
-
-# Regression diagnostic statistics
-ocir_baseline_model0b_reg_stats <- model0b.reg.stats(outcome = "ocir.sum_score_base",
-                                                 data_set = "dat")
-kable(ocir_baseline_model0b_reg_stats)
-ocir_baseline_model0b_reg_stats
-```
-
-### Model 1a: Disorder hierarchical, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
-```{r ocir model1a absolute whole sample}
-# Regression coefficients
-ocir_baseline_model1a_estimates <- model1a.estimates(outcome = "ocir.sum_score_base",
-                                                 data_set = "dat")
-kable(ocir_baseline_model1a_estimates)
-ocir_baseline_model1a_estimates
-
-# Regression diagnostic statistics
-ocir_baseline_model1a_reg_stats <- model1a.reg.stats(outcome = "ocir.sum_score_base",
-                                                 data_set = "dat")
-kable(ocir_baseline_model1a_reg_stats)
-ocir_baseline_model1a_reg_stats
-```
-
-### Model 1b: Overlapping disorders, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
-```{r ocir model1b absolute whole sample}
-# Regression coefficients
-ocir_baseline_model1b_estimates <- model1b.estimates(outcome = "ocir.sum_score_base",
-                                                 data_set = "dat")
-kable(ocir_baseline_model1b_estimates)
-ocir_baseline_model1b_estimates
-
-# Regression diagnostic statistics
-ocir_baseline_model1b_reg_stats <- model1b.reg.stats(outcome = "ocir.sum_score_base",
-                                                 data_set = "dat")
-kable(ocir_baseline_model1b_reg_stats)
-ocir_baseline_model1b_reg_stats
-```
-
 # OCIR prepan
@@
 
-# PCL baseline, not controlling for prior symptoms
-### Model 0a: Disorder_hierarchical, Unadjusted
-```{r pcl model0a absolute whole sample}
-# Regression coefficients
-pcl_baseline_model0a_estimates <- model0a.estimates(outcome = "pcl.sum_score_base",
-                                                 data_set = "dat")
-kable(pcl_baseline_model0a_estimates)
-pcl_baseline_model0a_estimates
-
-# Regression diagnostic statistics
-pcl_baseline_model0a_reg_stats <- model0a.reg.stats(outcome = "pcl.sum_score_base",
-                                                 data_set = "dat")
-kable(pcl_baseline_model0a_reg_stats)
-pcl_baseline_model0a_reg_stats
-```
-
-### Model 0b: Overlapping disorders, Unadjusted
-```{r pcl model0b absolute whole sample}
-# Regression coefficients
-pcl_baseline_model0b_estimates <- model0b.estimates(outcome = "pcl.sum_score_base",
-                                                 data_set = "dat")
-kable(pcl_baseline_model0b_estimates)
-pcl_baseline_model0b_estimates
-
-# Regression diagnostic statistics
-pcl_baseline_model0b_reg_stats <- model0b.reg.stats(outcome = "pcl.sum_score_base",
-                                                 data_set = "dat")
-kable(pcl_baseline_model0b_reg_stats)
-pcl_baseline_model0b_reg_stats
-```
-
-### Model 1a: Disorder hierarchical, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
-```{r pcl model1a absolute whole sample}
-# Regression coefficients
-pcl_baseline_model1a_estimates <- model1a.estimates(outcome = "pcl.sum_score_base",
-                                                 data_set = "dat")
-kable(pcl_baseline_model1a_estimates)
-pcl_baseline_model1a_estimates
-
-# Regression diagnostic statistics
-pcl_baseline_model1a_reg_stats <- model1a.reg.stats(outcome = "pcl.sum_score_base",
-                                                 data_set = "dat")
-kable(pcl_baseline_model1a_reg_stats)
-pcl_baseline_model1a_reg_stats
-```
-
-### Model 1b: Overlapping disorders, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
-```{r pcl model1b absolute whole sample}
-# Regression coefficients
-pcl_baseline_model1b_estimates <- model1b.estimates(outcome = "pcl.sum_score_base",
-                                                 data_set = "dat")
-kable(pcl_baseline_model1b_estimates)
-pcl_baseline_model1b_estimates
-
-# Regression diagnostic statistics
-pcl_baseline_model1b_reg_stats <- model1b.reg.stats(outcome = "pcl.sum_score_base",
-                                                 data_set = "dat")
-kable(pcl_baseline_model1b_reg_stats)
-pcl_baseline_model1b_reg_stats
-```
-
 # PCL prepan

### 2020-10-01 PANCHANGE_data_preprocessing2020-07-15.Rmd
a few summaries had the wrong variable name

@@
 
-summary(dat$phq.diff_score_prepan_retro)
+summary(dat$phq.diff_score_retro_prepan)
 
@@
 
-summary(dat$phq.diff_score_prepan_base)
+summary(dat$phq.diff_score_base_prepan)
 }
@@
 
-summary(dat$gad.diff_score_prepan_base)
+summary(dat$gad.diff_score_base_prepan)
 }
@@
 
-summary(dat$pcl.diff_score_prepan_base)
+summary(dat$pcl.diff_score_base_prepan)
 }
@@
 
-summary(dat$ocir.diff_score_prepan_base)
+summary(dat$ocir.diff_score_base_prepan)
 }

### 2020-10-01 archive/PANCHANGE_plot_backup.Rmd

---
title: "PANCHANGE_plot_backup"
author: "Christopher Huebel"
date: "30/09/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
summary_data <- dat.long.gad.sum %>%
  group_by(Time_point) %>%
  summarise(
    mean = mean(gad.sum_score, na.rm = T),
    min = mean(gad.sum_score, na.rm = T) - qnorm(0.975)*sd(gad.sum_score, na.rm = T)/sqrt(n()),
    max = mean(gad.sum_score, na.rm = T) + qnorm(0.975)*sd(gad.sum_score, na.rm = T)/sqrt(n()),
    sd_low = mean(gad.sum_score, na.rm = T) - sd(gad.sum_score, na.rm = T),
    sd_up = mean(gad.sum_score, na.rm = T) + sd(gad.sum_score, na.rm = T)
  )

summary_data
```

```{r gad violin sum}
violin.gad.sum.prepan.retro <- dat.long.gad.sum %>%
  filter(Time_point != "base") %>%
  ggplot(mapping = aes(
    x = Full_cohort,
    y = gad.sum_score,
    fill = Time_point)) +
    geom_hline(yintercept = 5, linetype = "dashed", color = "gray") +
  geom_hline(yintercept = 10, linetype = "dashed", color = "gray") +
  geom_hline(yintercept = 15, linetype = "dashed", color = "gray") +
  geom_split_violin(
    trim = FALSE,
    alpha = 0.5
    ) +
 stat_summary(fun.y = mean,
               fun.ymin = function(x) mean(x) - sd(x), 
               fun.ymax = function(x) mean(x) + sd(x), 
               geom = "pointrange",
              position = position_dodge(width = .25)) +
    labs(
    x = "GAD7 scores",
    y = "Percentage of participants",
    fill = "Time point") +
  theme_personal +
  scale_fill_manual(
    values = COPINGpalette3,
    breaks = c("prepan", "retro", "base"),
    labels = c("base" = "Baseline", "prepan" = "Prepandemic", "retro" = "Retrospective")
    )
violin.gad.sum.prepan.retro

violin.gad.sum.prepan.base <- dat.long.gad.sum %>%
  filter(Time_point != "retro") %>%
  ggplot(mapping = aes(
    x = Full_cohort,
    y = gad.sum_score,
    fill = Time_point)) +
    geom_hline(yintercept = 5, linetype = "dashed", color = "gray") +
  geom_hline(yintercept = 10, linetype = "dashed", color = "gray") +
  geom_hline(yintercept = 15, linetype = "dashed", color = "gray") +
  geom_split_violin(
    trim = FALSE,
    alpha = 0.5
    ) +
 stat_summary(fun.y = mean,
               fun.ymin = function(x) mean(x) - sd(x), 
               fun.ymax = function(x) mean(x) + sd(x), 
               geom = "pointrange",
              position = position_dodge(width = .25)) +
  labs(
    x = "GAD7 scores",
    y = "Percentage of participants",
    fill = "Time point") +
  theme_personal +
  scale_fill_manual(
    values = COPINGpalette3,
    breaks = c("prepan", "retro", "base"),
    labels = c("base" = "Baseline", "prepan" = "Prepandemic", "retro" = "Retrospective")
    )
violin.gad.sum.prepan.base

violin.gad.sum.retro.base <- dat.long.gad.sum %>%
  filter(Time_point != "prepan") %>%
  ggplot(mapping = aes(
    x = Full_cohort,
    y = gad.sum_score,
    fill = Time_point)) +
    geom_hline(yintercept = 5, linetype = "dashed", color = "gray") +
  geom_hline(yintercept = 10, linetype = "dashed", color = "gray") +
  geom_hline(yintercept = 15, linetype = "dashed", color = "gray") +
  geom_split_violin(
    trim = FALSE,
    alpha = 0.5
    ) +
 stat_summary(fun.y = mean,
               fun.ymin = function(x) mean(x) - sd(x), 
               fun.ymax = function(x) mean(x) + sd(x), 
               geom = "pointrange",
              position = position_dodge(width = .25)) +
  labs(
    x = "GAD7 scores",
    y = "Percentage of participants",
    fill = "Time point") +
  theme_personal +
  scale_fill_manual(
    values = COPINGpalette3,
    breaks = c("prepan", "retro", "base"),
    labels = c("base" = "Baseline", "prepan" = "Prepandemic", "retro" = "Retrospective")
    )
violin.gad.sum.retro.base

violin.gad.sum.prepan.retro +
  violin.gad.sum.prepan.base +
  violin.gad.sum.retro.base +
  plot_layout(guides = "collect", widths = c(1,1,1)) +
  plot_annotation(tag_levels = "A")
```

```{r gad violin sum}
dat.long.gad.sum %>%
  filter(Time_point != "base") %>%
  ggplot(mapping = aes(
    x = Sample,
    y = gad.sum_score,
    fill = Time_point)) +
  geom_split_violin(
#    color = textcolor,
    trim = FALSE,
    alpha = 0.5
    ) +
  labs(
    x = "GAD7 scores",
    y = "Percentage of participants",
    fill = "Time point") +
  theme_personal +
  scale_fill_manual(
    values = COPINGpalette3,
    breaks = c("prepan", "retro", "base"),
    labels = c("base" = "Baseline", "prepan" = "Prepandemic", "retro" = "Retrospective")
    )+
  coord_flip()
```

```{r gad violin sum}
dat.long.gad.sum %>%
  filter(Time_point != "base") %>%
  ggplot(mapping = aes(
    x = Disorder_hierarchical,
    y = gad.sum_score,
    fill = Time_point)) +
  geom_split_violin(
#    color = textcolor,
    trim = FALSE,
    alpha = 0.5
    ) +
  labs(
    x = "GAD7 scores",
    y = "Percentage of participants",
    fill = "Time point") +
  theme_personal +
  scale_fill_manual(
    values = COPINGpalette3,
    breaks = c("prepan", "retro", "base"),
    labels = c("base" = "Baseline", "prepan" = "Prepandemic", "retro" = "Retrospective")
    )+
  coord_flip()
```

### 2020-10-02 PANCHANGE_data_preprocessing2020-07-15.Rmd

@@
       recode_factor(Ethnicity_unc,
-        "White" = "European",
+        "White" = "White",
         "Mixed" = "Mixed or multiple ethnic origins",
         "Asian or Asian British" = "Asian or Asian British",
-        "Black or Black British" = "African or African British",
+        "Black or Black British" = "Black or Black British",
         "Arab" = "Arab",
@@
       recode_factor(Ethnicity_unc,
-        "White, white European or Caucasian" = "European",
+        "White, white European or Caucasian" = "White",
         "Mixed or multiple ethnic origins" = "Mixed or multiple ethnic origins",
         "Asian or Asian British (including Chinese)" = "Asian or Asian British",
-        "Black or Black British" = "African or African British",
+        "Black or Black British" = "Black or Black British",
         "Arab" = "Arab",
@@
       recode(Ethnicity,
-        "European" = 1,
+        "White" = 1,
         "Mixed or multiple ethnic origins" = 2,
         "Asian or Asian British" = 3,
-        "African or African British" = 4,
+        "Black or Black British" = 4,
         "Arab" = 5,

### 2020-10-09 PANCHANGE_analysis.Rmd
Dataset for retro sensitivity analsyes created. GAD and PHQ 9 retrospective regressions were added using the sensitivity dataset for these analyses.

@@
       data_group_ocir == "All prepandemic, baseline and retrospective data")) &
+      prepandemic_march_1_numeric == 1 # Exclude participants that signed up after the 1. March
+  )
+
+dim(dat.prepan)
+```
+
+Prepan-baseline analyses
+Exclude individuals with NA for MHD, age, gender; exclude if prepan data collected after 1 March
+
+```{r subsample for retro sensitivity analysis}
+dat.retro_sensitivity <- dat %>%
+  filter(
+    ((data_group_gad == "All prepandemic, baseline and retrospective data") |
+      (data_group_phq == "All prepandemic, baseline and retrospective data") |
+      (data_group_pcl == "All prepandemic, baseline and retrospective data") |
+      (data_group_ocir == "All prepandemic, baseline and retrospective data")) &
       prepandemic_march_1_numeric == 1 # Exclude participants that signed up after the 1. March
@@
 
+# GAD retro: sensitivity
+## Regression: Change scores
+### Model 0a: Disorder_hierarchical, Unadjusted
+```{r gad model0a diff_score retro (sensitivity analysis)}
+# Regression coefficients
+gad_retro_model0a_estimates <- model0a.estimates(outcome = "gad.diff_score_base_retro",
+                                                 data_set = "dat.retro_sensitivity")
+kable(gad_retro_model0a_estimates)
+gad_retro_model0a_estimates
+
+# Regression diagnostic statistics
+gad_retro_model0a_reg_stats <- model0a.reg.stats(outcome = "gad.diff_score_base_retro",
+                                                 data_set = "dat.retro_sensitivity")
+kable(gad_retro_model0a_reg_stats)
+gad_retro_model0a_reg_stats
+```
+
+### Model 0b: Overlapping disorders, Unadjusted
+```{r gad model0b diff_score retro (sensitivity analysis)}
+# Regression coefficients
+gad_retro_model0b_estimates <- model0b.estimates(outcome = "gad.diff_score_base_retro",
+                                                 data_set = "dat.retro_sensitivity")
+kable(gad_retro_model0b_estimates)
+gad_retro_model0b_estimates
+
+# Regression diagnostic statistics
+gad_retro_model0b_reg_stats <- model0b.reg.stats(outcome = "gad.diff_score_base_retro",
+                                                 data_set = "dat.retro_sensitivity")
+kable(gad_retro_model0b_reg_stats)
+gad_retro_model0b_reg_stats
+```
+
+### Model 1a: Disorder hierarchical, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r gad model1a diff_score retro (sensitivity analysis)}
+# Regression coefficients
+gad_retro_model1a_estimates <- model1a.estimates(outcome = "gad.diff_score_base_retro",
+                                                 data_set = "dat.retro_sensitivity")
+kable(gad_retro_model1a_estimates)
+gad_retro_model1a_estimates
+
+# Regression diagnostic statistics
+gad_retro_model1a_reg_stats <- model1a.reg.stats(outcome = "gad.diff_score_base_retro",
+                                                 data_set = "dat.retro_sensitivity")
+kable(gad_retro_model1a_reg_stats)
+gad_retro_model1a_reg_stats
+```
+
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r gad model1b diff_score retro (sensitivity analysis)}
+# Regression coefficients
+gad_retro_model1b_estimates <- model1b.estimates(outcome = "gad.diff_score_base_retro",
+                                                 data_set = "dat.retro_sensitivity")
+kable(gad_retro_model1b_estimates)
+gad_retro_model1b_estimates
+
+# Regression diagnostic statistics
+gad_retro_model1b_reg_stats <- model1b.reg.stats(outcome = "gad.diff_score_base_retro",
+                                                 data_set = "dat.retro_sensitivity")
+kable(gad_retro_model1b_reg_stats)
+gad_retro_model1b_reg_stats
+```
+
+## Regression: Absolute scores
+### Model 0a: Disorder_hierarchical, Unadjusted
+```{r gad model0a sum_score retro (sensitivity analysis)}
+# Regression coefficients
+gad_retro_model0a_explan_estimates <- model0a.explan.estimates(outcome = "gad.sum_score_base",
+                                                               explan_var = "gad.sum_score_retro",
+                                                               data_set = "dat.retro_sensitivity")
+kable(gad_retro_model0a_explan_estimates)
+gad_retro_model0a_explan_estimates
+
+# Regression diagnostic statistics
+gad_retro_model0a_explan_reg_stats <- model0a.explan.reg.stats(outcome = "gad.sum_score_base",
+                                                               explan_var = "gad.sum_score_retro",
+                                                               data_set = "dat.retro_sensitivity")
+kable(gad_retro_model0a_explan_reg_stats)
+gad_retro_model0a_explan_reg_stats
+```
+
+### Model 0b: Overlapping disorders, Unadjusted
+```{r gad model0b sum_score retro (sensitivity analysis)}
+# Regression coefficients
+gad_retro_model0b_explan_estimates <- model0b.explan.estimates(outcome = "gad.sum_score_base",
+                                                               explan_var = "gad.sum_score_retro",
+                                                               data_set = "dat.retro_sensitivity")
+kable(gad_retro_model0b_explan_estimates)
+gad_retro_model0b_explan_estimates
+
+# Regression diagnostic statistics
+gad_retro_model0b_explan_reg_stats <- model0b.explan.reg.stats(outcome = "gad.sum_score_base",
+                                                               explan_var = "gad.sum_score_retro",
+                                                               data_set = "dat.retro_sensitivity")
+kable(gad_retro_model0b_explan_reg_stats)
+gad_retro_model0b_explan_reg_stats
+```
+
+### Model 1a: Disorder hierarchical, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r gad model1a sum_score retro (sensitivity analysis)}
+# Regression coefficients
+gad_retro_model1a_explan_estimates <- model1a.explan.estimates(outcome = "gad.sum_score_base",
+                                                               explan_var = "gad.sum_score_retro",
+                                                               data_set = "dat.retro_sensitivity")
+kable(gad_retro_model1a_explan_estimates)
+gad_retro_model1a_explan_estimates
+
+# Regression diagnostic statistics
+gad_retro_model1a_explan_reg_stats <- model1a.explan.reg.stats(outcome = "gad.sum_score_base",
+                                                               explan_var = "gad.sum_score_retro",
+                                                               data_set = "dat.retro_sensitivity")
+kable(gad_retro_model1a_explan_reg_stats)
+gad_retro_model1a_explan_reg_stats
+```
+
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r gad model1b sum_score retro (sensitivity analysis)}
+# Regression coefficients
+gad_retro_model1b_explan_estimates <- model1b.explan.estimates(outcome = "gad.sum_score_base",
+                                                               explan_var = "gad.sum_score_retro",
+                                                               data_set = "dat.retro_sensitivity")
+kable(gad_retro_model1b_explan_estimates)
+gad_retro_model1b_explan_estimates
+
+# Regression diagnostic statistics
+gad_retro_model1b_explan_reg_stats <- model1b.explan.reg.stats(outcome = "gad.sum_score_base",
+                                                               explan_var = "gad.sum_score_retro",
+                                                               data_set = "dat.retro_sensitivity")
+kable(gad_retro_model1b_explan_reg_stats)
+gad_retro_model1b_explan_reg_stats
+```
+
 # PHQ baseline, not controlling for prior symptoms
@@
 
+# PHQ retro: Sensitivity
+## Regression: Change scores
+### Model 0a: Disorder_hierarchical, Unadjusted
+```{r phq model0a diff_score retro (sensitivity analysis)}
+# Regression coefficients
+phq_retro_model0a_estimates <- model0a.estimates(outcome = "phq.diff_score_base_retro",
+                                                 data_set = "dat.retro_sensitivity")
+kable(phq_retro_model0a_estimates)
+phq_retro_model0a_estimates
+
+# Regression diagnostic statistics
+phq_retro_model0a_reg_stats <- model0a.reg.stats(outcome = "phq.diff_score_base_retro",
+                                                 data_set = "dat.retro_sensitivity")
+kable(phq_retro_model0a_reg_stats)
+phq_retro_model0a_reg_stats
+```
+
+### Model 0b: Overlapping disorders, Unadjusted
+```{r phq model0b diff_score retro (sensitivity analysis)}
+# Regression coefficients
+phq_retro_model0b_estimates <- model0b.estimates(outcome = "phq.diff_score_base_retro",
+                                                 data_set = "dat.retro_sensitivity")
+kable(phq_retro_model0b_estimates)
+phq_retro_model0b_estimates
+
+# Regression diagnostic statistics
+phq_retro_model0b_reg_stats <- model0b.reg.stats(outcome = "phq.diff_score_base_retro",
+                                                 data_set = "dat.retro_sensitivity")
+kable(phq_retro_model0b_reg_stats)
+phq_retro_model0b_reg_stats
+```
+
+### Model 1a: Disorder hierarchical, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r phq model1a diff_score retro (sensitivity analysis)}
+# Regression coefficients
+phq_retro_model1a_estimates <- model1a.estimates(outcome = "phq.diff_score_base_retro",
+                                                 data_set = "dat.retro_sensitivity")
+kable(phq_retro_model1a_estimates)
+phq_retro_model1a_estimates
+
+# Regression diagnostic statistics
+phq_retro_model1a_reg_stats <- model1a.reg.stats(outcome = "phq.diff_score_base_retro",
+                                                 data_set = "dat.retro_sensitivity")
+kable(phq_retro_model1a_reg_stats)
+phq_retro_model1a_reg_stats
+```
+
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r phq model1b diff_score retro (sensitivity analysis)}
+# Regression coefficients
+phq_retro_model1b_estimates <- model1b.estimates(outcome = "phq.diff_score_base_retro",
+                                                 data_set = "dat.retro_sensitivity")
+kable(phq_retro_model1b_estimates)
+phq_retro_model1b_estimates
+
+# Regression diagnostic statistics
+phq_retro_model1b_reg_stats <- model1b.reg.stats(outcome = "phq.diff_score_base_retro",
+                                                 data_set = "dat.retro_sensitivity")
+kable(phq_retro_model1b_reg_stats)
+phq_retro_model1b_reg_stats
+```
+
+## Regression: Absolute scores
+### Model 0a: Disorder_hierarchical, Unadjusted
+```{r phq model0a sum_score retro (sensitivity analysis)}
+# Regression coefficients
+phq_retro_model0a_explan_estimates <- model0a.explan.estimates(outcome = "phq.sum_score_base",
+                                                               explan_var = "phq.sum_score_retro",
+                                                               data_set = "dat.retro_sensitivity")
+kable(phq_retro_model0a_explan_estimates)
+phq_retro_model0a_explan_estimates
+
+# Regression diagnostic statistics
+phq_retro_model0a_explan_reg_stats <- model0a.explan.reg.stats(outcome = "phq.sum_score_base",
+                                                               explan_var = "phq.sum_score_retro",
+                                                               data_set = "dat.retro_sensitivity")
+kable(phq_retro_model0a_explan_reg_stats)
+phq_retro_model0a_explan_reg_stats
+```
+
+### Model 0b: Overlapping disorders, Unadjusted
+```{r phq model0b sum_score retro (sensitivity analysis)}
+# Regression coefficients
+phq_retro_model0b_explan_estimates <- model0b.explan.estimates(outcome = "phq.sum_score_base",
+                                                               explan_var = "phq.sum_score_retro",
+                                                               data_set = "dat.retro_sensitivity")
+kable(phq_retro_model0b_explan_estimates)
+phq_retro_model0b_explan_estimates
+
+# Regression diagnostic statistics
+phq_retro_model0b_explan_reg_stats <- model0b.explan.reg.stats(outcome = "phq.sum_score_base",
+                                                               explan_var = "phq.sum_score_retro",
+                                                               data_set = "dat.retro_sensitivity")
+kable(phq_retro_model0b_explan_reg_stats)
+phq_retro_model0b_explan_reg_stats
+```
+
+### Model 1a: Disorder hierarchical, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r phq model1a sum_score retro (sensitivity analysis)}
+# Regression coefficients
+phq_retro_model1a_explan_estimates <- model1a.explan.estimates(outcome = "phq.sum_score_base",
+                                                               explan_var = "phq.sum_score_retro",
+                                                               data_set = "dat.retro_sensitivity")
+kable(phq_retro_model1a_explan_estimates)
+phq_retro_model1a_explan_estimates
+
+# Regression diagnostic statistics
+phq_retro_model1a_explan_reg_stats <- model1a.explan.reg.stats(outcome = "phq.sum_score_base",
+                                                               explan_var = "phq.sum_score_retro",
+                                                               data_set = "dat.retro_sensitivity")
+kable(phq_retro_model1a_explan_reg_stats)
+phq_retro_model1a_explan_reg_stats
+```
+
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r phq model1b sum_score retro (sensitivity analysis)}
+# Regression coefficients
+phq_retro_model1b_explan_estimates <- model1b.explan.estimates(outcome = "phq.sum_score_base",
+                                                               explan_var = "phq.sum_score_retro",
+                                                               data_set = "dat.retro_sensitivity")
+kable(phq_retro_model1b_explan_estimates)
+phq_retro_model1b_explan_estimates
+
+# Regression diagnostic statistics
+phq_retro_model1b_explan_reg_stats <- model1b.explan.reg.stats(outcome = "phq.sum_score_base",
+                                                               explan_var = "phq.sum_score_retro",
+                                                               data_set = "dat.retro_sensitivity")
+kable(phq_retro_model1b_explan_reg_stats)
+phq_retro_model1b_explan_reg_stats
+```
+
 # OCI-R baseline, not controlling for prior symptoms

### 2020-10-09 PANCHANGE_analysis.Rmd
Regressions for OCI-R sensitivity analyses have also been added (although these will likely just be archived since we aren't including the OCI in this paper)

@@
 
+# OCIR retro
+## Regression: Change scores
+### Model 0a: Disorder_hierarchical, Unadjusted
+```{r ocir model0a diff_score retro (sensitivity analyses)}
+# Regression coefficients
+ocir_retro_model0a_estimates <- model0a.estimates(outcome = "ocir.diff_score_base_retro",
+                                                 data_set = "dat.retro_sensitivity")
+kable(ocir_retro_model0a_estimates)
+ocir_retro_model0a_estimates
+
+# Regression diagnostic statistics
+ocir_retro_model0a_reg_stats <- model0a.reg.stats(outcome = "ocir.diff_score_base_retro",
+                                                 data_set = "dat.retro_sensitivity")
+kable(ocir_retro_model0a_reg_stats)
+ocir_retro_model0a_reg_stats
+```
+
+### Model 0b: Overlapping disorders, Unadjusted
+```{r ocir model0b diff_score retro (sensitivity analyses)}
+# Regression coefficients
+ocir_retro_model0b_estimates <- model0b.estimates(outcome = "ocir.diff_score_base_retro",
+                                                 data_set = "dat.retro_sensitivity")
+kable(ocir_retro_model0b_estimates)
+ocir_retro_model0b_estimates
+
+# Regression diagnostic statistics
+ocir_retro_model0b_reg_stats <- model0b.reg.stats(outcome = "ocir.diff_score_base_retro",
+                                                 data_set = "dat.retro_sensitivity")
+kable(ocir_retro_model0b_reg_stats)
+ocir_retro_model0b_reg_stats
+```
+
+### Model 1a: Disorder hierarchical, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r ocir model1a diff_score retro (sensitivity analyses)}
+# Regression coefficients
+ocir_retro_model1a_estimates <- model1a.estimates(outcome = "ocir.diff_score_base_retro",
+                                                 data_set = "dat.retro_sensitivity")
+kable(ocir_retro_model1a_estimates)
+ocir_retro_model1a_estimates
+
+# Regression diagnostic statistics
+ocir_retro_model1a_reg_stats <- model1a.reg.stats(outcome = "ocir.diff_score_base_retro",
+                                                 data_set = "dat.retro_sensitivity")
+kable(ocir_retro_model1a_reg_stats)
+ocir_retro_model1a_reg_stats
+```
+
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r ocir model1b diff_score retro (sensitivity analyses)}
+# Regression coefficients
+ocir_retro_model1b_estimates <- model1b.estimates(outcome = "ocir.diff_score_base_retro",
+                                                 data_set = "dat.retro_sensitivity")
+kable(ocir_retro_model1b_estimates)
+ocir_retro_model1b_estimates
+
+# Regression diagnostic statistics
+ocir_retro_model1b_reg_stats <- model1b.reg.stats(outcome = "ocir.diff_score_base_retro",
+                                                 data_set = "dat.retro_sensitivity")
+kable(ocir_retro_model1b_reg_stats)
+ocir_retro_model1b_reg_stats
+```
+
+## Regression: Absolute scores
+### Model 0a: Disorder_hierarchical, Unadjusted
+```{r ocir model0a sum_score retro (sensitivity analyses)}
+# Regression coefficients
+ocir_retro_model0a_explan_estimates <- model0a.explan.estimates(outcome = "ocir.sum_score_base",
+                                                               explan_var = "ocir.sum_score_retro",
+                                                               data_set = "dat.retro_sensitivity")
+kable(ocir_retro_model0a_explan_estimates)
+ocir_retro_model0a_explan_estimates
+
+# Regression diagnostic statistics
+ocir_retro_model0a_explan_reg_stats <- model0a.explan.reg.stats(outcome = "ocir.sum_score_base",
+                                                               explan_var = "ocir.sum_score_retro",
+                                                               data_set = "dat.retro_sensitivity")
+kable(ocir_retro_model0a_explan_reg_stats)
+ocir_retro_model0a_explan_reg_stats
+```
+
+### Model 0b: Overlapping disorders, Unadjusted
+```{r ocir model0b sum_score retro (sensitivity analyses)}
+# Regression coefficients
+ocir_retro_model0b_explan_estimates <- model0b.explan.estimates(outcome = "ocir.sum_score_base",
+                                                               explan_var = "ocir.sum_score_retro",
+                                                               data_set = "dat.retro_sensitivity")
+kable(ocir_retro_model0b_explan_estimates)
+ocir_retro_model0b_explan_estimates
+
+# Regression diagnostic statistics
+ocir_retro_model0b_explan_reg_stats <- model0b.explan.reg.stats(outcome = "ocir.sum_score_base",
+                                                               explan_var = "ocir.sum_score_retro",
+                                                               data_set = "dat.retro_sensitivity")
+kable(ocir_retro_model0b_explan_reg_stats)
+ocir_retro_model0b_explan_reg_stats
+```
+
+### Model 1a: Disorder hierarchical, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r ocir model1a sum_score retro (sensitivity analyses)}
+# Regression coefficients
+ocir_retro_model1a_explan_estimates <- model1a.explan.estimates(outcome = "ocir.sum_score_base",
+                                                               explan_var = "ocir.sum_score_retro",
+                                                               data_set = "dat.retro_sensitivity")
+kable(ocir_retro_model1a_explan_estimates)
+ocir_retro_model1a_explan_estimates
+
+# Regression diagnostic statistics
+ocir_retro_model1a_explan_reg_stats <- model1a.explan.reg.stats(outcome = "ocir.sum_score_base",
+                                                               explan_var = "ocir.sum_score_retro",
+                                                               data_set = "dat.retro_sensitivity")
+kable(ocir_retro_model1a_explan_reg_stats)
+ocir_retro_model1a_explan_reg_stats
+```
+
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r ocir model1b sum_score retro (sensitivity analyses)}
+# Regression coefficients
+ocir_retro_model1b_explan_estimates <- model1b.explan.estimates(outcome = "ocir.sum_score_base",
+                                                               explan_var = "ocir.sum_score_retro",
+                                                               data_set = "dat.retro_sensitivity")
+kable(ocir_retro_model1b_explan_estimates)
+ocir_retro_model1b_explan_estimates
+
+# Regression diagnostic statistics
+ocir_retro_model1b_explan_reg_stats <- model1b.explan.reg.stats(outcome = "ocir.sum_score_base",
+                                                               explan_var = "ocir.sum_score_retro",
+                                                               data_set = "dat.retro_sensitivity")
+kable(ocir_retro_model1b_explan_reg_stats)
+ocir_retro_model1b_explan_reg_stats
+```
+
 # PCL baseline, not controlling for prior symptoms

### 2020-10-26 PANNEURO_analysis_WHO_pres.Rmd

--- 2020-09-15 PANNEURO_analysis.Rmd
@@
 
+## COVID positive test (antibody or swab)
+```{r create COVID positive test variable}
+dat.raw <- dat.raw %>% 
+  mutate(covid_test_positive = 
+           case_when(
+             respiratory.results_antibody_test == "Negative" & 
+               respiratory.throat_swab_test_nose == "Negative" ~ 0,
+             respiratory.results_antibody_test == "Positive" | 
+               respiratory.throat_swab_test_nose == "Positive" ~ 1
+           ))
+
+dat.raw %>% 
+  count(covid_test_positive)
+```
+
 ## COVID probable diagnosis
@@
   mutate(Prop = round(n/sum(n), 2))
+
+#Rough count
+dat.raw %>%
+  count(covid_probable_case_incl_screening)
 ```
@@
 # Neurological frequencies
-
+** NEED TO BE CHANGED TO covid_probable_case_incl_screening **
 ```{r neurological frequencies alsfrs}
@@
 ```
+
+**ADD SCORING FOR NEURO MEASURES**

### 2020-10-26 PANNEURO_analysis_WHO_pres.Rmd
Update PANNEURO_analysis_WHO_pres.Rmd

@@
   filter(!is.na(startDate.coping)) %>%
-  filter(!is.na(covid_test_positive)) %>%
+  filter(!is.na(covid_probable_case_incl_screening)) %>%
   filter(!is.na(alsfrs.limb_weakness_noticed_past)) %>%
-  count(covid_test_positive, alsfrs.limb_weakness_noticed_past) %>%
+  count(covid_probable_case_incl_screening, alsfrs.limb_weakness_noticed_past) %>%
   mutate(Prop = round(n/sum(n), 2))
@@
   filter(!is.na(startDate.coping)) %>%
-  filter(!is.na(covid_test_positive)) %>%
+  filter(!is.na(covid_probable_case_incl_screening)) %>%
   filter(!is.na(alsfrs.normal)) %>%
-  group_by(covid_test_positive) %>%
-  count(covid_test_positive, alsfrs.normal) %>%
+  group_by(covid_probable_case_incl_screening) %>%
+  count(covid_probable_case_incl_screening, alsfrs.normal) %>%
   mutate(Prop = round(n/sum(n), 2))
@@
   filter(!is.na(startDate.coping)) %>%
-  filter(!is.na(covid_test_positive)) %>%
+  filter(!is.na(covid_probable_case_incl_screening)) %>%
   filter(!is.na(alsfrs.slow_or_sloppy_all_words_are_legible)) %>%
-  group_by(covid_test_positive) %>%
-  count(covid_test_positive, alsfrs.slow_or_sloppy_all_words_are_legible) %>%
+  group_by(covid_probable_case_incl_screening) %>%
+  count(covid_probable_case_incl_screening, alsfrs.slow_or_sloppy_all_words_are_legible) %>%
   mutate(Prop = round(n/sum(n), 2))
@@
   filter(!is.na(startDate.coping)) %>%
-  filter(!is.na(covid_test_positive)) %>%
+  filter(!is.na(covid_probable_case_incl_screening)) %>%
   filter(!is.na(alsfrs.not_all_words_are_legible)) %>%
-  group_by(covid_test_positive) %>%
-  count(covid_test_positive, alsfrs.not_all_words_are_legible) %>%
+  group_by(covid_probable_case_incl_screening) %>%
+  count(covid_probable_case_incl_screening, alsfrs.not_all_words_are_legible) %>%
   mutate(Prop = round(n/sum(n), 2))
@@
   filter(!is.na(startDate.coping)) %>%
-  filter(!is.na(covid_test_positive)) %>%
+  filter(!is.na(covid_probable_case_incl_screening)) %>%
   filter(!is.na(alsfrs.able_to_grip_pen)) %>%
-  group_by(covid_test_positive) %>%
-  count(covid_test_positive, alsfrs.able_to_grip_pen) %>%
+  group_by(covid_probable_case_incl_screening) %>%
+  count(covid_probable_case_incl_screening, alsfrs.able_to_grip_pen) %>%
   mutate(Prop = round(n/sum(n), 2))
@@
   filter(!is.na(startDate.coping)) %>%
-  filter(!is.na(covid_test_positive)) %>%
+  filter(!is.na(covid_probable_case_incl_screening)) %>%
   filter(!is.na(alsfrs.unable_to_grip_pen)) %>%
-  group_by(covid_test_positive) %>%
-  count(covid_test_positive, alsfrs.unable_to_grip_pen) %>%
+  group_by(covid_probable_case_incl_screening) %>%
+  count(covid_probable_case_incl_screening, alsfrs.unable_to_grip_pen) %>%
   mutate(Prop = round(n/sum(n), 2))
@@
   filter(!is.na(startDate.coping)) %>%
-  filter(!is.na(covid_test_positive)) %>%
+  filter(!is.na(covid_probable_case_incl_screening)) %>%
   filter(!is.na(alsfrs.have_you_noticed_any_difficulty_walking)) %>%
-  group_by(covid_test_positive) %>%
-  count(covid_test_positive, alsfrs.have_you_noticed_any_difficulty_walking) %>%
+  group_by(covid_probable_case_incl_screening) %>%
+  count(covid_probable_case_incl_screening, alsfrs.have_you_noticed_any_difficulty_walking) %>%
   mutate(Prop = round(n/sum(n), 2))
@@
   filter(!is.na(startDate.coping)) %>%
-  filter(!is.na(covid_test_positive)) %>%
+  filter(!is.na(covid_probable_case_incl_screening)) %>%
   filter(!is.na(alsfrs.do_you_have_any_difficulty_climbing_stairs)) %>%
-  group_by(covid_test_positive) %>%
-  count(covid_test_positive, alsfrs.do_you_have_any_difficulty_climbing_stairs) %>%
+  group_by(covid_probable_case_incl_screening) %>%
+  count(covid_probable_case_incl_screening, alsfrs.do_you_have_any_difficulty_climbing_stairs) %>%
   mutate(Prop = round(n/sum(n), 2))
@@
   filter(!is.na(startDate.coping)) %>%
-  filter(!is.na(covid_test_positive)) %>%
-  group_by(covid_test_positive) %>%
+  filter(!is.na(covid_probable_case_incl_screening)) %>%
+  group_by(covid_probable_case_incl_screening) %>%
   select(
@@
   filter(!is.na(startDate.coping)) %>%
-  filter(!is.na(covid_test_positive)) %>%
+  filter(!is.na(covid_probable_case_incl_screening)) %>%
   filter(!is.na(ess.felt_excessively_sleepy_past)) %>%
-  group_by(covid_test_positive) %>%
-  count(covid_test_positive, ess.felt_excessively_sleepy_past) %>%
+  group_by(covid_probable_case_incl_screening) %>%
+  count(covid_probable_case_incl_screening, ess.felt_excessively_sleepy_past) %>%
   mutate(Prop = round(n/sum(n), 2))
@@
   filter(!is.na(startDate.coping)) %>%
-  filter(!is.na(covid_test_positive)) %>%
+  filter(!is.na(covid_probable_case_incl_screening)) %>%
   filter(!is.na(ess.sitting_and_reading)) %>%
-  group_by(covid_test_positive) %>%
-  count(covid_test_positive, ess.sitting_and_reading) %>%
+  group_by(covid_probable_case_incl_screening) %>%
+  count(covid_probable_case_incl_screening, ess.sitting_and_reading) %>%
   mutate(Prop = round(n/sum(n), 2))
@@
   filter(!is.na(startDate.coping)) %>%
-  filter(!is.na(covid_test_positive)) %>%
+  filter(!is.na(covid_probable_case_incl_screening)) %>%
   filter(!is.na(ess.watching_tv)) %>%
-  group_by(covid_test_positive) %>%
-  count(covid_test_positive, ess.watching_tv) %>%
+  group_by(covid_probable_case_incl_screening) %>%
+  count(covid_probable_case_incl_screening, ess.watching_tv) %>%
   mutate(Prop = round(n/sum(n), 2))
@@
   filter(!is.na(startDate.coping)) %>%
-  filter(!is.na(covid_test_positive)) %>%
+  filter(!is.na(covid_probable_case_incl_screening)) %>%
   filter(!is.na(ess.sitting_inactive_in_a_public_place)) %>%
-  group_by(covid_test_positive) %>%
-  count(covid_test_positive, ess.sitting_inactive_in_a_public_place) %>%
+  group_by(covid_probable_case_incl_screening) %>%
+  count(covid_probable_case_incl_screening, ess.sitting_inactive_in_a_public_place) %>%
   mutate(Prop = round(n/sum(n), 2))
@@
   filter(!is.na(startDate.coping)) %>%
-  filter(!is.na(covid_test_positive)) %>%
+  filter(!is.na(covid_probable_case_incl_screening)) %>%
   filter(!is.na(ess.break_passenger_car_hour)) %>%
-  group_by(covid_test_positive) %>%
-  count(covid_test_positive, ess.break_passenger_car_hour) %>%
+  group_by(covid_probable_case_incl_screening) %>%
+  count(covid_probable_case_incl_screening, ess.break_passenger_car_hour) %>%
   mutate(Prop = round(n/sum(n), 2))
@@
   filter(!is.na(startDate.coping)) %>%
-  filter(!is.na(covid_test_positive)) %>%
+  filter(!is.na(covid_probable_case_incl_screening)) %>%
   filter(!is.na(ess.afternoon_rest_circumstances_lying)) %>%
-  group_by(covid_test_positive) %>%
-  count(covid_test_positive, ess.afternoon_rest_circumstances_lying) %>%
+  group_by(covid_probable_case_incl_screening) %>%
+  count(covid_probable_case_incl_screening, ess.afternoon_rest_circumstances_lying) %>%
   mutate(Prop = round(n/sum(n), 2))
@@
   filter(!is.na(startDate.coping)) %>%
-  filter(!is.na(covid_test_positive)) %>%
+  filter(!is.na(covid_probable_case_incl_screening)) %>%
   filter(!is.na(ess.sitting_and_talking_to_someone)) %>%
-  group_by(covid_test_positive) %>%
-  count(covid_test_positive, ess.sitting_and_talking_to_someone) %>%
+  group_by(covid_probable_case_incl_screening) %>%
+  count(covid_probable_case_incl_screening, ess.sitting_and_talking_to_someone) %>%
   mutate(Prop = round(n/sum(n), 2))
@@
   filter(!is.na(startDate.coping)) %>%
-  filter(!is.na(covid_test_positive)) %>%
+  filter(!is.na(covid_probable_case_incl_screening)) %>%
   filter(!is.na(ess.sitting_quietly_after_a_lunch_without_alcohol)) %>%
-  group_by(covid_test_positive) %>%
-  count(covid_test_positive, ess.sitting_quietly_after_a_lunch_without_alcohol) %>%
+  group_by(covid_probable_case_incl_screening) %>%
+  count(covid_probable_case_incl_screening, ess.sitting_quietly_after_a_lunch_without_alcohol) %>%
   mutate(Prop = round(n/sum(n), 2))
@@
   filter(!is.na(startDate.coping)) %>%
-  filter(!is.na(covid_test_positive)) %>%
+  filter(!is.na(covid_probable_case_incl_screening)) %>%
   filter(!is.na(ess.car_minutes_stopped_traffic)) %>%
-  group_by(covid_test_positive) %>%
-  count(covid_test_positive, ess.car_minutes_stopped_traffic) %>%
+  group_by(covid_probable_case_incl_screening) %>%
+  count(covid_probable_case_incl_screening, ess.car_minutes_stopped_traffic) %>%
   mutate(Prop = round(n/sum(n), 2))
@@
   filter(!is.na(startDate.coping)) %>%
-  filter(!is.na(covid_test_positive)) %>%
+  filter(!is.na(covid_probable_case_incl_screening)) %>%
   filter(!is.na(ess.insomnia)) %>%
-  group_by(covid_test_positive) %>%
-  count(covid_test_positive, ess.insomnia) %>%
+  group_by(covid_probable_case_incl_screening) %>%
+  count(covid_probable_case_incl_screening, ess.insomnia) %>%
   mutate(Prop = round(n/sum(n), 2))
@@
   filter(!is.na(startDate.coping)) %>%
-  filter(!is.na(covid_test_positive)) %>%
+  filter(!is.na(covid_probable_case_incl_screening)) %>%
   filter(!is.na(ess.narcolepsy)) %>%
-  group_by(covid_test_positive) %>%
-  count(covid_test_positive, ess.narcolepsy) %>%
+  group_by(covid_probable_case_incl_screening) %>%
+  count(covid_probable_case_incl_screening, ess.narcolepsy) %>%
   mutate(Prop = round(n/sum(n), 2))
@@
   filter(!is.na(startDate.coping)) %>%
-  filter(!is.na(covid_test_positive)) %>%
+  filter(!is.na(covid_probable_case_incl_screening)) %>%
   filter(!is.na(ess.rem_sleep_behaviour_disorder)) %>%
-  group_by(covid_test_positive) %>%
-  count(covid_test_positive, ess.rem_sleep_behaviour_disorder) %>%
+  group_by(covid_probable_case_incl_screening) %>%
+  count(covid_probable_case_incl_screening, ess.rem_sleep_behaviour_disorder) %>%
   mutate(Prop = round(n/sum(n), 2))
@@
   filter(!is.na(startDate.coping)) %>%
-  filter(!is.na(covid_test_positive)) %>%
+  filter(!is.na(covid_probable_case_incl_screening)) %>%
   filter(!is.na(ess.restless_legs_syndrome)) %>%
-  group_by(covid_test_positive) %>%
-  count(covid_test_positive, ess.restless_legs_syndrome) %>%
+  group_by(covid_probable_case_incl_screening) %>%
+  count(covid_probable_case_incl_screening, ess.restless_legs_syndrome) %>%
   mutate(Prop = round(n/sum(n), 2))
@@
   filter(!is.na(startDate.coping)) %>%
-  filter(!is.na(covid_test_positive)) %>%
+  filter(!is.na(covid_probable_case_incl_screening)) %>%
   filter(!is.na(ess.sleep_apnea)) %>%
-  group_by(covid_test_positive) %>%
-  count(covid_test_positive, ess.sleep_apnea) %>%
+  group_by(covid_probable_case_incl_screening) %>%
+  count(covid_probable_case_incl_screening, ess.sleep_apnea) %>%
   mutate(Prop = round(n/sum(n), 2))
@@
   filter(!is.na(startDate.coping)) %>%
-  filter(!is.na(covid_test_positive)) %>%
+  filter(!is.na(covid_probable_case_incl_screening)) %>%
   filter(!is.na(ess.sleep_terrors)) %>%
-  group_by(covid_test_positive) %>%
-  count(covid_test_positive, ess.sleep_terrors) %>%
+  group_by(covid_probable_case_incl_screening) %>%
+  count(covid_probable_case_incl_screening, ess.sleep_terrors) %>%
   mutate(Prop = round(n/sum(n), 2))
@@
   filter(!is.na(startDate.coping)) %>%
-  filter(!is.na(covid_test_positive)) %>%
+  filter(!is.na(covid_probable_case_incl_screening)) %>%
   filter(!is.na(ess.sleepwalking)) %>%
-  group_by(covid_test_positive) %>%
-  count(covid_test_positive, ess.sleepwalking) %>%
+  group_by(covid_probable_case_incl_screening) %>%
+  count(covid_probable_case_incl_screening, ess.sleepwalking) %>%
   mutate(Prop = round(n/sum(n), 2))
@@
   filter(!is.na(startDate.coping)) %>%
-  filter(!is.na(covid_test_positive)) %>%
+  filter(!is.na(covid_probable_case_incl_screening)) %>%
   filter(!is.na(ess.other)) %>%
-  group_by(covid_test_positive) %>%
-  count(covid_test_positive, ess.other) %>%
+  group_by(covid_probable_case_incl_screening) %>%
+  count(covid_probable_case_incl_screening, ess.other) %>%
   mutate(Prop = round(n/sum(n), 2))
@@
   filter(!is.na(startDate.coping)) %>%
-  filter(!is.na(covid_test_positive)) %>%
+  filter(!is.na(covid_probable_case_incl_screening)) %>%
   filter(!is.na(ess.none)) %>%
-  group_by(covid_test_positive) %>%
-  count(covid_test_positive, ess.none) %>%
+  group_by(covid_probable_case_incl_screening) %>%
+  count(covid_probable_case_incl_screening, ess.none) %>%
   mutate(Prop = round(n/sum(n), 2))
@@
   filter(!is.na(startDate.coping)) %>%
-  filter(!is.na(covid_test_positive)) %>%
+  filter(!is.na(covid_probable_case_incl_screening)) %>%
   filter(!is.na(midas.headaches_suffered_past_month)) %>%
-  group_by(covid_test_positive) %>%
-  count(covid_test_positive, midas.headaches_suffered_past_month) %>%
+  group_by(covid_probable_case_incl_screening) %>%
+  count(covid_probable_case_incl_screening, midas.headaches_suffered_past_month) %>%
   mutate(Prop = round(n/sum(n), 2))
@@
   filter(!is.na(startDate.coping)) %>%
-  filter(!is.na(covid_test_positive)) %>%
+  filter(!is.na(covid_probable_case_incl_screening)) %>%
   filter(!is.na(midas.days_past_month_miss_work_school)) %>%
-  group_by(covid_test_positive) %>%
-  count(covid_test_positive, midas.days_past_month_miss_work_school) %>%
+  group_by(covid_probable_case_incl_screening) %>%
+  count(covid_probable_case_incl_screening, midas.days_past_month_miss_work_school) %>%
   mutate(Prop = round(n/sum(n), 2))
@@
   filter(!is.na(startDate.coping)) %>%
-  filter(!is.na(covid_test_positive)) %>%
+  filter(!is.na(covid_probable_case_incl_screening)) %>%
   filter(!is.na(midas.days_past_month_work_school_half_productivity)) %>%
-  group_by(covid_test_positive) %>%
-  count(covid_test_positive, midas.days_past_month_work_school_half_productivity) %>%
+  group_by(covid_probable_case_incl_screening) %>%
+  count(covid_probable_case_incl_screening, midas.days_past_month_work_school_half_productivity) %>%
   mutate(Prop = round(n/sum(n), 2))
@@
   filter(!is.na(startDate.coping)) %>%
-  filter(!is.na(covid_test_positive)) %>%
+  filter(!is.na(covid_probable_case_incl_screening)) %>%
   filter(!is.na(midas.days_past_month_miss_housework)) %>%
-  group_by(covid_test_positive) %>%
-  count(covid_test_positive, midas.days_past_month_miss_housework) %>%
+  group_by(covid_probable_case_incl_screening) %>%
+  count(covid_probable_case_incl_screening, midas.days_past_month_miss_housework) %>%
   mutate(Prop = round(n/sum(n), 2))
@@
   filter(!is.na(startDate.coping)) %>%
-  filter(!is.na(covid_test_positive)) %>%
+  filter(!is.na(covid_probable_case_incl_screening)) %>%
   filter(!is.na(midas.days_past_month_housework_half_productivity)) %>%
-  group_by(covid_test_positive) %>%
-  count(covid_test_positive, midas.days_past_month_housework_half_productivity) %>%
+  group_by(covid_probable_case_incl_screening) %>%
+  count(covid_probable_case_incl_screening, midas.days_past_month_housework_half_productivity) %>%
   mutate(Prop = round(n/sum(n), 2))
@@
   filter(!is.na(startDate.coping)) %>%
-  filter(!is.na(covid_test_positive)) %>%
+  filter(!is.na(covid_probable_case_incl_screening)) %>%
   filter(!is.na(midas.days_past_month_miss_social_activities)) %>%
-  group_by(covid_test_positive) %>%
-  count(covid_test_positive, midas.days_past_month_miss_social_activities) %>%
+  group_by(covid_probable_case_incl_screening) %>%
+  count(covid_probable_case_incl_screening, midas.days_past_month_miss_social_activities) %>%
   mutate(Prop = round(n/sum(n), 2))

### 2020-10-26 PANNEURO_analysis_WHO_pres.Rmd
Update PANNEURO_analysis_WHO_pres.Rmd

--- 2020-10-26 PANNEURO_analysis_WHO_pres.Rmd
@@
 **ADD SCORING FOR NEURO MEASURES**
+
+```{r nmsw col names}
+nmsw.col.names <- dat.raw %>%
+  select(
+    starts_with("nmsw") & ends_with("numeric")
+  ) %>% 
+  colnames()
+nmsw.col.names
+
+```
+
+```{r scoring NMSW}
+dat.raw <- dat.raw %>% 
+  mutate(nmsw.sum_score = 
+           rowSums(select(.,nmsw.col.names), na.rm = FALSE)
+           )
+
+```
+
+```{r NMSW sum score frequencies}
+dat.raw %>%
+  filter(!is.na(startDate.coping)) %>%
+  filter(!is.na(covid_test_positive)) %>%
+  filter(!is.na(nmsw.sum_score)) %>%
+  group_by(covid_test_positive) %>%
+  count(covid_test_positive, nmsw.sum_score) %>%
+  mutate(Prop = round(n/sum(n), 2))
+```

### 2020-10-26 PANNEURO_preprocessing_CFS_WHO-pres.Rmd
Cleaning script for CFS wave 6 timepoint created.

---
title: "PANNEURO_CFS_cleaning_WHO_pres"
author: "Molly Davies (adapting from a script by K Purves, K Thompson, and C Huebel)"
date: "26/10/2020"
output: html_document
---

This is a script to quickly clean the Chalder Fatigue Scale in COPING follow-up set B, for the purpose of Gerome Breen's presentation to the WHO.

#Set up
```{r Setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      comment=NA,
                      prompt=FALSE,
                      cache=FALSE)

options(bitmapType = 'quartz') # to render fonts better
```

Clear global environment
```{r Clear global environment}
remove(list = ls())
```

Retrieve the current date to use it for file endings to not overwrite files when one exports files
```{r Recent date}
date = Sys.Date()
```

#Packages
Install packages (if they are not available in your version of R)
```{r Installing packages}
#install.packages("summarytools")
#install.packages("tidyverse")
#install.packages("psych")
#install.packages("eeptools")
#install.packages("skimr")
```

Load packages
```{r Load packages}
library(knitr)
library(summarytools)
library(psych)
library(eeptools) # Needed to calculate age from birthdate
library(tidyverse)
```

# Colour palettes
Define colours for plotting this are the standard coping colours
```{r Colour palettes: COPING}
COPINGpalette2 <- c("#78D9C5",
                    "#F5BE5E")

COPINGpalette3 <- c("#78D9C5",
                    "#F5BE5E",
                    "#EEB6E9")

COPINGpalette4 <- c("#78D9C5",
                    "#F5BE5E",
                    "#EEB6E9",
                    "#DBDB73")

COPINGpalette5 <- c("#78D9C5",
                    "#F5BE5E",
                    "#EEB6E9",
                    "#DBDB73", 
                    "#FFED98")

COPINGpalette6 <- c("#78D9C5",
                    "#F5BE5E",
                    "#EEB6E9",
                    "#DBDB73",
                    "#FFED98",
                    "#BFD2EB")

COPINGpalette7 <- c("#78D9C5",
                    "#F5BE5E",
                    "#EEB6E9",
                    "#DBDB73", 
                    "#FFED98",
                    "#BFD2EB", 
                    "#808080")

COPINGpaletteGRAD <- c("#F5BE5E",
                       "#FFD284",
                       "#FFEED1",
                       "#B5B5B5",
                       "#DEFFF8",
                       "#94F6E1",
                       "#78D9C5")

COPINGNeuCenterpalette <- c("#78D9C5",
                            "#808080",
                            "#F5BE5E")

RAMPworseGRADpalette <- c("#78D9C5",
                          "#FFEED1",
                          "#F5BE5E",
                          "#FFB1B5")
GLADpalette = c("#efc00b", 
                "#b7dee8")  
```

Choose in this chunk which palette to use
04.07.2020 - Default to 2 colour COPING palette
```{r Choose colour palette}
palette = COPINGpalette2
```

#Add_numeric function
Function used to convert character variables into numeric variables. 
```{r add_numeric function}
add_numeric <- function(dat, exclude = NULL) {
  dat_fct <- sjlabelled::as_label(dat)

  dat <- dat[!colnames(dat) %in% exclude]
  colnames(dat) <- paste(colnames(dat), "numeric", sep = "_")
  return(bind_cols(dat_fct, dat))
}
```

# Data import and merging

Note: GLAD only receives current measures and RAMP questionnaire
Note: All COPING surveys are separate surveys

# Source data file paths

```{r source file path}
#source raw data directory: data.raw_path
source("../PANCHANGE_raw_path.R")
```

# Read in data
```{r glad dem cols}
cfs.raw <- readRDS(file = paste0(data.raw_path, "/2020-10-22-CFS/chalder_coping_followup_setB_ongoing.rds"))
dim(cfs.raw)
colnames(cfs.raw)
```

# Select variables
```{r cfs cleaning}
exclude_cols <- c("ID",
                  "Sample",
                  "startDate")

# NBR cohort
nbr.cfs.raw.id <- cfs.raw %>%
  drop_na(externalDataReference) %>% # Drop NAs
  #distinct(externalDataReference, .keep_all = TRUE) %>% # DO NOT remove duplicates based on ID. We will need to divide them by startDate. 
  filter(startsWith(externalDataReference, 'SP', trim=TRUE)) %>%  #NBR cohort
  separate(externalDataReference, into = c("Sample", "ID.intm"), sep = 6) %>% # Split ID in Sample and Number
  separate(ID.intm, into = "ID", sep = 7) %>% 
  mutate(ID = as.numeric(ID)) %>%
  select(
         Sample, # Sample
         ID, # ID
         startDate, #Date when participant completed set B
         cfs.do_you_have_problems_with_tiredness = NA.8.do_you_have_problems_with_tiredness, 
         cfs.do_you_need_to_rest_more = NA.8.do_you_need_to_rest_more, 
         cfs.do_you_feel_sleepy_or_drowsy = NA.8.do_you_feel_sleepy_or_drowsy, 
         cfs.do_you_have_problems_starting_things = NA.8.do_you_have_problems_starting_things, 
         cfs.do_you_lack_energy = NA.8.do_you_lack_energy, 
         cfs.strength_muscles = NA.8.strength_muscles,
         cfs.do_you_feel_weak = NA.8.do_you_feel_weak,
         cfs.do_you_have_difficulty_concentrating = NA.8.do_you_have_difficulty_concentrating,
         cfs.make_slips_speaking_tongue = NA.8.make_slips_speaking_tongue,
         cfs.correct_word_find_difficult = NA.8.correct_word_find_difficult,
         cfs.how_is_your_memory = NA.8.how_is_your_memory
         ) %>%
  add_numeric(., exclude = exclude_cols) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

#GLAD/EDGI cohorts
glad.edgi.cfs.raw.id <- cfs.raw %>%
  drop_na(externalDataReference) %>% # Drop NAs
  #distinct(externalDataReference, .keep_all = TRUE) %>% # DO NOT remove duplicates based on ID. We will need to divide them by startDate. 
  filter(startsWith(externalDataReference, 'GLAD', trim=TRUE) | startsWith(externalDataReference, 'EDGI', trim=TRUE)) %>% 
  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
  mutate(ID = as.numeric(ID)) %>%
  select(
         Sample, # Sample
         ID, # ID
         startDate, #Date when participant completed set B
         cfs.do_you_have_problems_with_tiredness = NA.8.do_you_have_problems_with_tiredness, 
         cfs.do_you_need_to_rest_more = NA.8.do_you_need_to_rest_more, 
         cfs.do_you_feel_sleepy_or_drowsy = NA.8.do_you_feel_sleepy_or_drowsy, 
         cfs.do_you_have_problems_starting_things = NA.8.do_you_have_problems_starting_things, 
         cfs.do_you_lack_energy = NA.8.do_you_lack_energy, 
         cfs.strength_muscles = NA.8.strength_muscles,
         cfs.do_you_feel_weak = NA.8.do_you_feel_weak,
         cfs.do_you_have_difficulty_concentrating = NA.8.do_you_have_difficulty_concentrating,
         cfs.make_slips_speaking_tongue = NA.8.make_slips_speaking_tongue,
         cfs.correct_word_find_difficult = NA.8.correct_word_find_difficult,
         cfs.how_is_your_memory = NA.8.how_is_your_memory
         ) %>%
  add_numeric(., exclude = exclude_cols) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

# Merge datasets
cfs.raw.id <- bind_rows(
  nbr.cfs.raw.id,
  glad.edgi.cfs.raw.id
  )

# Inspect dimensions
dim(cfs.raw.id)
# Inspect colnames
colnames(cfs.raw.id)
#Differences
dim(cfs.raw)[1]-dim(cfs.raw.id)[1]

```

#Select subsample
Chalder Fatigue Scale was added to Set B on July 28.

For the purpose of the WHO presentation, we are filtering participants for the timepoint 6 between 28 July and 4 August.
```{r filter first CFS timepoint}
#Eventually we will need to create these timepoint variables for all timepoints.
startDate.timepoint <- as.Date("2020-07-27", format = "%Y-%m-%d")
endDate.timepoint <- as.Date("2020-08-04", format = "%Y-%m-%d")

#Filter responses within target timpeoint
cfs.raw.id_wave6 <- cfs.raw.id %>%
  filter((startDate > startDate.timepoint) & (startDate < endDate.timepoint)) %>% 
  distinct(paste0(Sample, ID), .keep_all = TRUE) #Remove duplicates for the single timepoint (hopefully this code works)

#Inspect dimensions
dim(cfs.raw.id_wave6)
#Differences
dim(cfs.raw.id)[1]-dim(cfs.raw.id_wave6)[1]
```

#Export dataset
```{r export data}
saveRDS(object = cfs.raw.id_wave6, file = paste0(data_path, "/cfs_wave6.rds"))
```

### 2020-10-26 PANNEURO_analysis_WHO_pres.Rmd
Changed data file for analyses to combined dataset with baseline and CFS data.

--- 2020-10-26 PANNEURO_analysis_WHO_pres.Rmd
@@
 ```{r read in data}
-dat.raw <- readRDS(file = paste0(data_path, "/four_cohorts.rds")) #NEEDS CHANGING
+dat.raw <- readRDS(file = paste0(data_path, "/baseline_and_cfs_wave6.rds")) #NEEDS CHANGING
 dim(dat.raw)

### 2020-10-26 PANNEURO_analysis_WHO_pres.Rmd
Changed dataset to read in combined CFS + baseline data

@@
   spread(key = covid_test_positive, value = n)
+```
+
+# Demographics
+## Ethnicity_collapsed
+### Pie charts
+**NEED TO CREATE ETHNICITY_collapsed variable**
+```{r Ethnicity_collapsed prop per total summary}
+Ethnicity_collapsed_prop_Covid <- dat.raw %>%
+  count(Ethnicity_collapsed, covid_probable_case_incl_screening) %>%
+  drop_na() %>%
+  mutate(freq = round(n/sum(n), 2))
+
+# total responders
+ethN <- sum(Ethnicity_collapsed_prop_Covid$n)
+
+kable(Ethnicity_collapsed_prop_Covid)
+Ethnicity_collapsed_prop_Covid
+```
+
+pie chart with only European label
+
+```{r ethnicity pie chart biggest group label}
+eth_pie_alllabel <- 
+  Ethnicity_collapsed_prop_Sample %>%
+   mutate(Ethnicity_collapsed = fct_reorder(Ethnicity_collapsed,-n)) %>%
+
+  ggplot(aes(x="", y=freq, fill=Ethnicity_collapsed)) +
+  geom_bar(width = 1, stat = "identity") +
+  scale_fill_manual(values =  COPINGpalette6) +
+  scale_color_manual(values =  COPINGpalette6) +
+  coord_polar("y",start=0) +
+  theme_void() +
+   labs(title = paste("RAMP/COPING sample self reported ethnicity",
+                      sep=" "),
+        subtitle = paste("n =", sum(Ethnicity_collapsed_prop_Sample$n),
+                         sep = " "),
+        fill = "Self reported ethnicity")  +
+    geom_text(aes(y = c(0.5),
+                  label= c(paste0(round((freq[1]*100),0),"%"))), #Frequency of European only
+             size=5,
+             face="bold"
+             )
+
+eth_pie_alllabel
+```
+
+Pie chart - no labels
+
+```{r ethnicity pie chart no label}
+eth_pie_nolabel <- 
+  Ethnicity_collapsed_prop_Sample %>%
+   mutate(Ethnicity_collapsed = fct_reorder(Ethnicity_collapsed,-n)) %>%
+
+  ggplot(aes(x="", y=freq, fill=Ethnicity_collapsed)) +
+  geom_bar(width = 1, stat = "identity") +
+  scale_fill_manual(values =  COPINGpalette6) +
+  scale_color_manual(values =  COPINGpalette6) +
+  coord_polar("y",start=0) +
+  theme_void() +
+   labs(title = paste("RAMP/COPING sample self reported ethnicity",
+                      sep=" "),
+        subtitle = paste("n =", sum(Ethnicity_collapsed_prop_Sample$n),
+                         sep = " "),
+        fill = "Self reported ethnicity")
+
+eth_pie_nolabel
 ```

### 2020-10-26 PANNEURO_analysis_WHO_pres.Rmd
rowsums_who

--- 2020-10-26 PANNEURO_analysis_WHO_pres.Rmd
@@
 ```{r read in data}
-dat.raw <- readRDS(file = paste0(data_path, "/baseline_and_cfs_wave6.rds")) #NEEDS CHANGING
+dat.raw <- readRDS(file = paste0(data_path, "/four_cohorts.rds")) #NEEDS CHANGING
 dim(dat.raw)
@@
 **ADD SCORING FOR NEURO MEASURES**
+
+# ALSfrs
+```{ALSfrs col names r}
+als.col.names <- dat.raw %>%
+  select(
+    starts_with("alsfrs") & ends_with("numeric")
+  ) %>%
+  colnames()
+
+```
+
+```{ALSfrs row sums r}
+dat.raw <- dat.raw %>%
+  mutate(als.sum.score =
+  rowSums(select(.,als.col.names), na.rm = F)
+   )
+```
+
+```{ALSfrs frequencies r}
+dat.raw %>%
+  filter(!is.na(startDate.coping)) %>%
+  filter(!is.na(covid_probable_case_incl_screening)) %>%
+  filter(!is.na(als.sum.score)) %>%
+  group_by(covid_probable_case_incl_screening) %>%
+  count(covid_probable_case_incl_screening, als.sum.score) %>%
+  mutate(Prop = round(n/sum(n), 2))
+
+```
+# ESS
+```{ESS col names r}
+ess.col.names <- dat.raw %>%
+  select(
+    starts_with("ess") & ends_with("numeric")
+  ) %>%
+  colnames()
+
+```
+
+```{ESS row sums r}
+dat.raw <- dat.raw %>%
+  mutate(ess.col.names =
+   rowSums(select(.,als.col.names), na.rm = F)
+   )
+```
+
+```{ESS frequencies r}
+dat.raw %>%
+  filter(!is.na(startDate.coping)) %>%
+  filter(!is.na(covid_probable_case_incl_screening)) %>%
+  filter(!is.na(ess.col.names)) %>%
+  group_by(covid_probable_case_incl_screening) %>%
+  count(covid_probable_case_incl_screening, ess.col.names) %>%
+  mutate(Prop = round(n/sum(n), 2))
+```

### 2020-10-26 PANNEURO_analysis_WHO_pres.Rmd

--- 2020-10-26 PANNEURO_analysis_WHO_pres.Rmd
@@
 **ADD SCORING FOR NEURO MEASURES**
+
+```{r nmsw col names}
+nmsw.col.names <- dat.raw %>%
+  select(
+    starts_with("nmsw") & ends_with("numeric")
+  ) %>% 
+  colnames()
+nmsw.col.names
+
+```
+
+```{r scoring NMSW}
+dat.raw <- dat.raw %>% 
+  mutate(nmsw.sum_score = 
+           rowSums(select(.,nmsw.col.names), na.rm = FALSE)
+           )
+
+```
+
+```{r}
+nmsw.col.names <- dat.raw %>%
+  select(
+    starts_with("ess") & ends_with("numeric")
+  ) %>% 
+  colnames()
+nmsw.col.names
+```
+```{r}
+dat.raw <- dat.raw %>% 
+  filter(ess.felt_excessively_sleepy_past_numeric == 1) %>%
+  mutate(ess.sum_score = 
+           rowSums(select(.,nmsw.col.names), na.rm = FALSE)
+           )
+
+```

### 2020-10-26 PANNEURO_CFS_merge_script_WHO-pres.Rmd

--- 2020-08-17 PANCHANGE_data_merging.Rmd
@@
 # Import data
-```{r export data}
-glad <- read_rds(path = paste0(data_path, "/glad.rds"))
-dim(glad)
+```{r import data}
+coping_baseline <- read_rds(path = paste0(data_path, "/four_cohorts.rds"))
+dim(coping_baseline)
 
-edgi <- read_rds(path = paste0(data_path, "/edgi.rds"))
-dim(edgi)
+cfs_wave6 <- read_rds(path = paste0(data_path, "/cfs_wave6.rds"))
+dim(cfs_wave6)
 
-nbr <- read_rds(path = paste0(data_path, "/nbr.rds"))
-dim(nbr)
-
-ramp <- read_rds(path = paste0(data_path, "/ramp.rds"))
-dim(ramp)
 ```
 
-glad/edgi data frame list
-```{r glad/edgi data frame list}
-dat <- bind_rows(
-  glad,
-  edgi,
-  nbr,
-  ramp
+```{r merge data frames}
+dat <- left_join(
+  coping_baseline,
+  cfs_wave6, by = c("Sample", "ID")
 )
@@
 #look at the data 
-skimr::skim(dat)
+#skimr::skim(dat) #(too big to run)
+dim(dat)
 ```
@@
 ```{r Save four cohorts as rds file}
-saveRDS(object = dat, file = paste0(data_path, "/four_cohorts.rds"))
+saveRDS(object = dat, file = paste0(data_path, "/baseline_and_cfs_wave6.rds"))
 ```

### 2020-10-26 PANNEURO_analysis_WHO_pres.Rmd

--- 2020-10-26 PANNEURO_analysis_WHO_pres.Rmd
@@
 **ADD SCORING FOR NEURO MEASURES**
-
 # ALSfrs
@@
 ```
+
+```{r nmsw col names}
+nmsw.col.names <- dat.raw %>%
+  select(
+    starts_with("nmsw") & ends_with("numeric")
+  ) %>% 
+  colnames()
+nmsw.col.names
+
+```
+
+```{r scoring NMSW}
+dat.raw <- dat.raw %>% 
+  mutate(nmsw.sum_score = 
+           rowSums(select(.,nmsw.col.names), na.rm = FALSE)
+           )
+
+```

### 2020-10-26 PANNEURO_analysis_WHO_pres.Rmd
probable_covid_all

@@
   spread(key = covid_test_positive, value = n)
-```
-
-# Demographics
-## Ethnicity_collapsed
-### Pie charts
-**NEED TO CREATE ETHNICITY_collapsed variable**
-```{r Ethnicity_collapsed prop per total summary}
-Ethnicity_collapsed_prop_Covid <- dat.raw %>%
-  count(Ethnicity_collapsed, covid_probable_case_incl_screening) %>%
-  drop_na() %>%
-  mutate(freq = round(n/sum(n), 2))
-
-# total responders
-ethN <- sum(Ethnicity_collapsed_prop_Covid$n)
-
-kable(Ethnicity_collapsed_prop_Covid)
-Ethnicity_collapsed_prop_Covid
-```
-
-pie chart with only European label
-
-```{r ethnicity pie chart biggest group label}
-eth_pie_alllabel <- 
-  Ethnicity_collapsed_prop_Sample %>%
-   mutate(Ethnicity_collapsed = fct_reorder(Ethnicity_collapsed,-n)) %>%
-
-  ggplot(aes(x="", y=freq, fill=Ethnicity_collapsed)) +
-  geom_bar(width = 1, stat = "identity") +
-  scale_fill_manual(values =  COPINGpalette6) +
-  scale_color_manual(values =  COPINGpalette6) +
-  coord_polar("y",start=0) +
-  theme_void() +
-   labs(title = paste("RAMP/COPING sample self reported ethnicity",
-                      sep=" "),
-        subtitle = paste("n =", sum(Ethnicity_collapsed_prop_Sample$n),
-                         sep = " "),
-        fill = "Self reported ethnicity")  +
-    geom_text(aes(y = c(0.5),
-                  label= c(paste0(round((freq[1]*100),0),"%"))), #Frequency of European only
-             size=5,
-             face="bold"
-             )
-
-eth_pie_alllabel
-```
-
-Pie chart - no labels
-
-```{r ethnicity pie chart no label}
-eth_pie_nolabel <- 
-  Ethnicity_collapsed_prop_Sample %>%
-   mutate(Ethnicity_collapsed = fct_reorder(Ethnicity_collapsed,-n)) %>%
-
-  ggplot(aes(x="", y=freq, fill=Ethnicity_collapsed)) +
-  geom_bar(width = 1, stat = "identity") +
-  scale_fill_manual(values =  COPINGpalette6) +
-  scale_color_manual(values =  COPINGpalette6) +
-  coord_polar("y",start=0) +
-  theme_void() +
-   labs(title = paste("RAMP/COPING sample self reported ethnicity",
-                      sep=" "),
-        subtitle = paste("n =", sum(Ethnicity_collapsed_prop_Sample$n),
-                         sep = " "),
-        fill = "Self reported ethnicity")
-
-eth_pie_nolabel
 ```
@@
   filter(!is.na(startDate.coping)) %>%
-  filter(!is.na(covid_test_positive)) %>%
+  filter(!is.na(covid_probable_case_incl_screening)) %>%
   filter(!is.na(nmss.ability_taste_food_smell)) %>%
-  group_by(covid_test_positive) %>%
-  count(covid_test_positive, nmss.ability_taste_food_smell) %>%
+  group_by(covid_probable_case_incl_screening) %>%
+  count(covid_probable_case_incl_screening, nmss.ability_taste_food_smell) %>%
   mutate(Prop = round(n/sum(n), 2))
@@
   filter(!is.na(startDate.coping)) %>%
-  filter(!is.na(covid_test_positive)) %>%
+  filter(!is.na(covid_probable_case_incl_screening)) %>%
   filter(!is.na(nmss.severe_taste_smell_loss)) %>%
-  group_by(covid_test_positive) %>%
-  count(covid_test_positive, nmss.severe_taste_smell_loss) %>%
+  group_by(covid_probable_case_incl_screening) %>%
+  count(covid_probable_case_incl_screening, nmss.severe_taste_smell_loss) %>%
   mutate(Prop = round(n/sum(n), 2))
@@
   filter(!is.na(startDate.coping)) %>%
-  filter(!is.na(covid_test_positive)) %>%
+  filter(!is.na(covid_probable_case_incl_screening)) %>%
   filter(!is.na(nmsw.drink_problems_choking_difficulty)) %>%
-  group_by(covid_test_positive) %>%
-  count(covid_test_positive, nmsw.drink_problems_choking_difficulty) %>%
+  group_by(covid_probable_case_incl_screening) %>%
+  count(covid_probable_case_incl_screening, nmsw.drink_problems_choking_difficulty) %>%
   mutate(Prop = round(n/sum(n), 2))
@@
   filter(!is.na(startDate.coping)) %>%
-  filter(!is.na(covid_test_positive)) %>%
+  filter(!is.na(covid_probable_case_incl_screening)) %>%
   filter(!is.na(nmsw.regularly_night_pass_urine)) %>%
-  group_by(covid_test_positive) %>%
-  count(covid_test_positive, nmsw.regularly_night_pass_urine) %>%
+  group_by(covid_probable_case_incl_screening) %>%
+  count(covid_probable_case_incl_screening, nmsw.regularly_night_pass_urine) %>%
   mutate(Prop = round(n/sum(n), 2))
@@
   filter(!is.na(startDate.coping)) %>%
-  filter(!is.na(covid_test_positive)) %>%
+  filter(!is.na(covid_probable_case_incl_screening)) %>%
   filter(!is.na(nmsw.sex_difficult_finding)) %>%
-  group_by(covid_test_positive) %>%
-  count(covid_test_positive, nmsw.sex_difficult_finding) %>%
+  group_by(covid_probable_case_incl_screening) %>%
+  count(covid_probable_case_incl_screening, nmsw.sex_difficult_finding) %>%
   mutate(Prop = round(n/sum(n), 2))
@@
   filter(!is.na(startDate.coping)) %>%
-  filter(!is.na(covid_test_positive)) %>%
+  filter(!is.na(covid_probable_case_incl_screening)) %>%
   filter(!is.na(nmsw.weak_standing_feeling_light)) %>%
-  group_by(covid_test_positive) %>%
-  count(covid_test_positive, nmsw.weak_standing_feeling_light) %>%
+  group_by(covid_probable_case_incl_screening) %>%
+  count(covid_probable_case_incl_screening, nmsw.weak_standing_feeling_light) %>%
   mutate(Prop = round(n/sum(n), 2))
@@
   filter(!is.na(startDate.coping)) %>%
-  filter(!is.na(covid_test_positive)) %>%
+  filter(!is.na(covid_probable_case_incl_screening)) %>%
   filter(!is.na(nmsw.acting_moving_sleep_talking)) %>%
-  group_by(covid_test_positive) %>%
-  count(covid_test_positive, nmsw.acting_moving_sleep_talking) %>%
+  group_by(covid_probable_case_incl_screening) %>%
+  count(covid_probable_case_incl_screening, nmsw.acting_moving_sleep_talking) %>%
   mutate(Prop = round(n/sum(n), 2))
@@
   filter(!is.na(startDate.coping)) %>%
-  filter(!is.na(covid_test_positive)) %>%
+  filter(!is.na(covid_probable_case_incl_screening)) %>%
   filter(!is.na(nmsw.double_vision)) %>%
-  group_by(covid_test_positive) %>%
-  count(covid_test_positive, nmsw.double_vision) %>%
+  group_by(covid_probable_case_incl_screening) %>%
+  count(covid_probable_case_incl_screening, nmsw.double_vision) %>%
   mutate(Prop = round(n/sum(n), 2))
@@
   filter(!is.na(startDate.coping)) %>%
-  filter(!is.na(covid_test_positive)) %>%
+  filter(!is.na(covid_probable_case_incl_screening)) %>%
   filter(!is.na(tinnitus.ears_noises_minutes_head)) %>%
-  group_by(covid_test_positive) %>%
-  count(covid_test_positive, tinnitus.ears_noises_minutes_head) %>%
+  group_by(covid_probable_case_incl_screening) %>%
+  count(covid_probable_case_incl_screening, tinnitus.ears_noises_minutes_head) %>%
   mutate(Prop = round(n/sum(n), 2))
@@
   filter(!is.na(startDate.coping)) %>%
-  filter(!is.na(covid_test_positive)) %>%
+  filter(!is.na(covid_probable_case_incl_screening)) %>%
   filter(!is.na(tinnitus.ears_noises_minutes_head_frequency)) %>%
-  group_by(covid_test_positive) %>%
-  count(covid_test_positive, tinnitus.ears_noises_minutes_head_frequency) %>%
+  group_by(covid_probable_case_incl_screening) %>%
+  count(covid_probable_case_incl_screening, tinnitus.ears_noises_minutes_head_frequency) %>%
   mutate(Prop = round(n/sum(n), 2))
@@
   filter(!is.na(startDate.coping)) %>%
-  filter(!is.na(covid_test_positive)) %>%
+  filter(!is.na(covid_probable_case_incl_screening)) %>%
   filter(!is.na(tinnitus.noises_worry_worst_upset)) %>%
-  group_by(covid_test_positive) %>%
-  count(covid_test_positive, tinnitus.noises_worry_worst_upset) %>%
+  group_by(covid_probable_case_incl_screening) %>%
+  count(covid_probable_case_incl_screening, tinnitus.noises_worry_worst_upset) %>%
   mutate(Prop = round(n/sum(n), 2))
@@
 **ADD SCORING FOR NEURO MEASURES**
+
 # ALSfrs
@@
 ```
-
-```{r nmsw col names}
-nmsw.col.names <- dat.raw %>%
-  select(
-    starts_with("nmsw") & ends_with("numeric")
-  ) %>% 
-  colnames()
-nmsw.col.names
-
-```
-
-```{r scoring NMSW}
-dat.raw <- dat.raw %>% 
-  mutate(nmsw.sum_score = 
-           rowSums(select(.,nmsw.col.names), na.rm = FALSE)
-           )
-
-```

### 2020-10-26 PANNEURO_analysis_WHO_pres.Rmd
Added chunks for ethnicity and started working on age.

--- 2020-10-26 PANNEURO_analysis_WHO_pres.Rmd
@@
 # Demographics
+
+## Age
+## Proportion tables
+```{r age_category per Sample prop per total}
+age_category_per_Covid_prop_total <- dat.raw %>%
+  count(age_category, covid_probable_case_incl_screening) %>%
+  mutate(Prop = round(n/sum(n), 2))
+
+kable(age_category_per_Covid_prop_total)
+age_category_per_Covid_prop_total
+```
+
+```{r age_category per Sample prop per Sample}
+age_category_per_Sample_prop_Sample <- dat %>%
+  group_by(Sample) %>%
+  count(age_category, Sample) %>%
+  mutate(Prop = round(n/sum(n), 2))
+
+kable(age_category_per_Sample_prop_Sample)
+age_category_per_Sample_prop_Sample
+```
+
+## Cross tables
+```{r age_category per Sample prop cross table}
+age_category_per_Sample_prop_Sample_cross_table <- dat %>%
+  group_by(Sample) %>%
+  count(age_category, Sample) %>%
+  mutate(Prop = round(n/sum(n), 2)) %>%
+  pivot_wider(names_from = Sample, values_from = c(n, Prop))
+
+kable(age_category_per_Sample_prop_Sample_cross_table)
+age_category_per_Sample_prop_Sample_cross_table
+```
+
+## Sex
+
+## Smoking
+
+## BMI
+
+## Key worker status
+
 ## Ethnicity_collapsed
 ### Pie charts
-**NEED TO CREATE ETHNICITY_collapsed variable**
+```{r Collapse Ethnicity}
+dat.raw <- dat.raw %>%
+  mutate(Ethnicity_collapsed_numeric =
+           case_when(
+             Ethnicity_numeric == 1 ~ 0, #European
+             Ethnicity_numeric == 2 ~ 1, #Mixed or multiple ethnic origins 
+             Ethnicity_numeric == 3 ~ 2, #Asian or Asian British
+             Ethnicity_numeric == 4 ~ 3, #African or African British
+             Ethnicity_numeric == 5 ~ 3, #Arab - combined with African/African British
+             Ethnicity_numeric == 6 ~ 4  #Other ethnic group
+           )
+  )
+
+dat.raw <- dat.raw %>%
+  mutate(Ethnicity_collapsed =
+           recode_factor(
+             Ethnicity_collapsed_numeric,
+             `0` = "European",
+             `1` = "Mixed or multiple ethnic origins",
+             `2` = "Asian or Asian British",
+             `3` = "African or African British",
+             `4` = "Other"
+           )
+  )
+
+dat.raw %>%
+  freq(Ethnicity_collapsed)
+```
+
 ```{r Ethnicity_collapsed prop per total summary}
 Ethnicity_collapsed_prop_Covid <- dat.raw %>%
-  count(Ethnicity_collapsed, covid_probable_case_incl_screening) %>%
+  count(covid_probable_case_incl_screening, Ethnicity_collapsed) %>%
   drop_na() %>%
@@
 ```{r ethnicity pie chart biggest group label}
-eth_pie_alllabel <- 
-  Ethnicity_collapsed_prop_Sample %>%
+Ethnicity_by_Covid_collapsed_count <- Ethnicity_collapsed_prop_Covid %>%
   mutate(Ethnicity_collapsed = fct_reorder(Ethnicity_collapsed,-n)) %>%
+  group_by(covid_probable_case_incl_screening) %>% 
+  ggplot(mapping = aes(
+    x = Ethnicity_collapsed,
+    y = n)
+    ) +
+  geom_bar(
+    aes(fill = covid_probable_case_incl_screening),
+    stat="identity",
+    binwidth = 1,
+    position = position_dodge2(preserve = "single")
+  ) +
+  labs(
+    x = "Ethnicity",
+    y = "Number of participants",
+    fill = "Covid status") +
+  theme_personal +
+  scale_fill_manual(
+    values = COPINGpalette4
+    ) +
+  coord_flip()
 
-  ggplot(aes(x="", y=freq, fill=Ethnicity_collapsed)) +
-  geom_bar(width = 1, stat = "identity") +
-  scale_fill_manual(values =  COPINGpalette6) +
-  scale_color_manual(values =  COPINGpalette6) +
-  coord_polar("y",start=0) +
-  theme_void() +
-   labs(title = paste("RAMP/COPING sample self reported ethnicity",
-                      sep=" "),
-        subtitle = paste("n =", sum(Ethnicity_collapsed_prop_Sample$n),
-                         sep = " "),
-        fill = "Self reported ethnicity")  +
-    geom_text(aes(y = c(0.5),
-                  label= c(paste0(round((freq[1]*100),0),"%"))), #Frequency of European only
-             size=5,
-             face="bold"
-             )
+Ethnicity_by_Covid_collapsed_count
 
-eth_pie_alllabel
-```
-
-Pie chart - no labels
-
-```{r ethnicity pie chart no label}
-eth_pie_nolabel <- 
-  Ethnicity_collapsed_prop_Sample %>%
-   mutate(Ethnicity_collapsed = fct_reorder(Ethnicity_collapsed,-n)) %>%
-
-  ggplot(aes(x="", y=freq, fill=Ethnicity_collapsed)) +
-  geom_bar(width = 1, stat = "identity") +
-  scale_fill_manual(values =  COPINGpalette6) +
-  scale_color_manual(values =  COPINGpalette6) +
-  coord_polar("y",start=0) +
-  theme_void() +
-   labs(title = paste("RAMP/COPING sample self reported ethnicity",
-                      sep=" "),
-        subtitle = paste("n =", sum(Ethnicity_collapsed_prop_Sample$n),
-                         sep = " "),
-        fill = "Self reported ethnicity")
-
-eth_pie_nolabel
 ```

### 2020-10-26 PANNEURO_analysis_WHO_pres.Rmd

--- 2020-10-26 PANNEURO_analysis_WHO_pres.Rmd
@@
   spread(key = covid_test_positive, value = n)
+```
+
+# Demographics
+
+## Age
+## Proportion tables
+```{r age_category per Sample prop per total}
+age_category_per_Covid_prop_total <- dat.raw %>%
+  count(age_category, covid_probable_case_incl_screening) %>%
+  mutate(Prop = round(n/sum(n), 2))
+
+kable(age_category_per_Covid_prop_total)
+age_category_per_Covid_prop_total
+```
+
+```{r age_category per Sample prop per Sample}
+age_category_per_Sample_prop_Sample <- dat %>%
+  group_by(Sample) %>%
+  count(age_category, Sample) %>%
+  mutate(Prop = round(n/sum(n), 2))
+
+kable(age_category_per_Sample_prop_Sample)
+age_category_per_Sample_prop_Sample
+```
+
+## Cross tables
+```{r age_category per Sample prop cross table}
+age_category_per_Sample_prop_Sample_cross_table <- dat %>%
+  group_by(Sample) %>%
+  count(age_category, Sample) %>%
+  mutate(Prop = round(n/sum(n), 2)) %>%
+  pivot_wider(names_from = Sample, values_from = c(n, Prop))
+
+kable(age_category_per_Sample_prop_Sample_cross_table)
+age_category_per_Sample_prop_Sample_cross_table
+```
+
+## Sex
+
+## Smoking
+
+## BMI
+
+## Key worker status
+
+## Ethnicity_collapsed
+### Pie charts
+```{r Collapse Ethnicity}
+dat.raw <- dat.raw %>%
+  mutate(Ethnicity_collapsed_numeric =
+           case_when(
+             Ethnicity_numeric == 1 ~ 0, #European
+             Ethnicity_numeric == 2 ~ 1, #Mixed or multiple ethnic origins 
+             Ethnicity_numeric == 3 ~ 2, #Asian or Asian British
+             Ethnicity_numeric == 4 ~ 3, #African or African British
+             Ethnicity_numeric == 5 ~ 3, #Arab - combined with African/African British
+             Ethnicity_numeric == 6 ~ 4  #Other ethnic group
+           )
+  )
+
+dat.raw <- dat.raw %>%
+  mutate(Ethnicity_collapsed =
+           recode_factor(
+             Ethnicity_collapsed_numeric,
+             `0` = "European",
+             `1` = "Mixed or multiple ethnic origins",
+             `2` = "Asian or Asian British",
+             `3` = "African or African British",
+             `4` = "Other"
+           )
+  )
+
+dat.raw %>%
+  freq(Ethnicity_collapsed)
+```
+
+```{r Ethnicity_collapsed prop per total summary}
+Ethnicity_collapsed_prop_Covid <- dat.raw %>%
+  count(covid_probable_case_incl_screening, Ethnicity_collapsed) %>%
+  drop_na() %>%
+  mutate(freq = round(n/sum(n), 2))
+
+# total responders
+ethN <- sum(Ethnicity_collapsed_prop_Covid$n)
+
+kable(Ethnicity_collapsed_prop_Covid)
+Ethnicity_collapsed_prop_Covid
+```
+
+pie chart with only European label
+
+```{r ethnicity pie chart biggest group label}
+Ethnicity_by_Covid_collapsed_count <- Ethnicity_collapsed_prop_Covid %>%
+  mutate(Ethnicity_collapsed = fct_reorder(Ethnicity_collapsed,-n)) %>%
+  group_by(covid_probable_case_incl_screening) %>% 
+  ggplot(mapping = aes(
+    x = Ethnicity_collapsed,
+    y = n)
+    ) +
+  geom_bar(
+    aes(fill = covid_probable_case_incl_screening),
+    stat="identity",
+    binwidth = 1,
+    position = position_dodge2(preserve = "single")
+  ) +
+  labs(
+    x = "Ethnicity",
+    y = "Number of participants",
+    fill = "Covid status") +
+  theme_personal +
+  scale_fill_manual(
+    values = COPINGpalette4
+    ) +
+  coord_flip()
+
+Ethnicity_by_Covid_collapsed_count
+
 ```

### 2020-10-26 PANNEURO_analysis_WHO_pres.Rmd

--- 2020-10-26 PANNEURO_analysis_WHO_pres.Rmd
@@
   filter(!is.na(startDate.coping)) %>%
-  filter(!is.na(covid_probable_case_incl_screening)) %>%
-  group_by(covid_probable_case_incl_screening) %>%
+  filter(!is.na(covid_test_positive)) %>%
+  group_by(covid_test_positive) %>%
   select(
@@
   filter(!is.na(startDate.coping)) %>%
-  filter(!is.na(covid_probable_case_incl_screening)) %>%
+  filter(!is.na(covid_test_positive)) %>%
   filter(!is.na(nmss.ability_taste_food_smell)) %>%
-  group_by(covid_probable_case_incl_screening) %>%
-  count(covid_probable_case_incl_screening, nmss.ability_taste_food_smell) %>%
+  group_by(covid_test_positive) %>%
+  count(covid_test_positive, nmss.ability_taste_food_smell) %>%
   mutate(Prop = round(n/sum(n), 2))
@@
   filter(!is.na(startDate.coping)) %>%
-  filter(!is.na(covid_probable_case_incl_screening)) %>%
+  filter(!is.na(covid_test_positive)) %>%
   filter(!is.na(nmss.severe_taste_smell_loss)) %>%
-  group_by(covid_probable_case_incl_screening) %>%
-  count(covid_probable_case_incl_screening, nmss.severe_taste_smell_loss) %>%
+  group_by(covid_test_positive) %>%
+  count(covid_test_positive, nmss.severe_taste_smell_loss) %>%
   mutate(Prop = round(n/sum(n), 2))
@@
   filter(!is.na(startDate.coping)) %>%
-  filter(!is.na(covid_probable_case_incl_screening)) %>%
+  filter(!is.na(covid_test_positive)) %>%
   filter(!is.na(nmsw.drink_problems_choking_difficulty)) %>%
-  group_by(covid_probable_case_incl_screening) %>%
-  count(covid_probable_case_incl_screening, nmsw.drink_problems_choking_difficulty) %>%
+  group_by(covid_test_positive) %>%
+  count(covid_test_positive, nmsw.drink_problems_choking_difficulty) %>%
   mutate(Prop = round(n/sum(n), 2))
@@
   filter(!is.na(startDate.coping)) %>%
-  filter(!is.na(covid_probable_case_incl_screening)) %>%
+  filter(!is.na(covid_test_positive)) %>%
   filter(!is.na(nmsw.regularly_night_pass_urine)) %>%
-  group_by(covid_probable_case_incl_screening) %>%
-  count(covid_probable_case_incl_screening, nmsw.regularly_night_pass_urine) %>%
+  group_by(covid_test_positive) %>%
+  count(covid_test_positive, nmsw.regularly_night_pass_urine) %>%
   mutate(Prop = round(n/sum(n), 2))
@@
   filter(!is.na(startDate.coping)) %>%
-  filter(!is.na(covid_probable_case_incl_screening)) %>%
+  filter(!is.na(covid_test_positive)) %>%
   filter(!is.na(nmsw.sex_difficult_finding)) %>%
-  group_by(covid_probable_case_incl_screening) %>%
-  count(covid_probable_case_incl_screening, nmsw.sex_difficult_finding) %>%
+  group_by(covid_test_positive) %>%
+  count(covid_test_positive, nmsw.sex_difficult_finding) %>%
   mutate(Prop = round(n/sum(n), 2))
@@
   filter(!is.na(startDate.coping)) %>%
-  filter(!is.na(covid_probable_case_incl_screening)) %>%
+  filter(!is.na(covid_test_positive)) %>%
   filter(!is.na(nmsw.weak_standing_feeling_light)) %>%
-  group_by(covid_probable_case_incl_screening) %>%
-  count(covid_probable_case_incl_screening, nmsw.weak_standing_feeling_light) %>%
+  group_by(covid_test_positive) %>%
+  count(covid_test_positive, nmsw.weak_standing_feeling_light) %>%
   mutate(Prop = round(n/sum(n), 2))
@@
   filter(!is.na(startDate.coping)) %>%
-  filter(!is.na(covid_probable_case_incl_screening)) %>%
+  filter(!is.na(covid_test_positive)) %>%
   filter(!is.na(nmsw.acting_moving_sleep_talking)) %>%
-  group_by(covid_probable_case_incl_screening) %>%
-  count(covid_probable_case_incl_screening, nmsw.acting_moving_sleep_talking) %>%
+  group_by(covid_test_positive) %>%
+  count(covid_test_positive, nmsw.acting_moving_sleep_talking) %>%
   mutate(Prop = round(n/sum(n), 2))
@@
   filter(!is.na(startDate.coping)) %>%
-  filter(!is.na(covid_probable_case_incl_screening)) %>%
+  filter(!is.na(covid_test_positive)) %>%
   filter(!is.na(nmsw.double_vision)) %>%
-  group_by(covid_probable_case_incl_screening) %>%
-  count(covid_probable_case_incl_screening, nmsw.double_vision) %>%
+  group_by(covid_test_positive) %>%
+  count(covid_test_positive, nmsw.double_vision) %>%
   mutate(Prop = round(n/sum(n), 2))
@@
   filter(!is.na(startDate.coping)) %>%
-  filter(!is.na(covid_probable_case_incl_screening)) %>%
+  filter(!is.na(covid_test_positive)) %>%
   filter(!is.na(tinnitus.ears_noises_minutes_head)) %>%
-  group_by(covid_probable_case_incl_screening) %>%
-  count(covid_probable_case_incl_screening, tinnitus.ears_noises_minutes_head) %>%
+  group_by(covid_test_positive) %>%
+  count(covid_test_positive, tinnitus.ears_noises_minutes_head) %>%
   mutate(Prop = round(n/sum(n), 2))
@@
   filter(!is.na(startDate.coping)) %>%
-  filter(!is.na(covid_probable_case_incl_screening)) %>%
+  filter(!is.na(covid_test_positive)) %>%
   filter(!is.na(tinnitus.ears_noises_minutes_head_frequency)) %>%
-  group_by(covid_probable_case_incl_screening) %>%
-  count(covid_probable_case_incl_screening, tinnitus.ears_noises_minutes_head_frequency) %>%
+  group_by(covid_test_positive) %>%
+  count(covid_test_positive, tinnitus.ears_noises_minutes_head_frequency) %>%
   mutate(Prop = round(n/sum(n), 2))
@@
   filter(!is.na(startDate.coping)) %>%
-  filter(!is.na(covid_probable_case_incl_screening)) %>%
+  filter(!is.na(covid_test_positive)) %>%
   filter(!is.na(tinnitus.noises_worry_worst_upset)) %>%
-  group_by(covid_probable_case_incl_screening) %>%
-  count(covid_probable_case_incl_screening, tinnitus.noises_worry_worst_upset) %>%
+  group_by(covid_test_positive) %>%
+  count(covid_test_positive, tinnitus.noises_worry_worst_upset) %>%
   mutate(Prop = round(n/sum(n), 2))
@@
 **ADD SCORING FOR NEURO MEASURES**
-# ALSfrs
-```{ALSfrs col names r}
-als.col.names <- dat.raw %>%
-  select(
-    starts_with("alsfrs") & ends_with("numeric")
-  ) %>%
-  colnames()
-
-```
-
-```{ALSfrs row sums r}
-dat.raw <- dat.raw %>%
-  mutate(als.sum.score =
-  rowSums(select(.,als.col.names), na.rm = F)
-   )
-```
-
-```{ALSfrs frequencies r}
-dat.raw %>%
-  filter(!is.na(startDate.coping)) %>%
-  filter(!is.na(covid_probable_case_incl_screening)) %>%
-  filter(!is.na(als.sum.score)) %>%
-  group_by(covid_probable_case_incl_screening) %>%
-  count(covid_probable_case_incl_screening, als.sum.score) %>%
-  mutate(Prop = round(n/sum(n), 2))
-
-```
-# ESS
-```{ESS col names r}
-ess.col.names <- dat.raw %>%
-  select(
-    starts_with("ess") & ends_with("numeric")
-  ) %>%
-  colnames()
-
-```
-
-```{ESS row sums r}
-dat.raw <- dat.raw %>%
-  mutate(ess.col.names =
-   rowSums(select(.,als.col.names), na.rm = F)
-   )
-```
-
-```{ESS frequencies r}
-dat.raw %>%
-  filter(!is.na(startDate.coping)) %>%
-  filter(!is.na(covid_probable_case_incl_screening)) %>%
-  filter(!is.na(ess.col.names)) %>%
-  group_by(covid_probable_case_incl_screening) %>%
-  count(covid_probable_case_incl_screening, ess.col.names) %>%
-  mutate(Prop = round(n/sum(n), 2))
-```
-
-```{r nmsw col names}
-nmsw.col.names <- dat.raw %>%
-  select(
-    starts_with("nmsw") & ends_with("numeric")
-  ) %>% 
-  colnames()
-nmsw.col.names
-
-```
-
-```{r scoring NMSW}
-dat.raw <- dat.raw %>% 
-  mutate(nmsw.sum_score = 
-           rowSums(select(.,nmsw.col.names), na.rm = FALSE)
-           )
-
-```

### 2020-10-26 PANNEURO_analysis_WHO_pres.Rmd
Update PANNEURO_analysis_WHO_pres.Rmd
added sum score and differences between case/control

@@
 **ADD SCORING FOR NEURO MEASURES**
+# ALSfrs
+```{ALSfrs col names r}
+als.col.names <- dat.raw %>%
+  select(
+    starts_with("alsfrs") & ends_with("numeric")
+  ) %>%
+  colnames()
+
+```
+
+```{ALSfrs row sums r}
+dat.raw <- dat.raw %>%
+  mutate(als.sum.score =
+  rowSums(select(.,als.col.names), na.rm = F)
+   )
+```
+
+```{ALSfrs frequencies r}
+dat.raw %>%
+  filter(!is.na(startDate.coping)) %>%
+  filter(!is.na(covid_probable_case_incl_screening)) %>%
+  filter(!is.na(als.sum.score)) %>%
+  group_by(covid_probable_case_incl_screening) %>%
+  count(covid_probable_case_incl_screening, als.sum.score) %>%
+  mutate(Prop = round(n/sum(n), 2))
+
+```
+# ESS
+```{ESS col names r}
+ess.col.names <- dat.raw %>%
+  select(
+    starts_with("ess") & ends_with("numeric")
+  ) %>%
+  colnames()
+
+```
+
+```{ESS row sums r}
+dat.raw <- dat.raw %>%
+  mutate(ess.col.names =
+   rowSums(select(.,ess.col.names), na.rm = F)
+   )
+```
+
+```{ESS frequencies r}
+dat.raw %>%
+  filter(!is.na(startDate.coping)) %>%
+  filter(!is.na(covid_probable_case_incl_screening)) %>%
+  filter(!is.na(ess.col.names)) %>%
+  group_by(covid_probable_case_incl_screening) %>%
+  count(covid_probable_case_incl_screening, ess.col.names) %>%
+  mutate(Prop = round(n/sum(n), 2))
+```
+
+```{r nmsw col names}
+nmsw.col.names <- dat.raw %>%
+  select(
+    starts_with("nmsw") & ends_with("numeric")
+  ) %>% 
+  colnames()
+nmsw.col.names
+
+```
+
+```{r scoring NMSW}
+dat.raw <- dat.raw %>% 
+  mutate(nmsw.sum_score = 
+           rowSums(select(.,nmsw.col.names), na.rm = FALSE)
+           )
+
+```
+
+## CFS
+
+```{r}
+cfs.col.names <- dat.raw %>%
+  select(
+    starts_with("cfs") & ends_with("numeric")
+  ) %>%
+  colnames()
+cfs.col.names
+```
+```{r}
+dat.raw <- dat.raw %>%
+  mutate(cfs.sum_score =
+   rowSums(select(.,cfs.col.names), na.rm = F) - 11
+   )
+cfs.col.names.physio <- cfs.col.names[1:7]
+
+dat.raw <- dat.raw <- dat.raw %>%
+  mutate(cfs.sum_score_physical=
+   rowSums(select(.,cfs.col.names.physio), na.rm = F) - 7
+   )
+
+cfs.col.names.psych <- cfs.col.names[8:11]
+
+dat.raw <- dat.raw <- dat.raw %>%
+  mutate(cfs.sum_score_psyhchological =
+   rowSums(select(.,cfs.col.names.psych), na.rm = F) -4
+   )
+```
+
+```{r}
+dat.raw %>%
+  filter(!is.na(startDate.coping)) %>%
+  filter(!is.na(covid_probable_case_incl_screening)) %>%
+  filter(!is.na(cfs.sum_score)) %>%
+  group_by(covid_probable_case_incl_screening) %>%
+  summarise(mean_total = mean(cfs.sum_score, na.rm = TRUE),
+            mean_physical = mean(cfs.sum_score_physical, na.rm = TRUE),
+            mean_psychological = mean (cfs.sum_score_psyhchological, na.rm = TRUE))
+
+```
+
+```{r}
+dat.raw <- dat.raw %>%
+  mutate(cfs.sum_score_case = if_else(cfs.sum_score > 11, "Fatigue", "No fatigue")) #not sure if 11 is the right cut off
+
+```
+
+```{r}
+dat.raw %>%
+  filter(!is.na(startDate.coping)) %>%
+  filter(!is.na(covid_probable_case_incl_screening)) %>%
+  filter(!is.na(cfs.sum_score_case)) %>%
+  group_by(covid_probable_case_incl_screening) %>%
+  count(covid_probable_case_incl_screening, cfs.sum_score_case) %>%
+  mutate(Prop = round(n/sum(n), 2))
+```

### 2020-10-26 PANNEURO_analysis_WHO_pres.Rmd
demographics

--- 2020-10-26 PANNEURO_analysis_WHO_pres.Rmd
@@
 ```{r age_category per Sample prop per Sample}
-age_category_per_Sample_prop_Sample <- dat %>%
+age_category_per_Sample_prop_Sample <- dat.raw %>%
   group_by(Sample) %>%
@@
 ```{r age_category per Sample prop cross table}
-age_category_per_Sample_prop_Sample_cross_table <- dat %>%
+age_category_per_Sample_prop_Sample_cross_table <- dat.raw %>%
   group_by(Sample) %>%
@@
 
-## Smoking
+```{r sex according to probable Covid}
+sex_category_per_Covid_prop_total <- dat.raw %>%
+  filter(!is.na(Sex)) %>%
+  filter(!is.na(covid_probable_case_incl_screening)) %>%
+  count(Sex, covid_probable_case_incl_screening) %>%
+  mutate(Prop = round(n/sum(n), 2))
 
-## BMI
+kable(sex_category_per_Covid_prop_total)
+sex_category_per_Covid_prop_total
+```
+
+## Smoking not available
+
+## BMI not available
 
 ## Key worker status
+
+```{r}
+key_worker_category_per_Covid_prop_total <- dat.raw %>%
+  filter(!is.na(key_worker)) %>%
+  filter(!is.na(covid_probable_case_incl_screening)) %>%
+  count(key_worker, covid_probable_case_incl_screening) %>%
+  mutate(Prop = round(n/sum(n), 2))
+
+kable(key_worker_category_per_Covid_prop_total)
+key_worker_category_per_Covid_prop_total
+```
 

### 2020-10-26 PANNEURO_analysis_WHO_pres.Rmd
Update PANNEURO_analysis_WHO_pres.Rmd
added binary case/control

--- 2020-10-26 PANNEURO_analysis_WHO_pres.Rmd
@@
 ```{r}
+dat.raw$cfs.correct_word_find_difficult_binary <- if_else(dat.raw$cfs.correct_word_find_difficult_numeric >= 3, 1,0)
+dat.raw$cfs.do_you_have_problems_with_tiredness_binary<- if_else(dat.raw$cfs.do_you_have_problems_with_tiredness_numeric >= 3, 1,0)
+dat.raw$cfs.do_you_feel_sleepy_or_drowsy_binary <- if_else(dat.raw$cfs.do_you_feel_sleepy_or_drowsy_numeric >= 3, 1,0)
+dat.raw$cfs.do_you_feel_weak_binary <- if_else(dat.raw$cfs.do_you_feel_weak_numeric >= 3, 1,0)
+dat.raw$cfs.do_you_have_difficulty_concentrating_binary <- if_else(dat.raw$cfs.do_you_have_difficulty_concentrating_numeric >= 3, 1,0)
+dat.raw$cfs.do_you_have_problems_starting_things_binary <- if_else(dat.raw$cfs.do_you_have_problems_starting_things_numeric >= 3, 1,0)
+dat.raw$cfs.do_you_lack_energy_binary <- if_else(dat.raw$cfs.do_you_lack_energy_numeric >= 3, 1,0)
+dat.raw$cfs.do_you_need_to_rest_more_binary <- if_else(dat.raw$cfs.do_you_need_to_rest_more_numeric >= 3, 1,0)
+dat.raw$cfs.how_is_your_memory_numeric_binary <- if_else(dat.raw$cfs.how_is_your_memory_numeric >= 3, 1,0) 
+dat.raw$cfs.make_slips_speaking_tongue_binary <- if_else(dat.raw$cfs.make_slips_speaking_tongue_numeric >= 3, 1,0)
+dat.raw$cfs.strength_muscles_binary <- if_else(dat.raw$cfs.strength_muscles_numeric >= 3, 1,0)
+```
+
+```{r}
+cfs.col.names.bi <- dat.raw %>%
+  select(
+    starts_with("cfs") & ends_with("binary")
+  ) %>%
+  colnames()
+cfs.col.names.bi
+```
+```{r}
 dat.raw <- dat.raw %>%
-  mutate(cfs.sum_score_case = if_else(cfs.sum_score > 11, "Fatigue", "No fatigue")) #not sure if 11 is the right cut off
+  mutate(cfs.sum_score_binary =
+   rowSums(select(.,cfs.col.names.bi), na.rm = F) 
+   )
+
+dat.raw <- dat.raw %>%
+  mutate(cfs.sum_score_case = if_else(cfs.sum_score_binary >= 4, "Fatigue", "No fatigue"))
 

### 2020-10-26 PANNEURO_analysis_WHO_pres.Rmd

--- 2020-10-26 PANNEURO_analysis_WHO_pres.Rmd
@@
 ```{r age_category per Sample prop per Sample}
-age_category_per_Sample_prop_Sample <- dat.raw %>%
+age_category_per_Sample_prop_Sample <- dat %>%
   group_by(Sample) %>%
@@
 ```{r age_category per Sample prop cross table}
-age_category_per_Sample_prop_Sample_cross_table <- dat.raw %>%
+age_category_per_Sample_prop_Sample_cross_table <- dat %>%
   group_by(Sample) %>%
@@
 
-```{r sex according to probable Covid}
-sex_category_per_Covid_prop_total <- dat.raw %>%
-  filter(!is.na(Sex)) %>%
-  filter(!is.na(covid_probable_case_incl_screening)) %>%
-  count(Sex, covid_probable_case_incl_screening) %>%
-  mutate(Prop = round(n/sum(n), 2))
+## Smoking
 
-kable(sex_category_per_Covid_prop_total)
-sex_category_per_Covid_prop_total
-```
-
-## Smoking not available
-
-## BMI not available
+## BMI
 
 ## Key worker status
-
-```{r}
-key_worker_category_per_Covid_prop_total <- dat.raw %>%
-  filter(!is.na(key_worker)) %>%
-  filter(!is.na(covid_probable_case_incl_screening)) %>%
-  count(key_worker, covid_probable_case_incl_screening) %>%
-  mutate(Prop = round(n/sum(n), 2))
-
-kable(key_worker_category_per_Covid_prop_total)
-key_worker_category_per_Covid_prop_total
-```
 
@@
            )
-
-```

### 2020-10-26 PANNEURO_analysis_WHO_pres.Rmd
Chi square tests added for age and ethnicity

--- 2020-10-26 PANNEURO_analysis_WHO_pres.Rmd
@@
 ## COVID probable diagnosis
-```{r COVID probable diagnosis}
+```{r COVID probable diagnosis frequencies}
 dat.raw %>%
@@
 # Demographics
+
+## Age
+### Proportion tables
+```{r age_category per Sample prop per total}
+age_category_per_Covid_prop_total <- dat.raw %>%
+  count(age_category, covid_probable_case_incl_screening) %>%
+  mutate(Prop = round(n/sum(n), 2)) %>% 
+  drop_na()
+
+kable(age_category_per_Covid_prop_total)
+age_category_per_Covid_prop_total
+```
+
+```{r age_category per Sample prop per Sample}
+age_category_per_Covid_prop_Covid <- dat.raw %>%
+  group_by(covid_probable_case_incl_screening) %>%
+  count(age_category, covid_probable_case_incl_screening) %>%
+  mutate(Prop = round(n/sum(n), 2)) %>% 
+  drop_na()
+
+kable(age_category_per_Covid_prop_Covid)
+age_category_per_Covid_prop_Covid
+```
+
+### Cross tables
+```{r age_category per Sample prop cross table}
+age_category_per_Covid_prop_Covid_cross_table <- dat.raw %>%
+  group_by(covid_probable_case_incl_screening) %>%
+  count(age_category, covid_probable_case_incl_screening) %>%
+  drop_na() %>% 
+  mutate(Prop = round(n/sum(n), 2)) %>%
+  pivot_wider(names_from = covid_probable_case_incl_screening, values_from = c(n, Prop))
+
+kable(age_category_per_Covid_prop_Covid_cross_table)
+age_category_per_Covid_prop_Covid_cross_table
+```
+
+### Collapse age categories
+```{r Collapse age_category}
+dat.raw <- dat.raw %>%
+  mutate(age_category_collapsed_numeric =
+           case_when(
+             age_category_numeric == 1 ~ 0,
+             age_category_numeric == 2 ~ 1,
+             age_category_numeric == 3 ~ 2,
+             age_category_numeric == 4 ~ 3,
+             age_category_numeric == 5 ~ 4,
+             age_category_numeric == 6 ~ 5,
+             age_category_numeric == 7 ~ 6,
+             age_category_numeric == 8 ~ 7,
+             age_category_numeric == 9 ~ 8,
+             age_category_numeric == 10 ~ 8,
+             age_category_numeric == 11 ~ 8,
+             age_category_numeric == 12 ~ 8,
+             age_category_numeric == 13 ~ 8
+
+           )
+  )
+
+dat.raw <- dat.raw %>%
+  mutate(age_category_collapsed =
+           recode_factor(
+             age_category_collapsed_numeric,
+             `0` = "16-18",
+             `1` = "19-25",
+             `2` = "26-35",
+             `3` = "36-45",
+             `4` = "46-55",
+             `5` = "56-65",
+             `6` = "66-70",
+             `7` = "71-75",
+             `8` = "76+"
+           )
+  )
+
+dat.raw %>%
+  freq(age_category_collapsed)
+```
+
+### Proportion tables
+```{r age_category_collapsed per Sample prop per total}
+age_category_collapsed_per_Covid_prop_total <- dat.raw %>%
+  count(age_category_collapsed, covid_probable_case_incl_screening) %>%
+  mutate(Prop = round(n/sum(n), 2)) %>% 
+  drop_na()
+
+kable(age_category_collapsed_per_Covid_prop_total)
+age_category_collapsed_per_Covid_prop_total
+```
+
+```{r age_category_collapsed per Sample prop per Sample}
+age_category_collapsed_per_Covid_prop_Covid <- dat.raw %>%
+  group_by(covid_probable_case_incl_screening) %>%
+  count(age_category_collapsed, covid_probable_case_incl_screening) %>%
+  mutate(Prop = round(n/sum(n), 2)) %>% 
+  drop_na()
+
+kable(age_category_collapsed_per_Covid_prop_Covid)
+age_category_collapsed_per_Covid_prop_Covid
+```
+
+### Cross tables
+```{r age_category_collapsed per Sample prop cross table}
+age_category_collapsed_per_Covid_prop_Covid_cross_table <- dat.raw %>%
+  group_by(covid_probable_case_incl_screening) %>%
+  count(age_category_collapsed, covid_probable_case_incl_screening) %>%
+  drop_na() %>% 
+  mutate(Prop = round(n/sum(n), 2)) %>%
+  pivot_wider(names_from = covid_probable_case_incl_screening, values_from = c(n, Prop))
+
+kable(age_category_collapsed_per_Covid_prop_Covid_cross_table)
+age_category_collapsed_per_Covid_prop_Covid_cross_table
+```
+
+### Chi square test
+```{r age_category per probable Covid chisquare test}
+age_category_per_Covid_chissquare_test <- dat.raw %>%
+  filter(!is.na(covid_probable_case_incl_screening)) %>%
+  count(age_category_collapsed, covid_probable_case_incl_screening) %>%
+  spread(key = covid_probable_case_incl_screening, value = n) %>%
+  select(-age_category_collapsed) %>%
+  chisq.test() %>%
+  glance()
+
+kable(age_category_per_Covid_chissquare_test)
+age_category_per_Covid_chissquare_test
+```
+
+## Sex
+
+## Smoking
+
+## BMI
+
+## Key worker status
+
 ## Ethnicity_collapsed
 ### Pie charts
-**NEED TO CREATE ETHNICITY_collapsed variable**
+```{r Collapse Ethnicity}
+dat.raw <- dat.raw %>%
+  mutate(Ethnicity_collapsed_numeric =
+           case_when(
+             Ethnicity_numeric == 1 ~ 0, #European
+             Ethnicity_numeric == 2 ~ 1, #Mixed or multiple ethnic origins 
+             Ethnicity_numeric == 3 ~ 2, #Asian or Asian British
+             Ethnicity_numeric == 4 ~ 3, #African or African British
+             Ethnicity_numeric == 5 ~ 3, #Arab - combined with African/African British
+             Ethnicity_numeric == 6 ~ 4  #Other ethnic group
+           )
+  )
+
+dat.raw <- dat.raw %>%
+  mutate(Ethnicity_collapsed =
+           recode_factor(
+             Ethnicity_collapsed_numeric,
+             `0` = "European",
+             `1` = "Mixed or multiple ethnic origins",
+             `2` = "Asian or Asian British",
+             `3` = "African or African British",
+             `4` = "Other"
+           )
+  )
+
+dat.raw %>%
+  freq(Ethnicity_collapsed)
+```
+
 ```{r Ethnicity_collapsed prop per total summary}
 Ethnicity_collapsed_prop_Covid <- dat.raw %>%
-  count(Ethnicity_collapsed, covid_probable_case_incl_screening) %>%
+  count(covid_probable_case_incl_screening, Ethnicity_collapsed) %>%
   drop_na() %>%
@@
 ```{r ethnicity pie chart biggest group label}
-eth_pie_alllabel <- 
-  Ethnicity_collapsed_prop_Sample %>%
+Ethnicity_by_Covid_collapsed_count <- Ethnicity_collapsed_prop_Covid %>%
   mutate(Ethnicity_collapsed = fct_reorder(Ethnicity_collapsed,-n)) %>%
+  group_by(covid_probable_case_incl_screening) %>% 
+  ggplot(mapping = aes(
+    x = Ethnicity_collapsed,
+    y = n)
+    ) +
+  geom_bar(
+    aes(fill = covid_probable_case_incl_screening),
+    stat="identity",
+    binwidth = 1,
+    position = position_dodge2(preserve = "single")
+  ) +
+  labs(
+    x = "Ethnicity",
+    y = "Number of participants",
+    fill = "Covid status") +
+  theme_personal +
+  scale_fill_manual(
+    values = COPINGpalette4
+    ) +
+  coord_flip()
 
-  ggplot(aes(x="", y=freq, fill=Ethnicity_collapsed)) +
-  geom_bar(width = 1, stat = "identity") +
-  scale_fill_manual(values =  COPINGpalette6) +
-  scale_color_manual(values =  COPINGpalette6) +
-  coord_polar("y",start=0) +
-  theme_void() +
-   labs(title = paste("RAMP/COPING sample self reported ethnicity",
-                      sep=" "),
-        subtitle = paste("n =", sum(Ethnicity_collapsed_prop_Sample$n),
-                         sep = " "),
-        fill = "Self reported ethnicity")  +
-    geom_text(aes(y = c(0.5),
-                  label= c(paste0(round((freq[1]*100),0),"%"))), #Frequency of European only
-             size=5,
-             face="bold"
-             )
+Ethnicity_by_Covid_collapsed_count
 
-eth_pie_alllabel
 ```
 
-Pie chart - no labels
+###Chi-square
 
-```{r ethnicity pie chart no label}
-eth_pie_nolabel <- 
-  Ethnicity_collapsed_prop_Sample %>%
-   mutate(Ethnicity_collapsed = fct_reorder(Ethnicity_collapsed,-n)) %>%
+```{r ethnicity per probable Covid chisquare test}
+ethnicity_per_Covid_chissquare_test <- dat.raw %>%
+  filter(!is.na(covid_probable_case_incl_screening)) %>%
+  count(Ethnicity_collapsed, covid_probable_case_incl_screening) %>%
+  spread(key = covid_probable_case_incl_screening, value = n) %>%
+  select(-Ethnicity_collapsed) %>%
+  chisq.test() %>%
+  glance()
 
-  ggplot(aes(x="", y=freq, fill=Ethnicity_collapsed)) +
-  geom_bar(width = 1, stat = "identity") +
-  scale_fill_manual(values =  COPINGpalette6) +
-  scale_color_manual(values =  COPINGpalette6) +
-  coord_polar("y",start=0) +
-  theme_void() +
-   labs(title = paste("RAMP/COPING sample self reported ethnicity",
-                      sep=" "),
-        subtitle = paste("n =", sum(Ethnicity_collapsed_prop_Sample$n),
-                         sep = " "),
-        fill = "Self reported ethnicity")
-
-eth_pie_nolabel
+kable(ethnicity_per_Covid_chissquare_test)
+ethnicity_per_Covid_chissquare_test
 ```
@@
 # Neurological frequencies
-** NEED TO BE CHANGED TO covid_probable_case_incl_screening **
+
 ```{r neurological frequencies alsfrs}
@@
   filter(!is.na(startDate.coping)) %>%
-  filter(!is.na(covid_probable_case_incl_screening)) %>%
+  filter(!is.na(covid_test_positive)) %>%
   filter(!is.na(alsfrs.limb_weakness_noticed_past)) %>%
-  count(covid_probable_case_incl_screening, alsfrs.limb_weakness_noticed_past) %>%
+  count(covid_test_positive, alsfrs.limb_weakness_noticed_past) %>%
   mutate(Prop = round(n/sum(n), 2))
@@
   filter(!is.na(startDate.coping)) %>%
-  filter(!is.na(covid_probable_case_incl_screening)) %>%
+  filter(!is.na(covid_test_positive)) %>%
   filter(!is.na(alsfrs.normal)) %>%
-  group_by(covid_probable_case_incl_screening) %>%
-  count(covid_probable_case_incl_screening, alsfrs.normal) %>%
+  group_by(covid_test_positive) %>%
+  count(covid_test_positive, alsfrs.normal) %>%
   mutate(Prop = round(n/sum(n), 2))
@@
   filter(!is.na(startDate.coping)) %>%
-  filter(!is.na(covid_probable_case_incl_screening)) %>%
+  filter(!is.na(covid_test_positive)) %>%
   filter(!is.na(alsfrs.slow_or_sloppy_all_words_are_legible)) %>%
-  group_by(covid_probable_case_incl_screening) %>%
-  count(covid_probable_case_incl_screening, alsfrs.slow_or_sloppy_all_words_are_legible) %>%
+  group_by(covid_test_positive) %>%
+  count(covid_test_positive, alsfrs.slow_or_sloppy_all_words_are_legible) %>%
   mutate(Prop = round(n/sum(n), 2))
@@
   filter(!is.na(startDate.coping)) %>%
-  filter(!is.na(covid_probable_case_incl_screening)) %>%
+  filter(!is.na(covid_test_positive)) %>%
   filter(!is.na(alsfrs.not_all_words_are_legible)) %>%
-  group_by(covid_probable_case_incl_screening) %>%
-  count(covid_probable_case_incl_screening, alsfrs.not_all_words_are_legible) %>%
+  group_by(covid_test_positive) %>%
+  count(covid_test_positive, alsfrs.not_all_words_are_legible) %>%
   mutate(Prop = round(n/sum(n), 2))
@@
   filter(!is.na(startDate.coping)) %>%
-  filter(!is.na(covid_probable_case_incl_screening)) %>%
+  filter(!is.na(covid_test_positive)) %>%
   filter(!is.na(alsfrs.able_to_grip_pen)) %>%
-  group_by(covid_probable_case_incl_screening) %>%
-  count(covid_probable_case_incl_screening, alsfrs.able_to_grip_pen) %>%
+  group_by(covid_test_positive) %>%
+  count(covid_test_positive, alsfrs.able_to_grip_pen) %>%
   mutate(Prop = round(n/sum(n), 2))
@@
   filter(!is.na(startDate.coping)) %>%
-  filter(!is.na(covid_probable_case_incl_screening)) %>%
+  filter(!is.na(covid_test_positive)) %>%
   filter(!is.na(alsfrs.unable_to_grip_pen)) %>%
-  group_by(covid_probable_case_incl_screening) %>%
-  count(covid_probable_case_incl_screening, alsfrs.unable_to_grip_pen) %>%
+  group_by(covid_test_positive) %>%
+  count(covid_test_positive, alsfrs.unable_to_grip_pen) %>%
   mutate(Prop = round(n/sum(n), 2))
@@
   filter(!is.na(startDate.coping)) %>%
-  filter(!is.na(covid_probable_case_incl_screening)) %>%
+  filter(!is.na(covid_test_positive)) %>%
   filter(!is.na(alsfrs.have_you_noticed_any_difficulty_walking)) %>%
-  group_by(covid_probable_case_incl_screening) %>%
-  count(covid_probable_case_incl_screening, alsfrs.have_you_noticed_any_difficulty_walking) %>%
+  group_by(covid_test_positive) %>%
+  count(covid_test_positive, alsfrs.have_you_noticed_any_difficulty_walking) %>%
   mutate(Prop = round(n/sum(n), 2))
@@
   filter(!is.na(startDate.coping)) %>%
-  filter(!is.na(covid_probable_case_incl_screening)) %>%
+  filter(!is.na(covid_test_positive)) %>%
   filter(!is.na(alsfrs.do_you_have_any_difficulty_climbing_stairs)) %>%
-  group_by(covid_probable_case_incl_screening) %>%
-  count(covid_probable_case_incl_screening, alsfrs.do_you_have_any_difficulty_climbing_stairs) %>%
+  group_by(covid_test_positive) %>%
+  count(covid_test_positive, alsfrs.do_you_have_any_difficulty_climbing_stairs) %>%
   mutate(Prop = round(n/sum(n), 2))
@@
   filter(!is.na(startDate.coping)) %>%
-  filter(!is.na(covid_probable_case_incl_screening)) %>%
+  filter(!is.na(covid_test_positive)) %>%
   filter(!is.na(ess.felt_excessively_sleepy_past)) %>%
-  group_by(covid_probable_case_incl_screening) %>%
-  count(covid_probable_case_incl_screening, ess.felt_excessively_sleepy_past) %>%
+  group_by(covid_test_positive) %>%
+  count(covid_test_positive, ess.felt_excessively_sleepy_past) %>%
   mutate(Prop = round(n/sum(n), 2))
@@
   filter(!is.na(startDate.coping)) %>%
-  filter(!is.na(covid_probable_case_incl_screening)) %>%
+  filter(!is.na(covid_test_positive)) %>%
   filter(!is.na(ess.sitting_and_reading)) %>%
-  group_by(covid_probable_case_incl_screening) %>%
-  count(covid_probable_case_incl_screening, ess.sitting_and_reading) %>%
+  group_by(covid_test_positive) %>%
+  count(covid_test_positive, ess.sitting_and_reading) %>%
   mutate(Prop = round(n/sum(n), 2))
@@
   filter(!is.na(startDate.coping)) %>%
-  filter(!is.na(covid_probable_case_incl_screening)) %>%
+  filter(!is.na(covid_test_positive)) %>%
   filter(!is.na(ess.watching_tv)) %>%
-  group_by(covid_probable_case_incl_screening) %>%
-  count(covid_probable_case_incl_screening, ess.watching_tv) %>%
+  group_by(covid_test_positive) %>%
+  count(covid_test_positive, ess.watching_tv) %>%
   mutate(Prop = round(n/sum(n), 2))
@@
   filter(!is.na(startDate.coping)) %>%
-  filter(!is.na(covid_probable_case_incl_screening)) %>%
+  filter(!is.na(covid_test_positive)) %>%
   filter(!is.na(ess.sitting_inactive_in_a_public_place)) %>%
-  group_by(covid_probable_case_incl_screening) %>%
-  count(covid_probable_case_incl_screening, ess.sitting_inactive_in_a_public_place) %>%
+  group_by(covid_test_positive) %>%
+  count(covid_test_positive, ess.sitting_inactive_in_a_public_place) %>%
   mutate(Prop = round(n/sum(n), 2))
@@
   filter(!is.na(startDate.coping)) %>%
-  filter(!is.na(covid_probable_case_incl_screening)) %>%
+  filter(!is.na(covid_test_positive)) %>%
   filter(!is.na(ess.break_passenger_car_hour)) %>%
-  group_by(covid_probable_case_incl_screening) %>%
-  count(covid_probable_case_incl_screening, ess.break_passenger_car_hour) %>%
+  group_by(covid_test_positive) %>%
+  count(covid_test_positive, ess.break_passenger_car_hour) %>%
   mutate(Prop = round(n/sum(n), 2))
@@
   filter(!is.na(startDate.coping)) %>%
-  filter(!is.na(covid_probable_case_incl_screening)) %>%
+  filter(!is.na(covid_test_positive)) %>%
   filter(!is.na(ess.afternoon_rest_circumstances_lying)) %>%
-  group_by(covid_probable_case_incl_screening) %>%
-  count(covid_probable_case_incl_screening, ess.afternoon_rest_circumstances_lying) %>%
+  group_by(covid_test_positive) %>%
+  count(covid_test_positive, ess.afternoon_rest_circumstances_lying) %>%
   mutate(Prop = round(n/sum(n), 2))
@@
   filter(!is.na(startDate.coping)) %>%
-  filter(!is.na(covid_probable_case_incl_screening)) %>%
+  filter(!is.na(covid_test_positive)) %>%
   filter(!is.na(ess.sitting_and_talking_to_someone)) %>%
-  group_by(covid_probable_case_incl_screening) %>%
-  count(covid_probable_case_incl_screening, ess.sitting_and_talking_to_someone) %>%
+  group_by(covid_test_positive) %>%
+  count(covid_test_positive, ess.sitting_and_talking_to_someone) %>%
   mutate(Prop = round(n/sum(n), 2))
@@
   filter(!is.na(startDate.coping)) %>%
-  filter(!is.na(covid_probable_case_incl_screening)) %>%
+  filter(!is.na(covid_test_positive)) %>%
   filter(!is.na(ess.sitting_quietly_after_a_lunch_without_alcohol)) %>%
-  group_by(covid_probable_case_incl_screening) %>%
-  count(covid_probable_case_incl_screening, ess.sitting_quietly_after_a_lunch_without_alcohol) %>%
+  group_by(covid_test_positive) %>%
+  count(covid_test_positive, ess.sitting_quietly_after_a_lunch_without_alcohol) %>%
   mutate(Prop = round(n/sum(n), 2))
@@
   filter(!is.na(startDate.coping)) %>%
-  filter(!is.na(covid_probable_case_incl_screening)) %>%
+  filter(!is.na(covid_test_positive)) %>%
   filter(!is.na(ess.car_minutes_stopped_traffic)) %>%
-  group_by(covid_probable_case_incl_screening) %>%
-  count(covid_probable_case_incl_screening, ess.car_minutes_stopped_traffic) %>%
+  group_by(covid_test_positive) %>%
+  count(covid_test_positive, ess.car_minutes_stopped_traffic) %>%
   mutate(Prop = round(n/sum(n), 2))
@@
   filter(!is.na(startDate.coping)) %>%
-  filter(!is.na(covid_probable_case_incl_screening)) %>%
+  filter(!is.na(covid_test_positive)) %>%
   filter(!is.na(ess.insomnia)) %>%
-  group_by(covid_probable_case_incl_screening) %>%
-  count(covid_probable_case_incl_screening, ess.insomnia) %>%
+  group_by(covid_test_positive) %>%
+  count(covid_test_positive, ess.insomnia) %>%
   mutate(Prop = round(n/sum(n), 2))
@@
   filter(!is.na(startDate.coping)) %>%
-  filter(!is.na(covid_probable_case_incl_screening)) %>%
+  filter(!is.na(covid_test_positive)) %>%
   filter(!is.na(ess.narcolepsy)) %>%
-  group_by(covid_probable_case_incl_screening) %>%
-  count(covid_probable_case_incl_screening, ess.narcolepsy) %>%
+  group_by(covid_test_positive) %>%
+  count(covid_test_positive, ess.narcolepsy) %>%
   mutate(Prop = round(n/sum(n), 2))
@@
   filter(!is.na(startDate.coping)) %>%
-  filter(!is.na(covid_probable_case_incl_screening)) %>%
+  filter(!is.na(covid_test_positive)) %>%
   filter(!is.na(ess.rem_sleep_behaviour_disorder)) %>%
-  group_by(covid_probable_case_incl_screening) %>%
-  count(covid_probable_case_incl_screening, ess.rem_sleep_behaviour_disorder) %>%
+  group_by(covid_test_positive) %>%
+  count(covid_test_positive, ess.rem_sleep_behaviour_disorder) %>%
   mutate(Prop = round(n/sum(n), 2))
@@
   filter(!is.na(startDate.coping)) %>%
-  filter(!is.na(covid_probable_case_incl_screening)) %>%
+  filter(!is.na(covid_test_positive)) %>%
   filter(!is.na(ess.restless_legs_syndrome)) %>%
-  group_by(covid_probable_case_incl_screening) %>%
-  count(covid_probable_case_incl_screening, ess.restless_legs_syndrome) %>%
+  group_by(covid_test_positive) %>%
+  count(covid_test_positive, ess.restless_legs_syndrome) %>%
   mutate(Prop = round(n/sum(n), 2))
@@
   filter(!is.na(startDate.coping)) %>%
-  filter(!is.na(covid_probable_case_incl_screening)) %>%
+  filter(!is.na(covid_test_positive)) %>%
   filter(!is.na(ess.sleep_apnea)) %>%
-  group_by(covid_probable_case_incl_screening) %>%
-  count(covid_probable_case_incl_screening, ess.sleep_apnea) %>%
+  group_by(covid_test_positive) %>%
+  count(covid_test_positive, ess.sleep_apnea) %>%
   mutate(Prop = round(n/sum(n), 2))
@@
   filter(!is.na(startDate.coping)) %>%
-  filter(!is.na(covid_probable_case_incl_screening)) %>%
+  filter(!is.na(covid_test_positive)) %>%
   filter(!is.na(ess.sleep_terrors)) %>%
-  group_by(covid_probable_case_incl_screening) %>%
-  count(covid_probable_case_incl_screening, ess.sleep_terrors) %>%
+  group_by(covid_test_positive) %>%
+  count(covid_test_positive, ess.sleep_terrors) %>%
   mutate(Prop = round(n/sum(n), 2))
@@
   filter(!is.na(startDate.coping)) %>%
-  filter(!is.na(covid_probable_case_incl_screening)) %>%
+  filter(!is.na(covid_test_positive)) %>%
   filter(!is.na(ess.sleepwalking)) %>%
-  group_by(covid_probable_case_incl_screening) %>%
-  count(covid_probable_case_incl_screening, ess.sleepwalking) %>%
+  group_by(covid_test_positive) %>%
+  count(covid_test_positive, ess.sleepwalking) %>%
   mutate(Prop = round(n/sum(n), 2))
@@
   filter(!is.na(startDate.coping)) %>%
-  filter(!is.na(covid_probable_case_incl_screening)) %>%
+  filter(!is.na(covid_test_positive)) %>%
   filter(!is.na(ess.other)) %>%
-  group_by(covid_probable_case_incl_screening) %>%
-  count(covid_probable_case_incl_screening, ess.other) %>%
+  group_by(covid_test_positive) %>%
+  count(covid_test_positive, ess.other) %>%
   mutate(Prop = round(n/sum(n), 2))
@@
   filter(!is.na(startDate.coping)) %>%
-  filter(!is.na(covid_probable_case_incl_screening)) %>%
+  filter(!is.na(covid_test_positive)) %>%
   filter(!is.na(ess.none)) %>%
-  group_by(covid_probable_case_incl_screening) %>%
-  count(covid_probable_case_incl_screening, ess.none) %>%
+  group_by(covid_test_positive) %>%
+  count(covid_test_positive, ess.none) %>%
   mutate(Prop = round(n/sum(n), 2))
@@
   filter(!is.na(startDate.coping)) %>%
-  filter(!is.na(covid_probable_case_incl_screening)) %>%
+  filter(!is.na(covid_test_positive)) %>%
   filter(!is.na(midas.headaches_suffered_past_month)) %>%
-  group_by(covid_probable_case_incl_screening) %>%
-  count(covid_probable_case_incl_screening, midas.headaches_suffered_past_month) %>%
+  group_by(covid_test_positive) %>%
+  count(covid_test_positive, midas.headaches_suffered_past_month) %>%
   mutate(Prop = round(n/sum(n), 2))
@@
   filter(!is.na(startDate.coping)) %>%
-  filter(!is.na(covid_probable_case_incl_screening)) %>%
+  filter(!is.na(covid_test_positive)) %>%
   filter(!is.na(midas.days_past_month_miss_work_school)) %>%
-  group_by(covid_probable_case_incl_screening) %>%
-  count(covid_probable_case_incl_screening, midas.days_past_month_miss_work_school) %>%
+  group_by(covid_test_positive) %>%
+  count(covid_test_positive, midas.days_past_month_miss_work_school) %>%
   mutate(Prop = round(n/sum(n), 2))
@@
   filter(!is.na(startDate.coping)) %>%
-  filter(!is.na(covid_probable_case_incl_screening)) %>%
+  filter(!is.na(covid_test_positive)) %>%
   filter(!is.na(midas.days_past_month_work_school_half_productivity)) %>%
-  group_by(covid_probable_case_incl_screening) %>%
-  count(covid_probable_case_incl_screening, midas.days_past_month_work_school_half_productivity) %>%
+  group_by(covid_test_positive) %>%
+  count(covid_test_positive, midas.days_past_month_work_school_half_productivity) %>%
   mutate(Prop = round(n/sum(n), 2))
@@
   filter(!is.na(startDate.coping)) %>%
-  filter(!is.na(covid_probable_case_incl_screening)) %>%
+  filter(!is.na(covid_test_positive)) %>%
   filter(!is.na(midas.days_past_month_miss_housework)) %>%
-  group_by(covid_probable_case_incl_screening) %>%
-  count(covid_probable_case_incl_screening, midas.days_past_month_miss_housework) %>%
+  group_by(covid_test_positive) %>%
+  count(covid_test_positive, midas.days_past_month_miss_housework) %>%
   mutate(Prop = round(n/sum(n), 2))
@@
   filter(!is.na(startDate.coping)) %>%
-  filter(!is.na(covid_probable_case_incl_screening)) %>%
+  filter(!is.na(covid_test_positive)) %>%
   filter(!is.na(midas.days_past_month_housework_half_productivity)) %>%
-  group_by(covid_probable_case_incl_screening) %>%
-  count(covid_probable_case_incl_screening, midas.days_past_month_housework_half_productivity) %>%
+  group_by(covid_test_positive) %>%
+  count(covid_test_positive, midas.days_past_month_housework_half_productivity) %>%
   mutate(Prop = round(n/sum(n), 2))
@@
   filter(!is.na(startDate.coping)) %>%
-  filter(!is.na(covid_probable_case_incl_screening)) %>%
+  filter(!is.na(covid_test_positive)) %>%
   filter(!is.na(midas.days_past_month_miss_social_activities)) %>%
-  group_by(covid_probable_case_incl_screening) %>%
-  count(covid_probable_case_incl_screening, midas.days_past_month_miss_social_activities) %>%
+  group_by(covid_test_positive) %>%
+  count(covid_test_positive, midas.days_past_month_miss_social_activities) %>%
   mutate(Prop = round(n/sum(n), 2))
@@
 
-**ADD SCORING FOR NEURO MEASURES**
-# ALSfrs
-```{ALSfrs col names r}
-als.col.names <- dat.raw %>%
-  select(
-    starts_with("alsfrs") & ends_with("numeric")
-  ) %>%
-  colnames()
-
-```
-
-```{ALSfrs row sums r}
-dat.raw <- dat.raw %>%
-  mutate(als.sum.score =
-  rowSums(select(.,als.col.names), na.rm = F)
-   )
-```
-
-```{ALSfrs frequencies r}
-dat.raw %>%
-  filter(!is.na(startDate.coping)) %>%
-  filter(!is.na(covid_probable_case_incl_screening)) %>%
-  filter(!is.na(als.sum.score)) %>%
-  group_by(covid_probable_case_incl_screening) %>%
-  count(covid_probable_case_incl_screening, als.sum.score) %>%
-  mutate(Prop = round(n/sum(n), 2))
-
-```
-# ESS
-```{ESS col names r}
-ess.col.names <- dat.raw %>%
-  select(
-    starts_with("ess") & ends_with("numeric")
-  ) %>%
-  colnames()
-
-```
-
-```{ESS row sums r}
-dat.raw <- dat.raw %>%
-  mutate(ess.col.names =
-   rowSums(select(.,ess.col.names), na.rm = F)
-   )
-```
-
-```{ESS frequencies r}
-dat.raw %>%
-  filter(!is.na(startDate.coping)) %>%
-  filter(!is.na(covid_probable_case_incl_screening)) %>%
-  filter(!is.na(ess.col.names)) %>%
-  group_by(covid_probable_case_incl_screening) %>%
-  count(covid_probable_case_incl_screening, ess.col.names) %>%
-  mutate(Prop = round(n/sum(n), 2))
-```
+# Scoring for neuro measures
 
@@
 
-## CFS
-
 ```{r}
-cfs.col.names <- dat.raw %>%
+nmsw.col.names <- dat.raw %>%
   select(
-    starts_with("cfs") & ends_with("numeric")
+    starts_with("ess") & ends_with("numeric")
   ) %>% 
   colnames()
-cfs.col.names
+nmsw.col.names
 ```
@@
 dat.raw <- dat.raw %>% 
-  mutate(cfs.sum_score =
-   rowSums(select(.,cfs.col.names), na.rm = F) - 11
-   )
-cfs.col.names.physio <- cfs.col.names[1:7]
-
-dat.raw <- dat.raw <- dat.raw %>%
-  mutate(cfs.sum_score_physical=
-   rowSums(select(.,cfs.col.names.physio), na.rm = F) - 7
+  filter(ess.felt_excessively_sleepy_past_numeric == 1) %>%
+  mutate(ess.sum_score = 
+           rowSums(select(.,nmsw.col.names), na.rm = FALSE)
            )
 
-cfs.col.names.psych <- cfs.col.names[8:11]
-
-dat.raw <- dat.raw <- dat.raw %>%
-  mutate(cfs.sum_score_psyhchological =
-   rowSums(select(.,cfs.col.names.psych), na.rm = F) -4
-   )
 ```
-
-```{r}
-dat.raw %>%
-  filter(!is.na(startDate.coping)) %>%
-  filter(!is.na(covid_probable_case_incl_screening)) %>%
-  filter(!is.na(cfs.sum_score)) %>%
-  group_by(covid_probable_case_incl_screening) %>%
-  summarise(mean_total = mean(cfs.sum_score, na.rm = TRUE),
-            mean_physical = mean(cfs.sum_score_physical, na.rm = TRUE),
-            mean_psychological = mean (cfs.sum_score_psyhchological, na.rm = TRUE))
-
-```
-
-```{r}
-dat.raw$cfs.correct_word_find_difficult_binary <- if_else(dat.raw$cfs.correct_word_find_difficult_numeric >= 3, 1,0)
-dat.raw$cfs.do_you_have_problems_with_tiredness_binary<- if_else(dat.raw$cfs.do_you_have_problems_with_tiredness_numeric >= 3, 1,0)
-dat.raw$cfs.do_you_feel_sleepy_or_drowsy_binary <- if_else(dat.raw$cfs.do_you_feel_sleepy_or_drowsy_numeric >= 3, 1,0)
-dat.raw$cfs.do_you_feel_weak_binary <- if_else(dat.raw$cfs.do_you_feel_weak_numeric >= 3, 1,0)
-dat.raw$cfs.do_you_have_difficulty_concentrating_binary <- if_else(dat.raw$cfs.do_you_have_difficulty_concentrating_numeric >= 3, 1,0)
-dat.raw$cfs.do_you_have_problems_starting_things_binary <- if_else(dat.raw$cfs.do_you_have_problems_starting_things_numeric >= 3, 1,0)
-dat.raw$cfs.do_you_lack_energy_binary <- if_else(dat.raw$cfs.do_you_lack_energy_numeric >= 3, 1,0)
-dat.raw$cfs.do_you_need_to_rest_more_binary <- if_else(dat.raw$cfs.do_you_need_to_rest_more_numeric >= 3, 1,0)
-dat.raw$cfs.how_is_your_memory_numeric_binary <- if_else(dat.raw$cfs.how_is_your_memory_numeric >= 3, 1,0) 
-dat.raw$cfs.make_slips_speaking_tongue_binary <- if_else(dat.raw$cfs.make_slips_speaking_tongue_numeric >= 3, 1,0)
-dat.raw$cfs.strength_muscles_binary <- if_else(dat.raw$cfs.strength_muscles_numeric >= 3, 1,0)
-```
-
-```{r}
-cfs.col.names.bi <- dat.raw %>%
-  select(
-    starts_with("cfs") & ends_with("binary")
-  ) %>%
-  colnames()
-cfs.col.names.bi
-```
-```{r}
-dat.raw <- dat.raw %>%
-  mutate(cfs.sum_score_binary =
-   rowSums(select(.,cfs.col.names.bi), na.rm = F) 
-   )
-
-dat.raw <- dat.raw %>%
-  mutate(cfs.sum_score_case = if_else(cfs.sum_score_binary >= 4, "Fatigue", "No fatigue"))
-
-```
-
-```{r}
-dat.raw %>%
-  filter(!is.na(startDate.coping)) %>%
-  filter(!is.na(covid_probable_case_incl_screening)) %>%
-  filter(!is.na(cfs.sum_score_case)) %>%
-  group_by(covid_probable_case_incl_screening) %>%
-  count(covid_probable_case_incl_screening, cfs.sum_score_case) %>%
-  mutate(Prop = round(n/sum(n), 2))
-```

### 2020-10-26 PANNEURO_analysis_WHO_pres.Rmd

--- 2020-10-26 PANNEURO_analysis_WHO_pres.Rmd
@@
   mutate(ess.col.names =
-   rowSums(select(.,als.col.names), na.rm = F)
+   rowSums(select(.,ess.col.names), na.rm = F)
    )
@@
            )
+
+```
+
+## CFS
+
+```{r}
+cfs.col.names <- dat.raw %>%
+  select(
+    starts_with("cfs") & ends_with("numeric")
+  ) %>%
+  colnames()
+cfs.col.names
+```
+```{r}
+dat.raw <- dat.raw %>%
+  mutate(cfs.sum_score =
+   rowSums(select(.,cfs.col.names), na.rm = F) - 11
+   )
+cfs.col.names.physio <- cfs.col.names[1:7]
+
+dat.raw <- dat.raw <- dat.raw %>%
+  mutate(cfs.sum_score_physical=
+   rowSums(select(.,cfs.col.names.physio), na.rm = F) - 7
+   )
+
+cfs.col.names.psych <- cfs.col.names[8:11]
+
+dat.raw <- dat.raw <- dat.raw %>%
+  mutate(cfs.sum_score_psyhchological =
+   rowSums(select(.,cfs.col.names.psych), na.rm = F) -4
+   )
+```
+
+```{r}
+dat.raw %>%
+  filter(!is.na(startDate.coping)) %>%
+  filter(!is.na(covid_probable_case_incl_screening)) %>%
+  filter(!is.na(cfs.sum_score)) %>%
+  group_by(covid_probable_case_incl_screening) %>%
+  summarise(mean_total = mean(cfs.sum_score, na.rm = TRUE),
+            mean_physical = mean(cfs.sum_score_physical, na.rm = TRUE),
+            mean_psychological = mean (cfs.sum_score_psyhchological, na.rm = TRUE))
+
+```
+
+```{r}
+dat.raw$cfs.correct_word_find_difficult_binary <- if_else(dat.raw$cfs.correct_word_find_difficult_numeric >= 3, 1,0)
+dat.raw$cfs.do_you_have_problems_with_tiredness_binary<- if_else(dat.raw$cfs.do_you_have_problems_with_tiredness_numeric >= 3, 1,0)
+dat.raw$cfs.do_you_feel_sleepy_or_drowsy_binary <- if_else(dat.raw$cfs.do_you_feel_sleepy_or_drowsy_numeric >= 3, 1,0)
+dat.raw$cfs.do_you_feel_weak_binary <- if_else(dat.raw$cfs.do_you_feel_weak_numeric >= 3, 1,0)
+dat.raw$cfs.do_you_have_difficulty_concentrating_binary <- if_else(dat.raw$cfs.do_you_have_difficulty_concentrating_numeric >= 3, 1,0)
+dat.raw$cfs.do_you_have_problems_starting_things_binary <- if_else(dat.raw$cfs.do_you_have_problems_starting_things_numeric >= 3, 1,0)
+dat.raw$cfs.do_you_lack_energy_binary <- if_else(dat.raw$cfs.do_you_lack_energy_numeric >= 3, 1,0)
+dat.raw$cfs.do_you_need_to_rest_more_binary <- if_else(dat.raw$cfs.do_you_need_to_rest_more_numeric >= 3, 1,0)
+dat.raw$cfs.how_is_your_memory_numeric_binary <- if_else(dat.raw$cfs.how_is_your_memory_numeric >= 3, 1,0) 
+dat.raw$cfs.make_slips_speaking_tongue_binary <- if_else(dat.raw$cfs.make_slips_speaking_tongue_numeric >= 3, 1,0)
+dat.raw$cfs.strength_muscles_binary <- if_else(dat.raw$cfs.strength_muscles_numeric >= 3, 1,0)
+```
+
+```{r}
+cfs.col.names.bi <- dat.raw %>%
+  select(
+    starts_with("cfs") & ends_with("binary")
+  ) %>%
+  colnames()
+cfs.col.names.bi
+```
+```{r}
+dat.raw <- dat.raw %>%
+  mutate(cfs.sum_score_binary =
+   rowSums(select(.,cfs.col.names.bi), na.rm = F) 
+   )
+
+dat.raw <- dat.raw %>%
+  mutate(cfs.sum_score_case = if_else(cfs.sum_score_binary >= 4, "Fatigue", "No fatigue"))
+
+```
+
+```{r}
+dat.raw %>%
+  filter(!is.na(startDate.coping)) %>%
+  filter(!is.na(covid_probable_case_incl_screening)) %>%
+  filter(!is.na(cfs.sum_score_case)) %>%
+  group_by(covid_probable_case_incl_screening) %>%
+  count(covid_probable_case_incl_screening, cfs.sum_score_case) %>%
+  mutate(Prop = round(n/sum(n), 2))
+```

### 2020-10-26 PANNEURO_analysis_WHO_pres.Rmd

@@
 ## Sex
+```{r sex according to probable Covid}
+sex_category_per_Covid_prop_total <- dat.raw %>%
+  filter(!is.na(Sex)) %>%
+  filter(!is.na(covid_probable_case_incl_screening)) %>%
+  count(Sex, covid_probable_case_incl_screening) %>%
+  mutate(Prop = round(n/sum(n), 2))
+
+kable(sex_category_per_Covid_prop_total)
+sex_category_per_Covid_prop_total
+```
+
+## Smoking not available
+
+## BMI not available
+
+## Key worker status
+
+```{r}
+key_worker_category_per_Covid_prop_total <- dat.raw %>%
+  filter(!is.na(key_worker)) %>%
+  filter(!is.na(covid_probable_case_incl_screening)) %>%
+  count(key_worker, covid_probable_case_incl_screening) %>%
+  mutate(Prop = round(n/sum(n), 2))
+
+kable(key_worker_category_per_Covid_prop_total)
+key_worker_category_per_Covid_prop_total
+```
 

### 2020-10-26 PANNEURO_analysis_WHO_pres.Rmd

@@
 ## Age
-## Proportion tables
-```{r age_category per Sample prop per total}
+### Proportion tables
+```{r age_category per Covid prop per total}
 age_category_per_Covid_prop_total <- dat.raw %>%
   count(age_category, covid_probable_case_incl_screening) %>%
-  mutate(Prop = round(n/sum(n), 2))
+  mutate(Prop = round(n/sum(n), 2)) %>% 
+  drop_na()
 
@@
 
-```{r age_category per Sample prop per Sample}
-age_category_per_Sample_prop_Sample <- dat.raw %>%
-  group_by(Sample) %>%
-  count(age_category, Sample) %>%
-  mutate(Prop = round(n/sum(n), 2))
-
-kable(age_category_per_Sample_prop_Sample)
-age_category_per_Sample_prop_Sample
-```
-
-## Cross tables
-```{r age_category per Sample prop cross table}
-age_category_per_Sample_prop_Sample_cross_table <- dat.raw %>%
-  group_by(Sample) %>%
-  count(age_category, Sample) %>%
+```{r age_category per Covid prop per Covid}
+age_category_per_Covid_prop_Covid <- dat.raw %>%
+  group_by(covid_probable_case_incl_screening) %>%
+  count(age_category, covid_probable_case_incl_screening) %>%
   mutate(Prop = round(n/sum(n), 2)) %>% 
-  pivot_wider(names_from = Sample, values_from = c(n, Prop))
-
-kable(age_category_per_Sample_prop_Sample_cross_table)
-age_category_per_Sample_prop_Sample_cross_table
+  drop_na()
+
+kable(age_category_per_Covid_prop_Covid)
+age_category_per_Covid_prop_Covid
+```
+
+### Cross tables
+```{r age_category per Covid prop cross table}
+age_category_per_Covid_prop_Covid_cross_table <- dat.raw %>%
+  group_by(covid_probable_case_incl_screening) %>%
+  count(age_category, covid_probable_case_incl_screening) %>%
+  drop_na() %>% 
+  mutate(Prop = round(n/sum(n), 2)) %>%
+  pivot_wider(names_from = covid_probable_case_incl_screening, values_from = c(n, Prop))
+
+kable(age_category_per_Covid_prop_Covid_cross_table)
+age_category_per_Covid_prop_Covid_cross_table
+```
+
+### Collapse age categories
+```{r Collapse age_category}
+dat.raw <- dat.raw %>%
+  mutate(age_category_collapsed_numeric =
+           case_when(
+             age_category_numeric == 1 ~ 0,
+             age_category_numeric == 2 ~ 1,
+             age_category_numeric == 3 ~ 2,
+             age_category_numeric == 4 ~ 3,
+             age_category_numeric == 5 ~ 4,
+             age_category_numeric == 6 ~ 5,
+             age_category_numeric == 7 ~ 6,
+             age_category_numeric == 8 ~ 7,
+             age_category_numeric == 9 ~ 8,
+             age_category_numeric == 10 ~ 8,
+             age_category_numeric == 11 ~ 8,
+             age_category_numeric == 12 ~ 8,
+             age_category_numeric == 13 ~ 8
+
+           )
+  )
+
+dat.raw <- dat.raw %>%
+  mutate(age_category_collapsed =
+           recode_factor(
+             age_category_collapsed_numeric,
+             `0` = "16-18",
+             `1` = "19-25",
+             `2` = "26-35",
+             `3` = "36-45",
+             `4` = "46-55",
+             `5` = "56-65",
+             `6` = "66-70",
+             `7` = "71-75",
+             `8` = "76+"
+           )
+  )
+
+dat.raw %>%
+  freq(age_category_collapsed)
+```
+
+### Proportion tables
+```{r age_category_collapsed per Sample prop per total}
+age_category_collapsed_per_Covid_prop_total <- dat.raw %>%
+  count(age_category_collapsed, covid_probable_case_incl_screening) %>%
+  mutate(Prop = round(n/sum(n), 2)) %>% 
+  drop_na()
+
+kable(age_category_collapsed_per_Covid_prop_total)
+age_category_collapsed_per_Covid_prop_total
+```
+
+```{r age_category_collapsed per Sample prop per Sample}
+age_category_collapsed_per_Covid_prop_Covid <- dat.raw %>%
+  group_by(covid_probable_case_incl_screening) %>%
+  count(age_category_collapsed, covid_probable_case_incl_screening) %>%
+  mutate(Prop = round(n/sum(n), 2)) %>% 
+  drop_na()
+
+kable(age_category_collapsed_per_Covid_prop_Covid)
+age_category_collapsed_per_Covid_prop_Covid
+```
+
+### Cross tables
+```{r age_category_collapsed per Sample prop cross table}
+age_category_collapsed_per_Covid_prop_Covid_cross_table <- dat.raw %>%
+  group_by(covid_probable_case_incl_screening) %>%
+  count(age_category_collapsed, covid_probable_case_incl_screening) %>%
+  drop_na() %>% 
+  mutate(Prop = round(n/sum(n), 2)) %>%
+  pivot_wider(names_from = covid_probable_case_incl_screening, values_from = c(n, Prop))
+
+kable(age_category_collapsed_per_Covid_prop_Covid_cross_table)
+age_category_collapsed_per_Covid_prop_Covid_cross_table
+```
+
+### Chi square test
+```{r age_category per probable Covid chisquare test}
+age_category_per_Covid_chissquare_test <- dat.raw %>%
+  filter(!is.na(covid_probable_case_incl_screening)) %>%
+  count(age_category_collapsed, covid_probable_case_incl_screening) %>%
+  spread(key = covid_probable_case_incl_screening, value = n) %>%
+  select(-age_category_collapsed) %>%
+  chisq.test() %>%
+  glance()
+
+kable(age_category_per_Covid_chissquare_test)
+age_category_per_Covid_chissquare_test
 ```
@@
 
+###Chi-square
+
+```{r ethnicity per probable Covid chisquare test}
+ethnicity_per_Covid_chissquare_test <- dat.raw %>%
+  filter(!is.na(covid_probable_case_incl_screening)) %>%
+  count(Ethnicity_collapsed, covid_probable_case_incl_screening) %>%
+  spread(key = covid_probable_case_incl_screening, value = n) %>%
+  select(-Ethnicity_collapsed) %>%
+  chisq.test() %>%
+  glance()
+
+kable(ethnicity_per_Covid_chissquare_test)
+ethnicity_per_Covid_chissquare_test
+```
+
 # Neurological frequencies
-** NEED TO BE CHANGED TO covid_probable_case_incl_screening **
+
 ```{r neurological frequencies alsfrs}
@@
 
-**ADD SCORING FOR NEURO MEASURES**
+# Scoring for neuro measures
+
 # ALSfrs

### 2020-10-26 PANNEURO_analysis_WHO_pres.Rmd
Fixed NBR IDs (hopefully).

@@
 # ALSfrs
-```{ALSfrs col names r}
+```{r ALSfrs col names}
 als.col.names <- dat.raw %>%
@@
 
-```{ALSfrs row sums r}
+```{r ALSfrs row sums}
 dat.raw <- dat.raw %>%
@@
 
-```{ALSfrs frequencies r}
+```{r ALSfrs frequencies}
 dat.raw %>%
@@
 # ESS
-```{ESS col names r}
+```{r ESS col names}
 ess.col.names <- dat.raw %>%
@@
 
-```{ESS row sums r}
+```{r ESS row sums}
 dat.raw <- dat.raw %>%
@@
 
-```{ESS frequencies r}
+```{r ESS frequencies}
 dat.raw %>%
@@
 
-```{r}
+```{r select cfs variables}
 cfs.col.names <- dat.raw %>%
@@
 ```
-```{r}
+
+```{r calculate sum score}
 dat.raw <- dat.raw %>%

### 2020-10-26 PANNEURO_preprocessing_CFS_WHO-pres.Rmd
Fixed NBR IDs (hopefully).

@@
   #distinct(externalDataReference, .keep_all = TRUE) %>% # DO NOT remove duplicates based on ID. We will need to divide them by startDate. 
-  filter(startsWith(externalDataReference, 'SP', trim=TRUE)) %>%  #NBR cohort
+  filter(str_detect(externalDataReference, "SP")) %>%  #NBR cohort
   separate(externalDataReference, into = c("Sample", "ID.intm"), sep = 6) %>% # Split ID in Sample and Number
@@
   #distinct(externalDataReference, .keep_all = TRUE) %>% # DO NOT remove duplicates based on ID. We will need to divide them by startDate. 
-  filter(startsWith(externalDataReference, 'GLAD', trim=TRUE) | startsWith(externalDataReference, 'EDGI', trim=TRUE)) %>% 
+  filter(str_detect(externalDataReference, "GLAD") | str_detect(externalDataReference, "EDGI")) %>% 
   separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
@@
 
-# Merge datasets
-cfs.raw.id <- bind_rows(
-  nbr.cfs.raw.id,
-  glad.edgi.cfs.raw.id
-  )
-
 # Inspect dimensions
@@
 dim(cfs.raw)[1]-dim(cfs.raw.id)[1]
+
+```
+
+```{r rename NBR cohort}
+nbr.cfs.raw.id <- nbr.cfs.raw.id%>%
+  mutate(
+    Sample = 
+    recode(
+      Sample, 
+      "SP0068" = "NBR"
+    )
+  )
+```
+
+```{r merge datasets}
+# Merge datasets
+cfs.raw.id <- bind_rows(
+  nbr.cfs.raw.id,
+  glad.edgi.cfs.raw.id
+  )
 

### 2020-10-26 PANNEURO_analysis_WHO_pres.Rmd
Edits to analysis script.

--- 2020-10-26 PANNEURO_analysis_WHO_pres.Rmd
@@
 title: "PANNEURO_analysis"
-author: "Christopher Huebel"
+author: "Christopher Huebel, Alish Palmos, Molly Davies, and Laura Hegemann"
 date: "Sys.Date()"
 output:
-  word_document:
-    toc: yes
-    toc_depth: '2'
-  pdf_document:
-    toc: yes
-    toc_depth: '2'
   html_document:
@@
       collapsed: no
+  pdf_document:
+    toc: yes
+    toc_depth: '2'
+  word_document:
+    toc: yes
+    toc_depth: '2'
 html_notebook:
@@
 Install packages (if they are not available in your version of R)
-```{r Installing packages}
+```{r Installing packages, include = FALSE}
 #install.packages("summarytools")
@@
 Load packages
-```{r Load packages}
+```{r Load packages, include = FALSE}
 library(knitr)
@@
 Define colours for plotting this are the standard coping colours
-```{r Colour palettes: COPING}
+```{r Colour palettes: COPING, include = FALSE}
 COPINGpalette2 <- c("#78D9C5",
@@
 Set up ggplot theme for the plots
-```{r ggplot theme}
+```{r ggplot theme, include=FALSE}
 theme_personal <-  theme(
@@
 ## Read in data
-```{r read in data}
+```{r read in data, include = FALSE}
 dat.raw <- readRDS(file = paste0(data_path, "/baseline_and_cfs_wave6.rds")) #NEEDS CHANGING
@@
 
-```{r}
+```{r key worker status frequencies by probable Covid}
 key_worker_category_per_Covid_prop_total <- dat.raw %>%
@@
 
-# Scoring for neuro measures
+# Scoring for neuro measures (NOT INCLUDED)
 
 # ALSfrs
-```{ALSfrs col names r}
+```{r ALSfrs col names, include = FALSE}
 als.col.names <- dat.raw %>%
@@
 
-```{ALSfrs row sums r}
+```{r ALSfrs row sums, include = FALSE}
 dat.raw <- dat.raw %>%
@@
 
-```{ALSfrs frequencies r}
+```{r ALSfrs frequencies, include = FALSE}
 dat.raw %>%
@@
 # ESS
-```{ESS col names r}
+```{r ESS col names, include = FALSE}
 ess.col.names <- dat.raw %>%
@@
 
-```{ESS row sums r}
+```{r ESS row sums, include = FALSE}
 dat.raw <- dat.raw %>%
@@
 
-```{ESS frequencies r}
+```{r ESS frequencies, include=FALSE}
 dat.raw %>%
@@
 
-```{r nmsw col names}
+```{r nmsw col names, include = FALSE}
 nmsw.col.names <- dat.raw %>%
@@
 
-```{r scoring NMSW}
+```{r scoring NMSW, include = FALSE}
 dat.raw <- dat.raw %>% 
@@
 
-```{r}
+```{r select cfs variables, include = FALSE}
 cfs.col.names <- dat.raw %>%
@@
 ```
-```{r}
+
+```{r calculate sum score, include = FALSE}
 dat.raw <- dat.raw %>%
@@
 
-```{r}
+```{r get sum scores by probable Covid}
 dat.raw %>%
@@
 
-```{r}
+CFS cut-off scores require individual symptom-level scores to be binary.
+Script below recodes variables to binary.
+```{r recode cfs variables to binary, include = FALSE}
 dat.raw$cfs.correct_word_find_difficult_binary <- if_else(dat.raw$cfs.correct_word_find_difficult_numeric >= 3, 1,0)
@@
 
-```{r}
+```{r cfs select binary variables, include = FALSE}
 cfs.col.names.bi <- dat.raw %>%
@@
 ```
-```{r}
+
+```{r calculate cfs cut-off groups, include = FALSE}
 dat.raw <- dat.raw %>%
@@
 
-```{r}
+```{r cfs fatigue cases by probable covid}
 dat.raw %>%
@@
 ```
+
+```{r cfs fatigue cases by probable covid by Sample}
+fatigue_by_covid_by_sample <- dat.raw %>%
+  filter(!is.na(startDate.coping)) %>%
+  filter(!is.na(covid_probable_case_incl_screening)) %>%
+  filter(!is.na(cfs.sum_score_case)) %>%
+  group_by(covid_probable_case_incl_screening, Sample) %>%
+  count(covid_probable_case_incl_screening, cfs.sum_score_case) %>%
+  mutate(Prop = round(n/sum(n), 2))
+
+kable(fatigue_by_covid_by_sample)
+```

### 2020-10-26 PANNEURO_CFS_merge_script_WHO-pres.Rmd
Added BMI data to merge script

@@
 ---
-title: "PANCHANGE_data_merging"
-author: "Christopher Huebel"
+title: "Data merging for WHO presentation"
+author: "Christopher Huebel and Molly Davies"
 date: "17/08/2020"
@@
 
+bmi_data <- read_rds(path = paste0(data_path, "/bmi.rds"))
+
+```
+
+```{r rename NBR cohort in bmi dataset}
+bmi_data <- bmi_data%>%
+  mutate(
+    Sample = 
+    recode(
+      Sample, 
+      "SP0068" = "NBR"
+    )
+  )
 ```
@@
 ```{r merge data frames}
-dat <- left_join(
+dat1 <- left_join(
   coping_baseline,
@@
 )
+
+dat <- left_join(
+  dat1,
+  bmi_data,
+  by = c("Sample", "ID")
+)
+
 ```

### 2020-10-27 PANNEURO_CFS_merge_script_WHO-pres.Rmd
bmi added

--- 2020-10-26 PANNEURO_CFS_merge_script_WHO-pres.Rmd
@@
 #source raw data directory: data.raw_path
-source("../PANCHANGE_raw_path.R")
+source("/Users/alishpalmos/Documents/GitHub//PANCHANGE_raw_path.R")
 ```
@@
 
+bmi <- read_rds(path = paste0(data_path, "/bmi.rds"))
+
 ```
@@
   cfs_wave6, by = c("Sample", "ID")
+)
+
+dat <- left_join(
+  dat, bmi, by = c("Sample", "ID")
 )

### 2020-10-27 PANNEURO_analysis_WHO_pres.Rmd
bmi added

--- 2020-10-26 PANNEURO_analysis_WHO_pres.Rmd
@@
 #source data directory: data_path
-source("../PANCHANGE_raw_path.R")
+source("/Users/alishpalmos/Documents/GitHub//PANCHANGE_raw_path.R")
 ```
@@
 ## COVID probable diagnosis
-```{r COVID probable diagnosis frequencies}
+```{r COVID probable diagnosis}
 dat.raw %>%
@@
 ## Age
-### Proportion tables
-```{r age_category per Covid prop per total}
+## Proportion tables
+```{r age_category per Sample prop per total}
 age_category_per_Covid_prop_total <- dat.raw %>%
   count(age_category, covid_probable_case_incl_screening) %>%
-  mutate(Prop = round(n/sum(n), 2)) %>% 
-  drop_na()
+  mutate(Prop = round(n/sum(n), 2))
 
@@
 
-```{r age_category per Covid prop per Covid}
-age_category_per_Covid_prop_Covid <- dat.raw %>%
-  group_by(covid_probable_case_incl_screening) %>%
-  count(age_category, covid_probable_case_incl_screening) %>%
+```{r age_category per Sample prop per Sample}
+age_category_per_Sample_prop_Sample <- dat.raw %>%
+  group_by(Sample) %>%
+  count(age_category, Sample) %>%
+  mutate(Prop = round(n/sum(n), 2))
+
+kable(age_category_per_Sample_prop_Sample)
+age_category_per_Sample_prop_Sample
+```
+
+## Cross tables
+```{r age_category per Sample prop cross table}
+age_category_per_Sample_prop_Sample_cross_table <- dat.raw %>%
+  group_by(Sample) %>%
+  count(age_category, Sample) %>%
   mutate(Prop = round(n/sum(n), 2)) %>%
-  drop_na()
-
-kable(age_category_per_Covid_prop_Covid)
-age_category_per_Covid_prop_Covid
-```
-
-### Cross tables
-```{r age_category per Covid prop cross table}
-age_category_per_Covid_prop_Covid_cross_table <- dat.raw %>%
-  group_by(covid_probable_case_incl_screening) %>%
-  count(age_category, covid_probable_case_incl_screening) %>%
-  drop_na() %>% 
-  mutate(Prop = round(n/sum(n), 2)) %>%
-  pivot_wider(names_from = covid_probable_case_incl_screening, values_from = c(n, Prop))
-
-kable(age_category_per_Covid_prop_Covid_cross_table)
-age_category_per_Covid_prop_Covid_cross_table
-```
-
-### Collapse age categories
-```{r Collapse age_category}
-dat.raw <- dat.raw %>%
-  mutate(age_category_collapsed_numeric =
-           case_when(
-             age_category_numeric == 1 ~ 0,
-             age_category_numeric == 2 ~ 1,
-             age_category_numeric == 3 ~ 2,
-             age_category_numeric == 4 ~ 3,
-             age_category_numeric == 5 ~ 4,
-             age_category_numeric == 6 ~ 5,
-             age_category_numeric == 7 ~ 6,
-             age_category_numeric == 8 ~ 7,
-             age_category_numeric == 9 ~ 8,
-             age_category_numeric == 10 ~ 8,
-             age_category_numeric == 11 ~ 8,
-             age_category_numeric == 12 ~ 8,
-             age_category_numeric == 13 ~ 8
-
-           )
-  )
-
-dat.raw <- dat.raw %>%
-  mutate(age_category_collapsed =
-           recode_factor(
-             age_category_collapsed_numeric,
-             `0` = "16-18",
-             `1` = "19-25",
-             `2` = "26-35",
-             `3` = "36-45",
-             `4` = "46-55",
-             `5` = "56-65",
-             `6` = "66-70",
-             `7` = "71-75",
-             `8` = "76+"
-           )
-  )
-
-dat.raw %>%
-  freq(age_category_collapsed)
-```
-
-### Proportion tables
-```{r age_category_collapsed per Sample prop per total}
-age_category_collapsed_per_Covid_prop_total <- dat.raw %>%
-  count(age_category_collapsed, covid_probable_case_incl_screening) %>%
-  mutate(Prop = round(n/sum(n), 2)) %>% 
-  drop_na()
-
-kable(age_category_collapsed_per_Covid_prop_total)
-age_category_collapsed_per_Covid_prop_total
-```
-
-```{r age_category_collapsed per Sample prop per Sample}
-age_category_collapsed_per_Covid_prop_Covid <- dat.raw %>%
-  group_by(covid_probable_case_incl_screening) %>%
-  count(age_category_collapsed, covid_probable_case_incl_screening) %>%
-  mutate(Prop = round(n/sum(n), 2)) %>% 
-  drop_na()
-
-kable(age_category_collapsed_per_Covid_prop_Covid)
-age_category_collapsed_per_Covid_prop_Covid
-```
-
-### Cross tables
-```{r age_category_collapsed per Sample prop cross table}
-age_category_collapsed_per_Covid_prop_Covid_cross_table <- dat.raw %>%
-  group_by(covid_probable_case_incl_screening) %>%
-  count(age_category_collapsed, covid_probable_case_incl_screening) %>%
-  drop_na() %>% 
-  mutate(Prop = round(n/sum(n), 2)) %>%
-  pivot_wider(names_from = covid_probable_case_incl_screening, values_from = c(n, Prop))
-
-kable(age_category_collapsed_per_Covid_prop_Covid_cross_table)
-age_category_collapsed_per_Covid_prop_Covid_cross_table
-```
-
-### Chi square test
-```{r age_category per probable Covid chisquare test}
-age_category_per_Covid_chissquare_test <- dat.raw %>%
-  filter(!is.na(covid_probable_case_incl_screening)) %>%
-  count(age_category_collapsed, covid_probable_case_incl_screening) %>%
-  spread(key = covid_probable_case_incl_screening, value = n) %>%
-  select(-age_category_collapsed) %>%
-  chisq.test() %>%
-  glance()
-
-kable(age_category_per_Covid_chissquare_test)
-age_category_per_Covid_chissquare_test
+  pivot_wider(names_from = Sample, values_from = c(n, Prop))
+
+kable(age_category_per_Sample_prop_Sample_cross_table)
+age_category_per_Sample_prop_Sample_cross_table
 ```
@@
 
-## BMI not available
+## BMI
+
+```{r}
+
+dat.raw$bmi[is.infinite(dat.raw$bmi)] = NA
+
+dat.raw <- dat.raw %>%
+  mutate(
+  bmi.categories=cut(dat.raw$bmi, breaks=c(-Inf, 10, 15, 20, 25, 30, 35, 40, 45, 50, 55,  Inf), labels=c("too low","10 and less","10 to 15", "15 to 20", "20 to 25", "25 to 30", "30 to 35", "35 to 40", "40 to 45", "45 to 50", "50 to 55")))
+
+```
+
+```{r bmi_category per Sample prop per total}
+
+bmi_category_per_Covid_prop_total <- dat.raw %>%
+  count(bmi.categories, covid_probable_case_incl_screening) %>%
+  mutate(Prop = round(n/sum(n), 2))
+
+options(knitr.kable.NA = '')
+kable(bmi_category_per_Covid_prop_total)
+bmi_category_per_Covid_prop_total
+```
+```{r bmi_category per Sample prop per Sample}
+bmi_category_per_Sample_prop_Sample <- dat.raw %>%
+  group_by(Sample) %>%
+  count(bmi.categories, Sample) %>%
+  mutate(Prop = round(n/sum(n), 2))
+
+kable(bmi_category_per_Sample_prop_Sample)
+bmi_category_per_Sample_prop_Sample
+```
 
@@
 ## Smoking
-
-## BMI
 
@@
 
-###Chi-square
-
-```{r ethnicity per probable Covid chisquare test}
-ethnicity_per_Covid_chissquare_test <- dat.raw %>%
-  filter(!is.na(covid_probable_case_incl_screening)) %>%
-  count(Ethnicity_collapsed, covid_probable_case_incl_screening) %>%
-  spread(key = covid_probable_case_incl_screening, value = n) %>%
-  select(-Ethnicity_collapsed) %>%
-  chisq.test() %>%
-  glance()
-
-kable(ethnicity_per_Covid_chissquare_test)
-ethnicity_per_Covid_chissquare_test
-```
-
 # Neurological frequencies
-
+** NEED TO BE CHANGED TO covid_probable_case_incl_screening **
 ```{r neurological frequencies alsfrs}
@@
 
-# Scoring for neuro measures
-
+**ADD SCORING FOR NEURO MEASURES**
 # ALSfrs

### 2020-10-27 PANNEURO_analysis_WHO_pres.Rmd
Small fixes.

--- 2020-10-26 PANNEURO_analysis_WHO_pres.Rmd
@@
 
-# Scoring for neuro measures (NOT INCLUDED)
-
-# ALSfrs
+# Scoring for neuro measures
+
+# ALSfrs (not included)
 ```{r ALSfrs col names, include = FALSE}
@@
 ```
+
 # ESS
@@
 
+ess.col.names
 ```
@@
 ```{r ESS row sums, include = FALSE}
+
+# Create vector with scoring key: If the item is reversed coded use -1. 
+# There needs to be the correct number of values for each item in the questionnaire. 
+ess.items_key <- c(1,1,1,1,1,1,1,1)
+
+# Create vector with items that are included in sum score
+ess.items <- c(
+  "ess.sitting_and_reading_numeric",
+  "ess.watching_tv_numeric",
+  "ess.sitting_inactive_in_a_public_place_numeric",
+  "ess.break_passenger_car_hour_numeric",
+  "ess.afternoon_rest_circumstances_lying_numeric",
+  "ess.sitting_and_talking_to_someone_numeric",
+  "ess.sitting_quietly_after_a_lunch_without_alcohol_numeric",
+  "ess.car_minutes_stopped_traffic_numeric"
+  )
+
+# Calculate sum score
+ess.scored_items <- scoreItems(keys = ess.items_key,
+                                        items = dat.raw[ess.items],
+                                        totals = TRUE, 
+                                        missing = TRUE, 
+                                        impute = 'none', 
+                                        min = 0, 
+                                        max = 3)
+# Add in column to tibble
+dat.raw$ess.sum_score_raw <- ess.scored_items$scores
+
+# Look at values
+dat.raw %>%
+  group_by(covid_probable_case_incl_screening) %>% 
+  descr(ess.sum_score_raw,
+        stats = "common"
+        )
+
+```
+
+```{r ESS raw score frequencies}
+ess_frequencies <- dat.raw %>%
+  filter(!is.na(startDate.coping)) %>%
+  filter(!is.na(covid_probable_case_incl_screening)) %>%
+  filter(!is.na(ess.col.names)) %>%
+  group_by(covid_probable_case_incl_screening) %>%
+  count(covid_probable_case_incl_screening, ess.sum_score_raw) %>%
+  mutate(Prop = round(n/sum(n), 2))
+
+kable(ess_frequencies)
+```
+
+ESS scores: Interpretation
+•	0 to 10 = normal range of sleepiness in healthy adults
+•	11 to 14 = mild sleepiness
+•	15 to 17 = moderate sleepiness
+•	18 to 24 = severe sleepiness
+
+```{r ess clinical categories}
 dat.raw <- dat.raw %>% 
-  mutate(ess.col.names =
-   rowSums(select(.,ess.col.names), na.rm = F)
-   )
-```
-
-```{r ESS frequencies, include=FALSE}
-dat.raw %>%
-  filter(!is.na(startDate.coping)) %>%
-  filter(!is.na(covid_probable_case_incl_screening)) %>%
-  filter(!is.na(ess.col.names)) %>%
-  group_by(covid_probable_case_incl_screening) %>%
-  count(covid_probable_case_incl_screening, ess.col.names) %>%
-  mutate(Prop = round(n/sum(n), 2))
+  mutate(ess.cutoff.scores =
+           case_when(ess.col.names <= 10 ~ "Normal sleepiness",
+                     ess.col.names > 10 & ess.col.names <= 14 ~ "Mild sleepiness",
+                     ess.col.names > 14 & ess.col.names <= 17 ~ "Moderate sleepiness",
+                     ess.col.names > 17 & ess.col.names <= 24 ~ "Severe sleepiness",
+                     )
+           )
+
+```
+
+```{r ESS clinical categories frequencies}
+ess_frequencies <- dat.raw %>%
+  filter(!is.na(startDate.coping)) %>%
+  filter(!is.na(covid_probable_case_incl_screening)) %>%
+  filter(!is.na(ess.cutoff.scores)) %>%
+  group_by(covid_probable_case_incl_screening) %>%
+  count(covid_probable_case_incl_screening, ess.cutoff.scores) %>%
+  mutate(Prop = round(n/sum(n), 2))
+
+kable(ess_frequencies)
 ```
@@
 ```
+
+## Memory
+
+```{r}
+
+```

### 2020-10-27 PANNEURO_analysis_WHO_pres.Rmd

--- 2020-10-27 PANNEURO_analysis_WHO_pres.Rmd
@@
            )
-
-```
 

### 2020-10-27 PANNEURO_preprocessing_BMI_WHO-pres.Rmd

---
title: "PANNEURO_CFS_cleaning_WHO_pres"
author: "Molly Davies (adapting from a script by K Purves, K Thompson, and C Huebel)"
date: "26/10/2020"
output: html_document
---

This is a script to quickly clean the Chalder Fatigue Scale in COPING follow-up set B, for the purpose of Gerome Breen's presentation to the WHO.

#Set up
```{r Setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      comment=NA,
                      prompt=FALSE,
                      cache=FALSE)

options(bitmapType = 'quartz') # to render fonts better
```

Clear global environment
```{r Clear global environment}
remove(list = ls())
```

Retrieve the current date to use it for file endings to not overwrite files when one exports files
```{r Recent date}
date = Sys.Date()
```

#Packages
Install packages (if they are not available in your version of R)
```{r Installing packages}
#install.packages("summarytools")
#install.packages("tidyverse")
#install.packages("psych")
#install.packages("eeptools")
#install.packages("skimr")
```

Load packages
```{r Load packages}
library(knitr)
library(summarytools)
library(psych)
library(eeptools) # Needed to calculate age from birthdate
library(tidyverse)
```

# Colour palettes
Define colours for plotting this are the standard coping colours
```{r Colour palettes: COPING}
COPINGpalette2 <- c("#78D9C5",
                    "#F5BE5E")

COPINGpalette3 <- c("#78D9C5",
                    "#F5BE5E",
                    "#EEB6E9")

COPINGpalette4 <- c("#78D9C5",
                    "#F5BE5E",
                    "#EEB6E9",
                    "#DBDB73")

COPINGpalette5 <- c("#78D9C5",
                    "#F5BE5E",
                    "#EEB6E9",
                    "#DBDB73", 
                    "#FFED98")

COPINGpalette6 <- c("#78D9C5",
                    "#F5BE5E",
                    "#EEB6E9",
                    "#DBDB73",
                    "#FFED98",
                    "#BFD2EB")

COPINGpalette7 <- c("#78D9C5",
                    "#F5BE5E",
                    "#EEB6E9",
                    "#DBDB73", 
                    "#FFED98",
                    "#BFD2EB", 
                    "#808080")

COPINGpaletteGRAD <- c("#F5BE5E",
                       "#FFD284",
                       "#FFEED1",
                       "#B5B5B5",
                       "#DEFFF8",
                       "#94F6E1",
                       "#78D9C5")

COPINGNeuCenterpalette <- c("#78D9C5",
                            "#808080",
                            "#F5BE5E")

RAMPworseGRADpalette <- c("#78D9C5",
                          "#FFEED1",
                          "#F5BE5E",
                          "#FFB1B5")
GLADpalette = c("#efc00b", 
                "#b7dee8")  
```

Choose in this chunk which palette to use
04.07.2020 - Default to 2 colour COPING palette
```{r Choose colour palette}
palette = COPINGpalette2
```

#Add_numeric function
Function used to convert character variables into numeric variables. 
```{r add_numeric function}
add_numeric <- function(dat, exclude = NULL) {
  dat_fct <- sjlabelled::as_label(dat)

  dat <- dat[!colnames(dat) %in% exclude]
  colnames(dat) <- paste(colnames(dat), "numeric", sep = "_")
  return(bind_cols(dat_fct, dat))
}
```

# Data import and merging

Note: GLAD only receives current measures and RAMP questionnaire
Note: All COPING surveys are separate surveys

# Source data file paths

```{r source file path}
#source raw data directory: data.raw_path
source("../PANCHANGE_raw_path.R")
```

# Read in data
```{r glad dem cols}
nbr.bmi.raw <- readRDS(file = paste0(data.raw_path, "/nbr/dem_nbr.rds"))
dim(nbr.bmi.raw)
colnames(nbr.bmi.raw)

glad.bmi.raw <- readRDS(file = paste0(data.raw_path, "/glad/dem_glad.rds"))
dim(glad.bmi.raw)
colnames(glad.bmi.raw)

edgi.bmi.raw <- readRDS(file = paste0(data.raw_path, "/edgi/dem_edgi.rds"))
dim(edgi.bmi.raw)
colnames(edgi.bmi.raw)
```

# Select variables
```{r cfs cleaning}

# NBR cohort
nbr.bmi.raw <- nbr.bmi.raw %>%
    drop_na(subjectid) %>% # Drop NAs
    distinct(subjectid, .keep_all = TRUE) %>% # Remove duplicates based on ID
    separate(subjectid, into = c("Sample", "ID.intm"), sep = 6) %>% # Split ID in Sample and Number
    separate(ID.intm, into = "ID", sep = 7) %>%
    mutate(ID = as.numeric(ID)) %>%
    select(
      Sample, # Sample
      ID, # ID
         height.1 = demographics.what_is_your_current_height.1, 
         height.2 = demographics.what_is_your_current_height.2, 
         height = demographics.what_is_your_current_height, 
         weight = demographics.provide_current_weight_pregnant,
         weight.1 = demographics.provide_current_weight_pregnant.1, 
         weight.2 = demographics.provide_current_weight_pregnant.2)

# GLAD cohort
glad.bmi.raw <- glad.bmi.raw %>%
    drop_na(externalDataReference) %>% # Drop NAs
    distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
    separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
    mutate(ID = as.numeric(ID)) %>%
    select(
      Sample, # Sample
      ID, # ID
         height.1 = demographics.what_is_your_current_height.1, 
         height.2 = demographics.what_is_your_current_height.2, 
         height = demographics.what_is_your_current_height, 
         weight = demographics.current_weight_pregnant_weight,
         weight.1 = demographics.current_weight_pregnant_weight.1, 
         weight.2 = demographics.current_weight_pregnant_weight.2
         )

# EDGI

edgi.bmi.raw <- edgi.bmi.raw %>%
  drop_na(externalDataReference) %>% # Drop NAs
    distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
    separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
    mutate(ID = as.numeric(ID)) %>%
    select(
      Sample, # Sample
      ID, # ID
         height.1 = demographics.what_is_your_current_height.1, 
         height.2 = demographics.what_is_your_current_height.2, 
         height = demographics.what_is_your_current_height, 
         weight = demographics.pregnant_current_weight_provide,
         weight.1 = demographics.pregnant_current_weight_provide.1, 
         weight.2 = demographics.pregnant_current_weight_provide.2
         )

 colnames(edgi.bmi.raw) <- c("Sample", "ID", "inch", "cm", "ft", "stn", "pnd", "kg")
 colnames(nbr.bmi.raw) <- c("Sample", "ID", "inch", "cm", "ft", "stn", "pnd", "kg")
 colnames(glad.bmi.raw) <- c("Sample", "ID", "ft", "inch", "cm", "kg", "stn", "pnd")

edgi.bmi.raw$ft_cm <- (edgi.bmi.raw$ft * 30.48)
edgi.bmi.raw$inch_cm <- (edgi.bmi.raw$inch * 2.54)
edgi.bmi.raw$new_cm <- (edgi.bmi.raw$ft_cm + edgi.bmi.raw$inch_cm)
edgi.bmi.raw$cm_all <- rowSums(edgi.bmi.raw[, c("cm", "new_cm")], na.rm=T)

edgi.bmi.raw$stn_kg <- (edgi.bmi.raw$stn * 6.35029)
edgi.bmi.raw$pnd_kg <- (edgi.bmi.raw$pnd * 0.453592)
edgi.bmi.raw$new_kg <- (edgi.bmi.raw$stn_kg + edgi.bmi.raw$pnd_kg)
edgi.bmi.raw$kg_all <- rowSums(edgi.bmi.raw[, c("kg", "new_kg")], na.rm=T)

nbr.bmi.raw$cm <- as.numeric(nbr.bmi.raw$cm)
nbr.bmi.raw$ft_cm <- (nbr.bmi.raw$ft * 30.48)
nbr.bmi.raw$inch_cm <- (nbr.bmi.raw$inch * 2.54)
nbr.bmi.raw$new_cm <- (nbr.bmi.raw$ft_cm + nbr.bmi.raw$inch_cm)
nbr.bmi.raw$cm_all <- rowSums(nbr.bmi.raw[, c("cm", "new_cm")], na.rm=T)

nbr.bmi.raw$stn_kg <- (nbr.bmi.raw$stn * 6.35029)
nbr.bmi.raw$pnd_kg <- (nbr.bmi.raw$pnd * 0.453592)
nbr.bmi.raw$new_kg <- (nbr.bmi.raw$stn_kg + nbr.bmi.raw$pnd_kg)
nbr.bmi.raw$kg_all <- rowSums(nbr.bmi.raw[, c("kg", "new_kg")], na.rm=T)

glad.bmi.raw$ft_cm <- (glad.bmi.raw$ft * 30.48)
glad.bmi.raw$inch_cm <- (glad.bmi.raw$inch * 2.54)
glad.bmi.raw$new_cm <- (glad.bmi.raw$ft_cm + glad.bmi.raw$inch_cm)
glad.bmi.raw$cm_all <- rowSums(glad.bmi.raw[, c("cm", "new_cm")], na.rm=T)

glad.bmi.raw$stn_kg <- (glad.bmi.raw$stn * 6.35029)
glad.bmi.raw$pnd_kg <- (glad.bmi.raw$pnd * 0.453592)
glad.bmi.raw$new_kg <- (glad.bmi.raw$stn_kg + glad.bmi.raw$pnd_kg)
glad.bmi.raw$kg_all <- rowSums(glad.bmi.raw[, c("kg", "new_kg")], na.rm=T)

# finally, we can calculate the BMI

edgi.bmi.raw$cm_whole <- edgi.bmi.raw$cm_all/100
edgi.bmi.raw$bmi <- edgi.bmi.raw$kg_all / (edgi.bmi.raw$cm_whole^2)

nbr.bmi.raw$cm_whole <- nbr.bmi.raw$cm_all/100
nbr.bmi.raw$bmi <- nbr.bmi.raw$kg_all / (nbr.bmi.raw$cm_whole^2)
nbr.bmi.raw$bmi_new <- round(nbr.bmi.raw$bmi, digits = 2)
nbr.bmi.raw$bmi <- nbr.bmi.raw$bmi_new

glad.bmi.raw$cm_whole <- glad.bmi.raw$cm_all/100
glad.bmi.raw$bmi <- glad.bmi.raw$kg_all / (glad.bmi.raw$cm_whole^2)

# then let's get this into the main COPING data frame and delete this one and also tidy up

# Merge datasets

glad.bmi.raw <- glad.bmi.raw %>%
  select(Sample, ID, bmi)

edgi.bmi.raw <- edgi.bmi.raw %>%
  select(Sample, ID, bmi)

nbr.bmi.raw <- nbr.bmi.raw %>%
  select(Sample, ID, bmi)

 bmi <- as.data.frame(rbind(nbr.bmi.raw, 
                                 glad.bmi.raw, 
                                 edgi.bmi.raw))

#Export dataset

saveRDS(object = bmi, file = paste0(data_path, "/bmi.rds"))

### 2020-10-27 PANNEURO_analysis_WHO_pres.Rmd
mem questions

--- 2020-10-27 PANNEURO_analysis_WHO_pres.Rmd
@@
 #source data directory: data_path
-source("/Users/alishpalmos/Documents/GitHub//PANCHANGE_raw_path.R")
+source("../PANCHANGE_raw_path.R")
 ```
@@
 
-## BMI
-
-```{r}
-
-dat.raw$bmi[is.infinite(dat.raw$bmi)] = NA
-
-dat.raw <- dat.raw %>%
-  mutate(
-  bmi.categories=cut(dat.raw$bmi, breaks=c(-Inf, 10, 15, 20, 25, 30, 35, 40, 45, 50, 55,  Inf), labels=c("too low","10 and less","10 to 15", "15 to 20", "20 to 25", "25 to 30", "30 to 35", "35 to 40", "40 to 45", "45 to 50", "50 to 55")))
-
-```
-
-```{r bmi_category per Sample prop per total}
-
-bmi_category_per_Covid_prop_total <- dat.raw %>%
-  count(bmi.categories, covid_probable_case_incl_screening) %>%
-  mutate(Prop = round(n/sum(n), 2))
-
-options(knitr.kable.NA = '')
-kable(bmi_category_per_Covid_prop_total)
-bmi_category_per_Covid_prop_total
-```
-```{r bmi_category per Sample prop per Sample}
-bmi_category_per_Sample_prop_Sample <- dat.raw %>%
-  group_by(Sample) %>%
-  count(bmi.categories, Sample) %>%
-  mutate(Prop = round(n/sum(n), 2))
-
-kable(bmi_category_per_Sample_prop_Sample)
-bmi_category_per_Sample_prop_Sample
-```
+## BMI not available
 
@@
 ## Smoking
+
+## BMI
 
@@
 
-## CFS
+```
+##CFS
 
@@
 dat.raw$cfs.do_you_need_to_rest_more_binary <- if_else(dat.raw$cfs.do_you_need_to_rest_more_numeric >= 3, 1,0)
-dat.raw$cfs.how_is_your_memory_numeric_binary <- if_else(dat.raw$cfs.how_is_your_memory_numeric >= 3, 1,0) 
+dat.raw$cfs.how_is_your_memory_binary <- if_else(dat.raw$cfs.how_is_your_memory_numeric >= 3, 1,0) 
 dat.raw$cfs.make_slips_speaking_tongue_binary <- if_else(dat.raw$cfs.make_slips_speaking_tongue_numeric >= 3, 1,0)
@@
 ```
+
+##memory
+
+```{r, echo = FALSE}
+
+dat.raw[616] <- data.frame(dat.raw[616] %>%
+             map(lfactor, levels = c(0,1), labels = c("same/better", "worse")))
+
+mem.table <- dat.raw %>%
+  filter(!is.na(startDate.coping)) %>%
+  filter(!is.na(covid_probable_case_incl_screening)) %>%
+  filter(!is.na(cfs.how_is_your_memory)) %>%
+  group_by(covid_probable_case_incl_screening) %>%
+  count(covid_probable_case_incl_screening, cfs.how_is_your_memory) %>%
+  mutate(Prop = round(n/sum(n), 2))
+
+kable(mem.table)
+```
+
+```{r, echo = FALSE}
+
+mem.table2 <- dat.raw %>%
+  filter(!is.na(startDate.coping)) %>%
+  filter(!is.na(covid_probable_case_incl_screening)) %>%
+  filter(!is.na(cfs.how_is_your_memory_binary)) %>%
+  group_by(covid_probable_case_incl_screening) %>%
+  count(covid_probable_case_incl_screening, cfs.how_is_your_memory_binary) %>%
+  mutate(Prop = round(n/sum(n), 2))
+
+kable(mem.table2)
+```
+
+```

### 2020-10-27 PANNEURO_analysis_WHO_pres.Rmd

--- 2020-10-27 PANNEURO_analysis_WHO_pres.Rmd
@@
 
-```{r cfs fatigue cases by probable covid}
-dat.raw %>%
-  filter(!is.na(startDate.coping)) %>%
-  filter(!is.na(covid_probable_case_incl_screening)) %>%
-  filter(!is.na(cfs.sum_score_case)) %>%
-  group_by(covid_probable_case_incl_screening) %>%
-  count(covid_probable_case_incl_screening, cfs.sum_score_case) %>%
-  mutate(Prop = round(n/sum(n), 2))
-```
-
 ```{r cfs fatigue cases by probable covid by Sample}
@@
 
-## Memory
-
-```{r}
-
-```
+##memory
+
+```{r, echo = FALSE}
+
+dat.raw[616] <- data.frame(dat.raw[616] %>%
+             map(lfactor, levels = c(0,1), labels = c("same/better", "worse")))
+
+mem.table <- dat.raw %>%
+  filter(!is.na(startDate.coping)) %>%
+  filter(!is.na(covid_probable_case_incl_screening)) %>%
+  filter(!is.na(cfs.how_is_your_memory)) %>%
+  group_by(covid_probable_case_incl_screening) %>%
+  count(covid_probable_case_incl_screening, cfs.how_is_your_memory) %>%
+  mutate(Prop = round(n/sum(n), 2))
+
+kable(mem.table)
+```
+
+```{r, echo = FALSE}
+
+mem.table2 <- dat.raw %>%
+  filter(!is.na(startDate.coping)) %>%
+  filter(!is.na(covid_probable_case_incl_screening)) %>%
+  filter(!is.na(cfs.how_is_your_memory_binary)) %>%
+  group_by(covid_probable_case_incl_screening) %>%
+  count(covid_probable_case_incl_screening, cfs.how_is_your_memory_binary) %>%
+  mutate(Prop = round(n/sum(n), 2))
+
+kable(mem.table2)
+```

### 2020-10-27 PANNEURO_analysis_WHO_pres.Rmd
Fixed error with ESS frequencies.

--- 2020-10-27 PANNEURO_analysis_WHO_pres.Rmd
@@
 
-```{r}
+```{r bmi recode}
 
@@
 
-```{r ESS raw score frequencies}
+```{r ESS raw scores by Covid case}
 ess_frequencies <- dat.raw %>%
@@
   filter(!is.na(covid_probable_case_incl_screening)) %>%
-  filter(!is.na(ess.col.names)) %>%
+  filter(!is.na(ess.sum_score_raw)) %>%
   group_by(covid_probable_case_incl_screening) %>%
@@
   mutate(ess.cutoff.scores =
-           case_when(ess.col.names <= 10 ~ "Normal sleepiness",
-                     ess.col.names > 10 & ess.col.names <= 14 ~ "Mild sleepiness",
-                     ess.col.names > 14 & ess.col.names <= 17 ~ "Moderate sleepiness",
-                     ess.col.names > 17 & ess.col.names <= 24 ~ "Severe sleepiness",
+           case_when(ess.sum_score_raw <= 10 ~ "Normal sleepiness",
+                     ess.sum_score_raw > 10 & ess.sum_score_raw <= 14 ~ "Mild sleepiness",
+                     ess.sum_score_raw > 14 & ess.sum_score_raw <= 17 ~ "Moderate sleepiness",
+                     ess.sum_score_raw > 17 & ess.sum_score_raw <= 24 ~ "Severe sleepiness",
                      )
@@
 ```{r ESS clinical categories frequencies}
-ess_frequencies <- dat.raw %>%
-  filter(!is.na(startDate.coping)) %>%
-  filter(!is.na(covid_probable_case_incl_screening)) %>%
-  filter(!is.na(ess.cutoff.scores)) %>%
+ess_frequencies_clinical <- dat.raw %>%
+  filter(!is.na(startDate.coping)) %>%
+  filter(!is.na(covid_probable_case_incl_screening)) %>%
+  filter(!is.na(ess.sum_score_raw)) %>%
   group_by(covid_probable_case_incl_screening) %>%
@@
 
-kable(ess_frequencies)
-```
-
+kable(ess_frequencies_clinical)
+```
+
+# NMSW
 ```{r nmsw col names, include = FALSE}

### 2020-11-03 PANCHANGE_exclusion_descriptives.Rmd
N sign up per month, impute retrospective if no change, retro and prepan correlations and drop na from education comparison tables

@@
 library(ggpubr)
+library(stringr)
 ```
@@
 ```{r read in data}
-dat.raw <- readRDS(file = paste0(data_path, "/four_cohorts_variables.rds"))
+dat.raw <- readRDS(file = paste0(data_path, "four_cohorts_variables.rds"))
 dim(dat.raw)
@@
 Exclude individuals with NA for the MHD categories
-Individuals with NAs for age/gender have already been excluded in pre-processing script, but they get excluded here to be save and to double check previous programming.
+Individuals with NAs for age/gender have already been excluded in pre-processing script, but they get excluded here to be safe and to double check previous programming.
 
@@
 
+#SB - Impute no change prepandemic scores
+
+I interpreted the presence of an NA in the retrospective score as an indicator of saying "no change" in their baseline scores.
+Hence, if this was the case, I imputed their baseline score.
+However, this interpretation could be wrong.
+
+Also, I'm not sure what to do if there is an NA for their baseline sum score (nothing to duplicate).
+This was the case for ocir for some reason: the retro scores were provided for some by not the corresponding baseline score?
+
+```{r Impute for gad measure}
+
+#Visualise the gad summary scores for baseline and retro
+head(dat$gad.sum_score_base, 30)
+head(dat$gad.sum_score_retro, 30)
+
+#Edit the gad sum retro score as follows: if there is a missing value in the retro sum score, give it the baseline sum score, else leave it as it is
+
+impute_dat <- dat %>% 
+  mutate(gad.sum_score_retro = 
+           if_else(is.na(dat$gad.sum_score_retro), dat$gad.sum_score_base, dat$gad.sum_score_retro))
+
+#Check that the Na's have been replaced with duplicated baseline sum scores
+head(impute_dat$gad.sum_score_base, 30)
+head(impute_dat$gad.sum_score_retro, 30)
+
+```
+
+```{r Impute for phq measure}
+
+#Visualise the phq summary scores for baseline and retro
+head(dat$phq.sum_score_base, 30)
+head(dat$phq.sum_score_retro, 30)
+
+#Edit the phq sum retro score as follows: if there is a missing value in the retro sum score, give it the baseline sum score, else leave it as it is
+
+impute_dat <- dat %>% 
+  mutate(phq.sum_score_retro = 
+           if_else(is.na(dat$phq.sum_score_retro), dat$phq.sum_score_base, dat$phq.sum_score_retro))
+
+#Check that the Na's have been replaced with duplicated baseline sum scores
+head(impute_dat$phq.sum_score_base, 30)
+head(impute_dat$phq.sum_score_retro, 30)
+
+```
+
+```{r Impute for ocir measure}
+
+#Visualise the ocir summary scores for baseline and retro
+head(dat$ocir.sum_score_base, 40)
+head(dat$ocir.sum_score_retro, 40)
+
+#Edit the ocir sum retro score as follows: if there is a missing value in the retro sum score, give it the baseline sum score, else leave it as it is
+
+impute_dat <- dat %>% 
+  mutate(ocir.sum_score_retro = 
+           if_else(is.na(dat$ocir.sum_score_retro), dat$ocir.sum_score_base,                                     dat$ocir.sum_score_retro))
+
+#Check that the Na's have been replaced with duplicated baseline sum scores
+head(impute_dat$ocir.sum_score_base, 40)
+head(impute_dat$ocir.sum_score_retro, 40)
+
+```
+
+```{r Impute for pcl measure}
+
+#Visualise the pcl summary scores for baseline and retro
+head(dat$pcl.sum_score_base, 30)
+head(dat$pcl.sum_score_retro, 30)
+
+#Edit the pcl sum retro score as follows: if there is a missing value in the retro sum score, give it the baseline sum score, else leave it as it is
+
+impute_dat <- dat %>% 
+  mutate(pcl.sum_score_retro = 
+           if_else(is.na(dat$pcl.sum_score_retro), dat$pcl.sum_score_base, dat$pcl.sum_score_retro))
+
+#Check that the Na's have been replaced with duplicated baseline sum scores
+head(impute_dat$pcl.sum_score_base, 30)
+head(impute_dat$pcl.sum_score_retro, 30)
+
+```
+
+#SB - Baseline survey completion (N per month)
+
+This is a summary of the amount of pt's completing the baseline survey per month
+
+```{r N completing coping per month}
+
+#Visualise some dates when participants completed the questionnaire
+head(dat$startDate.coping, 20)
+
+#Divide the data by sign up per month and summarise the amount of pt's completing the survey that month
+
+april_sign_up <- dat[str_detect(dat$startDate.coping, "-04-"), ] %>% 
+  select(startDate.coping) %>% 
+  summarise(April = n())
+
+may_sign_up <- dat[str_detect(dat$startDate.coping, "-05-"), ] %>% 
+  select(startDate.coping) %>% 
+  summarise(May = n())
+
+june_sign_up <- dat[str_detect(dat$startDate.coping, "-06-"), ] %>% 
+  select(startDate.coping) %>% 
+  summarise(June = n())
+
+july_sign_up <- dat[str_detect(dat$startDate.coping, "-07-"), ] %>% 
+  select(startDate.coping) %>% 
+  summarise(July = n())
+
+august_sign_up <- dat[str_detect(dat$startDate.coping, "-08-"), ] %>% 
+  select(startDate.coping) %>% 
+  summarise(August = n())
+
+september_sign_up <- dat[str_detect(dat$startDate.coping, "-09-"), ] %>% 
+  select(startDate.coping) %>% 
+  summarise(September = n())
+
+#Merge results into one tibble
+
+coping_sign_up <- april_sign_up %>% 
+  cbind(may_sign_up, june_sign_up, july_sign_up, august_sign_up, september_sign_up)
+
+#Gather the variables
+coping_sign_up <- coping_sign_up %>% 
+  gather(key = "month", value = "sign_up_number")
+
+#Proportion calculation
+coping_sign_up <- coping_sign_up %>% 
+  mutate(percentage = 
+           round((sign_up_number / sum(sign_up_number) * 100), 2))
+
+coping_sign_up
+
+```
+
 ## Vector
@@
          p.mat = mhd.p.matrix, # Matrix with p values
+         sig.level = 0.01, # Choose significant level
+         insig = "blank" # Nonsignificant correlations have no colour
+         )
+```
+
+#SB - Correlation between retropsective impute and prepan
+
+```{r Correlation prep chunk}
+# Select items for correlation matrix
+prepan_retro_items <- c(
+    "gad.sum_score_prepan",
+    "gad.sum_score_retro", 
+    "pcl.sum_score_prepan",
+    "pcl.sum_score_retro",
+    "ocir.sum_score_prepan",
+    "ocir.sum_score_retro",
+    "phq.sum_score_prepan",
+    "phq.sum_score_retro"
+)
+
+#Create a data set with only the COPING samples
+prepan_retro_dat <- dat[str_detect(dat$Sample, "NBR|GLAD|EDGI"), ]
+
+#Check that RAMP has been removed
+prepan_retro_dat %>% 
+  freq(Sample)
+
+# Calculate correlation matrix on specific columns (variables) from your data frame
+prepan_retro.corr.mat <- hetcor(
+  as.data.frame(prepan_retro_dat[,prepan_retro_items]), # Specify the data
+  use = "pairwise.complete.obs" # Use all pairwise observations
+)
+
+# Print the correlation matrix
+print(prepan_retro.corr.mat, digits = max(3, getOption("digits") - 3))
+
+# Save the correlations from the correlation matrix in an object
+prepan_retro.corr.matrix <- as.matrix(prepan_retro.corr.mat)
+
+# Save the p values from the correlation matrix in an object
+prepan_retro.p.matrix <- as.matrix(prepan_retro.corr.mat$tests)
+```
+
+```{r Correlation matrix of prepan base sum scores}
+corrplot(prepan_retro.corr.matrix, 
+         method = "color", # objects to represent the correlations on plot
+         type = "lower", # only use the lower triangle of the matrix
+         diag = FALSE, # do not show the correlations on the diagonal
+         addgrid.col = NA,
+         addCoef.col = "black", # colour for the correlation coefficients in the plot
+         tl.cex = 0.8,
+         tl.col = "black",
+         col=colorRampPalette(c("dodgerblue4","white","firebrick4"))(200), # colours for correlations
+         # Combine with significance
+         p.mat = prepan_retro.p.matrix, # Matrix with p values
          sig.level = 0.01, # Choose significant level
@@
   count(highest_education, Sample) %>%
+  drop_na() %>% 
   mutate(Prop = round(n/sum(n), 2))
@@
   count(highest_education, Sample) %>%
+  drop_na() %>% 
   mutate(Prop = round(n/sum(n), 2)) %>%
@@
   count(highest_education, Sample) %>%
+  drop_na() %>% 
   spread(key = Sample, value = n) %>%

### 2020-11-03 PANCHANGE_analysis.Rmd
find and replaced age_category_collapsed with age_category_collapsed_reordered

@@
 Prepan-baseline analyses
-Exclude individuals with NA for MHD, age, gender; exclude if prepan data collected after 1 March
+Exclude individuals with NA for MHD, age, gender; exclude if prepan data collected after 1 March (to ensure comparability with prepan analyses)
 
@@
                             "Gender_collapsed",
-                            "age_category_collapsed",
+                            "age_category_collapsed_reordered",
                             "Ethnicity_collapsed",
@@
                "Gender_collapsedNon-binary/Self-defined" = "Non-binary/Self-defined",
-               "age_category_collapsed19-25" = "19-25 years",
-               "age_category_collapsed26-35" = "26-35 years",
-               "age_category_collapsed36-45" = "36-45 years",
-               "age_category_collapsed46-55" = "46-55 years",
-               "age_category_collapsed56-65" = "56-65 years",
-               "age_category_collapsed66-70" = "66-70 years",
-               "age_category_collapsed71-75" = "71-75 years",
-               "age_category_collapsed76+" = "76+ years",
+               "age_category_collapsed_reordered19-25" = "19-25 years",
+               "age_category_collapsed_reordered26-35" = "26-35 years",
+               "age_category_collapsed_reordered36-45" = "36-45 years",
+               "age_category_collapsed_reordered46-55" = "46-55 years",
+               "age_category_collapsed_reordered56-65" = "56-65 years",
+               "age_category_collapsed_reordered66-70" = "66-70 years",
+               "age_category_collapsed_reordered71-75" = "71-75 years",
+               "age_category_collapsed_reordered76+" = "76+ years",
                "Ethnicity_collapsedMixed or multiple ethnic origins" = "Mixed or multiple ethnic origins",
@@
                              "Gender_collapsed",
-                             "age_category_collapsed",
+                             "age_category_collapsed_reordered",
                              "Ethnicity_collapsed",
@@
 ### Model 1a: Disorder hierarchical, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
 ```{r gad model1a absolute whole sample}
@@
 ### Model 1b: Overlapping disorders, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
 ```{r gad model1b absolute whole sample}
@@
 ### Model 1a: Disorder hierarchical, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
 ```{r gad model1a diff_score prepan}
@@
 ### Model 1b: Overlapping disorders, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
 ```{r gad model1b diff_score prepan}
@@
 ### Model 1a: Disorder hierarchical, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
 ```{r gad model1a sum_score prepan}
@@
 ### Model 1b: Overlapping disorders, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
 ```{r gad model1b sum_score prepan}
@@
 ### Model 1a: Disorder hierarchical, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
 ```{r gad model1a diff_score retro}
@@
 ### Model 1b: Overlapping disorders, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
 ```{r gad model1b diff_score retro}
@@
 ### Model 1a: Disorder hierarchical, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
 ```{r gad model1a sum_score retro}
@@
 ### Model 1b: Overlapping disorders, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
 ```{r gad model1b sum_score retro}
@@
 ### Model 1a: Disorder hierarchical, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
 ```{r gad model1a diff_score retro (sensitivity analysis)}
@@
 ### Model 1b: Overlapping disorders, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
 ```{r gad model1b diff_score retro (sensitivity analysis)}
@@
 ### Model 1a: Disorder hierarchical, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
 ```{r gad model1a sum_score retro (sensitivity analysis)}
@@
 ### Model 1b: Overlapping disorders, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
 ```{r gad model1b sum_score retro (sensitivity analysis)}
@@
 ### Model 1a: Disorder hierarchical, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
 ```{r phq model1a absolute whole sample}
@@
 ### Model 1b: Overlapping disorders, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
 ```{r phq model1b absolute whole sample}
@@
 ### Model 1a: Disorder hierarchical, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
 ```{r phq model1a diff_score prepan}
@@
 ### Model 1b: Overlapping disorders, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
 ```{r phq model1b diff_score prepan}
@@
 ### Model 1a: Disorder hierarchical, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
 ```{r phq model1a sum_score prepan}
@@
 ### Model 1b: Overlapping disorders, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
 ```{r phq model1b sum_score prepan}
@@
 ### Model 1a: Disorder hierarchical, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
 ```{r phq model1a diff_score retro}
@@
 ### Model 1b: Overlapping disorders, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
 ```{r phq model1b diff_score retro}
@@
 ### Model 1a: Disorder hierarchical, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
 ```{r phq model1a sum_score retro}
@@
 ### Model 1b: Overlapping disorders, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
 ```{r phq model1b sum_score retro}
@@
 ### Model 1a: Disorder hierarchical, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
 ```{r phq model1a diff_score retro (sensitivity analysis)}
@@
 ### Model 1b: Overlapping disorders, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
 ```{r phq model1b diff_score retro (sensitivity analysis)}
@@
 ### Model 1a: Disorder hierarchical, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
 ```{r phq model1a sum_score retro (sensitivity analysis)}
@@
 ### Model 1b: Overlapping disorders, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
 ```{r phq model1b sum_score retro (sensitivity analysis)}
@@
 ### Model 1a: Disorder hierarchical, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
 ```{r ocir model1a absolute whole sample}
@@
 ### Model 1b: Overlapping disorders, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
 ```{r ocir model1b absolute whole sample}
@@
 ### Model 1a: Disorder hierarchical, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
 ```{r ocir model1a diff_score prepan}
@@
 ### Model 1b: Overlapping disorders, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
 ```{r ocir model1b diff_score prepan}
@@
 ### Model 1a: Disorder hierarchical, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
 ```{r ocir model1a sum_score prepan}
@@
 ### Model 1b: Overlapping disorders, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
 ```{r ocir model1b sum_score prepan}
@@
 ### Model 1a: Disorder hierarchical, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
 ```{r ocir model1a diff_score retro}
@@
 ### Model 1b: Overlapping disorders, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
 ```{r ocir model1b diff_score retro}
@@
 ### Model 1a: Disorder hierarchical, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
 ```{r ocir model1a sum_score retro}
@@
 ### Model 1b: Overlapping disorders, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
 ```{r ocir model1b sum_score retro}
@@
 ### Model 1a: Disorder hierarchical, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
 ```{r ocir model1a diff_score retro (sensitivity analyses)}
@@
 ### Model 1b: Overlapping disorders, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
 ```{r ocir model1b diff_score retro (sensitivity analyses)}
@@
 ### Model 1a: Disorder hierarchical, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
 ```{r ocir model1a sum_score retro (sensitivity analyses)}
@@
 ### Model 1b: Overlapping disorders, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
 ```{r ocir model1b sum_score retro (sensitivity analyses)}
@@
 ### Model 1a: Disorder hierarchical, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
 ```{r pcl model1a absolute whole sample}
@@
 ### Model 1b: Overlapping disorders, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
 ```{r pcl model1b absolute whole sample}
@@
 ### Model 1a: Disorder hierarchical, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
 ```{r pcl model1a diff_score prepan}
@@
 ### Model 1b: Overlapping disorders, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
 ```{r pcl model1b diff_score prepan}
@@
 ### Model 1a: Disorder hierarchical, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
 ```{r pcl model1a sum_score prepan}
@@
 ### Model 1b: Overlapping disorders, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
 ```{r pcl model1b sum_score prepan}

### 2020-11-03 PANCHANGE_analysis.Rmd
Added subset of people who signed up 3 months prior to pandemic

@@
 dim(dat.prepan)
+```
+
+Sensitivity analysis for individuals who signed up to GLAD (prepan) either 3, 6 or 9 months before the pendemic began. 
+```{r subsample for pre-pan sensitivity analysis}
+# Participants who signed up in the three months before the pandemic began
+dat.prepan_sensitivity_3months <- dat %>%
+  filter(
+    ((data_group_gad == "Baseline and retrospective data" |
+      data_group_gad == "Prepandemic and baseline data" |
+      data_group_gad == "All prepandemic, baseline and retrospective data") |
+      (data_group_phq == "Baseline and retrospective data" |
+      data_group_phq == "Prepandemic and baseline data" |
+      data_group_phq == "All prepandemic, baseline and retrospective data") |
+      (data_group_pcl == "Baseline and retrospective data" |
+      data_group_pcl == "Prepandemic and baseline data" |
+      data_group_pcl == "All prepandemic, baseline and retrospective data") |
+      (data_group_ocir == "Baseline and retrospective data" |
+      data_group_ocir == "Prepandemic and baseline data" |
+      data_group_ocir == "All prepandemic, baseline and retrospective data")) &
+      prepandemic_march_1_numeric == 1  & # Exclude participants that signed up after the 1. March 
+      (startDate.prepandemic < date_3months_prior_march_1st), # The GLAD sign up is dated after the cut off
+  )
 ```

### 2020-11-03 PANCHANGE_variable_creation.Rmd
created date variables for 3, 6, 9 months prior to pandemic

@@
 
+```{r reorder age_category_collapsed for largest age group as reference category}
+dat <- dat %>%
+  mutate(age_category_collapsed_reordered = 
+           relevel(age_category_collapsed,
+                   ref = "26-35", #largest group
+                   first = TRUE, #listed first in a list
+                   collapse = "+", #string used for combined factor levels
+                   xlevels= TRUE #all other levels maintained
+                   )
+  )
+```
+
 ## Gender
@@
 ```
+
+Creating variables for subset of participants dependent on when they signed up to GLAD (prepan)
+```{r date variables for subset of participants who signed up in 3, 6, 9 months prior to pandemic}
+# Date of 3 months prior to the 1st of March
+date_3months_prior_march_1st <- as.POSIXct("2019-12-01")
+
+# Date of 6 months prior to the 1st of March
+date_6months_prior_march_1st <- as.POSIXct("2019-09-01")
+
+# Date of 9 months prior to the 1st of March
+date_9months_prior_march_1st <- as.POSIXct("2019-06-01")
+```

### 2020-11-03 PANCHANGE_variable_creation.Rmd
Added binary variable for if the participant signed up 3/6/9 month prior to pandemic

@@
 
-Creating variables for subset of participants dependent on when they signed up to GLAD (prepan)
+Creating date variables for subset of participants dependent on when they signed up to GLAD (prepan)
 ```{r date variables for subset of participants who signed up in 3, 6, 9 months prior to pandemic}
@@
 ```
+
+```{r subset of participants who signed up in 3 months prior to pandemic}
+dat <- dat %>%
+  mutate(
+    prepandemic_3_months_numeric =
+      if_else(
+        startDate.prepandemic > date_3months_prior_march_1st & # The GLAD sign up is dated before the cut off (> longer ago)
+        prepandemic_march_1_numeric == 1, #signed up before March 1st 
+        true = 0, # Participant signed up after December 1st 
+        false = 1, # Participant signed up before December 1st
+        missing = NA_real_
+      )
+  )
+
+dat <- dat %>%
+  mutate(
+    prepandemic_3_months =
+      recode_factor(
+        prepandemic_3_months_numeric,
+        "0" = "Sign up after 01 December",
+        "1" = "Sign up before 01 December"
+      )
+  )
+
+dat %>%
+  freq(prepandemic_3_months)
+```
+
+```{r subset of participants who signed up in 6 months prior to pandemic}
+dat <- dat %>%
+  mutate(
+    prepandemic_6_months_numeric =
+      if_else(
+        startDate.prepandemic > date_6months_prior_march_1st & # The GLAD sign up is dated before the cut off (> longer ago)
+        prepandemic_march_1_numeric == 1,
+        true = 0, # Participant signed up after September 1st 
+        false = 1, # Participant signed up before September 1st
+        missing = NA_real_
+      )
+  )
+
+dat <- dat %>%
+  mutate(
+    prepandemic_6_months =
+      recode_factor(
+        prepandemic_6_months_numeric,
+        "0" = "Sign up after 01 September",
+        "1" = "Sign up before 01 September"
+      )
+  )
+
+dat %>%
+  freq(prepandemic_6_months)
+```
+
+```{r subset of participants who signed up in 9 months prior to pandemic}
+dat <- dat %>%
+  mutate(
+    prepandemic_9_months_numeric =
+      if_else(
+        startDate.prepandemic > date_9months_prior_march_1st & # The GLAD sign up is dated before the cut off (> longer ago)
+        prepandemic_march_1_numeric == 1,
+        true = 0, # Participant signed up after June 1st 
+        false = 1, # Participant signed up before June 1st
+        missing = NA_real_
+      )
+  )
+
+dat <- dat %>%
+  mutate(
+    prepandemic_9_months =
+      recode_factor(
+        prepandemic_9_months_numeric,
+        "0" = "Sign up after 01 June",
+        "1" = "Sign up before 01 June"
+      )
+  )
+
+dat %>%
+  freq(prepandemic_9_months)
+```

### 2020-11-03 PANCHANGE_variable_creation.Rmd
minor edits to date variables

--- 2020-11-03 PANCHANGE_variable_creation.Rmd
@@
 ```
+
+```{r subset of participants who signed up in 3 months prior to pandemic}
+dat <- dat %>%
+  mutate(
+    prepandemic_3_months_numeric =
+      if_else(
+        startDate.prepandemic > date_3months_prior_march_1st & # The GLAD sign up is dated before the cut off (> longer ago)
+        prepandemic_march_1_numeric == 1, #participant did not sign up after pandemic began (March 1st)
+        true = 0, # Participant signed up after December 1st 
+        false = 1, # Participant signed up before December 1st
+        missing = NA_real_
+      )
+  )
+
+dat <- dat %>%
+  mutate(
+    prepandemic_3_months =
+      recode_factor(
+        prepandemic_3_months_numeric,
+        "0" = "Sign up after 01 December",
+        "1" = "Sign up before 01 December"
+      )
+  )
+
+dat %>%
+  freq(prepandemic_3_months)
+```
+
+```{r subset of participants who signed up in 6 months prior to pandemic}
+dat <- dat %>%
+  mutate(
+    prepandemic_6_months_numeric =
+      if_else(
+        startDate.prepandemic > date_6months_prior_march_1st & # The GLAD sign up is dated before the cut off (> longer ago)
+        prepandemic_march_1_numeric == 1, #participant did not sign up after pandemic began (March 1st)
+        true = 0, # Participant signed up after September 1st 
+        false = 1, # Participant signed up before September 1st
+        missing = NA_real_
+      )
+  )
+
+dat <- dat %>%
+  mutate(
+    prepandemic_6_months =
+      recode_factor(
+        prepandemic_6_months_numeric,
+        "0" = "Sign up after 01 September",
+        "1" = "Sign up before 01 September"
+      )
+  )
+
+dat %>%
+  freq(prepandemic_6_months)
+```
+
+```{r subset of participants who signed up in 9 months prior to pandemic}
+dat <- dat %>%
+  mutate(
+    prepandemic_9_months_numeric =
+      if_else(
+        startDate.prepandemic > date_9months_prior_march_1st & # The GLAD sign up is dated before the cut off (> longer ago)
+        prepandemic_march_1_numeric == 1, #participant did not sign up after pandemic began (March 1st)
+        true = 0, # Participant signed up after June 1st 
+        false = 1, # Participant signed up before June 1st
+        missing = NA_real_
+      )
+  )
+
+dat <- dat %>%
+  mutate(
+    prepandemic_9_months =
+      recode_factor(
+        prepandemic_9_months_numeric,
+        "0" = "Sign up after 01 June",
+        "1" = "Sign up before 01 June"
+      )
+  )
+
+dat %>%
+  freq(prepandemic_9_months)
+```

### 2020-11-03 PANCHANGE_analysis.Rmd
finalised grroup subsets for prepan sensitivity analysis

--- 2020-11-03 PANCHANGE_analysis.Rmd
@@
 dim(dat.prepan)
+```
+
+Sensitivity analysis for individuals who signed up to GLAD (prepan) either 3, 6 or 9 months before the pendemic began. 
+```{r subsample for pre-pan sensitivity analysis}
+# Participants who signed up in the three months before the pandemic began
+dat.prepan_sensitivity_3months <- dat %>%
+  filter(
+    ((data_group_gad == "Baseline and retrospective data" |
+      data_group_gad == "Prepandemic and baseline data" |
+      data_group_gad == "All prepandemic, baseline and retrospective data") |
+      (data_group_phq == "Baseline and retrospective data" |
+      data_group_phq == "Prepandemic and baseline data" |
+      data_group_phq == "All prepandemic, baseline and retrospective data") |
+      (data_group_pcl == "Baseline and retrospective data" |
+      data_group_pcl == "Prepandemic and baseline data" |
+      data_group_pcl == "All prepandemic, baseline and retrospective data") |
+      (data_group_ocir == "Baseline and retrospective data" |
+      data_group_ocir == "Prepandemic and baseline data" |
+      data_group_ocir == "All prepandemic, baseline and retrospective data")) &
+      prepandemic_3_months_numeric == 1 # Only participants who signed up between December 1st 2019 and March 1st 2020
+  )
+
+# Participants who signed up in the three months before the pandemic began
+dat.prepan_sensitivity_6months <- dat %>%
+  filter(
+    ((data_group_gad == "Baseline and retrospective data" |
+      data_group_gad == "Prepandemic and baseline data" |
+      data_group_gad == "All prepandemic, baseline and retrospective data") |
+      (data_group_phq == "Baseline and retrospective data" |
+      data_group_phq == "Prepandemic and baseline data" |
+      data_group_phq == "All prepandemic, baseline and retrospective data") |
+      (data_group_pcl == "Baseline and retrospective data" |
+      data_group_pcl == "Prepandemic and baseline data" |
+      data_group_pcl == "All prepandemic, baseline and retrospective data") |
+      (data_group_ocir == "Baseline and retrospective data" |
+      data_group_ocir == "Prepandemic and baseline data" |
+      data_group_ocir == "All prepandemic, baseline and retrospective data")) &
+      prepandemic_6_months_numeric == 1 # Only participants who signed up between September 1st 2019 and March 1st 2020
+  )
+
+# Participants who signed up in the three months before the pandemic began
+dat.prepan_sensitivity_9months <- dat %>%
+  filter(
+    ((data_group_gad == "Baseline and retrospective data" |
+      data_group_gad == "Prepandemic and baseline data" |
+      data_group_gad == "All prepandemic, baseline and retrospective data") |
+      (data_group_phq == "Baseline and retrospective data" |
+      data_group_phq == "Prepandemic and baseline data" |
+      data_group_phq == "All prepandemic, baseline and retrospective data") |
+      (data_group_pcl == "Baseline and retrospective data" |
+      data_group_pcl == "Prepandemic and baseline data" |
+      data_group_pcl == "All prepandemic, baseline and retrospective data") |
+      (data_group_ocir == "Baseline and retrospective data" |
+      data_group_ocir == "Prepandemic and baseline data" |
+      data_group_ocir == "All prepandemic, baseline and retrospective data")) &
+      prepandemic_9_months_numeric == 1 # Only participants who signed up between June 1st 2019 and March 1st 2020
+  )
+
 ```
@@
 ```
+# GAD prepan: sensitivity
 

### 2020-11-03 PANCHANGE_analysis.Rmd
Added sensitivty model 1b Absolute scores GAD for 3, 6, 9 months

@@
 # GAD prepan: sensitivity
+## Regression: Absolute scores
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
+#### Subset of participants 3 months prior to pandemic
+```{r gad model1b sum_score prepan}
+# Regression coefficients
+gad_prepan_model1b_explan_estimates <- model1b.explan.estimates(outcome = "gad.sum_score_base",
+                         explan_var = "gad.sum_score_prepan",
+                         data_set = "dat.prepan_sensitivity_3months")
+kable(gad_prepan_model1b_explan_estimates)
+gad_prepan_model1b_explan_estimates
+
+# Regression diagnostic statistics
+gad_prepan_model1b_explan_reg_stats <- model1b.explan.reg.stats(outcome = "gad.sum_score_base",
+                         explan_var = "gad.sum_score_prepan",
+                         data_set = "dat.prepan_sensitivity_3months")
+kable(gad_prepan_model1b_explan_reg_stats)
+gad_prepan_model1b_explan_reg_stats
+```
+
+#### Subset of participants 6 months prior to pandemic
+```{r gad model1b sum_score prepan}
+# Regression coefficients
+gad_prepan_model1b_explan_estimates <- model1b.explan.estimates(outcome = "gad.sum_score_base",
+                         explan_var = "gad.sum_score_prepan",
+                         data_set = "dat.prepan_sensitivity_6months")
+kable(gad_prepan_model1b_explan_estimates)
+gad_prepan_model1b_explan_estimates
+
+# Regression diagnostic statistics
+gad_prepan_model1b_explan_reg_stats <- model1b.explan.reg.stats(outcome = "gad.sum_score_base",
+                         explan_var = "gad.sum_score_prepan",
+                         data_set = "dat.prepan_sensitivity_6months")
+kable(gad_prepan_model1b_explan_reg_stats)
+gad_prepan_model1b_explan_reg_stats
+```
+
+#### Subset of participants 9 months prior to pandemic
+```{r gad model1b sum_score prepan}
+# Regression coefficients
+gad_prepan_model1b_explan_estimates <- model1b.explan.estimates(outcome = "gad.sum_score_base",
+                         explan_var = "gad.sum_score_prepan",
+                         data_set = "dat.prepan_sensitivity_9months")
+kable(gad_prepan_model1b_explan_estimates)
+gad_prepan_model1b_explan_estimates
+
+# Regression diagnostic statistics
+gad_prepan_model1b_explan_reg_stats <- model1b.explan.reg.stats(outcome = "gad.sum_score_base",
+                         explan_var = "gad.sum_score_prepan",
+                         data_set = "dat.prepan_sensitivity_9months")
+kable(gad_prepan_model1b_explan_reg_stats)
+gad_prepan_model1b_explan_reg_stats
+```
+##KT
 

### 2020-11-03 PANCHANGE_analysis.Rmd
Added sensitivty model 1b Absolute scores PHQ for 3, 6, 9 months

--- 2020-11-03 PANCHANGE_analysis.Rmd
@@
 # GAD prepan: sensitivity
+## Regression: Absolute scores
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
+#### Subset of participants 3 months prior to pandemic
+```{r gad model1b sum_score prepan - sensitivity 3 months}
+# Regression coefficients
+gad_prepan_model1b_explan_estimates <- model1b.explan.estimates(outcome = "gad.sum_score_base",
+                         explan_var = "gad.sum_score_prepan",
+                         data_set = "dat.prepan_sensitivity_3months")
+kable(gad_prepan_model1b_explan_estimates)
+gad_prepan_model1b_explan_estimates
+
+# Regression diagnostic statistics
+gad_prepan_model1b_explan_reg_stats <- model1b.explan.reg.stats(outcome = "gad.sum_score_base",
+                         explan_var = "gad.sum_score_prepan",
+                         data_set = "dat.prepan_sensitivity_3months")
+kable(gad_prepan_model1b_explan_reg_stats)
+gad_prepan_model1b_explan_reg_stats
+```
+
+#### Subset of participants 6 months prior to pandemic
+```{r gad model1b sum_score prepan - sensitivity 6 months}
+# Regression coefficients
+gad_prepan_model1b_explan_estimates <- model1b.explan.estimates(outcome = "gad.sum_score_base",
+                         explan_var = "gad.sum_score_prepan",
+                         data_set = "dat.prepan_sensitivity_6months")
+kable(gad_prepan_model1b_explan_estimates)
+gad_prepan_model1b_explan_estimates
+
+# Regression diagnostic statistics
+gad_prepan_model1b_explan_reg_stats <- model1b.explan.reg.stats(outcome = "gad.sum_score_base",
+                         explan_var = "gad.sum_score_prepan",
+                         data_set = "dat.prepan_sensitivity_6months")
+kable(gad_prepan_model1b_explan_reg_stats)
+gad_prepan_model1b_explan_reg_stats
+```
+
+#### Subset of participants 9 months prior to pandemic
+```{r gad model1b sum_score prepan - sensitivity 9 months}
+# Regression coefficients
+gad_prepan_model1b_explan_estimates <- model1b.explan.estimates(outcome = "gad.sum_score_base",
+                         explan_var = "gad.sum_score_prepan",
+                         data_set = "dat.prepan_sensitivity_9months")
+kable(gad_prepan_model1b_explan_estimates)
+gad_prepan_model1b_explan_estimates
+
+# Regression diagnostic statistics
+gad_prepan_model1b_explan_reg_stats <- model1b.explan.reg.stats(outcome = "gad.sum_score_base",
+                         explan_var = "gad.sum_score_prepan",
+                         data_set = "dat.prepan_sensitivity_9months")
+kable(gad_prepan_model1b_explan_reg_stats)
+gad_prepan_model1b_explan_reg_stats
+```
+##KT
 
@@
 ```
+# PHQ prepan: sensitivity
+## Regression: Absolute scores
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
+#### Subset of participants 3 months prior to pandemic
+```{r phq model1b sum_score prepan - sensitivity 3 months}
+# Regression coefficients
+phq_prepan_model1b_explan_estimates <- model1b.explan.estimates(outcome = "phq.sum_score_base",
+                         explan_var = "phq.sum_score_prepan",
+                         data_set = "dat.prepan_sensitivity_3months")
+kable(phq_prepan_model1b_explan_estimates)
+phq_prepan_model1b_explan_estimates
+
+# Regression diagnostic statistics
+phq_prepan_model1b_explan_reg_stats <- model1b.explan.reg.stats(outcome = "phq.sum_score_base",
+                         explan_var = "phq.sum_score_prepan",
+                         data_set = "dat.prepan_sensitivity_3months")
+kable(phq_prepan_model1b_explan_reg_stats)
+phq_prepan_model1b_explan_reg_stats
+```
+
+#### Subset of participants 6 months prior to pandemic
+```{r phq model1b sum_score prepan - sensitivity 6 months}
+# Regression coefficients
+phq_prepan_model1b_explan_estimates <- model1b.explan.estimates(outcome = "phq.sum_score_base",
+                         explan_var = "phq.sum_score_prepan",
+                         data_set = "dat.prepan_sensitivity_6months")
+kable(phq_prepan_model1b_explan_estimates)
+phq_prepan_model1b_explan_estimates
+
+# Regression diagnostic statistics
+phq_prepan_model1b_explan_reg_stats <- model1b.explan.reg.stats(outcome = "phq.sum_score_base",
+                         explan_var = "phq.sum_score_prepan",
+                         data_set = "dat.prepan_sensitivity_6months")
+kable(phq_prepan_model1b_explan_reg_stats)
+phq_prepan_model1b_explan_reg_stats
+```
+
+#### Subset of participants 9 months prior to pandemic
+```{r phq model1b sum_score prepan - sensitivity 9 months}
+# Regression coefficients
+phq_prepan_model1b_explan_estimates <- model1b.explan.estimates(outcome = "phq.sum_score_base",
+                         explan_var = "phq.sum_score_prepan",
+                         data_set = "dat.prepan_sensitivity_9months")
+kable(phq_prepan_model1b_explan_estimates)
+phq_prepan_model1b_explan_estimates
+
+# Regression diagnostic statistics
+phq_prepan_model1b_explan_reg_stats <- model1b.explan.reg.stats(outcome = "phq.sum_score_base",
+                         explan_var = "phq.sum_score_prepan",
+                         data_set = "dat.prepan_sensitivity_9months")
+kable(phq_prepan_model1b_explan_reg_stats)
+phq_prepan_model1b_explan_reg_stats
+```
 

### 2020-11-03 PANCHANGE_analysis.Rmd
Added sensitivty model 1b Absolute scores PCL for 3, 6, 9 months

@@
 ```
+
+# PCL prepan: sensitivity
+## Regression: Absolute scores
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
+#### Subset of participants 3 months prior to pandemic
+```{r pcl model1b sum_score prepan - sensitivity 3 months}
+# Regression coefficients
+pcl_prepan_model1b_explan_estimates <- model1b.explan.estimates(outcome = "pcl.sum_score_base",
+                         explan_var = "pcl.sum_score_prepan",
+                         data_set = "dat.prepan_sensitivity_3months")
+kable(pcl_prepan_model1b_explan_estimates)
+pcl_prepan_model1b_explan_estimates
+
+# Regression diagnostic statistics
+pcl_prepan_model1b_explan_reg_stats <- model1b.explan.reg.stats(outcome = "pcl.sum_score_base",
+                         explan_var = "pcl.sum_score_prepan",
+                         data_set = "dat.prepan_sensitivity_3months")
+kable(pcl_prepan_model1b_explan_reg_stats)
+pcl_prepan_model1b_explan_reg_stats
+```
+
+#### Subset of participants 6 months prior to pandemic
+```{r pcl model1b sum_score prepan - sensitivity 6 months}
+# Regression coefficients
+pcl_prepan_model1b_explan_estimates <- model1b.explan.estimates(outcome = "pcl.sum_score_base",
+                         explan_var = "pcl.sum_score_prepan",
+                         data_set = "dat.prepan_sensitivity_6months")
+kable(pcl_prepan_model1b_explan_estimates)
+pcl_prepan_model1b_explan_estimates
+
+# Regression diagnostic statistics
+pcl_prepan_model1b_explan_reg_stats <- model1b.explan.reg.stats(outcome = "pcl.sum_score_base",
+                         explan_var = "pcl.sum_score_prepan",
+                         data_set = "dat.prepan_sensitivity_6months")
+kable(pcl_prepan_model1b_explan_reg_stats)
+pcl_prepan_model1b_explan_reg_stats
+```
+
+#### Subset of participants 9 months prior to pandemic
+```{r pcl model1b sum_score prepan - sensitivity 9 months}
+# Regression coefficients
+pcl_prepan_model1b_explan_estimates <- model1b.explan.estimates(outcome = "pcl.sum_score_base",
+                         explan_var = "pcl.sum_score_prepan",
+                         data_set = "dat.prepan_sensitivity_9months")
+kable(pcl_prepan_model1b_explan_estimates)
+pcl_prepan_model1b_explan_estimates
+
+# Regression diagnostic statistics
+pcl_prepan_model1b_explan_reg_stats <- model1b.explan.reg.stats(outcome = "pcl.sum_score_base",
+                         explan_var = "pcl.sum_score_prepan",
+                         data_set = "dat.prepan_sensitivity_9months")
+kable(pcl_prepan_model1b_explan_reg_stats)
+pcl_prepan_model1b_explan_reg_stats
+```

### 2020-11-05 PANCHANGE_analysis.Rmd
added age^2 to model
only did for GAD baseline incase this was not how it should be approached.

--- 2020-11-03 PANCHANGE_analysis.Rmd
@@
 
-dim(dat.prepan)
-```
-
-Sensitivity analysis for individuals who signed up to GLAD (prepan) either 3, 6 or 9 months before the pendemic began. 
-```{r subsample for pre-pan sensitivity analysis}
-# Participants who signed up in the three months before the pandemic began
-dat.prepan_sensitivity_3months <- dat %>%
-  filter(
-    ((data_group_gad == "Baseline and retrospective data" |
-      data_group_gad == "Prepandemic and baseline data" |
-      data_group_gad == "All prepandemic, baseline and retrospective data") |
-      (data_group_phq == "Baseline and retrospective data" |
-      data_group_phq == "Prepandemic and baseline data" |
-      data_group_phq == "All prepandemic, baseline and retrospective data") |
-      (data_group_pcl == "Baseline and retrospective data" |
-      data_group_pcl == "Prepandemic and baseline data" |
-      data_group_pcl == "All prepandemic, baseline and retrospective data") |
-      (data_group_ocir == "Baseline and retrospective data" |
-      data_group_ocir == "Prepandemic and baseline data" |
-      data_group_ocir == "All prepandemic, baseline and retrospective data")) &
-      prepandemic_3_months_numeric == 1 # Only participants who signed up between December 1st 2019 and March 1st 2020
-  )
-
-# Participants who signed up in the three months before the pandemic began
-dat.prepan_sensitivity_6months <- dat %>%
-  filter(
-    ((data_group_gad == "Baseline and retrospective data" |
-      data_group_gad == "Prepandemic and baseline data" |
-      data_group_gad == "All prepandemic, baseline and retrospective data") |
-      (data_group_phq == "Baseline and retrospective data" |
-      data_group_phq == "Prepandemic and baseline data" |
-      data_group_phq == "All prepandemic, baseline and retrospective data") |
-      (data_group_pcl == "Baseline and retrospective data" |
-      data_group_pcl == "Prepandemic and baseline data" |
-      data_group_pcl == "All prepandemic, baseline and retrospective data") |
-      (data_group_ocir == "Baseline and retrospective data" |
-      data_group_ocir == "Prepandemic and baseline data" |
-      data_group_ocir == "All prepandemic, baseline and retrospective data")) &
-      prepandemic_6_months_numeric == 1 # Only participants who signed up between September 1st 2019 and March 1st 2020
-  )
-
-# Participants who signed up in the three months before the pandemic began
-dat.prepan_sensitivity_9months <- dat %>%
-  filter(
-    ((data_group_gad == "Baseline and retrospective data" |
-      data_group_gad == "Prepandemic and baseline data" |
-      data_group_gad == "All prepandemic, baseline and retrospective data") |
-      (data_group_phq == "Baseline and retrospective data" |
-      data_group_phq == "Prepandemic and baseline data" |
-      data_group_phq == "All prepandemic, baseline and retrospective data") |
-      (data_group_pcl == "Baseline and retrospective data" |
-      data_group_pcl == "Prepandemic and baseline data" |
-      data_group_pcl == "All prepandemic, baseline and retrospective data") |
-      (data_group_ocir == "Baseline and retrospective data" |
-      data_group_ocir == "Prepandemic and baseline data" |
-      data_group_ocir == "All prepandemic, baseline and retrospective data")) &
-      prepandemic_9_months_numeric == 1 # Only participants who signed up between June 1st 2019 and March 1st 2020
-  )
-
+dim(dat.retro_sensitivity)
+```
+age^2 sensitivity 
+Exclude individuals with NA for continuous Age variable
+```{r}
+dat_age_sensitivity <- dat %>%
+  filter(!is.na(Age))
+dim(dat_age_sensitivity)
 ```
@@
 1 - adjusted
+2 - adjusted with age^2
 a - hierarchical disorders
@@
                             "Gender_collapsed",
-                            "age_category_collapsed_reordered",
+                            "age_category_collapsed",
                             "Ethnicity_collapsed",
@@
                "Gender_collapsedNon-binary/Self-defined" = "Non-binary/Self-defined",
-               "age_category_collapsed_reordered19-25" = "19-25 years",
-               "age_category_collapsed_reordered26-35" = "26-35 years",
-               "age_category_collapsed_reordered36-45" = "36-45 years",
-               "age_category_collapsed_reordered46-55" = "46-55 years",
-               "age_category_collapsed_reordered56-65" = "56-65 years",
-               "age_category_collapsed_reordered66-70" = "66-70 years",
-               "age_category_collapsed_reordered71-75" = "71-75 years",
-               "age_category_collapsed_reordered76+" = "76+ years",
+               "age_category_collapsed19-25" = "19-25 years",
+               "age_category_collapsed26-35" = "26-35 years",
+               "age_category_collapsed36-45" = "36-45 years",
+               "age_category_collapsed46-55" = "46-55 years",
+               "age_category_collapsed56-65" = "56-65 years",
+               "age_category_collapsed66-70" = "66-70 years",
+               "age_category_collapsed71-75" = "71-75 years",
+               "age_category_collapsed76+" = "76+ years",
                "Ethnicity_collapsedMixed or multiple ethnic origins" = "Mixed or multiple ethnic origins",
@@
                              "Gender_collapsed",
-                             "age_category_collapsed_reordered",
+                             "age_category_collapsed",
                              "Ethnicity_collapsed",
@@
   return(get(paste0(outcome,"model1b_reg_stats")))
+}
+```
+
+```{r model2a function}
+model2a.estimates <- function(outcome, data_set) {
+  # define the variable name of the dependent variable
+  dependent.variable <- outcome
+  # define the independent variables
+  independent.variables <- c("Disorder_hierarchical",
+                            "Gender_collapsed",
+                            "poly(Age, 2)",
+                            "Ethnicity_collapsed",
+                            "time_diff_coping_lockdown_march_23"
+                            )
+  # create the formula
+  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
+  glm.formula
+
+  # run the glm
+  assign(paste0(outcome,".model2a"),
+         lm( formula = glm.formula,
+             data = get(data_set)
+         )
+  )
+
+  assign(paste0(outcome,"model2a_estimates"),
+         tidy(get(paste0(outcome,".model2a")), conf.int = TRUE) %>%
+           mutate(
+             "Indepent variable" = recode_factor(
+               term,
+               "(Intercept)" = "Intercept",
+               "Disorder_hierarchicalAnxiety disorders" = "Anxiety disorders",
+               "Disorder_hierarchicalEating disorders" = "Eating disorders",
+               "Disorder_hierarchicalOCDs" = "OCDs",
+               "Disorder_hierarchicalPTSD" = "PTSD",
+               "Disorder_hierarchicalDepressive disorders" = "Depressive disorders",
+               "Disorder_hierarchicalBipolar disorders" = "Bipolar disorders",
+               "Gender_collapsedFemale" = "Female",
+               "Gender_collapsedNon-binary/Self-defined" = "Non-binary/Self-defined",
+               "poly(Age, 2)1" = "Age",
+               "poly(Age, 2)2" = "Age^2", 
+               "Ethnicity_collapsedMixed or multiple ethnic origins" = "Mixed or multiple ethnic origins",
+               "Ethnicity_collapsedAsian or Asian British" = "Asian or Asian British",
+               "Ethnicity_collapsedAfrican or African British" = "African or African British",
+               "Ethnicity_collapsedOther" = "Other ethnicity",
+               "time_diff_coping_lockdown_march_23" = "Time difference: Lockdown to baseline"
+             ),
+             "Estimate" = format(
+               round(estimate,
+                     digits = 2),
+               nsmall = 2),
+             "95% CI low" = format(
+               round(conf.low,
+                     digits = 2),
+               nsmall = 2),
+             "95% CI up" = format(
+               round(conf.high,
+                     digits = 2),
+               nsmall = 2),
+             "SE" = format(
+               round(std.error,
+                     digits = 2),
+               nsmall = 2),
+             "z score" = format(
+               round(statistic,
+                     digits = 2),
+               nsmall = 2),
+             "p value" = case_when(
+               p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
+               p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
+               p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
+             )
+           ) %>%
+           select(
+             "Indepent variable",
+             "Estimate",
+             "95% CI low",
+             "95% CI up",
+             "SE",
+             #    "z score",
+             "p value"
+           )
+  )
+
+  return(get(paste0(outcome,"model2a_estimates")))
+}
+
+model2a.reg.stats <- function(outcome, data_set) {
+  # define the variable name of the dependent variable
+  dependent.variable <- outcome
+  # define the independent variables
+  independent.variables <- c("Disorder_hierarchical")
+  # create the formula
+  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
+  glm.formula
+
+  # run the glm
+  assign(paste0(outcome,".model2a"),
+         lm( formula = glm.formula,
+             data = get(data_set)
+         )
+  )
+
+  assign(paste0(outcome,"model2a_reg_stats"),
+         glance(get(paste0(outcome,".model2a"))) %>%
+           mutate(
+             "n" = format(
+               round(nobs,
+                     digits = 0),
+               nsmall = 0),
+             "R2" = format(
+               round(r.squared,
+                     digits = 2),
+               nsmall = 2),
+             "adjust. R2" = format(
+               round(adj.r.squared,
+                     digits = 2),
+               nsmall = 2),
+             "F" = format(
+               round(statistic,
+                     digits = 2),
+               nsmall = 2),
+             "p value" = case_when(
+               p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
+               p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
+               p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
+             )
+           ) %>%
+           select(
+             "n",
+             "R2",
+             "adjust. R2",
+             "F",
+             "p value",
+             "df"
+           )
+  )
+
+  return(get(paste0(outcome,"model2a_reg_stats")))
+}
+```
+
+```{r model2b function}
+model2b.estimates <- function(outcome, data_set) {
+  # define the variable name of the dependent variable
+  dependent.variable <- outcome
+  # define the independent variables
+  independent.variables <- c("depression_and_anxiety",
+                             "eating_disorders",
+                             "obsessive_compulsive_disorders",
+                             "bipolar_and_schizophrenia",
+                             "mhd.posttraumatic_stress_disorder_ptsd",
+                             "autism_spectrum_disorder",
+                             "mhd.attention_deficit_hyperactivity_disorder",
+                             "mhd.personality_disorder",
+                             "Gender_collapsed",
+                             "poly(Age, 2)",
+                             "Ethnicity_collapsed",
+                             "key_worker",
+                             "time_diff_coping_lockdown_march_23"
+                                )
+  # create the formula
+  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
+  glm.formula
+
+  # run the glm
+  assign(paste0(outcome,".model2b"),
+         lm( formula = glm.formula,
+             data = get(data_set)
+         )
+  )
+
+  assign(paste0(outcome,"model2b_estimates"),
+         tidy(get(paste0(outcome,".model2b")), conf.int = TRUE) %>%
+           mutate(
+             "Indepent variable" = recode_factor(
+               term,
+               "(Intercept)" = "Intercept",
+               "anxiety_disordersAnxiety disorder" = "Anxiety disorders",
+               "depressive_disordersDepressive disorder" = "Depressive disorders",
+               "depression_and_anxietyDepressive and anxiety disorder" = "Depressive and anxiety disorder",
+               "depression_and_anxietyOnly depressive disorder" = "Only depressive disorder",
+               "depression_and_anxietyOnly anxiety disorder" = "Only anxiety disorder",
+               "eating_disordersEating disorder" = "Eating disorders",
+               "obsessive_compulsive_disordersObsessive compulsive disorder" = "OCDs",
+               "bipolar_and_schizophreniaPsychotic and bipolar disorder" = "Psychotic and bipolar disorder",
+               "bipolar_and_schizophreniaOnly psychotic disorder" = "Only psychotic disorder",
+               "bipolar_and_schizophreniaOnly bipolar disorder" = "Only bipolar disorder",
+               "psychotic_disordersPsychotic disorder" = "Psychotic disorder",
+               "mhd.mania_hypomania_bipolar_or_manicdepressionMania, hypomania, bipolar or manic-depression" = "Bipolar disorder",
+               "mhd.posttraumatic_stress_disorder_ptsdPost-traumatic stress disorder (PTSD)" = "PTSD",
+               "autism_spectrum_disorderAutism spectrum disorder" = "ASD",
+               "mhd.attention_deficit_hyperactivity_disorderAttention deficit or attention deficit and hyperactivity disorder (ADD/ADHD)" = "ADHD",
+               "mhd.personality_disorderPersonality disorder" = "Personality disorder",
+               "Gender_collapsedFemale" = "Female",
+               "Gender_collapsedNon-binary/Self-defined" = "Non-binary/Self-defined",
+               "poly(Age, 2)1" = "Age",
+               "poly(Age, 2)2" = "Age^2", 
+               "Ethnicity_collapsedMixed or multiple ethnic origins" = "Mixed or multiple ethnic origins",
+               "Ethnicity_collapsedAsian or Asian British" = "Asian or Asian British",
+               "Ethnicity_collapsedAfrican or African British" = "African or African British",
+               "Ethnicity_collapsedOther" = "Other ethnicity",
+               "key_workerKey worker" = "Key worker",
+               "time_diff_coping_lockdown_march_23" = "Time difference: Lockdown to baseline"
+             ),
+             "Estimate" = format(
+               round(estimate,
+                     digits = 2),
+               nsmall = 2),
+             "95% CI low" = format(
+               round(conf.low,
+                     digits = 2),
+               nsmall = 2),
+             "95% CI up" = format(
+               round(conf.high,
+                     digits = 2),
+               nsmall = 2),
+             "SE" = format(
+               round(std.error,
+                     digits = 2),
+               nsmall = 2),
+             "z score" = format(
+               round(statistic,
+                     digits = 2),
+               nsmall = 2),
+             "p value" = case_when(
+               p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
+               p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
+               p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
+             )
+           ) %>%
+           select(
+             "Indepent variable",
+             "Estimate",
+             "95% CI low",
+             "95% CI up",
+             "SE",
+             #    "z score",
+             "p value"
+           )
+  )
+
+  return(get(paste0(outcome,"model2b_estimates")))
+}
+
+model2b.reg.stats <- function(outcome, data_set) {
+  # define the variable name of the dependent variable
+  dependent.variable <- outcome
+  # define the independent variables
+  independent.variables <- c("Disorder_hierarchical")
+  # create the formula
+  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
+  glm.formula
+
+  # run the glm
+  assign(paste0(outcome,".model2b"),
+         lm( formula = glm.formula,
+             data = get(data_set)
+         )
+  )
+
+  assign(paste0(outcome,"model2b_reg_stats"),
+         glance(get(paste0(outcome,".model2b"))) %>%
+           mutate(
+             "n" = format(
+               round(nobs,
+                     digits = 0),
+               nsmall = 0),
+             "R2" = format(
+               round(r.squared,
+                     digits = 2),
+               nsmall = 2),
+             "adjust. R2" = format(
+               round(adj.r.squared,
+                     digits = 2),
+               nsmall = 2),
+             "F" = format(
+               round(statistic,
+                     digits = 2),
+               nsmall = 2),
+             "p value" = case_when(
+               p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
+               p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
+               p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
+             )
+           ) %>%
+           select(
+             "n",
+             "R2",
+             "adjust. R2",
+             "F",
+             "p value",
+             "df"
+           )
+  )
+
+  return(get(paste0(outcome,"model2b_reg_stats")))
 }
@@
 ### Model 1a: Disorder hierarchical, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
 ```{r gad model1a absolute whole sample}
@@
 ### Model 1b: Overlapping disorders, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
 ```{r gad model1b absolute whole sample}
@@
 
+### Model 2a: Disorder hierarchical, Adjusted with Age^2 
+```{r}
+# Regression coefficients
+gad_baseline_model2a_estimates <- model2a.estimates(outcome = "gad.sum_score_base",
+                                                 data_set = "dat_age_sensitivity")
+kable(gad_baseline_model2a_estimates)
+gad_baseline_model2a_estimates
+
+# Regression diagnostic statistics
+gad_baseline_model2a_reg_stats <- model2a.reg.stats(outcome = "gad.sum_score_base",
+                                                 data_set = "dat_age_sensitivity")
+kable(gad_baseline_model2a_reg_stats)
+gad_baseline_model2a_reg_stats
+```
+### Model 2b: Disorder hierarchical, Adjusted with Age^2 
+```{r}
+# Regression coefficients
+gad_baseline_model2b_estimates <- model2b.estimates(outcome = "gad.sum_score_base",
+                                                 data_set = "dat_age_sensitivity")
+kable(gad_baseline_model2b_estimates)
+gad_baseline_model2b_estimates
+
+# Regression diagnostic statistics
+gad_baseline_model2b_reg_stats <- model2b.reg.stats(outcome = "gad.sum_score_base",
+                                                 data_set = "dat_age_sensitivity")
+kable(gad_baseline_model2b_reg_stats)
+gad_baseline_model2b_reg_stats
+```
+
 # GAD prepan
@@
 ### Model 1a: Disorder hierarchical, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
 ```{r gad model1a diff_score prepan}
@@
 ### Model 1b: Overlapping disorders, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
 ```{r gad model1b diff_score prepan}
@@
 ### Model 1a: Disorder hierarchical, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
 ```{r gad model1a sum_score prepan}
@@
 ### Model 1b: Overlapping disorders, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
 ```{r gad model1b sum_score prepan}
@@
 ```
-# GAD prepan: sensitivity
-## Regression: Absolute scores
-### Model 1b: Overlapping disorders, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
-#### Subset of participants 3 months prior to pandemic
-```{r gad model1b sum_score prepan}
-# Regression coefficients
-gad_prepan_model1b_explan_estimates <- model1b.explan.estimates(outcome = "gad.sum_score_base",
-                         explan_var = "gad.sum_score_prepan",
-                         data_set = "dat.prepan_sensitivity_3months")
-kable(gad_prepan_model1b_explan_estimates)
-gad_prepan_model1b_explan_estimates
-
-# Regression diagnostic statistics
-gad_prepan_model1b_explan_reg_stats <- model1b.explan.reg.stats(outcome = "gad.sum_score_base",
-                         explan_var = "gad.sum_score_prepan",
-                         data_set = "dat.prepan_sensitivity_3months")
-kable(gad_prepan_model1b_explan_reg_stats)
-gad_prepan_model1b_explan_reg_stats
-```
-
-#### Subset of participants 6 months prior to pandemic
-```{r gad model1b sum_score prepan}
-# Regression coefficients
-gad_prepan_model1b_explan_estimates <- model1b.explan.estimates(outcome = "gad.sum_score_base",
-                         explan_var = "gad.sum_score_prepan",
-                         data_set = "dat.prepan_sensitivity_6months")
-kable(gad_prepan_model1b_explan_estimates)
-gad_prepan_model1b_explan_estimates
-
-# Regression diagnostic statistics
-gad_prepan_model1b_explan_reg_stats <- model1b.explan.reg.stats(outcome = "gad.sum_score_base",
-                         explan_var = "gad.sum_score_prepan",
-                         data_set = "dat.prepan_sensitivity_6months")
-kable(gad_prepan_model1b_explan_reg_stats)
-gad_prepan_model1b_explan_reg_stats
-```
-
-#### Subset of participants 9 months prior to pandemic
-```{r gad model1b sum_score prepan}
-# Regression coefficients
-gad_prepan_model1b_explan_estimates <- model1b.explan.estimates(outcome = "gad.sum_score_base",
-                         explan_var = "gad.sum_score_prepan",
-                         data_set = "dat.prepan_sensitivity_9months")
-kable(gad_prepan_model1b_explan_estimates)
-gad_prepan_model1b_explan_estimates
-
-# Regression diagnostic statistics
-gad_prepan_model1b_explan_reg_stats <- model1b.explan.reg.stats(outcome = "gad.sum_score_base",
-                         explan_var = "gad.sum_score_prepan",
-                         data_set = "dat.prepan_sensitivity_9months")
-kable(gad_prepan_model1b_explan_reg_stats)
-gad_prepan_model1b_explan_reg_stats
-```
-##KT
 
@@
 ### Model 1a: Disorder hierarchical, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
 ```{r gad model1a diff_score retro}
@@
 ### Model 1b: Overlapping disorders, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
 ```{r gad model1b diff_score retro}
@@
 ### Model 1a: Disorder hierarchical, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
 ```{r gad model1a sum_score retro}
@@
 ### Model 1b: Overlapping disorders, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
 ```{r gad model1b sum_score retro}
@@
 ### Model 1a: Disorder hierarchical, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
 ```{r gad model1a diff_score retro (sensitivity analysis)}
@@
 ### Model 1b: Overlapping disorders, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
 ```{r gad model1b diff_score retro (sensitivity analysis)}
@@
 ### Model 1a: Disorder hierarchical, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
 ```{r gad model1a sum_score retro (sensitivity analysis)}
@@
 ### Model 1b: Overlapping disorders, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
 ```{r gad model1b sum_score retro (sensitivity analysis)}
@@
 ### Model 1a: Disorder hierarchical, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
 ```{r phq model1a absolute whole sample}
@@
 ### Model 1b: Overlapping disorders, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
 ```{r phq model1b absolute whole sample}
@@
 ### Model 1a: Disorder hierarchical, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
 ```{r phq model1a diff_score prepan}
@@
 ### Model 1b: Overlapping disorders, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
 ```{r phq model1b diff_score prepan}
@@
 ### Model 1a: Disorder hierarchical, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
 ```{r phq model1a sum_score prepan}
@@
 ### Model 1b: Overlapping disorders, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
 ```{r phq model1b sum_score prepan}
@@
 ### Model 1a: Disorder hierarchical, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
 ```{r phq model1a diff_score retro}
@@
 ### Model 1b: Overlapping disorders, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
 ```{r phq model1b diff_score retro}
@@
 ### Model 1a: Disorder hierarchical, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
 ```{r phq model1a sum_score retro}
@@
 ### Model 1b: Overlapping disorders, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
 ```{r phq model1b sum_score retro}
@@
 ### Model 1a: Disorder hierarchical, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
 ```{r phq model1a diff_score retro (sensitivity analysis)}
@@
 ### Model 1b: Overlapping disorders, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
 ```{r phq model1b diff_score retro (sensitivity analysis)}
@@
 ### Model 1a: Disorder hierarchical, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
 ```{r phq model1a sum_score retro (sensitivity analysis)}
@@
 ### Model 1b: Overlapping disorders, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
 ```{r phq model1b sum_score retro (sensitivity analysis)}
@@
 ### Model 1a: Disorder hierarchical, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
 ```{r ocir model1a absolute whole sample}
@@
 ### Model 1b: Overlapping disorders, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
 ```{r ocir model1b absolute whole sample}
@@
 ### Model 1a: Disorder hierarchical, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
 ```{r ocir model1a diff_score prepan}
@@
 ### Model 1b: Overlapping disorders, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
 ```{r ocir model1b diff_score prepan}
@@
 ### Model 1a: Disorder hierarchical, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
 ```{r ocir model1a sum_score prepan}
@@
 ### Model 1b: Overlapping disorders, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
 ```{r ocir model1b sum_score prepan}
@@
 ### Model 1a: Disorder hierarchical, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
 ```{r ocir model1a diff_score retro}
@@
 ### Model 1b: Overlapping disorders, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
 ```{r ocir model1b diff_score retro}
@@
 ### Model 1a: Disorder hierarchical, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
 ```{r ocir model1a sum_score retro}
@@
 ### Model 1b: Overlapping disorders, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
 ```{r ocir model1b sum_score retro}
@@
 ### Model 1a: Disorder hierarchical, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
 ```{r ocir model1a diff_score retro (sensitivity analyses)}
@@
 ### Model 1b: Overlapping disorders, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
 ```{r ocir model1b diff_score retro (sensitivity analyses)}
@@
 ### Model 1a: Disorder hierarchical, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
 ```{r ocir model1a sum_score retro (sensitivity analyses)}
@@
 ### Model 1b: Overlapping disorders, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
 ```{r ocir model1b sum_score retro (sensitivity analyses)}
@@
 ### Model 1a: Disorder hierarchical, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
 ```{r pcl model1a absolute whole sample}
@@
 ### Model 1b: Overlapping disorders, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
 ```{r pcl model1b absolute whole sample}
@@
 ### Model 1a: Disorder hierarchical, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
 ```{r pcl model1a diff_score prepan}
@@
 ### Model 1b: Overlapping disorders, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
 ```{r pcl model1b diff_score prepan}
@@
 ### Model 1a: Disorder hierarchical, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
 ```{r pcl model1a sum_score prepan}
@@
 ### Model 1b: Overlapping disorders, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
 ```{r pcl model1b sum_score prepan}

### 2020-11-05 PANCHANGE_analysis.Rmd
alish sensitivity analyses

@@
 
-dim(dat.retro_sensitivity)
-```
-age^2 sensitivity 
-Exclude individuals with NA for continuous Age variable
-```{r}
-dat_age_sensitivity <- dat %>%
-  filter(!is.na(Age))
-dim(dat_age_sensitivity)
+dim(dat.prepan)
 ```
@@
 1 - adjusted
-2 - adjusted with age^2
 a - hierarchical disorders
@@
 
-```{r model2a function}
-model2a.estimates <- function(outcome, data_set) {
-  # define the variable name of the dependent variable
-  dependent.variable <- outcome
-  # define the independent variables
-  independent.variables <- c("Disorder_hierarchical",
-                            "Gender_collapsed",
-                            "poly(Age, 2)",
-                            "Ethnicity_collapsed",
-                            "time_diff_coping_lockdown_march_23"
-                            )
-  # create the formula
-  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
-  glm.formula
-
-  # run the glm
-  assign(paste0(outcome,".model2a"),
-         lm( formula = glm.formula,
-             data = get(data_set)
-         )
-  )
-
-  assign(paste0(outcome,"model2a_estimates"),
-         tidy(get(paste0(outcome,".model2a")), conf.int = TRUE) %>%
-           mutate(
-             "Indepent variable" = recode_factor(
-               term,
-               "(Intercept)" = "Intercept",
-               "Disorder_hierarchicalAnxiety disorders" = "Anxiety disorders",
-               "Disorder_hierarchicalEating disorders" = "Eating disorders",
-               "Disorder_hierarchicalOCDs" = "OCDs",
-               "Disorder_hierarchicalPTSD" = "PTSD",
-               "Disorder_hierarchicalDepressive disorders" = "Depressive disorders",
-               "Disorder_hierarchicalBipolar disorders" = "Bipolar disorders",
-               "Gender_collapsedFemale" = "Female",
-               "Gender_collapsedNon-binary/Self-defined" = "Non-binary/Self-defined",
-               "poly(Age, 2)1" = "Age",
-               "poly(Age, 2)2" = "Age^2", 
-               "Ethnicity_collapsedMixed or multiple ethnic origins" = "Mixed or multiple ethnic origins",
-               "Ethnicity_collapsedAsian or Asian British" = "Asian or Asian British",
-               "Ethnicity_collapsedAfrican or African British" = "African or African British",
-               "Ethnicity_collapsedOther" = "Other ethnicity",
-               "time_diff_coping_lockdown_march_23" = "Time difference: Lockdown to baseline"
-             ),
-             "Estimate" = format(
-               round(estimate,
-                     digits = 2),
-               nsmall = 2),
-             "95% CI low" = format(
-               round(conf.low,
-                     digits = 2),
-               nsmall = 2),
-             "95% CI up" = format(
-               round(conf.high,
-                     digits = 2),
-               nsmall = 2),
-             "SE" = format(
-               round(std.error,
-                     digits = 2),
-               nsmall = 2),
-             "z score" = format(
-               round(statistic,
-                     digits = 2),
-               nsmall = 2),
-             "p value" = case_when(
-               p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
-               p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
-               p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
-             )
-           ) %>%
-           select(
-             "Indepent variable",
-             "Estimate",
-             "95% CI low",
-             "95% CI up",
-             "SE",
-             #    "z score",
-             "p value"
-           )
-  )
-
-  return(get(paste0(outcome,"model2a_estimates")))
-}
-
-model2a.reg.stats <- function(outcome, data_set) {
-  # define the variable name of the dependent variable
-  dependent.variable <- outcome
-  # define the independent variables
-  independent.variables <- c("Disorder_hierarchical")
-  # create the formula
-  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
-  glm.formula
-
-  # run the glm
-  assign(paste0(outcome,".model2a"),
-         lm( formula = glm.formula,
-             data = get(data_set)
-         )
-  )
-
-  assign(paste0(outcome,"model2a_reg_stats"),
-         glance(get(paste0(outcome,".model2a"))) %>%
-           mutate(
-             "n" = format(
-               round(nobs,
-                     digits = 0),
-               nsmall = 0),
-             "R2" = format(
-               round(r.squared,
-                     digits = 2),
-               nsmall = 2),
-             "adjust. R2" = format(
-               round(adj.r.squared,
-                     digits = 2),
-               nsmall = 2),
-             "F" = format(
-               round(statistic,
-                     digits = 2),
-               nsmall = 2),
-             "p value" = case_when(
-               p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
-               p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
-               p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
-             )
-           ) %>%
-           select(
-             "n",
-             "R2",
-             "adjust. R2",
-             "F",
-             "p value",
-             "df"
-           )
-  )
-
-  return(get(paste0(outcome,"model2a_reg_stats")))
-}
-```
-
-```{r model2b function}
-model2b.estimates <- function(outcome, data_set) {
-  # define the variable name of the dependent variable
-  dependent.variable <- outcome
-  # define the independent variables
-  independent.variables <- c("depression_and_anxiety",
-                             "eating_disorders",
-                             "obsessive_compulsive_disorders",
-                             "bipolar_and_schizophrenia",
-                             "mhd.posttraumatic_stress_disorder_ptsd",
-                             "autism_spectrum_disorder",
-                             "mhd.attention_deficit_hyperactivity_disorder",
-                             "mhd.personality_disorder",
-                             "Gender_collapsed",
-                             "poly(Age, 2)",
-                             "Ethnicity_collapsed",
-                             "key_worker",
-                             "time_diff_coping_lockdown_march_23"
-                                )
-  # create the formula
-  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
-  glm.formula
-
-  # run the glm
-  assign(paste0(outcome,".model2b"),
-         lm( formula = glm.formula,
-             data = get(data_set)
-         )
-  )
-
-  assign(paste0(outcome,"model2b_estimates"),
-         tidy(get(paste0(outcome,".model2b")), conf.int = TRUE) %>%
-           mutate(
-             "Indepent variable" = recode_factor(
-               term,
-               "(Intercept)" = "Intercept",
-               "anxiety_disordersAnxiety disorder" = "Anxiety disorders",
-               "depressive_disordersDepressive disorder" = "Depressive disorders",
-               "depression_and_anxietyDepressive and anxiety disorder" = "Depressive and anxiety disorder",
-               "depression_and_anxietyOnly depressive disorder" = "Only depressive disorder",
-               "depression_and_anxietyOnly anxiety disorder" = "Only anxiety disorder",
-               "eating_disordersEating disorder" = "Eating disorders",
-               "obsessive_compulsive_disordersObsessive compulsive disorder" = "OCDs",
-               "bipolar_and_schizophreniaPsychotic and bipolar disorder" = "Psychotic and bipolar disorder",
-               "bipolar_and_schizophreniaOnly psychotic disorder" = "Only psychotic disorder",
-               "bipolar_and_schizophreniaOnly bipolar disorder" = "Only bipolar disorder",
-               "psychotic_disordersPsychotic disorder" = "Psychotic disorder",
-               "mhd.mania_hypomania_bipolar_or_manicdepressionMania, hypomania, bipolar or manic-depression" = "Bipolar disorder",
-               "mhd.posttraumatic_stress_disorder_ptsdPost-traumatic stress disorder (PTSD)" = "PTSD",
-               "autism_spectrum_disorderAutism spectrum disorder" = "ASD",
-               "mhd.attention_deficit_hyperactivity_disorderAttention deficit or attention deficit and hyperactivity disorder (ADD/ADHD)" = "ADHD",
-               "mhd.personality_disorderPersonality disorder" = "Personality disorder",
-               "Gender_collapsedFemale" = "Female",
-               "Gender_collapsedNon-binary/Self-defined" = "Non-binary/Self-defined",
-               "poly(Age, 2)1" = "Age",
-               "poly(Age, 2)2" = "Age^2", 
-               "Ethnicity_collapsedMixed or multiple ethnic origins" = "Mixed or multiple ethnic origins",
-               "Ethnicity_collapsedAsian or Asian British" = "Asian or Asian British",
-               "Ethnicity_collapsedAfrican or African British" = "African or African British",
-               "Ethnicity_collapsedOther" = "Other ethnicity",
-               "key_workerKey worker" = "Key worker",
-               "time_diff_coping_lockdown_march_23" = "Time difference: Lockdown to baseline"
-             ),
-             "Estimate" = format(
-               round(estimate,
-                     digits = 2),
-               nsmall = 2),
-             "95% CI low" = format(
-               round(conf.low,
-                     digits = 2),
-               nsmall = 2),
-             "95% CI up" = format(
-               round(conf.high,
-                     digits = 2),
-               nsmall = 2),
-             "SE" = format(
-               round(std.error,
-                     digits = 2),
-               nsmall = 2),
-             "z score" = format(
-               round(statistic,
-                     digits = 2),
-               nsmall = 2),
-             "p value" = case_when(
-               p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
-               p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
-               p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
-             )
-           ) %>%
-           select(
-             "Indepent variable",
-             "Estimate",
-             "95% CI low",
-             "95% CI up",
-             "SE",
-             #    "z score",
-             "p value"
-           )
-  )
-
-  return(get(paste0(outcome,"model2b_estimates")))
-}
-
-model2b.reg.stats <- function(outcome, data_set) {
-  # define the variable name of the dependent variable
-  dependent.variable <- outcome
-  # define the independent variables
-  independent.variables <- c("Disorder_hierarchical")
-  # create the formula
-  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
-  glm.formula
-
-  # run the glm
-  assign(paste0(outcome,".model2b"),
-         lm( formula = glm.formula,
-             data = get(data_set)
-         )
-  )
-
-  assign(paste0(outcome,"model2b_reg_stats"),
-         glance(get(paste0(outcome,".model2b"))) %>%
-           mutate(
-             "n" = format(
-               round(nobs,
-                     digits = 0),
-               nsmall = 0),
-             "R2" = format(
-               round(r.squared,
-                     digits = 2),
-               nsmall = 2),
-             "adjust. R2" = format(
-               round(adj.r.squared,
-                     digits = 2),
-               nsmall = 2),
-             "F" = format(
-               round(statistic,
-                     digits = 2),
-               nsmall = 2),
-             "p value" = case_when(
-               p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
-               p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
-               p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
-             )
-           ) %>%
-           select(
-             "n",
-             "R2",
-             "adjust. R2",
-             "F",
-             "p value",
-             "df"
-           )
-  )
-
-  return(get(paste0(outcome,"model2b_reg_stats")))
-}
-```
-
 ```{r model0a.explan function}
@@
 
-### Model 2a: Disorder hierarchical, Adjusted with Age^2 
-```{r}
-# Regression coefficients
-gad_baseline_model2a_estimates <- model2a.estimates(outcome = "gad.sum_score_base",
-                                                 data_set = "dat_age_sensitivity")
-kable(gad_baseline_model2a_estimates)
-gad_baseline_model2a_estimates
-
-# Regression diagnostic statistics
-gad_baseline_model2a_reg_stats <- model2a.reg.stats(outcome = "gad.sum_score_base",
-                                                 data_set = "dat_age_sensitivity")
-kable(gad_baseline_model2a_reg_stats)
-gad_baseline_model2a_reg_stats
-```
-### Model 2b: Disorder hierarchical, Adjusted with Age^2 
-```{r}
-# Regression coefficients
-gad_baseline_model2b_estimates <- model2b.estimates(outcome = "gad.sum_score_base",
-                                                 data_set = "dat_age_sensitivity")
-kable(gad_baseline_model2b_estimates)
-gad_baseline_model2b_estimates
-
-# Regression diagnostic statistics
-gad_baseline_model2b_reg_stats <- model2b.reg.stats(outcome = "gad.sum_score_base",
-                                                 data_set = "dat_age_sensitivity")
-kable(gad_baseline_model2b_reg_stats)
-gad_baseline_model2b_reg_stats
-```
-
 # GAD prepan
@@
 ```
+
+# SENSITIVITY based on highest level of education
+
+# GAD prepan
+## Regression: Absolute scores
+### Model 0a: Disorder_hierarchical, Unadjusted
+```{r gad education sensitivity model0a sum_score prepan}
+# Regression coefficients
+gad_prepan_model0a_education_estimates <- model0a.explan.estimates(outcome = "gad.sum_score_base",
+                         explan_var = "highest_education_numeric",
+                         data_set = "dat.prepan")
+kable(gad_prepan_model0a_education_estimates)
+gad_prepan_model0a_education_estimates
+
+# Regression diagnostic statistics
+gad_prepan_model0a_education_reg_stats <- model0a.explan.reg.stats(outcome = "gad.sum_score_base",
+                         explan_var = "highest_education_numeric",
+                         data_set = "dat.prepan")
+kable(gad_prepan_model0a_education_reg_stats)
+gad_prepan_model0a_education_reg_stats
+```
+
+### Model 0b: Overlapping disorders, Unadjusted
+```{r gad education sensitivity model0b sum_score prepan}
+# Regression coefficients
+gad_prepan_model0b_education_estimates <- model0b.explan.estimates(outcome = "gad.sum_score_base",
+                         explan_var = "highest_education_numeric",
+                         data_set = "dat.prepan")
+kable(gad_prepan_model0b_education_estimates)
+gad_prepan_model0b_education_estimates
+
+# Regression diagnostic statistics
+gad_prepan_model0b_education_reg_stats <- model0b.explan.reg.stats(outcome = "gad.sum_score_base",
+                         explan_var = "highest_education_numeric",
+                         data_set = "dat.prepan")
+kable(gad_prepan_model0b_education_reg_stats)
+gad_prepan_model0b_education_reg_stats
+```
+
+### Model 1a: Disorder hierarchical, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r gad education sensitivity model1a sum_score prepan}
+# Regression coefficients
+gad_prepan_model1a_education_estimates <- model1a.explan.estimates(outcome = "gad.sum_score_base",
+                         explan_var = "highest_education_numeric",
+                         data_set = "dat.prepan")
+kable(gad_prepan_model1a_education_estimates)
+gad_prepan_model1a_education_estimates
+
+# Regression diagnostic statistics
+gad_prepan_model1a_education_reg_stats <- model1a.explan.reg.stats(outcome = "gad.sum_score_base",
+                         explan_var = "highest_education_numeric",
+                         data_set = "dat.prepan")
+kable(gad_prepan_model1a_education_reg_stats)
+gad_prepan_model1a_education_reg_stats
+```
+
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r gad education sensitivity model1b sum_score prepan}
+# Regression coefficients
+gad_prepan_model1b_education_estimates <- model1b.explan.estimates(outcome = "gad.sum_score_base",
+                         explan_var = "highest_education_numeric",
+                         data_set = "dat.prepan")
+kable(gad_prepan_model1b_education_estimates)
+gad_prepan_model1b_education_estimates
+
+# Regression diagnostic statistics
+gad_prepan_model1b_education_reg_stats <- model1b.explan.reg.stats(outcome = "gad.sum_score_base",
+                         explan_var = "highest_education_numeric",
+                         data_set = "dat.prepan")
+kable(gad_prepan_model1b_education_reg_stats)
+gad_prepan_model1b_education_reg_stats
+```
+
+# PHQ prepan
+## Regression: Absolute scores
+### Model 0a: Disorder_hierarchical, Unadjusted
+```{r phq education sensitivity model0a sum_score prepan}
+# Regression coefficients
+phq_prepan_model0a_education_estimates <- model0a.explan.estimates(outcome = "phq.sum_score_base",
+                         explan_var = "highest_education_numeric",
+                         data_set = "dat.prepan")
+kable(phq_prepan_model0a_education_estimates)
+phq_prepan_model0a_education_estimates
+
+# Regression diagnostic statistics
+phq_prepan_model0a_education_reg_stats <- model0a.explan.reg.stats(outcome = "phq.sum_score_base",
+                         explan_var = "highest_education_numeric",
+                         data_set = "dat.prepan")
+kable(phq_prepan_model0a_education_reg_stats)
+phq_prepan_model0a_education_reg_stats
+```
+
+### Model 0b: Overlapping disorders, Unadjusted
+```{r phq education sensitivity model0b sum_score prepan}
+# Regression coefficients
+phq_prepan_model0b_education_estimates <- model0b.explan.estimates(outcome = "phq.sum_score_base",
+                         explan_var = "highest_education_numeric",
+                         data_set = "dat.prepan")
+kable(phq_prepan_model0b_education_estimates)
+phq_prepan_model0b_education_estimates
+
+# Regression diagnostic statistics
+phq_prepan_model0b_education_reg_stats <- model0b.explan.reg.stats(outcome = "phq.sum_score_base",
+                         explan_var = "highest_education_numeric",
+                         data_set = "dat.prepan")
+kable(phq_prepan_model0b_education_reg_stats)
+phq_prepan_model0b_education_reg_stats
+```
+
+### Model 1a: Disorder hierarchical, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r phq education sensitivity model1a sum_score prepan}
+# Regression coefficients
+phq_prepan_model1a_education_estimates <- model1a.explan.estimates(outcome = "phq.sum_score_base",
+                         explan_var = "highest_education_numeric",
+                         data_set = "dat.prepan")
+kable(phq_prepan_model1a_education_estimates)
+phq_prepan_model1a_education_estimates
+
+# Regression diagnostic statistics
+phq_prepan_model1a_education_reg_stats <- model1a.explan.reg.stats(outcome = "phq.sum_score_base",
+                         explan_var = "highest_education_numeric",
+                         data_set = "dat.prepan")
+kable(phq_prepan_model1a_education_reg_stats)
+phq_prepan_model1a_education_reg_stats
+```
+
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r phq education sensitivity model1b sum_score prepan}
+# Regression coefficients
+phq_prepan_model1b_education_estimates <- model1b.explan.estimates(outcome = "phq.sum_score_base",
+                         explan_var = "highest_education_numeric",
+                         data_set = "dat.prepan")
+kable(phq_prepan_model1b_education_estimates)
+phq_prepan_model1b_education_estimates
+
+# Regression diagnostic statistics
+phq_prepan_model1b_education_reg_stats <- model1b.explan.reg.stats(outcome = "phq.sum_score_base",
+                         explan_var = "highest_education_numeric",
+                         data_set = "dat.prepan")
+kable(phq_prepan_model1b_education_reg_stats)
+phq_prepan_model1b_education_reg_stats
+```
+
+# OCIR prepan 
+## Regression: Absolute scores
+### Model 0a: Disorder_hierarchical, Unadjusted
+```{r ocir education sensitivity model0a sum_score prepan}
+# Regression coefficients
+ocir_prepan_model0a_education_estimates <- model0a.explan.estimates(outcome = "ocir.sum_score_base",
+                         explan_var = "highest_education_numeric",
+                         data_set = "dat.prepan")
+kable(ocir_prepan_model0a_education_estimates)
+ocir_prepan_model0a_education_estimates
+
+# Regression diagnostic statistics
+ocir_prepan_model0a_education_reg_stats <- model0a.explan.reg.stats(outcome = "ocir.sum_score_base",
+                         explan_var = "highest_education_numeric",
+                         data_set = "dat.prepan")
+kable(ocir_prepan_model0a_education_reg_stats)
+ocir_prepan_model0a_education_reg_stats
+```
+
+### Model 0b: Overlapping disorders, Unadjusted
+```{r ocir education sensitivity model0b sum_score prepan}
+# Regression coefficients
+ocir_prepan_model0b_education_estimates <- model0b.explan.estimates(outcome = "ocir.sum_score_base",
+                         explan_var = "highest_education_numeric",
+                         data_set = "dat.prepan")
+kable(ocir_prepan_model0b_education_estimates)
+ocir_prepan_model0b_education_estimates
+
+# Regression diagnostic statistics
+ocir_prepan_model0b_education_reg_stats <- model0b.explan.reg.stats(outcome = "ocir.sum_score_base",
+                         explan_var = "highest_education_numeric",
+                         data_set = "dat.prepan")
+kable(ocir_prepan_model0b_education_reg_stats)
+ocir_prepan_model0b_education_reg_stats
+```
+
+### Model 1a: Disorder hierarchical, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r ocir education sensitivity model1a sum_score prepan}
+# Regression coefficients
+ocir_prepan_model1a_education_estimates <- model1a.explan.estimates(outcome = "ocir.sum_score_base",
+                         explan_var = "highest_education_numeric",
+                         data_set = "dat.prepan")
+kable(ocir_prepan_model1a_education_estimates)
+ocir_prepan_model1a_education_estimates
+
+# Regression diagnostic statistics
+ocir_prepan_model1a_education_reg_stats <- model1a.explan.reg.stats(outcome = "ocir.sum_score_base",
+                         explan_var = "highest_education_numeric",
+                         data_set = "dat.prepan")
+kable(ocir_prepan_model1a_education_reg_stats)
+ocir_prepan_model1a_education_reg_stats
+```
+
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r ocir education sensitivity model1b sum_score prepan}
+# Regression coefficients
+ocir_prepan_model1b_education_estimates <- model1b.explan.estimates(outcome = "ocir.sum_score_base",
+                         explan_var = "highest_education_numeric",
+                         data_set = "dat.prepan")
+kable(ocir_prepan_model1b_education_estimates)
+ocir_prepan_model1b_education_estimates
+
+# Regression diagnostic statistics
+ocir_prepan_model1b_education_reg_stats <- model1b.explan.reg.stats(outcome = "ocir.sum_score_base",
+                         explan_var = "highest_education_numeric",
+                         data_set = "dat.prepan")
+kable(ocir_prepan_model1b_education_reg_stats)
+ocir_prepan_model1b_education_reg_stats
+```
+
+#PCL prepan 
+## Regression: Absolute scores
+### Model 0a: Disorder_hierarchical, Unadjusted
+```{r pcl education sensitivty model0a sum_score prepan}
+# Regression coefficients
+pcl_prepan_model0a_education_estimates <- model0a.explan.estimates(outcome = "pcl.sum_score_base",
+                         explan_var = "highest_education_numeric",
+                         data_set = "dat.prepan")
+kable(pcl_prepan_model0a_education_estimates)
+pcl_prepan_model0a_education_estimates
+
+# Regression diagnostic statistics
+pcl_prepan_model0a_education_reg_stats <- model0a.explan.reg.stats(outcome = "pcl.sum_score_base",
+                         explan_var = "highest_education_numeric",
+                         data_set = "dat.prepan")
+kable(pcl_prepan_model0a_education_reg_stats)
+pcl_prepan_model0a_education_reg_stats
+```
+
+### Model 0b: Overlapping disorders, Unadjusted
+```{r pcl education sensitivty model0b sum_score prepan}
+# Regression coefficients
+pcl_prepan_model0b_education_estimates <- model0b.explan.estimates(outcome = "pcl.sum_score_base",
+                         explan_var = "highest_education_numeric",
+                         data_set = "dat.prepan")
+kable(pcl_prepan_model0b_education_estimates)
+pcl_prepan_model0b_education_estimates
+
+# Regression diagnostic statistics
+pcl_prepan_model0b_education_reg_stats <- model0b.explan.reg.stats(outcome = "pcl.sum_score_base",
+                         explan_var = "highest_education_numeric",
+                         data_set = "dat.prepan")
+kable(pcl_prepan_model0b_education_reg_stats)
+pcl_prepan_model0b_education_reg_stats
+```
+
+### Model 1a: Disorder hierarchical, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r pcl education sensitivty model1a sum_score prepan}
+# Regression coefficients
+pcl_prepan_model1a_education_estimates <- model1a.explan.estimates(outcome = "pcl.sum_score_base",
+                         explan_var = "highest_education_numeric",
+                         data_set = "dat.prepan")
+kable(pcl_prepan_model1a_education_estimates)
+pcl_prepan_model1a_education_estimates
+
+# Regression diagnostic statistics
+pcl_prepan_model1a_education_reg_stats <- model1a.explan.reg.stats(outcome = "pcl.sum_score_base",
+                         explan_var = "highest_education_numeric",
+                         data_set = "dat.prepan")
+kable(pcl_prepan_model1a_education_reg_stats)
+pcl_prepan_model1a_education_reg_stats
+```
+
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r pcl education sensitivty model1b sum_score prepan}
+# Regression coefficients
+pcl_prepan_model1b_education_estimates <- model1b.explan.estimates(outcome = "pcl.sum_score_base",
+                         explan_var = "highest_education_numeric",
+                         data_set = "dat.prepan")
+kable(pcl_prepan_model1b_education_estimates)
+pcl_prepan_model1b_education_estimates
+
+# Regression diagnostic statistics
+pcl_prepan_model1b_education_reg_stats <- model1b.explan.reg.stats(outcome = "pcl.sum_score_base",
+                         explan_var = "highest_education_numeric",
+                         data_set = "dat.prepan")
+kable(pcl_prepan_model1b_education_reg_stats)
+pcl_prepan_model1b_education_reg_stats
+```
+
+# SENSITIVITY based on employment status
+
+# GAD prepan
+## Regression: Absolute scores
+### Model 0a: Disorder_hierarchical, Unadjusted
+```{r gad employment sensitivity model0a sum_score prepan}
+# Regression coefficients
+gad_prepan_model0a_employment_estimates <- model0a.explan.estimates(outcome = "gad.sum_score_base",
+                         explan_var = "employment.unemployed_numeric",
+                         data_set = "dat.prepan")
+kable(gad_prepan_model0a_employment_estimates)
+gad_prepan_model0a_employment_estimates
+
+# Regression diagnostic statistics
+gad_prepan_model0a_employment_reg_stats <- model0a.explan.reg.stats(outcome = "gad.sum_score_base",
+                         explan_var = "employment.unemployed_numeric",
+                         data_set = "dat.prepan")
+kable(gad_prepan_model0a_employment_reg_stats)
+gad_prepan_model0a_employment_reg_stats
+```
+
+### Model 0b: Overlapping disorders, Unadjusted
+```{r gad employment sensitivity model0b sum_score prepan}
+# Regression coefficients
+gad_prepan_model0b_employment_estimates <- model0b.explan.estimates(outcome = "gad.sum_score_base",
+                         explan_var = "employment.unemployed_numeric",
+                         data_set = "dat.prepan")
+kable(gad_prepan_model0b_employment_estimates)
+gad_prepan_model0b_employment_estimates
+
+# Regression diagnostic statistics
+gad_prepan_model0b_employment_reg_stats <- model0b.explan.reg.stats(outcome = "gad.sum_score_base",
+                         explan_var = "employment.unemployed_numeric",
+                         data_set = "dat.prepan")
+kable(gad_prepan_model0b_employment_reg_stats)
+gad_prepan_model0b_employment_reg_stats
+```
+
+### Model 1a: Disorder hierarchical, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r gad employment sensitivity model1a sum_score prepan}
+# Regression coefficients
+gad_prepan_model1a_employment_estimates <- model1a.explan.estimates(outcome = "gad.sum_score_base",
+                         explan_var = "employment.unemployed_numeric",
+                         data_set = "dat.prepan")
+kable(gad_prepan_model1a_employment_estimates)
+gad_prepan_model1a_employment_estimates
+
+# Regression diagnostic statistics
+gad_prepan_model1a_employment_reg_stats <- model1a.explan.reg.stats(outcome = "gad.sum_score_base",
+                         explan_var = "employment.unemployed_numeric",
+                         data_set = "dat.prepan")
+kable(gad_prepan_model1a_employment_reg_stats)
+gad_prepan_model1a_employment_reg_stats
+```
+
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r gad employment sensitivity model1b sum_score prepan}
+# Regression coefficients
+gad_prepan_model1b_employment_estimates <- model1b.explan.estimates(outcome = "gad.sum_score_base",
+                         explan_var = "employment.unemployed_numeric",
+                         data_set = "dat.prepan")
+kable(gad_prepan_model1b_employment_estimates)
+gad_prepan_model1b_employment_estimates
+
+# Regression diagnostic statistics
+gad_prepan_model1b_employment_reg_stats <- model1b.explan.reg.stats(outcome = "gad.sum_score_base",
+                         explan_var = "employment.unemployed_numeric",
+                         data_set = "dat.prepan")
+kable(gad_prepan_model1b_employment_reg_stats)
+gad_prepan_model1b_employment_reg_stats
+```
+
+# PHQ prepan
+## Regression: Absolute scores
+### Model 0a: Disorder_hierarchical, Unadjusted
+```{r phq employment sensitivity model0a sum_score prepan}
+# Regression coefficients
+phq_prepan_model0a_employment_estimates <- model0a.explan.estimates(outcome = "phq.sum_score_base",
+                         explan_var = "employment.unemployed_numeric",
+                         data_set = "dat.prepan")
+kable(phq_prepan_model0a_employment_estimates)
+phq_prepan_model0a_employment_estimates
+
+# Regression diagnostic statistics
+phq_prepan_model0a_employment_reg_stats <- model0a.explan.reg.stats(outcome = "phq.sum_score_base",
+                         explan_var = "employment.unemployed_numeric",
+                         data_set = "dat.prepan")
+kable(phq_prepan_model0a_employment_reg_stats)
+phq_prepan_model0a_employment_reg_stats
+```
+
+### Model 0b: Overlapping disorders, Unadjusted
+```{r phq employment sensitivity model0b sum_score prepan}
+# Regression coefficients
+phq_prepan_model0b_employment_estimates <- model0b.explan.estimates(outcome = "phq.sum_score_base",
+                         explan_var = "employment.unemployed_numeric",
+                         data_set = "dat.prepan")
+kable(phq_prepan_model0b_employment_estimates)
+phq_prepan_model0b_employment_estimates
+
+# Regression diagnostic statistics
+phq_prepan_model0b_employment_reg_stats <- model0b.explan.reg.stats(outcome = "phq.sum_score_base",
+                         explan_var = "employment.unemployed_numeric",
+                         data_set = "dat.prepan")
+kable(phq_prepan_model0b_employment_reg_stats)
+phq_prepan_model0b_employment_reg_stats
+```
+
+### Model 1a: Disorder hierarchical, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r phq employment sensitivity model1a sum_score prepan}
+# Regression coefficients
+phq_prepan_model1a_employment_estimates <- model1a.explan.estimates(outcome = "phq.sum_score_base",
+                         explan_var = "employment.unemployed_numeric",
+                         data_set = "dat.prepan")
+kable(phq_prepan_model1a_employment_estimates)
+phq_prepan_model1a_employment_estimates
+
+# Regression diagnostic statistics
+phq_prepan_model1a_employment_reg_stats <- model1a.explan.reg.stats(outcome = "phq.sum_score_base",
+                         explan_var = "employment.unemployed_numeric",
+                         data_set = "dat.prepan")
+kable(phq_prepan_model1a_employment_reg_stats)
+phq_prepan_model1a_employment_reg_stats
+```
+
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r phq employment sensitivity model1b sum_score prepan}
+# Regression coefficients
+phq_prepan_model1b_employment_estimates <- model1b.explan.estimates(outcome = "phq.sum_score_base",
+                         explan_var = "employment.unemployed_numeric",
+                         data_set = "dat.prepan")
+kable(phq_prepan_model1b_employment_estimates)
+phq_prepan_model1b_employment_estimates
+
+# Regression diagnostic statistics
+phq_prepan_model1b_employment_reg_stats <- model1b.explan.reg.stats(outcome = "phq.sum_score_base",
+                         explan_var = "employment.unemployed_numeric",
+                         data_set = "dat.prepan")
+kable(phq_prepan_model1b_employment_reg_stats)
+phq_prepan_model1b_employment_reg_stats
+```
+
+# OCIR prepan 
+## Regression: Absolute scores
+### Model 0a: Disorder_hierarchical, Unadjusted
+```{r ocir employment sensitivity model0a sum_score prepan}
+# Regression coefficients
+ocir_prepan_model0a_employment_estimates <- model0a.explan.estimates(outcome = "ocir.sum_score_base",
+                         explan_var = "employment.unemployed_numeric",
+                         data_set = "dat.prepan")
+kable(ocir_prepan_model0a_employment_estimates)
+ocir_prepan_model0a_employment_estimates
+
+# Regression diagnostic statistics
+ocir_prepan_model0a_employment_reg_stats <- model0a.explan.reg.stats(outcome = "ocir.sum_score_base",
+                         explan_var = "employment.unemployed_numeric",
+                         data_set = "dat.prepan")
+kable(ocir_prepan_model0a_employment_reg_stats)
+ocir_prepan_model0a_employment_reg_stats
+```
+
+### Model 0b: Overlapping disorders, Unadjusted
+```{r ocir employment sensitivity model0b sum_score prepan}
+# Regression coefficients
+ocir_prepan_model0b_employment_estimates <- model0b.explan.estimates(outcome = "ocir.sum_score_base",
+                         explan_var = "employment.unemployed_numeric",
+                         data_set = "dat.prepan")
+kable(ocir_prepan_model0b_employment_estimates)
+ocir_prepan_model0b_employment_estimates
+
+# Regression diagnostic statistics
+ocir_prepan_model0b_employment_reg_stats <- model0b.explan.reg.stats(outcome = "ocir.sum_score_base",
+                         explan_var = "employment.unemployed_numeric",
+                         data_set = "dat.prepan")
+kable(ocir_prepan_model0b_employment_reg_stats)
+ocir_prepan_model0b_employment_reg_stats
+```
+
+### Model 1a: Disorder hierarchical, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r ocir employment sensitivity model1a sum_score prepan}
+# Regression coefficients
+ocir_prepan_model1a_employment_estimates <- model1a.explan.estimates(outcome = "ocir.sum_score_base",
+                         explan_var = "employment.unemployed_numeric",
+                         data_set = "dat.prepan")
+kable(ocir_prepan_model1a_employment_estimates)
+ocir_prepan_model1a_employment_estimates
+
+# Regression diagnostic statistics
+ocir_prepan_model1a_employment_reg_stats <- model1a.explan.reg.stats(outcome = "ocir.sum_score_base",
+                         explan_var = "employment.unemployed_numeric",
+                         data_set = "dat.prepan")
+kable(ocir_prepan_model1a_employment_reg_stats)
+ocir_prepan_model1a_employment_reg_stats
+```
+
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r ocir employment sensitivity model1b sum_score prepan}
+# Regression coefficients
+ocir_prepan_model1b_employment_estimates <- model1b.explan.estimates(outcome = "ocir.sum_score_base",
+                         explan_var = "employment.unemployed_numeric",
+                         data_set = "dat.prepan")
+kable(ocir_prepan_model1b_employment_estimates)
+ocir_prepan_model1b_employment_estimates
+
+# Regression diagnostic statistics
+ocir_prepan_model1b_employment_reg_stats <- model1b.explan.reg.stats(outcome = "ocir.sum_score_base",
+                         explan_var = "employment.unemployed_numeric",
+                         data_set = "dat.prepan")
+kable(ocir_prepan_model1b_employment_reg_stats)
+ocir_prepan_model1b_employment_reg_stats
+```
+
+#PCL prepan 
+## Regression: Absolute scores
+### Model 0a: Disorder_hierarchical, Unadjusted
+```{r pcl employment sensitivty model0a sum_score prepan}
+# Regression coefficients
+pcl_prepan_model0a_employment_estimates <- model0a.explan.estimates(outcome = "pcl.sum_score_base",
+                         explan_var = "employment.unemployed_numeric",
+                         data_set = "dat.prepan")
+kable(pcl_prepan_model0a_employment_estimates)
+pcl_prepan_model0a_employment_estimates
+
+# Regression diagnostic statistics
+pcl_prepan_model0a_employment_reg_stats <- model0a.explan.reg.stats(outcome = "pcl.sum_score_base",
+                         explan_var = "employment.unemployed_numeric",
+                         data_set = "dat.prepan")
+kable(pcl_prepan_model0a_employment_reg_stats)
+pcl_prepan_model0a_employment_reg_stats
+```
+
+### Model 0b: Overlapping disorders, Unadjusted
+```{r pcl employment sensitivty model0b sum_score prepan}
+# Regression coefficients
+pcl_prepan_model0b_employment_estimates <- model0b.explan.estimates(outcome = "pcl.sum_score_base",
+                         explan_var = "employment.unemployed_numeric",
+                         data_set = "dat.prepan")
+kable(pcl_prepan_model0b_employment_estimates)
+pcl_prepan_model0b_employment_estimates
+
+# Regression diagnostic statistics
+pcl_prepan_model0b_employment_reg_stats <- model0b.explan.reg.stats(outcome = "pcl.sum_score_base",
+                         explan_var = "employment.unemployed_numeric",
+                         data_set = "dat.prepan")
+kable(pcl_prepan_model0b_employment_reg_stats)
+pcl_prepan_model0b_employment_reg_stats
+```
+
+### Model 1a: Disorder hierarchical, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r pcl employment sensitivty model1a sum_score prepan}
+# Regression coefficients
+pcl_prepan_model1a_employment_estimates <- model1a.explan.estimates(outcome = "pcl.sum_score_base",
+                         explan_var = "employment.unemployed_numeric",
+                         data_set = "dat.prepan")
+kable(pcl_prepan_model1a_employment_estimates)
+pcl_prepan_model1a_employment_estimates
+
+# Regression diagnostic statistics
+pcl_prepan_model1a_employment_reg_stats <- model1a.explan.reg.stats(outcome = "pcl.sum_score_base",
+                         explan_var = "employment.unemployed_numeric",
+                         data_set = "dat.prepan")
+kable(pcl_prepan_model1a_employment_reg_stats)
+pcl_prepan_model1a_employment_reg_stats
+```
+
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r pcl employment sensitivty model1b sum_score prepan}
+# Regression coefficients
+pcl_prepan_model1b_employment_estimates <- model1b.explan.estimates(outcome = "pcl.sum_score_base",
+                         explan_var = "employment.unemployed_numeric",
+                         data_set = "dat.prepan")
+kable(pcl_prepan_model1b_employment_estimates)
+pcl_prepan_model1b_employment_estimates
+
+# Regression diagnostic statistics
+pcl_prepan_model1b_employment_reg_stats <- model1b.explan.reg.stats(outcome = "pcl.sum_score_base",
+                         explan_var = "employment.unemployed_numeric",
+                         data_set = "dat.prepan")
+kable(pcl_prepan_model1b_employment_reg_stats)
+pcl_prepan_model1b_employment_reg_stats
+```
+
+# SENSITIVITY based on employment change
+
+```{r create an employment change variable}
+dat.prepan <- dat.prepan %>%
+  mutate(employment_change =
+           case_when(
+             employment.unemployed_numeric == "1" ~ "Unemployed",
+             employment.became_unemployed_numeric == "1" ~ "Became Unemployed",                         
+             employment.furloughed_or_paid_leave_government_funded_numeric == "1" ~ "Furlough",
+             employment.furloughed_or_paid_leave_company_funded_numeric == "1" ~ "Furlough",    
+             employment.paid_leave_furloughed_numeric == "1" ~ "Furlough",                             
+             key_worker_numeric == "1" ~ "Key Worker",                                            
+             employment.government_work_key_workers_numeric == "1" ~ "Key Worker",                
+             employment.zerohours_contract_numeric == "1" ~ "Zero Hours Contract",                         
+             employment.retired_numeric == "1" ~ "Retired",                                   
+             employment.student_gcse_or_a_level_numeric == "1" ~ "Student",                   
+             employment.student_university_numeric == "1" ~ "Student"                        
+           )
+  )
+
+dat.prepan$employment_change <- as.factor(dat.prepan$employment_change)
+```
+
+# GAD prepan
+## Regression: Absolute scores
+### Model 0a: Disorder_hierarchical, Unadjusted
+```{r gad employment change sensitivity model0a sum_score prepan}
+# Regression coefficients
+gad_prepan_model0a_employmentchange_estimates <- model0a.explan.estimates(outcome = "gad.sum_score_base",
+                         explan_var = "employment_change",
+                         data_set = "dat.prepan")
+kable(gad_prepan_model0a_employmentchange_estimates)
+gad_prepan_model0a_employmentchange_estimates
+
+# Regression diagnostic statistics
+gad_prepan_model0a_employmentchange_reg_stats <- model0a.explan.reg.stats(outcome = "gad.sum_score_base",
+                         explan_var = "employment_change",
+                         data_set = "dat.prepan")
+kable(gad_prepan_model0a_employmentchange_reg_stats)
+gad_prepan_model0a_employmentchange_reg_stats
+```
+
+### Model 0b: Overlapping disorders, Unadjusted
+```{r gad employment change sensitivity model0b sum_score prepan}
+# Regression coefficients
+gad_prepan_model0b_employmentchange_estimates <- model0b.explan.estimates(outcome = "gad.sum_score_base",
+                         explan_var = "employment_change",
+                         data_set = "dat.prepan")
+kable(gad_prepan_model0b_employmentchange_estimates)
+gad_prepan_model0b_employmentchange_estimates
+
+# Regression diagnostic statistics
+gad_prepan_model0b_employmentchange_reg_stats <- model0b.explan.reg.stats(outcome = "gad.sum_score_base",
+                         explan_var = "employment_change",
+                         data_set = "dat.prepan")
+kable(gad_prepan_model0b_employmentchange_reg_stats)
+gad_prepan_model0b_employmentchange_reg_stats
+```
+
+### Model 1a: Disorder hierarchical, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r gad employment change sensitivity model1a sum_score prepan}
+# Regression coefficients
+gad_prepan_model1a_employmentchange_estimates <- model1a.explan.estimates(outcome = "gad.sum_score_base",
+                         explan_var = "employment_change",
+                         data_set = "dat.prepan")
+kable(gad_prepan_model1a_employmentchange_estimates)
+gad_prepan_model1a_employmentchange_estimates
+
+# Regression diagnostic statistics
+gad_prepan_model1a_employmentchange_reg_stats <- model1a.explan.reg.stats(outcome = "gad.sum_score_base",
+                         explan_var = "employment_change",
+                         data_set = "dat.prepan")
+kable(gad_prepan_model1a_employmentchange_reg_stats)
+gad_prepan_model1a_employmentchange_reg_stats
+```
+
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r gad employment change sensitivity model1b sum_score prepan}
+# Regression coefficients
+gad_prepan_model1b_employmentchange_estimates <- model1b.explan.estimates(outcome = "gad.sum_score_base",
+                         explan_var = "employment_change",
+                         data_set = "dat.prepan")
+kable(gad_prepan_model1b_employmentchange_estimates)
+gad_prepan_model1b_employmentchange_estimates
+
+# Regression diagnostic statistics
+gad_prepan_model1b_employmentchange_reg_stats <- model1b.explan.reg.stats(outcome = "gad.sum_score_base",
+                         explan_var = "employment_change",
+                         data_set = "dat.prepan")
+kable(gad_prepan_model1b_employmentchange_reg_stats)
+gad_prepan_model1b_employmentchange_reg_stats
+```
+
+# PHQ prepan
+## Regression: Absolute scores
+### Model 0a: Disorder_hierarchical, Unadjusted
+```{r phq employment change sensitivity model0a sum_score prepan}
+# Regression coefficients
+phq_prepan_model0a_employmentchange_estimates <- model0a.explan.estimates(outcome = "phq.sum_score_base",
+                         explan_var = "employment_change",
+                         data_set = "dat.prepan")
+kable(phq_prepan_model0a_employmentchange_estimates)
+phq_prepan_model0a_employmentchange_estimates
+
+# Regression diagnostic statistics
+phq_prepan_model0a_employmentchange_reg_stats <- model0a.explan.reg.stats(outcome = "phq.sum_score_base",
+                         explan_var = "employment_change",
+                         data_set = "dat.prepan")
+kable(phq_prepan_model0a_employmentchange_reg_stats)
+phq_prepan_model0a_employmentchange_reg_stats
+```
+
+### Model 0b: Overlapping disorders, Unadjusted
+```{r phq employment change sensitivity model0b sum_score prepan}
+# Regression coefficients
+phq_prepan_model0b_employmentchange_estimates <- model0b.explan.estimates(outcome = "phq.sum_score_base",
+                         explan_var = "employment_change",
+                         data_set = "dat.prepan")
+kable(phq_prepan_model0b_employmentchange_estimates)
+phq_prepan_model0b_employmentchange_estimates
+
+# Regression diagnostic statistics
+phq_prepan_model0b_employmentchange_reg_stats <- model0b.explan.reg.stats(outcome = "phq.sum_score_base",
+                         explan_var = "employment_change",
+                         data_set = "dat.prepan")
+kable(phq_prepan_model0b_employmentchange_reg_stats)
+phq_prepan_model0b_employmentchange_reg_stats
+```
+
+### Model 1a: Disorder hierarchical, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r phq employment change sensitivity model1a sum_score prepan}
+# Regression coefficients
+phq_prepan_model1a_employmentchange_estimates <- model1a.explan.estimates(outcome = "phq.sum_score_base",
+                         explan_var = "employment_change",
+                         data_set = "dat.prepan")
+kable(phq_prepan_model1a_employmentchange_estimates)
+phq_prepan_model1a_employmentchange_estimates
+
+# Regression diagnostic statistics
+phq_prepan_model1a_employmentchange_reg_stats <- model1a.explan.reg.stats(outcome = "phq.sum_score_base",
+                         explan_var = "employment_change",
+                         data_set = "dat.prepan")
+kable(phq_prepan_model1a_employmentchange_reg_stats)
+phq_prepan_model1a_employmentchange_reg_stats
+```
+
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r phq employment change sensitivity model1b sum_score prepan}
+# Regression coefficients
+phq_prepan_model1b_employmentchange_estimates <- model1b.explan.estimates(outcome = "phq.sum_score_base",
+                         explan_var = "employment_change",
+                         data_set = "dat.prepan")
+kable(phq_prepan_model1b_employmentchange_estimates)
+phq_prepan_model1b_employmentchange_estimates
+
+# Regression diagnostic statistics
+phq_prepan_model1b_employmentchange_reg_stats <- model1b.explan.reg.stats(outcome = "phq.sum_score_base",
+                         explan_var = "employment_change",
+                         data_set = "dat.prepan")
+kable(phq_prepan_model1b_employmentchange_reg_stats)
+phq_prepan_model1b_employmentchange_reg_stats
+```
+
+# OCIR prepan 
+## Regression: Absolute scores
+### Model 0a: Disorder_hierarchical, Unadjusted
+```{r ocir employment change sensitivity model0a sum_score prepan}
+# Regression coefficients
+ocir_prepan_model0a_employmentchange_estimates <- model0a.explan.estimates(outcome = "ocir.sum_score_base",
+                         explan_var = "employment_change",
+                         data_set = "dat.prepan")
+kable(ocir_prepan_model0a_employmentchange_estimates)
+ocir_prepan_model0a_employmentchange_estimates
+
+# Regression diagnostic statistics
+ocir_prepan_model0a_employmentchange_reg_stats <- model0a.explan.reg.stats(outcome = "ocir.sum_score_base",
+                         explan_var = "employment_change",
+                         data_set = "dat.prepan")
+kable(ocir_prepan_model0a_employmentchange_reg_stats)
+ocir_prepan_model0a_employmentchange_reg_stats
+```
+
+### Model 0b: Overlapping disorders, Unadjusted
+```{r ocir employment change sensitivity model0b sum_score prepan}
+# Regression coefficients
+ocir_prepan_model0b_employmentchange_estimates <- model0b.explan.estimates(outcome = "ocir.sum_score_base",
+                         explan_var = "employment_change",
+                         data_set = "dat.prepan")
+kable(ocir_prepan_model0b_employmentchange_estimates)
+ocir_prepan_model0b_employmentchange_estimates
+
+# Regression diagnostic statistics
+ocir_prepan_model0b_employmentchange_reg_stats <- model0b.explan.reg.stats(outcome = "ocir.sum_score_base",
+                         explan_var = "employment_change",
+                         data_set = "dat.prepan")
+kable(ocir_prepan_model0b_employmentchange_reg_stats)
+ocir_prepan_model0b_employmentchange_reg_stats
+```
+
+### Model 1a: Disorder hierarchical, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r ocir employment change sensitivity model1a sum_score prepan}
+# Regression coefficients
+ocir_prepan_model1a_employmentchange_estimates <- model1a.explan.estimates(outcome = "ocir.sum_score_base",
+                         explan_var = "employment_change",
+                         data_set = "dat.prepan")
+kable(ocir_prepan_model1a_employmentchange_estimates)
+ocir_prepan_model1a_employmentchannge_estimates
+
+# Regression diagnostic statistics
+ocir_prepan_model1a_employmentchange_reg_stats <- model1a.explan.reg.stats(outcome = "ocir.sum_score_base",
+                         explan_var = "employment_change",
+                         data_set = "dat.prepan")
+kable(ocir_prepan_model1a_employmentchange_reg_stats)
+ocir_prepan_model1a_employmentchange_reg_stats
+```
+
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r ocir employment change sensitivity model1b sum_score prepan}
+# Regression coefficients
+ocir_prepan_model1b_employmentchange_estimates <- model1b.explan.estimates(outcome = "ocir.sum_score_base",
+                         explan_var = "employment_change",
+                         data_set = "dat.prepan")
+kable(ocir_prepan_model1b_employmentchange_estimates)
+ocir_prepan_model1b_employmentchange_estimates
+
+# Regression diagnostic statistics
+ocir_prepan_model1b_employmentchange_reg_stats <- model1b.explan.reg.stats(outcome = "ocir.sum_score_base",
+                         explan_var = "employment_change",
+                         data_set = "dat.prepan")
+kable(ocir_prepan_model1b_employmentchange_reg_stats)
+ocir_prepan_model1b_employmentchange_reg_stats
+```
+
+#PCL prepan 
+## Regression: Absolute scores
+### Model 0a: Disorder_hierarchical, Unadjusted
+```{r pcl employment change sensitivty model0a sum_score prepan}
+# Regression coefficients
+pcl_prepan_model0a_employmentchange_estimates <- model0a.explan.estimates(outcome = "pcl.sum_score_base",
+                         explan_var = "employment_change",
+                         data_set = "dat.prepan")
+kable(pcl_prepan_model0a_employmentchange_estimates)
+pcl_prepan_model0a_employmentchange_estimates
+
+# Regression diagnostic statistics
+pcl_prepan_model0a_employmentchange_reg_stats <- model0a.explan.reg.stats(outcome = "pcl.sum_score_base",
+                         explan_var = "employment_change",
+                         data_set = "dat.prepan")
+kable(pcl_prepan_model0a_employmentchange_reg_stats)
+pcl_prepan_model0a_employmentchange_reg_stats
+```
+
+### Model 0b: Overlapping disorders, Unadjusted
+```{r pcl employment change sensitivty model0b sum_score prepan}
+# Regression coefficients
+pcl_prepan_model0b_employmentchange_estimates <- model0b.explan.estimates(outcome = "pcl.sum_score_base",
+                         explan_var = "employment_change",
+                         data_set = "dat.prepan")
+kable(pcl_prepan_model0b_employmentchange_estimates)
+pcl_prepan_model0b_employmentchange_estimates
+
+# Regression diagnostic statistics
+pcl_prepan_model0b_employmentchange_reg_stats <- model0b.explan.reg.stats(outcome = "pcl.sum_score_base",
+                         explan_var = "employment_change",
+                         data_set = "dat.prepan")
+kable(pcl_prepan_model0b_employmentchange_reg_stats)
+pcl_prepan_model0b_employmentchange_reg_stats
+```
+
+### Model 1a: Disorder hierarchical, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r pcl employment change sensitivty model1a sum_score prepan}
+# Regression coefficients
+pcl_prepan_model1a_employmentchange_estimates <- model1a.explan.estimates(outcome = "pcl.sum_score_base",
+                         explan_var = "employment_change",
+                         data_set = "dat.prepan")
+kable(pcl_prepan_model1a_employmentchange_estimates)
+pcl_prepan_model1a_employmentchange_estimates
+
+# Regression diagnostic statistics
+pcl_prepan_model1a_employmentchange_reg_stats <- model1a.explan.reg.stats(outcome = "pcl.sum_score_base",
+                         explan_var = "employment_change",
+                         data_set = "dat.prepan")
+kable(pcl_prepan_model1a_employmentchange_reg_stats)
+pcl_prepan_model1a_employmentchange_reg_stats
+```
+
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r pcl employment change sensitivty model1b sum_score prepan}
+# Regression coefficients
+pcl_prepan_model1b_employmentchange_estimates <- model1b.explan.estimates(outcome = "pcl.sum_score_base",
+                         explan_var = "employment_change",
+                         data_set = "dat.prepan")
+kable(pcl_prepan_model1b_employmentchange_estimates)
+pcl_prepan_model1b_employmentchange_estimates
+
+# Regression diagnostic statistics
+pcl_prepan_model1b_employmentchange_reg_stats <- model1b.explan.reg.stats(outcome = "pcl.sum_score_base",
+                         explan_var = "employment_change",
+                         data_set = "dat.prepan")
+kable(pcl_prepan_model1b_employmentchange_reg_stats)
+pcl_prepan_model1b_employmentchange_reg_stats
+```

### 2020-11-05 PANNEURO_analysis_WHO_pres.Rmd
alish sensitivity analyses

--- 2020-10-27 PANNEURO_analysis_WHO_pres.Rmd
@@
 title: "PANNEURO_analysis"
-author: "Christopher Huebel, Alish Palmos, Molly Davies, and Laura Hegemann"
+author: "Christopher Huebel"
 date: "Sys.Date()"
@@
       collapsed: no
-  pdf_document:
+  word_document:
     toc: yes
     toc_depth: '2'
-  word_document:
+  pdf_document:
     toc: yes
@@
 Install packages (if they are not available in your version of R)
-```{r Installing packages, include = FALSE}
+```{r Installing packages}
 #install.packages("summarytools")
@@
 Load packages
-```{r Load packages, include = FALSE}
+```{r Load packages}
 library(knitr)
@@
 Define colours for plotting this are the standard coping colours
-```{r Colour palettes: COPING, include = FALSE}
+```{r Colour palettes: COPING}
 COPINGpalette2 <- c("#78D9C5",
@@
 Set up ggplot theme for the plots
-```{r ggplot theme, include=FALSE}
+```{r ggplot theme}
 theme_personal <-  theme(
@@
 ## Read in data
-```{r read in data, include = FALSE}
+```{r read in data}
 dat.raw <- readRDS(file = paste0(data_path, "/baseline_and_cfs_wave6.rds")) #NEEDS CHANGING
@@
 
-```{r bmi recode}
+```{r}
 
@@
 
-```{r key worker status frequencies by probable Covid}
+```{r}
 key_worker_category_per_Covid_prop_total <- dat.raw %>%
@@
 
-# Scoring for neuro measures
-
-# ALSfrs (not included)
-```{r ALSfrs col names, include = FALSE}
+**ADD SCORING FOR NEURO MEASURES**
+# ALSfrs
+```{ALSfrs col names r}
 als.col.names <- dat.raw %>%
@@
 
-```{r ALSfrs row sums, include = FALSE}
+```{ALSfrs row sums r}
 dat.raw <- dat.raw %>%
@@
 
-```{r ALSfrs frequencies, include = FALSE}
+```{ALSfrs frequencies r}
 dat.raw %>%
@@
 ```
-
 # ESS
-```{r ESS col names, include = FALSE}
+```{ESS col names r}
 ess.col.names <- dat.raw %>%
@@
 
-ess.col.names
-```
-
-```{r ESS row sums, include = FALSE}
-
-# Create vector with scoring key: If the item is reversed coded use -1. 
-# There needs to be the correct number of values for each item in the questionnaire. 
-ess.items_key <- c(1,1,1,1,1,1,1,1)
-
-# Create vector with items that are included in sum score
-ess.items <- c(
-  "ess.sitting_and_reading_numeric",
-  "ess.watching_tv_numeric",
-  "ess.sitting_inactive_in_a_public_place_numeric",
-  "ess.break_passenger_car_hour_numeric",
-  "ess.afternoon_rest_circumstances_lying_numeric",
-  "ess.sitting_and_talking_to_someone_numeric",
-  "ess.sitting_quietly_after_a_lunch_without_alcohol_numeric",
-  "ess.car_minutes_stopped_traffic_numeric"
-  )
-
-# Calculate sum score
-ess.scored_items <- scoreItems(keys = ess.items_key,
-                                        items = dat.raw[ess.items],
-                                        totals = TRUE, 
-                                        missing = TRUE, 
-                                        impute = 'none', 
-                                        min = 0, 
-                                        max = 3)
-# Add in column to tibble
-dat.raw$ess.sum_score_raw <- ess.scored_items$scores
-
-# Look at values
-dat.raw %>%
-  group_by(covid_probable_case_incl_screening) %>% 
-  descr(ess.sum_score_raw,
-        stats = "common"
-        )
-
-```
-
-```{r ESS raw scores by Covid case}
-ess_frequencies <- dat.raw %>%
-  filter(!is.na(startDate.coping)) %>%
-  filter(!is.na(covid_probable_case_incl_screening)) %>%
-  filter(!is.na(ess.sum_score_raw)) %>%
-  group_by(covid_probable_case_incl_screening) %>%
-  count(covid_probable_case_incl_screening, ess.sum_score_raw) %>%
-  mutate(Prop = round(n/sum(n), 2))
-
-kable(ess_frequencies)
-```
-
-ESS scores: Interpretation
-•	0 to 10 = normal range of sleepiness in healthy adults
-•	11 to 14 = mild sleepiness
-•	15 to 17 = moderate sleepiness
-•	18 to 24 = severe sleepiness
-
-```{r ess clinical categories}
+```
+
+```{ESS row sums r}
 dat.raw <- dat.raw %>%
-  mutate(ess.cutoff.scores =
-           case_when(ess.sum_score_raw <= 10 ~ "Normal sleepiness",
-                     ess.sum_score_raw > 10 & ess.sum_score_raw <= 14 ~ "Mild sleepiness",
-                     ess.sum_score_raw > 14 & ess.sum_score_raw <= 17 ~ "Moderate sleepiness",
-                     ess.sum_score_raw > 17 & ess.sum_score_raw <= 24 ~ "Severe sleepiness",
-                     )
-           )
-
-```
-
-```{r ESS clinical categories frequencies}
-ess_frequencies_clinical <- dat.raw %>%
-  filter(!is.na(startDate.coping)) %>%
-  filter(!is.na(covid_probable_case_incl_screening)) %>%
-  filter(!is.na(ess.sum_score_raw)) %>%
-  group_by(covid_probable_case_incl_screening) %>%
-  count(covid_probable_case_incl_screening, ess.cutoff.scores) %>%
-  mutate(Prop = round(n/sum(n), 2))
-
-kable(ess_frequencies_clinical)
-```
-
-# NMSW
-```{r nmsw col names, include = FALSE}
+  mutate(ess.col.names =
+   rowSums(select(.,ess.col.names), na.rm = F)
+   )
+```
+
+```{ESS frequencies r}
+dat.raw %>%
+  filter(!is.na(startDate.coping)) %>%
+  filter(!is.na(covid_probable_case_incl_screening)) %>%
+  filter(!is.na(ess.col.names)) %>%
+  group_by(covid_probable_case_incl_screening) %>%
+  count(covid_probable_case_incl_screening, ess.col.names) %>%
+  mutate(Prop = round(n/sum(n), 2))
+```
+
+```{r nmsw col names}
 nmsw.col.names <- dat.raw %>%
@@
 
-```{r scoring NMSW, include = FALSE}
+```{r scoring NMSW}
 dat.raw <- dat.raw %>% 
@@
 
-```{r select cfs variables, include = FALSE}
+```{r}
 cfs.col.names <- dat.raw %>%
@@
 ```
-
-```{r calculate sum score, include = FALSE}
+```{r}
 dat.raw <- dat.raw %>%
@@
 
-```{r get sum scores by probable Covid}
+```{r}
 dat.raw %>%
@@
 
-CFS cut-off scores require individual symptom-level scores to be binary.
-Script below recodes variables to binary.
-```{r recode cfs variables to binary, include = FALSE}
+```{r}
 dat.raw$cfs.correct_word_find_difficult_binary <- if_else(dat.raw$cfs.correct_word_find_difficult_numeric >= 3, 1,0)
@@
 
-```{r cfs select binary variables, include = FALSE}
+```{r}
 cfs.col.names.bi <- dat.raw %>%
@@
 ```
-
-```{r calculate cfs cut-off groups, include = FALSE}
+```{r}
 dat.raw <- dat.raw %>%
@@
 
-```{r cfs fatigue cases by probable covid}
+```{r}
 dat.raw %>%
@@
 ```
-
-```{r cfs fatigue cases by probable covid by Sample}
-fatigue_by_covid_by_sample <- dat.raw %>%
-  filter(!is.na(startDate.coping)) %>%
-  filter(!is.na(covid_probable_case_incl_screening)) %>%
-  filter(!is.na(cfs.sum_score_case)) %>%
-  group_by(covid_probable_case_incl_screening, Sample) %>%
-  count(covid_probable_case_incl_screening, cfs.sum_score_case) %>%
-  mutate(Prop = round(n/sum(n), 2))
-
-kable(fatigue_by_covid_by_sample)
-```
-
-## Memory
-
-```{r}
-
-```

### 2020-11-05 PANCHANGE_variable_creation.Rmd

--- 2020-11-03 PANCHANGE_variable_creation.Rmd
@@
 ```
-
-Creating variables for subset of participants dependent on when they signed up to GLAD (prepan)
-```{r date variables for subset of participants who signed up in 3, 6, 9 months prior to pandemic}
-# Date of 3 months prior to the 1st of March
-date_3months_prior_march_1st <- as.POSIXct("2019-12-01")
-
-# Date of 6 months prior to the 1st of March
-date_6months_prior_march_1st <- as.POSIXct("2019-09-01")
-
-# Date of 9 months prior to the 1st of March
-date_9months_prior_march_1st <- as.POSIXct("2019-06-01")
-```

### 2020-11-05 PANCHANGE_exclusion_descriptives.Rmd
Corrected the impute and correlations chunks

@@
 
-#SB - Impute no change prepandemic scores
-
-I interpreted the presence of an NA in the retrospective score as an indicator of saying "no change" in their baseline scores.
-Hence, if this was the case, I imputed their baseline score.
-However, this interpretation could be wrong.
-
-Also, I'm not sure what to do if there is an NA for their baseline sum score (nothing to duplicate).
-This was the case for ocir for some reason: the retro scores were provided for some by not the corresponding baseline score?
+#Impute no change prepandemic scores
 
@@
 
-#Edit the gad sum retro score as follows: if there is a missing value in the retro sum score, give it the baseline sum score, else leave it as it is
+#Visualise the gad pandemic feelings variables
+head(dat$gad.pandemic_felt_feelings, 10)
+head(dat$gad.pandemic_felt_feelings_numeric, 10)
+
+#Edit the gad sum retro score as follows: if the pt reports no different since pandemic and there is a missing value for their retro score, impute their baseline score, else if there isn't a missing value for their retro score, leave it as it is.
 
@@
   mutate(gad.sum_score_retro =
-           if_else(is.na(dat$gad.sum_score_retro), dat$gad.sum_score_base, dat$gad.sum_score_retro))
+           case_when(gad.pandemic_felt_feelings == "No different" & is.na(gad.sum_score_retro)                      ~ gad.sum_score_base,
+                     !is.na(gad.sum_score_retro) ~ gad.sum_score_retro))
 
@@
 
-#Edit the phq sum retro score as follows: if there is a missing value in the retro sum score, give it the baseline sum score, else leave it as it is
+#Visualise the phq pandemic feelings variables
+head(dat$phq.pandemic_felt_feelings, 10)
+head(dat$phq.pandemic_felt_feelings_numeric, 10)
+
+#Edit the phq sum retro score as follows: if the pt reports no different since pandemic and there is a missing value for their retro score, impute their baseline score, else if there isn't a missing value for their retro score, leave it as it is.
 
@@
   mutate(phq.sum_score_retro =
-           if_else(is.na(dat$phq.sum_score_retro), dat$phq.sum_score_base, dat$phq.sum_score_retro))
+           case_when(phq.pandemic_felt_feelings == "No different" & is.na(phq.sum_score_retro)                      ~ phq.sum_score_base,
+                     !is.na(phq.sum_score_retro) ~ phq.sum_score_retro))
 
@@
 
-```{r Impute for ocir measure}
-
-#Visualise the ocir summary scores for baseline and retro
-head(dat$ocir.sum_score_base, 40)
-head(dat$ocir.sum_score_retro, 40)
-
-#Edit the ocir sum retro score as follows: if there is a missing value in the retro sum score, give it the baseline sum score, else leave it as it is
-
-impute_dat <- dat %>% 
-  mutate(ocir.sum_score_retro = 
-           if_else(is.na(dat$ocir.sum_score_retro), dat$ocir.sum_score_base,                                     dat$ocir.sum_score_retro))
-
-#Check that the Na's have been replaced with duplicated baseline sum scores
-head(impute_dat$ocir.sum_score_base, 40)
-head(impute_dat$ocir.sum_score_retro, 40)
-
-```
-
-```{r Impute for pcl measure}
-
-#Visualise the pcl summary scores for baseline and retro
-head(dat$pcl.sum_score_base, 30)
-head(dat$pcl.sum_score_retro, 30)
-
-#Edit the pcl sum retro score as follows: if there is a missing value in the retro sum score, give it the baseline sum score, else leave it as it is
-
-impute_dat <- dat %>% 
-  mutate(pcl.sum_score_retro = 
-           if_else(is.na(dat$pcl.sum_score_retro), dat$pcl.sum_score_base, dat$pcl.sum_score_retro))
-
-#Check that the Na's have been replaced with duplicated baseline sum scores
-head(impute_dat$pcl.sum_score_base, 30)
-head(impute_dat$pcl.sum_score_retro, 30)
-
-```
-
-#SB - Baseline survey completion (N per month)
-
-This is a summary of the amount of pt's completing the baseline survey per month
+#Baseline survey completion (N per month)
 
@@
 
-#SB - Correlation between retropsective impute and prepan
+#Correlation between retropsective impute and prepan
 
@@
     "gad.sum_score_retro", 
-    "pcl.sum_score_prepan",
-    "pcl.sum_score_retro",
     "ocir.sum_score_prepan",

### 2020-11-06 PANCHANGE_exclusion_descriptives.Rmd
Created a chunk to look at accuracy of perceived better/worse feeling change due to the pandemic. The code compacts the labels of change into 'Worse', 'No change' and 'Better'. It then looks at the accuracy of perceived change from pre-pandemic to pandemic

--- 2020-11-03 PANCHANGE_exclusion_descriptives.Rmd
@@
   count(depression_and_anxiety_numeric == 1)
+```
+
+#HR
+
+```{r Accuray scores for gad: worse/better than pre-pandemic}
+
+dat.raw$gad.pandemic.change.group <- ifelse(dat.raw$gad.pandemic_felt_feelings_numeric <3,1,
+                                           ifelse(dat.raw$gad.pandemic_felt_feelings_numeric > 3,2,0))
+
+dat.raw$gad.pandemic.change.group <- factor(dat.raw$gad.pandemic.change.group,
+                                           levels = c(1,0,2),labels = c("Worse","No change","Better"))
+
+dat.raw <- dat.raw %>%
+    mutate(gad.change.accurate = case_when(dat.raw$gad.pandemic.change.group == "Better" &
+                                             dat.raw$gad.diff_score_base_prepan < 0 ~1,
+                                           dat.raw$gad.pandemic.change.group == "Worse" &
+                                             dat.raw$gad.diff_score_base_prepan > 0 ~ 1,
+                                           dat.raw$gad.pandemic.change.group == "Better" &
+                                             dat.raw$gad.diff_score_base_prepan > 0 ~ 0,
+                                           dat.raw$gad.pandemic.change.group == "Worse" &
+                                             dat.raw$gad.diff_score_base_prepan < 0 ~ 0))
+
 ```

### 2020-11-06 PANCHANGE_exclusion_descriptives.Rmd
Removed ocir from correlation plot between imputed retro scores and unimputed prepan scores

--- 2020-11-05 PANCHANGE_exclusion_descriptives.Rmd
@@
     "gad.sum_score_retro", 
-    "ocir.sum_score_prepan",
-    "ocir.sum_score_retro",
     "phq.sum_score_prepan",

### 2020-11-06 PANCHANGE_exclusion_descriptives.Rmd
added code to assess accuracy of retro change vs pre_pan change

--- 2020-11-06 PANCHANGE_exclusion_descriptives.Rmd
@@
 
+dat.raw <- dat.raw %>%
+    mutate(gad.change.retro.accurate = if_else(dat.raw$gad.pandemic.change.group == "Better" &
+                                             dat.raw$gad.diff_score_retro_prepan == 0 |
+                                             dat.raw$gad.pandemic.change.group == "Worse" &
+                                             dat.raw$gad.diff_score_retro_prepan == 0, 1, 3 ))
+dat.raw <- dat.raw %>%
+  mutate(gad.change.retro.accurate = if_else(dat.raw$gad.pandemic.change.group == "Better" &
+                                             dat.raw$gad.diff_score_retro_prepan >= -3 &
+                                             dat.raw$gad.diff_score_retro_prepan <= 3 &
+                                             dat.raw$gad.change.retro.accurate_temp != 1 |
+                                             dat.raw$gad.pandemic.change.group == "Worse" &
+                                             dat.raw$gad.diff_score_retro_prepan >= -3 &
+                                             dat.raw$gad.diff_score_retro_prepan <= 3 &
+                                             dat.raw$gad.change.retro.accurate_temp != 1,  2, gad.change.retro.accurate))
+
 ```
@@
 
-#Edit the gad sum retro score as follows: if there is a missing value in the retro sum score, give it the baseline sum score, else leave it as it is
+#Edit the gad sum retro score as follows: if there is a missing value in the retro sum s0core, give it the baseline sum score, else leave it as it is
 

### 2020-11-06 PANCHANGE_analysis.Rmd

--- 2020-11-03 PANCHANGE_analysis.Rmd
@@
 
-Sensitivity analysis for individuals who signed up to GLAD (prepan) either 3, 6 or 9 months before the pendemic began. 
-```{r subsample for pre-pan sensitivity analysis}
-# Participants who signed up in the three months before the pandemic began
-dat.prepan_sensitivity_3months <- dat %>%
-  filter(
-    ((data_group_gad == "Baseline and retrospective data" |
-      data_group_gad == "Prepandemic and baseline data" |
-      data_group_gad == "All prepandemic, baseline and retrospective data") |
-      (data_group_phq == "Baseline and retrospective data" |
-      data_group_phq == "Prepandemic and baseline data" |
-      data_group_phq == "All prepandemic, baseline and retrospective data") |
-      (data_group_pcl == "Baseline and retrospective data" |
-      data_group_pcl == "Prepandemic and baseline data" |
-      data_group_pcl == "All prepandemic, baseline and retrospective data") |
-      (data_group_ocir == "Baseline and retrospective data" |
-      data_group_ocir == "Prepandemic and baseline data" |
-      data_group_ocir == "All prepandemic, baseline and retrospective data")) &
-      prepandemic_3_months_numeric == 1 # Only participants who signed up between December 1st 2019 and March 1st 2020
-  )
-
-# Participants who signed up in the three months before the pandemic began
-dat.prepan_sensitivity_6months <- dat %>%
-  filter(
-    ((data_group_gad == "Baseline and retrospective data" |
-      data_group_gad == "Prepandemic and baseline data" |
-      data_group_gad == "All prepandemic, baseline and retrospective data") |
-      (data_group_phq == "Baseline and retrospective data" |
-      data_group_phq == "Prepandemic and baseline data" |
-      data_group_phq == "All prepandemic, baseline and retrospective data") |
-      (data_group_pcl == "Baseline and retrospective data" |
-      data_group_pcl == "Prepandemic and baseline data" |
-      data_group_pcl == "All prepandemic, baseline and retrospective data") |
-      (data_group_ocir == "Baseline and retrospective data" |
-      data_group_ocir == "Prepandemic and baseline data" |
-      data_group_ocir == "All prepandemic, baseline and retrospective data")) &
-      prepandemic_6_months_numeric == 1 # Only participants who signed up between September 1st 2019 and March 1st 2020
-  )
-
-# Participants who signed up in the three months before the pandemic began
-dat.prepan_sensitivity_9months <- dat %>%
-  filter(
-    ((data_group_gad == "Baseline and retrospective data" |
-      data_group_gad == "Prepandemic and baseline data" |
-      data_group_gad == "All prepandemic, baseline and retrospective data") |
-      (data_group_phq == "Baseline and retrospective data" |
-      data_group_phq == "Prepandemic and baseline data" |
-      data_group_phq == "All prepandemic, baseline and retrospective data") |
-      (data_group_pcl == "Baseline and retrospective data" |
-      data_group_pcl == "Prepandemic and baseline data" |
-      data_group_pcl == "All prepandemic, baseline and retrospective data") |
-      (data_group_ocir == "Baseline and retrospective data" |
-      data_group_ocir == "Prepandemic and baseline data" |
-      data_group_ocir == "All prepandemic, baseline and retrospective data")) &
-      prepandemic_9_months_numeric == 1 # Only participants who signed up between June 1st 2019 and March 1st 2020
-  )
-
-```
-
 2. Regression models (Regress covariates out of the change? Which?)
@@
 ```
-# GAD prepan: sensitivity
-## Regression: Absolute scores
-### Model 1b: Overlapping disorders, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
-#### Subset of participants 3 months prior to pandemic
-```{r gad model1b sum_score prepan - sensitivity 3 months}
-# Regression coefficients
-gad_prepan_model1b_explan_estimates <- model1b.explan.estimates(outcome = "gad.sum_score_base",
-                         explan_var = "gad.sum_score_prepan",
-                         data_set = "dat.prepan_sensitivity_3months")
-kable(gad_prepan_model1b_explan_estimates)
-gad_prepan_model1b_explan_estimates
-
-# Regression diagnostic statistics
-gad_prepan_model1b_explan_reg_stats <- model1b.explan.reg.stats(outcome = "gad.sum_score_base",
-                         explan_var = "gad.sum_score_prepan",
-                         data_set = "dat.prepan_sensitivity_3months")
-kable(gad_prepan_model1b_explan_reg_stats)
-gad_prepan_model1b_explan_reg_stats
-```
-
-#### Subset of participants 6 months prior to pandemic
-```{r gad model1b sum_score prepan - sensitivity 6 months}
-# Regression coefficients
-gad_prepan_model1b_explan_estimates <- model1b.explan.estimates(outcome = "gad.sum_score_base",
-                         explan_var = "gad.sum_score_prepan",
-                         data_set = "dat.prepan_sensitivity_6months")
-kable(gad_prepan_model1b_explan_estimates)
-gad_prepan_model1b_explan_estimates
-
-# Regression diagnostic statistics
-gad_prepan_model1b_explan_reg_stats <- model1b.explan.reg.stats(outcome = "gad.sum_score_base",
-                         explan_var = "gad.sum_score_prepan",
-                         data_set = "dat.prepan_sensitivity_6months")
-kable(gad_prepan_model1b_explan_reg_stats)
-gad_prepan_model1b_explan_reg_stats
-```
-
-#### Subset of participants 9 months prior to pandemic
-```{r gad model1b sum_score prepan - sensitivity 9 months}
-# Regression coefficients
-gad_prepan_model1b_explan_estimates <- model1b.explan.estimates(outcome = "gad.sum_score_base",
-                         explan_var = "gad.sum_score_prepan",
-                         data_set = "dat.prepan_sensitivity_9months")
-kable(gad_prepan_model1b_explan_estimates)
-gad_prepan_model1b_explan_estimates
-
-# Regression diagnostic statistics
-gad_prepan_model1b_explan_reg_stats <- model1b.explan.reg.stats(outcome = "gad.sum_score_base",
-                         explan_var = "gad.sum_score_prepan",
-                         data_set = "dat.prepan_sensitivity_9months")
-kable(gad_prepan_model1b_explan_reg_stats)
-gad_prepan_model1b_explan_reg_stats
-```
-##KT
 
@@
 ```
-# PHQ prepan: sensitivity
-## Regression: Absolute scores
-### Model 1b: Overlapping disorders, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
-#### Subset of participants 3 months prior to pandemic
-```{r phq model1b sum_score prepan - sensitivity 3 months}
-# Regression coefficients
-phq_prepan_model1b_explan_estimates <- model1b.explan.estimates(outcome = "phq.sum_score_base",
-                         explan_var = "phq.sum_score_prepan",
-                         data_set = "dat.prepan_sensitivity_3months")
-kable(phq_prepan_model1b_explan_estimates)
-phq_prepan_model1b_explan_estimates
-
-# Regression diagnostic statistics
-phq_prepan_model1b_explan_reg_stats <- model1b.explan.reg.stats(outcome = "phq.sum_score_base",
-                         explan_var = "phq.sum_score_prepan",
-                         data_set = "dat.prepan_sensitivity_3months")
-kable(phq_prepan_model1b_explan_reg_stats)
-phq_prepan_model1b_explan_reg_stats
-```
-
-#### Subset of participants 6 months prior to pandemic
-```{r phq model1b sum_score prepan - sensitivity 6 months}
-# Regression coefficients
-phq_prepan_model1b_explan_estimates <- model1b.explan.estimates(outcome = "phq.sum_score_base",
-                         explan_var = "phq.sum_score_prepan",
-                         data_set = "dat.prepan_sensitivity_6months")
-kable(phq_prepan_model1b_explan_estimates)
-phq_prepan_model1b_explan_estimates
-
-# Regression diagnostic statistics
-phq_prepan_model1b_explan_reg_stats <- model1b.explan.reg.stats(outcome = "phq.sum_score_base",
-                         explan_var = "phq.sum_score_prepan",
-                         data_set = "dat.prepan_sensitivity_6months")
-kable(phq_prepan_model1b_explan_reg_stats)
-phq_prepan_model1b_explan_reg_stats
-```
-
-#### Subset of participants 9 months prior to pandemic
-```{r phq model1b sum_score prepan - sensitivity 9 months}
-# Regression coefficients
-phq_prepan_model1b_explan_estimates <- model1b.explan.estimates(outcome = "phq.sum_score_base",
-                         explan_var = "phq.sum_score_prepan",
-                         data_set = "dat.prepan_sensitivity_9months")
-kable(phq_prepan_model1b_explan_estimates)
-phq_prepan_model1b_explan_estimates
-
-# Regression diagnostic statistics
-phq_prepan_model1b_explan_reg_stats <- model1b.explan.reg.stats(outcome = "phq.sum_score_base",
-                         explan_var = "phq.sum_score_prepan",
-                         data_set = "dat.prepan_sensitivity_9months")
-kable(phq_prepan_model1b_explan_reg_stats)
-phq_prepan_model1b_explan_reg_stats
-```
 
@@
 
-# PCL prepan: sensitivity
+# SENSITIVITY based on highest level of education
+
+# GAD prepan
 ## Regression: Absolute scores
+### Model 0a: Disorder_hierarchical, Unadjusted
+```{r gad education sensitivity model0a sum_score prepan}
+# Regression coefficients
+gad_prepan_model0a_education_estimates <- model0a.explan.estimates(outcome = "gad.sum_score_base",
+                         explan_var = "highest_education_numeric",
+                         data_set = "dat.prepan")
+kable(gad_prepan_model0a_education_estimates)
+gad_prepan_model0a_education_estimates
+
+# Regression diagnostic statistics
+gad_prepan_model0a_education_reg_stats <- model0a.explan.reg.stats(outcome = "gad.sum_score_base",
+                         explan_var = "highest_education_numeric",
+                         data_set = "dat.prepan")
+kable(gad_prepan_model0a_education_reg_stats)
+gad_prepan_model0a_education_reg_stats
+```
+
+### Model 0b: Overlapping disorders, Unadjusted
+```{r gad education sensitivity model0b sum_score prepan}
+# Regression coefficients
+gad_prepan_model0b_education_estimates <- model0b.explan.estimates(outcome = "gad.sum_score_base",
+                         explan_var = "highest_education_numeric",
+                         data_set = "dat.prepan")
+kable(gad_prepan_model0b_education_estimates)
+gad_prepan_model0b_education_estimates
+
+# Regression diagnostic statistics
+gad_prepan_model0b_education_reg_stats <- model0b.explan.reg.stats(outcome = "gad.sum_score_base",
+                         explan_var = "highest_education_numeric",
+                         data_set = "dat.prepan")
+kable(gad_prepan_model0b_education_reg_stats)
+gad_prepan_model0b_education_reg_stats
+```
+
+### Model 1a: Disorder hierarchical, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r gad education sensitivity model1a sum_score prepan}
+# Regression coefficients
+gad_prepan_model1a_education_estimates <- model1a.explan.estimates(outcome = "gad.sum_score_base",
+                         explan_var = "highest_education_numeric",
+                         data_set = "dat.prepan")
+kable(gad_prepan_model1a_education_estimates)
+gad_prepan_model1a_education_estimates
+
+# Regression diagnostic statistics
+gad_prepan_model1a_education_reg_stats <- model1a.explan.reg.stats(outcome = "gad.sum_score_base",
+                         explan_var = "highest_education_numeric",
+                         data_set = "dat.prepan")
+kable(gad_prepan_model1a_education_reg_stats)
+gad_prepan_model1a_education_reg_stats
+```
+
 ### Model 1b: Overlapping disorders, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
-#### Subset of participants 3 months prior to pandemic
-```{r pcl model1b sum_score prepan - sensitivity 3 months}
-# Regression coefficients
-pcl_prepan_model1b_explan_estimates <- model1b.explan.estimates(outcome = "pcl.sum_score_base",
-                         explan_var = "pcl.sum_score_prepan",
-                         data_set = "dat.prepan_sensitivity_3months")
-kable(pcl_prepan_model1b_explan_estimates)
-pcl_prepan_model1b_explan_estimates
-
-# Regression diagnostic statistics
-pcl_prepan_model1b_explan_reg_stats <- model1b.explan.reg.stats(outcome = "pcl.sum_score_base",
-                         explan_var = "pcl.sum_score_prepan",
-                         data_set = "dat.prepan_sensitivity_3months")
-kable(pcl_prepan_model1b_explan_reg_stats)
-pcl_prepan_model1b_explan_reg_stats
-```
-
-#### Subset of participants 6 months prior to pandemic
-```{r pcl model1b sum_score prepan - sensitivity 6 months}
-# Regression coefficients
-pcl_prepan_model1b_explan_estimates <- model1b.explan.estimates(outcome = "pcl.sum_score_base",
-                         explan_var = "pcl.sum_score_prepan",
-                         data_set = "dat.prepan_sensitivity_6months")
-kable(pcl_prepan_model1b_explan_estimates)
-pcl_prepan_model1b_explan_estimates
-
-# Regression diagnostic statistics
-pcl_prepan_model1b_explan_reg_stats <- model1b.explan.reg.stats(outcome = "pcl.sum_score_base",
-                         explan_var = "pcl.sum_score_prepan",
-                         data_set = "dat.prepan_sensitivity_6months")
-kable(pcl_prepan_model1b_explan_reg_stats)
-pcl_prepan_model1b_explan_reg_stats
-```
-
-#### Subset of participants 9 months prior to pandemic
-```{r pcl model1b sum_score prepan - sensitivity 9 months}
-# Regression coefficients
-pcl_prepan_model1b_explan_estimates <- model1b.explan.estimates(outcome = "pcl.sum_score_base",
-                         explan_var = "pcl.sum_score_prepan",
-                         data_set = "dat.prepan_sensitivity_9months")
-kable(pcl_prepan_model1b_explan_estimates)
-pcl_prepan_model1b_explan_estimates
-
-# Regression diagnostic statistics
-pcl_prepan_model1b_explan_reg_stats <- model1b.explan.reg.stats(outcome = "pcl.sum_score_base",
-                         explan_var = "pcl.sum_score_prepan",
-                         data_set = "dat.prepan_sensitivity_9months")
-kable(pcl_prepan_model1b_explan_reg_stats)
-pcl_prepan_model1b_explan_reg_stats
-```
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r gad education sensitivity model1b sum_score prepan}
+# Regression coefficients
+gad_prepan_model1b_education_estimates <- model1b.explan.estimates(outcome = "gad.sum_score_base",
+                         explan_var = "highest_education_numeric",
+                         data_set = "dat.prepan")
+kable(gad_prepan_model1b_education_estimates)
+gad_prepan_model1b_education_estimates
+
+# Regression diagnostic statistics
+gad_prepan_model1b_education_reg_stats <- model1b.explan.reg.stats(outcome = "gad.sum_score_base",
+                         explan_var = "highest_education_numeric",
+                         data_set = "dat.prepan")
+kable(gad_prepan_model1b_education_reg_stats)
+gad_prepan_model1b_education_reg_stats
+```
+
+# PHQ prepan
+## Regression: Absolute scores
+### Model 0a: Disorder_hierarchical, Unadjusted
+```{r phq education sensitivity model0a sum_score prepan}
+# Regression coefficients
+phq_prepan_model0a_education_estimates <- model0a.explan.estimates(outcome = "phq.sum_score_base",
+                         explan_var = "highest_education_numeric",
+                         data_set = "dat.prepan")
+kable(phq_prepan_model0a_education_estimates)
+phq_prepan_model0a_education_estimates
+
+# Regression diagnostic statistics
+phq_prepan_model0a_education_reg_stats <- model0a.explan.reg.stats(outcome = "phq.sum_score_base",
+                         explan_var = "highest_education_numeric",
+                         data_set = "dat.prepan")
+kable(phq_prepan_model0a_education_reg_stats)
+phq_prepan_model0a_education_reg_stats
+```
+
+### Model 0b: Overlapping disorders, Unadjusted
+```{r phq education sensitivity model0b sum_score prepan}
+# Regression coefficients
+phq_prepan_model0b_education_estimates <- model0b.explan.estimates(outcome = "phq.sum_score_base",
+                         explan_var = "highest_education_numeric",
+                         data_set = "dat.prepan")
+kable(phq_prepan_model0b_education_estimates)
+phq_prepan_model0b_education_estimates
+
+# Regression diagnostic statistics
+phq_prepan_model0b_education_reg_stats <- model0b.explan.reg.stats(outcome = "phq.sum_score_base",
+                         explan_var = "highest_education_numeric",
+                         data_set = "dat.prepan")
+kable(phq_prepan_model0b_education_reg_stats)
+phq_prepan_model0b_education_reg_stats
+```
+
+### Model 1a: Disorder hierarchical, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r phq education sensitivity model1a sum_score prepan}
+# Regression coefficients
+phq_prepan_model1a_education_estimates <- model1a.explan.estimates(outcome = "phq.sum_score_base",
+                         explan_var = "highest_education_numeric",
+                         data_set = "dat.prepan")
+kable(phq_prepan_model1a_education_estimates)
+phq_prepan_model1a_education_estimates
+
+# Regression diagnostic statistics
+phq_prepan_model1a_education_reg_stats <- model1a.explan.reg.stats(outcome = "phq.sum_score_base",
+                         explan_var = "highest_education_numeric",
+                         data_set = "dat.prepan")
+kable(phq_prepan_model1a_education_reg_stats)
+phq_prepan_model1a_education_reg_stats
+```
+
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r phq education sensitivity model1b sum_score prepan}
+# Regression coefficients
+phq_prepan_model1b_education_estimates <- model1b.explan.estimates(outcome = "phq.sum_score_base",
+                         explan_var = "highest_education_numeric",
+                         data_set = "dat.prepan")
+kable(phq_prepan_model1b_education_estimates)
+phq_prepan_model1b_education_estimates
+
+# Regression diagnostic statistics
+phq_prepan_model1b_education_reg_stats <- model1b.explan.reg.stats(outcome = "phq.sum_score_base",
+                         explan_var = "highest_education_numeric",
+                         data_set = "dat.prepan")
+kable(phq_prepan_model1b_education_reg_stats)
+phq_prepan_model1b_education_reg_stats
+```
+
+# OCIR prepan 
+## Regression: Absolute scores
+### Model 0a: Disorder_hierarchical, Unadjusted
+```{r ocir education sensitivity model0a sum_score prepan}
+# Regression coefficients
+ocir_prepan_model0a_education_estimates <- model0a.explan.estimates(outcome = "ocir.sum_score_base",
+                         explan_var = "highest_education_numeric",
+                         data_set = "dat.prepan")
+kable(ocir_prepan_model0a_education_estimates)
+ocir_prepan_model0a_education_estimates
+
+# Regression diagnostic statistics
+ocir_prepan_model0a_education_reg_stats <- model0a.explan.reg.stats(outcome = "ocir.sum_score_base",
+                         explan_var = "highest_education_numeric",
+                         data_set = "dat.prepan")
+kable(ocir_prepan_model0a_education_reg_stats)
+ocir_prepan_model0a_education_reg_stats
+```
+
+### Model 0b: Overlapping disorders, Unadjusted
+```{r ocir education sensitivity model0b sum_score prepan}
+# Regression coefficients
+ocir_prepan_model0b_education_estimates <- model0b.explan.estimates(outcome = "ocir.sum_score_base",
+                         explan_var = "highest_education_numeric",
+                         data_set = "dat.prepan")
+kable(ocir_prepan_model0b_education_estimates)
+ocir_prepan_model0b_education_estimates
+
+# Regression diagnostic statistics
+ocir_prepan_model0b_education_reg_stats <- model0b.explan.reg.stats(outcome = "ocir.sum_score_base",
+                         explan_var = "highest_education_numeric",
+                         data_set = "dat.prepan")
+kable(ocir_prepan_model0b_education_reg_stats)
+ocir_prepan_model0b_education_reg_stats
+```
+
+### Model 1a: Disorder hierarchical, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r ocir education sensitivity model1a sum_score prepan}
+# Regression coefficients
+ocir_prepan_model1a_education_estimates <- model1a.explan.estimates(outcome = "ocir.sum_score_base",
+                         explan_var = "highest_education_numeric",
+                         data_set = "dat.prepan")
+kable(ocir_prepan_model1a_education_estimates)
+ocir_prepan_model1a_education_estimates
+
+# Regression diagnostic statistics
+ocir_prepan_model1a_education_reg_stats <- model1a.explan.reg.stats(outcome = "ocir.sum_score_base",
+                         explan_var = "highest_education_numeric",
+                         data_set = "dat.prepan")
+kable(ocir_prepan_model1a_education_reg_stats)
+ocir_prepan_model1a_education_reg_stats
+```
+
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r ocir education sensitivity model1b sum_score prepan}
+# Regression coefficients
+ocir_prepan_model1b_education_estimates <- model1b.explan.estimates(outcome = "ocir.sum_score_base",
+                         explan_var = "highest_education_numeric",
+                         data_set = "dat.prepan")
+kable(ocir_prepan_model1b_education_estimates)
+ocir_prepan_model1b_education_estimates
+
+# Regression diagnostic statistics
+ocir_prepan_model1b_education_reg_stats <- model1b.explan.reg.stats(outcome = "ocir.sum_score_base",
+                         explan_var = "highest_education_numeric",
+                         data_set = "dat.prepan")
+kable(ocir_prepan_model1b_education_reg_stats)
+ocir_prepan_model1b_education_reg_stats
+```
+
+#PCL prepan 
+## Regression: Absolute scores
+### Model 0a: Disorder_hierarchical, Unadjusted
+```{r pcl education sensitivty model0a sum_score prepan}
+# Regression coefficients
+pcl_prepan_model0a_education_estimates <- model0a.explan.estimates(outcome = "pcl.sum_score_base",
+                         explan_var = "highest_education_numeric",
+                         data_set = "dat.prepan")
+kable(pcl_prepan_model0a_education_estimates)
+pcl_prepan_model0a_education_estimates
+
+# Regression diagnostic statistics
+pcl_prepan_model0a_education_reg_stats <- model0a.explan.reg.stats(outcome = "pcl.sum_score_base",
+                         explan_var = "highest_education_numeric",
+                         data_set = "dat.prepan")
+kable(pcl_prepan_model0a_education_reg_stats)
+pcl_prepan_model0a_education_reg_stats
+```
+
+### Model 0b: Overlapping disorders, Unadjusted
+```{r pcl education sensitivty model0b sum_score prepan}
+# Regression coefficients
+pcl_prepan_model0b_education_estimates <- model0b.explan.estimates(outcome = "pcl.sum_score_base",
+                         explan_var = "highest_education_numeric",
+                         data_set = "dat.prepan")
+kable(pcl_prepan_model0b_education_estimates)
+pcl_prepan_model0b_education_estimates
+
+# Regression diagnostic statistics
+pcl_prepan_model0b_education_reg_stats <- model0b.explan.reg.stats(outcome = "pcl.sum_score_base",
+                         explan_var = "highest_education_numeric",
+                         data_set = "dat.prepan")
+kable(pcl_prepan_model0b_education_reg_stats)
+pcl_prepan_model0b_education_reg_stats
+```
+
+### Model 1a: Disorder hierarchical, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r pcl education sensitivty model1a sum_score prepan}
+# Regression coefficients
+pcl_prepan_model1a_education_estimates <- model1a.explan.estimates(outcome = "pcl.sum_score_base",
+                         explan_var = "highest_education_numeric",
+                         data_set = "dat.prepan")
+kable(pcl_prepan_model1a_education_estimates)
+pcl_prepan_model1a_education_estimates
+
+# Regression diagnostic statistics
+pcl_prepan_model1a_education_reg_stats <- model1a.explan.reg.stats(outcome = "pcl.sum_score_base",
+                         explan_var = "highest_education_numeric",
+                         data_set = "dat.prepan")
+kable(pcl_prepan_model1a_education_reg_stats)
+pcl_prepan_model1a_education_reg_stats
+```
+
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r pcl education sensitivty model1b sum_score prepan}
+# Regression coefficients
+pcl_prepan_model1b_education_estimates <- model1b.explan.estimates(outcome = "pcl.sum_score_base",
+                         explan_var = "highest_education_numeric",
+                         data_set = "dat.prepan")
+kable(pcl_prepan_model1b_education_estimates)
+pcl_prepan_model1b_education_estimates
+
+# Regression diagnostic statistics
+pcl_prepan_model1b_education_reg_stats <- model1b.explan.reg.stats(outcome = "pcl.sum_score_base",
+                         explan_var = "highest_education_numeric",
+                         data_set = "dat.prepan")
+kable(pcl_prepan_model1b_education_reg_stats)
+pcl_prepan_model1b_education_reg_stats
+```
+
+# SENSITIVITY based on employment status
+
+# GAD prepan
+## Regression: Absolute scores
+### Model 0a: Disorder_hierarchical, Unadjusted
+```{r gad employment sensitivity model0a sum_score prepan}
+# Regression coefficients
+gad_prepan_model0a_employment_estimates <- model0a.explan.estimates(outcome = "gad.sum_score_base",
+                         explan_var = "employment.unemployed_numeric",
+                         data_set = "dat.prepan")
+kable(gad_prepan_model0a_employment_estimates)
+gad_prepan_model0a_employment_estimates
+
+# Regression diagnostic statistics
+gad_prepan_model0a_employment_reg_stats <- model0a.explan.reg.stats(outcome = "gad.sum_score_base",
+                         explan_var = "employment.unemployed_numeric",
+                         data_set = "dat.prepan")
+kable(gad_prepan_model0a_employment_reg_stats)
+gad_prepan_model0a_employment_reg_stats
+```
+
+### Model 0b: Overlapping disorders, Unadjusted
+```{r gad employment sensitivity model0b sum_score prepan}
+# Regression coefficients
+gad_prepan_model0b_employment_estimates <- model0b.explan.estimates(outcome = "gad.sum_score_base",
+                         explan_var = "employment.unemployed_numeric",
+                         data_set = "dat.prepan")
+kable(gad_prepan_model0b_employment_estimates)
+gad_prepan_model0b_employment_estimates
+
+# Regression diagnostic statistics
+gad_prepan_model0b_employment_reg_stats <- model0b.explan.reg.stats(outcome = "gad.sum_score_base",
+                         explan_var = "employment.unemployed_numeric",
+                         data_set = "dat.prepan")
+kable(gad_prepan_model0b_employment_reg_stats)
+gad_prepan_model0b_employment_reg_stats
+```
+
+### Model 1a: Disorder hierarchical, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r gad employment sensitivity model1a sum_score prepan}
+# Regression coefficients
+gad_prepan_model1a_employment_estimates <- model1a.explan.estimates(outcome = "gad.sum_score_base",
+                         explan_var = "employment.unemployed_numeric",
+                         data_set = "dat.prepan")
+kable(gad_prepan_model1a_employment_estimates)
+gad_prepan_model1a_employment_estimates
+
+# Regression diagnostic statistics
+gad_prepan_model1a_employment_reg_stats <- model1a.explan.reg.stats(outcome = "gad.sum_score_base",
+                         explan_var = "employment.unemployed_numeric",
+                         data_set = "dat.prepan")
+kable(gad_prepan_model1a_employment_reg_stats)
+gad_prepan_model1a_employment_reg_stats
+```
+
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r gad employment sensitivity model1b sum_score prepan}
+# Regression coefficients
+gad_prepan_model1b_employment_estimates <- model1b.explan.estimates(outcome = "gad.sum_score_base",
+                         explan_var = "employment.unemployed_numeric",
+                         data_set = "dat.prepan")
+kable(gad_prepan_model1b_employment_estimates)
+gad_prepan_model1b_employment_estimates
+
+# Regression diagnostic statistics
+gad_prepan_model1b_employment_reg_stats <- model1b.explan.reg.stats(outcome = "gad.sum_score_base",
+                         explan_var = "employment.unemployed_numeric",
+                         data_set = "dat.prepan")
+kable(gad_prepan_model1b_employment_reg_stats)
+gad_prepan_model1b_employment_reg_stats
+```
+
+# PHQ prepan
+## Regression: Absolute scores
+### Model 0a: Disorder_hierarchical, Unadjusted
+```{r phq employment sensitivity model0a sum_score prepan}
+# Regression coefficients
+phq_prepan_model0a_employment_estimates <- model0a.explan.estimates(outcome = "phq.sum_score_base",
+                         explan_var = "employment.unemployed_numeric",
+                         data_set = "dat.prepan")
+kable(phq_prepan_model0a_employment_estimates)
+phq_prepan_model0a_employment_estimates
+
+# Regression diagnostic statistics
+phq_prepan_model0a_employment_reg_stats <- model0a.explan.reg.stats(outcome = "phq.sum_score_base",
+                         explan_var = "employment.unemployed_numeric",
+                         data_set = "dat.prepan")
+kable(phq_prepan_model0a_employment_reg_stats)
+phq_prepan_model0a_employment_reg_stats
+```
+
+### Model 0b: Overlapping disorders, Unadjusted
+```{r phq employment sensitivity model0b sum_score prepan}
+# Regression coefficients
+phq_prepan_model0b_employment_estimates <- model0b.explan.estimates(outcome = "phq.sum_score_base",
+                         explan_var = "employment.unemployed_numeric",
+                         data_set = "dat.prepan")
+kable(phq_prepan_model0b_employment_estimates)
+phq_prepan_model0b_employment_estimates
+
+# Regression diagnostic statistics
+phq_prepan_model0b_employment_reg_stats <- model0b.explan.reg.stats(outcome = "phq.sum_score_base",
+                         explan_var = "employment.unemployed_numeric",
+                         data_set = "dat.prepan")
+kable(phq_prepan_model0b_employment_reg_stats)
+phq_prepan_model0b_employment_reg_stats
+```
+
+### Model 1a: Disorder hierarchical, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r phq employment sensitivity model1a sum_score prepan}
+# Regression coefficients
+phq_prepan_model1a_employment_estimates <- model1a.explan.estimates(outcome = "phq.sum_score_base",
+                         explan_var = "employment.unemployed_numeric",
+                         data_set = "dat.prepan")
+kable(phq_prepan_model1a_employment_estimates)
+phq_prepan_model1a_employment_estimates
+
+# Regression diagnostic statistics
+phq_prepan_model1a_employment_reg_stats <- model1a.explan.reg.stats(outcome = "phq.sum_score_base",
+                         explan_var = "employment.unemployed_numeric",
+                         data_set = "dat.prepan")
+kable(phq_prepan_model1a_employment_reg_stats)
+phq_prepan_model1a_employment_reg_stats
+```
+
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r phq employment sensitivity model1b sum_score prepan}
+# Regression coefficients
+phq_prepan_model1b_employment_estimates <- model1b.explan.estimates(outcome = "phq.sum_score_base",
+                         explan_var = "employment.unemployed_numeric",
+                         data_set = "dat.prepan")
+kable(phq_prepan_model1b_employment_estimates)
+phq_prepan_model1b_employment_estimates
+
+# Regression diagnostic statistics
+phq_prepan_model1b_employment_reg_stats <- model1b.explan.reg.stats(outcome = "phq.sum_score_base",
+                         explan_var = "employment.unemployed_numeric",
+                         data_set = "dat.prepan")
+kable(phq_prepan_model1b_employment_reg_stats)
+phq_prepan_model1b_employment_reg_stats
+```
+
+# OCIR prepan 
+## Regression: Absolute scores
+### Model 0a: Disorder_hierarchical, Unadjusted
+```{r ocir employment sensitivity model0a sum_score prepan}
+# Regression coefficients
+ocir_prepan_model0a_employment_estimates <- model0a.explan.estimates(outcome = "ocir.sum_score_base",
+                         explan_var = "employment.unemployed_numeric",
+                         data_set = "dat.prepan")
+kable(ocir_prepan_model0a_employment_estimates)
+ocir_prepan_model0a_employment_estimates
+
+# Regression diagnostic statistics
+ocir_prepan_model0a_employment_reg_stats <- model0a.explan.reg.stats(outcome = "ocir.sum_score_base",
+                         explan_var = "employment.unemployed_numeric",
+                         data_set = "dat.prepan")
+kable(ocir_prepan_model0a_employment_reg_stats)
+ocir_prepan_model0a_employment_reg_stats
+```
+
+### Model 0b: Overlapping disorders, Unadjusted
+```{r ocir employment sensitivity model0b sum_score prepan}
+# Regression coefficients
+ocir_prepan_model0b_employment_estimates <- model0b.explan.estimates(outcome = "ocir.sum_score_base",
+                         explan_var = "employment.unemployed_numeric",
+                         data_set = "dat.prepan")
+kable(ocir_prepan_model0b_employment_estimates)
+ocir_prepan_model0b_employment_estimates
+
+# Regression diagnostic statistics
+ocir_prepan_model0b_employment_reg_stats <- model0b.explan.reg.stats(outcome = "ocir.sum_score_base",
+                         explan_var = "employment.unemployed_numeric",
+                         data_set = "dat.prepan")
+kable(ocir_prepan_model0b_employment_reg_stats)
+ocir_prepan_model0b_employment_reg_stats
+```
+
+### Model 1a: Disorder hierarchical, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r ocir employment sensitivity model1a sum_score prepan}
+# Regression coefficients
+ocir_prepan_model1a_employment_estimates <- model1a.explan.estimates(outcome = "ocir.sum_score_base",
+                         explan_var = "employment.unemployed_numeric",
+                         data_set = "dat.prepan")
+kable(ocir_prepan_model1a_employment_estimates)
+ocir_prepan_model1a_employment_estimates
+
+# Regression diagnostic statistics
+ocir_prepan_model1a_employment_reg_stats <- model1a.explan.reg.stats(outcome = "ocir.sum_score_base",
+                         explan_var = "employment.unemployed_numeric",
+                         data_set = "dat.prepan")
+kable(ocir_prepan_model1a_employment_reg_stats)
+ocir_prepan_model1a_employment_reg_stats
+```
+
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r ocir employment sensitivity model1b sum_score prepan}
+# Regression coefficients
+ocir_prepan_model1b_employment_estimates <- model1b.explan.estimates(outcome = "ocir.sum_score_base",
+                         explan_var = "employment.unemployed_numeric",
+                         data_set = "dat.prepan")
+kable(ocir_prepan_model1b_employment_estimates)
+ocir_prepan_model1b_employment_estimates
+
+# Regression diagnostic statistics
+ocir_prepan_model1b_employment_reg_stats <- model1b.explan.reg.stats(outcome = "ocir.sum_score_base",
+                         explan_var = "employment.unemployed_numeric",
+                         data_set = "dat.prepan")
+kable(ocir_prepan_model1b_employment_reg_stats)
+ocir_prepan_model1b_employment_reg_stats
+```
+
+#PCL prepan 
+## Regression: Absolute scores
+### Model 0a: Disorder_hierarchical, Unadjusted
+```{r pcl employment sensitivty model0a sum_score prepan}
+# Regression coefficients
+pcl_prepan_model0a_employment_estimates <- model0a.explan.estimates(outcome = "pcl.sum_score_base",
+                         explan_var = "employment.unemployed_numeric",
+                         data_set = "dat.prepan")
+kable(pcl_prepan_model0a_employment_estimates)
+pcl_prepan_model0a_employment_estimates
+
+# Regression diagnostic statistics
+pcl_prepan_model0a_employment_reg_stats <- model0a.explan.reg.stats(outcome = "pcl.sum_score_base",
+                         explan_var = "employment.unemployed_numeric",
+                         data_set = "dat.prepan")
+kable(pcl_prepan_model0a_employment_reg_stats)
+pcl_prepan_model0a_employment_reg_stats
+```
+
+### Model 0b: Overlapping disorders, Unadjusted
+```{r pcl employment sensitivty model0b sum_score prepan}
+# Regression coefficients
+pcl_prepan_model0b_employment_estimates <- model0b.explan.estimates(outcome = "pcl.sum_score_base",
+                         explan_var = "employment.unemployed_numeric",
+                         data_set = "dat.prepan")
+kable(pcl_prepan_model0b_employment_estimates)
+pcl_prepan_model0b_employment_estimates
+
+# Regression diagnostic statistics
+pcl_prepan_model0b_employment_reg_stats <- model0b.explan.reg.stats(outcome = "pcl.sum_score_base",
+                         explan_var = "employment.unemployed_numeric",
+                         data_set = "dat.prepan")
+kable(pcl_prepan_model0b_employment_reg_stats)
+pcl_prepan_model0b_employment_reg_stats
+```
+
+### Model 1a: Disorder hierarchical, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r pcl employment sensitivty model1a sum_score prepan}
+# Regression coefficients
+pcl_prepan_model1a_employment_estimates <- model1a.explan.estimates(outcome = "pcl.sum_score_base",
+                         explan_var = "employment.unemployed_numeric",
+                         data_set = "dat.prepan")
+kable(pcl_prepan_model1a_employment_estimates)
+pcl_prepan_model1a_employment_estimates
+
+# Regression diagnostic statistics
+pcl_prepan_model1a_employment_reg_stats <- model1a.explan.reg.stats(outcome = "pcl.sum_score_base",
+                         explan_var = "employment.unemployed_numeric",
+                         data_set = "dat.prepan")
+kable(pcl_prepan_model1a_employment_reg_stats)
+pcl_prepan_model1a_employment_reg_stats
+```
+
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r pcl employment sensitivty model1b sum_score prepan}
+# Regression coefficients
+pcl_prepan_model1b_employment_estimates <- model1b.explan.estimates(outcome = "pcl.sum_score_base",
+                         explan_var = "employment.unemployed_numeric",
+                         data_set = "dat.prepan")
+kable(pcl_prepan_model1b_employment_estimates)
+pcl_prepan_model1b_employment_estimates
+
+# Regression diagnostic statistics
+pcl_prepan_model1b_employment_reg_stats <- model1b.explan.reg.stats(outcome = "pcl.sum_score_base",
+                         explan_var = "employment.unemployed_numeric",
+                         data_set = "dat.prepan")
+kable(pcl_prepan_model1b_employment_reg_stats)
+pcl_prepan_model1b_employment_reg_stats
+```
+
+# SENSITIVITY based on employment change
+
+```{r create an employment change variable}
+dat.prepan <- dat.prepan %>%
+  mutate(employment_change =
+           case_when(
+             employment.unemployed_numeric == "1" ~ "Unemployed",
+             employment.became_unemployed_numeric == "1" ~ "Became Unemployed",                         
+             employment.furloughed_or_paid_leave_government_funded_numeric == "1" ~ "Furlough",
+             employment.furloughed_or_paid_leave_company_funded_numeric == "1" ~ "Furlough",    
+             employment.paid_leave_furloughed_numeric == "1" ~ "Furlough",                             
+             key_worker_numeric == "1" ~ "Key Worker",                                            
+             employment.government_work_key_workers_numeric == "1" ~ "Key Worker",                
+             employment.zerohours_contract_numeric == "1" ~ "Zero Hours Contract",                         
+             employment.retired_numeric == "1" ~ "Retired",                                   
+             employment.student_gcse_or_a_level_numeric == "1" ~ "Student",                   
+             employment.student_university_numeric == "1" ~ "Student"                        
+           )
+  )
+
+dat.prepan$employment_change <- as.factor(dat.prepan$employment_change)
+```
+
+# GAD prepan
+## Regression: Absolute scores
+### Model 0a: Disorder_hierarchical, Unadjusted
+```{r gad employment change sensitivity model0a sum_score prepan}
+# Regression coefficients
+gad_prepan_model0a_employmentchange_estimates <- model0a.explan.estimates(outcome = "gad.sum_score_base",
+                         explan_var = "employment_change",
+                         data_set = "dat.prepan")
+kable(gad_prepan_model0a_employmentchange_estimates)
+gad_prepan_model0a_employmentchange_estimates
+
+# Regression diagnostic statistics
+gad_prepan_model0a_employmentchange_reg_stats <- model0a.explan.reg.stats(outcome = "gad.sum_score_base",
+                         explan_var = "employment_change",
+                         data_set = "dat.prepan")
+kable(gad_prepan_model0a_employmentchange_reg_stats)
+gad_prepan_model0a_employmentchange_reg_stats
+```
+
+### Model 0b: Overlapping disorders, Unadjusted
+```{r gad employment change sensitivity model0b sum_score prepan}
+# Regression coefficients
+gad_prepan_model0b_employmentchange_estimates <- model0b.explan.estimates(outcome = "gad.sum_score_base",
+                         explan_var = "employment_change",
+                         data_set = "dat.prepan")
+kable(gad_prepan_model0b_employmentchange_estimates)
+gad_prepan_model0b_employmentchange_estimates
+
+# Regression diagnostic statistics
+gad_prepan_model0b_employmentchange_reg_stats <- model0b.explan.reg.stats(outcome = "gad.sum_score_base",
+                         explan_var = "employment_change",
+                         data_set = "dat.prepan")
+kable(gad_prepan_model0b_employmentchange_reg_stats)
+gad_prepan_model0b_employmentchange_reg_stats
+```
+
+### Model 1a: Disorder hierarchical, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r gad employment change sensitivity model1a sum_score prepan}
+# Regression coefficients
+gad_prepan_model1a_employmentchange_estimates <- model1a.explan.estimates(outcome = "gad.sum_score_base",
+                         explan_var = "employment_change",
+                         data_set = "dat.prepan")
+kable(gad_prepan_model1a_employmentchange_estimates)
+gad_prepan_model1a_employmentchange_estimates
+
+# Regression diagnostic statistics
+gad_prepan_model1a_employmentchange_reg_stats <- model1a.explan.reg.stats(outcome = "gad.sum_score_base",
+                         explan_var = "employment_change",
+                         data_set = "dat.prepan")
+kable(gad_prepan_model1a_employmentchange_reg_stats)
+gad_prepan_model1a_employmentchange_reg_stats
+```
+
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r gad employment change sensitivity model1b sum_score prepan}
+# Regression coefficients
+gad_prepan_model1b_employmentchange_estimates <- model1b.explan.estimates(outcome = "gad.sum_score_base",
+                         explan_var = "employment_change",
+                         data_set = "dat.prepan")
+kable(gad_prepan_model1b_employmentchange_estimates)
+gad_prepan_model1b_employmentchange_estimates
+
+# Regression diagnostic statistics
+gad_prepan_model1b_employmentchange_reg_stats <- model1b.explan.reg.stats(outcome = "gad.sum_score_base",
+                         explan_var = "employment_change",
+                         data_set = "dat.prepan")
+kable(gad_prepan_model1b_employmentchange_reg_stats)
+gad_prepan_model1b_employmentchange_reg_stats
+```
+
+# PHQ prepan
+## Regression: Absolute scores
+### Model 0a: Disorder_hierarchical, Unadjusted
+```{r phq employment change sensitivity model0a sum_score prepan}
+# Regression coefficients
+phq_prepan_model0a_employmentchange_estimates <- model0a.explan.estimates(outcome = "phq.sum_score_base",
+                         explan_var = "employment_change",
+                         data_set = "dat.prepan")
+kable(phq_prepan_model0a_employmentchange_estimates)
+phq_prepan_model0a_employmentchange_estimates
+
+# Regression diagnostic statistics
+phq_prepan_model0a_employmentchange_reg_stats <- model0a.explan.reg.stats(outcome = "phq.sum_score_base",
+                         explan_var = "employment_change",
+                         data_set = "dat.prepan")
+kable(phq_prepan_model0a_employmentchange_reg_stats)
+phq_prepan_model0a_employmentchange_reg_stats
+```
+
+### Model 0b: Overlapping disorders, Unadjusted
+```{r phq employment change sensitivity model0b sum_score prepan}
+# Regression coefficients
+phq_prepan_model0b_employmentchange_estimates <- model0b.explan.estimates(outcome = "phq.sum_score_base",
+                         explan_var = "employment_change",
+                         data_set = "dat.prepan")
+kable(phq_prepan_model0b_employmentchange_estimates)
+phq_prepan_model0b_employmentchange_estimates
+
+# Regression diagnostic statistics
+phq_prepan_model0b_employmentchange_reg_stats <- model0b.explan.reg.stats(outcome = "phq.sum_score_base",
+                         explan_var = "employment_change",
+                         data_set = "dat.prepan")
+kable(phq_prepan_model0b_employmentchange_reg_stats)
+phq_prepan_model0b_employmentchange_reg_stats
+```
+
+### Model 1a: Disorder hierarchical, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r phq employment change sensitivity model1a sum_score prepan}
+# Regression coefficients
+phq_prepan_model1a_employmentchange_estimates <- model1a.explan.estimates(outcome = "phq.sum_score_base",
+                         explan_var = "employment_change",
+                         data_set = "dat.prepan")
+kable(phq_prepan_model1a_employmentchange_estimates)
+phq_prepan_model1a_employmentchange_estimates
+
+# Regression diagnostic statistics
+phq_prepan_model1a_employmentchange_reg_stats <- model1a.explan.reg.stats(outcome = "phq.sum_score_base",
+                         explan_var = "employment_change",
+                         data_set = "dat.prepan")
+kable(phq_prepan_model1a_employmentchange_reg_stats)
+phq_prepan_model1a_employmentchange_reg_stats
+```
+
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r phq employment change sensitivity model1b sum_score prepan}
+# Regression coefficients
+phq_prepan_model1b_employmentchange_estimates <- model1b.explan.estimates(outcome = "phq.sum_score_base",
+                         explan_var = "employment_change",
+                         data_set = "dat.prepan")
+kable(phq_prepan_model1b_employmentchange_estimates)
+phq_prepan_model1b_employmentchange_estimates
+
+# Regression diagnostic statistics
+phq_prepan_model1b_employmentchange_reg_stats <- model1b.explan.reg.stats(outcome = "phq.sum_score_base",
+                         explan_var = "employment_change",
+                         data_set = "dat.prepan")
+kable(phq_prepan_model1b_employmentchange_reg_stats)
+phq_prepan_model1b_employmentchange_reg_stats
+```
+
+# OCIR prepan 
+## Regression: Absolute scores
+### Model 0a: Disorder_hierarchical, Unadjusted
+```{r ocir employment change sensitivity model0a sum_score prepan}
+# Regression coefficients
+ocir_prepan_model0a_employmentchange_estimates <- model0a.explan.estimates(outcome = "ocir.sum_score_base",
+                         explan_var = "employment_change",
+                         data_set = "dat.prepan")
+kable(ocir_prepan_model0a_employmentchange_estimates)
+ocir_prepan_model0a_employmentchange_estimates
+
+# Regression diagnostic statistics
+ocir_prepan_model0a_employmentchange_reg_stats <- model0a.explan.reg.stats(outcome = "ocir.sum_score_base",
+                         explan_var = "employment_change",
+                         data_set = "dat.prepan")
+kable(ocir_prepan_model0a_employmentchange_reg_stats)
+ocir_prepan_model0a_employmentchange_reg_stats
+```
+
+### Model 0b: Overlapping disorders, Unadjusted
+```{r ocir employment change sensitivity model0b sum_score prepan}
+# Regression coefficients
+ocir_prepan_model0b_employmentchange_estimates <- model0b.explan.estimates(outcome = "ocir.sum_score_base",
+                         explan_var = "employment_change",
+                         data_set = "dat.prepan")
+kable(ocir_prepan_model0b_employmentchange_estimates)
+ocir_prepan_model0b_employmentchange_estimates
+
+# Regression diagnostic statistics
+ocir_prepan_model0b_employmentchange_reg_stats <- model0b.explan.reg.stats(outcome = "ocir.sum_score_base",
+                         explan_var = "employment_change",
+                         data_set = "dat.prepan")
+kable(ocir_prepan_model0b_employmentchange_reg_stats)
+ocir_prepan_model0b_employmentchange_reg_stats
+```
+
+### Model 1a: Disorder hierarchical, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r ocir employment change sensitivity model1a sum_score prepan}
+# Regression coefficients
+ocir_prepan_model1a_employmentchange_estimates <- model1a.explan.estimates(outcome = "ocir.sum_score_base",
+                         explan_var = "employment_change",
+                         data_set = "dat.prepan")
+kable(ocir_prepan_model1a_employmentchange_estimates)
+ocir_prepan_model1a_employmentchannge_estimates
+
+# Regression diagnostic statistics
+ocir_prepan_model1a_employmentchange_reg_stats <- model1a.explan.reg.stats(outcome = "ocir.sum_score_base",
+                         explan_var = "employment_change",
+                         data_set = "dat.prepan")
+kable(ocir_prepan_model1a_employmentchange_reg_stats)
+ocir_prepan_model1a_employmentchange_reg_stats
+```
+
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r ocir employment change sensitivity model1b sum_score prepan}
+# Regression coefficients
+ocir_prepan_model1b_employmentchange_estimates <- model1b.explan.estimates(outcome = "ocir.sum_score_base",
+                         explan_var = "employment_change",
+                         data_set = "dat.prepan")
+kable(ocir_prepan_model1b_employmentchange_estimates)
+ocir_prepan_model1b_employmentchange_estimates
+
+# Regression diagnostic statistics
+ocir_prepan_model1b_employmentchange_reg_stats <- model1b.explan.reg.stats(outcome = "ocir.sum_score_base",
+                         explan_var = "employment_change",
+                         data_set = "dat.prepan")
+kable(ocir_prepan_model1b_employmentchange_reg_stats)
+ocir_prepan_model1b_employmentchange_reg_stats
+```
+
+#PCL prepan 
+## Regression: Absolute scores
+### Model 0a: Disorder_hierarchical, Unadjusted
+```{r pcl employment change sensitivty model0a sum_score prepan}
+# Regression coefficients
+pcl_prepan_model0a_employmentchange_estimates <- model0a.explan.estimates(outcome = "pcl.sum_score_base",
+                         explan_var = "employment_change",
+                         data_set = "dat.prepan")
+kable(pcl_prepan_model0a_employmentchange_estimates)
+pcl_prepan_model0a_employmentchange_estimates
+
+# Regression diagnostic statistics
+pcl_prepan_model0a_employmentchange_reg_stats <- model0a.explan.reg.stats(outcome = "pcl.sum_score_base",
+                         explan_var = "employment_change",
+                         data_set = "dat.prepan")
+kable(pcl_prepan_model0a_employmentchange_reg_stats)
+pcl_prepan_model0a_employmentchange_reg_stats
+```
+
+### Model 0b: Overlapping disorders, Unadjusted
+```{r pcl employment change sensitivty model0b sum_score prepan}
+# Regression coefficients
+pcl_prepan_model0b_employmentchange_estimates <- model0b.explan.estimates(outcome = "pcl.sum_score_base",
+                         explan_var = "employment_change",
+                         data_set = "dat.prepan")
+kable(pcl_prepan_model0b_employmentchange_estimates)
+pcl_prepan_model0b_employmentchange_estimates
+
+# Regression diagnostic statistics
+pcl_prepan_model0b_employmentchange_reg_stats <- model0b.explan.reg.stats(outcome = "pcl.sum_score_base",
+                         explan_var = "employment_change",
+                         data_set = "dat.prepan")
+kable(pcl_prepan_model0b_employmentchange_reg_stats)
+pcl_prepan_model0b_employmentchange_reg_stats
+```
+
+### Model 1a: Disorder hierarchical, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r pcl employment change sensitivty model1a sum_score prepan}
+# Regression coefficients
+pcl_prepan_model1a_employmentchange_estimates <- model1a.explan.estimates(outcome = "pcl.sum_score_base",
+                         explan_var = "employment_change",
+                         data_set = "dat.prepan")
+kable(pcl_prepan_model1a_employmentchange_estimates)
+pcl_prepan_model1a_employmentchange_estimates
+
+# Regression diagnostic statistics
+pcl_prepan_model1a_employmentchange_reg_stats <- model1a.explan.reg.stats(outcome = "pcl.sum_score_base",
+                         explan_var = "employment_change",
+                         data_set = "dat.prepan")
+kable(pcl_prepan_model1a_employmentchange_reg_stats)
+pcl_prepan_model1a_employmentchange_reg_stats
+```
+
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r pcl employment change sensitivty model1b sum_score prepan}
+# Regression coefficients
+pcl_prepan_model1b_employmentchange_estimates <- model1b.explan.estimates(outcome = "pcl.sum_score_base",
+                         explan_var = "employment_change",
+                         data_set = "dat.prepan")
+kable(pcl_prepan_model1b_employmentchange_estimates)
+pcl_prepan_model1b_employmentchange_estimates
+
+# Regression diagnostic statistics
+pcl_prepan_model1b_employmentchange_reg_stats <- model1b.explan.reg.stats(outcome = "pcl.sum_score_base",
+                         explan_var = "employment_change",
+                         data_set = "dat.prepan")
+kable(pcl_prepan_model1b_employmentchange_reg_stats)
+pcl_prepan_model1b_employmentchange_reg_stats
+```

### 2020-11-06 PANCHANGE_exclusion_descriptives.Rmd

--- 2020-11-06 PANCHANGE_exclusion_descriptives.Rmd
@@
 library(ggpubr)
-library(stringr)
 ```
@@
 ```{r read in data}
-dat.raw <- readRDS(file = paste0(data_path, "four_cohorts_variables.rds"))
+dat.raw <- readRDS(file = paste0(data_path, "/four_cohorts_variables.rds"))
 dim(dat.raw)
@@
 Exclude individuals with NA for the MHD categories
-Individuals with NAs for age/gender have already been excluded in pre-processing script, but they get excluded here to be safe and to double check previous programming.
+Individuals with NAs for age/gender have already been excluded in pre-processing script, but they get excluded here to be save and to double check previous programming.
 
@@
 # Data availability per questionnaire GAD, PHQ, PCL, and OCI-R
+++MD: These 'data availability' chunks caused my R to crash, so I'm hashing them out for now. Others can test if it works for them and unhash as needed, otherwise I think they should be removed.
 
@@
 ```{r gad availability}
-dat.raw %>%
-  freq(
-    data_group_gad,
-    cumul = F)
+#dat.raw %>%
+#  freq(
+#    data_group_gad,
+#    cumul = F)
 ```
@@
 ```{r phq availability}
-dat.raw %>%
-  freq(
-    data_group_phq,
-    cumul = F)
+#dat.raw %>%
+#  freq(
+#    data_group_phq,
+#    cumul = F)
 ```
@@
 ```{r pcl availability}
-dat.raw %>%
-  freq(
-    data_group_pcl,
-    cumul = F)
+#dat.raw %>%
+#  freq(
+#    data_group_pcl,
+#    cumul = F)
 ```
@@
 ```{r ocir availability}
-dat.raw %>%
-  freq(
-    data_group_ocir,
-    cumul = F)
+#dat.raw %>%
+#  freq(
+#    data_group_ocir,
+#    cumul = F)
 ```
@@
   count(depression_and_anxiety_numeric == 1)
-```
-
-#Impute no change prepandemic scores
-
-```{r Impute for gad measure}
-
-#Visualise the gad summary scores for baseline and retro
-head(dat$gad.sum_score_base, 30)
-head(dat$gad.sum_score_retro, 30)
-
-#Visualise the gad pandemic feelings variables
-head(dat$gad.pandemic_felt_feelings, 10)
-head(dat$gad.pandemic_felt_feelings_numeric, 10)
-
-#Edit the gad sum retro score as follows: if the pt reports no different since pandemic and there is a missing value for their retro score, impute their baseline score, else if there isn't a missing value for their retro score, leave it as it is.
-
-impute_dat <- dat %>% 
-  mutate(gad.sum_score_retro =
-           case_when(gad.pandemic_felt_feelings == "No different" & is.na(gad.sum_score_retro)                      ~ gad.sum_score_base,
-                     !is.na(gad.sum_score_retro) ~ gad.sum_score_retro))
-
-#Check that the Na's have been replaced with duplicated baseline sum scores
-head(impute_dat$gad.sum_score_base, 30)
-head(impute_dat$gad.sum_score_retro, 30)
-
-```
-
-```{r Impute for phq measure}
-
-#Visualise the phq summary scores for baseline and retro
-head(dat$phq.sum_score_base, 30)
-head(dat$phq.sum_score_retro, 30)
-
-#Visualise the phq pandemic feelings variables
-head(dat$phq.pandemic_felt_feelings, 10)
-head(dat$phq.pandemic_felt_feelings_numeric, 10)
-
-#Edit the phq sum retro score as follows: if the pt reports no different since pandemic and there is a missing value for their retro score, impute their baseline score, else if there isn't a missing value for their retro score, leave it as it is.
-
-impute_dat <- dat %>% 
-  mutate(phq.sum_score_retro =
-           case_when(phq.pandemic_felt_feelings == "No different" & is.na(phq.sum_score_retro)                      ~ phq.sum_score_base,
-                     !is.na(phq.sum_score_retro) ~ phq.sum_score_retro))
-
-#Check that the Na's have been replaced with duplicated baseline sum scores
-head(impute_dat$phq.sum_score_base, 30)
-head(impute_dat$phq.sum_score_retro, 30)
-
-```
-
-#Baseline survey completion (N per month)
-
-```{r N completing coping per month}
-
-#Visualise some dates when participants completed the questionnaire
-head(dat$startDate.coping, 20)
-
-#Divide the data by sign up per month and summarise the amount of pt's completing the survey that month
-
-april_sign_up <- dat[str_detect(dat$startDate.coping, "-04-"), ] %>% 
-  select(startDate.coping) %>% 
-  summarise(April = n())
-
-may_sign_up <- dat[str_detect(dat$startDate.coping, "-05-"), ] %>% 
-  select(startDate.coping) %>% 
-  summarise(May = n())
-
-june_sign_up <- dat[str_detect(dat$startDate.coping, "-06-"), ] %>% 
-  select(startDate.coping) %>% 
-  summarise(June = n())
-
-july_sign_up <- dat[str_detect(dat$startDate.coping, "-07-"), ] %>% 
-  select(startDate.coping) %>% 
-  summarise(July = n())
-
-august_sign_up <- dat[str_detect(dat$startDate.coping, "-08-"), ] %>% 
-  select(startDate.coping) %>% 
-  summarise(August = n())
-
-september_sign_up <- dat[str_detect(dat$startDate.coping, "-09-"), ] %>% 
-  select(startDate.coping) %>% 
-  summarise(September = n())
-
-#Merge results into one tibble
-
-coping_sign_up <- april_sign_up %>% 
-  cbind(may_sign_up, june_sign_up, july_sign_up, august_sign_up, september_sign_up)
-
-#Gather the variables
-coping_sign_up <- coping_sign_up %>% 
-  gather(key = "month", value = "sign_up_number")
-
-#Proportion calculation
-coping_sign_up <- coping_sign_up %>% 
-  mutate(percentage = 
-           round((sign_up_number / sum(sign_up_number) * 100), 2))
-
-coping_sign_up
-
 ```
@@
          p.mat = mhd.p.matrix, # Matrix with p values
-         sig.level = 0.01, # Choose significant level
-         insig = "blank" # Nonsignificant correlations have no colour
-         )
-```
-
-#Correlation between retropsective impute and prepan
-
-```{r Correlation prep chunk}
-# Select items for correlation matrix
-prepan_retro_items <- c(
-    "gad.sum_score_prepan",
-    "gad.sum_score_retro", 
-    "phq.sum_score_prepan",
-    "phq.sum_score_retro"
-)
-
-#Create a data set with only the COPING samples
-prepan_retro_dat <- dat[str_detect(dat$Sample, "NBR|GLAD|EDGI"), ]
-
-#Check that RAMP has been removed
-prepan_retro_dat %>% 
-  freq(Sample)
-
-# Calculate correlation matrix on specific columns (variables) from your data frame
-prepan_retro.corr.mat <- hetcor(
-  as.data.frame(prepan_retro_dat[,prepan_retro_items]), # Specify the data
-  use = "pairwise.complete.obs" # Use all pairwise observations
-)
-
-# Print the correlation matrix
-print(prepan_retro.corr.mat, digits = max(3, getOption("digits") - 3))
-
-# Save the correlations from the correlation matrix in an object
-prepan_retro.corr.matrix <- as.matrix(prepan_retro.corr.mat)
-
-# Save the p values from the correlation matrix in an object
-prepan_retro.p.matrix <- as.matrix(prepan_retro.corr.mat$tests)
-```
-
-```{r Correlation matrix of prepan base sum scores}
-corrplot(prepan_retro.corr.matrix, 
-         method = "color", # objects to represent the correlations on plot
-         type = "lower", # only use the lower triangle of the matrix
-         diag = FALSE, # do not show the correlations on the diagonal
-         addgrid.col = NA,
-         addCoef.col = "black", # colour for the correlation coefficients in the plot
-         tl.cex = 0.8,
-         tl.col = "black",
-         col=colorRampPalette(c("dodgerblue4","white","firebrick4"))(200), # colours for correlations
-         # Combine with significance
-         p.mat = prepan_retro.p.matrix, # Matrix with p values
          sig.level = 0.01, # Choose significant level
@@
 
+```{r Disorder_inc by Sample prop table}
+Disorder_inc_by_Sample_collapsed <- dat.long.psych %>%
+  group_by(Disorder_inc) %>%
+  filter(Diagnosis == 1) %>%
+  count(Sample) %>%
+  mutate(Prop = round(n/sum(n), 2))
+
+kable(Disorder_inc_by_Sample_collapsed)
+```
+
 ```{r Disorder_inc by Sample plot}
@@
   count(highest_education, Sample) %>%
-  drop_na() %>% 
   mutate(Prop = round(n/sum(n), 2))
@@
   count(highest_education, Sample) %>%
-  drop_na() %>% 
   mutate(Prop = round(n/sum(n), 2)) %>%
@@
   count(highest_education, Sample) %>%
-  drop_na() %>% 
   spread(key = Sample, value = n) %>%

### 2020-11-06 PANCHANGE_exclusion_descriptives.Rmd

--- 2020-11-06 PANCHANGE_exclusion_descriptives.Rmd
@@
 
-#Impute no change prepandemic scores
+#HR
+
+```{r Accuray scores for gad: worse/better than pre-pandemic}
+
+dat.raw$gad.pandemic.change.group <- ifelse(dat.raw$gad.pandemic_felt_feelings_numeric <3,1,
+                                           ifelse(dat.raw$gad.pandemic_felt_feelings_numeric > 3,2,0))
+
+dat.raw$gad.pandemic.change.group <- factor(dat.raw$gad.pandemic.change.group,
+                                           levels = c(1,0,2),labels = c("Worse","No change","Better"))
+
+dat.raw <- dat.raw %>%
+    mutate(gad.change.accurate = case_when(dat.raw$gad.pandemic.change.group == "Better" &
+                                             dat.raw$gad.diff_score_base_prepan < 0 ~1,
+                                           dat.raw$gad.pandemic.change.group == "Worse" &
+                                             dat.raw$gad.diff_score_base_prepan > 0 ~ 1,
+                                           dat.raw$gad.pandemic.change.group == "Better" &
+                                             dat.raw$gad.diff_score_base_prepan > 0 ~ 0,
+                                           dat.raw$gad.pandemic.change.group == "Worse" &
+                                             dat.raw$gad.diff_score_base_prepan < 0 ~ 0))
+
+dat.raw <- dat.raw %>%
+    mutate(gad.change.retro.accurate = if_else(dat.raw$gad.pandemic.change.group == "Better" &
+                                             dat.raw$gad.diff_score_retro_prepan == 0 |
+                                             dat.raw$gad.pandemic.change.group == "Worse" &
+                                             dat.raw$gad.diff_score_retro_prepan == 0, 1, 3 ))
+dat.raw <- dat.raw %>%
+  mutate(gad.change.retro.accurate = if_else(dat.raw$gad.pandemic.change.group == "Better" &
+                                             dat.raw$gad.diff_score_retro_prepan >= -3 &
+                                             dat.raw$gad.diff_score_retro_prepan <= 3 &
+                                             dat.raw$gad.change.retro.accurate_temp != 1 |
+                                             dat.raw$gad.pandemic.change.group == "Worse" &
+                                             dat.raw$gad.diff_score_retro_prepan >= -3 &
+                                             dat.raw$gad.diff_score_retro_prepan <= 3 &
+                                             dat.raw$gad.change.retro.accurate_temp != 1,  2, gad.change.retro.accurate))
+
+```
+
+#SB - Impute no change prepandemic scores
+
+I interpreted the presence of an NA in the retrospective score as an indicator of saying "no change" in their baseline scores.
+Hence, if this was the case, I imputed their baseline score.
+However, this interpretation could be wrong.
+
+Also, I'm not sure what to do if there is an NA for their baseline sum score (nothing to duplicate).
+This was the case for ocir for some reason: the retro scores were provided for some by not the corresponding baseline score?
 
@@
     "gad.sum_score_retro", 
+    "ocir.sum_score_prepan",
+    "ocir.sum_score_retro",
     "phq.sum_score_prepan",

### 2020-11-09 PANCHANGE_analysis.Rmd

@@
 
-dim(dat.prepan)
+dim(dat.retro_sensitivity)
+```
+age^2 sensitivity 
+Exclude individuals with NA for continuous Age variable
+```{r}
+dat_age_sensitivity <- dat %>%
+  filter(!is.na(Age))
+dim(dat_age_sensitivity)
 ```
@@
 
+```{r model2a function}
+model2a.estimates <- function(outcome, data_set) {
+  # define the variable name of the dependent variable
+  dependent.variable <- outcome
+  # define the independent variables
+  independent.variables <- c("Disorder_hierarchical",
+                            "Gender_collapsed",
+                            "poly(Age, 2)",
+                            "Ethnicity_collapsed",
+                            "time_diff_coping_lockdown_march_23"
+                            )
+  # create the formula
+  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
+  glm.formula
+
+  # run the glm
+  assign(paste0(outcome,".model2a"),
+         lm( formula = glm.formula,
+             data = get(data_set)
+         )
+  )
+
+  assign(paste0(outcome,"model2a_estimates"),
+         tidy(get(paste0(outcome,".model2a")), conf.int = TRUE) %>%
+           mutate(
+             "Indepent variable" = recode_factor(
+               term,
+               "(Intercept)" = "Intercept",
+               "Disorder_hierarchicalAnxiety disorders" = "Anxiety disorders",
+               "Disorder_hierarchicalEating disorders" = "Eating disorders",
+               "Disorder_hierarchicalOCDs" = "OCDs",
+               "Disorder_hierarchicalPTSD" = "PTSD",
+               "Disorder_hierarchicalDepressive disorders" = "Depressive disorders",
+               "Disorder_hierarchicalBipolar disorders" = "Bipolar disorders",
+               "Gender_collapsedFemale" = "Female",
+               "Gender_collapsedNon-binary/Self-defined" = "Non-binary/Self-defined",
+               "poly(Age, 2)1" = "Age",
+               "poly(Age, 2)2" = "Age^2", 
+               "Ethnicity_collapsedMixed or multiple ethnic origins" = "Mixed or multiple ethnic origins",
+               "Ethnicity_collapsedAsian or Asian British" = "Asian or Asian British",
+               "Ethnicity_collapsedAfrican or African British" = "African or African British",
+               "Ethnicity_collapsedOther" = "Other ethnicity",
+               "time_diff_coping_lockdown_march_23" = "Time difference: Lockdown to baseline"
+             ),
+             "Estimate" = format(
+               round(estimate,
+                     digits = 2),
+               nsmall = 2),
+             "95% CI low" = format(
+               round(conf.low,
+                     digits = 2),
+               nsmall = 2),
+             "95% CI up" = format(
+               round(conf.high,
+                     digits = 2),
+               nsmall = 2),
+             "SE" = format(
+               round(std.error,
+                     digits = 2),
+               nsmall = 2),
+             "z score" = format(
+               round(statistic,
+                     digits = 2),
+               nsmall = 2),
+             "p value" = case_when(
+               p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
+               p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
+               p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
+             )
+           ) %>%
+           select(
+             "Indepent variable",
+             "Estimate",
+             "95% CI low",
+             "95% CI up",
+             "SE",
+             #    "z score",
+             "p value"
+           )
+  )
+
+  return(get(paste0(outcome,"model2a_estimates")))
+}
+
+model2a.reg.stats <- function(outcome, data_set) {
+  # define the variable name of the dependent variable
+  dependent.variable <- outcome
+  # define the independent variables
+  independent.variables <- c("Disorder_hierarchical")
+  # create the formula
+  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
+  glm.formula
+
+  # run the glm
+  assign(paste0(outcome,".model2a"),
+         lm( formula = glm.formula,
+             data = get(data_set)
+         )
+  )
+
+  assign(paste0(outcome,"model2a_reg_stats"),
+         glance(get(paste0(outcome,".model2a"))) %>%
+           mutate(
+             "n" = format(
+               round(nobs,
+                     digits = 0),
+               nsmall = 0),
+             "R2" = format(
+               round(r.squared,
+                     digits = 2),
+               nsmall = 2),
+             "adjust. R2" = format(
+               round(adj.r.squared,
+                     digits = 2),
+               nsmall = 2),
+             "F" = format(
+               round(statistic,
+                     digits = 2),
+               nsmall = 2),
+             "p value" = case_when(
+               p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
+               p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
+               p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
+             )
+           ) %>%
+           select(
+             "n",
+             "R2",
+             "adjust. R2",
+             "F",
+             "p value",
+             "df"
+           )
+  )
+
+  return(get(paste0(outcome,"model2a_reg_stats")))
+}
+```
+
+```{r model2b function}
+model2b.estimates <- function(outcome, data_set) {
+  # define the variable name of the dependent variable
+  dependent.variable <- outcome
+  # define the independent variables
+  independent.variables <- c("depression_and_anxiety",
+                             "eating_disorders",
+                             "obsessive_compulsive_disorders",
+                             "bipolar_and_schizophrenia",
+                             "mhd.posttraumatic_stress_disorder_ptsd",
+                             "autism_spectrum_disorder",
+                             "mhd.attention_deficit_hyperactivity_disorder",
+                             "mhd.personality_disorder",
+                             "Gender_collapsed",
+                             "poly(Age, 2)",
+                             "Ethnicity_collapsed",
+                             "key_worker",
+                             "time_diff_coping_lockdown_march_23"
+                                )
+  # create the formula
+  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
+  glm.formula
+
+  # run the glm
+  assign(paste0(outcome,".model2b"),
+         lm( formula = glm.formula,
+             data = get(data_set)
+         )
+  )
+
+  assign(paste0(outcome,"model2b_estimates"),
+         tidy(get(paste0(outcome,".model2b")), conf.int = TRUE) %>%
+           mutate(
+             "Indepent variable" = recode_factor(
+               term,
+               "(Intercept)" = "Intercept",
+               "anxiety_disordersAnxiety disorder" = "Anxiety disorders",
+               "depressive_disordersDepressive disorder" = "Depressive disorders",
+               "depression_and_anxietyDepressive and anxiety disorder" = "Depressive and anxiety disorder",
+               "depression_and_anxietyOnly depressive disorder" = "Only depressive disorder",
+               "depression_and_anxietyOnly anxiety disorder" = "Only anxiety disorder",
+               "eating_disordersEating disorder" = "Eating disorders",
+               "obsessive_compulsive_disordersObsessive compulsive disorder" = "OCDs",
+               "bipolar_and_schizophreniaPsychotic and bipolar disorder" = "Psychotic and bipolar disorder",
+               "bipolar_and_schizophreniaOnly psychotic disorder" = "Only psychotic disorder",
+               "bipolar_and_schizophreniaOnly bipolar disorder" = "Only bipolar disorder",
+               "psychotic_disordersPsychotic disorder" = "Psychotic disorder",
+               "mhd.mania_hypomania_bipolar_or_manicdepressionMania, hypomania, bipolar or manic-depression" = "Bipolar disorder",
+               "mhd.posttraumatic_stress_disorder_ptsdPost-traumatic stress disorder (PTSD)" = "PTSD",
+               "autism_spectrum_disorderAutism spectrum disorder" = "ASD",
+               "mhd.attention_deficit_hyperactivity_disorderAttention deficit or attention deficit and hyperactivity disorder (ADD/ADHD)" = "ADHD",
+               "mhd.personality_disorderPersonality disorder" = "Personality disorder",
+               "Gender_collapsedFemale" = "Female",
+               "Gender_collapsedNon-binary/Self-defined" = "Non-binary/Self-defined",
+               "poly(Age, 2)1" = "Age",
+               "poly(Age, 2)2" = "Age^2", 
+               "Ethnicity_collapsedMixed or multiple ethnic origins" = "Mixed or multiple ethnic origins",
+               "Ethnicity_collapsedAsian or Asian British" = "Asian or Asian British",
+               "Ethnicity_collapsedAfrican or African British" = "African or African British",
+               "Ethnicity_collapsedOther" = "Other ethnicity",
+               "key_workerKey worker" = "Key worker",
+               "time_diff_coping_lockdown_march_23" = "Time difference: Lockdown to baseline"
+             ),
+             "Estimate" = format(
+               round(estimate,
+                     digits = 2),
+               nsmall = 2),
+             "95% CI low" = format(
+               round(conf.low,
+                     digits = 2),
+               nsmall = 2),
+             "95% CI up" = format(
+               round(conf.high,
+                     digits = 2),
+               nsmall = 2),
+             "SE" = format(
+               round(std.error,
+                     digits = 2),
+               nsmall = 2),
+             "z score" = format(
+               round(statistic,
+                     digits = 2),
+               nsmall = 2),
+             "p value" = case_when(
+               p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
+               p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
+               p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
+             )
+           ) %>%
+           select(
+             "Indepent variable",
+             "Estimate",
+             "95% CI low",
+             "95% CI up",
+             "SE",
+             #    "z score",
+             "p value"
+           )
+  )
+
+  return(get(paste0(outcome,"model2b_estimates")))
+}
+
+model2b.reg.stats <- function(outcome, data_set) {
+  # define the variable name of the dependent variable
+  dependent.variable <- outcome
+  # define the independent variables
+  independent.variables <- c("Disorder_hierarchical")
+  # create the formula
+  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
+  glm.formula
+
+  # run the glm
+  assign(paste0(outcome,".model2b"),
+         lm( formula = glm.formula,
+             data = get(data_set)
+         )
+  )
+
+  assign(paste0(outcome,"model2b_reg_stats"),
+         glance(get(paste0(outcome,".model2b"))) %>%
+           mutate(
+             "n" = format(
+               round(nobs,
+                     digits = 0),
+               nsmall = 0),
+             "R2" = format(
+               round(r.squared,
+                     digits = 2),
+               nsmall = 2),
+             "adjust. R2" = format(
+               round(adj.r.squared,
+                     digits = 2),
+               nsmall = 2),
+             "F" = format(
+               round(statistic,
+                     digits = 2),
+               nsmall = 2),
+             "p value" = case_when(
+               p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
+               p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
+               p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
+             )
+           ) %>%
+           select(
+             "n",
+             "R2",
+             "adjust. R2",
+             "F",
+             "p value",
+             "df"
+           )
+  )
+
+  return(get(paste0(outcome,"model2b_reg_stats")))
+}
+```
+
 ```{r model0a.explan function}
@@
 ```
-
-# SENSITIVITY based on highest level of education
-
-# GAD prepan
-## Regression: Absolute scores
-### Model 0a: Disorder_hierarchical, Unadjusted
-```{r gad education sensitivity model0a sum_score prepan}
-# Regression coefficients
-gad_prepan_model0a_education_estimates <- model0a.explan.estimates(outcome = "gad.sum_score_base",
-                         explan_var = "highest_education_numeric",
-                         data_set = "dat.prepan")
-kable(gad_prepan_model0a_education_estimates)
-gad_prepan_model0a_education_estimates
-
-# Regression diagnostic statistics
-gad_prepan_model0a_education_reg_stats <- model0a.explan.reg.stats(outcome = "gad.sum_score_base",
-                         explan_var = "highest_education_numeric",
-                         data_set = "dat.prepan")
-kable(gad_prepan_model0a_education_reg_stats)
-gad_prepan_model0a_education_reg_stats
-```
-
-### Model 0b: Overlapping disorders, Unadjusted
-```{r gad education sensitivity model0b sum_score prepan}
-# Regression coefficients
-gad_prepan_model0b_education_estimates <- model0b.explan.estimates(outcome = "gad.sum_score_base",
-                         explan_var = "highest_education_numeric",
-                         data_set = "dat.prepan")
-kable(gad_prepan_model0b_education_estimates)
-gad_prepan_model0b_education_estimates
-
-# Regression diagnostic statistics
-gad_prepan_model0b_education_reg_stats <- model0b.explan.reg.stats(outcome = "gad.sum_score_base",
-                         explan_var = "highest_education_numeric",
-                         data_set = "dat.prepan")
-kable(gad_prepan_model0b_education_reg_stats)
-gad_prepan_model0b_education_reg_stats
-```
-
-### Model 1a: Disorder hierarchical, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
-```{r gad education sensitivity model1a sum_score prepan}
-# Regression coefficients
-gad_prepan_model1a_education_estimates <- model1a.explan.estimates(outcome = "gad.sum_score_base",
-                         explan_var = "highest_education_numeric",
-                         data_set = "dat.prepan")
-kable(gad_prepan_model1a_education_estimates)
-gad_prepan_model1a_education_estimates
-
-# Regression diagnostic statistics
-gad_prepan_model1a_education_reg_stats <- model1a.explan.reg.stats(outcome = "gad.sum_score_base",
-                         explan_var = "highest_education_numeric",
-                         data_set = "dat.prepan")
-kable(gad_prepan_model1a_education_reg_stats)
-gad_prepan_model1a_education_reg_stats
-```
-
-### Model 1b: Overlapping disorders, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
-```{r gad education sensitivity model1b sum_score prepan}
-# Regression coefficients
-gad_prepan_model1b_education_estimates <- model1b.explan.estimates(outcome = "gad.sum_score_base",
-                         explan_var = "highest_education_numeric",
-                         data_set = "dat.prepan")
-kable(gad_prepan_model1b_education_estimates)
-gad_prepan_model1b_education_estimates
-
-# Regression diagnostic statistics
-gad_prepan_model1b_education_reg_stats <- model1b.explan.reg.stats(outcome = "gad.sum_score_base",
-                         explan_var = "highest_education_numeric",
-                         data_set = "dat.prepan")
-kable(gad_prepan_model1b_education_reg_stats)
-gad_prepan_model1b_education_reg_stats
-```
-
-# PHQ prepan
-## Regression: Absolute scores
-### Model 0a: Disorder_hierarchical, Unadjusted
-```{r phq education sensitivity model0a sum_score prepan}
-# Regression coefficients
-phq_prepan_model0a_education_estimates <- model0a.explan.estimates(outcome = "phq.sum_score_base",
-                         explan_var = "highest_education_numeric",
-                         data_set = "dat.prepan")
-kable(phq_prepan_model0a_education_estimates)
-phq_prepan_model0a_education_estimates
-
-# Regression diagnostic statistics
-phq_prepan_model0a_education_reg_stats <- model0a.explan.reg.stats(outcome = "phq.sum_score_base",
-                         explan_var = "highest_education_numeric",
-                         data_set = "dat.prepan")
-kable(phq_prepan_model0a_education_reg_stats)
-phq_prepan_model0a_education_reg_stats
-```
-
-### Model 0b: Overlapping disorders, Unadjusted
-```{r phq education sensitivity model0b sum_score prepan}
-# Regression coefficients
-phq_prepan_model0b_education_estimates <- model0b.explan.estimates(outcome = "phq.sum_score_base",
-                         explan_var = "highest_education_numeric",
-                         data_set = "dat.prepan")
-kable(phq_prepan_model0b_education_estimates)
-phq_prepan_model0b_education_estimates
-
-# Regression diagnostic statistics
-phq_prepan_model0b_education_reg_stats <- model0b.explan.reg.stats(outcome = "phq.sum_score_base",
-                         explan_var = "highest_education_numeric",
-                         data_set = "dat.prepan")
-kable(phq_prepan_model0b_education_reg_stats)
-phq_prepan_model0b_education_reg_stats
-```
-
-### Model 1a: Disorder hierarchical, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
-```{r phq education sensitivity model1a sum_score prepan}
-# Regression coefficients
-phq_prepan_model1a_education_estimates <- model1a.explan.estimates(outcome = "phq.sum_score_base",
-                         explan_var = "highest_education_numeric",
-                         data_set = "dat.prepan")
-kable(phq_prepan_model1a_education_estimates)
-phq_prepan_model1a_education_estimates
-
-# Regression diagnostic statistics
-phq_prepan_model1a_education_reg_stats <- model1a.explan.reg.stats(outcome = "phq.sum_score_base",
-                         explan_var = "highest_education_numeric",
-                         data_set = "dat.prepan")
-kable(phq_prepan_model1a_education_reg_stats)
-phq_prepan_model1a_education_reg_stats
-```
-
-### Model 1b: Overlapping disorders, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
-```{r phq education sensitivity model1b sum_score prepan}
-# Regression coefficients
-phq_prepan_model1b_education_estimates <- model1b.explan.estimates(outcome = "phq.sum_score_base",
-                         explan_var = "highest_education_numeric",
-                         data_set = "dat.prepan")
-kable(phq_prepan_model1b_education_estimates)
-phq_prepan_model1b_education_estimates
-
-# Regression diagnostic statistics
-phq_prepan_model1b_education_reg_stats <- model1b.explan.reg.stats(outcome = "phq.sum_score_base",
-                         explan_var = "highest_education_numeric",
-                         data_set = "dat.prepan")
-kable(phq_prepan_model1b_education_reg_stats)
-phq_prepan_model1b_education_reg_stats
-```
-
-# OCIR prepan 
-## Regression: Absolute scores
-### Model 0a: Disorder_hierarchical, Unadjusted
-```{r ocir education sensitivity model0a sum_score prepan}
-# Regression coefficients
-ocir_prepan_model0a_education_estimates <- model0a.explan.estimates(outcome = "ocir.sum_score_base",
-                         explan_var = "highest_education_numeric",
-                         data_set = "dat.prepan")
-kable(ocir_prepan_model0a_education_estimates)
-ocir_prepan_model0a_education_estimates
-
-# Regression diagnostic statistics
-ocir_prepan_model0a_education_reg_stats <- model0a.explan.reg.stats(outcome = "ocir.sum_score_base",
-                         explan_var = "highest_education_numeric",
-                         data_set = "dat.prepan")
-kable(ocir_prepan_model0a_education_reg_stats)
-ocir_prepan_model0a_education_reg_stats
-```
-
-### Model 0b: Overlapping disorders, Unadjusted
-```{r ocir education sensitivity model0b sum_score prepan}
-# Regression coefficients
-ocir_prepan_model0b_education_estimates <- model0b.explan.estimates(outcome = "ocir.sum_score_base",
-                         explan_var = "highest_education_numeric",
-                         data_set = "dat.prepan")
-kable(ocir_prepan_model0b_education_estimates)
-ocir_prepan_model0b_education_estimates
-
-# Regression diagnostic statistics
-ocir_prepan_model0b_education_reg_stats <- model0b.explan.reg.stats(outcome = "ocir.sum_score_base",
-                         explan_var = "highest_education_numeric",
-                         data_set = "dat.prepan")
-kable(ocir_prepan_model0b_education_reg_stats)
-ocir_prepan_model0b_education_reg_stats
-```
-
-### Model 1a: Disorder hierarchical, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
-```{r ocir education sensitivity model1a sum_score prepan}
-# Regression coefficients
-ocir_prepan_model1a_education_estimates <- model1a.explan.estimates(outcome = "ocir.sum_score_base",
-                         explan_var = "highest_education_numeric",
-                         data_set = "dat.prepan")
-kable(ocir_prepan_model1a_education_estimates)
-ocir_prepan_model1a_education_estimates
-
-# Regression diagnostic statistics
-ocir_prepan_model1a_education_reg_stats <- model1a.explan.reg.stats(outcome = "ocir.sum_score_base",
-                         explan_var = "highest_education_numeric",
-                         data_set = "dat.prepan")
-kable(ocir_prepan_model1a_education_reg_stats)
-ocir_prepan_model1a_education_reg_stats
-```
-
-### Model 1b: Overlapping disorders, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
-```{r ocir education sensitivity model1b sum_score prepan}
-# Regression coefficients
-ocir_prepan_model1b_education_estimates <- model1b.explan.estimates(outcome = "ocir.sum_score_base",
-                         explan_var = "highest_education_numeric",
-                         data_set = "dat.prepan")
-kable(ocir_prepan_model1b_education_estimates)
-ocir_prepan_model1b_education_estimates
-
-# Regression diagnostic statistics
-ocir_prepan_model1b_education_reg_stats <- model1b.explan.reg.stats(outcome = "ocir.sum_score_base",
-                         explan_var = "highest_education_numeric",
-                         data_set = "dat.prepan")
-kable(ocir_prepan_model1b_education_reg_stats)
-ocir_prepan_model1b_education_reg_stats
-```
-
-#PCL prepan 
-## Regression: Absolute scores
-### Model 0a: Disorder_hierarchical, Unadjusted
-```{r pcl education sensitivty model0a sum_score prepan}
-# Regression coefficients
-pcl_prepan_model0a_education_estimates <- model0a.explan.estimates(outcome = "pcl.sum_score_base",
-                         explan_var = "highest_education_numeric",
-                         data_set = "dat.prepan")
-kable(pcl_prepan_model0a_education_estimates)
-pcl_prepan_model0a_education_estimates
-
-# Regression diagnostic statistics
-pcl_prepan_model0a_education_reg_stats <- model0a.explan.reg.stats(outcome = "pcl.sum_score_base",
-                         explan_var = "highest_education_numeric",
-                         data_set = "dat.prepan")
-kable(pcl_prepan_model0a_education_reg_stats)
-pcl_prepan_model0a_education_reg_stats
-```
-
-### Model 0b: Overlapping disorders, Unadjusted
-```{r pcl education sensitivty model0b sum_score prepan}
-# Regression coefficients
-pcl_prepan_model0b_education_estimates <- model0b.explan.estimates(outcome = "pcl.sum_score_base",
-                         explan_var = "highest_education_numeric",
-                         data_set = "dat.prepan")
-kable(pcl_prepan_model0b_education_estimates)
-pcl_prepan_model0b_education_estimates
-
-# Regression diagnostic statistics
-pcl_prepan_model0b_education_reg_stats <- model0b.explan.reg.stats(outcome = "pcl.sum_score_base",
-                         explan_var = "highest_education_numeric",
-                         data_set = "dat.prepan")
-kable(pcl_prepan_model0b_education_reg_stats)
-pcl_prepan_model0b_education_reg_stats
-```
-
-### Model 1a: Disorder hierarchical, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
-```{r pcl education sensitivty model1a sum_score prepan}
-# Regression coefficients
-pcl_prepan_model1a_education_estimates <- model1a.explan.estimates(outcome = "pcl.sum_score_base",
-                         explan_var = "highest_education_numeric",
-                         data_set = "dat.prepan")
-kable(pcl_prepan_model1a_education_estimates)
-pcl_prepan_model1a_education_estimates
-
-# Regression diagnostic statistics
-pcl_prepan_model1a_education_reg_stats <- model1a.explan.reg.stats(outcome = "pcl.sum_score_base",
-                         explan_var = "highest_education_numeric",
-                         data_set = "dat.prepan")
-kable(pcl_prepan_model1a_education_reg_stats)
-pcl_prepan_model1a_education_reg_stats
-```
-
-### Model 1b: Overlapping disorders, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
-```{r pcl education sensitivty model1b sum_score prepan}
-# Regression coefficients
-pcl_prepan_model1b_education_estimates <- model1b.explan.estimates(outcome = "pcl.sum_score_base",
-                         explan_var = "highest_education_numeric",
-                         data_set = "dat.prepan")
-kable(pcl_prepan_model1b_education_estimates)
-pcl_prepan_model1b_education_estimates
-
-# Regression diagnostic statistics
-pcl_prepan_model1b_education_reg_stats <- model1b.explan.reg.stats(outcome = "pcl.sum_score_base",
-                         explan_var = "highest_education_numeric",
-                         data_set = "dat.prepan")
-kable(pcl_prepan_model1b_education_reg_stats)
-pcl_prepan_model1b_education_reg_stats
-```
-
-# SENSITIVITY based on employment status
-
-# GAD prepan
-## Regression: Absolute scores
-### Model 0a: Disorder_hierarchical, Unadjusted
-```{r gad employment sensitivity model0a sum_score prepan}
-# Regression coefficients
-gad_prepan_model0a_employment_estimates <- model0a.explan.estimates(outcome = "gad.sum_score_base",
-                         explan_var = "employment.unemployed_numeric",
-                         data_set = "dat.prepan")
-kable(gad_prepan_model0a_employment_estimates)
-gad_prepan_model0a_employment_estimates
-
-# Regression diagnostic statistics
-gad_prepan_model0a_employment_reg_stats <- model0a.explan.reg.stats(outcome = "gad.sum_score_base",
-                         explan_var = "employment.unemployed_numeric",
-                         data_set = "dat.prepan")
-kable(gad_prepan_model0a_employment_reg_stats)
-gad_prepan_model0a_employment_reg_stats
-```
-
-### Model 0b: Overlapping disorders, Unadjusted
-```{r gad employment sensitivity model0b sum_score prepan}
-# Regression coefficients
-gad_prepan_model0b_employment_estimates <- model0b.explan.estimates(outcome = "gad.sum_score_base",
-                         explan_var = "employment.unemployed_numeric",
-                         data_set = "dat.prepan")
-kable(gad_prepan_model0b_employment_estimates)
-gad_prepan_model0b_employment_estimates
-
-# Regression diagnostic statistics
-gad_prepan_model0b_employment_reg_stats <- model0b.explan.reg.stats(outcome = "gad.sum_score_base",
-                         explan_var = "employment.unemployed_numeric",
-                         data_set = "dat.prepan")
-kable(gad_prepan_model0b_employment_reg_stats)
-gad_prepan_model0b_employment_reg_stats
-```
-
-### Model 1a: Disorder hierarchical, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
-```{r gad employment sensitivity model1a sum_score prepan}
-# Regression coefficients
-gad_prepan_model1a_employment_estimates <- model1a.explan.estimates(outcome = "gad.sum_score_base",
-                         explan_var = "employment.unemployed_numeric",
-                         data_set = "dat.prepan")
-kable(gad_prepan_model1a_employment_estimates)
-gad_prepan_model1a_employment_estimates
-
-# Regression diagnostic statistics
-gad_prepan_model1a_employment_reg_stats <- model1a.explan.reg.stats(outcome = "gad.sum_score_base",
-                         explan_var = "employment.unemployed_numeric",
-                         data_set = "dat.prepan")
-kable(gad_prepan_model1a_employment_reg_stats)
-gad_prepan_model1a_employment_reg_stats
-```
-
-### Model 1b: Overlapping disorders, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
-```{r gad employment sensitivity model1b sum_score prepan}
-# Regression coefficients
-gad_prepan_model1b_employment_estimates <- model1b.explan.estimates(outcome = "gad.sum_score_base",
-                         explan_var = "employment.unemployed_numeric",
-                         data_set = "dat.prepan")
-kable(gad_prepan_model1b_employment_estimates)
-gad_prepan_model1b_employment_estimates
-
-# Regression diagnostic statistics
-gad_prepan_model1b_employment_reg_stats <- model1b.explan.reg.stats(outcome = "gad.sum_score_base",
-                         explan_var = "employment.unemployed_numeric",
-                         data_set = "dat.prepan")
-kable(gad_prepan_model1b_employment_reg_stats)
-gad_prepan_model1b_employment_reg_stats
-```
-
-# PHQ prepan
-## Regression: Absolute scores
-### Model 0a: Disorder_hierarchical, Unadjusted
-```{r phq employment sensitivity model0a sum_score prepan}
-# Regression coefficients
-phq_prepan_model0a_employment_estimates <- model0a.explan.estimates(outcome = "phq.sum_score_base",
-                         explan_var = "employment.unemployed_numeric",
-                         data_set = "dat.prepan")
-kable(phq_prepan_model0a_employment_estimates)
-phq_prepan_model0a_employment_estimates
-
-# Regression diagnostic statistics
-phq_prepan_model0a_employment_reg_stats <- model0a.explan.reg.stats(outcome = "phq.sum_score_base",
-                         explan_var = "employment.unemployed_numeric",
-                         data_set = "dat.prepan")
-kable(phq_prepan_model0a_employment_reg_stats)
-phq_prepan_model0a_employment_reg_stats
-```
-
-### Model 0b: Overlapping disorders, Unadjusted
-```{r phq employment sensitivity model0b sum_score prepan}
-# Regression coefficients
-phq_prepan_model0b_employment_estimates <- model0b.explan.estimates(outcome = "phq.sum_score_base",
-                         explan_var = "employment.unemployed_numeric",
-                         data_set = "dat.prepan")
-kable(phq_prepan_model0b_employment_estimates)
-phq_prepan_model0b_employment_estimates
-
-# Regression diagnostic statistics
-phq_prepan_model0b_employment_reg_stats <- model0b.explan.reg.stats(outcome = "phq.sum_score_base",
-                         explan_var = "employment.unemployed_numeric",
-                         data_set = "dat.prepan")
-kable(phq_prepan_model0b_employment_reg_stats)
-phq_prepan_model0b_employment_reg_stats
-```
-
-### Model 1a: Disorder hierarchical, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
-```{r phq employment sensitivity model1a sum_score prepan}
-# Regression coefficients
-phq_prepan_model1a_employment_estimates <- model1a.explan.estimates(outcome = "phq.sum_score_base",
-                         explan_var = "employment.unemployed_numeric",
-                         data_set = "dat.prepan")
-kable(phq_prepan_model1a_employment_estimates)
-phq_prepan_model1a_employment_estimates
-
-# Regression diagnostic statistics
-phq_prepan_model1a_employment_reg_stats <- model1a.explan.reg.stats(outcome = "phq.sum_score_base",
-                         explan_var = "employment.unemployed_numeric",
-                         data_set = "dat.prepan")
-kable(phq_prepan_model1a_employment_reg_stats)
-phq_prepan_model1a_employment_reg_stats
-```
-
-### Model 1b: Overlapping disorders, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
-```{r phq employment sensitivity model1b sum_score prepan}
-# Regression coefficients
-phq_prepan_model1b_employment_estimates <- model1b.explan.estimates(outcome = "phq.sum_score_base",
-                         explan_var = "employment.unemployed_numeric",
-                         data_set = "dat.prepan")
-kable(phq_prepan_model1b_employment_estimates)
-phq_prepan_model1b_employment_estimates
-
-# Regression diagnostic statistics
-phq_prepan_model1b_employment_reg_stats <- model1b.explan.reg.stats(outcome = "phq.sum_score_base",
-                         explan_var = "employment.unemployed_numeric",
-                         data_set = "dat.prepan")
-kable(phq_prepan_model1b_employment_reg_stats)
-phq_prepan_model1b_employment_reg_stats
-```
-
-# OCIR prepan 
-## Regression: Absolute scores
-### Model 0a: Disorder_hierarchical, Unadjusted
-```{r ocir employment sensitivity model0a sum_score prepan}
-# Regression coefficients
-ocir_prepan_model0a_employment_estimates <- model0a.explan.estimates(outcome = "ocir.sum_score_base",
-                         explan_var = "employment.unemployed_numeric",
-                         data_set = "dat.prepan")
-kable(ocir_prepan_model0a_employment_estimates)
-ocir_prepan_model0a_employment_estimates
-
-# Regression diagnostic statistics
-ocir_prepan_model0a_employment_reg_stats <- model0a.explan.reg.stats(outcome = "ocir.sum_score_base",
-                         explan_var = "employment.unemployed_numeric",
-                         data_set = "dat.prepan")
-kable(ocir_prepan_model0a_employment_reg_stats)
-ocir_prepan_model0a_employment_reg_stats
-```
-
-### Model 0b: Overlapping disorders, Unadjusted
-```{r ocir employment sensitivity model0b sum_score prepan}
-# Regression coefficients
-ocir_prepan_model0b_employment_estimates <- model0b.explan.estimates(outcome = "ocir.sum_score_base",
-                         explan_var = "employment.unemployed_numeric",
-                         data_set = "dat.prepan")
-kable(ocir_prepan_model0b_employment_estimates)
-ocir_prepan_model0b_employment_estimates
-
-# Regression diagnostic statistics
-ocir_prepan_model0b_employment_reg_stats <- model0b.explan.reg.stats(outcome = "ocir.sum_score_base",
-                         explan_var = "employment.unemployed_numeric",
-                         data_set = "dat.prepan")
-kable(ocir_prepan_model0b_employment_reg_stats)
-ocir_prepan_model0b_employment_reg_stats
-```
-
-### Model 1a: Disorder hierarchical, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
-```{r ocir employment sensitivity model1a sum_score prepan}
-# Regression coefficients
-ocir_prepan_model1a_employment_estimates <- model1a.explan.estimates(outcome = "ocir.sum_score_base",
-                         explan_var = "employment.unemployed_numeric",
-                         data_set = "dat.prepan")
-kable(ocir_prepan_model1a_employment_estimates)
-ocir_prepan_model1a_employment_estimates
-
-# Regression diagnostic statistics
-ocir_prepan_model1a_employment_reg_stats <- model1a.explan.reg.stats(outcome = "ocir.sum_score_base",
-                         explan_var = "employment.unemployed_numeric",
-                         data_set = "dat.prepan")
-kable(ocir_prepan_model1a_employment_reg_stats)
-ocir_prepan_model1a_employment_reg_stats
-```
-
-### Model 1b: Overlapping disorders, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
-```{r ocir employment sensitivity model1b sum_score prepan}
-# Regression coefficients
-ocir_prepan_model1b_employment_estimates <- model1b.explan.estimates(outcome = "ocir.sum_score_base",
-                         explan_var = "employment.unemployed_numeric",
-                         data_set = "dat.prepan")
-kable(ocir_prepan_model1b_employment_estimates)
-ocir_prepan_model1b_employment_estimates
-
-# Regression diagnostic statistics
-ocir_prepan_model1b_employment_reg_stats <- model1b.explan.reg.stats(outcome = "ocir.sum_score_base",
-                         explan_var = "employment.unemployed_numeric",
-                         data_set = "dat.prepan")
-kable(ocir_prepan_model1b_employment_reg_stats)
-ocir_prepan_model1b_employment_reg_stats
-```
-
-#PCL prepan 
-## Regression: Absolute scores
-### Model 0a: Disorder_hierarchical, Unadjusted
-```{r pcl employment sensitivty model0a sum_score prepan}
-# Regression coefficients
-pcl_prepan_model0a_employment_estimates <- model0a.explan.estimates(outcome = "pcl.sum_score_base",
-                         explan_var = "employment.unemployed_numeric",
-                         data_set = "dat.prepan")
-kable(pcl_prepan_model0a_employment_estimates)
-pcl_prepan_model0a_employment_estimates
-
-# Regression diagnostic statistics
-pcl_prepan_model0a_employment_reg_stats <- model0a.explan.reg.stats(outcome = "pcl.sum_score_base",
-                         explan_var = "employment.unemployed_numeric",
-                         data_set = "dat.prepan")
-kable(pcl_prepan_model0a_employment_reg_stats)
-pcl_prepan_model0a_employment_reg_stats
-```
-
-### Model 0b: Overlapping disorders, Unadjusted
-```{r pcl employment sensitivty model0b sum_score prepan}
-# Regression coefficients
-pcl_prepan_model0b_employment_estimates <- model0b.explan.estimates(outcome = "pcl.sum_score_base",
-                         explan_var = "employment.unemployed_numeric",
-                         data_set = "dat.prepan")
-kable(pcl_prepan_model0b_employment_estimates)
-pcl_prepan_model0b_employment_estimates
-
-# Regression diagnostic statistics
-pcl_prepan_model0b_employment_reg_stats <- model0b.explan.reg.stats(outcome = "pcl.sum_score_base",
-                         explan_var = "employment.unemployed_numeric",
-                         data_set = "dat.prepan")
-kable(pcl_prepan_model0b_employment_reg_stats)
-pcl_prepan_model0b_employment_reg_stats
-```
-
-### Model 1a: Disorder hierarchical, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
-```{r pcl employment sensitivty model1a sum_score prepan}
-# Regression coefficients
-pcl_prepan_model1a_employment_estimates <- model1a.explan.estimates(outcome = "pcl.sum_score_base",
-                         explan_var = "employment.unemployed_numeric",
-                         data_set = "dat.prepan")
-kable(pcl_prepan_model1a_employment_estimates)
-pcl_prepan_model1a_employment_estimates
-
-# Regression diagnostic statistics
-pcl_prepan_model1a_employment_reg_stats <- model1a.explan.reg.stats(outcome = "pcl.sum_score_base",
-                         explan_var = "employment.unemployed_numeric",
-                         data_set = "dat.prepan")
-kable(pcl_prepan_model1a_employment_reg_stats)
-pcl_prepan_model1a_employment_reg_stats
-```
-
-### Model 1b: Overlapping disorders, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
-```{r pcl employment sensitivty model1b sum_score prepan}
-# Regression coefficients
-pcl_prepan_model1b_employment_estimates <- model1b.explan.estimates(outcome = "pcl.sum_score_base",
-                         explan_var = "employment.unemployed_numeric",
-                         data_set = "dat.prepan")
-kable(pcl_prepan_model1b_employment_estimates)
-pcl_prepan_model1b_employment_estimates
-
-# Regression diagnostic statistics
-pcl_prepan_model1b_employment_reg_stats <- model1b.explan.reg.stats(outcome = "pcl.sum_score_base",
-                         explan_var = "employment.unemployed_numeric",
-                         data_set = "dat.prepan")
-kable(pcl_prepan_model1b_employment_reg_stats)
-pcl_prepan_model1b_employment_reg_stats
-```
-
-# SENSITIVITY based on employment change
-
-```{r create an employment change variable}
-dat.prepan <- dat.prepan %>%
-  mutate(employment_change =
-           case_when(
-             employment.unemployed_numeric == "1" ~ "Unemployed",
-             employment.became_unemployed_numeric == "1" ~ "Became Unemployed",                         
-             employment.furloughed_or_paid_leave_government_funded_numeric == "1" ~ "Furlough",
-             employment.furloughed_or_paid_leave_company_funded_numeric == "1" ~ "Furlough",    
-             employment.paid_leave_furloughed_numeric == "1" ~ "Furlough",                             
-             key_worker_numeric == "1" ~ "Key Worker",                                            
-             employment.government_work_key_workers_numeric == "1" ~ "Key Worker",                
-             employment.zerohours_contract_numeric == "1" ~ "Zero Hours Contract",                         
-             employment.retired_numeric == "1" ~ "Retired",                                   
-             employment.student_gcse_or_a_level_numeric == "1" ~ "Student",                   
-             employment.student_university_numeric == "1" ~ "Student"                        
-           )
-  )
-
-dat.prepan$employment_change <- as.factor(dat.prepan$employment_change)
-```
-
-# GAD prepan
-## Regression: Absolute scores
-### Model 0a: Disorder_hierarchical, Unadjusted
-```{r gad employment change sensitivity model0a sum_score prepan}
-# Regression coefficients
-gad_prepan_model0a_employmentchange_estimates <- model0a.explan.estimates(outcome = "gad.sum_score_base",
-                         explan_var = "employment_change",
-                         data_set = "dat.prepan")
-kable(gad_prepan_model0a_employmentchange_estimates)
-gad_prepan_model0a_employmentchange_estimates
-
-# Regression diagnostic statistics
-gad_prepan_model0a_employmentchange_reg_stats <- model0a.explan.reg.stats(outcome = "gad.sum_score_base",
-                         explan_var = "employment_change",
-                         data_set = "dat.prepan")
-kable(gad_prepan_model0a_employmentchange_reg_stats)
-gad_prepan_model0a_employmentchange_reg_stats
-```
-
-### Model 0b: Overlapping disorders, Unadjusted
-```{r gad employment change sensitivity model0b sum_score prepan}
-# Regression coefficients
-gad_prepan_model0b_employmentchange_estimates <- model0b.explan.estimates(outcome = "gad.sum_score_base",
-                         explan_var = "employment_change",
-                         data_set = "dat.prepan")
-kable(gad_prepan_model0b_employmentchange_estimates)
-gad_prepan_model0b_employmentchange_estimates
-
-# Regression diagnostic statistics
-gad_prepan_model0b_employmentchange_reg_stats <- model0b.explan.reg.stats(outcome = "gad.sum_score_base",
-                         explan_var = "employment_change",
-                         data_set = "dat.prepan")
-kable(gad_prepan_model0b_employmentchange_reg_stats)
-gad_prepan_model0b_employmentchange_reg_stats
-```
-
-### Model 1a: Disorder hierarchical, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
-```{r gad employment change sensitivity model1a sum_score prepan}
-# Regression coefficients
-gad_prepan_model1a_employmentchange_estimates <- model1a.explan.estimates(outcome = "gad.sum_score_base",
-                         explan_var = "employment_change",
-                         data_set = "dat.prepan")
-kable(gad_prepan_model1a_employmentchange_estimates)
-gad_prepan_model1a_employmentchange_estimates
-
-# Regression diagnostic statistics
-gad_prepan_model1a_employmentchange_reg_stats <- model1a.explan.reg.stats(outcome = "gad.sum_score_base",
-                         explan_var = "employment_change",
-                         data_set = "dat.prepan")
-kable(gad_prepan_model1a_employmentchange_reg_stats)
-gad_prepan_model1a_employmentchange_reg_stats
-```
-
-### Model 1b: Overlapping disorders, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
-```{r gad employment change sensitivity model1b sum_score prepan}
-# Regression coefficients
-gad_prepan_model1b_employmentchange_estimates <- model1b.explan.estimates(outcome = "gad.sum_score_base",
-                         explan_var = "employment_change",
-                         data_set = "dat.prepan")
-kable(gad_prepan_model1b_employmentchange_estimates)
-gad_prepan_model1b_employmentchange_estimates
-
-# Regression diagnostic statistics
-gad_prepan_model1b_employmentchange_reg_stats <- model1b.explan.reg.stats(outcome = "gad.sum_score_base",
-                         explan_var = "employment_change",
-                         data_set = "dat.prepan")
-kable(gad_prepan_model1b_employmentchange_reg_stats)
-gad_prepan_model1b_employmentchange_reg_stats
-```
-
-# PHQ prepan
-## Regression: Absolute scores
-### Model 0a: Disorder_hierarchical, Unadjusted
-```{r phq employment change sensitivity model0a sum_score prepan}
-# Regression coefficients
-phq_prepan_model0a_employmentchange_estimates <- model0a.explan.estimates(outcome = "phq.sum_score_base",
-                         explan_var = "employment_change",
-                         data_set = "dat.prepan")
-kable(phq_prepan_model0a_employmentchange_estimates)
-phq_prepan_model0a_employmentchange_estimates
-
-# Regression diagnostic statistics
-phq_prepan_model0a_employmentchange_reg_stats <- model0a.explan.reg.stats(outcome = "phq.sum_score_base",
-                         explan_var = "employment_change",
-                         data_set = "dat.prepan")
-kable(phq_prepan_model0a_employmentchange_reg_stats)
-phq_prepan_model0a_employmentchange_reg_stats
-```
-
-### Model 0b: Overlapping disorders, Unadjusted
-```{r phq employment change sensitivity model0b sum_score prepan}
-# Regression coefficients
-phq_prepan_model0b_employmentchange_estimates <- model0b.explan.estimates(outcome = "phq.sum_score_base",
-                         explan_var = "employment_change",
-                         data_set = "dat.prepan")
-kable(phq_prepan_model0b_employmentchange_estimates)
-phq_prepan_model0b_employmentchange_estimates
-
-# Regression diagnostic statistics
-phq_prepan_model0b_employmentchange_reg_stats <- model0b.explan.reg.stats(outcome = "phq.sum_score_base",
-                         explan_var = "employment_change",
-                         data_set = "dat.prepan")
-kable(phq_prepan_model0b_employmentchange_reg_stats)
-phq_prepan_model0b_employmentchange_reg_stats
-```
-
-### Model 1a: Disorder hierarchical, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
-```{r phq employment change sensitivity model1a sum_score prepan}
-# Regression coefficients
-phq_prepan_model1a_employmentchange_estimates <- model1a.explan.estimates(outcome = "phq.sum_score_base",
-                         explan_var = "employment_change",
-                         data_set = "dat.prepan")
-kable(phq_prepan_model1a_employmentchange_estimates)
-phq_prepan_model1a_employmentchange_estimates
-
-# Regression diagnostic statistics
-phq_prepan_model1a_employmentchange_reg_stats <- model1a.explan.reg.stats(outcome = "phq.sum_score_base",
-                         explan_var = "employment_change",
-                         data_set = "dat.prepan")
-kable(phq_prepan_model1a_employmentchange_reg_stats)
-phq_prepan_model1a_employmentchange_reg_stats
-```
-
-### Model 1b: Overlapping disorders, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
-```{r phq employment change sensitivity model1b sum_score prepan}
-# Regression coefficients
-phq_prepan_model1b_employmentchange_estimates <- model1b.explan.estimates(outcome = "phq.sum_score_base",
-                         explan_var = "employment_change",
-                         data_set = "dat.prepan")
-kable(phq_prepan_model1b_employmentchange_estimates)
-phq_prepan_model1b_employmentchange_estimates
-
-# Regression diagnostic statistics
-phq_prepan_model1b_employmentchange_reg_stats <- model1b.explan.reg.stats(outcome = "phq.sum_score_base",
-                         explan_var = "employment_change",
-                         data_set = "dat.prepan")
-kable(phq_prepan_model1b_employmentchange_reg_stats)
-phq_prepan_model1b_employmentchange_reg_stats
-```
-
-# OCIR prepan 
-## Regression: Absolute scores
-### Model 0a: Disorder_hierarchical, Unadjusted
-```{r ocir employment change sensitivity model0a sum_score prepan}
-# Regression coefficients
-ocir_prepan_model0a_employmentchange_estimates <- model0a.explan.estimates(outcome = "ocir.sum_score_base",
-                         explan_var = "employment_change",
-                         data_set = "dat.prepan")
-kable(ocir_prepan_model0a_employmentchange_estimates)
-ocir_prepan_model0a_employmentchange_estimates
-
-# Regression diagnostic statistics
-ocir_prepan_model0a_employmentchange_reg_stats <- model0a.explan.reg.stats(outcome = "ocir.sum_score_base",
-                         explan_var = "employment_change",
-                         data_set = "dat.prepan")
-kable(ocir_prepan_model0a_employmentchange_reg_stats)
-ocir_prepan_model0a_employmentchange_reg_stats
-```
-
-### Model 0b: Overlapping disorders, Unadjusted
-```{r ocir employment change sensitivity model0b sum_score prepan}
-# Regression coefficients
-ocir_prepan_model0b_employmentchange_estimates <- model0b.explan.estimates(outcome = "ocir.sum_score_base",
-                         explan_var = "employment_change",
-                         data_set = "dat.prepan")
-kable(ocir_prepan_model0b_employmentchange_estimates)
-ocir_prepan_model0b_employmentchange_estimates
-
-# Regression diagnostic statistics
-ocir_prepan_model0b_employmentchange_reg_stats <- model0b.explan.reg.stats(outcome = "ocir.sum_score_base",
-                         explan_var = "employment_change",
-                         data_set = "dat.prepan")
-kable(ocir_prepan_model0b_employmentchange_reg_stats)
-ocir_prepan_model0b_employmentchange_reg_stats
-```
-
-### Model 1a: Disorder hierarchical, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
-```{r ocir employment change sensitivity model1a sum_score prepan}
-# Regression coefficients
-ocir_prepan_model1a_employmentchange_estimates <- model1a.explan.estimates(outcome = "ocir.sum_score_base",
-                         explan_var = "employment_change",
-                         data_set = "dat.prepan")
-kable(ocir_prepan_model1a_employmentchange_estimates)
-ocir_prepan_model1a_employmentchannge_estimates
-
-# Regression diagnostic statistics
-ocir_prepan_model1a_employmentchange_reg_stats <- model1a.explan.reg.stats(outcome = "ocir.sum_score_base",
-                         explan_var = "employment_change",
-                         data_set = "dat.prepan")
-kable(ocir_prepan_model1a_employmentchange_reg_stats)
-ocir_prepan_model1a_employmentchange_reg_stats
-```
-
-### Model 1b: Overlapping disorders, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
-```{r ocir employment change sensitivity model1b sum_score prepan}
-# Regression coefficients
-ocir_prepan_model1b_employmentchange_estimates <- model1b.explan.estimates(outcome = "ocir.sum_score_base",
-                         explan_var = "employment_change",
-                         data_set = "dat.prepan")
-kable(ocir_prepan_model1b_employmentchange_estimates)
-ocir_prepan_model1b_employmentchange_estimates
-
-# Regression diagnostic statistics
-ocir_prepan_model1b_employmentchange_reg_stats <- model1b.explan.reg.stats(outcome = "ocir.sum_score_base",
-                         explan_var = "employment_change",
-                         data_set = "dat.prepan")
-kable(ocir_prepan_model1b_employmentchange_reg_stats)
-ocir_prepan_model1b_employmentchange_reg_stats
-```
-
-#PCL prepan 
-## Regression: Absolute scores
-### Model 0a: Disorder_hierarchical, Unadjusted
-```{r pcl employment change sensitivty model0a sum_score prepan}
-# Regression coefficients
-pcl_prepan_model0a_employmentchange_estimates <- model0a.explan.estimates(outcome = "pcl.sum_score_base",
-                         explan_var = "employment_change",
-                         data_set = "dat.prepan")
-kable(pcl_prepan_model0a_employmentchange_estimates)
-pcl_prepan_model0a_employmentchange_estimates
-
-# Regression diagnostic statistics
-pcl_prepan_model0a_employmentchange_reg_stats <- model0a.explan.reg.stats(outcome = "pcl.sum_score_base",
-                         explan_var = "employment_change",
-                         data_set = "dat.prepan")
-kable(pcl_prepan_model0a_employmentchange_reg_stats)
-pcl_prepan_model0a_employmentchange_reg_stats
-```
-
-### Model 0b: Overlapping disorders, Unadjusted
-```{r pcl employment change sensitivty model0b sum_score prepan}
-# Regression coefficients
-pcl_prepan_model0b_employmentchange_estimates <- model0b.explan.estimates(outcome = "pcl.sum_score_base",
-                         explan_var = "employment_change",
-                         data_set = "dat.prepan")
-kable(pcl_prepan_model0b_employmentchange_estimates)
-pcl_prepan_model0b_employmentchange_estimates
-
-# Regression diagnostic statistics
-pcl_prepan_model0b_employmentchange_reg_stats <- model0b.explan.reg.stats(outcome = "pcl.sum_score_base",
-                         explan_var = "employment_change",
-                         data_set = "dat.prepan")
-kable(pcl_prepan_model0b_employmentchange_reg_stats)
-pcl_prepan_model0b_employmentchange_reg_stats
-```
-
-### Model 1a: Disorder hierarchical, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
-```{r pcl employment change sensitivty model1a sum_score prepan}
-# Regression coefficients
-pcl_prepan_model1a_employmentchange_estimates <- model1a.explan.estimates(outcome = "pcl.sum_score_base",
-                         explan_var = "employment_change",
-                         data_set = "dat.prepan")
-kable(pcl_prepan_model1a_employmentchange_estimates)
-pcl_prepan_model1a_employmentchange_estimates
-
-# Regression diagnostic statistics
-pcl_prepan_model1a_employmentchange_reg_stats <- model1a.explan.reg.stats(outcome = "pcl.sum_score_base",
-                         explan_var = "employment_change",
-                         data_set = "dat.prepan")
-kable(pcl_prepan_model1a_employmentchange_reg_stats)
-pcl_prepan_model1a_employmentchange_reg_stats
-```
-
-### Model 1b: Overlapping disorders, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
-```{r pcl employment change sensitivty model1b sum_score prepan}
-# Regression coefficients
-pcl_prepan_model1b_employmentchange_estimates <- model1b.explan.estimates(outcome = "pcl.sum_score_base",
-                         explan_var = "employment_change",
-                         data_set = "dat.prepan")
-kable(pcl_prepan_model1b_employmentchange_estimates)
-pcl_prepan_model1b_employmentchange_estimates
-
-# Regression diagnostic statistics
-pcl_prepan_model1b_employmentchange_reg_stats <- model1b.explan.reg.stats(outcome = "pcl.sum_score_base",
-                         explan_var = "employment_change",
-                         data_set = "dat.prepan")
-kable(pcl_prepan_model1b_employmentchange_reg_stats)
-pcl_prepan_model1b_employmentchange_reg_stats
-```

### 2020-11-09 PANCHANGE_analysis.Rmd

@@
 dim(dat_age_sensitivity)
+```
+
+Sensitivity analysis for individuals who signed up to GLAD (prepan) either 3, 6 or 9 months before the pendemic began. 
+```{r subsample for pre-pan sensitivity analysis}
+# Participants who signed up in the three months before the pandemic began
+dat.prepan_sensitivity_3months <- dat %>%
+  filter(
+    ((data_group_gad == "Baseline and retrospective data" |
+      data_group_gad == "Prepandemic and baseline data" |
+      data_group_gad == "All prepandemic, baseline and retrospective data") |
+      (data_group_phq == "Baseline and retrospective data" |
+      data_group_phq == "Prepandemic and baseline data" |
+      data_group_phq == "All prepandemic, baseline and retrospective data") |
+      (data_group_pcl == "Baseline and retrospective data" |
+      data_group_pcl == "Prepandemic and baseline data" |
+      data_group_pcl == "All prepandemic, baseline and retrospective data") |
+      (data_group_ocir == "Baseline and retrospective data" |
+      data_group_ocir == "Prepandemic and baseline data" |
+      data_group_ocir == "All prepandemic, baseline and retrospective data")) &
+      prepandemic_3_months_numeric == 1 # Only participants who signed up between December 1st 2019 and March 1st 2020
+  )
+
+# Participants who signed up in the three months before the pandemic began
+dat.prepan_sensitivity_6months <- dat %>%
+  filter(
+    ((data_group_gad == "Baseline and retrospective data" |
+      data_group_gad == "Prepandemic and baseline data" |
+      data_group_gad == "All prepandemic, baseline and retrospective data") |
+      (data_group_phq == "Baseline and retrospective data" |
+      data_group_phq == "Prepandemic and baseline data" |
+      data_group_phq == "All prepandemic, baseline and retrospective data") |
+      (data_group_pcl == "Baseline and retrospective data" |
+      data_group_pcl == "Prepandemic and baseline data" |
+      data_group_pcl == "All prepandemic, baseline and retrospective data") |
+      (data_group_ocir == "Baseline and retrospective data" |
+      data_group_ocir == "Prepandemic and baseline data" |
+      data_group_ocir == "All prepandemic, baseline and retrospective data")) &
+      prepandemic_6_months_numeric == 1 # Only participants who signed up between September 1st 2019 and March 1st 2020
+  )
+
+# Participants who signed up in the three months before the pandemic began
+dat.prepan_sensitivity_9months <- dat %>%
+  filter(
+    ((data_group_gad == "Baseline and retrospective data" |
+      data_group_gad == "Prepandemic and baseline data" |
+      data_group_gad == "All prepandemic, baseline and retrospective data") |
+      (data_group_phq == "Baseline and retrospective data" |
+      data_group_phq == "Prepandemic and baseline data" |
+      data_group_phq == "All prepandemic, baseline and retrospective data") |
+      (data_group_pcl == "Baseline and retrospective data" |
+      data_group_pcl == "Prepandemic and baseline data" |
+      data_group_pcl == "All prepandemic, baseline and retrospective data") |
+      (data_group_ocir == "Baseline and retrospective data" |
+      data_group_ocir == "Prepandemic and baseline data" |
+      data_group_ocir == "All prepandemic, baseline and retrospective data")) &
+      prepandemic_9_months_numeric == 1 # Only participants who signed up between June 1st 2019 and March 1st 2020
+  )
+
 ```
@@
 ```
+# GAD prepan: sensitivity
+## Regression: Absolute scores
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
+#### Subset of participants 3 months prior to pandemic
+```{r gad model1b sum_score prepan - sensitivity 3 months}
+# Regression coefficients
+gad_prepan_model1b_explan_estimates <- model1b.explan.estimates(outcome = "gad.sum_score_base",
+                         explan_var = "gad.sum_score_prepan",
+                         data_set = "dat.prepan_sensitivity_3months")
+kable(gad_prepan_model1b_explan_estimates)
+gad_prepan_model1b_explan_estimates
+
+# Regression diagnostic statistics
+gad_prepan_model1b_explan_reg_stats <- model1b.explan.reg.stats(outcome = "gad.sum_score_base",
+                         explan_var = "gad.sum_score_prepan",
+                         data_set = "dat.prepan_sensitivity_3months")
+kable(gad_prepan_model1b_explan_reg_stats)
+gad_prepan_model1b_explan_reg_stats
+```
+
+#### Subset of participants 6 months prior to pandemic
+```{r gad model1b sum_score prepan - sensitivity 6 months}
+# Regression coefficients
+gad_prepan_model1b_explan_estimates <- model1b.explan.estimates(outcome = "gad.sum_score_base",
+                         explan_var = "gad.sum_score_prepan",
+                         data_set = "dat.prepan_sensitivity_6months")
+kable(gad_prepan_model1b_explan_estimates)
+gad_prepan_model1b_explan_estimates
+
+# Regression diagnostic statistics
+gad_prepan_model1b_explan_reg_stats <- model1b.explan.reg.stats(outcome = "gad.sum_score_base",
+                         explan_var = "gad.sum_score_prepan",
+                         data_set = "dat.prepan_sensitivity_6months")
+kable(gad_prepan_model1b_explan_reg_stats)
+gad_prepan_model1b_explan_reg_stats
+```
+
+#### Subset of participants 9 months prior to pandemic
+```{r gad model1b sum_score prepan - sensitivity 9 months}
+# Regression coefficients
+gad_prepan_model1b_explan_estimates <- model1b.explan.estimates(outcome = "gad.sum_score_base",
+                         explan_var = "gad.sum_score_prepan",
+                         data_set = "dat.prepan_sensitivity_9months")
+kable(gad_prepan_model1b_explan_estimates)
+gad_prepan_model1b_explan_estimates
+
+# Regression diagnostic statistics
+gad_prepan_model1b_explan_reg_stats <- model1b.explan.reg.stats(outcome = "gad.sum_score_base",
+                         explan_var = "gad.sum_score_prepan",
+                         data_set = "dat.prepan_sensitivity_9months")
+kable(gad_prepan_model1b_explan_reg_stats)
+gad_prepan_model1b_explan_reg_stats
+```
+##KT
 

### 2020-11-09 PANCHANGE_variable_creation.Rmd

@@
 
+Creating date variables for subset of participants dependent on when they signed up to GLAD (prepan)
+```{r date variables for subset of participants who signed up in 3, 6, 9 months prior to pandemic}
+# Date of 3 months prior to the 1st of March
+date_3months_prior_march_1st <- as.POSIXct("2019-12-01")
+
+# Date of 6 months prior to the 1st of March
+date_6months_prior_march_1st <- as.POSIXct("2019-09-01")
+
+# Date of 9 months prior to the 1st of March
+date_9months_prior_march_1st <- as.POSIXct("2019-06-01")
+```
+
+```{r subset of participants who signed up in 3 months prior to pandemic}
+dat <- dat %>%
+  mutate(
+    prepandemic_3_months_numeric =
+      if_else(
+        startDate.prepandemic > date_3months_prior_march_1st & # The GLAD sign up is dated before the cut off (> longer ago)
+        prepandemic_march_1_numeric == 1, #participant sign up before pandemic began (March 1st)
+        true = 1, # Participant signed up after December 1st 
+        false = 0, # Participant signed up before December 1st
+        missing = NA_real_
+      )
+  )
+
+dat <- dat %>%
+  mutate(
+    prepandemic_3_months =
+      recode_factor(
+        prepandemic_3_months_numeric,
+        "0" = "Sign up before 01 December",
+        "1" = "Sign up after 01 December"
+      )
+  )
+
+dat %>%
+  freq(prepandemic_3_months)
+```
+
+```{r subset of participants who signed up in 6 months prior to pandemic}
+dat <- dat %>%
+  mutate(
+    prepandemic_6_months_numeric =
+      if_else(
+        startDate.prepandemic > date_6months_prior_march_1st & # The GLAD sign up is dated before the cut off (> longer ago)
+        prepandemic_march_1_numeric == 1, #participant did not sign up after pandemic began (March 1st)
+        true = 1, # Participant signed up after September 1st 
+        false = 0, # Participant signed up before September 1st
+        missing = NA_real_
+      )
+  )
+
+dat <- dat %>%
+  mutate(
+    prepandemic_6_months =
+      recode_factor(
+        prepandemic_6_months_numeric,
+        "1" = "Sign up after 01 September",
+        "0" = "Sign up before 01 September"
+      )
+  )
+
+dat %>%
+  freq(prepandemic_6_months)
+```
+
+```{r subset of participants who signed up in 9 months prior to pandemic}
+dat <- dat %>%
+  mutate(
+    prepandemic_9_months_numeric =
+      if_else(
+        startDate.prepandemic > date_9months_prior_march_1st & # The GLAD sign up is dated before the cut off (> longer ago)
+        prepandemic_march_1_numeric == 1, #participant did not sign up after pandemic began (March 1st)
+        true = 1, # Participant signed up after June 1st 
+        false = 0, # Participant signed up before June 1st
+        missing = NA_real_
+      )
+  )
+
+dat <- dat %>%
+  mutate(
+    prepandemic_9_months =
+      recode_factor(
+        prepandemic_9_months_numeric,
+        "1" = "Sign up after 01 June",
+        "0" = "Sign up before 01 June"
+      )
+  )
+
+dat %>%
+  freq(prepandemic_9_months)
+```
+
+##Export data
 ```{r Save four cohorts as rds file}

### 2020-11-09 PANCHANGE_analysis.Rmd

@@
 
-# PCL prepan: sensitivity
+# SENSITIVITY based on highest level of education
+
+# GAD prepan
+## Regression: Absolute scores
+
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r gad education sensitivity model1b sum_score prepan}
+# Regression coefficients
+gad_prepan_model1b_education_estimates <- model1b.explan.estimates(outcome = "gad.sum_score_base",
+                         explan_var = "highest_education_numeric",
+                         data_set = "dat.prepan")
+kable(gad_prepan_model1b_education_estimates)
+gad_prepan_model1b_education_estimates
+
+# Regression diagnostic statistics
+gad_prepan_model1b_education_reg_stats <- model1b.explan.reg.stats(outcome = "gad.sum_score_base",
+                         explan_var = "highest_education_numeric",
+                         data_set = "dat.prepan")
+kable(gad_prepan_model1b_education_reg_stats)
+gad_prepan_model1b_education_reg_stats
+```
+
+# PHQ prepan
+## Regression: Absolute scores
+
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r phq education sensitivity model1b sum_score prepan}
+# Regression coefficients
+phq_prepan_model1b_education_estimates <- model1b.explan.estimates(outcome = "phq.sum_score_base",
+                         explan_var = "highest_education_numeric",
+                         data_set = "dat.prepan")
+kable(phq_prepan_model1b_education_estimates)
+phq_prepan_model1b_education_estimates
+
+# Regression diagnostic statistics
+phq_prepan_model1b_education_reg_stats <- model1b.explan.reg.stats(outcome = "phq.sum_score_base",
+                         explan_var = "highest_education_numeric",
+                         data_set = "dat.prepan")
+kable(phq_prepan_model1b_education_reg_stats)
+phq_prepan_model1b_education_reg_stats
+```
+
+# OCIR prepan 
+## Regression: Absolute scores
+
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r ocir education sensitivity model1b sum_score prepan}
+# Regression coefficients
+ocir_prepan_model1b_education_estimates <- model1b.explan.estimates(outcome = "ocir.sum_score_base",
+                         explan_var = "highest_education_numeric",
+                         data_set = "dat.prepan")
+kable(ocir_prepan_model1b_education_estimates)
+ocir_prepan_model1b_education_estimates
+
+# Regression diagnostic statistics
+ocir_prepan_model1b_education_reg_stats <- model1b.explan.reg.stats(outcome = "ocir.sum_score_base",
+                         explan_var = "highest_education_numeric",
+                         data_set = "dat.prepan")
+kable(ocir_prepan_model1b_education_reg_stats)
+ocir_prepan_model1b_education_reg_stats
+```
+
+#PCL prepan 
+## Regression: Absolute scores
+
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r pcl education sensitivty model1b sum_score prepan}
+# Regression coefficients
+pcl_prepan_model1b_education_estimates <- model1b.explan.estimates(outcome = "pcl.sum_score_base",
+                         explan_var = "highest_education_numeric",
+                         data_set = "dat.prepan")
+kable(pcl_prepan_model1b_education_estimates)
+pcl_prepan_model1b_education_estimates
+
+# Regression diagnostic statistics
+pcl_prepan_model1b_education_reg_stats <- model1b.explan.reg.stats(outcome = "pcl.sum_score_base",
+                         explan_var = "highest_education_numeric",
+                         data_set = "dat.prepan")
+kable(pcl_prepan_model1b_education_reg_stats)
+pcl_prepan_model1b_education_reg_stats
+```
+
+# SENSITIVITY based on employment status
+
+# GAD prepan
+## Regression: Absolute scores
+
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r gad employment sensitivity model1b sum_score prepan}
+# Regression coefficients
+gad_prepan_model1b_employment_estimates <- model1b.explan.estimates(outcome = "gad.sum_score_base",
+                         explan_var = "employment.unemployed_numeric",
+                         data_set = "dat.prepan")
+kable(gad_prepan_model1b_employment_estimates)
+gad_prepan_model1b_employment_estimates
+
+# Regression diagnostic statistics
+gad_prepan_model1b_employment_reg_stats <- model1b.explan.reg.stats(outcome = "gad.sum_score_base",
+                         explan_var = "employment.unemployed_numeric",
+                         data_set = "dat.prepan")
+kable(gad_prepan_model1b_employment_reg_stats)
+gad_prepan_model1b_employment_reg_stats
+```
+
+# PHQ prepan
+## Regression: Absolute scores
+
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r phq employment sensitivity model1b sum_score prepan}
+# Regression coefficients
+phq_prepan_model1b_employment_estimates <- model1b.explan.estimates(outcome = "phq.sum_score_base",
+                         explan_var = "employment.unemployed_numeric",
+                         data_set = "dat.prepan")
+kable(phq_prepan_model1b_employment_estimates)
+phq_prepan_model1b_employment_estimates
+
+# Regression diagnostic statistics
+phq_prepan_model1b_employment_reg_stats <- model1b.explan.reg.stats(outcome = "phq.sum_score_base",
+                         explan_var = "employment.unemployed_numeric",
+                         data_set = "dat.prepan")
+kable(phq_prepan_model1b_employment_reg_stats)
+phq_prepan_model1b_employment_reg_stats
+```
+
+# OCIR prepan 
+## Regression: Absolute scores
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r ocir employment sensitivity model1b sum_score prepan}
+# Regression coefficients
+ocir_prepan_model1b_employment_estimates <- model1b.explan.estimates(outcome = "ocir.sum_score_base",
+                         explan_var = "employment.unemployed_numeric",
+                         data_set = "dat.prepan")
+kable(ocir_prepan_model1b_employment_estimates)
+ocir_prepan_model1b_employment_estimates
+
+# Regression diagnostic statistics
+ocir_prepan_model1b_employment_reg_stats <- model1b.explan.reg.stats(outcome = "ocir.sum_score_base",
+                         explan_var = "employment.unemployed_numeric",
+                         data_set = "dat.prepan")
+kable(ocir_prepan_model1b_employment_reg_stats)
+ocir_prepan_model1b_employment_reg_stats
+```
+
+#PCL prepan 
+## Regression: Absolute scores
+
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r pcl employment sensitivty model1b sum_score prepan}
+# Regression coefficients
+pcl_prepan_model1b_employment_estimates <- model1b.explan.estimates(outcome = "pcl.sum_score_base",
+                         explan_var = "employment.unemployed_numeric",
+                         data_set = "dat.prepan")
+kable(pcl_prepan_model1b_employment_estimates)
+pcl_prepan_model1b_employment_estimates
+
+# Regression diagnostic statistics
+pcl_prepan_model1b_employment_reg_stats <- model1b.explan.reg.stats(outcome = "pcl.sum_score_base",
+                         explan_var = "employment.unemployed_numeric",
+                         data_set = "dat.prepan")
+kable(pcl_prepan_model1b_employment_reg_stats)
+pcl_prepan_model1b_employment_reg_stats
+```
+
+# SENSITIVITY based on employment change
+
+```{r create an employment change variable}
+dat.prepan <- dat.prepan %>%
+  mutate(employment_change =
+           case_when(
+             employment.unemployed_numeric == "1" ~ "Unemployed",
+             employment.became_unemployed_numeric == "1" ~ "Became Unemployed",                         
+             employment.furloughed_or_paid_leave_government_funded_numeric == "1" ~ "Furlough",
+             employment.furloughed_or_paid_leave_company_funded_numeric == "1" ~ "Furlough",    
+             employment.paid_leave_furloughed_numeric == "1" ~ "Furlough",                             
+             key_worker_numeric == "1" ~ "Key Worker",                                            
+             employment.government_work_key_workers_numeric == "1" ~ "Key Worker",                
+             employment.zerohours_contract_numeric == "1" ~ "Zero Hours Contract",                         
+             employment.retired_numeric == "1" ~ "Retired",                                   
+             employment.student_gcse_or_a_level_numeric == "1" ~ "Student",                   
+             employment.student_university_numeric == "1" ~ "Student"                        
+           )
+  )
+
+dat.prepan$employment_change <- as.factor(dat.prepan$employment_change)
+```
+
+# GAD prepan
+## Regression: Absolute scores
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r gad employment change sensitivity model1b sum_score prepan}
+# Regression coefficients
+gad_prepan_model1b_employmentchange_estimates <- model1b.explan.estimates(outcome = "gad.sum_score_base",
+                         explan_var = "employment_change",
+                         data_set = "dat.prepan")
+kable(gad_prepan_model1b_employmentchange_estimates)
+gad_prepan_model1b_employmentchange_estimates
+
+# Regression diagnostic statistics
+gad_prepan_model1b_employmentchange_reg_stats <- model1b.explan.reg.stats(outcome = "gad.sum_score_base",
+                         explan_var = "employment_change",
+                         data_set = "dat.prepan")
+kable(gad_prepan_model1b_employmentchange_reg_stats)
+gad_prepan_model1b_employmentchange_reg_stats
+```
+
+# PHQ prepan
+## Regression: Absolute scores
+
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r phq employment change sensitivity model1b sum_score prepan}
+# Regression coefficients
+phq_prepan_model1b_employmentchange_estimates <- model1b.explan.estimates(outcome = "phq.sum_score_base",
+                         explan_var = "employment_change",
+                         data_set = "dat.prepan")
+kable(phq_prepan_model1b_employmentchange_estimates)
+phq_prepan_model1b_employmentchange_estimates
+
+# Regression diagnostic statistics
+phq_prepan_model1b_employmentchange_reg_stats <- model1b.explan.reg.stats(outcome = "phq.sum_score_base",
+                         explan_var = "employment_change",
+                         data_set = "dat.prepan")
+kable(phq_prepan_model1b_employmentchange_reg_stats)
+phq_prepan_model1b_employmentchange_reg_stats
+```
+
+# OCIR prepan 
+## Regression: Absolute scores
+
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r ocir employment change sensitivity model1b sum_score prepan}
+# Regression coefficients
+ocir_prepan_model1b_employmentchange_estimates <- model1b.explan.estimates(outcome = "ocir.sum_score_base",
+                         explan_var = "employment_change",
+                         data_set = "dat.prepan")
+kable(ocir_prepan_model1b_employmentchange_estimates)
+ocir_prepan_model1b_employmentchange_estimates
+
+# Regression diagnostic statistics
+ocir_prepan_model1b_employmentchange_reg_stats <- model1b.explan.reg.stats(outcome = "ocir.sum_score_base",
+                         explan_var = "employment_change",
+                         data_set = "dat.prepan")
+kable(ocir_prepan_model1b_employmentchange_reg_stats)
+ocir_prepan_model1b_employmentchange_reg_stats
+```
+
+#PCL prepan 
+## Regression: Absolute scores
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r pcl employment change sensitivty model1b sum_score prepan}
+# Regression coefficients
+pcl_prepan_model1b_employmentchange_estimates <- model1b.explan.estimates(outcome = "pcl.sum_score_base",
+                         explan_var = "employment_change",
+                         data_set = "dat.prepan")
+kable(pcl_prepan_model1b_employmentchange_estimates)
+pcl_prepan_model1b_employmentchange_estimates
+
+# Regression diagnostic statistics
+pcl_prepan_model1b_employmentchange_reg_stats <- model1b.explan.reg.stats(outcome = "pcl.sum_score_base",
+                         explan_var = "employment_change",
+                         data_set = "dat.prepan")
+kable(pcl_prepan_model1b_employmentchange_reg_stats)
+pcl_prepan_model1b_employmentchange_reg_stats
+```
+
+# Sensitivity based on GLAD sign up
+#PCL prepan: sensitivity
 ## Regression: Absolute scores

### 2020-11-09 PANCHANGE_data_preprocessing2020-07-15.Rmd

@@
 ```{r Specify cohort}
-GLAD = FALSE
-EDGI = FALSE
+GLAD = TRUE
+EDGI = TRUE
 NBR = FALSE
-RAMP = TRUE
+RAMP = FALSE
+GLAD_and_EDGI = TRUE
 ```
@@
 
+## GLAD and EDGI
+### Create data frame 
+```{r GLAD and EDGI combined}
+glad.and.edgi.dem.raw.id <- rbind(glad.dem.raw.id, edgi.dem.raw.id)
+```
+
+```{r glad and edgi copy dem}
+if(GLAD_and_EDGI == TRUE){
+  dem.raw.id <- glad.and.edgi.dem.raw.id
+}
+```
+
+### Get summary of combined GLAD and EDI
+```{r glad and edgi demographics summary}
+if(GLAD_and_EDGI == TRUE) {
+summarytools::dfSummary(
+  dem.raw.id,
+  graph.col = F,
+  valid.col = F,
+  labels.col = F)
+}
+```
+
 ## NBR
@@
 if(NBR == TRUE) {
+
+dem.raw.id <- dem.raw.id %>%
+  mutate(
+    Ethnicity = 
+      recode_factor(Ethnicity_unc,
+        "White, white European or Caucasian" = "White",
+        "Mixed or multiple ethnic origins" = "Mixed or multiple ethnic origins",
+        "Asian or Asian British (including Chinese)" = "Asian or Asian British",
+        "Black or Black British" = "Black or Black British",
+        "Arab" = "Arab",
+        "Other ethnic group (please specify)" = "Other ethnic group"
+      )
+  ) %>%
+  mutate(
+    Ethnicity_numeric = 
+      recode(Ethnicity,
+        "White" = 1,
+        "Mixed or multiple ethnic origins" = 2,
+        "Asian or Asian British" = 3,
+        "Black or Black British" = 4,
+        "Arab" = 5,
+        "Other ethnic group" = 6
+      )
+  )
+}
+```
+
+```{r ethnicity recoding for GLAD and EDGI combined}
+if(GLAD_and_EDGI == TRUE) {
 

### 2020-11-09 PANNEURO_analysis_WHO_pres.Rmd

--- 2020-10-27 PANNEURO_analysis_WHO_pres.Rmd
@@
       collapsed: no
-  pdf_document:
+
+  word_document:
     toc: yes
     toc_depth: '2'
-  word_document:
+  pdf_document:
+
     toc: yes
@@
 ```
-
-## Smoking
-
-## Key worker status
 

### 2020-11-09 PANNEURO_preprocessing_BMI_WHO-pres.Rmd

@@
 
+nbr.bmi.raw$Sample <- c("NBR")
+
+nbr.bmi.raw$height.2[ nbr.bmi.raw$height.2>300 ] <- NA
+nbr.bmi.raw$height.2[ nbr.bmi.raw$height.2<20 ] <- NA
+nbr.bmi.raw$height.1[ nbr.bmi.raw$height.1>15 ] <- NA
+nbr.bmi.raw$height.1[ nbr.bmi.raw$height.1<0.1 ] <- NA
+nbr.bmi.raw$height[ nbr.bmi.raw$height>15 ] <- NA
+nbr.bmi.raw$height[ nbr.bmi.raw$height<0.1 ] <- NA
+
 # GLAD cohort
@@
          )
+
+glad.bmi.raw$height[ glad.bmi.raw$height>300 ] <- NA
+glad.bmi.raw$height[ glad.bmi.raw$height<20 ] <- NA
+glad.bmi.raw$height.1[ glad.bmi.raw$height.1>15 ] <- NA
+glad.bmi.raw$height.1[ glad.bmi.raw$height.1<0.1 ] <- NA
+glad.bmi.raw$height.2[ glad.bmi.raw$height.2>15 ] <- NA
+glad.bmi.raw$height.2[ glad.bmi.raw$height.2<0.1 ] <- NA
 
@@
          )
+
+edgi.bmi.raw$height.2[ edgi.bmi.raw$height.2>300 ] <- NA
+edgi.bmi.raw$height.2[ edgi.bmi.raw$height.2<20 ] <- NA
+edgi.bmi.raw$height.1[ edgi.bmi.raw$height.1>15 ] <- NA
+edgi.bmi.raw$height.1[ edgi.bmi.raw$height.1<0.1 ] <- NA
+edgi.bmi.raw$height[ edgi.bmi.raw$height>15 ] <- NA
+edgi.bmi.raw$height[ edgi.bmi.raw$height<0.1 ] <- NA
 
@@
 nbr.bmi.raw$bmi <- nbr.bmi.raw$kg_all / (nbr.bmi.raw$cm_whole^2)
-nbr.bmi.raw$bmi_new <- round(nbr.bmi.raw$bmi, digits = 2)
-nbr.bmi.raw$bmi <- nbr.bmi.raw$bmi_new
 

### 2020-11-10 PANCHANGE_exclusion_descriptives.Rmd
Made the correlations for prepan and retro gad scores and their scatterplots

@@
 #install.packages("patchwork")
-#install.packages("ggpubr")
+#instlal.packages("ggpubr")
 ```
@@
 
-#HR
-
-```{r Accuray scores for gad: worse/better than pre-pandemic}
-
-dat.raw$gad.pandemic.change.group <- ifelse(dat.raw$gad.pandemic_felt_feelings_numeric <3,1,
-                                           ifelse(dat.raw$gad.pandemic_felt_feelings_numeric > 3,2,0))
-
-dat.raw$gad.pandemic.change.group <- factor(dat.raw$gad.pandemic.change.group,
-                                           levels = c(1,0,2),labels = c("Worse","No change","Better"))
-
-dat.raw <- dat.raw %>%
-    mutate(gad.change.accurate = case_when(dat.raw$gad.pandemic.change.group == "Better" &
-                                             dat.raw$gad.diff_score_base_prepan < 0 ~1,
-                                           dat.raw$gad.pandemic.change.group == "Worse" &
-                                             dat.raw$gad.diff_score_base_prepan > 0 ~ 1,
-                                           dat.raw$gad.pandemic.change.group == "Better" &
-                                             dat.raw$gad.diff_score_base_prepan > 0 ~ 0,
-                                           dat.raw$gad.pandemic.change.group == "Worse" &
-                                             dat.raw$gad.diff_score_base_prepan < 0 ~ 0))
-
-dat.raw <- dat.raw %>%
-    mutate(gad.change.retro.accurate = if_else(dat.raw$gad.pandemic.change.group == "Better" &
-                                             dat.raw$gad.diff_score_retro_prepan == 0 |
-                                             dat.raw$gad.pandemic.change.group == "Worse" &
-                                             dat.raw$gad.diff_score_retro_prepan == 0, 1, 3 ))
-dat.raw <- dat.raw %>%
-  mutate(gad.change.retro.accurate = if_else(dat.raw$gad.pandemic.change.group == "Better" &
-                                             dat.raw$gad.diff_score_retro_prepan >= -3 &
-                                             dat.raw$gad.diff_score_retro_prepan <= 3 &
-                                             dat.raw$gad.change.retro.accurate_temp != 1 |
-                                             dat.raw$gad.pandemic.change.group == "Worse" &
-                                             dat.raw$gad.diff_score_retro_prepan >= -3 &
-                                             dat.raw$gad.diff_score_retro_prepan <= 3 &
-                                             dat.raw$gad.change.retro.accurate_temp != 1,  2, gad.change.retro.accurate))
-
-```
-
-#SB - Impute no change prepandemic scores
-
-I interpreted the presence of an NA in the retrospective score as an indicator of saying "no change" in their baseline scores.
-Hence, if this was the case, I imputed their baseline score.
-However, this interpretation could be wrong.
-
-Also, I'm not sure what to do if there is an NA for their baseline sum score (nothing to duplicate).
-This was the case for ocir for some reason: the retro scores were provided for some by not the corresponding baseline score?
+#Impute no change prepandemic scores
 
@@
 
+```{r function to create upper and lower CI matrices}
+
+cor.mtest <- function(mat, conf.level = 0.95){
+mat <- as.matrix(mat)
+n <- ncol(mat)
+p.mat <- lowCI.mat <- uppCI.mat <- matrix(NA, n, n)
+diag(p.mat) <- 0
+diag(lowCI.mat) <- diag(uppCI.mat) <- 1
+for(i in 1:(n-1)){
+for(j in (i+1):n){
+tmp <- cor.test(mat[,i], mat[,j], conf.level = conf.level)
+p.mat[i,j] <- p.mat[j,i] <- tmp$p.value
+lowCI.mat[i,j] <- lowCI.mat[j,i] <- tmp$conf.int[1]
+uppCI.mat[i,j] <- uppCI.mat[j,i] <- tmp$conf.int[2]
+}
+}
+return(list(p.mat, lowCI.mat, uppCI.mat))
+}
+
+```
+
 ```{r Correlation prep chunk}
@@
 
-#Create a data set with only the COPING samples
-prepan_retro_dat <- dat[str_detect(dat$Sample, "NBR|GLAD|EDGI"), ]
-
-#Check that RAMP has been removed
+#Create a data set with only the GLAD and EDGI
+prepan_retro_dat <- dat[str_detect(dat$Sample, "GLAD|EDGI"), ]
+
+#Check that RAMP and NBR has been removed
 prepan_retro_dat %>% 
@@
 prepan_retro.p.matrix <- as.matrix(prepan_retro.corr.mat$tests)
+
+res1 <- cor.ci(prepan_retro.corr.matrix)
+lowci <- cor.plot.upperLowerCi(res1)
+lowci[upper.tri(lowci)] = t(lowci)[upper.tri(lowci)]
+
+upci <- cor.plot.upperLowerCi(res1)
+upci[lower.tri(upci)] = t(upci)[lower.tri(lowci)]
+
+conf <- paste0("[", format(lowci, digits=2), " - ", format(upci, digits=2), "]")
+
+xs <- row(lowci)
+ys <- (ncol(lowci)+1) - col(lowci)
+
+xs[lower.tri(xs,diag=TRUE)] <- 0
+ys[lower.tri(ys,diag=TRUE)] <- 0
+
 ```
@@
          )
+
+text(xs, ys, conf, pos=1, cex=0.8)
+
+```
+
+#Scatterplots for self-report pandemic change
+
+```{r Scatterplots for gad self-reported change individually}
+
+#Filter by self-reported change since pandemic started
+
+much_worse_gad <- dat %>% 
+  filter(gad.pandemic_felt_feelings == "Much worse")
+
+little_worse_gad <- dat %>% 
+  filter(gad.pandemic_felt_feelings == "A little worse")
+
+little_better_gad <- dat %>% 
+  filter(gad.pandemic_felt_feelings == "A little better")
+
+much_better_gad <- dat %>% 
+  filter(gad.pandemic_felt_feelings == "Much better")
+
+#Visualise each as a scatterplot
+
+much_worse_gad %>% ggplot(aes(x = gad.sum_score_prepan, y = gad.sum_score_retro)) +
+  geom_point(colour = "blue") +
+  stat_smooth(method = "lm") +
+  geom_jitter(w = 0.4, h = 0.4) +
+   labs(title = paste("Relationship between prepandemc and retrospective GAD scores\nfor participants reporting much worse",
+                      sep=" "),
+        subtitle = paste("n", dim(much_worse_gad)[1]))
+
+little_worse_gad %>% ggplot(aes(x = gad.sum_score_prepan, y = gad.sum_score_retro)) +
+  geom_point(colour = "blue") +
+  stat_smooth(method = "lm") +
+  geom_jitter(w = 0.4, h = 0.4) +
+   labs(title = paste("Relationship between prepandemc and retrospective GAD scores\nfor participants reporting a little worse",
+                      sep=" "),
+        subtitle = paste("n", dim(little_worse_gad)[1]))
+
+little_better_gad %>% ggplot(aes(x = gad.sum_score_prepan, y = gad.sum_score_retro)) +
+  geom_point(colour = "blue") +
+  stat_smooth(method = "lm") +
+  geom_jitter(w = 0.4, h = 0.4) +
+   labs(title = paste("Relationship between prepandemc and retrospective GAD scores\nfor participants reporting a little better",
+                      sep=" "),
+        subtitle = paste("n", dim(little_better_gad)[1]))
+
+much_better_gad %>% ggplot(aes(x = gad.sum_score_prepan, y = gad.sum_score_retro)) +
+  geom_point(colour = "blue") +
+  stat_smooth(method = "lm") +
+  geom_jitter(w = 0.4, h = 0.4) +
+   labs(title = paste("Relationship between prepandemc and retrospective GAD scores\nfor participants reporting a little worse",
+                      sep=" "),
+        subtitle = paste("n", dim(much_better_gad)[1]))
+
+```
+
+```{r Scatterplots for gad worse and better grouped}
+
+#Group pt reporting much worse and a little worse, and group pt reporting much better and a little better
+
+much_worse_little_worse_gad <- dat %>% 
+  filter(gad.pandemic_felt_feelings == "Much worse" | 
+           gad.pandemic_felt_feelings == "A little worse")
+
+much_better_little_better_gad <- dat %>% 
+  filter(gad.pandemic_felt_feelings == "Much better" | 
+           gad.pandemic_felt_feelings == "A little better")
+
+#Visualise the gad sum scores as scatterplots
+
+much_worse_little_worse_gad %>% ggplot(aes(x = gad.sum_score_prepan, y = gad.sum_score_retro)) +  geom_point(colour = "blue") +
+  stat_smooth(method = "lm") +
+  geom_jitter(w = 0.4, h = 0.4) +
+   labs(title = paste("Relationship between prepandemc and retrospective GAD scores\nfor participants reporting much worse and a little worse",
+                      sep=" "),
+        subtitle = paste("n", dim(much_worse_little_worse_gad)[1]))
+
+much_better_little_better_gad %>% ggplot(aes(x = gad.sum_score_prepan, y = gad.sum_score_retro)) +
+  geom_point(colour = "blue") +
+  stat_smooth(method = "lm") + 
+  geom_jitter(w = 0.4, h = 0.4) +
+   labs(title = paste("Relationship between prepandemc and retrospective GAD scores\nfor participants reporting much better and a little better",
+                      sep=" "),
+        subtitle = paste("n", dim(much_better_little_better_gad)[1]))
+
 ```

### 2020-11-10 PANCHANGE_data_preprocessing2020-07-15.Rmd
Fixed some minor errors for NBR cohort

@@
 ```{r Specify cohort}
-GLAD = TRUE
-EDGI = TRUE
-NBR = FALSE
+GLAD = FALSE
+EDGI = FALSE
+NBR = TRUE
 RAMP = FALSE
-GLAD_and_EDGI = TRUE
+GLAD_and_EDGI = FALSE
 ```
@@
 #source raw data directory: data.raw_path
-source("/Users/alishpalmos/Documents/GitHub//PANCHANGE_raw_path.R")
+source("..//PANCHANGE_raw_path.R")
 ```

### 2020-11-10 PANCHANGE_data_preprocessing2020-07-15.Rmd
Knitted NBR for preprocessing script and GLAD for same script (new html produced)

@@
 ```{r GLAD and EDGI combined}
+if(GLAD_and_EDGI == TRUE){
 glad.and.edgi.dem.raw.id <- rbind(glad.dem.raw.id, edgi.dem.raw.id)
+}
 ```

### 2020-11-10 PANCHANGE_analysis.Rmd
Knitted edgi preprocessing script

@@
 ### Model 0a: Disorder_hierarchical, Unadjusted
+
+#SB Hashing out this chunk of code as it is not included in our final analysis and is currently breaking the code.
 ```{r gad model0a absolute whole sample}
 # Regression coefficients
-gad_baseline_model0a_estimates <- model0a.estimates(outcome = "gad.sum_score_base",
-                                                 data_set = "dat")
-kable(gad_baseline_model0a_estimates)
-gad_baseline_model0a_estimates
-
-# Regression diagnostic statistics
-gad_baseline_model0a_reg_stats <- model0a.reg.stats(outcome = "gad.sum_score_base",
-                                                 data_set = "dat")
-kable(gad_baseline_model0a_reg_stats)
-gad_baseline_model0a_reg_stats
+#gad_baseline_model0a_estimates <- model0a.estimates(outcome = "gad.sum_score_base",
+ #                                                data_set = "dat")
+#kable(gad_baseline_model0a_estimates)
+#gad_baseline_model0a_estimates
+
+# Regression diagnostic statistics
+#gad_baseline_model0a_reg_stats <- model0a.reg.stats(outcome = "gad.sum_score_base",
+  #                                               data_set = "dat")
+#kable(gad_baseline_model0a_reg_stats)
+#gad_baseline_model0a_reg_stats
 ```

### 2020-11-11 PANCHANGE_exclusion_descriptives.Rmd
Added cor plot and scatterplots for little/much worse gad retro prepan

--- 2020-11-06 PANCHANGE_exclusion_descriptives.Rmd
@@
 
-I interpreted the presence of an NA in the retrospective score as an indicator of saying "no change" in their baseline scores.
-Hence, if this was the case, I imputed their baseline score.
-However, this interpretation could be wrong.
-
-Also, I'm not sure what to do if there is an NA for their baseline sum score (nothing to duplicate).
-This was the case for ocir for some reason: the retro scores were provided for some by not the corresponding baseline score?
-
 ```{r Impute for gad measure}
@@
 
-#Correlation between retropsective impute and prepan
-
-```{r Correlation prep chunk}
+#Correlation between whole sample retro impute and prepan
+##Create function to use for all of the corplots
+
+```{r function to create upper and lower CI matrices}
+
+cor.mtest <- function(mat, conf.level = 0.95){
+mat <- as.matrix(mat)
+n <- ncol(mat)
+p.mat <- lowCI.mat <- uppCI.mat <- matrix(NA, n, n)
+diag(p.mat) <- 0
+diag(lowCI.mat) <- diag(uppCI.mat) <- 1
+for(i in 1:(n-1)){
+for(j in (i+1):n){
+tmp <- cor.test(mat[,i], mat[,j], conf.level = conf.level)
+p.mat[i,j] <- p.mat[j,i] <- tmp$p.value
+lowCI.mat[i,j] <- lowCI.mat[j,i] <- tmp$conf.int[1]
+uppCI.mat[i,j] <- uppCI.mat[j,i] <- tmp$conf.int[2]
+}
+}
+return(list(p.mat, lowCI.mat, uppCI.mat))
+}
+
+```
+
+```{r Whole sample Correlation prep chunk}
 # Select items for correlation matrix
@@
 prepan_retro.p.matrix <- as.matrix(prepan_retro.corr.mat$tests)
-```
-
-```{r Correlation matrix of prepan base sum scores}
+
+res1 <- cor.ci(prepan_retro.corr.matrix)
+lowci <- cor.plot.upperLowerCi(res1)
+lowci[upper.tri(lowci)] = t(lowci)[upper.tri(lowci)]
+
+upci <- cor.plot.upperLowerCi(res1)
+upci[lower.tri(upci)] = t(upci)[lower.tri(lowci)]
+
+conf <- paste0("[", format(lowci, digits=2), " - ", format(upci, digits=2), "]")
+
+xs <- row(lowci)
+ys <- (ncol(lowci)+1) - col(lowci)
+
+xs[lower.tri(xs,diag=TRUE)] <- 0
+ys[lower.tri(ys,diag=TRUE)] <- 0
+
+```
+
+```{r Whole sample correlation matrix of prepan retro sum scores}
 corrplot(prepan_retro.corr.matrix, 
@@
          )
+
+text(xs, ys, conf, pos=1, cex=0.8)
+
+```
+
+```{r Whole sample scatterplot for gad prepan base}
+
+#Remove those saying "no different" since pandemic
+
+whole_retro_prepan_scatter <- dat %>% 
+  filter(gad.pandemic_felt_feelings == "Much worse" |
+           gad.pandemic_felt_feelings == "A little worse" |
+           gad.pandemic_felt_feelings == "A little better" |
+           gad.pandemic_felt_feelings == "Much better")
+
+whole_retro_prepan_scatter %>% ggplot(aes(x = gad.sum_score_retro, y = gad.sum_score_retro)) +
+  geom_point(colour = "blue") +
+  stat_smooth(method = "lm") +
+  geom_jitter(w = 0.4, h = 0.4)
+
+```
+
+#Correlation little/much worse prepan retro gad
+
+```{r Whole sample Correlation prep chunk}
+
+# Check the items are the same from the whole chunk
+prepan_retro_items
+
+#Create a data set with only the GLAD and EDGI
+prepan_retro_dat_worse <- dat[str_detect(dat$Sample, "GLAD|EDGI"), ]
+
+#Filter the data to only include those with self-reported little/much worse gad since pandemic
+
+prepan_retro_dat_worse <- prepan_retro_dat_worse %>% 
+  filter(gad.pandemic_felt_feelings == "A little worse" |
+           gad.pandemic_felt_feelings == "Much worse")
+
+#Check that RAMP and NBR has been removed
+prepan_retro_dat_worse %>% 
+  freq(Sample)
+
+# Calculate correlation matrix on specific columns (variables) from your data frame
+prepan_retro.corr.mat_worse <- hetcor(
+  as.data.frame(prepan_retro_dat_worse[,prepan_retro_items]), # Specify the data
+  use = "pairwise.complete.obs" # Use all pairwise observations
+)
+
+# Print the correlation matrix
+print(prepan_retro.corr.mat_worse, digits = max(3, getOption("digits") - 3))
+
+# Save the correlations from the correlation matrix in an object
+prepan_retro.corr.matrix_worse <- as.matrix(prepan_retro.corr.mat_worse)
+
+# Save the p values from the correlation matrix in an object
+prepan_retro.p.matrix_worse <- as.matrix(prepan_retro.corr.mat_worse$tests)
+
+res1 <- cor.ci(prepan_retro.corr.matrix_worse)
+lowci <- cor.plot.upperLowerCi(res1)
+lowci[upper.tri(lowci)] = t(lowci)[upper.tri(lowci)]
+
+upci <- cor.plot.upperLowerCi(res1)
+upci[lower.tri(upci)] = t(upci)[lower.tri(lowci)]
+
+conf <- paste0("[", format(lowci, digits=2), " - ", format(upci, digits=2), "]")
+
+xs <- row(lowci)
+ys <- (ncol(lowci)+1) - col(lowci)
+
+xs[lower.tri(xs,diag=TRUE)] <- 0
+ys[lower.tri(ys,diag=TRUE)] <- 0
+
+```
+
+```{r Little/much worse correlation matrix of prepan retro sum scores}
+corrplot(prepan_retro.corr.matrix_worse, 
+         method = "color", # objects to represent the correlations on plot
+         type = "lower", # only use the lower triangle of the matrix
+         diag = FALSE, # do not show the correlations on the diagonal
+         addgrid.col = NA,
+         addCoef.col = "black", # colour for the correlation coefficients in the plot
+         tl.cex = 0.8,
+         tl.col = "black",
+         col=colorRampPalette(c("dodgerblue4","white","firebrick4"))(200), # colours for correlations
+         # Combine with significance
+         p.mat = prepan_retro.p.matrix, # Matrix with p values
+         sig.level = 0.01, # Choose significant level
+         insig = "blank" # Nonsignificant correlations have no colour
+         )
+
+text(xs, ys, conf, pos=1, cex=0.8)
+
+```
+
+```{r Little/much worse scatterplots for gad}
+
+#Filter by little/much worse self-reported change since pandemic started in gad
+
+much_worse_gad <- dat %>% 
+  filter(gad.pandemic_felt_feelings == "Much worse")
+
+little_worse_gad <- dat %>% 
+  filter(gad.pandemic_felt_feelings == "A little worse")
+
+much_worse_little_worse_gad <- dat %>% 
+  filter(gad.pandemic_felt_feelings == "Much worse" | 
+           gad.pandemic_felt_feelings == "A little worse")
+
+#Visualise each as a scatterplot
+
+much_worse_gad %>% ggplot(aes(x = gad.sum_score_prepan, y = gad.sum_score_retro)) +
+  geom_point(colour = "blue") +
+  stat_smooth(method = "lm") +
+  geom_jitter(w = 0.4, h = 0.4) +
+   labs(title = paste("Relationship between prepandemic and retrospective GAD scores\nfor participants reporting much worse",
+                      sep=" "),
+        subtitle = paste("n", dim(much_worse_gad)[1]))
+
+little_worse_gad %>% ggplot(aes(x = gad.sum_score_prepan, y = gad.sum_score_retro)) +
+  geom_point(colour = "blue") +
+  stat_smooth(method = "lm") +
+  geom_jitter(w = 0.4, h = 0.4) +
+   labs(title = paste("Relationship between prepandemic and retrospective GAD scores\nfor participants reporting a little worse",
+                      sep=" "),
+        subtitle = paste("n", dim(little_worse_gad)[1]))
+
+much_worse_little_worse_gad %>% ggplot(aes(x = gad.sum_score_prepan, y = gad.sum_score_retro)) +  geom_point(colour = "blue") +
+  stat_smooth(method = "lm") +
+  geom_jitter(w = 0.4, h = 0.4) +
+   labs(title = paste("Relationship between prepandemic and retrospective GAD scores\nfor participants reporting much worse and a little worse",
+                      sep=" "),
+        subtitle = paste("n", dim(much_worse_little_worse_gad)[1]))
+
+```
+
+```{r Little/much better scatterplots for gad}
+
+#Filter by participants reporting little/much better in gad since pandemic started (separetely and grouped)
+
+little_better_gad <- dat %>% 
+  filter(gad.pandemic_felt_feelings == "A little better")
+
+much_better_gad <- dat %>% 
+  filter(gad.pandemic_felt_feelings == "Much better")
+
+much_better_little_better_gad <- dat %>% 
+  filter(gad.pandemic_felt_feelings == "Much better" | 
+           gad.pandemic_felt_feelings == "A little better")
+
+#Visualise them as scatterplots
+
+little_better_gad %>% ggplot(aes(x = gad.sum_score_prepan, y = gad.sum_score_retro)) +
+  geom_point(colour = "blue") +
+  stat_smooth(method = "lm") +
+  geom_jitter(w = 0.4, h = 0.4) +
+   labs(title = paste("Relationship between prepandemic and retrospective GAD scores\nfor participants reporting a little better",
+                      sep=" "),
+        subtitle = paste("n", dim(little_better_gad)[1]))
+
+much_better_gad %>% ggplot(aes(x = gad.sum_score_prepan, y = gad.sum_score_retro)) +
+  geom_point(colour = "blue") +
+  stat_smooth(method = "lm") +
+  geom_jitter(w = 0.4, h = 0.4) +
+   labs(title = paste("Relationship between prepandemic and retrospective GAD scores\nfor participants reporting a little worse",
+                      sep=" "),
+        subtitle = paste("n", dim(much_better_gad)[1]))
+
+much_better_little_better_gad %>% ggplot(aes(x = gad.sum_score_prepan, y = gad.sum_score_retro)) +
+  geom_point(colour = "blue") +
+  stat_smooth(method = "lm") + 
+  geom_jitter(w = 0.4, h = 0.4) +
+   labs(title = paste("Relationship between prepandemic and retrospective GAD scores\nfor participants reporting much better and a little better",
+                      sep=" "),
+        subtitle = paste("n", dim(much_better_little_better_gad)[1]))
+
 ```

### 2020-11-11 PANCHANGE_exclusion_descriptives.Rmd
Added a little/much better retro prepan correlation and scatterplots. Added a glad edgi participant filter to every scatterplot

@@
 
+#Create a data set with only the GLAD and EDGI participants
+whole_retro_prepan_scatter <- dat[str_detect(dat$Sample, "GLAD|EDGI"), ]
+
+#Check that RAMP and NBR has been removed
+whole_retro_prepan_scatter %>% 
+  freq(Sample)
+
 #Remove those saying "no different" since pandemic
@@
 
-```{r Whole sample Correlation prep chunk}
+```{r Little/much worse correlation prep chunk}
 
@@
 
+#Create a data set with only the GLAD and EDGI participants
+little_much_worse_retro_prepan <- dat[str_detect(dat$Sample, "GLAD|EDGI"), ]
+
+#Check that RAMP and NBR has been removed
+little_much_worse_retro_prepan %>% 
+  freq(Sample)
+
 #Filter by little/much worse self-reported change since pandemic started in gad
 
-much_worse_gad <- dat %>% 
+much_worse_gad_scatter <- dat %>% 
   filter(gad.pandemic_felt_feelings == "Much worse")
 
-little_worse_gad <- dat %>% 
+little_worse_gad_scatter <- dat %>% 
   filter(gad.pandemic_felt_feelings == "A little worse")
 
-much_worse_little_worse_gad <- dat %>% 
+much_little_worse_gad_scatter <- dat %>% 
   filter(gad.pandemic_felt_feelings == "Much worse" | 
@@
 
-much_worse_gad %>% ggplot(aes(x = gad.sum_score_prepan, y = gad.sum_score_retro)) +
+much_worse_gad_scatter %>% ggplot(aes(x = gad.sum_score_prepan, y = gad.sum_score_retro)) +
   geom_point(colour = "blue") +
@@
                       sep=" "),
-        subtitle = paste("n", dim(much_worse_gad)[1]))
-
-little_worse_gad %>% ggplot(aes(x = gad.sum_score_prepan, y = gad.sum_score_retro)) +
+        subtitle = paste("n", dim(much_worse_gad_scatter)[1]))
+
+little_worse_gad_scatter %>% ggplot(aes(x = gad.sum_score_prepan, y = gad.sum_score_retro)) +
   geom_point(colour = "blue") +
@@
                       sep=" "),
-        subtitle = paste("n", dim(little_worse_gad)[1]))
-
-much_worse_little_worse_gad %>% ggplot(aes(x = gad.sum_score_prepan, y = gad.sum_score_retro)) +  geom_point(colour = "blue") +
+        subtitle = paste("n", dim(little_worse_gad_scatter)[1]))
+
+much_little_worse_gad_scatter %>% ggplot(aes(x = gad.sum_score_prepan, y = gad.sum_score_retro)) +  geom_point(colour = "blue") +
   stat_smooth(method = "lm") +
@@
                       sep=" "),
-        subtitle = paste("n", dim(much_worse_little_worse_gad)[1]))
+        subtitle = paste("n", dim(much_little_worse_gad_scatter)[1]))
+
+```
+
+#Little/much better prepan retro correlation
+
+```{r Little/much better correlation prep chunk}
+
+# Check the items are the same from the whole chunk
+prepan_retro_items
+
+#Create a data set with only the GLAD and EDGI
+prepan_retro_dat_better <- dat[str_detect(dat$Sample, "GLAD|EDGI"), ]
+
+#Filter the data to only include those with self-reported little/much worse gad since pandemic
+
+prepan_retro_dat_better <- prepan_retro_dat_better %>% 
+  filter(gad.pandemic_felt_feelings == "A little better" |
+           gad.pandemic_felt_feelings == "Much better")
+
+#Check that RAMP and NBR has been removed
+prepan_retro_dat_better %>% 
+  freq(Sample)
+
+# Calculate correlation matrix on specific columns (variables) from your data frame
+prepan_retro.corr.mat_better <- hetcor(
+  as.data.frame(prepan_retro_dat_better[,prepan_retro_items]), # Specify the data
+  use = "pairwise.complete.obs" # Use all pairwise observations
+)
+
+# Print the correlation matrix
+print(prepan_retro.corr.mat_better, digits = max(3, getOption("digits") - 3))
+
+# Save the correlations from the correlation matrix in an object
+prepan_retro.corr.matrix_better <- as.matrix(prepan_retro.corr.mat_better)
+
+# Save the p values from the correlation matrix in an object
+prepan_retro.p.matrix_better <- as.matrix(prepan_retro.corr.mat_better$tests)
+
+res1 <- cor.ci(prepan_retro.corr.matrix_better)
+lowci <- cor.plot.upperLowerCi(res1)
+lowci[upper.tri(lowci)] = t(lowci)[upper.tri(lowci)]
+
+upci <- cor.plot.upperLowerCi(res1)
+upci[lower.tri(upci)] = t(upci)[lower.tri(lowci)]
+
+conf <- paste0("[", format(lowci, digits=2), " - ", format(upci, digits=2), "]")
+
+xs <- row(lowci)
+ys <- (ncol(lowci)+1) - col(lowci)
+
+xs[lower.tri(xs,diag=TRUE)] <- 0
+ys[lower.tri(ys,diag=TRUE)] <- 0
+
+```
+
+```{r Little/much better correlation matrix of prepan retro sum scores}
+corrplot(prepan_retro.corr.matrix_better, 
+         method = "color", # objects to represent the correlations on plot
+         type = "lower", # only use the lower triangle of the matrix
+         diag = FALSE, # do not show the correlations on the diagonal
+         addgrid.col = NA,
+         addCoef.col = "black", # colour for the correlation coefficients in the plot
+         tl.cex = 0.8,
+         tl.col = "black",
+         col=colorRampPalette(c("dodgerblue4","white","firebrick4"))(200), # colours for correlations
+         # Combine with significance
+         p.mat = prepan_retro.p.matrix, # Matrix with p values
+         sig.level = 0.01, # Choose significant level
+         insig = "blank" # Nonsignificant correlations have no colour
+         )
+
+text(xs, ys, conf, pos=1, cex=0.8)
 
@@
 
+#Create a data set with only the GLAD and EDGI participants
+little_much_better_retro_prepan <- dat[str_detect(dat$Sample, "GLAD|EDGI"), ]
+
+#Check that RAMP and NBR has been removed
+little_much_better_retro_prepan %>% 
+  freq(Sample)
+
 #Filter by participants reporting little/much better in gad since pandemic started (separetely and grouped)
 
-little_better_gad <- dat %>% 
+little_better_gad_scatter <- dat %>% 
   filter(gad.pandemic_felt_feelings == "A little better")
 
-much_better_gad <- dat %>% 
+much_better_gad_scatter <- dat %>% 
   filter(gad.pandemic_felt_feelings == "Much better")
 
-much_better_little_better_gad <- dat %>% 
+much_little_better_gad_scatter <- dat %>% 
   filter(gad.pandemic_felt_feelings == "Much better" | 
@@
 
-little_better_gad %>% ggplot(aes(x = gad.sum_score_prepan, y = gad.sum_score_retro)) +
+little_better_gad_scatter %>% ggplot(aes(x = gad.sum_score_prepan, y = gad.sum_score_retro)) +
   geom_point(colour = "blue") +
@@
                       sep=" "),
-        subtitle = paste("n", dim(little_better_gad)[1]))
-
-much_better_gad %>% ggplot(aes(x = gad.sum_score_prepan, y = gad.sum_score_retro)) +
+        subtitle = paste("n", dim(little_better_gad_scatter)[1]))
+
+much_better_gad_scatter %>% ggplot(aes(x = gad.sum_score_prepan, y = gad.sum_score_retro)) +
   geom_point(colour = "blue") +
@@
   geom_jitter(w = 0.4, h = 0.4) +
-   labs(title = paste("Relationship between prepandemic and retrospective GAD scores\nfor participants reporting a little worse",
+   labs(title = paste("Relationship between prepandemic and retrospective GAD scores\nfor participants reporting much better",
                       sep=" "),
-        subtitle = paste("n", dim(much_better_gad)[1]))
-
-much_better_little_better_gad %>% ggplot(aes(x = gad.sum_score_prepan, y = gad.sum_score_retro)) +
+        subtitle = paste("n", dim(much_better_gad_scatter)[1]))
+
+much_little_better_gad_scatter %>% ggplot(aes(x = gad.sum_score_prepan, y = gad.sum_score_retro)) +
   geom_point(colour = "blue") +
@@
                       sep=" "),
-        subtitle = paste("n", dim(much_better_little_better_gad)[1]))
+        subtitle = paste("n", dim(much_little_better_gad_scatter)[1]))
 

### 2020-11-11 PANCHANGE_exclusion_descriptives.Rmd
Added a phq retro prepan scatterplot for the whole sample

@@
 
-```{r Whole sample scatterplot for gad prepan base}
+```{r Whole sample scatterplots for gad and phq prepan retro}
 
@@
 
-whole_retro_prepan_scatter <- dat %>% 
+whole_retro_prepan_gad_scatter <- whole_retro_prepan_scatter %>% 
   filter(gad.pandemic_felt_feelings == "Much worse" |
@@
 
-whole_retro_prepan_scatter %>% ggplot(aes(x = gad.sum_score_retro, y = gad.sum_score_retro)) +
+whole_retro_prepan_phq_scatter <- whole_retro_prepan_scatter %>% 
+  filter(gad.pandemic_felt_feelings == "Much worse" |
+           gad.pandemic_felt_feelings == "A little worse" |
+           gad.pandemic_felt_feelings == "A little better" |
+           gad.pandemic_felt_feelings == "Much better")
+
+#Visualise as scatterplots
+
+whole_retro_prepan_gad_scatter %>% ggplot(aes(x = gad.sum_score_retro, y = gad.sum_score_retro)) +
   geom_point(colour = "blue") +
   stat_smooth(method = "lm") +
-  geom_jitter(w = 0.4, h = 0.4)
+  geom_jitter(w = 0.4, h = 0.4) +
+   labs(title = paste("Relationship between prepandemic and retrospective GAD scores\nfor whole sample",
+                      sep=" "),
+        subtitle = paste("n", dim(whole_retro_prepan_gad_scatter)[1]))
+
+whole_retro_prepan_gad_scatter %>% ggplot(aes(x = phq.sum_score_retro, y = phq.sum_score_retro)) +
+  geom_point(colour = "blue") +
+  stat_smooth(method = "lm") +
+  geom_jitter(w = 0.4, h = 0.4) +
+   labs(title = paste("Relationship between prepandemic and retrospective PHQ scores\nfor whole sample",
+                      sep=" "),
+        subtitle = paste("n", dim(whole_retro_prepan_gad_scatter)[1]))
 

### 2020-11-11 PANCHANGE_exclusion_descriptives.Rmd
Added phq scatterplots for little/much worse prepan retro scores for phq

@@
 
+###Whole sample prepan retro correlation
+
 ```{r Whole sample Correlation prep chunk}
@@
 
-#Correlation little/much worse prepan retro gad
+###Little/much worse prepan retro correlation
 
@@
 
-```{r Little/much worse scatterplots for gad}
+```{r Little/much worse prepan retro scatterplot prep}
 
@@
 
-#Filter by little/much worse self-reported change since pandemic started in gad
-
-much_worse_gad_scatter <- dat %>% 
+#Filter by little/much worse self-reported change since pandemic started in gad and phq
+
+much_worse_gad_scatter <- little_much_worse_retro_prepan %>% 
   filter(gad.pandemic_felt_feelings == "Much worse")
 
-little_worse_gad_scatter <- dat %>% 
+little_worse_gad_scatter <- little_much_worse_retro_prepan %>% 
   filter(gad.pandemic_felt_feelings == "A little worse")
 
-much_little_worse_gad_scatter <- dat %>% 
+much_little_worse_gad_scatter <- little_much_worse_retro_prepan %>% 
   filter(gad.pandemic_felt_feelings == "Much worse" | 
            gad.pandemic_felt_feelings == "A little worse")
+
+much_worse_phq_scatter <- little_much_worse_retro_prepan %>% 
+  filter(phq.pandemic_felt_feelings == "Much worse")
+
+little_worse_phq_scatter <- little_much_worse_retro_prepan %>% 
+  filter(phq.pandemic_felt_feelings == "A little worse")
+
+much_little_worse_phq_scatter <- little_much_worse_retro_prepan %>% 
+  filter(phq.pandemic_felt_feelings == "Much worse" | 
+           phq.pandemic_felt_feelings == "A little worse")
+
+```
+
+```{r Little/much worse prepan retro scatterplots}
 
@@
 
-```
-
-#Little/much better prepan retro correlation
+much_worse_phq_scatter %>% ggplot(aes(x = phq.sum_score_prepan, y = phq.sum_score_retro)) +
+  geom_point(colour = "blue") +
+  stat_smooth(method = "lm") +
+  geom_jitter(w = 0.4, h = 0.4) +
+   labs(title = paste("Relationship between prepandemic and retrospective PHQ scores\nfor participants reporting much worse",
+                      sep=" "),
+        subtitle = paste("n", dim(much_worse_phq_scatter)[1]))
+
+little_worse_phq_scatter %>% ggplot(aes(x = phq.sum_score_prepan, y = phq.sum_score_retro)) +
+  geom_point(colour = "blue") +
+  stat_smooth(method = "lm") +
+  geom_jitter(w = 0.4, h = 0.4) +
+   labs(title = paste("Relationship between prepandemic and retrospective PHQ scores\nfor participants reporting a little worse",
+                      sep=" "),
+        subtitle = paste("n", dim(little_worse_phq_scatter)[1]))
+
+much_little_worse_phq_scatter %>% ggplot(aes(x = phq.sum_score_prepan, y = phq.sum_score_retro)) +
+  geom_point(colour = "blue") +
+  stat_smooth(method = "lm") +
+  geom_jitter(w = 0.4, h = 0.4) +
+   labs(title = paste("Relationship between prepandemic and retrospective PHQ scores\nfor participants reporting much worse and a little worse",
+                      sep=" "),
+        subtitle = paste("n", dim(much_little_worse_phq_scatter)[1]))
+
+```
+
+###Little/much better prepan retro correlation
 

### 2020-11-11 PANCHANGE_exclusion_descriptives.Rmd
Added phq prepan retro scatterplots for participants reporting much better and a little better

@@
 
-#Correlation between whole sample retro impute and prepan
+#Correlations of retro impute and prepan
 ##Create function to use for all of the corplots
@@
 
-```{r Whole sample scatterplots for gad and phq prepan retro}
+```{r Whole sample prepan retro scatterplots prep}
 
@@
            gad.pandemic_felt_feelings == "Much better")
+
+```
+
+```{r Whole sample prepan retro scatterplots}
 
@@
 
-```{r Little/much better scatterplots for gad}
+```{r Little/much better prepan retro scatterplots prep}
 
@@
 
-#Filter by participants reporting little/much better in gad since pandemic started (separetely and grouped)
-
-little_better_gad_scatter <- dat %>% 
+#Filter by participants reporting little/much better in gad and phq since pandemic started (separetely and grouped)
+
+little_better_gad_scatter <- little_much_better_retro_prepan %>% 
   filter(gad.pandemic_felt_feelings == "A little better")
 
-much_better_gad_scatter <- dat %>% 
+much_better_gad_scatter <- little_much_better_retro_prepan %>% 
   filter(gad.pandemic_felt_feelings == "Much better")
 
-much_little_better_gad_scatter <- dat %>% 
+much_little_better_gad_scatter <- little_much_better_retro_prepan %>% 
   filter(gad.pandemic_felt_feelings == "Much better" | 
            gad.pandemic_felt_feelings == "A little better")
+
+little_better_phq_scatter <- little_much_better_retro_prepan %>% 
+  filter(phq.pandemic_felt_feelings == "A little better")
+
+much_better_phq_scatter <- little_much_better_retro_prepan %>% 
+  filter(phq.pandemic_felt_feelings == "Much better")
+
+much_little_better_phq_scatter <- little_much_better_retro_prepan %>% 
+  filter(phq.pandemic_felt_feelings == "Much better" | 
+           phq.pandemic_felt_feelings == "A little better")
+
+```
+
+```{r Little/much better prepan retro scatterplots}
 
@@
         subtitle = paste("n", dim(much_little_better_gad_scatter)[1]))
+
+little_better_phq_scatter %>% ggplot(aes(x = phq.sum_score_prepan, y = phq.sum_score_retro)) +
+  geom_point(colour = "blue") +
+  stat_smooth(method = "lm") +
+  geom_jitter(w = 0.4, h = 0.4) +
+   labs(title = paste("Relationship between prepandemic and retrospective PHQ scores\nfor participants reporting a little better",
+                      sep=" "),
+        subtitle = paste("n", dim(little_better_phq_scatter)[1]))
+
+much_better_phq_scatter %>% ggplot(aes(x = phq.sum_score_prepan, y = phq.sum_score_retro)) +
+  geom_point(colour = "blue") +
+  stat_smooth(method = "lm") +
+  geom_jitter(w = 0.4, h = 0.4) +
+   labs(title = paste("Relationship between prepandemic and retrospective PHQ scores\nfor participants reporting much better",
+                      sep=" "),
+        subtitle = paste("n", dim(much_better_phq_scatter)[1]))
+
+much_little_better_phq_scatter %>% ggplot(aes(x = phq.sum_score_prepan, y = phq.sum_score_retro)) +
+  geom_point(colour = "blue") +
+  stat_smooth(method = "lm") + 
+  geom_jitter(w = 0.4, h = 0.4) +
+   labs(title = paste("Relationship between prepandemic and retrospective PHQ scores\nfor participants reporting much better and a little better",
+                      sep=" "),
+        subtitle = paste("n", dim(much_little_better_phq_scatter)[1]))
 

### 2020-11-11 PANCHANGE_exclusion_descriptives.Rmd
Fixed plotting error in the whole sample prepan retro scatterplot and changed aesthetics

@@
 whole_retro_prepan_phq_scatter <- whole_retro_prepan_scatter %>% 
-  filter(gad.pandemic_felt_feelings == "Much worse" |
-           gad.pandemic_felt_feelings == "A little worse" |
-           gad.pandemic_felt_feelings == "A little better" |
-           gad.pandemic_felt_feelings == "Much better")
+  filter(phq.pandemic_felt_feelings == "Much worse" |
+           phq.pandemic_felt_feelings == "A little worse" |
+           phq.pandemic_felt_feelings == "A little better" |
+           phq.pandemic_felt_feelings == "Much better")
 
@@
 
-whole_retro_prepan_gad_scatter %>% ggplot(aes(x = gad.sum_score_retro, y = gad.sum_score_retro)) +
-  geom_point(colour = "blue") +
-  stat_smooth(method = "lm") +
-  geom_jitter(w = 0.4, h = 0.4) +
+whole_retro_prepan_gad_scatter %>% ggplot(aes(x = gad.sum_score_prepan, y = gad.sum_score_retro)) +
+  geom_point(colour = "grey") +
+  geom_jitter(w = 0.4, h = 0.4, colour = "grey") +
+  geom_smooth(method = "lm", colour = "navy", fill = "red") +
    labs(title = paste("Relationship between prepandemic and retrospective GAD scores\nfor whole sample",
@@
 
-whole_retro_prepan_gad_scatter %>% ggplot(aes(x = phq.sum_score_retro, y = phq.sum_score_retro)) +
-  geom_point(colour = "blue") +
-  stat_smooth(method = "lm") +
-  geom_jitter(w = 0.4, h = 0.4) +
+whole_retro_prepan_phq_scatter %>% ggplot(aes(x = phq.sum_score_retro, y = phq.sum_score_prepan)) +
+  geom_point(colour = "grey") +
+  geom_jitter(w = 0.4, h = 0.4, colour = "grey") +
+  geom_smooth(method = "lm", colour = "navy", fill = "red") +
    labs(title = paste("Relationship between prepandemic and retrospective PHQ scores\nfor whole sample",
                       sep=" "),
-        subtitle = paste("n", dim(whole_retro_prepan_gad_scatter)[1]))
+        subtitle = paste("n", dim(whole_retro_prepan_phq_scatter)[1]))
 

### 2020-11-11 PANCHANGE_exclusion_descriptives.Rmd
Changed aesthetics for the little/much worse prepan retro scatterplots

@@
 much_worse_gad_scatter %>% ggplot(aes(x = gad.sum_score_prepan, y = gad.sum_score_retro)) +
-  geom_point(colour = "blue") +
-  stat_smooth(method = "lm") +
-  geom_jitter(w = 0.4, h = 0.4) +
+  geom_point(colour = "grey") +
+  geom_jitter(w = 0.4, h = 0.4, colour = "grey") +
+  stat_smooth(method = "lm", colour = "navy", fill = "red") +
    labs(title = paste("Relationship between prepandemic and retrospective GAD scores\nfor participants reporting much worse",
@@
 little_worse_gad_scatter %>% ggplot(aes(x = gad.sum_score_prepan, y = gad.sum_score_retro)) +
-  geom_point(colour = "blue") +
-  stat_smooth(method = "lm") +
-  geom_jitter(w = 0.4, h = 0.4) +
+  geom_point(colour = "grey") +
+  geom_jitter(w = 0.4, h = 0.4, colour = "grey") +
+  stat_smooth(method = "lm", colour = "navy", fill = "red") +
    labs(title = paste("Relationship between prepandemic and retrospective GAD scores\nfor participants reporting a little worse",
@@
 
-much_little_worse_gad_scatter %>% ggplot(aes(x = gad.sum_score_prepan, y = gad.sum_score_retro)) +  geom_point(colour = "blue") +
-  stat_smooth(method = "lm") +
-  geom_jitter(w = 0.4, h = 0.4) +
+much_little_worse_gad_scatter %>% ggplot(aes(x = gad.sum_score_prepan, y = gad.sum_score_retro)) +  
+  geom_point(colour = "grey") +
+  geom_jitter(w = 0.4, h = 0.4, colour = "grey") +
+  stat_smooth(method = "lm", colour = "navy", fill = "red") +
    labs(title = paste("Relationship between prepandemic and retrospective GAD scores\nfor participants reporting much worse and a little worse",
@@
 much_worse_phq_scatter %>% ggplot(aes(x = phq.sum_score_prepan, y = phq.sum_score_retro)) +
-  geom_point(colour = "blue") +
-  stat_smooth(method = "lm") +
-  geom_jitter(w = 0.4, h = 0.4) +
+  geom_point(colour = "grey") +
+  geom_jitter(w = 0.4, h = 0.4, colour = "grey") +
+  stat_smooth(method = "lm", colour = "navy", fill = "red") +
    labs(title = paste("Relationship between prepandemic and retrospective PHQ scores\nfor participants reporting much worse",
@@
 little_worse_phq_scatter %>% ggplot(aes(x = phq.sum_score_prepan, y = phq.sum_score_retro)) +
-  geom_point(colour = "blue") +
-  stat_smooth(method = "lm") +
-  geom_jitter(w = 0.4, h = 0.4) +
+  geom_point(colour = "grey") +
+  geom_jitter(w = 0.4, h = 0.4, colour = "grey") +
+  stat_smooth(method = "lm", colour = "navy", fill = "red") +
    labs(title = paste("Relationship between prepandemic and retrospective PHQ scores\nfor participants reporting a little worse",
@@
 much_little_worse_phq_scatter %>% ggplot(aes(x = phq.sum_score_prepan, y = phq.sum_score_retro)) +
-  geom_point(colour = "blue") +
-  stat_smooth(method = "lm") +
-  geom_jitter(w = 0.4, h = 0.4) +
+  geom_point(colour = "grey") +
+  geom_jitter(w = 0.4, h = 0.4, colour = "grey") +
+  stat_smooth(method = "lm", colour = "navy", fill = "red") +
    labs(title = paste("Relationship between prepandemic and retrospective PHQ scores\nfor participants reporting much worse and a little worse",

### 2020-11-11 PANCHANGE_exclusion_descriptives.Rmd
Changed aesthetics for the little/much better prepan retro scatterplots

--- 2020-11-11 PANCHANGE_exclusion_descriptives.Rmd
@@
 much_worse_gad_scatter %>% ggplot(aes(x = gad.sum_score_prepan, y = gad.sum_score_retro)) +
-  geom_point(colour = "blue") +
-  stat_smooth(method = "lm") +
-  geom_jitter(w = 0.4, h = 0.4) +
+  geom_point(colour = "grey") +
+  geom_jitter(w = 0.4, h = 0.4, colour = "grey") +
+  geom_smooth(method = "lm", colour = "navy", fill = "red") +
    labs(title = paste("Relationship between prepandemic and retrospective GAD scores\nfor participants reporting much worse",
@@
 little_worse_gad_scatter %>% ggplot(aes(x = gad.sum_score_prepan, y = gad.sum_score_retro)) +
-  geom_point(colour = "blue") +
-  stat_smooth(method = "lm") +
-  geom_jitter(w = 0.4, h = 0.4) +
+  geom_point(colour = "grey") +
+  geom_jitter(w = 0.4, h = 0.4, colour = "grey") +
+  geom_smooth(method = "lm", colour = "navy", fill = "red") +
    labs(title = paste("Relationship between prepandemic and retrospective GAD scores\nfor participants reporting a little worse",
@@
 
-much_little_worse_gad_scatter %>% ggplot(aes(x = gad.sum_score_prepan, y = gad.sum_score_retro)) +  geom_point(colour = "blue") +
-  stat_smooth(method = "lm") +
-  geom_jitter(w = 0.4, h = 0.4) +
+much_little_worse_gad_scatter %>% ggplot(aes(x = gad.sum_score_prepan, y = gad.sum_score_retro)) +  
+  geom_point(colour = "grey") +
+  geom_jitter(w = 0.4, h = 0.4, colour = "grey") +
+  geom_smooth(method = "lm", colour = "navy", fill = "red") +
    labs(title = paste("Relationship between prepandemic and retrospective GAD scores\nfor participants reporting much worse and a little worse",
@@
 much_worse_phq_scatter %>% ggplot(aes(x = phq.sum_score_prepan, y = phq.sum_score_retro)) +
-  geom_point(colour = "blue") +
-  stat_smooth(method = "lm") +
-  geom_jitter(w = 0.4, h = 0.4) +
+  geom_point(colour = "grey") +
+  geom_jitter(w = 0.4, h = 0.4, colour = "grey") +
+  geom_smooth(method = "lm", colour = "navy", fill = "red") +
    labs(title = paste("Relationship between prepandemic and retrospective PHQ scores\nfor participants reporting much worse",
@@
 little_worse_phq_scatter %>% ggplot(aes(x = phq.sum_score_prepan, y = phq.sum_score_retro)) +
-  geom_point(colour = "blue") +
-  stat_smooth(method = "lm") +
-  geom_jitter(w = 0.4, h = 0.4) +
+  geom_point(colour = "grey") +
+  geom_jitter(w = 0.4, h = 0.4, colour = "grey") +
+  geom_smooth(method = "lm", colour = "navy", fill = "red") +
    labs(title = paste("Relationship between prepandemic and retrospective PHQ scores\nfor participants reporting a little worse",
@@
 much_little_worse_phq_scatter %>% ggplot(aes(x = phq.sum_score_prepan, y = phq.sum_score_retro)) +
-  geom_point(colour = "blue") +
-  stat_smooth(method = "lm") +
-  geom_jitter(w = 0.4, h = 0.4) +
+  geom_point(colour = "grey") +
+  geom_jitter(w = 0.4, h = 0.4, colour = "grey") +
+  geom_smooth(method = "lm", colour = "navy", fill = "red") +
    labs(title = paste("Relationship between prepandemic and retrospective PHQ scores\nfor participants reporting much worse and a little worse",
@@
 little_better_gad_scatter %>% ggplot(aes(x = gad.sum_score_prepan, y = gad.sum_score_retro)) +
-  geom_point(colour = "blue") +
-  stat_smooth(method = "lm") +
-  geom_jitter(w = 0.4, h = 0.4) +
+  geom_point(colour = "grey") +
+  geom_jitter(w = 0.4, h = 0.4, colour = "grey") +
+  geom_smooth(method = "lm", colour = "blue", fill = "red") +
    labs(title = paste("Relationship between prepandemic and retrospective GAD scores\nfor participants reporting a little better",
@@
 much_better_gad_scatter %>% ggplot(aes(x = gad.sum_score_prepan, y = gad.sum_score_retro)) +
-  geom_point(colour = "blue") +
-  stat_smooth(method = "lm") +
-  geom_jitter(w = 0.4, h = 0.4) +
+  geom_point(colour = "grey") +
+  geom_jitter(w = 0.4, h = 0.4, colour = "grey") +
+  geom_smooth(method = "lm", colour = "navy", fill = "red") +
    labs(title = paste("Relationship between prepandemic and retrospective GAD scores\nfor participants reporting much better",
@@
 much_little_better_gad_scatter %>% ggplot(aes(x = gad.sum_score_prepan, y = gad.sum_score_retro)) +
-  geom_point(colour = "blue") +
-  stat_smooth(method = "lm") + 
-  geom_jitter(w = 0.4, h = 0.4) +
+  geom_point(colour = "grey") +
+  geom_jitter(w = 0.4, h = 0.4, colour = "grey") +
+  geom_smooth(method = "lm", colour = "navy", fill = "red") + 
    labs(title = paste("Relationship between prepandemic and retrospective GAD scores\nfor participants reporting much better and a little better",
@@
 little_better_phq_scatter %>% ggplot(aes(x = phq.sum_score_prepan, y = phq.sum_score_retro)) +
-  geom_point(colour = "blue") +
-  stat_smooth(method = "lm") +
-  geom_jitter(w = 0.4, h = 0.4) +
+  geom_point(colour = "grey") +
+  geom_jitter(w = 0.4, h = 0.4, colour = "grey") +
+  geom_smooth(method = "lm", colour = "navy", fill = "red") +
    labs(title = paste("Relationship between prepandemic and retrospective PHQ scores\nfor participants reporting a little better",
@@
 much_better_phq_scatter %>% ggplot(aes(x = phq.sum_score_prepan, y = phq.sum_score_retro)) +
-  geom_point(colour = "blue") +
-  stat_smooth(method = "lm") +
-  geom_jitter(w = 0.4, h = 0.4) +
+  geom_point(colour = "grey") +
+  geom_jitter(w = 0.4, h = 0.4, colour = "grey") +
+  geom_smooth(method = "lm", colour = "navy", fill = "red") +
    labs(title = paste("Relationship between prepandemic and retrospective PHQ scores\nfor participants reporting much better",
@@
 much_little_better_phq_scatter %>% ggplot(aes(x = phq.sum_score_prepan, y = phq.sum_score_retro)) +
-  geom_point(colour = "blue") +
-  stat_smooth(method = "lm") + 
-  geom_jitter(w = 0.4, h = 0.4) +
+  geom_point(colour = "grey") +
+  geom_jitter(w = 0.4, h = 0.4, colour = "grey") +
+  geom_smooth(method = "lm", colour = "navy", fill = "red") + 
    labs(title = paste("Relationship between prepandemic and retrospective PHQ scores\nfor participants reporting much better and a little better",

### 2020-11-12 PANCHANGE_exclusion_descriptives.Rmd
Added themes to the scatterplots

--- 2020-11-11 PANCHANGE_exclusion_descriptives.Rmd
@@
   geom_smooth(method = "lm", colour = "navy", fill = "red") +
+  theme_minimal() +
    labs(title = paste("Relationship between prepandemic and retrospective GAD scores\nfor whole sample",
@@
   geom_smooth(method = "lm", colour = "navy", fill = "red") +
+  theme_minimal() +
    labs(title = paste("Relationship between prepandemic and retrospective PHQ scores\nfor whole sample",
@@
 much_worse_gad_scatter %>% ggplot(aes(x = gad.sum_score_prepan, y = gad.sum_score_retro)) +
-  geom_point(colour = "blue") +
-  stat_smooth(method = "lm") +
-  geom_jitter(w = 0.4, h = 0.4) +
+  geom_point(colour = "grey") +
+  geom_jitter(w = 0.4, h = 0.4, colour = "grey") +
+  geom_smooth(method = "lm", colour = "navy", fill = "red") +
+  theme_minimal() +
    labs(title = paste("Relationship between prepandemic and retrospective GAD scores\nfor participants reporting much worse",
@@
 little_worse_gad_scatter %>% ggplot(aes(x = gad.sum_score_prepan, y = gad.sum_score_retro)) +
-  geom_point(colour = "blue") +
-  stat_smooth(method = "lm") +
-  geom_jitter(w = 0.4, h = 0.4) +
+  geom_point(colour = "grey") +
+  geom_jitter(w = 0.4, h = 0.4, colour = "grey") +
+  geom_smooth(method = "lm", colour = "navy", fill = "red") +
+  theme_minimal() +
    labs(title = paste("Relationship between prepandemic and retrospective GAD scores\nfor participants reporting a little worse",
@@
 
-much_little_worse_gad_scatter %>% ggplot(aes(x = gad.sum_score_prepan, y = gad.sum_score_retro)) +  geom_point(colour = "blue") +
-  stat_smooth(method = "lm") +
-  geom_jitter(w = 0.4, h = 0.4) +
+much_little_worse_gad_scatter %>% ggplot(aes(x = gad.sum_score_prepan, y = gad.sum_score_retro)) +  
+  geom_point(colour = "grey") +
+  geom_jitter(w = 0.4, h = 0.4, colour = "grey") +
+  geom_smooth(method = "lm", colour = "navy", fill = "red") +
+  theme_minimal() +
    labs(title = paste("Relationship between prepandemic and retrospective GAD scores\nfor participants reporting much worse and a little worse",
@@
 much_worse_phq_scatter %>% ggplot(aes(x = phq.sum_score_prepan, y = phq.sum_score_retro)) +
-  geom_point(colour = "blue") +
-  stat_smooth(method = "lm") +
-  geom_jitter(w = 0.4, h = 0.4) +
+  geom_point(colour = "grey") +
+  geom_jitter(w = 0.4, h = 0.4, colour = "grey") +
+  geom_smooth(method = "lm", colour = "navy", fill = "red") +
+  theme_minimal() +
    labs(title = paste("Relationship between prepandemic and retrospective PHQ scores\nfor participants reporting much worse",
@@
 little_worse_phq_scatter %>% ggplot(aes(x = phq.sum_score_prepan, y = phq.sum_score_retro)) +
-  geom_point(colour = "blue") +
-  stat_smooth(method = "lm") +
-  geom_jitter(w = 0.4, h = 0.4) +
+  geom_point(colour = "grey") +
+  geom_jitter(w = 0.4, h = 0.4, colour = "grey") +
+  geom_smooth(method = "lm", colour = "navy", fill = "red") +
+  theme_minimal() +
    labs(title = paste("Relationship between prepandemic and retrospective PHQ scores\nfor participants reporting a little worse",
@@
 much_little_worse_phq_scatter %>% ggplot(aes(x = phq.sum_score_prepan, y = phq.sum_score_retro)) +
-  geom_point(colour = "blue") +
-  stat_smooth(method = "lm") +
-  geom_jitter(w = 0.4, h = 0.4) +
+  geom_point(colour = "grey") +
+  geom_jitter(w = 0.4, h = 0.4, colour = "grey") +
+  geom_smooth(method = "lm", colour = "navy", fill = "red") +
+  theme_minimal() +
    labs(title = paste("Relationship between prepandemic and retrospective PHQ scores\nfor participants reporting much worse and a little worse",
@@
 little_better_gad_scatter %>% ggplot(aes(x = gad.sum_score_prepan, y = gad.sum_score_retro)) +
-  geom_point(colour = "blue") +
-  stat_smooth(method = "lm") +
-  geom_jitter(w = 0.4, h = 0.4) +
+  geom_point(colour = "grey") +
+  geom_jitter(w = 0.4, h = 0.4, colour = "grey") +
+  geom_smooth(method = "lm", colour = "blue", fill = "red") +
+  theme_minimal() +
    labs(title = paste("Relationship between prepandemic and retrospective GAD scores\nfor participants reporting a little better",
@@
 much_better_gad_scatter %>% ggplot(aes(x = gad.sum_score_prepan, y = gad.sum_score_retro)) +
-  geom_point(colour = "blue") +
-  stat_smooth(method = "lm") +
-  geom_jitter(w = 0.4, h = 0.4) +
+  geom_point(colour = "grey") +
+  geom_jitter(w = 0.4, h = 0.4, colour = "grey") +
+  geom_smooth(method = "lm", colour = "navy", fill = "red") +
+  theme_minimal() +
    labs(title = paste("Relationship between prepandemic and retrospective GAD scores\nfor participants reporting much better",
@@
 much_little_better_gad_scatter %>% ggplot(aes(x = gad.sum_score_prepan, y = gad.sum_score_retro)) +
-  geom_point(colour = "blue") +
-  stat_smooth(method = "lm") + 
-  geom_jitter(w = 0.4, h = 0.4) +
+  geom_point(colour = "grey") +
+  geom_jitter(w = 0.4, h = 0.4, colour = "grey") +
+  geom_smooth(method = "lm", colour = "navy", fill = "red") + 
+  theme_minimal() +
    labs(title = paste("Relationship between prepandemic and retrospective GAD scores\nfor participants reporting much better and a little better",
@@
 little_better_phq_scatter %>% ggplot(aes(x = phq.sum_score_prepan, y = phq.sum_score_retro)) +
-  geom_point(colour = "blue") +
-  stat_smooth(method = "lm") +
-  geom_jitter(w = 0.4, h = 0.4) +
+  geom_point(colour = "grey") +
+  geom_jitter(w = 0.4, h = 0.4, colour = "grey") +
+  geom_smooth(method = "lm", colour = "navy", fill = "red") +
+  theme_minimal() +
    labs(title = paste("Relationship between prepandemic and retrospective PHQ scores\nfor participants reporting a little better",
@@
 much_better_phq_scatter %>% ggplot(aes(x = phq.sum_score_prepan, y = phq.sum_score_retro)) +
-  geom_point(colour = "blue") +
-  stat_smooth(method = "lm") +
-  geom_jitter(w = 0.4, h = 0.4) +
+  geom_point(colour = "grey") +
+  geom_jitter(w = 0.4, h = 0.4, colour = "grey") +
+  geom_smooth(method = "lm", colour = "navy", fill = "red") +
+  theme_minimal() +
    labs(title = paste("Relationship between prepandemic and retrospective PHQ scores\nfor participants reporting much better",
@@
 much_little_better_phq_scatter %>% ggplot(aes(x = phq.sum_score_prepan, y = phq.sum_score_retro)) +
-  geom_point(colour = "blue") +
-  stat_smooth(method = "lm") + 
-  geom_jitter(w = 0.4, h = 0.4) +
+  geom_point(colour = "grey") +
+  geom_jitter(w = 0.4, h = 0.4, colour = "grey") +
+  geom_smooth(method = "lm", colour = "navy", fill = "red") + 
+  theme_minimal() +
    labs(title = paste("Relationship between prepandemic and retrospective PHQ scores\nfor participants reporting much better and a little better",

### 2020-11-12 PANCHANGE_analysis.Rmd
updated education/employment sensitivity models

--- 2020-11-09 PANCHANGE_analysis.Rmd
@@
 
-dim(dat.retro_sensitivity)
-```
-age^2 sensitivity 
-Exclude individuals with NA for continuous Age variable
-```{r}
-dat_age_sensitivity <- dat %>%
-  filter(!is.na(Age))
-dim(dat_age_sensitivity)
-```
-
-Sensitivity analysis for individuals who signed up to GLAD (prepan) either 3, 6 or 9 months before the pendemic began. 
-```{r subsample for pre-pan sensitivity analysis}
-# Participants who signed up in the three months before the pandemic began
-dat.prepan_sensitivity_3months <- dat %>%
-  filter(
-    ((data_group_gad == "Baseline and retrospective data" |
-      data_group_gad == "Prepandemic and baseline data" |
-      data_group_gad == "All prepandemic, baseline and retrospective data") |
-      (data_group_phq == "Baseline and retrospective data" |
-      data_group_phq == "Prepandemic and baseline data" |
-      data_group_phq == "All prepandemic, baseline and retrospective data") |
-      (data_group_pcl == "Baseline and retrospective data" |
-      data_group_pcl == "Prepandemic and baseline data" |
-      data_group_pcl == "All prepandemic, baseline and retrospective data") |
-      (data_group_ocir == "Baseline and retrospective data" |
-      data_group_ocir == "Prepandemic and baseline data" |
-      data_group_ocir == "All prepandemic, baseline and retrospective data")) &
-      prepandemic_3_months_numeric == 1 # Only participants who signed up between December 1st 2019 and March 1st 2020
-  )
-
-# Participants who signed up in the three months before the pandemic began
-dat.prepan_sensitivity_6months <- dat %>%
-  filter(
-    ((data_group_gad == "Baseline and retrospective data" |
-      data_group_gad == "Prepandemic and baseline data" |
-      data_group_gad == "All prepandemic, baseline and retrospective data") |
-      (data_group_phq == "Baseline and retrospective data" |
-      data_group_phq == "Prepandemic and baseline data" |
-      data_group_phq == "All prepandemic, baseline and retrospective data") |
-      (data_group_pcl == "Baseline and retrospective data" |
-      data_group_pcl == "Prepandemic and baseline data" |
-      data_group_pcl == "All prepandemic, baseline and retrospective data") |
-      (data_group_ocir == "Baseline and retrospective data" |
-      data_group_ocir == "Prepandemic and baseline data" |
-      data_group_ocir == "All prepandemic, baseline and retrospective data")) &
-      prepandemic_6_months_numeric == 1 # Only participants who signed up between September 1st 2019 and March 1st 2020
-  )
-
-# Participants who signed up in the three months before the pandemic began
-dat.prepan_sensitivity_9months <- dat %>%
-  filter(
-    ((data_group_gad == "Baseline and retrospective data" |
-      data_group_gad == "Prepandemic and baseline data" |
-      data_group_gad == "All prepandemic, baseline and retrospective data") |
-      (data_group_phq == "Baseline and retrospective data" |
-      data_group_phq == "Prepandemic and baseline data" |
-      data_group_phq == "All prepandemic, baseline and retrospective data") |
-      (data_group_pcl == "Baseline and retrospective data" |
-      data_group_pcl == "Prepandemic and baseline data" |
-      data_group_pcl == "All prepandemic, baseline and retrospective data") |
-      (data_group_ocir == "Baseline and retrospective data" |
-      data_group_ocir == "Prepandemic and baseline data" |
-      data_group_ocir == "All prepandemic, baseline and retrospective data")) &
-      prepandemic_9_months_numeric == 1 # Only participants who signed up between June 1st 2019 and March 1st 2020
-  )
-
+dim(dat.prepan)
 ```
@@
   return(get(paste0(outcome,"model1b_reg_stats")))
-}
-```
-
-```{r model2a function}
-model2a.estimates <- function(outcome, data_set) {
-  # define the variable name of the dependent variable
-  dependent.variable <- outcome
-  # define the independent variables
-  independent.variables <- c("Disorder_hierarchical",
-                            "Gender_collapsed",
-                            "poly(Age, 2)",
-                            "Ethnicity_collapsed",
-                            "time_diff_coping_lockdown_march_23"
-                            )
-  # create the formula
-  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
-  glm.formula
-
-  # run the glm
-  assign(paste0(outcome,".model2a"),
-         lm( formula = glm.formula,
-             data = get(data_set)
-         )
-  )
-
-  assign(paste0(outcome,"model2a_estimates"),
-         tidy(get(paste0(outcome,".model2a")), conf.int = TRUE) %>%
-           mutate(
-             "Indepent variable" = recode_factor(
-               term,
-               "(Intercept)" = "Intercept",
-               "Disorder_hierarchicalAnxiety disorders" = "Anxiety disorders",
-               "Disorder_hierarchicalEating disorders" = "Eating disorders",
-               "Disorder_hierarchicalOCDs" = "OCDs",
-               "Disorder_hierarchicalPTSD" = "PTSD",
-               "Disorder_hierarchicalDepressive disorders" = "Depressive disorders",
-               "Disorder_hierarchicalBipolar disorders" = "Bipolar disorders",
-               "Gender_collapsedFemale" = "Female",
-               "Gender_collapsedNon-binary/Self-defined" = "Non-binary/Self-defined",
-               "poly(Age, 2)1" = "Age",
-               "poly(Age, 2)2" = "Age^2", 
-               "Ethnicity_collapsedMixed or multiple ethnic origins" = "Mixed or multiple ethnic origins",
-               "Ethnicity_collapsedAsian or Asian British" = "Asian or Asian British",
-               "Ethnicity_collapsedAfrican or African British" = "African or African British",
-               "Ethnicity_collapsedOther" = "Other ethnicity",
-               "time_diff_coping_lockdown_march_23" = "Time difference: Lockdown to baseline"
-             ),
-             "Estimate" = format(
-               round(estimate,
-                     digits = 2),
-               nsmall = 2),
-             "95% CI low" = format(
-               round(conf.low,
-                     digits = 2),
-               nsmall = 2),
-             "95% CI up" = format(
-               round(conf.high,
-                     digits = 2),
-               nsmall = 2),
-             "SE" = format(
-               round(std.error,
-                     digits = 2),
-               nsmall = 2),
-             "z score" = format(
-               round(statistic,
-                     digits = 2),
-               nsmall = 2),
-             "p value" = case_when(
-               p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
-               p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
-               p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
-             )
-           ) %>%
-           select(
-             "Indepent variable",
-             "Estimate",
-             "95% CI low",
-             "95% CI up",
-             "SE",
-             #    "z score",
-             "p value"
-           )
-  )
-
-  return(get(paste0(outcome,"model2a_estimates")))
-}
-
-model2a.reg.stats <- function(outcome, data_set) {
-  # define the variable name of the dependent variable
-  dependent.variable <- outcome
-  # define the independent variables
-  independent.variables <- c("Disorder_hierarchical")
-  # create the formula
-  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
-  glm.formula
-
-  # run the glm
-  assign(paste0(outcome,".model2a"),
-         lm( formula = glm.formula,
-             data = get(data_set)
-         )
-  )
-
-  assign(paste0(outcome,"model2a_reg_stats"),
-         glance(get(paste0(outcome,".model2a"))) %>%
-           mutate(
-             "n" = format(
-               round(nobs,
-                     digits = 0),
-               nsmall = 0),
-             "R2" = format(
-               round(r.squared,
-                     digits = 2),
-               nsmall = 2),
-             "adjust. R2" = format(
-               round(adj.r.squared,
-                     digits = 2),
-               nsmall = 2),
-             "F" = format(
-               round(statistic,
-                     digits = 2),
-               nsmall = 2),
-             "p value" = case_when(
-               p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
-               p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
-               p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
-             )
-           ) %>%
-           select(
-             "n",
-             "R2",
-             "adjust. R2",
-             "F",
-             "p value",
-             "df"
-           )
-  )
-
-  return(get(paste0(outcome,"model2a_reg_stats")))
-}
-```
-
-```{r model2b function}
-model2b.estimates <- function(outcome, data_set) {
-  # define the variable name of the dependent variable
-  dependent.variable <- outcome
-  # define the independent variables
-  independent.variables <- c("depression_and_anxiety",
-                             "eating_disorders",
-                             "obsessive_compulsive_disorders",
-                             "bipolar_and_schizophrenia",
-                             "mhd.posttraumatic_stress_disorder_ptsd",
-                             "autism_spectrum_disorder",
-                             "mhd.attention_deficit_hyperactivity_disorder",
-                             "mhd.personality_disorder",
-                             "Gender_collapsed",
-                             "poly(Age, 2)",
-                             "Ethnicity_collapsed",
-                             "key_worker",
-                             "time_diff_coping_lockdown_march_23"
-                                )
-  # create the formula
-  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
-  glm.formula
-
-  # run the glm
-  assign(paste0(outcome,".model2b"),
-         lm( formula = glm.formula,
-             data = get(data_set)
-         )
-  )
-
-  assign(paste0(outcome,"model2b_estimates"),
-         tidy(get(paste0(outcome,".model2b")), conf.int = TRUE) %>%
-           mutate(
-             "Indepent variable" = recode_factor(
-               term,
-               "(Intercept)" = "Intercept",
-               "anxiety_disordersAnxiety disorder" = "Anxiety disorders",
-               "depressive_disordersDepressive disorder" = "Depressive disorders",
-               "depression_and_anxietyDepressive and anxiety disorder" = "Depressive and anxiety disorder",
-               "depression_and_anxietyOnly depressive disorder" = "Only depressive disorder",
-               "depression_and_anxietyOnly anxiety disorder" = "Only anxiety disorder",
-               "eating_disordersEating disorder" = "Eating disorders",
-               "obsessive_compulsive_disordersObsessive compulsive disorder" = "OCDs",
-               "bipolar_and_schizophreniaPsychotic and bipolar disorder" = "Psychotic and bipolar disorder",
-               "bipolar_and_schizophreniaOnly psychotic disorder" = "Only psychotic disorder",
-               "bipolar_and_schizophreniaOnly bipolar disorder" = "Only bipolar disorder",
-               "psychotic_disordersPsychotic disorder" = "Psychotic disorder",
-               "mhd.mania_hypomania_bipolar_or_manicdepressionMania, hypomania, bipolar or manic-depression" = "Bipolar disorder",
-               "mhd.posttraumatic_stress_disorder_ptsdPost-traumatic stress disorder (PTSD)" = "PTSD",
-               "autism_spectrum_disorderAutism spectrum disorder" = "ASD",
-               "mhd.attention_deficit_hyperactivity_disorderAttention deficit or attention deficit and hyperactivity disorder (ADD/ADHD)" = "ADHD",
-               "mhd.personality_disorderPersonality disorder" = "Personality disorder",
-               "Gender_collapsedFemale" = "Female",
-               "Gender_collapsedNon-binary/Self-defined" = "Non-binary/Self-defined",
-               "poly(Age, 2)1" = "Age",
-               "poly(Age, 2)2" = "Age^2", 
-               "Ethnicity_collapsedMixed or multiple ethnic origins" = "Mixed or multiple ethnic origins",
-               "Ethnicity_collapsedAsian or Asian British" = "Asian or Asian British",
-               "Ethnicity_collapsedAfrican or African British" = "African or African British",
-               "Ethnicity_collapsedOther" = "Other ethnicity",
-               "key_workerKey worker" = "Key worker",
-               "time_diff_coping_lockdown_march_23" = "Time difference: Lockdown to baseline"
-             ),
-             "Estimate" = format(
-               round(estimate,
-                     digits = 2),
-               nsmall = 2),
-             "95% CI low" = format(
-               round(conf.low,
-                     digits = 2),
-               nsmall = 2),
-             "95% CI up" = format(
-               round(conf.high,
-                     digits = 2),
-               nsmall = 2),
-             "SE" = format(
-               round(std.error,
-                     digits = 2),
-               nsmall = 2),
-             "z score" = format(
-               round(statistic,
-                     digits = 2),
-               nsmall = 2),
-             "p value" = case_when(
-               p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
-               p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
-               p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
-             )
-           ) %>%
-           select(
-             "Indepent variable",
-             "Estimate",
-             "95% CI low",
-             "95% CI up",
-             "SE",
-             #    "z score",
-             "p value"
-           )
-  )
-
-  return(get(paste0(outcome,"model2b_estimates")))
-}
-
-model2b.reg.stats <- function(outcome, data_set) {
-  # define the variable name of the dependent variable
-  dependent.variable <- outcome
-  # define the independent variables
-  independent.variables <- c("Disorder_hierarchical")
-  # create the formula
-  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
-  glm.formula
-
-  # run the glm
-  assign(paste0(outcome,".model2b"),
-         lm( formula = glm.formula,
-             data = get(data_set)
-         )
-  )
-
-  assign(paste0(outcome,"model2b_reg_stats"),
-         glance(get(paste0(outcome,".model2b"))) %>%
-           mutate(
-             "n" = format(
-               round(nobs,
-                     digits = 0),
-               nsmall = 0),
-             "R2" = format(
-               round(r.squared,
-                     digits = 2),
-               nsmall = 2),
-             "adjust. R2" = format(
-               round(adj.r.squared,
-                     digits = 2),
-               nsmall = 2),
-             "F" = format(
-               round(statistic,
-                     digits = 2),
-               nsmall = 2),
-             "p value" = case_when(
-               p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
-               p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
-               p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
-             )
-           ) %>%
-           select(
-             "n",
-             "R2",
-             "adjust. R2",
-             "F",
-             "p value",
-             "df"
-           )
-  )
-
-  return(get(paste0(outcome,"model2b_reg_stats")))
 }
@@
                          data_set = "dat.prepan")
-kable(phq_prepan_model1b_explan_reg_stats)
-phq_prepan_model1b_explan_reg_stats
-```
-# PHQ prepan: sensitivity
-## Regression: Absolute scores
-### Model 1b: Overlapping disorders, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
-#### Subset of participants 3 months prior to pandemic
-```{r phq model1b sum_score prepan - sensitivity 3 months}
-# Regression coefficients
-phq_prepan_model1b_explan_estimates <- model1b.explan.estimates(outcome = "phq.sum_score_base",
-                         explan_var = "phq.sum_score_prepan",
-                         data_set = "dat.prepan_sensitivity_3months")
-kable(phq_prepan_model1b_explan_estimates)
-phq_prepan_model1b_explan_estimates
-
-# Regression diagnostic statistics
-phq_prepan_model1b_explan_reg_stats <- model1b.explan.reg.stats(outcome = "phq.sum_score_base",
-                         explan_var = "phq.sum_score_prepan",
-                         data_set = "dat.prepan_sensitivity_3months")
-kable(phq_prepan_model1b_explan_reg_stats)
-phq_prepan_model1b_explan_reg_stats
-```
-
-#### Subset of participants 6 months prior to pandemic
-```{r phq model1b sum_score prepan - sensitivity 6 months}
-# Regression coefficients
-phq_prepan_model1b_explan_estimates <- model1b.explan.estimates(outcome = "phq.sum_score_base",
-                         explan_var = "phq.sum_score_prepan",
-                         data_set = "dat.prepan_sensitivity_6months")
-kable(phq_prepan_model1b_explan_estimates)
-phq_prepan_model1b_explan_estimates
-
-# Regression diagnostic statistics
-phq_prepan_model1b_explan_reg_stats <- model1b.explan.reg.stats(outcome = "phq.sum_score_base",
-                         explan_var = "phq.sum_score_prepan",
-                         data_set = "dat.prepan_sensitivity_6months")
-kable(phq_prepan_model1b_explan_reg_stats)
-phq_prepan_model1b_explan_reg_stats
-```
-
-#### Subset of participants 9 months prior to pandemic
-```{r phq model1b sum_score prepan - sensitivity 9 months}
-# Regression coefficients
-phq_prepan_model1b_explan_estimates <- model1b.explan.estimates(outcome = "phq.sum_score_base",
-                         explan_var = "phq.sum_score_prepan",
-                         data_set = "dat.prepan_sensitivity_9months")
-kable(phq_prepan_model1b_explan_estimates)
-phq_prepan_model1b_explan_estimates
-
-# Regression diagnostic statistics
-phq_prepan_model1b_explan_reg_stats <- model1b.explan.reg.stats(outcome = "phq.sum_score_base",
-                         explan_var = "phq.sum_score_prepan",
-                         data_set = "dat.prepan_sensitivity_9months")
 kable(phq_prepan_model1b_explan_reg_stats)
@@
 
-# PCL prepan: sensitivity
+# SENSITIVITY based on highest level of education
+
+# GAD prepan
 ## Regression: Absolute scores
+### Model 0a: Disorder_hierarchical, Unadjusted
+```{r gad education sensitivity model0a sum_score prepan}
+# Regression coefficients
+gad_prepan_model0a_education_estimates <- model0a.explan.estimates(outcome = "gad.sum_score_base",
+                         explan_var = "highest_education",
+                         data_set = "dat.prepan")
+kable(gad_prepan_model0a_education_estimates)
+gad_prepan_model0a_education_estimates
+
+# Regression diagnostic statistics
+gad_prepan_model0a_education_reg_stats <- model0a.explan.reg.stats(outcome = "gad.sum_score_base",
+                         explan_var = "highest_education",
+                         data_set = "dat.prepan")
+kable(gad_prepan_model0a_education_reg_stats)
+gad_prepan_model0a_education_reg_stats
+```
+
+### Model 0b: Overlapping disorders, Unadjusted
+```{r gad education sensitivity model0b sum_score prepan}
+# Regression coefficients
+gad_prepan_model0b_education_estimates <- model0b.explan.estimates(outcome = "gad.sum_score_base",
+                         explan_var = "highest_education",
+                         data_set = "dat.prepan")
+kable(gad_prepan_model0b_education_estimates)
+gad_prepan_model0b_education_estimates
+
+# Regression diagnostic statistics
+gad_prepan_model0b_education_reg_stats <- model0b.explan.reg.stats(outcome = "gad.sum_score_base",
+                         explan_var = "highest_education",
+                         data_set = "dat.prepan")
+kable(gad_prepan_model0b_education_reg_stats)
+gad_prepan_model0b_education_reg_stats
+```
+
+### Model 1a: Disorder hierarchical, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r gad education sensitivity model1a sum_score prepan}
+# Regression coefficients
+gad_prepan_model1a_education_estimates <- model1a.explan.estimates(outcome = "gad.sum_score_base",
+                         explan_var = "highest_education",
+                         data_set = "dat.prepan")
+kable(gad_prepan_model1a_education_estimates)
+gad_prepan_model1a_education_estimates
+
+# Regression diagnostic statistics
+gad_prepan_model1a_education_reg_stats <- model1a.explan.reg.stats(outcome = "gad.sum_score_base",
+                         explan_var = "highest_education",
+                         data_set = "dat.prepan")
+kable(gad_prepan_model1a_education_reg_stats)
+gad_prepan_model1a_education_reg_stats
+```
+
 ### Model 1b: Overlapping disorders, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
-#### Subset of participants 3 months prior to pandemic
-```{r pcl model1b sum_score prepan - sensitivity 3 months}
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r gad education sensitivity model1b sum_score prepan}
+# Regression coefficients
+gad_prepan_model1b_education_estimates <- model1b.explan.estimates(outcome = "gad.sum_score_base",
+                         explan_var = "highest_education",
+                         data_set = "dat.prepan")
+kable(gad_prepan_model1b_education_estimates)
+gad_prepan_model1b_education_estimates
+
+# Regression diagnostic statistics
+gad_prepan_model1b_education_reg_stats <- model1b.explan.reg.stats(outcome = "gad.sum_score_base",
+                         explan_var = "highest_education",
+                         data_set = "dat.prepan")
+kable(gad_prepan_model1b_education_reg_stats)
+gad_prepan_model1b_education_reg_stats
+```
+
+# PHQ prepan
+## Regression: Absolute scores
+### Model 0a: Disorder_hierarchical, Unadjusted
+```{r phq education sensitivity model0a sum_score prepan}
+# Regression coefficients
+phq_prepan_model0a_education_estimates <- model0a.explan.estimates(outcome = "phq.sum_score_base",
+                         explan_var = "highest_education",
+                         data_set = "dat.prepan")
+kable(phq_prepan_model0a_education_estimates)
+phq_prepan_model0a_education_estimates
+
+# Regression diagnostic statistics
+phq_prepan_model0a_education_reg_stats <- model0a.explan.reg.stats(outcome = "phq.sum_score_base",
+                         explan_var = "highest_education",
+                         data_set = "dat.prepan")
+kable(phq_prepan_model0a_education_reg_stats)
+phq_prepan_model0a_education_reg_stats
+```
+
+### Model 0b: Overlapping disorders, Unadjusted
+```{r phq education sensitivity model0b sum_score prepan}
+# Regression coefficients
+phq_prepan_model0b_education_estimates <- model0b.explan.estimates(outcome = "phq.sum_score_base",
+                         explan_var = "highest_education",
+                         data_set = "dat.prepan")
+kable(phq_prepan_model0b_education_estimates)
+phq_prepan_model0b_education_estimates
+
+# Regression diagnostic statistics
+phq_prepan_model0b_education_reg_stats <- model0b.explan.reg.stats(outcome = "phq.sum_score_base",
+                         explan_var = "highest_education",
+                         data_set = "dat.prepan")
+kable(phq_prepan_model0b_education_reg_stats)
+phq_prepan_model0b_education_reg_stats
+```
+
+### Model 1a: Disorder hierarchical, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r phq education sensitivity model1a sum_score prepan}
+# Regression coefficients
+phq_prepan_model1a_education_estimates <- model1a.explan.estimates(outcome = "phq.sum_score_base",
+                         explan_var = "highest_education",
+                         data_set = "dat.prepan")
+kable(phq_prepan_model1a_education_estimates)
+phq_prepan_model1a_education_estimates
+
+# Regression diagnostic statistics
+phq_prepan_model1a_education_reg_stats <- model1a.explan.reg.stats(outcome = "phq.sum_score_base",
+                         explan_var = "highest_education",
+                         data_set = "dat.prepan")
+kable(phq_prepan_model1a_education_reg_stats)
+phq_prepan_model1a_education_reg_stats
+```
+
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r phq education sensitivity model1b sum_score prepan}
+# Regression coefficients
+phq_prepan_model1b_education_estimates <- model1b.explan.estimates(outcome = "phq.sum_score_base",
+                         explan_var = "highest_education",
+                         data_set = "dat.prepan")
+kable(phq_prepan_model1b_education_estimates)
+phq_prepan_model1b_education_estimates
+
+# Regression diagnostic statistics
+phq_prepan_model1b_education_reg_stats <- model1b.explan.reg.stats(outcome = "phq.sum_score_base",
+                         explan_var = "highest_education",
+                         data_set = "dat.prepan")
+kable(phq_prepan_model1b_education_reg_stats)
+phq_prepan_model1b_education_reg_stats
+```
+
+# OCIR prepan 
+## Regression: Absolute scores
+### Model 0a: Disorder_hierarchical, Unadjusted
+```{r ocir education sensitivity model0a sum_score prepan}
+# Regression coefficients
+ocir_prepan_model0a_education_estimates <- model0a.explan.estimates(outcome = "ocir.sum_score_base",
+                         explan_var = "highest_education",
+                         data_set = "dat.prepan")
+kable(ocir_prepan_model0a_education_estimates)
+ocir_prepan_model0a_education_estimates
+
+# Regression diagnostic statistics
+ocir_prepan_model0a_education_reg_stats <- model0a.explan.reg.stats(outcome = "ocir.sum_score_base",
+                         explan_var = "highest_education",
+                         data_set = "dat.prepan")
+kable(ocir_prepan_model0a_education_reg_stats)
+ocir_prepan_model0a_education_reg_stats
+```
+
+### Model 0b: Overlapping disorders, Unadjusted
+```{r ocir education sensitivity model0b sum_score prepan}
+# Regression coefficients
+ocir_prepan_model0b_education_estimates <- model0b.explan.estimates(outcome = "ocir.sum_score_base",
+                         explan_var = "highest_education",
+                         data_set = "dat.prepan")
+kable(ocir_prepan_model0b_education_estimates)
+ocir_prepan_model0b_education_estimates
+
+# Regression diagnostic statistics
+ocir_prepan_model0b_education_reg_stats <- model0b.explan.reg.stats(outcome = "ocir.sum_score_base",
+                         explan_var = "highest_education",
+                         data_set = "dat.prepan")
+kable(ocir_prepan_model0b_education_reg_stats)
+ocir_prepan_model0b_education_reg_stats
+```
+
+### Model 1a: Disorder hierarchical, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r ocir education sensitivity model1a sum_score prepan}
+# Regression coefficients
+ocir_prepan_model1a_education_estimates <- model1a.explan.estimates(outcome = "ocir.sum_score_base",
+                         explan_var = "highest_education",
+                         data_set = "dat.prepan")
+kable(ocir_prepan_model1a_education_estimates)
+ocir_prepan_model1a_education_estimates
+
+# Regression diagnostic statistics
+ocir_prepan_model1a_education_reg_stats <- model1a.explan.reg.stats(outcome = "ocir.sum_score_base",
+                         explan_var = "highest_education",
+                         data_set = "dat.prepan")
+kable(ocir_prepan_model1a_education_reg_stats)
+ocir_prepan_model1a_education_reg_stats
+```
+
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r ocir education sensitivity model1b sum_score prepan}
+# Regression coefficients
+ocir_prepan_model1b_education_estimates <- model1b.explan.estimates(outcome = "ocir.sum_score_base",
+                         explan_var = "highest_education",
+                         data_set = "dat.prepan")
+kable(ocir_prepan_model1b_education_estimates)
+ocir_prepan_model1b_education_estimates
+
+# Regression diagnostic statistics
+ocir_prepan_model1b_education_reg_stats <- model1b.explan.reg.stats(outcome = "ocir.sum_score_base",
+                         explan_var = "highest_education",
+                         data_set = "dat.prepan")
+kable(ocir_prepan_model1b_education_reg_stats)
+ocir_prepan_model1b_education_reg_stats
+```
+
+#PCL prepan 
+## Regression: Absolute scores
+### Model 0a: Disorder_hierarchical, Unadjusted
+```{r pcl education sensitivty model0a sum_score prepan}
+# Regression coefficients
+pcl_prepan_model0a_education_estimates <- model0a.explan.estimates(outcome = "pcl.sum_score_base",
+                         explan_var = "highest_education",
+                         data_set = "dat.prepan")
+kable(pcl_prepan_model0a_education_estimates)
+pcl_prepan_model0a_education_estimates
+
+# Regression diagnostic statistics
+pcl_prepan_model0a_education_reg_stats <- model0a.explan.reg.stats(outcome = "pcl.sum_score_base",
+                         explan_var = "highest_education",
+                         data_set = "dat.prepan")
+kable(pcl_prepan_model0a_education_reg_stats)
+pcl_prepan_model0a_education_reg_stats
+```
+
+### Model 0b: Overlapping disorders, Unadjusted
+```{r pcl education sensitivty model0b sum_score prepan}
+# Regression coefficients
+pcl_prepan_model0b_education_estimates <- model0b.explan.estimates(outcome = "pcl.sum_score_base",
+                         explan_var = "highest_education",
+                         data_set = "dat.prepan")
+kable(pcl_prepan_model0b_education_estimates)
+pcl_prepan_model0b_education_estimates
+
+# Regression diagnostic statistics
+pcl_prepan_model0b_education_reg_stats <- model0b.explan.reg.stats(outcome = "pcl.sum_score_base",
+                         explan_var = "highest_education",
+                         data_set = "dat.prepan")
+kable(pcl_prepan_model0b_education_reg_stats)
+pcl_prepan_model0b_education_reg_stats
+```
+
+### Model 1a: Disorder hierarchical, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r pcl education sensitivty model1a sum_score prepan}
+# Regression coefficients
+pcl_prepan_model1a_education_estimates <- model1a.explan.estimates(outcome = "pcl.sum_score_base",
+                         explan_var = "highest_education",
+                         data_set = "dat.prepan")
+kable(pcl_prepan_model1a_education_estimates)
+pcl_prepan_model1a_education_estimates
+
+# Regression diagnostic statistics
+pcl_prepan_model1a_education_reg_stats <- model1a.explan.reg.stats(outcome = "pcl.sum_score_base",
+                         explan_var = "highest_education",
+                         data_set = "dat.prepan")
+kable(pcl_prepan_model1a_education_reg_stats)
+pcl_prepan_model1a_education_reg_stats
+```
+
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r pcl education sensitivty model1b sum_score prepan}
+# Regression coefficients
+pcl_prepan_model1b_education_estimates <- model1b.explan.estimates(outcome = "pcl.sum_score_base",
+                         explan_var = "highest_education",
+                         data_set = "dat.prepan")
+kable(pcl_prepan_model1b_education_estimates)
+pcl_prepan_model1b_education_estimates
+
+# Regression diagnostic statistics
+pcl_prepan_model1b_education_reg_stats <- model1b.explan.reg.stats(outcome = "pcl.sum_score_base",
+                         explan_var = "highest_education",
+                         data_set = "dat.prepan")
+kable(pcl_prepan_model1b_education_reg_stats)
+pcl_prepan_model1b_education_reg_stats
+```
+
+# SENSITIVITY based on employment status
+
+# GAD prepan
+## Regression: Absolute scores
+### Model 0a: Disorder_hierarchical, Unadjusted
+```{r gad employment sensitivity model0a sum_score prepan}
+# Regression coefficients
+gad_prepan_model0a_employment_estimates <- model0a.explan.estimates(outcome = "gad.sum_score_base",
+                         explan_var = "employment.unemployed_numeric",
+                         data_set = "dat.prepan")
+kable(gad_prepan_model0a_employment_estimates)
+gad_prepan_model0a_employment_estimates
+
+# Regression diagnostic statistics
+gad_prepan_model0a_employment_reg_stats <- model0a.explan.reg.stats(outcome = "gad.sum_score_base",
+                         explan_var = "employment.unemployed_numeric",
+                         data_set = "dat.prepan")
+kable(gad_prepan_model0a_employment_reg_stats)
+gad_prepan_model0a_employment_reg_stats
+```
+
+### Model 0b: Overlapping disorders, Unadjusted
+```{r gad employment sensitivity model0b sum_score prepan}
+# Regression coefficients
+gad_prepan_model0b_employment_estimates <- model0b.explan.estimates(outcome = "gad.sum_score_base",
+                         explan_var = "employment.unemployed",
+                         data_set = "dat.prepan")
+kable(gad_prepan_model0b_employment_estimates)
+gad_prepan_model0b_employment_estimates
+
+# Regression diagnostic statistics
+gad_prepan_model0b_employment_reg_stats <- model0b.explan.reg.stats(outcome = "gad.sum_score_base",
+                         explan_var = "employment.unemployed",
+                         data_set = "dat.prepan")
+kable(gad_prepan_model0b_employment_reg_stats)
+gad_prepan_model0b_employment_reg_stats
+```
+
+### Model 1a: Disorder hierarchical, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r gad employment sensitivity model1a sum_score prepan}
+# Regression coefficients
+gad_prepan_model1a_employment_estimates <- model1a.explan.estimates(outcome = "gad.sum_score_base",
+                         explan_var = "employment.unemployed",
+                         data_set = "dat.prepan")
+kable(gad_prepan_model1a_employment_estimates)
+gad_prepan_model1a_employment_estimates
+
+# Regression diagnostic statistics
+gad_prepan_model1a_employment_reg_stats <- model1a.explan.reg.stats(outcome = "gad.sum_score_base",
+                         explan_var = "employment.unemployed",
+                         data_set = "dat.prepan")
+kable(gad_prepan_model1a_employment_reg_stats)
+gad_prepan_model1a_employment_reg_stats
+```
+
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r gad employment sensitivity model1b sum_score prepan}
+# Regression coefficients
+gad_prepan_model1b_employment_estimates <- model1b.explan.estimates(outcome = "gad.sum_score_base",
+                         explan_var = "employment.unemployed",
+                         data_set = "dat.prepan")
+kable(gad_prepan_model1b_employment_estimates)
+gad_prepan_model1b_employment_estimates
+
+# Regression diagnostic statistics
+gad_prepan_model1b_employment_reg_stats <- model1b.explan.reg.stats(outcome = "gad.sum_score_base",
+                         explan_var = "employment.unemployed",
+                         data_set = "dat.prepan")
+kable(gad_prepan_model1b_employment_reg_stats)
+gad_prepan_model1b_employment_reg_stats
+```
+
+# PHQ prepan
+## Regression: Absolute scores
+### Model 0a: Disorder_hierarchical, Unadjusted
+```{r phq employment sensitivity model0a sum_score prepan}
+# Regression coefficients
+phq_prepan_model0a_employment_estimates <- model0a.explan.estimates(outcome = "phq.sum_score_base",
+                         explan_var = "employment.unemployed",
+                         data_set = "dat.prepan")
+kable(phq_prepan_model0a_employment_estimates)
+phq_prepan_model0a_employment_estimates
+
+# Regression diagnostic statistics
+phq_prepan_model0a_employment_reg_stats <- model0a.explan.reg.stats(outcome = "phq.sum_score_base",
+                         explan_var = "employment.unemployed",
+                         data_set = "dat.prepan")
+kable(phq_prepan_model0a_employment_reg_stats)
+phq_prepan_model0a_employment_reg_stats
+```
+
+### Model 0b: Overlapping disorders, Unadjusted
+```{r phq employment sensitivity model0b sum_score prepan}
+# Regression coefficients
+phq_prepan_model0b_employment_estimates <- model0b.explan.estimates(outcome = "phq.sum_score_base",
+                         explan_var = "employment.unemployed",
+                         data_set = "dat.prepan")
+kable(phq_prepan_model0b_employment_estimates)
+phq_prepan_model0b_employment_estimates
+
+# Regression diagnostic statistics
+phq_prepan_model0b_employment_reg_stats <- model0b.explan.reg.stats(outcome = "phq.sum_score_base",
+                         explan_var = "employment.unemployed",
+                         data_set = "dat.prepan")
+kable(phq_prepan_model0b_employment_reg_stats)
+phq_prepan_model0b_employment_reg_stats
+```
+
+### Model 1a: Disorder hierarchical, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r phq employment sensitivity model1a sum_score prepan}
+# Regression coefficients
+phq_prepan_model1a_employment_estimates <- model1a.explan.estimates(outcome = "phq.sum_score_base",
+                         explan_var = "employment.unemployed",
+                         data_set = "dat.prepan")
+kable(phq_prepan_model1a_employment_estimates)
+phq_prepan_model1a_employment_estimates
+
+# Regression diagnostic statistics
+phq_prepan_model1a_employment_reg_stats <- model1a.explan.reg.stats(outcome = "phq.sum_score_base",
+                         explan_var = "employment.unemployed",
+                         data_set = "dat.prepan")
+kable(phq_prepan_model1a_employment_reg_stats)
+phq_prepan_model1a_employment_reg_stats
+```
+
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r phq employment sensitivity model1b sum_score prepan}
+# Regression coefficients
+phq_prepan_model1b_employment_estimates <- model1b.explan.estimates(outcome = "phq.sum_score_base",
+                         explan_var = "employment.unemployed",
+                         data_set = "dat.prepan")
+kable(phq_prepan_model1b_employment_estimates)
+phq_prepan_model1b_employment_estimates
+
+# Regression diagnostic statistics
+phq_prepan_model1b_employment_reg_stats <- model1b.explan.reg.stats(outcome = "phq.sum_score_base",
+                         explan_var = "employment.unemployed",
+                         data_set = "dat.prepan")
+kable(phq_prepan_model1b_employment_reg_stats)
+phq_prepan_model1b_employment_reg_stats
+```
+
+# OCIR prepan 
+## Regression: Absolute scores
+### Model 0a: Disorder_hierarchical, Unadjusted
+```{r ocir employment sensitivity model0a sum_score prepan}
+# Regression coefficients
+ocir_prepan_model0a_employment_estimates <- model0a.explan.estimates(outcome = "ocir.sum_score_base",
+                         explan_var = "employment.unemployed",
+                         data_set = "dat.prepan")
+kable(ocir_prepan_model0a_employment_estimates)
+ocir_prepan_model0a_employment_estimates
+
+# Regression diagnostic statistics
+ocir_prepan_model0a_employment_reg_stats <- model0a.explan.reg.stats(outcome = "ocir.sum_score_base",
+                         explan_var = "employment.unemployed",
+                         data_set = "dat.prepan")
+kable(ocir_prepan_model0a_employment_reg_stats)
+ocir_prepan_model0a_employment_reg_stats
+```
+
+### Model 0b: Overlapping disorders, Unadjusted
+```{r ocir employment sensitivity model0b sum_score prepan}
+# Regression coefficients
+ocir_prepan_model0b_employment_estimates <- model0b.explan.estimates(outcome = "ocir.sum_score_base",
+                         explan_var = "employment.unemployed",
+                         data_set = "dat.prepan")
+kable(ocir_prepan_model0b_employment_estimates)
+ocir_prepan_model0b_employment_estimates
+
+# Regression diagnostic statistics
+ocir_prepan_model0b_employment_reg_stats <- model0b.explan.reg.stats(outcome = "ocir.sum_score_base",
+                         explan_var = "employment.unemployed",
+                         data_set = "dat.prepan")
+kable(ocir_prepan_model0b_employment_reg_stats)
+ocir_prepan_model0b_employment_reg_stats
+```
+
+### Model 1a: Disorder hierarchical, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r ocir employment sensitivity model1a sum_score prepan}
+# Regression coefficients
+ocir_prepan_model1a_employment_estimates <- model1a.explan.estimates(outcome = "ocir.sum_score_base",
+                         explan_var = "employment.unemployed",
+                         data_set = "dat.prepan")
+kable(ocir_prepan_model1a_employment_estimates)
+ocir_prepan_model1a_employment_estimates
+
+# Regression diagnostic statistics
+ocir_prepan_model1a_employment_reg_stats <- model1a.explan.reg.stats(outcome = "ocir.sum_score_base",
+                         explan_var = "employment.unemployed",
+                         data_set = "dat.prepan")
+kable(ocir_prepan_model1a_employment_reg_stats)
+ocir_prepan_model1a_employment_reg_stats
+```
+
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r ocir employment sensitivity model1b sum_score prepan}
+# Regression coefficients
+ocir_prepan_model1b_employment_estimates <- model1b.explan.estimates(outcome = "ocir.sum_score_base",
+                         explan_var = "employment.unemployed",
+                         data_set = "dat.prepan")
+kable(ocir_prepan_model1b_employment_estimates)
+ocir_prepan_model1b_employment_estimates
+
+# Regression diagnostic statistics
+ocir_prepan_model1b_employment_reg_stats <- model1b.explan.reg.stats(outcome = "ocir.sum_score_base",
+                         explan_var = "employment.unemployed",
+                         data_set = "dat.prepan")
+kable(ocir_prepan_model1b_employment_reg_stats)
+ocir_prepan_model1b_employment_reg_stats
+```
+
+#PCL prepan 
+## Regression: Absolute scores
+### Model 0a: Disorder_hierarchical, Unadjusted
+```{r pcl employment sensitivty model0a sum_score prepan}
+# Regression coefficients
+pcl_prepan_model0a_employment_estimates <- model0a.explan.estimates(outcome = "pcl.sum_score_base",
+                         explan_var = "employment.unemployed",
+                         data_set = "dat.prepan")
+kable(pcl_prepan_model0a_employment_estimates)
+pcl_prepan_model0a_employment_estimates
+
+# Regression diagnostic statistics
+pcl_prepan_model0a_employment_reg_stats <- model0a.explan.reg.stats(outcome = "pcl.sum_score_base",
+                         explan_var = "employment.unemployed",
+                         data_set = "dat.prepan")
+kable(pcl_prepan_model0a_employment_reg_stats)
+pcl_prepan_model0a_employment_reg_stats
+```
+
+### Model 0b: Overlapping disorders, Unadjusted
+```{r pcl employment sensitivty model0b sum_score prepan}
+# Regression coefficients
+pcl_prepan_model0b_employment_estimates <- model0b.explan.estimates(outcome = "pcl.sum_score_base",
+                         explan_var = "employment.unemployed",
+                         data_set = "dat.prepan")
+kable(pcl_prepan_model0b_employment_estimates)
+pcl_prepan_model0b_employment_estimates
+
+# Regression diagnostic statistics
+pcl_prepan_model0b_employment_reg_stats <- model0b.explan.reg.stats(outcome = "pcl.sum_score_base",
+                         explan_var = "employment.unemployed",
+                         data_set = "dat.prepan")
+kable(pcl_prepan_model0b_employment_reg_stats)
+pcl_prepan_model0b_employment_reg_stats
+```
+
+### Model 1a: Disorder hierarchical, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r pcl employment sensitivty model1a sum_score prepan}
+# Regression coefficients
+pcl_prepan_model1a_employment_estimates <- model1a.explan.estimates(outcome = "pcl.sum_score_base",
+                         explan_var = "employment.unemployed",
+                         data_set = "dat.prepan")
+kable(pcl_prepan_model1a_employment_estimates)
+pcl_prepan_model1a_employment_estimates
+
+# Regression diagnostic statistics
+pcl_prepan_model1a_employment_reg_stats <- model1a.explan.reg.stats(outcome = "pcl.sum_score_base",
+                         explan_var = "employment.unemployed",
+                         data_set = "dat.prepan")
+kable(pcl_prepan_model1a_employment_reg_stats)
+pcl_prepan_model1a_employment_reg_stats
+```
+
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r pcl employment sensitivty model1b sum_score prepan}
+# Regression coefficients
+pcl_prepan_model1b_employment_estimates <- model1b.explan.estimates(outcome = "pcl.sum_score_base",
+                         explan_var = "employment.unemployed",
+                         data_set = "dat.prepan")
+kable(pcl_prepan_model1b_employment_estimates)
+pcl_prepan_model1b_employment_estimates
+
+# Regression diagnostic statistics
+pcl_prepan_model1b_employment_reg_stats <- model1b.explan.reg.stats(outcome = "pcl.sum_score_base",
+                         explan_var = "employment.unemployed",
+                         data_set = "dat.prepan")
+kable(pcl_prepan_model1b_employment_reg_stats)
+pcl_prepan_model1b_employment_reg_stats
+```
+
+# SENSITIVITY based on employment change
+
+```{r create an employment change variable}
+dat.prepan <- dat.prepan %>%
+  mutate(employment_change =
+           case_when(
+             employment.unemployed_numeric == "1" ~ "Unemployed",
+             employment.became_unemployed_numeric == "1" ~ "Became Unemployed",                         
+             employment.furloughed_or_paid_leave_government_funded_numeric == "1" ~ "Furlough",
+             employment.furloughed_or_paid_leave_company_funded_numeric == "1" ~ "Furlough",    
+             employment.paid_leave_furloughed_numeric == "1" ~ "Furlough",                             
+             key_worker_numeric == "1" ~ "Key Worker",                                            
+             employment.government_work_key_workers_numeric == "1" ~ "Key Worker",                
+             employment.zerohours_contract_numeric == "1" ~ "Zero Hours Contract",                         
+             employment.retired_numeric == "1" ~ "Retired",                                   
+             employment.student_gcse_or_a_level_numeric == "1" ~ "Student",                   
+             employment.student_university_numeric == "1" ~ "Student"                        
+           )
+  )
+
+dat.prepan$employment_change <- as.factor(dat.prepan$employment_change)
+```
+
+# GAD prepan
+## Regression: Absolute scores
+### Model 0a: Disorder_hierarchical, Unadjusted
+```{r gad employment change sensitivity model0a sum_score prepan}
+# Regression coefficients
+gad_prepan_model0a_employmentchange_estimates <- model0a.explan.estimates(outcome = "gad.sum_score_base",
+                         explan_var = "employment_change",
+                         data_set = "dat.prepan")
+kable(gad_prepan_model0a_employmentchange_estimates)
+gad_prepan_model0a_employmentchange_estimates
+
+# Regression diagnostic statistics
+gad_prepan_model0a_employmentchange_reg_stats <- model0a.explan.reg.stats(outcome = "gad.sum_score_base",
+                         explan_var = "employment_change",
+                         data_set = "dat.prepan")
+kable(gad_prepan_model0a_employmentchange_reg_stats)
+gad_prepan_model0a_employmentchange_reg_stats
+```
+
+### Model 0b: Overlapping disorders, Unadjusted
+```{r gad employment change sensitivity model0b sum_score prepan}
+# Regression coefficients
+gad_prepan_model0b_employmentchange_estimates <- model0b.explan.estimates(outcome = "gad.sum_score_base",
+                         explan_var = "employment_change",
+                         data_set = "dat.prepan")
+kable(gad_prepan_model0b_employmentchange_estimates)
+gad_prepan_model0b_employmentchange_estimates
+
+# Regression diagnostic statistics
+gad_prepan_model0b_employmentchange_reg_stats <- model0b.explan.reg.stats(outcome = "gad.sum_score_base",
+                         explan_var = "employment_change",
+                         data_set = "dat.prepan")
+kable(gad_prepan_model0b_employmentchange_reg_stats)
+gad_prepan_model0b_employmentchange_reg_stats
+```
+
+### Model 1a: Disorder hierarchical, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r gad employment change sensitivity model1a sum_score prepan}
+# Regression coefficients
+gad_prepan_model1a_employmentchange_estimates <- model1a.explan.estimates(outcome = "gad.sum_score_base",
+                         explan_var = "employment_change",
+                         data_set = "dat.prepan")
+kable(gad_prepan_model1a_employmentchange_estimates)
+gad_prepan_model1a_employmentchange_estimates
+
+# Regression diagnostic statistics
+gad_prepan_model1a_employmentchange_reg_stats <- model1a.explan.reg.stats(outcome = "gad.sum_score_base",
+                         explan_var = "employment_change",
+                         data_set = "dat.prepan")
+kable(gad_prepan_model1a_employmentchange_reg_stats)
+gad_prepan_model1a_employmentchange_reg_stats
+```
+
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r gad employment change sensitivity model1b sum_score prepan}
+# Regression coefficients
+gad_prepan_model1b_employmentchange_estimates <- model1b.explan.estimates(outcome = "gad.sum_score_base",
+                         explan_var = "employment_change",
+                         data_set = "dat.prepan")
+kable(gad_prepan_model1b_employmentchange_estimates)
+gad_prepan_model1b_employmentchange_estimates
+
+# Regression diagnostic statistics
+gad_prepan_model1b_employmentchange_reg_stats <- model1b.explan.reg.stats(outcome = "gad.sum_score_base",
+                         explan_var = "employment_change",
+                         data_set = "dat.prepan")
+kable(gad_prepan_model1b_employmentchange_reg_stats)
+gad_prepan_model1b_employmentchange_reg_stats
+```
+
+# PHQ prepan
+## Regression: Absolute scores
+### Model 0a: Disorder_hierarchical, Unadjusted
+```{r phq employment change sensitivity model0a sum_score prepan}
+# Regression coefficients
+phq_prepan_model0a_employmentchange_estimates <- model0a.explan.estimates(outcome = "phq.sum_score_base",
+                         explan_var = "employment_change",
+                         data_set = "dat.prepan")
+kable(phq_prepan_model0a_employmentchange_estimates)
+phq_prepan_model0a_employmentchange_estimates
+
+# Regression diagnostic statistics
+phq_prepan_model0a_employmentchange_reg_stats <- model0a.explan.reg.stats(outcome = "phq.sum_score_base",
+                         explan_var = "employment_change",
+                         data_set = "dat.prepan")
+kable(phq_prepan_model0a_employmentchange_reg_stats)
+phq_prepan_model0a_employmentchange_reg_stats
+```
+
+### Model 0b: Overlapping disorders, Unadjusted
+```{r phq employment change sensitivity model0b sum_score prepan}
+# Regression coefficients
+phq_prepan_model0b_employmentchange_estimates <- model0b.explan.estimates(outcome = "phq.sum_score_base",
+                         explan_var = "employment_change",
+                         data_set = "dat.prepan")
+kable(phq_prepan_model0b_employmentchange_estimates)
+phq_prepan_model0b_employmentchange_estimates
+
+# Regression diagnostic statistics
+phq_prepan_model0b_employmentchange_reg_stats <- model0b.explan.reg.stats(outcome = "phq.sum_score_base",
+                         explan_var = "employment_change",
+                         data_set = "dat.prepan")
+kable(phq_prepan_model0b_employmentchange_reg_stats)
+phq_prepan_model0b_employmentchange_reg_stats
+```
+
+### Model 1a: Disorder hierarchical, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r phq employment change sensitivity model1a sum_score prepan}
+# Regression coefficients
+phq_prepan_model1a_employmentchange_estimates <- model1a.explan.estimates(outcome = "phq.sum_score_base",
+                         explan_var = "employment_change",
+                         data_set = "dat.prepan")
+kable(phq_prepan_model1a_employmentchange_estimates)
+phq_prepan_model1a_employmentchange_estimates
+
+# Regression diagnostic statistics
+phq_prepan_model1a_employmentchange_reg_stats <- model1a.explan.reg.stats(outcome = "phq.sum_score_base",
+                         explan_var = "employment_change",
+                         data_set = "dat.prepan")
+kable(phq_prepan_model1a_employmentchange_reg_stats)
+phq_prepan_model1a_employmentchange_reg_stats
+```
+
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r phq employment change sensitivity model1b sum_score prepan}
+# Regression coefficients
+phq_prepan_model1b_employmentchange_estimates <- model1b.explan.estimates(outcome = "phq.sum_score_base",
+                         explan_var = "employment_change",
+                         data_set = "dat.prepan")
+kable(phq_prepan_model1b_employmentchange_estimates)
+phq_prepan_model1b_employmentchange_estimates
+
+# Regression diagnostic statistics
+phq_prepan_model1b_employmentchange_reg_stats <- model1b.explan.reg.stats(outcome = "phq.sum_score_base",
+                         explan_var = "employment_change",
+                         data_set = "dat.prepan")
+kable(phq_prepan_model1b_employmentchange_reg_stats)
+phq_prepan_model1b_employmentchange_reg_stats
+```
+
+# OCIR prepan 
+## Regression: Absolute scores
+### Model 0a: Disorder_hierarchical, Unadjusted
+```{r ocir employment change sensitivity model0a sum_score prepan}
+# Regression coefficients
+ocir_prepan_model0a_employmentchange_estimates <- model0a.explan.estimates(outcome = "ocir.sum_score_base",
+                         explan_var = "employment_change",
+                         data_set = "dat.prepan")
+kable(ocir_prepan_model0a_employmentchange_estimates)
+ocir_prepan_model0a_employmentchange_estimates
+
+# Regression diagnostic statistics
+ocir_prepan_model0a_employmentchange_reg_stats <- model0a.explan.reg.stats(outcome = "ocir.sum_score_base",
+                         explan_var = "employment_change",
+                         data_set = "dat.prepan")
+kable(ocir_prepan_model0a_employmentchange_reg_stats)
+ocir_prepan_model0a_employmentchange_reg_stats
+```
+
+### Model 0b: Overlapping disorders, Unadjusted
+```{r ocir employment change sensitivity model0b sum_score prepan}
+# Regression coefficients
+ocir_prepan_model0b_employmentchange_estimates <- model0b.explan.estimates(outcome = "ocir.sum_score_base",
+                         explan_var = "employment_change",
+                         data_set = "dat.prepan")
+kable(ocir_prepan_model0b_employmentchange_estimates)
+ocir_prepan_model0b_employmentchange_estimates
+
+# Regression diagnostic statistics
+ocir_prepan_model0b_employmentchange_reg_stats <- model0b.explan.reg.stats(outcome = "ocir.sum_score_base",
+                         explan_var = "employment_change",
+                         data_set = "dat.prepan")
+kable(ocir_prepan_model0b_employmentchange_reg_stats)
+ocir_prepan_model0b_employmentchange_reg_stats
+```
+
+### Model 1a: Disorder hierarchical, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r ocir employment change sensitivity model1a sum_score prepan}
+# Regression coefficients
+ocir_prepan_model1a_employmentchange_estimates <- model1a.explan.estimates(outcome = "ocir.sum_score_base",
+                         explan_var = "employment_change",
+                         data_set = "dat.prepan")
+kable(ocir_prepan_model1a_employmentchange_estimates)
+ocir_prepan_model1a_employmentchange_estimates
+
+# Regression diagnostic statistics
+ocir_prepan_model1a_employmentchange_reg_stats <- model1a.explan.reg.stats(outcome = "ocir.sum_score_base",
+                         explan_var = "employment_change",
+                         data_set = "dat.prepan")
+kable(ocir_prepan_model1a_employmentchange_reg_stats)
+ocir_prepan_model1a_employmentchange_reg_stats
+```
+
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r ocir employment change sensitivity model1b sum_score prepan}
+# Regression coefficients
+ocir_prepan_model1b_employmentchange_estimates <- model1b.explan.estimates(outcome = "ocir.sum_score_base",
+                         explan_var = "employment_change",
+                         data_set = "dat.prepan")
+kable(ocir_prepan_model1b_employmentchange_estimates)
+ocir_prepan_model1b_employmentchange_estimates
+
+# Regression diagnostic statistics
+ocir_prepan_model1b_employmentchange_reg_stats <- model1b.explan.reg.stats(outcome = "ocir.sum_score_base",
+                         explan_var = "employment_change",
+                         data_set = "dat.prepan")
+kable(ocir_prepan_model1b_employmentchange_reg_stats)
+ocir_prepan_model1b_employmentchange_reg_stats
+```
+
+#PCL prepan 
+## Regression: Absolute scores
+### Model 0a: Disorder_hierarchical, Unadjusted
+```{r pcl employment change sensitivty model0a sum_score prepan}
+# Regression coefficients
+pcl_prepan_model0a_employmentchange_estimates <- model0a.explan.estimates(outcome = "pcl.sum_score_base",
+                         explan_var = "employment_change",
+                         data_set = "dat.prepan")
+kable(pcl_prepan_model0a_employmentchange_estimates)
+pcl_prepan_model0a_employmentchange_estimates
+
+# Regression diagnostic statistics
+pcl_prepan_model0a_employmentchange_reg_stats <- model0a.explan.reg.stats(outcome = "pcl.sum_score_base",
+                         explan_var = "employment_change",
+                         data_set = "dat.prepan")
+kable(pcl_prepan_model0a_employmentchange_reg_stats)
+pcl_prepan_model0a_employmentchange_reg_stats
+```
+
+### Model 0b: Overlapping disorders, Unadjusted
+```{r pcl employment change sensitivty model0b sum_score prepan}
+# Regression coefficients
+pcl_prepan_model0b_employmentchange_estimates <- model0b.explan.estimates(outcome = "pcl.sum_score_base",
+                         explan_var = "employment_change",
+                         data_set = "dat.prepan")
+kable(pcl_prepan_model0b_employmentchange_estimates)
+pcl_prepan_model0b_employmentchange_estimates
+
+# Regression diagnostic statistics
+pcl_prepan_model0b_employmentchange_reg_stats <- model0b.explan.reg.stats(outcome = "pcl.sum_score_base",
+                         explan_var = "employment_change",
+                         data_set = "dat.prepan")
+kable(pcl_prepan_model0b_employmentchange_reg_stats)
+pcl_prepan_model0b_employmentchange_reg_stats
+```
+
+### Model 1a: Disorder hierarchical, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r pcl employment change sensitivty model1a sum_score prepan}
+# Regression coefficients
+pcl_prepan_model1a_employmentchange_estimates <- model1a.explan.estimates(outcome = "pcl.sum_score_base",
+                         explan_var = "employment_change",
+                         data_set = "dat.prepan")
+kable(pcl_prepan_model1a_employmentchange_estimates)
+pcl_prepan_model1a_employmentchange_estimates
+
+# Regression diagnostic statistics
+pcl_prepan_model1a_employmentchange_reg_stats <- model1a.explan.reg.stats(outcome = "pcl.sum_score_base",
+                         explan_var = "employment_change",
+                         data_set = "dat.prepan")
+kable(pcl_prepan_model1a_employmentchange_reg_stats)
+pcl_prepan_model1a_employmentchange_reg_stats
+```
+
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r pcl employment change sensitivty model1b sum_score prepan}
+# Regression coefficients
+pcl_prepan_model1b_employmentchange_estimates <- model1b.explan.estimates(outcome = "pcl.sum_score_base",
+                         explan_var = "employment_change",
+                         data_set = "dat.prepan")
+kable(pcl_prepan_model1b_employmentchange_estimates)
+pcl_prepan_model1b_employmentchange_estimates
+
+# Regression diagnostic statistics
+pcl_prepan_model1b_employmentchange_reg_stats <- model1b.explan.reg.stats(outcome = "pcl.sum_score_base",
+                         explan_var = "employment_change",
+                         data_set = "dat.prepan")
+kable(pcl_prepan_model1b_employmentchange_reg_stats)
+pcl_prepan_model1b_employmentchange_reg_stats
+```
+
+# Sensitivity anlayses based on education and employment
+# FUNCTION CHANGE to include education as predictors
+
+```{r model0a education function}
+model0a.estimates <- function(outcome, data_set) {
+  # define the variable name of the dependent variable
+  dependent.variable <- outcome
+  # define the independent variables
+  independent.variables <- c("Disorder_hierarchical",
+                             "highest_education")
+  # create the formula
+  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
+  glm.formula
+
+  # run the glm
+  assign(paste0(outcome,".model0a"),
+         lm( formula = glm.formula,
+              data = get(data_set)
+              )
+  )
+
+  assign(paste0(outcome,"model0a_estimates"),
+         tidy(get(paste0(outcome,".model0a")), conf.int = TRUE) %>%
+           mutate(
+             "Indepent variable" = recode_factor(
+               term,
+               "(Intercept)" = "Intercept",
+               "Disorder_hierarchicalAnxiety disorders" = "Anxiety disorders",
+               "Disorder_hierarchicalEating disorders" = "Eating disorders",
+               "Disorder_hierarchicalOCDs" = "OCDs",
+               "Disorder_hierarchicalPTSD" = "PTSD",
+               "Disorder_hierarchicalDepressive disorders" = "Depressive disorders",
+               "Disorder_hierarchicalBipolar disorders" = "Bipolar disorders", 
+               "highest_educationNVQ" = "Highest education NVQ", 
+               "highest_educationA-levels" = "Highest education A-Levels",
+               "highest_educationUniversity" = "Highest education University"
+             ),
+    "Estimate" = format(
+      round(estimate,
+            digits = 2),
+      nsmall = 2),
+    "95% CI low" = format(
+      round(conf.low,
+            digits = 2),
+      nsmall = 2),
+    "95% CI up" = format(
+      round(conf.high,
+            digits = 2),
+      nsmall = 2),
+    "SE" = format(
+      round(std.error,
+            digits = 2),
+      nsmall = 2),
+    "z score" = format(
+      round(statistic,
+            digits = 2),
+      nsmall = 2),
+    "p value" = case_when(
+      p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
+      p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
+      p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
+  )
+  ) %>%
+  select(
+    "Indepent variable",
+    "Estimate",
+    "95% CI low",
+    "95% CI up",
+    "SE",
+#    "z score",
+    "p value"
+  )
+  )
+
+  return(get(paste0(outcome,"model0a_estimates")))
+}
+
+model0a.reg.stats <- function(outcome, data_set) {
+  # define the variable name of the dependent variable
+  dependent.variable <- outcome
+  # define the independent variables
+  independent.variables <- c("Disorder_hierarchical")
+  # create the formula
+  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
+  glm.formula
+
+  # run the glm
+  assign(paste0(outcome,".model0a"),
+         lm( formula = glm.formula,
+              data = get(data_set)
+              )
+  )
+
+  assign(paste0(outcome,"model0a_reg_stats"),
+         glance(get(paste0(outcome,".model0a"))) %>%
+           mutate(
+             "n" = format(
+               round(nobs,
+                     digits = 0),
+               nsmall = 0),
+             "R2" = format(
+               round(r.squared,
+                     digits = 2),
+               nsmall = 2),
+             "adjust. R2" = format(
+               round(adj.r.squared,
+                     digits = 2),
+               nsmall = 2),
+             "F" = format(
+               round(statistic,
+                     digits = 2),
+               nsmall = 2),
+             "p value" = case_when(
+               p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
+               p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
+               p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
+             )
+           ) %>%
+           select(
+             "n",
+             "R2",
+             "adjust. R2",
+             "F",
+             "p value",
+             "df"
+           )
+  )
+
+  return(get(paste0(outcome,"model0a_reg_stats")))
+}
+```
+
+```{r model0b education function}
+model0b.estimates <- function(outcome, data_set) {
+  # define the variable name of the dependent variable
+  dependent.variable <- outcome
+  # define the independent variables
+  independent.variables <- c("depression_and_anxiety",
+                             "eating_disorders",
+                             "obsessive_compulsive_disorders",
+                             "bipolar_and_schizophrenia",
+                             "mhd.posttraumatic_stress_disorder_ptsd",
+                             "autism_spectrum_disorder",
+                             "mhd.attention_deficit_hyperactivity_disorder",
+                             "mhd.personality_disorder", 
+                             "highest_education"
+                                )
+  # create the formula
+  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
+  glm.formula
+
+  # run the glm
+  assign(paste0(outcome,".model0b"),
+         lm( formula = glm.formula,
+             data = get(data_set)
+         )
+  )
+
+  assign(paste0(outcome,"model0b_estimates"),
+         tidy(get(paste0(outcome,".model0b")), conf.int = TRUE) %>%
+           mutate(
+             "Indepent variable" = recode_factor(
+               term,
+               "(Intercept)" = "Intercept",
+               "anxiety_disordersAnxiety disorder" = "Anxiety disorders",
+               "depressive_disordersDepressive disorder" = "Depressive disorders",
+               "depression_and_anxietyDepressive and anxiety disorder" = "Depressive and anxiety disorder",
+               "depression_and_anxietyOnly depressive disorder" = "Only depressive disorder",
+               "depression_and_anxietyOnly anxiety disorder" = "Only anxiety disorder",
+               "eating_disordersEating disorder" = "Eating disorders",
+               "obsessive_compulsive_disordersObsessive compulsive disorder" = "OCDs",
+               "bipolar_and_schizophreniaPsychotic and bipolar disorder" = "Psychotic and bipolar disorder",
+               "bipolar_and_schizophreniaOnly psychotic disorder" = "Only psychotic disorder",
+               "bipolar_and_schizophreniaOnly bipolar disorder" = "Only bipolar disorder",
+               "psychotic_disordersPsychotic disorder" = "Psychotic disorder",
+               "mhd.mania_hypomania_bipolar_or_manicdepressionMania, hypomania, bipolar or manic-depression" = "Bipolar disorder",
+               "mhd.posttraumatic_stress_disorder_ptsdPost-traumatic stress disorder (PTSD)" = "PTSD",
+               "autism_spectrum_disorderAutism spectrum disorder" = "ASD",
+               "mhd.attention_deficit_hyperactivity_disorderAttention deficit or attention deficit and hyperactivity disorder (ADD/ADHD)" = "ADHD",
+               "mhd.personality_disorderPersonality disorder" = "Personality disorder", 
+               "highest_educationNVQ" = "Highest education NVQ", 
+               "highest_educationA-levels" = "Highest education A-Levels",
+               "highest_educationUniversity" = "Highest education University"
+             ),
+             "Estimate" = format(
+               round(estimate,
+                     digits = 2),
+               nsmall = 2),
+             "95% CI low" = format(
+               round(conf.low,
+                     digits = 2),
+               nsmall = 2),
+             "95% CI up" = format(
+               round(conf.high,
+                     digits = 2),
+               nsmall = 2),
+             "SE" = format(
+               round(std.error,
+                     digits = 2),
+               nsmall = 2),
+             "z score" = format(
+               round(statistic,
+                     digits = 2),
+               nsmall = 2),
+             "p value" = case_when(
+               p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
+               p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
+               p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
+             )
+           ) %>%
+           select(
+             "Indepent variable",
+             "Estimate",
+             "95% CI low",
+             "95% CI up",
+             "SE",
+             #    "z score",
+             "p value"
+           )
+  )
+
+  return(get(paste0(outcome,"model0b_estimates")))
+}
+
+model0b.reg.stats <- function(outcome, data_set) {
+  # define the variable name of the dependent variable
+  dependent.variable <- outcome
+  # define the independent variables
+  independent.variables <- c("Disorder_hierarchical")
+  # create the formula
+  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
+  glm.formula
+
+  # run the glm
+  assign(paste0(outcome,".model0b"),
+         lm( formula = glm.formula,
+             data = get(data_set)
+         )
+  )
+
+  assign(paste0(outcome,"model0b_reg_stats"),
+         glance(get(paste0(outcome,".model0b"))) %>%
+           mutate(
+             "n" = format(
+               round(nobs,
+                     digits = 0),
+               nsmall = 0),
+             "R2" = format(
+               round(r.squared,
+                     digits = 2),
+               nsmall = 2),
+             "adjust. R2" = format(
+               round(adj.r.squared,
+                     digits = 2),
+               nsmall = 2),
+             "F" = format(
+               round(statistic,
+                     digits = 2),
+               nsmall = 2),
+             "p value" = case_when(
+               p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
+               p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
+               p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
+             )
+           ) %>%
+           select(
+             "n",
+             "R2",
+             "adjust. R2",
+             "F",
+             "p value",
+             "df"
+           )
+  )
+
+  return(get(paste0(outcome,"model0b_reg_stats")))
+}
+```
+
+```{r model1a education function}
+model1a.estimates <- function(outcome, data_set) {
+  # define the variable name of the dependent variable
+  dependent.variable <- outcome
+  # define the independent variables
+  independent.variables <- c("Disorder_hierarchical",
+                            "Gender_collapsed",
+                            "age_category_collapsed",
+                            "Ethnicity_collapsed",
+                            "time_diff_coping_lockdown_march_23", 
+                            "highest_education"
+                            )
+  # create the formula
+  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
+  glm.formula
+
+  # run the glm
+  assign(paste0(outcome,".model1a"),
+         lm( formula = glm.formula,
+             data = get(data_set)
+         )
+  )
+
+  assign(paste0(outcome,"model1a_estimates"),
+         tidy(get(paste0(outcome,".model1a")), conf.int = TRUE) %>%
+           mutate(
+             "Indepent variable" = recode_factor(
+               term,
+               "(Intercept)" = "Intercept",
+               "Disorder_hierarchicalAnxiety disorders" = "Anxiety disorders",
+               "Disorder_hierarchicalEating disorders" = "Eating disorders",
+               "Disorder_hierarchicalOCDs" = "OCDs",
+               "Disorder_hierarchicalPTSD" = "PTSD",
+               "Disorder_hierarchicalDepressive disorders" = "Depressive disorders",
+               "Disorder_hierarchicalBipolar disorders" = "Bipolar disorders",
+               "Gender_collapsedFemale" = "Female",
+               "Gender_collapsedNon-binary/Self-defined" = "Non-binary/Self-defined",
+               "age_category_collapsed19-25" = "19-25 years",
+               "age_category_collapsed26-35" = "26-35 years",
+               "age_category_collapsed36-45" = "36-45 years",
+               "age_category_collapsed46-55" = "46-55 years",
+               "age_category_collapsed56-65" = "56-65 years",
+               "age_category_collapsed66-70" = "66-70 years",
+               "age_category_collapsed71-75" = "71-75 years",
+               "age_category_collapsed76+" = "76+ years",
+               "Ethnicity_collapsedMixed or multiple ethnic origins" = "Mixed or multiple ethnic origins",
+               "Ethnicity_collapsedAsian or Asian British" = "Asian or Asian British",
+               "Ethnicity_collapsedAfrican or African British" = "African or African British",
+               "Ethnicity_collapsedOther" = "Other ethnicity",
+               "time_diff_coping_lockdown_march_23" = "Time difference: Lockdown to baseline",
+               "highest_educationNVQ" = "Highest education NVQ", 
+               "highest_educationA-levels" = "Highest education A-Levels",
+               "highest_educationUniversity" = "Highest education University"
+             ),
+             "Estimate" = format(
+               round(estimate,
+                     digits = 2),
+               nsmall = 2),
+             "95% CI low" = format(
+               round(conf.low,
+                     digits = 2),
+               nsmall = 2),
+             "95% CI up" = format(
+               round(conf.high,
+                     digits = 2),
+               nsmall = 2),
+             "SE" = format(
+               round(std.error,
+                     digits = 2),
+               nsmall = 2),
+             "z score" = format(
+               round(statistic,
+                     digits = 2),
+               nsmall = 2),
+             "p value" = case_when(
+               p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
+               p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
+               p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
+             )
+           ) %>%
+           select(
+             "Indepent variable",
+             "Estimate",
+             "95% CI low",
+             "95% CI up",
+             "SE",
+             #    "z score",
+             "p value"
+           )
+  )
+
+  return(get(paste0(outcome,"model1a_estimates")))
+}
+
+model1a.reg.stats <- function(outcome, data_set) {
+  # define the variable name of the dependent variable
+  dependent.variable <- outcome
+  # define the independent variables
+  independent.variables <- c("Disorder_hierarchical")
+  # create the formula
+  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
+  glm.formula
+
+  # run the glm
+  assign(paste0(outcome,".model1a"),
+         lm( formula = glm.formula,
+             data = get(data_set)
+         )
+  )
+
+  assign(paste0(outcome,"model1a_reg_stats"),
+         glance(get(paste0(outcome,".model1a"))) %>%
+           mutate(
+             "n" = format(
+               round(nobs,
+                     digits = 0),
+               nsmall = 0),
+             "R2" = format(
+               round(r.squared,
+                     digits = 2),
+               nsmall = 2),
+             "adjust. R2" = format(
+               round(adj.r.squared,
+                     digits = 2),
+               nsmall = 2),
+             "F" = format(
+               round(statistic,
+                     digits = 2),
+               nsmall = 2),
+             "p value" = case_when(
+               p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
+               p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
+               p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
+             )
+           ) %>%
+           select(
+             "n",
+             "R2",
+             "adjust. R2",
+             "F",
+             "p value",
+             "df"
+           )
+  )
+
+  return(get(paste0(outcome,"model1a_reg_stats")))
+}
+```
+
+```{r model1b education function}
+model1b.estimates <- function(outcome, data_set) {
+  # define the variable name of the dependent variable
+  dependent.variable <- outcome
+  # define the independent variables
+  independent.variables <- c("depression_and_anxiety",
+                             "eating_disorders",
+                             "obsessive_compulsive_disorders",
+                             "bipolar_and_schizophrenia",
+                             "mhd.posttraumatic_stress_disorder_ptsd",
+                             "autism_spectrum_disorder",
+                             "mhd.attention_deficit_hyperactivity_disorder",
+                             "mhd.personality_disorder",
+                             "Gender_collapsed",
+                             "age_category_collapsed",
+                             "Ethnicity_collapsed",
+                             "key_worker",
+                             "time_diff_coping_lockdown_march_23", 
+                             "highest_education"
+                                )
+  # create the formula
+  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
+  glm.formula
+
+  # run the glm
+  assign(paste0(outcome,".model1b"),
+         lm( formula = glm.formula,
+             data = get(data_set)
+         )
+  )
+
+  assign(paste0(outcome,"model1b_estimates"),
+         tidy(get(paste0(outcome,".model1b")), conf.int = TRUE) %>%
+           mutate(
+             "Indepent variable" = recode_factor(
+               term,
+               "(Intercept)" = "Intercept",
+               "anxiety_disordersAnxiety disorder" = "Anxiety disorders",
+               "depressive_disordersDepressive disorder" = "Depressive disorders",
+               "depression_and_anxietyDepressive and anxiety disorder" = "Depressive and anxiety disorder",
+               "depression_and_anxietyOnly depressive disorder" = "Only depressive disorder",
+               "depression_and_anxietyOnly anxiety disorder" = "Only anxiety disorder",
+               "eating_disordersEating disorder" = "Eating disorders",
+               "obsessive_compulsive_disordersObsessive compulsive disorder" = "OCDs",
+               "bipolar_and_schizophreniaPsychotic and bipolar disorder" = "Psychotic and bipolar disorder",
+               "bipolar_and_schizophreniaOnly psychotic disorder" = "Only psychotic disorder",
+               "bipolar_and_schizophreniaOnly bipolar disorder" = "Only bipolar disorder",
+               "psychotic_disordersPsychotic disorder" = "Psychotic disorder",
+               "mhd.mania_hypomania_bipolar_or_manicdepressionMania, hypomania, bipolar or manic-depression" = "Bipolar disorder",
+               "mhd.posttraumatic_stress_disorder_ptsdPost-traumatic stress disorder (PTSD)" = "PTSD",
+               "autism_spectrum_disorderAutism spectrum disorder" = "ASD",
+               "mhd.attention_deficit_hyperactivity_disorderAttention deficit or attention deficit and hyperactivity disorder (ADD/ADHD)" = "ADHD",
+               "mhd.personality_disorderPersonality disorder" = "Personality disorder",
+               "Gender_collapsedFemale" = "Female",
+               "Gender_collapsedNon-binary/Self-defined" = "Non-binary/Self-defined",
+               "age_category_collapsed19-25" = "19-25 years",
+               "age_category_collapsed26-35" = "26-35 years",
+               "age_category_collapsed36-45" = "36-45 years",
+               "age_category_collapsed46-55" = "46-55 years",
+               "age_category_collapsed56-65" = "56-65 years",
+               "age_category_collapsed66-70" = "66-70 years",
+               "age_category_collapsed71-75" = "71-75 years",
+               "age_category_collapsed76+" = "76+ years",
+               "Ethnicity_collapsedMixed or multiple ethnic origins" = "Mixed or multiple ethnic origins",
+               "Ethnicity_collapsedAsian or Asian British" = "Asian or Asian British",
+               "Ethnicity_collapsedAfrican or African British" = "African or African British",
+               "Ethnicity_collapsedOther" = "Other ethnicity",
+               "key_workerKey worker" = "Key worker",
+               "time_diff_coping_lockdown_march_23" = "Time difference: Lockdown to baseline", 
+               "highest_educationNVQ" = "Highest education NVQ", 
+               "highest_educationA-levels" = "Highest education A-Levels",
+               "highest_educationUniversity" = "Highest education University"
+             ),
+             "Estimate" = format(
+               round(estimate,
+                     digits = 2),
+               nsmall = 2),
+             "95% CI low" = format(
+               round(conf.low,
+                     digits = 2),
+               nsmall = 2),
+             "95% CI up" = format(
+               round(conf.high,
+                     digits = 2),
+               nsmall = 2),
+             "SE" = format(
+               round(std.error,
+                     digits = 2),
+               nsmall = 2),
+             "z score" = format(
+               round(statistic,
+                     digits = 2),
+               nsmall = 2),
+             "p value" = case_when(
+               p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
+               p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
+               p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
+             )
+           ) %>%
+           select(
+             "Indepent variable",
+             "Estimate",
+             "95% CI low",
+             "95% CI up",
+             "SE",
+             #    "z score",
+             "p value"
+           )
+  )
+
+  return(get(paste0(outcome,"model1b_estimates")))
+}
+
+model1b.reg.stats <- function(outcome, data_set) {
+  # define the variable name of the dependent variable
+  dependent.variable <- outcome
+  # define the independent variables
+  independent.variables <- c("Disorder_hierarchical")
+  # create the formula
+  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
+  glm.formula
+
+  # run the glm
+  assign(paste0(outcome,".model1b"),
+         lm( formula = glm.formula,
+             data = get(data_set)
+         )
+  )
+
+  assign(paste0(outcome,"model1b_reg_stats"),
+         glance(get(paste0(outcome,".model1b"))) %>%
+           mutate(
+             "n" = format(
+               round(nobs,
+                     digits = 0),
+               nsmall = 0),
+             "R2" = format(
+               round(r.squared,
+                     digits = 2),
+               nsmall = 2),
+             "adjust. R2" = format(
+               round(adj.r.squared,
+                     digits = 2),
+               nsmall = 2),
+             "F" = format(
+               round(statistic,
+                     digits = 2),
+               nsmall = 2),
+             "p value" = case_when(
+               p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
+               p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
+               p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
+             )
+           ) %>%
+           select(
+             "n",
+             "R2",
+             "adjust. R2",
+             "F",
+             "p value",
+             "df"
+           )
+  )
+
+  return(get(paste0(outcome,"model1b_reg_stats")))
+}
+```
+
+```{r model0a.explan education function}
+model0a.explan.estimates <- function(outcome, explan_var, data_set) {
+  # define the variable name of the dependent variable
+  dependent.variable <- outcome
+  # define the independent variables
+  independent.variables <- c(explan_var, "Disorder_hierarchical", 
+                             "highest_education")
+  # create the formula
+  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
+  glm.formula
+
+  # run the glm
+  assign(paste0(outcome,".",explan_var,".model0a.explan"),
+         lm( formula = glm.formula,
+             data = get(data_set)
+         )
+  )
+
+  assign(paste0(outcome,".",explan_var,"model0a.explan_estimates"),
+         tidy(get(paste0(outcome,".",explan_var,".model0a.explan")), conf.int = TRUE) %>%
+           mutate(
+             "Indepent variable" = recode_factor(
+               term,
+               "(Intercept)" = "Intercept",
+               "Disorder_hierarchicalAnxiety disorders" = "Anxiety disorders",
+               "Disorder_hierarchicalEating disorders" = "Eating disorders",
+               "Disorder_hierarchicalOCDs" = "OCDs",
+               "Disorder_hierarchicalPTSD" = "PTSD",
+               "Disorder_hierarchicalDepressive disorders" = "Depressive disorders",
+               "Disorder_hierarchicalBipolar disorders" = "Bipolar disorders", 
+               "highest_educationNVQ" = "Highest education NVQ", 
+               "highest_educationA-levels" = "Highest education A-Levels",
+               "highest_educationUniversity" = "Highest education University"
+             ),
+             "Estimate" = format(
+               round(estimate,
+                     digits = 2),
+               nsmall = 2),
+             "95% CI low" = format(
+               round(conf.low,
+                     digits = 2),
+               nsmall = 2),
+             "95% CI up" = format(
+               round(conf.high,
+                     digits = 2),
+               nsmall = 2),
+             "SE" = format(
+               round(std.error,
+                     digits = 2),
+               nsmall = 2),
+             "z score" = format(
+               round(statistic,
+                     digits = 2),
+               nsmall = 2),
+             "p value" = case_when(
+               p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
+               p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
+               p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
+             )
+           ) %>%
+           select(
+             "Indepent variable",
+             "Estimate",
+             "95% CI low",
+             "95% CI up",
+             "SE",
+             #    "z score",
+             "p value"
+           )
+  )
+
+  return(get(paste0(outcome,".",explan_var,"model0a.explan_estimates")))
+}
+
+model0a.explan.reg.stats <- function(outcome, explan_var, data_set) {
+  # define the variable name of the dependent variable
+  dependent.variable <- outcome
+  # define the independent variables
+  independent.variables <- c(explan_var, "Disorder_hierarchical")
+  # create the formula
+  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
+  glm.formula
+
+  # run the glm
+  assign(paste0(outcome,".",explan_var,".model0a.explan"),
+         lm( formula = glm.formula,
+             data = get(data_set)
+         )
+  )
+
+  assign(paste0(outcome,".",explan_var,"model0a.explan_reg_stats"),
+         glance(get(paste0(outcome,".",explan_var,".model0a.explan"))) %>%
+           mutate(
+             "n" = format(
+               round(nobs,
+                     digits = 0),
+               nsmall = 0),
+             "R2" = format(
+               round(r.squared,
+                     digits = 2),
+               nsmall = 2),
+             "adjust. R2" = format(
+               round(adj.r.squared,
+                     digits = 2),
+               nsmall = 2),
+             "F" = format(
+               round(statistic,
+                     digits = 2),
+               nsmall = 2),
+             "p value" = case_when(
+               p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
+               p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
+               p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
+             )
+           ) %>%
+           select(
+             "n",
+             "R2",
+             "adjust. R2",
+             "F",
+             "p value",
+             "df"
+           )
+  )
+
+  return(get(paste0(outcome,".",explan_var,"model0a.explan_reg_stats")))
+}
+```
+
+```{r model0b.explan education function}
+model0b.explan.estimates <- function(outcome, explan_var, data_set) {
+  # define the variable name of the dependent variable
+  dependent.variable <- outcome
+  # define the independent variables
+  independent.variables <- c(explan_var,
+                             "depression_and_anxiety",
+                             "eating_disorders",
+                             "obsessive_compulsive_disorders",
+                             "bipolar_and_schizophrenia",
+                             "mhd.posttraumatic_stress_disorder_ptsd",
+                             "autism_spectrum_disorder",
+                             "mhd.attention_deficit_hyperactivity_disorder",
+                             "mhd.personality_disorder", 
+                             "highest_education"
+  )
+  # create the formula
+  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
+  glm.formula
+
+  # run the glm
+  assign(paste0(outcome,".",explan_var,".model0b.explan"),
+         lm( formula = glm.formula,
+             data = get(data_set)
+         )
+  )
+
+  assign(paste0(outcome,".",explan_var,"model0b.explan_estimates"),
+         tidy(get(paste0(outcome,".",explan_var,".model0b.explan")), conf.int = TRUE) %>%
+           mutate(
+             "Indepent variable" = recode_factor(
+               term,
+               "(Intercept)" = "Intercept",
+               "anxiety_disordersAnxiety disorder" = "Anxiety disorders",
+               "depressive_disordersDepressive disorder" = "Depressive disorders",
+               "depression_and_anxietyDepressive and anxiety disorder" = "Depressive and anxiety disorder",
+               "depression_and_anxietyOnly depressive disorder" = "Only depressive disorder",
+               "depression_and_anxietyOnly anxiety disorder" = "Only anxiety disorder",
+               "eating_disordersEating disorder" = "Eating disorders",
+               "obsessive_compulsive_disordersObsessive compulsive disorder" = "OCDs",
+               "bipolar_and_schizophreniaPsychotic and bipolar disorder" = "Psychotic and bipolar disorder",
+               "bipolar_and_schizophreniaOnly psychotic disorder" = "Only psychotic disorder",
+               "bipolar_and_schizophreniaOnly bipolar disorder" = "Only bipolar disorder",
+               "psychotic_disordersPsychotic disorder" = "Psychotic disorder",
+               "mhd.mania_hypomania_bipolar_or_manicdepressionMania, hypomania, bipolar or manic-depression" = "Bipolar disorder",
+               "mhd.posttraumatic_stress_disorder_ptsdPost-traumatic stress disorder (PTSD)" = "PTSD",
+               "autism_spectrum_disorderAutism spectrum disorder" = "ASD",
+               "mhd.attention_deficit_hyperactivity_disorderAttention deficit or attention deficit and hyperactivity disorder (ADD/ADHD)" = "ADHD",
+               "mhd.personality_disorderPersonality disorder" = "Personality disorder", 
+               "highest_educationNVQ" = "Highest education NVQ", 
+               "highest_educationA-levels" = "Highest education A-Levels",
+               "highest_educationUniversity" = "Highest education University"
+             ),
+             "Estimate" = format(
+               round(estimate,
+                     digits = 2),
+               nsmall = 2),
+             "95% CI low" = format(
+               round(conf.low,
+                     digits = 2),
+               nsmall = 2),
+             "95% CI up" = format(
+               round(conf.high,
+                     digits = 2),
+               nsmall = 2),
+             "SE" = format(
+               round(std.error,
+                     digits = 2),
+               nsmall = 2),
+             "z score" = format(
+               round(statistic,
+                     digits = 2),
+               nsmall = 2),
+             "p value" = case_when(
+               p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
+               p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
+               p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
+             )
+           ) %>%
+           select(
+             "Indepent variable",
+             "Estimate",
+             "95% CI low",
+             "95% CI up",
+             "SE",
+             #    "z score",
+             "p value"
+           )
+  )
+
+  return(get(paste0(outcome,".",explan_var,"model0b.explan_estimates")))
+}
+
+model0b.explan.reg.stats <- function(outcome, explan_var, data_set) {
+  # define the variable name of the dependent variable
+  dependent.variable <- outcome
+  # define the independent variables
+  independent.variables <- c("Disorder_hierarchical")
+  # create the formula
+  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
+  glm.formula
+
+  # run the glm
+  assign(paste0(outcome,".",explan_var,".model0b.explan"),
+         lm( formula = glm.formula,
+             data = get(data_set)
+         )
+  )
+
+  assign(paste0(outcome,".",explan_var,"model0b.explan_reg_stats"),
+         glance(get(paste0(outcome,".",explan_var,".model0b.explan"))) %>%
+           mutate(
+             "n" = format(
+               round(nobs,
+                     digits = 0),
+               nsmall = 0),
+             "R2" = format(
+               round(r.squared,
+                     digits = 2),
+               nsmall = 2),
+             "adjust. R2" = format(
+               round(adj.r.squared,
+                     digits = 2),
+               nsmall = 2),
+             "F" = format(
+               round(statistic,
+                     digits = 2),
+               nsmall = 2),
+             "p value" = case_when(
+               p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
+               p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
+               p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
+             )
+           ) %>%
+           select(
+             "n",
+             "R2",
+             "adjust. R2",
+             "F",
+             "p value",
+             "df"
+           )
+  )
+
+  return(get(paste0(outcome,".",explan_var,"model0b.explan_reg_stats")))
+}
+```
+
+```{r model1a.explan education function}
+model1a.explan.estimates <- function(outcome, explan_var, data_set) {
+  # define the variable name of the dependent variable
+  dependent.variable <- outcome
+  # define the independent variables
+  independent.variables <- c(explan_var,
+                             "Disorder_hierarchical",
+                             "Gender_collapsed",
+                             "age_category_collapsed",
+                             "Ethnicity_collapsed",
+                             "key_worker",
+                             "time_diff_coping_lockdown_march_23", 
+                             "highest_education"
+  )
+  # create the formula
+  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
+  glm.formula
+
+  # run the glm
+  assign(paste0(outcome,".",explan_var,".model1a.explan"),
+         lm( formula = glm.formula,
+             data = get(data_set)
+         )
+  )
+
+  assign(paste0(outcome,".",explan_var,"model1a.explan_estimates"),
+         tidy(get(paste0(outcome,".",explan_var,".model1a.explan")), conf.int = TRUE) %>%
+           mutate(
+             "Indepent variable" = recode_factor(
+               term,
+               "(Intercept)" = "Intercept",
+               "Disorder_hierarchicalAnxiety disorders" = "Anxiety disorders",
+               "Disorder_hierarchicalEating disorders" = "Eating disorders",
+               "Disorder_hierarchicalOCDs" = "OCDs",
+               "Disorder_hierarchicalPTSD" = "PTSD",
+               "Disorder_hierarchicalDepressive disorders" = "Depressive disorders",
+               "Disorder_hierarchicalBipolar disorders" = "Bipolar disorders",
+               "Gender_collapsedFemale" = "Female",
+               "Gender_collapsedNon-binary/Self-defined" = "Non-binary/Self-defined",
+               "age_category_collapsed19-25" = "19-25 years",
+               "age_category_collapsed26-35" = "26-35 years",
+               "age_category_collapsed36-45" = "36-45 years",
+               "age_category_collapsed46-55" = "46-55 years",
+               "age_category_collapsed56-65" = "56-65 years",
+               "age_category_collapsed66-70" = "66-70 years",
+               "age_category_collapsed71-75" = "71-75 years",
+               "age_category_collapsed76+" = "76+ years",
+               "Ethnicity_collapsedMixed or multiple ethnic origins" = "Mixed or multiple ethnic origins",
+               "Ethnicity_collapsedAsian or Asian British" = "Asian or Asian British",
+               "Ethnicity_collapsedAfrican or African British" = "African or African British",
+               "Ethnicity_collapsedOther" = "Other ethnicity",
+               "key_workerKey worker" = "Key worker",
+               "time_diff_coping_lockdown_march_23" = "Time difference: Lockdown to baseline", 
+               "highest_educationNVQ" = "Highest education NVQ", 
+               "highest_educationA-levels" = "Highest education A-Levels",
+               "highest_educationUniversity" = "Highest education University"
+             ),
+             "Estimate" = format(
+               round(estimate,
+                     digits = 2),
+               nsmall = 2),
+             "95% CI low" = format(
+               round(conf.low,
+                     digits = 2),
+               nsmall = 2),
+             "95% CI up" = format(
+               round(conf.high,
+                     digits = 2),
+               nsmall = 2),
+             "SE" = format(
+               round(std.error,
+                     digits = 2),
+               nsmall = 2),
+             "z score" = format(
+               round(statistic,
+                     digits = 2),
+               nsmall = 2),
+             "p value" = case_when(
+               p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
+               p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
+               p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
+             )
+           ) %>%
+           select(
+             "Indepent variable",
+             "Estimate",
+             "95% CI low",
+             "95% CI up",
+             "SE",
+             #    "z score",
+             "p value"
+           )
+  )
+
+  return(get(paste0(outcome,".",explan_var,"model1a.explan_estimates")))
+}
+
+model1a.explan.reg.stats <- function(outcome, explan_var, data_set) {
+  # define the variable name of the dependent variable
+  dependent.variable <- outcome
+  # define the independent variables
+  independent.variables <- c("Disorder_hierarchical")
+  # create the formula
+  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
+  glm.formula
+
+  # run the glm
+  assign(paste0(outcome,".",explan_var,".model1a.explan"),
+         lm( formula = glm.formula,
+             data = get(data_set)
+         )
+  )
+
+  assign(paste0(outcome,".",explan_var,"model1a.explan_reg_stats"),
+         glance(get(paste0(outcome,".",explan_var,".model1a.explan"))) %>%
+           mutate(
+             "n" = format(
+               round(nobs,
+                     digits = 0),
+               nsmall = 0),
+             "R2" = format(
+               round(r.squared,
+                     digits = 2),
+               nsmall = 2),
+             "adjust. R2" = format(
+               round(adj.r.squared,
+                     digits = 2),
+               nsmall = 2),
+             "F" = format(
+               round(statistic,
+                     digits = 2),
+               nsmall = 2),
+             "p value" = case_when(
+               p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
+               p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
+               p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
+             )
+           ) %>%
+           select(
+             "n",
+             "R2",
+             "adjust. R2",
+             "F",
+             "p value",
+             "df"
+           )
+  )
+
+  return(get(paste0(outcome,".",explan_var,"model1a.explan_reg_stats")))
+}
+```
+
+```{r model1b.explan education function}
+model1b.explan.estimates <- function(outcome, explan_var, data_set) {
+  # define the variable name of the dependent variable
+  dependent.variable <- outcome
+  # define the independent variables
+  independent.variables <- c(explan_var,
+                             "depression_and_anxiety",
+                             "eating_disorders",
+                             "obsessive_compulsive_disorders",
+                             "bipolar_and_schizophrenia",
+                             "mhd.posttraumatic_stress_disorder_ptsd",
+                             "autism_spectrum_disorder",
+                             "mhd.attention_deficit_hyperactivity_disorder",
+                             "mhd.personality_disorder",
+                             "Gender_collapsed",
+                             "age_category_collapsed",
+                             "Ethnicity_collapsed",
+                             "key_worker",
+                             "time_diff_coping_lockdown_march_23", 
+                             "highest_education"
+  )
+  # create the formula
+  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
+  glm.formula
+
+  # run the glm
+  assign(paste0(outcome,".",explan_var,".model1b.explan"),
+         lm( formula = glm.formula,
+             data = get(data_set)
+         )
+  )
+
+  assign(paste0(outcome,".",explan_var,"model1b.explan_estimates"),
+         tidy(get(paste0(outcome,".",explan_var,".model1b.explan")), conf.int = TRUE) %>%
+           mutate(
+             "Indepent variable" = recode_factor(
+               term,
+               "(Intercept)" = "Intercept",
+               "anxiety_disordersAnxiety disorder" = "Anxiety disorders",
+               "depressive_disordersDepressive disorder" = "Depressive disorders",
+               "depression_and_anxietyDepressive and anxiety disorder" = "Depressive and anxiety disorder",
+               "depression_and_anxietyOnly depressive disorder" = "Only depressive disorder",
+               "depression_and_anxietyOnly anxiety disorder" = "Only anxiety disorder",
+               "eating_disordersEating disorder" = "Eating disorders",
+               "obsessive_compulsive_disordersObsessive compulsive disorder" = "OCDs",
+               "bipolar_and_schizophreniaPsychotic and bipolar disorder" = "Psychotic and bipolar disorder",
+               "bipolar_and_schizophreniaOnly psychotic disorder" = "Only psychotic disorder",
+               "bipolar_and_schizophreniaOnly bipolar disorder" = "Only bipolar disorder",
+               "psychotic_disordersPsychotic disorder" = "Psychotic disorder",
+               "mhd.mania_hypomania_bipolar_or_manicdepressionMania, hypomania, bipolar or manic-depression" = "Bipolar disorder",
+               "mhd.posttraumatic_stress_disorder_ptsdPost-traumatic stress disorder (PTSD)" = "PTSD",
+               "autism_spectrum_disorderAutism spectrum disorder" = "ASD",
+               "mhd.attention_deficit_hyperactivity_disorderAttention deficit or attention deficit and hyperactivity disorder (ADD/ADHD)" = "ADHD",
+               "mhd.personality_disorderPersonality disorder" = "Personality disorder",
+               "Gender_collapsedFemale" = "Female",
+               "Gender_collapsedNon-binary/Self-defined" = "Non-binary/Self-defined",
+               "age_category_collapsed19-25" = "19-25 years",
+               "age_category_collapsed26-35" = "26-35 years",
+               "age_category_collapsed36-45" = "36-45 years",
+               "age_category_collapsed46-55" = "46-55 years",
+               "age_category_collapsed56-65" = "56-65 years",
+               "age_category_collapsed66-70" = "66-70 years",
+               "age_category_collapsed71-75" = "71-75 years",
+               "age_category_collapsed76+" = "76+ years",
+               "Ethnicity_collapsedMixed or multiple ethnic origins" = "Mixed or multiple ethnic origins",
+               "Ethnicity_collapsedAsian or Asian British" = "Asian or Asian British",
+               "Ethnicity_collapsedAfrican or African British" = "African or African British",
+               "Ethnicity_collapsedOther" = "Other ethnicity",
+               "key_workerKey worker" = "Key worker",
+               "time_diff_coping_lockdown_march_23" = "Time difference: Lockdown to baseline", 
+               "highest_educationNVQ" = "Highest education NVQ", 
+               "highest_educationA-levels" = "Highest education A-Levels",
+               "highest_educationUniversity" = "Highest education University"
+             ),
+             "Estimate" = format(
+               round(estimate,
+                     digits = 2),
+               nsmall = 2),
+             "95% CI low" = format(
+               round(conf.low,
+                     digits = 2),
+               nsmall = 2),
+             "95% CI up" = format(
+               round(conf.high,
+                     digits = 2),
+               nsmall = 2),
+             "SE" = format(
+               round(std.error,
+                     digits = 2),
+               nsmall = 2),
+             "z score" = format(
+               round(statistic,
+                     digits = 2),
+               nsmall = 2),
+             "p value" = case_when(
+               p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
+               p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
+               p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
+             )
+           ) %>%
+           select(
+             "Indepent variable",
+             "Estimate",
+             "95% CI low",
+             "95% CI up",
+             "SE",
+             #    "z score",
+             "p value"
+           )
+  )
+
+  return(get(paste0(outcome,".",explan_var,"model1b.explan_estimates")))
+}
+
+model1b.explan.reg.stats <- function(outcome, explan_var, data_set) {
+  # define the variable name of the dependent variable
+  dependent.variable <- outcome
+  # define the independent variables
+  independent.variables <- c("Disorder_hierarchical")
+  # create the formula
+  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
+  glm.formula
+
+  # run the glm
+  assign(paste0(outcome,".",explan_var,".model1b.explan"),
+         lm( formula = glm.formula,
+             data = get(data_set)
+         )
+  )
+
+  assign(paste0(outcome,".",explan_var,"model1b.explan_reg_stats"),
+         glance(get(paste0(outcome,".",explan_var,".model1b.explan"))) %>%
+           mutate(
+             "n" = format(
+               round(nobs,
+                     digits = 0),
+               nsmall = 0),
+             "R2" = format(
+               round(r.squared,
+                     digits = 2),
+               nsmall = 2),
+             "adjust. R2" = format(
+               round(adj.r.squared,
+                     digits = 2),
+               nsmall = 2),
+             "F" = format(
+               round(statistic,
+                     digits = 2),
+               nsmall = 2),
+             "p value" = case_when(
+               p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
+               p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
+               p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
+             )
+           ) %>%
+           select(
+             "n",
+             "R2",
+             "adjust. R2",
+             "F",
+             "p value",
+             "df"
+           )
+  )
+
+  return(get(paste0(outcome,".",explan_var,"model1b.explan_reg_stats")))
+}
+```
+
+# GAD prepan
+## Regression: Change scores
+### Model 0a: Disorder_hierarchical, Unadjusted
+```{r gad model0a diff_score w/education prepan}
+# Regression coefficients
+gad_prepan_model0a_estimates <- model0a.estimates(outcome = "gad.diff_score_base_prepan",
+                  data_set = "dat.prepan")
+kable(gad_prepan_model0a_estimates)
+gad_prepan_model0a_estimates
+
+# Regression diagnostic statistics
+gad_prepan_model0a_reg_stats <- model0a.reg.stats(outcome = "gad.diff_score_base_prepan",
+                  data_set = "dat.prepan")
+kable(gad_prepan_model0a_reg_stats)
+gad_prepan_model0a_reg_stats
+```
+
+### Model 0b: Overlapping disorders, Unadjusted
+```{r gad model0b diff_score w/education prepan}
+# Regression coefficients
+gad_prepan_model0b_estimates <- model0b.estimates(outcome = "gad.diff_score_base_prepan",
+                  data_set = "dat.prepan")
+kable(gad_prepan_model0b_estimates)
+gad_prepan_model0b_estimates
+
+# Regression diagnostic statistics
+gad_prepan_model0b_reg_stats <- model0b.reg.stats(outcome = "gad.diff_score_base_prepan",
+                  data_set = "dat.prepan")
+kable(gad_prepan_model0b_reg_stats)
+gad_prepan_model0b_reg_stats
+```
+
+### Model 1a: Disorder hierarchical, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r gad model1a diff_score w/education prepan}
+# Regression coefficients
+gad_prepan_model1a_estimates <- model1a.estimates(outcome = "gad.diff_score_base_prepan",
+                  data_set = "dat.prepan")
+kable(gad_prepan_model1a_estimates)
+gad_prepan_model1a_estimates
+
+# Regression diagnostic statistics
+gad_prepan_model1a_reg_stats <- model1a.reg.stats(outcome = "gad.diff_score_base_prepan",
+                  data_set = "dat.prepan")
+kable(gad_prepan_model1a_reg_stats)
+gad_prepan_model1a_reg_stats
+```
+
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r gad model1b diff_score w/education prepan}
+# Regression coefficients
+gad_prepan_model1b_estimates <- model1b.estimates(outcome = "gad.diff_score_base_prepan",
+                  data_set = "dat.prepan")
+kable(gad_prepan_model1b_estimates)
+gad_prepan_model1b_estimates
+
+# Regression diagnostic statistics
+gad_prepan_model1b_reg_stats <- model1b.reg.stats(outcome = "gad.diff_score_base_prepan",
+                  data_set = "dat.prepan")
+kable(gad_prepan_model1b_reg_stats)
+gad_prepan_model1b_reg_stats
+```
+
+## Regression: Absolute scores
+### Model 0a: Disorder_hierarchical, Unadjusted
+```{r gad model0a sum_score w/education prepan}
+# Regression coefficients
+gad_prepan_model0a_explan_estimates <- model0a.explan.estimates(outcome = "gad.sum_score_base",
+                         explan_var = "gad.sum_score_prepan",
+                         data_set = "dat.prepan")
+kable(gad_prepan_model0a_explan_estimates)
+gad_prepan_model0a_explan_estimates
+
+# Regression diagnostic statistics
+gad_prepan_model0a_explan_reg_stats <- model0a.explan.reg.stats(outcome = "gad.sum_score_base",
+                         explan_var = "gad.sum_score_prepan",
+                         data_set = "dat.prepan")
+kable(gad_prepan_model0a_explan_reg_stats)
+gad_prepan_model0a_explan_reg_stats
+```
+
+### Model 0b: Overlapping disorders, Unadjusted
+```{r gad model0b sum_score w/education prepan}
+# Regression coefficients
+gad_prepan_model0b_explan_estimates <- model0b.explan.estimates(outcome = "gad.sum_score_base",
+                         explan_var = "gad.sum_score_prepan",
+                         data_set = "dat.prepan")
+kable(gad_prepan_model0b_explan_estimates)
+gad_prepan_model0b_explan_estimates
+
+# Regression diagnostic statistics
+gad_prepan_model0b_explan_reg_stats <- model0b.explan.reg.stats(outcome = "gad.sum_score_base",
+                         explan_var = "gad.sum_score_prepan",
+                         data_set = "dat.prepan")
+kable(gad_prepan_model0b_explan_reg_stats)
+gad_prepan_model0b_explan_reg_stats
+```
+
+### Model 1a: Disorder hierarchical, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r gad model1a sum_score w/education prepan}
+# Regression coefficients
+gad_prepan_model1a_explan_estimates <- model1a.explan.estimates(outcome = "gad.sum_score_base",
+                         explan_var = "gad.sum_score_prepan",
+                         data_set = "dat.prepan")
+kable(gad_prepan_model1a_explan_estimates)
+gad_prepan_model1a_explan_estimates
+
+# Regression diagnostic statistics
+gad_prepan_model1a_explan_reg_stats <- model1a.explan.reg.stats(outcome = "gad.sum_score_base",
+                         explan_var = "gad.sum_score_prepan",
+                         data_set = "dat.prepan")
+kable(gad_prepan_model1a_explan_reg_stats)
+gad_prepan_model1a_explan_reg_stats
+```
+
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r gad model1b sum_score w/education prepan}
+# Regression coefficients
+gad_prepan_model1b_explan_estimates <- model1b.explan.estimates(outcome = "gad.sum_score_base",
+                         explan_var = "gad.sum_score_prepan",
+                         data_set = "dat.prepan")
+kable(gad_prepan_model1b_explan_estimates)
+gad_prepan_model1b_explan_estimates
+
+# Regression diagnostic statistics
+gad_prepan_model1b_explan_reg_stats <- model1b.explan.reg.stats(outcome = "gad.sum_score_base",
+                         explan_var = "gad.sum_score_prepan",
+                         data_set = "dat.prepan")
+kable(gad_prepan_model1b_explan_reg_stats)
+gad_prepan_model1b_explan_reg_stats
+```
+
+# GAD retro
+## Regression: Change scores
+### Model 0a: Disorder_hierarchical, Unadjusted
+```{r gad model0a diff_score w/education retro}
+# Regression coefficients
+gad_retro_model0a_estimates <- model0a.estimates(outcome = "gad.diff_score_base_retro",
+                                                 data_set = "dat.retro")
+kable(gad_retro_model0a_estimates)
+gad_retro_model0a_estimates
+
+# Regression diagnostic statistics
+gad_retro_model0a_reg_stats <- model0a.reg.stats(outcome = "gad.diff_score_base_retro",
+                                                 data_set = "dat.retro")
+kable(gad_retro_model0a_reg_stats)
+gad_retro_model0a_reg_stats
+```
+
+### Model 0b: Overlapping disorders, Unadjusted
+```{r gad model0b diff_score w/education retro}
+# Regression coefficients
+gad_retro_model0b_estimates <- model0b.estimates(outcome = "gad.diff_score_base_retro",
+                                                 data_set = "dat.retro")
+kable(gad_retro_model0b_estimates)
+gad_retro_model0b_estimates
+
+# Regression diagnostic statistics
+gad_retro_model0b_reg_stats <- model0b.reg.stats(outcome = "gad.diff_score_base_retro",
+                                                 data_set = "dat.retro")
+kable(gad_retro_model0b_reg_stats)
+gad_retro_model0b_reg_stats
+```
+
+### Model 1a: Disorder hierarchical, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r gad model1a diff_score w/education retro}
+# Regression coefficients
+gad_retro_model1a_estimates <- model1a.estimates(outcome = "gad.diff_score_base_retro",
+                                                 data_set = "dat.retro")
+kable(gad_retro_model1a_estimates)
+gad_retro_model1a_estimates
+
+# Regression diagnostic statistics
+gad_retro_model1a_reg_stats <- model1a.reg.stats(outcome = "gad.diff_score_base_retro",
+                                                 data_set = "dat.retro")
+kable(gad_retro_model1a_reg_stats)
+gad_retro_model1a_reg_stats
+```
+
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r gad model1b diff_score w/education retro}
+# Regression coefficients
+gad_retro_model1b_estimates <- model1b.estimates(outcome = "gad.diff_score_base_retro",
+                                                 data_set = "dat.retro")
+kable(gad_retro_model1b_estimates)
+gad_retro_model1b_estimates
+
+# Regression diagnostic statistics
+gad_retro_model1b_reg_stats <- model1b.reg.stats(outcome = "gad.diff_score_base_retro",
+                                                 data_set = "dat.retro")
+kable(gad_retro_model1b_reg_stats)
+gad_retro_model1b_reg_stats
+```
+
+## Regression: Absolute scores
+### Model 0a: Disorder_hierarchical, Unadjusted
+```{r gad model0a sum_score w/education retro}
+# Regression coefficients
+gad_retro_model0a_explan_estimates <- model0a.explan.estimates(outcome = "gad.sum_score_base",
+                                                               explan_var = "gad.sum_score_retro",
+                                                               data_set = "dat.retro")
+kable(gad_retro_model0a_explan_estimates)
+gad_retro_model0a_explan_estimates
+
+# Regression diagnostic statistics
+gad_retro_model0a_explan_reg_stats <- model0a.explan.reg.stats(outcome = "gad.sum_score_base",
+                                                               explan_var = "gad.sum_score_retro",
+                                                               data_set = "dat.retro")
+kable(gad_retro_model0a_explan_reg_stats)
+gad_retro_model0a_explan_reg_stats
+```
+
+### Model 0b: Overlapping disorders, Unadjusted
+```{r gad model0b sum_score w/education retro}
+# Regression coefficients
+gad_retro_model0b_explan_estimates <- model0b.explan.estimates(outcome = "gad.sum_score_base",
+                                                               explan_var = "gad.sum_score_retro",
+                                                               data_set = "dat.retro")
+kable(gad_retro_model0b_explan_estimates)
+gad_retro_model0b_explan_estimates
+
+# Regression diagnostic statistics
+gad_retro_model0b_explan_reg_stats <- model0b.explan.reg.stats(outcome = "gad.sum_score_base",
+                                                               explan_var = "gad.sum_score_retro",
+                                                               data_set = "dat.retro")
+kable(gad_retro_model0b_explan_reg_stats)
+gad_retro_model0b_explan_reg_stats
+```
+
+### Model 1a: Disorder hierarchical, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r gad model1a sum_score w/education retro}
+# Regression coefficients
+gad_retro_model1a_explan_estimates <- model1a.explan.estimates(outcome = "gad.sum_score_base",
+                                                               explan_var = "gad.sum_score_retro",
+                                                               data_set = "dat.retro")
+kable(gad_retro_model1a_explan_estimates)
+gad_retro_model1a_explan_estimates
+
+# Regression diagnostic statistics
+gad_retro_model1a_explan_reg_stats <- model1a.explan.reg.stats(outcome = "gad.sum_score_base",
+                                                               explan_var = "gad.sum_score_retro",
+                                                               data_set = "dat.retro")
+kable(gad_retro_model1a_explan_reg_stats)
+gad_retro_model1a_explan_reg_stats
+```
+
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r gad model1b sum_score w/education retro}
+# Regression coefficients
+gad_retro_model1b_explan_estimates <- model1b.explan.estimates(outcome = "gad.sum_score_base",
+                                                               explan_var = "gad.sum_score_retro",
+                                                               data_set = "dat.retro")
+kable(gad_retro_model1b_explan_estimates)
+gad_retro_model1b_explan_estimates
+
+# Regression diagnostic statistics
+gad_retro_model1b_explan_reg_stats <- model1b.explan.reg.stats(outcome = "gad.sum_score_base",
+                                                               explan_var = "gad.sum_score_retro",
+                                                               data_set = "dat.retro")
+kable(gad_retro_model1b_explan_reg_stats)
+gad_retro_model1b_explan_reg_stats
+```
+# PHQ prepan
+## Regression: Change scores
+### Model 0a: Disorder_hierarchical, Unadjusted
+```{r phq model0a diff_score w/education prepan}
+# Regression coefficients
+phq_prepan_model0a_estimates <- model0a.estimates(outcome = "phq.diff_score_base_prepan",
+                  data_set = "dat.prepan")
+kable(phq_prepan_model0a_estimates)
+phq_prepan_model0a_estimates
+
+# Regression diagnostic statistics
+phq_prepan_model0a_reg_stats <- model0a.reg.stats(outcome = "phq.diff_score_base_prepan",
+                  data_set = "dat.prepan")
+kable(phq_prepan_model0a_reg_stats)
+phq_prepan_model0a_reg_stats
+```
+
+### Model 0b: Overlapping disorders, Unadjusted
+```{r phq model0b diff_score w/education prepan}
+# Regression coefficients
+phq_prepan_model0b_estimates <- model0b.estimates(outcome = "phq.diff_score_base_prepan",
+                  data_set = "dat.prepan")
+kable(phq_prepan_model0b_estimates)
+phq_prepan_model0b_estimates
+
+# Regression diagnostic statistics
+phq_prepan_model0b_reg_stats <- model0b.reg.stats(outcome = "phq.diff_score_base_prepan",
+                  data_set = "dat.prepan")
+kable(phq_prepan_model0b_reg_stats)
+phq_prepan_model0b_reg_stats
+```
+
+### Model 1a: Disorder hierarchical, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r phq model1a diff_score w/education prepan}
+# Regression coefficients
+phq_prepan_model1a_estimates <- model1a.estimates(outcome = "phq.diff_score_base_prepan",
+                  data_set = "dat.prepan")
+kable(phq_prepan_model1a_estimates)
+phq_prepan_model1a_estimates
+
+# Regression diagnostic statistics
+phq_prepan_model1a_reg_stats <- model1a.reg.stats(outcome = "phq.diff_score_base_prepan",
+                  data_set = "dat.prepan")
+kable(phq_prepan_model1a_reg_stats)
+phq_prepan_model1a_reg_stats
+```
+
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r phq model1b diff_score w/education prepan}
+# Regression coefficients
+phq_prepan_model1b_estimates <- model1b.estimates(outcome = "phq.diff_score_base_prepan",
+                  data_set = "dat.prepan")
+kable(phq_prepan_model1b_estimates)
+phq_prepan_model1b_estimates
+
+# Regression diagnostic statistics
+phq_prepan_model1b_reg_stats <- model1b.reg.stats(outcome = "phq.diff_score_base_prepan",
+                  data_set = "dat.prepan")
+kable(phq_prepan_model1b_reg_stats)
+phq_prepan_model1b_reg_stats
+```
+
+## Regression: Absolute scores
+### Model 0a: Disorder_hierarchical, Unadjusted
+```{r phq model0a sum_score w/education prepan}
+# Regression coefficients
+phq_prepan_model0a_explan_estimates <- model0a.explan.estimates(outcome = "phq.sum_score_base",
+                         explan_var = "phq.sum_score_prepan",
+                         data_set = "dat.prepan")
+kable(phq_prepan_model0a_explan_estimates)
+phq_prepan_model0a_explan_estimates
+
+# Regression diagnostic statistics
+phq_prepan_model0a_explan_reg_stats <- model0a.explan.reg.stats(outcome = "phq.sum_score_base",
+                         explan_var = "phq.sum_score_prepan",
+                         data_set = "dat.prepan")
+kable(phq_prepan_model0a_explan_reg_stats)
+phq_prepan_model0a_explan_reg_stats
+```
+
+### Model 0b: Overlapping disorders, Unadjusted
+```{r phq model0b sum_score w/education prepan}
+# Regression coefficients
+phq_prepan_model0b_explan_estimates <- model0b.explan.estimates(outcome = "phq.sum_score_base",
+                         explan_var = "phq.sum_score_prepan",
+                         data_set = "dat.prepan")
+kable(phq_prepan_model0b_explan_estimates)
+phq_prepan_model0b_explan_estimates
+
+# Regression diagnostic statistics
+phq_prepan_model0b_explan_reg_stats <- model0b.explan.reg.stats(outcome = "phq.sum_score_base",
+                         explan_var = "phq.sum_score_prepan",
+                         data_set = "dat.prepan")
+kable(phq_prepan_model0b_explan_reg_stats)
+phq_prepan_model0b_explan_reg_stats
+```
+
+### Model 1a: Disorder hierarchical, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r phq model1a sum_score w/education prepan}
+# Regression coefficients
+phq_prepan_model1a_explan_estimates <- model1a.explan.estimates(outcome = "phq.sum_score_base",
+                         explan_var = "phq.sum_score_prepan",
+                         data_set = "dat.prepan")
+kable(phq_prepan_model1a_explan_estimates)
+phq_prepan_model1a_explan_estimates
+
+# Regression diagnostic statistics
+phq_prepan_model1a_explan_reg_stats <- model1a.explan.reg.stats(outcome = "phq.sum_score_base",
+                         explan_var = "phq.sum_score_prepan",
+                         data_set = "dat.prepan")
+kable(phq_prepan_model1a_explan_reg_stats)
+phq_prepan_model1a_explan_reg_stats
+```
+
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r phq model1b sum_score w/education prepan}
+# Regression coefficients
+phq_prepan_model1b_explan_estimates <- model1b.explan.estimates(outcome = "phq.sum_score_base",
+                         explan_var = "phq.sum_score_prepan",
+                         data_set = "dat.prepan")
+kable(phq_prepan_model1b_explan_estimates)
+phq_prepan_model1b_explan_estimates
+
+# Regression diagnostic statistics
+phq_prepan_model1b_explan_reg_stats <- model1b.explan.reg.stats(outcome = "phq.sum_score_base",
+                         explan_var = "phq.sum_score_prepan",
+                         data_set = "dat.prepan")
+kable(phq_prepan_model1b_explan_reg_stats)
+phq_prepan_model1b_explan_reg_stats
+```
+
+# PHQ retro
+## Regression: Change scores
+### Model 0a: Disorder_hierarchical, Unadjusted
+```{r phq model0a diff_score w/education retro}
+# Regression coefficients
+phq_retro_model0a_estimates <- model0a.estimates(outcome = "phq.diff_score_base_retro",
+                                                 data_set = "dat.retro")
+kable(phq_retro_model0a_estimates)
+phq_retro_model0a_estimates
+
+# Regression diagnostic statistics
+phq_retro_model0a_reg_stats <- model0a.reg.stats(outcome = "phq.diff_score_base_retro",
+                                                 data_set = "dat.retro")
+kable(phq_retro_model0a_reg_stats)
+phq_retro_model0a_reg_stats
+```
+
+### Model 0b: Overlapping disorders, Unadjusted
+```{r phq model0b diff_score w/education retro}
+# Regression coefficients
+phq_retro_model0b_estimates <- model0b.estimates(outcome = "phq.diff_score_base_retro",
+                                                 data_set = "dat.retro")
+kable(phq_retro_model0b_estimates)
+phq_retro_model0b_estimates
+
+# Regression diagnostic statistics
+phq_retro_model0b_reg_stats <- model0b.reg.stats(outcome = "phq.diff_score_base_retro",
+                                                 data_set = "dat.retro")
+kable(phq_retro_model0b_reg_stats)
+phq_retro_model0b_reg_stats
+```
+
+### Model 1a: Disorder hierarchical, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r phq model1a diff_score w/education retro}
+# Regression coefficients
+phq_retro_model1a_estimates <- model1a.estimates(outcome = "phq.diff_score_base_retro",
+                                                 data_set = "dat.retro")
+kable(phq_retro_model1a_estimates)
+phq_retro_model1a_estimates
+
+# Regression diagnostic statistics
+phq_retro_model1a_reg_stats <- model1a.reg.stats(outcome = "phq.diff_score_base_retro",
+                                                 data_set = "dat.retro")
+kable(phq_retro_model1a_reg_stats)
+phq_retro_model1a_reg_stats
+```
+
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r phq model1b diff_scor w/educatione retro}
+# Regression coefficients
+phq_retro_model1b_estimates <- model1b.estimates(outcome = "phq.diff_score_base_retro",
+                                                 data_set = "dat.retro")
+kable(phq_retro_model1b_estimates)
+phq_retro_model1b_estimates
+
+# Regression diagnostic statistics
+phq_retro_model1b_reg_stats <- model1b.reg.stats(outcome = "phq.diff_score_base_retro",
+                                                 data_set = "dat.retro")
+kable(phq_retro_model1b_reg_stats)
+phq_retro_model1b_reg_stats
+```
+
+## Regression: Absolute scores
+### Model 0a: Disorder_hierarchical, Unadjusted
+```{r phq model0a sum_score w/education retro}
+# Regression coefficients
+phq_retro_model0a_explan_estimates <- model0a.explan.estimates(outcome = "phq.sum_score_base",
+                                                               explan_var = "phq.sum_score_retro",
+                                                               data_set = "dat.retro")
+kable(phq_retro_model0a_explan_estimates)
+phq_retro_model0a_explan_estimates
+
+# Regression diagnostic statistics
+phq_retro_model0a_explan_reg_stats <- model0a.explan.reg.stats(outcome = "phq.sum_score_base",
+                                                               explan_var = "phq.sum_score_retro",
+                                                               data_set = "dat.retro")
+kable(phq_retro_model0a_explan_reg_stats)
+phq_retro_model0a_explan_reg_stats
+```
+
+### Model 0b: Overlapping disorders, Unadjusted
+```{r phq model0b sum_score w/education retro}
+# Regression coefficients
+phq_retro_model0b_explan_estimates <- model0b.explan.estimates(outcome = "phq.sum_score_base",
+                                                               explan_var = "phq.sum_score_retro",
+                                                               data_set = "dat.retro")
+kable(phq_retro_model0b_explan_estimates)
+phq_retro_model0b_explan_estimates
+
+# Regression diagnostic statistics
+phq_retro_model0b_explan_reg_stats <- model0b.explan.reg.stats(outcome = "phq.sum_score_base",
+                                                               explan_var = "phq.sum_score_retro",
+                                                               data_set = "dat.retro")
+kable(phq_retro_model0b_explan_reg_stats)
+phq_retro_model0b_explan_reg_stats
+```
+
+### Model 1a: Disorder hierarchical, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r phq model1a sum_score w/education retro}
+# Regression coefficients
+phq_retro_model1a_explan_estimates <- model1a.explan.estimates(outcome = "phq.sum_score_base",
+                                                               explan_var = "phq.sum_score_retro",
+                                                               data_set = "dat.retro")
+kable(phq_retro_model1a_explan_estimates)
+phq_retro_model1a_explan_estimates
+
+# Regression diagnostic statistics
+phq_retro_model1a_explan_reg_stats <- model1a.explan.reg.stats(outcome = "phq.sum_score_base",
+                                                               explan_var = "phq.sum_score_retro",
+                                                               data_set = "dat.retro")
+kable(phq_retro_model1a_explan_reg_stats)
+phq_retro_model1a_explan_reg_stats
+```
+
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r phq model1b sum_score w/education retro}
+# Regression coefficients
+phq_retro_model1b_explan_estimates <- model1b.explan.estimates(outcome = "phq.sum_score_base",
+                                                               explan_var = "phq.sum_score_retro",
+                                                               data_set = "dat.retro")
+kable(phq_retro_model1b_explan_estimates)
+phq_retro_model1b_explan_estimates
+
+# Regression diagnostic statistics
+phq_retro_model1b_explan_reg_stats <- model1b.explan.reg.stats(outcome = "phq.sum_score_base",
+                                                               explan_var = "phq.sum_score_retro",
+                                                               data_set = "dat.retro")
+kable(phq_retro_model1b_explan_reg_stats)
+phq_retro_model1b_explan_reg_stats
+```
+
+# OCIR prepan
+## Regression: Change scores
+### Model 0a: Disorder_hierarchical, Unadjusted
+```{r ocir model0a diff_score w/education prepan}
+# Regression coefficients
+ocir_prepan_model0a_estimates <- model0a.estimates(outcome = "ocir.diff_score_base_prepan",
+                  data_set = "dat.prepan")
+kable(ocir_prepan_model0a_estimates)
+ocir_prepan_model0a_estimates
+
+# Regression diagnostic statistics
+ocir_prepan_model0a_reg_stats <- model0a.reg.stats(outcome = "ocir.diff_score_base_prepan",
+                  data_set = "dat.prepan")
+kable(ocir_prepan_model0a_reg_stats)
+ocir_prepan_model0a_reg_stats
+```
+
+### Model 0b: Overlapping disorders, Unadjusted
+```{r ocir model0b diff_score w/education prepan}
+# Regression coefficients
+ocir_prepan_model0b_estimates <- model0b.estimates(outcome = "ocir.diff_score_base_prepan",
+                  data_set = "dat.prepan")
+kable(ocir_prepan_model0b_estimates)
+ocir_prepan_model0b_estimates
+
+# Regression diagnostic statistics
+ocir_prepan_model0b_reg_stats <- model0b.reg.stats(outcome = "ocir.diff_score_base_prepan",
+                  data_set = "dat.prepan")
+kable(ocir_prepan_model0b_reg_stats)
+ocir_prepan_model0b_reg_stats
+```
+
+### Model 1a: Disorder hierarchical, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r ocir model1a diff_score w/education prepan}
+# Regression coefficients
+ocir_prepan_model1a_estimates <- model1a.estimates(outcome = "ocir.diff_score_base_prepan",
+                  data_set = "dat.prepan")
+kable(ocir_prepan_model1a_estimates)
+ocir_prepan_model1a_estimates
+
+# Regression diagnostic statistics
+ocir_prepan_model1a_reg_stats <- model1a.reg.stats(outcome = "ocir.diff_score_base_prepan",
+                  data_set = "dat.prepan")
+kable(ocir_prepan_model1a_reg_stats)
+ocir_prepan_model1a_reg_stats
+```
+
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r ocir model1b diff_score w/education prepan}
+# Regression coefficients
+ocir_prepan_model1b_estimates <- model1b.estimates(outcome = "ocir.diff_score_base_prepan",
+                  data_set = "dat.prepan")
+kable(ocir_prepan_model1b_estimates)
+ocir_prepan_model1b_estimates
+
+# Regression diagnostic statistics
+ocir_prepan_model1b_reg_stats <- model1b.reg.stats(outcome = "ocir.diff_score_base_prepan",
+                  data_set = "dat.prepan")
+kable(ocir_prepan_model1b_reg_stats)
+ocir_prepan_model1b_reg_stats
+```
+
+## Regression: Absolute scores
+### Model 0a: Disorder_hierarchical, Unadjusted
+```{r ocir model0a sum_score w/education prepan}
+# Regression coefficients
+ocir_prepan_model0a_explan_estimates <- model0a.explan.estimates(outcome = "ocir.sum_score_base",
+                         explan_var = "ocir.sum_score_prepan",
+                         data_set = "dat.prepan")
+kable(ocir_prepan_model0a_explan_estimates)
+ocir_prepan_model0a_explan_estimates
+
+# Regression diagnostic statistics
+ocir_prepan_model0a_explan_reg_stats <- model0a.explan.reg.stats(outcome = "ocir.sum_score_base",
+                         explan_var = "ocir.sum_score_prepan",
+                         data_set = "dat.prepan")
+kable(ocir_prepan_model0a_explan_reg_stats)
+ocir_prepan_model0a_explan_reg_stats
+```
+
+### Model 0b: Overlapping disorders, Unadjusted
+```{r ocir model0b sum_score w/education prepan}
+# Regression coefficients
+ocir_prepan_model0b_explan_estimates <- model0b.explan.estimates(outcome = "ocir.sum_score_base",
+                         explan_var = "ocir.sum_score_prepan",
+                         data_set = "dat.prepan")
+kable(ocir_prepan_model0b_explan_estimates)
+ocir_prepan_model0b_explan_estimates
+
+# Regression diagnostic statistics
+ocir_prepan_model0b_explan_reg_stats <- model0b.explan.reg.stats(outcome = "ocir.sum_score_base",
+                         explan_var = "ocir.sum_score_prepan",
+                         data_set = "dat.prepan")
+kable(ocir_prepan_model0b_explan_reg_stats)
+ocir_prepan_model0b_explan_reg_stats
+```
+
+### Model 1a: Disorder hierarchical, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r ocir model1a sum_score w/education prepan}
+# Regression coefficients
+ocir_prepan_model1a_explan_estimates <- model1a.explan.estimates(outcome = "ocir.sum_score_base",
+                         explan_var = "ocir.sum_score_prepan",
+                         data_set = "dat.prepan")
+kable(ocir_prepan_model1a_explan_estimates)
+ocir_prepan_model1a_explan_estimates
+
+# Regression diagnostic statistics
+ocir_prepan_model1a_explan_reg_stats <- model1a.explan.reg.stats(outcome = "ocir.sum_score_base",
+                         explan_var = "ocir.sum_score_prepan",
+                         data_set = "dat.prepan")
+kable(ocir_prepan_model1a_explan_reg_stats)
+ocir_prepan_model1a_explan_reg_stats
+```
+
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r ocir model1b sum_score w/education prepan}
+# Regression coefficients
+ocir_prepan_model1b_explan_estimates <- model1b.explan.estimates(outcome = "ocir.sum_score_base",
+                         explan_var = "ocir.sum_score_prepan",
+                         data_set = "dat.prepan")
+kable(ocir_prepan_model1b_explan_estimates)
+ocir_prepan_model1b_explan_estimates
+
+# Regression diagnostic statistics
+ocir_prepan_model1b_explan_reg_stats <- model1b.explan.reg.stats(outcome = "ocir.sum_score_base",
+                         explan_var = "ocir.sum_score_prepan",
+                         data_set = "dat.prepan")
+kable(ocir_prepan_model1b_explan_reg_stats)
+ocir_prepan_model1b_explan_reg_stats
+```
+
+# OCIR retro
+## Regression: Change scores
+### Model 0a: Disorder_hierarchical, Unadjusted
+```{r ocir model0a diff_score w/education retro}
+# Regression coefficients
+ocir_retro_model0a_estimates <- model0a.estimates(outcome = "ocir.diff_score_base_retro",
+                                                 data_set = "dat.retro")
+kable(ocir_retro_model0a_estimates)
+ocir_retro_model0a_estimates
+
+# Regression diagnostic statistics
+ocir_retro_model0a_reg_stats <- model0a.reg.stats(outcome = "ocir.diff_score_base_retro",
+                                                 data_set = "dat.retro")
+kable(ocir_retro_model0a_reg_stats)
+ocir_retro_model0a_reg_stats
+```
+
+### Model 0b: Overlapping disorders, Unadjusted
+```{r ocir model0b diff_score w/education retro}
+# Regression coefficients
+ocir_retro_model0b_estimates <- model0b.estimates(outcome = "ocir.diff_score_base_retro",
+                                                 data_set = "dat.retro")
+kable(ocir_retro_model0b_estimates)
+ocir_retro_model0b_estimates
+
+# Regression diagnostic statistics
+ocir_retro_model0b_reg_stats <- model0b.reg.stats(outcome = "ocir.diff_score_base_retro",
+                                                 data_set = "dat.retro")
+kable(ocir_retro_model0b_reg_stats)
+ocir_retro_model0b_reg_stats
+```
+
+### Model 1a: Disorder hierarchical, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r ocir model1a diff_score w/education retro}
+# Regression coefficients
+ocir_retro_model1a_estimates <- model1a.estimates(outcome = "ocir.diff_score_base_retro",
+                                                 data_set = "dat.retro")
+kable(ocir_retro_model1a_estimates)
+ocir_retro_model1a_estimates
+
+# Regression diagnostic statistics
+ocir_retro_model1a_reg_stats <- model1a.reg.stats(outcome = "ocir.diff_score_base_retro",
+                                                 data_set = "dat.retro")
+kable(ocir_retro_model1a_reg_stats)
+ocir_retro_model1a_reg_stats
+```
+
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r ocir model1b diff_score w/education retro}
+# Regression coefficients
+ocir_retro_model1b_estimates <- model1b.estimates(outcome = "ocir.diff_score_base_retro",
+                                                 data_set = "dat.retro")
+kable(ocir_retro_model1b_estimates)
+ocir_retro_model1b_estimates
+
+# Regression diagnostic statistics
+ocir_retro_model1b_reg_stats <- model1b.reg.stats(outcome = "ocir.diff_score_base_retro",
+                                                 data_set = "dat.retro")
+kable(ocir_retro_model1b_reg_stats)
+ocir_retro_model1b_reg_stats
+```
+
+## Regression: Absolute scores
+### Model 0a: Disorder_hierarchical, Unadjusted
+```{r ocir model0a sum_score w/education retro}
+# Regression coefficients
+ocir_retro_model0a_explan_estimates <- model0a.explan.estimates(outcome = "ocir.sum_score_base",
+                                                               explan_var = "ocir.sum_score_retro",
+                                                               data_set = "dat.retro")
+kable(ocir_retro_model0a_explan_estimates)
+ocir_retro_model0a_explan_estimates
+
+# Regression diagnostic statistics
+ocir_retro_model0a_explan_reg_stats <- model0a.explan.reg.stats(outcome = "ocir.sum_score_base",
+                                                               explan_var = "ocir.sum_score_retro",
+                                                               data_set = "dat.retro")
+kable(ocir_retro_model0a_explan_reg_stats)
+ocir_retro_model0a_explan_reg_stats
+```
+
+### Model 0b: Overlapping disorders, Unadjusted
+```{r ocir model0b sum_score w/education retro}
+# Regression coefficients
+ocir_retro_model0b_explan_estimates <- model0b.explan.estimates(outcome = "ocir.sum_score_base",
+                                                               explan_var = "ocir.sum_score_retro",
+                                                               data_set = "dat.retro")
+kable(ocir_retro_model0b_explan_estimates)
+ocir_retro_model0b_explan_estimates
+
+# Regression diagnostic statistics
+ocir_retro_model0b_explan_reg_stats <- model0b.explan.reg.stats(outcome = "ocir.sum_score_base",
+                                                               explan_var = "ocir.sum_score_retro",
+                                                               data_set = "dat.retro")
+kable(ocir_retro_model0b_explan_reg_stats)
+ocir_retro_model0b_explan_reg_stats
+```
+
+### Model 1a: Disorder hierarchical, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r ocir model1a sum_score w/education retro}
+# Regression coefficients
+ocir_retro_model1a_explan_estimates <- model1a.explan.estimates(outcome = "ocir.sum_score_base",
+                                                               explan_var = "ocir.sum_score_retro",
+                                                               data_set = "dat.retro")
+kable(ocir_retro_model1a_explan_estimates)
+ocir_retro_model1a_explan_estimates
+
+# Regression diagnostic statistics
+ocir_retro_model1a_explan_reg_stats <- model1a.explan.reg.stats(outcome = "ocir.sum_score_base",
+                                                               explan_var = "ocir.sum_score_retro",
+                                                               data_set = "dat.retro")
+kable(ocir_retro_model1a_explan_reg_stats)
+ocir_retro_model1a_explan_reg_stats
+```
+
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r ocir model1b sum_score w/education retro}
+# Regression coefficients
+ocir_retro_model1b_explan_estimates <- model1b.explan.estimates(outcome = "ocir.sum_score_base",
+                                                               explan_var = "ocir.sum_score_retro",
+                                                               data_set = "dat.retro")
+kable(ocir_retro_model1b_explan_estimates)
+ocir_retro_model1b_explan_estimates
+
+# Regression diagnostic statistics
+ocir_retro_model1b_explan_reg_stats <- model1b.explan.reg.stats(outcome = "ocir.sum_score_base",
+                                                               explan_var = "ocir.sum_score_retro",
+                                                               data_set = "dat.retro")
+kable(ocir_retro_model1b_explan_reg_stats)
+ocir_retro_model1b_explan_reg_stats
+```
+
+# PCL prepan
+## Regression: Change scores
+### Model 0a: Disorder_hierarchical, Unadjusted
+```{r pcl model0a diff_score w/education prepan}
+# Regression coefficients
+pcl_prepan_model0a_estimates <- model0a.estimates(outcome = "pcl.diff_score_base_prepan",
+                  data_set = "dat.prepan")
+kable(pcl_prepan_model0a_estimates)
+pcl_prepan_model0a_estimates
+
+# Regression diagnostic statistics
+pcl_prepan_model0a_reg_stats <- model0a.reg.stats(outcome = "pcl.diff_score_base_prepan",
+                  data_set = "dat.prepan")
+kable(pcl_prepan_model0a_reg_stats)
+pcl_prepan_model0a_reg_stats
+```
+
+### Model 0b: Overlapping disorders, Unadjusted
+```{r pcl model0b diff_score w/education prepan}
+# Regression coefficients
+pcl_prepan_model0b_estimates <- model0b.estimates(outcome = "pcl.diff_score_base_prepan",
+                  data_set = "dat.prepan")
+kable(pcl_prepan_model0b_estimates)
+pcl_prepan_model0b_estimates
+
+# Regression diagnostic statistics
+pcl_prepan_model0b_reg_stats <- model0b.reg.stats(outcome = "pcl.diff_score_base_prepan",
+                  data_set = "dat.prepan")
+kable(pcl_prepan_model0b_reg_stats)
+pcl_prepan_model0b_reg_stats
+```
+
+### Model 1a: Disorder hierarchical, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r pcl model1a diff_score w/education prepan}
+# Regression coefficients
+pcl_prepan_model1a_estimates <- model1a.estimates(outcome = "pcl.diff_score_base_prepan",
+                  data_set = "dat.prepan")
+kable(pcl_prepan_model1a_estimates)
+pcl_prepan_model1a_estimates
+
+# Regression diagnostic statistics
+pcl_prepan_model1a_reg_stats <- model1a.reg.stats(outcome = "pcl.diff_score_base_prepan",
+                  data_set = "dat.prepan")
+kable(pcl_prepan_model1a_reg_stats)
+pcl_prepan_model1a_reg_stats
+```
+
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r pcl model1b diff_score w/education prepan}
+# Regression coefficients
+pcl_prepan_model1b_estimates <- model1b.estimates(outcome = "pcl.diff_score_base_prepan",
+                  data_set = "dat.prepan")
+kable(pcl_prepan_model1b_estimates)
+pcl_prepan_model1b_estimates
+
+# Regression diagnostic statistics
+pcl_prepan_model1b_reg_stats <- model1b.reg.stats(outcome = "pcl.diff_score_base_prepan",
+                  data_set = "dat.prepan")
+kable(pcl_prepan_model1b_reg_stats)
+pcl_prepan_model1b_reg_stats
+```
+
+## Regression: Absolute scores
+### Model 0a: Disorder_hierarchical, Unadjusted
+```{r pcl model0a sum_score w/education prepan}
+# Regression coefficients
+pcl_prepan_model0a_explan_estimates <- model0a.explan.estimates(outcome = "pcl.sum_score_base",
+                         explan_var = "pcl.sum_score_prepan",
+                         data_set = "dat.prepan")
+kable(pcl_prepan_model0a_explan_estimates)
+pcl_prepan_model0a_explan_estimates
+
+# Regression diagnostic statistics
+pcl_prepan_model0a_explan_reg_stats <- model0a.explan.reg.stats(outcome = "pcl.sum_score_base",
+                         explan_var = "pcl.sum_score_prepan",
+                         data_set = "dat.prepan")
+kable(pcl_prepan_model0a_explan_reg_stats)
+pcl_prepan_model0a_explan_reg_stats
+```
+
+### Model 0b: Overlapping disorders, Unadjusted
+```{r pcl model0b sum_score w/education prepan}
+# Regression coefficients
+pcl_prepan_model0b_explan_estimates <- model0b.explan.estimates(outcome = "pcl.sum_score_base",
+                         explan_var = "pcl.sum_score_prepan",
+                         data_set = "dat.prepan")
+kable(pcl_prepan_model0b_explan_estimates)
+pcl_prepan_model0b_explan_estimates
+
+# Regression diagnostic statistics
+pcl_prepan_model0b_explan_reg_stats <- model0b.explan.reg.stats(outcome = "pcl.sum_score_base",
+                         explan_var = "pcl.sum_score_prepan",
+                         data_set = "dat.prepan")
+kable(pcl_prepan_model0b_explan_reg_stats)
+pcl_prepan_model0b_explan_reg_stats
+```
+
+### Model 1a: Disorder hierarchical, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r pcl model1a sum_score w/education prepan}
+# Regression coefficients
+pcl_prepan_model1a_explan_estimates <- model1a.explan.estimates(outcome = "pcl.sum_score_base",
+                         explan_var = "pcl.sum_score_prepan",
+                         data_set = "dat.prepan")
+kable(pcl_prepan_model1a_explan_estimates)
+pcl_prepan_model1a_explan_estimates
+
+# Regression diagnostic statistics
+pcl_prepan_model1a_explan_reg_stats <- model1a.explan.reg.stats(outcome = "pcl.sum_score_base",
+                         explan_var = "pcl.sum_score_prepan",
+                         data_set = "dat.prepan")
+kable(pcl_prepan_model1a_explan_reg_stats)
+pcl_prepan_model1a_explan_reg_stats
+```
+
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r pcl model1b sum_score w/education prepan}
 # Regression coefficients
@@
                          explan_var = "pcl.sum_score_prepan",
-                         data_set = "dat.prepan_sensitivity_3months")
+                         data_set = "dat.prepan")
 kable(pcl_prepan_model1b_explan_estimates)
@@
                          explan_var = "pcl.sum_score_prepan",
-                         data_set = "dat.prepan_sensitivity_3months")
+                         data_set = "dat.prepan")
 kable(pcl_prepan_model1b_explan_reg_stats)
@@
 
-#### Subset of participants 6 months prior to pandemic
-```{r pcl model1b sum_score prepan - sensitivity 6 months}
+# FUNCTION CHANGE to include employment status as predictors
+
+```{r model0a employment function}
+model0a.estimates <- function(outcome, data_set) {
+  # define the variable name of the dependent variable
+  dependent.variable <- outcome
+  # define the independent variables
+  independent.variables <- c("Disorder_hierarchical",
+                             "employment.unemployed")
+  # create the formula
+  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
+  glm.formula
+
+  # run the glm
+  assign(paste0(outcome,".model0a"),
+         lm( formula = glm.formula,
+              data = get(data_set)
+              )
+  )
+
+  assign(paste0(outcome,"model0a_estimates"),
+         tidy(get(paste0(outcome,".model0a")), conf.int = TRUE) %>%
+           mutate(
+             "Indepent variable" = recode_factor(
+               term,
+               "(Intercept)" = "Intercept",
+               "Disorder_hierarchicalAnxiety disorders" = "Anxiety disorders",
+               "Disorder_hierarchicalEating disorders" = "Eating disorders",
+               "Disorder_hierarchicalOCDs" = "OCDs",
+               "Disorder_hierarchicalPTSD" = "PTSD",
+               "Disorder_hierarchicalDepressive disorders" = "Depressive disorders",
+               "Disorder_hierarchicalBipolar disorders" = "Bipolar disorders", 
+               "employment.unemployedUnemployed" = "Unemployed", 
+               "employment.unemployedNot Unemployed" = "Not unemployed"
+             ),
+    "Estimate" = format(
+      round(estimate,
+            digits = 2),
+      nsmall = 2),
+    "95% CI low" = format(
+      round(conf.low,
+            digits = 2),
+      nsmall = 2),
+    "95% CI up" = format(
+      round(conf.high,
+            digits = 2),
+      nsmall = 2),
+    "SE" = format(
+      round(std.error,
+            digits = 2),
+      nsmall = 2),
+    "z score" = format(
+      round(statistic,
+            digits = 2),
+      nsmall = 2),
+    "p value" = case_when(
+      p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
+      p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
+      p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
+  )
+  ) %>%
+  select(
+    "Indepent variable",
+    "Estimate",
+    "95% CI low",
+    "95% CI up",
+    "SE",
+#    "z score",
+    "p value"
+  )
+  )
+
+  return(get(paste0(outcome,"model0a_estimates")))
+}
+
+model0a.reg.stats <- function(outcome, data_set) {
+  # define the variable name of the dependent variable
+  dependent.variable <- outcome
+  # define the independent variables
+  independent.variables <- c("Disorder_hierarchical")
+  # create the formula
+  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
+  glm.formula
+
+  # run the glm
+  assign(paste0(outcome,".model0a"),
+         lm( formula = glm.formula,
+              data = get(data_set)
+              )
+  )
+
+  assign(paste0(outcome,"model0a_reg_stats"),
+         glance(get(paste0(outcome,".model0a"))) %>%
+           mutate(
+             "n" = format(
+               round(nobs,
+                     digits = 0),
+               nsmall = 0),
+             "R2" = format(
+               round(r.squared,
+                     digits = 2),
+               nsmall = 2),
+             "adjust. R2" = format(
+               round(adj.r.squared,
+                     digits = 2),
+               nsmall = 2),
+             "F" = format(
+               round(statistic,
+                     digits = 2),
+               nsmall = 2),
+             "p value" = case_when(
+               p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
+               p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
+               p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
+             )
+           ) %>%
+           select(
+             "n",
+             "R2",
+             "adjust. R2",
+             "F",
+             "p value",
+             "df"
+           )
+  )
+
+  return(get(paste0(outcome,"model0a_reg_stats")))
+}
+```
+
+```{r model0b employment function}
+model0b.estimates <- function(outcome, data_set) {
+  # define the variable name of the dependent variable
+  dependent.variable <- outcome
+  # define the independent variables
+  independent.variables <- c("depression_and_anxiety",
+                             "eating_disorders",
+                             "obsessive_compulsive_disorders",
+                             "bipolar_and_schizophrenia",
+                             "mhd.posttraumatic_stress_disorder_ptsd",
+                             "autism_spectrum_disorder",
+                             "mhd.attention_deficit_hyperactivity_disorder",
+                             "mhd.personality_disorder", 
+                             "employment.unemployed"
+                                )
+  # create the formula
+  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
+  glm.formula
+
+  # run the glm
+  assign(paste0(outcome,".model0b"),
+         lm( formula = glm.formula,
+             data = get(data_set)
+         )
+  )
+
+  assign(paste0(outcome,"model0b_estimates"),
+         tidy(get(paste0(outcome,".model0b")), conf.int = TRUE) %>%
+           mutate(
+             "Indepent variable" = recode_factor(
+               term,
+               "(Intercept)" = "Intercept",
+               "anxiety_disordersAnxiety disorder" = "Anxiety disorders",
+               "depressive_disordersDepressive disorder" = "Depressive disorders",
+               "depression_and_anxietyDepressive and anxiety disorder" = "Depressive and anxiety disorder",
+               "depression_and_anxietyOnly depressive disorder" = "Only depressive disorder",
+               "depression_and_anxietyOnly anxiety disorder" = "Only anxiety disorder",
+               "eating_disordersEating disorder" = "Eating disorders",
+               "obsessive_compulsive_disordersObsessive compulsive disorder" = "OCDs",
+               "bipolar_and_schizophreniaPsychotic and bipolar disorder" = "Psychotic and bipolar disorder",
+               "bipolar_and_schizophreniaOnly psychotic disorder" = "Only psychotic disorder",
+               "bipolar_and_schizophreniaOnly bipolar disorder" = "Only bipolar disorder",
+               "psychotic_disordersPsychotic disorder" = "Psychotic disorder",
+               "mhd.mania_hypomania_bipolar_or_manicdepressionMania, hypomania, bipolar or manic-depression" = "Bipolar disorder",
+               "mhd.posttraumatic_stress_disorder_ptsdPost-traumatic stress disorder (PTSD)" = "PTSD",
+               "autism_spectrum_disorderAutism spectrum disorder" = "ASD",
+               "mhd.attention_deficit_hyperactivity_disorderAttention deficit or attention deficit and hyperactivity disorder (ADD/ADHD)" = "ADHD",
+               "mhd.personality_disorderPersonality disorder" = "Personality disorder", 
+               "employment.unemployedUnemployed" = "Unemployed", 
+               "employment.unemployedNot Unemployed" = "Not unemployed"
+             ),
+             "Estimate" = format(
+               round(estimate,
+                     digits = 2),
+               nsmall = 2),
+             "95% CI low" = format(
+               round(conf.low,
+                     digits = 2),
+               nsmall = 2),
+             "95% CI up" = format(
+               round(conf.high,
+                     digits = 2),
+               nsmall = 2),
+             "SE" = format(
+               round(std.error,
+                     digits = 2),
+               nsmall = 2),
+             "z score" = format(
+               round(statistic,
+                     digits = 2),
+               nsmall = 2),
+             "p value" = case_when(
+               p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
+               p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
+               p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
+             )
+           ) %>%
+           select(
+             "Indepent variable",
+             "Estimate",
+             "95% CI low",
+             "95% CI up",
+             "SE",
+             #    "z score",
+             "p value"
+           )
+  )
+
+  return(get(paste0(outcome,"model0b_estimates")))
+}
+
+model0b.reg.stats <- function(outcome, data_set) {
+  # define the variable name of the dependent variable
+  dependent.variable <- outcome
+  # define the independent variables
+  independent.variables <- c("Disorder_hierarchical")
+  # create the formula
+  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
+  glm.formula
+
+  # run the glm
+  assign(paste0(outcome,".model0b"),
+         lm( formula = glm.formula,
+             data = get(data_set)
+         )
+  )
+
+  assign(paste0(outcome,"model0b_reg_stats"),
+         glance(get(paste0(outcome,".model0b"))) %>%
+           mutate(
+             "n" = format(
+               round(nobs,
+                     digits = 0),
+               nsmall = 0),
+             "R2" = format(
+               round(r.squared,
+                     digits = 2),
+               nsmall = 2),
+             "adjust. R2" = format(
+               round(adj.r.squared,
+                     digits = 2),
+               nsmall = 2),
+             "F" = format(
+               round(statistic,
+                     digits = 2),
+               nsmall = 2),
+             "p value" = case_when(
+               p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
+               p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
+               p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
+             )
+           ) %>%
+           select(
+             "n",
+             "R2",
+             "adjust. R2",
+             "F",
+             "p value",
+             "df"
+           )
+  )
+
+  return(get(paste0(outcome,"model0b_reg_stats")))
+}
+```
+
+```{r model1a employment function}
+model1a.estimates <- function(outcome, data_set) {
+  # define the variable name of the dependent variable
+  dependent.variable <- outcome
+  # define the independent variables
+  independent.variables <- c("Disorder_hierarchical",
+                            "Gender_collapsed",
+                            "age_category_collapsed",
+                            "Ethnicity_collapsed",
+                            "time_diff_coping_lockdown_march_23", 
+                            "employment.unemployed"
+                            )
+  # create the formula
+  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
+  glm.formula
+
+  # run the glm
+  assign(paste0(outcome,".model1a"),
+         lm( formula = glm.formula,
+             data = get(data_set)
+         )
+  )
+
+  assign(paste0(outcome,"model1a_estimates"),
+         tidy(get(paste0(outcome,".model1a")), conf.int = TRUE) %>%
+           mutate(
+             "Indepent variable" = recode_factor(
+               term,
+               "(Intercept)" = "Intercept",
+               "Disorder_hierarchicalAnxiety disorders" = "Anxiety disorders",
+               "Disorder_hierarchicalEating disorders" = "Eating disorders",
+               "Disorder_hierarchicalOCDs" = "OCDs",
+               "Disorder_hierarchicalPTSD" = "PTSD",
+               "Disorder_hierarchicalDepressive disorders" = "Depressive disorders",
+               "Disorder_hierarchicalBipolar disorders" = "Bipolar disorders",
+               "Gender_collapsedFemale" = "Female",
+               "Gender_collapsedNon-binary/Self-defined" = "Non-binary/Self-defined",
+               "age_category_collapsed19-25" = "19-25 years",
+               "age_category_collapsed26-35" = "26-35 years",
+               "age_category_collapsed36-45" = "36-45 years",
+               "age_category_collapsed46-55" = "46-55 years",
+               "age_category_collapsed56-65" = "56-65 years",
+               "age_category_collapsed66-70" = "66-70 years",
+               "age_category_collapsed71-75" = "71-75 years",
+               "age_category_collapsed76+" = "76+ years",
+               "Ethnicity_collapsedMixed or multiple ethnic origins" = "Mixed or multiple ethnic origins",
+               "Ethnicity_collapsedAsian or Asian British" = "Asian or Asian British",
+               "Ethnicity_collapsedAfrican or African British" = "African or African British",
+               "Ethnicity_collapsedOther" = "Other ethnicity",
+               "time_diff_coping_lockdown_march_23" = "Time difference: Lockdown to baseline",
+              "employment.unemployedUnemployed" = "Unemployed", 
+               "employment.unemployedNot Unemployed" = "Not unemployed"
+             ),
+             "Estimate" = format(
+               round(estimate,
+                     digits = 2),
+               nsmall = 2),
+             "95% CI low" = format(
+               round(conf.low,
+                     digits = 2),
+               nsmall = 2),
+             "95% CI up" = format(
+               round(conf.high,
+                     digits = 2),
+               nsmall = 2),
+             "SE" = format(
+               round(std.error,
+                     digits = 2),
+               nsmall = 2),
+             "z score" = format(
+               round(statistic,
+                     digits = 2),
+               nsmall = 2),
+             "p value" = case_when(
+               p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
+               p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
+               p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
+             )
+           ) %>%
+           select(
+             "Indepent variable",
+             "Estimate",
+             "95% CI low",
+             "95% CI up",
+             "SE",
+             #    "z score",
+             "p value"
+           )
+  )
+
+  return(get(paste0(outcome,"model1a_estimates")))
+}
+
+model1a.reg.stats <- function(outcome, data_set) {
+  # define the variable name of the dependent variable
+  dependent.variable <- outcome
+  # define the independent variables
+  independent.variables <- c("Disorder_hierarchical")
+  # create the formula
+  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
+  glm.formula
+
+  # run the glm
+  assign(paste0(outcome,".model1a"),
+         lm( formula = glm.formula,
+             data = get(data_set)
+         )
+  )
+
+  assign(paste0(outcome,"model1a_reg_stats"),
+         glance(get(paste0(outcome,".model1a"))) %>%
+           mutate(
+             "n" = format(
+               round(nobs,
+                     digits = 0),
+               nsmall = 0),
+             "R2" = format(
+               round(r.squared,
+                     digits = 2),
+               nsmall = 2),
+             "adjust. R2" = format(
+               round(adj.r.squared,
+                     digits = 2),
+               nsmall = 2),
+             "F" = format(
+               round(statistic,
+                     digits = 2),
+               nsmall = 2),
+             "p value" = case_when(
+               p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
+               p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
+               p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
+             )
+           ) %>%
+           select(
+             "n",
+             "R2",
+             "adjust. R2",
+             "F",
+             "p value",
+             "df"
+           )
+  )
+
+  return(get(paste0(outcome,"model1a_reg_stats")))
+}
+```
+
+```{r model1b employment function}
+model1b.estimates <- function(outcome, data_set) {
+  # define the variable name of the dependent variable
+  dependent.variable <- outcome
+  # define the independent variables
+  independent.variables <- c("depression_and_anxiety",
+                             "eating_disorders",
+                             "obsessive_compulsive_disorders",
+                             "bipolar_and_schizophrenia",
+                             "mhd.posttraumatic_stress_disorder_ptsd",
+                             "autism_spectrum_disorder",
+                             "mhd.attention_deficit_hyperactivity_disorder",
+                             "mhd.personality_disorder",
+                             "Gender_collapsed",
+                             "age_category_collapsed",
+                             "Ethnicity_collapsed",
+                             "key_worker",
+                             "time_diff_coping_lockdown_march_23", 
+                             "employment.unemployed"
+                                )
+  # create the formula
+  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
+  glm.formula
+
+  # run the glm
+  assign(paste0(outcome,".model1b"),
+         lm( formula = glm.formula,
+             data = get(data_set)
+         )
+  )
+
+  assign(paste0(outcome,"model1b_estimates"),
+         tidy(get(paste0(outcome,".model1b")), conf.int = TRUE) %>%
+           mutate(
+             "Indepent variable" = recode_factor(
+               term,
+               "(Intercept)" = "Intercept",
+               "anxiety_disordersAnxiety disorder" = "Anxiety disorders",
+               "depressive_disordersDepressive disorder" = "Depressive disorders",
+               "depression_and_anxietyDepressive and anxiety disorder" = "Depressive and anxiety disorder",
+               "depression_and_anxietyOnly depressive disorder" = "Only depressive disorder",
+               "depression_and_anxietyOnly anxiety disorder" = "Only anxiety disorder",
+               "eating_disordersEating disorder" = "Eating disorders",
+               "obsessive_compulsive_disordersObsessive compulsive disorder" = "OCDs",
+               "bipolar_and_schizophreniaPsychotic and bipolar disorder" = "Psychotic and bipolar disorder",
+               "bipolar_and_schizophreniaOnly psychotic disorder" = "Only psychotic disorder",
+               "bipolar_and_schizophreniaOnly bipolar disorder" = "Only bipolar disorder",
+               "psychotic_disordersPsychotic disorder" = "Psychotic disorder",
+               "mhd.mania_hypomania_bipolar_or_manicdepressionMania, hypomania, bipolar or manic-depression" = "Bipolar disorder",
+               "mhd.posttraumatic_stress_disorder_ptsdPost-traumatic stress disorder (PTSD)" = "PTSD",
+               "autism_spectrum_disorderAutism spectrum disorder" = "ASD",
+               "mhd.attention_deficit_hyperactivity_disorderAttention deficit or attention deficit and hyperactivity disorder (ADD/ADHD)" = "ADHD",
+               "mhd.personality_disorderPersonality disorder" = "Personality disorder",
+               "Gender_collapsedFemale" = "Female",
+               "Gender_collapsedNon-binary/Self-defined" = "Non-binary/Self-defined",
+               "age_category_collapsed19-25" = "19-25 years",
+               "age_category_collapsed26-35" = "26-35 years",
+               "age_category_collapsed36-45" = "36-45 years",
+               "age_category_collapsed46-55" = "46-55 years",
+               "age_category_collapsed56-65" = "56-65 years",
+               "age_category_collapsed66-70" = "66-70 years",
+               "age_category_collapsed71-75" = "71-75 years",
+               "age_category_collapsed76+" = "76+ years",
+               "Ethnicity_collapsedMixed or multiple ethnic origins" = "Mixed or multiple ethnic origins",
+               "Ethnicity_collapsedAsian or Asian British" = "Asian or Asian British",
+               "Ethnicity_collapsedAfrican or African British" = "African or African British",
+               "Ethnicity_collapsedOther" = "Other ethnicity",
+               "key_workerKey worker" = "Key worker",
+               "time_diff_coping_lockdown_march_23" = "Time difference: Lockdown to baseline", 
+               "employment.unemployedUnemployed" = "Unemployed", 
+               "employment.unemployedNot Unemployed" = "Not unemployed"
+             ),
+             "Estimate" = format(
+               round(estimate,
+                     digits = 2),
+               nsmall = 2),
+             "95% CI low" = format(
+               round(conf.low,
+                     digits = 2),
+               nsmall = 2),
+             "95% CI up" = format(
+               round(conf.high,
+                     digits = 2),
+               nsmall = 2),
+             "SE" = format(
+               round(std.error,
+                     digits = 2),
+               nsmall = 2),
+             "z score" = format(
+               round(statistic,
+                     digits = 2),
+               nsmall = 2),
+             "p value" = case_when(
+               p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
+               p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
+               p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
+             )
+           ) %>%
+           select(
+             "Indepent variable",
+             "Estimate",
+             "95% CI low",
+             "95% CI up",
+             "SE",
+             #    "z score",
+             "p value"
+           )
+  )
+
+  return(get(paste0(outcome,"model1b_estimates")))
+}
+
+model1b.reg.stats <- function(outcome, data_set) {
+  # define the variable name of the dependent variable
+  dependent.variable <- outcome
+  # define the independent variables
+  independent.variables <- c("Disorder_hierarchical")
+  # create the formula
+  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
+  glm.formula
+
+  # run the glm
+  assign(paste0(outcome,".model1b"),
+         lm( formula = glm.formula,
+             data = get(data_set)
+         )
+  )
+
+  assign(paste0(outcome,"model1b_reg_stats"),
+         glance(get(paste0(outcome,".model1b"))) %>%
+           mutate(
+             "n" = format(
+               round(nobs,
+                     digits = 0),
+               nsmall = 0),
+             "R2" = format(
+               round(r.squared,
+                     digits = 2),
+               nsmall = 2),
+             "adjust. R2" = format(
+               round(adj.r.squared,
+                     digits = 2),
+               nsmall = 2),
+             "F" = format(
+               round(statistic,
+                     digits = 2),
+               nsmall = 2),
+             "p value" = case_when(
+               p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
+               p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
+               p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
+             )
+           ) %>%
+           select(
+             "n",
+             "R2",
+             "adjust. R2",
+             "F",
+             "p value",
+             "df"
+           )
+  )
+
+  return(get(paste0(outcome,"model1b_reg_stats")))
+}
+```
+
+```{r model0a.explan employment function}
+model0a.explan.estimates <- function(outcome, explan_var, data_set) {
+  # define the variable name of the dependent variable
+  dependent.variable <- outcome
+  # define the independent variables
+  independent.variables <- c(explan_var, "Disorder_hierarchical", 
+                             "employment.unemployed")
+  # create the formula
+  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
+  glm.formula
+
+  # run the glm
+  assign(paste0(outcome,".",explan_var,".model0a.explan"),
+         lm( formula = glm.formula,
+             data = get(data_set)
+         )
+  )
+
+  assign(paste0(outcome,".",explan_var,"model0a.explan_estimates"),
+         tidy(get(paste0(outcome,".",explan_var,".model0a.explan")), conf.int = TRUE) %>%
+           mutate(
+             "Indepent variable" = recode_factor(
+               term,
+               "(Intercept)" = "Intercept",
+               "Disorder_hierarchicalAnxiety disorders" = "Anxiety disorders",
+               "Disorder_hierarchicalEating disorders" = "Eating disorders",
+               "Disorder_hierarchicalOCDs" = "OCDs",
+               "Disorder_hierarchicalPTSD" = "PTSD",
+               "Disorder_hierarchicalDepressive disorders" = "Depressive disorders",
+               "Disorder_hierarchicalBipolar disorders" = "Bipolar disorders", 
+              "employment.unemployedUnemployed" = "Unemployed", 
+               "employment.unemployedNot Unemployed" = "Not unemployed"
+             ),
+             "Estimate" = format(
+               round(estimate,
+                     digits = 2),
+               nsmall = 2),
+             "95% CI low" = format(
+               round(conf.low,
+                     digits = 2),
+               nsmall = 2),
+             "95% CI up" = format(
+               round(conf.high,
+                     digits = 2),
+               nsmall = 2),
+             "SE" = format(
+               round(std.error,
+                     digits = 2),
+               nsmall = 2),
+             "z score" = format(
+               round(statistic,
+                     digits = 2),
+               nsmall = 2),
+             "p value" = case_when(
+               p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
+               p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
+               p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
+             )
+           ) %>%
+           select(
+             "Indepent variable",
+             "Estimate",
+             "95% CI low",
+             "95% CI up",
+             "SE",
+             #    "z score",
+             "p value"
+           )
+  )
+
+  return(get(paste0(outcome,".",explan_var,"model0a.explan_estimates")))
+}
+
+model0a.explan.reg.stats <- function(outcome, explan_var, data_set) {
+  # define the variable name of the dependent variable
+  dependent.variable <- outcome
+  # define the independent variables
+  independent.variables <- c(explan_var, "Disorder_hierarchical")
+  # create the formula
+  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
+  glm.formula
+
+  # run the glm
+  assign(paste0(outcome,".",explan_var,".model0a.explan"),
+         lm( formula = glm.formula,
+             data = get(data_set)
+         )
+  )
+
+  assign(paste0(outcome,".",explan_var,"model0a.explan_reg_stats"),
+         glance(get(paste0(outcome,".",explan_var,".model0a.explan"))) %>%
+           mutate(
+             "n" = format(
+               round(nobs,
+                     digits = 0),
+               nsmall = 0),
+             "R2" = format(
+               round(r.squared,
+                     digits = 2),
+               nsmall = 2),
+             "adjust. R2" = format(
+               round(adj.r.squared,
+                     digits = 2),
+               nsmall = 2),
+             "F" = format(
+               round(statistic,
+                     digits = 2),
+               nsmall = 2),
+             "p value" = case_when(
+               p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
+               p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
+               p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
+             )
+           ) %>%
+           select(
+             "n",
+             "R2",
+             "adjust. R2",
+             "F",
+             "p value",
+             "df"
+           )
+  )
+
+  return(get(paste0(outcome,".",explan_var,"model0a.explan_reg_stats")))
+}
+```
+
+```{r model0b.explan employment function}
+model0b.explan.estimates <- function(outcome, explan_var, data_set) {
+  # define the variable name of the dependent variable
+  dependent.variable <- outcome
+  # define the independent variables
+  independent.variables <- c(explan_var,
+                             "depression_and_anxiety",
+                             "eating_disorders",
+                             "obsessive_compulsive_disorders",
+                             "bipolar_and_schizophrenia",
+                             "mhd.posttraumatic_stress_disorder_ptsd",
+                             "autism_spectrum_disorder",
+                             "mhd.attention_deficit_hyperactivity_disorder",
+                             "mhd.personality_disorder", 
+                             "employment.unemployed"
+  )
+  # create the formula
+  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
+  glm.formula
+
+  # run the glm
+  assign(paste0(outcome,".",explan_var,".model0b.explan"),
+         lm( formula = glm.formula,
+             data = get(data_set)
+         )
+  )
+
+  assign(paste0(outcome,".",explan_var,"model0b.explan_estimates"),
+         tidy(get(paste0(outcome,".",explan_var,".model0b.explan")), conf.int = TRUE) %>%
+           mutate(
+             "Indepent variable" = recode_factor(
+               term,
+               "(Intercept)" = "Intercept",
+               "anxiety_disordersAnxiety disorder" = "Anxiety disorders",
+               "depressive_disordersDepressive disorder" = "Depressive disorders",
+               "depression_and_anxietyDepressive and anxiety disorder" = "Depressive and anxiety disorder",
+               "depression_and_anxietyOnly depressive disorder" = "Only depressive disorder",
+               "depression_and_anxietyOnly anxiety disorder" = "Only anxiety disorder",
+               "eating_disordersEating disorder" = "Eating disorders",
+               "obsessive_compulsive_disordersObsessive compulsive disorder" = "OCDs",
+               "bipolar_and_schizophreniaPsychotic and bipolar disorder" = "Psychotic and bipolar disorder",
+               "bipolar_and_schizophreniaOnly psychotic disorder" = "Only psychotic disorder",
+               "bipolar_and_schizophreniaOnly bipolar disorder" = "Only bipolar disorder",
+               "psychotic_disordersPsychotic disorder" = "Psychotic disorder",
+               "mhd.mania_hypomania_bipolar_or_manicdepressionMania, hypomania, bipolar or manic-depression" = "Bipolar disorder",
+               "mhd.posttraumatic_stress_disorder_ptsdPost-traumatic stress disorder (PTSD)" = "PTSD",
+               "autism_spectrum_disorderAutism spectrum disorder" = "ASD",
+               "mhd.attention_deficit_hyperactivity_disorderAttention deficit or attention deficit and hyperactivity disorder (ADD/ADHD)" = "ADHD",
+               "mhd.personality_disorderPersonality disorder" = "Personality disorder", 
+               "employment.unemployedUnemployed" = "Unemployed", 
+               "employment.unemployedNot Unemployed" = "Not unemployed"
+             ),
+             "Estimate" = format(
+               round(estimate,
+                     digits = 2),
+               nsmall = 2),
+             "95% CI low" = format(
+               round(conf.low,
+                     digits = 2),
+               nsmall = 2),
+             "95% CI up" = format(
+               round(conf.high,
+                     digits = 2),
+               nsmall = 2),
+             "SE" = format(
+               round(std.error,
+                     digits = 2),
+               nsmall = 2),
+             "z score" = format(
+               round(statistic,
+                     digits = 2),
+               nsmall = 2),
+             "p value" = case_when(
+               p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
+               p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
+               p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
+             )
+           ) %>%
+           select(
+             "Indepent variable",
+             "Estimate",
+             "95% CI low",
+             "95% CI up",
+             "SE",
+             #    "z score",
+             "p value"
+           )
+  )
+
+  return(get(paste0(outcome,".",explan_var,"model0b.explan_estimates")))
+}
+
+model0b.explan.reg.stats <- function(outcome, explan_var, data_set) {
+  # define the variable name of the dependent variable
+  dependent.variable <- outcome
+  # define the independent variables
+  independent.variables <- c("Disorder_hierarchical")
+  # create the formula
+  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
+  glm.formula
+
+  # run the glm
+  assign(paste0(outcome,".",explan_var,".model0b.explan"),
+         lm( formula = glm.formula,
+             data = get(data_set)
+         )
+  )
+
+  assign(paste0(outcome,".",explan_var,"model0b.explan_reg_stats"),
+         glance(get(paste0(outcome,".",explan_var,".model0b.explan"))) %>%
+           mutate(
+             "n" = format(
+               round(nobs,
+                     digits = 0),
+               nsmall = 0),
+             "R2" = format(
+               round(r.squared,
+                     digits = 2),
+               nsmall = 2),
+             "adjust. R2" = format(
+               round(adj.r.squared,
+                     digits = 2),
+               nsmall = 2),
+             "F" = format(
+               round(statistic,
+                     digits = 2),
+               nsmall = 2),
+             "p value" = case_when(
+               p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
+               p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
+               p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
+             )
+           ) %>%
+           select(
+             "n",
+             "R2",
+             "adjust. R2",
+             "F",
+             "p value",
+             "df"
+           )
+  )
+
+  return(get(paste0(outcome,".",explan_var,"model0b.explan_reg_stats")))
+}
+```
+
+```{r model1a.explan employment function}
+model1a.explan.estimates <- function(outcome, explan_var, data_set) {
+  # define the variable name of the dependent variable
+  dependent.variable <- outcome
+  # define the independent variables
+  independent.variables <- c(explan_var,
+                             "Disorder_hierarchical",
+                             "Gender_collapsed",
+                             "age_category_collapsed",
+                             "Ethnicity_collapsed",
+                             "key_worker",
+                             "time_diff_coping_lockdown_march_23", 
+                             "employment.unemployed"
+  )
+  # create the formula
+  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
+  glm.formula
+
+  # run the glm
+  assign(paste0(outcome,".",explan_var,".model1a.explan"),
+         lm( formula = glm.formula,
+             data = get(data_set)
+         )
+  )
+
+  assign(paste0(outcome,".",explan_var,"model1a.explan_estimates"),
+         tidy(get(paste0(outcome,".",explan_var,".model1a.explan")), conf.int = TRUE) %>%
+           mutate(
+             "Indepent variable" = recode_factor(
+               term,
+               "(Intercept)" = "Intercept",
+               "Disorder_hierarchicalAnxiety disorders" = "Anxiety disorders",
+               "Disorder_hierarchicalEating disorders" = "Eating disorders",
+               "Disorder_hierarchicalOCDs" = "OCDs",
+               "Disorder_hierarchicalPTSD" = "PTSD",
+               "Disorder_hierarchicalDepressive disorders" = "Depressive disorders",
+               "Disorder_hierarchicalBipolar disorders" = "Bipolar disorders",
+               "Gender_collapsedFemale" = "Female",
+               "Gender_collapsedNon-binary/Self-defined" = "Non-binary/Self-defined",
+               "age_category_collapsed19-25" = "19-25 years",
+               "age_category_collapsed26-35" = "26-35 years",
+               "age_category_collapsed36-45" = "36-45 years",
+               "age_category_collapsed46-55" = "46-55 years",
+               "age_category_collapsed56-65" = "56-65 years",
+               "age_category_collapsed66-70" = "66-70 years",
+               "age_category_collapsed71-75" = "71-75 years",
+               "age_category_collapsed76+" = "76+ years",
+               "Ethnicity_collapsedMixed or multiple ethnic origins" = "Mixed or multiple ethnic origins",
+               "Ethnicity_collapsedAsian or Asian British" = "Asian or Asian British",
+               "Ethnicity_collapsedAfrican or African British" = "African or African British",
+               "Ethnicity_collapsedOther" = "Other ethnicity",
+               "key_workerKey worker" = "Key worker",
+               "time_diff_coping_lockdown_march_23" = "Time difference: Lockdown to baseline", 
+             "employment.unemployedUnemployed" = "Unemployed", 
+               "employment.unemployedNot Unemployed" = "Not unemployed"
+             ),
+             "Estimate" = format(
+               round(estimate,
+                     digits = 2),
+               nsmall = 2),
+             "95% CI low" = format(
+               round(conf.low,
+                     digits = 2),
+               nsmall = 2),
+             "95% CI up" = format(
+               round(conf.high,
+                     digits = 2),
+               nsmall = 2),
+             "SE" = format(
+               round(std.error,
+                     digits = 2),
+               nsmall = 2),
+             "z score" = format(
+               round(statistic,
+                     digits = 2),
+               nsmall = 2),
+             "p value" = case_when(
+               p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
+               p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
+               p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
+             )
+           ) %>%
+           select(
+             "Indepent variable",
+             "Estimate",
+             "95% CI low",
+             "95% CI up",
+             "SE",
+             #    "z score",
+             "p value"
+           )
+  )
+
+  return(get(paste0(outcome,".",explan_var,"model1a.explan_estimates")))
+}
+
+model1a.explan.reg.stats <- function(outcome, explan_var, data_set) {
+  # define the variable name of the dependent variable
+  dependent.variable <- outcome
+  # define the independent variables
+  independent.variables <- c("Disorder_hierarchical")
+  # create the formula
+  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
+  glm.formula
+
+  # run the glm
+  assign(paste0(outcome,".",explan_var,".model1a.explan"),
+         lm( formula = glm.formula,
+             data = get(data_set)
+         )
+  )
+
+  assign(paste0(outcome,".",explan_var,"model1a.explan_reg_stats"),
+         glance(get(paste0(outcome,".",explan_var,".model1a.explan"))) %>%
+           mutate(
+             "n" = format(
+               round(nobs,
+                     digits = 0),
+               nsmall = 0),
+             "R2" = format(
+               round(r.squared,
+                     digits = 2),
+               nsmall = 2),
+             "adjust. R2" = format(
+               round(adj.r.squared,
+                     digits = 2),
+               nsmall = 2),
+             "F" = format(
+               round(statistic,
+                     digits = 2),
+               nsmall = 2),
+             "p value" = case_when(
+               p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
+               p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
+               p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
+             )
+           ) %>%
+           select(
+             "n",
+             "R2",
+             "adjust. R2",
+             "F",
+             "p value",
+             "df"
+           )
+  )
+
+  return(get(paste0(outcome,".",explan_var,"model1a.explan_reg_stats")))
+}
+```
+
+```{r model1b.explan employment function}
+model1b.explan.estimates <- function(outcome, explan_var, data_set) {
+  # define the variable name of the dependent variable
+  dependent.variable <- outcome
+  # define the independent variables
+  independent.variables <- c(explan_var,
+                             "depression_and_anxiety",
+                             "eating_disorders",
+                             "obsessive_compulsive_disorders",
+                             "bipolar_and_schizophrenia",
+                             "mhd.posttraumatic_stress_disorder_ptsd",
+                             "autism_spectrum_disorder",
+                             "mhd.attention_deficit_hyperactivity_disorder",
+                             "mhd.personality_disorder",
+                             "Gender_collapsed",
+                             "age_category_collapsed",
+                             "Ethnicity_collapsed",
+                             "key_worker",
+                             "time_diff_coping_lockdown_march_23", 
+                             "employment.unemployed"
+  )
+  # create the formula
+  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
+  glm.formula
+
+  # run the glm
+  assign(paste0(outcome,".",explan_var,".model1b.explan"),
+         lm( formula = glm.formula,
+             data = get(data_set)
+         )
+  )
+
+  assign(paste0(outcome,".",explan_var,"model1b.explan_estimates"),
+         tidy(get(paste0(outcome,".",explan_var,".model1b.explan")), conf.int = TRUE) %>%
+           mutate(
+             "Indepent variable" = recode_factor(
+               term,
+               "(Intercept)" = "Intercept",
+               "anxiety_disordersAnxiety disorder" = "Anxiety disorders",
+               "depressive_disordersDepressive disorder" = "Depressive disorders",
+               "depression_and_anxietyDepressive and anxiety disorder" = "Depressive and anxiety disorder",
+               "depression_and_anxietyOnly depressive disorder" = "Only depressive disorder",
+               "depression_and_anxietyOnly anxiety disorder" = "Only anxiety disorder",
+               "eating_disordersEating disorder" = "Eating disorders",
+               "obsessive_compulsive_disordersObsessive compulsive disorder" = "OCDs",
+               "bipolar_and_schizophreniaPsychotic and bipolar disorder" = "Psychotic and bipolar disorder",
+               "bipolar_and_schizophreniaOnly psychotic disorder" = "Only psychotic disorder",
+               "bipolar_and_schizophreniaOnly bipolar disorder" = "Only bipolar disorder",
+               "psychotic_disordersPsychotic disorder" = "Psychotic disorder",
+               "mhd.mania_hypomania_bipolar_or_manicdepressionMania, hypomania, bipolar or manic-depression" = "Bipolar disorder",
+               "mhd.posttraumatic_stress_disorder_ptsdPost-traumatic stress disorder (PTSD)" = "PTSD",
+               "autism_spectrum_disorderAutism spectrum disorder" = "ASD",
+               "mhd.attention_deficit_hyperactivity_disorderAttention deficit or attention deficit and hyperactivity disorder (ADD/ADHD)" = "ADHD",
+               "mhd.personality_disorderPersonality disorder" = "Personality disorder",
+               "Gender_collapsedFemale" = "Female",
+               "Gender_collapsedNon-binary/Self-defined" = "Non-binary/Self-defined",
+               "age_category_collapsed19-25" = "19-25 years",
+               "age_category_collapsed26-35" = "26-35 years",
+               "age_category_collapsed36-45" = "36-45 years",
+               "age_category_collapsed46-55" = "46-55 years",
+               "age_category_collapsed56-65" = "56-65 years",
+               "age_category_collapsed66-70" = "66-70 years",
+               "age_category_collapsed71-75" = "71-75 years",
+               "age_category_collapsed76+" = "76+ years",
+               "Ethnicity_collapsedMixed or multiple ethnic origins" = "Mixed or multiple ethnic origins",
+               "Ethnicity_collapsedAsian or Asian British" = "Asian or Asian British",
+               "Ethnicity_collapsedAfrican or African British" = "African or African British",
+               "Ethnicity_collapsedOther" = "Other ethnicity",
+               "key_workerKey worker" = "Key worker",
+               "time_diff_coping_lockdown_march_23" = "Time difference: Lockdown to baseline", 
+               "employment.unemployedUnemployed" = "Unemployed", 
+               "employment.unemployedNot Unemployed" = "Not unemployed"
+                            ),
+             "Estimate" = format(
+               round(estimate,
+                     digits = 2),
+               nsmall = 2),
+             "95% CI low" = format(
+               round(conf.low,
+                     digits = 2),
+               nsmall = 2),
+             "95% CI up" = format(
+               round(conf.high,
+                     digits = 2),
+               nsmall = 2),
+             "SE" = format(
+               round(std.error,
+                     digits = 2),
+               nsmall = 2),
+             "z score" = format(
+               round(statistic,
+                     digits = 2),
+               nsmall = 2),
+             "p value" = case_when(
+               p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
+               p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
+               p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
+             )
+           ) %>%
+           select(
+             "Indepent variable",
+             "Estimate",
+             "95% CI low",
+             "95% CI up",
+             "SE",
+             #    "z score",
+             "p value"
+           )
+  )
+
+  return(get(paste0(outcome,".",explan_var,"model1b.explan_estimates")))
+}
+
+model1b.explan.reg.stats <- function(outcome, explan_var, data_set) {
+  # define the variable name of the dependent variable
+  dependent.variable <- outcome
+  # define the independent variables
+  independent.variables <- c("Disorder_hierarchical")
+  # create the formula
+  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
+  glm.formula
+
+  # run the glm
+  assign(paste0(outcome,".",explan_var,".model1b.explan"),
+         lm( formula = glm.formula,
+             data = get(data_set)
+         )
+  )
+
+  assign(paste0(outcome,".",explan_var,"model1b.explan_reg_stats"),
+         glance(get(paste0(outcome,".",explan_var,".model1b.explan"))) %>%
+           mutate(
+             "n" = format(
+               round(nobs,
+                     digits = 0),
+               nsmall = 0),
+             "R2" = format(
+               round(r.squared,
+                     digits = 2),
+               nsmall = 2),
+             "adjust. R2" = format(
+               round(adj.r.squared,
+                     digits = 2),
+               nsmall = 2),
+             "F" = format(
+               round(statistic,
+                     digits = 2),
+               nsmall = 2),
+             "p value" = case_when(
+               p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
+               p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
+               p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
+             )
+           ) %>%
+           select(
+             "n",
+             "R2",
+             "adjust. R2",
+             "F",
+             "p value",
+             "df"
+           )
+  )
+
+  return(get(paste0(outcome,".",explan_var,"model1b.explan_reg_stats")))
+}
+```
+
+# GAD prepan
+## Regression: Change scores
+### Model 0a: Disorder_hierarchical, Unadjusted
+```{r gad model0a diff_score w/employment prepan}
+# Regression coefficients
+gad_prepan_model0a_estimates <- model0a.estimates(outcome = "gad.diff_score_base_prepan",
+                  data_set = "dat.prepan")
+kable(gad_prepan_model0a_estimates)
+gad_prepan_model0a_estimates
+
+# Regression diagnostic statistics
+gad_prepan_model0a_reg_stats <- model0a.reg.stats(outcome = "gad.diff_score_base_prepan",
+                  data_set = "dat.prepan")
+kable(gad_prepan_model0a_reg_stats)
+gad_prepan_model0a_reg_stats
+```
+
+### Model 0b: Overlapping disorders, Unadjusted
+```{r gad model0b diff_score w/employment prepan}
+# Regression coefficients
+gad_prepan_model0b_estimates <- model0b.estimates(outcome = "gad.diff_score_base_prepan",
+                  data_set = "dat.prepan")
+kable(gad_prepan_model0b_estimates)
+gad_prepan_model0b_estimates
+
+# Regression diagnostic statistics
+gad_prepan_model0b_reg_stats <- model0b.reg.stats(outcome = "gad.diff_score_base_prepan",
+                  data_set = "dat.prepan")
+kable(gad_prepan_model0b_reg_stats)
+gad_prepan_model0b_reg_stats
+```
+
+### Model 1a: Disorder hierarchical, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r gad model1a diff_score w/employment prepan}
+# Regression coefficients
+gad_prepan_model1a_estimates <- model1a.estimates(outcome = "gad.diff_score_base_prepan",
+                  data_set = "dat.prepan")
+kable(gad_prepan_model1a_estimates)
+gad_prepan_model1a_estimates
+
+# Regression diagnostic statistics
+gad_prepan_model1a_reg_stats <- model1a.reg.stats(outcome = "gad.diff_score_base_prepan",
+                  data_set = "dat.prepan")
+kable(gad_prepan_model1a_reg_stats)
+gad_prepan_model1a_reg_stats
+```
+
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r gad model1b diff_score w/employment prepan}
+# Regression coefficients
+gad_prepan_model1b_estimates <- model1b.estimates(outcome = "gad.diff_score_base_prepan",
+                  data_set = "dat.prepan")
+kable(gad_prepan_model1b_estimates)
+gad_prepan_model1b_estimates
+
+# Regression diagnostic statistics
+gad_prepan_model1b_reg_stats <- model1b.reg.stats(outcome = "gad.diff_score_base_prepan",
+                  data_set = "dat.prepan")
+kable(gad_prepan_model1b_reg_stats)
+gad_prepan_model1b_reg_stats
+```
+
+## Regression: Absolute scores
+### Model 0a: Disorder_hierarchical, Unadjusted
+```{r gad model0a sum_score w/employment prepan}
+# Regression coefficients
+gad_prepan_model0a_explan_estimates <- model0a.explan.estimates(outcome = "gad.sum_score_base",
+                         explan_var = "gad.sum_score_prepan",
+                         data_set = "dat.prepan")
+kable(gad_prepan_model0a_explan_estimates)
+gad_prepan_model0a_explan_estimates
+
+# Regression diagnostic statistics
+gad_prepan_model0a_explan_reg_stats <- model0a.explan.reg.stats(outcome = "gad.sum_score_base",
+                         explan_var = "gad.sum_score_prepan",
+                         data_set = "dat.prepan")
+kable(gad_prepan_model0a_explan_reg_stats)
+gad_prepan_model0a_explan_reg_stats
+```
+
+### Model 0b: Overlapping disorders, Unadjusted
+```{r gad model0b sum_score w/employment prepan}
+# Regression coefficients
+gad_prepan_model0b_explan_estimates <- model0b.explan.estimates(outcome = "gad.sum_score_base",
+                         explan_var = "gad.sum_score_prepan",
+                         data_set = "dat.prepan")
+kable(gad_prepan_model0b_explan_estimates)
+gad_prepan_model0b_explan_estimates
+
+# Regression diagnostic statistics
+gad_prepan_model0b_explan_reg_stats <- model0b.explan.reg.stats(outcome = "gad.sum_score_base",
+                         explan_var = "gad.sum_score_prepan",
+                         data_set = "dat.prepan")
+kable(gad_prepan_model0b_explan_reg_stats)
+gad_prepan_model0b_explan_reg_stats
+```
+
+### Model 1a: Disorder hierarchical, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r gad model1a sum_score w/employment prepan}
+# Regression coefficients
+gad_prepan_model1a_explan_estimates <- model1a.explan.estimates(outcome = "gad.sum_score_base",
+                         explan_var = "gad.sum_score_prepan",
+                         data_set = "dat.prepan")
+kable(gad_prepan_model1a_explan_estimates)
+gad_prepan_model1a_explan_estimates
+
+# Regression diagnostic statistics
+gad_prepan_model1a_explan_reg_stats <- model1a.explan.reg.stats(outcome = "gad.sum_score_base",
+                         explan_var = "gad.sum_score_prepan",
+                         data_set = "dat.prepan")
+kable(gad_prepan_model1a_explan_reg_stats)
+gad_prepan_model1a_explan_reg_stats
+```
+
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r gad model1b sum_score w/employment prepan}
+# Regression coefficients
+gad_prepan_model1b_explan_estimates <- model1b.explan.estimates(outcome = "gad.sum_score_base",
+                         explan_var = "gad.sum_score_prepan",
+                         data_set = "dat.prepan")
+kable(gad_prepan_model1b_explan_estimates)
+gad_prepan_model1b_explan_estimates
+
+# Regression diagnostic statistics
+gad_prepan_model1b_explan_reg_stats <- model1b.explan.reg.stats(outcome = "gad.sum_score_base",
+                         explan_var = "gad.sum_score_prepan",
+                         data_set = "dat.prepan")
+kable(gad_prepan_model1b_explan_reg_stats)
+gad_prepan_model1b_explan_reg_stats
+```
+
+# GAD retro
+## Regression: Change scores
+### Model 0a: Disorder_hierarchical, Unadjusted
+```{r gad model0a diff_score w/employment retro}
+# Regression coefficients
+gad_retro_model0a_estimates <- model0a.estimates(outcome = "gad.diff_score_base_retro",
+                                                 data_set = "dat.retro")
+kable(gad_retro_model0a_estimates)
+gad_retro_model0a_estimates
+
+# Regression diagnostic statistics
+gad_retro_model0a_reg_stats <- model0a.reg.stats(outcome = "gad.diff_score_base_retro",
+                                                 data_set = "dat.retro")
+kable(gad_retro_model0a_reg_stats)
+gad_retro_model0a_reg_stats
+```
+
+### Model 0b: Overlapping disorders, Unadjusted
+```{r gad model0b diff_score w/employment retro}
+# Regression coefficients
+gad_retro_model0b_estimates <- model0b.estimates(outcome = "gad.diff_score_base_retro",
+                                                 data_set = "dat.retro")
+kable(gad_retro_model0b_estimates)
+gad_retro_model0b_estimates
+
+# Regression diagnostic statistics
+gad_retro_model0b_reg_stats <- model0b.reg.stats(outcome = "gad.diff_score_base_retro",
+                                                 data_set = "dat.retro")
+kable(gad_retro_model0b_reg_stats)
+gad_retro_model0b_reg_stats
+```
+
+### Model 1a: Disorder hierarchical, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r gad model1a diff_score w/employment retro}
+# Regression coefficients
+gad_retro_model1a_estimates <- model1a.estimates(outcome = "gad.diff_score_base_retro",
+                                                 data_set = "dat.retro")
+kable(gad_retro_model1a_estimates)
+gad_retro_model1a_estimates
+
+# Regression diagnostic statistics
+gad_retro_model1a_reg_stats <- model1a.reg.stats(outcome = "gad.diff_score_base_retro",
+                                                 data_set = "dat.retro")
+kable(gad_retro_model1a_reg_stats)
+gad_retro_model1a_reg_stats
+```
+
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r gad model1b diff_score w/employment retro}
+# Regression coefficients
+gad_retro_model1b_estimates <- model1b.estimates(outcome = "gad.diff_score_base_retro",
+                                                 data_set = "dat.retro")
+kable(gad_retro_model1b_estimates)
+gad_retro_model1b_estimates
+
+# Regression diagnostic statistics
+gad_retro_model1b_reg_stats <- model1b.reg.stats(outcome = "gad.diff_score_base_retro",
+                                                 data_set = "dat.retro")
+kable(gad_retro_model1b_reg_stats)
+gad_retro_model1b_reg_stats
+```
+
+## Regression: Absolute scores
+### Model 0a: Disorder_hierarchical, Unadjusted
+```{r gad model0a sum_score w/employment retro}
+# Regression coefficients
+gad_retro_model0a_explan_estimates <- model0a.explan.estimates(outcome = "gad.sum_score_base",
+                                                               explan_var = "gad.sum_score_retro",
+                                                               data_set = "dat.retro")
+kable(gad_retro_model0a_explan_estimates)
+gad_retro_model0a_explan_estimates
+
+# Regression diagnostic statistics
+gad_retro_model0a_explan_reg_stats <- model0a.explan.reg.stats(outcome = "gad.sum_score_base",
+                                                               explan_var = "gad.sum_score_retro",
+                                                               data_set = "dat.retro")
+kable(gad_retro_model0a_explan_reg_stats)
+gad_retro_model0a_explan_reg_stats
+```
+
+### Model 0b: Overlapping disorders, Unadjusted
+```{r gad model0b sum_score w/employment retro}
+# Regression coefficients
+gad_retro_model0b_explan_estimates <- model0b.explan.estimates(outcome = "gad.sum_score_base",
+                                                               explan_var = "gad.sum_score_retro",
+                                                               data_set = "dat.retro")
+kable(gad_retro_model0b_explan_estimates)
+gad_retro_model0b_explan_estimates
+
+# Regression diagnostic statistics
+gad_retro_model0b_explan_reg_stats <- model0b.explan.reg.stats(outcome = "gad.sum_score_base",
+                                                               explan_var = "gad.sum_score_retro",
+                                                               data_set = "dat.retro")
+kable(gad_retro_model0b_explan_reg_stats)
+gad_retro_model0b_explan_reg_stats
+```
+
+### Model 1a: Disorder hierarchical, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r gad model1a sum_score w/employment retro}
+# Regression coefficients
+gad_retro_model1a_explan_estimates <- model1a.explan.estimates(outcome = "gad.sum_score_base",
+                                                               explan_var = "gad.sum_score_retro",
+                                                               data_set = "dat.retro")
+kable(gad_retro_model1a_explan_estimates)
+gad_retro_model1a_explan_estimates
+
+# Regression diagnostic statistics
+gad_retro_model1a_explan_reg_stats <- model1a.explan.reg.stats(outcome = "gad.sum_score_base",
+                                                               explan_var = "gad.sum_score_retro",
+                                                               data_set = "dat.retro")
+kable(gad_retro_model1a_explan_reg_stats)
+gad_retro_model1a_explan_reg_stats
+```
+
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r gad model1b sum_score w/employment retro}
+# Regression coefficients
+gad_retro_model1b_explan_estimates <- model1b.explan.estimates(outcome = "gad.sum_score_base",
+                                                               explan_var = "gad.sum_score_retro",
+                                                               data_set = "dat.retro")
+kable(gad_retro_model1b_explan_estimates)
+gad_retro_model1b_explan_estimates
+
+# Regression diagnostic statistics
+gad_retro_model1b_explan_reg_stats <- model1b.explan.reg.stats(outcome = "gad.sum_score_base",
+                                                               explan_var = "gad.sum_score_retro",
+                                                               data_set = "dat.retro")
+kable(gad_retro_model1b_explan_reg_stats)
+gad_retro_model1b_explan_reg_stats
+```
+# PHQ prepan
+## Regression: Change scores
+### Model 0a: Disorder_hierarchical, Unadjusted
+```{r phq model0a diff_score w/employment prepan}
+# Regression coefficients
+phq_prepan_model0a_estimates <- model0a.estimates(outcome = "phq.diff_score_base_prepan",
+                  data_set = "dat.prepan")
+kable(phq_prepan_model0a_estimates)
+phq_prepan_model0a_estimates
+
+# Regression diagnostic statistics
+phq_prepan_model0a_reg_stats <- model0a.reg.stats(outcome = "phq.diff_score_base_prepan",
+                  data_set = "dat.prepan")
+kable(phq_prepan_model0a_reg_stats)
+phq_prepan_model0a_reg_stats
+```
+
+### Model 0b: Overlapping disorders, Unadjusted
+```{r phq model0b diff_score w/employment prepan}
+# Regression coefficients
+phq_prepan_model0b_estimates <- model0b.estimates(outcome = "phq.diff_score_base_prepan",
+                  data_set = "dat.prepan")
+kable(phq_prepan_model0b_estimates)
+phq_prepan_model0b_estimates
+
+# Regression diagnostic statistics
+phq_prepan_model0b_reg_stats <- model0b.reg.stats(outcome = "phq.diff_score_base_prepan",
+                  data_set = "dat.prepan")
+kable(phq_prepan_model0b_reg_stats)
+phq_prepan_model0b_reg_stats
+```
+
+### Model 1a: Disorder hierarchical, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r phq model1a diff_score w/employment prepan}
+# Regression coefficients
+phq_prepan_model1a_estimates <- model1a.estimates(outcome = "phq.diff_score_base_prepan",
+                  data_set = "dat.prepan")
+kable(phq_prepan_model1a_estimates)
+phq_prepan_model1a_estimates
+
+# Regression diagnostic statistics
+phq_prepan_model1a_reg_stats <- model1a.reg.stats(outcome = "phq.diff_score_base_prepan",
+                  data_set = "dat.prepan")
+kable(phq_prepan_model1a_reg_stats)
+phq_prepan_model1a_reg_stats
+```
+
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r phq model1b diff_score w/employment prepan}
+# Regression coefficients
+phq_prepan_model1b_estimates <- model1b.estimates(outcome = "phq.diff_score_base_prepan",
+                  data_set = "dat.prepan")
+kable(phq_prepan_model1b_estimates)
+phq_prepan_model1b_estimates
+
+# Regression diagnostic statistics
+phq_prepan_model1b_reg_stats <- model1b.reg.stats(outcome = "phq.diff_score_base_prepan",
+                  data_set = "dat.prepan")
+kable(phq_prepan_model1b_reg_stats)
+phq_prepan_model1b_reg_stats
+```
+
+## Regression: Absolute scores
+### Model 0a: Disorder_hierarchical, Unadjusted
+```{r phq model0a sum_score w/employment prepan}
+# Regression coefficients
+phq_prepan_model0a_explan_estimates <- model0a.explan.estimates(outcome = "phq.sum_score_base",
+                         explan_var = "phq.sum_score_prepan",
+                         data_set = "dat.prepan")
+kable(phq_prepan_model0a_explan_estimates)
+phq_prepan_model0a_explan_estimates
+
+# Regression diagnostic statistics
+phq_prepan_model0a_explan_reg_stats <- model0a.explan.reg.stats(outcome = "phq.sum_score_base",
+                         explan_var = "phq.sum_score_prepan",
+                         data_set = "dat.prepan")
+kable(phq_prepan_model0a_explan_reg_stats)
+phq_prepan_model0a_explan_reg_stats
+```
+
+### Model 0b: Overlapping disorders, Unadjusted
+```{r phq model0b sum_score w/employment prepan}
+# Regression coefficients
+phq_prepan_model0b_explan_estimates <- model0b.explan.estimates(outcome = "phq.sum_score_base",
+                         explan_var = "phq.sum_score_prepan",
+                         data_set = "dat.prepan")
+kable(phq_prepan_model0b_explan_estimates)
+phq_prepan_model0b_explan_estimates
+
+# Regression diagnostic statistics
+phq_prepan_model0b_explan_reg_stats <- model0b.explan.reg.stats(outcome = "phq.sum_score_base",
+                         explan_var = "phq.sum_score_prepan",
+                         data_set = "dat.prepan")
+kable(phq_prepan_model0b_explan_reg_stats)
+phq_prepan_model0b_explan_reg_stats
+```
+
+### Model 1a: Disorder hierarchical, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r phq model1a sum_score w/employment prepan}
+# Regression coefficients
+phq_prepan_model1a_explan_estimates <- model1a.explan.estimates(outcome = "phq.sum_score_base",
+                         explan_var = "phq.sum_score_prepan",
+                         data_set = "dat.prepan")
+kable(phq_prepan_model1a_explan_estimates)
+phq_prepan_model1a_explan_estimates
+
+# Regression diagnostic statistics
+phq_prepan_model1a_explan_reg_stats <- model1a.explan.reg.stats(outcome = "phq.sum_score_base",
+                         explan_var = "phq.sum_score_prepan",
+                         data_set = "dat.prepan")
+kable(phq_prepan_model1a_explan_reg_stats)
+phq_prepan_model1a_explan_reg_stats
+```
+
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r phq model1b sum_score w/employment prepan}
+# Regression coefficients
+phq_prepan_model1b_explan_estimates <- model1b.explan.estimates(outcome = "phq.sum_score_base",
+                         explan_var = "phq.sum_score_prepan",
+                         data_set = "dat.prepan")
+kable(phq_prepan_model1b_explan_estimates)
+phq_prepan_model1b_explan_estimates
+
+# Regression diagnostic statistics
+phq_prepan_model1b_explan_reg_stats <- model1b.explan.reg.stats(outcome = "phq.sum_score_base",
+                         explan_var = "phq.sum_score_prepan",
+                         data_set = "dat.prepan")
+kable(phq_prepan_model1b_explan_reg_stats)
+phq_prepan_model1b_explan_reg_stats
+```
+
+# PHQ retro
+## Regression: Change scores
+### Model 0a: Disorder_hierarchical, Unadjusted
+```{r phq model0a diff_score w/employment retro}
+# Regression coefficients
+phq_retro_model0a_estimates <- model0a.estimates(outcome = "phq.diff_score_base_retro",
+                                                 data_set = "dat.retro")
+kable(phq_retro_model0a_estimates)
+phq_retro_model0a_estimates
+
+# Regression diagnostic statistics
+phq_retro_model0a_reg_stats <- model0a.reg.stats(outcome = "phq.diff_score_base_retro",
+                                                 data_set = "dat.retro")
+kable(phq_retro_model0a_reg_stats)
+phq_retro_model0a_reg_stats
+```
+
+### Model 0b: Overlapping disorders, Unadjusted
+```{r phq model0b diff_score w/employment retro}
+# Regression coefficients
+phq_retro_model0b_estimates <- model0b.estimates(outcome = "phq.diff_score_base_retro",
+                                                 data_set = "dat.retro")
+kable(phq_retro_model0b_estimates)
+phq_retro_model0b_estimates
+
+# Regression diagnostic statistics
+phq_retro_model0b_reg_stats <- model0b.reg.stats(outcome = "phq.diff_score_base_retro",
+                                                 data_set = "dat.retro")
+kable(phq_retro_model0b_reg_stats)
+phq_retro_model0b_reg_stats
+```
+
+### Model 1a: Disorder hierarchical, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r phq model1a diff_score w/employment retro}
+# Regression coefficients
+phq_retro_model1a_estimates <- model1a.estimates(outcome = "phq.diff_score_base_retro",
+                                                 data_set = "dat.retro")
+kable(phq_retro_model1a_estimates)
+phq_retro_model1a_estimates
+
+# Regression diagnostic statistics
+phq_retro_model1a_reg_stats <- model1a.reg.stats(outcome = "phq.diff_score_base_retro",
+                                                 data_set = "dat.retro")
+kable(phq_retro_model1a_reg_stats)
+phq_retro_model1a_reg_stats
+```
+
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r phq model1b diff_score w/employment retro}
+# Regression coefficients
+phq_retro_model1b_estimates <- model1b.estimates(outcome = "phq.diff_score_base_retro",
+                                                 data_set = "dat.retro")
+kable(phq_retro_model1b_estimates)
+phq_retro_model1b_estimates
+
+# Regression diagnostic statistics
+phq_retro_model1b_reg_stats <- model1b.reg.stats(outcome = "phq.diff_score_base_retro",
+                                                 data_set = "dat.retro")
+kable(phq_retro_model1b_reg_stats)
+phq_retro_model1b_reg_stats
+```
+
+## Regression: Absolute scores
+### Model 0a: Disorder_hierarchical, Unadjusted
+```{r phq model0a sum_score w/employment retro}
+# Regression coefficients
+phq_retro_model0a_explan_estimates <- model0a.explan.estimates(outcome = "phq.sum_score_base",
+                                                               explan_var = "phq.sum_score_retro",
+                                                               data_set = "dat.retro")
+kable(phq_retro_model0a_explan_estimates)
+phq_retro_model0a_explan_estimates
+
+# Regression diagnostic statistics
+phq_retro_model0a_explan_reg_stats <- model0a.explan.reg.stats(outcome = "phq.sum_score_base",
+                                                               explan_var = "phq.sum_score_retro",
+                                                               data_set = "dat.retro")
+kable(phq_retro_model0a_explan_reg_stats)
+phq_retro_model0a_explan_reg_stats
+```
+
+### Model 0b: Overlapping disorders, Unadjusted
+```{r phq model0b sum_score w/employment retro}
+# Regression coefficients
+phq_retro_model0b_explan_estimates <- model0b.explan.estimates(outcome = "phq.sum_score_base",
+                                                               explan_var = "phq.sum_score_retro",
+                                                               data_set = "dat.retro")
+kable(phq_retro_model0b_explan_estimates)
+phq_retro_model0b_explan_estimates
+
+# Regression diagnostic statistics
+phq_retro_model0b_explan_reg_stats <- model0b.explan.reg.stats(outcome = "phq.sum_score_base",
+                                                               explan_var = "phq.sum_score_retro",
+                                                               data_set = "dat.retro")
+kable(phq_retro_model0b_explan_reg_stats)
+phq_retro_model0b_explan_reg_stats
+```
+
+### Model 1a: Disorder hierarchical, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r phq model1a sum_score w/employment retro}
+# Regression coefficients
+phq_retro_model1a_explan_estimates <- model1a.explan.estimates(outcome = "phq.sum_score_base",
+                                                               explan_var = "phq.sum_score_retro",
+                                                               data_set = "dat.retro")
+kable(phq_retro_model1a_explan_estimates)
+phq_retro_model1a_explan_estimates
+
+# Regression diagnostic statistics
+phq_retro_model1a_explan_reg_stats <- model1a.explan.reg.stats(outcome = "phq.sum_score_base",
+                                                               explan_var = "phq.sum_score_retro",
+                                                               data_set = "dat.retro")
+kable(phq_retro_model1a_explan_reg_stats)
+phq_retro_model1a_explan_reg_stats
+```
+
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r phq model1b sum_score w/employment retro}
+# Regression coefficients
+phq_retro_model1b_explan_estimates <- model1b.explan.estimates(outcome = "phq.sum_score_base",
+                                                               explan_var = "phq.sum_score_retro",
+                                                               data_set = "dat.retro")
+kable(phq_retro_model1b_explan_estimates)
+phq_retro_model1b_explan_estimates
+
+# Regression diagnostic statistics
+phq_retro_model1b_explan_reg_stats <- model1b.explan.reg.stats(outcome = "phq.sum_score_base",
+                                                               explan_var = "phq.sum_score_retro",
+                                                               data_set = "dat.retro")
+kable(phq_retro_model1b_explan_reg_stats)
+phq_retro_model1b_explan_reg_stats
+```
+
+# OCIR prepan
+## Regression: Change scores
+### Model 0a: Disorder_hierarchical, Unadjusted
+```{r ocir model0a diff_score w/employment prepan}
+# Regression coefficients
+ocir_prepan_model0a_estimates <- model0a.estimates(outcome = "ocir.diff_score_base_prepan",
+                  data_set = "dat.prepan")
+kable(ocir_prepan_model0a_estimates)
+ocir_prepan_model0a_estimates
+
+# Regression diagnostic statistics
+ocir_prepan_model0a_reg_stats <- model0a.reg.stats(outcome = "ocir.diff_score_base_prepan",
+                  data_set = "dat.prepan")
+kable(ocir_prepan_model0a_reg_stats)
+ocir_prepan_model0a_reg_stats
+```
+
+### Model 0b: Overlapping disorders, Unadjusted
+```{r ocir model0b diff_score w/employment prepan}
+# Regression coefficients
+ocir_prepan_model0b_estimates <- model0b.estimates(outcome = "ocir.diff_score_base_prepan",
+                  data_set = "dat.prepan")
+kable(ocir_prepan_model0b_estimates)
+ocir_prepan_model0b_estimates
+
+# Regression diagnostic statistics
+ocir_prepan_model0b_reg_stats <- model0b.reg.stats(outcome = "ocir.diff_score_base_prepan",
+                  data_set = "dat.prepan")
+kable(ocir_prepan_model0b_reg_stats)
+ocir_prepan_model0b_reg_stats
+```
+
+### Model 1a: Disorder hierarchical, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r ocir model1a diff_score w/employment prepan}
+# Regression coefficients
+ocir_prepan_model1a_estimates <- model1a.estimates(outcome = "ocir.diff_score_base_prepan",
+                  data_set = "dat.prepan")
+kable(ocir_prepan_model1a_estimates)
+ocir_prepan_model1a_estimates
+
+# Regression diagnostic statistics
+ocir_prepan_model1a_reg_stats <- model1a.reg.stats(outcome = "ocir.diff_score_base_prepan",
+                  data_set = "dat.prepan")
+kable(ocir_prepan_model1a_reg_stats)
+ocir_prepan_model1a_reg_stats
+```
+
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r ocir model1b diff_score w/employment prepan}
+# Regression coefficients
+ocir_prepan_model1b_estimates <- model1b.estimates(outcome = "ocir.diff_score_base_prepan",
+                  data_set = "dat.prepan")
+kable(ocir_prepan_model1b_estimates)
+ocir_prepan_model1b_estimates
+
+# Regression diagnostic statistics
+ocir_prepan_model1b_reg_stats <- model1b.reg.stats(outcome = "ocir.diff_score_base_prepan",
+                  data_set = "dat.prepan")
+kable(ocir_prepan_model1b_reg_stats)
+ocir_prepan_model1b_reg_stats
+```
+
+## Regression: Absolute scores
+### Model 0a: Disorder_hierarchical, Unadjusted
+```{r ocir model0a sum_score w/employment prepan}
+# Regression coefficients
+ocir_prepan_model0a_explan_estimates <- model0a.explan.estimates(outcome = "ocir.sum_score_base",
+                         explan_var = "ocir.sum_score_prepan",
+                         data_set = "dat.prepan")
+kable(ocir_prepan_model0a_explan_estimates)
+ocir_prepan_model0a_explan_estimates
+
+# Regression diagnostic statistics
+ocir_prepan_model0a_explan_reg_stats <- model0a.explan.reg.stats(outcome = "ocir.sum_score_base",
+                         explan_var = "ocir.sum_score_prepan",
+                         data_set = "dat.prepan")
+kable(ocir_prepan_model0a_explan_reg_stats)
+ocir_prepan_model0a_explan_reg_stats
+```
+
+### Model 0b: Overlapping disorders, Unadjusted
+```{r ocir model0b sum_score w/employment prepan}
+# Regression coefficients
+ocir_prepan_model0b_explan_estimates <- model0b.explan.estimates(outcome = "ocir.sum_score_base",
+                         explan_var = "ocir.sum_score_prepan",
+                         data_set = "dat.prepan")
+kable(ocir_prepan_model0b_explan_estimates)
+ocir_prepan_model0b_explan_estimates
+
+# Regression diagnostic statistics
+ocir_prepan_model0b_explan_reg_stats <- model0b.explan.reg.stats(outcome = "ocir.sum_score_base",
+                         explan_var = "ocir.sum_score_prepan",
+                         data_set = "dat.prepan")
+kable(ocir_prepan_model0b_explan_reg_stats)
+ocir_prepan_model0b_explan_reg_stats
+```
+
+### Model 1a: Disorder hierarchical, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r ocir model1a sum_score w/employment prepan}
+# Regression coefficients
+ocir_prepan_model1a_explan_estimates <- model1a.explan.estimates(outcome = "ocir.sum_score_base",
+                         explan_var = "ocir.sum_score_prepan",
+                         data_set = "dat.prepan")
+kable(ocir_prepan_model1a_explan_estimates)
+ocir_prepan_model1a_explan_estimates
+
+# Regression diagnostic statistics
+ocir_prepan_model1a_explan_reg_stats <- model1a.explan.reg.stats(outcome = "ocir.sum_score_base",
+                         explan_var = "ocir.sum_score_prepan",
+                         data_set = "dat.prepan")
+kable(ocir_prepan_model1a_explan_reg_stats)
+ocir_prepan_model1a_explan_reg_stats
+```
+
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r ocir model1b sum_score w/employment prepan}
+# Regression coefficients
+ocir_prepan_model1b_explan_estimates <- model1b.explan.estimates(outcome = "ocir.sum_score_base",
+                         explan_var = "ocir.sum_score_prepan",
+                         data_set = "dat.prepan")
+kable(ocir_prepan_model1b_explan_estimates)
+ocir_prepan_model1b_explan_estimates
+
+# Regression diagnostic statistics
+ocir_prepan_model1b_explan_reg_stats <- model1b.explan.reg.stats(outcome = "ocir.sum_score_base",
+                         explan_var = "ocir.sum_score_prepan",
+                         data_set = "dat.prepan")
+kable(ocir_prepan_model1b_explan_reg_stats)
+ocir_prepan_model1b_explan_reg_stats
+```
+
+# OCIR retro
+## Regression: Change scores
+### Model 0a: Disorder_hierarchical, Unadjusted
+```{r ocir model0a diff_score w/employment retro}
+# Regression coefficients
+ocir_retro_model0a_estimates <- model0a.estimates(outcome = "ocir.diff_score_base_retro",
+                                                 data_set = "dat.retro")
+kable(ocir_retro_model0a_estimates)
+ocir_retro_model0a_estimates
+
+# Regression diagnostic statistics
+ocir_retro_model0a_reg_stats <- model0a.reg.stats(outcome = "ocir.diff_score_base_retro",
+                                                 data_set = "dat.retro")
+kable(ocir_retro_model0a_reg_stats)
+ocir_retro_model0a_reg_stats
+```
+
+### Model 0b: Overlapping disorders, Unadjusted
+```{r ocir model0b diff_score w/employment retro}
+# Regression coefficients
+ocir_retro_model0b_estimates <- model0b.estimates(outcome = "ocir.diff_score_base_retro",
+                                                 data_set = "dat.retro")
+kable(ocir_retro_model0b_estimates)
+ocir_retro_model0b_estimates
+
+# Regression diagnostic statistics
+ocir_retro_model0b_reg_stats <- model0b.reg.stats(outcome = "ocir.diff_score_base_retro",
+                                                 data_set = "dat.retro")
+kable(ocir_retro_model0b_reg_stats)
+ocir_retro_model0b_reg_stats
+```
+
+### Model 1a: Disorder hierarchical, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r ocir model1a diff_score w/employment retro}
+# Regression coefficients
+ocir_retro_model1a_estimates <- model1a.estimates(outcome = "ocir.diff_score_base_retro",
+                                                 data_set = "dat.retro")
+kable(ocir_retro_model1a_estimates)
+ocir_retro_model1a_estimates
+
+# Regression diagnostic statistics
+ocir_retro_model1a_reg_stats <- model1a.reg.stats(outcome = "ocir.diff_score_base_retro",
+                                                 data_set = "dat.retro")
+kable(ocir_retro_model1a_reg_stats)
+ocir_retro_model1a_reg_stats
+```
+
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r ocir model1b diff_score w/employment retro}
+# Regression coefficients
+ocir_retro_model1b_estimates <- model1b.estimates(outcome = "ocir.diff_score_base_retro",
+                                                 data_set = "dat.retro")
+kable(ocir_retro_model1b_estimates)
+ocir_retro_model1b_estimates
+
+# Regression diagnostic statistics
+ocir_retro_model1b_reg_stats <- model1b.reg.stats(outcome = "ocir.diff_score_base_retro",
+                                                 data_set = "dat.retro")
+kable(ocir_retro_model1b_reg_stats)
+ocir_retro_model1b_reg_stats
+```
+
+## Regression: Absolute scores
+### Model 0a: Disorder_hierarchical, Unadjusted
+```{r ocir model0a sum_score w/employment retro}
+# Regression coefficients
+ocir_retro_model0a_explan_estimates <- model0a.explan.estimates(outcome = "ocir.sum_score_base",
+                                                               explan_var = "ocir.sum_score_retro",
+                                                               data_set = "dat.retro")
+kable(ocir_retro_model0a_explan_estimates)
+ocir_retro_model0a_explan_estimates
+
+# Regression diagnostic statistics
+ocir_retro_model0a_explan_reg_stats <- model0a.explan.reg.stats(outcome = "ocir.sum_score_base",
+                                                               explan_var = "ocir.sum_score_retro",
+                                                               data_set = "dat.retro")
+kable(ocir_retro_model0a_explan_reg_stats)
+ocir_retro_model0a_explan_reg_stats
+```
+
+### Model 0b: Overlapping disorders, Unadjusted
+```{r ocir model0b sum_score w/employment retro}
+# Regression coefficients
+ocir_retro_model0b_explan_estimates <- model0b.explan.estimates(outcome = "ocir.sum_score_base",
+                                                               explan_var = "ocir.sum_score_retro",
+                                                               data_set = "dat.retro")
+kable(ocir_retro_model0b_explan_estimates)
+ocir_retro_model0b_explan_estimates
+
+# Regression diagnostic statistics
+ocir_retro_model0b_explan_reg_stats <- model0b.explan.reg.stats(outcome = "ocir.sum_score_base",
+                                                               explan_var = "ocir.sum_score_retro",
+                                                               data_set = "dat.retro")
+kable(ocir_retro_model0b_explan_reg_stats)
+ocir_retro_model0b_explan_reg_stats
+```
+
+### Model 1a: Disorder hierarchical, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r ocir model1a sum_score w/employment retro}
+# Regression coefficients
+ocir_retro_model1a_explan_estimates <- model1a.explan.estimates(outcome = "ocir.sum_score_base",
+                                                               explan_var = "ocir.sum_score_retro",
+                                                               data_set = "dat.retro")
+kable(ocir_retro_model1a_explan_estimates)
+ocir_retro_model1a_explan_estimates
+
+# Regression diagnostic statistics
+ocir_retro_model1a_explan_reg_stats <- model1a.explan.reg.stats(outcome = "ocir.sum_score_base",
+                                                               explan_var = "ocir.sum_score_retro",
+                                                               data_set = "dat.retro")
+kable(ocir_retro_model1a_explan_reg_stats)
+ocir_retro_model1a_explan_reg_stats
+```
+
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r ocir model1b sum_score w/employment retro}
+# Regression coefficients
+ocir_retro_model1b_explan_estimates <- model1b.explan.estimates(outcome = "ocir.sum_score_base",
+                                                               explan_var = "ocir.sum_score_retro",
+                                                               data_set = "dat.retro")
+kable(ocir_retro_model1b_explan_estimates)
+ocir_retro_model1b_explan_estimates
+
+# Regression diagnostic statistics
+ocir_retro_model1b_explan_reg_stats <- model1b.explan.reg.stats(outcome = "ocir.sum_score_base",
+                                                               explan_var = "ocir.sum_score_retro",
+                                                               data_set = "dat.retro")
+kable(ocir_retro_model1b_explan_reg_stats)
+ocir_retro_model1b_explan_reg_stats
+```
+
+# PCL prepan
+## Regression: Change scores
+### Model 0a: Disorder_hierarchical, Unadjusted
+```{r pcl model0a diff_score w/employment prepan}
+# Regression coefficients
+pcl_prepan_model0a_estimates <- model0a.estimates(outcome = "pcl.diff_score_base_prepan",
+                  data_set = "dat.prepan")
+kable(pcl_prepan_model0a_estimates)
+pcl_prepan_model0a_estimates
+
+# Regression diagnostic statistics
+pcl_prepan_model0a_reg_stats <- model0a.reg.stats(outcome = "pcl.diff_score_base_prepan",
+                  data_set = "dat.prepan")
+kable(pcl_prepan_model0a_reg_stats)
+pcl_prepan_model0a_reg_stats
+```
+
+### Model 0b: Overlapping disorders, Unadjusted
+```{r pcl model0b diff_score w/employment prepan}
+# Regression coefficients
+pcl_prepan_model0b_estimates <- model0b.estimates(outcome = "pcl.diff_score_base_prepan",
+                  data_set = "dat.prepan")
+kable(pcl_prepan_model0b_estimates)
+pcl_prepan_model0b_estimates
+
+# Regression diagnostic statistics
+pcl_prepan_model0b_reg_stats <- model0b.reg.stats(outcome = "pcl.diff_score_base_prepan",
+                  data_set = "dat.prepan")
+kable(pcl_prepan_model0b_reg_stats)
+pcl_prepan_model0b_reg_stats
+```
+
+### Model 1a: Disorder hierarchical, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r pcl model1a diff_score w/employment prepan}
+# Regression coefficients
+pcl_prepan_model1a_estimates <- model1a.estimates(outcome = "pcl.diff_score_base_prepan",
+                  data_set = "dat.prepan")
+kable(pcl_prepan_model1a_estimates)
+pcl_prepan_model1a_estimates
+
+# Regression diagnostic statistics
+pcl_prepan_model1a_reg_stats <- model1a.reg.stats(outcome = "pcl.diff_score_base_prepan",
+                  data_set = "dat.prepan")
+kable(pcl_prepan_model1a_reg_stats)
+pcl_prepan_model1a_reg_stats
+```
+
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r pcl model1b diff_score w/employment prepan}
+# Regression coefficients
+pcl_prepan_model1b_estimates <- model1b.estimates(outcome = "pcl.diff_score_base_prepan",
+                  data_set = "dat.prepan")
+kable(pcl_prepan_model1b_estimates)
+pcl_prepan_model1b_estimates
+
+# Regression diagnostic statistics
+pcl_prepan_model1b_reg_stats <- model1b.reg.stats(outcome = "pcl.diff_score_base_prepan",
+                  data_set = "dat.prepan")
+kable(pcl_prepan_model1b_reg_stats)
+pcl_prepan_model1b_reg_stats
+```
+
+## Regression: Absolute scores
+### Model 0a: Disorder_hierarchical, Unadjusted
+```{r pcl model0a sum_score w/employment prepan}
+# Regression coefficients
+pcl_prepan_model0a_explan_estimates <- model0a.explan.estimates(outcome = "pcl.sum_score_base",
+                         explan_var = "pcl.sum_score_prepan",
+                         data_set = "dat.prepan")
+kable(pcl_prepan_model0a_explan_estimates)
+pcl_prepan_model0a_explan_estimates
+
+# Regression diagnostic statistics
+pcl_prepan_model0a_explan_reg_stats <- model0a.explan.reg.stats(outcome = "pcl.sum_score_base",
+                         explan_var = "pcl.sum_score_prepan",
+                         data_set = "dat.prepan")
+kable(pcl_prepan_model0a_explan_reg_stats)
+pcl_prepan_model0a_explan_reg_stats
+```
+
+### Model 0b: Overlapping disorders, Unadjusted
+```{r pcl model0b sum_score w/employment prepan}
+# Regression coefficients
+pcl_prepan_model0b_explan_estimates <- model0b.explan.estimates(outcome = "pcl.sum_score_base",
+                         explan_var = "pcl.sum_score_prepan",
+                         data_set = "dat.prepan")
+kable(pcl_prepan_model0b_explan_estimates)
+pcl_prepan_model0b_explan_estimates
+
+# Regression diagnostic statistics
+pcl_prepan_model0b_explan_reg_stats <- model0b.explan.reg.stats(outcome = "pcl.sum_score_base",
+                         explan_var = "pcl.sum_score_prepan",
+                         data_set = "dat.prepan")
+kable(pcl_prepan_model0b_explan_reg_stats)
+pcl_prepan_model0b_explan_reg_stats
+```
+
+### Model 1a: Disorder hierarchical, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r pcl model1a sum_score w/employment prepan}
+# Regression coefficients
+pcl_prepan_model1a_explan_estimates <- model1a.explan.estimates(outcome = "pcl.sum_score_base",
+                         explan_var = "pcl.sum_score_prepan",
+                         data_set = "dat.prepan")
+kable(pcl_prepan_model1a_explan_estimates)
+pcl_prepan_model1a_explan_estimates
+
+# Regression diagnostic statistics
+pcl_prepan_model1a_explan_reg_stats <- model1a.explan.reg.stats(outcome = "pcl.sum_score_base",
+                         explan_var = "pcl.sum_score_prepan",
+                         data_set = "dat.prepan")
+kable(pcl_prepan_model1a_explan_reg_stats)
+pcl_prepan_model1a_explan_reg_stats
+```
+
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r pcl model1b sum_score w/employment prepan}
 # Regression coefficients
@@
                          explan_var = "pcl.sum_score_prepan",
-                         data_set = "dat.prepan_sensitivity_6months")
+                         data_set = "dat.prepan")
 kable(pcl_prepan_model1b_explan_estimates)
@@
                          explan_var = "pcl.sum_score_prepan",
-                         data_set = "dat.prepan_sensitivity_6months")
+                         data_set = "dat.prepan")
 kable(pcl_prepan_model1b_explan_reg_stats)
@@
 ```
-
-#### Subset of participants 9 months prior to pandemic
-```{r pcl model1b sum_score prepan - sensitivity 9 months}
-# Regression coefficients
-pcl_prepan_model1b_explan_estimates <- model1b.explan.estimates(outcome = "pcl.sum_score_base",
-                         explan_var = "pcl.sum_score_prepan",
-                         data_set = "dat.prepan_sensitivity_9months")
-kable(pcl_prepan_model1b_explan_estimates)
-pcl_prepan_model1b_explan_estimates
-
-# Regression diagnostic statistics
-pcl_prepan_model1b_explan_reg_stats <- model1b.explan.reg.stats(outcome = "pcl.sum_score_base",
-                         explan_var = "pcl.sum_score_prepan",
-                         data_set = "dat.prepan_sensitivity_9months")
-kable(pcl_prepan_model1b_explan_reg_stats)
-pcl_prepan_model1b_explan_reg_stats
-```

### 2020-11-12 PANCHANGE_analysis.Rmd
added age^2 to phq, ocir,pcl
added age^2 sensitivity to other measures. Not sure if this is everywhere needed

--- 2020-11-09 PANCHANGE_analysis.Rmd
@@
 dim(dat_age_sensitivity)
+
+dat.retro_age_sensitivity <- dat.retro %>%
+  filter(!is.na(Age))
+dim(dat.retro_age_sensitivity)
+
+dat.prepan_age_sensitivity <- dat.prepan %>%
+  filter(!is.na(Age))
+dim(dat.prepan_age_sensitivity)
 ```
@@
 
+```{r model2a.explan function}
+model2a.explan.estimates <- function(outcome, explan_var, data_set) {
+  # define the variable name of the dependent variable
+  dependent.variable <- outcome
+  # define the independent variables
+  independent.variables <- c(explan_var,
+                             "Disorder_hierarchical",
+                             "Gender_collapsed",
+                             "poly(Age, 2)",
+                             "Ethnicity_collapsed",
+                             "key_worker",
+                             "time_diff_coping_lockdown_march_23"
+  )
+  # create the formula
+  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
+  glm.formula
+
+  # run the glm
+  assign(paste0(outcome,".",explan_var,".model2a.explan"),
+         lm( formula = glm.formula,
+             data = get(data_set)
+         )
+  )
+
+  assign(paste0(outcome,".",explan_var,"model2a.explan_estimates"),
+         tidy(get(paste0(outcome,".",explan_var,".model2a.explan")), conf.int = TRUE) %>%
+           mutate(
+             "Indepent variable" = recode_factor(
+               term,
+               "(Intercept)" = "Intercept",
+               "Disorder_hierarchicalAnxiety disorders" = "Anxiety disorders",
+               "Disorder_hierarchicalEating disorders" = "Eating disorders",
+               "Disorder_hierarchicalOCDs" = "OCDs",
+               "Disorder_hierarchicalPTSD" = "PTSD",
+               "Disorder_hierarchicalDepressive disorders" = "Depressive disorders",
+               "Disorder_hierarchicalBipolar disorders" = "Bipolar disorders",
+               "Gender_collapsedFemale" = "Female",
+               "Gender_collapsedNon-binary/Self-defined" = "Non-binary/Self-defined",
+               "poly(Age, 2)1" = "Age",
+               "poly(Age, 2)2" = "Age^2", 
+               "Ethnicity_collapsedMixed or multiple ethnic origins" = "Mixed or multiple ethnic origins",
+               "Ethnicity_collapsedAsian or Asian British" = "Asian or Asian British",
+               "Ethnicity_collapsedAfrican or African British" = "African or African British",
+               "Ethnicity_collapsedOther" = "Other ethnicity",
+               "key_workerKey worker" = "Key worker",
+               "time_diff_coping_lockdown_march_23" = "Time difference: Lockdown to baseline"
+             ),
+             "Estimate" = format(
+               round(estimate,
+                     digits = 2),
+               nsmall = 2),
+             "95% CI low" = format(
+               round(conf.low,
+                     digits = 2),
+               nsmall = 2),
+             "95% CI up" = format(
+               round(conf.high,
+                     digits = 2),
+               nsmall = 2),
+             "SE" = format(
+               round(std.error,
+                     digits = 2),
+               nsmall = 2),
+             "z score" = format(
+               round(statistic,
+                     digits = 2),
+               nsmall = 2),
+             "p value" = case_when(
+               p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
+               p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
+               p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
+             )
+           ) %>%
+           select(
+             "Indepent variable",
+             "Estimate",
+             "95% CI low",
+             "95% CI up",
+             "SE",
+             #    "z score",
+             "p value"
+           )
+  )
+
+  return(get(paste0(outcome,".",explan_var,"model2a.explan_estimates")))
+}
+
+model2a.explan.reg.stats <- function(outcome, explan_var, data_set) {
+  # define the variable name of the dependent variable
+  dependent.variable <- outcome
+  # define the independent variables
+  independent.variables <- c("Disorder_hierarchical")
+  # create the formula
+  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
+  glm.formula
+
+  # run the glm
+  assign(paste0(outcome,".",explan_var,".model2a.explan"),
+         lm( formula = glm.formula,
+             data = get(data_set)
+         )
+  )
+
+  assign(paste0(outcome,".",explan_var,"model2a.explan_reg_stats"),
+         glance(get(paste0(outcome,".",explan_var,".model2a.explan"))) %>%
+           mutate(
+             "n" = format(
+               round(nobs,
+                     digits = 0),
+               nsmall = 0),
+             "R2" = format(
+               round(r.squared,
+                     digits = 2),
+               nsmall = 2),
+             "adjust. R2" = format(
+               round(adj.r.squared,
+                     digits = 2),
+               nsmall = 2),
+             "F" = format(
+               round(statistic,
+                     digits = 2),
+               nsmall = 2),
+             "p value" = case_when(
+               p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
+               p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
+               p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
+             )
+           ) %>%
+           select(
+             "n",
+             "R2",
+             "adjust. R2",
+             "F",
+             "p value",
+             "df"
+           )
+  )
+
+  return(get(paste0(outcome,".",explan_var,"model2a.explan_reg_stats")))
+}
+```
+
+```{r model2b.explan function}
+model2b.explan.estimates <- function(outcome, explan_var, data_set) {
+  # define the variable name of the dependent variable
+  dependent.variable <- outcome
+  # define the independent variables
+  independent.variables <- c(explan_var,
+                             "depression_and_anxiety",
+                             "eating_disorders",
+                             "obsessive_compulsive_disorders",
+                             "bipolar_and_schizophrenia",
+                             "mhd.posttraumatic_stress_disorder_ptsd",
+                             "autism_spectrum_disorder",
+                             "mhd.attention_deficit_hyperactivity_disorder",
+                             "mhd.personality_disorder",
+                             "Gender_collapsed",
+                             "poly(Age, 2)",
+                             "Ethnicity_collapsed",
+                             "key_worker",
+                             "time_diff_coping_lockdown_march_23"
+  )
+  # create the formula
+  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
+  glm.formula
+
+  # run the glm
+  assign(paste0(outcome,".",explan_var,".model2b.explan"),
+         lm( formula = glm.formula,
+             data = get(data_set)
+         )
+  )
+
+  assign(paste0(outcome,".",explan_var,"model2b.explan_estimates"),
+         tidy(get(paste0(outcome,".",explan_var,".model2b.explan")), conf.int = TRUE) %>%
+           mutate(
+             "Indepent variable" = recode_factor(
+               term,
+               "(Intercept)" = "Intercept",
+               "anxiety_disordersAnxiety disorder" = "Anxiety disorders",
+               "depressive_disordersDepressive disorder" = "Depressive disorders",
+               "depression_and_anxietyDepressive and anxiety disorder" = "Depressive and anxiety disorder",
+               "depression_and_anxietyOnly depressive disorder" = "Only depressive disorder",
+               "depression_and_anxietyOnly anxiety disorder" = "Only anxiety disorder",
+               "eating_disordersEating disorder" = "Eating disorders",
+               "obsessive_compulsive_disordersObsessive compulsive disorder" = "OCDs",
+               "bipolar_and_schizophreniaPsychotic and bipolar disorder" = "Psychotic and bipolar disorder",
+               "bipolar_and_schizophreniaOnly psychotic disorder" = "Only psychotic disorder",
+               "bipolar_and_schizophreniaOnly bipolar disorder" = "Only bipolar disorder",
+               "psychotic_disordersPsychotic disorder" = "Psychotic disorder",
+               "mhd.mania_hypomania_bipolar_or_manicdepressionMania, hypomania, bipolar or manic-depression" = "Bipolar disorder",
+               "mhd.posttraumatic_stress_disorder_ptsdPost-traumatic stress disorder (PTSD)" = "PTSD",
+               "autism_spectrum_disorderAutism spectrum disorder" = "ASD",
+               "mhd.attention_deficit_hyperactivity_disorderAttention deficit or attention deficit and hyperactivity disorder (ADD/ADHD)" = "ADHD",
+               "mhd.personality_disorderPersonality disorder" = "Personality disorder",
+               "Gender_collapsedFemale" = "Female",
+               "Gender_collapsedNon-binary/Self-defined" = "Non-binary/Self-defined",
+               "poly(Age, 2)1" = "Age",
+               "poly(Age, 2)2" = "Age^2", 
+               "Ethnicity_collapsedMixed or multiple ethnic origins" = "Mixed or multiple ethnic origins",
+               "Ethnicity_collapsedAsian or Asian British" = "Asian or Asian British",
+               "Ethnicity_collapsedAfrican or African British" = "African or African British",
+               "Ethnicity_collapsedOther" = "Other ethnicity",
+               "key_workerKey worker" = "Key worker",
+               "time_diff_coping_lockdown_march_23" = "Time difference: Lockdown to baseline"
+             ),
+             "Estimate" = format(
+               round(estimate,
+                     digits = 2),
+               nsmall = 2),
+             "95% CI low" = format(
+               round(conf.low,
+                     digits = 2),
+               nsmall = 2),
+             "95% CI up" = format(
+               round(conf.high,
+                     digits = 2),
+               nsmall = 2),
+             "SE" = format(
+               round(std.error,
+                     digits = 2),
+               nsmall = 2),
+             "z score" = format(
+               round(statistic,
+                     digits = 2),
+               nsmall = 2),
+             "p value" = case_when(
+               p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
+               p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
+               p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
+             )
+           ) %>%
+           select(
+             "Indepent variable",
+             "Estimate",
+             "95% CI low",
+             "95% CI up",
+             "SE",
+             #    "z score",
+             "p value"
+           )
+  )
+
+  return(get(paste0(outcome,".",explan_var,"model2b.explan_estimates")))
+}
+
+model2b.explan.reg.stats <- function(outcome, explan_var, data_set) {
+  # define the variable name of the dependent variable
+  dependent.variable <- outcome
+  # define the independent variables
+  independent.variables <- c("Disorder_hierarchical")
+  # create the formula
+  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
+  glm.formula
+
+  # run the glm
+  assign(paste0(outcome,".",explan_var,".model2b.explan"),
+         lm( formula = glm.formula,
+             data = get(data_set)
+         )
+  )
+
+  assign(paste0(outcome,".",explan_var,"model2b.explan_reg_stats"),
+         glance(get(paste0(outcome,".",explan_var,".model2b.explan"))) %>%
+           mutate(
+             "n" = format(
+               round(nobs,
+                     digits = 0),
+               nsmall = 0),
+             "R2" = format(
+               round(r.squared,
+                     digits = 2),
+               nsmall = 2),
+             "adjust. R2" = format(
+               round(adj.r.squared,
+                     digits = 2),
+               nsmall = 2),
+             "F" = format(
+               round(statistic,
+                     digits = 2),
+               nsmall = 2),
+             "p value" = case_when(
+               p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
+               p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
+               p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
+             )
+           ) %>%
+           select(
+             "n",
+             "R2",
+             "adjust. R2",
+             "F",
+             "p value",
+             "df"
+           )
+  )
+
+  return(get(paste0(outcome,".",explan_var,"model2b.explan_reg_stats")))
+}
+```
+
 # GAD baseline, not controlling for prior symptoms
@@
 
+### Model 2a: Disorder hierarchical, Adjusted with Age^2 
+Model 0a + Gender_collapsed + age^2+ Ethnicity_collapsed + Time registration and baseline
+```{r gad model2a diff_score prepan}
+# Regression coefficients
+gad_prepan_model2a_estimates <- model2a.estimates(outcome = "gad.diff_score_base_prepan",
+                  data_set = "dat.prepan_age_sensitivity")
+kable(gad_prepan_model2a_estimates)
+gad_prepan_model2a_estimates
+
+# Regression diagnostic statistics
+gad_prepan_model2a_reg_stats <- model2a.reg.stats(outcome = "gad.diff_score_base_prepan",
+                  data_set = "dat.prepan_age_sensitivity")
+kable(gad_prepan_model2a_reg_stats)
+gad_prepan_model2a_reg_stats
+```
+
+### Model 2b: Overlapping disorders, Adjusted with Age^2 
+Model 0a + Gender_collapsed + age^2 + Ethnicity_collapsed + Time registration and baseline
+```{r gad model2b diff_score prepan}
+# Regression coefficients
+gad_prepan_model2b_estimates <- model2b.estimates(outcome = "gad.diff_score_base_prepan",
+                  data_set = "dat.prepan_age_sensitivity")
+kable(gad_prepan_model2b_estimates)
+gad_prepan_model2b_estimates
+
+# Regression diagnostic statistics
+gad_prepan_model2b_reg_stats <- model2b.reg.stats(outcome = "gad.diff_score_base_prepan",
+                  data_set = "dat.prepan_age_sensitivity")
+kable(gad_prepan_model2b_reg_stats)
+gad_prepan_model2b_reg_stats
+```
 ## Regression: Absolute scores
@@
 gad_prepan_model1b_explan_reg_stats
+```
+
+### Model 2a: Disorder hierarchical, Adjusted with age^2
+Model 0a + Gender_collapsed + age^2 + Ethnicity_collapsed + Time registration and baseline
+```{r gad model2a sum_score prepan}
+# Regression coefficients
+gad_prepan_model2a_explan_estimates <- model2a.explan.estimates(outcome = "gad.sum_score_base",
+                         explan_var = "gad.sum_score_prepan",
+                         data_set = "dat.prepan_age_sensitivity")
+kable(gad_prepan_model2a_explan_estimates)
+gad_prepan_model2a_explan_estimates
+
+# Regression diagnostic statistics
+gad_prepan_model2a_explan_reg_stats <- model2a.explan.reg.stats(outcome = "gad.sum_score_base",
+                         explan_var = "gad.sum_score_prepan",
+                         data_set = "dat.prepan_age_sensitivity")
+kable(gad_prepan_model2a_explan_reg_stats)
+gad_prepan_model2a_explan_reg_stats
+```
+
+### Model 2b: Overlapping disorders, Adjusted with age^2
+Model 0a + Gender_collapsed + age^2 + Ethnicity_collapsed + Time registration and baseline
+```{r gad model2b sum_score prepan}
+# Regression coefficients
+gad_prepan_model2b_explan_estimates <- model2b.explan.estimates(outcome = "gad.sum_score_base",
+                         explan_var = "gad.sum_score_prepan",
+                         data_set = "dat.prepan_age_sensitivity")
+kable(gad_prepan_model2b_explan_estimates)
+gad_prepan_model2b_explan_estimates
+
+# Regression diagnostic statistics
+gad_prepan_model2b_explan_reg_stats <- model2b.explan.reg.stats(outcome = "gad.sum_score_base",
+                         explan_var = "gad.sum_score_prepan",
+                         data_set = "dat.prepan_age_sensitivity")
+kable(gad_prepan_model2b_explan_reg_stats)
+gad_prepan_model2b_explan_reg_stats
 ```
@@
 ```
+### Model 2a: Disorder hierarchical, Adjusted with age^2
+Model 0a + Gender_collapsed + age^2 + Ethnicity_collapsed + Time registration and baseline
+```{r gad model2a diff_score retro}
+# Regression coefficients
+gad_retro_model2a_estimates <- model2a.estimates(outcome = "gad.diff_score_base_retro",
+                                                 data_set = "dat.retro_age_sensitivity")
+kable(gad_retro_model2a_estimates)
+gad_retro_model2a_estimates
+
+# Regression diagnostic statistics
+gad_retro_model2a_reg_stats <- model2a.reg.stats(outcome = "gad.diff_score_base_retro",
+                                                 data_set = "dat.retro_age_sensitivity")
+kable(gad_retro_model2a_reg_stats)
+gad_retro_model2a_reg_stats
+```
+
+### Model 2b: Overlapping disorders, Adjusted with age^2
+Model 0a + Gender_collapsed +  age^2 + Ethnicity_collapsed + Time registration and baseline
+```{r gad model2b diff_score retro}
+# Regression coefficients
+gad_retro_model2b_estimates <- model2b.estimates(outcome = "gad.diff_score_base_retro",
+                                                 data_set = "dat.retro_age_sensitivity")
+kable(gad_retro_model2b_estimates)
+gad_retro_model2b_estimates
+
+# Regression diagnostic statistics
+gad_retro_model2b_reg_stats <- model2b.reg.stats(outcome = "gad.diff_score_base_retro",
+                                                 data_set = "dat.retro_age_sensitivity")
+kable(gad_retro_model2b_reg_stats)
+gad_retro_model2b_reg_stats
+```
 
@@
 
+### Model 2a: Disorder hierarchical, Adjusted with age^2
+Model 0a + Gender_collapsed + age^2 + Ethnicity_collapsed + Time registration and baseline
+```{r gad model2a sum_score retro}
+# Regression coefficients
+gad_retro_model2a_explan_estimates <- model2a.explan.estimates(outcome = "gad.sum_score_base",
+                                                               explan_var = "gad.sum_score_retro",
+                                                               data_set = "dat.retro_age_sensitivity")
+kable(gad_retro_model2a_explan_estimates)
+gad_retro_model2a_explan_estimates
+
+# Regression diagnostic statistics
+gad_retro_model2a_explan_reg_stats <- model2a.explan.reg.stats(outcome = "gad.sum_score_base",
+                                                               explan_var = "gad.sum_score_retro",
+                                                               data_set = "dat.retro_age_sensitivity")
+kable(gad_retro_model2a_explan_reg_stats)
+gad_retro_model2a_explan_reg_stats
+```
+
+### Model 2b: Overlapping disorders, Adjusted with age^2
+Model 0a + Gender_collapsed + age^2 + Ethnicity_collapsed + Time registration and baseline
+```{r gad model2b sum_score retro}
+# Regression coefficients
+gad_retro_model2b_explan_estimates <- model2b.explan.estimates(outcome = "gad.sum_score_base",
+                                                               explan_var = "gad.sum_score_retro",
+                                                               data_set = "dat.retro_age_sensitivity")
+kable(gad_retro_model2b_explan_estimates)
+gad_retro_model2b_explan_estimates
+
+# Regression diagnostic statistics
+gad_retro_model2b_explan_reg_stats <- model2b.explan.reg.stats(outcome = "gad.sum_score_base",
+                                                               explan_var = "gad.sum_score_retro",
+                                                               data_set = "dat.retro_age_sensitivity")
+kable(gad_retro_model2b_explan_reg_stats)
+gad_retro_model2b_explan_reg_stats
+```
 # GAD retro: sensitivity
@@
 
+### Model 2a: Disorder hierarchical, Adjusted with age^2
+Model 0a + Gender_collapsed + age^2 + Ethnicity_collapsed + Time registration and baseline
+```{r phq model2a absolute whole sample}
+# Regression coefficients
+phq_baseline_model2a_estimates <- model2a.estimates(outcome = "phq.sum_score_base",
+                                                 data_set = "dat_age_sensitivity")
+kable(phq_baseline_model2a_estimates)
+phq_baseline_model2a_estimates
+
+# Regression diagnostic statistics
+phq_baseline_model2a_reg_stats <- model2a.reg.stats(outcome = "phq.sum_score_base",
+                                                 data_set = "dat_age_sensitivity")
+kable(phq_baseline_model2a_reg_stats)
+phq_baseline_model2a_reg_stats
+```
+
+### Model 2b: Overlapping disorders, Adjusted with age^2
+Model 0a + Gender_collapsed +  age^2 + Ethnicity_collapsed + Time registration and baseline
+```{r phq model2b absolute whole sample}
+# Regression coefficients
+phq_baseline_model2b_estimates <- model2b.estimates(outcome = "phq.sum_score_base",
+                                                 data_set = "dat_age_sensitivity")
+kable(phq_baseline_model2b_estimates)
+phq_baseline_model2b_estimates
+
+# Regression diagnostic statistics
+phq_baseline_model2b_reg_stats <- model2b.reg.stats(outcome = "phq.sum_score_base",
+                                                 data_set = "dat_age_sensitivity")
+kable(phq_baseline_model2b_reg_stats)
+phq_baseline_model2b_reg_stats
+```
+
 # PHQ prepan
@@
 
+### Model 2a: Disorder hierarchical, Adjusted with age^2
+Model 0a + Gender_collapsed + age^2 + Ethnicity_collapsed + Time registration and baseline
+```{r phq model2a diff_score prepan}
+# Regression coefficients
+phq_prepan_model2a_estimates <- model2a.estimates(outcome = "phq.diff_score_base_prepan",
+                  data_set = "dat.prepan_age_sensitivity")
+kable(phq_prepan_model2a_estimates)
+phq_prepan_model2a_estimates
+
+# Regression diagnostic statistics
+phq_prepan_model2a_reg_stats <- model2a.reg.stats(outcome = "phq.diff_score_base_prepan",
+                  data_set = "dat.prepan_age_sensitivity")
+kable(phq_prepan_model2a_reg_stats)
+phq_prepan_model2a_reg_stats
+```
+
+### Model 2b: Overlapping disorders, Adjusted with age^2
+Model 0a + Gender_collapsed +  age^2 + Ethnicity_collapsed + Time registration and baseline
+```{r phq model2b diff_score prepan}
+# Regression coefficients
+phq_prepan_model2b_estimates <- model2b.estimates(outcome = "phq.diff_score_base_prepan",
+                  data_set = "dat.prepan_age_sensitivity")
+kable(phq_prepan_model2b_estimates)
+phq_prepan_model2b_estimates
+
+# Regression diagnostic statistics
+phq_prepan_model2b_reg_stats <- model2b.reg.stats(outcome = "phq.diff_score_base_prepan",
+                  data_set = "dat.prepan_age_sensitivity")
+kable(phq_prepan_model2b_reg_stats)
+phq_prepan_model2b_reg_stats
+```
 ## Regression: Absolute scores
@@
 ```
+
+### Model 2a: Disorder hierarchical, Adjusted with age^2
+Model 0a + Gender_collapsed + age^2 + Ethnicity_collapsed + Time registration and baseline
+```{r phq model2a sum_score prepan}
+# Regression coefficients
+phq_prepan_model2a_explan_estimates <- model2a.explan.estimates(outcome = "phq.sum_score_base",
+                         explan_var = "phq.sum_score_prepan",
+                         data_set = "dat.prepan_age_sensitivity")
+kable(phq_prepan_model2a_explan_estimates)
+phq_prepan_model2a_explan_estimates
+
+# Regression diagnostic statistics
+phq_prepan_model2a_explan_reg_stats <- model2a.explan.reg.stats(outcome = "phq.sum_score_base",
+                         explan_var = "phq.sum_score_prepan",
+                         data_set = "dat.prepan_age_sensitivity")
+kable(phq_prepan_model2a_explan_reg_stats)
+phq_prepan_model2a_explan_reg_stats
+```
+
+### Model 2b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age^2 + Ethnicity_collapsed + Time registration and baseline
+```{r phq model2b sum_score prepan}
+# Regression coefficients
+phq_prepan_model2b_explan_estimates <- model2b.explan.estimates(outcome = "phq.sum_score_base",
+                         explan_var = "phq.sum_score_prepan",
+                         data_set = "dat.prepan_age_sensitivity")
+kable(phq_prepan_model2b_explan_estimates)
+phq_prepan_model2b_explan_estimates
+
+# Regression diagnostic statistics
+phq_prepan_model2b_explan_reg_stats <- model2b.explan.reg.stats(outcome = "phq.sum_score_base",
+                         explan_var = "phq.sum_score_prepan",
+                         data_set = "dat.prepan_age_sensitivity")
+kable(phq_prepan_model2b_explan_reg_stats)
+phq_prepan_model2b_explan_reg_stats
+```
+
 # PHQ prepan: sensitivity
@@
 
+### Model 2a: Disorder hierarchical, Adjusted with age^2
+Model 0a + Gender_collapsed + age^2 + Ethnicity_collapsed + Time registration and baseline
+```{r phq model2a diff_score retro}
+# Regression coefficients
+phq_retro_model2a_estimates <- model2a.estimates(outcome = "phq.diff_score_base_retro",
+                                                 data_set = "dat.retro_age_sensitivity")
+kable(phq_retro_model2a_estimates)
+phq_retro_model2a_estimates
+
+# Regression diagnostic statistics
+phq_retro_model2a_reg_stats <- model2a.reg.stats(outcome = "phq.diff_score_base_retro",
+                                                 data_set = "dat.retro_age_sensitivity")
+kable(phq_retro_model2a_reg_stats)
+phq_retro_model2a_reg_stats
+```
+
+### Model 2b: Overlapping disorders, Adjusted with age^2
+Model 0a + Gender_collapsed + age^2 + Ethnicity_collapsed + Time registration and baseline
+```{r phq model2b diff_score retro}
+# Regression coefficients
+phq_retro_model2b_estimates <- model2b.estimates(outcome = "phq.diff_score_base_retro",
+                                                 data_set = "dat.retro_age_sensitivity")
+kable(phq_retro_model2b_estimates)
+phq_retro_model2b_estimates
+
+# Regression diagnostic statistics
+phq_retro_model2b_reg_stats <- model2b.reg.stats(outcome = "phq.diff_score_base_retro",
+                                                 data_set = "dat.retro_age_sensitivity")
+kable(phq_retro_model2b_reg_stats)
+phq_retro_model2b_reg_stats
+```
 ## Regression: Absolute scores
@@
 
+### Model 2a: Disorder hierarchical, Adjusted with age^2
+Model 0a + Gender_collapsed + age^2 + Ethnicity_collapsed + Time registration and baseline
+```{r phq model2a sum_score retro}
+# Regression coefficients
+phq_retro_model2a_explan_estimates <- model2a.explan.estimates(outcome = "phq.sum_score_base",
+                                                               explan_var = "phq.sum_score_retro",
+                                                               data_set = "dat.retro_age_sensitivity")
+kable(phq_retro_model2a_explan_estimates)
+phq_retro_model2a_explan_estimates
+
+# Regression diagnostic statistics
+phq_retro_model2a_explan_reg_stats <- model2a.explan.reg.stats(outcome = "phq.sum_score_base",
+                                                               explan_var = "phq.sum_score_retro",
+                                                               data_set = "dat.retro_age_sensitivity")
+kable(phq_retro_model2a_explan_reg_stats)
+phq_retro_model2a_explan_reg_stats
+```
+
+### Model 2b: Overlapping disorders, Adjusted with age^2
+Model 0a + Gender_collapsed + age^2 + Ethnicity_collapsed + Time registration and baseline
+```{r phq model2b sum_score retro}
+# Regression coefficients
+phq_retro_model2b_explan_estimates <- model2b.explan.estimates(outcome = "phq.sum_score_base",
+                                                               explan_var = "phq.sum_score_retro",
+                                                               data_set = "dat.retro_age_sensitivity")
+kable(phq_retro_model2b_explan_estimates)
+phq_retro_model2b_explan_estimates
+
+# Regression diagnostic statistics
+phq_retro_model2b_explan_reg_stats <- model2b.explan.reg.stats(outcome = "phq.sum_score_base",
+                                                               explan_var = "phq.sum_score_retro",
+                                                               data_set = "dat.retro_age_sensitivity")
+kable(phq_retro_model2b_explan_reg_stats)
+phq_retro_model2b_explan_reg_stats
+```
+
 # PHQ retro: Sensitivity
@@
 
+### Model 2a: Disorder hierarchical, Adjusted with age^2
+Model 0a + Gender_collapsed + age^2 + Ethnicity_collapsed + Time registration and baseline
+```{r ocir model2a absolute whole sample}
+# Regression coefficients
+ocir_baseline_model2a_estimates <- model2a.estimates(outcome = "ocir.sum_score_base",
+                                                 data_set = "dat_age_sensitivity")
+kable(ocir_baseline_model2a_estimates)
+ocir_baseline_model2a_estimates
+
+# Regression diagnostic statistics
+ocir_baseline_model2a_reg_stats <- model2a.reg.stats(outcome = "ocir.sum_score_base",
+                                                 data_set = "dat_age_sensitivity")
+kable(ocir_baseline_model2a_reg_stats)
+ocir_baseline_model2a_reg_stats
+```
+
+### Model 2b: Overlapping disorders, Adjusted with age^2
+Model 0a + Gender_collapsed + age^2 + Ethnicity_collapsed + Time registration and baseline
+```{r ocir model2b absolute whole sample}
+# Regression coefficients
+ocir_baseline_model2b_estimates <- model2b.estimates(outcome = "ocir.sum_score_base",
+                                                 data_set = "dat_age_sensitivity")
+kable(ocir_baseline_model2b_estimates)
+ocir_baseline_model2b_estimates
+
+# Regression diagnostic statistics
+ocir_baseline_model2b_reg_stats <- model2b.reg.stats(outcome = "ocir.sum_score_base",
+                                                 data_set = "dat_age_sensitivity")
+kable(ocir_baseline_model2b_reg_stats)
+ocir_baseline_model2b_reg_stats
+```
+
 # OCIR prepan
@@
 
+### Model 2a: Disorder hierarchical, Adjusted with age^2
+Model 0a + Gender_collapsed + age^2 + Ethnicity_collapsed + Time registration and baseline
+```{r ocir model2a diff_score prepan}
+# Regression coefficients
+ocir_prepan_model2a_estimates <- model2a.estimates(outcome = "ocir.diff_score_base_prepan",
+                  data_set = "dat.prepan_age_sensitivity")
+kable(ocir_prepan_model2a_estimates)
+ocir_prepan_model2a_estimates
+
+# Regression diagnostic statistics
+ocir_prepan_model2a_reg_stats <- model2a.reg.stats(outcome = "ocir.diff_score_base_prepan",
+                  data_set = "dat.prepan_age_sensitivity")
+kable(ocir_prepan_model2a_reg_stats)
+ocir_prepan_model2a_reg_stats
+```
+
+### Model 2b: Overlapping disorders, Adjusted with age^2
+Model 0a + Gender_collapsed + age^2 + Ethnicity_collapsed + Time registration and baseline
+```{r ocir model2b diff_score prepan}
+# Regression coefficients
+ocir_prepan_model2b_estimates <- model2b.estimates(outcome = "ocir.diff_score_base_prepan",
+                  data_set = "dat.prepan_age_sensitivity")
+kable(ocir_prepan_model2b_estimates)
+ocir_prepan_model2b_estimates
+
+# Regression diagnostic statistics
+ocir_prepan_model2b_reg_stats <- model2b.reg.stats(outcome = "ocir.diff_score_base_prepan",
+                  data_set = "dat.prepan_age_sensitivity")
+kable(ocir_prepan_model2b_reg_stats)
+ocir_prepan_model2b_reg_stats
+```
+
 ## Regression: Absolute scores
@@
 
+### Model 2a: Disorder hierarchical, Adjusted with age^2
+Model 0a + Gender_collapsed + age^2 + Ethnicity_collapsed + Time registration and baseline
+```{r ocir model2a sum_score prepan}
+# Regression coefficients
+ocir_prepan_model2a_explan_estimates <- model2a.explan.estimates(outcome = "ocir.sum_score_base",
+                         explan_var = "ocir.sum_score_prepan",
+                         data_set = "dat.prepan_age_sensitivity")
+kable(ocir_prepan_model2a_explan_estimates)
+ocir_prepan_model2a_explan_estimates
+
+# Regression diagnostic statistics
+ocir_prepan_model2a_explan_reg_stats <- model2a.explan.reg.stats(outcome = "ocir.sum_score_base",
+                         explan_var = "ocir.sum_score_prepan",
+                         data_set = "dat.prepan_age_sensitivity")
+kable(ocir_prepan_model2a_explan_reg_stats)
+ocir_prepan_model2a_explan_reg_stats
+```
+
+### Model 2b: Overlapping disorders, Adjusted with age^2
+Model 0a + Gender_collapsed + age^2 + Ethnicity_collapsed + Time registration and baseline
+```{r ocir model2b sum_score prepan}
+# Regression coefficients
+ocir_prepan_model2b_explan_estimates <- model2b.explan.estimates(outcome = "ocir.sum_score_base",
+                         explan_var = "ocir.sum_score_prepan",
+                         data_set = "dat.prepan_age_sensitivity")
+kable(ocir_prepan_model2b_explan_estimates)
+ocir_prepan_model2b_explan_estimates
+
+# Regression diagnostic statistics
+ocir_prepan_model2b_explan_reg_stats <- model2b.explan.reg.stats(outcome = "ocir.sum_score_base",
+                         explan_var = "ocir.sum_score_prepan",
+                         data_set = "dat.prepan_age_sensitivity")
+kable(ocir_prepan_model2b_explan_reg_stats)
+ocir_prepan_model2b_explan_reg_stats
+```
 # OCIR retro
@@
 ocir_retro_model1b_reg_stats
+```
+
+### Model 2a: Disorder hierarchical, Adjusted with age^2
+Model 0a + Gender_collapsed + age^2 + Ethnicity_collapsed + Time registration and baseline
+```{r ocir model2a diff_score retro}
+# Regression coefficients
+ocir_retro_model2a_estimates <- model2a.estimates(outcome = "ocir.diff_score_base_retro",
+                                                 data_set = "dat.retro_age_sensitivity")
+kable(ocir_retro_model2a_estimates)
+ocir_retro_model2a_estimates
+
+# Regression diagnostic statistics
+ocir_retro_model2a_reg_stats <- model2a.reg.stats(outcome = "ocir.diff_score_base_retro",
+                                                 data_set = "dat.retro_age_sensitivity")
+kable(ocir_retro_model2a_reg_stats)
+ocir_retro_model2a_reg_stats
+```
+
+### Model 2b: Overlapping disorders, Adjusted with age^2
+Model 0a + Gender_collapsed + age^2 + Ethnicity_collapsed + Time registration and baseline
+```{r ocir model2b diff_score retro}
+# Regression coefficients
+ocir_retro_model2b_estimates <- model2b.estimates(outcome = "ocir.diff_score_base_retro",
+                                                 data_set = "dat.retro_age_sensitivity")
+kable(ocir_retro_model2b_estimates)
+ocir_retro_model2b_estimates
+
+# Regression diagnostic statistics
+ocir_retro_model2b_reg_stats <- model2b.reg.stats(outcome = "ocir.diff_score_base_retro",
+                                                 data_set = "dat.retro_age_sensitivity")
+kable(ocir_retro_model2b_reg_stats)
+ocir_retro_model2b_reg_stats
 ```
@@
 ```
+### Model 2a: Disorder hierarchical, Adjusted with age^2
+Model 0a + Gender_collapsed + age^2 + Ethnicity_collapsed + Time registration and baseline
+```{r ocir model2a sum_score retro}
+# Regression coefficients
+ocir_retro_model2a_explan_estimates <- model2a.explan.estimates(outcome = "ocir.sum_score_base",
+                                                               explan_var = "ocir.sum_score_retro",
+                                                               data_set = "dat.retro_age_sensitivity")
+kable(ocir_retro_model2a_explan_estimates)
+ocir_retro_model2a_explan_estimates
+
+# Regression diagnostic statistics
+ocir_retro_model2a_explan_reg_stats <- model2a.explan.reg.stats(outcome = "ocir.sum_score_base",
+                                                               explan_var = "ocir.sum_score_retro",
+                                                               data_set = "dat.retro_age_sensitivity")
+kable(ocir_retro_model2a_explan_reg_stats)
+ocir_retro_model2a_explan_reg_stats
+```
+
+### Model 2b: Overlapping disorders, Adjusted with age^2
+Model 0a + Gender_collapsed + age^2 + Ethnicity_collapsed + Time registration and baseline
+```{r ocir model2b sum_score retro}
+# Regression coefficients
+ocir_retro_model2b_explan_estimates <- model2b.explan.estimates(outcome = "ocir.sum_score_base",
+                                                               explan_var = "ocir.sum_score_retro",
+                                                               data_set = "dat.retro_age_sensitivity")
+kable(ocir_retro_model2b_explan_estimates)
+ocir_retro_model2b_explan_estimates
+
+# Regression diagnostic statistics
+ocir_retro_model2b_explan_reg_stats <- model2b.explan.reg.stats(outcome = "ocir.sum_score_base",
+                                                               explan_var = "ocir.sum_score_retro",
+                                                               data_set = "dat.retro_age_sensitivity")
+kable(ocir_retro_model2b_explan_reg_stats)
+ocir_retro_model2b_explan_reg_stats
+```
 
@@
 
+### Model 2a: Disorder hierarchical, Adjusted with age^2
+Model 0a + Gender_collapsed + age^2 + Ethnicity_collapsed + Time registration and baseline
+```{r pcl model2a absolute whole sample}
+# Regression coefficients
+pcl_baseline_model2a_estimates <- model2a.estimates(outcome = "pcl.sum_score_base",
+                                                 data_set = "dat_age_sensitivity")
+kable(pcl_baseline_model2a_estimates)
+pcl_baseline_model2a_estimates
+
+# Regression diagnostic statistics
+pcl_baseline_model2a_reg_stats <- model2a.reg.stats(outcome = "pcl.sum_score_base",
+                                                 data_set = "dat_age_sensitivity")
+kable(pcl_baseline_model2a_reg_stats)
+pcl_baseline_model2a_reg_stats
+```
+
+### Model 2b: Overlapping disorders, Adjusted with age^2
+Model 0a + Gender_collapsed + age^2 + Ethnicity_collapsed + Time registration and baseline
+```{r pcl model2b absolute whole sample}
+# Regression coefficients
+pcl_baseline_model2b_estimates <- model2b.estimates(outcome = "pcl.sum_score_base",
+                                                 data_set = "dat_age_sensitivity")
+kable(pcl_baseline_model2b_estimates)
+pcl_baseline_model2b_estimates
+
+# Regression diagnostic statistics
+pcl_baseline_model2b_reg_stats <- model2b.reg.stats(outcome = "pcl.sum_score_base",
+                                                 data_set = "dat_age_sensitivity")
+kable(pcl_baseline_model2b_reg_stats)
+pcl_baseline_model2b_reg_stats
+```
+
 # PCL prepan
@@
 
+### Model 2a: Disorder hierarchical, Adjusted with age^2
+Model 0a + Gender_collapsed + age^2 + Ethnicity_collapsed + Time registration and baseline
+```{r pcl model2a diff_score prepan}
+# Regression coefficients
+pcl_prepan_model2a_estimates <- model2a.estimates(outcome = "pcl.diff_score_base_prepan",
+                  data_set = "dat.prepan_age_sensitivity")
+kable(pcl_prepan_model2a_estimates)
+pcl_prepan_model2a_estimates
+
+# Regression diagnostic statistics
+pcl_prepan_model2a_reg_stats <- model2a.reg.stats(outcome = "pcl.diff_score_base_prepan",
+                  data_set = "dat.prepan_age_sensitivity")
+kable(pcl_prepan_model2a_reg_stats)
+pcl_prepan_model2a_reg_stats
+```
+
+### Model 2b: Overlapping disorders, Adjusted with age^2
+Model 0a + Gender_collapsed + age^2 + Ethnicity_collapsed + Time registration and baseline
+```{r pcl model2b diff_score prepan}
+# Regression coefficients
+pcl_prepan_model2b_estimates <- model2b.estimates(outcome = "pcl.diff_score_base_prepan",
+                  data_set = "dat.prepan_age_sensitivity")
+kable(pcl_prepan_model2b_estimates)
+pcl_prepan_model2b_estimates
+
+# Regression diagnostic statistics
+pcl_prepan_model2b_reg_stats <- model2b.reg.stats(outcome = "pcl.diff_score_base_prepan",
+                  data_set = "dat.prepan_age_sensitivity")
+kable(pcl_prepan_model2b_reg_stats)
+pcl_prepan_model2b_reg_stats
+```
+
 ## Regression: Absolute scores
@@
 
+### Model 2a: Disorder hierarchical, Adjusted with age^2
+Model 0a + Gender_collapsed + age^2 + Ethnicity_collapsed + Time registration and baseline
+```{r pcl model2a sum_score prepan}
+# Regression coefficients
+pcl_prepan_model2a_explan_estimates <- model2a.explan.estimates(outcome = "pcl.sum_score_base",
+                         explan_var = "pcl.sum_score_prepan",
+                         data_set = "dat.prepan_age_sensitivity")
+kable(pcl_prepan_model2a_explan_estimates)
+pcl_prepan_model2a_explan_estimates
+
+# Regression diagnostic statistics
+pcl_prepan_model2a_explan_reg_stats <- model2a.explan.reg.stats(outcome = "pcl.sum_score_base",
+                         explan_var = "pcl.sum_score_prepan",
+                         data_set = "dat.prepan_age_sensitivity")
+kable(pcl_prepan_model2a_explan_reg_stats)
+pcl_prepan_model2a_explan_reg_stats
+```
+
+### Model 2b: Overlapping disorders, Adjusted with age^2
+Model 0a + Gender_collapsed +  age^2 + Ethnicity_collapsed + Time registration and baseline
+```{r pcl model2b sum_score prepan}
+# Regression coefficients
+pcl_prepan_model2b_explan_estimates <- model2b.explan.estimates(outcome = "pcl.sum_score_base",
+                         explan_var = "pcl.sum_score_prepan",
+                         data_set = "dat.prepan_age_sensitivity")
+kable(pcl_prepan_model2b_explan_estimates)
+pcl_prepan_model2b_explan_estimates
+
+# Regression diagnostic statistics
+pcl_prepan_model2b_explan_reg_stats <- model2b.explan.reg.stats(outcome = "pcl.sum_score_base",
+                         explan_var = "pcl.sum_score_prepan",
+                         data_set = "dat.prepan_age_sensitivity")
+kable(pcl_prepan_model2b_explan_reg_stats)
+pcl_prepan_model2b_explan_reg_stats
+```
 # SENSITIVITY based on highest level of education

### 2020-11-13 PANCHANGE_exclusion_descriptives.Rmd
fixed a piece of code that prevented the creation of the 3 groups: accurate, accurate +-3, inaccurate

--- 2020-11-11 PANCHANGE_exclusion_descriptives.Rmd
@@
                                              dat.raw$gad.diff_score_retro_prepan <= 3 &
-                                             dat.raw$gad.change.retro.accurate_temp != 1 |
+                                             dat.raw$gad.change.retro.accurate != 1 |
                                              dat.raw$gad.pandemic.change.group == "Worse" &
@@
                                              dat.raw$gad.diff_score_retro_prepan <= 3 &
-                                             dat.raw$gad.change.retro.accurate_temp != 1,  2, gad.change.retro.accurate))
+                                             dat.raw$gad.change.retro.accurate != 1,  2, gad.change.retro.accurate))
 
@@
 #SB - Impute no change prepandemic scores
+
+I interpreted the presence of an NA in the retrospective score as an indicator of saying "no change" in their baseline scores.
+Hence, if this was the case, I imputed their baseline score.
+However, this interpretation could be wrong.
+
+Also, I'm not sure what to do if there is an NA for their baseline sum score (nothing to duplicate).
+This was the case for ocir for some reason: the retro scores were provided for some by not the corresponding baseline score?
 
@@
 
-#Correlations of retro impute and prepan
-##Create function to use for all of the corplots
-
-```{r function to create upper and lower CI matrices}
-
-cor.mtest <- function(mat, conf.level = 0.95){
-mat <- as.matrix(mat)
-n <- ncol(mat)
-p.mat <- lowCI.mat <- uppCI.mat <- matrix(NA, n, n)
-diag(p.mat) <- 0
-diag(lowCI.mat) <- diag(uppCI.mat) <- 1
-for(i in 1:(n-1)){
-for(j in (i+1):n){
-tmp <- cor.test(mat[,i], mat[,j], conf.level = conf.level)
-p.mat[i,j] <- p.mat[j,i] <- tmp$p.value
-lowCI.mat[i,j] <- lowCI.mat[j,i] <- tmp$conf.int[1]
-uppCI.mat[i,j] <- uppCI.mat[j,i] <- tmp$conf.int[2]
-}
-}
-return(list(p.mat, lowCI.mat, uppCI.mat))
-}
-
-```
-
-###Whole sample prepan retro correlation
-
-```{r Whole sample Correlation prep chunk}
+#Correlation between retropsective impute and prepan
+
+```{r Correlation prep chunk}
 # Select items for correlation matrix
@@
 
-#Create a data set with only the GLAD and EDGI
-prepan_retro_dat <- dat[str_detect(dat$Sample, "GLAD|EDGI"), ]
-
-#Check that RAMP and NBR has been removed
+#Create a data set with only the COPING samples
+prepan_retro_dat <- dat[str_detect(dat$Sample, "NBR|GLAD|EDGI"), ]
+
+#Check that RAMP has been removed
 prepan_retro_dat %>% 
@@
 prepan_retro.p.matrix <- as.matrix(prepan_retro.corr.mat$tests)
-
-res1 <- cor.ci(prepan_retro.corr.matrix)
-lowci <- cor.plot.upperLowerCi(res1)
-lowci[upper.tri(lowci)] = t(lowci)[upper.tri(lowci)]
-
-upci <- cor.plot.upperLowerCi(res1)
-upci[lower.tri(upci)] = t(upci)[lower.tri(lowci)]
-
-conf <- paste0("[", format(lowci, digits=2), " - ", format(upci, digits=2), "]")
-
-xs <- row(lowci)
-ys <- (ncol(lowci)+1) - col(lowci)
-
-xs[lower.tri(xs,diag=TRUE)] <- 0
-ys[lower.tri(ys,diag=TRUE)] <- 0
-
-```
-
-```{r Whole sample correlation matrix of prepan retro sum scores}
+```
+
+```{r Correlation matrix of prepan base sum scores}
 corrplot(prepan_retro.corr.matrix, 
@@
          )
-
-text(xs, ys, conf, pos=1, cex=0.8)
-
-```
-
-```{r Whole sample prepan retro scatterplots prep}
-
-#Create a data set with only the GLAD and EDGI participants
-whole_retro_prepan_scatter <- dat[str_detect(dat$Sample, "GLAD|EDGI"), ]
-
-#Check that RAMP and NBR has been removed
-whole_retro_prepan_scatter %>% 
-  freq(Sample)
-
-#Remove those saying "no different" since pandemic
-
-whole_retro_prepan_gad_scatter <- whole_retro_prepan_scatter %>% 
-  filter(gad.pandemic_felt_feelings == "Much worse" |
-           gad.pandemic_felt_feelings == "A little worse" |
-           gad.pandemic_felt_feelings == "A little better" |
-           gad.pandemic_felt_feelings == "Much better")
-
-whole_retro_prepan_phq_scatter <- whole_retro_prepan_scatter %>% 
-  filter(phq.pandemic_felt_feelings == "Much worse" |
-           phq.pandemic_felt_feelings == "A little worse" |
-           phq.pandemic_felt_feelings == "A little better" |
-           phq.pandemic_felt_feelings == "Much better")
-
-```
-
-```{r Whole sample prepan retro scatterplots}
-
-#Visualise as scatterplots
-
-whole_retro_prepan_gad_scatter %>% ggplot(aes(x = gad.sum_score_prepan, y = gad.sum_score_retro)) +
-  geom_point(colour = "grey") +
-  geom_jitter(w = 0.4, h = 0.4, colour = "grey") +
-  geom_smooth(method = "lm", colour = "navy", fill = "red") +
-   labs(title = paste("Relationship between prepandemic and retrospective GAD scores\nfor whole sample",
-                      sep=" "),
-        subtitle = paste("n", dim(whole_retro_prepan_gad_scatter)[1]))
-
-whole_retro_prepan_phq_scatter %>% ggplot(aes(x = phq.sum_score_retro, y = phq.sum_score_prepan)) +
-  geom_point(colour = "grey") +
-  geom_jitter(w = 0.4, h = 0.4, colour = "grey") +
-  geom_smooth(method = "lm", colour = "navy", fill = "red") +
-   labs(title = paste("Relationship between prepandemic and retrospective PHQ scores\nfor whole sample",
-                      sep=" "),
-        subtitle = paste("n", dim(whole_retro_prepan_phq_scatter)[1]))
-
-```
-
-###Little/much worse prepan retro correlation
-
-```{r Little/much worse correlation prep chunk}
-
-# Check the items are the same from the whole chunk
-prepan_retro_items
-
-#Create a data set with only the GLAD and EDGI
-prepan_retro_dat_worse <- dat[str_detect(dat$Sample, "GLAD|EDGI"), ]
-
-#Filter the data to only include those with self-reported little/much worse gad since pandemic
-
-prepan_retro_dat_worse <- prepan_retro_dat_worse %>% 
-  filter(gad.pandemic_felt_feelings == "A little worse" |
-           gad.pandemic_felt_feelings == "Much worse")
-
-#Check that RAMP and NBR has been removed
-prepan_retro_dat_worse %>% 
-  freq(Sample)
-
-# Calculate correlation matrix on specific columns (variables) from your data frame
-prepan_retro.corr.mat_worse <- hetcor(
-  as.data.frame(prepan_retro_dat_worse[,prepan_retro_items]), # Specify the data
-  use = "pairwise.complete.obs" # Use all pairwise observations
-)
-
-# Print the correlation matrix
-print(prepan_retro.corr.mat_worse, digits = max(3, getOption("digits") - 3))
-
-# Save the correlations from the correlation matrix in an object
-prepan_retro.corr.matrix_worse <- as.matrix(prepan_retro.corr.mat_worse)
-
-# Save the p values from the correlation matrix in an object
-prepan_retro.p.matrix_worse <- as.matrix(prepan_retro.corr.mat_worse$tests)
-
-res1 <- cor.ci(prepan_retro.corr.matrix_worse)
-lowci <- cor.plot.upperLowerCi(res1)
-lowci[upper.tri(lowci)] = t(lowci)[upper.tri(lowci)]
-
-upci <- cor.plot.upperLowerCi(res1)
-upci[lower.tri(upci)] = t(upci)[lower.tri(lowci)]
-
-conf <- paste0("[", format(lowci, digits=2), " - ", format(upci, digits=2), "]")
-
-xs <- row(lowci)
-ys <- (ncol(lowci)+1) - col(lowci)
-
-xs[lower.tri(xs,diag=TRUE)] <- 0
-ys[lower.tri(ys,diag=TRUE)] <- 0
-
-```
-
-```{r Little/much worse correlation matrix of prepan retro sum scores}
-corrplot(prepan_retro.corr.matrix_worse, 
-         method = "color", # objects to represent the correlations on plot
-         type = "lower", # only use the lower triangle of the matrix
-         diag = FALSE, # do not show the correlations on the diagonal
-         addgrid.col = NA,
-         addCoef.col = "black", # colour for the correlation coefficients in the plot
-         tl.cex = 0.8,
-         tl.col = "black",
-         col=colorRampPalette(c("dodgerblue4","white","firebrick4"))(200), # colours for correlations
-         # Combine with significance
-         p.mat = prepan_retro.p.matrix, # Matrix with p values
-         sig.level = 0.01, # Choose significant level
-         insig = "blank" # Nonsignificant correlations have no colour
-         )
-
-text(xs, ys, conf, pos=1, cex=0.8)
-
-```
-
-```{r Little/much worse prepan retro scatterplot prep}
-
-#Create a data set with only the GLAD and EDGI participants
-little_much_worse_retro_prepan <- dat[str_detect(dat$Sample, "GLAD|EDGI"), ]
-
-#Check that RAMP and NBR has been removed
-little_much_worse_retro_prepan %>% 
-  freq(Sample)
-
-#Filter by little/much worse self-reported change since pandemic started in gad and phq
-
-much_worse_gad_scatter <- little_much_worse_retro_prepan %>% 
-  filter(gad.pandemic_felt_feelings == "Much worse")
-
-little_worse_gad_scatter <- little_much_worse_retro_prepan %>% 
-  filter(gad.pandemic_felt_feelings == "A little worse")
-
-much_little_worse_gad_scatter <- little_much_worse_retro_prepan %>% 
-  filter(gad.pandemic_felt_feelings == "Much worse" | 
-           gad.pandemic_felt_feelings == "A little worse")
-
-much_worse_phq_scatter <- little_much_worse_retro_prepan %>% 
-  filter(phq.pandemic_felt_feelings == "Much worse")
-
-little_worse_phq_scatter <- little_much_worse_retro_prepan %>% 
-  filter(phq.pandemic_felt_feelings == "A little worse")
-
-much_little_worse_phq_scatter <- little_much_worse_retro_prepan %>% 
-  filter(phq.pandemic_felt_feelings == "Much worse" | 
-           phq.pandemic_felt_feelings == "A little worse")
-
-```
-
-```{r Little/much worse prepan retro scatterplots}
-
-#Visualise each as a scatterplot
-
-much_worse_gad_scatter %>% ggplot(aes(x = gad.sum_score_prepan, y = gad.sum_score_retro)) +
-  geom_point(colour = "grey") +
-  geom_jitter(w = 0.4, h = 0.4, colour = "grey") +
-  stat_smooth(method = "lm", colour = "navy", fill = "red") +
-   labs(title = paste("Relationship between prepandemic and retrospective GAD scores\nfor participants reporting much worse",
-                      sep=" "),
-        subtitle = paste("n", dim(much_worse_gad_scatter)[1]))
-
-little_worse_gad_scatter %>% ggplot(aes(x = gad.sum_score_prepan, y = gad.sum_score_retro)) +
-  geom_point(colour = "grey") +
-  geom_jitter(w = 0.4, h = 0.4, colour = "grey") +
-  stat_smooth(method = "lm", colour = "navy", fill = "red") +
-   labs(title = paste("Relationship between prepandemic and retrospective GAD scores\nfor participants reporting a little worse",
-                      sep=" "),
-        subtitle = paste("n", dim(little_worse_gad_scatter)[1]))
-
-much_little_worse_gad_scatter %>% ggplot(aes(x = gad.sum_score_prepan, y = gad.sum_score_retro)) +  
-  geom_point(colour = "grey") +
-  geom_jitter(w = 0.4, h = 0.4, colour = "grey") +
-  stat_smooth(method = "lm", colour = "navy", fill = "red") +
-   labs(title = paste("Relationship between prepandemic and retrospective GAD scores\nfor participants reporting much worse and a little worse",
-                      sep=" "),
-        subtitle = paste("n", dim(much_little_worse_gad_scatter)[1]))
-
-much_worse_phq_scatter %>% ggplot(aes(x = phq.sum_score_prepan, y = phq.sum_score_retro)) +
-  geom_point(colour = "grey") +
-  geom_jitter(w = 0.4, h = 0.4, colour = "grey") +
-  stat_smooth(method = "lm", colour = "navy", fill = "red") +
-   labs(title = paste("Relationship between prepandemic and retrospective PHQ scores\nfor participants reporting much worse",
-                      sep=" "),
-        subtitle = paste("n", dim(much_worse_phq_scatter)[1]))
-
-little_worse_phq_scatter %>% ggplot(aes(x = phq.sum_score_prepan, y = phq.sum_score_retro)) +
-  geom_point(colour = "grey") +
-  geom_jitter(w = 0.4, h = 0.4, colour = "grey") +
-  stat_smooth(method = "lm", colour = "navy", fill = "red") +
-   labs(title = paste("Relationship between prepandemic and retrospective PHQ scores\nfor participants reporting a little worse",
-                      sep=" "),
-        subtitle = paste("n", dim(little_worse_phq_scatter)[1]))
-
-much_little_worse_phq_scatter %>% ggplot(aes(x = phq.sum_score_prepan, y = phq.sum_score_retro)) +
-  geom_point(colour = "grey") +
-  geom_jitter(w = 0.4, h = 0.4, colour = "grey") +
-  stat_smooth(method = "lm", colour = "navy", fill = "red") +
-   labs(title = paste("Relationship between prepandemic and retrospective PHQ scores\nfor participants reporting much worse and a little worse",
-                      sep=" "),
-        subtitle = paste("n", dim(much_little_worse_phq_scatter)[1]))
-
-```
-
-###Little/much better prepan retro correlation
-
-```{r Little/much better correlation prep chunk}
-
-# Check the items are the same from the whole chunk
-prepan_retro_items
-
-#Create a data set with only the GLAD and EDGI
-prepan_retro_dat_better <- dat[str_detect(dat$Sample, "GLAD|EDGI"), ]
-
-#Filter the data to only include those with self-reported little/much worse gad since pandemic
-
-prepan_retro_dat_better <- prepan_retro_dat_better %>% 
-  filter(gad.pandemic_felt_feelings == "A little better" |
-           gad.pandemic_felt_feelings == "Much better")
-
-#Check that RAMP and NBR has been removed
-prepan_retro_dat_better %>% 
-  freq(Sample)
-
-# Calculate correlation matrix on specific columns (variables) from your data frame
-prepan_retro.corr.mat_better <- hetcor(
-  as.data.frame(prepan_retro_dat_better[,prepan_retro_items]), # Specify the data
-  use = "pairwise.complete.obs" # Use all pairwise observations
-)
-
-# Print the correlation matrix
-print(prepan_retro.corr.mat_better, digits = max(3, getOption("digits") - 3))
-
-# Save the correlations from the correlation matrix in an object
-prepan_retro.corr.matrix_better <- as.matrix(prepan_retro.corr.mat_better)
-
-# Save the p values from the correlation matrix in an object
-prepan_retro.p.matrix_better <- as.matrix(prepan_retro.corr.mat_better$tests)
-
-res1 <- cor.ci(prepan_retro.corr.matrix_better)
-lowci <- cor.plot.upperLowerCi(res1)
-lowci[upper.tri(lowci)] = t(lowci)[upper.tri(lowci)]
-
-upci <- cor.plot.upperLowerCi(res1)
-upci[lower.tri(upci)] = t(upci)[lower.tri(lowci)]
-
-conf <- paste0("[", format(lowci, digits=2), " - ", format(upci, digits=2), "]")
-
-xs <- row(lowci)
-ys <- (ncol(lowci)+1) - col(lowci)
-
-xs[lower.tri(xs,diag=TRUE)] <- 0
-ys[lower.tri(ys,diag=TRUE)] <- 0
-
-```
-
-```{r Little/much better correlation matrix of prepan retro sum scores}
-corrplot(prepan_retro.corr.matrix_better, 
-         method = "color", # objects to represent the correlations on plot
-         type = "lower", # only use the lower triangle of the matrix
-         diag = FALSE, # do not show the correlations on the diagonal
-         addgrid.col = NA,
-         addCoef.col = "black", # colour for the correlation coefficients in the plot
-         tl.cex = 0.8,
-         tl.col = "black",
-         col=colorRampPalette(c("dodgerblue4","white","firebrick4"))(200), # colours for correlations
-         # Combine with significance
-         p.mat = prepan_retro.p.matrix, # Matrix with p values
-         sig.level = 0.01, # Choose significant level
-         insig = "blank" # Nonsignificant correlations have no colour
-         )
-
-text(xs, ys, conf, pos=1, cex=0.8)
-
-```
-
-```{r Little/much better prepan retro scatterplots prep}
-
-#Create a data set with only the GLAD and EDGI participants
-little_much_better_retro_prepan <- dat[str_detect(dat$Sample, "GLAD|EDGI"), ]
-
-#Check that RAMP and NBR has been removed
-little_much_better_retro_prepan %>% 
-  freq(Sample)
-
-#Filter by participants reporting little/much better in gad and phq since pandemic started (separetely and grouped)
-
-little_better_gad_scatter <- little_much_better_retro_prepan %>% 
-  filter(gad.pandemic_felt_feelings == "A little better")
-
-much_better_gad_scatter <- little_much_better_retro_prepan %>% 
-  filter(gad.pandemic_felt_feelings == "Much better")
-
-much_little_better_gad_scatter <- little_much_better_retro_prepan %>% 
-  filter(gad.pandemic_felt_feelings == "Much better" | 
-           gad.pandemic_felt_feelings == "A little better")
-
-little_better_phq_scatter <- little_much_better_retro_prepan %>% 
-  filter(phq.pandemic_felt_feelings == "A little better")
-
-much_better_phq_scatter <- little_much_better_retro_prepan %>% 
-  filter(phq.pandemic_felt_feelings == "Much better")
-
-much_little_better_phq_scatter <- little_much_better_retro_prepan %>% 
-  filter(phq.pandemic_felt_feelings == "Much better" | 
-           phq.pandemic_felt_feelings == "A little better")
-
-```
-
-```{r Little/much better prepan retro scatterplots}
-
-#Visualise them as scatterplots
-
-little_better_gad_scatter %>% ggplot(aes(x = gad.sum_score_prepan, y = gad.sum_score_retro)) +
-  geom_point(colour = "blue") +
-  stat_smooth(method = "lm") +
-  geom_jitter(w = 0.4, h = 0.4) +
-   labs(title = paste("Relationship between prepandemic and retrospective GAD scores\nfor participants reporting a little better",
-                      sep=" "),
-        subtitle = paste("n", dim(little_better_gad_scatter)[1]))
-
-much_better_gad_scatter %>% ggplot(aes(x = gad.sum_score_prepan, y = gad.sum_score_retro)) +
-  geom_point(colour = "blue") +
-  stat_smooth(method = "lm") +
-  geom_jitter(w = 0.4, h = 0.4) +
-   labs(title = paste("Relationship between prepandemic and retrospective GAD scores\nfor participants reporting much better",
-                      sep=" "),
-        subtitle = paste("n", dim(much_better_gad_scatter)[1]))
-
-much_little_better_gad_scatter %>% ggplot(aes(x = gad.sum_score_prepan, y = gad.sum_score_retro)) +
-  geom_point(colour = "blue") +
-  stat_smooth(method = "lm") + 
-  geom_jitter(w = 0.4, h = 0.4) +
-   labs(title = paste("Relationship between prepandemic and retrospective GAD scores\nfor participants reporting much better and a little better",
-                      sep=" "),
-        subtitle = paste("n", dim(much_little_better_gad_scatter)[1]))
-
-little_better_phq_scatter %>% ggplot(aes(x = phq.sum_score_prepan, y = phq.sum_score_retro)) +
-  geom_point(colour = "blue") +
-  stat_smooth(method = "lm") +
-  geom_jitter(w = 0.4, h = 0.4) +
-   labs(title = paste("Relationship between prepandemic and retrospective PHQ scores\nfor participants reporting a little better",
-                      sep=" "),
-        subtitle = paste("n", dim(little_better_phq_scatter)[1]))
-
-much_better_phq_scatter %>% ggplot(aes(x = phq.sum_score_prepan, y = phq.sum_score_retro)) +
-  geom_point(colour = "blue") +
-  stat_smooth(method = "lm") +
-  geom_jitter(w = 0.4, h = 0.4) +
-   labs(title = paste("Relationship between prepandemic and retrospective PHQ scores\nfor participants reporting much better",
-                      sep=" "),
-        subtitle = paste("n", dim(much_better_phq_scatter)[1]))
-
-much_little_better_phq_scatter %>% ggplot(aes(x = phq.sum_score_prepan, y = phq.sum_score_retro)) +
-  geom_point(colour = "blue") +
-  stat_smooth(method = "lm") + 
-  geom_jitter(w = 0.4, h = 0.4) +
-   labs(title = paste("Relationship between prepandemic and retrospective PHQ scores\nfor participants reporting much better and a little better",
-                      sep=" "),
-        subtitle = paste("n", dim(much_little_better_phq_scatter)[1]))
-
 ```

### 2020-11-13 PANCHANGE_exclusion_descriptives.Rmd
changed the labels from 1,2,3 to Accurate, Accurate +- 3 and Inaccurate

@@
                                              dat.raw$gad.pandemic.change.group == "Worse" &
-                                             dat.raw$gad.diff_score_retro_prepan == 0, 1, 3 ))
+                                             dat.raw$gad.diff_score_retro_prepan == 0, "Accurate", "Inaccurate" ))
 dat.raw <- dat.raw %>%
@@
                                              dat.raw$gad.diff_score_retro_prepan <= 3 &
-                                             dat.raw$gad.change.retro.accurate != 1 |
+                                             dat.raw$gad.change.retro.accurate != "Accurate" |
                                              dat.raw$gad.pandemic.change.group == "Worse" &
@@
                                              dat.raw$gad.diff_score_retro_prepan <= 3 &
-                                             dat.raw$gad.change.retro.accurate != 1,  2, gad.change.retro.accurate))
+                                             dat.raw$gad.change.retro.accurate != "Accurate",
+                                             "Accurate +- 3", gad.change.retro.accurate))
 

### 2020-11-13 PANCHANGE_exclusion_descriptives.Rmd

--- 2020-11-12 PANCHANGE_exclusion_descriptives.Rmd
@@
                                              dat.raw$gad.diff_score_retro_prepan <= 3 &
-                                             dat.raw$gad.change.retro.accurate_temp != 1 |
+                                             dat.raw$gad.change.retro.accurate != "Accurate" |
                                              dat.raw$gad.pandemic.change.group == "Worse" &
@@
                                              dat.raw$gad.diff_score_retro_prepan <= 3 &
-                                             dat.raw$gad.change.retro.accurate_temp != 1,  2, gad.change.retro.accurate))
+                                             dat.raw$gad.change.retro.accurate != "Accurate",
+                                             "Accurate +- 3", gad.change.retro.accurate))
 

### 2020-11-13 PANCHANGE_analysis.Rmd

--- 2020-11-10 PANCHANGE_analysis.Rmd
@@
 author: "Katherine N Thompson, Christopher Hüebel, Molly R Davies, Kirstin L Purves"
-date: Sys.Date()
+date: '`r format(Sys.time(), "%d %B, %Y")`'
 output:
@@
 source("../PANCHANGE_raw_path.R")
+
+print(data_path)
+
 ```
@@
 # Regression coefficients
-#gad_baseline_model0a_estimates <- model0a.estimates(outcome = "gad.sum_score_base",
- #                                                data_set = "dat")
+gad_baseline_model0a_estimates <- model0a.estimates(outcome = "gad.sum_score_base",
+                                                 data_set = "dat")
 #kable(gad_baseline_model0a_estimates)
-#gad_baseline_model0a_estimates
-
-# Regression diagnostic statistics
-#gad_baseline_model0a_reg_stats <- model0a.reg.stats(outcome = "gad.sum_score_base",
-  #                                               data_set = "dat")
+gad_baseline_model0a_estimates
+
+# Regression diagnostic statistics
+gad_baseline_model0a_reg_stats <- model0a.reg.stats(outcome = "gad.sum_score_base",
+                                                 data_set = "dat")
 #kable(gad_baseline_model0a_reg_stats)
-#gad_baseline_model0a_reg_stats
+gad_baseline_model0a_reg_stats
 ```

### 2020-11-16 PANCHANGE_analysis.Rmd
education, employment & employment change sensitivity

@@
 author: "Katherine N Thompson, Christopher Hüebel, Molly R Davies, Kirstin L Purves"
-date: '`r format(Sys.time(), "%d %B, %Y")`'
+date: Sys.Date()
 output:
@@
 source("../PANCHANGE_raw_path.R")
-
-print(data_path)
-
 ```
@@
 ### Model 0a: Disorder_hierarchical, Unadjusted
-
-#SB Hashing out this chunk of code as it is not included in our final analysis and is currently breaking the code.
 ```{r gad model0a absolute whole sample}
@@
                                                  data_set = "dat")
-#kable(gad_baseline_model0a_estimates)
+kable(gad_baseline_model0a_estimates)
 gad_baseline_model0a_estimates
@@
                                                  data_set = "dat")
-#kable(gad_baseline_model0a_reg_stats)
+kable(gad_baseline_model0a_reg_stats)
 gad_baseline_model0a_reg_stats
@@
 
-# SENSITIVITY based on highest level of education
+# Sensitivity based on highest level of education 
+# Function change to include highest education as predictor
+
+```{r model1b education function}
+model1b.estimates <- function(outcome, data_set) {
+  # define the variable name of the dependent variable
+  dependent.variable <- outcome
+  # define the independent variables
+  independent.variables <- c("depression_and_anxiety",
+                             "eating_disorders",
+                             "obsessive_compulsive_disorders",
+                             "bipolar_and_schizophrenia",
+                             "mhd.posttraumatic_stress_disorder_ptsd",
+                             "autism_spectrum_disorder",
+                             "mhd.attention_deficit_hyperactivity_disorder",
+                             "mhd.personality_disorder",
+                             "Gender_collapsed",
+                             "age_category_collapsed",
+                             "Ethnicity_collapsed",
+                             "key_worker",
+                             "time_diff_coping_lockdown_march_23", 
+                             "highest_education"
+                                )
+  # create the formula
+  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
+  glm.formula
+
+  # run the glm
+  assign(paste0(outcome,".model1b"),
+         lm( formula = glm.formula,
+             data = get(data_set)
+         )
+  )
+
+  assign(paste0(outcome,"model1b_estimates"),
+         tidy(get(paste0(outcome,".model1b")), conf.int = TRUE) %>%
+           mutate(
+             "Indepent variable" = recode_factor(
+               term,
+               "(Intercept)" = "Intercept",
+               "anxiety_disordersAnxiety disorder" = "Anxiety disorders",
+               "depressive_disordersDepressive disorder" = "Depressive disorders",
+               "depression_and_anxietyDepressive and anxiety disorder" = "Depressive and anxiety disorder",
+               "depression_and_anxietyOnly depressive disorder" = "Only depressive disorder",
+               "depression_and_anxietyOnly anxiety disorder" = "Only anxiety disorder",
+               "eating_disordersEating disorder" = "Eating disorders",
+               "obsessive_compulsive_disordersObsessive compulsive disorder" = "OCDs",
+               "bipolar_and_schizophreniaPsychotic and bipolar disorder" = "Psychotic and bipolar disorder",
+               "bipolar_and_schizophreniaOnly psychotic disorder" = "Only psychotic disorder",
+               "bipolar_and_schizophreniaOnly bipolar disorder" = "Only bipolar disorder",
+               "psychotic_disordersPsychotic disorder" = "Psychotic disorder",
+               "mhd.mania_hypomania_bipolar_or_manicdepressionMania, hypomania, bipolar or manic-depression" = "Bipolar disorder",
+               "mhd.posttraumatic_stress_disorder_ptsdPost-traumatic stress disorder (PTSD)" = "PTSD",
+               "autism_spectrum_disorderAutism spectrum disorder" = "ASD",
+               "mhd.attention_deficit_hyperactivity_disorderAttention deficit or attention deficit and hyperactivity disorder (ADD/ADHD)" = "ADHD",
+               "mhd.personality_disorderPersonality disorder" = "Personality disorder",
+               "Gender_collapsedFemale" = "Female",
+               "Gender_collapsedNon-binary/Self-defined" = "Non-binary/Self-defined",
+               "age_category_collapsed19-25" = "19-25 years",
+               "age_category_collapsed26-35" = "26-35 years",
+               "age_category_collapsed36-45" = "36-45 years",
+               "age_category_collapsed46-55" = "46-55 years",
+               "age_category_collapsed56-65" = "56-65 years",
+               "age_category_collapsed66-70" = "66-70 years",
+               "age_category_collapsed71-75" = "71-75 years",
+               "age_category_collapsed76+" = "76+ years",
+               "Ethnicity_collapsedMixed or multiple ethnic origins" = "Mixed or multiple ethnic origins",
+               "Ethnicity_collapsedAsian or Asian British" = "Asian or Asian British",
+               "Ethnicity_collapsedAfrican or African British" = "African or African British",
+               "Ethnicity_collapsedOther" = "Other ethnicity",
+               "key_workerKey worker" = "Key worker",
+               "time_diff_coping_lockdown_march_23" = "Time difference: Lockdown to baseline", 
+               "highest_educationNVQ" = "Highest education NVQ", 
+               "highest_educationA-levels" = "Highest education A-Levels",
+               "highest_educationUniversity" = "Highest education University"
+             ),
+             "Estimate" = format(
+               round(estimate,
+                     digits = 2),
+               nsmall = 2),
+             "95% CI low" = format(
+               round(conf.low,
+                     digits = 2),
+               nsmall = 2),
+             "95% CI up" = format(
+               round(conf.high,
+                     digits = 2),
+               nsmall = 2),
+             "SE" = format(
+               round(std.error,
+                     digits = 2),
+               nsmall = 2),
+             "z score" = format(
+               round(statistic,
+                     digits = 2),
+               nsmall = 2),
+             "p value" = case_when(
+               p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
+               p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
+               p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
+             )
+           ) %>%
+           select(
+             "Indepent variable",
+             "Estimate",
+             "95% CI low",
+             "95% CI up",
+             "SE",
+             #    "z score",
+             "p value"
+           )
+  )
+
+  return(get(paste0(outcome,"model1b_estimates")))
+}
+
+model1b.reg.stats <- function(outcome, data_set) {
+  # define the variable name of the dependent variable
+  dependent.variable <- outcome
+  # define the independent variables
+  independent.variables <- c("Disorder_hierarchical")
+  # create the formula
+  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
+  glm.formula
+
+  # run the glm
+  assign(paste0(outcome,".model1b"),
+         lm( formula = glm.formula,
+             data = get(data_set)
+         )
+  )
+
+  assign(paste0(outcome,"model1b_reg_stats"),
+         glance(get(paste0(outcome,".model1b"))) %>%
+           mutate(
+             "n" = format(
+               round(nobs,
+                     digits = 0),
+               nsmall = 0),
+             "R2" = format(
+               round(r.squared,
+                     digits = 2),
+               nsmall = 2),
+             "adjust. R2" = format(
+               round(adj.r.squared,
+                     digits = 2),
+               nsmall = 2),
+             "F" = format(
+               round(statistic,
+                     digits = 2),
+               nsmall = 2),
+             "p value" = case_when(
+               p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
+               p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
+               p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
+             )
+           ) %>%
+           select(
+             "n",
+             "R2",
+             "adjust. R2",
+             "F",
+             "p value",
+             "df"
+           )
+  )
+
+  return(get(paste0(outcome,"model1b_reg_stats")))
+}
+```
+
+```{r model1b.explan education function}
+model1b.explan.estimates <- function(outcome, explan_var, data_set) {
+  # define the variable name of the dependent variable
+  dependent.variable <- outcome
+  # define the independent variables
+  independent.variables <- c(explan_var,
+                             "depression_and_anxiety",
+                             "eating_disorders",
+                             "obsessive_compulsive_disorders",
+                             "bipolar_and_schizophrenia",
+                             "mhd.posttraumatic_stress_disorder_ptsd",
+                             "autism_spectrum_disorder",
+                             "mhd.attention_deficit_hyperactivity_disorder",
+                             "mhd.personality_disorder",
+                             "Gender_collapsed",
+                             "age_category_collapsed",
+                             "Ethnicity_collapsed",
+                             "key_worker",
+                             "time_diff_coping_lockdown_march_23", 
+                             "highest_education"
+  )
+  # create the formula
+  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
+  glm.formula
+
+  # run the glm
+  assign(paste0(outcome,".",explan_var,".model1b.explan"),
+         lm( formula = glm.formula,
+             data = get(data_set)
+         )
+  )
+
+  assign(paste0(outcome,".",explan_var,"model1b.explan_estimates"),
+         tidy(get(paste0(outcome,".",explan_var,".model1b.explan")), conf.int = TRUE) %>%
+           mutate(
+             "Indepent variable" = recode_factor(
+               term,
+               "(Intercept)" = "Intercept",
+               "anxiety_disordersAnxiety disorder" = "Anxiety disorders",
+               "depressive_disordersDepressive disorder" = "Depressive disorders",
+               "depression_and_anxietyDepressive and anxiety disorder" = "Depressive and anxiety disorder",
+               "depression_and_anxietyOnly depressive disorder" = "Only depressive disorder",
+               "depression_and_anxietyOnly anxiety disorder" = "Only anxiety disorder",
+               "eating_disordersEating disorder" = "Eating disorders",
+               "obsessive_compulsive_disordersObsessive compulsive disorder" = "OCDs",
+               "bipolar_and_schizophreniaPsychotic and bipolar disorder" = "Psychotic and bipolar disorder",
+               "bipolar_and_schizophreniaOnly psychotic disorder" = "Only psychotic disorder",
+               "bipolar_and_schizophreniaOnly bipolar disorder" = "Only bipolar disorder",
+               "psychotic_disordersPsychotic disorder" = "Psychotic disorder",
+               "mhd.mania_hypomania_bipolar_or_manicdepressionMania, hypomania, bipolar or manic-depression" = "Bipolar disorder",
+               "mhd.posttraumatic_stress_disorder_ptsdPost-traumatic stress disorder (PTSD)" = "PTSD",
+               "autism_spectrum_disorderAutism spectrum disorder" = "ASD",
+               "mhd.attention_deficit_hyperactivity_disorderAttention deficit or attention deficit and hyperactivity disorder (ADD/ADHD)" = "ADHD",
+               "mhd.personality_disorderPersonality disorder" = "Personality disorder",
+               "Gender_collapsedFemale" = "Female",
+               "Gender_collapsedNon-binary/Self-defined" = "Non-binary/Self-defined",
+               "age_category_collapsed19-25" = "19-25 years",
+               "age_category_collapsed26-35" = "26-35 years",
+               "age_category_collapsed36-45" = "36-45 years",
+               "age_category_collapsed46-55" = "46-55 years",
+               "age_category_collapsed56-65" = "56-65 years",
+               "age_category_collapsed66-70" = "66-70 years",
+               "age_category_collapsed71-75" = "71-75 years",
+               "age_category_collapsed76+" = "76+ years",
+               "Ethnicity_collapsedMixed or multiple ethnic origins" = "Mixed or multiple ethnic origins",
+               "Ethnicity_collapsedAsian or Asian British" = "Asian or Asian British",
+               "Ethnicity_collapsedAfrican or African British" = "African or African British",
+               "Ethnicity_collapsedOther" = "Other ethnicity",
+               "key_workerKey worker" = "Key worker",
+               "time_diff_coping_lockdown_march_23" = "Time difference: Lockdown to baseline", 
+               "highest_educationNVQ" = "Highest education NVQ", 
+               "highest_educationA-levels" = "Highest education A-Levels",
+               "highest_educationUniversity" = "Highest education University"
+             ),
+             "Estimate" = format(
+               round(estimate,
+                     digits = 2),
+               nsmall = 2),
+             "95% CI low" = format(
+               round(conf.low,
+                     digits = 2),
+               nsmall = 2),
+             "95% CI up" = format(
+               round(conf.high,
+                     digits = 2),
+               nsmall = 2),
+             "SE" = format(
+               round(std.error,
+                     digits = 2),
+               nsmall = 2),
+             "z score" = format(
+               round(statistic,
+                     digits = 2),
+               nsmall = 2),
+             "p value" = case_when(
+               p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
+               p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
+               p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
+             )
+           ) %>%
+           select(
+             "Indepent variable",
+             "Estimate",
+             "95% CI low",
+             "95% CI up",
+             "SE",
+             #    "z score",
+             "p value"
+           )
+  )
+
+  return(get(paste0(outcome,".",explan_var,"model1b.explan_estimates")))
+}
+
+model1b.explan.reg.stats <- function(outcome, explan_var, data_set) {
+  # define the variable name of the dependent variable
+  dependent.variable <- outcome
+  # define the independent variables
+  independent.variables <- c("Disorder_hierarchical")
+  # create the formula
+  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
+  glm.formula
+
+  # run the glm
+  assign(paste0(outcome,".",explan_var,".model1b.explan"),
+         lm( formula = glm.formula,
+             data = get(data_set)
+         )
+  )
+
+  assign(paste0(outcome,".",explan_var,"model1b.explan_reg_stats"),
+         glance(get(paste0(outcome,".",explan_var,".model1b.explan"))) %>%
+           mutate(
+             "n" = format(
+               round(nobs,
+                     digits = 0),
+               nsmall = 0),
+             "R2" = format(
+               round(r.squared,
+                     digits = 2),
+               nsmall = 2),
+             "adjust. R2" = format(
+               round(adj.r.squared,
+                     digits = 2),
+               nsmall = 2),
+             "F" = format(
+               round(statistic,
+                     digits = 2),
+               nsmall = 2),
+             "p value" = case_when(
+               p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
+               p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
+               p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
+             )
+           ) %>%
+           select(
+             "n",
+             "R2",
+             "adjust. R2",
+             "F",
+             "p value",
+             "df"
+           )
+  )
+
+  return(get(paste0(outcome,".",explan_var,"model1b.explan_reg_stats")))
+}
+```
 
@@
 ## Regression: Absolute scores
-
 ### Model 1b: Overlapping disorders, Adjusted
@@
 gad_prepan_model1b_education_estimates <- model1b.explan.estimates(outcome = "gad.sum_score_base",
-                         explan_var = "highest_education_numeric",
+                         explan_var = "pcl.sum_score_prepan",
                          data_set = "dat.prepan")
@@
 gad_prepan_model1b_education_reg_stats <- model1b.explan.reg.stats(outcome = "gad.sum_score_base",
-                         explan_var = "highest_education_numeric",
+                         explan_var = "pcl.sum_score_prepan",
                          data_set = "dat.prepan")
@@
 phq_prepan_model1b_education_estimates <- model1b.explan.estimates(outcome = "phq.sum_score_base",
-                         explan_var = "highest_education_numeric",
+                         explan_var = "pcl.sum_score_prepan",
                          data_set = "dat.prepan")
@@
 phq_prepan_model1b_education_reg_stats <- model1b.explan.reg.stats(outcome = "phq.sum_score_base",
-                         explan_var = "highest_education_numeric",
+                         explan_var = "pcl.sum_score_prepan",
                          data_set = "dat.prepan")
@@
 phq_prepan_model1b_education_reg_stats
-```
-
-# OCIR prepan 
-## Regression: Absolute scores
-
-### Model 1b: Overlapping disorders, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
-```{r ocir education sensitivity model1b sum_score prepan}
-# Regression coefficients
-ocir_prepan_model1b_education_estimates <- model1b.explan.estimates(outcome = "ocir.sum_score_base",
-                         explan_var = "highest_education_numeric",
-                         data_set = "dat.prepan")
-kable(ocir_prepan_model1b_education_estimates)
-ocir_prepan_model1b_education_estimates
-
-# Regression diagnostic statistics
-ocir_prepan_model1b_education_reg_stats <- model1b.explan.reg.stats(outcome = "ocir.sum_score_base",
-                         explan_var = "highest_education_numeric",
-                         data_set = "dat.prepan")
-kable(ocir_prepan_model1b_education_reg_stats)
-ocir_prepan_model1b_education_reg_stats
-```
-
-#PCL prepan 
-## Regression: Absolute scores
-
-### Model 1b: Overlapping disorders, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
-```{r pcl education sensitivty model1b sum_score prepan}
-# Regression coefficients
-pcl_prepan_model1b_education_estimates <- model1b.explan.estimates(outcome = "pcl.sum_score_base",
-                         explan_var = "highest_education_numeric",
-                         data_set = "dat.prepan")
-kable(pcl_prepan_model1b_education_estimates)
-pcl_prepan_model1b_education_estimates
-
-# Regression diagnostic statistics
-pcl_prepan_model1b_education_reg_stats <- model1b.explan.reg.stats(outcome = "pcl.sum_score_base",
-                         explan_var = "highest_education_numeric",
-                         data_set = "dat.prepan")
-kable(pcl_prepan_model1b_education_reg_stats)
-pcl_prepan_model1b_education_reg_stats
-```
-
-# SENSITIVITY based on employment status
-
-# GAD prepan
-## Regression: Absolute scores
-
-### Model 1b: Overlapping disorders, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
-```{r gad employment sensitivity model1b sum_score prepan}
-# Regression coefficients
-gad_prepan_model1b_employment_estimates <- model1b.explan.estimates(outcome = "gad.sum_score_base",
-                         explan_var = "employment.unemployed_numeric",
-                         data_set = "dat.prepan")
-kable(gad_prepan_model1b_employment_estimates)
-gad_prepan_model1b_employment_estimates
-
-# Regression diagnostic statistics
-gad_prepan_model1b_employment_reg_stats <- model1b.explan.reg.stats(outcome = "gad.sum_score_base",
-                         explan_var = "employment.unemployed_numeric",
-                         data_set = "dat.prepan")
-kable(gad_prepan_model1b_employment_reg_stats)
-gad_prepan_model1b_employment_reg_stats
-```
-
-# PHQ prepan
-## Regression: Absolute scores
-
-### Model 1b: Overlapping disorders, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
-```{r phq employment sensitivity model1b sum_score prepan}
-# Regression coefficients
-phq_prepan_model1b_employment_estimates <- model1b.explan.estimates(outcome = "phq.sum_score_base",
-                         explan_var = "employment.unemployed_numeric",
-                         data_set = "dat.prepan")
-kable(phq_prepan_model1b_employment_estimates)
-phq_prepan_model1b_employment_estimates
-
-# Regression diagnostic statistics
-phq_prepan_model1b_employment_reg_stats <- model1b.explan.reg.stats(outcome = "phq.sum_score_base",
-                         explan_var = "employment.unemployed_numeric",
-                         data_set = "dat.prepan")
-kable(phq_prepan_model1b_employment_reg_stats)
-phq_prepan_model1b_employment_reg_stats
 ```
@@
 Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
-```{r ocir employment sensitivity model1b sum_score prepan}
-# Regression coefficients
-ocir_prepan_model1b_employment_estimates <- model1b.explan.estimates(outcome = "ocir.sum_score_base",
-                         explan_var = "employment.unemployed_numeric",
-                         data_set = "dat.prepan")
-kable(ocir_prepan_model1b_employment_estimates)
-ocir_prepan_model1b_employment_estimates
-
-# Regression diagnostic statistics
-ocir_prepan_model1b_employment_reg_stats <- model1b.explan.reg.stats(outcome = "ocir.sum_score_base",
-                         explan_var = "employment.unemployed_numeric",
-                         data_set = "dat.prepan")
-kable(ocir_prepan_model1b_employment_reg_stats)
-ocir_prepan_model1b_employment_reg_stats
+```{r ocir education sensitivity model1b sum_score prepan}
+# Regression coefficients
+ocir_prepan_model1b_education_estimates <- model1b.explan.estimates(outcome = "ocir.sum_score_base",
+                         explan_var = "pcl.sum_score_prepan",
+                         data_set = "dat.prepan")
+kable(ocir_prepan_model1b_education_estimates)
+ocir_prepan_model1b_education_estimates
+
+# Regression diagnostic statistics
+ocir_prepan_model1b_education_reg_stats <- model1b.explan.reg.stats(outcome = "ocir.sum_score_base",
+                         explan_var = "pcl.sum_score_prepan",
+                         data_set = "dat.prepan")
+kable(ocir_prepan_model1b_education_reg_stats)
+ocir_prepan_model1b_education_reg_stats
 ```
@@
 ## Regression: Absolute scores
-
 ### Model 1b: Overlapping disorders, Adjusted
 Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
-```{r pcl employment sensitivty model1b sum_score prepan}
-# Regression coefficients
-pcl_prepan_model1b_employment_estimates <- model1b.explan.estimates(outcome = "pcl.sum_score_base",
-                         explan_var = "employment.unemployed_numeric",
-                         data_set = "dat.prepan")
-kable(pcl_prepan_model1b_employment_estimates)
-pcl_prepan_model1b_employment_estimates
-
-# Regression diagnostic statistics
-pcl_prepan_model1b_employment_reg_stats <- model1b.explan.reg.stats(outcome = "pcl.sum_score_base",
-                         explan_var = "employment.unemployed_numeric",
-                         data_set = "dat.prepan")
-kable(pcl_prepan_model1b_employment_reg_stats)
-pcl_prepan_model1b_employment_reg_stats
-```
-
-# SENSITIVITY based on employment change
-
-```{r create an employment change variable}
-dat.prepan <- dat.prepan %>%
-  mutate(employment_change =
-           case_when(
-             employment.unemployed_numeric == "1" ~ "Unemployed",
-             employment.became_unemployed_numeric == "1" ~ "Became Unemployed",                         
-             employment.furloughed_or_paid_leave_government_funded_numeric == "1" ~ "Furlough",
-             employment.furloughed_or_paid_leave_company_funded_numeric == "1" ~ "Furlough",    
-             employment.paid_leave_furloughed_numeric == "1" ~ "Furlough",                             
-             key_worker_numeric == "1" ~ "Key Worker",                                            
-             employment.government_work_key_workers_numeric == "1" ~ "Key Worker",                
-             employment.zerohours_contract_numeric == "1" ~ "Zero Hours Contract",                         
-             employment.retired_numeric == "1" ~ "Retired",                                   
-             employment.student_gcse_or_a_level_numeric == "1" ~ "Student",                   
-             employment.student_university_numeric == "1" ~ "Student"                        
-           )
-  )
-
-dat.prepan$employment_change <- as.factor(dat.prepan$employment_change)
+```{r pcl education sensitivty model1b sum_score prepan}
+# Regression coefficients
+pcl_prepan_model1b_education_estimates <- model1b.explan.estimates(outcome = "pcl.sum_score_base",
+                         explan_var = "pcl.sum_score_prepan",
+                         data_set = "dat.prepan")
+kable(pcl_prepan_model1b_education_estimates)
+pcl_prepan_model1b_education_estimates
+
+# Regression diagnostic statistics
+pcl_prepan_model1b_education_reg_stats <- model1b.explan.reg.stats(outcome = "pcl.sum_score_base",
+                         explan_var = "pcl.sum_score_prepan",
+                         data_set = "dat.prepan")
+kable(pcl_prepan_model1b_education_reg_stats)
+pcl_prepan_model1b_education_reg_stats
+```
+
+# Sensitivity anlayses based on employment prior to covid
+# Function change to include employment prior to covid as predictors
+
+```{r model1b employment prior covid function}
+model1b.estimates <- function(outcome, data_set) {
+  # define the variable name of the dependent variable
+  dependent.variable <- outcome
+  # define the independent variables
+  independent.variables <- c("depression_and_anxiety",
+                             "eating_disorders",
+                             "obsessive_compulsive_disorders",
+                             "bipolar_and_schizophrenia",
+                             "mhd.posttraumatic_stress_disorder_ptsd",
+                             "autism_spectrum_disorder",
+                             "mhd.attention_deficit_hyperactivity_disorder",
+                             "mhd.personality_disorder",
+                             "Gender_collapsed",
+                             "age_category_collapsed",
+                             "Ethnicity_collapsed",
+                             "key_worker",
+                             "time_diff_coping_lockdown_march_23", 
+                             "employment_prior_covid"
+                                )
+  # create the formula
+  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
+  glm.formula
+
+  # run the glm
+  assign(paste0(outcome,".model1b"),
+         lm( formula = glm.formula,
+             data = get(data_set)
+         )
+  )
+
+  assign(paste0(outcome,"model1b_estimates"),
+         tidy(get(paste0(outcome,".model1b")), conf.int = TRUE) %>%
+           mutate(
+             "Indepent variable" = recode_factor(
+               term,
+               "(Intercept)" = "Intercept",
+               "anxiety_disordersAnxiety disorder" = "Anxiety disorders",
+               "depressive_disordersDepressive disorder" = "Depressive disorders",
+               "depression_and_anxietyDepressive and anxiety disorder" = "Depressive and anxiety disorder",
+               "depression_and_anxietyOnly depressive disorder" = "Only depressive disorder",
+               "depression_and_anxietyOnly anxiety disorder" = "Only anxiety disorder",
+               "eating_disordersEating disorder" = "Eating disorders",
+               "obsessive_compulsive_disordersObsessive compulsive disorder" = "OCDs",
+               "bipolar_and_schizophreniaPsychotic and bipolar disorder" = "Psychotic and bipolar disorder",
+               "bipolar_and_schizophreniaOnly psychotic disorder" = "Only psychotic disorder",
+               "bipolar_and_schizophreniaOnly bipolar disorder" = "Only bipolar disorder",
+               "psychotic_disordersPsychotic disorder" = "Psychotic disorder",
+               "mhd.mania_hypomania_bipolar_or_manicdepressionMania, hypomania, bipolar or manic-depression" = "Bipolar disorder",
+               "mhd.posttraumatic_stress_disorder_ptsdPost-traumatic stress disorder (PTSD)" = "PTSD",
+               "autism_spectrum_disorderAutism spectrum disorder" = "ASD",
+               "mhd.attention_deficit_hyperactivity_disorderAttention deficit or attention deficit and hyperactivity disorder (ADD/ADHD)" = "ADHD",
+               "mhd.personality_disorderPersonality disorder" = "Personality disorder",
+               "Gender_collapsedFemale" = "Female",
+               "Gender_collapsedNon-binary/Self-defined" = "Non-binary/Self-defined",
+               "age_category_collapsed19-25" = "19-25 years",
+               "age_category_collapsed26-35" = "26-35 years",
+               "age_category_collapsed36-45" = "36-45 years",
+               "age_category_collapsed46-55" = "46-55 years",
+               "age_category_collapsed56-65" = "56-65 years",
+               "age_category_collapsed66-70" = "66-70 years",
+               "age_category_collapsed71-75" = "71-75 years",
+               "age_category_collapsed76+" = "76+ years",
+               "Ethnicity_collapsedMixed or multiple ethnic origins" = "Mixed or multiple ethnic origins",
+               "Ethnicity_collapsedAsian or Asian British" = "Asian or Asian British",
+               "Ethnicity_collapsedAfrican or African British" = "African or African British",
+               "Ethnicity_collapsedOther" = "Other ethnicity",
+               "key_workerKey worker" = "Key worker",
+               "time_diff_coping_lockdown_march_23" = "Time difference: Lockdown to baseline", 
+               "employment_prior_covidEmployed" = "Employed",
+               "employment_prior_covidUnemployed" = "Unemployed",
+               "employment_prior_covidRetired" = "Retired",
+               "employment_prior_covidStudent" = "Student"
+             ),
+             "Estimate" = format(
+               round(estimate,
+                     digits = 2),
+               nsmall = 2),
+             "95% CI low" = format(
+               round(conf.low,
+                     digits = 2),
+               nsmall = 2),
+             "95% CI up" = format(
+               round(conf.high,
+                     digits = 2),
+               nsmall = 2),
+             "SE" = format(
+               round(std.error,
+                     digits = 2),
+               nsmall = 2),
+             "z score" = format(
+               round(statistic,
+                     digits = 2),
+               nsmall = 2),
+             "p value" = case_when(
+               p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
+               p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
+               p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
+             )
+           ) %>%
+           select(
+             "Indepent variable",
+             "Estimate",
+             "95% CI low",
+             "95% CI up",
+             "SE",
+             #    "z score",
+             "p value"
+           )
+  )
+
+  return(get(paste0(outcome,"model1b_estimates")))
+}
+
+model1b.reg.stats <- function(outcome, data_set) {
+  # define the variable name of the dependent variable
+  dependent.variable <- outcome
+  # define the independent variables
+  independent.variables <- c("Disorder_hierarchical")
+  # create the formula
+  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
+  glm.formula
+
+  # run the glm
+  assign(paste0(outcome,".model1b"),
+         lm( formula = glm.formula,
+             data = get(data_set)
+         )
+  )
+
+  assign(paste0(outcome,"model1b_reg_stats"),
+         glance(get(paste0(outcome,".model1b"))) %>%
+           mutate(
+             "n" = format(
+               round(nobs,
+                     digits = 0),
+               nsmall = 0),
+             "R2" = format(
+               round(r.squared,
+                     digits = 2),
+               nsmall = 2),
+             "adjust. R2" = format(
+               round(adj.r.squared,
+                     digits = 2),
+               nsmall = 2),
+             "F" = format(
+               round(statistic,
+                     digits = 2),
+               nsmall = 2),
+             "p value" = case_when(
+               p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
+               p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
+               p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
+             )
+           ) %>%
+           select(
+             "n",
+             "R2",
+             "adjust. R2",
+             "F",
+             "p value",
+             "df"
+           )
+  )
+
+  return(get(paste0(outcome,"model1b_reg_stats")))
+}
+```
+
+```{r model1b.explan employment prior covid function}
+model1b.explan.estimates <- function(outcome, explan_var, data_set) {
+  # define the variable name of the dependent variable
+  dependent.variable <- outcome
+  # define the independent variables
+  independent.variables <- c(explan_var,
+                             "depression_and_anxiety",
+                             "eating_disorders",
+                             "obsessive_compulsive_disorders",
+                             "bipolar_and_schizophrenia",
+                             "mhd.posttraumatic_stress_disorder_ptsd",
+                             "autism_spectrum_disorder",
+                             "mhd.attention_deficit_hyperactivity_disorder",
+                             "mhd.personality_disorder",
+                             "Gender_collapsed",
+                             "age_category_collapsed",
+                             "Ethnicity_collapsed",
+                             "key_worker",
+                             "time_diff_coping_lockdown_march_23", 
+                             "employment_prior_covid"
+  )
+  # create the formula
+  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
+  glm.formula
+
+  # run the glm
+  assign(paste0(outcome,".",explan_var,".model1b.explan"),
+         lm( formula = glm.formula,
+             data = get(data_set)
+         )
+  )
+
+  assign(paste0(outcome,".",explan_var,"model1b.explan_estimates"),
+         tidy(get(paste0(outcome,".",explan_var,".model1b.explan")), conf.int = TRUE) %>%
+           mutate(
+             "Indepent variable" = recode_factor(
+               term,
+               "(Intercept)" = "Intercept",
+               "anxiety_disordersAnxiety disorder" = "Anxiety disorders",
+               "depressive_disordersDepressive disorder" = "Depressive disorders",
+               "depression_and_anxietyDepressive and anxiety disorder" = "Depressive and anxiety disorder",
+               "depression_and_anxietyOnly depressive disorder" = "Only depressive disorder",
+               "depression_and_anxietyOnly anxiety disorder" = "Only anxiety disorder",
+               "eating_disordersEating disorder" = "Eating disorders",
+               "obsessive_compulsive_disordersObsessive compulsive disorder" = "OCDs",
+               "bipolar_and_schizophreniaPsychotic and bipolar disorder" = "Psychotic and bipolar disorder",
+               "bipolar_and_schizophreniaOnly psychotic disorder" = "Only psychotic disorder",
+               "bipolar_and_schizophreniaOnly bipolar disorder" = "Only bipolar disorder",
+               "psychotic_disordersPsychotic disorder" = "Psychotic disorder",
+               "mhd.mania_hypomania_bipolar_or_manicdepressionMania, hypomania, bipolar or manic-depression" = "Bipolar disorder",
+               "mhd.posttraumatic_stress_disorder_ptsdPost-traumatic stress disorder (PTSD)" = "PTSD",
+               "autism_spectrum_disorderAutism spectrum disorder" = "ASD",
+               "mhd.attention_deficit_hyperactivity_disorderAttention deficit or attention deficit and hyperactivity disorder (ADD/ADHD)" = "ADHD",
+               "mhd.personality_disorderPersonality disorder" = "Personality disorder",
+               "Gender_collapsedFemale" = "Female",
+               "Gender_collapsedNon-binary/Self-defined" = "Non-binary/Self-defined",
+               "age_category_collapsed19-25" = "19-25 years",
+               "age_category_collapsed26-35" = "26-35 years",
+               "age_category_collapsed36-45" = "36-45 years",
+               "age_category_collapsed46-55" = "46-55 years",
+               "age_category_collapsed56-65" = "56-65 years",
+               "age_category_collapsed66-70" = "66-70 years",
+               "age_category_collapsed71-75" = "71-75 years",
+               "age_category_collapsed76+" = "76+ years",
+               "Ethnicity_collapsedMixed or multiple ethnic origins" = "Mixed or multiple ethnic origins",
+               "Ethnicity_collapsedAsian or Asian British" = "Asian or Asian British",
+               "Ethnicity_collapsedAfrican or African British" = "African or African British",
+               "Ethnicity_collapsedOther" = "Other ethnicity",
+               "key_workerKey worker" = "Key worker",
+               "time_diff_coping_lockdown_march_23" = "Time difference: Lockdown to baseline", 
+               "employment_prior_covidEmployed" = "Employed",
+               "employment_prior_covidUnemployed" = "Unemployed",
+               "employment_prior_covidRetired" = "Retired",
+               "employment_prior_covidStudent" = "Student"
+             ),
+             "Estimate" = format(
+               round(estimate,
+                     digits = 2),
+               nsmall = 2),
+             "95% CI low" = format(
+               round(conf.low,
+                     digits = 2),
+               nsmall = 2),
+             "95% CI up" = format(
+               round(conf.high,
+                     digits = 2),
+               nsmall = 2),
+             "SE" = format(
+               round(std.error,
+                     digits = 2),
+               nsmall = 2),
+             "z score" = format(
+               round(statistic,
+                     digits = 2),
+               nsmall = 2),
+             "p value" = case_when(
+               p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
+               p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
+               p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
+             )
+           ) %>%
+           select(
+             "Indepent variable",
+             "Estimate",
+             "95% CI low",
+             "95% CI up",
+             "SE",
+             #    "z score",
+             "p value"
+           )
+  )
+
+  return(get(paste0(outcome,".",explan_var,"model1b.explan_estimates")))
+}
+
+model1b.explan.reg.stats <- function(outcome, explan_var, data_set) {
+  # define the variable name of the dependent variable
+  dependent.variable <- outcome
+  # define the independent variables
+  independent.variables <- c("Disorder_hierarchical")
+  # create the formula
+  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
+  glm.formula
+
+  # run the glm
+  assign(paste0(outcome,".",explan_var,".model1b.explan"),
+         lm( formula = glm.formula,
+             data = get(data_set)
+         )
+  )
+
+  assign(paste0(outcome,".",explan_var,"model1b.explan_reg_stats"),
+         glance(get(paste0(outcome,".",explan_var,".model1b.explan"))) %>%
+           mutate(
+             "n" = format(
+               round(nobs,
+                     digits = 0),
+               nsmall = 0),
+             "R2" = format(
+               round(r.squared,
+                     digits = 2),
+               nsmall = 2),
+             "adjust. R2" = format(
+               round(adj.r.squared,
+                     digits = 2),
+               nsmall = 2),
+             "F" = format(
+               round(statistic,
+                     digits = 2),
+               nsmall = 2),
+             "p value" = case_when(
+               p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
+               p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
+               p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
+             )
+           ) %>%
+           select(
+             "n",
+             "R2",
+             "adjust. R2",
+             "F",
+             "p value",
+             "df"
+           )
+  )
+
+  return(get(paste0(outcome,".",explan_var,"model1b.explan_reg_stats")))
+}
+```
+
+# GAD prepan
+## Regression: Absolute scores
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r gad employment prior covid sensitivity model1b sum_score prepan}
+# Regression coefficients
+gad_prepan_model1b_education_estimates <- model1b.explan.estimates(outcome = "gad.sum_score_base",
+                         explan_var = "pcl.sum_score_prepan",
+                         data_set = "dat.prepan")
+kable(gad_prepan_model1b_education_estimates)
+gad_prepan_model1b_education_estimates
+
+# Regression diagnostic statistics
+gad_prepan_model1b_education_reg_stats <- model1b.explan.reg.stats(outcome = "gad.sum_score_base",
+                         explan_var = "pcl.sum_score_prepan",
+                         data_set = "dat.prepan")
+kable(gad_prepan_model1b_education_reg_stats)
+gad_prepan_model1b_education_reg_stats
+```
+
+# PHQ prepan
+## Regression: Absolute scores
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r phq employment prior covid sensitivity model1b sum_score prepan}
+# Regression coefficients
+phq_prepan_model1b_education_estimates <- model1b.explan.estimates(outcome = "phq.sum_score_base",
+                         explan_var = "pcl.sum_score_prepan",
+                         data_set = "dat.prepan")
+kable(phq_prepan_model1b_education_estimates)
+phq_prepan_model1b_education_estimates
+
+# Regression diagnostic statistics
+phq_prepan_model1b_education_reg_stats <- model1b.explan.reg.stats(outcome = "phq.sum_score_base",
+                         explan_var = "pcl.sum_score_prepan",
+                         data_set = "dat.prepan")
+kable(phq_prepan_model1b_education_reg_stats)
+phq_prepan_model1b_education_reg_stats
+```
+
+# OCIR prepan 
+## Regression: Absolute scores
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r ocir employment prior covid sensitivity model1b sum_score prepan}
+# Regression coefficients
+ocir_prepan_model1b_education_estimates <- model1b.explan.estimates(outcome = "ocir.sum_score_base",
+                         explan_var = "pcl.sum_score_prepan",
+                         data_set = "dat.prepan")
+kable(ocir_prepan_model1b_education_estimates)
+ocir_prepan_model1b_education_estimates
+
+# Regression diagnostic statistics
+ocir_prepan_model1b_education_reg_stats <- model1b.explan.reg.stats(outcome = "ocir.sum_score_base",
+                         explan_var = "pcl.sum_score_prepan",
+                         data_set = "dat.prepan")
+kable(ocir_prepan_model1b_education_reg_stats)
+ocir_prepan_model1b_education_reg_stats
+```
+
+#PCL prepan 
+## Regression: Absolute scores
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r pcl employment prior covid sensitivty model1b sum_score prepan}
+# Regression coefficients
+pcl_prepan_model1b_education_estimates <- model1b.explan.estimates(outcome = "pcl.sum_score_base",
+                         explan_var = "pcl.sum_score_prepan",
+                         data_set = "dat.prepan")
+kable(pcl_prepan_model1b_education_estimates)
+pcl_prepan_model1b_education_estimates
+
+# Regression diagnostic statistics
+pcl_prepan_model1b_education_reg_stats <- model1b.explan.reg.stats(outcome = "pcl.sum_score_base",
+                         explan_var = "pcl.sum_score_prepan",
+                         data_set = "dat.prepan")
+kable(pcl_prepan_model1b_education_reg_stats)
+pcl_prepan_model1b_education_reg_stats
+```
+
+# Sensitivity anlayses based on employment change
+# Function change to include employment change as predictors
+
+```{r model1b employment change function}
+model1b.estimates <- function(outcome, data_set) {
+  # define the variable name of the dependent variable
+  dependent.variable <- outcome
+  # define the independent variables
+  independent.variables <- c("depression_and_anxiety",
+                             "eating_disorders",
+                             "obsessive_compulsive_disorders",
+                             "bipolar_and_schizophrenia",
+                             "mhd.posttraumatic_stress_disorder_ptsd",
+                             "autism_spectrum_disorder",
+                             "mhd.attention_deficit_hyperactivity_disorder",
+                             "mhd.personality_disorder",
+                             "Gender_collapsed",
+                             "age_category_collapsed",
+                             "Ethnicity_collapsed",
+                             "key_worker",
+                             "time_diff_coping_lockdown_march_23", 
+                             "employment_change"
+                                )
+  # create the formula
+  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
+  glm.formula
+
+  # run the glm
+  assign(paste0(outcome,".model1b"),
+         lm( formula = glm.formula,
+             data = get(data_set)
+         )
+  )
+
+  assign(paste0(outcome,"model1b_estimates"),
+         tidy(get(paste0(outcome,".model1b")), conf.int = TRUE) %>%
+           mutate(
+             "Indepent variable" = recode_factor(
+               term,
+               "(Intercept)" = "Intercept",
+               "anxiety_disordersAnxiety disorder" = "Anxiety disorders",
+               "depressive_disordersDepressive disorder" = "Depressive disorders",
+               "depression_and_anxietyDepressive and anxiety disorder" = "Depressive and anxiety disorder",
+               "depression_and_anxietyOnly depressive disorder" = "Only depressive disorder",
+               "depression_and_anxietyOnly anxiety disorder" = "Only anxiety disorder",
+               "eating_disordersEating disorder" = "Eating disorders",
+               "obsessive_compulsive_disordersObsessive compulsive disorder" = "OCDs",
+               "bipolar_and_schizophreniaPsychotic and bipolar disorder" = "Psychotic and bipolar disorder",
+               "bipolar_and_schizophreniaOnly psychotic disorder" = "Only psychotic disorder",
+               "bipolar_and_schizophreniaOnly bipolar disorder" = "Only bipolar disorder",
+               "psychotic_disordersPsychotic disorder" = "Psychotic disorder",
+               "mhd.mania_hypomania_bipolar_or_manicdepressionMania, hypomania, bipolar or manic-depression" = "Bipolar disorder",
+               "mhd.posttraumatic_stress_disorder_ptsdPost-traumatic stress disorder (PTSD)" = "PTSD",
+               "autism_spectrum_disorderAutism spectrum disorder" = "ASD",
+               "mhd.attention_deficit_hyperactivity_disorderAttention deficit or attention deficit and hyperactivity disorder (ADD/ADHD)" = "ADHD",
+               "mhd.personality_disorderPersonality disorder" = "Personality disorder",
+               "Gender_collapsedFemale" = "Female",
+               "Gender_collapsedNon-binary/Self-defined" = "Non-binary/Self-defined",
+               "age_category_collapsed19-25" = "19-25 years",
+               "age_category_collapsed26-35" = "26-35 years",
+               "age_category_collapsed36-45" = "36-45 years",
+               "age_category_collapsed46-55" = "46-55 years",
+               "age_category_collapsed56-65" = "56-65 years",
+               "age_category_collapsed66-70" = "66-70 years",
+               "age_category_collapsed71-75" = "71-75 years",
+               "age_category_collapsed76+" = "76+ years",
+               "Ethnicity_collapsedMixed or multiple ethnic origins" = "Mixed or multiple ethnic origins",
+               "Ethnicity_collapsedAsian or Asian British" = "Asian or Asian British",
+               "Ethnicity_collapsedAfrican or African British" = "African or African British",
+               "Ethnicity_collapsedOther" = "Other ethnicity",
+               "key_workerKey worker" = "Key worker",
+               "time_diff_coping_lockdown_march_23" = "Time difference: Lockdown to baseline", 
+               "employment_changeDecreased employment" = "Decreased employment",
+               "employment_changeIncreased employment" = "Increased employment",
+               "employment_changeFurloughed" = "Furloughed",
+               "employment_chnageEmployment not changed" = "Employment not changed"
+             ),
+             "Estimate" = format(
+               round(estimate,
+                     digits = 2),
+               nsmall = 2),
+             "95% CI low" = format(
+               round(conf.low,
+                     digits = 2),
+               nsmall = 2),
+             "95% CI up" = format(
+               round(conf.high,
+                     digits = 2),
+               nsmall = 2),
+             "SE" = format(
+               round(std.error,
+                     digits = 2),
+               nsmall = 2),
+             "z score" = format(
+               round(statistic,
+                     digits = 2),
+               nsmall = 2),
+             "p value" = case_when(
+               p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
+               p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
+               p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
+             )
+           ) %>%
+           select(
+             "Indepent variable",
+             "Estimate",
+             "95% CI low",
+             "95% CI up",
+             "SE",
+             #    "z score",
+             "p value"
+           )
+  )
+
+  return(get(paste0(outcome,"model1b_estimates")))
+}
+
+model1b.reg.stats <- function(outcome, data_set) {
+  # define the variable name of the dependent variable
+  dependent.variable <- outcome
+  # define the independent variables
+  independent.variables <- c("Disorder_hierarchical")
+  # create the formula
+  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
+  glm.formula
+
+  # run the glm
+  assign(paste0(outcome,".model1b"),
+         lm( formula = glm.formula,
+             data = get(data_set)
+         )
+  )
+
+  assign(paste0(outcome,"model1b_reg_stats"),
+         glance(get(paste0(outcome,".model1b"))) %>%
+           mutate(
+             "n" = format(
+               round(nobs,
+                     digits = 0),
+               nsmall = 0),
+             "R2" = format(
+               round(r.squared,
+                     digits = 2),
+               nsmall = 2),
+             "adjust. R2" = format(
+               round(adj.r.squared,
+                     digits = 2),
+               nsmall = 2),
+             "F" = format(
+               round(statistic,
+                     digits = 2),
+               nsmall = 2),
+             "p value" = case_when(
+               p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
+               p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
+               p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
+             )
+           ) %>%
+           select(
+             "n",
+             "R2",
+             "adjust. R2",
+             "F",
+             "p value",
+             "df"
+           )
+  )
+
+  return(get(paste0(outcome,"model1b_reg_stats")))
+}
+```
+
+```{r model1b.explan employment change function}
+model1b.explan.estimates <- function(outcome, explan_var, data_set) {
+  # define the variable name of the dependent variable
+  dependent.variable <- outcome
+  # define the independent variables
+  independent.variables <- c(explan_var,
+                             "depression_and_anxiety",
+                             "eating_disorders",
+                             "obsessive_compulsive_disorders",
+                             "bipolar_and_schizophrenia",
+                             "mhd.posttraumatic_stress_disorder_ptsd",
+                             "autism_spectrum_disorder",
+                             "mhd.attention_deficit_hyperactivity_disorder",
+                             "mhd.personality_disorder",
+                             "Gender_collapsed",
+                             "age_category_collapsed",
+                             "Ethnicity_collapsed",
+                             "key_worker",
+                             "time_diff_coping_lockdown_march_23", 
+                             "employment_change"
+  )
+  # create the formula
+  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
+  glm.formula
+
+  # run the glm
+  assign(paste0(outcome,".",explan_var,".model1b.explan"),
+         lm( formula = glm.formula,
+             data = get(data_set)
+         )
+  )
+
+  assign(paste0(outcome,".",explan_var,"model1b.explan_estimates"),
+         tidy(get(paste0(outcome,".",explan_var,".model1b.explan")), conf.int = TRUE) %>%
+           mutate(
+             "Indepent variable" = recode_factor(
+               term,
+               "(Intercept)" = "Intercept",
+               "anxiety_disordersAnxiety disorder" = "Anxiety disorders",
+               "depressive_disordersDepressive disorder" = "Depressive disorders",
+               "depression_and_anxietyDepressive and anxiety disorder" = "Depressive and anxiety disorder",
+               "depression_and_anxietyOnly depressive disorder" = "Only depressive disorder",
+               "depression_and_anxietyOnly anxiety disorder" = "Only anxiety disorder",
+               "eating_disordersEating disorder" = "Eating disorders",
+               "obsessive_compulsive_disordersObsessive compulsive disorder" = "OCDs",
+               "bipolar_and_schizophreniaPsychotic and bipolar disorder" = "Psychotic and bipolar disorder",
+               "bipolar_and_schizophreniaOnly psychotic disorder" = "Only psychotic disorder",
+               "bipolar_and_schizophreniaOnly bipolar disorder" = "Only bipolar disorder",
+               "psychotic_disordersPsychotic disorder" = "Psychotic disorder",
+               "mhd.mania_hypomania_bipolar_or_manicdepressionMania, hypomania, bipolar or manic-depression" = "Bipolar disorder",
+               "mhd.posttraumatic_stress_disorder_ptsdPost-traumatic stress disorder (PTSD)" = "PTSD",
+               "autism_spectrum_disorderAutism spectrum disorder" = "ASD",
+               "mhd.attention_deficit_hyperactivity_disorderAttention deficit or attention deficit and hyperactivity disorder (ADD/ADHD)" = "ADHD",
+               "mhd.personality_disorderPersonality disorder" = "Personality disorder",
+               "Gender_collapsedFemale" = "Female",
+               "Gender_collapsedNon-binary/Self-defined" = "Non-binary/Self-defined",
+               "age_category_collapsed19-25" = "19-25 years",
+               "age_category_collapsed26-35" = "26-35 years",
+               "age_category_collapsed36-45" = "36-45 years",
+               "age_category_collapsed46-55" = "46-55 years",
+               "age_category_collapsed56-65" = "56-65 years",
+               "age_category_collapsed66-70" = "66-70 years",
+               "age_category_collapsed71-75" = "71-75 years",
+               "age_category_collapsed76+" = "76+ years",
+               "Ethnicity_collapsedMixed or multiple ethnic origins" = "Mixed or multiple ethnic origins",
+               "Ethnicity_collapsedAsian or Asian British" = "Asian or Asian British",
+               "Ethnicity_collapsedAfrican or African British" = "African or African British",
+               "Ethnicity_collapsedOther" = "Other ethnicity",
+               "key_workerKey worker" = "Key worker",
+               "time_diff_coping_lockdown_march_23" = "Time difference: Lockdown to baseline", 
+               "employment_changeDecreased employment" = "Decreased employment",
+               "employment_changeIncreased employment" = "Increased employment",
+               "employment_changeFurloughed" = "Furloughed",
+               "employment_chnageEmployment not changed" = "Employment not changed"
+             ),
+             "Estimate" = format(
+               round(estimate,
+                     digits = 2),
+               nsmall = 2),
+             "95% CI low" = format(
+               round(conf.low,
+                     digits = 2),
+               nsmall = 2),
+             "95% CI up" = format(
+               round(conf.high,
+                     digits = 2),
+               nsmall = 2),
+             "SE" = format(
+               round(std.error,
+                     digits = 2),
+               nsmall = 2),
+             "z score" = format(
+               round(statistic,
+                     digits = 2),
+               nsmall = 2),
+             "p value" = case_when(
+               p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
+               p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
+               p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
+             )
+           ) %>%
+           select(
+             "Indepent variable",
+             "Estimate",
+             "95% CI low",
+             "95% CI up",
+             "SE",
+             #    "z score",
+             "p value"
+           )
+  )
+
+  return(get(paste0(outcome,".",explan_var,"model1b.explan_estimates")))
+}
+
+model1b.explan.reg.stats <- function(outcome, explan_var, data_set) {
+  # define the variable name of the dependent variable
+  dependent.variable <- outcome
+  # define the independent variables
+  independent.variables <- c("Disorder_hierarchical")
+  # create the formula
+  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
+  glm.formula
+
+  # run the glm
+  assign(paste0(outcome,".",explan_var,".model1b.explan"),
+         lm( formula = glm.formula,
+             data = get(data_set)
+         )
+  )
+
+  assign(paste0(outcome,".",explan_var,"model1b.explan_reg_stats"),
+         glance(get(paste0(outcome,".",explan_var,".model1b.explan"))) %>%
+           mutate(
+             "n" = format(
+               round(nobs,
+                     digits = 0),
+               nsmall = 0),
+             "R2" = format(
+               round(r.squared,
+                     digits = 2),
+               nsmall = 2),
+             "adjust. R2" = format(
+               round(adj.r.squared,
+                     digits = 2),
+               nsmall = 2),
+             "F" = format(
+               round(statistic,
+                     digits = 2),
+               nsmall = 2),
+             "p value" = case_when(
+               p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
+               p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
+               p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
+             )
+           ) %>%
+           select(
+             "n",
+             "R2",
+             "adjust. R2",
+             "F",
+             "p value",
+             "df"
+           )
+  )
+
+  return(get(paste0(outcome,".",explan_var,"model1b.explan_reg_stats")))
+}
 ```
@@
 # Regression coefficients
-gad_prepan_model1b_employmentchange_estimates <- model1b.explan.estimates(outcome = "gad.sum_score_base",
-                         explan_var = "employment_change",
-                         data_set = "dat.prepan")
-kable(gad_prepan_model1b_employmentchange_estimates)
-gad_prepan_model1b_employmentchange_estimates
-
-# Regression diagnostic statistics
-gad_prepan_model1b_employmentchange_reg_stats <- model1b.explan.reg.stats(outcome = "gad.sum_score_base",
-                         explan_var = "employment_change",
-                         data_set = "dat.prepan")
-kable(gad_prepan_model1b_employmentchange_reg_stats)
-gad_prepan_model1b_employmentchange_reg_stats
+gad_prepan_model1b_education_estimates <- model1b.explan.estimates(outcome = "gad.sum_score_base",
+                         explan_var = "pcl.sum_score_prepan",
+                         data_set = "dat.prepan")
+kable(gad_prepan_model1b_education_estimates)
+gad_prepan_model1b_education_estimates
+
+# Regression diagnostic statistics
+gad_prepan_model1b_education_reg_stats <- model1b.explan.reg.stats(outcome = "gad.sum_score_base",
+                         explan_var = "pcl.sum_score_prepan",
+                         data_set = "dat.prepan")
+kable(gad_prepan_model1b_education_reg_stats)
+gad_prepan_model1b_education_reg_stats
 ```
@@
 # Regression coefficients
-phq_prepan_model1b_employmentchange_estimates <- model1b.explan.estimates(outcome = "phq.sum_score_base",
-                         explan_var = "employment_change",
-                         data_set = "dat.prepan")
-kable(phq_prepan_model1b_employmentchange_estimates)
-phq_prepan_model1b_employmentchange_estimates
-
-# Regression diagnostic statistics
-phq_prepan_model1b_employmentchange_reg_stats <- model1b.explan.reg.stats(outcome = "phq.sum_score_base",
-                         explan_var = "employment_change",
-                         data_set = "dat.prepan")
-kable(phq_prepan_model1b_employmentchange_reg_stats)
-phq_prepan_model1b_employmentchange_reg_stats
+phq_prepan_model1b_education_estimates <- model1b.explan.estimates(outcome = "phq.sum_score_base",
+                         explan_var = "pcl.sum_score_prepan",
+                         data_set = "dat.prepan")
+kable(phq_prepan_model1b_education_estimates)
+phq_prepan_model1b_education_estimates
+
+# Regression diagnostic statistics
+phq_prepan_model1b_education_reg_stats <- model1b.explan.reg.stats(outcome = "phq.sum_score_base",
+                         explan_var = "pcl.sum_score_prepan",
+                         data_set = "dat.prepan")
+kable(phq_prepan_model1b_education_reg_stats)
+phq_prepan_model1b_education_reg_stats
 ```
@@
 # Regression coefficients
-ocir_prepan_model1b_employmentchange_estimates <- model1b.explan.estimates(outcome = "ocir.sum_score_base",
-                         explan_var = "employment_change",
-                         data_set = "dat.prepan")
-kable(ocir_prepan_model1b_employmentchange_estimates)
-ocir_prepan_model1b_employmentchange_estimates
-
-# Regression diagnostic statistics
-ocir_prepan_model1b_employmentchange_reg_stats <- model1b.explan.reg.stats(outcome = "ocir.sum_score_base",
-                         explan_var = "employment_change",
-                         data_set = "dat.prepan")
-kable(ocir_prepan_model1b_employmentchange_reg_stats)
-ocir_prepan_model1b_employmentchange_reg_stats
+ocir_prepan_model1b_education_estimates <- model1b.explan.estimates(outcome = "ocir.sum_score_base",
+                         explan_var = "pcl.sum_score_prepan",
+                         data_set = "dat.prepan")
+kable(ocir_prepan_model1b_education_estimates)
+ocir_prepan_model1b_education_estimates
+
+# Regression diagnostic statistics
+ocir_prepan_model1b_education_reg_stats <- model1b.explan.reg.stats(outcome = "ocir.sum_score_base",
+                         explan_var = "pcl.sum_score_prepan",
+                         data_set = "dat.prepan")
+kable(ocir_prepan_model1b_education_reg_stats)
+ocir_prepan_model1b_education_reg_stats
 ```
@@
 # Regression coefficients
-pcl_prepan_model1b_employmentchange_estimates <- model1b.explan.estimates(outcome = "pcl.sum_score_base",
-                         explan_var = "employment_change",
-                         data_set = "dat.prepan")
-kable(pcl_prepan_model1b_employmentchange_estimates)
-pcl_prepan_model1b_employmentchange_estimates
-
-# Regression diagnostic statistics
-pcl_prepan_model1b_employmentchange_reg_stats <- model1b.explan.reg.stats(outcome = "pcl.sum_score_base",
-                         explan_var = "employment_change",
-                         data_set = "dat.prepan")
-kable(pcl_prepan_model1b_employmentchange_reg_stats)
-pcl_prepan_model1b_employmentchange_reg_stats
-```
-
-# Sensitivity based on GLAD sign up
-#PCL prepan: sensitivity
-## Regression: Absolute scores
-### Model 1b: Overlapping disorders, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
-#### Subset of participants 3 months prior to pandemic
-```{r pcl model1b sum_score prepan - sensitivity 3 months}
-# Regression coefficients
-pcl_prepan_model1b_explan_estimates <- model1b.explan.estimates(outcome = "pcl.sum_score_base",
+pcl_prepan_model1b_education_estimates <- model1b.explan.estimates(outcome = "pcl.sum_score_base",
                          explan_var = "pcl.sum_score_prepan",
-                         data_set = "dat.prepan_sensitivity_3months")
-kable(pcl_prepan_model1b_explan_estimates)
-pcl_prepan_model1b_explan_estimates
-
-# Regression diagnostic statistics
-pcl_prepan_model1b_explan_reg_stats <- model1b.explan.reg.stats(outcome = "pcl.sum_score_base",
+                         data_set = "dat.prepan")
+kable(pcl_prepan_model1b_education_estimates)
+pcl_prepan_model1b_education_estimates
+
+# Regression diagnostic statistics
+pcl_prepan_model1b_education_reg_stats <- model1b.explan.reg.stats(outcome = "pcl.sum_score_base",
                          explan_var = "pcl.sum_score_prepan",
-                         data_set = "dat.prepan_sensitivity_3months")
-kable(pcl_prepan_model1b_explan_reg_stats)
-pcl_prepan_model1b_explan_reg_stats
-```
-
-#### Subset of participants 6 months prior to pandemic
-```{r pcl model1b sum_score prepan - sensitivity 6 months}
-# Regression coefficients
-pcl_prepan_model1b_explan_estimates <- model1b.explan.estimates(outcome = "pcl.sum_score_base",
-                         explan_var = "pcl.sum_score_prepan",
-                         data_set = "dat.prepan_sensitivity_6months")
-kable(pcl_prepan_model1b_explan_estimates)
-pcl_prepan_model1b_explan_estimates
-
-# Regression diagnostic statistics
-pcl_prepan_model1b_explan_reg_stats <- model1b.explan.reg.stats(outcome = "pcl.sum_score_base",
-                         explan_var = "pcl.sum_score_prepan",
-                         data_set = "dat.prepan_sensitivity_6months")
-kable(pcl_prepan_model1b_explan_reg_stats)
-pcl_prepan_model1b_explan_reg_stats
-```
-
-#### Subset of participants 9 months prior to pandemic
-```{r pcl model1b sum_score prepan - sensitivity 9 months}
-# Regression coefficients
-pcl_prepan_model1b_explan_estimates <- model1b.explan.estimates(outcome = "pcl.sum_score_base",
-                         explan_var = "pcl.sum_score_prepan",
-                         data_set = "dat.prepan_sensitivity_9months")
-kable(pcl_prepan_model1b_explan_estimates)
-pcl_prepan_model1b_explan_estimates
-
-# Regression diagnostic statistics
-pcl_prepan_model1b_explan_reg_stats <- model1b.explan.reg.stats(outcome = "pcl.sum_score_base",
-                         explan_var = "pcl.sum_score_prepan",
-                         data_set = "dat.prepan_sensitivity_9months")
-kable(pcl_prepan_model1b_explan_reg_stats)
-pcl_prepan_model1b_explan_reg_stats
-```
+                         data_set = "dat.prepan")
+kable(pcl_prepan_model1b_education_reg_stats)
+pcl_prepan_model1b_education_reg_stats
+```

### 2020-11-16 PANCHANGE_data_merging.Rmd
education, employment & employment change sensitivity

@@
 ```{r export data}
-glad <- read_rds(path = paste0(data_path, "/glad.rds"))
+glad <- read_rds(file = paste0(data_path, "/glad.rds"))
 dim(glad)
 
-edgi <- read_rds(path = paste0(data_path, "/edgi.rds"))
+edgi <- read_rds(file = paste0(data_path, "/edgi.rds"))
 dim(edgi)
 
-nbr <- read_rds(path = paste0(data_path, "/nbr.rds"))
+nbr <- read_rds(file = paste0(data_path, "/nbr.rds"))
 dim(nbr)
 
-ramp <- read_rds(path = paste0(data_path, "/ramp.rds"))
+ramp <- read_rds(file = paste0(data_path, "/ramp.rds"))
 dim(ramp)

### 2020-11-16 PANCHANGE_data_preprocessing2020-07-15.Rmd
Knitted exclusion descriptives script
education, employment & employment change sensitivity

--- 2020-11-10 PANCHANGE_data_preprocessing2020-07-15.Rmd
@@
 EDGI = FALSE
-NBR = TRUE
-RAMP = FALSE
+NBR = FALSE
+RAMP = TRUE
 GLAD_and_EDGI = FALSE
@@
 #source raw data directory: data.raw_path
-source("..//PANCHANGE_raw_path.R")
+source("../PANCHANGE_raw_path.R")
 ```
@@
 ```{r GLAD and EDGI combined}
+if(GLAD_and_EDGI == TRUE)
 glad.and.edgi.dem.raw.id <- rbind(glad.dem.raw.id, edgi.dem.raw.id)
@@
          employment.furloughed_or_paid_leave_company_funded, #key worker routing variable
-         employment.paid_leave_furloughed #key worker routing variable
+         employment.paid_leave_furloughed, #key worker routing variable
+         employment.fulltime_employed,
+         employment.parttime_employed,
+         employment.selfemployed,
+         employment.contract_or_freelance_work,
+         employment.small_business_owner, 
+         employment.receiving_state_income,
+         employment.my_employment_status_has_not_changed, 
+         employment.reduction_in_hours, 
+         employment.reduction_in_salary,
+         employment.benefits_increased,
+         employment.benefits_decreased,
+         employment.became_employed,
+         employment.became_unemployed,
+         employment.increased_hours,
+         employment.increased_salary,
                   ) %>%
@@
          employment.furloughed_or_paid_leave_company_funded, #key worker routing variable
-         employment.paid_leave_furloughed #key worker routing variable
+         employment.paid_leave_furloughed, #key worker routing variable
+         employment.fulltime_employed,
+         employment.parttime_employed,
+         employment.selfemployed,
+         employment.contract_or_freelance_work,
+         employment.small_business_owner, 
+         employment.receiving_state_income,
+         employment.my_employment_status_has_not_changed, 
+         employment.reduction_in_hours, 
+         employment.reduction_in_salary,
+         employment.benefits_increased,
+         employment.benefits_decreased,
+         employment.became_employed,
+         employment.became_unemployed,
+         employment.increased_hours,
+         employment.increased_salary
                   ) %>%
@@
          employment.furloughed_or_paid_leave_company_funded, #key worker routing variable
-         employment.paid_leave_furloughed #key worker routing variable
+         employment.paid_leave_furloughed, #key worker routing variable
+         employment.fulltime_employed,
+         employment.parttime_employed,
+         employment.selfemployed,
+         employment.contract_or_freelance_work,
+         employment.small_business_owner, 
+         employment.receiving_state_income,
+         employment.my_employment_status_has_not_changed, 
+         employment.reduction_in_hours, 
+         employment.reduction_in_salary,
+         employment.benefits_increased,
+         employment.benefits_decreased,
+         employment.became_employed,
+         employment.became_unemployed,
+         employment.increased_hours,
+         employment.increased_salary
          ) %>%
@@
          employment.what_is_your_highest_level_of_education_numeric
+  )
+}
+```
+
+## Employment prior to pandemic (baseline, GLAD, EDGI, NBR)
+Proceed along qualifications fields. If field is not blank, take that as highest qual. If field is blank, check next field. If all fields are blank, NA
+```{r Employment prior to pandemic baseline}
+if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE) {
+#create numeric version of the highest education variable
+employment.raw.id <- employment.raw.id %>%
+  mutate(
+    employment_prior_covid_numeric =
+      case_when(
+        employment.fulltime_employed_numeric == "1" ~ 1,
+        employment.parttime_employed_numeric == "1" ~ 1,
+        employment.unemployed_numeric == "1" ~ 2,
+        employment.zerohours_contract_numeric == "1" ~ 1,
+        employment.selfemployed_numeric == "1" ~ 1,
+        employment.contract_or_freelance_work_numeric == "1" ~ 1,
+        employment.small_business_owner_numeric == "1" ~ 1,
+        employment.retired_numeric  ==  "1" ~ 4,
+        employment.student_gcse_or_a_level_numeric == "1" ~ 3,
+        employment.student_university_numeric == "1" ~ 3
+      )
+    )
+
+#recode the numeric version into a factor
+employment.raw.id <- employment.raw.id %>%
+  mutate(
+    employment_prior_covid =
+      recode_factor(
+        employment_prior_covid_numeric,
+        `1` = "Employed",
+        `2` = "Unemployed",
+        `3` = "Student",
+        `4` = "Retired")
+    )
+
+employment.raw.id %>%
+  freq(employment_prior_covid)
+}
+```
+
+Check Employment prior to pandemic coding
+```{r Employment prior to pandemic check}
+if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE) {
+employment.raw.id %>%
+  select(employment_prior_covid,
+         employment_prior_covid_numeric,
+        employment.fulltime_employed_numeric, 
+        employment.parttime_employed_numeric, 
+        employment.unemployed_numeric, 
+        employment.zerohours_contract_numeric, 
+        employment.selfemployed_numeric,
+        employment.contract_or_freelance_work_numeric,
+        employment.small_business_owner_numeric,
+        employment.retired_numeric,
+        employment.student_gcse_or_a_level_numeric,
+        employment.student_university_numeric
+  )
+}
+```
+
+## Employment prior to pandemic (baseline, RAMP)
+```{r highest level of education for ramp}
+if(RAMP == TRUE) {
+#create numeric version of the highest education variable
+employment.raw.id <- employment.raw.id %>%
+  mutate(
+    employment_prior_covid_numeric =
+      case_when(
+        employment.fulltime_employed_numeric == "1" ~ 1,
+        employment.parttime_employed_numeric == "1" ~ 1,
+        employment.unemployed_numeric == "1" ~ 2,
+        employment.zerohours_contract_numeric == "1" ~ 1,
+        employment.selfemployed_numeric == "1" ~ 1,
+        employment.contract_or_freelance_work_numeric == "1" ~ 1,
+        employment.small_business_owner_numeric == "1" ~ 1,
+        employment.retired_numeric  ==  "1" ~ 4,
+        employment.student_gcse_or_a_level_numeric == "1" ~ 3,
+        employment.student_university_numeric == "1" ~ 3
+      )
+    )
+
+#recode the numeric version into a factor
+employment.raw.id <- employment.raw.id %>%
+  mutate(
+    employment_prior_covid =
+      recode_factor(
+        employment_prior_covid_numeric,
+        `1` = "Employed",
+        `2` = "Unemployed",
+        `3` = "Student",
+        `4` = "Retired")
+    )
+
+employment.raw.id %>%
+  freq(employment_prior_covid)
+}
+```
+
+Check Employment prior to pandemic coding for RAMP
+```{r Employment prior to pandemic check for RAMP}
+if(RAMP == TRUE) {
+employment.raw.id %>%
+  select(employment_prior_covid,
+         employment_prior_covid_numeric,
+        employment.fulltime_employed_numeric, 
+        employment.parttime_employed_numeric, 
+        employment.unemployed_numeric, 
+        employment.zerohours_contract_numeric, 
+        employment.selfemployed_numeric,
+        employment.contract_or_freelance_work_numeric,
+        employment.small_business_owner_numeric,
+        employment.retired_numeric,
+        employment.student_gcse_or_a_level_numeric,
+        employment.student_university_numeric
+  )
+}
+```
+
+## Employment change (baseline, GLAD, EDGI, NBR)
+Proceed along qualifications fields. If field is not blank, take that as highest qual. If field is blank, check next field. If all fields are blank, NA
+```{r Employment change baseline}
+if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE) {
+#create numeric version of the highest education variable
+employment.raw.id <- employment.raw.id %>%
+  mutate(
+    employment_change_numeric =
+      case_when(
+        employment.reduction_in_hours_numeric == "1" ~ 1,
+        employment.reduction_in_salary_numeric == "1" ~ 1,
+        employment.became_unemployed_numeric == "1" ~ 1,
+        employment.benefits_decreased_numeric == "1" ~ 1,
+        employment.increased_hours_numeric == "1" ~ 2,
+        employment.increased_salary_numeric == "1" ~ 3,
+        employment.became_employed_numeric == "1" ~ 3,
+        employment.benefits_increased_numeric  ==  "1" ~ 2,
+        employment.furloughed_or_paid_leave_government_funded_numeric == "1" ~ 3,
+        employment.furloughed_or_paid_leave_company_funded_numeric == "1" ~ 3,
+        employment.paid_leave_furloughed_numeric == "1" ~ 3,
+        employment.my_employment_status_has_not_changed_numeric == "1" ~ 4
+      )
+    )
+
+#recode the numeric version into a factor
+employment.raw.id <- employment.raw.id %>%
+  mutate(
+    employment_change =
+      recode_factor(
+        employment_change_numeric,
+        `1` = "Decreased employment",
+        `2` = "Increased employment",
+        `3` = "Furloughed",
+        `4` = "Employment not changed")
+    )
+
+employment.raw.id %>%
+  freq(employment_change)
+}
+```
+
+Check Employment change coding
+```{r Employment change check}
+if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE) {
+employment.raw.id %>%
+  select(employment_change,
+         employment_change_numeric,
+        employment.reduction_in_hours_numeric,
+        employment.reduction_in_salary_numeric,
+        employment.became_unemployed_numeric,
+        employment.benefits_decreased_numeric,
+        employment.increased_hours_numeric, 
+        employment.increased_salary_numeric, 
+        employment.became_employed_numeric,
+        employment.benefits_increased_numeric, 
+        employment.furloughed_or_paid_leave_government_funded_numeric,
+        employment.furloughed_or_paid_leave_company_funded_numeric, 
+        employment.paid_leave_furloughed_numeric, 
+        employment.my_employment_status_has_not_changed_numeric
+  )
+}
+```
+
+## Employment change (baseline, RAMP)
+```{r employment change for ramp}
+if(RAMP == TRUE) {
+#create numeric version of the highest education variable
+employment.raw.id <- employment.raw.id %>%
+  mutate(
+    employment_change_numeric =
+      case_when(
+        employment.reduction_in_hours_numeric == "1" ~ 1,
+        employment.reduction_in_salary_numeric == "1" ~ 1,
+        employment.became_unemployed_numeric == "1" ~ 1,
+        employment.benefits_decreased_numeric == "1" ~ 1,
+        employment.increased_hours_numeric == "1" ~ 2,
+        employment.increased_salary_numeric == "1" ~ 3,
+        employment.became_employed_numeric == "1" ~ 3,
+        employment.benefits_increased_numeric  ==  "1" ~ 2,
+        employment.furloughed_or_paid_leave_government_funded_numeric == "1" ~ 3,
+        employment.furloughed_or_paid_leave_company_funded_numeric== "1" ~ 3,
+        employment.paid_leave_furloughed_numeric == "1" ~ 3,
+        employment.my_employment_status_has_not_changed_numeric == "1" ~ 4
+      )
+    )
+
+#recode the numeric version into a factor
+employment.raw.id <- employment.raw.id %>%
+  mutate(
+    employment_change =
+      recode_factor(
+        employment_change_numeric,
+        `1` = "Decreased employment",
+        `2` = "Increased employment",
+        `3` = "Furloughed",
+        `4` = "Employment not changed")
+    )
+
+employment.raw.id %>%
+  freq(employment_change)
+}
+```
+
+Check Employment changen coding for RAMP
+```{r Employment change check for RAMP}
+if(RAMP == TRUE) {
+employment.raw.id %>%
+  select(employment_change,
+         employment_change_numeric,
+        employment.reduction_in_hours_numeric,
+        employment.reduction_in_salary_numeric,
+        employment.became_unemployed_numeric,
+        employment.benefits_decreased_numeric,
+        employment.increased_hours_numeric, 
+        employment.increased_salary_numeric, 
+        employment.became_employed_numeric,
+        employment.benefits_increased_numeric, 
+        employment.furloughed_or_paid_leave_government_funded_numeric,
+        employment.furloughed_or_paid_leave_company_funded_numeric, 
+        employment.paid_leave_furloughed_numeric, 
+        employment.my_employment_status_has_not_changed_numeric
   )

### 2020-11-16 PANCHANGE_analysis.Rmd
education, employment & employment change sensitivity

@@
 
+# GAD baseline
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r gad education sensitivity model1b absolute whole sample}
+# Regression coefficients
+gad_baseline_model1b_estimates <- model1b.estimates(outcome = "gad.sum_score_base",
+                                                 data_set = "dat")
+kable(gad_baseline_model1b_estimates)
+gad_baseline_model1b_estimates
+
+# Regression diagnostic statistics
+gad_baseline_model1b_reg_stats <- model1b.reg.stats(outcome = "gad.sum_score_base",
+                                                 data_set = "dat")
+kable(gad_baseline_model1b_reg_stats)
+gad_baseline_model1b_reg_stats
+```
+
+# GAD retro
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r gad education sensitivity model1b sum_score retro}
+# Regression coefficients
+gad_retro_model1b_explan_estimates <- model1b.explan.estimates(outcome = "gad.sum_score_base",
+                                                               explan_var = "gad.sum_score_retro",
+                                                               data_set = "dat.retro")
+kable(gad_retro_model1b_explan_estimates)
+gad_retro_model1b_explan_estimates
+
+# Regression diagnostic statistics
+gad_retro_model1b_explan_reg_stats <- model1b.explan.reg.stats(outcome = "gad.sum_score_base",
+                                                               explan_var = "gad.sum_score_retro",
+                                                               data_set = "dat.retro")
+kable(gad_retro_model1b_explan_reg_stats)
+gad_retro_model1b_explan_reg_stats
+```
+
 # GAD prepan
-## Regression: Absolute scores
 ### Model 1b: Overlapping disorders, Adjusted
@@
 
+# PHQ baseline
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r phq education sensitivity model1b absolute whole sample}
+# Regression coefficients
+phq_baseline_model1b_estimates <- model1b.estimates(outcome = "phq.sum_score_base",
+                                                 data_set = "dat")
+kable(phq_baseline_model1b_estimates)
+phq_baseline_model1b_estimates
+
+# Regression diagnostic statistics
+phq_baseline_model1b_reg_stats <- model1b.reg.stats(outcome = "phq.sum_score_base",
+                                                 data_set = "dat")
+kable(phq_baseline_model1b_reg_stats)
+phq_baseline_model1b_reg_stats
+```
+
+# PHQ retro
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r phq education sensitivity model1b sum_score retro}
+# Regression coefficients
+phq_retro_model1b_explan_estimates <- model1b.explan.estimates(outcome = "phq.sum_score_base",
+                                                               explan_var = "phq.sum_score_retro",
+                                                               data_set = "dat.retro")
+kable(phq_retro_model1b_explan_estimates)
+phq_retro_model1b_explan_estimates
+
+# Regression diagnostic statistics
+phq_retro_model1b_explan_reg_stats <- model1b.explan.reg.stats(outcome = "phq.sum_score_base",
+                                                               explan_var = "phq.sum_score_retro",
+                                                               data_set = "dat.retro")
+kable(phq_retro_model1b_explan_reg_stats)
+phq_retro_model1b_explan_reg_stats
+```
+
 # PHQ prepan
-## Regression: Absolute scores
 ### Model 1b: Overlapping disorders, Adjusted
@@
 
+# OCIR baseline
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r ocir education sensitivity model1b absolute whole sample}
+# Regression coefficients
+ocir_baseline_model1b_estimates <- model1b.estimates(outcome = "ocir.sum_score_base",
+                                                 data_set = "dat")
+kable(ocir_baseline_model1b_estimates)
+ocir_baseline_model1b_estimates
+
+# Regression diagnostic statistics
+ocir_baseline_model1b_reg_stats <- model1b.reg.stats(outcome = "ocir.sum_score_base",
+                                                 data_set = "dat")
+kable(ocir_baseline_model1b_reg_stats)
+ocir_baseline_model1b_reg_stats
+```
+
+# OCIR retro
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r ocir education sensitivity model1b sum_score retro}
+# Regression coefficients
+ocir_retro_model1b_explan_estimates <- model1b.explan.estimates(outcome = "ocir.sum_score_base",
+                                                               explan_var = "ocir.sum_score_retro",
+                                                               data_set = "dat.retro")
+kable(ocir_retro_model1b_explan_estimates)
+ocir_retro_model1b_explan_estimates
+
+# Regression diagnostic statistics
+ocir_retro_model1b_explan_reg_stats <- model1b.explan.reg.stats(outcome = "ocir.sum_score_base",
+                                                               explan_var = "ocir.sum_score_retro",
+                                                               data_set = "dat.retro")
+kable(ocir_retro_model1b_explan_reg_stats)
+ocir_retro_model1b_explan_reg_stats
+```
+
 # OCIR prepan 
-## Regression: Absolute scores
 ### Model 1b: Overlapping disorders, Adjusted
@@
 
+# PCL baseline
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r pcl education sensitivity model1b absolute whole sample}
+# Regression coefficients
+pcl_baseline_model1b_estimates <- model1b.estimates(outcome = "pcl.sum_score_base",
+                                                 data_set = "dat")
+kable(pcl_baseline_model1b_estimates)
+pcl_baseline_model1b_estimates
+
+# Regression diagnostic statistics
+pcl_baseline_model1b_reg_stats <- model1b.reg.stats(outcome = "pcl.sum_score_base",
+                                                 data_set = "dat")
+kable(pcl_baseline_model1b_reg_stats)
+pcl_baseline_model1b_reg_stats
+```
+
 #PCL prepan 
-## Regression: Absolute scores
 ### Model 1b: Overlapping disorders, Adjusted
@@
 
+# GAD baseline
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r gad employment prior covid sensitivity model1b absolute whole sample}
+# Regression coefficients
+gad_baseline_model1b_estimates <- model1b.estimates(outcome = "gad.sum_score_base",
+                                                 data_set = "dat")
+kable(gad_baseline_model1b_estimates)
+gad_baseline_model1b_estimates
+
+# Regression diagnostic statistics
+gad_baseline_model1b_reg_stats <- model1b.reg.stats(outcome = "gad.sum_score_base",
+                                                 data_set = "dat")
+kable(gad_baseline_model1b_reg_stats)
+gad_baseline_model1b_reg_stats
+```
+
+# GAD retro
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r gad employment prior covid sensitivity model1b sum_score retro}
+# Regression coefficients
+gad_retro_model1b_explan_estimates <- model1b.explan.estimates(outcome = "gad.sum_score_base",
+                                                               explan_var = "gad.sum_score_retro",
+                                                               data_set = "dat.retro")
+kable(gad_retro_model1b_explan_estimates)
+gad_retro_model1b_explan_estimates
+
+# Regression diagnostic statistics
+gad_retro_model1b_explan_reg_stats <- model1b.explan.reg.stats(outcome = "gad.sum_score_base",
+                                                               explan_var = "gad.sum_score_retro",
+                                                               data_set = "dat.retro")
+kable(gad_retro_model1b_explan_reg_stats)
+gad_retro_model1b_explan_reg_stats
+```
+
 # GAD prepan
-## Regression: Absolute scores
 ### Model 1b: Overlapping disorders, Adjusted
@@
 
+# PHQ baseline
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r phq employment prior covid sensitivity model1b absolute whole sample}
+# Regression coefficients
+phq_baseline_model1b_estimates <- model1b.estimates(outcome = "phq.sum_score_base",
+                                                 data_set = "dat")
+kable(phq_baseline_model1b_estimates)
+phq_baseline_model1b_estimates
+
+# Regression diagnostic statistics
+phq_baseline_model1b_reg_stats <- model1b.reg.stats(outcome = "phq.sum_score_base",
+                                                 data_set = "dat")
+kable(phq_baseline_model1b_reg_stats)
+phq_baseline_model1b_reg_stats
+```
+
+# PHQ retro
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r phq employment prior covid sensitivity model1b sum_score retro}
+# Regression coefficients
+phq_retro_model1b_explan_estimates <- model1b.explan.estimates(outcome = "phq.sum_score_base",
+                                                               explan_var = "phq.sum_score_retro",
+                                                               data_set = "dat.retro")
+kable(phq_retro_model1b_explan_estimates)
+phq_retro_model1b_explan_estimates
+
+# Regression diagnostic statistics
+phq_retro_model1b_explan_reg_stats <- model1b.explan.reg.stats(outcome = "phq.sum_score_base",
+                                                               explan_var = "phq.sum_score_retro",
+                                                               data_set = "dat.retro")
+kable(phq_retro_model1b_explan_reg_stats)
+phq_retro_model1b_explan_reg_stats
+```
+
 # PHQ prepan
-## Regression: Absolute scores
 ### Model 1b: Overlapping disorders, Adjusted
@@
 
+# OCIR baseline
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r ocir employment prior covid sensitivity model1b absolute whole sample}
+# Regression coefficients
+ocir_baseline_model1b_estimates <- model1b.estimates(outcome = "ocir.sum_score_base",
+                                                 data_set = "dat")
+kable(ocir_baseline_model1b_estimates)
+ocir_baseline_model1b_estimates
+
+# Regression diagnostic statistics
+ocir_baseline_model1b_reg_stats <- model1b.reg.stats(outcome = "ocir.sum_score_base",
+                                                 data_set = "dat")
+kable(ocir_baseline_model1b_reg_stats)
+ocir_baseline_model1b_reg_stats
+```
+
+# OCIR retro
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r ocir employment prior covid sensitivity model1b sum_score retro}
+# Regression coefficients
+ocir_retro_model1b_explan_estimates <- model1b.explan.estimates(outcome = "ocir.sum_score_base",
+                                                               explan_var = "ocir.sum_score_retro",
+                                                               data_set = "dat.retro")
+kable(ocir_retro_model1b_explan_estimates)
+ocir_retro_model1b_explan_estimates
+
+# Regression diagnostic statistics
+ocir_retro_model1b_explan_reg_stats <- model1b.explan.reg.stats(outcome = "ocir.sum_score_base",
+                                                               explan_var = "ocir.sum_score_retro",
+                                                               data_set = "dat.retro")
+kable(ocir_retro_model1b_explan_reg_stats)
+ocir_retro_model1b_explan_reg_stats
+```
+
 # OCIR prepan 
-## Regression: Absolute scores
 ### Model 1b: Overlapping disorders, Adjusted
@@
 
+# PCL baseline
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r pcl employment prior covid sensitivity model1b absolute whole sample}
+# Regression coefficients
+pcl_baseline_model1b_estimates <- model1b.estimates(outcome = "pcl.sum_score_base",
+                                                 data_set = "dat")
+kable(pcl_baseline_model1b_estimates)
+pcl_baseline_model1b_estimates
+
+# Regression diagnostic statistics
+pcl_baseline_model1b_reg_stats <- model1b.reg.stats(outcome = "pcl.sum_score_base",
+                                                 data_set = "dat")
+kable(pcl_baseline_model1b_reg_stats)
+pcl_baseline_model1b_reg_stats
+```
+
 #PCL prepan 
-## Regression: Absolute scores
 ### Model 1b: Overlapping disorders, Adjusted
@@
 
+# GAD baseline
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r gad employment change sensitivity model1b absolute whole sample}
+# Regression coefficients
+gad_baseline_model1b_estimates <- model1b.estimates(outcome = "gad.sum_score_base",
+                                                 data_set = "dat")
+kable(gad_baseline_model1b_estimates)
+gad_baseline_model1b_estimates
+
+# Regression diagnostic statistics
+gad_baseline_model1b_reg_stats <- model1b.reg.stats(outcome = "gad.sum_score_base",
+                                                 data_set = "dat")
+kable(gad_baseline_model1b_reg_stats)
+gad_baseline_model1b_reg_stats
+```
+
+# GAD retro
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r gad employment change sensitivity model1b sum_score retro}
+# Regression coefficients
+gad_retro_model1b_explan_estimates <- model1b.explan.estimates(outcome = "gad.sum_score_base",
+                                                               explan_var = "gad.sum_score_retro",
+                                                               data_set = "dat.retro")
+kable(gad_retro_model1b_explan_estimates)
+gad_retro_model1b_explan_estimates
+
+# Regression diagnostic statistics
+gad_retro_model1b_explan_reg_stats <- model1b.explan.reg.stats(outcome = "gad.sum_score_base",
+                                                               explan_var = "gad.sum_score_retro",
+                                                               data_set = "dat.retro")
+kable(gad_retro_model1b_explan_reg_stats)
+gad_retro_model1b_explan_reg_stats
+```
+
 # GAD prepan
-## Regression: Absolute scores
 ### Model 1b: Overlapping disorders, Adjusted
@@
 
+# PHQ baseline
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r phq employment change sensitivity model1b absolute whole sample}
+# Regression coefficients
+phq_baseline_model1b_estimates <- model1b.estimates(outcome = "phq.sum_score_base",
+                                                 data_set = "dat")
+kable(phq_baseline_model1b_estimates)
+phq_baseline_model1b_estimates
+
+# Regression diagnostic statistics
+phq_baseline_model1b_reg_stats <- model1b.reg.stats(outcome = "phq.sum_score_base",
+                                                 data_set = "dat")
+kable(phq_baseline_model1b_reg_stats)
+phq_baseline_model1b_reg_stats
+```
+
+# PHQ retro
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r phq employment change sensitivity model1b sum_score retro}
+# Regression coefficients
+phq_retro_model1b_explan_estimates <- model1b.explan.estimates(outcome = "phq.sum_score_base",
+                                                               explan_var = "phq.sum_score_retro",
+                                                               data_set = "dat.retro")
+kable(phq_retro_model1b_explan_estimates)
+phq_retro_model1b_explan_estimates
+
+# Regression diagnostic statistics
+phq_retro_model1b_explan_reg_stats <- model1b.explan.reg.stats(outcome = "phq.sum_score_base",
+                                                               explan_var = "phq.sum_score_retro",
+                                                               data_set = "dat.retro")
+kable(phq_retro_model1b_explan_reg_stats)
+phq_retro_model1b_explan_reg_stats
+```
+
 # PHQ prepan
-## Regression: Absolute scores
 ### Model 1b: Overlapping disorders, Adjusted
@@
 
+# OCIR baseline
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r ocir employment change sensitivity model1b absolute whole sample}
+# Regression coefficients
+ocir_baseline_model1b_estimates <- model1b.estimates(outcome = "ocir.sum_score_base",
+                                                 data_set = "dat")
+kable(ocir_baseline_model1b_estimates)
+ocir_baseline_model1b_estimates
+
+# Regression diagnostic statistics
+ocir_baseline_model1b_reg_stats <- model1b.reg.stats(outcome = "ocir.sum_score_base",
+                                                 data_set = "dat")
+kable(ocir_baseline_model1b_reg_stats)
+ocir_baseline_model1b_reg_stats
+```
+
+# OCIR retro
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r ocir employment change sensitivity model1b sum_score retro}
+# Regression coefficients
+ocir_retro_model1b_explan_estimates <- model1b.explan.estimates(outcome = "ocir.sum_score_base",
+                                                               explan_var = "ocir.sum_score_retro",
+                                                               data_set = "dat.retro")
+kable(ocir_retro_model1b_explan_estimates)
+ocir_retro_model1b_explan_estimates
+
+# Regression diagnostic statistics
+ocir_retro_model1b_explan_reg_stats <- model1b.explan.reg.stats(outcome = "ocir.sum_score_base",
+                                                               explan_var = "ocir.sum_score_retro",
+                                                               data_set = "dat.retro")
+kable(ocir_retro_model1b_explan_reg_stats)
+ocir_retro_model1b_explan_reg_stats
+```
+
 # OCIR prepan 
-## Regression: Absolute scores
 ### Model 1b: Overlapping disorders, Adjusted
@@
 
+# PCL baseline
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r pcl employment change sensitivity model1b absolute whole sample}
+# Regression coefficients
+pcl_baseline_model1b_estimates <- model1b.estimates(outcome = "pcl.sum_score_base",
+                                                 data_set = "dat")
+kable(pcl_baseline_model1b_estimates)
+pcl_baseline_model1b_estimates
+
+# Regression diagnostic statistics
+pcl_baseline_model1b_reg_stats <- model1b.reg.stats(outcome = "pcl.sum_score_base",
+                                                 data_set = "dat")
+kable(pcl_baseline_model1b_reg_stats)
+pcl_baseline_model1b_reg_stats
+```
+
 #PCL prepan 
-## Regression: Absolute scores
 ### Model 1b: Overlapping disorders, Adjusted

### 2020-11-20 PANCHANGE_exclusion_descriptives.Rmd
knitted all scripts

@@
 author: "Katie Thompson, Topher Huebel, Molly Davies, Kirstin Purves"
-date: Sys.Date()
+date: '`r format(Sys.time(), "%d %B, %Y")`'
 output:  

### 2020-11-20 PANCHANGE_analysis.Rmd
tweaked figure height and width for violin plots

@@
 
-```{r gad.sum violin plot Sample, fig.height=3.5, fig.width=2.5}
+```{r gad.sum violin plot Sample, fig.height=14, fig.width=8}
 dat.long.gad.sum %>%
@@
   coord_flip()
-```
-
-```{r gad.sum violin plot Disorder_hierarchical}
+
+```
+
+```{r gad.sum violin plot Disorder_hierarchical, fig.height=10, fig.width=15}
 dat.long.gad.sum %>%
@@
 
-```{r phq.sum violin plot Sample, fig.height=3.5, fig.width=2.5}
+```{r phq.sum violin plot Sample, fig.height=14, fig.width=8}
 dat.long.phq.sum %>%
@@
 
-```{r phq.sum violin plot Disorder_hierarchical}
+```{r phq.sum violin plot Disorder_hierarchical, fig.height=10, fig.width=15}
 dat.long.phq.sum %>%
@@
 
-```{r ocir.sum violin plot Sample, fig.height=3.5, fig.width=2.5}
+```{r ocir.sum violin plot Sample, fig.height=14, fig.width=8}
 dat.long.ocir.sum %>%
@@
 
-```{r ocir.sum violin plot Disorder_hierarchical}
+```{r ocir.sum violin plot Disorder_hierarchical, fig.height=10, fig.width=15}
 dat.long.ocir.sum %>%

### 2020-11-20 PANCHANGE_analysis.Rmd
made by disorder violin plots larger

@@
 
-```{r gad.sum violin plot Disorder_hierarchical, fig.height=10, fig.width=15}
+```{r gad.sum violin plot Disorder_hierarchical, fig.height=18, fig.width=20}
 dat.long.gad.sum %>%
@@
 
-```{r phq.sum violin plot Disorder_hierarchical, fig.height=10, fig.width=15}
+```{r phq.sum violin plot Disorder_hierarchical, fig.height=18, fig.width=20}
 dat.long.phq.sum %>%
@@
 
-```{r ocir.sum violin plot Disorder_hierarchical, fig.height=10, fig.width=15}
+```{r ocir.sum violin plot Disorder_hierarchical, fig.height=18, fig.width=20}
 dat.long.ocir.sum %>%

### 2020-12-03 PANCHANGE_analysis.Rmd

@@
 
-```{r gad.sum violin plot Sample, fig.height=14, fig.width=8}
+```{r gad.sum violin plot Sample, fig.height=14, fig.width=8, dpi=300}
 dat.long.gad.sum %>%
@@
 ```{r model1b function}
+
+# function to return standardised beta for plotting in a dataframe
+
+model1b.lm <- function(outcome, data_set) {
+  # define the variable name of the dependent variable
+  dependent.variable <- outcome
+  # define the independent variables
+  independent.variables <- c("depression_and_anxiety",
+                             "eating_disorders",
+                             "obsessive_compulsive_disorders",
+                             "bipolar_and_schizophrenia",
+                             "mhd.posttraumatic_stress_disorder_ptsd",
+                             "autism_spectrum_disorder",
+                             "mhd.attention_deficit_hyperactivity_disorder",
+                             "mhd.personality_disorder",
+                             "Gender_collapsed",
+                             "age_category_collapsed_reordered",
+                             "Ethnicity_collapsed",
+                             "key_worker",
+                             "time_diff_coping_lockdown_march_23"
+                                )
+  # create the formula
+  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
+  glm.formula
+
+  # run the glm
+  assign(paste0(outcome,".model1b.lm"),
+         lm( formula = glm.formula,
+             data = get(data_set)
+         )
+  )
+
+  return(get(paste0(outcome,".model1b.lm")))
+}
+
 model1b.estimates <- function(outcome, data_set) {
@@
 gad_baseline_model1b_reg_stats
+
+# get lm object to standardise beta
+
+gad_prepan_model1b_lm <- model1b.lm(outcome = "gad.diff_score_base_prepan",
+                                           data_set = "dat.prepan")
+
 ```
@@
 ### Model 1b: Overlapping disorders, Adjusted
-Model 0a + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
+Model 1b + Gender_collapsed + age_category_collapsed_reordered + Ethnicity_collapsed + Time registration and baseline
 ```{r gad model1b diff_score prepan}
@@
                   data_set = "dat.prepan")
+
 kable(gad_prepan_model1b_reg_stats)
-gad_prepan_model1b_reg_stats
+
 ```

### 2020-12-03 PANCHANGE_data_preprocessing2020-07-15.Rmd

--- 2020-11-10 PANCHANGE_data_preprocessing2020-07-15.Rmd
@@
 ```{r Specify cohort}
-GLAD = TRUE
+GLAD = FALSE
 EDGI = FALSE
@@
 RAMP = FALSE
-GLAD_and_EDGI = FALSE
+GLAD_and_EDGI = TRUE
 ```

### 2020-12-04 PANCHANGE_analysis.Rmd

@@
 
+```{r model1b education function}
+model1b.estimates <- function(outcome, data_set) {
+  # define the variable name of the dependent variable
+  dependent.variable <- outcome
+  # define the independent variables
+  independent.variables <- c("depression_and_anxiety",
+                             "eating_disorders",
+                             "obsessive_compulsive_disorders",
+                             "bipolar_and_schizophrenia",
+                             "mhd.posttraumatic_stress_disorder_ptsd",
+                             "autism_spectrum_disorder",
+                             "mhd.attention_deficit_hyperactivity_disorder",
+                             "mhd.personality_disorder",
+                             "Gender_collapsed",
+                             "age_category_collapsed",
+                             "Ethnicity_collapsed",
+                             "key_worker",
+                             "time_diff_coping_lockdown_march_23",
+                             "highest_education"
+                                )
+  # create the formula
+  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
+  glm.formula
+
+  # run the glm
+  assign(paste0(outcome,".model1b"),
+         lm( formula = glm.formula,
+             data = get(data_set)
+         )
+  )
+
+  assign(paste0(outcome,"model1b_estimates"),
+         tidy(get(paste0(outcome,".model1b")), conf.int = TRUE) %>%
+           mutate(
+             "Indepent variable" = recode_factor(
+               term,
+               "(Intercept)" = "Intercept",
+               "anxiety_disordersAnxiety disorder" = "Anxiety disorders",
+               "depressive_disordersDepressive disorder" = "Depressive disorders",
+               "depression_and_anxietyDepressive and anxiety disorder" = "Depressive and anxiety disorder",
+               "depression_and_anxietyOnly depressive disorder" = "Only depressive disorder",
+               "depression_and_anxietyOnly anxiety disorder" = "Only anxiety disorder",
+               "eating_disordersEating disorder" = "Eating disorders",
+               "obsessive_compulsive_disordersObsessive compulsive disorder" = "OCDs",
+               "bipolar_and_schizophreniaPsychotic and bipolar disorder" = "Psychotic and bipolar disorder",
+               "bipolar_and_schizophreniaOnly psychotic disorder" = "Only psychotic disorder",
+               "bipolar_and_schizophreniaOnly bipolar disorder" = "Only bipolar disorder",
+               "psychotic_disordersPsychotic disorder" = "Psychotic disorder",
+               "mhd.mania_hypomania_bipolar_or_manicdepressionMania, hypomania, bipolar or manic-depression" = "Bipolar disorder",
+               "mhd.posttraumatic_stress_disorder_ptsdPost-traumatic stress disorder (PTSD)" = "PTSD",
+               "autism_spectrum_disorderAutism spectrum disorder" = "ASD",
+               "mhd.attention_deficit_hyperactivity_disorderAttention deficit or attention deficit and hyperactivity disorder (ADD/ADHD)" = "ADHD",
+               "mhd.personality_disorderPersonality disorder" = "Personality disorder",
+               "Gender_collapsedFemale" = "Female",
+               "Gender_collapsedNon-binary/Self-defined" = "Non-binary/Self-defined",
+               "age_category_collapsed19-25" = "19-25 years",
+               "age_category_collapsed26-35" = "26-35 years",
+               "age_category_collapsed36-45" = "36-45 years",
+               "age_category_collapsed46-55" = "46-55 years",
+               "age_category_collapsed56-65" = "56-65 years",
+               "age_category_collapsed66-70" = "66-70 years",
+               "age_category_collapsed71-75" = "71-75 years",
+               "age_category_collapsed76+" = "76+ years",
+               "Ethnicity_collapsedMixed or multiple ethnic origins" = "Mixed or multiple ethnic origins",
+               "Ethnicity_collapsedAsian or Asian British" = "Asian or Asian British",
+               "Ethnicity_collapsedAfrican or African British" = "African or African British",
+               "Ethnicity_collapsedOther" = "Other ethnicity",
+               "key_workerKey worker" = "Key worker",
+               "time_diff_coping_lockdown_march_23" = "Time difference: Lockdown to baseline",
+               "highest_educationNVQ" = "Highest education NVQ",
+               "highest_educationA-levels" = "Highest education A-Levels",
+               "highest_educationUniversity" = "Highest education University"
+             ),
+             "Estimate" = format(
+               round(estimate,
+                     digits = 2),
+               nsmall = 2),
+             "95% CI low" = format(
+               round(conf.low,
+                     digits = 2),
+               nsmall = 2),
+             "95% CI up" = format(
+               round(conf.high,
+                     digits = 2),
+               nsmall = 2),
+             "SE" = format(
+               round(std.error,
+                     digits = 2),
+               nsmall = 2),
+             "z score" = format(
+               round(statistic,
+                     digits = 2),
+               nsmall = 2),
+             "p value" = case_when(
+               p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
+               p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
+               p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
+             )
+           ) %>%
+           select(
+             "Indepent variable",
+             "Estimate",
+             "95% CI low",
+             "95% CI up",
+             "SE",
+             #    "z score",
+             "p value"
+           )
+  )
+
+  return(get(paste0(outcome,"model1b_estimates")))
+}
+
+model1b.reg.stats <- function(outcome, data_set) {
+  # define the variable name of the dependent variable
+  dependent.variable <- outcome
+  # define the independent variables
+  independent.variables <- c("Disorder_hierarchical")
+  # create the formula
+  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
+  glm.formula
+
+  # run the glm
+  assign(paste0(outcome,".model1b"),
+         lm( formula = glm.formula,
+             data = get(data_set)
+         )
+  )
+
+  assign(paste0(outcome,"model1b_reg_stats"),
+         glance(get(paste0(outcome,".model1b"))) %>%
+           mutate(
+             "n" = format(
+               round(nobs,
+                     digits = 0),
+               nsmall = 0),
+             "R2" = format(
+               round(r.squared,
+                     digits = 2),
+               nsmall = 2),
+             "adjust. R2" = format(
+               round(adj.r.squared,
+                     digits = 2),
+               nsmall = 2),
+             "F" = format(
+               round(statistic,
+                     digits = 2),
+               nsmall = 2),
+             "p value" = case_when(
+               p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
+               p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
+               p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
+             )
+           ) %>%
+           select(
+             "n",
+             "R2",
+             "adjust. R2",
+             "F",
+             "p value",
+             "df"
+           )
+  )
+
+  return(get(paste0(outcome,"model1b_reg_stats")))
+}
+```
+
+```{r model1b.explan education function}
+model1b.explan.estimates <- function(outcome, explan_var, data_set) {
+  # define the variable name of the dependent variable
+  dependent.variable <- outcome
+  # define the independent variables
+  independent.variables <- c(explan_var,
+                             "depression_and_anxiety",
+                             "eating_disorders",
+                             "obsessive_compulsive_disorders",
+                             "bipolar_and_schizophrenia",
+                             "mhd.posttraumatic_stress_disorder_ptsd",
+                             "autism_spectrum_disorder",
+                             "mhd.attention_deficit_hyperactivity_disorder",
+                             "mhd.personality_disorder",
+                             "Gender_collapsed",
+                             "age_category_collapsed",
+                             "Ethnicity_collapsed",
+                             "key_worker",
+                             "time_diff_coping_lockdown_march_23",
+                             "highest_education"
+  )
+  # create the formula
+  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
+  glm.formula
+
+  # run the glm
+  assign(paste0(outcome,".",explan_var,".model1b.explan"),
+         lm( formula = glm.formula,
+             data = get(data_set)
+         )
+  )
+
+  assign(paste0(outcome,".",explan_var,"model1b.explan_estimates"),
+         tidy(get(paste0(outcome,".",explan_var,".model1b.explan")), conf.int = TRUE) %>%
+           mutate(
+             "Indepent variable" = recode_factor(
+               term,
+               "(Intercept)" = "Intercept",
+               "anxiety_disordersAnxiety disorder" = "Anxiety disorders",
+               "depressive_disordersDepressive disorder" = "Depressive disorders",
+               "depression_and_anxietyDepressive and anxiety disorder" = "Depressive and anxiety disorder",
+               "depression_and_anxietyOnly depressive disorder" = "Only depressive disorder",
+               "depression_and_anxietyOnly anxiety disorder" = "Only anxiety disorder",
+               "eating_disordersEating disorder" = "Eating disorders",
+               "obsessive_compulsive_disordersObsessive compulsive disorder" = "OCDs",
+               "bipolar_and_schizophreniaPsychotic and bipolar disorder" = "Psychotic and bipolar disorder",
+               "bipolar_and_schizophreniaOnly psychotic disorder" = "Only psychotic disorder",
+               "bipolar_and_schizophreniaOnly bipolar disorder" = "Only bipolar disorder",
+               "psychotic_disordersPsychotic disorder" = "Psychotic disorder",
+               "mhd.mania_hypomania_bipolar_or_manicdepressionMania, hypomania, bipolar or manic-depression" = "Bipolar disorder",
+               "mhd.posttraumatic_stress_disorder_ptsdPost-traumatic stress disorder (PTSD)" = "PTSD",
+               "autism_spectrum_disorderAutism spectrum disorder" = "ASD",
+               "mhd.attention_deficit_hyperactivity_disorderAttention deficit or attention deficit and hyperactivity disorder (ADD/ADHD)" = "ADHD",
+               "mhd.personality_disorderPersonality disorder" = "Personality disorder",
+               "Gender_collapsedFemale" = "Female",
+               "Gender_collapsedNon-binary/Self-defined" = "Non-binary/Self-defined",
+               "age_category_collapsed19-25" = "19-25 years",
+               "age_category_collapsed26-35" = "26-35 years",
+               "age_category_collapsed36-45" = "36-45 years",
+               "age_category_collapsed46-55" = "46-55 years",
+               "age_category_collapsed56-65" = "56-65 years",
+               "age_category_collapsed66-70" = "66-70 years",
+               "age_category_collapsed71-75" = "71-75 years",
+               "age_category_collapsed76+" = "76+ years",
+               "Ethnicity_collapsedMixed or multiple ethnic origins" = "Mixed or multiple ethnic origins",
+               "Ethnicity_collapsedAsian or Asian British" = "Asian or Asian British",
+               "Ethnicity_collapsedAfrican or African British" = "African or African British",
+               "Ethnicity_collapsedOther" = "Other ethnicity",
+               "key_workerKey worker" = "Key worker",
+               "time_diff_coping_lockdown_march_23" = "Time difference: Lockdown to baseline",
+               "highest_educationNVQ" = "Highest education NVQ",
+               "highest_educationA-levels" = "Highest education A-Levels",
+               "highest_educationUniversity" = "Highest education University"
+             ),
+             "Estimate" = format(
+               round(estimate,
+                     digits = 2),
+               nsmall = 2),
+             "95% CI low" = format(
+               round(conf.low,
+                     digits = 2),
+               nsmall = 2),
+             "95% CI up" = format(
+               round(conf.high,
+                     digits = 2),
+               nsmall = 2),
+             "SE" = format(
+               round(std.error,
+                     digits = 2),
+               nsmall = 2),
+             "z score" = format(
+               round(statistic,
+                     digits = 2),
+               nsmall = 2),
+             "p value" = case_when(
+               p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
+               p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
+               p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
+             )
+           ) %>%
+           select(
+             "Indepent variable",
+             "Estimate",
+             "95% CI low",
+             "95% CI up",
+             "SE",
+             #    "z score",
+             "p value"
+           )
+  )
+
+  return(get(paste0(outcome,".",explan_var,"model1b.explan_estimates")))
+}
+
+model1b.explan.reg.stats <- function(outcome, explan_var, data_set) {
+  # define the variable name of the dependent variable
+  dependent.variable <- outcome
+  # define the independent variables
+  independent.variables <- c("Disorder_hierarchical")
+  # create the formula
+  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
+  glm.formula
+
+  # run the glm
+  assign(paste0(outcome,".",explan_var,".model1b.explan"),
+         lm( formula = glm.formula,
+             data = get(data_set)
+         )
+  )
+
+  assign(paste0(outcome,".",explan_var,"model1b.explan_reg_stats"),
+         glance(get(paste0(outcome,".",explan_var,".model1b.explan"))) %>%
+           mutate(
+             "n" = format(
+               round(nobs,
+                     digits = 0),
+               nsmall = 0),
+             "R2" = format(
+               round(r.squared,
+                     digits = 2),
+               nsmall = 2),
+             "adjust. R2" = format(
+               round(adj.r.squared,
+                     digits = 2),
+               nsmall = 2),
+             "F" = format(
+               round(statistic,
+                     digits = 2),
+               nsmall = 2),
+             "p value" = case_when(
+               p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
+               p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
+               p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
+             )
+           ) %>%
+           select(
+             "n",
+             "R2",
+             "adjust. R2",
+             "F",
+             "p value",
+             "df"
+           )
+  )
+
+  return(get(paste0(outcome,".",explan_var,"model1b.explan_reg_stats")))
+}
+```
+
+# GAD baseline
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r gad education sensitivity model1b absolute whole sample}
+# Regression coefficients
+gad_baseline_model1b_estimates <- model1b.estimates(outcome = "gad.sum_score_base",
+                                                 data_set = "dat")
+kable(gad_baseline_model1b_estimates)
+gad_baseline_model1b_estimates
+
+# Regression diagnostic statistics
+gad_baseline_model1b_reg_stats <- model1b.reg.stats(outcome = "gad.sum_score_base",
+                                                 data_set = "dat")
+kable(gad_baseline_model1b_reg_stats)
+gad_baseline_model1b_reg_stats
+```
+
+# GAD retro
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r gad education sensitivity model1b sum_score retro}
+# Regression coefficients
+gad_retro_model1b_explan_estimates <- model1b.explan.estimates(outcome = "gad.sum_score_base",
+                                                               explan_var = "gad.sum_score_retro",
+                                                               data_set = "dat.retro")
+kable(gad_retro_model1b_explan_estimates)
+gad_retro_model1b_explan_estimates
+
+# Regression diagnostic statistics
+gad_retro_model1b_explan_reg_stats <- model1b.explan.reg.stats(outcome = "gad.sum_score_base",
+                                                               explan_var = "gad.sum_score_retro",
+                                                               data_set = "dat.retro")
+kable(gad_retro_model1b_explan_reg_stats)
+gad_retro_model1b_explan_reg_stats
+```
+
+# GAD prepan
 ### Model 1b: Overlapping disorders, Adjusted
@@
 
+# PHQ baseline
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r phq education sensitivity model1b absolute whole sample}
+# Regression coefficients
+phq_baseline_model1b_estimates <- model1b.estimates(outcome = "phq.sum_score_base",
+                                                 data_set = "dat")
+kable(phq_baseline_model1b_estimates)
+phq_baseline_model1b_estimates
+
+# Regression diagnostic statistics
+phq_baseline_model1b_reg_stats <- model1b.reg.stats(outcome = "phq.sum_score_base",
+                                                 data_set = "dat")
+kable(phq_baseline_model1b_reg_stats)
+phq_baseline_model1b_reg_stats
+```
+
+# PHQ retro
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r phq education sensitivity model1b sum_score retro}
+# Regression coefficients
+phq_retro_model1b_explan_estimates <- model1b.explan.estimates(outcome = "phq.sum_score_base",
+                                                               explan_var = "phq.sum_score_retro",
+                                                               data_set = "dat.retro")
+kable(phq_retro_model1b_explan_estimates)
+phq_retro_model1b_explan_estimates
+
+# Regression diagnostic statistics
+phq_retro_model1b_explan_reg_stats <- model1b.explan.reg.stats(outcome = "phq.sum_score_base",
+                                                               explan_var = "phq.sum_score_retro",
+                                                               data_set = "dat.retro")
+kable(phq_retro_model1b_explan_reg_stats)
+phq_retro_model1b_explan_reg_stats
+```
+
 # PHQ prepan
-## Regression: Absolute scores
-
 ### Model 1b: Overlapping disorders, Adjusted
@@
 
+# OCIR baseline
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r ocir education sensitivity model1b absolute whole sample}
+# Regression coefficients
+ocir_baseline_model1b_estimates <- model1b.estimates(outcome = "ocir.sum_score_base",
+                                                 data_set = "dat")
+kable(ocir_baseline_model1b_estimates)
+ocir_baseline_model1b_estimates
+
+# Regression diagnostic statistics
+ocir_baseline_model1b_reg_stats <- model1b.reg.stats(outcome = "ocir.sum_score_base",
+                                                 data_set = "dat")
+kable(ocir_baseline_model1b_reg_stats)
+ocir_baseline_model1b_reg_stats
+```
+
+# OCIR retro
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r ocir education sensitivity model1b sum_score retro}
+# Regression coefficients
+ocir_retro_model1b_explan_estimates <- model1b.explan.estimates(outcome = "ocir.sum_score_base",
+                                                               explan_var = "ocir.sum_score_retro",
+                                                               data_set = "dat.retro")
+kable(ocir_retro_model1b_explan_estimates)
+ocir_retro_model1b_explan_estimates
+
+# Regression diagnostic statistics
+ocir_retro_model1b_explan_reg_stats <- model1b.explan.reg.stats(outcome = "ocir.sum_score_base",
+                                                               explan_var = "ocir.sum_score_retro",
+                                                               data_set = "dat.retro")
+kable(ocir_retro_model1b_explan_reg_stats)
+ocir_retro_model1b_explan_reg_stats
+```
+
 # OCIR prepan
-## Regression: Absolute scores
-
 ### Model 1b: Overlapping disorders, Adjusted
@@
 ocir_prepan_model1b_education_estimates <- model1b.explan.estimates(outcome = "ocir.sum_score_base",
-                         explan_var = "highest_education_numeric",
+                         explan_var = "pcl.sum_score_prepan",
                          data_set = "dat.prepan")
@@
 ocir_prepan_model1b_education_reg_stats <- model1b.explan.reg.stats(outcome = "ocir.sum_score_base",
-                         explan_var = "highest_education_numeric",
+                         explan_var = "pcl.sum_score_prepan",
                          data_set = "dat.prepan")
@@
 
+# PCL baseline
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r pcl education sensitivity model1b absolute whole sample}
+# Regression coefficients
+pcl_baseline_model1b_estimates <- model1b.estimates(outcome = "pcl.sum_score_base",
+                                                 data_set = "dat")
+kable(pcl_baseline_model1b_estimates)
+pcl_baseline_model1b_estimates
+
+# Regression diagnostic statistics
+pcl_baseline_model1b_reg_stats <- model1b.reg.stats(outcome = "pcl.sum_score_base",
+                                                 data_set = "dat")
+kable(pcl_baseline_model1b_reg_stats)
+pcl_baseline_model1b_reg_stats
+```
+
 #PCL prepan
-## Regression: Absolute scores
-
 ### Model 1b: Overlapping disorders, Adjusted
@@
 pcl_prepan_model1b_education_estimates <- model1b.explan.estimates(outcome = "pcl.sum_score_base",
-                         explan_var = "highest_education_numeric",
+                         explan_var = "pcl.sum_score_prepan",
                          data_set = "dat.prepan")
@@
 pcl_prepan_model1b_education_reg_stats <- model1b.explan.reg.stats(outcome = "pcl.sum_score_base",
-                         explan_var = "highest_education_numeric",
+                         explan_var = "pcl.sum_score_prepan",
                          data_set = "dat.prepan")
@@
 
-# SENSITIVITY based on employment status
-
-# GAD prepan
-## Regression: Absolute scores
-
+# Sensitivity anlayses based on employment prior to covid
+# Function change to include employment prior to covid as predictors
+
+```{r model1b employment prior covid function}
+model1b.estimates <- function(outcome, data_set) {
+  # define the variable name of the dependent variable
+  dependent.variable <- outcome
+  # define the independent variables
+  independent.variables <- c("depression_and_anxiety",
+                             "eating_disorders",
+                             "obsessive_compulsive_disorders",
+                             "bipolar_and_schizophrenia",
+                             "mhd.posttraumatic_stress_disorder_ptsd",
+                             "autism_spectrum_disorder",
+                             "mhd.attention_deficit_hyperactivity_disorder",
+                             "mhd.personality_disorder",
+                             "Gender_collapsed",
+                             "age_category_collapsed",
+                             "Ethnicity_collapsed",
+                             "key_worker",
+                             "time_diff_coping_lockdown_march_23",
+                             "employment_prior_covid"
+                                )
+  # create the formula
+  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
+  glm.formula
+
+  # run the glm
+  assign(paste0(outcome,".model1b"),
+         lm( formula = glm.formula,
+             data = get(data_set)
+         )
+  )
+
+  assign(paste0(outcome,"model1b_estimates"),
+         tidy(get(paste0(outcome,".model1b")), conf.int = TRUE) %>%
+           mutate(
+             "Indepent variable" = recode_factor(
+               term,
+               "(Intercept)" = "Intercept",
+               "anxiety_disordersAnxiety disorder" = "Anxiety disorders",
+               "depressive_disordersDepressive disorder" = "Depressive disorders",
+               "depression_and_anxietyDepressive and anxiety disorder" = "Depressive and anxiety disorder",
+               "depression_and_anxietyOnly depressive disorder" = "Only depressive disorder",
+               "depression_and_anxietyOnly anxiety disorder" = "Only anxiety disorder",
+               "eating_disordersEating disorder" = "Eating disorders",
+               "obsessive_compulsive_disordersObsessive compulsive disorder" = "OCDs",
+               "bipolar_and_schizophreniaPsychotic and bipolar disorder" = "Psychotic and bipolar disorder",
+               "bipolar_and_schizophreniaOnly psychotic disorder" = "Only psychotic disorder",
+               "bipolar_and_schizophreniaOnly bipolar disorder" = "Only bipolar disorder",
+               "psychotic_disordersPsychotic disorder" = "Psychotic disorder",
+               "mhd.mania_hypomania_bipolar_or_manicdepressionMania, hypomania, bipolar or manic-depression" = "Bipolar disorder",
+               "mhd.posttraumatic_stress_disorder_ptsdPost-traumatic stress disorder (PTSD)" = "PTSD",
+               "autism_spectrum_disorderAutism spectrum disorder" = "ASD",
+               "mhd.attention_deficit_hyperactivity_disorderAttention deficit or attention deficit and hyperactivity disorder (ADD/ADHD)" = "ADHD",
+               "mhd.personality_disorderPersonality disorder" = "Personality disorder",
+               "Gender_collapsedFemale" = "Female",
+               "Gender_collapsedNon-binary/Self-defined" = "Non-binary/Self-defined",
+               "age_category_collapsed19-25" = "19-25 years",
+               "age_category_collapsed26-35" = "26-35 years",
+               "age_category_collapsed36-45" = "36-45 years",
+               "age_category_collapsed46-55" = "46-55 years",
+               "age_category_collapsed56-65" = "56-65 years",
+               "age_category_collapsed66-70" = "66-70 years",
+               "age_category_collapsed71-75" = "71-75 years",
+               "age_category_collapsed76+" = "76+ years",
+               "Ethnicity_collapsedMixed or multiple ethnic origins" = "Mixed or multiple ethnic origins",
+               "Ethnicity_collapsedAsian or Asian British" = "Asian or Asian British",
+               "Ethnicity_collapsedAfrican or African British" = "African or African British",
+               "Ethnicity_collapsedOther" = "Other ethnicity",
+               "key_workerKey worker" = "Key worker",
+               "time_diff_coping_lockdown_march_23" = "Time difference: Lockdown to baseline",
+               "employment_prior_covidEmployed" = "Employed",
+               "employment_prior_covidUnemployed" = "Unemployed",
+               "employment_prior_covidRetired" = "Retired",
+               "employment_prior_covidStudent" = "Student"
+             ),
+             "Estimate" = format(
+               round(estimate,
+                     digits = 2),
+               nsmall = 2),
+             "95% CI low" = format(
+               round(conf.low,
+                     digits = 2),
+               nsmall = 2),
+             "95% CI up" = format(
+               round(conf.high,
+                     digits = 2),
+               nsmall = 2),
+             "SE" = format(
+               round(std.error,
+                     digits = 2),
+               nsmall = 2),
+             "z score" = format(
+               round(statistic,
+                     digits = 2),
+               nsmall = 2),
+             "p value" = case_when(
+               p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
+               p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
+               p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
+             )
+           ) %>%
+           select(
+             "Indepent variable",
+             "Estimate",
+             "95% CI low",
+             "95% CI up",
+             "SE",
+             #    "z score",
+             "p value"
+           )
+  )
+
+  return(get(paste0(outcome,"model1b_estimates")))
+}
+
+model1b.reg.stats <- function(outcome, data_set) {
+  # define the variable name of the dependent variable
+  dependent.variable <- outcome
+  # define the independent variables
+  independent.variables <- c("Disorder_hierarchical")
+  # create the formula
+  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
+  glm.formula
+
+  # run the glm
+  assign(paste0(outcome,".model1b"),
+         lm( formula = glm.formula,
+             data = get(data_set)
+         )
+  )
+
+  assign(paste0(outcome,"model1b_reg_stats"),
+         glance(get(paste0(outcome,".model1b"))) %>%
+           mutate(
+             "n" = format(
+               round(nobs,
+                     digits = 0),
+               nsmall = 0),
+             "R2" = format(
+               round(r.squared,
+                     digits = 2),
+               nsmall = 2),
+             "adjust. R2" = format(
+               round(adj.r.squared,
+                     digits = 2),
+               nsmall = 2),
+             "F" = format(
+               round(statistic,
+                     digits = 2),
+               nsmall = 2),
+             "p value" = case_when(
+               p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
+               p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
+               p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
+             )
+           ) %>%
+           select(
+             "n",
+             "R2",
+             "adjust. R2",
+             "F",
+             "p value",
+             "df"
+           )
+  )
+
+  return(get(paste0(outcome,"model1b_reg_stats")))
+}
+```
+
+```{r model1b.explan employment prior covid function}
+model1b.explan.estimates <- function(outcome, explan_var, data_set) {
+  # define the variable name of the dependent variable
+  dependent.variable <- outcome
+  # define the independent variables
+  independent.variables <- c(explan_var,
+                             "depression_and_anxiety",
+                             "eating_disorders",
+                             "obsessive_compulsive_disorders",
+                             "bipolar_and_schizophrenia",
+                             "mhd.posttraumatic_stress_disorder_ptsd",
+                             "autism_spectrum_disorder",
+                             "mhd.attention_deficit_hyperactivity_disorder",
+                             "mhd.personality_disorder",
+                             "Gender_collapsed",
+                             "age_category_collapsed",
+                             "Ethnicity_collapsed",
+                             "key_worker",
+                             "time_diff_coping_lockdown_march_23",
+                             "employment_prior_covid"
+  )
+  # create the formula
+  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
+  glm.formula
+
+  # run the glm
+  assign(paste0(outcome,".",explan_var,".model1b.explan"),
+         lm( formula = glm.formula,
+             data = get(data_set)
+         )
+  )
+
+  assign(paste0(outcome,".",explan_var,"model1b.explan_estimates"),
+         tidy(get(paste0(outcome,".",explan_var,".model1b.explan")), conf.int = TRUE) %>%
+           mutate(
+             "Indepent variable" = recode_factor(
+               term,
+               "(Intercept)" = "Intercept",
+               "anxiety_disordersAnxiety disorder" = "Anxiety disorders",
+               "depressive_disordersDepressive disorder" = "Depressive disorders",
+               "depression_and_anxietyDepressive and anxiety disorder" = "Depressive and anxiety disorder",
+               "depression_and_anxietyOnly depressive disorder" = "Only depressive disorder",
+               "depression_and_anxietyOnly anxiety disorder" = "Only anxiety disorder",
+               "eating_disordersEating disorder" = "Eating disorders",
+               "obsessive_compulsive_disordersObsessive compulsive disorder" = "OCDs",
+               "bipolar_and_schizophreniaPsychotic and bipolar disorder" = "Psychotic and bipolar disorder",
+               "bipolar_and_schizophreniaOnly psychotic disorder" = "Only psychotic disorder",
+               "bipolar_and_schizophreniaOnly bipolar disorder" = "Only bipolar disorder",
+               "psychotic_disordersPsychotic disorder" = "Psychotic disorder",
+               "mhd.mania_hypomania_bipolar_or_manicdepressionMania, hypomania, bipolar or manic-depression" = "Bipolar disorder",
+               "mhd.posttraumatic_stress_disorder_ptsdPost-traumatic stress disorder (PTSD)" = "PTSD",
+               "autism_spectrum_disorderAutism spectrum disorder" = "ASD",
+               "mhd.attention_deficit_hyperactivity_disorderAttention deficit or attention deficit and hyperactivity disorder (ADD/ADHD)" = "ADHD",
+               "mhd.personality_disorderPersonality disorder" = "Personality disorder",
+               "Gender_collapsedFemale" = "Female",
+               "Gender_collapsedNon-binary/Self-defined" = "Non-binary/Self-defined",
+               "age_category_collapsed19-25" = "19-25 years",
+               "age_category_collapsed26-35" = "26-35 years",
+               "age_category_collapsed36-45" = "36-45 years",
+               "age_category_collapsed46-55" = "46-55 years",
+               "age_category_collapsed56-65" = "56-65 years",
+               "age_category_collapsed66-70" = "66-70 years",
+               "age_category_collapsed71-75" = "71-75 years",
+               "age_category_collapsed76+" = "76+ years",
+               "Ethnicity_collapsedMixed or multiple ethnic origins" = "Mixed or multiple ethnic origins",
+               "Ethnicity_collapsedAsian or Asian British" = "Asian or Asian British",
+               "Ethnicity_collapsedAfrican or African British" = "African or African British",
+               "Ethnicity_collapsedOther" = "Other ethnicity",
+               "key_workerKey worker" = "Key worker",
+               "time_diff_coping_lockdown_march_23" = "Time difference: Lockdown to baseline",
+               "employment_prior_covidEmployed" = "Employed",
+               "employment_prior_covidUnemployed" = "Unemployed",
+               "employment_prior_covidRetired" = "Retired",
+               "employment_prior_covidStudent" = "Student"
+             ),
+             "Estimate" = format(
+               round(estimate,
+                     digits = 2),
+               nsmall = 2),
+             "95% CI low" = format(
+               round(conf.low,
+                     digits = 2),
+               nsmall = 2),
+             "95% CI up" = format(
+               round(conf.high,
+                     digits = 2),
+               nsmall = 2),
+             "SE" = format(
+               round(std.error,
+                     digits = 2),
+               nsmall = 2),
+             "z score" = format(
+               round(statistic,
+                     digits = 2),
+               nsmall = 2),
+             "p value" = case_when(
+               p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
+               p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
+               p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
+             )
+           ) %>%
+           select(
+             "Indepent variable",
+             "Estimate",
+             "95% CI low",
+             "95% CI up",
+             "SE",
+             #    "z score",
+             "p value"
+           )
+  )
+
+  return(get(paste0(outcome,".",explan_var,"model1b.explan_estimates")))
+}
+
+model1b.explan.reg.stats <- function(outcome, explan_var, data_set) {
+  # define the variable name of the dependent variable
+  dependent.variable <- outcome
+  # define the independent variables
+  independent.variables <- c("Disorder_hierarchical")
+  # create the formula
+  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
+  glm.formula
+
+  # run the glm
+  assign(paste0(outcome,".",explan_var,".model1b.explan"),
+         lm( formula = glm.formula,
+             data = get(data_set)
+         )
+  )
+
+  assign(paste0(outcome,".",explan_var,"model1b.explan_reg_stats"),
+         glance(get(paste0(outcome,".",explan_var,".model1b.explan"))) %>%
+           mutate(
+             "n" = format(
+               round(nobs,
+                     digits = 0),
+               nsmall = 0),
+             "R2" = format(
+               round(r.squared,
+                     digits = 2),
+               nsmall = 2),
+             "adjust. R2" = format(
+               round(adj.r.squared,
+                     digits = 2),
+               nsmall = 2),
+             "F" = format(
+               round(statistic,
+                     digits = 2),
+               nsmall = 2),
+             "p value" = case_when(
+               p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
+               p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
+               p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
+             )
+           ) %>%
+           select(
+             "n",
+             "R2",
+             "adjust. R2",
+             "F",
+             "p value",
+             "df"
+           )
+  )
+
+  return(get(paste0(outcome,".",explan_var,"model1b.explan_reg_stats")))
+}
+```
+
+# GAD baseline
 ### Model 1b: Overlapping disorders, Adjusted
 Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
-```{r gad employment sensitivity model1b sum_score prepan}
-# Regression coefficients
-gad_prepan_model1b_employment_estimates <- model1b.explan.estimates(outcome = "gad.sum_score_base",
-                         explan_var = "employment.unemployed_numeric",
-                         data_set = "dat.prepan")
-kable(gad_prepan_model1b_employment_estimates)
-gad_prepan_model1b_employment_estimates
-
-# Regression diagnostic statistics
-gad_prepan_model1b_employment_reg_stats <- model1b.explan.reg.stats(outcome = "gad.sum_score_base",
-                         explan_var = "employment.unemployed_numeric",
-                         data_set = "dat.prepan")
-kable(gad_prepan_model1b_employment_reg_stats)
-gad_prepan_model1b_employment_reg_stats
-```
-
-# PHQ prepan
-## Regression: Absolute scores
-
+```{r gad employment prior covid sensitivity model1b absolute whole sample}
+# Regression coefficients
+gad_baseline_model1b_estimates <- model1b.estimates(outcome = "gad.sum_score_base",
+                                                 data_set = "dat")
+kable(gad_baseline_model1b_estimates)
+gad_baseline_model1b_estimates
+
+# Regression diagnostic statistics
+gad_baseline_model1b_reg_stats <- model1b.reg.stats(outcome = "gad.sum_score_base",
+                                                 data_set = "dat")
+kable(gad_baseline_model1b_reg_stats)
+gad_baseline_model1b_reg_stats
+```
+
+# GAD retro
 ### Model 1b: Overlapping disorders, Adjusted
 Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
-```{r phq employment sensitivity model1b sum_score prepan}
-# Regression coefficients
-phq_prepan_model1b_employment_estimates <- model1b.explan.estimates(outcome = "phq.sum_score_base",
-                         explan_var = "employment.unemployed_numeric",
-                         data_set = "dat.prepan")
-kable(phq_prepan_model1b_employment_estimates)
-phq_prepan_model1b_employment_estimates
-
-# Regression diagnostic statistics
-phq_prepan_model1b_employment_reg_stats <- model1b.explan.reg.stats(outcome = "phq.sum_score_base",
-                         explan_var = "employment.unemployed_numeric",
-                         data_set = "dat.prepan")
-kable(phq_prepan_model1b_employment_reg_stats)
-phq_prepan_model1b_employment_reg_stats
-```
-
-# OCIR prepan 
-## Regression: Absolute scores
+```{r gad employment prior covid sensitivity model1b sum_score retro}
+# Regression coefficients
+gad_retro_model1b_explan_estimates <- model1b.explan.estimates(outcome = "gad.sum_score_base",
+                                                               explan_var = "gad.sum_score_retro",
+                                                               data_set = "dat.retro")
+kable(gad_retro_model1b_explan_estimates)
+gad_retro_model1b_explan_estimates
+
+# Regression diagnostic statistics
+gad_retro_model1b_explan_reg_stats <- model1b.explan.reg.stats(outcome = "gad.sum_score_base",
+                                                               explan_var = "gad.sum_score_retro",
+                                                               data_set = "dat.retro")
+kable(gad_retro_model1b_explan_reg_stats)
+gad_retro_model1b_explan_reg_stats
+```
+
+# GAD prepan
 ### Model 1b: Overlapping disorders, Adjusted
 Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
-```{r ocir employment sensitivity model1b sum_score prepan}
-# Regression coefficients
-ocir_prepan_model1b_employment_estimates <- model1b.explan.estimates(outcome = "ocir.sum_score_base",
-                         explan_var = "employment.unemployed_numeric",
-                         data_set = "dat.prepan")
-kable(ocir_prepan_model1b_employment_estimates)
-ocir_prepan_model1b_employment_estimates
-
-# Regression diagnostic statistics
-ocir_prepan_model1b_employment_reg_stats <- model1b.explan.reg.stats(outcome = "ocir.sum_score_base",
-                         explan_var = "employment.unemployed_numeric",
-                         data_set = "dat.prepan")
-kable(ocir_prepan_model1b_employment_reg_stats)
-ocir_prepan_model1b_employment_reg_stats
-```
-
-#PCL prepan 
-## Regression: Absolute scores
-
+```{r gad employment prior covid sensitivity model1b sum_score prepan}
+# Regression coefficients
+gad_prepan_model1b_education_estimates <- model1b.explan.estimates(outcome = "gad.sum_score_base",
+                         explan_var = "pcl.sum_score_prepan",
+                         data_set = "dat.prepan")
+kable(gad_prepan_model1b_education_estimates)
+gad_prepan_model1b_education_estimates
+
+# Regression diagnostic statistics
+gad_prepan_model1b_education_reg_stats <- model1b.explan.reg.stats(outcome = "gad.sum_score_base",
+                         explan_var = "pcl.sum_score_prepan",
+                         data_set = "dat.prepan")
+kable(gad_prepan_model1b_education_reg_stats)
+gad_prepan_model1b_education_reg_stats
+```
+
+# PHQ baseline
 ### Model 1b: Overlapping disorders, Adjusted
 Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
-```{r pcl employment sensitivty model1b sum_score prepan}
-# Regression coefficients
-pcl_prepan_model1b_employment_estimates <- model1b.explan.estimates(outcome = "pcl.sum_score_base",
-                         explan_var = "employment.unemployed_numeric",
-                         data_set = "dat.prepan")
-kable(pcl_prepan_model1b_employment_estimates)
-pcl_prepan_model1b_employment_estimates
-
-# Regression diagnostic statistics
-pcl_prepan_model1b_employment_reg_stats <- model1b.explan.reg.stats(outcome = "pcl.sum_score_base",
-                         explan_var = "employment.unemployed_numeric",
-                         data_set = "dat.prepan")
-kable(pcl_prepan_model1b_employment_reg_stats)
-pcl_prepan_model1b_employment_reg_stats
-```
-
-# SENSITIVITY based on employment change
-
-```{r create an employment change variable}
-dat.prepan <- dat.prepan %>%
-  mutate(employment_change =
-           case_when(
-             employment.unemployed_numeric == "1" ~ "Unemployed",
-             employment.became_unemployed_numeric == "1" ~ "Became Unemployed",                         
-             employment.furloughed_or_paid_leave_government_funded_numeric == "1" ~ "Furlough",
-             employment.furloughed_or_paid_leave_company_funded_numeric == "1" ~ "Furlough",    
-             employment.paid_leave_furloughed_numeric == "1" ~ "Furlough",                             
-             key_worker_numeric == "1" ~ "Key Worker",                                            
-             employment.government_work_key_workers_numeric == "1" ~ "Key Worker",                
-             employment.zerohours_contract_numeric == "1" ~ "Zero Hours Contract",                         
-             employment.retired_numeric == "1" ~ "Retired",                                   
-             employment.student_gcse_or_a_level_numeric == "1" ~ "Student",                   
-             employment.student_university_numeric == "1" ~ "Student"                        
-           )
-  )
-
-dat.prepan$employment_change <- as.factor(dat.prepan$employment_change)
+```{r phq employment prior covid sensitivity model1b absolute whole sample}
+# Regression coefficients
+phq_baseline_model1b_estimates <- model1b.estimates(outcome = "phq.sum_score_base",
+                                                 data_set = "dat")
+kable(phq_baseline_model1b_estimates)
+phq_baseline_model1b_estimates
+
+# Regression diagnostic statistics
+phq_baseline_model1b_reg_stats <- model1b.reg.stats(outcome = "phq.sum_score_base",
+                                                 data_set = "dat")
+kable(phq_baseline_model1b_reg_stats)
+phq_baseline_model1b_reg_stats
+```
+
+# PHQ retro
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r phq employment prior covid sensitivity model1b sum_score retro}
+# Regression coefficients
+phq_retro_model1b_explan_estimates <- model1b.explan.estimates(outcome = "phq.sum_score_base",
+                                                               explan_var = "phq.sum_score_retro",
+                                                               data_set = "dat.retro")
+kable(phq_retro_model1b_explan_estimates)
+phq_retro_model1b_explan_estimates
+
+# Regression diagnostic statistics
+phq_retro_model1b_explan_reg_stats <- model1b.explan.reg.stats(outcome = "phq.sum_score_base",
+                                                               explan_var = "phq.sum_score_retro",
+                                                               data_set = "dat.retro")
+kable(phq_retro_model1b_explan_reg_stats)
+phq_retro_model1b_explan_reg_stats
+```
+
+# PHQ prepan
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r phq employment prior covid sensitivity model1b sum_score prepan}
+# Regression coefficients
+phq_prepan_model1b_education_estimates <- model1b.explan.estimates(outcome = "phq.sum_score_base",
+                         explan_var = "pcl.sum_score_prepan",
+                         data_set = "dat.prepan")
+kable(phq_prepan_model1b_education_estimates)
+phq_prepan_model1b_education_estimates
+
+# Regression diagnostic statistics
+phq_prepan_model1b_education_reg_stats <- model1b.explan.reg.stats(outcome = "phq.sum_score_base",
+                         explan_var = "pcl.sum_score_prepan",
+                         data_set = "dat.prepan")
+kable(phq_prepan_model1b_education_reg_stats)
+phq_prepan_model1b_education_reg_stats
+```
+
+# OCIR baseline
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r ocir employment prior covid sensitivity model1b absolute whole sample}
+# Regression coefficients
+ocir_baseline_model1b_estimates <- model1b.estimates(outcome = "ocir.sum_score_base",
+                                                 data_set = "dat")
+kable(ocir_baseline_model1b_estimates)
+ocir_baseline_model1b_estimates
+
+# Regression diagnostic statistics
+ocir_baseline_model1b_reg_stats <- model1b.reg.stats(outcome = "ocir.sum_score_base",
+                                                 data_set = "dat")
+kable(ocir_baseline_model1b_reg_stats)
+ocir_baseline_model1b_reg_stats
+```
+
+# OCIR retro
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r ocir employment prior covid sensitivity model1b sum_score retro}
+# Regression coefficients
+ocir_retro_model1b_explan_estimates <- model1b.explan.estimates(outcome = "ocir.sum_score_base",
+                                                               explan_var = "ocir.sum_score_retro",
+                                                               data_set = "dat.retro")
+kable(ocir_retro_model1b_explan_estimates)
+ocir_retro_model1b_explan_estimates
+
+# Regression diagnostic statistics
+ocir_retro_model1b_explan_reg_stats <- model1b.explan.reg.stats(outcome = "ocir.sum_score_base",
+                                                               explan_var = "ocir.sum_score_retro",
+                                                               data_set = "dat.retro")
+kable(ocir_retro_model1b_explan_reg_stats)
+ocir_retro_model1b_explan_reg_stats
+```
+
+# OCIR prepan
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r ocir employment prior covid sensitivity model1b sum_score prepan}
+# Regression coefficients
+ocir_prepan_model1b_education_estimates <- model1b.explan.estimates(outcome = "ocir.sum_score_base",
+                         explan_var = "pcl.sum_score_prepan",
+                         data_set = "dat.prepan")
+kable(ocir_prepan_model1b_education_estimates)
+ocir_prepan_model1b_education_estimates
+
+# Regression diagnostic statistics
+ocir_prepan_model1b_education_reg_stats <- model1b.explan.reg.stats(outcome = "ocir.sum_score_base",
+                         explan_var = "pcl.sum_score_prepan",
+                         data_set = "dat.prepan")
+kable(ocir_prepan_model1b_education_reg_stats)
+ocir_prepan_model1b_education_reg_stats
+```
+
+# PCL baseline
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r pcl employment prior covid sensitivity model1b absolute whole sample}
+# Regression coefficients
+pcl_baseline_model1b_estimates <- model1b.estimates(outcome = "pcl.sum_score_base",
+                                                 data_set = "dat")
+kable(pcl_baseline_model1b_estimates)
+pcl_baseline_model1b_estimates
+
+# Regression diagnostic statistics
+pcl_baseline_model1b_reg_stats <- model1b.reg.stats(outcome = "pcl.sum_score_base",
+                                                 data_set = "dat")
+kable(pcl_baseline_model1b_reg_stats)
+pcl_baseline_model1b_reg_stats
+```
+
+#PCL prepan
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r pcl employment prior covid sensitivty model1b sum_score prepan}
+# Regression coefficients
+pcl_prepan_model1b_education_estimates <- model1b.explan.estimates(outcome = "pcl.sum_score_base",
+                         explan_var = "pcl.sum_score_prepan",
+                         data_set = "dat.prepan")
+kable(pcl_prepan_model1b_education_estimates)
+pcl_prepan_model1b_education_estimates
+
+# Regression diagnostic statistics
+pcl_prepan_model1b_education_reg_stats <- model1b.explan.reg.stats(outcome = "pcl.sum_score_base",
+                         explan_var = "pcl.sum_score_prepan",
+                         data_set = "dat.prepan")
+kable(pcl_prepan_model1b_education_reg_stats)
+pcl_prepan_model1b_education_reg_stats
+```
+
+# Sensitivity anlayses based on employment change
+# Function change to include employment change as predictors
+
+```{r model1b employment change function}
+model1b.estimates <- function(outcome, data_set) {
+  # define the variable name of the dependent variable
+  dependent.variable <- outcome
+  # define the independent variables
+  independent.variables <- c("depression_and_anxiety",
+                             "eating_disorders",
+                             "obsessive_compulsive_disorders",
+                             "bipolar_and_schizophrenia",
+                             "mhd.posttraumatic_stress_disorder_ptsd",
+                             "autism_spectrum_disorder",
+                             "mhd.attention_deficit_hyperactivity_disorder",
+                             "mhd.personality_disorder",
+                             "Gender_collapsed",
+                             "age_category_collapsed",
+                             "Ethnicity_collapsed",
+                             "key_worker",
+                             "time_diff_coping_lockdown_march_23",
+                             "employment_change"
+                                )
+  # create the formula
+  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
+  glm.formula
+
+  # run the glm
+  assign(paste0(outcome,".model1b"),
+         lm( formula = glm.formula,
+             data = get(data_set)
+         )
+  )
+
+  assign(paste0(outcome,"model1b_estimates"),
+         tidy(get(paste0(outcome,".model1b")), conf.int = TRUE) %>%
+           mutate(
+             "Indepent variable" = recode_factor(
+               term,
+               "(Intercept)" = "Intercept",
+               "anxiety_disordersAnxiety disorder" = "Anxiety disorders",
+               "depressive_disordersDepressive disorder" = "Depressive disorders",
+               "depression_and_anxietyDepressive and anxiety disorder" = "Depressive and anxiety disorder",
+               "depression_and_anxietyOnly depressive disorder" = "Only depressive disorder",
+               "depression_and_anxietyOnly anxiety disorder" = "Only anxiety disorder",
+               "eating_disordersEating disorder" = "Eating disorders",
+               "obsessive_compulsive_disordersObsessive compulsive disorder" = "OCDs",
+               "bipolar_and_schizophreniaPsychotic and bipolar disorder" = "Psychotic and bipolar disorder",
+               "bipolar_and_schizophreniaOnly psychotic disorder" = "Only psychotic disorder",
+               "bipolar_and_schizophreniaOnly bipolar disorder" = "Only bipolar disorder",
+               "psychotic_disordersPsychotic disorder" = "Psychotic disorder",
+               "mhd.mania_hypomania_bipolar_or_manicdepressionMania, hypomania, bipolar or manic-depression" = "Bipolar disorder",
+               "mhd.posttraumatic_stress_disorder_ptsdPost-traumatic stress disorder (PTSD)" = "PTSD",
+               "autism_spectrum_disorderAutism spectrum disorder" = "ASD",
+               "mhd.attention_deficit_hyperactivity_disorderAttention deficit or attention deficit and hyperactivity disorder (ADD/ADHD)" = "ADHD",
+               "mhd.personality_disorderPersonality disorder" = "Personality disorder",
+               "Gender_collapsedFemale" = "Female",
+               "Gender_collapsedNon-binary/Self-defined" = "Non-binary/Self-defined",
+               "age_category_collapsed19-25" = "19-25 years",
+               "age_category_collapsed26-35" = "26-35 years",
+               "age_category_collapsed36-45" = "36-45 years",
+               "age_category_collapsed46-55" = "46-55 years",
+               "age_category_collapsed56-65" = "56-65 years",
+               "age_category_collapsed66-70" = "66-70 years",
+               "age_category_collapsed71-75" = "71-75 years",
+               "age_category_collapsed76+" = "76+ years",
+               "Ethnicity_collapsedMixed or multiple ethnic origins" = "Mixed or multiple ethnic origins",
+               "Ethnicity_collapsedAsian or Asian British" = "Asian or Asian British",
+               "Ethnicity_collapsedAfrican or African British" = "African or African British",
+               "Ethnicity_collapsedOther" = "Other ethnicity",
+               "key_workerKey worker" = "Key worker",
+               "time_diff_coping_lockdown_march_23" = "Time difference: Lockdown to baseline",
+               "employment_changeDecreased employment" = "Decreased employment",
+               "employment_changeIncreased employment" = "Increased employment",
+               "employment_changeFurloughed" = "Furloughed",
+               "employment_chnageEmployment not changed" = "Employment not changed"
+             ),
+             "Estimate" = format(
+               round(estimate,
+                     digits = 2),
+               nsmall = 2),
+             "95% CI low" = format(
+               round(conf.low,
+                     digits = 2),
+               nsmall = 2),
+             "95% CI up" = format(
+               round(conf.high,
+                     digits = 2),
+               nsmall = 2),
+             "SE" = format(
+               round(std.error,
+                     digits = 2),
+               nsmall = 2),
+             "z score" = format(
+               round(statistic,
+                     digits = 2),
+               nsmall = 2),
+             "p value" = case_when(
+               p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
+               p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
+               p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
+             )
+           ) %>%
+           select(
+             "Indepent variable",
+             "Estimate",
+             "95% CI low",
+             "95% CI up",
+             "SE",
+             #    "z score",
+             "p value"
+           )
+  )
+
+  return(get(paste0(outcome,"model1b_estimates")))
+}
+
+model1b.reg.stats <- function(outcome, data_set) {
+  # define the variable name of the dependent variable
+  dependent.variable <- outcome
+  # define the independent variables
+  independent.variables <- c("Disorder_hierarchical")
+  # create the formula
+  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
+  glm.formula
+
+  # run the glm
+  assign(paste0(outcome,".model1b"),
+         lm( formula = glm.formula,
+             data = get(data_set)
+         )
+  )
+
+  assign(paste0(outcome,"model1b_reg_stats"),
+         glance(get(paste0(outcome,".model1b"))) %>%
+           mutate(
+             "n" = format(
+               round(nobs,
+                     digits = 0),
+               nsmall = 0),
+             "R2" = format(
+               round(r.squared,
+                     digits = 2),
+               nsmall = 2),
+             "adjust. R2" = format(
+               round(adj.r.squared,
+                     digits = 2),
+               nsmall = 2),
+             "F" = format(
+               round(statistic,
+                     digits = 2),
+               nsmall = 2),
+             "p value" = case_when(
+               p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
+               p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
+               p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
+             )
+           ) %>%
+           select(
+             "n",
+             "R2",
+             "adjust. R2",
+             "F",
+             "p value",
+             "df"
+           )
+  )
+
+  return(get(paste0(outcome,"model1b_reg_stats")))
+}
+```
+
+```{r model1b.explan employment change function}
+model1b.explan.estimates <- function(outcome, explan_var, data_set) {
+  # define the variable name of the dependent variable
+  dependent.variable <- outcome
+  # define the independent variables
+  independent.variables <- c(explan_var,
+                             "depression_and_anxiety",
+                             "eating_disorders",
+                             "obsessive_compulsive_disorders",
+                             "bipolar_and_schizophrenia",
+                             "mhd.posttraumatic_stress_disorder_ptsd",
+                             "autism_spectrum_disorder",
+                             "mhd.attention_deficit_hyperactivity_disorder",
+                             "mhd.personality_disorder",
+                             "Gender_collapsed",
+                             "age_category_collapsed",
+                             "Ethnicity_collapsed",
+                             "key_worker",
+                             "time_diff_coping_lockdown_march_23",
+                             "employment_change"
+  )
+  # create the formula
+  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
+  glm.formula
+
+  # run the glm
+  assign(paste0(outcome,".",explan_var,".model1b.explan"),
+         lm( formula = glm.formula,
+             data = get(data_set)
+         )
+  )
+
+  assign(paste0(outcome,".",explan_var,"model1b.explan_estimates"),
+         tidy(get(paste0(outcome,".",explan_var,".model1b.explan")), conf.int = TRUE) %>%
+           mutate(
+             "Indepent variable" = recode_factor(
+               term,
+               "(Intercept)" = "Intercept",
+               "anxiety_disordersAnxiety disorder" = "Anxiety disorders",
+               "depressive_disordersDepressive disorder" = "Depressive disorders",
+               "depression_and_anxietyDepressive and anxiety disorder" = "Depressive and anxiety disorder",
+               "depression_and_anxietyOnly depressive disorder" = "Only depressive disorder",
+               "depression_and_anxietyOnly anxiety disorder" = "Only anxiety disorder",
+               "eating_disordersEating disorder" = "Eating disorders",
+               "obsessive_compulsive_disordersObsessive compulsive disorder" = "OCDs",
+               "bipolar_and_schizophreniaPsychotic and bipolar disorder" = "Psychotic and bipolar disorder",
+               "bipolar_and_schizophreniaOnly psychotic disorder" = "Only psychotic disorder",
+               "bipolar_and_schizophreniaOnly bipolar disorder" = "Only bipolar disorder",
+               "psychotic_disordersPsychotic disorder" = "Psychotic disorder",
+               "mhd.mania_hypomania_bipolar_or_manicdepressionMania, hypomania, bipolar or manic-depression" = "Bipolar disorder",
+               "mhd.posttraumatic_stress_disorder_ptsdPost-traumatic stress disorder (PTSD)" = "PTSD",
+               "autism_spectrum_disorderAutism spectrum disorder" = "ASD",
+               "mhd.attention_deficit_hyperactivity_disorderAttention deficit or attention deficit and hyperactivity disorder (ADD/ADHD)" = "ADHD",
+               "mhd.personality_disorderPersonality disorder" = "Personality disorder",
+               "Gender_collapsedFemale" = "Female",
+               "Gender_collapsedNon-binary/Self-defined" = "Non-binary/Self-defined",
+               "age_category_collapsed19-25" = "19-25 years",
+               "age_category_collapsed26-35" = "26-35 years",
+               "age_category_collapsed36-45" = "36-45 years",
+               "age_category_collapsed46-55" = "46-55 years",
+               "age_category_collapsed56-65" = "56-65 years",
+               "age_category_collapsed66-70" = "66-70 years",
+               "age_category_collapsed71-75" = "71-75 years",
+               "age_category_collapsed76+" = "76+ years",
+               "Ethnicity_collapsedMixed or multiple ethnic origins" = "Mixed or multiple ethnic origins",
+               "Ethnicity_collapsedAsian or Asian British" = "Asian or Asian British",
+               "Ethnicity_collapsedAfrican or African British" = "African or African British",
+               "Ethnicity_collapsedOther" = "Other ethnicity",
+               "key_workerKey worker" = "Key worker",
+               "time_diff_coping_lockdown_march_23" = "Time difference: Lockdown to baseline",
+               "employment_changeDecreased employment" = "Decreased employment",
+               "employment_changeIncreased employment" = "Increased employment",
+               "employment_changeFurloughed" = "Furloughed",
+               "employment_chnageEmployment not changed" = "Employment not changed"
+             ),
+             "Estimate" = format(
+               round(estimate,
+                     digits = 2),
+               nsmall = 2),
+             "95% CI low" = format(
+               round(conf.low,
+                     digits = 2),
+               nsmall = 2),
+             "95% CI up" = format(
+               round(conf.high,
+                     digits = 2),
+               nsmall = 2),
+             "SE" = format(
+               round(std.error,
+                     digits = 2),
+               nsmall = 2),
+             "z score" = format(
+               round(statistic,
+                     digits = 2),
+               nsmall = 2),
+             "p value" = case_when(
+               p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
+               p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
+               p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
+             )
+           ) %>%
+           select(
+             "Indepent variable",
+             "Estimate",
+             "95% CI low",
+             "95% CI up",
+             "SE",
+             #    "z score",
+             "p value"
+           )
+  )
+
+  return(get(paste0(outcome,".",explan_var,"model1b.explan_estimates")))
+}
+
+model1b.explan.reg.stats <- function(outcome, explan_var, data_set) {
+  # define the variable name of the dependent variable
+  dependent.variable <- outcome
+  # define the independent variables
+  independent.variables <- c("Disorder_hierarchical")
+  # create the formula
+  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
+  glm.formula
+
+  # run the glm
+  assign(paste0(outcome,".",explan_var,".model1b.explan"),
+         lm( formula = glm.formula,
+             data = get(data_set)
+         )
+  )
+
+  assign(paste0(outcome,".",explan_var,"model1b.explan_reg_stats"),
+         glance(get(paste0(outcome,".",explan_var,".model1b.explan"))) %>%
+           mutate(
+             "n" = format(
+               round(nobs,
+                     digits = 0),
+               nsmall = 0),
+             "R2" = format(
+               round(r.squared,
+                     digits = 2),
+               nsmall = 2),
+             "adjust. R2" = format(
+               round(adj.r.squared,
+                     digits = 2),
+               nsmall = 2),
+             "F" = format(
+               round(statistic,
+                     digits = 2),
+               nsmall = 2),
+             "p value" = case_when(
+               p.value < 0.001 ~ formatC(p.value, format = "e", digits = 2),
+               p.value >= 0.001 & p.value < 0.01 ~ formatC(p.value, format = "f", digits = 3),
+               p.value >= 0.01 ~ formatC(p.value, format = "f", digits = 2)
+             )
+           ) %>%
+           select(
+             "n",
+             "R2",
+             "adjust. R2",
+             "F",
+             "p value",
+             "df"
+           )
+  )
+
+  return(get(paste0(outcome,".",explan_var,"model1b.explan_reg_stats")))
+}
+```
+
+# GAD baseline
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r gad employment change sensitivity model1b absolute whole sample}
+# Regression coefficients
+gad_baseline_model1b_estimates <- model1b.estimates(outcome = "gad.sum_score_base",
+                                                 data_set = "dat")
+kable(gad_baseline_model1b_estimates)
+gad_baseline_model1b_estimates
+
+# Regression diagnostic statistics
+gad_baseline_model1b_reg_stats <- model1b.reg.stats(outcome = "gad.sum_score_base",
+                                                 data_set = "dat")
+kable(gad_baseline_model1b_reg_stats)
+gad_baseline_model1b_reg_stats
+```
+
+# GAD retro
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r gad employment change sensitivity model1b sum_score retro}
+# Regression coefficients
+gad_retro_model1b_explan_estimates <- model1b.explan.estimates(outcome = "gad.sum_score_base",
+                                                               explan_var = "gad.sum_score_retro",
+                                                               data_set = "dat.retro")
+kable(gad_retro_model1b_explan_estimates)
+gad_retro_model1b_explan_estimates
+
+# Regression diagnostic statistics
+gad_retro_model1b_explan_reg_stats <- model1b.explan.reg.stats(outcome = "gad.sum_score_base",
+                                                               explan_var = "gad.sum_score_retro",
+                                                               data_set = "dat.retro")
+kable(gad_retro_model1b_explan_reg_stats)
+gad_retro_model1b_explan_reg_stats
 ```
@@
 # GAD prepan
-## Regression: Absolute scores
 ### Model 1b: Overlapping disorders, Adjusted
@@
 # Regression coefficients
-gad_prepan_model1b_employmentchange_estimates <- model1b.explan.estimates(outcome = "gad.sum_score_base",
-                         explan_var = "employment_change",
-                         data_set = "dat.prepan")
-kable(gad_prepan_model1b_employmentchange_estimates)
-gad_prepan_model1b_employmentchange_estimates
-
-# Regression diagnostic statistics
-gad_prepan_model1b_employmentchange_reg_stats <- model1b.explan.reg.stats(outcome = "gad.sum_score_base",
-                         explan_var = "employment_change",
-                         data_set = "dat.prepan")
-kable(gad_prepan_model1b_employmentchange_reg_stats)
-gad_prepan_model1b_employmentchange_reg_stats
+gad_prepan_model1b_education_estimates <- model1b.explan.estimates(outcome = "gad.sum_score_base",
+                         explan_var = "pcl.sum_score_prepan",
+                         data_set = "dat.prepan")
+kable(gad_prepan_model1b_education_estimates)
+gad_prepan_model1b_education_estimates
+
+# Regression diagnostic statistics
+gad_prepan_model1b_education_reg_stats <- model1b.explan.reg.stats(outcome = "gad.sum_score_base",
+                         explan_var = "pcl.sum_score_prepan",
+                         data_set = "dat.prepan")
+kable(gad_prepan_model1b_education_reg_stats)
+gad_prepan_model1b_education_reg_stats
+```
+
+# PHQ baseline
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r phq employment change sensitivity model1b absolute whole sample}
+# Regression coefficients
+phq_baseline_model1b_estimates <- model1b.estimates(outcome = "phq.sum_score_base",
+                                                 data_set = "dat")
+kable(phq_baseline_model1b_estimates)
+phq_baseline_model1b_estimates
+
+# Regression diagnostic statistics
+phq_baseline_model1b_reg_stats <- model1b.reg.stats(outcome = "phq.sum_score_base",
+                                                 data_set = "dat")
+kable(phq_baseline_model1b_reg_stats)
+phq_baseline_model1b_reg_stats
+```
+
+# PHQ retro
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r phq employment change sensitivity model1b sum_score retro}
+# Regression coefficients
+phq_retro_model1b_explan_estimates <- model1b.explan.estimates(outcome = "phq.sum_score_base",
+                                                               explan_var = "phq.sum_score_retro",
+                                                               data_set = "dat.retro")
+kable(phq_retro_model1b_explan_estimates)
+phq_retro_model1b_explan_estimates
+
+# Regression diagnostic statistics
+phq_retro_model1b_explan_reg_stats <- model1b.explan.reg.stats(outcome = "phq.sum_score_base",
+                                                               explan_var = "phq.sum_score_retro",
+                                                               data_set = "dat.retro")
+kable(phq_retro_model1b_explan_reg_stats)
+phq_retro_model1b_explan_reg_stats
 ```
@@
 # PHQ prepan
-## Regression: Absolute scores
-
 ### Model 1b: Overlapping disorders, Adjusted
@@
 # Regression coefficients
-phq_prepan_model1b_employmentchange_estimates <- model1b.explan.estimates(outcome = "phq.sum_score_base",
-                         explan_var = "employment_change",
-                         data_set = "dat.prepan")
-kable(phq_prepan_model1b_employmentchange_estimates)
-phq_prepan_model1b_employmentchange_estimates
-
-# Regression diagnostic statistics
-phq_prepan_model1b_employmentchange_reg_stats <- model1b.explan.reg.stats(outcome = "phq.sum_score_base",
-                         explan_var = "employment_change",
-                         data_set = "dat.prepan")
-kable(phq_prepan_model1b_employmentchange_reg_stats)
-phq_prepan_model1b_employmentchange_reg_stats
+phq_prepan_model1b_education_estimates <- model1b.explan.estimates(outcome = "phq.sum_score_base",
+                         explan_var = "pcl.sum_score_prepan",
+                         data_set = "dat.prepan")
+kable(phq_prepan_model1b_education_estimates)
+phq_prepan_model1b_education_estimates
+
+# Regression diagnostic statistics
+phq_prepan_model1b_education_reg_stats <- model1b.explan.reg.stats(outcome = "phq.sum_score_base",
+                         explan_var = "pcl.sum_score_prepan",
+                         data_set = "dat.prepan")
+kable(phq_prepan_model1b_education_reg_stats)
+phq_prepan_model1b_education_reg_stats
+```
+
+# OCIR baseline
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r ocir employment change sensitivity model1b absolute whole sample}
+# Regression coefficients
+ocir_baseline_model1b_estimates <- model1b.estimates(outcome = "ocir.sum_score_base",
+                                                 data_set = "dat")
+kable(ocir_baseline_model1b_estimates)
+ocir_baseline_model1b_estimates
+
+# Regression diagnostic statistics
+ocir_baseline_model1b_reg_stats <- model1b.reg.stats(outcome = "ocir.sum_score_base",
+                                                 data_set = "dat")
+kable(ocir_baseline_model1b_reg_stats)
+ocir_baseline_model1b_reg_stats
+```
+
+# OCIR retro
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r ocir employment change sensitivity model1b sum_score retro}
+# Regression coefficients
+ocir_retro_model1b_explan_estimates <- model1b.explan.estimates(outcome = "ocir.sum_score_base",
+                                                               explan_var = "ocir.sum_score_retro",
+                                                               data_set = "dat.retro")
+kable(ocir_retro_model1b_explan_estimates)
+ocir_retro_model1b_explan_estimates
+
+# Regression diagnostic statistics
+ocir_retro_model1b_explan_reg_stats <- model1b.explan.reg.stats(outcome = "ocir.sum_score_base",
+                                                               explan_var = "ocir.sum_score_retro",
+                                                               data_set = "dat.retro")
+kable(ocir_retro_model1b_explan_reg_stats)
+ocir_retro_model1b_explan_reg_stats
 ```
@@
 # OCIR prepan
-## Regression: Absolute scores
-
 ### Model 1b: Overlapping disorders, Adjusted
@@
 # Regression coefficients
-ocir_prepan_model1b_employmentchange_estimates <- model1b.explan.estimates(outcome = "ocir.sum_score_base",
-                         explan_var = "employment_change",
-                         data_set = "dat.prepan")
-kable(ocir_prepan_model1b_employmentchange_estimates)
-ocir_prepan_model1b_employmentchange_estimates
-
-# Regression diagnostic statistics
-ocir_prepan_model1b_employmentchange_reg_stats <- model1b.explan.reg.stats(outcome = "ocir.sum_score_base",
-                         explan_var = "employment_change",
-                         data_set = "dat.prepan")
-kable(ocir_prepan_model1b_employmentchange_reg_stats)
-ocir_prepan_model1b_employmentchange_reg_stats
+ocir_prepan_model1b_education_estimates <- model1b.explan.estimates(outcome = "ocir.sum_score_base",
+                         explan_var = "pcl.sum_score_prepan",
+                         data_set = "dat.prepan")
+kable(ocir_prepan_model1b_education_estimates)
+ocir_prepan_model1b_education_estimates
+
+# Regression diagnostic statistics
+ocir_prepan_model1b_education_reg_stats <- model1b.explan.reg.stats(outcome = "ocir.sum_score_base",
+                         explan_var = "pcl.sum_score_prepan",
+                         data_set = "dat.prepan")
+kable(ocir_prepan_model1b_education_reg_stats)
+ocir_prepan_model1b_education_reg_stats
+```
+
+# PCL baseline
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r pcl employment change sensitivity model1b absolute whole sample}
+# Regression coefficients
+pcl_baseline_model1b_estimates <- model1b.estimates(outcome = "pcl.sum_score_base",
+                                                 data_set = "dat")
+kable(pcl_baseline_model1b_estimates)
+pcl_baseline_model1b_estimates
+
+# Regression diagnostic statistics
+pcl_baseline_model1b_reg_stats <- model1b.reg.stats(outcome = "pcl.sum_score_base",
+                                                 data_set = "dat")
+kable(pcl_baseline_model1b_reg_stats)
+pcl_baseline_model1b_reg_stats
 ```
@@
 #PCL prepan
-## Regression: Absolute scores
 ### Model 1b: Overlapping disorders, Adjusted

### 2020-12-04 PANCHANGE_data_preprocessing2020-07-15.Rmd

--- 2020-11-16 PANCHANGE_data_preprocessing2020-07-15.Rmd
@@
 author: "Katie Thompson, Topher Huebel, Molly Davies, Kirstin Purves"
-date: Sys.Date()
+date: '`r format(Sys.time(), "%d %B, %Y")`'
 output:
@@
 ```{r GLAD and EDGI combined}
-if(GLAD_and_EDGI == TRUE)
+if(GLAD_and_EDGI == TRUE){
 glad.and.edgi.dem.raw.id <- rbind(glad.dem.raw.id, edgi.dem.raw.id)
+}
 ```

### 2020-12-04 Retro and prepan comparisons.Rmd

---
title: "Retro and prepan comparisons"
author: "Steven Bright and Henry Rogers"
date: "30/10/2020"
output: html_document
---

#Set up

```{r clean environment}

remove(list = ls())

```

```{r Save a date object}

date <- Sys.Date()

```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Set WD

```{r Set WD}

#Steven's working environment
setwd("c:\\Users\\Student\\Documents\\Git\\PANCHANGE_analysis")
getwd()

#Henry's working environment

```

#Load packages

```{r Load packages}

library(tidyverse)
library(lfactors)
library(data.table)

```

#Set file paths and data names

```{r Source data and file paths}
#Sourcing data paths for raw data (data_path) and clean data (data_path_clean)
#Sourcing data files for 1) saliva_kits 2) coping_glad 3) demographic datasets

source(file = "../Coping_data_path.R")

#May need a different path for PC computers
#source(file = "..\\flare_data_path.R")

```

#Prepare data for merge

```{r Read in data}

data_glad <- read_csv(paste0(data_path, coping_glad))
data_nbr <- read_csv(paste0(data_path, coping_nbr))
data_edgi <- read_csv(paste0(data_path, coping_edgi))

```

```{r Drop first 2 rows}

coping_glad_cohort <- data_glad[3:dim(data_glad)[1],]
coping_edgi_cohort <- data_edgi[3:dim(data_edgi)[1],]
coping_nbr_cohort <- data_nbr[3:dim(data_nbr)[1],]

```

Perform the left join

```{r left join}

coping_data <- left_join(coping_nbr_cohort, 
                         coping_glad_cohort,
                         by = "ExternalReference")

coping_data <- left_join(coping_data, 
                         coping_edgi_cohort,
                         by = "ExternalReference")

#MD addition to visualise:
head(coping_data)

```

#Task overview

1) No change retrospective scores: "impute" to be the same as their pandemic baseline

2) Check correlation between these and the pre-pandemic scores in COPING

3) ACCURACY SCORES: Another question: what proportion of the time are people right about

worse / better / no change (compared to pre-pandemic)

Two categories: (1) is it accurate (i.e. if they say better are they at all better) and (2) is it more than 3 points different

#Task 1: Impute no change scores

### 2020-12-04 PANCHANGE_data_merging.Rmd
small tweak during review. New knit

@@
 ```{r export data}
-glad <- read_rds(file = paste0(data_path, "/glad.rds"))
+glad <- read_rds(paste0(data_path, "glad.rds"))
 dim(glad)
 
-edgi <- read_rds(file = paste0(data_path, "/edgi.rds"))
+edgi <- read_rds(paste0(data_path, "edgi.rds"))
 dim(edgi)
 
-nbr <- read_rds(file = paste0(data_path, "/nbr.rds"))
+nbr <- read_rds(paste0(data_path, "nbr.rds"))
 dim(nbr)
 
-ramp <- read_rds(file = paste0(data_path, "/ramp.rds"))
+ramp <- read_rds(paste0(data_path, "ramp.rds"))
 dim(ramp)

### 2020-12-08 PANCHANGE_analysis.Rmd
adde chnks for half violins with combined sa mples

@@
 
+```{r gad.sum violin plot Sample GLAD EDGI combined, fig.height=14, fig.width=8, dpi=300}
+dat.long.gad.sum %>%
+  mutate(Time_point_renamed = fct_recode(Time_point,
+            "Prepandemic" = "prepan",
+            "Retrospective" = "retro",
+            "Baseline" = "base")
+         ) %>%
+         mutate(Time_point_reordered = fct_relevel(Time_point_renamed,
+            "Baseline",
+            "Retrospective",
+            "Prepandemic")
+         ) %>%
+   mutate(Sample_combined = case_when(
+     Sample == "GLAD" ~ "GLAD and EDGI",
+     Sample == "EDGI" ~ "GLAD and EDGI",
+     Sample == "NBR" ~ "NBR",
+     Sample == "RAMP" ~ "RAMP",)
+         ) %>%
+  ggplot(mapping = aes(
+    x = Time_point_reordered,
+    y = gad.sum_score,
+    fill = Time_point_reordered)) +
+  geom_hline(yintercept = 5, linetype = "dashed", color = "gray") +
+  geom_hline(yintercept = 10, linetype = "dashed", color = "gray") +
+  geom_hline(yintercept = 15, linetype = "dashed", color = "gray") +
+  geom_flat_violin(
+    position = position_nudge(x = .2, y = 0),
+    trim = FALSE,
+    alpha = 0.5
+    ) +
+  geom_point(
+    aes(
+      y = gad.sum_score,
+      color = Time_point_reordered),
+    position = position_jitter(width = .15),
+    size = .5,
+    alpha = 0.8) +
+#  geom_boxplot(
+#    width = .1,
+#    guides = FALSE,
+#    outlier.shape = NA,
+#    alpha = 0.5) +
+ stat_summary(fun.y = mean,
+              fun.ymin = function(x) mean(x) - sd(x),
+              fun.ymax = function(x) mean(x) + sd(x),
+              geom = "pointrange"
+              ) +
+  labs(
+    y = "GAD7 scores",
+    fill = "Time point") +
+  theme_personal +
+  theme(
+    axis.text.y = element_blank()
+  ) +
+  scale_fill_manual(
+    values = COPINGpalette3,
+    breaks = c("Prepandemic", "Retrospective", "Baseline")) +
+  scale_alpha(guide = 'none') +
+  scale_size(guide = 'none') +
+  scale_color_manual(
+    values = COPINGpalette3,
+    breaks = c("Prepandemic", "Retrospective", "Baseline"),
+    guide = "none") +
+  facet_wrap(facets = vars(Sample_combined),
+             nrow = 4
+             ) +
+  coord_flip()
+
+```
+
 ```{r gad.sum violin plot Disorder_hierarchical, fig.height=18, fig.width=20}
@@
 
+```{r phq.sum violin plot Sample GLAD EDGI combined, fig.height=14, fig.width=8}
+dat.long.phq.sum %>%
+  mutate(Time_point_renamed = fct_recode(Time_point,
+                                         "Prepandemic" = "prepan",
+                                         "Retrospective" = "retro",
+                                         "Baseline" = "base")
+  ) %>%
+  mutate(Time_point_reordered = fct_relevel(Time_point_renamed,
+                                            "Baseline",
+                                            "Retrospective",
+                                            "Prepandemic")
+  ) %>%
+   mutate(Sample_combined = case_when(
+     Sample == "GLAD" ~ "GLAD and EDGI",
+     Sample == "EDGI" ~ "GLAD and EDGI",
+     Sample == "NBR" ~ "NBR",
+     Sample == "RAMP" ~ "RAMP",)
+         ) %>%
+  ggplot(mapping = aes(
+    x = Time_point_reordered,
+    y = phq.sum_score,
+    fill = Time_point_reordered)) +
+  geom_hline(yintercept = 8, linetype = "dashed", color = "gray") +
+  geom_hline(yintercept = 11, linetype = "dashed", color = "gray") +
+#  geom_hline(yintercept = 15, linetype = "dashed", color = "gray") +
+  geom_flat_violin(
+    position = position_nudge(x = .2, y = 0),
+    trim = FALSE,
+    alpha = 0.5
+  ) +
+  geom_point(
+    aes(
+      y = phq.sum_score,
+      color = Time_point_reordered),
+    position = position_jitter(width = .15),
+    size = .5,
+    alpha = 0.8) +
+  #  geom_boxplot(
+  #    width = .1,
+  #    guides = FALSE,
+  #    outlier.shape = NA,
+  #    alpha = 0.5) +
+  stat_summary(fun.y = mean,
+               fun.ymin = function(x) mean(x) - sd(x),
+               fun.ymax = function(x) mean(x) + sd(x),
+               geom = "pointrange"
+  ) +
+  labs(
+    y = "PHQ9 scores",
+    fill = "Time point") +
+  theme_personal +
+  theme(
+    axis.text.y = element_blank()
+  ) +
+  scale_fill_manual(
+    values = COPINGpalette3,
+    breaks = c("Prepandemic", "Retrospective", "Baseline")) +
+  scale_alpha(guide = 'none') +
+  scale_size(guide = 'none') +
+  scale_color_manual(
+    values = COPINGpalette3,
+    breaks = c("Prepandemic", "Retrospective", "Baseline"),
+    guide = "none") +
+  facet_wrap(facets = vars(Sample_combined),
+             nrow = 4
+  ) +
+  coord_flip()
+```
+
 ```{r phq.sum violin plot Disorder_hierarchical, fig.height=18, fig.width=20}
@@
 
+```{r ocir.sum violin plot Sample GLAD EDGI combined, fig.height=14, fig.width=8}
+dat.long.ocir.sum %>%
+  mutate(Time_point_renamed = fct_recode(Time_point,
+                                         "Prepandemic" = "prepan",
+                                         "Retrospective" = "retro",
+                                         "Baseline" = "base")
+  ) %>%
+  mutate(Time_point_reordered = fct_relevel(Time_point_renamed,
+                                            "Baseline",
+                                            "Retrospective",
+                                            "Prepandemic")
+  ) %>%
+   mutate(Sample_combined = case_when(
+     Sample == "GLAD" ~ "GLAD and EDGI",
+     Sample == "EDGI" ~ "GLAD and EDGI",
+     Sample == "NBR" ~ "NBR",
+     Sample == "RAMP" ~ "RAMP",)
+         ) %>%
+  ggplot(mapping = aes(
+    x = Time_point_reordered,
+    y = ocir.sum_score,
+    fill = Time_point_reordered)) +
+  geom_hline(yintercept = 21, linetype = "dashed", color = "gray") +
+#  geom_hline(yintercept = 10, linetype = "dashed", color = "gray") +
+#  geom_hline(yintercept = 15, linetype = "dashed", color = "gray") +
+  geom_flat_violin(
+    position = position_nudge(x = .2, y = 0),
+    trim = FALSE,
+    alpha = 0.5
+  ) +
+  geom_point(
+    aes(
+      y = ocir.sum_score,
+      color = Time_point_reordered),
+    position = position_jitter(width = .15),
+    size = .5,
+    alpha = 0.8) +
+  #  geom_boxplot(
+  #    width = .1,
+  #    guides = FALSE,
+  #    outlier.shape = NA,
+  #    alpha = 0.5) +
+  stat_summary(fun.y = mean,
+               fun.ymin = function(x) mean(x) - sd(x),
+               fun.ymax = function(x) mean(x) + sd(x),
+               geom = "pointrange"
+  ) +
+  labs(
+    y = "OCI-R scores",
+    fill = "Time point") +
+  theme_personal +
+  theme(
+    axis.text.y = element_blank()
+  ) +
+  scale_fill_manual(
+    values = COPINGpalette3,
+    breaks = c("Prepandemic", "Retrospective", "Baseline")) +
+  scale_alpha(guide = 'none') +
+  scale_size(guide = 'none') +
+  scale_color_manual(
+    values = COPINGpalette3,
+    breaks = c("Prepandemic", "Retrospective", "Baseline"),
+    guide = "none") +
+  facet_wrap(facets = vars(Sample_combined),
+             nrow = 4
+  ) +
+  coord_flip()
+```
+
 ```{r ocir.sum violin plot Disorder_hierarchical, fig.height=18, fig.width=20}

### 2020-12-08 PANCHANGE_analysis.Rmd
Knitted new.
added formula for making lm formula global to use in forest plots

@@
 library(ggpubr)
+
+if(!require(sjPlot)){
+    install.packages("sjPlot")
+    library(sjPlot)
+}
 ```
@@
 source("../PANCHANGE_raw_path.R")
-
-print(data_path)
 
@@
 
-# function to return standardised beta for plotting in a dataframe
-
-model1b.lm <- function(outcome, data_set) {
+# function to return lm formula for plotting
+
+model1b.lm.form <- function(outcome, data_set) {
   # define the variable name of the dependent variable
@@
   # create the formula
-  glm.formula <- as.formula(paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ "))
-  glm.formula
-
-  # run the glm
-  assign(paste0(outcome,".model1b.lm"),
-         lm( formula = glm.formula,
-             data = get(data_set)
-         )
-  )
-
-  return(get(paste0(outcome,".model1b.lm")))
+  glm.formula <- paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ ")
+
+  # assign it globally with the right variable name.
+  assign(paste0(outcome,".glmformula"),
+         glm.formula,
+         envir = .GlobalEnv
+  )
+
 }
@@
 
-# get lm object to standardise beta
+# get lm object to do forest plots
 
@@
 ```
+
+# Forest Plos
+
+Using standardised betas (2 stdev)
+```{r gad standardised forest plot}
+plot_models(gad_prepan_model1b_lm, std.est = "std2")
+
+```

### 2020-12-09 PANCHANGE_analysis.Rmd
added function to turn lm object into plottable dataset

@@
 
-# Forest Plos
-
-Using standardised betas (2 stdev)
-```{r gad standardised forest plot}
-plot_models(gad_prepan_model1b_lm, std.est = "std2")
-
-```
+# Forest Plots
+
+## run regression models to get normal output
+
+###Function to create formula
+
+```{r function create formula for lin models}
+
+# function for formula
+model1b.lm.form <- function(outcome,explan_var, data_set) {
+  # define the variable name of the dependent variable
+  dependent.variable <- outcome
+  # define the independent variables
+  independent.variables <- c(explan_var,
+                             "depression_and_anxiety",
+                             "eating_disorders",
+                             "obsessive_compulsive_disorders",
+                             "bipolar_and_schizophrenia",
+                             "mhd.posttraumatic_stress_disorder_ptsd",
+                             "autism_spectrum_disorder",
+                             "mhd.attention_deficit_hyperactivity_disorder",
+                             "mhd.personality_disorder",
+                             "Gender_collapsed",
+                             "age_category_collapsed_reordered",
+                             "Ethnicity_collapsed",
+                             "key_worker",
+                             "time_diff_coping_lockdown_march_23"
+  )
+  # create the formula
+  glm.formula <- paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ ")
+
+  # assign it globally with the right variable name.
+  assign(paste0(outcome,explan_var,".glmformula"),
+         glm.formula,
+         envir = .GlobalEnv
+  )
+
+}
+
+```
+
+###Standardise linear variables
+
+```{r standardise linear variables}
+lin_preds <- c("time_diff_coping_lockdown_march_23",
+               "gad.sum_score_prepan",
+               "phq.sum_score_prepan",
+               "pcl.sum_score_prepan",
+               "gad.sum_score_retro",
+               "phq.sum_score_retro",
+               "pcl.sum_score_retro"
+               )
+
+dat.prepan[(names(dat.prepan) %in% lin_preds)] <- apply(dat.prepan[(names(dat.prepan) %in% lin_preds)],2,scale)
+dat.retro[(names(dat.retro) %in% lin_preds)] <- apply(dat.retro[(names(dat.retro) %in% lin_preds)],2,scale)
+
+```
+
+## Run models
+
+```{r create formulas for forest models}
+
+model1b.lm.form("gad.sum_score_base", "gad.sum_score_prepan", dat.prepan)
+model1b.lm.form("gad.sum_score_base", "gad.sum_score_retro", dat.retro)
+
+model1b.lm.form("phq.sum_score_base", "phq.sum_score_prepan", dat.prepan)
+model1b.lm.form("phq.sum_score_base", "phq.sum_score_retro", dat.retro)
+
+model1b.lm.form("pcl.sum_score_base", "pcl.sum_score_prepan", dat.prepan)
+model1b.lm.form("pcl.sum_score_base", "pcl.sum_score_retro", dat.retro)
+
+```
+
+```{r run models for all forest plot items}
+
+gad.prepan.lm <-  lm(formula = gad.sum_score_base.gad.sum_score_prepan.glmformula,
+                            dat.prepan)
+gad.retro.lm <- lm(formula = gad.sum_score_base.gad.sum_score_retro.glmformula,
+                            dat.retro)
+
+phq.prepan.lm <-  lm(formula = phq.sum_score_base.phq.sum_score_prepan.glmformula,
+                            dat.prepan)
+phq.retro.lm <- lm(formula = phq.sum_score_base.phq.sum_score_retro.glmformula,
+                            dat.retro)
+
+pcl.prepan.lm <-  lm(formula = pcl.sum_score_base.pcl.sum_score_prepan.glmformula,
+                            dat.prepan)
+pcl.retro.lm <- lm(formula = pcl.sum_score_base.pcl.sum_score_retro.glmformula,
+                            dat.retro)
+
+```
+
+###Subset retrospective data by samples
+
+```{r subset data for forests into samples}
+
+dat.retro.glad <- dat.retro %>%
+  filter(Sample == "GLAD" | 
+           Sample == "EDGI")
+
+dat.retro.nbr <- dat.retro %>%
+  filter(Sample == "NBR")
+
+dat.retro.ramp <- dat.retro %>%
+  filter(Sample == "RAMP")
+
+```
+
+```{r run models for rero by sample forest plots}
+
+gad.retro.lm.glad <- lm(formula = gad.sum_score_base.gad.sum_score_retro.glmformula,
+                            dat.retro.glad)
+gad.retro.lm.nbr <- lm(formula = gad.sum_score_base.gad.sum_score_retro.glmformula,
+                            dat.retro.nbr)
+gad.retro.lm.ramp <- lm(formula = gad.sum_score_base.gad.sum_score_retro.glmformula,
+                            dat.retro.ramp)
+
+phq.retro.lm.glad <- lm(formula = phq.sum_score_base.phq.sum_score_retro.glmformula,
+                            dat.retro.glad)
+phq.retro.lm.nbr <- lm(formula = phq.sum_score_base.phq.sum_score_retro.glmformula,
+                            dat.retro.nbr)
+phq.retro.lm.ramp <- lm(formula = phq.sum_score_base.phq.sum_score_retro.glmformula,
+                            dat.retro.ramp)
+
+pcl.retro.lm.glad <- lm(formula = pcl.sum_score_base.pcl.sum_score_retro.glmformula,
+                            dat.retro.glad)
+pcl.retro.lm.nbr <- lm(formula = pcl.sum_score_base.pcl.sum_score_retro.glmformula,
+                            dat.retro.nbr)
+pcl.retro.lm.ramp <- lm(formula = pcl.sum_score_base.pcl.sum_score_retro.glmformula,
+                            dat.retro.ramp)
+
+```
+
+## Function to create dataframes ready for forest plots from lm models. 
+```{r function to create data for lm forest plots}
+
+# function to create dataframe from model output
+
+lmoutput_format <- function(lmobject,explan_var,dfname){
+
+  ## Row labels
+  independent.variables <- c("intercept",
+                             explan_var,
+                             "comorbid depression and anxiety compared to control",
+                             "depressive disorder compared to control",
+                             "anxiety disorder compared to control",
+                             "eating disorders compared to control",
+                             "obsessive compulsive disorders compared to control",
+                             "comorbid psychotic and bipolar disorder compared to control",
+                             "psychotic disorder compared to control",
+                             "bipolar disorder compared to control",
+                             "mhd.posttraumatic_stress_disorder_ptsd compared to control",
+                             "autism_spectrum_disorder compared to control",
+                             "mhd.attention_deficit_hyperactivity_disorder compared to control",
+                             "mhd.personality_disorder compared to control",
+                             "Female compared to male",
+                             "Non-binary/Self-defined compared to male",
+                             "16-18 compared to 26-35",
+                             "19-25 compared to 26-35",
+                             "36-45 compared to 26-35",
+                             "46-55 compared to 26-35",
+                             "56-65 compared to 26-35",
+                             "66-70 compared to 26-35",
+                             "71-75 compared to 26-35",
+                             "76+ compared to 26-35",
+                             "Mixed or multiple ethnicities compared to White",
+                             "Asian compared to White",
+                             "Black compared to White",
+                             "Other compared to White",
+                             "key_worker compared to non-keyworker",
+                             "time_diff_coping_lockdown_march_23")
+  ## categories to facet on  
+  categories <- c("Intercept",
+                  "Pre-existing mental health",
+                  "Pre-existing mental health",
+                  "Pre-existing mental health",
+                  "Pre-existing mental health",
+                  "Pre-existing mental health",
+                  "Pre-existing mental health",
+                  "Pre-existing mental health",
+                  "Pre-existing mental health",
+                  "Pre-existing mental health",
+                  "Pre-existing mental health",
+                  "Pre-existing mental health",
+                  "Pre-existing mental health",
+                  "Pre-existing mental health",
+                  "Gender",
+                  "Gender",
+                  "Age",
+                  "Age",
+                  "Age",
+                  "Age",
+                  "Age",
+                  "Age",
+                  "Age",
+                  "Age",
+                  "Ethnicity",
+                  "Ethnicity",
+                  "Ethnicity",
+                  "Ethnicity",
+                  "Other",
+                  "Other")
+
+  # create data frame
+  df <- as.data.frame(coef(summary(lmobject)),row.names=F)
+
+  # add row labels
+  df$RowLabels <- independent.variables
+
+  # Add category labels
+
+  df$Categories <- categories
+
+  # calculate upper and lower confidence intervals
+  df <- df %>%
+    mutate(LowerBound = Estimate - (1.96*`Std. Error`),
+           UpperBound = Estimate + (1.96*`Std. Error`))
+
+  assign(dfname, df, envir = .GlobalEnv)
+
+}
+
+```

### 2020-12-09 PANCHANGE_analysis.Rmd
created function for drawing forest plots in different congfigurations

@@
 
-lmoutput_format <- function(lmobject,explan_var,dfname){
+lmoutput_format <- function(lmobject,explan_var, group, dfname){
 
@@
 
+  ## Disoprder dimension  
+  groups <- c(group,
+                  group,
+                  group,
+                  group,
+                  group,
+                  group,
+                  group,
+                  group,
+                  group,
+                  group,
+                  group,
+                  group,
+                  group,
+                  group,
+                  group,
+                  group,
+                  group,
+                  group,
+                  group,
+                  group,
+                  group,
+                  group,
+                  group,
+                  group,
+                  group,
+                  group,
+                  group,
+                  group,
+                  group,
+                  group)
+
   # create data frame
@@
   # Add category labels
-
   df$Categories <- categories
+
+  # Add group labels
+  df$Group <- groups
 
@@
 
+  # drop intercept row
+    df <- df[(df$RowLabels != 'intercept'),]
+
+  # order factors
+
+  # assign dataframe to global environment
   assign(dfname, df, envir = .GlobalEnv)
@@
 ```
+
+## Function to create forest plots
+
+```{r function for creating forest plots}
+
+lm.forest <- function(data,title)
+
+  p = ggplot(data=data,
+             aes(x =RowLabels,y = Estimate,
+                colour = Group)) +
+
+    geom_point(size = 2,
+               position = position_dodge(0.9)) +
+
+    geom_hline(aes(fill=Group),
+               yintercept =0, 
+               linetype=2)  +
+
+    xlab('Group') + 
+    ylab("Estimate (95% Confidence Interval)")  +
+  ggtitle(title) +
+
+    geom_errorbar(aes(ymin = LowerBound,
+                      ymax = UpperBound),
+                  width = .5,
+                  position = position_dodge(0.9))  +
+
+    facet_wrap(. ~ Categories,
+               strip.position="left",nrow=5,scales = "free_y") +
+
+  scale_colour_manual(values=COPINGpalette5) +
+
+    theme(plot.title=element_text(size=20,face="bold"),
+          axis.text.y=element_text(face="bold"),
+          axis.text.x=element_text(face="bold"),
+          axis.title.x=element_text(size=14,face="bold"),
+          axis.title.y=element_blank(),
+          strip.text.y = element_text(angle=180,face="bold"),
+          panel.background = element_blank(),
+          strip.background = element_rect(fill = "light grey"),
+          panel.border = element_rect(colour = "grey",fill = NA)) +
+    coord_flip()
+  return(p)
+
+}
+
+```

### 2020-12-09 PANCHANGE_analysis.Rmd
added code to create and merge all forest plot datasets

@@
 
-lm.forest <- function(data,title)
+lm.forest <- function(data,title){
 
@@
 ```
+
+## Create data frames and plots using functions and models generated above.
+
+```{r generate datasets for all plots}
+# prepandemic and retrospective, grouped by disorder measure
+lmoutput_format(gad.prepan.lm,"gad.sum_score_prepan","GAD-7", "gad.prepan.lm.for.plot")
+lmoutput_format(gad.retro.lm,"gad.sum_score_retro","GAD-7", "gad.retro.lm.for.plot")
+
+lmoutput_format(phq.prepan.lm,"phq.sum_score_prepan","PHQ-9", "phq.prepan.lm.for.plot")
+lmoutput_format(phq.retro.lm,"phq.sum_score_retro","PHQ-9", "phq.retro.lm.for.plot")
+
+lmoutput_format(pcl.prepan.lm,"pcl.sum_score_prepan","PCL", "pcl.prepan.lm.for.plot")
+lmoutput_format(pcl.retro.lm,"pcl.sum_score_retro","PCL", "pcl.retro.lm.for.plot")
+
+# Retrospective, grouped by sample
+lmoutput_format(gad.retro.lm.glad,"gad.sum_score_retro","GLAD and EDGI", "gad.retro.lm.for.plot.GLAD")
+lmoutput_format(gad.retro.lm.nbr,"gad.sum_score_retro","NBR", "gad.retro.lm.for.plot.NBR")
+lmoutput_format(gad.retro.lm.ramp,"gad.sum_score_retro","RAMP", "gad.retro.lm.for.plot.RAMP")
+
+lmoutput_format(phq.retro.lm.glad,"phq.sum_score_retro","GLAD and EDGI", "phq.retro.lm.for.plot.GLAD")
+lmoutput_format(phq.retro.lm.nbr,"phq.sum_score_retro","NBR", "phq.retro.lm.for.plot.NBR")
+lmoutput_format(phq.retro.lm.ramp,"phq.sum_score_retro","RAMP", "phq.retro.lm.for.plot.RAMP")
+
+lmoutput_format(pcl.retro.lm.glad,"pcl.sum_score_retro","GLAD and EDGI", "pcl.retro.lm.for.plot.GLAD")
+lmoutput_format(pcl.retro.lm.nbr,"pcl.sum_score_retro","NBR", "pcl.retro.lm.for.plot.NBR")
+lmoutput_format(pcl.retro.lm.ramp,"pcl.sum_score_retro","RAMP", "pcl.retro.lm.for.plot.RAMP")
+
+```
+
+```{r merge datasets for different combinations}
+# Disorder groups
+plot.dat.disorder.prepan <- rbind(gad.prepan.lm.for.plot,
+                                  phq.prepan.lm.for.plot,
+                                  pcl.prepan.lm.for.plot)
+
+plot.dat.disorder.retro <- rbind(gad.retro.lm.for.plot,
+                                  phq.retro.lm.for.plot,
+                                  pcl.retro.lm.for.plot)
+
+# time of rating groups
+plot.dat.time.gad <- rbind(gad.prepan.lm.for.plot.timegroup,
+                           gad.retro.lm.for.plot.timegroup)
+
+plot.dat.time.phq <- rbind(phq.prepan.lm.for.plot.timegroup,
+                           phq.retro.lm.for.plot.timegroup)
+
+plot.dat.time.pcl <- rbind(pcl.prepan.lm.for.plot.timegroup,
+                           pcl.retro.lm.for.plot.timegroup)
+
+# by sample (for retrospective)
+
+plot.dat.sample.gad <- rbind(gad.retro.lm.for.plot.GLAD,
+                             gad.retro.lm.for.plot.NBR,
+                             gad.retro.lm.for.plot.RAMP)
+
+plot.dat.sample.phq <- rbind(phq.retro.lm.for.plot.GLAD,
+                             phq.retro.lm.for.plot.NBR,
+                             phq.retro.lm.for.plot.RAMP)
+
+plot.dat.sample.pcl <- rbind(pcl.retro.lm.for.plot.GLAD,
+                             pcl.retro.lm.for.plot.NBR,
+                             pcl.retro.lm.for.plot.RAMP)
+
+```

### 2020-12-09 PANCHANGE_analysis.Rmd
added chunks to run plot function for all configurations

@@
 ```
+
+## Forest plots
+### disorder
+```{r forest plot by disorder prepan, fig.height=14, fig.width=8}
+
+lm.forest(plot.dat.disorder.prepan,"Predictors of pandemic symptoms controlling for prepandemic symptoms")
+
+```
+
+```{r forest plot by disorder retro, fig.height=14, fig.width=8}
+
+lm.forest(plot.dat.disorder.retro,"Predictors of pandemic symptoms controlling for retrospective symptoms")
+
+```
+### time point 
+```{r forest plot by time point gad, fig.height=14, fig.width=8}
+
+lm.forest(plot.dat.time.gad,"Predictors of anxiety during pandemic controlling for retrospective or prepandemic symptoms")
+
+```
+```{r forest plot by time point phq, fig.height=14, fig.width=8}
+
+lm.forest(plot.dat.time.phq,"Predictors of depression during pandemic controlling for retrospective or prepandemic symptoms")
+
+```
+```{r forest plot by time point pcl, fig.height=14, fig.width=8}
+
+lm.forest(plot.dat.time.phq,"Predictors of PTSD during pandemic controlling for retrospective or prepandemic symptoms")
+
+```
+### Sample (retrospective only)
+
+```{r forest plot by sample retro only gad, fig.height=14, fig.width=8}
+
+lm.forest(plot.dat.sample.gad ,"Predictors of anxiety controlling for retrospective symptoms across samples")
+
+```
+```{r forest plot by sample retro only phq, fig.height=14, fig.width=8}
+
+lm.forest(plot.dat.sample.phq ,"Predictors of depression controlling for retrospective symptoms across samples")
+
+```
+```{r forest plot by sample retro only pcl, fig.height=14, fig.width=8}
+
+lm.forest(plot.dat.sample.pcl ,"Predictors of PTSD controlling for retrospective symptoms across samples")
+
+```

### 2020-12-09 PANCHANGE_analysis.Rmd
added figure path, folder and gitignore

@@
 
+opt_chunk$set(fig.path="./figures")
+
 options(bitmapType = 'quartz') # to render fonts better
@@
 # R functions
+
 ## Half-violin plot
@@
 
-# get lm object to do forest plots
-
-gad_prepan_model1b_lm <- model1b.lm(outcome = "gad.diff_score_base_prepan",
-                                           data_set = "dat.prepan")
-
 ```
@@
 
-# function for formula
-model1b.lm.form <- function(outcome,explan_var, data_set) {
+model1b.lm.form <- function(outcome, explan_var, data_set) {
+
   # define the variable name of the dependent variable
@@
   # assign it globally with the right variable name.
-  assign(paste0(outcome,explan_var,".glmformula"),
+  assign(paste0(outcome,".", explan_var, ".glmformula"),
          glm.formula,
          envir = .GlobalEnv
-  )
-
+
+  )
 }
@@
   filter(Sample == "RAMP")
+
+```
+
+### add a single "other ethnicity individual" as a jitter for NBR so this category remains included wihout adding explanation.
+```{r add jitter "other" for NBR other ethnicity so this cat is available for plotting}
+
+dat.retro.nbr$Ethnicity_collapsed[801] <- "Other"  #this person was an NA
+dat.retro.nbr$Ethnicity_collapsed[998] <- "Other"  #this person was an NA
 
@@
 
-  ## Disoprder dimension  
+  ## Disorder dimension  
   groups <- c(group,
@@
   # assign dataframe to global environment
-  assign(dfname, df, envir = .GlobalEnv)
+  assign(dfname, df, envir = knitr::knit_global())
 
@@
 ```{r generate datasets for all plots}
+
 # prepandemic and retrospective, grouped by disorder measure
@@
 lmoutput_format(pcl.retro.lm,"pcl.sum_score_retro","PCL", "pcl.retro.lm.for.plot")
+
+# prepandemic and retrospective, grouped by time point
+lmoutput_format(gad.prepan.lm,"gad.sum_score_prepan","Prepandemic", "gad.prepan.lm.for.plot.timegroup")
+lmoutput_format(gad.retro.lm,"gad.sum_score_retro","Retrospective", "gad.retro.lm.for.plot.timegroup")
+
+lmoutput_format(phq.prepan.lm,"phq.sum_score_prepan","Prepandemic", "phq.prepan.lm.for.plot.timegroup")
+lmoutput_format(phq.retro.lm,"phq.sum_score_retro","Retrospective", "phq.retro.lm.for.plot.timegroup")
+
+lmoutput_format(pcl.prepan.lm,"pcl.sum_score_prepan","Prepandemic", "pcl.prepan.lm.for.plot.timegroup")
+lmoutput_format(pcl.retro.lm,"pcl.sum_score_retro","Retrospective", "pcl.retro.lm.for.plot.timegroup")
 
@@
 
+# Disorder groups: No PCL
+
+plot.dat.disorder.prepan.gadphq <- rbind(gad.prepan.lm.for.plot,
+                                  phq.prepan.lm.for.plot)
+
+plot.dat.disorder.retro.gadphq <- rbind(gad.retro.lm.for.plot,
+                                 phq.retro.lm.for.plot)
+
 # time of rating groups
@@
 ```
+
+### disorder (no PCL)
+```{r forest plot by disorder prepan, fig.height=14, fig.width=8}
+
+lm.forest(plot.dat.disorder.prepan.gadphq,"Predictors of pandemic symptoms controlling for prepandemic symptoms")
+
+```
+
+```{r forest plot by disorder retro, fig.height=14, fig.width=8}
+
+lm.forest(plot.dat.disorder.retro.gadphq,"Predictors of pandemic symptoms controlling for retrospective symptoms")
+
+```
+
 ### time point 
@@
 ```
+
 ```{r forest plot by time point phq, fig.height=14, fig.width=8}
@@
 ```
+
 ```{r forest plot by time point pcl, fig.height=14, fig.width=8}
@@
 ```
+
 ```{r forest plot by sample retro only phq, fig.height=14, fig.width=8}
@@
 ```
+
 ```{r forest plot by sample retro only pcl, fig.height=14, fig.width=8}

### 2020-12-09 FunctionLib/lm_forest.R

@@ -1,0 +1,44 @@
+# Function to create forest plots with different grouping sets using formatted data
+# KLPurves
+
+
+lm.forest <- function(data,title){
+  
+  p = ggplot(data=data,
+             aes(x =RowLabels,y = Estimate,
+                 colour = Group)) +
+    
+    geom_point(size = 2,
+               position = position_dodge(0.9)) +
+    
+    geom_hline(aes(fill=Group),
+               yintercept =0, 
+               linetype=2)  +
+    
+    xlab('Group') + 
+    ylab("Estimate (95% Confidence Interval)")  +
+    ggtitle(title) +
+    
+    geom_errorbar(aes(ymin = LowerBound,
+                      ymax = UpperBound),
+                  width = .5,
+                  position = position_dodge(0.9))  + 
+    
+    facet_wrap(. ~ Categories,
+               strip.position="left",nrow=5,scales = "free_y") +
+    
+    scale_colour_manual(values=COPINGpalette5) +
+    
+    theme(plot.title=element_text(size=20,face="bold"),
+          axis.text.y=element_text(face="bold"),
+          axis.text.x=element_text(face="bold"),
+          axis.title.x=element_text(size=14,face="bold"),
+          axis.title.y=element_blank(),
+          strip.text.y = element_text(angle=180,face="bold"),
+          panel.background = element_blank(),
+          strip.background = element_rect(fill = "light grey"),
+          panel.border = element_rect(colour = "grey",fill = NA)) +
+    coord_flip()
+  return(p)
+  
+}

### 2020-12-09 FunctionLib/lm_formula.R

@@ -1,0 +1,35 @@
+# Function to create a formula for regressions and set this as a global variable
+# Independent variable set is not flexible as we will only need this for final models / limited model set.
+# KLPurves
+
+
+model1b.lm.form <- function(outcome, explan_var, data_set) {
+  
+  # define the variable name of the dependent variable
+  dependent.variable <- outcome
+  # define the independent variables
+  independent.variables <- c(explan_var,
+                             "depression_and_anxiety",
+                             "eating_disorders",
+                             "obsessive_compulsive_disorders",
+                             "bipolar_and_schizophrenia",
+                             "mhd.posttraumatic_stress_disorder_ptsd",
+                             "autism_spectrum_disorder",
+                             "mhd.attention_deficit_hyperactivity_disorder",
+                             "mhd.personality_disorder",
+                             "Gender_collapsed",
+                             "age_category_collapsed_reordered",
+                             "Ethnicity_collapsed",
+                             "key_worker",
+                             "time_diff_coping_lockdown_march_23"
+  )
+  # create the formula
+  glm.formula <- paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ ")
+  
+  # assign it globally with the right variable name.
+  assign(paste0(outcome,".", explan_var, ".glmformula"),
+         glm.formula,
+         envir = .GlobalEnv
+         
+  )
+}

### 2020-12-09 FunctionLib/lm_output.R

@@ -1,0 +1,131 @@
+# Function to format lm model for forest plot and set as global object with specified name
+# Independent variable set is not flexible as we will only need this for final models / limited model set.
+# KLPurves
+
+
+lmoutput_format <- function(lmobject, explan_var, group, dfname){
+  
+  ## Row labels
+  independent.variables <- c("intercept",
+                             explan_var,
+                             "comorbid depression and anxiety compared to control",
+                             "depressive disorder compared to control",
+                             "anxiety disorder compared to control",
+                             "eating disorders compared to control",
+                             "obsessive compulsive disorders compared to control",
+                             "comorbid psychotic and bipolar disorder compared to control",
+                             "psychotic disorder compared to control",
+                             "bipolar disorder compared to control",
+                             "mhd.posttraumatic_stress_disorder_ptsd compared to control",
+                             "autism_spectrum_disorder compared to control",
+                             "mhd.attention_deficit_hyperactivity_disorder compared to control",
+                             "mhd.personality_disorder compared to control",
+                             "Female compared to male",
+                             "Non-binary/Self-defined compared to male",
+                             "16-18 compared to 26-35",
+                             "19-25 compared to 26-35",
+                             "36-45 compared to 26-35",
+                             "46-55 compared to 26-35",
+                             "56-65 compared to 26-35",
+                             "66-70 compared to 26-35",
+                             "71-75 compared to 26-35",
+                             "76+ compared to 26-35",
+                             "Mixed or multiple ethnicities compared to White",
+                             "Asian compared to White",
+                             "Black compared to White",
+                             "Other compared to White",
+                             "key_worker compared to non-keyworker",
+                             "time_diff_coping_lockdown_march_23")
+  ## categories to facet on  
+  categories <- c("Intercept",
+                  "Pre-existing mental health",
+                  "Pre-existing mental health",
+                  "Pre-existing mental health",
+                  "Pre-existing mental health",
+                  "Pre-existing mental health",
+                  "Pre-existing mental health",
+                  "Pre-existing mental health",
+                  "Pre-existing mental health",
+                  "Pre-existing mental health",
+                  "Pre-existing mental health",
+                  "Pre-existing mental health",
+                  "Pre-existing mental health",
+                  "Pre-existing mental health",
[…]

### 2020-12-09 FunctionLib/manknit.R

@@ -1,0 +1,5 @@
+# manual knit to use global environment atfer the file has been run.
+# KLPurves
+
+library(knitr)
+knit('PANCHANGE_analysis.Rmd')

### 2020-12-09 PANCHANGE_analysis.Rmd
corrected figure path

@@
 
-opt_chunk$set(fig.path="./figures")
+knitr::opts_chunk$set(fig.path="figures/")
 
@@
 ### disorder (no PCL)
-```{r forest plot by disorder prepan, fig.height=14, fig.width=8}
+```{r forest plot by disorder prepan no pcl, fig.height=14, fig.width=8}
 
@@
 
-```{r forest plot by disorder retro, fig.height=14, fig.width=8}
+```{r forest plot by disorder retro no pcl, fig.height=14, fig.width=8}
 

### 2020-12-09 PANCHANGE_analysis.Rmd
added chunk to source all function scripts in FunctionLib folder

--- 2020-12-09 PANCHANGE_analysis.Rmd
@@
 # R functions
+
+```{r call in function library functions}
+
+# source all functions in the function library folder
+
+files.sources = list.files("FunctionLib/")
+sapply(files.sources, source)
+
+```
 
@@
 ### disorder
-```{r forest plot by disorder prepan, fig.height=14, fig.width=8}
+```{r forest plot by disorder prepan, fig.height=20, fig.width=12}
 
@@
 
-```{r forest plot by disorder retro, fig.height=14, fig.width=8}
+```{r forest plot by disorder retro, fig.height=20, fig.width=12}
 
@@
 ### disorder (no PCL)
-```{r forest plot by disorder prepan, fig.height=14, fig.width=8}
+```{r forest plot by disorder prepan no pcl, fig.height=20, fig.width=12}
 
@@
 
-```{r forest plot by disorder retro, fig.height=14, fig.width=8}
+```{r forest plot by disorder retro no pcl, fig.height=20, fig.width=12}
 
@@
 ### time point 
-```{r forest plot by time point gad, fig.height=14, fig.width=8}
+```{r forest plot by time point gad, fig.height=20, fig.width=12}
 
@@
 
-```{r forest plot by time point phq, fig.height=14, fig.width=8}
+```{r forest plot by time point phq, fig.height=20, fig.width=12}
 
@@
 
-```{r forest plot by sample retro only gad, fig.height=14, fig.width=8}
+```{r forest plot by sample retro only gad, fig.height=20, fig.width=12}
 
@@
 
-```{r forest plot by sample retro only phq, fig.height=14, fig.width=8}
+```{r forest plot by sample retro only phq, fig.height=20, fig.width=12}
 
@@
 
-```{r forest plot by sample retro only pcl, fig.height=14, fig.width=8}
+```{r forest plot by sample retro only pcl, fig.height=20, fig.width=12}
 

### 2020-12-09 PANCHANGE_analysis.Rmd
moved functions for forest out of script

@@
 
-files.sources = list.files("FunctionLib/")
+files.sources = paste0("FunctionLib/",list.files("FunctionLib/"))
+
 sapply(files.sources, source)
@@
 
-###Function to create formula
-
-```{r function create formula for lin models}
-
-model1b.lm.form <- function(outcome, explan_var, data_set) {
-
-  # define the variable name of the dependent variable
-  dependent.variable <- outcome
-  # define the independent variables
-  independent.variables <- c(explan_var,
-                             "depression_and_anxiety",
-                             "eating_disorders",
-                             "obsessive_compulsive_disorders",
-                             "bipolar_and_schizophrenia",
-                             "mhd.posttraumatic_stress_disorder_ptsd",
-                             "autism_spectrum_disorder",
-                             "mhd.attention_deficit_hyperactivity_disorder",
-                             "mhd.personality_disorder",
-                             "Gender_collapsed",
-                             "age_category_collapsed_reordered",
-                             "Ethnicity_collapsed",
-                             "key_worker",
-                             "time_diff_coping_lockdown_march_23"
-  )
-  # create the formula
-  glm.formula <- paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ ")
-
-  # assign it globally with the right variable name.
-  assign(paste0(outcome,".", explan_var, ".glmformula"),
-         glm.formula,
-         envir = .GlobalEnv
-
-  )
-}
-
-```
-
 ###Standardise linear variables
@@
 
-## Function to create dataframes ready for forest plots from lm models. 
-```{r function to create data for lm forest plots}
-
-# function to create dataframe from model output
-
-lmoutput_format <- function(lmobject,explan_var, group, dfname){
-
-  ## Row labels
-  independent.variables <- c("intercept",
-                             explan_var,
-                             "comorbid depression and anxiety compared to control",
-                             "depressive disorder compared to control",
-                             "anxiety disorder compared to control",
-                             "eating disorders compared to control",
-                             "obsessive compulsive disorders compared to control",
-                             "comorbid psychotic and bipolar disorder compared to control",
-                             "psychotic disorder compared to control",
-                             "bipolar disorder compared to control",
-                             "mhd.posttraumatic_stress_disorder_ptsd compared to control",
-                             "autism_spectrum_disorder compared to control",
-                             "mhd.attention_deficit_hyperactivity_disorder compared to control",
-                             "mhd.personality_disorder compared to control",
-                             "Female compared to male",
-                             "Non-binary/Self-defined compared to male",
-                             "16-18 compared to 26-35",
-                             "19-25 compared to 26-35",
-                             "36-45 compared to 26-35",
-                             "46-55 compared to 26-35",
-                             "56-65 compared to 26-35",
-                             "66-70 compared to 26-35",
-                             "71-75 compared to 26-35",
-                             "76+ compared to 26-35",
-                             "Mixed or multiple ethnicities compared to White",
-                             "Asian compared to White",
-                             "Black compared to White",
-                             "Other compared to White",
-                             "key_worker compared to non-keyworker",
-                             "time_diff_coping_lockdown_march_23")
-  ## categories to facet on  
-  categories <- c("Intercept",
-                  "Pre-existing mental health",
-                  "Pre-existing mental health",
-                  "Pre-existing mental health",
-                  "Pre-existing mental health",
-                  "Pre-existing mental health",
-                  "Pre-existing mental health",
-                  "Pre-existing mental health",
-                  "Pre-existing mental health",
-                  "Pre-existing mental health",
-                  "Pre-existing mental health",
-                  "Pre-existing mental health",
-                  "Pre-existing mental health",
-                  "Pre-existing mental health",
-                  "Gender",
-                  "Gender",
-                  "Age",
-                  "Age",
-                  "Age",
-                  "Age",
-                  "Age",
-                  "Age",
-                  "Age",
-                  "Age",
-                  "Ethnicity",
-                  "Ethnicity",
-                  "Ethnicity",
-                  "Ethnicity",
-                  "Other",
-                  "Other")
-
-  ## Disorder dimension  
-  groups <- c(group,
-                  group,
-                  group,
-                  group,
-                  group,
-                  group,
-                  group,
-                  group,
-                  group,
-                  group,
-                  group,
-                  group,
-                  group,
-                  group,
-                  group,
-                  group,
-                  group,
-                  group,
-                  group,
-                  group,
-                  group,
-                  group,
-                  group,
-                  group,
-                  group,
-                  group,
-                  group,
-                  group,
-                  group,
-                  group)
-
-  # create data frame
-  df <- as.data.frame(coef(summary(lmobject)),row.names=F)
-
-  # add row labels
-  df$RowLabels <- independent.variables
-
-  # Add category labels
-  df$Categories <- categories
-
-  # Add group labels
-  df$Group <- groups
-
-  # calculate upper and lower confidence intervals
-  df <- df %>%
-    mutate(LowerBound = Estimate - (1.96*`Std. Error`),
-           UpperBound = Estimate + (1.96*`Std. Error`))
-
-  # drop intercept row
-    df <- df[(df$RowLabels != 'intercept'),]
-
-  # order factors
-
-  # assign dataframe to global environment
-  assign(dfname, df, envir = knitr::knit_global())
-
-}
-
-```
-
-## Function to create forest plots
-
-```{r function for creating forest plots}
-
-lm.forest <- function(data,title){
-
-  p = ggplot(data=data,
-             aes(x =RowLabels,y = Estimate,
-                colour = Group)) +
-
-    geom_point(size = 2,
-               position = position_dodge(0.9)) +
-
-    geom_hline(aes(fill=Group),
-               yintercept =0, 
-               linetype=2)  +
-
-    xlab('Group') + 
-    ylab("Estimate (95% Confidence Interval)")  +
-  ggtitle(title) +
-
-    geom_errorbar(aes(ymin = LowerBound,
-                      ymax = UpperBound),
-                  width = .5,
-                  position = position_dodge(0.9))  +
-
-    facet_wrap(. ~ Categories,
-               strip.position="left",nrow=5,scales = "free_y") +
-
-  scale_colour_manual(values=COPINGpalette5) +
-
-    theme(plot.title=element_text(size=20,face="bold"),
-          axis.text.y=element_text(face="bold"),
-          axis.text.x=element_text(face="bold"),
-          axis.title.x=element_text(size=14,face="bold"),
-          axis.title.y=element_blank(),
-          strip.text.y = element_text(angle=180,face="bold"),
-          panel.background = element_blank(),
-          strip.background = element_rect(fill = "light grey"),
-          panel.border = element_rect(colour = "grey",fill = NA)) +
-    coord_flip()
-  return(p)
-
-}
-
-```
-
 ## Create data frames and plots using functions and models generated above.
@@
 ### disorder
-```{r forest plot by disorder prepan, fig.height=20, fig.width=12}
+```{r forest plot by disorder prepan, fig.height=20, fig.width=20, dpi=120}
 
@@
 
-```{r forest plot by disorder retro, fig.height=20, fig.width=12}
+```{r forest plot by disorder retro, fig.height=20, fig.width=20, dpi=120}
 
@@
 ### disorder (no PCL)
-```{r forest plot by disorder prepan no pcl, fig.height=20, fig.width=12}
+```{r forest plot by disorder prepan no pcl, fig.height=20, fig.width=20, dpi=120}
 
@@
 
-```{r forest plot by disorder retro no pcl, fig.height=20, fig.width=12}
+```{r forest plot by disorder retro no pcl, fig.height=20, fig.width=20, dpi=120}
 
@@
 ### time point 
-```{r forest plot by time point gad, fig.height=20, fig.width=12}
+```{r forest plot by time point gad, fig.height=20, fig.width=20, dpi=120}
 
@@
 
-```{r forest plot by time point phq, fig.height=20, fig.width=12}
+```{r forest plot by time point phq, fig.height=20, fig.width=20, dpi=120}
 
@@
 
-```{r forest plot by time point pcl, fig.height=14, fig.width=8}
+```{r forest plot by time point pcl, fig.height=20, fig.width=20, dpi=120}
 
@@
 
-```{r forest plot by sample retro only gad, fig.height=20, fig.width=12}
+```{r forest plot by sample retro only gad, fig.height=20, fig.width=20, dpi=120}
 
@@
 
-```{r forest plot by sample retro only phq, fig.height=20, fig.width=12}
+```{r forest plot by sample retro only phq, fig.height=20, fig.width=20, dpi=120}
 
@@
 
-```{r forest plot by sample retro only pcl, fig.height=20, fig.width=12}
+```{r forest plot by sample retro only pcl, fig.height=20, fig.width=20, dpi=120}
 

### 2020-12-09 FunctionLib/lm_forest.R

@@ -29,12 +29,12 @@ lm.forest <- function(data,title){
     
     scale_colour_manual(values=COPINGpalette5) +
     
-    theme(plot.title=element_text(size=20,face="bold"),
+    theme(plot.title=element_text(size=40,face="bold"),
           axis.text.y=element_text(face="bold"),
           axis.text.x=element_text(face="bold"),
-          axis.title.x=element_text(size=14,face="bold"),
+          axis.title.x=element_text(size=28,face="bold"),
           axis.title.y=element_blank(),
-          strip.text.y = element_text(angle=180,face="bold"),
+          strip.text.y = element_text(angle=180,face="bold",size=30),
           panel.background = element_blank(),
           strip.background = element_rect(fill = "light grey"),
           panel.border = element_rect(colour = "grey",fill = NA)) +

### 2020-12-09 FunctionLib/lm_output.R

@@ -2,7 +2,6 @@
 # Independent variable set is not flexible as we will only need this for final models / limited model set.
 # KLPurves
 
-
 lmoutput_format <- function(lmobject, explan_var, group, dfname){
   
   ## Row labels

### 2020-12-09 FunctionLib/manknit.R

@@ -1,5 +1,0 @@
-# manual knit to use global environment atfer the file has been run.
-# KLPurves
-
-library(knitr)
-knit('PANCHANGE_analysis.Rmd')

### 2020-12-09 PANCHANGE_analysis.Rmd
tweaked figure styles. new knit

@@
 
-if(!require(sjPlot)){
-    install.packages("sjPlot")
-    library(sjPlot)
-}
 ```
@@
 
-# Function for split violin plot
-```{r Function for split violin plot}
-GeomSplitViolin <- ggproto("GeomSplitViolin", GeomViolin,
-                           draw_group = function(self, data, ..., draw_quantiles = NULL) {
-  data <- transform(data, xminv = x - violinwidth * (x - xmin), xmaxv = x + violinwidth * (xmax - x))
-  grp <- data[1, "group"]
-  newdata <- plyr::arrange(transform(data, x = if (grp %% 2 == 1) xminv else xmaxv), if (grp %% 2 == 1) y else -y)
-  newdata <- rbind(newdata[1, ], newdata, newdata[nrow(newdata), ], newdata[1, ])
-  newdata[c(1, nrow(newdata) - 1, nrow(newdata)), "x"] <- round(newdata[1, "x"])
-
-  if (length(draw_quantiles) > 0 & !scales::zero_range(range(data$y))) {
-    stopifnot(all(draw_quantiles >= 0), all(draw_quantiles <=
-      1))
-    quantiles <- ggplot2:::create_quantile_segment_frame(data, draw_quantiles)
-    aesthetics <- data[rep(1, nrow(quantiles)), setdiff(names(data), c("x", "y")), drop = FALSE]
-    aesthetics$alpha <- rep(1, nrow(quantiles))
-    both <- cbind(quantiles, aesthetics)
-    quantile_grob <- GeomPath$draw_panel(both, ...)
-    ggplot2:::ggname("geom_split_violin", grid::grobTree(GeomPolygon$draw_panel(newdata, ...), quantile_grob))
-  }
-  else {
-    ggplot2:::ggname("geom_split_violin", GeomPolygon$draw_panel(newdata, ...))
-  }
-})
-
-geom_split_violin <- function(mapping = NULL, data = NULL, stat = "ydensity", position = "identity", ...,
-                              draw_quantiles = NULL, trim = TRUE, scale = "area", na.rm = FALSE,
-                              show.legend = NA, inherit.aes = TRUE) {
-  layer(data = data, mapping = mapping, stat = stat, geom = GeomSplitViolin,
-        position = position, show.legend = show.legend, inherit.aes = inherit.aes,
-        params = list(trim = trim, scale = scale, draw_quantiles = draw_quantiles, na.rm = na.rm, ...))
-}
-```
-
 # Data import
@@
 dim(dat)
-colnames(dat)
+
 ```
@@
 
+## functions that assign global variables and need to be in the markdown
+
+```{r functions required in book for globa assignments}
+lmoutput_format <- function(lmobject, explan_var, group, dfname){
+
+  ## Row labels
+  independent.variables <- c("intercept",
+                             explan_var,
+                             "comorbid depression and anxiety compared to control",
+                             "depressive disorder compared to control",
+                             "anxiety disorder compared to control",
+                             "eating disorders compared to control",
+                             "obsessive compulsive disorders compared to control",
+                             "comorbid psychotic and bipolar disorder compared to control",
+                             "psychotic disorder compared to control",
+                             "bipolar disorder compared to control",
+                             "mhd.posttraumatic_stress_disorder_ptsd compared to control",
+                             "autism_spectrum_disorder compared to control",
+                             "mhd.attention_deficit_hyperactivity_disorder compared to control",
+                             "mhd.personality_disorder compared to control",
+                             "Female compared to male",
+                             "Non-binary/Self-defined compared to male",
+                             "16-18 compared to 26-35",
+                             "19-25 compared to 26-35",
+                             "36-45 compared to 26-35",
+                             "46-55 compared to 26-35",
+                             "56-65 compared to 26-35",
+                             "66-70 compared to 26-35",
+                             "71-75 compared to 26-35",
+                             "76+ compared to 26-35",
+                             "Mixed or multiple ethnicities compared to White",
+                             "Asian compared to White",
+                             "Black compared to White",
+                             "Other compared to White",
+                             "key_worker compared to non-keyworker",
+                             "time_diff_coping_lockdown_march_23")
+  ## categories to facet on  
+  categories <- c("Intercept",
+                  "Pre-existing mental health",
+                  "Pre-existing mental health",
+                  "Pre-existing mental health",
+                  "Pre-existing mental health",
+                  "Pre-existing mental health",
+                  "Pre-existing mental health",
+                  "Pre-existing mental health",
+                  "Pre-existing mental health",
+                  "Pre-existing mental health",
+                  "Pre-existing mental health",
+                  "Pre-existing mental health",
+                  "Pre-existing mental health",
+                  "Pre-existing mental health",
+                  "Gender",
+                  "Gender",
+                  "Age",
+                  "Age",
+                  "Age",
+                  "Age",
+                  "Age",
+                  "Age",
+                  "Age",
+                  "Age",
+                  "Ethnicity",
+                  "Ethnicity",
+                  "Ethnicity",
+                  "Ethnicity",
+                  "Other",
+                  "Other")
+
+  ## Disoprder dimension  
+  groups <- c(group,
+              group,
+              group,
+              group,
+              group,
+              group,
+              group,
+              group,
+              group,
+              group,
+              group,
+              group,
+              group,
+              group,
+              group,
+              group,
+              group,
+              group,
+              group,
+              group,
+              group,
+              group,
+              group,
+              group,
+              group,
+              group,
+              group,
+              group,
+              group,
+              group)
+
+  # create data frame
+  df <- as.data.frame(coef(summary(lmobject)),row.names=F)
+
+  # add row labels
+  df$RowLabels <- independent.variables
+
+  # Add category labels
+  df$Categories <- categories
+
+  # Add group labels
+  df$Group <- groups
+
+  # calculate upper and lower confidence intervals
+  df <- df %>%
+    mutate(LowerBound = Estimate - (1.96*`Std. Error`),
+           UpperBound = Estimate + (1.96*`Std. Error`))
+
+  # drop intercept row
+  df <- df[(df$RowLabels != 'intercept'),]
+
+  # order factors
+  df$RowLabels <- factor(df$RowLabels, levels = rev(independent.variables))   ## individual rows
+  df$Categories <- factor(df$Categories, levels = unique(categories))   ## categories
+
+  # assign dataframe to global environment
+  assign(dfname, df, envir = .GlobalEnv)
+
+}
+
+model1b.lm.form <- function(outcome, explan_var) {
+
+  # define the variable name of the dependent variable
+  dependent.variable <- outcome
+  # define the independent variables
+  independent.variables <- c(explan_var,
+                             "depression_and_anxiety",
+                             "eating_disorders",
+                             "obsessive_compulsive_disorders",
+                             "bipolar_and_schizophrenia",
+                             "mhd.posttraumatic_stress_disorder_ptsd",
+                             "autism_spectrum_disorder",
+                             "mhd.attention_deficit_hyperactivity_disorder",
+                             "mhd.personality_disorder",
+                             "Gender_collapsed",
+                             "age_category_collapsed_reordered",
+                             "Ethnicity_collapsed",
+                             "key_worker",
+                             "time_diff_coping_lockdown_march_23"
+  )
+  # create the formula
+  glm.formula <- paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ ")
+
+  # assign it globally with the right variable name.
+  assign(paste0(outcome,".", explan_var, ".glmformula"),
+         glm.formula,
+         envir = .GlobalEnv
+
+  )
+}
+```
+
 ## run regression models to get normal output
@@
 
-model1b.lm.form("gad.sum_score_base", "gad.sum_score_prepan", dat.prepan)
-model1b.lm.form("gad.sum_score_base", "gad.sum_score_retro", dat.retro)
-
-model1b.lm.form("phq.sum_score_base", "phq.sum_score_prepan", dat.prepan)
-model1b.lm.form("phq.sum_score_base", "phq.sum_score_retro", dat.retro)
-
-model1b.lm.form("pcl.sum_score_base", "pcl.sum_score_prepan", dat.prepan)
-model1b.lm.form("pcl.sum_score_base", "pcl.sum_score_retro", dat.retro)
+model1b.lm.form("gad.sum_score_base", "gad.sum_score_prepan")
+model1b.lm.form("gad.sum_score_base", "gad.sum_score_retro")
+
+model1b.lm.form("phq.sum_score_base", "phq.sum_score_prepan")
+model1b.lm.form("phq.sum_score_base", "phq.sum_score_retro")
+
+model1b.lm.form("pcl.sum_score_base", "pcl.sum_score_prepan")
+model1b.lm.form("pcl.sum_score_base", "pcl.sum_score_retro")
 

### 2020-12-09 FunctionLib/lm_forest.R

@@ -8,7 +8,7 @@ lm.forest <- function(data,title){
              aes(x =RowLabels,y = Estimate,
                  colour = Group)) +
     
-    geom_point(size = 2,
+    geom_point(size = 4,
                position = position_dodge(0.9)) +
     
     geom_hline(aes(fill=Group),
@@ -29,12 +29,13 @@ lm.forest <- function(data,title){
     
     scale_colour_manual(values=COPINGpalette5) +
     
-    theme(plot.title=element_text(size=40,face="bold"),
-          axis.text.y=element_text(face="bold"),
-          axis.text.x=element_text(face="bold"),
+    theme(plot.title=element_text(size=20,face="bold"),
+          axis.text=element_text(face="bold",size=16,),
+          legend.text=element_text(size=16,),
+          legend.title=element_text(face="bold",size=18,),
           axis.title.x=element_text(size=28,face="bold"),
           axis.title.y=element_blank(),
-          strip.text.y = element_text(angle=180,face="bold",size=30),
+          strip.text.y = element_text(angle=180,face="bold",size=20),
           panel.background = element_blank(),
           strip.background = element_rect(fill = "light grey"),
           panel.border = element_rect(colour = "grey",fill = NA)) +

### 2020-12-09 FunctionLib/lm_formula.R

@@ -3,7 +3,7 @@
 # KLPurves
 
 
-model1b.lm.form <- function(outcome, explan_var, data_set) {
+model1b.lm.form <- function(outcome, explan_var) {
   
   # define the variable name of the dependent variable
   dependent.variable <- outcome

### 2020-12-09 FunctionLib/raincloud.R

@@ -1,0 +1,33 @@
+
+## Raincloud plot function (split violin)
+
+GeomSplitViolin <- ggproto("GeomSplitViolin", GeomViolin,
+                           draw_group = function(self, data, ..., draw_quantiles = NULL) {
+                             data <- transform(data, xminv = x - violinwidth * (x - xmin), xmaxv = x + violinwidth * (xmax - x))
+                             grp <- data[1, "group"]
+                             newdata <- plyr::arrange(transform(data, x = if (grp %% 2 == 1) xminv else xmaxv), if (grp %% 2 == 1) y else -y)
+                             newdata <- rbind(newdata[1, ], newdata, newdata[nrow(newdata), ], newdata[1, ])
+                             newdata[c(1, nrow(newdata) - 1, nrow(newdata)), "x"] <- round(newdata[1, "x"])
+                             
+                             if (length(draw_quantiles) > 0 & !scales::zero_range(range(data$y))) {
+                               stopifnot(all(draw_quantiles >= 0), all(draw_quantiles <=
+                                                                         1))
+                               quantiles <- ggplot2:::create_quantile_segment_frame(data, draw_quantiles)
+                               aesthetics <- data[rep(1, nrow(quantiles)), setdiff(names(data), c("x", "y")), drop = FALSE]
+                               aesthetics$alpha <- rep(1, nrow(quantiles))
+                               both <- cbind(quantiles, aesthetics)
+                               quantile_grob <- GeomPath$draw_panel(both, ...)
+                               ggplot2:::ggname("geom_split_violin", grid::grobTree(GeomPolygon$draw_panel(newdata, ...), quantile_grob))
+                             }
+                             else {
+                               ggplot2:::ggname("geom_split_violin", GeomPolygon$draw_panel(newdata, ...))
+                             }
+                           })
+
+geom_split_violin <- function(mapping = NULL, data = NULL, stat = "ydensity", position = "identity", ...,
+                              draw_quantiles = NULL, trim = TRUE, scale = "area", na.rm = FALSE,
+                              show.legend = NA, inherit.aes = TRUE) {
+  layer(data = data, mapping = mapping, stat = stat, geom = GeomSplitViolin,
+        position = position, show.legend = show.legend, inherit.aes = inherit.aes,
+        params = list(trim = trim, scale = scale, draw_quantiles = draw_quantiles, na.rm = na.rm, ...))
+}

### 2020-12-16 figures/Paper_detail_checks.R
added script for detail checks for paper

@@ -1,0 +1,10 @@
+## paper detail checks for PANCHANGE
+## KL Purves
+## 15 Dec 2020
+
+
+# Read in data
+library(tidyverse)
+
+source(./)
+

### 2020-12-16 PANCHANGE_exclusion_descriptives.Rmd
added figure knit to descriptive rmds. Fixed exclusions for MH diagnosis

@@
                       cache=FALSE)
+
+knitr::opts_chunk$set(fig.path="figures/")
 
@@
 dim(dat.raw)
-colnames(dat.raw)
+
 ```
@@
   filter( # Participants should have responded to the mental health diagnosis (MHD) questionnaire
-  !is.na(depressive_disorders) &
+  (!is.na(depressive_disorders) &
  !is.na(anxiety_disorders) &
@@
   !is.na(mhd.personality_disorder) &
-  !is.na(control)
+  !is.na(control)) |
+  !is.na(DidNotRespondMHD)
   ) %>% 
@@
 ```
+
+# frequencies and descriptives in exclusion data
 

### 2020-12-16 PANCHANGE_variable_creation.Rmd
added figure knit to descriptive rmds. Fixed exclusions for MH diagnosis

@@
              Ethnicity_numeric == 4 ~ 3, #African or African British
-             Ethnicity_numeric == 5 ~ 3, #Arab - combined with African/African British
+             Ethnicity_numeric == 5 ~ 4, #Arab - combined with African/African British
              Ethnicity_numeric == 6 ~ 4  #Other ethnic group
@@
 ```
+## create a variable for chose not to respond to the Mental health questions
+
+```{r choce not to respond MHD}
+
+dat <- dat %>%
+  mutate(DidNotRespondMHD  = 
+           case_when(
+             (is.na(depressive_disorders) &
+ is.na(anxiety_disorders) &
+  is.na(eating_disorders) &
+  is.na(obsessive_compulsive_disorders) &
+ is.na(psychotic_disorders) &
+  is.na(mhd.mania_hypomania_bipolar_or_manicdepression) &
+  is.na(mhd.posttraumatic_stress_disorder_ptsd) &    
+  is.na(autism_spectrum_disorder) &
+  is.na(mhd.attention_deficit_hyperactivity_disorder) &
+  is.na(mhd.personality_disorder) &
+  is.na(control)) ~ 1))
+
+```
 

### 2020-12-16 PANCHANGE_exclusion_descriptives.Rmd
added frequency tables for excluded dataset

@@
 # frequencies and descriptives in exclusion data
+
+### pandemic change gad
+
+```{r freq table gad perceived change}
+dat %>%
+  freq(gad.pandemic_felt_feelings)
+
+```
+### pandemic change phq
+
+```{r freq table phq perceived change}
+
+dat %>%
+  freq(phq.pandemic_felt_feelings)
+
+```
+
+### Ethnicity
+```{r freq table ethnicity}
+dat %>%
+  freq(Ethnicity_collapsed) 
+```
+### Gender
+```{r freq table gender}
+dat %>%
+  freq(Gender_collapsed) 
+```
+### age categorical
+```{r freq table age collapsed}
+dat %>%
+  freq(age_category_collapsed) 
+```
+
+### anxiety disorders
+```{r freq table diagnosis anxiety}
+dat %>%
+  freq(anxiety_disorders) 
+```
+
+### Depressive disorders
+```{r freq table diagnosis depression}
+dat %>%
+  freq(depressive_disorders) 
+```
+### Depression and anxiety
+```{r freq table diagnosis depression and anxiety}
+dat %>%
+  freq(depression_and_anxiety) 
+```
+### Eating disorders
+```{r freq table diagnosis eating disorder}
+dat %>%
+  freq(eating_disorders)
+
+```
+### OCD
+```{r freq table diagnosis obsessive compulsive disorders}
+dat %>%
+  freq(obsessive_compulsive_disorders)
+
+```
+
+### Psychosis
+```{r freq table diagnosis psychotic disorders}
+dat %>%
+  freq(psychotic_disorders)
+
+```
+
+### Bipolar
+```{r freq table diagnosis bipolar}
+dat %>%
+  freq(mhd.mania_hypomania_bipolar_or_manicdepression)
+
+```
+
+### PTSD
+```{r freq table diagnosis PTSD}
+dat %>%
+  freq(mhd.posttraumatic_stress_disorder_ptsd)
+
+```
+
+### ASD
+
+```{r freq table diagnosis ASD}
+dat %>%
+  freq(autism_spectrum_disorder)
+
+```
+
+### ADHD
+```{r freq table diagnosis ADHD}
+dat %>%
+  freq(mhd.attention_deficit_hyperactivity_disorder)
+
+```
+
+### Personality disorders
+```{r freq table diagnosis personality disorder}
+dat %>%
+  freq(mhd.personality_disorder)
+
+```
+
+### Controls 
+```{r freq table diagnosis control}
+dat %>%
+  freq(control) 
+```
 

### 2020-12-16 PANCHANGE_exclusion_descriptives.Rmd
Added keyworker status to employment variable

@@
   freq(age_category_collapsed) 
+```
+### Employment
+
+```{r freq table employment collapsed}
+dat %>%
+  freq(employment_prior_covid) 
 ```

### 2020-12-16 PANCHANGE_variable_creation.Rmd
Added keyworker status to employment variable

@@
 dim(dat)
-colnames(dat)
 ```
@@
   freq(Ethnicity_collapsed)
+```
+
+## Employment
+Adjust so employed category is keyworker vs non keyworker
+
+```{r adjust employment prior covid category}
+
+dat <- 
+  dat %>%
+  mutate(employment_prior_covid_2 =  
+           case_when(dat$employment_prior_covid == "Employed" & key_worker == "Key worker" ~ "Key worker",
+                     dat$employment_prior_covid == "Employed" & key_worker == "No key worker" ~ "Employed",
+                    dat$employment_prior_covid == "Unemployed" ~ "Unemployed",
+                     dat$employment_prior_covid == "Student" ~ "Student",
+                    dat$employment_prior_covid == "Retired" ~ "Retired"))
+
+dat$employment_prior_covid <- dat$employment_prior_covid_2
+
 ```

### 2020-12-16 figures/Paper_detail_checks.R

@@ -5,6 +5,35 @@
 
 # Read in data
 library(tidyverse)
+library(data.table)
+library(lubridate)
 
-source(./)
+# get file info
+source("/Users/kirstin/Dropbox/SGDP/RAMP/Projects/PANCHANGE/PANCHANGE_raw_path.R")
+
+
+# check the date of the last COPING baseline data point.
+
+# read in the 4 cohort data
+
+alldat <-  readRDS(file = paste0(data_path, "/four_cohorts.rds"))
+rampdat <-  readRDS(file = paste0(data_path, "/ramp.rds"))
+
+## Subset samples
+
+GLAD <- alldat %>%
+  filter(Sample == "GLAD" | 
+           Sample == "EDGI")
+
+NBR <- alldat %>%
+  filter(Sample == "NBR")
+
+RAMP <- alldat %>%
+  filter(Sample == "RAMP")
+
+## Get the most recent baseline sign up per sample
+
+max(RAMP$startDate.coping)
+max(GLAD$startDate.coping)
+max(NBR$startDate.coping)
 

### 2020-12-16 PANCHANGE_analysis.Rmd
knitted exclusion file with all datasets updated for employment

@@
                              "Ethnicity_collapsed",
-                             "key_worker",
                              "time_diff_coping_lockdown_march_23",
@@
                "Ethnicity_collapsedOther" = "Other ethnicity",
-               "key_workerKey worker" = "Key worker",
                "time_diff_coping_lockdown_march_23" = "Time difference: Lockdown to baseline",
+               "employment_prior_covidKey worker" = "Key worker",
                "employment_prior_covidEmployed" = "Employed",
@@
                              "Other compared to White",
-                             "key_worker compared to non-keyworker",
+                             "key_worker compared to employed",
+                             "unemployed compared to employed",
+                             "student compared to employed",
+                             "retired compared to employed",
                              "time_diff_coping_lockdown_march_23")
@@
                   "Ethnicity",
-                  "Other",
+                  "Employment",
+                  "Employment",
+                  "Employment",
+                  "Employment",
                   "Other")
 
-  ## Disoprder dimension  
+  ## Disorder dimension  
   groups <- c(group,
@@
               group,
+              group,
+              group,
+              group,
               group)
@@
                              "Ethnicity_collapsed",
-                             "key_worker",
+                             "employment_prior_covid",
                              "time_diff_coping_lockdown_march_23"

### 2020-12-17 PANCHANGE_analysis.Rmd
tweaked figure labelling for forest plots

@@
                              explan_var,
-                             "comorbid depression and anxiety compared to control",
-                             "depressive disorder compared to control",
-                             "anxiety disorder compared to control",
-                             "eating disorders compared to control",
-                             "obsessive compulsive disorders compared to control",
-                             "comorbid psychotic and bipolar disorder compared to control",
-                             "psychotic disorder compared to control",
-                             "bipolar disorder compared to control",
-                             "mhd.posttraumatic_stress_disorder_ptsd compared to control",
-                             "autism_spectrum_disorder compared to control",
-                             "mhd.attention_deficit_hyperactivity_disorder compared to control",
-                             "mhd.personality_disorder compared to control",
-                             "Female compared to male",
-                             "Non-binary/Self-defined compared to male",
-                             "16-18 compared to 26-35",
-                             "19-25 compared to 26-35",
-                             "36-45 compared to 26-35",
-                             "46-55 compared to 26-35",
-                             "56-65 compared to 26-35",
-                             "66-70 compared to 26-35",
-                             "71-75 compared to 26-35",
-                             "76+ compared to 26-35",
-                             "Mixed or multiple ethnicities compared to White",
-                             "Asian compared to White",
-                             "Black compared to White",
-                             "Other compared to White",
-                             "key_worker compared to employed",
-                             "unemployed compared to employed",
-                             "student compared to employed",
-                             "retired compared to employed",
-                             "time_diff_coping_lockdown_march_23")
+                             "Comorbid depression and anxiety",
+                             "Depressive disorders",
+                             "Anxiety disorders",
+                             "Eating disorders",
+                             "Obsessive compulsive disorders",
+                             "Comorbid psychotic and bipolar disorders",
+                             "Psychotic disorders",
+                             "Bipolar disorder",
+                             "Post traumatic stress disorder",
+                             "Autism spectrum disorder",
+                             "Attention deficit hyperactivity disorder",
+                             "Personality disorders",
+                             "Female",
+                             "Non-binary/Self-defined",
+                             "16-18",
+                             "19-25",
+                             "36-45",
+                             "46-55",
+                             "56-65",
+                             "66-70",
+                             "71-75",
+                             "76+",
+                             "Mixed or multiple ethnicities",
+                             "Asian",
+                             "Black",
+                             "Other",
+                             "Key worker",
+                             "Unemployed",
+                             "Student",
+                             "Retired",
+                             "Time between lockdown and baseline")
   ## categories to facet on  
   categories <- c("Intercept",
-                  "Pre-existing mental health",
-                  "Pre-existing mental health",
-                  "Pre-existing mental health",
-                  "Pre-existing mental health",
-                  "Pre-existing mental health",
-                  "Pre-existing mental health",
-                  "Pre-existing mental health",
-                  "Pre-existing mental health",
-                  "Pre-existing mental health",
-                  "Pre-existing mental health",
-                  "Pre-existing mental health",
-                  "Pre-existing mental health",
-                  "Pre-existing mental health",
-                  "Gender",
-                  "Gender",
-                  "Age",
-                  "Age",
-                  "Age",
-                  "Age",
-                  "Age",
-                  "Age",
-                  "Age",
-                  "Age",
-                  "Ethnicity",
-                  "Ethnicity",
-                  "Ethnicity",
-                  "Ethnicity",
-                  "Employment",
-                  "Employment",
-                  "Employment",
-                  "Employment",
+                  "Pre-existing mental health (Reference controls)",
+                  "Pre-existing mental health (Reference controls)",
+                  "Pre-existing mental health (Reference controls)",
+                  "Pre-existing mental health (Reference controls)",
+                  "Pre-existing mental health (Reference controls)",
+                  "Pre-existing mental health (Reference controls)",
+                  "Pre-existing mental health (Reference controls)",
+                  "Pre-existing mental health (Reference controls)",
+                  "Pre-existing mental health (Reference controls)",
+                  "Pre-existing mental health (Reference controls)",
+                  "Pre-existing mental health (Reference controls)",
+                  "Pre-existing mental health (Reference controls)",
+                  "Pre-existing mental health (Reference controls)",
+                  "Gender (Reference male)",
+                  "Gender (Reference male)",
+                  "Age (Reference 26-35)",
+                  "Age (Reference 26-35)",
+                  "Age (Reference 26-35)",
+                  "Age (Reference 26-35)",
+                  "Age (Reference 26-35)",
+                  "Age (Reference 26-35)",
+                  "Age (Reference 26-35)",
+                  "Age (Reference 26-35)",
+                  "Ethnicity (Reference White)",
+                  "Ethnicity (Reference White)",
+                  "Ethnicity (Reference White)",
+                  "Ethnicity (Reference White)",
+                  "Employment (Reference: Employed)",
+                  "Employment (Reference: Employed)",
+                  "Employment (Reference: Employed)",
+                  "Employment (Reference: Employed)",
                   "Other")
@@
 ```{r standardise linear variables}
+
+## Create copies of the variables renamed
+
+dat.prepan$GAD.prepandemic <- dat.prepan$gad.sum_score_prepan
+dat.prepan$PHQ.prepandemic <- dat.prepan$phq.sum_score_prepan
+dat.prepan$PCL.prepandemic <- dat.prepan$pcl.sum_score_prepan
+
+dat.retro$GAD.retrospective <- dat.retro$gad.sum_score_retro
+dat.retro$PHQ.retrospective <- dat.retro$phq.sum_score_retro
+dat.retro$PCL.retrospective <- dat.retro$pcl.sum_score_retro
+
 lin_preds <- c("time_diff_coping_lockdown_march_23",
-               "gad.sum_score_prepan",
-               "phq.sum_score_prepan",
-               "pcl.sum_score_prepan",
-               "gad.sum_score_retro",
-               "phq.sum_score_retro",
-               "pcl.sum_score_retro"
+               "GAD.prepandemic",
+               "PHQ.prepandemic",
+               "PCL.prepandemic",
+               "GAD.retrospective",
+               "PHQ.retrospective",
+               "PCL.retrospective"
                )
@@
 
-model1b.lm.form("gad.sum_score_base", "gad.sum_score_prepan")
-model1b.lm.form("gad.sum_score_base", "gad.sum_score_retro")
-
-model1b.lm.form("phq.sum_score_base", "phq.sum_score_prepan")
-model1b.lm.form("phq.sum_score_base", "phq.sum_score_retro")
-
-model1b.lm.form("pcl.sum_score_base", "pcl.sum_score_prepan")
-model1b.lm.form("pcl.sum_score_base", "pcl.sum_score_retro")
+model1b.lm.form("gad.sum_score_base", "GAD.prepandemic")
+model1b.lm.form("gad.sum_score_base", "GAD.retrospective")
+
+model1b.lm.form("phq.sum_score_base", "PHQ.prepandemic")
+model1b.lm.form("phq.sum_score_base", "PHQ.retrospective")
+
+model1b.lm.form("pcl.sum_score_base", "PCL.prepandemic")
+model1b.lm.form("pcl.sum_score_base", "PCL.retrospective")
 
@@
 
-gad.prepan.lm <-  lm(formula = gad.sum_score_base.gad.sum_score_prepan.glmformula,
+gad.prepan.lm <-  lm(formula = gad.sum_score_base.GAD.prepandemic.glmformula,
                             dat.prepan)
-gad.retro.lm <- lm(formula = gad.sum_score_base.gad.sum_score_retro.glmformula,
+gad.retro.lm <- lm(formula = gad.sum_score_base.GAD.retrospective.glmformula,
                             dat.retro)
 
-phq.prepan.lm <-  lm(formula = phq.sum_score_base.phq.sum_score_prepan.glmformula,
+phq.prepan.lm <-  lm(formula = phq.sum_score_base.PHQ.prepandemic.glmformula,
                             dat.prepan)
-phq.retro.lm <- lm(formula = phq.sum_score_base.phq.sum_score_retro.glmformula,
+phq.retro.lm <- lm(formula = phq.sum_score_base.PHQ.retrospective.glmformula,
                             dat.retro)
 
-pcl.prepan.lm <-  lm(formula = pcl.sum_score_base.pcl.sum_score_prepan.glmformula,
+pcl.prepan.lm <-  lm(formula = pcl.sum_score_base.PCL.prepandemic.glmformula,
                             dat.prepan)
-pcl.retro.lm <- lm(formula = pcl.sum_score_base.pcl.sum_score_retro.glmformula,
+pcl.retro.lm <- lm(formula = pcl.sum_score_base.PCL.retrospective.glmformula,
                             dat.retro)
@@
 
-gad.retro.lm.glad <- lm(formula = gad.sum_score_base.gad.sum_score_retro.glmformula,
+gad.retro.lm.glad <- lm(formula = gad.sum_score_base.GAD.retrospective.glmformula,
                             dat.retro.glad)
-gad.retro.lm.nbr <- lm(formula = gad.sum_score_base.gad.sum_score_retro.glmformula,
+gad.retro.lm.nbr <- lm(formula = gad.sum_score_base.GAD.retrospective.glmformula,
                             dat.retro.nbr)
-gad.retro.lm.ramp <- lm(formula = gad.sum_score_base.gad.sum_score_retro.glmformula,
+gad.retro.lm.ramp <- lm(formula = gad.sum_score_base.GAD.retrospective.glmformula,
                             dat.retro.ramp)
 
-phq.retro.lm.glad <- lm(formula = phq.sum_score_base.phq.sum_score_retro.glmformula,
+phq.retro.lm.glad <- lm(formula = phq.sum_score_base.PHQ.retrospective.glmformula,
                             dat.retro.glad)
-phq.retro.lm.nbr <- lm(formula = phq.sum_score_base.phq.sum_score_retro.glmformula,
+phq.retro.lm.nbr <- lm(formula = phq.sum_score_base.PHQ.retrospective.glmformula,
                             dat.retro.nbr)
-phq.retro.lm.ramp <- lm(formula = phq.sum_score_base.phq.sum_score_retro.glmformula,
+phq.retro.lm.ramp <- lm(formula = phq.sum_score_base.PHQ.retrospective.glmformula,
                             dat.retro.ramp)
 
-pcl.retro.lm.glad <- lm(formula = pcl.sum_score_base.pcl.sum_score_retro.glmformula,
+pcl.retro.lm.glad <- lm(formula = pcl.sum_score_base.PCL.retrospective.glmformula,
                             dat.retro.glad)
-pcl.retro.lm.nbr <- lm(formula = pcl.sum_score_base.pcl.sum_score_retro.glmformula,
+pcl.retro.lm.nbr <- lm(formula = pcl.sum_score_base.PCL.retrospective.glmformula,
                             dat.retro.nbr)
-pcl.retro.lm.ramp <- lm(formula = pcl.sum_score_base.pcl.sum_score_retro.glmformula,
+pcl.retro.lm.ramp <- lm(formula = pcl.sum_score_base.PCL.retrospective.glmformula,
                             dat.retro.ramp)
@@
 # prepandemic and retrospective, grouped by disorder measure
-lmoutput_format(gad.prepan.lm,"gad.sum_score_prepan","GAD-7", "gad.prepan.lm.for.plot")
-lmoutput_format(gad.retro.lm,"gad.sum_score_retro","GAD-7", "gad.retro.lm.for.plot")
-
-lmoutput_format(phq.prepan.lm,"phq.sum_score_prepan","PHQ-9", "phq.prepan.lm.for.plot")
-lmoutput_format(phq.retro.lm,"phq.sum_score_retro","PHQ-9", "phq.retro.lm.for.plot")
-
-lmoutput_format(pcl.prepan.lm,"pcl.sum_score_prepan","PCL", "pcl.prepan.lm.for.plot")
-lmoutput_format(pcl.retro.lm,"pcl.sum_score_retro","PCL", "pcl.retro.lm.for.plot")
+lmoutput_format(gad.prepan.lm,"GAD.prepandemic","GAD-7", "gad.prepan.lm.for.plot")
+lmoutput_format(gad.retro.lm,"GAD.retrospective","GAD-7", "gad.retro.lm.for.plot")
+
+lmoutput_format(phq.prepan.lm,"PHQ.prepandemic","PHQ-9", "phq.prepan.lm.for.plot")
+lmoutput_format(phq.retro.lm,"PHQ.retrospective","PHQ-9", "phq.retro.lm.for.plot")
+
+lmoutput_format(pcl.prepan.lm,"PCL.prepandemic","PCL", "pcl.prepan.lm.for.plot")
+lmoutput_format(pcl.retro.lm,"PCL.retrospective","PCL", "pcl.retro.lm.for.plot")
 
 # prepandemic and retrospective, grouped by time point
-lmoutput_format(gad.prepan.lm,"gad.sum_score_prepan","Prepandemic", "gad.prepan.lm.for.plot.timegroup")
-lmoutput_format(gad.retro.lm,"gad.sum_score_retro","Retrospective", "gad.retro.lm.for.plot.timegroup")
-
-lmoutput_format(phq.prepan.lm,"phq.sum_score_prepan","Prepandemic", "phq.prepan.lm.for.plot.timegroup")
-lmoutput_format(phq.retro.lm,"phq.sum_score_retro","Retrospective", "phq.retro.lm.for.plot.timegroup")
-
-lmoutput_format(pcl.prepan.lm,"pcl.sum_score_prepan","Prepandemic", "pcl.prepan.lm.for.plot.timegroup")
-lmoutput_format(pcl.retro.lm,"pcl.sum_score_retro","Retrospective", "pcl.retro.lm.for.plot.timegroup")
+lmoutput_format(gad.prepan.lm,"GAD.prepandemic","Prepandemic", "gad.prepan.lm.for.plot.timegroup")
+lmoutput_format(gad.retro.lm,"GAD.retrospective","Retrospective", "gad.retro.lm.for.plot.timegroup")
+
+lmoutput_format(phq.prepan.lm,"PHQ.prepandemic","Prepandemic", "phq.prepan.lm.for.plot.timegroup")
+lmoutput_format(phq.retro.lm,"PHQ.retrospective","Retrospective", "phq.retro.lm.for.plot.timegroup")
+
+lmoutput_format(pcl.prepan.lm,"PCL.prepandemic","Prepandemic", "pcl.prepan.lm.for.plot.timegroup")
+lmoutput_format(pcl.retro.lm,"PCL.retrospective","Retrospective", "pcl.retro.lm.for.plot.timegroup")
 
 # Retrospective, grouped by sample
-lmoutput_format(gad.retro.lm.glad,"gad.sum_score_retro","GLAD and EDGI", "gad.retro.lm.for.plot.GLAD")
-lmoutput_format(gad.retro.lm.nbr,"gad.sum_score_retro","NBR", "gad.retro.lm.for.plot.NBR")
-lmoutput_format(gad.retro.lm.ramp,"gad.sum_score_retro","RAMP", "gad.retro.lm.for.plot.RAMP")
-
-lmoutput_format(phq.retro.lm.glad,"phq.sum_score_retro","GLAD and EDGI", "phq.retro.lm.for.plot.GLAD")
-lmoutput_format(phq.retro.lm.nbr,"phq.sum_score_retro","NBR", "phq.retro.lm.for.plot.NBR")
-lmoutput_format(phq.retro.lm.ramp,"phq.sum_score_retro","RAMP", "phq.retro.lm.for.plot.RAMP")
-
-lmoutput_format(pcl.retro.lm.glad,"pcl.sum_score_retro","GLAD and EDGI", "pcl.retro.lm.for.plot.GLAD")
-lmoutput_format(pcl.retro.lm.nbr,"pcl.sum_score_retro","NBR", "pcl.retro.lm.for.plot.NBR")
-lmoutput_format(pcl.retro.lm.ramp,"pcl.sum_score_retro","RAMP", "pcl.retro.lm.for.plot.RAMP")
+lmoutput_format(gad.retro.lm.glad,"GAD.retrospective","GLAD and EDGI", "gad.retro.lm.for.plot.GLAD")
+lmoutput_format(gad.retro.lm.nbr,"GAD.retrospective","NBR", "gad.retro.lm.for.plot.NBR")
+lmoutput_format(gad.retro.lm.ramp,"GAD.retrospective","RAMP", "gad.retro.lm.for.plot.RAMP")
+
+lmoutput_format(phq.retro.lm.glad,"PHQ.retrospective","GLAD and EDGI", "phq.retro.lm.for.plot.GLAD")
+lmoutput_format(phq.retro.lm.nbr,"PHQ.retrospective","NBR", "phq.retro.lm.for.plot.NBR")
+lmoutput_format(phq.retro.lm.ramp,"PHQ.retrospective","RAMP", "phq.retro.lm.for.plot.RAMP")
+
+lmoutput_format(pcl.retro.lm.glad,"PCL.retrospective","GLAD and EDGI", "pcl.retro.lm.for.plot.GLAD")
+lmoutput_format(pcl.retro.lm.nbr,"PCL.retrospective","NBR", "pcl.retro.lm.for.plot.NBR")
+lmoutput_format(pcl.retro.lm.ramp,"PCL.retrospective","RAMP", "pcl.retro.lm.for.plot.RAMP")
 
@@
 ### disorder
-```{r forest plot by disorder prepan, fig.height=20, fig.width=20, dpi=120}
+```{r forest plot by disorder prepan, fig.height=30, fig.width=35, dpi=120}
 
@@
 
-```{r forest plot by disorder retro, fig.height=20, fig.width=20, dpi=120}
+```{r forest plot by disorder retro, fig.height=30, fig.width=30, dpi=120}
 
@@
 ### disorder (no PCL)
-```{r forest plot by disorder prepan no pcl, fig.height=20, fig.width=20, dpi=120}
+```{r forest plot by disorder prepan no pcl, fig.height=30, fig.width=30, dpi=120}
 
@@
 
-```{r forest plot by disorder retro no pcl, fig.height=20, fig.width=20, dpi=120}
+```{r forest plot by disorder retro no pcl, fig.height=30, fig.width=30, dpi=120}
 
@@
 ### time point 
-```{r forest plot by time point gad, fig.height=20, fig.width=20, dpi=120}
+```{r forest plot by time point gad, fig.height=30, fig.width=30, dpi=120}
 
@@
 
-```{r forest plot by time point phq, fig.height=20, fig.width=20, dpi=120}
+```{r forest plot by time point phq, fig.height=30, fig.width=30, dpi=120}
 
@@
 
-```{r forest plot by time point pcl, fig.height=20, fig.width=20, dpi=120}
+```{r forest plot by time point pcl, fig.height=30, fig.width=30, dpi=120}
 
@@
 
-```{r forest plot by sample retro only gad, fig.height=20, fig.width=20, dpi=120}
+```{r forest plot by sample retro only gad, fig.height=30, fig.width=30, dpi=120}
 
@@
 
-```{r forest plot by sample retro only phq, fig.height=20, fig.width=20, dpi=120}
+```{r forest plot by sample retro only phq, fig.height=30, fig.width=30, dpi=120}
 
@@
 
-```{r forest plot by sample retro only pcl, fig.height=20, fig.width=20, dpi=120}
+```{r forest plot by sample retro only pcl, fig.height=30, fig.width=30, dpi=120}
 

### 2020-12-17 PANCHANGE_analysis.Rmd
added paired ttests for sum scores

@@
 ### disorder
-```{r forest plot by disorder prepan, fig.height=30, fig.width=35, dpi=120}
+```{r forest plot by disorder prepan, fig.height=30, fig.width=50, dpi=120}
 
@@
 
-```{r forest plot by disorder retro, fig.height=30, fig.width=30, dpi=120}
+```{r forest plot by disorder retro, fig.height=30, fig.width=50, dpi=120}
 
@@
 ### disorder (no PCL)
-```{r forest plot by disorder prepan no pcl, fig.height=30, fig.width=30, dpi=120}
+```{r forest plot by disorder prepan no pcl, fig.height=30, fig.width=50, dpi=120}
 
@@
 
-```{r forest plot by disorder retro no pcl, fig.height=30, fig.width=30, dpi=120}
+```{r forest plot by disorder retro no pcl, fig.height=30, fig.width=50, dpi=120}
 
@@
 ### time point 
-```{r forest plot by time point gad, fig.height=30, fig.width=30, dpi=120}
+```{r forest plot by time point gad, fig.height=30, fig.width=50, dpi=120}
 
@@
 
-```{r forest plot by time point phq, fig.height=30, fig.width=30, dpi=120}
+```{r forest plot by time point phq, fig.height=30, fig.width=50, dpi=120}
 
@@
 
-```{r forest plot by time point pcl, fig.height=30, fig.width=30, dpi=120}
+```{r forest plot by time point pcl, fig.height=30, fig.width=50, dpi=120}
 
@@
 
-```{r forest plot by sample retro only gad, fig.height=30, fig.width=30, dpi=120}
+```{r forest plot by sample retro only gad, fig.height=30, fig.width=50, dpi=120}
 
@@
 
-```{r forest plot by sample retro only phq, fig.height=30, fig.width=30, dpi=120}
+```{r forest plot by sample retro only phq, fig.height=30, fig.width=50, dpi=120}
 
@@
 
-```{r forest plot by sample retro only pcl, fig.height=30, fig.width=30, dpi=120}
+```{r forest plot by sample retro only pcl, fig.height=30, fig.width=50, dpi=120}
 

### 2020-12-17 figures/Paper_detail_checks.R

@@ -16,9 +16,7 @@ source("/Users/kirstin/Dropbox/SGDP/RAMP/Projects/PANCHANGE/PANCHANGE_raw_path.R
 
 # read in the 4 cohort data
 
-alldat <-  readRDS(file = paste0(data_path, "/four_cohorts.rds"))
-rampdat <-  readRDS(file = paste0(data_path, "/ramp.rds"))
-
+alldat <-  readRDS(file = paste0(data_path, "/four_cohorts_variables_exclusion.rds"))
 ## Subset samples
 
 GLAD <- alldat %>%
@@ -37,3 +35,11 @@ max(RAMP$startDate.coping)
 max(GLAD$startDate.coping)
 max(NBR$startDate.coping)
 
+## T-tests for average scores
+
+
+t.test(alldat$gad.sum_score_base,alldat$gad.sum_score_prepan, paired = T)
+t.test(alldat$phq.sum_score_base,alldat$phq.sum_score_prepan, paired = T)
+
+t.test(alldat$gad.sum_score_base,alldat$gad.sum_score_retro, paired = T)
+t.test(alldat$phq.sum_score_base,alldat$phq.sum_score_retro, paired = T)

### 2020-12-17 PANCHANGE_analysis.Rmd
reknitted for figure size

@@
                   "Ethnicity (Reference White)",
-                  "Employment (Reference: Employed)",
-                  "Employment (Reference: Employed)",
-                  "Employment (Reference: Employed)",
-                  "Employment (Reference: Employed)",
+                  "Employment (Reference employed)",
+                  "Employment (Reference employed)",
+                  "Employment (Reference employed)",
+                  "Employment (Reference employed)",
                   "Other")

### 2020-12-17 PANCHANGE_analysis.Rmd
fixed prefer not to say factorising

@@
 
+Note: make sure we impute retrospective data for those who did not change their feelings
+
+```{r impute retro for those who did not change}
+
+dat$gad.sum_score_retro <- ifelse(dat$gad.pandemic_felt_feelings == "No different", dat$gad.sum_score_base,dat$gad.sum_score_retro)
+dat$phq.sum_score_retro <- ifelse(dat$phq.pandemic_felt_feelings == "No different", dat$phq.sum_score_base,dat$phq.sum_score_retro)
+
+```
+
 ```{r subsample for retro-baseline analysis}
@@
                              "Personality disorders",
+                             "Did not report or did not know",
                              "Female",
@@
                   "Pre-existing mental health (Reference controls)",
+                  "Pre-existing mental health (Reference controls)",
                   "Gender (Reference male)",
@@
               group,
+              group,
               group)
@@
                              "mhd.personality_disorder",
+                             "DidNotRespondMHD",
                              "Gender_collapsed",
@@
                             dat.prepan)
+
 gad.retro.lm <- lm(formula = gad.sum_score_base.GAD.retrospective.glmformula,

### 2020-12-17 PANCHANGE_variable_creation.Rmd
fixed prefer not to say factorising

@@
   is.na(mhd.personality_disorder) &
-  is.na(control)) ~ 1))
+  is.na(control)) ~ "Prefer not to say", 
+ TRUE ~ "Responded to MHD"))
+
+dat <- dat %>%
+  mutate(DidNotRespondMHD = recode_factor(DidNotRespondMHD, 
+                "Prefer not to say" ="Prefer not to say",
+                "Responded to MHD" ="Responded to MHD"))
 

### 2020-12-18 PANCHANGE_analysis.Rmd
updated frequencies by sample

--- 2020-12-17 PANCHANGE_analysis.Rmd
@@
 Retro-baseline analyses
+
+Note: make sure we impute retrospective data for those who did not change their feelings
+
+```{r impute retro for those who did not change}
+
+dat$gad.sum_score_retro <- ifelse(dat$gad.pandemic_felt_feelings == "No different", dat$gad.sum_score_base,dat$gad.sum_score_retro)
+dat$phq.sum_score_retro <- ifelse(dat$phq.pandemic_felt_feelings == "No different", dat$phq.sum_score_base,dat$phq.sum_score_retro)
+
+```
 

### 2020-12-18 PANCHANGE_exclusion_descriptives.Rmd
fixed prefer not to say factorising
updated frequencies by sample

--- 2020-12-16 PANCHANGE_exclusion_descriptives.Rmd
@@
 # frequencies and descriptives in exclusion data
+
+### pandemic change gad
+
+```{r freq table gad perceived change}
+dat %>%
+  group_by(Sample) %>%
+  freq(gad.pandemic_felt_feelings)
+
+```
+### pandemic change phq
+
+```{r freq table phq perceived change}
+
+dat %>%
+  group_by(Sample) %>%
+  freq(phq.pandemic_felt_feelings)
+
+```
+
+### Ethnicity
+```{r freq table ethnicity}
+dat %>%
+  group_by(Sample) %>%
+  freq(Ethnicity_collapsed) 
+```
+### Gender
+```{r freq table gender}
+dat %>%
+  group_by(Sample) %>%
+  freq(Gender_collapsed) 
+```
+### age categorical
+```{r freq table age collapsed}
+dat %>%
+  group_by(Sample) %>%
+  freq(age_category_collapsed) 
+```
+### Employment
+
+```{r freq table employment collapsed}
+dat %>%
+  group_by(Sample) %>%
+  freq(employment_prior_covid) 
+```
+
+### anxiety disorders
+```{r freq table diagnosis anxiety}
+dat %>%
+  group_by(Sample) %>%
+  freq(anxiety_disorders) 
+```
+
+### Depressive disorders
+```{r freq table diagnosis depression}
+dat %>%
+  group_by(Sample) %>%
+  freq(depressive_disorders) 
+```
+### Depression and anxiety
+```{r freq table diagnosis depression and anxiety}
+dat %>%
+  group_by(Sample) %>%
+  freq(depression_and_anxiety) 
+```
+### Eating disorders
+```{r freq table diagnosis eating disorder}
+dat %>%
+  group_by(Sample) %>%
+  freq(eating_disorders)
+
+```
+### OCD
+```{r freq table diagnosis obsessive compulsive disorders}
+dat %>%
+  group_by(Sample) %>%
+  freq(obsessive_compulsive_disorders)
+
+```
+
+### Psychosis
+```{r freq table diagnosis psychotic disorders}
+dat %>%
+  group_by(Sample) %>%
+  freq(psychotic_disorders)
+
+```
+
+### Bipolar
+```{r freq table diagnosis bipolar}
+dat %>%
+  group_by(Sample) %>%
+  freq(mhd.mania_hypomania_bipolar_or_manicdepression)
+
+```
+
+### PTSD
+```{r freq table diagnosis PTSD}
+dat %>%
+  group_by(Sample) %>%
+  freq(mhd.posttraumatic_stress_disorder_ptsd)
+
+```
+
+### ASD
+
+```{r freq table diagnosis ASD}
+dat %>%
+  group_by(Sample) %>%
+  freq(autism_spectrum_disorder)
+
+```
+
+### ADHD
+```{r freq table diagnosis ADHD}
+dat %>%
+  group_by(Sample) %>%
+  freq(mhd.attention_deficit_hyperactivity_disorder)
+
+```
+
+### Personality disorders
+```{r freq table diagnosis personality disorder}
+dat %>%
+  group_by(Sample) %>%
+  freq(mhd.personality_disorder)
+
+```
+
+### Controls 
+```{r freq table diagnosis control}
+dat %>%
+  group_by(Sample) %>%
+  freq(control) 
+```
+
+### Dont know or prefer not to say
+```{r freq table diagnosis prefer not to say}
+dat %>%
+  group_by(Sample) %>%
+  freq(DidNotRespondMHD) 
+```
 

### 2020-12-18 figures/Paper_detail_checks.R
added t-test by group for retrospective

@@ -42,4 +42,21 @@ t.test(alldat$gad.sum_score_base,alldat$gad.sum_score_prepan, paired = T)
 t.test(alldat$phq.sum_score_base,alldat$phq.sum_score_prepan, paired = T)
 
 t.test(alldat$gad.sum_score_base,alldat$gad.sum_score_retro, paired = T)
-t.test(alldat$phq.sum_score_base,alldat$phq.sum_score_retro, paired = T)
+unlist(t.test(alldat$phq.sum_score_base,alldat$phq.sum_score_retro, paired = T)$estimate)
+
+
+## T-tests for average scores by group (retrospective)
+
+alldat %>%
+  mutate(sample = case_when(Sample == "GLAD" | Sample == "EDGI" ~ "GLAD",
+                            Sample == "RAMP" ~ "RAMP",
+                            Sample == "NBR" ~ "NBR")) %>%
+  select(gad.sum_score_base,gad.sum_score_retro, sample) %>%
+  gather(key = variable, value = value, -sample) %>% 
+  group_by(sample,variable) %>% 
+  summarise(value = list(value)) %>%
+  spread(variable,value) %>%
+  group_by(sample) %>% 
+  mutate(p_value = t.test(unlist(gad.sum_score_base), unlist(gad.sum_score_retro))$p.value,
+         t_value = t.test(unlist(gad.sum_score_base), unlist(gad.sum_score_retro))$statistic,
+         df = t.test(unlist(gad.sum_score_base), unlist(gad.sum_score_retro))$parameter)

### 2020-12-18 figures/Paper_detail_checks.R
added mean and standard deviations overall and by group

@@ -60,3 +60,45 @@ alldat %>%
   mutate(p_value = t.test(unlist(gad.sum_score_base), unlist(gad.sum_score_retro))$p.value,
          t_value = t.test(unlist(gad.sum_score_base), unlist(gad.sum_score_retro))$statistic,
          df = t.test(unlist(gad.sum_score_base), unlist(gad.sum_score_retro))$parameter)
+
+## Means and standard deviations
+## over all
+
+vars <- alldat %>%
+  select(gad.sum_score_base,gad.sum_score_retro,gad.sum_score_prepan,
+         phq.sum_score_base,phq.sum_score_retro,phq.sum_score_prepan,
+         pcl.sum_score_base)
+
+
+apply(vars, 2, function(x) list(mean=mean(!is.na(x)), sd=sd(!is.na(x))))
+
+## By sample
+alldat %>%
+  mutate(sample = case_when(Sample == "GLAD" | Sample == "EDGI" ~ "GLAD",
+                            Sample == "RAMP" ~ "RAMP",
+                            Sample == "NBR" ~ "NBR")) %>%
+  group_by(sample) %>%
+  summarize(m.gad.base = mean(gad.sum_score_base, na.rm = TRUE),
+            sd.gad.base = sd(gad.sum_score_base, na.rm = TRUE),
+            m.gad.prepan = mean(gad.sum_score_prepan, na.rm = TRUE),
+            sd.gad.prepan = sd(gad.sum_score_prepan, na.rm = TRUE),
+            m.gad.retro = mean(gad.sum_score_retro, na.rm = TRUE),
+            sd.gad.retro = sd(gad.sum_score_retro, na.rm = TRUE),
+            
+            m.phq.base = mean(phq.sum_score_base, na.rm = TRUE),
+            sd.phq.base = sd(phq.sum_score_base, na.rm = TRUE),
+            m.phq.prepan = mean(phq.sum_score_prepan, na.rm = TRUE),
+            sd.phq.prepan = sd(phq.sum_score_prepan, na.rm = TRUE),
+            m.phq.retro = mean(phq.sum_score_retro, na.rm = TRUE),
+            sd.phq.retro = sd(phq.sum_score_retro, na.rm = TRUE),
+            
+            m.pcl.base = mean(pcl.sum_score_base, na.rm = TRUE),
+            sd.pcl.base = sd(pcl.sum_score_base, na.rm = TRUE)
[…]

### 2020-12-18 PANCHANGE_analysis.Rmd
added PCl violin plot

@@
   facet_wrap("Disorder_hierarchical")
+```
+
+### Violin plots
+
+```{r pcl.sum violin plot sample}
+dat.long.pcl.sum %>%
+  filter(Time_point != "retro") %>%
+  mutate(sample = case_when(Sample == "GLAD" | Sample == "EDGI" ~ "GLAD and EDGI",
+                            Sample == "RAMP" ~ "RAMP",
+                            Sample == "NBR" ~ "NBR")) %>% 
+  mutate(Time_point_renamed = fct_recode(Time_point,
+                                         "Prepandemic" = "prepan",
+                                         "Baseline" = "base")
+  ) %>%
+  mutate(Time_point_reordered = fct_relevel(Time_point_renamed,
+                                            "Baseline",
+                                            "Prepandemic")
+  ) %>%
+  ggplot(mapping = aes(
+    x = Time_point_reordered,
+    y = pcl.sum_score,
+    fill = Time_point_reordered)) +
+  geom_hline(yintercept = 21, linetype = "dashed", color = "gray") +
+#  geom_hline(yintercept = 10, linetype = "dashed", color = "gray") +
+#  geom_hline(yintercept = 15, linetype = "dashed", color = "gray") +
+  geom_flat_violin(
+    position = position_nudge(x = .2, y = 0),
+    trim = FALSE,
+    alpha = 0.5
+  ) +
+  geom_point(
+    aes(
+      y = pcl.sum_score,
+      color = Time_point_reordered),
+    position = position_jitter(width = .15),
+    size = .5,
+    alpha = 0.8) +
+  #  geom_boxplot(
+  #    width = .1,
+  #    guides = FALSE,
+  #    outlier.shape = NA,
+  #    alpha = 0.5) +
+  stat_summary(fun.y = mean,
+               fun.ymin = function(x) mean(x) - sd(x),
+               fun.ymax = function(x) mean(x) + sd(x),
+               geom = "pointrange"
+  ) +
+  labs(
+    y = "PCL scores",
+    fill = "Time point") +
+  theme_personal +
+  theme(
+    axis.text.y = element_blank()
+  ) +
+  scale_fill_manual(
+    values = COPINGpalette3,
+    breaks = c("Prepandemic", "Baseline")
+  ) +
+  scale_alpha(guide = 'none') +
+  scale_size(guide = 'none') +
+  scale_color_manual(
+    values = COPINGpalette3,
+    breaks = c("Prepandemic", "Baseline"),
+    guide = "none") +
+    facet_wrap(facets = vars(sample),
+             nrow = 4
+  ) +
+  coord_flip()
 ```
@@
 ```{r add jitter "other" for NBR other ethnicity so this cat is available for plotting}
-
-dat.retro.nbr$Ethnicity_collapsed[801] <- "Other"  #this person was an NA
-dat.retro.nbr$Ethnicity_collapsed[998] <- "Other"  #this person was an NA
+dat.retro.nbr$Ethnicity_collapsed[586] <- "Other"  #this person was an NA
+dat.retro.nbr$Ethnicity_collapsed[856] <- "Other"  #this person was an NA
+dat.retro.nbr$Ethnicity_collapsed[871] <- "Other"  #this person was an NA
 

### 2020-12-18 figures/Paper_detail_checks.R

@@ -95,10 +95,3 @@ alldat %>%
             m.pcl.base = mean(pcl.sum_score_base, na.rm = TRUE),
             sd.pcl.base = sd(pcl.sum_score_base, na.rm = TRUE)
             )
-
-
-
-apply(varssamp, 2, function(x) list(mean=mean(!is.na(x)), sd=sd(!is.na(x))))
-
-DT[, sapply(.SD, function(x) list(mean=mean(x), sd=sd(x))), by=ID]
-

### 2020-12-18 figures/Paper_detail_checks.R
fixed mean and sd for whole sample. Added for PCL prepan

@@ -70,7 +70,7 @@ vars <- alldat %>%
          pcl.sum_score_base)
 
 
-apply(vars, 2, function(x) list(mean=mean(!is.na(x)), sd=sd(!is.na(x))))
+apply(vars, 2, function(x) list(describe(x)))
 
 ## By sample
 alldat %>%
@@ -93,5 +93,7 @@ alldat %>%
             sd.phq.retro = sd(phq.sum_score_retro, na.rm = TRUE),
             
             m.pcl.base = mean(pcl.sum_score_base, na.rm = TRUE),
-            sd.pcl.base = sd(pcl.sum_score_base, na.rm = TRUE)
+            sd.pcl.base = sd(pcl.sum_score_base, na.rm = TRUE),
+            m.pcl.prepan = mean(pcl.sum_score_prepan, na.rm = TRUE),
+            sd.pcl.prepan = sd(pcl.sum_score_prepan, na.rm = TRUE),
             )

### 2020-12-18 PANCHANGE_analysis.Rmd
updated violin plot colours for PCL

--- 2020-12-18 PANCHANGE_analysis.Rmd
@@
   facet_wrap("Disorder_hierarchical")
+```
+
+### Violin plots
+
+```{r pcl.sum violin plot sample}
+dat.long.pcl.sum %>%
+  filter(Time_point != "retro") %>%
+  mutate(sample = case_when(Sample == "GLAD" | Sample == "EDGI" ~ "GLAD and EDGI",
+                            Sample == "RAMP" ~ "RAMP",
+                            Sample == "NBR" ~ "NBR")) %>% 
+  mutate(Time_point_renamed = fct_recode(Time_point,
+                                         "Prepandemic" = "prepan",
+                                         "Baseline" = "base")
+  ) %>%
+  mutate(Time_point_reordered = fct_relevel(Time_point_renamed,
+                                            "Baseline",
+                                            "Prepandemic")
+  ) %>%
+  ggplot(mapping = aes(
+    x = Time_point_reordered,
+    y = pcl.sum_score,
+    fill = Time_point_reordered)) +
+  geom_hline(yintercept = 21, linetype = "dashed", color = "gray") +
+#  geom_hline(yintercept = 10, linetype = "dashed", color = "gray") +
+#  geom_hline(yintercept = 15, linetype = "dashed", color = "gray") +
+  geom_flat_violin(
+    position = position_nudge(x = .2, y = 0),
+    trim = FALSE,
+    alpha = 0.5
+  ) +
+  geom_point(
+    aes(
+      y = pcl.sum_score,
+      color = Time_point_reordered),
+    position = position_jitter(width = .15),
+    size = .5,
+    alpha = 0.8) +
+  #  geom_boxplot(
+  #    width = .1,
+  #    guides = FALSE,
+  #    outlier.shape = NA,
+  #    alpha = 0.5) +
+  stat_summary(fun.y = mean,
+               fun.ymin = function(x) mean(x) - sd(x),
+               fun.ymax = function(x) mean(x) + sd(x),
+               geom = "pointrange"
+  ) +
+  labs(
+    y = "PCL scores",
+    fill = "Time point") +
+  theme_personal +
+  theme(
+    axis.text.y = element_blank()
+  ) +
+  scale_fill_manual(
+    values = c("#78D9C5","#EEB6E9"),
+    breaks = c("Prepandemic", "Baseline")
+  ) +
+  scale_alpha(guide = 'none') +
+  scale_size(guide = 'none') +
+  scale_color_manual(
+    values = c("#78D9C5","#EEB6E9"),
+    breaks = c("Prepandemic", "Baseline"),
+    guide = "none") +
+    facet_wrap(facets = vars(sample),
+             nrow = 4
+  ) +
+  coord_flip()
 ```

### 2020-12-18 figures/Paper_detail_checks.R

@@ -97,3 +97,10 @@ alldat %>%
             m.pcl.prepan = mean(pcl.sum_score_prepan, na.rm = TRUE),
             sd.pcl.prepan = sd(pcl.sum_score_prepan, na.rm = TRUE),
             )
+
+## Explore odd bumpy NBR data (retrospective PHQ 9, baseline GAD-7, )
+
+alldat %>% 
+  group_by(Sample) %>% 
+  do(h = hist(.$phq.sum_score_retro))
+

### 2020-12-18 PANCHANGE_analysis.Rmd
fixed age reference cat in employment regression

@@
 ```{r add jitter "other" for NBR other ethnicity so this cat is available for plotting}
+
 dat.retro.nbr$Ethnicity_collapsed[586] <- "Other"  #this person was an NA
 dat.retro.nbr$Ethnicity_collapsed[856] <- "Other"  #this person was an NA
-dat.retro.nbr$Ethnicity_collapsed[871] <- "Other"  #this person was an NA
+dat.retro.nbr$Ethnicity_collapsed[989] <- "Other"  #this person was an NA
 
@@
 
-pcl.retro.lm.glad <- lm(formula = pcl.sum_score_base.PCL.retrospective.glmformula,
-                            dat.retro.glad)
-pcl.retro.lm.nbr <- lm(formula = pcl.sum_score_base.PCL.retrospective.glmformula,
-                            dat.retro.nbr)
-pcl.retro.lm.ramp <- lm(formula = pcl.sum_score_base.PCL.retrospective.glmformula,
-                            dat.retro.ramp)
-
 ```
@@
 lmoutput_format(phq.retro.lm.ramp,"PHQ.retrospective","RAMP", "phq.retro.lm.for.plot.RAMP")
-
-lmoutput_format(pcl.retro.lm.glad,"PCL.retrospective","GLAD and EDGI", "pcl.retro.lm.for.plot.GLAD")
-lmoutput_format(pcl.retro.lm.nbr,"PCL.retrospective","NBR", "pcl.retro.lm.for.plot.NBR")
-lmoutput_format(pcl.retro.lm.ramp,"PCL.retrospective","RAMP", "pcl.retro.lm.for.plot.RAMP")
 
@@
 
-plot.dat.sample.pcl <- rbind(pcl.retro.lm.for.plot.GLAD,
-                             pcl.retro.lm.for.plot.NBR,
-                             pcl.retro.lm.for.plot.RAMP)
-
 ```
@@
 ```
-
-```{r forest plot by sample retro only pcl, fig.height=30, fig.width=50, dpi=120}
-
-lm.forest(plot.dat.sample.pcl ,"Predictors of PTSD controlling for retrospective symptoms across samples")
-
-```

### 2020-12-18 figures/Paper_detail_checks.R

@@ -97,10 +97,3 @@ alldat %>%
             m.pcl.prepan = mean(pcl.sum_score_prepan, na.rm = TRUE),
             sd.pcl.prepan = sd(pcl.sum_score_prepan, na.rm = TRUE),
             )
-
-## Explore odd bumpy NBR data (retrospective PHQ 9, baseline GAD-7, )
-
-alldat %>% 
-  group_by(Sample) %>% 
-  do(h = hist(.$phq.sum_score_retro))
-

### 2021-01-07 PANCHANGE_analysis.Rmd
any forgotten changes

@@
       (data_group_pcl == "Baseline and retrospective data" |
-      data_group_pcl == "All prepandemic, baseline and retrospective data") |
-      (data_group_ocir == "Baseline and retrospective data" |
-      data_group_ocir == "All prepandemic, baseline and retrospective data"))
+      data_group_pcl == "All prepandemic, baseline and retrospective data"))
   )
@@
   filter(
-    ((data_group_gad == "Baseline and retrospective data" |
-      data_group_gad == "Prepandemic and baseline data" |
+    ((data_group_gad == "Prepandemic and baseline data" |
       data_group_gad == "All prepandemic, baseline and retrospective data") |
-      (data_group_phq == "Baseline and retrospective data" |
-      data_group_phq == "Prepandemic and baseline data" |
+      (data_group_phq == "Prepandemic and baseline data" |
       data_group_phq == "All prepandemic, baseline and retrospective data") |
-      (data_group_pcl == "Baseline and retrospective data" |
-      data_group_pcl == "Prepandemic and baseline data" |
-      data_group_pcl == "All prepandemic, baseline and retrospective data") |
-      (data_group_ocir == "Baseline and retrospective data" |
-      data_group_ocir == "Prepandemic and baseline data" |
-      data_group_ocir == "All prepandemic, baseline and retrospective data")) &
+      (data_group_pcl == "Prepandemic and baseline data" |
+      data_group_pcl == "All prepandemic, baseline and retrospective data") ) &
       prepandemic_march_1_numeric == 1 # Exclude participants that signed up after the 1. March
@@
 ```
+
+# frequencies and descriptives in exclusion data
+
+after excluding for age, gender, or MHD being NA (as in skipped or missed. Prefer not to answer was categories as it's own option), and if they did not complete all measurement points.
+
+### sample size counts by cohort for each measurement point
+
+```{r freq table overall by sample}
+
+dat %>% 
+  group_by(Sample) %>%
+  (count)
+
+```
+
+```{r freq table prepandemic by sample}
+
+dat.prepan %>% 
+  group_by(Sample) %>%
+  (count)
+
+```
+
+```{r freq table retrospective by sample}
+
+dat.retro %>% 
+  group_by(Sample) %>%
+  (count)
+
+```
+
+### pandemic change gad
+
+```{r freq table gad perceived change}
+dat %>%
+  group_by(Sample) %>%
+  freq(gad.pandemic_felt_feelings)
+
+```
+### pandemic change phq
+
+```{r freq table phq perceived change}
+
+dat %>%
+  group_by(Sample) %>%
+  freq(phq.pandemic_felt_feelings)
+
+```
+
+### Ethnicity
+```{r freq table ethnicity}
+dat %>%
+  group_by(Sample) %>%
+  freq(Ethnicity_collapsed) 
+```
+
+### Gender
+```{r freq table gender}
+dat %>%
+  group_by(Sample) %>%
+  freq(Gender_collapsed) 
+```
+### age categorical
+```{r freq table age collapsed}
+dat %>%
+  group_by(Sample) %>%
+  freq(age_category_collapsed) 
+```
+### Employment
+
+```{r freq table employment collapsed}
+dat %>%
+  group_by(Sample) %>%
+  freq(employment_prior_covid) 
+```
+
+### anxiety disorders
+```{r freq table diagnosis anxiety}
+dat %>%
+  group_by(Sample) %>%
+  freq(anxiety_disorders) 
+```
+
+### Depressive disorders
+```{r freq table diagnosis depression}
+dat %>%
+  group_by(Sample) %>%
+  freq(depressive_disorders) 
+```
+### Depression and anxiety
+```{r freq table diagnosis depression and anxiety}
+dat %>%
+  group_by(Sample) %>%
+  freq(depression_and_anxiety) 
+```
+### Eating disorders
+```{r freq table diagnosis eating disorder}
+dat %>%
+  group_by(Sample) %>%
+  freq(eating_disorders)
+
+```
+### OCD
+```{r freq table diagnosis obsessive compulsive disorders}
+dat %>%
+  group_by(Sample) %>%
+  freq(obsessive_compulsive_disorders)
+
+```
+
+### Psychosis
+```{r freq table diagnosis psychotic disorders}
+dat %>%
+  group_by(Sample) %>%
+  freq(psychotic_disorders)
+
+```
+
+### Bipolar
+```{r freq table diagnosis bipolar}
+dat %>%
+  group_by(Sample) %>%
+  freq(mhd.mania_hypomania_bipolar_or_manicdepression)
+
+```
+
+### PTSD
+```{r freq table diagnosis PTSD}
+dat %>%
+  group_by(Sample) %>%
+  freq(mhd.posttraumatic_stress_disorder_ptsd)
+
+```
+
+### ASD
+
+```{r freq table diagnosis ASD}
+dat %>%
+  group_by(Sample) %>%
+  freq(autism_spectrum_disorder)
+
+```
+
+### ADHD
+```{r freq table diagnosis ADHD}
+dat %>%
+  group_by(Sample) %>%
+  freq(mhd.attention_deficit_hyperactivity_disorder)
+
+```
+
+### Personality disorders
+```{r freq table diagnosis personality disorder}
+dat %>%
+  group_by(Sample) %>%
+  freq(mhd.personality_disorder)
+
+```
+
+### Controls 
+```{r freq table diagnosis control}
+dat %>%
+  group_by(Sample) %>%
+  freq(control) 
+```
+
+### Dont know or prefer not to say
+```{r freq table diagnosis prefer not to say}
+dat %>%
+  group_by(Sample) %>%
+  freq(DidNotRespondMHD) 
+```
+
+## T tests
+
+retrospective OPHQ 9 vs baseline.
+
+Notes: We use the default (Welch's) t-test (to account for non equal variance)
+```{r t tests }
+
+datgladedgi <- dat.retro %>%
+  filter(Sample == "GLAD" |
+           Sample == "EDGI")
+
+t.test(datgladedgi$phq.sum_score_base,
+       datgladedgi$phq.sum_score_retro,
+       paired=T)
+
+t.test(datgladedgi$gad.sum_score_base,
+       datgladedgi$gad.sum_score_retro,
+       paired=T)
+
+```

### 2021-01-07 figures/Paper_detail_checks.R
ensured comaprable sample filtering for detail checks

@@ -17,32 +17,87 @@ source("/Users/kirstin/Dropbox/SGDP/RAMP/Projects/PANCHANGE/PANCHANGE_raw_path.R
 # read in the 4 cohort data
 
 alldat <-  readRDS(file = paste0(data_path, "/four_cohorts_variables_exclusion.rds"))
-## Subset samples
 
-GLAD <- alldat %>%
+# impute retro for those who did not change
+
+alldat$gad.sum_score_retro <- ifelse(alldat$gad.pandemic_felt_feelings == "No different", alldat$gad.sum_score_base,alldat$gad.sum_score_retro)
+alldat$phq.sum_score_retro <- ifelse(alldat$phq.pandemic_felt_feelings == "No different", alldat$phq.sum_score_base,alldat$phq.sum_score_retro)
+
+## subsample for retro-baseline analysis
+### exclude those who do not have complete responses for both baseline and retrospective
+### in addition to those already excluded for NA in age, gender and MH diagnosis.
+
+
+dat.retro <- alldat %>%
+  filter(
+    ((data_group_gad == "Baseline and retrospective data" |
+        data_group_gad == "All prepandemic, baseline and retrospective data") |
+       (data_group_phq == "Baseline and retrospective data" |
+          data_group_phq == "All prepandemic, baseline and retrospective data") |
+       (data_group_pcl == "Baseline and retrospective data" |
+          data_group_pcl == "All prepandemic, baseline and retrospective data"))
+  )
+
+
+## subsample for prepan-baseline analysis
+
+### exclude those who do not have complete responses for both baseline and prepandemic
+### in addition to those already excluded for NA in age, gender and MH diagnosis.
+
+dat.prepan <- alldat %>%
+  filter(
+    ((data_group_gad == "Prepandemic and baseline data" |
+        data_group_gad == "All prepandemic, baseline and retrospective data") |
+       (data_group_phq == "Prepandemic and baseline data" |
+          data_group_phq == "All prepandemic, baseline and retrospective data") |
+       (data_group_pcl == "Prepandemic and baseline data" |
+          data_group_pcl == "All prepandemic, baseline and retrospective data") ) &
[…]

### 2021-01-07 figures/Paper_detail_checks.R
updated t test functions

@@ -7,6 +7,7 @@
 library(tidyverse)
 library(data.table)
 library(lubridate)
+library(psych)
 
 # get file info
 source("/Users/kirstin/Dropbox/SGDP/RAMP/Projects/PANCHANGE/PANCHANGE_raw_path.R")
@@ -99,10 +100,11 @@ t.test(dat.retro$gad.sum_score_base,dat.retro$gad.sum_score_retro, paired = T)
 t.test(dat.retro$phq.sum_score_base,dat.retro$phq.sum_score_retro, paired = T)
 
 
+# RETROSPECTIVE (by group)
 
-## T-tests for average scores by group (retrospective)
+## T-tests for average scores by group (retrospective GAD)
 
-alldat %>%
+dat.retro %>%
   mutate(sample = case_when(Sample == "GLAD" | Sample == "EDGI" ~ "GLAD",
                             Sample == "RAMP" ~ "RAMP",
                             Sample == "NBR" ~ "NBR")) %>%
@@ -116,6 +118,75 @@ alldat %>%
          t_value = t.test(unlist(gad.sum_score_base), unlist(gad.sum_score_retro))$statistic,
          df = t.test(unlist(gad.sum_score_base), unlist(gad.sum_score_retro))$parameter)
 
+
+## T-tests for average scores by group (retrospective PHQ)
+
+dat.retro %>%
+  mutate(sample = case_when(Sample == "GLAD" | Sample == "EDGI" ~ "GLAD",
+                            Sample == "RAMP" ~ "RAMP",
+                            Sample == "NBR" ~ "NBR")) %>%
+  select(phq.sum_score_base,phq.sum_score_retro, sample) %>%
+  gather(key = variable, value = value, -sample) %>% 
+  group_by(sample,variable) %>% 
+  summarise(value = list(value)) %>%
+  spread(variable,value) %>%
+  group_by(sample) %>% 
+  mutate(p_value = t.test(unlist(phq.sum_score_base), unlist(phq.sum_score_retro))$p.value,
+         t_value = t.test(unlist(phq.sum_score_base), unlist(phq.sum_score_retro))$statistic,
+         df = t.test(unlist(phq.sum_score_base), unlist(phq.sum_score_retro))$parameter)
+
+# PREPANDEMIC (By group)
+## T-tests for average scores by group (prepandemic GAD)
+
+dat.prepan %>%
[…]

### 2021-01-07 Final_analyses_checks_notebook.Rmd
created notebook for final paper checks

---
title: "Final paper detail checks and analyses"

author: "Kirstin L Purves"
date: '`r format(Sys.time(), "%d %B, %Y")`'
output:
  html_document:
    df_print: paged
    toc: yes
    toc_depth: 2
    toc_float:
      collapsed: false
    number_sections: false
    highlight: monochrome
    theme: cerulean
code_folding: show

html_notebook:
  theme: cerulean
toc: yes
---

The final analyses, comparisons and checks for ***Predicting anxiety, depression and trauma symptoms during the COVID-19 pandemic in the UK***

Note that when GLAD, we always mean GLAD & EDGI

# Set up

```{r read in data } 
# Read in data
library(tidyverse)
library(data.table)
library(lubridate)
library(psych)

# get file info
source("/Users/kirstin/Dropbox/SGDP/RAMP/Projects/PANCHANGE/PANCHANGE_raw_path.R")

alldat <-  readRDS(file = paste0(data_path, "/four_cohorts_variables_exclusion.rds"))

```

# Impute and subset data

Impute retrospective scores if no change reported

```{r impute retro}

# impute retro for those who did not change

alldat$gad.sum_score_retro <- ifelse(alldat$gad.pandemic_felt_feelings == "No different", alldat$gad.sum_score_base,alldat$gad.sum_score_retro)
alldat$phq.sum_score_retro <- ifelse(alldat$phq.pandemic_felt_feelings == "No different", alldat$phq.sum_score_base,alldat$phq.sum_score_retro)
```

subsample for retro-baseline analysis
exclude those who do not have complete responses for both baseline and retrospective
in addition to those already excluded for NA in age, gender and MH diagnosis.

RETROSPECTIVE
```{r subset retrospective data }
dat.retro <- alldat %>%
  filter(
    ((data_group_gad == "Baseline and retrospective data" |
        data_group_gad == "All prepandemic, baseline and retrospective data") |
       (data_group_phq == "Baseline and retrospective data" |
          data_group_phq == "All prepandemic, baseline and retrospective data") |
       (data_group_pcl == "Baseline and retrospective data" |
          data_group_pcl == "All prepandemic, baseline and retrospective data"))
  )

dim(dat.retro)
```

subsample for prepan-baseline analysis
exclude those who do not have complete responses for both baseline and prepandemic
in addition to those already excluded for NA in age, gender and MH diagnosis.

PREPANDEMIC
```{r subset prepandemic}

dat.prepan <- alldat %>%
  filter(
    ((data_group_gad == "Prepandemic and baseline data" |
        data_group_gad == "All prepandemic, baseline and retrospective data") |
       (data_group_phq == "Prepandemic and baseline data" |
          data_group_phq == "All prepandemic, baseline and retrospective data") |
       (data_group_pcl == "Prepandemic and baseline data" |
          data_group_pcl == "All prepandemic, baseline and retrospective data") ) &
      prepandemic_march_1_numeric == 1 # Exclude participants that signed up after the 1. March
  )

dim(dat.prepan)

```

Subset by study

```{r subset by study}

## Subset samples by study

GLAD.prepan <- dat.prepan %>%
  filter(Sample == "GLAD" | 
           Sample == "EDGI")

NBR.prepan <- dat.prepan %>%
  filter(Sample == "NBR")

RAMP.prepan <- dat.prepan %>%
  filter(Sample == "RAMP")

### retro
GLAD.retro <- dat.retro %>%
  filter(Sample == "GLAD" | 
           Sample == "EDGI")

NBR.retro <- dat.retro %>%
  filter(Sample == "NBR")

RAMP.retro <- dat.retro %>%
  filter(Sample == "RAMP")

```

# Analytic checks and last pass

## Most recent sign up per sample

```{r most recent sign up}

max(RAMP.prepan$startDate.coping)
max(GLAD.prepan$startDate.coping)
max(NBR.prepan$startDate.coping)

```

## Means, SD and n

### overall

Retrospective
```{r means etc overall retro}

vars <- dat.retro %>%
  select(gad.sum_score_base,gad.sum_score_retro,
         phq.sum_score_base,phq.sum_score_retro,
         pcl.sum_score_base)

apply(vars, 2, function(x) list(describe(x)))

```

Prepandemic
```{r means etc overall prepan}

vars <- dat.prepan %>%
  select(gad.sum_score_base,gad.sum_score_prepan,
         phq.sum_score_base,phq.sum_score_prepan,
         pcl.sum_score_base,  pcl.sum_score_prepan)

apply(vars, 2, function(x) list(describe(x)))

```

### By sample

retrospective
```{r means etc by sample retro}
dat.retro %>%
  mutate(sample = case_when(Sample == "GLAD" | Sample == "EDGI" ~ "GLAD",
                            Sample == "RAMP" ~ "RAMP",
                            Sample == "NBR" ~ "NBR")) %>%
  group_by(sample) %>%
  summarize(m.gad.base = mean(gad.sum_score_base, na.rm = TRUE),
            sd.gad.base = sd(gad.sum_score_base, na.rm = TRUE),
            n.gad.base = sum(!is.na(gad.sum_score_base)),
            m.gad.retro = mean(gad.sum_score_retro, na.rm = TRUE),
            sd.gad.retro = sd(gad.sum_score_retro, na.rm = TRUE),
            n.gad.retro = sum(!is.na(gad.sum_score_retro)),

            m.phq.base = mean(phq.sum_score_base, na.rm = TRUE),
            sd.phq.base = sd(phq.sum_score_base, na.rm = TRUE),
            n.phq.base = sum(!is.na(phq.sum_score_base)),
            m.phq.retro = mean(phq.sum_score_retro, na.rm = TRUE),
            sd.phq.retro = sd(phq.sum_score_retro, na.rm = TRUE),
            n.phq.retro = sum(!is.na(phq.sum_score_retro)),

            m.pcl.base = mean(pcl.sum_score_base, na.rm = TRUE),
            sd.pcl.base = sd(pcl.sum_score_base, na.rm = TRUE),
            n.pcl.base = sum(!is.na(pcl.sum_score_base)),

            )
```

prepandemic
```{r means etc by sample prepan}
dat.prepan %>%
  mutate(sample = case_when(Sample == "GLAD" | Sample == "EDGI" ~ "GLAD",
                            Sample == "RAMP" ~ "RAMP",
                            Sample == "NBR" ~ "NBR")) %>%
  group_by(sample) %>%
  summarize(m.gad.base = mean(gad.sum_score_base, na.rm = TRUE),
            sd.gad.base = sd(gad.sum_score_base, na.rm = TRUE),
            n.gad.base = sum(!is.na(gad.sum_score_base)),
            m.gad.prepan = mean(gad.sum_score_prepan, na.rm = TRUE),
            sd.gad.prepan = sd(gad.sum_score_prepan, na.rm = TRUE),
            n.gad.prepan = sum(!is.na(gad.sum_score_prepan)),

            m.phq.base = mean(phq.sum_score_base, na.rm = TRUE),
            sd.phq.base = sd(phq.sum_score_base, na.rm = TRUE),
            n.phq.base = sum(!is.na(phq.sum_score_base)),
            m.phq.prepan = mean(phq.sum_score_prepan, na.rm = TRUE),
            sd.phq.prepan = sd(phq.sum_score_prepan, na.rm = TRUE),
            n.phq.prepan = sum(!is.na(phq.sum_score_prepan)),

            m.pcl.base = mean(pcl.sum_score_base, na.rm = TRUE),
            sd.pcl.base = sd(pcl.sum_score_base, na.rm = TRUE),
            n.pcl.base = sum(!is.na(pcl.sum_score_base)),
            m.pcl.prepan = mean(pcl.sum_score_prepan, na.rm = TRUE),
            sd.pcl.prepan = sd(pcl.sum_score_prepan, na.rm = TRUE),
            n.pcl.prepan = sum(!is.na(pcl.sum_score_prepan)),

  )
```

## T tests

All are Welch's (assuming non equal variances) paired t-tests

### Average scores
Prepandemic
```{r ttest for average scores prepandemic}

t.test(dat.prepan$gad.sum_score_base,dat.prepan$gad.sum_score_prepan, paired = T)
t.test(dat.prepan$phq.sum_score_base,dat.prepan$phq.sum_score_prepan, paired = T)
t.test(dat.prepan$pcl.sum_score_base,dat.prepan$pcl.sum_score_prepan, paired = T)

```

Retrospective
(no retrospective ratings for PCL)
```{r ttest for average scores retrosective}
t.test(dat.retro$gad.sum_score_base,dat.retro$gad.sum_score_retro, paired = T)
t.test(dat.retro$phq.sum_score_base,dat.retro$phq.sum_score_retro, paired = T)
```

### Average scores by sample

Retrospective GAD
```{r ttest average by sample retro gad}

dat.retro %>%
  mutate(sample = case_when(Sample == "GLAD" | Sample == "EDGI" ~ "GLAD",
                            Sample == "RAMP" ~ "RAMP",
                            Sample == "NBR" ~ "NBR")) %>%
  select(gad.sum_score_base,gad.sum_score_retro, sample) %>%
  gather(key = variable, value = value, -sample) %>% 
  group_by(sample,variable) %>% 
  summarise(value = list(value)) %>%
  spread(variable,value) %>%
  group_by(sample) %>% 
  mutate(p_value = t.test(unlist(gad.sum_score_base), unlist(gad.sum_score_retro))$p.value,
         t_value = t.test(unlist(gad.sum_score_base), unlist(gad.sum_score_retro))$statistic,
         df = t.test(unlist(gad.sum_score_base), unlist(gad.sum_score_retro))$parameter)

```

Retrospective PHQ
```{r ttest average by sample retro phq}
dat.retro %>%
  mutate(sample = case_when(Sample == "GLAD" | Sample == "EDGI" ~ "GLAD",
                            Sample == "RAMP" ~ "RAMP",
                            Sample == "NBR" ~ "NBR")) %>%
  select(phq.sum_score_base,phq.sum_score_retro, sample) %>%
  gather(key = variable, value = value, -sample) %>% 
  group_by(sample,variable) %>% 
  summarise(value = list(value)) %>%
  spread(variable,value) %>%
  group_by(sample) %>% 
  mutate(p_value = t.test(unlist(phq.sum_score_base), unlist(phq.sum_score_retro))$p.value,
         t_value = t.test(unlist(phq.sum_score_base), unlist(phq.sum_score_retro))$statistic,
         df = t.test(unlist(phq.sum_score_base), unlist(phq.sum_score_retro))$parameter)

```

Prepandemic GAD
```{r ttest average by sample prepan gad}
dat.prepan %>%
  mutate(sample = case_when(Sample == "GLAD" | Sample == "EDGI" ~ "GLAD",
                            Sample == "RAMP" ~ "RAMP",
                            Sample == "NBR" ~ "NBR")) %>%
  select(gad.sum_score_base,gad.sum_score_prepan, sample) %>%
  gather(key = variable, value = value, -sample) %>% 
  group_by(sample,variable) %>% 
  summarise(value = list(value)) %>%
  spread(variable,value) %>%
  group_by(sample) %>% 
  mutate(p_value = t.test(unlist(gad.sum_score_base), unlist(gad.sum_score_prepan))$p.value,
         t_value = t.test(unlist(gad.sum_score_base), unlist(gad.sum_score_prepan))$statistic,
         df = t.test(unlist(gad.sum_score_base), unlist(gad.sum_score_prepan))$parameter)

```

Prepandemic PHQ
```{r ttest average by sample prepan phq}
dat.prepan %>%
  mutate(sample = case_when(Sample == "GLAD" | Sample == "EDGI" ~ "GLAD",
                            Sample == "RAMP" ~ "RAMP",
                            Sample == "NBR" ~ "NBR")) %>%
  select(phq.sum_score_base,phq.sum_score_prepan, sample) %>%
  gather(key = variable, value = value, -sample) %>% 
  group_by(sample,variable) %>% 
  summarise(value = list(value)) %>%
  spread(variable,value) %>%
  group_by(sample) %>% 
  mutate(p_value = t.test(unlist(phq.sum_score_base), unlist(phq.sum_score_prepan))$p.value,
         t_value = t.test(unlist(phq.sum_score_base), unlist(phq.sum_score_prepan))$statistic,
         df = t.test(unlist(phq.sum_score_base), unlist(phq.sum_score_prepan))$parameter)
```

Prepandemic PCL
```{r ttest average by sample prepan pcl}

dat.prepan %>%
  mutate(sample = case_when(Sample == "GLAD" | Sample == "EDGI" ~ "GLAD",
                            Sample == "RAMP" ~ "RAMP",
                            Sample == "NBR" ~ "NBR")) %>%
  select(pcl.sum_score_base,pcl.sum_score_prepan, sample) %>%
  gather(key = variable, value = value, -sample) %>% 
  group_by(sample,variable) %>% 
  summarise(value = list(value)) %>%
  spread(variable,value) %>%
  group_by(sample) %>% 
  mutate(p_value = t.test(unlist(pcl.sum_score_base), unlist(pcl.sum_score_prepan))$p.value,
         t_value = t.test(unlist(pcl.sum_score_base), unlist(pcl.sum_score_prepan))$statistic,
         df = t.test(unlist(pcl.sum_score_base), unlist(pcl.sum_score_prepan))$parameter)

```

### 2021-01-07 Final_analyses_checks_notebook.Rmd
added frequency tables

@@
 # Read in data
+library(knitr)
+library(summarytools)
+library(psych)
+library(polycor)
+library(corrplot)
+library(patchwork)
+library(broom)
 library(tidyverse)
-library(data.table)
-library(lubridate)
-library(psych)
+library(ggpubr)
 
@@
 ```{r most recent sign up}
-
-max(RAMP.prepan$startDate.coping)
-max(GLAD.prepan$startDate.coping)
-max(NBR.prepan$startDate.coping)
+print("RAMP")
+max(RAMP.retro$startDate.coping)
+print("GLAD")
+max(GLAD.retro$startDate.coping)
+print("NBR")
+max(NBR.retro$startDate.coping)
 
@@
 
+## Sample sizes
+
+## frequencies (retrodemic dataset)
+
+### pandemic change gad
+
+```{r retro freq table gad perceived change}
+dat.retro %>%
+  group_by(Sample) %>%
+  freq(gad.pandemic_felt_feelings)
+
+```
+### pandemic change phq
+
+```{r retro freq table phq perceived change}
+
+dat.retro %>%
+  group_by(Sample) %>%
+  freq(phq.pandemic_felt_feelings)
+
+```
+
+### Ethnicity
+```{r retro freq table ethnicity}
+dat.retro %>%
+  group_by(Sample) %>%
+  freq(Ethnicity_collapsed) 
+```
+### Gender
+```{r retro freq table gender}
+dat.retro %>%
+  group_by(Sample) %>%
+  freq(Gender_collapsed) 
+```
+### age categorical
+```{r retro freq table age collapsed}
+dat.retro %>%
+  group_by(Sample) %>%
+  freq(age_category_collapsed) 
+```
+### Employment
+
+```{r retro freq table employment collapsed}
+dat.retro %>%
+  group_by(Sample) %>%
+  freq(employment_prior_covid) 
+```
+
+### anxiety disorders
+```{r retro freq table diagnosis anxiety}
+dat.retro %>%
+  group_by(Sample) %>%
+  freq(anxiety_disorders) 
+```
+
+### Depressive disorders
+```{r retro freq table diagnosis depression}
+dat.retro %>%
+  group_by(Sample) %>%
+  freq(depressive_disorders) 
+```
+### Depression and anxiety
+```{r retro freq table diagnosis depression and anxiety}
+dat.retro %>%
+  group_by(Sample) %>%
+  freq(depression_and_anxiety) 
+```
+### Eating disorders
+```{r retro freq table diagnosis eating disorder}
+dat.retro %>%
+  group_by(Sample) %>%
+  freq(eating_disorders)
+
+```
+### OCD
+```{r retro freq table diagnosis obsessive compulsive disorders}
+dat.retro %>%
+  group_by(Sample) %>%
+  freq(obsessive_compulsive_disorders)
+
+```
+
+### Psychosis
+```{r retro freq table diagnosis psychotic disorders}
+dat.retro %>%
+  group_by(Sample) %>%
+  freq(psychotic_disorders)
+
+```
+
+### Bipolar
+```{r retro freq table diagnosis bipolar}
+dat.retro %>%
+  group_by(Sample) %>%
+  freq(mhd.mania_hypomania_bipolar_or_manicdepression)
+
+```
+
+### PTSD
+```{r retro freq table diagnosis PTSD}
+dat.retro %>%
+  group_by(Sample) %>%
+  freq(mhd.posttraumatic_stress_disorder_ptsd)
+
+```
+
+### ASD
+
+```{r retro freq table diagnosis ASD}
+dat.retro %>%
+  group_by(Sample) %>%
+  freq(autism_spectrum_disorder)
+
+```
+
+### ADHD
+```{r retro freq table diagnosis ADHD}
+dat.retro %>%
+  group_by(Sample) %>%
+  freq(mhd.attention_deficit_hyperactivity_disorder)
+
+```
+
+### Personality disorders
+```{r retro freq table diagnosis personality disorder}
+dat.retro %>%
+  group_by(Sample) %>%
+  freq(mhd.personality_disorder)
+
+```
+
+### Controls 
+```{r retro freq table diagnosis control}
+dat.retro %>%
+  group_by(Sample) %>%
+  freq(control) 
+```
+
+### Dont know or prefer not to say
+```{r retro freq table diagnosis prefer not to say}
+dat.retro %>%
+  group_by(Sample) %>%
+  freq(DidNotRespondMHD) 
+```
+
 ## Means, SD and n
-
 ### overall

### 2021-01-11 PANCHANGE_analysis.Rmd
detail checks and fixes

@@
 ocir.diff_score_cols
+```
+
+# Create subsets of data for analyses
+Filter data frame to create 2 additional datasets. Additional exclusion criteria (beyond those listed above) are specified below:
+
+  1. Retrospective - baseline change anlyses
+        i. Exclude individuals missing retrospective and/or baseline data
+  2. Prepandemic - baseline change analyses
+          i. Exclude individuals missing pandemic and/or baseline data
+          ii. Exclude individuals with prepandemic data collected after 1st March.
+
+Retro-baseline analyses
+
+Note: make sure we impute retrospective data for those who did not change their feelings
+
+```{r impute retro for those who did not change}
+
+dat$gad.sum_score_retro <- ifelse(dat$gad.pandemic_felt_feelings == "No different", dat$gad.sum_score_base,dat$gad.sum_score_retro)
+dat$phq.sum_score_retro <- ifelse(dat$phq.pandemic_felt_feelings == "No different", dat$phq.sum_score_base,dat$phq.sum_score_retro)
+
+```
+
+```{r subsample for retro-baseline analysis}
+dat.retro <- dat %>%
+  filter(
+    ((data_group_gad == "Baseline and retrospective data" |
+      data_group_gad == "All prepandemic, baseline and retrospective data") |
+      (data_group_phq == "Baseline and retrospective data" |
+      data_group_phq == "All prepandemic, baseline and retrospective data") |
+      (data_group_pcl == "Baseline and retrospective data" |
+      data_group_pcl == "All prepandemic, baseline and retrospective data"))
+  )
+
+dim(dat.retro)
+```
+
+Prepan-baseline analyses
+Exclude individuals with NA for MHD, age, gender; exclude if prepan data collected after 1 March
+
+```{r subsample for prepan-baseline analysis}
+dat.prepan <- dat %>%
+  filter(
+    ((data_group_gad == "Prepandemic and baseline data" |
+      data_group_gad == "All prepandemic, baseline and retrospective data") |
+      (data_group_phq == "Prepandemic and baseline data" |
+      data_group_phq == "All prepandemic, baseline and retrospective data") |
+      (data_group_pcl == "Prepandemic and baseline data" |
+      data_group_pcl == "All prepandemic, baseline and retrospective data") ) &
+      prepandemic_march_1_numeric == 1 # Exclude participants that signed up after the 1. March
+  )
+
+dim(dat.prepan)
+```
+
+Prepan-baseline analyses
+Exclude individuals with NA for MHD, age, gender; exclude if prepan data collected after 1 March (to ensure comparability with prepan analyses)
+
+```{r subsample for retro sensitivity analysis}
+dat.retro_sensitivity <- dat %>%
+  filter(
+    ((data_group_gad == "All prepandemic, baseline and retrospective data") |
+      (data_group_phq == "All prepandemic, baseline and retrospective data") |
+      (data_group_pcl == "All prepandemic, baseline and retrospective data") |
+      (data_group_ocir == "All prepandemic, baseline and retrospective data")) &
+      prepandemic_march_1_numeric == 1 # Exclude participants that signed up after the 1. March
+  )
+
+dim(dat.retro_sensitivity)
+```
+age^2 sensitivity
+Exclude individuals with NA for continuous Age variable
+```{r}
+dat_age_sensitivity <- dat %>%
+  filter(!is.na(Age))
+dim(dat_age_sensitivity)
+
+dat.retro_age_sensitivity <- dat.retro %>%
+  filter(!is.na(Age))
+dim(dat.retro_age_sensitivity)
+
+dat.prepan_age_sensitivity <- dat.prepan %>%
+  filter(!is.na(Age))
+dim(dat.prepan_age_sensitivity)
+```
+
+Sensitivity analysis for individuals who signed up to GLAD (prepan) either 3, 6 or 9 months before the pendemic began.
+```{r subsample for pre-pan sensitivity analysis}
+# Participants who signed up in the three months before the pandemic began
+dat.prepan_sensitivity_3months <- dat %>%
+  filter(
+    ((data_group_gad == "Baseline and retrospective data" |
+      data_group_gad == "Prepandemic and baseline data" |
+      data_group_gad == "All prepandemic, baseline and retrospective data") |
+      (data_group_phq == "Baseline and retrospective data" |
+      data_group_phq == "Prepandemic and baseline data" |
+      data_group_phq == "All prepandemic, baseline and retrospective data") |
+      (data_group_pcl == "Baseline and retrospective data" |
+      data_group_pcl == "Prepandemic and baseline data" |
+      data_group_pcl == "All prepandemic, baseline and retrospective data") |
+      (data_group_ocir == "Baseline and retrospective data" |
+      data_group_ocir == "Prepandemic and baseline data" |
+      data_group_ocir == "All prepandemic, baseline and retrospective data")) &
+      prepandemic_3_months_numeric == 1 # Only participants who signed up between December 1st 2019 and March 1st 2020
+  )
+
+# Participants who signed up in the three months before the pandemic began
+dat.prepan_sensitivity_6months <- dat %>%
+  filter(
+    ((data_group_gad == "Baseline and retrospective data" |
+      data_group_gad == "Prepandemic and baseline data" |
+      data_group_gad == "All prepandemic, baseline and retrospective data") |
+      (data_group_phq == "Baseline and retrospective data" |
+      data_group_phq == "Prepandemic and baseline data" |
+      data_group_phq == "All prepandemic, baseline and retrospective data") |
+      (data_group_pcl == "Baseline and retrospective data" |
+      data_group_pcl == "Prepandemic and baseline data" |
+      data_group_pcl == "All prepandemic, baseline and retrospective data") |
+      (data_group_ocir == "Baseline and retrospective data" |
+      data_group_ocir == "Prepandemic and baseline data" |
+      data_group_ocir == "All prepandemic, baseline and retrospective data")) &
+      prepandemic_6_months_numeric == 1 # Only participants who signed up between September 1st 2019 and March 1st 2020
+  )
+
+# Participants who signed up in the three months before the pandemic began
+dat.prepan_sensitivity_9months <- dat %>%
+  filter(
+    ((data_group_gad == "Baseline and retrospective data" |
+      data_group_gad == "Prepandemic and baseline data" |
+      data_group_gad == "All prepandemic, baseline and retrospective data") |
+      (data_group_phq == "Baseline and retrospective data" |
+      data_group_phq == "Prepandemic and baseline data" |
+      data_group_phq == "All prepandemic, baseline and retrospective data") |
+      (data_group_pcl == "Baseline and retrospective data" |
+      data_group_pcl == "Prepandemic and baseline data" |
+      data_group_pcl == "All prepandemic, baseline and retrospective data") |
+      (data_group_ocir == "Baseline and retrospective data" |
+      data_group_ocir == "Prepandemic and baseline data" |
+      data_group_ocir == "All prepandemic, baseline and retrospective data")) &
+      prepandemic_9_months_numeric == 1 # Only participants who signed up between June 1st 2019 and March 1st 2020
+  )
+
 ```
@@
 
-# Create subsets of data for analyses
-Filter data frame to create 2 additional datasets. Additional exclusion criteria (beyond those listed above) are specified below:
-
-  1. Retrospective - baseline change anlyses
-        i. Exclude individuals missing retrospective and/or baseline data
-  2. Prepandemic - baseline change analyses
-          i. Exclude individuals missing pandemic and/or baseline data
-          ii. Exclude individuals with prepandemic data collected after 1st March.
-
-Retro-baseline analyses
-
-Note: make sure we impute retrospective data for those who did not change their feelings
-
-```{r impute retro for those who did not change}
-
-dat$gad.sum_score_retro <- ifelse(dat$gad.pandemic_felt_feelings == "No different", dat$gad.sum_score_base,dat$gad.sum_score_retro)
-dat$phq.sum_score_retro <- ifelse(dat$phq.pandemic_felt_feelings == "No different", dat$phq.sum_score_base,dat$phq.sum_score_retro)
-
-```
-
-```{r subsample for retro-baseline analysis}
-dat.retro <- dat %>%
-  filter(
-    ((data_group_gad == "Baseline and retrospective data" |
-      data_group_gad == "All prepandemic, baseline and retrospective data") |
-      (data_group_phq == "Baseline and retrospective data" |
-      data_group_phq == "All prepandemic, baseline and retrospective data") |
-      (data_group_pcl == "Baseline and retrospective data" |
-      data_group_pcl == "All prepandemic, baseline and retrospective data"))
-  )
-
-dim(dat.retro)
-```
-
-Prepan-baseline analyses
-Exclude individuals with NA for MHD, age, gender; exclude if prepan data collected after 1 March
-
-```{r subsample for prepan-baseline analysis}
-dat.prepan <- dat %>%
-  filter(
-    ((data_group_gad == "Prepandemic and baseline data" |
-      data_group_gad == "All prepandemic, baseline and retrospective data") |
-      (data_group_phq == "Prepandemic and baseline data" |
-      data_group_phq == "All prepandemic, baseline and retrospective data") |
-      (data_group_pcl == "Prepandemic and baseline data" |
-      data_group_pcl == "All prepandemic, baseline and retrospective data") ) &
-      prepandemic_march_1_numeric == 1 # Exclude participants that signed up after the 1. March
-  )
-
-dim(dat.prepan)
-```
-
-Prepan-baseline analyses
-Exclude individuals with NA for MHD, age, gender; exclude if prepan data collected after 1 March (to ensure comparability with prepan analyses)
-
-```{r subsample for retro sensitivity analysis}
-dat.retro_sensitivity <- dat %>%
-  filter(
-    ((data_group_gad == "All prepandemic, baseline and retrospective data") |
-      (data_group_phq == "All prepandemic, baseline and retrospective data") |
-      (data_group_pcl == "All prepandemic, baseline and retrospective data") |
-      (data_group_ocir == "All prepandemic, baseline and retrospective data")) &
-      prepandemic_march_1_numeric == 1 # Exclude participants that signed up after the 1. March
-  )
-
-dim(dat.retro_sensitivity)
-```
-age^2 sensitivity
-Exclude individuals with NA for continuous Age variable
-```{r}
-dat_age_sensitivity <- dat %>%
-  filter(!is.na(Age))
-dim(dat_age_sensitivity)
-
-dat.retro_age_sensitivity <- dat.retro %>%
-  filter(!is.na(Age))
-dim(dat.retro_age_sensitivity)
-
-dat.prepan_age_sensitivity <- dat.prepan %>%
-  filter(!is.na(Age))
-dim(dat.prepan_age_sensitivity)
-```
-
-Sensitivity analysis for individuals who signed up to GLAD (prepan) either 3, 6 or 9 months before the pendemic began.
-```{r subsample for pre-pan sensitivity analysis}
-# Participants who signed up in the three months before the pandemic began
-dat.prepan_sensitivity_3months <- dat %>%
-  filter(
-    ((data_group_gad == "Baseline and retrospective data" |
-      data_group_gad == "Prepandemic and baseline data" |
-      data_group_gad == "All prepandemic, baseline and retrospective data") |
-      (data_group_phq == "Baseline and retrospective data" |
-      data_group_phq == "Prepandemic and baseline data" |
-      data_group_phq == "All prepandemic, baseline and retrospective data") |
-      (data_group_pcl == "Baseline and retrospective data" |
-      data_group_pcl == "Prepandemic and baseline data" |
-      data_group_pcl == "All prepandemic, baseline and retrospective data") |
-      (data_group_ocir == "Baseline and retrospective data" |
-      data_group_ocir == "Prepandemic and baseline data" |
-      data_group_ocir == "All prepandemic, baseline and retrospective data")) &
-      prepandemic_3_months_numeric == 1 # Only participants who signed up between December 1st 2019 and March 1st 2020
-  )
-
-# Participants who signed up in the three months before the pandemic began
-dat.prepan_sensitivity_6months <- dat %>%
-  filter(
-    ((data_group_gad == "Baseline and retrospective data" |
-      data_group_gad == "Prepandemic and baseline data" |
-      data_group_gad == "All prepandemic, baseline and retrospective data") |
-      (data_group_phq == "Baseline and retrospective data" |
-      data_group_phq == "Prepandemic and baseline data" |
-      data_group_phq == "All prepandemic, baseline and retrospective data") |
-      (data_group_pcl == "Baseline and retrospective data" |
-      data_group_pcl == "Prepandemic and baseline data" |
-      data_group_pcl == "All prepandemic, baseline and retrospective data") |
-      (data_group_ocir == "Baseline and retrospective data" |
-      data_group_ocir == "Prepandemic and baseline data" |
-      data_group_ocir == "All prepandemic, baseline and retrospective data")) &
-      prepandemic_6_months_numeric == 1 # Only participants who signed up between September 1st 2019 and March 1st 2020
-  )
-
-# Participants who signed up in the three months before the pandemic began
-dat.prepan_sensitivity_9months <- dat %>%
-  filter(
-    ((data_group_gad == "Baseline and retrospective data" |
-      data_group_gad == "Prepandemic and baseline data" |
-      data_group_gad == "All prepandemic, baseline and retrospective data") |
-      (data_group_phq == "Baseline and retrospective data" |
-      data_group_phq == "Prepandemic and baseline data" |
-      data_group_phq == "All prepandemic, baseline and retrospective data") |
-      (data_group_pcl == "Baseline and retrospective data" |
-      data_group_pcl == "Prepandemic and baseline data" |
-      data_group_pcl == "All prepandemic, baseline and retrospective data") |
-      (data_group_ocir == "Baseline and retrospective data" |
-      data_group_ocir == "Prepandemic and baseline data" |
-      data_group_ocir == "All prepandemic, baseline and retrospective data")) &
-      prepandemic_9_months_numeric == 1 # Only participants who signed up between June 1st 2019 and March 1st 2020
-  )
-
-```
-
 2. Regression models (Regress covariates out of the change? Which?)
@@
                "Gender_collapsedNon-binary/Self-defined" = "Non-binary/Self-defined",
+                "age_category_collapsed16-18" = "16-18 years",
                "age_category_collapsed19-25" = "19-25 years",
-               "age_category_collapsed26-35" = "26-35 years",
                "age_category_collapsed36-45" = "36-45 years",
@@
                "Gender_collapsedNon-binary/Self-defined" = "Non-binary/Self-defined",
+               "age_category_collapsed16-18" = "16-18 years",
                "age_category_collapsed19-25" = "19-25 years",
-               "age_category_collapsed26-35" = "26-35 years",
                "age_category_collapsed36-45" = "36-45 years",
@@
                              "Gender_collapsed",
-                             "age_category_collapsed",
+                             "age_category_collapsed_reordered",
                              "Ethnicity_collapsed",
-                             "key_worker",
-                             "time_diff_coping_lockdown_march_23",
-                             "employment_change"
+                             "employment_prior_covid",
+                             "time_diff_coping_lockdown_march_23"
   )
@@
                "Ethnicity_collapsedOther" = "Other ethnicity",
-               "key_workerKey worker" = "Key worker",
                "time_diff_coping_lockdown_march_23" = "Time difference: Lockdown to baseline",
-               "employment_changeDecreased employment" = "Decreased employment",
-               "employment_changeIncreased employment" = "Increased employment",
-               "employment_changeFurloughed" = "Furloughed",
-               "employment_chnageEmployment not changed" = "Employment not changed"
+               "employment_prior_covidKey worker" = "Key worker",
+               "employment_prior_covidEmployed" = "Employed",
+               "employment_prior_covidUnemployed" = "Unemployed",
+               "employment_prior_covidRetired" = "Retired",
+               "employment_prior_covidStudent" = "Student"
              ),
@@
            ) %>%
-           select(
+           select(model1b.estimates,
              "n",
@@
 # Regression diagnostic statistics
-gad_baseline_model1b_reg_stats <- model1b.reg.stats(outcome = "gad.sum_score_base",
-                                                 data_set = "dat")
-kable(gad_baseline_model1b_reg_stats)
-gad_baseline_model1b_reg_stats
+# gad_baseline_model1b_reg_stats <- model1b.reg.stats(outcome = "gad.sum_score_base",
+#                                                  data_set = "dat")
+# kable(gad_baseline_model1b_reg_stats)
+# gad_baseline_model1b_reg_stats
 ```
@@
 # Regression diagnostic statistics
-gad_retro_model1b_explan_reg_stats <- model1b.explan.reg.stats(outcome = "gad.sum_score_base",
-                                                               explan_var = "gad.sum_score_retro",
-                                                               data_set = "dat.retro")
-kable(gad_retro_model1b_explan_reg_stats)
-gad_retro_model1b_explan_reg_stats
+# gad_retro_model1b_explan_reg_stats <- model1b.explan.reg.stats(outcome = "gad.sum_score_base",
+#                                                                explan_var = "gad.sum_score_retro",
+#                                                                data_set = "dat.retro")
+# kable(gad_retro_model1b_explan_reg_stats)
+# gad_retro_model1b_explan_reg_stats
 ```
@@
 gad_prepan_model1b_education_estimates <- model1b.explan.estimates(outcome = "gad.sum_score_base",
-                         explan_var = "pcl.sum_score_prepan",
+                         explan_var = "gad.sum_score_prepan",
                          data_set = "dat.prepan")
@@
 gad_prepan_model1b_education_estimates
-
-# Regression diagnostic statistics
-gad_prepan_model1b_education_reg_stats <- model1b.explan.reg.stats(outcome = "gad.sum_score_base",
-                         explan_var = "pcl.sum_score_prepan",
-                         data_set = "dat.prepan")
-kable(gad_prepan_model1b_education_reg_stats)
-gad_prepan_model1b_education_reg_stats
+# 
+# # Regression diagnostic statistics
+# gad_prepan_model1b_education_reg_stats <- model1b.explan.reg.stats(outcome = "gad.sum_score_base",
+#                          explan_var = "gad.sum_score_prepan",
+#                          data_set = "dat.prepan")
+# kable(gad_prepan_model1b_education_reg_stats)
+# gad_prepan_model1b_education_reg_stats
 ```
@@
 phq_baseline_model1b_estimates
-
-# Regression diagnostic statistics
-phq_baseline_model1b_reg_stats <- model1b.reg.stats(outcome = "phq.sum_score_base",
-                                                 data_set = "dat")
-kable(phq_baseline_model1b_reg_stats)
-phq_baseline_model1b_reg_stats
+# 
+# # Regression diagnostic statistics
+# phq_baseline_model1b_reg_stats <- model1b.reg.stats(outcome = "phq.sum_score_base",
+#                                                  data_set = "dat")
+# kable(phq_baseline_model1b_reg_stats)
+# phq_baseline_model1b_reg_stats
 ```
@@
 # Regression diagnostic statistics
-phq_retro_model1b_explan_reg_stats <- model1b.explan.reg.stats(outcome = "phq.sum_score_base",
-                                                               explan_var = "phq.sum_score_retro",
-                                                               data_set = "dat.retro")
-kable(phq_retro_model1b_explan_reg_stats)
-phq_retro_model1b_explan_reg_stats
+# phq_retro_model1b_explan_reg_stats <- model1b.explan.reg.stats(outcome = "phq.sum_score_base",
+#                                                                explan_var = "phq.sum_score_retro",
+#                                                                data_set = "dat.retro")
+# kable(phq_retro_model1b_explan_reg_stats)
+# phq_retro_model1b_explan_reg_stats
 ```
@@
 phq_prepan_model1b_education_estimates <- model1b.explan.estimates(outcome = "phq.sum_score_base",
-                         explan_var = "pcl.sum_score_prepan",
+                         explan_var = "phq.sum_score_prepan",
                          data_set = "dat.prepan")
@@
 # Regression diagnostic statistics
-phq_prepan_model1b_education_reg_stats <- model1b.explan.reg.stats(outcome = "phq.sum_score_base",
-                         explan_var = "pcl.sum_score_prepan",
-                         data_set = "dat.prepan")
-kable(phq_prepan_model1b_education_reg_stats)
-phq_prepan_model1b_education_reg_stats
+# phq_prepan_model1b_education_reg_stats <- model1b.explan.reg.stats(outcome = "phq.sum_score_base",
+#                          explan_var = "phq.sum_score_prepan",
+#                          data_set = "dat.prepan")
+# kable(phq_prepan_model1b_education_reg_stats)
+# phq_prepan_model1b_education_reg_stats
 ```
@@
 
-# Regression diagnostic statistics
-ocir_baseline_model1b_reg_stats <- model1b.reg.stats(outcome = "ocir.sum_score_base",
-                                                 data_set = "dat")
-kable(ocir_baseline_model1b_reg_stats)
-ocir_baseline_model1b_reg_stats
+# # Regression diagnostic statistics
+# ocir_baseline_model1b_reg_stats <- model1b.reg.stats(outcome = "ocir.sum_score_base",
+#                                                  data_set = "dat")
+# kable(ocir_baseline_model1b_reg_stats)
+# ocir_baseline_model1b_reg_stats
 ```
@@
 
-# Regression diagnostic statistics
-ocir_retro_model1b_explan_reg_stats <- model1b.explan.reg.stats(outcome = "ocir.sum_score_base",
-                                                               explan_var = "ocir.sum_score_retro",
-                                                               data_set = "dat.retro")
-kable(ocir_retro_model1b_explan_reg_stats)
-ocir_retro_model1b_explan_reg_stats
+# # Regression diagnostic statistics
+# ocir_retro_model1b_explan_reg_stats <- model1b.explan.reg.stats(outcome = "ocir.sum_score_base",
+#                                                                explan_var = "ocir.sum_score_retro",
+#                                                                data_set = "dat.retro")
+# kable(ocir_retro_model1b_explan_reg_stats)
+# ocir_retro_model1b_explan_reg_stats
 ```
@@
 
-# Regression diagnostic statistics
-ocir_prepan_model1b_education_reg_stats <- model1b.explan.reg.stats(outcome = "ocir.sum_score_base",
-                         explan_var = "pcl.sum_score_prepan",
-                         data_set = "dat.prepan")
-kable(ocir_prepan_model1b_education_reg_stats)
-ocir_prepan_model1b_education_reg_stats
+# # Regression diagnostic statistics
+# ocir_prepan_model1b_education_reg_stats <- model1b.explan.reg.stats(outcome = "ocir.sum_score_base",
+#                          explan_var = "pcl.sum_score_prepan",
+#                          data_set = "dat.prepan")
+# kable(ocir_prepan_model1b_education_reg_stats)
+# ocir_prepan_model1b_education_reg_stats
 ```
@@
 
-# Regression diagnostic statistics
-pcl_baseline_model1b_reg_stats <- model1b.reg.stats(outcome = "pcl.sum_score_base",
-                                                 data_set = "dat")
-kable(pcl_baseline_model1b_reg_stats)
-pcl_baseline_model1b_reg_stats
+# # Regression diagnostic statistics
+# pcl_baseline_model1b_reg_stats <- model1b.reg.stats(outcome = "pcl.sum_score_base",
+#                                                  data_set = "dat")
+# kable(pcl_baseline_model1b_reg_stats)
+# pcl_baseline_model1b_reg_stats
 ```
@@
 
-# Regression diagnostic statistics
-pcl_prepan_model1b_education_reg_stats <- model1b.explan.reg.stats(outcome = "pcl.sum_score_base",
-                         explan_var = "pcl.sum_score_prepan",
-                         data_set = "dat.prepan")
-kable(pcl_prepan_model1b_education_reg_stats)
-pcl_prepan_model1b_education_reg_stats
+# # Regression diagnostic statistics
+# pcl_prepan_model1b_education_reg_stats <- model1b.explan.reg.stats(outcome = "pcl.sum_score_base",
+#                          explan_var = "pcl.sum_score_prepan",
+#                          data_set = "dat.prepan")
+# kable(pcl_prepan_model1b_education_reg_stats)
+# pcl_prepan_model1b_education_reg_stats
 ```
@@
 
+```{r functions required in book for globa assignments no explan var}
+lmoutput_format_noexplan <- function(lmobject,  group, dfname){
+
+  ## Row labels
+  independent.variables <- c("intercept",
+                             "Comorbid depression and anxiety",
+                             "Depressive disorders",
+                             "Anxiety disorders",
+                             "Eating disorders",
+                             "Obsessive compulsive disorders",
+                             "Comorbid psychotic and bipolar disorders",
+                             "Psychotic disorders",
+                             "Bipolar disorder",
+                             "Post traumatic stress disorder",
+                             "Autism spectrum disorder",
+                             "Attention deficit hyperactivity disorder",
+                             "Personality disorders",
+                             "Female",
+                             "Non-binary/Self-defined",
+                             "16-18",
+                             "19-25",
+                             "36-45",
+                             "46-55",
+                             "56-65",
+                             "66-70",
+                             "71-75",
+                             "76+",
+                             "Mixed or multiple ethnicities",
+                             "Asian",
+                             "Black",
+                             "Other",
+                             "Key worker",
+                             "Unemployed",
+                             "Student",
+                             "Retired",
+                             "Time between lockdown and baseline")
+  ## categories to facet on  
+  categories <- c("Intercept",
+                  "Pre-existing mental health (Reference controls)",
+                  "Pre-existing mental health (Reference controls)",
+                  "Pre-existing mental health (Reference controls)",
+                  "Pre-existing mental health (Reference controls)",
+                  "Pre-existing mental health (Reference controls)",
+                  "Pre-existing mental health (Reference controls)",
+                  "Pre-existing mental health (Reference controls)",
+                  "Pre-existing mental health (Reference controls)",
+                  "Pre-existing mental health (Reference controls)",
+                  "Pre-existing mental health (Reference controls)",
+                  "Pre-existing mental health (Reference controls)",
+                  "Pre-existing mental health (Reference controls)",
+                  "Gender (Reference male)",
+                  "Gender (Reference male)",
+                  "Age (Reference 26-35)",
+                  "Age (Reference 26-35)",
+                  "Age (Reference 26-35)",
+                  "Age (Reference 26-35)",
+                  "Age (Reference 26-35)",
+                  "Age (Reference 26-35)",
+                  "Age (Reference 26-35)",
+                  "Age (Reference 26-35)",
+                  "Ethnicity (Reference White)",
+                  "Ethnicity (Reference White)",
+                  "Ethnicity (Reference White)",
+                  "Ethnicity (Reference White)",
+                  "Employment (Reference employed)",
+                  "Employment (Reference employed)",
+                  "Employment (Reference employed)",
+                  "Employment (Reference employed)",
+                  "Other")
+
+  ## Disorder dimension  
+  groups <- c(group,
+              group,
+              group,
+              group,
+              group,
+              group,
+              group,
+              group,
+              group,
+              group,
+              group,
+              group,
+              group,
+              group,
+              group,
+              group,
+              group,
+              group,
+              group,
+              group,
+              group,
+              group,
+              group,
+              group,
+              group,
+              group,
+              group,
+              group,
+              group,
+              group,
+              group,
+              group)
+
+  # create data frame
+  df <- as.data.frame(coef(summary(lmobject)),row.names=F)
+
+  # add row labels
+  df$RowLabels <- independent.variables
+
+  # Add category labels
+  df$Categories <- categories
+
+  # Add group labels
+  df$Group <- groups
+
+  # calculate upper and lower confidence intervals
+  df <- df %>%
+    mutate(LowerBound = Estimate - (1.96*`Std. Error`),
+           UpperBound = Estimate + (1.96*`Std. Error`))
+
+  # drop intercept row
+  df <- df[(df$RowLabels != 'intercept'),]
+
+  # order factors
+  df$RowLabels <- factor(df$RowLabels, levels = rev(independent.variables))   ## individual rows
+  df$Categories <- factor(df$Categories, levels = unique(categories))   ## categories
+
+  # assign dataframe to global environment
+  assign(dfname, df, envir = .GlobalEnv)
+
+}
+
+model1b.lm.form.noexplan <- function(outcome) {
+
+  # define the variable name of the dependent variable
+  dependent.variable <- outcome
+  # define the independent variables
+  independent.variables <- c("depression_and_anxiety",
+                             "eating_disorders",
+                             "obsessive_compulsive_disorders",
+                             "bipolar_and_schizophrenia",
+                             "mhd.posttraumatic_stress_disorder_ptsd",
+                             "autism_spectrum_disorder",
+                             "mhd.attention_deficit_hyperactivity_disorder",
+                             "mhd.personality_disorder",
+                             "Gender_collapsed",
+                             "age_category_collapsed_reordered",
+                             "Ethnicity_collapsed",
+                             "employment_prior_covid",
+                             "time_diff_coping_lockdown_march_23"
+  )
+  # create the formula
+  glm.formula <- paste(dependent.variable, paste(independent.variables, collapse=" + "), sep=" ~ ")
+
+  # assign it globally with the right variable name.
+  assign(paste0(outcome,".",  "glmformula"),
+         glm.formula,
+         envir = .GlobalEnv
+
+  )
+}
+```
+
 ## run regression models to get normal output
@@
 
+### no explan var
+
+```{r create formulas for forest models no explan}
+
+model1b.lm.form.noexplan("gad.sum_score_base")
+
+model1b.lm.form.noexplan("phq.sum_score_base")
+
+model1b.lm.form.noexplan("pcl.sum_score_base")
+
+```
+
+```{r run models for all forest plot items no explan}
+
+gad.lm.noexplan <-  lm(formula = gad.sum_score_base.glmformula,
+                            dat.prepan)
+
+phq.lm.noexplan <- lm(formula = phq.sum_score_base.glmformula,
+                            dat.retro)
+
+pcl.lm.noexplan <-  lm(formula = pcl.sum_score_base.glmformula,
+                            dat.prepan)
+
+```
+
 ###Subset retrospective data by samples
@@
 
-```{r run models for rero by sample forest plots}
+```{r run models for retro by sample forest plots}
 
@@
 
+### no explanatory variables
+```{r generate datasets for all plots no explan}
+
+# grouped by disorder measure
+lmoutput_format_noexplan(gad.lm.noexplan,"GAD-7", "gad.lm.for.plot")
+lmoutput_format_noexplan(phq.lm.noexplan,"PHQ-9", "phq.lm.for.plot")
+lmoutput_format_noexplan(pcl.lm.noexplan,"PCL", "pcl.lm.for.plot")
+
+# Grouped by sample
+lmoutput_format_noexplan(gad.lm.noexplan,"GLAD and EDGI", "gad.lm.for.plot.GLAD")
+lmoutput_format_noexplan(gad.lm.noexplan,"NBR", "gad.lm.for.plot.NBR")
+lmoutput_format_noexplan(gad.lm.noexplan,"RAMP", "gad.lm.for.plot.RAMP")
+
+lmoutput_format_noexplan(phq.lm.noexplan,"GLAD and EDGI", "phq.lm.for.plot.GLAD")
+lmoutput_format_noexplan(phq.lm.noexplan,"NBR", "phq.lm.for.plot.NBR")
+lmoutput_format_noexplan(phq.lm.noexplan,"RAMP", "phq.lm.for.plot.RAMP")
+
+lmoutput_format_noexplan(pcl.lm.noexplan,"GLAD and EDGI", "pcl.lm.for.plot.GLAD")
+lmoutput_format_noexplan(pcl.lm.noexplan,"NBR", "pcl.lm.for.plot.NBR")
+lmoutput_format_noexplan(pcl.lm.noexplan,"RAMP", "pcl.lm.for.plot.RAMP")
+
+```
+
 ```{r merge datasets for different combinations}
@@
 
+With no control for retro or prepan (no explanatory variables)
+
+```{r merge datasets for different combinations no explan}
+# Disorder groups
+plot.dat.disorder <- rbind(gad.lm.for.plot,
+                                  phq.lm.for.plot,
+                                  pcl.lm.for.plot)
+
+# by sample
+
+plot.dat.noexplan.sample.gad <- rbind(gad.lm.for.plot.GLAD,
+                             gad.lm.for.plot.NBR,
+                             gad.lm.for.plot.RAMP)
+
+plot.dat.noexplan.sample.phq <- rbind(phq.lm.for.plot.GLAD,
+                             phq.lm.for.plot.NBR,
+                             phq.lm.for.plot.RAMP)
+
+plot.dat.noexplan.sample.pcl <- rbind(pcl.lm.for.plot.GLAD,
+                             pcl.lm.for.plot.NBR,
+                             pcl.lm.for.plot.RAMP)
+
+```
+
 ## Forest plots
@@
 ```
+### disorder (no explan)
+
+```{r forest plot by disorder no explan, fig.height=30, fig.width=50, dpi=120}
+
+lm.forest(plot.dat.disorder,"Predictors of pandemic symptoms")
+
+```
 
@@
 lm.forest(plot.dat.sample.phq ,"Predictors of depression controlling for retrospective symptoms across samples")
+
+```
+
+### Sample pandemic only, no explanatory variable)
+
+```{r forest plot by sample no explan gad, fig.height=30, fig.width=50, dpi=120}
+
+lm.forest(plot.dat.noexplan.sample.gad  ,"Predictors of anxiety across samples")
+
+```
+
+```{r forest plot by sample no explan phq, fig.height=30, fig.width=50, dpi=120}
+
+lm.forest(plot.dat.noexplan.sample.phq  ,"Predictors of depression across samples")
+
+```
+
+```{r forest plot by sample no explan pcl, fig.height=30, fig.width=50, dpi=120}
+
+lm.forest(plot.dat.noexplan.sample.pcl  ,"Predictors of symptoms of PTSD across samples")
 

### 2021-01-11 PANCHANGE_data_preprocessing2020-07-15.Rmd
Added keyworker status to employment variable
knitted exclusion file with all datasets updated for employment
detail checks and fixes

@@
 NBR = FALSE
-RAMP = TRUE
-GLAD_and_EDGI = FALSE
+RAMP = FALSE
+GLAD_and_EDGI = TRUE
 ```
@@
 
+# IMPUTE RETROSPECTIE DATA for no change
+
+```{r impute retro}
+# impute retro for those who did not change
+dat$gad.sum_score_retro <- ifelse(dat$gad.pandemic_felt_feelings == "No different", dat$gad.sum_score_base,dat$gad.sum_score_retro)
+dat$phq.sum_score_retro <- ifelse(dat$phq.pandemic_felt_feelings == "No different", dat$phq.sum_score_base,dat$phq.sum_score_retro)
+```
+
 ```{r Investigating RAMP NAs}

### 2021-01-13 PANCHANGE_analysis.Rmd
fixed prepandemic regression models

@@
 gad_prepan_model1b_education_reg_stats <- model1b.explan.reg.stats(outcome = "gad.sum_score_base",
-                         explan_var = "pcl.sum_score_prepan",
+                         explan_var = "gad.sum_score_prepan",
                          data_set = "dat.prepan")
@@
 phq_prepan_model1b_education_reg_stats <- model1b.explan.reg.stats(outcome = "phq.sum_score_base",
-                         explan_var = "pcl.sum_score_prepan",
+                         explan_var = "phq.sum_score_prepan",
                          data_set = "dat.prepan")
@@
 ocir_prepan_model1b_education_estimates <- model1b.explan.estimates(outcome = "ocir.sum_score_base",
-                         explan_var = "pcl.sum_score_prepan",
+                         explan_var = "ocir.sum_score_prepan",
                          data_set = "dat.prepan")
@@
 ocir_prepan_model1b_education_reg_stats <- model1b.explan.reg.stats(outcome = "ocir.sum_score_base",
-                         explan_var = "pcl.sum_score_prepan",
+                         explan_var = "ocir.sum_score_prepan",
                          data_set = "dat.prepan")

### 2021-01-13 Final_analyses_checks_notebook.Rmd
detail checks and fixes
added knitted paper detail check doc
fixed retrospective data inclusion criteria

@@
           data_group_phq == "All prepandemic, baseline and retrospective data") |
-       (data_group_pcl == "Baseline and retrospective data" |
+        (data_group_pcl == "Baseline data only" |
       data_group_pcl == "All prepandemic, baseline and retrospective data"))
@@
 ## Sample sizes
+
+### full data (only excluding for NA on age, gender, MHD)
+
+```{r full data n}
+
+alldat %>%
+  freq(alldat$Sample)
+
+```
+### retrospective data (excluding for NA on age, gender, MHD, or either retrospective or baseline data )
+with exception of PCL which has nor etrospective data
+
+```{r retro data n}
+
+dat.retro %>%
+  freq(Sample)
+
+```
+
+### Prepandemic data (excluding for NA on age, gender, MHD, or either prepandemic or baseline data )
+
+```{r prepan data n}
+
+dat.prepan %>%
+  freq(Sample)
+
+```
 

### 2021-01-13 PANCHANGE_analysis.Rmd
fixed retrospective data inclusion criteria

@@
 
+Important note::: PCL does not have retrospective data, so we allow Baseline only or All prepandemic, baseline and retrospective
 ```{r subsample for retro-baseline analysis}
@@
       data_group_phq == "All prepandemic, baseline and retrospective data") |
-      (data_group_pcl == "Baseline and retrospective data" |
+      (data_group_pcl == "Baseline data only" |
       data_group_pcl == "All prepandemic, baseline and retrospective data"))
@@
       data_group_pcl == "Prepandemic and baseline data" |
-      data_group_pcl == "All prepandemic, baseline and retrospective data") |
-      (data_group_ocir == "Baseline and retrospective data" |
-      data_group_ocir == "Prepandemic and baseline data" |
-      data_group_ocir == "All prepandemic, baseline and retrospective data")) &
+      data_group_pcl == "Baseline data only" |
+      data_group_pcl == "All prepandemic, baseline and retrospective data"))  &
       prepandemic_3_months_numeric == 1 # Only participants who signed up between December 1st 2019 and March 1st 2020
@@
       data_group_pcl == "Prepandemic and baseline data" |
-      data_group_pcl == "All prepandemic, baseline and retrospective data") |
-      (data_group_ocir == "Baseline and retrospective data" |
-      data_group_ocir == "Prepandemic and baseline data" |
-      data_group_ocir == "All prepandemic, baseline and retrospective data")) &
+      data_group_pcl == "Baseline data only" |
+      data_group_pcl == "All prepandemic, baseline and retrospective data")) &
       prepandemic_6_months_numeric == 1 # Only participants who signed up between September 1st 2019 and March 1st 2020
@@
       data_group_pcl == "Prepandemic and baseline data" |
-      data_group_pcl == "All prepandemic, baseline and retrospective data") |
-      (data_group_ocir == "Baseline and retrospective data" |
-      data_group_ocir == "Prepandemic and baseline data" |
-      data_group_ocir == "All prepandemic, baseline and retrospective data")) &
+      data_group_pcl == "Baseline data only" |
+      data_group_pcl == "All prepandemic, baseline and retrospective data"))  &
       prepandemic_9_months_numeric == 1 # Only participants who signed up between June 1st 2019 and March 1st 2020

### 2021-01-14 Final_analyses_checks_notebook.Rmd
idnetified PCL sample drop issue and fixed

@@
         (data_group_pcl == "Baseline data only" |
+           data_group_pcl == "Baseline and retrospective data" |
+            data_group_pcl == "Prepandemic and baseline data" |
+      data_group_pcl == "All prepandemic, baseline and retrospective data"))
+  )
+
+dim(dat.retro)
+```
+
+```{r subset retrospective data }
+dat.retro <- alldat %>%
+  filter(
+    ((data_group_gad == "Baseline and retrospective data" |
+        data_group_gad == "All prepandemic, baseline and retrospective data") |
+       (data_group_phq == "Baseline and retrospective data" |
+          data_group_phq == "All prepandemic, baseline and retrospective data") |
+        (data_group_pcl == "Baseline data only" |
+           data_group_pcl == "Baseline and retrospective data" |
       data_group_pcl == "All prepandemic, baseline and retrospective data"))

### 2021-01-14 PANCHANGE_analysis.Rmd
idnetified PCL sample drop issue and fixed

@@
 
-Important note::: PCL does not have retrospective data, so we allow Baseline only or All prepandemic, baseline and retrospective
+Important note::: PCL does not have retrospective data, so we allow Baseline only or All prepandemic, baseline and retrospective OR Baseline and prepandemic data.
+Important logic here is that we need EVRYONE with ANY baseline data, but dont care about any other time point for this retrospective dataset for PCL.
 ```{r subsample for retro-baseline analysis}
@@
         (data_group_pcl == "Baseline data only" |
+           data_group_pcl == "Baseline and retrospective data" |
       data_group_pcl == "All prepandemic, baseline and retrospective data"))

### 2021-01-14 Final_analyses_checks_notebook.Rmd
fixed duplicate chunk name in check doc

@@
             data_group_pcl == "Prepandemic and baseline data" |
-      data_group_pcl == "All prepandemic, baseline and retrospective data"))
-  )
-
-dim(dat.retro)
-```
-
-```{r subset retrospective data }
-dat.retro <- alldat %>%
-  filter(
-    ((data_group_gad == "Baseline and retrospective data" |
-        data_group_gad == "All prepandemic, baseline and retrospective data") |
-       (data_group_phq == "Baseline and retrospective data" |
-          data_group_phq == "All prepandemic, baseline and retrospective data") |
-        (data_group_pcl == "Baseline data only" |
-           data_group_pcl == "Baseline and retrospective data" |
       data_group_pcl == "All prepandemic, baseline and retrospective data"))

### 2021-01-18 PANCHANGE_analysis.Rmd
added retrospective prepandemic ttests and glad edgi sensitivity

@@
 
+# GAD retro GLAD and EDGI sensitivity
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r gad employment change sensitivity model1b sum_score retro glad edgi sensitivity }
+# Regression coefficients
+gad_prepan_model1b_education_estimates <- model1b.explan.estimates(outcome = "gad.sum_score_base",
+                         explan_var = "gad.sum_score_retro",
+                         data_set = "dat.prepan")
+kable(gad_prepan_model1b_education_estimates)
+gad_prepan_model1b_education_estimates
+# 
+# # Regression diagnostic statistics
+# gad_prepan_model1b_education_reg_stats <- model1b.explan.reg.stats(outcome = "gad.sum_score_base",
+#                          explan_var = "gad.sum_score_prepan",
+#                          data_set = "dat.prepan")
+# kable(gad_prepan_model1b_education_reg_stats)
+# gad_prepan_model1b_education_reg_stats
+```
+
 # PHQ baseline
@@
                          explan_var = "phq.sum_score_prepan",
+                         data_set = "dat.prepan")
+kable(phq_prepan_model1b_education_estimates)
+phq_prepan_model1b_education_estimates
+
+# Regression diagnostic statistics
+# phq_prepan_model1b_education_reg_stats <- model1b.explan.reg.stats(outcome = "phq.sum_score_base",
+#                          explan_var = "phq.sum_score_prepan",
+#                          data_set = "dat.prepan")
+# kable(phq_prepan_model1b_education_reg_stats)
+# phq_prepan_model1b_education_reg_stats
+```
+
+# PHQ retro GLAD and EDGI sensitivity
+### Model 1b: Overlapping disorders, Adjusted
+Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
+```{r phq employment change sensitivity model1b sum_score retro in glad edgi sensitivity}
+# Regression coefficients
+phq_prepan_model1b_education_estimates <- model1b.explan.estimates(outcome = "phq.sum_score_base",
+                         explan_var = "phq.sum_score_retro",
                          data_set = "dat.prepan")

### 2021-02-05 Paper_Histograms.Rmd
Created Paper_historgams.Rmd for the histograms

--- 2020-12-04 Retro and prepan comparisons.Rmd
@@
 ---
-title: "Retro and prepan comparisons"
-author: "Steven Bright and Henry Rogers"
-date: "30/10/2020"
+title: "Placeholder"
+author: "Steven Bright"
+date: "05/02/2021"
 output: html_document
 ---
-
-#Set up
-
-```{r clean environment}
-
-remove(list = ls())
-
-```
-
-```{r Save a date object}
-
-date <- Sys.Date()
-
-```
 
@@
 ```
-
-#Set WD
-
-```{r Set WD}
-
-#Steven's working environment
-setwd("c:\\Users\\Student\\Documents\\Git\\PANCHANGE_analysis")
-getwd()
-
-#Henry's working environment
-
-```
-
-#Load packages
-
-```{r Load packages}
-
-library(tidyverse)
-library(lfactors)
-library(data.table)
-
-```
-
-#Set file paths and data names
-
-```{r Source data and file paths}
-#Sourcing data paths for raw data (data_path) and clean data (data_path_clean)
-#Sourcing data files for 1) saliva_kits 2) coping_glad 3) demographic datasets
-
-source(file = "../Coping_data_path.R")
-
-#May need a different path for PC computers
-#source(file = "..\\flare_data_path.R")
-
-```
-
-#Prepare data for merge
-
-```{r Read in data}
-
-data_glad <- read_csv(paste0(data_path, coping_glad))
-data_nbr <- read_csv(paste0(data_path, coping_nbr))
-data_edgi <- read_csv(paste0(data_path, coping_edgi))
-
-```
-
-```{r Drop first 2 rows}
-
-coping_glad_cohort <- data_glad[3:dim(data_glad)[1],]
-coping_edgi_cohort <- data_edgi[3:dim(data_edgi)[1],]
-coping_nbr_cohort <- data_nbr[3:dim(data_nbr)[1],]
-
-```
-
-Perform the left join
-
-```{r left join}
-
-coping_data <- left_join(coping_nbr_cohort, 
-                         coping_glad_cohort,
-                         by = "ExternalReference")
-
-coping_data <- left_join(coping_data, 
-                         coping_edgi_cohort,
-                         by = "ExternalReference")
-
-#MD addition to visualise:
-head(coping_data)
-
-```
-
-#Task overview
-
-1) No change retrospective scores: "impute" to be the same as their pandemic baseline
-
-2) Check correlation between these and the pre-pandemic scores in COPING
-
-3) ACCURACY SCORES: Another question: what proportion of the time are people right about
-
-worse / better / no change (compared to pre-pandemic)
-
-Two categories: (1) is it accurate (i.e. if they say better are they at all better) and (2) is it more than 3 points different
-
-#Task 1: Impute no change scores

### 2021-02-05 Paper_Histograms.Rmd
Copy and pasted impute chunks into hisograms script from final analyses check notebook script

@@
 ```
+
+# Set up
+
+```{r read in data }
+
+# Read in data
+library(knitr)
+library(summarytools)
+library(psych)
+library(polycor)
+library(corrplot)
+library(patchwork)
+library(broom)
+library(tidyverse)
+library(ggpubr)
+
+# get file info
+source("../PANCHANGE_raw_path.R")
+
+alldat <-  readRDS(file = paste0(data_path, "/four_cohorts_variables_exclusion.rds"))
+
+```
+
+# Impute and subset data
+
+Impute retrospective scores if no change reported
+
+```{r impute retro}
+
+# impute retro for those who did not change
+
+alldat$gad.sum_score_retro <- ifelse(alldat$gad.pandemic_felt_feelings == "No different", alldat$gad.sum_score_base,alldat$gad.sum_score_retro)
+alldat$phq.sum_score_retro <- ifelse(alldat$phq.pandemic_felt_feelings == "No different", alldat$phq.sum_score_base,alldat$phq.sum_score_retro)
+```
+
+subsample for retro-baseline analysis
+exclude those who do not have complete responses for both baseline and retrospective
+in addition to those already excluded for NA in age, gender and MH diagnosis.
+
+RETROSPECTIVE
+```{r subset retrospective data }
+dat.retro <- alldat %>%
+  filter(
+    ((data_group_gad == "Baseline and retrospective data" |
+        data_group_gad == "All prepandemic, baseline and retrospective data") |
+       (data_group_phq == "Baseline and retrospective data" |
+          data_group_phq == "All prepandemic, baseline and retrospective data") |
+        (data_group_pcl == "Baseline data only" |
+           data_group_pcl == "Baseline and retrospective data" |
+            data_group_pcl == "Prepandemic and baseline data" |
+      data_group_pcl == "All prepandemic, baseline and retrospective data"))
+  )
+
+dim(dat.retro)
+```
+
+subsample for prepan-baseline analysis
+exclude those who do not have complete responses for both baseline and prepandemic
+in addition to those already excluded for NA in age, gender and MH diagnosis.
+
+PREPANDEMIC
+```{r subset prepandemic}
+
+dat.prepan <- alldat %>%
+  filter(
+    ((data_group_gad == "Prepandemic and baseline data" |
+        data_group_gad == "All prepandemic, baseline and retrospective data") |
+       (data_group_phq == "Prepandemic and baseline data" |
+          data_group_phq == "All prepandemic, baseline and retrospective data") |
+       (data_group_pcl == "Prepandemic and baseline data" |
+          data_group_pcl == "All prepandemic, baseline and retrospective data") ) &
+      prepandemic_march_1_numeric == 1 # Exclude participants that signed up after the 1. March
+  )
+
+dim(dat.prepan)
+
+```
+
+Subset by study
+
+```{r subset by study}
+
+## Subset samples by study
+
+GLAD.prepan <- dat.prepan %>%
+  filter(Sample == "GLAD" | 
+           Sample == "EDGI")
+
+NBR.prepan <- dat.prepan %>%
+  filter(Sample == "NBR")
+
+RAMP.prepan <- dat.prepan %>%
+  filter(Sample == "RAMP")
+
+### retro
+GLAD.retro <- dat.retro %>%
+  filter(Sample == "GLAD" | 
+           Sample == "EDGI")
+
+NBR.retro <- dat.retro %>%
+  filter(Sample == "NBR")
+
+RAMP.retro <- dat.retro %>%
+  filter(Sample == "RAMP")
+
+```

### 2021-02-05 Paper_Histograms.Rmd
Add template code for GLAD/EDGI gender bar chart

@@
 knitr::opts_chunk$set(echo = TRUE)
+```
+
+```{r Clean environment}
+
+remove(list = ls())
+
 ```
@@
 alldat$gad.sum_score_retro <- ifelse(alldat$gad.pandemic_felt_feelings == "No different", alldat$gad.sum_score_base,alldat$gad.sum_score_retro)
+
 alldat$phq.sum_score_retro <- ifelse(alldat$phq.pandemic_felt_feelings == "No different", alldat$phq.sum_score_base,alldat$phq.sum_score_retro)
+
 ```
@@
 ```{r subset retrospective data }
+
 dat.retro <- alldat %>%
@@
 dim(dat.retro)
+
 ```
@@
 ```
+
+#Histograms
+
+##Gender
+###Prepan
+
+```{r GLAD/EDGI gender prepan histogram}
+
+GLAD.prepan %>%
+  ggplot(aes(x = Gender)) +
+  geom_bar(fill = "black") +
+  theme_minimal() +
+  theme(plot.title = element_text(hjust = 0.5),
+        plot.subtitle = element_text(hjust = 0.5)) +
+  labs(title = "Gender distribution of the GLAD/EDGI Cohort",
+       subtitle = paste("N =", dim(GLAD.prepan)[1]),
+       x = "",
+       y = "N participants")
+
+```

### 2021-02-05 Paper_Histograms.Rmd
Add palette code chunk from exclusion descriptives script
Add colour to the GLAD/EDGI gender graph template code

@@
 
+```
+
+```{r Colour palettes: COPING}
+
+COPINGpalette2 <- c("#78D9C5",
+                    "#F5BE5E")
+
+COPINGpalette3 <- c("#78D9C5",
+                    "#F5BE5E",
+                    "#EEB6E9")
+
+COPINGpalette4 <- c("#78D9C5",
+                    "#F5BE5E",
+                    "#EEB6E9",
+                    "#DBDB73")
+
+COPINGpalette5 <- c("#78D9C5",
+                    "#F5BE5E",
+                    "#EEB6E9",
+                    "#DBDB73", 
+                    "#FFED98")
+
+COPINGpalette6 <- c("#78D9C5",
+                    "#F5BE5E",
+                    "#EEB6E9",
+                    "#DBDB73",
+                    "#FFED98",
+                    "#BFD2EB")
+
+COPINGpalette7 <- c("#78D9C5",
+                    "#F5BE5E",
+                    "#EEB6E9",
+                    "#DBDB73", 
+                    "#FFED98",
+                    "#BFD2EB", 
+                    "#808080")
+
+COPINGpaletteGRAD <- c("#F5BE5E",
+                       "#FFD284",
+                       "#FFEED1",
+                       "#B5B5B5",
+                       "#DEFFF8",
+                       "#94F6E1",
+                       "#78D9C5")
+
+COPINGNeuCenterpalette <- c("#78D9C5",
+                            "#808080",
+                            "#F5BE5E")
+
+RAMPworseGRADpalette <- c("#78D9C5",
+                          "#FFEED1",
+                          "#F5BE5E",
+                          "#FFB1B5")
+GLADpalette = c("#efc00b", 
+                "#b7dee8")  
 ```
@@
   ggplot(aes(x = Gender)) +
-  geom_bar(fill = "black") +
+  geom_bar(fill = COPINGpalette4) +
   theme_minimal() +

### 2021-02-05 Paper_Histograms.Rmd
Add the GLAD/EDGI retro gender graph

@@
 
-```{r GLAD/EDGI gender prepan histogram}
+```{r GLAD/EDGI gender prepan}
 
@@
         plot.subtitle = element_text(hjust = 0.5)) +
-  labs(title = "Gender distribution of the GLAD/EDGI Cohort",
+  labs(title = "Gender distribution of the GLAD/EDGI prepan cohort",
        subtitle = paste("N =", dim(GLAD.prepan)[1]),
@@
 ```
+
+###Retrospective
+
+```{r NBR gender prepan}
+
+GLAD.retro %>%
+  ggplot(aes(x = Gender)) +
+  geom_bar(fill = COPINGpalette4) +
+  theme_minimal() +
+  theme(plot.title = element_text(hjust = 0.5),
+        plot.subtitle = element_text(hjust = 0.5)) +
+  labs(title = "Gender distribution of the GLAD/EDGI retro cohort",
+       subtitle = paste("N =", dim(GLAD.retro)[1]),
+       x = "",
+       y = "N participants")
+
+```
+
+```{r}
+
+```

### 2021-02-05 Paper_Histograms.Rmd
Added NBR gender retro graph

@@
 
-```{r NBR gender prepan}
+```{r GLAD/EDGI gender retro}
 
@@
 
-```{r}
+```{r NBR gender retro}
+
+NBR.retro %>%
+  ggplot(aes(x = Gender)) +
+  geom_bar(fill = COPINGpalette4) +
+  theme_minimal() +
+  theme(plot.title = element_text(hjust = 0.5),
+        plot.subtitle = element_text(hjust = 0.5)) +
+  labs(title = "Gender distribution of the NBR retro cohort",
+       subtitle = paste("N =", dim(NBR.retro)[1]),
+       x = "",
+       y = "N participants")
 

### 2021-02-05 Paper_Histograms.Rmd
Added RAMP gender retro graph

@@
 ```
+
+```{r RAMP gender retro}
+
+RAMP.retro %>%
+  ggplot(aes(x = Gender)) +
+  geom_bar(fill = COPINGpalette4) +
+  theme_minimal() +
+  theme(plot.title = element_text(hjust = 0.5),
+        plot.subtitle = element_text(hjust = 0.5)) +
+  labs(title = "Gender distribution of the RAMP retro cohort",
+       subtitle = paste("N =", dim(RAMP.retro)[1]),
+       x = "",
+       y = "N participants")
+
+```

### 2021-02-05 Paper_Histograms.Rmd
Added template code for GLAD/EDGI prepan age graph

@@
 ```
+
+##Age
+###Prepan
+
+```{r GLAD/EDGI age prepan}
+
+GLAD.prepan %>% 
+  ggplot(aes(x = age_category_collapsed)) +
+  geom_bar() +
+  theme_minimal() +
+  theme(plot.title = element_text(hjust = 0.5),
+        plot.subtitle = element_text(hjust = 0.5)) +
+  labs(title = "Age distribution of the GLAD/EDGI prepan cohort",
+       subtitle = paste("N =", dim(GLAD.prepan)[1]),
+       x = "",
+       y = "")
+
+```

### 2021-02-05 Paper_Histograms.Rmd
Added COPING palette 9 and applied to GLAD/EDGI age prepan graph

--- 2021-02-05 Paper_Histograms.Rmd
@@
                     "#808080")
+
+COPINGpalette9 <- c("#78D9C5",
+                    "#F5BE5E",
+                    "#EEB6E9",
+                    "#DBDB73", 
+                    "#FFED98",
+                    "#BFD2EB", 
+                    "#808080",
+                    "#cccccc",
+                    "3B47DA")
 
@@
 ```
+
+##Age
+###Prepan
+
+```{r GLAD/EDGI age prepan}
+
+GLAD.prepan %>% 
+  ggplot(aes(x = age_category_collapsed)) +
+  geom_bar(fill = COPINGpalette9) +
+  theme_minimal() +
+  theme(plot.title = element_text(hjust = 0.5),
+        plot.subtitle = element_text(hjust = 0.5)) +
+  labs(title = "Age distribution of the GLAD/EDGI prepan cohort",
+       subtitle = paste("N =", dim(GLAD.prepan)[1]),
+       x = "",
+       y = "")
+
+```

### 2021-02-05 Paper_Histograms.Rmd
Added template code for age retro bar chart by sample

@@
 ```
+
+###Retro
+
+```{r GLAD/EDGI, NBR and RAMP age}
+
+dat.retro %>% 
+  ggplot(aes(x = age_category_collapsed, fill = Sample)) +
+  geom_bar(position = "dodge") +
+  scale_fill_manual(values = COPINGpalette4) +
+  theme_minimal() +
+  theme(plot.title = element_text(hjust = 0.5),
+        plot.subtitle = element_text(hjust = 0.5)) +
+  labs(title = "Age distribution of the retro cohorts",
+       subtitle = paste("N =", dim(dat.retro)[1]),
+       x = "Age (years)",
+       y = "") +
+  theme(legend.position = "bottom")
+
+```

### 2021-02-05 Paper_Histograms.Rmd
Merged GLAD/EDGI cohorts together to collapse age retro plot to 3 cohorts

--- 2021-02-05 Paper_Histograms.Rmd
@@
 ```
+
+###Retro
+
+```{r Merge GLAD/EDGI samples together for plot}
+
+#Merge GLAD and EDGI Samples into one sample
+
+dat.retro <- dat.retro %>% 
+  mutate(Sample_plot = 
+           case_when(
+             dat.retro$Sample == "GLAD" ~ "GLAD/EDGI",
+             dat.retro$Sample == "EDGI" ~ "GLAD/EDGI",
+             dat.retro$Sample == "NBR" ~ "NBR",
+             dat.retro$Sample == "RAMP" ~ "RAMP"
+           ))
+
+#Check that it worked
+
+dat.retro %>% 
+  group_by(Sample_plot) %>% 
+  summarise(N = n())
+
+```
+
+```{r GLAD/EDGI, NBR and RAMP age}
+
+dat.retro %>% 
+  ggplot(aes(x = age_category_collapsed, fill = Sample_plot)) +
+  geom_bar(position = "dodge") +
+  scale_fill_manual(values = COPINGpalette4) +
+  theme_minimal() +
+  theme(plot.title = element_text(hjust = 0.5),
+        plot.subtitle = element_text(hjust = 0.5)) +
+  labs(title = "Age distribution of the retro cohorts",
+       subtitle = paste("N =", dim(dat.retro)[1]),
+       x = "Age (years)",
+       y = "") +
+  theme(legend.position = "bottom")
+
+```

### 2021-02-05 Paper_Histograms.Rmd
Moved GLAD/EDGI sample collapse chunk before all the histograms are made

@@
 
+```{r Merge GLAD/EDGI samples together for plot}
+
+#Merge GLAD and EDGI Samples into one sample
+
+dat.retro <- dat.retro %>% 
+  mutate(Sample_plot = 
+           case_when(
+             dat.retro$Sample == "GLAD" ~ "GLAD/EDGI",
+             dat.retro$Sample == "EDGI" ~ "GLAD/EDGI",
+             dat.retro$Sample == "NBR" ~ "NBR",
+             dat.retro$Sample == "RAMP" ~ "RAMP"
+           ))
+
+#Check that it worked
+
+dat.retro %>% 
+  group_by(Sample_plot) %>% 
+  summarise(N = n())
+
+```
+
 ##Gender
@@
 
-```{r Merge GLAD/EDGI samples together for plot}
-
-#Merge GLAD and EDGI Samples into one sample
-
-dat.retro <- dat.retro %>% 
-  mutate(Sample_plot = 
-           case_when(
-             dat.retro$Sample == "GLAD" ~ "GLAD/EDGI",
-             dat.retro$Sample == "EDGI" ~ "GLAD/EDGI",
-             dat.retro$Sample == "NBR" ~ "NBR",
-             dat.retro$Sample == "RAMP" ~ "RAMP"
-           ))
-
-#Check that it worked
-
-dat.retro %>% 
-  group_by(Sample_plot) %>% 
-  summarise(N = n())
-
-```
-
 ```{r GLAD/EDGI, NBR and RAMP age}
@@
   geom_bar(position = "dodge") +
-  scale_fill_manual(values = COPINGpalette4) +
+  scale_fill_manual(values = COPINGpalette3) +
   theme_minimal() +

### 2021-02-05 Paper_Histograms.Rmd
Added gender distribution including all samples. Removed legend title from here and age sample plot

@@
 
+```{r Retro gender together}
+
+dat.retro %>% 
+  ggplot(aes(x = Gender, fill = Sample_plot)) +
+  geom_bar(position = "dodge") +
+  scale_fill_manual(values = COPINGpalette4) +
+  theme_minimal() +
+  theme(plot.title = element_text(hjust = 0.5),
+        plot.subtitle = element_text(hjust = 0.5)) +
+  labs(title = "Gender distribution of the retro cohorts",
+       subtitle = paste("N =", dim(dat.retro)[1]),
+       x = "",
+       y = "") +
+  theme(legend.position = "bottom") + 
+  theme(legend.title = element_blank())
+
+```
+
 ##Age
@@
        y = "") +
-  theme(legend.position = "bottom")
+  theme(legend.position = "bottom") + 
+  theme(legend.title = element_blank())
 

### 2021-02-05 Paper_Histograms.Rmd
Added GLAD/EDGI ethnicity prepan graph

@@
 ```
+
+##Ethinicity
+###Prepan
+
+```{r GLAD/EDGI ethnicity prepan}
+
+GLAD.prepan %>% 
+  ggplot(aes(x = Ethnicity_collapsed)) +
+  geom_bar(fill = COPINGpalette6) +
+  theme_minimal() +
+  theme(plot.title = element_text(hjust = 0.5),
+        plot.subtitle = element_text(hjust = 0.5)) +
+  labs(title = "Ethnic distribution of the GLAD/EDGI prepan cohort",
+       subtitle = paste("N =", dim(GLAD.prepan)[1]),
+       x = "",
+       y = "N participants") +
+  scale_x_discrete(guide = guide_axis(n.dodge = 2))
+
+```

### 2021-02-05 Paper_Histograms.Rmd
Added ethnic retro graph for the combined samples

@@
 
-```{r GLAD/EDGI, NBR and RAMP age}
+```{r GLAD/EDGI NBR and RAMP age}
 
@@
 ```
+
+###Retro
+
+```{r GLAD/EDGI NBR and RAMP ethnicity}
+
+dat.retro %>% 
+  ggplot(aes(x = Ethnicity_collapsed, fill = Sample_plot)) +
+  geom_bar(position = "dodge") +
+  scale_fill_manual(values = COPINGpalette3) +
+  theme_minimal() +
+  theme(plot.title = element_text(hjust = 0.5),
+        plot.subtitle = element_text(hjust = 0.5)) +
+  labs(title = "Ethnic distribution of the retro cohorts",
+       subtitle = paste("N =", dim(dat.retro)[1]),
+       x = "",
+       y = "N participants") +
+  scale_x_discrete(guide = guide_axis(n.dodge = 2)) +
+  theme(legend.position = "bottom") + 
+  theme(legend.title = element_blank())
+
+```

### 2021-02-05 Paper_Histograms.Rmd
Added GLAD/EDGI employment prepan graph

@@
 ```
+
+##Employment
+###Prepan
+
+```{r GLAD/EDGI employment prepan}
+
+GLAD.prepan %>% 
+  ggplot(aes(x = employment_prior_covid)) +
+  geom_bar(fill = COPINGpalette6) +
+  theme_minimal() +
+  theme(plot.title = element_text(hjust = 0.5),
+        plot.subtitle = element_text(hjust = 0.5)) +
+  labs(title = "Employment of the GLAD/EDGI prepan cohort",
+       subtitle = paste("N =", dim(GLAD.prepan)[1]),
+       x = "",
+       y = "") +
+  scale_x_discrete(guide = guide_axis(n.dodge = 2))
+
+```

### 2021-02-05 Paper_Histograms.Rmd
Added employment retro graph for combined samples

@@
 ```
+
+###Retro
+
+```{r GLAD/EDGI NBR and RAMP retro employment}
+
+dat.retro %>% 
+  ggplot(aes(x = employment_prior_covid, fill = Sample_plot)) +
+  geom_bar(position = "dodge") +
+  scale_fill_manual(values = COPINGpalette6) +
+  theme_minimal() +
+  theme(plot.title = element_text(hjust = 0.5),
+        plot.subtitle = element_text(hjust = 0.5)) +
+  labs(title = "Employment distribution of the retro cohorts",
+       subtitle = paste("N =", dim(dat.retro)[1]),
+       x = "",
+       y = "") +
+  scale_x_discrete(guide = guide_axis(n.dodge = 2)) +
+  theme(legend.position = "bottom") + 
+  theme(legend.title = element_blank())
+
+```

### 2021-02-05 Paper_Histograms.Rmd
Created table of dat.retro participants with positive diagnosis

--- 2021-02-05 Paper_Histograms.Rmd
@@
 ```
+
+###Retro
+
+```{r GLAD/EDGI NBR and RAMP retro employment}
+
+dat.retro %>% 
+  ggplot(aes(x = employment_prior_covid, fill = Sample_plot)) +
+  geom_bar(position = "dodge") +
+  scale_fill_manual(values = COPINGpalette6) +
+  theme_minimal() +
+  theme(plot.title = element_text(hjust = 0.5),
+        plot.subtitle = element_text(hjust = 0.5)) +
+  labs(title = "Employment distribution of the retro cohorts",
+       subtitle = paste("N =", dim(dat.retro)[1]),
+       x = "",
+       y = "") +
+  theme(legend.position = "bottom") + 
+  theme(legend.title = element_blank())
+
+```
+
+##Diagnoses
+
+```{r Get data frame of positive diagnoses}
+
+dat.retro_diagnosis_sums <- data.frame(apply(dat.retro[c("depressive_disorders_numeric", "anxiety_disorders_numeric", "eating_disorders_numeric", "obsessive_compulsive_disorders_numeric", "psychotic_disorders_numeric", "autism_spectrum_disorder_numeric", "mhd.attention_deficit_hyperactivity_disorder_numeric", "personality_cluster_a_numeric", "personality_cluster_b_numeric", "personality_cluster_c_numeric", "mhd.mania_hypomania_bipolar_or_manicdepression_numeric", "mhd.posttraumatic_stress_disorder_ptsd_numeric", "control_numeric")],2,table))
+
+dat.retro_diagnosis_variables <- data.frame(c("depressive disorders", "anxiety disorders", "eating disorders", "obsessive compulsive disorders", "psychotic disorders", "autism spectrum disorder", "attention deficit hyperactivity disorder", "personality cluster a", "personality cluster b", "personality cluster c", "mania hypomania bipolar or manicdepression", "posttraumatic stress disorder ptsd", "control"))
+
+dat.retro_positive_diagnosis <- data.frame(t(dat.retro_diagnosis_sums[2,]))
+
+dat.retro_diagnosis_type <- cbind(dat.retro_diagnosis_variables, dat.retro_positive_diagnosis)
+
+names(dat.retro_diagnosis_type) <- c("diagnosis", "count")
+
+```

### 2021-02-05 Paper_Histograms.Rmd
Collapsed the personality disorder clusters to one variable for the diagnosis retro plot

@@
 
+```{r Collapse personality disorder clusters}
+
+dat.retro <- dat.retro %>% 
+  mutate(personality_disorder_numeric =
+           case_when(
+             personality_cluster_a_numeric == 1 | personality_cluster_b_numeric == 1 | personality_cluster_c_numeric == 1 ~ 1,
+             personality_cluster_a_numeric == 0 & personality_cluster_b_numeric == 0 & personality_cluster_c_numeric == 0 ~ 0
+           ))
+
+#Check that it worked
+head(dat.retro$personality_cluster_a_numeric, 10)
+head(dat.retro$personality_cluster_b_numeric, 10)
+head(dat.retro$personality_cluster_c_numeric, 10)
+head(dat.retro$personality_disorder_numeric, 10)
+
+```
+
 ```{r Get data frame of positive diagnoses}
@@
 
-dat.retro_diagnosis_variables <- data.frame(c("depressive disorders", "anxiety disorders", "eating disorders", "obsessive compulsive disorders", "psychotic disorders", "autism spectrum disorder", "attention deficit hyperactivity disorder", "personality cluster a", "personality cluster b", "personality cluster c", "mania hypomania bipolar or manicdepression", "posttraumatic stress disorder ptsd", "control"))
+dat.retro_diagnosis_variables <- data.frame(c("depressive disorders", "anxiety disorders", "eating disorders", "OCDs", "psychotic disorders", "aSD", "ADHD", "personality cluster a", "personality cluster b", "personality cluster c", "mania hypomania bipolar or manicdepression", "PTSD", "control"))
 
@@
 ```
+
+```{r GLAD/EDGI NBR and RAMP diagnosis retro}
+
+dat.retro_diagnosis_type %>% 
+  mutate(diagnosis_plot = fct_reorder(diagnosis, -count)) %>% 
+  ggplot(aes(x = diagnosis_plot, y = count)) +
+  geom_bar(stat = "identity") +
+  scale_x_discrete(guide = guide_axis(n.dodge = 3)) +
+  theme_minimal() +
+  labs(x = "",
+       y = "")
+
+```

### 2021-02-06 Paper_Histograms.Rmd
Added chunks to get positive depression and anxiety diagnosis bu sample cohort

@@
 
+```{r Get MDD positive total}
+
+dat.retro_mdd_by_sample <- dat.retro %>%
+  group_by(Sample_plot) %>% 
+  select(depressive_disorders_numeric) %>% 
+  filter(depressive_disorders_numeric == 1)
+
+dat.retro_mdd_by_sample %>% 
+  group_by(Sample_plot) %>% 
+  summarise(mdd_total = n())
+
+```
+
+```{r Get anxiety positive total}
+
+dat.retro_anxi_by_sample <- dat.retro %>%
+  group_by(Sample_plot) %>% 
+  select(anxiety_disorders_numeric) %>% 
+  filter(anxiety_disorders_numeric == 1)
+
+dat.retro_anxi_by_sample <- dat.retro_anxi_by_sample %>% 
+  group_by(Sample_plot) %>% 
+  summarise(anxi_total = n())
+
+```
+
 ```{r Get data frame of positive diagnoses}
 
-dat.retro_diagnosis_sums <- data.frame(apply(dat.retro[c("depressive_disorders_numeric", "anxiety_disorders_numeric", "eating_disorders_numeric", "obsessive_compulsive_disorders_numeric", "psychotic_disorders_numeric", "autism_spectrum_disorder_numeric", "mhd.attention_deficit_hyperactivity_disorder_numeric", "personality_cluster_a_numeric", "personality_cluster_b_numeric", "personality_cluster_c_numeric", "mhd.mania_hypomania_bipolar_or_manicdepression_numeric", "mhd.posttraumatic_stress_disorder_ptsd_numeric", "control_numeric")],2,table))
+#dat.retro_diagnosis_sums <- data.frame(apply(dat.retro[c("depressive_disorders_numeric", "anxiety_disorders_numeric", "eating_disorders_numeric", "obsessive_compulsive_disorders_numeric", "psychotic_disorders_numeric", "autism_spectrum_disorder_numeric", "mhd.attention_deficit_hyperactivity_disorder_numeric", "personality_disorder_numeric", "mhd.mania_hypomania_bipolar_or_manicdepression_numeric", "mhd.posttraumatic_stress_disorder_ptsd_numeric", "control_numeric")],2,table))
 
-dat.retro_diagnosis_variables <- data.frame(c("depressive disorders", "anxiety disorders", "eating disorders", "OCDs", "psychotic disorders", "aSD", "ADHD", "personality cluster a", "personality cluster b", "personality cluster c", "mania hypomania bipolar or manicdepression", "PTSD", "control"))
+#dat.retro_diagnosis_variables <- data.frame(c("depressive disorders", "anxiety disorders", "eating disorders", "OCDs", "psychotic disorders", "ASD", "ADHD", "personality disorders", "bipolar disorder", "PTSD", "control"))
 
-dat.retro_positive_diagnosis <- data.frame(t(dat.retro_diagnosis_sums[2,]))
+#dat.retro_positive_diagnosis <- data.frame(t(dat.retro_diagnosis_sums[2,]))
 
-dat.retro_diagnosis_type <- cbind(dat.retro_diagnosis_variables, dat.retro_positive_diagnosis)
+#dat.retro_diagnosis_type <- cbind(dat.retro_diagnosis_variables, dat.retro_positive_diagnosis)
 
-names(dat.retro_diagnosis_type) <- c("diagnosis", "count")
+#names(dat.retro_diagnosis_type) <- c("diagnosis", "count")
 
@@
 
+head(diamonds)
+
 ```

### 2021-02-06 Paper_Histograms.Rmd
Joining the positive diagnosis for depression and anxiety by sample

@@
 
-dat.retro_mdd_by_sample %>% 
+dat.retro_mdd_by_sample <- dat.retro_mdd_by_sample %>% 
   group_by(Sample_plot) %>% 
@@
   summarise(anxi_total = n())
+
+```
+
+```{r Merge the positive sample/diagnosis tibbles}
+
+dat.retro_positive_diagnosis_by_sample <- left_join(dat.retro_mdd_by_sample,
+                                                    dat.retro_anxi_by_sample,
+                                                    by = "Sample_plot")
+
+head(dat.retro_positive_diagnosis_by_sample)
 

### 2021-02-06 Paper_Histograms.Rmd
Tidy the left joined tibble with the positive diagnosis by sample data
Added template code to plot the retro diagnosis by sample

@@
   geom_bar(position = "dodge") +
-  scale_fill_manual(values = COPINGpalette6) +
+  scale_fill_manual(values = COPINGpalette3) +
   theme_minimal() +
@@
   group_by(Sample_plot) %>% 
-  summarise(mdd_total = n())
+  summarise(depressive_disorders = n())
 
@@
   group_by(Sample_plot) %>% 
-  summarise(anxi_total = n())
+  summarise(anxiety_disorders = n())
 
@@
 head(dat.retro_positive_diagnosis_by_sample)
+
+```
+
+```{r Re-organise the positive diagnosis by sample tib}
+
+dat.retro_positive_diagnosis_by_sample <- dat.retro_positive_diagnosis_by_sample %>% 
+  gather('depressive_disorders', 'anxiety_disorders', key = "Diagnosis", value = positive_n)
+
+```
+
+```{r GLAD/EDGI NBR and RAMP retro diagnosis}
+
+dat.retro_positive_diagnosis_by_sample %>% 
+  ggplot(aes(x = reorder(Diagnosis, -positive_n), y = positive_n, fill = Sample_plot)) +
+  geom_bar(stat = "identity") +
+  scale_fill_manual(values = COPINGpalette3) +
+  theme_minimal() +
+  theme(plot.title = element_text(hjust = 0.5),
+        plot.subtitle = element_text(hjust = 0.5)) +
+  labs(title = "Retro Diagnoses of the GLAD/EDGI, NBR and RAMP cohorts",
+       x = "",
+       y = "") +
+  scale_x_discrete(guide = guide_axis(n.dodge = 2)) +
+  theme(legend.position = "bottom") + 
+  theme(legend.title = element_blank())
 

### 2021-02-06 Paper_Histograms.Rmd
Removed previous chunks unsuccessfully trying to plot the retro diagnosis by sample

@@
 ```
-
-```{r Get data frame of positive diagnoses}
-
-#dat.retro_diagnosis_sums <- data.frame(apply(dat.retro[c("depressive_disorders_numeric", "anxiety_disorders_numeric", "eating_disorders_numeric", "obsessive_compulsive_disorders_numeric", "psychotic_disorders_numeric", "autism_spectrum_disorder_numeric", "mhd.attention_deficit_hyperactivity_disorder_numeric", "personality_disorder_numeric", "mhd.mania_hypomania_bipolar_or_manicdepression_numeric", "mhd.posttraumatic_stress_disorder_ptsd_numeric", "control_numeric")],2,table))
-
-#dat.retro_diagnosis_variables <- data.frame(c("depressive disorders", "anxiety disorders", "eating disorders", "OCDs", "psychotic disorders", "ASD", "ADHD", "personality disorders", "bipolar disorder", "PTSD", "control"))
-
-#dat.retro_positive_diagnosis <- data.frame(t(dat.retro_diagnosis_sums[2,]))
-
-#dat.retro_diagnosis_type <- cbind(dat.retro_diagnosis_variables, dat.retro_positive_diagnosis)
-
-#names(dat.retro_diagnosis_type) <- c("diagnosis", "count")
-
-```
-
-```{r GLAD/EDGI NBR and RAMP diagnosis retro}
-
-dat.retro_diagnosis_type %>% 
-  mutate(diagnosis_plot = fct_reorder(diagnosis, -count)) %>% 
-  ggplot(aes(x = diagnosis_plot, y = count)) +
-  geom_bar(stat = "identity") +
-  scale_x_discrete(guide = guide_axis(n.dodge = 3)) +
-  theme_minimal() +
-  labs(x = "",
-       y = "")
-
-head(diamonds)
-
-```

### 2021-02-06 Paper_Histograms.Rmd
Added eating disorder positive diagnosis by sample chunk

@@
 
-```{r Get MDD positive total}
+```{r Get MDD positive by sample}
 
@@
   group_by(Sample_plot) %>% 
-  summarise(depressive_disorders = n())
+  summarise("Depressive disorders" = n())
 
@@
 
-```{r Get anxiety positive total}
+```{r Get anxiety positive by sample}
 
@@
   group_by(Sample_plot) %>% 
-  summarise(anxiety_disorders = n())
+  summarise("Anxiety disorders" = n())
+
+```
+
+```{r Get eating disorder positive by sample}
+
+dat.retro_ED_by_sample <- dat.retro %>%
+  group_by(Sample_plot) %>% 
+  select(eating_disorders_numeric) %>% 
+  filter(eating_disorders_numeric == 1)
+
+dat.retro_ED_by_sample <- dat.retro_ED_by_sample %>% 
+  group_by(Sample_plot) %>% 
+  summarise("Eating disorders" = n())
 
@@
 
+###Retro
+
 ```{r GLAD/EDGI NBR and RAMP retro diagnosis}

### 2021-02-06 Paper_Histograms.Rmd
Added positive OCDs by sample chunk
Added positive psychotic disorders by sample chunk

@@
 
+```{r Get OCDs positive by sample}
+
+dat.retro_OCD_by_sample <- dat.retro %>%
+  group_by(Sample_plot) %>% 
+  select(obsessive_compulsive_disorders_numeric) %>% 
+  filter(obsessive_compulsive_disorders_numeric == 1)
+
+dat.retro_OCD_by_sample <- dat.retro_OCD_by_sample %>% 
+  group_by(Sample_plot) %>% 
+  summarise("OCDs" = n())
+
+```
+
+```{r Get psychotic disorder positive by sample}
+
+dat.retro_psychosis_by_sample <- dat.retro %>%
+  group_by(Sample_plot) %>% 
+  select(psychotic_disorders_numeric) %>% 
+  filter(psychotic_disorders_numeric == 1)
+
+dat.retro_psychosis_by_sample <- dat.retro_psychosis_by_sample %>% 
+  group_by(Sample_plot) %>% 
+  summarise("Psychotic disorders" = n())
+
+```
+
 ```{r Merge the positive sample/diagnosis tibbles}

### 2021-02-06 Paper_Histograms.Rmd
Added ASD positive diagnosis by sample chunk
Added ADHD positive diagnosis by sample chunk

@@
 
+```{r Get ASD positive by sample}
+
+dat.retro_ASD_by_sample <- dat.retro %>%
+  group_by(Sample_plot) %>% 
+  select(autism_spectrum_disorder_numeric) %>% 
+  filter(autism_spectrum_disorder_numeric == 1)
+
+dat.retro_ASD_by_sample <- dat.retro_ASD_by_sample %>% 
+  group_by(Sample_plot) %>% 
+  summarise("ASD" = n())
+
+```
+
+```{r Get ADHD positive by sample}
+
+dat.retro_ADHD_by_sample <- dat.retro %>%
+  group_by(Sample_plot) %>% 
+  select(mhd.attention_deficit_hyperactivity_disorder_numeric) %>% 
+  filter(mhd.attention_deficit_hyperactivity_disorder_numeric == 1)
+
+dat.retro_ADHD_by_sample <- dat.retro_ADHD_by_sample %>% 
+  group_by(Sample_plot) %>% 
+  summarise("ADHD" = n())
+
+```
+
 ```{r Merge the positive sample/diagnosis tibbles}

### 2021-02-06 Paper_Histograms.Rmd
Added personality disorder positive diagnosis by sample chunk

@@
 
+```{r Get personality disorders positive by sample}
+
+dat.retro_PD_by_sample <- dat.retro %>%
+  group_by(Sample_plot) %>% 
+  select(personality_disorder_numeric) %>% 
+  filter(personality_disorder_numeric == 1)
+
+dat.retro_PD_by_sample <- dat.retro_PD_by_sample %>% 
+  group_by(Sample_plot) %>% 
+  summarise("Personality disorders" = n())
+
+```
+
 ```{r Merge the positive sample/diagnosis tibbles}

### 2021-02-06 Paper_Histograms.Rmd
Added biploar disorders positive diagnosis by sample chunk

@@
 
+```{r Get Bipolar disorders positive by sample}
+
+dat.retro_BD_by_sample <- dat.retro %>%
+  group_by(Sample_plot) %>% 
+  select(mhd.mania_hypomania_bipolar_or_manicdepression_numeric) %>% 
+  filter(mhd.mania_hypomania_bipolar_or_manicdepression_numeric == 1)
+
+dat.retro_BD_by_sample <- dat.retro_BD_by_sample %>% 
+  group_by(Sample_plot) %>% 
+  summarise("Bipolar disorders" = n())
+
+```
+
 ```{r Merge the positive sample/diagnosis tibbles}

### 2021-02-06 Paper_Histograms.Rmd
Added PTSD positive diagnosis by sample chunk
Added control positive by sample chunk

@@
 
+```{r Get PTSD positive by sample}
+
+dat.retro_PTSD_by_sample <- dat.retro %>%
+  group_by(Sample_plot) %>% 
+  select(mhd.posttraumatic_stress_disorder_ptsd_numeric) %>% 
+  filter(mhd.posttraumatic_stress_disorder_ptsd_numeric == 1)
+
+dat.retro_PTSD_by_sample <- dat.retro_PTSD_by_sample %>% 
+  group_by(Sample_plot) %>% 
+  summarise("PTSD" = n())
+
+```
+
+```{r Get control positive by sample}
+
+dat.retro_control_by_sample <- dat.retro %>%
+  group_by(Sample_plot) %>% 
+  select(control_numeric) %>% 
+  filter(control_numeric == 1)
+
+dat.retro_control_by_sample <- dat.retro_control_by_sample %>% 
+  group_by(Sample_plot) %>% 
+  summarise("No diagnosis" = n())
+
+```
+
 ```{r Merge the positive sample/diagnosis tibbles}

### 2021-02-06 Paper_Histograms.Rmd
Merged all the positive diagnosis/positive control tibbles together

@@
 
+dat.retro_positive_diagnosis_by_sample <- left_join(dat.retro_positive_diagnosis_by_sample,
+                                                    dat.retro_ED_by_sample,
+                                                    by = "Sample_plot")
+
+dat.retro_positive_diagnosis_by_sample <- left_join(dat.retro_positive_diagnosis_by_sample,
+                                                    dat.retro_OCD_by_sample,
+                                                    by = "Sample_plot")
+
+dat.retro_positive_diagnosis_by_sample <- left_join(dat.retro_positive_diagnosis_by_sample,
+                                                    dat.retro_psychosis_by_sample,
+                                                    by = "Sample_plot")
+
+dat.retro_positive_diagnosis_by_sample <- left_join(dat.retro_positive_diagnosis_by_sample,
+                                                    dat.retro_ASD_by_sample,
+                                                    by = "Sample_plot")
+
+dat.retro_positive_diagnosis_by_sample <- left_join(dat.retro_positive_diagnosis_by_sample,
+                                                    dat.retro_ADHD_by_sample,
+                                                    by = "Sample_plot")
+
+dat.retro_positive_diagnosis_by_sample <- left_join(dat.retro_positive_diagnosis_by_sample,
+                                                    dat.retro_PD_by_sample,
+                                                    by = "Sample_plot")
+
+dat.retro_positive_diagnosis_by_sample <- left_join(dat.retro_positive_diagnosis_by_sample,
+                                                    dat.retro_BD_by_sample,
+                                                    by = "Sample_plot")
+
+dat.retro_positive_diagnosis_by_sample <- left_join(dat.retro_positive_diagnosis_by_sample,
+                                                    dat.retro_PTSD_by_sample,
+                                                    by = "Sample_plot")
+
+dat.retro_positive_diagnosis_by_sample <- left_join(dat.retro_positive_diagnosis_by_sample,
+                                                    dat.retro_control_by_sample,
+                                                    by = "Sample_plot")
+
 head(dat.retro_positive_diagnosis_by_sample)

### 2021-02-06 Paper_Histograms.Rmd
Tidied all the diagnoses into one column and their corresponding positive diagnosis into another by sample

@@
 dat.retro_positive_diagnosis_by_sample <- dat.retro_positive_diagnosis_by_sample %>% 
-  gather('depressive_disorders', 'anxiety_disorders', key = "Diagnosis", value = positive_n)
+  gather('Depressive disorders', 'Anxiety disorders', 'Eating disorders', 'OCDs', 'Psychotic disorders', 'ASD', 'ADHD', 'Personality disorders', 'Bipolar disorders', 'PTSD', 'No diagnosis', key = "Diagnosis", value = positive_n)
+
+head(dat.retro_positive_diagnosis_by_sample, 9)
 

### 2021-02-06 Paper_Histograms.Rmd
Added retro positive diagnosis by sample graphs, with and without angled x axis text

@@
 ###Retro
+####Style 1
+
+```{r GLAD/EDGI NBR and RAMP retro diagnosis}
+
+dat.retro_positive_diagnosis_by_sample %>% 
+  ggplot(aes(x = reorder(Diagnosis, -positive_n), y = positive_n, fill = Sample_plot)) +
+  geom_bar(stat = "identity") +
+  scale_fill_manual(values = COPINGpalette3) +
+  theme_minimal() +
+  theme(plot.title = element_text(hjust = 0.5),
+        plot.subtitle = element_text(hjust = 0.5)) +
+  labs(title = "Retro Diagnoses of the GLAD/EDGI, NBR and RAMP cohorts",
+       x = "",
+       y = "") +
+  theme(axis.text.x = element_text(angle = 70, vjust = 0.5)) +
+  theme(legend.position = "top") + 
+  theme(legend.title = element_blank())
+
+```
+
+####Style 2
 
@@
   scale_x_discrete(guide = guide_axis(n.dodge = 2)) +
-  theme(legend.position = "bottom") + 
+  theme(legend.position = "top") + 
   theme(legend.title = element_blank())

### 2021-02-06 Paper_Histograms.Rmd
Edited the format of the mental health diagnosis by sampple graph

@@
   labs(title = "Gender distribution of the retro cohorts",
-       subtitle = paste("N =", dim(dat.retro)[1]),
        x = "",
@@
   labs(title = "Age distribution of the retro cohorts",
-       subtitle = paste("N =", dim(dat.retro)[1]),
-       x = "Age (years)",
+       x = "",
        y = "") +
@@
   labs(title = "Ethnic distribution of the retro cohorts",
-       subtitle = paste("N =", dim(dat.retro)[1]),
        x = "",
-       y = "N participants") +
+       y = "") +
   scale_x_discrete(guide = guide_axis(n.dodge = 2)) +
@@
        x = "",
-       y = "") +
-  scale_x_discrete(guide = guide_axis(n.dodge = 2))
+       y = "")
 
@@
   labs(title = "Employment distribution of the retro cohorts",
-       subtitle = paste("N =", dim(dat.retro)[1]),
        x = "",
@@
         plot.subtitle = element_text(hjust = 0.5)) +
-  labs(title = "Retro Diagnoses of the GLAD/EDGI, NBR and RAMP cohorts",
-       x = "",
+  labs(x = "",
        y = "") +
@@
   theme(legend.position = "top") + 
-  theme(legend.title = element_blank())
+  theme(legend.title = element_blank()) +
+  ylim(0, 20000)
 

### 2021-02-06 Paper_Histograms.Rmd
Changed y axis limit for positive diagnosis by sample style 1 graph

@@
        y = "") +
+  ylim(0, 20000) +
   theme(axis.text.x = element_text(angle = 70, vjust = 0.5)) +

### 2021-02-06 Paper_Histograms.Rmd
Added chunk to get GLAD/EDGI prepan positive diagnosis for mdd

@@
 ```
+###Prepan
+
+```{r Get anxiety positive for GLAD/EDGI}
+
+GLAD.prepan_mdd_positive <- GLAD.prepan %>%
+  group_by(Sample) %>% 
+  select(depressive_disorders_numeric) %>% 
+  filter(depressive_disorders_numeric == 1)
+
+GLAD.prepan_mdd_positive <- GLAD.prepan_mdd_positive %>% 
+  group_by(Sample) %>% 
+  summarise("Depressive disorders" = n())
+
+```
+
+###Retro
 
@@
 
-###Retro
-####Style 1
+#### Plot Style 1
 
@@
 
-####Style 2
+####Plot Style 2
 

### 2021-02-06 Paper_Histograms.Rmd
Added chunk to get positive anxiety diagnosis for GLAD/EDGI prepan

--- 2021-02-06 Paper_Histograms.Rmd
@@
 ```
+###Prepan
+
+```{r Get depression positive for GLAD/EDGI}
+
+GLAD.prepan_mdd_positive <- GLAD.prepan %>%
+  select(depressive_disorders_numeric) %>% 
+  filter(depressive_disorders_numeric == 1)
+
+GLAD.prepan_mdd_positive <- GLAD.prepan_mdd_positive %>% 
+  summarise("Depressive disorders" = n())
+
+```
+
+```{r Get anxiety positive for GLAD/EDGI}
+
+GLAD.prepan_anxi_positive <- GLAD.prepan %>%
+  select(anxiety_disorders_numeric) %>% 
+  filter(anxiety_disorders_numeric == 1)
+
+GLAD.prepan_anxi_positive <- GLAD.prepan_anxi_positive %>% 
+  summarise("Anxiety disorders" = n())
+
+```
+
+###Retro
 

### 2021-02-06 Paper_Histograms.Rmd
Added chunk to get positive eating disorders for GLAD/EDGI prepan
Added chunk to get positive/negative OCDs diagnosis for GLAD/EDGI prepan

@@
 
+```{r Get eating disorders positive for GLAD/EDGI}
+
+GLAD.prepan_ED_positive <- GLAD.prepan %>%
+  select(eating_disorders_numeric) %>% 
+  filter(eating_disorders_numeric == 1)
+
+GLAD.prepan_ED_positive <- GLAD.prepan_ED_positive %>% 
+  summarise("Eating disorders" = n())
+
+```
+
+```{r Get anxiety positive for GLAD/EDGI}
+
+GLAD.prepan_OCD_positive <- GLAD.prepan %>%
+  select(obsessive_compulsive_disorders_numeric) %>% 
+  filter(obsessive_compulsive_disorders_numeric == 1)
+
+GLAD.prepan_OCD_positive <- GLAD.prepan_OCD_positive %>% 
+  summarise("OCDs" = n())
+
+```
+
 ###Retro

### 2021-02-06 Paper_Histograms.Rmd
Added chunk to get positive/negative psychosis diagnosis for GLAD/EDGI prepan

@@
 
-```{r Get anxiety positive for GLAD/EDGI}
+```{r Get OCDs positive for GLAD/EDGI}
 
@@
   summarise("OCDs" = n())
+
+```
+
+```{r Get psychosis positive for GLAD/EDGI}
+
+GLAD.prepan_psychosis_positive <- GLAD.prepan %>%
+  select(psychotic_disorders_numeric) %>% 
+  filter(psychotic_disorders_numeric == 1)
+
+GLAD.prepan_psychosis_positive <- GLAD.prepan_psychosis_positive %>% 
+  summarise("Psychotic disorders" = n())
 

### 2021-02-06 Paper_Histograms.Rmd
Added chunk to get positive/negative ASD diagnosis for GLAD/EDGI prepan
Added chunk to get positive ADHD diagnosis for GLAD/EDGI prepan

@@
 
+```{r Get ASD positive for GLAD/EDGI}
+
+GLAD.prepan_ASD_positive <- GLAD.prepan %>%
+  select(autism_spectrum_disorder_numeric) %>% 
+  filter(autism_spectrum_disorder_numeric == 1)
+
+GLAD.prepan_ASD_positive <- GLAD.prepan_ASD_positive %>% 
+  summarise("ASD" = n())
+
+```
+
+```{r Get ADHD positive for GLAD/EDGI}
+
+GLAD.prepan_ADHD_positive <- GLAD.prepan %>%
+  select(mhd.attention_deficit_hyperactivity_disorder_numeric) %>% 
+  filter(mhd.attention_deficit_hyperactivity_disorder_numeric == 1)
+
+GLAD.prepan_ADHD_positive <- GLAD.prepan_ADHD_positive %>% 
+  summarise("ADHD" = n())
+
+```
+
 ###Retro

### 2021-02-06 Paper_Histograms.Rmd
Added chunk to collapse personality clusters into one variable for GLAD/EDGI prepan

@@
 
-```{r Collapse personality disorder clusters}
+```{r Collapse personality disorder clusters for prepan data}
+
+GLAD.prepan <- GLAD.prepan %>% 
+  mutate(personality_disorder_numeric =
+           case_when(
+             personality_cluster_a_numeric == 1 | personality_cluster_b_numeric == 1 | personality_cluster_c_numeric == 1 ~ 1,
+             personality_cluster_a_numeric == 0 & personality_cluster_b_numeric == 0 & personality_cluster_c_numeric == 0 ~ 0
+           ))
+
+#Check that it worked
+head(GLAD.prepan$personality_cluster_a_numeric, 15)
+head(GLAD.prepan$personality_cluster_b_numeric, 15)
+head(GLAD.prepan$personality_cluster_c_numeric, 15)
+head(GLAD.prepan$personality_disorder_numeric, 15)
+
+```
+
+```{r Collapse personality disorder clusters for retro data}
 
@@
 #Check that it worked
-head(dat.retro$personality_cluster_a_numeric, 10)
-head(dat.retro$personality_cluster_b_numeric, 10)
-head(dat.retro$personality_cluster_c_numeric, 10)
-head(dat.retro$personality_disorder_numeric, 10)
+head(dat.retro$personality_cluster_a_numeric, 15)
+head(dat.retro$personality_cluster_b_numeric, 15)
+head(dat.retro$personality_cluster_c_numeric, 15)
+head(dat.retro$personality_disorder_numeric, 15)
 
@@
   summarise("ADHD" = n())
+
+```
+
+```{r Get PD positive for GLAD/EDGI}
+
+GLAD.prepan_PD_positive <- GLAD.prepan %>%
+  select(personality) %>% 
+  filter(psychotic_disorders_numeric == 1)
+
+GLAD.prepan_psychosis_positive <- GLAD.prepan_psychosis_positive %>% 
+  summarise("Psychotic disorders" = n())
 

### 2021-02-06 Paper_Histograms.Rmd
Added chunk to get positive PD diagnosis for GLAD/EDGI prepan

@@
 GLAD.prepan_PD_positive <- GLAD.prepan %>%
-  select(personality) %>% 
-  filter(psychotic_disorders_numeric == 1)
+  select(personality_disorder_numeric) %>% 
+  filter(personality_disorder_numeric == 1)
 
-GLAD.prepan_psychosis_positive <- GLAD.prepan_psychosis_positive %>% 
-  summarise("Psychotic disorders" = n())
+GLAD.prepan_PD_positive <- GLAD.prepan_PD_positive %>% 
+  summarise("Personality disorders" = n())
 

### 2021-02-06 Paper_Histograms.Rmd
Added chunk to get positive bipolar disorders diagnosis for GLAD/EDGI prepan

@@
 
-```{r Get PD positive for GLAD/EDGI}
+```{r Get Personality Disorders positive for GLAD/EDGI}
 
@@
   summarise("Personality disorders" = n())
+
+```
+
+```{r Get Bipolar Disorders positive for GLAD/EDGI}
+
+GLAD.prepan_BD_positive <- GLAD.prepan %>%
+  select(mhd.mania_hypomania_bipolar_or_manicdepression_numeric) %>% 
+  filter(mhd.mania_hypomania_bipolar_or_manicdepression_numeric == 1)
+
+GLAD.prepan_BD_positive <- GLAD.prepan_BD_positive %>% 
+  summarise("Bipolar disorders" = n())
 

### 2021-02-06 Paper_Histograms.Rmd
Added chunk to get positive PTSD diagnosis for GLAD/EDGI prepan
Added chunk to get positive no diagnosis for GLAD/EDGI prepan

@@
 
+```{r Get PTSD positive for GLAD/EDGI}
+
+GLAD.prepan_PTSD_positive <- GLAD.prepan %>%
+  select(mhd.posttraumatic_stress_disorder_ptsd_numeric) %>% 
+  filter(mhd.posttraumatic_stress_disorder_ptsd_numeric == 1)
+
+GLAD.prepan_PTSD_positive <- GLAD.prepan_PTSD_positive %>% 
+  summarise("PTSD" = n())
+
+```
+
+```{r Get control positive for GLAD/EDGI}
+
+GLAD.prepan_control_positive <- GLAD.prepan %>%
+  select(control_numeric) %>% 
+  filter(control_numeric == 1)
+
+GLAD.prepan_control_positive <- GLAD.prepan_control_positive %>% 
+  summarise("No diagnosis" = n())
+
+```
+
 ###Retro

### 2021-02-06 Paper_Histograms.Rmd
Added chunk to test combining the positive depression and anxiety positive diagnoses for GLAD/EDGI prepan
cbinded all the positive diagnoses for GLAD/EDGI prepan

@@
 
+```{r}
+
+GLAD.prepan_positive_diagnosis_GLADEDGI <- GLAD.prepan_mdd_positive %>% 
+  cbind(GLAD.prepan_anxi_positive,
+        GLAD.prepan_ED_positive,
+        GLAD.prepan_OCD_positive,
+        GLAD.prepan_psychosis_positive,
+        GLAD.prepan_ASD_positive,
+        GLAD.prepan_ADHD_positive,
+        GLAD.prepan_PD_positive,
+        GLAD.prepan_BD_positive,
+        GLAD.prepan_PTSD_positive,
+        GLAD.prepan_control_positive)
+
+head(GLAD.prepan_positive_diagnosis_GLADEDGI)
+
+```
+
 ###Retro

### 2021-02-06 Paper_Histograms.Rmd
Re-organised the positive diagnoses in GLAD/EDGI prepan into diagnosis and count columns

@@
 ###Prepan
+####Get positive diagnoses
 
@@
 
-```{r}
+####Merge and clean the data
+
+```{r Combine the positive diagnoses for GLAD/EDGI prepan}
 
@@
 head(GLAD.prepan_positive_diagnosis_GLADEDGI)
+
+```
+
+```{r Re-organise the positive diagnosis GLAD/EDGI prepan}
+
+GLAD.prepan_positive_diagnosis_GLADEDGI <- GLAD.prepan_positive_diagnosis_GLADEDGI %>% 
+  gather('Depressive disorders', 'Anxiety disorders', 'Eating disorders', 'OCDs', 'Psychotic disorders', 'ASD', 'ADHD', 'Personality disorders', 'Bipolar disorders', 'PTSD', 'No diagnosis', key = "Diagnosis", value = positive_n)
+
+head(GLAD.prepan_positive_diagnosis_GLADEDGI, 9)
 

### 2021-02-06 Paper_Histograms.Rmd
Plotted positive diagnosis/control for GLAD/EDGI prepan

@@
                     "3B47DA")
+
+COPINGpalette11 <- c("#78D9C5",
+                    "#F5BE5E",
+                    "#EEB6E9",
+                    "#DBDB73", 
+                    "#FFED98",
+                    "#BFD2EB", 
+                    "#808080",
+                    "#cccccc",
+                    "3B47DA",
+                    "#b7dee8",
+                    "#F567F3")
 
@@
 
+#####Plot positive diagnosis prepan
+
+```{r Plot GLAD/EDGI prepan positive diagnosis}
+
+GLAD.prepan_positive_diagnosis_GLADEDGI %>% 
+  ggplot(aes(x = reorder(Diagnosis, -positive_n), y = positive_n)) +
+  geom_bar(stat = "identity", fill = COPINGpalette11) + 
+  scale_fill_manual(values = COPINGpalette11) +
+  theme_minimal() +
+  theme(plot.title = element_text(hjust = 0.5),
+        plot.subtitle = element_text(hjust = 0.5)) +
+  labs(title = "Mental health diagnoses of the GLAD/EDGI prepan cohort",
+       subtitle = paste("N =", dim(GLAD.retro)[1]),
+         x = "",
+       y = "") +
+  scale_x_discrete(guide = guide_axis(n.dodge = 2)) +
+  theme(legend.position = "top") + 
+  theme(legend.title = element_blank())
+
+```
+
 ###Retro
+####Get positive diagnoses
 
@@
 ```
+####Merge and clean the data
 
@@
 
-#### Plot Style 1
+#####Plot Style 1
 
@@
 
-####Plot Style 2
+#####Plot Style 2
 

### 2021-02-06 Paper_Histograms.Rmd
Collaped gender plots to 3 levels instead of 4

@@
 GLAD.prepan %>%
-  ggplot(aes(x = Gender)) +
-  geom_bar(fill = COPINGpalette4) +
+  ggplot(aes(x = Gender_collapsed)) +
+  geom_bar(fill = COPINGpalette3) +
   theme_minimal() +
@@
 GLAD.retro %>%
-  ggplot(aes(x = Gender)) +
-  geom_bar(fill = COPINGpalette4) +
+  ggplot(aes(x = Gender_collapsed)) +
+  geom_bar(fill = COPINGpalette3) +
   theme_minimal() +
@@
 NBR.retro %>%
-  ggplot(aes(x = Gender)) +
-  geom_bar(fill = COPINGpalette4) +
+  ggplot(aes(x = Gender_collapsed)) +
+  geom_bar(fill = COPINGpalette3) +
   theme_minimal() +
@@
 RAMP.retro %>%
-  ggplot(aes(x = Gender)) +
-  geom_bar(fill = COPINGpalette4) +
+  ggplot(aes(x = Gender_collapsed)) +
+  geom_bar(fill = COPINGpalette3) +
   theme_minimal() +
@@
 dat.retro %>% 
-  ggplot(aes(x = Gender, fill = Sample_plot)) +
+  ggplot(aes(x = Gender_collapsed, fill = Sample_plot)) +
   geom_bar(position = "dodge") +
-  scale_fill_manual(values = COPINGpalette4) +
+  scale_fill_manual(values = COPINGpalette3) +
   theme_minimal() +

### 2021-02-06 Paper_Histograms.Rmd
Added chunk to get gender category distribution for each sample
Added pie chart for GLAD/EDGI, NBR and RAMP retro gender

@@
   theme(legend.title = element_blank())
+
+```
+
+```{r Prep gender retro pie chart}
+
+dat.retro_gender_pie <- dat.retro %>% 
+  group_by(Sample_plot, Gender_collapsed) %>% 
+  summarise(n = n()) %>% 
+  mutate(percent = 
+           round(n / sum(n) *  100, 1))
+
+```
+
+```{r Gender retro pie chart by sample}
+
+dat.retro_gender_pie %>% 
+  ggplot(aes(x = "", y = percent, fill = Gender_collapsed)) +
+  geom_col(stat = "identity") +
+  coord_polar("y",start=0) +
+  theme_void() +
+  scale_fill_manual(values =  COPINGpalette3) +
+  facet_wrap(~ Sample_plot, nrow = 1) +
+  theme(legend.position = "top",
+        legend.title = element_blank()) +
+  ggrepel::geom_label_repel(aes(label = paste0(percent, "%")),
+            position = position_stack(vjust = 0.6),
+            show.legend = FALSE)
 

### 2021-02-06 Paper_Histograms.Rmd
Added chunk to prep ethnicity retro pie chart
Added pie chart for GLAD/EDGI, NBR and RAMP retro ethnicity

@@
 
+####Gender retro pie chart
+
 ```{r Prep gender retro pie chart}
@@
   theme(legend.title = element_blank())
+
+```
+
+####Ethnicity retro pie chart
+
+```{r Prep ethnicity retro pie chart}
+
+dat.retro_ethnicity_pie <- dat.retro %>% 
+  group_by(Sample_plot, Ethnicity_collapsed) %>% 
+  summarise(n = n()) %>% 
+  drop_na() %>% 
+  mutate(percent = 
+           round(n / sum(n) *  100, 1))
+
+```
+
+```{r Gender retro pie chart by sample}
+
+dat.retro_ethnicity_pie %>% 
+  ggplot(aes(x = "", y = percent, fill = Ethnicity_collapsed)) +
+  geom_col(stat = "identity") +
+  coord_polar("y",start=0) +
+  theme_void() +
+  scale_fill_manual(values =  COPINGpalette5) +
+  facet_wrap(~ Sample_plot, nrow = 1) +
+  theme(legend.position = "top",
+        legend.title = element_blank()) +
+  ggrepel::geom_label_repel(aes(label = paste0(percent, "%")),
+            position = position_stack(vjust = 0.5),
+            show.legend = FALSE)
 

### 2021-02-06 Paper_Histograms.Rmd
Added chunk to prepare retro employment pie chart
Added GLAD/EDGI, NBR and RAMP retro employment pie chart

@@
 
+####Employment retro pie charts
+
+```{r Prep ethnicity retro pie chart}
+
+dat.retro_employ_pie <- dat.retro %>% 
+  group_by(Sample_plot, employment_prior_covid) %>% 
+  summarise(n = n()) %>% 
+  drop_na() %>% 
+  mutate(percent = 
+           round(n / sum(n) *  100, 1))
+
+```
+
+```{r Employment retro pie chart by sample}
+
+dat.retro_employ_pie %>% 
+  ggplot(aes(x = "", y = percent, fill = employment_prior_covid)) +
+  geom_col(stat = "identity") +
+  coord_polar("y",start=0) +
+  theme_void() +
+  scale_fill_manual(values =  COPINGpalette5) +
+  facet_wrap(~ Sample_plot, nrow = 1) +
+  theme(legend.position = "top",
+        legend.title = element_blank()) +
+  ggrepel::geom_label_repel(aes(label = paste0(percent, "%")),
+            position = position_stack(vjust = 0.6),
+            show.legend = FALSE)
+
+```
+
 ##Diagnoses

### 2021-02-08 Paper_Histograms.Rmd
Added new ethnicity labels to prepan ethnicity graph

@@
 
+ethnicity_levels <- c("White", "Asian or Asian British", "Black or Black British",
+                      "Mixed or multiple ethnic origin", "Other")
+
 GLAD.prepan %>% 
@@
        y = "N participants") +
-  scale_x_discrete(guide = guide_axis(n.dodge = 2))
+  scale_x_discrete(guide = guide_axis(n.dodge = 2),
+                   labels = ethnicity_levels)
 

### 2021-02-08 Paper_Histograms.Rmd
Changed ethnicity labels for retro histogram and pie chart

@@
        y = "") +
-  scale_x_discrete(guide = guide_axis(n.dodge = 2)) +
+  scale_x_discrete(guide = guide_axis(n.dodge = 2),
+                   labels = ethnicity_levels) +
   theme(legend.position = "bottom") + 
@@
 ```{r Gender retro pie chart by sample}
+
+dat.retro_ethnicity_pie <- dat.retro_ethnicity_pie %>% 
+  mutate(Ethnicity_collapsed = 
+           fct_recode(Ethnicity_collapsed,
+             "White" = "European",
+             "Asian or Asian British" = "Asian or Asian British",
+             "Black or Black British" = "African or African British",
+             "Mixed or multiple ethnic origins" = "Mixed or multiple ethnic origins",
+             "Other" = "Other"
+           ))
 

### 2021-02-08 Paper_Histograms.Rmd
Reformatted the GLAD/EDGI, NBR and RAMP ethnicity retro graph

@@
   geom_bar(fill = COPINGpalette6) +
-  theme_minimal() +
+  theme_void() +
   theme(plot.title = element_text(hjust = 0.5),
@@
 
-dat.retro %>% 
-  ggplot(aes(x = Ethnicity_collapsed, fill = Sample_plot)) +
-  geom_bar(position = "dodge") +
+dat.retro_ethnicity_plot <- dat.retro %>% 
+  group_by(Sample_plot, Ethnicity_collapsed) %>% 
+  summarise(n = n()) %>% 
+  drop_na()
+
+dat.retro_ethnicity_plot %>% 
+  ggplot(aes(x = Ethnicity_collapsed, y = n, fill = Sample_plot)) +
+  geom_bar(stat = "identity", position = "dodge") +
   scale_fill_manual(values = COPINGpalette3) +
-  theme_minimal() +
+  theme_classic() +
   theme(plot.title = element_text(hjust = 0.5),
         plot.subtitle = element_text(hjust = 0.5)) +
-  labs(title = "Ethnic distribution of the retro cohorts",
-       x = "",
-       y = "") +
+  labs(title = "",
+       x = "Ethnic origin",
+       y = "N participants") +
   scale_x_discrete(guide = guide_axis(n.dodge = 2),
@@
   theme(legend.position = "bottom") + 
-  theme(legend.title = element_blank())
+  theme(legend.title = element_blank()) +
+  geom_text(aes(label = n), 
+            position = position_dodge(width=0.9), 
+            vjust=-0.25)
 

### 2021-02-08 Paper_Histograms.Rmd
Reformatted the GLAD/EDGI, NBR and RAMP employment graph

@@
 
-dat.retro %>% 
-  ggplot(aes(x = employment_prior_covid, fill = Sample_plot)) +
-  geom_bar(position = "dodge") +
+dat.retro_employment_plot <- dat.retro %>% 
+  group_by(Sample_plot, employment_prior_covid) %>% 
+  summarise(n = n()) %>% 
+  drop_na()
+
+dat.retro_employment_plot %>% 
+  ggplot(aes(x = employment_prior_covid, y = n, fill = Sample_plot)) +
+  geom_bar(stat = "identity", position = "dodge") +
   scale_fill_manual(values = COPINGpalette3) +
-  theme_minimal() +
+  theme_classic() +
   theme(plot.title = element_text(hjust = 0.5),
         plot.subtitle = element_text(hjust = 0.5)) +
-  labs(title = "Employment distribution of the retro cohorts",
-       x = "",
-       y = "") +
+  labs(x = "Employment status",
+       y = "N participants") +
   theme(legend.position = "bottom") + 
-  theme(legend.title = element_blank())
+  theme(legend.title = element_blank()) +
+  scale_y_continuous(breaks = seq(0, 6000, by = 1000))
 

### 2021-02-08 Paper_Histograms.Rmd
Reformatted the GLAD/EDGI, NBR and RAMP gender retro graph

@@
   scale_fill_manual(values = COPINGpalette3) +
-  theme_minimal() +
+  theme_classic() +
   theme(plot.title = element_text(hjust = 0.5),
         plot.subtitle = element_text(hjust = 0.5)) +
-  labs(title = "Gender distribution of the retro cohorts",
-       x = "",
-       y = "") +
+  labs(x = "Participant Gender",
+       y = "N participants") +
   theme(legend.position = "bottom") + 

### 2021-02-08 Paper_Histograms.Rmd
Reformatted the GLAD/EDGI, NBR and RAMP age retro graph

@@
   scale_fill_manual(values = COPINGpalette3) +
-  theme_minimal() +
+  theme_classic() +
   theme(plot.title = element_text(hjust = 0.5),
         plot.subtitle = element_text(hjust = 0.5)) +
-  labs(title = "Age distribution of the retro cohorts",
-       x = "",
-       y = "") +
+  labs(x = "Age (years)",
+       y = "N participants") +
   theme(legend.position = "bottom") + 

### 2021-02-08 Paper_Histograms.Rmd
Reformatted the GLAD/EDGI, NBR and RAMP retro diagnosis graph

@@
   scale_fill_manual(values = COPINGpalette3) +
-  theme_minimal() +
+  theme_classic() +
   theme(plot.title = element_text(hjust = 0.5),
         plot.subtitle = element_text(hjust = 0.5)) +
-  labs(x = "",
-       y = "") +
+  labs(x = "Mental health diagnosis",
+       y = "N participants") +
   ylim(0, 20000) +

### 2021-02-08 Paper_Histograms.Rmd
Filtered white and non-white participants from GLAD/EDGI, NBR and RAMP for ethnicity retro plot

@@
 
-ethnicity_levels <- c("White", "Asian or Asian British", "Black or Black British",
-                      "Mixed or multiple ethnic origin", "Other")
-
-GLAD.prepan %>% 
+GLAD.prepan_ethnicity_plot <- dat.retro %>% 
+  mutate(Ethnicity_collapsed = 
+           fct_recode(Ethnicity_collapsed,
+             "White" = "European",
+             "Asian or Asian British" = "Asian or Asian British",
+             "Black or Black British" = "African or African British",
+             "Mixed or multiple ethnic origins" = "Mixed or multiple ethnic origins",
+             "Other" = "Other"
+           ))
+
+GLAD.prepan_ethnicity_plot %>% 
   ggplot(aes(x = Ethnicity_collapsed)) +
   geom_bar(fill = COPINGpalette6) +
-  theme_void() +
+  theme_classic() +
   theme(plot.title = element_text(hjust = 0.5),
@@
        y = "N participants") +
-  scale_x_discrete(guide = guide_axis(n.dodge = 2),
-                   labels = ethnicity_levels)
+  scale_x_discrete(guide = guide_axis(n.dodge = 2))
 
@@
 
-```{r GLAD/EDGI NBR and RAMP ethnicity}
+```{r Recode ethnicity levels and filter data}
 
 dat.retro_ethnicity_plot <- dat.retro %>% 
+  mutate(Ethnicity_collapsed = 
+           fct_recode(Ethnicity_collapsed,
+             "White" = "European",
+             "Asian or Asian British" = "Asian or Asian British",
+             "Black or Black British" = "African or African British",
+             "Mixed or multiple ethnic origins" = "Mixed or multiple ethnic origins",
+             "Other" = "Other"
+           ))
+
+#Filter White participants per sample
+
+dat.retro_ethnicity_white <- dat.retro_ethnicity_plot %>% 
   group_by(Sample_plot, Ethnicity_collapsed) %>% 
   summarise(n = n()) %>% 
-  drop_na()
+  drop_na() %>% 
+  filter(Ethnicity_collapsed == "White")
+
+#Filter non-white participants per study
+
+dat.retro_ethnicity_non_white <- dat.retro_ethnicity_plot %>% 
+  group_by(Sample_plot, Ethnicity_collapsed) %>% 
+  summarise(n = n()) %>% 
+  drop_na() %>% 
+  filter(Ethnicity_collapsed != "White")
+
+```
+
+```{r Plot GLAD/EDGI NBR and RAMP ethnicity retro}
 

### 2021-02-08 Paper_Histograms.Rmd
Reverted back to having all ethnicity data in one tibble, rather than separated by white/non-white

@@
 
-```{r Recode ethnicity levels and filter data}
+```{r GLAD/EDGI NBR and RAMP ethnicity}
 
@@
 
-#Filter White participants per sample
-
-dat.retro_ethnicity_white <- dat.retro_ethnicity_plot %>% 
+dat.retro_ethnicity_plot <- dat.retro %>% 
   group_by(Sample_plot, Ethnicity_collapsed) %>% 
   summarise(n = n()) %>% 
-  drop_na() %>% 
-  filter(Ethnicity_collapsed == "White")
-
-#Filter non-white participants per study
-
-dat.retro_ethnicity_non_white <- dat.retro_ethnicity_plot %>% 
-  group_by(Sample_plot, Ethnicity_collapsed) %>% 
-  summarise(n = n()) %>% 
-  drop_na() %>% 
-  filter(Ethnicity_collapsed != "White")
-
-```
-
-```{r Plot GLAD/EDGI NBR and RAMP ethnicity retro}
+  drop_na()
 
@@
        y = "N participants") +
-  scale_x_discrete(guide = guide_axis(n.dodge = 2),
-                   labels = ethnicity_levels) +
+  scale_x_discrete(guide = guide_axis(n.dodge = 2)) +
   theme(legend.position = "bottom") + 

### 2021-02-08 Paper_Histograms.Rmd
Made seperate plots for ethnicity white and non-white by sample, then plotted them side by side

--- 2021-02-08 Paper_Histograms.Rmd
@@
 library(ggpubr)
+library(cowplot)
 
@@
 
-#Filter White participants per sample
-
 dat.retro_ethnicity_white <- dat.retro_ethnicity_plot %>% 
@@
 
-#Filter non-white participants per study
-
 dat.retro_ethnicity_non_white <- dat.retro_ethnicity_plot %>% 
@@
 
-```{r Plot GLAD/EDGI NBR and RAMP ethnicity retro}
-
-dat.retro_ethnicity_plot %>% 
+```{r Plot graphs then merge}
+
+a <- dat.retro_ethnicity_white %>% 
   ggplot(aes(x = Ethnicity_collapsed, y = n, fill = Sample_plot)) +
@@
             vjust=-0.25)
+
+#Graph 2
+b <- dat.retro_ethnicity_non_white %>% 
+  ggplot(aes(x = Ethnicity_collapsed, y = n, fill = Sample_plot)) +
+  geom_bar(stat = "identity", position = "dodge") +
+  scale_fill_manual(values = COPINGpalette3) +
+  theme_classic() +
+  theme(plot.title = element_text(hjust = 0.5),
+        plot.subtitle = element_text(hjust = 0.5)) +
+  labs(title = "",
+       x = "Ethnic origin",
+       y = "N participants") +
+  scale_x_discrete(guide = guide_axis(n.dodge = 3)) +
+  theme(legend.position = "bottom") + 
+  theme(legend.title = element_blank()) +
+  geom_text(aes(label = n),
+            size = 3,
+            position = position_dodge(width=0.9), 
+            vjust=-0.25)
+
+plot_grid(a, b, labels = "AUTO")
 

### 2021-02-08 Paper_Histograms.Rmd
Made the names for the ethnicity retro graphs more clear

--- 2021-02-08 Paper_Histograms.Rmd
@@
 
-```{r Recode ethnicity levels and filter data}
+```{r GLAD/EDGI NBR and RAMP ethnicity data prep}
 
@@
 
-```{r Plot GLAD/EDGI NBR and RAMP ethnicity retro}
-
-dat.retro_ethnicity_plot %>% 
+```{r Plot ethnicity graphs then merge}
+
+retro_ethnicity_white <- dat.retro_ethnicity_white %>% 
   ggplot(aes(x = Ethnicity_collapsed, y = n, fill = Sample_plot)) +
@@
             vjust=-0.25)
+
+#Graph 2
+retro_ethnicity_non_white <- dat.retro_ethnicity_non_white %>% 
+  ggplot(aes(x = Ethnicity_collapsed, y = n, fill = Sample_plot)) +
+  geom_bar(stat = "identity", position = "dodge") +
+  scale_fill_manual(values = COPINGpalette3) +
+  theme_classic() +
+  theme(plot.title = element_text(hjust = 0.5),
+        plot.subtitle = element_text(hjust = 0.5)) +
+  labs(title = "",
+       x = "Ethnic origin",
+       y = "N participants") +
+  scale_x_discrete(guide = guide_axis(n.dodge = 3)) +
+  theme(legend.position = "bottom") + 
+  theme(legend.title = element_blank()) +
+  geom_text(aes(label = n),
+            size = 3,
+            position = position_dodge(width=0.9), 
+            vjust=-0.25)
+
+plot_grid(retro_ethnicity_white, retro_ethnicity_non_white, labels = "AUTO")
 

### 2021-02-08 Paper_Histograms.Rmd
Angled the x axis on the ethnicity retro graph

@@
        y = "N participants") +
-  scale_x_discrete(guide = guide_axis(n.dodge = 3)) +
+theme(axis.text.x = element_text(angle = 35, vjust = 0.5)) +
   theme(legend.position = "bottom") + 
@@
   geom_text(aes(label = n),
-            size = 3,
+            size = 2,
             position = position_dodge(width=0.9), 

### 2021-02-08 Paper_Histograms.Rmd
Removed plot style 2 for the retro diagnosis graph

--- 2021-02-08 Paper_Histograms.Rmd
@@
        y = "N participants") +
-  scale_x_discrete(guide = guide_axis(n.dodge = 3)) +
+theme(axis.text.x = element_text(angle = 70, vjust = 0.5)) +
   theme(legend.position = "bottom") + 
@@
 ```
-
-#####Plot Style 2
-
-```{r GLAD/EDGI NBR and RAMP retro diagnosis}
-
-dat.retro_positive_diagnosis_by_sample %>% 
-  ggplot(aes(x = reorder(Diagnosis, -positive_n), y = positive_n, fill = Sample_plot)) +
-  geom_bar(stat = "identity") +
-  scale_fill_manual(values = COPINGpalette3) +
-  theme_minimal() +
-  theme(plot.title = element_text(hjust = 0.5),
-        plot.subtitle = element_text(hjust = 0.5)) +
-  labs(x = "",
-       y = "") +
-  scale_x_discrete(guide = guide_axis(n.dodge = 2)) +
-  theme(legend.position = "top") + 
-  theme(legend.title = element_blank()) +
-  ylim(0, 20000)
-
-```

### 2021-02-08 Paper_Histograms.Rmd
Assigned the retro gender, age, ethnicity, employment and diagnosis graphs to objects

@@
 
-dat.retro %>% 
+retro_gender_plot <- dat.retro %>% 
   ggplot(aes(x = Gender_collapsed, fill = Sample_plot)) +
@@
 
-dat.retro %>% 
+retro_age_plot <- dat.retro %>% 
   ggplot(aes(x = age_category_collapsed, fill = Sample_plot)) +
@@
 
-plot_grid(retro_ethnicity_white, retro_ethnicity_non_white, labels = "AUTO")
+retro_ethnicity_plot <- plot_grid(retro_ethnicity_white, retro_ethnicity_non_white, labels = "AUTO")
 
@@
 
-dat.retro_employment_plot %>% 
+retro_employ_plot <- dat.retro_employment_plot %>% 
   ggplot(aes(x = employment_prior_covid, y = n, fill = Sample_plot)) +
@@
 
-dat.retro_positive_diagnosis_by_sample %>% 
+retro_diagnosis_plot <- dat.retro_positive_diagnosis_by_sample %>% 
   ggplot(aes(x = reorder(Diagnosis, -positive_n), y = positive_n, fill = Sample_plot)) +
@@
 ```
+
+#Plot Graphs together
+
+This will plot the stacked bar charts of the gender, age, employment, ethnicity and diagnosis variables together.
+
+```{r Plot histograms together}
+
+```

### 2021-02-08 Paper_Histograms.Rmd
Increased y axis limit and number size for the second retro ethnicity graph

@@
 remove(list = ls())
+
+```
+
+```{r Install packages}
+
+#install.packages("multipanelfigure")
 
@@
 library(cowplot)
+library(multipanelfigure)
 
@@
   geom_text(aes(label = n),
-            size = 2,
+            size = 3,
             position = position_dodge(width=0.9), 
-            vjust=-0.25)
+            vjust=-0.25) +
+     scale_y_continuous(expand = expansion(mult = c(0.1, 0.2)))
 
@@
 
-```
+#figure1 <- multi_panel_figure(columns = 3, rows = 3, panel_label_type = "none")
+#figure1
+
+#figure1 %>% 
+#  fill_panel(retro_age_plot, column = 1, row = 1) %>% 
+#  fill_panel(retro_gender_plot, column = 2, row = 1) %>% 
+#  fill_panel(retro_employ_plot, column = 3, row = 1) %>% 
+#  fill_panel(retro_ethnicity_plot, column = 1:3, row = 2) %>% 
+#  fill_panel(retro_diagnosis_plot, column = 1:3, row = 3)
+
+```

### 2021-02-08 Paper_Histograms.Rmd
Added code to imperfectly merge the retro graphs together

@@
        y = "N participants") +
-theme(axis.text.x = element_text(angle = 70, vjust = 0.5)) +
+theme(axis.text.x = element_text(angle = 70, 
+                                 vjust = 0.5,
+                                 size = 8)) +
   theme(legend.position = "bottom") + 
@@
 
-#figure1 <- multi_panel_figure(columns = 3, rows = 3, panel_label_type = "none")
-#figure1
-
-#figure1 %>% 
-#  fill_panel(retro_age_plot, column = 1, row = 1) %>% 
-#  fill_panel(retro_gender_plot, column = 2, row = 1) %>% 
-#  fill_panel(retro_employ_plot, column = 3, row = 1) %>% 
-#  fill_panel(retro_ethnicity_plot, column = 1:3, row = 2) %>% 
-#  fill_panel(retro_diagnosis_plot, column = 1:3, row = 3)
-
-```
+#Adding any more makes it look awful
+ggarrange(retro_age_plot, retro_gender_plot, retro_employ_plot,
+          labels = c("", "", ""),
+          ncol = 2, nrow = 2)
+
+ggarrange(retro_diagnosis_plot, retro_ethnicity_plot,
+         labels = c(""),
+         ncol = 2, nrow = 1)
+
+```

### 2021-02-08 Paper_Histograms.Rmd
Successfully merged the retro age, gender and employ graphs

@@
 
-This will plot the stacked bar charts of the gender, age, employment, ethnicity and diagnosis variables together.
-
-```{r Plot histograms together}
-
-#Adding any more makes it look awful
-ggarrange(retro_age_plot, retro_gender_plot, retro_employ_plot,
-          labels = c("", "", ""),
-          ncol = 2, nrow = 2)
+```{r Plot age gender and employ histograms together}
+
+arranged_gender_plot <- retro_gender_plot +
+  theme(legend.position = "none") +
+  scale_x_discrete(guide = guide_axis(n.dodge = 2),
+                   expand = expansion(mult = c(0.3, 0.4)))
+
+arranged_employ_plot <- retro_employ_plot +
+  theme(legend.position = "none") +
+  scale_x_discrete(guide = guide_axis(n.dodge = 2))
+
+#Combine retro age, gender and employ together
+ggarrange(retro_age_plot, 
+          ggarrange(arranged_gender_plot, arranged_employ_plot, ncol = 2), 
+          nrow = 2,
+          common.legend = TRUE)
+
+```
+
+```{r Plot retro diagnosis and ethnicity together}
 

### 2021-02-08 Paper_Histograms.Rmd
Successfully merged the retro diagnosis and ethnicity graphs

@@
 
-retro_ethnicity_plot <- plot_grid(retro_ethnicity_white, retro_ethnicity_non_white, labels = "AUTO")
+retro_ethnicity_plot <- plot_grid(retro_ethnicity_white, retro_ethnicity_non_white, labels = "")
 
@@
 
-#####Plot Style 1
+####Plot diagnosis
 
@@
 
+Note: I'm modifying the original retro plots to make them easier to merge together
+
 ```{r Plot age gender and employ histograms together}
@@
 
-ggarrange(retro_diagnosis_plot, retro_ethnicity_plot,
-         labels = c(""),
-         ncol = 2, nrow = 1)
-
-```
+#Note: Adding the data labels makes the graph look messy
+
+arranged_retro_ethnicity_white <- dat.retro_ethnicity_white %>% 
+  ggplot(aes(x = Ethnicity_collapsed, y = n, fill = Sample_plot)) +
+  geom_bar(stat = "identity", position = "dodge") +
+  scale_fill_manual(values = COPINGpalette3) +
+  theme_classic() +
+  theme(plot.title = element_text(hjust = 0.5),
+        plot.subtitle = element_text(hjust = 0.5)) +
+  labs(title = "",
+       x = "Ethnic origin",
+       y = "N participants") +
+  scale_x_discrete(guide = guide_axis(n.dodge = 2)) +
+  theme(legend.position = "none") + 
+  theme(legend.title = element_blank())# +
+#  geom_text(aes(label = n),
+#            size = 3,
+#            position = position_dodge(width=0.9), 
+#            vjust=-0.25)
+
+#Graph 2
+arranged_retro_ethnicity_non_white <- dat.retro_ethnicity_non_white %>% 
+  ggplot(aes(x = Ethnicity_collapsed, y = n, fill = Sample_plot)) +
+  geom_bar(stat = "identity", position = "dodge") +
+  scale_fill_manual(values = COPINGpalette3) +
+  theme_classic() +
+  theme(plot.title = element_text(hjust = 0.5),
+        plot.subtitle = element_text(hjust = 0.5)) +
+  labs(title = "",
+       x = "Ethnic origin",
+       y = "N participants") +
+theme(axis.text.x = element_text(angle = 70, 
+                                 vjust = 0.5,
+                                 size = 8)) +
+  theme(legend.position = "none") + 
+  #theme(legend.title = element_blank()) +
+  #geom_text(aes(label = n),
+  #          size = 3,
+  #          position = position_dodge(width=0.9), 
+  #          vjust=-0.25) +
+     scale_y_continuous(expand = expansion(mult = c(0.1, 0.2)))
+
+arranged_retro_ethnicity_plot <- plot_grid(arranged_retro_ethnicity_white, arranged_retro_ethnicity_non_white, labels = "")
+
+ggarrange(retro_diagnosis_plot, arranged_retro_ethnicity_plot,
+          common.legend = TRUE)
+
+```

### 2021-02-09 Paper_Histograms.Rmd
Plotted age, gender and employment retro together with additional data labels for gender

@@
 
+```{r Plot age gender employ and ethnicity retro together}
+
+dat.retro_gender_distribution <- dat.retro %>% 
+  group_by(Gender_collapsed, Sample_plot) %>% 
+  summarise(n = n())
+
+labelled_arranged_gender_plot <- dat.retro_gender_distribution %>% 
+  ggplot(aes(x = Gender_collapsed, y = n, fill = Sample_plot)) +
+  geom_bar(position = "dodge", stat = "identity") +
+  scale_fill_manual(values = COPINGpalette3) +
+  theme_classic() +
+  theme(plot.title = element_text(hjust = 0.5),
+        plot.subtitle = element_text(hjust = 0.5)) +
+  labs(x = "Participant Gender",
+       y = "N participants") +
+  theme(legend.position = "none") + 
+  theme(legend.title = element_blank()) +
+  geom_text(aes(label = n),
+            size = 3,
+            position = position_dodge(width=0.9), 
+            vjust=-0.25) +
+  scale_x_discrete(guide = guide_axis(n.dodge = 2),
+                   expand = expansion(mult = c(0.3, 0.4))) +
+  scale_y_continuous(expand = expansion(mult = c(0, 0.1)))
+
+#Combine retro age, gender and employ together
+ggarrange(retro_age_plot, 
+          ggarrange(labelled_arranged_gender_plot, arranged_employ_plot, ncol = 2), 
+          nrow = 2,
+          common.legend = TRUE)
+
+```
+
 ```{r Plot retro diagnosis and ethnicity together}

### 2021-02-09 Paper_Histograms.Rmd
Added template code to combine age, gender, employ and ethnicity in two ways

@@
 
-```{r Plot age gender employ and ethnicity retro together}
+```{r Add labels to gender retro and plot with gender and employ}
 
@@
           common.legend = TRUE)
+
+```
+
+```{r Tidy the ethnicity graphs}
+
+arranged_retro_ethnicity_white <- dat.retro_ethnicity_white %>% 
+  ggplot(aes(x = Ethnicity_collapsed, y = n, fill = Sample_plot)) +
+  geom_bar(stat = "identity", position = "dodge") +
+  scale_fill_manual(values = COPINGpalette3) +
+  theme_classic() +
+  theme(plot.title = element_text(hjust = 0.5),
+        plot.subtitle = element_text(hjust = 0.5)) +
+  labs(title = "",
+       x = "Ethnic origin",
+       y = "N participants") +
+  scale_x_discrete(guide = guide_axis(n.dodge = 2)) +
+  theme(legend.position = "none") + 
+  theme(legend.title = element_blank())# +
+#  geom_text(aes(label = n),
+#            size = 3,
+#            position = position_dodge(width=0.9), 
+#            vjust=-0.25)
+
+#Graph 2
+arranged_retro_ethnicity_non_white <- dat.retro_ethnicity_non_white %>% 
+  ggplot(aes(x = Ethnicity_collapsed, y = n, fill = Sample_plot)) +
+  geom_bar(stat = "identity", position = "dodge") +
+  scale_fill_manual(values = COPINGpalette3) +
+  theme_classic() +
+  theme(plot.title = element_text(hjust = 0.5),
+        plot.subtitle = element_text(hjust = 0.5)) +
+  labs(title = "",
+       x = "Ethnic origin",
+       y = "N participants") +
+  theme(legend.position = "none") + 
+  #theme(legend.title = element_blank()) +
+  #geom_text(aes(label = n),
+  #          size = 3,
+  #          position = position_dodge(width=0.9), 
+  #          vjust=-0.25) +
+     scale_y_continuous(expand = expansion(mult = c(0.1, 0.2))) +
+  scale_x_discrete(guide = guide_axis(n.dodge = 2))
+
+#arranged_retro_ethnicity_plot <- plot_grid(arranged_retro_ethnicity_white, arranged_retro_ethnicity_non_white, labels = "")
+
+```
+
+```{r Plot age gender employ and ethnicity together}
+
+ggarrange(arranged_retro_ethnicity_non_white,
+          ggarrange(arranged_retro_ethnicity_white, retro_employ_plot, ncol = 2),
+          ggarrange(retro_age_plot, arranged_gender_plot, ncol = 2),
+          nrow = 3,
+          common.legend =  TRUE)
+
+ggarrange(retro_age_plot, arranged_gender_plot, arranged_employ_plot,
+          arranged_retro_ethnicity_white, arranged_retro_ethnicity_non_white,
+          common.legend = TRUE,
+          ncol = 3,
+          nrow = 2)
 

### 2021-02-09 Paper_Histograms.Rmd
Added total mental health counter to each bar of the retro diagnosis histogram

@@
 retro_diagnosis_plot <- dat.retro_positive_diagnosis_by_sample %>% 
-  ggplot(aes(x = reorder(Diagnosis, -positive_n), y = positive_n, fill = Sample_plot)) +
+  ggplot(aes(x = reorder(Diagnosis, -positive_n, sum), y = positive_n, fill = Sample_plot)) +
   geom_bar(stat = "identity") +
@@
   theme(legend.position = "top") + 
-  theme(legend.title = element_blank())
+  theme(legend.title = element_blank()) +
+  geom_text(aes(label = stat(y), group = Diagnosis),
+            stat = "summary",
+            fun = sum,
+            vjust = -1)
 

### 2021-02-09 Paper_Histograms.Rmd
Stretched out the non white ethnicity figure in the combined retro graph

@@
 
-ggarrange(arranged_retro_ethnicity_non_white,
-          ggarrange(arranged_retro_ethnicity_white, retro_employ_plot, ncol = 2),
-          ggarrange(retro_age_plot, arranged_gender_plot, ncol = 2),
-          nrow = 3,
-          common.legend =  TRUE)
-
-ggarrange(retro_age_plot, arranged_gender_plot, arranged_employ_plot,
+#Two columns approach
+
+#ggarrange(arranged_retro_ethnicity_non_white,
+#          ggarrange(arranged_retro_ethnicity_white, retro_employ_plot, ncol = 2),
+#          ggarrange(retro_age_plot, arranged_gender_plot, ncol = 2),
+#          nrow = 3,
+#          common.legend =  TRUE)
+
+retro_matrix <- matrix(c(1, 2, 3, 4, 5, 5), nrow = 2, byrow = TRUE)
+
+gridExtra::grid.arrange(retro_age_plot, arranged_gender_plot, arranged_employ_plot,
           arranged_retro_ethnicity_white, arranged_retro_ethnicity_non_white,
-          common.legend = TRUE,
-          ncol = 3,
-          nrow = 2)
+          layout_matrix = retro_matrix, nrow = 2)
+
+#Three columns approach
+#ggarrange(retro_age_plot, arranged_gender_plot, arranged_employ_plot,
+#          arranged_retro_ethnicity_white, arranged_retro_ethnicity_non_white,
+#          common.legend = TRUE,
+#          ncol = 3,
+#          nrow = 2)
 
@@
 
-#Note: Adding the data labels makes the graph look messy
+#Note: Adding the data labels for ethnicity or diagnosis looks messy
 

### 2021-02-09 Paper_Histograms.Rmd
Reformatted the age retro graph in the gender, age, retro, ethnicity and employment figure

@@
 
+##Age gender and employ
+
 ```{r Plot age gender and employ histograms together}
@@
 ```
+
+##Age gender and employ with gender labelled
 
@@
 
+##Age gender employ and ethnicity
+
 ```{r Tidy the ethnicity graphs}
@@
 
+```{r Tidy the age gender and employ graphs}
+
+arranged_retro_age_plot <- dat.retro %>% 
+  ggplot(aes(x = age_category_collapsed, fill = Sample_plot)) +
+  geom_bar(position = "dodge") +
+  scale_fill_manual(values = COPINGpalette3) +
+  theme_classic() +
+  theme(plot.title = element_text(hjust = 0.5),
+        plot.subtitle = element_text(hjust = 0.5)) +
+  labs(x = "Age (years)",
+       y = "N participants") +
+  theme(legend.position = "none") + 
+  theme(legend.title = element_blank()) +
+  theme(axis.text.x = element_text(angle = 70, vjust = 0.5))
+
+```
+
 ```{r Plot age gender employ and ethnicity together}
@@
 
-gridExtra::grid.arrange(retro_age_plot, arranged_gender_plot, arranged_employ_plot,
+gridExtra::grid.arrange(arranged_gender_plot, arranged_retro_age_plot, arranged_employ_plot,
           arranged_retro_ethnicity_white, arranged_retro_ethnicity_non_white,

### 2021-02-09 Paper_Histograms.Rmd
Reformatted the gender and employ plots in the age, gender, ethnicity and employ retro figure

@@
 
+dat.retro_gender_male_female <- dat.retro_gender_distribution %>% 
+  filter(Gender_collapsed != "Non-binary/Self-defined")
+
+arranged_collapsed_gender_plot <- dat.retro_gender_male_female %>% 
+  ggplot(aes(x = Gender_collapsed, y = n, fill = Sample_plot)) +
+  geom_bar(position = "dodge", stat = "identity") +
+  scale_fill_manual(values = COPINGpalette3) +
+  theme_classic() +
+  theme(plot.title = element_text(hjust = 0.5),
+        plot.subtitle = element_text(hjust = 0.5)) +
+  labs(x = "Participant Gender",
+       y = "N participants") +
+  theme(legend.position = "none") + 
+  theme(legend.title = element_blank())
+
+arranged_employ_plot <- dat.retro_employment_plot %>% 
+  ggplot(aes(x = employment_prior_covid, y = n, fill = Sample_plot)) +
+  geom_bar(stat = "identity", position = "dodge") +
+  scale_fill_manual(values = COPINGpalette3) +
+  theme_classic() +
+  theme(plot.title = element_text(hjust = 0.5),
+        plot.subtitle = element_text(hjust = 0.5)) +
+  labs(x = "Employment status",
+       y = "N participants") +
+  theme(legend.position = "none") + 
+  theme(legend.title = element_blank()) +
+  scale_y_continuous(breaks = seq(0, 6000, by = 1000)) +
+  scale_x_discrete(guide = guide_axis(n.dodge = 3),
+                   expand = expansion(mult = c(0.2, 0.3)))
+
 ```
@@
 
-gridExtra::grid.arrange(arranged_gender_plot, arranged_retro_age_plot, arranged_employ_plot,
+gridExtra::grid.arrange(arranged_collapsed_gender_plot, arranged_retro_age_plot, arranged_employ_plot,
           arranged_retro_ethnicity_white, arranged_retro_ethnicity_non_white,

### 2021-02-09 Paper_Histograms.Rmd
Added legend to gender, age, employment and ethnicity retro plot

@@
        y = "N participants") +
-  theme(legend.position = "none") + 
+  theme(legend.position = "bottom") +
+  theme(legend.title = element_blank()) +
   #theme(legend.title = element_blank()) +

### 2021-02-09 Paper_Histograms.Rmd
Added gridExtra package to library

@@
 library(cowplot)
-library(multipanelfigure)
+library(gridExtra)
 
@@
 
-gridExtra::grid.arrange(arranged_collapsed_gender_plot, arranged_retro_age_plot, arranged_employ_plot,
+grid.arrange(arranged_collapsed_gender_plot, arranged_retro_age_plot, arranged_employ_plot,
           arranged_retro_ethnicity_white, arranged_retro_ethnicity_non_white,

### 2021-02-09 Paper_Histograms.Rmd
Added self-defined/non-binary caption to age, gender, employment and ethnicity retro figure

@@
   #theme(legend.title = element_blank()) +
-  #geom_text(aes(label = n),
-  #          size = 3,
-  #          position = position_dodge(width=0.9), 
-  #          vjust=-0.25) +
+  geom_text(aes(label = n),
+            size = 3,
+            position = position_dodge(width=0.9), 
+            vjust=-0.25) +
      scale_y_continuous(expand = expansion(mult = c(0.1, 0.2))) +
@@
   labs(x = "Participant Gender",
-       y = "N participants") +
+       y = "N participants",
+       caption = "Non-binary/Self-defined
+         GLAD/EDGI (243); NBR (39); RAMP (92)") +
   theme(legend.position = "none") + 

### 2021-02-13 Paper_Histograms.Rmd
Changed OCDs to OCDRs in the retro diagnosis graph

@@
   group_by(Sample_plot) %>% 
-  summarise("OCDs" = n())
+  summarise("OCDRs" = n())
 
@@
 dat.retro_positive_diagnosis_by_sample <- dat.retro_positive_diagnosis_by_sample %>% 
-  gather('Depressive disorders', 'Anxiety disorders', 'Eating disorders', 'OCDs', 'Psychotic disorders', 'ASD', 'ADHD', 'Personality disorders', 'Bipolar disorders', 'PTSD', 'No diagnosis', key = "Diagnosis", value = positive_n)
+  gather('Depressive disorders', 'Anxiety disorders', 'Eating disorders', 'OCDRs', 'Psychotic disorders', 'ASD', 'ADHD', 'Personality disorders', 'Bipolar disorders', 'PTSD', 'No diagnosis', key = "Diagnosis", value = positive_n)
 

### 2021-02-13 Paper_Histograms.Rmd
Changed x and y axis text to black on retro diagnosis graph

@@
             fun = sum,
-            vjust = -1)
+            vjust = -1,
+            colour = "black") +
+  theme(axis.text.x = element_text(colour = "black"),
+        axis.text.y = element_text(colour = "black"))
 

### 2021-02-13 Paper_Histograms.Rmd
Added black axis text to retro, gender, age, ethnicity, employ and combined retro graphs

@@
   theme(legend.position = "bottom") + 
-  theme(legend.title = element_blank())
+  theme(legend.title = element_blank()) +
+  theme(axis.text.x = element_text(colour = "black"),
+        axis.text.y = element_text(colour = "black"))
 
@@
             position = position_dodge(width=0.9), 
-            vjust=-0.25)
+            vjust=-0.25) +
+  theme(axis.text.x = element_text(colour = "black"),
+        axis.text.y = element_text(colour = "black"))
 
@@
        y = "N participants") +
-theme(axis.text.x = element_text(angle = 70, 
+theme(axis.text.x = element_text(angle = 45, 
                                  vjust = 0.5,
@@
             vjust=-0.25) +
-     scale_y_continuous(expand = expansion(mult = c(0.1, 0.2)))
+     scale_y_continuous(expand = expansion(mult = c(0.1, 0.2)))  +
+  theme(axis.text.x = element_text(colour = "black"),
+        axis.text.y = element_text(colour = "black"))
 
@@
 
-```{r Gender retro pie chart by sample}
+```{r Ethnicity retro pie chart by sample}
 
@@
   theme(legend.title = element_blank()) +
-  scale_y_continuous(breaks = seq(0, 6000, by = 1000))
+  scale_y_continuous(breaks = seq(0, 6000, by = 1000)) +
+  theme(axis.text.x = element_text(colour = "black"),
+        axis.text.y = element_text(colour = "black"))
 
@@
   theme(legend.position = "none") + 
-  theme(legend.title = element_blank())# +
+  theme(legend.title = element_blank()) +
+  theme(axis.text.x = element_text(colour = "black"),
+        axis.text.y = element_text(colour = "black"))# +
 #  geom_text(aes(label = n),
@@
      scale_y_continuous(expand = expansion(mult = c(0.1, 0.2))) +
-  scale_x_discrete(guide = guide_axis(n.dodge = 2))
+  scale_x_discrete(guide = guide_axis(n.dodge = 2)) +
+  theme(axis.text.x = element_text(colour = "black"),
+        axis.text.y = element_text(colour = "black"))
 
@@
   theme(legend.title = element_blank()) +
-  theme(axis.text.x = element_text(angle = 70, vjust = 0.5))
+  theme(axis.text.x = element_text(angle = 70, vjust = 0.5)) +
+  theme(axis.text.x = element_text(colour = "black"),
+        axis.text.y = element_text(colour = "black"))
 
@@
   theme(legend.position = "none") + 
-  theme(legend.title = element_blank())
+  theme(legend.title = element_blank())  +
+  theme(axis.text.x = element_text(colour = "black"),
+        axis.text.y = element_text(colour = "black"))
 
@@
   scale_x_discrete(guide = guide_axis(n.dodge = 3),
-                   expand = expansion(mult = c(0.2, 0.3)))
+                   expand = expansion(mult = c(0.2, 0.3))) +
+  theme(axis.text.x = element_text(colour = "black"),
+        axis.text.y = element_text(colour = "black"))
 

### 2021-02-16 Paper_Histograms.Rmd
Added template code to get the sign up per month for glad retrocohort

@@
   summarise(N = n())
+
+```
+
+##Sign-up histogram
+
+```{r Get GLAD/EDGI participant sign-up data}
+
+#Visualise some dates when participants completed the questionnaire
+head(GLAD.retro$startDate.coping, 10)
+
+#Divide the data by sign up per month and summarise the amount of pt's completing the survey that month
+names(GLAD.retro)
+GLAD.retro_april_sign_up <- GLAD.retro[str_detect(GLAD.retro$startDate.coping, "-04-"), ] %>% 
+  select(startDate.coping) %>% 
+  summarise(April = n())
+
+GLAD.retro_may_sign_up <- GLAD.retro[str_detect(GLAD.retro$startDate.coping, "-05-"), ] %>% 
+  select(startDate.coping) %>% 
+  summarise(May = n())
+
+GLAD.retro_june_sign_up <- GLAD.retro[str_detect(GLAD.retro$startDate.coping, "-06-"), ] %>% 
+  select(startDate.coping) %>% 
+  summarise(June = n())
+
+GLAD.retro_july_sign_up <- GLAD.retro[str_detect(GLAD.retro$startDate.coping, "-07-"), ] %>% 
+  select(startDate.coping) %>% 
+  summarise(July = n())
+
+GLAD.retro_august_sign_up <- GLAD.retro[str_detect(GLAD.retro$startDate.coping, "-08-"), ] %>%
+  select(startDate.coping) %>% 
+  summarise(August = n())
+
+GLAD.retro_september_sign_up <- GLAD.retro[str_detect(GLAD.retro$startDate.coping, "-09-"), ] %>% 
+  select(startDate.coping) %>% 
+  summarise(September = n())
+
+#Merge results into one tibble
+
+GLAD.retro_sign_up <- GLAD.retro_april_sign_up %>% 
+  cbind(GLAD.retro_may_sign_up,
+        GLAD.retro_june_sign_up,
+        GLAD.retro_july_sign_up,
+        GLAD.retro_august_sign_up,
+        GLAD.retro_september_sign_up)
+
+#Gather the variables
+GLAD.retro_sign_up <- GLAD.retro_sign_up %>% 
+  gather(key = "month", value = "n")
+
+head(GLAD.retro_sign_up, 10)
 

### 2021-02-16 Paper_Histograms.Rmd
Get sign up numbers per month by participant sample

--- 2021-02-13 Paper_Histograms.Rmd
@@
   summarise(N = n())
+
+```
+
+##Sign-up histogram
+
+```{r Get GLAD/EDGI participant sign-up data}
+
+#Visualise some dates when participants completed the questionnaire
+head(dat.retro$startDate.coping, 10)
+
+#Divide the data by sign up per month and summarise the amount of pt's completing the survey that month
+
+dat.retro_april_sign_up <- dat.retro[str_detect(dat.retro$startDate.coping, "-04-"), ] %>% 
+  select(Sample_plot, startDate.coping) %>%
+  group_by(Sample_plot) %>% 
+  summarise(April = n())
+
+dat.retro_may_sign_up <- dat.retro[str_detect(dat.retro$startDate.coping, "-05-"), ] %>% 
+  select(Sample_plot, startDate.coping) %>% 
+  group_by(Sample_plot) %>% 
+  summarise(May = n())
+
+dat.retro_june_sign_up <- dat.retro[str_detect(dat.retro$startDate.coping, "-06-"), ] %>% 
+  select(Sample_plot, startDate.coping) %>% 
+  group_by(Sample_plot) %>% 
+  summarise(June = n())
+
+dat.retro_july_sign_up <- dat.retro[str_detect(dat.retro$startDate.coping, "-07-"), ] %>% 
+  select(Sample_plot, startDate.coping) %>% 
+  group_by(Sample_plot) %>% 
+  summarise(July = n())
+
+dat.retro_august_sign_up <- dat.retro[str_detect(dat.retro$startDate.coping, "-08-"), ] %>%
+  select(Sample_plot, startDate.coping) %>% 
+  group_by(Sample_plot) %>% 
+  summarise(August = n())
+
+dat.retro_september_sign_up <- dat.retro[str_detect(dat.retro$startDate.coping, "-09-"), ] %>% 
+  select(Sample_plot, startDate.coping) %>% 
+  group_by(Sample_plot) %>% 
+  summarise(September = n())
+
+#Merge results into one tibble
+
+dat.retro_sign_up <- dat.retro_april_sign_up %>% 
+  cbind(dat.retro_may_sign_up,
+        dat.retro_june_sign_up,
+        dat.retro_july_sign_up,
+        dat.retro_august_sign_up,
+        dat.retro_september_sign_up)
+
+#Gather the variables
+dat.retro_sign_up <- dat.retro_sign_up %>% 
+  gather(key = "month", value = "n")
+
+head(GLAD.retro_sign_up, 10)
 

### 2021-02-16 Paper_Histograms.Rmd
Ensured that each sign up month tibble has 3 rows, one for each sample

@@
 
-head(GLAD.retro_sign_up, 10)
+```
+
+```{r Add extra rows to sign_up tibbles with only two samples}
+
+sign_up_NBR_empty_row_April <- tibble(
+  Sample_plot = "NBR",
+  April = 0
+)
+
+sign_up_NBR_empty_row_August <- tibble(
+  Sample_plot = "NBR",
+  August = 0
+)
+
+sign_up_NBR_empty_row_September <- tibble(
+  Sample_plot = "NBR",
+  September = 0
+)
+
+dat.retro_april_sign_up <- dat.retro_april_sign_up %>% 
+  rbind(sign_up_NBR_empty_row_April)
+
+dat.retro_august_sign_up <- dat.retro_august_sign_up %>% 
+  rbind(sign_up_NBR_empty_row_August)
+
+dat.retro_september_sign_up <- dat.retro_september_sign_up %>% 
+  rbind(sign_up_NBR_empty_row_September)
 

### 2021-02-16 Paper_Histograms.Rmd
Merged all the sign up per month by sample tibbles and tidied the columns

@@
 
-#Merge results into one tibble
-
-dat.retro_sign_up <- dat.retro_april_sign_up %>% 
-  cbind(dat.retro_may_sign_up,
-        dat.retro_june_sign_up,
-        dat.retro_july_sign_up,
-        dat.retro_august_sign_up,
-        dat.retro_september_sign_up)
-
-#Gather the variables
-dat.retro_sign_up <- dat.retro_sign_up %>% 
-  gather(key = "month", value = "n")
-
 ```
@@
   rbind(sign_up_NBR_empty_row_September)
+
+```
+
+```{r Left_join sign-up per month by sampple tibs and tidy}
+
+#Merge results into one tibble
+
+dat.retro_sign_up <- dat.retro_april_sign_up %>% 
+  left_join(dat.retro_may_sign_up,
+            by = "Sample_plot")
+
+dat.retro_sign_up <- dat.retro_sign_up %>% 
+  left_join(dat.retro_june_sign_up,
+            by = "Sample_plot")
+
+dat.retro_sign_up <- dat.retro_sign_up %>% 
+  left_join(dat.retro_july_sign_up,
+            by = "Sample_plot")
+
+dat.retro_sign_up <- dat.retro_sign_up %>% 
+  left_join(dat.retro_august_sign_up,
+            by = "Sample_plot")
+
+dat.retro_sign_up <- dat.retro_sign_up %>% 
+  left_join(dat.retro_september_sign_up,
+            by = "Sample_plot")
+
+#Gather the variables
+dat.retro_sign_up <- dat.retro_sign_up %>% 
+  gather(key = "month",
+         value = "n",
+         c(-Sample_plot))
 

### 2021-02-16 Paper_Histograms.Rmd
Added template code to plot sign up per month by study

@@
          c(-Sample_plot))
+
+```
+
+```{r Plot sign up per month by sample}
+
+dat.retro_sign_up %>% 
+  ggplot(aes(x = month, y = n, fill = Sample_plot)) +
+  geom_bar(stat = "identity", position = "dodge") +
+  scale_fill_manual(values = COPINGpalette3) +
+  theme_classic() +
+  labs(x = "Month of sign up",
+       y = "N participants") +
+  theme(legend.position = "top",
+        legend.title = element_blank(),
+        axis.text.x = element_text(colour = "black"),
+        axis.text.y = element_text(colour = "black")) +
+  geom_text(aes(label = n),
+            size = 3,
+            position = position_dodge(width=0.9), 
+            vjust=-0.25)
 

### 2021-02-16 Paper_Histograms.Rmd
Fixed month order on the sign up per month by sample plot
Changed y axis values for the sign up per month by sample plot

--- 2021-02-16 Paper_Histograms.Rmd
@@
          c(-Sample_plot))
+
+dat.retro_sign_up$month <- factor(dat.retro_sign_up$month,
+                                  levels = c("April", "May", "June", "July", "August",
+                                             "September"))
+
+```
+
+```{r Plot sign up per month by sample}
+
+dat.retro_sign_up %>% 
+  ggplot(aes(x = month, y = n, fill = Sample_plot)) +
+  geom_bar(stat = "identity", position = "dodge") +
+  scale_fill_manual(values = COPINGpalette3) +
+  theme_classic() +
+  labs(x = "Month of sign up",
+       y = "N participants") +
+  theme(legend.position = "top",
+        legend.title = element_blank(),
+        axis.text.x = element_text(colour = "black"),
+        axis.text.y = element_text(colour = "black")) +
+  scale_y_continuous(breaks = seq(0, 15000, by = 2500)) +
+  geom_text(aes(label = n),
+            size = 3,
+            position = position_dodge(width=0.9), 
+            vjust=-0.25)
 

### 2021-02-17 Paper_Histograms.Rmd
Added template code to add plot caption to the gender, age, employ, ethnicity merged retro plot

@@
           arranged_retro_ethnicity_white, arranged_retro_ethnicity_non_white,
-          layout_matrix = retro_matrix, nrow = 2)
+          layout_matrix = retro_matrix, 
+          nrow = 2,
+          bottom = textGrob("Grid caption", x = 1,
+                            hjust = 1,
+                            gp = gpar(fontface = 3L, fontsize = 9)))
+
+bottom = textGrob("grid caption", x = 1, 
+                                hjust = 1, gp = gpar(fontface = 3L, fontsize = 9)))
 
@@
 #          nrow = 2)
+
+```
+
+```{r Gender age ethnicity employ retro graph with plot caption}
+
+grid.arrange(arranged_collapsed_gender_plot, arranged_retro_age_plot, arranged_employ_plot,
+          arranged_retro_ethnicity_white, arranged_retro_ethnicity_non_white,
+          layout_matrix = retro_matrix, 
+          nrow = 2,
+          bottom = textGrob("Non-binary/Self-defined: GLAD/EDGI (243); NBR (39); RAMP (92)", x = 1,
+                            hjust = 1,
+                            gp = gpar(fontface = 3L, fontsize = 9)))
 

### 2021-02-17 Paper_Histograms.Rmd
Made non-binary/self-defined gender a plot caption for age, gender, employ and ethnicity merged retro graph

--- 2021-02-16 Paper_Histograms.Rmd
@@
 
-#Two columns approach
-
-#ggarrange(arranged_retro_ethnicity_non_white,
-#          ggarrange(arranged_retro_ethnicity_white, retro_employ_plot, ncol = 2),
-#          ggarrange(retro_age_plot, arranged_gender_plot, ncol = 2),
-#          nrow = 3,
-#          common.legend =  TRUE)
-
 retro_matrix <- matrix(c(1, 2, 3, 4, 5, 5), nrow = 2, byrow = TRUE)
@@
           arranged_retro_ethnicity_white, arranged_retro_ethnicity_non_white,
-          layout_matrix = retro_matrix, nrow = 2)
-
-#Three columns approach
-#ggarrange(retro_age_plot, arranged_gender_plot, arranged_employ_plot,
-#          arranged_retro_ethnicity_white, arranged_retro_ethnicity_non_white,
-#          common.legend = TRUE,
-#          ncol = 3,
-#          nrow = 2)
-
-```
-
-```{r Plot retro diagnosis and ethnicity together}
-
-#Note: Adding the data labels for ethnicity or diagnosis looks messy
-
-arranged_retro_ethnicity_white <- dat.retro_ethnicity_white %>% 
-  ggplot(aes(x = Ethnicity_collapsed, y = n, fill = Sample_plot)) +
-  geom_bar(stat = "identity", position = "dodge") +
-  scale_fill_manual(values = COPINGpalette3) +
-  theme_classic() +
-  theme(plot.title = element_text(hjust = 0.5),
-        plot.subtitle = element_text(hjust = 0.5)) +
-  labs(title = "",
-       x = "Ethnic origin",
+          layout_matrix = retro_matrix, 
+          nrow = 2)
+
+```
+
+```{r Gender age ethnicity employ retro graph with plot caption}
+
+#Remake gender plot without caption
+
+arranged_collapsed_gender_plot <- dat.retro_gender_male_female %>% 
+  ggplot(aes(x = Gender_collapsed, y = n, fill = Sample_plot)) +
+  geom_bar(position = "dodge", stat = "identity") +
+  scale_fill_manual(values = COPINGpalette3) +
+  theme_classic() +
+  theme(plot.title = element_text(hjust = 0.5),
+        plot.subtitle = element_text(hjust = 0.5)) +
+  labs(x = "Participant Gender",
        y = "N participants") +
-  scale_x_discrete(guide = guide_axis(n.dodge = 2)) +
   theme(legend.position = "none") + 
-  theme(legend.title = element_blank())# +
-#  geom_text(aes(label = n),
-#            size = 3,
-#            position = position_dodge(width=0.9), 
-#            vjust=-0.25)
-
-#Graph 2
-arranged_retro_ethnicity_non_white <- dat.retro_ethnicity_non_white %>% 
-  ggplot(aes(x = Ethnicity_collapsed, y = n, fill = Sample_plot)) +
-  geom_bar(stat = "identity", position = "dodge") +
-  scale_fill_manual(values = COPINGpalette3) +
-  theme_classic() +
-  theme(plot.title = element_text(hjust = 0.5),
-        plot.subtitle = element_text(hjust = 0.5)) +
-  labs(title = "",
-       x = "Ethnic origin",
-       y = "N participants") +
-theme(axis.text.x = element_text(angle = 70, 
-                                 vjust = 0.5,
-                                 size = 8)) +
-  theme(legend.position = "none") + 
-  #theme(legend.title = element_blank()) +
-  #geom_text(aes(label = n),
-  #          size = 3,
-  #          position = position_dodge(width=0.9), 
-  #          vjust=-0.25) +
-     scale_y_continuous(expand = expansion(mult = c(0.1, 0.2)))
-
-arranged_retro_ethnicity_plot <- plot_grid(arranged_retro_ethnicity_white, arranged_retro_ethnicity_non_white, labels = "")
-
-ggarrange(retro_diagnosis_plot, arranged_retro_ethnicity_plot,
-          common.legend = TRUE)
-
-```
+  theme(legend.title = element_blank())  +
+  theme(axis.text.x = element_text(colour = "black"),
+        axis.text.y = element_text(colour = "black"))
+
+```
+
+```{r plot age gender ethnicity and employ with plot caption}
+
+grid.arrange(arranged_collapsed_gender_plot, arranged_retro_age_plot, arranged_employ_plot,
+          arranged_retro_ethnicity_white, arranged_retro_ethnicity_non_white,
+          layout_matrix = retro_matrix, 
+          nrow = 2,
+          bottom = textGrob("Non-binary/Self-defined: GLAD/EDGI (243); NBR (39); RAMP (92)", x = 1,
+                            hjust = 1,
+                            gp = gpar(fontface = 3L, fontsize = 9)))
+
+```

### 2021-02-18 Paper_Histograms.Rmd
Removed unused packages from library chunk and added installations for used packages

@@
 
-#install.packages("multipanelfigure")
+#install.packages("knitr")
+#install.packages("tidyverse")
+#install.packages("ggpubr")
+#install.packages("cowplot")
+#install.packages("gridExtra")
+#install.packages("grid")
 
@@
 
-```{r read in data }
+```{r read in data}
 
@@
 library(knitr)
-library(summarytools)
-library(psych)
-library(polycor)
-library(corrplot)
-library(patchwork)
-library(broom)
 library(tidyverse)
@@
 library(gridExtra)
+library(grid)
 

### 2021-02-18 Paper_Histograms.Rmd
Adjusted the heights of the non-white retro graph in the age, gender, employ and ethnicity retro plot

@@
           nrow = 2,
+          heights=c(1, 1.2),
           bottom = textGrob("Non-binary/Self-defined: GLAD/EDGI (243); NBR (39); RAMP (92)", x = 1,

### 2021-02-18 Paper_Histograms.Rmd
Recoded 'Mixed or multiple ethinic origins' to be shorter for the final merged retro plot

@@
 
+```{r Recode ethnicity levels and re-create non-white plot}
+
+levels(dat.retro_ethnicity_non_white$Ethnicity_collapsed)
+
+dat.retro_ethnicity_non_white <- dat.retro_ethnicity_non_white %>% 
+  mutate(Ethnicity_collapsed = 
+           fct_recode(Ethnicity_collapsed,
+                       "Mixed or multiple origins" = "Mixed or multiple ethnic origins"))
+
+arranged_retro_ethnicity_non_white <- dat.retro_ethnicity_non_white %>% 
+  ggplot(aes(x = Ethnicity_collapsed, y = n, fill = Sample_plot)) +
+  geom_bar(stat = "identity", position = "dodge") +
+  scale_fill_manual(values = COPINGpalette3) +
+  theme_classic() +
+  theme(plot.title = element_text(hjust = 0.5),
+        plot.subtitle = element_text(hjust = 0.5)) +
+  labs(title = "",
+       x = "Ethnic origin",
+       y = "N participants") +
+  theme(legend.position = "bottom") +
+  theme(legend.title = element_blank()) +
+  #theme(legend.title = element_blank()) +
+  geom_text(aes(label = n),
+            size = 3,
+            position = position_dodge(width=0.9), 
+            vjust=-0.25) +
+     scale_y_continuous(expand = expansion(mult = c(0.1, 0.2))) +
+  scale_x_discrete(guide = guide_axis(n.dodge = 2)) +
+  theme(axis.text.x = element_text(colour = "black"),
+        axis.text.y = element_text(colour = "black"))
+
+```
+
 ```{r plot age gender ethnicity and employ with plot caption}

### 2021-02-20 Paper_Histograms.Rmd
Collapsed July to September sign ups together

@@
   rbind(sign_up_NBR_empty_row_September)
+
+```
+
+```{r Collapse July to September sign ups together}
+
+dat.retro_july_sep_sign_up <- dat.retro_july_sign_up %>% 
+  left_join(dat.retro_august_sign_up,
+            by = "Sample_plot")
+
+dat.retro_july_sep_sign_up <- dat.retro_july_sep_sign_up %>% 
+  left_join(dat.retro_september_sign_up,
+            by = "Sample_plot")
+
+dat.retro_july_sep_sign_up %>% 
+  group_by(Sample_plot) %>% 
+  mutate("July-September" = 
+           July + August + September) %>% 
+  select(Sample_plot, "July-September")
 

### 2021-02-20 Paper_Histograms.Rmd
Merged July to September sign ups with sign ups for other months to collapse sign up graph levels

@@
 
-dat.retro_july_sep_sign_up %>% 
+dat.retro_july_sep_sign_up <- dat.retro_july_sep_sign_up %>% 
   group_by(Sample_plot) %>% 
@@
 dat.retro_sign_up <- dat.retro_sign_up %>% 
-  left_join(dat.retro_july_sign_up,
-            by = "Sample_plot")
-
-dat.retro_sign_up <- dat.retro_sign_up %>% 
-  left_join(dat.retro_august_sign_up,
-            by = "Sample_plot")
-
-dat.retro_sign_up <- dat.retro_sign_up %>% 
-  left_join(dat.retro_september_sign_up,
+  left_join(dat.retro_july_sep_sign_up,
             by = "Sample_plot")
@@
 dat.retro_sign_up$month <- factor(dat.retro_sign_up$month,
-                                  levels = c("April", "May", "June", "July", "August",
-                                             "September"))
+                                  levels = c("April", "May", "June", "July-September"))
 

### 2021-02-20 Paper_Histograms.Rmd
Moved legend on age, gender, employment and ethnicity to middlerather than bottom

@@
   theme(legend.title = element_blank()) +
-  #theme(legend.title = element_blank()) +
   geom_text(aes(label = n),
@@
   theme(axis.text.x = element_text(colour = "black"),
-        axis.text.y = element_text(colour = "black"))
+        axis.text.y = element_text(colour = "black")) +
+  theme(legend.justification=c(1,0), legend.position=c(1, 0.95)) +
+  guides(fill = guide_legend(
+    nrow = 1,
+    override.aes = list(size = 4)
+  ))
 
@@
           nrow = 2,
-          heights=c(1, 1.2),
+          #heights=c(1, 1.2),
           bottom = textGrob("Non-binary/Self-defined: GLAD/EDGI (243); NBR (39); RAMP (92)", x = 1,

### 2021-02-22 Paper_Histograms.Rmd
Added space between July - September in retro sign up chart

@@
   group_by(Sample_plot) %>% 
-  mutate("July-September" = 
+  mutate("July - September" = 
            July + August + September) %>% 
-  select(Sample_plot, "July-September")
+  select(Sample_plot, "July - September")
 
@@
 dat.retro_sign_up$month <- factor(dat.retro_sign_up$month,
-                                  levels = c("April", "May", "June", "July-September"))
+                                  levels = c("April", "May", "June", "July - September"))
 

### 2021-02-22 Paper_Histograms.Rmd
Moved EDGI participants to the NBR cohort rather than GLAD

@@
 GLAD.prepan <- dat.prepan %>%
-  filter(Sample == "GLAD" | 
+  filter(Sample == "GLAD")
+
+NBR.prepan <- dat.prepan %>%
+  filter(Sample == "NBR" | 
            Sample == "EDGI")
-
-NBR.prepan <- dat.prepan %>%
-  filter(Sample == "NBR")
 
@@
 GLAD.retro <- dat.retro %>%
-  filter(Sample == "GLAD" | 
+  filter(Sample == "GLAD")
+
+NBR.retro <- dat.retro %>%
+  filter(Sample == "NBR" | 
            Sample == "EDGI")
-
-NBR.retro <- dat.retro %>%
-  filter(Sample == "NBR")
 
@@
              dat.retro$Sample == "GLAD" ~ "GLAD/EDGI",
-             dat.retro$Sample == "EDGI" ~ "GLAD/EDGI",
+             dat.retro$Sample == "EDGI" ~ "NBR",
              dat.retro$Sample == "NBR" ~ "NBR",

### 2021-02-22 Paper_Histograms.Rmd
Modified the cleaning/left_joining for the retro sign up graph after moving EDGI participants to NBR

@@
            case_when(
-             dat.retro$Sample == "GLAD" ~ "GLAD/EDGI",
-             dat.retro$Sample == "EDGI" ~ "NBR",
-             dat.retro$Sample == "NBR" ~ "NBR",
+             dat.retro$Sample == "GLAD" ~ "GLAD",
+             dat.retro$Sample == "EDGI" ~ "NBR/EDGI",
+             dat.retro$Sample == "NBR" ~ "NBR/EDGI",
              dat.retro$Sample == "RAMP" ~ "RAMP"
@@
 sign_up_NBR_empty_row_April <- tibble(
-  Sample_plot = "NBR",
+  Sample_plot = "NBR/EDGI",
   April = 0
@@
 
-sign_up_NBR_empty_row_August <- tibble(
-  Sample_plot = "NBR",
-  August = 0
-)
-
 sign_up_NBR_empty_row_September <- tibble(
-  Sample_plot = "NBR",
+  Sample_plot = "NBR/EDGI",
   September = 0
@@
   rbind(sign_up_NBR_empty_row_April)
-
-dat.retro_august_sign_up <- dat.retro_august_sign_up %>% 
-  rbind(sign_up_NBR_empty_row_August)
 

### 2021-02-22 Paper_Histograms.Rmd
Added extra subset for GLAD/EDGI pt's to use for all the prepan plots

@@
 
-```{r Merge GLAD/EDGI samples together for plot}
+```{r Create GLAD/EDGI prepan subset for prepan plots}
+
+GLAD.prepan_with_EDGI <- dat.prepan %>% 
+  filter(Sample == "GLAD" |
+           Sample == "EDGI")
+
+#Check that it worked
+
+GLAD.prepan_with_EDGI %>% 
+  group_by(Sample) %>% 
+  summarise(N = n())
+
+```
+
+```{r Create NBR/EDGI labelled sample variable for retro plots}
 

### 2021-02-22 Paper_Histograms.Rmd
Updated all prepan plots with GLAD/EDGI prepan subset data

@@
 
-GLAD.prepan %>%
+GLAD.prepan_with_EDGI %>%
   ggplot(aes(x = Gender_collapsed)) +
@@
         plot.subtitle = element_text(hjust = 0.5)) +
-  labs(title = "Gender distribution of the GLAD/EDGI prepan cohort",
-       subtitle = paste("N =", dim(GLAD.prepan)[1]),
-       x = "",
+  labs(x = "",
        y = "N participants")
@@
 
-GLAD.prepan %>% 
+GLAD.prepan_with_EDGI %>% 
   ggplot(aes(x = age_category_collapsed)) +
@@
         plot.subtitle = element_text(hjust = 0.5)) +
-  labs(title = "Age distribution of the GLAD/EDGI prepan cohort",
-       subtitle = paste("N =", dim(GLAD.prepan)[1]),
-       x = "",
+  labs(x = "",
        y = "")
@@
 
-GLAD.prepan_ethnicity_plot <- dat.retro %>% 
+GLAD.prepan_ethnicity_plot <- GLAD.prepan_with_EDGI %>% 
   mutate(Ethnicity_collapsed = 
@@
         plot.subtitle = element_text(hjust = 0.5)) +
-  labs(title = "Ethnic distribution of the GLAD/EDGI prepan cohort",
-       subtitle = paste("N =", dim(GLAD.prepan)[1]),
-       x = "",
+  labs(x = "",
        y = "N participants") +
@@
 
-GLAD.prepan %>% 
+GLAD.prepan_with_EDGI %>% 
   ggplot(aes(x = employment_prior_covid)) +
@@
         plot.subtitle = element_text(hjust = 0.5)) +
-  labs(title = "Employment of the GLAD/EDGI prepan cohort",
-       subtitle = paste("N =", dim(GLAD.prepan)[1]),
-       x = "",
+  labs(x = "",
        y = "")
@@
 
-GLAD.prepan <- GLAD.prepan %>% 
+GLAD.prepan_with_EDGI <- GLAD.prepan_with_EDGI %>% 
   mutate(personality_disorder_numeric =
@@
 
-GLAD.prepan_mdd_positive <- GLAD.prepan %>%
+GLAD.prepan_mdd_positive <- GLAD.prepan_with_EDGI %>%
   select(depressive_disorders_numeric) %>% 
@@
 
-GLAD.prepan_anxi_positive <- GLAD.prepan %>%
+GLAD.prepan_anxi_positive <- GLAD.prepan_with_EDGI %>%
   select(anxiety_disorders_numeric) %>% 
@@
 
-GLAD.prepan_ED_positive <- GLAD.prepan %>%
+GLAD.prepan_ED_positive <- GLAD.prepan_with_EDGI %>%
   select(eating_disorders_numeric) %>% 
@@
 
-GLAD.prepan_OCD_positive <- GLAD.prepan %>%
+GLAD.prepan_OCD_positive <- GLAD.prepan_with_EDGI %>%
   select(obsessive_compulsive_disorders_numeric) %>% 
@@
 
-GLAD.prepan_psychosis_positive <- GLAD.prepan %>%
+GLAD.prepan_psychosis_positive <- GLAD.prepan_with_EDGI %>%
   select(psychotic_disorders_numeric) %>% 
@@
 
-GLAD.prepan_ASD_positive <- GLAD.prepan %>%
+GLAD.prepan_ASD_positive <- GLAD.prepan_with_EDGI %>%
   select(autism_spectrum_disorder_numeric) %>% 
@@
 
-GLAD.prepan_ADHD_positive <- GLAD.prepan %>%
+GLAD.prepan_ADHD_positive <- GLAD.prepan_with_EDGI %>%
   select(mhd.attention_deficit_hyperactivity_disorder_numeric) %>% 
@@
 
-GLAD.prepan_PD_positive <- GLAD.prepan %>%
+GLAD.prepan_PD_positive <- GLAD.prepan_with_EDGI %>%
   select(personality_disorder_numeric) %>% 
@@
 
-GLAD.prepan_BD_positive <- GLAD.prepan %>%
+GLAD.prepan_BD_positive <- GLAD.prepan_with_EDGI %>%
   select(mhd.mania_hypomania_bipolar_or_manicdepression_numeric) %>% 
@@
 
-GLAD.prepan_PTSD_positive <- GLAD.prepan %>%
+GLAD.prepan_PTSD_positive <- GLAD.prepan_with_EDGI %>%
   select(mhd.posttraumatic_stress_disorder_ptsd_numeric) %>% 
@@
 
-GLAD.prepan_control_positive <- GLAD.prepan %>%
+GLAD.prepan_control_positive <- GLAD.prepan_with_EDGI %>%
   select(control_numeric) %>% 

### 2021-02-22 Paper_Histograms.Rmd
Updated caption for main retro plot concerning self-defined/non-binary pt's for each cohort

@@
 
+```{r See non-binary/self-defined pt's by sample for caption}
+
+dat.retro %>% 
+  group_by(Sample_plot, Gender_collapsed) %>% 
+  summarise(n = n())
+
+```
+
 ```{r plot age gender ethnicity and employ with plot caption}
@@
           #heights=c(1, 1.2),
-          bottom = textGrob("Non-binary/Self-defined: GLAD/EDGI (243); NBR (39); RAMP (92)", x = 1,
+          bottom = textGrob("Non-binary/Self-defined: GLAD (247); NBR/EDGI (41); RAMP (92)", x = 1,
                             hjust = 1,

### 2021-03-03 Final_analyses_checks_notebook.Rmd
added retrospective prepandemic ttests and glad edgi sensitivity
updated sample composition for final checks

@@
 GLAD.prepan <- dat.prepan %>%
-  filter(Sample == "GLAD" | 
-           Sample == "EDGI")
+  filter(Sample == "GLAD")
 
 NBR.prepan <- dat.prepan %>%
-  filter(Sample == "NBR")
+  filter(Sample == "NBR" | 
+           Sample == "EDGI")
 
@@
 GLAD.retro <- dat.retro %>%
-  filter(Sample == "GLAD" | 
-           Sample == "EDGI")
+  filter(Sample == "GLAD")
 
 NBR.retro <- dat.retro %>%
-  filter(Sample == "NBR")
+  filter(Sample == "NBR" | 
+           Sample == "EDGI")
 
@@
 dat.retro %>%
-  mutate(sample = case_when(Sample == "GLAD" | Sample == "EDGI" ~ "GLAD",
+  mutate(sample = case_when(Sample == "GLAD" ~ "GLAD",
                             Sample == "RAMP" ~ "RAMP",
-                            Sample == "NBR" ~ "NBR")) %>%
+                            Sample == "NBR" | Sample == "EDGI" ~ "NBR")) %>%
   group_by(sample) %>%
@@
 dat.prepan %>%
-  mutate(sample = case_when(Sample == "GLAD" | Sample == "EDGI" ~ "GLAD",
+  mutate(sample = case_when(Sample == "GLAD" ~ "GLAD",
                             Sample == "RAMP" ~ "RAMP",
-                            Sample == "NBR" ~ "NBR")) %>%
+                            Sample == "NBR" | Sample == "EDGI" ~ "NBR")) %>%
   group_by(sample) %>%
@@
 
+Prepandemic compared to retrospective
+(no retrospective ratings for PCL)
+```{r ttest for average scores retro compred to prepan}
+t.test(dat.prepan$gad.sum_score_prepan,dat.prepan$gad.sum_score_retro, paired = T)
+t.test(dat.prepan$phq.sum_score_prepan,dat.prepan$phq.sum_score_retro, paired = T)
+```
+
 ### Average scores by sample
@@
 dat.retro %>%
-  mutate(sample = case_when(Sample == "GLAD" | Sample == "EDGI" ~ "GLAD",
+  mutate(sample = case_when(Sample == "GLAD"  ~ "GLAD",
                             Sample == "RAMP" ~ "RAMP",
-                            Sample == "NBR" ~ "NBR")) %>%
+                            Sample == "NBR" | Sample == "EDGI" ~ "NBR")) %>%
   select(gad.sum_score_base,gad.sum_score_retro, sample) %>%
@@
 dat.retro %>%
-  mutate(sample = case_when(Sample == "GLAD" | Sample == "EDGI" ~ "GLAD",
+  mutate(sample = case_when(Sample == "GLAD" ~ "GLAD",
                             Sample == "RAMP" ~ "RAMP",
-                            Sample == "NBR" ~ "NBR")) %>%
+                            Sample == "NBR"| Sample == "EDGI" ~ "NBR")) %>%
   select(phq.sum_score_base,phq.sum_score_retro, sample) %>%
@@
 dat.prepan %>%
-  mutate(sample = case_when(Sample == "GLAD" | Sample == "EDGI" ~ "GLAD",
+  mutate(sample = case_when(Sample == "GLAD" ~ "GLAD",
                             Sample == "RAMP" ~ "RAMP",
-                            Sample == "NBR" ~ "NBR")) %>%
+                            Sample == "NBR" | Sample == "EDGI" ~ "NBR")) %>%
   select(gad.sum_score_base,gad.sum_score_prepan, sample) %>%
@@
 dat.prepan %>%
-  mutate(sample = case_when(Sample == "GLAD" | Sample == "EDGI" ~ "GLAD",
+  mutate(sample = case_when(Sample == "GLAD"  ~ "GLAD",
                             Sample == "RAMP" ~ "RAMP",
-                            Sample == "NBR" ~ "NBR")) %>%
+                            Sample == "NBR" | Sample == "EDGI" ~ "NBR")) %>%
   select(phq.sum_score_base,phq.sum_score_prepan, sample) %>%
@@
 dat.prepan %>%
-  mutate(sample = case_when(Sample == "GLAD" | Sample == "EDGI" ~ "GLAD",
+  mutate(sample = case_when(Sample == "GLAD" ~ "GLAD",
                             Sample == "RAMP" ~ "RAMP",
-                            Sample == "NBR" ~ "NBR")) %>%
+                            Sample == "NBR"| Sample == "EDGI"  ~ "NBR")) %>%
   select(pcl.sum_score_base,pcl.sum_score_prepan, sample) %>%

### 2021-03-03 Paper_Histograms.Rmd

@@
         axis.text.y = element_text(colour = "black"))
-
-```
-
-####Gender retro pie chart
-
-```{r Prep gender retro pie chart}
-
-dat.retro_gender_pie <- dat.retro %>% 
-  group_by(Sample_plot, Gender_collapsed) %>% 
-  summarise(n = n()) %>% 
-  mutate(percent = 
-           round(n / sum(n) *  100, 1))
-
-```
-
-```{r Gender retro pie chart by sample}
-
-dat.retro_gender_pie %>% 
-  ggplot(aes(x = "", y = percent, fill = Gender_collapsed)) +
-  geom_col(stat = "identity") +
-  coord_polar("y",start=0) +
-  theme_void() +
-  scale_fill_manual(values =  COPINGpalette3) +
-  facet_wrap(~ Sample_plot, nrow = 1) +
-  theme(legend.position = "top",
-        legend.title = element_blank()) +
-  ggrepel::geom_label_repel(aes(label = paste0(percent, "%")),
-            position = position_stack(vjust = 0.6),
-            show.legend = FALSE)
 
@@
 
-####Ethnicity retro pie chart
-
-```{r Prep ethnicity retro pie chart}
-
-dat.retro_ethnicity_pie <- dat.retro %>% 
-  group_by(Sample_plot, Ethnicity_collapsed) %>% 
-  summarise(n = n()) %>% 
-  drop_na() %>% 
-  mutate(percent = 
-           round(n / sum(n) *  100, 1))
-
-```
-
-```{r Ethnicity retro pie chart by sample}
-
-dat.retro_ethnicity_pie <- dat.retro_ethnicity_pie %>% 
-  mutate(Ethnicity_collapsed = 
-           fct_recode(Ethnicity_collapsed,
-             "White" = "European",
-             "Asian or Asian British" = "Asian or Asian British",
-             "Black or Black British" = "African or African British",
-             "Mixed or multiple ethnic origins" = "Mixed or multiple ethnic origins",
-             "Other" = "Other"
-           ))
-
-dat.retro_ethnicity_pie %>% 
-  ggplot(aes(x = "", y = percent, fill = Ethnicity_collapsed)) +
-  geom_col(stat = "identity") +
-  coord_polar("y",start=0) +
-  theme_void() +
-  scale_fill_manual(values =  COPINGpalette5) +
-  facet_wrap(~ Sample_plot, nrow = 1) +
-  theme(legend.position = "top",
-        legend.title = element_blank()) +
-  ggrepel::geom_label_repel(aes(label = paste0(percent, "%")),
-            position = position_stack(vjust = 0.5),
-            show.legend = FALSE)
-
-```
-
 ##Employment
@@
         axis.text.y = element_text(colour = "black"))
-
-```
-
-####Employment retro pie charts
-
-```{r Prep ethnicity retro pie chart}
-
-dat.retro_employ_pie <- dat.retro %>% 
-  group_by(Sample_plot, employment_prior_covid) %>% 
-  summarise(n = n()) %>% 
-  drop_na() %>% 
-  mutate(percent = 
-           round(n / sum(n) *  100, 1))
-
-```
-
-```{r Employment retro pie chart by sample}
-
-dat.retro_employ_pie %>% 
-  ggplot(aes(x = "", y = percent, fill = employment_prior_covid)) +
-  geom_col(stat = "identity") +
-  coord_polar("y",start=0) +
-  theme_void() +
-  scale_fill_manual(values =  COPINGpalette5) +
-  facet_wrap(~ Sample_plot, nrow = 1) +
-  theme(legend.position = "top",
-        legend.title = element_blank()) +
-  ggrepel::geom_label_repel(aes(label = paste0(percent, "%")),
-            position = position_stack(vjust = 0.6),
-            show.legend = FALSE)
 

### 2021-03-03 PANCHANGE_analysis.Rmd
added regression by sample for retrospective

@@
 
-```{r gad.sum violin plot Sample GLAD EDGI combined, fig.height=14, fig.width=8, dpi=300}
+```{r gad.sum violin plot Sample NBR EDGI combined, fig.height=14, fig.width=8, dpi=300}
 dat.long.gad.sum %>%
@@
    mutate(Sample_combined = case_when(
-     Sample == "GLAD" ~ "GLAD and EDGI",
-     Sample == "EDGI" ~ "GLAD and EDGI",
-     Sample == "NBR" ~ "NBR",
-     Sample == "RAMP" ~ "RAMP",)
+     Sample == "GLAD" ~ "GLAD",
+     Sample == "NBR" |  Sample == "EDGI" ~ "NBR and EDGI",
+     Sample == "RAMP" ~ "RAMP")
          ) %>%
@@
      mutate(Sample_combined = case_when(
-     Sample == "GLAD" ~ "GLAD and EDGI",
-     Sample == "EDGI" ~ "GLAD and EDGI",
-     Sample == "NBR" ~ "NBR",
-     Sample == "RAMP" ~ "RAMP",)
+     Sample == "GLAD" ~ "GLAD",
+     Sample == "NBR" |  Sample == "EDGI" ~ "NBR and EDGI",
+     Sample == "RAMP" ~ "RAMP")
          ) %>%
@@
   filter(Time_point != "retro") %>%
-  mutate(sample = case_when(Sample == "GLAD" | Sample == "EDGI" ~ "GLAD and EDGI",
+  mutate(sample = case_when(Sample == "GLAD" ~ "GLAD",
                             Sample == "RAMP" ~ "RAMP",
-                            Sample == "NBR" ~ "NBR")) %>% 
+                            Sample == "NBR" | Sample == "EDGI" ~ "NBR")) %>% 
   mutate(Time_point_renamed = fct_recode(Time_point,
@@
 dat.retro.glad <- dat.retro %>%
-  filter(Sample == "GLAD" | 
+  filter(Sample == "GLAD" )
+
+dat.retro.nbr <- dat.retro %>%
+  filter(Sample == "NBR"| 
            Sample == "EDGI")
-
-dat.retro.nbr <- dat.retro %>%
-  filter(Sample == "NBR")
 
@@
 
+# Retrospective regression models by sample
+
+## GLAD
+```{r gad employment prior covid sensitivity model1b sum_score retro by sample glad}
+# Regression coefficients
+gad_retro_model1b_explan_estimates <- model1b.explan.estimates(outcome = "gad.sum_score_base",
+                                                               explan_var = "gad.sum_score_retro",
+                                                               data_set = "dat.retro.glad")
+kable(gad_retro_model1b_explan_estimates)
+gad_retro_model1b_explan_estimates
+
+```
+
+## NBR
+```{r gad employment prior covid sensitivity model1b sum_score retro by sample nbr}
+# Regression coefficients
+gad_retro_model1b_explan_estimates <- model1b.explan.estimates(outcome = "gad.sum_score_base",
+                                                               explan_var = "gad.sum_score_retro",
+                                                               data_set = "dat.retro.nbr")
+kable(gad_retro_model1b_explan_estimates)
+gad_retro_model1b_explan_estimates
+
+```
+
+## RAMP
+```{r gad employment prior covid sensitivity model1b sum_score retro by sample ramp}
+# Regression coefficients
+gad_retro_model1b_explan_estimates <- model1b.explan.estimates(outcome = "gad.sum_score_base",
+                                                               explan_var = "gad.sum_score_retro",
+                                                               data_set = "dat.retro.ramp")
+kable(gad_retro_model1b_explan_estimates)
+gad_retro_model1b_explan_estimates
+
+```
+
 # frequencies and descriptives in exclusion data
@@
 datgladedgi <- dat.retro %>%
-  filter(Sample == "GLAD" |
-           Sample == "EDGI")
+  filter(Sample == "GLAD")
 

### 2021-03-03 PANCHANGE_analysis.Rmd
updated forest plot styling

@@
                              "Mixed or multiple ethnicities",
-                             "Asian",
-                             "Black",
+                             "Asian or Asian British",
+                             "Black or Black British",
                              "Other",
@@
                              "Retired",
-                             "Time between lockdown and baseline")
+                             "Time")
   ## categories to facet on  
   categories <- c("Intercept",
-                  "Pre-existing mental health (Reference controls)",
-                  "Pre-existing mental health (Reference controls)",
-                  "Pre-existing mental health (Reference controls)",
-                  "Pre-existing mental health (Reference controls)",
-                  "Pre-existing mental health (Reference controls)",
-                  "Pre-existing mental health (Reference controls)",
-                  "Pre-existing mental health (Reference controls)",
-                  "Pre-existing mental health (Reference controls)",
-                  "Pre-existing mental health (Reference controls)",
-                  "Pre-existing mental health (Reference controls)",
-                  "Pre-existing mental health (Reference controls)",
-                  "Pre-existing mental health (Reference controls)",
-                  "Pre-existing mental health (Reference controls)",
-                  "Gender (Reference male)",
-                  "Gender (Reference male)",
-                  "Age (Reference 26-35)",
-                  "Age (Reference 26-35)",
-                  "Age (Reference 26-35)",
-                  "Age (Reference 26-35)",
-                  "Age (Reference 26-35)",
-                  "Age (Reference 26-35)",
-                  "Age (Reference 26-35)",
-                  "Age (Reference 26-35)",
-                  "Ethnicity (Reference White)",
-                  "Ethnicity (Reference White)",
-                  "Ethnicity (Reference White)",
-                  "Ethnicity (Reference White)",
-                  "Employment (Reference employed)",
-                  "Employment (Reference employed)",
-                  "Employment (Reference employed)",
-                  "Employment (Reference employed)",
+                  "Pre-existing mental health",
+                  "Pre-existing mental health",
+                  "Pre-existing mental health",
+                  "Pre-existing mental health",
+                  "Pre-existing mental health",
+                  "Pre-existing mental health",
+                  "Pre-existing mental health",
+                  "Pre-existing mental health",
+                  "Pre-existing mental health",
+                  "Pre-existing mental health",
+                  "Pre-existing mental health",
+                  "Pre-existing mental health",
+                  "Pre-existing mental health",
+                  "Gender",
+                  "Gender",
+                  "Age",
+                  "Age",
+                  "Age",
+                  "Age",
+                  "Age",
+                  "Age",
+                  "Age",
+                  "Age",
+                  "Ethnicity",
+                  "Ethnicity",
+                  "Ethnicity",
+                  "Ethnicity",
+                  "Employment",
+                  "Employment",
+                  "Employment",
+                  "Employment",
                   "Other")
@@
 ### disorder
-```{r forest plot by disorder prepan, fig.height=30, fig.width=50, dpi=120}
+```{r forest plot by disorder prepan, fig.height=40, fig.width=60, dpi=120}
 
@@
 
-```{r forest plot by disorder retro, fig.height=30, fig.width=50, dpi=120}
+```{r forest plot by disorder retro, fig.height=40, fig.width=60, dpi=120}
 
@@
 
-```{r forest plot by disorder no explan, fig.height=30, fig.width=50, dpi=120}
+```{r forest plot by disorder no explan, fig.height=40, fig.width=60, dpi=120}
 
@@
 ### disorder (no PCL)
-```{r forest plot by disorder prepan no pcl, fig.height=30, fig.width=50, dpi=120}
+```{r forest plot by disorder prepan no pcl, fig.height=40, fig.width=60, dpi=120}
 
@@
 
-```{r forest plot by disorder retro no pcl, fig.height=30, fig.width=50, dpi=120}
+```{r forest plot by disorder retro no pcl, fig.height=40, fig.width=60, dpi=120}
 
@@
 ### time point 
-```{r forest plot by time point gad, fig.height=30, fig.width=50, dpi=120}
+```{r forest plot by time point gad, fig.height=40, fig.width=60, dpi=120}
 
@@
 
-```{r forest plot by time point phq, fig.height=30, fig.width=50, dpi=120}
+```{r forest plot by time point phq, fig.height=40, fig.width=60, dpi=120}
 
@@
 
-```{r forest plot by time point pcl, fig.height=30, fig.width=50, dpi=120}
+```{r forest plot by time point pcl, fig.height=40, fig.width=60, dpi=120}
 
@@
 
-```{r forest plot by sample retro only gad, fig.height=30, fig.width=50, dpi=120}
+```{r forest plot by sample retro only gad, fig.height=40, fig.width=60, dpi=120}
 
@@
 
-```{r forest plot by sample retro only phq, fig.height=30, fig.width=50, dpi=120}
+```{r forest plot by sample retro only phq, fig.height=40, fig.width=60, dpi=120}
 
@@
 
-```{r forest plot by sample no explan gad, fig.height=30, fig.width=50, dpi=120}
+```{r forest plot by sample no explan gad, fig.height=40, fig.width=60, dpi=120}
 
@@
 
-```{r forest plot by sample no explan phq, fig.height=30, fig.width=50, dpi=120}
+```{r forest plot by sample no explan phq, fig.height=40, fig.width=60, dpi=120}
 
@@
 
-```{r forest plot by sample no explan pcl, fig.height=30, fig.width=50, dpi=120}
+```{r forest plot by sample no explan pcl, fig.height=40, fig.width=60, dpi=120}
 

### 2021-03-03 FunctionLib/lm_forest.R

@@ -8,12 +8,13 @@ lm.forest <- function(data,title){
              aes(x =RowLabels,y = Estimate,
                  colour = Group)) +
     
-    geom_point(size = 4,
+    geom_point(size = 9,
                position = position_dodge(0.9)) +
     
     geom_hline(aes(fill=Group),
                yintercept =0, 
-               linetype=2)  +
+               linetype=2,
+               size = 3)  +
     
     xlab('Group') + 
     ylab("Estimate (95% Confidence Interval)")  +
@@ -21,21 +22,22 @@ lm.forest <- function(data,title){
     
     geom_errorbar(aes(ymin = LowerBound,
                       ymax = UpperBound),
-                  width = .5,
-                  position = position_dodge(0.9))  + 
+                  width = 1,
+                  position = position_dodge(0.9),
+                  size = 2)  + 
     
     facet_wrap(. ~ Categories,
-               strip.position="left",nrow=5,scales = "free_y") +
+               strip.position="left",nrow=2, scales="free") +
     
     scale_colour_manual(values=COPINGpalette5) +
     
-    theme(plot.title=element_text(size=20,face="bold"),
-          axis.text=element_text(face="bold",size=16,),
-          legend.text=element_text(size=16,),
-          legend.title=element_text(face="bold",size=18,),
-          axis.title.x=element_text(size=28,face="bold"),
+    theme(plot.title=element_text(size=10,face="bold"),
+          axis.text=element_text(face="bold",size=40,),
+          legend.text=element_text(size=40,),
+          legend.title=element_text(face="bold",size=50,),
+          axis.title.x=element_text(size=50,face="bold"),
           axis.title.y=element_blank(),
-          strip.text.y = element_text(angle=180,face="bold",size=20),
+          strip.text.y = element_text(angle=180,face="bold",size=40),
           panel.background = element_blank(),
           strip.background = element_rect(fill = "light grey"),
           panel.border = element_rect(colour = "grey",fill = NA)) +

### 2021-03-08 PANCHANGE_analysis.Rmd
added by sample retro regression for PHQ and PCL

@@
 
-## GLAD
+## GAD
+
+### GLAD
 ```{r gad employment prior covid sensitivity model1b sum_score retro by sample glad}
@@
 
-## NBR
+### NBR
 ```{r gad employment prior covid sensitivity model1b sum_score retro by sample nbr}
@@
 
-## RAMP
+### RAMP
 ```{r gad employment prior covid sensitivity model1b sum_score retro by sample ramp}
@@
 
+## PHQ
+
+### GLAD
+```{r phq employment prior covid sensitivity model1b sum_score retro by sample glad}
+# Regression coefficients
+phq_retro_model1b_explan_estimates <- model1b.explan.estimates(outcome = "phq.sum_score_base",
+                                                               explan_var = "phq.sum_score_retro",
+                                                               data_set = "dat.retro.glad")
+kable(phq_retro_model1b_explan_estimates)
+phq_retro_model1b_explan_estimates
+
+```
+
+### NBR
+```{r phq employment prior covid sensitivity model1b sum_score retro by sample nbr}
+# Regression coefficients
+phq_retro_model1b_explan_estimates <- model1b.explan.estimates(outcome = "phq.sum_score_base",
+                                                               explan_var = "phq.sum_score_retro",
+                                                               data_set = "dat.retro.nbr")
+kable(phq_retro_model1b_explan_estimates)
+phq_retro_model1b_explan_estimates
+
+```
+
+### RAMP
+```{r phq employment prior covid sensitivity model1b sum_score retro by sample ramp}
+# Regression coefficients
+phq_retro_model1b_explan_estimates <- model1b.explan.estimates(outcome = "phq.sum_score_base",
+                                                               explan_var = "phq.sum_score_retro",
+                                                               data_set = "dat.retro.ramp")
+kable(phq_retro_model1b_explan_estimates)
+phq_retro_model1b_explan_estimates
+
+```
+
+## PCL
+
+### GLAD
+```{r pcl employment prior covid sensitivity model1b sum_score retro by sample glad}
+# Regression coefficients
+pcl_retro_model1b_explan_estimates <- model1b.explan.estimates(outcome = "pcl.sum_score_base",
+                                                               explan_var = "pcl.sum_score_retro",
+                                                               data_set = "dat.retro.glad")
+kable(pcl_retro_model1b_explan_estimates)
+pcl_retro_model1b_explan_estimates
+
+```
+
+### NBR
+```{r pcl employment prior covid sensitivity model1b sum_score retro by sample nbr}
+# Regression coefficients
+pcl_retro_model1b_explan_estimates <- model1b.explan.estimates(outcome = "pcl.sum_score_base",
+                                                               explan_var = "pcl.sum_score_retro",
+                                                               data_set = "dat.retro.nbr")
+kable(pcl_retro_model1b_explan_estimates)
+pcl_retro_model1b_explan_estimates
+
+```
+
+### RAMP
+```{r pcl employment prior covid sensitivity model1b sum_score retro by sample ramp}
+# Regression coefficients
+pcl_retro_model1b_explan_estimates <- model1b.explan.estimates(outcome = "pcl.sum_score_base",
+                                                               explan_var = "pcl.sum_score_retro",
+                                                               data_set = "dat.retro.ramp")
+kable(pcl_retro_model1b_explan_estimates)
+pcl_retro_model1b_explan_estimates
+
+```
+
 # frequencies and descriptives in exclusion data

### 2021-03-08 Final_analyses_checks_notebook.Rmd
added sd for change scores to final checks

@@
     toc: yes
-    toc_depth: 2
+    toc_depth: 3
     toc_float:
@@
 
+### change scores
+
+#### Retrospective
+```{r means etc change overall retro}
+
+vars <- dat.retro %>%
+  select(gad.sum_score_base,gad.sum_score_retro,
+         phq.sum_score_base,phq.sum_score_retro) %>%
+  mutate(gad.retro.change = gad.sum_score_base - gad.sum_score_retro,
+         phq.retro.change = phq.sum_score_base - phq.sum_score_retro) %>%
+  select(gad.retro.change,
+         phq.retro.change)
+
+apply(vars, 2, function(x) list(describe(x)))
+
+```
+
+#### Prepandemic
+```{r means etc change overall prepan}
+
+vars <- dat.prepan %>%
+  select(gad.sum_score_base,gad.sum_score_prepan,
+         phq.sum_score_base,phq.sum_score_prepan,
+         pcl.sum_score_base,pcl.sum_score_prepan) %>%
+  mutate(gad.prepan.change = gad.sum_score_base - gad.sum_score_prepan,
+         phq.prepan.change = phq.sum_score_base - phq.sum_score_prepan,
+         pcl.prepan.change = pcl.sum_score_base - pcl.sum_score_prepan) %>%
+  select(gad.prepan.change,
+         phq.prepan.change,
+         pcl.prepan.change)
+
+apply(vars, 2, function(x) list(describe(x)))
+
+```
+
 ## T tests

### 2021-03-09 FunctionLib/lm_forest.R
tweaked figure params for forest plot

@@ -8,7 +8,7 @@ lm.forest <- function(data,title){
              aes(x =RowLabels,y = Estimate,
                  colour = Group)) +
     
-    geom_point(size = 9,
+    geom_point(size = 10,
                position = position_dodge(0.9)) +
     
     geom_hline(aes(fill=Group),
@@ -17,30 +17,33 @@ lm.forest <- function(data,title){
                size = 3)  +
     
     xlab('Group') + 
-    ylab("Estimate (95% Confidence Interval)")  +
+    ylab("\nEstimate (95% Confidence Interval)")  +
     ggtitle(title) +
     
     geom_errorbar(aes(ymin = LowerBound,
                       ymax = UpperBound),
                   width = 1,
                   position = position_dodge(0.9),
-                  size = 2)  + 
+                  size = 3)  + 
     
     facet_wrap(. ~ Categories,
-               strip.position="left",nrow=2, scales="free") +
+               strip.position="left",nrow=6, scales="free_y") +
     
     scale_colour_manual(values=COPINGpalette5) +
     
-    theme(plot.title=element_text(size=10,face="bold"),
-          axis.text=element_text(face="bold",size=40,),
-          legend.text=element_text(size=40,),
-          legend.title=element_text(face="bold",size=50,),
-          axis.title.x=element_text(size=50,face="bold"),
+    theme(plot.title=element_text(size=0,face="bold"),
+          axis.text=element_text(face="bold",size=60,),
+          legend.text=element_text(size=60,),
+          legend.title=element_text(face="bold",size=70,),
+          axis.title.x=element_text(size=80,face="bold"),
           axis.title.y=element_blank(),
-          strip.text.y = element_text(angle=180,face="bold",size=40),
+          strip.text.y = element_text(angle=180,face="bold",size=50),
           panel.background = element_blank(),
           strip.background = element_rect(fill = "light grey"),
           panel.border = element_rect(colour = "grey",fill = NA)) +
+    
+    guides(color = guide_legend(reverse = TRUE)) +
+    
     coord_flip()
   return(p)
   

### 2021-03-09 PANCHANGE_analysis.Rmd
updated figure height and width for forest plots

@@
 ### disorder
-```{r forest plot by disorder prepan, fig.height=40, fig.width=60, dpi=120}
+```{r forest plot by disorder prepan, fig.height=70, fig.width=55, dpi=120}
 
@@
 
-```{r forest plot by disorder retro, fig.height=40, fig.width=60, dpi=120}
+```{r forest plot by disorder retro, fig.height=70, fig.width=55, dpi=120}
 
@@
 
-```{r forest plot by disorder no explan, fig.height=40, fig.width=60, dpi=120}
+```{r forest plot by disorder no explan, fig.height=70, fig.width=55, dpi=120}
 
@@
 ### disorder (no PCL)
-```{r forest plot by disorder prepan no pcl, fig.height=40, fig.width=60, dpi=120}
+```{r forest plot by disorder prepan no pcl, fig.height=70, fig.width=55, dpi=120}
 
@@
 
-```{r forest plot by disorder retro no pcl, fig.height=40, fig.width=60, dpi=120}
+```{r forest plot by disorder retro no pcl, fig.height=70, fig.width=55, dpi=120}
 
@@
 ### time point 
-```{r forest plot by time point gad, fig.height=40, fig.width=60, dpi=120}
+```{r forest plot by time point gad, fig.height=70, fig.width=55, dpi=120}
 
@@
 
-```{r forest plot by time point phq, fig.height=40, fig.width=60, dpi=120}
+```{r forest plot by time point phq, fig.height=70, fig.width=55, dpi=120}
 
@@
 
-```{r forest plot by time point pcl, fig.height=40, fig.width=60, dpi=120}
+```{r forest plot by time point pcl, fig.height=70, fig.width=55, dpi=120}
 
@@
 
-```{r forest plot by sample retro only gad, fig.height=40, fig.width=60, dpi=120}
+```{r forest plot by sample retro only gad, fig.height=70, fig.width=55, dpi=120}
 
@@
 
-```{r forest plot by sample retro only phq, fig.height=40, fig.width=60, dpi=120}
+```{r forest plot by sample retro only phq, fig.height=70, fig.width=55, dpi=120}
 
@@
 
-```{r forest plot by sample no explan gad, fig.height=40, fig.width=60, dpi=120}
+```{r forest plot by sample no explan gad, fig.height=70, fig.width=55, dpi=120}
 
@@
 
-```{r forest plot by sample no explan phq, fig.height=40, fig.width=60, dpi=120}
+```{r forest plot by sample no explan phq, fig.height=70, fig.width=55, dpi=120}
 
@@
 
-```{r forest plot by sample no explan pcl, fig.height=40, fig.width=60, dpi=120}
+```{r forest plot by sample no explan pcl, fig.height=70, fig.width=55, dpi=120}
 

### 2021-03-09 PANCHANGE_analysis.Rmd
hashed out unneeded forest plots for size

@@
 
-lm.forest(plot.dat.disorder,"Predictors of pandemic symptoms")
+#lm.forest(plot.dat.disorder,"Predictors of pandemic symptoms")
 
@@
 
-lm.forest(plot.dat.disorder.prepan.gadphq,"Predictors of pandemic symptoms controlling for prepandemic symptoms")
+#lm.forest(plot.dat.disorder.prepan.gadphq,"Predictors of pandemic symptoms controlling for prepandemic symptoms")
 
@@
 
-lm.forest(plot.dat.disorder.retro.gadphq,"Predictors of pandemic symptoms controlling for retrospective symptoms")
+#lm.forest(plot.dat.disorder.retro.gadphq,"Predictors of pandemic symptoms controlling for retrospective symptoms")
 
@@
 
-lm.forest(plot.dat.time.gad,"Predictors of anxiety during pandemic controlling for retrospective or prepandemic symptoms")
+#lm.forest(plot.dat.time.gad,"Predictors of anxiety during pandemic controlling for retrospective or prepandemic symptoms")
 
@@
 
-lm.forest(plot.dat.time.phq,"Predictors of depression during pandemic controlling for retrospective or prepandemic symptoms")
+#lm.forest(plot.dat.time.phq,"Predictors of depression during pandemic controlling for retrospective or prepandemic symptoms")
 
@@
 
-lm.forest(plot.dat.time.phq,"Predictors of PTSD during pandemic controlling for retrospective or prepandemic symptoms")
+#lm.forest(plot.dat.time.phq,"Predictors of PTSD during pandemic controlling for retrospective or prepandemic symptoms")
 
@@
 
-lm.forest(plot.dat.sample.gad ,"Predictors of anxiety controlling for retrospective symptoms across samples")
+#lm.forest(plot.dat.sample.gad ,"Predictors of anxiety controlling for retrospective symptoms across samples")
 
@@
 
-lm.forest(plot.dat.sample.phq ,"Predictors of depression controlling for retrospective symptoms across samples")
+#lm.forest(plot.dat.sample.phq ,"Predictors of depression controlling for retrospective symptoms across samples")
 
@@
 
-lm.forest(plot.dat.noexplan.sample.gad  ,"Predictors of anxiety across samples")
+#lm.forest(plot.dat.noexplan.sample.gad  ,"Predictors of anxiety across samples")
 
@@
 
-lm.forest(plot.dat.noexplan.sample.phq  ,"Predictors of depression across samples")
+#lm.forest(plot.dat.noexplan.sample.phq  ,"Predictors of depression across samples")
 
@@
 
-lm.forest(plot.dat.noexplan.sample.pcl  ,"Predictors of symptoms of PTSD across samples")
+#lm.forest(plot.dat.noexplan.sample.pcl  ,"Predictors of symptoms of PTSD across samples")
 

### 2021-03-09 PANCHANGE_analysis.Rmd
renamed explanatory variables for disorder symptoms prepandemic
reordered Prepandemic and retrospective predictors to match legend

@@
                "GAD.prepandemic",
+               "PCL.prepandemic",
                "PHQ.prepandemic",
-               "PCL.prepandemic",
                "GAD.retrospective",
-               "PHQ.retrospective",
-               "PCL.retrospective"
+               "PCL.retrospective",
+               "PHQ.retrospective"
                )
@@
 
+plot.dat.disorder <- plot.dat.disorder %>%
+  mutate(RowLabels = recode(RowLabels,
+                            `PCL.prepandemic` = "PCL total prepandemic",
+                            `PHQ.prepandemic` = "PHQ total prepandemic",
+                            `GAD.prepandemic` = "GAD total prepandemic"
+                            ))
+
 # by sample

### 2021-03-09 PANCHANGE_analysis.Rmd
relabelled incorrect employment variables for forest plots

@@
                              "Key worker",
+                             "Retired",
+                             "Student",
                              "Unemployed",
-                             "Student",
-                             "Retired",
                              "Time")
@@
                              "Key worker",
+                             "Retired",
+                             "Student",
                              "Unemployed",
-                             "Student",
-                             "Retired",
                              "Time between lockdown and baseline")

### 2021-03-09 Final_analyses_checks_notebook.Rmd
added SD for GLAD only retrospective in final analysis checks html

@@
 #### Retrospective
+GLAD only
 ```{r means etc change overall retro}
@@
 vars <- dat.retro %>%
+  filter(Sample == "GLAD") %>%
   select(gad.sum_score_base,gad.sum_score_retro,

### 2021-03-09 PANCHANGE_analysis.Rmd
reordered explanatory variables for forest plots to match legend

@@
 plot.dat.disorder.prepan <- rbind(gad.prepan.lm.for.plot,
-                                  phq.prepan.lm.for.plot,
-                                  pcl.prepan.lm.for.plot)
+                                  pcl.prepan.lm.for.plot,
+                                  phq.prepan.lm.for.plot)
 
 plot.dat.disorder.retro <- rbind(gad.retro.lm.for.plot,
-                                  phq.retro.lm.for.plot,
-                                  pcl.retro.lm.for.plot)
+                                  pcl.retro.lm.for.plot,
+                                 phq.retro.lm.for.plot)
 
@@
 
-plot.dat.disorder <- plot.dat.disorder %>%
+# by sample
+
+plot.dat.noexplan.sample.gad <- rbind(gad.lm.for.plot.GLAD,
+                             gad.lm.for.plot.NBR,
+                             gad.lm.for.plot.RAMP)
+
+plot.dat.noexplan.sample.phq <- rbind(phq.lm.for.plot.GLAD,
+                             phq.lm.for.plot.NBR,
+                             phq.lm.for.plot.RAMP)
+
+plot.dat.noexplan.sample.pcl <- rbind(pcl.lm.for.plot.GLAD,
+                             pcl.lm.for.plot.NBR,
+                             pcl.lm.for.plot.RAMP)
+
+plot.dat.disorder.prepan <- plot.dat.disorder.prepan %>%
   mutate(RowLabels = recode(RowLabels,
@@
                             `PHQ.prepandemic` = "PHQ total prepandemic",
-                            `GAD.prepandemic` = "GAD total prepandemic"
-                            ))
-
-# by sample
-
-plot.dat.noexplan.sample.gad <- rbind(gad.lm.for.plot.GLAD,
-                             gad.lm.for.plot.NBR,
-                             gad.lm.for.plot.RAMP)
-
-plot.dat.noexplan.sample.phq <- rbind(phq.lm.for.plot.GLAD,
-                             phq.lm.for.plot.NBR,
-                             phq.lm.for.plot.RAMP)
-
-plot.dat.noexplan.sample.pcl <- rbind(pcl.lm.for.plot.GLAD,
-                             pcl.lm.for.plot.NBR,
-                             pcl.lm.for.plot.RAMP)
+                            `GAD.prepandemic` = "GAD total prepandemic"))
 

### 2021-03-16 Paper_Histograms.Rmd
Removed figure caption from final retro age, gender, ethincity employment plot

@@
           layout_matrix = retro_matrix, 
-          nrow = 2,
-          #heights=c(1, 1.2),
-          bottom = textGrob("Non-binary/Self-defined: GLAD (247); NBR/EDGI (41); RAMP (92)", x = 1,
-                            hjust = 1,
-                            gp = gpar(fontface = 3L, fontsize = 9)))
-
-```
+          nrow = 2)
+
+```

### 2021-03-16 Paper_Histograms.Rmd
Added '2' above the retro gender plot for the link to the second figure caption

@@
   theme(axis.text.x = element_text(colour = "black"),
-        axis.text.y = element_text(colour = "black"))
+        axis.text.y = element_text(colour = "black")) +
+  geom_text(x = Inf, y = Inf, label = "2", hjust = 1, vjust = 1)
 

### 2021-03-16 Paper_Histograms.Rmd
Changed 'OCDRs' to 'OCRDs' on the retro mental health diagnosis by sample plot

@@
   group_by(Sample_plot) %>% 
-  summarise("OCDRs" = n())
+  summarise("OCRDs" = n())
 
@@
 dat.retro_positive_diagnosis_by_sample <- dat.retro_positive_diagnosis_by_sample %>% 
-  gather('Depressive disorders', 'Anxiety disorders', 'Eating disorders', 'OCDRs', 'Psychotic disorders', 'ASD', 'ADHD', 'Personality disorders', 'Bipolar disorders', 'PTSD', 'No diagnosis', key = "Diagnosis", value = positive_n)
+  gather('Depressive disorders', 'Anxiety disorders', 'Eating disorders', 'OCRDs', 'Psychotic disorders', 'ASD', 'ADHD', 'Personality disorders', 'Bipolar disorders', 'PTSD', 'No diagnosis', key = "Diagnosis", value = positive_n)
 

### 2021-04-12 Final_analyses_checks_notebook.Rmd
checked proportion of people crossing diagnostic thresholds

@@
 
-alldat <-  readRDS(file = paste0(data_path, "/four_cohorts_variables_exclusion.rds"))
+alldat <-  readRDS(file = paste0(data_path, "four_cohorts_variables_exclusion.rds"))
 
@@
 ```
+
+# change in thresholds in GLAD only
+
+##1. Proportion scoring ≥10 on GAD-7 prepandemic
+
+```{r GLAD prop GAD >10 prepandemic}
+
+GLAD.prepan.GAD10 <-  GLAD.prepan %>%
+  filter(gad.sum_score_prepan >=10) %>%
+  count()
+
+GLAD.base <-  GLAD.prepan %>%
+  filter(!is.na(gad.sum_score_prepan)) %>%
+  count()
+
+print("proportion of GLAD sample with a GAD 7 score >= 10 prepandemic (i.e. and GLAD baseline)")
+GLAD.prepan.GAD10 / GLAD.base
+
+```
+
+## 2. Proportion scoring ≥10 on GAD-7 current/baseline
+
+```{r GLAD prop GAD >10 pandemic baseline}
+
+GLAD.base.GAD10 <-  GLAD.prepan %>%
+  filter(gad.sum_score_base >=10) %>%
+  count()
+
+GLAD.base <-  GLAD.prepan %>%
+  filter(!is.na(gad.sum_score_base)) %>%
+  count()
+
+print("proportion of GLAD sample with a GAD 7 score >= 10 at the pandemic baseline")
+GLAD.base.GAD10 / GLAD.base
+
+```
+## 3. Proportion scoring ≥ 10 on PHQ-9 prepandemic
+
+```{r GLAD prop PHQ >10 prepandemic}
+
+GLAD.prepan.PHQ9 <-  GLAD.prepan %>%
+  filter(phq.sum_score_prepan >=9) %>%
+  count()
+
+GLAD.base <-  GLAD.prepan %>%
+  filter(!is.na(phq.sum_score_prepan)) %>%
+  count()
+
+print("proportion of GLAD sample with a PHQ 9 score >= 10 at the pandemic baseline")
+GLAD.prepan.PHQ9 / GLAD.base
+
+```
+
+## 4. Proportion scoring ≥ 10 on PHQ-9 current/baseline
+
+```{r GLAD prop PHQ >10 pandemic baseline}
+
+GLAD.base.PHQ9 <-  GLAD.prepan %>%
+  filter(phq.sum_score_base >=9) %>%
+  count()
+
+GLAD.base <-  GLAD.prepan %>%
+  filter(!is.na(phq.sum_score_base)) %>%
+  count()
+
+print("proportion of GLAD sample with a PHQ 9 score >= 10 at the pandemic baseline")
+GLAD.base.PHQ9 / GLAD.base
+
+```
+## 5. Proportion scoring ≥ 14 on PCL-6 prepandemic
+
+```{r GLAD prop PCL >14 pre pandemic}
+
+GLAD.prepan.PCL <-  GLAD.prepan %>%
+  filter(pcl.sum_score_prepan >=14) %>%
+  count()
+
+GLAD.base <-  GLAD.prepan %>%
+  filter(!is.na(pcl.sum_score_prepan)) %>%
+  count()
+
+print("proportion of GLAD sample with a PCL score >= 14 at the pandemic baseline")
+GLAD.prepan.PCL / GLAD.base
+
+```
+
+## 6. Proportion scoring ≥ 14 on PCL-6 current/baseline
+
+```{r GLAD prop PCL >14 pandemic baseline}
+
+GLAD.base.PCL <-  GLAD.prepan %>%
+  filter(pcl.sum_score_base >=14) %>%
+  count()
+
+GLAD.base <-  GLAD.prepan %>%
+  filter(!is.na(pcl.sum_score_base)) %>%
+  count()
+
+print("proportion of GLAD sample with a PCL score >= 14 at the pandemic baseline")
+GLAD.base.PCL / GLAD.base
+
+```
+
+## RAMP PCL endorsement rate at pandemic baseline
+
+```{r}
+
+RAMP.retro.PCL <-  RAMP.retro %>%
+  filter(pcl.sum_score_base >=14) %>%
+  count()
+
+RAMP.base <-  RAMP.retro %>%
+  filter(!is.na(pcl.sum_score_base)) %>%
+  count()
+
+print("proportion of RAMP sample with a PCL score >= 14 at the pandemic baseline")
+RAMP.retro.PCL / RAMP.base
+
+```
+
+## NBR PCL endorsement rate at pandemic baseline
+
+```{r}
+
+NBR.retro.PCL <-  NBR.retro %>%
+  filter(pcl.sum_score_base >=14) %>%
+  count()
+
+NBR.base <-  NBR.retro %>%
+  filter(!is.na(pcl.sum_score_base)) %>%
+  count()
+
+print("proportion of NBR sample with a PCL score >= 14 at the pandemic baseline")
+NBR.retro.PCL / NBR.base
+
+```

### 2021-04-12 Paper_Histograms.Rmd

@@
   geom_text(aes(label = n),
-            size = 3,
+            size = 4.5,
             position = position_dodge(width=0.9), 
-            vjust=-0.25)
+            vjust=-0.25) +
+  theme(text=element_text(size=15))
 

### 2021-04-12 Final_analyses_checks_notebook.Rmd
resave

@@
 GLAD.prepan.PHQ9 <-  GLAD.prepan %>%
-  filter(phq.sum_score_prepan >=9) %>%
+  filter(phq.sum_score_prepan >=10) %>%
   count()
@@
 GLAD.base.PHQ9 <-  GLAD.prepan %>%
-  filter(phq.sum_score_base >=9) %>%
+  filter(phq.sum_score_base >=10) %>%
   count()

### 2021-04-12 PANCHANGE_analysis.Rmd
changed forest plot legend for PCL to PCL-6

@@
 
-lmoutput_format(pcl.prepan.lm,"PCL.prepandemic","PCL", "pcl.prepan.lm.for.plot")
-lmoutput_format(pcl.retro.lm,"PCL.retrospective","PCL", "pcl.retro.lm.for.plot")
+lmoutput_format(pcl.prepan.lm,"PCL.prepandemic","PCL-6", "pcl.prepan.lm.for.plot")
+lmoutput_format(pcl.retro.lm,"PCL.retrospective","PCL-6", "pcl.retro.lm.for.plot")
 
@@
 lmoutput_format_noexplan(phq.lm.noexplan,"PHQ-9", "phq.lm.for.plot")
-lmoutput_format_noexplan(pcl.lm.noexplan,"PCL", "pcl.lm.for.plot")
+lmoutput_format_noexplan(pcl.lm.noexplan,"PCL-6", "pcl.lm.for.plot")
 
@@
 
+plot.dat.disorder.retro <- plot.dat.disorder.retro %>%
+  mutate(RowLabels = recode(RowLabels,
+                            `PCL.retrospective` = "PCL total retrospective",
+                            `PHQ.retrospective` = "PHQ total retrospective",
+                            `GAD.retrospective` = "GAD total retrospective"))
+
 ```

### 2021-04-23 PANCHANGE_analysis.Rmd
added sensitivity analyses dropping NBR from retro regressions

@@
 
-#SB Hashing out this chunk of code as it is not included in our final analysis and is currently breaking the code.
 ```{r gad model0a absolute whole sample}
@@
 ```
-##KT
 
@@
 ```
+
+## Sensitivity: retrospective regression (excluding NBR)
+
+retrospective dataset, dropping NBR (which includes edgi)
+```{r make no nbr dat}
+
+dat.retro.noNBR <- dat.retro %>%
+  filter(Sample != "NBR" & 
+           Sample != "EDGI")
+
+```
+
+### GAD
+#### Original
+```{r retro original gad}
+
+gad_retro_model1b_explan_estimates <- model1b.explan.estimates(outcome = "gad.sum_score_base",
+                                                               explan_var = "gad.sum_score_retro",
+                                                               data_set = "dat.retro")
+kable(gad_retro_model1b_explan_estimates)
+gad_retro_model1b_explan_estimates
+
+```
+
+#### sensitivity
+```{r retro sensitivty no NBR gad}
+
+gad_retro_model1b_explan_estimates <- model1b.explan.estimates(outcome = "gad.sum_score_base",
+                                                               explan_var = "gad.sum_score_retro",
+                                                               data_set = "dat.retro.noNBR")
+kable(gad_retro_model1b_explan_estimates)
+gad_retro_model1b_explan_estimates
+
+```
+
+### PHQ
+#### Original
+```{r retro original phq}
+
+phq_retro_model1b_explan_estimates <- model1b.explan.estimates(outcome = "phq.sum_score_base",
+                                                               explan_var = "phq.sum_score_retro",
+                                                               data_set = "dat.retro")
+kable(phq_retro_model1b_explan_estimates)
+phq_retro_model1b_explan_estimates
+
+```
+
+#### sensitivity
+```{r retro sensitivty no NBR phq}
+
+phq_retro_model1b_explan_estimates <- model1b.explan.estimates(outcome = "phq.sum_score_base",
+                                                               explan_var = "phq.sum_score_retro",
+                                                               data_set = "dat.retro.noNBR")
+kable(phq_retro_model1b_explan_estimates)
+phq_retro_model1b_explan_estimates
+
+```
+
+### PCL
+#### Original
+```{r retro original pcl}
+
+pcl_retro_model1b_explan_estimates <- model1b.explan.estimates(outcome = "pcl.sum_score_base",
+                                                               explan_var = "pcl.sum_score_retro",
+                                                               data_set = "dat.retro")
+kable(pcl_retro_model1b_explan_estimates)
+pcl_retro_model1b_explan_estimates
+
+```
+
+#### sensitivity
+```{r retro sensitivty no NBR pcl}
+
+pcl_retro_model1b_explan_estimates <- model1b.explan.estimates(outcome = "pcl.sum_score_base",
+                                                               explan_var = "pcl.sum_score_retro",
+                                                               data_set = "dat.retro.noNBR")
+kable(pcl_retro_model1b_explan_estimates)
+pcl_retro_model1b_explan_estimates
+
+```

### 2021-04-27 PANCHANGE_analysis.Rmd
new forest functions with adaptations ro C rayner for spacing

@@
 
-Load packages
+#Load packages
 ```{r Load packages}
@@
   categories <- c("Intercept",
-                  "Pre-existing mental health (Reference controls)",
-                  "Pre-existing mental health (Reference controls)",
-                  "Pre-existing mental health (Reference controls)",
-                  "Pre-existing mental health (Reference controls)",
-                  "Pre-existing mental health (Reference controls)",
-                  "Pre-existing mental health (Reference controls)",
-                  "Pre-existing mental health (Reference controls)",
-                  "Pre-existing mental health (Reference controls)",
-                  "Pre-existing mental health (Reference controls)",
-                  "Pre-existing mental health (Reference controls)",
-                  "Pre-existing mental health (Reference controls)",
-                  "Pre-existing mental health (Reference controls)",
-                  "Gender (Reference male)",
-                  "Gender (Reference male)",
-                  "Age (Reference 26-35)",
-                  "Age (Reference 26-35)",
-                  "Age (Reference 26-35)",
-                  "Age (Reference 26-35)",
-                  "Age (Reference 26-35)",
-                  "Age (Reference 26-35)",
-                  "Age (Reference 26-35)",
-                  "Age (Reference 26-35)",
-                  "Ethnicity (Reference White)",
-                  "Ethnicity (Reference White)",
-                  "Ethnicity (Reference White)",
-                  "Ethnicity (Reference White)",
-                  "Employment (Reference employed)",
-                  "Employment (Reference employed)",
-                  "Employment (Reference employed)",
-                  "Employment (Reference employed)",
+                  "Pre-existing mental health",
+                  "Pre-existing mental health",
+                  "Pre-existing mental health",
+                  "Pre-existing mental health",
+                  "Pre-existing mental health",
+                  "Pre-existing mental health",
+                  "Pre-existing mental health",
+                  "Pre-existing mental health",
+                  "Pre-existing mental health",
+                  "Pre-existing mental health",
+                  "Pre-existing mental health",
+                  "Pre-existing mental health",
+                  "Gender",
+                  "Gender",
+                  "Age",
+                  "Age",
+                  "Age",
+                  "Age",
+                  "Age",
+                  "Age",
+                  "Age",
+                  "Age",
+                  "Ethnicity",
+                  "Ethnicity",
+                  "Ethnicity",
+                  "Ethnicity",
+                  "Employment",
+                  "Employment",
+                  "Employment",
+                  "Employment",
                   "Other")
@@
 ## Forest plots
+
+### palette
+
+```{r palette for forest}
+
+forestpal <- c("#993955","#2E5077","#E6C229")
+
+```
 ### disorder
+title: Predictors of pandemic symptoms controlling for prepandemic symptoms
 ```{r forest plot by disorder prepan, fig.height=70, fig.width=55, dpi=120}
 
-lm.forest(plot.dat.disorder.prepan,"Predictors of pandemic symptoms controlling for prepandemic symptoms")
-
-```
-
+plot_text_size=60
+
+plot_grid(
+  plot_grid(
+    lm.forest(plot.dat.disorder.prepan %>% filter(Categories=="Pre-existing mental health"), title="",colourpal=forestpal),
+    lm.forest(plot.dat.disorder.prepan %>% filter(Categories=="Gender"), title="",colourpal=forestpal),
+    lm.forest(plot.dat.disorder.prepan %>% filter(Categories=="Age"), title="",colourpal=forestpal),
+    lm.forest(plot.dat.disorder.prepan %>% filter(Categories=="Ethnicity"), title="",colourpal=forestpal),
+    lm.forest(plot.dat.disorder.prepan %>% filter(Categories=="Employment"), title="",colourpal=forestpal),
+    lm.forest(plot.dat.disorder.prepan %>% filter(Categories=="Other"), title="",colourpal=forestpal) +
+      theme(
+        axis.title.x = element_text(size = plot_text_size),
+        axis.text.x = element_text(size = plot_text_size)),
+
+    align = "v",
+    nrow = 6,
+    rel_heights = c(15/36, 2/36, 8/36, 4/36, 5/36, 2/36),
+    hjust = c(0,0,0,0,0,0),
+    vjust = c(2,0,0,0,0,0)
+  ),
+  as_ggplot(cowplot::get_legend(
+    lm.forest(data %>% filter(Categories=="Other"), title="") +
+      theme(legend.position = c(0.65,0.5),
+            legend.direction = "horizontal",
+            legend.box = "horizontal",
+            legend.box.just = "centre",
+            legend.title = element_blank(),
+            legend.text = element_text(size = plot_text_size)) +
+      guides(color = guide_legend(order = 1, reverse = T))
+  )),
+  ncol= 1,
+  nrow = 2,
+  rel_heights = c(1, 0.05)
+)
+
+```
+
+Predictors of pandemic symptoms controlling for retrospective symptoms
 ```{r forest plot by disorder retro, fig.height=70, fig.width=55, dpi=120}
 
-lm.forest(plot.dat.disorder.retro,"Predictors of pandemic symptoms controlling for retrospective symptoms")
+plot_grid(
+  plot_grid(
+    lm.forest(plot.dat.disorder.retro %>% filter(Categories=="Preexisting mental health"), title="",colourpal=forestpal),
+    lm.forest(plot.dat.disorder.retro %>% filter(Categories=="Gender"), title="",colourpal=forestpal),
+    lm.forest(plot.dat.disorder.retro %>% filter(Categories=="Age"), title="",colourpal=forestpal),
+    lm.forest(plot.dat.disorder.retro %>% filter(Categories=="Ethnicity"), title="",colourpal=forestpal),
+    lm.forest(plot.dat.disorder.retro %>% filter(Categories=="Employment"), title="",colourpal=forestpal),
+    lm.forest(plot.dat.disorder.retro %>% filter(Categories=="Other"), title="",colourpal=forestpal) +
+      theme(
+        axis.title.x = element_text(size = plot_text_size),
+        axis.text.x = element_text(size = plot_text_size)),
+
+    align = "v",
+    nrow = 6,
+    rel_heights = c(15/36, 2/36, 8/36, 4/36, 5/36, 2/36),
+    hjust = c(0,0,0,0,0,0),
+    vjust = c(2,0,0,0,0,0)
+  ),
+  as_ggplot(cowplot::get_legend(
+    lm.forest(data %>% filter(Categories=="Other"), title="") +
+      theme(legend.position = c(0.65,0.5),
+            legend.direction = "horizontal",
+            legend.box = "horizontal",
+            legend.box.just = "centre",
+            legend.title = element_blank(),
+            legend.text = element_text(size = plot_text_size)) +
+      guides(color = guide_legend(order = 1, reverse = T))
+  )),
+  ncol= 1,
+  nrow = 2,
+  rel_heights = c(1, 0.05)
+)
 

### 2021-04-27 FunctionLib/lm_forest.R

@@ -1,22 +1,21 @@
 # Function to create forest plots with different grouping sets using formatted data
 # KLPurves
 
-
-lm.forest <- function(data,title){
+lm.forest <- function(data,title,pointsize=10,linesize=3,errorsize=3,axistext=60,axistitle=80,legtitle=70,stripsize=50,colourpal=COPINGpalette5){
   
   p = ggplot(data=data,
              aes(x =RowLabels,y = Estimate,
                  colour = Group)) +
     
-    geom_point(size = 10,
+    geom_point(size = pointsize,
                position = position_dodge(0.9)) +
     
     geom_hline(aes(fill=Group),
-               yintercept =0, 
+               yintercept =0,
                linetype=2,
-               size = 3)  +
+               size = linesize)  +
     
-    xlab('Group') + 
+    xlab('Group') +
     ylab("\nEstimate (95% Confidence Interval)")  +
     ggtitle(title) +
     
@@ -24,27 +23,33 @@ lm.forest <- function(data,title){
                       ymax = UpperBound),
                   width = 1,
                   position = position_dodge(0.9),
-                  size = 3)  + 
+                  size = errorsize)  +
     
-    facet_wrap(. ~ Categories,
-               strip.position="left",nrow=6, scales="free_y") +
+    #facet_wrap(. ~ Categories,
+    #           strip.position="left",nrow=6, scales="free_y") +
     
-    scale_colour_manual(values=COPINGpalette5) +
+    facet_grid(. ~ Categories, strip.position="left", drop = TRUE) +
     
-    theme(plot.title=element_text(size=0,face="bold"),
-          axis.text=element_text(face="bold",size=60,),
-          legend.text=element_text(size=60,),
-          legend.title=element_text(face="bold",size=70,),
-          axis.title.x=element_text(size=80,face="bold"),
+    scale_colour_manual(values=colourpal) +
+    
+    theme(plot.title=element_blank(), #element_text(size=0,face="bold"),
+          axis.text=element_text(face="bold",size=axistext,),
+          legend.text=element_text(size=axistext,),
+          legend.title=element_text(face="bold",size=legtitle,),
+          legend.position = "none",
+          axis.title.x=element_blank(), #element_text(size=axistitle,face="bold"),
           axis.title.y=element_blank(),
-          strip.text.y = element_text(angle=180,face="bold",size=50),
+          strip.text.y = element_text(angle=180,face="bold",size=stripsize),
[…]

### 2021-04-27 FunctionLib/lm_forest.R
knitted new version with updated forest plots

@@ -1,17 +1,20 @@
 # Function to create forest plots with different grouping sets using formatted data
 # KLPurves
 
-lm.forest <- function(data,title,pointsize=10,linesize=3,errorsize=3,axistext=60,axistitle=80,legtitle=70,stripsize=50,colourpal=COPINGpalette5){
+lm.forest <- function(data,title,pointsize=10,linesize=3,errorsize=3,
+                      axistext=60,axistitle=80,legtitle=70,stripsize=50,
+                      colourpal=COPINGpalette5,lowlim=-3,uplim=4,dodge=0.5)
   
+  {
+
   p = ggplot(data=data,
              aes(x =RowLabels,y = Estimate,
                  colour = Group)) +
     
     geom_point(size = pointsize,
-               position = position_dodge(0.9)) +
+               position = position_dodge(dodge)) +
     
-    geom_hline(aes(fill=Group),
-               yintercept =0,
+    geom_hline(yintercept =0,
                linetype=2,
                size = linesize)  +
     
@@ -22,15 +25,16 @@ lm.forest <- function(data,title,pointsize=10,linesize=3,errorsize=3,axistext=60
     geom_errorbar(aes(ymin = LowerBound,
                       ymax = UpperBound),
                   width = 1,
-                  position = position_dodge(0.9),
+                  position = position_dodge(dodge),
                   size = errorsize)  +
     
     #facet_wrap(. ~ Categories,
     #           strip.position="left",nrow=6, scales="free_y") +
     
-    facet_grid(. ~ Categories, strip.position="left", drop = TRUE) +
+    facet_grid(. ~ Categories,  drop = TRUE) +
     
     scale_colour_manual(values=colourpal) +
+    scale_y_continuous(limits=c(lowlim,uplim)) +
     
     theme(plot.title=element_blank(), #element_text(size=0,face="bold"),
           axis.text=element_text(face="bold",size=axistext,),

### 2021-04-27 FunctionLib/lm_forest.R
minor change to test new authentication token

@@ -6,7 +6,6 @@ lm.forest <- function(data,title,pointsize=10,linesize=3,errorsize=3,
                       colourpal=COPINGpalette5,lowlim=-3,uplim=4,dodge=0.5)
   
   {
-
   p = ggplot(data=data,
              aes(x =RowLabels,y = Estimate,
                  colour = Group)) +

### 2021-05-14 PANCHANGE_analysis.Rmd

@@
   as_ggplot(cowplot::get_legend(
-    lm.forest(data %>% filter(Categories=="Other"), title="") +
+    lm.forest(plot.dat.disorder.prepan %>% filter(Categories=="Other"), title="",colourpal=forestpal) +
       theme(legend.position = c(0.65,0.5),
@@
   plot_grid(
-    lm.forest(plot.dat.disorder.retro %>% filter(Categories=="Preexisting mental health"), title="",colourpal=forestpal),
+    lm.forest(plot.dat.disorder.retro %>% filter(Categories=="Pre-existing mental health"), title="",colourpal=forestpal),
     lm.forest(plot.dat.disorder.retro %>% filter(Categories=="Gender"), title="",colourpal=forestpal),
@@
   as_ggplot(cowplot::get_legend(
-    lm.forest(data %>% filter(Categories=="Other"), title="") +
+    lm.forest(plot.dat.disorder.retro %>% filter(Categories=="Other"), title="",colourpal=forestpal) +
       theme(legend.position = c(0.65,0.5),
